### 2014-12-15 paper/RDF validation requirements/RDF validation requirements.tex
initial commit

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}

% allows for temporary adjustment of side margins
\usepackage{chngpage}

% just makes the table prettier (see \toprule, \bottomrule, etc. commands below)
\usepackage{booktabs}

\usepackage[utf8]{inputenc}

% URL handling
\usepackage{url}
\urlstyle{same}

% Todos
%\usepackage[colorinlistoftodos]{todonotes}
%\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
%\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}

%\usepackage{makeidx}  % allows for indexgeneration

%\usepackage{amsmath}
\usepackage{amsmath, amssymb}
\usepackage{mathabx}

% monospace within text
\newcommand{\ms}[1]{\texttt{#1}}

% examples
\usepackage{fancyvrb}
\DefineVerbatimEnvironment{ex}{Verbatim}{numbers=left,numbersep=2mm,frame=single,fontsize=\scriptsize}
\DefineVerbatimEnvironment{dl}{}{fontsize=\scriptsize}

\newenvironment{gcotable-old}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}\linebreak
  \begin{tabular}{l|l|l|l|l|l}
  \hline
  \textbf{c. type} & \textbf{context concept} & \textbf{p. list} & \textbf{concepts} & \textbf{c. element} & \textbf{c. value} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{gcotable}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
  \begin{tabular}{l|l|l|l|l|l|l}
  \hline
  \textbf{c. type} & \textbf{context concept} & \textbf{left p. list} & \textbf{right p. list} & \textbf{concepts} & \textbf{c. element} & \textbf{c. value} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{DL}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
  \begin{tabular}{l}
	\textbf{DL:} \\

}{
  \end{tabular}
  \linebreak
}

\newenvironment{evaluation}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
  \begin{tabular}{l|c|c|c|c|c}
  \hline
  \textbf{constraint} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\usepackage{xspace}
% Einfache und doppelte Anfuehrungszeichen
\newcommand{\qs}{``} 
\newcommand{\qe}{''\xspace} 
\newcommand{\sqs}{`} 
\newcommand{\sqe}{'\xspace}

% checkmark
\usepackage{tikz}
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}

% Xs
\usepackage{pifont}

% Tabellenabstände kleiner
\setlength{\intextsep}{10pt} % Vertical space above & below [h] floats
\setlength{\textfloatsep}{10pt} % Vertical space below (above) [t] ([b]) floats
% \setlength{\abovecaptionskip}{0pt}
% \setlength{\belowcaptionskip}{0pt}

\usepackage{tabularx}
\newcommand{\hr}{\hline\noalign{\smallskip}} % für die horizontalen linien in tabellen

% pipe
%\usepackage[T1]{fontenc}

% Todos
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\tb}[1]{\todo[size=\small, color=blue!40]{\textbf{Thomas:} #1}}
\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
\newcommand{\an}[1]{\todo[size=\small, color=green!40]{\textbf{Andreas:} #1}}
\newcommand{\er}[1]{\todo[size=\small, color=red!40]{\textbf{Erman:} #1}}

\setcounter{secnumdepth}{5}

\begin{document}

%
%
\title{XXXXX}
%
\titlerunning{XXXXX}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{XXXXX\inst{1} \and XXXXX\inst{2}}
%
\authorrunning{XXXXX} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\institute{XXXXX\\
\email{XXXXX},\\ 
\and
XXXXX \\
\email{XXXXX} 
}

\maketitle              % typeset the title of the contribution

\begin{abstract}

\keywords{..}
\end{abstract}
%

% ---------------

\section{Motivation}

\begin{itemize}
	\item mappings from RDF validation requirements (more specifically RDF constraint formulation requirements) to DL
	\item mappings from RDF validation requirements (more specifically RDF constraint formulation requirements) to generic constraints (expressed by generic constraint language)
\end{itemize}

\tb{I think we should provide mappings to DL directly in the requirements chapters and not just in 1 table at the end of the paper}

\section{Subsumption}

requirement:

\begin{itemize}
	\item R-100-SUBSUMPTION
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item DL terminology: concept inclusion
\end{itemize}

\subsection{Simple Example}

\begin{DL}
Mother $\sqsubseteq$ Parent 
\end{DL}

\begin{itemize}
	\item all mothers are parents
  \item the concept Mother is subsumed by the concept Parent
\end{itemize}

\begin{gcotable}
class & Mother & - & - & Parent & $\sqsubseteq$ \\
\end{gcotable}

\subsection{Simple Example}

\begin{itemize}
	\item Jedis feel the force 
\end{itemize}

\begin{ex}
# DSP
# ---
-
\end{ex}

\begin{ex}
# OWL2
# ----
:Jedi rdfs:subClassOf :FeelingForce .
\end{ex}

\begin{ex}
# ReSh
# ----
the extension ext:extendsShape may be used
\end{ex}

\begin{ex}
# ShEx
# ----
:FeelingForce {
    :feelingForce (true) }
:Jedi {
    & :FeelingForce ,
    :attitute ('good') }
\end{ex}

\begin{ex}
# data
# ----
:Yoda 
    :feelingForce true ;
    :attitute 'good' .
\end{ex}

\begin{DL}
:Jedi $\sqsubseteq$ :FeelingForce
\end{DL}

\subsection{Complex Example}

\begin{DL}
Rich $\sqsubseteq$ $\neg$ Poor 
\end{DL}

\begin{gcotable}
class & $\neg$ Poor & - & - & Poor & $\neg$ \\
class & Rich & - & - & $\neg$ Poor & $\sqsubseteq$ \\
\end{gcotable}

\section{Class Equivalence}

requirement:

\begin{itemize}
	\item R-3-EQUIVALENT-CLASSES
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item Concept equivalence asserts that two concepts have the same instances \cite{Kroetzsch2012}
  \item While synonyms are an obvious example of equivalent concepts, in practice one more
often uses concept equivalence to give a name to complex expression  \cite{Kroetzsch2012}
\item Concept equivalence is indeed subsumption  from left and right. ($A \sqsubseteq B$ and $B \sqsubseteq A$ implies $A \equiv B$ )

\end{itemize}

\subsection{Simple Example}

\begin{DL}
Person $\equiv$ Human
\end{DL}

\begin{gcotable}
class & Person & - & - & Human & $\equiv$ \\
class & Human & - & - & Person & $\equiv$ \\
\end{gcotable}

maybe better:
\er{It is not better since we should stick to what we use as syntax.}

\begin{gcotable}
class & Person & - & - & Human & $\sqsubseteq$ \\
class & Human & - & - & Person & $\sqsubseteq$ \\
\end{gcotable}
\section{Sub Object Properties}

requirements:

\begin{itemize}

	\item R-54-SUB-OBJECT-PROPERTIES
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item DL terminology: role inclusion 
\end{itemize}

\subsection{Simple Example}

\begin{DL}
parentOf $\sqsubseteq$ ancestorOf 
\end{DL}

\begin{itemize}
	\item states that parentOf is a subrole of ancestorOf , i.e., every pair of individuals related by parentOf is also related by ancestorOf
\end{itemize}

\begin{gcotable}
property & parentOf & ancestorOf & - & - & $\sqsubseteq$ \\
\end{gcotable}

better:

\begin{gcotable}
property & $\top$ & parentOf & ancestorOf & $\top$ & $\sqsubseteq$ \\
\end{gcotable}

%\subsection{Simple Example}

%\begin{DL}
%sitsOn $\sqsubseteq$ touches 
%\end{DL}

\subsection{Simple Example}

\begin{DL}
hasDog $\sqsubseteq$ hasPet 
\end{DL}

\section{Sub Data Properties}

requirements:

\begin{itemize}

	\item R-54-SUB-DATA-PROPERTIES
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item DL terminology: concrete domains functional roles  
\end{itemize}

\subsection{Simple Example}
\begin{DL}
 $Person \sqcap  \forall hasAge. \leq_{10} \sqsubseteq Person \sqcap \forall hasEvenAge. \leq_{10}$ 
\end{DL}

\section{Object Property Paths / Object Property Chains}

requirement:

\begin{itemize}
	\item R-55-OBJECT-PROPERTY-PATHS
\end{itemize}

\subsection{Description}

\begin{itemize}
  \item DL terminology: complex role inclusion axiom / role composition
	\item role composition can only appear on the left-hand side of complex role inclusions \cite{Kroetzsch2012}
\end{itemize}

\subsection{Simple Example}

\begin{DL}
brotherOf $\circ$ parentOf $\sqsubseteq$ uncleOf 
\end{DL}

\begin{ex}
# OWL2
# ----
:uncleOf owl:propertyChainAxiom ( :brotherOf :parentOf ) . 
\end{ex}

\begin{gcotable}
property & $\top$ & brotherOf, parentOf & uncleOf & $\top$ & $\sqsubseteq$ & -  \\
\end{gcotable}

old mapping:

\begin{gcotable}
property & uncleOf & brotherOf, parentOf & - & $\top$ & $\sqsubseteq$ \\
\end{gcotable}

\section{Disjoint Properties}

requirements:

\begin{itemize}
	\item R-9-DISJOINT-PROPERTIES
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item 
\end{itemize}

\subsection{Simple Example}

\begin{DL}
Disjoint(parentOf, childOf)
\end{DL}

\begin{gcotable}
property & $\top$ & parentOf & childOf & $\top$ & $\ne$ \\
\end{gcotable}

\section{Intersection}

requirements:

\begin{itemize}
  \item R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS
	\item R-16-CONJUNCTION-OF-DATA-RANGES
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item composition / conjunction
\end{itemize}

DLs allow new concepts and roles to be
built using a variety of different constructors. We distinguish concept and role 
constructors depending on whether concept or role expressions are constructed. In the case of
concepts, one can further separate basic Boolean constructors, role restrictions and nominals/enumerations \cite{Kroetzsch2012}.

Boolean concept constructors provide basic boolean operations that are closely related to
the familiar operations of intersection, union and complement of sets, or to conjunction,
disjunction and negation of logical expressions \cite{Kroetzsch2012}.

\begin{DL}
Mother $\equiv$ Female $\sqcap$ Parent
\end{DL}

concept inclusions allow us to state that all mothers are female and that
all mothers are parents, but what we really mean is that mothers are exactly the female
parents. DLs support such statements by allowing us to form complex concepts such as
the intersection (also called conjunction)
which denotes the set of individuals that are both female and parents. A complex concept
can be used in axioms in exactly the same way as an atomic concept, e.g., in the
equivalence Mother $\equiv$ Female $\sqcap$ Parent .

\subsection{Simple Example}

\begin{DL}
Female $\sqcap$ Parent
\end{DL}

\begin{itemize}
	\item complex concept of all individuals which are of the concept Female and of the concept Parent
\end{itemize}

\begin{gcotable}
class & Female $\sqcap$ Parent & - & - & Female, Parent & $\sqcap$ \\
\end{gcotable}

\begin{DL}
Mother $\equiv$ Female $\sqcap$ Parent
\end{DL}

\begin{gcotable}
class & Mother & - & - & Female, Parent & $\sqcap$ \\
\end{gcotable}

\section{Disjunction}

requirements:

\begin{itemize}
	\item R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS
	\item R-18-DISJUNCTION-OF-DATA-RANGES
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item union / inclusive OR
\end{itemize}

\subsection{Simple Example}

\begin{DL}
Father $\sqcup$ Mother $\sqcup$ Child
\end{DL}

\begin{gcotable}
class & complex concept & - & - & Father, Mother, Child & $\sqcup$ \\
\end{gcotable}

\subsection{Simple Example}

\begin{DL}
Parent $\equiv$ Father $\sqcup$ Mother
\end{DL}

\begin{gcotable}
class & Parent & - & - & Father, Mother & $\sqcup$ \\
\end{gcotable}

\section{Negation}

requirements:

\begin{itemize}
  \item R-19-NEGATION-OF-CLASS-EXPRESSIONS
	\item R-20-NEGATION-OF-DATA-RANGES
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item complement
\end{itemize}

\subsection{Simple Example}

\begin{DL}
$ \neg Married $ \\ 
\end{DL}

\begin{itemize}
	\item set of all individuals that are not married
\end{itemize}

\begin{gcotable}
class & $\neg$ Married & - & - & Married & $\neg$ \\
\end{gcotable}

\subsection{Complex Example}

\begin{DL}
Female $\sqcap$ $\neg$ Married \\
\end{DL}

\begin{gcotable}
class & $\neg$ Married & - & - & Married & $\neg$ \\
class & Female $\sqcap$ $\neg$ Married & - & - & Female, $\neg$ Married & $\sqcap$ \\
\end{gcotable}

\section{Disjoint Classes}

requirements:

\begin{itemize}
	\item R-7-DISJOINT-CLASSES
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item 
\end{itemize}

\subsection{Simple Example}

\begin{DL}
Male $\sqcap$ Female $\sqsubseteq$ $\perp$
\end{DL}

\begin{gcotable}
class & Male $\sqcap$ Female & - & - & Male, Female & $\sqcap$  \\
class & $\top$ & - & - & Male $\sqcap$ Female, $\perp$ & $\sqsubseteq$ \\
\end{gcotable}

syntactic sugar:

\begin{gcotable}
class & Male & - & - & Female & $\ne$ \\
class & Female & - & - & Male & $\ne$ \\
\end{gcotable}

\section{Existential Quantification on Properties}

requirements:

\begin{itemize}
	\item R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item DL termonology: existential restriction
	\item An existential class expression ObjectSomeValuesFrom( OPE CE ) consists of an object property expression OPE and a class expression CE, and it contains all those individuals that are connected by OPE to an individual that is an instance of CE. Such a class expression can be seen as a syntactic shortcut for the class expression ObjectMinCardinality( 1 OPE CE ).
	\item An existential class expression DataSomeValuesFrom( DPE1 ... DPEn DR ) consists of n data property expressions DPEi, 1 $\leq$ i $\leq$ n, and a data range DR whose arity MUST be n. Such a class expression contains all those individuals that are connected by DPEi to literals lti, 1 $\leq$ i $\leq$ n, such that the tuple ( lt1 , ..., ltn ) is in DR. A class expression of the form DataSomeValuesFrom( DPE DR ) can be seen as a syntactic shortcut for the class expression DataMinCardinality( 1 DPE DR ). 
\end{itemize}

\subsection{Simple Example}

\begin{DL}
$\exists$ parentOf . $\top$
\end{DL}

complex concept that describes the set
of individuals that are parents of at least one individual (instance of $\top$).

\begin{gcotable}
property & $\exists$ parentOf . $\top$ & parentOf & - & $\top$ & $\exists$ \\
\end{gcotable}

\subsection{Simple Example}

\begin{DL}
$\exists$ parentOf . Female
\end{DL}

the complex concept describes those individuals that are parents of at least one
female individual, i.e., those that have a daughter.

\begin{gcotable}
property & $\exists$ parentOf . Female & parentOf & - & Female & $\exists$ \\
\end{gcotable}

\subsection{Simple Example}

\begin{DL}
Parent $\equiv$ $\exists$ parentOf . $\top$
\end{DL}

\begin{gcotable}
property & Parent & parentOf & - & $\top$ & $\exists$ \\
\end{gcotable}

\section{Universal Quantification on Properties}

requirements:

\begin{itemize}
	\item R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item DL termonology: universal restriction
\end{itemize}

\tb{definition}

\subsection{Simple Example}

\begin{DL}
$\forall$ parentOf . Female
\end{DL}

\begin{itemize}
	\item set of individuals all of whose children are female
  \item also includes those that have no children at all
\end{itemize}

\begin{gcotable}
property & $\forall$ parentOf . Female & parentOf & - & Female & $\forall$ \\
\end{gcotable}

\section{Property Domain}

requirements:

\begin{itemize}
	\item R-25-OBJECT-PROPERTY-DOMAIN
	\item R-26-DATA-PROPERTY-DOMAIN
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item restrict domain of object and data properties
	\item DL terminology: domain restrictions on roles
	\item The language needs to include an easy-to-use vocabulary to declare that a given property is associated with a class, e.g. to populate input forms with appropriate widgets but also constraint checking. In OO terms this is the declaration of a member, field, attribute or association. 
\end{itemize}

\tb{definition}

\subsection{Simple Example}

\begin{DL}
$\exists$ sonOf . $\top$ $\sqsubseteq$ Male 
\end{DL}

\begin{itemize}
	\item restrict the domain of sonOf to male individual
\end{itemize}

\begin{gcotable}
property & $\top$ & sonOf & - & Male & domain \\
\end{gcotable}

\section{Property Range}

requirements:

\begin{itemize}
	\item R-28-OBJECT-PROPERTY-RANGE
	\item R-35-DATA-PROPERTY-RANGE
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item restrict range of object and data properties
	\item DL terminology: range restrictions on roles
\end{itemize}

\tb{definition}

\subsection{Simple Example}

\begin{DL}
$\top$ $\sqsubseteq$ $\forall$ sonOf . Parent 
\end{DL}

\begin{itemize}
	\item restrict the range of sonOf to parents
\end{itemize}

\begin{ex}
# OWL 2
# -----
sonOf rdfs:range Parent . 
\end{ex}

\begin{ex}
# DSP
# ---
:hasDogRange
        a dsp:DescriptionTemplate ; 
        dsp:resourceClass owl:Thing ; 
        dsp:statementTemplate [
            a dsp:NonLiteralStatementTemplate ;
            dsp:property sonOf ; 
            dsp:nonLiteralConstraint [ 
                a dsp:NonLiteralConstraint ;
                dsp:valueClass Parent ] ] .
\end{ex}

\begin{gcotable}
property & $\top$ & sonOf & - & Parent & range \\
\end{gcotable}

\section{Class-Specific Property Range}

requirements:

\begin{itemize}
	\item R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS
	\item R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS
\end{itemize}

\subsection{Description}

\begin{itemize}
  \item restrict range of object and data properties for individuals within specific context
	\item context: e.g. class
	\item The values of each member property of a class may be limited by their value type, such as xsd:string or ex:Person. 
\end{itemize}

\subsection{Simple Example}

\begin{itemize}
	\item property 'sonOf'
	\item context: class 'Man'
	\item range: class 'Parent'
	\item $\rightarrow$ individuals of the class 'Man' can only have 'sonOf' relationships to indivuduals of the class 'Parent'
\end{itemize}

\section{Minimum Unqualified Cardinality Restrictions on Properties}

requirements:

\begin{itemize}
	\item R-81-MINIMUM-UNQUALIFIED-CARDINALITY-ON-PROPERTIES
	\item R-211-CARDINALITY-CONSTRAINTS
\end{itemize}

description:

\begin{itemize}
	\item A minimum cardinality expression ObjectMinCardinality( n OPE CE ) consists of a nonnegative integer n, an object property expression OPE, and a class expression CE, and it contains all those individuals that are connected by OPE to at least n different individuals that are instances of CE. If CE is missing, it is taken to be owl:Thing.
	\item A minimum cardinality expression DataMinCardinality( n DPE DR ) consists of a nonnegative integer n, a data property expression DPE, and a unary data range DR, and it contains all those individuals that are connected by DPE to at least n different literals in DR. If DR is not present, it is taken to be rdfs:Literal. 
	\item unqualified: CE respective DR is NOT stated. 
\end{itemize}

\subsection{Simple Example}

\begin{ex}
# ShEx
# ----
:Jedi {
    :attitude ('good') }
:JediStudent {
    & :Jedi ,
    :studentOf {}{1} }
:JediMaster {
    & :Jedi ,
    :mentorOf {}{1,2} }
:SuperJediMaster {
    & :Jedi ,
    :mentorOf {}{3,} }
\end{ex}

\begin{itemize}
	\item Jedis have the attitude 'good'
	\item Jedi students are students of exactly 1 resource
	\item Jedi masters are mentoring at least 1 and at most 2 resources
	\item Super Jedi masters are mentoring at least 3 resources  
\end{itemize}

\begin{ex}
# data
# ----
:Yoda 
    :attitude 'good' ;
    :mentorOf :MaceWindu , :Obi-Wan , :Luke .
:MaceWindu
    :attitude 'good' ;
    :studentOf :Yoda .
:Obi-Wan 
    :attitude 'good' ;
    :studentOf :Yoda ;
    :mentorOf :Anakin .
:Anakin
    :attitude 'good' ; 
    :studentOf :Obi-Wan .
:Luke
    :attitude 'good' ;
    :studentOf :Yoda .
\end{ex}

\begin{ex}
# Individuals matching the ’:SuperJediMaster’ data shape
# ------------------------------------------------------
:Yoda 
\end{ex}

\tb{ToDO: add DL}

\section{Minimum Qualified Cardinality Restrictions on Properties}

requirements:

\begin{itemize}
	\item R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES
  \item R-211-CARDINALITY-CONSTRAINTS
\end{itemize}

description:

\begin{itemize}
	\item A minimum cardinality expression ObjectMinCardinality( n OPE CE ) consists of a nonnegative integer n, an object property expression OPE, and a class expression CE, and it contains all those individuals that are connected by OPE to at least n different individuals that are instances of CE. If CE is missing, it is taken to be owl:Thing.
	\item A minimum cardinality expression DataMinCardinality( n DPE DR ) consists of a nonnegative integer n, a data property expression DPE, and a unary data range DR, and it contains all those individuals that are connected by DPE to at least n different literals in DR. If DR is not present, it is taken to be rdfs:Literal. 
	\item qualified: CE respective DR is stated.
\end{itemize}

\subsection{Simple Example}

\begin{DL}
$\geq$ 2 childOf . Parent
\end{DL}

\tb{ToDO: check DL}

\begin{itemize}
	\item set of individuals that are children of at least two parents
\end{itemize}

\begin{ex}
# OWL 2
# -----
owl:Thing
    a owl:Restriction ;
    owl:minQualifiedCardinality "2"^^xsd:nonNegativeInteger ;
    owl:onProperty childOf ;
    owl:onClass Parent .
\end{ex}

\begin{gcotable}
property & $\geq$ 2 childOf . Parent & childOf & -  & Parent & $\geq$ & 2 \\
\end{gcotable}

\subsection{Simple Example}

\begin{DL}
foaf:Person $\equiv$ $\geq$ 2 hasName.xsd:string
\end{DL}

\tb{ToDO: check DL}

\begin{gcotable}
property & foaf:Person & hasName & - & xsd:string & $\geq$ & 2 \\
\end{gcotable}

\subsection{Simple Example}

\tb{ToDO: OWL 2 DL}

\begin{ex}
# ShEx
# ----
:Jedi {
    :attitude ('good') }
:JediStudent {
    & :Jedi ,
    :studentOf @:Jedi{1} }
:JediMaster {
    & :Jedi ,
    :mentorOf @:Jedi{1,2} }
:SuperJediMaster {
    & :Jedi ,
    :mentorOf @:Jedi{3,} }
\end{ex}

\begin{itemize}
	\item Jedis have the attitude 'good'
	\item Jedi students are students of exactly 1 Jedi
	\item Jedi masters are mentoring at least 1 and at most 2 Jedis
	\item Super Jedi masters are mentoring at least 3 Jedis
\end{itemize}

\begin{ex}
# data
# ----
:Yoda 
    :attitude 'good' ;
    :mentorOf :MaceWindu , :Obi-Wan , :Luke .
:MaceWindu
    :attitude 'good' ;
    :studentOf :Yoda .
:Obi-Wan 
    :attitude 'good' ;
    :studentOf :Yoda ;
    :mentorOf :Anakin .
:Anakin
    :attitude 'good' ; 
    :studentOf :Obi-Wan .
:Luke
    :attitude 'good' ;
    :studentOf :Yoda .
\end{ex}

\begin{ex}
# Individuals matching the ’:SuperJediMaster’ data shape
# ------------------------------------------------------
:Yoda

# Individuals matching the ’:JediMaster’ data shape
# -------------------------------------------------
:Obi-Wan
\end{ex}

\tb{ToDO: add DL}

\subsection{Complex Example}

\begin{DL}
Father2Daughters $\equiv$ Man $\sqcap$ ($\geq$ 2 hasChild.Woman)
\end{DL}

\tb{ToDO: check DL}

\begin{gcotable}
property & $\geq$ 2 hasChild.Woman & hasChild & - & Woman & $\geq$ & 2 \\
class & Father2Daughters & - & - & Man, $\geq$ 2 hasChild.Woman & $\sqcap$ & - \\
\end{gcotable}

\section{Maximum Unqualified Cardinality Restrictions on Properties}

requirements:

\begin{itemize}
	\item R-82-MAXIMUM-UNQUALIFIED-CARDINALITY-ON-PROPERTIES
	\item R-211-CARDINALITY-CONSTRAINTS
\end{itemize}

description:

\begin{itemize}
	\item A maximum cardinality expression ObjectMaxCardinality( n OPE CE ) consists of a nonnegative integer n, an object property expression OPE, and a class expression CE, and it contains all those individuals that are connected by OPE to at most n different individuals that are instances of CE. If CE is missing, it is taken to be owl:Thing.
	\item A maximum cardinality expression DataMaxCardinality( n DPE DR ) consists of a nonnegative integer n, a data property expression DPE, and a unary data range DR, and it contains all those individuals that are connected by DPE to at most n different literals in DR. If DR is not present, it is taken to be rdfs:Literal. 
	\item unqualified: CE respective DR is NOT stated. 
\end{itemize}

\subsection{Simple Example}

\begin{ex}
# ShEx
# ----
:Jedi {
    :attitude ('good') }
:JediStudent {
    & :Jedi ,
    :studentOf {}{1} }
:JediMaster {
    & :Jedi ,
    :mentorOf {}{1,2} }
:SuperJediMaster {
    & :Jedi ,
    :mentorOf {}{3,} }
\end{ex}

\begin{itemize}
	\item Jedis have the attitude 'good'
	\item Jedi students are students of exactly 1 resource
	\item Jedi masters are mentoring at least 1 and at most 2 resources
	\item Super Jedi masters are mentoring at least 3 resources  
\end{itemize}

\begin{ex}
# data
# ----
:Yoda 
    :attitude 'good' ;
    :mentorOf :MaceWindu , :Obi-Wan , :Luke .
:MaceWindu
    :attitude 'good' ;
    :studentOf :Yoda .
:Obi-Wan 
    :attitude 'good' ;
    :studentOf :Yoda ;
    :mentorOf :Anakin .
:Anakin
    :attitude 'good' ; 
    :studentOf :Obi-Wan .
:Luke
    :attitude 'good' ;
    :studentOf :Yoda .
\end{ex}

\begin{ex}
# Individuals matching the ’:JediMaster’ data shape
# -------------------------------------------------
:Obi-Wan
\end{ex}

\tb{ToDO: add DL}

\section{Maximum Qualified Cardinality Restrictions on Properties}

requirements:

\begin{itemize}
	\item R-76-MAXIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES
	\item R-211-CARDINALITY-CONSTRAINTS
\end{itemize}

description:

\begin{itemize}
	\item A maximum cardinality expression ObjectMaxCardinality( n OPE CE ) consists of a nonnegative integer n, an object property expression OPE, and a class expression CE, and it contains all those individuals that are connected by OPE to at most n different individuals that are instances of CE. If CE is missing, it is taken to be owl:Thing.
	\item A maximum cardinality expression DataMaxCardinality( n DPE DR ) consists of a nonnegative integer n, a data property expression DPE, and a unary data range DR, and it contains all those individuals that are connected by DPE to at most n different literals in DR. If DR is not present, it is taken to be rdfs:Literal. 
	\item qualified: CE respective DR is stated. 
\end{itemize}

\subsection{Simple Example}

\begin{DL}
$\leq$  2 childOf . Parent
\end{DL}

\tb{ToDO: check DL}

\begin{itemize}
	\item set of individuals that are children of at most two parents
\end{itemize}

\begin{gcotable}
property & $\leq$  2 childOf . Parent & childOf & - & Parent & $\leq$ & 2 \\
\end{gcotable}

\subsection{Simple Example}

\tb{ToDO: OWL 2 DL}

\begin{ex}
# ShEx
# ----
:Jedi {
    :attitude ('good') }
:JediStudent {
    & :Jedi ,
    :studentOf @:Jedi{1} }
:JediMaster {
    & :Jedi ,
    :mentorOf @:Jedi{1,2} }
:SuperJediMaster {
    & :Jedi ,
    :mentorOf @:Jedi{3,} }
\end{ex}

\begin{itemize}
	\item Jedis have the attitude 'good'
	\item Jedi students are students of exactly 1 Jedi
	\item Jedi masters are mentoring at least 1 and at most 2 Jedis
	\item Super Jedi masters are mentoring at least 3 Jedis
\end{itemize}

\begin{ex}
# data
# ----
:Yoda 
    :attitude 'good' ;
    :mentorOf :MaceWindu , :Obi-Wan , :Luke .
:MaceWindu
    :attitude 'good' ;
    :studentOf :Yoda .
:Obi-Wan 
    :attitude 'good' ;
    :studentOf :Yoda ;
    :mentorOf :Anakin .
:Anakin
    :attitude 'good' ; 
    :studentOf :Obi-Wan .
:Luke
    :attitude 'good' ;
    :studentOf :Yoda .
\end{ex}

\begin{ex}
# Individuals matching the ’:JediMaster’ data shape
# -------------------------------------------------
:Obi-Wan
\end{ex}

\tb{ToDO: add DL}

\section{Exact Unqualified Cardinality Restrictions on Properties}

requirements:

\begin{itemize}
	\item R-80-EXACT-UNQUALIFIED-CARDINALITY-ON-PROPERTIES
	\item R-211-CARDINALITY-CONSTRAINTS
\end{itemize}

description:

\begin{itemize}
	\item An exact cardinality expression ObjectExactCardinality( n OPE CE ) consists of a nonnegative integer n, an object property expression OPE, and a class expression CE, and it contains all those individuals that are connected by OPE to exactly n different individuals that are instances of CE. If CE is missing, it is taken to be owl:Thing. Such an expression is actually equivalent to the expression ObjectIntersectionOf( ObjectMinCardinality( n OPE CE ) ObjectMaxCardinality( n OPE CE ) ).
	\item An exact cardinality expression DataExactCardinality( n DPE DR ) consists of a nonnegative integer n, a data property expression DPE, and a unary data range DR, and it contains all those individuals that are connected by DPE to exactly n different literals in DR. If DR is not present, it is taken to be rdfs:Literal. 
	\item unqualified: CE respective DR is NOT stated. 
\end{itemize}

\subsection{Simple Example}

\tb{ToDo. OWL 2 DL}

\begin{ex}
# ShEx
# ----
:JediStudent {
    :studentOf {}{1} }
\end{ex}

\begin{ex}
# ReSh
# ----
:JediStudent a rs:ResourceShape ;
    rs:property [
        rs:name "studentOf" ;
        rs:propertyDefinition :studentOf ;
        rs:valueShape [ a rs:ResourceShape] ;
        rs:occurs rs:Exactly-one ; ] .
\end{ex}

\begin{itemize}
	\item Jedis have the attitude 'good'
	\item Jedi students are students of exactly 1 resource
\end{itemize}

\begin{ex}
# data
# ----
:Yoda 
    :attitude 'good' ;
    :mentorOf :MaceWindu , :Obi-Wan , :Luke .
:MaceWindu
    :attitude 'good' ;
    :studentOf :Yoda .
:Obi-Wan 
    :attitude 'good' ;
    :studentOf :Yoda ;
    :mentorOf :Anakin .
:Anakin
    :attitude 'good' ; 
    :studentOf :Obi-Wan .
:Luke
    :attitude 'good' ;
    :studentOf :Yoda .
\end{ex}

\begin{ex}
# Individuals matching the ’:JediStudent’ data shape
# --------------------------------------------------
:MaceWindu :Obi-Wan :Anakin :Luke
\end{ex}

\tb{ToDO: add DL}

\section{Exact Qualified Cardinality Restrictions on Properties}

requirements:

\begin{itemize}
	\item R-74-EXACT-QUALIFIED-CARDINALITY-ON-PROPERTIES
	\item R-211-CARDINALITY-CONSTRAINTS
\end{itemize}

description:

\begin{itemize}
	\item An exact cardinality expression ObjectExactCardinality( n OPE CE ) consists of a nonnegative integer n, an object property expression OPE, and a class expression CE, and it contains all those individuals that are connected by OPE to exactly n different individuals that are instances of CE. If CE is missing, it is taken to be owl:Thing. Such an expression is actually equivalent to the expression ObjectIntersectionOf( ObjectMinCardinality( n OPE CE ) ObjectMaxCardinality( n OPE CE ) ).
	\item An exact cardinality expression DataExactCardinality( n DPE DR ) consists of a nonnegative integer n, a data property expression DPE, and a unary data range DR, and it contains all those individuals that are connected by DPE to exactly n different literals in DR. If DR is not present, it is taken to be rdfs:Literal. 
	\item qualified: CE respective DR is stated. 
\end{itemize}

\subsection{Simple Example}

\tb{ToDO: OWL 2 DL}

\begin{ex}
# ShEx
# ----
:Jedi {
    :attitude ('good') }
:JediStudent {
    :studentOf @:Jedi{1} }
\end{ex}

\begin{ex}
# ReSh
# ----
:Jedi a rs:ResourceShape ;
    rs:property [
        rs:name "attitude" ;
        rs:propertyDefinition :attitude ;
        rs:allowedValue "good" ;
        rs:occurs rs:Exactly-one ;
    ] .
:JediStudent a rs:ResourceShape ;
    rs:property [
        rs:name "studentOf" ;
        rs:propertyDefinition :studentOf ;
        rs:valueShape :Jedi ;
        rs:occurs rs:Exactly-one ;
    ] .
\end{ex}

\begin{itemize}
	\item Jedis have the attitude 'good'
	\item Jedi students are students of exactly 1 Jedi
\end{itemize}

\begin{ex}
# data
# ----
:Yoda 
    :attitude 'good' ;
    :mentorOf :MaceWindu , :Obi-Wan , :Luke .
:MaceWindu
    :attitude 'good' ;
    :studentOf :Yoda .
:Obi-Wan 
    :attitude 'good' ;
    :studentOf :Yoda ;
    :mentorOf :Anakin .
:Anakin
    :attitude 'good' ; 
    :studentOf :Obi-Wan .
:Luke
    :attitude 'good' ;
    :studentOf :Yoda .
\end{ex}

\begin{ex}
# Individuals matching the ’:JediStudent’ data shape
# --------------------------------------------------
:MaceWindu :Obi-Wan :Anakin :Luke
\end{ex}

\tb{ToDO: add DL}

\subsection{Complex Example}

\begin{DL}
Person $\sqsubseteq$ $\geq$ 2 childOf . Parent $\sqcap$ $\leq$  2 childOf . Parent \\
\end{DL}

\tb{ToDO: check DL}

\begin{itemize}
	\item every person is a child of exactly two parents
\end{itemize}

\begin{gcotable}
property & $\geq$ 2 childOf . Parent & childOf & - & Parent & $\geq$ & 2 \\
property & $\leq$ 2 childOf . Parent & childOf & - & Parent & $\leq$ & 2 \\
class & Person & - & - & $\geq$ 2 childOf . Parent, $\leq$ 2 childOf . Parent & $\sqcap$ & - \\
\end{gcotable}

syntactic sugar:

\begin{gcotable}
property & Person & childOf & - & Parent & = & 2 \\
\end{gcotable}

\section{Inverse Object Properties}

requirement:

\begin{itemize}
	\item R-56-INVERSE-OBJECT-PROPERTIES
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item In many cases properties are used bi-directionally and then accessed in the inverse direction, e.g. parent $\equiv$ child$^{-}$. There should be a way to declare value type, cardinality etc of those inverse relations without having to declare a new property URI. 
	\item The object property expression OPE1 is an inverse of the object property expression OPE2. Thus, if an individual x is connected by OPE1 to an individual y, then y is also connected by OPE2 to x, and vice versa.
\end{itemize}

\subsection{Simple Example}

\begin{DL}
parentOf $\equiv$ $childOf^{-}$ \\
\end{DL}

\begin{gcotable}
property & parentOf & childOf & - & $\top$ & $inverse role (^{-})$ \\
\end{gcotable}

consistent with ontology:

\begin{gcotable}
property & $\top$ & parentOf & childOf & $\top$ & $inverse role (^{-})$ \\
\end{gcotable}

\section{Transitive Object Properties}

requirements:

\begin{itemize}
	\item R-63-TRANSITIVE-OBJECT-PROPERTIES
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item Transitivity is a special form of complex role inclusion
	\item An object property transitivity axiom TransitiveObjectProperty( OPE ) states that the object property expression OPE is transitive — that is, if an individual x is connected by OPE to an individual y that is connected by OPE to an individual z, then x is also connected by OPE to z.
\end{itemize}

\subsection{Simple Example}

\begin{DL}
ancestorOf $\circ$ ancestorOf $\sqsubseteq$ ancestorOf
\end{DL}

syntactic sugar:

\begin{gcotable}
property & ancesterOf & ancestorOf, ancestorOf & - & $\top$ & transitive role \\
\end{gcotable}

syntactic sugar (ontology conform):

\begin{gcotable}
property & $\top$ & ancestorOf, ancestorOf & ancestorOf & $\top$ & transitive role \\
\end{gcotable}

without syntactic sugar (ontology conform):

\begin{gcotable}
property & $\top$ & ancestorOf, ancestorOf & ancestorOf & $\top$ & $\sqsubseteq$ \\
\end{gcotable}

\section{Symmetric Object Properties}

requirement:

\begin{itemize}
	\item R-61-SYMMETRIC-OBJECT-PROPERTIES
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item A role is symmetric if it is equivalent to its own inverse \cite{Kroetzsch2012}
  \item An object property symmetry axiom SymmetricObjectProperty( OPE ) states that the object property expression OPE is symmetric — that is, if an individual x is connected by OPE to an individual y, then y is also connected by OPE to x. 	
\end{itemize}

\subsection{Simple Example}

\begin{DL}
marriedTo $\equiv$ $marriedTo^{-}$ \\
\end{DL}

\begin{gcotable}
property & marriedTo & marriedTo & - & $\top$ & $inverse role (^{-})$ \\
\end{gcotable}

ontology conform:

\begin{gcotable}
property & $\top$ & marriedTo & marriedTo & $\top$ & $inverse role (^{-})$ \\
\end{gcotable}

syntactic sugar:

\begin{gcotable}
property & $\top$ & marriedTo & - & $\top$ & symmetric role \\
\end{gcotable}

\subsubsection{Asymmetric Object Properties}

requirement:

\begin{itemize}
	\item R-62-ASYMMETRIC-OBJECT-PROPERTIES
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item A role is asymmetric if it is disjoint from its own inverse \cite{Kroetzsch2012}
	\item An object property asymmetry axiom AsymmetricObjectProperty( OPE ) states that the object property expression OPE is asymmetric — that is, if an individual x is connected by OPE to an individual y, then y cannot be connected by OPE to x. 
\end{itemize}

\subsection{Simple Example}

\begin{DL}
Disjoint( parentOf , $parentOf^{-}$ )
\end{DL}

\begin{gcotable}
property & $parentOf^{-}$ & parentOf & - & $\top$ & inverse role $(^{-})$ \\
property & parentOf & parentOf, $parentOf^{-}$ & - & $\top$ & disjoint role ($\ne$) \\
\end{gcotable}

ontology conform:

\begin{gcotable}
property & $\top$ & parentOf & - & $\top$ & inverse role $(^{-})$ \\
property & $\top$ & parentOf, $parentOf^{-}$ & - & $\top$ & disjoint role ($\ne$) \\
\end{gcotable}

syntactic sugar:

\begin{gcotable}
property & $\top$ & parentOf & - & $\top$ & asymmetric role \\
\end{gcotable}

\subsection{Simple Example}

\begin{itemize}
	\item child parent relations (dbo:child) cannot be symmetric
\end{itemize}

\subsection{Simple Example}

\begin{itemize}
	\item person birth place relations (dbo:birthPlace) cannot be symmetric
\end{itemize}

\section{Class-Specific Reflexive Object Properties / Local Reflexivity}

requirement:

\begin{itemize}
	\item 
\end{itemize}

\subsection{Description}

\begin{itemize}
  \item DL terminology: local reflexivity
	\item set of individuals that are related to themselves via a given role \cite{Kroetzsch2012}.
	\item set of individuals (of a specific class) that are related to themselves via a given object property
\end{itemize}

\subsection{Simple Example}

\begin{DL}
$\exists$ talksTo .Self. 
\end{DL}

\begin{itemize}
	\item set of individuals that are talking to themselves
\end{itemize}

\begin{gcotable}
property & $\exists$ talksTo .Self.  & talksTo & - & Self & $\exists$ \\
\end{gcotable}

syntactic sugar:

\begin{gcotable}
property & $\exists$ talksTo .Self. & talksTo & - & - & reflexive role \\
\end{gcotable}

\section{Reflexive Object Properties / Global Reflexivity}

requirement:

\begin{itemize}
	\item R-59-REFLEXIVE-OBJECT-PROPERTIES
\end{itemize}

\subsection{Description}

\begin{itemize}
  \item DL terminology: reflexive roles, global reflexivity
	\item global reflexivity can be expressed by imposing local reflexivity on the top concept \cite{Kroetzsch2012}
\end{itemize}

\subsection{Simple Example}

\begin{DL}
$\top$ $\sqsubseteq$ $\exists$ knows . Self
\end{DL}

syntactic sugar:

\begin{gcotable}
property & $\top$ & knows & - & $\top$ & reflexive role \\
\end{gcotable}

\begin{gcotable}
property & $\top$ & knows & - & Self & $\exists$ \\
\end{gcotable}

\section{Irreflexive Object Properties}

requirement:

\begin{itemize}
	\item R-60-IRREFLEXIVE-OBJECT-PROPERTIES
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item DL terminology: irreflexive roles
  \item A role is irreflexive if it is never locally reflexive \cite{Kroetzsch2012}
	\item An object property irreflexivity axiom IrreflexiveObjectProperty( OPE ) states that the object property expression OPE is irreflexive — that is, no individual is connected by OPE to itself. 
\end{itemize}

\subsection{Simple Example}

\begin{DL}
$\top$ $\sqsubseteq$ $\neg$ $\exists$ marriedTo . Self
\end{DL}

syntactic sugar:

\begin{gcotable}
property & $\top$ & marriedTo & - & $\top$ & irreflexive role \\
\end{gcotable}

\begin{gcotable}
property & $\exists$ marriedTo . Self & marriedTo & - & Self & $\exists$ \\
class & $\top$ & - & - & $\exists$ marriedTo . Self & $\neg$ \\
\end{gcotable}

\subsection{Simple Example}

\begin{itemize}
	\item a resource cannot be its own parent (dbo:parent)
\end{itemize}

\subsection{Simple Example}

\begin{itemize}
	\item a resource cannot be its own child (dbo:child)
\end{itemize}

\section{Context-Specific Property Groups}

requirement:

\begin{itemize}
	\item R-66-PROPERTY-GROUPS
\end{itemize}

\subsection{Description}

\subsection{Simple Example}

DSCL (ShEx):
\begin{ex}
<Human> { 
    (  
        foaf:name xsd:string ,
        foaf:givenName xsd:string 
    ) ,
    (
        foaf:mbox IRI ,
        foaf:homepage foaf:Document
    ) }
\end{ex}

\begin{itemize}
	\item 1. group: 1 foaf:name (range: xsd:string) and 1 foaf:givenName (range: xsd:string) and (,)
	\item 2. group: 1 foaf:mbox (range: IRI) and 1 foaf:homepage (range: foaf:Document) 
\end{itemize}

\begin{DL}
$A \equiv \forall foaf:name . xsd:string$ \\
$B \equiv \forall foaf:givenName . xsd:string$ \\
$C \equiv A XOR B$ \\
$D \equiv \forall foaf:mbox . xsd:string$ \\
$Human \equiv C \sqcap D$ \\
\end{DL}

\section{Context-Specific Exclusive OR of Properties}

requirements:

\begin{itemize}
	\item R-11-CONTEXT-SPECIFIC-EXCLUSIVE-OR-OF-PROPERTIES
\end{itemize}

\subsection{Description}

\begin{itemize}
  \item exclusive or: logical operation that outputs true whenever both inputs differ (one is true, the other is false).
	\item in OWL 2, inclusive OR of properties would be possible to express, but not exclusive OR of data properties
\end{itemize}

DL (general):

\begin{DL}
$C \sqsubseteq (\neg A \sqcap B) \sqcup (A \sqcap \neg B)$ \\
\end{DL}

DL (general) (alternative):

\begin{DL}
$C \sqsubseteq (A \sqcup B) \sqcap \neg(A \sqcap B)$ \\
\end{DL}

\subsection{Simple Example}

DSCL (ShEx):
\begin{ex}
<Human> { (  
    foaf:name xsd:string | 
    foaf:givenName xsd:string ) }
\end{ex}

DSCL (OWL 2):
\begin{ex}
:Human owl:disjointUnionOf ( :CC1 :CC2 ) .

:CC1 rdfs:subClassOf [
    a owl:Restriction ;
    owl:onProperty foaf:name ;
    owl:allValuesFrom xsd:string ] .
:CC2 rdfs:subClassOf [
    a owl:Restriction ;
    owl:onProperty foaf:givenNme ;
    owl:allValuesFrom xsd:string ] .
\end{ex}

\begin{itemize}
	\item 1 foaf:name (range xsd:string) XOR 1 foaf:givenName (range xsd:string)
\end{itemize}

\begin{DL}
A $\equiv$ $\forall$ foaf:name . xsd:string \\
B $\equiv$ $\forall$ foaf:givenName . xsd:string \\ 
Human $\sqsubseteq$ ($\neg$ A $\sqcap$ B) $\sqcup$ (A $\sqcap$ $\neg$ B) \\
\end{DL}

\begin{gcotable}
property & A & foaf:name & - & xsd:string & $\forall$ \\
property & B & foaf:givenName & - & xsd:string & $\forall$ \\
class & $\neg$ A & - & - & A & $\neg$ \\
class & $\neg$ B & - & - & B & $\neg$ \\
class & $\neg$ A $\sqcap$ B & - & - & $\neg$ A, B & $\sqcap$ \\
class & A $\sqcap$ $\neg$ B & - & - & A, $\neg$ B & $\sqcap$ \\
class & Human & - & - & $\neg$ A $\sqcap$ B, A $\sqcap$ $\neg$ B & $\sqcup$ \\
\end{gcotable}

syntactic sugar:

\begin{gcotable}
property & A & foaf:name & - & xsd:string & $\forall$ \\
property & B & foaf:givenName & - & xsd:string & $\forall$ \\
class & Human & - & - & A, B & XOR \\
\end{gcotable}

\subsection{Complex Example}

DSCL (ShEx):

\begin{ex}
<Human> { (  
    foaf:name xsd:string | foaf:givenName xsd:string+ , 
    foaf:familyName xsd:string ) }
\end{ex}

\begin{itemize}
	\item 1 foaf:name (range xsd:string) XOR 1-n foaf:givenName (range xsd:string)
	\item and
	\item 1 foaf:familyName (range xsd:string)
\end{itemize}

\tb{ToDo: DL}

Individuals matching the 'Human' data shape:

\begin{ex}
:Han
    foaf:name "Han Solo" ;
    foaf:familyName "Solo" .
:Anakin
    foaf:givenName "Anakin" ;
    foaf:givenName "Darth" ;
    foaf:familyName "Skywalker" .
\end{ex}

Individual not matching the 'Human' data shape:

\begin{ex}
:Anakin
    foaf:name "Anakin Skywalker" ;
    foaf:givenName "Anakin" ;
    foaf:familyName "Skywalker" .
\end{ex}

\section{Context-Specific Inclusive OR of Properties}

requirements:

\begin{itemize}
	\item R-202-CONTEXT-SPECIFIC-INCLUSIVE-OR-OF-PROPERTIES
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item inclusive or: A logical connective joining two or more predicates that yields the logical value "true" when at least one of the predicates is true.
	\item context can be a class $\rightarrow$ constraint applies for individuals of this specific class 
\end{itemize}

\subsection{Simple Example}

\begin{itemize}
	\item 1 foaf:name (range: xsd:string) OR 1 foaf:givenName (range: xsd:string)
	\item it is also possible that both 1 foaf:name and 1 foaf:givenName are stated
	\item context: class Human
\end{itemize}

\section{Context-Specific Exclusive OR of Property Groups}

requirement:

\begin{itemize}
	\item R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item exclusive or: logical operation that outputs true whenever both inputs differ (one is true, the other is false).
\end{itemize}

\subsection{Simple Example}

\begin{ex}
# DSCL (ShEx)
# -----------
<Human> { 
    (  
        foaf:name xsd:string ,
        foaf:givenName xsd:string ) 
    |
    (
        foaf:mbox IRI ,
        foaf:homepage foaf:Document ) }
\end{ex}

\begin{itemize}
  \item 1. group XOR 2. group
	\item 1. group: 1 foaf:name (range: xsd:string) and 1 foaf:givenName (range: xsd:string)
	\item 2. group: 1 foaf:mbox (range: IRI) and 1 foaf:homepage (range: foaf:Document) 
	\item context: class Human
\end{itemize}

\begin{ex}
# valid data
# ----------
:Thomas
    a :Human ;
    foaf:mbox <thomas.bosch@gesis.org> ;
    foaf:homepage <http://purl.org/net/thomasbosch> .
\end{ex}

\begin{ex}
# invalid data
# ----------
:Thomas
    a :Human ;
    foaf:name 'Thomas Bosch' ;
    foaf:givenName 'Thomas' ;
    foaf:mbox <thomas.bosch@gesis.org> ;
    foaf:homepage <http://purl.org/net/thomasbosch> .
\end{ex}

\begin{DL}
Human $\sqsubseteq$ ($\neg$ E $\sqcap$ F) $\sqcup$ (E $\sqcap$ $\neg$ F) \\ 
E $\equiv$ A $\sqcap$ B \\
F $\equiv$ C $\sqcap$ D \\
A $\equiv$ $\forall$ foaf:name . xsd:string \\
B $\equiv$ $\forall$ foaf:givenName . xsd:string \\ 
C $\equiv$ $\forall$ foaf:mbox . IRI \\
D $\equiv$ $\forall$ foaf:homepage . foaf:Document \\
\end{DL}

\subsection{Complex Example}

\begin{ex}
# ShExC
# -----
[[
  <UserShape> {                          # A User has
    (foaf:name xsd:string                #  either a foaf:name
     | foaf:givenName xsd:string+,       #   or 1+ givenNames
       foaf:familyName xsd:string),      #   and a family name
    foaf:mbox IRI                        # and an mbox.
  }
]]
\end{ex}

\begin{ex}
# ReSh
# ----

[[
  PREFIX rs:<http://open-services.net/ns/core#>
  PREFIX se:<http://www.w3.org/2013/ShEx/Definition#>

  <UserShape> a rs:ResourceShape ;       # A User has
    se:choice [
      rs:property [                      #  either a foaf:name
        rs:name "name" ;
        rs:propertyDefinition foaf:name ;
        rs:valueType xsd:string ;
        rs:occurs rs:Exactly-one ;
      ] ;
      se:ruleGroup [
        rs:property [                    #   or 1+ givenNames
          rs:name "givenName" ;
          rs:propertyDefinition foaf:givenName ;
          rs:valueType xsd:string ;
          rs:occurs rs:One-or-many ;
        ] ;
        rs:property [                    #   and a family name
          rs:name "familyName" ;
          rs:propertyDefinition foaf:familyName ;
          rs:valueType xsd:string ;
          rs:occurs rs:Exactly-one ;
        ] ;
      ] ;
    ] ;
    rs:property [                        # and an mbox.
      rs:name "mbox" ;
      rs:propertyDefinition foaf:mbox ;
      rs:valueType rs:Resource ;
      rs:occurs rs:Exactly-one ;
    ] .
]]
\end{ex}

\section{Context-Specific Inclusive OR of Property Groups}

requirements:

\begin{itemize}
	\item 
\end{itemize}

\subsection{Description}

\begin{itemize}
  \item at least one property group must match for individuals of a specific context 
	\item context: may be a class
\end{itemize}

\subsection{Simple Example}

\begin{itemize}
  \item 1. group OR 2. group
	\item 1. group: 1 foaf:firstName (range: xsd:string) and 1 foaf:lastName (range: xsd:string)
	\item 2. group: 1 foaf:givenName (range: xsd:string) and 1 foaf:familyName (range: xsd:string)
	\item context: class Person
\end{itemize}

\begin{ex}
# valid data
# ----------
:Anakin
    a :Person ;
    foaf:firstName 'Anakin' ;
    foaf:lastName 'Skywalker' ;
    foaf:givenName 'Anakin' ;
    foaf:familyName 'Skywalker' .
\end{ex}

\begin{ex}
# invalid data
# ----------
:Anakin
    a :Person .
\end{ex}

\section{Allowed Values}

requirements:

\begin{itemize}
	\item R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS
  \item R-37-ALLOWED-VALUES-FOR-RDF-LITERALS
\end{itemize}

\subsection{Description}

\begin{itemize}
  \item It is a common requirement to narrow down the value space of a property by an exhaustive enumeration of the valid values (both literals or resource). This is often rendered in drop down boxes or radio buttons in user interfaces. 
	\item define a concept by simply enumerating its instances
	\item A DL nominal is a concept that has exactly one instance
	\item DL enumeration: combining nominals with union
\end{itemize}

allowed values for properties

\begin{itemize}
	\item must be an IRI
  \item must be an IRI matching this pattern (e.g. http://id.loc.gov/authorities/names/)
  \item must be an IRI matching one of these patterns
  \item must be a (any) literal
  \item must be one of these literals ("red" "blue" "green")
  \item must be a typed literal of this type (e.g. XML dataType)
\end{itemize}

\subsection{Example}

\begin{ex}
# DSP
# ----------
:descriptionTemplate 
    a dsp:DescriptionTemplate ;
    dsp:minOccur "0"^^xsd:nonNegativeInteger ; 
    dsp:maxOccur "infinity"^^xsd:string ; 
    dsp:resourceClass swrc:Book ; 
    dsp:statementTemplate [
        a dsp:NonLiteralStatementTemplate ;
        dsp:minOccur "0"^^xsd:nonNegativeInteger ; 
        dsp:maxOccur "infinity"^^xsd:string ; 
        dsp:property dcterms:subject ; 
        dsp:nonLiteralConstraint [ 
            a dsp:NonLiteralConstraint ;
            dsp:valueClass skos:Concept ;
            dsp:valueURI :ComputerScience, :SocialScience, :Librarianship ] ] .
\end{ex}

\begin{ex}
# OWL2
# ----
dcterms:subject rdfs:range :ObjectOneOf . 
# EquivalentClasses( :ObjectOneOf ObjectOneOf( :ComputerScience :SocialScience :Librarianship ) )
:ObjectOneOf owl:equivalentClass [ 
    a owl:Class ;
    owl:oneOf ( :ComputerScience :SocialScience :Librarianship ) ] .
\end{ex}

\begin{itemize}
	\item the range of the object property dcterms:subject must consist of the individuals :ComputerScience :SocialScience :Librarianship which are of the class skos:Concept
\end{itemize}

\begin{DL}
$\top$ $\sqsubseteq$ $\forall$ dcterms:subject . skos:Concept $\sqcap$ ( $\{ComputerScience\}$ $\sqcup$ \{SocialScience\} $\sqcup$ \{Librarianship\} ) \\
\end{DL}

\subsection{Simple Example}

\begin{DL}
Beatle $\equiv$ \{john\} $\sqcup$ \{paul\} $\sqcup$ \{george\} $\sqcup$ \{ringo\} \\
\end{DL}

\begin{gcotable}
class & Beatle & - & - & $\{john\}$, $\{paul\}$, $\{george\}$, $\{ringo\}$ & $\sqcup$ \\
\end{gcotable}

\subsection{Simple Example}

\begin{DL}
\{ComputerScience\} $\sqcup$ \{SocialScience\} $\sqcup$ \{Librarianship\} \\
\end{DL}

\begin{gcotable}
class & complex concept & - & - & \{ComputerScience\}, \{SocialScience\}, \{Librarianship\} & $\sqcup$ & - \\
\end{gcotable}

\subsection{Simple Example}

\begin{itemize}
	\item Jedis have blue, green, or white laser swords
\end{itemize}

\begin{ex}
# DSP
# ---
:personDescriptionTemplate
    a dsp:DescriptionTemplate ;
    dsp:resourceClass :Jedi ;
    dsp:statementTemplate [
        a dsp:LiteralStatementTemplate ;
        dsp:property :laserSwordColor ;
        dsp:literalConstraint [
            a dsp:LiteralConstraint ;
            dsp:literal "blue" ;
            dsp:literal "green" ;
            dsp:literal "white"] ] .
\end{ex}

\begin{ex}
# OWL2
# ----
:laserSwordColor rdfs:range :laserSwordColors . 
:laserSwordColors
    a rdfs:Datatype .
    owl:oneOf ( "blue" "green" "white" ) .
\end{ex}

\begin{ex}
# ReSh
# ----
:Jedi a rs:ResourceShape ;
    rs:property [
        rs:name "laserSwordColor" ;
        rs:propertyDefinition :laserSwordColor ;
        rs:allowedValue "blue" , "green" , "white" ;
        rs:occurs rs:Exactly-one ;
    ] .
\end{ex}

\begin{ex}
# ShEx
# ----
:Jedi {
    :laserSwordColor ('blue' 'green' 'white') }
\end{ex}

\begin{ex}
# Jedi individuals
# ----------------
:Yoda 
    :laserSwordColor 'blue' .
\end{ex}

\begin{DL}
Jedi $\equiv$ $\exists$ laserSwordColor . \{'blue'\} $\sqcup$ \{'green'\} $\sqcup$ \{'white'\} \\
\end{DL}

\tb{ToDo: check DL}

\section{Not Allowed Values}

requirements:

\begin{itemize}
	\item R-33-NEGATIVE-OBJECT-CONSTRAINTS
	\item R-200-NEGATIVE-LITERAL-CONSTRAINTS
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item not allowed objects
	\item not allowed literals
	\item definition: A matching triple has any literal / object except those explicitly excluded
\end{itemize}

\subsection{Simple Example}

\begin{itemize}
	\item Siths do not have blue, green, or white laser swords
\end{itemize}

\begin{ex}
# DSP
# ---
-
\end{ex}

\begin{ex}
# OWL2
# ----
:laserSwordColor rdfs:range :negativeLaserSwordColors . 
:NegativeLaserSwordColors
    a rdfs:Datatype .
    owl:complementOf :laserSwordColors .
:laserSwordColors
    a rdfs:Datatype .
    owl:oneOf ( "blue" "green" "white" ) .
\end{ex}

\begin{ex}
# ReSh
# ----
-
\end{ex}

\begin{ex}
# ShEx
# ----
:Sith {
    ! :laserSwordColor ('blue' 'green' 'white') }
\end{ex}

\begin{ex}
# Sith individuals
# ----------------
:DarthSidious
    :laserSwordColor 'red' .
\end{ex}

\begin{DL}
Sith $\equiv$ $\neg$( $\exists$ laserSwordColor . \{'blue'\} $\sqcup$ \{'green'\} $\sqcup$ \{'white'\} ) \\
\end{DL}

\tb{ToDo: check DL}

\section{Membership in Controlled Vocabularies}

requirements:

\begin{itemize}
	\item R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES
	\item R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item resources can only be members of listed controlled vocabularies
\end{itemize}

\subsection{Simple Example}

\begin{ex}
# DSCL (DSP)
# ----------
:bookDescriptionTemplate 
    a dsp:DescriptionTemplate ;
    dsp:resourceClass swrc:Book ; 
    dsp:statementTemplate [
        a dsp:NonLiteralStatementTemplate ;
        dsp:property dcterms:subject ; 
        dsp:nonLiteralConstraint [ 
            a dsp:NonLiteralConstraint ;
            dsp:valueClass skos:Concept ; 
            dsp:vocabularyEncodingScheme :BookSubjects, :BookTopics, :BookCategories ] ] .
\end{ex}

\begin{itemize}
	\item \ms{skos:Concept} resources can only be members of the listed controlled vocabularies
\end{itemize}

\begin{DL}
$A \equiv skos:Concept \sqcap B$ \\
$B \equiv \forall skos:inScheme . C$ \\
$C \equiv skos:ConceptScheme \sqcap ( \{:BookSubjects\} \sqcup \{:BookTopics\} \sqcup \{:BookCategories\} )$ \\
\end{DL}

\begin{ex}
# valid data
# ----------
:ArtficialIntelligence
    a swrc:Book ;
    dcterms:subject :ComputerScience .
:ComputerScience
    a skos:Concept ;
    dcam:memberOf :BookSubjects ;
    skos:inScheme :BookSubjects .
:BookSubjects
    a skos:ConceptScheme .
\end{ex}

\begin{ex}
# invalid data
# ------------
:ArtficialIntelligence
    a swrc:Book ;
    dcterms:subject :ComputerScience .
:ComputerScience
    a skos:Concept ;
    dcam:memberOf :BooksAboutBirds ;
    skos:inScheme :BooksAboutBirds ;
    dcam:memberOf :BookSubjects ;
    skos:inScheme :BookSubjects .
:BookSubjects
    a skos:ConceptScheme .
\end{ex}

\begin{itemize}
	\item The related subject (\ms{:ComputerScience}) is a member of a controlled vocabulary (\ms{:BooksAboutBirds}) 
which is not part of the list of allowed controlled vocabularies.
\end{itemize}

\section{IRI Pattern Matching}

requirements:

\begin{itemize}
	\item R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS
  \item R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS
  \item R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item IRI pattern matching on subjects, properties, and objects
\end{itemize}

\section{Literal Pattern Matching}

requirements:

\begin{itemize}
  \item R-44-PATTERN-MATCHING-ON-RDF-LITERALS
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item pattern matching on literals
\end{itemize}

\subsection{Simple Example}

\begin{ex}
# OWL 2 QL (functional-style syntax)
# ----------------------------------
Declaration( Datatype( :SSN ) ) 
DatatypeDefinition( 
    :SSN
    DatatypeRestriction( xsd:string xsd:pattern "[0-9]{3}-[0-9]{2}-[0-9]{4}" ) )     
DataPropertyRange( :hasSSN :SSN ) 
\end{ex}

\begin{ex}
# OWL 2 QL (turtle syntax)
# ------------------------
:SSN 
    a rdfs:Datatype ;
    owl:equivalentClass [
        a rdfs:Datatype ;
        owl:onDatatype xsd:string ;
        owl:withRestrictions ( 
            [ xsd:pattern "[0-9]{3}-[0-9]{2}-[0-9]{4}" ] ) ] .
:hasSSN rdfs:range :SSN .
\end{ex}

\begin{itemize}
	\item A social security number is a string that matches the given regular expression. 
The second axiom defines :SSN as an abbreviation for a datatype restriction on xsd:string. 
The first axiom explicitly declares :SSN to be a datatype. 
The datatype :SSN can be used just like any other datatype; 
for example, it is used in the third axiom to define the range of the :hasSSN property. 
\end{itemize}

\begin{ex}
# valid data
# ----------
:TimBernersLee
    :hasSSN "123-45-6789"^^:SSN .
\end{ex}

\begin{ex}
# invalid data
# ------------
:TimBernersLee
    :hasSSN "123456789"^^:SSN .
\end{ex}

\begin{gcotable}
class & SSN & - & - & xsd:string & xsd:pattern & '[0-9]{3}-[0-9]{2}-[0-9]{4}' \\
\end{gcotable}

\section{Negative Literal Pattern Matching}

requirements:

\begin{itemize}
  \item R-44-PATTERN-MATCHING-ON-RDF-LITERALS
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item negative pattern matching on literals
\end{itemize}

\begin{ex}
# examples
# --------
1. dbo:isbn format is different ’!’ from '^([iIsSbBnN 0-9-])*$'
2. dbo:postCode format is different ‘!’ from 'ˆ[0-9]{5}$'
3. foaf:phone contains any letters ('[A-Za-z]')
\end{ex}

\subsection{Example}

\begin{ex}
# test binding (DQTP)
# -------------------
dbo:isbn format is different ’!’ from '^([iIsSbBnN 0-9-])*$'

P1 => dbo:isbn
NOP => !
REGEX => 'ˆ([iIsSbBnN 0-9-])*$'
\end{ex}

\begin{ex}
# DQTP
# ----
SELECT DISTINCT ?s WHERE { ?s %%P1%% ?value .
    FILTER ( %%NOP%% regex(str(?value), %%REGEX%) ) }
\end{ex}

\begin{itemize}
	\item MATCH Pattern \cite{Kontokostas2014} 
  \item P1 is the property we need to check against REGEX and
NOP can be a not operator (!) or empty.
\end{itemize}

\begin{ex}
# valid data
# ----------
:FoundationsOfSWTechnologies
    dbo:isbn 'ISBN-13 978-1420090505' .
\end{ex}

\begin{ex}
# invalid data
# ------------
:HandbookOfSWTechnologies
    dbo:isbn 'DOI 10.1007/978-3-540-92913-0' .
\end{ex}

\begin{gcotable}
property & $\top$ & dbo:isbn & - & $\neg$ A & domain & - \\
class & $\neg$ A & - & - & A & $\neg$ & - \\
class & A & - & - & xsd:string & regex & 'ˆ([iIsSbBnN 0-9-])*$' $ \\
\end{gcotable}

\section{Literal Value Comparison}

requirement:

\begin{itemize}
	\item R-43-LITERAL-VALUE-COMPARISON
\end{itemize}

\subsection{Description}

examples:

\begin{ex}
# examples
# --------
1. dbo:deathDate before ‘<’ dbo:birthDate
2. dbo:releaseDate after ‘>’ dbo:latestReleaseDate
3. dbo:demolitionDate before ‘<’ dbo:buildingStartDate
\end{ex}

\subsection{Simple Example}

\begin{ex}
# DSCL (DQTP)
# -----------
SELECT ?s WHERE { 
    ?s %%P1%% ?v1 .
    ?s %%P2%% ?v2 .
    FILTER ( ?v1 %%OP%% ?v2 ) }
\end{ex}

COMP Pattern \cite{Kontokostas2014}

Depending on the property semantics,
there are cases where two different literal values must have
a specific ordering with respect to an operator. 
P1 and P2 are the datatype properties we need to compare and 
OP is the comparison operator (\textless, \textless=, \textgreater, \textgreater=, =, !=).

\begin{ex}
# test binding (DQTP)
# -------------------
dbo:deathDate before ‘<’ dbo:birthDate

P1 => dbo:deathDate
P2 => dbo:birthDate
OP => <
\end{ex}

\begin{ex}
# valid data
# ----------
:AlbertEinstein
    dbo:birthDate '1879-03-14'^^xsd:date ;
    dbo:deathDate '1955-04-18'^^xsd:date .
\end{ex}

\begin{ex}
# invalid data
# ------------
:NeilArmstrong
    dbo:birthDate '2012-08-25'^^xsd:date ;
    dbo:deathDate '1930-08-05'^^xsd:date .
\end{ex}

\begin{gcotable}
property & $\top$ & dbo:birthDate & dbo:deathDate & xsd:date & \textgreater & - \\
\end{gcotable}

\section{Negative Literal Ranges}

requirements:

\begin{itemize}
	\item R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item The literal value of a resource (having a certain type) must (not) be within a specific range
  \item P1 is a data property of an instance of class T1 and its literal value must be between the range of [Vmin,Vmax] or outside ( ‘!' ).
\end{itemize}

\subsection{Simple Example}

\begin{itemize}
	\item dbo:height of a dbo:Person is not within [0.4,2.5]
\end{itemize}

\subsection{Simple Example}

\begin{itemize}
	\item geo:lat of a spatial:Feature is not within [-90,90]
\end{itemize}

\subsection{Simple Example}

\begin{itemize}
	\item geo:long of a gml:Feature must be in range [-180,180]
\end{itemize}

\section{Literal Ranges}

requirement:

\begin{itemize}
	\item R-45-RANGES-OF-RDF-LITERAL-VALUES
\end{itemize}

\subsection{Description}

\subsection{Example}

\begin{ex}
# OWL 2 DL (functional-style syntax)
# ----------------------------------
Declaration( Datatype( :NumberPlayersPerWorldCupTeam ) ) 
DatatypeDefinition( 
    :NumberPlayersPerWorldCupTeam
    DatatypeRestriction( 
        xsd:nonNegativeInteger 
        xsd:minInclusive "1"^^xsd:nonNegativeInteger 
        xsd:maxInclusive "23"^^xsd:nonNegativeInteger ) )     
DataPropertyRange( :position :NumberPlayersPerWorldCupTeam ) 
\end{ex}

\begin{ex}
# OWL 2 DL (turtle syntax)
# ------------------------
:NumberPlayersPerWorldCupTeam
    a rdfs:Datatype ;
    owl:equivalentClass [
        a rdfs:Datatype ;
        owl:onDatatype xsd:nonNegativeInteger ;
        owl:withRestrictions ( 
            [ xsd:minInclusive "1"^^xsd:nonNegativeInteger ]
            [ xsd:maxInclusive "23"^^xsd:nonNegativeInteger ] ) ] .
:position rdfs:range :NumberPlayersPerWorldCupTeam .
\end{ex}

\begin{itemize}
	\item The data range 'NumberPlayersPerWorldCupTeam' contains the non negative integers 1 to 23, as each world cup team can only have 23 football players at most
\end{itemize}

\begin{ex}
# valid data
# ----------
:MarioGoetze
    :position "19"^^:NumberPlayersPerWorldCupTeam .
\end{ex}

\begin{ex}
# invalid data
# ------------
:MarioGoetze
    :position "99"^^:NumberPlayersPerWorldCupTeam .
\end{ex}

\begin{itemize}
	\item range of position is the datatype 1-23
  \item constraints are stated on this datatype
\end{itemize}

\begin{DL}
1-23 $\equiv$ \{'1'\} $\sqcup$ \{'2'\} $\sqcup$ ... $\sqcup$ \{'23'\} \\
$\top$ $\sqsubseteq$ $\forall$ position . 1-23 \\
\end{DL}

\begin{gcotable}
class & AtLeast1 & - & - & xsd:nonNegativeInteger & $\geq$ & 1 \\
class & AtMost23 & - & - & xsd:nonNegativeInteger & $\leq$ & 23 \\
class & NumberPlayers... & - & - & AtLeast1, AtMost23 & $\sqcap$ & - \\
property & $\top$ & position & - & NumberPlayers... & range & - \\
\end{gcotable}

or:

\begin{gcotable}
property & $\top$ & position & - & 1-23 & range & - \\
class & 1-23 & - & - & xsd:nonNegativeInteger & $\geq$ & 1 \\
class & 1-23 & - & - & xsd:nonNegativeInteger & $\leq$ & 23 \\
\end{gcotable}

or:

\begin{gcotable}
class & 1-23 & - & - & \{'1'\}, \{'2'\}, ..., \{'23'\} & $\sqcup$ & - \\
property & $\top$ & position & - & 1-23 & range& - \\
\end{gcotable}

\section{Define Order}

requirements:

\begin{itemize}
  \item R-121-SPECIFY-ORDER-OF-RDF-RESOURCES
	\item R-217-DEFINE-ORDER-FOR-FORMS/DISPLAY
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item order properties
	\item order objects of object properties
	\item order literal of data properties
\end{itemize}

\subsection{Simple Example}

\section{Validation Levels}

requirements:

\begin{itemize}
	\item R-205-VARYING-LEVELS-OF-ERROR
	\item R-135-CONSTRAINT-LEVELS
	\item R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS
	\item R-193-MULTIPLE-CONSTRAINT-VALIDATION-EXECUTION-LEVELS
\end{itemize}

\subsection{Description}

\begin{itemize}
  \item Different levels of severity, priority
	\item validation levels: informational, warning, error, fail, should, recommended, must, may, optional, closed (only this) constraints, open (at least this) constraints
\end{itemize}

\subsection{Simple Example}

\section{String Operations}

requirement:

\begin{itemize}
	\item R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item Some constraints require building new strings out of other strings
\end{itemize}

examples:

\begin{itemize}
	\item string length
\end{itemize}

\subsection{Simple Example}

\section{Context-Specific Valid Classes}

requirements:

\begin{itemize}
	\item R-209-VALID-CLASSES
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item What types of resources (rdf:type) are valid in this context? Context can be an input stream, a data creation function, or an API.
\end{itemize}

\subsection{Simple Example}

\section{Context-Specific Valid Properties}

requirements:

\begin{itemize}
	\item R-210-VALID-PROPERTIES
\end{itemize}

\begin{itemize}
	\item What properties can be used within this context? Context can be an data receipt function, data creation function, API, etc.
\end{itemize}

\subsection{Simple Example}

\section{Default Values}

requirements:

\begin{itemize}
	\item R-31-DEFAULT-VALUES-OF-RDF-OBJECTS
  \item R-38-DEFAULT-VALUES-OF-RDF-LITERALS
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item default values for RDF literals
	\item default values for RDF objects
	\item default values are inferred automatically
	\item It should be possible to declare the default value for a given property, e.g. so that input forms can be pre-populated and to insert a required property that is missing in a web service call. 
\end{itemize}

\subsection{Simple Example}

Jedis have only 1 blue laser sword per default.
Siths, in contrast, normally have 2 red laser swords.

\begin{ex}
# rule (SPIN)
# -----------
owl:Thing
    spin:rule [
        a sp:Construct ;
            sp:text """
                CONSTRUCT {            
                    ?this :laserSwordColor "blue"^^xsd:string ;
                    ?this :numberLaserSwords "1"^^xsd:nonNegativeInteger . 
                }
                WHERE {             
                    ?this a :Jedi .            
                } """ ; ] .
owl:Thing
    spin:rule [
        a sp:Construct ;
            sp:text """
                CONSTRUCT {
                    ?this :laserSwordColor "red"^^xsd:string ;
                    ?this :numberLaserSwords "2"^^xsd:nonNegativeInteger . 
                }
                WHERE {             
                    ?this a :Sith .            
                } """ ; ] .
\end{ex}

\begin{ex}
# data
# ----
:Joda a :Jedi .
:DarthSidious a :Sith .
\end{ex}

\begin{ex}
# inferred triples
# ----------------
:Joda 
    :laserSwordColor "blue"^^xsd:string ;
    :numberLaserSwords "1"^^xsd:nonNegativeInteger .
:DarthSidious 
    :laserSwordColor "red"^^xsd:string ;
    :numberLaserSwords "2"^^xsd:nonNegativeInteger .
\end{ex}

\section{Mathematical Operations}

requirements:

\begin{itemize}
	\item R-42-MATHEMATICAL-OPERATIONS
	\item R-41-STATISTICAL-COMPUTATIONS
\end{itemize}

\subsection{Description}

examples:

\begin{itemize}
	\item adding 2 dates
	\item add number of days to start date
	\item area = width * height
	\item Statistical Computations: average, mean, sum
\end{itemize}

\subsection{Simple Example}

\section{Language Tag Matching}

requirement:

\begin{itemize}
	\item R-47-LANGUAGE-TAG-MATCHING
\end{itemize}

\section{Cardinality on Literal Language Tags}

requirements:

\begin{itemize}
	\item R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG
	\item R-48-MISSING-LANGUAGE-TAGS
\end{itemize}

\subsection{Description}

\subsection{Example}

check that no language is used more than once per property

\begin{ex}
# DQTP
# ----
SELECT DISTINCT ?s WHERE { ?s %%P1%% ?c
    BIND ( lang(?c) AS ?l )
    FILTER (isLiteral (?c) && lang(?c) = %%V1%%)}
GROUP BY ?s HAVING COUNT (?l) > 1
\end{ex}

\begin{itemize}
	\item ONELANGPattern \cite{Kontokostas2014} 
  \item A literal value should contain at most 1 literal for a language. 
  \item P1 is the property containing the literal and V1 is the language we want to check.
\end{itemize}

\begin{ex}
# test binding (DQTP)
---------------------
P1 => foaf:name
V1 => en
\end{ex}

\begin{itemize}
	\item a single English (“en”) foaf:name
\end{itemize}

\begin{ex}
# valid data
# ----------
:LeiaSkywalker
    foaf:name 'Leia Skywalker'@en .
\end{ex}

\begin{ex}
# invalid data
# ------------
:LeiaSkywalker
    foaf:name 'Leia Skywalker'@en ;
    foaf:name 'Leia'@en .
\end{ex}

\section{Whitespace Handling}

requirement:

\begin{itemize}
	\item R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item avoid whitespaces in literals neither leading nor trailing white spaces
\end{itemize}

\subsection{Simple Example}

\section{HTML Handling}

requirement:

\begin{itemize}
	\item R-51-HTML-HANDLING-OF-RDF-LITERALS
\end{itemize}

description:

\begin{itemize}
	\item check if there are no html tags included in literals (of specific data properties within the context of specific classes)
\end{itemize}

\subsection{Simple Example}

\section{Required Properties}

requirements:

\begin{itemize}
	\item R-68-REQUIRED-PROPERTIES
\end{itemize}

\subsection{Description}

\subsection{Simple Example}

\section{Optional Properties}

requirements:

\begin{itemize}
	\item R-69-OPTIONAL-PROPERTIES
\end{itemize}

\subsection{Description}

\subsection{Simple Example}

\section{Repeatable Properties}

requirements:

\begin{itemize}
	\item R-70-REPEATABLE-PROPERTIES
\end{itemize}

\subsection{Description}

\subsection{Simple Example}

\section{Conditional Properties}

requirements:

\begin{itemize}
	\item R-71-CONDITIONAL-PROPERTIES
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item various conditions possible
  \item condition: universal quantification on object and data properties
  \item condition: existential quantification on object and data properties
  \item condition: if specific properties are present, then specific other properties also have to be present
\end{itemize}

\subsection{Simple Example}

\section{Recommended Properties}

requirements:

\begin{itemize}
	\item R-72-RECOMMENDED-PROPERTIES
\end{itemize}

\subsection{Description}

\subsection{Simple Example}

\section{Negative Property Constraints}

requirements:

\begin{itemize}
	\item R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS
	\item R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item instances of a specific class must not have some object property
  \item OWL 2 DL: ObjectComplementOf ( ObjectSomeValuesFrom ( ObjectPropertyExpression owl:Thing ) )
\end{itemize}

\subsection{Example}

\begin{ex}
# ShEx
# ----
<FeelingForce> {
    :feelingForce (true) ,
    :attitute xsd:string }
<JediMentor> {
    :feelingForce (true) ,
    :attitute ('good') ,
    :laserSwordColor xsd:string ,
    :numberLaserSwords xsd:nonNegativeInteger ,
    :mentorOf @<JediStudent> ,
   !:studentOf @<JediMentor> }
<JediStudent> {
    :feelingForce (true) ,
    :attitute ('good') ,
    :laserSwordColor xsd:string ,
    :numberLaserSwords xsd:nonNegativeInteger ,
   !:mentorOf @<JediStudent> ,
    :studentOf @<JediMentor> }
\end{ex}

\begin{itemize}
	\item A matching triple has any predicate except those excluded by the '!' operator.
  \item \url{http://w3.org/brief/Mzk0}
\end{itemize}

\begin{ex}
# individuals matching 'FeelingForce' and 'JediMentor' data shapes
# ----------------------------------------------------------------
:Obi-Wan 
    :feelingForce true ;
    :attitute 'good' ;
    :laserSwordColor 'blue' ;
    :numberLaserSwords '1'^^xsd:nonNegativeInteger ;
    :mentorOf :Anakin .
\end{ex}

\begin{ex}
# individuals matching 'FeelingForce' and 'JediStudent' data shapes
# -----------------------------------------------------------------
:Anakin 
    :feelingForce true ;
    :attitute 'good' ;
    :laserSwordColor 'blue' ;
    :numberLaserSwords '1'^^xsd:nonNegativeInteger ;
    :studentOf :Obi-Wan .
\end{ex}

\section{Handle RDF Collections}

requirement:

\begin{itemize}
	\item R-120-HANDLE-RDF-COLLECTIONS
\end{itemize}

\subsection{Description}

examples:

\begin{itemize}
	\item size of collection
	\item first / last element of list must be a specific literal
	\item compare elements of collection
	\item are collections identical?
	\item actions on RDF lists: \url{http://www.snee.com/bobdc.blog/2014/04/rdf-lists-and-sparql.html}
	\item 2. list element equals ''
	\item Does the list have more than 10 elements?
\end{itemize}

\subsection{Example}

\begin{itemize}
	\item get 2. list element
\end{itemize}

\begin{ex}
# SPIN
# ----
:getListItem
    a spin:Function ; rdfs:subClassOf spin:Functions ;
    spin:constraint [
        rdf:type spl:Argument ;
        spl:predicate sp:arg1 ;
        spl:valueType rdf:List ;
        rdfs:comment "list" ; ] ;
    spin:constraint [
        rdf:type spl:Argument ;
        spl:predicate sp:arg2 ;
        spl:valueType xsd:nonNegativeInteger ;
        rdfs:comment "item position (starting with 0)" ; ] ;
    spin:body [
        a sp:SELECT ;
        sp:text """
            SELECT ?item
            WHERE {
                ?arg1 :contents/rdf:rest{?arg2}/rdf:first ?item } """ ; ] ;
    spin:returnType rdfs:Resource .
\end{ex}

\begin{ex}
# data
# ----
:Jinn :students 
     ( :Xanatos :Kenobi ) . 
\end{ex}

\begin{ex}
# SPIN
# ----
BIND ( :getListItem( ?list, "1"xsd:nonNegativeInteger ) AS ?listItem ) .
\end{ex}

\begin{itemize}
  \item SPIN function call
	\item retrieves the 2. item from the list (2. student of Jedi mentor Jinn)
\end{itemize}

\begin{ex}
# result
# ------
:Kenobi
\end{ex}

\section{Recursive Queries}

requirements:

\begin{itemize}
	\item R-222-RECURSIVE-QUERIES
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item If we want to define Resource Shapes, remember that it is a recursive
language (the valueShape of a Resource Shape is in turn another
Resource Shape). There is no way to express that in SPARQL without
hand-waving "and then you call the function again here" or "and then
you embed this operation here" text.  The embedding trick doesn't work
in the general case because SPARQL can't express recursive queries,
e.g. "test that this Issue is valid and all of the Issues that
references, recursively".
  \item Most SPARQL engines already have
functions that go beyond the official SPARQL 1.1 spec. The cost of that
sounds manageable to me.
\end{itemize}

\subsection{Simple Example}

\begin{ex}
# ShEx
# ----
<IssueShape> {
    :state (:unassigned :assigned),
    :reportedBy @<UserShape>,
    :related @<IssueShape>*
}
\end{ex}

\section{Value is Valid for Datatype}

requirements:

\begin{itemize}
	\item 
\end{itemize}

\subsection{Description}

\begin{itemize}
	\item make sure that a value is valid for its datatype
\end{itemize}

\subsection{Simple Example}

\begin{itemize}
	\item a date is really a date
  \item SPARQL regex can be used
\end{itemize}

\subsection{Simple Example}

\begin{ex}
# SPIN
# ----
FILTER ( datatype( ?shoeSize ) = xsd:nonNegativeInteger )
isNumeric ( ?shoeSize )
\end{ex}

\begin{itemize}
	\item datatype of ?showSize id xsd:nonNegativeInteger
	\item datatype is really numeric
\end{itemize}

\section{Individual Equality}

\subsection{Description}

\begin{itemize}
	\item states that two different names are known to refer to the same individual \cite{Kroetzsch2012}
\end{itemize}

\subsection{Simple Example}

\begin{DL}
julia = john \\
\end{DL}

\begin{gcotable}
class & \{julia\} & - & - & \{john\} & = \\
class & \{john\} & - & - & \{julia\} & = \\
\end{gcotable}

\section{Individual Inequality}

\subsection{Description}

\subsection{Simple Example}

\begin{DL}
julia $\ne$ john
\end{DL}

\begin{itemize}
	\item asserts that Julia and John are actually different individuals
\end{itemize}

\begin{gcotable}
class & \{julia\} & - & - & \{john\} & $\ne$ \\
class & \{john\} & - & - & \{julia\} & $\ne$ \\
\end{gcotable}

\section{Equivalent Properties}

\subsection{Description}

\begin{itemize}
	\item An equivalent object properties axiom EquivalentObjectProperties( OPE1 ... OPEn ) states that all of the object property expressions OPEi, 1 $\leq$ i $\leq$ n, are semantically equivalent to each other. This axiom allows one to use each OPEi as a synonym for each OPEj — that is, in any expression in the ontology containing such an axiom, OPEi can be replaced with OPEj without affecting the meaning of the ontology. The axiom EquivalentObjectProperties( OPE1 OPE2 ) is equivalent to the following two axioms SubObjectPropertyOf( OPE1 OPE2 ) and SubObjectPropertyOf( OPE2 OPE1 ).
	\item An equivalent data properties axiom EquivalentDataProperties( DPE1 ... DPEn ) states that all the data property expressions DPEi, 1 $\leq$ i $\leq$ n, are semantically equivalent to each other. This axiom allows one to use each DPEi as a synonym for each DPEj — that is, in any expression in the ontology containing such an axiom, DPEi can be replaced with DPEj without affecting the meaning of the ontology. The axiom EquivalentDataProperties( DPE1 DPE2 ) can be seen as a syntactic shortcut for the following axiom SubDataPropertyOf( DPE1 DPE2 ) and SubDataPropertyOf( DPE2 DPE1 ).

\end{itemize}

\subsection{Simple Example}

\begin{ex}
# OWL 2
# -----
:hasBrother owl:equivalentProperty :hasMaleSibling . 
:Chris :hasBrother :Stewie . 
:Stewie :hasMaleSibling :Chris .
\end{ex}

entailments:

\begin{ex}
:Chris :hasMaleSibling a:Stewie . 
:Stewie :hasBrother a:Chris .
\end{ex}

\begin{DL}
:hasBrother $\sqsubseteq$ :hasMaleSibling $\sqcap$ :hasMaleSibling $\sqsubseteq$ :hasBrother \\
\end{DL}

\section{Property Assertions}

\subsection{Description}

\begin{itemize}
	\item positive property assertions
  \item negative property assertions
	\item A positive object property assertion ObjectPropertyAssertion( OPE a1 a2 ) states that the individual a1 is connected by the object property expression OPE to the individual a2. 
	\item A negative object property assertion NegativeObjectPropertyAssertion( OPE a1 a2 ) states that the individual a1 is not connected by the object property expression OPE to the individual a2. 
	\item A positive data property assertion DataPropertyAssertion( DPE a lt ) states that the individual a is connected by the data property expression DPE to the literal lt. 
	\item A negative data property assertion NegativeDataPropertyAssertion( DPE a lt ) states that the individual a is not connected by the data property expression DPE to the literal lt.
\end{itemize}

\subsection{Simple Example}

\begin{ex}
# OWL 2
# -----
NegativeObjectPropertyAssertion( :hasSon :Peter :Meg )
\end{ex}

\begin{itemize}
	\item Meg is not a son of Peter.
\end{itemize}

\begin{DL}

\end{DL}

\tb{ToDo: DL}

\subsection{Simple Example}

\begin{ex}
# OWL 2
# -----
DataPropertyAssertion( :hasAge :Meg "17"^^xsd:integer )
\end{ex}

\begin{itemize}
	\item Meg is seventeen years old. 
\end{itemize}

\begin{DL}
:hasAge ( :Meg , "17"^^xsd:integer ) \\
\end{DL}

\section{Functional Properties}

\subsection{Description}

\begin{itemize}
	\item An object property functionality axiom FunctionalObjectProperty( OPE ) states that the object property expression OPE is functional — that is, for each individual x, there can be at most one distinct individual y such that x is connected by OPE to y. Each such axiom can be seen as a syntactic shortcut for the following axiom: SubClassOf( owl:Thing ObjectMaxCardinality( 1 OPE ) ).
\end{itemize}

\subsection{Simple Example}

\begin{ex}
# OWL 2
# -----
:hasFather rdf:type owl:FunctionalProperty . 	
:Stewie :hasFather :Peter . 	
:Stewie :hasFather :Peter_Griffin . 
\end{ex}

\begin{itemize}
	\item Each object can have at most one father. 
\end{itemize}

entailment:

\begin{ex}
:Peter_Griffin owl:sameAs :Peter .  
\end{ex}

\begin{DL}
owl:Thing $\sqsubseteq$ $\leq$ 1 :hasFather
\end{DL}

\section{Inverse-Functional Properties}

\subsection{Description}

\begin{itemize}
	\item An object property inverse functionality axiom InverseFunctionalObjectProperty( OPE ) states that the object property expression OPE is inverse-functional — that is, for each individual x, there can be at most one individual y such that y is connected by OPE with x. Each such axiom can be seen as a syntactic shortcut for the following axiom: SubClassOf( owl:Thing ObjectMaxCardinality( 1 ObjectInverseOf( OPE ) ) ).
\end{itemize}

\subsection{Simple Example}

\begin{ex}
# OWL 2
# -----
:fatherOf rdf:type owl:InverseFunctionalProperty . 	
:Peter :fatherOf :Stewie .
:Peter_Griffin :fatherOf :Stewie .
\end{ex}

\begin{itemize}
	\item Each object can have at most one father. 
\end{itemize}

entailment:

\begin{ex}
:Peter owl:sameAs :Peter_Griffin . 
\end{ex}

\begin{DL}

\end{DL}

\tb{ToDo: DL}

\section{Value Restrictions}

\subsection{Description}

\begin{itemize}
	\item Individual Value Restrictions: A has-value class expression ObjectHasValue( OPE a ) consists of an object property expression OPE and an individual a, and it contains all those individuals that are connected by OPE to a. Each such class expression can be seen as a syntactic shortcut for the class expression ObjectSomeValuesFrom( OPE ObjectOneOf( a ) ). 
	\item Literal Value Restrictions: A has-value class expression DataHasValue( DPE lt ) consists of a data property expression DPE and a literal lt, and it contains all those individuals that are connected by DPE to lt. Each such class expression can be seen as a syntactic shortcut for the class expression DataSomeValuesFrom( DPE DataOneOf( lt ) ).
\end{itemize}

\subsection{Simple Example}

\begin{ex}
:Peter :fatherOf :Stewie . 
ObjectHasValue( :fatherOf :Stewie )
\end{ex}

\begin{itemize}
	\item The has-value class expression contains those individuals that are connected through the :fatherOf property with the individual :Stewie
  \item :Peter is classified as its instance
\end{itemize}

\begin{DL}

\end{DL}

\tb{ToDo: DL}

\section{Self Restrictions}

\subsection{Description}

\begin{itemize}
	\item A self-restriction ObjectHasSelf( OPE ) consists of an object property expression OPE, and it contains all those individuals that are connected by OPE to themselves. 
\end{itemize}

\subsection{Simple Example}

\begin{ex}
:Peter :likes :Peter . 
ObjectHasSelf( :likes ) 
\end{ex}

\begin{itemize}
	\item The self-restriction contains those individuals that like themselves
  \item :Peter is classified as its instance
\end{itemize}

\section{Data Property Facets}

requirement:

\begin{itemize}
	\item R-46-CONSTRAINING-FACETS
\end{itemize}

\subsection{Description}

\begin{itemize}
  \item For datatype properties it should be possible to declare frequently needed "facets" to drive user interfaces and validate input against simple conditions, including min/max value, regular expressions, string length etc. similar to XSD datatypes. 
	\item constraining facets to restrict datatypes of RDF literals
  \item constraining facets: xsd:length, xsd:minLength, xsd:maxLength, xsd:pattern, xsd:enumeration, xsd:whiteSpace, xsd:maxInclusive, xsd:maxExclusive, xsd:minExclusive, xsd:minInclusive, xsd:totalDigits, xsd:fractionDigits

\end{itemize}

\subsection{Simple Example}

\textbf{string matches regular expression}

\begin{ex}
# OWL 2 QL (functional-style syntax)
# ----------------------------------
Declaration( Datatype( :SSN ) ) 
DatatypeDefinition( 
    :SSN
    DatatypeRestriction( xsd:string xsd:pattern "[0-9]{3}-[0-9]{2}-[0-9]{4}" ) )     
DataPropertyRange( :hasSSN :SSN ) 
\end{ex}

\begin{ex}
# OWL 2 QL (turtle syntax)
# ------------------------
:SSN 
    a rdfs:Datatype ;
    owl:equivalentClass [
        a rdfs:Datatype ;
        owl:onDatatype xsd:string ;
        owl:withRestrictions ( 
            [ xsd:pattern "[0-9]{3}-[0-9]{2}-[0-9]{4}" ] ) ] .
:hasSSN rdfs:range :SSN .
\end{ex}

\begin{itemize}
	\item A social security number is a string that matches the given regular expression. 
The second axiom defines :SSN as an abbreviation for a datatype restriction on xsd:string. 
The first axiom explicitly declares :SSN to be a datatype. 
The datatype :SSN can be used just like any other datatype; 
for example, it is used in the third axiom to define the range of the :hasSSN property. 
\end{itemize}

\begin{ex}
# valid data
# ----------
:TimBernersLee
    :hasSSN "123-45-6789"^^:SSN .
\end{ex}

\begin{ex}
# invalid data
# ------------
:TimBernersLee
    :hasSSN "123456789"^^:SSN .
\end{ex}

\begin{gcotable}
class & SSN & - & - & xsd:string & xsd:pattern & '[0-9]{3}-[0-9]{2}-[0-9]{4}' \\
\end{gcotable}

\section{Primary Key Properties}

requirement:

\begin{itemize}
	\item 
\end{itemize}

\subsection{Description}

\begin{itemize}
  \item It is often useful to declare a given (datatype) property as the "primary key" of a class, so that the system can enforce uniqueness and also automatically build URIs from user input and data imported from relational databases or spreadsheets. 
\end{itemize}

\subsection{Simple Example}

\begin{itemize}
	\item Each object is uniquely identified by its social security number.
\end{itemize}

\begin{ex}
# DSP
# ---
-
\end{ex}

\begin{ex}
# OWL2 DL
# -------
owl:Thing owl:hasKey ( :hasSSN ) . 	
\end{ex}

\begin{ex}
# ReSh
# ----
-
\end{ex}

\begin{ex}
# ShEx
# ----
-
\end{ex}

\begin{itemize}
	\item The first axiom makes :hasSSN the key for instances of the owl:Thing class; thus, only one individual can have a particular value for :hasSSN. 
\end{itemize}

\begin{ex}
# data
# ----
:Peter :hasSSN "123-45-6789" . 
:PeterGriffin :hasSSN "123-45-6789" . 
\end{ex}

\begin{itemize}
	\item Since the values of :hasSSN are the same for the individuals a:Peter and a:PeterGriffin, these two individuals are equal - that is, this ontology entails the following assertion :Peter owl:sameAs :PeterGriffin . 
\end{itemize}

\begin{DL}

\end{DL}

\tb{ToDo: DL}

\input{DL-Check}

\bibliography{../../literature/literature}{}
\bibliographystyle{plain}
\setcounter{tocdepth}{1}
%\listoftodos
\end{document}

### 2014-12-15 paper/paper 2/paper 2.tex
initial commit

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}

% allows for temporary adjustment of side margins
\usepackage{chngpage}

% just makes the table prettier (see \toprule, \bottomrule, etc. commands below)
\usepackage{booktabs}

\usepackage[utf8]{inputenc}

% URL handling
\usepackage{url}
\urlstyle{same}

% Todos
%\usepackage[colorinlistoftodos]{todonotes}
%\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
%\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}

%\usepackage{makeidx}  % allows for indexgeneration

%\usepackage{amsmath}
\usepackage{amsmath, amssymb}
\usepackage{mathabx}

% monospace within text
\newcommand{\ms}[1]{\texttt{#1}}

% examples
\usepackage{fancyvrb}
\DefineVerbatimEnvironment{ex}{Verbatim}{numbers=left,numbersep=2mm,frame=single,fontsize=\scriptsize}

\newenvironment{gcotable-1}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
  \begin{tabular}{l|l|l|l|l|l}
  \hline
  \textbf{c. type} & \textbf{context concept} & \textbf{p. list} & \textbf{concepts} & \textbf{c. element} & \textbf{c. value} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{gcotable}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
  \begin{tabular}{l|l|l|l|l|l|l}
  \hline
  \textbf{c. type} & \textbf{context concept} & \textbf{left p. list} & \textbf{right p. list} & \textbf{concepts} & \textbf{c. element} & \textbf{c. value} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{DL}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
  \begin{tabular}{l}
	\textbf{DL:} \\

}{
  \end{tabular}
  \linebreak
}

\usepackage{xspace}
% Einfache und doppelte Anfuehrungszeichen
\newcommand{\qs}{``} 
\newcommand{\qe}{''\xspace} 
\newcommand{\sqs}{`} 
\newcommand{\sqe}{'\xspace}

% checkmark
\usepackage{tikz}
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}

% Xs
\usepackage{pifont}

% Tabellenabstände kleiner
\setlength{\intextsep}{10pt} % Vertical space above & below [h] floats
\setlength{\textfloatsep}{10pt} % Vertical space below (above) [t] ([b]) floats
% \setlength{\abovecaptionskip}{0pt}
% \setlength{\belowcaptionskip}{0pt}

\usepackage{tabularx}
\newcommand{\hr}{\hline\noalign{\smallskip}} % für die horizontalen linien in tabellen

% pipe
%\usepackage[T1]{fontenc}

% Todos
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}

\setcounter{secnumdepth}{5}

\begin{document}

%
%
\title{XXXXX}
%
\titlerunning{XXXXX}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{XXXXX\inst{1} \and XXXXX\inst{2}}
%
\authorrunning{XXXXX} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\institute{XXXXX\\
\email{XXXXX},\\ 
\and
XXXXX \\
\email{XXXXX} 
}

\maketitle              % typeset the title of the contribution

\begin{abstract}

\keywords{..}
\end{abstract}
%

% ---------------

\section{Introduction}

\section{Motivation}

At-least restrictions can be expressed either generically by description logics (DL) or specifically by domain-specific constraint languages (DSCL) such as OWL 2, DSP, and ShEx.
With at-least restrictions we can state that having at least 2 female childs is equivalent to having at least 2 daughters. This axiom may be represented by DL in a logical way:

\begin{align*}
Having2Daughters \equiv \geq 2 hasChild.Woman
\end{align*}

The same axiom may also be represented by different DSCLs like OWL 2, DSP, and ShEx:

\begin{ex}
# OWL 2
# -----
:Having2Daughters
    a owl:Restriction ;
    owl:minQualifiedCardinality "2"^^xsd:nonNegativeInteger ;
    owl:onProperty :hasChild ;
    owl:onClass :Woman .

# DSP
# ---			
:descriptionTemplate 
    a dsp:DescriptionTemplate ; 
    dsp:resourceClass :Having2Daughters ; 
    dsp:statementTemplate [
        a dsp:NonLiteralStatementTemplate ;
        dsp:minOccur "1"^^xsd:nonNegativeInteger ; 
        dsp:maxOccur "infinity"^^xsd:string ; 
        dsp:property :hasChild ; 
        dsp:nonLiteralConstraint [ 
            a dsp:NonLiteralConstraint ;
            dsp:valueClass :Woman ] ] .

# ShEx
# ----
<Having2Daughters> {         
    :hasChild @<Woman>{2, }
}
<Woman> {         
    rdf:type (:Woman)
}
\end{ex}

Data, which is valid according to the specified at-least restriction, looks like this:

\begin{ex}
:Marge
    a :Having2Daughters , :Woman ;
    :hasChild :Maggie , :Lisa .
:Maggie
    a :Woman .
:Lisa
    a :Woman .
\end{ex}

If :Marge has only 1 child and if :Marge is assigned to the class :Having2Daughters, a constraint violation is raised for the following invalid data:

\begin{ex}
:Marge
    a :Having2Daughters , :Woman ;
    :hasChild :Lisa .
:Lisa
    a :Woman .
\end{ex}

As there is no standard constraint language, constraint designers may choose different DSCLs in order to express the same at-least restriction. 
When constraint designers choose one DSCL in order to express an arbitrary constraint, it should be possible to transform this constraint into a constraint expressed by any other DSCL. 
This is important as it is often the case that one constraint designer knows to read and to write constraints in one DSCL very well but not in another DSCL. 
This way, constraint designers may communicate with each other without the necessity to understand the other DSCL.

There are validation environments available enabling to automatically validate any RDF constraints expressed by just a few DSCL such as OWL 2 and DSP.
But it should be possible to validate any RDF constraints expressed by any DSCL automatically and what is even more important in the same manner without any differences.

The following table contains the mapping between the at-least restriction expressed by description logics and the at-least restriction expressed by a generic constraint language conforming to an ontology describing constraint languages.
Each constraint is either a constraint on classes or a constraint on properties.

\begin{gcotable}
property & Having2Daughters & hasChild & - & Woman & $\geq$ & 2 \\
\end{gcotable}

The at-least restriction (expressed by the generic constraint language) is represented in RDF as follows:

\begin{ex}
:minCardinalityConstraint
    a gclo:PropertyConstraint ;
    gclo:contextConcept :Having2Daughters ;
    gclo:propertyList ( :hasChild ) ;
    gclo:concept :Woman ;
    gclo:constrainingElement "\geq" ;
    gclo:constrainingValue "2" .
\end{ex}

We implement an automatic validation for any constraint expressed by a generic constraint language conforming to an ontology describing constraint languages.
If we transform a specific constraint (expressed by any DSCL) into a generic constraint (expressed by the generic constraint language), we will be able to validate the generic constraint and therefore the specific constraint immediately. 
As a consequence, we do not have to specify an automatic validation for each specific constraint, as we need to define an automatic validation once for each generic constraint. The underlying SPARQL query is executed within the SPIN validation environment:

\begin{ex}
# constraint
# ----------
?propertyConstraint
    a gclo:PropertyConstraint ;
    gclo:contextConcept ?contextConcept ;
    gclo:propertyList ( ?property ) ;
    gclo:concept ?concept ;
    gclo:constrainingElement ?constrainingElement ;
    gclo:constrainingValue ?constrainingValue .

# data
# ----
?this ?property ?o .
?this rdf:type ?contextConcept .

# validation ( at-least restriction )
# -----
FILTER ( ?constrainingElement = "\geq" ) .
BIND ( owl2spin:qualifiedCardinality( ?this, ?property, ?concept ) AS ?c ) .
BIND( STRDT ( STR ( ?constrainingValue ), xsd:nonNegativeInteger ) AS ?MinimumCardinality )
BIND( STRDT ( STR ( ?c ), xsd:nonNegativeInteger ) AS ?cardinality )
FILTER ( ?cardinality < ?MinimumCardinality ) .		  
\end{ex}

When domain experts use graphical user interfaces to define constraints in a user-friendly way, 
these constraints can be either mapped to either a specific or a generic constraint, as for both an automatic validation is provided in the background.    
So, the user does not have to know how to express specific constraints using a DSCL such as OWL 2, DSP, or ShEx.
If there is a new constraint not covered by any DSCL you can just define the automatic validation for this newly defined constraint.
This way, you are able to extend existing DSCL and to define new DSCL if existing DSCLs are not sufficient for further use cases.

Our \textbf{contributions} of this paper are:
\begin{enumerate}
	\item each constraint (expressed by any DSCL) can be validated automatically
	\item any specific constraint (expressed by any DSCL) can be transformed into a generic constraint (expressed by a generic constraint language)
	\item we developed an ontology describing any constraint language
\end{enumerate}

Benefits:
\begin{itemize}
	\item GCL with only 6 elements
	\item if a language designer develops a new DSCL the language designer only needs to define a mapping between the new DSCL and the GCLO 
	in order to be able to automatically validate the new DSCL constraints
\end{itemize}

\section{Ideas}

idea:
\begin{itemize}
	\item each specific constraint expressed using any domain specific language can be expressed as DL constraint using DL
	\item each DL constraint can be expressed as generic constraint using generic constraint language
	\item meta-model based ontology describing constraints
	\item possible limitation: maybe only typical constraints
\end{itemize}

purpose:
\begin{itemize}
	\item translations of constraints expressed using any domain specific constraint language
\end{itemize}

contributions:
\begin{itemize}
	\item 
\end{itemize}

assumption:
\begin{itemize}
	\item CWA
\end{itemize}

ontology design pattern.org
constraint grammar
constraint elements are the same
DSP uses other design pattern / 
constraint / constraint elements / constraint design patterns / constraint language
define terminology
related to requirements DB / relate requirements to constraints, constraint languages
constraint element: e.g. min cardinality
dependency between requirements / when this requirements is fulfilled then this is also fulfilled (e.g. min card and requ. car)
min car more powerful than req. propery
why ontology? automatic translation from DSP to OWL 
define general constraint language
we do not invent a new constraint languages
requirements in SPARQL umsetzten
only one validation for each requirement
constraints may be composed

\begin{itemize}
	\item any specific constraint (expressed by DSCL) must be mapped to a generic constraint (expressed by GCL)
\end{itemize}

\section{An Ontology Describing Constraint Languages}

fig:generic constraint language ontology.  
\begin{figure}
	\centering
		\includegraphics[width=1.00\textwidth]{generic constraint language ontology/generic constraint language ontology.png}
	\caption{generic constraint language ontology}
	\label{fig:generic constraint language ontology}
\end{figure}

terminology:
\begin{itemize}
	\item A "constraint" is an actual constraint, like dcterms:creator :hasMinCardinality "1" .
  \item a "constraint language" like DSP is used to formulate constraints.
  \item a constraint language consists of "constraint elements" like :hasMinCardinality (this is probably the most controverse definition).
	\item class constraint: constraint on context class
\end{itemize}

\begin{itemize}
	\item relationship to requirement
  \item ontology describing constraint languages
	\item interoperability between constraint languages
  \item express constraint in CL A and translate constraint in CL B
  \item provide SPARQL validation (SPIN mapping) for each general C 
\end{itemize}

\bibliography{../../literature/literature}{}
\bibliographystyle{plain}
\setcounter{tocdepth}{1}
%\listoftodos
\end{document}

### 2014-12-15 paper/paper 5/paper 5.tex
initial commit

--- 2014-12-15 paper/paper 2/paper 2.tex
@@
   \sffamily
-  \vspace{0.3cm}
+  \vspace{0.3cm}\linebreak
   \begin{tabular}{l|l|l|l|l|l}
@@
   \sffamily
-  \vspace{0.3cm}
+  \vspace{0.3cm}\linebreak
   \begin{tabular}{l|l|l|l|l|l|l}
@@
   \sffamily
-  \vspace{0.3cm}
+  \vspace{0.3cm}\linebreak
   \begin{tabular}{l}
@@
 
-\section{Introduction}
+\section{Ideas}
+
+\begin{itemize}
+	\item check quality of thesauri using validation
+\end{itemize}
+
+\textbf{validations:}
+\begin{itemize}
+	\item how far the thesaurus conforms to established ISO norms for thesauri
+	\item hierarchical relations between terms and relations
+	\item classification of terms
+	\item check links to other thesauri: STW Thesaurus for Economics of the ZBW, AGROVOC thesaurus of FAO, DBpedia
+	\item typical knowledge modeling patterns occurring by the use of SKOS and SKOS-XL
+	\item ambiguous terms: equivalence and compound equivalence relationships between preferred and non-preferred terms
+	\item representation of compound relationships and compound concept/ compound concepts are part of the ISO2788 standard
+\end{itemize}
+
+\textbf{validation of datasets conversion to SKOS:}
+\begin{itemize}
+	\item are terms and relations mapped adequately to SKOS class and properties? 
+	\item completeness
+	\item relations between generic and ambiguous terms (having different meanings in specialized contexts) 
+\end{itemize}
+
+\textbf{TheSoz specific validations:}
+\begin{itemize}
+	\item TheSoz extensions / own namespace / TheSoz specific classes and properties
+\end{itemize}
+
+\section{Validations}
+
+\textbf{map term to multiple terms not possible in SKOS:}
+A concept in one thesaurus
+might correspond to a combination of two concepts in
+another thesaurus, e.g. the term "Electronic Government" of the TheSoz has originally been mapped to
+the combination of the terms "Public Administration"
+and "Internet" of the STW. The mapping properties of
+SKOS do not allow such single-to-multiple relations
+(neither for one language nor for multiple languages).
 
@@
 
-At-least restrictions can be expressed either generically by description logics (DL) or specifically by domain-specific constraint languages (DSCL) such as OWL 2, DSP, and ShEx.
-With at-least restrictions we can state that having at least 2 female childs is equivalent to having at least 2 daughters. This axiom may be represented by DL in a logical way:
+\section{Visualization Ideas}
 
-\begin{align*}
-Having2Daughters \equiv \geq 2 hasChild.Woman
-\end{align*}
-
-The same axiom may also be represented by different DSCLs like OWL 2, DSP, and ShEx:
+ich erstelle ja constraint violation triples, die so aussehen:
 
 \begin{ex}
-# OWL 2
-# -----
-:Having2Daughters
-    a owl:Restriction ;
-    owl:minQualifiedCardinality "2"^^xsd:nonNegativeInteger ;
-    owl:onProperty :hasChild ;
-    owl:onClass :Woman .
-
-# DSP
-# ---			
-:descriptionTemplate 
-    a dsp:DescriptionTemplate ; 
-    dsp:resourceClass :Having2Daughters ; 
-    dsp:statementTemplate [
-        a dsp:NonLiteralStatementTemplate ;
-        dsp:minOccur "1"^^xsd:nonNegativeInteger ; 
-        dsp:maxOccur "infinity"^^xsd:string ; 
-        dsp:property :hasChild ; 
-        dsp:nonLiteralConstraint [ 
-            a dsp:NonLiteralConstraint ;
-            dsp:valueClass :Woman ] ] .
-
-# ShEx
-# ----
-<Having2Daughters> {         
-    :hasChild @<Woman>{2, }
-}
-<Woman> {         
-    rdf:type (:Woman)
-}
+CONSTRUCT {
+    _:violation
+        a spin:ConstraintViolation ;
+        rdfs:label ?violationMessage ;
+        spin:violationRoot ?violationRoot ;
+        spin:violationPath ?violationPath ;
+        spin:violationSource ?violationSource ;
+        spin:fix ?violationFix ;
+        :validationLevel :error }
 \end{ex}
 
-Data, which is valid according to the specified at-least restriction, looks like this:
+Auch den validation level möchte ich angeben, da wird es sicher was geben, zumindest irgendwann.
+Ich nutzte in der zwischenzeit spin:validationLevel obwohl es das im spin namespace (noch) nicht gibt, würde aber sehr viel soinn machen.
 
-\begin{ex}
-:Marge
-    a :Having2Daughters , :Woman ;
-    :hasChild :Maggie , :Lisa .
-:Maggie
-    a :Woman .
-:Lisa
-    a :Woman .
-\end{ex}
+Wir haben dann als ergebnis der validierung einen graphen mit constraint validation tripeln.
+diese kann man nach validation level (e.g. error, fail, message, ...) sortieren, unterteilen und auch getrennt visualisieren.
 
-If :Marge has only 1 child and if :Marge is assigned to the class :Having2Daughters, a constraint violation is raised for the following invalid data:
+use case:
+visualisierung nur der wirklich wirklich wichtigen (fail) constraint violation triples
 
-\begin{ex}
-:Marge
-    a :Having2Daughters , :Woman ;
-    :hasChild :Lisa .
-:Lisa
-    a :Woman .
-\end{ex}
+use case:
+visualisierung einer bestimmten constraint violation triple gruppe
 
-As there is no standard constraint language, constraint designers may choose different DSCLs in order to express the same at-least restriction. 
-When constraint designers choose one DSCL in order to express an arbitrary constraint, it should be possible to transform this constraint into a constraint expressed by any other DSCL. 
-This is important as it is often the case that one constraint designer knows to read and to write constraints in one DSCL very well but not in another DSCL. 
-This way, constraint designers may communicate with each other without the necessity to understand the other DSCL.
+-----
+da ich immer auch den root, also das subject von constraint violations mit generiere, kann man auch eine visualisierung erstellen bestimmter rdf subjects, die der grund für constraint violations darstellen, wieder sortiert nach validation level
 
-There are validation environments available enabling to automatically validate any RDF constraints expressed by just a few DSCL such as OWL 2 and DSP.
-But it should be possible to validate any RDF constraints expressed by any DSCL automatically and what is even more important in the same manner without any differences.
+----
+soertierung nach violation source ist auch denkbar, also welche constraint ausgedrückt durch welche DSCL hat welche (wieviele) constraint violations verursacht (spin:violationSource).
 
-The following table contains the mapping between the at-least restriction expressed by description logics and the at-least restriction expressed by a generic constraint language conforming to an ontology describing constraint languages.
-Each constraint is either a constraint on classes or a constraint on properties.
+----
 
-\begin{gcotable}
-property & Having2Daughters & hasChild & - & Woman & $\geq$ & 2 \\
-\end{gcotable}
+spin:fix zeigt auf triple die angeben, wie eine constraint violation behoben werden kann, auch das kann visualisiert werden.
+z.b. eine kette von aktionen, die dazu führen, dass bestimmte constraint violations behoben werden können.
 
-The at-least restriction (expressed by the generic constraint language) is represented in RDF as follows:
+--
 
-\begin{ex}
-:minCardinalityConstraint
-    a gclo:PropertyConstraint ;
-    gclo:contextConcept :Having2Daughters ;
-    gclo:propertyList ( :hasChild ) ;
-    gclo:concept :Woman ;
-    gclo:constrainingElement "\geq" ;
-    gclo:constrainingValue "2" .
-\end{ex}
+das sprudeln die ideen...
 
-We implement an automatic validation for any constraint expressed by a generic constraint language conforming to an ontology describing constraint languages.
-If we transform a specific constraint (expressed by any DSCL) into a generic constraint (expressed by the generic constraint language), we will be able to validate the generic constraint and therefore the specific constraint immediately.
-As a consequence, we do not have to specify an automatic validation for each specific constraint, as we need to define an automatic validation once for each generic constraint.
-The underlying SPARQL query is executed within the SPIN validation environment:
+-----
 
-\begin{ex}
-# constraint
-# ----------
-?propertyConstraint
-    a gclo:PropertyConstraint ;
-    gclo:contextConcept ?contextConcept ;
-    gclo:propertyList ( ?property ) ;
-    gclo:concept ?concept ;
-    gclo:constrainingElement ?constrainingElement ;
-    gclo:constrainingValue ?constrainingValue .
+spin:path --> welche properties sind an einem constraint violation beteiligt.
+hier könnte man einen pfad aufzeigen, der für eine bestimmte constraint violation zeigt, welche properties in welcher reihenflge beteiligt sind.
+eine property chain
 
-# data
-# ----
-?this ?property ?o .
-?this rdf:type ?contextConcept .
+--
 
-# validation ( at-least restriction )
-# -----
-FILTER ( ?constrainingElement = "\geq" ) .
-BIND ( owl2spin:qualifiedCardinality( ?this, ?property, ?concept ) AS ?c ) .
-BIND( STRDT ( STR ( ?constrainingValue ), xsd:nonNegativeInteger ) AS ?MinimumCardinality )
-BIND( STRDT ( STR ( ?c ), xsd:nonNegativeInteger ) AS ?cardinality )
-FILTER ( ?cardinality < ?MinimumCardinality ) .		  
-\end{ex}
+ also mit all diesen generierten informationen lässt sich viel anfangen und sinnvolle dinge visualisieren.
+wir können auch mal drüber sprechen.
 
-When domain experts use graphical user interfaces to define constraints in a user-friendly way, 
-these constraints can be either mapped to either a specific or a generic constraint, as for both an automatic validation is provided in the background.    
-So, the user does not have to know how to express specific constraints using a DSCL such as OWL 2, DSP, or ShEx.
-If there is a new constraint not covered by any DSCL you can just define the automatic validation for this newly defined constraint.
-This way, you are able to extend existing DSCL and to define new DSCL if existing DSCLs are not sufficient for further use cases.
+---
+macht es sinn auch die constraints selber zu visualisieren?
 
-Our \textbf{contributions} of this paper are:
-\begin{enumerate}
-	\item each constraint (expressed by any DSCL) can be validated automatically
-	\item any specific constraint (expressed by any DSCL) can be transformed into a generic constraint (expressed by a generic constraint language)
-	\item we developed an ontology describing any constraint language
-\end{enumerate}
+- welche constraints gibt es die für eine bestimmte DSCL in SPIN definiert wurden?
+- wenn eine specific constraint aug eine generic constraint gemappt wird, können wir visualisieren wie spezifische constraints zueinander in beziehung stehen und auch zu anderen spezifischen constraints anderer DSCLs
+- macht eine visualisierung der SPARQL queries sinn die verwendet werden constraints zu validieren?
+- welche specific und generic constraints sind welchen requirements zugeordnet, kömnte auch visualisiert werden...
 
-Benefits:
-\begin{itemize}
-	\item GCL with only 6 elements
-	\item if a language designer develops a new DSCL the language designer only needs to define a mapping between the new DSCL and the GCLO 
-	in order to be able to automatically validate the new DSCL constraints
-\end{itemize}
-
-\section{Ideas}
-
-idea:
-\begin{itemize}
-	\item each specific constraint expressed using any domain specific language can be expressed as DL constraint using DL
-	\item each DL constraint can be expressed as generic constraint using generic constraint language
-	\item meta-model based ontology describing constraints
-	\item possible limitation: maybe only typical constraints
-\end{itemize}
-
-purpose:
-\begin{itemize}
-	\item translations of constraints expressed using any domain specific constraint language
-\end{itemize}
-
-contributions:
-\begin{itemize}
-	\item 
-\end{itemize}
-
-assumption:
-\begin{itemize}
-	\item CWA
-\end{itemize}
-
-ontology design pattern.org
-constraint grammar
-constraint elements are the same
-DSP uses other design pattern / 
-constraint / constraint elements / constraint design patterns / constraint language
-define terminology
-related to requirements DB / relate requirements to constraints, constraint languages
-constraint element: e.g. min cardinality
-dependency between requirements / when this requirements is fulfilled then this is also fulfilled (e.g. min card and requ. car)
-min car more powerful than req. propery
-why ontology? automatic translation from DSP to OWL 
-define general constraint language
-we do not invent a new constraint languages
-requirements in SPARQL umsetzten
-only one validation for each requirement
-constraints may be composed
-
-\begin{itemize}
-	\item any specific constraint (expressed by DSCL) must be mapped to a generic constraint (expressed by GCL)
-\end{itemize}
-
-\section{An Ontology Describing Constraint Languages}
-
-fig:generic constraint language ontology.  
-\begin{figure}
-	\centering
-		\includegraphics[width=1.00\textwidth]{generic constraint language ontology/generic constraint language ontology.png}
-	\caption{generic constraint language ontology}
-	\label{fig:generic constraint language ontology}
-\end{figure}
-
-terminology:
-\begin{itemize}
-	\item A "constraint" is an actual constraint, like dcterms:creator :hasMinCardinality "1" .
-  \item a "constraint language" like DSP is used to formulate constraints.
-  \item a constraint language consists of "constraint elements" like :hasMinCardinality (this is probably the most controverse definition).
-	\item class constraint: constraint on context class
-\end{itemize}
-
-\begin{itemize}
-	\item relationship to requirement
-  \item ontology describing constraint languages
-	\item interoperability between constraint languages
-  \item express constraint in CL A and translate constraint in CL B
-  \item provide SPARQL validation (SPIN mapping) for each general C 
-\end{itemize}
+ich denke das reicht jetzt erst mal....
 

### 2014-12-15 paper/paper 1/paper 1 (appendix).tex
extra tex file for appendix

--- 2014-12-15 paper/paper 2/paper 2.tex
@@
 
-\newenvironment{gcotable-1}{
-  \scriptsize
-  \sffamily
-  \vspace{0.3cm}
-  \begin{tabular}{l|l|l|l|l|l}
-  \hline
-  \textbf{c. type} & \textbf{context concept} & \textbf{p. list} & \textbf{concepts} & \textbf{c. element} & \textbf{c. value} \\
-  \hline
-
-}{
-  \hline
-  \end{tabular}
-  \linebreak
-}
-
-\newenvironment{gcotable}{
-  \scriptsize
-  \sffamily
-  \vspace{0.3cm}
-  \begin{tabular}{l|l|l|l|l|l|l}
-  \hline
-  \textbf{c. type} & \textbf{context concept} & \textbf{left p. list} & \textbf{right p. list} & \textbf{concepts} & \textbf{c. element} & \textbf{c. value} \\
-  \hline
-
-}{
-  \hline
-  \end{tabular}
-  \linebreak
-}
-
-\newenvironment{DL}{
-  \scriptsize
-  \sffamily
-  \vspace{0.3cm}
-  \begin{tabular}{l}
-	\textbf{DL:} \\
-
-}{
-  \end{tabular}
-  \linebreak
-}
-
 \usepackage{xspace}
@@
 
-% pipe
-%\usepackage[T1]{fontenc}
-
 % Todos
@@
 \newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}
+
+\newenvironment{table-1cols}{
+  \scriptsize
+  \sffamily
+  \vspace{0.3cm}
+  \begin{tabular}{l}
+  \hline
+  \textbf{Requirements} \\
+  \hline
+
+}{
+  \hline
+  \end{tabular}
+  \linebreak
+}
+
+\newenvironment{table-2cols}{
+  \scriptsize
+  \sffamily
+  \vspace{0.3cm}
+  \begin{tabular}{l|l}
+  \hline
+  \textbf{Requirements} & \textbf{Covering DSCLs} \\
+  \hline
+
+}{
+  \hline
+  \end{tabular}
+  \linebreak
+}
+
+\newenvironment{DL}{
+  \scriptsize
+  \sffamily
+  \vspace{0.3cm}
+  \begin{tabular}{l}
+	\textbf{DL:} \\
+
+}{
+  \end{tabular}
+  \linebreak
+}
 
@@
 
-% ---------------
+\section{Appendix}
 
-\section{Introduction}
+\subsection{Allowed Usage of Constructs in Class Expressions in OWL 2 QL}
 
-\section{Motivation}
-
-At-least restrictions can be expressed either generically by description logics (DL) or specifically by domain-specific constraint languages (DSCL) such as OWL 2, DSP, and ShEx.
-With at-least restrictions we can state that having at least 2 female childs is equivalent to having at least 2 daughters. This axiom may be represented by DL in a logical way:
-
-\begin{align*}
-Having2Daughters \equiv \geq 2 hasChild.Woman
-\end{align*}
-
-The same axiom may also be represented by different DSCLs like OWL 2, DSP, and ShEx:
+\textbf{Subclass Expressions}
 
 \begin{ex}
-# OWL 2
-# -----
-:Having2Daughters
-    a owl:Restriction ;
-    owl:minQualifiedCardinality "2"^^xsd:nonNegativeInteger ;
-    owl:onProperty :hasChild ;
-    owl:onClass :Woman .
-
-# DSP
-# ---			
-:descriptionTemplate 
-    a dsp:DescriptionTemplate ; 
-    dsp:resourceClass :Having2Daughters ; 
-    dsp:statementTemplate [
-        a dsp:NonLiteralStatementTemplate ;
-        dsp:minOccur "1"^^xsd:nonNegativeInteger ; 
-        dsp:maxOccur "infinity"^^xsd:string ; 
-        dsp:property :hasChild ; 
-        dsp:nonLiteralConstraint [ 
-            a dsp:NonLiteralConstraint ;
-            dsp:valueClass :Woman ] ] .
-
-# ShEx
-# ----
-<Having2Daughters> {         
-    :hasChild @<Woman>{2, }
-}
-<Woman> {         
-    rdf:type (:Woman)
-}
+subClassExpression :=
+    Class |
+    subObjectSomeValuesFrom | DataSomeValuesFrom
+subObjectSomeValuesFrom := 'ObjectSomeValuesFrom' '(' ObjectPropertyExpression owl:Thing ')'
 \end{ex}
 
-Data, which is valid according to the specified at-least restriction, looks like this:
+\textbf{Superclass Expressions}
 
 \begin{ex}
-:Marge
-    a :Having2Daughters , :Woman ;
-    :hasChild :Maggie , :Lisa .
-:Maggie
-    a :Woman .
-:Lisa
-    a :Woman .
+superClassExpression :=
+    Class |
+    superObjectIntersectionOf | superObjectComplementOf |
+    superObjectSomeValuesFrom | DataSomeValuesFrom
 \end{ex}
 
-If :Marge has only 1 child and if :Marge is assigned to the class :Having2Daughters, a constraint violation is raised for the following invalid data:
+\subsection{Supported Constructs in OWL 2 QL}
 
-\begin{ex}
-:Marge
-    a :Having2Daughters , :Woman ;
-    :hasChild :Lisa .
-:Lisa
-    a :Woman .
-\end{ex}
-
-As there is no standard constraint language, constraint designers may choose different DSCLs in order to express the same at-least restriction. 
-When constraint designers choose one DSCL in order to express an arbitrary constraint, it should be possible to transform this constraint into a constraint expressed by any other DSCL. 
-This is important as it is often the case that one constraint designer knows to read and to write constraints in one DSCL very well but not in another DSCL. 
-This way, constraint designers may communicate with each other without the necessity to understand the other DSCL.
-
-There are validation environments available enabling to automatically validate any RDF constraints expressed by just a few DSCL such as OWL 2 and DSP.
-But it should be possible to validate any RDF constraints expressed by any DSCL automatically and what is even more important in the same manner without any differences.
-
-The following table contains the mapping between the at-least restriction expressed by description logics and the at-least restriction expressed by a generic constraint language conforming to an ontology describing constraint languages.
-Each constraint is either a constraint on classes or a constraint on properties.
-
-\begin{gcotable}
-property & Having2Daughters & hasChild & - & Woman & $\geq$ & 2 \\
-\end{gcotable}
-
-The at-least restriction (expressed by the generic constraint language) is represented in RDF as follows:
-
-\begin{ex}
-:minCardinalityConstraint
-    a gclo:PropertyConstraint ;
-    gclo:contextConcept :Having2Daughters ;
-    gclo:propertyList ( :hasChild ) ;
-    gclo:concept :Woman ;
-    gclo:constrainingElement "\geq" ;
-    gclo:constrainingValue "2" .
-\end{ex}
-
-We implement an automatic validation for any constraint expressed by a generic constraint language conforming to an ontology describing constraint languages.
-If we transform a specific constraint (expressed by any DSCL) into a generic constraint (expressed by the generic constraint language), we will be able to validate the generic constraint and therefore the specific constraint immediately.
-As a consequence, we do not have to specify an automatic validation for each specific constraint, as we need to define an automatic validation once for each generic constraint.
-The underlying SPARQL query is executed within the SPIN validation environment:
-
-\begin{ex}
-# constraint
-# ----------
-?propertyConstraint
-    a gclo:PropertyConstraint ;
-    gclo:contextConcept ?contextConcept ;
-    gclo:propertyList ( ?property ) ;
-    gclo:concept ?concept ;
-    gclo:constrainingElement ?constrainingElement ;
-    gclo:constrainingValue ?constrainingValue .
-
-# data
-# ----
-?this ?property ?o .
-?this rdf:type ?contextConcept .
-
-# validation ( at-least restriction )
-# -----
-FILTER ( ?constrainingElement = "\geq" ) .
-BIND ( owl2spin:qualifiedCardinality( ?this, ?property, ?concept ) AS ?c ) .
-BIND( STRDT ( STR ( ?constrainingValue ), xsd:nonNegativeInteger ) AS ?MinimumCardinality )
-BIND( STRDT ( STR ( ?c ), xsd:nonNegativeInteger ) AS ?cardinality )
-FILTER ( ?cardinality < ?MinimumCardinality ) .		  
-\end{ex}
-
-When domain experts use graphical user interfaces to define constraints in a user-friendly way, 
-these constraints can be either mapped to either a specific or a generic constraint, as for both an automatic validation is provided in the background.    
-So, the user does not have to know how to express specific constraints using a DSCL such as OWL 2, DSP, or ShEx.
-If there is a new constraint not covered by any DSCL you can just define the automatic validation for this newly defined constraint.
-This way, you are able to extend existing DSCL and to define new DSCL if existing DSCLs are not sufficient for further use cases.
-
-Our \textbf{contributions} of this paper are:
-\begin{enumerate}
-	\item each constraint (expressed by any DSCL) can be validated automatically
-	\item any specific constraint (expressed by any DSCL) can be transformed into a generic constraint (expressed by a generic constraint language)
-	\item we developed an ontology describing any constraint language
-\end{enumerate}
-
-Benefits:
 \begin{itemize}
-	\item GCL with only 6 elements
-	\item if a language designer develops a new DSCL the language designer only needs to define a mapping between the new DSCL and the GCLO 
-	in order to be able to automatically validate the new DSCL constraints
+	\item subclass axioms (SubClassOf)
+  \item class expression equivalence (EquivalentClasses)
+  \item class expression disjointness (DisjointClasses)
+  \item inverse object properties (InverseObjectProperties)
+  \item property inclusion (SubObjectPropertyOf not involving property chains and SubDataPropertyOf)
+  \item property equivalence (EquivalentObjectProperties and EquivalentDataProperties)
+  \item property domain (ObjectPropertyDomain and DataPropertyDomain)
+  \item property range (ObjectPropertyRange and DataPropertyRange)
+  \item disjoint properties (DisjointObjectProperties and DisjointDataProperties)
+  \item symmetric properties (SymmetricObjectProperty)
+  \item reflexive properties (ReflexiveObjectProperty)
+  \item irreflexive properties (IrreflexiveObjectProperty)
+  \item asymmetric properties (AsymmetricObjectProperty)
+  \item assertions: DifferentIndividuals, ClassAssertion, ObjectPropertyAssertion, and DataPropertyAssertion
 \end{itemize}
 
-\section{Ideas}
-
-idea:
-\begin{itemize}
-	\item each specific constraint expressed using any domain specific language can be expressed as DL constraint using DL
-	\item each DL constraint can be expressed as generic constraint using generic constraint language
-	\item meta-model based ontology describing constraints
-	\item possible limitation: maybe only typical constraints
-\end{itemize}
-
-purpose:
-\begin{itemize}
-	\item translations of constraints expressed using any domain specific constraint language
-\end{itemize}
-
-contributions:
-\begin{itemize}
-	\item 
-\end{itemize}
-
-assumption:
-\begin{itemize}
-	\item CWA
-\end{itemize}
-
-ontology design pattern.org
-constraint grammar
-constraint elements are the same
-DSP uses other design pattern / 
-constraint / constraint elements / constraint design patterns / constraint language
-define terminology
-related to requirements DB / relate requirements to constraints, constraint languages
-constraint element: e.g. min cardinality
-dependency between requirements / when this requirements is fulfilled then this is also fulfilled (e.g. min card and requ. car)
-min car more powerful than req. propery
-why ontology? automatic translation from DSP to OWL 
-define general constraint language
-we do not invent a new constraint languages
-requirements in SPARQL umsetzten
-only one validation for each requirement
-constraints may be composed
+\subsection{Not Supported Constructs in OWL 2 QL}
 
 \begin{itemize}
-	\item any specific constraint (expressed by DSCL) must be mapped to a generic constraint (expressed by GCL)
-\end{itemize}
-
-\section{An Ontology Describing Constraint Languages}
-
-fig:generic constraint language ontology.  
-\begin{figure}
-	\centering
-		\includegraphics[width=1.00\textwidth]{generic constraint language ontology/generic constraint language ontology.png}
-	\caption{generic constraint language ontology}
-	\label{fig:generic constraint language ontology}
-\end{figure}
-
-terminology:
-\begin{itemize}
-	\item A "constraint" is an actual constraint, like dcterms:creator :hasMinCardinality "1" .
-  \item a "constraint language" like DSP is used to formulate constraints.
-  \item a constraint language consists of "constraint elements" like :hasMinCardinality (this is probably the most controverse definition).
-	\item class constraint: constraint on context class
-\end{itemize}
-
-\begin{itemize}
-	\item relationship to requirement
-  \item ontology describing constraint languages
-	\item interoperability between constraint languages
-  \item express constraint in CL A and translate constraint in CL B
-  \item provide SPARQL validation (SPIN mapping) for each general C 
+	\item existential quantification to a class expression or a data range (ObjectSomeValuesFrom and DataSomeValuesFrom) in the subclass position
+  \item self-restriction (ObjectHasSelf)
+  \item existential quantification to an individual or a literal (ObjectHasValue, DataHasValue)
+  \item enumeration of individuals and literals (ObjectOneOf, DataOneOf)
+  \item universal quantification to a class expression or a data range (ObjectAllValuesFrom, DataAllValuesFrom)
+  \item cardinality restrictions (ObjectMaxCardinality, ObjectMinCardinality, ObjectExactCardinality, DataMaxCardinality, DataMinCardinality, DataExactCardinality)
+  \item disjunction (ObjectUnionOf, DisjointUnion, and DataUnionOf)
+  \item property inclusions (SubObjectPropertyOf) involving property chains
+  \item functional and inverse-functional properties (FunctionalObjectProperty, InverseFunctionalObjectProperty, and FunctionalDataProperty)
+  \item transitive properties (TransitiveObjectProperty)
+  \item keys (HasKey)
+  \item individual equality assertions and negative property assertions (SameIndividual, NegativeObjectPropertyAssertion, NegativeDataPropertyAssertion)
 \end{itemize}

### 2014-12-15 paper/RDF validation requirements/RDF validation and inferencing.tex
validation and inferencing

--- 2014-12-15 paper/RDF validation requirements/RDF validation requirements.tex
@@
 \newenvironment{DL}{
-  \scriptsize
   \sffamily
@@
   \begin{tabular}{l}
-	\textbf{DL:} \\
 
@@
 
-\section{Motivation}
+\section{Property Domain}
 
-\begin{itemize}
-	\item mappings from RDF validation requirements (more specifically RDF constraint formulation requirements) to DL
-	\item mappings from RDF validation requirements (more specifically RDF constraint formulation requirements) to generic constraints (expressed by generic constraint language)
-\end{itemize}
-
-\tb{I think we should provide mappings to DL directly in the requirements chapters and not just in 1 table at the end of the paper}
-
-\section{Subsumption}
-
-requirement:
-
-\begin{itemize}
-	\item R-100-SUBSUMPTION
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item DL terminology: concept inclusion
-\end{itemize}
-
-\subsection{Simple Example}
+The property domain constraint
 
 \begin{DL}
-Mother $\sqsubseteq$ Parent 
+$\exists$ :studentOf . $\top$ $\sqsubseteq$ :JediStudent 
 \end{DL}
 
-\begin{itemize}
-	\item all mothers are parents
-  \item the concept Mother is subsumed by the concept Parent
-\end{itemize}
-
-\begin{gcotable}
-class & Mother & - & - & Parent & $\sqsubseteq$ \\
-\end{gcotable}
-
-\subsection{Simple Example}
-
-\begin{itemize}
-	\item Jedis feel the force 
-\end{itemize}
+restricts that individuals having :studentOf relationships must be Jedi students.
+This property domain constraint can also be expressed by OWL 2 QL:
 
 \begin{ex}
-# DSP
-# ---
--
+:studentOf rdfs:domain :JediStudent .
 \end{ex}
 
-\begin{ex}
-# OWL2
-# ----
-:Jedi rdfs:subClassOf :FeelingForce .
-\end{ex}
+Without reasoning, the data \ms{:Anakin :studentOf :Obi-Wan} is invalid and causes a constraint violation, as it is not explicitly stated that \ms{:Anakin} is assigned to the class \ms{:Jedi}. 
+When inferencing is performed before validating, the class assignment \ms{:Anakin rdf:type :Jedi} is inferred which prevents the constraint violation to be raised.
 
-\begin{ex}
-# ReSh
-# ----
-the extension ext:extendsShape may be used
-\end{ex}
+\tb{complexity with OWL 2 QL inferencing?}
 
-\begin{ex}
-# ShEx
-# ----
-:FeelingForce {
-    :feelingForce (true) }
-:Jedi {
-    & :FeelingForce ,
-    :attitute ('good') }
-\end{ex}
-
-\begin{ex}
-# data
-# ----
-:Yoda 
-    :feelingForce true ;
-    :attitute 'good' .
-\end{ex}
-
-\begin{DL}
-:Jedi $\sqsubseteq$ :FeelingForce
-\end{DL}
-
-\subsection{Complex Example}
-
-\begin{DL}
-Rich $\sqsubseteq$ $\neg$ Poor 
-\end{DL}
-
-\begin{gcotable}
-class & $\neg$ Poor & - & - & Poor & $\neg$ \\
-class & Rich & - & - & $\neg$ Poor & $\sqsubseteq$ \\
-\end{gcotable}
-
-\section{Class Equivalence}
-
-requirement:
-
-\begin{itemize}
-	\item R-3-EQUIVALENT-CLASSES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item Concept equivalence asserts that two concepts have the same instances \cite{Kroetzsch2012}
-  \item While synonyms are an obvious example of equivalent concepts, in practice one more
-often uses concept equivalence to give a name to complex expression  \cite{Kroetzsch2012}
-\item Concept equivalence is indeed subsumption  from left and right. ($A \sqsubseteq B$ and $B \sqsubseteq A$ implies $A \equiv B$ )
-
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{DL}
-Person $\equiv$ Human
-\end{DL}
-
-\begin{gcotable}
-class & Person & - & - & Human & $\equiv$ \\
-class & Human & - & - & Person & $\equiv$ \\
-\end{gcotable}
-
-maybe better:
-\er{It is not better since we should stick to what we use as syntax.}
-
-\begin{gcotable}
-class & Person & - & - & Human & $\sqsubseteq$ \\
-class & Human & - & - & Person & $\sqsubseteq$ \\
-\end{gcotable}
-\section{Sub Object Properties}
-
-requirements:
-
-\begin{itemize}
-
-	\item R-54-SUB-OBJECT-PROPERTIES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item DL terminology: role inclusion 
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{DL}
-parentOf $\sqsubseteq$ ancestorOf 
-\end{DL}
-
-\begin{itemize}
-	\item states that parentOf is a subrole of ancestorOf , i.e., every pair of individuals related by parentOf is also related by ancestorOf
-\end{itemize}
-
-\begin{gcotable}
-property & parentOf & ancestorOf & - & - & $\sqsubseteq$ \\
-\end{gcotable}
-
-better:
-
-\begin{gcotable}
-property & $\top$ & parentOf & ancestorOf & $\top$ & $\sqsubseteq$ \\
-\end{gcotable}
-
-%\subsection{Simple Example}
-
-%\begin{DL}
-%sitsOn $\sqsubseteq$ touches 
-%\end{DL}
-
-\subsection{Simple Example}
-
-\begin{DL}
-hasDog $\sqsubseteq$ hasPet 
-\end{DL}
-
-\section{Sub Data Properties}
-
-requirements:
-
-\begin{itemize}
-
-	\item R-54-SUB-DATA-PROPERTIES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item DL terminology: concrete domains functional roles  
-\end{itemize}
-
-\subsection{Simple Example}
-\begin{DL}
- $Person \sqcap  \forall hasAge. \leq_{10} \sqsubseteq Person \sqcap \forall hasEvenAge. \leq_{10}$ 
-\end{DL}
-
-\section{Object Property Paths / Object Property Chains}
-
-requirement:
-
-\begin{itemize}
-	\item R-55-OBJECT-PROPERTY-PATHS
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-  \item DL terminology: complex role inclusion axiom / role composition
-	\item role composition can only appear on the left-hand side of complex role inclusions \cite{Kroetzsch2012}
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{DL}
-brotherOf $\circ$ parentOf $\sqsubseteq$ uncleOf 
-\end{DL}
-
-\begin{ex}
-# OWL2
-# ----
-:uncleOf owl:propertyChainAxiom ( :brotherOf :parentOf ) . 
-\end{ex}
-
-\begin{gcotable}
-property & $\top$ & brotherOf, parentOf & uncleOf & $\top$ & $\sqsubseteq$ & -  \\
-\end{gcotable}
-
-old mapping:
-
-\begin{gcotable}
-property & uncleOf & brotherOf, parentOf & - & $\top$ & $\sqsubseteq$ \\
-\end{gcotable}
-
-\section{Disjoint Properties}
-
-requirements:
-
-\begin{itemize}
-	\item R-9-DISJOINT-PROPERTIES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{DL}
-Disjoint(parentOf, childOf)
-\end{DL}
-
-\begin{gcotable}
-property & $\top$ & parentOf & childOf & $\top$ & $\ne$ \\
-\end{gcotable}
-
-\section{Intersection}
-
-requirements:
-
-\begin{itemize}
-  \item R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS
-	\item R-16-CONJUNCTION-OF-DATA-RANGES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item composition / conjunction
-\end{itemize}
-
-DLs allow new concepts and roles to be
-built using a variety of different constructors. We distinguish concept and role 
-constructors depending on whether concept or role expressions are constructed. In the case of
-concepts, one can further separate basic Boolean constructors, role restrictions and nominals/enumerations \cite{Kroetzsch2012}.
-
-Boolean concept constructors provide basic boolean operations that are closely related to
-the familiar operations of intersection, union and complement of sets, or to conjunction,
-disjunction and negation of logical expressions \cite{Kroetzsch2012}.
-
-\begin{DL}
-Mother $\equiv$ Female $\sqcap$ Parent
-\end{DL}
-
-concept inclusions allow us to state that all mothers are female and that
-all mothers are parents, but what we really mean is that mothers are exactly the female
-parents. DLs support such statements by allowing us to form complex concepts such as
-the intersection (also called conjunction)
-which denotes the set of individuals that are both female and parents. A complex concept
-can be used in axioms in exactly the same way as an atomic concept, e.g., in the
-equivalence Mother $\equiv$ Female $\sqcap$ Parent .
-
-\subsection{Simple Example}
-
-\begin{DL}
-Female $\sqcap$ Parent
-\end{DL}
-
-\begin{itemize}
-	\item complex concept of all individuals which are of the concept Female and of the concept Parent
-\end{itemize}
-
-\begin{gcotable}
-class & Female $\sqcap$ Parent & - & - & Female, Parent & $\sqcap$ \\
-\end{gcotable}
-
-\begin{DL}
-Mother $\equiv$ Female $\sqcap$ Parent
-\end{DL}
-
-\begin{gcotable}
-class & Mother & - & - & Female, Parent & $\sqcap$ \\
-\end{gcotable}
-
-\section{Disjunction}
-
-requirements:
-
-\begin{itemize}
-	\item R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS
-	\item R-18-DISJUNCTION-OF-DATA-RANGES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item union / inclusive OR
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{DL}
-Father $\sqcup$ Mother $\sqcup$ Child
-\end{DL}
-
-\begin{gcotable}
-class & complex concept & - & - & Father, Mother, Child & $\sqcup$ \\
-\end{gcotable}
-
-\subsection{Simple Example}
-
-\begin{DL}
-Parent $\equiv$ Father $\sqcup$ Mother
-\end{DL}
-
-\begin{gcotable}
-class & Parent & - & - & Father, Mother & $\sqcup$ \\
-\end{gcotable}
-
-\section{Negation}
-
-requirements:
-
-\begin{itemize}
-  \item R-19-NEGATION-OF-CLASS-EXPRESSIONS
-	\item R-20-NEGATION-OF-DATA-RANGES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item complement
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{DL}
-$ \neg Married $ \\ 
-\end{DL}
-
-\begin{itemize}
-	\item set of all individuals that are not married
-\end{itemize}
-
-\begin{gcotable}
-class & $\neg$ Married & - & - & Married & $\neg$ \\
-\end{gcotable}
-
-\subsection{Complex Example}
-
-\begin{DL}
-Female $\sqcap$ $\neg$ Married \\
-\end{DL}
-
-\begin{gcotable}
-class & $\neg$ Married & - & - & Married & $\neg$ \\
-class & Female $\sqcap$ $\neg$ Married & - & - & Female, $\neg$ Married & $\sqcap$ \\
-\end{gcotable}
-
-\section{Disjoint Classes}
-
-requirements:
-
-\begin{itemize}
-	\item R-7-DISJOINT-CLASSES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{DL}
-Male $\sqcap$ Female $\sqsubseteq$ $\perp$
-\end{DL}
-
-\begin{gcotable}
-class & Male $\sqcap$ Female & - & - & Male, Female & $\sqcap$  \\
-class & $\top$ & - & - & Male $\sqcap$ Female, $\perp$ & $\sqsubseteq$ \\
-\end{gcotable}
-
-syntactic sugar:
-
-\begin{gcotable}
-class & Male & - & - & Female & $\ne$ \\
-class & Female & - & - & Male & $\ne$ \\
-\end{gcotable}
-
-\section{Existential Quantification on Properties}
-
-requirements:
-
-\begin{itemize}
-	\item R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item DL termonology: existential restriction
-	\item An existential class expression ObjectSomeValuesFrom( OPE CE ) consists of an object property expression OPE and a class expression CE, and it contains all those individuals that are connected by OPE to an individual that is an instance of CE.
-Such a class expression can be seen as a syntactic shortcut for the class expression ObjectMinCardinality( 1 OPE CE ).
-	\item An existential class expression DataSomeValuesFrom( DPE1 ...
-DPEn DR ) consists of n data property expressions DPEi, 1 $\leq$ i $\leq$ n, and a data range DR whose arity MUST be n.
-Such a class expression contains all those individuals that are connected by DPEi to literals lti, 1 $\leq$ i $\leq$ n, such that the tuple ( lt1 , ..., ltn ) is in DR.
-A class expression of the form DataSomeValuesFrom( DPE DR ) can be seen as a syntactic shortcut for the class expression DataMinCardinality( 1 DPE DR ).
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{DL}
-$\exists$ parentOf . $\top$
-\end{DL}
-
-complex concept that describes the set
-of individuals that are parents of at least one individual (instance of $\top$).
-
-\begin{gcotable}
-property & $\exists$ parentOf . $\top$ & parentOf & - & $\top$ & $\exists$ \\
-\end{gcotable}
-
-\subsection{Simple Example}
-
-\begin{DL}
-$\exists$ parentOf . Female
-\end{DL}
-
-the complex concept describes those individuals that are parents of at least one
-female individual, i.e., those that have a daughter.
-
-\begin{gcotable}
-property & $\exists$ parentOf . Female & parentOf & - & Female & $\exists$ \\
-\end{gcotable}
-
-\subsection{Simple Example}
-
-\begin{DL}
-Parent $\equiv$ $\exists$ parentOf . $\top$
-\end{DL}
-
-\begin{gcotable}
-property & Parent & parentOf & - & $\top$ & $\exists$ \\
-\end{gcotable}
-
-\section{Universal Quantification on Properties}
-
-requirements:
-
-\begin{itemize}
-	\item R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item DL termonology: universal restriction
-\end{itemize}
-
-\tb{definition}
-
-\subsection{Simple Example}
-
-\begin{DL}
-$\forall$ parentOf . Female
-\end{DL}
-
-\begin{itemize}
-	\item set of individuals all of whose children are female
-  \item also includes those that have no children at all
-\end{itemize}
-
-\begin{gcotable}
-property & $\forall$ parentOf . Female & parentOf & - & Female & $\forall$ \\
-\end{gcotable}
-
-\section{Property Domain}
-
-requirements:
-
-\begin{itemize}
-	\item R-25-OBJECT-PROPERTY-DOMAIN
-	\item R-26-DATA-PROPERTY-DOMAIN
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item restrict domain of object and data properties
-	\item DL terminology: domain restrictions on roles
-	\item The language needs to include an easy-to-use vocabulary to declare that a given property is associated with a class, e.g.
-to populate input forms with appropriate widgets but also constraint checking.
-In OO terms this is the declaration of a member, field, attribute or association.
-\end{itemize}
-
-\tb{definition}
-
-\subsection{Simple Example}
-
-\begin{DL}
-$\exists$ sonOf . $\top$ $\sqsubseteq$ Male 
-\end{DL}
-
-\begin{itemize}
-	\item restrict the domain of sonOf to male individual
-\end{itemize}
-
-\begin{gcotable}
-property & $\top$ & sonOf & - & Male & domain \\
-\end{gcotable}
-
-\section{Property Range}
-
-requirements:
-
-\begin{itemize}
-	\item R-28-OBJECT-PROPERTY-RANGE
-	\item R-35-DATA-PROPERTY-RANGE
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item restrict range of object and data properties
-	\item DL terminology: range restrictions on roles
-\end{itemize}
-
-\tb{definition}
-
-\subsection{Simple Example}
-
-\begin{DL}
-$\top$ $\sqsubseteq$ $\forall$ sonOf . Parent 
-\end{DL}
-
-\begin{itemize}
-	\item restrict the range of sonOf to parents
-\end{itemize}
-
-\begin{ex}
-# OWL 2
-# -----
-sonOf rdfs:range Parent . 
-\end{ex}
-
-\begin{ex}
-# DSP
-# ---
-:hasDogRange
-        a dsp:DescriptionTemplate ; 
-        dsp:resourceClass owl:Thing ; 
-        dsp:statementTemplate [
-            a dsp:NonLiteralStatementTemplate ;
-            dsp:property sonOf ; 
-            dsp:nonLiteralConstraint [ 
-                a dsp:NonLiteralConstraint ;
-                dsp:valueClass Parent ] ] .
-\end{ex}
-
-\begin{gcotable}
-property & $\top$ & sonOf & - & Parent & range \\
-\end{gcotable}
-
-\section{Class-Specific Property Range}
-
-requirements:
-
-\begin{itemize}
-	\item R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS
-	\item R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-  \item restrict range of object and data properties for individuals within specific context
-	\item context: e.g. class
-	\item The values of each member property of a class may be limited by their value type, such as xsd:string or ex:Person. 
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{itemize}
-	\item property 'sonOf'
-	\item context: class 'Man'
-	\item range: class 'Parent'
-	\item $\rightarrow$ individuals of the class 'Man' can only have 'sonOf' relationships to indivuduals of the class 'Parent'
-\end{itemize}
-
-\section{Minimum Unqualified Cardinality Restrictions on Properties}
-
-requirements:
-
-\begin{itemize}
-	\item R-81-MINIMUM-UNQUALIFIED-CARDINALITY-ON-PROPERTIES
-	\item R-211-CARDINALITY-CONSTRAINTS
-\end{itemize}
-
-description:
-
-\begin{itemize}
-	\item A minimum cardinality expression ObjectMinCardinality( n OPE CE ) consists of a nonnegative integer n, an object property expression OPE, and a class expression CE, and it contains all those individuals that are connected by OPE to at least n different individuals that are instances of CE.
-If CE is missing, it is taken to be owl:Thing.
-	\item A minimum cardinality expression DataMinCardinality( n DPE DR ) consists of a nonnegative integer n, a data property expression DPE, and a unary data range DR, and it contains all those individuals that are connected by DPE to at least n different literals in DR.
-If DR is not present, it is taken to be rdfs:Literal.
-	\item unqualified: CE respective DR is NOT stated. 
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
-# ShEx
-# ----
-:Jedi {
-    :attitude ('good') }
-:JediStudent {
-    & :Jedi ,
-    :studentOf {}{1} }
-:JediMaster {
-    & :Jedi ,
-    :mentorOf {}{1,2} }
-:SuperJediMaster {
-    & :Jedi ,
-    :mentorOf {}{3,} }
-\end{ex}
-
-\begin{itemize}
-	\item Jedis have the attitude 'good'
-	\item Jedi students are students of exactly 1 resource
-	\item Jedi masters are mentoring at least 1 and at most 2 resources
-	\item Super Jedi masters are mentoring at least 3 resources  
-\end{itemize}
-
-\begin{ex}
-# data
-# ----
-:Yoda 
-    :attitude 'good' ;
-    :mentorOf :MaceWindu , :Obi-Wan , :Luke .
-:MaceWindu
-    :attitude 'good' ;
-    :studentOf :Yoda .
-:Obi-Wan 
-    :attitude 'good' ;
-    :studentOf :Yoda ;
-    :mentorOf :Anakin .
-:Anakin
-    :attitude 'good' ; 
-    :studentOf :Obi-Wan .
-:Luke
-    :attitude 'good' ;
-    :studentOf :Yoda .
-\end{ex}
-
-\begin{ex}
-# Individuals matching the ’:SuperJediMaster’ data shape
-# ------------------------------------------------------
-:Yoda 
-\end{ex}
-
-\tb{ToDO: add DL}
-
-\section{Minimum Qualified Cardinality Restrictions on Properties}
-
-requirements:
-
-\begin{itemize}
-	\item R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES
-  \item R-211-CARDINALITY-CONSTRAINTS
-\end{itemize}
-
-description:
-
-\begin{itemize}
-	\item A minimum cardinality expression ObjectMinCardinality( n OPE CE ) consists of a nonnegative integer n, an object property expression OPE, and a class expression CE, and it contains all those individuals that are connected by OPE to at least n different individuals that are instances of CE.
-If CE is missing, it is taken to be owl:Thing.
-	\item A minimum cardinality expression DataMinCardinality( n DPE DR ) consists of a nonnegative integer n, a data property expression DPE, and a unary data range DR, and it contains all those individuals that are connected by DPE to at least n different literals in DR.
-If DR is not present, it is taken to be rdfs:Literal.
-	\item qualified: CE respective DR is stated.
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{DL}
-$\geq$ 2 childOf . Parent
-\end{DL}
-
-\tb{ToDO: check DL}
-
-\begin{itemize}
-	\item set of individuals that are children of at least two parents
-\end{itemize}
-
-\begin{ex}
-# OWL 2
-# -----
-owl:Thing
-    a owl:Restriction ;
-    owl:minQualifiedCardinality "2"^^xsd:nonNegativeInteger ;
-    owl:onProperty childOf ;
-    owl:onClass Parent .
-\end{ex}
-
-\begin{gcotable}
-property & $\geq$ 2 childOf . Parent & childOf & -  & Parent & $\geq$ & 2 \\
-\end{gcotable}
-
-\subsection{Simple Example}
-
-\begin{DL}
-foaf:Person $\equiv$ $\geq$ 2 hasName.xsd:string
-\end{DL}
-
-\tb{ToDO: check DL}
-
-\begin{gcotable}
-property & foaf:Person & hasName & - & xsd:string & $\geq$ & 2 \\
-\end{gcotable}
-
-\subsection{Simple Example}
-
-\tb{ToDO: OWL 2 DL}
-
-\begin{ex}
-# ShEx
-# ----
-:Jedi {
-    :attitude ('good') }
-:JediStudent {
-    & :Jedi ,
-    :studentOf @:Jedi{1} }
-:JediMaster {
-    & :Jedi ,
-    :mentorOf @:Jedi{1,2} }
-:SuperJediMaster {
-    & :Jedi ,
-    :mentorOf @:Jedi{3,} }
-\end{ex}
-
-\begin{itemize}
-	\item Jedis have the attitude 'good'
-	\item Jedi students are students of exactly 1 Jedi
-	\item Jedi masters are mentoring at least 1 and at most 2 Jedis
-	\item Super Jedi masters are mentoring at least 3 Jedis
-\end{itemize}
-
-\begin{ex}
-# data
-# ----
-:Yoda 
-    :attitude 'good' ;
-    :mentorOf :MaceWindu , :Obi-Wan , :Luke .
-:MaceWindu
-    :attitude 'good' ;
-    :studentOf :Yoda .
-:Obi-Wan 
-    :attitude 'good' ;
-    :studentOf :Yoda ;
-    :mentorOf :Anakin .
-:Anakin
-    :attitude 'good' ; 
-    :studentOf :Obi-Wan .
-:Luke
-    :attitude 'good' ;
-    :studentOf :Yoda .
-\end{ex}
-
-\begin{ex}
-# Individuals matching the ’:SuperJediMaster’ data shape
-# ------------------------------------------------------
-:Yoda
-
-# Individuals matching the ’:JediMaster’ data shape
-# -------------------------------------------------
-:Obi-Wan
-\end{ex}
-
-\tb{ToDO: add DL}
-
-\subsection{Complex Example}
-
-\begin{DL}
-Father2Daughters $\equiv$ Man $\sqcap$ ($\geq$ 2 hasChild.Woman)
-\end{DL}
-
-\tb{ToDO: check DL}
-
-\begin{gcotable}
-property & $\geq$ 2 hasChild.Woman & hasChild & - & Woman & $\geq$ & 2 \\
-class & Father2Daughters & - & - & Man, $\geq$ 2 hasChild.Woman & $\sqcap$ & - \\
-\end{gcotable}
-
-\section{Maximum Unqualified Cardinality Restrictions on Properties}
-
-requirements:
-
-\begin{itemize}
-	\item R-82-MAXIMUM-UNQUALIFIED-CARDINALITY-ON-PROPERTIES
-	\item R-211-CARDINALITY-CONSTRAINTS
-\end{itemize}
-
-description:
-
-\begin{itemize}
-	\item A maximum cardinality expression ObjectMaxCardinality( n OPE CE ) consists of a nonnegative integer n, an object property expression OPE, and a class expression CE, and it contains all those individuals that are connected by OPE to at most n different individuals that are instances of CE.
-If CE is missing, it is taken to be owl:Thing.
-	\item A maximum cardinality expression DataMaxCardinality( n DPE DR ) consists of a nonnegative integer n, a data property expression DPE, and a unary data range DR, and it contains all those individuals that are connected by DPE to at most n different literals in DR.
-If DR is not present, it is taken to be rdfs:Literal.
-	\item unqualified: CE respective DR is NOT stated. 
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
-# ShEx
-# ----
-:Jedi {
-    :attitude ('good') }
-:JediStudent {
-    & :Jedi ,
-    :studentOf {}{1} }
-:JediMaster {
-    & :Jedi ,
-    :mentorOf {}{1,2} }
-:SuperJediMaster {
-    & :Jedi ,
-    :mentorOf {}{3,} }
-\end{ex}
-
-\begin{itemize}
-	\item Jedis have the attitude 'good'
-	\item Jedi students are students of exactly 1 resource
-	\item Jedi masters are mentoring at least 1 and at most 2 resources
-	\item Super Jedi masters are mentoring at least 3 resources  
-\end{itemize}
-
-\begin{ex}
-# data
-# ----
-:Yoda 
-    :attitude 'good' ;
-    :mentorOf :MaceWindu , :Obi-Wan , :Luke .
-:MaceWindu
-    :attitude 'good' ;
-    :studentOf :Yoda .
-:Obi-Wan 
-    :attitude 'good' ;
-    :studentOf :Yoda ;
-    :mentorOf :Anakin .
-:Anakin
-    :attitude 'good' ; 
-    :studentOf :Obi-Wan .
-:Luke
-    :attitude 'good' ;
-    :studentOf :Yoda .
-\end{ex}
-
-\begin{ex}
-# Individuals matching the ’:JediMaster’ data shape
-# -------------------------------------------------
-:Obi-Wan
-\end{ex}
-
-\tb{ToDO: add DL}
-
-\section{Maximum Qualified Cardinality Restrictions on Properties}
-
-requirements:
-
-\begin{itemize}
-	\item R-76-MAXIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES
-	\item R-211-CARDINALITY-CONSTRAINTS
-\end{itemize}
-
-description:
-
-\begin{itemize}
-	\item A maximum cardinality expression ObjectMaxCardinality( n OPE CE ) consists of a nonnegative integer n, an object property expression OPE, and a class expression CE, and it contains all those individuals that are connected by OPE to at most n different individuals that are instances of CE.
-If CE is missing, it is taken to be owl:Thing.
-	\item A maximum cardinality expression DataMaxCardinality( n DPE DR ) consists of a nonnegative integer n, a data property expression DPE, and a unary data range DR, and it contains all those individuals that are connected by DPE to at most n different literals in DR.
-If DR is not present, it is taken to be rdfs:Literal.
-	\item qualified: CE respective DR is stated. 
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{DL}
-$\leq$  2 childOf . Parent
-\end{DL}
-
-\tb{ToDO: check DL}
-
-\begin{itemize}
-	\item set of individuals that are children of at most two parents
-\end{itemize}
-
-\begin{gcotable}
-property & $\leq$  2 childOf . Parent & childOf & - & Parent & $\leq$ & 2 \\
-\end{gcotable}
-
-\subsection{Simple Example}
-
-\tb{ToDO: OWL 2 DL}
-
-\begin{ex}
-# ShEx
-# ----
-:Jedi {
-    :attitude ('good') }
-:JediStudent {
-    & :Jedi ,
-    :studentOf @:Jedi{1} }
-:JediMaster {
-    & :Jedi ,
-    :mentorOf @:Jedi{1,2} }
-:SuperJediMaster {
-    & :Jedi ,
-    :mentorOf @:Jedi{3,} }
-\end{ex}
-
-\begin{itemize}
-	\item Jedis have the attitude 'good'
-	\item Jedi students are students of exactly 1 Jedi
-	\item Jedi masters are mentoring at least 1 and at most 2 Jedis
-	\item Super Jedi masters are mentoring at least 3 Jedis
-\end{itemize}
-
-\begin{ex}
-# data
-# ----
-:Yoda 
-    :attitude 'good' ;
-    :mentorOf :MaceWindu , :Obi-Wan , :Luke .
-:MaceWindu
-    :attitude 'good' ;
-    :studentOf :Yoda .
-:Obi-Wan 
-    :attitude 'good' ;
-    :studentOf :Yoda ;
-    :mentorOf :Anakin .
-:Anakin
-    :attitude 'good' ; 
-    :studentOf :Obi-Wan .
-:Luke
-    :attitude 'good' ;
-    :studentOf :Yoda .
-\end{ex}
-
-\begin{ex}
-# Individuals matching the ’:JediMaster’ data shape
-# -------------------------------------------------
-:Obi-Wan
-\end{ex}
-
-\tb{ToDO: add DL}
-
-\section{Exact Unqualified Cardinality Restrictions on Properties}
-
-requirements:
-
-\begin{itemize}
-	\item R-80-EXACT-UNQUALIFIED-CARDINALITY-ON-PROPERTIES
-	\item R-211-CARDINALITY-CONSTRAINTS
-\end{itemize}
-
-description:
-
-\begin{itemize}
-	\item An exact cardinality expression ObjectExactCardinality( n OPE CE ) consists of a nonnegative integer n, an object property expression OPE, and a class expression CE, and it contains all those individuals that are connected by OPE to exactly n different individuals that are instances of CE.
-If CE is missing, it is taken to be owl:Thing.
-Such an expression is actually equivalent to the expression ObjectIntersectionOf( ObjectMinCardinality( n OPE CE ) ObjectMaxCardinality( n OPE CE ) ).
-	\item An exact cardinality expression DataExactCardinality( n DPE DR ) consists of a nonnegative integer n, a data property expression DPE, and a unary data range DR, and it contains all those individuals that are connected by DPE to exactly n different literals in DR.
-If DR is not present, it is taken to be rdfs:Literal.
-	\item unqualified: CE respective DR is NOT stated. 
-\end{itemize}
-
-\subsection{Simple Example}
-
-\tb{ToDo. OWL 2 DL}
-
-\begin{ex}
-# ShEx
-# ----
-:JediStudent {
-    :studentOf {}{1} }
-\end{ex}
-
-\begin{ex}
-# ReSh
-# ----
-:JediStudent a rs:ResourceShape ;
-    rs:property [
-        rs:name "studentOf" ;
-        rs:propertyDefinition :studentOf ;
-        rs:valueShape [ a rs:ResourceShape] ;
-        rs:occurs rs:Exactly-one ; ] .
-\end{ex}
-
-\begin{itemize}
-	\item Jedis have the attitude 'good'
-	\item Jedi students are students of exactly 1 resource
-\end{itemize}
-
-\begin{ex}
-# data
-# ----
-:Yoda 
-    :attitude 'good' ;
-    :mentorOf :MaceWindu , :Obi-Wan , :Luke .
-:MaceWindu
-    :attitude 'good' ;
-    :studentOf :Yoda .
-:Obi-Wan 
-    :attitude 'good' ;
-    :studentOf :Yoda ;
-    :mentorOf :Anakin .
-:Anakin
-    :attitude 'good' ; 
-    :studentOf :Obi-Wan .
-:Luke
-    :attitude 'good' ;
-    :studentOf :Yoda .
-\end{ex}
-
-\begin{ex}
-# Individuals matching the ’:JediStudent’ data shape
-# --------------------------------------------------
-:MaceWindu :Obi-Wan :Anakin :Luke
-\end{ex}
-
-\tb{ToDO: add DL}
-
-\section{Exact Qualified Cardinality Restrictions on Properties}
-
-requirements:
-
-\begin{itemize}
-	\item R-74-EXACT-QUALIFIED-CARDINALITY-ON-PROPERTIES
-	\item R-211-CARDINALITY-CONSTRAINTS
-\end{itemize}
-
-description:
-
-\begin{itemize}
-	\item An exact cardinality expression ObjectExactCardinality( n OPE CE ) consists of a nonnegative integer n, an object property expression OPE, and a class expression CE, and it contains all those individuals that are connected by OPE to exactly n different individuals that are instances of CE.
-If CE is missing, it is taken to be owl:Thing.
-Such an expression is actually equivalent to the expression ObjectIntersectionOf( ObjectMinCardinality( n OPE CE ) ObjectMaxCardinality( n OPE CE ) ).
-	\item An exact cardinality expression DataExactCardinality( n DPE DR ) consists of a nonnegative integer n, a data property expression DPE, and a unary data range DR, and it contains all those individuals that are connected by DPE to exactly n different literals in DR.
-If DR is not present, it is taken to be rdfs:Literal.
-	\item qualified: CE respective DR is stated. 
-\end{itemize}
-
-\subsection{Simple Example}
-
-\tb{ToDO: OWL 2 DL}
-
-\begin{ex}
-# ShEx
-# ----
-:Jedi {
-    :attitude ('good') }
-:JediStudent {
-    :studentOf @:Jedi{1} }
-\end{ex}
-
-\begin{ex}
-# ReSh
-# ----
-:Jedi a rs:ResourceShape ;
-    rs:property [
-        rs:name "attitude" ;
-        rs:propertyDefinition :attitude ;
-        rs:allowedValue "good" ;
-        rs:occurs rs:Exactly-one ;
-    ] .
-:JediStudent a rs:ResourceShape ;
-    rs:property [
-        rs:name "studentOf" ;
-        rs:propertyDefinition :studentOf ;
-        rs:valueShape :Jedi ;
-        rs:occurs rs:Exactly-one ;
-    ] .
-\end{ex}
-
-\begin{itemize}
-	\item Jedis have the attitude 'good'
-	\item Jedi students are students of exactly 1 Jedi
-\end{itemize}
-
-\begin{ex}
-# data
-# ----
-:Yoda 
-    :attitude 'good' ;
-    :mentorOf :MaceWindu , :Obi-Wan , :Luke .
-:MaceWindu
-    :attitude 'good' ;
-    :studentOf :Yoda .
-:Obi-Wan 
-    :attitude 'good' ;
-    :studentOf :Yoda ;
-    :mentorOf :Anakin .
-:Anakin
-    :attitude 'good' ; 
-    :studentOf :Obi-Wan .
-:Luke
-    :attitude 'good' ;
-    :studentOf :Yoda .
-\end{ex}
-
-\begin{ex}
-# Individuals matching the ’:JediStudent’ data shape
-# --------------------------------------------------
-:MaceWindu :Obi-Wan :Anakin :Luke
-\end{ex}
-
-\tb{ToDO: add DL}
-
-\subsection{Complex Example}
-
-\begin{DL}
-Person $\sqsubseteq$ $\geq$ 2 childOf . Parent $\sqcap$ $\leq$  2 childOf . Parent \\
-\end{DL}
-
-\tb{ToDO: check DL}
-
-\begin{itemize}
-	\item every person is a child of exactly two parents
-\end{itemize}
-
-\begin{gcotable}
-property & $\geq$ 2 childOf . Parent & childOf & - & Parent & $\geq$ & 2 \\
-property & $\leq$ 2 childOf . Parent & childOf & - & Parent & $\leq$ & 2 \\
-class & Person & - & - & $\geq$ 2 childOf . Parent, $\leq$ 2 childOf . Parent & $\sqcap$ & - \\
-\end{gcotable}
-
-syntactic sugar:
-
-\begin{gcotable}
-property & Person & childOf & - & Parent & = & 2 \\
-\end{gcotable}
-
-\section{Inverse Object Properties}
-
-requirement:
-
-\begin{itemize}
-	\item R-56-INVERSE-OBJECT-PROPERTIES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item In many cases properties are used bi-directionally and then accessed in the inverse direction, e.g.
-parent $\equiv$ child$^{-}$.
-There should be a way to declare value type, cardinality etc of those inverse relations without having to declare a new property URI.
-	\item The object property expression OPE1 is an inverse of the object property expression OPE2.
-Thus, if an individual x is connected by OPE1 to an individual y, then y is also connected by OPE2 to x, and vice versa.
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{DL}
-parentOf $\equiv$ $childOf^{-}$ \\
-\end{DL}
-
-\begin{gcotable}
-property & parentOf & childOf & - & $\top$ & $inverse role (^{-})$ \\
-\end{gcotable}
-
-consistent with ontology:
-
-\begin{gcotable}
-property & $\top$ & parentOf & childOf & $\top$ & $inverse role (^{-})$ \\
-\end{gcotable}
-
-\section{Transitive Object Properties}
-
-requirements:
-
-\begin{itemize}
-	\item R-63-TRANSITIVE-OBJECT-PROPERTIES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item Transitivity is a special form of complex role inclusion
-	\item An object property transitivity axiom TransitiveObjectProperty( OPE ) states that the object property expression OPE is transitive — that is, if an individual x is connected by OPE to an individual y that is connected by OPE to an individual z, then x is also connected by OPE to z.
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{DL}
-ancestorOf $\circ$ ancestorOf $\sqsubseteq$ ancestorOf
-\end{DL}
-
-syntactic sugar:
-
-\begin{gcotable}
-property & ancesterOf & ancestorOf, ancestorOf & - & $\top$ & transitive role \\
-\end{gcotable}
-
-syntactic sugar (ontology conform):
-
-\begin{gcotable}
-property & $\top$ & ancestorOf, ancestorOf & ancestorOf & $\top$ & transitive role \\
-\end{gcotable}
-
-without syntactic sugar (ontology conform):
-
-\begin{gcotable}
-property & $\top$ & ancestorOf, ancestorOf & ancestorOf & $\top$ & $\sqsubseteq$ \\
-\end{gcotable}
-
-\section{Symmetric Object Properties}
-
-requirement:
-
-\begin{itemize}
-	\item R-61-SYMMETRIC-OBJECT-PROPERTIES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item A role is symmetric if it is equivalent to its own inverse \cite{Kroetzsch2012}
-  \item An object property symmetry axiom SymmetricObjectProperty( OPE ) states that the object property expression OPE is symmetric — that is, if an individual x is connected by OPE to an individual y, then y is also connected by OPE to x.
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{DL}
-marriedTo $\equiv$ $marriedTo^{-}$ \\
-\end{DL}
-
-\begin{gcotable}
-property & marriedTo & marriedTo & - & $\top$ & $inverse role (^{-})$ \\
-\end{gcotable}
-
-ontology conform:
-
-\begin{gcotable}
-property & $\top$ & marriedTo & marriedTo & $\top$ & $inverse role (^{-})$ \\
-\end{gcotable}
-
-syntactic sugar:
-
-\begin{gcotable}
-property & $\top$ & marriedTo & - & $\top$ & symmetric role \\
-\end{gcotable}
-
-\subsubsection{Asymmetric Object Properties}
-
-requirement:
-
-\begin{itemize}
-	\item R-62-ASYMMETRIC-OBJECT-PROPERTIES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item A role is asymmetric if it is disjoint from its own inverse \cite{Kroetzsch2012}
-	\item An object property asymmetry axiom AsymmetricObjectProperty( OPE ) states that the object property expression OPE is asymmetric — that is, if an individual x is connected by OPE to an individual y, then y cannot be connected by OPE to x.
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{DL}
-Disjoint( parentOf , $parentOf^{-}$ )
-\end{DL}
-
-\begin{gcotable}
-property & $parentOf^{-}$ & parentOf & - & $\top$ & inverse role $(^{-})$ \\
-property & parentOf & parentOf, $parentOf^{-}$ & - & $\top$ & disjoint role ($\ne$) \\
-\end{gcotable}
-
-ontology conform:
-
-\begin{gcotable}
-property & $\top$ & parentOf & - & $\top$ & inverse role $(^{-})$ \\
-property & $\top$ & parentOf, $parentOf^{-}$ & - & $\top$ & disjoint role ($\ne$) \\
-\end{gcotable}
-
-syntactic sugar:
-
-\begin{gcotable}
-property & $\top$ & parentOf & - & $\top$ & asymmetric role \\
-\end{gcotable}
-
-\subsection{Simple Example}
-
-\begin{itemize}
-	\item child parent relations (dbo:child) cannot be symmetric
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{itemize}
-	\item person birth place relations (dbo:birthPlace) cannot be symmetric
-\end{itemize}
-
-\section{Class-Specific Reflexive Object Properties / Local Reflexivity}
-
-requirement:
-
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-  \item DL terminology: local reflexivity
-	\item set of individuals that are related to themselves via a given role \cite{Kroetzsch2012}.
-	\item set of individuals (of a specific class) that are related to themselves via a given object property
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{DL}
-$\exists$ talksTo .Self. 
-\end{DL}
-
-\begin{itemize}
-	\item set of individuals that are talking to themselves
-\end{itemize}
-
-\begin{gcotable}
-property & $\exists$ talksTo .Self.  & talksTo & - & Self & $\exists$ \\
-\end{gcotable}
-
-syntactic sugar:
-
-\begin{gcotable}
-property & $\exists$ talksTo .Self. & talksTo & - & - & reflexive role \\
-\end{gcotable}
-
-\section{Reflexive Object Properties / Global Reflexivity}
-
-requirement:
-
-\begin{itemize}
-	\item R-59-REFLEXIVE-OBJECT-PROPERTIES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-  \item DL terminology: reflexive roles, global reflexivity
-	\item global reflexivity can be expressed by imposing local reflexivity on the top concept \cite{Kroetzsch2012}
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{DL}
-$\top$ $\sqsubseteq$ $\exists$ knows . Self
-\end{DL}
-
-syntactic sugar:
-
-\begin{gcotable}
-property & $\top$ & knows & - & $\top$ & reflexive role \\
-\end{gcotable}
-
-\begin{gcotable}
-property & $\top$ & knows & - & Self & $\exists$ \\
-\end{gcotable}
-
-\section{Irreflexive Object Properties}
-
-requirement:
-
-\begin{itemize}
-	\item R-60-IRREFLEXIVE-OBJECT-PROPERTIES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item DL terminology: irreflexive roles
-  \item A role is irreflexive if it is never locally reflexive \cite{Kroetzsch2012}
-	\item An object property irreflexivity axiom IrreflexiveObjectProperty( OPE ) states that the object property expression OPE is irreflexive — that is, no individual is connected by OPE to itself. 
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{DL}
-$\top$ $\sqsubseteq$ $\neg$ $\exists$ marriedTo . Self
-\end{DL}
-
-syntactic sugar:
-
-\begin{gcotable}
-property & $\top$ & marriedTo & - & $\top$ & irreflexive role \\
-\end{gcotable}
-
-\begin{gcotable}
-property & $\exists$ marriedTo . Self & marriedTo & - & Self & $\exists$ \\
-class & $\top$ & - & - & $\exists$ marriedTo . Self & $\neg$ \\
-\end{gcotable}
-
-\subsection{Simple Example}
-
-\begin{itemize}
-	\item a resource cannot be its own parent (dbo:parent)
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{itemize}
-	\item a resource cannot be its own child (dbo:child)
-\end{itemize}
-
-\section{Context-Specific Property Groups}
-
-requirement:
-
-\begin{itemize}
-	\item R-66-PROPERTY-GROUPS
-\end{itemize}
-
-\subsection{Description}
-
-\subsection{Simple Example}
-
-DSCL (ShEx):
-\begin{ex}
-<Human> { 
-    (  
-        foaf:name xsd:string ,
-        foaf:givenName xsd:string 
-    ) ,
-    (
-        foaf:mbox IRI ,
-        foaf:homepage foaf:Document
-    ) }
-\end{ex}
-
-\begin{itemize}
-	\item 1. group: 1 foaf:name (range: xsd:string) and 1 foaf:givenName (range: xsd:string) and (,)
-	\item 2. group: 1 foaf:mbox (range: IRI) and 1 foaf:homepage (range: foaf:Document) 
-\end{itemize}
-
-\begin{DL}
-$A \equiv \forall foaf:name . xsd:string$ \\
-$B \equiv \forall foaf:givenName . xsd:string$ \\
-$C \equiv A XOR B$ \\
-$D \equiv \forall foaf:mbox . xsd:string$ \\
-$Human \equiv C \sqcap D$ \\
-\end{DL}
-
-\section{Context-Specific Exclusive OR of Properties}
-
-requirements:
-
-\begin{itemize}
-	\item R-11-CONTEXT-SPECIFIC-EXCLUSIVE-OR-OF-PROPERTIES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-  \item exclusive or: logical operation that outputs true whenever both inputs differ (one is true, the other is false).
-	\item in OWL 2, inclusive OR of properties would be possible to express, but not exclusive OR of data properties
-\end{itemize}
-
-DL (general):
-
-\begin{DL}
-$C \sqsubseteq (\neg A \sqcap B) \sqcup (A \sqcap \neg B)$ \\
-\end{DL}
-
-DL (general) (alternative):
-
-\begin{DL}
-$C \sqsubseteq (A \sqcup B) \sqcap \neg(A \sqcap B)$ \\
-\end{DL}
-
-\subsection{Simple Example}
-
-DSCL (ShEx):
-\begin{ex}
-<Human> { (  
-    foaf:name xsd:string | 
-    foaf:givenName xsd:string ) }
-\end{ex}
-
-DSCL (OWL 2):
-\begin{ex}
-:Human owl:disjointUnionOf ( :CC1 :CC2 ) .
-
-:CC1 rdfs:subClassOf [
-    a owl:Restriction ;
-    owl:onProperty foaf:name ;
-    owl:allValuesFrom xsd:string ] .
-:CC2 rdfs:subClassOf [
-    a owl:Restriction ;
-    owl:onProperty foaf:givenNme ;
-    owl:allValuesFrom xsd:string ] .
-\end{ex}
-
-\begin{itemize}
-	\item 1 foaf:name (range xsd:string) XOR 1 foaf:givenName (range xsd:string)
-\end{itemize}
-
-\begin{DL}
-A $\equiv$ $\forall$ foaf:name . xsd:string \\
-B $\equiv$ $\forall$ foaf:givenName . xsd:string \\ 
-Human $\sqsubseteq$ ($\neg$ A $\sqcap$ B) $\sqcup$ (A $\sqcap$ $\neg$ B) \\
-\end{DL}
-
-\begin{gcotable}
-property & A & foaf:name & - & xsd:string & $\forall$ \\
-property & B & foaf:givenName & - & xsd:string & $\forall$ \\
-class & $\neg$ A & - & - & A & $\neg$ \\
-class & $\neg$ B & - & - & B & $\neg$ \\
-class & $\neg$ A $\sqcap$ B & - & - & $\neg$ A, B & $\sqcap$ \\
-class & A $\sqcap$ $\neg$ B & - & - & A, $\neg$ B & $\sqcap$ \\
-class & Human & - & - & $\neg$ A $\sqcap$ B, A $\sqcap$ $\neg$ B & $\sqcup$ \\
-\end{gcotable}
-
-syntactic sugar:
-
-\begin{gcotable}
-property & A & foaf:name & - & xsd:string & $\forall$ \\
-property & B & foaf:givenName & - & xsd:string & $\forall$ \\
-class & Human & - & - & A, B & XOR \\
-\end{gcotable}
-
-\subsection{Complex Example}
-
-DSCL (ShEx):
-
-\begin{ex}
-<Human> { (  
-    foaf:name xsd:string | foaf:givenName xsd:string+ , 
-    foaf:familyName xsd:string ) }
-\end{ex}
-
-\begin{itemize}
-	\item 1 foaf:name (range xsd:string) XOR 1-n foaf:givenName (range xsd:string)
-	\item and
-	\item 1 foaf:familyName (range xsd:string)
-\end{itemize}
-
-\tb{ToDo: DL}
-
-Individuals matching the 'Human' data shape:
-
-\begin{ex}
-:Han
-    foaf:name "Han Solo" ;
-    foaf:familyName "Solo" .
-:Anakin
-    foaf:givenName "Anakin" ;
-    foaf:givenName "Darth" ;
-    foaf:familyName "Skywalker" .
-\end{ex}
-
-Individual not matching the 'Human' data shape:
-
-\begin{ex}
-:Anakin
-    foaf:name "Anakin Skywalker" ;
-    foaf:givenName "Anakin" ;
-    foaf:familyName "Skywalker" .
-\end{ex}
-
-\section{Context-Specific Inclusive OR of Properties}
-
-requirements:
-
-\begin{itemize}
-	\item R-202-CONTEXT-SPECIFIC-INCLUSIVE-OR-OF-PROPERTIES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item inclusive or: A logical connective joining two or more predicates that yields the logical value "true" when at least one of the predicates is true.
-	\item context can be a class $\rightarrow$ constraint applies for individuals of this specific class 
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{itemize}
-	\item 1 foaf:name (range: xsd:string) OR 1 foaf:givenName (range: xsd:string)
-	\item it is also possible that both 1 foaf:name and 1 foaf:givenName are stated
-	\item context: class Human
-\end{itemize}
-
-\section{Context-Specific Exclusive OR of Property Groups}
-
-requirement:
-
-\begin{itemize}
-	\item R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item exclusive or: logical operation that outputs true whenever both inputs differ (one is true, the other is false).
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
-# DSCL (ShEx)
-# -----------
-<Human> { 
-    (  
-        foaf:name xsd:string ,
-        foaf:givenName xsd:string ) 
-    |
-    (
-        foaf:mbox IRI ,
-        foaf:homepage foaf:Document ) }
-\end{ex}
-
-\begin{itemize}
-  \item 1. group XOR 2. group
-	\item 1. group: 1 foaf:name (range: xsd:string) and 1 foaf:givenName (range: xsd:string)
-	\item 2. group: 1 foaf:mbox (range: IRI) and 1 foaf:homepage (range: foaf:Document) 
-	\item context: class Human
-\end{itemize}
-
-\begin{ex}
-# valid data
-# ----------
-:Thomas
-    a :Human ;
-    foaf:mbox <thomas.bosch@gesis.org> ;
-    foaf:homepage <http://purl.org/net/thomasbosch> .
-\end{ex}
-
-\begin{ex}
-# invalid data
-# ----------
-:Thomas
-    a :Human ;
-    foaf:name 'Thomas Bosch' ;
-    foaf:givenName 'Thomas' ;
-    foaf:mbox <thomas.bosch@gesis.org> ;
-    foaf:homepage <http://purl.org/net/thomasbosch> .
-\end{ex}
-
-\begin{DL}
-Human $\sqsubseteq$ ($\neg$ E $\sqcap$ F) $\sqcup$ (E $\sqcap$ $\neg$ F) \\ 
-E $\equiv$ A $\sqcap$ B \\
-F $\equiv$ C $\sqcap$ D \\
-A $\equiv$ $\forall$ foaf:name . xsd:string \\
-B $\equiv$ $\forall$ foaf:givenName . xsd:string \\ 
-C $\equiv$ $\forall$ foaf:mbox . IRI \\
-D $\equiv$ $\forall$ foaf:homepage . foaf:Document \\
-\end{DL}
-
-\subsection{Complex Example}
-
-\begin{ex}
-# ShExC
-# -----
-[[
-  <UserShape> {                          # A User has
-    (foaf:name xsd:string                #  either a foaf:name
-     | foaf:givenName xsd:string+,       #   or 1+ givenNames
-       foaf:familyName xsd:string),      #   and a family name
-    foaf:mbox IRI                        # and an mbox.
-  }
-]]
-\end{ex}
-
-\begin{ex}
-# ReSh
-# ----
-
-[[
-  PREFIX rs:<http://open-services.net/ns/core#>
-  PREFIX se:<http://www.w3.org/2013/ShEx/Definition#>
-
-  <UserShape> a rs:ResourceShape ;       # A User has
-    se:choice [
-      rs:property [                      #  either a foaf:name
-        rs:name "name" ;
-        rs:propertyDefinition foaf:name ;
-        rs:valueType xsd:string ;
-        rs:occurs rs:Exactly-one ;
-      ] ;
-      se:ruleGroup [
-        rs:property [                    #   or 1+ givenNames
-          rs:name "givenName" ;
-          rs:propertyDefinition foaf:givenName ;
-          rs:valueType xsd:string ;
-          rs:occurs rs:One-or-many ;
-        ] ;
-        rs:property [                    #   and a family name
-          rs:name "familyName" ;
-          rs:propertyDefinition foaf:familyName ;
-          rs:valueType xsd:string ;
-          rs:occurs rs:Exactly-one ;
-        ] ;
-      ] ;
-    ] ;
-    rs:property [                        # and an mbox.
-      rs:name "mbox" ;
-      rs:propertyDefinition foaf:mbox ;
-      rs:valueType rs:Resource ;
-      rs:occurs rs:Exactly-one ;
-    ] .
-]]
-\end{ex}
-
-\section{Context-Specific Inclusive OR of Property Groups}
-
-requirements:
-
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-  \item at least one property group must match for individuals of a specific context 
-	\item context: may be a class
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{itemize}
-  \item 1. group OR 2. group
-	\item 1. group: 1 foaf:firstName (range: xsd:string) and 1 foaf:lastName (range: xsd:string)
-	\item 2. group: 1 foaf:givenName (range: xsd:string) and 1 foaf:familyName (range: xsd:string)
-	\item context: class Person
-\end{itemize}
-
-\begin{ex}
-# valid data
-# ----------
-:Anakin
-    a :Person ;
-    foaf:firstName 'Anakin' ;
-    foaf:lastName 'Skywalker' ;
-    foaf:givenName 'Anakin' ;
-    foaf:familyName 'Skywalker' .
-\end{ex}
-
-\begin{ex}
-# invalid data
-# ----------
-:Anakin
-    a :Person .
-\end{ex}
-
-\section{Allowed Values}
-
-requirements:
-
-\begin{itemize}
-	\item R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS
-  \item R-37-ALLOWED-VALUES-FOR-RDF-LITERALS
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-  \item It is a common requirement to narrow down the value space of a property by an exhaustive enumeration of the valid values (both literals or resource).
-This is often rendered in drop down boxes or radio buttons in user interfaces.
-	\item define a concept by simply enumerating its instances
-	\item A DL nominal is a concept that has exactly one instance
-	\item DL enumeration: combining nominals with union
-\end{itemize}
-
-allowed values for properties
-
-\begin{itemize}
-	\item must be an IRI
-  \item must be an IRI matching this pattern (e.g. http://id.loc.gov/authorities/names/)
-  \item must be an IRI matching one of these patterns
-  \item must be a (any) literal
-  \item must be one of these literals ("red" "blue" "green")
-  \item must be a typed literal of this type (e.g. XML dataType)
-\end{itemize}
-
-\subsection{Example}
-
-\begin{ex}
-# DSP
-# ----------
-:descriptionTemplate 
-    a dsp:DescriptionTemplate ;
-    dsp:minOccur "0"^^xsd:nonNegativeInteger ; 
-    dsp:maxOccur "infinity"^^xsd:string ; 
-    dsp:resourceClass swrc:Book ; 
-    dsp:statementTemplate [
-        a dsp:NonLiteralStatementTemplate ;
-        dsp:minOccur "0"^^xsd:nonNegativeInteger ; 
-        dsp:maxOccur "infinity"^^xsd:string ; 
-        dsp:property dcterms:subject ; 
-        dsp:nonLiteralConstraint [ 
-            a dsp:NonLiteralConstraint ;
-            dsp:valueClass skos:Concept ;
-            dsp:valueURI :ComputerScience, :SocialScience, :Librarianship ] ] .
-\end{ex}
-
-\begin{ex}
-# OWL2
-# ----
-dcterms:subject rdfs:range :ObjectOneOf . 
-# EquivalentClasses( :ObjectOneOf ObjectOneOf( :ComputerScience :SocialScience :Librarianship ) )
-:ObjectOneOf owl:equivalentClass [ 
-    a owl:Class ;
-    owl:oneOf ( :ComputerScience :SocialScience :Librarianship ) ] .
-\end{ex}
-
-\begin{itemize}
-	\item the range of the object property dcterms:subject must consist of the individuals :ComputerScience :SocialScience :Librarianship which are of the class skos:Concept
-\end{itemize}
-
-\begin{DL}
-$\top$ $\sqsubseteq$ $\forall$ dcterms:subject . skos:Concept $\sqcap$ ( $\{ComputerScience\}$ $\sqcup$ \{SocialScience\} $\sqcup$ \{Librarianship\} ) \\
-\end{DL}
-
-\subsection{Simple Example}
-
-\begin{DL}
-Beatle $\equiv$ \{john\} $\sqcup$ \{paul\} $\sqcup$ \{george\} $\sqcup$ \{ringo\} \\
-\end{DL}
-
-\begin{gcotable}
-class & Beatle & - & - & $\{john\}$, $\{paul\}$, $\{george\}$, $\{ringo\}$ & $\sqcup$ \\
-\end{gcotable}
-
-\subsection{Simple Example}
-
-\begin{DL}
-\{ComputerScience\} $\sqcup$ \{SocialScience\} $\sqcup$ \{Librarianship\} \\
-\end{DL}
-
-\begin{gcotable}
-class & complex concept & - & - & \{ComputerScience\}, \{SocialScience\}, \{Librarianship\} & $\sqcup$ & - \\
-\end{gcotable}
-
-\subsection{Simple Example}
-
-\begin{itemize}
-	\item Jedis have blue, green, or white laser swords
-\end{itemize}
-
-\begin{ex}
-# DSP
-# ---
-:personDescriptionTemplate
-    a dsp:DescriptionTemplate ;
-    dsp:resourceClass :Jedi ;
-    dsp:statementTemplate [
-        a dsp:LiteralStatementTemplate ;
-        dsp:property :laserSwordColor ;
-        dsp:literalConstraint [
-            a dsp:LiteralConstraint ;
-            dsp:literal "blue" ;
-            dsp:literal "green" ;
-            dsp:literal "white"] ] .
-\end{ex}
-
-\begin{ex}
-# OWL2
-# ----
-:laserSwordColor rdfs:range :laserSwordColors . 
-:laserSwordColors
-    a rdfs:Datatype .
-    owl:oneOf ( "blue" "green" "white" ) .
-\end{ex}
-
-\begin{ex}
-# ReSh
-# ----
-:Jedi a rs:ResourceShape ;
-    rs:property [
-        rs:name "laserSwordColor" ;
-        rs:propertyDefinition :laserSwordColor ;
-        rs:allowedValue "blue" , "green" , "white" ;
-        rs:occurs rs:Exactly-one ;
-    ] .
-\end{ex}
-
-\begin{ex}
-# ShEx
-# ----
-:Jedi {
-    :laserSwordColor ('blue' 'green' 'white') }
-\end{ex}
-
-\begin{ex}
-# Jedi individuals
-# ----------------
-:Yoda 
-    :laserSwordColor 'blue' .
-\end{ex}
-
-\begin{DL}
-Jedi $\equiv$ $\exists$ laserSwordColor . \{'blue'\} $\sqcup$ \{'green'\} $\sqcup$ \{'white'\} \\
-\end{DL}
-
-\tb{ToDo: check DL}
-
-\section{Not Allowed Values}
-
-requirements:
-
-\begin{itemize}
-	\item R-33-NEGATIVE-OBJECT-CONSTRAINTS
-	\item R-200-NEGATIVE-LITERAL-CONSTRAINTS
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item not allowed objects
-	\item not allowed literals
-	\item definition: A matching triple has any literal / object except those explicitly excluded
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{itemize}
-	\item Siths do not have blue, green, or white laser swords
-\end{itemize}
-
-\begin{ex}
-# DSP
-# ---
--
-\end{ex}
-
-\begin{ex}
-# OWL2
-# ----
-:laserSwordColor rdfs:range :negativeLaserSwordColors . 
-:NegativeLaserSwordColors
-    a rdfs:Datatype .
-    owl:complementOf :laserSwordColors .
-:laserSwordColors
-    a rdfs:Datatype .
-    owl:oneOf ( "blue" "green" "white" ) .
-\end{ex}
-
-\begin{ex}
-# ReSh
-# ----
--
-\end{ex}
-
-\begin{ex}
-# ShEx
-# ----
-:Sith {
-    ! :laserSwordColor ('blue' 'green' 'white') }
-\end{ex}
-
-\begin{ex}
-# Sith individuals
-# ----------------
-:DarthSidious
-    :laserSwordColor 'red' .
-\end{ex}
-
-\begin{DL}
-Sith $\equiv$ $\neg$( $\exists$ laserSwordColor . \{'blue'\} $\sqcup$ \{'green'\} $\sqcup$ \{'white'\} ) \\
-\end{DL}
-
-\tb{ToDo: check DL}
-
-\section{Membership in Controlled Vocabularies}
-
-requirements:
-
-\begin{itemize}
-	\item R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES
-	\item R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item resources can only be members of listed controlled vocabularies
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
-# DSCL (DSP)
-# ----------
-:bookDescriptionTemplate 
-    a dsp:DescriptionTemplate ;
-    dsp:resourceClass swrc:Book ; 
-    dsp:statementTemplate [
-        a dsp:NonLiteralStatementTemplate ;
-        dsp:property dcterms:subject ; 
-        dsp:nonLiteralConstraint [ 
-            a dsp:NonLiteralConstraint ;
-            dsp:valueClass skos:Concept ; 
-            dsp:vocabularyEncodingScheme :BookSubjects, :BookTopics, :BookCategories ] ] .
-\end{ex}
-
-\begin{itemize}
-	\item \ms{skos:Concept} resources can only be members of the listed controlled vocabularies
-\end{itemize}
-
-\begin{DL}
-$A \equiv skos:Concept \sqcap B$ \\
-$B \equiv \forall skos:inScheme . C$ \\
-$C \equiv skos:ConceptScheme \sqcap ( \{:BookSubjects\} \sqcup \{:BookTopics\} \sqcup \{:BookCategories\} )$ \\
-\end{DL}
-
-\begin{ex}
-# valid data
-# ----------
-:ArtficialIntelligence
-    a swrc:Book ;
-    dcterms:subject :ComputerScience .
-:ComputerScience
-    a skos:Concept ;
-    dcam:memberOf :BookSubjects ;
-    skos:inScheme :BookSubjects .
-:BookSubjects
-    a skos:ConceptScheme .
-\end{ex}
-
-\begin{ex}
-# invalid data
-# ------------
-:ArtficialIntelligence
-    a swrc:Book ;
-    dcterms:subject :ComputerScience .
-:ComputerScience
-    a skos:Concept ;
-    dcam:memberOf :BooksAboutBirds ;
-    skos:inScheme :BooksAboutBirds ;
-    dcam:memberOf :BookSubjects ;
-    skos:inScheme :BookSubjects .
-:BookSubjects
-    a skos:ConceptScheme .
-\end{ex}
-
-\begin{itemize}
-	\item The related subject (\ms{:ComputerScience}) is a member of a controlled vocabulary (\ms{:BooksAboutBirds}) 
-which is not part of the list of allowed controlled vocabularies.
-\end{itemize}
-
-\section{IRI Pattern Matching}
-
-requirements:
-
-\begin{itemize}
-	\item R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS
-  \item R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS
-  \item R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item IRI pattern matching on subjects, properties, and objects
-\end{itemize}
-
-\section{Literal Pattern Matching}
-
-requirements:
-
-\begin{itemize}
-  \item R-44-PATTERN-MATCHING-ON-RDF-LITERALS
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item pattern matching on literals
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
-# OWL 2 QL (functional-style syntax)
-# ----------------------------------
-Declaration( Datatype( :SSN ) ) 
-DatatypeDefinition( 
-    :SSN
-    DatatypeRestriction( xsd:string xsd:pattern "[0-9]{3}-[0-9]{2}-[0-9]{4}" ) )     
-DataPropertyRange( :hasSSN :SSN ) 
-\end{ex}
-
-\begin{ex}
-# OWL 2 QL (turtle syntax)
-# ------------------------
-:SSN 
-    a rdfs:Datatype ;
-    owl:equivalentClass [
-        a rdfs:Datatype ;
-        owl:onDatatype xsd:string ;
-        owl:withRestrictions ( 
-            [ xsd:pattern "[0-9]{3}-[0-9]{2}-[0-9]{4}" ] ) ] .
-:hasSSN rdfs:range :SSN .
-\end{ex}
-
-\begin{itemize}
-	\item A social security number is a string that matches the given regular expression. 
-The second axiom defines :SSN as an abbreviation for a datatype restriction on xsd:string. 
-The first axiom explicitly declares :SSN to be a datatype. 
-The datatype :SSN can be used just like any other datatype; 
-for example, it is used in the third axiom to define the range of the :hasSSN property. 
-\end{itemize}
-
-\begin{ex}
-# valid data
-# ----------
-:TimBernersLee
-    :hasSSN "123-45-6789"^^:SSN .
-\end{ex}
-
-\begin{ex}
-# invalid data
-# ------------
-:TimBernersLee
-    :hasSSN "123456789"^^:SSN .
-\end{ex}
-
-\begin{gcotable}
-class & SSN & - & - & xsd:string & xsd:pattern & '[0-9]{3}-[0-9]{2}-[0-9]{4}' \\
-\end{gcotable}
-
-\section{Negative Literal Pattern Matching}
-
-requirements:
-
-\begin{itemize}
-  \item R-44-PATTERN-MATCHING-ON-RDF-LITERALS
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item negative pattern matching on literals
-\end{itemize}
-
-\begin{ex}
-# examples
-# --------
-1. dbo:isbn format is different ’!’ from '^([iIsSbBnN 0-9-])*$'
-2. dbo:postCode format is different ‘!’ from 'ˆ[0-9]{5}$'
-3. foaf:phone contains any letters ('[A-Za-z]')
-\end{ex}
-
-\subsection{Example}
-
-\begin{ex}
-# test binding (DQTP)
-# -------------------
-dbo:isbn format is different ’!’ from '^([iIsSbBnN 0-9-])*$'
-
-P1 => dbo:isbn
-NOP => !
-REGEX => 'ˆ([iIsSbBnN 0-9-])*$'
-\end{ex}
-
-\begin{ex}
-# DQTP
-# ----
-SELECT DISTINCT ?s WHERE { ?s %%P1%% ?value .
-    FILTER ( %%NOP%% regex(str(?value), %%REGEX%) ) }
-\end{ex}
-
-\begin{itemize}
-	\item MATCH Pattern \cite{Kontokostas2014} 
-  \item P1 is the property we need to check against REGEX and
-NOP can be a not operator (!) or empty.
-\end{itemize}
-
-\begin{ex}
-# valid data
-# ----------
-:FoundationsOfSWTechnologies
-    dbo:isbn 'ISBN-13 978-1420090505' .
-\end{ex}
-
-\begin{ex}
-# invalid data
-# ------------
-:HandbookOfSWTechnologies
-    dbo:isbn 'DOI 10.1007/978-3-540-92913-0' .
-\end{ex}
-
-\begin{gcotable}
-property & $\top$ & dbo:isbn & - & $\neg$ A & domain & - \\
-class & $\neg$ A & - & - & A & $\neg$ & - \\
-class & A & - & - & xsd:string & regex & 'ˆ([iIsSbBnN 0-9-])*$' $ \\
-\end{gcotable}
-
-\section{Literal Value Comparison}
-
-requirement:
-
-\begin{itemize}
-	\item R-43-LITERAL-VALUE-COMPARISON
-\end{itemize}
-
-\subsection{Description}
-
-examples:
-
-\begin{ex}
-# examples
-# --------
-1. dbo:deathDate before ‘<’ dbo:birthDate
-2. dbo:releaseDate after ‘>’ dbo:latestReleaseDate
-3. dbo:demolitionDate before ‘<’ dbo:buildingStartDate
-\end{ex}
-
-\subsection{Simple Example}
-
-\begin{ex}
-# DSCL (DQTP)
-# -----------
-SELECT ?s WHERE { 
-    ?s %%P1%% ?v1 .
-    ?s %%P2%% ?v2 .
-    FILTER ( ?v1 %%OP%% ?v2 ) }
-\end{ex}
-
-COMP Pattern \cite{Kontokostas2014}
-
-Depending on the property semantics,
-there are cases where two different literal values must have
-a specific ordering with respect to an operator. 
-P1 and P2 are the datatype properties we need to compare and 
-OP is the comparison operator (\textless, \textless=, \textgreater, \textgreater=, =, !=).
-
-\begin{ex}
-# test binding (DQTP)
-# -------------------
-dbo:deathDate before ‘<’ dbo:birthDate
-
-P1 => dbo:deathDate
-P2 => dbo:birthDate
-OP => <
-\end{ex}
-
-\begin{ex}
-# valid data
-# ----------
-:AlbertEinstein
-    dbo:birthDate '1879-03-14'^^xsd:date ;
-    dbo:deathDate '1955-04-18'^^xsd:date .
-\end{ex}
-
-\begin{ex}
-# invalid data
-# ------------
-:NeilArmstrong
-    dbo:birthDate '2012-08-25'^^xsd:date ;
-    dbo:deathDate '1930-08-05'^^xsd:date .
-\end{ex}
-
-\begin{gcotable}
-property & $\top$ & dbo:birthDate & dbo:deathDate & xsd:date & \textgreater & - \\
-\end{gcotable}
-
-\section{Negative Literal Ranges}
-
-requirements:
-
-\begin{itemize}
-	\item R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item The literal value of a resource (having a certain type) must (not) be within a specific range
-  \item P1 is a data property of an instance of class T1 and its literal value must be between the range of [Vmin,Vmax] or outside ( ‘!' ).
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{itemize}
-	\item dbo:height of a dbo:Person is not within [0.4,2.5]
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{itemize}
-	\item geo:lat of a spatial:Feature is not within [-90,90]
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{itemize}
-	\item geo:long of a gml:Feature must be in range [-180,180]
-\end{itemize}
-
-\section{Literal Ranges}
-
-requirement:
-
-\begin{itemize}
-	\item R-45-RANGES-OF-RDF-LITERAL-VALUES
-\end{itemize}
-
-\subsection{Description}
-
-\subsection{Example}
-
-\begin{ex}
-# OWL 2 DL (functional-style syntax)
-# ----------------------------------
-Declaration( Datatype( :NumberPlayersPerWorldCupTeam ) ) 
-DatatypeDefinition( 
-    :NumberPlayersPerWorldCupTeam
-    DatatypeRestriction( 
-        xsd:nonNegativeInteger 
-        xsd:minInclusive "1"^^xsd:nonNegativeInteger 
-        xsd:maxInclusive "23"^^xsd:nonNegativeInteger ) )     
-DataPropertyRange( :position :NumberPlayersPerWorldCupTeam ) 
-\end{ex}
-
-\begin{ex}
-# OWL 2 DL (turtle syntax)
-# ------------------------
-:NumberPlayersPerWorldCupTeam
-    a rdfs:Datatype ;
-    owl:equivalentClass [
-        a rdfs:Datatype ;
-        owl:onDatatype xsd:nonNegativeInteger ;
-        owl:withRestrictions ( 
-            [ xsd:minInclusive "1"^^xsd:nonNegativeInteger ]
-            [ xsd:maxInclusive "23"^^xsd:nonNegativeInteger ] ) ] .
-:position rdfs:range :NumberPlayersPerWorldCupTeam .
-\end{ex}
-
-\begin{itemize}
-	\item The data range 'NumberPlayersPerWorldCupTeam' contains the non negative integers 1 to 23, as each world cup team can only have 23 football players at most
-\end{itemize}
-
-\begin{ex}
-# valid data
-# ----------
-:MarioGoetze
-    :position "19"^^:NumberPlayersPerWorldCupTeam .
-\end{ex}
-
-\begin{ex}
-# invalid data
-# ------------
-:MarioGoetze
-    :position "99"^^:NumberPlayersPerWorldCupTeam .
-\end{ex}
-
-\begin{itemize}
-	\item range of position is the datatype 1-23
-  \item constraints are stated on this datatype
-\end{itemize}
-
-\begin{DL}
-1-23 $\equiv$ \{'1'\} $\sqcup$ \{'2'\} $\sqcup$ ... $\sqcup$ \{'23'\} \\
-$\top$ $\sqsubseteq$ $\forall$ position . 1-23 \\
-\end{DL}
-
-\begin{gcotable}
-class & AtLeast1 & - & - & xsd:nonNegativeInteger & $\geq$ & 1 \\
-class & AtMost23 & - & - & xsd:nonNegativeInteger & $\leq$ & 23 \\
-class & NumberPlayers... & - & - & AtLeast1, AtMost23 & $\sqcap$ & - \\
-property & $\top$ & position & - & NumberPlayers... & range & - \\
-\end{gcotable}
-
-or:
-
-\begin{gcotable}
-property & $\top$ & position & - & 1-23 & range & - \\
-class & 1-23 & - & - & xsd:nonNegativeInteger & $\geq$ & 1 \\
-class & 1-23 & - & - & xsd:nonNegativeInteger & $\leq$ & 23 \\
-\end{gcotable}
-
-or:
-
-\begin{gcotable}
-class & 1-23 & - & - & \{'1'\}, \{'2'\}, ..., \{'23'\} & $\sqcup$ & - \\
-property & $\top$ & position & - & 1-23 & range& - \\
-\end{gcotable}
-
-\section{Define Order}
-
-requirements:
-
-\begin{itemize}
-  \item R-121-SPECIFY-ORDER-OF-RDF-RESOURCES
-	\item R-217-DEFINE-ORDER-FOR-FORMS/DISPLAY
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item order properties
-	\item order objects of object properties
-	\item order literal of data properties
-\end{itemize}
-
-\subsection{Simple Example}
-
-\section{Validation Levels}
-
-requirements:
-
-\begin{itemize}
-	\item R-205-VARYING-LEVELS-OF-ERROR
-	\item R-135-CONSTRAINT-LEVELS
-	\item R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS
-	\item R-193-MULTIPLE-CONSTRAINT-VALIDATION-EXECUTION-LEVELS
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-  \item Different levels of severity, priority
-	\item validation levels: informational, warning, error, fail, should, recommended, must, may, optional, closed (only this) constraints, open (at least this) constraints
-\end{itemize}
-
-\subsection{Simple Example}
-
-\section{String Operations}
-
-requirement:
-
-\begin{itemize}
-	\item R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item Some constraints require building new strings out of other strings
-\end{itemize}
-
-examples:
-
-\begin{itemize}
-	\item string length
-\end{itemize}
-
-\subsection{Simple Example}
-
-\section{Context-Specific Valid Classes}
-
-requirements:
-
-\begin{itemize}
-	\item R-209-VALID-CLASSES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item What types of resources (rdf:type) are valid in this context? Context can be an input stream, a data creation function, or an API.
-\end{itemize}
-
-\subsection{Simple Example}
-
-\section{Context-Specific Valid Properties}
-
-requirements:
-
-\begin{itemize}
-	\item R-210-VALID-PROPERTIES
-\end{itemize}
-
-\begin{itemize}
-	\item What properties can be used within this context? Context can be an data receipt function, data creation function, API, etc.
-\end{itemize}
-
-\subsection{Simple Example}
-
-\section{Default Values}
-
-requirements:
-
-\begin{itemize}
-	\item R-31-DEFAULT-VALUES-OF-RDF-OBJECTS
-  \item R-38-DEFAULT-VALUES-OF-RDF-LITERALS
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item default values for RDF literals
-	\item default values for RDF objects
-	\item default values are inferred automatically
-	\item It should be possible to declare the default value for a given property, e.g. so that input forms can be pre-populated and to insert a required property that is missing in a web service call. 
-\end{itemize}
-
-\subsection{Simple Example}
-
-Jedis have only 1 blue laser sword per default.
-Siths, in contrast, normally have 2 red laser swords.
-
-\begin{ex}
-# rule (SPIN)
-# -----------
-owl:Thing
-    spin:rule [
-        a sp:Construct ;
-            sp:text """
-                CONSTRUCT {            
-                    ?this :laserSwordColor "blue"^^xsd:string ;
-                    ?this :numberLaserSwords "1"^^xsd:nonNegativeInteger . 
-                }
-                WHERE {             
-                    ?this a :Jedi .            
-                } """ ; ] .
-owl:Thing
-    spin:rule [
-        a sp:Construct ;
-            sp:text """
-                CONSTRUCT {
-                    ?this :laserSwordColor "red"^^xsd:string ;
-                    ?this :numberLaserSwords "2"^^xsd:nonNegativeInteger . 
-                }
-                WHERE {             
-                    ?this a :Sith .            
-                } """ ; ] .
-\end{ex}
-
-\begin{ex}
-# data
-# ----
-:Joda a :Jedi .
-:DarthSidious a :Sith .
-\end{ex}
-
-\begin{ex}
-# inferred triples
-# ----------------
-:Joda 
-    :laserSwordColor "blue"^^xsd:string ;
-    :numberLaserSwords "1"^^xsd:nonNegativeInteger .
-:DarthSidious 
-    :laserSwordColor "red"^^xsd:string ;
-    :numberLaserSwords "2"^^xsd:nonNegativeInteger .
-\end{ex}
-
-\section{Mathematical Operations}
-
-requirements:
-
-\begin{itemize}
-	\item R-42-MATHEMATICAL-OPERATIONS
-	\item R-41-STATISTICAL-COMPUTATIONS
-\end{itemize}
-
-\subsection{Description}
-
-examples:
-
-\begin{itemize}
-	\item adding 2 dates
-	\item add number of days to start date
-	\item area = width * height
-	\item Statistical Computations: average, mean, sum
-\end{itemize}
-
-\subsection{Simple Example}
-
-\section{Language Tag Matching}
-
-requirement:
-
-\begin{itemize}
-	\item R-47-LANGUAGE-TAG-MATCHING
-\end{itemize}
-
-\section{Cardinality on Literal Language Tags}
-
-requirements:
-
-\begin{itemize}
-	\item R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG
-	\item R-48-MISSING-LANGUAGE-TAGS
-\end{itemize}
-
-\subsection{Description}
-
-\subsection{Example}
-
-check that no language is used more than once per property
-
-\begin{ex}
-# DQTP
-# ----
-SELECT DISTINCT ?s WHERE { ?s %%P1%% ?c
-    BIND ( lang(?c) AS ?l )
-    FILTER (isLiteral (?c) && lang(?c) = %%V1%%)}
-GROUP BY ?s HAVING COUNT (?l) > 1
-\end{ex}
-
-\begin{itemize}
-	\item ONELANGPattern \cite{Kontokostas2014} 
-  \item A literal value should contain at most 1 literal for a language. 
-  \item P1 is the property containing the literal and V1 is the language we want to check.
-\end{itemize}
-
-\begin{ex}
-# test binding (DQTP)
----------------------
-P1 => foaf:name
-V1 => en
-\end{ex}
-
-\begin{itemize}
-	\item a single English (“en”) foaf:name
-\end{itemize}
-
-\begin{ex}
-# valid data
-# ----------
-:LeiaSkywalker
-    foaf:name 'Leia Skywalker'@en .
-\end{ex}
-
-\begin{ex}
-# invalid data
-# ------------
-:LeiaSkywalker
-    foaf:name 'Leia Skywalker'@en ;
-    foaf:name 'Leia'@en .
-\end{ex}
-
-\section{Whitespace Handling}
-
-requirement:
-
-\begin{itemize}
-	\item R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item avoid whitespaces in literals neither leading nor trailing white spaces
-\end{itemize}
-
-\subsection{Simple Example}
-
-\section{HTML Handling}
-
-requirement:
-
-\begin{itemize}
-	\item R-51-HTML-HANDLING-OF-RDF-LITERALS
-\end{itemize}
-
-description:
-
-\begin{itemize}
-	\item check if there are no html tags included in literals (of specific data properties within the context of specific classes)
-\end{itemize}
-
-\subsection{Simple Example}
-
-\section{Required Properties}
-
-requirements:
-
-\begin{itemize}
-	\item R-68-REQUIRED-PROPERTIES
-\end{itemize}
-
-\subsection{Description}
-
-\subsection{Simple Example}
-
-\section{Optional Properties}
-
-requirements:
-
-\begin{itemize}
-	\item R-69-OPTIONAL-PROPERTIES
-\end{itemize}
-
-\subsection{Description}
-
-\subsection{Simple Example}
-
-\section{Repeatable Properties}
-
-requirements:
-
-\begin{itemize}
-	\item R-70-REPEATABLE-PROPERTIES
-\end{itemize}
-
-\subsection{Description}
-
-\subsection{Simple Example}
-
-\section{Conditional Properties}
-
-requirements:
-
-\begin{itemize}
-	\item R-71-CONDITIONAL-PROPERTIES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item various conditions possible
-  \item condition: universal quantification on object and data properties
-  \item condition: existential quantification on object and data properties
-  \item condition: if specific properties are present, then specific other properties also have to be present
-\end{itemize}
-
-\subsection{Simple Example}
-
-\section{Recommended Properties}
-
-requirements:
-
-\begin{itemize}
-	\item R-72-RECOMMENDED-PROPERTIES
-\end{itemize}
-
-\subsection{Description}
-
-\subsection{Simple Example}
-
-\section{Negative Property Constraints}
-
-requirements:
-
-\begin{itemize}
-	\item R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS
-	\item R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item instances of a specific class must not have some object property
-  \item OWL 2 DL: ObjectComplementOf ( ObjectSomeValuesFrom ( ObjectPropertyExpression owl:Thing ) )
-\end{itemize}
-
-\subsection{Example}
-
-\begin{ex}
-# ShEx
-# ----
-<FeelingForce> {
-    :feelingForce (true) ,
-    :attitute xsd:string }
-<JediMentor> {
-    :feelingForce (true) ,
-    :attitute ('good') ,
-    :laserSwordColor xsd:string ,
-    :numberLaserSwords xsd:nonNegativeInteger ,
-    :mentorOf @<JediStudent> ,
-   !:studentOf @<JediMentor> }
-<JediStudent> {
-    :feelingForce (true) ,
-    :attitute ('good') ,
-    :laserSwordColor xsd:string ,
-    :numberLaserSwords xsd:nonNegativeInteger ,
-   !:mentorOf @<JediStudent> ,
-    :studentOf @<JediMentor> }
-\end{ex}
-
-\begin{itemize}
-	\item A matching triple has any predicate except those excluded by the '!' operator.
-  \item \url{http://w3.org/brief/Mzk0}
-\end{itemize}
-
-\begin{ex}
-# individuals matching 'FeelingForce' and 'JediMentor' data shapes
-# ----------------------------------------------------------------
-:Obi-Wan 
-    :feelingForce true ;
-    :attitute 'good' ;
-    :laserSwordColor 'blue' ;
-    :numberLaserSwords '1'^^xsd:nonNegativeInteger ;
-    :mentorOf :Anakin .
-\end{ex}
-
-\begin{ex}
-# individuals matching 'FeelingForce' and 'JediStudent' data shapes
-# -----------------------------------------------------------------
-:Anakin 
-    :feelingForce true ;
-    :attitute 'good' ;
-    :laserSwordColor 'blue' ;
-    :numberLaserSwords '1'^^xsd:nonNegativeInteger ;
-    :studentOf :Obi-Wan .
-\end{ex}
-
-\section{Handle RDF Collections}
-
-requirement:
-
-\begin{itemize}
-	\item R-120-HANDLE-RDF-COLLECTIONS
-\end{itemize}
-
-\subsection{Description}
-
-examples:
-
-\begin{itemize}
-	\item size of collection
-	\item first / last element of list must be a specific literal
-	\item compare elements of collection
-	\item are collections identical?
-	\item actions on RDF lists: \url{http://www.snee.com/bobdc.blog/2014/04/rdf-lists-and-sparql.html}
-	\item 2. list element equals ''
-	\item Does the list have more than 10 elements?
-\end{itemize}
-
-\subsection{Example}
-
-\begin{itemize}
-	\item get 2. list element
-\end{itemize}
-
-\begin{ex}
-# SPIN
-# ----
-:getListItem
-    a spin:Function ; rdfs:subClassOf spin:Functions ;
-    spin:constraint [
-        rdf:type spl:Argument ;
-        spl:predicate sp:arg1 ;
-        spl:valueType rdf:List ;
-        rdfs:comment "list" ; ] ;
-    spin:constraint [
-        rdf:type spl:Argument ;
-        spl:predicate sp:arg2 ;
-        spl:valueType xsd:nonNegativeInteger ;
-        rdfs:comment "item position (starting with 0)" ; ] ;
-    spin:body [
-        a sp:SELECT ;
-        sp:text """
-            SELECT ?item
-            WHERE {
-                ?arg1 :contents/rdf:rest{?arg2}/rdf:first ?item } """ ; ] ;
-    spin:returnType rdfs:Resource .
-\end{ex}
-
-\begin{ex}
-# data
-# ----
-:Jinn :students 
-     ( :Xanatos :Kenobi ) . 
-\end{ex}
-
-\begin{ex}
-# SPIN
-# ----
-BIND ( :getListItem( ?list, "1"xsd:nonNegativeInteger ) AS ?listItem ) .
-\end{ex}
-
-\begin{itemize}
-  \item SPIN function call
-	\item retrieves the 2. item from the list (2. student of Jedi mentor Jinn)
-\end{itemize}
-
-\begin{ex}
-# result
-# ------
-:Kenobi
-\end{ex}
-
-\section{Recursive Queries}
-
-requirements:
-
-\begin{itemize}
-	\item R-222-RECURSIVE-QUERIES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item If we want to define Resource Shapes, remember that it is a recursive
-language (the valueShape of a Resource Shape is in turn another
-Resource Shape). There is no way to express that in SPARQL without
-hand-waving "and then you call the function again here" or "and then
-you embed this operation here" text.  The embedding trick doesn't work
-in the general case because SPARQL can't express recursive queries,
-e.g. "test that this Issue is valid and all of the Issues that
-references, recursively".
-  \item Most SPARQL engines already have
-functions that go beyond the official SPARQL 1.1 spec. The cost of that
-sounds manageable to me.
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
-# ShEx
-# ----
-<IssueShape> {
-    :state (:unassigned :assigned),
-    :reportedBy @<UserShape>,
-    :related @<IssueShape>*
-}
-\end{ex}
-
-\section{Value is Valid for Datatype}
-
-requirements:
-
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item make sure that a value is valid for its datatype
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{itemize}
-	\item a date is really a date
-  \item SPARQL regex can be used
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
-# SPIN
-# ----
-FILTER ( datatype( ?shoeSize ) = xsd:nonNegativeInteger )
-isNumeric ( ?shoeSize )
-\end{ex}
-
-\begin{itemize}
-	\item datatype of ?showSize id xsd:nonNegativeInteger
-	\item datatype is really numeric
-\end{itemize}
-
-\section{Individual Equality}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item states that two different names are known to refer to the same individual \cite{Kroetzsch2012}
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{DL}
-julia = john \\
-\end{DL}
-
-\begin{gcotable}
-class & \{julia\} & - & - & \{john\} & = \\
-class & \{john\} & - & - & \{julia\} & = \\
-\end{gcotable}
-
-\section{Individual Inequality}
-
-\subsection{Description}
-
-\subsection{Simple Example}
-
-\begin{DL}
-julia $\ne$ john
-\end{DL}
-
-\begin{itemize}
-	\item asserts that Julia and John are actually different individuals
-\end{itemize}
-
-\begin{gcotable}
-class & \{julia\} & - & - & \{john\} & $\ne$ \\
-class & \{john\} & - & - & \{julia\} & $\ne$ \\
-\end{gcotable}
-
-\section{Equivalent Properties}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item An equivalent object properties axiom EquivalentObjectProperties( OPE1 ...
-OPEn ) states that all of the object property expressions OPEi, 1 $\leq$ i $\leq$ n, are semantically equivalent to each other.
-This axiom allows one to use each OPEi as a synonym for each OPEj — that is, in any expression in the ontology containing such an axiom, OPEi can be replaced with OPEj without affecting the meaning of the ontology.
-The axiom EquivalentObjectProperties( OPE1 OPE2 ) is equivalent to the following two axioms SubObjectPropertyOf( OPE1 OPE2 ) and SubObjectPropertyOf( OPE2 OPE1 ).
-	\item An equivalent data properties axiom EquivalentDataProperties( DPE1 ...
-DPEn ) states that all the data property expressions DPEi, 1 $\leq$ i $\leq$ n, are semantically equivalent to each other.
-This axiom allows one to use each DPEi as a synonym for each DPEj — that is, in any expression in the ontology containing such an axiom, DPEi can be replaced with DPEj without affecting the meaning of the ontology.
-The axiom EquivalentDataProperties( DPE1 DPE2 ) can be seen as a syntactic shortcut for the following axiom SubDataPropertyOf( DPE1 DPE2 ) and SubDataPropertyOf( DPE2 DPE1 ).
-
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
-# OWL 2
-# -----
-:hasBrother owl:equivalentProperty :hasMaleSibling . 
-:Chris :hasBrother :Stewie . 
-:Stewie :hasMaleSibling :Chris .
-\end{ex}
-
-entailments:
-
-\begin{ex}
-:Chris :hasMaleSibling a:Stewie . 
-:Stewie :hasBrother a:Chris .
-\end{ex}
-
-\begin{DL}
-:hasBrother $\sqsubseteq$ :hasMaleSibling $\sqcap$ :hasMaleSibling $\sqsubseteq$ :hasBrother \\
-\end{DL}
-
-\section{Property Assertions}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item positive property assertions
-  \item negative property assertions
-	\item A positive object property assertion ObjectPropertyAssertion( OPE a1 a2 ) states that the individual a1 is connected by the object property expression OPE to the individual a2. 
-	\item A negative object property assertion NegativeObjectPropertyAssertion( OPE a1 a2 ) states that the individual a1 is not connected by the object property expression OPE to the individual a2. 
-	\item A positive data property assertion DataPropertyAssertion( DPE a lt ) states that the individual a is connected by the data property expression DPE to the literal lt. 
-	\item A negative data property assertion NegativeDataPropertyAssertion( DPE a lt ) states that the individual a is not connected by the data property expression DPE to the literal lt.
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
-# OWL 2
-# -----
-NegativeObjectPropertyAssertion( :hasSon :Peter :Meg )
-\end{ex}
-
-\begin{itemize}
-	\item Meg is not a son of Peter.
-\end{itemize}
-
-\begin{DL}
-
-\end{DL}
-
-\tb{ToDo: DL}
-
-\subsection{Simple Example}
-
-\begin{ex}
-# OWL 2
-# -----
-DataPropertyAssertion( :hasAge :Meg "17"^^xsd:integer )
-\end{ex}
-
-\begin{itemize}
-	\item Meg is seventeen years old. 
-\end{itemize}
-
-\begin{DL}
-:hasAge ( :Meg , "17"^^xsd:integer ) \\
-\end{DL}
-
-\section{Functional Properties}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item An object property functionality axiom FunctionalObjectProperty( OPE ) states that the object property expression OPE is functional — that is, for each individual x, there can be at most one distinct individual y such that x is connected by OPE to y.
-Each such axiom can be seen as a syntactic shortcut for the following axiom: SubClassOf( owl:Thing ObjectMaxCardinality( 1 OPE ) ).
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
-# OWL 2
-# -----
-:hasFather rdf:type owl:FunctionalProperty . 	
-:Stewie :hasFather :Peter . 	
-:Stewie :hasFather :Peter_Griffin . 
-\end{ex}
-
-\begin{itemize}
-	\item Each object can have at most one father. 
-\end{itemize}
-
-entailment:
-
-\begin{ex}
-:Peter_Griffin owl:sameAs :Peter .  
-\end{ex}
-
-\begin{DL}
-owl:Thing $\sqsubseteq$ $\leq$ 1 :hasFather
-\end{DL}
-
-\section{Inverse-Functional Properties}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item An object property inverse functionality axiom InverseFunctionalObjectProperty( OPE ) states that the object property expression OPE is inverse-functional — that is, for each individual x, there can be at most one individual y such that y is connected by OPE with x.
-Each such axiom can be seen as a syntactic shortcut for the following axiom: SubClassOf( owl:Thing ObjectMaxCardinality( 1 ObjectInverseOf( OPE ) ) ).
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
-# OWL 2
-# -----
-:fatherOf rdf:type owl:InverseFunctionalProperty . 	
-:Peter :fatherOf :Stewie .
-:Peter_Griffin :fatherOf :Stewie .
-\end{ex}
-
-\begin{itemize}
-	\item Each object can have at most one father. 
-\end{itemize}
-
-entailment:
-
-\begin{ex}
-:Peter owl:sameAs :Peter_Griffin . 
-\end{ex}
-
-\begin{DL}
-
-\end{DL}
-
-\tb{ToDo: DL}
-
-\section{Value Restrictions}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item Individual Value Restrictions: A has-value class expression ObjectHasValue( OPE a ) consists of an object property expression OPE and an individual a, and it contains all those individuals that are connected by OPE to a.
-Each such class expression can be seen as a syntactic shortcut for the class expression ObjectSomeValuesFrom( OPE ObjectOneOf( a ) ).
-	\item Literal Value Restrictions: A has-value class expression DataHasValue( DPE lt ) consists of a data property expression DPE and a literal lt, and it contains all those individuals that are connected by DPE to lt.
-Each such class expression can be seen as a syntactic shortcut for the class expression DataSomeValuesFrom( DPE DataOneOf( lt ) ).
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
-:Peter :fatherOf :Stewie . 
-ObjectHasValue( :fatherOf :Stewie )
-\end{ex}
-
-\begin{itemize}
-	\item The has-value class expression contains those individuals that are connected through the :fatherOf property with the individual :Stewie
-  \item :Peter is classified as its instance
-\end{itemize}
-
-\begin{DL}
-
-\end{DL}
-
-\tb{ToDo: DL}
-
-\section{Self Restrictions}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item A self-restriction ObjectHasSelf( OPE ) consists of an object property expression OPE, and it contains all those individuals that are connected by OPE to themselves. 
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
-:Peter :likes :Peter . 
-ObjectHasSelf( :likes ) 
-\end{ex}
-
-\begin{itemize}
-	\item The self-restriction contains those individuals that like themselves
-  \item :Peter is classified as its instance
-\end{itemize}
-
-\section{Data Property Facets}
-
-requirement:
-
-\begin{itemize}
-	\item R-46-CONSTRAINING-FACETS
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-  \item For datatype properties it should be possible to declare frequently needed "facets" to drive user interfaces and validate input against simple conditions, including min/max value, regular expressions, string length etc.
-similar to XSD datatypes.
-	\item constraining facets to restrict datatypes of RDF literals
-  \item constraining facets: xsd:length, xsd:minLength, xsd:maxLength, xsd:pattern, xsd:enumeration, xsd:whiteSpace, xsd:maxInclusive, xsd:maxExclusive, xsd:minExclusive, xsd:minInclusive, xsd:totalDigits, xsd:fractionDigits
-
-\end{itemize}
-
-\subsection{Simple Example}
-
-\textbf{string matches regular expression}
-
-\begin{ex}
-# OWL 2 QL (functional-style syntax)
-# ----------------------------------
-Declaration( Datatype( :SSN ) ) 
-DatatypeDefinition( 
-    :SSN
-    DatatypeRestriction( xsd:string xsd:pattern "[0-9]{3}-[0-9]{2}-[0-9]{4}" ) )     
-DataPropertyRange( :hasSSN :SSN ) 
-\end{ex}
-
-\begin{ex}
-# OWL 2 QL (turtle syntax)
-# ------------------------
-:SSN 
-    a rdfs:Datatype ;
-    owl:equivalentClass [
-        a rdfs:Datatype ;
-        owl:onDatatype xsd:string ;
-        owl:withRestrictions ( 
-            [ xsd:pattern "[0-9]{3}-[0-9]{2}-[0-9]{4}" ] ) ] .
-:hasSSN rdfs:range :SSN .
-\end{ex}
-
-\begin{itemize}
-	\item A social security number is a string that matches the given regular expression. 
-The second axiom defines :SSN as an abbreviation for a datatype restriction on xsd:string. 
-The first axiom explicitly declares :SSN to be a datatype. 
-The datatype :SSN can be used just like any other datatype; 
-for example, it is used in the third axiom to define the range of the :hasSSN property. 
-\end{itemize}
-
-\begin{ex}
-# valid data
-# ----------
-:TimBernersLee
-    :hasSSN "123-45-6789"^^:SSN .
-\end{ex}
-
-\begin{ex}
-# invalid data
-# ------------
-:TimBernersLee
-    :hasSSN "123456789"^^:SSN .
-\end{ex}
-
-\begin{gcotable}
-class & SSN & - & - & xsd:string & xsd:pattern & '[0-9]{3}-[0-9]{2}-[0-9]{4}' \\
-\end{gcotable}
-
-\section{Primary Key Properties}
-
-requirement:
-
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-  \item It is often useful to declare a given (datatype) property as the "primary key" of a class, so that the system can enforce uniqueness and also automatically build URIs from user input and data imported from relational databases or spreadsheets.
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{itemize}
-	\item Each object is uniquely identified by its social security number.
-\end{itemize}
-
-\begin{ex}
-# DSP
-# ---
--
-\end{ex}
-
-\begin{ex}
-# OWL2 DL
-# -------
-owl:Thing owl:hasKey ( :hasSSN ) . 	
-\end{ex}
-
-\begin{ex}
-# ReSh
-# ----
--
-\end{ex}
-
-\begin{ex}
-# ShEx
-# ----
--
-\end{ex}
-
-\begin{itemize}
-	\item The first axiom makes :hasSSN the key for instances of the owl:Thing class; thus, only one individual can have a particular value for :hasSSN. 
-\end{itemize}
-
-\begin{ex}
-# data
-# ----
-:Peter :hasSSN "123-45-6789" . 
-:PeterGriffin :hasSSN "123-45-6789" . 
-\end{ex}
-
-\begin{itemize}
-	\item Since the values of :hasSSN are the same for the individuals a:Peter and a:PeterGriffin, these two individuals are equal - that is, this ontology entails the following assertion :Peter owl:sameAs :PeterGriffin .
-\end{itemize}
-
-\begin{DL}
-
-\end{DL}
-
-\tb{ToDo: DL}
-
-\input{DL-Check}
+\tb{complexity without OWL 2 QL inferencing?}
 

### 2014-12-16 paper/RDF validation requirements/RDF validation requirements.tex
language tag operations
complexity

@@
 
-\section{Cardinality on Literal Language Tags}
+\section{Language Tag Cardinality}
 
@@
 
+\section{Exploiting Class/Property Specialization Ontology Axioms}
+
+requirement:
+
+\begin{itemize}
+	\item R-224-instance-level-data-validation-exploitingclass/property-specialization-axioms-in-ontologies
+\end{itemize}
+
+\subsection{Description}
+
+\begin{itemize}
+  \item Validation of instances data (direct or indirect) exploiting the subclass or sub-property link in a given ontology.
+  \item This validation can indicate when the data is verbose (redundant) or expressed at a too general level, and could be improved.
+\end{itemize}
+
+examples:
+
+\begin{itemize}
+	\item If dc:date and one of its sub-properties dcterms:created or dcterms:issued are present, check that the value in dc:date is not redundant with dcterms:created or dcterms:issued for ingestion
+  \item Check if dc:rights has the same value than edm:rights either as rdf:resource or literal, if yes dc:rights is redundant
+  \item If one or more dc:coverage are present, suggest the use of one of its sub-properties, dcterms spatial or dcterms:temporal.
+\end{itemize}
+
+\end{itemize}
+
 \input{DL-Check}

### 2014-12-16 paper/RDF validation requirements/RDF validation requirements.tex
RDF validation requirements tex file has been updated.

--- 2014-12-15 paper/RDF validation requirements/RDF validation requirements.tex
@@
 \begin{itemize}
-	\item DL termonology: universal restriction
-\end{itemize}
-
-\tb{definition}
+	\item DL terminology: value restriction
+\end{itemize}
+
+$(\forall R.C)^\mathcal{I}= \{a \in \Delta^\mathcal{I}\mid (a,b) \in R^\mathcal{I} \rightarrow b \in C^\mathcal{I} \}$ where $\cdot^\mathcal{I}$ is an interpretation function, $\Delta^I$ is the domain, $a,b \in \Delta^\mathcal{I}$ are individuals $C$ is a concept, $R$ is a role.
 
@@
 
-\tb{definition}
+$\exists R. \top \sqsubseteq C$ is the object property restriction where $R$ is the object property (role) whose domain is restricted to concept $C$.
 
@@
 
-\tb{definition}
+$\top \sqsubseteq \forall R . C$ is the range restriction to object property $R$ (restricted by concept $C$).
 
@@
 \end{itemize}
+
+Definition:\\
+
+$\leq n R. \top$ is minimum unqualified cardinality restriction where $n \in \mathbb{N}$ (written $\leq  n R$ in short).
 
@@
 \end{ex}
-
-\tb{ToDO: add DL}
+\er{Note that this example includes also has at-most restriction.}\\
+
+Assume that  mentorOf and studentOf are inverse properties.\\
+\begin{DL}
+$Jedi \sqsubseteq \exists attitude.\{good\} $\\
+$JediStudent \sqsubseteq Jedi \sqcap 1\geq studentOf.\top \sqcap 1\leq studentOf.\top$ \\
+$JediMasters \sqsubseteq Jedi \sqcap 1\leq studentOf^{-}.\top \sqcap 2\geq studentOf^{-}.\top $\\
+$SuperJediMaster \sqsubseteq Jedi \sqcap  3\leq studentOf^{-}.\top $
+\end{DL}
 
@@
 \end{itemize}
+Definition:\\
+
+$\leq n R. C$ is minimum qualified cardinality restriction where $n \in \mathbb{N}$.
 
@@
 \end{DL}
-
-\tb{ToDO: check DL}
 
@@
 \tb{ToDO: check DL}
-
+\er{foaf: or xsd:string is no DL syntax. So you can delete 18.2 if you are fine.}
 \begin{gcotable}
@@
 
-\tb{ToDO: OWL 2 DL}
+%\tb{ToDO: OWL 2 DL}
 
@@
 
-\tb{ToDO: add DL}
-
+\noindent $mentorOf$ and $studentOf$ are taken to be inverse properties:\\
+
+\begin{DL}
+$Jedi \sqsubseteq \exists attitude.\{good\} $\\
+$JediStudent \sqsubseteq Jedi \sqcap 1\geq studentOf.Jedi \sqcap 1\leq studentOf.Jedi$ \\
+$JediMasters \sqsubseteq Jedi \sqcap 1\leq studentOf^{-}.Jedi\sqcap 2\geq studentOf^{-}.Jedi $\\
+$SuperJediMaster \sqsubseteq Jedi \sqcap  3\leq studentOf^{-}.Jedi $
+\end{DL}
 \subsection{Complex Example}
@@
 
-\tb{ToDO: check DL}
+%\tb{ToDO: check DL}
 
@@
 
+Definition:\\
+
+$\geq n R. \top$ is maximum unqualified cardinality restriction where $n \in \mathbb{N}$ (written $\geq  n R$ in short).
 \subsection{Simple Example}
@@
 \end{itemize}
-
+\er{Notice that this example includes minimum restriction.}
 \begin{ex}
@@
 
-\tb{ToDO: add DL}
+%\tb{ToDO: add DL}
+\noindent Taking mentorOf and studentOf as inverse properties. \\
+\begin{DL}
+$Jedi \sqsubseteq \exists attitude.\{good\} $\\
+$JediStudent \sqsubseteq Jedi \sqcap 1\geq studentOf.\top \sqcap 1\leq studentOf.\top$ \\
+$JediMasters \sqsubseteq Jedi \sqcap 1\leq studentOf^{-}.\top \sqcap 2\geq studentOf^{-}.\top $\\
+$SuperJediMaster \sqsubseteq Jedi \sqcap  3\leq studentOf^{-}.\top $
+\end{DL}
 
@@
 \end{itemize}
+Definition:\\
+
+$\leq n R. C$ is maximum qualified cardinality restriction where $n \in \mathbb{N}$.
 
@@
 \tb{ToDO: OWL 2 DL}
-
+\er{why OWL 2 DL?}
 \begin{ex}
@@
 
-\tb{ToDO: add DL}
+%\tb{ToDO: add DL}
+
+\noindent $mentorOf$ and $studentOf$ are taken to be inverse properties:\\
+
+\begin{DL}
+$Jedi \sqsubseteq \exists attitude.\{good\} $\\
+$JediStudent \sqsubseteq Jedi \sqcap 1\geq studentOf.Jedi \sqcap 1\leq studentOf.Jedi$ \\
+$JediMasters \sqsubseteq Jedi \sqcap 1\leq studentOf^{-}.Jedi\sqcap 2\geq studentOf^{-}.Jedi $\\
+$SuperJediMaster \sqsubseteq Jedi \sqcap  3\leq studentOf^{-}.Jedi $
+\end{DL}
 
@@
 
+Definition:\\
+
+$\geq n R. \top \sqcap \leq n R. \top $ is exact unqualified cardinality restriction where $n \in \mathbb{N}$. ($\top$ can be dropped in short writing.)
 \subsection{Simple Example}
@@
 
-\tb{ToDO: add DL}
-
+%\tb{ToDO: add DL}
+\begin{DL}
+$Jedi \sqsubseteq \exists attitude.\{good\} $\\
+$JediStudent \sqsubseteq Jedi \sqcap 1\geq studentOf.\top \sqcap 1\leq studentOf.\top$ \\
+\end{DL}
 \section{Exact Qualified Cardinality Restrictions on Properties}
@@
 
-\subsection{Simple Example}
-
-\tb{ToDO: OWL 2 DL}
+Definition:\\
+
+$\geq n R. C \sqcap \leq n R. C $ is exact unqualified cardinality restriction where $n \in \mathbb{N}$.
+\subsection{Simple Example}
+
+%\tb{ToDO: OWL 2 DL}
 
@@
 
-\tb{ToDO: add DL}
+\begin{DL}
+$Jedi \sqsubseteq \exists attitude.\{good\} $\\
+$JediStudent \sqsubseteq Jedi \sqcap 1\geq studentOf.Jedi \sqcap 1\leq studentOf.Jedi$ \\
+\end{DL}
 
@@
 \begin{DL}
-marriedTo $\equiv$ $marriedTo^{-}$ \\
+$marriedTo \sqsubseteq marriedTo^{-}$ \\
 \end{DL}
@@
 \begin{DL}
-Disjoint( parentOf , $parentOf^{-}$ )
+$parentOf \sqsubseteq \neg parentOf^{-}$ or\\
+$parentOf \sqcap parentOf^{-} \sqsubseteq \bot$
 \end{DL}
@@
 \begin{DL}
-$\top$ $\sqsubseteq$ $\neg$ $\exists$ marriedTo . Self
+$\top$ $\sqsubseteq$ $\neg$ $\exists  marriedTo . Self$   OR\\
+$\exists marriedTo . Self \sqsubseteq \bot$  OR\\
+$marriedTo \sqcap marriedTo^{-} \sqsubseteq \bot$ (without special self-concept Self)
 \end{DL}
@@
 \end{DL}
-
+\er{Where does this using $foaf:$ in DL come from? We need a description.}
 \section{Context-Specific Exclusive OR of Properties}
@@
 
+\er{Let us mark that $foaf:$ occurs here.}
+
 \begin{gcotable}
@@
 
+\er{Unsure what is meant in this example.}
+
 \subsection{Complex Example}
@@
 
-\tb{ToDo: DL}
+%\tb{ToDo: DL}
+
+\er{Unsure what is meant in this example. Could be instead:}
+
+\begin{DL}
+$Person \sqsubseteq ((Male \sqcap \neg Female) \sqcup (\neg Male \sqcap  Female)) $ 
+\end{DL}
 
@@
 \begin{DL}
-Jedi $\equiv$ $\exists$ laserSwordColor . \{'blue'\} $\sqcup$ \{'green'\} $\sqcup$ \{'white'\} \\
-\end{DL}
-
-\tb{ToDo: check DL}
+Jedi $\equiv$ $\exists$ laserSwordColor . \{blue, green, white\} \\
+\end{DL}
+
+%\tb{ToDo: check DL}
 
@@
 \begin{DL}
-Sith $\equiv$ $\neg$( $\exists$ laserSwordColor . \{'blue'\} $\sqcup$ \{'green'\} $\sqcup$ \{'white'\} ) \\
-\end{DL}
-
-\tb{ToDo: check DL}
+Sith $\equiv$ $\neg$ $\exists$ laserSwordColor . \{blue, green, white\} \\
+\end{DL}
+
+%\tb{ToDo: check DL}
 
@@
 \end{itemize}
-
+\er{This sort of DL-syntax (with semicolon) must be rechecked.
+Note that in DL, it does not have to correspond directly to names of things in machine-readable syntax.
+It is fine to say BookSubjects rather than :BookSubjects for the sake of simplicity }
 \begin{DL}

### 2014-12-16 paper/RDF validation requirements/RDF validation requirements.tex
RDF validation requirements updated
cardinality shortcuts
Context-Specific Exclusive OR of Properties example

@@
 
-\tb{ToDo. OWL 2 DL}
+%\tb{ToDo. OWL 2 DL}
 
@@
     a owl:Restriction ;
-    owl:onProperty foaf:givenNme ;
+    owl:onProperty foaf:givenName ;
     owl:allValuesFrom xsd:string ] .
@@
 \er{Unsure what is meant in this example.}
+
+\subsection{Simple Example}
+
+\begin{ex}
+# ShEx
+# ----
+<FeelingForce> { (  
+    :attackingBySword xsd:boolean | 
+    :attackingByForce xsd:boolean ) }
+\end{ex}
+
+\begin{ex}
+# OWL 2 DL
+# --------
+:FeelingForce owl:disjointUnionOf ( :CC1 :CC2 ) . 
+:CC1 rdfs:subClassOf [
+    a owl:Restriction ;
+    owl:onProperty :attackingBySword ;
+    owl:allValuesFrom xsd:boolean ] .
+:CC2 rdfs:subClassOf [
+    a owl:Restriction ;
+    owl:onProperty :attackingByForce ;
+    owl:allValuesFrom xsd:boolean ] .
+\end{ex}
+
+\begin{itemize}
+	\item :FeelingForce $\equiv$ 1 :attackingBySword (range xsd:boolean) XOR 1 :attackingByForce (range xsd:boolean)
+\end{itemize}
+
+\begin{DL}
+A $\equiv$ $\forall$ :attackingBySword . xsd:boolean \\
+B $\equiv$ $\forall$ :attackingByForce . xsd:boolean \\ 
+:FeelingForce $\sqsubseteq$ ($\neg$ A $\sqcap$ B) $\sqcup$ (A $\sqcap$ $\neg$ B) \\
+\end{DL}
 
@@
 
-\end{itemize}
+\section{Cardinality Shortcuts}
+
+requirement:
+
+\begin{itemize}
+	\item 
+\end{itemize}
+
+\subsection{Description}
+
+\begin{itemize}
+  \item In most Library applications, these tend to appear in pairs, with repeatable / non-repeatable establishing max cardinality and optional / mandatory establishing min cardinality.
+	\item Optional \& Non-Repeatable = [0,1]
+  \item Optional \& Repeatable = [0,*]
+  \item Mandatory \& Non-Repeatable = [1,1]
+  \item Mandatory \& Repatable = [1,*]
+\end{itemize}
+
+\end{document}
 

### 2014-12-17 paper/RDF validation requirements/RDF validation requirements.tex
RDF Validation Requirements chapter
Context-Specific Exclusive OR of Properties
work on DL expressions for constraints starting at 36, some small improvements on earlier points

@@
 \usepackage{amsmath, amssymb}
+\usepackage{examplep}
 \usepackage{mathabx}
@@
 \newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
-\newcommand{\an}[1]{\todo[size=\small, color=green!40]{\textbf{Andreas:} #1}}
+\newcommand{\an}[1]{\todo[size=\small, color=green!40]{\textbf{Andy:} #1}}
 \newcommand{\er}[1]{\todo[size=\small, color=red!40]{\textbf{Erman:} #1}}
@@
 \begin{DL}
-Disjoint(parentOf, childOf)
+Disjoint(parentOf, childOf)\\
+Alternative:\\
+$parentOf \sqsubseteq \neg childOf$
 \end{DL}
@@
 \begin{DL}
-Male $\sqcap$ Female $\sqsubseteq$ $\perp$
+Male $\sqcap$ Female $\sqsubseteq$ $\perp$\\
+Alternative:\\
+$Male \sqsubseteq \neg Female$
 \end{DL}
@@
 \begin{DL}
-$\top$ $\sqsubseteq$ $\forall$ sonOf . Parent 
+$\top$ $\sqsubseteq$ $\forall$ sonOf . Parent \\
+Equivalent to:\\
+$\exists sonOf\sp{\overline{\ }}.\top \sqsubseteq Person$
 \end{DL}
@@
 parentOf $\equiv$ $childOf^{-}$ \\
-\end{DL}
+not sure if this should be rather\\
+$parentOf \sqsubseteq childOf^{-}$ \\
+\end{DL}
+
+\an{not sure!}
 
@@
 \er{Where does this using $foaf:$ in DL come from? We need a description.}
+
+\an{I think we should use the existential quantifier instead of the universal quantifier!?}
+\begin{DL}
+$A \sqsubseteq \exists name.xsd:string$ \\
+$B \sqsubseteq \exists givenName.xsd:string$ \\
+$D \sqsubseteq \exists mbox.xsd:string$ \\
+$Human \sqsubseteq C \sqcap D$ \\
+\end{DL}
+
 \section{Context-Specific Exclusive OR of Properties}
@@
 
+\begin{DL}
+NOT EXPRESSIBLE IN DL!!!
+\end{DL}
+
 \begin{gcotable}
@@
 \end{ex}
+
+\begin{DL}
+NOT EXPRESSIBLE IN DL!!!
+\end{DL}
 
@@
 $\top$ $\sqsubseteq$ $\forall$ position . 1-23 \\
+This is just an auxiliary construction and is not sufficient for general cases, so: NOT EXPRESSIBLE IN DL!!!
 \end{DL}
@@
 
+\begin{DL}
+NOT EXPRESSIBLE IN DL!!!
+\end{DL}
+
 \section{Validation Levels}
@@
 
+\begin{DL}
+NOT EXPRESSIBLE IN DL!!!
+\end{DL}
+
 \section{String Operations}
@@
 
+\begin{DL}
+NOT EXPRESSIBLE IN DL!!!
+\end{DL}
+
 \section{Context-Specific Valid Classes}
@@
 
+\begin{DL}
+I'm not sure about the meaning of this constraint, but for me this seams like e.g. the range of a role... but if this is the case, take into account the consequences of reasoning with OWA...
+\end{DL}
+
+\an{not sure!}
+
 \section{Context-Specific Valid Properties}
@@
 \subsection{Simple Example}
+
+\begin{DL}
+I'm not sure about the meaning of this constraint, but for me this seams like e.g. the domain of a role... but if this is the case, take into account the consequences of reasoning with OWA...
+\end{DL}
+
+\an{not sure!}
 
@@
 
+\begin{DL}
+NOT EXPRESSIBLE IN DL!!!
+\end{DL}
+
 \section{Mathematical Operations}
@@
 
+\begin{DL}
+NOT EXPRESSIBLE IN DL!!!
+\end{DL}
+
 \section{Language Tag Matching}
@@
 \end{itemize}
+
+\begin{DL}
+NOT EXPRESSIBLE IN DL!!!
+\end{DL}
 
@@
 
+\begin{DL}
+NOT EXPRESSIBLE IN DL!!!
+\end{DL}
+
 \section{Whitespace Handling}
@@
 
+\begin{DL}
+NOT EXPRESSIBLE IN DL!!!
+\end{DL}
+
 \section{HTML Handling}
@@
 
+\begin{DL}
+NOT EXPRESSIBLE IN DL!!!
+\end{DL}
+
 \section{Required Properties}
@@
 
+\begin{DL}
+$Person \sqsubseteq \exists hasAncestor.Person$
+\end{DL}
+
 \section{Optional Properties}
@@
 
+\begin{DL}
+$\exists hasAncestor.Person \sqsubseteq Person$ \\
+(same as the definition of domains)
+\end{DL}
+
 \section{Repeatable Properties}
@@
 \subsection{Simple Example}
+
+\begin{DL}
+Not sure about the meaning of this constraint...
+\end{DL}
+
+\an{not sure!}
 
@@
 
+\begin{DL}
+- condition: universal quantification on object and data properties\\
+\ \ \ \ same as above!?\\
+- condition: existential quantification on object and data properties\\
+\ \ \ \ same as above!?\\
+- condition: if specific properties are present, then specific other properties also have to be present
+\ \ \ \ same as super properties, so if a property (role or attribute) is used, all super properties are also present
+\end{DL}
+
 \section{Recommended Properties}
@@
 \end{ex}
+
+\begin{DL}
+$JediMentor \sqsubseteq \neg(\exists studentOf.JediMentor)$
+\end{DL}
 
@@
 
+\begin{DL}
+NOT EXPRESSIBLE IN DL!!!
+\end{DL}
+
 \section{Recursive Queries}
@@
 
+\begin{DL}
+NOT EXPRESSIBLE IN DL!!!
+\end{DL}
+
 \section{Value is Valid for Datatype}
@@
 
+\begin{DL} 
+$\rho(\textsf{hasBirthday}) \sqsubseteq \PVerb{xsd:dateTime}$\\
+(equal to the definition of an attribute (data property) range)
+\end{DL}
+
 \begin{itemize}
@@
 \begin{DL}
-julia = john \\
+$\{julia\} = \{john\} $\\
 \end{DL}
@@
 \begin{DL}
-julia $\ne$ john
+$\{julia\} \ne \{john\} $\\
+(this is by default because of the UNA)
 \end{DL}
@@
 :hasBrother $\sqsubseteq$ :hasMaleSibling $\sqcap$ :hasMaleSibling $\sqsubseteq$ :hasBrother \\
+equivalent to: $hasBrother = hasMaleSibling$
 \end{DL}
@@
 \begin{DL}
-
-\end{DL}
-
-\tb{ToDo: DL}
+$hasSon(\textbf{Peter},\textbf{Meg})$\\
+(negation of such an assertion is not necessary / meaningless!)
+\end{DL}
 
@@
 \begin{DL}
-:hasAge ( :Meg , "17"^^xsd:integer ) \\
+$hasAge ( \textbf{Meg} ,\textbf{ "17"}\hat{\ } \hat{\ } xsd:integer ) $\\
 \end{DL}
@@
 \begin{DL}
-owl:Thing $\sqsubseteq$ $\leq$ 1 :hasFather
+$(\textsf{funct } \textsf{hasFather})$
 \end{DL}
@@
 \begin{DL}
-
-\end{DL}
-
-\tb{ToDo: DL}
+$(\textsf{funct } \textsf{hasFather}\sp{\overline{\ }})$
+\end{DL}
 
@@
 \begin{DL}
-
-\end{DL}
-
-\tb{ToDo: DL}
+Not sure about the meaning of this constraint...\\
+May be it is:\\
+$Shortcut \sqsubseteq \exists fatherOf.\{\textbf{Stewie}\}$
+\end{DL}
+
+\an{not sure!}
 
@@
 \end{ex}
+
+\begin{DL}
+Not sure about if this constraint is expressible in DL, I think not!
+\end{DL}
+
+\an{not sure!}
 
@@
 \begin{DL}
-
-\end{DL}
-
-\tb{ToDo: DL}
+Not sure if this is expressible in DL, may be we should have a detailed look to \textit{DL-Lite}$_{\mathcal{A},id}$ \\
+(see \url{http://www.dis.uniroma1.it/~lembo/papers/calv-etal-RW-2009.pdf})
+\end{DL}
+
+\an{not sure!}
 
@@
 \end{itemize}
+
+\begin{DL}
+Not sure if this is expressible in DL, I think not!
+\end{DL}
+
+\an{not sure!}
 
@@
 
+\begin{DL}
+Not sure if the meaning of this constraint, probably it is the same as for cardinality restrictions?
+\end{DL}
+
+\an{not sure!}
+
 \end{document}

### 2014-12-18 paper/RDF validation requirements/RDF validation requirements.tex
examples clean up

@@
     owl:onProperty foaf:name ;
-    owl:allValuesFrom xsd:string ] .
+    owl:someValuesFrom xsd:string ] .
 :CC2 rdfs:subClassOf [
@@
     owl:onProperty foaf:givenName ;
-    owl:allValuesFrom xsd:string ] .
+    owl:someValuesFrom xsd:string ] .
 \end{ex}
@@
 \begin{DL}
-A $\equiv$ $\forall$ foaf:name . xsd:string \\
-B $\equiv$ $\forall$ foaf:givenName . xsd:string \\ 
+A $\equiv$ $\exists$ foaf:name . xsd:string \\
+B $\equiv$ $\exists$ foaf:givenName . xsd:string \\ 
 Human $\sqsubseteq$ ($\neg$ A $\sqcap$ B) $\sqcup$ (A $\sqcap$ $\neg$ B) \\
@@
     owl:onProperty :attackingBySword ;
-    owl:allValuesFrom xsd:boolean ] .
+    owl:someValuesFrom xsd:boolean ] .
 :CC2 rdfs:subClassOf [
@@
     owl:onProperty :attackingByForce ;
-    owl:allValuesFrom xsd:boolean ] .
+    owl:someValuesFrom xsd:boolean ] .
 \end{ex}
@@
 \begin{DL}
-A $\equiv$ $\forall$ :attackingBySword . xsd:boolean \\
-B $\equiv$ $\forall$ :attackingByForce . xsd:boolean \\ 
+A $\equiv$ $\exists$ :attackingBySword . xsd:boolean \\
+B $\equiv$ $\exists$ :attackingByForce . xsd:boolean \\ 
 :FeelingForce $\sqsubseteq$ ($\neg$ A $\sqcap$ B) $\sqcup$ (A $\sqcap$ $\neg$ B) \\
@@
 
-\begin{ex}
-# examples
-# --------
-1. dbo:deathDate before ‘<’ dbo:birthDate
-2. dbo:releaseDate after ‘>’ dbo:latestReleaseDate
-3. dbo:demolitionDate before ‘<’ dbo:buildingStartDate
-\end{ex}
+\begin{itemize}
+	\item dbo:deathDate before ‘<’ dbo:birthDate
+  \item dbo:releaseDate after ‘>’ dbo:latestReleaseDate
+  \item dbo:demolitionDate before ‘<’ dbo:buildingStartDate
+\end{itemize}
 
@@
 \end{gcotable}
+
+\subsection{Simple Example}
+
+duplicate strings are not allowed:
+
+\begin{ex}
+dc:subject "foo"@en
+dc:subject "foo"@fr
+dc:subject "bar"@fr
+dc:subject "foo"
+\end{ex}
+
+There are no identical strings.
 

### 2014-12-19 paper/RDF validation requirements/RDF validation requirements.tex
Aggregations
requirements evaluation complete

@@
   \vspace{0.3cm}
-  \begin{tabular}{l|c|c|c|c|c}
+  \begin{tabular}{l|c|c|c|c|c|c}
   \hline
-  \textbf{constraint} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
+  \textbf{constraint} & \textbf{DSP} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
   \hline
@@
 
+\section{Aggregations}
+
+\begin{itemize}
+  \item Some constraints require aggregating multiple values, especially via COUNT, MIN and MAX. 
+\end{itemize}
+
+\begin{DL}
+Not expressible in DL
+\end{DL}
+
+\section{Evaluation}
+
+\begin{evaluation}
+*Subsumption & \ding{55} & $\checkmark$ & $\checkmark$ & $\sim$ & $\checkmark$ & $\checkmark$ \\
+*Class Equivalence & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
+*Sub Properties & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
+*Property Domain & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
+*Property Range & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
+*Inverse Object Properties & \ding{55} & $\checkmark$ & $\checkmark$ & $\sim$ & \ding{55} & $\checkmark$ \\
+*Symmetric Object Properties & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
+*Asymmetric Object Properties & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
+*Reflexive Object Properties & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
+*Irreflexive Object Properties & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
+Disjoint Properties & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
+Disjoint Classes & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
+Context-Sp. Property Groups & \ding{55} & $\sim$ & $\sim$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+Context-Sp. Inclusive OR of P. & \ding{55} & $\sim$ & $\sim$ & \ding{55} & \ding{55} & $\checkmark$ \\
+Context-Sp. Inclusive OR of P. Groups & \ding{55} & $\sim$ & $\sim$ & \ding{55} & \ding{55} & $\checkmark$ \\
+Recursive Queries & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\sim$ \\
+Individual Inequality & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
+*Equivalent Properties & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
+Property Assertions & \ding{55} & $\checkmark$ & $\sim$ & \ding{55} & \ding{55} & $\checkmark$ \\
+Data Property Facets & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
+Literal Pattern Matching & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
+Negative Literal Pattern Matching & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
+*Object Property Paths & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+*Intersection & \ding{55} & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+*Disjunction & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+*Negation & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+*Existential Quantification & \ding{55} & $\checkmark$ & \ding{55} & $\sim$ & $\sim$ & $\checkmark$ \\
+*Universal Quantification & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+*Minimum Unqualified Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} & $\sim$ & $\checkmark$ & $\checkmark$ \\
+*Minimum Qualified Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} & $\sim$ & $\checkmark$ & $\checkmark$ \\
+*Maximum Unqualified Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} & $\sim$ & $\checkmark$ & $\checkmark$ \\
+*Maximum Qualified Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} & $\sim$ & $\checkmark$ & $\checkmark$ \\
+*Exact Unqualified Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} & $\sim$ & $\checkmark$ & $\checkmark$ \\
+*Exact Qualified Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} & $\sim$ & $\checkmark$ & $\checkmark$ \\
+*Transitive Object Properties & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+Context-Sp. Exclusive OR of P. & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ \\
+Context-Sp. Exclusive OR of P. Groups & \ding{55} & $\sim$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+Allowed Values & $\checkmark$ & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$& $\checkmark$ \\
+Not Allowed Values & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ \\
+Literal Ranges & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+Negative Literal Ranges & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+Required Properties & $\checkmark$ & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+Optional Properties & $\checkmark$ & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+Repeatable Properties & $\checkmark$ & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+Negative Property Constraints & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ \\
+*Individual Equality & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+*Functional Properties & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+*Inverse-Functional Properties & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+*Value Restrictions & $\checkmark$ & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+*Self Restrictions & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+Primary Key Properties & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+*Class-Specific Property Range & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+*Class-Sp. Reflexive Object P. & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+Membership in Controlled Vocabularies & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+IRI Pattern Matching & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ \\
+Literal Value Comparison & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ \\
+Define Order & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+Validation Levels & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+String Operations & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+\end{evaluation}
+
+\begin{evaluation}
+Context-Specific Valid Classes & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+Context-Specific Valid Properties & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+Default Values & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ & \ding{55} & $\checkmark$ \\
+Mathematical Operations & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+Language Tag Matching & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+Language Tag Cardinality & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+Whitespace Handling & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+HTML Handling & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+Conditional Properties & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+Recommended Properties & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+Handle RDF Collections & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+Value is Valid for Datatype & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+*Exploiting Class/Property Specialization Ontology Axioms & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+*Cardinality Shortcuts & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+Aggregations & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+\end{evaluation}
+
 \end{document}

### 2014-12-20 paper/RDF validation requirements/RDF validation requirements.tex
classification

@@
 \section{Evaluation}
+
+We evaluated to which extend the most promising five DSCLs fulfill each requirement.
+Tilde means that this constraint may be fulfilled by that particular constraint language - either by limitations, workarounds, or extensions.
+We also evaluated if a specific constraint is fulfilled by OWL 2 QL or if the more expressive OWL 2 DL is needed. 
+Inferencing may be performed prior to validating constraints. This is marked with an asterisk.
 

### 2014-12-23 paper/RDF validation requirements/RDF validation requirements.tex
DL mappings

@@
   \vspace{0.3cm}
+	\begin{center}
   \begin{tabular}{l|l|l|l|l|l|l}
   \hline
-  \textbf{c. type} & \textbf{context concept} & \textbf{left p. list} & \textbf{right p. list} & \textbf{concepts} & \textbf{c. element} & \textbf{c. value} \\
+  \textbf{c. type} & \textbf{context class} & \textbf{left r. list} & \textbf{right r. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+  \hline
+
+}{
+  \hline
+  \end{tabular}
+	\end{center}
+}
+
+\newenvironment{DL}{
+  %\scriptsize
+  %\sffamily
+  %\vspace{0.3cm}
+	\begin{center}
+  \begin{tabular}{r l}
+
+}{
+  \end{tabular}
+	\end{center}
+}
+
+\newenvironment{evaluation}{
+  \scriptsize
+  \sffamily
+  \vspace{0.3cm}
+	\begin{center}
+  \begin{tabular}{l|c|c|c|c|c|c}
+  \hline
+  \textbf{constraint} & \textbf{DSP} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
   \hline
@@
   \linebreak
+	\end{center}
 }
 
-\newenvironment{DL}{
+\newenvironment{evaluation-overall}{
   \scriptsize
@@
   \vspace{0.3cm}
-  \begin{tabular}{l}
-	\textbf{DL:} \\
-
-}{
-  \end{tabular}
-  \linebreak
-}
-
-\newenvironment{evaluation}{
-  \scriptsize
-  \sffamily
-  \vspace{0.3cm}
+	\begin{center}
   \begin{tabular}{l|c|c|c|c|c|c}
@@
   \linebreak
+	\end{center}
 }
@@
 %
-\title{XXXXX}
+\title{RDF Validation Requirements - Evaluation and Logical Underpinning}
+\subtitle{}
 %
@@
 %
-\author{XXXXX\inst{1} \and XXXXX\inst{2}}
+\author{Thomas Bosch\inst{1} \and Andreas Nolle\inst{2} \and Erman Acar\inst{3}}
 %
@@
 %%%% list of authors for the TOC (use if author list has to be modified)
-\institute{XXXXX\\
-\email{XXXXX},\\ 
+\institute{GESIS – Leibniz Institute for the Social Sciences, Germany\\
+\email{thomas.bosch@gesis.org},\\ 
 \and
-XXXXX \\
-\email{XXXXX} 
+Albstadt-Sigmaringen University, Germany \\
+\email{nolle@hs-albsig.de}
+\and
+University of Mannheim, Germany \\
+\email{\{christian,erman,kai\}@informatik.uni-mannheim.de} 
 }
@@
 
-\tb{I think we should provide mappings to DL directly in the requirements chapters and not just in 1 table at the end of the paper}
-
 \section{Subsumption}
 
-requirement:
-
-\begin{itemize}
-	\item R-100-SUBSUMPTION
-\end{itemize}
-
-\subsection{Description}
+\ms{Subsumption} corresponds to the requirement \ms{R-100-SUBSUMPTION}.
 
@@
 
-\subsection{Simple Example}
-
-\begin{DL}
-Mother $\sqsubseteq$ Parent 
-\end{DL}
+\begin{evaluation}
+*Subsumption & \ding{55} & $\checkmark$ & $\checkmark$ & $\sim$ & $\checkmark$ & $\checkmark$ \\
+\end{evaluation}
+
+\subsection{Simple Example}
 
@@
 
+\begin{DL}
+Mother $\sqsubseteq$ Parent \\
+\end{DL}
+
 \begin{gcotable}
@@
 
-\begin{itemize}
-	\item Jedis feel the force 
-\end{itemize}
+Jedis feel the force.
+
+\begin{DL}
+Jedi $\sqsubseteq$ FeelingForce
+\end{DL}
 
@@
 # ----
-:Jedi rdfs:subClassOf :FeelingForce .
+Jedi rdfs:subClassOf FeelingForce .
 \end{ex}
@@
 # ----
-:FeelingForce {
-    :feelingForce (true) }
-:Jedi {
-    & :FeelingForce ,
-    :attitute ('good') }
+FeelingForce {
+    feelingForce (true) }
+Jedi {
+    & FeelingForce ,
+    attitute ('good') }
 \end{ex}
@@
 # ----
-:Yoda 
-    :feelingForce true ;
-    :attitute 'good' .
-\end{ex}
-
-\begin{DL}
-:Jedi $\sqsubseteq$ :FeelingForce
-\end{DL}
+Yoda 
+    feelingForce true ;
+    attitute 'good' .
+\end{ex}
+
+\begin{gcotable}
+class & Jedi & - & - & FeelingForce & $\sqsubseteq$ \\
+\end{gcotable}
 
@@
 
-\subsection{Description}
-
-\begin{itemize}
-	\item Concept equivalence asserts that two concepts have the same instances \cite{Kroetzsch2012}
-  \item While synonyms are an obvious example of equivalent concepts, in practice one more
-often uses concept equivalence to give a name to complex expression  \cite{Kroetzsch2012}
-\item Concept equivalence is indeed subsumption  from left and right. ($A \sqsubseteq B$ and $B \sqsubseteq A$ implies $A \equiv B$ )
-
-\end{itemize}
+Concept equivalence asserts that two concepts have the same instances \cite{Kroetzsch2012}.
+While synonyms are an obvious example of equivalent concepts, in practice one more
+often uses concept equivalence to give a name to complex expression  \cite{Kroetzsch2012}.
+Concept equivalence is indeed subsumption from left and right ($A \sqsubseteq B$ and $B \sqsubseteq A$ implies $A \equiv B$ ).
 
@@
 \end{DL}
-
-\begin{gcotable}
-class & Person & - & - & Human & $\equiv$ \\
-class & Human & - & - & Person & $\equiv$ \\
-\end{gcotable}
-
-maybe better:
-\er{It is not better since we should stick to what we use as syntax.}
 
@@
 \end{gcotable}
+
 \section{Sub Object Properties}
@@
 
-\subsection{Description}
-
 \begin{itemize}
@@
 
-\begin{itemize}
-	\item states that parentOf is a subrole of ancestorOf , i.e., every pair of individuals related by parentOf is also related by ancestorOf
-\end{itemize}
-
-\begin{gcotable}
-property & parentOf & ancestorOf & - & - & $\sqsubseteq$ \\
-\end{gcotable}
-
-better:
+States that \ms{parentOf} is a sub-role of \ms{ancestorOf} , i.e., every pair of individuals related by \ms{parentOf} is also related by \ms{ancestorOf}.
 
@@
 
-\subsection{Simple Example}
+\subsection{Complex Example}
 \begin{DL}
@@
 \end{itemize}
-
-\subsection{Description}
 
@@
 
-old mapping:
-
-\begin{gcotable}
-property & uncleOf & brotherOf, parentOf & - & $\top$ & $\sqsubseteq$ \\
-\end{gcotable}
-
 \section{Disjoint Properties}
@@
 	\item R-9-DISJOINT-PROPERTIES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item 
 \end{itemize}
@@
 \begin{gcotable}
+property & $\top$ & parentOf & $\neg$childOf & $\top$ & $\sqsubseteq$ \\
+\end{gcotable}
+
+syntactic sugar:
+
+\begin{gcotable}
 property & $\top$ & parentOf & childOf & $\top$ & $\ne$ \\
@@
 
-\begin{itemize}
-	\item complex concept of all individuals which are of the concept Female and of the concept Parent
-\end{itemize}
+Complex concept of all individuals which are of the concept Female and of the concept Parent.
 
@@
 \end{gcotable}
+
+\subsection{Simple Example}
 
@@
 
-\subsection{Description}
-
-\begin{itemize}
-	\item union / inclusive OR
+\begin{itemize}
+	\item synonyms: union / inclusive OR
+	\item disjunction of classes, data ranges
 \end{itemize}
@@
 \begin{gcotable}
-class & complex concept & - & - & Father, Mother, Child & $\sqcup$ \\
+class & Father $\sqcup$ Mother $\sqcup$ Child & - & - & Father, Mother, Child & $\sqcup$ \\
 \end{gcotable}
@@
 
-\subsection{Description}
-
-\begin{itemize}
-	\item complement
+\begin{itemize}
+	\item synonym: complement
 \end{itemize}
@@
 
-\begin{itemize}
-	\item set of all individuals that are not married
-\end{itemize}
+set of all individuals that are not married.
 
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-7-DISJOINT-CLASSES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item 
-\end{itemize}
+requirement \ms{R-7-DISJOINT-CLASSES}
 
@@
 
+\subsection{Simple Example}
+
+\begin{DL}
+Hologram $\sqcap$ Human $\sqsubseteq$ $\perp$\\
+Alternative:\\
+$Hologram \sqsubseteq \neg Human$
+\end{DL}
+
+\begin{gcotable}
+class & Hologram $\sqcap$ Human & - & - & Hologram, Human & $\sqcap$  \\
+class & $\top$ & - & - & Hologram $\sqcap$ Human, $\perp$ & $\sqsubseteq$ \\
+\end{gcotable}
+
+syntactic sugar:
+
+\begin{gcotable}
+class & Hologram & - & - & Human & $\ne$ \\
+class & Human & - & - & Hologram & $\ne$ \\
+\end{gcotable}
+
 \section{Existential Quantification on Properties}
 
-requirements:
-
-\begin{itemize}
-	\item R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item DL termonology: existential restriction
-	\item An existential class expression ObjectSomeValuesFrom( OPE CE ) consists of an object property expression OPE and a class expression CE, and it contains all those individuals that are connected by OPE to an individual that is an instance of CE.
+\ms{Existential Quantification on Properties} conforms to the requirement \ms{R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}
+In DL terminology the \ms{existential quantification} is alco called \ms{existential restriction}.
+An existential class expression ObjectSomeValuesFrom( OPE CE ) consists of an object property expression OPE and a class expression CE, and it contains all those individuals that are connected by OPE to an individual that is an instance of CE.
 Such a class expression can be seen as a syntactic shortcut for the class expression ObjectMinCardinality( 1 OPE CE ).
-	\item An existential class expression DataSomeValuesFrom( DPE1 ...
+An existential class expression DataSomeValuesFrom( DPE1 ...
 DPEn DR ) consists of n data property expressions DPEi, 1 $\leq$ i $\leq$ n, and a data range DR whose arity MUST be n.
@@
 A class expression of the form DataSomeValuesFrom( DPE DR ) can be seen as a syntactic shortcut for the class expression DataMinCardinality( 1 DPE DR ).
-\end{itemize}
 
@@
 
+\subsection{Simple Example}
+
+\begin{DL}
+ParentOfSon $\equiv$ $\exists$ parentOf . Male
+\end{DL}
+
+\begin{gcotable}
+property & ParentOfSon & parentOf & - & Male & $\exists$ \\
+\end{gcotable}
+
 \section{Universal Quantification on Properties}
 
-requirements:
-
-\begin{itemize}
-	\item R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES
-\end{itemize}
-
-\subsection{Description}
-
-\begin{itemize}
-	\item DL terminology: value restriction
-\end{itemize}
-
-$(\forall R.C)^\mathcal{I}= \{a \in \Delta^\mathcal{I}\mid (a,b) \in R^\mathcal{I} \rightarrow b \in C^\mathcal{I} \}$ where $\cdot^\mathcal{I}$ is an interpretation function, $\Delta^I$ is the domain, $a,b \in \Delta^\mathcal{I}$ are individuals $C$ is a concept, $R$ is a role.
+\ms{Universal Quantification on Properties} corresponds to the requirement \ms{R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}, which is called \ms{value restriction} in DL terminology.
+
+\begin{center}
+\begin{DL} 
+$(\forall R.C)^\mathcal{I}= \{a \in \Delta^\mathcal{I}\mid (a,b) \in R^\mathcal{I} \rightarrow b \in C^\mathcal{I} \}$ where $\cdot^\mathcal{I}$ is an interpretation function, \\
+$\Delta^I$ is the domain, $a,b \in \Delta^\mathcal{I}$ are individuals $C$ is a concept, $R$ is a role. 
+\end{DL}
+\end{center}
 
@@
 
+syntactic sugar:
+
 \begin{gcotable}
@@
 \end{itemize}
+
+\begin{DL}
+Man $\sqsubseteq$ $\forall$ sonOf . Parent \\
+\end{DL}
 
@@
 
-\subsection{Description}
-
 examples:
@@
 
-\subsection{Description}
-
 \subsection{Simple Example}
@@
 \section{Equivalent Properties}
-
-\subsection{Description}
 
@@
 
-\begin{evaluation}
+\begin{evaluation-overall}
 *Subsumption & \ding{55} & $\checkmark$ & $\checkmark$ & $\sim$ & $\checkmark$ & $\checkmark$ \\
@@
 String Operations & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
-\end{evaluation}
-
-\begin{evaluation}
+\end{evaluation-overall}
+
+\begin{evaluation-overall}
 Context-Specific Valid Classes & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
@@
 Aggregations & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
-\end{evaluation}
+\end{evaluation-overall}
 

### 2014-12-23 paper/paper 2/paper 2.tex
DL mappings

@@
 \newenvironment{DL}{
-  \scriptsize
-  \sffamily
-  \vspace{0.3cm}
-  \begin{tabular}{l}
-	\textbf{DL:} \\
+  %\scriptsize
+  %\sffamily
+  %\vspace{0.3cm}
+	\begin{center}
+  \begin{tabular}{r l}
 
@@
   \end{tabular}
-  \linebreak
+	\end{center}
 }
@@
 \section{Introduction}
+
+\section{Notes}
+
+\begin{itemize}
+	\item requirements / constraints mapped to DL
+	\item requirements / constraints which cannot be mapped to DL
+	\item syntactic sugar for some constraints
+	\item complex constraints encompass complex constraints and simple constraints
+	\item DL statements of complex constraints are created out of DL statements of composed constraints 
+	\item define terminology for RDF constraints
+\end{itemize}
 
@@
 
+\section{Complex Constraints}
+
+\subsection{Disjoint Classes}
+
+\begin{DL}
+Hologram $\sqcap$ Human $\sqsubseteq$ $\perp$\\
+Alternative:\\
+$Hologram \sqsubseteq \neg Human$
+\end{DL}
+
+\subsection{Minimum Qualified Cardinality Restrictions on Properties}
+
+\begin{DL}
+$FederationCaptain \sqsubseteq Federation \sqcap \geq1 commandsVessel . Vessel $
+\end{DL}
+
 \bibliography{../../literature/literature}{}

### 2014-12-23 paper/RDF validation requirements/RDF validation requirements.tex
DL mappings

@@
 \end{ex}
-\er{Note that this example includes also has at-most restriction.}\\
 
@@
 \end{DL}
+
+\textcolor{red}{corrections (to verify):}
+
+\begin{DL}
+$Jedi \sqsubseteq \exists attitude.\{good\} $\\
+$JediStudent \sqsubseteq Jedi \sqcap \geq1 studentOf.\top \sqcap \leq1 studentOf.\top$ \\
+$JediMasters \sqsubseteq Jedi \sqcap \geq1 studentOf^{-}.\top \sqcap \leq2 studentOf^{-}.\top $\\
+$SuperJediMaster \sqsubseteq Jedi \sqcap  \geq3 studentOf^{-}.\top $
+\end{DL}
+
+\subsection{Simple Example}
+
+\begin{DL}
+$Captain \sqsubseteq \geq1 commandsVessel.\top $
+\end{DL}
+
+\begin{gcotable}
+property & Captain & commandsVessel & - & $\top$ & $\geq$ & 1 \\
+\end{gcotable}
 
@@
 
-\tb{ToDO: check DL}
-\er{foaf: or xsd:string is no DL syntax. So you can delete 18.2 if you are fine.}
 \begin{gcotable}
@@
 
-%\tb{ToDO: check DL}
-
 \begin{gcotable}
@@
 class & Father2Daughters & - & - & Man, $\geq$ 2 hasChild.Woman & $\sqcap$ & - \\
+\end{gcotable}
+
+\subsection{Simple Example}
+
+\begin{DL}
+$Captain \sqsubseteq \geq1 commandsVessel . Vessel $
+\end{DL}
+
+\begin{gcotable}
+property & Captain & commandsVessel & - & Vessel & $\geq$ & 1 \\
+\end{gcotable}
+
+\subsection{Complex Example}
+
+\begin{DL}
+$FederationCaptain \sqsubseteq Federation \sqcap \geq1 commandsVessel . Vessel $
+\end{DL}
+
+\begin{gcotable}
+property & $\geq$1 commandsVessel . Vessel & commandsVessel & - & Vessel & $\geq$ & 1 \\
+class & FederationCaptain & - & - & Federation, $\geq$1 commandsVessel . Vessel & $\sqcap$ & - \\
 \end{gcotable}
@@
 \end{itemize}
-\er{Notice that this example includes minimum restriction.}
 \begin{ex}
@@
 
-\tb{ToDO: OWL 2 DL}
-\er{why OWL 2 DL?}
 \begin{ex}

### 2014-12-24 paper/RDF validation requirements/RDF validation requirements.tex
corrected DL of cardinality restrictions
added mapping tables

@@
 }
+
+%\newenvironment{gcotable}{
+  %\scriptsize
+  %\sffamily
+  %\vspace{0.3cm}
+	%\begin{center}
+  %\begin{tabular}{l|l|l|l|l|l|l}
+  %\hline
+  %\textbf{c. type} & \textbf{context c. $\vert$ p.} & \textbf{left r. list} & \textbf{right r. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+  %\hline
+%
+%}{
+  %\hline
+  %\end{tabular}
+	%\end{center}
+%}
 
@@
 
-syntactic sugar:
+syntactic sugar (preferred):
 
@@
 
-Assume that  mentorOf and studentOf are inverse properties.\\
-\begin{DL}
-$Jedi \sqsubseteq \exists attitude.\{good\} $\\
-$JediStudent \sqsubseteq Jedi \sqcap 1\geq studentOf.\top \sqcap 1\leq studentOf.\top$ \\
-$JediMasters \sqsubseteq Jedi \sqcap 1\leq studentOf^{-}.\top \sqcap 2\geq studentOf^{-}.\top $\\
-$SuperJediMaster \sqsubseteq Jedi \sqcap  3\leq studentOf^{-}.\top $
-\end{DL}
-
-\textcolor{red}{corrections (to verify):}
-
 \begin{DL}
@@
 $JediStudent \sqsubseteq Jedi \sqcap \geq1 studentOf.\top \sqcap \leq1 studentOf.\top$ \\
-$JediMasters \sqsubseteq Jedi \sqcap \geq1 studentOf^{-}.\top \sqcap \leq2 studentOf^{-}.\top $\\
-$SuperJediMaster \sqsubseteq Jedi \sqcap  \geq3 studentOf^{-}.\top $
+$JediMasters \sqsubseteq Jedi \sqcap \geq1 mentorOf.\top \sqcap \leq2 mentorOf.\top $\\
+$SuperJediMaster \sqsubseteq Jedi \sqcap  \geq3 mentorOf.\top $
 \end{DL}
@@
 $Jedi \sqsubseteq \exists attitude.\{good\} $\\
-$JediStudent \sqsubseteq Jedi \sqcap 1\geq studentOf.Jedi \sqcap 1\leq studentOf.Jedi$ \\
-$JediMasters \sqsubseteq Jedi \sqcap 1\leq studentOf^{-}.Jedi\sqcap 2\geq studentOf^{-}.Jedi $\\
-$SuperJediMaster \sqsubseteq Jedi \sqcap  3\leq studentOf^{-}.Jedi $
-\end{DL}
+$JediStudent \sqsubseteq Jedi \sqcap \geq1 studentOf.Jedi \sqcap \leq1 studentOf.Jedi$ \\
+$JediMasters \sqsubseteq Jedi \sqcap \geq1 mentorOf.Jedi \sqcap \leq2 mentorOf.Jedi $\\
+$SuperJediMaster \sqsubseteq Jedi \sqcap  \geq3 mentorOf.Jedi $
+\end{DL}
+
 \subsection{Complex Example}
@@
 
-%\tb{ToDO: add DL}
-\noindent Taking mentorOf and studentOf as inverse properties. \\
 \begin{DL}
 $Jedi \sqsubseteq \exists attitude.\{good\} $\\
-$JediStudent \sqsubseteq Jedi \sqcap 1\geq studentOf.\top \sqcap 1\leq studentOf.\top$ \\
-$JediMasters \sqsubseteq Jedi \sqcap 1\leq studentOf^{-}.\top \sqcap 2\geq studentOf^{-}.\top $\\
-$SuperJediMaster \sqsubseteq Jedi \sqcap  3\leq studentOf^{-}.\top $
+$JediStudent \sqsubseteq Jedi \sqcap \geq1 studentOf.\top \sqcap \leq1 studentOf.\top$ \\
+$JediMasters \sqsubseteq Jedi \sqcap \geq1 mentorOf.\top \sqcap \leq2 mentorOf.\top $\\
+$SuperJediMaster \sqsubseteq Jedi \sqcap  \geq3 mentorOf.\top $
 \end{DL}
@@
 $Jedi \sqsubseteq \exists attitude.\{good\} $\\
-$JediStudent \sqsubseteq Jedi \sqcap 1\geq studentOf.Jedi \sqcap 1\leq studentOf.Jedi$ \\
-$JediMasters \sqsubseteq Jedi \sqcap 1\leq studentOf^{-}.Jedi\sqcap 2\geq studentOf^{-}.Jedi $\\
-$SuperJediMaster \sqsubseteq Jedi \sqcap  3\leq studentOf^{-}.Jedi $
+$JediStudent \sqsubseteq Jedi \sqcap \geq1 studentOf.Jedi \sqcap \leq1 studentOf.Jedi$ \\
+$JediMasters \sqsubseteq Jedi \sqcap \geq1 mentorOf.Jedi \sqcap \leq2 mentorOf.Jedi $\\
+$SuperJediMaster \sqsubseteq Jedi \sqcap  \geq3 mentorOf.Jedi $
 \end{DL}
@@
 
-%\tb{ToDO: add DL}
-\begin{DL}
-$Jedi \sqsubseteq \exists attitude.\{good\} $\\
-$JediStudent \sqsubseteq Jedi \sqcap 1\geq studentOf.\top \sqcap 1\leq studentOf.\top$ \\
-\end{DL}
+\begin{DL}
+$JediStudent \sqsubseteq Jedi \sqcap \geq1 studentOf.\top \sqcap \leq1 studentOf.\top$ \\
+\end{DL}
+
 \section{Exact Qualified Cardinality Restrictions on Properties}
@@
 $Jedi \sqsubseteq \exists attitude.\{good\} $\\
-$JediStudent \sqsubseteq Jedi \sqcap 1\geq studentOf.Jedi \sqcap 1\leq studentOf.Jedi$ \\
+$JediStudent \sqsubseteq Jedi \sqcap \geq1 studentOf.Jedi \sqcap \leq1 studentOf.Jedi$ \\
 \end{DL}
@@
 \begin{DL}
-parentOf $\equiv$ $childOf^{-}$ \\
-not sure if this should be rather\\
-$parentOf \sqsubseteq childOf^{-}$ \\
-\end{DL}
-
-\an{not sure!}
-
-\begin{gcotable}
-property & parentOf & childOf & - & $\top$ & $inverse role (^{-})$ \\
-\end{gcotable}
-
-consistent with ontology:
-
-\begin{gcotable}
-property & $\top$ & parentOf & childOf & $\top$ & $inverse role (^{-})$ \\
+$parentOf \equiv childOf^{-}$ \\
+\end{DL}
+
+outdated:
+
+\begin{gcotable}
+property & $\top$ & parentOf & childOf$^{-}$ & - & $\equiv$ \\
+\end{gcotable}
+
+\subsection{Simple Example}
+
+\begin{DL}
+captainOf $\equiv$ hasCaptain$^{-}$ \\
+\end{DL}
+
+\begin{gcotable}
+property & $\top$ & captainOf & hasCaptain & - & inverse \\
+\end{gcotable}
+
+alternative:
+
+\begin{gcotable}
+property & hasCaptain$^{-}$ & hasCaptain & - & - & inverse \\
+property & captainOf & hasCaptain$^{-}$ & - & - & $\equiv$ \\
+\end{gcotable}
+
+alternative:
+
+\begin{gcotable}
+property & captainOf & hasCaptain & - & - & inverse \\
 \end{gcotable}
@@
 
+\begin{gcotable}
+property & $\top$ & ancestorOf, ancestorOf & ancestorOf & - & $\sqsubseteq$ \\
+\end{gcotable}
+
 syntactic sugar:
@@
 \begin{gcotable}
-property & ancesterOf & ancestorOf, ancestorOf & - & $\top$ & transitive role \\
-\end{gcotable}
-
-syntactic sugar (ontology conform):
-
-\begin{gcotable}
-property & $\top$ & ancestorOf, ancestorOf & ancestorOf & $\top$ & transitive role \\
-\end{gcotable}
-
-without syntactic sugar (ontology conform):
-
-\begin{gcotable}
-property & $\top$ & ancestorOf, ancestorOf & ancestorOf & $\top$ & $\sqsubseteq$ \\
+property & $\top$ & ancestorOf & - & - & transitive \\
 \end{gcotable}
@@
 \begin{DL}
-$marriedTo \sqsubseteq marriedTo^{-}$ \\
-\end{DL}
-
-\begin{gcotable}
-property & marriedTo & marriedTo & - & $\top$ & $inverse role (^{-})$ \\
-\end{gcotable}
-
-ontology conform:
-
-\begin{gcotable}
-property & $\top$ & marriedTo & marriedTo & $\top$ & $inverse role (^{-})$ \\
+$marriedTo \equiv marriedTo^{-}$ \\
+\end{DL}
+
+\begin{gcotable}
+property & $\top$ & marriedTo & marriedTo & - & inverse \\
 \end{gcotable}
@@
 \begin{gcotable}
-property & $\top$ & marriedTo & - & $\top$ & symmetric role \\
+property & $\top$ & marriedTo & - & - & symmetric \\
 \end{gcotable}
@@
 $parentOf \sqsubseteq \neg parentOf^{-}$ or\\
-$parentOf \sqcap parentOf^{-} \sqsubseteq \bot$
-\end{DL}
-
-\begin{gcotable}
-property & $parentOf^{-}$ & parentOf & - & $\top$ & inverse role $(^{-})$ \\
-property & parentOf & parentOf, $parentOf^{-}$ & - & $\top$ & disjoint role ($\ne$) \\
-\end{gcotable}
-
-ontology conform:
-
-\begin{gcotable}
-property & $\top$ & parentOf & - & $\top$ & inverse role $(^{-})$ \\
-property & $\top$ & parentOf, $parentOf^{-}$ & - & $\top$ & disjoint role ($\ne$) \\
+$parentOf \sqcap parentOf^{-} \sqsubseteq \bot$ or \\
+disjoint(parentOf, parentOf$^{-}$)
+\end{DL}
+
+\begin{gcotable}
+property & $\top$ & $parentOf^{-}$ & parentOf & - & inverse \\
+property & $\top$ & parentOf & $parentOf^{-}$ & - & $\ne$ \\
 \end{gcotable}
@@
 \begin{gcotable}
-property & $\top$ & parentOf & - & $\top$ & asymmetric role \\
+property & $\top$ & parentOf & - & - & asymmetric \\
 \end{gcotable}
@@
 
-\section{Class-Specific Reflexive Object Properties / Local Reflexivity}
+\section{Class-Specific Reflexive Object Properties}
 
@@
 \begin{DL}
-$\exists$ talksTo .Self. 
+TalkingToThemselves $\sqsubseteq$ $\exists$ talksTo .Self. 
 \end{DL}
@@
 \begin{gcotable}
-property & $\exists$ talksTo .Self.  & talksTo & - & Self & $\exists$ \\
+property & TalkingToThemselves & talksTo & - & Self & $\exists$ \\
 \end{gcotable}
@@
 \begin{gcotable}
-property & $\exists$ talksTo .Self. & talksTo & - & - & reflexive role \\
-\end{gcotable}
-
-\section{Reflexive Object Properties / Global Reflexivity}
+property & $\exists$ talksTo .Self & talksTo & - & - & reflexive \\
+\end{gcotable}
+
+\section{Reflexive Object Properties}
 
@@
 
+\begin{gcotable}
+property & $\exists$ knows . Self & knows & - & Self & $\exists$ \\
+class & $\top$ & - & - & $\top$, $\exists$ knows . Self & \sqsubseteq \\
+\end{gcotable}
+
 syntactic sugar:
@@
 \begin{gcotable}
-property & $\top$ & knows & - & $\top$ & reflexive role \\
-\end{gcotable}
-
-\begin{gcotable}
-property & $\top$ & knows & - & Self & $\exists$ \\
+property & $\top$ & knows & - & - & reflexive \\
 \end{gcotable}
@@
 
+\begin{gcotable}
+property & $\exists$ knows . Self & knows & - & Self & $\exists$ \\
+class & $\neg$ $\exists$ knows . Self & - & - & $\exists$ knows . Self & $\neg$ \\
+class & $\top$ & - & - & $\top$, $\neg$ $\exists$ knows . Self & \sqsubseteq \\
+\end{gcotable}
+
 syntactic sugar:
@@
 \begin{gcotable}
-property & $\top$ & marriedTo & - & $\top$ & irreflexive role \\
-\end{gcotable}
-
-\begin{gcotable}
-property & $\exists$ marriedTo . Self & marriedTo & - & Self & $\exists$ \\
-class & $\top$ & - & - & $\exists$ marriedTo . Self & $\neg$ \\
+property & $\top$ & marriedTo & - & - & irreflexive \\
 \end{gcotable}
@@
 Data Property Facets & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
-Literal Pattern Matching & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
-Negative Literal Pattern Matching & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
+Literal Pattern Matching & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+Negative Literal Pattern Matching & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
 *Object Property Paths & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\

### 2014-12-24 paper/paper 2/paper 2.tex
corrected DL of cardinality restrictions
added mapping tables

@@
 
+\section{Syntactic Sugar}
+
+In Section 1.3 we introduced three forms of RBox axioms: role inclusions, role equiv-
+alences and role disjointness. OWL provides a variety of others, namely role transi-
+tivity, symmetry, asymmetry, reflexivity and irreflexivity. These are sometimes consid-
+ered as basic axiom types in DLs as well, using some suggestive notation such as
+Trans( ancestorOf ) to express that the role ancestorOf is transitive. However, such axioms
+are just syntactic sugar; all role characteristics can be expressed using the features
+of DLs that we have already introduced.
+
+\begin{itemize}
+  \item domain and range
+	\item (ir)reflexive object properties
+	\item Exact Qualified Cardinality Restrictions on Properties
+\end{itemize}
+
 \bibliography{../../literature/literature}{}

### 2014-12-25 paper/paper 1.tex

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}

% allows for temporary adjustment of side margins
\usepackage{chngpage}

% just makes the table prettier (see \toprule, \bottomrule, etc. commands below)
\usepackage{booktabs}

\usepackage[utf8]{inputenc}

% URL handling
\usepackage{url}
\urlstyle{same}

% Todos
%\usepackage[colorinlistoftodos]{todonotes}
%\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
%\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}

%\usepackage{makeidx}  % allows for indexgeneration

%\usepackage{amsmath}
\usepackage{amsmath, amssymb}
\usepackage{mathabx}

% monospace within text
\newcommand{\ms}[1]{\texttt{#1}}

% examples
\usepackage{fancyvrb}
\DefineVerbatimEnvironment{ex}{Verbatim}{numbers=left,numbersep=2mm,frame=single,fontsize=\scriptsize}

\usepackage{xspace}
% Einfache und doppelte Anfuehrungszeichen
\newcommand{\qs}{``} 
\newcommand{\qe}{''\xspace} 
\newcommand{\sqs}{`} 
\newcommand{\sqe}{'\xspace}

% checkmark
\usepackage{tikz}
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}

% Xs
\usepackage{pifont}

% Tabellenabstände kleiner
\setlength{\intextsep}{10pt} % Vertical space above & below [h] floats
\setlength{\textfloatsep}{10pt} % Vertical space below (above) [t] ([b]) floats
% \setlength{\abovecaptionskip}{0pt}
% \setlength{\belowcaptionskip}{0pt}

\usepackage{tabularx}
\newcommand{\hr}{\hline\noalign{\smallskip}} % für die horizontalen linien in tabellen

% Todos
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}
\newcommand{\er}[1]{\todo[size=\small, color=red!40]{\textbf{Erman:} #1}}
\newcommand{\an}[1]{\todo[size=\small, color=red!40]{\textbf{Andy:} #1}}

\newenvironment{table-1cols}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
  \begin{tabular}{l}
  \hline
  \textbf{Requirements} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{table-2cols}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
  \begin{tabular}{l|l}
  \hline
  \textbf{Requirements} & \textbf{Covering DSCLs} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{complexity}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
  \begin{tabular}{l|l}
  \hline
  \textbf{Validation Type} & \textbf{Complexity} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{DL}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
  \begin{tabular}{l}

}{
  \end{tabular}
  \linebreak
}

\newenvironment{evaluation}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
  \begin{tabular}{l|c|c|c|c|c|c}
  \hline
  \textbf{constraint} & \textbf{DSP} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{user-fiendliness}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
  \begin{tabular}{l|c|c|c|c|c}
  \hline
  \textbf{criterion} & \textbf{DSP} & \textbf{OWL2} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\setcounter{secnumdepth}{5}

\begin{document}

%
%
\title{RDF Validation}
\subtitle{Effects on Complexity with and without OWL 2 Reasoning}
%
\titlerunning{XXXXX}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Thomas Bosch\inst{1} \and Erman Acar\inst{2} \and XXXXX\inst{3} \and Kai Eckert\inst{2}}
%
\authorrunning{XXXXX} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\institute{GESIS – Leibniz Institute for the Social Sciences, Germany\\
\email{thomas.bosch@gesis.org},\\ 
\and
University of Mannheim, Germany \\
\email{\{erman,kai\}@informatik.uni-mannheim.de} 
\and
XXXXX \\
\email{XXXXX}
}

\maketitle              % typeset the title of the contribution

\begin{abstract}

\keywords{RDF Validation, RDF Constraints, OWL 2 QL, OWL 2 DL, Reasoning, RDF Validation Requirements, Linked Data, Semantic Web}
\end{abstract}
%

\section{Introduction}

For many RDF applications, the formulation of constraints and the automatic validation of data according to these constraints is a much sought-after feature. 
In 2013, the W3C invited experts from industry, government, and academia to the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
where first use cases have been presented and discussed. 
Two WGs, that follow up on this workshop and address RDF constraint formulation and validation, are established in 2014: 
the W3C RDF Data Shapes WG\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles WG\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.

Bosch and Eckert \cite{BoschEckert2014} initiated a database on RDF validation requirements, which is intended to be a way to collect case studies, use cases and especially requirements regarding RDF validation collaboratively and in a structured form \cite{DroegeBoschCharlesClayphanMatienzoRuehlePohlAlonenSvenssonCoyle2014}.
The comprehensive, continuously maintained and extended database, which is openly available at \url{http://purl.org/net/rdf-validation}, is used to evaluate and to compare several existing solutions for RDF constraint formulation and validation. 
The requirements are classified to provide a high-level view on different solutions and to facilitate a better understanding of the problem domain \cite{BoschEckert2014}.

There are multiple domain-specific constraint languages (DSCLs) having different syntaxes and semantics which can be used to express RDF constraints like at-least restrictions.
The most promising DSCLs are 
the SPARQL Inferencing Notation (SPIN)\footnote{\url{http://spinrdf.org/}}, 
the Web Ontology Language (OWL 2)\footnote{\url{http://www.w3.org/TR/owl2-syntax/}}, 
Shape Expressions (ShEx)\footnote{\url{http://www.w3.org/Submission/shex-primer/}}, 
Resource Shapes (ReSh)\footnote{\url{http://www.w3.org/Submission/shapes/}}, 
and Description Set Profiles (DSP)\footnote{\url{http://dublincore.org/documents/2008/03/31/dc-dsp/}}.
However, there is no single standard DSCL to express any constraint for each purpose.
The choice depends on the individual use case.

\section{Motivation}

\tb{1 simple example in motivation section}

OWL is based on a knowledge representation formalism with different complexity, but is created as a language which can be seen as a constraint language.
Constraint validation does not appear to be part of the services provided by OWL.  
This has lead to claims that OWL cannot be used for constraint validation. 
There are long and controversial discussions\footnote{\url{http://lists.w3.org/Archives/Public/public-data-shapes-wg/}, \url{https://www.jiscmail.ac.uk/cgi-bin/webadmin?A0=dc-architecture}} in the W3C and DCMI WGs if OWL should be used for RDF validation.
There are lots of pros and cons using OWL in order to formulate and to validate RDF constraints.
OWL is an instantiation of a high-level and very expressive DSCL with a compact human-readable syntax.
OWL is a language that many people already know.
In practice, many people use RDFS and OWL constructs to tell other people and applications about how valid instances should be created.
Normally, RDF documents follow the structure of RDFS/OWL ontologies. 
Thus, part of those declarations will be defined anyway and can therefore be reused for validating these RDF documents.
The standard semantics of OWL is:

\begin{itemize}
	\item Open World Assumptions (OWA): a statement cannot be inferred to be false on the basis of failures to prove it.
  \item non-Unique Name Assumptions (nUNA): two different names may refer to the same object.
\end{itemize}

This semantics is suitable for the distributed knowledge representation scenarios on the Semantic Web, 
where usually the knowledge about the domain comes from distributed
sources and a complete knowledge about the domain cannot be assumed, 
but makes it difficult to use OWL for RDF validation.

Although, most people don’t care about open world semantics, 
ambiguousness is one of the main reasons why OWL has not been adopted as standard DSCL for RDF validation in the past. 
When OWL would be used assuming both OWA (for reasoning) and CWA (for constraint validation),
it would be somewhat confusing to have two completely different semantics for OWL.
On the other hand, OWL constraints could be interpreted either with the OWA to support open
world reasoning, and exactly the same piece can also be interpreted in closed world
applications as a constraint.

You can't easily use OWL to even do cardinality checking. 
For example, suppose you assert that \ms{hasFather} is a functional property, and you have the triples \ms{Luke hasFather Anakin} and \ms{Luke hasFather Darth}.
An OWL reasoner will invoke the nUNA to infer that \ms{Anakin owl:sameAs Darth}.

Therefore, the semantics for RDF validation is Closed World Assumption (CWA) and the Unique Name Assumption.

As for an area where OWA is problematic, one need look no further than
FRBRer ontology is clearly designed using OWL constraints
(which I prefer to call "axioms" to avoid confusion) in a closed world
way. The definitions are quite strict, with all classes disjoint each
other, such that, using reasoning in the OWL, any FRBRer data will be
inconsistent with data not using that exact set of axioms. 
http://svn.aksw.org/papers/2014/WWW\_Databugger/public.pdf

%\tb{Andy, we want to use only star wars examples in our paper. We need 1 example showing the differences between OWA / CWA and /UNA / nUNA. You may reuse star wars examples which are already in the paper.}

Let us address the CWA vs. OWA via an example. Consider the knowledge base  $\mathcal{K} = \{\ms{Person} \sqsubseteq \exists \ms{hasAncestor.Person}, \ms{Person(Luke)}\}$. In case of OWA, we know that $\ms{Luke}$ has $\ms{Ancestor}$, but we do not know all of them. Notice that $\mathcal{K}$ is consistent. In CWA however, the constraint needs to be satisfied only by named individuals which yields in return some validation errors.\\
Consider the following case in CWA. 
\begin{eqnarray*}
\mathcal{K} &=  & \{\ms{Person} \sqsubseteq \exists \ms{hasAncestor.Person}, \\
 &&(\ms{funct }  \ms{hasAncestor}),\\  && \ms{Person(Luke)},\\ && \ms{hasAncestor(Luke, Anakin)},\\  && \ms{hasAncestor(Anakin, Shmi)}\}
\end{eqnarray*}

\noindent Now, observe that there is a clash because of the functional role $\ms{hasAncestor}$ and the UNA. However, in OWA there is no UNA by default, therefore the reasoning will conclude that  $\ms{Anakin}$ to be the same individual with $\ms{Shmi (Anakin} \equiv \ms{Shmi}$). Notice that this is not a problem if we add UNA to the OWA, like in the \textit{DL-Lite} family.
Another point is that, if we perform RDF validation without reasoning, we will get a further clash: $\ms{Anakin}$ is not defined to be a $\ms{Person}$. On the other hand, if we do the validation after the reasoning, then there is no clash since $\ms{Person(Anakin)}$ is inferred.

%\begin{itemize}
	%\item explain why specific OWL 2 constructs could be used for RDF validation 
	%\item explain why specific OWL 2 constructs should not be used for RDF validation
%\end{itemize}

Reasoning makes sense before actually validating constraints.
Reasoning, which is the core service provided by OWL,
and constraint validation are very closely related. 
\an{maybe we can use also the term 'User-defined Consistency' described in 'see below' as a further 'hook' to establish our approach?}
\url{http://www.aifb.kit.edu/images/d/d2/2005_925_Haase_Consistent_Evol_1.pdf}
\tb{Andy, can you describe this in the paper?}
\an{a more formal example would be nice! ;)}
Reasoning is the process of determining what follows from what has been
stated.  Reasoning ranges from simple (students are people, John is a
student, therefore John is a person) to the very complex. Reasoning can
also recognize impossibilities (students are people, John is a student, John
is not a person, therefore there is a contradiction). 
It both should be possible: (1) constraint validation with reasoning and (2) constraint validation without reasoning.

Reasoning may be a pre validation step to infer triples resolving constraint violations.
According to the existential restriction \ms{Jedi $\sqsubseteq$ $\exists$ hasJediWaepon . JediWeapon} every Jedi has at least one Jedi weapon.
Luke is a Jedi (\ms{Jedi(Luke)}) having a blue laser sword (\ms{hasLaserSword(Luke, BlueLaserSword)}.
As it is not defined that laser swords are Jedi weapons and as Luke is a Jedi, the existential restriction causes a constraint violation. 
This constraint violation is not raised when we define that laser swords are Jedi weapons (\ms{hasLaserSword $\sqsubseteq$ hasJediWaepon} ) 
and \ms{hasLaserSword} is a sub-property of \ms{hasJediWeapon} (\ms{LaserSword $\sqsubseteq$ JediWeapon}).

It makes also sense to perform reasoning to infer triples for which constraints are validated.
The existential restriction \ms{Jedi $\sqsubseteq$ $\exists$ hasLaserSword . LaserSword} forces Jedis to have at least one laser sword.
The existential restriction is not checked for the triple \ms{YediMaster(Yoda)}, as \ms{Yoda} is a \ms{JediMaster} and not a \ms{Jedi} as well.
If, however, our knowledge base contains the axiom \ms{JediMaster $\sqsubseteq$ Jedi}, the triple \ms{Jedi(Yoda)} is inferred and the existential restrictions is validated for the individual \ms{Yoda}, raising a constraint violation if a triple such as \ms{hasLaserSword(Yoda, GreenLaserSword)} is not included in the knowledge base.

\textcolor{red}{example}

%With regard to typing, W3C is assuming (AFAIK) that all types will be
%explicit in the instance data - for the purposes of validation. There is
%nothing, however, to prevent an application from running reasoning prior
%to validation to add inferred triples to the data being validated. But
%the general feeling right now is that validation acts on instance data
%without requiring that the validator apply reasoning in order to do so.

%Nehmen wir nun an, dass dein Framework welches entsprechende SPARQL Queries generiert diese auf einem SPARQL Endpoint evaluiert der zu der vorliegenden Ontologie bzw. des darin verwendeten OWL 2 Profils das entsprechende Entailment Regime realisiert, wären die zurückgegebenen Resultsets vollständig. Wie das Entailment Regime im Endpoint realisiert ist, also durch Query Rewriting oder durch Vervollständigung der ABox, ist dabei irrelevant.
%
%Wie allerdings bspw. in 
%\url{https://www.uni-ulm.de/fileadmin/website_uni_ulm/iui.inst.090/Lehre/WS_2011-2012/SemWebGrundlagen/LectureNotes.pdf}
%auf Seite 51 veranschaulicht, ist die Komplexität des Reasoning abhängig von der zugrunde gelegten Sprache und kann daher nur in bestimmten Fällen effizient durchgeführt werden. Wie in unserem letzten Paper beschrieben zielt unter anderem die Definition von DL-Lite gerade darauf ab Reasoning Aufgaben und Query Answering effizient zu ermöglichen und ist Grundlage des OWL 2 QL Profils. Nun ist allgemein bekannt, dass die logische Konsistenz für diese Art von Sprachen effizient geprüft werden kann. 
%
%Allerding wäre wie bspw. in 
%\url{http://www.aifb.kit.edu/images/d/d2/2005_925_Haase_Consistent_Evol_1.pdf} beschrieben auch eine sogenannte 'User-defined Consistency' denkbar. Genau an dieser Stelle könnten wir ansetzen.

%\textbf{Ideas}
%
%\begin{itemize}
	%\item RDF validation using OWL 2 QL reasoning by SPARQL query expansion
	%\item if using OWL 2 DL as constraint language or using constraints equivalent to OWL 2 QL you can use reasoning 
	%\item reasoning can also be executed using SPARQL query expansion.
	%\item reasoning not executing using reasoner
%\end{itemize}

%\begin{itemize}
	%\item complete with reasoning | OW
	%\item complete without reasoning | CW
	%\item there is no query rewriting mechanism for OWL 2, just for OWL 2 QL
%\end{itemize}

\textcolor{red}{high-level description of expressivity}

\textcolor{red}{
\begin{itemize}
  \item why is expressivity important for the paper?
	\item expressivity of query languages like SPARQL?
	\item expressivity of OWL 2 QL and OWL 2 DL?
	\item how is expressivity and complexity related?
\end{itemize}
}

\textcolor{red}{high-level description of complexity}

We group each RDF requirement into three complexity classes.
As case studies are linked to use cases and use cases to requirements, it is known how complex the task is to fulfill use cases and case studies.
For specific use cases, it can also be determined which of the associated requirements lead to a higher complexity class.
Imaginable is a system in which use cases can be selected which should be met for particular applications.
Then, the system determines the complexity class, can point to requirements and constraints causing a higher complexity class,
and can give hints how to rewrite the constraint in order to stay in a lower complexity class.

Query languages such as SPARQL or Datalog are more expressive than OWL 2 QL and DL,
but the complexity of query languages is less than the complexity of OWL 2 QL and DL, because of the reasoning calculations.
For many constraints reasoning can be done, but when reasoning is not needed for validation this constraint can be reformulated as a query by a query language
leading to a lower complexity class. 
\textcolor{red}{example}
Such a complexity aware RDF validator could help people writing constraints that can be efficiently computed.
For DL, there is a web application allowing you to select the needed DL constructs in order to determine the complexity of DL reasoning\footnote{\url{http://www.cs.man.ac.uk/~ezolin/dl/}}.

As we evaluated to which extend each constraint can be expressed by the most promising five DSCLs, 
we can determine the complexity of these DSCLs as well.

If we want to use OWL 2 for RDF validation, we have to ensure that as many requirements for formulating RDF constraints are fulfilled
and that the computational complexity to formulate these constraints is satisfying.

\textcolor{red}{research questions and contributions needs to be adapted}

Therefore, we answer five \textbf{research questions}:
\begin{enumerate}
	\item Which constraints are expressible by DL and which are only expressible by a query language (e.g Datalog or SPARQL)?
	\item For which requirements formulating constraints the expressivity of \textit{DL-Lite}$_\mathcal{A}$ (respectively OWL 2 QL) is sufficient
	and for which requirements additional DSCLs are needed?
	\item For which constraints a priori reasoning makes sense and how does reasoning affect their validation?  
	\item What are the effects on complexity to express these constraints with and without OWL 2 QL and OWL 2 DL reasoning?
	\item What are the effects on complexity of constraints not expressible by DL but by a query language?
\end{enumerate}

The three \textbf{main contributions} of this paper are:
\begin{enumerate}
  \item We investigate the effects on complexity expressing each constraint
	\item We show that OWL 2 QL together with additional DSCLs completely satisfy all RDF validation requirements.
	\item We evaluated to which extend the five possible standard DSCLs fulfill each requirement.
\end{enumerate}

\textcolor{red}{paper organization}

\section{Expressivity and Complexity of OWL and SPARQL}

\textcolor{red}{
\begin{itemize}
	\item OWL as a high-level language with reasoning capabilities which can be used for RDF validation
  \item OWL 2 QL (what is now the beginning of 4.1)
  \item OWL 2 DL (now beginning of 4.2)
  \item SPARQL as a low-level general-purpose implementation language for RDf validation
\end{itemize}
}

\subsection{OWL 2 QL Reasoning}

OWL 2 profiles (or fragments in logic literature) are restricted (sublanguage) versions of OWL 2 that offer different trade-offs regarding expressivity  vs. efficiency in reasoning. There are three main  profiles of OWL 2, which are OWL 2 QL, OWL 2 RL and OWL 2 EL namely, each designed to  be useful for different purposes and application scenarios. The choice of which profile to use is purpose-specific on what to express and to perform the reasoning about. We refer reader to \cite{owl2profiles2008} for a comprehensive treatment of those profiles.

OWL 2 QL is an OWL 2 profile which focuses on reasoning on query answering with very large size of instance data. The acronym QL stands for query language as query answering in this profile can be done by rewriting queries into a standard relational query language (also known as First-Order Rewritability). Also, conjunctive query answering can be done by using conventional relational database systems. Aiming at efficiency on working with large size data, the expressive power of the profile is quite limited as expected. As a result of this, reasoning in OWL 2 QL is highly efficient so that sound and complete conjunctive query answering can be performed in \textsc{LogSpace} in the size of the data assertions as well as  the ontology consistency and class expression subsumption can be performed in polynomial time.

OWL 2 QL is based on the \textit{DL-Lite} family of description logics, a tractable family of fragments of first-order logic \cite{Artale2009,Calvanese2007}. 
However, an important difference between the \textit{DL-Lite} family and OWL is the
unique name assumption (UNA). UNA is common in data management, therefore it is adopted in the \textit{DL-Lite} family whereas not adopted in OWL. In OWL, one uses constructs \textbf{sameAs} or \textbf{differentFrom} explicitly to state that two individuals, say  $a$ and $b$, are the \emph{same} or {different} respectively. For that reason in OWL 2 QL, any construct e.g., number restrictions or functionality constraints which can interfere with UNA and also which can cause higher complexity without the UNA, has been avoided. \an{but in \textit{DL-Lite}$_\mathcal{A}$ functionality is expressible, as far as I know there is also an extension to \textit{DL-Lite}$_\mathcal{A}$ that allows number restrictions...}

Among the members of \textit{DL-Lite} family, \textit{DL-Lite}$_\mathcal{R}$ is the one that OWL 2 QL is based on. The reason is to avoid any problematic issue which might appear in the explicit axiomatization of UNA, since  \textit{DL-Lite}$_\mathcal{R}$ in general does not require the UNA, because making this assumption has no semantic affect on a \textit{DL-Lite}$_\mathcal{R}$ ontology.

\subsection{OWL 2 DL Reasoning}

%\tb{ToDO for Erman and Andy: can you please write a short paragraph about OWL 2 DL reasoning?}

The Semantic Web ontology language OWL 2 DL\footnote{See \url{http://www.w3.org/TR/owl2-direct-semantics/}.} was standardized by
the World Wide Web Consortium (W3C) in 2009 (and updated in 2012) as a
description logic-like formalism.  OWL 2 DL has high expressivity, yet maintains  decidability for main reasoning tasks e.g., ontology satisability, 
entailment checking. The drawback of its expressive power results as a lack of computational efficiency in performance. In general, reasoning in OWL 2 DL is in \textsc{N2exptime} \cite{owl2profiles2008}.

As a result of its expressive power, OWL 2 DL allows a large variety of sophisticated modeling capabilities for many application domains.  On the other hand, to maintain the decidability, OWL 2 DL has a numerous ways of syntactic restrictions. One example is that OWL 2 DL allows  expressing transitive properties as well as asymmetric properties, yet a property to be both transitive and asymmetric (just as ancestor relation) is not allowed. In the sequel, from RDF validation perspective, we will give some examples of constraints that remain at the outside of its scope.

\section{Classification of RDF Constraints and DSCLs according to Expressivity and Complexity}

\textcolor{red}{
\begin{itemize}
	\item section 3 is needed as basis for this chapter to which extend do most promising five constraint languages cover RDF validation requirements?
	\item --> then, constraint languages can also be assigned to these classes (e.g. 6 out of 30 class A requirements are covered by constraint language A --> constraint language A is also assigned to that class)
\end{itemize}
}

According to our evaluation of requirements to formulate RDF constraints, we identified three main ways of validating constraints.

\begin{enumerate}
	\item validation by query answering without reasoning
	\item validation by query answering with OWL 2 QL reasoning
	\item validation by query answering with OWL 2 DL reasoning
\end{enumerate}

The next table gives an overview of the computational complexity for RDF validation when it is performed -with and without reasoning.

\begin{complexity}
validation by query answering without reasoning & \textsc{Pspace}-Complete \\
validation by query answering with OWL 2 QL reasoning & \textsc{Ptime} \\
validation by query answering with OWL 2 DL reasoning & \textsc{N2exptime} \\
\end{complexity}

What is considered by rdf validation w/o reasoning, corresponds to performing SPARQL queries.  It is known that performing SPARQL queries is in \textsc{Pspace}-Complete \cite{Perez2009}. Since OWL 2 profiles are based on \textit{DL-Lite} family and query answering in OWL 2 QL is in \textsc{LogSpace} (or rather in AC$^0$ ) \cite{Calvanese2007}, so is the constraint validation by queries with  reasoning. Furthermore, TBox reasoning in OWL 2 QL is in \textsc{Ptime} \cite{Calvanese2007}, hence complete query rewriting as well as combined complexity (reasoning and than querying) is in \textsc{Ptime} \cite{Artale2009,Calvanese2007}.  With the more expressive profile OWL 2 DL, reasoning is in \textsc{N2exptime} \cite{owl2profiles2008} which is a class of considerably higher complexity.

\textcolor{red}{at least 1 example for each class}

\tb{ToDo: venn diagram: expressivity classes missing / associate DSCLs with classes}

Figure~\ref{fig:VennDiagram}.  
\begin{figure}
	\centering
		\includegraphics[width=0.95\textwidth]{complexiity_and_expressivity.png}
	\caption{Complexity and Expressivity Classes}
	\label{fig:VennDiagram}
\end{figure}

We evaluated to which extend the five possible standard constraint languages fulfill each requirement to formulate RDF constraints.
Tilde means that this constraint may be fulfilled by that particular constraint language - either by limitations, workarounds, or extensions.
We also evaluated if a specific constraint is fulfilled by OWL 2 QL or if the more expressive OWL 2 DL is needed. 
Inferencing may be performed prior to validating constraints. This is marked with an asterisk.

We divide these constraints into three classes:
\begin{itemize}
	\item constraints expressible by OWL 2 QL
	\item constraints not expressible by OWL 2 QL but by OWL 2 DL
	\item constraints only expressible by other DSCLs
\end{itemize}

Bosch et al.\footnote{\url{https://github.com/boschthomas/rdf-validation-research/paper}} explained each requirement and associated constraint in detail and give at least one example for each of them\cite{BoschNolleAcarEckert2015}.
In order to logically underpin each requirement, we added mappings to DL.

\tb{How should we publish this? ordering of author not determined so far}

\textbf{Constraints Expressible by OWL 2 QL.}

\begin{evaluation}
*Subsumption & \ding{55} & $\checkmark$ & $\checkmark$ & $\sim$ & $\checkmark$ & $\checkmark$ \\
*Class Equivalence & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
*Sub Properties & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
*Property Domain & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
*Property Range & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
*Inverse Object Properties & \ding{55} & $\checkmark$ & $\checkmark$ & $\sim$ & \ding{55} & $\checkmark$ \\
*Symmetric Object Properties & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
*Asymmetric Object Properties & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
*Reflexive Object Properties & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
*Irreflexive Object Properties & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
Disjoint Properties & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
Disjoint Classes & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
Context-Sp. Property Groups & \ding{55} & $\sim$ & $\sim$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
Context-Sp. Inclusive OR of P. & \ding{55} & $\sim$ & $\sim$ & & \ding{55} & $\checkmark$ \\
Context-Sp. Inclusive OR of P. Groups & \ding{55} & $\sim$ & $\sim$ & & \ding{55} & $\checkmark$ \\
Recursive Queries & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\sim$ \\
Individual Inequality & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
*Equivalent Properties & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
Property Assertions & \ding{55} & $\checkmark$ & $\sim$ & \ding{55} & \ding{55} & $\checkmark$ \\
Data Property Facets & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
Literal Pattern Matching & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
Negative Literal Pattern Matching & \ding{55} & $\checkmark$ & $\checkmark$ & & & $\checkmark$ \\
\end{evaluation}

\textbf{Constraints not Expressible by OWL 2 QL but by OWL 2 DL.}

\begin{evaluation}
*Object Property Paths & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
*Intersection & \ding{55} & $\checkmark$ & \ding{55} & & & $\checkmark$ \\
*Disjunction & \ding{55} & $\checkmark$ & \ding{55} & & & $\checkmark$ \\
*Negation & \ding{55} & $\checkmark$ & \ding{55} & & & $\checkmark$ \\
*Existential Quantification & \ding{55} & $\checkmark$ & \ding{55} & $\sim$ & $\sim$ & $\checkmark$ \\
*Universal Quantification & \ding{55} & $\checkmark$ & \ding{55} & & & $\checkmark$ \\
*Minimum Unqualified Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} & $\sim$ & $\checkmark$ & $\checkmark$ \\
*Minimum Qualified Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} & $\sim$ & $\checkmark$ & $\checkmark$ \\
*Maximum Unqualified Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} & $\sim$ & $\checkmark$ & $\checkmark$ \\
*Maximum Qualified Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} & $\sim$ & $\checkmark$ & $\checkmark$ \\
*Exact Unqualified Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} & $\sim$ & $\checkmark$ & $\checkmark$ \\
*Exact Qualified Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} & $\sim$ & $\checkmark$ & $\checkmark$ \\
*Transitive Object Properties & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Context-Sp. Exclusive OR of P. & \ding{55} & $\checkmark$ & \ding{55} & & $\checkmark$ & $\checkmark$ \\
Context-Sp. Exclusive OR of P. Groups & \ding{55} & $\sim$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
Allowed Values & $\checkmark$ & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$& $\checkmark$ \\
Not Allowed Values & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ \\
Literal Ranges & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Negative Literal Ranges & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Required Properties & $\checkmark$ & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
Optional Properties & $\checkmark$ & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
Repeatable Properties & $\checkmark$ & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
Negative Property Constraints & \ding{55} & $\checkmark$ & \ding{55} & & $\checkmark$ & $\checkmark$ \\
*Individual Equality & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
*Functional Properties & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
*Inverse-Functional Properties & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
*Value Restrictions & & $\checkmark$ & \ding{55} & & & $\checkmark$ \\
*Self Restrictions & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Primary Key Properties & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
\end{evaluation}

\textbf{Constraints Only Expressible by Other DSCLs.}

\begin{evaluation}
*Class-Specific Property Range & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
*Class-Sp. Reflexive Object P. & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Membership in Controlled Vocabularies & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
IRI Pattern Matching & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ \\
Literal Value Comparison & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ \\
Define Order & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Validation Levels & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
String Operations & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Context-Specific Valid Classes & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Context-Specific Valid Properties & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Default Values & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ & \ding{55} & $\checkmark$ \\
Mathematical Operations & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Language Tag Matching & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Language Tag Cardinality & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Whitespace Handling & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
HTML Handling & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Conditional Properties & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Recommended Properties & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Handle RDF Collections & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
Value is Valid for Datatype & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
*Exploiting Class/Property Specialization Ontology Axioms & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
*Cardinality Shortcuts & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
\end{evaluation}

\subsection{Classification Dimension Complexity}

According to our evaluation of requirements to formulate RDF constraints, we identified three main ways of validating constraints.

\begin{enumerate}
	\item validation by query answering without reasoning
	\item validation by query answering with OWL 2 QL reasoning
	\item validation by query answering with OWL 2 DL reasoning
\end{enumerate}

The next table gives an overview of the computational complexity for RDF validation when it is performed -with and without reasoning.

\begin{complexity}
validation by query answering without reasoning & \textsc{Pspace}-Complete \\
validation by query answering with OWL 2 QL reasoning & \textsc{Ptime} \\
validation by query answering with OWL 2 DL reasoning & \textsc{N2exptime} \\
\end{complexity}

What is considered by rdf validation w/o reasoning, corresponds to performing SPARQL queries.  It is known that performing SPARQL queries is in \textsc{Pspace}-Complete \cite{Perez2009}. Since OWL 2 profiles are based on \textit{DL-Lite} family and query answering in OWL 2 QL is in \textsc{LogSpace} (or rather in AC$^0$ ) \cite{Calvanese2007}, so is the constraint validation by queries with  reasoning. Furthermore, TBox reasoning in OWL 2 QL is in \textsc{Ptime} \cite{Calvanese2007}, hence complete query rewriting as well as combined complexity (reasoning and than querying) is in \textsc{Ptime} \cite{Artale2009,Calvanese2007}.  With the more expressive profile OWL 2 DL, reasoning is in \textsc{N2exptime} \cite{owl2profiles2008} which is a class of considerably higher complexity.

\subsection{Classification Dimension User-Friendliness}

We cannot formally measure the user-friendliness of DSCLs as in the case of expressivity and complexity.

Rather subjective criteria to determine if a DSCL is user-friendliness are:

\begin{itemize}
	\item constraint formulation level: low-level vs. high-level
	\item intuitiveness: not intuitive $<$ less intuitive $<$ intuitive
	\item conciseness: not concise $<$ less concise $<$ concise
\end{itemize}

\begin{user-fiendliness}
level & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & \ding{55} \\
intuitiveness & $\sim$ & $\sim$ & $\sim$ & $\checkmark$ & \ding{55} \\
conciseness & $\sim$ & $\checkmark$ & $\sim$ & $\checkmark$ & \ding{55} \\
\end{user-fiendliness}

\textcolor{red}{examples for each criterion}

\subsection{Overall Classification}

\tb{ToDo: venn diagram: expressivity classes missing / associate DSCLs with classes}

Figure~\ref{fig:VennDiagram}.  
\begin{figure}
	\centering
		\includegraphics[width=0.60\textwidth]{venn-diagram.jpg}
	\caption{Complexity and Expressivity Classes}
	\label{fig:VennDiagram}
\end{figure}

\section{RDF validation requirements}

\textcolor{red}{
\begin{itemize}
	\item organization according to developed classification system regarding expressivity and complexity
	\item examples for rdf constraints for each class
\end{itemize}
}

\subsection{RDF Validation Requirements and Reasoning}

\tb{ToDO Thomas: RDF Validation Requirements and Inferencing}

\subsubsection{OWL 2 QL Reasoning}

\textbf{Subsumption}\footnote{corresponds to R-100-SUBSUMPTION}\textbf{.}
Subsumption relationships of both classes and properties are part of basic reasoning.

\begin{DL}
Jedi $\sqsubseteq$ FeelingForce \\
JediMaster $\sqsubseteq$ Jedi \\
\end{DL}

All Jedi masters are Jedis feeling the force.
These sub-class relationships can also be expressed by OWL 2 QL:

\begin{ex}
Jedi rdfs:subClassOf FeelingForce . 
JediMaster rdfs:subClassOf Jedi . 
\end{ex}

Valid data must contain the three class assignments \ms{JediMaster(Yoda)}, \ms{Jedi(Yoda)}, and \ms{FeelingForce(Yoda)}.
These class assignments can be either explicitly stated or implicitly inferred when reasoning is performed before actually validating the data.

When only the triple \ms{Yoda a JediMaster} is given and reasoning is not executed, then a constraint violation is raised.
After reasoning, however, the triples \ms{Yoda a Jedi , FeelingForce} are inferred resulting in valid data.

\textbf{Property Domain}\footnote{corresponds to R-25-PROPERTY-DOMAIN}\textbf{.}
The property domain constraint

\begin{DL}
$\exists$ studentOf . $\top$ $\sqsubseteq$ JediStudent \\
\end{DL}

restricts that individuals having studentOf relationships must be Jedi students.
This property domain constraint can also be expressed by OWL 2 QL:

\begin{ex}
studentOf rdfs:domain JediStudent .
\end{ex}

Without reasoning, the data \ms{Anakin studentOf Obi-Wan} is invalid and causes a constraint violation, as it is not explicitly stated that \ms{Anakin} is assigned to the class \ms{Jedi}. 
When inferencing is performed before validating, the class assignment \ms{Anakin a Jedi} is inferred which prevents the constraint violation to be raised.

\subsubsection{OWL 2 DL Reasoning}

\textbf{Existential Quantification}\footnote{corresponds to R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}\textbf{.}

\begin{DL}
Jedi $\sqsubseteq$ $\exists$ hasLaserSword . LaserSword
\end{DL}

This existential quantification contains all those individuals that are connected by \ms{hasLaserSword} to an individual that is an instance of the class \ms{LaserSword}.
In OWL 2 DL, this existential quantification can also be expressed:

\begin{ex}
[ a owl:Restriction ;
  owl:onProperty hasLaserSword ;
  owl:someValuesFrom LaserSword ;
  rdfs:subClassOf Jedi ] .
\end{ex}

When our data contains the triple \ms{Luke hasLaserSword BlueLaserSword} and we perform reasoning, we can infer that \ms{Luke} is a \ms{Jedi}, as he has a laser sword.
As the individual \ms{Luke} is assigned to the class \ms{Jedi}, all constraint associated with this class are also validated, for example that Jedis must have blue laser swords.
Without reasoning, these constraints won't be validated as \ms{Luke} is not within the class extension of \ms{Jedi}.

\subsection{RDF Validation Requirements without Reasoning}

For the majority of the requirements to formulate RDF constraints, reasoning is not related to the constraints and is therefore not needed to be performed prior to validation. 
It is also possible, however, to reason before validating constraints for which reasoning does not affect validation results.
If we do reasoning by query rewriting in terms of backward chaining and if we run a constraint validation query through an engine like --ontop-- (OBDA tool) or ELITE (federated query engine), the engine will only do some rewritings if it is possible, and if you just check e.g. pattern matching there will be no rewriting.

\tb{Andy, I inserted your comments here. may you have a look at it?}

%\an{If we do reasoning by query rewriting in terms of backward chaining we don't need to distinguish between them, because if you run a constraint validation query through an engine like --ontop-- (OBDA tool) or ELITE (federated query engine), the engine will only do some rewritings if it is possible, and if you just check e.g. pattern matching there will be no rewriting...}

\subsubsection{Expressible by OWL 2 QL}

\textbf{Literal Pattern Matching}\footnote{corresponds to R-44-PATTERN-MATCHING-ON-RDF-LITERALS}\textbf{.} 
\an{IMHO literal pattern matching is not expressible in DL!}\tb{but we can express it using OWL 2 DL as it is shown in the OWL 2 spec}
There are multiple use cases associated with the requirement to match literals according to given patterns.

%A social security number, for example, is a string that matches a given regular expression - which can be expressed by OWL 2 QL: 
%
%\begin{ex}
%SSN 
    %a rdfs:Datatype ;
    %owl:equivalentClass [
        %a rdfs:Datatype ;
        %owl:onDatatype xsd:string ;
        %owl:withRestrictions ( 
            %[ xsd:pattern "[0-9]{3}-[0-9]{2}-[0-9]{4}" ] ) ] .
%hasSSN rdfs:range SSN .
%\end{ex}
%
%The second axiom defines \ms{SSN} as an abbreviation for a datatype restriction on \ms{xsd:string}. 
%The first axiom explicitly declares \ms{SSN} to be a datatype. 
%The datatype \ms{SSN} can be used just like any other datatype like in the third axiom to define the range of the \ms{hasSSN} property.
%The literal pattern matching constraint above validates \ms{hasSSN} literals according to the stated regular expression causing a constraint violation for the triple 
%\ms{TimBernersLee hasSSN "123456789"\textasciicircum{}\textasciicircum{}SSN}, 
%but not for the triple \ms{TimBernersLee hasSSN "123-45-6789"\textasciicircum{}\textasciicircum{}SSN}.

Luke's droids can only have the numbers "R2-D2" or "C-3PO".
The universal restriction part of this constraint can be expressed by OWL 2 DL:
\ms{LukesDroids $\sqsubseteq$ $\forall$ droidNumber . DroidNumber}.
The restriction of the datatype \ms{DroidNumber}, however, cannot be expressed in DL, but OWL 2 QL can be used anyway:

\begin{ex}
DroidNumber 
    a rdfs:Datatype ;
    owl:equivalentClass [
        a rdfs:Datatype ;
        owl:onDatatype xsd:string ;
        owl:withRestrictions ( 
            [ xsd:pattern "R2-D2|C-3PO" ] ) ] .
\end{ex}

The second axiom defines \ms{DroidNumber} as an abbreviation for a datatype restriction on \ms{xsd:string}. 
The first axiom explicitly declares \ms{DroidNumber} to be a datatype. 
The datatype \ms{DroidNumber} can be used just like any other datatype like in the universal restriction above.
The literal pattern matching constraint validates \ms{DroidNumber} literals according to the stated regular expression causing a constraint violation for the triples 
\ms{Luke hasDroid Droideka} and \ms{Droideka droidNumber "Droideka"\textasciicircum{}\textasciicircum{}DroidNumber}, 
but not for the triples \ms{Luke hasDroid R2-D2} and \ms{R2-D2 droidNumber "R2-D2"\textasciicircum{}\textasciicircum{}DroidNumber}.

\subsubsection{Not Expressible by OWL 2 QL but by OWL 2 DL}

\textbf{Allowed Values}\footnote{corresponds to R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS and R-37-ALLOWED-VALUES-FOR-RDF-LITERALS}\textbf{.}
It is a common requirement to narrow down the value space of a property by an exhaustive enumeration of the valid values (both literals or resources). This is often rendered in drop down boxes or radio buttons in user interfaces. 
The constraint 'Jedis can only have blue, green, or white laser swords' can be expressed by OWL 2 DL, DSP, ReSh, ShEx, SPIN, and SPARQL.

\begin{DL}
Jedi $\equiv$ $\exists$ laserSwordColor . \{blue, green, white\} \\
\end{DL}

In DSP, the constraint does not look that concise:

\begin{ex}
personDescriptionTemplate
    a dsp:DescriptionTemplate ;
    dsp:resourceClass Jedi ;
    dsp:statementTemplate [
        a dsp:LiteralStatementTemplate ;
        dsp:property laserSwordColor ;
        dsp:literalConstraint [
            a dsp:LiteralConstraint ;
            dsp:literal "blue" ;
            dsp:literal "green" ;
            dsp:literal "white"] ] .
\end{ex}

When representing the constraint by OWL2 DL a new datatype is defined by simply enumerating its literals:

\begin{ex}
laserSwordColor rdfs:range laserSwordColors . 
laserSwordColors
    a rdfs:Datatype .
    owl:oneOf ( "blue" "green" "white" ) .
\end{ex}

Data containing the triples \ms{Yoda a Jedi ; laserSwordColor 'blue'} is valid, 
whereas data including the triples \ms{DarthMaul a Jedi ; laserSwordColor 'red'} is invalid.

\textbf{Context-Specific Exclusive OR of Properties}\footnote{corresponds to  R-11-CONTEXT-SPECIFIC-EXCLUSIVE-OR-OF-PROPERTIES}\textbf{.}
An individual can either have a relationship via property A or via property B, but not both.
To take an example, a Jedi is either attacking by sword or by force but not both (such a fight would not be fair):

\begin{DL}
Jedi $\sqsubseteq$ ($\neg$ A $\sqcap$ B) $\sqcup$ (A $\sqcap$ $\neg$ B) \\
A $\equiv$ $\exists$ attackingBySword . xsd:boolean \\
B $\equiv$ $\exists$ attackingByForce . xsd:boolean \\ 
\end{DL}

Context-specific exclusive OR of properties can be expressed by ShEx. 
In this case, the constraint context is the class \ms{Jedi}.

\begin{ex}
Jedi { (  
    attackingBySword xsd:boolean | 
    attackingByForce xsd:boolean ) }
\end{ex}

The same constraint may be expressed by OWL 2 DL \an{Do you mean DL or QL at this point?}\tb{DisjointUnion is only supported by DL, see OWL 2 Profile spec}, but not very intuitively and concisely.
This can rather be seen as a workaround, as anonymous classes are built for each of the exclusive properties.

\begin{ex}
Jedi owl:disjointUnionOf ( CC1 CC2 ) . 
CC1 rdfs:subClassOf [
    a owl:Restriction ;
    owl:onProperty attackingBySword ;
    owl:someValuesFrom xsd:boolean ] .
CC2 rdfs:subClassOf [
    a owl:Restriction ;
    owl:onProperty attackingByForce ;
    owl:someValuesFrom xsd:boolean ] .
\end{ex}

Consider the triples \ms{Jedi(Luke)}, \ms{attackingBySword(Luke,true)}, \ms{Jedi(DarthSidious)},
\ms{attackingByForce(DarthSidious,true)}, and \ms{attackingBySword(DarthSidious,true)}
Luke as well as Darth Sidious are associated with the class \ms{Jedi}.
As Darth Sidious has both relationships, a constraint Violation is raised.

\subsubsection{Not Expressible by OWL 2 DL But by Other Constraint Languages}

The majority of constraints can neither be expressed by OWL 2 QL nor by OWL 2 DL. 
In such cases, these constraints are represented by other constraint languages like DSP, ShEx, ReSh, or SPIN.

\textbf{Default Values}\footnote{corresponds to R-31-DEFAULT-VALUES-OF-RDF-OBJECTS and R-38-DEFAULT-VALUES-OF-RDF-LITERALS}\textbf{.}
It should be possible to declare the default value for a given object and data property, e.g. so that input forms can be pre-populated and to insert a required property that is missing in a web service call. 
Siths have per default two red laser swords.
If there is only stated that Darth Maul is a Sith (\ms{DarthMaul a Sith .}), then additional default triples should be inferred: 
\ms{laserSwordColor(DarthMaul,"red")} and \ms{numberLaserSwords(DarthMaul,2)}.

The default values constraint can only be expressed by ReSh, SPIN, and SPARQL.
In SPIN, we can define a rule associated with the class \ms{owl:Thing}.
This rule is applicable for each resource, as each resource is implicitly of the type \ms{owl:Thing}.

\begin{ex}
owl:Thing spin:rule [ a sp:Construct ; sp:text """
    CONSTRUCT {
        ?this laserSwordColor "red" ;
              numberLaserSwords 2 . }
    WHERE {             
        ?this a Sith . } """ ; ] .
\end{ex}

For each resource, the SPARQL CONSTRUCT query within the rule is executed creating the default triples.
ReSh can also be used to express default values:

\begin{ex}
Sith a ResourceShape ;
    property [
        name "laserSwordColor" ;
        propertyDefinition laserSwordColor ;
        valueType xsd:string ;
        defaultValue "red"'
        occurs Exactly-one ; ] .
\end{ex}

\section{Implementation}

SPARQL is generally seen as the method of choice to validate RDF data according to certain constraints, although it is not ideal for their formulation. 
In contrast, OWL 2 DL constraints are comparatively easy to understand, but lack an implementation to validate RDF data. 
\an{IMHO this should be described more precisely because validation in terms of inconsistency detection is still available, not sure about the completeness for OWL 2 DL}
\tb{Andy, can you write a short paragraph about inconsistency detection? Sounds interesting!}
Bosch and Eckert\cite{BoschEckert2014-2} use SPIN as basis to define a
validation environment in which the validation of any DSCL\footnote{the only limitation is that DSCLs must be represented in RDF} can be implemented by representing them in SPARQL. 
The validation implementation of DSCLs is fully declarative,
consisting of a mapping from a DSCL to SPIN in form of SPARQL CONSTRUCT queries.
SPIN represents both the SPIN mappings and the SPARQL queries in RDF. 
Within the validation environment, we fully implemented an automatic validation of all OWL 2 DL\footnote{and therefore all OWL 2 QL constructs} constructs. 
\an{you should mention at this point that this validation is in terms of RDF validation, because inconsistency can't be done completely}
The implementation can be tested at \url{http://purl.org/net/rdfval-demo} and
the OWL 2 SPIN mapping is maintained at \url{https://github.com/boschthomas/OWL2-SPIN-Mapping}.

\textcolor{red}{extensions to validator}

\section{Related Work}

\begin{itemize}
	\item See e.g. chapter 6 of Jiao Tao's dissertation - http://tw.rpi.edu/web/doc/JiaoTaoDissertation .
\end{itemize}

\textbf{CWA.}

alternate semantics for OWL (using CWA):

Several years ago Evren Siren et al proposed an alternate semantics for OWL (using CWA) so that it could be used for integrity constraint (IC) checking and this is implemented in the Stardog database.

However, this OWL IC semantics was never submitted to a standards organization.

\begin{itemize}
	\item Clark Parsia had previously proposed the ICV semantics for OWL, but this was not submitted to W3C.
\end{itemize}

\section{Conclusion and Future Work}

\bibliography{../../literature/literature}{}
\bibliographystyle{plain}
\setcounter{tocdepth}{1}
%\listoftodos
\end{document}

### 2014-12-25 paper/RDF validation requirements/RDF validation requirements.tex
mapping tables added

@@
 
-\begin{evaluation}
-*Subsumption & \ding{55} & $\checkmark$ & $\checkmark$ & $\sim$ & $\checkmark$ & $\checkmark$ \\
-\end{evaluation}
-
 \subsection{Simple Example}
@@
 property & $\exists$ knows . Self & knows & - & Self & $\exists$ \\
-class & $\top$ & - & - & $\top$, $\exists$ knows . Self & \sqsubseteq \\
+class & $\top$ & - & - & $\top$, $\exists$ knows . Self & $\sqsubseteq$ \\
 \end{gcotable}
@@
 class & $\neg$ $\exists$ knows . Self & - & - & $\exists$ knows . Self & $\neg$ \\
-class & $\top$ & - & - & $\top$, $\neg$ $\exists$ knows . Self & \sqsubseteq \\
+class & $\top$ & - & - & $\top$, $\neg$ $\exists$ knows . Self & $\sqsubseteq$ \\
 \end{gcotable}
@@
 
-DSCL (ShEx):
-\begin{ex}
+\begin{ex}
+# ShEx
+# ----
 <Human> { 
@@
 
-\begin{DL}
-$A \equiv \forall foaf:name . xsd:string$ \\
-$B \equiv \forall foaf:givenName . xsd:string$ \\
-$C \equiv A XOR B$ \\
-$D \equiv \forall foaf:mbox . xsd:string$ \\
-$Human \equiv C \sqcap D$ \\
-\end{DL}
-\er{Where does this using $foaf:$ in DL come from? We need a description.}
-
-\an{I think we should use the existential quantifier instead of the universal quantifier!?}
-\begin{DL}
-$A \sqsubseteq \exists name.xsd:string$ \\
-$B \sqsubseteq \exists givenName.xsd:string$ \\
-$D \sqsubseteq \exists mbox.xsd:string$ \\
-$Human \sqsubseteq C \sqcap D$ \\
-\end{DL}
+%\begin{DL}
+%$Human \equiv C \sqcap F$ \\
+%$C \equiv A \sqcap B$ \\
+%$A \sqsubseteq \exists name.xsd:string$ \\
+%$B \sqsubseteq \exists givenName.xsd:string$ \\
+%$F \equiv D \sqcap E$ \\
+%$D \sqsubseteq \exists mbox.xsd:string$ \\
+%$E \sqsubseteq \exists homepage.Document$ \\
+%\end{DL}
+
+\begin{DL}
+Human $\equiv$ M $\sqcap$ N \\
+M $\equiv$ C $\sqcap$ F \\
+C $\sqsubseteq$ $\geq$ 1 name . string $\sqcap$ $\leq$ 1 name . string \\
+F $\sqsubseteq$ $\geq$ 1 givenName . string $\sqcap$ $\leq$ 1 givenName . string \\
+N $\equiv$ I $\sqcap$ L \\
+I $\sqsubseteq$ $\geq$ 1 mbox . string $\sqcap$ $\leq$ 1 mbox . string \\
+L $\sqsubseteq$ $\geq$ 1 homepage . Document $\sqcap$ $\leq$ 1 homepage . Document \\
+\end{DL}
+
+\begin{gcotable}
+class & Human & - & - & M, N & $\sqcap$ & - \\
+\hline
+class & M & - & - & C, F & $\sqcap$ & - \\
+class & C & - & - & A, B & $\sqcap$ & - \\
+property & A & foaf:name & - & string & $\geq$ & 1 \\
+property & B & foaf:name & - & string & $\leq$ & 1 \\
+class & F & - & - & D, E & $\sqcap$ & - \\
+property & D & foaf:givenName & - & string & $\geq$ & 1 \\
+property & E & foaf:givenName & - & string & $\leq$ & 1 \\
+\hline
+class & N & - & - & I, L & $\sqcap$ & - \\
+class & I & - & - & G, H & $\sqcap$ & - \\
+property & G & foaf:mbox & - & string & $\geq$ & 1 \\
+property & H & foaf:mbox & - & string & $\leq$ & 1 \\
+class & L & - & - & J, K & $\sqcap$ & - \\
+property & J & foaf:homepage & - & foaf:Document & $\geq$ & 1 \\
+property & K & foaf:homepage & - & foaf:Document & $\leq$ & 1 \\
+\end{gcotable}
 
@@
 \begin{DL}
-A $\equiv$ $\exists$ foaf:name . xsd:string \\
-B $\equiv$ $\exists$ foaf:givenName . xsd:string \\ 
 Human $\sqsubseteq$ ($\neg$ A $\sqcap$ B) $\sqcup$ (A $\sqcap$ $\neg$ B) \\
-\end{DL}
-
-\er{Let us mark that $foaf:$ occurs here.}
-
-\begin{gcotable}
-property & A & foaf:name & - & xsd:string & $\forall$ \\
-property & B & foaf:givenName & - & xsd:string & $\forall$ \\
+A $\sqsubseteq$ $\geq$ 1 name . string $\sqcap$ $\leq$ 1 name . string \\
+B $\sqsubseteq$ $\geq$ 1 givenName . string $\sqcap$ $\leq$ 1 givenName . string \\
+\end{DL}
+
+\begin{gcotable}
+class & Human & - & - & $\neg$ A $\sqcap$ B, A $\sqcap$ $\neg$ B & $\sqcup$ \\
+\hline
+class & A $\sqcap$ $\neg$ B & - & - & A, $\neg$ B & $\sqcap$ \\
+class & $\neg$ A $\sqcap$ B & - & - & $\neg$ A, B & $\sqcap$ \\
+\hline
 class & $\neg$ A & - & - & A & $\neg$ \\
+class & A & - & - & $\geq$ 1 name.string, $\leq$ 1 name.string & $\sqcap$ & - \\
+property & $\geq$ 1 name.string & name & - & string & $\geq$ & 1 \\
+property & $\leq$ 1 name.string & name & - & string & $\leq$ & 1 \\
+\hline
 class & $\neg$ B & - & - & B & $\neg$ \\
-class & $\neg$ A $\sqcap$ B & - & - & $\neg$ A, B & $\sqcap$ \\
-class & A $\sqcap$ $\neg$ B & - & - & A, $\neg$ B & $\sqcap$ \\
-class & Human & - & - & $\neg$ A $\sqcap$ B, A $\sqcap$ $\neg$ B & $\sqcup$ \\
+class & B & - & - & $\geq$ 1 givenName.string, $\leq$ 1 givenName.string & $\sqcap$ & - \\
+property & $\geq$ 1 givenName.string & givenName & - & string & $\geq$ & 1 \\
+property & $\leq$ 1 givenName.string & givenName & - & string & $\leq$ & 1 \\
 \end{gcotable}
@@
 syntactic sugar:
-
-\begin{gcotable}
-property & A & foaf:name & - & xsd:string & $\forall$ \\
-property & B & foaf:givenName & - & xsd:string & $\forall$ \\
-class & Human & - & - & A, B & XOR \\
-\end{gcotable}
-
-\er{Unsure what is meant in this example.}
+\begin{gcotable}
+property & = 1 name.string & name & - & string & = & 1 \\
+property & = 1 givenName.string & givenName & - & string & = & 1 \\
+class & Human & - & - & = 1 name.string, = 1 givenName.string & XOR \\
+\end{gcotable}
 
@@
 
+\subsection{Simple Example}
+
+\begin{DL}
+$Person \sqsubseteq ((Male \sqcap \neg Female) \sqcup (\neg Male \sqcap  Female)) $ 
+\end{DL}
+
 \subsection{Complex Example}
@@
 \end{itemize}
-
-%\tb{ToDo: DL}
-
-\er{Unsure what is meant in this example. Could be instead:}
-
-\begin{DL}
-$Person \sqsubseteq ((Male \sqcap \neg Female) \sqcup (\neg Male \sqcap  Female)) $ 
-\end{DL}
 
@@
 \end{itemize}
+
+\begin{DL}
+Human $\sqsubseteq$ A $\sqcup$ B \\
+A $\sqsubseteq$ $\geq$ 1 name . string $\sqcap$ $\leq$ 1 name . string \\
+B $\sqsubseteq$ $\geq$ 1 givenName . string $\sqcap$ $\leq$ 1 givenName . string \\
+\end{DL}
+
+syntactic sugar:
+\begin{gcotable}
+property & = 1 name.string & name & - & string & = & 1 \\
+property & = 1 givenName.string & givenName & - & string & = & 1 \\
+class & Human & - & - & = 1 name.string, = 1 givenName.string & $\sqcup$ \\
+\end{gcotable}
 
@@
 F $\equiv$ C $\sqcap$ D \\
-A $\equiv$ $\forall$ foaf:name . xsd:string \\
-B $\equiv$ $\forall$ foaf:givenName . xsd:string \\ 
-C $\equiv$ $\forall$ foaf:mbox . IRI \\
-D $\equiv$ $\forall$ foaf:homepage . foaf:Document \\
-\end{DL}
+A $\sqsubseteq$ $\geq$ 1 name . string $\sqcap$ $\leq$ 1 name . string \\
+B $\sqsubseteq$ $\geq$ 1 givenName . string $\sqcap$ $\leq$ 1 givenName . string \\
+C $\sqsubseteq$ $\geq$ 1 mbox . IRI $\sqcap$ $\leq$ 1 mbox . IRI \\
+D $\sqsubseteq$ $\geq$ 1 homepage . Document $\sqcap$ $\leq$ 1 homepage . Document \\
+\end{DL}
+
+syntactic sugar:
+\begin{gcotable}
+class & Human & - & - & E, F & XOR \\
+class & E & - & - & = 1 name.string, = 1 givenName.string & $\sqcap$ \\
+class & F & - & - & = 1 mbox.IRI, = 1 homepage.Document & $\sqcap$ \\
+property & = 1 name.string & name & - & string & = & 1 \\
+property & = 1 givenName.string & givenName & - & string & = & 1 \\
+property & = 1 mbox.IRI & mbox & - & IRI & = & 1 \\
+property & = 1 homepage.Document & homepage & - & Document & = & 1 \\
+\end{gcotable}
 
@@
 \end{ex}
+
+\begin{DL}
+Human $\sqsubseteq$ E $\sqcup$ F \\ 
+E $\equiv$ A $\sqcap$ B \\
+F $\equiv$ C $\sqcap$ D \\
+A $\sqsubseteq$ $\geq$ 1 name . string $\sqcap$ $\leq$ 1 name . string \\
+B $\sqsubseteq$ $\geq$ 1 givenName . string $\sqcap$ $\leq$ 1 givenName . string \\
+C $\sqsubseteq$ $\geq$ 1 mbox . IRI $\sqcap$ $\leq$ 1 mbox . IRI \\
+D $\sqsubseteq$ $\geq$ 1 homepage . Document $\sqcap$ $\leq$ 1 homepage . Document \\
+\end{DL}
+
+syntactic sugar:
+\begin{gcotable}
+class & Human & - & - & E, F & $\sqcup$ \\
+class & E & - & - & = 1 name.string, = 1 givenName.string & $\sqcap$ \\
+class & F & - & - & = 1 mbox.IRI, = 1 homepage.Document & $\sqcap$ \\
+property & = 1 name.string & name & - & string & = & 1 \\
+property & = 1 givenName.string & givenName & - & string & = & 1 \\
+property & = 1 mbox.IRI & mbox & - & IRI & = & 1 \\
+property & = 1 homepage.Document & homepage & - & Document & = & 1 \\
+\end{gcotable}
 

### 2014-12-26 paper/RDF validation requirements/RDF validation requirements.tex
added mapping tables

@@
   \hline
-  \textbf{c. type} & \textbf{context class} & \textbf{left r. list} & \textbf{right r. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+  \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
   \hline
@@
 
-%\tb{ToDo: check DL}
+\begin{gcotable}
+property & Jedi & laserSwordColor & - & LaserSwordColor & $\exists$ & - \\
+class & LaserSwordColor & - & - & $\{blue\}$, $\{green\}$, $\{white\}$ & $\sqcup$ & - \\
+\end{gcotable}
 
@@
 
-%\tb{ToDo: check DL}
+\begin{gcotable}
+property & $\exists$ laserSwordColor . LaserSwordColor & laserSwordColor & - & LaserSwordColor & $\exists$ & - \\
+class & Jedi & - & - & $\exists$ laserSwordColor . LaserSwordColor & $\neg$ & - \\
+class & LaserSwordColor & - & - & $\{blue\}$, $\{green\}$, $\{white\}$ & $\sqcup$ & - \\
+\end{gcotable}
 
@@
 \end{itemize}
-\er{This sort of DL-syntax (with semicolon) must be rechecked.
+%\er{This sort of DL-syntax (with semicolon) must be rechecked.
 Note that in DL, it does not have to correspond directly to names of things in machine-readable syntax.
@@
 \begin{DL}
-$A \equiv skos:Concept \sqcap B$ \\
-$B \equiv \forall skos:inScheme . C$ \\
-$C \equiv skos:ConceptScheme \sqcap ( \{:BookSubjects\} \sqcup \{:BookTopics\} \sqcup \{:BookCategories\} )$ \\
-\end{DL}
+$A \equiv Concept \sqcap B$ \\
+$B \equiv \forall inScheme . C$ \\
+$C \equiv ConceptScheme \sqcap ( \{BookSubjects\} \sqcup \{BookTopics\} \sqcup \{BookCategories\} )$
+\end{DL}
+
+\begin{gcotable}
+property & $\top$ & subject & - & A & range & - \\
+class & A & - & - & Concept, B & $\sqcap$ & - \\
+property & B & inScheme & - & C & $\forall$ & - \\
+class & C & - & - & ConceptScheme, D & $\sqcap$ & - \\
+class & D & - & - & $\{BookSubjects\}$, $\{BookTopics\}$, $\{BookCategories\}$ & $\sqcup$ & - \\
+\end{gcotable}
 
@@
 \begin{ex}
-# OWL 2 QL (functional-style syntax)
+# OWL 2 DL (functional-style syntax)
 # ----------------------------------
@@
 \begin{ex}
-# OWL 2 QL (turtle syntax)
+# OWL 2 DL (turtle syntax)
 # ------------------------
@@
 \begin{DL}
-NOT EXPRESSIBLE IN DL!!!
+Not expressible in DL!
 \end{DL}
@@
 class & SSN & - & - & xsd:string & xsd:pattern & '[0-9]{3}-[0-9]{2}-[0-9]{4}' \\
+\end{gcotable}
+
+\subsection{Simple Example}
+
+There are multiple use cases associated with the requirement to match literals according to given patterns.
+
+Luke's droids can only have the numbers "R2-D2" or "C-3PO".
+The universal restriction part of this constraint can be expressed by OWL 2 DL:
+\ms{LukesDroids $\sqsubseteq$ $\forall$ droidNumber . DroidNumber}.
+The restriction of the datatype \ms{DroidNumber}, however, cannot be expressed in DL, but OWL 2 DL can be used anyway:
+
+\begin{ex}
+DroidNumber 
+    a rdfs:Datatype ;
+    owl:equivalentClass [
+        a rdfs:Datatype ;
+        owl:onDatatype xsd:string ;
+        owl:withRestrictions ( 
+            [ xsd:pattern "R2-D2|C-3PO" ] ) ] .
+\end{ex}
+
+The second axiom defines \ms{DroidNumber} as an abbreviation for a datatype restriction on \ms{xsd:string}. 
+The first axiom explicitly declares \ms{DroidNumber} to be a datatype. 
+The datatype \ms{DroidNumber} can be used just like any other datatype like in the universal restriction above.
+The literal pattern matching constraint validates \ms{DroidNumber} literals according to the stated regular expression causing a constraint violation for the triples 
+\ms{Luke hasDroid Droideka} and \ms{Droideka droidNumber "Droideka"\textasciicircum{}\textasciicircum{}DroidNumber}, 
+but not for the triples \ms{Luke hasDroid R2-D2} and \ms{R2-D2 droidNumber "R2-D2"\textasciicircum{}\textasciicircum{}DroidNumber}.
+
+\begin{DL}
+Not expressible in DL!
+\end{DL}
+
+\begin{gcotable}
+property & LukesDroids & droidNumber & - & DroidNumber & $\forall$ & - \\
+class & DroidNumber & - & - & xsd:string & xsd:pattern & 'R2-D2$|$C-3PO' \\
 \end{gcotable}
@@
 There are no identical strings.
+
+\begin{DL}
+Not expressible in DL!
+\end{DL}
+
+\begin{gcotable}
+property & $\top$ & dc:subject & dc:subject & xsd:string & $\neq$ & - \\
+\end{gcotable}
 
@@
 
-\begin{DL}
-1-23 $\equiv$ \{'1'\} $\sqcup$ \{'2'\} $\sqcup$ ... $\sqcup$ \{'23'\} \\
-$\top$ $\sqsubseteq$ $\forall$ position . 1-23 \\
-This is just an auxiliary construction and is not sufficient for general cases, so: NOT EXPRESSIBLE IN DL!!!
-\end{DL}
-
-\begin{gcotable}
-class & AtLeast1 & - & - & xsd:nonNegativeInteger & $\geq$ & 1 \\
-class & AtMost23 & - & - & xsd:nonNegativeInteger & $\leq$ & 23 \\
-class & NumberPlayers... & - & - & AtLeast1, AtMost23 & $\sqcap$ & - \\
-property & $\top$ & position & - & NumberPlayers... & range & - \\
-\end{gcotable}
-
-or:
+%\begin{DL}
+%1-23 $\equiv$ \{'1'\} $\sqcup$ \{'2'\} $\sqcup$ ... $\sqcup$ \{'23'\} \\
+%$\top$ $\sqsubseteq$ $\forall$ position . 1-23 \\
+%\end{DL}
+
+\begin{DL}
+Not expressible in DL!
+\end{DL}
+
+%\begin{gcotable}
+%class & AtLeast1 & - & - & xsd:nonNegativeInteger & $\geq$ & 1 \\
+%class & AtMost23 & - & - & xsd:nonNegativeInteger & $\leq$ & 23 \\
+%class & NumberPlayers... & - & - & AtLeast1, AtMost23 & $\sqcap$ & - \\
+%property & $\top$ & position & - & NumberPlayers... & range & - \\
+%\end{gcotable}
+%
+%or:
 
@@
 
-or:
-
-\begin{gcotable}
-class & 1-23 & - & - & \{'1'\}, \{'2'\}, ..., \{'23'\} & $\sqcup$ & - \\
-property & $\top$ & position & - & 1-23 & range& - \\
-\end{gcotable}
+%or:
+%
+%\begin{gcotable}
+%class & 1-23 & - & - & \{'1'\}, \{'2'\}, ..., \{'23'\} & $\sqcup$ & - \\
+%property & $\top$ & position & - & 1-23 & range& - \\
+%\end{gcotable}
 
@@
 
-\begin{DL}
 I'm not sure about the meaning of this constraint, but for me this seams like e.g. the range of a role... but if this is the case, take into account the consequences of reasoning with OWA...
-\end{DL}
-
-\an{not sure!}
 
@@
 
-\begin{DL}
 I'm not sure about the meaning of this constraint, but for me this seams like e.g. the domain of a role... but if this is the case, take into account the consequences of reasoning with OWA...
-\end{DL}
-
-\an{not sure!}
 
@@
 \begin{DL}
-NOT EXPRESSIBLE IN DL!!!
-\end{DL}
+Not expresible in DL!
+\end{DL}
+
+\begin{gcotable}
+class & Jedi & laserSwordColor & - & - & default values & 'blue' \\
+class & Jedi & numberLaserSwords & - & - & default values & '1' \\
+class & Sith & laserSwordColor & - & - & default values & 'red' \\
+class & Sith & numberLaserSwords & - & - & default values & '2' \\
+\end{gcotable}
 
@@
 \begin{DL}
-NOT EXPRESSIBLE IN DL!!!
+Not Expressible in DL!
 \end{DL}
@@
 
-\begin{DL}
-NOT EXPRESSIBLE IN DL!!!
-\end{DL}
+\subsection{Simple Example}
+
+Only English names are allowed.
+
+\begin{DL}
+Not expressible in DL!
+\end{DL}
+
+\begin{gcotable}
+class & $\top$ & name & - & - & language tag & 'en' \\
+\end{gcotable}
 
@@
 
-\subsection{Example}
+\subsection{Simple Example}
 
@@
 \begin{DL}
-NOT EXPRESSIBLE IN DL!!!
-\end{DL}
+Not expressible in DL!
+\end{DL}
+
+\begin{gcotable}
+class & $\top$ & foaf:name & - & - & language tag exact cardinality & 1 \\
+\end{gcotable}
 
@@
 
-\begin{DL}
-NOT EXPRESSIBLE IN DL!!!
-\end{DL}
+check if literals of the property \ms{p} do not include whitespaces
+
+\begin{DL}
+Not expressible in DL!
+\end{DL}
+
+\begin{gcotable}
+class & $\top$ & p & - & - & whitespace & - \\
+\end{gcotable}
 
@@
 
-description:
-
-\begin{itemize}
-	\item check if there are no html tags included in literals (of specific data properties within the context of specific classes)
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{DL}
-NOT EXPRESSIBLE IN DL!!!
-\end{DL}
+\begin{itemize}
+	\item check if there are no HTML tags included in literals (of specific data properties within the context of specific classes)
+\end{itemize}
+
+\subsection{Simple Example}
+
+check if literals of the property \ms{p} of the class \ms{C} do not include HTML tags
+
+\begin{DL}
+Not expressible in DL!
+\end{DL}
+
+\begin{gcotable}
+class & c & p & - & - & HTML & - \\
+\end{gcotable}
 
@@
 $\exists hasAncestor.Person \sqsubseteq Person$ \\
-(same as the definition of domains)
-\end{DL}
+\end{DL}
+
+Same as the definition of domains.
 
@@
 \subsection{Simple Example}
-
-\begin{DL}
-Not sure about the meaning of this constraint...
-\end{DL}
-
-\an{not sure!}
 
@@
 
-\begin{DL}
-- condition: universal quantification on object and data properties\\
-\ \ \ \ same as above!?\\
-- condition: existential quantification on object and data properties\\
-\ \ \ \ same as above!?\\
-- condition: if specific properties are present, then specific other properties also have to be present
-\ \ \ \ same as super properties, so if a property (role or attribute) is used, all super properties are also present
-\end{DL}
-
 \section{Recommended Properties}
@@
 
-\begin{DL}
-Not sure about the meaning of this constraint...
-\end{DL}
-
-\an{not sure!}
+Property \ms{p} is recommended to use within the context of the class \ms{C}.
+
+\begin{DL}
+Not expressible in DL!
+\end{DL}
+
+\begin{gcotable}
+class & C & p & - & - & recommended & - \\
+\end{gcotable}
 

### 2014-12-26 paper/RDF validation requirements/RDF validation requirements.tex
added mapping tables

@@
 
+\begin{gcotable}
+property & $\exists$ studentOf.JediMentor & studentOf & - & JediMentor & $\exists$ & - \\
+class & JediMentor & - & - & $\exists$ studentOf.JediMentor & $\neg$ & - \\
+\end{gcotable}
+
 \section{Handle RDF Collections}
@@
 <IssueShape> {
-    :state (:unassigned :assigned),
-    :reportedBy @<UserShape>,
     :related @<IssueShape>*
@@
 
-\begin{itemize}
-	\item make sure that a value is valid for its datatype
-\end{itemize}
+Make sure that a value is valid for its datatype.
 
@@
 
-\begin{DL} 
-$\rho(\textsf{hasBirthday}) \sqsubseteq \PVerb{xsd:dateTime}$\\
-(equal to the definition of an attribute (data property) range)
-\end{DL}
-
 \begin{itemize}
@@
 
+\begin{gcotable}
+class & $\top$ & shoeSize & - & xsd:nonNegativeInteger & value valid for datatype & - \\
+\end{gcotable}
+
+\subsection{Simple Example}
+
+\begin{DL} 
+$\rho(\textsf{hasBirthday}) \sqsubseteq \PVerb{xsd:dateTime}$\\
+\end{DL}
+
+Equal to the definition of a data property range.
+
+\tb{I do not understand the relation of this example to this constraint}
+
 \section{Individual Equality}
 
-\begin{itemize}
-	\item states that two different names are known to refer to the same individual \cite{Kroetzsch2012}
-\end{itemize}
+\ms{Individual equality} states that two different names are known to refer to the same individual \cite{Kroetzsch2012}.
 
@@
 \begin{gcotable}
-class & \{julia\} & - & - & \{john\} & = \\
-class & \{john\} & - & - & \{julia\} & = \\
+class & \{julia\} & - & - & \{john\} & = & - \\
+class & \{john\} & - & - & \{julia\} & = & - \\
 \end{gcotable}
@@
 
+This is by default because of the UNA.
+
 \subsection{Simple Example}
@@
 $\{julia\} \ne \{john\} $\\
-(this is by default because of the UNA)
-\end{DL}
-
-\begin{itemize}
-	\item asserts that Julia and John are actually different individuals
-\end{itemize}
-
-\begin{gcotable}
-class & \{julia\} & - & - & \{john\} & $\ne$ \\
-class & \{john\} & - & - & \{julia\} & $\ne$ \\
+\end{DL}
+
+Asserts that Julia and John are actually different individuals.
+
+\begin{gcotable}
+class & \{julia\} & - & - & \{john\} & $\ne$ & - \\
+class & \{john\} & - & - & \{julia\} & $\ne$ & - \\
 \end{gcotable}

### 2014-12-26 paper/RDF validation requirements/RDF validation requirements.tex
research questions and contributions

@@
 \section{Equivalent Properties}
-
-\begin{itemize}
-	\item An equivalent object properties axiom EquivalentObjectProperties( OPE1 ...
+An equivalent object properties axiom EquivalentObjectProperties( OPE1 ...
 OPEn ) states that all of the object property expressions OPEi, 1 $\leq$ i $\leq$ n, are semantically equivalent to each other.
@@
 The axiom EquivalentObjectProperties( OPE1 OPE2 ) is equivalent to the following two axioms SubObjectPropertyOf( OPE1 OPE2 ) and SubObjectPropertyOf( OPE2 OPE1 ).
-	\item An equivalent data properties axiom EquivalentDataProperties( DPE1 ...
+
+An equivalent data properties axiom EquivalentDataProperties( DPE1 ...
 DPEn ) states that all the data property expressions DPEi, 1 $\leq$ i $\leq$ n, are semantically equivalent to each other.
@@
 The axiom EquivalentDataProperties( DPE1 DPE2 ) can be seen as a syntactic shortcut for the following axiom SubDataPropertyOf( DPE1 DPE2 ) and SubDataPropertyOf( DPE2 DPE1 ).
-
-\end{itemize}
 
@@
 :hasBrother $\sqsubseteq$ :hasMaleSibling $\sqcap$ :hasMaleSibling $\sqsubseteq$ :hasBrother \\
-equivalent to: $hasBrother = hasMaleSibling$
+\end{DL}
+
+\begin{gcotable}
+property & $\top$ & hasBrother & hasMaleSibling & - & $\sqsubseteq$ \\
+property & $\top$ & hasMaleSibling & has Brother & - & $\sqsubseteq$ \\
+\end{gcotable}
+
+\begin{DL}
+$hasBrother \equiv hasMaleSibling$
 \end{DL}
@@
 
-\begin{itemize}
-	\item Meg is not a son of Peter.
-\end{itemize}
-
-\begin{DL}
-$hasSon(\textbf{Peter},\textbf{Meg})$\\
-(negation of such an assertion is not necessary / meaningless!)
-\end{DL}
+Meg is not a son of Peter.
+
+\begin{DL}
+$hasSon(Peter,Meg)$\\
+\end{DL}
+
+The negation of such an assertion is not necessary, as it's meaningless!
+
+\begin{gcotable}
+class & \{Peter\} & hasSon & - & \{Meg\} & $\neq$ & - \\
+\end{gcotable}
 
@@
 
-\begin{itemize}
-	\item Meg is seventeen years old. 
-\end{itemize}
-
-\begin{DL}
-$hasAge ( \textbf{Meg} ,\textbf{ "17"}\hat{\ } \hat{\ } xsd:integer ) $\\
-\end{DL}
+Meg is seventeen years old.
+
+\begin{DL}
+$hasAge ( Meg ,"17"\hat{\ } \hat{\ } xsd:integer ) $\\
+\end{DL}
+
+\begin{gcotable}
+class & \{Meg\} & hasAge & - & - & = & "17"$\hat{\ } \hat{\ }$ xsd:integer \\
+\end{gcotable}
 
@@
 
-\begin{itemize}
-	\item An object property functionality axiom FunctionalObjectProperty( OPE ) states that the object property expression OPE is functional — that is, for each individual x, there can be at most one distinct individual y such that x is connected by OPE to y.
+An object property functionality axiom FunctionalObjectProperty( OPE ) states that the object property expression OPE is functional — that is, for each individual x, there can be at most one distinct individual y such that x is connected by OPE to y.
 Each such axiom can be seen as a syntactic shortcut for the following axiom: SubClassOf( owl:Thing ObjectMaxCardinality( 1 OPE ) ).
-\end{itemize}
 
@@
 
-\begin{itemize}
-	\item Each object can have at most one father. 
-\end{itemize}
+Each object can have at most one father.
 
@@
 
+\begin{gcotable}
+property & $\top$ & hasFather & - & - & functional & - \\
+\end{gcotable}
+
 \section{Inverse-Functional Properties}
 
-\begin{itemize}
-	\item An object property inverse functionality axiom InverseFunctionalObjectProperty( OPE ) states that the object property expression OPE is inverse-functional — that is, for each individual x, there can be at most one individual y such that y is connected by OPE with x.
+An object property inverse functionality axiom InverseFunctionalObjectProperty( OPE ) states that the object property expression OPE is inverse-functional — that is, for each individual x, there can be at most one individual y such that y is connected by OPE with x.
 Each such axiom can be seen as a syntactic shortcut for the following axiom: SubClassOf( owl:Thing ObjectMaxCardinality( 1 ObjectInverseOf( OPE ) ) ).
-\end{itemize}
 
@@
 \end{DL}
+
+\begin{gcotable}
+property & $\top$ & hasFather$^{-}$ & hasFather & - & inverse & - \\
+property & $\top$ & hasFather$^{-}$ & - & - & functional & - \\
+\end{gcotable}
 

### 2014-12-27 paper/RDF validation requirements/RDF validation requirements.tex
Some editing all over has been done

@@
 $(\forall R.C)^\mathcal{I}= \{a \in \Delta^\mathcal{I}\mid (a,b) \in R^\mathcal{I} \rightarrow b \in C^\mathcal{I} \}$ where $\cdot^\mathcal{I}$ is an interpretation function, \\
-$\Delta^I$ is the domain, $a,b \in \Delta^\mathcal{I}$ are individuals $C$ is a concept, $R$ is a role. 
+$\Delta^\mathcal{I}$ is the domain, $a,b \in \Delta^\mathcal{I}$ are individuals $C$ is a concept, $R$ is a role. 
 \end{DL}

### 2014-12-27 paper/RDF validation requirements/RDF validation requirements.tex
DL mappings added

@@
 
-\begin{itemize}
-	\item Individual Value Restrictions: A has-value class expression ObjectHasValue( OPE a ) consists of an object property expression OPE and an individual a, and it contains all those individuals that are connected by OPE to a.
+Individual Value Restrictions: A has-value class expression ObjectHasValue( OPE a ) consists of an object property expression OPE and an individual a, and it contains all those individuals that are connected by OPE to a.
 Each such class expression can be seen as a syntactic shortcut for the class expression ObjectSomeValuesFrom( OPE ObjectOneOf( a ) ).
-	\item Literal Value Restrictions: A has-value class expression DataHasValue( DPE lt ) consists of a data property expression DPE and a literal lt, and it contains all those individuals that are connected by DPE to lt.
+Literal Value Restrictions: A has-value class expression DataHasValue( DPE lt ) consists of a data property expression DPE and a literal lt, and it contains all those individuals that are connected by DPE to lt.
 Each such class expression can be seen as a syntactic shortcut for the class expression DataSomeValuesFrom( DPE DataOneOf( lt ) ).
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
+
+\subsection{Simple Example}
+
+\begin{DL}
+$FatherOfStewie \sqsubseteq \exists fatherOf.\{Stewie\}$
+\end{DL}
+
+\begin{ex}
+# OWL 2
+# -----
 :Peter :fatherOf :Stewie . 
@@
 
-\begin{itemize}
-	\item The has-value class expression contains those individuals that are connected through the :fatherOf property with the individual :Stewie
-  \item :Peter is classified as its instance
-\end{itemize}
-
-\begin{DL}
-Not sure about the meaning of this constraint...\\
-May be it is:\\
-$Shortcut \sqsubseteq \exists fatherOf.\{\textbf{Stewie}\}$
-\end{DL}
-
-\an{not sure!}
+The has-value class expression contains those individuals that are connected through the :fatherOf property with the individual :Stewie.
+:Peter is classified as its instance.
+
+\begin{gcotable}
+property & FatherOfStewie & fatherOf & - & $\{Stewie\}$ & $\exists$ \\
+\end{gcotable}
 
@@
 
-\begin{itemize}
-	\item A self-restriction ObjectHasSelf( OPE ) consists of an object property expression OPE, and it contains all those individuals that are connected by OPE to themselves. 
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
+A self-restriction ObjectHasSelf( OPE ) consists of an object property expression OPE, and it contains all those individuals that are connected by OPE to themselves.
+
+\subsection{Simple Example}
+
+\begin{ex}
+# OWL 2
+# -----
 :Peter :likes :Peter . 
@@
 
-\begin{itemize}
-	\item The self-restriction contains those individuals that like themselves
-  \item :Peter is classified as its instance
-\end{itemize}
+\begin{DL}
+$\top$ $\sqsubseteq$ $\exists$ likes . Self
+\end{DL}
+
+\tb{my attempt}
+
+\begin{gcotable}
+property & $\exists$ likes . Self & likes & - & Self & $\exists$ \\
+class & $\top$ & - & - & $\top$, $\exists$ likes . Self & $\sqsubseteq$ \\
+\end{gcotable}
+
+The self-restriction contains those individuals that like themselves.
+:Peter is classified as its instance.
 
@@
 
-requirement:
-
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\begin{itemize}
-  \item It is often useful to declare a given (datatype) property as the "primary key" of a class, so that the system can enforce uniqueness and also automatically build URIs from user input and data imported from relational databases or spreadsheets.
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{itemize}
-	\item Each object is uniquely identified by its social security number.
-\end{itemize}
+It is often useful to declare a given (datatype) property as the "primary key" of a class, so that the system can enforce uniqueness and also automatically build URIs from user input and data imported from relational databases or spreadsheets.
+
+\subsection{Simple Example}
+Each object is uniquely identified by its social security number.
 
@@
 
-\begin{itemize}
-	\item The first axiom makes :hasSSN the key for instances of the owl:Thing class; thus, only one individual can have a particular value for :hasSSN. 
-\end{itemize}
+The first axiom makes :hasSSN the key for instances of the owl:Thing class; thus, only one individual can have a particular value for :hasSSN.
 
@@
 
-\begin{itemize}
-	\item Since the values of :hasSSN are the same for the individuals a:Peter and a:PeterGriffin, these two individuals are equal - that is, this ontology entails the following assertion :Peter owl:sameAs :PeterGriffin .
-\end{itemize}
+Since the values of :hasSSN are the same for the individuals a:Peter and a:PeterGriffin, these two individuals are equal - that is, this ontology entails the following assertion :Peter owl:sameAs :PeterGriffin .
 
@@
 \an{not sure!}
+
+\begin{DL}
+$(\textsf{funct } \textsf{hasSSN})$
+\end{DL}
+
+\begin{gcotable}
+property & $\top$ & hasSSN & - & - & functional & - \\
+\end{gcotable}
+
+\tb{my attempt}
 
@@
 
-\begin{itemize}
-  \item Some constraints require aggregating multiple values, especially via COUNT, MIN and MAX. 
-\end{itemize}
+Some constraints require aggregating multiple values, especially via COUNT, MIN and MAX.
 

### 2014-12-28 paper/RDF validation requirements/RDF validation requirements.tex
GCLO

@@
 \begin{gcotable}
-class & Jedi & laserSwordColor & - & - & default values & 'blue' \\
-class & Jedi & numberLaserSwords & - & - & default values & '1' \\
-class & Sith & laserSwordColor & - & - & default values & 'red' \\
-class & Sith & numberLaserSwords & - & - & default values & '2' \\
+property & Jedi & laserSwordColor & - & - & default values & 'blue' \\
+property & Jedi & numberLaserSwords & - & - & default values & '1' \\
+property & Sith & laserSwordColor & - & - & default values & 'red' \\
+property & Sith & numberLaserSwords & - & - & default values & '2' \\
 \end{gcotable}
@@
 \begin{gcotable}
-class & $\top$ & name & - & - & language tag & 'en' \\
+property & $\top$ & name & - & - & language tag & 'en' \\
 \end{gcotable}
@@
 \begin{gcotable}
-class & $\top$ & foaf:name & - & - & language tag exact cardinality & 1 \\
+property & $\top$ & foaf:name & - & - & language tag exact cardinality & 1 \\
 \end{gcotable}
@@
 \begin{gcotable}
-class & $\top$ & p & - & - & whitespace & - \\
+property & $\top$ & p & - & - & whitespace & - \\
 \end{gcotable}
@@
 \begin{gcotable}
-class & c & p & - & - & HTML & - \\
+property & c & p & - & - & HTML & - \\
 \end{gcotable}
@@
 \begin{gcotable}
-class & C & p & - & - & recommended & - \\
+property & C & p & - & - & recommended & - \\
 \end{gcotable}
@@
 \begin{gcotable}
-class & $\top$ & shoeSize & - & xsd:nonNegativeInteger & value valid for datatype & - \\
+property & $\top$ & shoeSize & - & xsd:nonNegativeInteger & value valid for datatype & - \\
 \end{gcotable}
@@
 \begin{gcotable}
-class & \{Peter\} & hasSon & - & \{Meg\} & $\neq$ & - \\
+property & \{Peter\} & hasSon & - & \{Meg\} & $\neq$ & - \\
 \end{gcotable}
@@
 \begin{gcotable}
-class & \{Meg\} & hasAge & - & - & = & "17"$\hat{\ } \hat{\ }$ xsd:integer \\
+property & \{Meg\} & hasAge & - & - & = & "17"$\hat{\ } \hat{\ }$ xsd:integer \\
 \end{gcotable}
@@
 \begin{DL}
-Not sure about if this constraint is expressible in DL, I think not!
-\end{DL}
-
-\an{not sure!}
-
-\begin{DL}
-$\top$ $\sqsubseteq$ $\exists$ likes . Self
-\end{DL}
-
-\tb{my attempt}
+LikesThemselves $\sqsubseteq$ $\exists$ likes . Self
+\end{DL}
 
@@
 property & $\exists$ likes . Self & likes & - & Self & $\exists$ \\
-class & $\top$ & - & - & $\top$, $\exists$ likes . Self & $\sqsubseteq$ \\
+class & LikesThemselves & - & - & $\top$, $\exists$ likes . Self & $\sqsubseteq$ \\
 \end{gcotable}
@@
 
+\begin{DL}
+$(\textsf{funct } \textsf{SSN}\sp{\overline{\ }})$
+\end{DL}
+
+\begin{gcotable}
+property & $\top$ & SSN$^{-}$ & SSN & - & inverse & - \\
+property & $\top$ & SSN$^{-}$ & - & - & functional & - \\
+\end{gcotable}
+
 Since the values of :hasSSN are the same for the individuals a:Peter and a:PeterGriffin, these two individuals are equal - that is, this ontology entails the following assertion :Peter owl:sameAs :PeterGriffin .
 
-\begin{DL}
-Not sure if this is expressible in DL, may be we should have a detailed look to \textit{DL-Lite}$_{\mathcal{A},id}$ \\
-(see \url{http://www.dis.uniroma1.it/~lembo/papers/calv-etal-RW-2009.pdf})
-\end{DL}
-
-\an{not sure!}
-
-\begin{DL}
-$(\textsf{funct } \textsf{hasSSN})$
-\end{DL}
-
-\begin{gcotable}
-property & $\top$ & hasSSN & - & - & functional & - \\
-\end{gcotable}
-
-\tb{my attempt}
+%\begin{DL}
+%Not sure if this is expressible in DL, may be we should have a detailed look to \textit{DL-Lite}$_{\mathcal{A},id}$ \\
+%(see \url{http://www.dis.uniroma1.it/~lembo/papers/calv-etal-RW-2009.pdf})
+%\end{DL}
+%
+%\an{not sure!}
+
+Since "Each object is uniquely identified by its social security number." It means it is inverse functional property.
+
+So instead,  a property can be defined as 
+\begin{DL}
+$(\textsf{funct } \textsf{SSN})$
+\end{DL}
+, and then by a property inclusion axiom
+
+\begin{DL}
+$haskey \sqsubseteq SSN^{-}$
+\end{DL}
+
+now for a given number haskey will give me the object (note that obviously it should be named, no ambigious individuals).
+
+However I needed to do some little research and found out that, keys are even more general (A generalisation of inverse functional properties) so that it can also be a chain of properties.
+(it is clear here: http://www.w3.org/TR/2012/REC-owl2-rdf-based-semantics-20121211/\#table-semcond-keys)
+
+For this generalisation purposes and many spooky interactions of different sorts of key (and with some elaboration they can lead to undecidability), they introduced "key boxes, and extended the language with special "keyfor" construct.
+So how it is done in DL community as I learned is
+
+\begin{DL}
+SSN "keyfor" Human $\sqcap$ TurkishCitizen
+\end{DL}
+
+ for instance. Now ssn behaves as an identifying element for individuals of right hand side.
+
+For comprehensive studies and resources, one can find lots of examples in:
+
+http://lat.inf.tu-dresden.de/research/mas/Din-Mas-06.pdf
+https://www.jair.org/media/1542/live-1542-2375-jair.pdf
+
+Yes you can, but as you see it is not restriction statement by its own.
+Nevertheless, I think, in DL mapping, use of "keyfor" and sending a reference to one of those papers is more convenient/safer, since it can be a datatype property, object property, or a chain of properties (from OWL world), as well as DL literature has it as "keyfor".
+
+\begin{gcotable}
+property & $\top$ & SSN & - & - & keyfor & - \\
+\end{gcotable}
 

### 2014-12-28 paper/paper 2/paper 2.tex
added mapping tables
GCLO

@@
   \vspace{0.3cm}
+	\begin{center}
   \begin{tabular}{l|l|l|l|l|l|l}
   \hline
-  \textbf{c. type} & \textbf{context concept} & \textbf{left p. list} & \textbf{right p. list} & \textbf{concepts} & \textbf{c. element} & \textbf{c. value} \\
+  \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
   \hline
@@
 
+\begin{itemize}
+	\item relationship to requirement
+	\item interoperability between constraint languages
+  \item express constraint in CL A and translate constraint in CL B
+  \item provide SPARQL validation (SPIN mapping) for each general C 
+\end{itemize}
+
 \section{Ideas}
@@
 
-fig:generic constraint language ontology.  
+We developed an ontology to describe any constraint language.
+We distinguish between two sub-types of \ms{constraint}: 
+\begin{itemize}
+	\item \ms{property constraints} and 
+	\item \ms{class constraints}. 
+\end{itemize}
+
+For both property and class constraints a context class, a list of classes, the constraining element, and the constraining value can be stated
+(see figure \ref{fig:generic-constraint-language-ontology}). Lists of left and right properties can only be stated for property constraints.
+
 \begin{figure}
 	\centering
-		\includegraphics[width=1.00\textwidth]{generic constraint language ontology/generic constraint language ontology.png}
+		\includegraphics[width=0.80\textwidth]{images/generic-constraint-language-ontology.png}
 	\caption{generic constraint language ontology}
-	\label{fig:generic constraint language ontology}
+	\label{fig:generic-constraint-language-ontology}
 \end{figure}
 
-terminology:
-\begin{itemize}
-	\item A "constraint" is an actual constraint, like dcterms:creator :hasMinCardinality "1" .
-  \item a "constraint language" like DSP is used to formulate constraints.
-  \item a constraint language consists of "constraint elements" like :hasMinCardinality (this is probably the most controverse definition).
-	\item class constraint: constraint on context class
-\end{itemize}
-
-\begin{itemize}
-	\item relationship to requirement
-  \item ontology describing constraint languages
-	\item interoperability between constraint languages
-  \item express constraint in CL A and translate constraint in CL B
-  \item provide SPARQL validation (SPIN mapping) for each general C 
-\end{itemize}
+In order to define this ontology, it is needed to define the terminology for the formulation of constraints. 
+A \ms{constraint language} is a language which is used to formulate constraints.
+The W3C Data Shapes WG defines \ms{constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
+A constraint holds for all individuals of a context class (\ms{contextClass}).
+Consider, e.g., the following cardinality restriction on the property \ms{commandsVessel}, which restricts that a captain must command at least one vessel: 
+\begin{DL}
+$Captain \sqsubseteq \geq1 commandsVessel . Vessel $
+\end{DL}
+Mapped to the GCLO the cardinality restriction is classified as a property constraint which holds for individuals of the class \ms{Captain} - the context class:
+\begin{gcotable}
+property & Captain & commandsVessel & - & Vessel & $\geq$ & 1 \\
+\end{gcotable}
+The constraining element (\ms{constrainingElement}) is the operator indicating the actual type of constraint like DL concept and role constructors, (in)equality, and further keywords for constrains which cannot be expressed in DL (e.g.
+regular expressions, constraining facets).
+In some cases, a constraint is only complete when in addition to the constraining element a constraining value (\ms{constrainingValue}) is stated.
+The cardinality restriction 
+\begin{DL}
+$\geq$1 commandsVessel . Vessel
+\end{DL}
+constructs an anonymous class of all individuals who command at least one vessel.
+Thus, the constraining element of this property constraint is the DL at-least restriction \ms{$\geq$} and the constraining value is \ms{1}.
+\ms{Classes} indicate the list of classes constraints refer to.
+In case of the property constraint above, the qualified cardinality restriction refers to the class \ms{Vessel}, 
+i.e., restricting the objects, the property \ms{commandsVessel} point to, to be of the class \ms{Vessel}.
 
@@
 
+\section{Constraints Not Expressible in DL}
+
+There are constraints which cannot be expressed by DL such as literal pattern matching, literal value comparison, literal ranges, default values, and language tag cardinality \cite{BoschNolleAcarEckert2015}.
+
+% maybe additional constraint default values:
+% ear shape of races, e.g. vulcans / teeth color
+
+There are multiple use cases associated with the requirement to match literals according to given patterns (\ms{Literal Pattern Matching} constraint).
+The enterprise vessel, e.g.,  can only have the registry numbers "NCC-1701", "NCC-1701-A", "NCC-1701-B", "NCC-1701-C", "NCC-1701-D", or "NCC-1701-E".
+The universal restriction part of this complex constraint can be expressed by OWL 2 DL:
+\ms{Enterprise $\sqsubseteq$ $\forall$ registryNumber.RegistryNumber}.
+The restriction of the datatype \ms{RegistryNumber}, however, cannot be expressed in DL, but OWL 2 DL can be used anyway to express the literal pattern matching constraint:
+
+\begin{ex}
+RegistryNumber
+    a rdfs:Datatype ;
+    owl:equivalentClass [
+        a rdfs:Datatype ;
+        owl:onDatatype xsd:string ;
+        owl:withRestrictions ( 
+            [ xsd:pattern "NCC-1701([-][A-E])?" ] ) ] .
+\end{ex}
+
+The second axiom defines \ms{RegistryNumber} as an abbreviation for a datatype restriction on \ms{xsd:string}. 
+The first axiom explicitly declares \ms{RegistryNumber} to be a datatype. 
+The datatype \ms{RegistryNumber} can be used just like any other datatype like in the universal restriction above.
+The literal pattern matching constraint validates \ms{RegistryNumber} literals according to the stated regular expression causing a constraint violation for the triples 
+\ms{Janeway commandsEnterprise Voyager} and \ms{Voyager registryNumber "NCC-74656"\textasciicircum{}\textasciicircum{}RegistryNumber}, 
+but not for the triples \ms{Picard commandsEnterprise Enterprise} and \ms{Enterprise registryNumber "NCC-1701-E"\textasciicircum{}\textasciicircum{}RegistryNumber}.
+The universal restriction and the literal pattern matching constraint are mapped to the generic constraint language as follows:
+
+\begin{gcotable}
+property & Enterprise & registryNumber & - & RegistryNumber & $\forall$ & - \\
+class & RegistryNumber & - & - & xsd:string & regex & 'NCC-1701([-][A-E])?' \\
+\end{gcotable}
+
+The \ms{Literal Pattern Matching} constraint introduces a new constraining element: \ms{regex}.
+For this new constraining element, an automatic validation must be implemented in SPIN.
+This has to be done once for each constraint which cannot be expressed in DL.
+
 \bibliography{../../literature/literature}{}

### 2014-12-28 paper/paper 2/paper 2.tex
ideas

@@
 %
-\title{XXXXX}
+\title{Formulating and Validating RDF Constraints Generically}
+%\subtitle{}
 %
@@
 %
-\author{XXXXX\inst{1} \and XXXXX\inst{2}}
+\author{Thomas Bosch\inst{1} \and X\inst{2} \and X\inst{2} \and X\inst{2} \and Kai Eckert\inst{2}}
 %
@@
 %%%% list of authors for the TOC (use if author list has to be modified)
-\institute{XXXXX\\
-\email{XXXXX},\\ 
+\institute{GESIS – Leibniz Institute for the Social Sciences, Germany\\
+\email{thomas.bosch@gesis.org},\\ 
 \and
-XXXXX \\
-\email{XXXXX} 
+University of Mannheim, Germany \\
+\email{\{kai\}@informatik.uni-mannheim.de} 
 }
@@
 
-\section{Notes}
+\begin{itemize}
+	\item requirements database
+	\item relationship between requirements and constraints
+\end{itemize}
+
+\section{Ideas}
 
 \begin{itemize}
-	\item requirements / constraints mapped to DL
-	\item requirements / constraints which cannot be mapped to DL
-	\item syntactic sugar for some constraints
-	\item complex constraints encompass complex constraints and simple constraints
-	\item DL statements of complex constraints are created out of DL statements of composed constraints 
-	\item define terminology for RDF constraints
+	\item the majority of specific constraints expressed by any specific constraint language can be expressed by DL
+	\item each DL statement can be expressed by a generic constraint using a generic constraint language
+\end{itemize}
+
+purpose:
+\begin{itemize}
+	\item translations of specific constraints expressed by any specific constraint language
+	\item we do not invent a new constraint languages
+\end{itemize}
+
+%constraint design patterns:
+% - ontology design pattern.org
+% - DSP uses other design pattern
+% - constraint elements are the same / 
+% - constraint / constraint elements / constraint design patterns / constraint language
+
+%dependency between requirements / when this requirements is fulfilled then this is also fulfilled (e.g. min card and requ. car)
+%min car more powerful than req. propery
+
+\begin{itemize}
+	\item any specific constraint (expressed by specific constraint language) must be mapped to a generic constraint (expressed by GCL)
 \end{itemize}
@@
 Our \textbf{contributions} of this paper are:
-\begin{enumerate}
+\begin{itemize}
 	\item each constraint (expressed by any DSCL) can be validated automatically
 	\item any specific constraint (expressed by any DSCL) can be transformed into a generic constraint (expressed by a generic constraint language)
+	\item We define the terminology for RDF constraints
 	\item we developed an ontology describing any constraint language
-\end{enumerate}
+\end{itemize}
 
@@
 
-\section{Ideas}
+\section{An Ontology Describing RDF Constraints Generically}
 
-idea:
-\begin{itemize}
-	\item each specific constraint expressed using any domain specific language can be expressed as DL constraint using DL
-	\item each DL constraint can be expressed as generic constraint using generic constraint language
-	\item meta-model based ontology describing constraints
-	\item possible limitation: maybe only typical constraints
-\end{itemize}
-
-purpose:
-\begin{itemize}
-	\item translations of constraints expressed using any domain specific constraint language
-\end{itemize}
-
-contributions:
-\begin{itemize}
-	\item 
-\end{itemize}
-
-assumption:
-\begin{itemize}
-	\item CWA
-\end{itemize}
-
-ontology design pattern.org
-constraint grammar
-constraint elements are the same
-DSP uses other design pattern / 
-constraint / constraint elements / constraint design patterns / constraint language
-define terminology
-related to requirements DB / relate requirements to constraints, constraint languages
-constraint element: e.g. min cardinality
-dependency between requirements / when this requirements is fulfilled then this is also fulfilled (e.g. min card and requ. car)
-min car more powerful than req. propery
-why ontology? automatic translation from DSP to OWL 
-define general constraint language
-we do not invent a new constraint languages
-requirements in SPARQL umsetzten
-only one validation for each requirement
-constraints may be composed
-
-\begin{itemize}
-	\item any specific constraint (expressed by DSCL) must be mapped to a generic constraint (expressed by GCL)
-\end{itemize}
-
-\section{An Ontology Describing Constraint Languages}
-
-We developed an ontology to describe any constraint language.
+We developed a very simple ontology (three classes, three object properties, and three data properties) which is universal enough to describe any RDF constraint expressible by any RDF constraint language.
 We distinguish between two sub-types of \ms{constraint}: 
@@
 
+Complex constraints encompass complex constraints and simple constraints.
+DL statements of complex constraints are created out of DL statements of composed constraints.
+
 \subsection{Disjoint Classes}
@@
 
+\begin{itemize}
+	\item syntactic sugar for some constraints
+\end{itemize}
+
 In Section 1.3 we introduced three forms of RBox axioms: role inclusions, role equiv-
@@
   \item domain and range
+	\item Primary Key Properties
 	\item (ir)reflexive object properties
@@
 \end{itemize}
+
+\section{Constraints Expressible in DL}
 
@@
 
+\section{Implementation}
+
+\section{Limitations}
+
+\begin{itemize}
+	\item in order to transform specific constraint languages, there must be a concrete syntax in RDF
+\end{itemize}
+
+\section{Related Work}
+
+\section{Conclusion and Future Work}
+
 \bibliography{../../literature/literature}{}

### 2014-12-28 paper/paper 2/paper 2.tex
motivation

@@
 \urlstyle{same}
+
+% footnotes
+\usepackage{scrextend}
 
@@
 	\item relationship between requirements and constraints
+	\item constraint languages
 \end{itemize}
@@
 
-At-least restrictions can be expressed either generically by description logics (DL) or specifically by domain-specific constraint languages (DSCL) such as OWL 2, DSP, and ShEx.
-With at-least restrictions we can state that having at least 2 female childs is equivalent to having at least 2 daughters. This axiom may be represented by DL in a logical way:
+Cardinality restrictions can be expressed either generically by description logics (DL) (\ms{generic constraints}) and additional constraints or specifically (\ms{specific constraints}) by domain-specific constraint languages such as OWL 2, DSP, ShEx, ReSh, and SPIN.
+With minimum qualified cardinality restrictions we can state, e.g., that a star fleet captain commands at least one vessel, which may be represented by DL in a logical way:
 
-\begin{align*}
-Having2Daughters \equiv \geq 2 hasChild.Woman
-\end{align*}
+\begin{DL}
+$StarFleetCaptain \sqsubseteq \geq1 commandsVessel . Vessel $
+\end{DL}
 
-The same axiom may also be represented by different DSCLs like OWL 2, DSP, and ShEx:
+The same constraint may also be represented by different constraint languages like OWL 2, ShEx, ReSh, or DSP:
 
@@
 # -----
-:Having2Daughters
+StarFleetCaptain
     a owl:Restriction ;
-    owl:minQualifiedCardinality "2"^^xsd:nonNegativeInteger ;
-    owl:onProperty :hasChild ;
-    owl:onClass :Woman .
+    owl:minQualifiedCardinality 1 ;
+    owl:onProperty commandsVessel ;
+    owl:onClass Vessel .
+
+# ShEx
+# ----
+StarFleetCaptain { commandsVessel @Vessel{1, } }
+
+# ReSh
+# ----
+StarFleetCaptain a rs:ResourceShape ; rs:property [
+    rs:name "commandsVessel" ; rs:propertyDefinition commandsVessel ;
+    rs:valueShape Vessel ;
+    rs:occurs rs:One-or-many ; ] .
 
@@
 # ---			
-:descriptionTemplate 
-    a dsp:DescriptionTemplate ; 
-    dsp:resourceClass :Having2Daughters ; 
-    dsp:statementTemplate [
-        a dsp:NonLiteralStatementTemplate ;
-        dsp:minOccur "1"^^xsd:nonNegativeInteger ; 
-        dsp:maxOccur "infinity"^^xsd:string ; 
-        dsp:property :hasChild ; 
-        dsp:nonLiteralConstraint [ 
-            a dsp:NonLiteralConstraint ;
-            dsp:valueClass :Woman ] ] .
-
-# ShEx
-# ----
-<Having2Daughters> {         
-    :hasChild @<Woman>{2, }
-}
-<Woman> {         
-    rdf:type (:Woman)
-}
+descriptionTemplate a dsp:DescriptionTemplate ; 
+    dsp:resourceClass StarFleetCaptain ; 
+    dsp:statementTemplate [ a dsp:NonLiteralStatementTemplate ;
+        dsp:minOccur 1 ; dsp:maxOccur "infinity" ; 
+        dsp:property commandsVessel ; 
+        dsp:nonLiteralConstraint [ a dsp:NonLiteralConstraint ;
+            dsp:valueClass Vessel ] ] .
 \end{ex}
 
-Data, which is valid according to the specified at-least restriction, looks like this:
+As \ms{Janeway} commands the vessel \ms{Voyager} (\ms{commandsVessel(Janeway,Voyager)}) and \ms{Voyager} is defined to be a \ms{Vessel} (\ms{rdf:type(Voyager,Vessel)}), the assignment of \ms{Janeway} to the class \ms{StarFleetCaptain} (\ms{rdf:type(Janeway,StarFleetCaptain)}) does not cause any constraint violation.
+A constraint violation is raised, however, when there is no \ms{commandsVessel} relationship pointing from the individual \ms{Janeway}. 
+A constraint violation is also raised, when there is a triple \ms{commandsVessel(Janeway,Voyager)}, but \ms{Voyager} is not explicitly defined to be a \ms{Vessel}, 
+i.e. the triple \ms{rdf:type(Voyager,Vessel)} is not present in the data. 
+As the object of the \ms{commandsVessel} property is assigned to another class than \ms{Vessel}, 
+the triples \ms{commandsVessel(Sisko,DS9)}, \ms{rdf:type(Sisko,StarFleetCaptain)}, and \ms{rdf:type(DS9,SpaceStation)}  
+also cause a constraint violation.
 
-\begin{ex}
-:Marge
-    a :Having2Daughters , :Woman ;
-    :hasChild :Maggie , :Lisa .
-:Maggie
-    a :Woman .
-:Lisa
-    a :Woman .
-\end{ex}
+As there is no standard constraint language, constraint designers may choose different constraint languages to express the identical cardinality restriction. 
+When constraint designers choose one constraint language to express an arbitrary constraint, it should be possible to transform this constraint into a constraint expressed by any other constraint language.
+This is important as it is often the case that one constraint designer knows to read and to write constraints in one constraint language very well but not in another constraint language. 
+This way, constraint designers may communicate with each other without the necessity to understand all constraint languages and the interoperability of constraint languages is enhanced.
 
-If :Marge has only 1 child and if :Marge is assigned to the class :Having2Daughters, a constraint violation is raised for the following invalid data:
+There are validation environments available enabling to automatically validate RDF constraints expressed by just a few constraint languages such as OWL 2\footnote{\url{purl.org/net/rdfval-demo}\label{footnote1}}, DSP\footref{footnote1}, and ShEx\footnote{\url{http://www.w3.org/2013/ShEx/FancyShExDemo}}.
+It should be possible to validate any RDF constraints expressed by any constraint language automatically and what is even more important in exactly the same manner without any differences.
 
-\begin{ex}
-:Marge
-    a :Having2Daughters , :Woman ;
-    :hasChild :Lisa .
-:Lisa
-    a :Woman .
-\end{ex}
-
-As there is no standard constraint language, constraint designers may choose different DSCLs in order to express the same at-least restriction. 
-When constraint designers choose one DSCL in order to express an arbitrary constraint, it should be possible to transform this constraint into a constraint expressed by any other DSCL. 
-This is important as it is often the case that one constraint designer knows to read and to write constraints in one DSCL very well but not in another DSCL. 
-This way, constraint designers may communicate with each other without the necessity to understand the other DSCL.
-
-There are validation environments available enabling to automatically validate any RDF constraints expressed by just a few DSCL such as OWL 2 and DSP.
-But it should be possible to validate any RDF constraints expressed by any DSCL automatically and what is even more important in the same manner without any differences.
-
-The following table contains the mapping between the at-least restriction expressed by description logics and the at-least restriction expressed by a generic constraint language conforming to an ontology describing constraint languages.
+The following table shows the mapping between the cardinality restriction expressed in DL and the cardinality restriction (\ms{generic constraint}) expressed by a generic constraint language conforming to an ontology to describe any RDF constraint generically (see section~\ref{sec:ontology}).
 Each constraint is either a constraint on classes or a constraint on properties.
@@
 \begin{gcotable}
-property & Having2Daughters & hasChild & - & Woman & $\geq$ & 2 \\
+property & Captain & commandsVessel & - & Vessel & $\geq$ & 1 \\
 \end{gcotable}
 
-The at-least restriction (expressed by the generic constraint language) is represented in RDF as follows:
+The cardinality restriction (expressed by the generic constraint language) is represented in RDF as follows:
 
 \begin{ex}
-:minCardinalityConstraint
-    a gclo:PropertyConstraint ;
-    gclo:contextConcept :Having2Daughters ;
-    gclo:propertyList ( :hasChild ) ;
-    gclo:concept :Woman ;
-    gclo:constrainingElement "\geq" ;
-    gclo:constrainingValue "2" .
+[   a PropertyConstraint ;
+    contextClass StarFleetCaptain ;
+    leftProperties ( commandsVessel ) ;
+    classes ( Vessel ) ;
+    constrainingElement ">=" ;
+    constrainingValue "1" ] .
 \end{ex}
 
-We implement an automatic validation for any constraint expressed by a generic constraint language conforming to an ontology describing constraint languages.
-If we transform a specific constraint (expressed by any DSCL) into a generic constraint (expressed by the generic constraint language), we will be able to validate the generic constraint and therefore the specific constraint immediately.
-As a consequence, we do not have to specify an automatic validation for each specific constraint, as we need to define an automatic validation once for each generic constraint.
-The underlying SPARQL query is executed within the SPIN validation environment:
+We implemented the automatic validation for the cardinality restriction expressed by the generic constraint language within our SPIN validation environment (see SPARQL query above):
 
@@
 # ----------
-?propertyConstraint
-    a gclo:PropertyConstraint ;
-    gclo:contextConcept ?contextConcept ;
-    gclo:propertyList ( ?property ) ;
-    gclo:concept ?concept ;
-    gclo:constrainingElement ?constrainingElement ;
-    gclo:constrainingValue ?constrainingValue .
+[   a PropertyConstraint ;
+    contextClass ?cc ;
+    leftProperties ( ?p1 ) ;
+    classes ( ?c1 ) ;
+    constrainingElement ">=" ;
+    constrainingValue ?cv ] .
 
@@
 # ----
-?this ?property ?o .
-?this rdf:type ?contextConcept .
+?subject rdf:type ?cc .
 
-# validation ( at-least restriction )
+# validation
 # -----
-FILTER ( ?constrainingElement = "\geq" ) .
-BIND ( owl2spin:qualifiedCardinality( ?this, ?property, ?concept ) AS ?c ) .
-BIND( STRDT ( STR ( ?constrainingValue ), xsd:nonNegativeInteger ) AS ?MinimumCardinality )
-BIND( STRDT ( STR ( ?c ), xsd:nonNegativeInteger ) AS ?cardinality )
-FILTER ( ?cardinality < ?MinimumCardinality ) .		  
+BIND ( qualifiedCardinality( ?subject, ?p1, ?c1 ) AS ?c ) .
+FILTER ( ?c < ?cv ) .		  
 \end{ex}
+
+If we transform a specific constraint (expressed by any constraint language) into a generic constraint (expressed by the generic constraint language), we will be able to validate the generic constraint and therefore the specific constraint immediately.
+As a consequence, we do not have to specify an automatic validation for each specific constraint, as we need to define an automatic validation only once for each generic constraint. 
+We have to provide an automatic validation for each generic constraint in order to support the automatic validation for each specific constraint.
 
@@
 these constraints can be either mapped to either a specific or a generic constraint, as for both an automatic validation is provided in the background.    
-So, the user does not have to know how to express specific constraints using a DSCL such as OWL 2, DSP, or ShEx.
-If there is a new constraint not covered by any DSCL you can just define the automatic validation for this newly defined constraint.
-This way, you are able to extend existing DSCL and to define new DSCL if existing DSCLs are not sufficient for further use cases.
+So, the user does not have to know how to express specific constraints using a constraint language such as OWL 2, DSP, or ShEx.
+If there is a new constraint not covered by any constraint language you can just define the automatic validation for this newly defined constraint.
+This way, you are able to extend existing constraint language and to define new constraint language if existing constraint languages are not sufficient for further use cases.
 
-Our \textbf{contributions} of this paper are:
+The \textbf{contributions} of this paper are:
 \begin{itemize}
-	\item each constraint (expressed by any DSCL) can be validated automatically
-	\item any specific constraint (expressed by any DSCL) can be transformed into a generic constraint (expressed by a generic constraint language)
-	\item We define the terminology for RDF constraints
-	\item we developed an ontology describing any constraint language
+	%\item Any specific constraint (expressed by any constraint language) can be transformed into a generic constraint (expressed by the generic constraint language)
+	%\item Any specific constraint (expressed by any constraint language A) can be transformed into any specific constraint (expressed by any constraint language B)
+	%\item Any specific constraint (expressed by any constraint language) can be validated automatically (if an automatic validation is defined only once for corresponding generic constraint)
+	\item We define a terminology for RDF constraints and constraining languages
+	\item We developed an ontology describing any RDF constraint which can also be expressed by any constraint language
+	\item We show how ...
+\end{itemize}
+
+The \textbf{benefits} of our framework are:
+\begin{itemize}
+	\item Any specific constraint (expressed by any constraint language) can be transformed into a generic constraint (expressed by the generic constraint language)
+	\item Any specific constraint (expressed by any constraint language A) can be transformed into any specific constraint (expressed by any constraint language B)
+	\item Any specific constraint (expressed by any constraint language) can be validated automatically (if an automatic validation is defined only once for corresponding generic constraint)
 \end{itemize}
@@
 \begin{itemize}
-	\item GCL with only 6 elements
-	\item if a language designer develops a new DSCL the language designer only needs to define a mapping between the new DSCL and the GCLO 
-	in order to be able to automatically validate the new DSCL constraints
+	\item if a language designer develops a new constraint language the language designer only needs to define a mapping between the new constraint language and the GCLO 
+	in order to be able to automatically validate the new constraint language constraints
 \end{itemize}
@@
 \begin{itemize}
-	\item relationship to requirement
-	\item interoperability between constraint languages
   \item express constraint in CL A and translate constraint in CL B
-  \item provide SPARQL validation (SPIN mapping) for each general C 
 \end{itemize}
 
+\textcolor{red}{paper organization}
+
 \section{An Ontology Describing RDF Constraints Generically} 
+\label{sec:ontology}
 

### 2014-12-28 paper/paper 2/paper 2.tex
motivation

@@
 
-When domain experts use graphical user interfaces to define constraints in a user-friendly way, 
-these constraints can be either mapped to either a specific or a generic constraint, as for both an automatic validation is provided in the background.    
-So, the user does not have to know how to express specific constraints using a constraint language such as OWL 2, DSP, or ShEx.
-If there is a new constraint not covered by any constraint language you can just define the automatic validation for this newly defined constraint.
-This way, you are able to extend existing constraint language and to define new constraint language if existing constraint languages are not sufficient for further use cases.
+When domain experts use graphical user interfaces to define constraints in a user-friendly way (without the necessity to express constraints on their own), 
+constraints can be mapped to either a specific or a generic constraint, as for both an automatic validation is provided in the background.    
+So, the user does not have to know how to express specific constraints using any constraint language.
+If there is a new constraint not covered by any existing constraint language, one can just define the automatic validation for a corresponding generic constraint.
+This way, one is able to extend existing constraint languages and also to define new constraint languages if existing constraint languages are not sufficient to express particular constraints.
+If a language designer develops a new constraint language, 
+the language designer only needs to define a mapping between the new constraint language and the generic constraint language
+in order to be able to automatically validate the constraints expressible by the new constraint language.
 
@@
 	\item We developed an ontology describing any RDF constraint which can also be expressed by any constraint language
-	\item We show how ...
+	\item We present that any RDF constraint can be described by the developed ontology - whether the constraint can be expressed in DL or not 
+	\item We show how to transform specific constraints (expressed by any constraint language A) into generic constraints and into specific constraints (expressed by any other constraint language B)
+  \item We explain that any specific constraint can be validated automatically (if an automatic validation is defined only once for corresponding generic constraint)
 \end{itemize}
 
-The \textbf{benefits} of our framework are:
-\begin{itemize}
-	\item Any specific constraint (expressed by any constraint language) can be transformed into a generic constraint (expressed by the generic constraint language)
-	\item Any specific constraint (expressed by any constraint language A) can be transformed into any specific constraint (expressed by any constraint language B)
-	\item Any specific constraint (expressed by any constraint language) can be validated automatically (if an automatic validation is defined only once for corresponding generic constraint)
-\end{itemize}
-
-Benefits:
-\begin{itemize}
-	\item if a language designer develops a new constraint language the language designer only needs to define a mapping between the new constraint language and the GCLO 
-	in order to be able to automatically validate the new constraint language constraints
-\end{itemize}
-
-\begin{itemize}
-  \item express constraint in CL A and translate constraint in CL B
-\end{itemize}
+%The \textbf{benefits} of our framework are:
+%\begin{itemize}
+	%\item Any specific constraint (expressed by any constraint language) can be transformed into a generic constraint (expressed by the generic constraint language)
+	%\item Any specific constraint (expressed by any constraint language A) can be transformed into any specific constraint (expressed by any constraint language B)
+	%\item Any specific constraint (expressed by any constraint language) can be validated automatically (if an automatic validation is defined only once for corresponding generic constraint)
+%\end{itemize}
 
@@
 
+\section{Transformations between Specific Constraints}
+
+\section{Automatic Validation of Specific Constraints}
+
 \section{Constraints Expressible in DL}

### 2014-12-29 paper/paper 2/paper 2.tex
Context-Specific Exclusive OR of Property Groups

@@
 
-Complex constraints encompass complex constraints and simple constraints.
+\ms{Complex constraints} encompass complex constraints and \ms{simple constraints} (atomic constraints).
 DL statements of complex constraints are created out of DL statements of composed constraints.
+
+\textbf{Context-Specific Exclusive OR of Property Groups}\footnote{corresponds to R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC}\textbf{.}
+Exclusive or is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
+Only one of multiple property groups should be present in the data.
+Half-Klingons, e.g., either have a klingon mother and a human father or a human mother and a klingon father, which can be expressed by ShEx:
+
+\begin{ex}
+Half-Klingon { 
+    ( klingonMother Klingon , humanFather Human ) |
+    ( humanMother Human , klingonFather Klingon ) }
+\end{ex}
+
+As \ms{B'Elanna Torres} is a \ms{Half-Klingon} with a klingon mother and a human father, this data is valid:
+
+\begin{ex}
+BElannaTorres a Half-Klingon ;
+    klingonMother Miral ; humanFather JohnTorres .
+\end{ex}
+
+%\begin{DL}
+%rdf:type(BElannaTorres,Half-Klingon) \\
+%klingonMother(BElannaTorres,Miral) \\
+%klingonMother(BElannaTorres,JohnTorres)
+%\end{DL}
+
+This complex constraint can be mapped to DL:
+
+\begin{DL}
+Half-Klingon $\sqsubseteq$ ($\neg$E $\sqcap$ F) $\sqcup$ (E $\sqcap$ $\neg$F) \\ 
+E $\equiv$ A $\sqcap$ B \\
+F $\equiv$ C $\sqcap$ D \\
+A $\sqsubseteq$ $\geq$ 1 klingonMother.Klingon $\sqcap$ $\leq$ 1 klingonMother.Klingon \\
+B $\sqsubseteq$ $\geq$ 1 humanFather.Human $\sqcap$ $\leq$ 1 humanFather.Human \\
+C $\sqsubseteq$ $\geq$ 1 humanMother.Human $\sqcap$ $\leq$ 1 humanMother.Human \\
+D $\sqsubseteq$ $\geq$ 1 klingonFather.Klingon $\sqcap$ $\leq$ 1 klingonFather.Klingon \\
+\end{DL}
+
+The constraint expressed by DL can be mapped to a generic constraint:
+
+\begin{gcotable}
+class & Half-Klingon & - & - & $\neg$E $\sqcap$ F, E $\sqcap$ $\neg$F & $\sqcup$ & - \\
+class & $\neg$E $\sqcap$ F & - & - & $\neg$E, F & $\sqcap$ & - \\
+class & E $\sqcap$ $\neg$F & - & - & E, $\neg$F & $\sqcap$ & - \\
+class & $\neg$E & - & - & E & $\neg$ & - \\
+class & E & - & - & A, B & $\sqcap$ & - \\
+class & $\neg$F & - & - & F & $\neg$ & - \\
+class & F & - & - & C, D & $\sqcap$ & - \\
+class & A & - & - & A1, A2 & $\sqcap$ & - \\
+property & A1 & klingonMother & - & Klingon & $\geq$ & 1 \\
+property & A2 & klingonMother & - & Klingon & $\leq$ & 1 \\
+class & B & - & - & B1, B2 & $\sqcap$ & - \\
+property & B1 & humanFather & - & Human & $\geq$ & 1 \\
+property & B2 & humanFather & - & Human & $\leq$ & 1 \\
+class & C & - & - & C1, C2 & $\sqcap$ & - \\
+property & C1 & humanMother & - & Human & $\geq$ & 1 \\
+property & C2 & humanMother & - & Human & $\leq$ & 1 \\
+class & D & - & - & D1, D2 & $\sqcap$ & - \\
+property & D1 & klingonFather & - & Klingon & $\geq$ & 1 \\
+property & D2 & klingonFather & - & Klingon & $\leq$ & 1 \\
+\end{gcotable}
+
+Even though, tools may generate generic constraints automatically, this complex constraint is composed of many other complex (e.g.
+minimum and maximum qualified cardinality restrictions) and simple constraints (e.g.
+constraints on sets).
+As \ms{exact (un)qualified cardinality restrictions} and \ms{exclusive or} are frequently used complex constraints,
+we propose using them as simple constraints - 	in terms of syntactic sugar.
+As a consequence, the \ms{Context-Specific Exclusive OR of Property Groups} constraint above is represented as a generic constraint more intuitively and concisely:
+
+\begin{gcotable}
+class & Half-Klingon & - & - & E, F & XOR \\
+class & E & - & - & A, B & $\sqcap$ \\
+class & F & - & - & C, D & $\sqcap$ \\
+property & A & klingonMother & - & Klingon & = & 1 \\
+property & B & humanFather & - & Human & = & 1 \\
+property & C & humanMother & - & Human & = & 1 \\
+property & D & klingonFather & - & Klingon & = & 1 \\
+\end{gcotable}
 
@@
 	\item (ir)reflexive object properties
-	\item Exact Qualified Cardinality Restrictions on Properties
+	\item ( Exact Qualified Cardinality Restrictions on Properties )
 \end{itemize}
+
+\textbf{Context-Specific Exclusive OR of Property Groups.}
+\begin{gcotable}
+class & Half-Klingon & - & - & E, F & XOR \\
+class & E & - & - & A, B & $\sqcap$ \\
+class & F & - & - & C, D & $\sqcap$ \\
+property & A & klingonMother & - & Klingon & = & 1 \\
+property & B & humanFather & - & Human & = & 1 \\
+property & C & humanMother & - & Human & = & 1 \\
+property & D & klingonFather & - & Klingon & = & 1 \\
+\end{gcotable}
 

### 2014-12-29 paper/RDF validation requirements/RDF validation requirements.tex
Context-Specific Exclusive OR of Property Groups
evaluation

@@
 property & $\exists$ laserSwordColor . LaserSwordColor & laserSwordColor & - & LaserSwordColor & $\exists$ & - \\
-class & Jedi & - & - & $\exists$ laserSwordColor . LaserSwordColor & $\neg$ & - \\
+class & Sith & - & - & $\exists$ laserSwordColor . LaserSwordColor & $\neg$ & - \\
 class & LaserSwordColor & - & - & $\{blue\}$, $\{green\}$, $\{white\}$ & $\sqcup$ & - \\
@@
 
+Define the order of the property \ms{listElement} for the class \ms{rdf:List}.
+List elements are of datatype \ms{xsd:string}.
+
 \begin{DL}
@@
 \end{DL}
+
+\begin{gcotable}
+property & rdf:List & listElement & - & xsd:string & order & 1 \\
+\end{gcotable}
 
@@
 
+The length of strings of the property \ms{hasISBN} for the context class \ms{Book} must be exactly 3.
+
 \begin{DL}
@@
 
+\begin{gcotable}
+property & Book & hasISBN & - & xsd:string & length & 3 \\
+\end{gcotable}
+
 \section{Context-Specific Valid Classes}
@@
 
-I'm not sure about the meaning of this constraint, but for me this seams like e.g. the range of a role... but if this is the case, take into account the consequences of reasoning with OWA...
+Within the context \ms{AP} (application profile) the classes \ms{Book} and \ms{Paper} are valid.
+
+\begin{DL}
+Not expressible in DL!
+\end{DL}
+
+\begin{gcotable}
+class & AP & - & - & Book, Paper & context-specific valid classes & true \\
+\end{gcotable}
 
@@
 
-I'm not sure about the meaning of this constraint, but for me this seams like e.g. the domain of a role... but if this is the case, take into account the consequences of reasoning with OWA...
+Within the context \ms{AP} (application profile) the properties \ms{dcterms:subject} and \ms{dcterms:title} are invalid.
+
+\begin{DL}
+Not expressible in DL!
+\end{DL}
+
+\begin{gcotable}
+property & AP & dcterms:subject, dcterms:title & - & - & context-specific valid properties & false \\
+\end{gcotable}
 
@@
 
-\begin{DL}
-Not Expressible in DL!
-\end{DL}
+Calculate rectangle areas.
+
+\begin{DL}
+Not expressible in DL!
+\end{DL}
+
+\begin{gcotable}
+property & Rectangle & area & width, height & xsd:integer & multiplication & - \\
+\end{gcotable}
 
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-68-REQUIRED-PROPERTIES
-\end{itemize}
-
-\subsection{Simple Example}
+\ms{Required Properties} corresponds to the requirement \ms{R-68-REQUIRED-PROPERTIES}.
+
+\subsection{Simple Example}
+
+For persons the property \ms{hasAncestor} has to be stated pointing to persons.
 
@@
 
+\begin{gcotable}
+property & Person & hasAncestor & - & Person & $\exists$ & - \\
+\end{gcotable}
+
 \section{Optional Properties}
 
-requirements:
-
-\begin{itemize}
-	\item R-69-OPTIONAL-PROPERTIES
-\end{itemize}
-
-\subsection{Simple Example}
+\ms{Optional Properties} corresponds to the requirement \ms{R-69-OPTIONAL-PROPERTIES}.
+
+\subsection{Simple Example}
+
+For persons the property \ms{hasAncestor} pointing to persons is optional.
 
@@
 Same as the definition of domains.
+
+\begin{gcotable}
+property & $\exists$ hasAncestor.Person & hasAncestor & - & Person & $\exists$ & - \\
+class & Person & - & - & $\exists$ hasAncestor.Person & $\sqsubseteq$ & - \\
+\end{gcotable}
+
+syntactic sugar:
+
+\begin{gcotable}
+property & Person & hasAncestor & - & Person & optional & - \\
+\end{gcotable}
 

### 2014-12-29 paper/paper 2/paper 2.tex
evaluation

@@
 }{
+  \end{tabular}
+	\end{center}
+}
+
+\newenvironment{evaluation}{
+  %\scriptsize
+  %\sffamily
+  %\vspace{0.3cm}
+	\begin{center}
+  \begin{tabular}{l|c|c|c|c|c|c}
+  \hline
+  \textbf{Constraint Class} & \textbf{DSP} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
+  \hline
+
+}{
+  \hline
   \end{tabular}
@@
 
-\ms{Complex constraints} encompass complex constraints and \ms{simple constraints} (atomic constraints).
+\ms{Complex constraints} encompass complex constraints and/or \ms{simple constraints} (atomic constraints).
 DL statements of complex constraints are created out of DL statements of composed constraints.
@@
 
-\textbf{Context-Specific Exclusive OR of Property Groups.}
-\begin{gcotable}
-class & Half-Klingon & - & - & E, F & XOR \\
-class & E & - & - & A, B & $\sqcap$ \\
-class & F & - & - & C, D & $\sqcap$ \\
-property & A & klingonMother & - & Klingon & = & 1 \\
-property & B & humanFather & - & Human & = & 1 \\
-property & C & humanMother & - & Human & = & 1 \\
-property & D & klingonFather & - & Klingon & = & 1 \\
-\end{gcotable}
-
 \section{Transformations between Specific Constraints}
@@
 
-\section{Constraints Expressible in DL}
+\section{Simple Constraints Not Expressible in DL}
 
-\section{Constraints Not Expressible in DL}
-
-There are constraints which cannot be expressed by DL such as literal pattern matching, literal value comparison, literal ranges, default values, and language tag cardinality \cite{BoschNolleAcarEckert2015}.
+There are simple constraints which cannot be expressed by DL such as literal pattern matching, literal value comparison, literal ranges, default values, and language tag cardinality \cite{BoschNolleAcarEckert2015}.
 
@@
 % ear shape of races, e.g. vulcans / teeth color
+% mathematical operations
 
@@
 
+\section{Evaluation}
+
+We evaluated to which extend the most promising five constraint languages fulfill each requirement to formulate RDF constraints \cite{BoschNolleAcarEckert2015}.
+If a constraint can be expressed in DL, we added the mapping to DL and to the generic constraint.
+If a constraint cannot be expressed in DL, we added a mapping to the generic constraint.
+Therefore, we show that each constraint can be mapped to a generic constraint.
+
+\begin{evaluation}
+\ms{Expr-C} (41) & 6 & 18(4) & 7(4) & 8 & 12 & 40(1)\\
+\ms{Expr-R} (33) & 8 & 29 & 11 & 11(2) & 11(1) & 33 \\ 
+\end{evaluation}
+
 \section{Related Work}

### 2014-12-30 paper/RDF validation requirements/RDF validation requirements.tex
evaluation of paper 2

@@
   \textbf{constraint} & \textbf{DSP} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
+  \hline
+
+}{
+  \hline
+  \end{tabular}
+  \linebreak
+	\end{center}
+}
+
+\newenvironment{evaluation-generic}{
+  \scriptsize
+  \sffamily
+  \vspace{0.3cm}
+	\begin{center}
+  \begin{tabular}{l|c|c|c}
+  \hline
+  \textbf{constraint} & \textbf{property c.} & \textbf{simple c.} & \textbf{DL} \\
+  \hline
+
+}{
+  \hline
+  \end{tabular}
+  \linebreak
+	\end{center}
+}
+
+\newenvironment{evaluation-generic-overview}{
+  \scriptsize
+  \sffamily
+  \vspace{0.3cm}
+	\begin{center}
+  \begin{tabular}{l|c|c}
+  \hline
+  \textbf{Constraint Classes} & \textbf{\#} & \textbf{\%} \\
   \hline
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-70-REPEATABLE-PROPERTIES
-\end{itemize}
-
-\subsection{Simple Example}
+\ms{Repeatable Properties} corresponds to the requirement \ms{R-70-REPEATABLE-PROPERTIES}.
+
+\subsection{Simple Example}
+
+The property \ms{commandsVessel} is repeatable for individuals of the class \ms{Captain}.
+
+\begin{DL}
+$Captain \sqsubseteq \geq1 commandsVessel.\top $
+\end{DL}
+
+\begin{gcotable}
+property & Captain & commandsVessel & - & $\top$ & $\geq$ & 1 \\
+\end{gcotable}
+
+syntactic sugar:
+
+\begin{gcotable}
+property & Captain & commandsVessel & - & $\top$ & repeatable & - \\
+\end{gcotable}
 
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-71-CONDITIONAL-PROPERTIES
-\end{itemize}
-
-\begin{itemize}
-	\item various conditions possible
-  \item condition: universal quantification on object and data properties
-  \item condition: existential quantification on object and data properties
-  \item condition: if specific properties are present, then specific other properties also have to be present
-\end{itemize}
-
-\subsection{Simple Example}
+\ms{Conditional Properties} corresponds to the requirement \ms{R-71-CONDITIONAL-PROPERTIES}.
+
+Multiple conditions are possible:
+
+\begin{itemize}
+  \item universal quantification on object and data properties,
+  \item existential quantification on object and data properties,
+  \item if specific properties are present, then specific other properties also have to be present
+\end{itemize}
+
+\subsection{Simple Example}
+
+If an individual has a \ms{parentOf} property relationship, then this individual also has a \ms{ancestorOf} property relationship.
+
+\begin{DL}
+parentOf $\sqsubseteq$ ancestorOf 
+\end{DL}
+
+\begin{gcotable}
+property & $\top$ & parentOf & ancestorOf & $\top$ & $\sqsubseteq$ \\
+\end{gcotable}
 
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-72-RECOMMENDED-PROPERTIES
-\end{itemize}
+\ms{Recommended Properties} corresponds to the requirement \ms{R-72-RECOMMENDED-PROPERTIES}.
 
@@
 
-\begin{itemize}
-	\item get 2. list element
-\end{itemize}
+get 2. list element
 
@@
 
+\subsection{Simple Example}
+
+Append a string list element 'list element' to a list the property \ms{p} of the class \ms{C} is pointing to.
+
+\begin{DL}
+Not expressible in DL!
+\end{DL}
+
+\begin{gcotable}
+property & C & p & - & xsd:string & append list element & 'list element' \\
+\end{gcotable}
+
 \section{Recursive Queries}
@@
 # ----
-<IssueShape> {
-    :related @<IssueShape>*
+IssueShape {
+    related @IssueShape*
 }
@@
 \begin{DL}
-Not expressible in DL!
-\end{DL}
+$IssueShape \sqsubseteq \geq1 related.IssueShape $
+\end{DL}
+
+\begin{gcotable}
+property & IssueShape & related & - & IssueShape & $\geq$ & 1 \\
+\end{gcotable}
 
@@
 
-\begin{DL}
-Not sure if this is expressible in DL, I think not!
-\end{DL}
-
-\an{not sure!}
+\subsection{Simple Example}
+
+If dc:date and one of its sub-properties dcterms:created or dcterms:issued are present, check that the value in dc:date is not redundant with dcterms:created or dcterms:issued for ingestion
+
+\begin{DL}
+Not expressible in DL!
+\end{DL}
+
+\begin{gcotable}
+property & $\top$ & dc:date & dcterms:created, dcterms:issued & - & not redundant & - \\
+\end{gcotable}
 
@@
 
-requirement:
-
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\begin{itemize}
-  \item In most Library applications, these tend to appear in pairs, with repeatable / non-repeatable establishing max cardinality and optional / mandatory establishing min cardinality.
+In most Library applications, cardinality shortcuts tend to appear in pairs, with repeatable / non-repeatable establishing maximum cardinality and optional / mandatory establishing minimum cardinality.
+\begin{itemize}
 	\item Optional \& Non-Repeatable = [0,1]
@@
 \end{itemize}
-
-\begin{DL}
-Not sure if the meaning of this constraint, probably it is the same as for cardinality restrictions?
-\end{DL}
-
-\an{not sure!}
+Can be expressed in DL using minimum and maximum cardinality restrictions.
+We propose to use syntactic sugar instead:
+\begin{gcotable}
+property & C & p & - & - & optional and non-repeatable & - \\
+\end{gcotable}
 
@@
 
+\subsection{Simple Example}
+
+\begin{DL}
+p = COUNT (q)
+\end{DL}
+
+Context class is \ms{C}.
+
 \begin{DL}
@@
 \end{DL}
+
+\begin{gcotable}
+property & C & p & q & - & count & - \\
+\end{gcotable}
 
@@
 
+\subsection{Generic Constraints}
+
+\begin{evaluation-generic-overview}
+Property Constraints & 48 & 65 (64.86) \\
+Class Constraints & 17 & 23 (22.96) \\
+Property and Class Constraints & 9 & 12 (12.16) \\
+\hline
+Simple Constraints & 46 & 62 (62.16) \\
+Simple Constraints (Syntactic Sugar) & 10 & 14 (13.51) \\
+Complex Constraints & 18 & 24 (24.32) \\
+\hline
+DL Expressible & 51 & 69 (68.92) \\
+DL Not Expressible & 23 & 31 (31.08) \\
+\hline
+Total & 74 & 100 \\
+\end{evaluation-generic-overview}
+
+legend of the detailed evaluation:
+\begin{itemize}
+	\item \ms{property constraint:} property constraint ($\checkmark$) vs. class constraint (\ding{55}) vs. property and class constraints ($\sim$) 
+	\item \ms{simple constraint:} simple constraint ($\checkmark$) vs. simple constraint [syntactic sugar] ($\sim$) vs. complex constraint (\ding{55})
+	\item \ms{DL:} expressible in DL ($\checkmark$) vs. not expressible in DL (\ding{55})
+\end{itemize}
+
+\begin{evaluation-generic}
+*Subsumption & \ding{55} & $\checkmark$ & $\checkmark$ \\ 
+*Class Equivalence & \ding{55} & \ding{55} & $\checkmark$ \\ 
+*Sub Properties & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
+*Property Domain & $\checkmark$ & $\sim$ & $\checkmark$ \\ 
+*Property Range & $\checkmark$ & $\sim$ & $\checkmark$ \\ 
+*Inverse Object Properties & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
+*Symmetric Object Properties & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
+*Asymmetric Object Properties & $\checkmark$ & $\sim$ & $\checkmark$ \\ 
+*Reflexive Object Properties & $\checkmark$ & $\sim$ & $\checkmark$ \\ 
+*Irreflexive Object Properties & $\checkmark$ & $\sim$ & $\checkmark$ \\
+Disjoint Properties & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
+Disjoint Classes & \ding{55} & \ding{55} & $\checkmark$ \\ 
+Context-Sp. Property Groups & $\sim$ & \ding{55} & $\checkmark$ \\  
+Context-Sp. Inclusive OR of P. & $\sim$ & \ding{55} & $\checkmark$ \\
+Context-Sp. Inclusive OR of P. Groups & $\sim$ & \ding{55} & $\checkmark$ \\ 
+Recursive Queries & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
+Individual Inequality & \ding{55} & \ding{55} & $\checkmark$ \\  
+*Equivalent Properties & $\checkmark$ & \ding{55} & $\checkmark$ \\   
+Property Assertions & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
+Data Property Facets & \ding{55} & $\checkmark$ & \ding{55} \\  
+Literal Pattern Matching & \ding{55} & $\checkmark$ & \ding{55} \\   
+Negative Literal Pattern Matching & \ding{55} & \ding{55} & \ding{55} \\ 
+*Object Property Paths & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
+*Intersection & \ding{55} & $\checkmark$ & $\checkmark$ \\  
+*Disjunction & \ding{55} & $\checkmark$ & $\checkmark$ \\ 
+*Negation & \ding{55} & $\checkmark$ & $\checkmark$ \\ 
+*Existential Quantification & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
+*Universal Quantification & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
+*Minimum Unqualified Cardinality & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
+*Minimum Qualified Cardinality & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
+*Maximum Unqualified Cardinality & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
+*Maximum Qualified Cardinality & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
+*Exact Unqualified Cardinality & $\checkmark$ & $\sim$ & $\checkmark$ \\ 
+*Exact Qualified Cardinality & $\checkmark$ & $\sim$ & $\checkmark$ \\ 
+*Transitive Object Properties & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
+Context-Sp. Exclusive OR of P. & $\sim$ & \ding{55} & $\checkmark$ \\ 
+Context-Sp. Exclusive OR of P. Groups & $\sim$ & \ding{55} & $\checkmark$ \\
+Allowed Values & \ding{55} & $\checkmark$ & $\checkmark$ \\  
+Not Allowed Values & \ding{55} & \ding{55} & $\checkmark$ \\  
+Literal Ranges & \ding{55} & \ding{55} & \ding{55} \\ 
+Negative Literal Ranges & \ding{55} & \ding{55} & \ding{55} \\ 
+Required Properties & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
+Optional Properties & $\checkmark$ & $\sim$ & $\checkmark$ \\
+Repeatable Properties & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
+Negative Property Constraints & $\sim$ & \ding{55} & $\checkmark$ \\ 
+*Individual Equality & \ding{55} & \ding{55} & $\checkmark$ \\  
+*Functional Properties & $\checkmark$ & $\checkmark$ & $\checkmark$ \\ 
+*Inverse-Functional Properties & $\checkmark$ & \ding{55} & $\checkmark$ \\ 
+*Value Restrictions & $\checkmark$ & $\checkmark$ & $\checkmark$ \\ 
+*Self Restrictions & $\sim$ & \ding{55} & $\checkmark$ \\
+Primary Key Properties & $\checkmark$ & $\sim$ & $\checkmark$ \\ 
+*Class-Specific Property Range & $\checkmark$ & $\sim$ & $\checkmark$ \\ 
+*Class-Sp. Reflexive Object P. & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
+Membership in Controlled Vocabularies & $\sim$ & \ding{55} & $\checkmark$ \\ 
+IRI Pattern Matching & \ding{55} & $\checkmark$ & \ding{55} \\   
+Literal Value Comparison & $\checkmark$ & $\checkmark$ & \ding{55} \\   
+Define Order & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
+Validation Levels & $\sim$ & $\checkmark$ & \ding{55} \\
+String Operations & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
+\end{evaluation-generic}
+
+\begin{evaluation-generic}
+Context-Specific Valid Classes & \ding{55} & $\checkmark$ & \ding{55} \\   
+Context-Specific Valid Properties & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
+Default Values & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
+Mathematical Operations & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
+Language Tag Matching & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
+Language Tag Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
+Whitespace Handling & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
+HTML Handling & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
+Conditional Properties & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
+Recommended Properties & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
+Handle RDF Collections & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
+Value is Valid for Datatype & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
+*Exploiting Class/Property Specialization Ontology Axioms & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
+*Cardinality Shortcuts & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
+Aggregations & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
+\end{evaluation-generic}
+
+%\begin{evaluation-generic}
+%*Subsumption 
+%*Class Equivalence
+%*Sub Properties 
+%*Property Domain 
+%*Property Range 
+%*Inverse Object Properties 
+%*Symmetric Object Properties 
+%*Asymmetric Object Properties 
+%*Reflexive Object Properties 
+%*Irreflexive Object Properties
+%Disjoint Properties 
+%Disjoint Classes
+%Context-Sp. Property Groups 
+%Context-Sp. Inclusive OR of P.
+%Context-Sp. Inclusive OR of P. Groups 
+%Recursive Queries 
+%Individual Inequality 
+%*Equivalent Properties 
+%Property Assertions 
+%Data Property Facets 
+%Literal Pattern Matching 
+%Negative Literal Pattern Matching 
+%*Object Property Paths 
+%*Intersection 
+%*Disjunction 
+%*Negation 
+%*Existential Quantification 
+%*Universal Quantification 
+%*Minimum Unqualified Cardinality 
+%*Minimum Qualified Cardinality 
+%*Maximum Unqualified Cardinality 
+%*Maximum Qualified Cardinality 
+%*Exact Unqualified Cardinality 
+%*Exact Qualified Cardinality 
+%*Transitive Object Properties 
+%Context-Sp. Exclusive OR of P. 
+%Context-Sp. Exclusive OR of P. Groups
+%Allowed Values 
+%Not Allowed Values 
+%Literal Ranges 
+%Negative Literal Ranges 
+%Required Properties 
+%Optional Properties
+%Repeatable Properties 
+%Negative Property Constraints 
+%*Individual Equality 
+%*Functional Properties
+%*Inverse-Functional Properties 
+%*Value Restrictions
+%*Self Restrictions
+%Primary Key Properties 
+%*Class-Specific Property Range 
+%*Class-Sp. Reflexive Object P. 
+%Membership in Controlled Vocabularies 
+%IRI Pattern Matching 
+%Literal Value Comparison 
+%Define Order 
+%Validation Levels 
+%String Operations 
+%\end{evaluation-generic}
+%
+%\begin{evaluation-generic}
+%Context-Specific Valid Classes 
+%Context-Specific Valid Properties 
+%Default Values 
+%Mathematical Operations 
+%Language Tag Matching 
+%Language Tag Cardinality 
+%Whitespace Handling 
+%HTML Handling 
+%Conditional Properties 
+%Recommended Properties 
+%Handle RDF Collections 
+%Value is Valid for Datatype 
+%*Exploiting Class/Property Specialization Ontology Axioms 
+%*Cardinality Shortcuts 
+%Aggregations 
+%\end{evaluation-generic}
+
 \end{document}

### 2014-12-30 paper/paper 2/paper 2.tex
evaluation of paper 2

@@
   \end{tabular}
+	\end{center}
+}
+
+\newenvironment{evaluation-generic-overview}{
+  %\scriptsize
+  %\sffamily
+  %\vspace{0.3cm}
+	\begin{center}
+  \begin{tabular}{l|c|c}
+  \hline
+  \textbf{Constraint Classes} & \textbf{\#} & \textbf{\%} \\
+  \hline
+
+}{
+  \hline
+  \end{tabular}
+  \linebreak
 	\end{center}
@@
 
-We evaluated to which extend the most promising five constraint languages fulfill each requirement to formulate RDF constraints \cite{BoschNolleAcarEckert2015}.
+We evaluated to which extend the most promising five constraint languages fulfill each of the overall 74 requirements to formulate RDF constraints \cite{BoschNolleAcarEckert2015}.
 If a constraint can be expressed in DL, we added the mapping to DL and to the generic constraint.
@@
 Therefore, we show that each constraint can be mapped to a generic constraint.
+The following table shows the absolute number and the relative percentage for the three dimensions to classify constraints:
 
-\begin{evaluation}
-\ms{Expr-C} (41) & 6 & 18(4) & 7(4) & 8 & 12 & 40(1)\\
-\ms{Expr-R} (33) & 8 & 29 & 11 & 11(2) & 11(1) & 33 \\ 
-\end{evaluation}
+\begin{evaluation-generic-overview}
+Property Constraints & 48 & 65 (64.86) \\
+Class Constraints & 17 & 23 (22.96) \\
+Property and Class Constraints & 9 & 12 (12.16) \\
+\hline
+Simple Constraints & 46 & 62 (62.16) \\
+Simple Constraints (Syntactic Sugar) & 10 & 14 (13.51) \\
+Complex Constraints & 18 & 24 (24.32) \\
+\hline
+DL Expressible & 51 & 69 (68.92) \\
+DL Not Expressible & 23 & 31 (31.08) \\
+\hline
+Total & 74 & 100 \\
+\end{evaluation-generic-overview}
+
+Constraints can be classified as \ms{property constraints} and \ms{class constraints}.
+Two thirds are property constraints, one fifth class constraints, and approx. 10\% are composed of both property and class constraints.
+Constraints may be either atomic (\ms{simple constraints}) or created out of simple and complex constraints (\ms{complex constraints}).
+Almost two thirds are simple constraints, a quarter are complex constraints.
+Almost 15 percent are complex constraints which can be formulated as simple constraints when used in terms of syntactic sugar.
+Constraints can either be expressible in DL or not.
+Nearly 70\% of the overall constraints are expressible in DL.
 

### 2014-12-30 paper/paper 2/paper 2.tex
implementation

@@
 
-\section{Limitations}
+SPARQL is generally seen as the method of choice to validate RDF data according to certain constraints, although it is not ideal for their formulation. 
+In contrast, OWL 2 and DSP constraints are comparatively easy to understand, but lack an implementation to validate RDF data. 
+DSPs are used to formulate constraints within a DCMI AP.
+Bosch and Eckert\cite{BoschEckert2014-2} use SPIN as basis to define a
+validation environment in which the validation of any constraint language\footnote{the only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL.
+The validation implementation of constraint languages is fully declarative,
+consisting of a mapping from constraint languages to SPIN in form of SPARQL CONSTRUCT queries.
+SPIN represents both the SPIN mappings and the SPARQL queries in RDF. 
+Within the validation environment, we fully implemented an automatic validation of all OWL 2 DL\footnote{OWL 2 SPIN mapping: \url{https://github.com/boschthomas/OWL2-SPIN-Mapping}} and DSP\footnote{DSP SPIN mapping: \url{https://github.com/dcmi/DSP-SPIN-Mapping}} constructs (for the complete DSP validation see \cite{BoschEckert2014-2}).
+The implementation can be tested at \url{http://purl.org/net/rdfval-demo}.
+The SPIN engine checks for each resource in the RDF data if the resource satisfies all defined constraints and generates a result RDF graph containing information about all constraint violations.
 
+We provide a mapping from the generic constraint language to SPIN in order to automatically validate each type of generic constraint (simple, complex, property, and class constraints).
+Part of future work will be 
 \begin{itemize}
-	\item in order to transform specific constraint languages, there must be a concrete syntax in RDF
+	\item to provide a GUI which generates generic constraints automatically according to inputs of domain experts who are not familiar with the formulation of constraints.
+	\item to extend our RDF validator to provide bidirectional transformations between specific constraints (expressed by multiple constraint languages) and generic constraints. 
 \end{itemize}

### 2014-12-30 paper/paper 2/paper 2.tex
implementation

@@
 In contrast, OWL 2 and DSP constraints are comparatively easy to understand, but lack an implementation to validate RDF data. 
-DSPs are used to formulate constraints within a DCMI AP.
 Bosch and Eckert\cite{BoschEckert2014-2} use SPIN as basis to define a
@@
 The implementation can be tested at \url{http://purl.org/net/rdfval-demo}.
-The SPIN engine checks for each resource in the RDF data if the resource satisfies all defined constraints and generates a result RDF graph containing information about all constraint violations.
+The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.
 
-We provide a mapping from the generic constraint language to SPIN in order to automatically validate each type of generic constraint (simple, complex, property, and class constraints).
+We provide a mapping from the generic constraint language to SPIN\footnote{GCL SPIN mapping: \url{https://github.com/boschthomas/GCL-SPIN-Mapping}} in order to automatically validate each type of generic constraint (simple, complex, property, and class constraints).
 Part of future work will be 

### 2014-12-30 paper/paper 2/paper 2.tex
implementation

@@
 
-\section{Ideas}
-
-\begin{itemize}
-	\item the majority of specific constraints expressed by any specific constraint language can be expressed by DL
-	\item each DL statement can be expressed by a generic constraint using a generic constraint language
-\end{itemize}
-
-purpose:
-\begin{itemize}
-	\item translations of specific constraints expressed by any specific constraint language
-	\item we do not invent a new constraint languages
-\end{itemize}
+%\section{Ideas}
 
@@
 %min car more powerful than req. propery
-
-\begin{itemize}
-	\item any specific constraint (expressed by specific constraint language) must be mapped to a generic constraint (expressed by GCL)
-\end{itemize}
 
@@
 	\item We show how to transform specific constraints (expressed by any constraint language A) into generic constraints and into specific constraints (expressed by any other constraint language B)
-  \item We explain that any specific constraint can be validated automatically (if an automatic validation is defined only once for corresponding generic constraint)
+  \item We explain that any specific constraint can be validated automatically (if an automatic validation is defined only once for the corresponding generic constraint)
 \end{itemize}
@@
 We developed a very simple ontology (three classes, three object properties, and three data properties) which is universal enough to describe any RDF constraint expressible by any RDF constraint language.
+Therefore, we do not invent a new constraint language.
 We distinguish between two sub-types of \ms{constraint}: 
@@
 
-\section{Automatic Validation of Specific Constraints}
-
 \section{Simple Constraints Not Expressible in DL}
@@
 	\item to provide a GUI which generates generic constraints automatically according to inputs of domain experts who are not familiar with the formulation of constraints.
-	\item to extend our RDF validator to provide bidirectional transformations between specific constraints (expressed by multiple constraint languages) and generic constraints. 
+	\item to offer bidirectional transformations between specific constraints (expressed by multiple constraint languages) and generic constraints. 
+	\item to provide translations between specific constraints (expressed by any specific constraint language) by using generic constraints as an intermediate transformation step.
 \end{itemize}
@@
 Constraints can either be expressible in DL or not.
-Nearly 70\% of the overall constraints are expressible in DL.
+The majority - nearly 70\% - of the overall constraints are expressible in DL.
 

### 2014-12-31 paper/paper 2/paper 2.tex
constraint classification

@@
 	%\item Any specific constraint (expressed by any constraint language) can be validated automatically (if an automatic validation is defined only once for corresponding generic constraint)
-	\item We define a terminology for RDF constraints and constraining languages
-	\item We developed an ontology describing any RDF constraint which can also be expressed by any constraint language
-	\item We present that any RDF constraint can be described by the developed ontology - whether the constraint can be expressed in DL or not 
+	\item We define a basic terminology and classification system for RDF constraints
+	\item We developed an ontology describing any RDF constraint generically (whether expressible in DL or not)%which can also be expressed by any constraint language
+	%\item We present that any RDF constraint can be described by the developed ontology - whether the constraint can be expressed in DL or not 
 	\item We show how to transform specific constraints (expressed by any constraint language A) into generic constraints and into specific constraints (expressed by any other constraint language B)
@@
 
-\section{An Ontology Describing RDF Constraints Generically} 
+\section{RDF Constraints Ontology} 
 \label{sec:ontology}
 
-We developed a very simple ontology (three classes, three object properties, and three data properties) which is universal enough to describe any RDF constraint expressible by any RDF constraint language.
-Therefore, we do not invent a new constraint language.
-We distinguish between two sub-types of \ms{constraint}: 
+In order to define this ontology to describe RDF constraints generically, it is needed to define the terminology for the formulation of constraints. 
+A \ms{constraint language} is a language which is used to formulate constraints.
+The W3C Data Shapes WG defines \ms{constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
+We identified four dimensions to classify constraints:
 \begin{itemize}
-	\item \ms{property constraints} and 
-	\item \ms{class constraints}. 
+  \item \ms{Universality:} specific constraints vs. generic constraints
+	\item \ms{Complexity:} simple constraints vs. complex constraints
+	\item \ms{Context:} property constraints vs. class constraints
+	\item \ms{DL Expressivity:} constraints expressible in DL vs. constraints not expressible in DL
 \end{itemize}
 
-For both property and class constraints a context class, a list of classes, the constraining element, and the constraining value can be stated
-(see figure \ref{fig:generic-constraint-language-ontology}). Lists of left and right properties can only be stated for property constraints.
+As there are already five promising constraint languages, our purpose is not to invent a new constraint language.
+We developed a very simple ontology (only three classes, three object properties, and three data properties) which is universal enough to describe any RDF constraint expressible by any RDF constraint language (see the conceptual model in figure \ref{fig:RDF-CO-conceptual-model}).
+We call this ontology the \ms{RDF constraints ontology (RDF-CO)}\footnote{Available at: \url{https://github.com/boschthomas/RDF-constraints-ontology}}.
 
@@
 	\centering
-		\includegraphics[width=0.80\textwidth]{images/generic-constraint-language-ontology.png}
-	\caption{generic constraint language ontology}
-	\label{fig:generic-constraint-language-ontology}
+		\includegraphics[width=0.80\textwidth]{images/RDF-CO-conceptual-model.png}
+	\caption{RDF constraints ontology (RDF-CO) - conceptual model}
+	\label{fig:RDF-CO-conceptual-model}
 \end{figure}
 
-In order to define this ontology, it is needed to define the terminology for the formulation of constraints. 
-A \ms{constraint language} is a language which is used to formulate constraints.
-The W3C Data Shapes WG defines \ms{constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
+\ms{Specific constraints} are expressed by specific constraint languages like DSP, OWL 2, ReSh, ShEx, and SPIN.
+\ms{Generic constraints} are expressed by the RDF-CO.
+As RDF-CO describes constraints generically, RDF-CO does not distinguish constraints according to the dimension \ms{universality}. 
+The majority of constraints can be expressed in DL (see section \ref{sec:evaluation}).
+In contrast, there are constraints which cannot be expressed in DL, but are also representable by the RDF-CO. 
+\ms{Complex constraints} encompass \ms{simple constraints} (atomic constraints) and/or further complex constraints.
+DL statements representing complex constraints are created out of DL statements representing composed constraints (if expressible in DL). 
+Simple constraints may be applied to either properties \ms{properties constraints} or classes \ms{class constraints}.
+There are no terms representing simple and complex constraints in the RDF-CO, since context classes (associated simple constraints hold for individuals of these classes) of simple constraints may just be reused by further constraints.
+As a consequence, the distinction of property and class constraints is sufficient to describe all possible RDF constraints.
+
+\subsection{Simple Constraints (Expressible in DL)}
+
+Sub-classes of \ms{simple constraints} are \ms{property constraints} and \ms{class constraints} (see the RDF-CO implementation model in figure \ref{fig:RDF-CO-implementation-model}). 
+For both property and class constraints a context class, a list of classes, the constraining element, and the constraining value can be stated. 
+Lists of left and right properties can only be stated for property constraints.
+
+\begin{figure}
+	\centering
+		\includegraphics[width=0.80\textwidth]{images/RDF-CO-implementation-model.png}
+	\caption{RDF constraints ontology (RDF-CO) - implementation model}
+	\label{fig:RDF-CO-implementation-model}
+\end{figure}
+
 A constraint holds for all individuals of a context class (\ms{contextClass}).
@@
 
-\section{Complex Constraints}
+\subsection{Simple Constraints (Not Expressible in DL)}
 
-\ms{Complex constraints} encompass complex constraints and/or \ms{simple constraints} (atomic constraints).
-DL statements of complex constraints are created out of DL statements of composed constraints.
+There are simple constraints which cannot be expressed by DL such as literal pattern matching, literal value comparison, literal ranges, default values, and language tag cardinality \cite{BoschNolleAcarEckert2015}.
 
+% maybe additional constraint default values:
+% ear shape of races, e.g. vulcans / teeth color
+% mathematical operations
+
+There are multiple use cases associated with the requirement to match literals according to given patterns (\ms{Literal Pattern Matching} constraint).
+The enterprise vessel, e.g.,  can only have the registry numbers "NCC-1701", "NCC-1701-A", "NCC-1701-B", "NCC-1701-C", "NCC-1701-D", or "NCC-1701-E".
+The universal restriction part of this complex constraint can be expressed by OWL 2 DL:
+\ms{Enterprise $\sqsubseteq$ $\forall$ registryNumber.RegistryNumber}.
+The restriction of the datatype \ms{RegistryNumber}, however, cannot be expressed in DL, but OWL 2 DL can be used anyway to express the literal pattern matching constraint:
+
+\begin{ex}
+RegistryNumber
+    a rdfs:Datatype ;
+    owl:equivalentClass [
+        a rdfs:Datatype ;
+        owl:onDatatype xsd:string ;
+        owl:withRestrictions ( 
+            [ xsd:pattern "NCC-1701([-][A-E])?" ] ) ] .
+\end{ex}
+
+The second axiom defines \ms{RegistryNumber} as an abbreviation for a datatype restriction on \ms{xsd:string}. 
+The first axiom explicitly declares \ms{RegistryNumber} to be a datatype. 
+The datatype \ms{RegistryNumber} can be used just like any other datatype like in the universal restriction above.
+The literal pattern matching constraint validates \ms{RegistryNumber} literals according to the stated regular expression causing a constraint violation for the triples 
+\ms{Janeway commandsEnterprise Voyager} and \ms{Voyager registryNumber "NCC-74656"\textasciicircum{}\textasciicircum{}RegistryNumber}, 
+but not for the triples \ms{Picard commandsEnterprise Enterprise} and \ms{Enterprise registryNumber "NCC-1701-E"\textasciicircum{}\textasciicircum{}RegistryNumber}.
+The universal restriction and the literal pattern matching constraint are mapped to the generic constraint language as follows:
+
+\begin{gcotable}
+property & Enterprise & registryNumber & - & RegistryNumber & $\forall$ & - \\
+class & RegistryNumber & - & - & xsd:string & regex & 'NCC-1701([-][A-E])?' \\
+\end{gcotable}
+
+The \ms{Literal Pattern Matching} constraint introduces a new constraining element: \ms{regex}.
+For this new constraining element, an automatic validation must be implemented in SPIN.
+This has to be done once for each constraint which cannot be expressed in DL.
+
+\subsection{Complex Constraints}
+
+\ms{Complex constraints} encompass simple constraints and/or complex constraints.
 \textbf{Context-Specific Exclusive OR of Property Groups}\footnote{corresponds to R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC}\textbf{.}
@@
 
-\subsection{Disjoint Classes}
+\subsection{Simple Constraints (Syntactic Sugar)}
 
-\begin{DL}
-Hologram $\sqcap$ Human $\sqsubseteq$ $\perp$\\
-Alternative:\\
-$Hologram \sqsubseteq \neg Human$
-\end{DL}
-
-\subsection{Minimum Qualified Cardinality Restrictions on Properties}
-
-\begin{DL}
-$FederationCaptain \sqsubseteq Federation \sqcap \geq1 commandsVessel . Vessel $
-\end{DL}
-
-\section{Syntactic Sugar}
-
-\begin{itemize}
-	\item syntactic sugar for some constraints
-\end{itemize}
+Almost 15 percent of all RDF constraints are complex constraints which can be simplified and therefore formulated as simple constraints when used in terms of syntactic sugar (see section \ref{sec:evaluation}).
 
@@
 
+\subsection{Disjoint Classes}
+
+\begin{DL}
+Hologram $\sqcap$ Human $\sqsubseteq$ $\perp$\\
+Alternative:\\
+$Hologram \sqsubseteq \neg Human$
+\end{DL}
+
+\subsection{Minimum Qualified Cardinality Restrictions on Properties}
+
+\begin{DL}
+$FederationCaptain \sqsubseteq Federation \sqcap \geq1 commandsVessel . Vessel $
+\end{DL}
+
 \section{Transformations between Specific Constraints}
-
-\section{Simple Constraints Not Expressible in DL}
-
-There are simple constraints which cannot be expressed by DL such as literal pattern matching, literal value comparison, literal ranges, default values, and language tag cardinality \cite{BoschNolleAcarEckert2015}.
-
-% maybe additional constraint default values:
-% ear shape of races, e.g. vulcans / teeth color
-% mathematical operations
-
-There are multiple use cases associated with the requirement to match literals according to given patterns (\ms{Literal Pattern Matching} constraint).
-The enterprise vessel, e.g.,  can only have the registry numbers "NCC-1701", "NCC-1701-A", "NCC-1701-B", "NCC-1701-C", "NCC-1701-D", or "NCC-1701-E".
-The universal restriction part of this complex constraint can be expressed by OWL 2 DL:
-\ms{Enterprise $\sqsubseteq$ $\forall$ registryNumber.RegistryNumber}.
-The restriction of the datatype \ms{RegistryNumber}, however, cannot be expressed in DL, but OWL 2 DL can be used anyway to express the literal pattern matching constraint:
-
-\begin{ex}
-RegistryNumber
-    a rdfs:Datatype ;
-    owl:equivalentClass [
-        a rdfs:Datatype ;
-        owl:onDatatype xsd:string ;
-        owl:withRestrictions ( 
-            [ xsd:pattern "NCC-1701([-][A-E])?" ] ) ] .
-\end{ex}
-
-The second axiom defines \ms{RegistryNumber} as an abbreviation for a datatype restriction on \ms{xsd:string}. 
-The first axiom explicitly declares \ms{RegistryNumber} to be a datatype. 
-The datatype \ms{RegistryNumber} can be used just like any other datatype like in the universal restriction above.
-The literal pattern matching constraint validates \ms{RegistryNumber} literals according to the stated regular expression causing a constraint violation for the triples 
-\ms{Janeway commandsEnterprise Voyager} and \ms{Voyager registryNumber "NCC-74656"\textasciicircum{}\textasciicircum{}RegistryNumber}, 
-but not for the triples \ms{Picard commandsEnterprise Enterprise} and \ms{Enterprise registryNumber "NCC-1701-E"\textasciicircum{}\textasciicircum{}RegistryNumber}.
-The universal restriction and the literal pattern matching constraint are mapped to the generic constraint language as follows:
-
-\begin{gcotable}
-property & Enterprise & registryNumber & - & RegistryNumber & $\forall$ & - \\
-class & RegistryNumber & - & - & xsd:string & regex & 'NCC-1701([-][A-E])?' \\
-\end{gcotable}
-
-The \ms{Literal Pattern Matching} constraint introduces a new constraining element: \ms{regex}.
-For this new constraining element, an automatic validation must be implemented in SPIN.
-This has to be done once for each constraint which cannot be expressed in DL.
 
@@
 \section{Evaluation}
+\label{sec:evaluation}
 

### 2015-01-02 paper/paper 2/paper 2.tex
automatic validation

@@
 \newcommand{\ms}[1]{\texttt{#1}}
+
+%\usepackage{listings}% http://ctan.org/pkg/listings
+%\lstset{
+  %numbers=left,numbersep=2mm,frame=single,mathescape,fontsize=\scriptsize
+%}
 
@@
 
-\keywords{..}
+\keywords{RDF Validation, RDF Constraints, RDF Validation Requirements, Linked Data, Semantic Web}
 \end{abstract}
@@
 
-\begin{itemize}
-	\item requirements database
-	\item relationship between requirements and constraints
-	\item constraint languages
-\end{itemize}
+For many RDF applications, the formulation of constraints and the automatic validation of data according to these constraints is a much sought-after feature. 
+In 2013, the W3C invited experts from industry, government, and academia to the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
+where first use cases have been presented and discussed. 
+Two working groups (WGs),  that follow up on this workshop and address RDF constraint formulation and validation, are established in 2014: 
+the W3C RDF Data Shapes WG\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles WG\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
+
+Bosch and Eckert \cite{BoschEckert2014} initiated a database on RDF validation requirements to collect case studies, use cases and especially requirements regarding RDF validation collaboratively and in a comprehensive and structured way.
+%\er{Just for reminding ourselves:  being careful using what is a use-case and what is a case-study later in the text.(http://www.w3.org/2001/sw/sweo/public/UseCases/)}
+%\tb{agreed, will take care}
+This database is continuously updated and openly available at \url{http://purl.org/net/rdf-validation}.
+It is used to evaluate and compare several existing solutions for RDF constraint formulation and validation.
+The requirements are classified to provide a high-level view on different solutions and to facilitate a better understanding of the problem domain \cite{BoschEckert2014}.  
+Each requirement to formulate RDF constraints is directly mapped to an RDF constraint.
+
+There are multiple constraint languages with different syntaxes and semantics which can be used to express RDF constraints, e.g., \emph{at-least} restrictions.
+The most promising ones on being the standard, are
+the SPARQL Inferencing Notation (SPIN)\footnote{\url{http://spinrdf.org/}}, 
+the Web Ontology Language (OWL 2)\footnote{\url{http://www.w3.org/TR/owl2-syntax/}}, 
+Shape Expressions (ShEx)\footnote{\url{http://www.w3.org/Submission/shex-primer/}}, 
+Resource Shapes (ReSh)\footnote{\url{http://www.w3.org/Submission/shapes/}}, 
+and Description Set Profiles (DSP)\footnote{\url{http://dublincore.org/documents/2008/03/31/dc-dsp/}}.
+However, there is no single standard general-purpose constraint language.
+The choice depends on the individual use case.
+
+\tb{copied from first paper - need to be modified}
 
@@
 
-In Section 1.3 we introduced three forms of RBox axioms: role inclusions, role equiv-
-alences and role disjointness. OWL provides a variety of others, namely role transi-
-tivity, symmetry, asymmetry, reflexivity and irreflexivity. These are sometimes consid-
-ered as basic axiom types in DLs as well, using some suggestive notation such as
-Trans( ancestorOf ) to express that the role ancestorOf is transitive. However, such axioms
-are just syntactic sugar; all role characteristics can be expressed using the features
-of DLs that we have already introduced.
+There three forms of RBox axioms: role inclusions, role equivalences and role disjointness. 
+OWL provides a variety of others, namely role transitivity, symmetry, asymmetry, reflexivity and irreflexivity. 
+These are sometimes considered as basic axiom types in DLs as well, using some suggestive notation such as
+\ms{Trans(ancestorOf)} to express that the role ancestorOf is transitive. 
+However, such axioms are just syntactic sugar; 
+all role characteristics can be expressed using the basic features of DLs.
+\ms{Irreflexive Object Properties}\footnote{corresponds to the requirement \ms{R-60-IRREFLEXIVE-OBJECT-PROPERTIES}}
+restricts that an object property is irreflexive if it is never locally reflexive, i.e. no individual is connected by the object property to itself \cite{Kroetzsch2012}.
+Irreflexivity constraints, stating that individuals cannot be married to themselves, can be represented in DL:
 
-\begin{itemize}
-  \item domain and range
-	\item Primary Key Properties
-	\item (ir)reflexive object properties
-	\item ( Exact Qualified Cardinality Restrictions on Properties )
-\end{itemize}
+\begin{DL}
+$\top$ $\sqsubseteq$ $\neg$ $\exists  marriedTo . Self$
+\end{DL}
+
+When mapped to the RDF-CO, the complex constraint aggregates three simple constraints (one property and two class constraints):
+
+\begin{gcotable}
+property & $\exists$ marriedTo . Self & marriedTo & - & Self & $\exists$ & - \\
+class & $\neg$ $\exists$ marriedTo . Self & - & - & $\exists$ marriedTo . Self & $\neg$ & - \\
+class & $\top$ & - & - & $\top$, $\neg$ $\exists$ marriedTo . Self & $\sqsubseteq$ & - \\
+\end{gcotable}
+
+When using the RBox axiom \ms{role irreflexivity} as syntactic sugar, 
+the complex constraint transforms into a simple property constraint with exactly the same semantics:
+
+\begin{gcotable}
+property & $\top$ & marriedTo & - & - & irreflexive & - \\
+\end{gcotable}
+
+The \ms{Primary Key Properties} constraint is often useful to declare a given (datatype) property as the "primary key" of a class, so that the system can enforce uniqueness. 
+Starfleet officers are uniquely identified by their command authorization code (e.g. to activate and cancel auto-destruct sequences).
+It means that the property \ms{commandAuthorizationCode} is inverse functional - mapped to DL and RDF-CO as follows:
+\begin{DL}
+$(\ms{funct } commandAuthorizationCode\sp{\overline{\ }})$
+\end{DL}
+\begin{gcotable}
+property & $\top$ & commandAuthorizationCode$^{-}$ & commandAuthorizationCode & - & inverse & - \\
+property & $\top$ & commandAuthorizationCode$^{-}$ & - & - & functional & - \\
+\end{gcotable}
+
+Keys are even more general, i.e., a generalization of inverse functional properties\footnote{\url{http://www.w3.org/TR/2012/REC-owl2-rdf-based-semantics-20121211/#Semantic_Conditions_for_Keys}}.
+A key can be a datatype property, an object property, or a chain of properties.
+For this generalization purposes, as there are different sorts of key, and as keys can lead to undecidability, 
+DL is extended with \ms{key boxes} and a special \ms{keyfor} construct\cite{Lutz2005}.
+This leads to the following DL and RDF-CO mappings (only one simple property constraint) for the example:
+
+\begin{DL}
+commandAuthorizationCode \ms{keyfor} StarfleetOfficer
+\end{DL}
+
+\begin{gcotable}
+property & StarFleetOfficer & commandAuthorizationCode & - & - & keyfor & - \\
+\end{gcotable}
+
+%\begin{itemize}
+  %\item domain and range
+	%\item Primary Key Properties
+	%\item ( Exact Qualified Cardinality Restrictions on Properties )
+%\end{itemize}
 
@@
 
-\section{Transformations between Specific Constraints}
+\section{Transformations and Automatic Validation of Specific Constraints}
+%\section{Transformations between Specific Constraints (Expressed by Different Constraint Languages)}
+
+RDF data providers ensure that their data conforms to constraints which are part of the contract between the providers and the consumers of that data.
+As there is no standard way, these constraints may be represented by multiple constraint languages (there are even more than the five promising ones)\footnote{i.a.
+Bibframe, DQTP, Pellet ICV, RDFUnit, SPARQL, Stardog ICV}.
+There is an obvious need to transform a specific constraint (\ms{$sc_{\alpha}$}) (expressed by any constraint language \ms{$\alpha$}) into a specific constraint (\ms{$sc_{\beta}$}) (expressed by any constraint language \ms{$\beta$}) - when they have the same semantics.
+We use the RDF-CO as intermediate language for these transformations.
+If we define mappings ($m(sc_{\alpha}), m(sc_{\beta})$) from these two specific constraints to the corresponding generic constraint (\ms{gc}),
+we can convert them automatically:
+
+\begin{DL}
+$ gc = m(sc_{\alpha}) = m(sc_{\beta}) $
+\end{DL}
+
+We do not need to define mappings for each pair of semantically equivalent specific constraint.
+Let's assume we are able to express a constraint by 5/6/7/8/9/10 constraint languages.
+Without the intermediate generic constraint, we would have to define one mapping for each pair of specific constraints expressed by a specific constraint language
+- that are \ms{\( {n \choose 2} \)} mappings for each constraint (example: 10/15/21/28/36/45).
+Without an intermediate generic constraint, we only need to define \ms{n} mappings from the specific constraints to the generic constraint (example: 5/6/7/8/9/10 ).
+
+%(n(n+1))/2
+
+%\begin{DL}
+%\(\sum \limits_{i=1}^n i = \frac{n(n+1)}{2}\)
+%\(\sum \limits_{i=1}^n i\)
+%\(\Binom{n}{2} \)
+%\( {n \choose 2} \)
+%\end{DL}
+
+\ms{Allowed Values}\footnote{correspond to the requirements \ms{R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS} and \ms{R-37-ALLOWED-VALUES-FOR-RDF-LITERALS}}
+is a common requirement to narrow down the value space of a property by an exhaustive enumeration of the valid values (both literals or resources). 
+This is often rendered in drop down boxes or radio buttons in user interfaces.
+Starfleet captains, e.g. can only be overruled by commodores and admirals\footnote{simplified}.
+This complex constraint is composed of two simple constraints: \ms{universal quantification} and \ms{allowed values} - which can be represented in DL:
+
+\begin{DL}
+StarfleetCaptain $\equiv$ $\forall$ overruledBy . \{Commodore\} $\sqcup$ \{Admiral\}
+\end{DL}
+
+First, we map these DL statements to two simple constraints corresponding to the RDF-CO (we define the class \ms{CaptainOverruler} by simply enumerating its instances):
+
+\begin{gcotable}
+property & StarfleetCaptain & overruledBy & - & CaptainOverruler & $\forall$ & - \\
+class & CaptainOverruler & - & - & \{Commodore\},\{Admiral\} & $\sqcup$ & - \\
+\end{gcotable}
+
+The next step is to define one mapping for each specific constraint to the generic constraint.
+The specific constraints (\ms{$sc_{OWL 2}$}, \ms{$sc_{ReSh}$}, and \ms{$sc_{ShEx}$}) expressed by OWL 2, ReSh, and ShEx look like this:
+
+\begin{ex}
+# OWL 2:
+Enterprise rdfs:subClassOf [ a owl:Restriction .
+    owl:onProperty commandedBy .
+    owl:allValuesFrom [ a owl:Class ;
+        owl:oneOf ( Archer Kirk Picard ) ] ] .
+# ReSh:
+Enterprise a rs:ResourceShape ; rs:property [
+    rs:name "commandedBy" ; rs:propertyDefinition commandedBy ;
+    rs:allowedValue Archer , Kirk , Picard ;
+    rs:occurs rs:Exactly-one ; ] .
+# ShEx:
+Enterprise {
+    commandedBy (Archer Kirk Picard) }
+\end{ex}
+
+%\begin{ex}
+%# DSP:
+%[ a dsp:DescriptionTemplate ;
+    %dsp:resourceClass StarfleetCaptain ; 
+    %dsp:statementTemplate [ a dsp:NonLiteralStatementTemplate ; 
+        %dsp:property overruledBy ; 
+        %dsp:nonLiteralConstraint [ a dsp:NonLiteralConstraint ;
+            %dsp:valueClass Commodore , Admiral ] ] ] .
+%# OWL 2:
+%StarfleetCaptain rdfs:subClassOf [ a owl:Restriction .
+    %owl:onProperty overruledBy .
+    %owl:allValuesFrom [ a owl:Class ;
+        %owl:oneOf ( Commodore Admiral ) ] ] .
+%# ReSh:
+%%StarfleetCaptain a rs:ResourceShape ;
+    %%rs:property [
+        %%rs:name "overruledBy" ; rs:propertyDefinition overruledBy ;
+        %%rs:valueShape Commodore ; rs:occurs rs:Zero-or-many ; ] ;
+    %%rs:property [
+        %%rs:name "overruledBy" ; rs:propertyDefinition overruledBy ;
+        %%rs:valueShape Admiral ; rs:occurs rs:Zero-or-many ; ] ;
+%# ShEx:
+%:StarfleetCaptain {
+    %:overruledBy @:Commodore* , :overruledBy @:Admiral* }
+%\end{ex}
+
+\section{Automatic Validation of Specific and Generic Constraints}
+
+We can provide an automatic validation of all specific constraints (expressed by any constraint language) by defining a mapping to SPIN.
+That's what we have done for all OWL 2 and DSP constructs (see section \ref{sec:implementation}).
+%We do not have to define a mapping to SPIN for each specific constraint. 
+%when we define a mapping to SPIN for each generic constraint.
+But, if we define a mapping from a specific constraint to the corresponding generic constraint and if we define a mapping from the generic constraint to SPIN,
+we do not have to define a mapping to SPIN for that specific constraint - we can perform an automatic validation for the generic and for the specific constraint as well.
+As a consequence, we only have to define one SPIN mapping for each constraint corresponding to a requirement within the RDF validation requirements database.
+19 of 74 RDF constraints can be expressed by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
+This means, that there must be 76 (four for each constraint) implementations for an automatic validation of these constraints - instead of only 19 (one for each constraint).
+
+Within our SPIN validation environment, we define a SPIN construct template for each generic constraint\footnote{for details about the SPIN validation environment see \cite{BoschEckert2014-2}}.
+The SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples (\ms{spin:ConstraintViolation}) indicating the subject (\ms{spin:violationRoot}) and the properties (\ms{spin:violationPath}), causing the constraint violation, and the reason why the constraint violation has been raised (\ms{rdfs:label}).
+The SPIN construct template creates the constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
+The SPARQL CONSTRUCT query for the universal quantification is shown below:
+
+\begin{ex}
+CONSTRUCT {
+    [   a spin:ConstraintViolation ; spin:violationRoot ?subject ;
+        rdfs:label ?violationMessage ; spin:violationPath ?p1 . }
+WHERE {	  
+    [   a gclo:PropertyConstraint ;
+        gclo:contextClass ?cc ;
+        gclo:leftProperties ( ?p1 ) ;
+        gclo:classes ( ?c1 ) ;
+        gclo:constrainingElement "universal quantification" ] .
+    [   a gclo:ClassConstraint ;
+        gclo:contextClass ?c1 ;
+        gclo:classes ( ?i1 ?i2 ?i3 ) ;
+        gclo:constrainingElement "union" ] .				
+    ?subject a ?cc ; ?p1 ?i .
+    FILTER ( ?i != ?i1 && ?i != ?i2 && ?i != ?i3 ) . }
+\end{ex}
+
+There can be no detailed difference in the automatic validation of a constraint when it is expressed by different constraint languages.
+So, the validation results do not differ on the basis of multiple validation implementations, as there is only one validation implementation for each constraint independent from the used constraint language.
+
+%\subsection{Not Allowed Values}
 
 \section{Implementation}
+\label{sec:implementation}
 

### 2015-01-02 paper/paper 2/paper 2.tex
automatic validation

@@
 
-\section{Transformations and Automatic Validation of Specific Constraints}
+%\section{Transformations and Automatic Validation of Specific Constraints}
 %\section{Transformations between Specific Constraints (Expressed by Different Constraint Languages)}
+\section{Transformations between Specific Constraints}
 
@@
 This is often rendered in drop down boxes or radio buttons in user interfaces.
-Starfleet captains, e.g. can only be overruled by commodores and admirals\footnote{simplified}.
+The Enterprise, e.g. is only commended by the captains Archer, Kirk, and Picard.
 This complex constraint is composed of two simple constraints: \ms{universal quantification} and \ms{allowed values} - which can be represented in DL:
 
+%\begin{DL}
+%StarfleetCaptain $\equiv$ $\forall$ overruledBy . \{Commodore\} $\sqcup$ \{Admiral\}
+%\end{DL}
+
 \begin{DL}
-StarfleetCaptain $\equiv$ $\forall$ overruledBy . \{Commodore\} $\sqcup$ \{Admiral\}
+Enterprise $\equiv$ $\forall$ commandedBy . \{Archer\} $\sqcup$ \{Kirk\} $\sqcup$ \{Picard\}
 \end{DL}
 
-First, we map these DL statements to two simple constraints corresponding to the RDF-CO (we define the class \ms{CaptainOverruler} by simply enumerating its instances):
+First, we map these DL statements to two simple constraints corresponding to the RDF-CO (we define the class \ms{EnterpriseCaptains} by simply enumerating its instances):
+
+%\begin{gcotable}
+%property & StarfleetCaptain & overruledBy & - & CaptainOverruler & $\forall$ & - \\
+%class & CaptainOverruler & - & - & \{Commodore\},\{Admiral\} & $\sqcup$ & - \\
+%\end{gcotable}
 
 \begin{gcotable}
-property & StarfleetCaptain & overruledBy & - & CaptainOverruler & $\forall$ & - \\
-class & CaptainOverruler & - & - & \{Commodore\},\{Admiral\} & $\sqcup$ & - \\
+property & Enterprise & commandedBy & - & EnterpriseCaptains & $\forall$ & - \\
+class & EnterpriseCaptains & - & - & \{Archer\},\{Kirk\},\{Picard\} & $\sqcup$ & - \\
 \end{gcotable}
@@
 
-There can be no detailed difference in the automatic validation of a constraint when it is expressed by different constraint languages.
+The implementation of the automatic validation of a constraint cannot be different when it is expressed by different constraint languages.
 So, the validation results do not differ on the basis of multiple validation implementations, as there is only one validation implementation for each constraint independent from the used constraint language.

### 2015-01-03 paper/paper 2/paper 2.tex
abstract

@@
   %\sffamily
-  %\vspace{0.3cm}
+  \vspace{0.3cm}
 	\begin{center}
@@
   \end{tabular}
-  \linebreak
+  %\linebreak
 	\end{center}
@@
 
-\keywords{RDF Validation, RDF Constraints, RDF Validation Requirements, Linked Data, Semantic Web}
+For XML, XML Schema is the standard constraint language to validate XML documents.
+For RDF, however, there are multiple candidates for languages to express constraints on RDF data - but there is no standard language for RDF validation.
+W3C and DCMI working groups on RDF validation identified requirements to formulate and to validate RDF constraints.
+The majority of these constraints can be represented in description logics providing a logical underpinning of these constraints.
+We developed an ontology describing any RDF constraint generically (whether expressible in description logics or not).
+In parallel, we defined a basic terminology and a classification system for RDF constraints.
+
+A constraint (expressed by constraint language \ms{$sc_{\alpha}$}) can be transformed to a constraint (expressed by constraint language \ms{$sc_{\beta}$}) by using the RDF constraint ontology as intermediate language.
+Currently, we cannot validate every constraint language or constraint of a constraint language.
+If we define a validation for a constraint generically and if we map semantically equivalent constraints (expressed by different constraint languages) to that generically expressed constraint, we are able to provide the validation of these constraints out of the box.
+
+\keywords{RDF Validation, RDF Constraints, RDF Validation Requirements, Transformation, Linked Data, Semantic Web}
 \end{abstract}
@@
 
-\tb{copied from first paper - need to be modified}
+\tb{introduction copied from first paper - need to be modified}
 
@@
 \begin{ex}
-# constraint
-# ----------
 [   a PropertyConstraint ;
@@
 
-# data
-# ----
 ?subject rdf:type ?cc .
 
-# validation
-# -----
 BIND ( qualifiedCardinality( ?subject, ?p1, ?c1 ) AS ?c ) .
@@
 	\centering
-		\includegraphics[width=0.80\textwidth]{images/RDF-CO-implementation-model.png}
+		\includegraphics[width=0.70\textwidth]{images/RDF-CO-implementation-model.png}
 	\caption{RDF constraints ontology (RDF-CO) - implementation model}
@@
 It means that the property \ms{commandAuthorizationCode} is inverse functional - mapped to DL and RDF-CO as follows:
+
 \begin{DL}
@@
 \end{DL}
+
 \begin{gcotable}
@@
 
-\subsection{Disjoint Classes}
-
-\begin{DL}
-Hologram $\sqcap$ Human $\sqsubseteq$ $\perp$\\
-Alternative:\\
-$Hologram \sqsubseteq \neg Human$
-\end{DL}
-
-\subsection{Minimum Qualified Cardinality Restrictions on Properties}
-
-\begin{DL}
-$FederationCaptain \sqsubseteq Federation \sqcap \geq1 commandsVessel . Vessel $
-\end{DL}
+%\subsection{Disjoint Classes}
+%
+%\begin{DL}
+%Hologram $\sqcap$ Human $\sqsubseteq$ $\perp$\\
+%Alternative:\\
+%$Hologram \sqsubseteq \neg Human$
+%\end{DL}
+%
+%\subsection{Minimum Qualified Cardinality Restrictions on Properties}
+%
+%\begin{DL}
+%$FederationCaptain \sqsubseteq Federation \sqcap \geq1 commandsVessel . Vessel $
+%\end{DL}
 
@@
 \section{Transformations between Specific Constraints}
+\label{sec:transformations}
 
@@
 - that are \ms{\( {n \choose 2} \)} mappings for each constraint (example: 10/15/21/28/36/45).
-Without an intermediate generic constraint, we only need to define \ms{n} mappings from the specific constraints to the generic constraint (example: 5/6/7/8/9/10 ).
+With an intermediate generic constraint, we only need to define \ms{n} mappings from the specific constraints to the generic constraint (example: 5/6/7/8/9/10 ).
 
@@
 
-\ms{Allowed Values}\footnote{correspond to the requirements \ms{R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS} and \ms{R-37-ALLOWED-VALUES-FOR-RDF-LITERALS}}
+\ms{Allowed Values}\footnote{corresponds to the requirements \ms{R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS} and \ms{R-37-ALLOWED-VALUES-FOR-RDF-LITERALS}}
 is a common requirement to narrow down the value space of a property by an exhaustive enumeration of the valid values (both literals or resources). 
-This is often rendered in drop down boxes or radio buttons in user interfaces.
-The Enterprise, e.g. is only commended by the captains Archer, Kirk, and Picard.
-This complex constraint is composed of two simple constraints: \ms{universal quantification} and \ms{allowed values} - which can be represented in DL:
+The Enterprise, e.g., is only commanded by the captains Archer, Kirk, and Picard.
+This complex constraint is composed of the two simple constraints \ms{universal quantification} and \ms{allowed values} which can be represented in DL:
 
@@
 19 of 74 RDF constraints can be expressed by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
-This means, that there must be 76 (four for each constraint) implementations for an automatic validation of these constraints - instead of only 19 (one for each constraint).
+This means, that there must be 76 (four for each constraint) implementations to validate  these constraints - instead of only 19 (one for each constraint).
 
@@
 The SPIN construct template creates the constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
-The SPARQL CONSTRUCT query for the universal quantification is shown below:
+The SPARQL CONSTRUCT query for the universal quantification (of the previous example in section \ref{sec:transformations}) is shown below:
 
@@
 
-The implementation of the automatic validation of a constraint cannot be different when it is expressed by different constraint languages.
-So, the validation results do not differ on the basis of multiple validation implementations, as there is only one validation implementation for each constraint independent from the used constraint language.
+As a consequence, the validation results do not differ for semantically equivalent constraints when they are based on multiple validation implementations, as there is only one validation implementation for each constraint - independent from the used constraint language.
 

### 2015-01-03 paper/paper 2/paper 2.tex
introduction

@@
 
-For many RDF applications, the formulation of constraints and the automatic validation of data according to these constraints is a much sought-after feature. 
-In 2013, the W3C invited experts from industry, government, and academia to the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
-where first use cases have been presented and discussed. 
-Two working groups (WGs),  that follow up on this workshop and address RDF constraint formulation and validation, are established in 2014: 
+The purpose of ontologies is to perform reasoning on RDF data and not to validate RDF data conforming to these ontologies.
+For RDF, we cannot use ontologies like we use XML Schemas, DTDs, RELAX NG, or Schematron to validate XML documents.
+The W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
+where experts from industry, government, and academia discussed first use cases for RDF constraint formulation and validation.
+In 2014, two working groups on RDF validation have been established: 
 the W3C RDF Data Shapes WG\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles WG\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
 
-Bosch and Eckert \cite{BoschEckert2014} initiated a database on RDF validation requirements to collect case studies, use cases and especially requirements regarding RDF validation collaboratively and in a comprehensive and structured way.
-%\er{Just for reminding ourselves:  being careful using what is a use-case and what is a case-study later in the text.(http://www.w3.org/2001/sw/sweo/public/UseCases/)}
-%\tb{agreed, will take care}
-This database is continuously updated and openly available at \url{http://purl.org/net/rdf-validation}.
-It is used to evaluate and compare several existing solutions for RDF constraint formulation and validation.
-The requirements are classified to provide a high-level view on different solutions and to facilitate a better understanding of the problem domain \cite{BoschEckert2014}.  
-Each requirement to formulate RDF constraints is directly mapped to an RDF constraint.
+Bosch and Eckert \cite{BoschEckert2014} collected the findings of these working groups and initiated a database of requirements to formulate and validate RDF constraints
+which is available for contribution at \url{http://purl.org/net/rdf-validation}.
+The intention associated with this database is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
+The requirements are classified to better evaluate existing solutions. 
+We mapped each requirement to formulate RDF constraints directly to an RDF constraint.
 
-There are multiple constraint languages with different syntaxes and semantics which can be used to express RDF constraints, e.g., \emph{at-least} restrictions.
-The most promising ones on being the standard, are
+There is no constraint language which can be seen as the standard.
+Although, there are multiple constraint languages (having different syntaxes and semantics) which can be used to express RDF constraints, such as existential and universal quantification, cardinality restrictions, and exclusive or of properties.
+The five most promising ones on being the standard are
+Description Set Profiles (DSP)\footnote{\url{http://dublincore.org/documents/2008/03/31/dc-dsp/}},
+Resource Shapes (ReSh)\footnote{\url{http://www.w3.org/Submission/shapes/}}, 
+Shape Expressions (ShEx)\footnote{\url{http://www.w3.org/Submission/shex-primer/}},
 the SPARQL Inferencing Notation (SPIN)\footnote{\url{http://spinrdf.org/}}, 
-the Web Ontology Language (OWL 2)\footnote{\url{http://www.w3.org/TR/owl2-syntax/}}, 
-Shape Expressions (ShEx)\footnote{\url{http://www.w3.org/Submission/shex-primer/}}, 
-Resource Shapes (ReSh)\footnote{\url{http://www.w3.org/Submission/shapes/}}, 
-and Description Set Profiles (DSP)\footnote{\url{http://dublincore.org/documents/2008/03/31/dc-dsp/}}.
-However, there is no single standard general-purpose constraint language.
-The choice depends on the individual use case.
-
-\tb{introduction copied from first paper - need to be modified}
+and the Web Ontology Language (OWL 2)\footnote{\url{http://www.w3.org/TR/owl2-syntax/}}.
 

### 2015-01-03 paper/paper 2/paper 2.tex
motivation

@@
 
-Cardinality restrictions can be expressed either generically by description logics (DL) (\ms{generic constraints}) and additional constraints or specifically (\ms{specific constraints}) by domain-specific constraint languages such as OWL 2, DSP, ShEx, ReSh, and SPIN.
-With minimum qualified cardinality restrictions we can state, e.g., that a star fleet captain commands at least one vessel, which may be represented by DL in a logical way:
+Cardinality restrictions can be expressed either generically by description logics (DL) and extensions (\ms{generic constraints}) 
+or specifically  by domain-specific constraint languages such as OWL 2, DSP, ShEx, ReSh, and SPIN (\ms{specific constraints}).
+With minimum qualified cardinality restrictions we can state, 
+e.g., that a starfleet captain commands at least one vessel, which can generically be represented in DL:
 
 \begin{DL}
-$StarFleetCaptain \sqsubseteq \geq1 commandsVessel . Vessel $
+$StarfleetCaptain \sqsubseteq \geq1 commandsVessel . Vessel $
 \end{DL}
 
-The same constraint may also be represented by different constraint languages like OWL 2, ShEx, ReSh, or DSP:
+The same constraint may also be represented specifically by multiple constraint languages like OWL 2, ShEx, ReSh, or DSP:
 
 \begin{ex}
-# OWL 2
-# -----
-StarFleetCaptain
+# OWL 2:
+StarfleetCaptain
     a owl:Restriction ;
@@
 
-# ShEx
-# ----
-StarFleetCaptain { commandsVessel @Vessel{1, } }
+# ShEx:
+StarfleetCaptain { commandsVessel @Vessel{1, } }
 
-# ReSh
-# ----
-StarFleetCaptain a rs:ResourceShape ; rs:property [
+# ReSh:
+StarfleetCaptain a rs:ResourceShape ; rs:property [
     rs:name "commandsVessel" ; rs:propertyDefinition commandsVessel ;
@@
 
-# DSP
-# ---			
-descriptionTemplate a dsp:DescriptionTemplate ; 
-    dsp:resourceClass StarFleetCaptain ; 
+# DSP:
+[   a dsp:DescriptionTemplate ; 
+    dsp:resourceClass StarfleetCaptain ; 
     dsp:statementTemplate [ a dsp:NonLiteralStatementTemplate ;
@@
         dsp:nonLiteralConstraint [ a dsp:NonLiteralConstraint ;
-            dsp:valueClass Vessel ] ] .
+            dsp:valueClass Vessel ] ] ] .
 \end{ex}
 
-As \ms{Janeway} commands the vessel \ms{Voyager} (\ms{commandsVessel(Janeway,Voyager)}) and \ms{Voyager} is defined to be a \ms{Vessel} (\ms{rdf:type(Voyager,Vessel)}), the assignment of \ms{Janeway} to the class \ms{StarFleetCaptain} (\ms{rdf:type(Janeway,StarFleetCaptain)}) does not cause any constraint violation.
-A constraint violation is raised, however, when there is no \ms{commandsVessel} relationship pointing from the individual \ms{Janeway}. 
+As \ms{Janeway} commands the vessel \ms{Voyager} (\ms{commandsVessel(Janeway,Voyager)}) and \ms{Voyager} is a \ms{Vessel} (\ms{rdf:type(Voyager,Vessel)}), the assignment of \ms{Janeway} to the class \ms{StarfleetCaptain} (\ms{rdf:type(Janeway,StarfleetCaptain)}) does not cause a constraint violation.
+A constraint violation is raised, however, when there is not at least one \ms{commandsVessel} relationship with \ms{Janeway} as the subject. 
 A constraint violation is also raised, when there is a triple \ms{commandsVessel(Janeway,Voyager)}, but \ms{Voyager} is not explicitly defined to be a \ms{Vessel}, 
 i.e. the triple \ms{rdf:type(Voyager,Vessel)} is not present in the data. 
-As the object of the \ms{commandsVessel} property is assigned to another class than \ms{Vessel}, 
-the triples \ms{commandsVessel(Sisko,DS9)}, \ms{rdf:type(Sisko,StarFleetCaptain)}, and \ms{rdf:type(DS9,SpaceStation)}  
+As \ms{DS9 is not a} \ms{Vessel}, 
+the triples \ms{commandsVessel(Sisko,DS9)}, \ms{rdf:type(Sisko,StarfleetCaptain)}, and \ms{rdf:type(DS9,SpaceStation)}  
 also cause a constraint violation.
 
-As there is no standard constraint language, constraint designers may choose different constraint languages to express the identical cardinality restriction. 
-When constraint designers choose one constraint language to express an arbitrary constraint, it should be possible to transform this constraint into a constraint expressed by any other constraint language.
-This is important as it is often the case that one constraint designer knows to read and to write constraints in one constraint language very well but not in another constraint language. 
-This way, constraint designers may communicate with each other without the necessity to understand all constraint languages and the interoperability of constraint languages is enhanced.
-
-There are validation environments available enabling to automatically validate RDF constraints expressed by just a few constraint languages such as OWL 2\footnote{\url{purl.org/net/rdfval-demo}\label{footnote1}}, DSP\footref{footnote1}, and ShEx\footnote{\url{http://www.w3.org/2013/ShEx/FancyShExDemo}}.
-It should be possible to validate any RDF constraints expressed by any constraint language automatically and what is even more important in exactly the same manner without any differences.
-
-The following table shows the mapping between the cardinality restriction expressed in DL and the cardinality restriction (\ms{generic constraint}) expressed by a generic constraint language conforming to an ontology to describe any RDF constraint generically (see section~\ref{sec:ontology}).
-Each constraint is either a constraint on classes or a constraint on properties.
+The following table shows the mapping between the cardinality restriction expressed in DL 
+and the cardinality restriction expressed by our developed ontology to describe any RDF constraint generically (see section~\ref{sec:ontology}):
 
 \begin{gcotable}
-property & Captain & commandsVessel & - & Vessel & $\geq$ & 1 \\
+property & StarfleetCaptain & commandsVessel & - & Vessel & $\geq$ & 1 \\
 \end{gcotable}
 
-The cardinality restriction (expressed by the generic constraint language) is represented in RDF as follows:
+According to this ontology, each constraint is either a constraint on classes or a constraint on properties.
+The generically expressed cardinality restriction is represented in RDF as follows:
 
@@
 [   a PropertyConstraint ;
-    contextClass StarFleetCaptain ;
+    contextClass StarfleetCaptain ;
     leftProperties ( commandsVessel ) ;
@@
     constrainingElement ">=" ;
-    constrainingValue "1" ] .
+    constrainingValue 1 ] .
 \end{ex}
 
-We implemented the automatic validation for the cardinality restriction expressed by the generic constraint language within our SPIN validation environment (see SPARQL query above):
+As there is no standard way to formulate RDF constraints, 
+semantically equivalent cardinality restrictions may be represented by different constraint languages. 
+When choosing constraint language \ms{$\alpha$} to express an arbitrary constraint, it should be possible to transform this constraint into a constraint expressed by any other constraint language \ms{$\beta$}.
+This is important as it is often the case that producers and consumers of RDF data are able to read and to write constraints in constraint language \ms{$\alpha$} very well but not in another constraint language \ms{$\beta$}.
+This way, producers and consumers of RDF data may communicate with each other without the necessity to understand all constraint languages and the interoperability of constraint languages is enhanced.
 
+There are validation environments enabling to validate RDF constraints expressed by just a few constraint languages such as OWL 2\footnote{\url{purl.org/net/rdfval-demo}\label{footnote1}}, DSP\footref{footnote1}, and ShEx\footnote{\url{http://www.w3.org/2013/ShEx/FancyShExDemo}}.
+But, it should be possible to validate any RDF constraints expressed by any constraint language and 
+what is even more important to validate them in exactly the same manner without any differences. 
+If we implement the validation of a generic constraint and if we transform a specific constraint into a generic constraint, we are able to validate the specific constraint immediately. 
+As a consequence, we do not have to implement the validation for each specific constraint, as we need to implement the validation only once for each generic constraint. 
+The generically expressed cardinality restriction is validated within our validation environment (see section \ref{sec:validation}) by means of a SPARQL query:
 \begin{ex}
@@
     constrainingValue ?cv ] .
-
 ?subject rdf:type ?cc .
-
 BIND ( qualifiedCardinality( ?subject, ?p1, ?c1 ) AS ?c ) .
@@
 
-If we transform a specific constraint (expressed by any constraint language) into a generic constraint (expressed by the generic constraint language), we will be able to validate the generic constraint and therefore the specific constraint immediately.
-As a consequence, we do not have to specify an automatic validation for each specific constraint, as we need to define an automatic validation only once for each generic constraint. 
-We have to provide an automatic validation for each generic constraint in order to support the automatic validation for each specific constraint.
-
 When domain experts use graphical user interfaces to define constraints in a user-friendly way (without the necessity to express constraints on their own), 
-constraints can be mapped to either a specific or a generic constraint, as for both an automatic validation is provided in the background.    
+constraints can be mapped to either a specific or a generic constraint, as for both the validation is provided in the background.    
 So, the user does not have to know how to express specific constraints using any constraint language.
-If there is a new constraint not covered by any existing constraint language, one can just define the automatic validation for a corresponding generic constraint.
-This way, one is able to extend existing constraint languages and also to define new constraint languages if existing constraint languages are not sufficient to express particular constraints.
+If there is a new constraint not covered by any existing constraint language, one can just define the validation for the corresponding generic constraint.
+This way, one is able to extend existing constraint languages and to define new constraint languages if existing constraint languages are not sufficient to express particular constraints.
 If a language designer develops a new constraint language, 
-the language designer only needs to define a mapping between the new constraint language and the generic constraint language
-in order to be able to automatically validate the constraints expressible by the new constraint language.
+the language designer only needs to define a mapping to the developed ontology
+to be able to automatically validate the constraints expressible by the new constraint language out of the box.
 
@@
 	%\item We present that any RDF constraint can be described by the developed ontology - whether the constraint can be expressed in DL or not 
-	\item We show how to transform specific constraints (expressed by any constraint language A) into generic constraints and into specific constraints (expressed by any other constraint language B)
-  \item We explain that any specific constraint can be validated automatically (if an automatic validation is defined only once for the corresponding generic constraint)
+	\item We show how to transform specific constraints (expressed by any constraint language \ms{$\alpha$}) into generic constraints and into specific constraints (expressed by any other constraint language \ms{$\beta$})
+  \item We explain that any specific constraint can be validated automatically (if the validation is implemented only once for the corresponding generic constraint)
 \end{itemize}
@@
 %\end{itemize}
-
-\textcolor{red}{paper organization}
 
@@
 \section{Automatic Validation of Specific and Generic Constraints}
+\label{sec:validation}
 

### 2015-01-04 paper/paper 2/paper 2.tex
property constraint example

@@
 
-\section{RDF Constraints Ontology} 
+\section{Ontology to Describe RDF Constraints Generically} 
 \label{sec:ontology}
 
-In order to define this ontology to describe RDF constraints generically, it is needed to define the terminology for the formulation of constraints. 
+In order to define an ontology to describe RDF constraints generically, it is needed to define the terminology for the formulation of RDF constraints and to classify them. 
 A \ms{constraint language} is a language which is used to formulate constraints.
-The W3C Data Shapes WG defines \ms{constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
+The W3C Data Shapes working group defines \ms{constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
 We identified four dimensions to classify constraints:
@@
 As there are already five promising constraint languages, our purpose is not to invent a new constraint language.
-We developed a very simple ontology (only three classes, three object properties, and three data properties) which is universal enough to describe any RDF constraint expressible by any RDF constraint language (see the conceptual model in figure \ref{fig:RDF-CO-conceptual-model}).
+We rather developed a very simple ontology (only three classes, three object properties, and three data properties) which is universal enough to describe any RDF constraint expressible by any RDF constraint language (see the conceptual model in figure \ref{fig:RDF-CO-conceptual-model}).
 We call this ontology the \ms{RDF constraints ontology (RDF-CO)}\footnote{Available at: \url{https://github.com/boschthomas/RDF-constraints-ontology}}.
@@
 DL statements representing complex constraints are created out of DL statements representing composed constraints (if expressible in DL). 
-Simple constraints may be applied to either properties \ms{properties constraints} or classes \ms{class constraints}.
+Simple constraints may be applied to either properties (\ms{properties constraints}) or classes (\ms{class constraints}).
 There are no terms representing simple and complex constraints in the RDF-CO, since context classes (associated simple constraints hold for individuals of these classes) of simple constraints may just be reused by further constraints.
@@
 A constraint holds for all individuals of a context class (\ms{contextClass}).
-Consider, e.g., the following cardinality restriction on the property \ms{commandsVessel}, which restricts that a captain must command at least one vessel: 
+Consider, e.g., the following cardinality restriction on the property \ms{commandsVessel}, which restricts Starfleet captains to command at least one vessel: 
 \begin{DL}
-$Captain \sqsubseteq \geq1 commandsVessel . Vessel $
+$StarfleetCaptain \sqsubseteq \geq1 commandsVessel . Vessel $
 \end{DL}
-Mapped to the GCLO the cardinality restriction is classified as a property constraint which holds for individuals of the class \ms{Captain} - the context class:
+Mapped to the RDF-CO the cardinality restriction is classified as a property constraint which holds for individuals of the class \ms{StarfleetCaptain}:
 \begin{gcotable}
-property & Captain & commandsVessel & - & Vessel & $\geq$ & 1 \\
+property & StarfleetCaptain & commandsVessel & - & Vessel & $\geq$ & 1 \\
 \end{gcotable}
-The constraining element (\ms{constrainingElement}) is the operator indicating the actual type of constraint like DL concept and role constructors, (in)equality, and further keywords for constrains which cannot be expressed in DL (e.g.
-regular expressions, constraining facets).
+The constraining element (\ms{constrainingElement}) indicates the actual type of constraint like DL concept and role constructors, (in)equality, and further keywords for constrains which cannot be expressed in DL (e.g.
+regular expressions and constraining facets).
 In some cases, a constraint is only complete when in addition to the constraining element a constraining value (\ms{constrainingValue}) is stated.
 The cardinality restriction 
-\begin{DL}
-$\geq$1 commandsVessel . Vessel
-\end{DL}
+\ms{$\geq$1 commandsVessel.Vessel}
 constructs an anonymous class of all individuals who command at least one vessel.
 Thus, the constraining element of this property constraint is the DL at-least restriction \ms{$\geq$} and the constraining value is \ms{1}.
-\ms{Classes} indicate the list of classes constraints refer to.
-In case of the property constraint above, the qualified cardinality restriction refers to the class \ms{Vessel}, 
-i.e., restricting the objects, the property \ms{commandsVessel} point to, to be of the class \ms{Vessel}.
+\ms{Classes} indicate the list of classes, constraints refer to.
+The qualified cardinality restriction refers to the class \ms{Vessel}, 
+i.e., restricting the objects, the property \ms{commandsVessel} points to, to be of the class \ms{Vessel}.
+
+For property constraints, left and right property lists (\ms{leftProperties}, \ms{rightProperties}) can be specified.
+The assignment of properties to these lists happens relative to the constraining element - which may be an operator (e.g. $\sqsubseteq$ in case of object property paths).
+\ms{Object Property Paths}\footnote{corresponds to the requirement \ms{R-55-OBJECT-PROPERTY-PATHS}} (also called complex role inclusion axioms in DL terminology)
+state that, if an individual x is connected by a sequence of object properties with an individual y, 
+then x is also connected with y by a particular object property. 
+According to the following object property path and some instance data, lieutenant commander \ms{Data} is commanded by captain \ms{Picard} 
+(as \ms{Data} is commanded by commander \ms{Riker} who is commanded by captain \ms{Picard}):
+\begin{DL}
+commandedByCommander $\circ$ commandedByCaptain $\sqsubseteq$ commandedByCaptain 
+\end{DL}
+When mapped to the RDF-CO, the properties \ms{commandedByCommander}, \ms{commandedByCaptain} are on the left side of the constraining element \ms{$\sqsubseteq$},
+and the property \ms{commandedByCaptain} is on the right side:
+
+\begin{gcotable}
+property & $\top$ & commandedByCommander, commandedByCaptain & commandedByCaptain & $\top$ & $\sqsubseteq$ & - \\
+\end{gcotable}
 
@@
 
+\tb{ToDO: too much space before and after DL and table environments}
+
 \bibliography{../../literature/literature}{}

### 2015-01-04 paper/paper 2/paper 2.tex
simple constraints syntactic sugar

@@
 There are simple constraints which cannot be expressed by DL such as literal pattern matching, literal value comparison, literal ranges, default values, and language tag cardinality \cite{BoschNolleAcarEckert2015}.
-
 % maybe additional constraint default values:
@@
 % mathematical operations
-
-There are multiple use cases associated with the requirement to match literals according to given patterns (\ms{Literal Pattern Matching} constraint).
+There are multiple use cases associated with the requirement to match literals according to given patterns (\ms{Literal Pattern Matching}\footnote{corresponds to the requirement \ms{R-44-PATTERN-MATCHING-ON-RDF-LITERALS}}).
 The enterprise vessel, e.g.,  can only have the registry numbers "NCC-1701", "NCC-1701-A", "NCC-1701-B", "NCC-1701-C", "NCC-1701-D", or "NCC-1701-E".
-The universal restriction part of this complex constraint can be expressed by OWL 2 DL:
+The universal restriction can be represented in DL:
 \ms{Enterprise $\sqsubseteq$ $\forall$ registryNumber.RegistryNumber}.
@@
 RegistryNumber
-    a rdfs:Datatype ;
-    owl:equivalentClass [
-        a rdfs:Datatype ;
+    a rdfs:Datatype ; owl:equivalentClass [ a rdfs:Datatype ;
         owl:onDatatype xsd:string ;
-        owl:withRestrictions ( 
-            [ xsd:pattern "NCC-1701([-][A-E])?" ] ) ] .
+        owl:withRestrictions ( [ xsd:pattern "NCC-1701([-][A-E])?" ] ) ] .
 \end{ex}
@@
 but not for the triples \ms{Picard commandsEnterprise Enterprise} and \ms{Enterprise registryNumber "NCC-1701-E"\textasciicircum{}\textasciicircum{}RegistryNumber}.
-The universal restriction and the literal pattern matching constraint are mapped to the generic constraint language as follows:
+The simple constraints - universal restriction and literal pattern matching - are mapped to the RDF-CO as follows:
 
@@
 
-The \ms{Literal Pattern Matching} constraint introduces a new constraining element: \ms{regex}.
-For this new constraining element, an automatic validation must be implemented in SPIN.
+The \ms{Literal Pattern Matching} constraint introduces the new constraining element \ms{regex}.
+For this new constraining element, the validation must be implemented.
 This has to be done once for each constraint which cannot be expressed in DL.
@@
 \ms{Complex constraints} encompass simple constraints and/or complex constraints.
-\textbf{Context-Specific Exclusive OR of Property Groups}\footnote{corresponds to R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC}\textbf{.}
 Exclusive or is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
-Only one of multiple property groups should be present in the data.
+The \ms{Context-Specific Exclusive OR of Property Groups}\footnote{corresponds to R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC} 
+constraint restricts the data to contain only one of multiple property groups.
 Half-Klingons, e.g., either have a klingon mother and a human father or a human mother and a klingon father, which can be expressed by ShEx:
@@
 
-As \ms{B'Elanna Torres} is a \ms{Half-Klingon} with a klingon mother and a human father, this data is valid:
+As \ms{B'Elanna Torres} is a \ms{Half-Klingon} with a klingon mother and a human father, the following data is valid:
 
@@
 
-The constraint expressed by DL can be mapped to a generic constraint:
+The complex constraint (expressed in DL) is mapped to a generic constraint:
 
@@
 
-Almost 15 percent of all RDF constraints are complex constraints which can be simplified and therefore formulated as simple constraints when used in terms of syntactic sugar (see section \ref{sec:evaluation}).
+Almost 15 percent of all RDF constraints are complex constraints which can be simplified and therefore formulated as simple constraints when using them in terms of syntactic sugar (see section \ref{sec:evaluation}).
 
-There three forms of RBox axioms: role inclusions, role equivalences and role disjointness. 
+There are three forms of RBox axioms: role inclusions, equivalences and disjointness. 
 OWL provides a variety of others, namely role transitivity, symmetry, asymmetry, reflexivity and irreflexivity. 
-These are sometimes considered as basic axiom types in DLs as well, using some suggestive notation such as
+These are sometimes considered as basic axiom types in DL as well, using some suggestive notation such as
 \ms{Trans(ancestorOf)} to express that the role ancestorOf is transitive. 
 However, such axioms are just syntactic sugar; 
-all role characteristics can be expressed using the basic features of DLs.
+all role characteristics can be expressed using the basic features of DL.
 \ms{Irreflexive Object Properties}\footnote{corresponds to the requirement \ms{R-60-IRREFLEXIVE-OBJECT-PROPERTIES}}
 restricts that an object property is irreflexive if it is never locally reflexive, i.e. no individual is connected by the object property to itself \cite{Kroetzsch2012}.
-Irreflexivity constraints, stating that individuals cannot be married to themselves, can be represented in DL:
+The irreflexivity constraint, stating that individuals cannot be married to themselves, can be represented in DL:
 
@@
 
-The \ms{Primary Key Properties} constraint is often useful to declare a given (datatype) property as the "primary key" of a class, so that the system can enforce uniqueness. 
-Starfleet officers are uniquely identified by their command authorization code (e.g. to activate and cancel auto-destruct sequences).
-It means that the property \ms{commandAuthorizationCode} is inverse functional - mapped to DL and RDF-CO as follows:
+The \ms{Primary Key Properties} constraint is often useful to declare a given (datatype) property as the "primary key" of a class, so that a system can enforce uniqueness. 
+Starfleet officers, e.g., are uniquely identified by their command authorization code (e.g. to activate and cancel auto-destruct sequences).
+It means that the property \ms{commandAuthorizationCode} is inverse functional - mapped to DL and the RDF-CO as follows:
 
@@
 \begin{gcotable}
-property & $\top$ & commandAuthorizationCode$^{-}$ & commandAuthorizationCode & - & inverse & - \\
+property & $\top$ & commandAuthorizationCode$^{-}$ & commandAuthorizationCode$^{-}$ & - & inverse & - \\
 property & $\top$ & commandAuthorizationCode$^{-}$ & - & - & functional & - \\
@@
 
-Keys are even more general, i.e., a generalization of inverse functional properties\footnote{\url{http://www.w3.org/TR/2012/REC-owl2-rdf-based-semantics-20121211/#Semantic_Conditions_for_Keys}}.
+Keys, however, are even more general, i.e., a generalization of inverse functional properties \cite{Schneider2009}.
 A key can be a datatype property, an object property, or a chain of properties.
@@
 DL is extended with \ms{key boxes} and a special \ms{keyfor} construct\cite{Lutz2005}.
-This leads to the following DL and RDF-CO mappings (only one simple property constraint) for the example:
+This leads to the following DL and RDF-CO mappings (only one simple property constraint):
 

### 2015-01-04 paper/paper 2/paper 2.tex
transformations

@@
   \sffamily
-  \vspace{0.3cm}
+  \vspace{0cm}
   \begin{tabular}{l|l|l|l|l|l}
@@
   \end{tabular}
-  \linebreak
 }
@@
   \sffamily
-  \vspace{0.3cm}
+  \vspace{0cm}
 	\begin{center}
@@
   %\sffamily
-  \vspace{0.3cm}
+  \vspace{0cm}
 	\begin{center}
@@
   %\sffamily
-  %\vspace{0.3cm}
+  \vspace{0cm}
 	\begin{center}
@@
 RDF data providers ensure that their data conforms to constraints which are part of the contract between the providers and the consumers of that data.
-As there is no standard way, these constraints may be represented by multiple constraint languages (there are even more than the five promising ones)\footnote{i.a.
-Bibframe, DQTP, Pellet ICV, RDFUnit, SPARQL, Stardog ICV}.
+As there is no standard way, these constraints may be represented by multiple constraint languages (there are even more than the five promising ones\footnote{i.a.
+Bibframe, DQTP, Pellet ICV, RDFUnit, SPARQL, Stardog ICV}).
 There is an obvious need to transform a specific constraint (\ms{$sc_{\alpha}$}) (expressed by any constraint language \ms{$\alpha$}) into a specific constraint (\ms{$sc_{\beta}$}) (expressed by any constraint language \ms{$\beta$}) - when they have the same semantics.
-We use the RDF-CO as intermediate language for these transformations.
-If we define mappings ($m(sc_{\alpha}), m(sc_{\beta})$) from these two specific constraints to the corresponding generic constraint (\ms{gc}),
+We use the RDF-CO as intermediate representation for these transformations.
+If we define mappings ($m(sc_{\alpha}), m(sc_{\beta})$) from two equivalent specific constraints to the corresponding generic constraint (\ms{gc}),
 we can convert them automatically:
@@
 
-We do not need to define mappings for each pair of semantically equivalent specific constraint.
+We do not need to define mappings for each pair of semantically equivalent specific constraints.
 Let's assume we are able to express a constraint by 5/6/7/8/9/10 constraint languages.
-Without the intermediate generic constraint, we would have to define one mapping for each pair of specific constraints expressed by a specific constraint language
-- that are \ms{\( {n \choose 2} \)} mappings for each constraint (example: 10/15/21/28/36/45).
-With an intermediate generic constraint, we only need to define \ms{n} mappings from the specific constraints to the generic constraint (example: 5/6/7/8/9/10 ).
+Without the intermediate generic constraint, we would have to define one mapping for each pair of specific constraints expressed by a different constraint languages
+- that are \ms{\( {n \choose 2} \)} mappings for each constraint (10/15/21/28/36/45 mappings).
+With an intermediate generic constraint, we only need to define \ms{n} mappings (one mapping for each specific constraint) from the specific constraints to the generic constraint (5/6/7/8/9/10 mappings).
 
@@
 
-First, we map these DL statements to two simple constraints corresponding to the RDF-CO (we define the class \ms{EnterpriseCaptains} by simply enumerating its instances):
+First, we map these DL statements to two simple generic constraints corresponding to the RDF-CO (we define the class \ms{EnterpriseCaptains} by simply enumerating its instances):
 
@@
 \tb{ToDO: too much space before and after DL and table environments}
+\tb{ToDo: there are no line breaks for ms environment}
 

### 2015-01-04 paper/paper 2/paper 2.tex
validation

@@
 
-\section{Automatic Validation of Specific and Generic Constraints}
+\section{Validation of Specific and Generic Constraints}
 \label{sec:validation}
 
-We can provide an automatic validation of all specific constraints (expressed by any constraint language) by defining a mapping to SPIN.
+We can provide the validation of all specific constraints (expressed by any constraint language) by defining a mapping to SPIN.
 That's what we have done for all OWL 2 and DSP constructs (see section \ref{sec:implementation}).
@@
 But, if we define a mapping from a specific constraint to the corresponding generic constraint and if we define a mapping from the generic constraint to SPIN,
-we do not have to define a mapping to SPIN for that specific constraint - we can perform an automatic validation for the generic and for the specific constraint as well.
+we do not have to define a mapping to SPIN for that specific constraint - 
+we are able to validate the generic as well as the specific constraint.
 As a consequence, we only have to define one SPIN mapping for each constraint corresponding to a requirement within the RDF validation requirements database.
 19 of 74 RDF constraints can be expressed by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
-This means, that there must be 76 (four for each constraint) implementations to validate  these constraints - instead of only 19 (one for each constraint).
+This means, that there must be 76 (four for each constraint) implementations to validate 76 specific constraints - instead of only 19 implementations (one for each generic constraint).
 
 Within our SPIN validation environment, we define a SPIN construct template for each generic constraint\footnote{for details about the SPIN validation environment see \cite{BoschEckert2014-2}}.
-The SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples (\ms{spin:ConstraintViolation}) indicating the subject (\ms{spin:violationRoot}) and the properties (\ms{spin:violationPath}), causing the constraint violation, and the reason why the constraint violation has been raised (\ms{rdfs:label}).
-The SPIN construct template creates the constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
+A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples (\ms{spin:ConstraintViolation}) indicating the subject (\ms{spin:violationRoot}) and the properties (\ms{spin:violationPath}), causing constraint violations, and the reason why constraint violations have been raised (\ms{rdfs:label}).
+A SPIN construct template creates constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
 The SPARQL CONSTRUCT query for the universal quantification (of the previous example in section \ref{sec:transformations}) is shown below:
@@
 
-As a consequence, the validation results do not differ for semantically equivalent constraints when they are based on multiple validation implementations, as there is only one validation implementation for each constraint - independent from the used constraint language.
+As a consequence, the validation results do not differ for semantically equivalent constraints expressed by multiple constraint languages,
+as we provide only one validation implementation for each generic constraint.
 

### 2015-01-04 paper/paper 2/paper 2.tex
evaluation

@@
 SPIN represents both the SPIN mappings and the SPARQL queries in RDF. 
-Within the validation environment, we fully implemented an automatic validation of all OWL 2 DL\footnote{OWL 2 SPIN mapping: \url{https://github.com/boschthomas/OWL2-SPIN-Mapping}} and DSP\footnote{DSP SPIN mapping: \url{https://github.com/dcmi/DSP-SPIN-Mapping}} constructs (for the complete DSP validation see \cite{BoschEckert2014-2}).
+Within the validation environment, we fully implemented the validation of all OWL 2 DL\footnote{OWL 2 SPIN mapping: \url{https://github.com/boschthomas/OWL2-SPIN-Mapping}} and DSP\footnote{DSP SPIN mapping: \url{https://github.com/dcmi/DSP-SPIN-Mapping}} constructs (for the complete DSP validation see \cite{BoschEckert2014-2}).
 The implementation can be tested at \url{http://purl.org/net/rdfval-demo}.
@@
 
-We provide a mapping from the generic constraint language to SPIN\footnote{GCL SPIN mapping: \url{https://github.com/boschthomas/GCL-SPIN-Mapping}} in order to automatically validate each type of generic constraint (simple, complex, property, and class constraints).
+We provide a mapping from RDF-CO to SPIN\footnote{RDF-CO SPIN mapping: \url{https://github.com/boschthomas/RDF-CO-SPIN-Mapping}} in order to automatically validate each type of generic constraint (simple, complex, property, and class constraints).
 Part of future work will be 
-\begin{itemize}
-	\item to provide a GUI which generates generic constraints automatically according to inputs of domain experts who are not familiar with the formulation of constraints.
-	\item to offer bidirectional transformations between specific constraints (expressed by multiple constraint languages) and generic constraints. 
-	\item to provide translations between specific constraints (expressed by any specific constraint language) by using generic constraints as an intermediate transformation step.
-\end{itemize}
-
+(1) to provide a GUI which generates generic constraints automatically according to inputs of domain experts who are not familiar with the formulation of constraints; 
+(2) to offer bidirectional transformations between specific constraints (expressed by multiple constraint languages) and generic constraints;
+(3) to provide translations between specific constraints (expressed by any specific constraint language) by using generic constraints as an intermediate transformation step.
+%\begin{itemize}
+	%\item to provide a GUI which generates generic constraints automatically according to inputs of domain experts who are not familiar with the formulation of constraints.
+	%\item to offer bidirectional transformations between specific constraints (expressed by multiple constraint languages) and generic constraints. 
+	%\item to provide translations between specific constraints (expressed by any specific constraint language) by using generic constraints as an intermediate transformation step.
+%\end{itemize}
 \section{Evaluation}
@@
 If a constraint can be expressed in DL, we added the mapping to DL and to the generic constraint.
-If a constraint cannot be expressed in DL, we added a mapping to the generic constraint.
+If a constraint cannot be expressed in DL, we only added the mapping to the generic constraint.
 Therefore, we show that each constraint can be mapped to a generic constraint.
-The following table shows the absolute number and the relative percentage for the three dimensions to classify constraints:
+The following table shows the absolute numbers and the relative percentages for each of the three dimensions to classify constraints:
 
@@
 Constraints can be classified as \ms{property constraints} and \ms{class constraints}.
-Two thirds are property constraints, one fifth class constraints, and approx. 10\% are composed of both property and class constraints.
-Constraints may be either atomic (\ms{simple constraints}) or created out of simple and complex constraints (\ms{complex constraints}).
+Two thirds of the total amount of constraints are property constraints, one fifth are class constraints, and approx. 10\% are composed of both property and class constraints.
+Constraints may be either atomic (\ms{simple constraints}) or created out of simple and/or complex constraints (\ms{complex constraints}).
 Almost two thirds are simple constraints, a quarter are complex constraints.
-Almost 15 percent are complex constraints which can be formulated as simple constraints when used in terms of syntactic sugar.
+Almost 15 percent are complex constraints which can be formulated as simple constraints when using them in terms of syntactic sugar.
 Constraints can either be expressible in DL or not.

### 2015-01-05 paper/RDF validation requirements/RDF validation requirements.tex
abstract introduction motivation

@@
 \begin{abstract}
-
-\keywords{..}
+There are many case studies for which the formulation of RDF constraints and the validation of RDF data conforming to these constraint is very important.  
+The W3C and the DCMI working groups on RDF validation identified many RDF validation requirements,
+whereupon we initiate an RDF validation requirements database which is available to contribute at \url{http://purl.org/net/rdf-validation}.
+The intention of this database is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation.
+Although, there are multiple constraint languages which can be used to formulate RDF constraints (associated with these requirements), 
+there is no standard way to formulate RDF constraints.
+
+This paper serves to evaluate to which extend each requirement is satisfied by each of these constraining languages.
+We take reasoning into account as a pre-validation step and distinguish between OWL 2 QL and OWL 2 DL constructs to express particular constraints.
+We classify constraints according to a developed classification mechanism for constraints.
+We show that each constraint can be mapped to an ontology describing RDF constraints generically.
+If a constraint can be expressed in DL, we add the mapping to DL and to the generic constraint in order to logically underpin associated requirements.
+If a constraint cannot be expressed in DL, we only add the mapping to the generic constraint.
+
+\keywords{RDF Validation, RDF Validation Requirements, RDF Constraints, Constraint Languages, Evaluation, Linked Data, Semantic Web}
 \end{abstract}
@@
 
+\section{Introduction}
+
+\tb{why is the references section not shown? / references are not resolved}
+
+The purpose of ontologies is to perform reasoning on RDF data and not to validate RDF data conforming to these ontologies.
+For RDF, we cannot use ontologies like we use XML Schemas, DTDs, RELAX NG, or Schematron to validate XML documents.
+The W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
+where experts from industry, government, and academia discussed first use cases for RDF constraint formulation and validation.
+In 2014, two working groups on RDF validation have been established: 
+the W3C RDF Data Shapes WG\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles WG\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
+
+Bosch and Eckert \cite{BoschEckert2014} collected the findings of these working groups and initiated a database of requirements to formulate and validate RDF constraints
+which is available for contribution at \url{http://purl.org/net/rdf-validation}.
+The intention associated with this database is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
+The requirements are classified to better evaluate existing solutions. 
+We mapped each requirement to formulate RDF constraints directly to an RDF constraint.
+
+There is no constraint language which can be seen as the standard.
+Although, there are multiple constraint languages (having different syntaxes and semantics) which can be used to express RDF constraints, such as existential and universal quantification, cardinality restrictions, and exclusive or of properties.
+The five most promising ones on being the standard are
+Description Set Profiles (DSP)\footnote{\url{http://dublincore.org/documents/2008/03/31/dc-dsp/}},
+Resource Shapes (ReSh)\footnote{\url{http://www.w3.org/Submission/shapes/}}, 
+Shape Expressions (ShEx)\footnote{\url{http://www.w3.org/Submission/shex-primer/}},
+the SPARQL Inferencing Notation (SPIN)\footnote{\url{http://spinrdf.org/}}, 
+and the Web Ontology Language (OWL 2)\footnote{\url{http://www.w3.org/TR/owl2-syntax/}}.
+
 \section{Motivation}
 
-\begin{itemize}
-	\item mappings from RDF validation requirements (more specifically RDF constraint formulation requirements) to DL
-	\item mappings from RDF validation requirements (more specifically RDF constraint formulation requirements) to generic constraints (expressed by generic constraint language)
-\end{itemize}
+In this paper, we describe each requirement within the RDF validation requirements database in detail (sections 3-76).
+Each requirement corresponds to an RDF constraint which may be expressible by multiple constraint languages.
+For each requirement, we represent some examples in different constraint languages.
+
+We evaluated to which extend the most promising five constraint languages fulfill each of the overall 74 requirements to formulate RDF constraints (section \ref{sec:evaluation-1}).
+We distinguished if a constraint is fulfilled by OWL 2 QL or if the more expressive OWL 2 DL is needed. 
+We also take reasoning into account, as reasoning may be performed prior to validating constraints.
+
+In order to define an ontology to describe RDF constraints generically, it is needed to define the terminology for the formulation of RDF constraints and to classify them. 
+A \ms{constraint language} is a language which is used to formulate constraints.
+The W3C Data Shapes working group defines \ms{constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
+We identified four dimensions to classify constraints:
+\begin{itemize}
+  \item \ms{Universality:} specific constraints vs. generic constraints
+	\item \ms{Complexity:} simple constraints vs. complex constraints
+	\item \ms{Context:} property constraints vs. class constraints
+	\item \ms{DL Expressivity:} constraints expressible in DL vs. constraints not expressible in DL
+\end{itemize}
+
+As there are already five promising constraint languages, our purpose is not to invent a new constraint language.
+We rather developed a very simple ontology (only three classes, three object properties, and three data properties) which is universal enough to describe any RDF constraint expressible by any RDF constraint language.
+We call this ontology the \ms{RDF constraints ontology (RDF-CO)}\footnote{Available at: \url{https://github.com/boschthomas/RDF-constraints-ontology}}.
+
+\ms{Specific constraints} are expressed by specific constraint languages like DSP, OWL 2, ReSh, ShEx, and SPIN.
+\ms{Generic constraints} are expressed by the RDF-CO.
+As RDF-CO describes constraints generically, RDF-CO does not distinguish constraints according to the dimension \ms{universality}. 
+The majority of constraints can be expressed in DL.
+In contrast, there are constraints which cannot be expressed in DL, but are also representable by the RDF-CO. 
+\ms{Complex constraints} encompass \ms{simple constraints} (atomic constraints) and/or further complex constraints.
+DL statements representing complex constraints are created out of DL statements representing composed constraints (if expressible in DL). 
+Simple constraints may be applied to either properties (\ms{properties constraints}) or classes (\ms{class constraints}).
+There are no terms representing simple and complex constraints in the RDF-CO, since context classes (associated simple constraints hold for individuals of these classes) of simple constraints may just be reused by further constraints.
+As a consequence, the distinction of property and class constraints is sufficient to describe all possible RDF constraints.
+
+In this paper, we investigate which constraints can be expressed in DL and which not.
+If a constraint can be expressed in DL, we added the mapping to DL and to the generic constraint in order to logically underpin associated requirements.
+If a constraint cannot be expressed in DL, we only added the mapping to the generic constraint.
+Therefore, we show that each constraint can be mapped to a generic constraint.
+In section \ref{sec:evaluation-2} we classify the constraints according to the dimensions to classify constraints.
 
@@
 
-We evaluated to which extend the most promising five DSCLs fulfill each requirement.
+\subsection{Evaluation of Constraint Languages}
+\label{sec:evaluation-1}
+
+We evaluated to which extend the most promising five constraint languages fulfill each requirement.
 Tilde means that this constraint may be fulfilled by that particular constraint language - either by limitations, workarounds, or extensions.
@@
 
-\subsection{Generic Constraints}
+\subsection{Evaluation of Constraints Classes}
+\label{sec:evaluation-2}
+
+We evaluated to which extend the most promising five constraint languages fulfill each of the overall 74 requirements to formulate RDF constraints \cite{BoschNolleAcarEckert2015}.
+If a constraint can be expressed in DL, we added the mapping to DL and to the generic constraint.
+If a constraint cannot be expressed in DL, we only added the mapping to the generic constraint.
+Therefore, we show that each constraint can be mapped to a generic constraint.
+The following table shows the absolute numbers and the relative percentages for each of the three dimensions to classify constraints:
 
@@
 \end{evaluation-generic}
+
+Constraints can be classified as \ms{property constraints} and \ms{class constraints}.
+Two thirds of the total amount of constraints are property constraints, one fifth are class constraints, and approx. 10\% are composed of both property and class constraints.
+Constraints may be either atomic (\ms{simple constraints}) or created out of simple and/or complex constraints (\ms{complex constraints}).
+Almost two thirds are simple constraints, a quarter are complex constraints.
+Almost 15 percent are complex constraints which can be formulated as simple constraints when using them in terms of syntactic sugar.
+Constraints can either be expressible in DL or not.
+The majority - nearly 70\% - of the overall constraints are expressible in DL.
 
@@
 
+\section{Conclusion and Future Work}
+
 \end{document}
-
-\input{DL-Check}
 

### 2015-01-05 paper/RDF validation requirements/RDF validation requirements.tex
finalize RDF validation requirements paper

@@
   \sffamily
-  \vspace{0.3cm}\linebreak
+  \vspace{0cm}\linebreak
   \begin{tabular}{l|l|l|l|l|l}
@@
   \sffamily
-  \vspace{0.3cm}
+  \vspace{0cm}
 	\begin{center}
+	\textbf{\vspace{0.4cm}Mapping to RDF-CO:} \\
   \begin{tabular}{l|l|l|l|l|l|l}
@@
 
-\ms{Subsumption} corresponds to the requirement \ms{R-100-SUBSUMPTION}.
-
-\begin{itemize}
-	\item DL terminology: concept inclusion
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{itemize}
-	\item all mothers are parents
-  \item the concept Mother is subsumed by the concept Parent
-\end{itemize}
+\ms{Subsumption} (DL terminology: \ms{concept inclusion}) corresponds to the requirement \ms{R-100-SUBSUMPTION}.
+A subclass axiom SubClassOf( CE1 CE2 ) states that the class expression CE1 is a subclass of the class expression CE2. 
+Roughly speaking, this states that CE1 is more specific than CE2.
+
+\subsection{Simple Example}
+
+All mothers are parents.
+The concept \ms{Mother} is subsumed by the concept \ms{Parent}:
 
@@
 
-Jedis feel the force.
+Jedis feel the force:
 
@@
 
-\begin{ex}
-# DSP
-# ---
--
-\end{ex}
-
-\begin{ex}
-# OWL2
-# ----
+Expressed by multiple constraint languages:
+
+\begin{ex}
+# OWL2:
 Jedi rdfs:subClassOf FeelingForce .
@@
 \begin{ex}
-# ReSh
-# ----
+# ReSh:
 the extension ext:extendsShape may be used
@@
 \begin{ex}
-# ShEx
-# ----
+# ShEx:
 FeelingForce {
@@
 
-\begin{ex}
-# data
-# ----
+Data matching the shapes \ms{FeelingForce} and \ms{Jedi}:
+
+\begin{ex}
 Yoda 
@@
 
+If an individual is rich, then this individual is not poor:
+
 \begin{DL}
@@
 
-requirement:
-
-\begin{itemize}
-	\item R-3-EQUIVALENT-CLASSES
-\end{itemize}
-
+\ms{Class Equivalence} corresponds to the requirement \ms{R-3-EQUIVALENT-CLASSES}.
 Concept equivalence asserts that two concepts have the same instances \cite{Kroetzsch2012}.
 While synonyms are an obvious example of equivalent concepts, in practice one more
-often uses concept equivalence to give a name to complex expression  \cite{Kroetzsch2012}.
+often uses concept equivalence to give a name to complex expressions \cite{Kroetzsch2012}.
 Concept equivalence is indeed subsumption from left and right ($A \sqsubseteq B$ and $B \sqsubseteq A$ implies $A \equiv B$ ).
@@
 
-\section{Sub Object Properties}
-
-requirements:
-
-\begin{itemize}
-
-	\item R-54-SUB-OBJECT-PROPERTIES
-\end{itemize}
-
-\begin{itemize}
-	\item DL terminology: role inclusion 
-\end{itemize}
+\section{Sub Properties}
+
+\ms{Sub Properties} (DL terminology: \ms{role inclusion}) correspond to the requirements \ms{R-54-SUB-OBJECT-PROPERTIES} and \ms{R-54-SUB-DATA-PROPERTIES}.
+Subproperty axioms are analogous to subclass axioms.
+These axioms state that the property expression PE1 is a subproperty of the property expression PE2 — that is, if an individual x is connected by PE1 to an individual or a literal y, then x is also connected by PE2 to y.
 
@@
 
-\section{Sub Data Properties}
-
-requirements:
-
-\begin{itemize}
-
-	\item R-54-SUB-DATA-PROPERTIES
-\end{itemize}
-
-\begin{itemize}
-	\item DL terminology: concrete domains functional roles  
-\end{itemize}
+%\begin{itemize}
+	%\item DL terminology: concrete domains functional roles  
+%\end{itemize}
 
 \subsection{Complex Example}
+
 \begin{DL}
@@
 
-\section{Object Property Paths / Object Property Chains}
-
-requirement:
-
-\begin{itemize}
-	\item R-55-OBJECT-PROPERTY-PATHS
-\end{itemize}
-
-\begin{itemize}
-  \item DL terminology: complex role inclusion axiom / role composition
-	\item role composition can only appear on the left-hand side of complex role inclusions \cite{Kroetzsch2012}
-\end{itemize}
+\section{Object Property Paths}
+
+\ms{Object Property Paths} (or Object Property Chains and in DL terminology complex role inclusion axiom or role composition)
+corresponds to the requirement \ms{R-55-OBJECT-PROPERTY-PATHS}.
+The more complex form of sub properties.
+This axiom states that, if an individual x is connected by a sequence of object property expressions OPE1, ..., OPEn with an individual y, then x is also connected with y by the object property expression OPE.
+Role composition can only appear on the left-hand side of complex role inclusions \cite{Kroetzsch2012}.
 
@@
 \begin{ex}
-# OWL2
-# ----
-:uncleOf owl:propertyChainAxiom ( :brotherOf :parentOf ) . 
+# OWL2:
+uncleOf owl:propertyChainAxiom ( brotherOf parentOf ) . 
 \end{ex}
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-9-DISJOINT-PROPERTIES
-\end{itemize}
-
-\subsection{Simple Example}
+\ms{Disjoint Properties} corresponds to the requirement \ms{R-9-DISJOINT-PROPERTIES}.
+A disjoint properties axiom states that all of the properties are pairwise disjoint; 
+that is, no individual x can be connected to an individual y by these properties.
+
+\subsection{Simple Example}
+
+The object properties \ms{parentOf} and \ms{childOf} are disjoint:
 
@@
 Disjoint(parentOf, childOf)\\
-Alternative:\\
+\end{DL}
+
+or alternatively:
+
+\begin{DL}
 $parentOf \sqsubseteq \neg childOf$
@@
 
-syntactic sugar (preferred):
+syntactic sugar:
 
@@
 
-requirements:
-
-\begin{itemize}
-  \item R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS
-	\item R-16-CONJUNCTION-OF-DATA-RANGES
-\end{itemize}
-
-\begin{itemize}
-	\item composition / conjunction
-\end{itemize}
-
+\ms{Intersection} (composition, conjunction) corresponds to the requirements \ms{R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS} and \ms{R-16-CONJUNCTION-OF-DATA-RANGES}.
 DLs allow new concepts and roles to be
@@
 concepts, one can further separate basic Boolean constructors, role restrictions and nominals/enumerations \cite{Kroetzsch2012}.
-
 Boolean concept constructors provide basic boolean operations that are closely related to
@@
 
-concept inclusions allow us to state that all mothers are female and that
+Concept inclusions allow us to state that all mothers are female and that
 all mothers are parents, but what we really mean is that mothers are exactly the female
@@
 
-Complex concept of all individuals which are of the concept Female and of the concept Parent.
+Complex concept of all individuals which are of the concept \ms{Female} and of the concept \ms{Parent}.
 
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS
-	\item R-18-DISJUNCTION-OF-DATA-RANGES
-\end{itemize}
-
-\begin{itemize}
-	\item synonyms: union / inclusive OR
-	\item disjunction of classes, data ranges
-\end{itemize}
+\ms{Disjunction} of classes or data ranges corresponds to the requirements \\
+\ms{R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS} and \ms{R-18-DISJUNCTION-OF-DATA-RANGES}.
+Synonyms are union and inclusive or.
 
@@
 
-requirements:
-
-\begin{itemize}
-  \item R-19-NEGATION-OF-CLASS-EXPRESSIONS
-	\item R-20-NEGATION-OF-DATA-RANGES
-\end{itemize}
-
-\begin{itemize}
-	\item synonym: complement
-\end{itemize}
+\ms{Negation} (complement) corresponds to the requirements \ms{R-19-NEGATION-OF-CLASS-EXPRESSIONS} and \ms{R-20-NEGATION-OF-DATA-RANGES}.
 
@@
 
-set of all individuals that are not married.
+Set of all individuals that are not married.
 
@@
 \end{DL}
+
+All female individuals that are not married.
 
@@
 
-requirement \ms{R-7-DISJOINT-CLASSES}
-
-\subsection{Simple Example}
+\ms{Disjoint Classes} corresponds to the requirement \ms{R-7-DISJOINT-CLASSES}.
+A disjoint classes axiom states that all of the classes are pairwise disjoint; 
+that is, no individual can be at the same time an instance of these classes.
+
+\subsection{Simple Example}
+
+Individuals cannot be male and female at the same time:
 
@@
 Male $\sqcap$ Female $\sqsubseteq$ $\perp$\\
-Alternative:\\
+\end{DL}
+
+or alternatively:
+
+\begin{DL}
 $Male \sqsubseteq \neg Female$
@@
 
+One can either be a hologram or a human, but not both:
+
 \begin{DL}
 Hologram $\sqcap$ Human $\sqsubseteq$ $\perp$\\
-Alternative:\\
+\end{DL}
+
+or alternatively:
+
+\begin{DL}
 $Hologram \sqsubseteq \neg Human$
@@
 
-\ms{Existential Quantification on Properties} conforms to the requirement \ms{R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}
+\ms{Existential Quantification on Properties} conforms to the requirement \\
+\ms{R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}.
 In DL terminology the \ms{existential quantification} is alco called \ms{existential restriction}.
-An existential class expression ObjectSomeValuesFrom( OPE CE ) consists of an object property expression OPE and a class expression CE, and it contains all those individuals that are connected by OPE to an individual that is an instance of CE.
-Such a class expression can be seen as a syntactic shortcut for the class expression ObjectMinCardinality( 1 OPE CE ).
-An existential class expression DataSomeValuesFrom( DPE1 ...
-DPEn DR ) consists of n data property expressions DPEi, 1 $\leq$ i $\leq$ n, and a data range DR whose arity MUST be n.
-Such a class expression contains all those individuals that are connected by DPEi to literals lti, 1 $\leq$ i $\leq$ n, such that the tuple ( lt1 , ..., ltn ) is in DR.
-A class expression of the form DataSomeValuesFrom( DPE DR ) can be seen as a syntactic shortcut for the class expression DataMinCardinality( 1 DPE DR ).
+An existential class expression consists of a property expression and a class expression or a data range, and it contains all those individuals that are connected by the property expression to an individual that is an instance of the class expression or to literals that are in the data range.
 
@@
 
-complex concept that describes the set
+Complex concept that describes the set
 of individuals that are parents of at least one individual (instance of $\top$).
@@
 
-the complex concept describes those individuals that are parents of at least one
+The complex concept describes those individuals that are parents of at least one
 female individual, i.e., those that have a daughter.
@@
 
-\ms{Universal Quantification on Properties} corresponds to the requirement \ms{R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}, which is called \ms{value restriction} in DL terminology.
+\ms{Universal Quantification on Properties} corresponds to the requirement \ms{R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}, 
+which is also called \ms{value} \ms{restriction} in DL terminology.
 
@@
 
-\begin{itemize}
-	\item set of individuals all of whose children are female
-  \item also includes those that have no children at all
-\end{itemize}
+The set of individuals all of whose children are female also includes those that have no children at all.
 
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-25-OBJECT-PROPERTY-DOMAIN
-	\item R-26-DATA-PROPERTY-DOMAIN
-\end{itemize}
-
-\begin{itemize}
-	\item restrict domain of object and data properties
-	\item DL terminology: domain restrictions on roles
-	\item The language needs to include an easy-to-use vocabulary to declare that a given property is associated with a class, e.g.
+\ms{Property Domain} corresponds to the requirements \ms{R-25-OBJECT-PROPERTY-DOMAIN} and \ms{R-26-DATA-PROPERTY-DOMAIN}.
+The constraint restricts the domain of object and data properties.
+In DL terminology this constraint is also called domain restrictions on roles.
+The purpose is to declare that a given property is associated with a class, e.g.
 to populate input forms with appropriate widgets but also constraint checking.
 In OO terms this is the declaration of a member, field, attribute or association.
-\end{itemize}
-
 $\exists R. \top \sqsubseteq C$ is the object property restriction where $R$ is the object property (role) whose domain is restricted to concept $C$.
@@
 
-\begin{itemize}
-	\item restrict the domain of sonOf to male individual
-\end{itemize}
+Restricts the domain of \ms{sonOf} to male individual.
 
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-28-OBJECT-PROPERTY-RANGE
-	\item R-35-DATA-PROPERTY-RANGE
-\end{itemize}
-
-\begin{itemize}
-	\item restrict range of object and data properties
-	\item DL terminology: range restrictions on roles
-\end{itemize}
-
-$\top \sqsubseteq \forall R . C$ is the range restriction to object property $R$ (restricted by concept $C$).
+\ms{Property Range} corresponds to the requirements \ms{R-28-OBJECT-PROPERTY-RANGE} and \ms{R-35-DATA-PROPERTY-RANGE}.
+This constraint restricts the range of object and data properties
+In DL terminology it is also called range restrictions on roles.
+$\top \sqsubseteq \forall R . C$ is the range restriction to the object property $R$ (restricted by the concept $C$).
 
@@
 $\top$ $\sqsubseteq$ $\forall$ sonOf . Parent \\
-Equivalent to:\\
+\end{DL}
+
+equivalent to:
+
+\begin{DL}
 $\exists sonOf\sp{\overline{\ }}.\top \sqsubseteq Person$
@@
 
-\begin{itemize}
-	\item restrict the range of sonOf to parents
-\end{itemize}
-
-\begin{ex}
-# OWL 2
-# -----
+Restricts the range of \ms{sonOf} to parents.
+
+\begin{ex}
+# OWL 2:
 sonOf rdfs:range Parent . 
@@
 \begin{ex}
-# DSP
-# ---
+# DSP:
 :hasDogRange
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS
-	\item R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS
-\end{itemize}
-
-\begin{itemize}
-  \item restrict range of object and data properties for individuals within specific context
-	\item context: e.g. class
-	\item The values of each member property of a class may be limited by their value type, such as xsd:string or ex:Person. 
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{itemize}
-	\item property 'sonOf'
-	\item context: class 'Man'
-	\item range: class 'Parent'
-	\item $\rightarrow$ individuals of the class 'Man' can only have 'sonOf' relationships to indivuduals of the class 'Parent'
-\end{itemize}
+\ms{Class-Specific Property Range} corresponds to the requirements
+\ms{R-29-CLASS-} \ms{SPECIFIC-RANGE-OF-RDF-OBJECTS} and \ms{R-36-CLASS-SPECIFIC-RANGE-OF-RDF-} \ms{LITERALS}.
+The constraint restricts the range of object and data properties for individuals within a specific context (e.g. class, application profile).
+The values of each member property of a class may be limited by their value type, such as xsd:string or Person.
+
+\subsection{Simple Example}
 
@@
 
+Individuals of the class \ms{Man} (context class) can only have \ms{sonOf} relationships to individuals of the class \ms{Parent} (range class).
+
 \section{Minimum Unqualified Cardinality Restrictions on Properties}
 
-requirements:
-
-\begin{itemize}
-	\item R-81-MINIMUM-UNQUALIFIED-CARDINALITY-ON-PROPERTIES
-	\item R-211-CARDINALITY-CONSTRAINTS
-\end{itemize}
-
-Definition:\\
-
-$\leq n R. \top$ is minimum unqualified cardinality restriction where $n \in \mathbb{N}$ (written $\leq  n R$ in short).
-
-description:
-
-\begin{itemize}
-	\item A minimum cardinality expression ObjectMinCardinality( n OPE CE ) consists of a nonnegative integer n, an object property expression OPE, and a class expression CE, and it contains all those individuals that are connected by OPE to at least n different individuals that are instances of CE.
-If CE is missing, it is taken to be owl:Thing.
-	\item A minimum cardinality expression DataMinCardinality( n DPE DR ) consists of a nonnegative integer n, a data property expression DPE, and a unary data range DR, and it contains all those individuals that are connected by DPE to at least n different literals in DR.
-If DR is not present, it is taken to be rdfs:Literal.
-	\item unqualified: CE respective DR is NOT stated. 
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
-# ShEx
-# ----
+\ms{Minimum Unqualified Cardinality Restrictions on Properties}
+corresponds to the requirements
+\ms{R-81-MINIMUM-UNQUALIFIED-CARDINALITY-ON-PROPERTIES} and
+\ms{R-211-CARDINALITY-CONSTRAINTS}.
+$\leq n R. \top$ is the minimum unqualified cardinality restriction where $n \in \mathbb{N}$ (written $\leq  n R$ in short).
+A minimum cardinality restrictions contains all those individuals that are connected by a property to at least n different individuals/literals 
+that are instances of a particular class or data range. If the class is missing, it is taken to be owl:Thing. 
+If the data range is missing, it is taken to be rdfs:Literal.
+
+\subsection{Simple Example}
+
+\begin{ex}
+# ShEx:
 :Jedi {
@@
 \begin{ex}
-# data
-# ----
+# data:
 :Yoda 
@@
 \begin{ex}
-# Individuals matching the ’:SuperJediMaster’ data shape
-# ------------------------------------------------------
+# Individuals matching the ’:SuperJediMaster’ data shape:
 :Yoda 
@@
 \end{DL}
+
+Captains command at least one vessel.
 

### 2015-01-05 paper/RDF validation requirements/RDF validation requirements.tex
finalize RDF validation requirements paper

@@
 If the data range is missing, it is taken to be rdfs:Literal.
+For unqualified cardinality restrictions, classes respective data ranges are not stated.
 
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES
-  \item R-211-CARDINALITY-CONSTRAINTS
-\end{itemize}
-
-description:
-
-\begin{itemize}
-	\item A minimum cardinality expression ObjectMinCardinality( n OPE CE ) consists of a nonnegative integer n, an object property expression OPE, and a class expression CE, and it contains all those individuals that are connected by OPE to at least n different individuals that are instances of CE.
-If CE is missing, it is taken to be owl:Thing.
-	\item A minimum cardinality expression DataMinCardinality( n DPE DR ) consists of a nonnegative integer n, a data property expression DPE, and a unary data range DR, and it contains all those individuals that are connected by DPE to at least n different literals in DR.
-If DR is not present, it is taken to be rdfs:Literal.
-	\item qualified: CE respective DR is stated.
-\end{itemize}
-Definition:\\
-
-$\leq n R. C$ is minimum qualified cardinality restriction where $n \in \mathbb{N}$.
+\ms{Minimum Qualified Cardinality Restrictions on Properties} corresponds to the requirements
+\ms{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES} and \ms{R-211-CARDINALITY-CONSTRAINTS}
+A minimum cardinality restrictions contains all those individuals that are connected by a property to at least n different individuals/literals 
+that are instances of a particular class or data range. If the class is missing, it is taken to be owl:Thing. 
+If the data range is missing, it is taken to be rdfs:Literal.
+For qualified cardinality restrictions, classes respective data ranges are stated.
+$\leq n R. C$ is a minimum qualified cardinality restriction where $n \in \mathbb{N}$.
 
@@
 
-\begin{itemize}
-	\item set of individuals that are children of at least two parents
-\end{itemize}
-
-\begin{ex}
-# OWL 2
-# -----
+Set of individuals that are children of at least two parents.
+
+\begin{ex}
+# OWL 2:
 owl:Thing
@@
 \begin{ex}
-# ShEx
-# ----
+# ShEx:
 :Jedi {
@@
 \begin{ex}
-# Individuals matching the ’:SuperJediMaster’ data shape
-# ------------------------------------------------------
+# Individuals matching the ’:SuperJediMaster’ data shape:
 :Yoda
 
-# Individuals matching the ’:JediMaster’ data shape
-# -------------------------------------------------
+# Individuals matching the ’:JediMaster’ data shape:
 :Obi-Wan
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-82-MAXIMUM-UNQUALIFIED-CARDINALITY-ON-PROPERTIES
-	\item R-211-CARDINALITY-CONSTRAINTS
-\end{itemize}
-
-description:
-
-\begin{itemize}
-	\item A maximum cardinality expression ObjectMaxCardinality( n OPE CE ) consists of a nonnegative integer n, an object property expression OPE, and a class expression CE, and it contains all those individuals that are connected by OPE to at most n different individuals that are instances of CE.
-If CE is missing, it is taken to be owl:Thing.
-	\item A maximum cardinality expression DataMaxCardinality( n DPE DR ) consists of a nonnegative integer n, a data property expression DPE, and a unary data range DR, and it contains all those individuals that are connected by DPE to at most n different literals in DR.
-If DR is not present, it is taken to be rdfs:Literal.
-	\item unqualified: CE respective DR is NOT stated. 
-\end{itemize}
-
-Definition:\\
-
-$\geq n R. \top$ is maximum unqualified cardinality restriction where $n \in \mathbb{N}$ (written $\geq  n R$ in short).
-\subsection{Simple Example}
-
-\begin{ex}
-# ShEx
-# ----
+\ms{Maximum Unqualified Cardinality Restrictions on Properties} corresponds to the requirements 
+\ms{R-82-MAXIMUM-UNQUALIFIED-CARDINALITY-ON-PROPERTIES} and \ms{R-211-CARDINALITY-CONSTRAINTS}.
+A maximum cardinality restriction contains all those individuals that are connected by a property to at most n different individuals/literals that are instances of a particular class or data range.
+If the class is missing, it is taken to be owl:Thing.
+If the data range is not present, it is taken to be rdfs:Literal.
+Unqualified means that the class respective the data range is not stated. 
+$\geq n R. \top$ is a maximum unqualified cardinality restriction where $n \in \mathbb{N}$ (written $\geq  n R$ in short).
+\subsection{Simple Example}
+
+\begin{ex}
+# ShEx:
 :Jedi {
@@
 \begin{ex}
-# Individuals matching the ’:JediMaster’ data shape
-# -------------------------------------------------
+# Individuals matching the ’:JediMaster’ data shape:
 :Obi-Wan
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-76-MAXIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES
-	\item R-211-CARDINALITY-CONSTRAINTS
-\end{itemize}
-
-description:
-
-\begin{itemize}
-	\item A maximum cardinality expression ObjectMaxCardinality( n OPE CE ) consists of a nonnegative integer n, an object property expression OPE, and a class expression CE, and it contains all those individuals that are connected by OPE to at most n different individuals that are instances of CE.
-If CE is missing, it is taken to be owl:Thing.
-	\item A maximum cardinality expression DataMaxCardinality( n DPE DR ) consists of a nonnegative integer n, a data property expression DPE, and a unary data range DR, and it contains all those individuals that are connected by DPE to at most n different literals in DR.
-If DR is not present, it is taken to be rdfs:Literal.
-	\item qualified: CE respective DR is stated. 
-\end{itemize}
-Definition:\\
-
-$\leq n R. C$ is maximum qualified cardinality restriction where $n \in \mathbb{N}$.
+\ms{Maximum Qualified Cardinality Restrictions on Properties} corresponds to the requirements
+\ms{R-76-MAXIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES} and
+\ms{R-211-CARDINALITY-CONSTRAINTS}.
+A maximum cardinality restriction contains all those individuals that are connected by a property to at most n different individuals/literals that are instances of a particular class or data range.
+If the class is missing, it is taken to be owl:Thing.
+If the data range is not present, it is taken to be rdfs:Literal.
+Qualified means that the class respective the data range is stated. 
+$\leq n R. C$ is a maximum qualified cardinality restriction where $n \in \mathbb{N}$.
 
@@
 
-%\tb{ToDO: check DL}
-
-\begin{itemize}
-	\item set of individuals that are children of at most two parents
-\end{itemize}
+Set of individuals that are children of at most two parents.
 
@@
 
-%\tb{ToDO: add DL}
-
-\noindent $mentorOf$ and $studentOf$ are taken to be inverse properties:\\
+%\noindent $mentorOf$ and $studentOf$ are taken to be inverse properties:\\
 
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-80-EXACT-UNQUALIFIED-CARDINALITY-ON-PROPERTIES
-	\item R-211-CARDINALITY-CONSTRAINTS
-\end{itemize}
-
-description:
-
-\begin{itemize}
-	\item An exact cardinality expression ObjectExactCardinality( n OPE CE ) consists of a nonnegative integer n, an object property expression OPE, and a class expression CE, and it contains all those individuals that are connected by OPE to exactly n different individuals that are instances of CE.
-If CE is missing, it is taken to be owl:Thing.
-Such an expression is actually equivalent to the expression ObjectIntersectionOf( ObjectMinCardinality( n OPE CE ) ObjectMaxCardinality( n OPE CE ) ).
-	\item An exact cardinality expression DataExactCardinality( n DPE DR ) consists of a nonnegative integer n, a data property expression DPE, and a unary data range DR, and it contains all those individuals that are connected by DPE to exactly n different literals in DR.
-If DR is not present, it is taken to be rdfs:Literal.
-	\item unqualified: CE respective DR is NOT stated. 
-\end{itemize}
-
-Definition:\\
-
-$\geq n R. \top \sqcap \leq n R. \top $ is exact unqualified cardinality restriction where $n \in \mathbb{N}$. ($\top$ can be dropped in short writing.)
+\ms{Exact Unqualified Cardinality Restrictions on Properties} corresponds to the requirements
+\ms{R-80-EXACT-UNQUALIFIED-CARDINALITY-ON-PROPERTIES} and
+\ms{R-211-CARDINALITY-CONSTRAINTS}.
+An exact cardinality restriction contains all those individuals that are connected by a property to exactly n different individuals that are instances of a particular class or data range. 
+If the class is missing, it is taken to be owl:Thing. 
+If the data range is not present, it is taken to be rdfs:Literal.
+Unqualified means that the class respective data range is not stated. 
+$\geq n R. \top \sqcap \leq n R. \top $ is an exact unqualified cardinality restriction where $n \in \mathbb{N}$.
+
 \subsection{Simple Example}
@@
 \begin{ex}
-# ShEx
-# ----
+# ShEx:
 :JediStudent {
@@
 \begin{ex}
-# ReSh
-# ----
+# ReSh:
 :JediStudent a rs:ResourceShape ;
@@
 \begin{ex}
-# Individuals matching the ’:JediStudent’ data shape
-# --------------------------------------------------
+# Individuals matching the ’:JediStudent’ data shape:
 :MaceWindu :Obi-Wan :Anakin :Luke
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-74-EXACT-QUALIFIED-CARDINALITY-ON-PROPERTIES
-	\item R-211-CARDINALITY-CONSTRAINTS
-\end{itemize}
-
-description:
-
-\begin{itemize}
-	\item An exact cardinality expression ObjectExactCardinality( n OPE CE ) consists of a nonnegative integer n, an object property expression OPE, and a class expression CE, and it contains all those individuals that are connected by OPE to exactly n different individuals that are instances of CE.
-If CE is missing, it is taken to be owl:Thing.
-Such an expression is actually equivalent to the expression ObjectIntersectionOf( ObjectMinCardinality( n OPE CE ) ObjectMaxCardinality( n OPE CE ) ).
-	\item An exact cardinality expression DataExactCardinality( n DPE DR ) consists of a nonnegative integer n, a data property expression DPE, and a unary data range DR, and it contains all those individuals that are connected by DPE to exactly n different literals in DR.
-If DR is not present, it is taken to be rdfs:Literal.
-	\item qualified: CE respective DR is stated. 
-\end{itemize}
-
-Definition:\\
-
-$\geq n R. C \sqcap \leq n R. C $ is exact unqualified cardinality restriction where $n \in \mathbb{N}$.
+\ms{Exact Qualified Cardinality Restrictions on Properties} corresponds to the requirements
+\ms{R-74-EXACT-QUALIFIED-CARDINALITY-ON-PROPERTIES} and \\
+\ms{R-211-CARDINALITY-CONSTRAINTS}.
+An exact cardinality restriction contains all those individuals that are connected by a property to exactly n different individuals that are instances of a particular class or data range. 
+If the class is missing, it is taken to be owl:Thing. 
+If the data range is not present, it is taken to be rdfs:Literal.
+Qualified means that the class respective data range is stated. 
+$\geq n R. C \sqcap \leq n R. C $ is an exact qualified cardinality restriction where $n \in \mathbb{N}$.
+
 \subsection{Simple Example}
@@
 \begin{ex}
-# ReSh
-# ----
+# ReSh:
 :Jedi a rs:ResourceShape ;
@@
 
-%\tb{ToDO: check DL}
-
-\begin{itemize}
-	\item every person is a child of exactly two parents
-\end{itemize}
+Every person is a child of exactly two parents.
 

### 2015-01-06 paper/RDF validation requirements/RDF validation requirements.tex
replied to comments

@@
 
-requirement:
-
-\begin{itemize}
-	\item R-56-INVERSE-OBJECT-PROPERTIES
-\end{itemize}
-
-\begin{itemize}
-	\item In many cases properties are used bi-directionally and then accessed in the inverse direction, e.g.
+\ms{Inverse Object Properties} corresponds to the requirement
+\ms{R-56-INVERSE-} \ms{OBJECT-PROPERTIES}.
+In many cases properties are used bi-directionally and then accessed in the inverse direction, e.g.
 parent $\equiv$ child$^{-}$.
 There should be a way to declare value type, cardinality etc of those inverse relations without having to declare a new property URI.
-	\item The object property expression OPE1 is an inverse of the object property expression OPE2.
-Thus, if an individual x is connected by OPE1 to an individual y, then y is also connected by OPE2 to x, and vice versa.
-\end{itemize}
+The object property OP1 is an inverse of the object property OP2. 
+Thus, if an individual x is connected by OP1 to an individual y, then y is also connected by OP2 to x, and vice versa.
 
@@
 
-outdated:
-
-\begin{gcotable}
-property & $\top$ & parentOf & childOf$^{-}$ & - & $\equiv$ \\
-\end{gcotable}
+\begin{gcotable}
+property & $\top$ & parentOf & childOf & - & inverse \\
+\end{gcotable}
+
+%outdated:
+%
+%\begin{gcotable}
+%property & $\top$ & parentOf & childOf$^{-}$ & - & $\equiv$ \\
+%\end{gcotable}
 
@@
 
-alternative:
-
-\begin{gcotable}
-property & hasCaptain$^{-}$ & hasCaptain & - & - & inverse \\
-property & captainOf & hasCaptain$^{-}$ & - & - & $\equiv$ \\
-\end{gcotable}
-
-alternative:
-
-\begin{gcotable}
-property & captainOf & hasCaptain & - & - & inverse \\
-\end{gcotable}
+%alternative:
+%
+%\begin{gcotable}
+%property & hasCaptain$^{-}$ & hasCaptain & - & - & inverse \\
+%property & captainOf & hasCaptain$^{-}$ & - & - & $\equiv$ \\
+%\end{gcotable}
+%
+%alternative:
+%
+%\begin{gcotable}
+%property & captainOf & hasCaptain & - & - & inverse \\
+%\end{gcotable}
 
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-63-TRANSITIVE-OBJECT-PROPERTIES
-\end{itemize}
-
-\begin{itemize}
-	\item Transitivity is a special form of complex role inclusion
-	\item An object property transitivity axiom TransitiveObjectProperty( OPE ) states that the object property expression OPE is transitive — that is, if an individual x is connected by OPE to an individual y that is connected by OPE to an individual z, then x is also connected by OPE to z.
-\end{itemize}
+\ms{Transitive Object Properties} corresponds to the requirement \\
+\ms{R-63-TRANSITIVE-OBJECT-PROPERTIES}.
+Transitivity is a special form of complex role inclusion.
+An object property transitivity axiom states that the object property is transitive — that is, if an individual x is connected by the object property to an individual y that is connected by the object property to an individual z, then x is also connected by the object property to z.
 

### 2015-01-06 paper/RDF validation requirements/RDF validation requirements.tex
add descriptions

@@
 
-requirement:
-
-\begin{itemize}
-	\item R-61-SYMMETRIC-OBJECT-PROPERTIES
-\end{itemize}
-
-\begin{itemize}
-	\item A role is symmetric if it is equivalent to its own inverse \cite{Kroetzsch2012}
-  \item An object property symmetry axiom SymmetricObjectProperty( OPE ) states that the object property expression OPE is symmetric — that is, if an individual x is connected by OPE to an individual y, then y is also connected by OPE to x.
-\end{itemize}
-
-\subsection{Simple Example}
+\ms{Symmetric Object Properties} corresponds to the requirement \\
+\ms{R-61-SYMMETRIC-OBJECT-PROPERTIES}.
+A role is symmetric if it is equivalent to its own inverse \cite{Kroetzsch2012}.
+An object property symmetry axiom states that the object property expression OPE is symmetric - that is, if an individual x is connected by OPE to an individual y, then y is also connected by OPE to x.
+
+\subsection{Simple Example}
+
+The property \ms{marriedTo} is symmetric:
 
@@
 
-\subsubsection{Asymmetric Object Properties}
-
-requirement:
-
-\begin{itemize}
-	\item R-62-ASYMMETRIC-OBJECT-PROPERTIES
-\end{itemize}
-
-\begin{itemize}
-	\item A role is asymmetric if it is disjoint from its own inverse \cite{Kroetzsch2012}
-	\item An object property asymmetry axiom AsymmetricObjectProperty( OPE ) states that the object property expression OPE is asymmetric — that is, if an individual x is connected by OPE to an individual y, then y cannot be connected by OPE to x.
-\end{itemize}
+\section{Asymmetric Object Properties}
+
+\ms{Asymmetric Object Properties} corresponds to the requirement \\
+\ms{R-62-ASYMMETRIC-OBJECT-PROPERTIES}.
+A role is asymmetric if it is disjoint from its own inverse \cite{Kroetzsch2012}.
+An object property asymmetry axiom AsymmetricObjectProperty( OPE ) states that the object property expression OPE is asymmetric - that is, if an individual x is connected by OPE to an individual y, then y cannot be connected by OPE to x.
 

### 2015-01-06 paper/RDF validation requirements/RDF validation requirements.tex
add descriptions

@@
 
-\begin{DL}
-$parentOf \sqsubseteq \neg parentOf^{-}$ or\\
-$parentOf \sqcap parentOf^{-} \sqsubseteq \bot$ or \\
+The property \ms{parentOf} is asymmetric:
+
+\begin{DL}
+$parentOf \sqsubseteq \neg parentOf^{-}$ 
+\end{DL}
+
+alternatively:
+
+\begin{DL}
+$parentOf \sqcap parentOf^{-} \sqsubseteq \bot$ 
+\end{DL}
+
+alternatively:
+
+\begin{DL}
 disjoint(parentOf, parentOf$^{-}$)
@@
 
-\begin{itemize}
-	\item child parent relations (dbo:child) cannot be symmetric
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{itemize}
-	\item person birth place relations (dbo:birthPlace) cannot be symmetric
-\end{itemize}
+Child parent relations (dbo:child) cannot be symmetric.
+
+\subsection{Simple Example}
+
+Person birth place relations (dbo:birthPlace) cannot be symmetric.
 
@@
 
-requirement:
-
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\begin{itemize}
-  \item DL terminology: local reflexivity
-	\item set of individuals that are related to themselves via a given role \cite{Kroetzsch2012}.
-	\item set of individuals (of a specific class) that are related to themselves via a given object property
-\end{itemize}
+Using DL terminology \ms{Class-Specific Reflexive Object Properties} is called local reflexivity - a set of individuals (of a specific class) that are related to themselves via a given role \cite{Kroetzsch2012}.
 
@@
 
-\begin{itemize}
-	\item set of individuals that are talking to themselves
-\end{itemize}
+Set of individuals that are talking to themselves.
 
@@
 
-requirement:
-
-\begin{itemize}
-	\item R-59-REFLEXIVE-OBJECT-PROPERTIES
-\end{itemize}
-
-\begin{itemize}
-  \item DL terminology: reflexive roles, global reflexivity
-	\item global reflexivity can be expressed by imposing local reflexivity on the top concept \cite{Kroetzsch2012}
-\end{itemize}
-
-\subsection{Simple Example}
+\ms{Reflexive Object Properties} (reflexive roles, global reflexivity in DL) corresponds to the requirement \ms{R-59-REFLEXIVE-OBJECT-PROPERTIES}.
+Global reflexivity can be expressed by imposing local reflexivity on the top concept \cite{Kroetzsch2012}.
+
+\subsection{Simple Example}
+
+Each individual knows itself:
 
@@
 
-requirement:
-
-\begin{itemize}
-	\item R-60-IRREFLEXIVE-OBJECT-PROPERTIES
-\end{itemize}
-
-\begin{itemize}
-	\item DL terminology: irreflexive roles
-  \item A role is irreflexive if it is never locally reflexive \cite{Kroetzsch2012}
-	\item An object property irreflexivity axiom IrreflexiveObjectProperty( OPE ) states that the object property expression OPE is irreflexive — that is, no individual is connected by OPE to itself. 
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{DL}
-$\top$ $\sqsubseteq$ $\neg$ $\exists  marriedTo . Self$   OR\\
-$\exists marriedTo . Self \sqsubseteq \bot$  OR\\
+\ms{Irreflexive Object Properties} (irreflexive roles in DL) corresponds to the requirement \ms{R-60-IRREFLEXIVE-OBJECT-PROPERTIES}.
+A role is irreflexive if it is never locally reflexive \cite{Kroetzsch2012}.
+An object property irreflexivity axiom IrreflexiveObjectProperty( OPE ) states that the object property expression OPE is irreflexive - that is, no individual is connected by OPE to itself.
+
+\subsection{Simple Example}
+
+\begin{DL}
+$\top$ $\sqsubseteq$ $\neg$ $\exists  marriedTo . Self$ 
+\end{DL}
+
+alternatively:
+
+\begin{DL}
+$\exists marriedTo . Self \sqsubseteq \bot$  
+\end{DL}
+
+alternatively:
+
+\begin{DL}
 $marriedTo \sqcap marriedTo^{-} \sqsubseteq \bot$ (without special self-concept Self)
@@
 
-\begin{itemize}
-	\item a resource cannot be its own parent (dbo:parent)
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{itemize}
-	\item a resource cannot be its own child (dbo:child)
-\end{itemize}
+A resource cannot be its own parent (dbo:parent).
+
+\subsection{Simple Example}
+
+A resource cannot be its own child (dbo:child).
 
@@
 
-requirement:
-
-\begin{itemize}
-	\item R-66-PROPERTY-GROUPS
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
-# ShEx
-# ----
+\ms{Context-Specific Property Groups} corresponds to the requirement \\
+\ms{R-66-PROPERTY-GROUPS} to group data and object properties.
+
+\subsection{Simple Example}
+
+\begin{ex}
+# ShEx:
 <Human> { 
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-11-CONTEXT-SPECIFIC-EXCLUSIVE-OR-OF-PROPERTIES
-\end{itemize}
-
-\begin{itemize}
-  \item exclusive or: logical operation that outputs true whenever both inputs differ (one is true, the other is false).
-	\item in OWL 2, inclusive OR of properties would be possible to express, but not exclusive OR of data properties
-\end{itemize}
-
-DL (general):
+\ms{Context-Specific Exclusive OR of Properties} correponds to the requirement
+\ms{R-11-CONTEXT-SPECIFIC-EXCLUSIVE-OR-OF-PROPERTIES}.
+Exclusive or is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
+%In OWL 2, inclusive OR of properties would be possible to express, but not exclusive OR of data properties
+This constraint is generally expressed in DL as follows:
 
@@
 
-DL (general) (alternative):
+and alternatively:
 
@@
 
-DSCL (ShEx):
-\begin{ex}
+\begin{ex}
+# ShEx:
 <Human> { (  
@@
 
-DSCL (OWL 2):
-\begin{ex}
-:Human owl:disjointUnionOf ( :CC1 :CC2 ) .
-
-:CC1 rdfs:subClassOf [
+\begin{ex}
+# OWL 2:
+Human owl:disjointUnionOf ( :CC1 :CC2 ) .
+
+CC1 rdfs:subClassOf [
     a owl:Restriction ;
@@
     owl:someValuesFrom xsd:string ] .
-:CC2 rdfs:subClassOf [
+CC2 rdfs:subClassOf [
     a owl:Restriction ;
@@
 \begin{ex}
-# ShEx
-# ----
+# ShEx:
 <FeelingForce> { (  
-    :attackingBySword xsd:boolean | 
-    :attackingByForce xsd:boolean ) }
-\end{ex}
-
-\begin{ex}
-# OWL 2 DL
-# --------
-:FeelingForce owl:disjointUnionOf ( :CC1 :CC2 ) . 
-:CC1 rdfs:subClassOf [
+    attackingBySword xsd:boolean | 
+    attackingByForce xsd:boolean ) }
+\end{ex}
+
+\begin{ex}
+# OWL 2 DL:
+FeelingForce owl:disjointUnionOf ( CC1 CC2 ) . 
+CC1 rdfs:subClassOf [
     a owl:Restriction ;
-    owl:onProperty :attackingBySword ;
+    owl:onProperty attackingBySword ;
     owl:someValuesFrom xsd:boolean ] .
-:CC2 rdfs:subClassOf [
+CC2 rdfs:subClassOf [
     a owl:Restriction ;
-    owl:onProperty :attackingByForce ;
+    owl:onProperty attackingByForce ;
     owl:someValuesFrom xsd:boolean ] .
@@
 
-\begin{itemize}
-	\item :FeelingForce $\equiv$ 1 :attackingBySword (range xsd:boolean) XOR 1 :attackingByForce (range xsd:boolean)
-\end{itemize}
-
-\begin{DL}
-A $\equiv$ $\exists$ :attackingBySword . xsd:boolean \\
-B $\equiv$ $\exists$ :attackingByForce . xsd:boolean \\ 
-:FeelingForce $\sqsubseteq$ ($\neg$ A $\sqcap$ B) $\sqcup$ (A $\sqcap$ $\neg$ B) \\
+This means that \ms{FeelingForce} individuals are individuals having one \ms{attackingBySword} relationship (range xsd:boolean) or one \ms{attackingByForce} relationship (range xsd:boolean) but not both.
+
+\begin{DL}
+A $\equiv$ $\exists$ attackingBySword.xsd:boolean \\
+B $\equiv$ $\exists$ attackingByForce.xsd:boolean \\ 
+FeelingForce $\sqsubseteq$ ($\neg$ A $\sqcap$ B) $\sqcup$ (A $\sqcap$ $\neg$ B) \\
 \end{DL}
@@
 
-DSCL (ShEx):
-
-\begin{ex}
+\begin{ex}
+# ShEx:
 <Human> { (  
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-202-CONTEXT-SPECIFIC-INCLUSIVE-OR-OF-PROPERTIES
-\end{itemize}
-
-\begin{itemize}
-	\item inclusive or: A logical connective joining two or more predicates that yields the logical value "true" when at least one of the predicates is true.
-	\item context can be a class $\rightarrow$ constraint applies for individuals of this specific class 
-\end{itemize}
+\ms{Context-Specific Inclusive OR of Properties} corresponds to the requirement
+\ms{R-202-CONTEXT-SPECIFIC-INCLUSIVE-OR-OF-PROPERTIES}.
+Inclusive or is a logical connective joining two or more predicates that yields the logical value "true" when at least one of the predicates is true.
+The context can be a class, i.e., the constraint applies for individuals of this specific class.
 

### 2015-01-06 paper/RDF validation requirements/RDF validation requirements.tex
add descriptions

@@
 
-requirement:
-
-\begin{itemize}
-	\item R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC
-\end{itemize}
-
-\begin{itemize}
-	\item exclusive or: logical operation that outputs true whenever both inputs differ (one is true, the other is false).
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
-# DSCL (ShEx)
-# -----------
+\ms{Context-Specific Exclusive OR of Property Groups} corresponds to the requirement:
+\ms{R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC}.
+Exclusive or is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
+Only one of multiple property groups leads to valid data.
+
+\subsection{Simple Example}
+
+\begin{ex}
+# ShEx:
 <Human> { 
@@
 \begin{ex}
-# valid data
-# ----------
-:Thomas
-    a :Human ;
+# valid data:
+Thomas
+    a Human ;
     foaf:mbox <thomas.bosch@gesis.org> ;
@@
 \begin{ex}
-# invalid data
-# ----------
-:Thomas
-    a :Human ;
+# invalid data:
+Thomas
+    a Human ;
     foaf:name 'Thomas Bosch' ;
@@
 
-\subsection{Complex Example}
-
-\begin{ex}
-# ShExC
-# -----
-[[
-  <UserShape> {                          # A User has
-    (foaf:name xsd:string                #  either a foaf:name
-     | foaf:givenName xsd:string+,       #   or 1+ givenNames
-       foaf:familyName xsd:string),      #   and a family name
-    foaf:mbox IRI                        # and an mbox.
-  }
-]]
-\end{ex}
-
-\begin{ex}
-# ReSh
-# ----
-
-[[
-  PREFIX rs:<http://open-services.net/ns/core#>
-  PREFIX se:<http://www.w3.org/2013/ShEx/Definition#>
-
-  <UserShape> a rs:ResourceShape ;       # A User has
-    se:choice [
-      rs:property [                      #  either a foaf:name
-        rs:name "name" ;
-        rs:propertyDefinition foaf:name ;
-        rs:valueType xsd:string ;
-        rs:occurs rs:Exactly-one ;
-      ] ;
-      se:ruleGroup [
-        rs:property [                    #   or 1+ givenNames
-          rs:name "givenName" ;
-          rs:propertyDefinition foaf:givenName ;
-          rs:valueType xsd:string ;
-          rs:occurs rs:One-or-many ;
-        ] ;
-        rs:property [                    #   and a family name
-          rs:name "familyName" ;
-          rs:propertyDefinition foaf:familyName ;
-          rs:valueType xsd:string ;
-          rs:occurs rs:Exactly-one ;
-        ] ;
-      ] ;
-    ] ;
-    rs:property [                        # and an mbox.
-      rs:name "mbox" ;
-      rs:propertyDefinition foaf:mbox ;
-      rs:valueType rs:Resource ;
-      rs:occurs rs:Exactly-one ;
-    ] .
-]]
-\end{ex}
+%\subsection{Complex Example}
+%
+%\begin{ex}
+%# ShExC
+%# -----
+%[[
+  %<UserShape> {                          # A User has
+    %(foaf:name xsd:string                #  either a foaf:name
+     %| foaf:givenName xsd:string+,       #   or 1+ givenNames
+       %foaf:familyName xsd:string),      #   and a family name
+    %foaf:mbox IRI                        # and an mbox.
+  %}
+%]]
+%\end{ex}
+%
+%\begin{ex}
+%# ReSh
+%# ----
+%
+%[[
+  %PREFIX rs:<http://open-services.net/ns/core#>
+  %PREFIX se:<http://www.w3.org/2013/ShEx/Definition#>
+%
+  %<UserShape> a rs:ResourceShape ;       # A User has
+    %se:choice [
+      %rs:property [                      #  either a foaf:name
+        %rs:name "name" ;
+        %rs:propertyDefinition foaf:name ;
+        %rs:valueType xsd:string ;
+        %rs:occurs rs:Exactly-one ;
+      %] ;
+      %se:ruleGroup [
+        %rs:property [                    #   or 1+ givenNames
+          %rs:name "givenName" ;
+          %rs:propertyDefinition foaf:givenName ;
+          %rs:valueType xsd:string ;
+          %rs:occurs rs:One-or-many ;
+        %] ;
+        %rs:property [                    #   and a family name
+          %rs:name "familyName" ;
+          %rs:propertyDefinition foaf:familyName ;
+          %rs:valueType xsd:string ;
+          %rs:occurs rs:Exactly-one ;
+        %] ;
+      %] ;
+    %] ;
+    %rs:property [                        # and an mbox.
+      %rs:name "mbox" ;
+      %rs:propertyDefinition foaf:mbox ;
+      %rs:valueType rs:Resource ;
+      %rs:occurs rs:Exactly-one ;
+    %] .
+%]]
+%\end{ex}
 
@@
 
-requirements:
-
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\begin{itemize}
-  \item at least one property group must match for individuals of a specific context 
-	\item context: may be a class
-\end{itemize}
+At least one property group must match for individuals of a specific context. 
+Context may be a class, a shape, or an application profile.
 
@@
 \begin{ex}
-# valid data
-# ----------
+# valid data:
 :Anakin
@@
 \begin{ex}
-# invalid data
-# ----------
+# invalid data:
 :Anakin
@@
 syntactic sugar:
+
 \begin{gcotable}
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS
-  \item R-37-ALLOWED-VALUES-FOR-RDF-LITERALS
-\end{itemize}
-
-\begin{itemize}
-  \item It is a common requirement to narrow down the value space of a property by an exhaustive enumeration of the valid values (both literals or resource).
+\ms{Allowed Values} corresponds to the requirements:
+\ms{R-30-ALLOWED-VALUES-FOR-} \ms{RDF-OBJECTS} and 
+\ms{R-37-ALLOWED-VALUES-FOR-RDF-LITERALS}.
+It is a common requirement to narrow down the value space of a property by an exhaustive enumeration of the valid values (both literals or resource).
 This is often rendered in drop down boxes or radio buttons in user interfaces.
-	\item define a concept by simply enumerating its instances
-	\item A DL nominal is a concept that has exactly one instance
-	\item DL enumeration: combining nominals with union
-\end{itemize}
-
-allowed values for properties
-
-\begin{itemize}
-	\item must be an IRI
-  \item must be an IRI matching this pattern (e.g. http://id.loc.gov/authorities/names/)
-  \item must be an IRI matching one of these patterns
-  \item must be a (any) literal
-  \item must be one of these literals ("red" "blue" "green")
-  \item must be a typed literal of this type (e.g. XML dataType)
+%\begin{itemize}
+  %\item define a concept by simply enumerating its instances
+	%\item A DL nominal is a concept that has exactly one instance
+	%\item DL enumeration: combining nominals with union
+%\end{itemize}
+Allowed values for properties
+\begin{itemize}
+	\item must be these IRIs,
+  \item must be IRIs matching specific patterns,
+  \item must be IRIs matching one of multiple patterns,
+  \item must be (any) literals,
+  \item must be literals of a list of allowed literals (e.g. "red" "blue" "green"),
+  \item must be typed literals of this type (e.g. XML dataType).
 \end{itemize}
@@
 \begin{ex}
-# DSP
-# ----------
-:descriptionTemplate 
+# DSP:
+descriptionTemplate 
     a dsp:DescriptionTemplate ;
@@
             dsp:valueClass skos:Concept ;
-            dsp:valueURI :ComputerScience, :SocialScience, :Librarianship ] ] .
-\end{ex}
-
-\begin{ex}
-# OWL2
-# ----
-dcterms:subject rdfs:range :ObjectOneOf . 
-# EquivalentClasses( :ObjectOneOf ObjectOneOf( :ComputerScience :SocialScience :Librarianship ) )
-:ObjectOneOf owl:equivalentClass [ 
+            dsp:valueURI ComputerScience, SocialScience, Librarianship ] ] .
+\end{ex}
+
+\begin{ex}
+# OWL2:
+dcterms:subject rdfs:range ObjectOneOf . 
+# EquivalentClasses( ObjectOneOf ObjectOneOf( ComputerScience SocialScience Librarianship ) )
+ObjectOneOf owl:equivalentClass [ 
     a owl:Class ;
-    owl:oneOf ( :ComputerScience :SocialScience :Librarianship ) ] .
-\end{ex}
-
-\begin{itemize}
-	\item the range of the object property dcterms:subject must consist of the individuals :ComputerScience :SocialScience :Librarianship which are of the class skos:Concept
-\end{itemize}
-
-\begin{DL}
-$\top$ $\sqsubseteq$ $\forall$ dcterms:subject . skos:Concept $\sqcap$ ( $\{ComputerScience\}$ $\sqcup$ \{SocialScience\} $\sqcup$ \{Librarianship\} ) \\
+    owl:oneOf ( ComputerScience SocialScience Librarianship ) ] .
+\end{ex}
+
+The range of the object property \ms{dcterms:subject} must consist of the individuals \ms{ComputerScience} \ms{SocialScience} \ms{Librarianship} which are of the class \ms{skos:Concept}:
+
+\begin{DL}
+$\top$ $\sqsubseteq$ $\forall$ dcterms:subject . skos:Concept $\sqcap$ \\
+( $\{ComputerScience\}$ $\sqcup$ \{SocialScience\} $\sqcup$ \{Librarianship\} ) \\
 \end{DL}
@@
 
-\begin{itemize}
-	\item Jedis have blue, green, or white laser swords
-\end{itemize}
-
-\begin{ex}
-# DSP
-# ---
-:personDescriptionTemplate
+Jedis have blue, green, or white laser swords.
+
+\begin{ex}
+# DSP:
+personDescriptionTemplate
     a dsp:DescriptionTemplate ;
-    dsp:resourceClass :Jedi ;
+    dsp:resourceClass Jedi ;
     dsp:statementTemplate [
         a dsp:LiteralStatementTemplate ;
-        dsp:property :laserSwordColor ;
+        dsp:property laserSwordColor ;
         dsp:literalConstraint [
@@
 \begin{ex}
-# OWL2
-# ----
-:laserSwordColor rdfs:range :laserSwordColors . 
-:laserSwordColors
+# OWL2:
+laserSwordColor rdfs:range laserSwordColors . 
+laserSwordColors
     a rdfs:Datatype .
@@
 \begin{ex}
-# ReSh
-# ----
-:Jedi a rs:ResourceShape ;
+# ReSh:
+Jedi a rs:ResourceShape ;
     rs:property [
         rs:name "laserSwordColor" ;
-        rs:propertyDefinition :laserSwordColor ;
+        rs:propertyDefinition laserSwordColor ;
         rs:allowedValue "blue" , "green" , "white" ;
-        rs:occurs rs:Exactly-one ;
-    ] .
-\end{ex}
-
-\begin{ex}
-# ShEx
-# ----
-:Jedi {
-    :laserSwordColor ('blue' 'green' 'white') }
-\end{ex}
-
-\begin{ex}
-# Jedi individuals
-# ----------------
-:Yoda 
-    :laserSwordColor 'blue' .
-\end{ex}
-
-\begin{DL}
-Jedi $\equiv$ $\exists$ laserSwordColor . \{blue, green, white\} \\
+        rs:occurs rs:Exactly-one ; ] .
+\end{ex}
+
+\begin{ex}
+# ShEx:
+Jedi {
+    laserSwordColor ('blue' 'green' 'white') }
+\end{ex}
+
+\begin{ex}
+# Jedi individuals:
+Yoda 
+    laserSwordColor 'blue' .
+\end{ex}
+
+\begin{DL}
+Jedi $\equiv$ $\exists$ laserSwordColor.\{blue, green, white\} \\
 \end{DL}

### 2015-01-06 paper/RDF validation requirements/RDF validation requirements.tex
solved some issues

@@
 
-requirements:
-
-\begin{itemize}
-	\item R-33-NEGATIVE-OBJECT-CONSTRAINTS
-	\item R-200-NEGATIVE-LITERAL-CONSTRAINTS
-\end{itemize}
-
-\begin{itemize}
-	\item not allowed objects
-	\item not allowed literals
-	\item definition: A matching triple has any literal / object except those explicitly excluded
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{itemize}
-	\item Siths do not have blue, green, or white laser swords
-\end{itemize}
-
-\begin{ex}
-# DSP
-# ---
--
-\end{ex}
-
-\begin{ex}
-# OWL2
-# ----
-:laserSwordColor rdfs:range :negativeLaserSwordColors . 
-:NegativeLaserSwordColors
+\ms{Not Allowed Values} corresponds to the requirements
+\ms{R-33-NEGATIVE-OBJECT-} \ms{CONSTRAINTS} and
+\ms{R-200-NEGATIVE-LITERAL-CONSTRAINTS}.
+A matching triple has any literal / object except those explicitly excluded.
+
+\subsection{Simple Example}
+
+Siths do not have blue, green, or white laser swords.
+
+\begin{ex}
+# OWL2:
+laserSwordColor rdfs:range negativeLaserSwordColors . 
+NegativeLaserSwordColors
     a rdfs:Datatype .
-    owl:complementOf :laserSwordColors .
-:laserSwordColors
+    owl:complementOf laserSwordColors .
+laserSwordColors
     a rdfs:Datatype .
@@
 \begin{ex}
-# ReSh
-# ----
--
-\end{ex}
-
-\begin{ex}
-# ShEx
-# ----
-:Sith {
-    ! :laserSwordColor ('blue' 'green' 'white') }
-\end{ex}
-
-\begin{ex}
-# Sith individuals
-# ----------------
-:DarthSidious
-    :laserSwordColor 'red' .
+# ShEx:
+Sith {
+    ! laserSwordColor ('blue' 'green' 'white') }
+\end{ex}
+
+\begin{ex}
+# Sith individuals:
+DarthSidious
+    laserSwordColor 'red' .
 \end{ex}
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES
-	\item R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES
-\end{itemize}
-
-\begin{itemize}
-	\item resources can only be members of listed controlled vocabularies
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
-# DSCL (DSP)
-# ----------
-:bookDescriptionTemplate 
+\ms{Membership in Controlled Vocabularies} corresponds to the requirements \\
+\ms{R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES} and \\
+\ms{R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES}
+Resources can only be members of listed controlled vocabularies.
+
+\subsection{Simple Example}
+
+\begin{ex}
+# DSP:
+bookDescriptionTemplate 
     a dsp:DescriptionTemplate ;
@@
             dsp:valueClass skos:Concept ; 
-            dsp:vocabularyEncodingScheme :BookSubjects, :BookTopics, :BookCategories ] ] .
-\end{ex}
-
-\begin{itemize}
-	\item \ms{skos:Concept} resources can only be members of the listed controlled vocabularies
-\end{itemize}
+            dsp:vocabularyEncodingScheme BookSubjects, BookTopics, BookCategories ] ] .
+\end{ex}
+
+\ms{skos:Concept} resources can only be members of the listed controlled vocabularies.
+
 %\er{This sort of DL-syntax (with semicolon) must be rechecked.
@@
 \begin{ex}
-# valid data
-# ----------
-:ArtficialIntelligence
+# valid data:
+ArtficialIntelligence
     a swrc:Book ;
-    dcterms:subject :ComputerScience .
-:ComputerScience
+    dcterms:subject ComputerScience .
+ComputerScience
     a skos:Concept ;
-    dcam:memberOf :BookSubjects ;
-    skos:inScheme :BookSubjects .
-:BookSubjects
+    dcam:memberOf BookSubjects ;
+    skos:inScheme BookSubjects .
+BookSubjects
     a skos:ConceptScheme .
@@
 \begin{ex}
-# invalid data
-# ------------
-:ArtficialIntelligence
+# invalid data:
+ArtficialIntelligence
     a swrc:Book ;
-    dcterms:subject :ComputerScience .
-:ComputerScience
+    dcterms:subject ComputerScience .
+ComputerScience
     a skos:Concept ;
-    dcam:memberOf :BooksAboutBirds ;
-    skos:inScheme :BooksAboutBirds ;
-    dcam:memberOf :BookSubjects ;
-    skos:inScheme :BookSubjects .
-:BookSubjects
+    dcam:memberOf BooksAboutBirds ;
+    skos:inScheme BooksAboutBirds ;
+    dcam:memberOf BookSubjects ;
+    skos:inScheme BookSubjects .
+BookSubjects
     a skos:ConceptScheme .
@@
 
-\begin{itemize}
-	\item The related subject (\ms{:ComputerScience}) is a member of a controlled vocabulary (\ms{:BooksAboutBirds}) 
+The related subject (\ms{ComputerScience}) is a member of a controlled vocabulary (\ms{BooksAboutBirds}) 
 which is not part of the list of allowed controlled vocabularies.
-\end{itemize}
 

### 2015-01-06 paper/RDF validation requirements/RDF validation requirements.tex
5.2 but need to modify it again

@@
 
-requirements:
-
-\begin{itemize}
-	\item R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS
-  \item R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS
-  \item R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES
-\end{itemize}
-
-\begin{itemize}
-	\item IRI pattern matching on subjects, properties, and objects
-\end{itemize}
+\ms{IRI Pattern Matching} corresponds to the requirements
+\begin{itemize}
+	\item \ms{R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS},
+	\item \ms{R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS} and
+	\item \ms{R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES} 
+\end{itemize}
+indicating IRI pattern matching on subjects, properties, and objects.
 
@@
 
-requirements:
-
-\begin{itemize}
-  \item R-44-PATTERN-MATCHING-ON-RDF-LITERALS
-\end{itemize}
-
-\begin{itemize}
-	\item pattern matching on literals
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
-# OWL 2 DL (functional-style syntax)
-# ----------------------------------
-Declaration( Datatype( :SSN ) ) 
+\ms{Literal Pattern Matching} corresponds to the requirement \\
+\ms{R-44-PATTERN-MATCHING-ON-RDF-LITERALS}.
+indicating pattern matching on literals.
+
+\subsection{Simple Example}
+
+\begin{ex}
+# OWL 2 DL (functional-style syntax):
+Declaration( Datatype( SSN ) ) 
 DatatypeDefinition( 
-    :SSN
+    SSN
     DatatypeRestriction( xsd:string xsd:pattern "[0-9]{3}-[0-9]{2}-[0-9]{4}" ) )     
-DataPropertyRange( :hasSSN :SSN ) 
-\end{ex}
-
-\begin{ex}
-# OWL 2 DL (turtle syntax)
-# ------------------------
-:SSN 
+DataPropertyRange( hasSSN SSN ) 
+\end{ex}
+
+\begin{ex}
+# OWL 2 DL (turtle syntax):
+SSN 
     a rdfs:Datatype ;
@@
             [ xsd:pattern "[0-9]{3}-[0-9]{2}-[0-9]{4}" ] ) ] .
-:hasSSN rdfs:range :SSN .
-\end{ex}
-
-\begin{itemize}
-	\item A social security number is a string that matches the given regular expression. 
-The second axiom defines :SSN as an abbreviation for a datatype restriction on xsd:string. 
-The first axiom explicitly declares :SSN to be a datatype. 
-The datatype :SSN can be used just like any other datatype; 
-for example, it is used in the third axiom to define the range of the :hasSSN property. 
-\end{itemize}
-
-\begin{ex}
-# valid data
-# ----------
-:TimBernersLee
-    :hasSSN "123-45-6789"^^:SSN .
-\end{ex}
-
-\begin{ex}
-# invalid data
-# ------------
-:TimBernersLee
-    :hasSSN "123456789"^^:SSN .
+hasSSN rdfs:range SSN .
+\end{ex}
+
+A social security number is a string that matches the given regular expression. 
+The second axiom defines SSN as an abbreviation for a datatype restriction on xsd:string. 
+The first axiom explicitly declares SSN to be a datatype. 
+The datatype SSN can be used just like any other datatype; 
+for example, it is used in the third axiom to define the range of the hasSSN property.
+
+\begin{ex}
+# valid data:
+TimBernersLee
+    hasSSN "123-45-6789"^^SSN .
+\end{ex}
+
+\begin{ex}
+# invalid data:
+TimBernersLee
+    hasSSN "123456789"^^SSN .
 \end{ex}
@@
 The universal restriction part of this constraint can be expressed by OWL 2 DL:
-\ms{LukesDroids $\sqsubseteq$ $\forall$ droidNumber . DroidNumber}.
+\ms{LukesDroids $\sqsubseteq$ $\forall$ droidNumber.DroidNumber}.
 The restriction of the datatype \ms{DroidNumber}, however, cannot be expressed in DL, but OWL 2 DL can be used anyway:
@@
 
-requirements:
-
-\begin{itemize}
-  \item R-44-PATTERN-MATCHING-ON-RDF-LITERALS
-\end{itemize}
-
-\begin{itemize}
-	\item negative pattern matching on literals
-\end{itemize}
-
-\begin{ex}
-# examples
-# --------
+\ms{Negative Literal Pattern Matching} corresponds to the requirement \\
+\ms{R-44-PATTERN-MATCHING-ON-RDF-LITERALS}
+indicating negative pattern matching on literals.
+
+\begin{ex}
+# examples:
 1. dbo:isbn format is different ’!’ from '^([iIsSbBnN 0-9-])*$'
@@
 \begin{ex}
-# test binding (DQTP)
-# -------------------
+# test binding (DQTP):
 dbo:isbn format is different ’!’ from '^([iIsSbBnN 0-9-])*$'
@@
 \begin{ex}
-# DQTP
-# ----
+# DQTP:
 SELECT DISTINCT ?s WHERE { ?s %%P1%% ?value .
@@
 \begin{ex}
-# valid data
-# ----------
-:FoundationsOfSWTechnologies
+# valid data:
+FoundationsOfSWTechnologies
     dbo:isbn 'ISBN-13 978-1420090505' .
@@
 \begin{ex}
-# invalid data
-# ------------
-:HandbookOfSWTechnologies
+# invalid data:
+HandbookOfSWTechnologies
     dbo:isbn 'DOI 10.1007/978-3-540-92913-0' .
@@
 
-requirement:
-
-\begin{itemize}
-	\item R-43-LITERAL-VALUE-COMPARISON
-\end{itemize}
-
-examples:
-
-\begin{itemize}
-	\item dbo:deathDate before ‘<’ dbo:birthDate
-  \item dbo:releaseDate after ‘>’ dbo:latestReleaseDate
-  \item dbo:demolitionDate before ‘<’ dbo:buildingStartDate
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
-# DSCL (DQTP)
-# -----------
+\ms{Literal Value Comparison} corresponds to the requirement \\
+\ms{R-43-LITERAL-VALUE-COMPARISON}.
+Examples are:
+
+\begin{itemize}
+	\item dbo:deathDate before ‘\textless’ dbo:birthDate
+  \item dbo:releaseDate after ‘\textgreater’ dbo:latestReleaseDate
+  \item dbo:demolitionDate before ‘\textless’ dbo:buildingStartDate
+\end{itemize}
+
+\subsection{Simple Example}
+
+\begin{ex}
+# DSCL (DQTP):
 SELECT ?s WHERE { 
@@
 
-COMP Pattern \cite{Kontokostas2014}
-
+This constraint corresponds to the COMP Pattern \cite{Kontokostas2014}. 
 Depending on the property semantics,
@@
 \begin{ex}
-# test binding (DQTP)
-# -------------------
+# test binding (DQTP):
 dbo:deathDate before ‘<’ dbo:birthDate
@@
 \begin{ex}
-# valid data
-# ----------
+# valid data:
 :AlbertEinstein
@@
 \begin{ex}
-# invalid data
-# ------------
+# invalid data:
 :NeilArmstrong
@@
 
-duplicate strings are not allowed:
+Duplicate strings are not allowed:
 
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES
-\end{itemize}
-
-\begin{itemize}
-	\item The literal value of a resource (having a certain type) must (not) be within a specific range
-  \item P1 is a data property of an instance of class T1 and its literal value must be between the range of [Vmin,Vmax] or outside ( ‘!' ).
-\end{itemize}
+\ms{Negative Literal Ranges} corresponds to the requirement
+\ms{R-142-NEGATIVE-} \ms{RANGES-OF-RDF-LITERAL-VALUES}.
+The literal value of a resource (having a certain type) must (not) be within a specific range.
+P1 is a data property of an instance of class T1 and its literal value must be between the range of [Vmin,Vmax] or outside ( ‘!' ).
 
@@
 
-requirement:
-
-\begin{itemize}
-	\item R-45-RANGES-OF-RDF-LITERAL-VALUES
-\end{itemize}
+\ms{Literal Ranges} corresponds to the requirement
+\ms{R-45-RANGES-OF-RDF-LITERAL-} \ms{VALUES}.
 
@@
 \begin{ex}
-# OWL 2 DL (functional-style syntax)
-# ----------------------------------
-Declaration( Datatype( :NumberPlayersPerWorldCupTeam ) ) 
+# OWL 2 DL (functional-style syntax):
+Declaration( Datatype( NumberPlayersPerWorldCupTeam ) ) 
 DatatypeDefinition( 
-    :NumberPlayersPerWorldCupTeam
+    NumberPlayersPerWorldCupTeam
     DatatypeRestriction( 
@@
         xsd:maxInclusive "23"^^xsd:nonNegativeInteger ) )     
-DataPropertyRange( :position :NumberPlayersPerWorldCupTeam ) 
-\end{ex}
-
-\begin{ex}
-# OWL 2 DL (turtle syntax)
-# ------------------------
-:NumberPlayersPerWorldCupTeam
+DataPropertyRange( position NumberPlayersPerWorldCupTeam ) 
+\end{ex}
+
+\begin{ex}
+# OWL 2 DL (turtle syntax):
+NumberPlayersPerWorldCupTeam
     a rdfs:Datatype ;
@@
             [ xsd:maxInclusive "23"^^xsd:nonNegativeInteger ] ) ] .
-:position rdfs:range :NumberPlayersPerWorldCupTeam .
-\end{ex}
-
-\begin{itemize}
-	\item The data range 'NumberPlayersPerWorldCupTeam' contains the non negative integers 1 to 23, as each world cup team can only have 23 football players at most
-\end{itemize}
-
-\begin{ex}
-# valid data
-# ----------
-:MarioGoetze
-    :position "19"^^:NumberPlayersPerWorldCupTeam .
-\end{ex}
-
-\begin{ex}
-# invalid data
-# ------------
-:MarioGoetze
-    :position "99"^^:NumberPlayersPerWorldCupTeam .
-\end{ex}
-
-\begin{itemize}
-	\item range of position is the datatype 1-23
-  \item constraints are stated on this datatype
-\end{itemize}
+position rdfs:range NumberPlayersPerWorldCupTeam .
+\end{ex}
+
+The data range 'NumberPlayersPerWorldCupTeam' contains the non negative integers 1 to 23, as each world cup team can only have 23 football players at most.
+
+\begin{ex}
+# valid data:
+MarioGoetze
+    position "19"^^:NumberPlayersPerWorldCupTeam .
+\end{ex}
+
+\begin{ex}
+# invalid data:
+MarioGoetze
+    position "99"^^:NumberPlayersPerWorldCupTeam .
+\end{ex}
+
+%The range of \ms{position} is the datatype 1-23
+  %\item constraints are stated on this datatype
+%\end{itemize}
 
@@
 
-requirements:
-
-\begin{itemize}
-  \item R-121-SPECIFY-ORDER-OF-RDF-RESOURCES
-	\item R-217-DEFINE-ORDER-FOR-FORMS/DISPLAY
-\end{itemize}
-
-\begin{itemize}
-	\item order properties
-	\item order objects of object properties
-	\item order literal of data properties
-\end{itemize}
+\ms{Define Order} corresponds to the requirements
+\ms{R-121-SPECIFY-ORDER-OF-RDF-} \ms{RESOURCES} and
+\ms{R-217-DEFINE-ORDER-FOR-FORMS/DISPLAY}.
+With this constraint objects of object properties can be ordered as well as literals of data properties and objects of object properties.
 

### 2015-01-07 paper/RDF validation requirements/RDF validation requirements.tex

@@
 
-\begin{DL}
-Man $\sqsubseteq$ $\forall$ sonOf . Parent \\
-\end{DL}
-
-Individuals of the class \ms{Man} (context class) can only have \ms{sonOf} relationships to individuals of the class \ms{Parent} (range class).
+Only men can have \ms{sonOf} relationships to parents:
+
+\begin{DL}
+%Man $\sqsubseteq$ $\forall$ sonOf . Parent \\
+$\neg$Man $\sqsubseteq$ $\neg\exists$ sonOf.Parent
+\end{DL}
+
+%Individuals of the class \ms{Man} (context class) can only have \ms{sonOf} relationships to individuals of the class \ms{Parent} (range class).
+
+\subsection{Simple Example}
+
+Only vulcans can have friendship relationships to cardassians
+
+\begin{DL}
+$\neg$Vulcan $\sqsubseteq$ $\neg\exists$ friendOf.Carsassian
+\end{DL}
 
@@
 Primary Key Properties & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
-*Class-Specific Property Range & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
-*Class-Sp. Reflexive Object P. & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+*Class-Specific Property Range & $\checkmark$ & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+*Class-Sp. Reflexive Object P. & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
 Membership in Controlled Vocabularies & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
@@
 Value is Valid for Datatype & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
-*Exploiting Class/Property Specialization Ontology Axioms & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
-*Cardinality Shortcuts & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+Exploiting Class/Property Specialization Ontology Axioms & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+*Cardinality Shortcuts & \ding{55} & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
 Aggregations & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\

### 2015-01-07 paper/ESWC 2015 Tutorial/ESWC2015Tutorial.tex
ESWC 2015 Tutorial

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}

% allows for temporary adjustment of side margins
\usepackage{chngpage}

% just makes the table prettier (see \toprule, \bottomrule, etc. commands below)
\usepackage{booktabs}

\usepackage[utf8]{inputenc}
%\usepackage[font=small,skip=0pt]{caption}

% footnotes
\usepackage{scrextend}

% URL handling
\usepackage{url}
\urlstyle{same}

% Todos
%\usepackage[colorinlistoftodos]{todonotes}
%\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
%\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}

%\usepackage{makeidx}  % allows for indexgeneration

%\usepackage{amsmath}
\usepackage{amsmath, amssymb}
\usepackage{mathabx}

% monospace within text
\newcommand{\ms}[1]{\texttt{#1}}

% examples
\usepackage{fancyvrb}
\DefineVerbatimEnvironment{ex}{Verbatim}{numbers=left,numbersep=2mm,frame=single,fontsize=\scriptsize}

\usepackage{xspace}
% Einfache und doppelte Anfuehrungszeichen
\newcommand{\qs}{``} 
\newcommand{\qe}{''\xspace} 
\newcommand{\sqs}{`} 
\newcommand{\sqe}{'\xspace}

% checkmark
\usepackage{tikz}
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}

% Xs
\usepackage{pifont}

% Tabellenabstände kleiner
\setlength{\intextsep}{10pt} % Vertical space above & below [h] floats
\setlength{\textfloatsep}{10pt} % Vertical space below (above) [t] ([b]) floats
% \setlength{\abovecaptionskip}{0pt}
% \setlength{\belowcaptionskip}{0pt}

\usepackage{tabularx}
\newcommand{\hr}{\hline\noalign{\smallskip}} % für die horizontalen linien in tabellen

% Todos
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\bz}[1]{\todo[size=\small, color=orange!40]{\textbf{Ben:} #1}}
\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}

\newenvironment{table-1cols}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
  \begin{tabular}{l}
  \hline
  \textbf{Requirements} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{table-2cols}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
  \begin{tabular}{l|l}
  \hline
  \textbf{Requirements} & \textbf{Covering DSCLs} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{complexity}{
  %\scriptsize
  %\sffamily
  %\vspace{0.3cm}
  \begin{tabular}{l|l}
  \hline
  \textbf{Complexity Class} & \textbf{Complexity} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{DL}{
  %\scriptsize
  %\sffamily
  \vspace{0cm}
  \begin{tabular}{r l}

}{
  \end{tabular}
  %\linebreak
}

\newenvironment{evaluation}{
  %\scriptsize
  %\sffamily
  %\vspace{0.3cm}
  \begin{tabular}{l|c|c|c|c|c|c}
  \hline
  \textbf{Constraint Class} & \textbf{DSP} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{constraint-languages-complexity}{
  %\scriptsize
  %\sffamily
  %\vspace{0.3cm}
  \begin{tabular}{l|c|c|c|c|c|c}
  \hline
  \textbf{Complexity Class} & \textbf{DSP} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{user-fiendliness}{
  %\scriptsize
  %\sffamily
  %\vspace{0.3cm}
  \begin{tabular}{l|c|c|c|c|c}
  \hline
  \textbf{criterion} & \textbf{DSP} & \textbf{OWL2} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\setcounter{secnumdepth}{5}

\begin{document}

%
%
\title{Let’s Disco – Publishing person-level data as Linked Data.}
\subtitle{Building a Data Portal with DCAT, DDI-RDF Discovery, PHDD, and other vocabularies.\bz{Ben's Kommentar}
}
%
\titlerunning{XXXXX}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{XXX\inst{1} \and XXX\inst{2}}
%
\authorrunning{XXXXX} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\institute{GESIS – Leibniz Institute for the Social Sciences, Germany\\
\email{thomas.bosch@gesis.org},\\ 
\and
University of Mannheim, Germany \\
\email{\{christian,erman,kai\}@informatik.uni-mannheim.de} 
\and
Albstadt-Sigmaringen University, Germany \\
\email{nolle@hs-albsig.de}
}

\maketitle              % typeset the title of the contribution

\begin{abstract}
200 words

\keywords{RDF Validation, RDF Constraints, OWL 2 QL, OWL 2 DL, Reasoning, RDF Validation Requirements, Linked Data, Semantic Web}
\end{abstract}
%

\section{Anweisungen}

Proposals should not exceed 5 pages using a reasonable font size (not less than 11 pts). They should include the call for participation together with the following details:
- Abstract: 200 words maximum, for inclusion to the ESWC 2015 Web site.
- Tutorial description: objectives of the tutorial and relevance to ESWC 2015; information about the scope and level of detail of the material to be covered; intended audiences; learning objectives; practical sessions.
- Tutorial length: Half or full day, including preferences.
- Previous versions or related tutorials: other venues of this or similar tutorials (potentially by a different team of tutors), motivation for offering the tutorial again, at the ESWC2015.
- Tutoring team: short bios of the presenters, including previous training and public speaking experience (e.g., teaching in English, conference presentations, tutorials etc.)

\section{Call for Participation}

The DDI-RDF Discovery Vocabulary (Disco) is a RDF Schema vocabulary that supports the discovery of microdata sets and related metadata using RDF technologies in the Web of Linked Data. Disco can be used to discover datasets by searching for specific questions, topics, and geographical coverage. Disco is intended to provide means to describe microdata by essential metadata for the discovery purpose.

The DDI (Data Documentation Initiative) is a structured metadata standard related to the observation and measurement of human activity.
It started out in the mid-1990s as a replacement for traditional archival code books documenting research data, and then branched off to cover the research data life cycle. Over time, as the data landscape has
changed, the DDI XML specifications have evolved to add new coverage and functionality to respond to new user requirements.
While the Data Documentation Initiative (DDI) is an international metadata standard with origins in the quantitative social sciences, it is increasingly being used by researchers and practitioners in other disciplines. The DDI specifications are also being used to document other data types, such as social media, biomarkers, administrative data, and transaction data. The specification itself is modular and can document and manage different stages of the data lifecycle, such as conceptualization, collection, processing, analysis, distribution, discovery, repurposing, and archiving.
Existing DDI-XML instances can be transformed into this RDF format and therefore exposed as Linked Data. This workshop aims to present the Disco vocabulary and its practical appliance with DDI metadata in detail.

For a publication of DDI metadata as Linked Data, widely accepted and adopted RDF vocabularies (e.g. RDF Data Cube, DCAT, and PHDD) are reused to a large extend. The workshop organizers show how Disco is interwoven with these vocabularies. The Data Cube vocabulary is a W3C standard for representing data cubes representing multidimensional aggregate data derived from microdata which is represented by Disco. DCAT is a W3C standard for describing catalogs of datasets. Physical data description (PHDD) represents data (tables) in a rectangular format. The data could be either represented in records with character-separated values (CSV) or in records with fixed length. The combined usage of PHDD, Disco, and DCAT enables the creation of data repositories which provide metadata for the description of collections, for data discovery, and for processing of the data.

In different real world use cases, the workshop organizers demonstrate the adoption and inclusion of Disco in existing information systems. Workshop participants are encouraged to present their own use cases where Disco has been applied or will be used. Together with the workshop organizers, workshop participants will have the possibility to elaborate an RDF representation of their use cases and to formulate typical queries which are necessary to solve use case related problems.
The workshop has a technical perspective and addresses software developers as well as data publishers who want to publish DDI metadata as Linked Data. No prerequisites are necessary, since a short introduction to RDF and Linked Open Data will be given.

\section{Tutorial Description}

\textbf{objectives of the tutorial}

\textbf{relevance to ESWC 2015}

\textbf{information about the scope and level of detail of the material to be covered}

\textbf{intended audiences}

\textbf{learning objectives}

\textbf{practical sessions}

\section{Tutorial Length}

Half or full day, including preferences

\section{Previous Versions or Related Tutorials}

Thomas Bosch and Benjamin Zapilko hold a half-day tutorial at the EDDI14 – 6th Annual European DDI User Conference in London [1].
We got great feedback for this tutorial and had the idea to provide this tutorial at the ESWC conference next year as well.

\section{Tutoring Team}

\bibliography{../../literature/literature}{}
\bibliographystyle{plain}
\setcounter{tocdepth}{1}
%\listoftodos
\end{document}

### 2015-01-07 paper/ESWC 2015 Tutorial/ESWC2015Tutorial.tex
ESWC 2015 Tutorial

@@
 
-Thomas Bosch and Benjamin Zapilko hold a half-day tutorial at the EDDI14 – 6th Annual European DDI User Conference in London [1].
-We got great feedback for this tutorial and had the idea to provide this tutorial at the ESWC conference next year as well.
+Thomas Bosch and Benjamin Zapilko hold a half-day tutorial at the EDDI14 – 6th Annual European DDI User Conference in London\footnote{\url{http://www.eddi-conferences.eu/ocs/index.php/eddi/eddi14/schedConf/program}}.
+We got great feedback for this tutorial and had the idea to provide this tutorial at the ESWC conference as well.
+At the EDDI conference, we reached the first part of our audience - data professionals and the DDI community.
+At the ESWC conference, we want to reach the second part of our audience - Linked Data experts.
 
 \section{Tutoring Team}
+
+%short bios of the presenters, including previous training and public speaking experience (e.g., teaching in English, conference presentations, tutorials etc.)
+
+Thomas Bosch\footnote{\url{http://boschthomas.blogspot.com}} (M.Sc. in Computer Science) is a PhD student at Gesis - Leibniz Institute for the Social Sciences in Mannheim , Germany since 2010.
+He studied Information Systems at the Technical University of Munich.
+His general research topic is about RDF validation. 
+He hold multiple conference and workshop presentations (e.g. ISWC, DC, WWW, Dagstuhl seminars) in the last five years.
 

### 2015-01-07 paper/ESWC 2015 Tutorial/ESWC2015Tutorial.tex
ESWC 2015 Tutorial
ESWC 2015 Tutorial abstract

@@
 \institute{GESIS – Leibniz Institute for the Social Sciences, Germany\\
-\email{thomas.bosch@gesis.org},\\ 
-\and
-University of Mannheim, Germany \\
-\email{\{christian,erman,kai\}@informatik.uni-mannheim.de} 
-\and
-Albstadt-Sigmaringen University, Germany \\
-\email{nolle@hs-albsig.de}
-}
+\email{\{benjamin,thomas\}}.bosch@gesis.org}
 
@@
 \begin{abstract}
-200 words
+The DDI-RDF Discovery Vocabulary (Disco) is an RDF Schema vocabulary that supports the discovery of microdata sets and related metadata using RDF technologies in the Web of Linked Data.
+Disco can be used to discover datasets by searching for specific questions, topics, and geographical coverage.
+Disco is intended to provide means to describe microdata by essential metadata for the discovery purpose.
+ The DDI (Data Documentation Initiative) is a structured metadata standard related to the observation and measurement of human activity.
 
-\keywords{RDF Validation, RDF Constraints, OWL 2 QL, OWL 2 DL, Reasoning, RDF Validation Requirements, Linked Data, Semantic Web}
+For a publication of DDI metadata as Linked Data, widely accepted and adopted RDF vocabularies (e.g. RDF Data Cube, DCAT, SKOS, and Physical Data Description) are reused to a large extend. 
+The workshop organizers show how Disco is interwoven with these vocabularies. 
+The combined usage of Physical Data Description, Disco, and DCAT enables the creation of data repositories which provide metadata for the description of collections, for data discovery, and for processing of the data.
+
+In different real world use cases, the workshop organizers demonstrate the adoption and inclusion of Disco in existing information systems.
+
+\keywords{DDI-RDF Discovery Vocabulary, Disco, Microdata, Microdata Metadata, Discovery of Microdata, Data Documentation Initiative, DDI, Linked Data, Semantic Web}
 \end{abstract}
@@
 
-The DDI-RDF Discovery Vocabulary (Disco) is a RDF Schema vocabulary that supports the discovery of microdata sets and related metadata using RDF technologies in the Web of Linked Data.
+The DDI-RDF Discovery Vocabulary (Disco) is an RDF Schema vocabulary that supports the discovery of microdata sets and related metadata using RDF technologies in the Web of Linked Data.
 Disco can be used to discover datasets by searching for specific questions, topics, and geographical coverage.
@@
 
+\tb{we could provide full day if we make the hands on exercises with the SPARQL queries / do you think we should do that?}
+
 \section{Previous Versions or Related Tutorials}

### 2015-01-07 paper/ESWC 2015 Tutorial/ESWC2015Tutorial.tex
ESWC 2015 Tutorial abstract - RDF validation

@@
 %
-\author{XXX\inst{1} \and XXX\inst{2}}
+\author{XXX\inst{1} \and XXX\inst{1} \and Joachim Wackerow\inst{1}}
 %
@@
 \institute{GESIS – Leibniz Institute for the Social Sciences, Germany\\
-\email{\{benjamin,thomas\}}.bosch@gesis.org}
+\email{\{thomas.bosch,benjamin.zapilko,joachim.wackerow\}}@gesis.org}
 
@@
 
-In different real world use cases, the workshop organizers demonstrate the adoption and inclusion of Disco in existing information systems.
+In different real world use cases, we demonstrate the adoption and inclusion of Disco in existing information systems. 
+Existing DDI instances are stored in form of XML documents which can be transformed into DDI-RDF and therefore exposed as Linked Data.
+We describe typical constraints on metadata of DDI metadata, as well as how to formulate them by different constraint languages (e.g. OWL 2) and how to actually validate them.
 
@@
 
+Existing DDI instances are stored in form of XML documents and validated against XML Schemas\footnote{XML Schemas of current DDI version available at \url{http://www.ddialliance.org/Specification/DDI-Lifecycle/3.2/XMLSchema/}}.
+DDI-XML documents can be transformed into DDI-RDF and therefore exposed as Linked Data.
+For XML, XML Schema is the standard constraint language to validate XML documents.
+For RDF, however, there are multiple candidates for languages to express constraints on RDF data - but there is no standard language for RDF validation.
+In 2014, two working groups on RDF validation have been established: the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles working group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
+These working groups address the formulation and validation of RDF constraints.
+We will describe typical constraints on metadata of DDI metadata, as well as how to formulate and to validate them.
+We will show how to formulate these constraints by different constraint languages such as OWL 2.
+
 \section{Tutorial Description}
@@
 
-Half or full day, including preferences
-
-\tb{we could provide full day if we make the hands on exercises with the SPARQL queries / do you think we should do that?}
+We would like to provide a full day workshop as our experience in the previous tutorial about disco showed that a whole day is needed to explain the most important things about disco and to hold the hands-on exercises.
+We also want to address the validation of DDI-RDF which we did not covered at the last tutorial.
 
@@
 
-Thomas Bosch and Benjamin Zapilko hold a half-day tutorial at the EDDI14 – 6th Annual European DDI User Conference in London\footnote{\url{http://www.eddi-conferences.eu/ocs/index.php/eddi/eddi14/schedConf/program}}.
+Thomas Bosch and Benjamin Zapilko hold a half-day tutorial\footnote{tutorial slides avaliable at: \url{http://de.slideshare.net/boschthomas/201412-lets-disco-eddi-2014} and \url{http://de.slideshare.net/boschthomas/201412-lets-disco-2-eddi-2014}} at the EDDI14 – 6th Annual European DDI User Conference in London\footnote{\url{http://www.eddi-conferences.eu/ocs/index.php/eddi/eddi14/schedConf/program}}.
 We got great feedback for this tutorial and had the idea to provide this tutorial at the ESWC conference as well.

### 2015-01-07 paper/ESWC 2015 Tutorial/ESWC2015Tutorial.tex
additions for sections 3 to 6

@@
 
-\textbf{objectives of the tutorial}
+\subsection{Objectives of the Tutorial}
 
-\textbf{relevance to ESWC 2015}
+\subsection{Relevance to ESWC 2015}
+In this tutorial, the DDI-RDF Discovery vocabulary (Disco) and its interplay with other existing vocabularies is introduced.
+In contrast to other newly developed vocabularies that can be adopted easily by Linked Data experts in most cases, the complexity of Disco is higher because of its domain-specific origin and the tight interplay with other existing vocabularies.
+This makes Disco more difficult to be adopted by Linked Data experts that may not be familiar with the domain-specific background of person-level micro data.
+However, since the number of organizations that aim to publish their complex data as Linked Data grows and the number of researchers that want to conduct their research with real-world data grows, a tutorial on representing such highly complex and inter-connected data sets may be a beneficial addition for the audience of ESWC 2015.
 
-\textbf{information about the scope and level of detail of the material to be covered}
+\subsection{Scope and Level of Detail of the Material}
 
-\textbf{intended audiences}
+\subsection{Intended Audiences}
+Linked Data experts that are interested in modelling and publishing complex and highly inter-connected data sets as Linked Data
 
-\textbf{learning objectives}
+\subsection{Learning Objectives}
+The learning objectives of this tutorial are the following:
+\begin{itemize} 
+\item Introduction of Disco for modelling complex person-level micro data
+\item Representing the interplay of Disco data with existing vocabularies
+\item Validation of Disco
+\end{itemize}
 
-\textbf{practical sessions}
+\subsection{Practical Sessions}
+During the tutorial, one complex data set will be built, which serves as ongoing running example.
+In all sessions, there will be practical exercises where the participants are asked to model and query particular parts of the example data sets.
+The infrastructure for these exercises, i.e.
+a triple store with example data, will be provided for all participants by the presenters.
 
@@
 
-We would like to provide a full day workshop as our experience in the previous tutorial about disco showed that a whole day is needed to explain the most important things about disco and to hold the hands-on exercises.
-We also want to address the validation of DDI-RDF which we did not covered at the last tutorial.
+We propose a full-day workshop.
+In the previous tutorial about disco, we experienced that a half-day tutorial offers only enough time to cover the most important aspects about disco and to include few hands-on exercises.
+Since we now want to expand the focus of the tutorial to the interplay of disco with other vocabularies and its validation, a full-day seems to be appropriate.
+Furthermore, we want to offer hands-on exercises again, because they were well received at the last tutorial.
 
@@
 
-Thomas Bosch and Benjamin Zapilko hold a half-day tutorial\footnote{tutorial slides avaliable at: \url{http://de.slideshare.net/boschthomas/201412-lets-disco-eddi-2014} and \url{http://de.slideshare.net/boschthomas/201412-lets-disco-2-eddi-2014}} at the EDDI14 – 6th Annual European DDI User Conference in London\footnote{\url{http://www.eddi-conferences.eu/ocs/index.php/eddi/eddi14/schedConf/program}}.
-We got great feedback for this tutorial and had the idea to provide this tutorial at the ESWC conference as well.
-At the EDDI conference, we reached the first part of our audience - data professionals and the DDI community.
-At the ESWC conference, we want to reach the second part of our audience - Linked Data experts.
+Thomas Bosch and Benjamin Zapilko held a half-day tutorial\footnote{tutorial slides avaliable at: \url{http://de.slideshare.net/boschthomas/201412-lets-disco-eddi-2014} and \url{http://de.slideshare.net/boschthomas/201412-lets-disco-2-eddi-2014}} at the EDDI14 – 6th Annual European DDI User Conference in London\footnote{\url{http://www.eddi-conferences.eu/ocs/index.php/eddi/eddi14/schedConf/program}}.
+The tutorial was well received and the presenters got overall positive feedback.
+Since the audience of disco is two-fold - data professionals and the DDI community at the one hand and Linked Data experts at the other hand - the idea was to offer this tutorial at the ESWC conference as well.
+At the EDDI conference, the first part of the audience - data professionals and the DDI community - was addressed.
+At the ESWC conference, the second part of our audience - Linked Data experts - will be addressed.
 
@@
 His general research topic is about RDF validation. 
-He hold multiple conference and workshop presentations (e.g. ISWC, DC, WWW, Dagstuhl seminars) in the last five years.
+He held multiple conference and workshop presentations (e.g. ISWC, DC, WWW, Dagstuhl seminars) in the last five years.
+
+Benjamin Zapilko holds a degree in Computer Sceince and has recently finished his PhD thesis about methods for matching social science relevant Linked Data.
+The defense talk will be at the end of January.
+Beside his PhD research, he works on modelling and publishing social science relevant data as Linked Data with the focus on data modelling and integration of heterogeneous data sources and information types.
+He presented his work at several international conferences.
 

### 2015-01-07 paper/RDF validation requirements/RDF validation requirements.tex

@@
 
-requirements:
-
-\begin{itemize}
-	\item R-205-VARYING-LEVELS-OF-ERROR
-	\item R-135-CONSTRAINT-LEVELS
-	\item R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS
-	\item R-193-MULTIPLE-CONSTRAINT-VALIDATION-EXECUTION-LEVELS
-\end{itemize}
-
-\begin{itemize}
-  \item Different levels of severity, priority
-	\item validation levels: informational, warning, error, fail, should, recommended, must, may, optional, closed (only this) constraints, open (at least this) constraints
-\end{itemize}
-
-\subsection{Simple Example}
+\ms{Validation Levels} corresponds to the requirements
+
+\begin{itemize}
+	\item \ms{R-205-VARYING-LEVELS-OF-ERROR},
+	\item \ms{R-135-CONSTRAINT-LEVELS},
+	\item \ms{R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS}, and
+	\item \ms{R-193-MULTIPLE-CONSTRAINT-VALIDATION-EXECUTION-LEVELS}.
+\end{itemize}
+
+Different levels of severity, priority should be assigned to constraints.
+Possible validation levels could be: informational, warning, error, fail, should, recommended, must, may, optional, closed (only this) constraints, open (at least this).
 

### 2015-01-07 paper/ESWC 2015 Tutorial/ESWC2015Tutorial.tex
zechnical review publication bio

@@
 
-\section{Anweisungen}
-
-Proposals should not exceed 5 pages using a reasonable font size (not less than 11 pts). They should include the call for participation together with the following details:
-- Abstract: 200 words maximum, for inclusion to the ESWC 2015 Web site.
-- Tutorial description: objectives of the tutorial and relevance to ESWC 2015; information about the scope and level of detail of the material to be covered; intended audiences; learning objectives; practical sessions.
-- Tutorial length: Half or full day, including preferences.
-- Previous versions or related tutorials: other venues of this or similar tutorials (potentially by a different team of tutors), motivation for offering the tutorial again, at the ESWC2015.
-- Tutoring team: short bios of the presenters, including previous training and public speaking experience (e.g., teaching in English, conference presentations, tutorials etc.)
+%\section{Anweisungen}
+%
+%Proposals should not exceed 5 pages using a reasonable font size (not less than 11 pts). They should include the call for participation together with the following details:
+%- Abstract: 200 words maximum, for inclusion to the ESWC 2015 Web site.
+%- Tutorial description: objectives of the tutorial and relevance to ESWC 2015; information about the scope and level of detail of the material to be covered; intended audiences; learning objectives; practical sessions.
+%- Tutorial length: Half or full day, including preferences.
+%- Previous versions or related tutorials: other venues of this or similar tutorials (potentially by a different team of tutors), motivation for offering the tutorial again, at the ESWC2015.
+%- Tutoring team: short bios of the presenters, including previous training and public speaking experience (e.g., teaching in English, conference presentations, tutorials etc.)
 
@@
 
-The DDI-RDF Discovery Vocabulary (Disco) is an RDF Schema vocabulary that supports the discovery of microdata sets and related metadata using RDF technologies in the Web of Linked Data.
+In different real world use cases, the workshop organizers demonstrate the adoption and inclusion of Disco in existing information systems. 
+Workshop participants are encouraged to present their own use cases where Disco has been applied or will be used. 
+Together with the workshop organizers, workshop participants will have the possibility to elaborate an RDF representation of their use cases and to formulate typical queries which are necessary to solve use case related problems.
+The workshop addresses software developers as well as data publishers who want to publish DDI metadata as Linked Data.
+
+\section{Tutorial Description}
+
+The DDI-RDF Discovery Vocabulary (Disco)\footnote{current specification is available at \url{https://github.com/linked-statistics/disco-spec}}  is an RDF Schema vocabulary that supports the discovery of microdata sets and related metadata using RDF technologies in the Web of Linked Data.
 Disco can be used to discover datasets by searching for specific questions, topics, and geographical coverage.
@@
 
-In different real world use cases, the workshop organizers demonstrate the adoption and inclusion of Disco in existing information systems.
-Workshop participants are encouraged to present their own use cases where Disco has been applied or will be used.
-Together with the workshop organizers, workshop participants will have the possibility to elaborate an RDF representation of their use cases and to formulate typical queries which are necessary to solve use case related problems.
-The workshop has a technical perspective and addresses software developers as well as data publishers who want to publish DDI metadata as Linked Data.
-No prerequisites are necessary, since a short introduction to RDF and Linked Open Data will be given.
-
 Existing DDI instances are stored in form of XML documents and validated against XML Schemas\footnote{XML Schemas of current DDI version available at \url{http://www.ddialliance.org/Specification/DDI-Lifecycle/3.2/XMLSchema/}}.
@@
 
-\section{Tutorial Description}
+In 2012, we started the development of Disco in form of a one-week Dagstuhl seminar - another one-week Dagstuhl seminar and two one-week workshops followed.  
+In 2014, we finished the technical review of Disco.
+We addressed more than ten mailing lists from the Linked Data and the DDI communities and got feedback which has been incorporated into the Disco specification.
+We are planning to officially publish Disco after three years of development in the first half of the year 2015 after an additional official technical review of the DDI Alliance\footnote{\url{http://www.ddialliance.org/}}.
 
@@
 \subsection{Intended Audiences}
-Linked Data experts that are interested in modelling and publishing complex and highly inter-connected data sets as Linked Data
+Linked Data experts that are interested in modelling and publishing complex and highly inter-connected data sets as Linked Data.
 
@@
 
-Thomas Bosch\footnote{\url{http://boschthomas.blogspot.com}} (M.Sc. in Computer Science) is a PhD student at Gesis - Leibniz Institute for the Social Sciences in Mannheim , Germany since 2010.
-He studied Information Systems at the Technical University of Munich.
-His general research topic is about RDF validation. 
-He held multiple conference and workshop presentations (e.g. ISWC, DC, WWW, Dagstuhl seminars) in the last five years.
+Thomas Bosch\footnote{\url{http://boschthomas.blogspot.com}} studies information systems, holds a degree in Computer Science (M.Sc.), and is currently a PhD student.
+His research topic is all about RDF validation.
+More specifically, he investigates how to validate any RDF constraints (formulated by multiple constraint languages) and how to express them generically. 
+He held multiple presentations at international conferences and workshops (e.g. WWW, ISWC, DC, Dagstuhl seminars).
 
-Benjamin Zapilko holds a degree in Computer Sceince and has recently finished his PhD thesis about methods for matching social science relevant Linked Data.
+Benjamin Zapilko holds a degree in Computer Science and has recently finished his PhD thesis about methods for matching social science relevant Linked Data.
 The defense talk will be at the end of January.

### 2015-01-08 paper/ESWC 2015 Tutorial/ESWC2015Tutorial.tex
material and bio

@@
 \title{Let’s Disco – Publishing person-level data as Linked Data.}
-\subtitle{Building a Data Portal with DCAT, DDI-RDF Discovery, PHDD, and other vocabularies.\bz{Ben's Kommentar}
+\subtitle{Building a Highly-Complex Data Set with Disco, PHDD, XKOS and widely used vocabularies.
 }
@@
 
-\keywords{DDI-RDF Discovery Vocabulary, Disco, Microdata, Microdata Metadata, Discovery of Microdata, Data Documentation Initiative, DDI, Linked Data, Semantic Web}
+\keywords{DDI-RDF Discovery Vocabulary, Disco, Microdata Metadata, Data Documentation Initiative, Linked Data}
 \end{abstract}
@@
 The specification itself is modular and can document and manage different stages of the data lifecycle, such as conceptualization, collection, processing, analysis, distribution, discovery, repurposing, and archiving.
-Existing DDI-XML instances can be transformed into this RDF format and therefore exposed as Linked Data.
 This workshop aims to present the Disco vocabulary and its practical appliance with DDI metadata in detail.
@@
 
+During the tutorial, we built one real world complex data set which serves as ongoing running example. 
+The whole data set can be exported from the Microdata Information System\footnote{\url{http://www.gesis.org/missy/editor/}}. 
+In all sessions, there will be practical hands-on exercises where the participants are asked to model and query particular parts of this data set. 
+The infrastructure for these exercises, i.e. a triple store, will be provided for all participants.
+We will extend slides of a previous tutorial\footnote{tutorial slides avaliable at: \url{http://de.slideshare.net/boschthomas/201412-lets-disco-eddi-2014} and \url{http://de.slideshare.net/boschthomas/201412-lets-disco-2-eddi-2014}}
+and where appropriate refer to the current Disco specification\footnote{current specification is available at \url{https://github.com/linked-statistics/disco-spec}}.
+
 \subsection{Intended Audiences}
@@
 \begin{itemize} 
-\item Introduction of Disco for modelling complex person-level micro data
+\item Introduction of Disco, PHDD, and XKOS for modelling complex person-level micro data
 \item Representing the interplay of Disco data with existing vocabularies
@@
 
-Thomas Bosch and Benjamin Zapilko held a half-day tutorial\footnote{tutorial slides avaliable at: \url{http://de.slideshare.net/boschthomas/201412-lets-disco-eddi-2014} and \url{http://de.slideshare.net/boschthomas/201412-lets-disco-2-eddi-2014}} at the EDDI14 – 6th Annual European DDI User Conference in London\footnote{\url{http://www.eddi-conferences.eu/ocs/index.php/eddi/eddi14/schedConf/program}}.
+Thomas Bosch and Benjamin Zapilko held a half-day tutorial at the EDDI14 – 6th Annual European DDI User Conference in London\footnote{\url{http://www.eddi-conferences.eu/ocs/index.php/eddi/eddi14/schedConf/program}}.
 The tutorial was well received and the presenters got overall positive feedback.
@@
 
+Joachim Wackerow holds a degree in sociology. 
+He is the vice chair of the DDI Alliance Technical Committee whose charge is to create, maintain, and enhance the DDI specification.
+He is the chair of the DDI Alliance RDF Vocabularies Working Group whose charge is to develop RDF vocabularies for efficient use of DDI metadata in the context of the Semantic Web/Linked Data.
+He organizes the annual European DDI user conferences and holds DDI introduction workshops.
+
 \bibliography{../../literature/literature}{}

### 2015-01-08 paper/ESWC 2015 Tutorial/ESWC2015Tutorial.tex
objectives and audience

@@
 \subsection{Objectives of the Tutorial} 
+The domain-specific origin of Disco increases the difficulties for adopting it by developers who are not familiar with the domain.
+However, person-level metadata is not restricted to a particular domain and may be an interesting data source for Linked Data developers.
+Hence, as our main objective, we want to provide assistence for creating such complex Linked Data sets using Disco.
+Because of the complexity, we especially want to demonstrate how Disco data sets can be connected with information represented using other existing vocabularies that are relevant in that context.
+Vice verse, we show how these other vocabualries and data represented with such can benefit from the interplay with Disco.
+
+Another objective of the tutorial is to share our experience in developing a RDF vocabulary out of an existing and highly-complex domain-specific data model.
+We provide insight into the development and engineering process for creating Disco.
+Finally, since Disco is already being adopted in the DDI community, we aim to increase the use of Disco in the Linked Data community.
 
@@
 \subsection{Intended Audiences}
-Linked Data experts that are interested in modelling and publishing complex and highly inter-connected data sets as Linked Data.
+The intended audience of this tutorial are Linked Data developers - beginners as well as experts - who are interested in modelling and publishing complex and highly inter-connected data sets as Linked Data.
+Since the connection with other vocabulaires like QB, DCAT and PROV-O plays a major role in this context, the tutorial is not restricted to participants who are interested in person-level micro data.
 
@@
 
-Thomas Bosch\footnote{\url{http://boschthomas.blogspot.com}} studies information systems, holds a degree in Computer Science (M.Sc.), and is currently a PhD student.
+Thomas Bosch\footnote{\url{http://boschthomas.blogspot.com}} studied information systems, holds a degree in Computer Science (M.Sc.), and is currently a PhD student.
 His research topic is all about RDF validation.

### 2015-01-08 paper/ESWC 2015 Tutorial/ESWC2015Tutorial.tex
call for participation and minor stuff

@@
 
-For a publication of DDI metadata as Linked Data, widely accepted and adopted RDF vocabularies (e.g. RDF Data Cube, DCAT, SKOS, and Physical Data Description) are reused to a large extend. 
-The workshop organizers show how Disco is interwoven with these vocabularies. 
+For a publication of DDI metadata as Linked Data, widely accepted and adopted RDF vocabularies (e.g. RDF Data Cube, DCAT, SKOS, PROV-O and Physical Data Description) are reused to a large extend. 
+In this tutorial it is shown how Disco is interwoven with these vocabularies. 
 The combined usage of Physical Data Description, Disco, and DCAT enables the creation of data repositories which provide metadata for the description of collections, for data discovery, and for processing of the data.
@@
 \section{Call for Participation}
+The DDI-RDF Discovery Vocabulary (Disco) is an RDF Schema vocabulary that supports the discovery of microdata sets and related metadata using RDF technologies in the Web of Linked Data. 
+It is based on the DDI (Data Documentation Initiative) which is a structured metadata standard related to the observation and measurement of human activity.
+Since this data is highly complex, widely accepted and adopted RDF vocabularies (e.g. RDF Data Cube, DCAT, SKOS, PROV-O and Physical Data Description) are reused to a large extend.
 
-In different real world use cases, the workshop organizers demonstrate the adoption and inclusion of Disco in existing information systems. 
-Workshop participants are encouraged to present their own use cases where Disco has been applied or will be used. 
-Together with the workshop organizers, workshop participants will have the possibility to elaborate an RDF representation of their use cases and to formulate typical queries which are necessary to solve use case related problems.
-The workshop addresses software developers as well as data publishers who want to publish DDI metadata as Linked Data.
+In different real world use cases, the presenters of the tutorial demonstrate the adoption and inclusion of Disco in existing information systems.
+Participants are encouraged to present their own use cases where Disco has been applied or will be used. 
+Together with the presenters, participants will have the possibility to elaborate an RDF representation of their use cases and to formulate typical queries which are necessary to solve use case related problems.
+
+This tutorial addresses Linked Data developers who want to publish Linked Data sets based on complex data like person-level microdata in combination with essential informationlike provenance, data aggregates and data catalogs.
 
@@
 The specification itself is modular and can document and manage different stages of the data lifecycle, such as conceptualization, collection, processing, analysis, distribution, discovery, repurposing, and archiving.
-This workshop aims to present the Disco vocabulary and its practical appliance with DDI metadata in detail.
+This tutorial aims to present the Disco vocabulary and its practical appliance with DDI metadata in detail.
 
@@
 RDF Data Cube, DCAT, and PHDD) are reused to a large extend.
-The workshop organizers show how Disco is interwoven with these vocabularies.
+It is shown how Disco is interwoven with these vocabularies.
 The Data Cube vocabulary is a W3C standard for representing data cubes representing multidimensional aggregate data derived from microdata which is represented by Disco.
@@
 
-We propose a full-day workshop.
-In the previous tutorial about disco, we experienced that a half-day tutorial offers only enough time to cover the most important aspects about disco and to include few hands-on exercises.
-Since we now want to expand the focus of the tutorial to the interplay of disco with other vocabularies and its validation, a full-day seems to be appropriate.
+We propose a full-day tutorial.
+In the previous tutorial about Disco, we experienced that a half-day tutorial offers only enough time to cover the most important aspects about Disco and to include few hands-on exercises.
+Since we now want to expand the focus of the tutorial to the interplay of Disco with other vocabularies and its validation, a full-day seems to be appropriate.
 Furthermore, we want to offer hands-on exercises again, because they were well received at the last tutorial.
@@
 The tutorial was well received and the presenters got overall positive feedback.
-Since the audience of disco is two-fold - data professionals and the DDI community at the one hand and Linked Data experts at the other hand - the idea was to offer this tutorial at the ESWC conference as well.
+Since the audience of Disco is two-fold - data professionals and the DDI community at the one hand and Linked Data experts at the other hand - the idea was to offer this tutorial at the ESWC conference as well.
 At the EDDI conference, the first part of the audience - data professionals and the DDI community - was addressed.

### 2015-01-09 paper/ESWC 2015 Tutorial/ESWC2015Tutorial.tex
typos

@@
 The DDI-RDF Discovery Vocabulary (Disco) is an RDF Schema vocabulary that supports the discovery of microdata sets and related metadata using RDF technologies in the Web of Linked Data.
-Disco can be used to discover datasets by searching for specific questions, topics, and geographical coverage.
+Disco can be used to discover data sets by searching for specific questions, topics, and geographical coverage.
 Disco is intended to provide means to describe microdata by essential metadata for the discovery purpose.
@@
 
-This tutorial addresses Linked Data developers who want to publish Linked Data sets based on complex data like person-level microdata in combination with essential informationlike provenance, data aggregates and data catalogs.
+This tutorial addresses Linked Data developers who want to publish Linked Data sets based on complex data like person-level microdata in combination with essential information like provenance, data aggregates and data catalogs.
 
@@
 The DDI-RDF Discovery Vocabulary (Disco)\footnote{current specification is available at \url{https://github.com/linked-statistics/disco-spec}}  is an RDF Schema vocabulary that supports the discovery of microdata sets and related metadata using RDF technologies in the Web of Linked Data.
-Disco can be used to discover datasets by searching for specific questions, topics, and geographical coverage.
+Disco can be used to discover data sets by searching for specific questions, topics, and geographical coverage.
 Disco is intended to provide means to describe microdata by essential metadata for the discovery purpose.
@@
 The Data Cube vocabulary is a W3C standard for representing data cubes representing multidimensional aggregate data derived from microdata which is represented by Disco.
-DCAT is a W3C standard for describing catalogs of datasets.
+DCAT is a W3C standard for describing catalogs of data sets.
 Physical data description (PHDD) represents data (tables) in a rectangular format.
@@
 However, person-level metadata is not restricted to a particular domain and may be an interesting data source for Linked Data developers.
-Hence, as our main objective, we want to provide assistence for creating such complex Linked Data sets using Disco.
+Hence, as our main objective, we want to provide assistance for creating such complex Linked Data sets using Disco.
 Because of the complexity, we especially want to demonstrate how Disco data sets can be connected with information represented using other existing vocabularies that are relevant in that context.
-Vice verse, we show how these other vocabualries and data represented with such can benefit from the interplay with Disco.
+Vice versa, we show how these other vocabularies and data represented with such can benefit from the interplay with Disco.
 
@@
 The infrastructure for these exercises, i.e. a triple store, will be provided for all participants.
-We will extend slides of a previous tutorial\footnote{tutorial slides avaliable at: \url{http://de.slideshare.net/boschthomas/201412-lets-disco-eddi-2014} and \url{http://de.slideshare.net/boschthomas/201412-lets-disco-2-eddi-2014}}
+We will extend slides of a previous tutorial\footnote{tutorial slides available at: \url{http://de.slideshare.net/boschthomas/201412-lets-disco-eddi-2014} and \url{http://de.slideshare.net/boschthomas/201412-lets-disco-2-eddi-2014}}
 and where appropriate refer to the current Disco specification\footnote{current specification is available at \url{https://github.com/linked-statistics/disco-spec}}.
@@
 \subsection{Intended Audiences}
-The intended audience of this tutorial are Linked Data developers - beginners as well as experts - who are interested in modelling and publishing complex and highly inter-connected data sets as Linked Data.
-Since the connection with other vocabulaires like QB, DCAT and PROV-O plays a major role in this context, the tutorial is not restricted to participants who are interested in person-level micro data.
+The intended audience of this tutorial are Linked Data developers - beginners as well as experts - who are interested in modeling and publishing complex and highly inter-connected data sets as Linked Data.
+Since the connection with other vocabularies like QB, DCAT and PROV-O plays a major role in this context, the tutorial is not restricted to participants who are interested in person-level micro data.
 
@@
 \begin{itemize} 
-\item Introduction of Disco, PHDD, and XKOS for modelling complex person-level micro data
+\item Introduction of Disco, PHDD, and XKOS for modeling complex person-level micro data
 \item Representing the interplay of Disco data with existing vocabularies
@@
 The defense talk will be at the end of January.
-Beside his PhD research, he works on modelling and publishing social science relevant data as Linked Data with the focus on data modelling and integration of heterogeneous data sources and information types.
+Beside his PhD research, he works on modeling and publishing social science relevant data as Linked Data with the focus on data modeling and integration of heterogeneous data sources and information types.
 He presented his work at several international conferences.

### 2015-01-09 paper/RDF validation requirements/RDF validation requirements.tex
typos

@@
 In this paper, we describe each requirement within the RDF validation requirements database in detail (sections 3-76).
+Additional descriptions can be found directly in the database.
 Each requirement corresponds to an RDF constraint which may be expressible by multiple constraint languages.
@@
 
-requirement:
-
-\begin{itemize}
-	\item R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS
-\end{itemize}
-
-\begin{itemize}
-	\item Some constraints require building new strings out of other strings
-\end{itemize}
-
-examples:
-
-\begin{itemize}
-	\item string length
-\end{itemize}
+\ms{String Operations} corresponds to the requirement
+\ms{R-194-PROVIDE-STRING-} \ms{FUNCTIONS-FOR-RDF-LITERALS}.
+Some constraints require building new strings out of other strings.
+Calculating the string length would also be another constraint of this type.
 
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-209-VALID-CLASSES
-\end{itemize}
-
-\begin{itemize}
-	\item What types of resources (rdf:type) are valid in this context? Context can be an input stream, a data creation function, or an API.
-\end{itemize}
+\ms{Context-Specific Valid Classes} corresponds to the requirements \\
+\ms{R-209-VALID-CLASSES}.
+What types of resources (rdf:type) are valid in a specific context? 
+Context can be an input stream, a data creation function, or an API.
 
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-210-VALID-PROPERTIES
-\end{itemize}
-
-\begin{itemize}
-	\item What properties can be used within this context? Context can be an data receipt function, data creation function, API, etc.
-\end{itemize}
+\ms{Context-Specific Valid Properties} corresponds to the requirement
+\ms{R-210-} \ms{VALID-PROPERTIES}.
+What properties can be used within this context? 
+Context can be an data receipt function, data creation function, or API.
 
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-31-DEFAULT-VALUES-OF-RDF-OBJECTS
-  \item R-38-DEFAULT-VALUES-OF-RDF-LITERALS
-\end{itemize}
-
-\begin{itemize}
-	\item default values for RDF literals
-	\item default values for RDF objects
-	\item default values are inferred automatically
-	\item It should be possible to declare the default value for a given property, e.g. so that input forms can be pre-populated and to insert a required property that is missing in a web service call. 
-\end{itemize}
+\ms{Default Values} corresponds to the requirements
+\ms{R-31-DEFAULT-VALUES-OF-RDF-} \ms{OBJECTS} and
+\ms{R-38-DEFAULT-VALUES-OF-RDF-LITERALS}.
+Default values for objects and literals are inferred automatically.
+It should be possible to declare the default value for a given property, e.g. so that input forms can be pre-populated and to insert a required property that is missing in a web service call.
 
@@
                 CONSTRUCT {            
-                    ?this :laserSwordColor "blue"^^xsd:string ;
-                    ?this :numberLaserSwords "1"^^xsd:nonNegativeInteger . 
+                    ?this laserSwordColor "blue"^^xsd:string ;
+                    ?this numberLaserSwords "1"^^xsd:nonNegativeInteger . 
                 }
                 WHERE {             
-                    ?this a :Jedi .            
+                    ?this a Jedi .            
                 } """ ; ] .
@@
                 CONSTRUCT {
-                    ?this :laserSwordColor "red"^^xsd:string ;
-                    ?this :numberLaserSwords "2"^^xsd:nonNegativeInteger . 
+                    ?this laserSwordColor "red"^^xsd:string ;
+                    ?this numberLaserSwords "2"^^xsd:nonNegativeInteger . 
                 }
                 WHERE {             
-                    ?this a :Sith .            
+                    ?this a Sith .            
                 } """ ; ] .
@@
 \begin{ex}
-# data
-# ----
-:Joda a :Jedi .
-:DarthSidious a :Sith .
-\end{ex}
-
-\begin{ex}
-# inferred triples
-# ----------------
-:Joda 
-    :laserSwordColor "blue"^^xsd:string ;
-    :numberLaserSwords "1"^^xsd:nonNegativeInteger .
-:DarthSidious 
-    :laserSwordColor "red"^^xsd:string ;
-    :numberLaserSwords "2"^^xsd:nonNegativeInteger .
+# data:
+Joda a Jedi .
+DarthSidious a Sith .
+\end{ex}
+
+\begin{ex}
+# inferred triples:
+Joda 
+    laserSwordColor "blue"^^xsd:string ;
+    numberLaserSwords "1"^^xsd:nonNegativeInteger .
+DarthSidious 
+    laserSwordColor "red"^^xsd:string ;
+    numberLaserSwords "2"^^xsd:nonNegativeInteger .
 \end{ex}
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-42-MATHEMATICAL-OPERATIONS
-	\item R-41-STATISTICAL-COMPUTATIONS
-\end{itemize}
-
-examples:
-
+\ms{Mathematical Operations} corresponds to the requirements
+\begin{itemize}
+	\item \ms{R-42-MATHEMATICAL-OPERATIONS} and
+  \item \ms{R-41-STATISTICAL-COMPUTATIONS}.
+\end{itemize}
+Examples are:
 \begin{itemize}
@@
 
-requirement:
-
-\begin{itemize}
-	\item R-47-LANGUAGE-TAG-MATCHING
-\end{itemize}
+\ms{Language Tag Matching} corresponds to the requirement \\
+\ms{R-47-LANGUAGE-TAG-MATCHING}.
 
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG
-	\item R-48-MISSING-LANGUAGE-TAGS
-\end{itemize}
-
-\subsection{Simple Example}
-
-check that no language is used more than once per property
-
-\begin{ex}
-# DQTP
-# ----
+\ms{Language Tag Cardinality} corresponds to the requirements
+\begin{itemize}
+	\item \ms{R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG} and
+	\item \ms{R-48-MISSING-LANGUAGE-TAGS}.
+\end{itemize}
+
+\subsection{Simple Example}
+
+Check that no language is used more than once per property
+
+\begin{ex}
+# DQTP:
 SELECT DISTINCT ?s WHERE { ?s %%P1%% ?c
@@
 
-\begin{itemize}
-	\item ONELANGPattern \cite{Kontokostas2014} 
-  \item A literal value should contain at most 1 literal for a language. 
-  \item P1 is the property containing the literal and V1 is the language we want to check.
-\end{itemize}
-
-\begin{ex}
-# test binding (DQTP)
----------------------
+This corresponds to the test pattern \ms{ONELANGPattern} \cite{Kontokostas2014}.
+A literal value should contain at most 1 literal for a language. 
+\ms{P1} is the property containing the literal and \ms{V1} is the language we want to check.
+
+\begin{ex}
+# test binding (DQTP):
 P1 => foaf:name
@@
 
-\begin{itemize}
-	\item a single English (“en”) foaf:name
-\end{itemize}
-
-\begin{ex}
-# valid data
-# ----------
+A single English (“en”) \ms{foaf:name}.
+
+\begin{ex}
+# valid data:
 :LeiaSkywalker
@@
 \begin{ex}
-# invalid data
-# ------------
+# invalid data:
 :LeiaSkywalker

### 2015-01-09 paper/ESWC 2015 Tutorial/ESWC2015Tutorial.tex
typos

@@
 
-Another objective of the tutorial is to share our experience in developing a RDF vocabulary out of an existing and highly-complex domain-specific data model.
+Another objective of the tutorial is to share our experience in developing an RDF vocabulary out of an existing and highly-complex domain-specific data model.
 We provide insight into the development and engineering process for creating Disco.

### 2015-01-09 paper/RDF validation requirements/RDF validation requirements.tex
finalize paper

@@
 
-\ms{Intersection} (composition, conjunction) corresponds to the requirements \ms{R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS} and \ms{R-16-CONJUNCTION-OF-DATA-RANGES}.
+\ms{Intersection} (composition, conjunction) corresponds to the requirements \\
+\ms{R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS} and \ms{R-16-CONJUNCTION-OF-DATA-} \ms{RANGES}.
 DLs allow new concepts and roles to be
@@
 
-requirement:
-
-\begin{itemize}
-	\item R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS
-\end{itemize}
-
-\begin{itemize}
-	\item avoid whitespaces in literals neither leading nor trailing white spaces
-\end{itemize}
-
-\subsection{Simple Example}
-
-check if literals of the property \ms{p} do not include whitespaces
+\ms{Whitespace Handling} corresponds to the requirement
+\ms{R-50-WHITESPACE-} \\
+\ms{HANDLING-OF-RDF-LITERALS}.
+Avoid whitespaces in literals neither leading nor trailing white spaces.
+
+\subsection{Simple Example}
+
+Check if literals of the property \ms{p} do not include whitespaces.
 
@@
 
-requirement:
-
-\begin{itemize}
-	\item R-51-HTML-HANDLING-OF-RDF-LITERALS
-\end{itemize}
-
-\begin{itemize}
-	\item check if there are no HTML tags included in literals (of specific data properties within the context of specific classes)
-\end{itemize}
-
-\subsection{Simple Example}
-
-check if literals of the property \ms{p} of the class \ms{C} do not include HTML tags
+\ms{HTML Handling} corresponds to the requirement
+\ms{R-51-HTML-HANDLING-OF-RDF-} \ms{LITERALS}.
+Check if there are no HTML tags included in literals (of specific data properties within the context of specific classes).
+
+\subsection{Simple Example}
+
+Check if literals of the property \ms{p} of the class \ms{C} do not include HTML tags.
 
@@
 
-requirements:
-
+\ms{Negative Property Constraints} corresponds to the requirements
 \begin{itemize}
-	\item R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS
-	\item R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS
+	\item \ms{R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS} and
+	\item \ms{R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS}.
 \end{itemize}
-
-\begin{itemize}
-	\item instances of a specific class must not have some object property
-  \item OWL 2 DL: ObjectComplementOf ( ObjectSomeValuesFrom ( ObjectPropertyExpression owl:Thing ) )
-\end{itemize}
+Instances of a specific class must not have some object property.
+In OWL 2 DL, this can be expressed as follows: \ms{ObjectComplementOf ( ObjectSomeValuesFrom ( ObjectPropertyExpression owl:Thing ) )}.
 
@@
 \begin{ex}
-# ShEx
-# ----
+# ShEx:
 <FeelingForce> {
-    :feelingForce (true) ,
-    :attitute xsd:string }
+    feelingForce (true) ,
+    attitute xsd:string }
 <JediMentor> {
-    :feelingForce (true) ,
-    :attitute ('good') ,
-    :laserSwordColor xsd:string ,
-    :numberLaserSwords xsd:nonNegativeInteger ,
-    :mentorOf @<JediStudent> ,
-   !:studentOf @<JediMentor> }
+    feelingForce (true) ,
+    attitute ('good') ,
+    laserSwordColor xsd:string ,
+    numberLaserSwords xsd:nonNegativeInteger ,
+    mentorOf @<JediStudent> ,
+   !studentOf @<JediMentor> }
 <JediStudent> {
-    :feelingForce (true) ,
-    :attitute ('good') ,
-    :laserSwordColor xsd:string ,
-    :numberLaserSwords xsd:nonNegativeInteger ,
-   !:mentorOf @<JediStudent> ,
-    :studentOf @<JediMentor> }
-\end{ex}
-
-\begin{itemize}
-	\item A matching triple has any predicate except those excluded by the '!' operator.
-  \item \url{http://w3.org/brief/Mzk0}
-\end{itemize}
-
-\begin{ex}
-# individuals matching 'FeelingForce' and 'JediMentor' data shapes
-# ----------------------------------------------------------------
-:Obi-Wan 
-    :feelingForce true ;
-    :attitute 'good' ;
-    :laserSwordColor 'blue' ;
-    :numberLaserSwords '1'^^xsd:nonNegativeInteger ;
-    :mentorOf :Anakin .
-\end{ex}
-
-\begin{ex}
-# individuals matching 'FeelingForce' and 'JediStudent' data shapes
-# -----------------------------------------------------------------
-:Anakin 
-    :feelingForce true ;
-    :attitute 'good' ;
-    :laserSwordColor 'blue' ;
-    :numberLaserSwords '1'^^xsd:nonNegativeInteger ;
-    :studentOf :Obi-Wan .
+    feelingForce (true) ,
+    attitute ('good') ,
+    laserSwordColor xsd:string ,
+    numberLaserSwords xsd:nonNegativeInteger ,
+   !mentorOf @<JediStudent> ,
+    studentOf @<JediMentor> }
+\end{ex}
+
+A matching triple has any predicate except those excluded by the '!' operator.
+
+\begin{ex}
+# individuals matching 'FeelingForce' and 'JediMentor' data shapes:
+Obi-Wan 
+    feelingForce true ;
+    attitute 'good' ;
+    laserSwordColor 'blue' ;
+    numberLaserSwords '1'^^xsd:nonNegativeInteger ;
+    mentorOf Anakin .
+\end{ex}
+
+\begin{ex}
+# individuals matching 'FeelingForce' and 'JediStudent' data shapes:
+Anakin 
+    feelingForce true ;
+    attitute 'good' ;
+    laserSwordColor 'blue' ;
+    numberLaserSwords '1'^^xsd:nonNegativeInteger ;
+    studentOf Obi-Wan .
 \end{ex}
@@
 
-requirement:
-
-\begin{itemize}
-	\item R-120-HANDLE-RDF-COLLECTIONS
-\end{itemize}
-
-examples:
-
+\ms{Handle RDF Collections} corresponds to the requirement
+\ms{R-120-HANDLE-RDF-} \ms{COLLECTIONS}.
+Examples are:
 \begin{itemize}
@@
 	\item are collections identical?
-	\item actions on RDF lists: \url{http://www.snee.com/bobdc.blog/2014/04/rdf-lists-and-sparql.html}
-	\item 2. list element equals ''
+	\item actions on RDF lists\footnote{See \url{http://www.snee.com/bobdc.blog/2014/04/rdf-lists-and-sparql.html}}
+	\item 2. list element equals 'XXX'
 	\item Does the list have more than 10 elements?
@@
 
-get 2. list element
-
-\begin{ex}
-# SPIN
-# ----
-:getListItem
+Get 2. list element:
+
+\begin{ex}
+# SPIN:
+getListItem
     a spin:Function ; rdfs:subClassOf spin:Functions ;
@@
             WHERE {
-                ?arg1 :contents/rdf:rest{?arg2}/rdf:first ?item } """ ; ] ;
+                ?arg1 contents/rdf:rest{?arg2}/rdf:first ?item } """ ; ] ;
     spin:returnType rdfs:Resource .
@@
 \begin{ex}
-# data
-# ----
-:Jinn :students 
-     ( :Xanatos :Kenobi ) . 
-\end{ex}
-
-\begin{ex}
-# SPIN
-# ----
-BIND ( :getListItem( ?list, "1"xsd:nonNegativeInteger ) AS ?listItem ) .
+# data:
+Jinn students 
+     ( Xanatos Kenobi ) . 
+\end{ex}
+
+\begin{ex}
+# SPIN:
+BIND ( getListItem( ?list, "1"xsd:nonNegativeInteger ) AS ?listItem ) .
 \end{ex}
@@
 \begin{ex}
-# result
-# ------
-:Kenobi
+# result:
+Kenobi
 \end{ex}
@@
 
-requirements:
-
-\begin{itemize}
-	\item R-222-RECURSIVE-QUERIES
-\end{itemize}
-
-\begin{itemize}
-	\item If we want to define Resource Shapes, remember that it is a recursive
+\ms{Recursive Queries} corresponds to the requirement
+\ms{R-222-RECURSIVE-QUERIES}.
+If we want to define Resource Shapes, remember that it is a recursive
 language (the valueShape of a Resource Shape is in turn another
@@
 references, recursively".
-  \item Most SPARQL engines already have
+Most SPARQL engines already have
 functions that go beyond the official SPARQL 1.1 spec. The cost of that
-sounds manageable to me.
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
-# ShEx
-# ----
+sounds manageable.
+
+\subsection{Simple Example}
+
+\begin{ex}
+# ShEx:
 IssueShape {
@@
 
-requirements:
-
-\begin{itemize}
-	\item 
-\end{itemize}
-
 Make sure that a value is valid for its datatype.
@@
 
-\begin{itemize}
-	\item a date is really a date
-  \item SPARQL regex can be used
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
-# SPIN
-# ----
+A date is really a date, as an example.
+SPARQL regex can be used for this purpose.
+
+\subsection{Simple Example}
+
+\begin{ex}
+# SPIN:
 FILTER ( datatype( ?shoeSize ) = xsd:nonNegativeInteger )
@@
 
-\begin{itemize}
-	\item datatype of ?showSize id xsd:nonNegativeInteger
-	\item datatype is really numeric
-\end{itemize}
+The datatype of ?showSize is xsd:nonNegativeInteger.
+The datatype is really numeric.
 
@@
 
-\subsection{Simple Example}
-
-\begin{DL} 
-$\rho(\textsf{hasBirthday}) \sqsubseteq \PVerb{xsd:dateTime}$\\
-\end{DL}
-
-Equal to the definition of a data property range.
-
-\tb{I do not understand the relation of this example to this constraint}
+%\subsection{Simple Example}
+%
+%\begin{DL} 
+%$\rho(\textsf{hasBirthday}) \sqsubseteq \PVerb{xsd:dateTime}$\\
+%\end{DL}
+%
+%Equal to the definition of a data property range.
 
@@
 \begin{ex}
-# OWL 2
-# -----
-:hasBrother owl:equivalentProperty :hasMaleSibling . 
-:Chris :hasBrother :Stewie . 
-:Stewie :hasMaleSibling :Chris .
+# OWL 2:
+hasBrother owl:equivalentProperty hasMaleSibling . 
+Chris hasBrother Stewie . 
+Stewie hasMaleSibling Chris .
 \end{ex}
@@
 \begin{ex}
-:Chris :hasMaleSibling a:Stewie . 
-:Stewie :hasBrother a:Chris .
-\end{ex}
-
-\begin{DL}
-:hasBrother $\sqsubseteq$ :hasMaleSibling $\sqcap$ :hasMaleSibling $\sqsubseteq$ :hasBrother \\
+Chris hasMaleSibling Stewie . 
+Stewie hasBrother Chris .
+\end{ex}
+
+\begin{DL}
+hasBrother $\sqsubseteq$ hasMaleSibling $\sqcap$ hasMaleSibling $\sqsubseteq$ hasBrother \\
 \end{DL}
@@
 
-\begin{itemize}
-	\item positive property assertions
-  \item negative property assertions
-	\item A positive object property assertion ObjectPropertyAssertion( OPE a1 a2 ) states that the individual a1 is connected by the object property expression OPE to the individual a2. 
-	\item A negative object property assertion NegativeObjectPropertyAssertion( OPE a1 a2 ) states that the individual a1 is not connected by the object property expression OPE to the individual a2. 
-	\item A positive data property assertion DataPropertyAssertion( DPE a lt ) states that the individual a is connected by the data property expression DPE to the literal lt. 
-	\item A negative data property assertion NegativeDataPropertyAssertion( DPE a lt ) states that the individual a is not connected by the data property expression DPE to the literal lt.
-\end{itemize}
-
-\subsection{Simple Example}
-
-\begin{ex}
-# OWL 2
-# -----
-NegativeObjectPropertyAssertion( :hasSon :Peter :Meg )
+\ms{{Property Assertions}} corresponds to the requirement \ms{R-96-PROPERTY-ASSERTIONS}
+and includes positive property assertions and negative property assertions.
+A positive object property assertion ObjectPropertyAssertion( OPE a1 a2 ) states that the individual a1 is connected by the object property expression OPE to the individual a2. 
+A negative object property assertion NegativeObjectPropertyAssertion( OPE a1 a2 ) states that the individual a1 is not connected by the object property expression OPE to the individual a2. 
+A positive data property assertion DataPropertyAssertion( DPE a lt ) states that the individual a is connected by the data property expression DPE to the literal lt. 
+A negative data property assertion NegativeDataPropertyAssertion( DPE a lt ) states that the individual a is not connected by the data property expression DPE to the literal lt.
+
+\subsection{Simple Example}
+
+\begin{ex}
+# OWL 2:
+NegativeObjectPropertyAssertion( hasSon Peter Meg )
 \end{ex}
@@
 \begin{ex}
-# OWL 2
-# -----
+# OWL 2:
 DataPropertyAssertion( :hasAge :Meg "17"^^xsd:integer )
@@
 \begin{ex}
-# OWL 2
-# -----
-:hasFather rdf:type owl:FunctionalProperty . 	
-:Stewie :hasFather :Peter . 	
-:Stewie :hasFather :Peter_Griffin . 
+# OWL 2:
+hasFather rdf:type owl:FunctionalProperty . 	
+Stewie hasFather Peter . 	
+Stewie hasFather Peter_Griffin . 
 \end{ex}
@@
 \begin{ex}
-:Peter_Griffin owl:sameAs :Peter .  
+Peter_Griffin owl:sameAs Peter .  
 \end{ex}
@@
 
-An object property inverse functionality axiom InverseFunctionalObjectProperty( OPE ) states that the object property expression OPE is inverse-functional — that is, for each individual x, there can be at most one individual y such that y is connected by OPE with x.
+An object property inverse functionality axiom InverseFunctionalObjectProperty( OPE ) states that the object property expression OPE is inverse-functional - that is, for each individual x, there can be at most one individual y such that y is connected by OPE with x.
 Each such axiom can be seen as a syntactic shortcut for the following axiom: SubClassOf( owl:Thing ObjectMaxCardinality( 1 ObjectInverseOf( OPE ) ) ).
@@
 \begin{ex}
-# OWL 2
-# -----
-:fatherOf rdf:type owl:InverseFunctionalProperty . 	
-:Peter :fatherOf :Stewie .
-:Peter_Griffin :fatherOf :Stewie .
+# OWL 2:
+fatherOf rdf:type owl:InverseFunctionalProperty . 	
+Peter fatherOf Stewie .
+Peter_Griffin fatherOf Stewie .
 \end{ex}
@@
 
-entailment:
-
-\begin{ex}
-:Peter owl:sameAs :Peter_Griffin . 
+Entailment:
+
+\begin{ex}
+Peter owl:sameAs Peter_Griffin . 
 \end{ex}
@@
 \begin{ex}
-# OWL 2
-# -----
-:Peter :fatherOf :Stewie . 
-ObjectHasValue( :fatherOf :Stewie )
-\end{ex}
-
-The has-value class expression contains those individuals that are connected through the :fatherOf property with the individual :Stewie.
-:Peter is classified as its instance.
+# OWL 2:
+Peter fatherOf Stewie . 
+ObjectHasValue( fatherOf Stewie )
+\end{ex}
+
+The has-value class expression contains those individuals that are connected through the \ms{fatherOf} property with the individual \ms{Stewie}.
+\ms{Peter} is classified as its instance.
 
@@
 \begin{ex}
-# OWL 2
-# -----
-:Peter :likes :Peter . 
-ObjectHasSelf( :likes ) 
-\end{ex}
-
-\begin{DL}
-LikesThemselves $\sqsubseteq$ $\exists$ likes . Self
+# OWL 2:
+Peter likes Peter . 
+ObjectHasSelf( likes ) 
+\end{ex}
+
+\begin{DL}
+LikesThemselves $\sqsubseteq$ $\exists$ likes.Self
 \end{DL}
@@
 The self-restriction contains those individuals that like themselves.
-:Peter is classified as its instance.
+\ms{Peter} is classified as its instance.
 
@@
 
-requirement:
-
-\begin{itemize}
-	\item R-46-CONSTRAINING-FACETS
-\end{itemize}
-
-\begin{itemize}
-  \item For datatype properties it should be possible to declare frequently needed "facets" to drive user interfaces and validate input against simple conditions, including min/max value, regular expressions, string length etc.
+\ms{Data Property Facets} corresponds to the requirement
+\ms{R-46-CONSTRAINING-FACETS}.
+For datatype properties it should be possible to declare frequently needed "facets" to drive user interfaces and validate input against simple conditions, including min/max value, regular expressions, string length etc.
 similar to XSD datatypes.
-	\item constraining facets to restrict datatypes of RDF literals
-  \item constraining facets: xsd:length, xsd:minLength, xsd:maxLength, xsd:pattern, xsd:enumeration, xsd:whiteSpace, xsd:maxInclusive, xsd:maxExclusive, xsd:minExclusive, xsd:minInclusive, xsd:totalDigits, xsd:fractionDigits
-
-\end{itemize}
+Constraining facets to restrict datatypes of RDF literals.
+Constraining facets may be: xsd:length, xsd:minLength, xsd:maxLength, xsd:pattern, xsd:enumeration, xsd:whiteSpace, xsd:maxInclusive, xsd:maxExclusive, xsd:minExclusive, xsd:minInclusive, xsd:totalDigits, xsd:fractionDigits.
 
@@
 \begin{ex}
-# OWL 2 QL (functional-style syntax)
-# ----------------------------------
-Declaration( Datatype( :SSN ) ) 
+# OWL 2 QL (functional-style syntax):
+Declaration( Datatype( SSN ) ) 
 DatatypeDefinition( 
-    :SSN
+    SSN
     DatatypeRestriction( xsd:string xsd:pattern "[0-9]{3}-[0-9]{2}-[0-9]{4}" ) )     
-DataPropertyRange( :hasSSN :SSN ) 
-\end{ex}
-
-\begin{ex}
-# OWL 2 QL (turtle syntax)
-# ------------------------
-:SSN 
+DataPropertyRange( hasSSN SSN ) 
+\end{ex}
+
+\begin{ex}
+# OWL 2 QL (turtle syntax):
+SSN 
     a rdfs:Datatype ;
@@
 
-\subsection{Simple Example}
-Each object is uniquely identified by its social security number.
-
-\begin{ex}
-# DSP
-# ---
--
-\end{ex}
-
-\begin{ex}
-# OWL2 DL
-# -------
-owl:Thing owl:hasKey ( :hasSSN ) . 	
-\end{ex}
-
-\begin{ex}
-# ReSh
-# ----
--
-\end{ex}
-
-\begin{ex}
-# ShEx
-# ----
--
-\end{ex}
-
-The first axiom makes :hasSSN the key for instances of the owl:Thing class; thus, only one individual can have a particular value for :hasSSN.
-
-\begin{ex}
-# data
-# ----
-:Peter :hasSSN "123-45-6789" . 
-:PeterGriffin :hasSSN "123-45-6789" . 
-\end{ex}
-
-\begin{DL}
-$(\textsf{funct } \textsf{SSN}\sp{\overline{\ }})$
-\end{DL}
-
-\begin{gcotable}
-property & $\top$ & SSN$^{-}$ & SSN & - & inverse & - \\
-property & $\top$ & SSN$^{-}$ & - & - & functional & - \\
-\end{gcotable}
-
-Since the values of :hasSSN are the same for the individuals a:Peter and a:PeterGriffin, these two individuals are equal - that is, this ontology entails the following assertion :Peter owl:sameAs :PeterGriffin .
+%\subsection{Simple Example}
+%Each object is uniquely identified by its social security number.
+%
+%\begin{ex}
+%# OWL2 DL:
+%owl:Thing owl:hasKey ( hasSSN ) . 	
+%\end{ex}
+%
+%The first axiom makes hasSSN the key for instances of the owl:Thing class; thus, only one individual can have a particular value for hasSSN. 
+%
+%\begin{ex}
+%# data
+%Peter hasSSN "123-45-6789" . 
+%PeterGriffin hasSSN "123-45-6789" . 
+%\end{ex}
+%
+%\begin{DL}
+%$(\textsf{funct } \textsf{SSN}\sp{\overline{\ }})$
+%\end{DL}
+%
+%\begin{gcotable}
+%property & $\top$ & SSN$^{-}$ & SSN & - & inverse & - \\
+%property & $\top$ & SSN$^{-}$ & - & - & functional & - \\
+%\end{gcotable}
+%
+%Since the values of hasSSN are the same for the individuals Peter and PeterGriffin, these two individuals are equal - that is, this ontology entails the following assertion Peter owl:sameAs PeterGriffin .
 
@@
 
-Since "Each object is uniquely identified by its social security number." It means it is inverse functional property.
-
-So instead,  a property can be defined as 
-\begin{DL}
-$(\textsf{funct } \textsf{SSN})$
-\end{DL}
-, and then by a property inclusion axiom
-
-\begin{DL}
-$haskey \sqsubseteq SSN^{-}$
-\end{DL}
-
-now for a given number haskey will give me the object (note that obviously it should be named, no ambigious individuals).
-
-However I needed to do some little research and found out that, keys are even more general (A generalisation of inverse functional properties) so that it can also be a chain of properties.
+%Since "Each object is uniquely identified by its social security number." It means it is inverse functional property.
+%
+%So instead, a property can be defined as 
+%\begin{DL}
+%$(\textsf{funct } \textsf{SSN})$
+%\end{DL}
+%, and then by a property inclusion axiom
+%
+%\begin{DL}
+%$haskey \sqsubseteq SSN^{-}$
+%\end{DL}
+%
+%now for a given number haskey will give me the object (note that obviously it should be named, no ambigious individuals).
+%
+%However I needed to do some little research and found out that, keys are even more general (A generalisation of inverse functional properties) so that it can also be a chain of properties.
 (it is clear here: http://www.w3.org/TR/2012/REC-owl2-rdf-based-semantics-20121211/\#table-semcond-keys)
-
-For this generalisation purposes and many spooky interactions of different sorts of key (and with some elaboration they can lead to undecidability), they introduced "key boxes, and extended the language with special "keyfor" construct.
+%
+%For this generalisation purposes and many spooky interactions of different sorts of key (and with some elaboration they can lead to undecidability), they introduced "key boxes, and extended the language with special "keyfor" construct.
 So how it is done in DL community as I learned is
-
-\begin{DL}
-SSN "keyfor" Human $\sqcap$ TurkishCitizen
-\end{DL}
-
- for instance. Now ssn behaves as an identifying element for individuals of right hand side.
-
-For comprehensive studies and resources, one can find lots of examples in:
-
-http://lat.inf.tu-dresden.de/research/mas/Din-Mas-06.pdf
-https://www.jair.org/media/1542/live-1542-2375-jair.pdf
-
-Yes you can, but as you see it is not restriction statement by its own.
+%
+%\begin{DL}
+%SSN "keyfor" Human $\sqcap$ TurkishCitizen
+%\end{DL}
+%
+ %for instance. Now ssn behaves as an identifying element for individuals of right hand side.
+%
+%For comprehensive studies and resources, one can find lots of examples in:
+%
+%http://lat.inf.tu-dresden.de/research/mas/Din-Mas-06.pdf
+%https://www.jair.org/media/1542/live-1542-2375-jair.pdf
+%
+%Yes you can, but as you see it is not restriction statement by its own.
 Nevertheless, I think, in DL mapping, use of "keyfor" and sending a reference to one of those papers is more convenient/safer, since it can be a datatype property, object property, or a chain of properties (from OWL world), as well as DL literature has it as "keyfor".
-
-\begin{gcotable}
-property & $\top$ & SSN & - & - & keyfor & - \\
+%
+%\begin{gcotable}
+%property & $\top$ & SSN & - & - & keyfor & - \\
+%\end{gcotable}
+
+\subsection{Simple Example}
+
+The \ms{Primary Key Properties} constraint is often useful to declare a given (datatype) property as the "primary key" of a class, so that a system can enforce uniqueness. 
+Starfleet officers, e.g., are uniquely identified by their command authorization code (e.g. to activate and cancel auto-destruct sequences).
+It means that the property \ms{commandAuthorizationCode} is inverse functional - mapped to DL and the RDF-CO as follows:
+
+\begin{DL}
+$(\ms{funct } commandAuthorizationCode\sp{\overline{\ }})$
+\end{DL}
+
+\begin{gcotable}
+property & $\top$ & commandAuthorizationCode$^{-}$ & commandAuthorizationCode$^{-}$ & - & inverse & - \\
+property & $\top$ & commandAuthorizationCode$^{-}$ & - & - & functional & - \\
+\end{gcotable}
+
+Keys, however, are even more general, i.e., a generalization of inverse functional properties \cite{Schneider2009}.
+A key can be a datatype property, an object property, or a chain of properties.
+For this generalization purposes, as there are different sorts of key, and as keys can lead to undecidability, 
+DL is extended with \ms{key boxes} and a special \ms{keyfor} construct\cite{Lutz2005}.
+This leads to the following DL and RDF-CO mappings (only one simple property constraint):
+
+\begin{DL}
+commandAuthorizationCode \ms{keyfor} StarfleetOfficer
+\end{DL}
+
+\begin{gcotable}
+property & StarFleetOfficer & commandAuthorizationCode & - & - & keyfor & - \\
 \end{gcotable}
@@
 
-requirement:
-
-\begin{itemize}
-	\item R-224-instance-level-data-validation-exploitingclass/property-specialization-axioms-in-ontologies
-\end{itemize}
-
-\begin{itemize}
-  \item Validation of instances data (direct or indirect) exploiting the subclass or sub-property link in a given ontology.
-  \item This validation can indicate when the data is verbose (redundant) or expressed at a too general level, and could be improved.
-\end{itemize}
-
-examples:
-
+\ms{Exploiting Class/Property Specialization Ontology Axioms} corresponds to the requirement
+\ms{R-224-instance-level-data-validation-exploitingclass/} \ms{property-specialization-axioms-in-ontologies}.
+Validation of instances data (direct or indirect) exploiting the subclass or sub-property link in a given ontology.
+This validation can indicate when the data is verbose (redundant) or expressed at a too general level, and could be improved.
+Examples are:
 \begin{itemize}

### 2015-01-09 paper/RDF validation requirements/RDF validation requirements.tex
conclusion

@@
 \ms{Disjunction} of classes or data ranges corresponds to the requirements \\
-\ms{R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS} and \ms{R-18-DISJUNCTION-OF-DATA-RANGES}.
+\ms{R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS} and \ms{R-18-DISJUNCTION-OF-} \\
+\ms{DATA-RANGES}.
 Synonyms are union and inclusive or.
@@
 
-\ms{Negation} (complement) corresponds to the requirements \ms{R-19-NEGATION-OF-CLASS-EXPRESSIONS} and \ms{R-20-NEGATION-OF-DATA-RANGES}.
+\ms{Negation} (complement) corresponds to the requirements \ms{R-19-NEGATION-OF-} \ms{CLASS-EXPRESSIONS} and \ms{R-20-NEGATION-OF-DATA-RANGES}.
 
@@
 
-This means that \ms{FeelingForce} individuals are individuals having one \ms{attackingBySword} relationship (range xsd:boolean) or one \ms{attackingByForce} relationship (range xsd:boolean) but not both.
+This means that \ms{FeelingForce} individuals are individuals having one \\
+\ms{attackingBySword} relationship (range xsd:boolean) or one \ms{attackingByForce} relationship (range xsd:boolean) but not both.
 
@@
 
-\ms{Repeatable Properties} corresponds to the requirement \ms{R-70-REPEATABLE-PROPERTIES}.
+\ms{Repeatable Properties} corresponds to the requirement \\
+\ms{R-70-REPEATABLE-PROPERTIES}.
 
@@
 
-\ms{Conditional Properties} corresponds to the requirement \ms{R-71-CONDITIONAL-PROPERTIES}.
+\ms{Conditional Properties} corresponds to the requirement \\
+\ms{R-71-CONDITIONAL-PROPERTIES}.
 
@@
 
-\ms{Recommended Properties} corresponds to the requirement \ms{R-72-RECOMMENDED-PROPERTIES}.
+\ms{Recommended Properties} corresponds to the requirement \\
+\ms{R-72-RECOMMENDED-PROPERTIES}.
 
@@
 \section{Conclusion and Future Work}
+There is no standard way to validate RDF data conforming to RDF constraints like XML Schemas serve to validate XML documents.
+Two working groups currently try to achieve a solution for RDF validation - the W3C RDF Data Shapes working group and the DCMI RDF Application Profiles working group. 
+We initiated a comprehensive database on RDF validation requirements: \url{http://purl.org/net/rdf-validation}.
+The intention of this database is to collaboratively work on case studies, use cases, requirements, and solutions on RDF validation.
+In this paper, we evaluated to which extend the five most promising constraint languages on being the standard (DSP, OWL2, ReSh, ShEx, and SPIN) fulfill each of the requirements to formulate RDF constraints.
+Each of these requirements corresponds to a type of constraint.
+The majority of the constraints can be expressed in DL, which serves as a logical underpinning of related requirements.
+We developed an ontology to express any constraint generically, so that constrains expressed by a constraint language $\alpha$ can be transformed into constraints expressed by a constraint language $\beta$ without any information loss.
+By expressing any constraint generically, we can provide a validation of the generically expressed constraint.
+When specific constraints are then transformed into generic constraints, we can provide the validation of the semantically equivalent specific constraints (expressed by multiple constraint languages) out-of-the-box without any additional effort and without any difference in validation results.
+As not every constrains can be represented in DL, we need to represent \emph{constraints expressible by DL} as well as \emph{constraints not expressible by DL} by means of this ontology.
+We shown in terms of an evaluation that any constraint can be expressed using the developed ontology.
+As part of future work, we will continuously add, modify, and maintain case studies, use cases, requirements, and solutions within the RDF validation requirements database.
 

### 2015-01-09 paper/ESWC 2015 Tutorial/ESWC2015Tutorial.tex
reworking every section, shortnening

--- 2015-01-08 paper/ESWC 2015 Tutorial/ESWC2015Tutorial.tex
@@
 \title{Let’s Disco – Publishing person-level data as Linked Data.}
-\subtitle{Building a Highly-Complex Data Set with Disco, PHDD, XKOS and widely used vocabularies.
+\subtitle{Building a Highly-Complex Data Set with Disco, PHDD, XKOS and widely used Vocabularies.
 }
@@
 \begin{abstract}
-The DDI-RDF Discovery Vocabulary (Disco) is an RDF Schema vocabulary that supports the discovery of microdata sets and related metadata using RDF technologies in the Web of Linked Data.
-Disco can be used to discover datasets by searching for specific questions, topics, and geographical coverage.
-Disco is intended to provide means to describe microdata by essential metadata for the discovery purpose.
-The DDI (Data Documentation Initiative) is a structured metadata standard related to the observation and measurement of human activity.
+The DDI-RDF Discovery Vocabulary (Disco) is an RDF Schema vocabulary that enables the representation of person-level data sets and related metadata.
+It is based on DDI (Data Documentation Initiative) which is a structured metadata standard related to the observation and measurement of human activity.
+%Disco is intended to provide means to describe person-level data by essential metadata for the discovery purpose. 
+Using Disco, such data sets can be discovered in the Web of Linked Data by using RDF technologies, e.g. searching for specific questions, topics, and geographical coverage.
 
-For a publication of DDI metadata as Linked Data, widely accepted and adopted RDF vocabularies (e.g. RDF Data Cube, DCAT, SKOS, PROV-O and Physical Data Description) are reused to a large extend. 
-In this tutorial it is shown how Disco is interwoven with these vocabularies. 
-The combined usage of Physical Data Description, Disco, and DCAT enables the creation of data repositories which provide metadata for the description of collections, for data discovery, and for processing of the data.
+For a meaningful publication of DDI metadata as Linked Data, additional established RDF vocabularies (e.g. RDF Data Cube, DCAT, SKOS, PROV-O, XKOS, and PHDD) are reused to a large extend. 
+This combined usage enables the creation of data repositories providing metadata of data collections, data sets, relationships between them and related provenance information.
 
+In this tutorial, we show how Disco is interwoven with these vocabularies and how these connections can be used in order to publish highly complex data sets.
 In different real world use cases, we demonstrate the adoption and inclusion of Disco in existing information systems. 
-Existing DDI instances are stored in form of XML documents which can be transformed into DDI-RDF and therefore exposed as Linked Data.
-We describe typical constraints on metadata of DDI metadata, as well as how to formulate them by different constraint languages (e.g. OWL 2) and how to actually validate them.
+%Existing DDI instances are stored in form of XML documents which can be transformed into DDI-RDF and therefore exposed as Linked Data.
+Additionally, we present typical metadata constraints of DDI metadata as well as how to formulate them by different constraint languages (e.g. OWL 2) and how to actually validate them.
 
-\keywords{DDI-RDF Discovery Vocabulary, Disco, Microdata Metadata, Data Documentation Initiative, Linked Data}
+\keywords{DDI-RDF Discovery Vocabulary, Disco, Person-level Metadata, Data Documentation Initiative, Linked Data}
 \end{abstract}
@@
 \section{Call for Participation}
-The DDI-RDF Discovery Vocabulary (Disco) is an RDF Schema vocabulary that supports the discovery of microdata sets and related metadata using RDF technologies in the Web of Linked Data. 
-It is based on the DDI (Data Documentation Initiative) which is a structured metadata standard related to the observation and measurement of human activity.
-Since this data is highly complex, widely accepted and adopted RDF vocabularies (e.g. RDF Data Cube, DCAT, SKOS, PROV-O and Physical Data Description) are reused to a large extend.
+The DDI-RDF Discovery Vocabulary (Disco) \cite{Bosch2012} is an RDF Schema vocabulary which can be utilized to represent person-level data sets and related metadata as Linked Data. 
+It is based on DDI (Data Documentation Initiative) which is a structured metadata standard related to the observation and measurement of human activity.
+The metadata of such data can get highly complex by e.g. necessary provenance information and relationships to data aggregates, data collections, and the physical data sources.
+Hence beside Disco, additional widely accepted and adopted RDF vocabularies (e.g.
+RDF Data Cube\footnote{\url{http://www.w3.org/TR/vocab-data-cube/}}, DCAT\footnote{\url{http://www.w3.org/TR/vocab-dcat/}}, SKOS\footnote{\url{http://www.w3.org/TR/skos-reference/}}, and PROV-O\footnote{\url{http://www.w3.org/TR/prov-o/}}) are reused to a large extend \cite{Bosch2013} in order to enable a full data documentation, which is necessary for discovering such data.
 
-In different real world use cases, the presenters of the tutorial demonstrate the adoption and inclusion of Disco in existing information systems.
-Participants are encouraged to present their own use cases where Disco has been applied or will be used. 
-Together with the presenters, participants will have the possibility to elaborate an RDF representation of their use cases and to formulate typical queries which are necessary to solve use case related problems.
+In this tutorial, an introduction to Disco and its inter-connections to these vocabularies is provided. 
+It is presented how these connections can be used in order to publish highly complex data sets.
+In different real world use cases and by building a data set serving as running example, the presenters of the tutorial demonstrate the adoption and inclusion of Disco in existing information systems.
+During practical exercises, participants will have the possibility to elaborate an RDF representation of the running example or their own data sets and to formulate typical queries.
+Participants are encouraged to present their own data sets and use cases where Disco has been applied or will be used.
 
-This tutorial addresses Linked Data developers who want to publish Linked Data sets based on complex data like person-level microdata in combination with essential informationlike provenance, data aggregates and data catalogs.
+This tutorial addresses Linked Data developers (beginners and experts) who want to publish Linked Data sets based on complex data like person-level data where essential information like provenance, data aggregates and data catalogs is necessary.
 
@@
 
-The DDI-RDF Discovery Vocabulary (Disco)\footnote{current specification is available at \url{https://github.com/linked-statistics/disco-spec}}  is an RDF Schema vocabulary that supports the discovery of microdata sets and related metadata using RDF technologies in the Web of Linked Data.
-Disco can be used to discover datasets by searching for specific questions, topics, and geographical coverage.
-Disco is intended to provide means to describe microdata by essential metadata for the discovery purpose.
+The DDI-RDF Discovery Vocabulary (Disco)\cite{Bosch2012,Bosch2013} is an RDF Schema vocabulary that enables the representation of person-level data sets and related metadata as Linked Data.
+It is based on DDI (Data Documentation Initiative)\footnote{\url{http://www.ddialliance.org/}}, a structured metadata standard related to the observation and measurement of human activity.
+%DDI started out in the mid-1990s as a replacement for traditional archival code books documenting research data, and then branched off to cover the research data life cycle. 
+%Over time, as the data landscape has changed, the DDI XML specifications have evolved to add new coverage and functionality to respond to new user requirements.
+While DDI is an international metadata standard with origins in the quantitative social sciences, it is increasingly being used by researchers and practitioners in other disciplines.
+It is also being used to document other data types, such as social media, biomarkers, administrative data, and transaction data.
+The specification itself is modular and can document and manage different stages of the data lifecycle, such as conceptualization, collection, processing, analysis, distribution, discovery, repurposing, and archiving.
+This tutorial aims to present the Disco vocabulary, its relationship to other necessary RDF vocabularies, and its validation.
 
-The DDI (Data Documentation Initiative) is a structured metadata standard related to the observation and measurement of human activity.
-It started out in the mid-1990s as a replacement for traditional archival code books documenting research data, and then branched off to cover the research data life cycle.
-Over time, as the data landscape has
-changed, the DDI XML specifications have evolved to add new coverage and functionality to respond to new user requirements.
-While the Data Documentation Initiative (DDI) is an international metadata standard with origins in the quantitative social sciences, it is increasingly being used by researchers and practitioners in other disciplines.
-The DDI specifications are also being used to document other data types, such as social media, biomarkers, administrative data, and transaction data.
-The specification itself is modular and can document and manage different stages of the data lifecycle, such as conceptualization, collection, processing, analysis, distribution, discovery, repurposing, and archiving.
-This tutorial aims to present the Disco vocabulary and its practical appliance with DDI metadata in detail.
-
-For a publication of DDI metadata as Linked Data, widely accepted and adopted RDF vocabularies (e.g.
-RDF Data Cube, DCAT, and PHDD) are reused to a large extend.
+For a publication of DDI metadata or similar metadata as Linked Data, additional established RDF vocabularies (e.g.
+RDF Data Cube, DCAT, SKOS, PROV-O, XKOS, and PHDD) are reused to a large extend.
 It is shown how Disco is interwoven with these vocabularies.
-The Data Cube vocabulary is a W3C standard for representing data cubes representing multidimensional aggregate data derived from microdata which is represented by Disco.
+These connections enable the representation of various relevant aspects, e.g.
+aggregate data derived from person-level data (micro data) by RDF Data Cube, PROV-O and Disco, data collections and catalogs (together with DCAT), and data (tables) in a rectangular format by using PHDD.
+XKOS can be used to represent statistical classifications.
+%The Data Cube vocabulary is a W3C standard for representing data cubes representing multidimensional aggregate data derived from microdata which is represented by Disco.
 DCAT is a W3C standard for describing catalogs of datasets.
@@
 
-Existing DDI instances are stored in form of XML documents and validated against XML Schemas\footnote{XML Schemas of current DDI version available at \url{http://www.ddialliance.org/Specification/DDI-Lifecycle/3.2/XMLSchema/}}.
-DDI-XML documents can be transformed into DDI-RDF and therefore exposed as Linked Data.
-For XML, XML Schema is the standard constraint language to validate XML documents.
-For RDF, however, there are multiple candidates for languages to express constraints on RDF data - but there is no standard language for RDF validation.
-In 2014, two working groups on RDF validation have been established: the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles working group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
-These working groups address the formulation and validation of RDF constraints.
-We will describe typical constraints on metadata of DDI metadata, as well as how to formulate and to validate them.
-We will show how to formulate these constraints by different constraint languages such as OWL 2.
+When publishing data sets, their validation is a necessary requirement.
+%Existing DDI instances are stored in form of XML documents and validated against XML Schemas\footnote{XML Schemas of current DDI version available at \url{http://www.ddialliance.org/Specification/DDI-Lifecycle/3.2/XMLSchema/}}.
+%DDI-XML documents can be transformed into DDI-RDF and therefore exposed as Linked Data.
+%For XML, XML Schema is the standard constraint language to validate XML documents.
+%For RDF, 
+While XML Schema is the standard constraint language to validate XML documents, there is no standard language for RDF validation.
+However, there are multiple candidates for languages to express constraints on RDF data.
+In 2014, two working groups on RDF validation have been established addressing these issues: the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles working group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
+%These working groups address the formulation and validation of RDF constraints.
+We will describe typical metadata constraints of Disco data sets as well as how to formulate them using different constraint languages such as OWL 2 and to validate them.
+%We will show how to formulate these constraints by different constraint languages such as OWL 2.
 
-In 2012, we started the development of Disco in form of a one-week Dagstuhl seminar - another one-week Dagstuhl seminar and two one-week workshops followed.  
-In 2014, we finished the technical review of Disco.
-We addressed more than ten mailing lists from the Linked Data and the DDI communities and got feedback which has been incorporated into the Disco specification.
-We are planning to officially publish Disco after three years of development in the first half of the year 2015 after an additional official technical review of the DDI Alliance\footnote{\url{http://www.ddialliance.org/}}.
+The development of Disco started in 2012 at a Dagstuhl seminar followed by additional seminars and workshops.  
+In 2014, we finished the technical review of Disco after contacting multiple mailing lists from the Linked Data and the DDI communities. 
+%The received feedback has been incorporated into the Disco specification.
+We are planning to officially publish Disco after three years of development in the first half of the year 2015. 
+%after an additional official technical review of the DDI Alliance\footnote{\url{http://www.ddialliance.org/}}.
 
 \subsection{Objectives of the Tutorial} 
-The domain-specific origin of Disco increases the difficulties for adopting it by developers who are not familiar with the domain.
-However, person-level metadata is not restricted to a particular domain and may be an interesting data source for Linked Data developers.
-Hence, as our main objective, we want to provide assistence for creating such complex Linked Data sets using Disco.
-Because of the complexity, we especially want to demonstrate how Disco data sets can be connected with information represented using other existing vocabularies that are relevant in that context.
+The main objective of this tutorial is to introduce Disco and to provide assistence for creating Linked Data sets using Disco.
+Person-level or similar metadata is not restricted to a particular domain and may be an interesting data source for Linked Data developers.
+Because of the complexity that comes along with such data, we especially want to demonstrate how Disco data sets can be connected with information represented using other existing vocabularies that are relevant in that context.
 Vice verse, we show how these other vocabualries and data represented with such can benefit from the interplay with Disco.
 
-Another objective of the tutorial is to share our experience in developing a RDF vocabulary out of an existing and highly-complex domain-specific data model.
+Another objective of the tutorial is to share our experience in developing a RDF vocabulary out of an existing and complex domain-specific data model like DDI.
 We provide insight into the development and engineering process for creating Disco.
@@
 \subsection{Relevance to ESWC 2015}
-In this tutorial, the DDI-RDF Discovery vocabulary (Disco) and its interplay with other existing vocabularies is introduced.
-In contrast to other newly developed vocabularies that can be adopted easily by Linked Data experts in most cases, the complexity of Disco is higher because of its domain-specific origin and the tight interplay with other existing vocabularies.
-This makes Disco more difficult to be adopted by Linked Data experts that may not be familiar with the domain-specific background of person-level micro data.
-However, since the number of organizations that aim to publish their complex data as Linked Data grows and the number of researchers that want to conduct their research with real-world data grows, a tutorial on representing such highly complex and inter-connected data sets may be a beneficial addition for the audience of ESWC 2015.
+%In this tutorial, the DDI-RDF Discovery vocabulary (Disco) and its interplay with other existing vocabularies is introduced.
+In contrast to other newly developed vocabularies that can be adopted easily in most cases, the complexity of Disco is higher because of its domain-specific origin and the tight interplay with other existing vocabularies.
+This makes Disco more difficult to be adopted by developers who may not be familiar with the domain-specific background of person-level or similar data.
+However, since the number of organizations that aim to publish their data as Linked Data grows and the number of Linked Data researchers that want to use real-world data grows, a tutorial on representing such inter-connected data sets may be a beneficial addition for the audience of ESWC 2015.
 
@@
 
-During the tutorial, we built one real world complex data set which serves as ongoing running example. 
-The whole data set can be exported from the Microdata Information System\footnote{\url{http://www.gesis.org/missy/editor/}}. 
-In all sessions, there will be practical hands-on exercises where the participants are asked to model and query particular parts of this data set. 
-The infrastructure for these exercises, i.e. a triple store, will be provided for all participants.
-We will extend slides of a previous tutorial\footnote{tutorial slides avaliable at: \url{http://de.slideshare.net/boschthomas/201412-lets-disco-eddi-2014} and \url{http://de.slideshare.net/boschthomas/201412-lets-disco-2-eddi-2014}}
-and where appropriate refer to the current Disco specification\footnote{current specification is available at \url{https://github.com/linked-statistics/disco-spec}}.
+%During the tutorial, we will build one real world data set which serves as ongoing running example. 
+%The whole data set can be exported from the Microdata Information System\footnote{\url{http://www.gesis.org/missy/editor/}}. 
+%In all sessions, there will be practical exercises where the participants are asked to model and query particular parts of this data set. 
+%The infrastructure for these exercises, i.e. a triple store and the data set, will be provided for all participants.
+The scope of the tutorial covers the introduction of the Disco vocabulary, its connected vocabularies PHDD and XKOS as well as their interplay with other established vocabularies.
+Additionally, the validation of Disco data sets will be covered.
+Slides of a previous tutorial\footnote{tutorial slides avaliable at: \url{http://de.slideshare.net/boschthomas/201412-lets-disco-eddi-2014} and \url{http://de.slideshare.net/boschthomas/201412-lets-disco-2-eddi-2014}}
+will be reused and extended. We will also refer to the current Disco specification\footnote{current specification is available at \url{https://github.com/linked-statistics/disco-spec}}.
+Material for the practical exercises will be provided by the presenters (see Section 2.6).
 
@@
 The intended audience of this tutorial are Linked Data developers - beginners as well as experts - who are interested in modelling and publishing complex and highly inter-connected data sets as Linked Data.
-Since the connection with other vocabulaires like QB, DCAT and PROV-O plays a major role in this context, the tutorial is not restricted to participants who are interested in person-level micro data.
+Since the connection with other vocabulaires like RDF Data Cube, DCAT and PROV-O plays a major role in this context, the tutorial is not restricted to participants who are interested in person-level or similar data.
 
 \subsection{Learning Objectives}
-The learning objectives of this tutorial are the following:
-\begin{itemize} 
-\item Introduction of Disco, PHDD, and XKOS for modelling complex person-level micro data
-\item Representing the interplay of Disco data with existing vocabularies
-\item Validation of Disco
-\end{itemize}
+The learning objectives of this tutorial are the following: (1) introducing Disco, PHDD, and XKOS for modelling complex person-level data, (2) representing the interplay of Disco data with existing and established vocabularies like RDF Data Cube, DCAT, and PROV-O, and (3) the validation of Disco.
 
@@
 We propose a full-day tutorial.
-In the previous tutorial about Disco, we experienced that a half-day tutorial offers only enough time to cover the most important aspects about Disco and to include few hands-on exercises.
+In a previous tutorial about Disco, we experienced that a half-day tutorial offers only enough time to cover the most important aspects about Disco and to include few hands-on exercises.
 Since we now want to expand the focus of the tutorial to the interplay of Disco with other vocabularies and its validation, a full-day seems to be appropriate.
@@
 The tutorial was well received and the presenters got overall positive feedback.
-Since the audience of Disco is two-fold - data professionals and the DDI community at the one hand and Linked Data experts at the other hand - the idea was to offer this tutorial at the ESWC conference as well.
-At the EDDI conference, the first part of the audience - data professionals and the DDI community - was addressed.
-At the ESWC conference, the second part of our audience - Linked Data experts - will be addressed.
+Since the audience of Disco is two-fold - data professionals and the DDI community at the one hand and Linked Data experts at the other hand - the idea was to offer this tutorial at the ESWC conference as well in order to address the the Linked Data community.
+%At the EDDI conference, the first part of the audience - data professionals and the DDI community - was addressed.
+%At the ESWC conference, the second part of our audience - Linked Data experts - will be addressed.
 
@@
 
-\bibliography{../../literature/literature}{}
-\bibliographystyle{plain}
-\setcounter{tocdepth}{1}
+%\bibliography{../../literature/literature}{}
+%\bibliographystyle{plain}
+%\setcounter{tocdepth}{1}
+\begin{thebibliography}{1}
+\bibitem{Bosch2012}
+Thomas Bosch, Richard Cyganiak, Joachim Wackerow and Benjamin Zapilko.
+Leveraging the {DDI} Model for Linked Statistical Data in the Social, Behavioural, and Economic Sciences.
+Proceedings of the 2012 International Conference on Dublin Core and 	Metadata Applications
+\bibitem{Bosch2013}
+Thomas Bosch, Benjamin Zapilko, Joachim Wackerow and Arofan Gregory.
+Towards the discovery of person-level data: reuse of vocabularies and related use cases.
+Proceedings of the International Workshop on Semantic Statistics (SemStats 2013) collocated with the 12th International Semantic Web Conference (ISWC-2013)
+\end{thebibliography}
 %\listoftodos

### 2015-01-09 paper/RDF validation requirements/RDF validation requirements.tex
RDF citations

--- 2015-01-09 paper/RDF validation requirements/RDF validation requirements.tex
@@
 In this paper, we describe each requirement within the RDF validation requirements database in detail (sections 3-76).
-Additional descriptions can be found directly in the database.
 Each requirement corresponds to an RDF constraint which may be expressible by multiple constraint languages.
@@
 
-\ms{String Operations} corresponds to the requirement
-\ms{R-194-PROVIDE-STRING-} \ms{FUNCTIONS-FOR-RDF-LITERALS}.
-Some constraints require building new strings out of other strings.
-Calculating the string length would also be another constraint of this type.
+requirement:
+
+\begin{itemize}
+	\item R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS
+\end{itemize}
+
+\begin{itemize}
+	\item Some constraints require building new strings out of other strings
+\end{itemize}
+
+examples:
+
+\begin{itemize}
+	\item string length
+\end{itemize}
 
@@
 
-\ms{Context-Specific Valid Classes} corresponds to the requirements \\
-\ms{R-209-VALID-CLASSES}.
-What types of resources (rdf:type) are valid in a specific context? 
-Context can be an input stream, a data creation function, or an API.
+requirements:
+
+\begin{itemize}
+	\item R-209-VALID-CLASSES
+\end{itemize}
+
+\begin{itemize}
+	\item What types of resources (rdf:type) are valid in this context? Context can be an input stream, a data creation function, or an API.
+\end{itemize}
 
@@
 
-\ms{Context-Specific Valid Properties} corresponds to the requirement
-\ms{R-210-} \ms{VALID-PROPERTIES}.
-What properties can be used within this context? 
-Context can be an data receipt function, data creation function, or API.
+requirements:
+
+\begin{itemize}
+	\item R-210-VALID-PROPERTIES
+\end{itemize}
+
+\begin{itemize}
+	\item What properties can be used within this context? Context can be an data receipt function, data creation function, API, etc.
+\end{itemize}
 
@@
 
-\ms{Default Values} corresponds to the requirements
-\ms{R-31-DEFAULT-VALUES-OF-RDF-} \ms{OBJECTS} and
-\ms{R-38-DEFAULT-VALUES-OF-RDF-LITERALS}.
-Default values for objects and literals are inferred automatically.
-It should be possible to declare the default value for a given property, e.g. so that input forms can be pre-populated and to insert a required property that is missing in a web service call.
+requirements:
+
+\begin{itemize}
+	\item R-31-DEFAULT-VALUES-OF-RDF-OBJECTS
+  \item R-38-DEFAULT-VALUES-OF-RDF-LITERALS
+\end{itemize}
+
+\begin{itemize}
+	\item default values for RDF literals
+	\item default values for RDF objects
+	\item default values are inferred automatically
+	\item It should be possible to declare the default value for a given property, e.g. so that input forms can be pre-populated and to insert a required property that is missing in a web service call. 
+\end{itemize}
 
@@
                 CONSTRUCT {            
-                    ?this laserSwordColor "blue"^^xsd:string ;
-                    ?this numberLaserSwords "1"^^xsd:nonNegativeInteger . 
+                    ?this :laserSwordColor "blue"^^xsd:string ;
+                    ?this :numberLaserSwords "1"^^xsd:nonNegativeInteger . 
                 }
                 WHERE {             
-                    ?this a Jedi .            
+                    ?this a :Jedi .            
                 } """ ; ] .
@@
                 CONSTRUCT {
-                    ?this laserSwordColor "red"^^xsd:string ;
-                    ?this numberLaserSwords "2"^^xsd:nonNegativeInteger . 
+                    ?this :laserSwordColor "red"^^xsd:string ;
+                    ?this :numberLaserSwords "2"^^xsd:nonNegativeInteger . 
                 }
                 WHERE {             
-                    ?this a Sith .            
+                    ?this a :Sith .            
                 } """ ; ] .
@@
 \begin{ex}
-# data:
-Joda a Jedi .
-DarthSidious a Sith .
-\end{ex}
-
-\begin{ex}
-# inferred triples:
-Joda 
-    laserSwordColor "blue"^^xsd:string ;
-    numberLaserSwords "1"^^xsd:nonNegativeInteger .
-DarthSidious 
-    laserSwordColor "red"^^xsd:string ;
-    numberLaserSwords "2"^^xsd:nonNegativeInteger .
+# data
+# ----
+:Joda a :Jedi .
+:DarthSidious a :Sith .
+\end{ex}
+
+\begin{ex}
+# inferred triples
+# ----------------
+:Joda 
+    :laserSwordColor "blue"^^xsd:string ;
+    :numberLaserSwords "1"^^xsd:nonNegativeInteger .
+:DarthSidious 
+    :laserSwordColor "red"^^xsd:string ;
+    :numberLaserSwords "2"^^xsd:nonNegativeInteger .
 \end{ex}
@@
 
-\ms{Mathematical Operations} corresponds to the requirements
-\begin{itemize}
-	\item \ms{R-42-MATHEMATICAL-OPERATIONS} and
-  \item \ms{R-41-STATISTICAL-COMPUTATIONS}.
-\end{itemize}
-Examples are:
+requirements:
+
+\begin{itemize}
+	\item R-42-MATHEMATICAL-OPERATIONS
+	\item R-41-STATISTICAL-COMPUTATIONS
+\end{itemize}
+
+examples:
+
 \begin{itemize}
@@
 
-\ms{Language Tag Matching} corresponds to the requirement \\
-\ms{R-47-LANGUAGE-TAG-MATCHING}.
+requirement:
+
+\begin{itemize}
+	\item R-47-LANGUAGE-TAG-MATCHING
+\end{itemize}
 
@@
 
-\ms{Language Tag Cardinality} corresponds to the requirements
-\begin{itemize}
-	\item \ms{R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG} and
-	\item \ms{R-48-MISSING-LANGUAGE-TAGS}.
-\end{itemize}
-
-\subsection{Simple Example}
-
-Check that no language is used more than once per property
-
-\begin{ex}
-# DQTP:
+requirements:
+
+\begin{itemize}
+	\item R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG
+	\item R-48-MISSING-LANGUAGE-TAGS
+\end{itemize}
+
+\subsection{Simple Example}
+
+check that no language is used more than once per property
+
+\begin{ex}
+# DQTP
+# ----
 SELECT DISTINCT ?s WHERE { ?s %%P1%% ?c
@@
 
-This corresponds to the test pattern \ms{ONELANGPattern} \cite{Kontokostas2014}.
-A literal value should contain at most 1 literal for a language. 
-\ms{P1} is the property containing the literal and \ms{V1} is the language we want to check.
-
-\begin{ex}
-# test binding (DQTP):
+\begin{itemize}
+	\item ONELANGPattern \cite{Kontokostas2014} 
+  \item A literal value should contain at most 1 literal for a language. 
+  \item P1 is the property containing the literal and V1 is the language we want to check.
+\end{itemize}
+
+\begin{ex}
+# test binding (DQTP)
+---------------------
 P1 => foaf:name
@@
 
-A single English (“en”) \ms{foaf:name}.
-
-\begin{ex}
-# valid data:
+\begin{itemize}
+	\item a single English (“en”) foaf:name
+\end{itemize}
+
+\begin{ex}
+# valid data
+# ----------
 :LeiaSkywalker
@@
 \begin{ex}
-# invalid data:
+# invalid data
+# ------------
 :LeiaSkywalker
@@
 
-\end{document}
-
 \bibliography{../../literature/literature}{}

### 2015-01-10 paper/paper6/paper6.tex
elsevier tex

%% JWS example using Elsevier elsart classes, adapted by Tim 
%% Finin, finin@cs.umbc.edu

%% comment out one of these to get preprint vs. journal format

%\documentclass{elsart}       %% one column for review, preprint
\documentclass{elsart3p}    %% two columns for publication

\usepackage{graphicx,amssymb}

\renewcommand\floatpagefraction{.2}
\makeatletter
\def\elsartstyle{%
    \def\normalsize{\@setfontsize\normalsize\@xiipt{14.5}}
    \def\small{\@setfontsize\small\@xipt{13.6}}
    \let\footnotesize=\small
    \def\large{\@setfontsize\large\@xivpt{18}}
    \def\Large{\@setfontsize\Large\@xviipt{22}}
    \skip\@mpfootins = 18\p@ \@plus 2\p@
    \normalsize
}
\@ifundefined{square}{}{\let\Box\square}
\makeatother

%% tell Latex where to look for files menioned in \includegraphics
\graphicspath{{jwsGraphics/}}

\begin{document}

\begin{frontmatter}

%% This TITLE has a note reference (titleNote) whose 
%% contants is specified about 10 lines later.

\title{RDF Validation of \\ Metadata on Highly-Complex Person-Level Data Sets}

%% Here are the three AUTHORS.  Note the separating commas
%% with no and.

\author[gesis]{Thomas Bosch\corauthref{C}},
\ead{thomas.bosch@gesis.org}
\author[gesis]{Benjamin Zapilko},
\ead{benjamin.zapilko@gesis.org}
\author[gesis]{Joachim Wackerow}
\ead{joachim.wackerow@gesis.org}
\author[mannheim]{Kai Eckert}
\ead{kai@informatik.uni-mannheim.de}

%% these specify any 'notes' for the title and authors,
%% including 'thanks' that acknowledge support, etc. and an
%% indication of who the corresponding author is if there's
%% more than one author.

%\thanks[titleNote]{Adapted from a document written by Simon Pepping}
%\thanks[fininGrants]{Partisl support provided by NSF award NSF-ITR-IIS-0326460} 
\corauth[C]{Corresponding author. Tel: + 49 (0) 621 / 1246-271}

\medskip

%% Here are the addresses refereenced for the authors.  If
%% all of the authors are from the same institution you need
%% not have the lables for the author and address commands.

\address[gesis]{Gesis - Leibniz Institute for the Social Sciences, 68159 Mannheim, Germany}
\address[mannheim]{University of Mannheim, 68159 Mannheim, Germany}

\begin{abstract}

\end{abstract}

%% you choose your own keywords

\begin{keyword}
 RDF Validation, Person-Level Metadata, DDI-RDF Discovery Vocabulary, Disco, Linked Data
\end{keyword}

\end{frontmatter}

\section{Introduction}
\label{introduction}

\bibliographystyle{elsart-num-sort}

\bibliography{../../literature/literature}

\end{document}

### 2015-01-10 paper/paper6/paper6.tex
RDF Data Cube constraints

@@
 
+% Todos
+\usepackage[colorinlistoftodos]{todonotes}
+\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
+\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}
+\newcommand{\bz}[1]{\todo[size=\small, color=red!40]{\textbf{Ben:} #1}}
+\newcommand{\jw}[1]{\todo[size=\small, color=blue!40]{\textbf{Achim:} #1}}
+
 \begin{document}
@@
 \author[gesis]{Joachim Wackerow}
-\ead{joachim.wackerow@gesis.org}
+\ead{joachim.wackerow@gesis.org},
 \author[mannheim]{Kai Eckert}
@@
 
-\section{Introduction}
-\label{introduction}
+\section{Motivation}
+
+\begin{itemize}
+	\item Why do we need RDF Validation?
+	\item Why do we need to validate metadata on person-level data sets? 
+\end{itemize}
+
+\section{Data Documentation Initiative}
+
+\section{DDI-RDF Discovery Vocabulary}
+
+\begin{itemize}
+  \item overview of disco
+	\item description of disco
+\end{itemize}
+
+\subsection{Conceptional Model}
+
+\subsection{Use Cases}
+
+\subsection{Relationships to other Vocabularies}
+
+\begin{itemize}
+	\item RDF Data Cube, DCAT, PHDD, XKOS
+	\item brief description of vocabularies
+\end{itemize}
+
+\section{Validation of Metadata on Person-Level Data Sets}
+
+\subsection{Qualified Cardinality Restrictions}
+
+\section{Validation in Combination with other Vocabularies}
+
+\subsection{RDF Data Cube Vocabulary}
+
+There are 22 RDF Data Cube integrity constraints\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf} \cite{CyganiakReynolds2014}.
+
+\textcolor{blue}{describe 1 constraint of each type in detail with Datalog query}
+
+\textbf{Datatypes.}
+\begin{itemize}
+	\item {\em IC-0:} Datatypes must be consistent under RDF D-entailment using a datatype map containing all the datatypes used within the graph.
+\end{itemize}
+
+\textbf{Unqualified Cardinality Restrictions.}
+\begin{itemize}
+	\item {\em IC-4:} Every dimension declared in a {\em qb:DataStructureDefinition} must have a declared {\em rdfs:range}.  
+\end{itemize}
+
+\textbf{Qualified Cardinality Restrictions.}
+\begin{itemize}
+	\item {\em IC-1:} Every {\em qb:Observation} has exactly one associated {\em qb:DataSet}. 
+	\item {\em IC-2:} Every {\em qb:DataSet} has exactly one associated {\em qb:DataStructureDefinition}. 
+	\item {\em IC-3:} Every {\em qb:DataStructureDefinition} must include at least one declared measure. 
+\end{itemize}
+
+\textcolor{blue}{are there further constraints which can be described in this paper?}
+
+\subsection{SKOS and XKOS}
+
+\subsection{PHDD}
+
+\section{Implementation}
+
+\textbf{Validation of Data Cube instances.}
+\begin{itemize}
+	\item \textcolor{blue}{is there an implementation available yet? If not I implement it in our validation environment}
+\end{itemize}
+
+\section{Related Work}
+
+\textbf{RDF Data Cube Vocabulary.}
+A well-formed RDF Data Cube is an a RDF graph describing one or more instances of {\em qb:DataSet} for which each of the defined integrity constraints passes.
+Each integrity constraint is expressed as narrative prose and, where possible, a SPARQL ASK query or query template. 
+If the ASK query is applied to an RDF graph then it will return true if that graph contains one or more Data Cube instances which violate the corresponding constraint.
+\cite{CyganiakReynolds2014}
+
+\section{Conclusion and Future Work}
 

### 2015-01-10 paper/paper6/paper6.tex
disco constraints

@@
 \newcommand{\jw}[1]{\todo[size=\small, color=blue!40]{\textbf{Achim:} #1}}
+
+\newenvironment{DL}{
+  %\scriptsize
+  %\sffamily
+  \vspace{0cm}
+  \begin{tabular}{l l}
+
+}{
+  \end{tabular}
+  %\linebreak
+}
 
@@
 
+\textbf{Contributions.}
+\begin{itemize}
+  \item We define constraints on Disco, Data Cube, PHDD, DCAT, XKOS data sets
+	\item WE provide an implementation to validate Disco, Data Cube, PHDD, DCAT, XKOS data sets 
+\end{itemize}
+
 \section{Data Documentation Initiative}
@@
 
+\section{Validation Environment}
+
 \section{Validation of Metadata on Person-Level Data Sets}
 
-\subsection{Qualified Cardinality Restrictions}
+\subsection{Data Model Consistency}
+
+Is the data consistent with the intended semantics of the data model?
+Ensures the integrity of the data according to the data model.
+
+\subsection{Unqualified Cardinality Restrictions}
+
+\subsection{Minimum Qualified Cardinality Restrictions}
+
+{\em DISCO-C-XX}. 
+A {\em disco:Questionnaire} has at least 1 {\em disco:question} relationship to {\em disco:Question}.
+
+\begin{DL}
+Questionnaire $\sqsubseteq$ $\geq$1 question.Question
+\end{DL}
+
+\subsection{Exact Qualified Cardinality Restrictions}
+
+{\em DISCO-C-XX}. 
+A {\em disco:Question} has exactly 1 {\em disco:universe} relationship to {\em disco:Universe}.
+
+\begin{DL}
+Question $\sqsubseteq$ \\
+$\geq$1 universe.Universe $\sqcap$ $\leq$1 universe.Universe \\
+\end{DL}
+
+\subsection{Universal Quantifications}
+
+{\em DISCO-C-XX}. 
+Only {\em disco:LogicalDataSet}s can have {\em disco:aggregation} relationships to {\em qb:DataSet}s.
+
+\begin{DL}
+LogicalDataSet $\sqsubseteq$ $\forall$ aggregation.DataSet \\
+\end{DL}
+
+\subsection{Existential Quantifications}
+
+{\em DISCO-C-XX}. 
+There must be at least 1 {\em disco:universe} relationship from {\em disco:Studies} or {\em disco:StudyGroups} to {\em disco:Universe}.
+
+\begin{DL}
+Study $\sqcup$ StudyGroup $\sqsubseteq$ $\exists$ universe.Universe \\
+\end{DL}
+
+\subsection{SKOS-Related Constraints}
+
+\subsubsection{Membership in Controlled Vocabularies.}
+
+Questions, variables, and represented variables may have representations.
+
+\subsubsection{Hierarchies}
+
+Hierarchies of DDI concepts
+
+\begin{itemize}
+	\item root?
+\end{itemize}
+
+\subsection{Ordering}
+
+In DDI, variables, questions, and categories are typically organized in a particular order. 
+For obtaining this order, {\em skos:OrderedCollection} resources are used. 
+A collection of variables, e.g, is represented as being of the type {\em skos:OrderedCollection} containing multiple variables (each represented as {\em skos:Concept}) in a {\em skos:memberList}.
 
@@
 
-\textcolor{blue}{describe 1 constraint of each type in detail with Datalog query}
-
-\textbf{Datatypes.}
 \begin{itemize}
-	\item {\em IC-0:} Datatypes must be consistent under RDF D-entailment using a datatype map containing all the datatypes used within the graph.
+	\item \textcolor{blue}{describe 1 constraint of each type in detail with Datalog query}
 \end{itemize}
 
+\textbf{Data Model Consistency.}
+{\em IC-0}, \textcolor{red}{{\em IC-8}}, {\em IC-13}, {\em IC-14}, {\em IC-15}, {\em IC-16}, {\em IC-17}, \textcolor{red}{{\em IC-18}}
+%\begin{itemize}
+	%\item {\em IC-0:} Datatypes must be consistent under RDF D-entailment using a datatype map containing all the datatypes used within the graph.
+	%\item \textcolor{red}{{\em IC-8:} Every {\em qb:componentProperty} on a {\em qb:SliceKey} must also be declared as a {\em qb:component} of the associated {\em qb:DataStructureDefinition}.} 
+%\end{itemize}
+
 \textbf{Unqualified Cardinality Restrictions.}
-\begin{itemize}
-	\item {\em IC-4:} Every dimension declared in a {\em qb:DataStructureDefinition} must have a declared {\em rdfs:range}.  
-\end{itemize}
+{\em IC-4}, {\em IC-5}, {\em IC-10}, {\em IC-11}
+%\begin{itemize}
+	%\item {\em IC-4:} Every dimension declared in a {\em qb:DataStructureDefinition} must have a declared {\em rdfs:range}. 
+	%\item {\em IC-5:} Every dimension with range {\em skos:Concept} must have a {\em qb:codeList}. 
+	%\item {\em IC-10:} Every {\em qb:Slice} must have a value for every dimension declared in its {\em qb:sliceStructure}. 
+	%\item {\em IC-11:} All dimensions required - Every {\em qb:Observation} has a value for each dimension declared in its associated {\em qb:DataStructureDefinition}.
+%\end{itemize}
 
 \textbf{Qualified Cardinality Restrictions.}
+{\em IC-1}, {\em IC-2}, {\em IC-3}, {\em IC-6}, {\em IC-7}, {\em IC-9} 
+%\begin{itemize}
+	%\item {\em IC-1:} Every {\em qb:Observation} has exactly one associated {\em qb:DataSet}. 
+	%\item {\em IC-2:} Every {\em qb:DataSet} has exactly one associated {\em qb:DataStructureDefinition}. 
+	%\item {\em IC-3:} Every {\em qb:DataStructureDefinition} must include at least one declared measure. 
+	%\item {\em IC-6:} The only components of a {\em qb:DataStructureDefinition} that may be marked as optional, using {\em qb:componentRequired} are attributes. 
+	%\item {\em IC-7:} Every {\em qb:SliceKey} must be associated with a {\em qb:DataStructureDefinition}. 
+	%\item {\em IC-9:} Each {\em qb:Slice} must have exactly one associated {\em qb:sliceStructure}. 
+%\end{itemize}
+
+\textbf{Duplicate Detection.}
+{\em IC-12}
+%\begin{itemize}
+	%\item {\em IC-12:} No duplicate observations - No two {\em qb:Observations} in the same {\em qb:DataSet} may have the same value for all dimensions. 
+%\end{itemize}
+
+\textbf{Membership in Controlled Vocabularies.}
+\textcolor{red}{{\em IC-19}}
+
+\textbf{SKOS Hierarchies.}
+{\em IC-20}, {\em IC-21}
+
+%\textbf{Mandatory Properties.}
+
+%\textbf{Optional Properties.}
+
 \begin{itemize}
-	\item {\em IC-1:} Every {\em qb:Observation} has exactly one associated {\em qb:DataSet}. 
-	\item {\em IC-2:} Every {\em qb:DataSet} has exactly one associated {\em qb:DataStructureDefinition}. 
-	\item {\em IC-3:} Every {\em qb:DataStructureDefinition} must include at least one declared measure. 
+	\item \textcolor{blue}{are there further constraints which can be described in this paper?}
 \end{itemize}
-
-\textcolor{blue}{are there further constraints which can be described in this paper?}
 
@@
 \subsection{PHDD}
+
+\subsection{DCAT}
+
+\section{DDI 4 Validation}
 
@@
 	\item \textcolor{blue}{is there an implementation available yet? If not I implement it in our validation environment}
+	\item \textcolor{blue}{example QB data set / we could use the one from the QB spec}
+\end{itemize}
+
+\section{Evaluation}
+
+\begin{itemize}
+	\item validate constraints on complex example data set
 \end{itemize}
@@
 
+\textbf{DCAT.}
+\textcolor{blue}{are there already constraints defined for DCAT?}
+
 \section{Conclusion and Future Work}

### 2015-01-11 paper/paper6/paper6.tex
disco constraints

@@
 
-\title{RDF Validation of \\ Metadata on Highly-Complex Person-Level Data Sets}
+\title{Modeling and Validation of Metadata on \\ Highly-Complex Person-Level Data Sets in RDF}
 
@@
 \begin{itemize}
+  \item why do we need these newly defined vocabularies?
 	\item Why do we need RDF Validation?
@@
 \begin{itemize}
+  \item We show how to model highly complex person-level data sets in RDF using different vocabularies 
   \item We define constraints on Disco, Data Cube, PHDD, DCAT, XKOS data sets
@@
 
+Constraint types marked with an asterisk can be used as an OWL 2 axiom.
+Thus, reasoners may be used to infer implicit triples resolving constraint violations causing when these constraints are validated.
+\textcolor{blue}{example}
+
 \subsection{Data Model Consistency}
@@
 
-{\em DISCO-C-XX}. 
-A {\em disco:Questionnaire} has at least 1 {\em disco:question} relationship to {\em disco:Question}.
+\textbf{{\em DISCO-C-XX}}.
+A {\em disco:Questionnaire} has at least 1 {\em disco:question} relationship to {\em disco:Question}\footnote{When mapped to DL, we do not state namespace prefixes for simplicity reasons}.
 
@@
 
-{\em DISCO-C-XX}. 
+\textbf{{\em DISCO-C-XX}}. 
 A {\em disco:Question} has exactly 1 {\em disco:universe} relationship to {\em disco:Universe}.
@@
 
-\subsection{Universal Quantifications}
+\subsection{Universal Quantifications*}
 
-{\em DISCO-C-XX}. 
+\footnote{R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}
+
+\textbf{{\em DISCO-C-XX}}.
 Only {\em disco:LogicalDataSet}s can have {\em disco:aggregation} relationships to {\em qb:DataSet}s.
@@
 
-{\em DISCO-C-XX}. 
+An existential class expression ({\em existential restriction} in DL terminology) contains all those individuals that are connected by the property P to an individual x that is an instance of the class C or to literals that are in the data range DR\footnote{R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}.
+
+\textbf{{\em DISCO-C-XX}}. 
 There must be at least 1 {\em disco:universe} relationship from {\em disco:Studies} or {\em disco:StudyGroups} to {\em disco:Universe}.
@@
 Study $\sqcup$ StudyGroup $\sqsubseteq$ $\exists$ universe.Universe \\
+\end{DL}
+
+\subsection{Disjunction}
+
+\textbf{{\em DISCO-C-XX}}. 
+Only {\em disco:Variable}s or {\em disco:Question}s or {\em disco:RepresentedVariable}s can have {\em disco:concept} relationships to {\em skos:Concept}s.
+
+\begin{DL}
+Variable $\sqcup$ Question $\sqcup$ RepresentedVariable \\
+$\sqsubseteq$ $\forall$ concept.Concept \\
+\end{DL}
+
+\subsection{Property Domains*}
+
+{\em Property Domain} constraints are defined for each Disco object and data property.
+
+\textbf{{\em DISCO-C-XX}}. 
+Only {\em disco:Question}s can have {\em disco:responseDomain} relationships.
+
+\begin{DL}
+$\exists$ responseDomain.$\top$ $\sqsubseteq$ Question 
+\end{DL}
+
+\subsection{Property Ranges*}
+
+\textbf{{\em DISCO-C-XX}}. 
+{\em disco:caseQuantity} relationships can only point to literals of the datatype {\em xsd:nonNegativeInteger}.
+
+\begin{DL}
+$\top$ $\sqsubseteq$ $\forall$ caseQuantity.nonNegativeInteger \\
+\end{DL}
+
+\subsection{Class-Specific Property Ranges}
+
+\textbf{{\em DISCO-C-XX}}. 
+Only {\em disco:Question}s can have {\em disco:questionText} relationships to literals of the datatype {\em rdf:langString}.
+
+\begin{DL}
+$\neg$Question $\sqsubseteq$ $\neg\exists$ questionText.langString
+\end{DL}
+
+\subsection{Subsumption*}
+
+\textbf{{\em DISCO-C-XX}}. 
+All {\em disco:Universe}s must also be {\em skos:Concept}s.
+
+\begin{DL}
+Universe $\sqsubseteq$ Concept
+\end{DL}
+
+\subsection{Class Equivalence*}
+
+\textbf{{\em DISCO-C-XX}}. 
+All {\em sio:SIO\_000367}s must also be {\em disco:Variable}s.
+
+\begin{DL}
+Variable $\equiv$ SIO\_000367
+\end{DL}
+
+The Semanticscience Integrated Ontology (SIO)\footnote{https://code.google.com/p/semanticscience/wiki/SIO} provides a simple, integrated ontology of types and relations for rich description of objects, processes and their attributes.
+{\em sio:SIO\_000367} is a variable defined as a value that may change within the scope of a given problem or set of operations.
+Thus, {\em sio:SIO\_000367} is equivalent to {\em disco:Variable}.
+
+\subsection{Sub Properties*}
+
+{\em Sub Properties} state that the property P1 is a sub property of the property P2 - that is, if an individual x is connected by P1 to an individual or a literal y, then x is also connected by P2 to y.
+
+\textbf{{\em DISCO-C-XX}}. 
+If an individual x is connected by {\em disco:fundedBy} to an individual y, then x is also connected by {\em dcterms:contributor} to y.
+
+\begin{DL}
+fundedBy $\sqsubseteq$ contributor 
+\end{DL}
+
+\subsection{Disjoint Classes}
+
+{\em Disjoint Classes} state that all of the classes are pairwise disjoint; 
+that is, no individual can be at the same time an instance of these disjoint classes\footnote{R-7-DISJOINT-CLASSES}.
+\textbf{{\em DISCO-DISJOINT-CLASSES-01}}.All Disco classes are defined to be pairwise disjoint.
+The following DL statements holds for each pair of Disco classes:
+
+\begin{DL}
+Study $\sqcap$ Variable $\sqsubseteq$ $\perp$\\
 \end{DL}
@@
 	\item validate constraints on complex example data set
+	\item count Disco, QB, PHDD, XKOS, DCAT constraints by constraint groups 
 \end{itemize}

### 2015-01-11 paper/paper6/paper6.tex
disco constraints

@@
 
+Where appropriate constraint types are related to complementary requirements of the RDF validation requirements database.
+
+We state one Disco constraint for each constraint type.
+
 Constraint types marked with an asterisk can be used as an OWL 2 axiom.
@@
 
+A minimum cardinality restrictions contains all those individuals that are connected by a property to at least n different individuals/literals 
+that are instances of a particular class or data range. If the class is missing, it is taken to be owl:Thing. 
+If the data range is missing, it is taken to be rdfs:Literal.
+$\geq n R. C$ is a minimum qualified cardinality restriction where $n \in \mathbb{N}$\footnote{{\em R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES} and {\em R-211-CARDINALITY-CONSTRAINTS}}.
+
 \textbf{{\em DISCO-C-XX}}.
@@
 \subsection{Exact Qualified Cardinality Restrictions}
+
+An exact cardinality restriction contains all those individuals that are connected by a property to exactly n different individuals that are instances of a particular class or data range. 
+If the class is missing, it is taken to be owl:Thing. 
+If the data range is not present, it is taken to be rdfs:Literal.
+$\geq n R.
+C \sqcap \leq n R.
+C $ is an exact qualified cardinality restriction where $n \in \mathbb{N}$\footnote{{\em R-74-EXACT-QUALIFIED-CARDINALITY-ON-PROPERTIES} and {\em R-211-CARDINALITY-CONSTRAINTS}.}.
 
@@
 
-\footnote{R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}
+A universal class expression ({\em value restriction} in DL) contains all those individuals that are connected by an object property only to individuals that are instances of a particular class\footnote{{\em R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}}.
 
@@
 
-An existential class expression ({\em existential restriction} in DL terminology) contains all those individuals that are connected by the property P to an individual x that is an instance of the class C or to literals that are in the data range DR\footnote{R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}.
+An existential class expression ({\em existential restriction} in DL terminology) contains all those individuals that are connected by the property P to an individual x that is an instance of the class C or to literals that are in the data range DR\footnote{{\em R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}}.
 
@@
 \subsection{Disjunction}
+
+A union class expression contains all individuals that are instances of at least one class $C_{i}$ for 1 $\leq$ i $\leq$ n. 
+A union data range contains all tuples of literals that are contained in the at least one data range $DR_{i}$ for 1 $\leq$ i $\leq$ n.
+Synonyms of {\em disjunction} are {\em union} and {\em inclusive or}\footnote{{\em R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS} and {\em R-18-DISJUNCTION-OF-DATA-RANGES}}.
 
@@
 
+{\em Property Domains} ({\em domain restrictions on roles} in DL) restricts the domain of object and data properties.
+The purpose is to declare that a given property is associated with a class. 
+In OO terms this is the declaration of a member, field, attribute or association. 
+$\exists R.
+\top \sqsubseteq C$ is the object property restriction where $R$ is the object property (role) whose domain is restricted to concept $C$\footnote{{\em R-25-OBJECT-PROPERTY-DOMAIN} and {\em R-26-DATA-PROPERTY-DOMAIN}}.
 {\em Property Domain} constraints are defined for each Disco object and data property.
@@
 
+{\em Property Range} ({\em range restrictions on roles} in DL) restricts the range of object and data properties.
+$\top \sqsubseteq \forall R . C$ is the range restriction to the object property $R$ (restricted by the concept $C$)\footnote{{\em R-28-OBJECT-PROPERTY-RANGE} and {\em R-35-DATA-PROPERTY-RANGE}}.
+
 \textbf{{\em DISCO-C-XX}}. 
@@
 \subsection{Class-Specific Property Ranges}
+
+{\em Class-Specific Property Range} restricts the range of object and data properties for individuals within a specific context (e.g. class, shape, application profile).
+The values of each member property of a class may be limited by their value type, such as xsd:string or foaf:Person\footnote{{\em R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS} and {\em R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS}}.
 
@@
 
+A subclass axiom ({\em concept inclusion} in DL) states that the class C1 is a subclass of the class C2 - C1 is more specific than C2\footnote{{\em R-100-SUBSUMPTION}}.
+
 \textbf{{\em DISCO-C-XX}}. 
@@
 \subsection{Class Equivalence*}
+
+{\em Class Equivalence} asserts that two concepts have the same instances.
+While synonyms are an obvious example of equivalent concepts, in practice one more
+often uses concept equivalence to give a name to complex expressions \cite{Kroetzsch2012}.
+Concept equivalence is indeed subsumption from left and right ($A \sqsubseteq B$ and $B \sqsubseteq A$ implies $A \equiv B$)\footnote{{\em R-3-EQUIVALENT-CLASSES}}.
 
@@
 {\em Disjoint Classes} state that all of the classes are pairwise disjoint; 
-that is, no individual can be at the same time an instance of these disjoint classes\footnote{R-7-DISJOINT-CLASSES}.
-\textbf{{\em DISCO-DISJOINT-CLASSES-01}}.All Disco classes are defined to be pairwise disjoint.
+that is, no individual can be at the same time an instance of these disjoint classes\footnote{{\em R-7-DISJOINT-CLASSES}}.
+\textbf{{\em DISCO-C-01}}. All Disco classes are defined to be pairwise disjoint.
 The following DL statements holds for each pair of Disco classes:
@@
 Study $\sqcap$ Variable $\sqsubseteq$ $\perp$\\
+\end{DL}
+
+\subsection{Asymmetric Object Properties}
+
+A property is asymmetric if it is disjoint from its own inverse \cite{Kroetzsch2012}.
+An object property asymmetry axiom states that the object property OP is asymmetric - that is, if an individual x is connected by OP to an individual y, then y cannot be connected by OP to x\footnote{{\em R-62-ASYMMETRIC-OBJECT-PROPERTIES}}.
+
+\textbf{{\em DISCO-C-01}}. 
+A {\em disco:Variable} may be based on a {\em disco:RepresentedVariable}.
+A {\em disco:RepresentedVariable}, however, cannot be based on a {\em disco:Variable}.
+This is a kind of mistake may occur as a semantically equivalent object property for the other direction may also be possible ({\em disco:basisOf}).
+
+\begin{DL}
+$basedOn \sqcap basedOn^{-} \sqsubseteq \bot$ 
+\end{DL}
+
+\subsection{Class-Specific Irreflexive Object Properties}
+
+A property is irreflexive if it is never locally reflexive \cite{Kroetzsch2012}.
+An object property irreflexivity axiom states that the object property OP is irreflexive - that is, no individual is connected by OP to itself.
+
+\textbf{{\em DISCO-C-XX}}.
+Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:boader} to themselves.
+
+\begin{DL}
+Concept $\sqsubseteq$ $\neg$$\exists$ broader.Self. 
+\end{DL}
+
+\textbf{{\em DISCO-C-XX}}.
+Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:narrower} to themselves.
+
+\begin{DL}
+Concept $\sqsubseteq$ $\neg$$\exists$ narrower.Self. 
+\end{DL}
+
+\subsection{Context-Specific Exclusive OR of Property Groups}
+
+{\em Context-Specific Exclusive OR of Property Groups} corresponds to the requirement:
+{\em R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC}.
+Exclusive or is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
+Only one of multiple property groups leads to valid data.
+
+\textbf{{\em DISCO-C-XX}}.
+Within the context of Disco, skos:Concepts can have either skos:definition (when interpreted as DDI concepts) or skos:notation and skos:prefLabel properties (when interpreted as DDI codes and categories), but not both.
+
+\begin{DL}
+Human $\sqsubseteq$ ($\neg$ E $\sqcap$ F) $\sqcup$ (E $\sqcap$ $\neg$ F) \\ 
+E $\equiv$ A $\sqcap$ B \\
+F $\equiv$ C $\sqcap$ D \\
+A $\sqsubseteq$ $\geq$ 1 name . string $\sqcap$ $\leq$ 1 name . string \\
+B $\sqsubseteq$ $\geq$ 1 givenName . string $\sqcap$ $\leq$ 1 givenName . string \\
+C $\sqsubseteq$ $\geq$ 1 mbox . IRI $\sqcap$ $\leq$ 1 mbox . IRI \\
+D $\sqsubseteq$ $\geq$ 1 homepage . Document $\sqcap$ $\leq$ 1 homepage . Document \\
 \end{DL}

### 2015-01-11 paper/paper6/paper6.tex
disco constraints

@@
 \newcommand{\jw}[1]{\todo[size=\small, color=blue!40]{\textbf{Achim:} #1}}
+
+% examples
+\usepackage{fancyvrb}
+\DefineVerbatimEnvironment{ex}{Verbatim}{numbers=left,numbersep=2mm,frame=single,fontsize=\scriptsize}
 
@@
 
-{\em Context-Specific Exclusive OR of Property Groups} corresponds to the requirement:
-{\em R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC}.
 Exclusive or is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
-Only one of multiple property groups leads to valid data.
+Only one of multiple property groups leads to valid data\footnote{{\em R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC}}.
 
@@
 \begin{DL}
-Human $\sqsubseteq$ ($\neg$ E $\sqcap$ F) $\sqcup$ (E $\sqcap$ $\neg$ F) \\ 
-E $\equiv$ A $\sqcap$ B \\
-F $\equiv$ C $\sqcap$ D \\
-A $\sqsubseteq$ $\geq$ 1 name . string $\sqcap$ $\leq$ 1 name . string \\
-B $\sqsubseteq$ $\geq$ 1 givenName . string $\sqcap$ $\leq$ 1 givenName . string \\
-C $\sqsubseteq$ $\geq$ 1 mbox . IRI $\sqcap$ $\leq$ 1 mbox . IRI \\
-D $\sqsubseteq$ $\geq$ 1 homepage . Document $\sqcap$ $\leq$ 1 homepage . Document \\
+Concept $\sqsubseteq$ ($\neg$ D $\sqcap$ C) $\sqcup$ (D $\sqcap$ $\neg$ C) \\ 
+D $\equiv$ A $\sqcap$ B \\
+A $\sqsubseteq$ $\geq$ 1 notation.string $\sqcap$ $\leq$ 1 notation.string \\
+B $\sqsubseteq$ $\geq$ 1 prefLabel.string $\sqcap$ $\leq$ 1 prefLabel.string \\
+C $\sqsubseteq$ $\geq$ 1 definition.string $\sqcap$ $\leq$ 1 definition.string \\
 \end{DL}
 
-\subsection{SKOS-Related Constraints}
+\section{Allowed Values}
 
-\subsubsection{Membership in Controlled Vocabularies.}
+It is a common requirement to narrow down the value space of a property by an exhaustive enumeration of the valid values (both literals or resource). 
+This is often rendered in drop down boxes or radio buttons in user interfaces. 
+Allowed values for properties can be IRIs, IRIs (matching one or multiple patterns), (any) literals, literals of a list of allowed literals (e.g.
+'red' 'blue' 'green'), typed literals one or multiple type(s) (e.g.
+xsd:string)\footnote{{\em R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS} and
+{\em R-37-ALLOWED-VALUES-FOR-RDF-LITERALS}}.
 
-Questions, variables, and represented variables may have representations.
+\textbf{{\em DISCO-C-XX}}.
+{\em disco:CategoryStatistics} can only have {\em disco:computationBase} relationships to the values 'valid' and 'invalid' of the datatype {\em rdf:langString}.
 
-\subsubsection{Hierarchies}
+\begin{DL}
+CategoryStatistics $\equiv$ \\ $\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString \\
+\end{DL}
+
+\subsection{Membership in Controlled Vocabularies.}
+
+Resources can only be members of listed controlled vocabularies\footnote{{\em R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES} and
+{\em R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES}}.
+
+\textbf{{\em DISCO-C-XX}}.
+{\em disco:SummaryStatistics} can only have {\em disco:summaryStatisticType} relationships to {\em skos:Concept}s which must be members of the controlled vocabulary {\em ddicv:SummaryStatisticType} which is a {\em skos:ConceptScheme}.
+
+\begin{DL}
+SummaryStatistics $\sqsubseteq$ \\
+$\forall summaryStatisticType.Concept \sqcap \forall inScheme . A$ \\
+$A \equiv ConceptScheme \sqcap \{SummaryStatisticType\}$
+\end{DL}
+
+\subsection{Literal Value Comparison}
+
+Depending on the property semantics,
+there are cases where two different literal values must have
+a specific ordering with respect to an operator. 
+P1 and P2 are the datatype properties we need to compare and 
+OP is the comparison operator (\textless, \textless=, \textgreater, \textgreater=, =, !=)\footnote{{\em R-43-LITERAL-VALUE-COMPARISON}}.
+The {\em COMP Pattern}, one of the Data Quality Test Pattern, can be used to validate the {\em Literal Value Comparison} constraint \cite{Kontokostas2014}:
+
+\begin{ex}
+SELECT ?s WHERE { 
+    ?s %%P1%% ?v1 .
+    ?s %%P2%% ?v2 .
+    FILTER ( ?v1 %%OP%% ?v2 ) }
+\end{ex}
+
+\textbf{{\em DISCO-C-XX}}.
+{\em disco:startDate}s must be before (‘\textless’) the {\em disco:endDate}s.
+To validate this constraint we bind the variables as follows (P1: {\em disco:startDate}, P2: {\em disco:endDate}, OP: \textless).
+
+\subsection{Hierarchies}
 

### 2015-01-12 paper/RDF validation requirements/RDF validation requirements.tex
paper ideas
disco constraints
incorporate feedback

--- 2015-01-09 paper/RDF validation requirements/RDF validation requirements.tex
@@
 
-\tb{why is the references section not shown? / references are not resolved}
-
 The purpose of ontologies is to perform reasoning on RDF data and not to validate RDF data conforming to these ontologies.
@@
 \ms{R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}.
-In DL terminology the \ms{existential quantification} is alco called \ms{existential restriction}.
+In DL terminology the \ms{existential quantification} is also called \ms{existential restriction}.
 An existential class expression consists of a property expression and a class expression or a data range, and it contains all those individuals that are connected by the property expression to an individual that is an instance of the class expression or to literals that are in the data range.
@@
 \begin{DL}
-$\forall$ parentOf . Female
+$\forall$ parentOf.Female
 \end{DL}
@@
 For qualified cardinality restrictions, classes respective data ranges are stated.
-$\leq n R. C$ is a minimum qualified cardinality restriction where $n \in \mathbb{N}$.
+$\geq n R. C$ is a minimum qualified cardinality restriction where $n \in \mathbb{N}$.
 
@@
 \begin{ex}
-# DSCL (DQTP):
+# DQTP:
 SELECT ?s WHERE { 
@@
 \ms{R-45-RANGES-OF-RDF-LITERAL-} \ms{VALUES}.
+P1 is a data property (of an instance of class C1) and its literal value must be between the range of [$V_{min}$,$V_{max}$].
 
@@
 \ms{R-72-RECOMMENDED-PROPERTIES}.
+Which properties are not required but recommended within a particular context.
 

### 2015-01-12 paper/paper6/paper6.tex
incorporate feedback

@@
 
+\textcolor{blue}{multiple validation levels}
+
 Where appropriate constraint types are related to complementary requirements of the RDF validation requirements database.
@@
 $\geq n R. C$ is a minimum qualified cardinality restriction where $n \in \mathbb{N}$\footnote{{\em R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES} and {\em R-211-CARDINALITY-CONSTRAINTS}}.
-
-\textbf{{\em DISCO-C-XX}}.
+\textbf{{\em DISCO-C-XX:}}
 A {\em disco:Questionnaire} has at least 1 {\em disco:question} relationship to {\em disco:Question}\footnote{When mapped to DL, we do not state namespace prefixes for simplicity reasons}.
@@
 C $ is an exact qualified cardinality restriction where $n \in \mathbb{N}$\footnote{{\em R-74-EXACT-QUALIFIED-CARDINALITY-ON-PROPERTIES} and {\em R-211-CARDINALITY-CONSTRAINTS}.}.
-
-\textbf{{\em DISCO-C-XX}}. 
+\textbf{{\em DISCO-C-XX:}}
 A {\em disco:Question} has exactly 1 {\em disco:universe} relationship to {\em disco:Universe}.
@@
 A universal class expression ({\em value restriction} in DL) contains all those individuals that are connected by an object property only to individuals that are instances of a particular class\footnote{{\em R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}}.
-
-\textbf{{\em DISCO-C-XX}}.
+\textbf{{\em DISCO-C-XX:}}
 Only {\em disco:LogicalDataSet}s can have {\em disco:aggregation} relationships to {\em qb:DataSet}s.
@@
 An existential class expression ({\em existential restriction} in DL terminology) contains all those individuals that are connected by the property P to an individual x that is an instance of the class C or to literals that are in the data range DR\footnote{{\em R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}}.
-
-\textbf{{\em DISCO-C-XX}}. 
+\textbf{{\em DISCO-C-XX:}} 
 There must be at least 1 {\em disco:universe} relationship from {\em disco:Studies} or {\em disco:StudyGroups} to {\em disco:Universe}.
@@
 Synonyms of {\em disjunction} are {\em union} and {\em inclusive or}\footnote{{\em R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS} and {\em R-18-DISJUNCTION-OF-DATA-RANGES}}.
-
-\textbf{{\em DISCO-C-XX}}. 
+\textbf{{\em DISCO-C-XX:}} 
 Only {\em disco:Variable}s or {\em disco:Question}s or {\em disco:RepresentedVariable}s can have {\em disco:concept} relationships to {\em skos:Concept}s.
@@
 {\em Property Domain} constraints are defined for each Disco object and data property.
-
-\textbf{{\em DISCO-C-XX}}. 
+\textbf{{\em DISCO-C-XX:}} 
 Only {\em disco:Question}s can have {\em disco:responseDomain} relationships.
@@
 $\top \sqsubseteq \forall R . C$ is the range restriction to the object property $R$ (restricted by the concept $C$)\footnote{{\em R-28-OBJECT-PROPERTY-RANGE} and {\em R-35-DATA-PROPERTY-RANGE}}. 
-
-\textbf{{\em DISCO-C-XX}}. 
+\textbf{{\em DISCO-C-XX:}} 
 {\em disco:caseQuantity} relationships can only point to literals of the datatype {\em xsd:nonNegativeInteger}.
@@
 The values of each member property of a class may be limited by their value type, such as xsd:string or foaf:Person\footnote{{\em R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS} and {\em R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS}}.
-
-\textbf{{\em DISCO-C-XX}}. 
+\textbf{{\em DISCO-C-XX:}} 
 Only {\em disco:Question}s can have {\em disco:questionText} relationships to literals of the datatype {\em rdf:langString}.
@@
 A subclass axiom ({\em concept inclusion} in DL) states that the class C1 is a subclass of the class C2 - C1 is more specific than C2\footnote{{\em R-100-SUBSUMPTION}}.
-
-\textbf{{\em DISCO-C-XX}}. 
+\textbf{{\em DISCO-C-XX:}} 
 All {\em disco:Universe}s must also be {\em skos:Concept}s.
@@
 Concept equivalence is indeed subsumption from left and right ($A \sqsubseteq B$ and $B \sqsubseteq A$ implies $A \equiv B$)\footnote{{\em R-3-EQUIVALENT-CLASSES}}.
-
-\textbf{{\em DISCO-C-XX}}. 
+\textbf{{\em DISCO-C-XX:}}
 All {\em sio:SIO\_000367}s must also be {\em disco:Variable}s.
@@
 {\em Sub Properties} state that the property P1 is a sub property of the property P2 - that is, if an individual x is connected by P1 to an individual or a literal y, then x is also connected by P2 to y.
-
-\textbf{{\em DISCO-C-XX}}. 
+\textbf{{\em DISCO-C-XX:}}
 If an individual x is connected by {\em disco:fundedBy} to an individual y, then x is also connected by {\em dcterms:contributor} to y.
@@
 that is, no individual can be at the same time an instance of these disjoint classes\footnote{{\em R-7-DISJOINT-CLASSES}}.
-\textbf{{\em DISCO-C-01}}. All Disco classes are defined to be pairwise disjoint.
+\textbf{{\em DISCO-C-XX:}} 
+All Disco classes are defined to be pairwise disjoint.
 The following DL statements holds for each pair of Disco classes:
@@
 An object property asymmetry axiom states that the object property OP is asymmetric - that is, if an individual x is connected by OP to an individual y, then y cannot be connected by OP to x\footnote{{\em R-62-ASYMMETRIC-OBJECT-PROPERTIES}}.
-
-\textbf{{\em DISCO-C-01}}. 
+\textbf{{\em DISCO-C-XX:}} 
 A {\em disco:Variable} may be based on a {\em disco:RepresentedVariable}.
@@
 An object property irreflexivity axiom states that the object property OP is irreflexive - that is, no individual is connected by OP to itself. 
+\textbf{{\em DISCO-C-XX:}}
+Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:boader} to themselves (DL: Concept $\sqsubseteq$ $\neg$$\exists$ broader.Self).
 
-\textbf{{\em DISCO-C-XX}}.
-Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:boader} to themselves.
-
-\begin{DL}
-Concept $\sqsubseteq$ $\neg$$\exists$ broader.Self. 
-\end{DL}
-
-\textbf{{\em DISCO-C-XX}}.
+\textbf{{\em DISCO-C-XX:}}
 Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:narrower} to themselves.
@@
 Only one of multiple property groups leads to valid data\footnote{{\em R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC}}.
-
-\textbf{{\em DISCO-C-XX}}.
+\textbf{{\em DISCO-C-XX:}}
 Within the context of Disco, skos:Concepts can have either skos:definition (when interpreted as DDI concepts) or skos:notation and skos:prefLabel properties (when interpreted as DDI codes and categories), but not both.
@@
 
-\section{Allowed Values}
+\subsection{Allowed Values}
 
@@
 To validate this constraint we bind the variables as follows (P1: {\em disco:startDate}, P2: {\em disco:endDate}, OP: \textless).
+
+\subsection{Literal Ranges}
+
+P1 is a data property (of an instance of class C1) and its literal value must be between the range of [$V_{min}$,$V_{max}$].
+\textbf{{\em DISCO-C-XX:}}
+{\em disco:percentage} (domain: {\em disco:CategoryStatistics}) literals must be of the datatype {\em xsd:double} whose range should be restricted to be between 0 and 100 (not expressible in DL)\footnote{{\em R-45-RANGES-OF-RDF-LITERAL-VALUES}}.
+
+\subsection{Mathematical Operations}
+
+Examples for {\em Mathematical Operations} are the addition of two dates, the addition of days to a start date, and statistical computations (e.g. average, mean, sum).
+\textbf{{\em DISCO-C-XX:}}
+The sum of {\em disco:percentage} {\em xsd:double} values of all codes (represented as {\em skos:Concept}s) of a code list ({\em skos:ConceptScheme} or {\em skos:OrderedCollection}), serving as representation of a particular {\em disco:Variable}, must exactly be 100
+(not expressible in DL)\footnote{{\em R-42-MATHEMATICAL-OPERATIONS} and {\em R-41-STATISTICAL-COMPUTATIONS}}.
+
+\subsection{Default Values}
+
+Default values for objects and literals are inferred automatically.
+It should be possible to declare the default value for a given property, e.g.
+so that input forms can be pre-populated and to insert a required property that is missing in a web service call\footnote{{\em R-31-DEFAULT-VALUES-OF-RDF-OBJECTS} and {\em R-38-DEFAULT-VALUES-OF-RDF-LITERALS}}.
+\textbf{{\em DISCO-C-XX:}}
+The value 'true' for the property {\em disco:isPublic} ({\em xsd:boolean}) indicates that the data set ({\em disco:LogicalDataSet}) can be accessed (usually downloaded) by anyone.
+Per default, access to data sets should be restricted ('false').
+
+\subsection{Language Tag Matching}
+
+For particular data properties, values must be stated for predefined languages (not expressible in DL)\footnote{{\em R-47-LANGUAGE-TAG-MATCHING}}.
+\textbf{{\em DISCO-C-XX:}}
+There must be an English variable name ({\em skos:notation}) for each {\em disco:Variable} within {\em disco:LogicalDataSet}s.
+
+\subsection{Language Tag Cardinality}
+
+For particular data properties, values of predefined languages must be stated for determined number of times (not expressible in DL)
+\footnote{{\em R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG} and {\em R-48-MISSING-LANGUAGE-TAGS}}.
+\textbf{{\em DISCO-C-XX:}}
+There must be at least one English {\em disco:questionText} for each {\em disco:Question} within {\em disco:LogicalDataSet}s.
+\textbf{{\em DISCO-C-XX:}}
+There should be at most one English literal value for variable names ({\em skos:notation}, domain: {\em disco:Variable}).
+
+\subsection{Conditional Properties}
+
+If specific properties exist, then specific other properties also have to be present\footnote{{\em R-71-CONDITIONAL-PROPERTIES}}.
+\textbf{{\em DISCO-C-XX:}}
+If a {\em skos:Concept represents a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
+then the property {\em disco:isValid} has to be stated indicating if the code is valid ('true') or missing ('false').
+
+\subsection{Recommended Properties}
+
+Which properties are not required but recommended within a particular context\footnote{{\em R-72-RECOMMENDED-PROPERTIES}}.
+\textbf{{\em DISCO-C-XX:}}
+The property ({\em skos:notation} is not mandatory for {\em disco:Variable}s, but recommended to indicate variable names.
+
+\subsection{Value is Valid for Datatype}
+
+Make sure that a value is valid for its datatype.
+It has to be ensured, e.g., that a date is really a date, or that a xsd:nonNegativeInteger value is not negative. 
+\textbf{{\em DISCO-C-XX:}}
+Check if literal values of the property {\em disco:startDate} are really of the datatype {\em xsd:date}(not expressible in DL).
+
+\subsection{Equivalent Properties}
+
+\subsection{Functional Properties}
+
+\subsection{Data Property Facets}
+
+xsd:length of disco:purpose
 

### 2015-01-13 paper/RDF validation requirements/RDF validation requirements.tex
minor
small touch.
authors
abstract

@@
 %
-\author{Thomas Bosch\inst{1} \and Andreas Nolle\inst{2} \and Erman Acar\inst{3}}
+\author{Thomas Bosch\inst{1} \and Andreas Nolle\inst{2} \and Erman Acar\inst{3} \and Kai Eckert \inst{3}}
 %
@@
 University of Mannheim, Germany \\
-\email{\{christian,erman,kai\}@informatik.uni-mannheim.de} 
-}
+\email{\{erman, kai\}@informatik.uni-mannheim.de}}
 
@@
 Although, there are multiple constraint languages which can be used to formulate RDF constraints (associated with these requirements), 
-there is no standard way to formulate RDF constraints.
-
-This paper serves to evaluate to which extend each requirement is satisfied by each of these constraining languages.
-We take reasoning into account as a pre-validation step and distinguish between OWL 2 QL and OWL 2 DL constructs to express particular constraints.
-We classify constraints according to a developed classification mechanism for constraints.
-We show that each constraint can be mapped to an ontology describing RDF constraints generically.
-If a constraint can be expressed in DL, we add the mapping to DL and to the generic constraint in order to logically underpin associated requirements.
-If a constraint cannot be expressed in DL, we only add the mapping to the generic constraint.
+there is no standard way to formulate them.
+This paper serves to evaluate to which extend each requirement is satisfied by each of these constraint languages.
+We take reasoning into account as an important pre-validation step and map constraints to DL
+%, and distinguish between OWL 2 QL and OWL 2 DL constructs to express particular constraints.
+%We classify constraints according to a developed classification mechanism for constraints.
+in order to show that each constraint can be mapped to an ontology describing RDF constraints generically.
+%If a constraint can be expressed in DL, we add the mapping to DL and to the generic constraint in order to logically underpin associated requirements.
+%If a constraint cannot be expressed in DL, we only add the mapping to the generic constraint.
 

### 2015-01-13 paper/RDF validation requirements/RDF validation requirements.tex
abstract

@@
 There are many case studies for which the formulation of RDF constraints and the validation of RDF data conforming to these constraint is very important.  
-The W3C and the DCMI working groups on RDF validation identified many RDF validation requirements,
-whereupon we initiate an RDF validation requirements database which is available to contribute at \url{http://purl.org/net/rdf-validation}.
+By contributing to the W3C and the DCMI working groups on RDF validation, we identified many RDF validation requirements
+and initiated an RDF validation requirements database which is available to contribute at \url{http://purl.org/net/rdf-validation}.
 The intention of this database is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation.

### 2015-01-13 paper/RDF validation requirements/RDF validation requirements.tex
small touches

--- 2015-01-12 paper/RDF validation requirements/RDF validation requirements.tex
@@
 There are many case studies for which the formulation of RDF constraints and the validation of RDF data conforming to these constraint is very important.  
-The W3C and the DCMI working groups on RDF validation identified many RDF validation requirements,
-whereupon we initiate an RDF validation requirements database which is available to contribute at \url{http://purl.org/net/rdf-validation}.
-The intention of this database is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation.
+The W3C and the DCMI working groups on RDF validation identified many RDF validation requirements.
+To collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation, we initiated a publicly open database of RDF validation requirements  (\url{http://purl.org/net/rdf-validation}).
+The intention of this database .
 Although, there are multiple constraint languages which can be used to formulate RDF constraints (associated with these requirements), 
@@
 
-This paper serves to evaluate to which extend each requirement is satisfied by each of these constraining languages.
+This paper serves to evaluate to which extend each requirement is satisfied by each of these constrain languages.
 We take reasoning into account as a pre-validation step and distinguish between OWL 2 QL and OWL 2 DL constructs to express particular constraints.
@@
 
-The purpose of ontologies is to perform reasoning on RDF data and not to validate RDF data conforming to these ontologies.
-For RDF, we cannot use ontologies like we use XML Schemas, DTDs, RELAX NG, or Schematron to validate XML documents.
 The W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 

### 2015-01-13 paper/RDF validation requirements/RDF validation requirements.tex

--- 2015-01-13 paper/RDF validation requirements/RDF validation requirements.tex
@@
 There are many case studies for which the formulation of RDF constraints and the validation of RDF data conforming to these constraint is very important.  
-The W3C and the DCMI working groups on RDF validation identified many RDF validation requirements,
-whereupon we initiate an RDF validation requirements database which is available to contribute at \url{http://purl.org/net/rdf-validation}.
-The intention of this database is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation.
+The W3C and the DCMI working groups on RDF validation identified many RDF validation requirements.
+To collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation, we initiated a publicly open database of RDF validation requirements  (\url{http://purl.org/net/rdf-validation}).
+The intention of this database .
 Although, there are multiple constraint languages which can be used to formulate RDF constraints (associated with these requirements),
+
 there is no standard way to formulate them.

### 2015-01-13 paper/RDF validation requirements/RDF validation requirements.tex

--- 2015-01-13 paper/RDF validation requirements/RDF validation requirements.tex
@@
 There are many case studies for which the formulation of RDF constraints and the validation of RDF data conforming to these constraint is very important.
-By contributing to the W3C and the DCMI working groups on RDF validation, we identified many RDF validation requirements
+By contributing to the W3C and the DCMI working groups on RDF validation, we identified major RDF validation requirements
 and initiated an RDF validation requirements database which is available to contribute at \url{http://purl.org/net/rdf-validation}.

### 2015-01-13 paper/RDF validation requirements/RDF validation requirements.tex
abstract

@@
 There are many case studies for which the formulation of RDF constraints and the validation of RDF data conforming to these constraint is very important.
-By contributing to the W3C and the DCMI working groups on RDF validation, we identified major RDF validation requirements
+As a part of the collaboration with the W3C and the DCMI working groups on RDF validation, we identified major RDF validation requirements
 and initiated an RDF validation requirements database which is available to contribute at \url{http://purl.org/net/rdf-validation}.
-The intention of this database is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation.
+The purpose of this database is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation.
 Although, there are multiple constraint languages which can be used to formulate RDF constraints (associated with these requirements),
@@
 This paper serves to evaluate to which extend each requirement is satisfied by each of these constraint languages.
-We take reasoning into account as an important pre-validation step and map constraints to DL
+We take reasoning into account  as an important pre-validation step and therefore map constraints to DL
 %, and distinguish between OWL 2 QL and OWL 2 DL constructs to express particular constraints.

### 2015-01-13 paper/RDF validation requirements/RDF validation requirements.tex
introduction edited

@@
 
-There is no constraint language which can be seen as the standard.
-Although, there are multiple constraint languages (having different syntaxes and semantics) which can be used to express RDF constraints, such as existential and universal quantification, cardinality restrictions, and exclusive or of properties.
-The five most promising ones on being the standard are
+There is no constraint language which can be seen as the standalone standard.
+However, there are multiple constraint languages (each having its own  syntax and semantics) which can be used to express RDF constraints, such as existential and universal quantification, cardinality restrictions, and exclusive-or of properties.
+The five popular constraint languages are 
 Description Set Profiles (DSP)\footnote{\url{http://dublincore.org/documents/2008/03/31/dc-dsp/}},

### 2015-01-13 paper/RDF validation requirements/RDF validation requirements.tex
Motivation and introduction merged

@@
 
+A \ms{constraint language} is a language which is used to formulate constraints.
+The W3C Data Shapes working group defines \ms{constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
 There is no constraint language which can be seen as the standalone standard.
@@
 
-\section{Motivation}
-
 In this paper, we describe each requirement within the RDF validation requirements database in detail (sections 3-76).
@@
 In order to define an ontology to describe RDF constraints generically, it is needed to define the terminology for the formulation of RDF constraints and to classify them.
-A \ms{constraint language} is a language which is used to formulate constraints.
-The W3C Data Shapes working group defines \ms{constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
+
 We identified four dimensions to classify constraints:
@@
 \ms{Generic constraints} are expressed by the RDF-CO.
-As RDF-CO describes constraints generically, RDF-CO does not distinguish constraints according to the dimension \ms{universality}. 
+As RDF-CO describes constraints generically, it does not distinguish constraints according to the dimension \ms{universality}. 
 The majority of constraints can be expressed in DL.
-In contrast, there are constraints which cannot be expressed in DL, but are also representable by the RDF-CO. 
-\ms{Complex constraints} encompass \ms{simple constraints} (atomic constraints) and/or further complex constraints.
-DL statements representing complex constraints are created out of DL statements representing composed constraints (if expressible in DL). 
+In contrast, there are constraints which cannot be expressed in DL, but are also expressible in the RDF-CO. 
+\ms{Complex constraints} are built by combining \ms{simple constraints} or complex constraints.
+DL statements which represents complex constraints are created out of DL statements representing composed constraints (if expressible in DL). 
 Simple constraints may be applied to either properties (\ms{properties constraints}) or classes (\ms{class constraints}).

### 2015-01-16 paper/RDF validation requirements/RDF validation requirements.tex
CWA UNA

@@
 In 2014, two working groups on RDF validation have been established: 
-the W3C RDF Data Shapes WG\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles WG\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
-
-Bosch and Eckert \cite{BoschEckert2014} collected the findings of these working groups and initiated a database of requirements to formulate and validate RDF constraints
-which is available for contribution at \url{http://purl.org/net/rdf-validation}.
+the W3C RDF Data Shapes\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles working groups\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
+Bosch and Eckert \cite{BoschEckert2014} collected the findings of these working groups and initiated a database of requirements to formulate and validate RDF constraints.
+The database is available for contribution at \url{http://purl.org/net/rdf-validation}.
 The intention associated with this database is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
 The requirements are classified to better evaluate existing solutions. 
-We mapped each requirement to formulate RDF constraints directly to an RDF constraint.
+We mapped each requirement to formulate RDF constraints directly to an RDF constraint type.
 
@@
 However, there are multiple constraint languages (each having its own  syntax and semantics) which can be used to express RDF constraints, such as existential and universal quantification, cardinality restrictions, and exclusive-or of properties.
-The five popular constraint languages are 
+The five most popular constraint languages are 
 Description Set Profiles (DSP)\footnote{\url{http://dublincore.org/documents/2008/03/31/dc-dsp/}},
@@
 
-In this paper, we describe each requirement within the RDF validation requirements database in detail (sections 3-76).
+In this paper, we describe each requirement within the RDF validation requirements database in detail (sections 2-75).
 Additional descriptions can be found directly in the database.
-Each requirement corresponds to an RDF constraint which may be expressible by multiple constraint languages.
+Each requirement corresponds to an RDF constraint type which may be expressible by multiple constraint languages.
 For each requirement, we represent some examples in different constraint languages.
@@
 In order to define an ontology to describe RDF constraints generically, it is needed to define the terminology for the formulation of RDF constraints and to classify them. 
-
 We identified four dimensions to classify constraints:
@@
 We rather developed a very simple ontology (only three classes, three object properties, and three data properties) which is universal enough to describe any RDF constraint expressible by any RDF constraint language.
-We call this ontology the \ms{RDF constraints ontology (RDF-CO)}\footnote{Available at: \url{https://github.com/boschthomas/RDF-constraints-ontology}}.
+We call this ontology the \ms{RDF constraints ontology (RDF-CO)}\footnote{Available at: \url{https://github.com/boschthomas/RDF-CO}}.
 

### 2015-01-17 paper/RDF validation requirements/RDF validation requirements.tex
CWA/UNA dependency evaluation

@@
   \textbf{Constraint Classes} & \textbf{\#} & \textbf{\%} \\
+  \hline
+
+}{
+  \hline
+  \end{tabular}
+  \linebreak
+	\end{center}
+}
+
+\newenvironment{evaluation-cwa-una-dependency}{
+  \scriptsize
+  \sffamily
+  \vspace{0cm}
+	\begin{center}
+  \begin{tabular}{l|c}
+  \hline
+  \textbf{Constraint Type} & \textbf{CWA/UNA Dependent} \\
   \hline
@@
 The majority - nearly 70\% - of the overall constraints are expressible in DL.
+
+\subsection{Evaluation of CWA/UNA Dependency}
+
+\begin{evaluation-cwa-una-dependency}
+*Subsumption & $\checkmark$ \\
+*Class Equivalence & \ding{55} \\
+*Sub Properties & $\checkmark$ \\
+*Property Domain & $\checkmark$ \\ 
+*Property Range & $\checkmark$ \\ 
+*Inverse Object Properties & $\checkmark$ \\ 
+*Symmetric Object Properties & $\checkmark$ \\ 
+*Asymmetric Object Properties & $\checkmark$ \\ 
+*Reflexive Object Properties & $\checkmark$ \\ 
+*Irreflexive Object Properties & $\checkmark$ \\
+Disjoint Properties & \ding{55} \\ 
+Disjoint Classes & \ding{55} \\
+Context-Sp. Property Groups & \ding{55} \\ 
+Context-Sp. Inclusive OR of P. & \ding{55} \\
+Context-Sp. Inclusive OR of P. Groups & \ding{55} \\ 
+Recursive Queries & \ding{55} \\ 
+Individual Inequality & $\checkmark$ \\ 
+*Equivalent Properties & \ding{55} \\ 
+Property Assertions & \ding{55} \\ 
+Data Property Facets & \ding{55} \\ 
+Literal Pattern Matching & \ding{55} \\ 
+Negative Literal Pattern Matching & \ding{55} \\ 
+*Object Property Paths & $\checkmark$ \\ 
+*Intersection & $\checkmark$ \\ 
+*Disjunction & $\checkmark$ \\ 
+*Negation & $\checkmark$ \\ 
+*Existential Quantification & $\checkmark$ \\ 
+*Universal Quantification & $\checkmark$ \\ 
+*Minimum Unqualified Cardinality & $\checkmark$ \\ 
+*Minimum Qualified Cardinality & $\checkmark$ \\ 
+*Maximum Unqualified Cardinality & $\checkmark$ \\ 
+*Maximum Qualified Cardinality & $\checkmark$ \\ 
+*Exact Unqualified Cardinality & $\checkmark$ \\ 
+*Exact Qualified Cardinality & $\checkmark$ \\ 
+*Transitive Object Properties & $\checkmark$ \\ 
+Context-Sp. Exclusive OR of P. & $\checkmark$ \\ 
+Context-Sp. Exclusive OR of P. Groups & $\checkmark$ \\
+Allowed Values & $\checkmark$ \\ 
+Not Allowed Values & $\checkmark$ \\ 
+Literal Ranges & \ding{55} \\ 
+Negative Literal Ranges & \ding{55} \\ 
+Required Properties & $\checkmark$ \\ 
+Optional Properties & \ding{55} \\
+Repeatable Properties & $\checkmark$ \\ 
+Negative Property Constraints & $\checkmark$ \\ 
+*Individual Equality & $\checkmark$ \\ 
+*Functional Properties & $\checkmark$ \\
+*Inverse-Functional Properties & $\checkmark$ \\ 
+*Value Restrictions & $\checkmark$ \\
+*Self Restrictions & $\checkmark$ \\
+Primary Key Properties & $\checkmark$ \\ 
+*Class-Specific Property Range & $\checkmark$ \\ 
+*Class-Sp. Reflexive Object P. & $\checkmark$ \\ 
+Membership in Controlled Vocabularies & $\checkmark$ \\ 
+IRI Pattern Matching & \ding{55} \\ 
+Literal Value Comparison & \ding{55} \\ 
+Define Order & \ding{55} \\ 
+Validation Levels & \ding{55} \\ 
+String Operations & \ding{55} \\ 
+\end{evaluation-cwa-una-dependency}
+
+\begin{evaluation-cwa-una-dependency}
+Context-Specific Valid Classes & \ding{55} \\
+Context-Specific Valid Properties & \ding{55} \\ 
+Default Values & \ding{55} \\ 
+Mathematical Operations & \ding{55} \\ 
+Language Tag Matching & \ding{55} \\ 
+Language Tag Cardinality & $\checkmark$ \\ 
+Whitespace Handling & \ding{55} \\ 
+HTML Handling & \ding{55} \\ 
+Conditional Properties & $\checkmark$ \\ 
+Recommended Properties & \ding{55} \\ 
+Handle RDF Collections & \ding{55} \\ 
+Value is Valid for Datatype & \ding{55} \\ 
+*Exploiting Class/Property Specialization Ontology Axioms & \ding{55} \\ 
+*Cardinality Shortcuts & $\checkmark$ \\ 
+Aggregations & \ding{55} \\ 
+\end{evaluation-cwa-una-dependency}
+
+% -----
 

### 2015-02-04 paper/paper7/paper7-appendix.tex
abstract and introduction

--- 2015-01-09 paper/ESWC 2015 Tutorial/ESWC2015Tutorial.tex
@@
 
-% Todos
-%\usepackage[colorinlistoftodos]{todonotes}
-%\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
-%\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}
-
 %\usepackage{makeidx}  % allows for indexgeneration
@@
 \usepackage{mathabx}
+\usepackage{caption} 
+\captionsetup[table]{skip=10pt}
 
@@
 \usepackage[colorinlistoftodos]{todonotes}
-\newcommand{\bz}[1]{\todo[size=\small, color=orange!40]{\textbf{Ben:} #1}}
+\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
 \newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}
+\newcommand{\er}[1]{\todo[size=\small, color=red!40]{\textbf{Erman:} #1}}
+\newcommand{\an}[1]{\todo[size=\small, color=blue!40]{\textbf{Andy:} #1}}
 
@@
 \begin{document}
-
+\renewcommand{\arraystretch}{1.3}
 %
 %
-\title{Let’s Disco – Publishing person-level data as Linked Data.}
-\subtitle{Building a Highly-Complex Data Set with Disco, PHDD, XKOS and widely used vocabularies.
-}
-%
+\title{RDF Validation of Metadata \\ on Highly-Complex Person-Level Data}
+\subtitle{}
+
 \titlerunning{XXXXX}  % abbreviated title (for running head)
@@
 %
-\author{XXX\inst{1} \and XXX\inst{1} \and Joachim Wackerow\inst{1}}
+\author{Thomas Bosch\inst{1} \and Benjamin Zapilko\inst{1} \and Joachim Wackerow\inst{1} \and Kai Eckert\inst{2}}
 %
-\authorrunning{XXXXX} % abbreviated author list (for running head)
+\authorrunning{} % abbreviated author list (for running head)
 %
@@
 \institute{GESIS – Leibniz Institute for the Social Sciences, Germany\\
-\email{\{thomas.bosch,benjamin.zapilko,joachim.wackerow\}}@gesis.org}
+\email{\{firstname.lastname\}@gesis.org},\\ 
+\and
+University of Mannheim, Germany \\
+\email{kai@informatik.uni-mannheim.de} 
+}
 
@@
 \begin{abstract}
-The DDI-RDF Discovery Vocabulary (Disco) is an RDF Schema vocabulary that supports the discovery of microdata sets and related metadata using RDF technologies in the Web of Linked Data.
-Disco can be used to discover data sets by searching for specific questions, topics, and geographical coverage.
-Disco is intended to provide means to describe microdata by essential metadata for the discovery purpose.
-The DDI (Data Documentation Initiative) is a structured metadata standard related to the observation and measurement of human activity.
 
-For a publication of DDI metadata as Linked Data, widely accepted and adopted RDF vocabularies (e.g. RDF Data Cube, DCAT, SKOS, PROV-O and Physical Data Description) are reused to a large extend. 
-In this tutorial it is shown how Disco is interwoven with these vocabularies. 
-The combined usage of Physical Data Description, Disco, and DCAT enables the creation of data repositories which provide metadata for the description of collections, for data discovery, and for processing of the data.
+\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, Disco, RDF Data Cube Vocabulary, Linked Data, Semantic Web}
+\end{abstract}
 
-In different real world use cases, we demonstrate the adoption and inclusion of Disco in existing information systems. 
-Existing DDI instances are stored in form of XML documents which can be transformed into DDI-RDF and therefore exposed as Linked Data.
-We describe typical constraints on metadata of DDI metadata, as well as how to formulate them by different constraint languages (e.g. OWL 2) and how to actually validate them.
+\section{Introduction}
 
-\keywords{DDI-RDF Discovery Vocabulary, Disco, Microdata Metadata, Data Documentation Initiative, Linked Data}
-\end{abstract}
-%
-
-%\section{Anweisungen}
-%
-%Proposals should not exceed 5 pages using a reasonable font size (not less than 11 pts). They should include the call for participation together with the following details:
-%- Abstract: 200 words maximum, for inclusion to the ESWC 2015 Web site.
-%- Tutorial description: objectives of the tutorial and relevance to ESWC 2015; information about the scope and level of detail of the material to be covered; intended audiences; learning objectives; practical sessions.
-%- Tutorial length: Half or full day, including preferences.
-%- Previous versions or related tutorials: other venues of this or similar tutorials (potentially by a different team of tutors), motivation for offering the tutorial again, at the ESWC2015.
-%- Tutoring team: short bios of the presenters, including previous training and public speaking experience (e.g., teaching in English, conference presentations, tutorials etc.)
-
-\section{Call for Participation}
-The DDI-RDF Discovery Vocabulary (Disco) is an RDF Schema vocabulary that supports the discovery of microdata sets and related metadata using RDF technologies in the Web of Linked Data. 
-It is based on the DDI (Data Documentation Initiative) which is a structured metadata standard related to the observation and measurement of human activity.
-Since this data is highly complex, widely accepted and adopted RDF vocabularies (e.g. RDF Data Cube, DCAT, SKOS, PROV-O and Physical Data Description) are reused to a large extend.
-
-In different real world use cases, the presenters of the tutorial demonstrate the adoption and inclusion of Disco in existing information systems.
-Participants are encouraged to present their own use cases where Disco has been applied or will be used. 
-Together with the presenters, participants will have the possibility to elaborate an RDF representation of their use cases and to formulate typical queries which are necessary to solve use case related problems.
-
-This tutorial addresses Linked Data developers who want to publish Linked Data sets based on complex data like person-level microdata in combination with essential information like provenance, data aggregates and data catalogs.
-
-\section{Tutorial Description}
-
-The DDI-RDF Discovery Vocabulary (Disco)\footnote{current specification is available at \url{https://github.com/linked-statistics/disco-spec}}  is an RDF Schema vocabulary that supports the discovery of microdata sets and related metadata using RDF technologies in the Web of Linked Data.
-Disco can be used to discover data sets by searching for specific questions, topics, and geographical coverage.
-Disco is intended to provide means to describe microdata by essential metadata for the discovery purpose.
-
-The DDI (Data Documentation Initiative) is a structured metadata standard related to the observation and measurement of human activity.
-It started out in the mid-1990s as a replacement for traditional archival code books documenting research data, and then branched off to cover the research data life cycle.
-Over time, as the data landscape has
-changed, the DDI XML specifications have evolved to add new coverage and functionality to respond to new user requirements.
-While the Data Documentation Initiative (DDI) is an international metadata standard with origins in the quantitative social sciences, it is increasingly being used by researchers and practitioners in other disciplines.
-The DDI specifications are also being used to document other data types, such as social media, biomarkers, administrative data, and transaction data.
-The specification itself is modular and can document and manage different stages of the data lifecycle, such as conceptualization, collection, processing, analysis, distribution, discovery, repurposing, and archiving.
-This tutorial aims to present the Disco vocabulary and its practical appliance with DDI metadata in detail.
-
-For a publication of DDI metadata as Linked Data, widely accepted and adopted RDF vocabularies (e.g.
-RDF Data Cube, DCAT, and PHDD) are reused to a large extend.
-It is shown how Disco is interwoven with these vocabularies.
-The Data Cube vocabulary is a W3C standard for representing data cubes representing multidimensional aggregate data derived from microdata which is represented by Disco.
-DCAT is a W3C standard for describing catalogs of data sets.
-Physical data description (PHDD) represents data (tables) in a rectangular format.
-The data could be either represented in records with character-separated values (CSV) or in records with fixed length.
-The combined usage of PHDD, Disco, and DCAT enables the creation of data repositories which provide metadata for the description of collections, for data discovery, and for processing of the data.
-
-Existing DDI instances are stored in form of XML documents and validated against XML Schemas\footnote{XML Schemas of current DDI version available at \url{http://www.ddialliance.org/Specification/DDI-Lifecycle/3.2/XMLSchema/}}.
-DDI-XML documents can be transformed into DDI-RDF and therefore exposed as Linked Data.
-For XML, XML Schema is the standard constraint language to validate XML documents.
-For RDF, however, there are multiple candidates for languages to express constraints on RDF data - but there is no standard language for RDF validation.
-In 2014, two working groups on RDF validation have been established: the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles working group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
-These working groups address the formulation and validation of RDF constraints.
-We will describe typical constraints on metadata of DDI metadata, as well as how to formulate and to validate them.
-We will show how to formulate these constraints by different constraint languages such as OWL 2.
-
-In 2012, we started the development of Disco in form of a one-week Dagstuhl seminar - another one-week Dagstuhl seminar and two one-week workshops followed.  
-In 2014, we finished the technical review of Disco.
-We addressed more than ten mailing lists from the Linked Data and the DDI communities and got feedback which has been incorporated into the Disco specification.
-We are planning to officially publish Disco after three years of development in the first half of the year 2015 after an additional official technical review of the DDI Alliance\footnote{\url{http://www.ddialliance.org/}}.
-
-\subsection{Objectives of the Tutorial} 
-The domain-specific origin of Disco increases the difficulties for adopting it by developers who are not familiar with the domain.
-However, person-level metadata is not restricted to a particular domain and may be an interesting data source for Linked Data developers.
-Hence, as our main objective, we want to provide assistance for creating such complex Linked Data sets using Disco.
-Because of the complexity, we especially want to demonstrate how Disco data sets can be connected with information represented using other existing vocabularies that are relevant in that context.
-Vice versa, we show how these other vocabularies and data represented with such can benefit from the interplay with Disco.
-
-Another objective of the tutorial is to share our experience in developing a RDF vocabulary out of an existing and highly-complex domain-specific data model.
-We provide insight into the development and engineering process for creating Disco.
-Finally, since Disco is already being adopted in the DDI community, we aim to increase the use of Disco in the Linked Data community.
-
-\subsection{Relevance to ESWC 2015}
-In this tutorial, the DDI-RDF Discovery vocabulary (Disco) and its interplay with other existing vocabularies is introduced.
-In contrast to other newly developed vocabularies that can be adopted easily by Linked Data experts in most cases, the complexity of Disco is higher because of its domain-specific origin and the tight interplay with other existing vocabularies.
-This makes Disco more difficult to be adopted by Linked Data experts that may not be familiar with the domain-specific background of person-level micro data.
-However, since the number of organizations that aim to publish their complex data as Linked Data grows and the number of researchers that want to conduct their research with real-world data grows, a tutorial on representing such highly complex and inter-connected data sets may be a beneficial addition for the audience of ESWC 2015.
-
-\subsection{Scope and Level of Detail of the Material}
-
-During the tutorial, we built one real world complex data set which serves as ongoing running example. 
-The whole data set can be exported from the Microdata Information System\footnote{\url{http://www.gesis.org/missy/editor/}}. 
-In all sessions, there will be practical hands-on exercises where the participants are asked to model and query particular parts of this data set. 
-The infrastructure for these exercises, i.e. a triple store, will be provided for all participants.
-We will extend slides of a previous tutorial\footnote{tutorial slides available at: \url{http://de.slideshare.net/boschthomas/201412-lets-disco-eddi-2014} and \url{http://de.slideshare.net/boschthomas/201412-lets-disco-2-eddi-2014}}
-and where appropriate refer to the current Disco specification\footnote{current specification is available at \url{https://github.com/linked-statistics/disco-spec}}.
-
-\subsection{Intended Audiences}
-The intended audience of this tutorial are Linked Data developers - beginners as well as experts - who are interested in modeling and publishing complex and highly inter-connected data sets as Linked Data.
-Since the connection with other vocabularies like QB, DCAT and PROV-O plays a major role in this context, the tutorial is not restricted to participants who are interested in person-level micro data.
-
-\subsection{Learning Objectives}
-The learning objectives of this tutorial are the following:
-\begin{itemize} 
-\item Introduction of Disco, PHDD, and XKOS for modeling complex person-level micro data
-\item Representing the interplay of Disco data with existing vocabularies
-\item Validation of Disco
-\end{itemize}
-
-\subsection{Practical Sessions}
-During the tutorial, one complex data set will be built, which serves as ongoing running example.
-In all sessions, there will be practical exercises where the participants are asked to model and query particular parts of the example data sets.
-The infrastructure for these exercises, i.e.
-a triple store with example data, will be provided for all participants by the presenters.
-
-\section{Tutorial Length}
-
-We propose a full-day tutorial.
-In the previous tutorial about Disco, we experienced that a half-day tutorial offers only enough time to cover the most important aspects about Disco and to include few hands-on exercises.
-Since we now want to expand the focus of the tutorial to the interplay of Disco with other vocabularies and its validation, a full-day seems to be appropriate.
-Furthermore, we want to offer hands-on exercises again, because they were well received at the last tutorial.
-
-\section{Previous Versions or Related Tutorials}
-
-Thomas Bosch and Benjamin Zapilko held a half-day tutorial at the EDDI14 – 6th Annual European DDI User Conference in London\footnote{\url{http://www.eddi-conferences.eu/ocs/index.php/eddi/eddi14/schedConf/program}}.
-The tutorial was well received and the presenters got overall positive feedback.
-Since the audience of Disco is two-fold - data professionals and the DDI community at the one hand and Linked Data experts at the other hand - the idea was to offer this tutorial at the ESWC conference as well.
-At the EDDI conference, the first part of the audience - data professionals and the DDI community - was addressed.
-At the ESWC conference, the second part of our audience - Linked Data experts - will be addressed.
-
-\section{Tutoring Team}
-
-%short bios of the presenters, including previous training and public speaking experience (e.g., teaching in English, conference presentations, tutorials etc.)
-
-Thomas Bosch\footnote{\url{http://boschthomas.blogspot.com}} studied information systems, holds a degree in Computer Science (M.Sc.), and is currently a PhD student.
-His research topic is all about RDF validation.
-More specifically, he investigates how to validate any RDF constraints (formulated by multiple constraint languages) and how to express them generically. 
-He held multiple presentations at international conferences and workshops (e.g. WWW, ISWC, DC, Dagstuhl seminars).
-
-Benjamin Zapilko holds a degree in Computer Science and has recently finished his PhD thesis about methods for matching social science relevant Linked Data.
-The defense talk will be at the end of January.
-Beside his PhD research, he works on modeling and publishing social science relevant data as Linked Data with the focus on data modeling and integration of heterogeneous data sources and information types.
-He presented his work at several international conferences.
-
-Joachim Wackerow holds a degree in sociology. 
-He is the vice chair of the DDI Alliance Technical Committee whose charge is to create, maintain, and enhance the DDI specification.
-He is the chair of the DDI Alliance RDF Vocabularies Working Group whose charge is to develop RDF vocabularies for efficient use of DDI metadata in the context of the Semantic Web/Linked Data.
-He organizes the annual European DDI user conferences and holds DDI introduction workshops.
+\section{Conclusion and Future Work}
 

### 2015-02-04 paper/paper7/paper7.tex
abstract and introduction

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}

% allows for temporary adjustment of side margins
\usepackage{chngpage}

% just makes the table prettier (see \toprule, \bottomrule, etc. commands below)
\usepackage{booktabs}

\usepackage[utf8]{inputenc}
%\usepackage[font=small,skip=0pt]{caption}

% footnotes
\usepackage{scrextend}

% URL handling
\usepackage{url}
\urlstyle{same}

%\usepackage{makeidx}  % allows for indexgeneration

%\usepackage{amsmath}
\usepackage{amsmath, amssymb}
\usepackage{mathabx}
\usepackage{caption} 
\captionsetup[table]{skip=10pt}

% monospace within text
\newcommand{\ms}[1]{\texttt{#1}}

% examples
\usepackage{fancyvrb}
\DefineVerbatimEnvironment{ex}{Verbatim}{numbers=left,numbersep=2mm,frame=single,fontsize=\scriptsize}

\usepackage{xspace}
% Einfache und doppelte Anfuehrungszeichen
\newcommand{\qs}{``} 
\newcommand{\qe}{''\xspace} 
\newcommand{\sqs}{`} 
\newcommand{\sqe}{'\xspace}

% checkmark
\usepackage{tikz}
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}

% Xs
\usepackage{pifont}

% Tabellenabstände kleiner
\setlength{\intextsep}{10pt} % Vertical space above & below [h] floats
\setlength{\textfloatsep}{10pt} % Vertical space below (above) [t] ([b]) floats
% \setlength{\abovecaptionskip}{0pt}
% \setlength{\belowcaptionskip}{0pt}

\usepackage{tabularx}
\newcommand{\hr}{\hline\noalign{\smallskip}} % für die horizontalen linien in tabellen

% Todos
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}
\newcommand{\er}[1]{\todo[size=\small, color=red!40]{\textbf{Erman:} #1}}
\newcommand{\an}[1]{\todo[size=\small, color=blue!40]{\textbf{Andy:} #1}}

\newenvironment{table-1cols}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
  \begin{tabular}{l}
  \hline
  \textbf{Requirements} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{table-2cols}{
  \scriptsize
  \sffamily
  \vspace{0.3cm}
  \begin{tabular}{l|l}
  \hline
  \textbf{Requirements} & \textbf{Covering DSCLs} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{complexity}{
  %\scriptsize
  %\sffamily
  %\vspace{0.3cm}
  \begin{tabular}{l|l}
  \hline
  \textbf{Complexity Class} & \textbf{Complexity} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{DL}{
  %\scriptsize
  %\sffamily
  \vspace{0cm}
  \begin{tabular}{r l}

}{
  \end{tabular}
  %\linebreak
}

\newenvironment{evaluation}{
  %\scriptsize
  %\sffamily
  %\vspace{0.3cm}
  \begin{tabular}{l|c|c|c|c|c|c}
  \hline
  \textbf{Constraint Class} & \textbf{DSP} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{constraint-languages-complexity}{
  %\scriptsize
  %\sffamily
  %\vspace{0.3cm}
  \begin{tabular}{l|c|c|c|c|c|c}
  \hline
  \textbf{Complexity Class} & \textbf{DSP} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\newenvironment{user-fiendliness}{
  %\scriptsize
  %\sffamily
  %\vspace{0.3cm}
  \begin{tabular}{l|c|c|c|c|c}
  \hline
  \textbf{criterion} & \textbf{DSP} & \textbf{OWL2} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
  \hline

}{
  \hline
  \end{tabular}
  \linebreak
}

\setcounter{secnumdepth}{5}

\begin{document}
\renewcommand{\arraystretch}{1.3}
%
%
\title{RDF Validation of Metadata \\ on Highly-Complex Person-Level Data}
\subtitle{}

\titlerunning{XXXXX}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Thomas Bosch\inst{1} \and Benjamin Zapilko\inst{1} \and Joachim Wackerow\inst{1} \and Kai Eckert\inst{2}}
%
\authorrunning{} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\institute{GESIS – Leibniz Institute for the Social Sciences, Germany\\
\email{\{firstname.lastname\}@gesis.org},\\ 
\and
University of Mannheim, Germany \\
\email{kai@informatik.uni-mannheim.de} 
}

\maketitle              % typeset the title of the contribution

\begin{abstract}
For research institutes, data libraries, and data archives,
RDF data validation according to predefined constraints is a much sought-after feature, 
particularly as this is taken for granted in the XML world.
The data most often used in research within the community around research data for the social, behavioural, and economic sciences is person-level data, i.e. data collected about individuals (households, businesses). 
%The DDI-RDF Discovery Vocabulary is used to describe and to discover this kind of research data.
While performing research, the detailed, often access restricted person-level
data is aggregated into less confidential publicly available multi-dimensional tables which answer particular research questions and whose purpose is to gain an interest in further more detailed analyses on the underlying person-level data.
To ensure high quality and trust, metadata and data must satisfy certain criteria - specified in terms of RDF constraints.

In this paper, we show how metadata and underlying data on different level of aggregation as well as collections of these data sets are represented in RDF and how therefore used vocabularies are interrelated.
We explain why RDF validation is important in this context and how (meta)data is validated against RDF constraints to ensure high quality and trust.

\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, Disco, RDF Data Cube Vocabulary, Linked Data, Semantic Web}
\end{abstract}

\section{Introduction}

\tb{we use data in singular form / we use data set instead of dataset / We use person-level data and not microdata}

For more than a decade, members of the community around research data for the social, behavioural, and economic (SBE) sciences have been developing and using a
metadata standard (composed of almost twelve hundred metadata fields) known as the \emph{Data Documentation Initiative (DDI)} \cite{Vardigan2008}.
DDI is an XML format designed for the purposes of supporting the dissemination, management,
and reuse of the data collected and archived for research purposes.  
DDI is heavily used by the CESSDA community of European national data archives, 
the International Household Survey Network community (made up of more than 90 statistical agencies),
and ICPSR - the largest SBE data archive in the US.
Recently, members of the SBE and Linked Data community developed the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}}, 
an effort to leverage the mature DDI metadata model for the purposes of exposing DDI metadata as resources within the Web of Linked Data. 
For data archives, research institutes, and data libraries,
RDF data validation according to predefined constraints is a much sought-after feature, 
particularly as this is taken for granted in the XML world (DDI-XML documents are validated against diverse XSDs\footnote{\url{http://www.ddialliance.org/Specification/}}).
Several approaches exist to meet this requirement, ranging from using \emph{OWL 2} as a constraint language to \emph{SPIN}\footnote{\url{http://spinRDF.org/}}, a SPARQL-based way to formulate and check constraints. 
There are also specific constraint languages like \emph{Shape Expressions}\footnote{\url{http://www.w3.org/Submission/shex-primer/}}, \emph{Resource Shapes}\footnote{\url{http://www.w3.org/Submission/shapes/}} or \emph{Description Set Profiles}\footnote{\url{http://dublincore.org/documents/2008/03/31/dc-dsp/}} that more or less explicitly address the aforementioned SBE community.
Bosch and Eckert\cite{BoschEckert2014-2} use SPIN as basis to define a
validation environment (\url{http://purl.org/net/rdfval-demo}) in which the validation of any constraint language\footnote{the only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL. 
The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.

The data most often used in research within the SBE community is \emph{person-level data}, i.e. data collected about individuals 
(and sometimes also businesses and households) in the form of responses to surveys or taken from administrative registers
(such as hospital records, registers of births and deaths). 
The range of person-level data is very broad (covering many different domains), 
including census, education, and health data as well as all types of business, social, and labor force surveys.  
Increasingly, this type of research data is
held within data archives or data libraries after it has been collected, so that it may be
reused by future researchers. 
In performing their research, the detailed person-level
data is aggregated into less confidential multi-dimensional tables which answer particular research questions.
Portals harvest metadata (as well as publicly available data) from multiple data providers in form of RDF.
To ensure high quality, the metadata must satisfy certain criteria - specified in terms of RDF constraints.  
After validating the metadata according to these constraints, portals offer added values to their customers, e.g. by searching over and comparing metadata of multiple providers.

By its nature, person-level data is highly confidential, and access is often only permitted for qualified researchers who must apply for access. 
The purpose of publicly available aggregated data, on the other hand, is to get a first overview and to gain an interest in further analyses on the underlying person-level data.
Researchers typically represent their results as aggregated data in form of two-dimensional tables with only a few columns (so-called \emph{variables} such as \emph{sex} or \emph{age}).
The \emph{RDF Data Cube Vocabulary (Data Cube)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e. multi-dimensional aggregate data, in RDF \cite{Cyganiak2010}. 
Aggregate data is derived from person-level data by statistics on groups or aggregates such as counts, means, and frequencies.
The SDMX metadata standard\footnote{http://sdmx.org/} – used as the basis for \emph{Data Cube} – and DDI have traditionally made efforts to align their content. 
Similarly, some of the developers of \emph{Disco} were also involved in the development of \emph{Data Cube}, 
allowing the RDF versions of these standards to retain that alignment.
While \emph{Disco} and \emph{Data Cube} provide terms for the description of data sets, 
both on a different level of aggregation, 
the \emph{Data Catalog Vocabulary (DCAT)}\footnote{\url{http://www.w3.org/TR/vocab-dcat/}} enables the representation of these data sets inside of data collections like repositories, catalogs, or archives. 
The relationship between data collections and their contained data sets is useful, since such collections are a typical entry point when searching for data.
Although, in most cases aggregated data is still published in form of PDFs, 
it is more and more common to publish aggregated data as CSV files,
allowing to perform first calculations (either using all variables or only a subset).
%For these calculations, definitions of the columns are needed (e.g. is a given variable interpreted numerically or as a string).
In 2014, SBE and Linked Data community members developed the \emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} vocabulary to represent aggregated data in a rectangular format. 
The data could be either represented in records with character-separated values (CSV) or in records with fixed length.

For more detailed analyses, researchers refer to person-level data from which aggregated data is derived from, 
as person-level data include additional variables needed for further research.
%Although not that common, the other direction is also possible, 
%i.e. researchers may use metadata on person-level data to search for aggregated data.
One very common example for detailed analyses on person-level data is the content-driven comparison of multiple surveys.
Researchers get promising findings (in form of published tables with a few columns) within a metadata portal leading to subsequent research questions 
like 'How to compare the unemployment rate of different countries (e.g. Germany, UK, and France) in the last 10 years grouped by age?'.
The first step is to determine in which countries the unemployment rate is collected and which other variables of each country-specific survey are theoretically comparable and can therefore be used to answer the underlying research question.
Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger}, or by a code list including multiple age clusters (such as '0 to 10' and '11 to 20'). 
To determine if variables measuring \emph{age} 
- collected within multiple surveys of different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
are comparable, both content-driven and technology-driven validation is performed either
within our developed validation environment or by matching algorithms. 
An example for a content-driven validation is to investigate if variables are represented in a compatible way,
i.e. are the variables' code lists theoretically comparable.
Technically, it can be validated (1) if variable definitions are available, (2) if code lists are properly structured, and (3) if for each code an associated category (a human-readable label) is specified.

\tb{maybe this paragraph should be moved to one of the subsequent sections and not be part of introduction}
Data providers and harvesters do not only offer metadata but also publicly available data on different level of detail.
To ensure high data quality and trust, they have to analyze and validate the data (are fundamental data fragments available?, how does valid data look like?). 
%They validate, e.g., if fundamental data parts are available and define how valid data should look like (using syntactic rules).
Provenance (where does the data come from?) is an important aspect in evaluating data quality.
As data searchers know exactly which data sources they trust and which are reasonable to meet their individual use cases, 
data validation can only be performed semi-automatically, i.e. an automatic approach serves as basis for intellectual decisions.

This paper aims to address two main \textbf{audiences}: 
(1) metadata practitioners seeking for how to represent metadata on data sets on different aggregation levels and
(2) metadata providers and harvesters ensuring high quality metadata by validating metadata on highly complex RDF data sets.
In this paper, we show in form of a complete real world running example how to represent metadata on highly complex person-level data (\emph{Disco}), metadata on aggregated data (\emph{Data Cube}), and aggregated data in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}).
We explain why RDF validation is important in this context and how (meta)data is validated against RDF constraints to ensure high quality (meta)data within this complex of data sets on different levels of aggregation (\textbf{contribution 2}). 
The remainder of the paper is structured as follows.

\section{Running Example}

- European data in Missy

- multiple countries (+) $-->$ region in query

\section{ideas}

- different sets of constraints for different use cases / use case specific constraints

- validation against minimal set of requirements / constraints

\section{Use Cases}

\textbf{application of matching algorithms.}
- the value for a specific data property (e.g. birth date) is needed as prerequisite to perform matching algorithms
- 1. step: validation
- 2. step: matching
- validation as reasonable extension of pattern of Ben (e.g. for pattern: is this digit correct?)

\textbf{Data Integration.}
use RDF validation for data integration

\textbf{XKOS validation}
only 1 sentence / only special case / e.g. profession classification ISCO

extended version of SKOS – XKOS – to describe formal statistical classifications.

\section{RDF Validation}

RDF validation scenarios require the closed-world assumption (CWA) (i.e., a statement is inferred to be false if it cannot be proved to be true).

- different severity levels for different validation types

\subsection{Content-Driven Validation}

\textbf{Theoretical Concepts.}
Variables must have at least one relation to a theoretical concept.
The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}.

\textbf{Search for Studies.}
Each study must have an abstract. 
If an abstract is missing a study title may be sufficient in many cases.

\subsection{Technology-Driven Validation}

\section{Related Work}

With RDF validation, one can overcome the drawbacks when validating XML documents.
Certain things cannot be validated using XSDs.
As a consequence, so-called secondary-level validation tools like Schematron have been introduced to overcome the limitations of XSDs.
Schematron generated validation rules and validates XML documents according to them.
It cannot be validated if each code of a variable's code list is associated with a category \tb{further explanation needed}.
It cannot be validated that if an element has a specific value, then certain child elements must be present.

\tb{Achim, which kind of things cannot be validated using XSDs / we also need references}

\section{Conclusion and Future Work}

\bibliography{../../literature/literature}{}
\bibliographystyle{plain}
\setcounter{tocdepth}{1}
%\listoftodos
\end{document}

### 2015-02-04 paper/paper6/paper6.tex
abstract and introduction
added validation rules

--- 2015-01-11 paper/paper6/paper6.tex
@@
 
+% examples
+\usepackage{fancyvrb}
+\DefineVerbatimEnvironment{ex}{Verbatim}{numbers=left,numbersep=2mm,frame=single,fontsize=\scriptsize}
+
 \newenvironment{DL}{
@@
 
-\title{Modeling and Validation of Metadata on \\ Highly-Complex Person-Level Data Sets in RDF}
+\title{}
 
@@
 
-\section{Motivation}
-
-\begin{itemize}
-  \item why do we need these newly defined vocabularies?
-	\item Why do we need RDF Validation?
-	\item Why do we need to validate metadata on person-level data sets? 
-\end{itemize}
-
-\textbf{Contributions.}
-\begin{itemize}
-  \item We show how to model highly complex person-level data sets in RDF using different vocabularies 
-  \item We define constraints on Disco, Data Cube, PHDD, DCAT, XKOS data sets
-	\item WE provide an implementation to validate Disco, Data Cube, PHDD, DCAT, XKOS data sets 
-\end{itemize}
-
-\section{Data Documentation Initiative}
-
-\section{DDI-RDF Discovery Vocabulary}
-
-\begin{itemize}
-  \item overview of disco
-	\item description of disco
-\end{itemize}
-
-\subsection{Conceptional Model}
-
-\subsection{Use Cases}
-
-\subsection{Relationships to other Vocabularies}
-
-\begin{itemize}
-	\item RDF Data Cube, DCAT, PHDD, XKOS
-	\item brief description of vocabularies
-\end{itemize}
-
-\section{Validation Environment}
-
-\section{Validation of Metadata on Person-Level Data Sets}
-
-Where appropriate constraint types are related to complementary requirements of the RDF validation requirements database.
-
-We state one Disco constraint for each constraint type.
-
-Constraint types marked with an asterisk can be used as an OWL 2 axiom.
-Thus, reasoners may be used to infer implicit triples resolving constraint violations causing when these constraints are validated.
-\textcolor{blue}{example}
-
-\subsection{Data Model Consistency}
-
-Is the data consistent with the intended semantics of the data model?
-Ensures the integrity of the data according to the data model.
-
-\subsection{Unqualified Cardinality Restrictions}
-
-\subsection{Minimum Qualified Cardinality Restrictions}
-
-A minimum cardinality restrictions contains all those individuals that are connected by a property to at least n different individuals/literals 
-that are instances of a particular class or data range. If the class is missing, it is taken to be owl:Thing. 
-If the data range is missing, it is taken to be rdfs:Literal.
-$\geq n R. C$ is a minimum qualified cardinality restriction where $n \in \mathbb{N}$\footnote{{\em R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES} and {\em R-211-CARDINALITY-CONSTRAINTS}}.
-
-\textbf{{\em DISCO-C-XX}}.
-A {\em disco:Questionnaire} has at least 1 {\em disco:question} relationship to {\em disco:Question}\footnote{When mapped to DL, we do not state namespace prefixes for simplicity reasons}.
-
-\begin{DL}
-Questionnaire $\sqsubseteq$ $\geq$1 question.Question
-\end{DL}
-
-\subsection{Exact Qualified Cardinality Restrictions}
-
-An exact cardinality restriction contains all those individuals that are connected by a property to exactly n different individuals that are instances of a particular class or data range. 
-If the class is missing, it is taken to be owl:Thing. 
-If the data range is not present, it is taken to be rdfs:Literal.
-$\geq n R.
-C \sqcap \leq n R.
-C $ is an exact qualified cardinality restriction where $n \in \mathbb{N}$\footnote{{\em R-74-EXACT-QUALIFIED-CARDINALITY-ON-PROPERTIES} and {\em R-211-CARDINALITY-CONSTRAINTS}.}.
-
-\textbf{{\em DISCO-C-XX}}. 
-A {\em disco:Question} has exactly 1 {\em disco:universe} relationship to {\em disco:Universe}.
-
-\begin{DL}
-Question $\sqsubseteq$ \\
-$\geq$1 universe.Universe $\sqcap$ $\leq$1 universe.Universe \\
-\end{DL}
-
-\subsection{Universal Quantifications*}
-
-A universal class expression ({\em value restriction} in DL) contains all those individuals that are connected by an object property only to individuals that are instances of a particular class\footnote{{\em R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}}.
-
-\textbf{{\em DISCO-C-XX}}.
-Only {\em disco:LogicalDataSet}s can have {\em disco:aggregation} relationships to {\em qb:DataSet}s.
-
-\begin{DL}
-LogicalDataSet $\sqsubseteq$ $\forall$ aggregation.DataSet \\
-\end{DL}
-
-\subsection{Existential Quantifications}
-
-An existential class expression ({\em existential restriction} in DL terminology) contains all those individuals that are connected by the property P to an individual x that is an instance of the class C or to literals that are in the data range DR\footnote{{\em R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}}.
-
-\textbf{{\em DISCO-C-XX}}. 
-There must be at least 1 {\em disco:universe} relationship from {\em disco:Studies} or {\em disco:StudyGroups} to {\em disco:Universe}.
-
-\begin{DL}
-Study $\sqcup$ StudyGroup $\sqsubseteq$ $\exists$ universe.Universe \\
-\end{DL}
-
-\subsection{Disjunction}
-
-A union class expression contains all individuals that are instances of at least one class $C_{i}$ for 1 $\leq$ i $\leq$ n. 
-A union data range contains all tuples of literals that are contained in the at least one data range $DR_{i}$ for 1 $\leq$ i $\leq$ n.
-Synonyms of {\em disjunction} are {\em union} and {\em inclusive or}\footnote{{\em R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS} and {\em R-18-DISJUNCTION-OF-DATA-RANGES}}.
-
-\textbf{{\em DISCO-C-XX}}. 
-Only {\em disco:Variable}s or {\em disco:Question}s or {\em disco:RepresentedVariable}s can have {\em disco:concept} relationships to {\em skos:Concept}s.
-
-\begin{DL}
-Variable $\sqcup$ Question $\sqcup$ RepresentedVariable \\
-$\sqsubseteq$ $\forall$ concept.Concept \\
-\end{DL}
-
-\subsection{Property Domains*}
-
-{\em Property Domains} ({\em domain restrictions on roles} in DL) restricts the domain of object and data properties.
-The purpose is to declare that a given property is associated with a class. 
-In OO terms this is the declaration of a member, field, attribute or association. 
-$\exists R.
-\top \sqsubseteq C$ is the object property restriction where $R$ is the object property (role) whose domain is restricted to concept $C$\footnote{{\em R-25-OBJECT-PROPERTY-DOMAIN} and {\em R-26-DATA-PROPERTY-DOMAIN}}.
-{\em Property Domain} constraints are defined for each Disco object and data property.
-
-\textbf{{\em DISCO-C-XX}}. 
-Only {\em disco:Question}s can have {\em disco:responseDomain} relationships.
-
-\begin{DL}
-$\exists$ responseDomain.$\top$ $\sqsubseteq$ Question 
-\end{DL}
-
-\subsection{Property Ranges*}
-
-{\em Property Range} ({\em range restrictions on roles} in DL) restricts the range of object and data properties.
-$\top \sqsubseteq \forall R . C$ is the range restriction to the object property $R$ (restricted by the concept $C$)\footnote{{\em R-28-OBJECT-PROPERTY-RANGE} and {\em R-35-DATA-PROPERTY-RANGE}}.
-
-\textbf{{\em DISCO-C-XX}}. 
-{\em disco:caseQuantity} relationships can only point to literals of the datatype {\em xsd:nonNegativeInteger}.
-
-\begin{DL}
-$\top$ $\sqsubseteq$ $\forall$ caseQuantity.nonNegativeInteger \\
-\end{DL}
-
-\subsection{Class-Specific Property Ranges}
-
-{\em Class-Specific Property Range} restricts the range of object and data properties for individuals within a specific context (e.g. class, shape, application profile).
-The values of each member property of a class may be limited by their value type, such as xsd:string or foaf:Person\footnote{{\em R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS} and {\em R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS}}.
-
-\textbf{{\em DISCO-C-XX}}. 
-Only {\em disco:Question}s can have {\em disco:questionText} relationships to literals of the datatype {\em rdf:langString}.
-
-\begin{DL}
-$\neg$Question $\sqsubseteq$ $\neg\exists$ questionText.langString
-\end{DL}
-
-\subsection{Subsumption*}
-
-A subclass axiom ({\em concept inclusion} in DL) states that the class C1 is a subclass of the class C2 - C1 is more specific than C2\footnote{{\em R-100-SUBSUMPTION}}.
-
-\textbf{{\em DISCO-C-XX}}. 
-All {\em disco:Universe}s must also be {\em skos:Concept}s.
-
-\begin{DL}
-Universe $\sqsubseteq$ Concept
-\end{DL}
-
-\subsection{Class Equivalence*}
-
-{\em Class Equivalence} asserts that two concepts have the same instances.
-While synonyms are an obvious example of equivalent concepts, in practice one more
-often uses concept equivalence to give a name to complex expressions \cite{Kroetzsch2012}.
-Concept equivalence is indeed subsumption from left and right ($A \sqsubseteq B$ and $B \sqsubseteq A$ implies $A \equiv B$)\footnote{{\em R-3-EQUIVALENT-CLASSES}}.
-
-\textbf{{\em DISCO-C-XX}}. 
-All {\em sio:SIO\_000367}s must also be {\em disco:Variable}s.
-
-\begin{DL}
-Variable $\equiv$ SIO\_000367
-\end{DL}
-
-The Semanticscience Integrated Ontology (SIO)\footnote{https://code.google.com/p/semanticscience/wiki/SIO} provides a simple, integrated ontology of types and relations for rich description of objects, processes and their attributes.
-{\em sio:SIO\_000367} is a variable defined as a value that may change within the scope of a given problem or set of operations.
-Thus, {\em sio:SIO\_000367} is equivalent to {\em disco:Variable}.
-
-\subsection{Sub Properties*}
-
-{\em Sub Properties} state that the property P1 is a sub property of the property P2 - that is, if an individual x is connected by P1 to an individual or a literal y, then x is also connected by P2 to y.
-
-\textbf{{\em DISCO-C-XX}}. 
-If an individual x is connected by {\em disco:fundedBy} to an individual y, then x is also connected by {\em dcterms:contributor} to y.
-
-\begin{DL}
-fundedBy $\sqsubseteq$ contributor 
-\end{DL}
-
-\subsection{Disjoint Classes}
-
-{\em Disjoint Classes} state that all of the classes are pairwise disjoint; 
-that is, no individual can be at the same time an instance of these disjoint classes\footnote{{\em R-7-DISJOINT-CLASSES}}.
-\textbf{{\em DISCO-C-01}}. All Disco classes are defined to be pairwise disjoint.
-The following DL statements holds for each pair of Disco classes:
-
-\begin{DL}
-Study $\sqcap$ Variable $\sqsubseteq$ $\perp$\\
-\end{DL}
-
-\subsection{Asymmetric Object Properties}
-
-A property is asymmetric if it is disjoint from its own inverse \cite{Kroetzsch2012}.
-An object property asymmetry axiom states that the object property OP is asymmetric - that is, if an individual x is connected by OP to an individual y, then y cannot be connected by OP to x\footnote{{\em R-62-ASYMMETRIC-OBJECT-PROPERTIES}}.
-
-\textbf{{\em DISCO-C-01}}. 
-A {\em disco:Variable} may be based on a {\em disco:RepresentedVariable}.
-A {\em disco:RepresentedVariable}, however, cannot be based on a {\em disco:Variable}.
-This is a kind of mistake may occur as a semantically equivalent object property for the other direction may also be possible ({\em disco:basisOf}).
-
-\begin{DL}
-$basedOn \sqcap basedOn^{-} \sqsubseteq \bot$ 
-\end{DL}
-
-\subsection{Class-Specific Irreflexive Object Properties}
-
-A property is irreflexive if it is never locally reflexive \cite{Kroetzsch2012}.
-An object property irreflexivity axiom states that the object property OP is irreflexive - that is, no individual is connected by OP to itself.
-
-\textbf{{\em DISCO-C-XX}}.
-Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:boader} to themselves.
-
-\begin{DL}
-Concept $\sqsubseteq$ $\neg$$\exists$ broader.Self. 
-\end{DL}
-
-\textbf{{\em DISCO-C-XX}}.
-Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:narrower} to themselves.
-
-\begin{DL}
-Concept $\sqsubseteq$ $\neg$$\exists$ narrower.Self. 
-\end{DL}
-
-\subsection{Context-Specific Exclusive OR of Property Groups}
-
-{\em Context-Specific Exclusive OR of Property Groups} corresponds to the requirement:
-{\em R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC}.
-Exclusive or is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
-Only one of multiple property groups leads to valid data.
-
-\textbf{{\em DISCO-C-XX}}.
-Within the context of Disco, skos:Concepts can have either skos:definition (when interpreted as DDI concepts) or skos:notation and skos:prefLabel properties (when interpreted as DDI codes and categories), but not both.
-
-\begin{DL}
-Human $\sqsubseteq$ ($\neg$ E $\sqcap$ F) $\sqcup$ (E $\sqcap$ $\neg$ F) \\ 
-E $\equiv$ A $\sqcap$ B \\
-F $\equiv$ C $\sqcap$ D \\
-A $\sqsubseteq$ $\geq$ 1 name . string $\sqcap$ $\leq$ 1 name . string \\
-B $\sqsubseteq$ $\geq$ 1 givenName . string $\sqcap$ $\leq$ 1 givenName . string \\
-C $\sqsubseteq$ $\geq$ 1 mbox . IRI $\sqcap$ $\leq$ 1 mbox . IRI \\
-D $\sqsubseteq$ $\geq$ 1 homepage . Document $\sqcap$ $\leq$ 1 homepage . Document \\
-\end{DL}
-
-\subsection{SKOS-Related Constraints}
-
-\subsubsection{Membership in Controlled Vocabularies.}
-
-Questions, variables, and represented variables may have representations.
-
-\subsubsection{Hierarchies}
-
-Hierarchies of DDI concepts
-
-\begin{itemize}
-	\item root?
-\end{itemize}
-
-\subsection{Ordering}
-
-In DDI, variables, questions, and categories are typically organized in a particular order. 
-For obtaining this order, {\em skos:OrderedCollection} resources are used. 
-A collection of variables, e.g, is represented as being of the type {\em skos:OrderedCollection} containing multiple variables (each represented as {\em skos:Concept}) in a {\em skos:memberList}.
-
-\section{Validation in Combination with other Vocabularies}
-
-\subsection{RDF Data Cube Vocabulary}
-
-There are 22 RDF Data Cube integrity constraints\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf} \cite{CyganiakReynolds2014}.
-
-\begin{itemize}
-	\item \textcolor{blue}{describe 1 constraint of each type in detail with Datalog query}
-\end{itemize}
-
-\textbf{Data Model Consistency.}
-{\em IC-0}, \textcolor{red}{{\em IC-8}}, {\em IC-13}, {\em IC-14}, {\em IC-15}, {\em IC-16}, {\em IC-17}, \textcolor{red}{{\em IC-18}}
-%\begin{itemize}
-	%\item {\em IC-0:} Datatypes must be consistent under RDF D-entailment using a datatype map containing all the datatypes used within the graph.
-	%\item \textcolor{red}{{\em IC-8:} Every {\em qb:componentProperty} on a {\em qb:SliceKey} must also be declared as a {\em qb:component} of the associated {\em qb:DataStructureDefinition}.} 
-%\end{itemize}
-
-\textbf{Unqualified Cardinality Restrictions.}
-{\em IC-4}, {\em IC-5}, {\em IC-10}, {\em IC-11}
-%\begin{itemize}
-	%\item {\em IC-4:} Every dimension declared in a {\em qb:DataStructureDefinition} must have a declared {\em rdfs:range}. 
-	%\item {\em IC-5:} Every dimension with range {\em skos:Concept} must have a {\em qb:codeList}. 
-	%\item {\em IC-10:} Every {\em qb:Slice} must have a value for every dimension declared in its {\em qb:sliceStructure}. 
-	%\item {\em IC-11:} All dimensions required - Every {\em qb:Observation} has a value for each dimension declared in its associated {\em qb:DataStructureDefinition}.
-%\end{itemize}
-
-\textbf{Qualified Cardinality Restrictions.}
-{\em IC-1}, {\em IC-2}, {\em IC-3}, {\em IC-6}, {\em IC-7}, {\em IC-9} 
-%\begin{itemize}
-	%\item {\em IC-1:} Every {\em qb:Observation} has exactly one associated {\em qb:DataSet}. 
-	%\item {\em IC-2:} Every {\em qb:DataSet} has exactly one associated {\em qb:DataStructureDefinition}. 
-	%\item {\em IC-3:} Every {\em qb:DataStructureDefinition} must include at least one declared measure. 
-	%\item {\em IC-6:} The only components of a {\em qb:DataStructureDefinition} that may be marked as optional, using {\em qb:componentRequired} are attributes. 
-	%\item {\em IC-7:} Every {\em qb:SliceKey} must be associated with a {\em qb:DataStructureDefinition}. 
-	%\item {\em IC-9:} Each {\em qb:Slice} must have exactly one associated {\em qb:sliceStructure}. 
-%\end{itemize}
-
-\textbf{Duplicate Detection.}
-{\em IC-12}
-%\begin{itemize}
-	%\item {\em IC-12:} No duplicate observations - No two {\em qb:Observations} in the same {\em qb:DataSet} may have the same value for all dimensions. 
-%\end{itemize}
-
-\textbf{Membership in Controlled Vocabularies.}
-\textcolor{red}{{\em IC-19}}
-
-\textbf{SKOS Hierarchies.}
-{\em IC-20}, {\em IC-21}
-
-%\textbf{Mandatory Properties.}
-
-%\textbf{Optional Properties.}
-
-\begin{itemize}
-	\item \textcolor{blue}{are there further constraints which can be described in this paper?}
-\end{itemize}
-
-\subsection{SKOS and XKOS}
-
-\subsection{PHDD}
-
-\subsection{DCAT}
-
-\section{DDI 4 Validation}
-
-\section{Implementation}
-
-\textbf{Validation of Data Cube instances.}
-\begin{itemize}
-	\item \textcolor{blue}{is there an implementation available yet? If not I implement it in our validation environment}
-	\item \textcolor{blue}{example QB data set / we could use the one from the QB spec}
-\end{itemize}
-
-\section{Evaluation}
-
-\begin{itemize}
-	\item validate constraints on complex example data set
-	\item count Disco, QB, PHDD, XKOS, DCAT constraints by constraint groups 
-\end{itemize}
-
-\section{Related Work}
-
-\textbf{RDF Data Cube Vocabulary.}
-A well-formed RDF Data Cube is an a RDF graph describing one or more instances of {\em qb:DataSet} for which each of the defined integrity constraints passes.
-Each integrity constraint is expressed as narrative prose and, where possible, a SPARQL ASK query or query template. 
-If the ASK query is applied to an RDF graph then it will return true if that graph contains one or more Data Cube instances which violate the corresponding constraint.
-\cite{CyganiakReynolds2014}
-
-\textbf{DCAT.}
-\textcolor{blue}{are there already constraints defined for DCAT?}
-
 \section{Conclusion and Future Work}

### 2015-02-04 paper/paper7/paper7-appendix.tex
added validation rules

@@
 
+\section{Validation of Metadata on Person-Level Data Sets}
+
+\textcolor{blue}{multiple validation levels}
+
+Where appropriate constraint types are related to complementary requirements of the RDF validation requirements database.
+
+We state one Disco constraint for each constraint type.
+
+Constraint types marked with an asterisk can be used as an OWL 2 axiom.
+Thus, reasoners may be used to infer implicit triples resolving constraint violations causing when these constraints are validated.
+\textcolor{blue}{example}
+
+\subsection{Data Model Consistency}
+
+Is the data consistent with the intended semantics of the data model?
+Ensures the integrity of the data according to the data model.
+
+\subsection{Unqualified Cardinality Restrictions}
+
+\subsection{Minimum Qualified Cardinality Restrictions}
+
+A minimum cardinality restrictions contains all those individuals that are connected by a property to at least n different individuals/literals 
+that are instances of a particular class or data range. If the class is missing, it is taken to be owl:Thing. 
+If the data range is missing, it is taken to be rdfs:Literal.
+$\geq n R. C$ is a minimum qualified cardinality restriction where $n \in \mathbb{N}$\footnote{{\em R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES} and {\em R-211-CARDINALITY-CONSTRAINTS}}.
+\textbf{{\em DISCO-C-XX:}}
+A {\em disco:Questionnaire} has at least 1 {\em disco:question} relationship to {\em disco:Question}\footnote{When mapped to DL, we do not state namespace prefixes for simplicity reasons}.
+
+\begin{DL}
+Questionnaire $\sqsubseteq$ $\geq$1 question.Question
+\end{DL}
+
+\subsection{Exact Qualified Cardinality Restrictions}
+
+An exact cardinality restriction contains all those individuals that are connected by a property to exactly n different individuals that are instances of a particular class or data range. 
+If the class is missing, it is taken to be owl:Thing. 
+If the data range is not present, it is taken to be rdfs:Literal.
+$\geq n R.
+C \sqcap \leq n R.
+C $ is an exact qualified cardinality restriction where $n \in \mathbb{N}$\footnote{{\em R-74-EXACT-QUALIFIED-CARDINALITY-ON-PROPERTIES} and {\em R-211-CARDINALITY-CONSTRAINTS}.}.
+\textbf{{\em DISCO-C-XX:}}
+A {\em disco:Question} has exactly 1 {\em disco:universe} relationship to {\em disco:Universe}.
+
+\begin{DL}
+Question $\sqsubseteq$ \\
+$\geq$1 universe.Universe $\sqcap$ $\leq$1 universe.Universe \\
+\end{DL}
+
+\subsection{Universal Quantifications*}
+
+A universal class expression ({\em value restriction} in DL) contains all those individuals that are connected by an object property only to individuals that are instances of a particular class\footnote{{\em R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}}.
+\textbf{{\em DISCO-C-XX:}}
+Only {\em disco:LogicalDataSet}s can have {\em disco:aggregation} relationships to {\em qb:DataSet}s.
+
+\begin{DL}
+LogicalDataSet $\sqsubseteq$ $\forall$ aggregation.DataSet \\
+\end{DL}
+
+\subsection{Existential Quantifications}
+
+An existential class expression ({\em existential restriction} in DL terminology) contains all those individuals that are connected by the property P to an individual x that is an instance of the class C or to literals that are in the data range DR\footnote{{\em R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}}.
+\textbf{{\em DISCO-C-XX:}} 
+There must be at least 1 {\em disco:universe} relationship from {\em disco:Studies} or {\em disco:StudyGroups} to {\em disco:Universe}.
+
+\begin{DL}
+Study $\sqcup$ StudyGroup $\sqsubseteq$ $\exists$ universe.Universe \\
+\end{DL}
+
+\subsection{Disjunction}
+
+A union class expression contains all individuals that are instances of at least one class $C_{i}$ for 1 $\leq$ i $\leq$ n. 
+A union data range contains all tuples of literals that are contained in the at least one data range $DR_{i}$ for 1 $\leq$ i $\leq$ n.
+Synonyms of {\em disjunction} are {\em union} and {\em inclusive or}\footnote{{\em R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS} and {\em R-18-DISJUNCTION-OF-DATA-RANGES}}.
+\textbf{{\em DISCO-C-XX:}} 
+Only {\em disco:Variable}s or {\em disco:Question}s or {\em disco:RepresentedVariable}s can have {\em disco:concept} relationships to {\em skos:Concept}s.
+
+\begin{DL}
+Variable $\sqcup$ Question $\sqcup$ RepresentedVariable \\
+$\sqsubseteq$ $\forall$ concept.Concept \\
+\end{DL}
+
+\subsection{Property Domains*}
+
+{\em Property Domains} ({\em domain restrictions on roles} in DL) restricts the domain of object and data properties.
+The purpose is to declare that a given property is associated with a class. 
+In OO terms this is the declaration of a member, field, attribute or association. 
+$\exists R.
+\top \sqsubseteq C$ is the object property restriction where $R$ is the object property (role) whose domain is restricted to concept $C$\footnote{{\em R-25-OBJECT-PROPERTY-DOMAIN} and {\em R-26-DATA-PROPERTY-DOMAIN}}.
+{\em Property Domain} constraints are defined for each Disco object and data property.
+\textbf{{\em DISCO-C-XX:}} 
+Only {\em disco:Question}s can have {\em disco:responseDomain} relationships.
+
+\begin{DL}
+$\exists$ responseDomain.$\top$ $\sqsubseteq$ Question 
+\end{DL}
+
+\subsection{Property Ranges*}
+
+{\em Property Range} ({\em range restrictions on roles} in DL) restricts the range of object and data properties.
+$\top \sqsubseteq \forall R . C$ is the range restriction to the object property $R$ (restricted by the concept $C$)\footnote{{\em R-28-OBJECT-PROPERTY-RANGE} and {\em R-35-DATA-PROPERTY-RANGE}}. 
+\textbf{{\em DISCO-C-XX:}} 
+{\em disco:caseQuantity} relationships can only point to literals of the datatype {\em xsd:nonNegativeInteger}.
+
+\begin{DL}
+$\top$ $\sqsubseteq$ $\forall$ caseQuantity.nonNegativeInteger \\
+\end{DL}
+
+\subsection{Class-Specific Property Ranges}
+
+{\em Class-Specific Property Range} restricts the range of object and data properties for individuals within a specific context (e.g. class, shape, application profile).
+The values of each member property of a class may be limited by their value type, such as xsd:string or foaf:Person\footnote{{\em R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS} and {\em R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS}}.
+\textbf{{\em DISCO-C-XX:}} 
+Only {\em disco:Question}s can have {\em disco:questionText} relationships to literals of the datatype {\em rdf:langString}.
+
+\begin{DL}
+$\neg$Question $\sqsubseteq$ $\neg\exists$ questionText.langString
+\end{DL}
+
+\subsection{Subsumption*}
+
+A subclass axiom ({\em concept inclusion} in DL) states that the class C1 is a subclass of the class C2 - C1 is more specific than C2\footnote{{\em R-100-SUBSUMPTION}}.
+\textbf{{\em DISCO-C-XX:}} 
+All {\em disco:Universe}s must also be {\em skos:Concept}s.
+
+\begin{DL}
+Universe $\sqsubseteq$ Concept
+\end{DL}
+
+\subsection{Class Equivalence*}
+
+{\em Class Equivalence} asserts that two concepts have the same instances.
+While synonyms are an obvious example of equivalent concepts, in practice one more
+often uses concept equivalence to give a name to complex expressions \cite{Kroetzsch2012}.
+Concept equivalence is indeed subsumption from left and right ($A \sqsubseteq B$ and $B \sqsubseteq A$ implies $A \equiv B$)\footnote{{\em R-3-EQUIVALENT-CLASSES}}.
+\textbf{{\em DISCO-C-XX:}}
+All {\em sio:SIO\_000367}s must also be {\em disco:Variable}s.
+
+\begin{DL}
+Variable $\equiv$ SIO\_000367
+\end{DL}
+
+The Semanticscience Integrated Ontology (SIO)\footnote{https://code.google.com/p/semanticscience/wiki/SIO} provides a simple, integrated ontology of types and relations for rich description of objects, processes and their attributes.
+{\em sio:SIO\_000367} is a variable defined as a value that may change within the scope of a given problem or set of operations.
+Thus, {\em sio:SIO\_000367} is equivalent to {\em disco:Variable}.
+
+\subsection{Sub Properties*}
+
+{\em Sub Properties} state that the property P1 is a sub property of the property P2 - that is, if an individual x is connected by P1 to an individual or a literal y, then x is also connected by P2 to y.
+\textbf{{\em DISCO-C-XX:}}
+If an individual x is connected by {\em disco:fundedBy} to an individual y, then x is also connected by {\em dcterms:contributor} to y.
+
+\begin{DL}
+fundedBy $\sqsubseteq$ contributor 
+\end{DL}
+
+\subsection{Disjoint Classes}
+
+{\em Disjoint Classes} state that all of the classes are pairwise disjoint; 
+that is, no individual can be at the same time an instance of these disjoint classes\footnote{{\em R-7-DISJOINT-CLASSES}}.
+\textbf{{\em DISCO-C-XX:}} 
+All Disco classes are defined to be pairwise disjoint.
+The following DL statements holds for each pair of Disco classes:
+
+\begin{DL}
+Study $\sqcap$ Variable $\sqsubseteq$ $\perp$\\
+\end{DL}
+
+\subsection{Asymmetric Object Properties}
+
+A property is asymmetric if it is disjoint from its own inverse \cite{Kroetzsch2012}.
+An object property asymmetry axiom states that the object property OP is asymmetric - that is, if an individual x is connected by OP to an individual y, then y cannot be connected by OP to x\footnote{{\em R-62-ASYMMETRIC-OBJECT-PROPERTIES}}.
+\textbf{{\em DISCO-C-XX:}} 
+A {\em disco:Variable} may be based on a {\em disco:RepresentedVariable}.
+A {\em disco:RepresentedVariable}, however, cannot be based on a {\em disco:Variable}.
+This is a kind of mistake may occur as a semantically equivalent object property for the other direction may also be possible ({\em disco:basisOf}).
+
+\begin{DL}
+$basedOn \sqcap basedOn^{-} \sqsubseteq \bot$ 
+\end{DL}
+
+\subsection{Class-Specific Irreflexive Object Properties}
+
+A property is irreflexive if it is never locally reflexive \cite{Kroetzsch2012}.
+An object property irreflexivity axiom states that the object property OP is irreflexive - that is, no individual is connected by OP to itself. 
+\textbf{{\em DISCO-C-XX:}}
+Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:boader} to themselves (DL: Concept $\sqsubseteq$ $\neg$$\exists$ broader.Self).
+
+\textbf{{\em DISCO-C-XX:}}
+Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:narrower} to themselves.
+
+\begin{DL}
+Concept $\sqsubseteq$ $\neg$$\exists$ narrower.Self. 
+\end{DL}
+
+\subsection{Context-Specific Exclusive OR of Property Groups}
+
+Exclusive or is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
+Only one of multiple property groups leads to valid data\footnote{{\em R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC}}.
+\textbf{{\em DISCO-C-XX:}}
+Within the context of Disco, skos:Concepts can have either skos:definition (when interpreted as DDI concepts) or skos:notation and skos:prefLabel properties (when interpreted as DDI codes and categories), but not both.
+
+\begin{DL}
+Concept $\sqsubseteq$ ($\neg$ D $\sqcap$ C) $\sqcup$ (D $\sqcap$ $\neg$ C) \\ 
+D $\equiv$ A $\sqcap$ B \\
+A $\sqsubseteq$ $\geq$ 1 notation.string $\sqcap$ $\leq$ 1 notation.string \\
+B $\sqsubseteq$ $\geq$ 1 prefLabel.string $\sqcap$ $\leq$ 1 prefLabel.string \\
+C $\sqsubseteq$ $\geq$ 1 definition.string $\sqcap$ $\leq$ 1 definition.string \\
+\end{DL}
+
+\subsection{Allowed Values}
+
+It is a common requirement to narrow down the value space of a property by an exhaustive enumeration of the valid values (both literals or resource). 
+This is often rendered in drop down boxes or radio buttons in user interfaces. 
+Allowed values for properties can be IRIs, IRIs (matching one or multiple patterns), (any) literals, literals of a list of allowed literals (e.g.
+'red' 'blue' 'green'), typed literals one or multiple type(s) (e.g.
+xsd:string)\footnote{{\em R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS} and
+{\em R-37-ALLOWED-VALUES-FOR-RDF-LITERALS}}.
+
+\textbf{{\em DISCO-C-XX}}.
+{\em disco:CategoryStatistics} can only have {\em disco:computationBase} relationships to the values 'valid' and 'invalid' of the datatype {\em rdf:langString}.
+
+\begin{DL}
+CategoryStatistics $\equiv$ \\ $\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString \\
+\end{DL}
+
+\subsection{Membership in Controlled Vocabularies.}
+
+Resources can only be members of listed controlled vocabularies\footnote{{\em R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES} and
+{\em R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES}}.
+
+\textbf{{\em DISCO-C-XX}}.
+{\em disco:SummaryStatistics} can only have {\em disco:summaryStatisticType} relationships to {\em skos:Concept}s which must be members of the controlled vocabulary {\em ddicv:SummaryStatisticType} which is a {\em skos:ConceptScheme}.
+
+\begin{DL}
+SummaryStatistics $\sqsubseteq$ \\
+$\forall summaryStatisticType.Concept \sqcap \forall inScheme . A$ \\
+$A \equiv ConceptScheme \sqcap \{SummaryStatisticType\}$
+\end{DL}
+
+\subsection{Literal Value Comparison}
+
+Depending on the property semantics,
+there are cases where two different literal values must have
+a specific ordering with respect to an operator. 
+P1 and P2 are the datatype properties we need to compare and 
+OP is the comparison operator (\textless, \textless=, \textgreater, \textgreater=, =, !=)\footnote{{\em R-43-LITERAL-VALUE-COMPARISON}}.
+The {\em COMP Pattern}, one of the Data Quality Test Pattern, can be used to validate the {\em Literal Value Comparison} constraint \cite{Kontokostas2014}:
+
+\begin{ex}
+SELECT ?s WHERE { 
+    ?s %%P1%% ?v1 .
+    ?s %%P2%% ?v2 .
+    FILTER ( ?v1 %%OP%% ?v2 ) }
+\end{ex}
+
+\textbf{{\em DISCO-C-XX}}.
+{\em disco:startDate}s must be before (‘\textless’) the {\em disco:endDate}s.
+To validate this constraint we bind the variables as follows (P1: {\em disco:startDate}, P2: {\em disco:endDate}, OP: \textless).
+
+\subsection{Literal Ranges}
+
+P1 is a data property (of an instance of class C1) and its literal value must be between the range of [$V_{min}$,$V_{max}$].
+\textbf{{\em DISCO-C-XX:}}
+{\em disco:percentage} (domain: {\em disco:CategoryStatistics}) literals must be of the datatype {\em xsd:double} whose range should be restricted to be between 0 and 100 (not expressible in DL)\footnote{{\em R-45-RANGES-OF-RDF-LITERAL-VALUES}}.
+
+\subsection{Mathematical Operations}
+
+Examples for {\em Mathematical Operations} are the addition of two dates, the addition of days to a start date, and statistical computations (e.g. average, mean, sum).
+\textbf{{\em DISCO-C-XX:}}
+The sum of {\em disco:percentage} {\em xsd:double} values of all codes (represented as {\em skos:Concept}s) of a code list ({\em skos:ConceptScheme} or {\em skos:OrderedCollection}), serving as representation of a particular {\em disco:Variable}, must exactly be 100
+(not expressible in DL)\footnote{{\em R-42-MATHEMATICAL-OPERATIONS} and {\em R-41-STATISTICAL-COMPUTATIONS}}.
+
+\subsection{Default Values}
+
+Default values for objects and literals are inferred automatically.
+It should be possible to declare the default value for a given property, e.g.
+so that input forms can be pre-populated and to insert a required property that is missing in a web service call\footnote{{\em R-31-DEFAULT-VALUES-OF-RDF-OBJECTS} and {\em R-38-DEFAULT-VALUES-OF-RDF-LITERALS}}.
+\textbf{{\em DISCO-C-XX:}}
+The value 'true' for the property {\em disco:isPublic} ({\em xsd:boolean}) indicates that the data set ({\em disco:LogicalDataSet}) can be accessed (usually downloaded) by anyone.
+Per default, access to data sets should be restricted ('false').
+
+\subsection{Language Tag Matching}
+
+For particular data properties, values must be stated for predefined languages (not expressible in DL)\footnote{{\em R-47-LANGUAGE-TAG-MATCHING}}.
+\textbf{{\em DISCO-C-XX:}}
+There must be an English variable name ({\em skos:notation}) for each {\em disco:Variable} within {\em disco:LogicalDataSet}s.
+
+\subsection{Language Tag Cardinality}
+
+For particular data properties, values of predefined languages must be stated for determined number of times (not expressible in DL)
+\footnote{{\em R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG} and {\em R-48-MISSING-LANGUAGE-TAGS}}.
+\textbf{{\em DISCO-C-XX:}}
+There must be at least one English {\em disco:questionText} for each {\em disco:Question} within {\em disco:LogicalDataSet}s.
+\textbf{{\em DISCO-C-XX:}}
+There should be at most one English literal value for variable names ({\em skos:notation}, domain: {\em disco:Variable}).
+
+\subsection{Conditional Properties}
+
+If specific properties exist, then specific other properties also have to be present\footnote{{\em R-71-CONDITIONAL-PROPERTIES}}.
+\textbf{{\em DISCO-C-XX:}}
+If a {\em skos:Concept represents a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
+then the property {\em disco:isValid} has to be stated indicating if the code is valid ('true') or missing ('false').
+
+\subsection{Recommended Properties}
+
+Which properties are not required but recommended within a particular context\footnote{{\em R-72-RECOMMENDED-PROPERTIES}}.
+\textbf{{\em DISCO-C-XX:}}
+The property ({\em skos:notation} is not mandatory for {\em disco:Variable}s, but recommended to indicate variable names.
+
+\subsection{Value is Valid for Datatype}
+
+Make sure that a value is valid for its datatype.
+It has to be ensured, e.g., that a date is really a date, or that a xsd:nonNegativeInteger value is not negative. 
+\textbf{{\em DISCO-C-XX:}}
+Check if literal values of the property {\em disco:startDate} are really of the datatype {\em xsd:date}(not expressible in DL).
+
+\subsection{Equivalent Properties}
+
+\subsection{Functional Properties}
+
+\subsection{Data Property Facets}
+
+xsd:length of disco:purpose
+
+\subsection{Hierarchies}
+
+Hierarchies of DDI concepts
+
+\begin{itemize}
+	\item root?
+\end{itemize}
+
+\subsection{Ordering}
+
+In DDI, variables, questions, and categories are typically organized in a particular order. 
+For obtaining this order, {\em skos:OrderedCollection} resources are used. 
+A collection of variables, e.g, is represented as being of the type {\em skos:OrderedCollection} containing multiple variables (each represented as {\em skos:Concept}) in a {\em skos:memberList}.
+
+\section{Validation in Combination with other Vocabularies}
+
+\subsection{RDF Data Cube Vocabulary}
+
+There are 22 RDF Data Cube integrity constraints\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf} \cite{CyganiakReynolds2014}.
+
+\begin{itemize}
+	\item \textcolor{blue}{describe 1 constraint of each type in detail with Datalog query}
+\end{itemize}
+
+\textbf{Data Model Consistency.}
+{\em IC-0}, \textcolor{red}{{\em IC-8}}, {\em IC-13}, {\em IC-14}, {\em IC-15}, {\em IC-16}, {\em IC-17}, \textcolor{red}{{\em IC-18}}
+%\begin{itemize}
+	%\item {\em IC-0:} Datatypes must be consistent under RDF D-entailment using a datatype map containing all the datatypes used within the graph.
+	%\item \textcolor{red}{{\em IC-8:} Every {\em qb:componentProperty} on a {\em qb:SliceKey} must also be declared as a {\em qb:component} of the associated {\em qb:DataStructureDefinition}.} 
+%\end{itemize}
+
+\textbf{Unqualified Cardinality Restrictions.}
+{\em IC-4}, {\em IC-5}, {\em IC-10}, {\em IC-11}
+%\begin{itemize}
+	%\item {\em IC-4:} Every dimension declared in a {\em qb:DataStructureDefinition} must have a declared {\em rdfs:range}. 
+	%\item {\em IC-5:} Every dimension with range {\em skos:Concept} must have a {\em qb:codeList}. 
+	%\item {\em IC-10:} Every {\em qb:Slice} must have a value for every dimension declared in its {\em qb:sliceStructure}. 
+	%\item {\em IC-11:} All dimensions required - Every {\em qb:Observation} has a value for each dimension declared in its associated {\em qb:DataStructureDefinition}.
+%\end{itemize}
+
+\textbf{Qualified Cardinality Restrictions.}
+{\em IC-1}, {\em IC-2}, {\em IC-3}, {\em IC-6}, {\em IC-7}, {\em IC-9} 
+%\begin{itemize}
+	%\item {\em IC-1:} Every {\em qb:Observation} has exactly one associated {\em qb:DataSet}. 
+	%\item {\em IC-2:} Every {\em qb:DataSet} has exactly one associated {\em qb:DataStructureDefinition}. 
+	%\item {\em IC-3:} Every {\em qb:DataStructureDefinition} must include at least one declared measure. 
+	%\item {\em IC-6:} The only components of a {\em qb:DataStructureDefinition} that may be marked as optional, using {\em qb:componentRequired} are attributes. 
+	%\item {\em IC-7:} Every {\em qb:SliceKey} must be associated with a {\em qb:DataStructureDefinition}. 
+	%\item {\em IC-9:} Each {\em qb:Slice} must have exactly one associated {\em qb:sliceStructure}. 
+%\end{itemize}
+
+\textbf{Duplicate Detection.}
+{\em IC-12}
+%\begin{itemize}
+	%\item {\em IC-12:} No duplicate observations - No two {\em qb:Observations} in the same {\em qb:DataSet} may have the same value for all dimensions. 
+%\end{itemize}
+
+\textbf{Membership in Controlled Vocabularies.}
+\textcolor{red}{{\em IC-19}}
+
+\textbf{SKOS Hierarchies.}
+{\em IC-20}, {\em IC-21}
+
+%\textbf{Mandatory Properties.}
+
+%\textbf{Optional Properties.}
+
+\begin{itemize}
+	\item \textcolor{blue}{are there further constraints which can be described in this paper?}
+\end{itemize}
+
+\subsection{SKOS and XKOS}
+
+\subsection{PHDD}
+
+\subsection{DCAT}
+
 \section{Conclusion and Future Work}

### 2015-02-04 paper/paper7/paper7.tex
added validation rules

@@
 
-\section{Use Cases}
+\section{RDF Representation of Metadata}
+
+\section{RDF Validation of Metadata}
+
+RDF validation scenarios require the closed-world assumption (CWA) (i.e., a statement is inferred to be false if it cannot be proved to be true).
+
+- different severity levels for different validation types
 
@@
 
-\textbf{Data Integration.}
-use RDF validation for data integration
-
 \textbf{XKOS validation}
@@
 extended version of SKOS – XKOS – to describe formal statistical classifications.
-
-\section{RDF Validation}
-
-RDF validation scenarios require the closed-world assumption (CWA) (i.e., a statement is inferred to be false if it cannot be proved to be true).
-
-- different severity levels for different validation types
 
@@
 
+\section{RDF Validation of Data}
+
+\textbf{Data Integration.}
+use RDF validation for data integration
+
+\section{Implementation}
+
+\textbf{Validation of Data Cube instances.}
+\begin{itemize}
+	\item \textcolor{blue}{is there an implementation available yet? If not I implement it in our validation environment}
+	\item \textcolor{blue}{example QB data set / we could use the one from the QB spec}
+\end{itemize}
+
+\section{Evaluation}
+
+\begin{itemize}
+	\item validate constraints on complex example data set
+	\item count Disco, QB, PHDD, XKOS, DCAT constraints by constraint groups 
+\end{itemize}
+
 \section{Related Work}
@@
 
+\textbf{RDF Data Cube Vocabulary.}
+A well-formed RDF Data Cube is an a RDF graph describing one or more instances of {\em qb:DataSet} for which each of the defined integrity constraints passes.
+Each integrity constraint is expressed as narrative prose and, where possible, a SPARQL ASK query or query template. 
+If the ASK query is applied to an RDF graph then it will return true if that graph contains one or more Data Cube instances which violate the corresponding constraint.
+\cite{CyganiakReynolds2014}
+
+\textbf{DCAT.}
+\textcolor{blue}{are there already constraints defined for DCAT?}
+
 \section{Conclusion and Future Work}

### 2015-02-04 paper/paper7/paper7-appendix.tex
disco validation rules

@@
 \begin{abstract}
+...
 
@@
 
+Bosch and Eckert initiated a comprehensive database\footnote{Publicly available at \url{http://purl.org/net/rdf-validation}.} on RDF validation requirements to collect case studies, use cases, and requirements \cite{BoschEckert2014}.
+It is continuously updated and used to evaluate and to compare various existing solutions for RDF constraint formulation and validation. 
+Requirements are classified to provide a high-level view on different solutions and to facilitate a better understanding of the problem domain.
+Bosch et al. identified in total 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
+They recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which they explain each requirement (constraint type) in detail and give examples for each (represented by listed constraint languages) \cite{BoschNolleAcarEckert2015}.
+
 \section{Validation of Metadata on Person-Level Data Sets}
 
-\textcolor{blue}{multiple validation levels}
-
+We state at least one Disco constraint for the majority of the constraint types.
 Where appropriate constraint types are related to complementary requirements of the RDF validation requirements database.
-
-We state one Disco constraint for each constraint type.
-
-Constraint types marked with an asterisk can be used as an OWL 2 axiom.
-Thus, reasoners may be used to infer implicit triples resolving constraint violations causing when these constraints are validated.
-\textcolor{blue}{example}
+Constraint types marked with an asterisk can be used as OWL 2 axioms.
+Thus, reasoners may be used to infer implicit triples resolving constraint violations caused when these constraints are validated.
 
@@
 Ensures the integrity of the data according to the data model.
+
+\subsection{Subsumption*}
+
+A subclass axiom ({\em concept inclusion} in DL) states that the class C1 is a subclass of the class C2 - C1 is more specific than C2\footnote{{\em R-100-SUBSUMPTION}}.
+\textbf{{\em DISCO-C-XX:}} 
+All {\em disco:Universe}s must also be {\em skos:Concept}s.
+
+\begin{DL}
+Universe $\sqsubseteq$ Concept
+\end{DL}
 
@@
 $\neg$Question $\sqsubseteq$ $\neg\exists$ questionText.langString
-\end{DL}
-
-\subsection{Subsumption*}
-
-A subclass axiom ({\em concept inclusion} in DL) states that the class C1 is a subclass of the class C2 - C1 is more specific than C2\footnote{{\em R-100-SUBSUMPTION}}.
-\textbf{{\em DISCO-C-XX:}} 
-All {\em disco:Universe}s must also be {\em skos:Concept}s.
-
-\begin{DL}
-Universe $\sqsubseteq$ Concept
 \end{DL}

### 2015-02-04 paper/paper7/paper7.tex
disco validation rules

@@
 Each integrity constraint is expressed as narrative prose and, where possible, a SPARQL ASK query or query template. 
-If the ASK query is applied to an RDF graph then it will return true if that graph contains one or more Data Cube instances which violate the corresponding constraint.
-\cite{CyganiakReynolds2014}
+If the ASK query is applied to an RDF graph then it will return true if that graph contains one or more Data Cube instances which violate the corresponding constraint \cite{CyganiakReynolds2014}.
 

### 2015-02-04 paper/paper7/paper7-appendix.tex
disco validation rules

@@
 Is the data consistent with the intended semantics of the data model?
-Ensures the integrity of the data according to the data model.
+Such validation rules ensure the integrity of the data according to the data model.
 
@@
 
-A subclass axiom ({\em concept inclusion} in DL) states that the class C1 is a subclass of the class C2 - C1 is more specific than C2\footnote{{\em R-100-SUBSUMPTION}}.
-\textbf{{\em DISCO-C-XX:}} 
-All {\em disco:Universe}s must also be {\em skos:Concept}s.
+A \emph{subclass axiom}\footnote{{\em R-100-SUBSUMPTION}} ({\em concept inclusion} in DL) states that the class \emph{C1} is a subclass of the class \emph{C2} - \emph{C1} is more specific than \emph{C2},
+i.e. each resources of the class \emph{C1} must also be part of the class extension of \emph{C2}.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX:}} 
+All {\em disco:Universe}s must also be {\em skos:Concept}s:
 
@@
 \end{DL}
+\end{itemize}
+
+\subsection{Class Equivalence*}
+
+{\em Class Equivalence}\footnote{{\em R-3-EQUIVALENT-CLASSES}} asserts that two concepts have the same instances.
+While synonyms are an obvious example of equivalent concepts, in practice one more
+often uses concept equivalence to give a name to complex expressions \cite{Kroetzsch2012}.
+Concept equivalence is indeed subsumption from left and right ($A \sqsubseteq B$ and $B \sqsubseteq A$ implies $A \equiv B$).
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX:}}
+All {\em sio:SIO\_000367} resources must also be {\em disco:Variable}s:
+
+\begin{DL}
+Variable $\equiv$ SIO\_000367
+\end{DL}
+
+The Semanticscience Integrated Ontology (SIO)\footnote{https://code.google.com/p/semanticscience/wiki/SIO} provides a simple, integrated ontology of types and relations for rich description of objects, processes and their attributes.
+{\em sio:SIO\_000367} is a variable defined as a value that may change within the scope of a given problem or set of operations.
+Thus, {\em sio:SIO\_000367} is equivalent to {\em disco:Variable}.
+\end{itemize}
+
+\subsection{Sub Properties*}
+
+{\em Sub Properties}\footnote{\emph{R-54-SUB-OBJECT-PROPERTIES}, \emph{R-54-SUB-DATA-PROPERTIES}} state that the property \emph{P1} is a sub property of the property \emph{P2} - that is, if an individual \emph{x} is connected by \emph{P1} to an individual or a literal \emph{y}, then \emph{x} is also connected by \emph{P2} to \emph{y}.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX:}}
+If an individual \emph{x} is connected by {\em disco:fundedBy} to an individual \emph{y}, then \emph{x} is also connected by {\em dcterms:contributor} to \emph{y}.
+
+\begin{DL}
+fundedBy $\sqsubseteq$ contributor 
+\end{DL}
+\end{itemize}
+
+\subsection{Property Domains*}
+
+{\em Property Domains}\footnote{{\em R-25-OBJECT-PROPERTY-DOMAIN}, {\em R-26-DATA-PROPERTY-DOMAIN}} ({\em domain restrictions on roles} in DL) restrict the domain of object and data properties.
+The purpose is to declare that a given property is associated with a class. 
+In OO terms this is the declaration of a member, field, attribute or association. 
+$\exists R. \top \sqsubseteq C$ is the object property restriction where $R$ is the object property (role) whose domain is restricted to concept $C$.
+{\em Property Domain} constraints are defined for each \emph{Disco} object and data property.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX:}} 
+Only {\em disco:Question}s can have {\em disco:responseDomain} relationships.
+
+\begin{DL}
+$\exists$ responseDomain.$\top$ $\sqsubseteq$ Question 
+\end{DL}
+\end{itemize}
+
+\subsection{Property Ranges*}
+
+{\em Property Ranges}\footnote{{\em R-28-OBJECT-PROPERTY-RANGE}, {\em R-35-DATA-PROPERTY-RANGE}} ({\em range restrictions on roles} in DL) restrict the range of object and data properties.
+$\top \sqsubseteq \forall R . C$ is the range restriction to the object property $R$ (restricted by the concept $C$).
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX:}} 
+{\em disco:caseQuantity} relationships can only point to literals of the datatype {\em xsd:nonNegativeInteger}.
+
+\begin{DL}
+$\top$ $\sqsubseteq$ $\forall$ caseQuantity.nonNegativeInteger \\
+\end{DL}
+\end{itemize}
+
+\subsection{Inverse Object Properties*}
+
+\subsection{Symmetric Object Properties*}
+
+\subsection{Asymmetric Object Properties*}
+
+A property is asymmetric\footnote{{\em R-62-ASYMMETRIC-OBJECT-PROPERTIES}} if it is disjoint from its own inverse \cite{Kroetzsch2012}.
+An object property asymmetry axiom states that the object property \emph{OP} is asymmetric - that is, if an individual \emph{x} is connected by \emph{OP} to an individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX:}} 
+A {\em disco:Variable} may be based on a {\em disco:RepresentedVariable}.
+A {\em disco:RepresentedVariable}, however, cannot be based on a {\em disco:Variable}.
+This is a kind of mistake which may occur as a semantically equivalent object property for the other direction may also be possible ({\em disco:basisOf}).
+
+\begin{DL}
+$basedOn \sqcap basedOn^{-} \sqsubseteq \bot$ 
+\end{DL}
+\end{itemize}
+
+\subsection{Reflexive Object Properties*}
+
+\emph{Reflexive Object Properties}\footnote{\emph{R-59-REFLEXIVE-OBJECT-PROPERTIES}} (\emph{reflexive roles}, \emph{global reflexivity} in DL) can be expressed by imposing local reflexivity on the top concept \cite{Kroetzsch2012}.
+
+\subsection{Irreflexive Object Properties*}
+
+An object property is irreflexive\footnote{\emph{R-60-IRREFLEXIVE-OBJECT-PROPERTIES}} (\emph{irreflexive role} in DL) if it is never locally reflexive \cite{Kroetzsch2012}.
+An object property irreflexivity axiom \emph{IrreflexiveObjectProperty( OPE )} states that the object property expression \emph{OPE} is irreflexive - that is, no individual is connected by \emph{OPE} to itself.
+In \emph{Disco}, every object property is irreflexive.
+
+\begin{itemize}
+  \item \textbf{{\em DISCO-C-XX:}}
+Within the Disco context, no individual is connected by the object property {\em instrument} to itself
+
+\begin{DL}
+$\top$ $\sqsubseteq$ $\neg$ $\exists  instrument . Self$ 
+\end{DL}
+\end{itemize}
+
+\subsection{Class-Specific Irreflexive Object Properties*}
+
+A property is \emph{irreflexive} if it is never locally reflexive \cite{Kroetzsch2012}.
+An object property irreflexivity axiom states that the object property \emph{OP} is irreflexive - that is, no individual is connected by \emph{OP} to itself.
+\emph{Class-Specific Irreflexive Object Properties} are object properties which are irreflexive within a given context, e.g. a class.
+
+\begin{itemize}
+  \item \textbf{{\em DISCO-C-XX:}}
+Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:boader} to themselves
+
+\begin{DL}
+Concept $\sqsubseteq$ $\neg$$\exists$ broader.Self. 
+\end{DL}
+
+	\item \textbf{{\em DISCO-C-XX:}}
+Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:narrower} to themselves.
+
+\begin{DL}
+Concept $\sqsubseteq$ $\neg$$\exists$ narrower.Self. 
+\end{DL}
+\end{itemize}
+
+\subsection{Disjoint Properties}
+
+A \emph{disjoint properties axiom}\footnote{\emph{R-9-DISJOINT-PROPERTIES}} states that all of the properties are pairwise disjoint; 
+that is, no individual \emph{x} can be connected to an individual \emph{y} by these properties.
+
+\subsection{Disjoint Classes}
+
+{\em Disjoint Classes}\footnote{{\em R-7-DISJOINT-CLASSES}} state that all of the classes are pairwise disjoint; 
+that is, no individual can be at the same time an instance of these disjoint classes.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX:}} 
+All \emph{Disco} classes are defined to be pairwise disjoint.
+The following DL statements holds for each pair of Disco classes:
+
+\begin{DL}
+Study $\sqcap$ Variable $\sqsubseteq$ $\perp$\\
+\end{DL}
+\end{itemize}
+
+\subsection{Context-Specific Property Groups}
+
+The \emph{Context-Specific Property Groups}\footnote{\emph{R-66-PROPERTY-GROUPS}} constraint groups data and object properties within a context (e.g. a class).
+
+\subsection{Context-Specific Inclusive OR of Properties}
+
+\subsection{Context-Specific Inclusive OR of Property Groups}
+
+\subsection{Recursive Queries}
+
+\subsection{Individual Inequality}
+
+\subsection{Equivalent Properties*}
+
+\subsection{Property Assertions}
+
+\subsection{Data Property Facets}
+
+For datatype properties it should be possible to declare frequently needed \emph{facets}\footnote{\emph{R-46-CONSTRAINING-FACETS}} to drive user interfaces and validate input against simple conditions, including min/max value, regular expressions, string length - similar to XSD datatypes.
+Constraining facets, to restrict datatypes of RDF literals, may be: \emph{xsd:length}, \emph{xsd:minLength}, \emph{xsd:maxLength}, \emph{xsd:pattern}, \emph{xsd:enumeration}, \emph{xsd:whiteSpace}, \\ \emph{xsd:maxInclusive}, \emph{xsd:maxExclusive}, \emph{xsd:minExclusive}, \emph{xsd:minInclusive}, \emph{xsd:total} \emph{Digits}, \emph{xsd:fractionDigits}.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX:}} The abstract of a study (\emph{disco:purpose}) should have a minimum length (\emph{xsd:minInclusive}) of x. 
+\end{itemize}
+
+\subsection{Literal Pattern Matching}
+
+There are multiple use cases associated with the requirement to match literals according to given patterns\footnote{\emph{R-44-PATTERN-MATCHING-ON-RDF-LITERALS}}.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX:}} Each \emph{disco:Variable} of a given \emph{disco:LogicalDataSet} must have a given prefix for its variable name (\emph{skos:notation}). 
+\end{itemize}
+
+\subsection{Negative Literal Pattern Matching}
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX:}} 
+\end{itemize}
+
+\subsection{Object Property Paths*}
+
+\emph{Object Property Paths}\footnote{\emph{R-55-OBJECT-PROPERTY-PATHS}} (or \emph{Object Property Chains} and in DL terminology \emph{complex role inclusion axiom} or \emph{role composition}) is the more complex form of sub properties.
+This axiom states that, if an individual \emph{x} is connected by a sequence of object property expressions \emph{OPE$_1$, ..., OPE$_n$} with an individual \emph{y}, then \emph{x} is also connected with \emph{y} by the object property expression \emph{OPE}.
+Role composition can only appear on the left-hand side of complex role inclusions \cite{Kroetzsch2012}.
+
+\subsection{Intersection*}
+
+\subsection{Disjunction*}
+
+A \emph{union class expression}\footnote{{\em R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS} and {\em R-18-DISJUNCTION-OF-DATA-RANGES}} contains all individuals that are instances of at least one class $C_{i}$ for 1 $\leq$ i $\leq$ n.
+A \emph{union data range} contains all tuples of literals that are contained in at least one data range $DR_{i}$ for 1 $\leq$ i $\leq$ n.
+Synonyms of {\em disjunction} are {\em union} and {\em inclusive or}.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX:}} 
+Only {\em disco:Variable}s or {\em disco:Question}s or {\em disco:RepresentedVariable}s can have {\em disco:concept} relationships to {\em skos:Concept}s.
+
+\begin{DL}
+Variable $\sqcup$ Question $\sqcup$ RepresentedVariable $\sqsubseteq$ $\forall$ concept.Concept \\
+\end{DL}
+\end{itemize}
 
@@
 
-\subsection{Disjunction}
-
-A union class expression contains all individuals that are instances of at least one class $C_{i}$ for 1 $\leq$ i $\leq$ n. 
-A union data range contains all tuples of literals that are contained in the at least one data range $DR_{i}$ for 1 $\leq$ i $\leq$ n.
-Synonyms of {\em disjunction} are {\em union} and {\em inclusive or}\footnote{{\em R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS} and {\em R-18-DISJUNCTION-OF-DATA-RANGES}}.
-\textbf{{\em DISCO-C-XX:}} 
-Only {\em disco:Variable}s or {\em disco:Question}s or {\em disco:RepresentedVariable}s can have {\em disco:concept} relationships to {\em skos:Concept}s.
-
-\begin{DL}
-Variable $\sqcup$ Question $\sqcup$ RepresentedVariable \\
-$\sqsubseteq$ $\forall$ concept.Concept \\
-\end{DL}
-
-\subsection{Property Domains*}
-
-{\em Property Domains} ({\em domain restrictions on roles} in DL) restricts the domain of object and data properties.
-The purpose is to declare that a given property is associated with a class. 
-In OO terms this is the declaration of a member, field, attribute or association. 
-$\exists R.
-\top \sqsubseteq C$ is the object property restriction where $R$ is the object property (role) whose domain is restricted to concept $C$\footnote{{\em R-25-OBJECT-PROPERTY-DOMAIN} and {\em R-26-DATA-PROPERTY-DOMAIN}}.
-{\em Property Domain} constraints are defined for each Disco object and data property.
-\textbf{{\em DISCO-C-XX:}} 
-Only {\em disco:Question}s can have {\em disco:responseDomain} relationships.
-
-\begin{DL}
-$\exists$ responseDomain.$\top$ $\sqsubseteq$ Question 
-\end{DL}
-
-\subsection{Property Ranges*}
-
-{\em Property Range} ({\em range restrictions on roles} in DL) restricts the range of object and data properties.
-$\top \sqsubseteq \forall R . C$ is the range restriction to the object property $R$ (restricted by the concept $C$)\footnote{{\em R-28-OBJECT-PROPERTY-RANGE} and {\em R-35-DATA-PROPERTY-RANGE}}. 
-\textbf{{\em DISCO-C-XX:}} 
-{\em disco:caseQuantity} relationships can only point to literals of the datatype {\em xsd:nonNegativeInteger}.
-
-\begin{DL}
-$\top$ $\sqsubseteq$ $\forall$ caseQuantity.nonNegativeInteger \\
-\end{DL}
-
 \subsection{Class-Specific Property Ranges}
@@
 $\neg$Question $\sqsubseteq$ $\neg\exists$ questionText.langString
-\end{DL}
-
-\subsection{Class Equivalence*}
-
-{\em Class Equivalence} asserts that two concepts have the same instances.
-While synonyms are an obvious example of equivalent concepts, in practice one more
-often uses concept equivalence to give a name to complex expressions \cite{Kroetzsch2012}.
-Concept equivalence is indeed subsumption from left and right ($A \sqsubseteq B$ and $B \sqsubseteq A$ implies $A \equiv B$)\footnote{{\em R-3-EQUIVALENT-CLASSES}}.
-\textbf{{\em DISCO-C-XX:}}
-All {\em sio:SIO\_000367}s must also be {\em disco:Variable}s.
-
-\begin{DL}
-Variable $\equiv$ SIO\_000367
-\end{DL}
-
-The Semanticscience Integrated Ontology (SIO)\footnote{https://code.google.com/p/semanticscience/wiki/SIO} provides a simple, integrated ontology of types and relations for rich description of objects, processes and their attributes.
-{\em sio:SIO\_000367} is a variable defined as a value that may change within the scope of a given problem or set of operations.
-Thus, {\em sio:SIO\_000367} is equivalent to {\em disco:Variable}.
-
-\subsection{Sub Properties*}
-
-{\em Sub Properties} state that the property P1 is a sub property of the property P2 - that is, if an individual x is connected by P1 to an individual or a literal y, then x is also connected by P2 to y.
-\textbf{{\em DISCO-C-XX:}}
-If an individual x is connected by {\em disco:fundedBy} to an individual y, then x is also connected by {\em dcterms:contributor} to y.
-
-\begin{DL}
-fundedBy $\sqsubseteq$ contributor 
-\end{DL}
-
-\subsection{Disjoint Classes}
-
-{\em Disjoint Classes} state that all of the classes are pairwise disjoint; 
-that is, no individual can be at the same time an instance of these disjoint classes\footnote{{\em R-7-DISJOINT-CLASSES}}.
-\textbf{{\em DISCO-C-XX:}} 
-All Disco classes are defined to be pairwise disjoint.
-The following DL statements holds for each pair of Disco classes:
-
-\begin{DL}
-Study $\sqcap$ Variable $\sqsubseteq$ $\perp$\\
-\end{DL}
-
-\subsection{Asymmetric Object Properties}
-
-A property is asymmetric if it is disjoint from its own inverse \cite{Kroetzsch2012}.
-An object property asymmetry axiom states that the object property OP is asymmetric - that is, if an individual x is connected by OP to an individual y, then y cannot be connected by OP to x\footnote{{\em R-62-ASYMMETRIC-OBJECT-PROPERTIES}}.
-\textbf{{\em DISCO-C-XX:}} 
-A {\em disco:Variable} may be based on a {\em disco:RepresentedVariable}.
-A {\em disco:RepresentedVariable}, however, cannot be based on a {\em disco:Variable}.
-This is a kind of mistake may occur as a semantically equivalent object property for the other direction may also be possible ({\em disco:basisOf}).
-
-\begin{DL}
-$basedOn \sqcap basedOn^{-} \sqsubseteq \bot$ 
-\end{DL}
-
-\subsection{Class-Specific Irreflexive Object Properties}
-
-A property is irreflexive if it is never locally reflexive \cite{Kroetzsch2012}.
-An object property irreflexivity axiom states that the object property OP is irreflexive - that is, no individual is connected by OP to itself. 
-\textbf{{\em DISCO-C-XX:}}
-Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:boader} to themselves (DL: Concept $\sqsubseteq$ $\neg$$\exists$ broader.Self).
-
-\textbf{{\em DISCO-C-XX:}}
-Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:narrower} to themselves.
-
-\begin{DL}
-Concept $\sqsubseteq$ $\neg$$\exists$ narrower.Self. 
 \end{DL}
@@
 
-\subsection{Equivalent Properties}
-
 \subsection{Functional Properties}
-
-\subsection{Data Property Facets}
-
-xsd:length of disco:purpose
 

### 2015-02-05 paper/paper7/paper7-appendix.tex
disco validation rules

@@
 Thus, reasoners may be used to infer implicit triples resolving constraint violations caused when these constraints are validated.
+When constraint types are mapped to DL, we do not state namespace prefixes for simplicity reasons.
 
@@
 
-A \emph{union class expression}\footnote{{\em R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS} and {\em R-18-DISJUNCTION-OF-DATA-RANGES}} contains all individuals that are instances of at least one class $C_{i}$ for 1 $\leq$ i $\leq$ n.
+A \emph{union class expression}\footnote{{\em R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS}, {\em R-18-DISJUNCTION-OF-DATA-RANGES}} contains all individuals that are instances of at least one class $C_{i}$ for 1 $\leq$ i $\leq$ n.
 A \emph{union data range} contains all tuples of literals that are contained in at least one data range $DR_{i}$ for 1 $\leq$ i $\leq$ n.
@@
 
-\subsection{Unqualified Cardinality Restrictions}
+\subsection{Negation*}
 
-\subsection{Minimum Qualified Cardinality Restrictions}
+\subsection{Existential Quantifications*}
 
-A minimum cardinality restrictions contains all those individuals that are connected by a property to at least n different individuals/literals 
-that are instances of a particular class or data range. If the class is missing, it is taken to be owl:Thing. 
-If the data range is missing, it is taken to be rdfs:Literal.
-$\geq n R. C$ is a minimum qualified cardinality restriction where $n \in \mathbb{N}$\footnote{{\em R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES} and {\em R-211-CARDINALITY-CONSTRAINTS}}.
-\textbf{{\em DISCO-C-XX:}}
-A {\em disco:Questionnaire} has at least 1 {\em disco:question} relationship to {\em disco:Question}\footnote{When mapped to DL, we do not state namespace prefixes for simplicity reasons}.
+An \emph{existential class expression}\footnote{{\em R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}} ({\em existential restriction} in DL terminology) contains all those individuals that are connected by the property \emph{P} to an individual \emph{x} that is an instance of the class \emph{C} or to literals that are in the data range \emph{DR}.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX:}} 
+There must be at least one {\em disco:universe} relationship from {\em disco:Studies} or {\em disco:StudyGroups} to {\em disco:Universe}.
 
 \begin{DL}
-Questionnaire $\sqsubseteq$ $\geq$1 question.Question
+Study $\sqcup$ StudyGroup $\sqsubseteq$ $\exists$ universe.Universe \\
 \end{DL}
-
-\subsection{Exact Qualified Cardinality Restrictions}
-
-An exact cardinality restriction contains all those individuals that are connected by a property to exactly n different individuals that are instances of a particular class or data range. 
-If the class is missing, it is taken to be owl:Thing. 
-If the data range is not present, it is taken to be rdfs:Literal.
-$\geq n R.
-C \sqcap \leq n R.
-C $ is an exact qualified cardinality restriction where $n \in \mathbb{N}$\footnote{{\em R-74-EXACT-QUALIFIED-CARDINALITY-ON-PROPERTIES} and {\em R-211-CARDINALITY-CONSTRAINTS}.}.
-\textbf{{\em DISCO-C-XX:}}
-A {\em disco:Question} has exactly 1 {\em disco:universe} relationship to {\em disco:Universe}.
-
-\begin{DL}
-Question $\sqsubseteq$ \\
-$\geq$1 universe.Universe $\sqcap$ $\leq$1 universe.Universe \\
-\end{DL}
+\end{itemize}
 
@@
 
-A universal class expression ({\em value restriction} in DL) contains all those individuals that are connected by an object property only to individuals that are instances of a particular class\footnote{{\em R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}}.
-\textbf{{\em DISCO-C-XX:}}
+A \emph{universal class expression}\footnote{{\em R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}} ({\em value restriction} in DL) contains all those individuals that are connected by an object property only to individuals that are instances of a particular class.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX:}}
 Only {\em disco:LogicalDataSet}s can have {\em disco:aggregation} relationships to {\em qb:DataSet}s.
@@
 \end{DL}
+\end{itemize}
 
-\subsection{Existential Quantifications}
+\subsection{Minimum Unqualified Cardinality Restrictions*}
 
-An existential class expression ({\em existential restriction} in DL terminology) contains all those individuals that are connected by the property P to an individual x that is an instance of the class C or to literals that are in the data range DR\footnote{{\em R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}}.
-\textbf{{\em DISCO-C-XX:}} 
-There must be at least 1 {\em disco:universe} relationship from {\em disco:Studies} or {\em disco:StudyGroups} to {\em disco:Universe}.
+\subsection{Minimum Qualified Cardinality Restrictions*}
+
+A \emph{minimum cardinality restriction}\footnote{{\em R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}, {\em R-211-CARDINALITY-CONSTRAINTS}} contains all those individuals that are connected by a property to at least n different individuals/literals
+that are instances of a particular class or data range. If the class is missing, it is taken to be \emph{owl:Thing}. 
+If the data range is missing, it is taken to be \emph{rdfs:Literal}.
+$\geq n R. C$ is a minimum qualified cardinality restriction where $n \in \mathbb{N}$.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX:}}
+A {\em disco:Questionnaire} has at least one {\em disco:question} relationship to {\em disco:Question}.
 
 \begin{DL}
-Study $\sqcup$ StudyGroup $\sqsubseteq$ $\exists$ universe.Universe \\
+Questionnaire $\sqsubseteq$ $\geq$1 question.Question
 \end{DL}
+\end{itemize}
+
+\subsection{Maximum Unqualified Cardinality Restrictions*}
+
+\subsection{Maximum Qualified Cardinality Restrictions*}
+
+\subsection{Exact Unqualified Cardinality Restrictions*}
+
+\subsection{Exact Qualified Cardinality Restrictions*}
+
+An \emph{exact cardinality restriction}\footnote{{\em R-74-EXACT-QUALIFIED-CARDINALITY-ON-PROPERTIES}, {\em R-211-CARDINALITY-CONSTRAINTS}} contains all those individuals that are connected by a property to exactly n different individuals that are instances of a particular class or data range.
+If the class is missing, it is taken to be \emph{owl:Thing}. 
+If the data range is not present, it is taken to be \emph{rdfs:Literal}.
+$\geq n R. C \sqcap \leq n R. C $ is an exact qualified cardinality restriction where $n \in \mathbb{N}$.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX:}}
+A {\em disco:Question} has exactly 1 {\em disco:universe} relationship to {\em disco:Universe}.
+
+\begin{DL}
+Question $\sqsubseteq$ $\geq$1 universe.Universe $\sqcap$ $\leq$1 universe.Universe \\
+\end{DL}
+\end{itemize}
+
+\subsection{Transitive Object Properties*}
+
+\subsection{Context-Specific Exclusive OR of Properties}
+
+\subsection{Context-Specific Exclusive OR of Property Groups}
+
+\emph{Exclusive or} is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
+Only one of multiple property groups leads to valid data\footnote{{\em R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC}}.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX:}}
+Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as DDI concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as DDI codes and categories), but not both.
+
+\begin{DL}
+Concept $\sqsubseteq$ ($\neg$ D $\sqcap$ C) $\sqcup$ (D $\sqcap$ $\neg$ C) \\ 
+D $\equiv$ A $\sqcap$ B \\
+A $\sqsubseteq$ $\geq$ 1 notation.string $\sqcap$ $\leq$ 1 notation.string \\
+B $\sqsubseteq$ $\geq$ 1 prefLabel.string $\sqcap$ $\leq$ 1 prefLabel.string \\
+C $\sqsubseteq$ $\geq$ 1 definition.string $\sqcap$ $\leq$ 1 definition.string \\
+\end{DL}
+\end{itemize}
+
+\subsection{Allowed Values}
+
+It is a common requirement to narrow down the value space of a property by an exhaustive enumeration of the valid values (both literals or resources). 
+This is often rendered in drop down boxes or radio buttons in user interfaces. 
+Allowed values\footnote{{\em R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS} and 
+{\em R-37-ALLOWED-VALUES-FOR-RDF-LITERALS}} for properties can be IRIs, IRIs (matching one or multiple patterns), (any) literals, literals of a list of allowed literals (e.g.
+'red' 'blue' 'green'), typed literals of one or multiple type(s) (e.g.
+xsd:string).
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX}}.
+{\em disco:CategoryStatistics} can only have {\em disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype {\em rdf:langString}.
+
+\begin{DL}
+CategoryStatistics $\equiv$ $\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString \\
+\end{DL}
+\end{itemize}
+
+\subsection{Not Allowed Values}
+
+A matching triple has any literal / object except those explicitly excluded\footnote{\emph{R-33-NEGATIVE-OBJECT-CONSTRAINTS}, \emph{R-200-NEGATIVE-LITERAL-CONSTRAINTS}}.
+
+\subsection{Literal Ranges}
+
+\emph{P1} is a data property (of an instance of class \emph{C1}) and its literal value must be between the range of [$V_{min}$,$V_{max}$]\footnote{{\em R-45-RANGES-OF-RDF-LITERAL-VALUES}}.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX:}}
+{\em disco:percentage} (domain: {\em disco:CategoryStatistics}) literals must be of the datatype {\em xsd:double} whose range should be restricted to be between 0 and 100 (not expressible in DL).
+\end{itemize}
+
+\subsection{Negative Literal Ranges}
+
+\subsection{Required Properties}
+
+\subsection{Optional Properties}
+
+\subsection{Repeatable Properties}
+
+\subsection{Negative Property Constraints}
+
+Instances of a specific class must not have some object property\footnote{\emph{R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS}, \emph{R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS}}.
+
+\subsection{Individual Equality*}
+
+\subsection{Functional Properties*}
+
+An \emph{object property functionality axiom}\footnote{\emph{R-57-FUNCTIONAL-OBJECT-PROPERTIES}} \emph{FunctionalObjectProperty( OPE )} states that the object property expression \emph{OPE} is functional — that is, for each individual \emph{x}, there can be at most one distinct individual \emph{y} such that \emph{x} is connected by \emph{OPE} to \emph{y}.
+Each such axiom can be seen as a syntactic shortcut for the following axiom: \emph{SubClassOf( owl:Thing ObjectMaxCardinality( 1 OPE ) )}.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX:}} for each \emph{rdfs:Resource x}, there can be at most one distinct \emph{rdfs:Resource y} such that \emph{x} is connected by \emph{adms:identifier} to \emph{y}.
+
+\begin{DL}
+$(\textsf{funct } \textsf{identifier})$
+\end{DL}
+\end{itemize}
+
+\tb{Achim, we created an open issue for DDI 4 how keys should be defined}
+
+\subsection{Inverse-Functional Properties*}
+
+An \emph{object property inverse functionality axiom}\footnote{\emph{R-58-INVERSE-FUNCTIONAL-OBJECT-PROPERTIES}} \emph{InverseFunctionalObjectProperty( OPE )} states that the object property expression \emph{OPE} is inverse-functional - that is, for each individual \emph{x}, there can be at most one individual \emph{y} such that \emph{y} is connected by \emph{OPE} with \emph{x}.
+Each such axiom can be seen as a syntactic shortcut for the following axiom: \emph{SubClassOf( owl:Thing ObjectMaxCardinality( 1 ObjectInverseOf( OPE ) ) )}.
+
+\subsection{Value Restrictions*}
+
+\emph{Individual Value Restrictions}\footnote{\emph{R-88-VALUE-RESTRICTIONS}}: A has-value class expression \emph{ObjectHasValue( OPE a )} consists of an object property expression \emph{OPE} and an individual \emph{a}, and it contains all those individuals that are connected by \emph{OPE} to \emph{a}.
+Each such class expression can be seen as a syntactic shortcut for the class expression \emph{ObjectSomeValuesFrom( OPE ObjectOneOf( a ) )}.
+\emph{Literal Value Restrictions}: A has-value class expression \emph{DataHasValue( DPE lt )} consists of a data property expression \emph{DPE} and a literal \emph{lt}, and it contains all those individuals that are connected by \emph{DPE} to \emph{lt}.
+Each such class expression can be seen as a syntactic shortcut for the class expression \emph{DataSomeValuesFrom( DPE DataOneOf( lt ) )}.
+
+\subsection{Self Restrictions*}
+
+A \emph{self-restriction} \emph{ObjectHasSelf( OPE )} consists of an object property expression \emph{OPE}, and it contains all those individuals that are connected by \emph{OPE} to themselves.
+
+\subsection{Primary Key Properties}
+
+The \emph{Primary Key Properties} constraint is often useful to declare a given (datatype) property as the "primary key" of a class, so that a system can enforce uniqueness and also automatically build URIs from user input and data imported from relational databases or spreadsheets..
+Starfleet officers, e.g., are uniquely identified by their command authorization code (e.g. to activate and cancel auto-destruct sequences).
+It means that the property \emph{commandAuthorizationCode} is inverse functional - mapped to DL as follows:
+$(\ms{funct commandAuthorizationCode}\sp{\overline{\ }})$
+Keys, however, are even more general, i.e., a generalization of inverse functional properties \cite{Schneider2009}.
+A key can be a datatype property, an object property, or a chain of properties.
+For this generalization purposes, as there are different sorts of key, and as keys can lead to undecidability, 
+DL is extended with \emph{key boxes} and a special \emph{keyfor} construct\cite{Lutz2005}.
+This leads to the following DL mapping (only one simple property constraint):
+\ms{commandAuthorizationCode \ms{keyfor} StarfleetOfficer}
+
+\begin{itemize}
+	\item see \emph{functional properties}
+\end{itemize}
 
@@
 $\neg$Question $\sqsubseteq$ $\neg\exists$ questionText.langString
-\end{DL}
-
-\subsection{Context-Specific Exclusive OR of Property Groups}
-
-Exclusive or is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
-Only one of multiple property groups leads to valid data\footnote{{\em R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC}}.
-\textbf{{\em DISCO-C-XX:}}
-Within the context of Disco, skos:Concepts can have either skos:definition (when interpreted as DDI concepts) or skos:notation and skos:prefLabel properties (when interpreted as DDI codes and categories), but not both.
-
-\begin{DL}
-Concept $\sqsubseteq$ ($\neg$ D $\sqcap$ C) $\sqcup$ (D $\sqcap$ $\neg$ C) \\ 
-D $\equiv$ A $\sqcap$ B \\
-A $\sqsubseteq$ $\geq$ 1 notation.string $\sqcap$ $\leq$ 1 notation.string \\
-B $\sqsubseteq$ $\geq$ 1 prefLabel.string $\sqcap$ $\leq$ 1 prefLabel.string \\
-C $\sqsubseteq$ $\geq$ 1 definition.string $\sqcap$ $\leq$ 1 definition.string \\
-\end{DL}
-
-\subsection{Allowed Values}
-
-It is a common requirement to narrow down the value space of a property by an exhaustive enumeration of the valid values (both literals or resource). 
-This is often rendered in drop down boxes or radio buttons in user interfaces. 
-Allowed values for properties can be IRIs, IRIs (matching one or multiple patterns), (any) literals, literals of a list of allowed literals (e.g.
-'red' 'blue' 'green'), typed literals one or multiple type(s) (e.g.
-xsd:string)\footnote{{\em R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS} and
-{\em R-37-ALLOWED-VALUES-FOR-RDF-LITERALS}}.
-
-\textbf{{\em DISCO-C-XX}}.
-{\em disco:CategoryStatistics} can only have {\em disco:computationBase} relationships to the values 'valid' and 'invalid' of the datatype {\em rdf:langString}.
-
-\begin{DL}
-CategoryStatistics $\equiv$ \\ $\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString \\
 \end{DL}
@@
 To validate this constraint we bind the variables as follows (P1: {\em disco:startDate}, P2: {\em disco:endDate}, OP: \textless).
-
-\subsection{Literal Ranges}
-
-P1 is a data property (of an instance of class C1) and its literal value must be between the range of [$V_{min}$,$V_{max}$].
-\textbf{{\em DISCO-C-XX:}}
-{\em disco:percentage} (domain: {\em disco:CategoryStatistics}) literals must be of the datatype {\em xsd:double} whose range should be restricted to be between 0 and 100 (not expressible in DL)\footnote{{\em R-45-RANGES-OF-RDF-LITERAL-VALUES}}.
 
@@
 Check if literal values of the property {\em disco:startDate} are really of the datatype {\em xsd:date}(not expressible in DL).
-
-\subsection{Functional Properties}
 

### 2015-02-06 paper/paper7/paper7-appendix.tex
disco validation rules

@@
 
-\subsection{Class-Specific Property Ranges}
+\subsection{Class-Specific Property Range*}
 
-{\em Class-Specific Property Range} restricts the range of object and data properties for individuals within a specific context (e.g. class, shape, application profile).
-The values of each member property of a class may be limited by their value type, such as xsd:string or foaf:Person\footnote{{\em R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS} and {\em R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS}}.
-\textbf{{\em DISCO-C-XX:}} 
+{\em Class-Specific Property Range}\footnote{{\em R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS}, {\em R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS}} restricts the range of object and data properties for individuals within a specific context (e.g.
+class, shape, application profile).
+The values of each member property of a class may be limited by their value type, such as \emph{xsd:string} or \emph{foaf:Person}.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX:}} 
 Only {\em disco:Question}s can have {\em disco:questionText} relationships to literals of the datatype {\em rdf:langString}.
@@
 \end{DL}
+\end{itemize}
+
+\subsection{Class-Specific Reflexive Object Properties*}
+
+Using DL terminology \emph{Class-Specific Reflexive Object Properties} is called local reflexivity - a set of individuals (of a specific class) that are related to themselves via a given role \cite{Kroetzsch2012}.
 
@@
 
-Resources can only be members of listed controlled vocabularies\footnote{{\em R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES} and
+Resources can only be members of listed controlled vocabularies\footnote{{\em R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES}, 
 {\em R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES}}.
 
-\textbf{{\em DISCO-C-XX}}.
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX}}:
 {\em disco:SummaryStatistics} can only have {\em disco:summaryStatisticType} relationships to {\em skos:Concept}s which must be members of the controlled vocabulary {\em ddicv:SummaryStatisticType} which is a {\em skos:ConceptScheme}.
@@
 \begin{DL}
-SummaryStatistics $\sqsubseteq$ \\
-$\forall summaryStatisticType.Concept \sqcap \forall inScheme . A$ \\
-$A \equiv ConceptScheme \sqcap \{SummaryStatisticType\}$
+SummaryStatistics $\sqsubseteq$ $\forall summaryStatisticType.A$ \\
+$A \equiv Concept \sqcap \forall inScheme . B$ \\
+$B \equiv ConceptScheme \sqcap \{SummaryStatisticType\}$
 \end{DL}
+\end{itemize}
+
+\subsection{IRI Pattern Matching}
+
+IRI pattern matching applied on subjects, properties, and objects\footnote{\emph{R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS}, \emph{R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS}, \emph{R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES}}.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX}}: \emph{disco:Study} resources must match a given IRI pattern.
+\end{itemize}
 
@@
 a specific ordering with respect to an operator. 
-P1 and P2 are the datatype properties we need to compare and 
-OP is the comparison operator (\textless, \textless=, \textgreater, \textgreater=, =, !=)\footnote{{\em R-43-LITERAL-VALUE-COMPARISON}}.
-The {\em COMP Pattern}, one of the Data Quality Test Pattern, can be used to validate the {\em Literal Value Comparison} constraint \cite{Kontokostas2014}:
+\emph{P1} and \emph{P2} are the datatype properties we need to compare and 
+\emph{OP} is the comparison operator (\textless, \textless=, \textgreater, \textgreater=, =, !=)\footnote{{\em R-43-LITERAL-VALUE-COMPARISON}}.
+The {\em COMP Pattern}, one of the Data Quality Test Patterns, can be used to validate the {\em Literal Value Comparison} constraint \cite{Kontokostas2014}:
 
@@
 
-\textbf{{\em DISCO-C-XX}}.
-{\em disco:startDate}s must be before (‘\textless’) the {\em disco:endDate}s.
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-XX}}:
+{\em disco:startDate}s must be before (‘\textless’) {\em disco:endDate}s.
 To validate this constraint we bind the variables as follows (P1: {\em disco:startDate}, P2: {\em disco:endDate}, OP: \textless). 
+\end{itemize}
+
+\subsection{Ordering}
+
+With this constraint objects of object properties can be ordered as well as literals of data properties and objects of object properties\footnote{\emph{R-121-SPECIFY-ORDER-OF-RDF-RESOURCES}, \emph{R-217-DEFINE-ORDER-FOR-FORMS/DISPLAY}}.
+
+In DDI, variables, questions, and codes/categories are typically organized in a particular order. 
+For obtaining this order, {\em skos:OrderedCollection} resources are used.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-ORDERING-01}}: If \emph{disco:Variable}s of a given \emph{disco:LogicalDataSet} should be ordered, a collection of variables must be present in the data and connected with the data set.
+The collection of variables is of the type {\em skos:OrderedCollection} containing multiple variables (each represented as {\em skos:Concept}) in a {\em skos:memberList}.
+	\item \textbf{{\em DISCO-C-ORDERING-02}}: If \emph{disco:Question}s of a given \emph{disco:Questionnaire} should be ordered, a collection of questions must be present in the data and connected with the questionnaire.
+The collection of questions is of the type {\em skos:OrderedCollection} containing multiple questions (each represented as {\em skos:Concept}) in a {\em skos:memberList}.
+	\item \textbf{{\em DISCO-C-ORDERING-03}}: If codes/categories (\emph{skos:Concept}s) of a given \emph{disco:Representation} of a given \emph{disco:Variable} should be ordered, the variable representation should also be of the type {\em skos:OrderedCollection} containing multiple codes/categories (each represented as {\em skos:Concept}) in a {\em skos:memberList}.
+\end{itemize}
+
+\section{Validation Levels}
+
+Different levels of severity (priority)\footnote{\emph{R-205-VARYING-LEVELS-OF-ERROR}, \emph{R-135-CONSTRAINT-LEVELS}, \emph{R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS}, \emph{R-193-MULTIPLE-CONSTRAINT-VALIDATION-EXECUTION-LEVELS}} should be assigned to constraints.
+Possible validation levels could be: informational, warning, error, fail, should, recommended, must, may, optional, closed (only this) constraints, open (at least this) constraint.
+
+For \emph{Disco} each constraint should be assigned to exactly one \emph{validation level}.
+
+\section{String Operations}
+
+Many different \emph{string operations}\footnote{\emph{R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS}} are possible.
+Some constraints require building new strings out of other strings.
+Calculating the string length would also be another constraint of this type.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-STRING-OPERATIONS-01}}: The title of a study (\emph{dcterms:title}) (e.g.
+'EU-SILC 2005') may be calculated out of the title of the containing series (\emph{dcterms:title}) (e.g.
+'EU-SILC') and the human-readable label of the study (\emph{rdfs:label}) (e.g.
+'2005').
+\end{itemize}
+
+\subsection{Context-Specific Valid Classes}
+
+What types are valid in a specific context?\footnote{\emph{R-209-VALID-CLASSES}} 
+Context can be an input stream, a data creation function, or an API.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-CONTEXT-SPECIFIC-VALID-CLASSES-01}}: For future versions of \emph{Disco}, out-dated classes can be marked as deprecated.
+\end{itemize}
+
+\subsection{Context-Specific Valid Properties}
+
+What properties can be used within this context?\footnote{\emph{R-210-VALID-PROPERTIES}} 
+Context can be an data receipt function, data creation function, or API.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-CONTEXT-SPECIFIC-VALID-PROPERTIES-01}}: For future versions of \emph{Disco}, out-dated properties can be marked as deprecated.
+\end{itemize}
+
+\subsection{Default Values}
+
+\emph{Default values}\footnote{{\em R-31-DEFAULT-VALUES-OF-RDF-OBJECTS}, {\em R-38-DEFAULT-VALUES-OF-RDF-LITERALS}} for objects and literals are inferred automatically.
+It should be possible to declare the default value for a given property, e.g. so that input forms can be pre-populated and to insert a required property that is missing in a web service call.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-DEFAULT-VALUES-01:}}
+The value 'true' for the property {\em disco:isPublic} ({\em xsd:boolean}) indicates that the data set ({\em disco:LogicalDataSet}) can be accessed (usually downloaded) by anyone.
+Per default, access to data sets should be restricted ('false').
+\end{itemize}
 
@@
 
-Examples for {\em Mathematical Operations} are the addition of two dates, the addition of days to a start date, and statistical computations (e.g. average, mean, sum).
-\textbf{{\em DISCO-C-XX:}}
-The sum of {\em disco:percentage} {\em xsd:double} values of all codes (represented as {\em skos:Concept}s) of a code list ({\em skos:ConceptScheme} or {\em skos:OrderedCollection}), serving as representation of a particular {\em disco:Variable}, must exactly be 100
-(not expressible in DL)\footnote{{\em R-42-MATHEMATICAL-OPERATIONS} and {\em R-41-STATISTICAL-COMPUTATIONS}}.
+Examples for {\em Mathematical Operations}\footnote{{\em R-42-MATHEMATICAL-OPERATIONS}, {\em R-41-STATISTICAL-COMPUTATIONS}} are the addition of two dates, the addition of days to a start date, and statistical computations (e.g.
+average, mean, sum).
 
-\subsection{Default Values}
-
-Default values for objects and literals are inferred automatically.
-It should be possible to declare the default value for a given property, e.g.
-so that input forms can be pre-populated and to insert a required property that is missing in a web service call\footnote{{\em R-31-DEFAULT-VALUES-OF-RDF-OBJECTS} and {\em R-38-DEFAULT-VALUES-OF-RDF-LITERALS}}.
-\textbf{{\em DISCO-C-XX:}}
-The value 'true' for the property {\em disco:isPublic} ({\em xsd:boolean}) indicates that the data set ({\em disco:LogicalDataSet}) can be accessed (usually downloaded) by anyone.
-Per default, access to data sets should be restricted ('false').
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-MATHEMATICAL-OPERATIONS-01:}}
+The sum of {\em disco:percentage} (datatype: {\em xsd:double}) values of all codes (represented as {\em skos:Concept}s) of a code list ({\em skos:ConceptScheme} or {\em skos:OrderedCollection}), serving as representation of a particular {\em disco:Variable}, must exactly be 100.
+\end{itemize}
 
@@
 
-For particular data properties, values must be stated for predefined languages (not expressible in DL)\footnote{{\em R-47-LANGUAGE-TAG-MATCHING}}.
-\textbf{{\em DISCO-C-XX:}}
+For particular data properties, values must be stated for predefined languages\footnote{{\em R-47-LANGUAGE-TAG-MATCHING}}.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-LANGUAGE-TAG-MATCHING:}}
 There must be an English variable name ({\em skos:notation}) for each {\em disco:Variable} within {\em disco:LogicalDataSet}s.
+\end{itemize}
 
@@
 There should be at most one English literal value for variable names ({\em skos:notation}, domain: {\em disco:Variable}).
+
+\subsection{Whitespace Handling}
+
+\subsection{HTML Handling}
 
@@
 
+\subsection{Handle RDF Collections}
+
 \subsection{Value is Valid for Datatype}
@@
 Check if literal values of the property {\em disco:startDate} are really of the datatype {\em xsd:date}(not expressible in DL).
+
+\subsection{Exploiting Class/Property Specialization Ontology Axioms}
+
+\subsection{Cardinality Shortcuts*}
+
+\subsection{Aggregation}
 
@@
 \end{itemize}
-
-\subsection{Ordering}
-
-In DDI, variables, questions, and categories are typically organized in a particular order. 
-For obtaining this order, {\em skos:OrderedCollection} resources are used. 
-A collection of variables, e.g, is represented as being of the type {\em skos:OrderedCollection} containing multiple variables (each represented as {\em skos:Concept}) in a {\em skos:memberList}.
 

### 2015-02-06 paper/paper7/paper7-appendix.tex
disco validation rules

@@
 
-\section{Validation Levels}
+\subsection{Validation Levels}
 
@@
 
-\section{String Operations}
+\subsection{String Operations}
 
@@
 
-For particular data properties, values of predefined languages must be stated for determined number of times (not expressible in DL)
-\footnote{{\em R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG} and {\em R-48-MISSING-LANGUAGE-TAGS}}.
-\textbf{{\em DISCO-C-XX:}}
+For particular data properties, values of predefined languages must be stated for determined number of times\footnote{{\em R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG}, {\em R-48-MISSING-LANGUAGE-TAGS}}.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-LANGUAGE-TAG-CARDINALITY-01:}}
 There must be at least one English {\em disco:questionText} for each {\em disco:Question} within {\em disco:LogicalDataSet}s.
-\textbf{{\em DISCO-C-XX:}}
+  \item \textbf{{\em DISCO-C-LANGUAGE-TAG-CARDINALITY-02:}}
 There should be at most one English literal value for variable names ({\em skos:notation}, domain: {\em disco:Variable}).
+\end{itemize}
 
@@
 
+Avoid whitespaces in literals neither leading nor trailing white spaces\footnote{\emph{R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS}}.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-WHITESPACE-HANDLING-01:}} Delete whitespaces of series and study abstracts (\emph{dcterms:abstract}; domain: \emph{disco:StudyGroup}, \emph{disco:Study}) automatically.
+\end{itemize}
+
 \subsection{HTML Handling}
+
+Check if all HTML tags, included in literals (of specific data properties within the context of specific classes)\footnote{\emph{R-51-HTML-HANDLING-OF-RDF-LITERALS}}, are closed properly.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-HTML-HANDLING-01:}} Check if all HTML tags, included in literals of all \emph{Disco} data properties, are closed properly.
+	\item \textbf{{\em DISCO-C-HTML-HANDLING-02:}} Check if all HTML tags, included in literals of all data properties whose domains are \emph{Disco} classes, are closed properly.
+\end{itemize}
 
@@
 
-If specific properties exist, then specific other properties also have to be present\footnote{{\em R-71-CONDITIONAL-PROPERTIES}}.
-\textbf{{\em DISCO-C-XX:}}
-If a {\em skos:Concept represents a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
+If specific properties exist, then specific other properties must also be present\footnote{{\em R-71-CONDITIONAL-PROPERTIES}}.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-CONDITIONAL-PROPERTIES-01:}}
+If a {\em skos:Concept} represents a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
 then the property {\em disco:isValid} has to be stated indicating if the code is valid ('true') or missing ('false').
+\end{itemize}
 
@@
 
-Which properties are not required but recommended within a particular context\footnote{{\em R-72-RECOMMENDED-PROPERTIES}}.
-\textbf{{\em DISCO-C-XX:}}
-The property ({\em skos:notation} is not mandatory for {\em disco:Variable}s, but recommended to indicate variable names.
+Which properties are not necessarily required but recommended within a particular context\footnote{{\em R-72-RECOMMENDED-PROPERTIES}}.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-RECOMMENDED-PROPERTIES-01:}}
+The property {\em skos:notation} is not mandatory for {\em disco:Variable}s, but recommended to indicate variable names.
+\end{itemize}
 
 \subsection{Handle RDF Collections}
+
+Examples of the \emph{Handle RDF Collections}\footnote{\emph{R-120-HANDLE-RDF-COLLECTIONS}} constraint are: a collection must have a specific size; the first/last element of a given list must be a specific literal; the elements of collections are compared; are collections identical?; actions on RDF lists\footnote{See \url{http://www.snee.com/bobdc.blog/2014/04/rdf-lists-and-sparql.html}}; the 2.
+list element must be equal to 'XXX'; does the list have more than 10 elements?
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-HANDLE-RDF-COLLECTIONS-01}}: Have comparable \emph{disco:Variable}s the same number of codes in their code lists?
+	\item \textbf{{\em DISCO-C-HANDLE-RDF-COLLECTIONS-02}}: Does the actual number of \emph{disco:Variable}s within an (un)ordered collection of a given \emph{disco:LogicalDataSet} match the expected number?
+\end{itemize}
 
@@
 Make sure that a value is valid for its datatype.
-It has to be ensured, e.g., that a date is really a date, or that a xsd:nonNegativeInteger value is not negative. 
-\textbf{{\em DISCO-C-XX:}}
-Check if literal values of the property {\em disco:startDate} are really of the datatype {\em xsd:date}(not expressible in DL).
+It has to be ensured, e.g., that a date is really a date, or that a \emph{xsd:nonNegativeInteger} value is not negative.
 
-\subsection{Exploiting Class/Property Specialization Ontology Axioms}
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-VALUE-IS-VALID-FOR-DATATYPE-01}}: Check if all literal values of properties used within the \emph{Disco} context of the datatype {\em xsd:date} (e.g.
+{\em disco:startDate}, {\em disco:endDate}, {\em dcterms:date}) are really of the datatype {\em xsd:date}.
+\end{itemize}
+
+\subsection{Use Sub-Super Relations in Validation}
+
+\footnote{\emph{R-224-USE-SUB-SUPER-RELATIONS-IN-VALIDATION}}
+
+The validation of instances data (direct or indirect) exploits the sub-class or sub-property link in a given ontology.
+This validation can indicate when the data is verbose (redundant) or expressed at a too general level, and could be improved.
+If dcterms:date and one of its sub-properties dcterms:created or dcterms:issued are present, check that the value in dcterms:date is not redundant with dcterms:created or dcterms:issued for ingestion.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-USE-SUB-SUPER-RELATIONS-IN-VALIDATION-01}}: 
+	If one or more \emph{dcterms:coverage} properties are present, suggest the use of one of its sub-properties \emph{dcterms:spatial} or \emph{dcterms:temporal}.
+\end{itemize}
 

### 2015-02-06 paper/paper7/paper7-appendix.tex
disco validation rules

@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX:}} 
-All {\em disco:Universe}s must also be {\em skos:Concept}s:
-
-\begin{DL}
-Universe $\sqsubseteq$ Concept
-\end{DL}
+	\item \textbf{{\em DISCO-C-SUBSUMPTION-01:}} 
+All {\em disco:Universe}s must also be {\em skos:Concept}s (\ms{Universe $\sqsubseteq$ Concept}).
 \end{itemize}
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX:}}
-All {\em sio:SIO\_000367} resources must also be {\em disco:Variable}s:
-
-\begin{DL}
-Variable $\equiv$ SIO\_000367
-\end{DL}
-
+	\item \textbf{{\em DISCO-C-CLASS-EQUIVALENCE-01:}}
+All {\em sio:SIO\_000367} resources must also be {\em disco:Variable}s (\ms{Variable $\equiv$ SIO\_000367}).
 The Semanticscience Integrated Ontology (SIO)\footnote{https://code.google.com/p/semanticscience/wiki/SIO} provides a simple, integrated ontology of types and relations for rich description of objects, processes and their attributes.
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX:}}
-If an individual \emph{x} is connected by {\em disco:fundedBy} to an individual \emph{y}, then \emph{x} is also connected by {\em dcterms:contributor} to \emph{y}.
-
-\begin{DL}
-fundedBy $\sqsubseteq$ contributor 
-\end{DL}
+	\item \textbf{{\em DISCO-C-SUB-PROPERTIES-01:}}
+If an individual \emph{x} is connected by {\em disco:fundedBy} to an individual \emph{y}, then \emph{x} is also connected by {\em dcterms:contributor} to \emph{y} (\ms{fundedBy $\sqsubseteq$ contributor}).
 \end{itemize}
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX:}} 
-Only {\em disco:Question}s can have {\em disco:responseDomain} relationships.
-
-\begin{DL}
-$\exists$ responseDomain.$\top$ $\sqsubseteq$ Question 
-\end{DL}
+	\item \textbf{{\em DISCO-C-PROPERTY-DOMAIN-01:}} 
+Only {\em disco:Question}s can have {\em disco:responseDomain} relationships (\ms{$\exists$ responseDomain.$\top$ $\sqsubseteq$ Question}).
 \end{itemize}
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX:}} 
-{\em disco:caseQuantity} relationships can only point to literals of the datatype {\em xsd:nonNegativeInteger}.
-
-\begin{DL}
-$\top$ $\sqsubseteq$ $\forall$ caseQuantity.nonNegativeInteger \\
-\end{DL}
+	\item \textbf{{\em DISCO-C-PROPERTY-RANGES-01:}} 
+{\em disco:caseQuantity} relationships can only point to literals of the datatype {\em xsd:nonNegativeInteger} (\ms{$\top$ $\sqsubseteq$ $\forall$ caseQuantity.nonNegativeInteger}).
 \end{itemize}
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX:}} 
+	\item \textbf{{\em DISCO-C-ASYMMETRIC-OBJECT-PROPERTIES-01:}} 
 A {\em disco:Variable} may be based on a {\em disco:RepresentedVariable}.
 A {\em disco:RepresentedVariable}, however, cannot be based on a {\em disco:Variable}.
-This is a kind of mistake which may occur as a semantically equivalent object property for the other direction may also be possible ({\em disco:basisOf}).
-
-\begin{DL}
-$basedOn \sqcap basedOn^{-} \sqsubseteq \bot$ 
-\end{DL}
+This is a kind of mistake which may occur as a semantically equivalent object property for the other direction may also be possible ({\em disco:basisOf}) (\ms{$basedOn \sqcap basedOn^{-} \sqsubseteq \bot$}).
 \end{itemize}
@@
 \begin{itemize}
-  \item \textbf{{\em DISCO-C-XX:}}
-Within the Disco context, no individual is connected by the object property {\em instrument} to itself
-
-\begin{DL}
-$\top$ $\sqsubseteq$ $\neg$ $\exists  instrument . Self$ 
-\end{DL}
+  \item \textbf{{\em DISCO-C-IRREFLEXIVE-OBJECT-PROPERTIES-01:}}
+Within the Disco context, no individual is connected by the object property {\em instrument} to itself (\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists  instrument . Self$}).
 \end{itemize}
@@
 \begin{itemize}
-  \item \textbf{{\em DISCO-C-XX:}}
-Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:boader} to themselves
-
-\begin{DL}
-Concept $\sqsubseteq$ $\neg$$\exists$ broader.Self. 
-\end{DL}
-
-	\item \textbf{{\em DISCO-C-XX:}}
-Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:narrower} to themselves.
-
-\begin{DL}
-Concept $\sqsubseteq$ $\neg$$\exists$ narrower.Self. 
-\end{DL}
+  \item \textbf{{\em DISCO-C-CLASS-SPECIFIC-IRREFLEXIVE-OBJECT-PROPERTIES-01:}}
+Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:boader} to themselves (\ms{Concept $\sqsubseteq$ $\neg$$\exists$ broader.Self.}). 
+	\item \textbf{{\em DISCO-C-CLASS-SPECIFIC-IRREFLEXIVE-OBJECT-PROPERTIES-02:}}
+Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:narrower} to themselves (\ms{Concept $\sqsubseteq$ $\neg$$\exists$ narrower.Self.}). 
 \end{itemize}
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX:}} 
+	\item \textbf{{\em DISCO-C-DISJOINT-CLASSES-01:}} 
 All \emph{Disco} classes are defined to be pairwise disjoint.
-The following DL statements holds for each pair of Disco classes:
-
-\begin{DL}
-Study $\sqcap$ Variable $\sqsubseteq$ $\perp$\\
-\end{DL}
+The following DL statements holds for each pair of Disco classes (\ms{Study $\sqcap$ Variable $\sqsubseteq$ $\perp$}).
 \end{itemize}
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX:}} The abstract of a study (\emph{disco:purpose}) should have a minimum length (\emph{xsd:minInclusive}) of x. 
+	\item \textbf{{\em DISCO-C-DATA-PROPERTY-FACETS-01:}} The abstract of a study (\emph{disco:purpose}) should have a minimum length (\emph{xsd:minInclusive}) of x. 
 \end{itemize}
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX:}} Each \emph{disco:Variable} of a given \emph{disco:LogicalDataSet} must have a given prefix for its variable name (\emph{skos:notation}). 
+	\item \textbf{{\em DISCO-C-LITERAL-PATTERN-MATCHING-01:}} Each \emph{disco:Variable} of a given \emph{disco:LogicalDataSet} must have a given prefix for its variable name (\emph{skos:notation}). 
 \end{itemize}
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX:}} 
+	\item \textbf{{\em DISCO-C-NEGATIVE-LITERAL-PATTERN-MATCHING-01:}} 
 \end{itemize}
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX:}} 
+	\item \textbf{{\em DISCO-C-DISJUNCTION-01:}} 
 Only {\em disco:Variable}s or {\em disco:Question}s or {\em disco:RepresentedVariable}s can have {\em disco:concept} relationships to {\em skos:Concept}s.
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX:}} 
-There must be at least one {\em disco:universe} relationship from {\em disco:Studies} or {\em disco:StudyGroups} to {\em disco:Universe}.
-
-\begin{DL}
-Study $\sqcup$ StudyGroup $\sqsubseteq$ $\exists$ universe.Universe \\
-\end{DL}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-01:}} 
+There must be at least one {\em disco:universe} relationship from {\em disco:Studies} or {\em disco:StudyGroups} to {\em disco:Universe} (\ms{Study $\sqcup$ StudyGroup $\sqsubseteq$ $\exists$ universe.Universe}).
 \end{itemize}
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX:}}
-Only {\em disco:LogicalDataSet}s can have {\em disco:aggregation} relationships to {\em qb:DataSet}s.
-
-\begin{DL}
-LogicalDataSet $\sqsubseteq$ $\forall$ aggregation.DataSet \\
-\end{DL}
+	\item \textbf{{\em DISCO-C-UNIVERSAL-QUANTIFICATIONS-01:}}
+Only {\em disco:LogicalDataSet}s can have {\em disco:aggregation} relationships to {\em qb:DataSet}s (\ms{LogicalDataSet $\sqsubseteq$ $\forall$ aggregation.DataSet}).
 \end{itemize}
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX:}}
-A {\em disco:Questionnaire} has at least one {\em disco:question} relationship to {\em disco:Question}.
-
-\begin{DL}
-Questionnaire $\sqsubseteq$ $\geq$1 question.Question
-\end{DL}
+	\item \textbf{{\em DISCO-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
+A {\em disco:Questionnaire} has at least one {\em disco:question} relationship to {\em disco:Question} (\ms{Questionnaire $\sqsubseteq$ $\geq$1 question.Question}).
 \end{itemize}
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX:}}
-A {\em disco:Question} has exactly 1 {\em disco:universe} relationship to {\em disco:Universe}.
-
-\begin{DL}
-Question $\sqsubseteq$ $\geq$1 universe.Universe $\sqcap$ $\leq$1 universe.Universe \\
-\end{DL}
+	\item \textbf{{\em DISCO-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
+A {\em disco:Question} has exactly 1 {\em disco:universe} relationship to {\em disco:Universe} (\ms{Question $\sqsubseteq$ $\geq$1 universe.Universe $\sqcap$ $\leq$1 universe.Universe}).
 \end{itemize}
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX:}}
+	\item \textbf{{\em DISCO-C-CONTEXT-SPECIFIC-EXCLUSIVE-OR-OF-PROPERTY-GROUPS-01:}}
 Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as DDI concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as DDI codes and categories), but not both.
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX}}.
-{\em disco:CategoryStatistics} can only have {\em disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype {\em rdf:langString}.
-
-\begin{DL}
-CategoryStatistics $\equiv$ $\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString \\
-\end{DL}
+	\item \textbf{{\em DISCO-C-ALLOWED-VALUES-01}}.
+{\em disco:CategoryStatistics} can only have {\em disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype {\em rdf:langString} (\ms{CategoryStatistics $\equiv$ $\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString}).
 \end{itemize}
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX:}}
-{\em disco:percentage} (domain: {\em disco:CategoryStatistics}) literals must be of the datatype {\em xsd:double} whose range should be restricted to be between 0 and 100 (not expressible in DL).
+	\item \textbf{{\em DISCO-C-LITERAL-RANGES-01:}}
+{\em disco:percentage} (domain: {\em disco:CategoryStatistics}) literals must be of the datatype {\em xsd:double} whose range should be restricted to be between 0 and 100.
 \end{itemize}
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX:}} for each \emph{rdfs:Resource x}, there can be at most one distinct \emph{rdfs:Resource y} such that \emph{x} is connected by \emph{adms:identifier} to \emph{y}.
-
-\begin{DL}
-$(\textsf{funct } \textsf{identifier})$
-\end{DL}
+	\item \textbf{{\em DISCO-C-FUNCTIONAL-PROPERTIES-01:}} for each \emph{rdfs:Resource x}, there can be at most one distinct \emph{rdfs:Resource y} such that \emph{x} is connected by \emph{adms:identifier} to \emph{y} (\ms{$(\textsf{funct } \textsf{identifier})$}).
 \end{itemize}
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX:}} 
-Only {\em disco:Question}s can have {\em disco:questionText} relationships to literals of the datatype {\em rdf:langString}.
-
-\begin{DL}
-$\neg$Question $\sqsubseteq$ $\neg\exists$ questionText.langString
-\end{DL}
+	\item \textbf{{\em DISCO-C-CLASS-SPECIFIC-PROPERTY-RANGE-01:}} 
+Only {\em disco:Question}s can have {\em disco:questionText} relationships to literals of the datatype {\em rdf:langString} (\ms{$\neg$Question $\sqsubseteq$ $\neg\exists$ questionText.langString}).
 \end{itemize}
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX}}:
+	\item \textbf{{\em DISCO-C-MEMBERSHIP-IN-CONTROLLED-VOCABULARIES-01}}:
 {\em disco:SummaryStatistics} can only have {\em disco:summaryStatisticType} relationships to {\em skos:Concept}s which must be members of the controlled vocabulary {\em ddicv:SummaryStatisticType} which is a {\em skos:ConceptScheme}.
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX}}: \emph{disco:Study} resources must match a given IRI pattern.
+	\item \textbf{{\em DISCO-C-IRI-PATTERN-MATCHING}}: \emph{disco:Study} resources must match a given IRI pattern.
 \end{itemize}
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-XX}}:
+	\item \textbf{{\em DISCO-C-LITERAL-VALUE-COMPARISON-01}}:
 {\em disco:startDate}s must be before (‘\textless’) {\em disco:endDate}s.
@@
 This validation can indicate when the data is verbose (redundant) or expressed at a too general level, and could be improved.
-If dcterms:date and one of its sub-properties dcterms:created or dcterms:issued are present, check that the value in dcterms:date is not redundant with dcterms:created or dcterms:issued for ingestion.
+If \emph{dcterms:date} and one of its sub-properties \emph{dcterms:created} or \emph{dcterms:issued} are present, e.g., check that the value in \emph{dcterms:date} is not redundant with \emph{dcterms:created} or \emph{dcterms:issued} for ingestion.
 
@@
 	If one or more \emph{dcterms:coverage} properties are present, suggest the use of one of its sub-properties \emph{dcterms:spatial} or \emph{dcterms:temporal}.
+	\item \textbf{{\em DISCO-C-USE-SUB-SUPER-RELATIONS-IN-VALIDATION-02}}: 
+	If the \emph{dcterms:contributor} property is present, suggest the use of one of its sub-properties, e.g. \emph{disco:fundedBy}.
 \end{itemize}
@@
 
+In most library applications, cardinality shortcuts tend to appear in pairs, with repeatable/non-repeatable establishing maximum cardinality and optional/mandatory establishing minimum cardinality.
+These are shortcuts for more detailed \emph{cardinality restrictions}.
+
 \subsection{Aggregation}
 
+Some constraints require aggregating multiple values, especially via \emph{COUNT}, \emph{MIN} and \emph{MAX}.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-AGGREGATION-01}}: calculate the number of theoretical concepts in the thematic classification of a given study.
+  \item \textbf{{\em DISCO-C-AGGREGATION-02}}: calculate the number of variables of a data set.
+	\item \textbf{{\em DISCO-C-AGGREGATION-03}}: calculate the number of questions in a given questionnaire.
+	\item \textbf{{\em DISCO-C-AGGREGATION-04}}: the number of codes of a given variable must be below a maximum value.
+	\item \textbf{{\em DISCO-C-AGGREGATION-05}}: the number of questions of a given questionnaire must exactly be a given value.
+	\item \textbf{{\em DISCO-C-AGGREGATION-06}}: the cumulative percentage of all codes of a given variable must be 100.
+  \item \textbf{{\em DISCO-C-AGGREGATION-07}}: the absolute frequency of all valid codes of a given variable must be equal to a given value.
+\end{itemize}
+
+\section{SKOS-Related RDF Validation Requirements / Constraint Types}
+\tb{from other paper of Antoine}
 \subsection{Hierarchies}
 
-Hierarchies of DDI concepts
-
 \begin{itemize}
-	\item root?
+	\item \textbf{{\em DISCO-C-HIERARCHIES-01}}: there must be exactly one root in the hierarchy of DDI concepts. 
 \end{itemize}

### 2015-02-07 paper/paper7/paper7-appendix.tex
Data Cube validation rules

@@
 \usepackage{scrextend}
+
+% colors
+\usepackage[usenames, dvipsnames]{color}
+
+% underline
+\usepackage{tikz}
+\newcommand{\udensdot}[1]{%
+    \tikz[baseline=(todotted.base)]{
+        \node[inner sep=1pt,outer sep=0pt] (todotted) {#1};
+        \draw[densely dotted] (todotted.south west) -- (todotted.south east);
+    }%
+}%
+
+\newcommand{\uloosdot}[1]{%
+    \tikz[baseline=(todotted.base)]{
+        \node[inner sep=1pt,outer sep=0pt] (todotted) {#1};
+        \draw[loosely dotted] (todotted.south west) -- (todotted.south east);
+    }%
+}%
+
+\newcommand{\udash}[1]{%
+    \tikz[baseline=(todotted.base)]{
+        \node[inner sep=1pt,outer sep=0pt] (todotted) {#1};
+        \draw[dashed] (todotted.south west) -- (todotted.south east);
+    }%
+}%
+
+\newcommand{\udensdash}[1]{%
+    \tikz[baseline=(todotted.base)]{
+        \node[inner sep=1pt,outer sep=0pt] (todotted) {#1};
+        \draw[densely dashed] (todotted.south west) -- (todotted.south east);
+    }%
+}%
+
+\newcommand{\uloosdash}[1]{%
+    \tikz[baseline=(todotted.base)]{
+        \node[inner sep=1pt,outer sep=0pt] (todotted) {#1};
+        \draw[loosely dashed] (todotted.south west) -- (todotted.south east);
+    }%
+}%
 
@@
 %
-\title{RDF Validation of Metadata \\ on Highly-Complex Person-Level Data}
+\title{RDF Constraint Types to Validate Metadata \\ on Highly-Complex Person-Level and Aggregated Data}
 \subtitle{}
@@
 They recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which they explain each requirement (constraint type) in detail and give examples for each (represented by listed constraint languages) \cite{BoschNolleAcarEckert2015}.
-
-\section{Validation of Metadata on Person-Level Data Sets}
-
 We state at least one Disco constraint for the majority of the constraint types.
 Where appropriate constraint types are related to complementary requirements of the RDF validation requirements database.
-Constraint types marked with an asterisk can be used as OWL 2 axioms.
-Thus, reasoners may be used to infer implicit triples resolving constraint violations caused when these constraints are validated.
 When constraint types are mapped to DL, we do not state namespace prefixes for simplicity reasons.
 
-\subsection{Data Model Consistency}
+\section{Validation Types}
 
+\textbf{Content-Driven Validation / Data Model Consistency}.
 Is the data consistent with the intended semantics of the data model?
 Such validation rules ensure the integrity of the data according to the data model.
+
+\textbf{Technology-Driven Validation}.
+Some validation rules can be generated automatically out of the defined data model, such as cardinality restrictions, universal quantifications, domains, ranges.
+
+\section{Validation of Metadata on Person-Level and Aggregated Data}
+
+\begin{itemize}
+  \item Constraint types marked with an asterisk (*) can be used as OWL 2 axioms.
+Thus, reasoners may be used to infer implicit triples resolving constraint violations caused when these constraints are validated.
+	\item \underline{Underlined subsections} are data  model specific constraint types and do not correspond to RDF validation requirements (constraint types).
+%	\item \underline{Underlined constraints} are part of content-driven validation.
+%	\item \udash{Dashed underlined constraints} are part of technology-driven validation.
+\end{itemize}
+
+\subsection{\underline{Comparison}}
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-01}}: 
+	are compared variables represented in a compatible way, i.e. are the variables' code lists theoretically comparable?
+	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-02}}: 
+	are variable definitions (\emph{dcterms:description}) available for each variable (\emph{disco:Variable}) to compare?
+	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-03}}:
+	are code lists structured properly for each variable (\emph{disco:Variable}) to compare?
+	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-04}}:
+	is for each code (for each variable (\emph{disco:Variable}) to compare) an associated category (a human-readable label) specified?
+\end{itemize}
+
+\subsection{\underline{Data Model Consistency}}.
+Is the data consistent with the intended semantics of the data model?
+Such validation rules ensure the integrity of the data according to the data model.
+
+\begin{itemize}
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-01:}}
+	Only attributes may be optional (\emph{IC-6} \cite{CyganiakReynolds2014}) - 
+	The only components of a \emph{qb:DataStructureDefinition} that may be marked as optional, using \emph{qb:componentRequired} are attributes. 
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-02:}}
+	No duplicate observations (\emph{IC-12} \cite{CyganiakReynolds2014}) - 
+	No two \emph{qb:Observations} in the same \emph{qb:DataSet} may have the same value for all dimensions. 
+\end{itemize}
 
@@
 
+\begin{itemize}
+	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-01:}}
+	Dimensions have range (\emph{IC-4} \cite{CyganiakReynolds2014}) - 
+	Every dimension declared in a \emph{qb:DataStructureDefinition} must have a declared \emph{rdfs:range}. 
+	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-02:}}
+	Concept dimensions have code lists (\emph{IC-5} \cite{CyganiakReynolds2014}) - 
+	Every dimension with range \emph{skos:Concept} must have a \emph{qb:codeList}. 
+	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-03:}} 
+	Slice dimensions complete (\emph{IC-10} \cite{CyganiakReynolds2014}) - 
+	Every \emph{qb:Slice} must have a value for every dimension declared in its \emph{qb:sliceStructure}. 
+	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-04:}}
+	All dimensions required (\emph{IC-11} \cite{CyganiakReynolds2014}) - 
+	Every \emph{qb:Observation} has a value for each dimension declared in its associated \emph{qb:DataStructureDefinition}. 
+  \item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-05:}}
+	DSD includes measure (\emph{IC-3} \cite{CyganiakReynolds2014}) -  
+	Every \emph{qb:DataStructureDefinition} must include (\emph{qb:component}, \emph{qb:componentProperty}) at least one declared measure. 
+	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-06:}}
+	Slice Keys must be declared (\emph{IC-7} \cite{CyganiakReynolds2014}) -
+	Every \emph{qb:SliceKey} must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition}. 
+\end{itemize}
+
 \subsection{Universal Quantifications*}
@@
 
+An \emph{exact cardinality restriction}\footnote{{\em R-80-EXACT-UNQUALIFIED-CARDINALITY-ON-PROPERTIES}, {\em R-211-CARDINALITY-CONSTRAINTS}} contains all those individuals that are connected by a property to exactly n different individuals that are instances of a particular class or data range.
+If the class is missing, it is taken to be \emph{owl:Thing}. 
+If the data range is not present, it is taken to be \emph{rdfs:Literal}.
+Unqualified means that the class respective data range is not stated. 
+$\geq n R. \top \sqcap \leq n R. \top $ is an exact unqualified cardinality restriction where $n \in \mathbb{N}$.
+
+\begin{itemize}
+	\item \textbf{{\em DATA-CUBE-C-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
+	Unique slice structure (\emph{IC-9} \cite{CyganiakReynolds2014}) -  
+	Each \emph{qb:Slice} must have exactly one associated \emph{qb:sliceStructure}. 
+\end{itemize}
+
 \subsection{Exact Qualified Cardinality Restrictions*}
@@
 A {\em disco:Question} has exactly 1 {\em disco:universe} relationship to {\em disco:Universe} (\ms{Question $\sqsubseteq$ $\geq$1 universe.Universe $\sqcap$ $\leq$1 universe.Universe}).
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
+	Unique data set (\emph{IC-1} \cite{CyganiakReynolds2014}) -  
+	Every \emph{qb:Observation} has (\emph{qb:dataSet}) exactly one associated \emph{qb:DataSet}. 
+	\item \textbf{{\em DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02:}}
+	Unique DSD (\emph{IC-2} \cite{CyganiakReynolds2014}) -  
+	Every \emph{qb:DataSet} has (\emph{qb:structure}) exactly one associated \emph{qb:DataStructureDefinition}. 
 \end{itemize}
@@
 \end{DL}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em DATA-CUBE-C-MEMBERSHIP-IN-CONTROLLED-VOCABULARIES-01:}}
+	Codes from code list (\emph{IC-19} \cite{CyganiakReynolds2014}) - 
+	If a dimension property has a \emph{qb:codeList}, then the value of the dimension property on every \emph{qb:Observation} must be in the code list. 
 \end{itemize}

### 2015-02-08 paper/paper7/paper7-appendix.tex
Data Cube integrity constraints

@@
 	No two \emph{qb:Observations} in the same \emph{qb:DataSet} may have the same value for all dimensions. 
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-03:}}
+	Slice Keys consistent with DSD (\emph{IC-8} \cite{CyganiakReynolds2014}) -
+	Every \emph{qb:componentProperty} on a \emph{qb:SliceKey} must also be declared as a \emph{qb:component} of the associated \emph{qb:DataStructureDefinition}. 
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-04:}}
+	Required attributes (\emph{IC-13} \cite{CyganiakReynolds2014}) -
+	Every \emph{qb:Observation} has a value for each declared attribute that is marked as required. 
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05:}}
+	All measures present (\emph{IC-14} \cite{CyganiakReynolds2014}) -
+	In a \emph{qb:DataSet} which does not use a Measure dimension then each individual \emph{qb:Observation} must have a value for every declared measure. 
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-06:}}
+	Measure dimension consistent (\emph{IC-15} \cite{CyganiakReynolds2014}) -
+	In a \emph{qb:DataSet} which uses a Measure dimension then each qb:Observation must have a value for the measure corresponding to its given \emph{qb:measureType}. 
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-07:}}
+	Single measure on measure dimension observation (\emph{IC-16} \cite{CyganiakReynolds2014}) -
+	In a \emph{qb:DataSet} which uses a Measure dimension then each \emph{qb:Observation} must only have a value for one measure (by \emph{IC-15} this will be the measure corresponding to its \emph{qb:measureType}).
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-08:}}
+	All measures present in measures dimension cube (\emph{IC-17} \cite{CyganiakReynolds2014}) -
+	In a \emph{qb:DataSet} which uses a Measure dimension then if there is a Observation for some combination of non-measure dimensions then there must be other Observations with the same non-measure dimension values for each of the declared measures.
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-09:}}
+	Consistent data set links (\emph{IC-18} \cite{CyganiakReynolds2014}) -
+	If a \emph{qb:DataSet} \emph{D} has a \emph{qb:slice} \emph{S}, and \emph{S} has an \emph{qb:observation} \emph{O}, then the \emph{qb:dataSet} corresponding to \emph{O} must be \emph{D}. 
 \end{itemize}
@@
 
+\begin{itemize}
+	\item \textbf{{\em DATA-CUBE-C-VALUE-IS-VALID-FOR-DATATYPE-01:}}
+	Datatype consistency (\emph{IC-0} \cite{CyganiakReynolds2014}) -  
+	The RDF graph must be consistent under RDF D-entailment using a datatype map containing all the datatypes used within the graph. 
+\end{itemize}
+
 \subsection{Use Sub-Super Relations in Validation}
@@
 
-\section{SKOS-Related RDF Validation Requirements / Constraint Types}
-\tb{from other paper of Antoine}
-\subsection{Hierarchies}
+\subsection{\underline{Hierarchies}}
 
@@
 
+\begin{itemize}
+	\item \textbf{{\em DATA-CUBE-C-HIERARCHIES-01:}}
+	Codes from hierarchy (\emph{IC-20} \cite{CyganiakReynolds2014}) -  
+	If a dimension property has a \emph{qb:HierarchicalCodeList} with a non-blank \emph{qb:parentChildProperty} then the value of that dimension property on every \emph{qb:Observation} must be reachable from a root of the hierarchy using zero or more hops along the \emph{qb:parentChildProperty} links.
+	\item \textbf{{\em DATA-CUBE-C-HIERARCHIES-02:}}
+	Codes from hierarchy (inverse) (\emph{IC-21} \cite{CyganiakReynolds2014}) -  
+	If a dimension property has a \emph{qb:HierarchicalCodeList} with an inverse \emph{qb:parentChildProperty} then the value of that dimension property on every \emph{qb:Observation} must be reachable from a root of the hierarchy using zero or more hops along the inverse \emph{qb:parentChildProperty} links.
+\end{itemize}
+
+\section{SKOS-Related RDF Validation Requirements / Constraint Types}
+\tb{from other paper of Antoine}
+
 \section{Validation in Combination with other Vocabularies}
@@
 \subsection{RDF Data Cube Vocabulary}
-
-There are 22 RDF Data Cube integrity constraints\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf} \cite{CyganiakReynolds2014}.
-
-\begin{itemize}
-	\item \textcolor{blue}{describe 1 constraint of each type in detail with Datalog query}
-\end{itemize}
-
-\textbf{Data Model Consistency.}
-{\em IC-0}, \textcolor{red}{{\em IC-8}}, {\em IC-13}, {\em IC-14}, {\em IC-15}, {\em IC-16}, {\em IC-17}, \textcolor{red}{{\em IC-18}}
-%\begin{itemize}
-	%\item {\em IC-0:} Datatypes must be consistent under RDF D-entailment using a datatype map containing all the datatypes used within the graph.
-	%\item \textcolor{red}{{\em IC-8:} Every {\em qb:componentProperty} on a {\em qb:SliceKey} must also be declared as a {\em qb:component} of the associated {\em qb:DataStructureDefinition}.} 
-%\end{itemize}
-
-\textbf{Unqualified Cardinality Restrictions.}
-{\em IC-4}, {\em IC-5}, {\em IC-10}, {\em IC-11}
-%\begin{itemize}
-	%\item {\em IC-4:} Every dimension declared in a {\em qb:DataStructureDefinition} must have a declared {\em rdfs:range}. 
-	%\item {\em IC-5:} Every dimension with range {\em skos:Concept} must have a {\em qb:codeList}. 
-	%\item {\em IC-10:} Every {\em qb:Slice} must have a value for every dimension declared in its {\em qb:sliceStructure}. 
-	%\item {\em IC-11:} All dimensions required - Every {\em qb:Observation} has a value for each dimension declared in its associated {\em qb:DataStructureDefinition}.
-%\end{itemize}
-
-\textbf{Qualified Cardinality Restrictions.}
-{\em IC-1}, {\em IC-2}, {\em IC-3}, {\em IC-6}, {\em IC-7}, {\em IC-9} 
-%\begin{itemize}
-	%\item {\em IC-1:} Every {\em qb:Observation} has exactly one associated {\em qb:DataSet}. 
-	%\item {\em IC-2:} Every {\em qb:DataSet} has exactly one associated {\em qb:DataStructureDefinition}. 
-	%\item {\em IC-3:} Every {\em qb:DataStructureDefinition} must include at least one declared measure. 
-	%\item {\em IC-6:} The only components of a {\em qb:DataStructureDefinition} that may be marked as optional, using {\em qb:componentRequired} are attributes. 
-	%\item {\em IC-7:} Every {\em qb:SliceKey} must be associated with a {\em qb:DataStructureDefinition}. 
-	%\item {\em IC-9:} Each {\em qb:Slice} must have exactly one associated {\em qb:sliceStructure}. 
-%\end{itemize}
-
-\textbf{Duplicate Detection.}
-{\em IC-12}
-%\begin{itemize}
-	%\item {\em IC-12:} No duplicate observations - No two {\em qb:Observations} in the same {\em qb:DataSet} may have the same value for all dimensions. 
-%\end{itemize}
-
-\textbf{Membership in Controlled Vocabularies.}
-\textcolor{red}{{\em IC-19}}
-
-\textbf{SKOS Hierarchies.}
-{\em IC-20}, {\em IC-21}
-
-%\textbf{Mandatory Properties.}
-
-%\textbf{Optional Properties.}
-
-\begin{itemize}
-	\item \textcolor{blue}{are there further constraints which can be described in this paper?}
-\end{itemize}
 

### 2015-02-08 paper/paper7/paper7.tex
disco validation rules
Data Cube integrity constraints

@@
 
+- Missy / DDI-RDF export / multiple concrete syntaxes / Triple store / content negotiation / reference implementation of the Disco data model / Missy data model is based in Disco data model
+
+- RDF validator
+
 \textbf{Validation of Data Cube instances.}
@@
 \textbf{RDF Data Cube Vocabulary.}
-A well-formed RDF Data Cube is an a RDF graph describing one or more instances of {\em qb:DataSet} for which each of the defined integrity constraints passes.
+A well-formed RDF Data Cube is an a RDF graph describing one or more instances of {\em qb:DataSet} for which each of the 22 defined integrity constraints\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf} passes.
 Each integrity constraint is expressed as narrative prose and, where possible, a SPARQL ASK query or query template. 

### 2015-02-08 paper/paper7/paper7-appendix.tex
constraint type descriptions

@@
 
-\subsection{\underline{Data Model Consistency}}.
+\subsection{\underline{Data Model Consistency}}
 Is the data consistent with the intended semantics of the data model?
@@
 
+In many cases, properties are used bi-directionally and then accessed in the inverse direction, e.g.
+parent $\equiv$ child$^{-}$.
+There should be a way to declare value type, cardinality etc of those inverse relations without having to declare a new property URI.
+The object property \emph{OP1} is an inverse\footnote{\emph{R-56-INVERSE-OBJECT-PROPERTIES}} of the object property \emph{OP2}. 
+Thus, if an individual \emph{x} is connected by \emph{OP1} to an individual \emph{y}, then \emph{y} is also connected by \emph{OP2} to \emph{x}, and vice versa.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-INVERSE-OBJECT-PROPERTIES-01}}:
+	\emph{disco:CategoryStatistics} resources are accessed from codes (\emph{skos:Concept}s) via \emph{disco:statisticsCategory}$^{-}$.
+	\item \textbf{{\em DISCO-C-INVERSE-OBJECT-PROPERTIES-02}}:
+	\emph{disco:SummaryStatistics} resources are accessed from \emph{disco:Variable}s via \emph{disco:statisticsVariable}$^{-}$.
+	\item \textbf{{\em DISCO-C-INVERSE-OBJECT-PROPERTIES-03}}:
+	\emph{disco:Variable}s are accessed from \emph{disco:Question}s via \emph{disco:question}$^{-}$.
+\end{itemize}
+
 \subsection{Symmetric Object Properties*}
+
+A role is symmetric if it is equivalent to its own inverse \cite{Kroetzsch2012}.
+An object property symmetry axiom\footnote{\emph{R-61-SYMMETRIC-OBJECT-PROPERTIES}} states that the object property expression \emph{OPE} is symmetric - that is, if an individual \emph{x} is connected by \emph{OPE} to an individual \emph{y}, then \emph{y} is also connected by \emph{OPE} to \emph{x}.
 
@@
 
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-DISJOINT-PROPERTIES-01:}} 
+All \emph{Disco} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
+The following DL statements holds for each pair of \emph{Disco} properties (not having the same domain and range classes) ($variable \sqsubseteq \neg question$).
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em DATA-CUBE-C-DISJOINT-PROPERTIES-01:}} 
+All \emph{Data Cube} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
+The following DL statements holds for each pair of \emph{Data Cube} properties (not having the same domain and range classes) ($dataSet \sqsubseteq \neg structure$).
+\end{itemize}
+
 \subsection{Disjoint Classes}
@@
 
+\emph{Inclusive or} is a logical connective joining two or more predicates that yields the logical value "true" when at least one of the predicates is true.
+\emph{Context-Specific Inclusive OR of Properties}\footnote{\emph{R-202-CONTEXT-SPECIFIC-INCLUSIVE-OR-OF-PROPERTIES}} constraints specify that individuals are valid if they have at least one property relationship of one or multiple properties stated within a given context.
+The context can be an application profile, a shape, or a class, i.e., the constraint applies for individuals of this specific class.
+
 \subsection{Context-Specific Inclusive OR of Property Groups}
 
+At least one property group must match for individuals of a specific context. 
+Context may be a class, a shape, or an application profile.
+
 \subsection{Recursive Queries}
 
+Resource Shapes is a recursive language\footnote{\emph{R-222-RECURSIVE-QUERIES}} (the value shape of a Resource Shape is in turn another Resource Shape). 
+There is no way to express that in SPARQL without hand-waving "and then you call the function again here" or "and then you embed this operation here" text.  
+The embedding trick doesn't work
+in the general case because SPARQL can't express recursive queries,
+e.g. "test that this Issue is valid and all of the Issues that references, recursively".
+Most SPARQL engines already have
+functions that go beyond the official SPARQL 1.1 spec. 
+The cost of that sounds manageable.
+
 \subsection{Individual Inequality}
 
+An \emph{individual inequality axiom}\footnote{\emph{R-14-DISJOINT-INDIVIDUALS}} DifferentIndividuals( a$_1$ ...
+a$_n$ ) states that all of the individuals a$_i$, 1 $\leq$ i $\leq$ n, are different from each other;
+that is, no individuals a$_i$ and a$_j$ with i $\neq$ j can be derived to be equal. 
+This axiom can be used to axiomatize the unique name assumption — the assumption that all different individual names denote different individuals.
+
 \subsection{Equivalent Properties*}
 
+An \emph{equivalent object properties axiom}\footnote{\emph{R-4-EQUIVALENT-OBJECT-PROPERTIES}} \emph{EquivalentObjectProperties( OPE$_1$ ...
+OPE$_n$ )} states that all of the object property expressions \emph{OPE$_i$, 1 $\leq$ i $\leq$ n}, are semantically equivalent to each other.
+This axiom allows one to use each \emph{OPE$_i$} as a synonym for each \emph{OPE$_j$} — that is, in any expression in the ontology containing such an axiom, \emph{OPE$_i$} can be replaced with \emph{OPE$_j$} without affecting the meaning of the ontology.
+The axiom \emph{EquivalentObjectProperties( OPE$_1$ OPE$_2$ )} is equivalent to the following two axioms \emph{SubObjectPropertyOf( OPE$_1$ OPE$_2$ )} and \emph{SubObjectPropertyOf( OPE$_1$ OPE$_2$ )}.
+
+An \emph{equivalent data properties axiom}\footnote{\emph{R-5-EQUIVALENT-DATA-PROPERTIES}} \emph{EquivalentDataProperties( DPE$_1$ ...
+DPE$_n$ )} states that all the data property expressions \emph{DPE$_i$, 1 $\leq$ i $\leq$ n}, are semantically equivalent to each other.
+This axiom allows one to use each \emph{DPE$_i$} as a synonym for each \emph{DPE$_j$} — that is, in any expression in the ontology containing such an axiom, DPE$_i$ can be replaced with \emph{DPE$_j$} without affecting the meaning of the ontology.
+The axiom \emph{EquivalentDataProperties( DPE$_1$ DPE$_2$ )} can be seen as a syntactic shortcut for the following axiom \emph{SubDataPropertyOf( DPE$_1$ DPE$_2$ )} and \emph{SubDataPropertyOf( DPE$_1$ DPE$_2$ )}.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-EQUIVALENT-PROPERTIES-01:}}
+	Equivalent properties from different versions of \emph{Disco} can be marked as equivalent, e.g. \emph{disco:containsVariable} and \emph{disco:variable}. 
+	As a consequence, the properties can be replaced by each other without affecting the meaning.
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em DATA-CUBE-C-EQUIVALENT-PROPERTIES-01:}}
+	Equivalent properties from different versions of \emph{Data Cube} can be marked as equivalent. 
+	As a consequence, the properties can be replaced by each other without affecting the meaning.
+\end{itemize}
+
 \subsection{Property Assertions}
+
+\emph{{Property Assertions}}\footnote{\emph{R-96-PROPERTY-ASSERTIONS}}
+and includes positive property assertions and negative property assertions.
+A \emph{positive object property assertion ObjectPropertyAssertion( OPE a$_1$ a$_2$ )} states that the individual a$_1$ is connected by the object property expression \emph{OPE} to the individual a$_2$.
+A \emph{negative object property assertion NegativeObjectPropertyAssertion( OPE a$_1$ a$_2$ )} states that the individual a$_1$ is not connected by the object property expression \emph{OPE} to the individual a$_2$.
+A \emph{positive data property assertion DataPropertyAssertion( DPE a lt )} states that the individual a is connected by the data property expression DPE to the literal \emph{lt}. 
+A \emph{negative data property assertion NegativeDataPropertyAssertion( DPE a lt )} states that the individual a is not connected by the data property expression \emph{DPE} to the literal \emph{lt}.
 
@@
 \subsection{Negative Literal Pattern Matching}
+
+Literals of given data properties within given contexts do not have to match given patterns\footnote{\emph{R-44-PATTERN-MATCHING-ON-RDF-LITERALS}}.
 
@@
 
+Concept inclusions allow us to state that all mothers are female and that
+all mothers are parents, but what we really mean is that mothers are exactly the female
+parents. DLs support such statements by allowing us to form complex concepts such as
+the \emph{intersection}\footnote{\ms{R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS}, \ms{R-16-CONJUNCTION-OF-DATA-RANGES}} (also called \emph{conjunction})
+which denotes the set of individuals that are both female and parents. A complex concept
+can be used in axioms in exactly the same way as an atomic concept, e.g., in the
+equivalence Mother $\equiv$ Female $\sqcap$ Parent .
+
 \subsection{Disjunction*}
@@
 \subsection{Negation*}
+
+A \emph{complement class expression}\footnote{\emph{R-19-NEGATION-OF-CLASS-EXPRESSIONS}, \emph{R-20-NEGATION-OF-DATA-RANGES}} \emph{ObjectComplementOf( CE )} contains all individuals that are not instances of the class expression \emph{CE}.
 
@@
 
+A \emph{minimum cardinality restriction}\footnote{{\em R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}, {\em R-211-CARDINALITY-CONSTRAINTS}} contains all those individuals that are connected by a property to at least n different individuals/literals
+that are instances of a particular class or data range. If the class is missing, it is taken to be \emph{owl:Thing}. 
+If the data range is missing, it is taken to be \emph{rdfs:Literal}.
+$\leq n R. \top$ is the minimum unqualified cardinality restriction where $n \in \mathbb{N}$ (written $\leq  n R$ in short).
+For unqualified cardinality restrictions, classes respective data ranges are not stated.
+
 \subsection{Minimum Qualified Cardinality Restrictions*}
@@
 
+A \emph{maximum cardinality restriction} contains all those individuals that are connected by a property to at most n different individuals/literals that are instances of a particular class or data range.
+If the class is missing, it is taken to be \emph{owl:Thing}.
+If the data range is not present, it is taken to be \emph{rdfs:Literal}.
+Unqualified means that the class respective the data range is not stated. 
+$\geq n R.
+\top$ is a \emph{maximum unqualified cardinality restriction}\footnote{\emph{R-82-MAXIMUM-UNQUALIFIED-CARDINALITY-ON-PROPERTIES}, \emph{R-211-CARDINALITY-CONSTRAINTS}} where $n \in \mathbb{N}$ (written $\geq  n R$ in short).
+
 \subsection{Maximum Qualified Cardinality Restrictions*}
+
+A \emph{maximum cardinality restriction} contains all those individuals that are connected by a property to at most n different individuals/literals that are instances of a particular class or data range.
+If the class is missing, it is taken to be \emph{owl:Thing}.
+If the data range is not present, it is taken to be \emph{rdfs:Literal}.
+Qualified means that the class respective the data range is stated. 
+$\leq n R. C$ is a \emph{maximum qualified cardinality restriction}\footnote{\emph{R-76-MAXIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}, \emph{R-211-CARDINALITY-CONSTRAINTS}} where $n \in \mathbb{N}$.
 
@@
 \subsection{Individual Equality*}
+
+\emph{Individual equality}\footnote{\emph{R-6-EQUIVALENT-INDIVIDUALS}} states that two different names are known to refer to the same individual \cite{Kroetzsch2012}.
 

### 2015-02-09 paper/paper7/paper7-appendix.tex
constraint type descriptions

@@
 
+\emph{Transitivity} is a special form of \emph{complex role inclusion}.
+An \emph{object property transitivity axiom}\footnote{\emph{R-63-TRANSITIVE-OBJECT-PROPERTIES}} states that the object property is transitive — that is, if an individual \emph{x} is connected by the object property to an individual \emph{y} that is connected by the object property to an individual \emph{z}, then \emph{x} is also connected by the object property to \emph{z}.
+
 \subsection{Context-Specific Exclusive OR of Properties}
+
+\emph{Exclusive or} is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
+%In OWL 2, inclusive OR of properties would be possible to express, but not exclusive OR of data properties
+Only one of multiple properties within some context (e.g. a class, a shape, or an  application profile) leads to valid data\footnote{\emph{R-11-CONTEXT-SPECIFIC-EXCLUSIVE-OR-OF-PROPERTIES}}.
+This constraint is generally expressed in DL as follows: \ms{$C \sqsubseteq (\neg A \sqcap B) \sqcup (A \sqcap \neg B)$}.
 
@@
 
+\emph{P1} is a data property (of an instance of class \emph{C1}) and its literal value must not be between the range of [$V_{min}$,$V_{max}$]\footnote{{\em R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES}}.
+
 \subsection{Required Properties}
 
+Properties may be required\footnote{\emph{R-68-REQUIRED-PROPERTIES}}.
+
 \subsection{Optional Properties}
 
+Properties may be optional\footnote{\emph{R-69-OPTIONAL-PROPERTIES}}.
+
 \subsection{Repeatable Properties}
+
+Properties may be repeatable\footnote{\emph{R-70-REPEATABLE-PROPERTIES}}.
 

### 2015-02-09 paper/paper 2/paper 2.tex
introduction of paper 2

@@
 %
-\author{Thomas Bosch\inst{1} \and X\inst{2} \and X\inst{2} \and X\inst{2} \and Kai Eckert\inst{2}}
+\author{Thomas Bosch\inst{1} \and Erman Acar\inst{2} \and Kai Eckert\inst{2}}
 %
@@
 University of Mannheim, Germany \\
-\email{\{kai\}@informatik.uni-mannheim.de} 
+\email{\{erman,kai\}@informatik.uni-mannheim.de} 
 }
@@
 
+More and more domains adopt Linked Data principles
+and seek now for ways to ensure data quality by validating RDF data, as they are used to have this functionality in the XML world.
 For XML, XML Schema is the standard constraint language to validate XML documents.
 For RDF, however, there are multiple candidates for languages to express constraints on RDF data - but there is no standard language for RDF validation.
-W3C and DCMI working groups on RDF validation identified requirements to formulate and to validate RDF constraints.
-The majority of these constraints can be represented in description logics providing a logical underpinning of these constraints.
-We developed an ontology describing any RDF constraint generically (whether expressible in description logics or not).
-In parallel, we defined a basic terminology and a classification system for RDF constraints.
+We identified requirements to formulate and validate RDF constraints and mapped each requirement to a constraint type.
+The majority of these constraint types can be represented in description logics providing a logical underpinning.
 
-A constraint (expressed by constraint language \ms{$sc_{\alpha}$}) can be transformed to a constraint (expressed by constraint language \ms{$sc_{\beta}$}) by using the RDF constraint ontology as intermediate language.
-Currently, we cannot validate every constraint language or constraint of a constraint language.
-If we define a validation for a constraint generically and if we map semantically equivalent constraints (expressed by different constraint languages) to that generically expressed constraint, we are able to provide the validation of these constraints out of the box.
+In this paper, we provide a basic terminology and classification system for RDF constraint types,
+we developed a vocabulary describing any RDF constraint type generically (whether expressible in DL or not),
+we show how to transform \emph{specific constraints} (expressed by any constraint language \ms{$\alpha$}) into \emph{generic constraints} and \emph{specific constraints} (expressed by any other constraint language \ms{$\beta$}), and
+we explain how to provide the validation of any \emph{specific constraint} immediately and why this is important.
 
@@
 
-The purpose of ontologies is to perform reasoning on RDF data and not to validate RDF data conforming to these ontologies.
-For RDF, we cannot use ontologies like we use XML Schemas, DTDs, RELAX NG, or Schematron to validate XML documents.
-The W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
+The purpose of OWL 2 ontologies is to perform reasoning on RDF data and not to validate RDF data conforming to these ontologies.
+OWL 2 is based on the {\em non-unique name assumption} (nUNA) whereas RDF validation requires that different names represent different objects ({\em unique name assumption} (UNA)). 
+Reasoning in OWL 2 is based on the semantics of {\em open-world assumption} (OWA), i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose: to represent knowledge on the World Wide Web.
+On the other hand, many RDF validation scenarios require the {\em closed-world assumption} (CWA) (i.e., a statement is inferred to be false if it cannot be proved to be true).
+This ambiguity in semantics is one of the main reasons why OWL 2 has not been adopted as a standard constraint language for RDF validation.  
+For this reason, we cannot use OWL 2 ontologies for RDF validation as we use XML Schemas, DTDs, RELAX NG, or Schematron to validate XML documents.
+
+In 2013, the W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
 where experts from industry, government, and academia discussed first use cases for RDF constraint formulation and validation.
-In 2014, two working groups on RDF validation have been established: 
+In 2014, two working groups on RDF validation have been established to develop a language to express RDF constraints on RDF data: 
 the W3C RDF Data Shapes WG\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles WG\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}. 
-
 Bosch and Eckert \cite{BoschEckert2014} collected the findings of these working groups and initiated a database of requirements to formulate and validate RDF constraints
@@
 The intention associated with this database is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
-The requirements are classified to better evaluate existing solutions. 
-We mapped each requirement to formulate RDF constraints directly to an RDF constraint.
+The requirements are classified to better evaluate existing solutions and each requirement to formulate RDF constraints is directly mapped to an RDF constraint type.
+Bosch et al. identified in total 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
+They recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which they explain each requirement in detail and give examples for each (represented by different constraint languages) \cite{BoschNolleAcarEckert2015}.
+
+\tb{I copied this paragraph from the ESWC paper, we have to modify it a bit}
+Recently, RDF validation as a research field gained speed due to common needs of data practitioners.
+A typical example is the library domain that co-developed and adopted Linked Data principles very early.
+For libraries, the common description of resources are key business and they have a long tradition in developing and using interoperable data formats.
+While they embrace the openness of Linked Data and the data modeling principles provided by RDF, the data is still mostly represented in XML and this is unlikely to change soon.
+Among the reasons for the success of XML is the possibility to formulate fine-grained constraints to be met by the data and to validate the data according to these constraints using powerful systems like DTDs, XML Schemas, RELAX NG, or Schematron.
+A typical example is the definition of a library record describing a book.
+There are clear rules which information has to be available to describe a book properly (required fields, like a title), but also how information like an ISBN number is properly represented.
+Libraries seek to make their own data reusable for general purposes, but also to enrich and interlink their own data.
+Checking if third-party data meets own requirements or validating existing data according to new needs for a Linked Data application are among common use cases for RDF validation.
 
 There is no constraint language which can be seen as the standard.
-Although, there are multiple constraint languages (having different syntaxes and semantics) which can be used to express RDF constraints, such as existential and universal quantification, cardinality restrictions, and exclusive or of properties.
+Although, there are multiple constraint languages (having different syntaxes and semantics) which can be used to express RDF constraints (such as existential and universal quantification, cardinality restrictions, and exclusive or of properties).
 The five most promising ones on being the standard are
@@
 and the Web Ontology Language (OWL 2)\footnote{\url{http://www.w3.org/TR/owl2-syntax/}}.
-
 %\section{Ideas}
-
 %constraint design patterns:
@@
 % - constraint / constraint elements / constraint design patterns / constraint language
-
 %dependency between requirements / when this requirements is fulfilled then this is also fulfilled (e.g. min card and requ. car)
 %min car more powerful than req. propery
+The idea behind this paper is to express any constraint type (corresponding to a requirement to formulate RDF constraints) in a generic way using a lightweight ontology (consisting of only a few terms).
 
-\section{Motivation}
+Cardinality restrictions, e.g., can be expressed either generically (\emph{generic constraints}) by \emph{description logics (DL)} 
+%and extensions  
+or specifically (\emph{specific constraints}) by domain-specific constraint languages such as OWL 2, DSP, ShEx, ReSh, and SPIN.
+The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints generically. 
+For that reason, we map constraint types to DL statements.
+With minimum qualified cardinality restrictions, researchers from the library domain can state
+that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
+This constraint can be represented generically in DL as follows: \ms{Publication $\sqsubseteq$ $\geq$1 author.Person}.
+The same constraint may also be represented specifically by multiple constraint languages like OWL 2 and ShEx:
 
-Cardinality restrictions can be expressed either generically by description logics (DL) and extensions (\ms{generic constraints}) 
-or specifically  by domain-specific constraint languages such as OWL 2, DSP, ShEx, ReSh, and SPIN (\ms{specific constraints}).
-With minimum qualified cardinality restrictions we can state, 
-e.g., that a starfleet captain commands at least one vessel, which can generically be represented in DL:
+\begin{ex}
+# OWL 2:
+Publication
+    a owl:Restriction ;
+    owl:minQualifiedCardinality 1 ;
+    owl:onProperty author ;
+    owl:onClass Person .
 
-\begin{DL}
-$StarfleetCaptain \sqsubseteq \geq1 commandsVessel . Vessel $
-\end{DL}
+# ShEx:
+Publication { author @Person{1, } }
+\end{ex}
+
+As there is no standard way to formulate RDF constraints, 
+semantically equivalent cardinality restrictions may be represented by different constraint languages, which causes confusion and weakens the understanding how to ensure metadata quality between multiple parties.
+Therefore, when choosing constraint language \ms{$\alpha$} to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a constraint expressed by any other constraint language \ms{$\beta$}.
+This is important in order to enhance the interoperability of constraint languages and to simplify the communication of RDF data producers and consumers, 
+as constraint transformations resolve the necessity to read, write, and understand all languages used to express RDF constraints.
+
+There are validation environments enabling to validate RDF constraints expressed by just a few constraint languages such as OWL 2\footnote{\url{purl.org/net/rdfval-demo}\label{footnote1}}, DSP\footref{footnote1}, and ShEx\footnote{\url{http://www.w3.org/2013/ShEx/FancyShExDemo}}.
+But, it should be possible to validate any RDF constraints expressed by any constraint language and 
+what is even more important to validate them in exactly the same manner without any differences. 
+If we implement the validation of a \emph{generic constraint} and if we transform a \emph{specific constraint} into a \emph{generic constraint}, we are able to validate the \emph{specific constraint} immediately.
+As a consequence, we do not have to implement the validation for each \emph{specific constraint}, as we need to implement the validation only once for each \emph{generic constraint}.
+
+%When domain experts use graphical user interfaces to define constraints in a user-friendly way (without the necessity to express constraints on their own), 
+%constraints can be mapped to either a specific or a generic constraint, as for both the validation is provided in the background.    
+%So, the user does not have to know how to express specific constraints using any constraint language.
+
+Existing constraint languages can be extended and new constraint languages can be developed, if existing constraint languages are not sufficient to represent needed constraint types.
+If (1) a new constraint type is expressed generically, (2) the \emph{generic constraint type} is mapped to \emph{specific constraint types} (expressed by constraint languages), and (3) the validation is implemented for this particular \emph{generic constraint type},
+the validation of \emph{specific constraint types} is provided out of the box.
+As a consequence, constraint language designers do not have to implement the validation of their constraint languages and each semantically equivalent \emph{specific constraint type} is validated the same way (i.e.
+leading to identical validation results).
+
+This paper aims to address two main \textbf{audiences}:
+(1) RDF data providers and consumers seeking how to ensure high quality (meta)data and thus for ways to enhance the interoperability and communication of RDF constraints expressed by multiple constraint languages and
+(2) RDF practitioners thinking of how to implement the validation of existing an newly developed constraint languages.
+The \textbf{contributions} of this paper are:
+(1) We provide a basic terminology and classification system for RDF constraint types,
+(2) we developed a vocabulary describing any RDF constraint type generically (whether expressible in DL or not),
+(3) we show how to transform \emph{specific constraints} (expressed by any constraint language \ms{$\alpha$}) into \emph{generic constraints} and \emph{specific constraints} (expressed by any other constraint language \ms{$\beta$}), and
+(4) we explain how to provide the validation of any \emph{specific constraint} immediately. 
+%(if the validation is implemented once for the corresponding \emph{generic constraint type} to which the \emph{specific constraint type} is mapped)
+The remainder of the paper is as follows.
+
+%\begin{itemize}
+	%\item Any specific constraint (expressed by any constraint language) can be transformed into a generic constraint (expressed by the generic constraint language)
+	%\item Any specific constraint (expressed by any constraint language A) can be transformed into any specific constraint (expressed by any constraint language B)
+	%\item Any specific constraint (expressed by any constraint language) can be validated automatically (if an automatic validation is defined only once for corresponding generic constraint)
+	%\item We define a basic terminology and classification system for RDF constraints
+	%\item We developed an ontology describing any RDF constraint generically (whether expressible in DL or not)%which can also be expressed by any constraint language
+	%\item We present that any RDF constraint can be described by the developed ontology - whether the constraint can be expressed in DL or not 
+	%\item We show how to transform specific constraints (expressed by any constraint language \ms{$\alpha$}) into generic constraints and into specific constraints (expressed by any other constraint language \ms{$\beta$})
+  %\item We explain that any specific constraint can be validated automatically (if the validation is implemented only once for the corresponding generic constraint)
+%\end{itemize}
+
+%The \textbf{benefits} of our framework are:
+%\begin{itemize}
+	%\item Any specific constraint (expressed by any constraint language) can be transformed into a generic constraint (expressed by the generic constraint language)
+	%\item Any specific constraint (expressed by any constraint language A) can be transformed into any specific constraint (expressed by any constraint language B)
+	%\item Any specific constraint (expressed by any constraint language) can be validated automatically (if an automatic validation is defined only once for corresponding generic constraint)
+%\end{itemize}
+
+\section{include this in next section}
+
+With minimum qualified cardinality restrictions, researchers from the library domain can state
+that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
+This constraint can be represented generically in DL as follows: \ms{Publication $\sqsubseteq$ $\geq$1 author.Person}.
 
@@
 # OWL 2:
-StarfleetCaptain
+Publication
     a owl:Restriction ;
     owl:minQualifiedCardinality 1 ;
-    owl:onProperty commandsVessel ;
-    owl:onClass Vessel .
+    owl:onProperty author ;
+    owl:onClass Person .
 
 # ShEx:
-StarfleetCaptain { commandsVessel @Vessel{1, } }
+Publication { author @Person{1, } }
 
 # ReSh:
-StarfleetCaptain a rs:ResourceShape ; rs:property [
-    rs:name "commandsVessel" ; rs:propertyDefinition commandsVessel ;
-    rs:valueShape Vessel ;
+Publication a rs:ResourceShape ; rs:property [
+    rs:name "author" ; rs:propertyDefinition author ;
+    rs:valueShape Person ;
     rs:occurs rs:One-or-many ; ] .
@@
 [   a dsp:DescriptionTemplate ; 
-    dsp:resourceClass StarfleetCaptain ; 
+    dsp:resourceClass Publication ; 
     dsp:statementTemplate [ a dsp:NonLiteralStatementTemplate ;
         dsp:minOccur 1 ; dsp:maxOccur "infinity" ; 
-        dsp:property commandsVessel ; 
+        dsp:property author ; 
         dsp:nonLiteralConstraint [ a dsp:NonLiteralConstraint ;
-            dsp:valueClass Vessel ] ] ] .
+            dsp:valueClass Person ] ] ] .
 \end{ex}
@@
 
-As there is no standard way to formulate RDF constraints, 
-semantically equivalent cardinality restrictions may be represented by different constraint languages. 
-When choosing constraint language \ms{$\alpha$} to express an arbitrary constraint, it should be possible to transform this constraint into a constraint expressed by any other constraint language \ms{$\beta$}.
-This is important as it is often the case that producers and consumers of RDF data are able to read and to write constraints in constraint language \ms{$\alpha$} very well but not in another constraint language \ms{$\beta$}.
-This way, producers and consumers of RDF data may communicate with each other without the necessity to understand all constraint languages and the interoperability of constraint languages is enhanced.
+-----
 
-There are validation environments enabling to validate RDF constraints expressed by just a few constraint languages such as OWL 2\footnote{\url{purl.org/net/rdfval-demo}\label{footnote1}}, DSP\footref{footnote1}, and ShEx\footnote{\url{http://www.w3.org/2013/ShEx/FancyShExDemo}}.
-But, it should be possible to validate any RDF constraints expressed by any constraint language and 
-what is even more important to validate them in exactly the same manner without any differences. 
-If we implement the validation of a generic constraint and if we transform a specific constraint into a generic constraint, we are able to validate the specific constraint immediately. 
-As a consequence, we do not have to implement the validation for each specific constraint, as we need to implement the validation only once for each generic constraint. 
 The generically expressed cardinality restriction is validated within our validation environment (see section \ref{sec:validation}) by means of a SPARQL query:
@@
 \end{ex}
-
-When domain experts use graphical user interfaces to define constraints in a user-friendly way (without the necessity to express constraints on their own), 
-constraints can be mapped to either a specific or a generic constraint, as for both the validation is provided in the background.    
-So, the user does not have to know how to express specific constraints using any constraint language.
-If there is a new constraint not covered by any existing constraint language, one can just define the validation for the corresponding generic constraint.
-This way, one is able to extend existing constraint languages and to define new constraint languages if existing constraint languages are not sufficient to express particular constraints.
-If a language designer develops a new constraint language, 
-the language designer only needs to define a mapping to the developed ontology
-to be able to automatically validate the constraints expressible by the new constraint language out of the box.
-
-The \textbf{contributions} of this paper are:
-\begin{itemize}
-	%\item Any specific constraint (expressed by any constraint language) can be transformed into a generic constraint (expressed by the generic constraint language)
-	%\item Any specific constraint (expressed by any constraint language A) can be transformed into any specific constraint (expressed by any constraint language B)
-	%\item Any specific constraint (expressed by any constraint language) can be validated automatically (if an automatic validation is defined only once for corresponding generic constraint)
-	\item We define a basic terminology and classification system for RDF constraints
-	\item We developed an ontology describing any RDF constraint generically (whether expressible in DL or not)%which can also be expressed by any constraint language
-	%\item We present that any RDF constraint can be described by the developed ontology - whether the constraint can be expressed in DL or not 
-	\item We show how to transform specific constraints (expressed by any constraint language \ms{$\alpha$}) into generic constraints and into specific constraints (expressed by any other constraint language \ms{$\beta$})
-  \item We explain that any specific constraint can be validated automatically (if the validation is implemented only once for the corresponding generic constraint)
-\end{itemize}
-
-%The \textbf{benefits} of our framework are:
-%\begin{itemize}
-	%\item Any specific constraint (expressed by any constraint language) can be transformed into a generic constraint (expressed by the generic constraint language)
-	%\item Any specific constraint (expressed by any constraint language A) can be transformed into any specific constraint (expressed by any constraint language B)
-	%\item Any specific constraint (expressed by any constraint language) can be validated automatically (if an automatic validation is defined only once for corresponding generic constraint)
-%\end{itemize}
 

### 2015-02-10 paper/paper 2/paper 2.tex
running example

@@
 %min car more powerful than req. propery
-The idea behind this paper is to express any constraint type (corresponding to a requirement to formulate RDF constraints) in a generic way using a lightweight ontology (consisting of only a few terms).
+The idea behind this paper is to express any constraint type (corresponding to a requirement to formulate RDF constraints) in a generic way using a lightweight vocabulary (consisting of only a few terms).
 
@@
 
-\section{include this in next section}
+\section{Running Example}
 
-With minimum qualified cardinality restrictions, researchers from the library domain can state
-that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
-This constraint can be represented generically in DL as follows: \ms{Publication $\sqsubseteq$ $\geq$1 author.Person}.
-
-The same constraint may also be represented specifically by multiple constraint languages like OWL 2, ShEx, ReSh, or DSP:
+With minimum qualified cardinality restrictions, \emph{publications} can be enforced to have at least one \emph{author} which must be a \emph{person}.
+This constraint can be represented generically (\emph{generic constraint}) using DL (\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}), but also specifically (\emph{specific constraint}) by multiple constraint languages like OWL 2, ShEx, ReSh, or DSP:
 
@@
 
-As \ms{Janeway} commands the vessel \ms{Voyager} (\ms{commandsVessel(Janeway,Voyager)}) and \ms{Voyager} is a \ms{Vessel} (\ms{rdf:type(Voyager,Vessel)}), the assignment of \ms{Janeway} to the class \ms{StarfleetCaptain} (\ms{rdf:type(Janeway,StarfleetCaptain)}) does not cause a constraint violation.
-A constraint violation is raised, however, when there is not at least one \ms{commandsVessel} relationship with \ms{Janeway} as the subject. 
-A constraint violation is also raised, when there is a triple \ms{commandsVessel(Janeway,Voyager)}, but \ms{Voyager} is not explicitly defined to be a \ms{Vessel}, 
-i.e. the triple \ms{rdf:type(Voyager,Vessel)} is not present in the data. 
-As \ms{DS9 is not a} \ms{Vessel}, 
-the triples \ms{commandsVessel(Sisko,DS9)}, \ms{rdf:type(Sisko,StarfleetCaptain)}, and \ms{rdf:type(DS9,SpaceStation)}  
-also cause a constraint violation.
+As each \emph{publication} must have at least one \emph{author} relationship to a \emph{person} 
+and as the book \emph{The-Lord-Of-The-Rings} is a \emph{publication} \ms{rdf:type(The-Lord-Of-The-Rings, Publication)}, 
+\emph{The-Lord-Of-The-Rings} must have at least one \emph{author} relationship to a \emph{person}.
+If \emph{The-Lord-Of-The-Rings} has no \emph{author} relationship, a constraint violation is raised. 
+It leads to invalid data, if \emph{The-Lord-Of-The-Rings} has an \emph{author} property pointing to some resource which is assigned to another class than \emph{Person}
+(\ms{author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Human)}).
+It also causes a constraint violation, if \emph{The-Lord-Of-The-Rings} has an \emph{author} relation to an object for which no class is associated
+(\ms{author(The-Lord-Of-The-Rings, Tolkien)}).
+The data is valid, if \emph{The-Lord-Of-The-Rings} is connected to a \emph{person} via the object property \emph{author}
+(\ms{author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Person)}).
 
 The following table shows the mapping between the cardinality restriction expressed in DL 
-and the cardinality restriction expressed by our developed ontology to describe any RDF constraint generically (see section~\ref{sec:ontology}):
+and the cardinality restriction expressed by our developed vocabulary to describe any RDF constraint generically (see section~\ref{sec:ontology}):
 
 \begin{gcotable}
-property & StarfleetCaptain & commandsVessel & - & Vessel & $\geq$ & 1 \\
+property & Publication & author & - & Person & $\geq$ & 1 \\
 \end{gcotable}
 
-According to this ontology, each constraint is either a constraint on classes or a constraint on properties.
+According to this vocabulary, each constraint is either a constraint on classes or a constraint on properties.
 The generically expressed cardinality restriction is represented in RDF as follows:
@@
 [   a PropertyConstraint ;
-    contextClass StarfleetCaptain ;
-    leftProperties ( commandsVessel ) ;
-    classes ( Vessel ) ;
+    contextClass Publication ;
+    leftProperties ( author ) ;
+    classes ( Person ) ;
     constrainingElement ">=" ;
@@
 
------
-
-The generically expressed cardinality restriction is validated within our validation environment (see section \ref{sec:validation}) by means of a SPARQL query:
+Bosch and Eckert\cite{BoschEckert2014-2} use SPIN as basis to define a
+validation environment (available at \url{http://purl.org/net/rdfval-demo}) in which the validation of any constraint language\footnote{the only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL.
+The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.
+The generically expressed cardinality restriction above is validated within our validation environment (see section \ref{sec:validation}) by means of a SPARQL CONSTRUCT query:
 \begin{ex}
@@
 
-\section{Ontology to Describe RDF Constraints Generically} 
+\section{A Vocabulary to Describe RDF Constraints Generically} 
 \label{sec:ontology}
 
-In order to define an ontology to describe RDF constraints generically, it is needed to define the terminology for the formulation of RDF constraints and to classify them. 
+In order to define a vocabulary to describe RDF constraints generically, it is needed to define the terminology for the formulation of RDF constraints and to classify them. 
 A \ms{constraint language} is a language which is used to formulate constraints.
@@
 We rather developed a very simple ontology (only three classes, three object properties, and three data properties) which is universal enough to describe any RDF constraint expressible by any RDF constraint language (see the conceptual model in figure \ref{fig:RDF-CO-conceptual-model}).
-We call this ontology the \ms{RDF constraints ontology (RDF-CO)}\footnote{Available at: \url{https://github.com/boschthomas/RDF-constraints-ontology}}.
+We call this vocabulary the \ms{RDF constraints ontology (RDF-CO)}\footnote{Available at: \url{https://github.com/boschthomas/RDF-constraints-ontology}}.
 

### 2015-02-10 paper/paper7/paper7-appendix.tex
running example

@@
 $\exists R. \top \sqsubseteq C$ is the object property restriction where $R$ is the object property (role) whose domain is restricted to concept $C$.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-PROPERTY-DOMAIN-01:}} 
 	{\em Property Domain} constraints are defined for each \emph{Disco} object and data property.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-PROPERTY-DOMAIN-01:}} 
-Only {\em disco:Question}s can have {\em disco:responseDomain} relationships (\ms{$\exists$ responseDomain.$\top$ $\sqsubseteq$ Question}).
+  Only {\em disco:Question}s, e.g., can have {\em disco:responseDomain} relationships (\ms{$\exists$ responseDomain.$\top$ $\sqsubseteq$ Question}).
 \end{itemize}
@@
 	\item \textbf{{\em DISCO-C-PROPERTY-RANGES-01:}} 
-{\em disco:caseQuantity} relationships can only point to literals of the datatype {\em xsd:nonNegativeInteger} (\ms{$\top$ $\sqsubseteq$ $\forall$ caseQuantity.nonNegativeInteger}).
+	{\em Property Range} constraints are defined for each \emph{Disco} object and data property.
+  {\em disco:caseQuantity} relationships, e.g., can only point to literals of the datatype {\em xsd:nonNegativeInteger} (\ms{$\top$ $\sqsubseteq$ $\forall$ caseQuantity.nonNegativeInteger}).
 \end{itemize}

### 2015-02-10 paper/paper 2/paper 2.tex
section 3

@@
 
-In order to define a vocabulary to describe RDF constraints generically, it is needed to define the terminology for the formulation of RDF constraints and to classify them. 
-A \ms{constraint language} is a language which is used to formulate constraints.
-The W3C Data Shapes working group defines \ms{constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
-We identified four dimensions to classify constraints:
+In order to develop a vocabulary to describe any RDF constraint generically, it is needed to define the terminology for the formulation of RDF constraints and to classify them. 
+A \emph{constraint language} is a language which is used to formulate constraints.
+The W3C Data Shapes working group defines \emph{RDF constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
+We identified four dimensions to classify RDF constraints:
 \begin{itemize}
-  \item \ms{Universality:} specific constraints vs. generic constraints
-	\item \ms{Complexity:} simple constraints vs. complex constraints
-	\item \ms{Context:} property constraints vs. class constraints
-	\item \ms{DL Expressivity:} constraints expressible in DL vs. constraints not expressible in DL
+  \item \emph{Universality:} specific constraints vs. generic constraints
+	\item \emph{Complexity:} simple constraints vs. complex constraints
+	\item \emph{Context:} property constraints vs. class constraints
+	\item \emph{DL Expressivity:} constraints expressible in DL vs. constraints not expressible in DL
 \end{itemize}
@@
 As there are already five promising constraint languages, our purpose is not to invent a new constraint language.
-We rather developed a very simple ontology (only three classes, three object properties, and three data properties) which is universal enough to describe any RDF constraint expressible by any RDF constraint language (see the conceptual model in figure \ref{fig:RDF-CO-conceptual-model}).
-We call this vocabulary the \ms{RDF constraints ontology (RDF-CO)}\footnote{Available at: \url{https://github.com/boschthomas/RDF-constraints-ontology}}.
+We rather developed a very simple vocabulary (only three classes, three object properties, and three data properties) which is universal enough to describe any RDF constraint\footnote{Bosch et al.
+identified in total 74 requirements to formulate RDF constraints; each of them corresponds to a constraint type \cite{BoschNolleAcarEckert2015}} expressible by any constraint language (see the conceptual model in figure \ref{fig:RDF-CV-conceptual-model}).
+We call this vocabulary the \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.
 
@@
 	\centering
-		\includegraphics[width=0.80\textwidth]{images/RDF-CO-conceptual-model.png}
-	\caption{RDF constraints ontology (RDF-CO) - conceptual model}
-	\label{fig:RDF-CO-conceptual-model}
+		\includegraphics[width=0.80\textwidth]{images/RDF-CV-conceptual-model.png}
+	\caption{RDF Constraints Vocabulary (RDF-CV) - conceptual model}
+	\label{fig:RDF-CV-conceptual-model}
 \end{figure}
 
-\ms{Specific constraints} are expressed by specific constraint languages like DSP, OWL 2, ReSh, ShEx, and SPIN.
-\ms{Generic constraints} are expressed by the RDF-CO.
-As RDF-CO describes constraints generically, RDF-CO does not distinguish constraints according to the dimension \ms{universality}. 
-The majority of constraints can be expressed in DL (see section \ref{sec:evaluation}).
-In contrast, there are constraints which cannot be expressed in DL, but are also representable by the RDF-CO. 
-\ms{Complex constraints} encompass \ms{simple constraints} (atomic constraints) and/or further complex constraints.
-DL statements representing complex constraints are created out of DL statements representing composed constraints (if expressible in DL). 
-Simple constraints may be applied to either properties (\ms{properties constraints}) or classes (\ms{class constraints}).
-There are no terms representing simple and complex constraints in the RDF-CO, since context classes (associated simple constraints hold for individuals of these classes) of simple constraints may just be reused by further constraints.
-As a consequence, the distinction of property and class constraints is sufficient to describe all possible RDF constraints.
+The \emph{RDF-CV} represents \emph{generic constraints} and \emph{specific constraints} are expressed by specific constraint languages.
+As the RDF-CV describes constraints generically, the \emph{RDF-CV} does not distinguish constraints according to the dimension \emph{universality}. 
+The majority of constraints can be expressed in DL.
+In contrast, there are constraints which cannot be expressed in DL, but are also representable by the \emph{RDF-CV} (see section \ref{sec:evaluation}). 
+\emph{Complex constraints} encompass \emph{simple constraints} (atomic constraints) and/or further \emph{complex constraints},
+i.e. DL statements representing \emph{complex constraints} are created out of DL statements standing for composed constraints (if expressible in DL). 
+Simple constraints may be applied to either properties (\emph{property constraints}) or classes (\emph{class constraints}).
+There are no terms standing for \emph{simple} and \emph{complex constraints} in the \emph{RDF-CV}, since \emph{context classes} of \emph{simple constraints} may just be reused within further \emph{complex constraints} (\emph{simple constraints} associated with \emph{context classes} must hold for individuals of these \emph{context classes}).
+As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to describe all possible RDF constraint types.
 
@@
 
-Sub-classes of \ms{simple constraints} are \ms{property constraints} and \ms{class constraints} (see the RDF-CO implementation model in figure \ref{fig:RDF-CO-implementation-model}). 
+Sub-classes of \ms{simple constraints} are \ms{property constraints} and \ms{class constraints} (see the RDF-CO implementation model in figure \ref{fig:RDF-CV-implementation-model}). 
 For both property and class constraints a context class, a list of classes, the constraining element, and the constraining value can be stated. 
@@
 	\centering
-		\includegraphics[width=0.70\textwidth]{images/RDF-CO-implementation-model.png}
-	\caption{RDF constraints ontology (RDF-CO) - implementation model}
-	\label{fig:RDF-CO-implementation-model}
+		\includegraphics[width=0.70\textwidth]{images/RDF-CV-implementation-model.png}
+	\caption{RDF Constraints Vocabulary (RDF-CV) - implementation model}
+	\label{fig:RDF-CV-implementation-model}
 \end{figure}
@@
 
-\subsection{Simple Constraints (Syntactic Sugar)}
+\subsection{Complex Constraints as Simple Constraints (Syntactic Sugar)}
 

### 2015-02-10 paper/paper 2/paper 2.tex
section 3.1

@@
 
-\begin{gcotable}
+\begin{table}
+  \scriptsize
+  \sffamily
+  \vspace{0cm}
+	\centering
+		\begin{tabular}{l|l|l|l|l|l|l}
+      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      \hline
       property & Publication & author & - & Person & $\geq$ & 1 \\
-\end{gcotable}
+		\end{tabular}
+	\caption{Property Constraint}
+	\label{tab:property-constraint}
+\end{table}
 
@@
 In order to develop a vocabulary to describe any RDF constraint generically, it is needed to define the terminology for the formulation of RDF constraints and to classify them. 
-A \emph{constraint language} is a language which is used to formulate constraints.
-The W3C Data Shapes working group defines \emph{RDF constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
+A \textbf{\emph{constraint language}} is a language which is used to formulate constraints.
+The W3C Data Shapes working group defines \textbf{\emph{RDF constraint}} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
 We identified four dimensions to classify RDF constraints:
 \begin{itemize}
-  \item \emph{Universality:} specific constraints vs. generic constraints
-	\item \emph{Complexity:} simple constraints vs. complex constraints
-	\item \emph{Context:} property constraints vs. class constraints
-	\item \emph{DL Expressivity:} constraints expressible in DL vs. constraints not expressible in DL
+  \item \textbf{\emph{Universality:}} \emph{specific constraints} vs. \emph{generic constraints}
+	\item \textbf{\emph{Complexity:}} \emph{simple constraints} vs. \emph{complex constraints}
+	\item \textbf{\emph{Context:}} \emph{property constraints} vs. \emph{class constraints}
+	\item \textbf{\emph{DL Expressivity:}} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}
 \end{itemize}
@@
 identified in total 74 requirements to formulate RDF constraints; each of them corresponds to a constraint type \cite{BoschNolleAcarEckert2015}} expressible by any constraint language (see the conceptual model in figure \ref{fig:RDF-CV-conceptual-model}).
-We call this vocabulary the \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.
+We call this vocabulary the \textbf{\emph{RDF Constraints Vocabulary (RDF-CV)}}\footnote{Available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.
 
@@
 		\includegraphics[width=0.80\textwidth]{images/RDF-CV-conceptual-model.png}
-	\caption{RDF Constraints Vocabulary (RDF-CV) - conceptual model}
+	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} - conceptual model}
 	\label{fig:RDF-CV-conceptual-model}
@@
 
-The \emph{RDF-CV} represents \emph{generic constraints} and \emph{specific constraints} are expressed by specific constraint languages.
+The \emph{RDF-CV} represents \textbf{\emph{generic constraints}} and \textbf{\emph{specific constraints}} are expressed by specific constraint languages.
 As the RDF-CV describes constraints generically, the \emph{RDF-CV} does not distinguish constraints according to the dimension \emph{universality}. 
@@
 In contrast, there are constraints which cannot be expressed in DL, but are also representable by the \emph{RDF-CV} (see section \ref{sec:evaluation}). 
-\emph{Complex constraints} encompass \emph{simple constraints} (atomic constraints) and/or further \emph{complex constraints},
+\textbf{\emph{Complex constraints}} encompass \textbf{\emph{simple constraints}} (atomic constraints) and/or further \emph{complex constraints},
 i.e. DL statements representing \emph{complex constraints} are created out of DL statements standing for composed constraints (if expressible in DL). 
-Simple constraints may be applied to either properties (\emph{property constraints}) or classes (\emph{class constraints}).
+Simple constraints may be applied to either properties (\textbf{\emph{property constraints}}) or classes (\textbf{\emph{class constraints}}).
 There are no terms standing for \emph{simple} and \emph{complex constraints} in the \emph{RDF-CV}, since \emph{context classes} of \emph{simple constraints} may just be reused within further \emph{complex constraints} (\emph{simple constraints} associated with \emph{context classes} must hold for individuals of these \emph{context classes}).
@@
 
-Sub-classes of \ms{simple constraints} are \ms{property constraints} and \ms{class constraints} (see the RDF-CO implementation model in figure \ref{fig:RDF-CV-implementation-model}). 
-For both property and class constraints a context class, a list of classes, the constraining element, and the constraining value can be stated. 
-Lists of left and right properties can only be stated for property constraints.
+Sub-classes of \textbf{\emph{simple constraints}} are \textbf{\emph{property constraints}} and \textbf{\emph{class constraints}} (see the \emph{RDF-CV} implementation model in figure \ref{fig:RDF-CV-implementation-model}).
+For both \emph{property} and \emph{class constraints} a \emph{context class}, a list of \emph{classes}, the \emph{constraining element}, and the \emph{constraining value} can be stated. 
+Lists of \emph{left} and \emph{right properties} can only be stated for \emph{property constraints}.
 
@@
 		\includegraphics[width=0.70\textwidth]{images/RDF-CV-implementation-model.png}
-	\caption{RDF Constraints Vocabulary (RDF-CV) - implementation model}
+	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} - implementation model}
 	\label{fig:RDF-CV-implementation-model}
@@
 
-A constraint holds for all individuals of a context class (\ms{contextClass}).
-Consider, e.g., the following cardinality restriction on the property \ms{commandsVessel}, which restricts Starfleet captains to command at least one vessel: 
+A constraint holds for all individuals of a \emph{context class} (\textbf{\emph{contextClass}}).
+Consider, e.g., the following minimum qualified cardinality restriction on the object property \emph{author}, which restricts \emph{publications} to have at least one \emph{author} which is a \emph{person}:
 \begin{DL}
-$StarfleetCaptain \sqsubseteq \geq1 commandsVessel . Vessel $
+$Publication \sqsubseteq \geq1 author . Person $
 \end{DL}
-Mapped to the RDF-CO the cardinality restriction is classified as a property constraint which holds for individuals of the class \ms{StarfleetCaptain}:
-\begin{gcotable}
-property & StarfleetCaptain & commandsVessel & - & Vessel & $\geq$ & 1 \\
-\end{gcotable}
-The constraining element (\ms{constrainingElement}) indicates the actual type of constraint like DL concept and role constructors, (in)equality, and further keywords for constrains which cannot be expressed in DL (e.g.
+Mapped to the \emph{RDF-CV}, the cardinality restriction is classified as a \emph{property constraint} which holds for all individuals of the class \emph{Publication}:
+
+\begin{table}
+  \scriptsize
+  \sffamily
+  \vspace{0cm}
+	\centering
+		\begin{tabular}{l|l|l|l|l|l|l}
+      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      \hline
+      property & Publication & author & - & Person & $\geq$ & 1 \\
+		\end{tabular}
+	\caption{Property Constraint - Cardinality Restriction}
+	\label{tab:property-constraint-cardinality-restriction}
+\end{table}
+
+The \emph{constraining element} (\textbf{\emph{constrainingElement}}) indicates the actual type of constraint like DL concept and role constructors, (in)equality, and further keywords for constraint types which cannot be expressed in DL (e.g.
 regular expressions and constraining facets).
-In some cases, a constraint is only complete when in addition to the constraining element a constraining value (\ms{constrainingValue}) is stated.
+In some cases, a constraint is only complete when in addition to the \emph{constraining element} a \emph{constraining value} (\textbf{\emph{constrainingValue}}) is stated.
 The cardinality restriction 
-\ms{$\geq$1 commandsVessel.Vessel}
-constructs an anonymous class of all individuals who command at least one vessel.
-Thus, the constraining element of this property constraint is the DL at-least restriction \ms{$\geq$} and the constraining value is \ms{1}.
-\ms{Classes} indicate the list of classes, constraints refer to.
-The qualified cardinality restriction refers to the class \ms{Vessel}, 
-i.e., restricting the objects, the property \ms{commandsVessel} points to, to be of the class \ms{Vessel}.
+\ms{$\geq$1 author.Person}, e.g., 
+constructs an anonymous class of all individuals having at least one \emph{author} relationship to \emph{persons}.
+The \emph{constraining element} of this \emph{property constraint} is the DL at-least restriction \emph{$\geq$} and the \emph{constraining value} is \emph{1}.
+\textbf{\emph{Classes}} indicate the list of classes, constraints refer to.
+The qualified cardinality restriction above, e.g., refers to the class \emph{Person}, 
+i.e. restricts the objects, the property \emph{author} points to, to be of the class \emph{Person}.
 
-For property constraints, left and right property lists (\ms{leftProperties}, \ms{rightProperties}) can be specified.
-The assignment of properties to these lists happens relative to the constraining element - which may be an operator (e.g. $\sqsubseteq$ in case of object property paths).
-\ms{Object Property Paths}\footnote{corresponds to the requirement \ms{R-55-OBJECT-PROPERTY-PATHS}} (also called complex role inclusion axioms in DL terminology)
-state that, if an individual x is connected by a sequence of object properties with an individual y, 
-then x is also connected with y by a particular object property. 
-According to the following object property path and some instance data, lieutenant commander \ms{Data} is commanded by captain \ms{Picard} 
-(as \ms{Data} is commanded by commander \ms{Riker} who is commanded by captain \ms{Picard}):
+For \emph{property constraints}, \emph{left} and \emph{right property lists} (\textbf{\emph{leftProperties}}, \textbf{\emph{rightProperties}}) are specified.
+The assignment of properties to these lists happens relative to the \emph{constraining element} - which may be an operator (e.g. $\sqsubseteq$ in case of object property paths).
+\emph{Object Property Paths}\footnote{corresponds to the requirement \emph{R-55-OBJECT-PROPERTY-PATHS}} (also called \emph{complex role inclusion axioms} in DL terminology)
+state that, if an individual \emph{x} is connected by a sequence of object properties with an individual \emph{y}, 
+then \emph{x} is also connected with \emph{y} by a particular object property. 
+According to the following object property path and some instance data, \emph{Stephen-Hawking} is an author of the genre \emph{Popular-Science} 
+(as \emph{Stephen-Hawking} is an author of the book \emph{A-Brief-History-Of-Time} whose genre is \emph{Popular-Science}):
+
 \begin{DL}
-commandedByCommander $\circ$ commandedByCaptain $\sqsubseteq$ commandedByCaptain 
+authorOf $\circ$ genre $\sqsubseteq$ authorOfGenre 
 \end{DL}
-When mapped to the RDF-CO, the properties \ms{commandedByCommander}, \ms{commandedByCaptain} are on the left side of the constraining element \ms{$\sqsubseteq$},
-and the property \ms{commandedByCaptain} is on the right side:
 
-\begin{gcotable}
-property & $\top$ & commandedByCommander, commandedByCaptain & commandedByCaptain & $\top$ & $\sqsubseteq$ & - \\
-\end{gcotable}
+When mapped to the \emph{RDF-CV}, the properties \emph{authorOf} and \emph{genre} are on the left side of the \emph{constraining element} \emph{$\sqsubseteq$},
+and the property \emph{authorOfGenre} is on the right side:
+
+\begin{table}
+  \scriptsize
+  \sffamily
+  \vspace{0cm}
+	\centering
+		\begin{tabular}{l|l|l|l|l|l|l}
+      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      \hline
+      property & $\top$ & authorOf, genre & authorOfGenre & $\top$ & $\sqsubseteq$ & - \\
+		\end{tabular}
+	\caption{Property Constraint - Object Property Paths}
+	\label{tab:property-constraint-object-property-paths}
+\end{table}
 

### 2015-02-10 paper/paper 2/paper 2.tex
section 3.2

@@
 
-The following table shows the mapping between the cardinality restriction expressed in DL 
+Table \ref{tab:cardinality-restriction-mapped-to-vocabulary} shows the mapping between the cardinality restriction expressed in DL 
 and the cardinality restriction expressed by our developed vocabulary to describe any RDF constraint generically (see section~\ref{sec:ontology}):
@@
 		\end{tabular}
-	\caption{Property Constraint}
-	\label{tab:property-constraint}
+	\caption{Cardinality Restriction Mapped to Vocabulary}
+	\label{tab:cardinality-restriction-mapped-to-vocabulary}
 \end{table}
@@
 Bosch and Eckert\cite{BoschEckert2014-2} use SPIN as basis to define a
-validation environment (available at \url{http://purl.org/net/rdfval-demo}) in which the validation of any constraint language\footnote{the only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL.
+validation environment (available at \url{http://purl.org/net/rdfval-demo}) in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL.
 The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.
@@
 \end{DL}
-Mapped to the \emph{RDF-CV}, the cardinality restriction is classified as a \emph{property constraint} which holds for all individuals of the class \emph{Publication}:
+Mapped to the \emph{RDF-CV} (see table \ref{tab:property-constraint-cardinality-restriction}), the cardinality restriction is classified as a \emph{property constraint} which holds for all individuals of the class \emph{Publication}:
 
@@
 The assignment of properties to these lists happens relative to the \emph{constraining element} - which may be an operator (e.g. $\sqsubseteq$ in case of object property paths).
-\emph{Object Property Paths}\footnote{corresponds to the requirement \emph{R-55-OBJECT-PROPERTY-PATHS}} (also called \emph{complex role inclusion axioms} in DL terminology)
+\emph{Object Property Paths}\footnote{Corresponds to the requirement \emph{R-55-OBJECT-PROPERTY-PATHS}} (also called \emph{complex role inclusion axioms} in DL terminology)
 state that, if an individual \emph{x} is connected by a sequence of object properties with an individual \emph{y}, 
@@
 
-When mapped to the \emph{RDF-CV}, the properties \emph{authorOf} and \emph{genre} are on the left side of the \emph{constraining element} \emph{$\sqsubseteq$},
+When mapped to the \emph{RDF-CV} (see table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are on the left side of the \emph{constraining element} \emph{$\sqsubseteq$},
 and the property \emph{authorOfGenre} is on the right side:
@@
 
-There are simple constraints which cannot be expressed by DL such as literal pattern matching, literal value comparison, literal ranges, default values, and language tag cardinality \cite{BoschNolleAcarEckert2015}.
+There are \emph{simple constraints} which cannot be expressed in DL such as \emph{literal pattern matching}, \emph{literal value comparison}, \emph{literal ranges}, \emph{default values}, and \emph{language tag cardinality} \cite{BoschNolleAcarEckert2015}.
 % maybe additional constraint default values:
@@
 % mathematical operations
-There are multiple use cases associated with the requirement to match literals according to given patterns (\ms{Literal Pattern Matching}\footnote{corresponds to the requirement \ms{R-44-PATTERN-MATCHING-ON-RDF-LITERALS}}).
-The enterprise vessel, e.g.,  can only have the registry numbers "NCC-1701", "NCC-1701-A", "NCC-1701-B", "NCC-1701-C", "NCC-1701-D", or "NCC-1701-E".
-The universal restriction can be represented in DL:
-\ms{Enterprise $\sqsubseteq$ $\forall$ registryNumber.RegistryNumber}.
-The restriction of the datatype \ms{RegistryNumber}, however, cannot be expressed in DL, but OWL 2 DL can be used anyway to express the literal pattern matching constraint:
+
+{\em Literal pattern matching}\footnote{Corresponds to {\em R-44-PATTERN-MATCHING-ON-RDF-LITERALS}} restricts literals to match given patterns.
+The universal restriction \ms{Book $\sqsubseteq$ $\forall$ identifier.ISBN}, e.g., ensures that \emph{books} can only have valid ISBN identifiers, 
+i.e. strings that match a given regular expression. 
+The restriction of the datatype \emph{ISBN}, however, cannot be expressed in DL, but OWL 2 DL can be used anyway to express the \emph{literal pattern matching} constraint:
 
 \begin{ex}
-RegistryNumber
-    a rdfs:Datatype ; owl:equivalentClass [ a rdfs:Datatype ;
-        owl:onDatatype xsd:string ;
-        owl:withRestrictions ( [ xsd:pattern "NCC-1701([-][A-E])?" ] ) ] .
+ISBN a RDFS:Datatype ; owl:equivalentClass [ a RDFS:Datatype ;
+    owl:onDatatype xsd:string ; owl:withRestrictions ([ xsd:pattern "^\d{9}[\d|X]\$" ])] .
 \end{ex}
+\tb{Erman, can you please delete the slash in front of the dollar sign from the output of the code fragment above (in the stated pattern)?}
+The first OWL 2 axiom explicitly declares {\em ISBN} to be a datatype.
+%\er{Why start from second and then first?
+Also better we say "owl axiom" when we talk axiom of owl, to prevent ambiguity.}\tb{resolved}
+The second OWL 2 axiom defines {\em ISBN} as an abbreviation for a datatype restriction on {\em xsd:string}. 
+The datatype {\em ISBN} can be used just like any other datatype like in the universal restriction above.
+%There are multiple use cases associated with the requirement to match literals according to given patterns (\emph{Literal Pattern Matching}\footnote{Corresponds to \emph{R-44-PATTERN-MATCHING-ON-RDF-LITERALS}}).
+%The enterprise vessel, e.g.,  can only have the registry numbers "NCC-1701", "NCC-1701-A", "NCC-1701-B", "NCC-1701-C", "NCC-1701-D", or "NCC-1701-E".
+%The universal restriction can be represented in DL:
+%\ms{Enterprise $\sqsubseteq$ $\forall$ registryNumber.RegistryNumber}.
+%The restriction of the datatype \ms{RegistryNumber}, however, cannot be expressed in DL, but OWL 2 DL can be used anyway to express the literal pattern matching constraint:
+%
+%\begin{ex}
+%RegistryNumber
+    %a rdfs:Datatype ; owl:equivalentClass [ a rdfs:Datatype ;
+        %owl:onDatatype xsd:string ;
+        %owl:withRestrictions ( [ xsd:pattern "NCC-1701([-][A-E])?" ] ) ] .
+%\end{ex}
+%The second axiom defines \ms{RegistryNumber} as an abbreviation for a datatype restriction on \ms{xsd:string}. 
+%The first axiom explicitly declares \ms{RegistryNumber} to be a datatype. 
+%The datatype \ms{RegistryNumber} can be used just like any other datatype like in the universal restriction above.
+The \emph{literal pattern matching} constraint validates \emph{ISBN} literals according to the stated regular expression causing constraint violations for triples not matching the regular expression. 
+%\ms{Janeway commandsEnterprise Voyager} and \ms{Voyager registryNumber "NCC-74656"\textasciicircum{}\textasciicircum{}RegistryNumber}, 
+%but not for the triples \ms{Picard commandsEnterprise Enterprise} and \ms{Enterprise registryNumber "NCC-1701-E"\textasciicircum{}\textasciicircum{}RegistryNumber}.
+In table \ref{tab:simple-constraint-not-expressible-in-dl)}, the \emph{simple constraint} (\emph{literal pattern matching}) and the \emph{complex constraint} (\emph{universal restriction}) are mapped to the \emph{RDF-CV}.
 
-The second axiom defines \ms{RegistryNumber} as an abbreviation for a datatype restriction on \ms{xsd:string}. 
-The first axiom explicitly declares \ms{RegistryNumber} to be a datatype. 
-The datatype \ms{RegistryNumber} can be used just like any other datatype like in the universal restriction above.
-The literal pattern matching constraint validates \ms{RegistryNumber} literals according to the stated regular expression causing a constraint violation for the triples 
-\ms{Janeway commandsEnterprise Voyager} and \ms{Voyager registryNumber "NCC-74656"\textasciicircum{}\textasciicircum{}RegistryNumber}, 
-but not for the triples \ms{Picard commandsEnterprise Enterprise} and \ms{Enterprise registryNumber "NCC-1701-E"\textasciicircum{}\textasciicircum{}RegistryNumber}.
-The simple constraints - universal restriction and literal pattern matching - are mapped to the RDF-CO as follows:
+%\begin{gcotable}
+%property & Enterprise & registryNumber & - & RegistryNumber & $\forall$ & - \\
+%class & RegistryNumber & - & - & xsd:string & regex & 'NCC-1701([-][A-E])?' \\
+%\end{gcotable}
 
-\begin{gcotable}
-property & Enterprise & registryNumber & - & RegistryNumber & $\forall$ & - \\
-class & RegistryNumber & - & - & xsd:string & regex & 'NCC-1701([-][A-E])?' \\
-\end{gcotable}
-
-The \ms{Literal Pattern Matching} constraint introduces the new constraining element \ms{regex}.
-For this new constraining element, the validation must be implemented.
-This has to be done once for each constraint which cannot be expressed in DL.
+\begin{table}
+  \scriptsize
+  \sffamily
+  \vspace{0cm}
+	\centering
+		\begin{tabular}{l|l|l|l|l|l|l}
+      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      \hline
+      property & Book & identifier & - & ISBN & $\forall$ & - \\
+      class & ISBN & - & - & xsd:string & regex & '\string^\d{9}[\d|X]\$' \\
+		\end{tabular}
+	\caption{Simple Constraint (Not Expressible in DL)}
+	\label{tab:simple-constraint-not-expressible-in-dl)}
+\end{table} \tb{Erman, can you please format the regular expression in the table above correctly?}
+The \emph{literal pattern matching} constraint introduces the new \emph{constraining element} \emph{regex}.
+For this new \emph{constraining element}, the validation must be implemented.
+This has to be done once for each \emph{generic constraint type} which cannot be expressed in DL.
 
@@
 Exclusive or is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
-The \ms{Context-Specific Exclusive OR of Property Groups}\footnote{corresponds to R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC} 
+The \ms{Context-Specific Exclusive OR of Property Groups}\footnote{Corresponds to R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC} 
 constraint restricts the data to contain only one of multiple property groups.
@@
 all role characteristics can be expressed using the basic features of DL.
-\ms{Irreflexive Object Properties}\footnote{corresponds to the requirement \ms{R-60-IRREFLEXIVE-OBJECT-PROPERTIES}}
+\ms{Irreflexive Object Properties}\footnote{Corresponds to \emph{R-60-IRREFLEXIVE-OBJECT-PROPERTIES}}
 restricts that an object property is irreflexive if it is never locally reflexive, i.e. no individual is connected by the object property to itself \cite{Kroetzsch2012}.
@@
 
-\ms{Allowed Values}\footnote{corresponds to the requirements \ms{R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS} and \ms{R-37-ALLOWED-VALUES-FOR-RDF-LITERALS}}
+\ms{Allowed Values}\footnote{corresponds to \emph{R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS} and \emph{R-37-ALLOWED-VALUES-FOR-RDF-LITERALS}}
 is a common requirement to narrow down the value space of a property by an exhaustive enumeration of the valid values (both literals or resources). 
@@
 
-Within our SPIN validation environment, we define a SPIN construct template for each generic constraint\footnote{for details about the SPIN validation environment see \cite{BoschEckert2014-2}}.
+Within our SPIN validation environment, we define a SPIN construct template for each generic constraint\footnote{For details about the SPIN validation environment see \cite{BoschEckert2014-2}}.
 A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples (\ms{spin:ConstraintViolation}) indicating the subject (\ms{spin:violationRoot}) and the properties (\ms{spin:violationPath}), causing constraint violations, and the reason why constraint violations have been raised (\ms{rdfs:label}).
@@
 Bosch and Eckert\cite{BoschEckert2014-2} use SPIN as basis to define a
-validation environment in which the validation of any constraint language\footnote{the only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL.
+validation environment in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL.
 The validation implementation of constraint languages is fully declarative,

### 2015-02-10 paper/paper 2/paper 2.tex
section 3.3

@@
 
-\ms{Complex constraints} encompass simple constraints and/or complex constraints.
-Exclusive or is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
-The \ms{Context-Specific Exclusive OR of Property Groups}\footnote{Corresponds to R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC} 
-constraint restricts the data to contain only one of multiple property groups.
-Half-Klingons, e.g., either have a klingon mother and a human father or a human mother and a klingon father, which can be expressed by ShEx:
+\textbf{\emph{Complex constraints}} encompass \emph{simple constraints} and/or \emph{complex constraints}.
+\emph{Exclusive or} is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
+The \emph{Context-Specific Exclusive OR of Property Groups}\footnote{Corresponds to R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC} 
+is a \emph{complex constraint} restricting individuals of a given context (here a class) to contain only one of multiple property groups.
+Publications, e.g., are either identified by an ISBN and a title (for books) or by an ISSN and a title (for periodical publications), but it should not be possible to assign both identifiers to a given publication, which can be represented in ShEx:
+
+%Half-Klingons, e.g., either have a klingon mother and a human father or a human mother and a klingon father, which can be expressed by ShEx:
+
+%\begin{ex}
+%Half-Klingon { 
+    %( klingonMother Klingon , humanFather Human ) |
+    %( humanMother Human , klingonFather Klingon ) }
+%\end{ex}
 
 \begin{ex}
-Half-Klingon { 
-    ( klingonMother Klingon , humanFather Human ) |
-    ( humanMother Human , klingonFather Klingon ) }
+Publication { 
+    ( isbn string , title string ) |
+    ( issn string , title string ) }
 \end{ex}
 
-As \ms{B'Elanna Torres} is a \ms{Half-Klingon} with a klingon mother and a human father, the following data is valid:
+%As \ms{B'Elanna Torres} is a \ms{Half-Klingon} with a klingon mother and a human father, the following data is valid:
 
-\begin{ex}
-BElannaTorres a Half-Klingon ;
-    klingonMother Miral ; humanFather JohnTorres .
-\end{ex}
+%\begin{ex}
+%BElannaTorres a Half-Klingon ;
+    %klingonMother Miral ; humanFather JohnTorres .
+%\end{ex}
 
+As, e.g., the \emph{The-Great-Gatsby} is a \emph{publication} (\ms{rdf:type(The-Great-Gatsby, Publication)}) having an \emph{ISBN} number (\ms{isbn(The-Great-Gatsby, '978-0241965672')}) and a \emph{title} (\ms{title(The-Great-Gatsby, 'The Great Gatsby')}) and not an additional \emph{ISSN} identifier, the data is valid.
 %\begin{DL}
@@
 %\end{DL}
+The \emph{complex constraint} above is mapped to DL as follows:
 
-This complex constraint can be mapped to DL:
+%\begin{DL}
+%Half-Klingon $\sqsubseteq$ ($\neg$E $\sqcap$ F) $\sqcup$ (E $\sqcap$ $\neg$F) \\ 
+%E $\equiv$ A $\sqcap$ B \\
+%F $\equiv$ C $\sqcap$ D \\
+%A $\sqsubseteq$ $\geq$ 1 klingonMother.Klingon $\sqcap$ $\leq$ 1 klingonMother.Klingon \\
+%B $\sqsubseteq$ $\geq$ 1 humanFather.Human $\sqcap$ $\leq$ 1 humanFather.Human \\
+%C $\sqsubseteq$ $\geq$ 1 humanMother.Human $\sqcap$ $\leq$ 1 humanMother.Human \\
+%D $\sqsubseteq$ $\geq$ 1 klingonFather.Klingon $\sqcap$ $\leq$ 1 klingonFather.Klingon \\
+%\end{DL}
 
 \begin{DL}
-Half-Klingon $\sqsubseteq$ ($\neg$E $\sqcap$ F) $\sqcup$ (E $\sqcap$ $\neg$F) \\ 
+Publication $\sqsubseteq$ ($\neg$E $\sqcap$ F) $\sqcup$ (E $\sqcap$ $\neg$F) \\ 
 E $\equiv$ A $\sqcap$ B \\
 F $\equiv$ C $\sqcap$ D \\
-A $\sqsubseteq$ $\geq$ 1 klingonMother.Klingon $\sqcap$ $\leq$ 1 klingonMother.Klingon \\
-B $\sqsubseteq$ $\geq$ 1 humanFather.Human $\sqcap$ $\leq$ 1 humanFather.Human \\
-C $\sqsubseteq$ $\geq$ 1 humanMother.Human $\sqcap$ $\leq$ 1 humanMother.Human \\
-D $\sqsubseteq$ $\geq$ 1 klingonFather.Klingon $\sqcap$ $\leq$ 1 klingonFather.Klingon \\
+A $\sqsubseteq$ $\geq$ 1 isbn.string $\sqcap$ $\leq$ 1 isbn.string \\
+B $\sqsubseteq$ $\geq$ 1 title.string $\sqcap$ $\leq$ 1 title.string \\
+C $\sqsubseteq$ $\geq$ 1 issn.string $\sqcap$ $\leq$ 1 issn.string \\
+D $\sqsubseteq$ $\geq$ 1 title.string $\sqcap$ $\leq$ 1 title.string \\
 \end{DL}
 
-The complex constraint (expressed in DL) is mapped to a generic constraint:
+The \emph{complex constraint} (expressed in DL) is mapped to a \emph{generic constraint} using the \emph{RDF-CV} (see table \ref{tab:complex-constraints}).
 
-\begin{gcotable}
+%\begin{gcotable}
+%class & Half-Klingon & - & - & $\neg$E $\sqcap$ F, E $\sqcap$ $\neg$F & $\sqcup$ & - \\
+%class & $\neg$E $\sqcap$ F & - & - & $\neg$E, F & $\sqcap$ & - \\
+%class & E $\sqcap$ $\neg$F & - & - & E, $\neg$F & $\sqcap$ & - \\
+%class & $\neg$E & - & - & E & $\neg$ & - \\
+%class & E & - & - & A, B & $\sqcap$ & - \\
+%class & $\neg$F & - & - & F & $\neg$ & - \\
+%class & F & - & - & C, D & $\sqcap$ & - \\
+%class & A & - & - & A1, A2 & $\sqcap$ & - \\
+%property & A1 & klingonMother & - & Klingon & $\geq$ & 1 \\
+%property & A2 & klingonMother & - & Klingon & $\leq$ & 1 \\
+%class & B & - & - & B1, B2 & $\sqcap$ & - \\
+%property & B1 & humanFather & - & Human & $\geq$ & 1 \\
+%property & B2 & humanFather & - & Human & $\leq$ & 1 \\
+%class & C & - & - & C1, C2 & $\sqcap$ & - \\
+%property & C1 & humanMother & - & Human & $\geq$ & 1 \\
+%property & C2 & humanMother & - & Human & $\leq$ & 1 \\
+%class & D & - & - & D1, D2 & $\sqcap$ & - \\
+%property & D1 & klingonFather & - & Klingon & $\geq$ & 1 \\
+%property & D2 & klingonFather & - & Klingon & $\leq$ & 1 \\
+%\end{gcotable}
+
+\begin{table}
+  \scriptsize
+  \sffamily
+  \vspace{0cm}
+	\centering
+		\begin{tabular}{l|l|l|l|l|l|l}
+      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      \hline
 class & Half-Klingon & - & - & $\neg$E $\sqcap$ F, E $\sqcap$ $\neg$F & $\sqcup$ & - \\
@@
 class & A & - & - & A1, A2 & $\sqcap$ & - \\
-property & A1 & klingonMother & - & Klingon & $\geq$ & 1 \\
-property & A2 & klingonMother & - & Klingon & $\leq$ & 1 \\
+property & A1 & isbn & - & string & $\geq$ & 1 \\
+property & A2 & isbn & - & string & $\leq$ & 1 \\
 class & B & - & - & B1, B2 & $\sqcap$ & - \\
-property & B1 & humanFather & - & Human & $\geq$ & 1 \\
-property & B2 & humanFather & - & Human & $\leq$ & 1 \\
+property & B1 & title & - & string & $\geq$ & 1 \\
+property & B2 & title & - & string & $\leq$ & 1 \\
 class & C & - & - & C1, C2 & $\sqcap$ & - \\
-property & C1 & humanMother & - & Human & $\geq$ & 1 \\
-property & C2 & humanMother & - & Human & $\leq$ & 1 \\
+property & C1 & issn & - & string & $\geq$ & 1 \\
+property & C2 & issn & - & string & $\leq$ & 1 \\
 class & D & - & - & D1, D2 & $\sqcap$ & - \\
-property & D1 & klingonFather & - & Klingon & $\geq$ & 1 \\
-property & D2 & klingonFather & - & Klingon & $\leq$ & 1 \\
-\end{gcotable}
+property & D1 & title & - & string & $\geq$ & 1 \\
+property & D2 & title & - & string & $\leq$ & 1 \\
+		\end{tabular}
+	\caption{Complex Constraints}
+	\label{tab:complex-constraints}
+\end{table}
 
-Even though, tools may generate generic constraints automatically, this complex constraint is composed of many other complex (e.g.
-minimum and maximum qualified cardinality restrictions) and simple constraints (e.g.
+Even though, tools may generate \emph{generic constraints} automatically, this \emph{complex constraint} is composed of many other \emph{complex} (e.g.
+minimum and maximum qualified cardinality restrictions) and \emph{simple constraints} (e.g.
 constraints on sets).
-As \ms{exact (un)qualified cardinality restrictions} and \ms{exclusive or} are frequently used complex constraints,
-we propose using them as simple constraints - 	in terms of syntactic sugar.
-As a consequence, the \ms{Context-Specific Exclusive OR of Property Groups} constraint above is represented as a generic constraint more intuitively and concisely:
+As \emph{exact (un)qualified cardinality restrictions (=n)} and \emph{exclusive or (XOR)} are frequently used \emph{complex constraints},
+we propose using them as \emph{simple constraints} - in terms of syntactic sugar.
+As a consequence, the \emph{Context-Specific Exclusive OR of Property Groups} constraint above is represented as a \emph{generic constraint} more intuitively and concisely (see table \ref{tab:complex-constraints-as-simple-constraints}).
 
-\begin{gcotable}
-class & Half-Klingon & - & - & E, F & XOR \\
+%\begin{gcotable}
+%class & Half-Klingon & - & - & E, F & XOR \\
+%class & E & - & - & A, B & $\sqcap$ \\
+%class & F & - & - & C, D & $\sqcap$ \\
+%property & A & klingonMother & - & Klingon & = & 1 \\
+%property & B & humanFather & - & Human & = & 1 \\
+%property & C & humanMother & - & Human & = & 1 \\
+%property & D & klingonFather & - & Klingon & = & 1 \\
+%\end{gcotable}
+
+\begin{table}
+  \scriptsize
+  \sffamily
+  \vspace{0cm}
+	\centering
+		\begin{tabular}{l|l|l|l|l|l|l}
+      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      \hline
+class & Publication & - & - & E, F & XOR \\
 class & E & - & - & A, B & $\sqcap$ \\
 class & F & - & - & C, D & $\sqcap$ \\
-property & A & klingonMother & - & Klingon & = & 1 \\
-property & B & humanFather & - & Human & = & 1 \\
-property & C & humanMother & - & Human & = & 1 \\
-property & D & klingonFather & - & Klingon & = & 1 \\
-\end{gcotable}
+property & A & isbn & - & string & = & 1 \\
+property & B & title & - & string & = & 1 \\
+property & C & issn & - & string & = & 1 \\
+property & D & title & - & string & = & 1 \\
+		\end{tabular}
+	\caption{Complex Constraints as Simple Constraints}
+	\label{tab:complex-constraints-as-simple-constraints}
+\end{table}
 

### 2015-02-11 paper/paper 2/paper 2.tex
3.4

@@
 we propose using them as \emph{simple constraints} - in terms of syntactic sugar.
-As a consequence, the \emph{Context-Specific Exclusive OR of Property Groups} constraint above is represented as a \emph{generic constraint} more intuitively and concisely (see table \ref{tab:complex-constraints-as-simple-constraints}).
+As a consequence, the \emph{Context-Specific Exclusive OR of Property Groups} constraint above is represented as a \emph{generic constraint} more intuitively and concisely (see table \ref{tab:simplified-complex-constraints}).
 
@@
 		\end{tabular}
-	\caption{Complex Constraints as Simple Constraints}
-	\label{tab:complex-constraints-as-simple-constraints}
+	\caption{Simplified Complex Constraints}
+	\label{tab:simplified-complex-constraints}
 \end{table}
@@
 
-Almost 15 percent of all RDF constraints are complex constraints which can be simplified and therefore formulated as simple constraints when using them in terms of syntactic sugar (see section \ref{sec:evaluation}).
-
-There are three forms of RBox axioms: role inclusions, equivalences and disjointness. 
-OWL provides a variety of others, namely role transitivity, symmetry, asymmetry, reflexivity and irreflexivity. 
+Almost 15 percent of all RDF constraint types are \emph{complex constraints} which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar (see section \ref{sec:evaluation}).
+
+There are three forms of \emph{OWL RBox axioms}: \emph{role inclusions}, \emph{equivalence} and \emph{disjointness}. 
+OWL provides a variety of others, namely \emph{role transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity}. 
 These are sometimes considered as basic axiom types in DL as well, using some suggestive notation such as
-\ms{Trans(ancestorOf)} to express that the role ancestorOf is transitive. 
+\ms{Trans(ancestorOf)} to express that the role \emph{ancestorOf} is transitive. \tb{transitive property example from the library domain}
 However, such axioms are just syntactic sugar; 
 all role characteristics can be expressed using the basic features of DL.
-\ms{Irreflexive Object Properties}\footnote{Corresponds to \emph{R-60-IRREFLEXIVE-OBJECT-PROPERTIES}}
+The \emph{Irreflexive Object Properties} constraint type\footnote{Corresponds to \emph{R-60-IRREFLEXIVE-OBJECT-PROPERTIES}}, e.g., 
 restricts that an object property is irreflexive if it is never locally reflexive, i.e. no individual is connected by the object property to itself \cite{Kroetzsch2012}.
-The irreflexivity constraint, stating that individuals cannot be married to themselves, can be represented in DL:
-
-\begin{DL}
-$\top$ $\sqsubseteq$ $\neg$ $\exists  marriedTo . Self$
-\end{DL}
-
-When mapped to the RDF-CO, the complex constraint aggregates three simple constraints (one property and two class constraints):
-
-\begin{gcotable}
-property & $\exists$ marriedTo . Self & marriedTo & - & Self & $\exists$ & - \\
-class & $\neg$ $\exists$ marriedTo . Self & - & - & $\exists$ marriedTo . Self & $\neg$ & - \\
-class & $\top$ & - & - & $\top$, $\neg$ $\exists$ marriedTo . Self & $\sqsubseteq$ & - \\
-\end{gcotable}
-
-When using the RBox axiom \ms{role irreflexivity} as syntactic sugar, 
-the complex constraint transforms into a simple property constraint with exactly the same semantics:
-
-\begin{gcotable}
-property & $\top$ & marriedTo & - & - & irreflexive & - \\
-\end{gcotable}
-
-The \ms{Primary Key Properties} constraint is often useful to declare a given (datatype) property as the "primary key" of a class, so that a system can enforce uniqueness. 
-Starfleet officers, e.g., are uniquely identified by their command authorization code (e.g. to activate and cancel auto-destruct sequences).
-It means that the property \ms{commandAuthorizationCode} is inverse functional - mapped to DL and the RDF-CO as follows:
-
-\begin{DL}
-$(\ms{funct } commandAuthorizationCode\sp{\overline{\ }})$
-\end{DL}
-
-\begin{gcotable}
-property & $\top$ & commandAuthorizationCode$^{-}$ & commandAuthorizationCode$^{-}$ & - & inverse & - \\
-property & $\top$ & commandAuthorizationCode$^{-}$ & - & - & functional & - \\
-\end{gcotable}
-
-Keys, however, are even more general, i.e., a generalization of inverse functional properties \cite{Schneider2009}.
+The irreflexivity constraint \ms{$\top$ $\sqsubseteq$ $\neg$ $\exists authorOf.Self$}
+states that individuals cannot be authors of themselves.
+When mapped to the \emph{RDF-CV} (see table \ref{tab:irreflexive-object-properties-as-complex-constraints}), the \emph{complex constraint} aggregates three \emph{simple constraints} (one \emph{property} and two \emph{class constraints}).
+
+%\begin{gcotable}
+%property & $\exists$ marriedTo . Self & marriedTo & - & Self & $\exists$ & - \\
+%class & $\neg$ $\exists$ marriedTo . Self & - & - & $\exists$ marriedTo . Self & $\neg$ & - \\
+%class & $\top$ & - & - & $\top$, $\neg$ $\exists$ marriedTo . Self & $\sqsubseteq$ & - \\
+%\end{gcotable}
+
+\begin{table}
+  \scriptsize
+  \sffamily
+  \vspace{0cm}
+	\centering
+		\begin{tabular}{l|l|l|l|l|l|l}
+      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      \hline
+property & $\exists$ authorOf.Self & marriedTo & - & Self & $\exists$ & - \\
+class & $\neg$ $\exists$ authorOf.Self & - & - & $\exists$ authorOf.Self & $\neg$ & - \\
+class & $\top$ & - & - & $\top$, $\neg$ $\exists$ authorOf.Self & $\sqsubseteq$ & - \\
+		\end{tabular}
+	\caption{Irreflexive Object Properties as Complex Constraints}
+	\label{tab:irreflexive-object-properties-as-complex-constraints}
+\end{table}
+
+When using the OWL RBox axiom \emph{role irreflexivity} as syntactic sugar, 
+the \emph{complex constraint} transforms into a \emph{simple property constraint} with exactly the same semantics (see table \ref{tab:irreflexive-object-properties-as-simple-constraints}).
+
+%\begin{gcotable}
+%property & $\top$ & marriedTo & - & - & irreflexive & - \\
+%\end{gcotable}
+
+\begin{table}
+  \scriptsize
+  \sffamily
+  \vspace{0cm}
+	\centering
+		\begin{tabular}{l|l|l|l|l|l|l}
+      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      \hline
+property & $\top$ & authorOf & - & - & irreflexive & - \\
+		\end{tabular}
+	\caption{Irreflexive Object Properties as Simple Constraints}
+	\label{tab:irreflexive-object-properties-as-simple-constraints}
+\end{table}
+
+The \emph{Primary Key Properties}\footnote{Corresponds to \emph{R-226-PRIMARY-KEY-PROPERTIES}} constraint type is often useful to declare a given (datatype) property as the "primary key" of a class, so that a system can enforce uniqueness.
+Books, e.g., are uniquely identified by their ISBN, i.e. the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}, 
+which can be mapped to the \emph{RDF-CV} (see table \ref{tab:primary-key-properties-as-complex-constraints}).
+
+%\begin{gcotable}
+%property & $\top$ & commandAuthorizationCode$^{-}$ & commandAuthorizationCode$^{-}$ & - & inverse & - \\
+%property & $\top$ & commandAuthorizationCode$^{-}$ & - & - & functional & - \\
+%\end{gcotable}
+
+\begin{table}
+  \scriptsize
+  \sffamily
+  \vspace{0cm}
+	\centering
+		\begin{tabular}{l|l|l|l|l|l|l}
+      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      \hline
+property & $\top$ & isbn$^{-}$ & isbn$^{-}$ & - & inverse & - \\
+property & Book & isbn$^{-}$ & - & - & functional & - \\
+		\end{tabular}
+	\caption{Primary Key Properties as Complex Constraints}
+	\label{tab:primary-key-properties-as-complex-constraints}
+\end{table}
+
+\emph{Keys}, however, are even more general, i.e. a generalization of inverse functional properties \cite{Schneider2009}.
 A key can be a datatype property, an object property, or a chain of properties.
-For this generalization purposes, as there are different sorts of key, and as keys can lead to undecidability, 
-DL is extended with \ms{key boxes} and a special \ms{keyfor} construct\cite{Lutz2005}.
-This leads to the following DL and RDF-CO mappings (only one simple property constraint):
-
-\begin{DL}
-commandAuthorizationCode \ms{keyfor} StarfleetOfficer
-\end{DL}
-
-\begin{gcotable}
-property & StarFleetOfficer & commandAuthorizationCode & - & - & keyfor & - \\
-\end{gcotable}
+For these generalization purposes, as there are different sorts of keys, and as keys can lead to undecidability, 
+DL is extended with \emph{key boxes} and a special construct \emph{keyfor} \cite{Lutz2005}.
+When using the \emph{keyfor} DL construct (\ms{isbn keyfor Book}), the \emph{complex constraint} can be expressed by only one \emph{simple property constraint} (see table \ref{tab:primary-key-properties-as-simple-constraints} for the mapping to the \emph{RDF-CV}).
+
+%\begin{gcotable}
+%property & StarFleetOfficer & commandAuthorizationCode & - & - & keyfor & - \\
+%\end{gcotable}
+
+\begin{table}
+  \scriptsize
+  \sffamily
+  \vspace{0cm}
+	\centering
+		\begin{tabular}{l|l|l|l|l|l|l}
+      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      \hline
+property & Book & isbn & - & - & keyfor & - \\
+		\end{tabular}
+	\caption{Primary Key Properties as Simple Constraints}
+	\label{tab:primary-key-properties-as-simple-constraints}
+\end{table}
+
+%Starfleet officers, e.g., are uniquely identified by their command authorization code (e.g. to activate and cancel auto-destruct sequences).
+%It means that the property \emph{commandAuthorizationCode} is inverse functional - mapped to DL and the \emph{RDF-CV} as follows:
+%
+%\begin{DL}
+%$(\ms{funct } commandAuthorizationCode\sp{\overline{\ }})$
+%\end{DL}
+%
+%%\begin{gcotable}
+%%property & $\top$ & commandAuthorizationCode$^{-}$ & commandAuthorizationCode$^{-}$ & - & inverse & - \\
+%%property & $\top$ & commandAuthorizationCode$^{-}$ & - & - & functional & - \\
+%%\end{gcotable}
+%
+%\begin{table}
+  %\scriptsize
+  %\sffamily
+  %\vspace{0cm}
+	%\centering
+		%\begin{tabular}{l|l|l|l|l|l|l}
+      %\textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      %\hline
+%property & $\top$ & commandAuthorizationCode$^{-}$ & commandAuthorizationCode$^{-}$ & - & inverse & - \\
+%property & $\top$ & commandAuthorizationCode$^{-}$ & - & - & functional & - \\
+		%\end{tabular}
+	%\caption{Primary Key Properties as Complex Constraints}
+	%\label{tab:primary-key-properties-as-complex-constraints}
+%\end{table}
+%
+%Keys, however, are even more general, i.e., a generalization of inverse functional properties \cite{Schneider2009}.
+%A key can be a datatype property, an object property, or a chain of properties.
+%For this generalization purposes, as there are different sorts of key, and as keys can lead to undecidability, 
+%DL is extended with \emph{key boxes} and a special \emph{keyfor} construct\cite{Lutz2005}.
+%This leads to the following DL and \emph{RDF-CV} mappings (only one \emph{simple property constraint}):
+%
+%\begin{DL}
+%commandAuthorizationCode \ms{keyfor} StarfleetOfficer
+%\end{DL}
+
+%\begin{table}
+  %\scriptsize
+  %\sffamily
+  %\vspace{0cm}
+	%\centering
+		%\begin{tabular}{l|l|l|l|l|l|l}
+      %\textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      %\hline
+%property & StarFleetOfficer & commandAuthorizationCode & - & - & keyfor & - \\
+		%\end{tabular}
+	%\caption{Primary Key Properties as Simple Constraints}
+	%\label{tab:primary-key-properties-as-simple-constraints}
+%\end{table}
 

### 2015-02-11 paper/paper 2/paper 2.tex
4

@@
 %\section{Transformations between Specific Constraints (Expressed by Different Constraint Languages)}
-\section{Transformations between Specific Constraints}
+%\section{Transformations between Specific Constraints}
+\section{How to Improve the Interoperability of Constraints}
 \label{sec:transformations}
 
-RDF data providers ensure that their data conforms to constraints which are part of the contract between the providers and the consumers of that data.
-As there is no standard way, these constraints may be represented by multiple constraint languages (there are even more than the five promising ones\footnote{i.a.
-Bibframe, DQTP, Pellet ICV, RDFUnit, SPARQL, Stardog ICV}).
-There is an obvious need to transform a specific constraint (\ms{$sc_{\alpha}$}) (expressed by any constraint language \ms{$\alpha$}) into a specific constraint (\ms{$sc_{\beta}$}) (expressed by any constraint language \ms{$\beta$}) - when they have the same semantics.
-We use the RDF-CO as intermediate representation for these transformations.
-If we define mappings ($m(sc_{\alpha}), m(sc_{\beta})$) from two equivalent specific constraints to the corresponding generic constraint (\ms{gc}),
+RDF data providers have to ensure that their data conforms to constraints which are part of explicitly or implicitly concluded contracts between data providers and consumers.
+As there is no standard way, these constraints may be represented by a variety of possible constraint languages (there are even more than the five promising ones\footnote{i.a.
+Bibframe, Data Quality Test Patterns, Pellet ICV, RDFUnit, SPARQL, Stardog ICV}).
+There is an obvious need to transform any \emph{specific constraint} (\emph{$sc_{\alpha}$}) (expressed by any constraint language \emph{$\alpha$}) into any other \emph{specific constraint} (\emph{$sc_{\beta}$}) (expressed by any constraint language \emph{$\beta$}) - when they have the same semantics.
+We use the \emph{RDF-CV} as an intermediate representation vocabulary for these transformations.
+If we define mappings ($m(sc_{\alpha}), m(sc_{\beta})$) between equivalent \emph{specific constraints} and the corresponding \emph{generic constraint} (\emph{gc}),
 we can convert them automatically:
@@
 
-We do not need to define mappings for each pair of semantically equivalent specific constraints.
-Let's assume we are able to express a constraint by 5/6/7/8/9/10 constraint languages.
-Without the intermediate generic constraint, we would have to define one mapping for each pair of specific constraints expressed by a different constraint languages
-- that are \ms{\( {n \choose 2} \)} mappings for each constraint (10/15/21/28/36/45 mappings).
-With an intermediate generic constraint, we only need to define \ms{n} mappings (one mapping for each specific constraint) from the specific constraints to the generic constraint (5/6/7/8/9/10 mappings).
+We do not need to define mappings for each pair of semantically equivalent \emph{specific constraints}.
+Let's assume we are able to express a constraint type by 5/6/7/8/9/10 constraint languages.
+Without the intermediate \emph{generic constraint}, we would have to define for each constraint type \emph{1} mapping for each pair of \emph{specific constraints} (expressed by different constraint languages)
+- that are \emph{\( {n \choose 2} \)} mappings (10/15/21/28/36/45 mappings).
+With an intermediate \emph{generic constraint}, however, we only need to define for each constraint type \emph{n} mappings (one mapping for each \emph{specific constraint}) from \emph{n} \emph{specific constraints} to the corresponding \emph{generic constraint} (5/6/7/8/9/10 mappings).
 
@@
 
-\ms{Allowed Values}\footnote{corresponds to \emph{R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS} and \emph{R-37-ALLOWED-VALUES-FOR-RDF-LITERALS}}
-is a common requirement to narrow down the value space of a property by an exhaustive enumeration of the valid values (both literals or resources). 
-The Enterprise, e.g., is only commanded by the captains Archer, Kirk, and Picard.
-This complex constraint is composed of the two simple constraints \ms{universal quantification} and \ms{allowed values} which can be represented in DL:
+The {\em existential quantification}\footnote{Corresponds to {\em R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}}
+\ms{Publication $\equiv$ $\exists$ publisher.Publisher} restricts publications to have at least one publisher and can be expressed by at least 10 constraint languages\footnote{at least by OWL2, SPARQL, ShEx, Bibframe, DSP, ReSh, SPIN, DQTP, Pellet IVC, Stardog ICV}:
+
+\begin{ex}
+# OWL 2:
+[ a owl:Restriction ;
+  owl:onProperty publisher ;
+  owl:someValuesFrom Publisher ;
+  rdfs:subClassOf Publication ] .
+
+# SPARQL:
+ASK { ?x a Publication . FILTER NOT EXISTS { ?x publisher [ a Publisher ] } . }
+
+# ShEx:
+Publication {
+    publisher @Publisher{1,} }
+
+# DSP:
+descriptionTemplate a dsp:DescriptionTemplate ;
+    dsp:resourceClass Publication ; 
+    dsp:statementTemplate [ a dsp:NonLiteralStatementTemplate ;
+        dsp:minOccur 1 ; dsp:maxOccur "infinity" ; 
+        dsp:property publisher ; 
+        dsp:nonLiteralConstraint [ a dsp:NonLiteralConstraint ;
+            dsp:valueClass Publisher ] ] .
+
+# ReSh:
+Publication a rs:ResourceShape ; rs:property [
+    rs:propertyDefinition :publisher ;
+    rs:valueShape :Publisher ;
+    se:min 1 ; se:maxundefined true ; ] .
+
+# SPIN:
+CONSTRUCT {
+    _:cv a spin:ConstraintViolation ; spin:violationRoot ?subject ;
+         rdfs:label ?violationMessage ; spin:violationPath ?property . } WHERE 
+{ ?subject a ?classSubject . FILTER NOT EXISTS { ?subject ?property [ a ?classObject ] } . }
+\end{ex}
+
+%\emph{Allowed Values}\footnote{corresponds to \emph{R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS} and \emph{R-37-ALLOWED-VALUES-FOR-RDF-LITERALS}}
+%is a common requirement (constraint type) to narrow down the value space of a property by an exhaustive enumeration of the valid values (both literals or resources). 
+%The Enterprise, e.g., is only commanded by the captains Archer, Kirk, and Picard.
+%This \emph{complex constraint} is composed of the two \emph{simple constraints} \emph{universal quantification} and \emph{allowed values} which can be represented in DL:
 
@@
 
-\begin{DL}
-Enterprise $\equiv$ $\forall$ commandedBy . \{Archer\} $\sqcup$ \{Kirk\} $\sqcup$ \{Picard\}
-\end{DL}
-
-First, we map these DL statements to two simple generic constraints corresponding to the RDF-CO (we define the class \ms{EnterpriseCaptains} by simply enumerating its instances):
+%\begin{DL}
+%Enterprise $\equiv$ $\forall$ commandedBy . \{Archer\} $\sqcup$ \{Kirk\} $\sqcup$ \{Picard\}
+%\end{DL}
+
+%First, we map these DL statements to two \emph{simple generic constraints} corresponding to the \emph{RDF-CV} (we define the class \ms{EnterpriseCaptains} by simply enumerating its instances):
+
+First, the DL statement \ms{Publication $\equiv$ $\exists$ publisher.Publisher} is mapped to a \emph{simple generic constraint} according to the \emph{RDF-CV} (see table \ref{tab:existential-quantification-as-simple-constraints}).
 
@@
 
-\begin{gcotable}
-property & Enterprise & commandedBy & - & EnterpriseCaptains & $\forall$ & - \\
-class & EnterpriseCaptains & - & - & \{Archer\},\{Kirk\},\{Picard\} & $\sqcup$ & - \\
-\end{gcotable}
-
-The next step is to define one mapping for each specific constraint to the generic constraint.
-The specific constraints (\ms{$sc_{OWL 2}$}, \ms{$sc_{ReSh}$}, and \ms{$sc_{ShEx}$}) expressed by OWL 2, ReSh, and ShEx look like this:
-
-\begin{ex}
-# OWL 2:
-Enterprise rdfs:subClassOf [ a owl:Restriction .
-    owl:onProperty commandedBy .
-    owl:allValuesFrom [ a owl:Class ;
-        owl:oneOf ( Archer Kirk Picard ) ] ] .
-# ReSh:
-Enterprise a rs:ResourceShape ; rs:property [
-    rs:name "commandedBy" ; rs:propertyDefinition commandedBy ;
-    rs:allowedValue Archer , Kirk , Picard ;
-    rs:occurs rs:Exactly-one ; ] .
-# ShEx:
-Enterprise {
-    commandedBy (Archer Kirk Picard) }
-\end{ex}
+%\begin{gcotable}
+%property & Enterprise & commandedBy & - & EnterpriseCaptains & $\forall$ & - \\
+%class & EnterpriseCaptains & - & - & \{Archer\},\{Kirk\},\{Picard\} & $\sqcup$ & - \\
+%\end{gcotable}
+
+\begin{table}
+  \scriptsize
+  \sffamily
+  \vspace{0cm}
+	\centering
+		\begin{tabular}{l|l|l|l|l|l|l}
+      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      \hline
+property & Publication & publisher & - & Publisher & $\exists$ \\
+		\end{tabular}
+	\caption{Existential Quantification as Simple Constraints}
+	\label{tab:existential-quantification-as-simple-constraints}
+\end{table}
+
+The next step is to define one mapping for each \emph{specific constraint} (\emph{$sc_{OWL 2}$}, \emph{$sc_{ReSh}$}, \emph{$sc_{ShEx}$}, ...) to the \emph{generic constraint}.
+
+%\begin{ex}
+%# OWL 2:
+%Enterprise rdfs:subClassOf [ a owl:Restriction .
+    %owl:onProperty commandedBy .
+    %owl:allValuesFrom [ a owl:Class ;
+        %owl:oneOf ( Archer Kirk Picard ) ] ] .
+%# ReSh:
+%Enterprise a rs:ResourceShape ; rs:property [
+    %rs:name "commandedBy" ; rs:propertyDefinition commandedBy ;
+    %rs:allowedValue Archer , Kirk , Picard ;
+    %rs:occurs rs:Exactly-one ; ] .
+%# ShEx:
+%Enterprise {
+    %commandedBy (Archer Kirk Picard) }
+%\end{ex}
 
@@
 
-\section{Validation of Specific and Generic Constraints}
+%\section{Validation of Specific and Generic Constraints}
+\section{How to Provide Constraint Validation Out-Of-The-Box}
 \label{sec:validation}

### 2015-02-11 paper/paper 2/paper 2.tex
5

@@
 
-We can provide the validation of all specific constraints (expressed by any constraint language) by defining a mapping to SPIN.
-That's what we have done for all OWL 2 and DSP constructs (see section \ref{sec:implementation}).
+We are able to offer the validation of all \emph{specific constraints} (expressed by any constraint language) by defining mappings from each \emph{specific constraint} to SPIN, 
+what we have done for all OWL 2 and DSP constructs and for some constructs of other constraint languages (see section \ref{sec:implementation}).
 %We do not have to define a mapping to SPIN for each specific constraint. 
 %when we define a mapping to SPIN for each generic constraint.
-But, if we define a mapping from a specific constraint to the corresponding generic constraint and if we define a mapping from the generic constraint to SPIN,
-we do not have to define a mapping to SPIN for that specific constraint - 
-we are able to validate the generic as well as the specific constraint.
-As a consequence, we only have to define one SPIN mapping for each constraint corresponding to a requirement within the RDF validation requirements database.
-19 of 74 RDF constraints can be expressed by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
-This means, that there must be 76 (four for each constraint) implementations to validate 76 specific constraints - instead of only 19 implementations (one for each generic constraint).
-
-Within our SPIN validation environment, we define a SPIN construct template for each generic constraint\footnote{For details about the SPIN validation environment see \cite{BoschEckert2014-2}}.
-A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples (\ms{spin:ConstraintViolation}) indicating the subject (\ms{spin:violationRoot}) and the properties (\ms{spin:violationPath}), causing constraint violations, and the reason why constraint violations have been raised (\ms{rdfs:label}).
+We do not have to map each \emph{specific constraint} to SPIN and we get identical validation results for semantically equivalent \emph{specific constraints},
+(1) if we map semantically equivalent \emph{specific constraints} to the corresponding \emph{generic constraint} and 
+(2) if we map the \emph{generic constraint} to SPIN.
+As a consequence, we only have to define one SPIN mapping for each constraint type corresponding to a requirement within the RDF validation requirements database.
+19 of 74 RDF constraint types can be expressed by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
+This means that there must be 76 (four for each constraint type) implementations to validate 76 \emph{specific constraints} - instead of only 19 implementations (one for each \emph{generic constraint}).
+
+Within our validation environment, we define one SPIN construct template for each \emph{generic constraint}\footnote{For details about the validation environment see \cite{BoschEckert2014-2}}.
+A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples (\emph{spin:ConstraintViolation}) indicating the subject (\emph{spin:violationRoot}) and the properties (\emph{spin:violationPath}), causing constraint violations, and the reason why constraint violations have been raised (\emph{rdfs:label}).
 A SPIN construct template creates constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
-The SPARQL CONSTRUCT query for the universal quantification (of the previous example in section \ref{sec:transformations}) is shown below:
+The SPARQL CONSTRUCT query for validating \emph{universal quantifications}\footnote{Corresponds to \emph{R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}}, e.g.
+\emph{authors} of \emph{publications} must be \emph{persons} (\ms{Publication $\equiv$ $\forall$ author.Person}), is shown below:
 
@@
     [   a spin:ConstraintViolation ; spin:violationRoot ?subject ;
-        rdfs:label ?violationMessage ; spin:violationPath ?p1 . }
+        rdfs:label ?violationMessage ; spin:violationPath ?lp1 . ] }
 WHERE {	  
@@
         gclo:contextClass ?cc ;
-        gclo:leftProperties ( ?p1 ) ;
+        gclo:leftProperties ( ?lp1 ) ;
         gclo:classes ( ?c1 ) ;
         gclo:constrainingElement "universal quantification" ] .
-    [   a gclo:ClassConstraint ;
-        gclo:contextClass ?c1 ;
-        gclo:classes ( ?i1 ?i2 ?i3 ) ;
-        gclo:constrainingElement "union" ] .				
-    ?subject a ?cc ; ?p1 ?i .
-    FILTER ( ?i != ?i1 && ?i != ?i2 && ?i != ?i3 ) . }
+    ?subject a ?cc .
+    ?subject ?lp1 ?o .
+    FILTER NOT EXISTS { ?o a ?c1 } . }
 \end{ex}
-
-As a consequence, the validation results do not differ for semantically equivalent constraints expressed by multiple constraint languages,
-as we provide only one validation implementation for each generic constraint.
 
@@
 SPIN represents both the SPIN mappings and the SPARQL queries in RDF. 
-Within the validation environment, we fully implemented the validation of all OWL 2 DL\footnote{OWL 2 SPIN mapping: \url{https://github.com/boschthomas/OWL2-SPIN-Mapping}} and DSP\footnote{DSP SPIN mapping: \url{https://github.com/dcmi/DSP-SPIN-Mapping}} constructs (for the complete DSP validation see \cite{BoschEckert2014-2}).
+Within the validation environment, we fully implemented the validation of all OWL 2 DL\footnote{OWL to SPIN: \url{https://github.com/boschthomas/OWL2-SPIN-Mapping}} and DSP\footnote{DSP to SPIN: \url{https://github.com/dcmi/DSP-SPIN-Mapping}} constructs (for the complete DSP validation see \cite{BoschEckert2014-2}).
 The implementation can be tested at \url{http://purl.org/net/rdfval-demo}.
@@
 
-We provide a mapping from RDF-CO to SPIN\footnote{RDF-CO SPIN mapping: \url{https://github.com/boschthomas/RDF-CO-SPIN-Mapping}} in order to automatically validate each type of generic constraint (simple, complex, property, and class constraints).
+We provide a mapping from RDF-CO to SPIN\footnote{RDF-CV to SPIN: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}} in order to automatically validate each type of generic constraint (simple, complex, property, and class constraints).
 Part of future work will be 

### 2015-02-12 paper/paper 2/paper 2.tex
5

@@
 
+SPARQL is generally seen as the method of choice to validate RDF data according to certain constraints, although it is not ideal for their formulation. 
+In contrast, OWL 2, DSP, ReSh, and ShEx constraints are comparatively easy to understand. 
+Bosch and Eckert \cite{BoschEckert2014-2} use SPIN as basis to define a
+validation environment in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL
+(the implementation can be tested at \url{http://purl.org/net/rdfval-demo}).
+The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.
 We are able to offer the validation of all \emph{specific constraints} (expressed by any constraint language) by defining mappings from each \emph{specific constraint} to SPIN, 
-what we have done for all OWL 2 and DSP constructs and for some constructs of other constraint languages (see section \ref{sec:implementation}).
+what we have done for all OWL 2\footnote{OWL to SPIN: \url{https://github.com/boschthomas/OWL2-SPIN-Mapping}} and DSP\footnote{DSP to SPIN: \url{https://github.com/dcmi/DSP-SPIN-Mapping}} constructs and for some constructs of other constraint languages.
 %We do not have to define a mapping to SPIN for each specific constraint. 
@@
 This means that there must be 76 (four for each constraint type) implementations to validate 76 \emph{specific constraints} - instead of only 19 implementations (one for each \emph{generic constraint}).
+
+%The validation implementation of constraint languages is fully declarative,
+%consisting of a mapping from constraint languages to SPIN in form of SPARQL CONSTRUCT queries.
+%SPIN represents both the SPIN mappings and the SPARQL queries in RDF. 
+%Within the validation environment, we fully implemented the validation of all OWL 2 DL and DSP constructs 
+%(for the complete DSP validation see \cite{BoschEckert2014-2}).
 
@@
 
-%\subsection{Not Allowed Values}
-
-\section{Implementation}
-\label{sec:implementation}
-
-SPARQL is generally seen as the method of choice to validate RDF data according to certain constraints, although it is not ideal for their formulation. 
-In contrast, OWL 2 and DSP constraints are comparatively easy to understand, but lack an implementation to validate RDF data. 
-Bosch and Eckert\cite{BoschEckert2014-2} use SPIN as basis to define a
-validation environment in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL.
-The validation implementation of constraint languages is fully declarative,
-consisting of a mapping from constraint languages to SPIN in form of SPARQL CONSTRUCT queries.
-SPIN represents both the SPIN mappings and the SPARQL queries in RDF. 
-Within the validation environment, we fully implemented the validation of all OWL 2 DL\footnote{OWL to SPIN: \url{https://github.com/boschthomas/OWL2-SPIN-Mapping}} and DSP\footnote{DSP to SPIN: \url{https://github.com/dcmi/DSP-SPIN-Mapping}} constructs (for the complete DSP validation see \cite{BoschEckert2014-2}).
-The implementation can be tested at \url{http://purl.org/net/rdfval-demo}.
-The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.
-
-We provide a mapping from RDF-CO to SPIN\footnote{RDF-CV to SPIN: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}} in order to automatically validate each type of generic constraint (simple, complex, property, and class constraints).
+We provide a mapping from the \emph{RDF-CV} to SPIN\footnote{RDF-CV to SPIN: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}} in order to automatically validate each type of \emph{generic constraint} (\emph{simple}, \emph{complex}, \emph{property}, and \emph{class constraints}).
 Part of future work will be 
-(1) to provide a GUI which generates generic constraints automatically according to inputs of domain experts who are not familiar with the formulation of constraints; 
-(2) to offer bidirectional transformations between specific constraints (expressed by multiple constraint languages) and generic constraints;
-(3) to provide translations between specific constraints (expressed by any specific constraint language) by using generic constraints as an intermediate transformation step.
+(1) to provide a GUI which generates \emph{generic constraints} automatically according to inputs of domain experts who are not familiar with the formulation of constraints,
+(2) to offer bidirectional transformations between \emph{specific constraints} (expressed by multiple constraint languages) and \emph{generic constraints}, and
+(3) to provide translations between semantically equivalent \emph{specific constraints} (expressed by any constraint language) by using \emph{generic constraints} as an intermediate transformation step.
 %\begin{itemize}
@@
 %\end{itemize}
+
+%\subsection{Not Allowed Values}
+
 \section{Evaluation}

### 2015-02-12 paper/paper 2/paper 2.tex
paper 2 - evaluation

@@
 
-We evaluated to which extend the most promising five constraint languages fulfill each of the overall 74 requirements to formulate RDF constraints \cite{BoschNolleAcarEckert2015}.
-If a constraint can be expressed in DL, we added the mapping to DL and to the generic constraint.
-If a constraint cannot be expressed in DL, we only added the mapping to the generic constraint.
-Therefore, we show that each constraint can be mapped to a generic constraint.
-The following table shows the absolute numbers and the relative percentages for each of the three dimensions to classify constraints:
-
-\begin{evaluation-generic-overview}
-Property Constraints & 48 & 65 (64.86) \\
-Class Constraints & 17 & 23 (22.96) \\
-Property and Class Constraints & 9 & 12 (12.16) \\
-\hline
-Simple Constraints & 46 & 62 (62.16) \\
-Simple Constraints (Syntactic Sugar) & 10 & 14 (13.51) \\
-Complex Constraints & 18 & 24 (24.32) \\
-\hline
-DL Expressible & 51 & 69 (68.92) \\
-DL Not Expressible & 23 & 31 (31.08) \\
+We evaluated to which extend the most promising five constraint languages fulfill each of the overall 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type.
+We recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} (serving as appendix of this paper) in which we explain each requirement (constraint type) in detail and give examples for each (represented by listed constraint languages).
+This technical report also contains mappings to DL to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
+If a constraint type can be expressed in DL, we added the mapping to DL and to the \emph{generic constraint}.
+If a constraint type cannot be expressed in DL, we only added the mapping to the \emph{generic constraint}.
+Therefore, we show that each constraint type can be mapped to a \emph{generic constraint}.
+Table \ref{tab:evaluation} shows the absolute numbers and the relative percentages for each of the three dimensions to classify constraint types \emph{context}, \emph{complexity}, and \emph{DL expressivity}:
+
+%\begin{evaluation-generic-overview}
+%\emph{Property Constraints} & 48 & 65 (64.86) \\
+%\emph{Class Constraints} & 17 & 23 (22.96) \\
+%\emph{Property and Class Constraints} & 9 & 12 (12.16) \\
+%\hline
+%\emph{Simple Constraints} & 46 & 62 (62.16) \\
+%\emph{Simple Constraints} (Syntactic Sugar) & 10 & 14 (13.51) \\
+%\emph{Complex Constraints} & 18 & 24 (24.32) \\
+%\hline
+%\emph{DL Expressible} & 51 & 69 (68.92) \\
+%\emph{DL Not Expressible} & 23 & 31 (31.08) \\
+%\hline
+%Total & 74 & 100 \\
+%\end{evaluation-generic-overview}
+
+\begin{table}
+  %\scriptsize
+  %\sffamily
+  \vspace{0cm}
+	\centering
+		\begin{tabular}{l|c|c}
+      \textbf{Constraint Classes} & \textbf{\#} & \textbf{\%} \\
+      \hline
+\emph{Property Constraints} & 48 & 65 (64.86) \\
+\emph{Class Constraints} & 17 & 23 (22.96) \\
+\emph{Property and Class Constraints} & 9 & 12 (12.16) \\
+\hline
+\emph{Simple Constraints} & 46 & 62 (62.16) \\
+\emph{Simple Constraints} (Syntactic Sugar) & 10 & 14 (13.51) \\
+\emph{Complex Constraints} & 18 & 24 (24.32) \\
+\hline
+\emph{DL Expressible} & 51 & 69 (68.92) \\
+\emph{DL Not Expressible} & 23 & 31 (31.08) \\
 \hline
 Total & 74 & 100 \\
-\end{evaluation-generic-overview}
-
-Constraints can be classified as \ms{property constraints} and \ms{class constraints}.
-Two thirds of the total amount of constraints are property constraints, one fifth are class constraints, and approx. 10\% are composed of both property and class constraints.
-Constraints may be either atomic (\ms{simple constraints}) or created out of simple and/or complex constraints (\ms{complex constraints}).
-Almost two thirds are simple constraints, a quarter are complex constraints.
-Almost 15 percent are complex constraints which can be formulated as simple constraints when using them in terms of syntactic sugar.
-Constraints can either be expressible in DL or not.
-The majority - nearly 70\% - of the overall constraints are expressible in DL.
+		\end{tabular}
+	\caption{Evaluation}
+	\label{tab:evaluation}
+\end{table}
+
+%\newenvironment{evaluation-generic-overview}{
+  %%\scriptsize
+  %%\sffamily
+  %\vspace{0cm}
+	%\begin{center}
+  %\begin{tabular}{l|c|c}
+  %\hline
+  %\textbf{Constraint Classes} & \textbf{\#} & \textbf{\%} \\
+  %\hline
+%
+%}{
+  %\hline
+  %\end{tabular}
+  %%\linebreak
+	%\end{center}
+%}
+
+Constraints types can be classified as \emph{property constraints} and \emph{class constraints} (classification dimension \emph{context}).
+Two thirds of the total amount of constraint types are \emph{property constraints} (e.g.
+\emph{existential} and \emph{universal quantification}), one fifth are \emph{class constraints} (e.g.
+\emph{allowed values}\footnote{Corresponds to \emph{R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS} and
+\emph{R-37-ALLOWED-VALUES-FOR-RDF-LITERALS}} for literals and objects), and approx.
+10\% are composed of both \emph{property and class constraints} (e.g.
+\emph{context-specific exclusive or of property groups}).
+Constraint types may be either atomic (\emph{simple constraints}) or created out of \emph{simple} and/or \emph{complex constraints} (\emph{complex constraints}) (classification dimension \emph{complexity}).
+Almost two thirds of the constraint types are \emph{simple constraints} (e.g.
+\emph{object property paths}), a quarter are \emph{complex constraints} (e.g.
+\emph{ranges of literal values}\footnote{Corresponds to \emph{R-45-RANGES-OF-RDF-LITERAL-VALUES}}), and
+nearly 15 percent are \emph{complex constraints} which can be formulated as \emph{simple constraints} when using them in terms of syntactic sugar (e.g. \emph{(un)qualified cardinality restrictions}).
+Constraint types can either be \emph{expressible in DL} or \emph{not} (classification dimension \emph{DL expressivity}).
+The majority - nearly 70\% - of the overall constraint types are expressible in DL.	
+\emph{Literal pattern matching} is an example of a constraint type which cannot be represented in DL.
+\tb{examples}
 

### 2015-02-12 paper/paper 2/paper 2.tex
paper 2 - running example

@@
 
-\tb{I copied this paragraph from the ESWC paper, we have to modify it a bit}
+\tb{I copied this paragraph from the ESWC paper, we have to modify it}
 Recently, RDF validation as a research field gained speed due to common needs of data practitioners.
@@
 
-With minimum qualified cardinality restrictions, \emph{publications} can be enforced to have at least one \emph{author} which must be a \emph{person}.
+With \emph{minimum qualified cardinality restrictions}, \emph{publications} can be enforced to have at least one \emph{author} which must be a \emph{person}.
 This constraint can be represented generically (\emph{generic constraint}) using DL (\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}), but also specifically (\emph{specific constraint}) by multiple constraint languages like OWL 2, ShEx, ReSh, or DSP:
@@
 \emph{The-Lord-Of-The-Rings} must have at least one \emph{author} relationship to a \emph{person}.
-If \emph{The-Lord-Of-The-Rings} has no \emph{author} relationship, a constraint violation is raised. 
-It leads to invalid data, if \emph{The-Lord-Of-The-Rings} has an \emph{author} property pointing to some resource which is assigned to another class than \emph{Person}
+If \emph{The-Lord-Of-The-Rings} does not have an \emph{author} relationship, a constraint violation is raised. 
+It leads to invalid data, if \emph{The-Lord-Of-The-Rings} has an \emph{author} property pointing to some resource which is assigned to other classes than \emph{person}
 (\ms{author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Human)}).
@@
 (\ms{author(The-Lord-Of-The-Rings, Tolkien)}).
-The data is valid, if \emph{The-Lord-Of-The-Rings} is connected to a \emph{person} via the object property \emph{author}
+The data is valid, however, if \emph{The-Lord-Of-The-Rings} is connected to a \emph{person} via the object property \emph{author}
 (\ms{author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Person)}).
 
-Table \ref{tab:cardinality-restriction-mapped-to-vocabulary} shows the mapping between the cardinality restriction expressed in DL 
-and the cardinality restriction expressed by our developed vocabulary to describe any RDF constraint generically (see section~\ref{sec:ontology}):
+Table \ref{tab:cardinality-restriction-mapped-to-vocabulary} shows the mapping between the \emph{cardinality restriction} represented in DL 
+and the \emph{cardinality restriction} expressed by our developed vocabulary to describe any RDF constraint generically (see section~\ref{sec:ontology}):
 
@@
 		\end{tabular}
-	\caption{Cardinality Restriction Mapped to Vocabulary}
+	\caption{Cardinality Restriction Expressed Generically}
 	\label{tab:cardinality-restriction-mapped-to-vocabulary}
@@
 
-According to this vocabulary, each constraint is either a constraint on classes or a constraint on properties.
-The generically expressed cardinality restriction is represented in RDF as follows:
-
-\begin{ex}
-[   a PropertyConstraint ;
-    contextClass Publication ;
-    leftProperties ( author ) ;
-    classes ( Person ) ;
-    constrainingElement ">=" ;
-    constrainingValue 1 ] .
-\end{ex}
+%According to this vocabulary, each constraint is either a constraint on classes or a constraint on properties.
+%The generically expressed cardinality restriction is represented in RDF as follows:
+%
+%\begin{ex}
+%[   a PropertyConstraint ;
+    %contextClass Publication ;
+    %leftProperties ( author ) ;
+    %classes ( Person ) ;
+    %constrainingElement ">=" ;
+    %constrainingValue 1 ] .
+%\end{ex}
 
@@
 The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.
-The generically expressed cardinality restriction above is validated within our validation environment (see section \ref{sec:validation}) by means of a SPARQL CONSTRUCT query:
-\begin{ex}
-[   a PropertyConstraint ;
-    contextClass ?cc ;
-    leftProperties ( ?p1 ) ;
-    classes ( ?c1 ) ;
-    constrainingElement ">=" ;
-    constrainingValue ?cv ] .
-?subject rdf:type ?cc .
-BIND ( qualifiedCardinality( ?subject, ?p1, ?c1 ) AS ?c ) .
-FILTER ( ?c < ?cv ) .		  
-\end{ex}
+The generically expressed \emph{cardinality restriction} above is validated within the validation environment (see section \ref{sec:validation}) by means of a SPARQL CONSTRUCT query.
+
+%\begin{ex}
+%[   a PropertyConstraint ;
+    %contextClass ?cc ;
+    %leftProperties ( ?p1 ) ;
+    %classes ( ?c1 ) ;
+    %constrainingElement ">=" ;
+    %constrainingValue ?cv ] .
+%?subject rdf:type ?cc .
+%BIND ( qualifiedCardinality( ?subject, ?p1, ?c1 ) AS ?c ) .
+%FILTER ( ?c < ?cv ) .		  
+%\end{ex}
 
@@
 \emph{Literal pattern matching} is an example of a constraint type which cannot be represented in DL.
-\tb{examples}
 
@@
 
-\tb{ToDO: too much space before and after DL and table environments}
-\tb{ToDo: there are no line breaks for ms environment}
+\tb{Erman, there is too much space before and after DL and table environments / can your resolve that please?}
 

### 2015-02-12 paper/paper 2/paper 2.tex
introduction and running example merged

@@
 
-The purpose of OWL 2 ontologies is to perform reasoning on RDF data and not to validate RDF data conforming to these ontologies.
-OWL 2 is based on the {\em non-unique name assumption} (nUNA) whereas RDF validation requires that different names represent different objects ({\em unique name assumption} (UNA)). 
-Reasoning in OWL 2 is based on the semantics of {\em open-world assumption} (OWA), i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose: to represent knowledge on the World Wide Web.
-On the other hand, many RDF validation scenarios require the {\em closed-world assumption} (CWA) (i.e., a statement is inferred to be false if it cannot be proved to be true).
-This ambiguity in semantics is one of the main reasons why OWL 2 has not been adopted as a standard constraint language for RDF validation.  
-For this reason, we cannot use OWL 2 ontologies for RDF validation as we use XML Schemas, DTDs, RELAX NG, or Schematron to validate XML documents.
+%The purpose of OWL 2 ontologies is to perform reasoning on RDF data and not to validate RDF data conforming to these ontologies.
+%OWL 2 is based on the {\em non-unique name assumption} (nUNA) whereas RDF validation requires that different names represent different objects ({\em unique name assumption} (UNA)). 
+%Reasoning in OWL 2 is based on the semantics of {\em open-world assumption} (OWA), i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose: to represent knowledge on the World Wide Web.
+%On the other hand, many RDF validation scenarios require the {\em closed-world assumption} (CWA) (i.e., a statement is inferred to be false if it cannot be proved to be true).
+%This ambiguity in semantics is one of the main reasons why OWL 2 has not been adopted as a standard constraint language for RDF validation.  
+%For this reason, we cannot use OWL 2 ontologies for RDF validation as we use XML Schemas, DTDs, RELAX NG, or Schematron to validate XML documents.
 
@@
 where experts from industry, government, and academia discussed first use cases for RDF constraint formulation and validation.
-In 2014, two working groups on RDF validation have been established to develop a language to express RDF constraints on RDF data: 
+In 2014, two working groups on RDF validation have been established to develop a language to express constraints on RDF data: 
 the W3C RDF Data Shapes WG\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles WG\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}. 
@@
 The intention associated with this database is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
-The requirements are classified to better evaluate existing solutions and each requirement to formulate RDF constraints is directly mapped to an RDF constraint type.
-Bosch et al. identified in total 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
-They recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which they explain each requirement in detail and give examples for each (represented by different constraint languages) \cite{BoschNolleAcarEckert2015}.
+The requirements are classified to better evaluate existing solutions and each requirement is directly mapped to a constraint type.
 
@@
 The five most promising ones on being the standard are
-Description Set Profiles (DSP)\footnote{\url{http://dublincore.org/documents/2008/03/31/dc-dsp/}},
-Resource Shapes (ReSh)\footnote{\url{http://www.w3.org/Submission/shapes/}}, 
-Shape Expressions (ShEx)\footnote{\url{http://www.w3.org/Submission/shex-primer/}},
-the SPARQL Inferencing Notation (SPIN)\footnote{\url{http://spinrdf.org/}}, 
-and the Web Ontology Language (OWL 2)\footnote{\url{http://www.w3.org/TR/owl2-syntax/}}.
+\emph{Description Set Profiles (DSP)}\footnote{\url{http://dublincore.org/documents/2008/03/31/dc-dsp/}},
+\emph{Resource Shapes (ReSh)}\footnote{\url{http://www.w3.org/Submission/shapes/}}, 
+\emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/shex-primer/}},
+the \emph{SPARQL Inferencing Notation (SPIN)}\footnote{\url{http://spinrdf.org/}}, 
+and the \emph{Web Ontology Language (OWL 2)}\footnote{\url{http://www.w3.org/TR/owl2-syntax/}}.
 %\section{Ideas}
@@
 %min car more powerful than req. propery
-The idea behind this paper is to express any constraint type (corresponding to a requirement to formulate RDF constraints) in a generic way using a lightweight vocabulary (consisting of only a few terms).
-
-Cardinality restrictions, e.g., can be expressed either generically (\emph{generic constraints}) by \emph{description logics (DL)} 
+The idea behind this paper is to express any constraint type (corresponding to a requirement to formulate RDF constraints) in a generic way using a lightweight vocabulary (consisting of only a few terms) (section \ref{sec:vocabulary}).
+
+\emph{Cardinality restrictions}, e.g., can be expressed either generically (\emph{generic constraints}) by \emph{description logics (DL)} 
 %and extensions  
 or specifically (\emph{specific constraints}) by domain-specific constraint languages such as OWL 2, DSP, ShEx, ReSh, and SPIN.
-The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints generically. 
+The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
 For that reason, we map constraint types to DL statements.
-With minimum qualified cardinality restrictions, researchers from the library domain can state
+With \emph{minimum qualified cardinality restrictions}, researchers (e.g. from the library domain) can state
 that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
-This constraint can be represented generically in DL as follows: \ms{Publication $\sqsubseteq$ $\geq$1 author.Person}.
-The same constraint may also be represented specifically by multiple constraint languages like OWL 2 and ShEx:
+This constraint can be represented generically (\emph{generic constraint}) using DL (\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}), but also specifically (\emph{specific constraint}) by multiple constraint languages like OWL 2, ShEx, ReSh, or DSP:
 
@@
 Publication { author @Person{1, } }
+
+# ReSh:
+Publication a rs:ResourceShape ; rs:property [
+    rs:name "author" ; rs:propertyDefinition author ;
+    rs:valueShape Person ;
+    rs:occurs rs:One-or-many ; ] .
+
+# DSP:
+[   a dsp:DescriptionTemplate ; 
+    dsp:resourceClass Publication ; 
+    dsp:statementTemplate [ a dsp:NonLiteralStatementTemplate ;
+        dsp:minOccur 1 ; dsp:maxOccur "infinity" ; 
+        dsp:property author ; 
+        dsp:nonLiteralConstraint [ a dsp:NonLiteralConstraint ;
+            dsp:valueClass Person ] ] ] .
 \end{ex}
 
+As each \emph{publication} must have at least one \emph{author} relationship to a \emph{person} 
+and as the book \emph{The-Lord-Of-The-Rings} is a \emph{publication} \ms{rdf:type(The-Lord-Of-The-Rings, Publication)}, 
+\emph{The-Lord-Of-The-Rings} must have at least one \emph{author} relationship to a \emph{person}.
+If \emph{The-Lord-Of-The-Rings} does not have an \emph{author} relationship, a constraint violation is raised. 
+It leads to invalid data, if \emph{The-Lord-Of-The-Rings} has an \emph{author} property pointing to some resource which is assigned to other classes than \emph{person}
+(\ms{author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Human)}).
+It also causes a constraint violation, if \emph{The-Lord-Of-The-Rings} has an \emph{author} relation to an object for which no class is associated
+(\ms{author(The-Lord-Of-The-Rings, Tolkien)}).
+The data is valid, however, if \emph{The-Lord-Of-The-Rings} is connected to a \emph{person} via the object property \emph{author}
+(\ms{author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Person)}).
+
 As there is no standard way to formulate RDF constraints, 
-semantically equivalent cardinality restrictions may be represented by different constraint languages, which causes confusion and weakens the understanding how to ensure metadata quality between multiple parties.
-Therefore, when choosing constraint language \ms{$\alpha$} to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a constraint expressed by any other constraint language \ms{$\beta$}.
+semantically equivalent \emph{cardinality restrictions} may be represented by different constraint languages, which causes confusion and weakens the understanding how to ensure metadata quality between multiple parties.
+Therefore, when choosing constraint language \ms{$\alpha$} to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a constraint expressed by any other constraint language \ms{$\beta$} (section \ref{sec:transformations}).
 This is important in order to enhance the interoperability of constraint languages and to simplify the communication of RDF data producers and consumers, 
@@
 
-There are validation environments enabling to validate RDF constraints expressed by just a few constraint languages such as OWL 2\footnote{\url{purl.org/net/rdfval-demo}\label{footnote1}}, DSP\footref{footnote1}, and ShEx\footnote{\url{http://www.w3.org/2013/ShEx/FancyShExDemo}}.
-But, it should be possible to validate any RDF constraints expressed by any constraint language and 
-what is even more important to validate them in exactly the same manner without any differences. 
-If we implement the validation of a \emph{generic constraint} and if we transform a \emph{specific constraint} into a \emph{generic constraint}, we are able to validate the \emph{specific constraint} immediately.
-As a consequence, we do not have to implement the validation for each \emph{specific constraint}, as we need to implement the validation only once for each \emph{generic constraint}.
+We provide a validation environment (available at \url{http://purl.org/net/rdfval-demo}) which enables to validate RDF data according to constraints expressed by multiple  constraint languages such as OWL 2, DSP, ReSh, and ShEx.
+The next step, however, is to validate any constraint type expressed by any constraint language and 
+what is even more important to validate them in exactly the same way, i.e. leading to identical validation results (section \ref{sec:validation}). 
+We are able to offer validation of any \emph{specific constraint} out-of-the-box, (1) if we implement the validation of the corresponding constraint type once and (2) if we transform semantically equivalent \emph{specific constraints} into the corresponding \emph{generic constraint}.
+As a consequence, we do not have to implement the validation for each \emph{specific constraint}.
 
@@
 
-Existing constraint languages can be extended and new constraint languages can be developed, if existing constraint languages are not sufficient to represent needed constraint types.
-If (1) a new constraint type is expressed generically, (2) the \emph{generic constraint type} is mapped to \emph{specific constraint types} (expressed by constraint languages), and (3) the validation is implemented for this particular \emph{generic constraint type},
-the validation of \emph{specific constraint types} is provided out of the box.
-As a consequence, constraint language designers do not have to implement the validation of their constraint languages and each semantically equivalent \emph{specific constraint type} is validated the same way (i.e.
+%Existing constraint languages can be extended and new constraint languages can be developed, if existing constraint languages are not sufficient to represent needed constraint types.
+
+%If (1) a new constraint type is expressed generically, (2) the \emph{generic constraint type} is mapped to \emph{specific constraint types} (expressed by constraint languages), and (3) the validation is implemented for this particular \emph{generic constraint type},
+%the validation of \emph{specific constraint types} is provided out of the box.
+%As a consequence, constraint language designers do not have to implement the validation of their constraint languages and each semantically equivalent \emph{specific constraint type} is validated the same way (i.e.
 leading to identical validation results).
@@
 
-\section{Running Example}
-
-With \emph{minimum qualified cardinality restrictions}, \emph{publications} can be enforced to have at least one \emph{author} which must be a \emph{person}.
-This constraint can be represented generically (\emph{generic constraint}) using DL (\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}), but also specifically (\emph{specific constraint}) by multiple constraint languages like OWL 2, ShEx, ReSh, or DSP:
-
-\begin{ex}
-# OWL 2:
-Publication
-    a owl:Restriction ;
-    owl:minQualifiedCardinality 1 ;
-    owl:onProperty author ;
-    owl:onClass Person .
-
-# ShEx:
-Publication { author @Person{1, } }
-
-# ReSh:
-Publication a rs:ResourceShape ; rs:property [
-    rs:name "author" ; rs:propertyDefinition author ;
-    rs:valueShape Person ;
-    rs:occurs rs:One-or-many ; ] .
-
-# DSP:
-[   a dsp:DescriptionTemplate ; 
-    dsp:resourceClass Publication ; 
-    dsp:statementTemplate [ a dsp:NonLiteralStatementTemplate ;
-        dsp:minOccur 1 ; dsp:maxOccur "infinity" ; 
-        dsp:property author ; 
-        dsp:nonLiteralConstraint [ a dsp:NonLiteralConstraint ;
-            dsp:valueClass Person ] ] ] .
-\end{ex}
-
-As each \emph{publication} must have at least one \emph{author} relationship to a \emph{person} 
-and as the book \emph{The-Lord-Of-The-Rings} is a \emph{publication} \ms{rdf:type(The-Lord-Of-The-Rings, Publication)}, 
-\emph{The-Lord-Of-The-Rings} must have at least one \emph{author} relationship to a \emph{person}.
-If \emph{The-Lord-Of-The-Rings} does not have an \emph{author} relationship, a constraint violation is raised. 
-It leads to invalid data, if \emph{The-Lord-Of-The-Rings} has an \emph{author} property pointing to some resource which is assigned to other classes than \emph{person}
-(\ms{author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Human)}).
-It also causes a constraint violation, if \emph{The-Lord-Of-The-Rings} has an \emph{author} relation to an object for which no class is associated
-(\ms{author(The-Lord-Of-The-Rings, Tolkien)}).
-The data is valid, however, if \emph{The-Lord-Of-The-Rings} is connected to a \emph{person} via the object property \emph{author}
-(\ms{author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Person)}).
-
-Table \ref{tab:cardinality-restriction-mapped-to-vocabulary} shows the mapping between the \emph{cardinality restriction} represented in DL 
-and the \emph{cardinality restriction} expressed by our developed vocabulary to describe any RDF constraint generically (see section~\ref{sec:ontology}):
-
-\begin{table}
-  \scriptsize
-  \sffamily
-  \vspace{0cm}
-	\centering
-		\begin{tabular}{l|l|l|l|l|l|l}
-      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
-      \hline
-      property & Publication & author & - & Person & $\geq$ & 1 \\
-		\end{tabular}
-	\caption{Cardinality Restriction Expressed Generically}
-	\label{tab:cardinality-restriction-mapped-to-vocabulary}
-\end{table}
+%\section{Running Example}
+%
+%Table \ref{tab:cardinality-restriction-mapped-to-vocabulary} shows the mapping between the \emph{cardinality restriction} represented in DL 
+%and the \emph{cardinality restriction} expressed by our developed vocabulary to describe any RDF constraint generically (see section~\ref{sec:ontology}):
+%
+%\begin{table}
+  %\scriptsize
+  %\sffamily
+  %\vspace{0cm}
+	%\centering
+		%\begin{tabular}{l|l|l|l|l|l|l}
+      %\textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      %\hline
+      %property & Publication & author & - & Person & $\geq$ & 1 \\
+		%\end{tabular}
+	%\caption{Cardinality Restriction Expressed Generically}
+	%\label{tab:cardinality-restriction-mapped-to-vocabulary}
+%\end{table}
 
@@
 
-Bosch and Eckert\cite{BoschEckert2014-2} use SPIN as basis to define a
-validation environment (available at \url{http://purl.org/net/rdfval-demo}) in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL.
-The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.
-The generically expressed \emph{cardinality restriction} above is validated within the validation environment (see section \ref{sec:validation}) by means of a SPARQL CONSTRUCT query.
+%Bosch and Eckert\cite{BoschEckert2014-2} use SPIN as basis to define a
+%validation environment in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL.
+%The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.
+%The generically expressed \emph{cardinality restriction} above is validated within the validation environment (see section \ref{sec:validation}) by means of a SPARQL CONSTRUCT query.
 
@@
 \section{A Vocabulary to Describe RDF Constraints Generically} 
-\label{sec:ontology}
+\label{sec:vocabulary}
 

### 2015-02-15 paper/paper 2/paper 2.tex
SKOS constraint types

@@
 More and more domains adopt Linked Data principles
-and seek now for ways to ensure data quality by validating RDF data, as they are used to have this functionality in the XML world.
+and seek now for ways to ensure data quality by validating RDF data according to constraints, as they are used to have this functionality in the XML world.
 For XML, XML Schema is the standard constraint language to validate XML documents.
@@
 We identified requirements to formulate and validate RDF constraints and mapped each requirement to a constraint type.
-The majority of these constraint types can be represented in description logics providing a logical underpinning.
+The majority of these constraint types can be represented in description logics providing their logical underpinning.
 
 In this paper, we provide a basic terminology and classification system for RDF constraint types,
-we developed a vocabulary describing any RDF constraint type generically (whether expressible in DL or not),
+we developed a vocabulary describing any RDF constraint type generically (whether expressible in description logics or not),
 we show how to transform \emph{specific constraints} (expressed by any constraint language \ms{$\alpha$}) into \emph{generic constraints} and \emph{specific constraints} (expressed by any other constraint language \ms{$\beta$}), and
-we explain how to provide the validation of any \emph{specific constraint} immediately and why this is important.
+we explain how to provide the validation of any \emph{specific constraint} out-of-the-box.
 
@@
 The \textbf{contributions} of this paper are:
-(1) We provide a basic terminology and classification system for RDF constraint types,
+(1) we provide a basic terminology and classification system for RDF constraint types,
 (2) we developed a vocabulary describing any RDF constraint type generically (whether expressible in DL or not),
@@
 We call this vocabulary the \textbf{\emph{RDF Constraints Vocabulary (RDF-CV)}}\footnote{Available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.
-
+\tb{make entry in LOV?}
 \begin{figure}

### 2015-02-15 paper/paper7/paper7-appendix.tex
SKOS constraint types

@@
   Only {\em disco:Question}s, e.g., can have {\em disco:responseDomain} relationships (\ms{$\exists$ responseDomain.$\top$ $\sqsubseteq$ Question}).
+	Severity level: ERROR
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em DATA-CUBE-C-PROPERTY-DOMAIN-01:}} 
+	{\em Property Domain} constraints are defined for each \emph{Data Cube} object and data property.
+  Only {\em qb:Observation}s, e.g., can have {\em qb:dataSet} relationships (\ms{$\exists$ dataSet.$\top$ $\sqsubseteq$ Observation}).
+	Severity level: ERROR
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em DCAT-C-PROPERTY-DOMAIN-01:}} 
+	{\em Property Domain} constraints are defined for each \emph{DCAT} object and data property.
+  Only {\em dcat:Catalog}s, e.g., can have {\em dcat:dataset} relationships (\ms{$\exists$ dataset.$\top$ $\sqsubseteq$ Catalog}).
+	Severity level: ERROR
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em PHDD-C-PROPERTY-DOMAIN-01:}} 
+	{\em Property Domain} constraints are defined for each \emph{PHDD} object and data property.
+  Only {\em phdd:Table}s, e.g., can have {\em phdd:isStructuredBy} relationships (\ms{$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table}).
+	Severity level: ERROR
 \end{itemize}
@@
   {\em disco:caseQuantity} relationships, e.g., can only point to literals of the datatype {\em xsd:nonNegativeInteger} (\ms{$\top$ $\sqsubseteq$ $\forall$ caseQuantity.nonNegativeInteger}).
+	Severity level: ERROR
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em DATA-CUBE-C-PROPERTY-RANGES-01:}} 
+	{\em Property Range} constraints are defined for each \emph{Data Cube} object and data property.
+  {\em qb:order} relationships, e.g., can only point to literals of the datatype {\em xsd:string} (\ms{$\top$ $\sqsubseteq$ $\forall$ order.string}).
+	Severity level: ERROR
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em DCAT-C-PROPERTY-RANGES-01:}} 
+	{\em Property Range} constraints are defined for each \emph{DCAT} object and data property.
+  {\em dcat:bytes} relationships, e.g., can only point to literals of the datatype {\em xsd:integer} (\ms{$\top$ $\sqsubseteq$ $\forall$ bytes.integer}).
+	Severity level: ERROR
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em PHDD-C-PROPERTY-RANGES-01:}} 
+	{\em Property Range} constraints are defined for each \emph{PHDD} object and data property.
+  {\em phdd:caseQuantity} relationships, e.g., can only point to literals of the datatype {\em xsd:nonNegativeInteger} (\ms{$\top$ $\sqsubseteq$ $\forall$ caseQuantity.nonNegativeInteger}).
+	Severity level: ERROR
 \end{itemize}
@@
 
+\begin{itemize}
+	\item \textbf{{\em SKOS-C-LANGUAGE-TAG-CARDINALITY-01\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Omitted or Invalid Language Tags}:}}
+Some controlled vocabularies contain literals in natural language, but without information what language has actually been used.
+Language tags might also not conform to language standards, such as RFC 3066.
+Iteration over all triples in the vocabulary that have a predicate which is a (subclass of) \emph{rdfs:label} or \emph{skos:note}. 
+Severity level: INFO
+  \item \textbf{{\em SKOS-C-LANGUAGE-TAG-CARDINALITY-02\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Incomplete Language Coverage}:}}
+	Some concepts in a thesaurus are labeled in only one language, some in multiple languages.
+It may be desirable to have each concept labeled in each of the languages that also are used on the other concepts.
+This is not always possible, but incompleteness of language coverage for some concepts can indicate shortcomings of the vocabulary.
+	Severity level: INFO
+	\item \textbf{{\em SKOS-C-LANGUAGE-TAG-CARDINALITY-03\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - No Common Language}:}}
+	Checks if all concepts have at least one common language, i.e. they have assigned at least one literal in the same language. 
+	Severity level: INFO
+\end{itemize}
+
 \subsection{Whitespace Handling}
@@
 
-\subsection{\underline{Hierarchies}}
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-HIERARCHIES-01}}: there must be exactly one root in the hierarchy of DDI concepts. 
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DATA-CUBE-C-HIERARCHIES-01:}}
+\subsection{\underline{Structure}}
+
+SKOS is based on RDF, which is a graph-based data model.
+Therefore we can concentrate on the vocabulary's graph-based structure for assessing the quality of SKOS vocabularies and apply graph- and network-analysis techniques.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-STRUCTURE-01}}: there must be exactly one root in the hierarchy of DDI concepts. 
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em DATA-CUBE-C-STRUCTURE-01:}}
 	Codes from hierarchy (\emph{IC-20} \cite{CyganiakReynolds2014}) -  
 	If a dimension property has a \emph{qb:HierarchicalCodeList} with a non-blank \emph{qb:parentChildProperty} then the value of that dimension property on every \emph{qb:Observation} must be reachable from a root of the hierarchy using zero or more hops along the \emph{qb:parentChildProperty} links.
-	\item \textbf{{\em DATA-CUBE-C-HIERARCHIES-02:}}
+	\item \textbf{{\em DATA-CUBE-C-STRUCTURE-02:}}
 	Codes from hierarchy (inverse) (\emph{IC-21} \cite{CyganiakReynolds2014}) -  
@@
 
-\section{SKOS-Related RDF Validation Requirements / Constraint Types}
-\tb{from other paper of Antoine}
+\begin{itemize}
+	\item \textbf{{\em SKOS-C-STRUCTURE-01\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Orphan Concepts}:}}
+	Orphan Concepts:
+  An orphan concept is a concept without any associative or hierarchical relations.
+It might have attached literals like e.g., labels, but is not connected to any other resource, lacking valuable context information.
+A controlled vocabulary that contains many orphan concepts is less usable for search and retrieval use cases, because, e.g., no hierarchical query expansion can be performed on search terms to find documents with more general content.
+	Iteration over all concepts in the vocabulary and returning that don't have associated resources using (subproperties of) \emph{skos:semanticRelation}. 
+  Severity level: INFO
+	\item \textbf{{\em SKOS-C-STRUCTURE-02\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Disconnected Concept Clusters}:}}
+	Disconnected Concept Clusters:
+	Checking the connectivity of the graph, it is possible to identify all weakly connected components.
+These datasets form "islands" in the vocabulary and might be caused by incomplete data acquisition, "forgotten" test data, outdated terms and the like.
+	Implementation: Creation of an undirected graph that includes all non-orphan concepts as nodes and all semantic relations as edges.
+Tarjan's algorithm then finds and returns all weakly connected components.
+	Severity level: INFO
+	\item \textbf{{\em SKOS-C-STRUCTURE-03\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Cyclic Hierarchical Relations}:}}
+	Cyclic Hierarchical Relations: 
+	Although perfectly consistent with the SKOS data model, cyclic relations may reveal a logical problem in the thesaurus.
+Consider the following example: "decision" $\rightarrow$ "problem resolution" $\rightarrow$ "problem" ($\rightarrow$ "decision": here the cycle is closed).
+The concepts are connected using \emph{skos:broader} relationships (indicated with "$\rightarrow$").
+Due to the fact that a thesaurus is in many cases a product of consensus between the contributors (or just the decision of one dedicated thesaurus manager), it will be almost impossible to automatically resolve the cycle (i.e.
+deleting an edge).
+	Implementation: Construction of a graph having all concepts as nodes and the set of edges being \emph{skos:broader} relations. 
+	Severity level: INFO
+	\item \textbf{{\em SKOS-C-STRUCTURE-04\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Valueless Associative Relations}:}}
+	Valueless Associative Relations:
+	Two concepts are sibling, but also connected by an associative relation. In that context, the associative relation is not necessary. See ISO\_DIS\_25964-1, 11.3.2.2 
+	Implementation:
+	Identification of all pairs of concepts that have the same broader or narrower concepts, i.e. they are "sibling terms". All siblings that are related by a \emph{skos:related} property are returned. 
+	Severity level: INFO
+	\item \textbf{{\em SKOS-C-STRUCTURE-05\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Solely Transitively Related Concepts}:}}
+	Solely Transitively Related Concepts:
+	\emph{skos:broaderTransitive} and \emph{skos:narrowerTransitive} are, according to the SKOS reference document, "not used to make assertions", so they should not be the only relations hierarchically relating two concepts.
+	Implementation: Identification of all concept pairs that are related by \emph{skos:broaderTransitive} or \emph{skos:narrowerTransitive} properties but not by their \emph{skos:broader} and \emph{skos:narrower} subproperties.
+	Severity level: INFO
+	\item \textbf{{\em SKOS-C-STRUCTURE-06\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Unidirectionally Related Concepts}:}}
+	Unidirectionally Related Concepts:
+	Reciprocal relations (e.g., \emph{broader/narrower, related, hasTopConcept/topConceptOf}) should be included in the controlled vocabularies to achieve better search results using SPARQL in systems without reasoner support.
+	Implementation:
+	This issue is checked without inference of \emph{owl:inverseOf} properties.
+We iterate over all triples and check for each property if an inverse property is defined in the SKOS ontology and if the respective statement using this property is included in the vocabulary.
+If not, the resources associated with this property are returned.
+	Severity level: INFO
+	\item \textbf{{\em SKOS-C-STRUCTURE-07\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Omitted Top Concepts}:}}
+	Omitted Top Concepts:
+	A vocabulary should provide "entry points" to the data to provide “efficient access” (SKOS primer) and guidance for human users. 
+	Implementation:
+	For every ConceptScheme in the controlled vocabulary, a SPARQL query is issued finding resources that are associated with this ConceptScheme by one of the properties \emph{skos:hasTopConcept} or \emph{skos:topConceptOf}.
+Top concepts are also concepts having no broader concept.
+	Severity level: SHOULD
+\end{itemize}
+
+\subsection{\underline{Labeling and Documentation}}
+
+\begin{itemize}
+	\item \textbf{{\em SKOS-C-LABELING-AND-DOCUMENTATION-01\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Undocumented Concepts}:}}
+	Undocumented Concepts:
+  The SKOS standard defines a number of properties useful for documenting the meaning of the concepts in a thesaurus also in a human-readable form.
+Intense use of these properties leads to a well-documented thesaurus which should also improve its quality.
+	Iteration over all concepts in the vocabulary and find those not using one of \emph{skos:note}, \emph{skos:changeNote}, \emph{skos:definition}, \emph{skos:editorialNote}, \emph{skos:example}, \emph{skos:historyNote}, or \emph{skos:scopeNote}.
+  Severity level: INFO
+	\item \textbf{{\em SKOS-C-LABELING-AND-DOCUMENTATION-02\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Overlapping Labels}:}}
+	Overlapping Labels:
+	This is a generalization of a recommendation in the SKOS primer, that “no two concepts have the same preferred lexical label in a given language when they belong to the same concept scheme”.
+This could indicate missing disambiguation information and thus lead to problems in autocompletion application.
+	Severity level: INFO
+	\item \textbf{{\em SKOS-C-LABELING-AND-DOCUMENTATION-03\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Missing Labels}:}}
+	Missing Labels:
+	To make the vocabulary more convenient for humans to use, instances of SKOS classes (Concept, ConceptScheme, Collection) should be labeled using e.g., \emph{skos:prefLabel}, \emph{altLabel}, \emph{rdfs:label}, \emph{dc:title}.
+	Severity level: INFO
+	\item \textbf{{\em SKOS-C-LABELING-AND-DOCUMENTATION-04\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Unprintable Characters in Labels}:}}
+	Unprintable Characters in Labels:
+	\emph{pref/alt/hiddenlabels} contain characters that are not alphanumeric characters or blanks.
+	Severity level: INFO
+	\item \textbf{{\em SKOS-C-LABELING-AND-DOCUMENTATION-05\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Empty Labels}:}}
+	Empty Labels:
+	Labels also need to contain textual information to be useful, thus we find all SKOS labels with length 0 (after removing whitespaces). 
+	Severity level: INFO
+	\item \textbf{{\em SKOS-C-LABELING-AND-DOCUMENTATION-06\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Ambiguous Notation References}:}}
+	Ambiguous Notation References:
+	Concepts within the same concept scheme should not have identlical \emph{skos:notation} literals. 
+	Severity level: INFO
+\end{itemize}
+
+\section{SKOS-Related Constraint Types}
 

### 2015-02-19 paper/paper7/paper7-appendix.tex
added Heike's ideas

@@
 	Severity level: SHOULD
+	\item \textbf{{\em SKOS-C-STRUCTURE-08\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Top Concepts Having Broader Concepts}:}}
+	Top Concepts Having Broader Concepts:
+	Concepts "internal to the tree" should not be indicated as top concepts.
+	Implementation:
+	A SPARQL query finds all top concepts (being defined by one of the properties \emph{skos:hasTopConcept} or \emph{skos:topConceptOf}) having associated a broader concept. 
+	Severity level: ERROR
+	\item \textbf{{\em SKOS-C-STRUCTURE-09\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Hierarchical Redundancy}:}}
+	Hierarchical Redundancy:
+	As stated in the SKOS reference document, \emph{skos:broader} and \emph{skos:narrower} are not transitive properties.
+However, they are subproperties of \emph{skos:broaderTransitive} and \emph{skos:narrowerTransitive} which enables inference of a "transitive closure".
+This, in fact, leaves it up to the user to interpret wheter a vocabulary's hierarchical structure is seen as transitive or not.
+In the former case, this check can be useful.
+It finds pairs of concepts (A,B) that are directly hierarchically related but there also exits an hierarchical path through a concept C that connects A and B.
+	Severity level: INFO
+	\item \textbf{{\em SKOS-C-STRUCTURE-10\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Reflexive Relations}:}}
+	Reflexive Relations:
+	Concepts related to themselves. 
+	Severity level: INFO
 \end{itemize}

### 2015-02-19 paper/paper7/paper7.tex
added Heike's ideas

@@
 
-- European data in Missy
+- DESCRIPTION OF EUROSTAT -
+Eurostat\footnote{\url{http://ec.europa.eu/eurostat}} provides publicly available European aggregated data.
 
-- multiple countries (+) $-->$ region in query
+SBE researchers have a strong interest in the availability of childcare services across the EU Member States.
+
+The aggregated variable \emph{formal childcare} \footnote{\url{http://appsso.eurostat.ec.europa.eu/nui/show.do?dataset=ilc_caindformal&lang=en}}
+stores the measured formal childcare in percent over the population of each age group.
+
+The present data collection refers to data on formal childcare and other types of care by \emph{year}, \emph{duration} (0 hours, 1 to 29 hours a usual week; 30 hours or more a usual week), \emph{age} of the child (0-2 years; 3 to admission age for compulsory school; admission age for compulsory school to 12) and \emph{country}.
+
+The metadata on the aggregated data can be downloaded in different forms like CSV files.
+
+For a broader view of the data framework and more detailed analyses we have to refer to the metadata on person-level data collected for the series EU-SILC (European Union Statistics on Income and Living Conditions)\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}.
+\emph{Formal childcare} is calculated/composed out of six person-level variables: 
+(1) Education at pre-school\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC/2011/Cross-sectional/original#2011-Cross-sectional-RL010}},
+(2) Education at compulsory school,
+(3) Child care at centre-based services,
+(4) Child care at day-care centre,
+(5) Child care by a professional child-minder, and
+(6) Child care by grand-parents, household members, relatives, friends, neighbours.
+For each person-level variable detailed metadata (definitions, descriptions, theoretical concepts, questions, code lists, frequencies, countries) is given which enables the researchers to replicate the results shown in the aggregated data table from Eurostat.
+
+\emph{MISSY (Microdata Information System)}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}} is an online service platform that provides systematically structured metadata for official statistics.
+This includes data documentation at the study and variable level as well as documentation materials, tools and further information.
+Missy provides metadata on European person-level data sets.
+
+-----
+
+comparisons:
+
+- compare formal childcare for available countries (for which the variable is collected for the survey) with other countries in Europe
+
+- compare with non European countries e.g. OSCE
+
+prerequisites / validation for comparison:
+
+- variable must be present
+
+- code lists must be similar or ideally identical (strong severity level / or weaker severity level if one wants to have only an overview)
+
+-----
+
+use of XKOS:
+
+- classification system e.g. NACE
+
+- ask Franck if INSEE already expressed well known classification systems with XKOS
+
+-----
 
@@
 - validation against minimal set of requirements / constraints
+
+-----
+
+severity level:
+
+- use case specific severity levels
+- users specify severity level of constraint types according to their individual use case
+- for some use case the severity level of a given constraint type may be different as for another use case
 
@@
 
+- variable does not have associated codes / categories
+
 \textbf{Theoretical Concepts.}
@@
 The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
+The severity level of this constraint is a warning and not an error, as research can be continued without an associated theoretical concept.
 
@@
 
+\url{http://www.xmlmind.com/xmleditor/_distrib/doc/xmltool/xsd_structure_limitations.html}
+
+\url{https://msdn.microsoft.com/en-us/library/aa468554.aspx}
+
 \textbf{RDF Data Cube Vocabulary.}

### 2015-02-20 paper/paper7/paper7.tex
running example

--- 2015-02-08 paper/paper7/paper7.tex
@@
 
-- European data in Missy
+- DESCRIPTION OF EUROSTAT -
+Eurostat\footnote{\url{http://ec.europa.eu/eurostat}} provides publicly available European aggregated data.
+ SBE researchers have a strong interest in the availability of childcare services across the European Union Member States.
+The variable \emph{formal childcare}\footnote{\url{http://appsso.eurostat.ec.europa.eu/nui/show.do?dataset=ilc_caindformal&lang=en}}
+stores the measured formal childcare in percent over the population of each age group.
+The present data collection refers to data on formal childcare and other types of care by the variables \emph{year}, \emph{duration} (0 hours, 1 to 29 hours a usual week; 30 hours or more a usual week), \emph{age} of the child (0-2 years; 3 to admission age for compulsory school; admission age for compulsory school to 12) and \emph{country}.
+Eurostat provides the metadata on the aggregated data in different forms like CSV files.
 
-- multiple countries (+) $-->$ region in query
+For a broader view of the data framework and more detailed analyses we have to refer to the metadata on person-level data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}.
+The \emph{Microdata Information System (MISSY)}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}} is an online service platform that provides systematically structured metadata for official statistics on European person-level data sets.
+This includes data documentation at the study and variable level as well as documentation materials, tools and further information.
+The calculation of the aggregated variable \emph{formal childcare} is based on six person-level variables: 
+(1) Education at pre-school\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC/2011/Cross-sectional/original#2011-Cross-sectional-RL010}},
+(2) Education at compulsory school,
+(3) Child care at centre-based services,
+(4) Child care at day-care centre,
+(5) Child care by a professional child-minder, and
+(6) Child care by grand-parents, household members, relatives, friends, neighbours.
+For each person-level variable detailed metadata (definitions, descriptions, theoretical concepts, questions, code lists, frequencies, countries) is given which enables the researchers to replicate the results shown in the aggregated data tables from Eurostat.
 
-\section{ideas}
+Metadata on person-level data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
+One common research question is to compare 
+\emph{formal childcare} between countries, for which the variable is collected for the individual survey, and other European or non European countries (e.g. OSCE).
+
+\section{Represent Metadata and Data in RDF}
+
+\emph{Data Cube} is a vocabulary to represent metadata on multi-dimensional aggregate data.
+
+\begin{ex}
+EXAMPLE
+\end{ex}
+
+\emph{PHDD} is a vocabulary to represent aggregated data in a rectangular format. 
+The data could be either represented in records with character-separated values (CSV) or in records with fixed length.
+
+\begin{ex}
+EXAMPLE
+\end{ex}
+
+\emph{Disco} is a vocabulary to represent person-level data in RDF.
+
+\begin{ex}
+EXAMPLE
+\end{ex}
+
+\emph{DCAT} enables to represent aggregated and person-level data inside of data collections like repositories, catalogs, or archives.
+
+\begin{ex}
+EXAMPLE
+\end{ex}
+
+The \emph{Simple Knowledge Organization System (SKOS)}...
+
+\begin{ex}
+EXAMPLE
+\end{ex}
+
+\emph{XKOS}\footnote{\url{https://github.com/linked-statistics/xkos}} is a \emph{SKOS} extension to describe formal statistical classifications like the profession classification \emph{ISCO}.
+
+\begin{ex}
+EXAMPLE
+\end{ex}
+
+\section{RDF Validation of Metadata and Data}
+
+-----
 
@@
 
-\section{RDF Representation of Metadata}
+-----
 
-\section{RDF Validation of Metadata}
+severity level:
+
+- use case specific severity levels
+
+- users specify severity level of constraint types according to their individual use case
+
+- for some use case the severity level of a given constraint type may be different as for another use case
+
+-----
 
@@
 
-\textbf{XKOS validation}
-only 1 sentence / only special case / e.g. profession classification ISCO
+%\subsection{Content-Driven Validation}
 
-extended version of SKOS – XKOS – to describe formal statistical classifications.
+\subsection{Aggregated (Meta)Data}
 
-\subsection{Content-Driven Validation}
+\subsection{Person-Level (Meta)Data}
+
+\textbf{Studies.}
+Each study must have an abstract. 
+If an abstract is missing a study title may be sufficient in many cases.
+
+\textbf{Variables.}
+
+- variable does not have associated codes / categories
 
@@
 The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
+The severity level of this constraint is a warning and not an error, as research can be continued without an associated theoretical concept.
 
-\textbf{Search for Studies.}
-Each study must have an abstract. 
-If an abstract is missing a study title may be sufficient in many cases.
+\textbf{Comparison.}
 
-\subsection{Technology-Driven Validation}
+- variable must be present
 
-\section{RDF Validation of Data}
+- code lists must be similar or ideally identical (strong severity level / or weaker severity level if one wants to have only an overview)
+
+(1) variable definitions are available
+
+(2) if code lists are properly structured
+
+(3) if for each code an associated category (a human-readable label) is specified.
+
+\textbf{DCAT Validation}
+
+\textbf{SKOS and XKOS Validation}
+
+- SKOS validation of hierarchies of theoretical concepts
+
+XKOS Validation:
+
+- classification system e.g. NACE, profession classification ISCO
+
+- ask Franck if INSEE already expressed well known classification systems with XKOS
+
+%\subsection{Technology-Driven Validation}
 

### 2015-02-20 paper/paper7/paper7-appendix.tex
RDF Validation of Metadata and Data

@@
 	are compared variables represented in a compatible way, i.e. are the variables' code lists theoretically comparable?
+		\begin{itemize}
+		\item severity level: WARNING
+	\end{itemize}
 	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-02}}: 
 	are variable definitions (\emph{dcterms:description}) available for each variable (\emph{disco:Variable}) to compare?
+		\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-03}}:
 	are code lists structured properly for each variable (\emph{disco:Variable}) to compare?
+		\begin{itemize}
+		\item severity level: WARNING
+	\end{itemize}
 	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-04}}:
 	is for each code (for each variable (\emph{disco:Variable}) to compare) an associated category (a human-readable label) specified?
+		\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-05}}:
+	each (\emph{disco:Variable}) to compare must be present.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-CONDITIONAL-PROPERTIES-01:}}
+	\item \textbf{{\em DISCO-C-CONDITIONAL-PROPERTIES-01}}:
   If a {\em skos:Concept} represents a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
 then the property {\em disco:isValid} has to be stated indicating if the code is valid ('true') or missing ('false').
+	\item \textbf{{\em DISCO-C-CONDITIONAL-PROPERTIES-02}}:
+	If the abstract (\emph{dcterms:abstract}) of a \emph{disco:Study} is missing, a study title (\emph{dcterms:title}) has to be stated.
 \end{itemize}

### 2015-02-20 paper/paper7/paper7.tex
RDF Validation of Metadata and Data

@@
 
-\tb{we use data in singular form / we use data set instead of dataset / We use person-level data and not microdata}
+\tb{terminology: we use data in singular form / we use data set instead of dataset / We use person-level data and not microdata}
 
@@
 
------
+Bosch et al. identified in total 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
+We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement (constraint type) in detail and give examples for each (represented by different constraint languages).
+This technical report also contains mappings to description logics to logically underpin each requirement and to determine which description logics constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
+Bosch et al.
+recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/XXXXX}} (serving as appendix of this paper) in which we describe RDF constraints to validate metadata on person-level and aggregated data.
+We assign each constraint to constraint types corresponding to RDF validation requirements or to data model specific constraint types
+\cite{BoschZapilkoWackerowEckert2015}.
 
-- different sets of constraints for different use cases / use case specific constraints
-
-- validation against minimal set of requirements / constraints
+We distinguish two validation types:
+\emph{Content-Driven Validation} contains the set of constraints ensuring that the data is consistent with the intended semantics of data models,
+i.e. the integrity of the data according to data models.
+\emph{Technology-Driven Validation} includes the set of constraints which can be generated automatically out of defined data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges.
+We determined the default \emph{severity level}\footnote{Corresponds to \emph{R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS}} for each constraint indicating how serious the violation of the constraint is.
+The continuum of \emph{severity levels} ranges from informational via warning and error to fatal error. 
+Although we provide default \emph{severity levels} for each constraint, users should be able to specify \emph{severity levels} of constraints they need to validate within the context of their individual use cases.
+Therefore, use case specific \emph{severity levels} can be defined for constraints.
 
 -----
-
-severity level:
-
-- use case specific severity levels
-
-- users specify severity level of constraint types according to their individual use case
-
-- for some use case the severity level of a given constraint type may be different as for another use case
-
------
+%
+%- different sets of constraints for different use cases / use case specific constraints
+%
+%- validation against minimal set of requirements / constraints
+%
+%-----
 
 RDF validation scenarios require the closed-world assumption (CWA) (i.e., a statement is inferred to be false if it cannot be proved to be true).
-
-- different severity levels for different validation types
 
@@
 
-\textbf{Studies.}
-Each study must have an abstract. 
-If an abstract is missing a study title may be sufficient in many cases.
+\textbf{Surveys.}
+Each survey must have an abstract\footnote{\emph{ DISCO-C-DATA-PROPERTY-FACETS-01}}. 
+If the abstract of the survey is missing, a title of the survey has to be stated\footnote{\emph{DISCO-C-CONDITIONAL-PROPERTIES-02}}.
 
@@
 
-\textbf{Comparison.}
-
-- variable must be present
-
-- code lists must be similar or ideally identical (strong severity level / or weaker severity level if one wants to have only an overview)
-
-(1) variable definitions are available
-
-(2) if code lists are properly structured
-
-(3) if for each code an associated category (a human-readable label) is specified.
+\textbf{Variable Comparisons\footnote{Constraint types: \emph{DISCO-C-COMPARISON-VARIABLES-XX}}.}
+One very common research question is to compare variables of multiple surveys or countries.
+To compare variables, 
+(1) variables and (2) variable definitions must be present,
+(3) code lists must be structured properly,
+(4) for each code an associated category (human-readable label) must be specified, and
+(5) code lists must either be identical or at least similar.
+If a researcher wants to get a first overview over comparable variables (use case 1), 
+the first three constraints may be sufficient for this purpose.
+Thus, the \emph{severity level} of the first three constraints is stronger than the \emph{severity level} of the next constraints.
+If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the remaining constraints is also more serious.
 
@@
 
-%\subsection{Technology-Driven Validation}
-
 \textbf{Data Integration.}
 use RDF validation for data integration
+
+\subsection{Technology-Driven Validation}
 

### 2015-02-21 paper/paper7/paper7-appendix.tex
technology-driven validation

@@
   Only {\em disco:Question}s, e.g., can have {\em disco:responseDomain} relationships (\ms{$\exists$ responseDomain.$\top$ $\sqsubseteq$ Question}).
-	Severity level: ERROR
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
   Only {\em qb:Observation}s, e.g., can have {\em qb:dataSet} relationships (\ms{$\exists$ dataSet.$\top$ $\sqsubseteq$ Observation}).
-	Severity level: ERROR
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
   Only {\em dcat:Catalog}s, e.g., can have {\em dcat:dataset} relationships (\ms{$\exists$ dataset.$\top$ $\sqsubseteq$ Catalog}).
-	Severity level: ERROR
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
   Only {\em phdd:Table}s, e.g., can have {\em phdd:isStructuredBy} relationships (\ms{$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table}).
-	Severity level: ERROR
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em SKOS-C-PROPERTY-DOMAIN-01:}} 
+	{\em Property Domain} constraints are defined for each \emph{SKOS} object and data property.
+	Only {\em skos:ConceptSchemes}, e.g., can have {\em skos:hasTopConcept} relationships (\ms{$\exists$ hasTopConcept.$\top$ $\sqsubseteq$ ConceptScheme}).
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em XKOS-C-PROPERTY-DOMAIN-01:}} 
+	{\em Property Domain} constraints are defined for each \emph{XKOS} object and data property.
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
   {\em disco:caseQuantity} relationships, e.g., can only point to literals of the datatype {\em xsd:nonNegativeInteger} (\ms{$\top$ $\sqsubseteq$ $\forall$ caseQuantity.nonNegativeInteger}).
-	Severity level: ERROR
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
   {\em qb:order} relationships, e.g., can only point to literals of the datatype {\em xsd:string} (\ms{$\top$ $\sqsubseteq$ $\forall$ order.string}).
-	Severity level: ERROR
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
   {\em dcat:bytes} relationships, e.g., can only point to literals of the datatype {\em xsd:integer} (\ms{$\top$ $\sqsubseteq$ $\forall$ bytes.integer}).
-	Severity level: ERROR
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
   {\em phdd:caseQuantity} relationships, e.g., can only point to literals of the datatype {\em xsd:nonNegativeInteger} (\ms{$\top$ $\sqsubseteq$ $\forall$ caseQuantity.nonNegativeInteger}).
-	Severity level: ERROR
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em SKOS-C-PROPERTY-RANGES-01:}} 
+	{\em Property Range} constraints are defined for each \emph{SKOS} object and data property.
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em XKOS-C-PROPERTY-RANGES-01:}} 
+	{\em Property Range} constraints are defined for each \emph{XKOS} object and data property.
+  {\em xkos:belongsTo} relationships, e.g., can only point to instances of the class {\em skos:Concept} (\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}).
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 parents. DLs support such statements by allowing us to form complex concepts such as
-the \emph{intersection}\footnote{\ms{R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS}, \ms{R-16-CONJUNCTION-OF-DATA-RANGES}} (also called \emph{conjunction})
+the \emph{intersection}\footnote{\emph{R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS}, \emph{R-16-CONJUNCTION-OF-DATA-RANGES}} (also called \emph{conjunction})
 which denotes the set of individuals that are both female and parents. A complex concept
@@
 	Slice Keys must be declared (\emph{IC-7} \cite{CyganiakReynolds2014}) -
-	Every \emph{qb:SliceKey} must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition}. 
+	Every \emph{qb:SliceKey} must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}). 
 \end{itemize}
@@
 \begin{itemize}
+	\item \textbf{{\em DATA-CUBE-C-UNIVERSAL-QUANTIFICATIONS-01:}}
+	\emph{Universal quantifications} are defined for each \emph{Data Cube} object and data property.
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em DCAT-C-UNIVERSAL-QUANTIFICATIONS-01:}}
+	\emph{Universal quantifications} are defined for each \emph{DCAT} object and data property.
+	Only {\em dcat:Catalogs} can have {\em dcat:dataset} relationships to {\em dcat:Datasets} (\ms{Catalog $\sqsubseteq$ $\forall$ dataset.Dataset}).
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
 	\item \textbf{{\em DISCO-C-UNIVERSAL-QUANTIFICATIONS-01:}}
+	\emph{Universal quantifications} are defined for each \emph{Disco} object and data property.
   Only {\em disco:LogicalDataSet}s can have {\em disco:aggregation} relationships to {\em qb:DataSet}s (\ms{LogicalDataSet $\sqsubseteq$ $\forall$ aggregation.DataSet}).
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em PHDD-C-UNIVERSAL-QUANTIFICATIONS-01:}}
+	\emph{Universal quantifications} are defined for each \emph{PHDD} object and data property.
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em SKOS-C-UNIVERSAL-QUANTIFICATIONS-01:}}
+	\emph{Universal quantifications} are defined for each \emph{SKOS} object and data property.
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em XKOS-C-UNIVERSAL-QUANTIFICATIONS-01:}}
+	\emph{Universal quantifications} are defined for each \emph{XKOS} object and data property.
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 \begin{itemize}
+	\item \textbf{{\em DATA-CUBE-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
+	{\em Minimum Qualified Cardinality Restrictions} constraints are defined for each \emph{Data Cube} object and data property.
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em DCAT-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
+	{\em Minimum Qualified Cardinality Restrictions} constraints are defined for each \emph{DCAT} object and data property.
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
 	\item \textbf{{\em DISCO-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
-A {\em disco:Questionnaire} has at least one {\em disco:question} relationship to {\em disco:Question} (\ms{Questionnaire $\sqsubseteq$ $\geq$1 question.Question}).
+	{\em Minimum Qualified Cardinality Restrictions} constraints are defined for each \emph{Disco} object and data property.
+  A {\em disco:Questionnaire}, e.g., has at least one {\em disco:question} relationship to {\em disco:Questions} (\ms{Questionnaire $\sqsubseteq$ $\geq$1 question.Question}).
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em PHDD-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
+	{\em Minimum Qualified Cardinality Restrictions} constraints are defined for each \emph{PHDD} object and data property.
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
+	A {\em disco:Variable} has at most one {\em disco:concept} relationship to a theoretical concept ({\em skos:Concept}) (\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}).
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
 \subsection{Exact Unqualified Cardinality Restrictions*}
@@
 	Each \emph{qb:Slice} must have exactly one associated \emph{qb:sliceStructure}. 
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 A {\em disco:Question} has exactly 1 {\em disco:universe} relationship to {\em disco:Universe} (\ms{Question $\sqsubseteq$ $\geq$1 universe.Universe $\sqcap$ $\leq$1 universe.Universe}).
+  \begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 	Unique data set (\emph{IC-1} \cite{CyganiakReynolds2014}) -  
-	Every \emph{qb:Observation} has (\emph{qb:dataSet}) exactly one associated \emph{qb:DataSet}. 
+	Every \emph{qb:Observation} has (\emph{qb:dataSet}) exactly one associated \emph{qb:DataSet} (\ms{Observation $\sqsubseteq$ $\geq$1 dataSet.DataSet $\sqcap$ $\leq$1 dataSet.DataSet}). 
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
 	\item \textbf{{\em DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02:}}
 	Unique DSD (\emph{IC-2} \cite{CyganiakReynolds2014}) -  
-	Every \emph{qb:DataSet} has (\emph{qb:structure}) exactly one associated \emph{qb:DataStructureDefinition}. 
+	Every \emph{qb:DataSet} has (\emph{qb:structure}) exactly one associated \emph{qb:DataStructureDefinition} (\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition $\sqcap$ $\leq$1 structure.DataStructureDefinition}).
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 	\item \textbf{{\em DISCO-C-CONTEXT-SPECIFIC-EXCLUSIVE-OR-OF-PROPERTY-GROUPS-01:}}
-Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as DDI concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as DDI codes and categories), but not both.
+Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes and categories), but not both.
 

### 2015-02-21 paper/paper7/paper7.tex
technology-driven validation

@@
 We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement (constraint type) in detail and give examples for each (represented by different constraint languages).
-This technical report also contains mappings to description logics to logically underpin each requirement and to determine which description logics constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
+The knowledge representation formalism {\em Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
+Therefore, this technical report contains mappings to DL to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
 Bosch et al.
@@
 We determined the default \emph{severity level}\footnote{Corresponds to \emph{R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS}} for each constraint indicating how serious the violation of the constraint is.
-The continuum of \emph{severity levels} ranges from informational via warning and error to fatal error. 
-Although we provide default \emph{severity levels} for each constraint, users should be able to specify \emph{severity levels} of constraints they need to validate within the context of their individual use cases.
-Therefore, use case specific \emph{severity levels} can be defined for constraints.
+The continuum of severity levels ranges from informational via warning and error to fatal error. 
+Although we provide default severity levels for each constraint, users should be able to specify severity levels of constraints they need to validate within the context of their individual use cases.
+Therefore, use case specific severity levels can be defined for constraints.
 
@@
 \textbf{Surveys.}
-Each survey must have an abstract\footnote{\emph{ DISCO-C-DATA-PROPERTY-FACETS-01}}. 
+Each survey must have an abstract\footnote{\emph{DISCO-C-DATA-PROPERTY-FACETS-01}}. 
 If the abstract of the survey is missing, a title of the survey has to be stated\footnote{\emph{DISCO-C-CONDITIONAL-PROPERTIES-02}}.
@@
 \textbf{Theoretical Concepts.}
-Variables must have at least one relation to a theoretical concept.
-The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
-The severity level of this constraint is a warning and not an error, as research can be continued without an associated theoretical concept.
+Variables must have at least one relationship to a theoretical concept\footnote{{\em DISCO-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01}}.
+%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
+The variable \emph{Education at pre-school}, e.g., is associated with the theoretical concept \emph{education}. 
+The severity level of this constraint is \emph{warning} and not \emph{error}, as research can be continued without an associated theoretical concept.
 
-\textbf{Variable Comparisons\footnote{Constraint types: \emph{DISCO-C-COMPARISON-VARIABLES-XX}}.}
-One very common research question is to compare variables of multiple surveys or countries.
+One very common research question is to \emph{compare variables}\footnote{Constraint types: \emph{DISCO-C-COMPARISON-VARIABLES-XX}} of multiple surveys or countries.
 To compare variables, 
@@
 the first three constraints may be sufficient for this purpose.
-Thus, the \emph{severity level} of the first three constraints is stronger than the \emph{severity level} of the next constraints.
+Thus, the severity level of the first three constraints is stronger than the severity level of the next constraints.
 If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the remaining constraints is also more serious.
+
+Constraints of the constraint type \emph{Context-Specific Exclusive OR of Property Groups}
+restrict individuals of given classes to have only one of multiple property groups\footnote{{\em R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC}}.
+Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes and categories), but not both\footnote{\emph{DISCO-C-CONTEXT-SPECIFIC-EXCLUSIVE-OR-OF-PROPERTY-GROUPS-01:}}.
+
+\begin{DL}
+Concept $\sqsubseteq$ ($\neg$ D $\sqcap$ C) $\sqcup$ (D $\sqcap$ $\neg$ C) \\ 
+D $\equiv$ A $\sqcap$ B \\
+A $\sqsubseteq$ $\geq$ 1 notation.string $\sqcap$ $\leq$ 1 notation.string \\
+B $\sqsubseteq$ $\geq$ 1 prefLabel.string $\sqcap$ $\leq$ 1 prefLabel.string \\
+C $\sqsubseteq$ $\geq$ 1 definition.string $\sqcap$ $\leq$ 1 definition.string \\
+\end{DL}
 
@@
 \subsection{Technology-Driven Validation}
+
+Constraints of some constraint types are directly and automatically derived from conceptual models of multiple vocabularies.
+This way, \emph{property domains and ranges, universal and existential quantifications, minimum, maximum, and exact cardinality restrictions} are defined for each object and data property of vocabularies against which one wish to validate.
+As these constraints directly depend on the intended semantics of data models, associated severity levels are very strong.
+
+{\em Property Domains}\footnote{{\em R-25-OBJECT-PROPERTY-DOMAIN}, {\em R-26-DATA-PROPERTY-DOMAIN}} and {\em Ranges}\footnote{{\em R-28-OBJECT-PROPERTY-RANGE}, {\em R-35-DATA-PROPERTY-RANGE}}restrict domains and ranges of properties.
+Only {\em skos:ConceptSchemes}, e.g., can have {\em skos:hasTopConcept} relationships (\ms{$\exists$ hasTopConcept.$\top$ $\sqsubseteq$ ConceptScheme}) and
+{\em xkos:belongsTo} relationships can only point to instances of the class {\em skos:Concept} (\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}).
+A \emph{universal quantification}\footnote{{\em R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}} contains all those individuals that are connected by a property only to individuals/literals that are instances of particular classes  or data ranges.
+Only {\em dcat:Catalogs}, e.g., can have {\em dcat:dataset} relationships to {\em dcat:Datasets} (\ms{Catalog $\sqsubseteq$ $\forall$ dataset.Dataset}).
+An \emph{existential quantification}\footnote{{\em R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}} contains all those individuals that are connected by a property to individuals/literals that are instances of given classes or data ranges.
+Every \emph{qb:SliceKey}, e.g., must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}).
+\emph{Minimum/maximum/exact qualified cardinality restrictions}\footnote{\emph{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES, \\ R-76-MAXIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES, \\ R-74-EXACT-QUALIFIED-CARDINALITY-ON-PROPERTIES}} contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals that are instances of particular classes or data ranges.
+\emph{Minimum qualified cardinality restrictions} are defined for each property of multiple vocabularies like \emph{Disco}.
+A \emph{disco:Questionnaire}, e.g., has at least one {\em disco:question} relationship to {\em disco:Questions} (\ms{Questionnaire $\sqsubseteq$ $\geq$1 question.Question}),
+a {\em disco:Variable} has at most one {\em disco:concept} relationship to a theoretical concept ({\em skos:Concept}) (\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}), and every \emph{qb:DataSet} has (\emph{qb:structure}) exactly one associated \emph{qb:DataStructureDefinition} (\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition $\sqcap$ $\leq$1 structure.DataStructureDefinition}).
+%\footnote{\emph{DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02}}.
+
+-----
+
+reasoning constraints / sub-classes / sub-properties
 

### 2015-02-21 paper/paper7/paper7-appendix.tex
technology-driven validation

@@
 A \emph{subclass axiom}\footnote{{\em R-100-SUBSUMPTION}} ({\em concept inclusion} in DL) states that the class \emph{C1} is a subclass of the class \emph{C2} - \emph{C1} is more specific than \emph{C2},
-i.e. each resources of the class \emph{C1} must also be part of the class extension of \emph{C2}.
+i.e. each resource of the class \emph{C1} must also be part of the class extension of \emph{C2}.
 
@@
 An object property irreflexivity axiom \emph{IrreflexiveObjectProperty( OPE )} states that the object property expression \emph{OPE} is irreflexive - that is, no individual is connected by \emph{OPE} to itself.
+
+\begin{itemize}
+  \item \textbf{{\em DISCO-C-IRREFLEXIVE-OBJECT-PROPERTIES-01:}}
 	In \emph{Disco}, every object property is irreflexive.
-
-\begin{itemize}
-  \item \textbf{{\em DISCO-C-IRREFLEXIVE-OBJECT-PROPERTIES-01:}}
-Within the Disco context, no individual is connected by the object property {\em instrument} to itself (\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists  instrument . Self$}).
+  No individual is connected by the object property {\em instrument} to itself (\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists  instrument . Self$}).
 \end{itemize}
@@
 A \emph{disjoint properties axiom}\footnote{\emph{R-9-DISJOINT-PROPERTIES}} states that all of the properties are pairwise disjoint; 
-that is, no individual \emph{x} can be connected to an individual \emph{y} by these properties.
+that is, no individual \emph{x} can be connected to an individual/literal \emph{y} by these properties.
+
+\begin{itemize}
+	\item \textbf{{\em DATA-CUBE-C-DISJOINT-PROPERTIES-01:}} 
+	All \emph{Data Cube} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
+  The properties \emph{qb:dataSet} and \emph{qb:structure} are disjoint ($dataSet \sqsubseteq \neg structure$).
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em DCAT-C-DISJOINT-PROPERTIES-01:}} 
+	All \emph{DCAT} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
+\end{itemize}
 
@@
 	All \emph{Disco} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
-The following DL statements holds for each pair of \emph{Disco} properties (not having the same domain and range classes) ($variable \sqsubseteq \neg question$).
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DATA-CUBE-C-DISJOINT-PROPERTIES-01:}} 
-All \emph{Data Cube} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
-The following DL statements holds for each pair of \emph{Data Cube} properties (not having the same domain and range classes) ($dataSet \sqsubseteq \neg structure$).
+  The properties \emph{disco:variable} and \emph{disco:question} are disjoint ($variable \sqsubseteq \neg question$).
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em PHDD-C-DISJOINT-PROPERTIES-01:}} 
+	All \emph{PHDD} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
+	The properties \emph{phdd:isStructuredBy} and \emph{phdd:column} are disjoint ($isStructuredBy \sqsubseteq \neg column$)
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em SKOS-C-DISJOINT-PROPERTIES-01:}} 
+	All \emph{SKOS} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em XKOS-C-DISJOINT-PROPERTIES-01:}} 
+	All \emph{XKOS} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
 \end{itemize}
@@
 \begin{itemize}
+	\item \textbf{{\em DATA-CUBE-C-DISJOINT-CLASSES-01:}} 
+All \emph{Data Cube} classes are defined to be pairwise disjoint.
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em DCAT-C-DISJOINT-CLASSES-01:}} 
+All \emph{DCAT} classes are defined to be pairwise disjoint.
+\end{itemize}
+
+\begin{itemize}
 	\item \textbf{{\em DISCO-C-DISJOINT-CLASSES-01:}} 
-All \emph{Disco} classes are defined to be pairwise disjoint.
-The following DL statements holds for each pair of Disco classes (\ms{Study $\sqcap$ Variable $\sqsubseteq$ $\perp$}).
+All \emph{Disco} classes are defined to be pairwise disjoint (e.g. \ms{Study $\sqcap$ Variable $\sqsubseteq$ $\perp$}).
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em PHDD-C-DISJOINT-CLASSES-01:}} 
+All \emph{PHDD} classes are defined to be pairwise disjoint.
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em SKOS-C-DISJOINT-CLASSES-01:}} 
+All \emph{SKOS} classes are defined to be pairwise disjoint.
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em XKOS-C-DISJOINT-CLASSES-01:}} 
+All \emph{XKOS} classes are defined to be pairwise disjoint.
 \end{itemize}
@@
 \begin{itemize}
+	\item \textbf{{\em DATA-CUBE-C-EQUIVALENT-PROPERTIES-01:}}
+	Equivalent properties from different versions of \emph{Data Cube} can be marked as equivalent. 
+	As a consequence, the properties can be replaced by each other without affecting the meaning.
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em DCAT-C-EQUIVALENT-PROPERTIES-01:}}
+	Equivalent properties from different versions of \emph{DCAT} can be marked as equivalent. 
+	As a consequence, the properties can be replaced by each other without affecting the meaning.
+\end{itemize}
+
+\begin{itemize}
 	\item \textbf{{\em DISCO-C-EQUIVALENT-PROPERTIES-01:}}
@@
 \begin{itemize}
-	\item \textbf{{\em DATA-CUBE-C-EQUIVALENT-PROPERTIES-01:}}
-	Equivalent properties from different versions of \emph{Data Cube} can be marked as equivalent. 
+	\item \textbf{{\em PHDD-C-EQUIVALENT-PROPERTIES-01:}}
+	Equivalent properties from different versions of \emph{PHDD} can be marked as equivalent. 
+	As a consequence, the properties can be replaced by each other without affecting the meaning.
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em SKOS-C-EQUIVALENT-PROPERTIES-01:}}
+	Equivalent properties from different versions of \emph{SKOS} can be marked as equivalent. 
+	As a consequence, the properties can be replaced by each other without affecting the meaning.
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em XKOS-C-EQUIVALENT-PROPERTIES-01:}}
+	Equivalent properties from different versions of \emph{XKOS} can be marked as equivalent. 
 	As a consequence, the properties can be replaced by each other without affecting the meaning.
@@
 This is often rendered in drop down boxes or radio buttons in user interfaces. 
-Allowed values\footnote{{\em R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS} and 
+\emph{Allowed values}\footnote{{\em R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS} and 
 {\em R-37-ALLOWED-VALUES-FOR-RDF-LITERALS}} for properties can be IRIs, IRIs (matching one or multiple patterns), (any) literals, literals of a list of allowed literals (e.g.
 'red' 'blue' 'green'), typed literals of one or multiple type(s) (e.g.
-xsd:string).
+\emph{xsd:string}).
 
@@
 
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-FUNCTIONAL-PROPERTIES-01:}} for each \emph{rdfs:Resource x}, there can be at most one distinct \emph{rdfs:Resource y} such that \emph{x} is connected by \emph{adms:identifier} to \emph{y} (\ms{$(\textsf{funct } \textsf{identifier})$}).
-\end{itemize}
-
-\tb{Achim, we created an open issue for DDI 4 how keys should be defined}
-
 \subsection{Inverse-Functional Properties*}
@@
 Each such axiom can be seen as a syntactic shortcut for the following axiom: \emph{SubClassOf( owl:Thing ObjectMaxCardinality( 1 ObjectInverseOf( OPE ) ) )}.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-INVERSE-FUNCTIONAL-PROPERTIES-01:}} for each \emph{rdfs:Resource x}, there can be at most one distinct \emph{rdfs:Resource y} such that \emph{y} is connected by \emph{adms:identifier} to \emph{x} $(\ms{funct identifier}\sp{\overline{\ }})$.
+\end{itemize}
+
+\tb{Achim, we created an open issue for DDI 4 how keys should be defined}
 
@@
 \begin{itemize}
-	\item see \emph{functional properties}
+	\item see \emph{inverse-functional properties}
 \end{itemize}

### 2015-02-21 paper/paper7/paper7.tex
technology-driven validation

@@
 
+-----
+
+Restricting data property ranges [$V_{min}$,$V_{max}$] within the context of given classes is a very common requirement (\emph{Literal Ranges}\footnote{{\em R-45-RANGES-OF-RDF-LITERAL-VALUES}}) 
+- disco:CategoryStatistics resources, e.g., point to percentage values via the data property {\em disco:percentage}; 
+these values must be of the datatype {\em xsd:double} and must be between 0 and 100.
+
+-----
+
+The \emph{Primary Key Properties} constraint is often useful to declare a given (datatype) property as the "primary key" of a class, so that a system can enforce uniqueness and also automatically build URIs from user input and data imported from relational databases or spreadsheets..
+Within the context of \emph{Disco}, resources are uniquely identified by the property \emph{adms:identifier},
+which is therefore inverse-functional
+$(\ms{funct identifier}\sp{\overline{\ }})$,
+i.e. for each \emph{rdfs:Resource x}, there can be at most one distinct \emph{rdfs:Resource y} such that \emph{y} is connected by \emph{adms:identifier} to \emph{x}.
+Keys, however, are even more general, i.e., a generalization of inverse-functional properties\footnote{\emph{R-58-INVERSE-FUNCTIONAL-OBJECT-PROPERTIES}} \cite{Schneider2009}.
+A key can be a data or an object property, or a chain of properties.
+For this generalization purposes, as there are different sorts of key, and as keys can lead to undecidability, 
+DL is extended with \emph{key boxes} and a special \emph{keyfor} (\ms{identifier \ms{keyfor} Resource}) construct\cite{Lutz2005}.
+
 \textbf{DCAT Validation}
@@
 Constraints of some constraint types are directly and automatically derived from conceptual models of multiple vocabularies.
-This way, \emph{property domains and ranges, universal and existential quantifications, minimum, maximum, and exact cardinality restrictions} are defined for each object and data property of vocabularies against which one wish to validate.
+This way, \emph{property domains and ranges, universal and existential quantifications, minimum, maximum, and exact cardinality restrictions} are defined for each property of vocabularies against which one wish to validate.
 As these constraints directly depend on the intended semantics of data models, associated severity levels are very strong.
@@
 
------
+All properties, not having the same domain and range classes, are defined to be pairwise disjoint
+(\emph{disjoint properties}\footnote{\emph{R-9-DISJOINT-PROPERTIES}}), stating that no individual \emph{x} can be connected to an individual/literal \emph{y} by disjoint properties like \emph{phdd:isStructuredBy} and \emph{phdd:column} ($isStructuredBy \sqsubseteq \neg column$).
+All \emph{Disco} classes are defined to be pairwise disjoint ({\em Disjoint Classes}\footnote{{\em R-7-DISJOINT-CLASSES}}; e.g. \ms{Study $\sqcap$ Variable $\sqsubseteq$ $\perp$}),
+i.e. no individual can be at the same time an instance of more than one disjoint class.
+It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values.  
+\emph{Allowed values}\footnote{{\em R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS}, 
+{\em R-37-ALLOWED-VALUES-FOR-RDF-LITERALS}} for properties can be IRIs (matching one or multiple patterns), any literals, allowed literals (e.g.
+'red' 'blue' 'green'), and typed literals of one or multiple type(s) (e.g.
+\emph{xsd:string}) -
+{\em disco:CategoryStatistics}, e.g., can only have {\em disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype {\em rdf:langString} (\ms{CategoryStatistics $\equiv$ $\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString}).
 
-reasoning constraints / sub-classes / sub-properties
+Constraints of some constraint types can be derived from vocabularies' data models for which reasoning can be performed prior to validation which enables to resolve possible constraint violations.
+\emph{Subsumption}\footnote{{\em R-100-SUBSUMPTION}} states that the class \emph{C1} is a sub-class of the class \emph{C2} - \emph{C1} is more specific than \emph{C2}, 
+i.e. each resource of the class \emph{C1} must also be part of the class extension of \emph{C2}. 
+All {\em disco:Universe}s, e.g., must also be {\em skos:Concept}s (\ms{Universe $\sqsubseteq$ Concept}).
+{\em Sub Properties}\footnote{\emph{R-54-SUB-OBJECT-PROPERTIES}, \emph{R-54-SUB-DATA-PROPERTIES}} state that the property \emph{P1} is a sub-property of the property \emph{P2} - that is, if individual \emph{x} is connected by \emph{P1} to individual/literal \emph{y}, then \emph{x} is also connected by \emph{P2} to \emph{y}.
+If \emph{x} is connected by {\em disco:fundedBy} to \emph{y}, then \emph{x} is also connected by {\em dcterms:contributor} to \emph{y} (\ms{fundedBy $\sqsubseteq$ contributor}).
+\emph{Asymmetric object properties}\footnote{{\em R-62-ASYMMETRIC-OBJECT-PROPERTIES}} restrict that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}.
+\emph{Asymmetric object properties} are defined for each asymmetric object property for which a semantically equivalent object property pointing from the other direction may also be possible to be specified in the appropriate vocabulary.
+A {\em disco:Variable}, e.g., may be based on (\emph{disco:basedOn}) a {\em disco:RepresentedVariable}.
+A {\em disco:RepresentedVariable}, however, cannot be based on a {\em disco:Variable} (\ms{$basedOn \sqcap basedOn^{-} \sqsubseteq \bot$}).
 

### 2015-02-22 paper/paper7/paper7-appendix.tex
constraints

@@
 
-With this constraint objects of object properties can be ordered as well as literals of data properties and objects of object properties\footnote{\emph{R-121-SPECIFY-ORDER-OF-RDF-RESOURCES}, \emph{R-217-DEFINE-ORDER-FOR-FORMS/DISPLAY}}.
+With this constraint objects of object properties can be ordered as well as literals of data properties\footnote{\emph{R-121-SPECIFY-ORDER-OF-RDF-RESOURCES}, \emph{R-217-DEFINE-ORDER-FOR-FORMS/DISPLAY}}.
 
@@
 \begin{itemize}
+	\item \textbf{{\em DATA-CUBE-C-CONTEXT-SPECIFIC-VALID-CLASSES-01}}: For future versions of \emph{Data Cube}, out-dated classes can be marked as deprecated.
+	\begin{itemize}
+		\item severity level: RECOMMENDED
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em DCAT-C-CONTEXT-SPECIFIC-VALID-CLASSES-01}}: For future versions of \emph{DCAT}, out-dated classes can be marked as deprecated.
+	\begin{itemize}
+		\item severity level: RECOMMENDED
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
 	\item \textbf{{\em DISCO-C-CONTEXT-SPECIFIC-VALID-CLASSES-01}}: For future versions of \emph{Disco}, out-dated classes can be marked as deprecated.
+	\begin{itemize}
+		\item severity level: RECOMMENDED
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em PHDD-C-CONTEXT-SPECIFIC-VALID-CLASSES-01}}: For future versions of \emph{PHDD}, out-dated classes can be marked as deprecated.
+	\begin{itemize}
+		\item severity level: RECOMMENDED
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em SKOS-C-CONTEXT-SPECIFIC-VALID-CLASSES-01}}: For future versions of \emph{SKOS}, out-dated classes can be marked as deprecated.
+	\begin{itemize}
+		\item severity level: RECOMMENDED
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em XKOS-C-CONTEXT-SPECIFIC-VALID-CLASSES-01}}: For future versions of \emph{XKOS}, out-dated classes can be marked as deprecated.
+	\begin{itemize}
+		\item severity level: RECOMMENDED
+	\end{itemize}
 \end{itemize}
@@
 \begin{itemize}
+	\item \textbf{{\em DATA-CUBE-C-CONTEXT-SPECIFIC-VALID-PROPERTIES-01}}: For future versions of \emph{Data Cube}, out-dated properties can be marked as deprecated.
+	\begin{itemize}
+		\item severity level: RECOMMENDED
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em DCAT-C-CONTEXT-SPECIFIC-VALID-PROPERTIES-01}}: For future versions of \emph{DCAT}, out-dated properties can be marked as deprecated.
+	\begin{itemize}
+		\item severity level: RECOMMENDED
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
 	\item \textbf{{\em DISCO-C-CONTEXT-SPECIFIC-VALID-PROPERTIES-01}}: For future versions of \emph{Disco}, out-dated properties can be marked as deprecated.
-\end{itemize}
-
-\subsection{Default Values}
+	\begin{itemize}
+		\item severity level: RECOMMENDED
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em PHDD-C-CONTEXT-SPECIFIC-VALID-PROPERTIES-01}}: For future versions of \emph{PHDD}, out-dated properties can be marked as deprecated.
+	\begin{itemize}
+		\item severity level: RECOMMENDED
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em SKOS-C-CONTEXT-SPECIFIC-VALID-PROPERTIES-01}}: For future versions of \emph{SKOS}, out-dated properties can be marked as deprecated.
+	\begin{itemize}
+		\item severity level: RECOMMENDED
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em XKOS-C-CONTEXT-SPECIFIC-VALID-PROPERTIES-01}}: For future versions of \emph{XKOS}, out-dated properties can be marked as deprecated.
+	\begin{itemize}
+		\item severity level: RECOMMENDED
+	\end{itemize}
+\end{itemize}
+
+\subsection{Default Values*}
 
@@
 \begin{itemize}
+	\item \textbf{{\em DATA-CUBE-C-RECOMMENDED-PROPERTIES-01:}}
+	\begin{itemize}
+		\item severity level: RECOMMENDED
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em DCAT-C-RECOMMENDED-PROPERTIES-01:}}
+	\begin{itemize}
+		\item severity level: RECOMMENDED
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
 	\item \textbf{{\em DISCO-C-RECOMMENDED-PROPERTIES-01:}}
   The property {\em skos:notation} is not mandatory for {\em disco:Variable}s, but recommended to indicate variable names.
+	\begin{itemize}
+		\item severity level: RECOMMENDED
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em PHDD-C-RECOMMENDED-PROPERTIES-01:}}
+	\begin{itemize}
+		\item severity level: RECOMMENDED
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em SKOS-C-RECOMMENDED-PROPERTIES-01:}}
+	\begin{itemize}
+		\item severity level: RECOMMENDED
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em XKOS-C-RECOMMENDED-PROPERTIES-01:}}
+	\begin{itemize}
+		\item severity level: RECOMMENDED
+	\end{itemize}
 \end{itemize}

### 2015-02-22 paper/paper7/paper7.tex
constraints

--- 2015-02-21 paper/paper7/paper7.tex
@@
 We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement (constraint type) in detail and give examples for each (represented by different constraint languages).
-The knowledge representation formalism {\em Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
+The knowledge representation formalism \emph{Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
 Therefore, this technical report contains mappings to DL to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
@@
 \textbf{Theoretical Concepts.}
-Variables must have at least one relationship to a theoretical concept\footnote{{\em DISCO-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01}}.
+Variables must have at least one relationship to a theoretical concept\footnote{\emph{DISCO-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01}}.
 %The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
@@
 Constraints of the constraint type \emph{Context-Specific Exclusive OR of Property Groups}
-restrict individuals of given classes to have only one of multiple property groups\footnote{{\em R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC}}.
+restrict individuals of given classes to have only one of multiple property groups\footnote{\emph{R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC}}.
 Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes and categories), but not both\footnote{\emph{DISCO-C-CONTEXT-SPECIFIC-EXCLUSIVE-OR-OF-PROPERTY-GROUPS-01:}}.
@@
 \end{DL}
+
+It is useful to declare properties to be conditional, i.e.
+if particular properties exist, then specific other properties must also be present (\emph{conditional properties})\footnote{{\em R-71-CONDITIONAL-PROPERTIES}\label{R-71-CONDITIONAL-PROPERTIES}}.
+If a {\em skos:Concept} represents a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
+then the property {\em disco:isValid} has to be stated indicating if the code is valid (\emph{true}) or missing (\emph{false}).
+%\footref{R-71-CONDITIONAL-PROPERTIES}
+
+-----
+
+Restricting data property ranges [$V_{min}$,$V_{max}$] within the context of given classes is a very common requirement (\emph{Literal Ranges}\footnote{\emph{R-45-RANGES-OF-RDF-LITERAL-VALUES}}) 
+- disco:CategoryStatistics resources, e.g., point to percentage values via the data property \emph{disco:percentage}; 
+these values must be of the datatype \emph{xsd:double} and must be between 0 and 100.
+
+-----
+
+It is often useful to declare a given (data) property as the \emph{primary key} of a class (\emph{Primary Key Properties}), so that a system can enforce uniqueness and also automatically build URIs from user inputs and imported data.
+In \emph{Disco}, resources are uniquely identified by the property \emph{adms:identifier},
+which is therefore inverse-functional
+$(\ms{funct identifier}\sp{\overline{\ }})$,
+i.e. for each \emph{rdfs:Resource x}, there can be at most one distinct \emph{rdfs:Resource y} such that \emph{y} is connected by \emph{adms:identifier$\sp{\overline{\ }}$} to \emph{x}.
+Keys, however, are even more general than inverse-functional properties\footnote{\emph{R-58-INVERSE-FUNCTIONAL-OBJECT-PROPERTIES}},
+as a key can be a data, an object property, or a chain of properties \cite{Schneider2009}.
+For this generalization purposes, as there are different sorts of key, and as keys can lead to undecidability, 
+DL is extended with \emph{key boxes} and a special \emph{keyfor} construct (\ms{identifier \ms{keyfor} Resource}) \cite{Lutz2005}.
+
+-----
+
+In many cases, resources must be members of listed controlled vocabularies\footnote{\emph{R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES}, 
+\emph{R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES}}.
+\emph{disco:SummaryStatistics}, e.g., can only have \emph{disco:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType} which is a \emph{skos:ConceptScheme}.
+
+\begin{DL}
+SummaryStatistics $\sqsubseteq$ $\forall summaryStatisticType.A$ \\
+$A \equiv Concept \sqcap \forall inScheme . B$ \\
+$B \equiv ConceptScheme \sqcap \{SummaryStatisticType\}$
+\end{DL}
+
+-----
+
+Depending on property datatypes,
+two different literal values have
+a specific ordering with respect to an operator. 
+\emph{P1} and \emph{P2} are the data properties we need to compare and 
+\emph{OP} is the comparison operator (e.g. \textless, \textless=, \textgreater, \textgreater=, =, !=) (\emph{Literal Value Comparison}\footnote{\emph{R-43-LITERAL-VALUE-COMPARISON}}).
+\emph{disco:startDate}s, e.g., must be before (\emph{\textless}) \emph{disco:endDate}s.
+To validate this constraint we bind the variables (P1: \emph{disco:startDate}, P2: \emph{disco:endDate}, OP: \emph{\textless}).
+
+-----
+
+Objects/literals can be ordered\footnote{\emph{R-121-SPECIFY-ORDER-OF-RDF-RESOURCES}, \emph{R-217-DEFINE-ORDER-FOR-FORMS/DISPLAY}} for given properties.
+\emph{Disco }variables, questions, and codes/categories are typically organized in a particular order. 
+If codes/categories of a \emph{disco:Representation} of a \emph{disco:Variable} should be ordered, the variable representation should also be of the type \emph{skos:OrderedCollection} containing multiple codes/categories (each represented as \emph{skos:Concept}) in a \emph{skos:memberList}.
+
+-----
+
+{\em Mathematical Operations}\footnote{{\em R-42-MATHEMATICAL-OPERATIONS}, {\em R-41-STATISTICAL-COMPUTATIONS}} (e.g.
+date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
+The sum of {\em disco:percentage} (datatype: {\em xsd:double}) values of all codes ({\em skos:Concept}s) of a code list ({\em skos:ConceptScheme} or {\em skos:OrderedCollection}), serving as representation of a particular {\em disco:Variable} must exactly be 100.
+
+-----
 
@@
 Constraints of some constraint types are directly and automatically derived from conceptual models of multiple vocabularies.
-This way, \emph{property domains and ranges, universal and existential quantifications, minimum, maximum, and exact cardinality restrictions} are defined for each object and data property of vocabularies against which one wish to validate.
+This way, \emph{property domains and ranges, universal and existential quantifications, minimum, maximum, and exact cardinality restrictions} are defined for each property of vocabularies against which one wish to validate.
 As these constraints directly depend on the intended semantics of data models, associated severity levels are very strong.
 
-{\em Property Domains}\footnote{{\em R-25-OBJECT-PROPERTY-DOMAIN}, {\em R-26-DATA-PROPERTY-DOMAIN}} and {\em Ranges}\footnote{{\em R-28-OBJECT-PROPERTY-RANGE}, {\em R-35-DATA-PROPERTY-RANGE}}restrict domains and ranges of properties.
-Only {\em skos:ConceptSchemes}, e.g., can have {\em skos:hasTopConcept} relationships (\ms{$\exists$ hasTopConcept.$\top$ $\sqsubseteq$ ConceptScheme}) and
-{\em xkos:belongsTo} relationships can only point to instances of the class {\em skos:Concept} (\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}).
-A \emph{universal quantification}\footnote{{\em R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}} contains all those individuals that are connected by a property only to individuals/literals that are instances of particular classes  or data ranges.
-Only {\em dcat:Catalogs}, e.g., can have {\em dcat:dataset} relationships to {\em dcat:Datasets} (\ms{Catalog $\sqsubseteq$ $\forall$ dataset.Dataset}).
-An \emph{existential quantification}\footnote{{\em R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}} contains all those individuals that are connected by a property to individuals/literals that are instances of given classes or data ranges.
+\emph{Property Domains}\footnote{\emph{R-25-OBJECT-PROPERTY-DOMAIN}, \emph{R-26-DATA-PROPERTY-DOMAIN}} and \emph{Ranges}\footnote{\emph{R-28-OBJECT-PROPERTY-RANGE}, \emph{R-35-DATA-PROPERTY-RANGE}}restrict domains and ranges of properties.
+Only \emph{skos:ConceptSchemes}, e.g., can have \emph{skos:hasTopConcept} relationships (\ms{$\exists$ hasTopConcept.$\top$ $\sqsubseteq$ ConceptScheme}) and
+\emph{xkos:belongsTo} relationships can only point to instances of the class \emph{skos:Concept} (\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}).
+A \emph{universal quantification}\footnote{\emph{R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}} contains all those individuals that are connected by a property only to individuals/literals that are instances of particular classes  or data ranges.
+Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets} (\ms{Catalog $\sqsubseteq$ $\forall$ dataset.Dataset}).
+An \emph{existential quantification}\footnote{\emph{R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}} contains all those individuals that are connected by a property to individuals/literals that are instances of given classes or data ranges.
 Every \emph{qb:SliceKey}, e.g., must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}).
+
 \emph{Minimum/maximum/exact qualified cardinality restrictions}\footnote{\emph{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES, \\ R-76-MAXIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES, \\ R-74-EXACT-QUALIFIED-CARDINALITY-ON-PROPERTIES}} contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals that are instances of particular classes or data ranges.
 \emph{Minimum qualified cardinality restrictions} are defined for each property of multiple vocabularies like \emph{Disco}.
-A \emph{disco:Questionnaire}, e.g., has at least one {\em disco:question} relationship to {\em disco:Questions} (\ms{Questionnaire $\sqsubseteq$ $\geq$1 question.Question}),
-a {\em disco:Variable} has at most one {\em disco:concept} relationship to a theoretical concept ({\em skos:Concept}) (\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}), and every \emph{qb:DataSet} has (\emph{qb:structure}) exactly one associated \emph{qb:DataStructureDefinition} (\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition $\sqcap$ $\leq$1 structure.DataStructureDefinition}).
+A \emph{disco:Questionnaire}, e.g., has at least one \emph{disco:question} relationship to \emph{disco:Questions} (\ms{Questionnaire $\sqsubseteq$ $\geq$1 question.Question}),
+a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}) (\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}), and every \emph{qb:DataSet} has (\emph{qb:structure}) exactly one associated \emph{qb:DataStructureDefinition} (\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition $\sqcap$ $\leq$1 structure.DataStructureDefinition}).
 %\footnote{\emph{DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02}}.
+For particular data properties, values of predefined languages must be stated for determined number of times\footnote{{\em R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG}, {\em R-48-MISSING-LANGUAGE-TAGS}}.
+Some controlled vocabularies contain literals in natural language, but without information what language has actually been used. Language tags might also not conform to language standards. 
+Some concepts in a thesaurus are labeled in only one language, some in multiple languages.
+It may be desirable to have each concept labeled in each of the languages that also are used on the other concepts.
+This is not always possible, but incompleteness of language coverage for some concepts can indicate shortcomings of the vocabulary
+(severity level: informational) \cite{MaderHaslhoferIsaac2012}.
+
+All properties, not having the same domain and range classes, are defined to be pairwise disjoint
+(\emph{disjoint properties}\footnote{\emph{R-9-DISJOINT-PROPERTIES}}), stating that no individual \emph{x} can be connected to an individual/literal \emph{y} by disjoint properties like \emph{phdd:isStructuredBy} and \emph{phdd:column} ($isStructuredBy \sqsubseteq \neg column$).
+All \emph{Disco} classes are defined to be pairwise disjoint (\emph{Disjoint Classes}\footnote{\emph{R-7-DISJOINT-CLASSES}}; e.g. \ms{Study $\sqcap$ Variable $\sqsubseteq$ $\perp$}),
+i.e. no individual can be at the same time an instance of more than one disjoint class.
+It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values.  
+\emph{Allowed values}\footnote{\emph{R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS}, 
+\emph{R-37-ALLOWED-VALUES-FOR-RDF-LITERALS}} for properties can be IRIs (matching one or multiple patterns), any literals, allowed literals (e.g.
+'red' 'blue' 'green'), and typed literals of one or multiple type(s) (e.g.
+\emph{xsd:string}) -
+\emph{disco:CategoryStatistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString} (\ms{CategoryStatistics $\equiv$ $\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString}).
+
+Constraints of some constraint types can be derived from vocabularies' data models for which reasoning can be performed prior to validation which enables to resolve possible constraint violations.
+\emph{Subsumption}\footnote{\emph{R-100-SUBSUMPTION}} states that the class \emph{C1} is a sub-class of the class \emph{C2} - \emph{C1} is more specific than \emph{C2}, 
+i.e. each resource of the class \emph{C1} must also be part of the class extension of \emph{C2}. 
+All \emph{disco:Universe}s, e.g., must also be \emph{skos:Concept}s (\ms{Universe $\sqsubseteq$ Concept}).
+\emph{Sub Properties}\footnote{\emph{R-54-SUB-OBJECT-PROPERTIES}, \emph{R-54-SUB-DATA-PROPERTIES}} state that the property \emph{P1} is a sub-property of the property \emph{P2} - that is, if individual \emph{x} is connected by \emph{P1} to individual/literal \emph{y}, then \emph{x} is also connected by \emph{P2} to \emph{y}.
+If \emph{x} is connected by \emph{disco:fundedBy} to \emph{y}, then \emph{x} is also connected by \emph{dcterms:contributor} to \emph{y} (\ms{fundedBy $\sqsubseteq$ contributor}).
+\emph{Asymmetric object properties}\footnote{\emph{R-62-ASYMMETRIC-OBJECT-PROPERTIES}} restrict that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}.
+\emph{Asymmetric object properties} are defined for each asymmetric object property for which a semantically equivalent object property pointing from the other direction may also be possible to be specified in the appropriate vocabulary.
+A \emph{disco:Variable}, e.g., may be based on (\emph{disco:basedOn}) a \emph{disco:RepresentedVariable}.
+A \emph{disco:RepresentedVariable}, however, cannot be based on a \emph{disco:Variable} (\ms{$basedOn \sqcap basedOn^{-} \sqsubseteq \bot$}).
+\emph{Default values}\footnote{{\em R-31-DEFAULT-VALUES-OF-RDF-OBJECTS}, {\em R-38-DEFAULT-VALUES-OF-RDF-LITERALS}} for objects/literals of given prooperties are inferred automatically when properties are not stated, in order to pre-populate input forms and to insert a required property that is missing in a web service call.
+The value \emph{true} for the property {\em disco:isPublic} ({\em xsd:boolean}) indicates that the data set ({\em disco:LogicalDataSet}) can be accessed by anyone.
+Per default, access to data sets should be restricted (\emph{false}).
 
@@
 
-reasoning constraints / sub-classes / sub-properties
+For future vocabulary versions, out-dated classes and properties can be marked as deprecated.
+There are constraint types (\emph{context-specific valid classes and properties}) to specify which classes and properties are valid in which context (here a specific vocabulary version).
+Many properties are not necessarily required but recommended within a particular context (\emph{recommended properties}).
+The property {\em skos:notation} is not mandatory for {\em disco:Variable}s, but recommended to indicate variable names.
+
+-----
+
+It has to be ensured that a value is valid for its datatype (\emph{Value is Valid for Datatype}), e.g., 
+that a date is really a date, or that a \emph{xsd:nonNegativeInteger} value is not negative. 
+It is checked if all literals of {\em xsd:date} properties are really dates (e.g. {\em disco:startDate}, {\em disco:endDate}, {\em dcterms:date}).
+
+-----
+
+The validation of instances data (direct or indirect) exploits the sub-class or sub-property link in a given ontology (\emph{Use Sub-Super Relations in Validation}).
+This validation can indicate when the data is verbose (redundant) or expressed at a too general level, and could thus be improved.
+If \emph{dcterms:coverage} and one of its sub-properties (\emph{dcterms:spatial}, \emph{dcterms:temporal}) are present,
+it is checked that \emph{dcterms:coverage} is not redundant with its sub-properties.
+
+-----
 
@@
 \textbf{RDF Data Cube Vocabulary.}
-A well-formed RDF Data Cube is an a RDF graph describing one or more instances of {\em qb:DataSet} for which each of the 22 defined integrity constraints\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf} passes.
+A well-formed RDF Data Cube is an a RDF graph describing one or more instances of \emph{qb:DataSet} for which each of the 22 defined integrity constraints\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf} passes.
 Each integrity constraint is expressed as narrative prose and, where possible, a SPARQL ASK query or query template. 

### 2015-02-23 paper/paper7/paper7-appendix.tex
added constraints

@@
 A controlled vocabulary that contains many orphan concepts is less usable for search and retrieval use cases, because, e.g., no hierarchical query expansion can be performed on search terms to find documents with more general content.
-	Iteration over all concepts in the vocabulary and returning that don't have associated resources using (subproperties of) \emph{skos:semanticRelation}. 
-  Severity level: INFO
+	\begin{itemize}
+		\item Implementation: Iteration over all concepts in the vocabulary and returning that don't have associated resources using (subproperties of) \emph{skos:semanticRelation}. 
+		\item Severity level: INFO
+\end{itemize}
 	\item \textbf{{\em SKOS-C-STRUCTURE-02\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Disconnected Concept Clusters}:}}
@@
 These datasets form "islands" in the vocabulary and might be caused by incomplete data acquisition, "forgotten" test data, outdated terms and the like.
-	Implementation: Creation of an undirected graph that includes all non-orphan concepts as nodes and all semantic relations as edges.
+	\begin{itemize}
+		\item Implementation: Creation of an undirected graph that includes all non-orphan concepts as nodes and all semantic relations as edges.
 Tarjan's algorithm then finds and returns all weakly connected components.
-	Severity level: INFO
+		\item Severity level: INFO
+\end{itemize}
 	\item \textbf{{\em SKOS-C-STRUCTURE-03\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Cyclic Hierarchical Relations}:}}
@@
 deleting an edge).
-	Implementation: Construction of a graph having all concepts as nodes and the set of edges being \emph{skos:broader} relations. 
-	Severity level: INFO
+	\begin{itemize}
+		\item Implementation: Construction of a graph having all concepts as nodes and the set of edges being \emph{skos:broader} relations. 
+		\item Severity level: INFO
+\end{itemize}
 	\item \textbf{{\em SKOS-C-STRUCTURE-04\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Valueless Associative Relations}:}}
@@
 	Two concepts are sibling, but also connected by an associative relation. In that context, the associative relation is not necessary. See ISO\_DIS\_25964-1, 11.3.2.2 
-	Implementation:
+	\begin{itemize}
+		\item Implementation:
 		Identification of all pairs of concepts that have the same broader or narrower concepts, i.e. they are "sibling terms". All siblings that are related by a \emph{skos:related} property are returned. 
-	Severity level: INFO
+	  \item Severity level: INFO
+\end{itemize}
 	\item \textbf{{\em SKOS-C-STRUCTURE-05\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Solely Transitively Related Concepts}:}}
@@
 	\emph{skos:broaderTransitive} and \emph{skos:narrowerTransitive} are, according to the SKOS reference document, "not used to make assertions", so they should not be the only relations hierarchically relating two concepts.
-	Implementation: Identification of all concept pairs that are related by \emph{skos:broaderTransitive} or \emph{skos:narrowerTransitive} properties but not by their \emph{skos:broader} and \emph{skos:narrower} subproperties.
-	Severity level: INFO
+	\begin{itemize}
+		\item Implementation: Identification of all concept pairs that are related by \emph{skos:broaderTransitive} or \emph{skos:narrowerTransitive} properties but not by their \emph{skos:broader} and \emph{skos:narrower} subproperties.
+		\item Severity level: INFO
+\end{itemize}
 	\item \textbf{{\em SKOS-C-STRUCTURE-06\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Unidirectionally Related Concepts}:}}
@@
 	Reciprocal relations (e.g., \emph{broader/narrower, related, hasTopConcept/topConceptOf}) should be included in the controlled vocabularies to achieve better search results using SPARQL in systems without reasoner support.
-	Implementation:
+	\begin{itemize}
+		\item Implementation:
 		This issue is checked without inference of \emph{owl:inverseOf} properties.
@@
 If not, the resources associated with this property are returned.
-	Severity level: INFO
+	  \item Severity level: INFO
+\end{itemize}
 	\item \textbf{{\em SKOS-C-STRUCTURE-07\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Omitted Top Concepts}:}}
@@
 	A vocabulary should provide "entry points" to the data to provide “efficient access” (SKOS primer) and guidance for human users. 
-	Implementation:
+	\begin{itemize}
+		\item Implementation:
 		For every ConceptScheme in the controlled vocabulary, a SPARQL query is issued finding resources that are associated with this ConceptScheme by one of the properties \emph{skos:hasTopConcept} or \emph{skos:topConceptOf}.
 Top concepts are also concepts having no broader concept.
-	Severity level: SHOULD
+	  \item Severity level: SHOULD
+\end{itemize}
 	\item \textbf{{\em SKOS-C-STRUCTURE-08\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Top Concepts Having Broader Concepts}:}}
@@
 	Concepts "internal to the tree" should not be indicated as top concepts.
-	Implementation:
+	\begin{itemize}
+		\item Implementation:
 		A SPARQL query finds all top concepts (being defined by one of the properties \emph{skos:hasTopConcept} or \emph{skos:topConceptOf}) having associated a broader concept. 
-	Severity level: ERROR
+	  \item Severity level: ERROR
+\end{itemize}
 	\item \textbf{{\em SKOS-C-STRUCTURE-09\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Hierarchical Redundancy}:}}
@@
 	Concepts related to themselves. 
-	Severity level: INFO
+	\begin{itemize}
+		\item Severity level: INFO
+	\end{itemize}
 \end{itemize}
@@
 	Iteration over all concepts in the vocabulary and find those not using one of \emph{skos:note}, \emph{skos:changeNote}, \emph{skos:definition}, \emph{skos:editorialNote}, \emph{skos:example}, \emph{skos:historyNote}, or \emph{skos:scopeNote}.
-  Severity level: INFO
+	\begin{itemize}
+		\item Severity level: INFO
+	\end{itemize}
 	\item \textbf{{\em SKOS-C-LABELING-AND-DOCUMENTATION-02\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Overlapping Labels}:}}
@@
 This could indicate missing disambiguation information and thus lead to problems in autocompletion application.
-	Severity level: INFO
+	\begin{itemize}
+		\item Severity level: INFO
+	\end{itemize}
 	\item \textbf{{\em SKOS-C-LABELING-AND-DOCUMENTATION-03\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Missing Labels}:}}
@@
 	To make the vocabulary more convenient for humans to use, instances of SKOS classes (Concept, ConceptScheme, Collection) should be labeled using e.g., \emph{skos:prefLabel}, \emph{altLabel}, \emph{rdfs:label}, \emph{dc:title}.
-	Severity level: INFO
+	\begin{itemize}
+		\item Severity level: INFO
+	\end{itemize}
 	\item \textbf{{\em SKOS-C-LABELING-AND-DOCUMENTATION-04\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Unprintable Characters in Labels}:}}
@@
 	\emph{pref/alt/hiddenlabels} contain characters that are not alphanumeric characters or blanks.
-	Severity level: INFO
+	\begin{itemize}
+		\item Severity level: INFO
+	\end{itemize}
 	\item \textbf{{\em SKOS-C-LABELING-AND-DOCUMENTATION-05\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Empty Labels}:}}
@@
 	Labels also need to contain textual information to be useful, thus we find all SKOS labels with length 0 (after removing whitespaces). 
-	Severity level: INFO
+	\begin{itemize}
+		\item Severity level: INFO
+	\end{itemize}
 	\item \textbf{{\em SKOS-C-LABELING-AND-DOCUMENTATION-06\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Ambiguous Notation References}:}}
@@
 	Concepts within the same concept scheme should not have identlical \emph{skos:notation} literals. 
-	Severity level: INFO
+	\begin{itemize}
+		\item Severity level: INFO
+	\end{itemize}
+\end{itemize}
+
+\subsection{\underline{Vocabulary}}
+Vocabularies should not invent any new terms or use deprecated elements.
+
+\begin{itemize}
+	\item \textbf{\em DATA-CUBE-C-VOCABULARY-01} 
+	\begin{itemize}
+		\item Severity level: FATALERROR
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{\em DCAT-C-VOCABULARY-01} 
+	\begin{itemize}
+		\item Severity level: FATALERROR
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{\em DISCO-C-VOCABULARY-01} 
+	\begin{itemize}
+		\item Severity level: FATALERROR
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{\em PHDD-C-VOCABULARY-01} 
+	\begin{itemize}
+		\item Severity level: FATALERROR
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em SKOS-C-VOCABULARY-01\footnote{Corresponds to qSKOS Quality Issues - Linked Data Specific Issues - Undefined SKOS Resources}:}}
+	Undefined SKOS Resources:
+	The vocabulary should not invent any new terms within the SKOS namespace or use deprecated SKOS elements. 
+	\begin{itemize}
+		\item Severity level: FATALERROR
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{\em XKOS-C-VOCABULARY-01} 
+	\begin{itemize}
+		\item Severity level: FATALERROR
+	\end{itemize}
 \end{itemize}

### 2015-02-23 paper/paper7/paper7.tex
added constraints

@@
 
+SKOS is based on RDF, which is a graph-based data model.
+Therefore, we can concentrate on the vocabulary's graph-based structure for assessing the quality of SKOS vocabularies and apply graph- and network-analysis techniques (\emph{structure}) like
+(1) a vocabulary should provide entry points (top concepts) to the data to provide efficient access and guidance for human users and
+(2) concepts, internal to the tree, should not be indicated as top concepts, and
+(3) a vocabulary should not contain many orphan concepts 
+(An orphan concept is a concept without any associative or hierarchical relations lacking valuable context information.
+A controlled vocabulary that contains many orphan concepts is less usable for search and retrieval use cases, as, e.g., no hierarchical query expansion can be performed on search terms to find documents with more general content.) \cite{MaderHaslhoferIsaac2012}.
+\tb{add disco example}
 - SKOS validation of hierarchies of theoretical concepts
@@
 
+Vocabularies should not invent any new terms or use deprecated elements.
+The \emph{vocabulary} constraint should be the first one to be checked for each reused vocabulary.
 \emph{Property Domains}\footnote{\emph{R-25-OBJECT-PROPERTY-DOMAIN}, \emph{R-26-DATA-PROPERTY-DOMAIN}} and \emph{Ranges}\footnote{\emph{R-28-OBJECT-PROPERTY-RANGE}, \emph{R-35-DATA-PROPERTY-RANGE}}restrict domains and ranges of properties.

### 2015-02-23 paper/paper7/paper7.tex
running example

@@
 %
-\title{RDF Validation of Metadata \\ on Highly-Complex Person-Level Data}
+\title{RDF Validation of Metadata \\ on Person-Level and Aggregated Data}
 \subtitle{}
@@
 - DESCRIPTION OF EUROSTAT -
-Eurostat\footnote{\url{http://ec.europa.eu/eurostat}} provides publicly available European aggregated data.
- SBE researchers have a strong interest in the availability of childcare services across the European Union Member States.
-The variable \emph{formal childcare}\footnote{\url{http://appsso.eurostat.ec.europa.eu/nui/show.do?dataset=ilc_caindformal&lang=en}}
-stores the measured formal childcare in percent over the population of each age group.
-The present data collection refers to data on formal childcare and other types of care by the variables \emph{year}, \emph{duration} (0 hours, 1 to 29 hours a usual week; 30 hours or more a usual week), \emph{age} of the child (0-2 years; 3 to admission age for compulsory school; admission age for compulsory school to 12) and \emph{country}.
-Eurostat provides the metadata on the aggregated data in different forms like CSV files.
+Eurostat\footnote{\url{http://ec.europa.eu/eurostat}} provides publicly available European aggregated data.\tb{aggregated (meta)data ?}
+SBE researchers have a strong interest, e.g., in the availability of childcare services across European Union Member States.
+The variable \emph{formal childcare}\footnote{\url{http://appsso.eurostat.ec.europa.eu/nui/show.do?dataset=ilc_caindformal&lang=en}} (in contrast to childcare at home)
+captures the measured availability of childcare services in percent over the population.
+The present data collection refers to data on formal childcare and other types of care by the \tb{aggregated?}variables \emph{year}, \emph{duration} (0 hours, 1 - 29 h/week; 30 h/week)\tb{HPW ?}, \emph{age} of the child (0-2 years; 3 to admission age for compulsory school; admission age for compulsory school to 12) and \emph{country}.
+Eurostat provides the metadata on the aggregated data in different forms like CSV files.\tb{some metadata in form of SDMX and data in form of CSV files?}
 
-For a broader view of the data framework and more detailed analyses we have to refer to the metadata on person-level data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}.
+For a broader view of the data framework and more detailed analyses we refer to the metadata on person-level data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}.
 The \emph{Microdata Information System (MISSY)}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}} is an online service platform that provides systematically structured metadata for official statistics on European person-level data sets.
 This includes data documentation at the study and variable level as well as documentation materials, tools and further information.
-The calculation of the aggregated variable \emph{formal childcare} is based on six person-level variables: 
-(1) Education at pre-school\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC/2011/Cross-sectional/original#2011-Cross-sectional-RL010}},
-(2) Education at compulsory school,
-(3) Child care at centre-based services,
-(4) Child care at day-care centre,
-(5) Child care by a professional child-minder, and
-(6) Child care by grand-parents, household members, relatives, friends, neighbours.
-For each person-level variable detailed metadata (definitions, descriptions, theoretical concepts, questions, code lists, frequencies, countries) is given which enables the researchers to replicate the results shown in the aggregated data tables from Eurostat.
+The aggregated variable \emph{formal childcare} is calculated on the basis of six person-level variables like 
+\emph{Education at pre-school}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC/2011/Cross-sectional/original#2011-Cross-sectional-RL010}}.
+%(2) Education at compulsory school,
+%(3) Child care at centre-based services,
+%(4) Child care at day-care centre,
+%(5) Child care by a professional child-minder, and
+%(6) Child care by grand-parents, household members, relatives, friends, neighbours.
+For each person-level variable detailed metadata is given (definitions and descriptions, theoretical concepts, underlying questions, code lists, frequencies and descriptive statistics, countries, year of data collection, classifications) enabling researchers to replicate the results shown in the aggregated data tables from Eurostat.
 
 Metadata on person-level data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
-One common research question is to compare 
-\emph{formal childcare} between countries, for which the variable is collected for the individual survey, and other European or non European countries (e.g. OSCE).
+One common research question is ,e.g., the comparison of variables like 
+\emph{formal childcare} between countries, for which the variable is collected within the context of an individual survey, and other European or non European countries (e.g. OSCE).
 
@@
 \end{ex}
-
+\tb{Achim, can we start with the PHDD representation?}
 \emph{Disco} is a vocabulary to represent person-level data in RDF.

### 2015-02-27 paper/paper7/paper7-appendix.tex
pushed pdfs

@@
 
+\begin{itemize}
+
+	\item \textbf{{\em SKOS-C-DATA-MODEL-CONSISTENCY-01\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Relation Clashes}:}}
+	Relation Clashes:
+  Covers condition S27 from the SKOS reference document, that has not been defined formally. 
+	\begin{itemize}
+	  \item Implementation:
+		In a first step, all pairs of concepts are found that are associatively connected, using a SPARQL query.
+In the second step, a graph is created, containing only hierarchically related concepts and the respective relations.
+For each concept pair from the first step, we check for a path in the graph from step two.
+If such a path is found, a clash has been identified and the causing concepts are returned.
+		\item Severity level: 
+	\end{itemize}
+
+	\item \textbf{{\em SKOS-C-DATA-MODEL-CONSISTENCY-02\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Mapping Clashes}:}}
+	Mapping Clashes:
+  Covers condition S46 from the SKOS reference document, that has not been defined formally. 
+	\begin{itemize}
+	  \item Implementation:
+		Can be solved by issuing a SPARQL query. 
+		\item Severity level: 
+	\end{itemize}
+
+	\item \textbf{{\em SKOS-C-DATA-MODEL-CONSISTENCY-03\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Mapping Relations Misuse}:}}
+	Mapping Relations Misuse:
+  According to the SKOS reference documentation, mapping relations (e.g., \emph{skos:broadMatch} or \emph{skos:relatedMatch}) should be asserted to concepts being members of different concept schemes.
+This check finds concepts that are related by a mapping property and are either members of the same concept scheme or members of no concept scheme at all.
+	\begin{itemize}
+		\item Severity level: 
+	\end{itemize}
+
+\end{itemize}
+
 \subsection{Subsumption*}
@@
 \begin{itemize}
+
 	\item \textbf{{\em SKOS-C-DISJOINT-PROPERTIES-01:}} 
 	All \emph{SKOS} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
+
+	\item \textbf{{\em SKOS-C-DISJOINT-PROPERTIES-02\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Disjoint Labels Violation}:}}
+	Disjoint Labels Violation:
+  Covers condition S13 from the SKOS reference document stating that "\emph{skos:prefLabel}, \emph{skos:altLabel} and \emph{skos:hiddenLabel} are pairwise disjoint properties". 
+	\begin{itemize}
+	  \item Implementation:
+		A SPARQL query collects all labels of all concepts, building an in-memory structure. This structure is then checked for disjoint entries. 
+		\item Severity level: 
+	\end{itemize}
+
 \end{itemize}
@@
 \begin{itemize}
+
 	\item \textbf{{\em SKOS-C-LANGUAGE-TAG-CARDINALITY-01\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Omitted or Invalid Language Tags}:}}
@@
 Severity level: INFO
+
   \item \textbf{{\em SKOS-C-LANGUAGE-TAG-CARDINALITY-02\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Incomplete Language Coverage}:}}
@@
 	Severity level: INFO
+
 	\item \textbf{{\em SKOS-C-LANGUAGE-TAG-CARDINALITY-03\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - No Common Language}:}}
@@
 	Severity level: INFO
+
+	\item \textbf{{\em SKOS-C-LANGUAGE-TAG-CARDINALITY-04\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Inconsistent Preferred Labels}:}}
+	Inconsistent Preferred Labels:
+  According to the SKOS reference document, "A resource has no more than one value of skos:prefLabel per language tag".  
+	\begin{itemize}
+	  \item Implementation:
+		A SPARQL query is used to find concepts with at least two prefLabels. In a second step, the language tags of these prefLabels are analyzed and an ambiguity is detected if they are equal.  
+		\item Severity level: INFO
+	\end{itemize}
+
 \end{itemize}

### 2015-02-27 paper/paper7/paper7-appendix.tex
incorporated feedback from Achim

@@
   The sum of {\em disco:percentage} (datatype: {\em xsd:double}) values of all codes (represented as {\em skos:Concept}s) of a code list ({\em skos:ConceptScheme} or {\em skos:OrderedCollection}), serving as representation of a particular {\em disco:Variable}, must exactly be 100.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+
+	\item \textbf{{\em DISCO-C-MATHEMATICAL-OPERATIONS-02}}:
+	For a given variable, the sum of all category statistics (frequency) has to be equal to the 'total' value of summary statistics.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+
+	\item \textbf{{\em DISCO-C-MATHEMATICAL-OPERATIONS-03}}:
+	For a given variable, the sum of 'valid total' and 'missing total' has to be equal to 'total'.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+
+	\item \textbf{{\em DISCO-C-MATHEMATICAL-OPERATIONS-04}}:
+	For a given variable, the 'total' value for country 'All' must be equal to the sum of the 'total' value for all Countries.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+
+	\item \textbf{{\em DISCO-C-MATHEMATICAL-OPERATIONS-05}}:
+	Minimum values do not have to be greater than maximum values (\emph{disco:SummaryStatistics}).
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+
 \end{itemize}
@@
 \begin{itemize}
+
 	\item \textbf{{\em DISCO-C-LANGUAGE-TAG-CARDINALITY-01:}}
   There must be at least one English {\em disco:questionText} for each {\em disco:Question} within {\em disco:LogicalDataSet}s.
+
   \item \textbf{{\em DISCO-C-LANGUAGE-TAG-CARDINALITY-02:}}
   There should be at most one English literal value for variable names ({\em skos:notation}, domain: {\em disco:Variable}).
+
+  \item \textbf{{\em DISCO-C-LANGUAGE-TAG-CARDINALITY-03}}:
+	For each question (\emph{disco:Question}), there must be at least one question text (\emph{disco:questionText}) associated with a language tag of an arbitrary language or with an English language tag.
+
 \end{itemize}

### 2015-02-27 paper/paper7/paper7.tex
incorporated feedback from Achim

@@
 and ICPSR - the largest SBE data archive in the US.
+Increasingly, data professionals, national statistical institutes, data archives, data libraries, and government statisticians (e.g. \url{data.gov}, \url{data.gov.uk})
+are very interested in having their data be discovered and used by providing their metadata on the web in form of RDF (e.g. metadata about unemployment rates or income).
+
 Recently, members of the SBE and Linked Data community developed the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}}, 
@@
 The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.
+
+\section{Motivation}
 
@@
 %For these calculations, definitions of the columns are needed (e.g. is a given variable interpreted numerically or as a string).
-In 2014, SBE and Linked Data community members developed the \emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} vocabulary to represent aggregated data in a rectangular format.
+In 2014, SBE and Linked Data community members developed the \emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} vocabulary to represent aggregated and person-level data in a rectangular format.
 The data could be either represented in records with character-separated values (CSV) or in records with fixed length.
@@
 (2) metadata providers and harvesters ensuring high quality metadata by validating metadata on highly complex RDF data sets.
-In this paper, we show in form of a complete real world running example how to represent metadata on highly complex person-level data (\emph{Disco}), metadata on aggregated data (\emph{Data Cube}), and aggregated data in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}).
-We explain why RDF validation is important in this context and how (meta)data is validated against RDF constraints to ensure high quality (meta)data within this complex of data sets on different levels of aggregation (\textbf{contribution 2}).
+In this paper, we show in form of a complete real world running example how to represent metadata on highly complex person-level data (\emph{Disco}), metadata on aggregated data (\emph{Data Cube}), and aggregated data in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, sections \ref{running-example}-\ref{rdf-representation}).
+We explain why RDF validation is important in this context and how (meta)data is validated against RDF constraints to ensure high quality (meta)data within this complex of data sets on different levels of aggregation (\textbf{contribution 2}, section \ref{rdf-validation}).
 The remainder of the paper is structured as follows.
@@
 \section{Running Example}
+\label{running-example}
 
-- DESCRIPTION OF EUROSTAT -
-Eurostat\footnote{\url{http://ec.europa.eu/eurostat}} provides publicly available European aggregated data.\tb{aggregated (meta)data ?}
+Eurostat\footnote{\url{http://ec.europa.eu/eurostat}} is the statistical office of the European Union.
+Its task is to provide statistics at European level that enable comparisons between countries and regions.
+Eurostat provides publicly available European aggregated data (downloadable in machine-readable format like CSV files) and its metadata (only textual descriptions).
 SBE researchers have a strong interest, e.g., in the availability of childcare services across European Union Member States.
@@
 captures the measured availability of childcare services in percent over the population.
-The present data collection refers to data on formal childcare and other types of care by the \tb{aggregated?}variables \emph{year}, \emph{duration} (0 hours, 1 - 29 h/week; 30 h/week)\tb{HPW ?}, \emph{age} of the child (0-2 years; 3 to admission age for compulsory school; admission age for compulsory school to 12) and \emph{country}.
-Eurostat provides the metadata on the aggregated data in different forms like CSV files.\tb{some metadata in form of SDMX and data in form of CSV files?}
+The present data collection refers to data on formal childcare and other types of care by the variables \emph{year}, \emph{duration} (0 hours, 1 - 29 HPW; 30 HPW), \emph{age} of the child (0-2 years; 3 to admission age for compulsory school; admission age for compulsory school to 12) and \emph{country}.
+As Eurostat provides aggregated data (here a two-dimensional table) as CSV files, we can easily represent the aggregated data with \emph{PHDD} in RDF. 
+This conversion enables further aggregations and calculations, e.g., in order to compare \emph{formal childcare} between Northern and Southern Europe or between otherwise grouped countries.
+% macht mehr sinn wenn Tabelle in mehreren Dimensionen vorhanden ist ode wenn Klassifikationen wie ISCO verwendet werden
 
@@
 For each person-level variable detailed metadata is given (definitions and descriptions, theoretical concepts, underlying questions, code lists, frequencies and descriptive statistics, countries, year of data collection, classifications) enabling researchers to replicate the results shown in the aggregated data tables from Eurostat.
-
 Metadata on person-level data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
@@
 \section{Represent Metadata and Data in RDF}
+\label{rdf-representation}
 
@@
 \end{ex}
-\tb{Achim, can we start with the PHDD representation?}
+
 \emph{Disco} is a vocabulary to represent person-level data in RDF.
@@
 
-The \emph{Simple Knowledge Organization System (SKOS)}...
+The \emph{Simple Knowledge Organization System (SKOS)} is used multiple times within the context of aggregated and person-level (meta)data, e.g., to represent controlled vocabularies or hierarchies of \emph{SBE theoretical concepts} (e.g.
+education).
 
@@
 
-\emph{XKOS}\footnote{\url{https://github.com/linked-statistics/xkos}} is a \emph{SKOS} extension to describe formal statistical classifications like the profession classification \emph{ISCO}.
+\emph{XKOS}\footnote{\url{https://github.com/linked-statistics/xkos}} is a \emph{SKOS} extension to describe formal statistical classifications like the International Standard Classification of Occupations (\emph{ISCO}) and the Statistical classification of economic activities in the European Community \emph{NACE}.
 
@@
 \section{RDF Validation of Metadata and Data}
+\label{rdf-validation}
 
@@
 The continuum of severity levels ranges from informational via warning and error to fatal error. 
-Although we provide default severity levels for each constraint, users should be able to specify severity levels of constraints they need to validate within the context of their individual use cases.
-Therefore, use case specific severity levels can be defined for constraints.
+Although we provide default severity levels for each constraint, users should be able to specify the severity levels of constraints they need to validate for their individual use cases, i.e., users should be able to define use case specific severity levels for constraints.
 
@@
 \subsection{Aggregated (Meta)Data}
+
+\tb{ToDo}
+
+- for each dimension there should be a description and code lists.
+
+- for each code list there should be a description.
+
+- there should be a relationship to the underlying person-level data.
 
@@
 
-- classification system e.g. NACE, profession classification ISCO
-
-- ask Franck if INSEE already expressed well known classification systems with XKOS
+\tb{ToDO: ask Franck if INSEE already expressed well known classification systems with XKOS}
 

### 2015-02-27 paper/paper7/paper7-appendix.tex
resolved footnotes

@@
 
-{\em Sub Properties}\footnote{\emph{R-54-SUB-OBJECT-PROPERTIES}, \emph{R-54-SUB-DATA-PROPERTIES}} state that the property \emph{P1} is a sub property of the property \emph{P2} - that is, if an individual \emph{x} is connected by \emph{P1} to an individual or a literal \emph{y}, then \emph{x} is also connected by \emph{P2} to \emph{y}.
+{\em Sub Properties}\footnote{\emph{R-54-SUB-OBJECT-PROPERTIES}, \emph{R-64-SUB-DATA-PROPERTIES}} state that the property \emph{P1} is a sub property of the property \emph{P2} - that is, if an individual \emph{x} is connected by \emph{P1} to an individual or a literal \emph{y}, then \emph{x} is also connected by \emph{P2} to \emph{y}.
 
@@
 
-A \emph{minimum cardinality restriction}\footnote{{\em R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}, {\em R-211-CARDINALITY-CONSTRAINTS}} contains all those individuals that are connected by a property to at least n different individuals/literals
+A \emph{minimum cardinality restriction}\footnote{{\em R-81-MINIMUM-UNQUALIFIED-CARDINALITY-ON-PROPERTIES}, {\em R-211-CARDINALITY-CONSTRAINTS}} contains all those individuals that are connected by a property to at least n different individuals/literals
 that are instances of a particular class or data range. If the class is missing, it is taken to be \emph{owl:Thing}. 
@@
 
-The \emph{Primary Key Properties} constraint is often useful to declare a given (datatype) property as the "primary key" of a class, so that a system can enforce uniqueness and also automatically build URIs from user input and data imported from relational databases or spreadsheets..
+The \emph{Primary Key Properties}\footnote{R-226-PRIMARY-KEY-PROPERTIES} constraint is often useful to declare a given (datatype) property as the "primary key" of a class, so that a system can enforce uniqueness and also automatically build URIs from user input and data imported from relational databases or spreadsheets..
 Starfleet officers, e.g., are uniquely identified by their command authorization code (e.g. to activate and cancel auto-destruct sequences).

### 2015-02-27 paper/paper7/paper7.tex
resolved footnotes

@@
 recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/XXXXX}} (serving as appendix of this paper) in which we describe RDF constraints to validate metadata on person-level and aggregated data.
-We assign each constraint to constraint types corresponding to RDF validation requirements or to data model specific constraint types
-\cite{BoschZapilkoWackerowEckert2015}.
+We assign each constraint to constraint types corresponding to RDF validation requirements or to data model specific constraint types\footnote{Requirements/Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-1}}
+\cite{BoschZapilkoWackerowEckert2015}\tb{ToDo: publish technical report}.
 
@@
 \emph{Technology-Driven Validation} includes the set of constraints which can be generated automatically out of defined data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges.
-We determined the default \emph{severity level}\footnote{Corresponds to \emph{R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS}} for each constraint indicating how serious the violation of the constraint is.
+We determined the default \emph{severity level} (\emph{R-158}) for each constraint indicating how serious the violation of the constraint is.
 The continuum of severity levels ranges from informational via warning and error to fatal error. 
@@
 
-\textbf{application of matching algorithms.}
+\textbf{application of matching algorithms.}\tb{@Ben ToDo: macht es sinn matching algorithmen anzuwenden?}
 - the value for a specific data property (e.g. birth date) is needed as prerequisite to perform matching algorithms
@@
 \textbf{Surveys.}
-Each survey must have an abstract\footnote{\emph{DISCO-C-DATA-PROPERTY-FACETS-01}}. 
-If the abstract of the survey is missing, a title of the survey has to be stated\footnote{\emph{DISCO-C-CONDITIONAL-PROPERTIES-02}}.
+Each survey must have an abstract ({\emph{R-46: data property facets}). 
+If the abstract of the survey is missing, a title of the survey has to be stated (\emph{R-71: conditional properties}).
 
@@
 \textbf{Theoretical Concepts.}
-Variables must have at least one relationship to a theoretical concept\footnote{\emph{DISCO-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01}}.
+Variables must have at least one relationship to a theoretical concept ({\emph{R-75: minimum qualified cardinality restrictions}).
 %The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
@@
 
-One very common research question is to \emph{compare variables}\footnote{Constraint types: \emph{DISCO-C-COMPARISON-VARIABLES-XX}} of multiple surveys or countries.
+A very common research question is to compare variables (\emph{comparison}) of multiple surveys or countries.
 To compare variables, 
@@
 
-Constraints of the constraint type \emph{Context-Specific Exclusive OR of Property Groups}
-restrict individuals of given classes to have only one of multiple property groups\footnote{\emph{R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC}}.
-Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes and categories), but not both\footnote{\emph{DISCO-C-CONTEXT-SPECIFIC-EXCLUSIVE-OR-OF-PROPERTY-GROUPS-01:}}.
+Constraints of the constraint type \emph{Context-Specific Exclusive OR of Property Groups} (\emph{R-11})
+restrict individuals of given classes to have only one of multiple property groups.
+Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes and categories), but not both.
 
@@
 
-It is useful to declare properties to be conditional, i.e.
-if particular properties exist, then specific other properties must also be present (\emph{conditional properties})\footnote{{\em R-71-CONDITIONAL-PROPERTIES}\label{R-71-CONDITIONAL-PROPERTIES}}.
+It is useful to declare properties to be conditional, i.e. if particular properties exist, then specific other properties must also be present (\emph{R-71: conditional properties}).
 If a {\em skos:Concept} represents a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
@@
 
-Restricting data property ranges [$V_{min}$,$V_{max}$] within the context of given classes is a very common requirement (\emph{Literal Ranges}\footnote{\emph{R-45-RANGES-OF-RDF-LITERAL-VALUES}}) 
+Restricting data property ranges [$V_{min}$,$V_{max}$] within the context of given classes is a very common requirement (\emph{R-45: literal ranges}) 
 - disco:CategoryStatistics resources, e.g., point to percentage values via the data property \emph{disco:percentage}; 
@@
 
-It is often useful to declare a given (data) property as the \emph{primary key} of a class (\emph{Primary Key Properties}), so that a system can enforce uniqueness and also automatically build URIs from user inputs and imported data.
+It is often useful to declare a given (data) property as the \emph{primary key} (\emph{R-226}) of a class, so that a system can enforce uniqueness and also automatically build URIs from user inputs and imported data.
 In \emph{Disco}, resources are uniquely identified by the property \emph{adms:identifier},
@@
 i.e. for each \emph{rdfs:Resource x}, there can be at most one distinct \emph{rdfs:Resource y} such that \emph{y} is connected by \emph{adms:identifier$\sp{\overline{\ }}$} to \emph{x}.
-Keys, however, are even more general than inverse-functional properties\footnote{\emph{R-58-INVERSE-FUNCTIONAL-OBJECT-PROPERTIES}},
+Keys, however, are even more general than inverse-functional properties (\emph{R-58}),
 as a key can be a data, an object property, or a chain of properties \cite{Schneider2009}.
@@
 
-In many cases, resources must be members of listed controlled vocabularies\footnote{\emph{R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES}, 
-\emph{R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES}}.
+In many cases, resources must be members of listed controlled vocabularies (\emph{R-32}).
 \emph{disco:SummaryStatistics}, e.g., can only have \emph{disco:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType} which is a \emph{skos:ConceptScheme}.
@@
 \emph{P1} and \emph{P2} are the data properties we need to compare and 
-\emph{OP} is the comparison operator (e.g. \textless, \textless=, \textgreater, \textgreater=, =, !=) (\emph{Literal Value Comparison}\footnote{\emph{R-43-LITERAL-VALUE-COMPARISON}}).
+\emph{OP} is the comparison operator (e.g. \textless, \textless=, \textgreater, \textgreater=, =, !=) (\emph{R-43: literal value comparison}).
 \emph{disco:startDate}s, e.g., must be before (\emph{\textless}) \emph{disco:endDate}s.
@@
 
-Objects/literals can be ordered\footnote{\emph{R-121-SPECIFY-ORDER-OF-RDF-RESOURCES}, \emph{R-217-DEFINE-ORDER-FOR-FORMS/DISPLAY}} for given properties.
+Objects/literals can be ordered (\emph{R-121, R-217}) for given properties.
 \emph{Disco }variables, questions, and codes/categories are typically organized in a particular order. 
@@
 
-{\em Mathematical Operations}\footnote{{\em R-42-MATHEMATICAL-OPERATIONS}, {\em R-41-STATISTICAL-COMPUTATIONS}} (e.g.
-date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
+{\em Mathematical Operations} (\emph{R-41, R-42}; e.g. date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
 The sum of {\em disco:percentage} (datatype: {\em xsd:double}) values of all codes ({\em skos:Concept}s) of a code list ({\em skos:ConceptScheme} or {\em skos:OrderedCollection}), serving as representation of a particular {\em disco:Variable} must exactly be 100.
@@
 The \emph{vocabulary} constraint should be the first one to be checked for each reused vocabulary.
-\emph{Property Domains}\footnote{\emph{R-25-OBJECT-PROPERTY-DOMAIN}, \emph{R-26-DATA-PROPERTY-DOMAIN}} and \emph{Ranges}\footnote{\emph{R-28-OBJECT-PROPERTY-RANGE}, \emph{R-35-DATA-PROPERTY-RANGE}}restrict domains and ranges of properties.
+\emph{Property Domains} (\emph{R-25, R-26}) and \emph{Ranges} (\emph{R-28, R-35}) restrict domains and ranges of properties.
 Only \emph{skos:ConceptSchemes}, e.g., can have \emph{skos:hasTopConcept} relationships (\ms{$\exists$ hasTopConcept.$\top$ $\sqsubseteq$ ConceptScheme}) and
 \emph{xkos:belongsTo} relationships can only point to instances of the class \emph{skos:Concept} (\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}).
-A \emph{universal quantification}\footnote{\emph{R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}} contains all those individuals that are connected by a property only to individuals/literals that are instances of particular classes  or data ranges.
+A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals that are instances of particular classes  or data ranges.
 Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets} (\ms{Catalog $\sqsubseteq$ $\forall$ dataset.Dataset}).
-An \emph{existential quantification}\footnote{\emph{R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}} contains all those individuals that are connected by a property to individuals/literals that are instances of given classes or data ranges.
+An \emph{existential quantification} (\emph{R-86}) contains all those individuals that are connected by a property to individuals/literals that are instances of given classes or data ranges.
 Every \emph{qb:SliceKey}, e.g., must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}).
 
-\emph{Minimum/maximum/exact qualified cardinality restrictions}\footnote{\emph{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES, \\ R-76-MAXIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES, \\ R-74-EXACT-QUALIFIED-CARDINALITY-ON-PROPERTIES}} contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals that are instances of particular classes or data ranges.
+\emph{Minimum/maximum/exact qualified cardinality restrictions} (\emph{R-74, R-75, R-76}) contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals that are instances of particular classes or data ranges.
 \emph{Minimum qualified cardinality restrictions} are defined for each property of multiple vocabularies like \emph{Disco}.
@@
 %\footnote{\emph{DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02}}.
-For particular data properties, values of predefined languages must be stated for determined number of times\footnote{{\em R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG}, {\em R-48-MISSING-LANGUAGE-TAGS}}.
+For particular data properties, values of predefined languages must be stated for determined number of times (\emph{R-48, R-49}).
 Some controlled vocabularies contain literals in natural language, but without information what language has actually been used. Language tags might also not conform to language standards. 
@@
 All properties, not having the same domain and range classes, are defined to be pairwise disjoint
-(\emph{disjoint properties}\footnote{\emph{R-9-DISJOINT-PROPERTIES}}), stating that no individual \emph{x} can be connected to an individual/literal \emph{y} by disjoint properties like \emph{phdd:isStructuredBy} and \emph{phdd:column} ($isStructuredBy \sqsubseteq \neg column$).
-All \emph{Disco} classes are defined to be pairwise disjoint (\emph{Disjoint Classes}\footnote{\emph{R-7-DISJOINT-CLASSES}}; e.g. \ms{Study $\sqcap$ Variable $\sqsubseteq$ $\perp$}),
+(\emph{R-9: disjoint properties}), stating that no individual \emph{x} can be connected to an individual/literal \emph{y} by disjoint properties like \emph{phdd:isStructuredBy} and \emph{phdd:column} ($isStructuredBy \sqsubseteq \neg column$).
+All \emph{Disco} classes are defined to be pairwise disjoint (\emph{R-7: disjoint classes}; e.g. \ms{Study $\sqcap$ Variable $\sqsubseteq$ $\perp$}),
 i.e. no individual can be at the same time an instance of more than one disjoint class.
 It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values.  
-\emph{Allowed values}\footnote{\emph{R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS}, 
-\emph{R-37-ALLOWED-VALUES-FOR-RDF-LITERALS}} for properties can be IRIs (matching one or multiple patterns), any literals, allowed literals (e.g.
+\emph{Allowed values} (\emph{R-30, R-37}) for properties can be IRIs (matching one or multiple patterns), any literals, allowed literals (e.g.
 'red' 'blue' 'green'), and typed literals of one or multiple type(s) (e.g.
@@
 Constraints of some constraint types can be derived from vocabularies' data models for which reasoning can be performed prior to validation which enables to resolve possible constraint violations.
-\emph{Subsumption}\footnote{\emph{R-100-SUBSUMPTION}} states that the class \emph{C1} is a sub-class of the class \emph{C2} - \emph{C1} is more specific than \emph{C2}, 
+\emph{Subsumption} (\emph{R-100}) states that the class \emph{C1} is a sub-class of the class \emph{C2} - \emph{C1} is more specific than \emph{C2}, 
 i.e. each resource of the class \emph{C1} must also be part of the class extension of \emph{C2}. 
 All \emph{disco:Universe}s, e.g., must also be \emph{skos:Concept}s (\ms{Universe $\sqsubseteq$ Concept}).
-\emph{Sub Properties}\footnote{\emph{R-54-SUB-OBJECT-PROPERTIES}, \emph{R-54-SUB-DATA-PROPERTIES}} state that the property \emph{P1} is a sub-property of the property \emph{P2} - that is, if individual \emph{x} is connected by \emph{P1} to individual/literal \emph{y}, then \emph{x} is also connected by \emph{P2} to \emph{y}.
+\emph{Sub Properties} (\emph{R-54, R-64}) state that the property \emph{P1} is a sub-property of the property \emph{P2} - that is, if individual \emph{x} is connected by \emph{P1} to individual/literal \emph{y}, then \emph{x} is also connected by \emph{P2} to \emph{y}.
 If \emph{x} is connected by \emph{disco:fundedBy} to \emph{y}, then \emph{x} is also connected by \emph{dcterms:contributor} to \emph{y} (\ms{fundedBy $\sqsubseteq$ contributor}).
-\emph{Asymmetric object properties}\footnote{\emph{R-62-ASYMMETRIC-OBJECT-PROPERTIES}} restrict that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}.
+\emph{Asymmetric object properties} (\emph{R-62}) restrict that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}.
 \emph{Asymmetric object properties} are defined for each asymmetric object property for which a semantically equivalent object property pointing from the other direction may also be possible to be specified in the appropriate vocabulary.
@@
 A \emph{disco:RepresentedVariable}, however, cannot be based on a \emph{disco:Variable} (\ms{$basedOn \sqcap basedOn^{-} \sqsubseteq \bot$}).
-\emph{Default values}\footnote{{\em R-31-DEFAULT-VALUES-OF-RDF-OBJECTS}, {\em R-38-DEFAULT-VALUES-OF-RDF-LITERALS}} for objects/literals of given prooperties are inferred automatically when properties are not stated, in order to pre-populate input forms and to insert a required property that is missing in a web service call.
+\emph{Default values} (\emph{R-31, R-38}) for objects/literals of given prooperties are inferred automatically when properties are not stated, in order to pre-populate input forms and to insert a required property that is missing in a web service call.
 The value \emph{true} for the property {\em disco:isPublic} ({\em xsd:boolean}) indicates that the data set ({\em disco:LogicalDataSet}) can be accessed by anyone.

### 2015-02-28 paper/paper7/paper7.tex
running example

@@
 The data could be either represented in records with character-separated values (CSV) or in records with fixed length. 
-
-\begin{ex}
-EXAMPLE
-\end{ex}
+The two-dimensional table about \emph{formal childcare} can be downloaded as CSV file\footnote{CSV file and complete PHDD representation available at: \url{XXXXX}}. 
+The table is represented as \emph{phdd:Table} and structured by a table structure (\emph{phdd:TableStructure}, \emph{phdd:Delimited}).
+The running example table structure includes information about the character set (\emph{ASCII}), the variable delimiter (\emph{,}), the new line marker (\emph{CRLF}), and the first line where the data starts (\emph{2}).
+The table structure relates to the table columns (\emph{phdd:Column}) which are described by column descriptions (\emph{phdd:DelimitedColumnDescription}).
+For the column containing the cell values in percent, e.g., the CSV column position (\emph{5}), the recommended data type (\emph{xsd:nonNegativeInteger}), and the storage format (\emph{TINYINT}) is stated.
 

### 2015-02-28 paper/paper7/paper7.tex
RDFication of running example

@@
 (2) metadata providers and harvesters ensuring high quality metadata by validating metadata on highly complex RDF data sets.
-In this paper, we show in form of a complete real world running example how to represent metadata on highly complex person-level data (\emph{Disco}), metadata on aggregated data (\emph{Data Cube}), and aggregated data in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, sections \ref{running-example}-\ref{rdf-representation}).
+In this paper, we show in form of a complete real world running example how to represent metadata on highly complex person-level data (\emph{Disco}), metadata on aggregated data (\emph{Data Cube}), and aggregated as well as person-level data in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
 We explain why RDF validation is important in this context and how (meta)data is validated against RDF constraints to ensure high quality (meta)data within this complex of data sets on different levels of aggregation (\textbf{contribution 2}, section \ref{rdf-validation}).
@@
 
-\section{Running Example}
-\label{running-example}
+%\section{Running Example}
+%\label{running-example}
+\section{Represent Metadata and Data in RDF}
+\label{rdf-representation}
 
@@
 SBE researchers have a strong interest, e.g., in the availability of childcare services across European Union Member States.
+
+\textbf{Metadata on Aggregated Data in RDF.}
 The variable \emph{formal childcare}\footnote{\url{http://appsso.eurostat.ec.europa.eu/nui/show.do?dataset=ilc_caindformal&lang=en}} (in contrast to childcare at home)
@@
 The present data collection refers to data on formal childcare and other types of care by the variables \emph{year}, \emph{duration} (0 hours, 1 - 29 HPW; 30 HPW), \emph{age} of the child (0-2 years; 3 to admission age for compulsory school; admission age for compulsory school to 12) and \emph{country}.
-As Eurostat provides aggregated data (here a two-dimensional table) as CSV files, we can easily represent the aggregated data with \emph{PHDD} in RDF. 
-This conversion enables further aggregations and calculations, e.g., in order to compare \emph{formal childcare} between Northern and Southern Europe or between otherwise grouped countries.
+
+\tb{ToDO: insert how example is represented in Data Cube in this paragraph}
+
+\emph{Data Cube} is a vocabulary to represent metadata on multi-dimensional aggregate data.
+
+\begin{ex}
+EXAMPLE
+\end{ex}
+
+\textbf{Aggregated Data in RDF.}
+As Eurostat provides aggregated data as CSV files, we can easily represent the two-dimensional table in RDF by means of \emph{PHDD}.
+\emph{PHDD} is a vocabulary to represent aggregated and person-level data in a rectangular format. 
+The data could be either represented in records with character-separated values (CSV) or in records with fixed length. 
+The two-dimensional table about \emph{formal childcare} can be downloaded as CSV file\footnote{CSV file and complete PHDD representation available at: \url{XXXXX}}. 
+The table is represented as \emph{phdd:Table} and structured by a table structure (\emph{phdd:TableStructure}, \emph{phdd:Delimited}).
+The running example table structure includes information about the character set (\emph{ASCII}), the variable delimiter (\emph{,}), the new line marker (\emph{CRLF}), and the first line where the data starts (\emph{2}).
+The table structure relates to the table columns (\emph{phdd:Column}) which are described by column descriptions (\emph{phdd:DelimitedColumnDescription}).
+For the column containing the cell values in percent, e.g., the CSV column position (\emph{5}), the recommended data type (\emph{xsd:nonNegativeInteger}), and the storage format (\emph{TINYINT}) is stated.
+The RDFication enables further aggregations and calculations, e.g., in order to compare \emph{formal childcare} between Northern and Southern Europe or between otherwise grouped countries.
 % macht mehr sinn wenn Tabelle in mehreren Dimensionen vorhanden ist ode wenn Klassifikationen wie ISCO verwendet werden
 
+\textbf{Metadata on Person-Level Data in RDF.}
 For a broader view of the data framework and more detailed analyses we refer to the metadata on person-level data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}.
@@
 \emph{formal childcare} between countries, for which the variable is collected within the context of an individual survey, and other European or non European countries (e.g. OSCE).
-
-\section{Represent Metadata and Data in RDF}
-\label{rdf-representation}
-
-\emph{Data Cube} is a vocabulary to represent metadata on multi-dimensional aggregate data.
-
-\begin{ex}
-EXAMPLE
-\end{ex}
-
-\emph{PHDD} is a vocabulary to represent aggregated data in a rectangular format. 
-The data could be either represented in records with character-separated values (CSV) or in records with fixed length. 
-The two-dimensional table about \emph{formal childcare} can be downloaded as CSV file\footnote{CSV file and complete PHDD representation available at: \url{XXXXX}}. 
-The table is represented as \emph{phdd:Table} and structured by a table structure (\emph{phdd:TableStructure}, \emph{phdd:Delimited}).
-The running example table structure includes information about the character set (\emph{ASCII}), the variable delimiter (\emph{,}), the new line marker (\emph{CRLF}), and the first line where the data starts (\emph{2}).
-The table structure relates to the table columns (\emph{phdd:Column}) which are described by column descriptions (\emph{phdd:DelimitedColumnDescription}).
-For the column containing the cell values in percent, e.g., the CSV column position (\emph{5}), the recommended data type (\emph{xsd:nonNegativeInteger}), and the storage format (\emph{TINYINT}) is stated.
 

### 2015-03-01 paper/paper7/paper7.tex
SKOS and XKOS in RDF

@@
 
+\footnote{The complete running example in RDF is available at: \url{XXXXX}}
+
 \textbf{Aggregated Data in RDF.}
@@
 The data could be either represented in records with character-separated values (CSV) or in records with fixed length. 
-The two-dimensional table about \emph{formal childcare} can be downloaded as CSV file\footnote{CSV file and complete PHDD representation available at: \url{XXXXX}}. 
+The two-dimensional table about \emph{formal childcare} can be downloaded as CSV file. 
 The table is represented as \emph{phdd:Table} and structured by a table structure (\emph{phdd:TableStructure}, \emph{phdd:Delimited}).
@@
 \textbf{Metadata on Person-Level Data in RDF.}
-For a broader view of the data framework and more detailed analyses we refer to the metadata on person-level data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}.
-The \emph{Microdata Information System (MISSY)}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}} is an online service platform that provides systematically structured metadata for official statistics on European person-level data sets.
+For a broader view of the data framework and more detailed analyses we refer to the metadata on person-level data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}
+and publicly provided by the \emph{Microdata Information System (MISSY)}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}}.
+\emph{Missy} is an online service platform that provides systematically structured metadata for official statistics on European person-level data sets.
 This includes data documentation at the study and variable level as well as documentation materials, tools and further information.
@@
 For each person-level variable detailed metadata is given (definitions and descriptions, theoretical concepts, underlying questions, code lists, frequencies and descriptive statistics, countries, year of data collection, classifications) enabling researchers to replicate the results shown in the aggregated data tables from Eurostat.
+Metadata on person-level data is represented in RDF using the \emph{Disco} vocabulary.
+The series (\emph{disco:StudyGroup}) \emph{EU-SILC} contains (\emph{disco:inGroup}) one study (\emph{disco:Study}) for each year (\emph{dcterms:temporal}) of data collection, e.g.
+\emph{EU-SILC 2011}.
+The property \emph{dcterms:spatial} points to the countries (\emph{dcterms:Location} resources which are the same as \emph{GeoNames} resources representing these countries) for which the data has been collected.
+The study \emph{EU-SILC 2011} contains (\emph{disco:product}) eight person-level data sets (\emph{disco:LogicalDataSet}).
+Data sets include (\emph{disco:variable}) person-level variables (\emph{disco:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
+\emph{DCAT} enables to represent aggregated and person-level data inside of data collections like repositories, catalogs, or archives. 
+\tb{ToDo: DCAT example}
+
 Metadata on person-level data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
@@
 
-\emph{Disco} is a vocabulary to represent person-level data in RDF.
-
-\begin{ex}
-EXAMPLE
-\end{ex}
-
-\emph{DCAT} enables to represent aggregated and person-level data inside of data collections like repositories, catalogs, or archives.
-
-\begin{ex}
-EXAMPLE
-\end{ex}
-
-The \emph{Simple Knowledge Organization System (SKOS)} is used multiple times within the context of aggregated and person-level (meta)data, e.g., to represent controlled vocabularies or hierarchies of \emph{SBE theoretical concepts} (e.g.
-education).
-
-\begin{ex}
-EXAMPLE
-\end{ex}
-
-\emph{XKOS}\footnote{\url{https://github.com/linked-statistics/xkos}} is a \emph{SKOS} extension to describe formal statistical classifications like the International Standard Classification of Occupations (\emph{ISCO}) and the Statistical classification of economic activities in the European Community \emph{NACE}.
-
-\begin{ex}
-EXAMPLE
-\end{ex}
+The \emph{Simple Knowledge Organization System (SKOS)} is used multiple times within the context of aggregated and person-level (meta)data.
+Variables, e.g., are constructed (\emph{disco:representation}) out of values (of one or multiple datatypes) and/or code lists.
+The values of the variable \emph{Education at pre-school}, representing the number of education hours during a usual week, are expressed as \emph{skos:Concepts}. 
+\emph{Disco} uses \emph{skos:OrderedCollection} to organize them in a particular order in a \emph{skos:memberList}. 
+SKOS is also used to form hierarchies of \emph{SBE theoretical concepts} (e.g. Education) with which variables may be associated.
+The compete hierarchy (\emph{skos:ConceptScheme}) of theoretical concepts (\emph{skos:Concepts}) of series is built using \emph{skos:narrower}.
+The variable \emph{Education at pre-school} is assigned to the theoretical concept \emph{Child Care} which is a narrower concept of \emph{Education} - one of the top concept of the series \emph{EU-SILC}.
+Controlled vocabularies serve as extension and reuse mechanism.
+For \emph{Disco}, concepts (\emph{skos:Concepts}), organized within controlled vocabularies (\emph{skos:ConceptSchemes}), indicate types of descriptive statistics (\emph{\emph{disco:SummaryStatistics}}) like minimum, maximum, mean, and standard deviation.
+From 2012 to 2015, SBE and Linked Data community members developed \emph{XKOS}\footnote{\url{https://github.com/linked-statistics/xkos}} - a SKOS extension to describe formal statistical classifications like the International Standard Classification of Occupations (\emph{ISCO}) and the Statistical Classification of Economic Activities in the European Community \emph{NACE}.
 

### 2015-03-01 paper/paper7/paper7.tex
Searching for metadata and data

@@
 particularly as this is taken for granted in the XML world.
-The data most often used in research within the community around research data for the social, behavioural, and economic sciences is person-level data, i.e.
+The data most often used in research within the community around research data for the social, behavioural, and economic sciences (\emph{SBE}) is person-level data, i.e.
 data collected about individuals (households, businesses).
@@
 To ensure high quality and trust, metadata and data must satisfy certain criteria - specified in terms of RDF constraints. 
+From 2012 to 2015 together with other Linked Data community members and \emph{SBE} experts, we developed diverse vocabularies to represent \emph{SBE} metadata and data in RDF.
 
@@
 This includes data documentation at the study and variable level as well as documentation materials, tools and further information.
+Aggregated (qb:DataSet) and underlying person-level data sets (\emph{disco:LogicalDataSet}) are connected by \emph{prov:wasDerivedFrom}. 
 The aggregated variable \emph{formal childcare} is calculated on the basis of six person-level variables like 
@@
 Data sets include (\emph{disco:variable}) person-level variables (\emph{disco:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
-\emph{DCAT} enables to represent aggregated and person-level data inside of data collections like repositories, catalogs, or archives. 
-\tb{ToDo: DCAT example}
-
 Metadata on person-level data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
@@
 
+\textbf{Organizations, Hierarchies, and Classifications.}
+%\textbf{Reusing SKOS.}
 The \emph{Simple Knowledge Organization System (SKOS)} is used multiple times within the context of aggregated and person-level (meta)data.
@@
 For \emph{Disco}, concepts (\emph{skos:Concepts}), organized within controlled vocabularies (\emph{skos:ConceptSchemes}), indicate types of descriptive statistics (\emph{\emph{disco:SummaryStatistics}}) like minimum, maximum, mean, and standard deviation.
-From 2012 to 2015, SBE and Linked Data community members developed \emph{XKOS}\footnote{\url{https://github.com/linked-statistics/xkos}} - a SKOS extension to describe formal statistical classifications like the International Standard Classification of Occupations (\emph{ISCO}) and the Statistical Classification of Economic Activities in the European Community \emph{NACE}.
+From 2012 to 2015, SBE and Linked Data community members developed \emph{XKOS}\footnote{\url{https://github.com/linked-statistics/xkos}} - a SKOS extension to describe formal statistical classifications like the International Standard Classification of Occupations (\emph{ISCO}).
+%and the Statistical Classification of Economic Activities in the European Community \emph{NACE}.
+
+\textbf{Searching for (Meta)data.}
+\emph{DCAT} enables to represent aggregated and person-level data inside of data collections like portals, repositories, catalogs, or archives
+serving as typical entry points when searching for data.
+Users search for aggregated and person-level data records (\emph{dcat:CatalogRecord}) inside data catalogs (\emph{dcat:Catalog}). 
+This search differs depending on the users’ information need. 
+While it is possible to search for metadata provided inside such a record (e.g. \emph{dcterms:title}, \emph{dcterms:description}), 
+users can also formulate more sophisticated queries on aggregated and person-level data sets (\emph{dcat:Dataset}) or their
+distributions (\emph{dcat:Distribution}), which are part of the records. 
+Users may want to search for data sets covering particular topical (\emph{dcat:keyword}, \emph{dcat:theme}), temporal (\emph{dcterms:temporal}),  or  spatial  coverages (\emph{dcterms:spatial}), 
+or certain formats in which the data distribution is available (\emph{dcterms:format}).
 

### 2015-03-01 paper/paper7/paper7.tex
4.2

@@
 
-\tb{terminology: we use data in singular form / we use data set instead of dataset / We use person-level data and not microdata}
+\tb{terminology: data in singular form / data set - NOT dataset / person-level data - NOT microdata / study - NOT survey}
 
@@
 The data most often used in research within the SBE community is \emph{person-level data}, i.e. data collected about individuals 
-(and sometimes also businesses and households) in the form of responses to surveys or taken from administrative registers
+(and sometimes also businesses and households) in the form of responses to studies or taken from administrative registers
 (such as hospital records, registers of births and deaths). 
@@
 %i.e. researchers may use metadata on person-level data to search for aggregated data.
-One very common example for detailed analyses on person-level data is the content-driven comparison of multiple surveys.
+One very common example for detailed analyses on person-level data is the content-driven comparison of multiple studies.
 Researchers get promising findings (in form of published tables with a few columns) within a metadata portal leading to subsequent research questions 
 like 'How to compare the unemployment rate of different countries (e.g. Germany, UK, and France) in the last 10 years grouped by age?'.
-The first step is to determine in which countries the unemployment rate is collected and which other variables of each country-specific survey are theoretically comparable and can therefore be used to answer the underlying research question.
+The first step is to determine in which countries the unemployment rate is collected and which other variables of each country-specific study are theoretically comparable and can therefore be used to answer the underlying research question.
 Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
@@
 To determine if variables measuring \emph{age} 
-- collected within multiple surveys of different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
+- collected within multiple studies of different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
 are comparable, both content-driven and technology-driven validation is performed either
@@
 One common research question is ,e.g., the comparison of variables like 
-\emph{formal childcare} between countries, for which the variable is collected within the context of an individual survey, and other European or non European countries (e.g. OSCE).
+\emph{formal childcare} between countries, for which the variable is collected within the context of an individual study, and other European or non European countries (e.g. OSCE).
 
@@
 
-\textbf{Surveys.}
-Each survey must have an abstract ({\emph{R-46: data property facets}). 
-If the abstract of the survey is missing, a title of the survey has to be stated (\emph{R-71: conditional properties}).
+\textbf{Studies.}
+A \emph{study} represents the process by which a data set was generated or collected.
+Each study must have an abstract ({\emph{R-46: data property facets}), or if the abstract is missing, a title (\emph{R-71: conditional properties}).
 
@@
 - variable does not have associated codes / categories
+
+It is useful to declare properties to be conditional, i.e. if particular properties exist, then specific other properties must also be present (\emph{R-71: conditional properties}).
+If a {\em skos:Concept} represents a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
+then the property {\em disco:isValid} has to be stated indicating if the code is valid (\emph{true}) or missing (\emph{false}).
+%\footref{R-71-CONDITIONAL-PROPERTIES}
 
@@
 
-A very common research question is to compare variables (\emph{comparison}) of multiple surveys or countries.
+\textbf{Comparison.}
+A very common research question is to compare variables (\emph{comparison}) of multiple studies or countries.
 To compare variables, 
@@
 
+\textbf{Reusability.}
 Constraints of the constraint type \emph{Context-Specific Exclusive OR of Property Groups} (\emph{R-11})
@@
 
-It is useful to declare properties to be conditional, i.e. if particular properties exist, then specific other properties must also be present (\emph{R-71: conditional properties}).
-If a {\em skos:Concept} represents a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
-then the property {\em disco:isValid} has to be stated indicating if the code is valid (\emph{true}) or missing (\emph{false}).
-%\footref{R-71-CONDITIONAL-PROPERTIES}
-
------
-
+\textbf{Frequencies and Descriptive Statistics.}
 Restricting data property ranges [$V_{min}$,$V_{max}$] within the context of given classes is a very common requirement (\emph{R-45: literal ranges}) 
@@
 
------
+{\em Mathematical Operations} (\emph{R-41, R-42}; e.g. date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
+The sum of {\em disco:percentage} (datatype: {\em xsd:double}) values of all codes ({\em skos:Concept}s) of a code list ({\em skos:ConceptScheme} or {\em skos:OrderedCollection}), serving as representation of a particular {\em disco:Variable} must exactly be 100.
 
+\textbf{Unique Identification.}
 It is often useful to declare a given (data) property as the \emph{primary key} (\emph{R-226}) of a class, so that a system can enforce uniqueness and also automatically build URIs from user inputs and imported data.
@@
 
------
-
+\textbf{Membership in Controlled Vocabularies.}
 In many cases, resources must be members of listed controlled vocabularies (\emph{R-32}).
@@
 
------
-
+\textbf{Coverage.}
 Depending on property datatypes,
@@
 
------
-
-Objects/literals can be ordered (\emph{R-121, R-217}) for given properties.
-\emph{Disco }variables, questions, and codes/categories are typically organized in a particular order. 
-If codes/categories of a \emph{disco:Representation} of a \emph{disco:Variable} should be ordered, the variable representation should also be of the type \emph{skos:OrderedCollection} containing multiple codes/categories (each represented as \emph{skos:Concept}) in a \emph{skos:memberList}.
-
------
-
-{\em Mathematical Operations} (\emph{R-41, R-42}; e.g. date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
-The sum of {\em disco:percentage} (datatype: {\em xsd:double}) values of all codes ({\em skos:Concept}s) of a code list ({\em skos:ConceptScheme} or {\em skos:OrderedCollection}), serving as representation of a particular {\em disco:Variable} must exactly be 100.
-
------
-
-\textbf{DCAT Validation}
-
-\textbf{SKOS and XKOS Validation}
-
+\textbf{Organizations, Hierarchies, Classifications, and Ordering.}
 SKOS is based on RDF, which is a graph-based data model.
@@
 \tb{add disco example}
+
+Objects/literals can be ordered (\emph{R-121, R-217}) for given properties.
+\emph{Disco }variables, questions, and codes/categories are typically organized in a particular order. 
+If codes/categories of a \emph{disco:Representation} of a \emph{disco:Variable} should be ordered, the variable representation should also be of the type \emph{skos:OrderedCollection} containing multiple codes/categories (each represented as \emph{skos:Concept}) in a \emph{skos:memberList}.
+
 - SKOS validation of hierarchies of theoretical concepts
 
-XKOS Validation:
+\tb{ToDO: ask Franck if INSEE already expressed well known classification systems with XKOS}
 
-\tb{ToDO: ask Franck if INSEE already expressed well known classification systems with XKOS}
+\textbf{Searching for (Meta)data.}
+
+- DCAT
 

### 2015-03-01 paper/paper7/paper7.tex
implementation

@@
 
-- Missy / DDI-RDF export / multiple concrete syntaxes / Triple store / content negotiation / reference implementation of the Disco data model / Missy data model is based in Disco data model
+With \emph{Missy}, we provide comprehensive Linked Data services\footnote{\textcolor{red}{\url{www.gesis.org/en/missy/linked-data}}} like a \textcolor{red}{triple store} and exports of person-level metadata to Disco RDF in multiple concrete syntaxes (e.g.
+turtle).
 
-- RDF validator
+SPARQL is generally seen as the method of choice to validate RDF data according to certain constraints.
+We use the \emph{SPIN}\footnote{\url{http://spinrdf.org/}}, 
+a SPARQL-based way to formulate and check constraints, as basis to define a
+validation environment (available at \url{http://purl.org/net/rdfval-demo}) \cite{BoschEckert2014-2}.
+The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.
+Within the validation environment, we define one SPIN construct template for each constraint type (corresponding to a requirement) and vocabulary-specific constraint \footnote{For details about the validation environment see \cite{BoschEckert2014-2}}.
+A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples (\emph{spin:ConstraintViolation}) indicating the subject (\emph{spin:violationRoot}) and the properties (\emph{spin:violationPath}), causing constraint violations, and the reason why constraint violations have been raised (\emph{rdfs:label}).
+A SPIN construct template creates constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
 
-\textbf{Validation of Data Cube instances.}
-\begin{itemize}
-	\item \textcolor{blue}{is there an implementation available yet? If not I implement it in our validation environment}
-	\item \textcolor{blue}{example QB data set / we could use the one from the QB spec}
-\end{itemize}
+- Validation of Data Cube instances
 
 \section{Evaluation}
+
+For \emph{Disco} RDF data, we validated XX series, XX studies, XX data sets, XX theoretical concepts, XX variables, XX questions, XX codes, XX category statistics (frequencies), and XX summary statistics (descriptive statistics like minimum).
 
@@
 \end{itemize}
+
+%\begin{table}
+	%\centering
+		%\begin{tabular}{l|c|c|c|c|c|c}
+      %\textbf{Expressivity Class} & \textbf{DSP} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\		
+      %\hline
+      %$Expr(\overline{\mathcal{C}_R})$ (42) & 6 & 18(4) & 7(4) & 8 & 12 & 41(1)\\
+      %$Expr(\mathcal{C}_R)$ (32) & 8 & 29 & 11 & 11(2) & 11(1) & 32 \\ 	
+		%\end{tabular}
+	%\caption{Constraint Type Specific Expressivity}
+	%\label{tab:constraint-type-specific-expressivity}
+%\end{table}
 

### 2015-03-02 paper/paper7/paper7.tex
implementation

@@
 
-With \emph{Missy}, we provide comprehensive Linked Data services\footnote{\textcolor{red}{\url{www.gesis.org/en/missy/linked-data}}} like a \textcolor{red}{triple store} and exports of person-level metadata to Disco RDF in multiple concrete syntaxes (e.g.
+In \emph{Missy}, we provide comprehensive Linked Data services\footnote{\textcolor{red}{\url{www.gesis.org/en/missy/linked-data}}} like a \textcolor{red}{triple store} and diverse RDF exports of person-level metadata conforming to the \emph{Disco} vocabulary in multiple concrete syntaxes (e.g.
 turtle).
@@
 SPARQL is generally seen as the method of choice to validate RDF data according to certain constraints.
-We use the \emph{SPIN}\footnote{\url{http://spinrdf.org/}}, 
+We use \emph{SPIN}\footnote{\url{http://spinrdf.org/}}, 
 a SPARQL-based way to formulate and check constraints, as basis to define a
-validation environment (available at \url{http://purl.org/net/rdfval-demo}) \cite{BoschEckert2014-2}.
+validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages like Shape Expressions\footnote{\url{http://www.w3.org/Submission/shex-primer/}} and the Web Ontology Language \cite{BoschEckert2014-2}.
+The \emph{RDF Validator} also validates RDF data conforming to SPARQL constraints to ensure correct syntax and semantics of vocabularies such as \emph{Disco, Data Cube, PHDD, DCAT, SKOS, and XKOS}.
 The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.
-Within the validation environment, we define one SPIN construct template for each constraint type (corresponding to a requirement) and vocabulary-specific constraint \footnote{For details about the validation environment see \cite{BoschEckert2014-2}}.
-A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples (\emph{spin:ConstraintViolation}) indicating the subject (\emph{spin:violationRoot}) and the properties (\emph{spin:violationPath}), causing constraint violations, and the reason why constraint violations have been raised (\emph{rdfs:label}).
+We define one SPIN construct template for each constraint type (corresponding to a requirement) and vocabulary-specific constraint\footnote{For details about the validation environment see \cite{BoschEckert2014-2}}.
+A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples indicating the subject, the properties causing constraint violations, and the reason why constraint violations have been raised.
 A SPIN construct template creates constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
-
-- Validation of Data Cube instances
 

### 2015-03-02 paper/paper7/paper7.tex
4

@@
 
-Bosch et al. identified in total 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
+Bosch et al. identified in total \textcolor{red}{74} requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
 We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement (constraint type) in detail and give examples for each (represented by different constraint languages).
@@
 Therefore, this technical report contains mappings to DL to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
-Bosch et al.
-recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/XXXXX}} (serving as appendix of this paper) in which we describe RDF constraints to validate metadata on person-level and aggregated data.
+We recently published a technical report\footnote{\textcolor{red}{Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as appendix of this paper) in which we describe RDF constraints to validate metadata on person-level and aggregated data.
 We assign each constraint to constraint types corresponding to RDF validation requirements or to data model specific constraint types\footnote{Requirements/Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-1}}
-\cite{BoschZapilkoWackerowEckert2015}\tb{ToDo: publish technical report}.
+\cite{BoschZapilkoWackerowEckert2015}.
 
 We distinguish two validation types:
-\emph{Content-Driven Validation} contains the set of constraints ensuring that the data is consistent with the intended semantics of data models,
-i.e. the integrity of the data according to data models.
-\emph{Technology-Driven Validation} includes the set of constraints which can be generated automatically out of defined data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges.
-We determined the default \emph{severity level} (\emph{R-158}) for each constraint indicating how serious the violation of the constraint is.
+(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of given data models (sections \ref{aggregated-metadata-and-data}-\ref{person-level-metadata-and-data}).
+(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges (section \ref{technology-driven-validation}).
+We determined the default \emph{severity level} (corresponds to requirement \emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
 The continuum of severity levels ranges from informational via warning and error to fatal error. 
-Although we provide default severity levels for each constraint, users should be able to specify the severity levels of constraints they need to validate for their individual use cases, i.e., users should be able to define use case specific severity levels for constraints.
+Although we provide default severity levels for each constraint, users should be able to specify severity levels of constraints they need to validate for their individual use cases, i.e., users should be able to define use case specific severity levels for constraints.
 
@@
 %-----
+
+further ideas:
 
@@
 
-\subsection{Aggregated (Meta)Data}
+\subsection{Aggregated Metadata and Data}
+\label{aggregated-metadata-and-data}
 
@@
 
-\subsection{Person-Level (Meta)Data}
+\subsection{Person-Level Metadata and Data}
+\label{person-level-metadata-and-data}
 
@@
 \subsection{Technology-Driven Validation}
+\label{technology-driven-validation}
 

### 2015-03-02 paper/paper7/paper7-appendix.tex
4.2

@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-DATA-PROPERTY-FACETS-01:}} The abstract of a study (\emph{disco:purpose}) should have a minimum length (\emph{xsd:minInclusive}) of x. 
+	\item \textbf{{\em DISCO-C-DATA-PROPERTY-FACETS-01:}} The abstract of a study (\emph{disco:purpose}) should have a minimum length (\emph{xsd:minLength}) of x. 
 \end{itemize}

### 2015-03-02 paper/paper7/paper7.tex
4.2

@@
 The first step is to determine in which countries the unemployment rate is collected and which other variables of each country-specific study are theoretically comparable and can therefore be used to answer the underlying research question.
+A \emph{study} represents the process by which a data set was generated or collected.
 Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
@@
 and publicly provided by the \emph{Microdata Information System (MISSY)}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}}.
+Where data collection is cyclic, data sets may be released as a \emph{series}, 
+where each cycle of the data collection activity produces one or more data sets. 
 \emph{Missy} is an online service platform that provides systematically structured metadata for official statistics on European person-level data sets.
@@
 \textbf{Studies.}
-A \emph{study} represents the process by which a data set was generated or collected.
-Each study must have an abstract ({\emph{R-46: data property facets}), or if the abstract is missing, a title (\emph{R-71: conditional properties}).
+For datatype properties it should be possible to declare frequently needed \emph{facets} to drive user interfaces and validate input against simple conditions, including min/max values, regular expressions, and string length ({\emph{R-46: data property facets}).
+Each study must have an abstract, i.e., the abstract (\emph{disco:purpose}) should have a minimum length (\emph{xsd:minLength}) of 0.
+It is useful to declare properties to be conditional, i.e., if particular properties exist (or do not exist), then specific other properties must also be present (\emph{R-71: conditional properties}).
+If the abstract of a study is missing, a title has to be stated.
 
@@
 
-It is useful to declare properties to be conditional, i.e. if particular properties exist, then specific other properties must also be present (\emph{R-71: conditional properties}).
+ (\emph{R-71: conditional properties}).
 If a {\em skos:Concept} represents a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 

### 2015-03-02 paper/paper7/paper7.tex
4.2

@@
 \textbf{Variables.}
-
-- variable does not have associated codes / categories
-
- (\emph{R-71: conditional properties}).
+Each variable should have a variable representation (\emph{R-86: existential quantification}), which is either an (un)ordered code list or a union of XML Schema datatypes.
 If a {\em skos:Concept} represents a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
-then the property {\em disco:isValid} has to be stated indicating if the code is valid (\emph{true}) or missing (\emph{false}).
+then the property {\em disco:isValid} has to be stated indicating if the code is valid (\emph{true}) or missing (\emph{false}) (\emph{R-71: conditional properties}).
 %\footref{R-71-CONDITIONAL-PROPERTIES}

### 2015-03-02 paper/paper7/paper7.tex
added severity levels metric

--- 2015-03-02 paper/paper7/paper7.tex
@@
 We determined the default \emph{severity level} (corresponds to requirement \emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
-The continuum of severity levels ranges from informational via warning and error to fatal error. 
+We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ (informational) via $\mathcal{SL}_{1}$ (warning) to $\mathcal{SL}_{2}$ (error). 
 Although we provide default severity levels for each constraint, users should be able to specify severity levels of constraints they need to validate for their individual use cases, i.e., users should be able to define use case specific severity levels for constraints.
@@
 For datatype properties it should be possible to declare frequently needed \emph{facets} to drive user interfaces and validate input against simple conditions, including min/max values, regular expressions, and string length ({\emph{R-46: data property facets}).
-Each study must have an abstract, i.e., the abstract (\emph{disco:purpose}) should have a minimum length (\emph{xsd:minLength}) of 0.
+Each study must have an abstract, i.e., the abstract (\emph{disco:purpose}) should have a minimum length (\emph{xsd:minLength}) of 0 ($\mathcal{SL}_{1}$).
 It is useful to declare properties to be conditional, i.e., if particular properties exist (or do not exist), then specific other properties must also be present (\emph{R-71: conditional properties}).
-If the abstract of a study is missing, a title has to be stated.
+If the abstract of a study is missing, a title has to be stated ($\mathcal{SL}_{2}$).
 
 \textbf{Variables.}
-
-- variable does not have associated codes / categories
-
- (\emph{R-71: conditional properties}).
+Each variable should have a variable representation (\emph{R-86}; $\mathcal{SL}_{1}$), which is either an (un)ordered code list or a union of XML Schema datatypes.
+In case of a code list, associated categories should be stated (\emph{R-71}; $\mathcal{SL}_{0}$).
+As the variable \emph{Education at pre-school} has an associated code list, the constraint is not violated.
 If a {\em skos:Concept} represents a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
-then the property {\em disco:isValid} has to be stated indicating if the code is valid (\emph{true}) or missing (\emph{false}).
-%\footref{R-71-CONDITIONAL-PROPERTIES}
+then the property {\em disco:isValid} has to be stated indicating if the code is valid (\emph{true}) or missing (\emph{false}) (\emph{R-71}; $\mathcal{SL}_{1}$).
 
@@
 %The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
-The variable \emph{Education at pre-school}, e.g., is associated with the theoretical concept \emph{education}. 
-The severity level of this constraint is \emph{warning} and not \emph{error}, as research can be continued without an associated theoretical concept.
+The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{education}. 
+The default severity level of this constraint is \emph{warning} and not \emph{error}, as in most cases research can be continued without an associated theoretical concept of a given variable.
 

### 2015-03-03 paper/paper7/paper7.tex
4.2

@@
 \textbf{Variables.}
-Each variable should have a variable representation (\emph{R-86}; $\mathcal{SL}_{1}$), which is either an (un)ordered code list or a union of XML Schema datatypes.
+Each variable should have a variable representation (\emph{R-86}; $\mathcal{SL}_{1}$), which is either an (un)ordered code list or a union of datatypes.
 In case of a code list, associated categories should be stated (\emph{R-71}; $\mathcal{SL}_{0}$).
-As the variable \emph{Education at pre-school} has an associated code list, the constraint is not violated.
+The variable \emph{Education at pre-school} has an associated code list, but without any associated categories.
 If a {\em skos:Concept} represents a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
 then the property {\em disco:isValid} has to be stated indicating if the code is valid (\emph{true}) or missing (\emph{false}) (\emph{R-71}; $\mathcal{SL}_{1}$).
+Variables must have at least one relationship to a theoretical concept ({\emph{R-75: minimum qualified cardinality restrictions}; $\mathcal{SL}_{1}$).
+%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
+The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
+The default severity level of this constraint is $\mathcal{SL}_{1}$ and not $\mathcal{SL}_{2}$, as in most cases research can be continued without associated theoretical concepts of given variables.
 
-\textbf{Theoretical Concepts.}
-Variables must have at least one relationship to a theoretical concept ({\emph{R-75: minimum qualified cardinality restrictions}).
-%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
-The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{education}. 
-The default severity level of this constraint is \emph{warning} and not \emph{error}, as in most cases research can be continued without an associated theoretical concept of a given variable.
-
-\textbf{Comparison.}
-A very common research question is to compare variables (\emph{comparison}) of multiple studies or countries.
+\textbf{Variable Comparison.}
+A very common research question is to compare variables of multiple studies or countries (\emph{comparison}).
 To compare variables, 
@@
 the first three constraints may be sufficient for this purpose.
-Thus, the severity level of the first three constraints is stronger than the severity level of the next constraints.
-If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the remaining constraints is also more serious.
-
-\textbf{Reusability.}
-Constraints of the constraint type \emph{Context-Specific Exclusive OR of Property Groups} (\emph{R-11})
-restrict individuals of given classes to have only one of multiple property groups.
-Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes and categories), but not both.
-
-\begin{DL}
-Concept $\sqsubseteq$ ($\neg$ D $\sqcap$ C) $\sqcup$ (D $\sqcap$ $\neg$ C) \\ 
-D $\equiv$ A $\sqcap$ B \\
-A $\sqsubseteq$ $\geq$ 1 notation.string $\sqcap$ $\leq$ 1 notation.string \\
-B $\sqsubseteq$ $\geq$ 1 prefLabel.string $\sqcap$ $\leq$ 1 prefLabel.string \\
-C $\sqsubseteq$ $\geq$ 1 definition.string $\sqcap$ $\leq$ 1 definition.string \\
-\end{DL}
+Thus, the severity level of the first three constraints is stronger ($\mathcal{SL}_{2}$) than the severity level of the next two constraints ($\mathcal{SL}_{1}$).
+If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the remaining constraints is getting more serious ($\mathcal{SL}_{2}$).
 
@@
 
+\begin{center}
 \begin{DL}
@@
 \end{DL}
+\end{center}
 
@@
 \tb{ToDO: ask Franck if INSEE already expressed well known classification systems with XKOS}
+
+\textbf{Reusability.}
+Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes and categories), but not both ($\mathcal{SL}_{2}$).
+Constraints of the constraint type \emph{context-specific exclusive or of property groups} (\emph{R-11})
+restrict individuals of given classes to have exactly one of multiple property groups.
+
+\begin{center}
+\begin{DL}
+Concept $\sqsubseteq$ ($\neg$ D $\sqcap$ C) $\sqcup$ (D $\sqcap$ $\neg$ C), D $\equiv$ A $\sqcap$ B \\
+A $\sqsubseteq$ $\geq$ 1 notation.string $\sqcap$ $\leq$ 1 notation.string \\
+B $\sqsubseteq$ $\geq$ 1 prefLabel.string $\sqcap$ $\leq$ 1 prefLabel.string \\
+C $\sqsubseteq$ $\geq$ 1 definition.string $\sqcap$ $\leq$ 1 definition.string \\
+\end{DL}
+\end{center}
 
@@
 
-In \emph{Missy}, we provide comprehensive Linked Data services\footnote{\textcolor{red}{\url{www.gesis.org/en/missy/linked-data}}} like a \textcolor{red}{triple store} and diverse RDF exports of person-level metadata conforming to the \emph{Disco} vocabulary in multiple concrete syntaxes (e.g.
+In \emph{Missy}, we provide comprehensive Linked Data services\footnote{\textcolor{red}{\url{http://www.gesis.org/missy/eu/general-information/linked-data/}}} like a \textcolor{red}{triple store} and diverse RDF exports of person-level metadata conforming to the \emph{Disco} vocabulary in multiple concrete syntaxes (e.g.
 turtle).

### 2015-03-03 paper/paper7/paper7.tex
4.2

@@
 \textbf{Frequencies and Descriptive Statistics.}
-Restricting data property ranges [$V_{min}$,$V_{max}$] within the context of given classes is a very common requirement (\emph{R-45: literal ranges}) 
-- disco:CategoryStatistics resources, e.g., point to percentage values via the data property \emph{disco:percentage}; 
-these values must be of the datatype \emph{xsd:double} and must be between 0 and 100.
+Percentage values are valid when they are between 0 and 100.
+The constraint type \emph{literal ranges} (\emph{R-45}) restricts data property ranges [$V_{min}$,$V_{max}$] within the context of given classes.
+A constraint of this type applies to the property \emph{disco:percentage} standing for the number of cases of a given code in relation to the total number of cases for a particular variable within a data set ($\mathcal{SL}_{2}$).
+
+-----
 

### 2015-03-03 paper/paper7/paper7.tex
4.2

@@
 A constraint of this type applies to the property \emph{disco:percentage} standing for the number of cases of a given code in relation to the total number of cases for a particular variable within a data set ($\mathcal{SL}_{2}$).
-
------
-
 {\em Mathematical Operations} (\emph{R-41, R-42}; e.g. date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
-The sum of {\em disco:percentage} (datatype: {\em xsd:double}) values of all codes ({\em skos:Concept}s) of a code list ({\em skos:ConceptScheme} or {\em skos:OrderedCollection}), serving as representation of a particular {\em disco:Variable} must exactly be 100.
+The sum of {\em disco:percentage} (datatype: {\em xsd:double}) values of all codes ({\em skos:Concept}) of a variable code list ({\em skos:ConceptScheme} or {\em skos:OrderedCollection}), e.g., must exactly be 100 ($\mathcal{SL}_{2}$).
 

### 2015-03-03 paper/paper7/paper7.tex
ideas about evaluation

@@
 We distinguish two validation types:
-(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of given data models (sections \ref{aggregated-metadata-and-data}-\ref{person-level-metadata-and-data}).
+(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of given data models (section \ref{content-driven-validation}).
 (2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges (section \ref{technology-driven-validation}).
@@
 Although we provide default severity levels for each constraint, users should be able to specify severity levels of constraints they need to validate for their individual use cases, i.e., users should be able to define use case specific severity levels for constraints.
+In this section, we describe constraints and constraint types which are important to ensure the quality of metadata and data on different levels of aggregation. 
+We classify them according to the type of validation, and associate default severity levels with them.
 
@@
 
-%\subsection{Content-Driven Validation}
+-----
 
-\subsection{Aggregated Metadata and Data}
+use-case specific constraints, e.g., DCAT: searching for metadata
+\tb{Thomas: ToDo}
+
+\subsection{Content-Driven Validation}
+\label{content-driven-validation}
+
+\subsubsection{Aggregated Metadata and Data}
 \label{aggregated-metadata-and-data}
@@
 
-\subsection{Person-Level Metadata and Data}
+\subsubsection{Person-Level Metadata and Data}
 \label{person-level-metadata-and-data}
@@
 In many cases, resources must be members of listed controlled vocabularies (\emph{R-32}).
-\emph{disco:SummaryStatistics}, e.g., can only have \emph{disco:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType} which is a \emph{skos:ConceptScheme}.
-
+Descriptive statistics types like minimum, maximum, and mode are maintained within a controlled vocabulary.  
+Thus, descriptive statistics (\emph{disco:SummaryStatistics}) can only have \emph{disco:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType}, a \emph{skos:ConceptScheme} (\emph{R-91: universal quantification}; $\mathcal{SL}_{2}$):
 \begin{center}
@@
 \textbf{Coverage.}
+In order to express the temporal coverage of series, studies, or data sets dates can be stated.
+
 Depending on property datatypes,
@@
 
-For \emph{Disco} RDF data, we validated XX series, XX studies, XX data sets, XX theoretical concepts, XX variables, XX questions, XX codes, XX category statistics (frequencies), and XX summary statistics (descriptive statistics like minimum).
+We evaluated multiple aggregated and person-level data sets
 
-\begin{itemize}
-	\item validate constraints on complex example data set
-	\item count Disco, QB, PHDD, XKOS, DCAT constraints by constraint groups 
-\end{itemize}
+the most important constraints and constraint types
+
+- Data Cube: XXXXX
+- 3 thesauri: The Thesaurus for the Social Sciences (TheSoz), STW Thesaurus for Economics of the ZBW, and the AGROVOC thesaurus of FAO
+- Disco: 5 series like EU-SILC 
+- PHDD
+- XKOS
+
+in order to ensure high quality of existing large real world data sets
+
+Exported from Missy, we validated \emph{Disco} person-level data containing overall XX resources (5 series, XX studies, XX data sets, XX theoretical concepts, XX variables, XX questions, XX codes, XX category statistics (frequencies), and XX summary statistics).
+
+triple store\footnote{\textcolor{red}{\url{http://multiweb.gesis.org/openrdf-workbench/}}}
+
+The correctness of $\mathcal{C}_{C}$ constraints, i.e., the gold standard has been designed by a SBE domain expert.
 

### 2015-03-06 paper/paper 2/paper 2.tex
formatting

@@
       property & Book & identifier & - & ISBN & $\forall$ & - \\
-      class & ISBN & - & - & xsd:string & regex & '\string^\d{9}[\d|X]\$' \\
+      class & ISBN & - & - & xsd:string & regex & '\string^\text{$\backslash$d$\{9\}$[$\backslash$d$\mid$X]}\$' \\
 		\end{tabular}
@@
 	\label{tab:simple-constraint-not-expressible-in-dl)}
-\end{table} \tb{Erman, can you please format the regular expression in the table above correctly?}
+\end{table} %\tb{Erman, can you please format the regular expression in the table above correctly?}
 The \emph{literal pattern matching} constraint introduces the new \emph{constraining element} \emph{regex}.

### 2015-03-11 paper/paper7/paper7-appendix.tex
evaluation

@@
 	\item \textbf{{\em SKOS-C-LANGUAGE-TAG-CARDINALITY-01\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Omitted or Invalid Language Tags}:}}
+	Omitted or Invalid Language Tags:
 Some controlled vocabularies contain literals in natural language, but without information what language has actually been used.
 Language tags might also not conform to language standards, such as RFC 3066.
-Iteration over all triples in the vocabulary that have a predicate which is a (subclass of) \emph{rdfs:label} or \emph{skos:note}. 
-Severity level: INFO
+\begin{itemize}
+	\item Implementation: Iteration over all triples in the vocabulary that have a predicate which is a (subclass of) \emph{rdfs:label} or \emph{skos:note}. 
+  \item Severity level: WARNING
+\end{itemize}
 
   \item \textbf{{\em SKOS-C-LANGUAGE-TAG-CARDINALITY-02\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Incomplete Language Coverage}:}}
+	Incomplete Language Coverage:
 	Some concepts in a thesaurus are labeled in only one language, some in multiple languages.
@@
 This is not always possible, but incompleteness of language coverage for some concepts can indicate shortcomings of the vocabulary.
-	Severity level: INFO
+	\begin{itemize}
+		\item Severity level: INFO
+	\end{itemize}
 
 	\item \textbf{{\em SKOS-C-LANGUAGE-TAG-CARDINALITY-03\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - No Common Language}:}}
+	No Common Language:
 	Checks if all concepts have at least one common language, i.e. they have assigned at least one literal in the same language. 
-	Severity level: INFO
+	\begin{itemize}
+		\item Severity level: INFO
+	\end{itemize}
 
@@
 	\begin{itemize}
-		\item Implementation: Iteration over all concepts in the vocabulary and returning that don't have associated resources using (subproperties of) \emph{skos:semanticRelation}. 
-		\item Severity level: INFO
+		\item Implementation: Iteration over all concepts in the vocabulary and returning that don't have associated resources using (sub-properties of) \emph{skos:semanticRelation}. 
+		\item Severity level: WARNING
 \end{itemize}
@@
 		\item Implementation: Construction of a graph having all concepts as nodes and the set of edges being \emph{skos:broader} relations. 
-		\item Severity level: INFO
+		\item Severity level: WARNING
 \end{itemize}
@@
 Top concepts are also concepts having no broader concept.
-	  \item Severity level: SHOULD
+	  \item Severity level: WARNING
 \end{itemize}
@@
 	As stated in the SKOS reference document, \emph{skos:broader} and \emph{skos:narrower} are not transitive properties.
-However, they are subproperties of \emph{skos:broaderTransitive} and \emph{skos:narrowerTransitive} which enables inference of a "transitive closure".
-This, in fact, leaves it up to the user to interpret wheter a vocabulary's hierarchical structure is seen as transitive or not.
+However, they are sub-properties of \emph{skos:broaderTransitive} and \emph{skos:narrowerTransitive} which enables inference of a "transitive closure".
+This, in fact, leaves it up to the user to interpret whether a vocabulary's hierarchical structure is seen as transitive or not.
 In the former case, this check can be useful.
 It finds pairs of concepts (A,B) that are directly hierarchically related but there also exits an hierarchical path through a concept C that connects A and B.
-	Severity level: INFO
+	\begin{itemize}
+		\item Severity level: INFO
+	\end{itemize}
 	\item \textbf{{\em SKOS-C-STRUCTURE-10\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Reflexive Relations}:}}
@@
 	\begin{itemize}
-		\item Severity level: INFO
+		\item Severity level: WARNING
 	\end{itemize}
@@
 Intense use of these properties leads to a well-documented thesaurus which should also improve its quality.
+	\begin{itemize}
+	  \item Implementation:
 		Iteration over all concepts in the vocabulary and find those not using one of \emph{skos:note}, \emph{skos:changeNote}, \emph{skos:definition}, \emph{skos:editorialNote}, \emph{skos:example}, \emph{skos:historyNote}, or \emph{skos:scopeNote}.
-	\begin{itemize}
 		\item Severity level: INFO
@@
 	Ambiguous Notation References:
-	Concepts within the same concept scheme should not have identlical \emph{skos:notation} literals. 
+	Concepts within the same concept scheme should not have identical \emph{skos:notation} literals. 
 	\begin{itemize}
@@
 		\item Severity level: FATALERROR
+	\end{itemize}
+\end{itemize}
+
+\subsection{\underline{Linked Data}}
+
+\begin{itemize}
+	\item \textbf{\em R-HTTP-URI-SCHEME-VIOLATION\footnote{Corresponds to qSKOS Quality Issues - Linked Data Specific Issues - HTTP URI Scheme Violation}}: 
+	In the context of Linked Data, we restrict ourselves to using HTTP URIs only and avoid other URI schemes such as URNs and DOIs.
+	\begin{itemize}
+		\item Severity level: ERROR
 	\end{itemize}

### 2015-03-11 paper/paper7/paper7.tex
evaluation

@@
 DL is extended with \emph{key boxes} and a special \emph{keyfor} construct (\ms{identifier \ms{keyfor} Resource}) \cite{Lutz2005}.
+OWL 2 \emph{hasKey} implements \emph{keyfor} and can therefore be used to identify resources uniquely, to merge resources with identical key property values, and to recognize constraint violations.
+%OWL 2 hasKey can be used to identify resources uniquely
+%
+%We used Protégé 5.
+%
+%example: owl:Thing owl:hasKey ( :hasSSN ) . :Peter :hasSSN "123-45-6789" .
+%:Peter_Griffin :hasSSN "123-45-6789" .
+%
+%We use the predefined Reasoner HermiT.
+%
+%:Peter and :Peter_Griffin are derived as identical from the reasoner as they have the same value for :hasSSN.
+%
+%hasKey can be used to merge resources and to recognize constraint violations.
+%
+%Alternative to OWL 2 hasKey: concise bounded description (proposal of Dan)
+%
+%action: explore CBD document solution might be using both approaches
+%
+%benefit: additional identification to URI / IRI benefit: compound properties can be used as key
 
@@
 
-In \emph{Missy}, we provide comprehensive Linked Data services\footnote{\textcolor{red}{\url{http://www.gesis.org/missy/eu/general-information/linked-data/}}} like a \textcolor{red}{triple store} and diverse RDF exports of person-level metadata conforming to the \emph{Disco} vocabulary in multiple concrete syntaxes (e.g.
+In \emph{Missy}, we provide comprehensive Linked Data services\footnote{\textcolor{red}{\url{http://www.gesis.org/missy/eu/general-information/linked-data/}}} like a triple store and diverse RDF exports of person-level metadata conforming to the \emph{Disco} vocabulary in multiple concrete syntaxes (e.g.
 turtle).
@@
 validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages like Shape Expressions\footnote{\url{http://www.w3.org/Submission/shex-primer/}} and the Web Ontology Language \cite{BoschEckert2014-2}.
-The \emph{RDF Validator} also validates RDF data conforming to SPARQL constraints to ensure correct syntax and semantics of vocabularies such as \emph{Disco, Data Cube, PHDD, DCAT, SKOS, and XKOS}.
+The \emph{RDF Validator} also validates RDF data conforming to SPARQL constraints to ensure correct syntax and semantics of vocabularies such as \emph{Disco, Data Cube, PHDD, DCAT, SKOS, and XKOS}\footnote{\textcolor{red}{SPIN mappings: \url{https://github.com/boschthomas/rdf-validation/SPIN}}}.
 The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.
-We define one SPIN construct template for each constraint type (corresponding to a requirement) and vocabulary-specific constraint\footnote{For details about the validation environment see \cite{BoschEckert2014-2}}.
+We define one SPIN construct template for each constraint type (corresponding to a requirement) and vocabulary-specific constraint\footnote{For details about the \emph{RDF Validator} see \cite{BoschEckert2014-2}}.
 A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples indicating the subject, the properties causing constraint violations, and the reason why constraint violations have been raised.
@@
 
-We evaluated multiple aggregated and person-level data sets
+We used $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints 
+to evaluate the metadata and data quality of existing large real world aggregated and person-level data sets.
+We provide a triple store\footnote{\textcolor{red}{\url{http://multiweb.gesis.org/openrdf-workbench/}}}, containing these data sets, 
+and the constraints\footnote{\url{https://github.com/boschthomas/rdf-validation/constraints}} in form of SPARQL CONSTRUCT queries.
+We validated 
+(1) \emph{QB} data sets (\textcolor{red}{XX}),
+(2) \emph{Disco} data sets (overall \textcolor{red}{XX} resources exported from \emph{Missy} - 5 series, \textcolor{red}{XX} studies, \textcolor{red}{XX} data sets, \textcolor{red}{XX} theoretical concepts, \textcolor{red}{XX} variables, \textcolor{red}{XX} questions, \textcolor{red}{XX} codes, \textcolor{red}{XX} category statistics (frequencies), and \textcolor{red}{XX} summary statistics),
+(3) \emph{DCAT} data sets (\textcolor{red}{XX}),
+(4) \emph{PHDD} data sets (\textcolor{red}{XX}),
+(5) \emph{SKOS} data sets (The Thesaurus for the Social Sciences (TheSoz), the STW Thesaurus for Economics of the ZBW, and the AGROVOC thesaurus of FAO), and
+(6) \emph{XKOS} data sets (\textcolor{red}{XX}).
 
-the most important constraints and constraint types
-
-- Data Cube: XXXXX
-- 3 thesauri: The Thesaurus for the Social Sciences (TheSoz), STW Thesaurus for Economics of the ZBW, and the AGROVOC thesaurus of FAO
-- Disco: 5 series like EU-SILC 
-- PHDD
-- XKOS
-
-in order to ensure high quality of existing large real world data sets
-
-Exported from Missy, we validated \emph{Disco} person-level data containing overall XX resources (5 series, XX studies, XX data sets, XX theoretical concepts, XX variables, XX questions, XX codes, XX category statistics (frequencies), and XX summary statistics).
-
-triple store\footnote{\textcolor{red}{\url{http://multiweb.gesis.org/openrdf-workbench/}}}
-
-The correctness of $\mathcal{C}_{C}$ constraints, i.e., the gold standard has been designed by a SBE domain expert.
+The correctness of $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints, i.e., the gold standard has been designed by a SBE domain expert.
+As proof-of-concept, we use the \emph{RDF Validator} to offer examples for both valid and invalid RDF data regarding particular constraints.
 

### 2015-03-12 paper/ISWC 2015 Tutorial/ISWC-2015-tutorial.tex
ISWC 2015 Tutorial

--- 2015-01-09 paper/ESWC 2015 Tutorial/ESWC2015Tutorial.tex
@@
 %
-\author{XXX\inst{1} \and XXX\inst{1} \and Joachim Wackerow\inst{1}}
+\author{Benjamin Zapilko\inst{1} \and Thomas Bosch\inst{1} \and Joachim Wackerow\inst{1}}
 %
@@
 \institute{GESIS – Leibniz Institute for the Social Sciences, Germany\\
-\email{\{thomas.bosch,benjamin.zapilko,joachim.wackerow\}}@gesis.org}
+\email{firstname.lastname}@gesis.org}
 
@@
 %Proposals should not exceed 5 pages using a reasonable font size (not less than 11 pts). They should include the call for participation together with the following details:
-%- Abstract: 200 words maximum, for inclusion to the ESWC 2015 Web site.
-%- Tutorial description: objectives of the tutorial and relevance to ESWC 2015; information about the scope and level of detail of the material to be covered; intended audiences; learning objectives; practical sessions.
+%- Abstract: 200 words maximum, for inclusion to the ISWC 2015 Web site.
+%- Tutorial description: objectives of the tutorial and relevance to ISWC 2015; information about the scope and level of detail of the material to be covered; intended audiences; learning objectives; practical sessions.
 %- Tutorial length: Half or full day, including preferences.
-%- Previous versions or related tutorials: other venues of this or similar tutorials (potentially by a different team of tutors), motivation for offering the tutorial again, at the ESWC2015.
+%- Previous versions or related tutorials: other venues of this or similar tutorials (potentially by a different team of tutors), motivation for offering the tutorial again, at the ISWC2015.
 %- Tutoring team: short bios of the presenters, including previous training and public speaking experience (e.g., teaching in English, conference presentations, tutorials etc.)
 
-\section{Call for Participation}
+\section{Motivation}
 The DDI-RDF Discovery Vocabulary (Disco) \cite{Bosch2012} is an RDF Schema vocabulary which can be utilized to represent person-level data sets and related metadata as Linked Data. 
@@
 Participants are encouraged to present their own data sets and use cases where Disco has been applied or will be used. 
+This tutorial addresses Linked Data developers (beginners and experts) who want to publish Linked Data sets based on complex data like person-level data where essential information like provenance, data aggregates and data catalogs is necessary.
 
-This tutorial addresses Linked Data developers (beginners and experts) who want to publish Linked Data sets based on complex data like person-level data where essential information like provenance, data aggregates and data catalogs is necessary.
+\textbf{Relevance to ISWC 2015.}
+%In this tutorial, the DDI-RDF Discovery vocabulary (Disco) and its interplay with other existing vocabularies is introduced.
+In contrast to other newly developed vocabularies that can be adopted easily in most cases, the complexity of Disco is higher because of its domain-specific origin and the tight interplay with other existing vocabularies.
+This makes Disco more difficult to be adopted by developers who may not be familiar with the domain-specific background of person-level or similar data.
+However, since the number of organizations that aim to publish their data as Linked Data grows and the number of Linked Data researchers that want to use real-world data grows, a tutorial on representing such inter-connected data sets may be a beneficial addition for the audience of ISWC 2015.
+
+\textbf{Previous Versions or Related Tutorials.}
+Thomas Bosch and Benjamin Zapilko held a half-day tutorial at the EDDI14 – 6th Annual European DDI User Conference in London\footnote{\url{http://www.eddi-conferences.eu/ocs/index.php/eddi/eddi14/schedConf/program}}.
+The tutorial was well received and the presenters got overall positive feedback.
+Since the audience of Disco is two-fold - data professionals and the DDI community at the one hand and Linked Data experts at the other hand - the idea was to offer this tutorial at the ISWC conference as well in order to address the the Linked Data community.
+%At the EDDI conference, the first part of the audience - data professionals and the DDI community - was addressed.
+%At the ISWC conference, the second part of our audience - Linked Data experts - will be addressed.
 
@@
 
-\subsection{Objectives of the Tutorial} 
+\subsection{Objectives of the Tutorial and Learning Objectives.} 
 The main objective of this tutorial is to introduce Disco and to provide assistence for creating Linked Data sets using Disco.
@@
 Vice verse, we show how these other vocabualries and data represented with such can benefit from the interplay with Disco.
-
 Another objective of the tutorial is to share our experience in developing a RDF vocabulary out of an existing and complex domain-specific data model like DDI.
@@
 Finally, since Disco is already being adopted in the DDI community, we aim to increase the use of Disco in the Linked Data community.
+The learning objectives of this tutorial are the following: (1) introducing Disco, PHDD, and XKOS for modeling complex person-level data, (2) representing the interplay of Disco data with existing and established vocabularies like RDF Data Cube, DCAT, and PROV-O, and (3) the validation of Disco.
 
-\subsection{Relevance to ESWC 2015}
-%In this tutorial, the DDI-RDF Discovery vocabulary (Disco) and its interplay with other existing vocabularies is introduced.
-In contrast to other newly developed vocabularies that can be adopted easily in most cases, the complexity of Disco is higher because of its domain-specific origin and the tight interplay with other existing vocabularies.
-This makes Disco more difficult to be adopted by developers who may not be familiar with the domain-specific background of person-level or similar data.
-However, since the number of organizations that aim to publish their data as Linked Data grows and the number of Linked Data researchers that want to use real-world data grows, a tutorial on representing such inter-connected data sets may be a beneficial addition for the audience of ESWC 2015.
-
-\subsection{Scope and Level of Detail of the Material}
-
+\subsection{Tutorial Format and Presentation Style.}
 %During the tutorial, we will build one real world data set which serves as ongoing running example. 
@@
 Material for the practical exercises will be provided by the presenters (see Section 2.6).
-
-\subsection{Intended Audiences}
-The intended audience of this tutorial are Linked Data developers - beginners as well as experts - who are interested in modelling and publishing complex and highly inter-connected data sets as Linked Data.
-Since the connection with other vocabulaires like RDF Data Cube, DCAT and PROV-O plays a major role in this context, the tutorial is not restricted to participants who are interested in person-level or similar data.
-
-\subsection{Learning Objectives}
-The learning objectives of this tutorial are the following: (1) introducing Disco, PHDD, and XKOS for modelling complex person-level data, (2) representing the interplay of Disco data with existing and established vocabularies like RDF Data Cube, DCAT, and PROV-O, and (3) the validation of Disco.
-
-\subsection{Practical Sessions}
 During the tutorial, one complex data set will be built, which serves as ongoing running example.
@@
 
-\section{Tutorial Length}
+\section{\textcolor{red}{Tutorial Length}}
 
@@
 
-\section{Previous Versions or Related Tutorials}
-
-Thomas Bosch and Benjamin Zapilko held a half-day tutorial at the EDDI14 – 6th Annual European DDI User Conference in London\footnote{\url{http://www.eddi-conferences.eu/ocs/index.php/eddi/eddi14/schedConf/program}}.
-The tutorial was well received and the presenters got overall positive feedback.
-Since the audience of Disco is two-fold - data professionals and the DDI community at the one hand and Linked Data experts at the other hand - the idea was to offer this tutorial at the ESWC conference as well in order to address the the Linked Data community.
-%At the EDDI conference, the first part of the audience - data professionals and the DDI community - was addressed.
-%At the ESWC conference, the second part of our audience - Linked Data experts - will be addressed.
+\section{Intended Audiences}
+The intended audience of this tutorial are Linked Data developers - beginners as well as experts - who are interested in modeling and publishing complex and highly inter-connected data sets as Linked Data.
+Since the connection with other vocabularies like RDF Data Cube, DCAT and PROV-O plays a major role in this context, the tutorial is not restricted to participants who are interested in person-level or similar data.
 
@@
 
-Thomas Bosch\footnote{\url{http://boschthomas.blogspot.com}} studied information systems, holds a degree in Computer Science (M.Sc.), and is currently a PhD student.
+\textbf{Thomas Bosch} studied information systems, holds a degree in Computer Science (M.Sc.), and is currently a PhD student.
 His research topic is all about RDF validation.
@@
 
-Benjamin Zapilko holds a degree in Computer Science and has recently finished his PhD thesis about methods for matching social science relevant Linked Data.
+\begin{itemize}
+  \item affiliation: Gesis - Leibniz Institute for the Social Sciences
+  \item email address: thomas.bosch@gesis.org
+	\item homepage: \url{http://boschthomas.blogspot.com/}; \url{www.gesis.org}
+\end{itemize}
+
+\textbf{Benjamin Zapilko} holds a degree in Computer Science and has recently finished his PhD thesis about methods for matching social science relevant Linked Data.
 The defense talk will be at the end of January.
@@
 
-Joachim Wackerow holds a degree in sociology. 
+\begin{itemize}
+  \item affiliation: Gesis - Leibniz Institute for the Social Sciences
+  \item email address: benjamin.zapilko@gesis.org
+	\item homepage: \url{www.gesis.org}
+	\item primary contact person
+\end{itemize}
+
+\textbf{Joachim Wackerow} holds a degree in sociology. 
 He is the vice chair of the DDI Alliance Technical Committee whose charge is to create, maintain, and enhance the DDI specification.
@@
 He organizes the annual European DDI user conferences and holds DDI introduction workshops.
+
+\begin{itemize}
+  \item affiliation: Gesis - Leibniz Institute for the Social Sciences
+  \item email address: joachim.wackerow@gesis.org
+	\item homepage: \url{www.gesis.org}
+\end{itemize}
 

### 2015-03-12 paper/paper7/paper7-evaluation.tex
evaluation

--- 2015-03-02 paper/paper7/paper7-appendix.tex
@@
 %
-\title{RDF Constraint Types to Validate Metadata \\ on Highly-Complex Person-Level and Aggregated Data}
+\title{An Evaluation of RDF Constraint Types to Validate Metadata on Person-Level and Aggregated Data}
 \subtitle{}
@@
 
-Bosch and Eckert initiated a comprehensive database\footnote{Publicly available at \url{http://purl.org/net/rdf-validation}.} on RDF validation requirements to collect case studies, use cases, and requirements \cite{BoschEckert2014}.
-It is continuously updated and used to evaluate and to compare various existing solutions for RDF constraint formulation and validation. 
-Requirements are classified to provide a high-level view on different solutions and to facilitate a better understanding of the problem domain.
-Bosch et al. identified in total 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
-They recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which they explain each requirement (constraint type) in detail and give examples for each (represented by listed constraint languages) \cite{BoschNolleAcarEckert2015}.
-We state at least one Disco constraint for the majority of the constraint types.
-Where appropriate constraint types are related to complementary requirements of the RDF validation requirements database.
-When constraint types are mapped to DL, we do not state namespace prefixes for simplicity reasons.
-
-\section{Validation Types}
-
-\textbf{Content-Driven Validation / Data Model Consistency}.
-Is the data consistent with the intended semantics of the data model?
-Such validation rules ensure the integrity of the data according to the data model.
-
-\textbf{Technology-Driven Validation}.
-Some validation rules can be generated automatically out of the defined data model, such as cardinality restrictions, universal quantifications, domains, ranges.
-
-\section{Validation of Metadata on Person-Level and Aggregated Data}
+\section{Data Cube}
 
 \begin{itemize}
-  \item Constraint types marked with an asterisk (*) can be used as OWL 2 axioms.
-Thus, reasoners may be used to infer implicit triples resolving constraint violations caused when these constraints are validated.
-	\item \underline{Underlined subsections} are data model specific constraint types and do not correspond to RDF validation requirements (constraint types).
-%	\item \underline{Underlined constraints} are part of content-driven validation.
-%	\item \udash{Dashed underlined constraints} are part of technology-driven validation.
+	\item \url{http://270a.info/} (see the VoID which points to other
+VoIDs) is full of data sets (probably close to 10k) using RDF Data Cube,
+and some of those also include XKOS.
 \end{itemize}
-
-\subsection{\underline{Comparison}}
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-01}}: 
-	are compared variables represented in a compatible way, i.e. are the variables' code lists theoretically comparable?
-		\begin{itemize}
-		\item severity level: WARNING
-	\end{itemize}
-	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-02}}: 
-	are variable definitions (\emph{dcterms:description}) available for each variable (\emph{disco:Variable}) to compare?
-		\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-03}}:
-	are code lists structured properly for each variable (\emph{disco:Variable}) to compare?
-		\begin{itemize}
-		\item severity level: WARNING
-	\end{itemize}
-	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-04}}:
-	is for each code (for each variable (\emph{disco:Variable}) to compare) an associated category (a human-readable label) specified?
-		\begin{itemize}
-		\item severity level: INFO
-	\end{itemize}
-	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-05}}:
-	each (\emph{disco:Variable}) to compare must be present.
-	\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\subsection{\underline{Data Model Consistency}}
-Is the data consistent with the intended semantics of the data model?
-Such validation rules ensure the integrity of the data according to the data model.
-
-\begin{itemize}
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-01:}}
-	Only attributes may be optional (\emph{IC-6} \cite{CyganiakReynolds2014}) - 
-	The only components of a \emph{qb:DataStructureDefinition} that may be marked as optional, using \emph{qb:componentRequired} are attributes. 
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-02:}}
-	No duplicate observations (\emph{IC-12} \cite{CyganiakReynolds2014}) - 
-	No two \emph{qb:Observations} in the same \emph{qb:DataSet} may have the same value for all dimensions. 
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-03:}}
-	Slice Keys consistent with DSD (\emph{IC-8} \cite{CyganiakReynolds2014}) -
-	Every \emph{qb:componentProperty} on a \emph{qb:SliceKey} must also be declared as a \emph{qb:component} of the associated \emph{qb:DataStructureDefinition}. 
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-04:}}
-	Required attributes (\emph{IC-13} \cite{CyganiakReynolds2014}) -
-	Every \emph{qb:Observation} has a value for each declared attribute that is marked as required. 
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05:}}
-	All measures present (\emph{IC-14} \cite{CyganiakReynolds2014}) -
-	In a \emph{qb:DataSet} which does not use a Measure dimension then each individual \emph{qb:Observation} must have a value for every declared measure. 
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-06:}}
-	Measure dimension consistent (\emph{IC-15} \cite{CyganiakReynolds2014}) -
-	In a \emph{qb:DataSet} which uses a Measure dimension then each qb:Observation must have a value for the measure corresponding to its given \emph{qb:measureType}. 
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-07:}}
-	Single measure on measure dimension observation (\emph{IC-16} \cite{CyganiakReynolds2014}) -
-	In a \emph{qb:DataSet} which uses a Measure dimension then each \emph{qb:Observation} must only have a value for one measure (by \emph{IC-15} this will be the measure corresponding to its \emph{qb:measureType}).
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-08:}}
-	All measures present in measures dimension cube (\emph{IC-17} \cite{CyganiakReynolds2014}) -
-	In a \emph{qb:DataSet} which uses a Measure dimension then if there is a Observation for some combination of non-measure dimensions then there must be other Observations with the same non-measure dimension values for each of the declared measures.
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-09:}}
-	Consistent data set links (\emph{IC-18} \cite{CyganiakReynolds2014}) -
-	If a \emph{qb:DataSet} \emph{D} has a \emph{qb:slice} \emph{S}, and \emph{S} has an \emph{qb:observation} \emph{O}, then the \emph{qb:dataSet} corresponding to \emph{O} must be \emph{D}. 
-\end{itemize}
-
-\begin{itemize}
-
-	\item \textbf{{\em SKOS-C-DATA-MODEL-CONSISTENCY-01\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Relation Clashes}:}}
-	Relation Clashes:
-  Covers condition S27 from the SKOS reference document, that has not been defined formally. 
-	\begin{itemize}
-	  \item Implementation:
-		In a first step, all pairs of concepts are found that are associatively connected, using a SPARQL query.
-In the second step, a graph is created, containing only hierarchically related concepts and the respective relations.
-For each concept pair from the first step, we check for a path in the graph from step two.
-If such a path is found, a clash has been identified and the causing concepts are returned.
-		\item Severity level: 
-	\end{itemize}
-
-	\item \textbf{{\em SKOS-C-DATA-MODEL-CONSISTENCY-02\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Mapping Clashes}:}}
-	Mapping Clashes:
-  Covers condition S46 from the SKOS reference document, that has not been defined formally. 
-	\begin{itemize}
-	  \item Implementation:
-		Can be solved by issuing a SPARQL query. 
-		\item Severity level: 
-	\end{itemize}
-
-	\item \textbf{{\em SKOS-C-DATA-MODEL-CONSISTENCY-03\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Mapping Relations Misuse}:}}
-	Mapping Relations Misuse:
-  According to the SKOS reference documentation, mapping relations (e.g., \emph{skos:broadMatch} or \emph{skos:relatedMatch}) should be asserted to concepts being members of different concept schemes.
-This check finds concepts that are related by a mapping property and are either members of the same concept scheme or members of no concept scheme at all.
-	\begin{itemize}
-		\item Severity level: 
-	\end{itemize}
-
-\end{itemize}
-
-\subsection{Subsumption*}
-
-A \emph{subclass axiom}\footnote{{\em R-100-SUBSUMPTION}} ({\em concept inclusion} in DL) states that the class \emph{C1} is a subclass of the class \emph{C2} - \emph{C1} is more specific than \emph{C2},
-i.e. each resource of the class \emph{C1} must also be part of the class extension of \emph{C2}.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-SUBSUMPTION-01:}} 
-All {\em disco:Universe}s must also be {\em skos:Concept}s (\ms{Universe $\sqsubseteq$ Concept}).
-\end{itemize}
-
-\subsection{Class Equivalence*}
-
-{\em Class Equivalence}\footnote{{\em R-3-EQUIVALENT-CLASSES}} asserts that two concepts have the same instances.
-While synonyms are an obvious example of equivalent concepts, in practice one more
-often uses concept equivalence to give a name to complex expressions \cite{Kroetzsch2012}.
-Concept equivalence is indeed subsumption from left and right ($A \sqsubseteq B$ and $B \sqsubseteq A$ implies $A \equiv B$).
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-CLASS-EQUIVALENCE-01:}}
-All {\em sio:SIO\_000367} resources must also be {\em disco:Variable}s (\ms{Variable $\equiv$ SIO\_000367}).
-The Semanticscience Integrated Ontology (SIO)\footnote{https://code.google.com/p/semanticscience/wiki/SIO} provides a simple, integrated ontology of types and relations for rich description of objects, processes and their attributes.
-{\em sio:SIO\_000367} is a variable defined as a value that may change within the scope of a given problem or set of operations.
-Thus, {\em sio:SIO\_000367} is equivalent to {\em disco:Variable}.
-\end{itemize}
-
-\subsection{Sub Properties*}
-
-{\em Sub Properties}\footnote{\emph{R-54-SUB-OBJECT-PROPERTIES}, \emph{R-64-SUB-DATA-PROPERTIES}} state that the property \emph{P1} is a sub property of the property \emph{P2} - that is, if an individual \emph{x} is connected by \emph{P1} to an individual or a literal \emph{y}, then \emph{x} is also connected by \emph{P2} to \emph{y}.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-SUB-PROPERTIES-01:}}
-If an individual \emph{x} is connected by {\em disco:fundedBy} to an individual \emph{y}, then \emph{x} is also connected by {\em dcterms:contributor} to \emph{y} (\ms{fundedBy $\sqsubseteq$ contributor}).
-\end{itemize}
-
-\subsection{Property Domains*}
-
-{\em Property Domains}\footnote{{\em R-25-OBJECT-PROPERTY-DOMAIN}, {\em R-26-DATA-PROPERTY-DOMAIN}} ({\em domain restrictions on roles} in DL) restrict the domain of object and data properties.
-The purpose is to declare that a given property is associated with a class. 
-In OO terms this is the declaration of a member, field, attribute or association. 
-$\exists R. \top \sqsubseteq C$ is the object property restriction where $R$ is the object property (role) whose domain is restricted to concept $C$.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-PROPERTY-DOMAIN-01:}} 
-	{\em Property Domain} constraints are defined for each \emph{Disco} object and data property.
-  Only {\em disco:Question}s, e.g., can have {\em disco:responseDomain} relationships (\ms{$\exists$ responseDomain.$\top$ $\sqsubseteq$ Question}).
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DATA-CUBE-C-PROPERTY-DOMAIN-01:}} 
-	{\em Property Domain} constraints are defined for each \emph{Data Cube} object and data property.
-  Only {\em qb:Observation}s, e.g., can have {\em qb:dataSet} relationships (\ms{$\exists$ dataSet.$\top$ $\sqsubseteq$ Observation}).
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DCAT-C-PROPERTY-DOMAIN-01:}} 
-	{\em Property Domain} constraints are defined for each \emph{DCAT} object and data property.
-  Only {\em dcat:Catalog}s, e.g., can have {\em dcat:dataset} relationships (\ms{$\exists$ dataset.$\top$ $\sqsubseteq$ Catalog}).
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em PHDD-C-PROPERTY-DOMAIN-01:}} 
-	{\em Property Domain} constraints are defined for each \emph{PHDD} object and data property.
-  Only {\em phdd:Table}s, e.g., can have {\em phdd:isStructuredBy} relationships (\ms{$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table}).
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em SKOS-C-PROPERTY-DOMAIN-01:}} 
-	{\em Property Domain} constraints are defined for each \emph{SKOS} object and data property.
-	Only {\em skos:ConceptSchemes}, e.g., can have {\em skos:hasTopConcept} relationships (\ms{$\exists$ hasTopConcept.$\top$ $\sqsubseteq$ ConceptScheme}).
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em XKOS-C-PROPERTY-DOMAIN-01:}} 
-	{\em Property Domain} constraints are defined for each \emph{XKOS} object and data property.
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\subsection{Property Ranges*}
-
-{\em Property Ranges}\footnote{{\em R-28-OBJECT-PROPERTY-RANGE}, {\em R-35-DATA-PROPERTY-RANGE}} ({\em range restrictions on roles} in DL) restrict the range of object and data properties.
-$\top \sqsubseteq \forall R . C$ is the range restriction to the object property $R$ (restricted by the concept $C$).
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-PROPERTY-RANGES-01:}} 
-	{\em Property Range} constraints are defined for each \emph{Disco} object and data property.
-  {\em disco:caseQuantity} relationships, e.g., can only point to literals of the datatype {\em xsd:nonNegativeInteger} (\ms{$\top$ $\sqsubseteq$ $\forall$ caseQuantity.nonNegativeInteger}).
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DATA-CUBE-C-PROPERTY-RANGES-01:}} 
-	{\em Property Range} constraints are defined for each \emph{Data Cube} object and data property.
-  {\em qb:order} relationships, e.g., can only point to literals of the datatype {\em xsd:string} (\ms{$\top$ $\sqsubseteq$ $\forall$ order.string}).
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DCAT-C-PROPERTY-RANGES-01:}} 
-	{\em Property Range} constraints are defined for each \emph{DCAT} object and data property.
-  {\em dcat:bytes} relationships, e.g., can only point to literals of the datatype {\em xsd:integer} (\ms{$\top$ $\sqsubseteq$ $\forall$ bytes.integer}).
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em PHDD-C-PROPERTY-RANGES-01:}} 
-	{\em Property Range} constraints are defined for each \emph{PHDD} object and data property.
-  {\em phdd:caseQuantity} relationships, e.g., can only point to literals of the datatype {\em xsd:nonNegativeInteger} (\ms{$\top$ $\sqsubseteq$ $\forall$ caseQuantity.nonNegativeInteger}).
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em SKOS-C-PROPERTY-RANGES-01:}} 
-	{\em Property Range} constraints are defined for each \emph{SKOS} object and data property.
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em XKOS-C-PROPERTY-RANGES-01:}} 
-	{\em Property Range} constraints are defined for each \emph{XKOS} object and data property.
-  {\em xkos:belongsTo} relationships, e.g., can only point to instances of the class {\em skos:Concept} (\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}).
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\subsection{Inverse Object Properties*}
-
-In many cases, properties are used bi-directionally and then accessed in the inverse direction, e.g.
-parent $\equiv$ child$^{-}$.
-There should be a way to declare value type, cardinality etc of those inverse relations without having to declare a new property URI.
-The object property \emph{OP1} is an inverse\footnote{\emph{R-56-INVERSE-OBJECT-PROPERTIES}} of the object property \emph{OP2}. 
-Thus, if an individual \emph{x} is connected by \emph{OP1} to an individual \emph{y}, then \emph{y} is also connected by \emph{OP2} to \emph{x}, and vice versa.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-INVERSE-OBJECT-PROPERTIES-01}}:
-	\emph{disco:CategoryStatistics} resources are accessed from codes (\emph{skos:Concept}s) via \emph{disco:statisticsCategory}$^{-}$.
-	\item \textbf{{\em DISCO-C-INVERSE-OBJECT-PROPERTIES-02}}:
-	\emph{disco:SummaryStatistics} resources are accessed from \emph{disco:Variable}s via \emph{disco:statisticsVariable}$^{-}$.
-	\item \textbf{{\em DISCO-C-INVERSE-OBJECT-PROPERTIES-03}}:
-	\emph{disco:Variable}s are accessed from \emph{disco:Question}s via \emph{disco:question}$^{-}$.
-\end{itemize}
-
-\subsection{Symmetric Object Properties*}
-
-A role is symmetric if it is equivalent to its own inverse \cite{Kroetzsch2012}.
-An object property symmetry axiom\footnote{\emph{R-61-SYMMETRIC-OBJECT-PROPERTIES}} states that the object property expression \emph{OPE} is symmetric - that is, if an individual \emph{x} is connected by \emph{OPE} to an individual \emph{y}, then \emph{y} is also connected by \emph{OPE} to \emph{x}.
-
-\subsection{Asymmetric Object Properties*}
-
-A property is asymmetric\footnote{{\em R-62-ASYMMETRIC-OBJECT-PROPERTIES}} if it is disjoint from its own inverse \cite{Kroetzsch2012}.
-An object property asymmetry axiom states that the object property \emph{OP} is asymmetric - that is, if an individual \emph{x} is connected by \emph{OP} to an individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-ASYMMETRIC-OBJECT-PROPERTIES-01:}} 
-A {\em disco:Variable} may be based on a {\em disco:RepresentedVariable}.
-A {\em disco:RepresentedVariable}, however, cannot be based on a {\em disco:Variable}.
-This is a kind of mistake which may occur as a semantically equivalent object property for the other direction may also be possible ({\em disco:basisOf}) (\ms{$basedOn \sqcap basedOn^{-} \sqsubseteq \bot$}).
-\end{itemize}
-
-\subsection{Reflexive Object Properties*}
-
-\emph{Reflexive Object Properties}\footnote{\emph{R-59-REFLEXIVE-OBJECT-PROPERTIES}} (\emph{reflexive roles}, \emph{global reflexivity} in DL) can be expressed by imposing local reflexivity on the top concept \cite{Kroetzsch2012}.
-
-\subsection{Irreflexive Object Properties*}
-
-An object property is irreflexive\footnote{\emph{R-60-IRREFLEXIVE-OBJECT-PROPERTIES}} (\emph{irreflexive role} in DL) if it is never locally reflexive \cite{Kroetzsch2012}.
-An object property irreflexivity axiom \emph{IrreflexiveObjectProperty( OPE )} states that the object property expression \emph{OPE} is irreflexive - that is, no individual is connected by \emph{OPE} to itself.
-
-\begin{itemize}
-  \item \textbf{{\em DISCO-C-IRREFLEXIVE-OBJECT-PROPERTIES-01:}}
-	In \emph{Disco}, every object property is irreflexive.
-  No individual is connected by the object property {\em instrument} to itself (\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists  instrument . Self$}).
-\end{itemize}
-
-\subsection{Class-Specific Irreflexive Object Properties*}
-
-A property is \emph{irreflexive} if it is never locally reflexive \cite{Kroetzsch2012}.
-An object property irreflexivity axiom states that the object property \emph{OP} is irreflexive - that is, no individual is connected by \emph{OP} to itself.
-\emph{Class-Specific Irreflexive Object Properties} are object properties which are irreflexive within a given context, e.g. a class.
-
-\begin{itemize}
-  \item \textbf{{\em DISCO-C-CLASS-SPECIFIC-IRREFLEXIVE-OBJECT-PROPERTIES-01:}}
-Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:boader} to themselves (\ms{Concept $\sqsubseteq$ $\neg$$\exists$ broader.Self.}). 
-	\item \textbf{{\em DISCO-C-CLASS-SPECIFIC-IRREFLEXIVE-OBJECT-PROPERTIES-02:}}
-Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:narrower} to themselves (\ms{Concept $\sqsubseteq$ $\neg$$\exists$ narrower.Self.}). 
-\end{itemize}
-
-\subsection{Disjoint Properties}
-
-A \emph{disjoint properties axiom}\footnote{\emph{R-9-DISJOINT-PROPERTIES}} states that all of the properties are pairwise disjoint; 
-that is, no individual \emph{x} can be connected to an individual/literal \emph{y} by these properties.
-
-\begin{itemize}
-	\item \textbf{{\em DATA-CUBE-C-DISJOINT-PROPERTIES-01:}} 
-	All \emph{Data Cube} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
-  The properties \emph{qb:dataSet} and \emph{qb:structure} are disjoint ($dataSet \sqsubseteq \neg structure$).
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DCAT-C-DISJOINT-PROPERTIES-01:}} 
-	All \emph{DCAT} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-DISJOINT-PROPERTIES-01:}} 
-	All \emph{Disco} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
-  The properties \emph{disco:variable} and \emph{disco:question} are disjoint ($variable \sqsubseteq \neg question$).
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em PHDD-C-DISJOINT-PROPERTIES-01:}} 
-	All \emph{PHDD} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
-	The properties \emph{phdd:isStructuredBy} and \emph{phdd:column} are disjoint ($isStructuredBy \sqsubseteq \neg column$)
-\end{itemize}
-
-\begin{itemize}
-
-	\item \textbf{{\em SKOS-C-DISJOINT-PROPERTIES-01:}} 
-	All \emph{SKOS} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
-
-	\item \textbf{{\em SKOS-C-DISJOINT-PROPERTIES-02\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Disjoint Labels Violation}:}}
-	Disjoint Labels Violation:
-  Covers condition S13 from the SKOS reference document stating that "\emph{skos:prefLabel}, \emph{skos:altLabel} and \emph{skos:hiddenLabel} are pairwise disjoint properties". 
-	\begin{itemize}
-	  \item Implementation:
-		A SPARQL query collects all labels of all concepts, building an in-memory structure. This structure is then checked for disjoint entries. 
-		\item Severity level: 
-	\end{itemize}
-
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em XKOS-C-DISJOINT-PROPERTIES-01:}} 
-	All \emph{XKOS} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
-\end{itemize}
-
-\subsection{Disjoint Classes}
-
-{\em Disjoint Classes}\footnote{{\em R-7-DISJOINT-CLASSES}} state that all of the classes are pairwise disjoint; 
-that is, no individual can be at the same time an instance of these disjoint classes.
-
-\begin{itemize}
-	\item \textbf{{\em DATA-CUBE-C-DISJOINT-CLASSES-01:}} 
-All \emph{Data Cube} classes are defined to be pairwise disjoint.
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DCAT-C-DISJOINT-CLASSES-01:}} 
-All \emph{DCAT} classes are defined to be pairwise disjoint.
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-DISJOINT-CLASSES-01:}} 
-All \emph{Disco} classes are defined to be pairwise disjoint (e.g. \ms{Study $\sqcap$ Variable $\sqsubseteq$ $\perp$}).
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em PHDD-C-DISJOINT-CLASSES-01:}} 
-All \emph{PHDD} classes are defined to be pairwise disjoint.
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em SKOS-C-DISJOINT-CLASSES-01:}} 
-All \emph{SKOS} classes are defined to be pairwise disjoint.
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em XKOS-C-DISJOINT-CLASSES-01:}} 
-All \emph{XKOS} classes are defined to be pairwise disjoint.
-\end{itemize}
-
-\subsection{Context-Specific Property Groups}
-
-The \emph{Context-Specific Property Groups}\footnote{\emph{R-66-PROPERTY-GROUPS}} constraint groups data and object properties within a context (e.g. a class).
-
-\subsection{Context-Specific Inclusive OR of Properties}
-
-\emph{Inclusive or} is a logical connective joining two or more predicates that yields the logical value "true" when at least one of the predicates is true.
-\emph{Context-Specific Inclusive OR of Properties}\footnote{\emph{R-202-CONTEXT-SPECIFIC-INCLUSIVE-OR-OF-PROPERTIES}} constraints specify that individuals are valid if they have at least one property relationship of one or multiple properties stated within a given context.
-The context can be an application profile, a shape, or a class, i.e., the constraint applies for individuals of this specific class.
-
-\subsection{Context-Specific Inclusive OR of Property Groups}
-
-At least one property group must match for individuals of a specific context. 
-Context may be a class, a shape, or an application profile.
-
-\subsection{Recursive Queries}
-
-Resource Shapes is a recursive language\footnote{\emph{R-222-RECURSIVE-QUERIES}} (the value shape of a Resource Shape is in turn another Resource Shape). 
-There is no way to express that in SPARQL without hand-waving "and then you call the function again here" or "and then you embed this operation here" text.  
-The embedding trick doesn't work
-in the general case because SPARQL can't express recursive queries,
-e.g. "test that this Issue is valid and all of the Issues that references, recursively".
-Most SPARQL engines already have
-functions that go beyond the official SPARQL 1.1 spec. 
-The cost of that sounds manageable.
-
-\subsection{Individual Inequality}
-
-An \emph{individual inequality axiom}\footnote{\emph{R-14-DISJOINT-INDIVIDUALS}} DifferentIndividuals( a$_1$ ...
-a$_n$ ) states that all of the individuals a$_i$, 1 $\leq$ i $\leq$ n, are different from each other;
-that is, no individuals a$_i$ and a$_j$ with i $\neq$ j can be derived to be equal. 
-This axiom can be used to axiomatize the unique name assumption — the assumption that all different individual names denote different individuals.
-
-\subsection{Equivalent Properties*}
-
-An \emph{equivalent object properties axiom}\footnote{\emph{R-4-EQUIVALENT-OBJECT-PROPERTIES}} \emph{EquivalentObjectProperties( OPE$_1$ ...
-OPE$_n$ )} states that all of the object property expressions \emph{OPE$_i$, 1 $\leq$ i $\leq$ n}, are semantically equivalent to each other.
-This axiom allows one to use each \emph{OPE$_i$} as a synonym for each \emph{OPE$_j$} — that is, in any expression in the ontology containing such an axiom, \emph{OPE$_i$} can be replaced with \emph{OPE$_j$} without affecting the meaning of the ontology.
-The axiom \emph{EquivalentObjectProperties( OPE$_1$ OPE$_2$ )} is equivalent to the following two axioms \emph{SubObjectPropertyOf( OPE$_1$ OPE$_2$ )} and \emph{SubObjectPropertyOf( OPE$_1$ OPE$_2$ )}.
-
-An \emph{equivalent data properties axiom}\footnote{\emph{R-5-EQUIVALENT-DATA-PROPERTIES}} \emph{EquivalentDataProperties( DPE$_1$ ...
-DPE$_n$ )} states that all the data property expressions \emph{DPE$_i$, 1 $\leq$ i $\leq$ n}, are semantically equivalent to each other.
-This axiom allows one to use each \emph{DPE$_i$} as a synonym for each \emph{DPE$_j$} — that is, in any expression in the ontology containing such an axiom, DPE$_i$ can be replaced with \emph{DPE$_j$} without affecting the meaning of the ontology.
-The axiom \emph{EquivalentDataProperties( DPE$_1$ DPE$_2$ )} can be seen as a syntactic shortcut for the following axiom \emph{SubDataPropertyOf( DPE$_1$ DPE$_2$ )} and \emph{SubDataPropertyOf( DPE$_1$ DPE$_2$ )}.
-
-\begin{itemize}
-	\item \textbf{{\em DATA-CUBE-C-EQUIVALENT-PROPERTIES-01:}}
-	Equivalent properties from different versions of \emph{Data Cube} can be marked as equivalent. 
-	As a consequence, the properties can be replaced by each other without affecting the meaning.
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DCAT-C-EQUIVALENT-PROPERTIES-01:}}
-	Equivalent properties from different versions of \emph{DCAT} can be marked as equivalent. 
-	As a consequence, the properties can be replaced by each other without affecting the meaning.
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-EQUIVALENT-PROPERTIES-01:}}
-	Equivalent properties from different versions of \emph{Disco} can be marked as equivalent, e.g. \emph{disco:containsVariable} and \emph{disco:variable}. 
-	As a consequence, the properties can be replaced by each other without affecting the meaning.
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em PHDD-C-EQUIVALENT-PROPERTIES-01:}}
-	Equivalent properties from different versions of \emph{PHDD} can be marked as equivalent. 
-	As a consequence, the properties can be replaced by each other without affecting the meaning.
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em SKOS-C-EQUIVALENT-PROPERTIES-01:}}
-	Equivalent properties from different versions of \emph{SKOS} can be marked as equivalent. 
-	As a consequence, the properties can be replaced by each other without affecting the meaning.
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em XKOS-C-EQUIVALENT-PROPERTIES-01:}}
-	Equivalent properties from different versions of \emph{XKOS} can be marked as equivalent. 
-	As a consequence, the properties can be replaced by each other without affecting the meaning.
-\end{itemize}
-
-\subsection{Property Assertions}
-
-\emph{{Property Assertions}}\footnote{\emph{R-96-PROPERTY-ASSERTIONS}}
-and includes positive property assertions and negative property assertions.
-A \emph{positive object property assertion ObjectPropertyAssertion( OPE a$_1$ a$_2$ )} states that the individual a$_1$ is connected by the object property expression \emph{OPE} to the individual a$_2$.
-A \emph{negative object property assertion NegativeObjectPropertyAssertion( OPE a$_1$ a$_2$ )} states that the individual a$_1$ is not connected by the object property expression \emph{OPE} to the individual a$_2$.
-A \emph{positive data property assertion DataPropertyAssertion( DPE a lt )} states that the individual a is connected by the data property expression DPE to the literal \emph{lt}. 
-A \emph{negative data property assertion NegativeDataPropertyAssertion( DPE a lt )} states that the individual a is not connected by the data property expression \emph{DPE} to the literal \emph{lt}.
-
-\subsection{Data Property Facets}
-
-For datatype properties it should be possible to declare frequently needed \emph{facets}\footnote{\emph{R-46-CONSTRAINING-FACETS}} to drive user interfaces and validate input against simple conditions, including min/max value, regular expressions, string length - similar to XSD datatypes.
-Constraining facets, to restrict datatypes of RDF literals, may be: \emph{xsd:length}, \emph{xsd:minLength}, \emph{xsd:maxLength}, \emph{xsd:pattern}, \emph{xsd:enumeration}, \emph{xsd:whiteSpace}, \\ \emph{xsd:maxInclusive}, \emph{xsd:maxExclusive}, \emph{xsd:minExclusive}, \emph{xsd:minInclusive}, \emph{xsd:total} \emph{Digits}, \emph{xsd:fractionDigits}.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-DATA-PROPERTY-FACETS-01:}} The abstract of a study (\emph{disco:purpose}) should have a minimum length (\emph{xsd:minLength}) of x. 
-\end{itemize}
-
-\subsection{Literal Pattern Matching}
-
-There are multiple use cases associated with the requirement to match literals according to given patterns\footnote{\emph{R-44-PATTERN-MATCHING-ON-RDF-LITERALS}}.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-LITERAL-PATTERN-MATCHING-01:}} Each \emph{disco:Variable} of a given \emph{disco:LogicalDataSet} must have a given prefix for its variable name (\emph{skos:notation}). 
-\end{itemize}
-
-\subsection{Negative Literal Pattern Matching}
-
-Literals of given data properties within given contexts do not have to match given patterns\footnote{\emph{R-44-PATTERN-MATCHING-ON-RDF-LITERALS}}.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-NEGATIVE-LITERAL-PATTERN-MATCHING-01:}} 
-\end{itemize}
-
-\subsection{Object Property Paths*}
-
-\emph{Object Property Paths}\footnote{\emph{R-55-OBJECT-PROPERTY-PATHS}} (or \emph{Object Property Chains} and in DL terminology \emph{complex role inclusion axiom} or \emph{role composition}) is the more complex form of sub properties.
-This axiom states that, if an individual \emph{x} is connected by a sequence of object property expressions \emph{OPE$_1$, ..., OPE$_n$} with an individual \emph{y}, then \emph{x} is also connected with \emph{y} by the object property expression \emph{OPE}.
-Role composition can only appear on the left-hand side of complex role inclusions \cite{Kroetzsch2012}.
-
-\subsection{Intersection*}
-
-Concept inclusions allow us to state that all mothers are female and that
-all mothers are parents, but what we really mean is that mothers are exactly the female
-parents. DLs support such statements by allowing us to form complex concepts such as
-the \emph{intersection}\footnote{\emph{R-15-CONJUNCTION-OF-CLASS-EXPRESSIONS}, \emph{R-16-CONJUNCTION-OF-DATA-RANGES}} (also called \emph{conjunction})
-which denotes the set of individuals that are both female and parents. A complex concept
-can be used in axioms in exactly the same way as an atomic concept, e.g., in the
-equivalence Mother $\equiv$ Female $\sqcap$ Parent .
-
-\subsection{Disjunction*}
-
-A \emph{union class expression}\footnote{{\em R-17-DISJUNCTION-OF-CLASS-EXPRESSIONS}, {\em R-18-DISJUNCTION-OF-DATA-RANGES}} contains all individuals that are instances of at least one class $C_{i}$ for 1 $\leq$ i $\leq$ n.
-A \emph{union data range} contains all tuples of literals that are contained in at least one data range $DR_{i}$ for 1 $\leq$ i $\leq$ n.
-Synonyms of {\em disjunction} are {\em union} and {\em inclusive or}.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-DISJUNCTION-01:}} 
-Only {\em disco:Variable}s or {\em disco:Question}s or {\em disco:RepresentedVariable}s can have {\em disco:concept} relationships to {\em skos:Concept}s.
-
-\begin{DL}
-Variable $\sqcup$ Question $\sqcup$ RepresentedVariable $\sqsubseteq$ $\forall$ concept.Concept \\
-\end{DL}
-\end{itemize}
-
-\subsection{Negation*}
-
-A \emph{complement class expression}\footnote{\emph{R-19-NEGATION-OF-CLASS-EXPRESSIONS}, \emph{R-20-NEGATION-OF-DATA-RANGES}} \emph{ObjectComplementOf( CE )} contains all individuals that are not instances of the class expression \emph{CE}.
-
-\subsection{Existential Quantifications*}
-
-An \emph{existential class expression}\footnote{{\em R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}} ({\em existential restriction} in DL terminology) contains all those individuals that are connected by the property \emph{P} to an individual \emph{x} that is an instance of the class \emph{C} or to literals that are in the data range \emph{DR}.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-01:}} 
-There must be at least one {\em disco:universe} relationship from {\em disco:Studies} or {\em disco:StudyGroups} to {\em disco:Universe} (\ms{Study $\sqcup$ StudyGroup $\sqsubseteq$ $\exists$ universe.Universe}).
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-01:}}
-	Dimensions have range (\emph{IC-4} \cite{CyganiakReynolds2014}) - 
-	Every dimension declared in a \emph{qb:DataStructureDefinition} must have a declared \emph{rdfs:range}. 
-	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-02:}}
-	Concept dimensions have code lists (\emph{IC-5} \cite{CyganiakReynolds2014}) - 
-	Every dimension with range \emph{skos:Concept} must have a \emph{qb:codeList}. 
-	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-03:}} 
-	Slice dimensions complete (\emph{IC-10} \cite{CyganiakReynolds2014}) - 
-	Every \emph{qb:Slice} must have a value for every dimension declared in its \emph{qb:sliceStructure}. 
-	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-04:}}
-	All dimensions required (\emph{IC-11} \cite{CyganiakReynolds2014}) - 
-	Every \emph{qb:Observation} has a value for each dimension declared in its associated \emph{qb:DataStructureDefinition}. 
-  \item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-05:}}
-	DSD includes measure (\emph{IC-3} \cite{CyganiakReynolds2014}) -  
-	Every \emph{qb:DataStructureDefinition} must include (\emph{qb:component}, \emph{qb:componentProperty}) at least one declared measure. 
-	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-06:}}
-	Slice Keys must be declared (\emph{IC-7} \cite{CyganiakReynolds2014}) -
-	Every \emph{qb:SliceKey} must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}). 
-\end{itemize}
-
-\subsection{Universal Quantifications*}
-
-A \emph{universal class expression}\footnote{{\em R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}} ({\em value restriction} in DL) contains all those individuals that are connected by an object property only to individuals that are instances of a particular class.
-
-\begin{itemize}
-	\item \textbf{{\em DATA-CUBE-C-UNIVERSAL-QUANTIFICATIONS-01:}}
-	\emph{Universal quantifications} are defined for each \emph{Data Cube} object and data property.
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DCAT-C-UNIVERSAL-QUANTIFICATIONS-01:}}
-	\emph{Universal quantifications} are defined for each \emph{DCAT} object and data property.
-	Only {\em dcat:Catalogs} can have {\em dcat:dataset} relationships to {\em dcat:Datasets} (\ms{Catalog $\sqsubseteq$ $\forall$ dataset.Dataset}).
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-UNIVERSAL-QUANTIFICATIONS-01:}}
-	\emph{Universal quantifications} are defined for each \emph{Disco} object and data property.
-  Only {\em disco:LogicalDataSet}s can have {\em disco:aggregation} relationships to {\em qb:DataSet}s (\ms{LogicalDataSet $\sqsubseteq$ $\forall$ aggregation.DataSet}).
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em PHDD-C-UNIVERSAL-QUANTIFICATIONS-01:}}
-	\emph{Universal quantifications} are defined for each \emph{PHDD} object and data property.
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em SKOS-C-UNIVERSAL-QUANTIFICATIONS-01:}}
-	\emph{Universal quantifications} are defined for each \emph{SKOS} object and data property.
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em XKOS-C-UNIVERSAL-QUANTIFICATIONS-01:}}
-	\emph{Universal quantifications} are defined for each \emph{XKOS} object and data property.
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\subsection{Minimum Unqualified Cardinality Restrictions*}
-
-A \emph{minimum cardinality restriction}\footnote{{\em R-81-MINIMUM-UNQUALIFIED-CARDINALITY-ON-PROPERTIES}, {\em R-211-CARDINALITY-CONSTRAINTS}} contains all those individuals that are connected by a property to at least n different individuals/literals
-that are instances of a particular class or data range. If the class is missing, it is taken to be \emph{owl:Thing}. 
-If the data range is missing, it is taken to be \emph{rdfs:Literal}.
-$\leq n R. \top$ is the minimum unqualified cardinality restriction where $n \in \mathbb{N}$ (written $\leq  n R$ in short).
-For unqualified cardinality restrictions, classes respective data ranges are not stated.
-
-\subsection{Minimum Qualified Cardinality Restrictions*}
-
-A \emph{minimum cardinality restriction}\footnote{{\em R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}, {\em R-211-CARDINALITY-CONSTRAINTS}} contains all those individuals that are connected by a property to at least n different individuals/literals
-that are instances of a particular class or data range. If the class is missing, it is taken to be \emph{owl:Thing}. 
-If the data range is missing, it is taken to be \emph{rdfs:Literal}.
-$\geq n R. C$ is a minimum qualified cardinality restriction where $n \in \mathbb{N}$.
-
-\begin{itemize}
-	\item \textbf{{\em DATA-CUBE-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
-	{\em Minimum Qualified Cardinality Restrictions} constraints are defined for each \emph{Data Cube} object and data property.
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DCAT-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
-	{\em Minimum Qualified Cardinality Restrictions} constraints are defined for each \emph{DCAT} object and data property.
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
-	{\em Minimum Qualified Cardinality Restrictions} constraints are defined for each \emph{Disco} object and data property.
-  A {\em disco:Questionnaire}, e.g., has at least one {\em disco:question} relationship to {\em disco:Questions} (\ms{Questionnaire $\sqsubseteq$ $\geq$1 question.Question}).
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em PHDD-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
-	{\em Minimum Qualified Cardinality Restrictions} constraints are defined for each \emph{PHDD} object and data property.
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\subsection{Maximum Unqualified Cardinality Restrictions*}
-
-A \emph{maximum cardinality restriction} contains all those individuals that are connected by a property to at most n different individuals/literals that are instances of a particular class or data range.
-If the class is missing, it is taken to be \emph{owl:Thing}.
-If the data range is not present, it is taken to be \emph{rdfs:Literal}.
-Unqualified means that the class respective the data range is not stated. 
-$\geq n R.
-\top$ is a \emph{maximum unqualified cardinality restriction}\footnote{\emph{R-82-MAXIMUM-UNQUALIFIED-CARDINALITY-ON-PROPERTIES}, \emph{R-211-CARDINALITY-CONSTRAINTS}} where $n \in \mathbb{N}$ (written $\geq  n R$ in short).
-
-\subsection{Maximum Qualified Cardinality Restrictions*}
-
-A \emph{maximum cardinality restriction} contains all those individuals that are connected by a property to at most n different individuals/literals that are instances of a particular class or data range.
-If the class is missing, it is taken to be \emph{owl:Thing}.
-If the data range is not present, it is taken to be \emph{rdfs:Literal}.
-Qualified means that the class respective the data range is stated. 
-$\leq n R. C$ is a \emph{maximum qualified cardinality restriction}\footnote{\emph{R-76-MAXIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}, \emph{R-211-CARDINALITY-CONSTRAINTS}} where $n \in \mathbb{N}$.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
-	A {\em disco:Variable} has at most one {\em disco:concept} relationship to a theoretical concept ({\em skos:Concept}) (\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}).
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\subsection{Exact Unqualified Cardinality Restrictions*}
-
-An \emph{exact cardinality restriction}\footnote{{\em R-80-EXACT-UNQUALIFIED-CARDINALITY-ON-PROPERTIES}, {\em R-211-CARDINALITY-CONSTRAINTS}} contains all those individuals that are connected by a property to exactly n different individuals that are instances of a particular class or data range.
-If the class is missing, it is taken to be \emph{owl:Thing}. 
-If the data range is not present, it is taken to be \emph{rdfs:Literal}.
-Unqualified means that the class respective data range is not stated. 
-$\geq n R. \top \sqcap \leq n R. \top $ is an exact unqualified cardinality restriction where $n \in \mathbb{N}$.
-
-\begin{itemize}
-	\item \textbf{{\em DATA-CUBE-C-EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
-	Unique slice structure (\emph{IC-9} \cite{CyganiakReynolds2014}) -  
-	Each \emph{qb:Slice} must have exactly one associated \emph{qb:sliceStructure}. 
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\subsection{Exact Qualified Cardinality Restrictions*}
-
-An \emph{exact cardinality restriction}\footnote{{\em R-74-EXACT-QUALIFIED-CARDINALITY-ON-PROPERTIES}, {\em R-211-CARDINALITY-CONSTRAINTS}} contains all those individuals that are connected by a property to exactly n different individuals that are instances of a particular class or data range.
-If the class is missing, it is taken to be \emph{owl:Thing}. 
-If the data range is not present, it is taken to be \emph{rdfs:Literal}.
-$\geq n R. C \sqcap \leq n R. C $ is an exact qualified cardinality restriction where $n \in \mathbb{N}$.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
-A {\em disco:Question} has exactly 1 {\em disco:universe} relationship to {\em disco:Universe} (\ms{Question $\sqsubseteq$ $\geq$1 universe.Universe $\sqcap$ $\leq$1 universe.Universe}).
-  \begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
-	Unique data set (\emph{IC-1} \cite{CyganiakReynolds2014}) -  
-	Every \emph{qb:Observation} has (\emph{qb:dataSet}) exactly one associated \emph{qb:DataSet} (\ms{Observation $\sqsubseteq$ $\geq$1 dataSet.DataSet $\sqcap$ $\leq$1 dataSet.DataSet}). 
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-	\item \textbf{{\em DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02:}}
-	Unique DSD (\emph{IC-2} \cite{CyganiakReynolds2014}) -  
-	Every \emph{qb:DataSet} has (\emph{qb:structure}) exactly one associated \emph{qb:DataStructureDefinition} (\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition $\sqcap$ $\leq$1 structure.DataStructureDefinition}).
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\subsection{Transitive Object Properties*}
-
-\emph{Transitivity} is a special form of \emph{complex role inclusion}.
-An \emph{object property transitivity axiom}\footnote{\emph{R-63-TRANSITIVE-OBJECT-PROPERTIES}} states that the object property is transitive — that is, if an individual \emph{x} is connected by the object property to an individual \emph{y} that is connected by the object property to an individual \emph{z}, then \emph{x} is also connected by the object property to \emph{z}.
-
-\subsection{Context-Specific Exclusive OR of Properties}
-
-\emph{Exclusive or} is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
-%In OWL 2, inclusive OR of properties would be possible to express, but not exclusive OR of data properties
-Only one of multiple properties within some context (e.g. a class, a shape, or an  application profile) leads to valid data\footnote{\emph{R-11-CONTEXT-SPECIFIC-EXCLUSIVE-OR-OF-PROPERTIES}}.
-This constraint is generally expressed in DL as follows: \ms{$C \sqsubseteq (\neg A \sqcap B) \sqcup (A \sqcap \neg B)$}.
-
-\subsection{Context-Specific Exclusive OR of Property Groups}
-
-\emph{Exclusive or} is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
-Only one of multiple property groups leads to valid data\footnote{{\em R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC}}.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-CONTEXT-SPECIFIC-EXCLUSIVE-OR-OF-PROPERTY-GROUPS-01:}}
-Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes and categories), but not both.
-
-\begin{DL}
-Concept $\sqsubseteq$ ($\neg$ D $\sqcap$ C) $\sqcup$ (D $\sqcap$ $\neg$ C) \\ 
-D $\equiv$ A $\sqcap$ B \\
-A $\sqsubseteq$ $\geq$ 1 notation.string $\sqcap$ $\leq$ 1 notation.string \\
-B $\sqsubseteq$ $\geq$ 1 prefLabel.string $\sqcap$ $\leq$ 1 prefLabel.string \\
-C $\sqsubseteq$ $\geq$ 1 definition.string $\sqcap$ $\leq$ 1 definition.string \\
-\end{DL}
-\end{itemize}
-
-\subsection{Allowed Values}
-
-It is a common requirement to narrow down the value space of a property by an exhaustive enumeration of the valid values (both literals or resources). 
-This is often rendered in drop down boxes or radio buttons in user interfaces. 
-\emph{Allowed values}\footnote{{\em R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS} and 
-{\em R-37-ALLOWED-VALUES-FOR-RDF-LITERALS}} for properties can be IRIs, IRIs (matching one or multiple patterns), (any) literals, literals of a list of allowed literals (e.g.
-'red' 'blue' 'green'), typed literals of one or multiple type(s) (e.g.
-\emph{xsd:string}).
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-ALLOWED-VALUES-01}}.
-{\em disco:CategoryStatistics} can only have {\em disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype {\em rdf:langString} (\ms{CategoryStatistics $\equiv$ $\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString}).
-\end{itemize}
-
-\subsection{Not Allowed Values}
-
-A matching triple has any literal / object except those explicitly excluded\footnote{\emph{R-33-NEGATIVE-OBJECT-CONSTRAINTS}, \emph{R-200-NEGATIVE-LITERAL-CONSTRAINTS}}.
-
-\subsection{Literal Ranges}
-
-\emph{P1} is a data property (of an instance of class \emph{C1}) and its literal value must be between the range of [$V_{min}$,$V_{max}$]\footnote{{\em R-45-RANGES-OF-RDF-LITERAL-VALUES}}.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-LITERAL-RANGES-01:}}
-{\em disco:percentage} (domain: {\em disco:CategoryStatistics}) literals must be of the datatype {\em xsd:double} whose range should be restricted to be between 0 and 100.
-\end{itemize}
-
-\subsection{Negative Literal Ranges}
-
-\emph{P1} is a data property (of an instance of class \emph{C1}) and its literal value must not be between the range of [$V_{min}$,$V_{max}$]\footnote{{\em R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES}}.
-
-\subsection{Required Properties}
-
-Properties may be required\footnote{\emph{R-68-REQUIRED-PROPERTIES}}.
-
-\subsection{Optional Properties}
-
-Properties may be optional\footnote{\emph{R-69-OPTIONAL-PROPERTIES}}.
-
-\subsection{Repeatable Properties}
-
-Properties may be repeatable\footnote{\emph{R-70-REPEATABLE-PROPERTIES}}.
-
-\subsection{Negative Property Constraints}
-
-Instances of a specific class must not have some object property\footnote{\emph{R-52-NEGATIVE-OBJECT-PROPERTY-CONSTRAINTS}, \emph{R-53-NEGATIVE-DATA-PROPERTY-CONSTRAINTS}}.
-
-\subsection{Individual Equality*}
-
-\emph{Individual equality}\footnote{\emph{R-6-EQUIVALENT-INDIVIDUALS}} states that two different names are known to refer to the same individual \cite{Kroetzsch2012}.
-
-\subsection{Functional Properties*}
-
-An \emph{object property functionality axiom}\footnote{\emph{R-57-FUNCTIONAL-OBJECT-PROPERTIES}} \emph{FunctionalObjectProperty( OPE )} states that the object property expression \emph{OPE} is functional — that is, for each individual \emph{x}, there can be at most one distinct individual \emph{y} such that \emph{x} is connected by \emph{OPE} to \emph{y}.
-Each such axiom can be seen as a syntactic shortcut for the following axiom: \emph{SubClassOf( owl:Thing ObjectMaxCardinality( 1 OPE ) )}.
-
-\subsection{Inverse-Functional Properties*}
-
-An \emph{object property inverse functionality axiom}\footnote{\emph{R-58-INVERSE-FUNCTIONAL-OBJECT-PROPERTIES}} \emph{InverseFunctionalObjectProperty( OPE )} states that the object property expression \emph{OPE} is inverse-functional - that is, for each individual \emph{x}, there can be at most one individual \emph{y} such that \emph{y} is connected by \emph{OPE} with \emph{x}.
-Each such axiom can be seen as a syntactic shortcut for the following axiom: \emph{SubClassOf( owl:Thing ObjectMaxCardinality( 1 ObjectInverseOf( OPE ) ) )}.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-INVERSE-FUNCTIONAL-PROPERTIES-01:}} for each \emph{rdfs:Resource x}, there can be at most one distinct \emph{rdfs:Resource y} such that \emph{y} is connected by \emph{adms:identifier} to \emph{x} $(\ms{funct identifier}\sp{\overline{\ }})$.
-\end{itemize}
-
-\tb{Achim, we created an open issue for DDI 4 how keys should be defined}
-
-\subsection{Value Restrictions*}
-
-\emph{Individual Value Restrictions}\footnote{\emph{R-88-VALUE-RESTRICTIONS}}: A has-value class expression \emph{ObjectHasValue( OPE a )} consists of an object property expression \emph{OPE} and an individual \emph{a}, and it contains all those individuals that are connected by \emph{OPE} to \emph{a}.
-Each such class expression can be seen as a syntactic shortcut for the class expression \emph{ObjectSomeValuesFrom( OPE ObjectOneOf( a ) )}.
-\emph{Literal Value Restrictions}: A has-value class expression \emph{DataHasValue( DPE lt )} consists of a data property expression \emph{DPE} and a literal \emph{lt}, and it contains all those individuals that are connected by \emph{DPE} to \emph{lt}.
-Each such class expression can be seen as a syntactic shortcut for the class expression \emph{DataSomeValuesFrom( DPE DataOneOf( lt ) )}.
-
-\subsection{Self Restrictions*}
-
-A \emph{self-restriction} \emph{ObjectHasSelf( OPE )} consists of an object property expression \emph{OPE}, and it contains all those individuals that are connected by \emph{OPE} to themselves.
-
-\subsection{Primary Key Properties}
-
-The \emph{Primary Key Properties}\footnote{R-226-PRIMARY-KEY-PROPERTIES} constraint is often useful to declare a given (datatype) property as the "primary key" of a class, so that a system can enforce uniqueness and also automatically build URIs from user input and data imported from relational databases or spreadsheets..
-Starfleet officers, e.g., are uniquely identified by their command authorization code (e.g. to activate and cancel auto-destruct sequences).
-It means that the property \emph{commandAuthorizationCode} is inverse functional - mapped to DL as follows:
-$(\ms{funct commandAuthorizationCode}\sp{\overline{\ }})$
-Keys, however, are even more general, i.e., a generalization of inverse functional properties \cite{Schneider2009}.
-A key can be a datatype property, an object property, or a chain of properties.
-For this generalization purposes, as there are different sorts of key, and as keys can lead to undecidability, 
-DL is extended with \emph{key boxes} and a special \emph{keyfor} construct\cite{Lutz2005}.
-This leads to the following DL mapping (only one simple property constraint):
-\ms{commandAuthorizationCode \ms{keyfor} StarfleetOfficer}
-
-\begin{itemize}
-	\item see \emph{inverse-functional properties}
-\end{itemize}
-
-\subsection{Class-Specific Property Range*}
-
-{\em Class-Specific Property Range}\footnote{{\em R-29-CLASS-SPECIFIC-RANGE-OF-RDF-OBJECTS}, {\em R-36-CLASS-SPECIFIC-RANGE-OF-RDF-LITERALS}} restricts the range of object and data properties for individuals within a specific context (e.g.
-class, shape, application profile).
-The values of each member property of a class may be limited by their value type, such as \emph{xsd:string} or \emph{foaf:Person}.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-CLASS-SPECIFIC-PROPERTY-RANGE-01:}} 
-Only {\em disco:Question}s can have {\em disco:questionText} relationships to literals of the datatype {\em rdf:langString} (\ms{$\neg$Question $\sqsubseteq$ $\neg\exists$ questionText.langString}).
-\end{itemize}
-
-\subsection{Class-Specific Reflexive Object Properties*}
-
-Using DL terminology \emph{Class-Specific Reflexive Object Properties} is called local reflexivity - a set of individuals (of a specific class) that are related to themselves via a given role \cite{Kroetzsch2012}.
-
-\subsection{Membership in Controlled Vocabularies.}
-
-Resources can only be members of listed controlled vocabularies\footnote{{\em R-32-MEMBERSHIP-OF-RDF-OBJECTS-IN-CONTROLLED-VOCABULARIES}, 
-{\em R-39-MEMBERSHIP-OF-RDF-LITERALS-IN-CONTROLLED-VOCABULARIES}}.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-MEMBERSHIP-IN-CONTROLLED-VOCABULARIES-01}}:
-{\em disco:SummaryStatistics} can only have {\em disco:summaryStatisticType} relationships to {\em skos:Concept}s which must be members of the controlled vocabulary {\em ddicv:SummaryStatisticType} which is a {\em skos:ConceptScheme}.
-
-\begin{DL}
-SummaryStatistics $\sqsubseteq$ $\forall summaryStatisticType.A$ \\
-$A \equiv Concept \sqcap \forall inScheme . B$ \\
-$B \equiv ConceptScheme \sqcap \{SummaryStatisticType\}$
-\end{DL}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DATA-CUBE-C-MEMBERSHIP-IN-CONTROLLED-VOCABULARIES-01:}}
-	Codes from code list (\emph{IC-19} \cite{CyganiakReynolds2014}) - 
-	If a dimension property has a \emph{qb:codeList}, then the value of the dimension property on every \emph{qb:Observation} must be in the code list. 
-\end{itemize}
-
-\subsection{IRI Pattern Matching}
-
-IRI pattern matching applied on subjects, properties, and objects\footnote{\emph{R-21-IRI-PATTERN-MATCHING-ON-RDF-SUBJECTS}, \emph{R-22-IRI-PATTERN-MATCHING-ON-RDF-OBJECTS}, \emph{R-23-IRI-PATTERN-MATCHING-ON-RDF-PROPERTIES}}.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-IRI-PATTERN-MATCHING}}: \emph{disco:Study} resources must match a given IRI pattern.
-\end{itemize}
-
-\subsection{Literal Value Comparison}
-
-Depending on the property semantics,
-there are cases where two different literal values must have
-a specific ordering with respect to an operator. 
-\emph{P1} and \emph{P2} are the datatype properties we need to compare and 
-\emph{OP} is the comparison operator (\textless, \textless=, \textgreater, \textgreater=, =, !=)\footnote{{\em R-43-LITERAL-VALUE-COMPARISON}}.
-The {\em COMP Pattern}, one of the Data Quality Test Patterns, can be used to validate the {\em Literal Value Comparison} constraint \cite{Kontokostas2014}:
-
-\begin{ex}
-SELECT ?s WHERE { 
-    ?s %%P1%% ?v1 .
-    ?s %%P2%% ?v2 .
-    FILTER ( ?v1 %%OP%% ?v2 ) }
-\end{ex}
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-LITERAL-VALUE-COMPARISON-01}}:
-{\em disco:startDate}s must be before (‘\textless’) {\em disco:endDate}s.
-To validate this constraint we bind the variables as follows (P1: {\em disco:startDate}, P2: {\em disco:endDate}, OP: \textless). 
-\end{itemize}
-
-\subsection{Ordering}
-
-With this constraint objects of object properties can be ordered as well as literals of data properties\footnote{\emph{R-121-SPECIFY-ORDER-OF-RDF-RESOURCES}, \emph{R-217-DEFINE-ORDER-FOR-FORMS/DISPLAY}}.
-
-In DDI, variables, questions, and codes/categories are typically organized in a particular order. 
-For obtaining this order, {\em skos:OrderedCollection} resources are used.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-ORDERING-01}}: If \emph{disco:Variable}s of a given \emph{disco:LogicalDataSet} should be ordered, a collection of variables must be present in the data and connected with the data set.
-The collection of variables is of the type {\em skos:OrderedCollection} containing multiple variables (each represented as {\em skos:Concept}) in a {\em skos:memberList}.
-	\item \textbf{{\em DISCO-C-ORDERING-02}}: If \emph{disco:Question}s of a given \emph{disco:Questionnaire} should be ordered, a collection of questions must be present in the data and connected with the questionnaire.
-The collection of questions is of the type {\em skos:OrderedCollection} containing multiple questions (each represented as {\em skos:Concept}) in a {\em skos:memberList}.
-	\item \textbf{{\em DISCO-C-ORDERING-03}}: If codes/categories (\emph{skos:Concept}s) of a given \emph{disco:Representation} of a given \emph{disco:Variable} should be ordered, the variable representation should also be of the type {\em skos:OrderedCollection} containing multiple codes/categories (each represented as {\em skos:Concept}) in a {\em skos:memberList}.
-\end{itemize}
-
-\subsection{Validation Levels}
-
-Different levels of severity (priority)\footnote{\emph{R-205-VARYING-LEVELS-OF-ERROR}, \emph{R-135-CONSTRAINT-LEVELS}, \emph{R-158-SEVERITY-LEVELS-OF-CONSTRAINT-VIOLATIONS}, \emph{R-193-MULTIPLE-CONSTRAINT-VALIDATION-EXECUTION-LEVELS}} should be assigned to constraints.
-Possible validation levels could be: informational, warning, error, fail, should, recommended, must, may, optional, closed (only this) constraints, open (at least this) constraint.
-
-For \emph{Disco} each constraint should be assigned to exactly one \emph{validation level}.
-
-\subsection{String Operations}
-
-Many different \emph{string operations}\footnote{\emph{R-194-PROVIDE-STRING-FUNCTIONS-FOR-RDF-LITERALS}} are possible.
-Some constraints require building new strings out of other strings.
-Calculating the string length would also be another constraint of this type.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-STRING-OPERATIONS-01}}: The title of a study (\emph{dcterms:title}) (e.g.
-'EU-SILC 2005') may be calculated out of the title of the containing series (\emph{dcterms:title}) (e.g.
-'EU-SILC') and the human-readable label of the study (\emph{rdfs:label}) (e.g.
-'2005').
-\end{itemize}
-
-\subsection{Context-Specific Valid Classes}
-
-What types are valid in a specific context?\footnote{\emph{R-209-VALID-CLASSES}} 
-Context can be an input stream, a data creation function, or an API.
-
-\begin{itemize}
-	\item \textbf{{\em DATA-CUBE-C-CONTEXT-SPECIFIC-VALID-CLASSES-01}}: For future versions of \emph{Data Cube}, out-dated classes can be marked as deprecated.
-	\begin{itemize}
-		\item severity level: RECOMMENDED
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DCAT-C-CONTEXT-SPECIFIC-VALID-CLASSES-01}}: For future versions of \emph{DCAT}, out-dated classes can be marked as deprecated.
-	\begin{itemize}
-		\item severity level: RECOMMENDED
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-CONTEXT-SPECIFIC-VALID-CLASSES-01}}: For future versions of \emph{Disco}, out-dated classes can be marked as deprecated.
-	\begin{itemize}
-		\item severity level: RECOMMENDED
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em PHDD-C-CONTEXT-SPECIFIC-VALID-CLASSES-01}}: For future versions of \emph{PHDD}, out-dated classes can be marked as deprecated.
-	\begin{itemize}
-		\item severity level: RECOMMENDED
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em SKOS-C-CONTEXT-SPECIFIC-VALID-CLASSES-01}}: For future versions of \emph{SKOS}, out-dated classes can be marked as deprecated.
-	\begin{itemize}
-		\item severity level: RECOMMENDED
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em XKOS-C-CONTEXT-SPECIFIC-VALID-CLASSES-01}}: For future versions of \emph{XKOS}, out-dated classes can be marked as deprecated.
-	\begin{itemize}
-		\item severity level: RECOMMENDED
-	\end{itemize}
-\end{itemize}
-
-\subsection{Context-Specific Valid Properties}
-
-What properties can be used within this context?\footnote{\emph{R-210-VALID-PROPERTIES}} 
-Context can be an data receipt function, data creation function, or API.
-
-\begin{itemize}
-	\item \textbf{{\em DATA-CUBE-C-CONTEXT-SPECIFIC-VALID-PROPERTIES-01}}: For future versions of \emph{Data Cube}, out-dated properties can be marked as deprecated.
-	\begin{itemize}
-		\item severity level: RECOMMENDED
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DCAT-C-CONTEXT-SPECIFIC-VALID-PROPERTIES-01}}: For future versions of \emph{DCAT}, out-dated properties can be marked as deprecated.
-	\begin{itemize}
-		\item severity level: RECOMMENDED
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-CONTEXT-SPECIFIC-VALID-PROPERTIES-01}}: For future versions of \emph{Disco}, out-dated properties can be marked as deprecated.
-	\begin{itemize}
-		\item severity level: RECOMMENDED
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em PHDD-C-CONTEXT-SPECIFIC-VALID-PROPERTIES-01}}: For future versions of \emph{PHDD}, out-dated properties can be marked as deprecated.
-	\begin{itemize}
-		\item severity level: RECOMMENDED
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em SKOS-C-CONTEXT-SPECIFIC-VALID-PROPERTIES-01}}: For future versions of \emph{SKOS}, out-dated properties can be marked as deprecated.
-	\begin{itemize}
-		\item severity level: RECOMMENDED
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em XKOS-C-CONTEXT-SPECIFIC-VALID-PROPERTIES-01}}: For future versions of \emph{XKOS}, out-dated properties can be marked as deprecated.
-	\begin{itemize}
-		\item severity level: RECOMMENDED
-	\end{itemize}
-\end{itemize}
-
-\subsection{Default Values*}
-
-\emph{Default values}\footnote{{\em R-31-DEFAULT-VALUES-OF-RDF-OBJECTS}, {\em R-38-DEFAULT-VALUES-OF-RDF-LITERALS}} for objects and literals are inferred automatically.
-It should be possible to declare the default value for a given property, e.g. so that input forms can be pre-populated and to insert a required property that is missing in a web service call.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-DEFAULT-VALUES-01:}}
-The value 'true' for the property {\em disco:isPublic} ({\em xsd:boolean}) indicates that the data set ({\em disco:LogicalDataSet}) can be accessed (usually downloaded) by anyone.
-Per default, access to data sets should be restricted ('false').
-\end{itemize}
-
-\subsection{Mathematical Operations}
-
-Examples for {\em Mathematical Operations}\footnote{{\em R-42-MATHEMATICAL-OPERATIONS}, {\em R-41-STATISTICAL-COMPUTATIONS}} are the addition of two dates, the addition of days to a start date, and statistical computations (e.g.
-average, mean, sum).
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-MATHEMATICAL-OPERATIONS-01:}}
-  The sum of {\em disco:percentage} (datatype: {\em xsd:double}) values of all codes (represented as {\em skos:Concept}s) of a code list ({\em skos:ConceptScheme} or {\em skos:OrderedCollection}), serving as representation of a particular {\em disco:Variable}, must exactly be 100.
-	\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-
-	\item \textbf{{\em DISCO-C-MATHEMATICAL-OPERATIONS-02}}:
-	For a given variable, the sum of all category statistics (frequency) has to be equal to the 'total' value of summary statistics.
-	\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-
-	\item \textbf{{\em DISCO-C-MATHEMATICAL-OPERATIONS-03}}:
-	For a given variable, the sum of 'valid total' and 'missing total' has to be equal to 'total'.
-	\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-
-	\item \textbf{{\em DISCO-C-MATHEMATICAL-OPERATIONS-04}}:
-	For a given variable, the 'total' value for country 'All' must be equal to the sum of the 'total' value for all Countries.
-	\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-
-	\item \textbf{{\em DISCO-C-MATHEMATICAL-OPERATIONS-05}}:
-	Minimum values do not have to be greater than maximum values (\emph{disco:SummaryStatistics}).
-	\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-
-\end{itemize}
-
-\subsection{Language Tag Matching}
-
-For particular data properties, values must be stated for predefined languages\footnote{{\em R-47-LANGUAGE-TAG-MATCHING}}.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-LANGUAGE-TAG-MATCHING:}}
-There must be an English variable name ({\em skos:notation}) for each {\em disco:Variable} within {\em disco:LogicalDataSet}s.
-\end{itemize}
-
-\subsection{Language Tag Cardinality}
-
-For particular data properties, values of predefined languages must be stated for determined number of times\footnote{{\em R-49-RDF-LITERALS-HAVING-AT-MOST-ONE-LANGUAGE-TAG}, {\em R-48-MISSING-LANGUAGE-TAGS}}.
-
-\begin{itemize}
-
-	\item \textbf{{\em DISCO-C-LANGUAGE-TAG-CARDINALITY-01:}}
-  There must be at least one English {\em disco:questionText} for each {\em disco:Question} within {\em disco:LogicalDataSet}s.
-
-  \item \textbf{{\em DISCO-C-LANGUAGE-TAG-CARDINALITY-02:}}
-  There should be at most one English literal value for variable names ({\em skos:notation}, domain: {\em disco:Variable}).
-
-  \item \textbf{{\em DISCO-C-LANGUAGE-TAG-CARDINALITY-03}}:
-	For each question (\emph{disco:Question}), there must be at least one question text (\emph{disco:questionText}) associated with a language tag of an arbitrary language or with an English language tag.
-
-\end{itemize}
-
-\begin{itemize}
-
-	\item \textbf{{\em SKOS-C-LANGUAGE-TAG-CARDINALITY-01\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Omitted or Invalid Language Tags}:}}
-Some controlled vocabularies contain literals in natural language, but without information what language has actually been used.
-Language tags might also not conform to language standards, such as RFC 3066.
-Iteration over all triples in the vocabulary that have a predicate which is a (subclass of) \emph{rdfs:label} or \emph{skos:note}. 
-Severity level: INFO
-
-  \item \textbf{{\em SKOS-C-LANGUAGE-TAG-CARDINALITY-02\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Incomplete Language Coverage}:}}
-	Some concepts in a thesaurus are labeled in only one language, some in multiple languages.
-It may be desirable to have each concept labeled in each of the languages that also are used on the other concepts.
-This is not always possible, but incompleteness of language coverage for some concepts can indicate shortcomings of the vocabulary.
-	Severity level: INFO
-
-	\item \textbf{{\em SKOS-C-LANGUAGE-TAG-CARDINALITY-03\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - No Common Language}:}}
-	Checks if all concepts have at least one common language, i.e. they have assigned at least one literal in the same language. 
-	Severity level: INFO
-
-	\item \textbf{{\em SKOS-C-LANGUAGE-TAG-CARDINALITY-04\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Inconsistent Preferred Labels}:}}
-	Inconsistent Preferred Labels:
-  According to the SKOS reference document, "A resource has no more than one value of skos:prefLabel per language tag".  
-	\begin{itemize}
-	  \item Implementation:
-		A SPARQL query is used to find concepts with at least two prefLabels. In a second step, the language tags of these prefLabels are analyzed and an ambiguity is detected if they are equal.  
-		\item Severity level: INFO
-	\end{itemize}
-
-\end{itemize}
-
-\subsection{Whitespace Handling}
-
-Avoid whitespaces in literals neither leading nor trailing white spaces\footnote{\emph{R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS}}.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-WHITESPACE-HANDLING-01:}} Delete whitespaces of series and study abstracts (\emph{dcterms:abstract}; domain: \emph{disco:StudyGroup}, \emph{disco:Study}) automatically.
-\end{itemize}
-
-\subsection{HTML Handling}
-
-Check if all HTML tags, included in literals (of specific data properties within the context of specific classes)\footnote{\emph{R-51-HTML-HANDLING-OF-RDF-LITERALS}}, are closed properly.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-HTML-HANDLING-01:}} Check if all HTML tags, included in literals of all \emph{Disco} data properties, are closed properly.
-	\item \textbf{{\em DISCO-C-HTML-HANDLING-02:}} Check if all HTML tags, included in literals of all data properties whose domains are \emph{Disco} classes, are closed properly.
-\end{itemize}
-
-\subsection{Conditional Properties}
-
-If specific properties exist, then specific other properties must also be present\footnote{{\em R-71-CONDITIONAL-PROPERTIES}}.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-CONDITIONAL-PROPERTIES-01}}:
-  If a {\em skos:Concept} represents a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
-then the property {\em disco:isValid} has to be stated indicating if the code is valid ('true') or missing ('false').
-	\item \textbf{{\em DISCO-C-CONDITIONAL-PROPERTIES-02}}:
-	If the abstract (\emph{dcterms:abstract}) of a \emph{disco:Study} is missing, a study title (\emph{dcterms:title}) has to be stated.
-\end{itemize}
-
-\subsection{Recommended Properties}
-
-Which properties are not necessarily required but recommended within a particular context\footnote{{\em R-72-RECOMMENDED-PROPERTIES}}.
-
-\begin{itemize}
-	\item \textbf{{\em DATA-CUBE-C-RECOMMENDED-PROPERTIES-01:}}
-	\begin{itemize}
-		\item severity level: RECOMMENDED
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DCAT-C-RECOMMENDED-PROPERTIES-01:}}
-	\begin{itemize}
-		\item severity level: RECOMMENDED
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-RECOMMENDED-PROPERTIES-01:}}
-  The property {\em skos:notation} is not mandatory for {\em disco:Variable}s, but recommended to indicate variable names.
-	\begin{itemize}
-		\item severity level: RECOMMENDED
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em PHDD-C-RECOMMENDED-PROPERTIES-01:}}
-	\begin{itemize}
-		\item severity level: RECOMMENDED
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em SKOS-C-RECOMMENDED-PROPERTIES-01:}}
-	\begin{itemize}
-		\item severity level: RECOMMENDED
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em XKOS-C-RECOMMENDED-PROPERTIES-01:}}
-	\begin{itemize}
-		\item severity level: RECOMMENDED
-	\end{itemize}
-\end{itemize}
-
-\subsection{Handle RDF Collections}
-
-Examples of the \emph{Handle RDF Collections}\footnote{\emph{R-120-HANDLE-RDF-COLLECTIONS}} constraint are: a collection must have a specific size; the first/last element of a given list must be a specific literal; the elements of collections are compared; are collections identical?; actions on RDF lists\footnote{See \url{http://www.snee.com/bobdc.blog/2014/04/rdf-lists-and-sparql.html}}; the 2.
-list element must be equal to 'XXX'; does the list have more than 10 elements?
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-HANDLE-RDF-COLLECTIONS-01}}: Have comparable \emph{disco:Variable}s the same number of codes in their code lists?
-	\item \textbf{{\em DISCO-C-HANDLE-RDF-COLLECTIONS-02}}: Does the actual number of \emph{disco:Variable}s within an (un)ordered collection of a given \emph{disco:LogicalDataSet} match the expected number?
-\end{itemize}
-
-\subsection{Value is Valid for Datatype}
-
-Make sure that a value is valid for its datatype.
-It has to be ensured, e.g., that a date is really a date, or that a \emph{xsd:nonNegativeInteger} value is not negative.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-VALUE-IS-VALID-FOR-DATATYPE-01}}: Check if all literal values of properties used within the \emph{Disco} context of the datatype {\em xsd:date} (e.g.
-{\em disco:startDate}, {\em disco:endDate}, {\em dcterms:date}) are really of the datatype {\em xsd:date}.
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DATA-CUBE-C-VALUE-IS-VALID-FOR-DATATYPE-01:}}
-	Datatype consistency (\emph{IC-0} \cite{CyganiakReynolds2014}) -  
-	The RDF graph must be consistent under RDF D-entailment using a datatype map containing all the datatypes used within the graph. 
-\end{itemize}
-
-\subsection{Use Sub-Super Relations in Validation}
-
-\footnote{\emph{R-224-USE-SUB-SUPER-RELATIONS-IN-VALIDATION}}
-
-The validation of instances data (direct or indirect) exploits the sub-class or sub-property link in a given ontology.
-This validation can indicate when the data is verbose (redundant) or expressed at a too general level, and could be improved.
-If \emph{dcterms:date} and one of its sub-properties \emph{dcterms:created} or \emph{dcterms:issued} are present, e.g., check that the value in \emph{dcterms:date} is not redundant with \emph{dcterms:created} or \emph{dcterms:issued} for ingestion.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-USE-SUB-SUPER-RELATIONS-IN-VALIDATION-01}}: 
-	If one or more \emph{dcterms:coverage} properties are present, suggest the use of one of its sub-properties \emph{dcterms:spatial} or \emph{dcterms:temporal}.
-	\item \textbf{{\em DISCO-C-USE-SUB-SUPER-RELATIONS-IN-VALIDATION-02}}: 
-	If the \emph{dcterms:contributor} property is present, suggest the use of one of its sub-properties, e.g. \emph{disco:fundedBy}.
-\end{itemize}
-
-\subsection{Cardinality Shortcuts*}
-
-In most library applications, cardinality shortcuts tend to appear in pairs, with repeatable/non-repeatable establishing maximum cardinality and optional/mandatory establishing minimum cardinality.
-These are shortcuts for more detailed \emph{cardinality restrictions}.
-
-\subsection{Aggregation}
-
-Some constraints require aggregating multiple values, especially via \emph{COUNT}, \emph{MIN} and \emph{MAX}.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-AGGREGATION-01}}: calculate the number of theoretical concepts in the thematic classification of a given study.
-  \item \textbf{{\em DISCO-C-AGGREGATION-02}}: calculate the number of variables of a data set.
-	\item \textbf{{\em DISCO-C-AGGREGATION-03}}: calculate the number of questions in a given questionnaire.
-	\item \textbf{{\em DISCO-C-AGGREGATION-04}}: the number of codes of a given variable must be below a maximum value.
-	\item \textbf{{\em DISCO-C-AGGREGATION-05}}: the number of questions of a given questionnaire must exactly be a given value.
-	\item \textbf{{\em DISCO-C-AGGREGATION-06}}: the cumulative percentage of all codes of a given variable must be 100.
-  \item \textbf{{\em DISCO-C-AGGREGATION-07}}: the absolute frequency of all valid codes of a given variable must be equal to a given value.
-\end{itemize}
-
-\subsection{\underline{Structure}}
-
-SKOS is based on RDF, which is a graph-based data model.
-Therefore we can concentrate on the vocabulary's graph-based structure for assessing the quality of SKOS vocabularies and apply graph- and network-analysis techniques.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-STRUCTURE-01}}: there must be exactly one root in the hierarchy of DDI concepts. 
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DATA-CUBE-C-STRUCTURE-01:}}
-	Codes from hierarchy (\emph{IC-20} \cite{CyganiakReynolds2014}) -  
-	If a dimension property has a \emph{qb:HierarchicalCodeList} with a non-blank \emph{qb:parentChildProperty} then the value of that dimension property on every \emph{qb:Observation} must be reachable from a root of the hierarchy using zero or more hops along the \emph{qb:parentChildProperty} links.
-	\item \textbf{{\em DATA-CUBE-C-STRUCTURE-02:}}
-	Codes from hierarchy (inverse) (\emph{IC-21} \cite{CyganiakReynolds2014}) -  
-	If a dimension property has a \emph{qb:HierarchicalCodeList} with an inverse \emph{qb:parentChildProperty} then the value of that dimension property on every \emph{qb:Observation} must be reachable from a root of the hierarchy using zero or more hops along the inverse \emph{qb:parentChildProperty} links.
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em SKOS-C-STRUCTURE-01\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Orphan Concepts}:}}
-	Orphan Concepts:
-  An orphan concept is a concept without any associative or hierarchical relations.
-It might have attached literals like e.g., labels, but is not connected to any other resource, lacking valuable context information.
-A controlled vocabulary that contains many orphan concepts is less usable for search and retrieval use cases, because, e.g., no hierarchical query expansion can be performed on search terms to find documents with more general content.
-	\begin{itemize}
-		\item Implementation: Iteration over all concepts in the vocabulary and returning that don't have associated resources using (subproperties of) \emph{skos:semanticRelation}. 
-		\item Severity level: INFO
-\end{itemize}
-	\item \textbf{{\em SKOS-C-STRUCTURE-02\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Disconnected Concept Clusters}:}}
-	Disconnected Concept Clusters:
-	Checking the connectivity of the graph, it is possible to identify all weakly connected components.
-These datasets form "islands" in the vocabulary and might be caused by incomplete data acquisition, "forgotten" test data, outdated terms and the like.
-	\begin{itemize}
-		\item Implementation: Creation of an undirected graph that includes all non-orphan concepts as nodes and all semantic relations as edges.
-Tarjan's algorithm then finds and returns all weakly connected components.
-		\item Severity level: INFO
-\end{itemize}
-	\item \textbf{{\em SKOS-C-STRUCTURE-03\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Cyclic Hierarchical Relations}:}}
-	Cyclic Hierarchical Relations: 
-	Although perfectly consistent with the SKOS data model, cyclic relations may reveal a logical problem in the thesaurus.
-Consider the following example: "decision" $\rightarrow$ "problem resolution" $\rightarrow$ "problem" ($\rightarrow$ "decision": here the cycle is closed).
-The concepts are connected using \emph{skos:broader} relationships (indicated with "$\rightarrow$").
-Due to the fact that a thesaurus is in many cases a product of consensus between the contributors (or just the decision of one dedicated thesaurus manager), it will be almost impossible to automatically resolve the cycle (i.e.
-deleting an edge).
-	\begin{itemize}
-		\item Implementation: Construction of a graph having all concepts as nodes and the set of edges being \emph{skos:broader} relations. 
-		\item Severity level: INFO
-\end{itemize}
-	\item \textbf{{\em SKOS-C-STRUCTURE-04\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Valueless Associative Relations}:}}
-	Valueless Associative Relations:
-	Two concepts are sibling, but also connected by an associative relation. In that context, the associative relation is not necessary. See ISO\_DIS\_25964-1, 11.3.2.2 
-	\begin{itemize}
-		\item Implementation:
-		Identification of all pairs of concepts that have the same broader or narrower concepts, i.e. they are "sibling terms". All siblings that are related by a \emph{skos:related} property are returned. 
-	  \item Severity level: INFO
-\end{itemize}
-	\item \textbf{{\em SKOS-C-STRUCTURE-05\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Solely Transitively Related Concepts}:}}
-	Solely Transitively Related Concepts:
-	\emph{skos:broaderTransitive} and \emph{skos:narrowerTransitive} are, according to the SKOS reference document, "not used to make assertions", so they should not be the only relations hierarchically relating two concepts.
-	\begin{itemize}
-		\item Implementation: Identification of all concept pairs that are related by \emph{skos:broaderTransitive} or \emph{skos:narrowerTransitive} properties but not by their \emph{skos:broader} and \emph{skos:narrower} subproperties.
-		\item Severity level: INFO
-\end{itemize}
-	\item \textbf{{\em SKOS-C-STRUCTURE-06\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Unidirectionally Related Concepts}:}}
-	Unidirectionally Related Concepts:
-	Reciprocal relations (e.g., \emph{broader/narrower, related, hasTopConcept/topConceptOf}) should be included in the controlled vocabularies to achieve better search results using SPARQL in systems without reasoner support.
-	\begin{itemize}
-		\item Implementation:
-		This issue is checked without inference of \emph{owl:inverseOf} properties.
-We iterate over all triples and check for each property if an inverse property is defined in the SKOS ontology and if the respective statement using this property is included in the vocabulary.
-If not, the resources associated with this property are returned.
-	  \item Severity level: INFO
-\end{itemize}
-	\item \textbf{{\em SKOS-C-STRUCTURE-07\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Omitted Top Concepts}:}}
-	Omitted Top Concepts:
-	A vocabulary should provide "entry points" to the data to provide “efficient access” (SKOS primer) and guidance for human users. 
-	\begin{itemize}
-		\item Implementation:
-		For every ConceptScheme in the controlled vocabulary, a SPARQL query is issued finding resources that are associated with this ConceptScheme by one of the properties \emph{skos:hasTopConcept} or \emph{skos:topConceptOf}.
-Top concepts are also concepts having no broader concept.
-	  \item Severity level: SHOULD
-\end{itemize}
-	\item \textbf{{\em SKOS-C-STRUCTURE-08\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Top Concepts Having Broader Concepts}:}}
-	Top Concepts Having Broader Concepts:
-	Concepts "internal to the tree" should not be indicated as top concepts.
-	\begin{itemize}
-		\item Implementation:
-		A SPARQL query finds all top concepts (being defined by one of the properties \emph{skos:hasTopConcept} or \emph{skos:topConceptOf}) having associated a broader concept. 
-	  \item Severity level: ERROR
-\end{itemize}
-	\item \textbf{{\em SKOS-C-STRUCTURE-09\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Hierarchical Redundancy}:}}
-	Hierarchical Redundancy:
-	As stated in the SKOS reference document, \emph{skos:broader} and \emph{skos:narrower} are not transitive properties.
-However, they are subproperties of \emph{skos:broaderTransitive} and \emph{skos:narrowerTransitive} which enables inference of a "transitive closure".
-This, in fact, leaves it up to the user to interpret wheter a vocabulary's hierarchical structure is seen as transitive or not.
-In the former case, this check can be useful.
-It finds pairs of concepts (A,B) that are directly hierarchically related but there also exits an hierarchical path through a concept C that connects A and B.
-	Severity level: INFO
-	\item \textbf{{\em SKOS-C-STRUCTURE-10\footnote{Corresponds to qSKOS Quality Issues - Structural Issues - Reflexive Relations}:}}
-	Reflexive Relations:
-	Concepts related to themselves. 
-	\begin{itemize}
-		\item Severity level: INFO
-	\end{itemize}
-\end{itemize}
-
-\subsection{\underline{Labeling and Documentation}}
-
-\begin{itemize}
-	\item \textbf{{\em SKOS-C-LABELING-AND-DOCUMENTATION-01\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Undocumented Concepts}:}}
-	Undocumented Concepts:
-  The SKOS standard defines a number of properties useful for documenting the meaning of the concepts in a thesaurus also in a human-readable form.
-Intense use of these properties leads to a well-documented thesaurus which should also improve its quality.
-	Iteration over all concepts in the vocabulary and find those not using one of \emph{skos:note}, \emph{skos:changeNote}, \emph{skos:definition}, \emph{skos:editorialNote}, \emph{skos:example}, \emph{skos:historyNote}, or \emph{skos:scopeNote}.
-	\begin{itemize}
-		\item Severity level: INFO
-	\end{itemize}
-	\item \textbf{{\em SKOS-C-LABELING-AND-DOCUMENTATION-02\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Overlapping Labels}:}}
-	Overlapping Labels:
-	This is a generalization of a recommendation in the SKOS primer, that “no two concepts have the same preferred lexical label in a given language when they belong to the same concept scheme”.
-This could indicate missing disambiguation information and thus lead to problems in autocompletion application.
-	\begin{itemize}
-		\item Severity level: INFO
-	\end{itemize}
-	\item \textbf{{\em SKOS-C-LABELING-AND-DOCUMENTATION-03\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Missing Labels}:}}
-	Missing Labels:
-	To make the vocabulary more convenient for humans to use, instances of SKOS classes (Concept, ConceptScheme, Collection) should be labeled using e.g., \emph{skos:prefLabel}, \emph{altLabel}, \emph{rdfs:label}, \emph{dc:title}.
-	\begin{itemize}
-		\item Severity level: INFO
-	\end{itemize}
-	\item \textbf{{\em SKOS-C-LABELING-AND-DOCUMENTATION-04\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Unprintable Characters in Labels}:}}
-	Unprintable Characters in Labels:
-	\emph{pref/alt/hiddenlabels} contain characters that are not alphanumeric characters or blanks.
-	\begin{itemize}
-		\item Severity level: INFO
-	\end{itemize}
-	\item \textbf{{\em SKOS-C-LABELING-AND-DOCUMENTATION-05\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Empty Labels}:}}
-	Empty Labels:
-	Labels also need to contain textual information to be useful, thus we find all SKOS labels with length 0 (after removing whitespaces). 
-	\begin{itemize}
-		\item Severity level: INFO
-	\end{itemize}
-	\item \textbf{{\em SKOS-C-LABELING-AND-DOCUMENTATION-06\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Ambiguous Notation References}:}}
-	Ambiguous Notation References:
-	Concepts within the same concept scheme should not have identlical \emph{skos:notation} literals. 
-	\begin{itemize}
-		\item Severity level: INFO
-	\end{itemize}
-\end{itemize}
-
-\subsection{\underline{Vocabulary}}
-Vocabularies should not invent any new terms or use deprecated elements.
-
-\begin{itemize}
-	\item \textbf{\em DATA-CUBE-C-VOCABULARY-01} 
-	\begin{itemize}
-		\item Severity level: FATALERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{\em DCAT-C-VOCABULARY-01} 
-	\begin{itemize}
-		\item Severity level: FATALERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{\em DISCO-C-VOCABULARY-01} 
-	\begin{itemize}
-		\item Severity level: FATALERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{\em PHDD-C-VOCABULARY-01} 
-	\begin{itemize}
-		\item Severity level: FATALERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em SKOS-C-VOCABULARY-01\footnote{Corresponds to qSKOS Quality Issues - Linked Data Specific Issues - Undefined SKOS Resources}:}}
-	Undefined SKOS Resources:
-	The vocabulary should not invent any new terms within the SKOS namespace or use deprecated SKOS elements. 
-	\begin{itemize}
-		\item Severity level: FATALERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{\em XKOS-C-VOCABULARY-01} 
-	\begin{itemize}
-		\item Severity level: FATALERROR
-	\end{itemize}
-\end{itemize}
-
-\section{SKOS-Related Constraint Types}
-
-\section{Validation in Combination with other Vocabularies}
-
-\subsection{RDF Data Cube Vocabulary}
-
-\subsection{SKOS and XKOS}
-
-\subsection{PHDD}
-
-\subsection{DCAT}
-
-\section{Conclusion and Future Work}
 

### 2015-03-12 paper/paper7/paper7-evaluation.tex
evaluation

@@
 
+\section{Disco}
+
+\begin{itemize}
+	\item DwB Resource Discovery Portal
+	\begin{itemize}
+	  \item Metadata records for each study are available on the study landing pages.
+		\item \url{http://dwb-dev.nsd.uib.no/portal/#/study/http://portal.dwbproject.org/resource/Study/de.gesis/zacat/ZA5597/en}
+    \item Search interface: \url{http://dwb-dev.nsd.uib.no/portal/#/search?q=smoking&p=1&s=score&d=desc&f=text}
+	\end{itemize}
+\end{itemize}
+
 \section{Data Cube}

### 2015-03-16 paper/ISWC 2015 Tutorial/ISWC-2015-tutorial.tex
iswc tutorial

@@
 \title{Let’s Disco – Publishing person-level data as Linked Data.}
-\subtitle{Building a Highly-Complex Data Set with Disco, PHDD, XKOS and widely used Vocabularies.
+\subtitle{Building domain-specific Data Sets with Disco, PHDD, XKOS and widely used Vocabularies.
 }
@@
 %Disco is intended to provide means to describe person-level data by essential metadata for the discovery purpose. 
-Using Disco, such data sets can be discovered in the Web of Linked Data by using RDF technologies, e.g. searching for specific questions, topics, and geographical coverage.
-
-For a meaningful publication of DDI metadata as Linked Data, additional established RDF vocabularies (e.g. RDF Data Cube, DCAT, SKOS, PROV-O, XKOS, and PHDD) are reused to a large extend. 
+%Using Disco, such data sets can be discovered in the Web of Linked Data by using RDF technologies, e.g. searching for specific questions, topics, and geographical coverage. 
+Using Disco, such data sets which are frequently used in different domains like the social, ecomical and behavoural sciences can be published as Linked Data. 
+However, for a meaningful and complete publication of these data sets, additional established RDF vocabularies (e.g. RDF Data Cube, DCAT, SKOS, PROV-O, XKOS, and PHDD) are reused to a large extend. 
 This combined usage enables the creation of data repositories providing metadata of data collections, data sets, relationships between them and related provenance information. 
-
-In this tutorial, we show how Disco is interwoven with these vocabularies and how these connections can be used in order to publish highly complex data sets.
+In this tutorial, we show how Disco is interwoven with these vocabularies and how these connections can be used in order to publish complex and domain-specific data sets.
 In different real world use cases, we demonstrate the adoption and inclusion of Disco in existing information systems. 
 %Existing DDI instances are stored in form of XML documents which can be transformed into DDI-RDF and therefore exposed as Linked Data.
-Additionally, we present typical metadata constraints of DDI metadata as well as how to formulate them by different constraint languages (e.g. OWL 2) and how to actually validate them.
+%Additionally, we present typical metadata constraints of DDI metadata as well as how to formulate them by different constraint languages (e.g. OWL 2) and how to actually validate them.
 
@@
 The DDI-RDF Discovery Vocabulary (Disco) \cite{Bosch2012} is an RDF Schema vocabulary which can be utilized to represent person-level data sets and related metadata as Linked Data. 
-It is based on DDI (Data Documentation Initiative) which is a structured metadata standard related to the observation and measurement of human activity.
+It is based on the metadata standard DDI (Data Documentation Initiative) which is related to the observation and measurement of human activity and often used in domains like the social, ecomical and behavoural sciences.
 The metadata of such data can get highly complex by e.g. necessary provenance information and relationships to data aggregates, data collections, and the physical data sources.
@@
 RDF Data Cube\footnote{\url{http://www.w3.org/TR/vocab-data-cube/}}, DCAT\footnote{\url{http://www.w3.org/TR/vocab-dcat/}}, SKOS\footnote{\url{http://www.w3.org/TR/skos-reference/}}, and PROV-O\footnote{\url{http://www.w3.org/TR/prov-o/}}) are reused to a large extend \cite{Bosch2013} in order to enable a full data documentation, which is necessary for discovering such data.
-
 In this tutorial, an introduction to Disco and its inter-connections to these vocabularies is provided. 
-It is presented how these connections can be used in order to publish highly complex data sets.
+It is presented how these connections can be used in order to publish complex domain-specific data sets.
 In different real world use cases and by building a data set serving as running example, the presenters of the tutorial demonstrate the adoption and inclusion of Disco in existing information systems.
-During practical exercises, participants will have the possibility to elaborate an RDF representation of the running example or their own data sets and to formulate typical queries.
-Participants are encouraged to present their own data sets and use cases where Disco has been applied or will be used. 
-This tutorial addresses Linked Data developers (beginners and experts) who want to publish Linked Data sets based on complex data like person-level data where essential information like provenance, data aggregates and data catalogs is necessary.
+%During practical exercises, participants will have the possibility to elaborate an RDF representation of the running example or their own data sets and to formulate typical queries.
+Participants are encouraged to present their own data sets and use cases where Disco may been applied.
 
@@
 This makes Disco more difficult to be adopted by developers who may not be familiar with the domain-specific background of person-level or similar data.
-However, since the number of organizations that aim to publish their data as Linked Data grows and the number of Linked Data researchers that want to use real-world data grows, a tutorial on representing such inter-connected data sets may be a beneficial addition for the audience of ISWC 2015.
+However, since the number of organizations that aim to publish their data as Linked Data grows and the number of Linked Data researchers that want to use real-world data grows, a tutorial on representing such inter-connected domain-specific data sets may be a beneficial addition for the audience of ISWC 2015.
+This tutorial addresses Linked Data developers (beginners and experts) who want to publish Linked Data sets based on complex data like person-level data where essential information like provenance, data aggregates and data catalogs is necessary.
 
 \textbf{Previous Versions or Related Tutorials.}
-Thomas Bosch and Benjamin Zapilko held a half-day tutorial at the EDDI14 – 6th Annual European DDI User Conference in London\footnote{\url{http://www.eddi-conferences.eu/ocs/index.php/eddi/eddi14/schedConf/program}}.
+Benjamin Zapilko and Thomas Bosch held a half-day tutorial at the EDDI14 – 6th Annual European DDI User Conference in London\footnote{\url{http://www.eddi-conferences.eu/ocs/index.php/eddi/eddi14}}.
 The tutorial was well received and the presenters got overall positive feedback.
-Since the audience of Disco is two-fold - data professionals and the DDI community at the one hand and Linked Data experts at the other hand - the idea was to offer this tutorial at the ISWC conference as well in order to address the the Linked Data community.
+Since the audience of Disco is two-fold - data professionals and the DDI community at the one hand and Linked Data experts at the other hand - the idea was to offer this tutorial at the ISWC conference as well in order to address the Linked Data community in particular.
 %At the EDDI conference, the first part of the audience - data professionals and the DDI community - was addressed.
@@
 
-\section{Tutorial Description}
+\section{Detailed Description}
 
@@
 
-For a publication of DDI metadata or similar metadata as Linked Data, additional established RDF vocabularies (e.g.
+For a publication of domain-specific metadata as Linked Data, additional established RDF vocabularies (e.g.
 RDF Data Cube, DCAT, SKOS, PROV-O, XKOS, and PHDD) are reused to a large extend.
@@
 
-When publishing data sets, their validation is a necessary requirement.
+%When publishing data sets, their validation is a necessary requirement.
 %Existing DDI instances are stored in form of XML documents and validated against XML Schemas\footnote{XML Schemas of current DDI version available at \url{http://www.ddialliance.org/Specification/DDI-Lifecycle/3.2/XMLSchema/}}.
@@
 %For RDF, 
-While XML Schema is the standard constraint language to validate XML documents, there is no standard language for RDF validation.
-However, there are multiple candidates for languages to express constraints on RDF data.
-In 2014, two working groups on RDF validation have been established addressing these issues: the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles working group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
+%While XML Schema is the standard constraint language to validate XML documents, there is no standard language for RDF validation.
+%However, there are multiple candidates for languages to express constraints on RDF data.
+%In 2014, two working groups on RDF validation have been established addressing these issues: the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles working group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
 %These working groups address the formulation and validation of RDF constraints.
-We will describe typical metadata constraints of Disco data sets as well as how to formulate them using different constraint languages such as OWL 2 and to validate them.
+%We will describe typical metadata constraints of Disco data sets as well as how to formulate them using different constraint languages such as OWL 2 and to validate them.
 %We will show how to formulate these constraints by different constraint languages such as OWL 2.
@@
 Finally, since Disco is already being adopted in the DDI community, we aim to increase the use of Disco in the Linked Data community.
-The learning objectives of this tutorial are the following: (1) introducing Disco, PHDD, and XKOS for modeling complex person-level data, (2) representing the interplay of Disco data with existing and established vocabularies like RDF Data Cube, DCAT, and PROV-O, and (3) the validation of Disco.
+The learning objectives of this tutorial are the following: (1) introducing Disco, PHDD, and XKOS for modeling complex person-level data, and (2) representing the interplay of Disco data with existing and established vocabularies like RDF Data Cube, DCAT, and PROV-O.
 
@@
 The scope of the tutorial covers the introduction of the Disco vocabulary, its connected vocabularies PHDD and XKOS as well as their interplay with other established vocabularies.
-Additionally, the validation of Disco data sets will be covered.
+%Additionally, the validation of Disco data sets will be covered.
 Slides of a previous tutorial\footnote{tutorial slides avaliable at: \url{http://de.slideshare.net/boschthomas/201412-lets-disco-eddi-2014} and \url{http://de.slideshare.net/boschthomas/201412-lets-disco-2-eddi-2014}}
@@
 
-\section{\textcolor{red}{Tutorial Length}}
-
-We propose a full-day tutorial.
-In a previous tutorial about Disco, we experienced that a half-day tutorial offers only enough time to cover the most important aspects about Disco and to include few hands-on exercises.
-Since we now want to expand the focus of the tutorial to the interplay of Disco with other vocabularies and its validation, a full-day seems to be appropriate.
-Furthermore, we want to offer hands-on exercises again, because they were well received at the last tutorial.
-
-\section{Intended Audiences}
-The intended audience of this tutorial are Linked Data developers - beginners as well as experts - who are interested in modeling and publishing complex and highly inter-connected data sets as Linked Data.
+\section{Audience}
+The intended audience of this tutorial are Linked Data developers - beginners as well as experts - who are interested in modeling and publishing complex domain-specific and highly inter-connected data sets as Linked Data.
 Since the connection with other vocabularies like RDF Data Cube, DCAT and PROV-O plays a major role in this context, the tutorial is not restricted to participants who are interested in person-level or similar data.
 
-\section{Tutoring Team}
+\section{Presenters}
 
 %short bios of the presenters, including previous training and public speaking experience (e.g., teaching in English, conference presentations, tutorials etc.)
+
+\textbf{Benjamin Zapilko} is a postdoctoral researcher and lead of the team Data Linking at the GESIS department Knowledge Technologies for the Social Sciences (WTS).
+He holds a degree in computer science and finished his doctoral research on publishing and matching of Linked Open Data in the application area of the social sciences at Mannheim University in early 2015.
+His research interests focus on the domain-specific application of semantic technologies and Linked Open Data.
+He presented his work at several international conferences and workshops.
+Benjamin Zapilko is member of the RDF Vocabularies Working Group of the DDI Alliance and co-organizer of the Library Track at the Ontology Alignment Evaluation Initiative (OAEI) since 2012.
+Together with Thomas Bosch, he held a tutorial about Disco at the EDDI14 – 6th Annual European DDI User Conference\footnote{\url{http://www.eddi-conferences.eu/ocs/index.php/eddi/eddi14}} in 2014.
+
+\begin{itemize}
+\item primary contact person 
+ \item affiliation: GESIS - Leibniz Institute for the Social Sciences
+  \item email address: benjamin.zapilko@gesis.org
+	\item homepage: \url{http://www.gesis.org/}
+\end{itemize}
 
@@
 \begin{itemize}
-  \item affiliation: Gesis - Leibniz Institute for the Social Sciences
+  \item affiliation: GESIS - Leibniz Institute for the Social Sciences
   \item email address: thomas.bosch@gesis.org
-	\item homepage: \url{http://boschthomas.blogspot.com/}; \url{www.gesis.org}
-\end{itemize}
-
-\textbf{Benjamin Zapilko} holds a degree in Computer Science and has recently finished his PhD thesis about methods for matching social science relevant Linked Data.
-The defense talk will be at the end of January.
-Beside his PhD research, he works on modelling and publishing social science relevant data as Linked Data with the focus on data modelling and integration of heterogeneous data sources and information types.
-He presented his work at several international conferences.
-
-\begin{itemize}
-  \item affiliation: Gesis - Leibniz Institute for the Social Sciences
-  \item email address: benjamin.zapilko@gesis.org
-	\item homepage: \url{www.gesis.org}
-	\item primary contact person
+	\item homepage: \url{http://boschthomas.blogspot.com/}; \url{http://www.gesis.org/}
 \end{itemize}
@@
 \begin{itemize}
-  \item affiliation: Gesis - Leibniz Institute for the Social Sciences
+  \item affiliation: GESIS - Leibniz Institute for the Social Sciences
   \item email address: joachim.wackerow@gesis.org
-	\item homepage: \url{www.gesis.org}
+	\item homepage: \url{http://www.gesis.org/}
 \end{itemize}
+
+%\section{\textcolor{red}{Tutorial Length}}
+
+%We propose a full-day tutorial.
+In a previous tutorial about Disco, we experienced that a half-day tutorial offers only enough time to cover the most important aspects about Disco and to include few hands-on exercises.
+Since we now want to expand the focus of the tutorial to the interplay of Disco with other vocabularies and its validation, a full-day seems to be appropriate.
+Furthermore, we want to offer hands-on exercises again, because they were well received at the last tutorial.
+
+\section{Requirements}
+
+Besides a beamer and wifi access, there are no additional requirements for the tutorial.
+In case wifi access may not be availabe or interupted, the intended hands on sessions will be presented on a locally installed triple store.
 

### 2015-03-16 paper/ISWC 2015 Tutorial/ISWC-2015-tutorial.tex
presenters

@@
 
-\textbf{Thomas Bosch} studied information systems, holds a degree in Computer Science (M.Sc.), and is currently a PhD student.
+\textbf{Thomas Bosch} studied information systems, holds a degree in Computer Science (M.Sc.), and is currently a PhD student in Computer Science.
 His research topic is all about RDF validation.
-More specifically, he investigates how to validate any RDF constraints (formulated by multiple constraint languages) and how to express them generically. 
-He held multiple presentations at international conferences and workshops (e.g. WWW, ISWC, DC, Dagstuhl seminars).
+He investigates how to validate any RDF constraints (formulated by arbitrary constraint languages) and how to express them generically. 
+He presented his work at international conferences and workshops (e.g. WWW, ISWC, DC, and Dagstuhl seminars). 
+Thomas Bosch is member of the RDF Vocabularies Working Group\footnote{\url{http://www.ddialliance.org/alliance/working-groups#RDF}} of the DDI Alliance,
+part of the editorial board of the  DCMI RDF Application Profiles Task Group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}, 
+editor of the specifications DDI-RDF Discovery Vocabulary (Disco)\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}}
+and Physical Data Description (PHDD)\footnote{A vocabulary to represent data in a rectangular format in RDF; \url{https://github.com/linked-statistics/physical-data-description}},
+and contributes to the W3C RDF Data Shapes Working Group\footnote{\url{http://www.w3.org/2014/data-shapes/charter}}.
 

### 2015-03-16 paper/paper7/paper7-appendix.tex
presenters

@@
 	The only components of a \emph{qb:DataStructureDefinition} that may be marked as optional, using \emph{qb:componentRequired} are attributes. 
+	\begin{itemize}
+		\item severity level: WARNING
+	\end{itemize}
 	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-02:}}
+	Slice Keys consistent with DSD (\emph{IC-8} \cite{CyganiakReynolds2014}) -
+	Every \emph{qb:componentProperty} on a \emph{qb:SliceKey} must also be declared as a \emph{qb:component} of the associated \emph{qb:DataStructureDefinition}. 
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-03:}} 
+	Slice dimensions complete (\emph{IC-10} \cite{CyganiakReynolds2014}) - 
+	Every \emph{qb:Slice} must have a value for every dimension declared in its \emph{qb:sliceStructure}. 
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+		\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-04:}}
+	All dimensions required (\emph{IC-11} \cite{CyganiakReynolds2014}) - 
+	Every \emph{qb:Observation} has a value for each dimension declared in its associated \emph{qb:DataStructureDefinition}. 
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+		\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05:}}
 	No duplicate observations (\emph{IC-12} \cite{CyganiakReynolds2014}) - 
 	No two \emph{qb:Observations} in the same \emph{qb:DataSet} may have the same value for all dimensions. 
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-03:}}
-	Slice Keys consistent with DSD (\emph{IC-8} \cite{CyganiakReynolds2014}) -
-	Every \emph{qb:componentProperty} on a \emph{qb:SliceKey} must also be declared as a \emph{qb:component} of the associated \emph{qb:DataStructureDefinition}. 
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-04:}}
+	\begin{itemize}
+		\item severity level: WARNING
+	\end{itemize}
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-06:}}
 	Required attributes (\emph{IC-13} \cite{CyganiakReynolds2014}) -
 	Every \emph{qb:Observation} has a value for each declared attribute that is marked as required. 
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05:}}
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-07:}}
 	All measures present (\emph{IC-14} \cite{CyganiakReynolds2014}) -
 	In a \emph{qb:DataSet} which does not use a Measure dimension then each individual \emph{qb:Observation} must have a value for every declared measure. 
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-06:}}
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-08:}}
 	Measure dimension consistent (\emph{IC-15} \cite{CyganiakReynolds2014}) -
 	In a \emph{qb:DataSet} which uses a Measure dimension then each qb:Observation must have a value for the measure corresponding to its given \emph{qb:measureType}. 
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-07:}}
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-09:}}
 	Single measure on measure dimension observation (\emph{IC-16} \cite{CyganiakReynolds2014}) -
 	In a \emph{qb:DataSet} which uses a Measure dimension then each \emph{qb:Observation} must only have a value for one measure (by \emph{IC-15} this will be the measure corresponding to its \emph{qb:measureType}).
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-08:}}
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-10:}}
 	All measures present in measures dimension cube (\emph{IC-17} \cite{CyganiakReynolds2014}) -
 	In a \emph{qb:DataSet} which uses a Measure dimension then if there is a Observation for some combination of non-measure dimensions then there must be other Observations with the same non-measure dimension values for each of the declared measures.
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-09:}}
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-11:}}
 	Consistent data set links (\emph{IC-18} \cite{CyganiakReynolds2014}) -
 	If a \emph{qb:DataSet} \emph{D} has a \emph{qb:slice} \emph{S}, and \emph{S} has an \emph{qb:observation} \emph{O}, then the \emph{qb:dataSet} corresponding to \emph{O} must be \emph{D}. 
+	\begin{itemize}
+		\item severity level: WARNING
+	\end{itemize}
 \end{itemize}
@@
 	Every dimension declared in a \emph{qb:DataStructureDefinition} must have a declared \emph{rdfs:range}. 
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-02:}}
@@
 	Every dimension with range \emph{skos:Concept} must have a \emph{qb:codeList}. 
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
   \item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-03:}}
-	Slice dimensions complete (\emph{IC-10} \cite{CyganiakReynolds2014}) - 
-	Every \emph{qb:Slice} must have a value for every dimension declared in its \emph{qb:sliceStructure}. 
-	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-04:}}
-	All dimensions required (\emph{IC-11} \cite{CyganiakReynolds2014}) - 
-	Every \emph{qb:Observation} has a value for each dimension declared in its associated \emph{qb:DataStructureDefinition}. 
-  \item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-05:}}
 	DSD includes measure (\emph{IC-3} \cite{CyganiakReynolds2014}) -  
 	Every \emph{qb:DataStructureDefinition} must include (\emph{qb:component}, \emph{qb:componentProperty}) at least one declared measure. 
-	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-06:}}
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DATA-CUBE-C-EXISTENTIAL-QUANTIFICATIONS-04	:}}
 	Slice Keys must be declared (\emph{IC-7} \cite{CyganiakReynolds2014}) -
 	Every \emph{qb:SliceKey} must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}). 
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 	If a dimension property has a \emph{qb:codeList}, then the value of the dimension property on every \emph{qb:Observation} must be in the code list. 
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 	The RDF graph must be consistent under RDF D-entailment using a datatype map containing all the datatypes used within the graph. 
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 	If a dimension property has a \emph{qb:HierarchicalCodeList} with a non-blank \emph{qb:parentChildProperty} then the value of that dimension property on every \emph{qb:Observation} must be reachable from a root of the hierarchy using zero or more hops along the \emph{qb:parentChildProperty} links.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 	\item \textbf{{\em DATA-CUBE-C-STRUCTURE-02:}}
@@
 	If a dimension property has a \emph{qb:HierarchicalCodeList} with an inverse \emph{qb:parentChildProperty} then the value of that dimension property on every \emph{qb:Observation} must be reachable from a root of the hierarchy using zero or more hops along the inverse \emph{qb:parentChildProperty} links.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}

### 2015-03-16 paper/paper7/paper7-evaluation.tex
presenters

@@
 \begin{itemize}
+  \item Microdata Information System (Missy)
 	\item DwB Resource Discovery Portal
@@
     \item Search interface: \url{http://dwb-dev.nsd.uib.no/portal/#/search?q=smoking&p=1&s=score&d=desc&f=text}
+	\end{itemize}
+	\item DDA and SND SPARQL endpoint\footnote{\url{http://ddi-rdf.borsna.se/}} 
+	\begin{itemize}
+		\item triples: 2,271,415
+		\item studies: 1,490
+		\item universes: 10,188
+		\item questions: 139,237
+		\item variables: 80,070
 	\end{itemize}
@@
 
+\section{XKOS}
+
+\begin{itemize}
+	\item Nomenclature d'activités française (NAF)\footnote{\url{http://rdf.insee.fr/codes/index.html}}: French classification expressed in XKOS.
+the French refinement of the NACE, because it has explanatory notes.
+	\item Nomenclature des Professions et Catégories Socioprofessionnelles (PCS)\footnote{\url{http://rdf.insee.fr/codes/index.html}}: French classification expressed in XKOS.
+	\item Nomenclature des catégories juridiques (CJ)\footnote{\url{http://rdf.insee.fr/codes/index.html}}: French classification expressed in XKOS.
+	\item ISIC: has explanatory notes too. 
+	\item ISCO
+\end{itemize}
+
 \bibliography{../../literature/literature}{}

### 2015-03-17 paper/ISWC 2015 Tutorial/ISWC-2015-tutorial.tex
final version

@@
 The DDI-RDF Discovery Vocabulary (Disco) is an RDF Schema vocabulary that enables the representation of person-level data sets and related metadata.
-It is based on DDI (Data Documentation Initiative) which is a structured metadata standard related to the observation and measurement of human activity.
+It is based on DDI (Data Documentation Initiative) which is a metadata standard related to the observation and measurement of human activity.
 %Disco is intended to provide means to describe person-level data by essential metadata for the discovery purpose. 
 %Using Disco, such data sets can be discovered in the Web of Linked Data by using RDF technologies, e.g. searching for specific questions, topics, and geographical coverage. 
-Using Disco, such data sets which are frequently used in different domains like the social, ecomical and behavoural sciences can be published as Linked Data. 
+Using Disco, such data sets which are often used in different domains like the social, ecomical and behavoural sciences can be published as Linked Data. 
 However, for a meaningful and complete publication of these data sets, additional established RDF vocabularies (e.g. RDF Data Cube, DCAT, SKOS, PROV-O, XKOS, and PHDD) are reused to a large extend. 
-This combined usage enables the creation of data repositories providing metadata of data collections, data sets, relationships between them and related provenance information. 
+This combination allows for expressing information on metadata of data collections, single data sets, relationships between them, different versions of them and related provenance information. 
 In this tutorial, we show how Disco is interwoven with these vocabularies and how these connections can be used in order to publish complex and domain-specific data sets.
@@
 The DDI-RDF Discovery Vocabulary (Disco) \cite{Bosch2012} is an RDF Schema vocabulary which can be utilized to represent person-level data sets and related metadata as Linked Data. 
-It is based on the metadata standard DDI (Data Documentation Initiative) which is related to the observation and measurement of human activity and often used in domains like the social, ecomical and behavoural sciences.
+It is based on the metadata standard DDI (Data Documentation Initiative) which enables the representation of the observation and measurement of human activity and which is often used in domains like the social, ecomical and behavoural sciences.
 The metadata of such data can get highly complex by e.g. necessary provenance information and relationships to data aggregates, data collections, and the physical data sources.
 Hence beside Disco, additional widely accepted and adopted RDF vocabularies (e.g.
-RDF Data Cube\footnote{\url{http://www.w3.org/TR/vocab-data-cube/}}, DCAT\footnote{\url{http://www.w3.org/TR/vocab-dcat/}}, SKOS\footnote{\url{http://www.w3.org/TR/skos-reference/}}, and PROV-O\footnote{\url{http://www.w3.org/TR/prov-o/}}) are reused to a large extend \cite{Bosch2013} in order to enable a full data documentation, which is necessary for discovering such data.
-In this tutorial, an introduction to Disco and its inter-connections to these vocabularies is provided. 
+RDF Data Cube\footnote{\url{http://www.w3.org/TR/vocab-data-cube/}}, DCAT\footnote{\url{http://www.w3.org/TR/vocab-dcat/}}, SKOS\footnote{\url{http://www.w3.org/TR/skos-reference/}}, and PROV-O\footnote{\url{http://www.w3.org/TR/prov-o/}}) are reused to a large extend \cite{Bosch2013} in order to enable a full data documentation, which is necessary to represent such data in full extent.
+In this tutorial, an introduction to Disco and its inter-connections to these vocabularies is given. 
 It is presented how these connections can be used in order to publish complex domain-specific data sets.
@@
 %During practical exercises, participants will have the possibility to elaborate an RDF representation of the running example or their own data sets and to formulate typical queries.
-Participants are encouraged to present their own data sets and use cases where Disco may been applied.
+Participants are encouraged to present their own data sets and use cases where Disco may be applied.
 
@@
 However, since the number of organizations that aim to publish their data as Linked Data grows and the number of Linked Data researchers that want to use real-world data grows, a tutorial on representing such inter-connected domain-specific data sets may be a beneficial addition for the audience of ISWC 2015.
-This tutorial addresses Linked Data developers (beginners and experts) who want to publish Linked Data sets based on complex data like person-level data where essential information like provenance, data aggregates and data catalogs is necessary.
+This tutorial addresses Linked Data developers (beginners and experts) who want to publish Linked Data sets based on person-level or similar data as well as researchers who want to use such data sets for their research.
 
@@
 The tutorial was well received and the presenters got overall positive feedback.
-Since the audience of Disco is two-fold - data professionals and the DDI community at the one hand and Linked Data experts at the other hand - the idea was to offer this tutorial at the ISWC conference as well in order to address the Linked Data community in particular.
+Since the audience of Disco is two-fold - data professionals and the DDI community at the one hand and the Linked Data community at the other hand - the idea was to offer this tutorial at the ISWC conference as well in order to address the Linked Data community in particular.
 %At the EDDI conference, the first part of the audience - data professionals and the DDI community - was addressed.
@@
 These connections enable the representation of various relevant aspects, e.g.
-aggregate data derived from person-level data (micro data) by RDF Data Cube, PROV-O and Disco, data collections and catalogs (together with DCAT), and data (tables) in a rectangular format by using PHDD.
+aggregate data derived from person-level data (also known as micro data) by the RDF Data Cube vocabulary, PROV-O and Disco, data collections and catalogs (together with DCAT), and data (tables) in a rectangular format by using PHDD.
 XKOS can be used to represent statistical classifications.
@@
 The main objective of this tutorial is to introduce Disco and to provide assistence for creating Linked Data sets using Disco.
-Person-level or similar metadata is not restricted to a particular domain and may be an interesting data source for Linked Data developers.
+Person-level or similar metadata is not restricted to a particular domain and may be an interesting data source for Linked Data developers and researchers.
 Because of the complexity that comes along with such data, we especially want to demonstrate how Disco data sets can be connected with information represented using other existing vocabularies that are relevant in that context.
@@
 Material for the practical exercises will be provided by the presenters (see Section 2.6).
-During the tutorial, one complex data set will be built, which serves as ongoing running example.
-In all sessions, there will be practical exercises where the participants are asked to model and query particular parts of the example data sets.
+During the tutorial, one complex data set will be built, which serves as running example.
+There will be practical exercises where the participants are asked to model particular parts of the example data sets.
 The infrastructure for these exercises, i.e.
@@
 \section{Audience}
-The intended audience of this tutorial are Linked Data developers - beginners as well as experts - who are interested in modeling and publishing complex domain-specific and highly inter-connected data sets as Linked Data.
+The intended audience of this tutorial is Linked Data developers - beginners as well as experts - who are interested in modeling and publishing complex domain-specific and highly inter-connected data sets as Linked Data.
+Additionally, we address researchers who want to use such data sets for, e.g., running reasoning or matching algorithms.
 Since the connection with other vocabularies like RDF Data Cube, DCAT and PROV-O plays a major role in this context, the tutorial is not restricted to participants who are interested in person-level or similar data.
+Experiences from our last tutorial have shown that the size of a school class (15-30 persons) seems to be a reasonable number of participants.
+However, depending on the number of participants we are able to adjust the proportion of the practical session in order to avoid losing too much time by conducting the exercises.
 
@@
 Besides a beamer and wifi access, there are no additional requirements for the tutorial.
-In case wifi access may not be availabe or interupted, the intended hands on sessions will be presented on a locally installed triple store.
+In case wifi access may not be available or interrupted, the intended hands on sessions will be presented on a locally installed triple store.
 

### 2015-03-17 paper/ISWC 2015 Tutorial/ISWC-2015-tutorial.tex
Last changes

@@
 %
-\title{Let’s Disco – Publishing person-level data as Linked Data.}
-\subtitle{Building domain-specific Data Sets with Disco, PHDD, XKOS and widely used Vocabularies.
+\title{Let’s Disco – Publishing person-level data as Linked Data}
+\subtitle{Building domain-specific Data Sets with Disco, PHDD, XKOS and widely used Vocabularies
 }
@@
 It is based on DDI (Data Documentation Initiative) which is a metadata standard related to the observation and measurement of human activity.
-%Disco is intended to provide means to describe person-level data by essential metadata for the discovery purpose. 
-%Using Disco, such data sets can be discovered in the Web of Linked Data by using RDF technologies, e.g. searching for specific questions, topics, and geographical coverage. 
 Using Disco, such data sets which are often used in different domains like the social, ecomical and behavoural sciences can be published as Linked Data. 

### 2015-03-17 paper/ISWC 2015 Tutorial/ISWC-2015-tutorial.tex
last fix

@@
 It is based on DDI (Data Documentation Initiative) which is a metadata standard related to the observation and measurement of human activity.
-Using Disco, such data sets which are often used in different domains like the social, ecomical and behavoural sciences can be published as Linked Data. 
+Using Disco, such data sets which are often used in different domains like the social, ecomical and behavioral sciences can be published as Linked Data. 
 However, for a meaningful and complete publication of these data sets, additional established RDF vocabularies (e.g. RDF Data Cube, DCAT, SKOS, PROV-O, XKOS, and PHDD) are reused to a large extend. 
@@
 The DDI-RDF Discovery Vocabulary (Disco) \cite{Bosch2012} is an RDF Schema vocabulary which can be utilized to represent person-level data sets and related metadata as Linked Data. 
-It is based on the metadata standard DDI (Data Documentation Initiative) which enables the representation of the observation and measurement of human activity and which is often used in domains like the social, ecomical and behavoural sciences.
+It is based on the metadata standard DDI (Data Documentation Initiative) which enables the representation of the observation and measurement of human activity and which is often used in domains like the social, ecomical and behavioral sciences.
 The metadata of such data can get highly complex by e.g. necessary provenance information and relationships to data aggregates, data collections, and the physical data sources.

### 2015-03-17 paper/ISWC 2015 Tutorial/ISWC-2015-tutorial.tex
jetzt aber :)

@@
 Using Disco, such data sets which are often used in different domains like the social, ecomical and behavioral sciences can be published as Linked Data. 
-However, for a meaningful and complete publication of these data sets, additional established RDF vocabularies (e.g. RDF Data Cube, DCAT, SKOS, PROV-O, XKOS, and PHDD) are reused to a large extend. 
+However, for a meaningful and complete publication of these data sets, additional established RDF vocabularies (e.g. RDF Data Cube, DCAT, SKOS, PROV-O, XKOS, and PHDD) are reused to a large extent. 
 This combination allows for expressing information on metadata of data collections, single data sets, relationships between them, different versions of them and related provenance information. 
@@
 Hence beside Disco, additional widely accepted and adopted RDF vocabularies (e.g.
-RDF Data Cube\footnote{\url{http://www.w3.org/TR/vocab-data-cube/}}, DCAT\footnote{\url{http://www.w3.org/TR/vocab-dcat/}}, SKOS\footnote{\url{http://www.w3.org/TR/skos-reference/}}, and PROV-O\footnote{\url{http://www.w3.org/TR/prov-o/}}) are reused to a large extend \cite{Bosch2013} in order to enable a full data documentation, which is necessary to represent such data in full extent.
+RDF Data Cube\footnote{\url{http://www.w3.org/TR/vocab-data-cube/}}, DCAT\footnote{\url{http://www.w3.org/TR/vocab-dcat/}}, SKOS\footnote{\url{http://www.w3.org/TR/skos-reference/}}, and PROV-O\footnote{\url{http://www.w3.org/TR/prov-o/}}) are reused to a large extent \cite{Bosch2013} in order to enable a full data documentation, which is necessary to represent such data in full extent.
 In this tutorial, an introduction to Disco and its inter-connections to these vocabularies is given. 
@@
 For a publication of domain-specific metadata as Linked Data, additional established RDF vocabularies (e.g.
-RDF Data Cube, DCAT, SKOS, PROV-O, XKOS, and PHDD) are reused to a large extend.
+RDF Data Cube, DCAT, SKOS, PROV-O, XKOS, and PHDD) are reused to a large extent.
 It is shown how Disco is interwoven with these vocabularies.

### 2015-03-18 paper/ISWC 2015 Tutorial/ISWC-2015-tutorial.tex
typo fixing

@@
 It is based on DDI (Data Documentation Initiative) which is a metadata standard related to the observation and measurement of human activity.
-Using Disco, such data sets which are often used in different domains like the social, ecomical and behavioral sciences can be published as Linked Data. 
+Using Disco, such data sets which are often used in different domains like the social, economic and behavioral sciences can be published as Linked Data. 
 However, for a meaningful and complete publication of these data sets, additional established RDF vocabularies (e.g. RDF Data Cube, DCAT, SKOS, PROV-O, XKOS, and PHDD) are reused to a large extent. 
@@
 The DDI-RDF Discovery Vocabulary (Disco) \cite{Bosch2012} is an RDF Schema vocabulary which can be utilized to represent person-level data sets and related metadata as Linked Data. 
-It is based on the metadata standard DDI (Data Documentation Initiative) which enables the representation of the observation and measurement of human activity and which is often used in domains like the social, ecomical and behavioral sciences.
+It is based on the metadata standard DDI (Data Documentation Initiative) which enables the representation of the observation and measurement of human activity and which is often used in domains like the social, economic and behavioral sciences.
 The metadata of such data can get highly complex by e.g. necessary provenance information and relationships to data aggregates, data collections, and the physical data sources.

### 2015-03-24 paper/paper7/paper7-evaluation.tex
evaluation

--- 2015-03-12 paper/paper7/paper7-evaluation.tex
@@
 
+% tables
+\usepackage{array,graphicx}
+\usepackage{booktabs}
+\usepackage{pifont}
+\newcommand*\rot{\rotatebox{90}}
+\newcommand*\OK{\ding{51}}
+\usepackage{booktabs}
+\newcommand*\ON[0]{$\surd$}
+
+\usepackage{tablefootnote}
+
+\usepackage{float}
+
 \begin{document}
@@
 
+\section{Evaluation}
+
+\subsection{Legend}
+
+\begin{table}
+	\centering
+		\begin{tabular}{c|l}
+      \textbf{Symbol} & \textbf{Description} \\		
+			\emph{X} & \textbf{Validation Successful} \\
+			\hline
+			\textbf{\textgreater} \emph{X} & \textbf{Poor Performance/Scaling} \\
+			\hline
+      \ding{55} & \textbf{Very Poor Performance/Scaling} \\
+			\hline
+			$\dagger$ & \textbf{SPARQL Endpoint Error}
+		\end{tabular}
+	\caption{Legend}
+	\label{tab:legend}
+\end{table}
+
+\textbf{Validation Successful:} 
+\emph{X} indicates the number of raised constraint violation triples.
+
+\textbf{Poor Performance/Scaling:}
+The performance of the implementation of the underlying SPARQL CONSTRUCT query 
+is too poor to get all resulting constraint violation triples. 
+Therefore, a limit of \emph{X} result constraint violation triples is set. 
+It is likely that there are more than \emph{X} constraint violations.
+Although, the result set contains not the whole set of raised constraint violation triples,
+the constraint can be used as an indicator if there data not conforming to the constraint and
+to resolve constraint violations step by step. 
+As part of future work, the performance will be improved.
+
+\textbf{Very Poor Performance/Scaling:} 
+The performance of the implementation of the underlying SPARQL CONSTRUCT query 
+is too poor to get any results, even though a limit of result constraint violation triples is set. 
+As part of future work, the performance will be improved.
+
 \section{Disco}
@@
 \begin{itemize}
-	\item DwB Resource Discovery Portal
+	\item DwB Discovery Portal
 	\begin{itemize}
@@
 
+\begin{table}[H]
+	\centering
+		\begin{tabular}{l|l}
+      \textbf{Abbr.} & \textbf{Disco Data Sets} \\		
+      \hline
+    Missy & Microdata Information System\tablefootnote{\url{http://www.gesis.org/missy/eu/missy-home}} \\
+		DwB & DwB Discovery Portal\tablefootnote{\url{http://dwb-dev.nsd.uib.no/portal}} \\
+		DDA-SND & DDA and SND DDI-RDF\tablefootnote{\url{http://ddi-rdf.borsna.se/}} \\ 
+		\end{tabular}
+	\caption{Disco Data Sets Abbreviations}
+	\label{tab:disco-data-sets-abbreviations}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccccccccccc@{}}
+           & \multicolumn{9}{c}{\textbf{Counts}}
+    \\  \cmidrule{2-10}
+    \\       \textbf{Data Sets}
+           & \textbf{\rot{triples}}
+           & \textbf{\rot{disco:StudyGroup}}
+           & \textbf{\rot{disco:Study}}
+           & \textbf{\rot{disco:LogicalDataSet}}
+           & \textbf{\rot{disco:Universe}}
+					 & \textbf{\rot{disco:Variable}}
+					 & \textbf{\rot{disco:Question}}
+				   & \textbf{\rot{disco:SummaryStatistics}}
+					 & \textbf{\rot{disco:CategoryStatistics}}
+					 & \textbf{\rot{skos:Concept}}
+    \\ \midrule
+    Missy &  &  &  &  &  & \\
+		DwB & 2,332,802 & 0 & 1,387 & 1,367 & 2,796 & 446,806 & 0 & 0 & 0 & 0 \\
+		DDA-SND & 2,271,415 & 0 & 1,490 & 0 & 10,188 & 80,070 & 139,237 & 0 & 0 & 290,963 \\ 
+    \bottomrule
+    \end{tabular}
+    \caption{Disco Data Sets Overview}
+		\label{tab:disco-overview}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+	\centering
+		\begin{tabular}{l|l}
+      \textbf{Data Sets} & \textbf{SPARQL Endpoint} \\		
+      \hline
+      Missy & \textcolor{red}{XXXXX} \\
+			DwB & \url{http://dwb-dev.nsd.uib.no/sparql} \\
+			DDA-SND & \url{http://ddi-rdf.borsna.se/endpoint/} \\
+		\end{tabular}
+	\caption{Disco SPARQL Endpoints}
+	\label{tab:disco-sparql-endpoints}
+\end{table}
+
 \section{Data Cube}
@@
 \begin{itemize}
-	\item \url{http://270a.info/} (see the VoID which points to other
-VoIDs) is full of data sets (probably close to 10k) using RDF Data Cube,
-and some of those also include XKOS.
+  \item overview over Data Cube data sets\footnote{\url{http://270a.info/}; \url{http://datahub.io/de/dataset?tags=format-qb}} 
+  \item \url{http://ontologycentral.com/}
 \end{itemize}
+
+%\begin{table}
+	%\centering
+		%\begin{tabular}{l|c|c|c|c|c|c}
+      %\textbf{Data Set} & \textbf{triples} & \textbf{data sets} & \textbf{data structure definitions} & \textbf{observations} & \textbf{slices} & \textbf{dimensions} \\		
+      %\hline
+      %European Central Bank (ECB)\tablefootnote{\url{http://www.ecb.europa.eu/home/html/index.en.html}} &  &  &  &  &  &  \\
+			%UNESCO Institute for Statistics (UIS)\tablefootnote{\url{http://www.uis.unesco.org/Pages/default.aspx}} &  &  &  &  &  &  \\
+			%International Monetary Fund (IMF)\tablefootnote{\url{http://www.imf.org/external/index.htm}} &  &  &  &  &  &  \\
+			%Bundesamt für Statistik - Swiss Federal Statistics (BFS)\tablefootnote{\url{http://www.bfs.admin.ch/}} &  &  &  &  &  &  \\
+			%Food and Agriculture Organization of the United Nations (FAO)\tablefootnote{\url{http://www.fao.org/home/en/}} &  &  &  &  &  &  \\
+			%World Bank (WB)\tablefootnote{\url{http://www.worldbank.org/}} &  &  &  &  &  &  \\
+			%Federal Reserve Board (FRB)\tablefootnote{\url{http://www.federalreserve.gov/}} &  &  &  &  &  &  \\
+			%Transparency International (TI)\tablefootnote{\url{http://www.transparency.org/}} &  &  &  &  &  &  \\
+			%Organisation for Economic Co-operation and Development (OECD)\tablefootnote{\url{http://www.oecd.org/}} &  &  &  &  &  &  \\
+			%Bank for International Settlements (BIS)\tablefootnote{\url{http://www.bis.org/}} &  &  &  &  &  &  \\
+			%Australian Bureau of Statistics (ABS)\tablefootnote{\url{http://abs.gov.au/}} &  &  &  &  &  &  \\
+		%\end{tabular}
+	%\caption{Data Cube Data Sets}
+	%\label{tab:data-cube-data-sets}
+%\end{table}
+
+\begin{table}[H]
+	\centering
+		\begin{tabular}{l|l}
+      \textbf{Abbr.} & \textbf{Data Cube Data Sets} \\		
+      \hline
+    ECB & European Central Bank\tablefootnote{\url{http://www.ecb.europa.eu/home/html/index.en.html}} \\
+		UIS & UNESCO Institute for Statistics\tablefootnote{\url{http://www.uis.unesco.org/Pages/default.aspx}} \\
+		IMF & International Monetary Fund\tablefootnote{\url{http://www.imf.org/external/index.htm}} \\
+		BFS & Bundesamt für Statistik - Swiss Federal Statistics\tablefootnote{\url{http://www.bfs.admin.ch/}} \\
+		FAO & Food and Agriculture Organization of the United Nations\tablefootnote{\url{http://www.fao.org/home/en/}} \\
+		WB & World Bank\tablefootnote{\url{http://www.worldbank.org/}} \\
+		FRB & Federal Reserve Board\tablefootnote{\url{http://www.federalreserve.gov/}} \\
+		TI & Transparency International\tablefootnote{\url{http://www.transparency.org/}} \\
+		OECD & Organisation for Economic Co-operation and Development\tablefootnote{\url{http://www.oecd.org/}} \\
+		BIS & Bank for International Settlements\tablefootnote{\url{http://www.bis.org/}} \\
+		ABS & Australian Bureau of Statistics\tablefootnote{\url{http://abs.gov.au/}} \\
+		IEEE-VIS & IEEE VIS Source Data \\
+		ACORN-SAT & Australian Climate Observations Reference Network - Surface Air Temperature Dataset \\
+		HDP & HealthData.gov Platform (HDP) on the Semantic Web \\
+		Eurostat & The Eurostat Linked Data  \\
+		Asturias & Nomenclator Asturias \\
+		ISTAT & ISTAT Immigration (LinkedOpenData.it) \\
+		ICANE & Statistical Office of Cantabria (Instituto Cántabro de Estadística, ICANE) \\
+		EE-2009 & European Election Results 2009 \\
+		EU-B & Standard Eurobarometer \\
+		ECB-S & European Central Bank Statistics (PublicData.eu) \\
+		CPV-2008 & Common Procurement Vocabulary (CPV) 2008 \\
+		CPV-2003 & Common Procurement Vocabulary (CPV) 2003 \\
+		GHI-2011 & Global Hunger Index (GHI) 2011 \\
+		\end{tabular}
+	\caption{Data Cube Data Sets Abbreviations}
+	\label{tab:data-cube-data-sets-abbreviations}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccccccccccc@{}}
+           & \multicolumn{5}{c}{\textbf{Counts}}
+    \\  \cmidrule{2-6}
+    \\       \textbf{Data Sets}
+           & \textbf{\rot{triples}}
+           & \textbf{\rot{qb:DataSet}}
+           & \textbf{\rot{qb:DataStructureDefinition}}
+           & \textbf{\rot{qb:Observation}}
+           & \textbf{\rot{qb:Slice}}
+    \\ \midrule
+    ECB & 468,899,474 & 55 & 46 & $>$11,000,000 & 428,698 \\
+		UIS & 10,400,534 & 5 & 5 & 1,437,651 & 0 &  \\
+		IMF & 35,688,446 & 4 & 8 & 3,603,719 & 0 &  \\
+		BFS & 1,533,743 & 0 & 0 & 8 & 0 &  \\
+		FAO & 53,000,000 & 10 & 10 & $>$7,100,000 & 0 \\
+		WB & 174,006,552 & 9,466 & 59 & $>$17,000,000 & 0 \\
+		FRB & 185,266,900 & 49 & 98 & $>$9,500,000 & 0 \\
+		TI & 52,233 & 6 & 6 & 3,928 & 0 \\
+		OECD & 304,995,160 & 136 & 140 & $>$12,000,000 & 0 \\
+		BIS & 54,197,482 & 6 & 12 & 3,606,466 & 47,914 \\
+		ABS & 2,357,400,000 & 253 & 257 & $>$11,000,000 & 0  \\
+		IEEE-VIS & 19,935,340 & 0 & 0 & 1,350 & 0 \\
+		ACORN-SAT & 61,406,503 &  &  &  &  &  \\
+		HDP & 1,934,046,908 &  &  &  &  &  \\
+		Eurostat & 8,000,000,000 &  &  &  &  &  \\
+		Asturias & 4,508,050 &  &  &  &  &  \\
+		ISTAT & 3,024,396 &  &  &  &  &  \\
+		ICANE & 52,412 &  &  &  &  &  \\
+		EE-2009 & 3,165 &  &  &  &  &  \\
+		EU-B & 1,193,494 &  &  &  &  &  \\
+		ECB-S & 10,000,000 &  &  &  &  &  \\
+		CPV-2008 & 803,311 &  &  &  &  &  \\
+		CPV-2003 & 546,135 &  &  &  &  &  \\
+		GHI-2011 & 19,369 (dump) &  &  &  &  &  \\
+    \bottomrule
+    \end{tabular}
+    \caption{Data Cube Data Sets Overview}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+	\centering
+		\begin{tabular}{l|l}
+      \textbf{Data Sets} & \textbf{SPARQL Endpoints} \\		
+      \hline
+      ECB & \url{http://ecb.270a.info/sparql} \\
+			UIS & \url{http://uis.270a.info/sparql} \\
+			IMF & \url{http://imf.270a.info/sparql} \\
+			BFS & \url{http://bfs.270a.info/sparql} \\
+			FAO & \url{http://fao.270a.info/sparql} \\
+			WB & \url{http://worldbank.270a.info/sparql} \\
+			FRB & \url{http://frb.270a.info/sparql} \\
+			TI & \url{http://transparency.270a.info/sparql} \\
+			OECD & \url{http://oecd.270a.info/sparql} \\
+			BIS & \url{http://bis.270a.info/sparql} \\
+			ABS & \url{http://abs.270a.info/sparql} \\
+		\end{tabular}
+	\caption{Data Cube Data Sets SPARQL Endpoints}
+	\label{tab:data-cube-data-sets-sparql-endpoints}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccccccccccc@{}}
+           & \multicolumn{12}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-13}
+    \\       \textbf{Data Model Consistency}
+           & \rot{ECB}
+           & \rot{UIS}
+           & \rot{IMF}
+           & \rot{BFS}
+           & \rot{FAO}
+					 & \rot{WB}
+					 & \rot{FRB}
+					 & \rot{TI}
+					 & \rot{OECD}
+					 & \rot{BIS}
+					 & \rot{ABS}
+					 & \rot{IEEE-VIS}
+    \\ \midrule
+    DATA-MODEL-CONSISTENCY-01 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    DATA-MODEL-CONSISTENCY-02 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    DATA-MODEL-CONSISTENCY-03 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    DATA-MODEL-CONSISTENCY-04 & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ &  & & & $\checkmark$ \\
+		DATA-MODEL-CONSISTENCY-05 &  &  &  &  &  & & & & & & & $\checkmark$ \\
+		DATA-MODEL-CONSISTENCY-06 &  &  &  &  &  & \\
+		DATA-MODEL-CONSISTENCY-07 &  &  &  &  &  & \\
+		DATA-MODEL-CONSISTENCY-08 &  &  &  &  &  & \\
+		DATA-MODEL-CONSISTENCY-09 &  &  &  &  &  & \\
+		DATA-MODEL-CONSISTENCY-10 &  &  &  &  &  & \\
+		DATA-MODEL-CONSISTENCY-11 &  &  &  &  &  & \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Data Cube Data Sets}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccccccccccc@{}}
+           & \multicolumn{12}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-13}
+    \\       \textbf{Existential Quantifications}
+           & \rot{ECB}
+           & \rot{UIS}
+           & \rot{IMF}
+           & \rot{BFS}
+           & \rot{FAO}
+					 & \rot{WB}
+					 & \rot{FRB}
+					 & \rot{TI}
+					 & \rot{OECD}
+					 & \rot{BIS}
+					 & \rot{ABS}
+					 & \rot{IEEE-VIS}
+    \\ \midrule
+		EXISTENTIAL-QUANTIFICATIONS-01 & 9 & $\checkmark$ & 11 & 7 & 8 & 77 & 8 & 9 & 7 & 8 & 7 & $\checkmark$ \\
+		EXISTENTIAL-QUANTIFICATIONS-02 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		EXISTENTIAL-QUANTIFICATIONS-03 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & 59 & $\checkmark$ & 6 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		EXISTENTIAL-QUANTIFICATIONS-04 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Data Cube Data Sets}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccccccccccc@{}}
+           & \multicolumn{12}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-13}
+    \\       \textbf{Cardinality Restrictions}
+           & \rot{ECB}
+           & \rot{UIS}
+           & \rot{IMF}
+           & \rot{BFS}
+           & \rot{FAO}
+					 & \rot{WB}
+					 & \rot{FRB}
+					 & \rot{TI}
+					 & \rot{OECD}
+					 & \rot{BIS}
+					 & \rot{ABS}
+					 & \rot{IEEE-VIS}
+    \\ \midrule
+		MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01 &  &  &  &  &  & \\
+		EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-01 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-01 & \ding{55} & 118 & 8 & 8 & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ & \ding{55} & 12 & \ding{55} & 1,350 \\
+		EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & 1 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Data Cube Data Sets}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccccccccccc@{}}
+           & \multicolumn{12}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-13}
+    \\       \textbf{Structure}
+           & \rot{ECB}
+           & \rot{UIS}
+           & \rot{IMF}
+           & \rot{BFS}
+           & \rot{FAO}
+					 & \rot{WB}
+					 & \rot{FRB}
+					 & \rot{TI}
+					 & \rot{OECD}
+					 & \rot{BIS}
+					 & \rot{ABS}
+					 & \rot{IEEE-VIS}
+    \\ \midrule
+		STRUCTURE-01 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		STRUCTURE-02 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Data Cube Data Sets}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccccccccccc@{}}
+           & \multicolumn{12}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-13}
+    \\       \textbf{Constraints}
+           & \rot{ECB}
+           & \rot{UIS}
+           & \rot{IMF}
+           & \rot{BFS}
+           & \rot{FAO}
+					 & \rot{WB}
+					 & \rot{FRB}
+					 & \rot{TI}
+					 & \rot{OECD}
+					 & \rot{BIS}
+					 & \rot{ABS}
+					 & \rot{IEEE-VIS}
+    \\ \midrule
+		PROPERTY-DOMAIN-01 &  &  &  &  &  & \\
+		PROPERTY-RANGES-01 &  &  &  &  &  & \\
+		DISJOINT-PROPERTIES-01 &  &  &  &  &  & \\
+		DISJOINT-CLASSES-01 &  &  &  &  &  & \\
+		EQUIVALENT-PROPERTIES-01 &  &  &  &  &  & \\
+		UNIVERSAL-QUANTIFICATIONS-01 &  &  &  &  &  & \\
+		MEMBERSHIP-IN-CONTROLLED-VOCABULARIES-01 &  &  &  &  &  & \\
+		CONTEXT-SPECIFIC-VALID-CLASSES-01 &  &  &  &  &  & \\
+		CONTEXT-SPECIFIC-VALID-PROPERTIES-01 &  &  &  &  &  & \\
+		RECOMMENDED-PROPERTIES-01 &  &  &  &  &  & \\
+		VALUE-IS-VALID-FOR-DATATYPE-01 &  &  &  &  &  & \\
+		VOCABULARY-01 &  &  &  &  &  & \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Data Cube Data Sets}
+    \end{center}
+\end{table}
+
+\section{SKOS}
+
+\begin{itemize}
+  \item overview over SKOS data sets\footnote{\url{http://datahub.io/de/dataset?tags=format-skos}}
+	\item overview over thesauri\footnote{\url{http://datahub.io/de/dataset?tags=thesaurus}} (table \ref{tab:thesauri-overview})
+\end{itemize}
+
+\begin{table}[H]
+	\centering
+		\begin{tabular}{l|l}
+      \textbf{Abbr.} & \textbf{Thesauri} \\		
+      \hline
+    TheSoz & Thesaurus for the Social Sciences\tablefootnote{\url{http://www.ecb.europa.eu/home/html/index.en.html}} \\
+	  STW & Thesaurus for Economics\tablefootnote{\url{http://zbw.eu/stw/versions/latest/about}} \\
+	  AGROVOC & AGROVOC Multilingual agricultural thesaurus\tablefootnote{\url{http://202.45.139.84:10035/catalogs/fao/repositories/agrovoc}} \\
+		UNESCO & UNESCO Thesaurus\tablefootnote{\url{http://skos.um.es/sparql/}} \\
+		TGN & The Getty Thesaurus of Geographic Names\tablefootnote{\url{http://vocab.getty.edu/sparql}} \\
+		EARTh & Environmental Applications Reference Thesaurus\tablefootnote{\url{http://linkeddata.ge.imati.cnr.it/resource/EARTh/}} \\
+		ODT & Open Data Thesaurus\tablefootnote{\url{http://vocabulary.semantic-web.at/PoolParty/wiki/OpenData}} \\
+		SLD & Spanish Linguistic Datasets\tablefootnote{\url{http://linguistic.linkeddata.es}} \\
+		SSWT & Social Semantic Web Thesaurus\tablefootnote{\url{http://vocabulary.semantic-web.at/PoolParty/wiki/semweb}} \\
+		GBA-GU & Thesaurus of the Geological Survey of Austria (GBA) - Geology Unit\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
+		GBA-GTS & Thesaurus of the Geological Survey of Austria (GBA) - Geologic Time Scale\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
+		GBA-L & Thesaurus of the Geological Survey of Austria (GBA) - Lithology\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
+		GBA-LU & Thesaurus of the Geological Survey of Austria (GBA) - Lithotectonic Unit\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
+		GEMET & GEneral Multilingual Environmental Thesaurus\tablefootnote{\url{http://www.eionet.europa.eu/gemet/}} \\
+		EuroVoc & EuroVoc\tablefootnote{\url{http://open-data.europa.eu/de/data/dataset/eurovoc}} \\
+		CECCT & Clean Energy and Climate Change Thesaurus\tablefootnote{\url{http://data.reegle.info/thesaurus/guide}} \\
+		\end{tabular}
+	\caption{Thesauri Abbreviations}
+	\label{tab:thesauri-abbreviations}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccccccccccc@{}}
+           & \multicolumn{6}{c}{\textbf{Counts}}
+    \\  \cmidrule{2-7}
+    \\       \textbf{Thesauri}
+           & \textbf{\rot{triples}}
+           & \textbf{\rot{skos:ConceptScheme}}
+           & \textbf{\rot{sko:Concept}}
+           & \textbf{\rot{skos:broader}}
+           & \textbf{\rot{skos:narrower}}
+					 & \textbf{\rot{skos:hasTopConcept}}
+					 & \textbf{\rot{skos:inScheme}}
+    \\ \midrule
+    TheSoz & 439,153 & 1 & 8,426 & 13,705 & 13,706 & 0 & 48,529 \\
+	  STW & 221,668 & 1 & 13,468 & 13,732 & 13732 & 7 & 13,180 \\
+	  AGROVOC & 6,080,477 & 1 & 32,310 & 33,507 & 33,507 & 25 & 32,310 \\
+		UNESCO & 288,346 & 9 & 26,714 & 20,028 & 20,028 & 607 & 32,009 \\
+		TGN & 16,112,321 & 8 & 2,898,775 & 0 & 0 & 0 & 1,453,767\\
+		EARTh & 9,287,364 &  &  &  & \\
+		ODT & 3,290 &  &  &  & \\
+		SLD & 7,629,211 &  &  &  & \\
+		SSWT & 64,698 &  &  &  & \\
+		GBA-GU & 25,718 &  &  &  & \\
+		GBA-GTS & 7,875 &  &  &  & \\
+		GBA-L & 9,317 &  &  &  & \\
+		GBA-LU & 9,504 &  &  &  & \\
+		GEMET & 372,889,229 &  &  &  & \\
+		EuroVoc & 64,477,774 &  &  &  & \\
+		CECCT & 191,336 &  &  &  & \\
+    \bottomrule
+    \end{tabular}
+    \caption{Thesauri Overview}
+		\label{tab:thesauri-overview}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+	\centering
+		\begin{tabular}{l|l}
+      \textbf{Thesauri} & \textbf{SPARQL Endpoints} \\		
+      \hline
+      TheSoz & \url{http://lod.gesis.org/thesoz/sparql} \\
+			STW & \url{http://zbw.eu/beta/sparql/stw/query} \\
+			AGROVOC & \url{http://202.45.139.84:10035/catalogs/fao/repositories/agrovoc} \\
+			UNESCO & \url{http://skos.um.es/sparql/} \\
+			TGN & \url{http://vocab.getty.edu/} \\
+			EARTh & \url{http://linkeddata.ge.imati.cnr.it:8890/sparql} \\
+			ODT & \url{http://vocabulary.semantic-web.at/PoolParty/sparql/OpenData} \\
+			SLD & \url{http://linguistic.linkeddata.es/sparql} \\
+			SSWT & \url{http://vocabulary.semantic-web.at/PoolParty/sparql/semweb} \\
+			GBA-GU & \url{http://resource.geolba.ac.at/PoolParty/sparql/GeologicUnit} \\
+			GBA-GTS & \url{http://resource.geolba.ac.at/PoolParty/sparql/GeologicTimeScale} \\
+			GBA-L & \url{http://resource.geolba.ac.at/PoolParty/sparql/lithology} \\
+			GBA-LU & \url{http://resource.geolba.ac.at/PoolParty/sparql/tectonicunit} \\
+			GEMET & \url{http://semantic.eea.europa.eu/sparql} \\
+			EuroVoc & \url{http://open-data.europa.eu/de/linked-data} \\
+			CECCT & \url{http://poolparty.reegle.info/PoolParty/sparql/glossary}
+		\end{tabular}
+	\caption{Thesauri SPARQL Endpoints}
+	\label{tab:thesauri-sparql-endpoints}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccccccccccc@{}}
+           & \multicolumn{12}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-13}
+    \\       \textbf{Data Model Consistency}
+           & \rot{TheSoz}
+           & \rot{STW}
+           & \rot{AGROVOC}
+					 & \rot{TGN}
+           & \rot{UNESCO}
+					 & \rot{ODT}
+					 & \rot{SSWT}
+					 & \rot{GBA-GU}
+					 & \rot{GBA-GTS}
+					 & \rot{GBA-L}
+					 & \rot{GBA-LU}
+					 & \rot{CECCT}
+    \\ \midrule
+    DATA-MODEL-CONSISTENCY-01 &  &  &  &  &  & \\
+    DATA-MODEL-CONSISTENCY-02 &  &  &  &  &  & \\
+    DATA-MODEL-CONSISTENCY-03 &  &  &  &  &  & \\
+    \bottomrule
+    \end{tabular}
+    \caption{Thesauri Evaluation}
+		\label{tab:thesauri-evaluation-1}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccccccccccc@{}}
+           & \multicolumn{12}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-13}
+    \\       \textbf{Labeling and Documentation}
+           & \rot{TheSoz}
+           & \rot{STW}
+           & \rot{AGROVOC}
+					 & \rot{TGN}
+           & \rot{UNESCO}
+					 & \rot{ODT}
+					 & \rot{SSWT}
+					 & \rot{GBA-GU}
+					 & \rot{GBA-GTS}
+					 & \rot{GBA-L}
+					 & \rot{GBA-LU}
+					 & \rot{CECCT}
+    \\ \midrule
+		LABELING-AND-DOCUMENTATION-01 & 8,426 & 11,508 & 19,829 & $\checkmark$ & & 36 & 1,475 & 6 & 2 & $\checkmark$ & 107 & 486 \\
+		LABELING-AND-DOCUMENTATION-02 & $>$1 & \ding{55} & $>$100 & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		LABELING-AND-DOCUMENTATION-03 & $\checkmark$ & $\checkmark$ & 1 & $\checkmark$ & & $\checkmark$ & $\checkmark$ & 1 & $\checkmark$ & $\checkmark$ & 1 & $\checkmark$ \\
+		LABELING-AND-DOCUMENTATION-04 &  &  &  &  &  & & &  \\
+		LABELING-AND-DOCUMENTATION-05 & $\checkmark$ & $\checkmark$ & \ding{55} & $\checkmark$ & & $\checkmark$ & $\checkmark$ & 1 & $\checkmark$ & $\checkmark$ & $\checkmark$ & 3 \\
+		LABELING-AND-DOCUMENTATION-06 & $>$1 & \ding{55} & \ding{55} & $\checkmark$ & & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Thesauri Evaluation}
+		\label{tab:thesauri-evaluation-2}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccccccccccc@{}}
+           & \multicolumn{12}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-13}
+    \\       \textbf{Structure}
+           & \rot{TheSoz}
+           & \rot{STW}
+           & \rot{AGROVOC}
+					 & \rot{TGN}
+           & \rot{UNESCO}
+					 & \rot{ODT}
+					 & \rot{SSWT}
+					 & \rot{GBA-GU}
+					 & \rot{GBA-GTS}
+					 & \rot{GBA-L}
+					 & \rot{GBA-LU}
+					 & \rot{CECCT}
+    \\ \midrule
+		STRUCTURE-01 & 1 & 1,074 & $\checkmark$ & $\checkmark$ &  & 5 & 1 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		STRUCTURE-02 &  &  &  &  &  & \\
+		STRUCTURE-03 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ &  & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		STRUCTURE-04 & 2,906 & $>$1,000 & 726 & $\checkmark$ &  & 12 & 124 & 84 & 256 & $>$54 & 22 & 2,422 \\
+		STRUCTURE-05 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ &  & 90 & 5,150 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & 9,864 \\
+		STRUCTURE-06 & 2 & $\checkmark$ & $\checkmark$ & $\checkmark$ &  & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & 113 \\
+		STRUCTURE-07 & 8 & 1,074 & $\checkmark$ & $\checkmark$ &  & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		STRUCTURE-08 &  &  &  &  &  & \\
+		STRUCTURE-09 & 6,741 & $>$3,297 & 135 & $\checkmark$ &  & 2 & 16 & 25 & $\checkmark$ & $\checkmark$ & $\checkmark$ & 81 \\
+		STRUCTURE-10 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ &  & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Thesauri Evaluation}
+		\label{tab:thesauri-evaluation-3}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccccccccccc@{}}
+           & \multicolumn{12}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-13}
+    \\       \textbf{Language Tag Cardinality}
+           & \rot{TheSoz}
+           & \rot{STW}
+           & \rot{AGROVOC}
+					 & \rot{TGN}
+           & \rot{UNESCO}
+					 & \rot{ODT}
+					 & \rot{SSWT}
+					 & \rot{GBA-GU}
+					 & \rot{GBA-GTS}
+					 & \rot{GBA-L}
+					 & \rot{GBA-LU}
+					 & \rot{CECCT}
+    \\ \midrule
+		LANGUAGE-TAG-CARDINALITY-01 & 9,435 & 13,468 & 98,894 & $\checkmark$ &  & 541 & 10,147 & 5,117 & 2,061 & 1,742 & 2,272 & 15,550 \\
+		LANGUAGE-TAG-CARDINALITY-02 & 8,222 & 36,936 & \ding{55} & $\checkmark$ &  & 265 & 3,627 & 2,212 & 635 & 631 & 1,253 & 9,607 \\
+		LANGUAGE-TAG-CARDINALITY-03 & 8,222 & $\checkmark$ & 135 & $\checkmark$ &  & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		LANGUAGE-TAG-CARDINALITY-04 & $\checkmark$ & 476 & \ding{55} & 50 &  & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Thesauri Evaluation}
+		\label{tab:thesauri-evaluation-4}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccccccccccc@{}}
+           & \multicolumn{12}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-13}
+    \\       \textbf{Constraints}
+           & \rot{TheSoz}
+           & \rot{STW}
+           & \rot{AGROVOC}
+					 & \rot{TGN}
+           & \rot{UNESCO}
+					 & \rot{ODT}
+					 & \rot{SSWT}
+					 & \rot{GBA-GU}
+					 & \rot{GBA-GTS}
+					 & \rot{GBA-L}
+					 & \rot{GBA-LU}
+					 & \rot{CECCT}
+    \\ \midrule
+		PROPERTY-DOMAIN-01 &  &  &  &  &  & \\
+		PROPERTY-RANGES-01 &  &  &  &  &  & \\
+		DISJOINT-PROPERTIES-01 &  &  &  &  &  & \\
+		DISJOINT-PROPERTIES-02 &  &  &  &  &  & \\
+		DISJOINT-CLASSES-01 &  &  &  &  &  & \\
+		EQUIVALENT-PROPERTIES-01 &  &  &  &  &  & \\
+		UNIVERSAL-QUANTIFICATIONS-01 &  &  &  &  &  & \\
+		CONTEXT-SPECIFIC-VALID-CLASSES-01 &  &  &  &  &  & \\
+		CONTEXT-SPECIFIC-VALID-PROPERTIES-01 &  &  &  &  &  & \\
+		RECOMMENDED-PROPERTIES-01 &  &  &  &  &  & \\
+		VOCABULARY-01 &  &  &  &  &  & \\
+    \bottomrule
+    \end{tabular}
+    \caption{Thesauri Evaluation}
+		\label{tab:thesauri-evaluation-5}
+    \end{center}
+\end{table}
+
+\section{XKOS}
+
+\begin{itemize}
+	\item Nomenclature d'activités française (NAF): French classification expressed in XKOS. the French refinement of the NACE, because it has explanatory notes.
+	\item Nomenclature des Professions et Catégories Socioprofessionnelles (PCS): French classification expressed in XKOS.
+	\item Nomenclature des catégories juridiques (CJ): French classification expressed in XKOS.
+	\item ISIC: has explanatory notes too. 
+	\item ISCO
+\end{itemize}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccccccccccc@{}}
+           & \multicolumn{6}{c}{\textbf{Counts}}
+    \\  \cmidrule{2-7}
+    \\       \textbf{Data Sets}
+           & \textbf{\rot{triples}}
+           & \textbf{\rot{}}
+           & \textbf{\rot{}}
+           & \textbf{\rot{}}
+           & \textbf{\rot{}}
+					 & \textbf{\rot{}}
+					 & \textbf{\rot{}}
+    \\ \midrule
+    Nomenclature d'activités française (NAF)\tablefootnote{\url{http://rdf.insee.fr/codes/index.html}} &  &  &  &  &  & \\
+		Nomenclature des Professions et Catégories Socioprofessionnelles (PCS)\tablefootnote{\url{http://rdf.insee.fr/codes/index.html}} &  &  &  &  &  & \\
+		Nomenclature des catégories juridiques (CJ)\tablefootnote{\url{http://rdf.insee.fr/codes/index.html}} &  &  &  &  &  & \\
+		ISIC &  &  &  &  &  & \\
+		ISCO &  &  &  &  &  & \\
+    \bottomrule
+    \end{tabular}
+    \caption{Statistical Classifications Overview}
+		\label{tab:statistical-classifications-overview}
+    \end{center}
+\end{table}
 

### 2015-03-24 paper/paper7/paper7.tex
evaluation

@@
 \textbf{Metadata on Aggregated Data in RDF.}
-The variable \emph{formal childcare}\footnote{\url{http://appsso.eurostat.ec.europa.eu/nui/show.do?dataset=ilc_caindformal&lang=en}} (in contrast to childcare at home)
+The variable \emph{formal childcare}\footnote{\url{http://ec.europa.eu/eurostat/web/products-datasets/-/ilc_caindformal}} (in contrast to childcare at home)
 captures the measured availability of childcare services in percent over the population.

### 2015-04-08 paper/paper 2/paper 2.tex
evaluation

@@
 \section{Introduction}
-
+\tb{feedback from Erman: the major problem is semantics. OWL basically work in different semantics than others. And their semantics are formal. Closed world vs. Open World is also a part of this.}
 %The purpose of OWL 2 ontologies is to perform reasoning on RDF data and not to validate RDF data conforming to these ontologies.
@@
       \hline
-class & Half-Klingon & - & - & $\neg$E $\sqcap$ F, E $\sqcap$ $\neg$F & $\sqcup$ & - \\
+class & Publication & - & - & $\neg$E $\sqcap$ F, E $\sqcap$ $\neg$F & $\sqcup$ & - \\
 class & $\neg$E $\sqcap$ F & - & - & $\neg$E, F & $\sqcap$ & - \\

### 2015-04-08 paper/paper7/paper7-appendix.tex
evaluation

@@
 
-\textbf{Content-Driven Validation / Data Model Consistency}.
-Is the data consistent with the intended semantics of the data model?
-Such validation rules ensure the integrity of the data according to the data model.
-
-\textbf{Technology-Driven Validation}.
-Some validation rules can be generated automatically out of the defined data model, such as cardinality restrictions, universal quantifications, domains, ranges.
+We distinguish two validation types:
+(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of given data models.
+(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges.
 
@@
 Thus, reasoners may be used to infer implicit triples resolving constraint violations caused when these constraints are validated.
-	\item \underline{Underlined subsections} are data model specific constraint types and do not correspond to RDF validation requirements (constraint types).
+	\item \underline{Underlined subsections} represent data model specific constraint types and do not correspond to RDF validation requirements (constraint types).
 %	\item \underline{Underlined constraints} are part of content-driven validation.
 %	\item \udash{Dashed underlined constraints} are part of technology-driven validation.
+	\item $\mathcal{C}_{T}$ constraint types are marked with the superscript\textsuperscript{T}
+	\item $\mathcal{C}_{C}$ constraint types are not marked
 \end{itemize}
@@
 		\begin{itemize}
-		\item severity level: WARNING
+		\item severity level: ERROR
 	\end{itemize}
@@
 Such validation rules ensure the integrity of the data according to the data model.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-01}}: 
+	Codes (\emph{skos:Concept}) are ordered and therefore have fixed positions in an ordered collection (\emph{skos:OrderedCollection}) within a variable representation.
+	The cumulative percentage of the current code is the cumulative percentage of the previous code (\emph{disco:cumulativePercentage})
+	plus the percentage value (\emph{disco:percentage}) of the current code. 
+		\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-02}}: 
+	The cumulative percentage (\emph{disco:cumulativePercentage}) of the last code must be 100. 
+		\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-03}}: 
+	The number of valid cases (\emph{disco:SummaryStatistics} of the type (\emph{disco:summaryStatisticType}) \emph{ddicv-sumstats:ValidCases}) 
+	for a particular variable must exactly be the sum of absolute frequencies of all valid cases (\emph{disco:inValid} of \emph{skos:Concept} is true).
+		\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-04}}: 
+	The number of invalid cases (\emph{disco:SummaryStatistics} of the type (\emph{disco:summaryStatisticType}) \emph{ddicv-sumstats:InvalidCases}) 
+	for a particular variable must exactly be the sum of absolute frequencies of all invalid cases (\emph{disco:inValid} of \emph{skos:Concept} is false).
+		\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-05}}: 
+	The total number of valid and invalid cases (\emph{disco:SummaryStatistics} of the type (\emph{disco:summaryStatisticType}) \emph{ddicv-sumstats:NumberOfCases}) 
+	for a particular variable must exactly be the number of valid cases plus the number of invalid cases.
+		\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-06}}: 
+	Some summary statistics types can only be calculated for given variable types. 
+	It is not possible to compute minimum values for string variables.
+		\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-07}}: 
+	Some summary statistics types can only be calculated for given variable types. 
+	It is not possible to compute mean values for categorical variables, only for metric variables.
+		\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+\end{itemize}
 
@@
 If such a path is found, a clash has been identified and the causing concepts are returned.
-		\item Severity level: 
+		\item Severity level: INFO
 	\end{itemize}
@@
 		Can be solved by issuing a SPARQL query. 
-		\item Severity level: 
+		\item Severity level: INFO
 	\end{itemize}
@@
 	\begin{itemize}
-		\item Severity level: 
-	\end{itemize}
-
-\end{itemize}
-
-\subsection{Subsumption*}
+		\item Severity level: INFO
+	\end{itemize}
+
+\end{itemize}
+
+\subsection{Subsumption*\textsuperscript{T}}
 
@@
 All {\em disco:Universe}s must also be {\em skos:Concept}s (\ms{Universe $\sqsubseteq$ Concept}).
-\end{itemize}
-
-\subsection{Class Equivalence*}
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
+\subsection{Class Equivalence*\textsuperscript{T}}
 
@@
 Thus, {\em sio:SIO\_000367} is equivalent to {\em disco:Variable}.
-\end{itemize}
-
-\subsection{Sub Properties*}
+\begin{itemize}
+	\item severity level: INFO
+\end{itemize}
+\end{itemize}
+
+\subsection{Sub Properties*\textsuperscript{T}}
 
@@
 If an individual \emph{x} is connected by {\em disco:fundedBy} to an individual \emph{y}, then \emph{x} is also connected by {\em dcterms:contributor} to \emph{y} (\ms{fundedBy $\sqsubseteq$ contributor}).
-\end{itemize}
-
-\subsection{Property Domains*}
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
+\subsection{Property Domains*\textsuperscript{T}}
 
@@
 
-\subsection{Property Ranges*}
+\subsection{Property Ranges*\textsuperscript{T}}
 
@@
 	\emph{disco:CategoryStatistics} resources are accessed from codes (\emph{skos:Concept}s) via \emph{disco:statisticsCategory}$^{-}$.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 	\item \textbf{{\em DISCO-C-INVERSE-OBJECT-PROPERTIES-02}}:
 	\emph{disco:SummaryStatistics} resources are accessed from \emph{disco:Variable}s via \emph{disco:statisticsVariable}$^{-}$.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 	\item \textbf{{\em DISCO-C-INVERSE-OBJECT-PROPERTIES-03}}:
 	\emph{disco:Variable}s are accessed from \emph{disco:Question}s via \emph{disco:question}$^{-}$.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 
-\subsection{Asymmetric Object Properties*}
+\subsection{Asymmetric Object Properties*\textsuperscript{T}}
 
@@
 This is a kind of mistake which may occur as a semantically equivalent object property for the other direction may also be possible ({\em disco:basisOf}) (\ms{$basedOn \sqcap basedOn^{-} \sqsubseteq \bot$}).
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
   No individual is connected by the object property {\em instrument} to itself (\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists  instrument . Self$}).
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:boader} to themselves (\ms{Concept $\sqsubseteq$ $\neg$$\exists$ broader.Self.}). 
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 	\item \textbf{{\em DISCO-C-CLASS-SPECIFIC-IRREFLEXIVE-OBJECT-PROPERTIES-02:}}
 Within the Disco context, {\em skos:Concept}s cannot be related via the object property {\em skos:narrower} to themselves (\ms{Concept $\sqsubseteq$ $\neg$$\exists$ narrower.Self.}). 
-\end{itemize}
-
-\subsection{Disjoint Properties}
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
+\subsection{Disjoint Properties\textsuperscript{T}}
 
@@
   The properties \emph{qb:dataSet} and \emph{qb:structure} are disjoint ($dataSet \sqsubseteq \neg structure$).
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 	All \emph{DCAT} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
   The properties \emph{disco:variable} and \emph{disco:question} are disjoint ($variable \sqsubseteq \neg question$).
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 	The properties \emph{phdd:isStructuredBy} and \emph{phdd:column} are disjoint ($isStructuredBy \sqsubseteq \neg column$)
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 	All \emph{SKOS} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
-
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 	\item \textbf{{\em SKOS-C-DISJOINT-PROPERTIES-02\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Disjoint Labels Violation}:}}
@@
 		A SPARQL query collects all labels of all concepts, building an in-memory structure. This structure is then checked for disjoint entries. 
-		\item Severity level: 
+		\item severity level: ERROR
 	\end{itemize}
@@
 	All \emph{XKOS} properties (not having the same domain and range classes) are defined to be pairwise disjoint.
-\end{itemize}
-
-\subsection{Disjoint Classes}
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
+\subsection{Disjoint Classes\textsuperscript{T}}
 
@@
 All \emph{Data Cube} classes are defined to be pairwise disjoint.
+\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 All \emph{DCAT} classes are defined to be pairwise disjoint.
+\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 All \emph{Disco} classes are defined to be pairwise disjoint (e.g. \ms{Study $\sqcap$ Variable $\sqsubseteq$ $\perp$}).
+\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 All \emph{PHDD} classes are defined to be pairwise disjoint.
+\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 All \emph{SKOS} classes are defined to be pairwise disjoint.
+\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 All \emph{XKOS} classes are defined to be pairwise disjoint.
+\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 
-\subsection{Equivalent Properties*}
+\subsection{Equivalent Properties*\textsuperscript{T}}
 
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-DATA-PROPERTY-FACETS-01:}} The abstract of a study (\emph{disco:purpose}) should have a minimum length (\emph{xsd:minLength}) of x. 
+	\item \textbf{{\em DISCO-C-DATA-PROPERTY-FACETS-01:}} The abstract of a series (\emph{dcterms:abstract}) should have a minimum length (\emph{xsd:minLength}) of some determined minimum length \emph{X}.
+	\begin{itemize}
+		\item severity level: WARNING
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-DATA-PROPERTY-FACETS-02:}} The abstract of a study (\emph{dcterms:abstract}) should have a minimum length (\emph{xsd:minLength}) of some determined minimum length \emph{X}.
+	\begin{itemize}
+		\item severity level: WARNING
+	\end{itemize}
 \end{itemize}
@@
 	\item \textbf{{\em DISCO-C-LITERAL-PATTERN-MATCHING-01:}} Each \emph{disco:Variable} of a given \emph{disco:LogicalDataSet} must have a given prefix for its variable name (\emph{skos:notation}). 
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
 \end{itemize}
@@
 \end{DL}
+\begin{itemize}
+	\item severity level: ERROR
+\end{itemize}
 \end{itemize}
@@
 
-\subsection{Existential Quantifications*}
+\subsection{Existential Quantifications*\textsuperscript{T}}
 
@@
 	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-01:}} 
-There must be at least one {\em disco:universe} relationship from {\em disco:Studies} or {\em disco:StudyGroups} to {\em disco:Universe} (\ms{Study $\sqcup$ StudyGroup $\sqsubseteq$ $\exists$ universe.Universe}).
+There must be at least one {\em disco:universe} relationship from {\em disco:StudyGroups} to {\em disco:Universe} (\ms{StudyGroup $\sqsubseteq$ $\exists$ universe.Universe}).
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-02:}} 
+There must be at least one {\em disco:universe} relationship from {\em disco:Studies} to {\em disco:Universe} (\ms{Study $\sqsubseteq$ $\exists$ universe.Universe}).
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-03:}} 
+There may be a {\em disco:universe} relationship from {\em disco:RepresentedVariable} to {\em disco:Universe} (\ms{RepresentedVariable $\sqsubseteq$ $\exists$ universe.Universe}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-04:}} 
+There may be a {\em disco:universe} relationship from {\em disco:Variable} to {\em disco:Universe} (\ms{Variable $\sqsubseteq$ $\exists$ universe.Universe}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-05:}} 
+There may be a {\em disco:universe} relationship from {\em disco:Question} to {\em disco:Universe} (\ms{Question $\sqsubseteq$ $\exists$ universe.Universe}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-06:}} 
+There may be a {\em disco:universe} relationship from {\em disco:LogicalDataSet} to {\em disco:Universe} (\ms{LogicalDataSet $\sqsubseteq$ $\exists$ universe.Universe}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-07:}} 
+  There is no relationship (\emph{disco:ddifile}) to a DDI-XML file containing further information about the series (\emph{disco:StudyGroup}) for further analyses.
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-08:}} 
+  There is no relationship (\emph{disco:ddifile}) to a DDI-XML file containing further information about the study (\emph{disco:Study}) for further analyses.
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-09:}} 
+  It is important to know the kind of data (\emph{disco:kindOfData}) collected for a particular series (\emph{disco:StudyGroup}).
+	Survey data, e.g., is much easier accessible than census data. 
+	For census data, it is necessary to get in contact with the individual data archive and if data access is granted it may take months to actually get the data.
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-10:}}
+  It is important to know the kind of data (\emph{disco:kindOfData}) collected for a particular study (\emph{disco:Study}).
+	Survey data, e.g., is much easier accessible than census data. 
+	For census data, it is necessary to get in contact with the individual data archive and if data access is granted it may take months to actually get the data.
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-11:}} 
+  Information about the temporal coverage (\emph{dcterms:temporal}) of a series (\emph{disco:StudyGroup}) is of interest for particular queries 
+	(e.g. to search for all series of a given year (temporal coverage) and for which data is collected in which countries (spatial coverage) about which topics (topical coverage)).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-12:}} 
+  Information about the spatial coverage (\emph{dcterms:spatial}) of a series (\emph{disco:StudyGroup}) is of interest for particular queries 
+	(e.g. to search for all series of a given year (temporal coverage) and for which data is collected in which countries (spatial coverage) about which topics (topical coverage)).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-13:}} 
+  Information about the topical coverage (\emph{dcterms:subject}) of a series (\emph{disco:StudyGroup}) is of interest for particular queries 
+	(e.g. to search for all series of a given year (temporal coverage) and for which data is collected in which countries (spatial coverage) about which topics (topical coverage)).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-14:}} 
+  Information about the temporal coverage (\emph{dcterms:temporal}) of a study (\emph{disco:Study}) is of interest for particular queries 
+	(e.g. to search for all studies of a given year (temporal coverage) and for which data is collected in which countries (spatial coverage) about which topics (topical coverage)).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-15:}} 
+  Information about the spatial coverage (\emph{dcterms:spatial}) of a study (\emph{disco:Study}) is of interest for particular queries 
+	(e.g. to search for all studies of a given year (temporal coverage) and for which data is collected in which countries (spatial coverage) about which topics (topical coverage)).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-16:}} 
+  Information about the topical coverage (\emph{dcterms:subject}) of a study (\emph{disco:Study}) is of interest for particular queries 
+	(e.g. to search for all studies of a given year (temporal coverage) and for which data is collected in which countries (spatial coverage) about which topics (topical coverage)).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-17:}} 
+  Information about the temporal coverage (\emph{dcterms:temporal}) of a data set (\emph{disco:LogicalDataSet}) is of interest for particular queries 
+	(e.g. to search for all data sets of a given year (temporal coverage) and for which data is collected in which countries (spatial coverage) about which topics (topical coverage)).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-18:}} 
+  Information about the spatial coverage (\emph{dcterms:spatial}) of a data set (\emph{disco:LogicalDataSet}) is of interest for particular queries 
+	(e.g. to search for all data sets of a given year (temporal coverage) and for which data is collected in which countries (spatial coverage) about which topics (topical coverage)).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-19:}} 
+  Information about the topical coverage (\emph{dcterms:subject}) of a data set (\emph{disco:LogicalDataSet}) is of interest for particular queries 
+	(e.g. to search for all data sets of a given year (temporal coverage) and for which data is collected in which countries (spatial coverage) about which topics (topical coverage)).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-20:}} 
+  Information about the temporal coverage (\emph{dcterms:temporal}) of a data file (\emph{disco:DataFile}) is of interest for particular queries 
+	(e.g. to search for all data files of a given year (temporal coverage) and for which data is collected in which countries (spatial coverage) about which topics (topical coverage)).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-21:}} 
+  Information about the spatial coverage (\emph{dcterms:spatial}) of a data file (\emph{disco:DataFile}) is of interest for particular queries 
+	(e.g. to search for all data files of a given year (temporal coverage) and for which data is collected in which countries (spatial coverage) about which topics (topical coverage)).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-22:}} 
+  Information about the topical coverage (\emph{dcterms:subject}) of a data file (\emph{disco:DataFile}) is of interest for particular queries 
+	(e.g. to search for all data files of a given year (temporal coverage) and for which data is collected in which countries (spatial coverage) about which topics (topical coverage)).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-23:}} 
+  Information about creators (\emph{dcterms:creator}) (persons or organizations) of a series is important when searching for series of the same creators.
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-24:}} 
+  Information about creators (\emph{dcterms:creator}) (persons or organizations) of a studies is important when searching for studies of the same creators.
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-25:}} 
+  If summary statistics are collected for studies, detailed further analyses are possible. 
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-26:}} 
+  If category statistics are collected for studies, detailed further analyses are possible. 
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-27:}} 
+  If a study has no associated data sets, the actual description of the data is missing. 
+	Eventually, it is very hard or even impossible to get access to the data.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-28:}} 
+  If there is no data file for a given data set, the description of the data set and the containing study is not sufficient.
+	\begin{itemize}
+		\item severity level: WARNING
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-29:}} 
+	The case quantity measures how many cases are collected for a study.
+  High case quantity (disco:caseQuantity), stated for data files, is an indicator for high statistical quality of the underlying study.
+	It indicates how comprehensive the study is.
+	\begin{itemize}
+		\item severity level: WARNING
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-30:}} 
+  High variable quantity (disco:variableQuantity), stated for data files, is an indicator for high statistical quality of the underlying study.
+	It indicates how comprehensive the study is.
+	\begin{itemize}
+		\item severity level: WARNING
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-31:}} 
+  High variable quantity (disco:variableQuantity), stated for data sets, is an indicator for high statistical quality of the underlying study.
+	It indicates how comprehensive the study is.
+	\begin{itemize}
+		\item severity level: WARNING
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-32:}} 
+  There is no summary statistics type information (\emph{disco:summaryStatisticsType}) for a summary statistics resource.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-33:}} 
+  There is no summary statistics value (\emph{rdf:value}) for a summary statistics resource.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-34:}} 
+  There is no relationship to a variable (\emph{disco:statisticsVariable}) for a summary statistics resource.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-35:}} 
+  Category statistics resources must be related (\emph{disco:statisticsCategory}) to codes/categories
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-36:}} 
+  Category statistics resources must have at minimum one value for either frequency, percentage, or cumulative percentage.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-37:}} 
+  Codes should be associated with categories (human-readable labels).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-38:}} 
+  An instrument (\emph{disco:Instrument}) may have a link (\emph{disco:externalDocumentation}) to the questionnaire.
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-39:}} 
+  Questions (\emph{disco:Question}) must have question texts (\emph{disco:questionText}).
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-40:}} 
+  Questions (\emph{disco:Question}) may have response domains (\emph{disco:responseDomain}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-41:}} 
+  Questionnaires (\emph{disco:Questionnaire}) may contain (\emph{disco:question}) questions (\emph{disco:Question}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-42:}} 
+  Questions (\emph{disco:Question}) may have question numbers (\emph{skos:prefLabel}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-43:}} 
+  Variables (\emph{disco:Variable}) may have relationships (\emph{disco:question}) to questions (\emph{disco:Question}), as variables are created out of questions or calculated on the basis of other variables.
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-44:}} 
+  Data sets (\emph{disco:LogicalDataSet}) may have (\emph{disco:variable}) variables (\emph{disco:Variable}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-45:}} 
+  Variables (\emph{disco:Variable}) may have (\emph{disco:concept}) an associated theoretical concept (\emph{skos:Concept}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-EXISTENTIAL-QUANTIFICATIONS-46:}} 
+  Each variable (\emph{disco:Variable}) should have (\emph{disco:representation}) a variable representation (\emph{disco:Representation}) which is either an ordered code list (\emph{skos:OrderedCollection}), an unordered code list (\emph{skos:ConceptScheme}) or a union of datatypes (\emph{rdfs:Datatype}).
+	\begin{itemize}
+		\item severity level: WARNING
+	\end{itemize}
 \end{itemize}
@@
 
-\subsection{Universal Quantifications*}
+\subsection{Universal Quantifications*\textsuperscript{T}}
 
@@
 
-\subsection{Minimum Unqualified Cardinality Restrictions*}
+\subsection{Minimum Unqualified Cardinality Restrictions*\textsuperscript{T}}
 
@@
 
-\subsection{Minimum Qualified Cardinality Restrictions*}
+\subsection{Minimum Qualified Cardinality Restrictions*\textsuperscript{T}}
 
@@
 	\end{itemize}
+		\item \textbf{{\em DATA-CUBE-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-02:}}
+	Unique data set (\emph{IC-1} \cite{CyganiakReynolds2014}) -  
+	Every \emph{qb:Observation} has (\emph{qb:dataSet}) exactly one associated \emph{qb:DataSet} (\ms{Observation $\sqsubseteq$ $\geq$1 dataSet.DataSet $\sqcap$ $\leq$1 dataSet.DataSet}). 
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 
-\subsection{Maximum Unqualified Cardinality Restrictions*}
+\subsection{Maximum Unqualified Cardinality Restrictions*\textsuperscript{T}}
 
@@
 
-\subsection{Maximum Qualified Cardinality Restrictions*}
+\subsection{Maximum Qualified Cardinality Restrictions*\textsuperscript{T}}
 
@@
 	\end{itemize}
-\end{itemize}
-
-\subsection{Exact Unqualified Cardinality Restrictions*}
+	\item \textbf{{\em DATA-CUBE-C-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
+	Unique data set (\emph{IC-1} \cite{CyganiakReynolds2014}) -  
+	Every \emph{qb:Observation} has (\emph{qb:dataSet}) exactly one associated \emph{qb:DataSet} (\ms{Observation $\sqsubseteq$ $\geq$1 dataSet.DataSet $\sqcap$ $\leq$1 dataSet.DataSet}). 
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
+\subsection{Exact Unqualified Cardinality Restrictions*\textsuperscript{T}}
 
@@
 
-\subsection{Exact Qualified Cardinality Restrictions*}
+\subsection{Exact Qualified Cardinality Restrictions*\textsuperscript{T}}
 
@@
 \begin{itemize}
-	\item \textbf{{\em DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-01:}}
-	Unique data set (\emph{IC-1} \cite{CyganiakReynolds2014}) -  
-	Every \emph{qb:Observation} has (\emph{qb:dataSet}) exactly one associated \emph{qb:DataSet} (\ms{Observation $\sqsubseteq$ $\geq$1 dataSet.DataSet $\sqcap$ $\leq$1 dataSet.DataSet}). 
-	\begin{itemize}
-		\item Severity level: ERROR
-	\end{itemize}
 	\item \textbf{{\em DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02:}}
@@
 Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes and categories), but not both.
-
 \begin{DL}
@@
 \end{DL}
-\end{itemize}
-
-\subsection{Allowed Values}
+\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+\end{itemize}
+
+\subsection{Allowed Values\textsuperscript{T}}
 
@@
 {\em disco:CategoryStatistics} can only have {\em disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype {\em rdf:langString} (\ms{CategoryStatistics $\equiv$ $\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString}).
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 {\em disco:percentage} (domain: {\em disco:CategoryStatistics}) literals must be of the datatype {\em xsd:double} whose range should be restricted to be between 0 and 100.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 
-\subsection{Required Properties}
+\subsection{Required Properties\textsuperscript{T}}
 
@@
 
-\subsection{Optional Properties}
+\subsection{Optional Properties\textsuperscript{T}}
 
@@
 
-\subsection{Repeatable Properties}
+\subsection{Repeatable Properties\textsuperscript{T}}
 
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-INVERSE-FUNCTIONAL-PROPERTIES-01:}} for each \emph{rdfs:Resource x}, there can be at most one distinct \emph{rdfs:Resource y} such that \emph{y} is connected by \emph{adms:identifier} to \emph{x} $(\ms{funct identifier}\sp{\overline{\ }})$.
-\end{itemize}
-
-\tb{Achim, we created an open issue for DDI 4 how keys should be defined}
+	\item \textbf{{\em DISCO-C-INVERSE-FUNCTIONAL-PROPERTIES-01:}}
+	For each \emph{rdfs:Resource x}, there can be at most one distinct \emph{rdfs:Resource y} such that \emph{y} is connected by \emph{adms:identifier} to \emph{x} $(\ms{funct identifier}\sp{\overline{\ }})$.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-INVERSE-FUNCTIONAL-PROPERTIES-02:}}
+	Keys are even more general than inverse-functional properties,
+as a key can be a data, an object property, or a chain of properties \cite{Schneider2009}.
+For this generalization purposes, as there are different sorts of key, and as keys can lead to undecidability, 
+DL is extended with \emph{key boxes} and a special \emph{keyfor} construct (\ms{identifier \ms{keyfor} Resource}) \cite{Lutz2005}.
+OWL 2 \emph{hasKey} implements \emph{keyfor} and thus can be used to identify resources uniquely, to merge resources with identical key property values, and to recognize constraint violations.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+\end{itemize}
 
@@
 
-\subsection{Class-Specific Property Range*}
+\subsection{Class-Specific Property Range*\textsuperscript{T}}
 
@@
 Only {\em disco:Question}s can have {\em disco:questionText} relationships to literals of the datatype {\em rdf:langString} (\ms{$\neg$Question $\sqsubseteq$ $\neg\exists$ questionText.langString}).
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 \end{DL}
+
+\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-IRI-PATTERN-MATCHING}}: \emph{disco:Study} resources must match a given IRI pattern.
+	\item \textbf{{\em DISCO-C-IRI-PATTERN-MATCHING-01}}: \emph{disco:Study} resources must match a given IRI pattern.
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
 \end{itemize}
@@
 To validate this constraint we bind the variables as follows (P1: {\em disco:startDate}, P2: {\em disco:endDate}, OP: \textless). 
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 The collection of variables is of the type {\em skos:OrderedCollection} containing multiple variables (each represented as {\em skos:Concept}) in a {\em skos:memberList}.
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
 	\item \textbf{{\em DISCO-C-ORDERING-02}}: If \emph{disco:Question}s of a given \emph{disco:Questionnaire} should be ordered, a collection of questions must be present in the data and connected with the questionnaire.
 The collection of questions is of the type {\em skos:OrderedCollection} containing multiple questions (each represented as {\em skos:Concept}) in a {\em skos:memberList}.
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
 	\item \textbf{{\em DISCO-C-ORDERING-03}}: If codes/categories (\emph{skos:Concept}s) of a given \emph{disco:Representation} of a given \emph{disco:Variable} should be ordered, the variable representation should also be of the type {\em skos:OrderedCollection} containing multiple codes/categories (each represented as {\em skos:Concept}) in a {\em skos:memberList}.
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
 \end{itemize}
@@
 '2005').
-\end{itemize}
-
-\subsection{Context-Specific Valid Classes}
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+\end{itemize}
+
+\subsection{Context-Specific Valid Classes\textsuperscript{T}}
 
@@
 	\begin{itemize}
-		\item severity level: RECOMMENDED
+		\item severity level: INFO
 	\end{itemize}
@@
 	\begin{itemize}
-		\item severity level: RECOMMENDED
-	\end{itemize}
-\end{itemize}
-
-\subsection{Context-Specific Valid Properties}
+		\item severity level: INFO
+	\end{itemize}
+\end{itemize}
+
+\subsection{Context-Specific Valid Properties\textsuperscript{T}}
 
@@
 	\begin{itemize}
-		\item severity level: RECOMMENDED
-	\end{itemize}
-\end{itemize}
-
-\subsection{Default Values*}
+		\item severity level: INFO
+	\end{itemize}
+\end{itemize}
+
+\subsection{Default Values*\textsuperscript{T}}
 
@@
 Per default, access to data sets should be restricted ('false').
+\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
 \end{itemize}
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-LANGUAGE-TAG-MATCHING:}}
+	\item \textbf{{\em DISCO-C-LANGUAGE-TAG-MATCHING-01:}}
 There must be an English variable name ({\em skos:notation}) for each {\em disco:Variable} within {\em disco:LogicalDataSet}s.
+\begin{itemize}
+	\item severity level: INFO
+\end{itemize}
 \end{itemize}
@@
   There must be at least one English {\em disco:questionText} for each {\em disco:Question} within {\em disco:LogicalDataSet}s.
-
+\begin{itemize}
+	\item severity level: INFO
+\end{itemize}
   \item \textbf{{\em DISCO-C-LANGUAGE-TAG-CARDINALITY-02:}}
   There should be at most one English literal value for variable names ({\em skos:notation}, domain: {\em disco:Variable}).
-
+\begin{itemize}
+	\item severity level: INFO
+\end{itemize}
   \item \textbf{{\em DISCO-C-LANGUAGE-TAG-CARDINALITY-03}}:
 	For each question (\emph{disco:Question}), there must be at least one question text (\emph{disco:questionText}) associated with a language tag of an arbitrary language or with an English language tag.
-
+\begin{itemize}
+	\item severity level: INFO
+\end{itemize}
 \end{itemize}
@@
 	\item \textbf{{\em DISCO-C-WHITESPACE-HANDLING-01:}} Delete whitespaces of series and study abstracts (\emph{dcterms:abstract}; domain: \emph{disco:StudyGroup}, \emph{disco:Study}) automatically.
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
 \end{itemize}
@@
 	\item \textbf{{\em DISCO-C-HTML-HANDLING-01:}} Check if all HTML tags, included in literals of all \emph{Disco} data properties, are closed properly.
+		\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
 	\item \textbf{{\em DISCO-C-HTML-HANDLING-02:}} Check if all HTML tags, included in literals of all data properties whose domains are \emph{Disco} classes, are closed properly.
+		\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
 \end{itemize}
@@
 then the property {\em disco:isValid} has to be stated indicating if the code is valid ('true') or missing ('false').
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 	\item \textbf{{\em DISCO-C-CONDITIONAL-PROPERTIES-02}}:
-	If the abstract (\emph{dcterms:abstract}) of a \emph{disco:Study} is missing, a study title (\emph{dcterms:title}) has to be stated.
+	In order to get an overview over a series or a study either an abstract, a title, an alternative title, or links to external descriptions should be stated. 
+	If the abstract (\emph{dcterms:abstract}) of a series (\emph{disco:StudyGroup}) and an external description of the series (\emph{disco:ddifile}) is missing, 
+	a series title (\emph{dcterms:title}) or an alternative series title (\emph{dcterms:alternative}) has to be stated.
+	\begin{itemize}
+		\item severity level: WARNING
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-CONDITIONAL-PROPERTIES-03}}:
+	In order to get an overview over a series or a study either an abstract, a title, an alternative title, or links to external descriptions should be stated. 
+	If the abstract (\emph{dcterms:abstract}) of a study (\emph{disco:Study}) and an external description of the study (\emph{disco:ddifile}) is missing, 
+	a study title (\emph{dcterms:title}) or an alternative study title (\emph{dcterms:alternative}) has to be stated.
+	\begin{itemize}
+		\item severity level: WARNING
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-CONDITIONAL-PROPERTIES-04}}:
+	If the abstract (\emph{dcterms:abstract}) of a series (\emph{disco:StudyGroup}), an external description of the series (\emph{disco:ddifile}), 
+	a series title (\emph{dcterms:title}), and an alternative series title (\emph{dcterms:alternative}) is missing, an error message should be shown.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-CONDITIONAL-PROPERTIES-05}}:
+	If the abstract (\emph{dcterms:abstract}) of a study (\emph{disco:Study}), an external description of the study (\emph{disco:ddifile}), 
+	a study title (\emph{dcterms:title}), and an alternative study title (\emph{dcterms:alternative}) is missing, an error message should be shown.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-CONDITIONAL-PROPERTIES-06}}:
+	If a category statistics resource is connected with a code, it must be stated if the code is valid (\emph{disco:isValid}) and the code must be stated (\emph{skos:notation})
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 	\item \textbf{{\em DISCO-C-HANDLE-RDF-COLLECTIONS-01}}: Have comparable \emph{disco:Variable}s the same number of codes in their code lists?
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
 	\item \textbf{{\em DISCO-C-HANDLE-RDF-COLLECTIONS-02}}: Does the actual number of \emph{disco:Variable}s within an (un)ordered collection of a given \emph{disco:LogicalDataSet} match the expected number?
-\end{itemize}
-
-\subsection{Value is Valid for Datatype}
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+\end{itemize}
+
+\subsection{Value is Valid for Datatype\textsuperscript{T}}
 
@@
 \begin{itemize}
-	\item \textbf{{\em DISCO-C-VALUE-IS-VALID-FOR-DATATYPE-01}}: Check if all literal values of properties used within the \emph{Disco} context of the datatype {\em xsd:date} (e.g.
+	\item \textbf{{\em DISCO-C-VALUE-IS-VALID-FOR-DATATYPE-01}}: 
+	Check if all literal values of properties used within the \emph{Disco} context of the datatype {\em xsd:date} (e.g.
 {\em disco:startDate}, {\em disco:endDate}, {\em dcterms:date}) are really of the datatype {\em xsd:date}.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-VALUE-IS-VALID-FOR-DATATYPE-02}}: 
+	Frequencies (disco:frequency) cannot be negative, i.e., must correspond  to the XML Schema datatype \emph{xsd:nonNegativeInteger}.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 
-\subsection{Use Sub-Super Relations in Validation}
+\subsection{Use Sub-Super Relations in Validation\textsuperscript{T}}
 
@@
 	If one or more \emph{dcterms:coverage} properties are present, suggest the use of one of its sub-properties \emph{dcterms:spatial} or \emph{dcterms:temporal}.
+		\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
 	\item \textbf{{\em DISCO-C-USE-SUB-SUPER-RELATIONS-IN-VALIDATION-02}}: 
 	If the \emph{dcterms:contributor} property is present, suggest the use of one of its sub-properties, e.g. \emph{disco:fundedBy}.
-\end{itemize}
-
-\subsection{Cardinality Shortcuts*}
+		\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+\end{itemize}
+
+\subsection{Cardinality Shortcuts*\textsuperscript{T}}
 
@@
 	\item \textbf{{\em DISCO-C-AGGREGATION-01}}: calculate the number of theoretical concepts in the thematic classification of a given study.
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
   \item \textbf{{\em DISCO-C-AGGREGATION-02}}: calculate the number of variables of a data set.
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
 	\item \textbf{{\em DISCO-C-AGGREGATION-03}}: calculate the number of questions in a given questionnaire.
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
 	\item \textbf{{\em DISCO-C-AGGREGATION-04}}: the number of codes of a given variable must be below a maximum value.
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
 	\item \textbf{{\em DISCO-C-AGGREGATION-05}}: the number of questions of a given questionnaire must exactly be a given value.
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
 	\item \textbf{{\em DISCO-C-AGGREGATION-06}}: the cumulative percentage of all codes of a given variable must be 100.
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
   \item \textbf{{\em DISCO-C-AGGREGATION-07}}: the absolute frequency of all valid codes of a given variable must be equal to a given value.
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
 \end{itemize}
@@
 	\item \textbf{{\em DISCO-C-STRUCTURE-01}}: there must be exactly one root in the hierarchy of DDI concepts. 
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
 \end{itemize}
@@
 \begin{itemize}
+	\item \textbf{{\em DISCO-C-LABELING-AND-DOCUMENTATION-01}}: 
+	Series should be described (\emph{dcterms:description}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-LABELING-AND-DOCUMENTATION-02}}: 
+	Studies should be described (\emph{dcterms:description}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-LABELING-AND-DOCUMENTATION-03}}: 
+	Data sets should be described (\emph{dcterms:description}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-LABELING-AND-DOCUMENTATION-04}}: 
+	Data files should be described (\emph{dcterms:description}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-LABELING-AND-DOCUMENTATION-05}}: 
+	Instruments should be described (\emph{dcterms:description}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-LABELING-AND-DOCUMENTATION-06}}: 
+	Variables should be described (\emph{dcterms:description}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
 	\item \textbf{{\em SKOS-C-LABELING-AND-DOCUMENTATION-01\footnote{Corresponds to qSKOS Quality Issues - Labeling and Documentation Issues - Undocumented Concepts}:}}
@@
 
-\subsection{\underline{Vocabulary}}
+\subsection{\underline{Vocabulary}\textsuperscript{T}}
 Vocabularies should not invent any new terms or use deprecated elements.
@@
 	\begin{itemize}
-		\item Severity level: FATALERROR
+		\item Severity level: ERROR
 	\end{itemize}
@@
 \begin{itemize}
-	\item \textbf{\em R-HTTP-URI-SCHEME-VIOLATION\footnote{Corresponds to qSKOS Quality Issues - Linked Data Specific Issues - HTTP URI Scheme Violation}}: 
+	\item \textbf{\em DISCO-C-HTTP-URI-SCHEME-VIOLATION\footnote{Corresponds to qSKOS Quality Issues - Linked Data Specific Issues - HTTP URI Scheme Violation}}: 
 	In the context of Linked Data, we restrict ourselves to using HTTP URIs only and avoid other URI schemes such as URNs and DOIs.
@@
 
-\section{SKOS-Related Constraint Types}
-
-\section{Validation in Combination with other Vocabularies}
-
-\subsection{RDF Data Cube Vocabulary}
-
-\subsection{SKOS and XKOS}
-
-\subsection{PHDD}
-
-\subsection{DCAT}
-
-\section{Conclusion and Future Work}
+\begin{itemize}
+	\item \textbf{\em DATA-CUBE-C-HTTP-URI-SCHEME-VIOLATION\footnote{Corresponds to qSKOS Quality Issues - Linked Data Specific Issues - HTTP URI Scheme Violation}}: 
+	In the context of Linked Data, we restrict ourselves to using HTTP URIs only and avoid other URI schemes such as URNs and DOIs.
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{\em PHDD-C-HTTP-URI-SCHEME-VIOLATION\footnote{Corresponds to qSKOS Quality Issues - Linked Data Specific Issues - HTTP URI Scheme Violation}}: 
+	In the context of Linked Data, we restrict ourselves to using HTTP URIs only and avoid other URI schemes such as URNs and DOIs.
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{\em SKOS-C-HTTP-URI-SCHEME-VIOLATION\footnote{Corresponds to qSKOS Quality Issues - Linked Data Specific Issues - HTTP URI Scheme Violation}}: 
+	In the context of Linked Data, we restrict ourselves to using HTTP URIs only and avoid other URI schemes such as URNs and DOIs.
+	\begin{itemize}
+		\item Severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
+\subsection{Provenance}
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-PROVENANCE-01}}: 
+	Series should have provenance information (\emph{dcterms:provenance}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-PROVENANCE-02}}: 
+	Studies should have provenance information (\emph{dcterms:provenance}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-PROVENANCE-03}}: 
+	Data sets should have provenance information (\emph{dcterms:provenance}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-PROVENANCE-04}}: 
+	Data files should have provenance information (\emph{dcterms:provenance}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+\end{itemize}
 

### 2015-04-08 paper/paper7/paper7-evaluation.tex
evaluation

--- 2015-03-12 paper/paper7/paper7-evaluation.tex
@@
 
-\section{Introduction}
+\section{Evaluation}
 
-\section{Disco}
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccccc@{}}
+           & \multicolumn{6}{c}{\textbf{Vocabularies}}
+    \\  \cmidrule{2-7}
+    \\       \textbf{Criteria (Counts)}
+           & \textbf{\rot{Person-Level Metadata (Disco)}}
+           & \textbf{\rot{Aggregated Metadata (Data Cube)}}
+					 & \textbf{\rot{Thesauri (SKOS)}}
+					 & \textbf{\rot{Rectangular Data (PHDD)}}
+					 & \textbf{\rot{Statistical Classifications (XKOS)}}
+					 & \textbf{\rot{Total}}
+    \\ \midrule
+		\emph{Validated Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 \\
+		\emph{Validated Data Sets} & 1,526 & 9,990 & 4,178 \\
+		\hline
+		\emph{Constraint Violations} & \textcolor{red}{XXXXX} \\
+		\emph{Constraint Violations ($\mathcal{SL}_{0}$)} & \textcolor{red}{XXXXX} \\
+		\emph{Constraint Violations ($\mathcal{SL}_{1}$)} & 473,574 $\equiv$ \textcolor{red}{XXXXX}\% \\
+    \emph{Constraint Violations ($\mathcal{SL}_{2}$)} & \textcolor{red}{XXXXX} \\
+				\hline
+		\emph{Constraint Types} & 52 (15\textbar 37) \\
+		\emph{Constraint Types} ($\mathcal{C}_{C}$) & 30 $\equiv$ 57.7 \% \\
+		\emph{Constraint Types} ($\mathcal{C}_{T}$) & 22 $\equiv$ 42.3 \% \\
+		\hline
+		\emph{Constraints} & 142 (77\textbar 65) \\
+		\emph{Constraints} ($\mathcal{C}_{C}$) & 72 $\equiv$ 50.7 \% \\
+		\emph{Constraints} ($\mathcal{C}_{T}$) & 70 $\equiv$ 49.3 \% \\
+		\emph{Constraints ($\mathcal{SL}_{0}$)} & 75 $\equiv$ 52.8\% (44\textbar 31)\\
+		\emph{Constraints ($\mathcal{SL}_{1}$)} & 9 $\equiv$ 6.3\% (8\textbar 1)\\
+		\emph{Constraints ($\mathcal{SL}_{2}$)} & 58 $\equiv$ 40.8\% (25\textbar 33)\\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation}
+		\label{tab:evaluation}
+    \end{center}
+\end{table}
+
+\subsection{Legend}
+
+\begin{table}
+	\centering
+		\begin{tabular}{c|l}
+      \textbf{Symbol} & \textbf{Description} \\		
+			\textbf{\emph{X}} & Validation Successful \\
+			\hline
+			\textbf{\textgreater \emph{X}} & Poor Performance/Scaling \\
+			\hline
+      \ding{55} & Very Poor Performance/Scaling \\
+			\hline
+			\textbf{\emph{(!)}} & Not Yet Implemented Constraint \\
+			\hline
+			\textbf{\emph{(X)}} & The validation of \emph{X} data sets could not be finished \\
+			           & due to SPARQL endpoints' technical restrictions (e.g. the defined timeout). \\
+			\hline
+			\textbf{\emph{\textsuperscript{*}}} & severity level $\mathcal{SL}_{0}$ (informational) \\
+			\hline
+			\textbf{\emph{\textsuperscript{**}}} & severity level $\mathcal{SL}_{1}$ (warning) \\
+			\hline
+			\textbf{\emph{\textsuperscript{***}}} & severity level $\mathcal{SL}_{2}$ (error) \\
+		\end{tabular}
+	\caption{Legend}
+	\label{tab:legend}
+\end{table}
+
+\textbf{Validation Successful:} 
+\emph{X} indicates the number of raised constraint violation triples.
+
+\textbf{Poor Performance/Scaling:}
+The performance of the implementation of the underlying SPARQL CONSTRUCT query 
+is too poor to get all resulting constraint violation triples. 
+Therefore, a limit of \emph{X} result constraint violation triples is set. 
+It is likely that there are more than \emph{X} constraint violations.
+Although, the result set contains not the whole set of raised constraint violation triples,
+the constraint can be used as an indicator if there data not conforming to the constraint and
+to resolve constraint violations step by step. 
+As part of future work, the performance will be improved.
+
+\textbf{Very Poor Performance/Scaling:} 
+The performance of the implementation of the underlying SPARQL CONSTRUCT query 
+is too poor to get any results, even though a limit of result constraint violation triples is set. 
+As part of future work, the performance will be improved.
+
+\section{Person-Level Metadata (Disco)}
+
+\subsection{Evaluation Results}
+
+Legend: total (implemented\textbar not yet implemented)
+
+\begin{table}[H]
+	\centering
+		\begin{tabular}{l|l}
+      \textbf{Evaluation Criteria} & \textbf{Counts} \\		
+      \hline
+		\emph{Validated Triples} & 9,673,055 \\
+		\emph{Validated Data Sets} & 1,526 \\
+		\hline
+		\emph{Constraint Violations} & \textcolor{red}{XXXXX} \\
+		\emph{Constraint Violations ($\mathcal{SL}_{0}$)} & \textcolor{red}{XXXXX} \\
+		\emph{Constraint Violations ($\mathcal{SL}_{1}$)} & 473,574 $\equiv$ \textcolor{red}{XXXXX}\% \\
+    \emph{Constraint Violations ($\mathcal{SL}_{2}$)} & \textcolor{red}{XXXXX} \\
+		\hline
+		\emph{Constraint (Most Constraint Violations)} & \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} (547,916) \\
+		                                               & \emph{DISCO-C-COMPARISON-VARIABLES-02} (547,916) \\
+		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{0}$))} & \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} (547,916) \\
+		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{1}$))} & \emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-46} (468,807) \\
+		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{2}$))} & \emph{DISCO-C-COMPARISON-VARIABLES-02} (547,916) \\
+		\hline
+		\emph{Constraint Types} & 52 (15\textbar 37) \\
+		\emph{Constraint Types} ($\mathcal{C}_{C}$) & 30 $\equiv$ 57.7 \% \\
+		\emph{Constraint Types} ($\mathcal{C}_{T}$) & 22 $\equiv$ 42.3 \% \\
+		\hline
+		\emph{Constraint Types (Most Constraints)} & 1. Existential Quantifications: 46 $\equiv$ 32.4\% (46\textbar 0) \\
+		                                            & 2. Data Model Consistency: 7 (1\textbar 6) \\
+																								& 3. Aggregation: 7 (0\textbar 7) \\
+		\emph{Constraint Type (Most Constraints ($\mathcal{SL}_{2}$))} & Existential Quantifications: 9 (9\textbar 0) \\
+		\hline
+		\emph{Constraints} & 142 (77\textbar 65) \\
+		\emph{Constraints} ($\mathcal{C}_{C}$) & 72 $\equiv$ 50.7 \% \\
+		\emph{Constraints} ($\mathcal{C}_{T}$) & 70 $\equiv$ 49.3 \% \\
+		\emph{Constraints ($\mathcal{SL}_{0}$)} & 75 $\equiv$ 52.8\% (44\textbar 31)\\
+		\emph{Constraints ($\mathcal{SL}_{1}$)} & 9 $\equiv$ 6.3\% (8\textbar 1)\\
+		\emph{Constraints ($\mathcal{SL}_{2}$)} & 58 $\equiv$ 40.8\% (25\textbar 33)\\
+		\end{tabular}
+    \caption{Evaluation of Disco Data Sets - Evaluation Results}
+		\label{tab:disco-evaluation-results}
+\end{table}
+
+%\begin{table}[H]
+    %\begin{center}
+    %\begin{tabular}{@{}lc@{}}
+           %& \multicolumn{1}{c}{\textbf{Constraint Types}}
+    %\\  \cmidrule{2-2}
+    %\\       \textbf{Criteria (Counts)}
+           %& \textbf{\rot{Existential Quantifications}}
+    %\\ \midrule
+		%\emph{Constraints / Constraint Type} & 46 \\
+    %\bottomrule
+    %\end{tabular}
+    %\caption{Evaluation of Disco Data Sets - Evaluation Results (2)}
+		%\label{tab:disco-evaluation-results-2}
+    %\end{center}
+%\end{table}
+
+\subsection{Data Sets Overview}
+
+\begin{table}[H]
+	\centering
+		\begin{tabular}{l|l}
+      \textbf{Abbr.} & \textbf{Disco Data Sets} \\		
+      \hline
+    \emph{Missy} & \emph{Microdata Information System}\tablefootnote{\url{http://www.gesis.org/missy/eu/missy-home}} \\
+		\emph{DwB} & \emph{DwB Discovery Portal}\tablefootnote{\url{http://dwb-dev.nsd.uib.no/portal}} \\
+		\emph{DDA-SND} & \emph{DDI-RDF}\tablefootnote{\url{http://ddi-rdf.borsna.se/}} \\
+		               & provided by the \emph{Danish Data Archive (DDA)}\tablefootnote{\url{http://samfund.dda.dk/dda/default-en.asp}} and Swedish National Data Service (SND)\tablefootnote{\url{http://snd.gu.se/en}} \\
+		\end{tabular}
+	\caption{Disco Data Sets Abbreviations}
+	\label{tab:disco-data-sets-abbreviations}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccccccccccc@{}}
+           & \multicolumn{9}{c}{\textbf{Counts}}
+    \\  \cmidrule{2-10}
+    \\       \textbf{Data Sets}
+           & \textbf{\rot{triples}}
+           & \textbf{\rot{disco:StudyGroup}}
+           & \textbf{\rot{disco:Study}}
+           & \textbf{\rot{disco:LogicalDataSet}}
+           & \textbf{\rot{disco:Universe}}
+					 & \textbf{\rot{disco:Variable}}
+					 & \textbf{\rot{disco:Question}}
+				   & \textbf{\rot{disco:SummaryStatistics}}
+					 & \textbf{\rot{disco:CategoryStatistics}}
+					 & \textbf{\rot{skos:Concept}}
+    \\ \midrule
+    \emph{Missy} & 5,068,838 & 6 & 45 & 159 & 1,125 & 21,040 & 0 & 0 & 0 & 147,193 \\
+		\emph{DwB} & 2,332,802 & 0 & 1,387 & 1,367 & 2,796 & 446,806 & 0 & 0 & 0 & 0 \\
+		\emph{DDA-SND} & 2,271,415 & 0 & 1,490 & 0 & 10,188 & 80,070 & 139,237 & 0 & 0 & 290,963 \\ 
+		\hline
+		\textbf{\emph{Total}} & 9,673,055 & & & 1,526 \\
+    \bottomrule
+    \end{tabular}
+    \caption{Disco Data Sets Overview}
+		\label{tab:disco-overview}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+	\centering
+		\begin{tabular}{l|l}
+      \textbf{Data Sets} & \textbf{SPARQL Endpoint} \\		
+      \hline
+      \emph{Missy} & \url{http://svko-missy:8181/openrdf-workbench/repositories/native-java-store/summary} \\
+			\emph{DwB} & \url{http://dwb-dev.nsd.uib.no/sparql} \\
+			\emph{DDA-SND} & \url{http://ddi-rdf.borsna.se/endpoint/} \\
+		\end{tabular}
+	\caption{Disco SPARQL Endpoints}
+	\label{tab:disco-sparql-endpoints}
+\end{table}
+
+\subsection{Detailed Evaluation}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccc@{}}
+           & \multicolumn{3}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-4}
+    \\       \textbf{Existential Quantifications (1)}
+           & \rot{\emph{Missy}}
+           & \rot{\emph{DwB}}
+           & \rot{\emph{DDA-SND}}
+    \\ \midrule
+    \emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-02}\textsuperscript{***} & 7 & 17 & 1,490 \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-03}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-04}\textsuperscript{*} & 11,021 & 445,381 & 62,260 \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-05}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & 139,237 \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-06}\textsuperscript{*} & 12 & 1,367 & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-07}\textsuperscript{*} & 6 & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-08}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-09}\textsuperscript{*} & 6 & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-10}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Disco Data Sets - Existential Quantifications (1)}
+		\label{tab:evaluation-disco-existential-quantifications-1}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccc@{}}
+           & \multicolumn{3}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-4}
+    \\       \textbf{Existential Quantifications (2)}
+           & \rot{\emph{Missy}}
+           & \rot{\emph{DwB}}
+           & \rot{\emph{DDA-SND}}
+    \\ \midrule
+    \emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-11}\textsuperscript{*} & 6 & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-12}\textsuperscript{*} & 6 & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-13}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-14}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-15}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-16}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-17}\textsuperscript{*} & 159 & 1,367 & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-18}\textsuperscript{*} & 159 & 1,367 & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-19}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-20}\textsuperscript{*} & $\checkmark$ & 1,367 & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Disco Data Sets - Existential Quantifications (2)}
+		\label{tab:evaluation-disco-existential-quantifications-2}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccc@{}}
+           & \multicolumn{3}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-4}
+    \\       \textbf{Existential Quantifications (3)}
+           & \rot{\emph{Missy}}
+           & \rot{\emph{DwB}}
+           & \rot{\emph{DDA-SND}}
+    \\ \midrule
+    \emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-21}\textsuperscript{*} & $\checkmark$ & 1,367 & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-22}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-23}\textsuperscript{*} & 6 & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-24}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-25}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-26}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-27}\textsuperscript{***} & $\checkmark$ & 130 & 1,490 \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-28}\textsuperscript{**} & 159 & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-29}\textsuperscript{**} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-30}\textsuperscript{**} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Disco Data Sets - Existential Quantifications (3)}
+		\label{tab:evaluation-disco-existential-quantifications-3}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccc@{}}
+           & \multicolumn{3}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-4}
+    \\       \textbf{Existential Quantifications (4)}
+           & \rot{\emph{Missy}}
+           & \rot{\emph{DwB}}
+           & \rot{\emph{DDA-SND}}
+    \\ \midrule
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-31}\textsuperscript{**} & 159 & 1,367 & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-32}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-33}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-34}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-35}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-36}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-37}\textsuperscript{*} & 18,625 & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-38}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & 750 \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-39}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-40}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & 139,237 \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Disco Data Sets - Existential Quantifications (4)}
+		\label{tab:evaluation-disco-existential-quantifications-4}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccc@{}}
+           & \multicolumn{3}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-4}
+    \\       \textbf{Existential Quantifications (5)}
+           & \rot{\emph{Missy}}
+           & \rot{\emph{DwB}}
+           & \rot{\emph{DDA-SND}}
+    \\ \midrule
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-41}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-42}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-43}\textsuperscript{*} & 15,733 & 446,806 & 80,070 \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-44}\textsuperscript{*} & 159 & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-45}\textsuperscript{*} & 6,784 & 446,806 & 19,221 \\
+		\emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-46}\textsuperscript{**} & 11,550 & 446,806 & 10,451 \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Disco Data Sets - Existential Quantifications (5)}
+		\label{tab:evaluation-disco-existential-quantifications-5}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccc@{}}
+           & \multicolumn{3}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-4}
+    \\       \textbf{Conditional Properties}
+           & \rot{\emph{Missy}}
+           & \rot{\emph{DwB}}
+           & \rot{\emph{DDA-SND}}
+    \\ \midrule
+    \emph{ DISCO-C-CONDITIONAL-PROPERTIES-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & 80,070 \\
+		\emph{ DISCO-C-CONDITIONAL-PROPERTIES-02}\textsuperscript{**} & 12 & $\checkmark$ & $\checkmark$ \\
+		\emph{ DISCO-C-CONDITIONAL-PROPERTIES-03}\textsuperscript{**} & 90 & $\checkmark$ & 2,980 \\
+		\emph{ DISCO-C-CONDITIONAL-PROPERTIES-04}\textsuperscript{***} & 6 & $\checkmark$ & $\checkmark$ \\
+		\emph{ DISCO-C-CONDITIONAL-PROPERTIES-05}\textsuperscript{***} & 45 & 1,387 & 1,490 \\
+		\emph{ DISCO-C-CONDITIONAL-PROPERTIES-06}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Disco Data Sets - Conditional Properties}
+		\label{tab:evaluation-disco-conditional-properties}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccc@{}}
+           & \multicolumn{3}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-4}
+    \\       \textbf{Provenance}
+           & \rot{\emph{Missy}}
+           & \rot{\emph{DwB}}
+           & \rot{\emph{DDA-SND}}
+    \\ \midrule
+    \emph{DISCO-C-PROVENANCE-01}\textsuperscript{*} & 6 & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-PROVENANCE-02}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
+		\emph{DISCO-C-PROVENANCE-03}\textsuperscript{*} & 159 & 1,367 & $\checkmark$ \\
+		\emph{DISCO-C-PROVENANCE-04}\textsuperscript{*} & $\checkmark$ & 1,367 & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Disco Data Sets - Provenance}
+		\label{tab:evaluation-disco-provenance}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccc@{}}
+           & \multicolumn{3}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-4}
+    \\       \textbf{Labeling and Documentation}
+           & \rot{\emph{Missy}}
+           & \rot{\emph{DwB}}
+           & \rot{\emph{DDA-SND}}
+    \\ \midrule
+    \emph{DISCO-C-LABELING-AND-DOCUMENTATION-01}\textsuperscript{*} & 6 & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-LABELING-AND-DOCUMENTATION-02}\textsuperscript{*} & 45 & 1,387 & 1,490 \\
+		\emph{DISCO-C-LABELING-AND-DOCUMENTATION-03}\textsuperscript{*} & 159 & 1,367 & $\checkmark$ \\
+		\emph{DISCO-C-LABELING-AND-DOCUMENTATION-04}\textsuperscript{*} & $\checkmark$ & 1,367 & $\checkmark$ \\
+		\emph{DISCO-C-LABELING-AND-DOCUMENTATION-05}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-LABELING-AND-DOCUMENTATION-06}\textsuperscript{*} & 21,040 & 446,806 & 80,070 \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Disco Data Sets - Labeling and Documentation}
+		\label{tab:evaluation-disco-labeling-and-documentation}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccc@{}}
+           & \multicolumn{3}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-4}
+    \\       \textbf{Data Model Consistency}
+           & \rot{\emph{Missy}}
+           & \rot{\emph{DwB}}
+           & \rot{\emph{DDA-SND}}
+    \\ \midrule
+    \emph{DISCO-C-DATA-MODEL-CONSISTENCY-01 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-DATA-MODEL-CONSISTENCY-02 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-DATA-MODEL-CONSISTENCY-03 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-DATA-MODEL-CONSISTENCY-04 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-DATA-MODEL-CONSISTENCY-05}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-DATA-MODEL-CONSISTENCY-06 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-DATA-MODEL-CONSISTENCY-07 (!)}\textsuperscript{***} \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Disco Data Sets - Data Model Consistency}
+		\label{tab:evaluation-disco-data-model-consistency}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccc@{}}
+           & \multicolumn{3}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-4}
+    \\       \textbf{Comparison}
+           & \rot{\emph{Missy}}
+           & \rot{\emph{DwB}}
+           & \rot{\emph{DDA-SND}}
+    \\ \midrule
+    \emph{DISCO-C-COMPARISON-VARIABLES-01 (!)}\textsuperscript{**} \\
+		\emph{DISCO-C-COMPARISON-VARIABLES-02}\textsuperscript{***} & 21,040 & 446,806 & 80,070 \\
+		\emph{DISCO-C-COMPARISON-VARIABLES-03 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-COMPARISON-VARIABLES-04}\textsuperscript{*} & 18,625 & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-COMPARISON-VARIABLES-05}\textsuperscript{***} & 159 & $\checkmark$ & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Disco Data Sets - Comparison}
+		\label{tab:evaluation-disco-comparison}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccc@{}}
+           & \multicolumn{3}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-4}
+    \\       \textbf{Mathematical Operations}
+           & \rot{\emph{Missy}}
+           & \rot{\emph{DwB}}
+           & \rot{\emph{DDA-SND}}
+    \\ \midrule
+    \emph{DISCO-C-MATHEMATICAL-OPERATIONS-01 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-MATHEMATICAL-OPERATIONS-02 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-MATHEMATICAL-OPERATIONS-03 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-MATHEMATICAL-OPERATIONS-04 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-MATHEMATICAL-OPERATIONS-05 (!)}\textsuperscript{***} \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Disco Data Sets - Mathematical Operations}
+		\label{tab:evaluation-disco-mathematical-operations}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccc@{}}
+           & \multicolumn{3}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-4}
+    \\       \textbf{Language Tags}
+           & \rot{\emph{Missy}}
+           & \rot{\emph{DwB}}
+           & \rot{\emph{DDA-SND}}
+    \\ \midrule
+    \emph{DISCO-C-LANGUAGE-TAG-MATCHING-01 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-LANGUAGE-TAG-CARDINALITY-01 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-LANGUAGE-TAG-CARDINALITY-02 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-LANGUAGE-TAG-CARDINALITY-03 (!)}\textsuperscript{*} \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Disco Data Sets - Language Tags}
+		\label{tab:evaluation-disco-language-tags}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccc@{}}
+           & \multicolumn{3}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-4}
+    \\       \textbf{Aggregation}
+           & \rot{\emph{Missy}}
+           & \rot{\emph{DwB}}
+           & \rot{\emph{DDA-SND}}
+    \\ \midrule
+    \emph{DISCO-C-AGGREGATION-01 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-AGGREGATION-02 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-AGGREGATION-03 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-AGGREGATION-04 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-AGGREGATION-05 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-AGGREGATION-06 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-AGGREGATION-07 (!)}\textsuperscript{*} \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Disco Data Sets - Aggregation}
+		\label{tab:evaluation-disco-aggregation}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccc@{}}
+           & \multicolumn{3}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-4}
+    \\       \textbf{Disco Constraints}
+           & \rot{\emph{Missy}}
+           & \rot{\emph{DwB}}
+           & \rot{\emph{DDA-SND}}
+    \\ \midrule
+    \emph{DISCO-C-ALLOWED-VALUES-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-LITERAL-RANGES-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-INVERSE-FUNCTIONAL-PROPERTIES-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-INVERSE-FUNCTIONAL-PROPERTIES-02}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-CLASS-SPECIFIC-PROPERTY-RANGE-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-MEMBERSHIP-IN-CONTROLLED-VOCABULARIES-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & \ding{55} \\
+		\emph{DISCO-C-LITERAL-VALUE-COMPARISON-01}\textsuperscript{***} & $\checkmark$ & 1,299 & $\checkmark$ \\
+		\emph{DISCO-C-CONTEXT-SPECIFIC-VALID-PROPERTIES-01}\textsuperscript{*} & 21,038 & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-DATA-PROPERTY-FACETS-01}\textsuperscript{**} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-DATA-PROPERTY-FACETS-02}\textsuperscript{**} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Disco Data Sets - Disco Constraints (1)}
+		\label{tab:evaluation-disco-disco-constraints-1}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccc@{}}
+           & \multicolumn{3}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-4}
+    \\       \textbf{Disco Constraints}
+           & \rot{\emph{Missy}}
+           & \rot{\emph{DwB}}
+           & \rot{\emph{DDA-SND}}
+    \\ \midrule
+		\emph{DISCO-C-VALUE-IS-VALID-FOR-DATATYPE-01}\textsuperscript{***} & 30 & 6,932 & $\checkmark$ \\
+		\emph{DISCO-C-VALUE-IS-VALID-FOR-DATATYPE-02}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DISCO-C-SUBSUMPTION-01 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-CLASS-EQUIVALENCE-01 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-SUB-PROPERTIES-01 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-PROPERTY-DOMAIN-01 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-PROPERTY-RANGES-01 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-INVERSE-OBJECT-PROPERTIES-01 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-INVERSE-OBJECT-PROPERTIES-02 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-INVERSE-OBJECT-PROPERTIES-03 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-DISJOINT-PROPERTIES-01 (!)}\textsuperscript{***} \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Disco Data Sets - Disco Constraints (2)}
+		\label{tab:evaluation-disco-disco-constraints-2}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccc@{}}
+           & \multicolumn{3}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-4}
+    \\       \textbf{Disco Constraints}
+           & \rot{\emph{Missy}}
+           & \rot{\emph{DwB}}
+           & \rot{\emph{DDA-SND}}
+    \\ \midrule
+		\emph{DISCO-C-ASYMMETRIC-OBJECT-PROPERTIES-01 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-IRREFLEXIVE-OBJECT-PROPERTIES-01 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-CLASS-SPECIFIC-IRREFLEXIVE-OBJECT-PROPERTIES-01 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-CLASS-SPECIFIC-IRREFLEXIVE-OBJECT-PROPERTIES-02 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-DISJOINT-CLASSES-01 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-EQUIVALENT-PROPERTIES-01 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-LITERAL-PATTERN-MATCHING-01 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-DISJUNCTION-01 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-UNIVERSAL-QUANTIFICATIONS-01 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01 (!)}\textsuperscript{***} \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Disco Data Sets - Disco Constraints (3)}
+		\label{tab:evaluation-disco-disco-constraints-3}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccc@{}}
+           & \multicolumn{3}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-4}
+    \\       \textbf{Disco Constraints}
+           & \rot{\emph{Missy}}
+           & \rot{\emph{DwB}}
+           & \rot{\emph{DDA-SND}}
+    \\ \midrule
+		\emph{DISCO-C-MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-01 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-CONTEXT-SPECIFIC-EXCLUSIVE-OR-OF-PROPERTY-GROUPS-01 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-IRI-PATTERN-MATCHING-01 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-ORDERING-01 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-ORDERING-02 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-ORDERING-03 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-STRING-OPERATIONS-01 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-CONTEXT-SPECIFIC-VALID-CLASSES-01 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-CONTEXT-SPECIFIC-VALID-PROPERTIES-01 (!)}\textsuperscript{*} \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Disco Data Sets - Disco Constraints (4)}
+		\label{tab:evaluation-disco-disco-constraints-4}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccc@{}}
+           & \multicolumn{3}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-4}
+    \\       \textbf{Disco Constraints}
+           & \rot{\emph{Missy}}
+           & \rot{\emph{DwB}}
+           & \rot{\emph{DDA-SND}}
+    \\ \midrule
+		\emph{DISCO-C-DEFAULT-VALUES-01 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-WHITESPACE-HANDLING-01 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-HTML-HANDLING-01 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-HTML-HANDLING-02 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-RECOMMENDED-PROPERTIES-01 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-HANDLE-RDF-COLLECTIONS-01 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-HANDLE-RDF-COLLECTIONS-02 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-USE-SUB-SUPER-RELATIONS-IN-VALIDATION-01 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-USE-SUB-SUPER-RELATIONS-IN-VALIDATION-02 (!)}\textsuperscript{*} \\
+		\emph{DISCO-C-STRUCTURE-01 (!)}\textsuperscript{***} \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Disco Data Sets - Disco Constraints (5)}
+		\label{tab:evaluation-disco-disco-constraints-5}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccc@{}}
+           & \multicolumn{3}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-4}
+    \\       \textbf{Disco Constraints}
+           & \rot{\emph{Missy}}
+           & \rot{\emph{DwB}}
+           & \rot{\emph{DDA-SND}}
+    \\ \midrule
+		\emph{DISCO-C-VOCABULARY-01 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-HTTP-URI-SCHEME-VIOLATION (!)}\textsuperscript{***} \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Disco Data Sets - Disco Constraints (6)}
+		\label{tab:evaluation-disco-disco-constraints-6}
+    \end{center}
+\end{table}
+
+\section{Aggregated Metadata (Data Cube)}
+
+\subsection{Evaluation Results}
+
+\begin{table}[H]
+	\centering
+		\begin{tabular}{l|l}
+      \textbf{Evaluation Criteria} & \textbf{Counts} \\		
+      \hline
+		\emph{Validated Triples} & 3,775,983,610 \\
+		\emph{Validated Data Sets} & 9,990 \\
+		\hline
+		\emph{Constraint Violations} & 45,635,846 \\
+		\emph{Constraint Violations ($\mathcal{SL}_{0}$)} & 0 $\equiv$ 0\% \\
+		\emph{Constraint Violations ($\mathcal{SL}_{1}$)} & 45,520,613 $\equiv$ 99.75\% \\
+    \emph{Constraint Violations ($\mathcal{SL}_{2}$)} & 115,233 $\equiv$ 0.25\% \\
+		\hline
+		\emph{Constraint (Most Constraint Violations)} & \emph{DATA-MODEL-CONSISTENCY-05} (45,514,102) \\
+		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{0}$))} & - \\
+		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{1}$))} & \emph{DATA-MODEL-CONSISTENCY-05} (45,514,102) \\
+		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{2}$))} & \emph{MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-02} \\
+		                                                                    & (1,556) \\
+		\hline
+		\emph{Constraint Types} & 20 (7\textbar 13) \\
+		\emph{Constraint Types} ($\mathcal{C}_{C}$) & 5 $\equiv$ 25 \% \\
+		\emph{Constraint Types} ($\mathcal{C}_{T}$) & 15 $\equiv$ 75 \% \\
+		\hline
+		\emph{Constraint Types (Most Constraints)} & 1. Data Model Consistency: 11 $\equiv$ 31.4\% (10\textbar 1) \\
+		                                           & 2. Existential Quantifications: 4 $\equiv$ 11.4\% (4\textbar 0) \\
+		\emph{Constraint Type (Most Constraints ($\mathcal{SL}_{2}$))} & Data Model Consistency: 8 $\equiv$ 22.9\% (7\textbar 1) \\
+		\hline
+		\emph{Constraints} & 35 (20\textbar 15) \\
+		\emph{Constraints} ($\mathcal{C}_{C}$) & 16 (12\textbar 4) \\
+		\emph{Constraints} ($\mathcal{C}_{T}$) & 19 (8\textbar 11) \\
+		\emph{Constraints ($\mathcal{SL}_{0}$)} & 4 $\equiv$ 11.4\% (0\textbar 4) \\
+		\emph{Constraints ($\mathcal{SL}_{1}$)} & 3 $\equiv$ 8.6\% (3\textbar 0) \\
+		\emph{Constraints ($\mathcal{SL}_{2}$)} & 28 $\equiv$ 80\% (17\textbar 11) \\
+		\end{tabular}
+    \caption{Evaluation of Data Cube Data Sets - Evaluation Results}
+		\label{tab:data-cube-evaluation-results}
+\end{table}
+
+\subsection{Data Sets Overview}
 
 \begin{itemize}
-	\item DwB Resource Discovery Portal
-	\begin{itemize}
-	  \item Metadata records for each study are available on the study landing pages.
-		\item \url{http://dwb-dev.nsd.uib.no/portal/#/study/http://portal.dwbproject.org/resource/Study/de.gesis/zacat/ZA5597/en}
-    \item Search interface: \url{http://dwb-dev.nsd.uib.no/portal/#/search?q=smoking&p=1&s=score&d=desc&f=text}
-	\end{itemize}
+  \item overview over Data Cube data sets\footnote{\url{http://270a.info/}; \url{http://datahub.io/de/dataset?tags=format-qb}} 
+  \item \url{http://ontologycentral.com/}
 \end{itemize}
 
-\section{Data Cube}
+%\begin{table}
+	%\centering
+		%\begin{tabular}{l|c|c|c|c|c|c}
+      %\textbf{Data Set} & \textbf{triples} & \textbf{data sets} & \textbf{data structure definitions} & \textbf{observations} & \textbf{slices} & \textbf{dimensions} \\		
+      %\hline
+      %European Central Bank (ECB)\tablefootnote{\url{http://www.ecb.europa.eu/home/html/index.en.html}} &  &  &  &  &  &  \\
+			%UNESCO Institute for Statistics (UIS)\tablefootnote{\url{http://www.uis.unesco.org/Pages/default.aspx}} &  &  &  &  &  &  \\
+			%International Monetary Fund (IMF)\tablefootnote{\url{http://www.imf.org/external/index.htm}} &  &  &  &  &  &  \\
+			%Bundesamt für Statistik - Swiss Federal Statistics (BFS)\tablefootnote{\url{http://www.bfs.admin.ch/}} &  &  &  &  &  &  \\
+			%Food and Agriculture Organization of the United Nations (FAO)\tablefootnote{\url{http://www.fao.org/home/en/}} &  &  &  &  &  &  \\
+			%World Bank (WB)\tablefootnote{\url{http://www.worldbank.org/}} &  &  &  &  &  &  \\
+			%Federal Reserve Board (FRB)\tablefootnote{\url{http://www.federalreserve.gov/}} &  &  &  &  &  &  \\
+			%Transparency International (TI)\tablefootnote{\url{http://www.transparency.org/}} &  &  &  &  &  &  \\
+			%Organisation for Economic Co-operation and Development (OECD)\tablefootnote{\url{http://www.oecd.org/}} &  &  &  &  &  &  \\
+			%Bank for International Settlements (BIS)\tablefootnote{\url{http://www.bis.org/}} &  &  &  &  &  &  \\
+			%Australian Bureau of Statistics (ABS)\tablefootnote{\url{http://abs.gov.au/}} &  &  &  &  &  &  \\
+		%\end{tabular}
+	%\caption{Data Cube Data Sets}
+	%\label{tab:data-cube-data-sets}
+%\end{table}
+
+\begin{table}[H]
+	\centering
+		\begin{tabular}{l|l}
+      \textbf{Abbr.} & \textbf{Data Cube Data Sets} \\		
+      \hline
+    \emph{ECB} & \emph{European Central Bank}\tablefootnote{\url{http://www.ecb.europa.eu/home/html/index.en.html}} \\
+		\emph{UIS} & \emph{UNESCO Institute for Statistics}\tablefootnote{\url{http://www.uis.unesco.org/Pages/default.aspx}} \\
+		\emph{IMF} & \emph{International Monetary Fund}\tablefootnote{\url{http://www.imf.org/external/index.htm}} \\
+		\emph{BFS} & \emph{Bundesamt für Statistik - Swiss Federal Statistics}\tablefootnote{\url{http://www.bfs.admin.ch/}} \\
+		\emph{FAO} & \emph{Food and Agriculture Organization of the United Nations}\tablefootnote{\url{http://www.fao.org/home/en/}} \\
+		\emph{WB} & \emph{World Bank}\tablefootnote{\url{http://www.worldbank.org/}} \\
+		\emph{FRB} & \emph{Federal Reserve Board}\tablefootnote{\url{http://www.federalreserve.gov/}} \\
+		\emph{TI} & \emph{Transparency International}\tablefootnote{\url{http://www.transparency.org/}} \\
+		\emph{OECD} & \emph{Organisation for Economic Co-operation and Development}\tablefootnote{\url{http://www.oecd.org/}} \\
+		\emph{BIS} & \emph{Bank for International Settlements}\tablefootnote{\url{http://www.bis.org/}} \\
+		\emph{ABS} & \emph{Australian Bureau of Statistics}\tablefootnote{\url{http://abs.gov.au/}} \\
+		\emph{IEEE-VIS} & \emph{IEEE VIS Source Data} \\
+		\emph{ACORN-SAT} & \emph{Australian Climate Observations Reference Network - Surface Air Temperature Dataset} \\
+		\emph{HDP} & \emph{HealthData.gov Platform (HDP) on the Semantic Web} \\
+		\emph{Eurostat} & \emph{The Eurostat Linked Data} (SPARQL endpoint unavailable) \\
+		\emph{Asturias} & \emph{Nomenclator Asturias} (SPARQL endpoint unavailable!) \\
+		\emph{ISTAT} & \emph{ISTAT Immigration (LinkedOpenData.it)} (SPARQL endpoint unavailable) \\
+		\emph{ICANE} & \emph{Statistical Office of Cantabria (Instituto Cántabro de Estadística, ICANE)} \\ 
+		      & (SPARQL endpoint unavailable) \\
+		\emph{EE-2009} & \emph{European Election Results 2009} (SPARQL endpoint unavailable) \\
+		\emph{EU-B} & \emph{Standard Eurobarometer} (SPARQL endpoint unavailable) \\
+		\emph{ECB-S} & \emph{European Central Bank Statistics (PublicData.eu)} (SPARQL endpoint unavailable) \\
+		\emph{CPV-2008} & \emph{Common Procurement Vocabulary (CPV) 2008} (SPARQL endpoint unavailable) \\
+		\emph{CPV-2003} & \emph{Common Procurement Vocabulary (CPV) 2003} (SPARQL endpoint unavailable) \\
+		%GHI-2011 & Global Hunger Index (GHI) 2011 (dump) \\
+		\end{tabular}
+	\caption{Data Cube Data Sets Abbreviations}
+	\label{tab:data-cube-data-sets-abbreviations}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccccccccccc@{}}
+           & \multicolumn{5}{c}{\textbf{Counts}}
+    \\  \cmidrule{2-6}
+    \\       \textbf{Data Sets}
+           & \textbf{\rot{triples}}
+           & \textbf{\rot{qb:DataSet}}
+           & \textbf{\rot{qb:DataStructureDefinition}}
+           & \textbf{\rot{qb:Observation}}
+           & \textbf{\rot{qb:Slice}}
+    \\ \midrule
+    \emph{ECB} & 468,899,474 & 55 & 46 & $>$11,000,000 & 428,698 \\
+		\emph{UIS} & 10,400,534 & 5 & 5 & 1,437,651 & 0 &  \\
+		\emph{IMF} & 35,688,446 & 4 & 8 & 3,603,719 & 0 &  \\
+		\emph{BFS} & 1,533,743 & 0 & 0 & 8 & 0 &  \\
+		\emph{FAO} & 53,000,000 & 10 & 10 & $>$7,100,000 & 0 \\
+		\emph{WB} & 174,006,552 & 9,466 & 59 & $>$17,000,000 & 0 \\
+		\emph{FRB} & 185,266,900 & 49 & 98 & $>$9,500,000 & 0 \\
+		\emph{TI} & 52,233 & 6 & 6 & 3,928 & 0 \\
+		\emph{OECD} & 304,995,160 & 136 & 140 & $>$12,000,000 & 0 \\
+		\emph{BIS} & 54,197,482 & 6 & 12 & 3,606,466 & 47,914 \\
+		\emph{ABS} & 2,357,400,000 & 253 & 257 & $>$11,000,000 & 0  \\
+		\emph{IEEE-VIS} & 19,935,340 & 0 & 0 & 1,350 & 0 \\
+		\emph{ACORN-SAT} & 98,381,319 & 0 & 4 & 0 & 0 \\
+		\emph{HDP} & 12,226,427 & 0 & 0 & 0 & 0 \\
+		%Eurostat & 8,000,000,000 &  &  &  &  &  \\
+		%Asturias & 4,508,050 &  &  &  &  &  \\
+		%ISTAT & 3,024,396 &  &  &  &  &  \\
+		%ICANE & 52,412 &  &  &  &  &  \\
+		%EE-2009 & 3,165 &  &  &  &  &  \\
+		%EU-B & 1,193,494 &  &  &  &  &  \\
+		%ECB-S & 10,000,000 &  &  &  &  &  \\
+		%CPV-2008 & 803,311 &  &  &  &  &  \\
+		%CPV-2003 & 546,135 &  &  &  &  &  \\
+		%GHI-2011 & 19,369 (dump) &  &  &  &  &  \\
+		\hline
+		\textbf{Total} & 3,775,983,610 & 9,990 & & & & \\
+    \bottomrule
+    \end{tabular}
+    \caption{Data Cube Data Sets Overview}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+	\centering
+		\begin{tabular}{l|l}
+      \textbf{Data Sets} & \textbf{SPARQL Endpoints} \\		
+      \hline
+      \emph{ECB} & \url{http://ecb.270a.info/sparql} \\
+			\emph{UIS} & \url{http://uis.270a.info/sparql} \\
+			\emph{IMF} & \url{http://imf.270a.info/sparql} \\
+			\emph{BFS} & \url{http://bfs.270a.info/sparql} \\
+			\emph{FAO} & \url{http://fao.270a.info/sparql} \\
+			\emph{WB} & \url{http://worldbank.270a.info/sparql} \\
+			\emph{FRB} & \url{http://frb.270a.info/sparql} \\
+			\emph{TI} & \url{http://transparency.270a.info/sparql} \\
+			\emph{OECD} & \url{http://oecd.270a.info/sparql} \\
+			\emph{BIS} & \url{http://bis.270a.info/sparql} \\
+			\emph{ABS} & \url{http://abs.270a.info/sparql} \\
+			\emph{ACORN-SAT} & \url{http://lab.environment.data.gov.au/sparql} \\
+			\emph{HDP} & \url{http://healthdata.tw.rpi.edu/sparql} \\
+		\end{tabular}
+	\caption{Data Cube SPARQL Endpoints}
+	\label{tab:data-cube-sparql-endpoints}
+\end{table}
+
+\subsection{Detailed Evaluation}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccccccc@{}}
+           & \multicolumn{7}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-8}
+    \\       \textbf{Data Model Consistency}
+           & \rot{\emph{ECB}}
+           & \rot{\emph{UIS}}
+           & \rot{\emph{IMF}}
+           & \rot{\emph{BFS}}
+           & \rot{\emph{FAO}}
+					 & \rot{\emph{WB}}
+					 & \rot{\emph{FRB}}
+    \\ \midrule
+    \emph{DATA-MODEL-CONSISTENCY-01}\textsuperscript{**} & $\checkmark$ (2) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    \emph{DATA-MODEL-CONSISTENCY-02}\textsuperscript{***} & $\checkmark$ (2) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    \emph{DATA-MODEL-CONSISTENCY-03}\textsuperscript{***} & $\checkmark$ (2) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    \emph{DATA-MODEL-CONSISTENCY-04}\textsuperscript{***} & $\checkmark$ (6) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & 14,372 \\
+		\emph{DATA-MODEL-CONSISTENCY-05}\textsuperscript{**} & 1,198,352 (50) & \ding{55} & \ding{55} & $\checkmark$ & \ding{55} & $\checkmark$ & 16,175,814 (42) \\
+		\emph{DATA-MODEL-CONSISTENCY-06}\textsuperscript{***} & $\checkmark$ (2) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DATA-MODEL-CONSISTENCY-07}\textsuperscript{***} & $\checkmark$ (9) & $\checkmark$ & 99,091 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ (1) \\
+		\emph{DATA-MODEL-CONSISTENCY-08}\textsuperscript{***} & $\checkmark$ (2) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DATA-MODEL-CONSISTENCY-09}\textsuperscript{***} & $\checkmark$ (2) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DATA-MODEL-CONSISTENCY-10}\textsuperscript{***} (!) & - & - & - & - & - & - & - \\
+		\emph{DATA-MODEL-CONSISTENCY-11}\textsuperscript{**} & 6,511 (10) & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Data Cube Data Sets - Data Model Consistency (1)}
+		\label{evaluation-of-data-cube-data-sets-data-model-consistency-1}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccccccc@{}}
+           & \multicolumn{7}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-8}
+    \\       \textbf{Data Model Consistency}
+					 & \rot{\emph{TI}}
+					 & \rot{\emph{OECD}}
+					 & \rot{\emph{BIS}}
+					 & \rot{\emph{ABS}}
+					 & \rot{\emph{IEEE-VIS}}
+					 & \rot{\emph{ACORN-SAT}}
+					 & \rot{\emph{HDP}}
+    \\ \midrule
+    \emph{DATA-MODEL-CONSISTENCY-01}\textsuperscript{**} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    \emph{DATA-MODEL-CONSISTENCY-02}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & 8 & $\checkmark$ \\
+    \emph{DATA-MODEL-CONSISTENCY-03}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    \emph{DATA-MODEL-CONSISTENCY-04}\textsuperscript{***} & $\checkmark$ & $\checkmark$& $\checkmark$ & $\checkmark$ (6) & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DATA-MODEL-CONSISTENCY-05}\textsuperscript{**} & $\checkmark$ & 21,142,838 (116) & \ding{55} &  6,997,098 (246) & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DATA-MODEL-CONSISTENCY-06}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DATA-MODEL-CONSISTENCY-07}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ (8) & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DATA-MODEL-CONSISTENCY-08}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DATA-MODEL-CONSISTENCY-09}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{DATA-MODEL-CONSISTENCY-10}\textsuperscript{***} (!) & - & - & - & - & - & - & - \\
+		\emph{DATA-MODEL-CONSISTENCY-11}\textsuperscript{**} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Data Cube Data Sets - Data Model Consistency (2)}
+		\label{evaluation-of-data-cube-data-sets-data-model-consistency-1}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccccccccccccc@{}}
+           & \multicolumn{14}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-15}
+    \\       \textbf{Existential Quantifications}
+           & \rot{\emph{ECB}}
+           & \rot{\emph{UIS}}
+           & \rot{\emph{IMF}}
+           & \rot{\emph{BFS}}
+           & \rot{\emph{FAO}}
+					 & \rot{\emph{WB}}
+					 & \rot{\emph{FRB}}
+					 & \rot{\emph{TI}}
+					 & \rot{\emph{OECD}}
+					 & \rot{\emph{BIS}}
+					 & \rot{\emph{ABS}}
+					 & \rot{\emph{IEEE-VIS}}
+					 & \rot{\emph{ACORN-SAT}}
+					 & \rot{\emph{HDP}}
+    \\ \midrule
+		\emph{EXISTENTIAL-QUANTIFICATIONS-01}\textsuperscript{***} & 9 & $\checkmark$ & 11 & 7 & 8 & 77 & 8 & 9 & 7 & 8 & 7 & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{EXISTENTIAL-QUANTIFICATIONS-02}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{EXISTENTIAL-QUANTIFICATIONS-03}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & 59 & $\checkmark$ & 6 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & 4 & $\checkmark$ \\
+		\emph{EXISTENTIAL-QUANTIFICATIONS-04}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Data Cube Data Sets - Existential Quantifications}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccccccccc@{}}
+           & \multicolumn{10}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-11}
+    \\       \textbf{Cardinality Restrictions}
+           & \rot{\emph{ECB}}
+           & \rot{\emph{UIS}}
+           & \rot{\emph{IMF}}
+           & \rot{\emph{BFS}}
+           & \rot{\emph{FAO}}
+					 & \rot{\emph{WB}}
+					 & \rot{\emph{FRB}}
+					 & \rot{\emph{TI}}
+					 & \rot{\emph{OECD}}
+					 & \rot{\emph{BIS}}
+    \\ \midrule
+		\emph{MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01 (!)}\textsuperscript{***} & - & - & - & - & - & - & - & - & - & - \\
+		\emph{MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-02}\textsuperscript{***} & \ding{55} & 118 & 8 & 8 & 30 & $\checkmark$ & 30 & $\checkmark$ & \ding{55} & 12 \\
+		\emph{MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & 1 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Data Cube Data Sets - Cardinality Restrictions (1)}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccc@{}}
+           & \multicolumn{4}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-5}
+    \\       \textbf{Cardinality Restrictions}
+					 & \rot{\emph{ABS}}
+					 & \rot{\emph{IEEE-VIS}}
+					 & \rot{\emph{ACORN-SAT}}
+					 & \rot{\emph{HDP}}
+    \\ \midrule
+		\emph{MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01 (!)}\textsuperscript{***} & - & - & - & - \\
+		\emph{MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-02}\textsuperscript{***} & \ding{55} & 1,350 & $\checkmark$ & $\checkmark$ \\
+		\emph{MAXIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-01}\textsuperscript{***} & $\checkmark$ (2) & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{EXACT-UNQUALIFIED-CARDINALITY-RESTRICTIONS-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Data Cube Data Sets - Cardinality Restrictions (2)}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccccccccccccc@{}}
+           & \multicolumn{14}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-15}
+    \\       \textbf{Structure}
+           & \rot{\emph{ECB}}
+           & \rot{\emph{UIS}}
+           & \rot{\emph{IMF}}
+           & \rot{\emph{BFS}}
+           & \rot{\emph{FAO}}
+					 & \rot{\emph{WB}}
+					 & \rot{\emph{FRB}}
+					 & \rot{\emph{TI}}
+					 & \rot{\emph{OECD}}
+					 & \rot{\emph{BIS}}
+					 & \rot{\emph{ABS}}
+					 & \rot{\emph{IEEE-VIS}}
+					 & \rot{\emph{ACORN-SAT}}
+					 & \rot{\emph{HDP}}
+    \\ \midrule
+		\emph{STRUCTURE-01}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{STRUCTURE-02}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Data Cube Data Sets - Structure}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccccccccccccc@{}}
+           & \multicolumn{14}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-15}
+    \\       \textbf{Constraints}
+           & \rot{\emph{ECB}}
+           & \rot{\emph{UIS}}
+           & \rot{\emph{IMF}}
+           & \rot{\emph{BFS}}
+           & \rot{\emph{FAO}}
+					 & \rot{\emph{WB}}
+					 & \rot{\emph{FRB}}
+					 & \rot{\emph{TI}}
+					 & \rot{\emph{OECD}}
+					 & \rot{\emph{BIS}}
+					 & \rot{\emph{ABS}}
+					 & \rot{\emph{IEEE-VIS}}
+					 & \rot{\emph{ACORN-SAT}}
+					 & \rot{\emph{HDP}}
+    \\ \midrule
+		\emph{PROPERTY-DOMAIN-01 (!)}\textsuperscript{***} &  &  &  &  &  &  &  &  &  &  &  &  \\
+		\emph{PROPERTY-RANGES-01 (!)}\textsuperscript{***} &  &  &  &  &  &  &  &  &  &  &  &  \\
+		\emph{DISJOINT-PROPERTIES-01 (!)}\textsuperscript{***} &  &  &  &  &  &  &  &  &  &  &  &  \\
+		\emph{DISJOINT-CLASSES-01 (!)}\textsuperscript{***} &  &  &  &  &  &  &  &  &  &  &  &  \\
+		\emph{EQUIVALENT-PROPERTIES-01 (!)}\textsuperscript{*} &  &  &  &  &  &  &  &  &  &  &  &  \\
+		\emph{UNIVERSAL-QUANTIFICATIONS-01 (!)}\textsuperscript{***} &  &  &  &  &  &  &  &  &  &  &  &  \\
+		\emph{MEMBERSHIP-IN-CONTROLLED-VOCABULARIES-01 (!)}\textsuperscript{***} &  &  &  &  &  &  &  &  &  &  &  &  \\
+		\emph{CONTEXT-SPECIFIC-VALID-CLASSES-01 (!)}\textsuperscript{*} &  &  &  &  &  &  &  &  &  &  &  &  \\
+		\emph{CONTEXT-SPECIFIC-VALID-PROPERTIES-01 (!)}\textsuperscript{*} &  &  &  &  &  &  &  &  &  &  &  &  \\
+		\emph{RECOMMENDED-PROPERTIES-01 (!)}\textsuperscript{*} &  &  &  &  &  &  &  &  &  &  &  &  \\
+		\emph{VALUE-IS-VALID-FOR-DATATYPE-01 (!)}\textsuperscript{***} &  &  &  &  &  &  &  &  &  &  &  &  \\
+		\emph{VOCABULARY-01 (!)}\textsuperscript{***} &  &  &  &  &  &  &  &  &  &  &  &  \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Data Cube Data Sets - Constraints (1)}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccccccccccccc@{}}
+           & \multicolumn{14}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-15}
+    \\       \textbf{Constraints}
+           & \rot{\emph{ECB}}
+           & \rot{\emph{UIS}}
+           & \rot{\emph{IMF}}
+           & \rot{\emph{BFS}}
+           & \rot{\emph{FAO}}
+					 & \rot{\emph{WB}}
+					 & \rot{\emph{FRB}}
+					 & \rot{\emph{TI}}
+					 & \rot{\emph{OECD}}
+					 & \rot{\emph{BIS}}
+					 & \rot{\emph{ABS}}
+					 & \rot{\emph{IEEE-VIS}}
+					 & \rot{\emph{ACORN-SAT}}
+					 & \rot{\emph{HDP}}
+    \\ \midrule
+		\emph{HTTP-URI-SCHEME-VIOLATION (!)}\textsuperscript{***} \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation of Data Cube Data Sets - Constraints (2)}
+    \end{center}
+\end{table}
+
+\section{Thesauri (SKOS)}
+
+\subsection{Evaluation Results}
+
+\begin{table}[H]
+	\centering
+		\begin{tabular}{l|l}
+      \textbf{Evaluation Criteria} & \textbf{Counts} \\		
+      \hline
+		\emph{Validated Triples} & \textcolor{red}{XXXXX} \\
+		\emph{Validated Data Sets} & \textcolor{red}{XXXXX} \\
+		\hline
+		\emph{Constraint Violations} & \textcolor{red}{XXXXX} \\
+		\emph{Constraint Violations ($\mathcal{SL}_{0}$)} & \textcolor{red}{XXXXX} \\
+		\emph{Constraint Violations ($\mathcal{SL}_{1}$)} & \textcolor{red}{XXXXX} $\equiv$ \textcolor{red}{XXXXX}\% \\
+    \emph{Constraint Violations ($\mathcal{SL}_{2}$)} & \textcolor{red}{XXXXX} \\
+		\hline
+		\emph{Constraint (Most Constraint Violations)} & \emph{LANGUAGE-TAG-CARDINALITY-01} (2,508,903) \\
+		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{0}$))} & \emph{LABELING-AND-DOCUMENTATION-06} (1,022,362) \\
+		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{1}$))} & \emph{LANGUAGE-TAG-CARDINALITY-01} (2,508,903) \\
+		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{2}$))} & - \\
+		\hline
+		\emph{Constraint Types} & 14 (4\textbar 10) \\
+		\emph{Constraint Types} ($\mathcal{C}_{C}$) & 5 $\equiv$ 35.7\% \\
+		\emph{Constraint Types} ($\mathcal{C}_{T}$) & 9 $\equiv$ 64.3\% \\
+		\hline
+		\emph{Constraint Types (Most Constraints)} & 1. Structure: 10 $\equiv$ XX\% (8\textbar 2) \\
+		                                           & 2. Labeling and Documentation: 6 $\equiv$ XX\% (5\textbar 1) \\
+																							 & 3. Language Tag Cardinality: 4 $\equiv$ XX\% (4\textbar 0) \\
+		\emph{Constraint Type (Most Constraints ($\mathcal{SL}_{2}$))} & Structure: 1 (0\textbar 1) \\
+		\hline
+		\emph{Constraints} & 35 (17\textbar 18) \\
+		\emph{Constraints} ($\mathcal{C}_{C}$) & 21 (13\textbar 8) \\
+		\emph{Constraints} ($\mathcal{C}_{T}$) & 14 (4\textbar 10) \\
+		\emph{Constraints ($\mathcal{SL}_{0}$)} & 21 $\equiv$ 60\% (12\textbar 9) \\
+		\emph{Constraints ($\mathcal{SL}_{1}$)} & 5 $\equiv$ 14.3\% (5\textbar 0) \\
+		\emph{Constraints ($\mathcal{SL}_{2}$)} & 9 $\equiv$ 25.7\% (0\textbar 9) \\
+		\end{tabular}
+    \caption{Evaluation of Thesauri Data Sets - Evaluation Results}
+		\label{tab:thesauri-evaluation-results}
+\end{table}
+
+\subsection{Data Sets Overview}
 
 \begin{itemize}
-	\item \url{http://270a.info/} (see the VoID which points to other
-VoIDs) is full of data sets (probably close to 10k) using RDF Data Cube,
-and some of those also include XKOS.
+  \item overview over SKOS data sets\footnote{\url{http://datahub.io/de/dataset?tags=format-skos}}
+	\item overview over thesauri\footnote{\url{http://datahub.io/de/dataset?tags=thesaurus}} (table \ref{tab:thesauri-overview})
 \end{itemize}
+
+\begin{table}[H]
+	\centering
+		\begin{tabular}{l|l}
+      \textbf{Abbr.} & \textbf{Thesauri} \\		
+      \hline
+    \emph{TheSoz} & \emph{Thesaurus for the Social Sciences}\tablefootnote{\url{http://www.ecb.europa.eu/home/html/index.en.html}} \\
+	  \emph{STW} & \emph{Thesaurus for Economics}\tablefootnote{\url{http://zbw.eu/stw/versions/latest/about}} \\
+	  \emph{AGROVOC} & \emph{AGROVOC Multilingual agricultural thesaurus}\tablefootnote{\url{http://202.45.139.84:10035/catalogs/fao/repositories/agrovoc}} \\
+		\emph{UNESCO} & \emph{UNESCO Thesaurus}\tablefootnote{\url{http://skos.um.es/sparql/}} \\
+		\emph{TGN} & \emph{The Getty Thesaurus of Geographic Names}\tablefootnote{\url{http://vocab.getty.edu/sparql}} \\
+		\emph{EARTh} & \emph{Environmental Applications Reference Thesaurus}\tablefootnote{\url{http://linkeddata.ge.imati.cnr.it/resource/EARTh/}} \\
+		\emph{ODT} & \emph{Open Data Thesaurus}\tablefootnote{\url{http://vocabulary.semantic-web.at/PoolParty/wiki/OpenData}} \\
+		\emph{SLD} & \emph{Spanish Linguistic Datasets}\tablefootnote{\url{http://linguistic.linkeddata.es}} \\
+		\emph{SSWT} & \emph{Social Semantic Web Thesaurus}\tablefootnote{\url{http://vocabulary.semantic-web.at/PoolParty/wiki/semweb}} \\
+		\emph{GBA-GU} & \emph{Thesaurus of the Geological Survey of Austria (GBA) - Geology Unit}\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
+		\emph{GBA-GTS} & \emph{Thesaurus of the Geological Survey of Austria (GBA) - Geologic Time Scale}\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
+		\emph{GBA-L} & \emph{Thesaurus of the Geological Survey of Austria (GBA) - Lithology}\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
+		\emph{GBA-LU} & \emph{Thesaurus of the Geological Survey of Austria (GBA) - Lithotectonic Unit}\tablefootnote{\url{http://resource.geolba.ac.at/}} \\
+		\emph{GEMET} & \emph{GEneral Multilingual Environmental Thesaurus}\tablefootnote{\url{http://www.eionet.europa.eu/gemet/}} \\
+		\emph{EuroVoc} & \emph{EuroVoc}\tablefootnote{\url{http://open-data.europa.eu/de/data/dataset/eurovoc}} \\
+		\emph{CECCT} & \emph{Clean Energy and Climate Change Thesaurus}\tablefootnote{\url{http://data.reegle.info/thesaurus/guide}} \\
+		\end{tabular}
+	\caption{Thesauri Abbreviations}
+	\label{tab:thesauri-abbreviations}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccccccccccc@{}}
+           & \multicolumn{7}{c}{\textbf{Counts}}
+    \\  \cmidrule{2-8}
+    \\       \textbf{Thesauri}
+           & \textbf{\rot{triples}}
+           & \textbf{\rot{skos:ConceptScheme}}
+           & \textbf{\rot{sko:Concept}}
+           & \textbf{\rot{skos:broader}}
+           & \textbf{\rot{skos:narrower}}
+					 & \textbf{\rot{skos:hasTopConcept}}
+					 & \textbf{\rot{skos:inScheme}}
+    \\ \midrule
+    \emph{TheSoz} & 439,153 & 1 & 8,426 & 13,705 & 13,706 & 0 & 48,529 \\
+	  \emph{STW} & 221,668 & 1 & 13,468 & 13,732 & 13732 & 7 & 13,180 \\
+	  \emph{AGROVOC} & 6,080,477 & 1 & 32,310 & 33,507 & 33,507 & 25 & 32,310 \\
+		\emph{UNESCO} & 288,346 & 9 & 26,714 & 20,028 & 20,028 & 607 & 32,009 \\
+		\emph{TGN} & 16,112,321 & 8 & 2,898,775 & 0 & 0 & 0 & 1,453,767\\
+		\emph{EARTh} & 9,287,364 & 11 & 295,375 & 288,208 & 93,827 & 479 & 295,376 \\
+		\emph{ODT} & 3,290 & 6 & 108 & 93 & 93 & 30 & 0 \\
+		\emph{SLD} & 7,629,211 & 0 & 31,195 & 0 & 0 & 0 & 0 \\
+		\emph{SSWT} & 64,698 & 9 & 2,127 & 2,300 & 2,301 & 38 & 0 \\
+		\emph{GBA-GU} & 25,718 & 3 & 878 & 1,005 & 1,005 & 14 & 0 \\
+		\emph{GBA-GTS} & 7,875 & 3 & 213 & 208 & 208 & 5 & 0 \\
+		\emph{GBA-L} & 9,317 & 1 & 249 & 249 & 249 & 4 & 0 \\
+		\emph{GBA-LU} & 9,504 & 3 & 364 & 359 & 359 & 7 & 0 \\
+		\emph{GEMET} & 372,889,229 & 3,680 & 414,659 & 62,193 & 21,685 & 30,806 & 409,290 \\
+		\emph{EuroVoc} & 64,477,774 & 439 & 79,557 & 6,922 & 0 & 532 & 14,428 \\
+		\emph{CECCT} & 191,336 & 3 & 3,419 & 3,761 & 3,762 & 28 & 0 \\
+		\hline
+		\textbf{Total} & 477,737,281 & 4,178 & & & & \\
+    \bottomrule
+    \end{tabular}
+    \caption{Thesauri Overview}
+		\label{tab:thesauri-overview}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+	\centering
+		\begin{tabular}{l|l}
+      \textbf{Thesauri} & \textbf{SPARQL Endpoints} \\		
+      \hline
+      \emph{TheSoz} & \url{http://lod.gesis.org/thesoz/sparql} \\
+			\emph{STW} & \url{http://zbw.eu/beta/sparql/stw/query} \\
+			\emph{AGROVOC} & \url{http://202.45.139.84:10035/catalogs/fao/repositories/agrovoc} \\
+			\emph{UNESCO} & \url{http://skos.um.es/sparql/} \\
+			\emph{TGN} & \url{http://vocab.getty.edu/} \\
+			\emph{EARTh} & \url{http://linkeddata.ge.imati.cnr.it:8890/sparql} \\
+			\emph{ODT} & \url{http://vocabulary.semantic-web.at/PoolParty/sparql/OpenData} \\
+			\emph{SLD} & \url{http://linguistic.linkeddata.es/sparql} \\
+			\emph{SSWT} & \url{http://vocabulary.semantic-web.at/PoolParty/sparql/semweb} \\
+			\emph{GBA-GU} & \url{http://resource.geolba.ac.at/PoolParty/sparql/GeologicUnit} \\
+			\emph{GBA-GTS} & \url{http://resource.geolba.ac.at/PoolParty/sparql/GeologicTimeScale} \\
+			\emph{GBA-L} & \url{http://resource.geolba.ac.at/PoolParty/sparql/lithology} \\
+			\emph{GBA-LU} & \url{http://resource.geolba.ac.at/PoolParty/sparql/tectonicunit} \\
+			\emph{GEMET} & \url{http://semantic.eea.europa.eu/sparql} \\
+			\emph{EuroVoc} & \url{http://open-data.europa.eu/de/linked-data} \\
+			\emph{CECCT} & \url{http://poolparty.reegle.info/PoolParty/sparql/glossary}
+		\end{tabular}
+	\caption{Thesauri SPARQL Endpoints}
+	\label{tab:thesauri-sparql-endpoints}
+\end{table}
+
+\subsection{Detailed Evaluation}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccccccccccc@{}}
+           & \multicolumn{12}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-13}
+    \\       \textbf{Data Model Consistency}
+           & \emph{\rot{TheSoz}}
+           & \emph{\rot{STW}}
+           & \emph{\rot{AGROVOC}}
+					 & \emph{\rot{TGN}}
+           & \emph{\rot{UNESCO}}
+					 & \emph{\rot{ODT}}
+					 & \emph{\rot{SSWT}}
+					 & \emph{\rot{GBA-GU}}
+					 & \emph{\rot{GBA-GTS}}
+					 & \emph{\rot{GBA-L}}
+					 & \emph{\rot{GBA-LU}}
+					 & \emph{\rot{CECCT}}
+    \\ \midrule
+    \emph{DATA-MODEL-CONSISTENCY-01 (!)}\textsuperscript{*} &  &  &  &  &  & \\
+    \emph{DATA-MODEL-CONSISTENCY-02 (!)}\textsuperscript{*} &  &  &  &  &  & \\
+    \emph{DATA-MODEL-CONSISTENCY-03 (!)}\textsuperscript{*} &  &  &  &  &  & \\
+    \bottomrule
+    \end{tabular}
+    \caption{Thesauri Evaluation - Data Model Consistency (1)}
+		\label{tab:thesauri-evaluation-data-model-consistency-1}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccc@{}}
+           & \multicolumn{4}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-5}
+    \\       \textbf{Data Model Consistency}
+					 & \emph{\rot{EARTh}}
+					 & \emph{\rot{GEMET}}
+					 & \emph{\rot{EuroVoc}}
+					 & \emph{\rot{SLD}}
+    \\ \midrule
+    \emph{DATA-MODEL-CONSISTENCY-01 (!)}\textsuperscript{*} \\
+    \emph{DATA-MODEL-CONSISTENCY-02 (!)}\textsuperscript{*} \\
+    \emph{DATA-MODEL-CONSISTENCY-03 (!)}\textsuperscript{*} \\
+    \bottomrule
+    \end{tabular}
+    \caption{Thesauri Evaluation - Data Model Consistency (2)}
+		\label{tab:thesauri-evaluation-data-model-consistency-2}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccccccccccc@{}}
+           & \multicolumn{12}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-13}
+    \\       \textbf{Labeling and Documentation}
+           & \emph{\rot{TheSoz}}
+           & \emph{\rot{STW}}
+           & \emph{\rot{AGROVOC}}
+					 & \emph{\rot{TGN}}
+           & \emph{\rot{UNESCO}}
+					 & \emph{\rot{ODT}}
+					 & \emph{\rot{SSWT}}
+					 & \emph{\rot{GBA-GU}}
+					 & \emph{\rot{GBA-GTS}}
+					 & \emph{\rot{GBA-L}}
+					 & \emph{\rot{GBA-LU}}
+					 & \emph{\rot{CECCT}}
+    \\ \midrule
+		\emph{LABELING-AND-DOCUMENTATION-01}\textsuperscript{*} & 8,426 & 11,508 & 19,829 & 1,110 & \ding{55} & 36 & 1,475 & 5 & 2 & $\checkmark$ & 107 & 486 \\
+		\emph{LABELING-AND-DOCUMENTATION-02}\textsuperscript{*} & $>$1 & \ding{55} & $>$100 & 287 & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{LABELING-AND-DOCUMENTATION-03}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & 1 & 14,114 & \ding{55} & $\checkmark$ & $\checkmark$ & 1 & $\checkmark$ & $\checkmark$ & 1 & $\checkmark$ \\
+		\emph{LABELING-AND-DOCUMENTATION-04 (!)}\textsuperscript{*} &  &  &  &  &  & & &  \\
+		\emph{LABELING-AND-DOCUMENTATION-05}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & 4 & $\checkmark$ & 1 & 2 & 2 & 1 & $\checkmark$ & $\checkmark$ & $\checkmark$ & 7 \\
+		\emph{LABELING-AND-DOCUMENTATION-06}\textsuperscript{*} & 975,340 & $\checkmark$ & $\checkmark$ & 2 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\
+    \bottomrule
+    \end{tabular}
+    \caption{Thesauri Evaluation - Labeling and Documentation (1)}
+		\label{tab:thesauri-evaluation-labeling-and-documentation-1}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccc@{}}
+           & \multicolumn{4}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-5}
+    \\       \textbf{Labeling and Documentation}
+					 & \emph{\rot{EARTh}}
+					 & \emph{\rot{GEMET}}
+					 & \emph{\rot{EuroVoc}}
+					 & \emph{\rot{SLD}}
+    \\ \midrule
+		\emph{LABELING-AND-DOCUMENTATION-01}\textsuperscript{*}& 264,687 & \ding{55} & 54,911 & 31,195 \\
+		\emph{LABELING-AND-DOCUMENTATION-02}\textsuperscript{*} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+		\emph{LABELING-AND-DOCUMENTATION-03}\textsuperscript{*} & 2 & \ding{55} & 55,556 & 31,195 \\
+		\emph{LABELING-AND-DOCUMENTATION-04 (!)}\textsuperscript{*} & \\
+		\emph{LABELING-AND-DOCUMENTATION-05}\textsuperscript{*} & 39 & \ding{55} & \ding{55} & 978 \\
+		\emph{LABELING-AND-DOCUMENTATION-06}\textsuperscript{*} &  302 & 46,718 & $\checkmark$ & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Thesauri Evaluation - Labeling and Documentation (2)}
+		\label{tab:thesauri-evaluation-labeling-and-documentation-2}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccccccccccc@{}}
+           & \multicolumn{12}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-13}
+    \\       \textbf{Structure}
+           & \emph{\rot{TheSoz}}
+           & \emph{\rot{STW}}
+           & \emph{\rot{AGROVOC}}
+					 & \emph{\rot{TGN}}
+           & \emph{\rot{UNESCO}}
+					 & \emph{\rot{ODT}}
+					 & \emph{\rot{SSWT}}
+					 & \emph{\rot{GBA-GU}}
+					 & \emph{\rot{GBA-GTS}}
+					 & \emph{\rot{GBA-L}}
+					 & \emph{\rot{GBA-LU}}
+					 & \emph{\rot{CECCT}}
+    \\ \midrule
+		\emph{STRUCTURE-01}\textsuperscript{**} & 1 & 1,074 & $\checkmark$ & $\checkmark$ & 1 & 5 & 1 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{STRUCTURE-02 (!)}\textsuperscript{*} &  &  &  &  &  & \\
+		\emph{STRUCTURE-03}\textsuperscript{**} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & 84 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{STRUCTURE-04}\textsuperscript{*} & 2,906 & 8,046 & 726 & $\checkmark$ & 3,840 & 12 & 124 & 84 & 256 & 68 & 22 & 2,422 \\
+		\emph{STRUCTURE-05}\textsuperscript{*} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & \ding{55} & 90 & 5,150 & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & 9,864 \\
+		\emph{STRUCTURE-06}\textsuperscript{*} & 1,457 & 37 & $\checkmark$ & $\checkmark$ & \ding{55} & $\checkmark$ & 4 & 1 & 1 & 64 & $\checkmark$ & 136 \\
+		\emph{STRUCTURE-07}\textsuperscript{**} & 40 & 5,370 & $\checkmark$ & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{STRUCTURE-08 (!)}\textsuperscript{***} &  &  &  &  &  & \\
+		\emph{STRUCTURE-09}\textsuperscript{*} & 7,897 & 19,844 & 99 & $\checkmark$ & 552 & 2 & 16 & 26 & $\checkmark$ & $\checkmark$ & $\checkmark$ & 82 \\
+		\emph{STRUCTURE-10}\textsuperscript{**} & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Thesauri Evaluation - Structure (1)}
+		\label{tab:thesauri-evaluation-structure-1}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccc@{}}
+           & \multicolumn{4}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-5}
+    \\       \textbf{Structure}
+					 & \emph{\rot{EARTh}}
+					 & \emph{\rot{GEMET}}
+					 & \emph{\rot{EuroVoc}}
+					 & \emph{\rot{SLD}}
+    \\ \midrule
+		\emph{STRUCTURE-01}\textsuperscript{**} & 18,240 & \ding{55} & 55,757 & 31,195 \\
+		\emph{STRUCTURE-02 (!)}\textsuperscript{*} & \\
+		\emph{STRUCTURE-03}\textsuperscript{**} & 39 & 4,244 & $\checkmark$ & $\checkmark$ \\
+		\emph{STRUCTURE-04}\textsuperscript{*} & 11,286 & 74 & $\checkmark$ & $\checkmark$ \\
+		\emph{STRUCTURE-05}\textsuperscript{*} & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ \\
+		\emph{STRUCTURE-06}\textsuperscript{*} & 239,346 & \ding{55} & 13,876 & $\checkmark$ \\
+		\emph{STRUCTURE-07}\textsuperscript{**} & 110,015 & \ding{55} & 366,155 & 155,975 \\
+		\emph{STRUCTURE-08 (!)}\textsuperscript{***} & \\
+		\emph{STRUCTURE-09}\textsuperscript{*} & 107,195 & 32 & $\checkmark$ & $\checkmark$ \\
+		\emph{STRUCTURE-10}\textsuperscript{**} & 27 & 2,122 & $\checkmark$ & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Thesauri Evaluation - Structure (2)}
+		\label{tab:thesauri-evaluation-structure-2}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccccccccccc@{}}
+           & \multicolumn{12}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-13}
+    \\       \textbf{Language Tag Cardinality}
+           & \emph{\rot{TheSoz}}
+           & \emph{\rot{STW}}
+           & \emph{\rot{AGROVOC}}
+					 & \emph{\rot{TGN}}
+           & \emph{\rot{UNESCO}}
+					 & \emph{\rot{ODT}}
+					 & \emph{\rot{SSWT}}
+					 & \emph{\rot{GBA-GU}}
+					 & \emph{\rot{GBA-GTS}}
+					 & \emph{\rot{GBA-L}}
+					 & \emph{\rot{GBA-LU}}
+					 & \emph{\rot{CECCT}}
+    \\ \midrule
+		\emph{LANGUAGE-TAG-CARDINALITY-01}\textsuperscript{**} & 9,435 & 13,468 & 98,894 & $\checkmark$ &  & 541 & 10,147 & 5,117 & 2,061 & 1,742 & 2,272 & 15,550 \\
+		\emph{LANGUAGE-TAG-CARDINALITY-02}\textsuperscript{*} & 8,222 & 36,936 & \ding{55} & $\checkmark$ &  & 265 & 3,627 & 2,212 & 635 & 631 & 1,253 & 9,607 \\
+		\emph{LANGUAGE-TAG-CARDINALITY-03}\textsuperscript{*} & 8,222 & $\checkmark$ & 135 & $\checkmark$ &  & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+		\emph{LANGUAGE-TAG-CARDINALITY-04}\textsuperscript{*} & $\checkmark$ & 476 & \ding{55} & 50 &  & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Thesauri Evaluation - Language Tag Cardinality (1)}
+		\label{tab:thesauri-evaluation-language-tag-cardinality-1}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccc@{}}
+           & \multicolumn{4}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-5}
+    \\       \textbf{Language Tag Cardinality}
+					 & \emph{\rot{EARTh}}
+					 & \emph{\rot{GEMET}}
+					 & \emph{\rot{EuroVoc}}
+					 & \emph{\rot{SLD}}
+    \\ \midrule
+		\emph{LANGUAGE-TAG-CARDINALITY-01}\textsuperscript{**} & \ding{55} & 2,318,895 & \ding{55} & 30,781 \\
+		\emph{LANGUAGE-TAG-CARDINALITY-02}\textsuperscript{*} & \ding{55} & \ding{55} & \ding{55} & \ding{55} \\
+		\emph{LANGUAGE-TAG-CARDINALITY-03}\textsuperscript{*} & 224,206 & \ding{55} & \ding{55} & 31,195 \\
+		\emph{LANGUAGE-TAG-CARDINALITY-04}\textsuperscript{*} & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+    \caption{Thesauri Evaluation - Language Tag Cardinality (2)}
+		\label{tab:thesauri-evaluation-language-tag-cardinality-2}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccccccccccc@{}}
+           & \multicolumn{12}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-13}
+    \\       \textbf{Constraints}
+           & \emph{\rot{TheSoz}}
+           & \emph{\rot{STW}}
+           & \emph{\rot{AGROVOC}}
+					 & \emph{\rot{TGN}}
+           & \emph{\rot{UNESCO}}
+					 & \emph{\rot{ODT}}
+					 & \emph{\rot{SSWT}}
+					 & \emph{\rot{GBA-GU}}
+					 & \emph{\rot{GBA-GTS}}
+					 & \emph{\rot{GBA-L}}
+					 & \emph{\rot{GBA-LU}}
+					 & \emph{\rot{CECCT}}
+    \\ \midrule
+		\emph{PROPERTY-DOMAIN-01 (!)}\textsuperscript{***} &  &  &  &  &  & \\
+		\emph{PROPERTY-RANGES-01 (!)}\textsuperscript{***} &  &  &  &  &  & \\
+		\emph{DISJOINT-PROPERTIES-01 (!)}\textsuperscript{***} &  &  &  &  &  & \\
+		\emph{DISJOINT-PROPERTIES-02 (!)}\textsuperscript{***} &  &  &  &  &  & \\
+		\emph{DISJOINT-CLASSES-01 (!)}\textsuperscript{***} &  &  &  &  &  & \\
+		\emph{EQUIVALENT-PROPERTIES-01 (!)}\textsuperscript{*} &  &  &  &  &  & \\
+		\emph{UNIVERSAL-QUANTIFICATIONS-01 (!)}\textsuperscript{***} &  &  &  &  &  & \\
+		\emph{CONTEXT-SPECIFIC-VALID-CLASSES-01 (!)}\textsuperscript{*} \\ &  &  &  &  &  & \\
+		\emph{CONTEXT-SPECIFIC-VALID-PROPERTIES-01 (!)}\textsuperscript{*} &  &  &  &  &  & \\
+		\emph{RECOMMENDED-PROPERTIES-01 (!)}\textsuperscript{*} &  &  &  &  &  & \\
+		\emph{VOCABULARY-01 (!)}\textsuperscript{***} &  &  &  &  &  & \\
+		\emph{HTTP-URI-SCHEME-VIOLATION (!)}\textsuperscript{***} \\
+    \bottomrule
+    \end{tabular}
+    \caption{Thesauri Evaluation - Constraints (1)}
+		\label{tab:thesauri-evaluation-constraints-1}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcccc@{}}
+           & \multicolumn{4}{c}{\textbf{Data Sets}}
+    \\  \cmidrule{2-5}
+    \\       \textbf{Constraints}
+					 & \emph{\rot{EARTh}}
+					 & \emph{\rot{GEMET}}
+					 & \emph{\rot{EuroVoc}}
+					 & \emph{\rot{SLD}}
+    \\ \midrule
+		\emph{PROPERTY-DOMAIN-01 (!)}\textsuperscript{***}\\
+		\emph{PROPERTY-RANGES-01 (!)}\textsuperscript{***}\\
+		\emph{DISJOINT-PROPERTIES-01 (!)}\textsuperscript{***}\\
+		\emph{DISJOINT-PROPERTIES-02 (!)}\textsuperscript{***}\\
+		\emph{DISJOINT-CLASSES-01 (!)}\textsuperscript{***}\\
+		\emph{EQUIVALENT-PROPERTIES-01 (!)}\textsuperscript{*}\\
+		\emph{UNIVERSAL-QUANTIFICATIONS-01 (!)}\textsuperscript{***}\\
+		\emph{CONTEXT-SPECIFIC-VALID-CLASSES-01 (!)}\textsuperscript{*} \\
+		\emph{CONTEXT-SPECIFIC-VALID-PROPERTIES-01 (!)}\textsuperscript{*} \\
+		\emph{RECOMMENDED-PROPERTIES-01 (!)}\textsuperscript{*} \\
+		\emph{VOCABULARY-01 (!)}\textsuperscript{***} \\
+		\emph{HTTP-URI-SCHEME-VIOLATION (!)}\textsuperscript{***} \\
+    \bottomrule
+    \end{tabular}
+    \caption{Thesauri Evaluation - Constraints (2)}
+		\label{tab:thesauri-evaluation-constraints-2}
+    \end{center}
+\end{table}
+
+\section{Rectangular Data (PHDD)}
+
+\tb{ToDo}
+
+\subsection{Evaluation Results}
+
+\subsection{Data Sets Overview}
+
+\subsection{Detailed Evaluation}
+
+\section{Statistical Classifications (XKOS)}
+
+\tb{ToDo}
+
+\subsection{Evaluation Results}
+
+\subsection{Data Sets Overview}
+
+\begin{table}[H]
+	\centering
+		\begin{tabular}{l|l}
+      \textbf{Abbr.} & \textbf{Statistical Classifications} \\		
+      \hline
+    \emph{NAF} & \emph{Nomenclature d'activités française}\tablefootnote{\url{http://rdf.insee.fr/codes/index.html}} \\
+		\emph{PCS} & \emph{Nomenclature des Professions et Catégories Socioprofessionnelles}\tablefootnote{\url{http://rdf.insee.fr/codes/index.html}} \\
+		\emph{CJ} & \emph{Nomenclature des catégories juridiques}\tablefootnote{\url{http://rdf.insee.fr/codes/index.html}} \\
+		\emph{ISIC} & \emph{}\tablefootnote{\url{}} \\
+		\emph{ISCO} & \emph{}\tablefootnote{\url{}} \\
+		\end{tabular}
+	\caption{Statistical Classifications Abbreviations}
+	\label{tab:statistical-classifications-abbreviations}
+\end{table}
+
+\begin{itemize}
+	\item \emph{Nomenclature d'activités française (NAF)}: French classification expressed in XKOS. the French refinement of the NACE, because it has explanatory notes.
+	\item \emph{Nomenclature des Professions et Catégories Socioprofessionnelles (PCS)}: French classification expressed in XKOS.
+	\item \emph{Nomenclature des catégories juridiques (CJ)}: French classification expressed in XKOS.
+	\item \emph{ISIC}: has explanatory notes too. 
+	\item \emph{ISCO}
+\end{itemize}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lccccccccccc@{}}
+           & \multicolumn{6}{c}{\textbf{Counts}}
+    \\  \cmidrule{2-7}
+    \\       \textbf{Data Sets}
+           & \textbf{\rot{triples}}
+           & \textbf{\rot{}}
+           & \textbf{\rot{}}
+           & \textbf{\rot{}}
+           & \textbf{\rot{}}
+					 & \textbf{\rot{}}
+					 & \textbf{\rot{}}
+    \\ \midrule
+    \emph{NAF} &  &  &  &  &  & \\
+		\emph{PCS} &  &  &  &  &  & \\
+		\emph{CJ} &  &  &  &  &  & \\
+		\emph{ISIC} &  &  &  &  &  & \\
+		\emph{ISCO} &  &  &  &  &  & \\
+		\hline
+		\textbf{Total} & & & & & & \\
+    \bottomrule
+    \end{tabular}
+    \caption{Statistical Classifications Overview}
+		\label{tab:statistical-classifications-overview}
+    \end{center}
+\end{table}
+
+\subsection{Detailed Evaluation}
 

### 2015-04-08 paper/paper7/paper7.tex
evaluation

@@
 \section{Introduction}
-
-\tb{terminology: data in singular form / data set - NOT dataset / person-level data - NOT microdata / study - NOT survey}
+\tb{replace Data Cube by QB?}
+%\tb{terminology: data in singular form / data set - NOT dataset / person-level data - NOT microdata / study - NOT survey}
 
@@
 Therefore, this technical report contains mappings to DL to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
-We recently published a technical report\footnote{\textcolor{red}{Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as appendix of this paper) in which we describe RDF constraints to validate metadata on person-level and aggregated data.
+We recently published a technical report\footnote{\textcolor{red}{Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as first appendix of this paper) in which we describe constraints to validate metadata on person-level, aggregated data, and thesauri.
 We assign each constraint to constraint types corresponding to RDF validation requirements or to data model specific constraint types\footnote{Requirements/Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-1}}
@@
 
-\textbf{application of matching algorithms.}\tb{@Ben ToDo: macht es sinn matching algorithmen anzuwenden?}
-- the value for a specific data property (e.g. birth date) is needed as prerequisite to perform matching algorithms
-- 1. step: validation
-- 2. step: matching
-- validation as reasonable extension of pattern of Ben (e.g. for pattern: is this digit correct?)
-
 -----
@@
 
-\subsubsection{Person-Level Metadata and Data}
+\subsubsection{Person-Level Metadata and Data}. 
 \label{person-level-metadata-and-data}
 
-\textbf{Studies.}
-For datatype properties it should be possible to declare frequently needed \emph{facets} to drive user interfaces and validate input against simple conditions, including min/max values, regular expressions, and string length ({\emph{R-46: data property facets}).
-Each study must have an abstract, i.e., the abstract (\emph{disco:purpose}) should have a minimum length (\emph{xsd:minLength}) of 0 ($\mathcal{SL}_{1}$).
-It is useful to declare properties to be conditional, i.e., if particular properties exist (or do not exist), then specific other properties must also be present (\emph{R-71: conditional properties}).
-If the abstract of a study is missing, a title has to be stated ($\mathcal{SL}_{2}$).
+\textbf{Series, Studies, Data Sets, and Data Files.}
+It is useful to declare properties to be \emph{conditional} (\emph{R-71}), i.e., if particular properties exist (or do not exist), then other properties must also be present (or absent).
+To get an overview over a series/study either an abstract, a title, an alternative title, or links to external descriptions should be provided. 
+If the abstract and an external description are absent, 
+a title or an alternative title has to be stated ($\mathcal{SL}_{1}$).
+For datatype properties it should be possible to declare frequently needed \emph{facets} ({\emph{R-46}) to drive user interfaces and validate input against simple conditions including min/max values, regular expressions, and string length.
+The abstract of series/studies, e.g., should have a minimum length (\emph{xsd:minLength}; $\mathcal{SL}_{1}$).
+\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relations to individuals of certain types.
+If a study, e.g., has no associated data sets ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
+If there is no metadata (especially case and variable quantities) on data files including the actual data of data sets ($\mathcal{SL}_{1}$), the description of the data sets and the underlying study is not sufficient.
+The case quantity measures how many cases are collected for a study.
+A high case and variable quantity is an indicator for high statistical quality and comprehensiveness of the conducted study ($\mathcal{SL}_{1}$).
 
-\textbf{Variables.}
+\textbf{Variables and Variable Comparison.}
 Each variable should have a variable representation (\emph{R-86}; $\mathcal{SL}_{1}$), which is either an (un)ordered code list or a union of datatypes.
-In case of a code list, associated categories should be stated (\emph{R-71}; $\mathcal{SL}_{0}$).
-The variable \emph{Education at pre-school} has an associated code list, but without any associated categories.
-If a {\em skos:Concept} represents a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
-then the property {\em disco:isValid} has to be stated indicating if the code is valid (\emph{true}) or missing (\emph{false}) (\emph{R-71}; $\mathcal{SL}_{1}$).
-Variables must have at least one relationship to a theoretical concept ({\emph{R-75: minimum qualified cardinality restrictions}; $\mathcal{SL}_{1}$).
+In case of a code list, associated categories (human-readable labels) may be stated (\emph{R-71}; $\mathcal{SL}_{0}$).
+The variable \emph{Education at pre-school} is represented as ordered code list without any categories.
+If a {\em skos:Concept} stands for a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
+then the property {\em disco:isValid} has to be stated indicating if the code is valid (\emph{true}) or missing (\emph{false}) (\emph{R-71}; $\mathcal{SL}_{2}$).
+Variables may have at least one relationship to a theoretical concept ({\emph{R-86}; $\mathcal{SL}_{0}$).
 %The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
 The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
-The default severity level of this constraint is $\mathcal{SL}_{1}$ and not $\mathcal{SL}_{2}$, as in most cases research can be continued without associated theoretical concepts of given variables.
-
-\textbf{Variable Comparison.}
+The default severity level of this constraint is weak, as in most cases research can be continued without associated theoretical concepts.
 A very common research question is to compare variables of multiple studies or countries (\emph{comparison}).
@@
 the first three constraints may be sufficient for this purpose.
-Thus, the severity level of the first three constraints is stronger ($\mathcal{SL}_{2}$) than the severity level of the next two constraints ($\mathcal{SL}_{1}$).
-If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the remaining constraints is getting more serious ($\mathcal{SL}_{2}$).
+Thus, the severity level of the first three constraints is stronger ($\mathcal{SL}_{2}$) than the severity level of the next two constraints ($\mathcal{SL}_{1}$ and $\mathcal{SL}_{0}$).
+If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the remaining two constraints is getting more serious.
 
 \textbf{Frequencies and Descriptive Statistics.}
-Percentage values are valid when they are between 0 and 100.
-The constraint type \emph{literal ranges} (\emph{R-45}) restricts data property ranges [$V_{min}$,$V_{max}$] within the context of given classes.
-A constraint of this type applies to the property \emph{disco:percentage} standing for the number of cases of a given code in relation to the total number of cases for a particular variable within a data set ($\mathcal{SL}_{2}$).
+The property \emph{disco:percentage} stands for the number of cases of a given code in relation to the total number of cases for a particular variable within a data set.
+Percentage values are only valid when they are within the \emph{literal range} of 0 and 100 (\emph{R-45}; $\mathcal{SL}_{2}$).
 {\em Mathematical Operations} (\emph{R-41, R-42}; e.g. date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
-The sum of {\em disco:percentage} (datatype: {\em xsd:double}) values of all codes ({\em skos:Concept}) of a variable code list ({\em skos:ConceptScheme} or {\em skos:OrderedCollection}), e.g., must exactly be 100 ($\mathcal{SL}_{2}$).
+The sum of percentage values of all codes of a variable code list, e.g., must exactly be 100 ($\mathcal{SL}_{2}$)
+and the minimum of all variable codes do not have to be greater than the maximum ($\mathcal{SL}_{2}$).
+Some constraints ensure the integrity of the data according to intended data model semantics (\emph{data model consistency}).
+Codes (\emph{skos:Concept}), e.g, are ordered and therefore have fixed positions in an ordered collection (\emph{skos:OrderedCollection}) within variable representations.
+In order to check the correctness of relative frequencies' calculations, the cumulative percentage (\emph{disco:cumulativePercentage}) of the current code must exactly be the cumulative percentage of the previous code (\emph{disco:cumulativePercentage})
+plus the percentage value (\emph{disco:percentage}) of the current code ($\mathcal{SL}_{2}$).
 
@@
 $(\ms{funct identifier}\sp{\overline{\ }})$,
-i.e. for each \emph{rdfs:Resource x}, there can be at most one distinct \emph{rdfs:Resource y} such that \emph{y} is connected by \emph{adms:identifier$\sp{\overline{\ }}$} to \emph{x}.
+i.e.
+for each \emph{rdfs:Resource x}, there can be at most one distinct \emph{rdfs:Resource y} such that \emph{y} is connected by \emph{adms:identifier$\sp{\overline{\ }}$} to \emph{x} ($\mathcal{SL}_{2}$).
 Keys, however, are even more general than inverse-functional properties (\emph{R-58}),
@@
 DL is extended with \emph{key boxes} and a special \emph{keyfor} construct (\ms{identifier \ms{keyfor} Resource}) \cite{Lutz2005}.
-OWL 2 \emph{hasKey} implements \emph{keyfor} and can therefore be used to identify resources uniquely, to merge resources with identical key property values, and to recognize constraint violations.
+OWL 2 \emph{hasKey} implements \emph{keyfor} ($\mathcal{SL}_{2}$) and thus can be used to identify resources uniquely, to merge resources with identical key property values, and to recognize constraint violations.
 %OWL 2 hasKey can be used to identify resources uniquely
@@
 In many cases, resources must be members of listed controlled vocabularies (\emph{R-32}).
-Descriptive statistics types like minimum, maximum, and mode are maintained within a controlled vocabulary.  
-Thus, descriptive statistics (\emph{disco:SummaryStatistics}) can only have \emph{disco:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType}, a \emph{skos:ConceptScheme} (\emph{R-91: universal quantification}; $\mathcal{SL}_{2}$):
+Types of summary statistics like minimum, maximum, and mode are maintained within a controlled vocabulary.  
+Thus, summary statistics can only have \emph{disco:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType}, a \emph{skos:ConceptScheme} (\emph{R-91: universal quantification}; $\mathcal{SL}_{2}$):
 \begin{center}
@@
 \textbf{Coverage.}
-In order to express the temporal coverage of series, studies, or data sets dates can be stated.
-
+Information about the temporal (\emph{dcterms:temporal}), the spatial (\emph{dcterms:spatial}), and the topical coverage (\emph{dcterms:subject}) of series, studies, data sets, and data files (\emph{R-86: existential quantification}; $\mathcal{SL}_{1}$) is of interest when performing particular queries
+	(e.g. to search for all data sets of given years (temporal coverage) in which data is collected in given countries (spatial coverage) about given topics (topical coverage)).
 Depending on property datatypes,
 two different literal values have
-a specific ordering with respect to an operator. 
-\emph{P1} and \emph{P2} are the data properties we need to compare and 
-\emph{OP} is the comparison operator (e.g. \textless, \textless=, \textgreater, \textgreater=, =, !=) (\emph{R-43: literal value comparison}).
-\emph{disco:startDate}s, e.g., must be before (\emph{\textless}) \emph{disco:endDate}s.
-To validate this constraint we bind the variables (P1: \emph{disco:startDate}, P2: \emph{disco:endDate}, OP: \emph{\textless}).
+a specific ordering with respect to an operator (e.g. \textless, \textless=, \textgreater, \textgreater=, =, !=) (\emph{R-43: literal value comparison}).
+Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}) ($\mathcal{SL}_{2}$).
+It must be made sure that all literal values are valid for their datatypes (\emph{R-223: value is valid for datatype}; $\mathcal{SL}_{2}$).
+It has to be ensured, e.g., that all date values (e.g.
+{\em disco:startDate}, {\em disco:endDate}, {\em dcterms:date}) are really of the datatype \emph{xsd:date}, or that \emph{xsd:nonNegativeInteger} values (e.g.
+\emph{disco:frequency}) are not negative.
 
@@
 
-We used $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints 
-to evaluate the metadata and data quality of existing large real world aggregated and person-level data sets.
-We provide a triple store\footnote{\textcolor{red}{\url{http://multiweb.gesis.org/openrdf-workbench/}}}, containing these data sets, 
-and the constraints\footnote{\url{https://github.com/boschthomas/rdf-validation/constraints}} in form of SPARQL CONSTRUCT queries.
+We exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets by means of both $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
 We validated 
-(1) \emph{QB} data sets (\textcolor{red}{XX}),
-(2) \emph{Disco} data sets (overall \textcolor{red}{XX} resources exported from \emph{Missy} - 5 series, \textcolor{red}{XX} studies, \textcolor{red}{XX} data sets, \textcolor{red}{XX} theoretical concepts, \textcolor{red}{XX} variables, \textcolor{red}{XX} questions, \textcolor{red}{XX} codes, \textcolor{red}{XX} category statistics (frequencies), and \textcolor{red}{XX} summary statistics),
-(3) \emph{DCAT} data sets (\textcolor{red}{XX}),
-(4) \emph{PHDD} data sets (\textcolor{red}{XX}),
-(5) \emph{SKOS} data sets (The Thesaurus for the Social Sciences (TheSoz), the STW Thesaurus for Economics of the ZBW, and the AGROVOC thesaurus of FAO), and
-(6) \emph{XKOS} data sets (\textcolor{red}{XX}).
+9,990 / 3,775,983,610 (\emph{QB}),
+4,178 / 477,737,281 (\emph{SKOS}), and 
+1,526 / 9,673,055 (\emph{Disco}) data sets / triples using the \emph{RDF Validator} in batch mode.
+Among others data sets, we validated 
+(1) \emph{QB} data sets published by the \emph{Australian Bureau of Statistics (ABS)},
+the \emph{European Central Bank (ECB)}, and the
+\emph{Organisation for Economic Co-operation and Development (OECD)},
+(2) \emph{SKOS} thesauri like the \emph{AGROVOC Multilingual agricultural thesaurus},
+the \emph{STW Thesaurus for Economics}, and the
+\emph{Thesaurus for the Social Sciences (TheSoz)}, and
+(3) \emph{Disco} data sets provided by the \emph{Microdata Information System (Missy)}, 
+the \emph{DwB Discovery Portal}, the
+\emph{Danish Data Archive (DDA)}, and the
+\emph{Swedish National Data Service (SND)}.
 
-The correctness of $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints, i.e., the gold standard has been designed by a SBE domain expert.
-As proof-of-concept, we use the \emph{RDF Validator} to offer examples for both valid and invalid RDF data regarding particular constraints.
+We recently published a technical report\footnote{\textcolor{red}{Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as second appendix of this paper) 
+in which we describe the evaluation in detail. 
+As we validated 9,990 aggregated data sets, we published the validation results of all aggregated data sets in form of one document per SPARQL endpoint\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.
+Although accessible within the \emph{RDF Validator}, we provide all implemented constraints\footnote{\textcolor{red}{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}}} in form of SPARQL CONSTRUCT queries.
+The correctness of all evaluated constraints, i.e., the gold standard, has been proved by SBE domain experts.
 
-%\begin{table}
-	%\centering
-		%\begin{tabular}{l|c|c|c|c|c|c}
-      %\textbf{Expressivity Class} & \textbf{DSP} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\		
-      %\hline
-      %$Expr(\overline{\mathcal{C}_R})$ (42) & 6 & 18(4) & 7(4) & 8 & 12 & 41(1)\\
-      %$Expr(\mathcal{C}_R)$ (32) & 8 & 29 & 11 & 11(2) & 11(1) & 32 \\ 	
-		%\end{tabular}
-	%\caption{Constraint Type Specific Expressivity}
-	%\label{tab:constraint-type-specific-expressivity}
-%\end{table}
+We defined 142 (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) constraints assigned to 52 (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) distinct constraint types and implemented 77 (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS})  of them to actually validate data sets.
+49.3\% (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) of the defined constraints are $\mathcal{C}_{T}$ constraints, and 
+42.3\% (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) of the constraint types are $\mathcal{C}_{T}$ constraint types.
+52.8\% (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) of the defined constraints are associated with the default severity level $\mathcal{SL}_{0}$, 6.3\% (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) are $\mathcal{SL}_{1}$, and
+40.8\% (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) are $\mathcal{SL}_{2}$ constraints.
+\emph{R-86: Existential quantifications} (32.4\%, \emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) are the constraint types with the most defined constraints.
+We got \textcolor{red}{XX} (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) / \textcolor{red}{XX} (\emph{In Total}) constraint violations. 
+\textcolor{red}{XX} (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) / \textcolor{red}{XX} (\emph{In Total}) constraint violations caused by violating $\mathcal{SL}_{0}$ constraints,
+473,574 (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) / \textcolor{red}{XX} (\emph{In Total}) by $\mathcal{SL}_{1}$ constraints, and 
+\textcolor{red}{XX} (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) / \textcolor{red}{XX} (\emph{In Total}) by $\mathcal{SL}_{2}$ constraints.
+\emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} (547,916) and \emph{DISCO-C-COMPARISON-VARIABLES-02} (547,916) (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) are the constraints responsible for the most constraint violations.
 
@@
 
+As part of future work, we will identify constraints on rectangular data and statistical classifications and classify them.
+
 \bibliography{../../literature/literature}{}

### 2015-04-10 paper/paper7/paper7-appendix.tex
evaluation

@@
 %
-\title{RDF Constraint Types to Validate Metadata \\ on Highly-Complex Person-Level and Aggregated Data}
-\subtitle{}
+\title{RDF Constraints to Validate}
+\subtitle{Metadata on Person-Level, Aggregated, Thesauri, and Statistical Classifications Data Sets and Rectangular Data}
 
@@
 \begin{abstract}
-...
-
-\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, Disco, RDF Data Cube Vocabulary, Linked Data, Semantic Web}
+To ensure high quality and trust, RDF data as well as its metadata must satisfy certain criteria - specified in terms of RDF constraints.
+From 2012 to 2015 together with other Linked Data community members and experts from the social, behavioural, and economic sciences (\emph{SBE}), we developed diverse vocabularies to represent \emph{SBE} metadata and data in RDF.
+The \emph{DDI-RDF Discovery Vocabulary (Disco)} 
+is designed for the purposes of supporting the dissemination, management,
+and reuse of person-level data (data about individuals) collected in form of responses to studies and archived for research purposes.
+The \emph{RDF Data Cube Vocabulary (Data Cube, QB)} is a W3C recommendation for representing \emph{data cubes}, i.e. multi-dimensional aggregate data, in RDF. 
+\emph{Physical Data Description (PHDD)} is a vocabulary to represent aggregated and person-level data in a rectangular format. 
+The data could be either represented in records with character-separated values (\emph{CSV}) or in records with fixed length. 
+The \emph{Simple Knowledge Organization System (SKOS)} is a vocabulary to represent knowledge organization systems such as thesauri, classification schemes, subject heading lists, and taxonomies in RDF.
+\emph{XKOS} is a SKOS extension to describe formal statistical classifications like the \emph{International Standard Classification of Occupations} (\emph{ISCO}).
+
+In this paper, we describe RDF constraints to validate metadata on person-level (\emph{Disco}), aggregated (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) data sets and to validate rectangular data (\emph{PHDD}).
+We assign each constraint to constraint types either corresponding to RDF validation requirements or to data model specific constraint types.
+This document is updated continuously as modifying and adding constraints is ongoing work.
+
+\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, Disco, RDF Data Cube Vocabulary, QB, Thesauri, SKOS, Rectangular Data, PHDD, Statistical Classifications, Extended SKOS, XKOS, Linked Data, Semantic Web}
 \end{abstract}
@@
 They recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which they explain each requirement (constraint type) in detail and give examples for each (represented by listed constraint languages) \cite{BoschNolleAcarEckert2015}.
-We state at least one Disco constraint for the majority of the constraint types.
 Where appropriate constraint types are related to complementary requirements of the RDF validation requirements database.
-When constraint types are mapped to DL, we do not state namespace prefixes for simplicity reasons.
-
-\section{Validation Types}
 
@@
 (2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges.
-
-\section{Validation of Metadata on Person-Level and Aggregated Data}
-
-\begin{itemize}
-  \item Constraint types marked with an asterisk (*) can be used as OWL 2 axioms.
-Thus, reasoners may be used to infer implicit triples resolving constraint violations caused when these constraints are validated.
-	\item \underline{Underlined subsections} represent data model specific constraint types and do not correspond to RDF validation requirements (constraint types).
-%	\item \underline{Underlined constraints} are part of content-driven validation.
-%	\item \udash{Dashed underlined constraints} are part of technology-driven validation.
-	\item $\mathcal{C}_{T}$ constraint types are marked with the superscript\textsuperscript{T}
-	\item $\mathcal{C}_{C}$ constraint types are not marked
-\end{itemize}
+We determined the default \emph{severity level} (corresponds to requirement \emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
+We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ (informational) via $\mathcal{SL}_{1}$ (warning) to $\mathcal{SL}_{2}$ (error). 
+Although we provide default severity levels for each constraint, users should be able to specify severity levels of constraints they need to validate for their individual use cases, i.e., users should be able to define use case specific severity levels for constraints.
+
+\section{RDF Constraints to Validate Metadata and Data}
+
+Each of the following subsections stands for a constraint type either corresponding to an RDF validation requirement or to a data model specific constraint type.
+Constraint types marked with an asterisk (*) can be used as OWL 2 axioms.
+Thus, reasoners may be used to infer implicit triples which may resolve constraint violations caused when these constraints are validated.
+\underline{Underlined subsections} represent data model specific constraint types and do not correspond to RDF validation requirements (constraint types).
+$\mathcal{C}_{T}$ constraint types are marked with the superscript\textsuperscript{T}.
+$\mathcal{C}_{C}$ constraint types are not marked.
 

### 2015-04-10 paper/paper7/paper7-evaluation.tex
evaluation

@@
 %
-\title{An Evaluation of RDF Constraint Types to Validate Metadata on Person-Level and Aggregated Data}
-\subtitle{}
+\title{An Evaluation \\
+of Metadata and Data Quality}
+\subtitle{on Person-Level, Aggregated, Thesauri, Statistical Classifications, and Rectangular Data Sets}
+
+%\title{An Evaluation}
+%\subtitle{of the Quality of Metadata on Person-Level, Aggregated, Thesauri, and Statistical Classifications Data Sets and of the Quality of Rectangular Data}
 
@@
 \begin{abstract}
-...
-
-\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, Disco, RDF Data Cube Vocabulary, Linked Data, Semantic Web}
+From 2012 to 2015 together with other Linked Data community members and experts from the social, behavioural, and economic sciences (\emph{SBE}), we developed diverse vocabularies to represent \emph{SBE} metadata and data in RDF.
+The \emph{DDI-RDF Discovery Vocabulary (Disco)} 
+is designed for the purposes of supporting the dissemination, management,
+and reuse of person-level data (data about individuals) collected in form of responses to studies and archived for research purposes.
+The \emph{RDF Data Cube Vocabulary (Data Cube, QB)} is a W3C recommendation for representing \emph{data cubes}, i.e. multi-dimensional aggregate data, in RDF. 
+\emph{Physical Data Description (PHDD)} is a vocabulary to represent aggregated and person-level data in a rectangular format. 
+The data could be either represented in records with character-separated values (\emph{CSV}) or in records with fixed length. 
+The \emph{Simple Knowledge Organization System (SKOS)} is a vocabulary to represent knowledge organization systems such as thesauri, classification schemes, subject heading lists, and taxonomies in RDF.
+\emph{XKOS} is a SKOS extension to describe formal statistical classifications like the \emph{International Standard Classification of Occupations} (\emph{ISCO}).
+
+To ensure high quality and trust, RDF data as well as its metadata must satisfy certain criteria - specified in terms of RDF constraints.
+In this paper, we evaluated the metadata and data quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), thesauri (\emph{SKOS}), rectangular (\emph{PHDD}), and statistical classification (\emph{XKOS}) data sets by means of RDF constraints assigned to multiple constraint types.
+We validated more than 4.2 billion triples and 15 thousand data sets
+using the \emph{RDF Validator} which is available at \url{http://purl.org/net/rdfval-demo}.
+
+\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, Disco, RDF Data Cube Vocabulary, QB, Thesauri, SKOS, Rectangular Data, PHDD, Statistical Classifications, Extended SKOS, XKOS, Linked Data, Semantic Web}
 \end{abstract}
 
+\section{RDF Validation of Metadata and Data}
+\label{rdf-validation}
+
+Bosch et al. identified in total 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
+We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement (constraint type) in detail and give examples for each (represented by different constraint languages).
+The knowledge representation formalism \emph{Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
+Therefore, this technical report contains mappings to DL to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
+We recently published a technical report in which we describe constraints to validate metadata on person-level, aggregated data, and thesauri.
+We assign each constraint to constraint types corresponding to RDF validation requirements or to data model specific constraint types\footnote{Requirements/Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-1}}
+\cite{BoschZapilkoWackerowEckert2015}.
+
+We distinguish two validation types:
+(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of given data models.
+(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges.
+We determined the default \emph{severity level} (corresponds to requirement \emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
+We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ (informational) via $\mathcal{SL}_{1}$ (warning) to $\mathcal{SL}_{2}$ (error). 
+Although we provide default severity levels for each constraint, users should be able to specify severity levels of constraints they need to validate for their individual use cases, i.e., users should be able to define use case specific severity levels for constraints.
+
 \section{Evaluation}
 
-\begin{table}[H]
-    \begin{center}
-    \begin{tabular}{@{}lcccccc@{}}
-           & \multicolumn{6}{c}{\textbf{Vocabularies}}
-    \\  \cmidrule{2-7}
-    \\       \textbf{Criteria (Counts)}
-           & \textbf{\rot{Person-Level Metadata (Disco)}}
-           & \textbf{\rot{Aggregated Metadata (Data Cube)}}
-					 & \textbf{\rot{Thesauri (SKOS)}}
-					 & \textbf{\rot{Rectangular Data (PHDD)}}
-					 & \textbf{\rot{Statistical Classifications (XKOS)}}
-					 & \textbf{\rot{Total}}
-    \\ \midrule
-		\emph{Validated Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 \\
-		\emph{Validated Data Sets} & 1,526 & 9,990 & 4,178 \\
-		\hline
-		\emph{Constraint Violations} & \textcolor{red}{XXXXX} \\
-		\emph{Constraint Violations ($\mathcal{SL}_{0}$)} & \textcolor{red}{XXXXX} \\
-		\emph{Constraint Violations ($\mathcal{SL}_{1}$)} & 473,574 $\equiv$ \textcolor{red}{XXXXX}\% \\
-    \emph{Constraint Violations ($\mathcal{SL}_{2}$)} & \textcolor{red}{XXXXX} \\
-				\hline
-		\emph{Constraint Types} & 52 (15\textbar 37) \\
-		\emph{Constraint Types} ($\mathcal{C}_{C}$) & 30 $\equiv$ 57.7 \% \\
-		\emph{Constraint Types} ($\mathcal{C}_{T}$) & 22 $\equiv$ 42.3 \% \\
-		\hline
-		\emph{Constraints} & 142 (77\textbar 65) \\
-		\emph{Constraints} ($\mathcal{C}_{C}$) & 72 $\equiv$ 50.7 \% \\
-		\emph{Constraints} ($\mathcal{C}_{T}$) & 70 $\equiv$ 49.3 \% \\
-		\emph{Constraints ($\mathcal{SL}_{0}$)} & 75 $\equiv$ 52.8\% (44\textbar 31)\\
-		\emph{Constraints ($\mathcal{SL}_{1}$)} & 9 $\equiv$ 6.3\% (8\textbar 1)\\
-		\emph{Constraints ($\mathcal{SL}_{2}$)} & 58 $\equiv$ 40.8\% (25\textbar 33)\\
+We exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets by means of both $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
+We validated 
+9,990 / 3,775,983,610 (\emph{QB}),
+4,178 / 477,737,281 (\emph{SKOS}), and 
+1,526 / 9,673,055 (\emph{Disco}) data sets / triples using the \emph{RDF Validator}\footnote{For details about the \emph{RDF Validator} see \cite{BoschEckert2014-2}} (available at \url{http://purl.org/net/rdfval-demo}) in batch mode.
+That are more than 4.2 billion triples and 15 thousand data sets.
+We validated, i.a., 
+(1) \emph{QB} data sets published by the \emph{Australian Bureau of Statistics (ABS)},
+the \emph{European Central Bank (ECB)}, and the
+\emph{Organisation for Economic Co-operation and Development (OECD)},
+(2) \emph{SKOS} thesauri like the \emph{AGROVOC Multilingual agricultural thesaurus},
+the \emph{STW Thesaurus for Economics}, and the
+\emph{Thesaurus for the Social Sciences (TheSoz)}, and
+(3) \emph{Disco} data sets provided by the \emph{Microdata Information System (Missy)}, 
+the \emph{DwB Discovery Portal}, the
+\emph{Danish Data Archive (DDA)}, and the
+\emph{Swedish National Data Service (SND)}.
+As we evaluated nearly 10 thousand \emph{QB} data sets, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.
+The correctness of all constraints, i.e., the gold standard, has been proved by SBE domain experts.
+Table \ref{tab:evaluation} shows the evaluation results.
+
+\begin{table}[H]
+		\scriptsize
+    \begin{center}
+    \begin{tabular}{@{}lcccc@{}}
+%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
+%    \\  \cmidrule{2-7}
+    \\       \textbf{Criteria\tablefootnote{\emph{C (constraints), CT (constraint types), CV (constraint violations)}}}
+           & \textbf{\emph{Disco}}
+           & \textbf{\emph{QB}}
+					 & \textbf{\emph{SKOS}}
+					 & \textbf{Total}
+    \\ \midrule
+		\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
+		\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
+		\hline
+    \emph{CV} & 3,545,703 & 45,635,846 & 5,540,988 & 54,722,537\\
+		\emph{CV ($\mathcal{SL}_{0}$)} & 2,437,922 (68.8\%) & 0 (0\%) & 2,281,740 (41.2\%) & 4,719,662 (8.6\%) \\
+		\emph{CV ($\mathcal{SL}_{1}$)} & 473,574 (13.4\%) & 45,520,613 (99.75\%) & 3,259,248 (58.8\%) & 49,253,435 (90\%) \\
+    \emph{CV ($\mathcal{SL}_{2}$)} & 634,207 (17.9\%) & 115,233 (0.25\%) & 0 (0\%) & 749,440 (1.4\%) \\
+		\hline
+		\emph{CT} & 52 (15\textbar 37)\tablefootnote{(\label{fnt:1}implemented \textbar not yet implemented)} & 20 (7\textbar 13)\footnotemark[\ref{fnt:1}] & 14 (4\textbar 10)\footnotemark[\ref{fnt:1}] & 53 \\
+		\emph{CT} ($\mathcal{C}_{C}$) & 30 (57.7\%) & 5 (25\%) & 5 (35.7\%) & 30 (56.6\%) \\
+		\emph{CT} ($\mathcal{C}_{T}$) & 22 (42.3\%) & 15 (75\%) & 9 (64.3\%) & 23 (43.4\%) \\
+		\hline
+		\emph{C} & 142 (77\textbar 65) & 35 (20\textbar 15) & 35 (17\textbar 18) & 212 \\
+		\emph{C} ($\mathcal{C}_{C}$) & 72 (50.7\%) & 16 (45.7\%\textbar12\textbar4) & 21 (60\%\textbar13\textbar8) & 109 (51.4\%) \\
+		\emph{C} ($\mathcal{C}_{T}$) & 70 (49.3\%) & 19 (54.3\%\textbar8\textbar11) & 14 (40\%\textbar4\textbar10) & 103 (48.6\%) \\
+		\emph{C ($\mathcal{SL}_{0}$)} & 75 (52.8\%\textbar44\textbar31)& 4 (11.4\%\textbar0\textbar4) & 21 (60\%\textbar12\textbar9) & 100 (47.2\%) \\
+		\emph{C ($\mathcal{SL}_{1}$)} & 9 (6.3\%\textbar8\textbar1)& 3 (8.6\%\textbar3\textbar0) & 5 (14.3\%\textbar5\textbar0) & 17 (8\%) \\
+		\emph{C ($\mathcal{SL}_{2}$)} & 58 (40.8\%\textbar25\textbar33) & 28 (80\%\textbar17\textbar11) & 9 (25.7\%\textbar0\textbar9) & 95 (44.8\%) \\
     \bottomrule
@@
 
+We identified 142 \emph{Disco} constraints ($\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints to the same extend) assigned to 52 distinct constraint types and implemented 77 of them to actually validate person-level data sets.
+For \emph{QB}, we specified more $\mathcal{C}_{T}$ (54\%) than $\mathcal{C}_{C}$ constraints; for \emph{SKOS}, however, more $\mathcal{C}_{C}$ constraints (60\%).
+We instantiated more $\mathcal{C}_{C}$ (58\%) than $\mathcal{C}_{T}$ constraint types to define \emph{Disco} constraints; 
+for \emph{QB} (75\%) and \emph{SKOS} (64\%), on the other side, more $\mathcal{C}_{T}$ constraint types. 
+In total, we used 53 of overall 82 distinct constraint types (57\% of them are $\mathcal{C}_{C}$ constraint types) to define 212 constraints (equally $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints).
+
+For \emph{Disco} and \emph{SKOS}, more than the half of the constraints are associated with the weakest severity level $\mathcal{SL}_{0}$.
+Within the context of \emph{QB}, 80\% of the constraints are classified as the most serious ones ($\mathcal{SL}_{2}$).
+All in all, there are a little bit more $\mathcal{SL}_{0}$ then $\mathcal{SL}_{2}$ constraints, whereas $\mathcal{SL}_{1}$ constraints are negligible.
+\emph{Existential quantifications} (32.4\%, \emph{Disco}), \emph{data model consistency} (31.4\%, \emph{QB}), and \emph{structure} (28.6\%, \emph{SKOS}) are the constraint types the most constraints are instantiated from.
+By validating \emph{QB} data sets, we got the most constraint violations (more than 45 millions), followed by \emph{SKOS} and \emph{Disco} (with more than 5.5 and 3.5 millions) - consequently, almost 55 million constraint violations were raised during the evaluation which could be used to enhance the metadata quality of these data sets.
+Close to 70\% of all \emph{Disco} constraint violations are caused by violating $\mathcal{SL}_{0}$ constraints.
+For \emph{QB} (nearly 100\%) and \emph{SKOS} (almost 60\%), the majority of the raised constraint violations are classified to be more serious ($\mathcal{SL}_{1}$).
+80\% of all \emph{QB} constraints are $\mathcal{SL}_{2}$ constraints leading to less than 1\% of all \emph{QB} constraint violations.
+Altogether, exactly 90\% of the constraint violations are assigned to the severity level $\mathcal{SL}_{1}$.
+These findings are surprising as only 8\% of all defined constraints are $\mathcal{SL}_{1}$ constraints.
+The constraints responsible for the largest numbers of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916) (\emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102) (\emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903) (\emph{SKOS}).
+
 \subsection{Legend}
+
+In this section, we describe how the tables in this paper should be read.
+Table \ref{tab:legend} gives an overview over the symbols used in subsequent tables.
 
@@
       \textbf{Symbol} & \textbf{Description} \\	
-			\textbf{\emph{X}} & Validation Successful \\
+			\hline
+			\textbf{$\checkmark$} & Validation Successful (without any constraint violation) \\
+			\textbf{\emph{X}} & Constraint Violations \\
 			\hline
 			\textbf{\textgreater \emph{X}} & Poor Performance/Scaling \\
-			\hline
       \ding{55} & Very Poor Performance/Scaling \\
@@
 			\hline
-			\textbf{\emph{(X)}} & The validation of \emph{X} data sets could not be finished \\
-			           & due to SPARQL endpoints' technical restrictions (e.g. the defined timeout). \\
-			\hline
-			\textbf{\emph{\textsuperscript{*}}} & severity level $\mathcal{SL}_{0}$ (informational) \\
-			\hline
-			\textbf{\emph{\textsuperscript{**}}} & severity level $\mathcal{SL}_{1}$ (warning) \\
-			\hline
-			\textbf{\emph{\textsuperscript{***}}} & severity level $\mathcal{SL}_{2}$ (error) \\
+			\textbf{\emph{(X)}} & The validation of \emph{X} data sets could not be finished, \\
+			           & due to SPARQL endpoints' technical restrictions (e.g. defined timeouts). \\
+			\hline
+			\textbf{\emph{\textsuperscript{*}}} & default severity level $\mathcal{SL}_{0}$ (informational) \\
+			\textbf{\emph{\textsuperscript{**}}} & default severity level $\mathcal{SL}_{1}$ (warning) \\
+			\textbf{\emph{\textsuperscript{***}}} & default severity level $\mathcal{SL}_{2}$ (error) \\
 		\end{tabular}
@@
 
-\textbf{Validation Successful:} 
+\begin{itemize}
+	\item \textbf{Constraint Violations.}
+When constraints are violated, 
 \emph{X} indicates the number of raised constraint violation triples.
 
-\textbf{Poor Performance/Scaling:}
+  \item
+\textbf{Poor Performance/Scaling.}
 The performance of the implementation of the underlying SPARQL CONSTRUCT query 
@@
 Although, the result set contains not the whole set of raised constraint violation triples,
-the constraint can be used as an indicator if there data not conforming to the constraint and
+the constraint can be used as an indicator if there is data not conforming to the constraint and
 to resolve constraint violations step by step. 
@@
 
-\textbf{Very Poor Performance/Scaling:} 
+  \item
+\textbf{Very Poor Performance/Scaling.} 
 The performance of the implementation of the underlying SPARQL CONSTRUCT query 
@@
 As part of future work, the performance will be improved. 
-
-\section{Person-Level Metadata (Disco)}
+\end{itemize}
+
+\section{Evaluation of Person-Level Metadata (\emph{Disco})}
 
@@
 
-Legend: total (implemented\textbar not yet implemented)
-
-\begin{table}[H]
+Table \ref{tab:disco-evaluation-results} shows the results of the evaluation of \emph{Disco} data sets.
+
+\begin{table}[H]
+  \scriptsize
 	\centering
@@
 		\hline
-		\emph{Constraint Violations} & \textcolor{red}{XXXXX} \\
-		\emph{Constraint Violations ($\mathcal{SL}_{0}$)} & \textcolor{red}{XXXXX} \\
-		\emph{Constraint Violations ($\mathcal{SL}_{1}$)} & 473,574 $\equiv$ \textcolor{red}{XXXXX}\% \\
-    \emph{Constraint Violations ($\mathcal{SL}_{2}$)} & \textcolor{red}{XXXXX} \\
+		\emph{Constraint Violations} & 3,545,703 \\
+		\emph{Constraint Violations ($\mathcal{SL}_{0}$)} & 2,437,922 (68.8\%) \\
+		\emph{Constraint Violations ($\mathcal{SL}_{1}$)} & 473,574 (13.4\%) \\
+    \emph{Constraint Violations ($\mathcal{SL}_{2}$)} & 634,207 (17.9\%) \\
 		\hline
@@
 		\hline
-		\emph{Constraint Types} & 52 (15\textbar 37) \\
-		\emph{Constraint Types} ($\mathcal{C}_{C}$) & 30 $\equiv$ 57.7 \% \\
-		\emph{Constraint Types} ($\mathcal{C}_{T}$) & 22 $\equiv$ 42.3 \% \\
-		\hline
-		\emph{Constraint Types (Most Constraints)} & 1. Existential Quantifications: 46 $\equiv$ 32.4\% (46\textbar 0) \\
-		                                            & 2. Data Model Consistency: 7 (1\textbar 6) \\
-																								& 3. Aggregation: 7 (0\textbar 7) \\
-		\emph{Constraint Type (Most Constraints ($\mathcal{SL}_{2}$))} & Existential Quantifications: 9 (9\textbar 0) \\
+		\emph{Constraint Types} & 52 (15\textbar 37)\tablefootnote{legend: absolute number (absolute number implemented \textbar  absolute number not yet implemented)} \\
+		\emph{Constraint Types} ($\mathcal{C}_{C}$) & 30 (57.7\%) \\
+		\emph{Constraint Types} ($\mathcal{C}_{T}$) & 22 (42.3\%) \\
+		\hline
+		\emph{Constraint Types (Most Constraints)} & 1.
+Existential Quantifications: 46 (32.4\%\textbar46\textbar0)\tablefootnote{legend: absolute number (percentage value \textbar  absolute number implemented \textbar  absolute number not yet implemented)} \\
+		                                           & 2. Data Model Consistency: 7 (1\textbar6) \\
+																							 & 3. Aggregation: 7 (0\textbar7) \\
+		\emph{Constraint Type (Most Constraints ($\mathcal{SL}_{2}$))} & Existential Quantifications: 9 (9\textbar0) \\
 		\hline
 		\emph{Constraints} & 142 (77\textbar 65) \\
-		\emph{Constraints} ($\mathcal{C}_{C}$) & 72 $\equiv$ 50.7 \% \\
-		\emph{Constraints} ($\mathcal{C}_{T}$) & 70 $\equiv$ 49.3 \% \\
-		\emph{Constraints ($\mathcal{SL}_{0}$)} & 75 $\equiv$ 52.8\% (44\textbar 31)\\
-		\emph{Constraints ($\mathcal{SL}_{1}$)} & 9 $\equiv$ 6.3\% (8\textbar 1)\\
-		\emph{Constraints ($\mathcal{SL}_{2}$)} & 58 $\equiv$ 40.8\% (25\textbar 33)\\
+		\emph{Constraints} ($\mathcal{C}_{C}$) & 72 (50.7\%) \\
+		\emph{Constraints} ($\mathcal{C}_{T}$) & 70 (49.3\%) \\
+		\emph{Constraints ($\mathcal{SL}_{0}$)} & 75 (52.8\%\textbar44\textbar31)\\
+		\emph{Constraints ($\mathcal{SL}_{1}$)} & 9 (6.3\%\textbar8\textbar1)\\
+		\emph{Constraints ($\mathcal{SL}_{2}$)} & 58 (40.8\%\textbar25\textbar33)\\
 		\end{tabular}
@@
 
+Tables \ref{tab:disco-data-sets-abbreviations} and \ref{tab:disco-sparql-endpoints} give an overview over the evaluated \emph{Disco} data sets, their abbreviations, and publicly available SPARQL endpoints.
+Table \ref{tab:disco-overview} comprehends the number of triples, data sets, and instances of multiple vocabulary-specific classes.
+
 \begin{table}[H]
@@
 
-\section{Aggregated Metadata (Data Cube)}
+\section{Evaluation of Aggregated Metadata (\emph{Data Cube})}
 
@@
 
-\begin{table}[H]
+Table \ref{tab:data-cube-evaluation-results} shows the results of the evaluation of \emph{Data Cube} data sets.
+
+\begin{table}[H]
+  \scriptsize
 	\centering
@@
 		\emph{Constraint Violations} & 45,635,846 \\
-		\emph{Constraint Violations ($\mathcal{SL}_{0}$)} & 0 $\equiv$ 0\% \\
-		\emph{Constraint Violations ($\mathcal{SL}_{1}$)} & 45,520,613 $\equiv$ 99.75\% \\
-    \emph{Constraint Violations ($\mathcal{SL}_{2}$)} & 115,233 $\equiv$ 0.25\% \\
+		\emph{Constraint Violations ($\mathcal{SL}_{0}$)} & 0 (0\%) \\
+		\emph{Constraint Violations ($\mathcal{SL}_{1}$)} & 45,520,613 (99.75\%) \\
+    \emph{Constraint Violations ($\mathcal{SL}_{2}$)} & 115,233 (0.25\%) \\
 		\hline
@@
 		\emph{Constraint Types} & 20 (7\textbar 13) \\
-		\emph{Constraint Types} ($\mathcal{C}_{C}$) & 5 $\equiv$ 25 \% \\
-		\emph{Constraint Types} ($\mathcal{C}_{T}$) & 15 $\equiv$ 75 \% \\
-		\hline
-		\emph{Constraint Types (Most Constraints)} & 1. Data Model Consistency: 11 $\equiv$ 31.4\% (10\textbar 1) \\
-		                                           & 2. Existential Quantifications: 4 $\equiv$ 11.4\% (4\textbar 0) \\
-		\emph{Constraint Type (Most Constraints ($\mathcal{SL}_{2}$))} & Data Model Consistency: 8 $\equiv$ 22.9\% (7\textbar 1) \\
+		\emph{Constraint Types} ($\mathcal{C}_{C}$) & 5 (25\%) \\
+		\emph{Constraint Types} ($\mathcal{C}_{T}$) & 15 (75\%) \\
+		\hline
+		\emph{Constraint Types (Most Constraints)} & 1. Data Model Consistency: 11 (31.4\%\textbar10\textbar1) \\
+		                                           & 2. Existential Quantifications: 4 (11.4\%\textbar4\textbar0) \\
+		\emph{Constraint Type (Most Constraints ($\mathcal{SL}_{2}$))} & Data Model Consistency: 8 (22.9\%\textbar7\textbar1) \\
 		\hline
 		\emph{Constraints} & 35 (20\textbar 15) \\
-		\emph{Constraints} ($\mathcal{C}_{C}$) & 16 (12\textbar 4) \\
-		\emph{Constraints} ($\mathcal{C}_{T}$) & 19 (8\textbar 11) \\
-		\emph{Constraints ($\mathcal{SL}_{0}$)} & 4 $\equiv$ 11.4\% (0\textbar 4) \\
-		\emph{Constraints ($\mathcal{SL}_{1}$)} & 3 $\equiv$ 8.6\% (3\textbar 0) \\
-		\emph{Constraints ($\mathcal{SL}_{2}$)} & 28 $\equiv$ 80\% (17\textbar 11) \\
+		\emph{Constraints} ($\mathcal{C}_{C}$) & 16 (45.7\%\textbar12\textbar4) \\
+		\emph{Constraints} ($\mathcal{C}_{T}$) & 19 (54.3\%\textbar8\textbar11) \\
+		\emph{Constraints ($\mathcal{SL}_{0}$)} & 4 (11.4\%\textbar0\textbar4) \\
+		\emph{Constraints ($\mathcal{SL}_{1}$)} & 3 (8.6\%\textbar3\textbar0) \\
+		\emph{Constraints ($\mathcal{SL}_{2}$)} & 28 (80\%\textbar17\textbar11) \\
 		\end{tabular}
@@
 
-\begin{itemize}
-  \item overview over Data Cube data sets\footnote{\url{http://270a.info/}; \url{http://datahub.io/de/dataset?tags=format-qb}} 
-  \item \url{http://ontologycentral.com/}
-\end{itemize}
+There are websites giving an overview over available \emph{Data Cube} data sets\footnote{\url{http://270a.info/}; \url{http://datahub.io/de/dataset?tags=format-qb}; \url{http://ontologycentral.com/}}.
+Tables \ref{tab:data-cube-data-sets-abbreviations} and \ref{tab:data-cube-sparql-endpoints} give an overview over the evaluated \emph{Data Cube} data sets, their abbreviations, and publicly available SPARQL endpoints.
+Table \ref{tab:data-cube-overview} comprehends the number of triples, data sets, and instances of multiple vocabulary-specific classes.
 
@@
     \caption{Data Cube Data Sets Overview}
+		\label{tab:data-cube-overview}
     \end{center}
@@
 
-\section{Thesauri (SKOS)}
+\section{Evaluation of Thesauri (\emph{SKOS})}
 
@@
 
-\begin{table}[H]
+Table \ref{tab:thesauri-evaluation-results} shows the results of the evaluation of \emph{thesauri}.
+
+\begin{table}[H]
+  \scriptsize
 	\centering
@@
       \hline
-		\emph{Validated Triples} & \textcolor{red}{XXXXX} \\
-		\emph{Validated Data Sets} & \textcolor{red}{XXXXX} \\
-		\hline
-		\emph{Constraint Violations} & \textcolor{red}{XXXXX} \\
-		\emph{Constraint Violations ($\mathcal{SL}_{0}$)} & \textcolor{red}{XXXXX} \\
-		\emph{Constraint Violations ($\mathcal{SL}_{1}$)} & \textcolor{red}{XXXXX} $\equiv$ \textcolor{red}{XXXXX}\% \\
-    \emph{Constraint Violations ($\mathcal{SL}_{2}$)} & \textcolor{red}{XXXXX} \\
+		\emph{Validated Triples} & 477,737,281 \\
+		\emph{Validated Data Sets} & 4,178 \\
+		\hline
+		\emph{Constraint Violations} & 5,540,988 \\
+		\emph{Constraint Violations ($\mathcal{SL}_{0}$)} & 2,281,740 (41.2\%) \\
+		\emph{Constraint Violations ($\mathcal{SL}_{1}$)} & 3,259,248 (58.8\%) \\
+    \emph{Constraint Violations ($\mathcal{SL}_{2}$)} & 0 (0\%) \\
 		\hline
@@
 		\emph{Constraint Types} & 14 (4\textbar 10) \\
-		\emph{Constraint Types} ($\mathcal{C}_{C}$) & 5 $\equiv$ 35.7\% \\
-		\emph{Constraint Types} ($\mathcal{C}_{T}$) & 9 $\equiv$ 64.3\% \\
-		\hline
-		\emph{Constraint Types (Most Constraints)} & 1. Structure: 10 $\equiv$ XX\% (8\textbar 2) \\
-		                                           & 2. Labeling and Documentation: 6 $\equiv$ XX\% (5\textbar 1) \\
-																							 & 3. Language Tag Cardinality: 4 $\equiv$ XX\% (4\textbar 0) \\
-		\emph{Constraint Type (Most Constraints ($\mathcal{SL}_{2}$))} & Structure: 1 (0\textbar 1) \\
+		\emph{Constraint Types} ($\mathcal{C}_{C}$) & 5 (35.7\%) \\
+		\emph{Constraint Types} ($\mathcal{C}_{T}$) & 9 (64.3\%) \\
+		\hline
+		\emph{Constraint Types (Most Constraints)} & 1. Structure: 10 (28.6\%\textbar8\textbar2) \\
+		                                           & 2. Labeling and Documentation: 6 (17.1\%\textbar5\textbar1) \\
+																							 & 3. Language Tag Cardinality: 4 (11.4\%\textbar4\textbar0) \\
+		\emph{Constraint Type (Most Constraints ($\mathcal{SL}_{2}$))} & Structure: 1 (0\textbar1) \\
 		\hline
 		\emph{Constraints} & 35 (17\textbar 18) \\
-		\emph{Constraints} ($\mathcal{C}_{C}$) & 21 (13\textbar 8) \\
-		\emph{Constraints} ($\mathcal{C}_{T}$) & 14 (4\textbar 10) \\
-		\emph{Constraints ($\mathcal{SL}_{0}$)} & 21 $\equiv$ 60\% (12\textbar 9) \\
-		\emph{Constraints ($\mathcal{SL}_{1}$)} & 5 $\equiv$ 14.3\% (5\textbar 0) \\
-		\emph{Constraints ($\mathcal{SL}_{2}$)} & 9 $\equiv$ 25.7\% (0\textbar 9) \\
+		\emph{Constraints} ($\mathcal{C}_{C}$) & 21 (60\%\textbar13\textbar8) \\
+		\emph{Constraints} ($\mathcal{C}_{T}$) & 14 (40\%\textbar4\textbar10) \\
+		\emph{Constraints ($\mathcal{SL}_{0}$)} & 21 (60\%\textbar12\textbar9) \\
+		\emph{Constraints ($\mathcal{SL}_{1}$)} & 5 (14.3\%\textbar5\textbar0) \\
+		\emph{Constraints ($\mathcal{SL}_{2}$)} & 9 (25.7\%\textbar0\textbar9) \\
 		\end{tabular}
@@
 
-\begin{itemize}
-  \item overview over SKOS data sets\footnote{\url{http://datahub.io/de/dataset?tags=format-skos}}
-	\item overview over thesauri\footnote{\url{http://datahub.io/de/dataset?tags=thesaurus}} (table \ref{tab:thesauri-overview})
-\end{itemize}
+There is a website giving an overview over available \emph{SKOS} data sets\footnote{\url{http://datahub.io/de/dataset?tags=format-skos}}
+and another one giving an overview over available thesauri\footnote{\url{http://datahub.io/de/dataset?tags=thesaurus}}.
+Tables \ref{tab:thesauri-abbreviations} and \ref{tab:thesauri-sparql-endpoints} give an overview over the evaluated thesauri, their abbreviations, and publicly available SPARQL endpoints.
+Table \ref{tab:thesauri-overview} comprehends the number of triples, data sets, and instances of multiple vocabulary-specific classes.
 
@@
 		\emph{UNIVERSAL-QUANTIFICATIONS-01 (!)}\textsuperscript{***} &  &  &  &  &  & \\
-		\emph{CONTEXT-SPECIFIC-VALID-CLASSES-01 (!)}\textsuperscript{*} \\ &  &  &  &  &  & \\
+		\emph{CONTEXT-SPECIFIC-VALID-CLASSES-01 (!)}\textsuperscript{*} &  &  &  &  &  & \\
 		\emph{CONTEXT-SPECIFIC-VALID-PROPERTIES-01 (!)}\textsuperscript{*} &  &  &  &  &  & \\
@@
 
-\section{Rectangular Data (PHDD)}
-
-\tb{ToDo}
+\section{Evaluation of Rectangular Data (\emph{PHDD})}
 
@@
 
-\section{Statistical Classifications (XKOS)}
-
-\tb{ToDo}
+\section{Evaluation of Statistical Classifications (\emph{XKOS})}
 
@@
 		\emph{CJ} & \emph{Nomenclature des catégories juridiques}\tablefootnote{\url{http://rdf.insee.fr/codes/index.html}} \\
-		\emph{ISIC} & \emph{}\tablefootnote{\url{}} \\
-		\emph{ISCO} & \emph{}\tablefootnote{\url{}} \\
+		\emph{ISIC} & \\
+		\emph{ISCO} & \\
 		\end{tabular}
@@
 
-\begin{itemize}
-	\item \emph{Nomenclature d'activités française (NAF)}: French classification expressed in XKOS. the French refinement of the NACE, because it has explanatory notes.
-	\item \emph{Nomenclature des Professions et Catégories Socioprofessionnelles (PCS)}: French classification expressed in XKOS.
-	\item \emph{Nomenclature des catégories juridiques (CJ)}: French classification expressed in XKOS.
-	\item \emph{ISIC}: has explanatory notes too. 
-	\item \emph{ISCO}
-\end{itemize}
-
-\begin{table}[H]
-    \begin{center}
-    \begin{tabular}{@{}lccccccccccc@{}}
-           & \multicolumn{6}{c}{\textbf{Counts}}
-    \\  \cmidrule{2-7}
-    \\       \textbf{Data Sets}
-           & \textbf{\rot{triples}}
-           & \textbf{\rot{}}
-           & \textbf{\rot{}}
-           & \textbf{\rot{}}
-           & \textbf{\rot{}}
-					 & \textbf{\rot{}}
-					 & \textbf{\rot{}}
-    \\ \midrule
-    \emph{NAF} &  &  &  &  &  & \\
-		\emph{PCS} &  &  &  &  &  & \\
-		\emph{CJ} &  &  &  &  &  & \\
-		\emph{ISIC} &  &  &  &  &  & \\
-		\emph{ISCO} &  &  &  &  &  & \\
-		\hline
-		\textbf{Total} & & & & & & \\
-    \bottomrule
-    \end{tabular}
-    \caption{Statistical Classifications Overview}
-		\label{tab:statistical-classifications-overview}
-    \end{center}
-\end{table}
+\emph{Nomenclature d'activités française (NAF)} is the French refinement of the \emph{NACE} classification expressed in XKOS having explanatory notes.
+\emph{Nomenclature des Professions et Catégories Socioprofessionnelles (PCS)} and \emph{Nomenclature des catégories juridiques (CJ)} are French classifications expressed in XKOS.
+The statistical classification \emph{ISIC} has explanatory notes too.
+
+%\begin{table}[H]
+    %\begin{center}
+    %\begin{tabular}{@{}lccccccccccc@{}}
+           %& \multicolumn{6}{c}{\textbf{Counts}}
+    %\\  \cmidrule{2-7}
+    %\\       \textbf{Data Sets}
+           %& \textbf{\rot{triples}}
+           %& \textbf{\rot{}}
+           %& \textbf{\rot{}}
+           %& \textbf{\rot{}}
+           %& \textbf{\rot{}}
+					 %& \textbf{\rot{}}
+					 %& \textbf{\rot{}}
+    %\\ \midrule
+    %\emph{NAF} &  &  &  &  &  & \\
+		%\emph{PCS} &  &  &  &  &  & \\
+		%\emph{CJ} &  &  &  &  &  & \\
+		%\emph{ISIC} &  &  &  &  &  & \\
+		%\emph{ISCO} &  &  &  &  &  & \\
+		%\hline
+		%\textbf{Total} & & & & & & \\
+    %\bottomrule
+    %\end{tabular}
+    %\caption{Statistical Classifications Overview}
+		%\label{tab:statistical-classifications-overview}
+    %\end{center}
+%\end{table}
 

### 2015-04-10 paper/paper7/paper7.tex
evaluation

@@
 \setcounter{secnumdepth}{5}
+
+% tables
+\usepackage{array,graphicx}
+\usepackage{booktabs}
+\usepackage{pifont}
+\newcommand*\rot{\rotatebox{90}}
+\newcommand*\OK{\ding{51}}
+\usepackage{booktabs}
+\newcommand*\ON[0]{$\surd$}
+
+\usepackage{tablefootnote}
+
+\usepackage{float}
 
@@
 Therefore, this technical report contains mappings to DL to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
-We recently published a technical report\footnote{\textcolor{red}{Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as first appendix of this paper) in which we describe constraints to validate metadata on person-level, aggregated data, and thesauri.
+We recently published a technical report\footnote{\textcolor{red}{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as first appendix of this paper) in which we describe constraints to validate metadata on person-level, aggregated data, and thesauri.
 We assign each constraint to constraint types corresponding to RDF validation requirements or to data model specific constraint types\footnote{Requirements/Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-1}}
@@
 
+-----
+
+Although accessible within the \emph{RDF Validator}, we provide all implemented constraints\footnote{\textcolor{red}{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}}} in form of SPARQL CONSTRUCT queries.
+
 \section{Evaluation}
@@
 1,526 / 9,673,055 (\emph{Disco}) data sets / triples using the \emph{RDF Validator} in batch mode.
-Among others data sets, we validated 
+That are more than 4.2 billion triples and 15 thousand data sets.
+We validated, i.a., 
 (1) \emph{QB} data sets published by the \emph{Australian Bureau of Statistics (ABS)},
@@
 
-We recently published a technical report\footnote{\textcolor{red}{Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as second appendix of this paper) 
-in which we describe the evaluation in detail. 
-As we validated 9,990 aggregated data sets, we published the validation results of all aggregated data sets in form of one document per SPARQL endpoint\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.
-Although accessible within the \emph{RDF Validator}, we provide all implemented constraints\footnote{\textcolor{red}{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}}} in form of SPARQL CONSTRUCT queries.
-The correctness of all evaluated constraints, i.e., the gold standard, has been proved by SBE domain experts.
+We recently published a technical report\footnote{\label{technical-report-2}\textcolor{red}{Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as second appendix of this paper) 
+in which we describe the comprehensive evaluation in detail \cite{BoschZapilkoWackerowEckert2015-2}. 
+As we evaluated nearly 10 thousand \emph{QB} data sets, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.
+The correctness of all constraints, i.e., the gold standard, has been proved by SBE domain experts.
+Table \ref{tab:evaluation} shows the evaluation results.
 
-We defined 142 (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) constraints assigned to 52 (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) distinct constraint types and implemented 77 (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS})  of them to actually validate data sets.
-49.3\% (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) of the defined constraints are $\mathcal{C}_{T}$ constraints, and 
-42.3\% (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) of the constraint types are $\mathcal{C}_{T}$ constraint types.
-52.8\% (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) of the defined constraints are associated with the default severity level $\mathcal{SL}_{0}$, 6.3\% (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) are $\mathcal{SL}_{1}$, and
-40.8\% (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) are $\mathcal{SL}_{2}$ constraints.
-\emph{R-86: Existential quantifications} (32.4\%, \emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) are the constraint types with the most defined constraints.
-We got \textcolor{red}{XX} (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) / \textcolor{red}{XX} (\emph{In Total}) constraint violations. 
-\textcolor{red}{XX} (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) / \textcolor{red}{XX} (\emph{In Total}) constraint violations caused by violating $\mathcal{SL}_{0}$ constraints,
-473,574 (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) / \textcolor{red}{XX} (\emph{In Total}) by $\mathcal{SL}_{1}$ constraints, and 
-\textcolor{red}{XX} (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) / \textcolor{red}{XX} (\emph{In Total}) by $\mathcal{SL}_{2}$ constraints.
-\emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} (547,916) and \emph{DISCO-C-COMPARISON-VARIABLES-02} (547,916) (\emph{Disco}) / \textcolor{red}{XX} (\emph{QB}) / \textcolor{red}{XX} (\emph{SKOS}) are the constraints responsible for the most constraint violations.
+\begin{table}[H]
+		\scriptsize
+    \begin{center}
+    \begin{tabular}{@{}lcccc@{}}
+%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
+%    \\  \cmidrule{2-7}
+    \\       \textbf{Criteria\tablefootnote{\emph{C (constraints), CT (constraint types), CV (constraint violations)}}}
+           & \textbf{\emph{Disco}}
+           & \textbf{\emph{QB}}
+					 & \textbf{\emph{SKOS}}
+					 & \textbf{Total}
+    \\ \midrule
+		\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
+		\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
+		\hline
+    \emph{CV} & 3,545,703 & 45,635,846 & 5,540,988 & 54,722,537\\
+		\emph{CV ($\mathcal{SL}_{0}$)} & 2,437,922 (68.8\%) & 0 (0\%) & 2,281,740 (41.2\%) & 4,719,662 (8.6\%) \\
+		\emph{CV ($\mathcal{SL}_{1}$)} & 473,574 (13.4\%) & 45,520,613 (99.75\%) & 3,259,248 (58.8\%) & 49,253,435 (90\%) \\
+    \emph{CV ($\mathcal{SL}_{2}$)} & 634,207 (17.9\%) & 115,233 (0.25\%) & 0 (0\%) & 749,440 (1.4\%) \\
+		\hline
+		\emph{CT} & 52 (15\textbar 37)\tablefootnote{(\label{fnt:1}implemented \textbar not yet implemented)} & 20 (7\textbar 13)\footnotemark[\ref{fnt:1}] & 14 (4\textbar 10)\footnotemark[\ref{fnt:1}] & 53 \\
+		\emph{CT} ($\mathcal{C}_{C}$) & 30 (57.7\%) & 5 (25\%) & 5 (35.7\%) & 30 (56.6\%) \\
+		\emph{CT} ($\mathcal{C}_{T}$) & 22 (42.3\%) & 15 (75\%) & 9 (64.3\%) & 23 (43.4\%) \\
+		\hline
+		\emph{C} & 142 (77\textbar 65)\footnotemark[\ref{fnt:1}] & 35 (20\textbar 15)\footnotemark[\ref{fnt:1}] & 35 (17\textbar 18)\footnotemark[\ref{fnt:1}] & 212 \\
+		\emph{C} ($\mathcal{C}_{C}$) & 72 (50.7\%) & 16 (45.7\%) & 21 (60\%) & 109 (51.4\%) \\
+		\emph{C} ($\mathcal{C}_{T}$) & 70 (49.3\%) & 19 (54.3\%) & 14 (40\%) & 103 (48.6\%) \\
+		\emph{C ($\mathcal{SL}_{0}$)} & 75 (52.8\%)& 4 (11.4\%) & 21 (60\%) & 100 (47.2\%) \\
+		\emph{C ($\mathcal{SL}_{1}$)} & 9 (6.3\%)& 3 (8.6\%) & 5 (14.3\%) & 17 (8\%) \\
+		\emph{C ($\mathcal{SL}_{2}$)} & 58 (40.8\%) & 28 (80\%) & 9 (25.7\%) & 95 (44.8\%) \\
+    \bottomrule
+    \end{tabular}
+    \caption{Evaluation}
+		\label{tab:evaluation}
+    \end{center}
+\end{table}
+
+We identified 142 \emph{Disco} constraints ($\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints to the same extend) assigned to 52 distinct constraint types and implemented 77 of them to actually validate person-level data sets.
+For \emph{QB}, we specified more $\mathcal{C}_{T}$ (54\%) than $\mathcal{C}_{C}$ constraints; for \emph{SKOS}, however, more $\mathcal{C}_{C}$ constraints (60\%).
+We instantiated more $\mathcal{C}_{C}$ (58\%) than $\mathcal{C}_{T}$ constraint types to define \emph{Disco} constraints; 
+for \emph{QB} (75\%) and \emph{SKOS} (64\%), on the other side, more $\mathcal{C}_{T}$ constraint types. 
+In total, we used 53 of overall 82 distinct constraint types (57\% of them are $\mathcal{C}_{C}$ constraint types) to define 212 constraints (equally $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints).
+
+For \emph{Disco} and \emph{SKOS}, more than the half of the constraints are associated with the weakest severity level $\mathcal{SL}_{0}$.
+Within the context of \emph{QB}, 80\% of the constraints are classified as the most serious ones ($\mathcal{SL}_{2}$).
+All in all, there are a little bit more $\mathcal{SL}_{0}$ then $\mathcal{SL}_{2}$ constraints, whereas $\mathcal{SL}_{1}$ constraints are negligible.
+\emph{Existential quantifications} (32.4\%, \emph{Disco}), \emph{data model consistency} (31.4\%, \emph{QB}), and \emph{structure} (28.6\%, \emph{SKOS}) are the constraint types the most constraints are instantiated from.
+By validating \emph{QB} data sets, we got the most constraint violations (more than 45 millions), followed by \emph{SKOS} and \emph{Disco} (with more than 5.5 and 3.5 millions) - consequently, almost 55 million constraint violations were raised during the evaluation which could be used to enhance the metadata quality of these data sets.
+Close to 70\% of all \emph{Disco} constraint violations are caused by violating $\mathcal{SL}_{0}$ constraints.
+For \emph{QB} (nearly 100\%) and \emph{SKOS} (almost 60\%), the majority of the raised constraint violations are classified to be more serious ($\mathcal{SL}_{1}$).
+80\% of all \emph{QB} constraints are $\mathcal{SL}_{2}$ constraints leading to less than 1\% of all \emph{QB} constraint violations.
+Altogether, exactly 90\% of the constraint violations are assigned to the severity level $\mathcal{SL}_{1}$.
+These findings are surprising as only 8\% of all defined constraints are $\mathcal{SL}_{1}$ constraints.
+The constraints responsible for the largest numbers of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916) (\emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102) (\emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903) (\emph{SKOS}).
+We refer to the technical reports\footnotemark[\ref{technical-report-1}] \footnotemark[\ref{technical-report-2}] to get details about constraints on and the evaluation of \emph{XKOS} and \emph{PHDD} data sets.
 
@@
 
-As part of future work, we will identify constraints on rectangular data and statistical classifications and classify them.
+It is still ongoing work to identify and classify constraints on rectangular data (\emph{PHDD}) and statistical classifications (\emph{XKOS}) and to actually evaluate the quality of real world \emph{PHDD} and \emph{XKOS} data sets.
 

### 2015-04-10 paper/paper7/paper7.tex
implementation

@@
 
-In \emph{Missy}, we provide comprehensive Linked Data services\footnote{\textcolor{red}{\url{http://www.gesis.org/missy/eu/general-information/linked-data/}}} like a triple store and diverse RDF exports of person-level metadata conforming to the \emph{Disco} vocabulary in multiple concrete syntaxes (e.g.
-turtle).
-
 SPARQL is generally seen as the method of choice to validate RDF data according to certain constraints.
-We use \emph{SPIN}\footnote{\url{http://spinrdf.org/}}, 
-a SPARQL-based way to formulate and check constraints, as basis to define a
-validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages like Shape Expressions\footnote{\url{http://www.w3.org/Submission/shex-primer/}} and the Web Ontology Language \cite{BoschEckert2014-2}.
-The \emph{RDF Validator} also validates RDF data conforming to SPARQL constraints to ensure correct syntax and semantics of vocabularies such as \emph{Disco, Data Cube, PHDD, DCAT, SKOS, and XKOS}\footnote{\textcolor{red}{SPIN mappings: \url{https://github.com/boschthomas/rdf-validation/SPIN}}}.
-The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.
-We define one SPIN construct template for each constraint type (corresponding to a requirement) and vocabulary-specific constraint\footnote{For details about the \emph{RDF Validator} see \cite{BoschEckert2014-2}}.
-A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples indicating the subject, the properties causing constraint violations, and the reason why constraint violations have been raised.
+We use \emph{SPIN}, 
+a SPARQL-based way to formulate and check constraints, as basis to develop a
+validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages like Shape Expressions,
+%\footnote{\url{http://www.w3.org/Submission/shex-primer/}}
+Resource Shapes, and the Web Ontology Language\footnote{\textcolor{red}{SPIN mappings available at: \url{https://github.com/boschthomas/rdf-validation/SPIN}}} \cite{BoschEckert2014-2}.
+The \emph{RDF Validator} also validates RDF data to ensure correct syntax, semantics, and integrity of diverse vocabularies such as \emph{Disco, QB, PHDD, SKOS, and XKOS}.
+Although accessible within our validation tool, we provide all implemented constraints\footnote{\textcolor{red}{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}}} in form of SPARQL CONSTRUCT queries.
+For the subsequent evaluation, we implemented 212 constraints on \emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{XKOS}, and \emph{PHDD} data sets.
+The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.
+There is one SPIN construct template for each constraint type and vocabulary-specific constraint\footnote{For a comprehensive description of the \emph{RDF Validator}, we refer to \cite{BoschEckert2014-2}}.
+A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples indicating the subject and the properties causing constraint violations, and the reason why constraint violations have been raised.
 A SPIN construct template creates constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
-
------
-
-Although accessible within the \emph{RDF Validator}, we provide all implemented constraints\footnote{\textcolor{red}{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}}} in form of SPARQL CONSTRUCT queries.
+\emph{Missy}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}} provides comprehensive Linked Data services like diverse RDF exports of person-level metadata conforming to the \emph{Disco} vocabulary in form of multiple concrete syntaxes.
 

### 2015-04-10 paper/paper7/paper7.tex
content-driven validation

@@
 \section{Introduction}
-\tb{replace Data Cube by QB?}
+
 %\tb{terminology: data in singular form / data set - NOT dataset / person-level data - NOT microdata / study - NOT survey}
@@
 
-Bosch et al. identified in total \textcolor{red}{74} requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
+Bosch et al. identified in total 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
 We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement (constraint type) in detail and give examples for each (represented by different constraint languages).
@@
 
------
 %
@@
 
-further ideas:
+%further ideas:
+%
+%RDF validation scenarios require the closed-world assumption (CWA) (i.e., a statement is inferred to be false if it cannot be proved to be true).
 
-RDF validation scenarios require the closed-world assumption (CWA) (i.e., a statement is inferred to be false if it cannot be proved to be true).
-
------
-
-use-case specific constraints, e.g., DCAT: searching for metadata
-\tb{Thomas: ToDo}
+%use-case specific constraints, e.g., DCAT: searching for metadata
+%\tb{Thomas: ToDo}
 
@@
 
-\subsubsection{Aggregated Metadata and Data}
-\label{aggregated-metadata-and-data}
+\textbf{Observations of Aggregated Data Sets.}
+The purpose of some constraints is to ensure the integrity of
+the data according to intended data model semantics (\emph{data model consistency}).
+Every \emph{qb:Observation}, e.g., must have a value for each dimension
+declared in its associated \emph{qb:DataStructureDefinition} ($\mathcal{SL}_{2}$)
+and no two \emph{qb:Observations} in the same \emph{qb:DataSet}
+may have the same value for all dimensions ($\mathcal{SL}_{1}$).
+If a \emph{qb:DataSet} \emph{D} has a \emph{qb:Slice} \emph{S}, and \emph{S} has an
+\emph{qb:Observation} \emph{O}, then the \emph{qb:DataSet} corresponding to \emph{O} must be \emph{D} ($\mathcal{SL}_{1}$).
 
-\tb{ToDo}
-
-- for each dimension there should be a description and code lists.
-
-- for each code list there should be a description.
-
-- there should be a relationship to the underlying person-level data.
-
-\subsubsection{Person-Level Metadata and Data}. 
-\label{person-level-metadata-and-data}
+%- for each dimension there should be a description and code lists.
+%
+%- for each code list there should be a description.
+%
+%- there should be a relationship to the underlying person-level data.
 
@@
 
-\textbf{Frequencies and Descriptive Statistics.}
+\textbf{Descriptive Statistics.}
 The property \emph{disco:percentage} stands for the number of cases of a given code in relation to the total number of cases for a particular variable within a data set.
@@
 and the minimum of all variable codes do not have to be greater than the maximum ($\mathcal{SL}_{2}$).
-Some constraints ensure the integrity of the data according to intended data model semantics (\emph{data model consistency}).
 Codes (\emph{skos:Concept}), e.g, are ordered and therefore have fixed positions in an ordered collection (\emph{skos:OrderedCollection}) within variable representations.
 In order to check the correctness of relative frequencies' calculations, the cumulative percentage (\emph{disco:cumulativePercentage}) of the current code must exactly be the cumulative percentage of the previous code (\emph{disco:cumulativePercentage})
-plus the percentage value (\emph{disco:percentage}) of the current code ($\mathcal{SL}_{2}$).
+plus the percentage value (\emph{disco:percentage}) of the current code (\emph{data model consistency}; $\mathcal{SL}_{2}$).
 
@@
 \textbf{Membership in Controlled Vocabularies.}
-In many cases, resources must be members of listed controlled vocabularies (\emph{R-32}).
-Types of summary statistics like minimum, maximum, and mode are maintained within a controlled vocabulary.  
-Thus, summary statistics can only have \emph{disco:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType}, a \emph{skos:ConceptScheme} (\emph{R-91: universal quantification}; $\mathcal{SL}_{2}$):
-\begin{center}
-\begin{DL}
-SummaryStatistics $\sqsubseteq$ $\forall summaryStatisticType.A$ \\
-$A \equiv Concept \sqcap \forall inScheme . B$ \\
-$B \equiv ConceptScheme \sqcap \{SummaryStatisticType\}$
-\end{DL}
-\end{center}
+In many cases, resources must be members of controlled vocabularies (\emph{R-32}).
+Summary statistics types like minimum, maximum, and arithmetic mean, e.g., are maintained within a controlled vocabulary.  
+Summary statistics can only have \emph{disco:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType}, a \emph{skos:ConceptScheme} ($\mathcal{SL}_{2}$).
+If a dimension property has a \emph{qb:codeList},
+then the value of the dimension property on every \emph{qb:Observation} must be in the code list ($\mathcal{SL}_{2}$).
+
+%\begin{center}
+%\begin{DL}
+%SummaryStatistics $\sqsubseteq$ $\forall summaryStatisticType.A$ \\
+%$A \equiv Concept \sqcap \forall inScheme . B$ \\
+%$B \equiv ConceptScheme \sqcap \{SummaryStatisticType\}$
+%\end{DL}
+%\end{center}
 
@@
 
-\textbf{Searching for (Meta)data.}
-
-- DCAT
-
-\textbf{Data Integration.}
-use RDF validation for data integration
+%\textbf{Searching for (Meta)data.}
+%
+%- DCAT
+%
+%\textbf{Data Integration.}
+%use RDF validation for data integration
 
@@
 a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}) (\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}), and every \emph{qb:DataSet} has (\emph{qb:structure}) exactly one associated \emph{qb:DataStructureDefinition} (\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition $\sqcap$ $\leq$1 structure.DataStructureDefinition}).
+
+%DATA-CUBE-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-
+%02: Unique data set (IC-1 [3]) - Every qb:Observation has (qb:dataSet) ex-
+%actly one associated qb:DataSet (Observation  ¥1 dataSet.DataSet [
+%¤1 dataSet.DataSet).
+%Severity level: ERROR
+%
+%(\emph{R-75: minimum qualified cardinality restrictions})
+%
+%DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-
+%02: Unique DSD (IC-2 [3]) - Every qb:DataSet has (qb:structure) exactly one
+%associated qb:DataStructureDefinition (DataSet  ¥1 structure.DataStructureDefinition
+%[ ¤1 structure.DataStructureDefinition).
+%Severity level: ERROR
+%
+%(\emph{R-74: exact qualified cardinality restrictions})
+
 %\footnote{\emph{DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02}}.

### 2015-04-11 paper/paper7/paper7.tex
technology-driven validation

@@
 Researchers typically represent their results as aggregated data in form of two-dimensional tables with only a few columns (so-called \emph{variables} such as \emph{sex} or \emph{age}).
-The \emph{RDF Data Cube Vocabulary (Data Cube)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e.
+The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e.
 multi-dimensional aggregate data, in RDF \cite{Cyganiak2010}.
 Aggregate data is derived from person-level data by statistics on groups or aggregates such as counts, means, and frequencies.
-The SDMX metadata standard\footnote{http://sdmx.org/} – used as the basis for \emph{Data Cube} – and DDI have traditionally made efforts to align their content. 
-Similarly, some of the developers of \emph{Disco} were also involved in the development of \emph{Data Cube}, 
+The SDMX metadata standard\footnote{http://sdmx.org/} – used as the basis for \emph{QB} – and DDI have traditionally made efforts to align their content. 
+Similarly, some of the developers of \emph{Disco} were also involved in the development of \emph{QB}, 
 allowing the RDF versions of these standards to retain that alignment.
-While \emph{Disco} and \emph{Data Cube} provide terms for the description of data sets, 
+While \emph{Disco} and \emph{QB} provide terms for the description of data sets, 
 both on a different level of aggregation, 
@@
 (2) metadata providers and harvesters ensuring high quality metadata by validating metadata on highly complex RDF data sets.
-In this paper, we show in form of a complete real world running example how to represent metadata on highly complex person-level data (\emph{Disco}), metadata on aggregated data (\emph{Data Cube}), and aggregated as well as person-level data in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
+In this paper, we show in form of a complete real world running example how to represent metadata on highly complex person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and aggregated as well as person-level data in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
 We explain why RDF validation is important in this context and how (meta)data is validated against RDF constraints to ensure high quality (meta)data within this complex of data sets on different levels of aggregation (\textbf{contribution 2}, section \ref{rdf-validation}).
@@
 
-\tb{ToDO: insert how example is represented in Data Cube in this paragraph}
+\tb{ToDO for Ben: can you please insert how example is represented in Data Cube in this paragraph}
 
-\emph{Data Cube} is a vocabulary to represent metadata on multi-dimensional aggregate data.
+\emph{QB} is a vocabulary to represent metadata on multi-dimensional aggregate data.
 
-\begin{ex}
-EXAMPLE
-\end{ex}
+data set
 
-\footnote{The complete running example in RDF is available at: \url{XXXXX}}
+data structure definition
+
+dimensions
+
+measure
+
+observations
+
+\footnote{\textcolor{red}{The complete running example in RDF is available at: \url{XXXXX}}}
 
@@
 We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ (informational) via $\mathcal{SL}_{1}$ (warning) to $\mathcal{SL}_{2}$ (error).
+The violation of $\mathcal{SL}_{0}$ constraints does not mean that there are serious mistakes in either syntax or semantics.
+These constraints may point to possible data improvements in order to get ideal RDF representations.
+Data not conforming to $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is syntactically or semantically not correctly represented.
+The difference between $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is that $\mathcal{SL}_{1}$ invalid data could be processed 
+whereas $\mathcal{SL}_{1}$ invalid data cannot be processed further. 
 Although we provide default severity levels for each constraint, users should be able to specify severity levels of constraints they need to validate for their individual use cases, i.e., users should be able to define use case specific severity levels for constraints.
-In this section, we describe constraints and constraint types which are important to ensure the quality of metadata and data on different levels of aggregation. 
-We classify them according to the type of validation, and associate default severity levels with them.
+In this section, we describe constraints and constraint types which are important to ensure (meta)data  quality on different aggregation levels. 
+Furthermore, we associate constraints with default severity levels and assign them to validation types.
 
@@
 To get an overview over a series/study either an abstract, a title, an alternative title, or links to external descriptions should be provided. 
-If the abstract and an external description are absent, 
+If an abstract and an external description are absent, 
 a title or an alternative title has to be stated ($\mathcal{SL}_{1}$).
@@
 The abstract of series/studies, e.g., should have a minimum length (\emph{xsd:minLength}; $\mathcal{SL}_{1}$).
-\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relations to individuals of certain types.
+\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals of certain types.
 If a study, e.g., has no associated data sets ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
-If there is no metadata (especially case and variable quantities) on data files including the actual data of data sets ($\mathcal{SL}_{1}$), the description of the data sets and the underlying study is not sufficient.
+If there is no metadata on data files including the actual data of data sets (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the underlying study is not sufficient.
 The case quantity measures how many cases are collected for a study.
@@
 If a researcher wants to get a first overview over comparable variables (use case 1), 
-the first three constraints may be sufficient for this purpose.
+covering the first three constraints may be sufficient for this purpose.
 Thus, the severity level of the first three constraints is stronger ($\mathcal{SL}_{2}$) than the severity level of the next two constraints ($\mathcal{SL}_{1}$ and $\mathcal{SL}_{0}$).
@@
 and the minimum of all variable codes do not have to be greater than the maximum ($\mathcal{SL}_{2}$).
-Codes (\emph{skos:Concept}), e.g, are ordered and therefore have fixed positions in an ordered collection (\emph{skos:OrderedCollection}) within variable representations.
-In order to check the correctness of relative frequencies' calculations, the cumulative percentage (\emph{disco:cumulativePercentage}) of the current code must exactly be the cumulative percentage of the previous code (\emph{disco:cumulativePercentage})
+Codes (\emph{skos:Concept}) are ordered and therefore have fixed positions in an ordered collection (\emph{skos:OrderedCollection}) within variable representations.
+In order to check the correctness of relative frequencies' calculations, the cumulative percentage (\emph{disco:cumulativePercentage}) of the current code must exactly be the cumulative percentage of the previous code
 plus the percentage value (\emph{disco:percentage}) of the current code (\emph{data model consistency}; $\mathcal{SL}_{2}$).
@@
 In many cases, resources must be members of controlled vocabularies (\emph{R-32}).
-Summary statistics types like minimum, maximum, and arithmetic mean, e.g., are maintained within a controlled vocabulary.  
+If a dimension property, e.g., has a \emph{qb:codeList},
+then the value of the dimension property on every \emph{qb:Observation} must be in the code list ($\mathcal{SL}_{2}$).
+Summary statistics types like minimum, maximum, and arithmetic mean are maintained within a controlled vocabulary.  
 Summary statistics can only have \emph{disco:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType}, a \emph{skos:ConceptScheme} ($\mathcal{SL}_{2}$).
-If a dimension property has a \emph{qb:codeList},
-then the value of the dimension property on every \emph{qb:Observation} must be in the code list ($\mathcal{SL}_{2}$).
 
@@
 \textbf{Coverage.}
-Information about the temporal (\emph{dcterms:temporal}), the spatial (\emph{dcterms:spatial}), and the topical coverage (\emph{dcterms:subject}) of series, studies, data sets, and data files (\emph{R-86: existential quantification}; $\mathcal{SL}_{1}$) is of interest when performing particular queries
-	(e.g. to search for all data sets of given years (temporal coverage) in which data is collected in given countries (spatial coverage) about given topics (topical coverage)).
+Information about the temporal (\emph{dcterms:temporal}), the spatial (\emph{dcterms:spatial}), and the topical coverage (\emph{dcterms:subject}) of series, studies, data sets, and data files (\emph{R-86}; $\mathcal{SL}_{1}$) is of interest when performing frequently formulated queries
+	(e.g. to search for all data sets of given years (temporal coverage) in which data is collected in certain countries (spatial coverage) about particular topics (topical coverage)).
 Depending on property datatypes,
 two different literal values have
-a specific ordering with respect to an operator (e.g. \textless, \textless=, \textgreater, \textgreater=, =, !=) (\emph{R-43: literal value comparison}).
+a specific ordering with respect to an operator like \textless (\emph{R-43: literal value comparison}).
 Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}) ($\mathcal{SL}_{2}$).
-It must be made sure that all literal values are valid for their datatypes (\emph{R-223: value is valid for datatype}; $\mathcal{SL}_{2}$).
-It has to be ensured, e.g., that all date values (e.g.
-{\em disco:startDate}, {\em disco:endDate}, {\em dcterms:date}) are really of the datatype \emph{xsd:date}, or that \emph{xsd:nonNegativeInteger} values (e.g.
-\emph{disco:frequency}) are not negative.
+\emph{R-223} serves to make sure that all literal values are valid with regard to their datatypes ($\mathcal{SL}_{2}$).
+Thus, all date values (e.g.
+{\em disco:startDate}, {\em disco:endDate}, {\em dcterms:date}) must be of the datatype \emph{xsd:date} and \emph{xsd:nonNegativeInteger} values (e.g.
+\emph{disco:frequency}) do not have to be negative.
 
-\textbf{Organizations, Hierarchies, Classifications, and Ordering.}
+%\textbf{Organizations, Hierarchies, Classifications, and Ordering.}
+\textbf{Hierarchies and Ordering.}
 SKOS is based on RDF, which is a graph-based data model.
 Therefore, we can concentrate on the vocabulary's graph-based structure for assessing the quality of SKOS vocabularies and apply graph- and network-analysis techniques (\emph{structure}) like
-(1) a vocabulary should provide entry points (top concepts) to the data to provide efficient access and guidance for human users and
+(1) a vocabulary should provide entry points (top concepts) to the data to provide efficient access and guidance for human users,
 (2) concepts, internal to the tree, should not be indicated as top concepts, and
 (3) a vocabulary should not contain many orphan concepts 
-(An orphan concept is a concept without any associative or hierarchical relations lacking valuable context information.
-A controlled vocabulary that contains many orphan concepts is less usable for search and retrieval use cases, as, e.g., no hierarchical query expansion can be performed on search terms to find documents with more general content.) \cite{MaderHaslhoferIsaac2012}.
-\tb{add disco example}
-
-Objects/literals can be ordered (\emph{R-121, R-217}) for given properties.
+(concepts without any associative or hierarchical relations) lacking valuable context information.
+A controlled vocabulary that contains many orphan concepts is less usable for search and retrieval use cases.
+%, as, e.g., no hierarchical query expansion can be performed on search terms to find documents with more general content.) \cite{MaderHaslhoferIsaac2012}. 
+Objects and literals can be \emph{ordered} (\emph{R-121, R-217}) for given properties.
 \emph{Disco }variables, questions, and codes/categories are typically organized in a particular order. 
-If codes/categories of a \emph{disco:Representation} of a \emph{disco:Variable} should be ordered, the variable representation should also be of the type \emph{skos:OrderedCollection} containing multiple codes/categories (each represented as \emph{skos:Concept}) in a \emph{skos:memberList}.
-
-- SKOS validation of hierarchies of theoretical concepts
-
-\tb{ToDO: ask Franck if INSEE already expressed well known classification systems with XKOS}
+If a variable code list should be ordered, the variable representation should be of the type \emph{skos:OrderedCollection} containing multiple codes/categories (each represented as \emph{skos:Concept}) in a \emph{skos:memberList}.
 
 \textbf{Reusability.}
-Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes and categories), but not both ($\mathcal{SL}_{2}$).
-Constraints of the constraint type \emph{context-specific exclusive or of property groups} (\emph{R-11})
-restrict individuals of given classes to have exactly one of multiple property groups.
+Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes/categories), but not both ($\mathcal{SL}_{2}$).
+The constraint type \emph{context-specific exclusive or of property groups} (\emph{R-11})
+restricts individuals of given classes to have exactly one of multiple property groups.
 
-\begin{center}
-\begin{DL}
-Concept $\sqsubseteq$ ($\neg$ D $\sqcap$ C) $\sqcup$ (D $\sqcap$ $\neg$ C), D $\equiv$ A $\sqcap$ B \\
-A $\sqsubseteq$ $\geq$ 1 notation.string $\sqcap$ $\leq$ 1 notation.string \\
-B $\sqsubseteq$ $\geq$ 1 prefLabel.string $\sqcap$ $\leq$ 1 prefLabel.string \\
-C $\sqsubseteq$ $\geq$ 1 definition.string $\sqcap$ $\leq$ 1 definition.string \\
-\end{DL}
-\end{center}
+%\begin{center}
+%\begin{DL}
+%Concept $\sqsubseteq$ ($\neg$ D $\sqcap$ C) $\sqcup$ (D $\sqcap$ $\neg$ C), D $\equiv$ A $\sqcap$ B \\
+%A $\sqsubseteq$ $\geq$ 1 notation.string $\sqcap$ $\leq$ 1 notation.string \\
+%B $\sqsubseteq$ $\geq$ 1 prefLabel.string $\sqcap$ $\leq$ 1 prefLabel.string \\
+%C $\sqsubseteq$ $\geq$ 1 definition.string $\sqcap$ $\leq$ 1 definition.string \\
+%\end{DL}
+%\end{center}
 
@@
 
-Constraints of some constraint types are directly and automatically derived from conceptual models of multiple vocabularies.
-This way, \emph{property domains and ranges, universal and existential quantifications, minimum, maximum, and exact cardinality restrictions} are defined for each property of vocabularies against which one wish to validate.
-As these constraints directly depend on the intended semantics of data models, associated severity levels are very strong.
+\tb{use PHDD and XKOS here}
 
-Vocabularies should not invent any new terms or use deprecated elements.
-The \emph{vocabulary} constraint should be the first one to be checked for each reused vocabulary.
+Constraints of some constraint types are directly and automatically derived from syntax and semantics of vocabularies' conceptual models.
+As these constraints depend on data models' intended semantics, associated default severity levels are in most cases very strong ($\mathcal{SL}_{2}$).
+
+\textbf{Vocabulary.}
+One should not invent new or use deprecated terms of vocabularies (\emph{vocabulary}).
 \emph{Property Domains} (\emph{R-25, R-26}) and \emph{Ranges} (\emph{R-28, R-35}) restrict domains and ranges of properties.
-Only \emph{skos:ConceptSchemes}, e.g., can have \emph{skos:hasTopConcept} relationships (\ms{$\exists$ hasTopConcept.$\top$ $\sqsubseteq$ ConceptScheme}) and
-\emph{xkos:belongsTo} relationships can only point to instances of the class \emph{skos:Concept} (\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}).
-A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals that are instances of particular classes  or data ranges.
+Only \emph{phdd:Tables}, e.g., can have \emph{phdd:isStructuredBy} relationships (\ms{$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table}) and
+\emph{xkos:belongsTo} relationships can only point to \emph{skos:Concept} instances (\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}).
+A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
 Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets} (\ms{Catalog $\sqsubseteq$ $\forall$ dataset.Dataset}).
-An \emph{existential quantification} (\emph{R-86}) contains all those individuals that are connected by a property to individuals/literals that are instances of given classes or data ranges.
+Out-dated classes and properties of previous vocabulary versions can be marked as deprecated.
+The constraint type \emph{context-specific valid classes and properties} (\emph{R-209; R-210}) can be used to specify which classes and properties are valid in which context - here a given vocabulary version.
+Many properties are not necessarily required but \emph{recommended} within a particular context (\emph{R-72}).
+The property {\em skos:notation}, e.g., is not mandatory for {\em disco:Variable}s, but recommended to represent variable names.
+
+\textbf{Cardinality Restrictions.}
+An \emph{existential quantification} (\emph{R-86}) contains all those individuals that are connected by a property to individuals/literals of given classes or data ranges.
 Every \emph{qb:SliceKey}, e.g., must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}).
-
-\emph{Minimum/maximum/exact qualified cardinality restrictions} (\emph{R-74, R-75, R-76}) contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals that are instances of particular classes or data ranges.
-\emph{Minimum qualified cardinality restrictions} are defined for each property of multiple vocabularies like \emph{Disco}.
-A \emph{disco:Questionnaire}, e.g., has at least one \emph{disco:question} relationship to \emph{disco:Questions} (\ms{Questionnaire $\sqsubseteq$ $\geq$1 question.Question}),
-a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}) (\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}), and every \emph{qb:DataSet} has (\emph{qb:structure}) exactly one associated \emph{qb:DataStructureDefinition} (\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition $\sqcap$ $\leq$1 structure.DataStructureDefinition}).
+\emph{Minimum/maximum/exact qualified cardinality restrictions} (\emph{R-74, R-75, R-76}) contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals of particular classes or data ranges.
+A \emph{phdd:TableStructure}, e.g., has at least one \emph{phdd:column} relationship to a \emph{phdd:Column} (\ms{TableStructure $\sqsubseteq$ $\geq$1 column.Column}),
+a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}) (\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}), and a \emph{qb:DataSet} has (\emph{qb:structure}) exactly one associated \emph{qb:DataStructureDefinition} (\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition $\sqcap$ $\leq$1 structure.DataStructureDefinition}).
 
@@
 %\footnote{\emph{DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02}}.
-For particular data properties, values of predefined languages must be stated for determined number of times (\emph{R-48, R-49}).
-Some controlled vocabularies contain literals in natural language, but without information what language has actually been used. Language tags might also not conform to language standards. 
-Some concepts in a thesaurus are labeled in only one language, some in multiple languages.
-It may be desirable to have each concept labeled in each of the languages that also are used on the other concepts.
-This is not always possible, but incompleteness of language coverage for some concepts can indicate shortcomings of the vocabulary
-(severity level: informational) \cite{MaderHaslhoferIsaac2012}.
 
-All properties, not having the same domain and range classes, are defined to be pairwise disjoint
+\textbf{Language Tag Cardinality.}
+For data properties, it may be desirable to restrict that values of predefined languages must be present for determined number of times (\emph{R-48, R-49}):
+(1) Some controlled vocabularies contain literals in natural language, but without information what language has actually been used. 
+(2) Language tags must conform to language standards. 
+(3) Some thesaurus concepts are labeled in only one, others in multiple languages.
+It may be desirable to have each concept labeled in each of the languages that are also used on the other concepts.
+Although not always possible, incompleteness of language coverage for some concepts may indicate shortcomings of thesauri
+\cite{MaderHaslhoferIsaac2012}.
+
+\textbf{Disjointness and Allowed Values.}
+All properties, not having the same domain and range classes, are defined to be pairwise \emph{disjoint}
 (\emph{R-9: disjoint properties}), stating that no individual \emph{x} can be connected to an individual/literal \emph{y} by disjoint properties like \emph{phdd:isStructuredBy} and \emph{phdd:column} ($isStructuredBy \sqsubseteq \neg column$).
@@
 i.e. no individual can be at the same time an instance of more than one disjoint class.
-It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values.  
+Furthermore, it is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values.  
 \emph{Allowed values} (\emph{R-30, R-37}) for properties can be IRIs (matching one or multiple patterns), any literals, allowed literals (e.g.
@@
 
+\textbf{Validation and Reasoning.}
 Constraints of some constraint types can be derived from vocabularies' data models for which reasoning can be performed prior to validation which enables to resolve possible constraint violations.
-\emph{Subsumption} (\emph{R-100}) states that the class \emph{C1} is a sub-class of the class \emph{C2} - \emph{C1} is more specific than \emph{C2}, 
-i.e. each resource of the class \emph{C1} must also be part of the class extension of \emph{C2}. 
-All \emph{disco:Universe}s, e.g., must also be \emph{skos:Concept}s (\ms{Universe $\sqsubseteq$ Concept}).
-\emph{Sub Properties} (\emph{R-54, R-64}) state that the property \emph{P1} is a sub-property of the property \emph{P2} - that is, if individual \emph{x} is connected by \emph{P1} to individual/literal \emph{y}, then \emph{x} is also connected by \emph{P2} to \emph{y}.
-If \emph{x} is connected by \emph{disco:fundedBy} to \emph{y}, then \emph{x} is also connected by \emph{dcterms:contributor} to \emph{y} (\ms{fundedBy $\sqsubseteq$ contributor}).
-\emph{Asymmetric object properties} (\emph{R-62}) restrict that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}.
-\emph{Asymmetric object properties} are defined for each asymmetric object property for which a semantically equivalent object property pointing from the other direction may also be possible to be specified in the appropriate vocabulary.
+\emph{Subsumption} (\emph{R-100}) states that \emph{C1} is a sub-class of \emph{C2} - \emph{C1} is more specific than \emph{C2}, 
+i.e., each \emph{C1} resource must also be part of the \emph{C2} class extension. 
+All \emph{disco:Universe}s, e.g., must also be of the type \emph{skos:Concept} (\ms{Universe $\sqsubseteq$ Concept}).
+\emph{Sub Properties} (\emph{R-54, R-64}) state that \emph{P1} is a sub-property of \emph{P2} - i.e., if individual \emph{x} is connected by \emph{P1} to individual/literal \emph{y}, then \emph{x} is also connected by \emph{P2} to \emph{y}.
+If a study is funded by (\emph{disco:fundedBy}) an organization, then this organization contributed (\emph{dcterms:contributor}) to this study (\ms{fundedBy $\sqsubseteq$ contributor}).
+With \emph{Asymmetric object properties} (\emph{R-62}) it can be restricted that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}.
+Such constraints are defined for each vocabulary's object property for which a semantically equivalent object property pointing from the other direction would also be possible but is not defined within the vocabulary.
 A \emph{disco:Variable}, e.g., may be based on (\emph{disco:basedOn}) a \emph{disco:RepresentedVariable}.
 A \emph{disco:RepresentedVariable}, however, cannot be based on a \emph{disco:Variable} (\ms{$basedOn \sqcap basedOn^{-} \sqsubseteq \bot$}).
-\emph{Default values} (\emph{R-31, R-38}) for objects/literals of given prooperties are inferred automatically when properties are not stated, in order to pre-populate input forms and to insert a required property that is missing in a web service call.
-The value \emph{true} for the property {\em disco:isPublic} ({\em xsd:boolean}) indicates that the data set ({\em disco:LogicalDataSet}) can be accessed by anyone.
-Per default, access to data sets should be restricted (\emph{false}).
-
------
-
-For future vocabulary versions, out-dated classes and properties can be marked as deprecated.
-There are constraint types (\emph{context-specific valid classes and properties}) to specify which classes and properties are valid in which context (here a specific vocabulary version).
-Many properties are not necessarily required but recommended within a particular context (\emph{recommended properties}).
-The property {\em skos:notation} is not mandatory for {\em disco:Variable}s, but recommended to indicate variable names.
+\emph{Default values} (\emph{R-31, R-38}) for objects/literals of given prooperties are inferred automatically when properties are not stated.
+The value \emph{true} for the property {\em disco:isPublic} ({\em xsd:boolean}) indicates that a data set ({\em disco:LogicalDataSet}) can be accessed by anyone.
+Per default, however, access to data sets should be restricted (\emph{false}).
 
@@
 Each integrity constraint is expressed as narrative prose and, where possible, a SPARQL ASK query or query template. 
-If the ASK query is applied to an RDF graph then it will return true if that graph contains one or more Data Cube instances which violate the corresponding constraint \cite{CyganiakReynolds2014}.
+If the ASK query is applied to an RDF graph then it will return true if that graph contains one or more \emph{QB} instances which violate the corresponding constraint \cite{CyganiakReynolds2014}.
 

### 2015-04-12 paper/paper7/paper7.tex
technology-driven validation

@@
 Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}) ($\mathcal{SL}_{2}$).
-\emph{R-223} serves to make sure that all literal values are valid with regard to their datatypes ($\mathcal{SL}_{2}$).
-Thus, all date values (e.g.
-{\em disco:startDate}, {\em disco:endDate}, {\em dcterms:date}) must be of the datatype \emph{xsd:date} and \emph{xsd:nonNegativeInteger} values (e.g.
-\emph{disco:frequency}) do not have to be negative.
 
@@
 
-\tb{use PHDD and XKOS here}
-
 Constraints of some constraint types are directly and automatically derived from syntax and semantics of vocabularies' conceptual models.
@@
 The property {\em skos:notation}, e.g., is not mandatory for {\em disco:Variable}s, but recommended to represent variable names.
+\emph{R-223} serves to make sure that all literal values are valid with regard to their datatypes.
+Thus, all date values (e.g.
+{\em disco:startDate}, {\em disco:endDate}, {\em dcterms:date}) must be of the datatype \emph{xsd:date} and \emph{xsd:nonNegativeInteger} values (e.g.
+\emph{disco:frequency}) do not have to be negative.
 
@@
 \textbf{Disjointness and Allowed Values.}
-All properties, not having the same domain and range classes, are defined to be pairwise \emph{disjoint}
+All properties, not having the same domain and range classes, are defined to be pairwise disjoint
 (\emph{R-9: disjoint properties}), stating that no individual \emph{x} can be connected to an individual/literal \emph{y} by disjoint properties like \emph{phdd:isStructuredBy} and \emph{phdd:column} ($isStructuredBy \sqsubseteq \neg column$).
-All \emph{Disco} classes are defined to be pairwise disjoint (\emph{R-7: disjoint classes}; e.g. \ms{Study $\sqcap$ Variable $\sqsubseteq$ $\perp$}),
-i.e. no individual can be at the same time an instance of more than one disjoint class.
-Furthermore, it is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values.  
+All \emph{XKOS} classes are pairwise disjoint (\emph{R-7: disjoint classes}; e.g. \ms{ClassificationLevel $\sqcap$ ConceptAssociation $\sqsubseteq$ $\perp$}),
+i.e., individuals cannot be instances of multiple disjoint classes.
+It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values.  
 \emph{Allowed values} (\emph{R-30, R-37}) for properties can be IRIs (matching one or multiple patterns), any literals, allowed literals (e.g.
@@
 \textbf{Validation and Reasoning.}
-Constraints of some constraint types can be derived from vocabularies' data models for which reasoning can be performed prior to validation which enables to resolve possible constraint violations.
-\emph{Subsumption} (\emph{R-100}) states that \emph{C1} is a sub-class of \emph{C2} - \emph{C1} is more specific than \emph{C2}, 
-i.e., each \emph{C1} resource must also be part of the \emph{C2} class extension. 
-All \emph{disco:Universe}s, e.g., must also be of the type \emph{skos:Concept} (\ms{Universe $\sqsubseteq$ Concept}).
-\emph{Sub Properties} (\emph{R-54, R-64}) state that \emph{P1} is a sub-property of \emph{P2} - i.e., if individual \emph{x} is connected by \emph{P1} to individual/literal \emph{y}, then \emph{x} is also connected by \emph{P2} to \emph{y}.
-If a study is funded by (\emph{disco:fundedBy}) an organization, then this organization contributed (\emph{dcterms:contributor}) to this study (\ms{fundedBy $\sqsubseteq$ contributor}).
-With \emph{Asymmetric object properties} (\emph{R-62}) it can be restricted that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}.
-Such constraints are defined for each vocabulary's object property for which a semantically equivalent object property pointing from the other direction would also be possible but is not defined within the vocabulary.
+Some constraint types enable performing reasoning prior to validation which may resolve or cause constraint violations.
+With \emph{subsumption} (\emph{R-100}) one can state that \emph{xkos:ClassificationLevel} is a sub-class of \emph{skos:Collection}, i.e., each \emph{xkos:ClassificationLevel} resource must also be part of the \emph{skos:Collection} class extension (\ms{xkos:ClassificationLevel $\sqsubseteq$ skos:Collection}).
+With \emph{sub properties} (\emph{R-54, R-64}) one can state that \emph{disco:fundedBy} is a sub-property of \emph{dcterms:contributor} - i.e., if a study is funded by an organization, then this organization contributed to this study (\ms{disco:fundedBy $\sqsubseteq$ dcterms:contributor}).
+\emph{Asymmetric object properties} (\emph{R-62}) restrict that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}.
+Such constraints are defined for each object property for which a semantically equivalent object property pointing from the other direction would also be possible but is not defined within the vocabulary.
 A \emph{disco:Variable}, e.g., may be based on (\emph{disco:basedOn}) a \emph{disco:RepresentedVariable}.
-A \emph{disco:RepresentedVariable}, however, cannot be based on a \emph{disco:Variable} (\ms{$basedOn \sqcap basedOn^{-} \sqsubseteq \bot$}).
-\emph{Default values} (\emph{R-31, R-38}) for objects/literals of given prooperties are inferred automatically when properties are not stated.
-The value \emph{true} for the property {\em disco:isPublic} ({\em xsd:boolean}) indicates that a data set ({\em disco:LogicalDataSet}) can be accessed by anyone.
+A \emph{disco:RepresentedVariable}, however, cannot be based on a \emph{disco:Variable} (\ms{$disco:basedOn \sqcap disco:basedOn^{-} \sqsubseteq \bot$}).
+\emph{Default values} (\emph{R-31, R-38}) for objects/literals of given prooperties are inferred automatically when properties are not present.
+The value \emph{true} for the property {\em disco:isPublic} indicates that a {\em disco:LogicalDataSet} can be accessed by anyone.
 Per default, however, access to data sets should be restricted (\emph{false}).
-
------
-
-It has to be ensured that a value is valid for its datatype (\emph{Value is Valid for Datatype}), e.g., 
-that a date is really a date, or that a \emph{xsd:nonNegativeInteger} value is not negative. 
-It is checked if all literals of {\em xsd:date} properties are really dates (e.g. {\em disco:startDate}, {\em disco:endDate}, {\em dcterms:date}).
-
------
-
-The validation of instances data (direct or indirect) exploits the sub-class or sub-property link in a given ontology (\emph{Use Sub-Super Relations in Validation}).
-This validation can indicate when the data is verbose (redundant) or expressed at a too general level, and could thus be improved.
+Validation should \emph{exploit sub-super relations} in vocabularies (\emph{R-224}).
 If \emph{dcterms:coverage} and one of its sub-properties (\emph{dcterms:spatial}, \emph{dcterms:temporal}) are present,
 it is checked that \emph{dcterms:coverage} is not redundant with its sub-properties. 
-
------
+This validation can indicate when the data is verbose (redundant) or expressed at a too general level and could thus be improved.
 

### 2015-04-12 paper/paper7/paper7.tex
related work

@@
 RDF data validation according to predefined constraints is a much sought-after feature, 
-particularly as this is taken for granted in the XML world (DDI-XML documents are validated against diverse XSDs\footnote{\url{http://www.ddialliance.org/Specification/}}).
+particularly as this is taken for granted in the XML world (DDI-XML documents are validated against diverse XSDs\footnote{\label{fnt:DDI-XSDs}\url{http://www.ddialliance.org/Specification/}}).
 Several approaches exist to meet this requirement, ranging from using \emph{OWL 2} as a constraint language to \emph{SPIN}\footnote{\url{http://spinRDF.org/}}, a SPARQL-based way to formulate and check constraints.
@@
 
-With RDF validation, one can overcome the drawbacks when validating XML documents.
-Certain things cannot be validated using XSDs.
-As a consequence, so-called secondary-level validation tools like Schematron have been introduced to overcome the limitations of XSDs.
-Schematron generated validation rules and validates XML documents according to them.
-It cannot be validated if each code of a variable's code list is associated with a category \tb{further explanation needed}.
-It cannot be validated that if an element has a specific value, then certain child elements must be present.
+%\textbf{XML vs. RDF Validation.}
+For data archives, research institutes, and data libraries,
+RDF validation according to predefined constraints is a much sought-after feature, 
+particularly as this is taken for granted in the XML world.
+DDI-XML documents, e.g., are validated against diverse XSDs\footnotemark[\ref{fnt:DDI-XSDs}].
+As certain constraints cannot be formulated and validated by XSDs, 
+so-called secondary-level validation tools like \emph{Schematron}\footnote{\url{https://msdn.microsoft.com/en-us/library/aa468554.aspx}} have been introduced to overcome the limitations of XML validation.
+\emph{Schematron} generates validation rules and validates XML documents according to them.
+With RDF validation, one can overcome drawbacks when validating XML documents\footnote{\url{http://www.xmlmind.com/xmleditor/_distrib/doc/xmltool/xsd_structure_limitations.html}}.
+It cannot be validated, e.g., if each code of a variable's code list is associated with a category (\emph{R-86}).
+Additionally, it cannot be validated that if an element has a specific value, then certain child elements must be present (\emph{R-71}).  
+A comprehensive comparison of XML and RDF validation is not the purpose of this paper.
 
-\tb{Achim, which kind of things cannot be validated using XSDs / we also need references}
-
-\url{http://www.xmlmind.com/xmleditor/_distrib/doc/xmltool/xsd_structure_limitations.html}
-
-\url{https://msdn.microsoft.com/en-us/library/aa468554.aspx}
-
-\textbf{RDF Data Cube Vocabulary.}
-A well-formed RDF Data Cube is an a RDF graph describing one or more instances of \emph{qb:DataSet} for which each of the 22 defined integrity constraints\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf} passes.
+%\textbf{RDF Data Cube Vocabulary.}
+A well-formed \emph{RDF Data Cube} is an a RDF graph describing one or more instances of \emph{qb:DataSet} for which each of the 22 integrity constraints\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf}, defined within the \emph{QB} specification, passes.
 Each integrity constraint is expressed as narrative prose and, where possible, a SPARQL ASK query or query template. 
 If the ASK query is applied to an RDF graph then it will return true if that graph contains one or more \emph{QB} instances which violate the corresponding constraint \cite{CyganiakReynolds2014}.
-
-\textbf{DCAT.}
-\textcolor{blue}{are there already constraints defined for DCAT?}
+Mader, Haslhofer, and Isaac investigated how to support
+taxonomists in improving SKOS vocabularies by pointing out quality
+issues that go beyond the integrity constraints defined in the SKOS specification \cite{MaderHaslhoferIsaac2012}.
 
@@
 
-It is still ongoing work to identify and classify constraints on rectangular data (\emph{PHDD}) and statistical classifications (\emph{XKOS}) and to actually evaluate the quality of real world \emph{PHDD} and \emph{XKOS} data sets.
+It is still ongoing work to identify and classify constraints on rectangular data (\emph{PHDD}) and statistical classifications (\emph{XKOS}) and to actually evaluate the metadata and data quality of real world \emph{XKOS} and \emph{PHDD} data sets.
 

### 2015-04-12 paper/paper7/paper7.tex
conclusion

@@
 particularly as this is taken for granted in the XML world.
-The data most often used in research within the community around research data for the social, behavioural, and economic sciences (\emph{SBE}) is person-level data, i.e.
-data collected about individuals (households, businesses).
+The data most often used in research within the community around research data for the social, behavioural, and economic sciences (\emph{SBE}) is person-level data, i.e., data collected about individuals (households, businesses).
 %The DDI-RDF Discovery Vocabulary is used to describe and to discover this kind of research data.
@@
 
-In this paper, we show how metadata and underlying data on different level of aggregation as well as collections of these data sets are represented in RDF and how therefore used vocabularies are interrelated.
+In this paper, we show how metadata and data on different level of aggregation as well as collections of these data sets are represented in RDF and how therefore used vocabularies are interrelated.
 We explain why RDF validation is important in this context and how (meta)data is validated against RDF constraints to ensure high quality and trust.
@@
 Several approaches exist to meet this requirement, ranging from using \emph{OWL 2} as a constraint language to \emph{SPIN}\footnote{\url{http://spinRDF.org/}}, a SPARQL-based way to formulate and check constraints.
-There are also specific constraint languages like \emph{Shape Expressions}\footnote{\url{http://www.w3.org/Submission/shex-primer/}}, \emph{Resource Shapes}\footnote{\url{http://www.w3.org/Submission/shapes/}} or \emph{Description Set Profiles}\footnote{\url{http://dublincore.org/documents/2008/03/31/dc-dsp/}} that more or less explicitly address the aforementioned SBE community.
+There are also specific constraint languages like \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles} that more or less explicitly address the aforementioned SBE community.
 Bosch and Eckert\cite{BoschEckert2014-2} use SPIN as basis to define a
-validation environment (\url{http://purl.org/net/rdfval-demo}) in which the validation of any constraint language\footnote{the only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL.
-The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.
+validation environment (\url{http://purl.org/net/rdfval-demo}) in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL.
+The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.
 
@@
 
-The data most often used in research within the SBE community is \emph{person-level data}, i.e. data collected about individuals 
-(and sometimes also businesses and households) in the form of responses to studies or taken from administrative registers
+The data most often used in research within the SBE community is \emph{person-level data}, i.e.
+data collected about individuals, businesses, and households in form of responses to studies or taken from administrative registers
 (such as hospital records, registers of births and deaths). 
-The range of person-level data is very broad (covering many different domains), 
+The range of person-level data covers many different domains and is very broad - 
 including census, education, and health data as well as all types of business, social, and labor force surveys.  
@@
 
-By its nature, person-level data is highly confidential, and access is often only permitted for qualified researchers who must apply for access. 
+By its nature, person-level data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 
 The purpose of publicly available aggregated data, on the other hand, is to get a first overview and to gain an interest in further analyses on the underlying person-level data.
@@
 Aggregate data is derived from person-level data by statistics on groups or aggregates such as counts, means, and frequencies.
-The SDMX metadata standard\footnote{http://sdmx.org/} – used as the basis for \emph{QB} – and DDI have traditionally made efforts to align their content. 
+The SDMX metadata standard – used as the basis for \emph{QB} – and DDI have traditionally made efforts to align their content. 
 Similarly, some of the developers of \emph{Disco} were also involved in the development of \emph{QB}, 
@@
 - collected within multiple studies of different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
-are comparable, both content-driven and technology-driven validation is performed either
-within our developed validation environment or by matching algorithms. 
+are comparable, both content-driven and technology-driven validation is performed.
 An example for a content-driven validation is to investigate if variables are represented in a compatible way,
@@
 
-\tb{maybe this paragraph should be moved to one of the subsequent sections and not be part of introduction}
 Data providers and harvesters do not only offer metadata but also publicly available data on different level of detail.
@@
 As data searchers know exactly which data sources they trust and which are reasonable to meet their individual use cases, 
-data validation can only be performed semi-automatically, i.e. an automatic approach serves as basis for intellectual decisions.
+RDF data validation can only be performed semi-automatically, i.e., an automatic approach serves as basis for intellectual decisions.
 
 This paper aims to address two main \textbf{audiences}: 
-(1) metadata practitioners seeking for how to represent metadata on data sets on different aggregation levels and
-(2) metadata providers and harvesters ensuring high quality metadata by validating metadata on highly complex RDF data sets.
-In this paper, we show in form of a complete real world running example how to represent metadata on highly complex person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and aggregated as well as person-level data in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
-We explain why RDF validation is important in this context and how (meta)data is validated against RDF constraints to ensure high quality (meta)data within this complex of data sets on different levels of aggregation (\textbf{contribution 2}, section \ref{rdf-validation}).
-The remainder of the paper is structured as follows.
+(1) metadata practitioners seeking for how to represent metadata and data on different aggregation levels in RDF and
+(2) metadata providers and harvesters ensuring high quality data and metadata by validating RDF data according to certain constraints.
+In this paper, we show in form of a complete real world running example how to represent metadata on person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
+We explained why RDF validation is important in this context and how metadata on person-level data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality (\textbf{contribution 2}, section \ref{rdf-validation}).
+
+%The remainder of the paper is structured as follows.
 
@@
 
-\textbf{Aggregated Data in RDF.}
+\textbf{Aggregated and Person-Level Data in RDF.}
 As Eurostat provides aggregated data as CSV files, we can easily represent the two-dimensional table in RDF by means of \emph{PHDD}.
@@
 Therefore, this technical report contains mappings to DL to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
-We recently published a technical report\footnote{\textcolor{red}{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as first appendix of this paper) in which we describe constraints to validate metadata on person-level, aggregated data, and thesauri.
-We assign each constraint to constraint types corresponding to RDF validation requirements or to data model specific constraint types\footnote{Requirements/Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-1}}
+We recently published a technical report\footnote{\textcolor{red}{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as first appendix of this paper) in which we describe constraints to validate metadata on person-level data, aggregated data, thesauri, and statistical classifications as well as constraints on data on both aggregation levels.
+We assign each constraint to constraint types either corresponding to RDF validation requirements or to data model specific constraint types\footnote{Requirements/Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-1}}
 \cite{BoschZapilkoWackerowEckert2015}.
@@
 \section{Implementation}
+\label{implementation}
 
@@
 a SPARQL-based way to formulate and check constraints, as basis to develop a
-validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages like Shape Expressions,
+validation environment (available at \url{http://purl.org/net/rdfval-demo})\footnote{Source code downloadable at: \textcolor{red}{\url{https://github.com/boschthomas/rdf-validator}}} to validate RDF data according to constraints expressed my arbitrary constraint languages like Shape Expressions,
 %\footnote{\url{http://www.w3.org/Submission/shex-primer/}}
@@
 \section{Evaluation}
+\label{evaluation}
 
@@
 
-It is still ongoing work to identify and classify constraints on rectangular data (\emph{PHDD}) and statistical classifications (\emph{XKOS}) and to actually evaluate the metadata and data quality of real world \emph{XKOS} and \emph{PHDD} data sets.
+In this paper, we showed in form of a complete real world running example how to represent metadata on person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
+We explained why RDF validation is important in this context and how metadata on person-level data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality\footnote{The first appendix of this paper describing each constraint in detail is available at: \textcolor{red}{\url{http://arxiv.org/abs/XXXXX}} \cite{BoschZapilkoWackerowEckert2015}} (\textbf{contribution 2}, section \ref{rdf-validation}).
+We distinguish two validation types:
+(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of data models (section \ref{content-driven-validation}).
+(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges (section \ref{technology-driven-validation}).
+We determined the default \emph{severity level} for each constraint to indicate how serious the violation of the constraint is
+and propose an extensible metric to measure the continuum of severity levels.
+
+We implemented a validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages and to ensure correct syntax, semantics, and integrity of diverse vocabularies such as \emph{Disco, QB, PHDD, SKOS, and XKOS} (section \ref{implementation}).
+We exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets by means of 212 $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
+We validated more than 4.2 billion triples and 15 thousand data sets\footnote{The second appendix of this paper describing the evaluation in detail is available at: \textcolor{red}{\url{http://arxiv.org/abs/XXXXX}} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).
+It is still ongoing work to identify and classify constraints on rectangular data (\emph{PHDD}) and statistical classifications (\emph{XKOS}) and to actually evaluate the (meta)data quality of real world \emph{XKOS} and \emph{PHDD} data sets.
 

### 2015-04-13 paper/paper 2/paper 2.tex
paper 2 - abstract and introduction

@@
 %
-\title{Formulating and Validating RDF Constraints Generically}
+\title{Formulating RDF Constraints and \\ Validating RDF Data Generically}
 %\subtitle{}
@@
 More and more domains adopt Linked Data principles
-and seek now for ways to ensure data quality by validating RDF data according to constraints, as they are used to have this functionality in the XML world.
-For XML, XML Schema is the standard constraint language to validate XML documents.
-For RDF, however, there are multiple candidates for languages to express constraints on RDF data - but there is no standard language for RDF validation.
-We identified requirements to formulate and validate RDF constraints and mapped each requirement to a constraint type.
+and seek for ways to ensure data quality by validating RDF data according to predefined constraints, 
+particularly as many communities are used to have this functionality in the XML world.
+XML Schema is the standard constraint language to formulate constraints on and to validate XML documents.
+For RDF, however, there are more than 10 candidates for languages to express constraints on RDF data - but no standard one meeting the majority of RDF validation use cases.
+We identified requirements to formulate constraints and to validate RDF data and mapped each requirement to a constraint type.
 The majority of these constraint types can be represented in description logics providing their logical underpinning.
 
-In this paper, we provide a basic terminology and classification system for RDF constraint types,
-we developed a vocabulary describing any RDF constraint type generically (whether expressible in description logics or not),
-we show how to transform \emph{specific constraints} (expressed by any constraint language \ms{$\alpha$}) into \emph{generic constraints} and \emph{specific constraints} (expressed by any other constraint language \ms{$\beta$}), and
-we explain how to provide the validation of any \emph{specific constraint} out-of-the-box.
-
-\keywords{RDF Validation, RDF Constraints, RDF Validation Requirements, Transformation, Linked Data, Semantic Web}
+In this paper, we provide a basic terminology and classification system for RDF constraints.
+We developed a vocabulary describing any RDF constraint type generically. 
+%(whether expressible in description logics or not).
+We show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and why these transformations are useful.
+We explain how to overcome the necessity to implement the validation of each constraint type (for multiple constraint languages) by providing mappings to generically expressed constraints
+
+\keywords{RDF Validation, RDF Constraints, RDF Validation Requirements, Linked Data, Semantic Web}
 \end{abstract}
@@
 \section{Introduction}
+\tb{split introdution and motivation}
 \tb{feedback from Erman: the major problem is semantics. OWL basically work in different semantics than others. And their semantics are formal. Closed world vs. Open World is also a part of this.}
@@
 In 2013, the W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
-where experts from industry, government, and academia discussed first use cases for RDF constraint formulation and validation.
+where experts from industry, government, and academia discussed first use cases for RDF constraint formulation and RDF data validation.
 In 2014, two working groups on RDF validation have been established to develop a language to express constraints on RDF data: 
-the W3C RDF Data Shapes WG\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles WG\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}. 
-Bosch and Eckert \cite{BoschEckert2014} collected the findings of these working groups and initiated a database of requirements to formulate and validate RDF constraints
+the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles task group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
+Bosch and Eckert \cite{BoschEckert2014} collected the findings of these working groups and initiated a database of RDF validation requirements
 which is available for contribution at \url{http://purl.org/net/rdf-validation}.
-The intention associated with this database is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
-The requirements are classified to better evaluate existing solutions and each requirement is directly mapped to a constraint type.
-
-\tb{I copied this paragraph from the ESWC paper, we have to modify it}
+The intention is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
+The requirements are classified to better evaluate existing solutions and each requirement is directly mapped to a constraint type which may be expressed by at least one existing constraint language.
+
 Recently, RDF validation as a research field gained speed due to common needs of data practitioners.
@@
 
-There is no constraint language which can be seen as the standard.
-Although, there are multiple constraint languages (having different syntaxes and semantics) which can be used to express RDF constraints (such as existential and universal quantification, cardinality restrictions, and exclusive or of properties).
+\section{Motivation}
+
+There is not one language meeting the majority of requirements to formulate RDF constraints.
+Even though there are more than 10 languages with different syntaxes and semantics which can be used to express RDF constraints (e.g.
+existential and universal quantification, cardinality restrictions, and exclusive or of properties), the language selection depends on the individual use case.
 The five most promising ones on being the standard are
@@
 \end{ex}
-\tb{Erman, can you please delete the slash in front of the dollar sign from the output of the code fragment above (in the stated pattern)?}
+\tb{ToDO: delete the slash in front of the dollar sign from the output of the code fragment above (in the stated pattern)?}
 The first OWL 2 axiom explicitly declares {\em ISBN} to be a datatype.
@@
 As there is no standard way, these constraints may be represented by a variety of possible constraint languages (there are even more than the five promising ones\footnote{i.a.
-Bibframe, Data Quality Test Patterns, Pellet ICV, RDFUnit, SPARQL, Stardog ICV}).
+Bibframe, DQTP, Pellet ICV, RDFUnit, SPARQL, Stardog ICV}).
 There is an obvious need to transform any \emph{specific constraint} (\emph{$sc_{\alpha}$}) (expressed by any constraint language \emph{$\alpha$}) into any other \emph{specific constraint} (\emph{$sc_{\beta}$}) (expressed by any constraint language \emph{$\beta$}) - when they have the same semantics.
@@
 
-\tb{Erman, there is too much space before and after DL and table environments / can your resolve that please?}
+\tb{ToDo: there is too much space before and after DL and table environments / can your resolve that please?}
 

### 2015-04-13 paper/paper 2/paper 2.tex
paper 2 - motivation

@@
 
-There is not one language meeting the majority of requirements to formulate RDF constraints.
-Even though there are more than 10 languages with different syntaxes and semantics which can be used to express RDF constraints (e.g.
-existential and universal quantification, cardinality restrictions, and exclusive or of properties), the language selection depends on the individual use case.
-The five most promising ones on being the standard are
-\emph{Description Set Profiles (DSP)}\footnote{\url{http://dublincore.org/documents/2008/03/31/dc-dsp/}},
-\emph{Resource Shapes (ReSh)}\footnote{\url{http://www.w3.org/Submission/shapes/}}, 
-\emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/shex-primer/}},
-the \emph{SPARQL Inferencing Notation (SPIN)}\footnote{\url{http://spinrdf.org/}}, 
-and the \emph{Web Ontology Language (OWL 2)}\footnote{\url{http://www.w3.org/TR/owl2-syntax/}}.
+There is not one language meeting nearly all or even the majority of requirements to formulate RDF constraints.
+As there are more than 10 languages with different syntaxes and semantics which can be used to express RDF constraints, 
+%(e.g. existential and universal quantification, cardinality restrictions, and exclusive or of properties)
+the language selection heavily depends on the individual use case.
+The five most promising constraint languages on being the standard are
+\emph{Description Set Profiles (DSP)},
+\emph{Resource Shapes (ReSh)}, 
+\emph{Shape Expressions (ShEx)},
+the \emph{SPARQL Inferencing Notation (SPIN)}, 
+and the \emph{Web Ontology Language (OWL 2)}.
 %\section{Ideas}
@@
 %min car more powerful than req. propery
-The idea behind this paper is to express any constraint type (corresponding to a requirement to formulate RDF constraints) in a generic way using a lightweight vocabulary (consisting of only a few terms) (section \ref{sec:vocabulary}).
-
-\emph{Cardinality restrictions}, e.g., can be expressed either generically (\emph{generic constraints}) by \emph{description logics (DL)} 
+The idea behind this paper is to achieve complete RDF validation requirements coverage by representing any constraint type (corresponding to a requirement to formulate RDF constraints) in a generic way using a lightweight vocabulary consisting of only a few terms (see section \ref{sec:vocabulary}).
+
+\emph{Cardinality restrictions}, e.g., can be expressed either generically (\textbf{\emph{generic constraints}}) by \emph{description logics (DL)} 
 %and extensions  
-or specifically (\emph{specific constraints}) by domain-specific constraint languages such as OWL 2, DSP, ShEx, ReSh, and SPIN.
+or specifically (\textbf{\emph{specific constraints}}) by domain-specific constraint languages such as OWL 2, DSP, ShEx, ReSh, and SPIN.
 The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
 For that reason, we map constraint types to DL statements.
-With \emph{minimum qualified cardinality restrictions}, researchers (e.g. from the library domain) can state
+With \emph{minimum qualified cardinality restrictions}, researchers from the library domain may state
 that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
@@
 
-As each \emph{publication} must have at least one \emph{author} relationship to a \emph{person} 
-and as the book \emph{The-Lord-Of-The-Rings} is a \emph{publication} \ms{rdf:type(The-Lord-Of-The-Rings, Publication)}, 
+As each \emph{publication} must have at least one \emph{author} which must be a \emph{person} 
+and as the book \emph{The-Lord-Of-The-Rings} is a \emph{publication} (\ms{rdf:type(The-Lord-Of-The-Rings, Publication)}), 
 \emph{The-Lord-Of-The-Rings} must have at least one \emph{author} relationship to a \emph{person}.
-If \emph{The-Lord-Of-The-Rings} does not have an \emph{author} relationship, a constraint violation is raised. 
-It leads to invalid data, if \emph{The-Lord-Of-The-Rings} has an \emph{author} property pointing to some resource which is assigned to other classes than \emph{person}
-(\ms{author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Human)}).
-It also causes a constraint violation, if \emph{The-Lord-Of-The-Rings} has an \emph{author} relation to an object for which no class is associated
+Constraint violations are raised either if
+\emph{The-Lord-Of-The-Rings} does not have an \emph{author} relationship, or if 
+\emph{The-Lord-Of-The-Rings} has an \emph{author} which is not a \emph{person}
+(\ms{author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Hobbit)}), 
+or if \emph{The-Lord-Of-The-Rings} has an \emph{author} for which no class is assigned
 (\ms{author(The-Lord-Of-The-Rings, Tolkien)}).
-The data is valid, however, if \emph{The-Lord-Of-The-Rings} is connected to a \emph{person} via the object property \emph{author}
+The data is valid, however, if \emph{The-Lord-Of-The-Rings} is connected to a \emph{person} via the property \emph{author}
 (\ms{author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Person)}).
@@
 As there is no standard way to formulate RDF constraints, 
-semantically equivalent \emph{cardinality restrictions} may be represented by different constraint languages, which causes confusion and weakens the understanding how to ensure metadata quality between multiple parties.
+semantically equivalent \emph{cardinality restrictions} may be represented by multiple constraint languages with different syntax and semantics.
+This causes confusion and weakens the common understanding between several parties how to represent particular constraints and therefore how to ensure high data quality. 
 Therefore, when choosing constraint language \ms{$\alpha$} to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a constraint expressed by any other constraint language \ms{$\beta$} (section \ref{sec:transformations}).

### 2015-04-13 paper/paper 2/paper 2.tex
paper 2 - motivation

@@
 We show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and why these transformations are useful.
-We explain how to overcome the necessity to implement the validation of each constraint type (for multiple constraint languages) by providing mappings to generically expressed constraints
+We explain how to overcome the necessity to implement the validation of each constraint type (for multiple constraint languages) by providing mappings to generically expressed constraints.
 
@@
 semantically equivalent \emph{cardinality restrictions} may be represented by multiple constraint languages with different syntax and semantics.
-This causes confusion and weakens the common understanding between several parties how to represent particular constraints and therefore how to ensure high data quality. 
-Therefore, when choosing constraint language \ms{$\alpha$} to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a constraint expressed by any other constraint language \ms{$\beta$} (section \ref{sec:transformations}).
-This is important in order to enhance the interoperability of constraint languages and to simplify the communication of RDF data producers and consumers, 
-as constraint transformations resolve the necessity to read, write, and understand all languages used to express RDF constraints.
-
-We provide a validation environment (available at \url{http://purl.org/net/rdfval-demo}) which enables to validate RDF data according to constraints expressed by multiple  constraint languages such as OWL 2, DSP, ReSh, and ShEx.
-The next step, however, is to validate any constraint type expressed by any constraint language and 
-what is even more important to validate them in exactly the same way, i.e. leading to identical validation results (section \ref{sec:validation}). 
-We are able to offer validation of any \emph{specific constraint} out-of-the-box, (1) if we implement the validation of the corresponding constraint type once and (2) if we transform semantically equivalent \emph{specific constraints} into the corresponding \emph{generic constraint}.
-As a consequence, we do not have to implement the validation for each \emph{specific constraint}.
+This causes confusion and weakens the common understanding between several parties about the semantics of particular constraints and therefore how to ensure high data quality. 
+Thus, when choosing constraint language \ms{$\alpha$} to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a semantically equivalent constraint formulated by any other constraint language \ms{$\beta$} (see section \ref{sec:transformations}).
+This is important in order to enhance the interoperability of constraint languages and to resolve ambiguities in the communication of RDF data producers and consumers, 
+as constraint transformations avoid the necessity to understand several constraint languages.
+
+We provide a validation environment (available at \url{http://purl.org/net/rdfval-demo}) which enables to validate RDF data according to constraints expressed by diverse  constraint languages.
+The next step, however, is to extend the \textbf{\emph{RDF Validator}} by validating any constraint type represented by any constraint language and 
+to validate semantically equivalent \emph{specific constraints}, expressed by different constraint languages, in exactly the same way, 
+i.e., validation is independent from the used constraint language (see section \ref{sec:validation}). 
+%i.e., validation leads to identical validation results - independently from the used constraint language (see section \ref{sec:validation}).
+We are able to offer an already implemented validation mechanism for any \emph{specific constraint} out-of-the-box, 
+(1) if we implement the validation of the corresponding \emph{generic constraint type} once and 
+(2) if we transform semantically equivalent \emph{specific constraints} into generically expressed constraints.
 
@@
 This paper aims to address two main \textbf{audiences}:
-(1) RDF data providers and consumers seeking how to ensure high quality (meta)data and thus for ways to enhance the interoperability and communication of RDF constraints expressed by multiple constraint languages and
-(2) RDF practitioners thinking of how to implement the validation of existing an newly developed constraint languages.
-The \textbf{contributions} of this paper are:
-(1) we provide a basic terminology and classification system for RDF constraint types,
-(2) we developed a vocabulary describing any RDF constraint type generically (whether expressible in DL or not),
-(3) we show how to transform \emph{specific constraints} (expressed by any constraint language \ms{$\alpha$}) into \emph{generic constraints} and \emph{specific constraints} (expressed by any other constraint language \ms{$\beta$}), and
-(4) we explain how to provide the validation of any \emph{specific constraint} immediately. 
+(1) RDF data providers and consumers seeking how to ensure high quality (meta)data and thus for ways to enhance the interoperability and common understanding of RDF constraints expressible by multiple constraint languages and
+(2) RDF practitioners thinking of how to provide aligned implementations for the validation of both existing an newly developed constraint languages.
+The main \textbf{contributions} of this paper are:
+(1) we provide a basic terminology and classification system for RDF constraints (section \ref{sec:vocabulary}),
+(2) we developed a vocabulary describing any RDF constraint type generically (section \ref{sec:vocabulary}),
+(3) we show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and why these transformations are useful (section \label{ref:transformations}), and
+(4) we explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages (section \ref{sec:validation}).
 %(if the validation is implemented once for the corresponding \emph{generic constraint type} to which the \emph{specific constraint type} is mapped)
-The remainder of the paper is as follows.
+
+%The remainder of the paper is as follows.
 

### 2015-04-17 paper/paper7/paper7-appendix.tex
finalized arXiv articles

--- 2015-04-08 paper/paper7/paper7-appendix.tex
@@
 %
-\title{RDF Constraint Types to Validate Metadata \\ on Highly-Complex Person-Level and Aggregated Data}
-\subtitle{}
+\title{RDF Constraints to Validate}
+\subtitle{Rectangular Data and Metadata on Person-Level Data, Aggregated Data, Thesauri, and Statistical Classifications}
 
@@
 \begin{abstract}
-...
-
-\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, Disco, RDF Data Cube Vocabulary, Linked Data, Semantic Web}
+To ensure high quality of and trust in both metadata and data, their representation in RDF must satisfy certain criteria - specified in terms of RDF constraints.
+From 2012 to 2015 together with other Linked Data community members and experts from the social, behavioural, and economic sciences (\emph{SBE}), we developed diverse vocabularies to represent \emph{SBE} metadata and rectangular data in RDF.
+The \emph{DDI-RDF Discovery Vocabulary (Disco)} 
+is designed to support the dissemination, management,
+and reuse of person-level data, i.e., data about individuals, households, and businesses, collected in form of responses to studies and archived for research purposes.
+The \emph{RDF Data Cube Vocabulary (Data Cube)} is a W3C recommendation for expressing \emph{data cubes}, i.e. multi-dimensional aggregate data. 
+\emph{Physical Data Description (PHDD)} is a vocabulary to model data in rectangular format. 
+The data could either be represented in records with character-separated values (\emph{CSV}) or fixed length. 
+The \emph{Simple Knowledge Organization System (SKOS)} is a vocabulary to build knowledge organization systems such as thesauri, classification schemes, and taxonomies.
+\emph{XKOS} is a SKOS extension to describe formal statistical classifications.
+
+In this paper, we describe RDF constraints to validate metadata on person-level data (\emph{Disco}), aggregated data (\emph{Data Cube}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) and to validate rectangular data (\emph{PHDD}).
+We assign RDF constraints to RDF constraint types either corresponding to RDF validation requirements or to data model specific constraint types.
+This technical report is updated continuously as modifying, adding, and deleting constraints remains ongoing work.
+
+\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, RDF Data Cube Vocabulary, Thesauri, SKOS, Rectangular Data, Statistical Classifications, XKOS, Linked Data, Semantic Web}
 \end{abstract}
@@
 (2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges.
-
-\section{Validation of Metadata on Person-Level and Aggregated Data}
-
-\begin{itemize}
-  \item Constraint types marked with an asterisk (*) can be used as OWL 2 axioms.
-Thus, reasoners may be used to infer implicit triples resolving constraint violations caused when these constraints are validated.
-	\item \underline{Underlined subsections} represent data model specific constraint types and do not correspond to RDF validation requirements (constraint types).
-%	\item \underline{Underlined constraints} are part of content-driven validation.
-%	\item \udash{Dashed underlined constraints} are part of technology-driven validation.
-	\item $\mathcal{C}_{T}$ constraint types are marked with the superscript\textsuperscript{T}
-	\item $\mathcal{C}_{C}$ constraint types are not marked
-\end{itemize}
-
-\subsection{\underline{Comparison}}
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-01}}: 
-	are compared variables represented in a compatible way, i.e. are the variables' code lists theoretically comparable?
-		\begin{itemize}
-		\item severity level: WARNING
-	\end{itemize}
-	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-02}}: 
-	are variable definitions (\emph{dcterms:description}) available for each variable (\emph{disco:Variable}) to compare?
-		\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-03}}:
-	are code lists structured properly for each variable (\emph{disco:Variable}) to compare?
-		\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-04}}:
-	is for each code (for each variable (\emph{disco:Variable}) to compare) an associated category (a human-readable label) specified?
-		\begin{itemize}
-		\item severity level: INFO
-	\end{itemize}
-	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-05}}:
-	each (\emph{disco:Variable}) to compare must be present.
-	\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\subsection{\underline{Data Model Consistency}}
-Is the data consistent with the intended semantics of the data model?
-Such validation rules ensure the integrity of the data according to the data model.
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-01}}: 
-	Codes (\emph{skos:Concept}) are ordered and therefore have fixed positions in an ordered collection (\emph{skos:OrderedCollection}) within a variable representation.
-	The cumulative percentage of the current code is the cumulative percentage of the previous code (\emph{disco:cumulativePercentage})
-	plus the percentage value (\emph{disco:percentage}) of the current code. 
-		\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-02}}: 
-	The cumulative percentage (\emph{disco:cumulativePercentage}) of the last code must be 100. 
-		\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-03}}: 
-	The number of valid cases (\emph{disco:SummaryStatistics} of the type (\emph{disco:summaryStatisticType}) \emph{ddicv-sumstats:ValidCases}) 
-	for a particular variable must exactly be the sum of absolute frequencies of all valid cases (\emph{disco:inValid} of \emph{skos:Concept} is true).
-		\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-04}}: 
-	The number of invalid cases (\emph{disco:SummaryStatistics} of the type (\emph{disco:summaryStatisticType}) \emph{ddicv-sumstats:InvalidCases}) 
-	for a particular variable must exactly be the sum of absolute frequencies of all invalid cases (\emph{disco:inValid} of \emph{skos:Concept} is false).
-		\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-05}}: 
-	The total number of valid and invalid cases (\emph{disco:SummaryStatistics} of the type (\emph{disco:summaryStatisticType}) \emph{ddicv-sumstats:NumberOfCases}) 
-	for a particular variable must exactly be the number of valid cases plus the number of invalid cases.
-		\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-06}}: 
-	Some summary statistics types can only be calculated for given variable types. 
-	It is not possible to compute minimum values for string variables.
-		\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-07}}: 
-	Some summary statistics types can only be calculated for given variable types. 
-	It is not possible to compute mean values for categorical variables, only for metric variables.
-		\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-01:}}
-	Only attributes may be optional (\emph{IC-6} \cite{CyganiakReynolds2014}) - 
-	The only components of a \emph{qb:DataStructureDefinition} that may be marked as optional, using \emph{qb:componentRequired} are attributes. 
-	\begin{itemize}
-		\item severity level: WARNING
-	\end{itemize}
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-02:}}
-	Slice Keys consistent with DSD (\emph{IC-8} \cite{CyganiakReynolds2014}) -
-	Every \emph{qb:componentProperty} on a \emph{qb:SliceKey} must also be declared as a \emph{qb:component} of the associated \emph{qb:DataStructureDefinition}. 
-	\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-03:}} 
-	Slice dimensions complete (\emph{IC-10} \cite{CyganiakReynolds2014}) - 
-	Every \emph{qb:Slice} must have a value for every dimension declared in its \emph{qb:sliceStructure}. 
-	\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-		\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-04:}}
-	All dimensions required (\emph{IC-11} \cite{CyganiakReynolds2014}) - 
-	Every \emph{qb:Observation} has a value for each dimension declared in its associated \emph{qb:DataStructureDefinition}. 
-	\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-		\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05:}}
-	No duplicate observations (\emph{IC-12} \cite{CyganiakReynolds2014}) - 
-	No two \emph{qb:Observations} in the same \emph{qb:DataSet} may have the same value for all dimensions. 
-	\begin{itemize}
-		\item severity level: WARNING
-	\end{itemize}
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-06:}}
-	Required attributes (\emph{IC-13} \cite{CyganiakReynolds2014}) -
-	Every \emph{qb:Observation} has a value for each declared attribute that is marked as required. 
-	\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-07:}}
-	All measures present (\emph{IC-14} \cite{CyganiakReynolds2014}) -
-	In a \emph{qb:DataSet} which does not use a Measure dimension then each individual \emph{qb:Observation} must have a value for every declared measure. 
-	\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-08:}}
-	Measure dimension consistent (\emph{IC-15} \cite{CyganiakReynolds2014}) -
-	In a \emph{qb:DataSet} which uses a Measure dimension then each qb:Observation must have a value for the measure corresponding to its given \emph{qb:measureType}. 
-	\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-09:}}
-	Single measure on measure dimension observation (\emph{IC-16} \cite{CyganiakReynolds2014}) -
-	In a \emph{qb:DataSet} which uses a Measure dimension then each \emph{qb:Observation} must only have a value for one measure (by \emph{IC-15} this will be the measure corresponding to its \emph{qb:measureType}).
-	\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-10:}}
-	All measures present in measures dimension cube (\emph{IC-17} \cite{CyganiakReynolds2014}) -
-	In a \emph{qb:DataSet} which uses a Measure dimension then if there is a Observation for some combination of non-measure dimensions then there must be other Observations with the same non-measure dimension values for each of the declared measures.
-	\begin{itemize}
-		\item severity level: ERROR
-	\end{itemize}
-	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-11:}}
-	Consistent data set links (\emph{IC-18} \cite{CyganiakReynolds2014}) -
-	If a \emph{qb:DataSet} \emph{D} has a \emph{qb:slice} \emph{S}, and \emph{S} has an \emph{qb:observation} \emph{O}, then the \emph{qb:dataSet} corresponding to \emph{O} must be \emph{D}. 
-	\begin{itemize}
-		\item severity level: WARNING
-	\end{itemize}
-\end{itemize}
-
-\begin{itemize}
-
-	\item \textbf{{\em SKOS-C-DATA-MODEL-CONSISTENCY-01\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Relation Clashes}:}}
-	Relation Clashes:
-  Covers condition S27 from the SKOS reference document, that has not been defined formally. 
-	\begin{itemize}
-	  \item Implementation:
-		In a first step, all pairs of concepts are found that are associatively connected, using a SPARQL query.
-In the second step, a graph is created, containing only hierarchically related concepts and the respective relations.
-For each concept pair from the first step, we check for a path in the graph from step two.
-If such a path is found, a clash has been identified and the causing concepts are returned.
-		\item Severity level: INFO
-	\end{itemize}
-
-	\item \textbf{{\em SKOS-C-DATA-MODEL-CONSISTENCY-02\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Mapping Clashes}:}}
-	Mapping Clashes:
-  Covers condition S46 from the SKOS reference document, that has not been defined formally. 
-	\begin{itemize}
-	  \item Implementation:
-		Can be solved by issuing a SPARQL query. 
-		\item Severity level: INFO
-	\end{itemize}
-
-	\item \textbf{{\em SKOS-C-DATA-MODEL-CONSISTENCY-03\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Mapping Relations Misuse}:}}
-	Mapping Relations Misuse:
-  According to the SKOS reference documentation, mapping relations (e.g., \emph{skos:broadMatch} or \emph{skos:relatedMatch}) should be asserted to concepts being members of different concept schemes.
-This check finds concepts that are related by a mapping property and are either members of the same concept scheme or members of no concept scheme at all.
-	\begin{itemize}
-		\item Severity level: INFO
-	\end{itemize}
-
-\end{itemize}
+We determined the default \emph{severity level} (corresponds to requirement \emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
+We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ (informational) via $\mathcal{SL}_{1}$ (warning) to $\mathcal{SL}_{2}$ (error). 
+Although we provide default severity levels for each constraint, users should be able to specify severity levels of constraints they need to validate for their individual use cases, i.e., users should be able to define use case specific severity levels for constraints.
+
+The following two sections encompass RDF constraints classified as constraint types either corresponding to RDF validation requirements (section \ref{RDF-validation-requirements-constraint-types}) or data model specific constraint types (section \ref{data-model-specific-constraint-types}).
+Constraint types marked with an asterisk (*) can be used as OWL 2 axioms.
+Thus, reasoners may be used prior to the validation to infer implicit triples which may resolve or cause constraint violations.
+$\mathcal{C}_{T}$ constraint types are marked with the superscript\textsuperscript{T}.
+As $\mathcal{C}_{T}$ and $\mathcal{C}_{C}$ are disjoint sets, $\mathcal{C}_{C}$ constraint types are not explicitly marked.
+
+%\section{RDF Constraints to Validate Metadata and Data}
+
+\section{RDF Constraint Types Corresponding to RDF Validation Requirements}
+\label{RDF-validation-requirements-constraint-types}
 
@@
 	\end{itemize}
+
+	\textcolor{blue}{
+	\item \textbf{{\em DISCO-C-LITERAL-RANGES-02:}}
+{\em disco:cumulativePercentage} (domain: {\em disco:CategoryStatistics}) literals must be of the datatype {\em xsd:double} whose range should be restricted to be between 0 and 100.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	}
+
 \end{itemize}
@@
 	\item \textbf{{\em DISCO-C-MATHEMATICAL-OPERATIONS-02}}:
-	For a given variable, the sum of all category statistics (frequency) has to be equal to the 'total' value of summary statistics.
+	For a given variable, the sum of the frequencies of all codes of the variable's code list has to be equal to the variable's total number of cases (summary statistics of the type 'number of cases').
 	\begin{itemize}
@@
 	\item \textbf{{\em DISCO-C-MATHEMATICAL-OPERATIONS-03}}:
-	For a given variable, the sum of 'valid total' and 'missing total' has to be equal to 'total'.
+	For a given variable, the sum of 'valid cases' and 'invalid cases' has to be equal to the total 'number of cases'.
 	\begin{itemize}
@@
 	\item \textbf{{\em DISCO-C-MATHEMATICAL-OPERATIONS-04}}:
-	For a given variable, the 'total' value for country 'All' must be equal to the sum of the 'total' value for all Countries.
+	For a given variable, the total 'number of cases' value for the country 'All' must be equal to the sum of the total 'number of cases' value for each country.
 	\begin{itemize}
@@
 	\end{itemize}
-	\item \textbf{{\em DISCO-C-AGGREGATION-06}}: the cumulative percentage of all codes of a given variable must be 100.
+	\item \textbf{{\em DISCO-C-AGGREGATION-06}}: the sum of percentages of all codes of a given variable must be 100.
 	\begin{itemize}
@@
 
-\subsection{\underline{Structure}}
+\subsection{Provenance}
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-PROVENANCE-01}}: 
+	Series should have provenance information (\emph{dcterms:provenance}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-PROVENANCE-02}}: 
+	Studies should have provenance information (\emph{dcterms:provenance}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-PROVENANCE-03}}: 
+	Data sets should have provenance information (\emph{dcterms:provenance}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-PROVENANCE-04}}: 
+	Data files should have provenance information (\emph{dcterms:provenance}).
+	\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+\end{itemize}
+
+\section{Data Model Specific RDF Constraint Types}
+\label{data-model-specific-constraint-types}
+
+\subsection{Comparison}
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-01}}: 
+	are compared variables represented in a compatible way, i.e. are the variables' code lists theoretically comparable?
+		\begin{itemize}
+		\item severity level: WARNING
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-02}}: 
+	are variable definitions (\emph{dcterms:description}) available for each variable (\emph{disco:Variable}) to compare?
+		\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-03}}:
+	are code lists structured properly for each variable (\emph{disco:Variable}) to compare?
+		\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-04}}:
+	is for each code (for each variable (\emph{disco:Variable}) to compare) an associated category (a human-readable label) specified?
+		\begin{itemize}
+		\item severity level: INFO
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-COMPARISON-VARIABLES-05}}:
+	each (\emph{disco:Variable}) to compare must be present.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
+\subsection{Data Model Consistency}
+Is the data consistent with the intended semantics of the data model?
+Such validation rules ensure the integrity of the data according to the data model.
+
+\begin{itemize}
+	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-01}}: 
+	Codes (\emph{skos:Concept}) are ordered and therefore have fixed positions in an ordered collection (\emph{skos:OrderedCollection}) within a variable representation.
+	The cumulative percentage of the current code is the cumulative percentage of the previous code (\emph{disco:cumulativePercentage})
+	plus the percentage value (\emph{disco:percentage}) of the current code. 
+		\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-02}}: 
+	The cumulative percentage (\emph{disco:cumulativePercentage}) of the last code must be 100. 
+		\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-03}}: 
+	The number of valid cases (\emph{disco:SummaryStatistics} of the type (\emph{disco:summaryStatisticType}) \emph{ddicv-sumstats:ValidCases}) 
+	for a particular variable must exactly be the sum of all frequencies of all valid cases (\emph{disco:inValid} of \emph{skos:Concept} is true).
+		\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-04}}: 
+	The number of invalid cases (\emph{disco:SummaryStatistics} of the type (\emph{disco:summaryStatisticType}) \emph{ddicv-sumstats:InvalidCases})
+	for a particular variable must exactly be the sum of all frequencies of all invalid cases (\emph{disco:inValid} of \emph{skos:Concept} is false).
+		\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-05}}: 
+	The total number of cases (\emph{rdf:value} of the \emph{disco:SummaryStatistics} resource of the type (\emph{disco:summaryStatisticType}) \emph{ddicv-sumstats:NumberOfCases}) 
+	for a particular variable must exactly be the number of valid cases plus the number of invalid cases.
+		\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-06}}: 
+	Some summary statistics types can only be calculated for given variable types. 
+	It is not possible to compute minimum values for string variables.
+		\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DISCO-C-DATA-MODEL-CONSISTENCY-07}}: 
+	Some summary statistics types can only be calculated for given variable types. 
+	It is not possible to compute mean values for categorical variables, only for metric variables.
+		\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-01:}}
+	Only attributes may be optional (\emph{IC-6} \cite{CyganiakReynolds2014}) - 
+	The only components of a \emph{qb:DataStructureDefinition} that may be marked as optional, using \emph{qb:componentRequired} are attributes. 
+	\begin{itemize}
+		\item severity level: WARNING
+	\end{itemize}
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-02:}}
+	Slice Keys consistent with DSD (\emph{IC-8} \cite{CyganiakReynolds2014}) -
+	Every \emph{qb:componentProperty} on a \emph{qb:SliceKey} must also be declared as a \emph{qb:component} of the associated \emph{qb:DataStructureDefinition}. 
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-03:}} 
+	Slice dimensions complete (\emph{IC-10} \cite{CyganiakReynolds2014}) - 
+	Every \emph{qb:Slice} must have a value for every dimension declared in its \emph{qb:sliceStructure}. 
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+		\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-04:}}
+	All dimensions required (\emph{IC-11} \cite{CyganiakReynolds2014}) - 
+	Every \emph{qb:Observation} has a value for each dimension declared in its associated \emph{qb:DataStructureDefinition}. 
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+		\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05:}}
+	No duplicate observations (\emph{IC-12} \cite{CyganiakReynolds2014}) - 
+	No two \emph{qb:Observations} in the same \emph{qb:DataSet} may have the same value for all dimensions. 
+	\begin{itemize}
+		\item severity level: WARNING
+	\end{itemize}
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-06:}}
+	Required attributes (\emph{IC-13} \cite{CyganiakReynolds2014}) -
+	Every \emph{qb:Observation} has a value for each declared attribute that is marked as required. 
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-07:}}
+	All measures present (\emph{IC-14} \cite{CyganiakReynolds2014}) -
+	In a \emph{qb:DataSet} which does not use a Measure dimension then each individual \emph{qb:Observation} must have a value for every declared measure. 
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-08:}}
+	Measure dimension consistent (\emph{IC-15} \cite{CyganiakReynolds2014}) -
+	In a \emph{qb:DataSet} which uses a Measure dimension then each qb:Observation must have a value for the measure corresponding to its given \emph{qb:measureType}. 
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-09:}}
+	Single measure on measure dimension observation (\emph{IC-16} \cite{CyganiakReynolds2014}) -
+	In a \emph{qb:DataSet} which uses a Measure dimension then each \emph{qb:Observation} must only have a value for one measure (by \emph{IC-15} this will be the measure corresponding to its \emph{qb:measureType}).
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-10:}}
+	All measures present in measures dimension cube (\emph{IC-17} \cite{CyganiakReynolds2014}) -
+	In a \emph{qb:DataSet} which uses a Measure dimension then if there is a Observation for some combination of non-measure dimensions then there must be other Observations with the same non-measure dimension values for each of the declared measures.
+	\begin{itemize}
+		\item severity level: ERROR
+	\end{itemize}
+	\item \textbf{{\em DATA-CUBE-C-DATA-MODEL-CONSISTENCY-11:}}
+	Consistent data set links (\emph{IC-18} \cite{CyganiakReynolds2014}) -
+	If a \emph{qb:DataSet} \emph{D} has a \emph{qb:slice} \emph{S}, and \emph{S} has an \emph{qb:observation} \emph{O}, then the \emph{qb:dataSet} corresponding to \emph{O} must be \emph{D}. 
+	\begin{itemize}
+		\item severity level: WARNING
+	\end{itemize}
+\end{itemize}
+
+\begin{itemize}
+
+	\item \textbf{{\em SKOS-C-DATA-MODEL-CONSISTENCY-01\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Relation Clashes}:}}
+	Relation Clashes:
+  Covers condition S27 from the SKOS reference document, that has not been defined formally. 
+	\begin{itemize}
+	  \item Implementation:
+		In a first step, all pairs of concepts are found that are associatively connected, using a SPARQL query.
+In the second step, a graph is created, containing only hierarchically related concepts and the respective relations.
+For each concept pair from the first step, we check for a path in the graph from step two.
+If such a path is found, a clash has been identified and the causing concepts are returned.
+		\item Severity level: INFO
+	\end{itemize}
+
+	\item \textbf{{\em SKOS-C-DATA-MODEL-CONSISTENCY-02\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Mapping Clashes}:}}
+	Mapping Clashes:
+  Covers condition S46 from the SKOS reference document, that has not been defined formally. 
+	\begin{itemize}
+	  \item Implementation:
+		Can be solved by issuing a SPARQL query. 
+		\item Severity level: INFO
+	\end{itemize}
+
+	\item \textbf{{\em SKOS-C-DATA-MODEL-CONSISTENCY-03\footnote{Corresponds to qSKOS Quality Issues - SKOS Semi-Formal Consistency Issues - Mapping Relations Misuse}:}}
+	Mapping Relations Misuse:
+  According to the SKOS reference documentation, mapping relations (e.g., \emph{skos:broadMatch} or \emph{skos:relatedMatch}) should be asserted to concepts being members of different concept schemes.
+This check finds concepts that are related by a mapping property and are either members of the same concept scheme or members of no concept scheme at all.
+	\begin{itemize}
+		\item Severity level: INFO
+	\end{itemize}
+
+\end{itemize}
+
+\subsection{Structure}
 
@@
 
-\subsection{\underline{Labeling and Documentation}}
+\subsection{Labeling and Documentation}
 
@@
 
-\subsection{\underline{Vocabulary}\textsuperscript{T}}
+\subsection{Vocabulary\textsuperscript{T}}
 Vocabularies should not invent any new terms or use deprecated elements.
@@
 
-\subsection{\underline{Linked Data}}
+\subsection{Linked Data}
 
@@
 		\item Severity level: ERROR
-	\end{itemize}
-\end{itemize}
-
-\subsection{Provenance}
-
-\begin{itemize}
-	\item \textbf{{\em DISCO-C-PROVENANCE-01}}: 
-	Series should have provenance information (\emph{dcterms:provenance}).
-	\begin{itemize}
-		\item severity level: INFO
-	\end{itemize}
-	\item \textbf{{\em DISCO-C-PROVENANCE-02}}: 
-	Studies should have provenance information (\emph{dcterms:provenance}).
-	\begin{itemize}
-		\item severity level: INFO
-	\end{itemize}
-	\item \textbf{{\em DISCO-C-PROVENANCE-03}}: 
-	Data sets should have provenance information (\emph{dcterms:provenance}).
-	\begin{itemize}
-		\item severity level: INFO
-	\end{itemize}
-	\item \textbf{{\em DISCO-C-PROVENANCE-04}}: 
-	Data files should have provenance information (\emph{dcterms:provenance}).
-	\begin{itemize}
-		\item severity level: INFO
 	\end{itemize}

### 2015-04-17 paper/paper7/paper7-evaluation.tex
finalized arXiv articles

@@
 \begin{abstract}
-From 2012 to 2015 together with other Linked Data community members and experts from the social, behavioural, and economic sciences (\emph{SBE}), we developed diverse vocabularies to represent \emph{SBE} metadata and data in RDF.
+From 2012 to 2015 together with other Linked Data community members and experts from the social, behavioural, and economic sciences (\emph{SBE}), we developed diverse vocabularies to represent \emph{SBE} metadata and rectangular data in RDF.
 The \emph{DDI-RDF Discovery Vocabulary (Disco)} 
-is designed for the purposes of supporting the dissemination, management,
-and reuse of person-level data (data about individuals) collected in form of responses to studies and archived for research purposes.
-The \emph{RDF Data Cube Vocabulary (Data Cube, QB)} is a W3C recommendation for representing \emph{data cubes}, i.e. multi-dimensional aggregate data, in RDF. 
-\emph{Physical Data Description (PHDD)} is a vocabulary to represent aggregated and person-level data in a rectangular format. 
-The data could be either represented in records with character-separated values (\emph{CSV}) or in records with fixed length. 
-The \emph{Simple Knowledge Organization System (SKOS)} is a vocabulary to represent knowledge organization systems such as thesauri, classification schemes, subject heading lists, and taxonomies in RDF.
-\emph{XKOS} is a SKOS extension to describe formal statistical classifications like the \emph{International Standard Classification of Occupations} (\emph{ISCO}).
-
-To ensure high quality and trust, RDF data as well as its metadata must satisfy certain criteria - specified in terms of RDF constraints.
-In this paper, we evaluated the metadata and data quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), thesauri (\emph{SKOS}), rectangular (\emph{PHDD}), and statistical classification (\emph{XKOS}) data sets by means of RDF constraints assigned to multiple constraint types.
+is designed to support the dissemination, management,
+and reuse of person-level data, i.e., data about individuals, households, and businesses, collected in form of responses to studies and archived for research purposes.
+The \emph{RDF Data Cube Vocabulary (Data Cube)} is a W3C recommendation for expressing \emph{data cubes}, i.e. multi-dimensional aggregate data. 
+\emph{Physical Data Description (PHDD)} is a vocabulary to model data in rectangular format. 
+The data could either be represented in records with character-separated values (\emph{CSV}) or fixed length. 
+The \emph{Simple Knowledge Organization System (SKOS)} is a vocabulary to build knowledge organization systems such as thesauri, classification schemes, and taxonomies.
+\emph{XKOS} is a SKOS extension to describe formal statistical classifications.
+
+To ensure high quality of and trust in both metadata and data, their representation in RDF must satisfy certain criteria - specified in terms of RDF constraints.
+In this paper, we evaluated the metadata and data quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), thesauri (\emph{SKOS}), rectangular (\emph{PHDD}), and statistical classification (\emph{XKOS}) data sets by means of RDF constraints.
+RDF Constraints are instances of RDF constraint types either corresponding to RDF validation requirements or to data model specific constraint types.
 We validated more than 4.2 billion triples and 15 thousand data sets
-using the \emph{RDF Validator} which is available at \url{http://purl.org/net/rdfval-demo}.
-
-\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, Disco, RDF Data Cube Vocabulary, QB, Thesauri, SKOS, Rectangular Data, PHDD, Statistical Classifications, Extended SKOS, XKOS, Linked Data, Semantic Web}
+using the \emph{RDF Validator}, a validation environment which is available at \url{http://purl.org/net/rdfval-demo}.
+
+\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, RDF Data Cube Vocabulary, Thesauri, SKOS, Rectangular Data, Statistical Classifications, XKOS, Linked Data, Semantic Web}
 \end{abstract}
@@
 		\hline
-		\emph{CT} & 52 (15\textbar 37)\tablefootnote{(\label{fnt:1}implemented \textbar not yet implemented)} & 20 (7\textbar 13)\footnotemark[\ref{fnt:1}] & 14 (4\textbar 10)\footnotemark[\ref{fnt:1}] & 53 \\
+		\emph{CT} & 52 (15\textbar 37)\tablefootnote{(\label{fnt:1}implemented \textbar not yet implemented)} & 20 (7\textbar 13) & 14 (4\textbar 10) & 53 \\
 		\emph{CT} ($\mathcal{C}_{C}$) & 30 (57.7\%) & 5 (25\%) & 5 (35.7\%) & 30 (56.6\%) \\
@@
 \section{Evaluation of Person-Level Metadata (\emph{Disco})}
+
+In this section, the quality of the metadata on person-level (\emph{Disco}) data sets is evaluated by validating appropriate RDF constraints assigned to several RDF constraint types.
+First, we show the results of the evaluation of diverse data sets, then we give an overview over the evaluated data sets, and finally we provide details about the evaluation.
 
@@
 
+In this sub section, we give details about the evaluation in form of diverse tables containing the number of constraint violations per evaluated data set and constraint of particular constraint types.
+
 \begin{table}[H]
@@
 \section{Evaluation of Aggregated Metadata (\emph{Data Cube})}
+
+In this section, the quality of the metadata on aggregated data (\emph{Data Cube}) data sets is evaluated by validating appropriate RDF constraints assigned to several RDF constraint types.
+First, we show the results of the evaluation of diverse data sets, then we give an overview over the evaluated data sets, and finally we provide details about the evaluation.
 
@@
 
+In this section, the quality of the metadata on thesauri (\emph{SKOS}) is evaluated by validating appropriate RDF constraints assigned to several RDF constraint types.
+First, we show the results of the evaluation of diverse thesauri, then we give an overview over the evaluated thesauri, and finally we provide details about the evaluation.
+
 \subsection{Evaluation Results}
@@
 
+In this section, the quality of rectangular (\emph{PHDD}) data sets is evaluated by validating appropriate RDF constraints assigned to several RDF constraint types.
+First, we show the results of the evaluation of diverse data sets, then we give an overview over the evaluated data sets, and finally we provide details about the evaluation.
+
 \subsection{Evaluation Results}
@@
 
+In this sub section, we give details about the evaluation in form of diverse tables containing the number of constraint violations per evaluated data set and constraint of particular constraint types.
+
 \section{Evaluation of Statistical Classifications (\emph{XKOS})}
+
+In this section, the quality of the metadata on statistical classifications (\emph{XKOS}) data sets is evaluated by validating appropriate RDF constraints assigned to several RDF constraint types.
+First, we show the results of the evaluation of diverse data sets, then we give an overview over the evaluated data sets, and finally we provide details about the evaluation.
 
@@
 
+In this sub section, we give details about the evaluation in form of diverse tables containing the number of constraint violations per evaluated data set and constraint of particular constraint types.
+
+\section{Related Work}
+
+The data most often used in research within the SBE community is \emph{person-level data}, i.e.
+data collected about individuals, businesses, and households in form of responses to studies or taken from administrative registers
+(such as hospital records, registers of births and deaths). 
+The range of person-level data covers many different domains and is very broad - 
+including census, education, and health data as well as all types of business, social, and labor force surveys.  
+Increasingly, this type of research data is
+held within data archives or data libraries after it has been collected, so that it may be
+reused by future researchers. 
+In performing their research, the detailed person-level
+data is aggregated into less confidential multi-dimensional tables which answer particular research questions.
+Portals harvest metadata (as well as publicly available data) from multiple data providers in form of RDF.
+To ensure high quality, the metadata must satisfy certain criteria - specified in terms of RDF constraints.  
+After validating the metadata according to these constraints, portals offer added values to their customers, e.g. by searching over and comparing metadata of multiple providers.
+
+By its nature, person-level data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 
+The purpose of publicly available aggregated data, on the other hand, is to get a first overview and to gain an interest in further analyses on the underlying person-level data.
+Researchers typically represent their results as aggregated data in form of two-dimensional tables with only a few columns (so-called \emph{variables} such as \emph{sex} or \emph{age}).
+The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e.
+multi-dimensional aggregate data, in RDF \cite{Cyganiak2010}.
+Aggregate data is derived from person-level data by statistics on groups or aggregates such as counts, means, and frequencies.
+The SDMX metadata standard – used as the basis for \emph{QB} – and DDI have traditionally made efforts to align their content. 
+Similarly, some of the developers of \emph{Disco} were also involved in the development of \emph{QB}, 
+allowing the RDF versions of these standards to retain that alignment.
+While \emph{Disco} and \emph{QB} provide terms for the description of data sets, 
+both on a different level of aggregation, 
+the \emph{Data Catalog Vocabulary (DCAT)}\footnote{\url{http://www.w3.org/TR/vocab-dcat/}} enables the representation of these data sets inside of data collections like repositories, catalogs, or archives.
+The relationship between data collections and their contained data sets is useful, since such collections are a typical entry point when searching for data.
+Although, in most cases aggregated data is still published in form of PDFs, 
+it is more and more common to publish aggregated data as CSV files,
+allowing to perform first calculations (either using all variables or only a subset).
+%For these calculations, definitions of the columns are needed (e.g. is a given variable interpreted numerically or as a string).
+In 2014, SBE and Linked Data community members developed the \emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} vocabulary to represent aggregated and person-level data in a rectangular format.
+The data could be either represented in records with character-separated values (CSV) or in records with fixed length.
+
+For more detailed analyses, researchers refer to person-level data from which aggregated data is derived from, 
+as person-level data include additional variables needed for further research.
+%Although not that common, the other direction is also possible, 
+%i.e. researchers may use metadata on person-level data to search for aggregated data.
+One very common example for detailed analyses on person-level data is the content-driven comparison of multiple studies.
+Researchers get promising findings (in form of published tables with a few columns) within a metadata portal leading to subsequent research questions 
+like 'How to compare the unemployment rate of different countries (e.g. Germany, UK, and France) in the last 10 years grouped by age?'.
+The first step is to determine in which countries the unemployment rate is collected and which other variables of each country-specific study are theoretically comparable and can therefore be used to answer the underlying research question.
+A \emph{study} represents the process by which a data set was generated or collected.
+Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
+The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger}, or by a code list including multiple age clusters (such as '0 to 10' and '11 to 20'). 
+To determine if variables measuring \emph{age} 
+- collected within multiple studies of different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
+are comparable, both content-driven and technology-driven validation is performed.
+An example for a content-driven validation is to investigate if variables are represented in a compatible way,
+i.e. are the variables' code lists theoretically comparable.
+Technically, it can be validated (1) if variable definitions are available, (2) if code lists are properly structured, and (3) if for each code an associated category (a human-readable label) is specified.
+
+Data providers and harvesters do not only offer metadata but also publicly available data on different level of detail.
+To ensure high data quality and trust, they have to analyze and validate the data (are fundamental data fragments available?, how does valid data look like?). 
+%They validate, e.g., if fundamental data parts are available and define how valid data should look like (using syntactic rules).
+Provenance (where does the data come from?) is an important aspect in evaluating data quality.
+As data searchers know exactly which data sources they trust and which are reasonable to meet their individual use cases, 
+RDF data validation can only be performed semi-automatically, i.e., an automatic approach serves as basis for intellectual decisions.
+
+\section{Conclusion and Future Work}
+
+We implemented a validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages and to ensure correct syntax, semantics, and integrity of diverse vocabularies such as \emph{Disco, QB, PHDD, SKOS, and XKOS}.
+We exhaustively evaluated the metadata quality of large real world aggregated data sets (\emph{QB}), person-level data sets (\emph{Disco}), thesauri (\emph{SKOS}), statistical classifications (\emph{XKOS}), and rectangular data sets (\emph{PHDD}) by means of 212 $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
+In total, we validated more than 4.2 billion triples and 15 thousand data sets.
+
 \bibliography{../../literature/literature}{}

### 2015-04-17 paper/paper7/paper7.tex
finalized arXiv articles

@@
 The \emph{RDF Validator} also validates RDF data to ensure correct syntax, semantics, and integrity of diverse vocabularies such as \emph{Disco, QB, PHDD, SKOS, and XKOS}.
-Although accessible within our validation tool, we provide all implemented constraints\footnote{\textcolor{red}{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}}} in form of SPARQL CONSTRUCT queries.
+Although accessible within our validation tool, we provide all implemented constraints\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} in form of SPARQL CONSTRUCT queries.
 For the subsequent evaluation, we implemented 212 constraints on \emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{XKOS}, and \emph{PHDD} data sets.

### 2015-04-17 paper/paper7/paper7.tex
classification

@@
 
-\section{RDF Validation of Metadata and Data}
+\section{Classification of RDF Constraint Types and RDF Constraints to Validate Metadata and Data}
 \label{rdf-validation}
 
-Bosch et al. identified in total 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
-We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement (constraint type) in detail and give examples for each (represented by different constraint languages).
+Bosch et al.
+identified 74 requirements to formulate RDF constraints; each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}\cite{BoschNolleAcarEckert2015}.
+We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement (constraint type) in detail and give examples for each expressed by different constraint languages.
 The knowledge representation formalism \emph{Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
 Therefore, this technical report contains mappings to DL to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
-We recently published a technical report\footnote{\textcolor{red}{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as first appendix of this paper) in which we describe constraints to validate metadata on person-level data, aggregated data, thesauri, and statistical classifications as well as constraints on data on both aggregation levels.
-We assign each constraint to constraint types either corresponding to RDF validation requirements or to data model specific constraint types\footnote{Requirements/Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-1}}
-\cite{BoschZapilkoWackerowEckert2015}.
+For this paper, we developed a system to classify RDF constraint types and RDF constraints\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper}.
+Constraints are instantiated from constraint types, which are organized as disjoint sets, in order to validate both metadata and data represented by any vocabulary.
+We recently published another technical report\footnote{\textcolor{red}{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as first appendix of this paper) in which we describe and classify constraints to validate rectangular data and metadata on person-level data sets, aggregated data sets, thesauri, and statistical classifications.
 
-We distinguish two validation types:
-(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of given data models (section \ref{content-driven-validation}).
-(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges (section \ref{technology-driven-validation}).
-We determined the default \emph{severity level} (corresponds to requirement \emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
-We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ (informational) via $\mathcal{SL}_{1}$ (warning) to $\mathcal{SL}_{2}$ (error).
+Constraints are classified as constraint types either corresponding to
+\begin{enumerate}
+	\item \emph{RDF validation requirements} (e.g. \emph{R-75, R-81: minimum qualified cardinality restrictions}) or to
+	\item \emph{data model specific constraint types} (e.g. \emph{data model consistency})\cite{BoschZapilkoWackerowEckert2015}.
+\end{enumerate}
+
+The complete set of \emph{constraint types} ($\mathcal{CT}$) encompasses two disjoint \textbf{\emph{sets of constraint types}}:
+\begin{enumerate}
+	\item $\mathcal{CT}_{C}$: \emph{Content-Driven Constraint Types}
+	\item $\mathcal{CT}_{T}$: \emph{Technology-Driven Constraint Types}
+\end{enumerate}
+
+$\mathcal{CT}_{C}$ (\emph{Content-Driven Constraint Types}) is the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of vocabularies' data models (section \ref{content-driven-validation}).
+Therefore, domain experts may formulate $\mathcal{CT}_{C}$ constraints manually in prose English which is technically expressed by a constraint language afterwards.  
+$\mathcal{CT}_{T}$ (\emph{Technology-Driven Constraint Types}) is the set of constraints which can be generated completely automatically out of vocabularies' data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges (section \ref{technology-driven-validation}).
+
+We determined the default \textbf{\emph{severity level}} (corresponds to requirement \emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
+We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ to $\mathcal{SL}_{2}$.
+According to the constraints' default severity level the complete set of constraints ($\mathcal{C}$) encompasses three disjoint \textbf{\emph{sets of constraints}}:
+\begin{enumerate}
+	\item $\mathcal{SL}_{0}$: set of constraints with severity level \emph{informational}
+	\item $\mathcal{SL}_{1}$: set of constraints with severity level \emph{warning}
+	\item $\mathcal{SL}_{2}$: set of constraints with severity level \emph{error}
+\end{enumerate}
 The violation of $\mathcal{SL}_{0}$ constraints does not mean that there are serious mistakes in either syntax or semantics.
@@
 
-\subsection{Content-Driven Validation}
+\subsection{Content-Driven Constraint Types}
 \label{content-driven-validation}
+
+\textcolor{red}{short description}
 
@@
 
-\subsection{Technology-Driven Validation}
+\subsection{Technology-Driven Constraint Types}
 \label{technology-driven-validation}

### 2015-04-17 paper/paper7/paper7.tex
feedback

@@
 
+%This paper aims to address two main \textbf{audiences}: 
+%(1) metadata practitioners seeking for how to represent metadata and data on different aggregation levels in RDF and
+%(2) metadata providers and harvesters ensuring high quality data and metadata by validating RDF data according to certain constraints.
+In this paper, we show in form of a complete real world running example how to represent metadata on person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
+We explained why RDF validation is important in this context and how metadata on person-level data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality (\textbf{contribution 2}, section \ref{rdf-validation}).
+%The remainder of the paper is structured as follows.
+\tb{nur eine contribution}
 \section{Motivation}
@@
 
-This paper aims to address two main \textbf{audiences}: 
-(1) metadata practitioners seeking for how to represent metadata and data on different aggregation levels in RDF and
-(2) metadata providers and harvesters ensuring high quality data and metadata by validating RDF data according to certain constraints.
-In this paper, we show in form of a complete real world running example how to represent metadata on person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
-We explained why RDF validation is important in this context and how metadata on person-level data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality (\textbf{contribution 2}, section \ref{rdf-validation}).
-
-%The remainder of the paper is structured as follows.
-
 %\section{Running Example}
@@
 
+\textcolor{red}{figure / metadata: person-level, aggregated, thesauri, catalogs, statistical classifications / data: rectangular data}
+
 Eurostat\footnote{\url{http://ec.europa.eu/eurostat}} is the statistical office of the European Union.
@@
 SBE researchers have a strong interest, e.g., in the availability of childcare services across European Union Member States.
+\tb{folgendes beispiel bezieht sich auf diesen datensatz}
 
@@
 The present data collection refers to data on formal childcare and other types of care by the variables \emph{year}, \emph{duration} (0 hours, 1 - 29 HPW; 30 HPW), \emph{age} of the child (0-2 years; 3 to admission age for compulsory school; admission age for compulsory school to 12) and \emph{country}.
-
-\tb{ToDO for Ben: can you please insert how example is represented in Data Cube in this paragraph}
-
 \emph{QB} is a vocabulary to represent metadata on multi-dimensional aggregate data.
-
-data set
-
-data structure definition
-
-dimensions
-
-measure
-
-observations
+Such data is represented using \emph{QB} in two files, a \emph{qb:DataSet} and a \emph{qb:DataStructureDefinition}.
+The \emph{qb:DataStructureDefinition} contains metadata of the present data collection.
+Thereby, the variable \emph{formal childcare} is modelled as \emph{qb:measure}, since it expresses what has been measured in the data collection.
+The \emph{year}, \emph{duration}, \emph{age}, etc. are defined as \emph{qb:dimension}.
+The particular data values, i.e.
+the specific availability of childcare services in percent over the population in particular years, are collected in a \emph{qb:DataSet}.
+Each data value is represented inside a \emph{qb:Observation} which additionally contains the particular dimensional values associated with that data value, e.g.
+the concrete year in which the formal childcare has been determined.
 
@@
 
-\textbf{Aggregated and Person-Level Data in RDF.}
+\tb{aut SDMX sind year, duration, age, etc. keine Variablen, sondern Dimensionen}
+
+\textbf{Rectangular Data in RDF.}
 As Eurostat provides aggregated data as CSV files, we can easily represent the two-dimensional table in RDF by means of \emph{PHDD}.
@@
 Therefore, this technical report contains mappings to DL to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
+
 For this paper, we developed a system to classify RDF constraint types and RDF constraints\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper}.
-Constraints are instantiated from constraint types, which are organized as disjoint sets, in order to validate both metadata and data represented by any vocabulary.
-We recently published another technical report\footnote{\textcolor{red}{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as first appendix of this paper) in which we describe and classify constraints to validate rectangular data and metadata on person-level data sets, aggregated data sets, thesauri, and statistical classifications.
+Constraints are instantiated from constraint types, which are organized as disjoint sets, in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent.
+Constraint types either corresponding to
 
-Constraints are classified as constraint types either corresponding to
 \begin{enumerate}
@@
 Furthermore, we associate constraints with default severity levels and assign them to validation types.
+
+We recently published a technical report\footnote{\textcolor{red}{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as first appendix of this paper) in which we describe and classify constraints to validate rectangular data and metadata on person-level data sets, aggregated data sets, thesauri, and statistical classifications and therefore apply the proposed classification system.
 
@@
 
-We exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets by means of both $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
+\subsection{Evaluation Setup}
+
+First, several SBE domain experts of the vocabularies \emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{XKOS}, and \emph{PHDD} evaluated the correctness (i.e., the gold standard) of all $\mathcal{CT}_{C}$ and $\mathcal{CT}_{T}$ constraints and therefore the generic applicability of the developed classification system of constraint types and constraints.
+%i.e., the gold standard, has been proved by multiple SBE domain experts.
+Second, we exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets by means of both $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
 We validated 
@@
 As we evaluated nearly 10 thousand \emph{QB} data sets, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.
-The correctness of all constraints, i.e., the gold standard, has been proved by SBE domain experts.
 Table \ref{tab:evaluation} shows the evaluation results.
+
+\subsection{Evaluation Results and Discussion}
 
@@
 %    \\  \cmidrule{2-7}
-    \\       \textbf{Criteria\tablefootnote{\emph{C (constraints), CT (constraint types), CV (constraint violations)}}}
+    \\       \textbf{Criteria}
            & \textbf{\emph{Disco}}
@@
     \emph{CV} & 3,545,703 & 45,635,846 & 5,540,988 & 54,722,537\\
-		\emph{CV ($\mathcal{SL}_{0}$)} & 2,437,922 (68.8\%) & 0 (0\%) & 2,281,740 (41.2\%) & 4,719,662 (8.6\%) \\
-		\emph{CV ($\mathcal{SL}_{1}$)} & 473,574 (13.4\%) & 45,520,613 (99.75\%) & 3,259,248 (58.8\%) & 49,253,435 (90\%) \\
+		\emph{CV ($\mathcal{SL}_{0}$)} & 2,437,922 (\textbf{68.8\%}) & 0 (0\%) & 2,281,740 (41.2\%) & 4,719,662 (8.6\%) \\
+		\emph{CV ($\mathcal{SL}_{1}$)} & 473,574 (13.4\%) & 45,520,613 (\textbf{99.75\%}) & 3,259,248 (\textbf{58.8\%}) & 49,253,435 (\textbf{90\%}) \\
     \emph{CV ($\mathcal{SL}_{2}$)} & 634,207 (17.9\%) & 115,233 (0.25\%) & 0 (0\%) & 749,440 (1.4\%) \\
 		\hline
-		\emph{CT} & 52 (15\textbar 37)\tablefootnote{(\label{fnt:1}implemented \textbar not yet implemented)} & 20 (7\textbar 13)\footnotemark[\ref{fnt:1}] & 14 (4\textbar 10)\footnotemark[\ref{fnt:1}] & 53 \\
-		\emph{CT} ($\mathcal{C}_{C}$) & 30 (57.7\%) & 5 (25\%) & 5 (35.7\%) & 30 (56.6\%) \\
-		\emph{CT} ($\mathcal{C}_{T}$) & 22 (42.3\%) & 15 (75\%) & 9 (64.3\%) & 23 (43.4\%) \\
+		\emph{CT} & 52 & 20 & 14 & 53 \\
+		\emph{CT} ($\mathcal{C}_{C}$) & 30 (\textbf{57.7\%}) & 5 (25\%) & 5 (35.7\%) & 30 (\textbf{56.6\%}) \\
+		\emph{CT} ($\mathcal{C}_{T}$) & 22 (42.3\%) & 15 (\textbf{75\%}) & 9 (\textbf{64.3\%}) & 23 (43.4\%) \\
 		\hline
-		\emph{C} & 142 (77\textbar 65)\footnotemark[\ref{fnt:1}] & 35 (20\textbar 15)\footnotemark[\ref{fnt:1}] & 35 (17\textbar 18)\footnotemark[\ref{fnt:1}] & 212 \\
-		\emph{C} ($\mathcal{C}_{C}$) & 72 (50.7\%) & 16 (45.7\%) & 21 (60\%) & 109 (51.4\%) \\
-		\emph{C} ($\mathcal{C}_{T}$) & 70 (49.3\%) & 19 (54.3\%) & 14 (40\%) & 103 (48.6\%) \\
-		\emph{C ($\mathcal{SL}_{0}$)} & 75 (52.8\%)& 4 (11.4\%) & 21 (60\%) & 100 (47.2\%) \\
+		\emph{C} & 142 & 35 & 35 & 212 \\
+		\hline
+		\emph{C} ($\mathcal{C}_{C}$) & 72 (\textbf{50.7\%}) & 16 (45.7\%) & 21 (\textbf{60\%}) & 109 (\textbf{51.4\%}) \\
+		\emph{C} ($\mathcal{C}_{T}$) & 70 (\textbf{49.3\%}) & 19 (\textbf{54.3\%}) & 14 (40\%) & 103 (\textbf{48.6\%}) \\
+		\hline
+		\emph{C ($\mathcal{SL}_{0}$)} & 75 (\textbf{52.8\%})& 4 (11.4\%) & 21 (\textbf{60\%}) & 100 (\textbf{47.2\%}) \\
 		\emph{C ($\mathcal{SL}_{1}$)} & 9 (6.3\%)& 3 (8.6\%) & 5 (14.3\%) & 17 (8\%) \\
-		\emph{C ($\mathcal{SL}_{2}$)} & 58 (40.8\%) & 28 (80\%) & 9 (25.7\%) & 95 (44.8\%) \\
+		\emph{C ($\mathcal{SL}_{2}$)} & 58 (40.8\%) & 28 (\textbf{80\%}) & 9 (25.7\%) & 95 (\textbf{44.8\%}) \\
     \bottomrule
     \end{tabular}
+    \\ \emph{C (constraints), CT (constraint types), CV (constraint violations)}
     \caption{Evaluation}
@@
 These findings are surprising as only 8\% of all defined constraints are $\mathcal{SL}_{1}$ constraints.
-The constraints responsible for the largest numbers of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916) (\emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102) (\emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903) (\emph{SKOS}).
+The constraints responsible for the largest numbers of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916) (\emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102) (\emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903) (\emph{SKOS})\tb{kurz beschreiben}.
 We refer to the technical reports\footnotemark[\ref{technical-report-1}] \footnotemark[\ref{technical-report-2}] to get details about constraints on and the evaluation of \emph{XKOS} and \emph{PHDD} data sets.
@@
 Additionally, it cannot be validated that if an element has a specific value, then certain child elements must be present (\emph{R-71}).  
-A comprehensive comparison of XML and RDF validation is not the purpose of this paper.
+A comprehensive comparison of XML and RDF validation, however, is not within the scope of this paper.
 
@@
 \section{Conclusion and Future Work}
-
+\tb{kürzer!}
 In this paper, we showed in form of a complete real world running example how to represent metadata on person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
@@
 We validated more than 4.2 billion triples and 15 thousand data sets\footnote{The second appendix of this paper describing the evaluation in detail is available at: \textcolor{red}{\url{http://arxiv.org/abs/XXXXX}} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).
-It is still ongoing work to identify and classify constraints on rectangular data (\emph{PHDD}) and statistical classifications (\emph{XKOS}) and to actually evaluate the (meta)data quality of real world \emph{XKOS} and \emph{PHDD} data sets.
+
+%It is still ongoing work to identify and classify constraints on rectangular data (\emph{PHDD}) and statistical classifications (\emph{XKOS}) and to actually evaluate the (meta)data quality of real world \emph{XKOS} and \emph{PHDD} data sets.
 

### 2015-04-18 paper/paper7/paper7.tex
introduction

@@
 %
-\title{RDF Validation of Metadata \\ on Person-Level and Aggregated Data}
+%\title{RDF Validation of Metadata \\ on Person-Level and Aggregated Data}
+%\title{RDF Constraints to Ensure High Quality \\ of Metadata and Data Represented by any Vocabulary }
+%\title{RDF Constraints to Ensure High Quality \\ of Metadata and Data}
+\title{RDF Constraints Classification Ensuring \\ High Quality of Metadata and Data}
 \subtitle{}
@@
 particularly as this is taken for granted in the XML world.
-The data most often used in research within the community around research data for the social, behavioural, and economic sciences (\emph{SBE}) is person-level data, i.e., data collected about individuals (households, businesses).
-%The DDI-RDF Discovery Vocabulary is used to describe and to discover this kind of research data.
-While performing research, the detailed, often access restricted person-level
-data is aggregated into less confidential publicly available multi-dimensional tables which answer particular research questions and whose purpose is to gain an interest in further more detailed analyses on the underlying person-level data.
+%The data most often used in research within the community around research data for the social, behavioural, and economic sciences (\emph{SBE}) is person-level data, i.e., data collected about individuals (households, businesses).
+%%The DDI-RDF Discovery Vocabulary is used to describe and to discover this kind of research data.
+%While performing research, the detailed, often access restricted person-level
+%data is aggregated into less confidential publicly available multi-dimensional tables which answer particular research questions and whose purpose is to gain an interest in further more detailed analyses on the underlying person-level data.
 To ensure high quality and trust, metadata and data must satisfy certain criteria - specified in terms of RDF constraints. 
-From 2012 to 2015 together with other Linked Data community members and \emph{SBE} experts, we developed diverse vocabularies to represent \emph{SBE} metadata and data in RDF.
+%From 2012 to 2015 together with other Linked Data community members and \emph{SBE} experts, we developed diverse vocabularies to represent \emph{SBE} metadata and data in RDF.
 
-In this paper, we show how metadata and data on different level of aggregation as well as collections of these data sets are represented in RDF and how therefore used vocabularies are interrelated.
-We explain why RDF validation is important in this context and how (meta)data is validated against RDF constraints to ensure high quality and trust.
+In this paper, we propose a system to classify RDF constraints and RDF constraint types, which in most cases correspond to RDF validation requirements.
+Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary. 
+Within the context of a complex and complete real world running example within the community around research data for the \emph{social, behavioural, and economic (SBE) sciences}, we prove the claim that the developed classification system perfectly applies for diverse vocabularies.
+We show how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF and how therefore reused vocabularies are interrelated.
+We explain how \emph{SBE} (meta)data is validated against constraints to ensure high quality of and trust in (meta)data.
+We exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets (more than 4.2 billion triples and 15 thousand data sets) by means of constraints of the majority of the constraint types.
 
@@
 
-For more than a decade, members of the community around research data for the social, behavioural, and economic (SBE) sciences have been developing and using a
+For more than a decade, members of the community around research data for the \emph{social, behavioural, and economic (SBE) sciences} have been developing and using a
 metadata standard (composed of almost twelve hundred metadata fields) known as the \emph{Data Documentation Initiative (DDI)} \cite{Vardigan2008}.
-DDI is an XML format designed for the purposes of supporting the dissemination, management,
+\emph{DDI} is an XML format designed to support the dissemination, management,
 and reuse of the data collected and archived for research purposes.  
-DDI is heavily used by the CESSDA community of European national data archives, 
-the International Household Survey Network community (made up of more than 90 statistical agencies),
-and ICPSR - the largest SBE data archive in the US.
+%DDI is heavily used by the CESSDA community of European national data archives, 
+%the International Household Survey Network community (made up of more than 90 statistical agencies),
+%and ICPSR - the largest SBE data archive in the US.
 Increasingly, data professionals, national statistical institutes, data archives, data libraries, and government statisticians (e.g. \url{data.gov}, \url{data.gov.uk})
-are very interested in having their data be discovered and used by providing their metadata on the web in form of RDF (e.g. metadata about unemployment rates or income).
-
+are very interested in having their data be discovered and used by providing their metadata (e.g. about unemployment rates or income) on the web in form of RDF.
 Recently, members of the SBE and Linked Data community developed the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}}, 
 an effort to leverage the mature DDI metadata model for the purposes of exposing DDI metadata as resources within the Web of Linked Data.
+
 For data archives, research institutes, and data libraries,
 RDF data validation according to predefined constraints is a much sought-after feature, 
-particularly as this is taken for granted in the XML world (DDI-XML documents are validated against diverse XSDs\footnote{\label{fnt:DDI-XSDs}\url{http://www.ddialliance.org/Specification/}}).
+particularly as this is taken for granted in the XML world as DDI-XML documents are validated against diverse XSDs\footnote{\label{fnt:DDI-XSDs}\url{http://www.ddialliance.org/Specification/}}.
 Several approaches exist to meet this requirement, ranging from using \emph{OWL 2} as a constraint language to \emph{SPIN}\footnote{\url{http://spinRDF.org/}}, a SPARQL-based way to formulate and check constraints.
-There are also specific constraint languages like \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles} that more or less explicitly address the aforementioned SBE community.
-Bosch and Eckert\cite{BoschEckert2014-2} use SPIN as basis to define a
-validation environment (\url{http://purl.org/net/rdfval-demo}) in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL.
+There are also constraint languages like \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles} that more or less explicitly address the SBE community.
+In 2013, the W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
+where experts from industry, government, and academia discussed first use cases for RDF constraint formulation and RDF data validation.
+In 2014, two working groups on RDF validation have been established to develop a language to express constraints on RDF data: 
+the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles task group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
+
+Bosch and Eckert \cite{BoschEckert2014} collected the findings of these working groups and initiated a database of RDF validation requirements
+which is available for contribution at \url{http://purl.org/net/rdf-validation}.
+The intention is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
+The requirements are classified to better evaluate existing solutions and each requirement is directly mapped to a constraint type which may be expressed by at least one existing constraint language.
+Bosch and Eckert \cite{BoschEckert2014-2} use SPIN as basis to define a
+validation environment (available at \url{http://purl.org/net/rdfval-demo}) in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL.
 The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.
@@
 %(2) metadata providers and harvesters ensuring high quality data and metadata by validating RDF data according to certain constraints.
-In this paper, we show in form of a complete real world running example how to represent metadata on person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
-We explained why RDF validation is important in this context and how metadata on person-level data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality (\textbf{contribution 2}, section \ref{rdf-validation}).
+
+The main \textbf{contribution} of this paper is the development of a system to classify RDF constraints and RDF constraint types, which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (section \ref{classification}).
+Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary. 
+As constraint types are used to define constraints on (meta)data expressed by any vocabulary, the proposed constraint classification can be applied generically, i.e. vocabulary-independent. 
+Within the context of a complex and complete real world running example from the \emph{SBE} domain, we prove the claim that the developed classification system perfectly applies for diverse vocabularies.
+%, i.e., that it does not matter which vocabularies are used to represent (meta)data and for which domains constraints are defined.
+We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
+show how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF and how therefore reused vocabularies are interrelated (section \ref{rdf-representation}).
+We explain how \emph{SBE} (meta)data is validated against constraints, instantiated from constraint types organized in the constraint classification system, to ensure high quality of and trust in (meta)data.
+
 %The remainder of the paper is structured as follows.
-\tb{nur eine contribution}
+For the extensive evaluation, we implemented 53 constraint types by instantiating 212 constraints on \emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{XKOS}, and \emph{PHDD} data sets (section \ref{implementation}).
+First, several \emph{SBE} domain experts evaluated the correctness (i.e., the gold standard) of all constraints and therefore the generic applicability of the developed constraint classification system.
+Second, we exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets (more than 4.2 billion triples and 15 thousand data sets) by means of constraints of the majority of the constraint types (section \ref{evaluation}).
+
 \section{Motivation}
+\label{motivation}
 
@@
 %\label{running-example}
-\section{Represent Metadata and Data in RDF}
+\section{Vocabularies to Represent Metadata and Data in RDF}
 \label{rdf-representation}
@@
 
-\textbf{Metadata on Aggregated Data in RDF.}
+\textbf{Metadata on Aggregated Data.}
 The variable \emph{formal childcare}\footnote{\url{http://ec.europa.eu/eurostat/web/products-datasets/-/ilc_caindformal}} (in contrast to childcare at home)
@@
 
-\textbf{Rectangular Data in RDF.}
+\textbf{Rectangular Data.}
 As Eurostat provides aggregated data as CSV files, we can easily represent the two-dimensional table in RDF by means of \emph{PHDD}.
@@
 
-\textbf{Metadata on Person-Level Data in RDF.}
+\textbf{Metadata on Person-Level Data.}
 For a broader view of the data framework and more detailed analyses we refer to the metadata on person-level data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}
@@
 \section{Classification of RDF Constraint Types and RDF Constraints to Validate Metadata and Data}
-\label{rdf-validation}
+\label{classification}
 
@@
 
-For this paper, we developed a system to classify RDF constraint types and RDF constraints\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper}.
+For this paper, we developed a system to classify RDF constraint types and RDF constraints.
 Constraints are instantiated from constraint types, which are organized as disjoint sets, in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent.
@@
 \section{Conclusion and Future Work}
-\tb{kürzer!}
+
 In this paper, we showed in form of a complete real world running example how to represent metadata on person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).

### 2015-04-18 paper/paper7/paper7.tex
introduction

@@
 The main \textbf{contribution} of this paper is the development of a system to classify RDF constraints and RDF constraint types, which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (section \ref{classification}).
+We propose an extensible metric to measure the continuum of severity levels to indicate how serious the violation of given constraints is.
 Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary. 
@@
 
-\section{Classification of RDF Constraint Types and RDF Constraints to Validate Metadata and Data}
+\section{RDF Constraints Classification}
 \label{classification}
@@
 Bosch et al.
-identified 74 requirements to formulate RDF constraints; each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}\cite{BoschNolleAcarEckert2015}.
+identified 74 requirements to formulate RDF constraints (e.g.
+\emph{R-75, R-81: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}\cite{BoschNolleAcarEckert2015}.
 We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement (constraint type) in detail and give examples for each expressed by different constraint languages.
@@
 
-For this paper, we developed a system to classify RDF constraint types and RDF constraints.
-Constraints are instantiated from constraint types, which are organized as disjoint sets, in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent.
-Constraint types either corresponding to
-
-\begin{enumerate}
-	\item \emph{RDF validation requirements} (e.g. \emph{R-75, R-81: minimum qualified cardinality restrictions}) or to
-	\item \emph{data model specific constraint types} (e.g. \emph{data model consistency})\cite{BoschZapilkoWackerowEckert2015}.
-\end{enumerate}
-
+We developed a system to classify RDF constraints and RDF constraint types.
+Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
+%\emph{data model specific constraint types} (e.g. \emph{data model consistency})
 The complete set of \emph{constraint types} ($\mathcal{CT}$) encompasses two disjoint \textbf{\emph{sets of constraint types}}:
@@
 Therefore, domain experts may formulate $\mathcal{CT}_{C}$ constraints manually in prose English which is technically expressed by a constraint language afterwards.
-$\mathcal{CT}_{T}$ (\emph{Technology-Driven Constraint Types}) is the set of constraints which can be generated completely automatically out of vocabularies' data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges (section \ref{technology-driven-validation}).
+For assessing the quality of thesauri, e.g., we concentrate on the graph-based structure and apply graph- and network-analysis techniques (constraint type: \emph{structure}). 
+A thesaurus, e.g., should not contain many orphan concepts (concepts without any associative or hierarchical relations) lacking valuable context information for search and retrieval.  
+$\mathcal{CT}_{T}$ (\emph{Technology-Driven Constraint Types}) is the set of constraints which can be generated completely automatically out of vocabularies' data models (section \ref{technology-driven-validation}).
+With \emph{minimum qualified cardinality restrictions} (\emph{R-74}), e.g., one can restrict that
+a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column} (in DL: \ms{TableStructure $\sqsubseteq$ $\geq$1 column.Column})\footnote{For simplicity reasons, we do not use namespace prefixes in DL statements.}.
 
@@
 \end{enumerate}
-The violation of $\mathcal{SL}_{0}$ constraints does not mean that there are serious mistakes in either syntax or semantics.
-These constraints may point to possible data improvements in order to get ideal RDF representations.
+Violations of $\mathcal{SL}_{0}$ constraints point to possible data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies. 
 Data not conforming to $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is syntactically or semantically not correctly represented.
-The difference between $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is that $\mathcal{SL}_{1}$ invalid data could be processed 
+The difference between $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is that $\mathcal{SL}_{1}$ invalid data could be
 whereas $\mathcal{SL}_{1}$ invalid data cannot be processed further. 
-Although we provide default severity levels for each constraint, users should be able to specify severity levels of constraints they need to validate for their individual use cases, i.e., users should be able to define use case specific severity levels for constraints.
+Although, we provide default severity levels for each constraint, users should be able to specify constraints' severity levels according to their individual needs, i.e., use case specific severity levels.
+
 In this section, we describe constraints and constraint types which are important to ensure (meta)data  quality on different aggregation levels. 
@@
 
-We recently published a technical report\footnote{\textcolor{red}{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as first appendix of this paper) in which we describe and classify constraints to validate rectangular data and metadata on person-level data sets, aggregated data sets, thesauri, and statistical classifications and therefore apply the proposed classification system.
+We recently published a technical report\footnote{\textcolor{red}{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as first appendix of this paper) in which we describe and classify constraints to validate rectangular data and metadata on person-level data sets, aggregated data sets, thesauri, and statistical classifications and therefore apply the proposed classification system \cite{BoschZapilkoWackerowEckert2015}.
 
@@
 \label{content-driven-validation}
+
+\tb{die einzelnen Paragraphen sollten constraint types clustern entsprechen - Unterkapitel umorganisieren!}
 

### 2015-04-18 paper/paper7/paper7.tex
introduction

@@
 \usepackage[colorinlistoftodos]{todonotes}
-\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
+\newcommand{\ke}[1]{\todo[size=\small, color=red!40]{\textbf{Kai:} #1}}
 \newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}
-\newcommand{\er}[1]{\todo[size=\small, color=red!40]{\textbf{Erman:} #1}}
-\newcommand{\an}[1]{\todo[size=\small, color=blue!40]{\textbf{Andy:} #1}}
+\newcommand{\er}[1]{\todo[size=\small, color=blue!40]{\textbf{Erman:} #1}}
 
@@
 \label{motivation}
-
+\ke{@KAI: Dieses Kapitel werde ich noch deutlich kürzen!}
 The data most often used in research within the SBE community is \emph{person-level data}, i.e.
@@
 \label{rdf-representation}
-
-\textcolor{red}{figure / metadata: person-level, aggregated, thesauri, catalogs, statistical classifications / data: rectangular data}
+\ke{@KAI: Dieses Kapitel werde ich noch deutlich kürzen!}
+\tb{figure / metadata: person-level, aggregated, thesauri, catalogs, statistical classifications / data: rectangular data}
 
@@
 
-\tb{aut SDMX sind year, duration, age, etc. keine Variablen, sondern Dimensionen}
+\tb{laut SDMX sind year, duration, age, etc. keine Variablen, sondern Dimensionen}
 
@@
 
-In this section, we describe constraints and constraint types which are important to ensure (meta)data  quality on different aggregation levels. 
+We recently published a technical report\footnote{\textcolor{red}{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as first appendix of this paper) in which we describe and classify constraints to validate rectangular data and metadata on person-level data sets, aggregated data sets, thesauri, and statistical classifications and therefore apply the proposed classification system \cite{BoschZapilkoWackerowEckert2015}.
+In this section, we describe constraint types and constraints which are important to ensure (meta)data  quality on different aggregation levels. 
 Furthermore, we associate constraints with default severity levels and assign them to validation types.
-
-We recently published a technical report\footnote{\textcolor{red}{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as first appendix of this paper) in which we describe and classify constraints to validate rectangular data and metadata on person-level data sets, aggregated data sets, thesauri, and statistical classifications and therefore apply the proposed classification system \cite{BoschZapilkoWackerowEckert2015}.
 
@@
 \label{content-driven-validation}
+\ke{@KAI: Dieses Kapitel werde ich noch umorganisieren! Die einzelnen Paragraphen sollten zusammengehörigen Clustern von constraint types entsprechen!}
 
-\tb{die einzelnen Paragraphen sollten constraint types clustern entsprechen - Unterkapitel umorganisieren!}
-
-\textcolor{red}{short description}
+\tb{short description}
 
@@
 \section{Conclusion and Future Work}
-
+\ke{@KAI: Dieses Kapitel muss ich noch an die Änderungen im Paper anpassen!}
 In this paper, we showed in form of a complete real world running example how to represent metadata on person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).

### 2015-04-18 paper/paper7/paper7.tex
RDF constraints classification

@@
 
-We recently published a technical report\footnote{\textcolor{red}{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as first appendix of this paper) in which we describe and classify constraints to validate rectangular data and metadata on person-level data sets, aggregated data sets, thesauri, and statistical classifications and therefore apply the proposed classification system \cite{BoschZapilkoWackerowEckert2015}.
-In this section, we describe constraint types and constraints which are important to ensure (meta)data  quality on different aggregation levels. 
-Furthermore, we associate constraints with default severity levels and assign them to validation types.
+We recently published a technical report\footnote{\textcolor{red}{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as first appendix of this paper) in which we describe 212 constraints (classified as 53 constraint types) to validate rectangular data (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}), and therefore apply the proposed classification system to several vocabularies to represent both data and metadata \cite{BoschZapilkoWackerowEckert2015}.
+In this section, we describe constraints, which are important to ensure \emph{SBE} (meta)data quality, 
+associate them with default severity levels, and assign them to $\mathcal{CT}_{C}$ and $\mathcal{CT}_{T}$ constraint types.
 

### 2015-04-18 paper/paper7/paper7.tex
RDF constraints classification

@@
 Within the context of a complex and complete real world running example within the community around research data for the \emph{social, behavioural, and economic (SBE) sciences}, we prove the claim that the developed classification system perfectly applies for diverse vocabularies.
-We show how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF and how therefore reused vocabularies are interrelated.
-We explain how \emph{SBE} (meta)data is validated against constraints to ensure high quality of and trust in (meta)data.
-We exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets (more than 4.2 billion triples and 15 thousand data sets) by means of constraints of the majority of the constraint types.
+We show how data in rectangular format and metadata on person-level data sets (i.e., data about individuals, households, businesses), aggregated data sets, thesauri, and statistical classifications are represented in RDF and how therefore reused vocabularies are interrelated.
+We explain how \emph{SBE} (meta)data is validated against constraints to ensure high quality and trust.
+We exhaustively evaluated the metadata quality of large real world aggregated, person-level, and thesauri data sets (more than 4.2 billion triples and 15 thousand data sets) by means of constraints of the majority of constraint types.
 
-\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, Disco, RDF Data Cube Vocabulary, Linked Data, Semantic Web}
+\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, RDF Data Cube Vocabulary, Rectangular Data, SKOS, XKOS, Linked Data, Semantic Web}
 \end{abstract}
@@
 %and ICPSR - the largest SBE data archive in the US.
-Increasingly, data professionals, national statistical institutes, data archives, data libraries, and government statisticians (e.g. \url{data.gov}, \url{data.gov.uk})
+Increasingly, data professionals, data archives, data libraries, government statisticians (e.g. \url{data.gov}, \url{data.gov.uk}), and national statistical institutes
 are very interested in having their data be discovered and used by providing their metadata (e.g. about unemployment rates or income) on the web in form of RDF.
@@
 Several approaches exist to meet this requirement, ranging from using \emph{OWL 2} as a constraint language to \emph{SPIN}\footnote{\url{http://spinRDF.org/}}, a SPARQL-based way to formulate and check constraints.
-There are also constraint languages like \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles} that more or less explicitly address the SBE community.
+There are also constraint languages like \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles} that more or less explicitly address the \emph{SBE} community.
 In 2013, the W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
@@
 We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
-show how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF and how therefore reused vocabularies are interrelated (section \ref{rdf-representation}).
+how data in rectangular format (expressed by the \emph{PHDD} vocabulary) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF, and how therefore reused vocabularies are interrelated (section \ref{rdf-representation}).
 We explain how \emph{SBE} (meta)data is validated against constraints, instantiated from constraint types organized in the constraint classification system, to ensure high quality of and trust in (meta)data.
@@
 First, several \emph{SBE} domain experts evaluated the correctness (i.e., the gold standard) of all constraints and therefore the generic applicability of the developed constraint classification system.
-Second, we exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets (more than 4.2 billion triples and 15 thousand data sets) by means of constraints of the majority of the constraint types (section \ref{evaluation}).
+Second, we exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets (more than 4.2 billion triples and 15 thousand data sets) by means of constraints of the majority of constraint types (section \ref{evaluation}).
 

### 2015-04-18 paper/paper7/paper7.tex
RDF constraints classification

@@
 \label{motivation}
-\ke{@KAI: Dieses Kapitel werde ich noch deutlich kürzen!}
+
 The data most often used in research within the SBE community is \emph{person-level data}, i.e.
-data collected about individuals, businesses, and households in form of responses to studies or taken from administrative registers
+data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers
 (such as hospital records, registers of births and deaths). 
-The range of person-level data covers many different domains and is very broad - 
+The range of person-level data is very broad - 
 including census, education, and health data as well as all types of business, social, and labor force surveys.  
-Increasingly, this type of research data is
+This type of research data is
 held within data archives or data libraries after it has been collected, so that it may be
@@
 To ensure high quality, the metadata must satisfy certain criteria - specified in terms of RDF constraints.  
-After validating the metadata according to these constraints, portals offer added values to their customers, e.g. by searching over and comparing metadata of multiple providers.
+After validating the metadata according to these constraints, portals offer added values to their customers, e.g., by searching over and comparing metadata of multiple providers.
 
@@
 Researchers typically represent their results as aggregated data in form of two-dimensional tables with only a few columns (so-called \emph{variables} such as \emph{sex} or \emph{age}).
-The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e.
-multi-dimensional aggregate data, in RDF \cite{Cyganiak2010}.
-Aggregate data is derived from person-level data by statistics on groups or aggregates such as counts, means, and frequencies.
-The SDMX metadata standard – used as the basis for \emph{QB} – and DDI have traditionally made efforts to align their content. 
-Similarly, some of the developers of \emph{Disco} were also involved in the development of \emph{QB}, 
-allowing the RDF versions of these standards to retain that alignment.
+The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing metadata on \emph{data cubes}, i.e.
+multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}.
+Aggregated data is derived from person-level data by statistics on groups or aggregates such as counts, means, and frequencies.
+%The SDMX metadata standard – used as the basis for \emph{QB} – and DDI have traditionally made efforts to align their content. 
+%Similarly, some of the developers of \emph{Disco} were also involved in the development of \emph{QB}, 
+%allowing the RDF versions of these standards to retain that alignment.
 While \emph{Disco} and \emph{QB} provide terms for the description of data sets, 
@@
 The relationship between data collections and their contained data sets is useful, since such collections are a typical entry point when searching for data.
-Although, in most cases aggregated data is still published in form of PDFs, 
-it is more and more common to publish aggregated data as CSV files,
-allowing to perform first calculations (either using all variables or only a subset).
+%Although, in most cases aggregated data is still published in form of PDFs, 
+%it is more and more common to publish aggregated data as CSV files,
+Aggregated data is more and more published as CSV files,
+allowing to perform first data calculations.
 %For these calculations, definitions of the columns are needed (e.g. is a given variable interpreted numerically or as a string).
-In 2014, SBE and Linked Data community members developed the \emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} vocabulary to represent aggregated and person-level data in a rectangular format.
+In 2014, SBE and Linked Data community members developed the \emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} vocabulary to represent data in a rectangular format.
 The data could be either represented in records with character-separated values (CSV) or in records with fixed length.

### 2015-04-19 paper/paper7/paper7.tex
chapter 3

@@
 One very common example for detailed analyses on person-level data is the content-driven comparison of multiple studies.
-Researchers get promising findings (in form of published tables with a few columns) within a metadata portal leading to subsequent research questions 
-like 'How to compare the unemployment rate of different countries (e.g. Germany, UK, and France) in the last 10 years grouped by age?'.
-The first step is to determine in which countries the unemployment rate is collected and which other variables of each country-specific study are theoretically comparable and can therefore be used to answer the underlying research question.
 A \emph{study} represents the process by which a data set was generated or collected.
+Eurostat\footnote{\url{http://ec.europa.eu/eurostat}} is the statistical office of the European Union.
+Its task is to provide statistics at European level that enable comparisons between countries and regions.
+Eurostat provides publicly available European aggregated data (downloadable as CSV files) and its metadata.
+This way, researchers get promising findings (in form of published tables with a few columns), e.g., about the availability of childcare services in European Union Member States by year, duration, and child age  leading to subsequent research questions.
+%The first step is to determine in which countries the unemployment rate is collected and which other variables of each country-specific study are theoretically comparable and can therefore be used to answer the underlying research question.
+
+The variable \emph{formal childcare}\footnote{The data set is available at: \url{http://ec.europa.eu/eurostat/web/products-datasets/-/ilc_caindformal}} (in contrast to childcare at home)
+captures the measured availability of childcare services in percent over the population.
+The present data collection refers to data on formal childcare by the variables \emph{year}, \emph{duration} (in hours per week), \emph{age} of the child, and \emph{country}.
 Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
@@
 To determine if variables measuring \emph{age} 
-- collected within multiple studies of different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
-are comparable, both content-driven and technology-driven validation is performed.
-An example for a content-driven validation is to investigate if variables are represented in a compatible way,
-i.e. are the variables' code lists theoretically comparable.
-Technically, it can be validated (1) if variable definitions are available, (2) if code lists are properly structured, and (3) if for each code an associated category (a human-readable label) is specified.
+- collected for different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
+are comparable, both content-driven and technology-driven constraints are validated.
+Content-driven constraints ensure that the data is consistent with the intended syntax, semantics, and integrity of vocabularies' data models and 
+technology-driven constraints can be generated completely automatically out of vocabularies' data models. 
+Examples for content-driven constraints are to investigate (1) if variables are represented in a compatible way,
+i.e. are the variables' code lists theoretically comparable, and (2) if variables' code lists are properly structured.
+With technology-driven constraints, it can be validated (1) if variable definitions are available and (2) if for each code an associated category (a human-readable label) is specified.
 
-Data providers and harvesters do not only offer metadata but also publicly available data on different level of detail.
-To ensure high data quality and trust, they have to analyze and validate the data (are fundamental data fragments available?, how does valid data look like?). 
+%\textbf{Data validation.}
+Data providers and harvesters do not only offer metadata but also publicly available data on different level of aggregation.
+To ensure high data quality, they have to check provenance information and to analyze and therefore validate the data according to predefined constraints (e.g.
+'are fundamental data fragments available?', and 'how does valid data look like?').
 %They validate, e.g., if fundamental data parts are available and define how valid data should look like (using syntactic rules).
-Provenance (where does the data come from?) is an important aspect in evaluating data quality.
-As data searchers know exactly which data sources they trust and which are reasonable to meet their individual use cases, 
-RDF data validation can only be performed semi-automatically, i.e., an automatic approach serves as basis for intellectual decisions.
+%Provenance (where does the data come from?) is an important aspect in evaluating data quality.
+%As data searchers know exactly which data sources they trust and which are reasonable to meet their individual use cases, 
+%RDF data validation can only be performed semi-automatically, i.e., an automatic approach serves as basis for intellectual decisions.
 
@@
 \label{rdf-representation}
-\ke{@KAI: Dieses Kapitel werde ich noch deutlich kürzen!}
-\tb{figure / metadata: person-level, aggregated, thesauri, catalogs, statistical classifications / data: rectangular data}
 
-Eurostat\footnote{\url{http://ec.europa.eu/eurostat}} is the statistical office of the European Union.
-Its task is to provide statistics at European level that enable comparisons between countries and regions.
-Eurostat provides publicly available European aggregated data (downloadable in machine-readable format like CSV files) and its metadata (only textual descriptions).
-SBE researchers have a strong interest, e.g., in the availability of childcare services across European Union Member States.
-\tb{folgendes beispiel bezieht sich auf diesen datensatz}
+In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.
 
 \textbf{Metadata on Aggregated Data.}
-The variable \emph{formal childcare}\footnote{\url{http://ec.europa.eu/eurostat/web/products-datasets/-/ilc_caindformal}} (in contrast to childcare at home)
-captures the measured availability of childcare services in percent over the population.
-The present data collection refers to data on formal childcare and other types of care by the variables \emph{year}, \emph{duration} (0 hours, 1 - 29 HPW; 30 HPW), \emph{age} of the child (0-2 years; 3 to admission age for compulsory school; admission age for compulsory school to 12) and \emph{country}.
-\emph{QB} is a vocabulary to represent metadata on multi-dimensional aggregate data.
-Such data is represented using \emph{QB} in two files, a \emph{qb:DataSet} and a \emph{qb:DataStructureDefinition}.
+The vocabulary \emph{QB} represents metadata on multi-dimensional aggregate data in two files, a \emph{qb:DataSet} and a \emph{qb:DataStructureDefinition}.
 The \emph{qb:DataStructureDefinition} contains metadata of the present data collection.
-Thereby, the variable \emph{formal childcare} is modelled as \emph{qb:measure}, since it expresses what has been measured in the data collection.
-The \emph{year}, \emph{duration}, \emph{age}, etc. are defined as \emph{qb:dimension}.
-The particular data values, i.e.
-the specific availability of childcare services in percent over the population in particular years, are collected in a \emph{qb:DataSet}.
-Each data value is represented inside a \emph{qb:Observation} which additionally contains the particular dimensional values associated with that data value, e.g.
-the concrete year in which the formal childcare has been determined.
-
-\footnote{\textcolor{red}{The complete running example in RDF is available at: \url{XXXXX}}}
-
-\tb{laut SDMX sind year, duration, age, etc. keine Variablen, sondern Dimensionen}
+Thereby, the variable \emph{formal childcare} is modelled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
+The variables \emph{year}, \emph{duration}, \emph{age}, and \emph{country} are defined as \emph{qb:dimension}.
+Data values, i.e., the availability of childcare services in percent over the population, are collected in a \emph{qb:DataSet}. 
+Each data value is represented inside a \emph{qb:Observation} which additionally contains values for each dimension 
+(e.g., the year in which \emph{formal childcare} has been determined).
 
 \textbf{Rectangular Data.}
-As Eurostat provides aggregated data as CSV files, we can easily represent the two-dimensional table in RDF by means of \emph{PHDD}.
-\emph{PHDD} is a vocabulary to represent aggregated and person-level data in a rectangular format. 
-The data could be either represented in records with character-separated values (CSV) or in records with fixed length. 
-The two-dimensional table about \emph{formal childcare} can be downloaded as CSV file. 
-The table is represented as \emph{phdd:Table} and structured by a table structure (\emph{phdd:TableStructure}, \emph{phdd:Delimited}).
-The running example table structure includes information about the character set (\emph{ASCII}), the variable delimiter (\emph{,}), the new line marker (\emph{CRLF}), and the first line where the data starts (\emph{2}).
-The table structure relates to the table columns (\emph{phdd:Column}) which are described by column descriptions (\emph{phdd:DelimitedColumnDescription}).
-For the column containing the cell values in percent, e.g., the CSV column position (\emph{5}), the recommended data type (\emph{xsd:nonNegativeInteger}), and the storage format (\emph{TINYINT}) is stated.
+\emph{PHDD} represents data in a rectangular format in RDF. 
+The data could be either represented in records with character-separated values (CSV) or fixed length. 
+Eurostat provides the two-dimensional table about \emph{formal childcare} in form of a CSV file. 
+The \emph{phdd:Table} is structured by a table structure (\emph{phdd:TableStructure}, \emph{phdd:Delimited}).
+The table structure includes information about the character set (\emph{ASCII}), the variable delimiter (\emph{,}), the new line marker (\emph{CRLF}), and the first line where the data starts (\emph{2}).
+The table structure is related to table columns (\emph{phdd:Column}) which are described by column descriptions (\emph{phdd:DelimitedColumnDescription}).
+For the column containing the cell values in percent, the column position (\emph{5}), the recommended data type (\emph{xsd:nonNegativeInteger}), and the storage format (\emph{TINYINT}) is stated. 
 The RDFication enables further aggregations and calculations, e.g., in order to compare \emph{formal childcare} between Northern and Southern Europe or between otherwise grouped countries.
@@
 For a broader view of the data framework and more detailed analyses we refer to the metadata on person-level data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}
-and publicly provided by the \emph{Microdata Information System (MISSY)}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}}.
-Where data collection is cyclic, data sets may be released as a \emph{series}, 
+published by the \emph{Microdata Information System (MISSY)}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}}.
+Where data collection is cyclic, data sets may be released as \emph{series}, 
 where each cycle of the data collection activity produces one or more data sets. 
 \emph{Missy} is an online service platform that provides systematically structured metadata for official statistics on European person-level data sets. 
-This includes data documentation at the study and variable level as well as documentation materials, tools and further information.
+%This includes data documentation at the study and variable level as well as documentation materials, tools and further information. 
 Aggregated (qb:DataSet) and underlying person-level data sets (\emph{disco:LogicalDataSet}) are connected by \emph{prov:wasDerivedFrom}. 
@@
 %(6) Child care by grand-parents, household members, relatives, friends, neighbours.
-For each person-level variable detailed metadata is given (definitions and descriptions, theoretical concepts, underlying questions, code lists, frequencies and descriptive statistics, countries, year of data collection, classifications) enabling researchers to replicate the results shown in the aggregated data tables from Eurostat.
-Metadata on person-level data is represented in RDF using the \emph{Disco} vocabulary.
-The series (\emph{disco:StudyGroup}) \emph{EU-SILC} contains (\emph{disco:inGroup}) one study (\emph{disco:Study}) for each year (\emph{dcterms:temporal}) of data collection, e.g.
-\emph{EU-SILC 2011}.
-The property \emph{dcterms:spatial} points to the countries (\emph{dcterms:Location} resources which are the same as \emph{GeoNames} resources representing these countries) for which the data has been collected.
-The study \emph{EU-SILC 2011} contains (\emph{disco:product}) eight person-level data sets (\emph{disco:LogicalDataSet}).
-Data sets include (\emph{disco:variable}) person-level variables (\emph{disco:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
-Metadata on person-level data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
-One common research question is ,e.g., the comparison of variables like 
-\emph{formal childcare} between countries, for which the variable is collected within the context of an individual study, and other European or non European countries (e.g. OSCE).
+For each person-level variable detailed metadata is given (definitions, descriptions, theoretical concepts, questions variables are based on, code lists, frequencies, descriptive statistics, countries, year of data collection, and classifications) which enables researchers to replicate the results shown in the aggregated data tables from Eurostat.
+The vocabulary \emph{Disco} represents metadata on person-level data in RDF.
+The series (\emph{disco:StudyGroup}) \emph{EU-SILC} contains one study (\emph{disco:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
+\emph{dcterms:spatial} points to the countries for which the data has been collected.
+The study \emph{EU-SILC 2011} contains eight person-level data sets (\emph{disco:LogicalDataSet})
+including person-level variables (\emph{disco:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
+%Metadata on person-level data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
+%One common research question is ,e.g., the comparison of variables like 
+%\emph{formal childcare} between countries, for which the variable is collected within the context of an individual study, and other European or non European countries (e.g. OSCE).
 

### 2015-04-19 paper/paper7/paper7.tex
chapter 3

@@
 %\textbf{Reusing SKOS.}
-The \emph{Simple Knowledge Organization System (SKOS)} is used multiple times within the context of aggregated and person-level (meta)data.
-Variables, e.g., are constructed (\emph{disco:representation}) out of values (of one or multiple datatypes) and/or code lists.
-The values of the variable \emph{Education at pre-school}, representing the number of education hours during a usual week, are expressed as \emph{skos:Concepts}. 
-\emph{Disco} uses \emph{skos:OrderedCollection} to organize them in a particular order in a \emph{skos:memberList}. 
-SKOS is also used to form hierarchies of \emph{SBE theoretical concepts} (e.g. Education) with which variables may be associated.
-The compete hierarchy (\emph{skos:ConceptScheme}) of theoretical concepts (\emph{skos:Concepts}) of series is built using \emph{skos:narrower}.
-The variable \emph{Education at pre-school} is assigned to the theoretical concept \emph{Child Care} which is a narrower concept of \emph{Education} - one of the top concept of the series \emph{EU-SILC}.
-Controlled vocabularies serve as extension and reuse mechanism.
-For \emph{Disco}, concepts (\emph{skos:Concepts}), organized within controlled vocabularies (\emph{skos:ConceptSchemes}), indicate types of descriptive statistics (\emph{\emph{disco:SummaryStatistics}}) like minimum, maximum, mean, and standard deviation.
-From 2012 to 2015, SBE and Linked Data community members developed \emph{XKOS}\footnote{\url{https://github.com/linked-statistics/xkos}} - a SKOS extension to describe formal statistical classifications like the International Standard Classification of Occupations (\emph{ISCO}).
+The \emph{Simple Knowledge Organization System (SKOS)} is reused multiple times to represent metadata on aggregated and person-level data.
+Variables are constructed out of values and/or (un)ordered code lists.
+The codes of the variable \emph{Education at pre-school} (number of education hours per week) are modeled as \emph{skos:Concepts} and 
+a \emph{skos:OrderedCollection} organizes them in a particular order within a \emph{skos:memberList}.
+A variable may be associated with a theoretical concept (\emph{skos:Concept}) and   
+\emph{skos:narrower} builds the hierarchy of theoretical concepts within the \emph{skos:ConceptScheme} of a series.
+The variable \emph{Education at pre-school}, e.g., is assigned to the theoretical concept \emph{Child Care} which is the narrower concept of \emph{Education} - one of the top concepts of the series \emph{EU-SILC}.
+Controlled vocabularies (\emph{skos:ConceptScheme}), serving as extension and reuse mechanism,
+organize types (\emph{skos:Concept}) of descriptive statistics (\emph{\emph{disco:SummaryStatistics}}) like minimum, maximum, and arithmetic mean.
+\emph{XKOS}\footnote{\url{https://github.com/linked-statistics/xkos}} is a SKOS extension to describe formal statistical classifications like the International Standard Classification of Occupations (\emph{ISCO}).
 %and the Statistical Classification of Economic Activities in the European Community \emph{NACE}.
@@
 \textbf{Searching for (Meta)data.}
-\emph{DCAT} enables to represent aggregated and person-level data inside of data collections like portals, repositories, catalogs, or archives
-serving as typical entry points when searching for data.
+\emph{DCAT} enables to represent aggregated and person-level data sets inside of data collections like portals, repositories, catalogs, and archives
+which serve as typical entry points when searching for data.
 Users search for aggregated and person-level data records (\emph{dcat:CatalogRecord}) inside data catalogs (\emph{dcat:Catalog}). 
-This search differs depending on the users’ information need. 
-While it is possible to search for metadata provided inside such a record (e.g. \emph{dcterms:title}, \emph{dcterms:description}), 
-users can also formulate more sophisticated queries on aggregated and person-level data sets (\emph{dcat:Dataset}) or their
-distributions (\emph{dcat:Distribution}), which are part of the records. 
-Users may want to search for data sets covering particular topical (\emph{dcat:keyword}, \emph{dcat:theme}), temporal (\emph{dcterms:temporal}),  or  spatial  coverages (\emph{dcterms:spatial}), 
-or certain formats in which the data distribution is available (\emph{dcterms:format}).
+As search differs depending on the users’ information need,
+users may only search for records' metadata (e.g., \emph{dcterms:title}, \emph{dcterms:description}), 
+or may formulate more sophisticated queries on aggregated and person-level data sets (\emph{dcat:Dataset}) or their
+distributions (\emph{dcat:Distribution}) which are part of the records. 
+Often, users search for data sets covering particular topics (\emph{dcat:keyword}, \emph{dcat:theme}), time periods (\emph{dcterms:temporal}),  or  locations (\emph{dcterms:spatial}), 
+or for certain formats in which the data distribution is available (\emph{dcterms:format}).
 

### 2015-04-19 paper/paper7/paper7.tex
content-driven constraint types

@@
 According to the constraints' default severity level the complete set of constraints ($\mathcal{C}$) encompasses three disjoint \textbf{\emph{sets of constraints}}:
-\begin{enumerate}
+\begin{itemize}
 	\item $\mathcal{SL}_{0}$: set of constraints with severity level \emph{informational}
@@
 	\item $\mathcal{SL}_{2}$: set of constraints with severity level \emph{error}
-\end{enumerate}
+\end{itemize}
 Violations of $\mathcal{SL}_{0}$ constraints point to possible data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies. 
@@
 
-\subsection{Content-Driven Constraint Types}
-\label{content-driven-validation}
-\ke{@KAI: Dieses Kapitel werde ich noch umorganisieren! Die einzelnen Paragraphen sollten zusammengehörigen Clustern von constraint types entsprechen!}
-
-\tb{short description}
-
-\textbf{Observations of Aggregated Data Sets.}
-The purpose of some constraints is to ensure the integrity of
-the data according to intended data model semantics (\emph{data model consistency}).
-Every \emph{qb:Observation}, e.g., must have a value for each dimension
-declared in its associated \emph{qb:DataStructureDefinition} ($\mathcal{SL}_{2}$)
-and no two \emph{qb:Observations} in the same \emph{qb:DataSet}
-may have the same value for all dimensions ($\mathcal{SL}_{1}$).
-If a \emph{qb:DataSet} \emph{D} has a \emph{qb:Slice} \emph{S}, and \emph{S} has an
-\emph{qb:Observation} \emph{O}, then the \emph{qb:DataSet} corresponding to \emph{O} must be \emph{D} ($\mathcal{SL}_{1}$).
-
-%- for each dimension there should be a description and code lists.
-%
-%- for each code list there should be a description.
-%
-%- there should be a relationship to the underlying person-level data.
-
-\textbf{Series, Studies, Data Sets, and Data Files.}
-It is useful to declare properties to be \emph{conditional} (\emph{R-71}), i.e., if particular properties exist (or do not exist), then other properties must also be present (or absent).
-To get an overview over a series/study either an abstract, a title, an alternative title, or links to external descriptions should be provided. 
-If an abstract and an external description are absent, 
-a title or an alternative title has to be stated ($\mathcal{SL}_{1}$).
-For datatype properties it should be possible to declare frequently needed \emph{facets} ({\emph{R-46}) to drive user interfaces and validate input against simple conditions including min/max values, regular expressions, and string length.
-The abstract of series/studies, e.g., should have a minimum length (\emph{xsd:minLength}; $\mathcal{SL}_{1}$).
-\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals of certain types.
-If a study, e.g., has no associated data sets ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
-If there is no metadata on data files including the actual data of data sets (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the underlying study is not sufficient.
-The case quantity measures how many cases are collected for a study.
-A high case and variable quantity is an indicator for high statistical quality and comprehensiveness of the conducted study ($\mathcal{SL}_{1}$).
-
-\textbf{Variables and Variable Comparison.}
-Each variable should have a variable representation (\emph{R-86}; $\mathcal{SL}_{1}$), which is either an (un)ordered code list or a union of datatypes.
-In case of a code list, associated categories (human-readable labels) may be stated (\emph{R-71}; $\mathcal{SL}_{0}$).
-The variable \emph{Education at pre-school} is represented as ordered code list without any categories.
-If a {\em skos:Concept} stands for a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
-then the property {\em disco:isValid} has to be stated indicating if the code is valid (\emph{true}) or missing (\emph{false}) (\emph{R-71}; $\mathcal{SL}_{2}$).
-Variables may have at least one relationship to a theoretical concept ({\emph{R-86}; $\mathcal{SL}_{0}$).
-%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
-The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
-The default severity level of this constraint is weak, as in most cases research can be continued without associated theoretical concepts.
-A very common research question is to compare variables of multiple studies or countries (\emph{comparison}).
-To compare variables, 
-(1) variables and (2) variable definitions must be present,
-(3) code lists must be structured properly,
-(4) for each code an associated category (human-readable label) must be specified, and
-(5) code lists must either be identical or at least similar.
-If a researcher wants to get a first overview over comparable variables (use case 1), 
-covering the first three constraints may be sufficient for this purpose.
-Thus, the severity level of the first three constraints is stronger ($\mathcal{SL}_{2}$) than the severity level of the next two constraints ($\mathcal{SL}_{1}$ and $\mathcal{SL}_{0}$).
-If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the remaining two constraints is getting more serious.
-
-\textbf{Descriptive Statistics.}
-The property \emph{disco:percentage} stands for the number of cases of a given code in relation to the total number of cases for a particular variable within a data set.
-Percentage values are only valid when they are within the \emph{literal range} of 0 and 100 (\emph{R-45}; $\mathcal{SL}_{2}$).
-{\em Mathematical Operations} (\emph{R-41, R-42}; e.g. date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
-The sum of percentage values of all codes of a variable code list, e.g., must exactly be 100 ($\mathcal{SL}_{2}$)
-and the minimum of all variable codes do not have to be greater than the maximum ($\mathcal{SL}_{2}$).
-Codes (\emph{skos:Concept}) are ordered and therefore have fixed positions in an ordered collection (\emph{skos:OrderedCollection}) within variable representations.
-In order to check the correctness of relative frequencies' calculations, the cumulative percentage (\emph{disco:cumulativePercentage}) of the current code must exactly be the cumulative percentage of the previous code
-plus the percentage value (\emph{disco:percentage}) of the current code (\emph{data model consistency}; $\mathcal{SL}_{2}$).
-
-\textbf{Unique Identification.}
-It is often useful to declare a given (data) property as the \emph{primary key} (\emph{R-226}) of a class, so that a system can enforce uniqueness and also automatically build URIs from user inputs and imported data.
-In \emph{Disco}, resources are uniquely identified by the property \emph{adms:identifier},
-which is therefore inverse-functional
-$(\ms{funct identifier}\sp{\overline{\ }})$,
-i.e.
-for each \emph{rdfs:Resource x}, there can be at most one distinct \emph{rdfs:Resource y} such that \emph{y} is connected by \emph{adms:identifier$\sp{\overline{\ }}$} to \emph{x} ($\mathcal{SL}_{2}$).
-Keys, however, are even more general than inverse-functional properties (\emph{R-58}),
-as a key can be a data, an object property, or a chain of properties \cite{Schneider2009}.
-For this generalization purposes, as there are different sorts of key, and as keys can lead to undecidability, 
-DL is extended with \emph{key boxes} and a special \emph{keyfor} construct (\ms{identifier \ms{keyfor} Resource}) \cite{Lutz2005}.
-OWL 2 \emph{hasKey} implements \emph{keyfor} ($\mathcal{SL}_{2}$) and thus can be used to identify resources uniquely, to merge resources with identical key property values, and to recognize constraint violations.
-%OWL 2 hasKey can be used to identify resources uniquely
-%
-%We used Protégé 5.
-%
-%example: owl:Thing owl:hasKey ( :hasSSN ) . :Peter :hasSSN "123-45-6789" .
-%:Peter_Griffin :hasSSN "123-45-6789" .
-%
-%We use the predefined Reasoner HermiT.
-%
-%:Peter and :Peter_Griffin are derived as identical from the reasoner as they have the same value for :hasSSN.
-%
-%hasKey can be used to merge resources and to recognize constraint violations.
-%
-%Alternative to OWL 2 hasKey: concise bounded description (proposal of Dan)
-%
-%action: explore CBD document solution might be using both approaches
-%
-%benefit: additional identification to URI / IRI benefit: compound properties can be used as key
-
-\textbf{Membership in Controlled Vocabularies.}
-In many cases, resources must be members of controlled vocabularies (\emph{R-32}).
-If a dimension property, e.g., has a \emph{qb:codeList},
-then the value of the dimension property on every \emph{qb:Observation} must be in the code list ($\mathcal{SL}_{2}$).
-Summary statistics types like minimum, maximum, and arithmetic mean are maintained within a controlled vocabulary.  
-Summary statistics can only have \emph{disco:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType}, a \emph{skos:ConceptScheme} ($\mathcal{SL}_{2}$).
-
-%\begin{center}
-%\begin{DL}
-%SummaryStatistics $\sqsubseteq$ $\forall summaryStatisticType.A$ \\
-%$A \equiv Concept \sqcap \forall inScheme . B$ \\
-%$B \equiv ConceptScheme \sqcap \{SummaryStatisticType\}$
-%\end{DL}
-%\end{center}
-
-\textbf{Coverage.}
-Information about the temporal (\emph{dcterms:temporal}), the spatial (\emph{dcterms:spatial}), and the topical coverage (\emph{dcterms:subject}) of series, studies, data sets, and data files (\emph{R-86}; $\mathcal{SL}_{1}$) is of interest when performing frequently formulated queries
-	(e.g. to search for all data sets of given years (temporal coverage) in which data is collected in certain countries (spatial coverage) about particular topics (topical coverage)).
-Depending on property datatypes,
-two different literal values have
-a specific ordering with respect to an operator like \textless (\emph{R-43: literal value comparison}).
-Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}) ($\mathcal{SL}_{2}$).
-
-%\textbf{Organizations, Hierarchies, Classifications, and Ordering.}
-\textbf{Hierarchies and Ordering.}
-SKOS is based on RDF, which is a graph-based data model.
-Therefore, we can concentrate on the vocabulary's graph-based structure for assessing the quality of SKOS vocabularies and apply graph- and network-analysis techniques (\emph{structure}) like
-(1) a vocabulary should provide entry points (top concepts) to the data to provide efficient access and guidance for human users,
-(2) concepts, internal to the tree, should not be indicated as top concepts, and
-(3) a vocabulary should not contain many orphan concepts 
-(concepts without any associative or hierarchical relations) lacking valuable context information.
-A controlled vocabulary that contains many orphan concepts is less usable for search and retrieval use cases.
-%, as, e.g., no hierarchical query expansion can be performed on search terms to find documents with more general content.) \cite{MaderHaslhoferIsaac2012}. 
-Objects and literals can be \emph{ordered} (\emph{R-121, R-217}) for given properties.
-\emph{Disco }variables, questions, and codes/categories are typically organized in a particular order. 
-If a variable code list should be ordered, the variable representation should be of the type \emph{skos:OrderedCollection} containing multiple codes/categories (each represented as \emph{skos:Concept}) in a \emph{skos:memberList}.
-
-\textbf{Reusability.}
-Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes/categories), but not both ($\mathcal{SL}_{2}$).
-The constraint type \emph{context-specific exclusive or of property groups} (\emph{R-11})
-restricts individuals of given classes to have exactly one of multiple property groups.
-
-%\begin{center}
-%\begin{DL}
-%Concept $\sqsubseteq$ ($\neg$ D $\sqcap$ C) $\sqcup$ (D $\sqcap$ $\neg$ C), D $\equiv$ A $\sqcap$ B \\
-%A $\sqsubseteq$ $\geq$ 1 notation.string $\sqcap$ $\leq$ 1 notation.string \\
-%B $\sqsubseteq$ $\geq$ 1 prefLabel.string $\sqcap$ $\leq$ 1 prefLabel.string \\
-%C $\sqsubseteq$ $\geq$ 1 definition.string $\sqcap$ $\leq$ 1 definition.string \\
-%\end{DL}
-%\end{center}
-
-%\textbf{Searching for (Meta)data.}
-%
-%- DCAT
-%
-%\textbf{Data Integration.}
-%use RDF validation for data integration
-
 \subsection{Technology-Driven Constraint Types}
@@
 
-Constraints of some constraint types are directly and automatically derived from syntax and semantics of vocabularies' conceptual models.
-As these constraints depend on data models' intended semantics, associated default severity levels are in most cases very strong ($\mathcal{SL}_{2}$).
+$\mathcal{CT}_{T}$ constraints can be directly and automatically derived from explicitly stated syntax and semantics of vocabularies' data models.
+Thus, associated default severity levels are in most cases very strong ($\mathcal{SL}_{2}$).
 
@@
 
-\textbf{Cardinality Restrictions.}
-An \emph{existential quantification} (\emph{R-86}) contains all those individuals that are connected by a property to individuals/literals of given classes or data ranges.
-Every \emph{qb:SliceKey}, e.g., must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}).
+\textbf{Existential Quantifications.}
+\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals of certain types.
+If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
+If metadata on data files, including the actual data, is missing (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the study is not sufficient.
+Case quantity measures how many cases are collected for a study.
+High case and variable quantities are indicators for high statistical quality and comprehensiveness of the underlying study ($\mathcal{SL}_{1}$).
+Variables should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
+%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
+The variable \emph{Education at pre-school},.e.g, is associated with the theoretical concept \emph{Child Care}. 
+The constraint's severity level is weak, as in most cases research can be continued without having information about theoretical concepts.
+
+\textbf{Cardinality Restrictions on Properties and Language Tags.}
+%An \emph{existential quantification} (\emph{R-86}) contains all those individuals that are connected by a property to individuals/literals of given classes or data ranges.
+%Every \emph{qb:SliceKey}, e.g., must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}).
 \emph{Minimum/maximum/exact qualified cardinality restrictions} (\emph{R-74, R-75, R-76}) contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals of particular classes or data ranges.
@@
 
-\textbf{Language Tag Cardinality.}
+%\textbf{Language Tag Cardinality.}
 For data properties, it may be desirable to restrict that values of predefined languages must be present for determined number of times (\emph{R-48, R-49}):
@@
 This validation can indicate when the data is verbose (redundant) or expressed at a too general level and could thus be improved.
+
+\subsection{Content-Driven Constraint Types}
+\label{content-driven-validation}
+
+In this sub-chapter, we assign default severity levels to and describe constraints of diverse $\mathcal{CT}_{C}$ constraint types 
+to ensure that the data is consistent with the intended syntax, semantics, and integrity of vocabularies' data models.
+
+%\textbf{Observations of Aggregated Data Sets.}
+%- for each dimension there should be a description and code lists.
+%- for each code list there should be a description.
+%- there should be a relationship to the underlying person-level data.
+
+\textbf{Data Model Consistency.}
+The purpose of some constraints is to ensure the integrity of
+the data according to intended data model semantics (\emph{data model consistency}).
+Every \emph{qb:Observation}, e.g., must have a value for each dimension
+declared in its \emph{qb:DataStructureDefinition} ($\mathcal{SL}_{2}$)
+and no two \emph{qb:Observations} in the same \emph{qb:DataSet}
+can have the same value for all dimensions ($\mathcal{SL}_{1}$).
+If a \emph{qb:DataSet} \emph{D} has a \emph{qb:Slice} \emph{S}, and \emph{S} has an
+\emph{qb:Observation} \emph{O}, then the \emph{qb:DataSet} corresponding to \emph{O} must be \emph{D} ($\mathcal{SL}_{1}$).
+Relative frequencies of variable codes are calculated correctly, if the cumulative percentage (\emph{disco:cumulativePercentage}) of a given code exactly matches the cumulative percentage of the previous code
+plus the percentage value (\emph{disco:percentage}) of the current code ($\mathcal{SL}_{2}$).
+
+%\textbf{Hierarchies and Ordering.}
+\textbf{Structure and Ordering.}
+For assessing the quality of \emph{SKOS} vocabularies, we concentrate on graph-based structures and apply graph- and network-analysis techniques (\emph{structure}) like 
+(1) a thesaurus should provide entry points (top concepts) to the data to provide efficient access and guidance for human users,
+(2) concepts, internal to the tree, should not be indicated as top concepts, and
+(3) a thesaurus should not contain many orphan concepts 
+(concepts without any associative or hierarchical relations) lacking valuable context information for retrieval.
+%, as, e.g., no hierarchical query expansion can be performed on search terms to find documents with more general content.) \cite{MaderHaslhoferIsaac2012}. 
+Objects/literals can be declared to be \emph{ordered} (\emph{R-121, R-217}) for given properties.
+Variables, questions, and codes, e.g., are typically organized in a particular order. 
+If codes (\emph{skos:Concept}) should be ordered, they must be members (\emph{skos:memberList}) in an ordered collection (\emph{skos:OrderedCollection}), the variable's code list.
+
+\textbf{Comparison.}
+A very common research question is to compare variables of multiple studies or countries (\emph{comparison}).
+To compare variables, 
+(1) variables and (2) variable definitions must be present,
+(3) code lists must be structured properly,
+(4) for each code an associated category must be specified, and
+(5) code lists must either be identical or at least similar.
+If a researcher wants to get a first overview over comparable variables (use case 1), 
+covering the first three constraints may be sufficient.
+Thus, the severity level of the first three constraints is stronger ($\mathcal{SL}_{2}$) than for the last two constraints ($\mathcal{SL}_{1}$ and $\mathcal{SL}_{0}$).
+If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the remaining two constraints is getting more serious.
+
+\textbf{Unique Identification.}
+It is often useful to declare a given (data) property as the \emph{primary key} (\emph{R-226}) of a class, so that a system can enforce uniqueness and also automatically build URIs from user inputs and imported data.
+In \emph{Disco}, resources are uniquely identified by the property \emph{adms:identifier},
+which is therefore inverse-functional
+$(\ms{funct identifier}\sp{\overline{\ }})$,
+i.e.
+for each \emph{rdfs:Resource x}, there can be at most one distinct \emph{rdfs:Resource y} such that \emph{y} is connected by \emph{adms:identifier$\sp{\overline{\ }}$} to \emph{x} ($\mathcal{SL}_{2}$).
+Keys, however, are even more general than \emph{inverse-functional properties} (\emph{R-58}),
+as a key can be a data, an object property, or a chain of properties \cite{Schneider2009}.
+For this generalization purposes, as there are different sorts of key, and as keys can lead to undecidability, 
+DL is extended with \emph{key boxes} and the construct \emph{keyfor} (\ms{identifier \ms{keyfor} Resource}) \cite{Lutz2005}.
+OWL 2 \emph{hasKey} implements \emph{keyfor} ($\mathcal{SL}_{2}$) and thus can be used to identify resources uniquely, to merge resources with identical key property values, and to recognize constraint violations.
+
+\textbf{Membership in Controlled Vocabularies.}
+In many cases, resources must be \emph{members of controlled vocabularies} (\emph{R-32}).
+If a dimension property, e.g., has a \emph{qb:codeList},
+then the value of the dimension property on every \emph{qb:Observation} must be in the code list ($\mathcal{SL}_{2}$).
+Summary statistics types like minimum, maximum, and arithmetic mean are maintained within a controlled vocabulary.  
+Thus, summary statistics can only have \emph{disco:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType}, a \emph{skos:ConceptScheme} ($\mathcal{SL}_{2}$).
+
+\textbf{Constraints on Properties.}
+It is useful to declare properties to be \emph{conditional} (\emph{R-71}), i.e., if particular properties exist (or do not exist), then other properties must also be present (or absent).
+To get an overview over a series/study either an abstract, a title, an alternative title, or links to external descriptions should be provided. 
+If an abstract and an external description are absent, however,  
+a title or an alternative title should be given ($\mathcal{SL}_{1}$).
+In case a variable is represented in form of a code list, codes may be associated with categories, i.e., human-readable labels ($\mathcal{SL}_{0}$).
+The variable \emph{Education at pre-school}, e.g., is represented as ordered code list without any categories.
+If a {\em skos:Concept} represents a code (having {\em skos:notation} and {\em skos:prefLabel} properties), 
+then the property {\em disco:isValid} has to be stated indicating if the code stands for valid (\emph{true}) or missing (\emph{false}) cases ($\mathcal{SL}_{2}$).
+Constraints of type \emph{context-specific exclusive or of property groups} (\emph{R-11})
+restrict individuals of given classes to have properties defined within exactly one of multiple property groups.
+\emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes/categories), but not both ($\mathcal{SL}_{2}$).
+For datatype properties, it should be possible to declare frequently needed \emph{facets} ({\emph{R-46}) to validate input against simple conditions including min/max values, regular expressions, and string length.
+The abstract of series/studies, e.g., should have a minimum length ($\mathcal{SL}_{1}$).
+
+\textbf{Constraints on Literals.}
+\emph{disco:percentage} stands for the number of cases of a given code in relation to the total number of cases for a particular variable.
+Percentage values are only valid when they are within the \emph{literal range} of 0 and 100 (\emph{R-45}; $\mathcal{SL}_{2}$).
+{\em Mathematical Operations} (\emph{R-41, R-42}; e.g. date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
+The sum of percentage values of all variable codes, e.g., must exactly be 100 ($\mathcal{SL}_{2}$)
+and the minimum absolute frequency of all variable codes do not have to be greater than the maximum ($\mathcal{SL}_{2}$).
+Depending on property datatypes, two different literal values have
+a specific ordering with respect to an operator like \textless (\emph{R-43: literal value comparison}).
+Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}) ($\mathcal{SL}_{2}$).
+
+%\begin{center}
+%\begin{DL}
+%Concept $\sqsubseteq$ ($\neg$ D $\sqcap$ C) $\sqcup$ (D $\sqcap$ $\neg$ C), D $\equiv$ A $\sqcap$ B \\
+%A $\sqsubseteq$ $\geq$ 1 notation.string $\sqcap$ $\leq$ 1 notation.string \\
+%B $\sqsubseteq$ $\geq$ 1 prefLabel.string $\sqcap$ $\leq$ 1 prefLabel.string \\
+%C $\sqsubseteq$ $\geq$ 1 definition.string $\sqcap$ $\leq$ 1 definition.string \\
+%\end{DL}
+%\end{center}
+
+%\textbf{Searching for (Meta)data.}
+%
+%- DCAT
+%
+%\textbf{Data Integration.}
+%use RDF validation for data integration
+
+%\textbf{Series, Studies, Data Sets, and Data Files.}
+%It is useful to declare properties to be \emph{conditional} (\emph{R-71}), i.e., if particular properties exist (or do not exist), then other properties must also be present (or absent).
+%To get an overview over a series/study either an abstract, a title, an alternative title, or links to external descriptions should be provided. 
+%If an abstract and an external description are absent, however,  
+%a title or an alternative title should be given ($\mathcal{SL}_{1}$).
+%For datatype properties, it should be possible to declare frequently needed \emph{facets} ({\emph{R-46}) to validate input against simple conditions including min/max values, regular expressions, and string length.
+%The abstract of series/studies, e.g., should have a minimum length ($\mathcal{SL}_{1}$).
+%\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals of certain types.
+%If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
+%If metadata on data files, including the actual data, is missing (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the study is not sufficient.
+%Case quantity measures how many cases are collected for a study.
+%High case and variable quantities are indicators for high statistical quality and comprehensiveness of the underlying study ($\mathcal{SL}_{1}$).
+%
+%\textbf{Variables and Variable Comparison.}
+%Variables should be represented (\emph{R-86}; $\mathcal{SL}_{1}$) either as (un)ordered code lists or as unions of datatypes.
+%In case of a code list, associated categories (human-readable labels) may be stated (\emph{R-71}; $\mathcal{SL}_{0}$).
+%The variable \emph{Education at pre-school}, e.g., is represented as ordered code list without any categories.
+%If a {\em skos:Concept} represents a code (having {\em skos:notation} and {\em skos:prefLabel} properties), 
+%then the property {\em disco:isValid} has to be stated indicating if the code stands for valid (\emph{true}) or missing (\emph{false}) cases (\emph{R-71}; $\mathcal{SL}_{2}$).
+%Variables may have at least one relationship to a theoretical concept ({\emph{R-86}; $\mathcal{SL}_{0}$).
+%%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
+%The variable \emph{Education at pre-school},.e.g, is associated with the theoretical concept \emph{Child Care}. 
+%The default severity level of this constraint is weak, as in most cases research can be continued without associated theoretical concepts.
+%A very common research question is to compare variables of multiple studies or countries (\emph{comparison}).
+%To compare variables, 
+%(1) variables and (2) variable definitions must be present,
+%(3) code lists must be structured properly,
+%(4) for each code an associated category (human-readable label) must be specified, and
+%(5) code lists must either be identical or at least similar.
+%If a researcher wants to get a first overview over comparable variables (use case 1), 
+%covering the first three constraints may be sufficient for this purpose.
+%Thus, the severity level of the first three constraints is stronger ($\mathcal{SL}_{2}$) than the severity level of the next two constraints ($\mathcal{SL}_{1}$ and $\mathcal{SL}_{0}$).
+%If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the remaining two constraints is getting more serious.
+%
+%\textbf{Descriptive Statistics.}
+%The property \emph{disco:percentage} stands for the number of cases of a given code in relation to the total number of cases for a particular variable within a data set.
+%Percentage values are only valid when they are within the \emph{literal range} of 0 and 100 (\emph{R-45}; $\mathcal{SL}_{2}$).
+%{\em Mathematical Operations} (\emph{R-41, R-42}; e.g. date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
+%The sum of percentage values of all codes of a variable code list, e.g., must exactly be 100 ($\mathcal{SL}_{2}$)
+%and the minimum of all variable codes do not have to be greater than the maximum ($\mathcal{SL}_{2}$).
+%Codes (\emph{skos:Concept}) are ordered and therefore have fixed positions in an ordered collection (\emph{skos:OrderedCollection}) within variable representations.
+%In order to check the correctness of relative frequencies' calculations, the cumulative percentage (\emph{disco:cumulativePercentage}) of the current code must exactly be the cumulative percentage of the previous code
+%plus the percentage value (\emph{disco:percentage}) of the current code (\emph{data model consistency}; $\mathcal{SL}_{2}$).
+%
+%\textbf{Unique Identification.}
+%It is often useful to declare a given (data) property as the \emph{primary key} (\emph{R-226}) of a class, so that a system can enforce uniqueness and also automatically build URIs from user inputs and imported data.
+%In \emph{Disco}, resources are uniquely identified by the property \emph{adms:identifier},
+%which is therefore inverse-functional
+%$(\ms{funct identifier}\sp{\overline{\ }})$,
+%i.e.
+for each \emph{rdfs:Resource x}, there can be at most one distinct \emph{rdfs:Resource y} such that \emph{y} is connected by \emph{adms:identifier$\sp{\overline{\ }}$} to \emph{x} ($\mathcal{SL}_{2}$).
+%Keys, however, are even more general than inverse-functional properties (\emph{R-58}),
+%as a key can be a data, an object property, or a chain of properties \cite{Schneider2009}.
+%For this generalization purposes, as there are different sorts of key, and as keys can lead to undecidability, 
+%DL is extended with \emph{key boxes} and a special \emph{keyfor} construct (\ms{identifier \ms{keyfor} Resource}) \cite{Lutz2005}.
+%OWL 2 \emph{hasKey} implements \emph{keyfor} ($\mathcal{SL}_{2}$) and thus can be used to identify resources uniquely, to merge resources with identical key property values, and to recognize constraint violations.
+%%OWL 2 hasKey can be used to identify resources uniquely
+%%
+%%We used Protégé 5.
+%%
+%%example: owl:Thing owl:hasKey ( :hasSSN ) . :Peter :hasSSN "123-45-6789" .
+%%:Peter_Griffin :hasSSN "123-45-6789" .
+%%
+%%We use the predefined Reasoner HermiT.
+%%
+%%:Peter and :Peter_Griffin are derived as identical from the reasoner as they have the same value for :hasSSN.
+%%
+%%hasKey can be used to merge resources and to recognize constraint violations.
+%%
+%%Alternative to OWL 2 hasKey: concise bounded description (proposal of Dan)
+%%
+%%action: explore CBD document solution might be using both approaches
+%%
+%%benefit: additional identification to URI / IRI benefit: compound properties can be used as key
+%
+%
+%\textbf{Membership in Controlled Vocabularies.}
+%In many cases, resources must be members of controlled vocabularies (\emph{R-32}).
+%If a dimension property, e.g., has a \emph{qb:codeList},
+%then the value of the dimension property on every \emph{qb:Observation} must be in the code list ($\mathcal{SL}_{2}$).
+%Summary statistics types like minimum, maximum, and arithmetic mean are maintained within a controlled vocabulary.  
+%Summary statistics can only have \emph{disco:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType}, a \emph{skos:ConceptScheme} ($\mathcal{SL}_{2}$).
+%
+%%\begin{center}
+%%\begin{DL}
+%%SummaryStatistics $\sqsubseteq$ $\forall summaryStatisticType.A$ \\
+%%$A \equiv Concept \sqcap \forall inScheme . B$ \\
+%%$B \equiv ConceptScheme \sqcap \{SummaryStatisticType\}$
+%%\end{DL}
+%%\end{center}
+%
+%\textbf{Coverage.}
+%Information about the temporal (\emph{dcterms:temporal}), the spatial (\emph{dcterms:spatial}), and the topical coverage (\emph{dcterms:subject}) of series, studies, data sets, and data files (\emph{R-86}; $\mathcal{SL}_{1}$) is of interest when performing frequently formulated queries
+	%(e.g. to search for all data sets of given years (temporal coverage) in which data is collected in certain countries (spatial coverage) about particular topics (topical coverage)).
+%Depending on property datatypes,
+%two different literal values have
+%a specific ordering with respect to an operator like \textless (\emph{R-43: literal value comparison}).
+%Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}) ($\mathcal{SL}_{2}$).
+%
+%%\textbf{Organizations, Hierarchies, Classifications, and Ordering.}
+%\textbf{Hierarchies and Ordering.}
+%SKOS is based on RDF, which is a graph-based data model.
+Therefore, we can concentrate on the vocabulary's graph-based structure for assessing the quality of SKOS vocabularies and apply graph- and network-analysis techniques (\emph{structure}) like
+%(1) a vocabulary should provide entry points (top concepts) to the data to provide efficient access and guidance for human users,
+%(2) concepts, internal to the tree, should not be indicated as top concepts, and
+%(3) a vocabulary should not contain many orphan concepts 
+%(concepts without any associative or hierarchical relations) lacking valuable context information.
+A controlled vocabulary that contains many orphan concepts is less usable for search and retrieval use cases.
+%%, as, e.g., no hierarchical query expansion can be performed on search terms to find documents with more general content.) \cite{MaderHaslhoferIsaac2012}. 
+%Objects and literals can be \emph{ordered} (\emph{R-121, R-217}) for given properties.
+%\emph{Disco }variables, questions, and codes/categories are typically organized in a particular order. 
+%If a variable code list should be ordered, the variable representation should be of the type \emph{skos:OrderedCollection} containing multiple codes/categories (each represented as \emph{skos:Concept}) in a \emph{skos:memberList}.
+%
+%\textbf{Reusability.}
+%Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes/categories), but not both ($\mathcal{SL}_{2}$).
+%The constraint type \emph{context-specific exclusive or of property groups} (\emph{R-11})
+%restricts individuals of given classes to have exactly one of multiple property groups.
 

### 2015-04-19 paper/paper7/paper7.tex
content-driven constraint types

@@
 a SPARQL-based way to formulate and check constraints, as basis to develop a
-validation environment (available at \url{http://purl.org/net/rdfval-demo})\footnote{Source code downloadable at: \textcolor{red}{\url{https://github.com/boschthomas/rdf-validator}}} to validate RDF data according to constraints expressed my arbitrary constraint languages like Shape Expressions,
+validation environment (available at \url{http://purl.org/net/rdfval-demo})\footnote{Source code downloadable at: \url{https://github.com/boschthomas/rdf-validator}} to validate RDF data according to constraints expressed my arbitrary constraint languages like Shape Expressions,
 %\footnote{\url{http://www.w3.org/Submission/shex-primer/}}
-Resource Shapes, and the Web Ontology Language\footnote{\textcolor{red}{SPIN mappings available at: \url{https://github.com/boschthomas/rdf-validation/SPIN}}} \cite{BoschEckert2014-2}.
+Resource Shapes, and the Web Ontology Language\footnote{SPIN mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} \cite{BoschEckert2014-2}.
 The \emph{RDF Validator} also validates RDF data to ensure correct syntax, semantics, and integrity of diverse vocabularies such as \emph{Disco, QB, PHDD, SKOS, and XKOS}.

### 2015-04-20 paper/paper7/paper7.tex
arxiv articles cited

@@
 
-We recently published a technical report\footnote{\textcolor{red}{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as first appendix of this paper) in which we describe 212 constraints (classified as 53 constraint types) to validate rectangular data (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}), and therefore apply the proposed classification system to several vocabularies to represent both data and metadata \cite{BoschZapilkoWackerowEckert2015}.
+We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as first appendix of this paper) in which we describe 212 constraints (classified as 53 constraint types) to validate rectangular data (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}), and therefore apply the proposed classification system to several vocabularies to represent both data and metadata \cite{BoschZapilkoWackerowEckert2015}.
 In this section, we describe constraints, which are important to ensure \emph{SBE} (meta)data quality, 
@@
 
-We recently published a technical report\footnote{\label{technical-report-2}\textcolor{red}{Available at: \url{http://arxiv.org/abs/XXXXX}}} (serving as second appendix of this paper) 
+We recently published a technical report\footnote{\label{technical-report-2}Available at: \url{http://arxiv.org/abs/1504.04478}} (serving as second appendix of this paper) 
 in which we describe the comprehensive evaluation in detail \cite{BoschZapilkoWackerowEckert2015-2}. 
@@
 In this paper, we showed in form of a complete real world running example how to represent metadata on person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
-We explained why RDF validation is important in this context and how metadata on person-level data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality\footnote{The first appendix of this paper describing each constraint in detail is available at: \textcolor{red}{\url{http://arxiv.org/abs/XXXXX}} \cite{BoschZapilkoWackerowEckert2015}} (\textbf{contribution 2}, section \ref{rdf-validation}).
+We explained why RDF validation is important in this context and how metadata on person-level data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality\footnote{The first appendix of this paper describing each constraint in detail is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}} (\textbf{contribution 2}, section \ref{rdf-validation}).
 We distinguish two validation types:
@@
 We exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets by means of 212 $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
-We validated more than 4.2 billion triples and 15 thousand data sets\footnote{The second appendix of this paper describing the evaluation in detail is available at: \textcolor{red}{\url{http://arxiv.org/abs/XXXXX}} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).
+We validated more than 4.2 billion triples and 15 thousand data sets\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).
 

### 2015-04-20 paper/paper7/paper7.tex
technology-driven constraint types

@@
 
+%\textbf{Constraints Derived From Vocabularies.}
 \textbf{Vocabulary.}
-One should not invent new or use deprecated terms of vocabularies (\emph{vocabulary}).
-\emph{Property Domains} (\emph{R-25, R-26}) and \emph{Ranges} (\emph{R-28, R-35}) restrict domains and ranges of properties.
+One should not invent new or use deprecated terms (e.g. \emph{disco:containsVariable}) of vocabularies (\emph{vocabulary}).
+\emph{Property domain} (\emph{R-25, R-26}) and \emph{range} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties.
 Only \emph{phdd:Tables}, e.g., can have \emph{phdd:isStructuredBy} relationships (\ms{$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table}) and
-\emph{xkos:belongsTo} relationships can only point to \emph{skos:Concept} instances (\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}).
+\emph{xkos:belongsTo} relationships can only point to \emph{skos:Concepts} (\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}).
 A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
@@
 Out-dated classes and properties of previous vocabulary versions can be marked as deprecated.
-The constraint type \emph{context-specific valid classes and properties} (\emph{R-209; R-210}) can be used to specify which classes and properties are valid in which context - here a given vocabulary version.
+The constraint types \emph{context-specific valid classes and properties} (\emph{R-209; R-210}) can be used to specify which classes and properties are valid in which context - here a given vocabulary version.
 Many properties are not necessarily required but \emph{recommended} within a particular context (\emph{R-72}).
@@
 \textbf{Existential Quantifications.}
-\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals of certain types.
+\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals/literals of certain types.
 If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
@@
 \emph{Minimum/maximum/exact qualified cardinality restrictions} (\emph{R-74, R-75, R-76}) contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals of particular classes or data ranges.
-A \emph{phdd:TableStructure}, e.g., has at least one \emph{phdd:column} relationship to a \emph{phdd:Column} (\ms{TableStructure $\sqsubseteq$ $\geq$1 column.Column}),
-a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}) (\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}), and a \emph{qb:DataSet} has (\emph{qb:structure}) exactly one associated \emph{qb:DataStructureDefinition} (\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition $\sqcap$ $\leq$1 structure.DataStructureDefinition}).
-
+A \emph{phdd:TableStructure}, e.g., has (\emph{phdd:column}) at least one \emph{phdd:Column} (\ms{TableStructure $\sqsubseteq$ $\geq$1 column.Column}),
+a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}) (\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}), and a \emph{qb:DataSet} is structured by (\emph{qb:structure}) exactly one \emph{qb:DataStructureDefinition} (\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition $\sqcap$ $\leq$1 structure.DataStructureDefinition}).
 %DATA-CUBE-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-
@@
 %(\emph{R-74: exact qualified cardinality restrictions})
-
 %\footnote{\emph{DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02}}.
-
 %\textbf{Language Tag Cardinality.}
@@
 Some constraint types enable performing reasoning prior to validation which may resolve or cause constraint violations.
-With \emph{subsumption} (\emph{R-100}) one can state that \emph{xkos:ClassificationLevel} is a sub-class of \emph{skos:Collection}, i.e., each \emph{xkos:ClassificationLevel} resource must also be part of the \emph{skos:Collection} class extension (\ms{xkos:ClassificationLevel $\sqsubseteq$ skos:Collection}).
-With \emph{sub properties} (\emph{R-54, R-64}) one can state that \emph{disco:fundedBy} is a sub-property of \emph{dcterms:contributor} - i.e., if a study is funded by an organization, then this organization contributed to this study (\ms{disco:fundedBy $\sqsubseteq$ dcterms:contributor}).
+With \emph{subsumption} (\emph{R-100}) one can state that \emph{xkos:ClassificationLevel} is a sub-class of \emph{skos:Collection}, i.e., each \emph{xkos:ClassificationLevel} resource must also be part of the \emph{skos:Collection} class extension (\ms{ClassificationLevel $\sqsubseteq$ Collection}).
+With \emph{sub properties} (\emph{R-54, R-64}) one can state that \emph{disco:fundedBy} is a sub-property of \emph{dcterms:contributor} - i.e., if a study is funded by an organization, then this organization contributed to this study (\ms{fundedBy $\sqsubseteq$ contributor}).
 \emph{Asymmetric object properties} (\emph{R-62}) restrict that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}.

### 2015-04-20 paper/paper7/paper7.tex
technology-driven constraint types

@@
 \textbf{Disjointness and Allowed Values.}
-All properties, not having the same domain and range classes, are defined to be pairwise disjoint
-(\emph{R-9: disjoint properties}), stating that no individual \emph{x} can be connected to an individual/literal \emph{y} by disjoint properties like \emph{phdd:isStructuredBy} and \emph{phdd:column} ($isStructuredBy \sqsubseteq \neg column$).
+All properties, not having the same domain and range types, are defined to be pairwise disjoint
+(\emph{R-9: disjoint properties}), i.e., no individual \emph{x} can be connected to an individual/literal \emph{y} by disjoint properties like \emph{phdd:isStructuredBy} and \emph{phdd:column} ($isStructuredBy \sqsubseteq \neg column$).
 All \emph{XKOS} classes are pairwise disjoint (\emph{R-7: disjoint classes}; e.g. \ms{ClassificationLevel $\sqcap$ ConceptAssociation $\sqsubseteq$ $\perp$}),
@@
 'red' 'blue' 'green'), and typed literals of one or multiple type(s) (e.g.
-\emph{xsd:string}) -
+\emph{xsd:string}).
 \emph{disco:CategoryStatistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString} (\ms{CategoryStatistics $\equiv$ $\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString}).
@@
 Some constraint types enable performing reasoning prior to validation which may resolve or cause constraint violations.
-With \emph{subsumption} (\emph{R-100}) one can state that \emph{xkos:ClassificationLevel} is a sub-class of \emph{skos:Collection}, i.e., each \emph{xkos:ClassificationLevel} resource must also be part of the \emph{skos:Collection} class extension (\ms{ClassificationLevel $\sqsubseteq$ Collection}).
-With \emph{sub properties} (\emph{R-54, R-64}) one can state that \emph{disco:fundedBy} is a sub-property of \emph{dcterms:contributor} - i.e., if a study is funded by an organization, then this organization contributed to this study (\ms{fundedBy $\sqsubseteq$ contributor}).
-\emph{Asymmetric object properties} (\emph{R-62}) restrict that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}.
-Such constraints are defined for each object property for which a semantically equivalent object property pointing from the other direction would also be possible but is not defined within the vocabulary.
-A \emph{disco:Variable}, e.g., may be based on (\emph{disco:basedOn}) a \emph{disco:RepresentedVariable}.
-A \emph{disco:RepresentedVariable}, however, cannot be based on a \emph{disco:Variable} (\ms{$disco:basedOn \sqcap disco:basedOn^{-} \sqsubseteq \bot$}).
-\emph{Default values} (\emph{R-31, R-38}) for objects/literals of given prooperties are inferred automatically when properties are not present.
+With \emph{subsumption} (\emph{R-100}), one can state that \emph{xkos:ClassificationLevel} is a sub-class of \emph{skos:Collection}, i.e., each \emph{xkos:ClassificationLevel} must also be part of the \emph{skos:Collection} class extension (\ms{ClassificationLevel $\sqsubseteq$ Collection}).
+With \emph{sub properties} (\emph{R-54, R-64}), one can state that \emph{disco:fundedBy} is a sub-property of \emph{dcterms:contributor} - i.e., if a study is funded by an organization, then this organization contributed to this study (\ms{fundedBy $\sqsubseteq$ contributor}).
+%\emph{Asymmetric object properties} (\emph{R-62}) restrict that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}.
+%Such constraints are defined for each object property for which a semantically equivalent object property pointing from the other direction would also be possible but is not defined within the vocabulary.
+%A \emph{disco:Variable}, e.g., may be based on (\emph{disco:basedOn}) a \emph{disco:RepresentedVariable}.
+%A \emph{disco:RepresentedVariable}, however, cannot be based on a \emph{disco:Variable} (\ms{$disco:basedOn \sqcap disco:basedOn^{-} \sqsubseteq \bot$}).
+\emph{Default values} (\emph{R-31, R-38}) for objects/literals of given properties are inferred automatically when properties are not present in the data.
 The value \emph{true} for the property {\em disco:isPublic} indicates that a {\em disco:LogicalDataSet} can be accessed by anyone.
@@
 These findings are surprising as only 8\% of all defined constraints are $\mathcal{SL}_{1}$ constraints.
-The constraints responsible for the largest numbers of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916) (\emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102) (\emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903) (\emph{SKOS})\tb{kurz beschreiben}.
+The constraints responsible for the largest numbers of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916) (\emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102) (\emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903) (\emph{SKOS}).
 We refer to the technical reports\footnotemark[\ref{technical-report-1}] \footnotemark[\ref{technical-report-2}] to get details about constraints on and the evaluation of \emph{XKOS} and \emph{PHDD} data sets.

### 2015-04-20 paper/paper 2/paper 2.tex
abstract introduction and motivation of paper 2

@@
 XML Schema is the standard constraint language to formulate constraints on and to validate XML documents.
-For RDF, however, there are more than 10 candidates for languages to express constraints on RDF data - but no standard one meeting the majority of RDF validation use cases.
-We identified requirements to formulate constraints and to validate RDF data and mapped each requirement to a constraint type.
+For RDF, however, there are several candidates for languages to express constraints on RDF data - but no standard one meeting the majority of RDF validation use cases.
+We identified requirements to formulate constraints and to validate RDF data and mapped each requirement to an RDF constraint type.
 The majority of these constraint types can be represented in description logics providing their logical underpinning.
 
-In this paper, we provide a basic terminology and classification system for RDF constraints.
-We developed a vocabulary describing any RDF constraint type generically. 
-%(whether expressible in description logics or not).
-We show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and why these transformations are useful.
-We explain how to overcome the necessity to implement the validation of each constraint type (for multiple constraint languages) by providing mappings to generically expressed constraints.
+%In this paper, we provide a basic terminology and classification system for RDF constraints.\tb{The contributions of this paper are the following. (1)...}
+%We developed a vocabulary to describe constraints of any RDF constraint type generically. 
+%%(whether expressible in description logics or not).
+%We show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful.
+%We explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages by providing mappings to generically expressed constraints.
+
+The \textbf{contributions} of this paper are:
+(1) we provide a basic terminology and classification system for RDF constraints,
+(2) we developed a vocabulary to describe constraints of any constraint type generically,
+(3) we show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful, and
+(4) we explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages.
 
@@
 \section{Introduction}
-\tb{split introdution and motivation}
-\tb{feedback from Erman: the major problem is semantics. OWL basically work in different semantics than others. And their semantics are formal. Closed world vs. Open World is also a part of this.}
+\tb{feedback: the major problem is semantics. OWL basically work in different semantics than others. And their semantics are formal. Closed world vs. Open World is also a part of this.}
 %The purpose of OWL 2 ontologies is to perform reasoning on RDF data and not to validate RDF data conforming to these ontologies.
@@
 In 2013, the W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
-where experts from industry, government, and academia discussed first use cases for RDF constraint formulation and RDF data validation.
+where experts from industry, government, and academia discussed first use cases for RDF constraint\footnote{\textcolor{red}{For simplicity reasons, we use the terms \emph{constraint types/constraints} instead of \emph{RDF constraint types/RDF constraints} in the rest of the paper}} formulation and RDF data validation.
 In 2014, two working groups on RDF validation have been established to develop a language to express constraints on RDF data: 
@@
 
-There is not one language meeting nearly all or even the majority of requirements to formulate RDF constraints.
-As there are more than 10 languages with different syntaxes and semantics which can be used to express RDF constraints, 
+There is not the one language meeting the majority of requirements to formulate constraints.
+As there are more than 10 candidate languages with different syntaxes and semantics which can be used to express constraints, 
 %(e.g. existential and universal quantification, cardinality restrictions, and exclusive or of properties)
@@
 %min car more powerful than req. propery
-The idea behind this paper is to achieve complete RDF validation requirements coverage by representing any constraint type (corresponding to a requirement to formulate RDF constraints) in a generic way using a lightweight vocabulary consisting of only a few terms (see section \ref{sec:vocabulary}).
+The idea behind this paper is to achieve complete RDF validation requirements coverage by representing any constraint type (corresponding to a requirement to formulate constraints) in a generic way using a lightweight vocabulary consisting of only a few terms (see section \ref{sec:vocabulary}).
 
@@
 %and extensions  
-or specifically (\textbf{\emph{specific constraints}}) by domain-specific constraint languages such as OWL 2, DSP, ShEx, ReSh, and SPIN.
+or specifically (\textbf{\emph{specific constraints}}) by domain-specific constraint languages such as \emph{OWL 2}, \emph{DSP}, \emph{ShEx}, \emph{ReSh}, and \emph{SPIN}.
 The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
-For that reason, we map constraint types to DL statements.
-With \emph{minimum qualified cardinality restrictions}, researchers from the library domain may state
+For that reason, we map constraint types to \emph{DL} statements.
+With \emph{minimum qualified cardinality restrictions}, researchers from the library domain may restrict
 that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
-This constraint can be represented generically (\emph{generic constraint}) using DL (\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}), but also specifically (\emph{specific constraint}) by multiple constraint languages like OWL 2, ShEx, ReSh, or DSP:
+This constraint can be represented generically (\emph{generic constraint}) using \emph{DL} (\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}), but also specifically (\emph{specific constraint}) by multiple constraint languages:
 
@@
 Constraint violations are raised either if
-\emph{The-Lord-Of-The-Rings} does not have an \emph{author} relationship, or if 
+\emph{The-Lord-Of-The-Rings} does not have any \emph{author} relationship, or if 
 \emph{The-Lord-Of-The-Rings} has an \emph{author} which is not a \emph{person}
@@
 
-As there is no standard way to formulate RDF constraints, 
+As there is no standard way to formulate constraints, 
 semantically equivalent \emph{cardinality restrictions} may be represented by multiple constraint languages with different syntax and semantics.
@@
 We provide a validation environment (available at \url{http://purl.org/net/rdfval-demo}) which enables to validate RDF data according to constraints expressed by diverse  constraint languages.
-The next step, however, is to extend the \textbf{\emph{RDF Validator}} by validating any constraint type represented by any constraint language and 
+The next step, however, is to extend the \textbf{\emph{RDF Validator}} by validating constraints of any constraint type represented by any constraint language and 
 to validate semantically equivalent \emph{specific constraints}, expressed by different constraint languages, in exactly the same way, 
@@
 This paper aims to address two main \textbf{audiences}:
-(1) RDF data providers and consumers seeking how to ensure high quality (meta)data and thus for ways to enhance the interoperability and common understanding of RDF constraints expressible by multiple constraint languages and
+(1) RDF data providers and consumers seeking how to ensure high quality (meta)data and thus for ways to enhance the interoperability and common understanding of constraints expressible by multiple constraint languages and
 (2) RDF practitioners thinking of how to provide aligned implementations for the validation of both existing an newly developed constraint languages.
@@
 (1) we provide a basic terminology and classification system for RDF constraints (section \ref{sec:vocabulary}),
-(2) we developed a vocabulary describing any RDF constraint type generically (section \ref{sec:vocabulary}),
-(3) we show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and why these transformations are useful (section \label{ref:transformations}), and
+(2) we developed a vocabulary to describe constraints of any RDF constraint type generically (section \ref{sec:vocabulary}),
+(3) we show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful (section \label{ref:transformations}), and
 (4) we explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages (section \ref{sec:validation}).

### 2015-04-20 paper/paper 2/paper 2.tex
RDF-CV

@@
 In 2013, the W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
-where experts from industry, government, and academia discussed first use cases for RDF constraint\footnote{\textcolor{red}{For simplicity reasons, we use the terms \emph{constraint types/constraints} instead of \emph{RDF constraint types/RDF constraints} in the rest of the paper}} formulation and RDF data validation.
+where experts from industry, government, and academia discussed first use cases for RDF constraint\footnote{For simplicity reasons, we use the terms \emph{constraint types/constraints} instead of \emph{RDF constraint types/RDF constraints} in the rest of the paper} formulation and RDF data validation.
 In 2014, two working groups on RDF validation have been established to develop a language to express constraints on RDF data: 
@@
 The intention is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
-The requirements are classified to better evaluate existing solutions and each requirement is directly mapped to a constraint type which may be expressed by at least one existing constraint language.
+Bosch et al.
+identified 74 requirements to formulate constraints; each of them corresponding to a constraint type which may be expressed by at least one existing constraint language \cite{BoschNolleAcarEckert2015}.
 
@@
 For that reason, we map constraint types to \emph{DL} statements.
-With \emph{minimum qualified cardinality restrictions}, researchers from the library domain may restrict
+With \emph{minimum qualified cardinality restrictions} (\emph{R-75, R-81})\footnote{Requirements/constraint types are uniquely identified by alphanumeric technical identifiers like \emph{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}}, researchers from the library domain may restrict
 that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
@@
 This causes confusion and weakens the common understanding between several parties about the semantics of particular constraints and therefore how to ensure high data quality. 
-Thus, when choosing constraint language \ms{$\alpha$} to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a semantically equivalent constraint formulated by any other constraint language \ms{$\beta$} (see section \ref{sec:transformations}).
+Thus, when choosing constraint language \ms{$\alpha$} to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a semantically equivalent \tb{Erman thinks formal generic semantics should be defined} constraint formulated by any other constraint language \ms{$\beta$} (see section \ref{sec:transformations}).
 This is important in order to enhance the interoperability of constraint languages and to resolve ambiguities in the communication of RDF data producers and consumers, 
@@
 
-In order to develop a vocabulary to describe any RDF constraint generically, it is needed to define the terminology for the formulation of RDF constraints and to classify them. 
+In order to develop a vocabulary to describe constraints of any constraint type generically, it is needed to define the basic terminology for the formulation of constraints and to classify them first.
 A \textbf{\emph{constraint language}} is a language which is used to formulate constraints.
 The W3C Data Shapes working group defines \textbf{\emph{RDF constraint}} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
-We identified four dimensions to classify RDF constraints:
+We identified four dimensions to classify constraints:
 \begin{itemize}
@@
 As there are already five promising constraint languages, our purpose is not to invent a new constraint language.
-We rather developed a very simple vocabulary (only three classes, three object properties, and three data properties) which is universal enough to describe any RDF constraint\footnote{Bosch et al.
-identified in total 74 requirements to formulate RDF constraints; each of them corresponds to a constraint type \cite{BoschNolleAcarEckert2015}} expressible by any constraint language (see the conceptual model in figure \ref{fig:RDF-CV-conceptual-model}).
+We rather developed a very simple lightweight vocabulary (only three classes, three object properties, and three data properties) which is universal enough to describe constraints of any constraint type expressible by any constraint language (see the conceptual model in figure \ref{fig:RDF-CV-conceptual-model}).
 We call this vocabulary the \textbf{\emph{RDF Constraints Vocabulary (RDF-CV)}}\footnote{Available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.
-\tb{make entry in LOV?}
+
 \begin{figure}
@@
 
-The \emph{RDF-CV} represents \textbf{\emph{generic constraints}} and \textbf{\emph{specific constraints}} are expressed by specific constraint languages.
-As the RDF-CV describes constraints generically, the \emph{RDF-CV} does not distinguish constraints according to the dimension \emph{universality}. 
-The majority of constraints can be expressed in DL.
-In contrast, there are constraints which cannot be expressed in DL, but are also representable by the \emph{RDF-CV} (see section \ref{sec:evaluation}). 
+Constraints can be expressed either generically (\textbf{\emph{generic constraints}}) by the \emph{RDF-CV}   
+or specifically (\textbf{\emph{specific constraints}}) by domain-specific constraint languages.
+As the \emph{RDF-CV} describes constraints generically, the vocabulary does not distinguish constraints according to the dimension \emph{universality}. 
+The majority of the constraint types can be expressed in \emph{DL}.
+In contrast, there are constraint types which cannot be expressed in \emph{DL}, but are also representable by the \emph{RDF-CV} (see section \ref{sec:evaluation}). 
 \textbf{\emph{Complex constraints}} encompass \textbf{\emph{simple constraints}} (atomic constraints) and/or further \emph{complex constraints},
-i.e. DL statements representing \emph{complex constraints} are created out of DL statements standing for composed constraints (if expressible in DL). 
+i.e. \emph{DL} statements representing \emph{complex constraints} are created out of \emph{DL} statements standing for atomic and composed constraints (if expressible in \emph{DL}). 
 Simple constraints may be applied to either properties (\textbf{\emph{property constraints}}) or classes (\textbf{\emph{class constraints}}).
-There are no terms standing for \emph{simple} and \emph{complex constraints} in the \emph{RDF-CV}, since \emph{context classes} of \emph{simple constraints} may just be reused within further \emph{complex constraints} (\emph{simple constraints} associated with \emph{context classes} must hold for individuals of these \emph{context classes}).
-As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to describe all possible RDF constraint types.
+The \emph{RDF-CV} does not contain any terms standing for \emph{simple} and \emph{complex constraints}, since \emph{context classes} of \emph{simple constraints} are just reused within \emph{complex constraints} (\emph{simple constraints} associated with \emph{context classes} must hold for individuals of these \emph{context classes}).
+As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to describe constraints of all possible constraint types.
 

### 2015-04-20 paper/paper 2/paper 2.tex
simple constraints

@@
 
-\subsection{Simple Constraints (Expressible in DL)}
+\subsection{\emph{Simple Constraints} (Expressible in \emph{DL})}
 
@@
 For both \emph{property} and \emph{class constraints} a \emph{context class}, a list of \emph{classes}, the \emph{constraining element}, and the \emph{constraining value} can be stated. 
-Lists of \emph{left} and \emph{right properties} can only be stated for \emph{property constraints}.
+Lists of \emph{left} and \emph{right properties} can only be specified for \emph{property constraints}.
 
@@
 
-A constraint holds for all individuals of a \emph{context class} (\textbf{\emph{contextClass}}).
-Consider, e.g., the following minimum qualified cardinality restriction on the object property \emph{author}, which restricts \emph{publications} to have at least one \emph{author} which is a \emph{person}:
+A \emph{simple constraint} holds for all individuals of a \textbf{\emph{context class}}.
+Consider, e.g., the following \emph{minimum qualified cardinality restriction} on the object property \emph{author}, which restricts \emph{publications} to have at least one \emph{author} which is a \emph{person}:
 \begin{DL}
@@
 \end{DL}
-Mapped to the \emph{RDF-CV} (see table \ref{tab:property-constraint-cardinality-restriction}), the cardinality restriction is classified as a \emph{property constraint} which holds for all individuals of the class \emph{Publication}:
+The cardinality restriction is a constraint on the property \emph{author} and is therefore classified as a \emph{property constraint} which holds for all individuals of the class \emph{Publication} (see table \ref{tab:property-constraint-cardinality-restriction} for the mapping to \emph{RDF-CV}):
 
@@
 
-The \emph{constraining element} (\textbf{\emph{constrainingElement}}) indicates the actual type of constraint like DL concept and role constructors, (in)equality, and further keywords for constraint types which cannot be expressed in DL (e.g.
+The \textbf{\emph{constraining element}} indicates the actual type of constraint like \emph{DL} concept and role constructors, (in)equality, and further keywords for constraint types which cannot be expressed in \emph{DL} (e.g.
 regular expressions and constraining facets).
-In some cases, a constraint is only complete when in addition to the \emph{constraining element} a \emph{constraining value} (\textbf{\emph{constrainingValue}}) is stated.
+In some cases, a constraint is only complete when in addition to the \emph{constraining element} a \textbf{\emph{constraining value}} is stated.
 The cardinality restriction 
@@
 constructs an anonymous class of all individuals having at least one \emph{author} relationship to \emph{persons}.
-The \emph{constraining element} of this \emph{property constraint} is the DL at-least restriction \emph{$\geq$} and the \emph{constraining value} is \emph{1}.
-\textbf{\emph{Classes}} indicate the list of classes, constraints refer to.
+The \emph{constraining element} of this \emph{property constraint} is the \emph{DL} at-least restriction \emph{$\geq$} and the \emph{constraining value} is \emph{1}.
+\emph{Simple constraints} may refer to a list of \textbf{\emph{classes}}.
 The qualified cardinality restriction above, e.g., refers to the class \emph{Person}, 
-i.e. restricts the objects, the property \emph{author} points to, to be of the class \emph{Person}.
-
-For \emph{property constraints}, \emph{left} and \emph{right property lists} (\textbf{\emph{leftProperties}}, \textbf{\emph{rightProperties}}) are specified.
-The assignment of properties to these lists happens relative to the \emph{constraining element} - which may be an operator (e.g. $\sqsubseteq$ in case of object property paths).
-\emph{Object Property Paths}\footnote{Corresponds to the requirement \emph{R-55-OBJECT-PROPERTY-PATHS}} (also called \emph{complex role inclusion axioms} in DL terminology)
-state that, if an individual \emph{x} is connected by a sequence of object properties with an individual \emph{y}, 
-then \emph{x} is also connected with \emph{y} by a particular object property. 
-According to the following object property path and some instance data, \emph{Stephen-Hawking} is an author of the genre \emph{Popular-Science} 
-(as \emph{Stephen-Hawking} is an author of the book \emph{A-Brief-History-Of-Time} whose genre is \emph{Popular-Science}):
+i.e. restricts the objects of the property \emph{author} to be of the class \emph{Person}.
+
+For \emph{property constraints}, \textbf{\emph{left}} and \textbf{\emph{right property lists}} are specified.
+The assignment of properties to these lists happens relative to the \emph{constraining element} - which may be an operator (e.g., $\sqsubseteq$ in case of \emph{object property paths}).
+\emph{Object Property Paths}\footnote{Corresponds to the requirement \emph{R-55-OBJECT-PROPERTY-PATHS}} (also called \emph{complex role inclusion axioms} in \emph{DL})
+express that, if an individual \emph{x} is connected by a sequence of object properties with an individual \emph{y}, 
+then \emph{x} is also related to \emph{y} by a particular object property. 
+As \emph{Stephen-Hawking} is the \emph{author} of the book \emph{A-Brief-History-Of-Time} (\ms{authorOf(Stephen-Hawking, A-Brief-History-Of-Time)}) whose \emph{genre} is \emph{Popular-Science} ({\ms{genre(A-Brief-History-Of-Time, Popular-Science)}),
+the following \emph{object property path} infers that \emph{Stephen-Hawking} is an \emph{author} of the \emph{genre} \emph{Popular-Science} (\ms{authorOfGenre(Stephen-Hawking, Popular-Science)}):
 
@@
 
-When mapped to the \emph{RDF-CV} (see table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are on the left side of the \emph{constraining element} \emph{$\sqsubseteq$},
+Thus, when mapped to the \emph{RDF-CV} (see table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are on the left side of the \emph{constraining element} \emph{$\sqsubseteq$},
 and the property \emph{authorOfGenre} is on the right side:
@@
 
-\subsection{Simple Constraints (Not Expressible in DL)}
+\subsection{\emph{Simple Constraints} (Not Expressible in \emph{DL})}
 
@@
 
-\subsection{Complex Constraints}
+\subsection{\emph{Complex Constraints}}
 
@@
 
-\subsection{Complex Constraints as Simple Constraints (Syntactic Sugar)}
+\subsection{\emph{Complex Constraints} as \emph{Simple Constraints} (Syntactic Sugar)}
 

### 2015-04-20 paper/paper 2/paper 2.tex
simple constraints

@@
 the following \emph{object property path} infers that \emph{Stephen-Hawking} is an \emph{author} of the \emph{genre} \emph{Popular-Science} (\ms{authorOfGenre(Stephen-Hawking, Popular-Science)}):
-
 \begin{DL}
@@
 \end{DL}
-
 Thus, when mapped to the \emph{RDF-CV} (see table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are on the left side of the \emph{constraining element} \emph{$\sqsubseteq$},
@@
 
-There are \emph{simple constraints} which cannot be expressed in DL such as \emph{literal pattern matching}, \emph{literal value comparison}, \emph{literal ranges}, \emph{default values}, and \emph{language tag cardinality} \cite{BoschNolleAcarEckert2015}.
+There are \emph{simple constraints} which cannot be expressed in \emph{DL} such as \emph{literal pattern matching}, \emph{literal value comparison}, \emph{literal ranges}, \emph{default values}, and \emph{language tag cardinality} \cite{BoschNolleAcarEckert2015}.
 % maybe additional constraint default values:
@@
 {\em Literal pattern matching}\footnote{Corresponds to {\em R-44-PATTERN-MATCHING-ON-RDF-LITERALS}} restricts literals to match given patterns.
-The universal restriction \ms{Book $\sqsubseteq$ $\forall$ identifier.ISBN}, e.g., ensures that \emph{books} can only have valid ISBN identifiers, 
-i.e. strings that match a given regular expression. 
-The restriction of the datatype \emph{ISBN}, however, cannot be expressed in DL, but OWL 2 DL can be used anyway to express the \emph{literal pattern matching} constraint:
+The following \emph{universal restriction}, e.g., ensures that \emph{books} can only have valid \emph{ISBN} identifiers, 
+i.e., strings that match a given regular expression:
+\begin{DL}
+\ms{Book $\sqsubseteq$ $\forall$ identifier.ISBN} 
+\end{DL}
+Even though, the restriction of the datatype \emph{ISBN} cannot be expressed in \emph{DL}, \emph{OWL 2 DL} can be used to express the \emph{literal pattern matching} constraint:
 
@@
 ISBN a RDFS:Datatype ; owl:equivalentClass [ a RDFS:Datatype ;
-    owl:onDatatype xsd:string ; owl:withRestrictions ([ xsd:pattern "^\d{9}[\d|X]\$" ])] .
-\end{ex}
-\tb{ToDO: delete the slash in front of the dollar sign from the output of the code fragment above (in the stated pattern)?}
+    owl:onDatatype xsd:string ; 
+    owl:withRestrictions ([ xsd:pattern "^\d{9}[\d|X]$" ])] .
+\end{ex}\$$
 The first OWL 2 axiom explicitly declares {\em ISBN} to be a datatype.
@@
 The second OWL 2 axiom defines {\em ISBN} as an abbreviation for a datatype restriction on {\em xsd:string}. 
-The datatype {\em ISBN} can be used just like any other datatype like in the universal restriction above.
+The datatype {\em ISBN} can be used just like any other datatype like in the \emph{universal restriction} above.
 %There are multiple use cases associated with the requirement to match literals according to given patterns (\emph{Literal Pattern Matching}\footnote{Corresponds to \emph{R-44-PATTERN-MATCHING-ON-RDF-LITERALS}}).
@@
 %The datatype \ms{RegistryNumber} can be used just like any other datatype like in the universal restriction above.
-The \emph{literal pattern matching} constraint validates \emph{ISBN} literals according to the stated regular expression causing constraint violations for triples not matching the regular expression. 
+The \emph{literal pattern matching} constraint validates \emph{ISBN} literals according to the regular expression causing constraint violations for triples which do not not match. 
 %\ms{Janeway commandsEnterprise Voyager} and \ms{Voyager registryNumber "NCC-74656"\textasciicircum{}\textasciicircum{}RegistryNumber}, 
 %but not for the triples \ms{Picard commandsEnterprise Enterprise} and \ms{Enterprise registryNumber "NCC-1701-E"\textasciicircum{}\textasciicircum{}RegistryNumber}.
-In table \ref{tab:simple-constraint-not-expressible-in-dl)}, the \emph{simple constraint} (\emph{literal pattern matching}) and the \emph{complex constraint} (\emph{universal restriction}) are mapped to the \emph{RDF-CV}.
+In table \ref{tab:simple-constraint-not-expressible-in-dl)}, the \emph{simple constraint} (\emph{literal pattern matching}) and the \emph{complex constraint} (\emph{universal restriction}) are mapped to the \emph{RDF-CV}:
 
@@
 \end{table} %\tb{Erman, can you please format the regular expression in the table above correctly?}
-The \emph{literal pattern matching} constraint introduces the new \emph{constraining element} \emph{regex}.
-For this new \emph{constraining element}, the validation must be implemented.
-This has to be done once for each \emph{generic constraint type} which cannot be expressed in DL.
+The \emph{literal pattern matching} constraint type introduces the new \emph{constraining element} \emph{regex},
+for which a validation mechanism has to be implemented.
+Validation has to be implemented once for each \emph{generic constraint type} which is not expressible in \emph{DL}.
 

### 2015-04-21 paper/paper7/paper7.tex
feedback

@@
 In this paper, we propose a system to classify RDF constraints and RDF constraint types, which in most cases correspond to RDF validation requirements.
-Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary. 
+Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary\tb{vocabulary-independent}. 
 Within the context of a complex and complete real world running example within the community around research data for the \emph{social, behavioural, and economic (SBE) sciences}, we prove the claim that the developed classification system perfectly applies for diverse vocabularies.
-We show how data in rectangular format and metadata on person-level data sets (i.e., data about individuals, households, businesses), aggregated data sets, thesauri, and statistical classifications are represented in RDF and how therefore reused vocabularies are interrelated.
+We show how data in rectangular format and metadata on record-unit data sets (i.e., data about individuals, households, businesses) or more specifically person-level data sets, aggregated data sets, thesauri, and statistical classifications are represented in RDF and how therefore reused vocabularies are interrelated.\tb{record-unit or more specific person-level data sets}
 We explain how \emph{SBE} (meta)data is validated against constraints to ensure high quality and trust.
 We exhaustively evaluated the metadata quality of large real world aggregated, person-level, and thesauri data sets (more than 4.2 billion triples and 15 thousand data sets) by means of constraints of the majority of constraint types.
-
+\tb{DCAT und XKOS nur im future work}
 \keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, RDF Data Cube Vocabulary, Rectangular Data, SKOS, XKOS, Linked Data, Semantic Web}
@@
 RDF data validation according to predefined constraints is a much sought-after feature, 
-particularly as this is taken for granted in the XML world as DDI-XML documents are validated against diverse XSDs\footnote{\label{fnt:DDI-XSDs}\url{http://www.ddialliance.org/Specification/}}.
+particularly as this is taken for granted in the XML world as DDI-XML documents are validated against diverse XSDs\footnote{\label{fnt:DDI-XSDs}\url{http://www.ddialliance.org/Specification/}} (section \ref{related-work}).
 Several approaches exist to meet this requirement, ranging from using \emph{OWL 2} as a constraint language to \emph{SPIN}\footnote{\url{http://spinRDF.org/}}, a SPARQL-based way to formulate and check constraints.
@@
 The requirements are classified to better evaluate existing solutions and each requirement is directly mapped to a constraint type which may be expressed by at least one existing constraint language.
-Bosch and Eckert \cite{BoschEckert2014-2} use SPIN as basis to define a
+Bosch and Eckert \cite{BoschEckert2014-2} \tb{why do we use spin?}use SPIN as basis to define a
 validation environment (available at \url{http://purl.org/net/rdfval-demo}) in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL.
@@
 The purpose of publicly available aggregated data, on the other hand, is to get a first overview and to gain an interest in further analyses on the underlying person-level data.
-Researchers typically represent their results as aggregated data in form of two-dimensional tables with only a few columns (so-called \emph{variables} such as \emph{sex} or \emph{age}).
+Researchers typically represent their results as aggregated data in form of two-, three-, or four-dimensional tables with only a few columns (so-called \emph{variables} such as \emph{sex} or \emph{age}).
 The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing metadata on \emph{data cubes}, i.e.
 multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}.
-Aggregated data is derived from person-level data by statistics on groups or aggregates such as counts, means, and frequencies.
+Aggregated data is derived from person-level data by statistics on groups or aggregates such as frequencies and arithmetic means.
 %The SDMX metadata standard – used as the basis for \emph{QB} – and DDI have traditionally made efforts to align their content. 
@@
 Eurostat provides publicly available European aggregated data (downloadable as CSV files) and its metadata.
-This way, researchers get promising findings (in form of published tables with a few columns), e.g., about the availability of childcare services in European Union Member States by year, duration, and child age  leading to subsequent research questions.
+This way, researchers get promising findings (in form of published tables with a few columns).
+
+We use the availability of childcare services in European Union Member States by year, duration, and child age leading to subsequent research questions as running example of this paper.\tb{nochmals drüber schauen}
 %The first step is to determine in which countries the unemployment rate is collected and which other variables of each country-specific study are theoretically comparable and can therefore be used to answer the underlying research question.
-
 The variable \emph{formal childcare}\footnote{The data set is available at: \url{http://ec.europa.eu/eurostat/web/products-datasets/-/ilc_caindformal}} (in contrast to childcare at home)
@@
 The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger}, or by a code list including multiple age clusters (such as '0 to 10' and '11 to 20').
-To determine if variables measuring \emph{age} 
+
+To determine if variables measuring \emph{age}\tb{vielleicht zu den letzten paragraphen hinzufügen} 
 - collected for different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
@@
 In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.
+\tb{reihenfolge / DCAT fehlt}
 
@@
 \section{Related Work}
+\label{related-work}
 
@@
 
+%validation or relational databases: types, relations
+
 %\textbf{RDF Data Cube Vocabulary.}
@@
 We validated more than 4.2 billion triples and 15 thousand data sets\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).
-
+\tb{auswahl an constraints, die validiert werden sollen / je nach use cases sollen z.b.
+nur technology-driven constraints validiert werden oder sind wichtiger / use solen je nach use case selbt bestimmen welche constraints validiert werden sollen}
 %It is still ongoing work to identify and classify constraints on rectangular data (\emph{PHDD}) and statistical classifications (\emph{XKOS}) and to actually evaluate the (meta)data quality of real world \emph{XKOS} and \emph{PHDD} data sets.

### 2015-04-21 paper/paper7/paper7.tex
feedback from Achim and Kai

@@
 The requirements are classified to better evaluate existing solutions and each requirement is directly mapped to a constraint type which may be expressed by at least one existing constraint language.
-Bosch and Eckert \cite{BoschEckert2014-2} \tb{why do we use spin?}use SPIN as basis to define a
+Bosch and Eckert \cite{BoschEckert2014-2} \tb{why do we use spin?not the best for constraint language, but for validating / akzeptierte beste form constraints zu definieren}use SPIN as basis to define a
 validation environment (available at \url{http://purl.org/net/rdfval-demo}) in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL.
@@
 %For these calculations, definitions of the columns are needed (e.g. is a given variable interpreted numerically or as a string).
-In 2014, SBE and Linked Data community members developed the \emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} vocabulary to represent data in a rectangular format.
+In 2014, SBE and Linked Data community members developed the \emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} vocabulary to represent data in a rectangular format.\tb{tabular data}
 The data could be either represented in records with character-separated values (CSV) or in records with fixed length.
@@
 \begin{enumerate}
-	\item $\mathcal{CT}_{C}$: \emph{Content-Driven Constraint Types}
-	\item $\mathcal{CT}_{T}$: \emph{Technology-Driven Constraint Types}
+	\item $\mathcal{CT}_{C}$: \emph{Content-Driven Constraint Types}\tb{complex constraints / zahlen interpretierbar / in einem bestimten vokabulare werden viele basic constraints verletzt / daten haben bessere qualität vokabular / wichtigkeit constraint languages, dass complexe constraints beschrieben}
+	\item $\mathcal{CT}_{T}$: \emph{Technology-Driven Constraint Types}\tb{basic constraints / welche constraints können automatisch abgeleitet werden / bestimmte constraints werden in den vokabularen definiert bzw sehr leicht zu implementieren wäre / studie ohne daten macht keinen sinn --> cardinality restriction / alle constraints die mit rdf + rdfs + owl definiert werden können / vokabukare werden heutzutage mit rdf / rdfs / owl beschrieben / constraints die typischerweise hinterlegt werden / constraints die amn als vokabular}
 \end{enumerate}
+
+\tb{große datenbestände untersuchen um ein besseres verständnis zu bekommen / liste von constraints / jedes einzelne constraint für jeded einzelne vokabular severity level / warum severity was bringt das}
 
@@
 
-We determined the default \textbf{\emph{severity level}} (corresponds to requirement \emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
+\emph{SBE} experts \tb{todo / wieviele constraints welche klasse} determined the default \textbf{\emph{severity level}} (corresponds to requirement \emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
 We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ to $\mathcal{SL}_{2}$.
@@
 The constraints responsible for the largest numbers of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916) (\emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102) (\emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903) (\emph{SKOS}).
-We refer to the technical reports\footnotemark[\ref{technical-report-1}] \footnotemark[\ref{technical-report-2}] to get details about constraints on and the evaluation of \emph{XKOS} and \emph{PHDD} data sets.
+We refer to the technical reports\footnotemark[\ref{technical-report-1}] \footnotemark[\ref{technical-report-2}] to get details about constraints on and the evaluation of \emph{XKOS} and \emph{PHDD} data sets.\tb{bezug nehmen auf severity levels / technology-driven werden oft eingehalten?
+/ }
 

### 2015-04-21 paper/paper 2/paper 2.tex
paper 2 transformations

@@
 
-\textbf{\emph{Complex constraints}} encompass \emph{simple constraints} and/or \emph{complex constraints}.
+\textbf{\emph{Complex constraints}} are composed out of \emph{simple constraints} and/or \emph{complex constraints}.
 \emph{Exclusive or} is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
-The \emph{Context-Specific Exclusive OR of Property Groups}\footnote{Corresponds to R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC} 
-is a \emph{complex constraint} restricting individuals of a given context (here a class) to contain only one of multiple property groups.
-Publications, e.g., are either identified by an ISBN and a title (for books) or by an ISSN and a title (for periodical publications), but it should not be possible to assign both identifiers to a given publication, which can be represented in ShEx:
+The \emph{complex constraint} \emph{context-specific exclusive or of property groups}\footnote{Corresponds to R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC} 
+restricts individuals of given classes to have properties of only one of multiple mutually exclusive property groups.
+\emph{Publications}, e.g., are either identified by an \emph{ISBN} and a \emph{title} (for books) or by an \emph{ISSN} and a \emph{title} (for periodical \emph{publications}), but it should not be possible to assign both identifiers to a given \emph{publication}, which can be expressed in \emph{ShEx} as follows:
 
@@
 
-As, e.g., the \emph{The-Great-Gatsby} is a \emph{publication} (\ms{rdf:type(The-Great-Gatsby, Publication)}) having an \emph{ISBN} number (\ms{isbn(The-Great-Gatsby, '978-0241965672')}) and a \emph{title} (\ms{title(The-Great-Gatsby, 'The Great Gatsby')}) and not an additional \emph{ISSN} identifier, the data is valid.
+As the \emph{The-Great-Gatsby} is a \emph{publication} (\ms{rdf:type(The-Great-Gatsby, Publication)}) having an \emph{ISBN} number (\ms{isbn(The-Great-Gatsby, '978-0241965672')}) and a \emph{title} (\ms{title(The-Great-Gatsby, 'The Great Gatsby')}) and not an additional \emph{ISSN} identifier, the \emph{The-Great-Gatsby} is a valid \emph{publication}.
 %\begin{DL}
@@
 %\end{DL}
-The \emph{complex constraint} above is mapped to DL as follows:
+The \emph{complex constraint} is mapped to the \emph{RDF-CV} (see table \ref{tab:complex-constraints}) and expressed in \emph{DL} as follows:
 
@@
 \end{DL}
-
-The \emph{complex constraint} (expressed in DL) is mapped to a \emph{generic constraint} using the \emph{RDF-CV} (see table \ref{tab:complex-constraints}).
 
@@
 
-Even though, tools may generate \emph{generic constraints} automatically, this \emph{complex constraint} is composed of many other \emph{complex} (e.g.
-minimum and maximum qualified cardinality restrictions) and \emph{simple constraints} (e.g.
-constraints on sets).
+%Even though, tools may generate \emph{generic constraints} automatically, this 
+\emph{Complex constraints} are composed of many other \emph{complex} (e.g. \emph{minimum and maximum qualified cardinality restrictions}) and \emph{simple constraints} (e.g. constraints on sets).
 As \emph{exact (un)qualified cardinality restrictions (=n)} and \emph{exclusive or (XOR)} are frequently used \emph{complex constraints},
 we propose using them as \emph{simple constraints} - in terms of syntactic sugar.
-As a consequence, the \emph{Context-Specific Exclusive OR of Property Groups} constraint above is represented as a \emph{generic constraint} more intuitively and concisely (see table \ref{tab:simplified-complex-constraints}).
+As a consequence, the \emph{context-specific exclusive or of property groups} constraint above is represented as a \emph{generic constraint} more intuitively and concisely (see table \ref{tab:simplified-complex-constraints}).
 
@@
 
-\subsection{\emph{Complex Constraints} as \emph{Simple Constraints} (Syntactic Sugar)}
-
-Almost 15 percent of all RDF constraint types are \emph{complex constraints} which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar (see section \ref{sec:evaluation}).
+\subsection{\emph{Complex Constraints} as \emph{Simple Constraints}}
+
+Almost 15 percent of all constraint types are \emph{complex constraints} which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar (see section \ref{sec:evaluation}).
 
 There are three forms of \emph{OWL RBox axioms}: \emph{role inclusions}, \emph{equivalence} and \emph{disjointness}. 
-OWL provides a variety of others, namely \emph{role transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity}. 
-These are sometimes considered as basic axiom types in DL as well, using some suggestive notation such as
-\ms{Trans(ancestorOf)} to express that the role \emph{ancestorOf} is transitive. \tb{transitive property example from the library domain}
-However, such axioms are just syntactic sugar; 
-all role characteristics can be expressed using the basic features of DL.
-The \emph{Irreflexive Object Properties} constraint type\footnote{Corresponds to \emph{R-60-IRREFLEXIVE-OBJECT-PROPERTIES}}, e.g., 
-restricts that an object property is irreflexive if it is never locally reflexive, i.e. no individual is connected by the object property to itself \cite{Kroetzsch2012}.
-The irreflexivity constraint \ms{$\top$ $\sqsubseteq$ $\neg$ $\exists authorOf.Self$}
-states that individuals cannot be authors of themselves.
-When mapped to the \emph{RDF-CV} (see table \ref{tab:irreflexive-object-properties-as-complex-constraints}), the \emph{complex constraint} aggregates three \emph{simple constraints} (one \emph{property} and two \emph{class constraints}).
+\emph{OWL} provides a variety of other axiom types: \emph{role transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity}. 
+These axiom types are sometimes considered as basic axiom types in \emph{DL} - using some suggestive notation such as
+\ms{Trans(ancestorOf)} to express that the role \emph{ancestorOf} is transitive.
+Such axioms, however, are just syntactic sugar - 
+all role characteristics can be expressed using the basic features of \emph{DL}.
+The \emph{irreflexive object properties} constraint type\footnote{Corresponds to \emph{R-60-IRREFLEXIVE-OBJECT-PROPERTIES}} 
+restricts that no individual is connected by a given object property to itself \cite{Kroetzsch2012}.
+With the following \emph{irreflexive object property} constraint, e.g., one can state that individuals cannot be authors of themselves:
+\begin{DL}
+\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists authorOf.Self$}
+\end{DL}
+When mapped to the \emph{RDF-CV} (see table \ref{tab:irreflexive-object-properties-as-complex-constraints}), the \emph{complex constraint} aggregates three \emph{simple constraints} (one \emph{property} and two \emph{class constraints}):
 
@@
 
-When using the OWL RBox axiom \emph{role irreflexivity} as syntactic sugar, 
-the \emph{complex constraint} transforms into a \emph{simple property constraint} with exactly the same semantics (see table \ref{tab:irreflexive-object-properties-as-simple-constraints}).
+When using the \emph{OWL RBox axiom} \emph{role irreflexivity} in terms of syntactic sugar, 
+the \emph{complex constraint} can be expressed more concisely in form of a \emph{simple property constraint} with exactly the same semantics (see table \ref{tab:irreflexive-object-properties-as-simple-constraints}):
 
@@
 
-The \emph{Primary Key Properties}\footnote{Corresponds to \emph{R-226-PRIMARY-KEY-PROPERTIES}} constraint type is often useful to declare a given (datatype) property as the "primary key" of a class, so that a system can enforce uniqueness.
-Books, e.g., are uniquely identified by their ISBN, i.e. the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}, 
-which can be mapped to the \emph{RDF-CV} (see table \ref{tab:primary-key-properties-as-complex-constraints}).
+The \emph{primary key properties}\footnote{Corresponds to \emph{R-226-PRIMARY-KEY-PROPERTIES}} constraint type is often useful to declare a given (datatype) property as the "primary key" of a class, so that a system can enforce uniqueness.
+\emph{Books}, e.g., are uniquely identified by their \emph{ISBN} number, i.e., the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}, 
+which can be represented by the \emph{RDF-CV} in form of a \emph{complex constraint} (see table \ref{tab:primary-key-properties-as-complex-constraints}):
 
@@
 
-\emph{Keys}, however, are even more general, i.e. a generalization of inverse functional properties \cite{Schneider2009}.
-A key can be a datatype property, an object property, or a chain of properties.
+\emph{Keys}, however, are even more general, i.e., a generalization of \emph{inverse functional properties} \cite{Schneider2009}.
+A key can be a datatype, an object property, or a chain of properties.
 For these generalization purposes, as there are different sorts of keys, and as keys can lead to undecidability, 
-DL is extended with \emph{key boxes} and a special construct \emph{keyfor} \cite{Lutz2005}.
-When using the \emph{keyfor} DL construct (\ms{isbn keyfor Book}), the \emph{complex constraint} can be expressed by only one \emph{simple property constraint} (see table \ref{tab:primary-key-properties-as-simple-constraints} for the mapping to the \emph{RDF-CV}).
+\emph{DL} is extended with \emph{key boxes} and a special construct \emph{keyfor} \cite{Lutz2005}.
+When using the \emph{keyfor} \emph{DL} construct (\ms{isbn keyfor Book}), the \emph{complex constraint} can be expressed by only one \emph{simple property constraint} (see table \ref{tab:primary-key-properties-as-simple-constraints} for the mapping to the \emph{RDF-CV}).
 
@@
 
-RDF data providers have to ensure that their data conforms to constraints which are part of explicitly or implicitly concluded contracts between data providers and consumers.
-As there is no standard way, these constraints may be represented by a variety of possible constraint languages (there are even more than the five promising ones\footnote{i.a.
-Bibframe, DQTP, Pellet ICV, RDFUnit, SPARQL, Stardog ICV}).
-There is an obvious need to transform any \emph{specific constraint} (\emph{$sc_{\alpha}$}) (expressed by any constraint language \emph{$\alpha$}) into any other \emph{specific constraint} (\emph{$sc_{\beta}$}) (expressed by any constraint language \emph{$\beta$}) - when they have the same semantics.
-We use the \emph{RDF-CV} as an intermediate representation vocabulary for these transformations.
-If we define mappings ($m(sc_{\alpha}), m(sc_{\beta})$) between equivalent \emph{specific constraints} and the corresponding \emph{generic constraint} (\emph{gc}),
-we can convert them automatically:
+RDF data providers have to ensure that their data conforms to constraints which are explicitly defined within contracts between data providers and consumers.
+As there is no standard way to express these constraints, they may be represented by a variety of constraint languages - different in syntax and semantics (there are even more than the five promising ones\footnote{i.a.
+Bibframe, DQTP, Pellet ICV, RDFUnit, SPARQL, and Stardog ICV}).
+To overcome the necessity to understand diverse constraint languages, 
+we propose to provide a mechanism which transforms any \emph{specific constraint} (\emph{$sc_{\alpha}$}) (expressed by any constraint language \emph{$\alpha$}) into any other \emph{specific constraint} (\emph{$sc_{\beta}$}) (expressed by any constraint language \emph{$\beta$}) - when they have the same semantics.
+We use the \emph{RDF-CV} to intermediately represent constraints for these transformations.
+By defining mappings ($m(sc_{\alpha}), m(sc_{\beta})$) between equivalent \emph{specific constraints} and the corresponding \emph{generic constraint} (\emph{gc}) we are able to convert them automatically:
 
@@
 We do not need to define mappings for each pair of semantically equivalent \emph{specific constraints}.
-Let's assume we are able to express a constraint type by 5/6/7/8/9/10 constraint languages.
+Let's assume we are able to express a particular constraint type by 5/6/7/8/9/10 constraint languages.
 Without the intermediate \emph{generic constraint}, we would have to define for each constraint type \emph{1} mapping for each pair of \emph{specific constraints} (expressed by different constraint languages)
@@
 
+\begin{DL}
+Publication $\equiv$ $\exists$ publisher.Publisher
+\end{DL}
+
 The {\em existential quantification}\footnote{Corresponds to {\em R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}}
-\ms{Publication $\equiv$ $\exists$ publisher.Publisher} restricts publications to have at least one publisher and can be expressed by at least 10 constraint languages\footnote{at least by OWL2, SPARQL, ShEx, Bibframe, DSP, ReSh, SPIN, DQTP, Pellet IVC, Stardog ICV}:
+%\ms{Publication $\equiv$ $\exists$ publisher.Publisher} 
+above restricts \emph{publications} to have at least one \emph{publisher} and can be expressed by at least 10 different constraint languages\footnote{at least by OWL 2, SPARQL, ShEx, Bibframe, DSP, ReSh, SPIN, DQTP, Pellet IVC, and Stardog ICV}:
 
@@
 
-First, the DL statement \ms{Publication $\equiv$ $\exists$ publisher.Publisher} is mapped to a \emph{simple generic constraint} according to the \emph{RDF-CV} (see table \ref{tab:existential-quantification-as-simple-constraints}).
+First, the \emph{DL} statement \ms{Publication $\equiv$ $\exists$ publisher.Publisher} is mapped to a \emph{simple generic constraint} according to the \emph{RDF-CV} (see table \ref{tab:existential-quantification-as-simple-constraints}) and
+the next step is to define one mapping for each \emph{specific constraint} (\emph{$sc_{OWL 2}$}, \emph{$sc_{ReSh}$}, \emph{$sc_{ShEx}$}, ...) to the corresponding \emph{generic constraint}.
 
@@
 \end{table}
-
-The next step is to define one mapping for each \emph{specific constraint} (\emph{$sc_{OWL 2}$}, \emph{$sc_{ReSh}$}, \emph{$sc_{ShEx}$}, ...) to the \emph{generic constraint}.
 

### 2015-04-22 paper/paper 2/paper 2.tex
implementation

@@
 %\section{Transformations between Specific Constraints}
-\section{How to Improve the Interoperability of Constraints}
+\section{How to Improve the Understandability of Constraints}
 \label{sec:transformations}
@@
 RDF data providers have to ensure that their data conforms to constraints which are explicitly defined within contracts between data providers and consumers.
-As there is no standard way to express these constraints, they may be represented by a variety of constraint languages - different in syntax and semantics (there are even more than the five promising ones\footnote{i.a.
-Bibframe, DQTP, Pellet ICV, RDFUnit, SPARQL, and Stardog ICV}).
+As there is no standard way to express constraints, they may be represented by a variety of constraint languages\footnote{Candidates for constraint languages are, i.a., SPIN, OWL 2, DSP, ShEx, ReSh, Bibframe, DQTP, Pellet ICV, RDFUnit, SPARQL, and Stardog ICV} - each of them different in syntax and semantics.
 To overcome the necessity to understand diverse constraint languages, 
-we propose to provide a mechanism which transforms any \emph{specific constraint} (\emph{$sc_{\alpha}$}) (expressed by any constraint language \emph{$\alpha$}) into any other \emph{specific constraint} (\emph{$sc_{\beta}$}) (expressed by any constraint language \emph{$\beta$}) - when they have the same semantics.
-We use the \emph{RDF-CV} to intermediately represent constraints for these transformations.
+we propose to transform any \emph{specific constraint} (\emph{$sc_{\alpha}$}) (expressed by any constraint language \emph{$\alpha$}) into any other \emph{specific constraint} (\emph{$sc_{\beta}$}) (expressed by any other constraint language \emph{$\beta$}) - in case they have the same semantics.
+We use the \emph{RDF-CV} to intermediately represent constraints in a generic way for these transformations.
 By defining mappings ($m(sc_{\alpha}), m(sc_{\beta})$) between equivalent \emph{specific constraints} and the corresponding \emph{generic constraint} (\emph{gc}) we are able to convert them automatically:
@@
 
-We do not need to define mappings for each pair of semantically equivalent \emph{specific constraints}.
+We do not need to define mappings between each pair of semantically equivalent \emph{specific constraints}.
 Let's assume we are able to express a particular constraint type by 5/6/7/8/9/10 constraint languages.
@@
 - that are \emph{\( {n \choose 2} \)} mappings (10/15/21/28/36/45 mappings).
-With an intermediate \emph{generic constraint}, however, we only need to define for each constraint type \emph{n} mappings (one mapping for each \emph{specific constraint}) from \emph{n} \emph{specific constraints} to the corresponding \emph{generic constraint} (5/6/7/8/9/10 mappings).
+With an intermediate \emph{generic constraint}, however, we only need to define for each constraint type \emph{n} mappings (1 mapping for each \emph{specific constraint}) from \emph{n} \emph{specific constraints} to the corresponding \emph{generic constraint} (5/6/7/8/9/10 mappings).
 
@@
 %\ms{Publication $\equiv$ $\exists$ publisher.Publisher} 
-above restricts \emph{publications} to have at least one \emph{publisher} and can be expressed by at least 10 different constraint languages\footnote{at least by OWL 2, SPARQL, ShEx, Bibframe, DSP, ReSh, SPIN, DQTP, Pellet IVC, and Stardog ICV}:
+above restricts \emph{publications} to have at least one \emph{publisher} and can be expressed by at least 10 different constraint languages\footnote{OWL 2, SPARQL, ShEx, Bibframe, DSP, ReSh, SPIN, DQTP, Pellet IVC, and Stardog ICV}:
 
@@
 
-First, the \emph{DL} statement \ms{Publication $\equiv$ $\exists$ publisher.Publisher} is mapped to a \emph{simple generic constraint} according to the \emph{RDF-CV} (see table \ref{tab:existential-quantification-as-simple-constraints}) and
-the next step is to define one mapping for each \emph{specific constraint} (\emph{$sc_{OWL 2}$}, \emph{$sc_{ReSh}$}, \emph{$sc_{ShEx}$}, ...) to the corresponding \emph{generic constraint}.
+The \emph{DL} statement \ms{Publication $\equiv$ $\exists$ publisher.Publisher} is mapped to a \emph{(simple) generic constraint} conforming to the \emph{RDF-CV} (see table \ref{tab:existential-quantification-as-simple-constraints}).
+Then, one mapping (\emph{$m(sc_{OWL 2})$}, \emph{$m(sc_{ReSh})$}, \emph{$m(sc_{ShEx})$}, ...) is defined for each \emph{specific constraint} (\emph{$sc_{OWL 2}$}, \emph{$sc_{ReSh}$}, \emph{$sc_{ShEx}$}, ...) to the corresponding \emph{generic constraint} (\emph{gc}).
 
@@
 
-SPARQL is generally seen as the method of choice to validate RDF data according to certain constraints, although it is not ideal for their formulation. 
+SPARQL is generally seen as the method of choice to validate RDF data according to certain constraints, although, it is not ideal for their formulation. 
 In contrast, OWL 2, DSP, ReSh, and ShEx constraints are comparatively easy to understand. 
-Bosch and Eckert \cite{BoschEckert2014-2} use SPIN as basis to define a
+We use SPIN as basis to define a
 validation environment in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL
 (the implementation can be tested at \url{http://purl.org/net/rdfval-demo}).
-The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.
-We are able to offer the validation of all \emph{specific constraints} (expressed by any constraint language) by defining mappings from each \emph{specific constraint} to SPIN, 
-what we have done for all OWL 2\footnote{OWL to SPIN: \url{https://github.com/boschthomas/OWL2-SPIN-Mapping}} and DSP\footnote{DSP to SPIN: \url{https://github.com/dcmi/DSP-SPIN-Mapping}} constructs and for some constructs of other constraint languages.
+The SPIN engine checks for each resource if it satisfies all constraints, which are associated with the classes assigned to the resource, and generates a result RDF graph containing information about all constraint violations \cite{BoschEckert2014-2}.
+This way, we are able to offer RDF data validation according to all \emph{specific constraints} (expressed by any constraint language) by defining mappings from each \emph{specific constraint} to \emph{SPIN}.
+We already specified mappings to \emph{SPIN} for all \emph{OWL 2} and \emph{DSP}\footnote{SPIN mappings: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} constructs and for some \emph{ReSh} and \emph{ShEx} constructs.
 %We do not have to define a mapping to SPIN for each specific constraint. 
 %when we define a mapping to SPIN for each generic constraint.
-We do not have to map each \emph{specific constraint} to SPIN and we get identical validation results for semantically equivalent \emph{specific constraints},
+As constraint languages differ in syntax and semantics it is rather difficult to ensure that semantically equivalent \emph{specific constraints} always lead to identical validation results.
+
+We do not have to map each \emph{specific constraint} to SPIN and we get identical validation results for semantically equivalent \emph{specific constraints} (expressed by different constraint languages),
 (1) if we map semantically equivalent \emph{specific constraints} to the corresponding \emph{generic constraint} and 
 (2) if we map the \emph{generic constraint} to SPIN.
-As a consequence, we only have to define one SPIN mapping for each constraint type corresponding to a requirement within the RDF validation requirements database.
-19 of 74 RDF constraint types can be expressed by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
-This means that there must be 76 (four for each constraint type) implementations to validate 76 \emph{specific constraints} - instead of only 19 implementations (one for each \emph{generic constraint}).
+As a consequence, we only have to define one SPIN mapping for each constraint type corresponding to an RDF validation requirement.
+19 of the overall 74 identified constraint types can be expressed by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
+This means that there must be 76 (four for each constraint type) implementations to validate RDF data according to 76 \emph{specific constraints} - instead of only 19 implementations (one for each \emph{generic constraint}) leading to identical validation results.
 
@@
 
-Within our validation environment, we define one SPIN construct template for each \emph{generic constraint}\footnote{For details about the validation environment see \cite{BoschEckert2014-2}}.
+Within the \emph{RDF Validator}\footnote{For details about the validation environment see \cite{BoschEckert2014-2}}, we define one SPIN construct template for each \emph{generic constraint} and therefore constraint type.
 A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples (\emph{spin:ConstraintViolation}) indicating the subject (\emph{spin:violationRoot}) and the properties (\emph{spin:violationPath}), causing constraint violations, and the reason why constraint violations have been raised (\emph{rdfs:label}).
@@
 
+\tb{how are typical constraints expressed by different constraint languages}
+
 \section{Conclusion and Future Work}

### 2015-04-22 paper/paper 2/paper 2.tex
implementation

@@
 Within the \emph{RDF Validator}\footnote{For details about the validation environment see \cite{BoschEckert2014-2}}, we define one SPIN construct template for each \emph{generic constraint} and therefore constraint type.
-A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples (\emph{spin:ConstraintViolation}) indicating the subject (\emph{spin:violationRoot}) and the properties (\emph{spin:violationPath}), causing constraint violations, and the reason why constraint violations have been raised (\emph{rdfs:label}).
+A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples (\emph{spin:ConstraintViolation}) indicating the subject (\emph{spin:violationRoot}) and the properties (\emph{spin:violationPath}) causing constraint violations, and the reason why constraint violations have been raised (\emph{rdfs:label}).
 A SPIN construct template creates constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
-The SPARQL CONSTRUCT query for validating \emph{universal quantifications}\footnote{Corresponds to \emph{R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}}, e.g.
-\emph{authors} of \emph{publications} must be \emph{persons} (\ms{Publication $\equiv$ $\forall$ author.Person}), is shown below:
+
+\begin{DL}
+Publication $\equiv$ $\forall$ author.Person
+\end{DL}
+
+According to the \emph{universal quantification}\footnote{Corresponds to \emph{R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}} above, \emph{authors} of \emph{publications} must be \emph{persons}.
+The SPARQL CONSTRUCT query for the constraint type \emph{universal quantification} is shown below:
 
@@
 
-We provide a mapping from the \emph{RDF-CV} to SPIN\footnote{RDF-CV to SPIN: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}} in order to automatically validate each type of \emph{generic constraint} (\emph{simple}, \emph{complex}, \emph{property}, and \emph{class constraints}).
-Part of future work will be 
-(1) to provide a GUI which generates \emph{generic constraints} automatically according to inputs of domain experts who are not familiar with the formulation of constraints,
-(2) to offer bidirectional transformations between \emph{specific constraints} (expressed by multiple constraint languages) and \emph{generic constraints}, and
-(3) to provide translations between semantically equivalent \emph{specific constraints} (expressed by any constraint language) by using \emph{generic constraints} as an intermediate transformation step.
-%\begin{itemize}
-	%\item to provide a GUI which generates generic constraints automatically according to inputs of domain experts who are not familiar with the formulation of constraints.
-	%\item to offer bidirectional transformations between specific constraints (expressed by multiple constraint languages) and generic constraints. 
-	%\item to provide translations between specific constraints (expressed by any specific constraint language) by using generic constraints as an intermediate transformation step.
-%\end{itemize}
+We provide a mapping from the \emph{RDF-CV} to SPIN\footnote{RDF-CV to SPIN: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}} 
+in order to automatically validate RDF data complying with each type of \emph{generic constraint} (\emph{simple}, \emph{complex}, \emph{property}, and \emph{class constraints}).
 
@@
 
-\tb{ToDo: there is too much space before and after DL and table environments / can your resolve that please?}
+It is part of future work 
+(1) to extend the \emph{RDF Validator} by creating \emph{generic constraints} automatically according to inputs of domain experts who may not be familiar with the formulation of constraints,
+(2) to offer bidirectional transformations between all \emph{specific constraints} (expressed by all existing constraint languages) and the corresponding \emph{generic constraints}, and
+(3) to provide translations between semantically equivalent \emph{specific constraints} (expressed by any constraint language) by using \emph{generic constraints} as an intermediate transformation step.
+%\begin{itemize}
+	%\item to provide a GUI which generates generic constraints automatically according to inputs of domain experts who are not familiar with the formulation of constraints.
+	%\item to offer bidirectional transformations between specific constraints (expressed by multiple constraint languages) and generic constraints. 
+	%\item to provide translations between specific constraints (expressed by any specific constraint language) by using generic constraints as an intermediate transformation step.
+%\end{itemize}
 

### 2015-04-22 paper/paper 2/paper 2.tex
evaluation

@@
 \section{Introduction}
-\tb{feedback: the major problem is semantics. OWL basically work in different semantics than others. And their semantics are formal. Closed world vs. Open World is also a part of this.}
+\tb{feedback from Erman: the major problem is semantics. OWL basically work in different semantics than others. And their semantics are formal. Closed world vs. Open World is also a part of this.}
 %The purpose of OWL 2 ontologies is to perform reasoning on RDF data and not to validate RDF data conforming to these ontologies.
@@
 
-In order to develop a vocabulary to describe constraints of any constraint type generically, it is needed to define the basic terminology for the formulation of constraints and to classify them first.
+In order to develop a vocabulary to describe constraints of any constraint type generically, it is needed to define the basic terminology for the formulation of constraints and to classify them. 
 A \textbf{\emph{constraint language}} is a language which is used to formulate constraints.
 The W3C Data Shapes working group defines \textbf{\emph{RDF constraint}} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
-We identified four dimensions to classify constraints:
+We identified four dimensions to classify constraint types:
 \begin{itemize}
@@
 The assignment of properties to these lists happens relative to the \emph{constraining element} - which may be an operator (e.g., $\sqsubseteq$ in case of \emph{object property paths}).
-\emph{Object Property Paths}\footnote{Corresponds to the requirement \emph{R-55-OBJECT-PROPERTY-PATHS}} (also called \emph{complex role inclusion axioms} in \emph{DL})
+\emph{Object Property Paths} (\emph{R-55}; also called \emph{complex role inclusion axioms} in \emph{DL})
 express that, if an individual \emph{x} is connected by a sequence of object properties with an individual \emph{y}, 
@@
 
-{\em Literal pattern matching}\footnote{Corresponds to {\em R-44-PATTERN-MATCHING-ON-RDF-LITERALS}} restricts literals to match given patterns.
+{\em Literal pattern matching} (\emph{R-44}) restricts literals to match given patterns.
 The following \emph{universal restriction}, e.g., ensures that \emph{books} can only have valid \emph{ISBN} identifiers, 
@@
 \emph{Exclusive or} is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
-The \emph{complex constraint} \emph{context-specific exclusive or of property groups}\footnote{Corresponds to R-13-DISJOINT-GROUP-OF-PROPERTIES-CLASS-SPECIFIC} 
+The \emph{complex constraint} \emph{context-specific exclusive or of property groups} (\emph{R-13})
 restricts individuals of given classes to have properties of only one of multiple mutually exclusive property groups.
@@
 all role characteristics can be expressed using the basic features of \emph{DL}.
-The \emph{irreflexive object properties} constraint type\footnote{Corresponds to \emph{R-60-IRREFLEXIVE-OBJECT-PROPERTIES}} 
+The \emph{irreflexive object properties} constraint type (\emph{R-60}) 
 restricts that no individual is connected by a given object property to itself \cite{Kroetzsch2012}.
@@
 
-The \emph{primary key properties}\footnote{Corresponds to \emph{R-226-PRIMARY-KEY-PROPERTIES}} constraint type is often useful to declare a given (datatype) property as the "primary key" of a class, so that a system can enforce uniqueness.
+The \emph{primary key properties} constraint type (\emph{R-226}) is often useful to declare a given (datatype) property as the "primary key" of a class, so that a system can enforce uniqueness. 
 \emph{Books}, e.g., are uniquely identified by their \emph{ISBN} number, i.e., the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}, 
@@
 
-The {\em existential quantification}\footnote{Corresponds to {\em R-86-EXISTENTIAL-QUANTIFICATION-ON-PROPERTIES}}
+The {\em existential quantification} (\emph{R-86})
 %\ms{Publication $\equiv$ $\exists$ publisher.Publisher} 
@@
 
-According to the \emph{universal quantification}\footnote{Corresponds to \emph{R-91-UNIVERSAL-QUANTIFICATION-ON-PROPERTIES}} above, \emph{authors} of \emph{publications} must be \emph{persons}.
+According to the \emph{universal quantification} (\emph{R-91}) above, \emph{authors} of \emph{publications} must be \emph{persons}.
 The SPARQL CONSTRUCT query for the constraint type \emph{universal quantification} is shown below:
@@
 
-We evaluated to which extend the most promising five constraint languages fulfill each of the overall 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type.
-We recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} (serving as appendix of this paper) in which we explain each requirement (constraint type) in detail and give examples for each (represented by listed constraint languages).
-This technical report also contains mappings to DL to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
-If a constraint type can be expressed in DL, we added the mapping to DL and to the \emph{generic constraint}.
-If a constraint type cannot be expressed in DL, we only added the mapping to the \emph{generic constraint}.
-Therefore, we show that each constraint type can be mapped to a \emph{generic constraint}.
-Table \ref{tab:evaluation} shows the absolute numbers and the relative percentages for each of the three dimensions to classify constraint types \emph{context}, \emph{complexity}, and \emph{DL expressivity}:
+We evaluated to which extend the five most promising constraint languages on being the standard fulfill each of the overall 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type.
+We recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} (serving as appendix of this paper) in which we explain each constraint type in detail and give examples for each (represented by different constraint languages).
+The technical report also contains mappings to \emph{DL} to logically underpin each constraint type and to determine which \emph{DL} constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
+If a constraint type can be expressed in \emph{DL}, we added the mapping to \emph{DL} and to the \emph{generic constraint} conforming to the \emph{RDF-CV}.
+In contrast, if a constraint type cannot be expressed in \emph{DL}, we only added the mapping to the \emph{generic constraint}.
+This way, we prove that each constraint type can be mapped to a \emph{generic constraint} and therefore be represented generically by means of the \emph{RDF-CV}.
+Table \ref{tab:evaluation} displays the classification of constraint types according to the dimensions \emph{context}, \emph{complexity}, and \emph{DL expressivity}:
 
@@
 		\begin{tabular}{l|c|c}
-      \textbf{Constraint Classes} & \textbf{\#} & \textbf{\%} \\
-      \hline
-\emph{Property Constraints} & 48 & 65 (64.86) \\
-\emph{Class Constraints} & 17 & 23 (22.96) \\
-\emph{Property and Class Constraints} & 9 & 12 (12.16) \\
-\hline
-\emph{Simple Constraints} & 46 & 62 (62.16) \\
-\emph{Simple Constraints} (Syntactic Sugar) & 10 & 14 (13.51) \\
-\emph{Complex Constraints} & 18 & 24 (24.32) \\
-\hline
-\emph{DL Expressible} & 51 & 69 (68.92) \\
-\emph{DL Not Expressible} & 23 & 31 (31.08) \\
+      \textbf{Classes of Constraint Types} & \textbf{\#} & \textbf{\%} \\
+      \hline
+%\textbf{\emph{Context}} & & \\
+\emph{Property Constraints} & 48 & 64.86 \\
+\emph{Class Constraints} & 17 & 22.96 \\
+\emph{Property and Class Constraints} & 9 & 12.16 \\
+\hline
+%\textbf{\emph{Complexity}} & & \\
+\emph{Simple Constraints} & 46 & 62.16 \\
+\emph{Simple Constraints} (Syntactic Sugar) & 10 & 13.51 \\
+\emph{Complex Constraints} & 18 & 24.32 \\
+\hline
+%\textbf{\emph{DL Expressivity}} & & \\
+\emph{DL Expressible} & 51 & 68.92 \\
+\emph{DL Not Expressible} & 23 & 31.08 \\
 \hline
@@
 
-Constraints types can be classified as \emph{property constraints} and \emph{class constraints} (classification dimension \emph{context}).
-Two thirds of the total amount of constraint types are \emph{property constraints} (e.g.
-\emph{existential} and \emph{universal quantification}), one fifth are \emph{class constraints} (e.g.
-\emph{allowed values}\footnote{Corresponds to \emph{R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS} and
-\emph{R-37-ALLOWED-VALUES-FOR-RDF-LITERALS}} for literals and objects), and approx.
-10\% are composed of both \emph{property and class constraints} (e.g.
-\emph{context-specific exclusive or of property groups}).
-Constraint types may be either atomic (\emph{simple constraints}) or created out of \emph{simple} and/or \emph{complex constraints} (\emph{complex constraints}) (classification dimension \emph{complexity}).
-Almost two thirds of the constraint types are \emph{simple constraints} (e.g.
-\emph{object property paths}), a quarter are \emph{complex constraints} (e.g.
-\emph{ranges of literal values}\footnote{Corresponds to \emph{R-45-RANGES-OF-RDF-LITERAL-VALUES}}), and
-nearly 15 percent are \emph{complex constraints} which can be formulated as \emph{simple constraints} when using them in terms of syntactic sugar (e.g. \emph{(un)qualified cardinality restrictions}).
-Constraint types can either be \emph{expressible in DL} or \emph{not} (classification dimension \emph{DL expressivity}).
-The majority - nearly 70\% - of the overall constraint types are expressible in DL.	
-\emph{Literal pattern matching} is an example of a constraint type which cannot be represented in DL.
+Constraint types can be classified as \emph{property constraints} and \emph{class constraints} (\emph{context}).
+Two thirds of the total amount of constraint types are \emph{property constraints} (e.g., \emph{R-86: existential quantification} and \emph{R-91: universal quantification}), one fifth are \emph{class constraints} (e.g., \emph{R-30/37: allowed values} for objects/literals), and approx.
+10\% are composed of both \emph{property and class constraints} (e.g., \emph{R-13: context-specific exclusive or of property groups}).
+According to the dimesion \emph{complexity}, constraint types can be either atomic (\emph{simple constraints}) or complex (\emph{complex constraints}), i.e., created out of \emph{simple} and/or \emph{complex constraints}.
+Almost two thirds of the constraint types are \emph{simple constraints} (e.g., \emph{R-55: object property paths}), a quarter are \emph{complex constraints} (e.g., \emph{R-45: ranges of literal values}), and
+nearly 15 percent are \emph{complex constraints} which can be formulated as \emph{simple constraints} when using them in terms of syntactic sugar (e.g., \emph{R-81/75/82/76/80/74: (un)qualified cardinality restrictions}).
+Constraint types can either be \emph{expressible in DL} or \emph{not} (\emph{DL expressivity}).
+The majority - nearly 70\% - of the overall constraint types are expressible in \emph{DL}.	
+\emph{Literal pattern matching} (\emph{R-44}) is an example of a constraint type which cannot be represented in \emph{DL}, but can also be represented generically by means of the \emph{RDF-CV}.
+Altogether, most of the constraint types are \emph{simple constraints on properties} which are \emph{expressible in DL}. 
+Thus, the majority of constraint types are directly and relatively easy formulated in form of \emph{simple constraints} which can be mapped to equivalent \emph{DL} constructs.
 
@@
 
-\tb{how are typical constraints expressed by different constraint languages}
+\tb{1 page / explain how typical constraints are expressed by different constraint languages}
 

### 2015-04-22 paper/paper 2/paper 2.tex
semantics

@@
 %
-\title{Formulating RDF Constraints and \\ Validating RDF Data Generically}
+%\title{Formulating RDF Constraints and \\ Validating RDF Data Generically}
+\title{Formulating RDF Constraints Generically and Validating RDF Data Out-Of-The-Box }
 %\subtitle{}
@@
 particularly as many communities are used to have this functionality in the XML world.
-XML Schema is the standard constraint language to formulate constraints on and to validate XML documents.
+XML Schema is the standard language to formulate constraints on and to validate XML documents.
 For RDF, however, there are several candidates for languages to express constraints on RDF data - but no standard one meeting the majority of RDF validation use cases.
-We identified requirements to formulate constraints and to validate RDF data and mapped each requirement to an RDF constraint type.
-The majority of these constraint types can be represented in description logics providing their logical underpinning.
+We identified requirements to formulate constraints and to validate RDF data and mapped each requirement to a constraint type.
+The majority of these constraint types can be expressed in description logics providing their logical underpinning.
 
@@
 (1) we provide a basic terminology and classification system for RDF constraints,
-(2) we developed a vocabulary to describe constraints of any constraint type generically,
+(2) we developed a vocabulary to describe constraints of any constraint type generically and specified its underlying semantics,
 (3) we show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful, and
-(4) we explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages.
+(4) we explain how to overcome the necessity to implement the validation of each constraint type for diverse constraint languages.
 
@@
 \section{Introduction}
-\tb{feedback from Erman: the major problem is semantics. OWL basically work in different semantics than others. And their semantics are formal. Closed world vs. Open World is also a part of this.}
 %The purpose of OWL 2 ontologies is to perform reasoning on RDF data and not to validate RDF data conforming to these ontologies.
@@
 
-There is not the one language meeting the majority of requirements to formulate constraints.
-As there are more than 10 candidate languages with different syntaxes and semantics which can be used to express constraints, 
+There is not the one language meeting the majority of requirements to formulate constraints and validate RDF data.
+As there are more than 10 candidate languages with different syntaxes and semantics which can be used to express constraints and to validate RDF data, 
 %(e.g. existential and universal quantification, cardinality restrictions, and exclusive or of properties)
@@
 %min car more powerful than req. propery
-The idea behind this paper is to achieve complete RDF validation requirements coverage by representing any constraint type (corresponding to a requirement to formulate constraints) in a generic way using a lightweight vocabulary consisting of only a few terms (see section \ref{sec:vocabulary}).
+The idea behind this paper is to achieve complete RDF validation requirements coverage by representing any constraint type (corresponding to a requirement to formulate constraints and to validate RDF data) in a generic way using a lightweight vocabulary consisting of only a few terms (see section \ref{sec:vocabulary}).
 
@@
 This causes confusion and weakens the common understanding between several parties about the semantics of particular constraints and therefore how to ensure high data quality. 
-Thus, when choosing constraint language \ms{$\alpha$} to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a semantically equivalent \tb{Erman thinks formal generic semantics should be defined} constraint formulated by any other constraint language \ms{$\beta$} (see section \ref{sec:transformations}).
+Thus, when choosing constraint language \ms{$\alpha$} to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a semantically equivalent constraint formulated by any other constraint language \ms{$\beta$} (see section \ref{sec:transformations}).
 This is important in order to enhance the interoperability of constraint languages and to resolve ambiguities in the communication of RDF data producers and consumers, 
@@
 (1) we provide a basic terminology and classification system for RDF constraints (section \ref{sec:vocabulary}),
-(2) we developed a vocabulary to describe constraints of any RDF constraint type generically (section \ref{sec:vocabulary}),
+(2) we developed a vocabulary to describe constraints of any RDF constraint type generically and specified its underlying semantics (section \ref{sec:vocabulary}),
 (3) we show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful (section \label{ref:transformations}), and
@@
 
-In order to develop a vocabulary to describe constraints of any constraint type generically, it is needed to define the basic terminology for the formulation of constraints and to classify them. 
+In order to develop a vocabulary to describe constraints of any constraint type in a generic way, prerequisites are to specify the vocabulary's underlying semantics, to define the basic terminology for the formulation of constraints, and to classify them.
+The underlying \textbf{\emph{semantics}} for RDF validation are \emph{UNA} and \emph{CWA}.
+RDF validation requires that different names represent different objects ({\em unique name assumption (UNA)}), whereas,
+\emph{OWL 2} is based on the {\em non-unique name assumption (nUNA)}. 
+A data property is \emph{functional} (\emph{R-65}) if for each individual \emph{x}, there can be at most one distinct literal \emph{y} such that \emph{x} is connected by the data property to \emph{y}.
+When assuming \emph{UNA}, the functional property {\em title} (\ms{funct (title)}) causes a clash
+in case the book {\em Huckleberry-Finn} has more than one \emph{title}
+(\ms{title(Huckleberry-Finn, The-Adventures-of-Huckleberry-Finn)}, \ms{title(Huckleberry-Finn, Die-Abenteuer-des-Huckleberry-Finn)}).
+Assuming nUNA, however, reasoning concludes that the titles {\em The-Adventures-of-Huckleberry-Finn} and {\em Die-Abenteuer-des-Huckleberry-Finn} are the same (\ms{\{The-Adventures-of-Huckleberry-Finn\}} = \ms{\{Die-Abenteuer-des-Huckle} \ms{berry-}\ms{Finn\}}).
+
+Reasoning in \emph{OWL 2} is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose to represent knowledge on the World Wide Web.
+%Most of the constraint languages except OWL, have a major shortcoming of redundancy.
+%With its open-world semantics, used as a constraint language, OWL solves the redundancy problem. 
+%\tb{the following example does not show the redundancy problem!}
+%\tb{2. benefit: reasoning solves redundancy problem}
+As each \emph{book} must have a \emph{title} (\ms{Book $\sqsubseteq \exists$ title.$\top$}) and {\em Hamlet} is a \emph{book} (\ms{Book(Hamlet)}),
+{\em Hamlet} must have at least one \emph{title}.
+In an \emph{OWA} setting, this axiom does not cause a constraint violation (even if there is no explicitly defined \emph{title}), since there must be a \emph{title} for this \emph{book} which we may not know.
+On the other hand, RDF validation scenarios require the {\em closed-world assumption (CWA)}, i.e., a statement is inferred to be false if it cannot be proved to be true.
+Hence, classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals which yields in return to a constraint violation.
+This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past.  
+Thus, in case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics than for RDF validation in general. 
+\tb{feedback from Erman: the major problem is semantics.
+OWL basically work in different semantics than others.
+And their semantics are formal.
+Closed world vs.
+Open World is also a part of this.
+/ Thomas: I think your issue is tackled now?}
+\tb{Erman thinks formal generic semantics should be defined / Thomas: what do you mean by this? / I inserted these 2 paragraphs about RDF validation semantics. Are your concerns resolved now?}
+
 A \textbf{\emph{constraint language}} is a language which is used to formulate constraints.
@@
 
-\tb{1 page / explain how typical constraints are expressed by different constraint languages}
+\tb{0.75 page / explain how typical constraints are expressed by different constraint languages}
 

### 2015-04-22 paper/paper 2/paper 2.tex
paper 2 draft finalized

@@
 XML Schema is the standard language to formulate constraints on and to validate XML documents.
-For RDF, however, there are several candidates for languages to express constraints on RDF data - but no standard one meeting the majority of RDF validation use cases.
+For RDF, however, there are several languages which can be used to express constraints on RDF data - but no standard one meeting the majority of RDF validation use cases.
 We identified requirements to formulate constraints and to validate RDF data and mapped each requirement to a constraint type.
@@
 where experts from industry, government, and academia discussed first use cases for RDF constraint\footnote{For simplicity reasons, we use the terms \emph{constraint types/constraints} instead of \emph{RDF constraint types/RDF constraints} in the rest of the paper} formulation and RDF data validation.
-In 2014, two working groups on RDF validation have been established to develop a language to express constraints on RDF data: 
+In 2014, two working groups on RDF validation have been established to focus on RDF validation: 
 the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles task group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
@@
 Bosch et al.
-identified 74 requirements to formulate constraints; each of them corresponding to a constraint type which may be expressed by at least one existing constraint language \cite{BoschNolleAcarEckert2015}.
+identified 74 requirements to formulate constraints; each of them corresponding to a constraint type which can be expressed by at least one existing constraint language \cite{BoschNolleAcarEckert2015}.
 
@@
 
-There is not the one language meeting the majority of requirements to formulate constraints and validate RDF data.
-As there are more than 10 candidate languages with different syntaxes and semantics which can be used to express constraints and to validate RDF data, 
+As there is not the one language meeting the majority of requirements to formulate constraints and to validate RDF data
+and as there are more than 10 candidate languages with different syntaxes and semantics, 
+%which can be used to express constraints and to validate RDF data, 
 %(e.g. existential and universal quantification, cardinality restrictions, and exclusive or of properties)
-the language selection heavily depends on the individual use case.
-The five most promising constraint languages on being the standard are
+language selection heavily depends on the individual use case.
+The five most promising languages on being the standard constraint language are
 \emph{Description Set Profiles (DSP)},
@@
 %min car more powerful than req. propery
-The idea behind this paper is to achieve complete RDF validation requirements coverage by representing any constraint type (corresponding to a requirement to formulate constraints and to validate RDF data) in a generic way using a lightweight vocabulary consisting of only a few terms (see section \ref{sec:vocabulary}).
+The idea behind this paper is to achieve complete RDF validation requirements coverage by representing any constraint type (each of them corresponding to a requirement to formulate constraints and to validate RDF data) in a generic way using a lightweight vocabulary consisting of only a few terms (see section \ref{sec:vocabulary}).
 
@@
 For that reason, we map constraint types to \emph{DL} statements.
-With \emph{minimum qualified cardinality restrictions} (\emph{R-75, R-81})\footnote{Requirements/constraint types are uniquely identified by alphanumeric technical identifiers like \emph{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}}, researchers from the library domain may restrict
+With \emph{minimum qualified cardinality restrictions} (\emph{R-75/81})\footnote{Requirements/constraint types are uniquely identified by alphanumeric technical identifiers like \emph{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}}, researchers from the library domain may restrict
 that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
-This constraint can be represented generically (\emph{generic constraint}) using \emph{DL} (\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}), but also specifically (\emph{specific constraint}) by multiple constraint languages:
+This constraint can be represented generically (\emph{generic constraint}) in \emph{DL} (\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}), but also specifically (\emph{specific constraint}) by multiple constraint languages:
 
@@
 and as the book \emph{The-Lord-Of-The-Rings} is a \emph{publication} (\ms{rdf:type(The-Lord-Of-The-Rings, Publication)}), 
-\emph{The-Lord-Of-The-Rings} must have at least one \emph{author} relationship to a \emph{person}.
-Constraint violations are raised either if
-\emph{The-Lord-Of-The-Rings} does not have any \emph{author} relationship, or if 
-\emph{The-Lord-Of-The-Rings} has an \emph{author} which is not a \emph{person}
+it must have at least one \emph{author} relationship to a \emph{person}.
+Constraint violations are raised either (1) if
+\emph{The-Lord-Of-The-Rings} does not have any \emph{author} relationship, or (2) if 
+it has an \emph{author} which is not a \emph{person}
 (\ms{author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Hobbit)}), 
-or if \emph{The-Lord-Of-The-Rings} has an \emph{author} for which no class is assigned
+or (3) if it has an \emph{author} for which no class is assigned
 (\ms{author(The-Lord-Of-The-Rings, Tolkien)}).
-The data is valid, however, if \emph{The-Lord-Of-The-Rings} is connected to a \emph{person} via the property \emph{author}
+In contrast, \emph{The-Lord-Of-The-Rings} is a valid \emph{publication}, if it is connected to a \emph{person} via the property \emph{author}
 (\ms{author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Person)}).
@@
 As there is no standard way to formulate constraints, 
-semantically equivalent \emph{cardinality restrictions} may be represented by multiple constraint languages with different syntax and semantics.
+semantically equivalent \emph{cardinality restrictions} may be represented by multiple constraint languages having different syntax and semantics.
 This causes confusion and weakens the common understanding between several parties about the semantics of particular constraints and therefore how to ensure high data quality. 
 Thus, when choosing constraint language \ms{$\alpha$} to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a semantically equivalent constraint formulated by any other constraint language \ms{$\beta$} (see section \ref{sec:transformations}).
-This is important in order to enhance the interoperability of constraint languages and to resolve ambiguities in the communication of RDF data producers and consumers, 
+This is important in order to enhance the interoperability of constraint languages and to resolve misunderstandings and ambiguities in the communication of RDF data producers and consumers, 
 as constraint transformations avoid the necessity to understand several constraint languages.
@@
 We provide a validation environment (available at \url{http://purl.org/net/rdfval-demo}) which enables to validate RDF data according to constraints expressed by diverse  constraint languages.
-The next step, however, is to extend the \textbf{\emph{RDF Validator}} by validating constraints of any constraint type represented by any constraint language and 
-to validate semantically equivalent \emph{specific constraints}, expressed by different constraint languages, in exactly the same way, 
+As a second step, the \emph{RDF Validator} is extended by validating RDF data conforming to constraints of any constraint type represented by any constraint language and 
+to perform validation on semantically equivalent \emph{specific constraints}, expressed by different constraint languages, in exactly the same way, 
 i.e., validation is independent from the used constraint language (see section \ref{sec:validation}). 
@@
 
-This paper aims to address two main \textbf{audiences}:
-(1) RDF data providers and consumers seeking how to ensure high quality (meta)data and thus for ways to enhance the interoperability and common understanding of constraints expressible by multiple constraint languages and
-(2) RDF practitioners thinking of how to provide aligned implementations for the validation of both existing an newly developed constraint languages.
+%This paper aims to address two main \textbf{audiences}:
+%(1) RDF data providers and consumers seeking how to ensure high data quality and thus for ways to enhance the interoperability and common understanding of constraints expressible by multiple constraint languages and
+%(2) RDF practitioners thinking of how to provide aligned implementations for the validation of both existing an newly developed constraint languages.
 The main \textbf{contributions} of this paper are:
@@
 (2) we developed a vocabulary to describe constraints of any RDF constraint type generically and specified its underlying semantics (section \ref{sec:vocabulary}),
-(3) we show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful (section \label{ref:transformations}), and
+(3) we show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful (section \ref{sec:transformations}), and
 (4) we explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages (section \ref{sec:validation}).

### 2015-04-26 paper/paper7/paper7.tex
set focus on constraint type classification

@@
   \vspace{0cm}
-  \begin{tabular}{r l}
+	\begin{center}
+  \begin{tabular}{c l}
 
@@
   \end{tabular}
-  %\linebreak
+	\end{center}
 }
@@
 In this paper, we propose a system to classify RDF constraints and RDF constraint types, which in most cases correspond to RDF validation requirements.
-Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary\tb{vocabulary-independent}. 
+Constraints are instantiated from constraint types in order to validate both metadata and data independently from used vocabularies. 
 Within the context of a complex and complete real world running example within the community around research data for the \emph{social, behavioural, and economic (SBE) sciences}, we prove the claim that the developed classification system perfectly applies for diverse vocabularies.
-We show how data in rectangular format and metadata on record-unit data sets (i.e., data about individuals, households, businesses) or more specifically person-level data sets, aggregated data sets, thesauri, and statistical classifications are represented in RDF and how therefore reused vocabularies are interrelated.\tb{record-unit or more specific person-level data sets}
+We show how data in rectangular format and metadata on person-level or more generally record-unit data sets (i.e., data about individuals, households, businesses), aggregated data sets, thesauri, and statistical classifications are represented in RDF and how therefore reused vocabularies are interrelated.
 We explain how \emph{SBE} (meta)data is validated against constraints to ensure high quality and trust.
 We exhaustively evaluated the metadata quality of large real world aggregated, person-level, and thesauri data sets (more than 4.2 billion triples and 15 thousand data sets) by means of constraints of the majority of constraint types.
-\tb{DCAT und XKOS nur im future work}
+\tb{DCAT und XKOS nur in future work}
 \keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, RDF Data Cube Vocabulary, Rectangular Data, SKOS, XKOS, Linked Data, Semantic Web}
@@
 %The remainder of the paper is structured as follows.
-For the extensive evaluation, we implemented 53 constraint types by instantiating 212 constraints on \emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{XKOS}, and \emph{PHDD} data sets (section \ref{implementation}).
+For the extensive evaluation, we implemented 53 constraint types by instantiating 213 constraints on \emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{XKOS}, and \emph{PHDD} data sets (section \ref{implementation}).
 First, several \emph{SBE} domain experts evaluated the correctness (i.e., the gold standard) of all constraints and therefore the generic applicability of the developed constraint classification system.
@@
 
-\section{RDF Constraints Classification}
+\section{Classification of Constraint Types and Constraints}
 \label{classification}
@@
 Bosch et al.
-identified 74 requirements to formulate RDF constraints (e.g.
+identified 76 requirements to formulate RDF constraints (e.g.
 \emph{R-75, R-81: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}\cite{BoschNolleAcarEckert2015}.
@@
 %\emph{data model specific constraint types} (e.g. \emph{data model consistency})
-The complete set of \emph{constraint types} ($\mathcal{CT}$) encompasses two disjoint \textbf{\emph{sets of constraint types}}:
-\begin{enumerate}
-	\item $\mathcal{CT}_{C}$: \emph{Content-Driven Constraint Types}\tb{complex constraints / zahlen interpretierbar / in einem bestimten vokabulare werden viele basic constraints verletzt / daten haben bessere qualität vokabular / wichtigkeit constraint languages, dass complexe constraints beschrieben}
-	\item $\mathcal{CT}_{T}$: \emph{Technology-Driven Constraint Types}\tb{basic constraints / welche constraints können automatisch abgeleitet werden / bestimmte constraints werden in den vokabularen definiert bzw sehr leicht zu implementieren wäre / studie ohne daten macht keinen sinn --> cardinality restriction / alle constraints die mit rdf + rdfs + owl definiert werden können / vokabukare werden heutzutage mit rdf / rdfs / owl beschrieben / constraints die typischerweise hinterlegt werden / constraints die amn als vokabular}
-\end{enumerate}
-
-\tb{große datenbestände untersuchen um ein besseres verständnis zu bekommen / liste von constraints / jedes einzelne constraint für jeded einzelne vokabular severity level / warum severity was bringt das}
-
-$\mathcal{CT}_{C}$ (\emph{Content-Driven Constraint Types}) is the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of vocabularies' data models (section \ref{content-driven-validation}).
-Therefore, domain experts may formulate $\mathcal{CT}_{C}$ constraints manually in prose English which is technically expressed by a constraint language afterwards.
-For assessing the quality of thesauri, e.g., we concentrate on the graph-based structure and apply graph- and network-analysis techniques (constraint type: \emph{structure}). 
-A thesaurus, e.g., should not contain many orphan concepts (concepts without any associative or hierarchical relations) lacking valuable context information for search and retrieval.  
-$\mathcal{CT}_{T}$ (\emph{Technology-Driven Constraint Types}) is the set of constraints which can be generated completely automatically out of vocabularies' data models (section \ref{technology-driven-validation}).
-With \emph{minimum qualified cardinality restrictions} (\emph{R-74}), e.g., one can restrict that
-a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column} (in DL: \ms{TableStructure $\sqsubseteq$ $\geq$1 column.Column})\footnote{For simplicity reasons, we do not use namespace prefixes in DL statements.}.
-
-\emph{SBE} experts \tb{todo / wieviele constraints welche klasse} determined the default \textbf{\emph{severity level}} (corresponds to requirement \emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
-We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ to $\mathcal{SL}_{2}$.
-According to the constraints' default severity level the complete set of constraints ($\mathcal{C}$) encompasses three disjoint \textbf{\emph{sets of constraints}}:
-\begin{itemize}
-	\item $\mathcal{SL}_{0}$: set of constraints with severity level \emph{informational}
-	\item $\mathcal{SL}_{1}$: set of constraints with severity level \emph{warning}
-	\item $\mathcal{SL}_{2}$: set of constraints with severity level \emph{error}
-\end{itemize}
-Violations of $\mathcal{SL}_{0}$ constraints point to possible data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies. 
-Data not conforming to $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is syntactically or semantically not correctly represented.
-The difference between $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is that $\mathcal{SL}_{1}$ invalid data could be
-whereas $\mathcal{SL}_{1}$ invalid data cannot be processed further. 
-Although, we provide default severity levels for each constraint, users should be able to specify constraints' severity levels according to their individual needs, i.e., use case specific severity levels.
-
-We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as first appendix of this paper) in which we describe 212 constraints (classified as 53 constraint types) to validate rectangular data (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}), and therefore apply the proposed classification system to several vocabularies to represent both data and metadata \cite{BoschZapilkoWackerowEckert2015}.
+
+We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as first appendix of this paper) in which we describe 213 constraints (classified as 53 distinct constraint types) to validate rectangular data (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}), and therefore apply the proposed classification system to several vocabularies to represent both data and metadata \cite{BoschZapilkoWackerowEckert2015}.
 In this section, we describe constraints, which are important to ensure \emph{SBE} (meta)data quality, 
@@
 
+\subsection{Classification of Constraint Types}
+
+The complete set of \emph{constraint types} ($\mathcal{CT}$) encompasses three disjoint \emph{sets of constraint types}:
+\begin{enumerate}
+	\item \textbf{$\mathcal{CT}_{B}$: \emph{Basic Constraint Types}}
+	\item \textbf{$\mathcal{CT}_{S}$: \emph{Simple Constraint Types}}
+	\item \textbf{$\mathcal{CT}_{C}$: \emph{Complex Constraint Types}}
+\end{enumerate}
+
+The modeling languages \emph{RDF}, \emph{RDFS}, and \emph{OWL} are typically used to define vocabularies.
+\emph{Basic constraint types} ($\mathcal{CT}_{B}$) 
+denotes the set of constraint types whose constraints 
+can be extracted completely automatically out of vocabularies.
+As vocabularies have been specified using \emph{RDF}, \emph{RDFS}, and \emph{OWL},
+\emph{basic constraints} ensure that the data is consistent with the intended syntaxes, semantics, and integrity of vocabularies' data models.
+%The {\em existential quantification} (\emph{R-86}) 
+%\ms{Study $\equiv$ $\exists$ product.LogicalDataSet} (\emph{DL}), e.g., restricts studies to contain at least one data set which is expressible in OWL 2:
+\emph{Minimum qualified cardinality restrictions} (\emph{R-74}), e.g., guarantee that individuals of given classes are connected by particular properties to at least n different individuals/literals of certain classes or data ranges.
+This way, it is expressible in OWL 2 that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:
+\begin{ex}
+[   a owl:Restriction ; rdfs:subClassOf TableStructure ;
+    owl:minQualifiedCardinality 1 ;
+    owl:onProperty column ;
+    owl:onClass Column ] .
+\end{ex}
+
+\emph{Simple constraint types} ($\mathcal{CT}_{S}$) is the set of constraint types whose constraints can be easily defined without much effort in addition to $\mathcal{CT}_{B}$ constraints.
+The {\emph{data property facets} (\emph{R-46}) $\mathcal{CT}_{S}$ constraint type enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
+The abstract of series/studies, e.g., should have a minimum length ($\mathcal{SL}_{1}$).
+
+\emph{Complex constraint types} ($\mathcal{CT}_{C}$) encompass constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
+Complex constraints show the importance of constraint languages enabling to describe complex constraints.
+For assessing the quality of thesauri, e.g., we concentrate on the graph-based structure and apply graph- and network-analysis techniques.
+An example of such \emph{structure} constraints is that 
+a thesaurus should not contain many orphan concepts, i.e., concepts without any associative or hierarchical relations, lacking context information valuable for search.
+
+\tb{refer to evaluation / what do we want to know?}
+
+\subsection{Classification of Constraints}
+
+\emph{SBE} experts determined the default \textbf{\emph{severity level}} (\emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
+We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ to $\mathcal{SL}_{2}$.
+According to the constraints' default severity level the complete set of constraints ($\mathcal{C}$) encompasses three disjoint \emph{sets of constraints}:
+\begin{itemize}
+	\item $\mathcal{SL}_{0}$: set of constraints with \textbf{severity level \emph{informational}}
+	\item $\mathcal{SL}_{1}$: set of constraints with \textbf{severity level \emph{warning}}
+	\item $\mathcal{SL}_{2}$: set of constraints with \textbf{severity level \emph{error}}
+\end{itemize}
+Violations of $\mathcal{SL}_{0}$ constraints point to desirable data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies. 
+Data not conforming to $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is syntactically and/or semantically not correctly represented.
+The difference between $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is that data, not conforming to $\mathcal{SL}_{1}$ but conforming to $\mathcal{SL}_{2}$ constraints, could be processed further,
+whereas data, not corresponding to $\mathcal{SL}_{2}$ constraints, cannot be processed further after validation. 
+Although, we provide default severity levels for each constraint, validation environments should enable users to adapt constraints' severity levels according to their individual needs.
+
+As $\mathcal{CT}_{B}$ constraints are derived from explicitly stated semantics of vocabularies' data models, 
+default severity levels of $\mathcal{CT}_{B}$ constraints are in most cases very strong ($\mathcal{SL}_{2}$) and 
+in average stronger than severity levels of $\mathcal{CT}_{S}$ and $\mathcal{CT}_{C}$ constraints.
+As a consequence, violating many $\mathcal{CT}_{B}$ constraints is an indicator for bad data quality\footnote{For simplicity reasons, we only assign severity levels to $\mathcal{CT}_{B}$ constraints when they differ from $\mathcal{SL}_{2}$.}.
+
 %
@@
 
-\subsection{Technology-Driven Constraint Types}
-\label{technology-driven-validation}
-
-$\mathcal{CT}_{T}$ constraints can be directly and automatically derived from explicitly stated syntax and semantics of vocabularies' data models.
-Thus, associated default severity levels are in most cases very strong ($\mathcal{SL}_{2}$).
-
-%\textbf{Constraints Derived From Vocabularies.}
-\textbf{Vocabulary.}
-One should not invent new or use deprecated terms (e.g. \emph{disco:containsVariable}) of vocabularies (\emph{vocabulary}).
-\emph{Property domain} (\emph{R-25, R-26}) and \emph{range} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties.
-Only \emph{phdd:Tables}, e.g., can have \emph{phdd:isStructuredBy} relationships (\ms{$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table}) and
-\emph{xkos:belongsTo} relationships can only point to \emph{skos:Concepts} (\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}).
+\section{Basic Constraint Types}
+\label{basic-constraint-types}
+
+As \emph{RDFS} and \emph{OWL} are typically used to define vocabularies, \emph{RDFS} and \emph{OWL} reasoning may be performed prior to validation. 
+Reasoning and validation are indeed very closely related. 
+\emph{Reasoning} is the process of determining what follows from what has been stated.
+%Both should be possible: (1) validation with reasoning and (2) validation without reasoning. 
+We divide the whole set of \emph{basic constraint types} ($\mathcal{CT}_{B}$) into two disjoint sets to investigate the affect of reasoning to the validation process: 
+\begin{enumerate}
+	\item $\mathcal{C}_B ^{\mathcal{R}}$ corresponds to axioms in \emph{OWL 2} and denotes the set of constraint types which enable performing reasoning prior to validation, especially when not all the knowledge is explicit (section \ref{basic-constraint-types-with-reasoning}).
+  \item $\overline{\mathcal{C}_B ^{\mathcal{R}}}$  denotes the set of constraint types for which reasoning cannot be done or does not improve the result in any obvious sense (section \ref{basic-constraint-types-without-reasoning}).
+\end{enumerate}
+
+\subsection{Basic Constraint Types with Reasoning}
+\label{basic-constraint-types-with-reasoning}
+
+Validation environments should enable users to decide if they wish to perform reasoning prior to validation.
+Reasoning as an optional pre validation step is beneficial for RDF validation as 
+(1) it may resolve constraint violations and  
+(2) it may cause useful constraint violations.
 A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
-Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets} (\ms{Catalog $\sqsubseteq$ $\forall$ dataset.Dataset}).
-Out-dated classes and properties of previous vocabulary versions can be marked as deprecated.
-The constraint types \emph{context-specific valid classes and properties} (\emph{R-209; R-210}) can be used to specify which classes and properties are valid in which context - here a given vocabulary version.
-Many properties are not necessarily required but \emph{recommended} within a particular context (\emph{R-72}).
-The property {\em skos:notation}, e.g., is not mandatory for {\em disco:Variable}s, but recommended to represent variable names.
-\emph{R-223} serves to make sure that all literal values are valid with regard to their datatypes.
-Thus, all date values (e.g.
-{\em disco:startDate}, {\em disco:endDate}, {\em dcterms:date}) must be of the datatype \emph{xsd:date} and \emph{xsd:nonNegativeInteger} values (e.g.
-\emph{disco:frequency}) do not have to be negative.
-
-\textbf{Existential Quantifications.}
-\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals/literals of certain types.
-If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
-If metadata on data files, including the actual data, is missing (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the study is not sufficient.
-Case quantity measures how many cases are collected for a study.
-High case and variable quantities are indicators for high statistical quality and comprehensiveness of the underlying study ($\mathcal{SL}_{1}$).
-Variables should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
+%Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets}:
+%\begin{DL}
+%Catalog $\sqsubseteq$ $\forall$ dataset.Dataset
+%\end{DL}
+Consider the following DL knowledge base $\mathcal{K}$\footnote{A knowledge base is a collection of formal statements which corresponds to \emph{facts} or what is known explicitly.
+For simplicity reasons, we only write namespace prefixes in DL statements to avoid ambiguities.}:
+
+\begin{center}
+\begin{DL} 
+$\mathcal{K}=\{$ &\ms{LogicalDataSet $\sqsubseteq$ dcat:DataSet},\\
+ &\ms{LogicalDataSet $\sqsubseteq \forall$ aggregation.qb:DataSet},\\
+ %&\ms{dcat:DataSet $\equiv$ $\exists$ dcat:distribution . dcat:Distribution},\\
+ &\ms{LogicalDataSet( logical-data-set )},\\
+ &\ms{aggregation( logical-data-set, aggregated-data-set )}
+ \}\\ 
+\end{DL}
+\end{center}
+
+As we know that only person-level data sets (\emph{disco:LogicalDataSet}) can derive (\emph{disco:aggregation}) aggregated data sets (\emph{qb:DataSet}), 
+{\em logical-data-set} is a \emph{disco:LogicalDataSet}, 
+and \emph{aggregated-data-set} is derived from \emph{logical-data-set},
+we conclude that \emph{aggregated-data-set} must be a \emph{qb:DataSet}.
+As \emph{aggregated-data-set} is not explicitly defined to be a \emph{qb:DataSet}, however, a constraint violation is raised.
+If we perform reasoning prior to validation, the constraint violation is resolved, as the implicit triple \ms{qb:DataSet(aggregated-data-set)} is inferred.
+
+Reasoning may also cause constraint violations which are needed to enhance data quality.
+With \emph{subsumption} (\emph{R-100}), one can state that \emph{disco:LogicalDataSet} is a sub-class of \emph{dcat:DataSet}, 
+i.e., each person-level data set is also a catalog data set.
+Thus, constraints on catalog data sets are also validated for person-level data sets;
+e.g., the \emph{existential quantification} below restricting that person-level data sets must have a distribution:
+
+\begin{center}
+\begin{DL} 
+$\mathcal{K}=\{$ 
+ &\ms{DataSet $\equiv$ $\exists$ distribution.Distribution},\\
+&\ms{Variable $\equiv$ $\exists$ concept.Concept}
+ \}\\ 
+\end{DL}
+\end{center}
+
+We extend $\mathcal{K}$ by \emph{existential quantifications} (\emph{R-86}) enforcing that instances of given classes must have some property relation to individuals/literals of certain types.
+Variables, e.g., should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
 %The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
-The variable \emph{Education at pre-school},.e.g, is associated with the theoretical concept \emph{Child Care}. 
-The constraint's severity level is weak, as in most cases research can be continued without having information about theoretical concepts.
-
-\textbf{Cardinality Restrictions on Properties and Language Tags.}
+The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
+The default severity level of the constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
+%If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
+%If metadata on data files, including the actual data, is missing (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the study is not sufficient.
+%Case quantity measures how many cases are collected for a study.
+%High case and variable quantities are indicators for high statistical quality and comprehensiveness of the underlying study ($\mathcal{SL}_{1}$).
+
+\begin{center}
+\begin{DL} 
+$\mathcal{K}=\{$ 
+  &\ms{fundedBy $\sqsubseteq$ contributor}
+ \}\\ 
+\end{DL}
+\end{center}
+
+By stating that \emph{disco:fundedBy} is a sub property of \emph{dcterms:contributor},
+the {\em sub property} (\emph{R-54, R-64}) above assures that if a series is funded by an organization, then the organization must also contribute to the series.
+In case the \emph{sub-property} is applied without reasoning and $\mathcal{K}$ contains the triple \ms{disco:fundedBy} \ms{(EU-SILC,} \ms{organization)},
+a constraint violation is thrown if $\mathcal{K}$ does not explicitly include the triple \ms{dcterms:contributor} \ms{(EU-SILC,} \ms{organization)}.
+If the \emph{sub property} is applied with reasoning, on the other side, the latter triple is derived which resolves the constraint violation.
+
+%\begin{DL}
+%fundedBy $\sqsubseteq$ contributor
+%\end{DL}
+
+%\emph{Asymmetric object properties} (\emph{R-62}) restrict that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}.
+%Such constraints are defined for each object property for which a semantically equivalent object property pointing from the other direction would also be possible but is not defined within the vocabulary.
+%A \emph{disco:Variable}, e.g., may be based on (\emph{disco:basedOn}) a \emph{disco:RepresentedVariable}.
+%A \emph{disco:RepresentedVariable}, however, cannot be based on a \emph{disco:Variable} (\ms{$disco:basedOn \sqcap disco:basedOn^{-} \sqsubseteq \bot$}).
+
+%\emph{Property domain} (\emph{R-25, R-26}) and \emph{range} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties.
+%Only \emph{phdd:Tables}, e.g., can have \emph{phdd:isStructuredBy} relationships and
+%\emph{xkos:belongsTo} relationships can only point to \emph{skos:Concepts}:
+%\begin{DL}
+%$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table \\
+%$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept
+%\end{DL}
+
+%\begin{center}
+%\begin{DL} 
+%$\mathcal{K}=\{$ 
+  %&\ms{TableStructure $\sqsubseteq$ $\geq$1 column.Column}, \\
+	%&\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}, \\
+	%&\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition} \\ 
+	%&\ms{$\sqcap$ $\leq$1 structure.DataStructureDefinition}
+ %\}\\ 
+%\end{DL}
+%\end{center}
+
+%\textbf{Cardinality Restrictions on Properties.}
 %An \emph{existential quantification} (\emph{R-86}) contains all those individuals that are connected by a property to individuals/literals of given classes or data ranges.
 %Every \emph{qb:SliceKey}, e.g., must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}).
-\emph{Minimum/maximum/exact qualified cardinality restrictions} (\emph{R-74, R-75, R-76}) contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals of particular classes or data ranges.
-A \emph{phdd:TableStructure}, e.g., has (\emph{phdd:column}) at least one \emph{phdd:Column} (\ms{TableStructure $\sqsubseteq$ $\geq$1 column.Column}),
-a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}) (\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}), and a \emph{qb:DataSet} is structured by (\emph{qb:structure}) exactly one \emph{qb:DataStructureDefinition} (\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition $\sqcap$ $\leq$1 structure.DataStructureDefinition}).
+%\emph{Minimum/maximum/exact qualified cardinality restrictions} (\emph{R-74, R-75, R-76}) contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals of particular classes or data ranges.
+%A \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column},
+%a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}), and a \emph{qb:DataSet} is structured by (\emph{qb:structure}) exactly one \emph{qb:DataStructureDefinition}.
 %DATA-CUBE-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-
@@
 %\textbf{Language Tag Cardinality.}
-For data properties, it may be desirable to restrict that values of predefined languages must be present for determined number of times (\emph{R-48, R-49}):
-(1) Some controlled vocabularies contain literals in natural language, but without information what language has actually been used. 
-(2) Language tags must conform to language standards. 
-(3) Some thesaurus concepts are labeled in only one, others in multiple languages.
-It may be desirable to have each concept labeled in each of the languages that are also used on the other concepts.
-Although not always possible, incompleteness of language coverage for some concepts may indicate shortcomings of thesauri
-\cite{MaderHaslhoferIsaac2012}.
-
-\textbf{Disjointness and Allowed Values.}
+
+\subsection{Basic Constraint Types without Reasoning}
+\label{basic-constraint-types-without-reasoning}
+
+$\overline{\mathcal{C}_B ^{\mathcal{R}}}$  denotes the set of constraint types for which reasoning cannot be done or does not improve the result in any obvious sense.
+The constraint type \emph{vocabulary} guarantees that users do not invent new or use deprecated terms of vocabularies.
+%Out-dated classes and properties of previous vocabulary versions can be marked as deprecated.
+%The constraint types \emph{context-specific valid classes and properties} (\emph{R-209; R-210}) can be used to specify which classes and properties are valid in which context - here a given vocabulary version.
+\emph{Value is valid for datatype} (\emph{R-223}) constraints serve to make sure that all literal values are valid with regard to their datatypes - as stated in the vocabularies.
+Thus, it is checked that all date values (e.g., {{\em dcterms:date}, \em disco:startDate}, {\em disco:endDate}) are actually of the datatype \emph{xsd:date} and that \emph{xsd:nonNegativeInteger} values (e.g.
+\emph{disco:frequency}) are not negative.
+Depending on property datatypes, two different literal values have
+a specific ordering with respect to operators like \textless  (\emph{R-43: literal value comparison}).
+Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}).
+
+\begin{center}
+\begin{DL} 
+$\mathcal{K}=\{$ 
+	&\ms{isStructuredBy $\sqsubseteq$ $\neg$ column}, \\
+	&\ms{TableDescription $\sqcap$ ColumnDescription $\sqsubseteq$ $\perp$}, \\
+	&\ms{CategoryStatistics $\equiv$} \\
+	&\ms{$\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString}
+ \}\\ 
+\end{DL}
+\end{center}
+
 All properties, not having the same domain and range types, are defined to be pairwise disjoint
-(\emph{R-9: disjoint properties}), i.e., no individual \emph{x} can be connected to an individual/literal \emph{y} by disjoint properties like \emph{phdd:isStructuredBy} and \emph{phdd:column} ($isStructuredBy \sqsubseteq \neg column$).
-All \emph{XKOS} classes are pairwise disjoint (\emph{R-7: disjoint classes}; e.g. \ms{ClassificationLevel $\sqcap$ ConceptAssociation $\sqsubseteq$ $\perp$}),
+(\emph{R-9: disjoint properties}), i.e., no individual \emph{x} can be connected to an individual/literal \emph{y} by disjoint properties (e.g., \emph{phdd:isStructuredBy} and \emph{phdd:column}).
+All \emph{PHDD} classes (e.g., \emph{phdd:TableDescription}, \emph{phdd:ColumnDescription}) are pairwise disjoint (\emph{R-7: disjoint classes}),
 i.e., individuals cannot be instances of multiple disjoint classes.
-It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values.  
-\emph{Allowed values} (\emph{R-30, R-37}) for properties can be IRIs (matching one or multiple patterns), any literals, allowed literals (e.g.
+It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values (\emph{R-30/37: allowed values}). 
+%\emph{Allowed values} (\emph{R-30, R-37}) for properties can be IRIs (matching one or multiple patterns), any literals, allowed literals (e.g.
 'red' 'blue' 'green'), and typed literals of one or multiple type(s) (e.g.
 \emph{xsd:string}).
-\emph{disco:CategoryStatistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString} (\ms{CategoryStatistics $\equiv$ $\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString}).
-
-\textbf{Validation and Reasoning.}
-Some constraint types enable performing reasoning prior to validation which may resolve or cause constraint violations.
-With \emph{subsumption} (\emph{R-100}), one can state that \emph{xkos:ClassificationLevel} is a sub-class of \emph{skos:Collection}, i.e., each \emph{xkos:ClassificationLevel} must also be part of the \emph{skos:Collection} class extension (\ms{ClassificationLevel $\sqsubseteq$ Collection}).
-With \emph{sub properties} (\emph{R-54, R-64}), one can state that \emph{disco:fundedBy} is a sub-property of \emph{dcterms:contributor} - i.e., if a study is funded by an organization, then this organization contributed to this study (\ms{fundedBy $\sqsubseteq$ contributor}).
-%\emph{Asymmetric object properties} (\emph{R-62}) restrict that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}.
-%Such constraints are defined for each object property for which a semantically equivalent object property pointing from the other direction would also be possible but is not defined within the vocabulary.
-%A \emph{disco:Variable}, e.g., may be based on (\emph{disco:basedOn}) a \emph{disco:RepresentedVariable}.
-%A \emph{disco:RepresentedVariable}, however, cannot be based on a \emph{disco:Variable} (\ms{$disco:basedOn \sqcap disco:basedOn^{-} \sqsubseteq \bot$}).
+\emph{disco:CategoryStatistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString}.
+Validation should \emph{exploit sub-super relations} in vocabularies (\emph{R-224}).
+If \emph{dcterms:coverage} and one of its sub-properties (\emph{dcterms:spatial}, \emph{dcterms:temporal}) are given,
+it is checked that \emph{dcterms:coverage} is not redundant with its sub-properties 
+which may indicate when the data is verbose/redundant or expressed at a too general level.
+
+\section{Simple Constraint Types}
+
+$\mathcal{CT}_{S}$ is the set of constraint types whose constraints can be easily defined without much effort in addition to $\mathcal{CT}_{B}$ constraints.
+For data properties, it may be desirable to restrict that values of predefined languages must be present for determined number of times (\emph{R-48/49: language tag cardinality}):
+(1) It is checked if literal language tags are set.
+Some controlled vocabularies, e.g., contain literals in natural language, but without information what language has actually been used ($\mathcal{SL}_{1}$).
+(2) Language tags must conform to language standards ($\mathcal{SL}_{2}$). 
+(3) Some thesaurus concepts are labeled in only one, others in multiple languages. 
+It may be desirable to have each concept labeled in each of the languages that are also used on the other concepts,
+as language coverage incompleteness for some concepts may indicate shortcomings of thesauri ($\mathcal{SL}_{0}$)
+\cite{MaderHaslhoferIsaac2012}.
+
+%\textbf{Validation and Reasoning.}
 \emph{Default values} (\emph{R-31, R-38}) for objects/literals of given properties are inferred automatically when properties are not present in the data.
 The value \emph{true} for the property {\em disco:isPublic} indicates that a {\em disco:LogicalDataSet} can be accessed by anyone.
-Per default, however, access to data sets should be restricted (\emph{false}).
-Validation should \emph{exploit sub-super relations} in vocabularies (\emph{R-224}).
-If \emph{dcterms:coverage} and one of its sub-properties (\emph{dcterms:spatial}, \emph{dcterms:temporal}) are present,
-it is checked that \emph{dcterms:coverage} is not redundant with its sub-properties. 
-This validation can indicate when the data is verbose (redundant) or expressed at a too general level and could thus be improved.
-
-\subsection{Content-Driven Constraint Types}
-\label{content-driven-validation}
-
-In this sub-chapter, we assign default severity levels to and describe constraints of diverse $\mathcal{CT}_{C}$ constraint types 
-to ensure that the data is consistent with the intended syntax, semantics, and integrity of vocabularies' data models.
-
+Per default, however, access to data sets should be restricted (\emph{false}) ($\mathcal{SL}_{0}$).
+Many properties are not necessarily required but \emph{recommended} within a particular context (\emph{R-72}).
+The property {\em skos:notation}, e.g., is not mandatory for {\em disco:Variable}s, but recommended to represent variable names ($\mathcal{SL}_{0}$).
+Percentage values are only valid when they are within the literal range of 0 and 100 (\emph{R-45: literal ranges}; $\mathcal{SL}_{2}$)
+which is checked for \emph{disco:percentage} standing for the number of cases of a given code in relation to the total number of cases for a particular variable.
+
+\begin{center}
+\begin{DL} 
+$\mathcal{K}=\{$ 
+	&\ms{(funct identifier$\sp{\overline{\ }})$, identifier keyfor Resource}
+ \}\\ 
+\end{DL}
+\end{center}
+
+It is often useful to declare a given (data) property as the \emph{primary key} (\emph{R-226}) of a class, so that a system can enforce uniqueness and build URIs from user inputs and imported data. 
+In \emph{Disco}, resources are uniquely identified by the property \emph{adms:identifier},
+which is therefore inverse-functional,
+i.e., for each \emph{rdfs:Resource x}, there can be at most one distinct resource \emph{y} such that \emph{y} is connected by \emph{adms:identifier$\sp{\overline{\ }}$} to \emph{x} ($\mathcal{SL}_{2}$).
+%\begin{DL}
+%$(\ms{funct identifier}\sp{\overline{\ }})$
+%\end{DL} 
+Keys, however, are even more general than \emph{inverse-functional properties} (\emph{R-58}),
+as a key can be a data property, an object property, or a chain of properties \cite{Schneider2009}.
+Thus and as there are different sorts of key, and as keys can lead to undecidability, 
+\emph{DL} is extended with the construct \emph{keyfor} \cite{Lutz2005} which is implemented by the \emph{OWL 2} \emph{hasKey} construct.
+%\emph{OWL 2} \emph{hasKey} implements \emph{keyfor} ($\mathcal{SL}_{2}$) and thus can be used to identify resources uniquely, to merge resources with identical key property values, and to recognize constraint violations.
+%\begin{DL}
+%identifier \ms{keyfor} Resource
+%\end{DL}
+
+\section{Complex Constraint Types}
+\label{complex-constraint-types}
+
+%\textcolor{red}{
+%In this sub-chapter, we assign default severity levels to and describe constraints of diverse $\mathcal{CT}_{C}$ constraint types 
+%to ensure that the data is consistent with the intended syntax, semantics, and integrity of vocabularies' data models.
+%}
 %\textbf{Observations of Aggregated Data Sets.}
@@
 
-\textbf{Data Model Consistency.}
-The purpose of some constraints is to ensure the integrity of
-the data according to intended data model semantics (\emph{data model consistency}).
+$\mathcal{CT}_{C}$ denotes the set of constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
+\emph{Data model consistency} constraints ensure the integrity of
+the data according to the intended semantics of vocabularies.
 Every \emph{qb:Observation}, e.g., must have a value for each dimension
@@
 \emph{qb:Observation} \emph{O}, then the \emph{qb:DataSet} corresponding to \emph{O} must be \emph{D} ($\mathcal{SL}_{1}$).
-Relative frequencies of variable codes are calculated correctly, if the cumulative percentage (\emph{disco:cumulativePercentage}) of a given code exactly matches the cumulative percentage of the previous code
-plus the percentage value (\emph{disco:percentage}) of the current code ($\mathcal{SL}_{2}$).
+%Relative frequencies of variable codes are calculated correctly, if the cumulative percentage (\emph{disco:cumulativePercentage}) of a given code exactly matches the cumulative percentage of the previous code
+%plus the percentage value (\emph{disco:percentage}) of the current code ($\mathcal{SL}_{2}$).
+{\em Mathematical Operations} (\emph{R-41, R-42}; e.g. date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
+The sum of percentage values of all variable codes, e.g., must exactly be 100 ($\mathcal{SL}_{2}$)
+and the minimum absolute frequency of all variable codes do not have to be greater than the maximum ($\mathcal{SL}_{2}$).
 
 %\textbf{Hierarchies and Ordering.}
-\textbf{Structure and Ordering.}
-For assessing the quality of \emph{SKOS} vocabularies, we concentrate on graph-based structures and apply graph- and network-analysis techniques (\emph{structure}) like 
-(1) a thesaurus should provide entry points (top concepts) to the data to provide efficient access and guidance for human users,
-(2) concepts, internal to the tree, should not be indicated as top concepts, and
-(3) a thesaurus should not contain many orphan concepts 
-(concepts without any associative or hierarchical relations) lacking valuable context information for retrieval.
+%\textbf{Structure and Ordering.}
+%For assessing the quality of \emph{SKOS} vocabularies, we concentrate on graph-based structures and apply graph- and network-analysis techniques (\emph{structure} constraints) like 
+%(1) a thesaurus should provide entry points (top concepts) to the data to provide efficient access and guidance for human users,
+%(2) concepts, internal to the tree, should not be indicated as top concepts, and
+%(3) a thesaurus should not contain many orphan concepts 
+%(concepts without any associative or hierarchical relations) lacking valuable context information for retrieval.
 %, as, e.g., no hierarchical query expansion can be performed on search terms to find documents with more general content.) \cite{MaderHaslhoferIsaac2012}.
-Objects/literals can be declared to be \emph{ordered} (\emph{R-121, R-217}) for given properties.
-Variables, questions, and codes, e.g., are typically organized in a particular order. 
-If codes (\emph{skos:Concept}) should be ordered, they must be members (\emph{skos:memberList}) in an ordered collection (\emph{skos:OrderedCollection}), the variable's code list.
-
-\textbf{Comparison.}
-A very common research question is to compare variables of multiple studies or countries (\emph{comparison}).
-To compare variables, 
-(1) variables and (2) variable definitions must be present,
-(3) code lists must be structured properly,
-(4) for each code an associated category must be specified, and
-(5) code lists must either be identical or at least similar.
-If a researcher wants to get a first overview over comparable variables (use case 1), 
-covering the first three constraints may be sufficient.
-Thus, the severity level of the first three constraints is stronger ($\mathcal{SL}_{2}$) than for the last two constraints ($\mathcal{SL}_{1}$ and $\mathcal{SL}_{0}$).
-If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the remaining two constraints is getting more serious.
-
-\textbf{Unique Identification.}
-It is often useful to declare a given (data) property as the \emph{primary key} (\emph{R-226}) of a class, so that a system can enforce uniqueness and also automatically build URIs from user inputs and imported data.
-In \emph{Disco}, resources are uniquely identified by the property \emph{adms:identifier},
-which is therefore inverse-functional
-$(\ms{funct identifier}\sp{\overline{\ }})$,
-i.e.
-for each \emph{rdfs:Resource x}, there can be at most one distinct \emph{rdfs:Resource y} such that \emph{y} is connected by \emph{adms:identifier$\sp{\overline{\ }}$} to \emph{x} ($\mathcal{SL}_{2}$).
-Keys, however, are even more general than \emph{inverse-functional properties} (\emph{R-58}),
-as a key can be a data, an object property, or a chain of properties \cite{Schneider2009}.
-For this generalization purposes, as there are different sorts of key, and as keys can lead to undecidability, 
-DL is extended with \emph{key boxes} and the construct \emph{keyfor} (\ms{identifier \ms{keyfor} Resource}) \cite{Lutz2005}.
-OWL 2 \emph{hasKey} implements \emph{keyfor} ($\mathcal{SL}_{2}$) and thus can be used to identify resources uniquely, to merge resources with identical key property values, and to recognize constraint violations.
-
-\textbf{Membership in Controlled Vocabularies.}
+
+A very common research question is to compare variables of multiple studies or countries (constraint type: \emph{comparison}).
+To compare variables 
+(1) their code lists must be structured properly and
+(2) their code lists must either be identical or at least similar.
+If a researcher only wants to get a first overview over comparable variables (use case 1), 
+covering the first constraint may be sufficient.
+Thus, the severity level of the first constraint is stronger ($\mathcal{SL}_{2}$) than the one for the second constraint ($\mathcal{SL}_{0}$).
+If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the second constraint is getting more serious
+and the user may raise its severity level.
+%\textbf{Comparison.}
+%A very common research question is to compare variables of multiple studies or countries (constraint type: \emph{comparison}).
+%To compare variables, 
+%(1) variables and (2) variable definitions must be present,
+%(3) code lists must be structured properly,
+%(4) for each code an associated category must be specified, and
+%(5) code lists must either be identical or at least similar.
+%If a researcher wants to get a first overview over comparable variables (use case 1), 
+%covering the first three constraints may be sufficient.
+%Thus, the severity level of the first three constraints is stronger ($\mathcal{SL}_{2}$) than for the last two constraints ($\mathcal{SL}_{1}$ and $\mathcal{SL}_{0}$).
+%If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the remaining two constraints is getting more serious.
+
+%\textbf{Membership in Controlled Vocabularies.}
 In many cases, resources must be \emph{members of controlled vocabularies} (\emph{R-32}).
@@
 Thus, summary statistics can only have \emph{disco:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType}, a \emph{skos:ConceptScheme} ($\mathcal{SL}_{2}$).
-
-\textbf{Constraints on Properties.}
+Objects/literals can be declared to be ordered for given properties (\emph{R-121/217: ordering}).
+Variables, questions, and codes, e.g., are typically organized in a particular order. 
+If codes (\emph{skos:Concept}) should be ordered, they must be members (\emph{skos:memberList}) in an ordered collection (\emph{skos:OrderedCollection}), the variable's code list ($\mathcal{SL}_{0}$).
+
+%\textbf{Constraints on Properties.}
 It is useful to declare properties to be \emph{conditional} (\emph{R-71}), i.e., if particular properties exist (or do not exist), then other properties must also be present (or absent).
@@
 then the property {\em disco:isValid} has to be stated indicating if the code stands for valid (\emph{true}) or missing (\emph{false}) cases ($\mathcal{SL}_{2}$).
-Constraints of type \emph{context-specific exclusive or of property groups} (\emph{R-11})
+\emph{Context-specific exclusive or of property groups} (\emph{R-11}) constraints
 restrict individuals of given classes to have properties defined within exactly one of multiple property groups.
 \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes/categories), but not both ($\mathcal{SL}_{2}$).
-For datatype properties, it should be possible to declare frequently needed \emph{facets} ({\emph{R-46}) to validate input against simple conditions including min/max values, regular expressions, and string length.
-The abstract of series/studies, e.g., should have a minimum length ($\mathcal{SL}_{1}$).
-
-\textbf{Constraints on Literals.}
-\emph{disco:percentage} stands for the number of cases of a given code in relation to the total number of cases for a particular variable.
-Percentage values are only valid when they are within the \emph{literal range} of 0 and 100 (\emph{R-45}; $\mathcal{SL}_{2}$).
-{\em Mathematical Operations} (\emph{R-41, R-42}; e.g. date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
-The sum of percentage values of all variable codes, e.g., must exactly be 100 ($\mathcal{SL}_{2}$)
-and the minimum absolute frequency of all variable codes do not have to be greater than the maximum ($\mathcal{SL}_{2}$).
-Depending on property datatypes, two different literal values have
-a specific ordering with respect to an operator like \textless (\emph{R-43: literal value comparison}).
-Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}) ($\mathcal{SL}_{2}$).
+
+%\textbf{Constraints on Literals.}
 
@@
 Although accessible within our validation tool, we provide all implemented constraints\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} in form of SPARQL CONSTRUCT queries.
-For the subsequent evaluation, we implemented 212 constraints on \emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{XKOS}, and \emph{PHDD} data sets.
+For the subsequent evaluation, we implemented 213 constraints on \emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{XKOS}, and \emph{PHDD} data sets.
 The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.
@@
 
-First, several SBE domain experts of the vocabularies \emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{XKOS}, and \emph{PHDD} evaluated the correctness (i.e., the gold standard) of all $\mathcal{CT}_{C}$ and $\mathcal{CT}_{T}$ constraints and therefore the generic applicability of the developed classification system of constraint types and constraints.
+\begin{enumerate}
+	\item First, we assigned each constraint type to exactly one of the disjoint sets of constraint types 
+in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$).
+  \item Second, several SBE domain experts of the vocabularies \emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{XKOS}, and \emph{PHDD} evaluated the correctness (i.e., the gold standard) of all $\mathcal{CT}_{C}$ and $\mathcal{CT}_{T}$ constraints and therefore the generic applicability of the developed classification system of constraint types and constraints.
 %i.e., the gold standard, has been proved by multiple SBE domain experts.
-Second, we exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets by means of both $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
+  \item Third, we exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets by means of both $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
+\end{enumerate}
 We validated 
@@
 As we evaluated nearly 10 thousand \emph{QB} data sets, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.
-Table \ref{tab:evaluation} shows the evaluation results.
 
 \subsection{Evaluation Results and Discussion}
+
+The majority (48 $\equiv$ 58.5\%) of the overall 82 $\mathcal{CT}$ constraint types are $\mathcal{CT}_{B}$ constraint types whose constraints can therefore be derived from vocabularies without any effort.
+Among the $\mathcal{CT}_{B}$ constraint types, two-thirds (34 $\equiv$ 70.8\%) are $\mathcal{C}_B ^{\mathcal{R}}$, i.e., constraint types for which reasoning may be performed prior to validation, and one third (14 $\equiv$ 29.2\%) are $\overline{\mathcal{C}_B ^{\mathcal{R}}}$ constraint types, i.e., constraint types for which reasoning does not make any sense.
+A quarter (20 $\equiv$ 24.4\%) of all constraint types are $\mathcal{CT}_{S}$ and a sixth (14 $\equiv$ 17.1\%) are $\mathcal{CT}_{C}$ constraint types.
 
@@
     \\ \midrule
-		\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
-		\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
-		\hline
-    \emph{CV} & 3,545,703 & 45,635,846 & 5,540,988 & 54,722,537\\
-		\emph{CV ($\mathcal{SL}_{0}$)} & 2,437,922 (\textbf{68.8\%}) & 0 (0\%) & 2,281,740 (41.2\%) & 4,719,662 (8.6\%) \\
-		\emph{CV ($\mathcal{SL}_{1}$)} & 473,574 (13.4\%) & 45,520,613 (\textbf{99.75\%}) & 3,259,248 (\textbf{58.8\%}) & 49,253,435 (\textbf{90\%}) \\
-    \emph{CV ($\mathcal{SL}_{2}$)} & 634,207 (17.9\%) & 115,233 (0.25\%) & 0 (0\%) & 749,440 (1.4\%) \\
-		\hline
-		\emph{CT} & 52 & 20 & 14 & 53 \\
-		\emph{CT} ($\mathcal{C}_{C}$) & 30 (\textbf{57.7\%}) & 5 (25\%) & 5 (35.7\%) & 30 (\textbf{56.6\%}) \\
-		\emph{CT} ($\mathcal{C}_{T}$) & 22 (42.3\%) & 15 (\textbf{75\%}) & 9 (\textbf{64.3\%}) & 23 (43.4\%) \\
-		\hline
-		\emph{C} & 142 & 35 & 35 & 212 \\
-		\hline
-		\emph{C} ($\mathcal{C}_{C}$) & 72 (\textbf{50.7\%}) & 16 (45.7\%) & 21 (\textbf{60\%}) & 109 (\textbf{51.4\%}) \\
-		\emph{C} ($\mathcal{C}_{T}$) & 70 (\textbf{49.3\%}) & 19 (\textbf{54.3\%}) & 14 (40\%) & 103 (\textbf{48.6\%}) \\
-		\hline
-		\emph{C ($\mathcal{SL}_{0}$)} & 75 (\textbf{52.8\%})& 4 (11.4\%) & 21 (\textbf{60\%}) & 100 (\textbf{47.2\%}) \\
-		\emph{C ($\mathcal{SL}_{1}$)} & 9 (6.3\%)& 3 (8.6\%) & 5 (14.3\%) & 17 (8\%) \\
-		\emph{C ($\mathcal{SL}_{2}$)} & 58 (40.8\%) & 28 (\textbf{80\%}) & 9 (25.7\%) & 95 (\textbf{44.8\%}) \\
+		%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
+		%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
+		%\hline
+		\emph{CT} & 52 & 20 & 15 & 53 \\
+		\hline
+		$\mathcal{CT}_{C}$ & 9 (17.3\%) & 2 (10\%) & 2 (13.3\%) & 9 (17\%) \\
+		$\mathcal{CT}_{S}$ & 16 (30.8\%) & 3 (15\%) & 4 (26,7\%) & 16 (30.2\%) \\
+		$\mathcal{CT}_{B}$ & 27 (\textbf{51.9\%}) & 15 (\textbf{75\%}) & 9 (\textbf{60\%}) & 28 (\textbf{52.8\%}) \\
+		\hline
+		$\mathcal{C}_B ^{\mathcal{R}}$ & 18 (34.6\%) & 9 (45\%) & 4 (26.7\%) & 19 (35.9\%) \\
+		$\overline{\mathcal{C}_B ^{\mathcal{R}}}$ & 9 (17.3\%) & 6 (30\%) & 5 (33.3\%) & 9 (17\%) \\
     \bottomrule
     \end{tabular}
-    \\ \emph{C (constraints), CT (constraint types), CV (constraint violations)}
-    \caption{Evaluation}
-		\label{tab:evaluation}
+    %\\ \emph{C (constraints), CT (constraint types)}
+    \caption{Evaluation - Constraint Types}
+		\label{tab:evaluation-constraint-types}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+		\scriptsize
+    \begin{center}
+    \begin{tabular}{@{}lcccc@{}}
+%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
+%    \\  \cmidrule{2-7}
+    \\       \textbf{Criteria}
+           & \textbf{\emph{Disco}}
+           & \textbf{\emph{QB}}
+					 & \textbf{\emph{SKOS}}
+					 & \textbf{Total}
+    \\ \midrule
+		%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
+		%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
+		%\hline
+		\emph{C} & 143 & 35 & 35 & 213 \\
+		\hline
+		\emph{C (}$\mathcal{CT}_{C}$\emph{)} & 37 (25.9\%) & 13 (37.1\%) & 13 (\textbf{37.1\%}) & 63 (29.6\%) \\
+		\emph{C (}$\mathcal{CT}_{S}$\emph{)} & 28 (19.6\%) & 3 (8.6\%) & 12 (\textbf{34.3\%}) & 43 (20.2\%) \\
+		\emph{C (}$\mathcal{CT}_{B}$\emph{)} & 78 (\textbf{54.6\%}) & 19 (\textbf{54.3\%}) & 10 (\textbf{28.6\%}) & 107 (\textbf{50.2\%}) \\
+		\hline
+		\emph{C (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 67 (46.9\%) & 13 (37.1\%) & 4 (11.4\%) & 84 (39.4\%) \\
+		\emph{C (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 11 (7.7\%) & 6 (17.1\%) & 6 (17.1\%) & 23 (10.8\%) \\
+		\hline
+		\emph{C ($\mathcal{SL}_{0}$)} & 75 (\textbf{52.5\%}) & 4 (11.4\%) & 21 (\textbf{60\%}) & 100 (\textbf{46.9\%}) \\
+		\emph{C ($\mathcal{SL}_{1}$)} & 10 (7\%) & 3 (8.6\%) & 5 (14.3\%) & 18 (8.5\%) \\
+		\emph{C ($\mathcal{SL}_{2}$)} & 58 (40.6\%) & 28 (\textbf{80\%}) & 9 (25.7\%) & 95 (\textbf{44.6\%}) \\
+    \bottomrule
+    \end{tabular}
+    %\\ \emph{C (constraints), CT (constraint types)}
+    \caption{Evaluation - Constraints}
+		\label{tab:evaluation-constraints}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+		\scriptsize
+    \begin{center}
+    \begin{tabular}{@{}lcccc@{}}
+%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
+%    \\  \cmidrule{2-7}
+    \\       \textbf{Criteria}
+           & \textbf{\emph{Disco}}
+           & \textbf{\emph{QB}}
+					 & \textbf{\emph{SKOS}}
+					 & \textbf{Total}
+    \\ \midrule
+		\emph{CV} & 3,575,002 & 45,635,861 & 5,540,988 & 54,751,851 \\
+		\hline
+		\emph{CV (}$\mathcal{CT}_{C}$\emph{)} & 652,780 (18.3\%) & 45,634,084 (\textbf{100\%}) & 1,185,982 (21.4\%) & 47,472,846 (\textbf{86.7\%}) \\
+		\emph{CV (}$\mathcal{CT}_{S}$\emph{)} & 560,857 (15.7\%) & 0 (0\%) & 4,355,006 (\textbf{78.6\%}) & 4,915,863 (9\%) \\
+		\emph{CV (}$\mathcal{CT}_{B}$\emph{)} & 2,361,365 (\textbf{66.1\%}) & 1,777 (0\%) & 0 (0\%) & 2,363,142 (4.3\%) \\
+		\hline
+		\emph{CV (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 2,333,365 (65.3\%) & 1,777 (0\%) & 0 (0\%) & 2,335,142 (4.3\%) \\
+		\emph{CV (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 28,000 (0.8\%) & 0 (0\%) & 0 (0\%) & 28,000 (0.1\%) \\
+		\hline
+		\emph{CV ($\mathcal{SL}_{0}$)} & 1,880,777 (\textbf{52.6\%}) & 0 (0\%) & 2,281,740 (41.2\%) & 4,162,517 (7.6\%) \\
+		\emph{CV ($\mathcal{SL}_{1}$)} & 1,051,757 (29.4\%) & 45,520,613 (\textbf{99,8\%}) & 3,259,248 (\textbf{58.8\%}) & 49,831,618 (\textbf{91\%}) \\
+		\emph{CV ($\mathcal{SL}_{2}$)} & 642,468 (18\%) & 115,248 (0.3\%) & 0 (0\%) & 757,716 (1.4\%) \\
+    \bottomrule
+    \end{tabular}
+    %\\ \emph{CV (constraint violations)}
+    \caption{Evaluation - Constraint Violations}
+		\label{tab:evaluation-constraint-violations}
     \end{center}
@@
 for \emph{QB} (75\%) and \emph{SKOS} (64\%), on the other side, more $\mathcal{C}_{T}$ constraint types. 
-In total, we used 53 of overall 82 distinct constraint types (57\% of them are $\mathcal{C}_{C}$ constraint types) to define 212 constraints (equally $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints).
+In total, we used 53 of overall 82 distinct constraint types (57\% of them are $\mathcal{C}_{C}$ constraint types) to define 213 constraints (equally $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints).
 
@@
 The constraints responsible for the largest numbers of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916) (\emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102) (\emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903) (\emph{SKOS}).
-We refer to the technical reports\footnotemark[\ref{technical-report-1}] \footnotemark[\ref{technical-report-2}] to get details about constraints on and the evaluation of \emph{XKOS} and \emph{PHDD} data sets.\tb{bezug nehmen auf severity levels / technology-driven werden oft eingehalten?
-/ }
+We refer to the technical reports\footnotemark[\ref{technical-report-1}] \footnotemark[\ref{technical-report-2}] to get details about constraints on and the evaluation of \emph{XKOS} and \emph{PHDD} data sets.
+\tb{bezug nehmen auf severity levels / technology-driven werden oft eingehalten?
+/ werden in einem bestimmten vokabular vor allem basic oder complex constraints verletzt?
+/ es werden große datenbestände untersucht um ein besseres verständnis zu bekommen welche art von constraints für welche vokabulare am häufigsten verletzt werden und welche severity levles für welche vokabulare am häufigsten verletzt werden}
 
@@
 We distinguish two validation types:
-(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of data models (section \ref{content-driven-validation}).
-(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges (section \ref{technology-driven-validation}).
+(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of data models (section \ref{complex-constraint-types}).
+(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges (section \ref{basic-constraint-types}).
 We determined the default \emph{severity level} for each constraint to indicate how serious the violation of the constraint is
@@
 We implemented a validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages and to ensure correct syntax, semantics, and integrity of diverse vocabularies such as \emph{Disco, QB, PHDD, SKOS, and XKOS} (section \ref{implementation}).
-We exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets by means of 212 $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
+We exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets by means of 213 $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
 We validated more than 4.2 billion triples and 15 thousand data sets\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).

### 2015-04-26 paper/paper7/paper7.tex
evaluation

@@
 associate them with default severity levels, and assign them to $\mathcal{CT}_{C}$ and $\mathcal{CT}_{T}$ constraint types. 
+\tb{Depending on individual use cases, validation environments should enable users to select which constraints to validate against.
+For some use cases, validating $\mathcal{CT}_{B}$ constraints may be more important than validating $\mathcal{CT}_{S}$ or $\mathcal{CT}_{C}$ constraints.}
 
@@
 \emph{Swedish National Data Service (SND)}.
-
 We recently published a technical report\footnote{\label{technical-report-2}Available at: \url{http://arxiv.org/abs/1504.04478}} (serving as second appendix of this paper) 
@@
 
-The majority (48 $\equiv$ 58.5\%) of the overall 82 $\mathcal{CT}$ constraint types are $\mathcal{CT}_{B}$ constraint types whose constraints can therefore be derived from vocabularies without any effort.
-Among the $\mathcal{CT}_{B}$ constraint types, two-thirds (34 $\equiv$ 70.8\%) are $\mathcal{C}_B ^{\mathcal{R}}$, i.e., constraint types for which reasoning may be performed prior to validation, and one third (14 $\equiv$ 29.2\%) are $\overline{\mathcal{C}_B ^{\mathcal{R}}}$ constraint types, i.e., constraint types for which reasoning does not make any sense.
-A quarter (20 $\equiv$ 24.4\%) of all constraint types are $\mathcal{CT}_{S}$ and a sixth (14 $\equiv$ 17.1\%) are $\mathcal{CT}_{C}$ constraint types.
+The majority (48 $\equiv$ 58.5\%) of the overall 82 $\mathcal{CT}$ constraint types are $\mathcal{CT}_{B}$ whose constraints can therefore be derived from vocabularies without any effort.
+Among $\mathcal{CT}_{B}$, two-thirds (34 $\equiv$ 70.8\%) are $\mathcal{C}_B ^{\mathcal{R}}$, i.e., constraint types for which reasoning may be performed prior to validation, and one third (14 $\equiv$ 29.2\%) are $\overline{\mathcal{C}_B ^{\mathcal{R}}}$, i.e., constraint types for which reasoning does not make any sense.
+A quarter (20 $\equiv$ 24.4\%) of all constraint types are $\mathcal{CT}_{S}$ and a sixth (14 $\equiv$ 17.1\%) are $\mathcal{CT}_{C}$.
 
@@
 
+%Table \ref{tab:evaluation-constraint-types} displays the evaluation of the metadata quality on real world data sets regarding constraint types.
+We defined constraints of 53 distinct $\mathcal{CT}$ constraint types (see table \ref{tab:evaluation-constraint-types}).
+More than the half of them are $\mathcal{CT}_{B}$, more than a third $\mathcal{C}_B ^{\mathcal{R}}$, nearly a third $\mathcal{CT}_{S}$, and only a sixth $\mathcal{CT}_{C}$ constraint types.
+For \emph{Disco}, \emph{QB}, and \emph{SKOS}, more than 50\% of the instantiated constraint types are $\mathcal{CT}_{B}$ constraint types 
+(for \emph{QB} even three quarters).
+\emph{Existential quantifications} (\emph{R-86}, 32.4\%, \emph{Disco}), \emph{data model consistency} (31.4\%, \emph{QB}), and \emph{structure} (28.6\%, \emph{SKOS}) are the constraint types the most constraints are instantiated from.
+
 \begin{table}[H]
@@
 		%\hline
-		\emph{C} & 143 & 35 & 35 & 213 \\
+		\emph{C} & 143 (67.1\%) & 35 (16.4\%) & 35 (16.4\%) & 213 \\
 		\hline
@@
 \end{table}
+
+Half of the overall 213 $\mathcal{CT}$ constraints are $\mathcal{CT}_{B}$ constraints (almost 40\% $\mathcal{C}_B ^{\mathcal{R}}$) (see table \ref{tab:evaluation-constraints}).
+This is not surprising as more than the half of the instantiated constraints types are $\mathcal{CT}_{B}$ constraint types.
+More than 50\% of the \emph{Disco} and \emph{QB} constraints are $\mathcal{CT}_{B}$ constraints.
+The \emph{SKOS} constraints, on the other side, are equally assigned to the three disjoint constraint type sets. 
+\emph{SBE} domain experts associated almost the half of the constraints with the severity levels $\mathcal{SL}_{0}$ (\emph{informational}) (47\%) and $\mathcal{SL}_{2}$ (\emph{error}) (45\%);
+only 8.5\% are $\mathcal{SL}_{1}$ (\emph{warning}) constraints.
+The violation of 80\% of the \emph{QB} constraints is very serious ($\mathcal{SL}_{2}$).
+More than 50\% of the \emph{Disco} and \emph{SKOS} constraints, however, are assigned to the weakest default severity level ($\mathcal{SL}_{0}$).
 
@@
     \\ \midrule
-		\emph{CV} & 3,575,002 & 45,635,861 & 5,540,988 & 54,751,851 \\
+		\emph{CV} & 3,575,002 (6.5\%) & 45,635,861 (83.4\%) & 5,540,988 (10.1\%) & 54,751,851 \\
 		\hline
@@
 
-We identified 142 \emph{Disco} constraints ($\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints to the same extend) assigned to 52 distinct constraint types and implemented 77 of them to actually validate person-level data sets.
-For \emph{QB}, we specified more $\mathcal{C}_{T}$ (54\%) than $\mathcal{C}_{C}$ constraints; for \emph{SKOS}, however, more $\mathcal{C}_{C}$ constraints (60\%).
-We instantiated more $\mathcal{C}_{C}$ (58\%) than $\mathcal{C}_{T}$ constraint types to define \emph{Disco} constraints; 
-for \emph{QB} (75\%) and \emph{SKOS} (64\%), on the other side, more $\mathcal{C}_{T}$ constraint types. 
-In total, we used 53 of overall 82 distinct constraint types (57\% of them are $\mathcal{C}_{C}$ constraint types) to define 213 constraints (equally $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints).
-
-For \emph{Disco} and \emph{SKOS}, more than the half of the constraints are associated with the weakest severity level $\mathcal{SL}_{0}$.
-Within the context of \emph{QB}, 80\% of the constraints are classified as the most serious ones ($\mathcal{SL}_{2}$).
-All in all, there are a little bit more $\mathcal{SL}_{0}$ then $\mathcal{SL}_{2}$ constraints, whereas $\mathcal{SL}_{1}$ constraints are negligible.
-\emph{Existential quantifications} (32.4\%, \emph{Disco}), \emph{data model consistency} (31.4\%, \emph{QB}), and \emph{structure} (28.6\%, \emph{SKOS}) are the constraint types the most constraints are instantiated from.
-By validating \emph{QB} data sets, we got the most constraint violations (more than 45 millions), followed by \emph{SKOS} and \emph{Disco} (with more than 5.5 and 3.5 millions) - consequently, almost 55 million constraint violations were raised during the evaluation which could be used to enhance the metadata quality of these data sets.
-Close to 70\% of all \emph{Disco} constraint violations are caused by violating $\mathcal{SL}_{0}$ constraints.
-For \emph{QB} (nearly 100\%) and \emph{SKOS} (almost 60\%), the majority of the raised constraint violations are classified to be more serious ($\mathcal{SL}_{1}$).
-80\% of all \emph{QB} constraints are $\mathcal{SL}_{2}$ constraints leading to less than 1\% of all \emph{QB} constraint violations.
-Altogether, exactly 90\% of the constraint violations are assigned to the severity level $\mathcal{SL}_{1}$.
-These findings are surprising as only 8\% of all defined constraints are $\mathcal{SL}_{1}$ constraints.
-The constraints responsible for the largest numbers of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916) (\emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102) (\emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903) (\emph{SKOS}).
-We refer to the technical reports\footnotemark[\ref{technical-report-1}] \footnotemark[\ref{technical-report-2}] to get details about constraints on and the evaluation of \emph{XKOS} and \emph{PHDD} data sets.
-\tb{bezug nehmen auf severity levels / technology-driven werden oft eingehalten?
-/ werden in einem bestimmten vokabular vor allem basic oder complex constraints verletzt?
-/ es werden große datenbestände untersucht um ein besseres verständnis zu bekommen welche art von constraints für welche vokabulare am häufigsten verletzt werden und welche severity levles für welche vokabulare am häufigsten verletzt werden}
+More than 80\% of the overall approx. 55 million constraint violations are caused by \emph{QB} constraints (see table \ref{tab:evaluation-constraint-violations}).
+The majority (86.7\%) of the constraint violations are caused by $\mathcal{CT}_{C}$ constraints and only 9\% by $\mathcal{CT}_{S}$ constraints.
+The fact that only 4\% of all constraint violations result from $\mathcal{CT}_{B}$ constraints, 
+even though, more than 50\% of all constraints are $\mathcal{CT}_{B}$ constraints,
+is an indicator that data producers achieve good data quality with respect to the constraints extracted by vocabularies.
+Two-thirds of the constraint violations, thrown for \emph{Disco} data sets, result from $\mathcal{CT}_{B}$ constraints,
+almost only $\mathcal{CT}_{C}$ constraints raised constraint violations for \emph{QB} data sets, and 
+nearly 80\% of the \emph{SKOS} constraint violations are caused by $\mathcal{CT}_{S}$ constraints.
+Although, only 8.5\% of all constraints are $\mathcal{SL}_{1}$ constraints,
+9 0f 10 constraint violations are caused by constraints associated with the default severity level $\mathcal{SL}_{1}$.
+More than 50\% of all constraint violations thrown for \emph{Disco} data sets are not seen to be that significant ($\mathcal{SL}_{0}$).
+Almost all constraint violations raised by \emph{QB} constraints and 59\% of the constraint violations caused by \emph{SKOS} constraints are classified as warnings ($\mathcal{SL}_{1}$).  
+As this evaluation serves as indication for \emph{good} or \emph{bad} (meta)data quality, 
+we conclude that
+the metadata quality of all evaluated \emph{Disco} data sets is \emph{good} and that the metadata quality of all evaluated \emph{QB} and \emph{SKOS} data sets is \emph{satisfactory}.
+%The constraints responsible for the largest amounts of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916; \emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102; \emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903; \emph{SKOS}).
+
+\tb{es werden große datenbestände untersucht um ein besseres verständnis zu bekommen welche art von constraints für welche vokabulare am häufigsten verletzt werden und welche severity levles für welche vokabulare am häufigsten verletzt werden}
 
@@
 \section{Conclusion and Future Work}
-\ke{@KAI: Dieses Kapitel muss ich noch an die Änderungen im Paper anpassen!}
+\tb{ToDO}
 In this paper, we showed in form of a complete real world running example how to represent metadata on person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
@@
 We validated more than 4.2 billion triples and 15 thousand data sets\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).
-\tb{auswahl an constraints, die validiert werden sollen / je nach use cases sollen z.b.
-nur technology-driven constraints validiert werden oder sind wichtiger / use solen je nach use case selbt bestimmen welche constraints validiert werden sollen}
-%It is still ongoing work to identify and classify constraints on rectangular data (\emph{PHDD}) and statistical classifications (\emph{XKOS}) and to actually evaluate the (meta)data quality of real world \emph{XKOS} and \emph{PHDD} data sets.
 

### 2015-04-27 paper/paper7/paper7.tex
section 4

@@
 \emph{R-75, R-81: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}\cite{BoschNolleAcarEckert2015}.
-We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement (constraint type) in detail and give examples for each expressed by different constraint languages.
+We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages.
 The knowledge representation formalism \emph{Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
-Therefore, this technical report contains mappings to DL to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
-
-We developed a system to classify RDF constraints and RDF constraint types.
-Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
-%\emph{data model specific constraint types} (e.g. \emph{data model consistency})
-
-We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as first appendix of this paper) in which we describe 213 constraints (classified as 53 distinct constraint types) to validate rectangular data (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}), and therefore apply the proposed classification system to several vocabularies to represent both data and metadata \cite{BoschZapilkoWackerowEckert2015}.
-In this section, we describe constraints, which are important to ensure \emph{SBE} (meta)data quality, 
-associate them with default severity levels, and assign them to $\mathcal{CT}_{C}$ and $\mathcal{CT}_{T}$ constraint types. 
+Therefore, this technical report contains mappings to \emph{DL} to logically underpin each requirement and to determine which \emph{DL} constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
+
+We developed a system to classify both RDF constraint types and RDF constraints to evaluate the quality of metadata and data which may be represented by any vocabulary.
+%Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
+We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as first appendix of this paper) in which we describe 213 constraints of 53 distinct constraint types
+to validate tabular data (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), and thesauri (\emph{SKOS}).
+By applying the proposed classification system to several vocabularies to represent both metadata and data, we show its generality \cite{BoschZapilkoWackerowEckert2015}.
+
 \tb{Depending on individual use cases, validation environments should enable users to select which constraints to validate against.

### 2015-04-27 paper/paper7/paper7.tex
section 4

@@
 We explain how \emph{SBE} (meta)data is validated against constraints, instantiated from constraint types organized in the constraint classification system, to ensure high quality of and trust in (meta)data.
+
+We evaluate a huge amount of metadata and data represented by multiple vocabularies in order to get an understanding which kind of constraints are violated to which extend and which constraint associated with particular severity levels are mostly violated for which vocabularies.
 
@@
 In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.
-\tb{reihenfolge / DCAT fehlt}
 
@@
 to validate tabular data (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), and thesauri (\emph{SKOS}).
-By applying the proposed classification system to several vocabularies to represent both metadata and data, we show its generality \cite{BoschZapilkoWackerowEckert2015}.
+By applying the proposed classification system to several vocabularies to represent both metadata and data, we prove its generality \cite{BoschZapilkoWackerowEckert2015}.
 
@@
 
-\tb{es werden große datenbestände untersucht um ein besseres verständnis zu bekommen welche art von constraints für welche vokabulare am häufigsten verletzt werden und welche severity levles für welche vokabulare am häufigsten verletzt werden}
-
 \section{Related Work}

### 2015-04-27 paper/paper7/paper7.tex
section 4

@@
 
-\tb{Depending on individual use cases, validation environments should enable users to select which constraints to validate against.
-For some use cases, validating $\mathcal{CT}_{B}$ constraints may be more important than validating $\mathcal{CT}_{S}$ or $\mathcal{CT}_{C}$ constraints.}
-
 \subsection{Classification of Constraint Types}
@@
 \begin{enumerate}
-	\item \textbf{$\mathcal{CT}_{B}$: \emph{Basic Constraint Types}}
-	\item \textbf{$\mathcal{CT}_{S}$: \emph{Simple Constraint Types}}
-	\item \textbf{$\mathcal{CT}_{C}$: \emph{Complex Constraint Types}}
+	\item $\mathcal{CT}_{B}$: \textbf{\emph{Basic Constraint Types}}
+	\item $\mathcal{CT}_{S}$: \textbf{\emph{Simple Constraint Types}}
+	\item $\mathcal{CT}_{C}$: \textbf{\emph{Complex Constraint Types}}
 \end{enumerate}
@@
 \emph{Minimum qualified cardinality restrictions} (\emph{R-74}), e.g., guarantee that individuals of given classes are connected by particular properties to at least n different individuals/literals of certain classes or data ranges.
-This way, it is expressible in OWL 2 that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:
+This way, it is expressible in \emph{OWL 2} that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:
 \begin{ex}
@@
 \emph{Simple constraint types} ($\mathcal{CT}_{S}$) is the set of constraint types whose constraints can be easily defined without much effort in addition to $\mathcal{CT}_{B}$ constraints.
-The {\emph{data property facets} (\emph{R-46}) $\mathcal{CT}_{S}$ constraint type enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
+{\emph{Data property facets} (\emph{R-46}) is an example of an $\mathcal{CT}_{S}$ constraint type which enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
 The abstract of series/studies, e.g., should have a minimum length ($\mathcal{SL}_{1}$).
@@
 \emph{Complex constraint types} ($\mathcal{CT}_{C}$) encompass constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
-Complex constraints show the importance of constraint languages enabling to describe complex constraints.
+Complex constraints show the importance of constraint languages enabling to describe more complex constraints.
 For assessing the quality of thesauri, e.g., we concentrate on the graph-based structure and apply graph- and network-analysis techniques.
-An example of such \emph{structure} constraints is that 
+An example of such constraints of the constraint type \emph{structure} is that 
 a thesaurus should not contain many orphan concepts, i.e., concepts without any associative or hierarchical relations, lacking context information valuable for search.
-
-\tb{refer to evaluation / what do we want to know?}
 
@@
 
+Validation environments should enable users to select which constraints to validate against depending on their individual use cases.
+For some use cases, 
+validating constraints of $\mathcal{CT}_{B}$ constraint types may be more important than validating constraints of $\mathcal{CT}_{S}$ or $\mathcal{CT}_{C}$ constraint types.
+For other use cases,
+validating $\mathcal{SL}_{2}$ constraints may be sufficient without taking $\mathcal{SL}_{1}$ and $\mathcal{SL}_{0}$ constraints into account.
+\tb{refer to evaluation / what do we want to know?} 
 %

### 2015-04-27 paper/paper7/paper7.tex
section 4

@@
 validating $\mathcal{SL}_{2}$ constraints may be sufficient without taking $\mathcal{SL}_{1}$ and $\mathcal{SL}_{0}$ constraints into account.
-\tb{refer to evaluation / what do we want to know?} 
+We evaluate a huge amount of metadata and data represented by multiple vocabularies to get an understanding 
+(1) which sets of constraint types and 
+(2) which sets of constraints (associated with particular severity levels) encompass the most/fewest violated constraints (see section \ref{evaluation}).
+
 %

### 2015-04-27 paper/paper7/paper7.tex
section 4

@@
 whereas data, not corresponding to $\mathcal{SL}_{2}$ constraints, cannot be processed further after validation. 
+As constraints of $\mathcal{CT}_{B}$ constraint types are derived from explicitly stated semantics of vocabularies, 
+their default severity levels are in most cases very strong ($\mathcal{SL}_{2}$) and 
+in average stronger than the severity levels of constraints assigned to $\mathcal{CT}_{S}$ and $\mathcal{CT}_{C}$ constraint types.
+As a consequence, violating many constraints of $\mathcal{CT}_{B}$ constraint types is an indicator for bad (meta)data quality\footnote{For simplicity reasons, we only assign severity levels to $\mathcal{CT}_{B}$ constraints in this paper in case they differ from $\mathcal{SL}_{2}$.}.
+
 Although, we provide default severity levels for each constraint, validation environments should enable users to adapt constraints' severity levels according to their individual needs.
-
-As $\mathcal{CT}_{B}$ constraints are derived from explicitly stated semantics of vocabularies' data models, 
-default severity levels of $\mathcal{CT}_{B}$ constraints are in most cases very strong ($\mathcal{SL}_{2}$) and 
-in average stronger than severity levels of $\mathcal{CT}_{S}$ and $\mathcal{CT}_{C}$ constraints.
-As a consequence, violating many $\mathcal{CT}_{B}$ constraints is an indicator for bad data quality\footnote{For simplicity reasons, we only assign severity levels to $\mathcal{CT}_{B}$ constraints when they differ from $\mathcal{SL}_{2}$.}.
-
 Validation environments should enable users to select which constraints to validate against depending on their individual use cases.

### 2015-04-27 paper/paper7/paper7.tex
contribution

@@
 
-The main \textbf{contribution} of this paper is the development of a system to classify RDF constraints and RDF constraint types, which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (section \ref{classification}).
+We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as first appendix of this paper) in which we describe 213 constraints of 53 distinct constraint types
+to validate tabular data (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), and thesauri (\emph{SKOS}).
+By applying the proposed classification system to several vocabularies to represent both metadata and data, we prove its generality \cite{BoschZapilkoWackerowEckert2015}.
+
+-----
+
+The main \textbf{contribution} of this paper is the development of a system 
+\begin{enumerate}
+	\item to classify RDF constraints to evaluate the quality of metadata and data which may be represented by any vocabulary and 
+	\item to classify RDF constraint types which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (section \ref{classification}).
+\end{enumerate}
+By defining a huge amount of constraints of different constraint types,   
+we apply the proposed classification system to several and different vocabularies from the \emph{SBE} domain to represent both metadata and data and therefore prove its generality.
+
 We propose an extensible metric to measure the continuum of severity levels to indicate how serious the violation of given constraints is.

### 2015-04-27 paper/paper7/paper7.tex
contribution

@@
 %\title{RDF Constraints to Ensure High Quality \\ of Metadata and Data}
-\title{RDF Constraints Classification Ensuring \\ High Quality of Metadata and Data}
+\title{Classification of RDF Constraint Types Ensuring High Quality of Metadata and Data}
 \subtitle{}
@@
 We exhaustively evaluated the metadata quality of large real world aggregated, person-level, and thesauri data sets (more than 4.2 billion triples and 15 thousand data sets) by means of constraints of the majority of constraint types.
-\tb{DCAT und XKOS nur in future work}
+
 \keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, RDF Data Cube Vocabulary, Rectangular Data, SKOS, XKOS, Linked Data, Semantic Web}
@@
 %\tb{terminology: data in singular form / data set - NOT dataset / person-level data - NOT microdata / study - NOT survey}
-
+\tb{DCAT und XKOS nur in future work}
 For more than a decade, members of the community around research data for the \emph{social, behavioural, and economic (SBE) sciences} have been developing and using a
@@
 
-We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as first appendix of this paper) in which we describe 213 constraints of 53 distinct constraint types
-to validate tabular data (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), and thesauri (\emph{SKOS}).
-By applying the proposed classification system to several vocabularies to represent both metadata and data, we prove its generality \cite{BoschZapilkoWackerowEckert2015}.
-
------
-
 The main \textbf{contribution} of this paper is the development of a system 
@@
 	\item to classify RDF constraints to evaluate the quality of metadata and data which may be represented by any vocabulary and 
-	\item to classify RDF constraint types which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (section \ref{classification}).
+	\item to classify RDF constraint types which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (section \ref{classification} - \ref{complex-constraint-types}).
 \end{enumerate}
 By defining a huge amount of constraints of different constraint types,   
-we apply the proposed classification system to several and different vocabularies from the \emph{SBE} domain to represent both metadata and data and therefore prove its generality.
-
-We propose an extensible metric to measure the continuum of severity levels to indicate how serious the violation of given constraints is.
-Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary. 
-As constraint types are used to define constraints on (meta)data expressed by any vocabulary, the proposed constraint classification can be applied generically, i.e. vocabulary-independent. 
-Within the context of a complex and complete real world running example from the \emph{SBE} domain, we prove the claim that the developed classification system perfectly applies for diverse vocabularies.
+we apply the developed classification system to several and different vocabularies from the \emph{SBE} domain to represent both metadata and data and therefore prove the generality of the proposed classification system.
+A complex and complete real world running example from the \emph{SBE} domain serves to prove the claim that the developed classification system perfectly applies for diverse vocabularies.
 %, i.e., that it does not matter which vocabularies are used to represent (meta)data and for which domains constraints are defined.
 We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
-how data in rectangular format (expressed by the \emph{PHDD} vocabulary) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF, and how therefore reused vocabularies are interrelated (section \ref{rdf-representation}).
-We explain how \emph{SBE} (meta)data is validated against constraints, instantiated from constraint types organized in the constraint classification system, to ensure high quality of and trust in (meta)data.
-
-We evaluate a huge amount of metadata and data represented by multiple vocabularies in order to get an understanding which kind of constraints are violated to which extend and which constraint associated with particular severity levels are mostly violated for which vocabularies.
-
-%The remainder of the paper is structured as follows.
-For the extensive evaluation, we implemented 53 constraint types by instantiating 213 constraints on \emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{XKOS}, and \emph{PHDD} data sets (section \ref{implementation}).
-First, several \emph{SBE} domain experts evaluated the correctness (i.e., the gold standard) of all constraints and therefore the generic applicability of the developed constraint classification system.
-Second, we exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets (more than 4.2 billion triples and 15 thousand data sets) by means of constraints of the majority of constraint types (section \ref{evaluation}).
+how data in tabular format (expressed by the \emph{PHDD} vocabulary) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), and thesauri (\emph{SKOS}) are represented in RDF, and how therefore reused vocabularies are interrelated (section \ref{rdf-representation}).
+We explain how \emph{SBE} (meta)data is validated against constraints, instantiated from constraint types organized in the classification system, to ensure high quality of and trust in (meta)data.
+
+We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple and different vocabularies to get an understanding
+(1) which sets of constraint types and 
+(2) which sets of constraints (associated with particular severity levels) encompass the most/fewest violated constraints (see section \ref{evaluation}).
+
+%We propose an extensible metric to measure the continuum of severity levels to indicate how serious the violation of given constraints is.
+%Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary. 
+%As constraint types are used to define constraints on (meta)data expressed by any vocabulary, the proposed constraint classification can be applied generically, i.e. vocabulary-independent.
 
@@
 validating $\mathcal{SL}_{2}$ constraints may be sufficient without taking $\mathcal{SL}_{1}$ and $\mathcal{SL}_{0}$ constraints into account.
-We evaluate a huge amount of metadata and data represented by multiple vocabularies to get an understanding 
+We evaluated the (meta)data quality of large real world data sets represented by multiple and different vocabularies to get an understanding  
 (1) which sets of constraint types and 

### 2015-04-27 paper/paper7/paper7.tex
abstract

@@
 %data is aggregated into less confidential publicly available multi-dimensional tables which answer particular research questions and whose purpose is to gain an interest in further more detailed analyses on the underlying person-level data.
-To ensure high quality and trust, metadata and data must satisfy certain criteria - specified in terms of RDF constraints. 
+To ensure high quality and trust, both metadata and data must satisfy certain criteria - specified in terms of RDF constraints. 
 %From 2012 to 2015 together with other Linked Data community members and \emph{SBE} experts, we developed diverse vocabularies to represent \emph{SBE} metadata and data in RDF.
 
-In this paper, we propose a system to classify RDF constraints and RDF constraint types, which in most cases correspond to RDF validation requirements.
-Constraints are instantiated from constraint types in order to validate both metadata and data independently from used vocabularies. 
-Within the context of a complex and complete real world running example within the community around research data for the \emph{social, behavioural, and economic (SBE) sciences}, we prove the claim that the developed classification system perfectly applies for diverse vocabularies.
-We show how data in rectangular format and metadata on person-level or more generally record-unit data sets (i.e., data about individuals, households, businesses), aggregated data sets, thesauri, and statistical classifications are represented in RDF and how therefore reused vocabularies are interrelated.
-We explain how \emph{SBE} (meta)data is validated against constraints to ensure high quality and trust.
-We exhaustively evaluated the metadata quality of large real world aggregated, person-level, and thesauri data sets (more than 4.2 billion triples and 15 thousand data sets) by means of constraints of the majority of constraint types.
-
-\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, RDF Data Cube Vocabulary, Rectangular Data, SKOS, XKOS, Linked Data, Semantic Web}
+The \textbf{contribution} of this paper is the development of a system 
+(1) to classify RDF constraints to evaluate the quality of (meta)data which may be represented by any vocabulary and 
+(2) to classify RDF constraint types which in most cases correspond to RDF validation requirements.
+By defining a huge amount of constraints of the majority of constraint types
+to validate data sets from the community around research data for the \emph{social, behavioural, and economic (SBE) sciences},  
+%we apply the developed classification system to several and different vocabularies from the community around research data for the \emph{social, behavioural, and economic (SBE) sciences} in order to
+we prove the claim that the developed classification system perfectly applies vocabulary-independent and therefore to prove the generality of the proposed classification system.
+
+We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple and different vocabularies to get an understanding
+(1) which sets of constraint types and 
+(2) which sets of constraints (associated with particular severity levels) encompass the most/fewest violated constraints.
+
+\keywords{RDF Validation, RDF Constraints, Metadata Quality, Data Quality, Tabular Data, DDI-RDF Discovery Vocabulary, RDF Data Cube Vocabulary, SKOS, Thesauri, Linked Data, Semantic Web}
 \end{abstract}
@@
 %\tb{terminology: data in singular form / data set - NOT dataset / person-level data - NOT microdata / study - NOT survey}
+\tb{metadata on person-level or more generally record-unit data sets (i.e., data about individuals, households, businesses)}
 \tb{DCAT und XKOS nur in future work}
@@
 
-The main \textbf{contribution} of this paper is the development of a system 
+The \textbf{contribution} of this paper is the development of a system 
 \begin{enumerate}

### 2015-04-27 paper/paper7/paper7.tex
introduction

@@
 
-%\tb{terminology: data in singular form / data set - NOT dataset / person-level data - NOT microdata / study - NOT survey}
-\tb{metadata on person-level or more generally record-unit data sets (i.e., data about individuals, households, businesses)}
-\tb{DCAT und XKOS nur in future work}
-For more than a decade, members of the community around research data for the \emph{social, behavioural, and economic (SBE) sciences} have been developing and using a
-metadata standard (composed of almost twelve hundred metadata fields) known as the \emph{Data Documentation Initiative (DDI)} \cite{Vardigan2008}.
-\emph{DDI} is an XML format designed to support the dissemination, management,
-and reuse of the data collected and archived for research purposes.  
-%DDI is heavily used by the CESSDA community of European national data archives, 
-%the International Household Survey Network community (made up of more than 90 statistical agencies),
-%and ICPSR - the largest SBE data archive in the US.
-Increasingly, data professionals, data archives, data libraries, government statisticians (e.g. \url{data.gov}, \url{data.gov.uk}), and national statistical institutes
-are very interested in having their data be discovered and used by providing their metadata (e.g. about unemployment rates or income) on the web in form of RDF.
-Recently, members of the SBE and Linked Data community developed the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}}, 
-an effort to leverage the mature DDI metadata model for the purposes of exposing DDI metadata as resources within the Web of Linked Data.
-
 For data archives, research institutes, and data libraries,
 RDF data validation according to predefined constraints is a much sought-after feature, 
-particularly as this is taken for granted in the XML world as DDI-XML documents are validated against diverse XSDs\footnote{\label{fnt:DDI-XSDs}\url{http://www.ddialliance.org/Specification/}} (section \ref{related-work}).
-Several approaches exist to meet this requirement, ranging from using \emph{OWL 2} as a constraint language to \emph{SPIN}\footnote{\url{http://spinRDF.org/}}, a SPARQL-based way to formulate and check constraints.
-There are also constraint languages like \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles} that more or less explicitly address the \emph{SBE} community.
+particularly as this is taken for granted in the XML world. 
+%as DDI-XML documents are validated against diverse XSDs\footnote{\label{fnt:DDI-XSDs}\url{http://www.ddialliance.org/Specification/}} (section \ref{related-work}).
+Several languages exist to formulate and check constraints on RDF data, ranging from \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles} to using \emph{OWL 2} as a constraint language and the SPARQL-based \emph{SPIN}\footnote{\url{http://spinRDF.org/}}.
+%that more or less explicitly address the \emph{SBE} community.
 In 2013, the W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
@@
 The intention is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
-The requirements are classified to better evaluate existing solutions and each requirement is directly mapped to a constraint type which may be expressed by at least one existing constraint language.
-Bosch and Eckert \cite{BoschEckert2014-2} \tb{why do we use spin?not the best for constraint language, but for validating / akzeptierte beste form constraints zu definieren}use SPIN as basis to define a
+The requirements are classified to better evaluate existing solutions and each requirement is directly mapped to a constraint type which is expressible by at least one existing constraint language.
+As \emph{SPIN} is the within the RDF validation community accepted and widely adopted way to check constraints on RDF data, Bosch and Eckert \cite{BoschEckert2014-2} use \emph{SPIN} as basis to define a
 validation environment (available at \url{http://purl.org/net/rdfval-demo}) in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL.
@@
 \label{motivation}
+
+\tb{metadata on person-level or more generally record-unit data sets (i.e., data about individuals, households, businesses)}
+
+For more than a decade, members of the community around research data for the \emph{social, behavioural, and economic (SBE) sciences} have been developing and using a
+metadata standard (composed of almost twelve hundred metadata fields) known as the \emph{Data Documentation Initiative (DDI)} \cite{Vardigan2008}.
+\emph{DDI} is an XML format designed to support the dissemination, management,
+and reuse of the data collected and archived for research purposes.  
+%DDI is heavily used by the CESSDA community of European national data archives, 
+%the International Household Survey Network community (made up of more than 90 statistical agencies),
+%and ICPSR - the largest SBE data archive in the US.
+Increasingly, data professionals, data archives, data libraries, government statisticians (e.g. \url{data.gov}, \url{data.gov.uk}), and national statistical institutes
+are very interested in having their data be discovered and used by providing their metadata (e.g. about unemployment rates or income) on the web in form of RDF.
+Recently, members of the SBE and Linked Data community developed the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}}, 
+an effort to leverage the mature DDI metadata model for the purposes of exposing DDI metadata as resources within the Web of Linked Data.
 
@@
 
-\textbf{Searching for (Meta)data.}
-\emph{DCAT} enables to represent aggregated and person-level data sets inside of data collections like portals, repositories, catalogs, and archives
-which serve as typical entry points when searching for data.
-Users search for aggregated and person-level data records (\emph{dcat:CatalogRecord}) inside data catalogs (\emph{dcat:Catalog}). 
-As search differs depending on the users’ information need,
-users may only search for records' metadata (e.g., \emph{dcterms:title}, \emph{dcterms:description}), 
-or may formulate more sophisticated queries on aggregated and person-level data sets (\emph{dcat:Dataset}) or their
-distributions (\emph{dcat:Distribution}) which are part of the records. 
-Often, users search for data sets covering particular topics (\emph{dcat:keyword}, \emph{dcat:theme}), time periods (\emph{dcterms:temporal}),  or  locations (\emph{dcterms:spatial}), 
-or for certain formats in which the data distribution is available (\emph{dcterms:format}).
+%\textbf{Searching for (Meta)data.}
+%\emph{DCAT} enables to represent aggregated and person-level data sets inside of data collections like portals, repositories, catalogs, and archives
+%which serve as typical entry points when searching for data.
+%Users search for aggregated and person-level data records (\emph{dcat:CatalogRecord}) inside data catalogs (\emph{dcat:Catalog}). 
+%As search differs depending on the users’ information need,
+%users may only search for records' metadata (e.g., \emph{dcterms:title}, \emph{dcterms:description}), 
+%or may formulate more sophisticated queries on aggregated and person-level data sets (\emph{dcat:Dataset}) or their
+%distributions (\emph{dcat:Distribution}) which are part of the records. 
+%Often, users search for data sets covering particular topics (\emph{dcat:keyword}, \emph{dcat:theme}), time periods (\emph{dcterms:temporal}),  or  locations (\emph{dcterms:spatial}), 
+%or for certain formats in which the data distribution is available (\emph{dcterms:format}).
 
@@
 particularly as this is taken for granted in the XML world.
-DDI-XML documents, e.g., are validated against diverse XSDs\footnotemark[\ref{fnt:DDI-XSDs}].
+DDI-XML documents, e.g., are validated against diverse XSDs\footnote{\url{http://www.ddialliance.org/Specification/}}.
 As certain constraints cannot be formulated and validated by XSDs, 

### 2015-04-27 paper/paper7/paper7.tex
motivation

@@
 
-\tb{metadata on person-level or more generally record-unit data sets (i.e., data about individuals, households, businesses)}
-
-For more than a decade, members of the community around research data for the \emph{social, behavioural, and economic (SBE) sciences} have been developing and using a
-metadata standard (composed of almost twelve hundred metadata fields) known as the \emph{Data Documentation Initiative (DDI)} \cite{Vardigan2008}.
-\emph{DDI} is an XML format designed to support the dissemination, management,
-and reuse of the data collected and archived for research purposes.  
-%DDI is heavily used by the CESSDA community of European national data archives, 
-%the International Household Survey Network community (made up of more than 90 statistical agencies),
-%and ICPSR - the largest SBE data archive in the US.
-Increasingly, data professionals, data archives, data libraries, government statisticians (e.g. \url{data.gov}, \url{data.gov.uk}), and national statistical institutes
-are very interested in having their data be discovered and used by providing their metadata (e.g. about unemployment rates or income) on the web in form of RDF.
-Recently, members of the SBE and Linked Data community developed the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}}, 
-an effort to leverage the mature DDI metadata model for the purposes of exposing DDI metadata as resources within the Web of Linked Data.
-
-The data most often used in research within the SBE community is \emph{person-level data}, i.e.
-data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers
+The data most often used in research within the \emph{SBE} community is \emph{person-level data} or more generally \emph{record-unit data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers
 (such as hospital records, registers of births and deaths). 
@@
 Portals harvest metadata (as well as publicly available data) from multiple data providers in form of RDF.
-To ensure high quality, the metadata must satisfy certain criteria - specified in terms of RDF constraints.  
-After validating the metadata according to these constraints, portals offer added values to their customers, e.g., by searching over and comparing metadata of multiple providers.
+To ensure high quality, (meta)data must satisfy certain criteria - specified in terms of RDF constraints.  
+%After validating the metadata according to these constraints, portals offer added values to their customers, e.g., by searching over and comparing metadata of multiple providers.
 
@@
 %allowing the RDF versions of these standards to retain that alignment.
-While \emph{Disco} and \emph{QB} provide terms for the description of data sets, 
-both on a different level of aggregation, 
-the \emph{Data Catalog Vocabulary (DCAT)}\footnote{\url{http://www.w3.org/TR/vocab-dcat/}} enables the representation of these data sets inside of data collections like repositories, catalogs, or archives.
-The relationship between data collections and their contained data sets is useful, since such collections are a typical entry point when searching for data.
+%While \emph{Disco} and \emph{QB} provide terms for the description of data sets, 
+%both on a different level of aggregation, 
+%the \emph{Data Catalog Vocabulary (DCAT)}\footnote{\url{http://www.w3.org/TR/vocab-dcat/}} enables the representation of these data sets inside of data collections like repositories, catalogs, or archives.
+%The relationship between data collections and their contained data sets is useful, since such collections are a typical entry point when searching for data.
 %Although, in most cases aggregated data is still published in form of PDFs, 
 %it is more and more common to publish aggregated data as CSV files,
+
 Aggregated data is more and more published as CSV files,
@@
 %For these calculations, definitions of the columns are needed (e.g. is a given variable interpreted numerically or as a string).
-In 2014, SBE and Linked Data community members developed the \emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} vocabulary to represent data in a rectangular format.\tb{tabular data}
+\emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} is a vocabulary to represent data in tabular format in RDF.\tb{tabular data} 
 The data could be either represented in records with character-separated values (CSV) or in records with fixed length.
@@
 %\textbf{Data validation.}
-Data providers and harvesters do not only offer metadata but also publicly available data on different level of aggregation.
-To ensure high data quality, they have to check provenance information and to analyze and therefore validate the data according to predefined constraints (e.g.
+%Data providers and harvesters do not only offer metadata but also publicly available data on different level of aggregation.
+%To ensure high data quality, they have to check provenance information and to analyze and therefore validate the data according to predefined constraints (e.g.
 'are fundamental data fragments available?', and 'how does valid data look like?').
@@
 
+%For more than a decade, members of the community around research data for the \emph{social, behavioural, and economic (SBE) sciences} have been developing and using a
+%metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)},
+%an XML format to disseminate, manage,
+%and reuse data collected and archived for research \cite{Vardigan2008}.  
+%%DDI is heavily used by the CESSDA community of European national data archives, 
+%%the International Household Survey Network community (made up of more than 90 statistical agencies),
+%%and ICPSR - the largest SBE data archive in the US.
+%Increasingly, data professionals, data archives, data libraries, government statisticians (e.g. \url{data.gov}, \url{data.gov.uk}), and national statistical institutes
+%are very interested in having their data be discovered and used by providing their metadata (e.g. about unemployment rates or income) on the web in form of RDF.
+%Recently, members of the \emph{SBE} and Linked Data community developed the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}}, 
+%an effort to expose \emph{DDI} metadata within the Web of Linked Data.
+
 %\section{Running Example}
@@
 
-In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.
-
-\textbf{Metadata on Aggregated Data.}
-The vocabulary \emph{QB} represents metadata on multi-dimensional aggregate data in two files, a \emph{qb:DataSet} and a \emph{qb:DataStructureDefinition}.
-The \emph{qb:DataStructureDefinition} contains metadata of the present data collection.
-Thereby, the variable \emph{formal childcare} is modelled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
-The variables \emph{year}, \emph{duration}, \emph{age}, and \emph{country} are defined as \emph{qb:dimension}.
+%In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.
+
+%\textbf{Metadata on Aggregated Data.}
+\emph{QB} represents metadata on multi-dimensional aggregate data in two files: a \emph{qb:DataSet} and a \emph{qb:DataStructureDefinition}.
+The \emph{qb:DataStructureDefinition} contains metadata of the data collection.
+The variable \emph{formal childcare} is modelled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
+The variables \emph{year}, \emph{duration}, \emph{age}, and \emph{country} are \emph{qb:dimensions}.
 Data values, i.e., the availability of childcare services in percent over the population, are collected in a \emph{qb:DataSet}. 
-Each data value is represented inside a \emph{qb:Observation} which additionally contains values for each dimension 
-(e.g., the year in which \emph{formal childcare} has been determined).
-
-\textbf{Rectangular Data.}
-\emph{PHDD} represents data in a rectangular format in RDF. 
+Each data value is represented inside a \emph{qb:Observation} which contains values for each dimension\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}}.
+%(e.g., the year in which \emph{formal childcare} has been determined).
+
+%\textbf{Rectangular Data.}
+\emph{PHDD} represents data in tabular format in RDF enabling further aggregations and calculations. 
 The data could be either represented in records with character-separated values (CSV) or fixed length. 
-Eurostat provides the two-dimensional table about \emph{formal childcare} in form of a CSV file. 
-The \emph{phdd:Table} is structured by a table structure (\emph{phdd:TableStructure}, \emph{phdd:Delimited}).
-The table structure includes information about the character set (\emph{ASCII}), the variable delimiter (\emph{,}), the new line marker (\emph{CRLF}), and the first line where the data starts (\emph{2}).
+\emph{Eurostat} provides a CSV file, a two-dimensional table (\emph{phdd:Table}) about \emph{formal childcare} 
+which is structured by a table structure (\emph{phdd:TableStructure}, \emph{phdd:Delimited})
+including information about the character set (\emph{ASCII}), the variable delimiter (\emph{,}), the new line marker (\emph{CRLF}), and the first line where the data starts (\emph{2}).
 The table structure is related to table columns (\emph{phdd:Column}) which are described by column descriptions (\emph{phdd:DelimitedColumnDescription}).
 For the column containing the cell values in percent, the column position (\emph{5}), the recommended data type (\emph{xsd:nonNegativeInteger}), and the storage format (\emph{TINYINT}) is stated. 
-The RDFication enables further aggregations and calculations, e.g., in order to compare \emph{formal childcare} between Northern and Southern Europe or between otherwise grouped countries.
+%The RDFication enables further aggregations and calculations, e.g., in order to compare \emph{formal childcare} between Northern and Southern Europe or between otherwise grouped countries.
 % macht mehr sinn wenn Tabelle in mehreren Dimensionen vorhanden ist ode wenn Klassifikationen wie ISCO verwendet werden
 
-\textbf{Metadata on Person-Level Data.}
-For a broader view of the data framework and more detailed analyses we refer to the metadata on person-level data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}
-published by the \emph{Microdata Information System (MISSY)}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}}.
+%\textbf{Metadata on Person-Level Data.}
+For more detailed analyses we refer to the metadata on person-level data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}.
+%published by the \emph{Microdata Information System (MISSY)}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}}.
 Where data collection is cyclic, data sets may be released as \emph{series}, 
-where each cycle of the data collection activity produces one or more data sets. 
-\emph{Missy} is an online service platform that provides systematically structured metadata for official statistics on European person-level data sets. 
+where each cycle produces one or more data sets. 
+%\emph{Missy} is an online service platform that provides systematically structured metadata for official statistics on European person-level data sets. 
 %This includes data documentation at the study and variable level as well as documentation materials, tools and further information. 
 Aggregated (qb:DataSet) and underlying person-level data sets (\emph{disco:LogicalDataSet}) are connected by \emph{prov:wasDerivedFrom}. 
-The aggregated variable \emph{formal childcare} is calculated on the basis of six person-level variables like 
-\emph{Education at pre-school}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC/2011/Cross-sectional/original#2011-Cross-sectional-RL010}}.
+The aggregated variable \emph{formal childcare} is calculated on the basis of six person-level variables 
+(e.g., \emph{Education at pre-school}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC/2011/Cross-sectional/original#2011-Cross-sectional-RL010}})
 %(2) Education at compulsory school,
@@
 %(6) Child care by grand-parents, household members, relatives, friends, neighbours.
-For each person-level variable detailed metadata is given (definitions, descriptions, theoretical concepts, questions variables are based on, code lists, frequencies, descriptive statistics, countries, year of data collection, and classifications) which enables researchers to replicate the results shown in the aggregated data tables from Eurostat.
-The vocabulary \emph{Disco} represents metadata on person-level data in RDF.
+for which detailed metadata is given 
+%(definitions, descriptions, theoretical concepts, questions variables are based on, code lists, frequencies, descriptive statistics, countries, year of data collection, and classifications) 
+(e.g., code lists)
+enabling researchers to replicate the results shown in aggregated data tables.
+The \emph{DDI-RDF Discovery Vocabulary (Disco)} is a vocabulary to represent metadata on person-level data in RDF.
 The series (\emph{disco:StudyGroup}) \emph{EU-SILC} contains one study (\emph{disco:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
@@
 
-\textbf{Organizations, Hierarchies, and Classifications.}
+%\textbf{Organizations, Hierarchies, and Classifications.}
 %\textbf{Reusing SKOS.}
-The \emph{Simple Knowledge Organization System (SKOS)} is reused multiple times to represent metadata on aggregated and person-level data.
+The \emph{Simple Knowledge Organization System (SKOS)} is reused multiple times to build \emph{SBE} vocabularies.
 Variables are constructed out of values and/or (un)ordered code lists.
@@
 a \emph{skos:OrderedCollection} organizes them in a particular order within a \emph{skos:memberList}.
-A variable may be associated with a theoretical concept (\emph{skos:Concept}) and   
-\emph{skos:narrower} builds the hierarchy of theoretical concepts within the \emph{skos:ConceptScheme} of a series.
-The variable \emph{Education at pre-school}, e.g., is assigned to the theoretical concept \emph{Child Care} which is the narrower concept of \emph{Education} - one of the top concepts of the series \emph{EU-SILC}.
+A variable may be associated with a theoretical concept (\emph{skos:Concept}). 
+\emph{skos:narrower} builds the hierarchy of theoretical concepts within a \emph{skos:ConceptScheme} of a series.
+The variable \emph{Education at pre-school} is assigned to the theoretical concept \emph{Child Care} which is the narrower concept of \emph{Education} - one of the top concepts of the series \emph{EU-SILC}.
 Controlled vocabularies (\emph{skos:ConceptScheme}), serving as extension and reuse mechanism,
-organize types (\emph{skos:Concept}) of descriptive statistics (\emph{\emph{disco:SummaryStatistics}}) like minimum, maximum, and arithmetic mean.
-\emph{XKOS}\footnote{\url{https://github.com/linked-statistics/xkos}} is a SKOS extension to describe formal statistical classifications like the International Standard Classification of Occupations (\emph{ISCO}).
+organize types (\emph{skos:Concept}) of descriptive statistics (\emph{disco:SummaryStatistics}) like minimum, maximum, and arithmetic mean.
+%\emph{XKOS}\footnote{\url{https://github.com/linked-statistics/xkos}} is a SKOS extension to describe formal statistical classifications like the International Standard Classification of Occupations (\emph{ISCO}).
 %and the Statistical Classification of Economic Activities in the European Community \emph{NACE}.

### 2015-04-27 paper/paper7/paper7.tex
motivation

@@
 
-The data most often used in research within the \emph{SBE} community is \emph{person-level data} or more generally \emph{record-unit data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers
+The data most often used in research within the \emph{SBE} community is \emph{person-level data} (or more generally \emph{record-unit data}, i.e., data collected about individuals, businesses, and households) in form of responses to studies or taken from administrative registers
 (such as hospital records, registers of births and deaths). 
 The range of person-level data is very broad - 
-including census, education, and health data as well as all types of business, social, and labor force surveys.  
+including census, education, health data and business, social, and labor force surveys.  
 This type of research data is
@@
 reused by future researchers.
-In performing their research, the detailed person-level
-data is aggregated into less confidential multi-dimensional tables which answer particular research questions.
-Portals harvest metadata (as well as publicly available data) from multiple data providers in form of RDF.
-To ensure high quality, (meta)data must satisfy certain criteria - specified in terms of RDF constraints.  
-%After validating the metadata according to these constraints, portals offer added values to their customers, e.g., by searching over and comparing metadata of multiple providers.
 
 By its nature, person-level data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 
-The purpose of publicly available aggregated data, on the other hand, is to get a first overview and to gain an interest in further analyses on the underlying person-level data.
-Researchers typically represent their results as aggregated data in form of two-, three-, or four-dimensional tables with only a few columns (so-called \emph{variables} such as \emph{sex} or \emph{age}).
-The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing metadata on \emph{data cubes}, i.e.
-multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}.
-Aggregated data is derived from person-level data by statistics on groups or aggregates such as frequencies and arithmetic means.
+Researchers typically represent their results as aggregated data in form of multi-dimensional tables with only a few columns; so-called \emph{variables} such as \emph{sex} or \emph{age}.
+%In performing their research, the detailed person-level
+%data is aggregated into multi-dimensional tables which answer particular research questions.
+Aggregated data, which answers particular research questions, is derived from person-level data by statistics on groups or aggregates such as frequencies and arithmetic means.
 %The SDMX metadata standard – used as the basis for \emph{QB} – and DDI have traditionally made efforts to align their content. 
@@
 %it is more and more common to publish aggregated data as CSV files,
-
-Aggregated data is more and more published as CSV files,
-allowing to perform first data calculations.
+The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying person-level data.
+Aggregated data is more and more published in form of CSV files,
+allowing to perform data calculations.
 %For these calculations, definitions of the columns are needed (e.g. is a given variable interpreted numerically or as a string).
-\emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} is a vocabulary to represent data in tabular format in RDF.\tb{tabular data} 
-The data could be either represented in records with character-separated values (CSV) or in records with fixed length.
-
-For more detailed analyses, researchers refer to person-level data from which aggregated data is derived from, 
-as person-level data include additional variables needed for further research.
+%\emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} is a vocabulary to represent data in tabular format in RDF.\tb{tabular data} 
+%The data could be either represented in records with character-separated values (CSV) or in records with fixed length.
+
+For more detailed analyses, researchers refer to person-level data including additional variables needed to answer subsequent research questions
 %Although not that common, the other direction is also possible, 
 %i.e. researchers may use metadata on person-level data to search for aggregated data.
-One very common example for detailed analyses on person-level data is the content-driven comparison of multiple studies.
+like the comparison of studies between countries.
 A \emph{study} represents the process by which a data set was generated or collected.
-Eurostat\footnote{\url{http://ec.europa.eu/eurostat}} is the statistical office of the European Union.
-Its task is to provide statistics at European level that enable comparisons between countries and regions.
-Eurostat provides publicly available European aggregated data (downloadable as CSV files) and its metadata.
-This way, researchers get promising findings (in form of published tables with a few columns).
-
-We use the availability of childcare services in European Union Member States by year, duration, and child age leading to subsequent research questions as running example of this paper.\tb{nochmals drüber schauen}
+Eurostat\footnote{\url{http://ec.europa.eu/eurostat}}, the statistical office of the European Union, provides research findings in form of aggregated data (downloadable as CSV files) and its metadata at European level that enable comparisons between countries.
+%This way, researchers get promising findings (in form of published tables with a few columns).
+
+%We use the availability of childcare services in European Union member states by year, duration, and child age leading to subsequent research questions as running example of this paper.
 %The first step is to determine in which countries the unemployment rate is collected and which other variables of each country-specific study are theoretically comparable and can therefore be used to answer the underlying research question.
-The variable \emph{formal childcare}\footnote{The data set is available at: \url{http://ec.europa.eu/eurostat/web/products-datasets/-/ilc_caindformal}} (in contrast to childcare at home)
-captures the measured availability of childcare services in percent over the population.
-The present data collection refers to data on formal childcare by the variables \emph{year}, \emph{duration} (in hours per week), \emph{age} of the child, and \emph{country}.
+The variable \emph{formal childcare}\footnote{Aggregated data and its metadata is available at: \url{http://ec.europa.eu/eurostat/web/products-datasets/-/ilc_caindformal}} %(in contrast to childcare at home)
+captures the measured availability of childcare services in percent over the population in European Union member states by 
+the variables \emph{year}, \emph{duration} (in hours per week), \emph{age} of the child, and \emph{country}.
 Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
@@
 
-To determine if variables measuring \emph{age}\tb{vielleicht zu den letzten paragraphen hinzufügen} 
+To determine if variables measuring \emph{age} 
 - collected for different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
@@
 With technology-driven constraints, it can be validated (1) if variable definitions are available and (2) if for each code an associated category (a human-readable label) is specified.
+
+-----
+
+Portals harvest metadata (as well as publicly available data) from multiple RDF data providers.
+To ensure high quality, (meta)data must satisfy certain criteria - specified in terms of RDF constraints.  
+%After validating the metadata according to these constraints, portals offer added values to their customers, e.g., by searching over and comparing metadata of multiple providers.
 
@@
 %\textbf{Metadata on Aggregated Data.}
-\emph{QB} represents metadata on multi-dimensional aggregate data in two files: a \emph{qb:DataSet} and a \emph{qb:DataStructureDefinition}.
-The \emph{qb:DataStructureDefinition} contains metadata of the data collection.
+The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing metadata on \emph{data cubes}, i.e.
+multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}.
+%\emph{QB} represents metadata on multi-dimensional aggregate data in two files: a \emph{qb:DataSet} and a \emph{qb:DataStructureDefinition}.
+A \emph{qb:DataStructureDefinition} contains metadata of the data collection.
 The variable \emph{formal childcare} is modelled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
@@
 %\textbf{Rectangular Data.}
-\emph{PHDD} represents data in tabular format in RDF enabling further aggregations and calculations. 
+\emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} is a vocabulary to represent data in tabular format in RDF enabling further aggregations and calculations.
 The data could be either represented in records with character-separated values (CSV) or fixed length. 

### 2015-04-27 paper/paper7/paper7.tex
motivation

@@
 %The data could be either represented in records with character-separated values (CSV) or in records with fixed length. 
+Portals harvest metadata (as well as publicly available data) from multiple RDF data providers.
+To ensure high quality, (meta)data must satisfy certain criteria - specified in terms of RDF constraints.
 
@@
 %This way, researchers get promising findings (in form of published tables with a few columns).
-
 %We use the availability of childcare services in European Union member states by year, duration, and child age leading to subsequent research questions as running example of this paper.
@@
 Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
-The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger}, or by a code list including multiple age clusters (such as '0 to 10' and '11 to 20').
+The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger} or by a code list of age clusters (e.g., '0 to 10' and '11 to 20').
 
@@
 - collected for different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
-are comparable, both content-driven and technology-driven constraints are validated.
-Content-driven constraints ensure that the data is consistent with the intended syntax, semantics, and integrity of vocabularies' data models and 
-technology-driven constraints can be generated completely automatically out of vocabularies' data models. 
-Examples for content-driven constraints are to investigate (1) if variables are represented in a compatible way,
-i.e. are the variables' code lists theoretically comparable, and (2) if variables' code lists are properly structured.
-With technology-driven constraints, it can be validated (1) if variable definitions are available and (2) if for each code an associated category (a human-readable label) is specified.
-
------
-
-Portals harvest metadata (as well as publicly available data) from multiple RDF data providers.
-To ensure high quality, (meta)data must satisfy certain criteria - specified in terms of RDF constraints.  
+are comparable, diverse constraints are checked:
+(1) variable definitions must be available, 
+(2) for each code a human-readable label has to be specified,
+(3) code lists must be structured properly, and
+(4) code lists must either be identical or at least similar.
+If a researcher only wants to get a first overview over comparable variables (use case 1), 
+covering the first three constraints may be sufficient,
+i.e., the violation of the first three constraints is more serious than the violation of the last constraint.
+If the intention of the researcher is to perform more sophisticated comparisons (use case 2), however, the user may raise the severity level of last constraint.
+
 %After validating the metadata according to these constraints, portals offer added values to their customers, e.g., by searching over and comparing metadata of multiple providers.
@@
 The \emph{Simple Knowledge Organization System (SKOS)} is reused multiple times to build \emph{SBE} vocabularies.
-Variables are constructed out of values and/or (un)ordered code lists.
+%Variables are constructed out of values and/or (un)ordered code lists.
 The codes of the variable \emph{Education at pre-school} (number of education hours per week) are modeled as \emph{skos:Concepts} and 
@@
 
-A very common research question is to compare variables of multiple studies or countries (constraint type: \emph{comparison}).
-To compare variables 
-(1) their code lists must be structured properly and
-(2) their code lists must either be identical or at least similar.
-If a researcher only wants to get a first overview over comparable variables (use case 1), 
-covering the first constraint may be sufficient.
-Thus, the severity level of the first constraint is stronger ($\mathcal{SL}_{2}$) than the one for the second constraint ($\mathcal{SL}_{0}$).
-If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the second constraint is getting more serious
-and the user may raise its severity level.
+%A very common research question is to compare variables of multiple studies or countries (constraint type: \emph{comparison}).
+%To compare variables 
+%(1) their code lists must be structured properly and
+%(2) their code lists must either be identical or at least similar.
+%If a researcher only wants to get a first overview over comparable variables (use case 1), 
+%covering the first constraint may be sufficient.
+%Thus, the severity level of the first constraint is stronger ($\mathcal{SL}_{2}$) than the one for the second constraint ($\mathcal{SL}_{0}$).
+%If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the second constraint is getting more serious
+%and the user may raise its severity level.
 %\textbf{Comparison.}

### 2015-04-27 paper/paper7/paper7.tex
motivation

@@
 %\title{RDF Constraints to Ensure High Quality \\ of Metadata and Data}
-\title{Classification of RDF Constraint Types Ensuring High Quality of Metadata and Data}
+\title{Classification of RDF Constraint Types to Ensure High Quality of Metadata and Data}
 \subtitle{}
@@
 \and
-University of Mannheim, Germany \\
-\email{kai@informatik.uni-mannheim.de} 
+Stuttgart Media University, Germany \\
+\email{eckert@hdm-stuttgart.de} 
 }
@@
 The \textbf{contribution} of this paper is the development of a system 
-(1) to classify RDF constraints to evaluate the quality of (meta)data which may be represented by any vocabulary and 
-(2) to classify RDF constraint types which in most cases correspond to RDF validation requirements.
+(1) to classify RDF constraints (according to their severity levels) to evaluate the quality of (meta)data which may be represented by any vocabulary and 
+(2) to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements.
 By defining a huge amount of constraints of the majority of constraint types
@@
 %we apply the developed classification system to several and different vocabularies from the community around research data for the \emph{social, behavioural, and economic (SBE) sciences} in order to
-we prove the claim that the developed classification system perfectly applies vocabulary-independent and therefore to prove the generality of the proposed classification system.
+we prove the claim that the developed classification system perfectly applies vocabulary-independent and therefore to prove its generality.
 
 We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple and different vocabularies to get an understanding
-(1) which sets of constraint types and 
-(2) which sets of constraints (associated with particular severity levels) encompass the most/fewest violated constraints.
+(1) which sets of constraint types (on different levels of complexity) and 
+(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations.
 
@@
 
-For data archives, research institutes, and data libraries,
-RDF data validation according to predefined constraints is a much sought-after feature, 
-particularly as this is taken for granted in the XML world. 
+For more than a decade, members of the \emph{SBE} community have been developing and using a
+metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)},
+an XML format to disseminate, manage,
+and reuse data collected and archived for research \cite{Vardigan2008}.  
+%DDI is heavily used by the CESSDA community of European national data archives, 
+%the International Household Survey Network community (made up of more than 90 statistical agencies),
+%and ICPSR - the largest SBE data archive in the US.
+Increasingly, data professionals, data archives, data libraries, government statisticians (e.g. \url{data.gov}, \url{data.gov.uk}), and national statistical institutes
+are very interested in having their data be discovered and used by exposing their metadata (e.g. about unemployment rates or income) within the Web of Linked Data.
+%Recently, members of the \emph{SBE} and Linked Data community developed the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}}, 
+%an effort to expose \emph{DDI} metadata within the Web of Linked Data. 
+%For data archives, research institutes, and data libraries,
+%RDF data validation according to predefined constraints is a much sought-after feature, 
+%particularly as this is taken for granted in the XML world. 
 %as DDI-XML documents are validated against diverse XSDs\footnote{\label{fnt:DDI-XSDs}\url{http://www.ddialliance.org/Specification/}} (section \ref{related-work}).
@@
 \begin{enumerate}
-	\item to classify RDF constraints to evaluate the quality of metadata and data which may be represented by any vocabulary and 
-	\item to classify RDF constraint types which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (section \ref{classification} - \ref{complex-constraint-types}).
+	\item to classify RDF constraints (according to their severity levels) to evaluate the quality of metadata and data which may be represented by any vocabulary and 
+	\item to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (section \ref{classification} - \ref{complex-constraint-types}).
 \end{enumerate}
@@
 We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple and different vocabularies to get an understanding
-(1) which sets of constraint types and 
-(2) which sets of constraints (associated with particular severity levels) encompass the most/fewest violated constraints (see section \ref{evaluation}).
+(1) which sets of constraint types (on different levels of complexity) and 
+(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).
 
@@
 %RDF data validation can only be performed semi-automatically, i.e., an automatic approach serves as basis for intellectual decisions.
-
-%For more than a decade, members of the community around research data for the \emph{social, behavioural, and economic (SBE) sciences} have been developing and using a
-%metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)},
-%an XML format to disseminate, manage,
-%and reuse data collected and archived for research \cite{Vardigan2008}.  
-%%DDI is heavily used by the CESSDA community of European national data archives, 
-%%the International Household Survey Network community (made up of more than 90 statistical agencies),
-%%and ICPSR - the largest SBE data archive in the US.
-%Increasingly, data professionals, data archives, data libraries, government statisticians (e.g. \url{data.gov}, \url{data.gov.uk}), and national statistical institutes
-%are very interested in having their data be discovered and used by providing their metadata (e.g. about unemployment rates or income) on the web in form of RDF.
-%Recently, members of the \emph{SBE} and Linked Data community developed the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}}, 
-%an effort to expose \emph{DDI} metadata within the Web of Linked Data.
 
@@
 
-The complete set of \emph{constraint types} ($\mathcal{CT}$) encompasses three disjoint \emph{sets of constraint types}:
+According to the complexity of constraint types, the complete set of \emph{constraint types} ($\mathcal{CT}$) encompasses three disjoint \emph{sets of constraint types}:
 \begin{enumerate}
@@
 We evaluated the (meta)data quality of large real world data sets represented by multiple and different vocabularies to get an understanding  
-(1) which sets of constraint types and 
-(2) which sets of constraints (associated with particular severity levels) encompass the most/fewest violated constraints (see section \ref{evaluation}).
+(1) which sets of constraint types (on different levels of complexity) and 
+(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).
 
@@
 Resource Shapes, and the Web Ontology Language\footnote{SPIN mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} \cite{BoschEckert2014-2}.
-The \emph{RDF Validator} also validates RDF data to ensure correct syntax, semantics, and integrity of diverse vocabularies such as \emph{Disco, QB, PHDD, SKOS, and XKOS}.
+The \emph{RDF Validator} also validates RDF data to ensure correct syntax, semantics, and integrity of diverse vocabularies such as \emph{Disco}, \emph{QB}, \emph{SKOS}, and \emph{PHDD}.
 Although accessible within our validation tool, we provide all implemented constraints\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} in form of SPARQL CONSTRUCT queries.
-For the subsequent evaluation, we implemented 213 constraints on \emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{XKOS}, and \emph{PHDD} data sets.
+For the subsequent evaluation, we implemented 213 constraints on \emph{Disco}, \emph{QB}, \emph{SKOS}, and \emph{PHDD} data sets.
 The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.
@@
 \section{Conclusion and Future Work}
+
 \tb{ToDO}
-In this paper, we showed in form of a complete real world running example how to represent metadata on person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
-We explained why RDF validation is important in this context and how metadata on person-level data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality\footnote{The first appendix of this paper describing each constraint in detail is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}} (\textbf{contribution 2}, section \ref{rdf-validation}).
-We distinguish two validation types:
-(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of data models (section \ref{complex-constraint-types}).
-(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges (section \ref{basic-constraint-types}).
-We determined the default \emph{severity level} for each constraint to indicate how serious the violation of the constraint is
-and propose an extensible metric to measure the continuum of severity levels.
-
-We implemented a validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages and to ensure correct syntax, semantics, and integrity of diverse vocabularies such as \emph{Disco, QB, PHDD, SKOS, and XKOS} (section \ref{implementation}).
-We exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets by means of 213 $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
-We validated more than 4.2 billion triples and 15 thousand data sets\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).
+
+%In this paper, we showed in form of a complete real world running example how to represent metadata on person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
+%We explained why RDF validation is important in this context and how metadata on person-level data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality\footnote{The first appendix of this paper describing each constraint in detail is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}} (\textbf{contribution 2}, section \ref{rdf-validation}).
+%We distinguish two validation types:
+%(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of data models (section \ref{complex-constraint-types}).
+%(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges (section \ref{basic-constraint-types}).
+%We determined the default \emph{severity level} for each constraint to indicate how serious the violation of the constraint is
+%and propose an extensible metric to measure the continuum of severity levels.
+
+\footnote{The first appendix of this paper describing each constraint in detail is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}}
+
+We implemented a validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages and to ensure correct syntax and semantics of diverse vocabularies such as \emph{Disco}, \emph{QB}, \emph{SKOS}, and \emph{PHDD} (section \ref{implementation}).
+We exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets (more than 4.2 billion triples and 15 thousand data sets) by means of 213  constraints of the majority of the constraint types\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).
 

### 2015-04-28 paper/paper7/paper7.tex
introduction

@@
 The intention is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
-The requirements are classified to better evaluate existing solutions and each requirement is directly mapped to a constraint type which is expressible by at least one existing constraint language.
+The requirements are classified to better evaluate existing solutions and each requirement is directly mapped to a constraint type which is expressible by at least one constraint language.
 As \emph{SPIN} is the within the RDF validation community accepted and widely adopted way to check constraints on RDF data, Bosch and Eckert \cite{BoschEckert2014-2} use \emph{SPIN} as basis to define a
@@
 	\item to classify RDF constraints (according to their severity levels) to evaluate the quality of metadata and data which may be represented by any vocabulary and 
-	\item to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (section \ref{classification} - \ref{complex-constraint-types}).
+	\item to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (sections \ref{classification} - \ref{complex-constraint-types}).
 \end{enumerate}
-By defining a huge amount of constraints of different constraint types,   
-we apply the developed classification system to several and different vocabularies from the \emph{SBE} domain to represent both metadata and data and therefore prove the generality of the proposed classification system.
+By defining a huge amount of constraints of the majority of the constraint types,   
+we apply the developed classification system to several and different vocabularies from the \emph{SBE} domain to represent both metadata and data and therefore prove its generality.
 A complex and complete real world running example from the \emph{SBE} domain serves to prove the claim that the developed classification system perfectly applies for diverse vocabularies.
@@
 We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
-how data in tabular format (expressed by the \emph{PHDD} vocabulary) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), and thesauri (\emph{SKOS}) are represented in RDF, and how therefore reused vocabularies are interrelated (section \ref{rdf-representation}).
+how data in tabular format and metadata on person-level data sets, aggregated data sets, and thesauri are represented in RDF, and how therefore reused vocabularies are interrelated (section \ref{rdf-representation}).
 We explain how \emph{SBE} (meta)data is validated against constraints, instantiated from constraint types organized in the classification system, to ensure high quality of and trust in (meta)data.

### 2015-04-28 paper/paper7/paper7.tex
introduction

@@
 We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
-how data in tabular format and metadata on person-level data sets, aggregated data sets, and thesauri are represented in RDF, and how therefore reused vocabularies are interrelated (section \ref{rdf-representation}).
-We explain how \emph{SBE} (meta)data is validated against constraints, instantiated from constraint types organized in the classification system, to ensure high quality of and trust in (meta)data.
+how data in tabular format and metadata on person-level data sets, aggregated data sets, and thesauri are represented in RDF, 
+how therefore reused vocabularies are interrelated (section \ref{rdf-representation}),
+and how \emph{SBE} (meta)data is validated against constraints of different constraint types (sections \ref{classification} - \ref{complex-constraint-types}).
 

### 2015-04-28 paper/paper7/paper7.tex
introduction

@@
 %we apply the developed classification system to several and different vocabularies from the community around research data for the \emph{social, behavioural, and economic (SBE) sciences} in order to
-we prove the claim that the developed classification system perfectly applies vocabulary-independent and therefore to prove its generality.
-
-We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple and different vocabularies to get an understanding
+we prove the claim that the proposed classification system perfectly applies vocabulary-independent and therefore we prove its generality.
+
+We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple vocabularies to get an understanding
 (1) which sets of constraint types (on different levels of complexity) and 
@@
 and how \emph{SBE} (meta)data is validated against constraints of different constraint types (sections \ref{classification} - \ref{complex-constraint-types}).
-
-We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple and different vocabularies to get an understanding
+We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple vocabularies to get an understanding
 (1) which sets of constraint types (on different levels of complexity) and 

### 2015-04-28 paper/paper7/paper7.tex
introduction

@@
   %\sffamily
+  \small
   \vspace{0cm}
@@
 are very interested in having their data be discovered and used by exposing their metadata (e.g. about unemployment rates or income) within the Web of Linked Data.
+As \emph{DDI} XML documents are validated against diverse XSDs\footnote{\label{fnt:DDI-XSDs}\url{http://www.ddialliance.org/Specification/}} (see section \ref{related-work}),
+the \emph{SBE} community is used to have this functionality in the XML world.
 %Recently, members of the \emph{SBE} and Linked Data community developed the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}}, 
@@
 identified 76 requirements to formulate RDF constraints (e.g.
-\emph{R-75, R-81: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}\cite{BoschNolleAcarEckert2015}.
+\emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}\cite{BoschNolleAcarEckert2015}.
 We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages.
@@
 {\emph{Data property facets} (\emph{R-46}) is an example of an $\mathcal{CT}_{S}$ constraint type which enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
-The abstract of series/studies, e.g., should have a minimum length ($\mathcal{SL}_{1}$).
+The abstract of series/studies, e.g., should have a minimum length.
 

### 2015-04-28 paper/paper7/paper7.tex
feedback Kai

@@
 \begin{abstract}
+\tb{nur data und nicht metadata}
 For research institutes, data libraries, and data archives,
@@
 
-The \textbf{contribution} of this paper is the development of a system 
-(1) to classify RDF constraints (according to their severity levels) to evaluate the quality of (meta)data which may be represented by any vocabulary and 
-(2) to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements.
-By defining a huge amount of constraints of the majority of constraint types
-to validate data sets from the community around research data for the \emph{social, behavioural, and economic (SBE) sciences},  
-%we apply the developed classification system to several and different vocabularies from the community around research data for the \emph{social, behavioural, and economic (SBE) sciences} in order to
-we prove the claim that the proposed classification system perfectly applies vocabulary-independent and therefore we prove its generality.
-
-We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple vocabularies to get an understanding
-(1) which sets of constraint types (on different levels of complexity) and 
-(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations.
+Based on our work in the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group, we identified and published by today 82 types of constraints that are required by various stakeholders for data applications.
+
+In this paper, we formulate 213 constraints of 53 different types on four different vocabularies (Disco, QB, SKOS, PHDD) and classify them according to the complexity level of their type and their severity level for the vocabulary.
+Further, for 114 of these constraints, we evaluate the data quality of 15,694 datasets (4,26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.
+
+Based on the results, we postulate three important findings: (1) A significant amount of 47\% of the violations refer to complex constraints that are not easily expressible in existing languages which confirms the necessity to provide suitable constraint languages.
+(2) For well-established vocabularies, the explicitly defined constraints are almost completely satisfied which demonstrates that constraint formulation in general works.
+(3) The percentage of severe constraint violations is very low, compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
+
+%The \textbf{contribution} of this paper is the development of a system 
+%(1) to classify RDF constraints (according to their severity levels) to evaluate the quality of (meta)data which may be represented by any vocabulary and 
+%(2) to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements.
+%By defining a huge amount of constraints of the majority of constraint types
+%to validate data sets from the community around research data for the \emph{social, behavioural, and economic (SBE) sciences},  
+%we prove the claim that the proposed classification system perfectly applies vocabulary-independent and therefore we prove its generality.
+%
+%We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple vocabularies to get an understanding
+%(1) which sets of constraint types (on different levels of complexity) and 
+%(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations.
 
@@
 
-\subsection{Classification of Constraint Types}
+\subsection{Classification of RDF Constraint Types}
 
@@
 
-\subsection{Classification of Constraints}
-
-\emph{SBE} experts determined the default \textbf{\emph{severity level}} (\emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
+\subsection{Classification of RDF Constraints}
+
+\emph{SBE} experts determined the default \textbf{\emph{severity level}} (\emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.\tb{of the 213 constraints}
 We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ to $\mathcal{SL}_{2}$.

### 2015-04-28 paper/paper7/paper7.tex
feedback

@@
 %\title{RDF Constraints to Ensure High Quality \\ of Metadata and Data}
-\title{Classification of RDF Constraint Types to Ensure High Quality of Metadata and Data}
+\title{RDF Constraint Types to Ensure High Data Quality}
 \subtitle{}
@@
 \begin{abstract}
-\tb{nur data und nicht metadata}
+
 For research institutes, data libraries, and data archives,
@@
 
-In this paper, we formulate 213 constraints of 53 different types on four different vocabularies (Disco, QB, SKOS, PHDD) and classify them according to the complexity level of their type and their severity level for the vocabulary.
-Further, for 114 of these constraints, we evaluate the data quality of 15,694 datasets (4,26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.
+In this paper, we formulate 213 constraints of 53 different types on four different vocabularies (Disco, QB, SKOS, PHDD) and classify them according to the complexity level of their type and their severity level.
+For 114 of these constraints, we evaluate the data quality of 15,694 datasets (4,26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.
 
@@
 \section{Introduction}
+
+\tb{nur data und nicht metadata}
 
@@
 		\emph{C (}$\mathcal{CT}_{B}$\emph{)} & 78 (\textbf{54.6\%}) & 19 (\textbf{54.3\%}) & 10 (\textbf{28.6\%}) & 107 (\textbf{50.2\%}) \\
-		\hline
-		\emph{C (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 67 (46.9\%) & 13 (37.1\%) & 4 (11.4\%) & 84 (39.4\%) \\
-		\emph{C (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 11 (7.7\%) & 6 (17.1\%) & 6 (17.1\%) & 23 (10.8\%) \\
+		%\hline
+		%\emph{C (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 67 (46.9\%) & 13 (37.1\%) & 4 (11.4\%) & 84 (39.4\%) \\
+		%\emph{C (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 11 (7.7\%) & 6 (17.1\%) & 6 (17.1\%) & 23 (10.8\%) \\
 		\hline
@@
     \\ \midrule
-		\emph{CV} & 3,575,002 (6.5\%) & 45,635,861 (83.4\%) & 5,540,988 (10.1\%) & 54,751,851 \\
-		\hline
-		\emph{CV (}$\mathcal{CT}_{C}$\emph{)} & 652,780 (18.3\%) & 45,634,084 (\textbf{100\%}) & 1,185,982 (21.4\%) & 47,472,846 (\textbf{86.7\%}) \\
-		\emph{CV (}$\mathcal{CT}_{S}$\emph{)} & 560,857 (15.7\%) & 0 (0\%) & 4,355,006 (\textbf{78.6\%}) & 4,915,863 (9\%) \\
-		\emph{CV (}$\mathcal{CT}_{B}$\emph{)} & 2,361,365 (\textbf{66.1\%}) & 1,777 (0\%) & 0 (0\%) & 2,363,142 (4.3\%) \\
-		\hline
-		\emph{CV (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 2,333,365 (65.3\%) & 1,777 (0\%) & 0 (0\%) & 2,335,142 (4.3\%) \\
-		\emph{CV (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 28,000 (0.8\%) & 0 (0\%) & 0 (0\%) & 28,000 (0.1\%) \\
+		\emph{CV} & 3,575,002 & 45,635,861 & 5,540,988 & 54,751,851 \\
+		\hline
+		\emph{CV (}$\mathcal{CT}_{C}$\emph{)} & 18.3\% & 45,634,084 (\textbf{100\%}) & 1,185,982 (21.4\%) & 47,472,846 (\textbf{86.7\%}) \\
+		\emph{CV (}$\mathcal{CT}_{S}$\emph{)} & 15.7\% & 0 (0\%) & 4,355,006 (\textbf{78.6\%}) & 4,915,863 (9\%) \\
+		\emph{CV (}$\mathcal{CT}_{B}$\emph{)} & \textbf{66.1\%} & 1,777 (0\%) & 0 (0\%) & 2,363,142 (4.3\%) \\
+		%\hline
+		%\emph{CV (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 2,333,365 (65.3\%) & 1,777 (0\%) & 0 (0\%) & 2,335,142 (4.3\%) \\
+		%\emph{CV (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 28,000 (0.8\%) & 0 (0\%) & 0 (0\%) & 28,000 (0.1\%) \\
 		\hline
@@
 \end{table}
-
+\tb{prozent beziehen sich auf die oberste zeile / auch 0.0\%}
+\textcolor{red}{wir versuchen eine aussage zu trefen für alle vokabulare mit werten nur von 3 vokabularen / vorsichtig generelle aussagen zu treffen / normalisiterte werte mit prozentwerten / neues vokabulare, noch nicht so konsistente daten / hypothesen werden aufgestellt / conclusion: hypothesen werden aufgestellt, die vorsichtig zu genießen sind / basic constraints sind bei etablierten vokabularen publitierte datensätze werden eingehalten hohe datenqualität / schwerwiegende constraintverletzungen treten kaum auf / schwere constraints sind in idesen vielen daten nicht auf / disco ist in beiden fällen anders / erheblichen anteil von schwersten constraint verletzungen / disco neues vokabular das noch daten gelten noch einenm draft von disco oder hat disco nicht verstanden schnlechtere daten als entabliete vokabulare / es ist sinnvoll sprachen zu entwickeln komplexere constraints auszudrücken / simple und vocabulary können heute schon sehr gut beschrieben werden / wir wünschen und dass es komplexere constraint languages gibt mit denen complex constraints besser abgebildet werden können / deulticherer verbesserung in der datenualitt wenn wir diese constraint languages hätten / gibt es weitere hypothesen?
+- alles was in der tabelle auffällig ist / normaliisert über die datensatzgröße / 3 sehr wichtige und repräsentative vokabulare im sbe bereich / interessanate constraints mit ausreißern / hypothesen über weitere vokabulare müssen verifiziert oder falsifiziert werden / diskussion: / 3 constraints werden zufällig nie verletzt / basis für future work / motivation, dass man constraint languages entwicken muss die complexe constraints abbilden / datenqualität ist generell sehr hoch / als hypothese postulieren}
 More than 80\% of the overall approx. 55 million constraint violations are caused by \emph{QB} constraints (see table \ref{tab:evaluation-constraint-violations}).

### 2015-04-28 paper/paper7/paper7.tex
feedback

--- 2015-04-28 paper/paper7/paper7.tex
@@
 
+\usepackage{ntheorem}
+\newtheorem{hyp}{Hypothesis}
+
+\makeatletter
+\newcounter{subhyp} 
+\let\savedc@hyp\c@hyp
+\newenvironment{subhyp}
+ {%
+  \setcounter{subhyp}{0}%
+  \stepcounter{hyp}%
+  \edef\saved@hyp{\thehyp}% Save the current value of hyp
+  \let\c@hyp\c@subhyp     % Now hyp is subhyp
+  \renewcommand{\thehyp}{\saved@hyp\alph{hyp}}%
+ }
+ {}
+\newcommand{\normhyp}{%
+  \let\c@hyp\savedc@hyp % revert to the old one
+  \renewcommand\thehyp{\arabic{hyp}}%
+} 
+\makeatother
+
+\usepackage{multirow}
+
 \begin{document}
@@
     \begin{center}
-    \begin{tabular}{@{}lcccc@{}}
-%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
-%    \\  \cmidrule{2-7}
-    \\       \textbf{Criteria}
-           & \textbf{\emph{Disco}}
-           & \textbf{\emph{QB}}
-					 & \textbf{\emph{SKOS}}
-					 & \textbf{Total}
-    \\ \midrule
-		\emph{CV} & 3,575,002 (6.5\%) & 45,635,861 (83.4\%) & 5,540,988 (10.1\%) & 54,751,851 \\
-		\hline
-		\emph{CV (}$\mathcal{CT}_{C}$\emph{)} & 652,780 (18.3\%) & 45,634,084 (\textbf{100\%}) & 1,185,982 (21.4\%) & 47,472,846 (\textbf{86.7\%}) \\
-		\emph{CV (}$\mathcal{CT}_{S}$\emph{)} & 560,857 (15.7\%) & 0 (0\%) & 4,355,006 (\textbf{78.6\%}) & 4,915,863 (9\%) \\
-		\emph{CV (}$\mathcal{CT}_{B}$\emph{)} & 2,361,365 (\textbf{66.1\%}) & 1,777 (0\%) & 0 (0\%) & 2,363,142 (4.3\%) \\
-		\hline
-		\emph{CV (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 2,333,365 (65.3\%) & 1,777 (0\%) & 0 (0\%) & 2,335,142 (4.3\%) \\
-		\emph{CV (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 28,000 (0.8\%) & 0 (0\%) & 0 (0\%) & 28,000 (0.1\%) \\
-		\hline
-		\emph{CV ($\mathcal{SL}_{0}$)} & 1,880,777 (\textbf{52.6\%}) & 0 (0\%) & 2,281,740 (41.2\%) & 4,162,517 (7.6\%) \\
-		\emph{CV ($\mathcal{SL}_{1}$)} & 1,051,757 (29.4\%) & 45,520,613 (\textbf{99,8\%}) & 3,259,248 (\textbf{58.8\%}) & 49,831,618 (\textbf{91\%}) \\
-		\emph{CV ($\mathcal{SL}_{2}$)} & 642,468 (18\%) & 115,248 (0.3\%) & 0 (0\%) & 757,716 (1.4\%) \\
+    \begin{tabular}{@{}lcccccccc@{}}
+    %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
+    %\\  \cmidrule{2-3}
+		\hline
+    \multirow{2}{*}{} &
+      \multicolumn{2}{c}{\textbf{\emph{Disco}}} &
+      \multicolumn{2}{c}{\textbf{\emph{QB}}} &
+      \multicolumn{2}{c}{\textbf{\emph{SKOS}}} &
+      \multicolumn{2}{c}{\textbf{\emph{Total}}} \\
+    \textbf{} & C & CV & C & CV & C & CV & C & CV \\
+    \hline
+    %\\ \midrule
+		 & 143 & 3,575,002 & 35 & 45,635,861 & 35 & 5,540,988 & 213 & 54,751,851 \\
+		\hline
+		\textbf{\emph{complex}} & 25.9\% & 18.3\% & 37.1\% & \textbf{100\%} & \textbf{37.1\%} & 21.4\% & 33.4\% & \textbf{46.6\%} \\
+		\textbf{\emph{simple}} & 19.6\% & 15.7\% & 8.6\% & 0.0\% & \textbf{34.3\%} & \textbf{78.6\%} & 20.8\% & 31.4\% \\
+		\textbf{\emph{vocabulary}} & \textbf{54.6\%} & \textbf{66.1\%} & \textbf{54.3\%} & 0.0\% & \textbf{28.6\%} & 0.0\% & \textbf{45.8\%} & 22.0\% \\
+		%\hline
+		%\emph{CV (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 2,333,365 (65.3\%) & 1,777 (0\%) & 0 (0\%) & 2,335,142 (4.3\%) \\
+		%\emph{CV (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 28,000 (0.8\%) & 0 (0\%) & 0 (0\%) & 28,000 (0.1\%) \\
+		\hline
+		\textbf{\emph{info}} & \textbf{52.5\%} & \textbf{52.6\%} & 11.4\% & 0.0\% & \textbf{60.0\%} & 41.2\% & \textbf{41.3\%} & 31.3\% \\
+		\textbf{\emph{warning}} & 7.0\% & 29.4\% & 8.6\% & \textbf{99,8\%} & 14.3\% & \textbf{58.8\%} & 10.0\% & \textbf{62.7\%} \\
+		\textbf{\emph{error}} & 40.6\% & 18\% & \textbf{80.0\%} & 0.3\% & 25.7\% & 0.0\% & \textbf{48.8\%} & 6.1\%\\
     \bottomrule
     \end{tabular}
-    %\\ \emph{CV (constraint violations)}
-    \caption{Evaluation - Constraint Violations}
+    \\ \emph{C (constraints), CV (constraint violations)}
+    \caption{Constraints and Constraint Violations}
 		\label{tab:evaluation-constraint-violations}
@@
 \end{table}
+
+%\begin{table}[H]
+		%\scriptsize
+    %\begin{center}
+    %\begin{tabular}{@{}lcccccccc@{}}
+%%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
+%%    \\  \cmidrule{2-7}
+    %\\       \textbf{}
+           %& \textbf{\emph{Disco}}
+           %& \textbf{\emph{QB}}
+					 %& \textbf{\emph{SKOS}}
+					 %& \textbf{Total}
+					 %& \textbf{\emph{Disco}}
+           %& \textbf{\emph{QB}}
+					 %& \textbf{\emph{SKOS}}
+					 %& \textbf{Total}
+    %\\ \midrule
+		 %& 3,575,002 & 45,635,861 & 5,540,988 & 54,751,851 & & & &  \\
+		%\hline
+		%\textbf{\emph{complex}} & 18.3\% & \textbf{100\%} & 21.4\% & \textbf{86.7\%} & & & & \\
+		%\textbf{\emph{simple}} & 15.7\% & 0.0\% & \textbf{78.6\%} & 9\% & & & & \\
+		%\textbf{\emph{vocabulary}} & \textbf{66.1\%} & 0.0\% & 0\% & 4.3\% & & & & \\
+		%%\hline
+		%%\emph{CV (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 2,333,365 (65.3\%) & 1,777 (0\%) & 0 (0\%) & 2,335,142 (4.3\%) \\
+		%%\emph{CV (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 28,000 (0.8\%) & 0 (0\%) & 0 (0\%) & 28,000 (0.1\%) \\
+		%\hline
+		%\textbf{\emph{info}} & \textbf{52.6\%} & 0.0\% & 41.2\% & 7.6\% & & & & \\
+		%\textbf{\emph{warning}} & 29.4\% & \textbf{99,8\%} & \textbf{58.8\%} & \textbf{91\%} & & & & \\
+		%\textbf{\emph{error}} & 18\% & 0.3\% & 0.0\% & 1.4\% & & & & \\
+    %\bottomrule
+    %\end{tabular}
+    %%\\ \emph{CV (constraint violations)}
+    %\caption{Constraint Violations}
+		%\label{tab:evaluation-constraint-violations}
+    %\end{center}
+%\end{table}
+
+\tb{difference between 0\% and 78.6\%}
+\tb{basic constraints sind bei etablierten vokabularen publitierte datensätze werden eingehalten hohe datenqualität / schwerwiegende constraintverletzungen treten kaum auf / schwere constraints sind in idesen vielen daten nicht auf / disco ist in beiden fällen anders / erheblichen anteil von schwersten constraint verletzungen / disco neues vokabular das noch daten gelten noch einenm draft von disco oder hat disco nicht verstanden schnlechtere daten als entabliete vokabulare / es ist sinnvoll sprachen zu entwickeln komplexere constraints auszudrücken / simple und vocabulary können heute schon sehr gut beschrieben werden / wir wünschen und dass es komplexere constraint languages gibt mit denen complex constraints besser abgebildet werden können / deulticherer verbesserung in der datenualitt wenn wir diese constraint languages hätten / gibt es weitere hypothesen?
+- alles was in der tabelle auffällig ist / normaliisert über die datensatzgröße / 3 sehr wichtige und repräsentative vokabulare im sbe bereich / interessanate constraints mit ausreißern / hypothesen über weitere vokabulare müssen verifiziert oder falsifiziert werden / diskussion: / 3 constraints werden zufällig nie verletzt / basis für future work / motivation, dass man constraint languages entwicken muss die complexe constraints abbilden / datenqualität ist generell sehr hoch / als hypothese postulieren}
+
+-----
+
+\begin{hyp}
+
+\end{hyp}
+
+We hypothesise
+
+-----
+
+As the number of evaluated triples differs between the vocabularies, the stated total values are normalized percentage values.
+
+-----
+
+Disco is a new vocabulary which is published in 2015
+
+for this vocabulary the published data is not consistent with the vocabulary
+
+-----
+
+We have to be careful making general statements for all vocabularies as we evaluate only 3 vocabularies
+
+-----
+
+future work:
+To make general statements for all vocabularies, we will evaluate data sets of more vocabularies
+
+-----
 
@@
 
+-----
+
+\begin{hyp}
+More than the half of the vocabulary constraints are associated with the severity level error and
+more than 3/4 of the simple constraints are only informational constraints. 
+\end{hyp}
+Table \ref{tab:evaluation-complexity-severity} shows the relation between the complexity and the severity level of all 213 constraints.
+
+\begin{table}[H]
+		\scriptsize
+    \begin{center}
+    \begin{tabular}{@{}lcccc@{}}
+%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
+%    \\  \cmidrule{2-7}
+    \\       \textbf{}
+           & \textbf{\emph{vocabulary}}
+           & \textbf{\emph{simple}}
+					 & \textbf{\emph{complex}}
+    \\ \midrule
+		%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
+		%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
+		%\hline
+		\textbf{\emph{info}} & 38.7 \% & \textbf{76.2 \%} & \textbf{42.3 \%} \\
+		\textbf{\emph{warning}} & 6.7 \% & 7.1 \% & 13.5 \% \\
+		\textbf{\emph{error}} & \textbf{54.6 \%} & 16.7 \% & \textbf{44.2 \%} \\
+    \bottomrule
+    \end{tabular}
+    %\\ \emph{C (constraints), CT (constraint types)}
+    \caption{Complexity vs. Severity of Constraints}
+		\label{tab:evaluation-complexity-severity}
+    \end{center}
+\end{table}
+
 \section{Related Work}

### 2015-04-29 paper/paper7/paper7.tex
feedback
evaluation

@@
 
-In this paper, we formulate 213 constraints of 53 different types on four different vocabularies (Disco, QB, SKOS, PHDD) and classify them according to the complexity level of their type and their severity level.
-For 114 of these constraints, we evaluate the data quality of 15,694 datasets (4,26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.
+In this paper, we formulate 246 constraints of 53 different types on six different vocabularies (Disco, QB, SKOS, PHDD, DCAT, XKOS) and classify them according to the complexity level of their type and their severity level.
+For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4,26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.
 
@@
 
-\begin{enumerate}
-	\item First, we assigned each constraint type to exactly one of the disjoint sets of constraint types 
-in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$).
-  \item Second, several SBE domain experts of the vocabularies \emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{XKOS}, and \emph{PHDD} evaluated the correctness (i.e., the gold standard) of all $\mathcal{CT}_{C}$ and $\mathcal{CT}_{T}$ constraints and therefore the generic applicability of the developed classification system of constraint types and constraints.
-%i.e., the gold standard, has been proved by multiple SBE domain experts.
-  \item Third, we exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets by means of both $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
-\end{enumerate}
+	%\item First, we assigned each constraint type to exactly one of the disjoint sets of constraint types 
+%in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$).
+In close collaboration with several \emph{SBE} domain experts, we defined 246 constraint 
+of 53 different types on six vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classifies them according to the complexity level of their type and their severity level.
+For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4,26 billion triples) of \emph{SBE} research data on three vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
+These vocabularies are the central and most representative ones within the \emph{SBE} community. 
+We distinct two classes of vocabularies: 
+(1) established vocabularies which are widely adopted and accepted and 
+(2) newly developed vocabularies which are either recently published or are still in the publication process.
+It is likely that such a vocabulary is still subject of constant change, that published data may not be consistent with its current version,
+and that early adopters did not properly understand its formal specification.
+We investigate the quality of data conforming to the established vocabularies \emph{QB} and \emph{SKOS} and to the newly developed vocabulary \emph{Disco} which will be published in 2015.
+
+We evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets by means of both $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
+
 We validated 
@@
 
+Based on this evaluation we formulate hypotheses.
+Nevertheless, we have to be careful making general statements for all vocabularies 
+as these hypotheses still have to be verified or falsified in terms of future work 
+by evaluating the quality of data represented by additional established and newly developed vocabularies.
+
 \subsection{Evaluation Results and Discussion}
 
-The majority (48 $\equiv$ 58.5\%) of the overall 82 $\mathcal{CT}$ constraint types are $\mathcal{CT}_{B}$ whose constraints can therefore be derived from vocabularies without any effort.
-Among $\mathcal{CT}_{B}$, two-thirds (34 $\equiv$ 70.8\%) are $\mathcal{C}_B ^{\mathcal{R}}$, i.e., constraint types for which reasoning may be performed prior to validation, and one third (14 $\equiv$ 29.2\%) are $\overline{\mathcal{C}_B ^{\mathcal{R}}}$, i.e., constraint types for which reasoning does not make any sense.
-A quarter (20 $\equiv$ 24.4\%) of all constraint types are $\mathcal{CT}_{S}$ and a sixth (14 $\equiv$ 17.1\%) are $\mathcal{CT}_{C}$.
-
-\begin{table}[H]
-		\scriptsize
-    \begin{center}
-    \begin{tabular}{@{}lcccc@{}}
-%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
-%    \\  \cmidrule{2-7}
-    \\       \textbf{Criteria}
-           & \textbf{\emph{Disco}}
-           & \textbf{\emph{QB}}
-					 & \textbf{\emph{SKOS}}
-					 & \textbf{Total}
-    \\ \midrule
-		%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
-		%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
+%DCAT: 11 constraints defined
+%PHDD: 12
+%XKOS: 10
+
+%The majority (48 $\equiv$ 58.5\%) of the overall 82 $\mathcal{CT}$ constraint types are $\mathcal{CT}_{B}$ whose constraints can therefore be derived from vocabularies without any effort.
+%Among $\mathcal{CT}_{B}$, two-thirds (34 $\equiv$ 70.8\%) are $\mathcal{C}_B ^{\mathcal{R}}$, i.e., constraint types for which reasoning may be performed prior to validation, and one third (14 $\equiv$ 29.2\%) are $\overline{\mathcal{C}_B ^{\mathcal{R}}}$, i.e., constraint types for which reasoning does not make any sense.
+%A quarter (20 $\equiv$ 24.4\%) of all constraint types are $\mathcal{CT}_{S}$ and a sixth (14 $\equiv$ 17.1\%) are $\mathcal{CT}_{C}$.
+%
+%\begin{table}[H]
+		%\scriptsize
+    %\begin{center}
+    %\begin{tabular}{@{}lcccc@{}}
+%%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
+%%    \\  \cmidrule{2-7}
+    %\\       \textbf{Criteria}
+           %& \textbf{\emph{Disco}}
+           %& \textbf{\emph{QB}}
+					 %& \textbf{\emph{SKOS}}
+					 %& \textbf{Total}
+    %\\ \midrule
+		%%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
+		%%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
+		%%\hline
+		%\emph{CT} & 52 & 20 & 15 & 53 \\
 		%\hline
-		\emph{CT} & 52 & 20 & 15 & 53 \\
-		\hline
-		$\mathcal{CT}_{C}$ & 9 (17.3\%) & 2 (10\%) & 2 (13.3\%) & 9 (17\%) \\
-		$\mathcal{CT}_{S}$ & 16 (30.8\%) & 3 (15\%) & 4 (26,7\%) & 16 (30.2\%) \\
-		$\mathcal{CT}_{B}$ & 27 (\textbf{51.9\%}) & 15 (\textbf{75\%}) & 9 (\textbf{60\%}) & 28 (\textbf{52.8\%}) \\
-		\hline
-		$\mathcal{C}_B ^{\mathcal{R}}$ & 18 (34.6\%) & 9 (45\%) & 4 (26.7\%) & 19 (35.9\%) \\
-		$\overline{\mathcal{C}_B ^{\mathcal{R}}}$ & 9 (17.3\%) & 6 (30\%) & 5 (33.3\%) & 9 (17\%) \\
-    \bottomrule
-    \end{tabular}
-    %\\ \emph{C (constraints), CT (constraint types)}
-    \caption{Evaluation - Constraint Types}
-		\label{tab:evaluation-constraint-types}
-    \end{center}
-\end{table}
+		%$\mathcal{CT}_{C}$ & 9 (17.3\%) & 2 (10\%) & 2 (13.3\%) & 9 (17\%) \\
+		%$\mathcal{CT}_{S}$ & 16 (30.8\%) & 3 (15\%) & 4 (26,7\%) & 16 (30.2\%) \\
+		%$\mathcal{CT}_{B}$ & 27 (\textbf{51.9\%}) & 15 (\textbf{75\%}) & 9 (\textbf{60\%}) & 28 (\textbf{52.8\%}) \\
+		%\hline
+		%$\mathcal{C}_B ^{\mathcal{R}}$ & 18 (34.6\%) & 9 (45\%) & 4 (26.7\%) & 19 (35.9\%) \\
+		%$\overline{\mathcal{C}_B ^{\mathcal{R}}}$ & 9 (17.3\%) & 6 (30\%) & 5 (33.3\%) & 9 (17\%) \\
+    %\bottomrule
+    %\end{tabular}
+    %%\\ \emph{C (constraints), CT (constraint types)}
+    %\caption{Evaluation - Constraint Types}
+		%\label{tab:evaluation-constraint-types}
+    %\end{center}
+%\end{table}
 
 %Table \ref{tab:evaluation-constraint-types} displays the evaluation of the metadata quality on real world data sets regarding constraint types.
-We defined constraints of 53 distinct $\mathcal{CT}$ constraint types (see table \ref{tab:evaluation-constraint-types}).
-More than the half of them are $\mathcal{CT}_{B}$, more than a third $\mathcal{C}_B ^{\mathcal{R}}$, nearly a third $\mathcal{CT}_{S}$, and only a sixth $\mathcal{CT}_{C}$ constraint types.
-For \emph{Disco}, \emph{QB}, and \emph{SKOS}, more than 50\% of the instantiated constraint types are $\mathcal{CT}_{B}$ constraint types 
-(for \emph{QB} even three quarters).
-\emph{Existential quantifications} (\emph{R-86}, 32.4\%, \emph{Disco}), \emph{data model consistency} (31.4\%, \emph{QB}), and \emph{structure} (28.6\%, \emph{SKOS}) are the constraint types the most constraints are instantiated from.
-
-\begin{table}[H]
-		\scriptsize
-    \begin{center}
-    \begin{tabular}{@{}lcccc@{}}
-%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
-%    \\  \cmidrule{2-7}
-    \\       \textbf{Criteria}
-           & \textbf{\emph{Disco}}
-           & \textbf{\emph{QB}}
-					 & \textbf{\emph{SKOS}}
-					 & \textbf{Total}
-    \\ \midrule
-		%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
-		%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
-		%\hline
-		\emph{C} & 143 (67.1\%) & 35 (16.4\%) & 35 (16.4\%) & 213 \\
-		\hline
-		\emph{C (}$\mathcal{CT}_{C}$\emph{)} & 37 (25.9\%) & 13 (37.1\%) & 13 (\textbf{37.1\%}) & 63 (29.6\%) \\
-		\emph{C (}$\mathcal{CT}_{S}$\emph{)} & 28 (19.6\%) & 3 (8.6\%) & 12 (\textbf{34.3\%}) & 43 (20.2\%) \\
-		\emph{C (}$\mathcal{CT}_{B}$\emph{)} & 78 (\textbf{54.6\%}) & 19 (\textbf{54.3\%}) & 10 (\textbf{28.6\%}) & 107 (\textbf{50.2\%}) \\
-		%\hline
-		%\emph{C (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 67 (46.9\%) & 13 (37.1\%) & 4 (11.4\%) & 84 (39.4\%) \\
-		%\emph{C (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 11 (7.7\%) & 6 (17.1\%) & 6 (17.1\%) & 23 (10.8\%) \\
-		\hline
-		\emph{C ($\mathcal{SL}_{0}$)} & 75 (\textbf{52.5\%}) & 4 (11.4\%) & 21 (\textbf{60\%}) & 100 (\textbf{46.9\%}) \\
-		\emph{C ($\mathcal{SL}_{1}$)} & 10 (7\%) & 3 (8.6\%) & 5 (14.3\%) & 18 (8.5\%) \\
-		\emph{C ($\mathcal{SL}_{2}$)} & 58 (40.6\%) & 28 (\textbf{80\%}) & 9 (25.7\%) & 95 (\textbf{44.6\%}) \\
-    \bottomrule
-    \end{tabular}
-    %\\ \emph{C (constraints), CT (constraint types)}
-    \caption{Evaluation - Constraints}
-		\label{tab:evaluation-constraints}
-    \end{center}
-\end{table}
-
-Half of the overall 213 $\mathcal{CT}$ constraints are $\mathcal{CT}_{B}$ constraints (almost 40\% $\mathcal{C}_B ^{\mathcal{R}}$) (see table \ref{tab:evaluation-constraints}).
-This is not surprising as more than the half of the instantiated constraints types are $\mathcal{CT}_{B}$ constraint types.
-More than 50\% of the \emph{Disco} and \emph{QB} constraints are $\mathcal{CT}_{B}$ constraints.
-The \emph{SKOS} constraints, on the other side, are equally assigned to the three disjoint constraint type sets. 
-\emph{SBE} domain experts associated almost the half of the constraints with the severity levels $\mathcal{SL}_{0}$ (\emph{informational}) (47\%) and $\mathcal{SL}_{2}$ (\emph{error}) (45\%);
-only 8.5\% are $\mathcal{SL}_{1}$ (\emph{warning}) constraints.
-The violation of 80\% of the \emph{QB} constraints is very serious ($\mathcal{SL}_{2}$).
-More than 50\% of the \emph{Disco} and \emph{SKOS} constraints, however, are assigned to the weakest default severity level ($\mathcal{SL}_{0}$).
+Table \ref{tab:evaluation-constraint-violations} shows the results of the evaluation, more specifically the constraints and the constraint violations, which are caused by these constraints, in percent.
+The constraints and their resulting constraint violations are grouped by vocabulary, complexity level of their type, and severity level.
+The number of evaluated triples and data sets differs between the vocabularies
+as we evaluated 3.8 billion QB, 480 million SKOS, and 10 million Disco triples.
+In order to get suitable statements for all vocabularies,  
+we normalize the total values which apply for all vocabularies
+by building the arithmetic mean over the individual vocabularies' percentage values.
 
@@
 \end{table}
+
+More than the half of them are $\mathcal{CT}_{B}$, nearly a third $\mathcal{CT}_{S}$, and only a sixth $\mathcal{CT}_{C}$ constraint types.
+For \emph{Disco}, \emph{QB}, and \emph{SKOS}, more than 50\% of the instantiated constraint types are $\mathcal{CT}_{B}$ constraint types 
+(for \emph{QB} even three quarters).
+\emph{Existential quantifications} (\emph{R-86}, 32.4\%, \emph{Disco}), \emph{data model consistency} (31.4\%, \emph{QB}), and \emph{structure} (28.6\%, \emph{SKOS}) are the constraint types the most constraints are instantiated from.
+Half of the overall 213 $\mathcal{CT}$ constraints are $\mathcal{CT}_{B}$ constraints (almost 40\% $\mathcal{C}_B ^{\mathcal{R}}$).
+This is not surprising as more than the half of the instantiated constraints types are $\mathcal{CT}_{B}$ constraint types.
+More than 50\% of the \emph{Disco} and \emph{QB} constraints are $\mathcal{CT}_{B}$ constraints.
+The \emph{SKOS} constraints, on the other side, are equally assigned to the three disjoint constraint type sets. 
+More than 80\% of the overall approx. 55 million constraint violations are caused by \emph{QB} constraints (see table \ref{tab:evaluation-constraint-violations}).
+The majority (86.7\%) of the constraint violations are caused by $\mathcal{CT}_{C}$ constraints and only 9\% by $\mathcal{CT}_{S}$ constraints.
+The fact that only 4\% of all constraint violations result from $\mathcal{CT}_{B}$ constraints, 
+even though, more than 50\% of all constraints are $\mathcal{CT}_{B}$ constraints,
+is an indicator that data producers achieve good data quality with respect to the constraints extracted by vocabularies.
+Two-thirds of the constraint violations, thrown for \emph{Disco} data sets, result from $\mathcal{CT}_{B}$ constraints,
+almost only $\mathcal{CT}_{C}$ constraints raised constraint violations for \emph{QB} data sets, and 
+nearly 80\% of the \emph{SKOS} constraint violations are caused by $\mathcal{CT}_{S}$ constraints.
+\begin{hyp}
+A significant amount of 47\% of the violations refer to complex constraints that are not easily expressible in existing languages which confirms the necessity to provide suitable constraint languages.
+\end{hyp} 
+These days, vocabulary and simple constraints can be easily, concisely, and intuitively expressed by either modeling languages (e.g., RDF, RDFS, OWL 2) or constraint languages (e.g., ShEx, ReSh, and SPIN).
+This is not the case, however, for complex constraints which still have to be expressed by plain SPARQL. 
+There is a huge motivation to extend existing constraint languages or to develop new constraint languages which enable to express complex constraints
+As a consequence, being able to express complex constraints more easily, concisely, and intuitively leads to significant improvements in data quality.
+
+Data quality is not bad since only a small amount of the constraint violations are caused by error constraints
+\emph{SBE} domain experts associated almost the half of the constraints with the severity levels $\mathcal{SL}_{0}$ (\emph{informational}) (47\%) and $\mathcal{SL}_{2}$ (\emph{error}) (45\%);
+only 8.5\% are $\mathcal{SL}_{1}$ (\emph{warning}) constraints.
+The violation of 80\% of the \emph{QB} constraints is very serious ($\mathcal{SL}_{2}$).
+More than 50\% of the \emph{Disco} and \emph{SKOS} constraints, however, are assigned to the weakest default severity level ($\mathcal{SL}_{0}$).
+For Disco, 1/6 of the constraint violations are serious.
+Although, only 8.5\% of all constraints are $\mathcal{SL}_{1}$ constraints,
+9 0f 10 constraint violations are caused by constraints associated with the default severity level $\mathcal{SL}_{1}$.
+More than 50\% of all constraint violations thrown for \emph{Disco} data sets are not seen to be that significant ($\mathcal{SL}_{0}$).
+Almost all constraint violations raised by \emph{QB} constraints and 59\% of the constraint violations caused by \emph{SKOS} constraints are classified as warnings ($\mathcal{SL}_{1}$).  
+As this evaluation serves as indication for \emph{good} or \emph{bad} (meta)data quality, 
+we conclude that
+the metadata quality of all evaluated \emph{Disco} data sets is \emph{good} and that the metadata quality of all evaluated \emph{QB} and \emph{SKOS} data sets is \emph{satisfactory}.
+\begin{hyp}
+In general, data quality is very high.
+The quality of data represented by established vocabularies is good,
+as serious constraint violations rarely appear.
+The quality of data represented by newly developed vocabularies, however, is worse,
+as serious constraint violations occur partially.
+For well-established vocabularies, the explicitly defined constraints are almost completely satisfied which demonstrates that constraint formulation in general works.
+\end{hyp}
+
+\begin{hyp}
+The percentage of severe constraint violations is very low, compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
+\end{hyp}
+
+%For the vocabularies \emph{Disco}, \emph{QB}, and \emph{SKOS}, we defined 213 constraints of 53 constraint types .
+
+%\begin{table}[H]
+		%\scriptsize
+    %\begin{center}
+    %\begin{tabular}{@{}lcccc@{}}
+%%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
+%%    \\  \cmidrule{2-7}
+    %\\       \textbf{Criteria}
+           %& \textbf{\emph{Disco}}
+           %& \textbf{\emph{QB}}
+					 %& \textbf{\emph{SKOS}}
+					 %& \textbf{Total}
+    %\\ \midrule
+		%%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
+		%%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
+		%%\hline
+		%\emph{C} & 143 (67.1\%) & 35 (16.4\%) & 35 (16.4\%) & 213 \\
+		%\hline
+		%\emph{C (}$\mathcal{CT}_{C}$\emph{)} & 37 (25.9\%) & 13 (37.1\%) & 13 (\textbf{37.1\%}) & 63 (29.6\%) \\
+		%\emph{C (}$\mathcal{CT}_{S}$\emph{)} & 28 (19.6\%) & 3 (8.6\%) & 12 (\textbf{34.3\%}) & 43 (20.2\%) \\
+		%\emph{C (}$\mathcal{CT}_{B}$\emph{)} & 78 (\textbf{54.6\%}) & 19 (\textbf{54.3\%}) & 10 (\textbf{28.6\%}) & 107 (\textbf{50.2\%}) \\
+		%%\hline
+		%%\emph{C (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 67 (46.9\%) & 13 (37.1\%) & 4 (11.4\%) & 84 (39.4\%) \\
+		%%\emph{C (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 11 (7.7\%) & 6 (17.1\%) & 6 (17.1\%) & 23 (10.8\%) \\
+		%\hline
+		%\emph{C ($\mathcal{SL}_{0}$)} & 75 (\textbf{52.5\%}) & 4 (11.4\%) & 21 (\textbf{60\%}) & 100 (\textbf{46.9\%}) \\
+		%\emph{C ($\mathcal{SL}_{1}$)} & 10 (7\%) & 3 (8.6\%) & 5 (14.3\%) & 18 (8.5\%) \\
+		%\emph{C ($\mathcal{SL}_{2}$)} & 58 (40.6\%) & 28 (\textbf{80\%}) & 9 (25.7\%) & 95 (\textbf{44.6\%}) \\
+    %\bottomrule
+    %\end{tabular}
+    %%\\ \emph{C (constraints), CT (constraint types)}
+    %\caption{Evaluation - Constraints}
+		%\label{tab:evaluation-constraints}
+    %\end{center}
+%\end{table}
 
@@
 \tb{difference between 0\% and 78.6\%}
-\tb{basic constraints sind bei etablierten vokabularen publitierte datensätze werden eingehalten hohe datenqualität / schwerwiegende constraintverletzungen treten kaum auf / schwere constraints sind in idesen vielen daten nicht auf / disco ist in beiden fällen anders / erheblichen anteil von schwersten constraint verletzungen / disco neues vokabular das noch daten gelten noch einenm draft von disco oder hat disco nicht verstanden schnlechtere daten als entabliete vokabulare / es ist sinnvoll sprachen zu entwickeln komplexere constraints auszudrücken / simple und vocabulary können heute schon sehr gut beschrieben werden / wir wünschen und dass es komplexere constraint languages gibt mit denen complex constraints besser abgebildet werden können / deulticherer verbesserung in der datenualitt wenn wir diese constraint languages hätten / gibt es weitere hypothesen?
-- alles was in der tabelle auffällig ist / normaliisert über die datensatzgröße / 3 sehr wichtige und repräsentative vokabulare im sbe bereich / interessanate constraints mit ausreißern / hypothesen über weitere vokabulare müssen verifiziert oder falsifiziert werden / diskussion: / 3 constraints werden zufällig nie verletzt / basis für future work / motivation, dass man constraint languages entwicken muss die complexe constraints abbilden / datenqualität ist generell sehr hoch / als hypothese postulieren}
-
------
-
-\begin{hyp}
-
-\end{hyp}
-
-We hypothesise
-
------
-
-As the number of evaluated triples differs between the vocabularies, the stated total values are normalized percentage values.
-
------
-
-Disco is a new vocabulary which is published in 2015
-
-for this vocabulary the published data is not consistent with the vocabulary
-
------
-
-We have to be careful making general statements for all vocabularies as we evaluate only 3 vocabularies
-
------
-
-future work:
-To make general statements for all vocabularies, we will evaluate data sets of more vocabularies
-
------
-
-More than 80\% of the overall approx. 55 million constraint violations are caused by \emph{QB} constraints (see table \ref{tab:evaluation-constraint-violations}).
-The majority (86.7\%) of the constraint violations are caused by $\mathcal{CT}_{C}$ constraints and only 9\% by $\mathcal{CT}_{S}$ constraints.
-The fact that only 4\% of all constraint violations result from $\mathcal{CT}_{B}$ constraints, 
-even though, more than 50\% of all constraints are $\mathcal{CT}_{B}$ constraints,
-is an indicator that data producers achieve good data quality with respect to the constraints extracted by vocabularies.
-Two-thirds of the constraint violations, thrown for \emph{Disco} data sets, result from $\mathcal{CT}_{B}$ constraints,
-almost only $\mathcal{CT}_{C}$ constraints raised constraint violations for \emph{QB} data sets, and 
-nearly 80\% of the \emph{SKOS} constraint violations are caused by $\mathcal{CT}_{S}$ constraints.
-Although, only 8.5\% of all constraints are $\mathcal{SL}_{1}$ constraints,
-9 0f 10 constraint violations are caused by constraints associated with the default severity level $\mathcal{SL}_{1}$.
-More than 50\% of all constraint violations thrown for \emph{Disco} data sets are not seen to be that significant ($\mathcal{SL}_{0}$).
-Almost all constraint violations raised by \emph{QB} constraints and 59\% of the constraint violations caused by \emph{SKOS} constraints are classified as warnings ($\mathcal{SL}_{1}$).  
-As this evaluation serves as indication for \emph{good} or \emph{bad} (meta)data quality, 
-we conclude that
-the metadata quality of all evaluated \emph{Disco} data sets is \emph{good} and that the metadata quality of all evaluated \emph{QB} and \emph{SKOS} data sets is \emph{satisfactory}.
+
+\tb{it has to be ensured that constraints within a particular set are not violated randomly  
+in case there are only a few constraints within a set}
+
+\tb{established vocabularies meet vocabulary constraints / data sets represented by established vocabularies meet vocabulary constraints which indicates good data quality}
+
+\tb{QB data sets contain data and metadata and therefore there are the differences between constraint violations}
+
 %The constraints responsible for the largest amounts of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916; \emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102; \emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903; \emph{SKOS}).
 
------
-
-\begin{hyp}
-More than the half of the vocabulary constraints are associated with the severity level error and
-more than 3/4 of the simple constraints are only informational constraints. 
-\end{hyp}
 Table \ref{tab:evaluation-complexity-severity} shows the relation between the complexity and the severity level of all 213 constraints.
@@
 
+\begin{hyp}
+More than the half of the vocabulary constraints are associated with the severity level error and
+more than 3/4 of the simple constraints are only informational constraints. 
+\end{hyp}
+
 \section{Related Work}

### 2015-04-29 Bosch/paper 2/paper 2.tex
Language Improvement in Paper 2

--- 2015-04-22 paper/paper 2/paper 2.tex
@@
 %
-\author{Thomas Bosch\inst{1} \and Erman Acar\inst{2} \and Kai Eckert\inst{2}}
+\author{Thomas Bosch\inst{1} \and Erman Acar\inst{2} \and Kai Eckert\inst{3}}
 %
@@
 University of Mannheim, Germany \\
-\email{\{erman,kai\}@informatik.uni-mannheim.de} 
+\email{erman@informatik.uni-mannheim.de} 
+\and
+Stuttgart Media University, Germany \\
+\email{eckert@hdm-stuttgart.de} 
 }
@@
 More and more domains adopt Linked Data principles
-and seek for ways to ensure data quality by validating RDF data according to predefined constraints, 
-particularly as many communities are used to have this functionality in the XML world.
-XML Schema is the standard language to formulate constraints on and to validate XML documents.
-For RDF, however, there are several languages which can be used to express constraints on RDF data - but no standard one meeting the majority of RDF validation use cases.
-We identified requirements to formulate constraints and to validate RDF data and mapped each requirement to a constraint type.
-The majority of these constraint types can be expressed in description logics providing their logical underpinning.
+and seek for ways to ensure data quality by validating RDF data according to predefined constraints.  In particular, as many communities are used to have this functionality in the XML world.
+XML Schema is the standard language to formulate constraints to validate XML documents.
+For RDF, however, there are several languages which can be used to express constraints on RDF data - but not a stand-alone standard one meeting the majority of RDF validation use cases. 
+% Truth be told, we do may two things, blabla on and to blabla, however for the flow of the text we dont need to overkill the text.
+In abstract and introduction, we just give general idea so at such points we better focus on flow.
+We identified requirements to formulate constraints for  validating RDF data and mapped each requirement to a constraint type.
+The majority of these constraint types can be expressed in description logics providing which provides logical underpinning.
 
@@
 
-The \textbf{contributions} of this paper are:
+The contributions of this paper are:
 (1) we provide a basic terminology and classification system for RDF constraints,
-(2) we developed a vocabulary to describe constraints of any constraint type generically and specified its underlying semantics,
-(3) we show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful, and
-(4) we explain how to overcome the necessity to implement the validation of each constraint type for diverse constraint languages.
+(2) we develop a vocabulary to describe constraints of any constraint type generically and specified its underlying semantics,
+(3) we show how to transform constraints which are expressed by any constraint language, into generically expressed constraints and discuss why these transformations are useful, and
+(4) we explain how to overcome the problems to implement the validation of each constraint type for diverse constraint languages.
 
@@
 For libraries, the common description of resources are key business and they have a long tradition in developing and using interoperable data formats.
-While they embrace the openness of Linked Data and the data modeling principles provided by RDF, the data is still mostly represented in XML and this is unlikely to change soon.
+While they embrace the openness of Linked Data and the data modeling principles provided by RDF, the data is still mostly represented in XML and this is unlikely to change any time soon.
 Among the reasons for the success of XML is the possibility to formulate fine-grained constraints to be met by the data and to validate the data according to these constraints using powerful systems like DTDs, XML Schemas, RELAX NG, or Schematron.
@@
 
-As there is not the one language meeting the majority of requirements to formulate constraints and to validate RDF data
-and as there are more than 10 candidate languages with different syntaxes and semantics, 
+As there is no do-it-all language meeting the majority of requirements to formulate constraints, and to validate RDF data,
+
 %which can be used to express constraints and to validate RDF data, 
@@
 language selection heavily depends on the individual use case.
-The five most promising languages on being the standard constraint language are
+Loosely speaking, there are more than 10 candidate languages with different syntaxes and semantics, and we will focus on five which, in our opinion, are the most promising languages on being the standard constraint languages.
+Those are
 \emph{Description Set Profiles (DSP)},
@@
 %min car more powerful than req. propery
-The idea behind this paper is to achieve complete RDF validation requirements coverage by representing any constraint type (each of them corresponding to a requirement to formulate constraints and to validate RDF data) in a generic way using a lightweight vocabulary consisting of only a few terms (see section \ref{sec:vocabulary}).
-
-\emph{Cardinality restrictions}, e.g., can be expressed either generically (\textbf{\emph{generic constraints}}) by \emph{description logics (DL)} 
+The idea behind this paper is to achieve complete RDF validation requirements coverage by representing any constraint type (each of them corresponding to a requirement to formulate constraints and to validate RDF data) in a generic way using a lightweight vocabulary, say,  consisting of only a few terms (see section \ref{sec:vocabulary}).
+
+\emph{Cardinality restrictions} can be expressed either generically (\textbf{\emph{generic constraints}}) by \emph{description logics (DL)} 
 %and extensions  
@@
 For that reason, we map constraint types to \emph{DL} statements.
+
 With \emph{minimum qualified cardinality restrictions} (\emph{R-75/81})\footnote{Requirements/constraint types are uniquely identified by alphanumeric technical identifiers like \emph{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}}, researchers from the library domain may restrict
@@
 
-As each \emph{publication} must have at least one \emph{author} which must be a \emph{person} 
-and as the book \emph{The-Lord-Of-The-Rings} is a \emph{publication} (\ms{rdf:type(The-Lord-Of-The-Rings, Publication)}), 
+As every \emph{publication} must have at least one \emph{author} which must be a \emph{person}, 
+and since the book \emph{The-Lord-Of-The-Rings} is a \emph{publication} \\(\ms{rdf:type(The-Lord-Of-The-Rings, Publication)}), 
 it must have at least one \emph{author} relationship to a \emph{person}.
@@
 \emph{The-Lord-Of-The-Rings} does not have any \emph{author} relationship, or (2) if 
-it has an \emph{author} which is not a \emph{person}
+it has an \emph{author} which is not a \emph{person} \\
 (\ms{author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Hobbit)}), 
@@
 As there is no standard way to formulate constraints, 
-semantically equivalent \emph{cardinality restrictions} may be represented by multiple constraint languages having different syntax and semantics.
-This causes confusion and weakens the common understanding between several parties about the semantics of particular constraints and therefore how to ensure high data quality. 
-Thus, when choosing constraint language \ms{$\alpha$} to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a semantically equivalent constraint formulated by any other constraint language \ms{$\beta$} (see section \ref{sec:transformations}).
+semantically equivalent \emph{cardinality restrictions} may be represented by multiple constraint languages that have different syntax and semantics.
+This causes confusion and weakens the common understanding between several parties about the semantics of particular constraints. Also, it raises  questions on how to ensure high data quality. 
+Therefore, when choosing a constraint language, say \ms{$\alpha$}, to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a semantically equivalent constraint in another other constraint language \ms{$\beta$} (see section \ref{sec:transformations}).
 This is important in order to enhance the interoperability of constraint languages and to resolve misunderstandings and ambiguities in the communication of RDF data producers and consumers, 
-as constraint transformations avoid the necessity to understand several constraint languages.
-
-We provide a validation environment (available at \url{http://purl.org/net/rdfval-demo}) which enables to validate RDF data according to constraints expressed by diverse  constraint languages.
-As a second step, the \emph{RDF Validator} is extended by validating RDF data conforming to constraints of any constraint type represented by any constraint language and 
-to perform validation on semantically equivalent \emph{specific constraints}, expressed by different constraint languages, in exactly the same way, 
+since constraint transformations avoid the necessity to understand several constraint languages.
+
+We provide a validation environment \footnote{Available \url{http://purl.org/net/rdfval-demo}} which enables to validate RDF data according to constraints expressed by diverse  constraint languages.
+As a second step, the \emph{RDF Validator} is extended by validating RDF data conforming to constraints of any constraint type represented by any constraint language,  
+to perform validation on semantically equivalent \emph{specific constraints}, expressed by different constraint languages 
 i.e., validation is independent from the used constraint language (see section \ref{sec:validation}). 
@@
 
-In order to develop a vocabulary to describe constraints of any constraint type in a generic way, prerequisites are to specify the vocabulary's underlying semantics, to define the basic terminology for the formulation of constraints, and to classify them.
-The underlying \textbf{\emph{semantics}} for RDF validation are \emph{UNA} and \emph{CWA}.
+In order to develop a vocabulary to describe constraints of any constraint type in a generic way, what we need to do is to specify the vocabulary's underlying semantics and define the basic terminology for the formulation of constraints.
+The underlying \emph{semantics} for RDF validation are \emph{UNA} and \emph{CWA}.
 RDF validation requires that different names represent different objects ({\em unique name assumption (UNA)}), whereas,
 \emph{OWL 2} is based on the {\em non-unique name assumption (nUNA)}.
+\tb{ Erman: One usual problem is that, a constraint that says book should have a single author in OWA, does not mean that it has a unique author.
+In every model  (an interpretation that makes a set of DL knowledge base true), it can be the case that a book has a single author, however, bringing all those together, this author is not unique.
+In some models it is Ali, in others its Veli.
+And since in every model there is only one, DL sentences are satisfied.
+But this does not correspond to the intended constraint which is usual in CWA way.}
 A data property is \emph{functional} (\emph{R-65}) if for each individual \emph{x}, there can be at most one distinct literal \emph{y} such that \emph{x} is connected by the data property to \emph{y}.
+(See \cite{resource} for this terminology.)
 When assuming \emph{UNA}, the functional property {\em title} (\ms{funct (title)}) causes a clash
@@
 
-Reasoning in \emph{OWL 2} is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose to represent knowledge on the World Wide Web.
+Reasoning in \emph{OWL 2} is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true . 
+%which fits its primary design purpose to represent knowledge on the World Wide Web. 
 %Most of the constraint languages except OWL, have a major shortcoming of redundancy.
@@
 On the other hand, RDF validation scenarios require the {\em closed-world assumption (CWA)}, i.e., a statement is inferred to be false if it cannot be proved to be true.
-Hence, classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals which yields in return to a constraint violation.
+Classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals which yields a constraint violation.
 This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past.  
-Thus, in case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics than for RDF validation in general. 
+In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general. 
 \tb{feedback from Erman: the major problem is semantics.
@@
 Open World is also a part of this.
-/ Thomas: I think your issue is tackled now?}
-\tb{Erman thinks formal generic semantics should be defined / Thomas: what do you mean by this? / I inserted these 2 paragraphs about RDF validation semantics. Are your concerns resolved now?}
+/ Thomas: I think your issue is tackled now?
+No.}
+\tb{Erman: The problem is OWL doesn't work CWA way, just because we want it.
+If a constraint is represented (recognized) by two different languages, that means, whenever it is violated in one language it is violated in other.
+Since the time is tight and we cannot provide formal semantics for it; nor formally prove those statements.
+We  can go on with whats at hand.
+}
+\tb{Erman thinks formal generic semantics should be defined / Thomas: what do you mean by this? / I inserted these 2 paragraphs about RDF validation semantics. Are your concerns resolved now? }
 
@@
 
-As there are already five promising constraint languages, our purpose is not to invent a new constraint language.
-We rather developed a very simple lightweight vocabulary (only three classes, three object properties, and three data properties) which is universal enough to describe constraints of any constraint type expressible by any constraint language (see the conceptual model in figure \ref{fig:RDF-CV-conceptual-model}).
+As there are already five promising constraint languages and our purpose is not to put a new constraint language, we rather developed a very simple lightweight vocabulary (only three classes, three object properties, and three data properties) which is universal enough to describe constraints of any constraint type expressible by any constraint language (see the conceptual model in figure \ref{fig:RDF-CV-conceptual-model}).
 We call this vocabulary the \textbf{\emph{RDF Constraints Vocabulary (RDF-CV)}}\footnote{Available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.
@@
 The majority of the constraint types can be expressed in \emph{DL}.
-In contrast, there are constraint types which cannot be expressed in \emph{DL}, but are also representable by the \emph{RDF-CV} (see section \ref{sec:evaluation}). 
+In contrast, there are certain constraint types which cannot be expressed in \emph{DL}, but are also expressible by the \emph{RDF-CV} . 
 \textbf{\emph{Complex constraints}} encompass \textbf{\emph{simple constraints}} (atomic constraints) and/or further \emph{complex constraints},
@@
 The \emph{RDF-CV} does not contain any terms standing for \emph{simple} and \emph{complex constraints}, since \emph{context classes} of \emph{simple constraints} are just reused within \emph{complex constraints} (\emph{simple constraints} associated with \emph{context classes} must hold for individuals of these \emph{context classes}).
+\tb{Erman: If you say its expressible in RDF-CV, than you impose that RDF-CV is a language rather than a vocabulary.
+"in different contexts they call it signature which is the same thing".
+Generally, a language uses vocabulary to construct sentences, and the set of those sentences, is the language.} (see section \ref{sec:evaluation})
 As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to describe constraints of all possible constraint types.
@@
     owl:onDatatype xsd:string ; 
-    owl:withRestrictions ([ xsd:pattern "^\d{9}[\d|X]$" ])] .
-\end{ex}\$$
+    owl:withRestrictions ([ xsd:pattern "^\d{9}[\d|X]" ])] .
+\end{ex} 
 The first OWL 2 axiom explicitly declares {\em ISBN} to be a datatype.

### 2015-04-29 paper/paper 3/paper 3.tex
Revert "Language Improvement in Paper 2"
This reverts commit 970632ac38c80aacbc178530c32b0c1e1a48fbad.

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}

\usepackage[utf8]{inputenc}

% URL handling
\usepackage{url}
\urlstyle{same}

% Todos
%\usepackage[colorinlistoftodos]{todonotes}
%\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
%\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}

%\usepackage{makeidx}  % allows for indexgeneration

%\usepackage{amsmath}
\usepackage{amsmath, amssymb}
\usepackage{mathabx}

% monospace within text
\newcommand{\ms}[1]{\texttt{#1}}

% examples
\usepackage{fancyvrb}
\DefineVerbatimEnvironment{ex}{Verbatim}{numbers=left,numbersep=2mm,frame=single,fontsize=\scriptsize}

\usepackage{xspace}
% Einfache und doppelte Anfuehrungszeichen
\newcommand{\qs}{``} 
\newcommand{\qe}{''\xspace} 
\newcommand{\sqs}{`} 
\newcommand{\sqe}{'\xspace}

% checkmark
\usepackage{tikz}
\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}

% Xs
\usepackage{pifont}

% Tabellenabstände kleiner
\setlength{\intextsep}{10pt} % Vertical space above & below [h] floats
\setlength{\textfloatsep}{10pt} % Vertical space below (above) [t] ([b]) floats
% \setlength{\abovecaptionskip}{0pt}
% \setlength{\belowcaptionskip}{0pt}

\usepackage{tabularx}
\newcommand{\hr}{\hline\noalign{\smallskip}} % für die horizontalen linien in tabellen

% Todos
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}

\begin{document}

%
%
\title{Constraint Validation with OWL 2 | Closed World Semantics | With and Without Reasoning}
%
\titlerunning{Constraint Validation with OWL 2}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{XXXXX\inst{1} \and XXXXX\inst{2}}
%
\authorrunning{XXXXX} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\institute{XXXXX\\
\email{XXXXX},\\ 
\and
XXXXX \\
\email{XXXXX} 
}

\maketitle              % typeset the title of the contribution

\begin{abstract}
OWL (and RDFS) semantics (and syntax) can be used to specify constraints.

\keywords{..}
\end{abstract}
%

\section{Introduction}

\section{OWL as Constraint Validation Language}

\subsection{Compact, Human-Readable Syntax}

1 (2) example(s)

\begin{enumerate}
	\item SPARQL
	\item SPIN (Turtle syntax)
	\item OWL 2 (Turtle syntax)
	\item OWL 2 (Manchester Syntax)
\end{enumerate}

\textbf{cardinality restrictions}

for the simple cases the sytax in compact form and manchester are not that different. 
As well as showing that the RDF versions are quite close as well.

In Shex Compact (corrections welcome),

\begin{ex}
<WebServicePersonShape> {
  rdf:type foad:Person ,
  foaf:name xsd:string ,
  foo:email xsd:string ,
  foo:phone xsd:string *
}
\end{ex}

In ShEx RDF
\begin{ex}
<WebServicePersonShape> a rs:ResourceShape ;
     rs:property  [ rs:name                "one name" ;
                    rs:occurs              rs:Exactly-one .  ;
                    rs:propertyDefinition  foaf:name ;
                    rs:valueShape          foaf:Person
                   ],
                   [ rs:name                "one e mail" ;
                    rs:occurs              rs:Exactly-one ;
                    rs:propertyDefinition  foo:email ;
                    rs:valueShape          foaf:Person
                   ] ,
                   [ rs:name                "some number of phone numbers" ;
                    rs:occurs              rs:Zero-or-many ;
                    rs:propertyDefinition  foo:phone ;
                    rs:valueShape          foaf:Person
                   ] ;
\end{ex}

In spin turtle

\begin{ex}
foaf:person a owl:Class;
  spin:constraint [ rdfs:label "one name" ;
                    a spl:Attribute ;
                    spl:predicate foaf:name ;
                    spl:count 1 ] ,
                  [ rdfs:label "one e-mail" ;
                    a spl:Attribute ;
                    spl:predicate foo:email ;
                    spl:count 1 ] ,
                  [ rdfs:label "some number of phone numbers"
                    a spl:Attribute ;
                    spl:predicate foo:phone ;
                    spl:minCount 0 ] .
\end{ex}

--> As given it looks horrible, but with a compact syntax on top

In Closed world owl rdf turtle serialisation

\begin{ex}
foaf:person a owl:Class;
  rdfs:subClassOf [ a       owl:Restriction ;
                    owl:cardinality "1"^^xsd:nonNegativeInteger ;
                    owl:onProperty foaf:name ;
                    rdfs:label "one name"
                  ] ,
                  [ a       owl:Restriction ;
                    owl:cardinality "1"^^xsd:nonNegativeInteger ;
                    owl:onProperty foo:email ;
                    rdfs:label "one email"
                  ] ,
                  [ a       owl:Restriction ;
                    owl:minCardinality "0"^^xsd:nonNegativeInteger ;
                    owl:onProperty foo:phone ;
                    rdfs:label "some number of phone numbers"
                  ] ,
\end{ex}

Some Manchester syntax (again corrections welcome)

\begin{ex}
Class: foaf:person
   foaf:name exactly 1
   foo:email exactly 1
   foo:phone min 0
\end{ex}

which existing technology should be used as guide. 
As well as showing what the technologies in the field can do already.

\textbf{syntactically well-formed email addresses}

\tb{example}

Yes, your specific example can be 
nicely represented in a very compact textual form. But your example only 
talks about cardinality, and there is obviously much more that people 
want to specify when they publish data models. For example you may want 
to say that the values of foo:email are syntactically well-formed email 
addresses. Simple languages quickly reach limits and then need to be 
overloaded with all kinds of escape mechanisms.

RDF is designed to be 
extensible - anyone can add their own classes and properties to 
represent any kind of extra information. Therefore a model that talks 
about other data models should also be represented in RDF, and that's 
where Shapes come into the picture. For certain common shapes (such as 
cardinality) a short-hand syntax could be added, but still the 
underlying semantics need to be more flexible.

\textbf{JSON-LD.}

example:

\begin{ex}
{
     "@context" : "http://w3.org/2014/shapes/context",
     "@id" : "ex:Person",
     "constraint" : {
         "type" : "shapes:Property",
         "property" : "ex:firstName",
         "occurs" : "shapes:Exactly-one",
         "valueType" : "xsd:string"
     }
}

\end{ex}

benefits:

- understandable by anyone who does some coding, without being a "semantic web engineer."

\textbf{Why compact human-readable syntax?}
don't think RDF, don't know RDF, they don't want to know RDF.
They don't think open world or closed world, etc.

Writing validation rules in RDF would be simpler than writing them in SPARQL,
but still much more tedious than having a concise, compact syntax for
expressing them.

\textbf{requirements on compact human-readable syntax.}

- understandable by anyone who does some coding, without being a "semantic web engineer."

- Now the question is: who creates this and how? And do they have to be fully versed in RDF?

\textbf{structure of syntax.}
The structure itself should guide novices to make good RDF-compatible decisions.

\textbf{expressing constraints in OWL enables thinking in RDF. | syntax using the same paradigm and semantics of RDF [important!]}

We need a syntax that is related to RDF, uses the same paradigm and semantics.

I've seen RDF/XML and, to a lesser extent, JSON-LD act as gateways to 
RDF. (I almost wanted to say: gateway drugs.) The down side of that is 
that users tend not to learn to think in terms of key RDF concepts like 
graphs, inferencing, and the meaning of class membership in RDF. So it 
does help that there are known serializations, but those known 
serializations can hide the ways that RDF semantics differ from our 
previous ways of thinking about data. Therefore people tend to create 
perfectly good XML or JSON data that isn't RDF at heart.

My concern is that we had this confusion before: When RDF and OWL were standardized, they came with RDF/XML syntax only, and people thought this semantic web is just another kind of XML. But a complicating kind of XML, where the idea of graphs was hidden behind rdf:ID and rdf:about attributes.

From the data model perspective, RDF was never a kind of XML. It can be serialized as XML, but it has a different data model. This difference was, perhaps, obvious to the standard committee and they never thought anyone would be confused or that this confusion would be an issue.

In reality, this was, however,  a big issue. It was very difficult for other people to understand what RDF was without a lot of education that had to change the assumptions they quickly made after first getting to know about RDF. First impressions are hard to change. Things became easier after Turtle became better known as the way to serialize and RDF/XML faded into background as just one (lesser used) serialization.

\subsection{Readability in the face of complexity and internationalization of human friendly syntaxes}

\textbf{use of templates for better readability and management of complexity}

complexity needs to be managed not ignored.

example in a number of syntaxes.

In ShEX Compact

\begin{ex}
<WebServicePersonShape> {
  rdf:type foaf:Person ,
  foaf:name xsd:string ,
  foo:email xsd:string ,
  foo:phone xsd:string *
}
\end{ex}

In ShEx RDF

\begin{ex}
<WebServicePersonShape> a rs:ResourceShape ;
   rs:property  [ rs:occurs              rs:Exactly-one .  ;
                  rs:propertyDefinition  foaf:name ;
                  rs:valueShape          foaf:Person ],
                 [ rs:occurs              rs:Exactly-one ;
                  rs:propertyDefinition  foo:email ;
                  rs:valueShape          foaf:Person ] ,
                 [ rs:occurs              rs:Zero-or-many ;
                  rs:propertyDefinition  foo:phone ;
                  rs:valueShape          foaf:Person ] .
\end{ex}

In SPIN turtle

\begin{ex}
foaf:person a owl:Class;
spin:constraint [ spl:predicate foaf:name ;
                  spl:count 1 ] ,
                [ spl:predicate foo:email ;
                  spl:count 1 ] ,
                [ spl:predicate foo:phone ;
                  spl:minCount 0 ] .
\end{ex}

Now we change the requirements very slightly. Instead of any string being acceptable as e-mail we need to ensure
it is actually a valid e-mail for an employee in our organisation.

How would you determine what is a valid e-mail for an employee in a organisation?
The first approach is to say that it has to match a specific regex. e.g. for the university I went to any e-mail
address of an employee needs to match the regex \begin{verbatim}“.+@pl.hanze.nl^”\end{verbatim}.

Let's try that in ShEx compact shall we.

\begin{ex}
<WebServicePersonShape> {
  rdf:type foaf:Person ,
  foaf:name xsd:string ,
  foo:email IRI %sparql{ ?s foo:email ?mbox . FILTER (REGEX(str(?mbox), “.+@pl.hanze.nl^”) %}
  foo:phone xsd:string *
}
\end{ex}

And in spin turtle

\begin{ex}
foaf:person a owl:Class;
spin:constraint [ spl:predicate foaf:name ;
                  spl:count 1 ] ,
                [ spl:predicate foo:email ;
                  spl:count 1 ] ,
                [ sp:text “ASK{?s foo:email ?mbox . FILTER (!(REGEX(str(?mbox), “.+@pl.hanze.nl^”)) }"
                [ spl:predicate foo:phone ;
                  spl:minCount 0 ] .
\end{ex}

This can be simplified again with a template library e.g. similar to of the ones given at [1].

\begin{ex}
our-company:employee-email 
      a       spin:Template ;
      rdfs:comment "This template check a IRI to be a valid employee e-mail property ?arg1."@en ;
      rdfs:label "syntax check in all instances:  valid employee email"@en ;
      spin:body
              [ sp:text """CONSTRUCT {
                 _:b0 a spin:ConstraintViolation .
                 _:b0 spin:violationRoot ?s .
                 _:b0 spin:violationPath ?arg1 .
                }
                WHERE {
                 ?arg1 foo:email ?mbox .
                 FILTER (!(REGEX(str(?mbox), “.+@pl.hanze.nl^”))
                }""" ;
\end{ex}

So now the spin turtle becomes

\begin{ex}
foaf:person a owl:Class;
spin:constraint [ spl:predicate foaf:name ;
                  spl:count 1 ] ,
                [ spl:predicate foo:email ;
                  spl:count 1 ;
		  a our-company:employee-email] ,
                [ spl:predicate foo:phone ;
                  spl:minCount 0 ] .
\end{ex}

Which is more likely to be readable to the “business” users.

The second advantage of this kind of approach is that these templates are maintainable independently from the rules themselves.

This becomes even more the case when the validation starts to be more complicated.
Few companies have a clean separation between e-mails addresses for employees and mailing lists.
However, most do have a LDAP or equivalent system. Assuming Squirrel RDF for LDAP[2] is still working
a system can adapt that as an information source.

Shex now turns into this.

\begin{ex}
<WebServicePersonShape> {
  rdf:type foaf:Person ,
  foaf:name xsd:string ,
  foo:email IRI %sparql{ ?s foo:email ?mbox . SERVICE<ourcompanyLdap>{ ?employee foaf:mbox ?mbox ; a :Employee }) %}
  foo:phone xsd:string *
}
\end{ex}

While the SPIN solution stays like this.

\begin{ex}
foaf:person a owl:Class;
spin:constraint [ spl:predicate foaf:name ;
                  spl:count 1 ] ,
                [ spl:predicate foo:email ;
                  spl:count 1 ;
		  a our-company:employee-email] ,
                [ spl:predicate foo:phone ;
                  spl:minCount 0 ] .
\end{ex}

The SPIN solution can be made more compact if it had more predicates e.g.

\begin{ex}
foaf:person a owl:Class;
shape:hasOne  [ spl:predicate foaf:name  ] ,
	      [ a our-company:employee-email ] .
shape:some    [ spl:predicate foo:phone ] .
\end{ex}

Compare this to the compact ShEx form? Is the SPIN one that bad?

\subsection{define vocabulary terms and constraints with the same syntax}
If you want to properly publish a "schema" then 
you also need a way to define the properties and classes that are used, 
together with their rdfs:labels, rdfs:comments, relationships etc. These 
are attached to the properties globally, and already exist in triple 
format. Developers would end up using a Turtle/JSON-LD file for one part 
of their schema, and then a custom syntax just for the constraints?

\section{Class-Based Validation}

Constraints can be associated with instances of RDFS/OWL types.  
I view the ability to associate constraints with instances of types as the most important aspect of a constraint system.

\tb{how is it done using our approach}

\subsection{modularization of constraints / class-based validation vs. shapes-based validation}

constraints can be hosted by a "Shape" object or to an OWL class.

\textbf{class-based validation}

If we want to be based on RDF, then we should honor its basic principles. One of those principles is that of self-describing data, where applications can look up the definition of a resource by resolving URIs. For example, if a resource declares an rdf:type, then an application should be able to look up the definition of the class, including its semantic declarations and constraints. This should be the default assumption: someone creates an ontology and when he publishes it on the web then anyone who wants to reuse that ontology should honor the same constraints.

Having said this, applications may overload the default behavior. In TopBraid we do this by first looking at local files for the same URI, and preferring those over the files from the web. This also makes it possible to refer to graphs that do not even exist on the web.

\textbf{shapes-based validation}

When resources do not even have to have an rdf:type - how is this going to be
self-describing data? What is the entry point into the validation?"

- It is self-describing because the Shape is either linked to the service
description or the instance document.

- The entry point is the entire RDF document (aka graph) just like in
SPARQL.  There is not necessarily a special node in the graph. You use a
general graph pattern to either find a subgraph that must exist (an
assertion), or to find a subgraph that must not exist (a constraint
violation).

This is motivated by Linked Data API considerations. Here
one deals with REST services. For example, when creating new resources,
one POSTs an RDF document to some URL. We want to describe the API
contract for the service. The service is described by a Service
Description resource. The Service Description resource refers to the Shape
accepted by the POST request. Shape may require that the request contains
a node with an rdf:type property. However, the Shape may apply to several
different rdf:types. The Shape is therefore attached to the service, not
each type. After the resource is POSTed, the service may added new
triples, so the Shape of the created resource is different than the Shape
of the POST request. The created resource may contain a link to its Shape.
A service that lets you query across a set of resources may also link to a
set of Shapes that define the data available for querying. This metadata
both tells you what properties are available and may let you define more
efficient queries.

The above use cases are orthogonal to use cases where an RDF class defines
constraints that must be universally obeyed, independent of the context,
i.e. a bicycle must have two wheels.

We have seen many more examples of the
latter than the former, and I believe the structure of existing ontology
languages suggests that it should be possible to "attach" constraints to
classes. I personally believe your use case is the exception, not the
rule, but of course I would like to see a generic solution that covers
all use cases so that the standardization process succeeds.

% -

Well if you only consider constraints for objects of properties, 
then it may turn out that constraints associated with an RDF class
are in the minority.  Of course, I strongly feel that constraints for objects
of properties is not a central aspect of RDF validation.

\subsection{Pros}

In our experience, having an rdf:type is the norm, and typeless resources are 
the exception. I don't think it is a good idea to base the design of 
such an important aspect on the exception cases. Attaching 
the semantics to classes gives you a natural way of encapsulation, 
inheritance and allows us to reuse all existing ontologies in an 
incremental way, rather than coming up with a parallel world of 
free-floating shapes.
- Object-orientation is mainstream.
- (simple and consistent) "object-oriented" design used by all other ontology languages.
In our experience, using rdf:type triples and classes is a more intuitive mechanism, and it 
already exists, is consistent with OWL etc.
%\footnote{\url{http://lists.w3.org/Archives/Public/public-rdf-shapes/2014Jul/0307.html}}

Yes: RDF is all about graphs, but does 
this mean that a constraint language may not exploit certain triples 
from those graphs and give them special meaning?
%\footnote{\url{http://lists.w3.org/Archives/Public/public-rdf-shapes/2014Jul/0307.html}}

Another analogy is XML, where every XML element also has a name. This is 
comparable to its rdf:type.
%\footnote{\url{http://lists.w3.org/Archives/Public/public-rdf-shapes/2014Jul/0307.html}}

If we are talking about Linked Data and want to stay
aligned with the way that ontologies are currently being built, then
relating constraints to classes remains a requirement.

\subsection{Cons}
An RDF document is a set of triples (statements). The triples do not 
necessarily have to look like they came from an object (in the OO sense), 
i.e. that there is one distinguished root node (this, self) that has some 
type (class) attribute, and other triples (properties) that have the root 
node as their subject, and so on recursively. 
%\footnote{\url{http://lists.w3.org/Archives/Public/public-rdf-shapes/2014Jul/0300.html}}

If you think of an RDF document as a graph, then there should be no special 
significance to a node that happens to have a type attribute. We should be 
able to state constraints on the graph in the absence of type triples. 
This is very consistent with SPARQL. SPARQL includes a graph pattern 
matching language. SPARQL queries are not associated with any specific 
type, so why should constraints be?
%\footnote{\url{http://lists.w3.org/Archives/Public/public-rdf-shapes/2014Jul/0300.html}}

However, even if the RDF document was the representation of some OO-like 
object that had a root node and some type (class) attribute, its shape 
could vary depending on the context. For example, when you create a 
resource using POST, certain triples will be absent, e.g. creation date, 
and if present they may be ignored or the server may fail the request. 
When you GET that resource you will normally see other triples that the 
server added, e.g. creation date, and these will occur exactly once. 
%\footnote{\url{http://lists.w3.org/Archives/Public/public-rdf-shapes/2014Jul/0300.html}}

OSLC lets you associate shapes with operations. Resource instances may 
link to shape resources that describe the instance. There is no need to 
base the association between resources and constraints using an RDF type. 
A shape could apply to several types or to no types.
%\footnote{\url{http://lists.w3.org/Archives/Public/public-rdf-shapes/2014Jul/0300.html}}

\section{Inferencing as a pre/post validation step | Reasoning and Constraint Checking}

Both should be possible:

\begin{itemize}
	\item Constraint Checking with Reasoning
	\item Constraint Checking without Reasoning
\end{itemize}

\subsection{our approach}

Existential Quantification on Object Properties

constraint (formal syntax):
\begin{ex}

\end{ex}

constraint (Manchester syntax):
\begin{ex}

\end{ex}

constraint (functional-style syntax):
\begin{ex}
SubClassOf( ObjectSomeValuesFrom( :hasDog owl:Thing ) :DogOwner ) 
\end{ex}

constraint (turtle syntax):
\begin{ex}
    _:x 
        a owl:Restriction ;
        owl:onProperty :hasDog ;
        owl:someValuesFrom owl:Thing ;
        rdfs:subClassOf :DogOwner .
\end{ex}

data (Turtle syntax):
\begin{ex}
    :Peter 
        a owl:Thing , owl2spin:ToInfer ; 
        :hasDog :Brian . 	
    :Brian
        a owl:Thing .
\end{ex}

inferred triples (Turtle syntax):
\begin{ex}
:Peter a :DogOwner .
\end{ex}

\subsection{Constraint Checking with Reasoning}

Constraint validation does not appear to be part of the services provided by
OWL.  This has lead to claims that OWL cannot be used for constraint
validation.  However inference, which is the core service provided by OWL,
and constraint validation are indeed very closely related.

Inference is the process of determining what follows from what has been
stated.  Inference ranges from simple (students are people, John is a
student, therefore John is a person) to the very complex.  Inference can
also recognize impossibilities (students are people, John is a student, John
is not a person, therefore there is a contradiction).  In the presence of
complete information, nothing new can be inferred, so inference only checks
for impossibilities, i.e., constraint violations.  So the way do constraints
in OWL is to first set up complete information, and then just perform
inference [this is related work].

For example, with the concept axiom

\begin{ex}
  ex:Person <= =1 foaf:name & all foaf:name xsd:string &
               =1 foaf:phone & all foaf:phone xsd:string &
               =2 ex:child
\end{ex}

and in the presence of (locally) complete information, such as

\begin{ex}
  <John> in ex:Person .
  <John> foaf:name "John"^^xsd:string .
  <John> foaf:phone "+19085551212"^^xsd:string .
  <John> ex:child <Bill> .
  <John> ex:child <William> .
  <John> in <=1 foaf:name .
  <John> in <=1 foaf:phone .
  <John> in all child {<Bill>, <William>, <Susan>} .
  <Bill> /= <William> .
  <Bill> /= <Susan> .
  <Susan> /= <John> .
\end{ex}

determining whether <John> belongs to ex:Person is just constraint validation.

Setting up complete information is just what was done above.  In a model
there is complete information, so considering an RDF graph (plus
consequences) as a model turns OWL inference into constraint validation.
Of course, this doesn't mean that you have to implement OWL inference in a
model the same way that you need to with incomplete information.  In fact,
as above, constraint validation can be implemented as SPARQL queries.

Conclusion

In fact the main difference between recognition and constraint checking is
that the former either has no axioms or only uses axioms defining names that
do not occur in the RDF graph whereas constraint checking uses axioms that
relate concepts appearing in the RDF graph to descriptions.

So OWL can indeed be used for both the syntax and semantics of constraint
checking and closed-world recognition in RDF, and most or all of it can be
implemented using a translation to SPARQL queries.

-----

\begin{enumerate}
	\item inference --> complete model
	\item constraint checking
\end{enumerate}

-----

Mentioning the use of inferencing as a pre/post validation step option is perfectly fine, enforcing it is a completely different thing.

Well it's not as simple as just mentioning that inferencing is a pre/post 
validation step option, depending on how your validation process is defined. 
To make validation play well with inference you may have to be able to handle 
infinite sets and multiple models on one side and too-central-to-turn-off 
inferences on the other.

% -

\textbf{use structural information for inferencing}

- use structural information to produce new output (e.g. XML trees or other RDF triples) (see ShEx paper)

\textbf{rules}

- Another example is spin:rule, which is in our experience 
tremendously useful for defining mappings between ontologies, and to
calculate the ex:area of a ex:Rectangle from ex:width and ex:height.
Once we have a mechanism to attach SPARQL and templates to classes for
constraint checking, we could use exactly the same mechanism to define
such production rules.

% -

\textbf{sub-class super-class inferencing}

Constraint definitions attached to a superclass (assuming
Shape=class) need to also apply to instances of a subclass.

\subsection{Constraint Validation Without Reasoning}

\section{Context-Sensitive Constraint Validation}

main assertions:
\begin{itemize}
	\item Reasoning and Closed World Assumption
	\item constraints depend on the context
\end{itemize}

But without reasoning things can work very well as well.

reasoning would either hide the error

There is an underlying practical problem, which we face daily in the management of the LOV repository.
Again, it's not a minor point that RDF uses URIs for classes and properties. If you find a class or property URI somewhere in data (e.g., DBpedia) how do you figure the semantics of this URI, IOW how do you find the document(s) you are speaking about which define it, and which ones will you abide by, to figure in practice the closure of the description of this URI? 
Look at the result of this query  http://bit.ly/UPGA25  ran on current LOV database of 450 vocabularies/ontologies. It yields all elements related to foaf:Person in various namespaces (and so many documents). Somehow each of those 300+ assertions is refining the semantics of foaf:Person. If you ignore the 25 ones defined by the foaf: namespace itself, you are lefy with more than twenty different namespaces/vocabularies/documents to explore, and select or not to figure the closure.

Of course, looking only at the FOAF vocabulary using a HTTP GET on foaf:Person, you will not access and even be aware of all this extra semantics, and you can ignore it, apart of those which FOAF itself reuses.

This is an extreme case maybe, but it illustrates what the practical problem will be, when using a URI, to first find out to which semantics you abide by before passing it to reasoners or constraint checkers. One could imagine something like a content negotiation on the URI where you pass in parameters the type of description you want for this URI (give me SPIN, OWL, Shapes ...). But given the messy way content negotiation is already implemented after httpRange14 resolution (based also on our LOV experience), I'm very skeptical about such a solution in practice. Moreover, different parties will use different documents of which the original URI owner does not control, is not aware of, let alone agrees with.

My concern is to see a door wide open to more balkanization of the Semantic Web, each tribe abiding by its own, not necessarily public, interpretation of shared vocabularies.

So if you use RDFS and OWL, and include a lot of constraints, then the
terms are not very reusable because they carry a lot of baggage in the
form of inferences which may not make sense in your application.

Note that I am describing the state of the practice. Many ontologies in 
fact do contain a lot of inferences and this makes them less reusable. 
This is true even in absence of constraints since W3C OWL doesn't 
officially handle constraints, just inference rules.

The point I was trying to make is that applications often need to impose 
additional constraints on terms and that these constraints often depend on 
the context.

Let's refocus the discussion on how an application designer would reuse an 
externally published OWL ontology and impose additional constraints. Let's 
assume OWL IC semantics. What would the application designer provide to 
describe a REST API that required exactly one dcterms:title triple in the 
request body on POST?

% -----

\subsection{entailment regimes}

ShEx and Resource Shapes work on an RDF graph.  This does not mean that they 
can be used in combination with a reasoner, even an RDF reasoner.  SPARQL has 
entailment regimes, which specifies how SPARQL is supposed to work with reasoning.

Consider, for example, that there are infinitely many RDF consequences of a 
finite RDF graph.  How do I run ShEx and Resource Shapes on an infinite graph?

Consider, for example, that the OWL consequences of a finite RDF graph are 
generally not representable as an RDF graph.  How do I combine ShEx or 
Resource Shapes with OWL?

\textbf{support of inferences from ontologies}
It may be that there are many ontologies that support a lot of inferences.
However, there are lots of ontologies that are small and do not support a
lot of inferences.  RDFS and OWL can be used both ways.

Further, why should an ontology that supports many inferences be
undesirable, even if it is less reusable?  I don't think that you can argue
that reusability is a good in and of itself.  For example, the ontology
containing only the axiom stating that owl:Thing is a subclass of owl:Thing
is maximally reusable, but not very useful.

\section{Comparison of Validation/Constraint Languages | Why OWL 2 and SPARQL for RDF Validation?}

\textbf{dependencies between validation languages}

Here is a diagram draft illustrating the dependencies among various 
Semantic Web languages, as I see them:

     https://twitter.com/HolgerKnublauch/statuses/494648159931346944

The stacking of boxes on top of each other means "uses features of". 
Please don't get caught up in details. The points that I am trying to 
make are:

- There can be multiple "schema" languages for the same RDF models

- Different languages have different design goals (e.g. OWL was mainly 
created for classification tasks)

- All these languages can live alongside with each other without 
breaking each others interpretations, for example via separate import 
mechanisms (owl:imports, spin:imports, ic:imports). A SPIN model can 
ignore OWL constructs, but SPARQL queries can also be executed on top of 
graphs that have OWL inferencing activated. Likewise, OWL models can 
ignore spin:constraint definitions.

To me one of the important things is to ensure that classes, properties 
and instances can be reused. The concept of "Classes" is quite basic, 
established and successful, and is therefore a good foundation for 
Shapes too.

And yes, I am fully aware that there are other languages that did not 
make it into this diagram. I just wanted to focus on the comparison 
between OWL and Shapes+SPIN and make clear that this is not an either-or 
discussion. There is plenty of space for both approaches, and indeed 
both "communities" can benefit from each other when the Semantic Web 
grows as a whole.

\textbf{Why OWL & SPARQL for RDF validation?}

\begin{itemize}
	\item OWL & SPARQL are sufficient for validation in a CWA
	\item Normally, the RDF has already an OWL / RDFS. Thus, part of those declarations will be defined anyway
	\item In most cases reusing existing OWL schemas for validation is enough
	\item What we need in the end is tools that translate OWL to SPARQL - or to something intermediate like ShEx or SPIN
	\item language that many people already know
	\item in practice that most people out there make use of RDFS and OWL constructs to tell other people and applications about how valid instances should be created.Whether this is good or bad is another question, but that's the reality.
	\item OWL semantics:
Most people don't care about open world semantics, but of course nobody would admit that because it's against the specs and thousands of academic papers.
	\item could be interpreted either with the open world assumption to support open world reasoning, and (exactly the same piece) interpreted in closed world applications as a constraint for interfaces or a validation rule
\end{itemize}

\textbf{difference between a declarative validation / constraint language (e.g. OWL 2, ShEx) and a more general purpose validation / constraint language (e.g. SPARQL)}

\textbf{Why declarative validation / constraint language?}

a human readable syntax is vastly preferable to an RDF based syntax

\textbf{Why general purpose validation / constraint language?}

- maximum expressivity
	- SPARQL is very expressive, so most typical constraints can be expressed
	- need to express more complicated constraints, and SPARQL is the best available language to represent those

\textbf{Why NOT general purpose validation / constraint language?}

too low-level:
SPARQL is too low-level. If you look at a SPARQL query, you'd have a hard time figuring out what constraint it is checking.

\textbf{Why OWL / OWL 2 for RDF validation?}

\textbf{Why NOT OWL / OWL 2 for RDF validation?}

The problem with OWL is the different semantics so people have to rewrite it in another languages such as SPIN / ShEx / SPARQL

http://composing-the-semantic-web.blogspot.com.au/2010/04/where-owl-fails.html

intended for
(1) semantic description
(2) reasoning: infer new triples from a given set of triples

not intended for
(1) validation
(2) describe a database structure

Why not use OWL to describe database structures? (example)

it is hard to read an OWL ontology to understand the structure of a database.

ShEx:

\begin{ex}
A {
  (ex:samepred1 @B | ex:samepred1 @E) #either referencing B or E
}
C {
  ex:samepred1 @D
}
\end{ex}

OWL:

\begin{ex}
Class A -> ex:samepred1 -> Class B
Class C -> ex:samepred1 -> Class D
A <= all ex:samepred1 Extra
C <= all ex:samePred1 D
Class B -> rdfs:subClassOf -> Class Extra
Class E -> rdfs:subClassOf -> Class Extra
\end{ex}

Here have an extra class 'Extra' for which it is not clear whether is created for making the ontology work or is an actual Concept in my database.

OWL has disjunction, so you can say
A <= all ex:samepred1 (B or E)
which is even better than the ShEx version you give.

(3) to be used as Schema language for validation
(4) further reasons:  conclusion of this paper (http://arxiv.org/pdf/1404.1270v1.pdf)
(5) Another thing you can not do in OWL is to define the following:

\begin{ex}
Type A -> ex:samepred1 -> Type B
Type C -> ex:samepred1 -> Type D
\end{ex}

If you would define this in OWL you will also get, because OWL is property oriented and a property can only define a range and domain

\begin{ex}
Type A -> ex:samepred1 -> Type D
Type C -> ex:samepred1 -> Type B
\end{ex}

Which is something we do not want.

Why do you say that?  OWL includes many constructs that are local.  Here you
can use allValuesFrom, as in

\begin{ex}
A <= all ex:samepred1 B
C <= all ex:samePred1 D
\end{ex}

\begin{itemize}
	\item 
	Clark & Parsia had previously proposed the ICV semantics for OWL, but this was not submitted to W3C.
	\item
	Ambiguousness when OWL would be used assuming both OWA (for inferencing) and CWA (for constraint validation) (see section XXXXX).
It would be somewhat confusing to have two completely different semantics for OWL.
	\item
	OWL cannot represent all possible use cases
\end{itemize}

(6) modeling goals / orientation

SHEX is oriented on Shapes and Shape Properties (Property per shape), 
whereas OWL is oriented on (Restriction) Classes and Properties.
Orientation on (Restriction) Classes and Properties is a logic and the best thing to do when working in the world of reasoning.

However if we look from user point of view, which would like to understand the structure of database or interface of a service then an orientation on Shape and Shape Properties is better. This is what a user needs when he wants to write some queries for a database as noted earlier on by me.

\textbf{OWL vs. ShEx}

OWL is very good at semantic level / Shape Expressions are more suited for the syntactic level or data integration level

classes are semantic / shapes are syntactic

OWL: inferencing

ShEx: looks at the shape of the RDF graph

\textbf{Why SPIN?}

combines the flexibility of SPARQL with the simple declarative syntax of RDF triples

SPIN is self-describing

is extensible to any constraint

grows with the evolution and adoption of SPARQL

\section{Validation using Closed World vs. Open World Semantics | OWL Closed World + SPARQL for RDF Validation | Underlying Semantics / Assumptions: Closed World Assumption and Unique Name Assumption}

Underlying Assumptions: Closed World Assumption and Unique Name Assumption

OWL descriptions and the OWL semantics provide the necessary framework for
both validating constraints and providing recognition facilities.
Why then are there claims that
OWL is inadequate for these purposes?  I do not know why, but there are
several aspects of OWL that might not be consonant with constraints and the
kind of recognition that might be desired.  However, it turns out that both
OWL syntax and semantics are arguably the right solution for RDF constraint
checking and closed-world recognition.

Closed-World Recognition / class assertions

Determining whether an individual belongs to an OWL concept is recognition.

Let's first look at recognition.  Recognition is the basic operation in
ShEx - we want to determine whether a particular node in an RDF graph matches
a ShEx shape, for example, to say that John in

\begin{ex}
  <John> foaf:name "John"^^xsd:string .
  <John> foaf:phone "+19085551212"^^xsd:string .
  <John> ex:child <Bill> .
  <John> ex:child <William> .
\end{ex}

matches

\begin{ex}
  { foaf:name xsd:string , foaf:phone xsd:string, ex:child [2] }
\end{ex}

Recognition is also a basic operation of OWL.

The OWL version of the above ShEx expression (using a version of the OWL-DL
publication syntax) is

\begin{ex}
    =1 foaf:name & all foaf:name xsd:string &
    =1 foaf:phone & all foaf:phone xsd:string &
    =2 ex:child
\end{ex}

So it seems that OWL can easily handle ShEx recognition.

However, John does not match the above OWL description.  Why is this?  It is
precisely that OWL does not assume that absence of information is
information about absence.  RDF works under the same assumptions, by the
way.  John could have more than one name as far as the above information is
concerned.   OWL (and RDF too) also does not assume that different names
refer to different individuals.  Bill and William could be the same person.

OWL has facilities to explicitly state information about absence and
information about differences.  If we add

\begin{ex}
    <John> in <=1 foaf:name .
    <John> in <=1 foaf:phone .
     <John> in all child {<Bill>, <William>} .
    <Bill> /= <William> .
\end{ex}

then John does match the above description.

So it is not that OWL does not perform the kind of recognition that
underlies ShEx, it is just that OWL does not make the assumption that
absence of information is information about absence.

However, suppose that we want to make this assumption.  This is roughly
equivalent to saying that a system assumes that if it can't determine some
fact, then that fact is false.  There is a very large body of work on this
topic because there are many tricky questions that arise with respect to
closure in any sophisticated formalism, and OWL is indeed sophisticated.

Fortunately RDF and RDFS are not very sophisticated at all, and the tricky
questions just do not arise if information comes in the form of RDF and RDFS
triples.  The basic idea is to treat the triples (and their RDF and RDFS
consequences if desired) as completely describing the world.  So, 1/ if a
triple is not present then it is false and 2/ different IRIs describe
different individuals.  This is precisely the same idea that underlies model
checking.  First-order inference is undecidable, but determining whether a
first-order sentence is true in one particular state of the world is much,
much easier.

So it is possible to use the OWL syntactic and semantic machinery to define
how to recognize OWL descriptions under just the same assumptions that
underlie ShEx.  The only change from the standard OWL setup is to define how
to go from an RDF graph to an OWL model.  (There are some technical details
that interfere with this general description of the account, but they are
easy to handle.)  Definitions, even recursive definitions, can be handled
with only minor extensions to the framework.

This is all quite easy and conforms to a common thread of both theoretical
and practical work.  It also matches how StarDog ICV works (as the
theoretical underpinning of StarDog ICV is one of these theoretical
results).  Further, the approach can be implemented by translation into
SPARQL queries, showing that it is practical.  (There may be some constructs
of OWL that do not translate into SPARQL queries when working with complete
information, but at least the parts of OWL that correspond to the usual
recognition conditions do so translate.)

-----

This mailing list provides plenty of evidence that OWL is not expressive 
enough and something on the level of SPARQL is needed. ShEx has an 
escape mechanism to fall back to SPARQL [1], and IBM has explicitly 
stated that this is required too [2].

So as a minimum, the outcome of 
this group should be to agree on a high-level vocabulary (possibly OWL 
and/or Shapes) plus a mechanism to represent other cases with something 
like SPARQL.

\subsection{Why OWL Closed World for RDF Validation?}

There are some key principles that need to be right. I believe that lack of the wider use of Semantic Web standards, has to do with a small handful of assumptions that ended up being obstacles instead of enablers. Commitment to the OWA to make monotonous reasoning possible, in my view, was one of them. On one hand, this decision has many implications that are too strange for people. On the other hand, monotonous reasoning is only possible when the asserted facts never change, just get added to. In real life, this rarely happens. Data often has errors which need to be corrected, facts that were true at some point get changed, etc. With this, the pluses of OWA don't seem to compensate for its minuses.

\subsection{Why NOT OWL Closed World for RDF Validation?}

- OWL cannot even do basic math

- OWL cannot do string operations

- OWL does not have have a concept of "variables" that is very much needed to do complex joins.

-----

Why is OWA and validation with OWL problematic (example)?

As for an area where OWA is problematic, one need look no further than
FRBRer ontology[1], which is clearly designed using OWL constraints
(which I prefer to call "axioms" to avoid confusion) in a closed world
way. The definitions are quite strict, with all classes disjoint each
other, such that, using reasoning in the OW, any FRBRer data will be
inconsistent with data not using that exact set of axioms.

We used a FRBRer dataset as a use case in the main RDFUnit paper [1] and we actually came to the same conclusions.
[1] http://svn.aksw.org/papers/2014/WWW_Databugger/public.pdf

\subsection{Discussion Why (NOT) OWL Closed World for RDF Validation?}

ambiguousness:
Reusing OWL syntax with a closed world interpretation is of course a seductive path but I've always been a bit uneasy about it. OWA is built in the OWL Recommendation. I would rather have a neutral language, with non-ambiguous open world interpretation in OWL, and another one in any closed-world language (SPIN, SPARQL, you name it).

Yeah, I appreciate that concern. Everyone keeps telling me that this seems like a problem in principle; apparently we're the only ones who built it *as a real thing* and *in practice* it's not a problem at all. Our customers don't find it in the least bit confusing. In fact, as we originally said, most people who wanted OWL always wanted closed world semantics anyway, so giving it to them is a big win.
Would using different namespaces help in acceptance?
NO → to not break existing tools like Protege which knew how to manipulate that *syntax*
YES → avoid confusion

\subsection{Unique Naming Assumption}

Non-Unique Naming Assumption
You can't easily use OWL to even do cardinality checking. For example, suppose you assert that :hasFather is a functional property, and you have the triples :Luke :hasFather :Anakin and :Luke :hasFather :Darth.An OWL reasoner will invoke the Non-Unique Naming Assumption to infer that :Anakin owl:sameAs :Darth.

\subsection{example validation + inferencing with CWA/UNA}

\begin{ex}
Let's take an example schema:

  my:IssueShape {
    x:submitter @my:SubmitterShape
  }
  my:SubmitterShape {
    foaf:name LITERAL
  }

We can express that as OWL CWA/UNA like so:

  x:submitter a owl:ObjectProperty .

  my:IssueType
    rdfs:subClassOf
      [ owl:onProperty x:submitter ;
        owl:cardinality 1 ] ,
      [ owl:onProperty x:submitter ;
        owl:allValuesFrom my:SubmitterType ] .

  foaf:givenName a owl:DatatypeProperty ;
    rdfs:range xsd:string .
  foaf:familyName a owl:DatatypeProperty ;
    rdfs:range xsd:string .

  my:SubmitterType
    rdfs:subClassOf
      [ owl:onProperty foaf:givenName ;
        owl:cardinality 1 ] ,
      [ owl:onProperty foaf:familyName ;
        owl:cardinality 1 ] .

A piece of instance data like

  <Issue1> x:submitter _:submitter .
  _:submitter foaf:givenName "Bob" .

has two untyped nodes. In order to validate, We posit that:

  <Isseu1> a my:IssueType .

and the system then gets to infer that:

  _:submitter a my:SubmitterType .

(Of course, this could have been an anonymous class in the OWL, but I
gave it a label for clarity here.) CWA validation leads us to believe
that the foaf:familyName property is missing for _:submitter.

If any arcs are missing from _:submitter other than a type arc, those
are considered validation errors, but in order to even validate, I
believe that OWL UNA/CWA (e.g. ICV) is required to do type inferencing
in order to get anything done. It was this juxtaposition that I was
trying to point out.
\end{ex}

\section{Modularize and Separate Semantics and Constraints}

semantics (OWL ontologies)

In some cases, inferred triples are not intended or do not make sense within a specific application.

\textbf{Constraints are application-specific.}
When combining terms from multiple sources, 
the constraints associated with a term often depend on how 
the term is used in a particular application. Consider DC Terms. It was 
designed to provide a highly reusable vocabulary. There are very few 
constraints imposed by DC Terms and this makes it very reusable. For 
example, consider dcterms:title. In one application dcterms:title may be a 
required property while in another it may be optional. So where do you put 
those constraints? They do not belong in the DC Terms vocabulary. You need 
another place to define constraints and associate them with the 
application.

Different consumers of information conforming to an ontology may want
different constraints to be checked against that ontology.

\textbf{Inferencing and Constraint Validation.}
So if you use RDFS and OWL, and include a lot of constraints, then the 
terms are not very reusable because they carry a lot of baggage in the 
form of inferences which may not make sense in your application. For 
example, if you used rdfs:domain or rdfs:range then you infer certain type 
triples. I once was looking for terms that defined start and stop dates. I 
found dtstart and dtend in http://www.w3.org/2002/12/cal/ical but when I 
looked at the RDFS/OWL it had a lot of undesired inferences concerning the 
domain. So if I had reused dtstart in my application, then a reasoner 
would have inferred a lot of triples that didn't make sense.

\textbf{Reuse of Terms from Vocabularies.}
At OSLC we are trying to integrate information from a lot of applications. 
We try to reuse terms from established vocabularies. We define new common 
terms in a core OSLC vocabulary. We do this to make writing queries 
easier. This means that resources contain terms from many vocabularies.

%\footnote{\url{http://lists.w3.org/Archives/Public/public-rdf-shapes/2014Jul/0301.html}}

\textbf{Modularization of ontologies and constraints.}

All these complaints about RDFS and OWL appear to be based on the conception 
that RDFS and OWL work with a single document containing everything that can 
ever be said about a particular vocabulary.

However, this is a misconception.  It is certainly possible in RDFS and OWL to 
have multiple documents that speak to the same vocabulary.  This is done, for 
example, when OWL ontologies are extended.  A core document talks about the 
core vocabulary and other documents add new vocabulary and add new information 
about the core vocabulary as well.

The exact same thing can (and should) be done with constraints.  You can have 
a document that provides the core information about a vocabulary.  You can 
have multiple documents that provide constraints on this vocabulary for 
various purposes.  When validating some information one can pick which set or 
sets of constraints to apply.

This division can also be done with the axioms of the ontology.  There is no 
need for all the axioms of an ontology to be in the same document, leading to 
the possibility of having the RDFS portion be in one document and the non-RDFS 
portion in another document.  Other divisions are also possible.

[Assume w.l.o.g. that we are only considering standardized OWL semantics.*]
If an axiom is part of the core meaning of a term then it belongs in the core  ontology.  For example, if it is part of the definition of the term  'bicycle' in the ontology that it must have exactly two wheels, this axiom belongs in the core ontology. Unicycles are thus excluded.

Bicycles with 'training wheels' attached may or may not qualify, based on how 'training wheels' are defined.  
Removing a core axiom from the ontology does not provide more opportunities for *reuse* ; it provides more opportunities for *misuse*.
If an axiom is not part of the core meaning of a term, then it does not belong in the core ontology.  If there are no meaningful cardinality constraints on the number of titles a thing can have then they don't belong in the core ontology.
Fortunately it is possible to build new, more restrictive ontologies that reuse and restrict existing ontologies. If one wishes to describe a world where bicycles can only have wheels with spokes (e.g.  things with solid wheels are not within the meaning of 'bicycle') , one can use an import statement to include the axioms from another ontology, then add the additional axioms that commitments only in this new ontology.

If you are engaged in an information fusion task, the more precise the definitions used in the shared ontology, the more feasible the task becomes.  The more diverse the information contexts become the less useful generic terms become.
Having a broad  property named "health" is useless if in one part of the organization it refers to having up to date vaccinations , and in another it refers to the whether an aircraft is ready to deploy.
%\footnote{http://lists.w3.org/Archives/Public/public-rdf-shapes/2014Jul/0305.html}}

\textbf{separate declarations (shapes, constraints) and OWL restrictions (semantics).}
The declarations of classes, properties and instances can happen in one graph, 
and then there can be 
multiple interpretations, including specifications in multiple 
languages. OWL already has owl:imports, SPIN already has spin:imports, 
ICV has ic:imports. RDF should probably have rdf:imports (and rdf:Graph 
similar to owl:Ontology).

I guess the question remains is what to do with the published 
vocabularies that do not honor this separation and mix the OWL 
restrictions and class definitions into a single file. Even rdfs:domain 
and range statements are often too restrictive. One answer is to simply 
ignore those statements and start with the languages in the right hand 
side of the diagram. After all, an rdfs:domain statement is just another 
triple. But there will be applications where mixing Shapes or SPIN with 
OWL semantics is desirable. There is no single truth here, and the 
application developer is already allowed to choose.

%\footnote{http://lists.w3.org/Archives/Public/public-rdf-shapes/2014Jul/0306.html}}

-----

Our suggestion:
Separate facts, axioms, and constraints

- documents containing facts (import other documents)
- documents containing OWL axioms / semantics / ontology
- documents containing constraints

\subsection{difference between ontologies and constraints}

To make an analogy with natural language, we have words and they are 
defined in a dictionary. We also have grammars and they define how the 
words are combined. We have the general rules of grammar for ordinary 
prose. We also have other types of grammars for specialized texts such as 
poetry. There are rules for sonnets, limericks, etc. The dictionary is 
analogous to the RDFS or OWL document. The grammar is analogous to a Shape 
document.

\subsection{vocabularies/ontologies and constraints are independent}

create / maintain / control vocabularies/ontologies and constraints independently

They (and I) want one party to create and maintain a
vocabulary/ontology, while multiple other (unrelated) parties are able
to create and maintain reusable sets of constraints involving that
vocabulary (and not violating the constraints in that ontology).

difference between ontology and vocabulary

They presume something which perhaps you do not, which is that the
party which hosts the IRIs comprising a vocabulary is empowered to
maintain the definitive ontology for that vocabulary.  That's why I
wrote "vocabulary/ontology", because with this Linked Data approach, the
two go together.  I think this approach is widely accepted, although I
don't think it's explicit in any W3C Recommendation.

What I hear you saying here is that regardless of that, it's reasonable
for other people to publish/maintain what we might call a "secondary" or
"third-party" ontology, which contains axioms concerning someone else's
vocabulary.    My sense is this kind of thing is generally regarded as a
Bad Practice, although I don't offhand know why, and there might not be
any good reason.  I think I've seen people yelled at for suggesting
something like this (which doesn't necessarily mean it's a bad idea).

For my use case, I think the important thing is to be able to attach
constraints to interfaces.  To simplify somewhat, I want to say when
you're POSTing to URL U, if you want things to work properly, you MUST
include exactly one foaf:firstName on each instance of foaf:Person.

I can imagine writing that as:

    <U> eg:interfaceConstraints <UC>

and then <UC> would contain OWL of the form:

    foaf:Person owl:subClassOf [
       a owl:Restriction;
       owl:cardinality 1;
       owl:onProperty foaf:firstName
    ].

I don't really know Manchester syntax, but maybe it would be something like:

    Class: foaf:Person
       Types: foaf:firstName exactly 1

Is that how you would propose I get the functionality I want?

Somewhere I'd need to say that this OWL is to be understood with closed
world semantics, right?

Are there other problems I might have?

-----

\textbf{axioms restricting base ontologies}

It is absolutely normal to assert axioms in an ontology that restrict the models of terms in another ontology. It's an important part of ontology modularity.
Think about all the axioms that are defined on Thing and Nothing.
The key things to realize is that these axioms *only hold for that ontology*, and that statements made that are true in the restricted ontology are true in the unrestricted ontology, but not vice versa.  
*ANY* method you use to constrain the set of things that some ontology allows to exist is *BY DEFINITION* creating a new ontology using the terms of the original.

\textbf{constraints and vocabularies/ontologies are dependent}

One can argue that particular vocabularies/ontologies should permit multiple sets of constraints.  I agree with this argument.  This does not make the constraints independent of the vocabulary or ontology, however.  In fact, every example of ShEx that I have seen is very tied to a particular vocabulary.

use of OWL for validation:

(1) import base ontology + add. axioms

(2) import set of constraints (for different uses)

OWL and RDFS do not fail on this point at all.  One can use OWL and RDFS in a very flexible manner, where there is a base ontology and additional axioms.  A constraint system using OWL or RDFS can work in a similar fashion.

Even StarDog ICV can be used in this manner.  All you have to do is have an overall file that imports the base ontology and separately constraint-imports the constraints.  Different uses can have the same ontology and different constraints.  Some uses can even have just the constraints.  One could also have a trivial modification of StarDog ICV that had an extra explicit input - the constraints.

\section{constraints vs. axioms}

see R-201-SEPARATION-OF-CONSTRAINTS-AND-ONTOLOGY-SEMANTICS

\section{separate constraints and axioms}

\subsection{disjointness}

A disjointness constraint is actually different (both
semantically and in practice) from the OWL disjointness axiom. I see no
problem with adding disjointness to an AP where such disjointness is
needed in the applications that will use the AP (data creation, quality
control, documentation of your "data set"). In fact, I believe I have
seen such constraints being used in validation functions that use
SPARQL, and it doesn't seem to be a problem. As we know (and Tom and I
will show some examples in Austin), disjointness in the open world can
be ill-advised precisely because it does not mean the same as
disjointness in the closed world. In the closed world it may be a common
requirement; in the open world it can greatly interfere with data
compatibility. The same is true of cardinality (which has a very
different meaning in the open world).

I do not see APs as duplicating the OWL axioms -- although the natural
language terms we use may be the same, the functionality is quite different.

Obviously, this is what we need to keep in mind as we go through our use
cases. I don't know what problems might arise when we get into the details.

\section{Diskussionen}

Man müsste mit der Behauptung "vollständig gegen OWL 2 Konstrukte"
vorsichtig sein, in einer gewissen Lesart von Vollständigkeit bist du
vielleicht nicht vollstädnig. Überprüfts du auch so Sachen, die sich
durch folgende Konmbination an Axiomen und Assertions ergeben? Hier ein
Beispiel.

\begin{align*}

(1) \exists teachesStudent.\top \sqsubseteq TeacherUniversity

(2) TeacherUniversity \sqsubseteq EmployeeUniversity

(3) EmployeeUniversity \sqsubseteq \neg EmployeeCompany

(4) teachesStudent(eckert,schmidt)

(5) EmployeeCompany(eckert)

(1)+4) = (6) TeacherUniversity(eckert)

(6) + (2) = (7) EmployeeUniversity(eckert)

(7) + (3) = (8) \neg EmployeeCompany(eckert)
\end{align*}

(8) und (5) sind im direkten Widerspruch. Das Problem ist hier dass
Reasoning und Constraints sozusagen zusammenarbeiten, und mir ist kein
Ansatz bekannt, der das Reasoning für OWL 2 in Query Rewriting erledigen
kann.

Aber vielleicht wird das Beispiel ja tatsächlich von deinem Ansatz
erwischt (tatsächlichkann man etwas definieren, was für dieses Beispiel
vollständig ist = etwas was für DL lite vollständig ist, wenn ich grade
nix falsch sehe).

\section{Validation in RDF, XML, and Relational Worlds}

\subsection{Similarities}

\subsection{Differences}

\textbf{Difference between XML world and RDF world}
XML document with correct syntax->Well-formed

XML document with correct syntax and accomplishing with a DTD|XML Schema->Well-formed and Valid

check if a RDF graph is "well formed" (RDF syntax, etc.)

check if the RDF graph is *valid* under a certain taste RDFS, OWLx, etc. (integrity and cardinality constraints, etc with a reasoner, SPIN, etc.) (for instance cardinality of properties and data types)

\section{Related Work}

\begin{itemize}
	\item See e.g. chapter 6 of Jiao Tao's dissertation - http://tw.rpi.edu/web/doc/JiaoTaoDissertation .
\end{itemize}

\textbf{CWA.}

alternate semantics for OWL (using CWA):

Several years ago Evren Siren et al proposed an alternate semantics for OWL (using CWA) so that it could be used for integrity constraint (IC) checking and this is implemented in the Stardog database.

However, this OWL IC semantics was never submitted to a standards organization.

\subsection{validate XHTML+RDFa}

\url{https://code.google.com/p/rdf-rule-validator/}
Idea of this validator was to point out invalid class or property in XHTML+RDFa document structure. We implemented extension to owl based on CCTS metamodel to model documents in social welfare. We also did workshop paper to ESWC 2011:
\url{http://link.springer.com/chapter/10.1007/978-3-642-25953-1_19}

\section{Conclusion and Future Work}

\bibliography{../../literature/literature}{}
\bibliographystyle{plain}
\setcounter{tocdepth}{1}
%\listoftodos
\end{document}

### 2015-04-29 paper/paper7/paper7-appendix.tex
Revert "Language Improvement in Paper 2"
This reverts commit 970632ac38c80aacbc178530c32b0c1e1a48fbad.

@@
 Requirements are classified to provide a high-level view on different solutions and to facilitate a better understanding of the problem domain.
-Bosch et al. identified in total 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
+Bosch et al. identified in total 76 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
 They recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which they explain each requirement (constraint type) in detail and give examples for each (represented by listed constraint languages) \cite{BoschNolleAcarEckert2015}.
@@
 Thus, reasoners may be used prior to the validation to infer implicit triples which may resolve or cause constraint violations.
-$\mathcal{C}_{T}$ constraint types are marked with the superscript\textsuperscript{T}.
+$\mathcal{C}_{T}$ constraint types are marked with the superscript\textsuperscript{B}.
 As $\mathcal{C}_{T}$ and $\mathcal{C}_{C}$ are disjoint sets, $\mathcal{C}_{C}$ constraint types are not explicitly marked.
@@
 
-\subsection{Subsumption*\textsuperscript{T}}
+\subsection{Subsumption*\textsuperscript{B}}
 
@@
 
-\subsection{Class Equivalence*\textsuperscript{T}}
+\subsection{Class Equivalence*\textsuperscript{B}}
 
@@
 
-\subsection{Sub Properties*\textsuperscript{T}}
+\subsection{Sub Properties*\textsuperscript{B}}
 
@@
 
-\subsection{Property Domains*\textsuperscript{T}}
+\subsection{Property Domains*\textsuperscript{B}}
 
@@
 
-\subsection{Property Ranges*\textsuperscript{T}}
+\subsection{Property Ranges*\textsuperscript{B}}
 
@@
 
-\subsection{Inverse Object Properties*}
+\subsection{Inverse Object Properties*\textsuperscript{B}}
 
@@
 
-\subsection{Symmetric Object Properties*}
+\subsection{Symmetric Object Properties*\textsuperscript{B}}
 
@@
 
-\subsection{Asymmetric Object Properties*\textsuperscript{T}}
+\subsection{Asymmetric Object Properties*\textsuperscript{B}}
 
@@
 
-\subsection{Reflexive Object Properties*}
+\subsection{Reflexive Object Properties*\textsuperscript{B}}
 
@@
 
-\subsection{Irreflexive Object Properties*}
+\subsection{Irreflexive Object Properties*\textsuperscript{B}}
 
@@
 
-\subsection{Class-Specific Irreflexive Object Properties*}
+\subsection{Class-Specific Irreflexive Object Properties*\textsuperscript{B}}
 
@@
 
-\subsection{Disjoint Properties\textsuperscript{T}}
+\subsection{Disjoint Properties\textsuperscript{B}}
 
@@
 
-\subsection{Disjoint Classes\textsuperscript{T}}
+\subsection{Disjoint Classes\textsuperscript{B}}
 
@@
 
-\subsection{Context-Specific Property Groups}
+\subsection{Context-Specific Property Groups\textsuperscript{C}}
 
@@
 
-\subsection{Context-Specific Inclusive OR of Properties}
+\subsection{Context-Specific Inclusive OR of Properties\textsuperscript{C}}
 
@@
 
-\subsection{Context-Specific Inclusive OR of Property Groups}
+\subsection{Context-Specific Inclusive OR of Property Groups\textsuperscript{C}}
 
@@
 
-\subsection{Recursive Queries}
+\subsection{Recursive Queries\textsuperscript{C}}
 
@@
 
-\subsection{Individual Inequality}
+\subsection{Individual Inequality\textsuperscript{B}}
 
@@
 
-\subsection{Equivalent Properties*\textsuperscript{T}}
+\subsection{Equivalent Properties*\textsuperscript{B}}
 
@@
 
-\subsection{Property Assertions}
+\subsection{Property Assertions\textsuperscript{B}}
 
@@
 
-\subsection{Data Property Facets}
+\subsection{Data Property Facets\textsuperscript{S}}
 
@@
 
-\subsection{Literal Pattern Matching}
+\subsection{Literal Pattern Matching\textsuperscript{S}}
 
@@
 
-\subsection{Negative Literal Pattern Matching}
+\subsection{Negative Literal Pattern Matching\textsuperscript{S}}
 
@@
 
-\subsection{Object Property Paths*}
+\subsection{Object Property Paths*\textsuperscript{B}}
 
@@
 
-\subsection{Intersection*}
+\subsection{Intersection*\textsuperscript{B}}
 
@@
 
-\subsection{Disjunction*}
+\subsection{Disjunction*\textsuperscript{B}}
 
@@
 
-\subsection{Negation*}
+\subsection{Negation*\textsuperscript{B}}
 
@@
 
-\subsection{Existential Quantifications*\textsuperscript{T}}
+\subsection{Existential Quantifications*\textsuperscript{B}}
 
@@
 
-\subsection{Universal Quantifications*\textsuperscript{T}}
+\subsection{Universal Quantifications*\textsuperscript{B}}
 
@@
 
-\subsection{Minimum Unqualified Cardinality Restrictions*\textsuperscript{T}}
+\subsection{Minimum Unqualified Cardinality Restrictions*\textsuperscript{B}}
 
@@
 
-\subsection{Minimum Qualified Cardinality Restrictions*\textsuperscript{T}}
+\subsection{Minimum Qualified Cardinality Restrictions*\textsuperscript{B}}
 
@@
 
-\subsection{Maximum Unqualified Cardinality Restrictions*\textsuperscript{T}}
+\subsection{Maximum Unqualified Cardinality Restrictions*\textsuperscript{B}}
 
@@
 
-\subsection{Maximum Qualified Cardinality Restrictions*\textsuperscript{T}}
+\subsection{Maximum Qualified Cardinality Restrictions*\textsuperscript{B}}
 
@@
 
-\subsection{Exact Unqualified Cardinality Restrictions*\textsuperscript{T}}
+\subsection{Exact Unqualified Cardinality Restrictions*\textsuperscript{B}}
 
@@
 
-\subsection{Exact Qualified Cardinality Restrictions*\textsuperscript{T}}
+\subsection{Exact Qualified Cardinality Restrictions*\textsuperscript{B}}
 
@@
 
-\subsection{Transitive Object Properties*}
+\subsection{Transitive Object Properties*\textsuperscript{B}}
 
@@
 
-\subsection{Context-Specific Exclusive OR of Properties}
+\subsection{Context-Specific Exclusive OR of Properties\textsuperscript{C}}
 
@@
 
-\subsection{Context-Specific Exclusive OR of Property Groups}
+\subsection{Context-Specific Exclusive OR of Property Groups\textsuperscript{C}}
 
@@
 
-\subsection{Allowed Values\textsuperscript{T}}
+\subsection{Allowed Values\textsuperscript{B}}
 
@@
 
-\subsection{Not Allowed Values}
+\subsection{Not Allowed Values\textsuperscript{B}}
 
@@
 
-\subsection{Literal Ranges}
+\subsection{Literal Ranges\textsuperscript{S}}
 
@@
 
-\subsection{Negative Literal Ranges}
+\subsection{Negative Literal Ranges\textsuperscript{S}}
 
@@
 
-\subsection{Required Properties\textsuperscript{T}}
+\subsection{Required Properties\textsuperscript{B}}
 
@@
 
-\subsection{Optional Properties\textsuperscript{T}}
+\subsection{Optional Properties\textsuperscript{B}}
 
@@
 
-\subsection{Repeatable Properties\textsuperscript{T}}
+\subsection{Repeatable Properties\textsuperscript{B}}
 
@@
 
-\subsection{Negative Property Constraints}
+\subsection{Negative Property Constraints\textsuperscript{S}}
 
@@
 
-\subsection{Individual Equality*}
+\subsection{Individual Equality*\textsuperscript{B}}
 
@@
 
-\subsection{Functional Properties*}
+\subsection{Functional Properties*\textsuperscript{B}}
 
@@
 
-\subsection{Inverse-Functional Properties*}
+\subsection{Inverse-Functional Properties*\textsuperscript{B}}
 
@@
 
-\subsection{Value Restrictions*}
+\subsection{Value Restrictions*\textsuperscript{B}}
 
@@
 
-\subsection{Self Restrictions*}
+\subsection{Self Restrictions*\textsuperscript{B}}
 
@@
 
-\subsection{Primary Key Properties}
+\subsection{Primary Key Properties*\textsuperscript{B}}
 
@@
 
-\subsection{Class-Specific Property Range*\textsuperscript{T}}
+\subsection{Class-Specific Property Range*\textsuperscript{B}}
 
@@
 
-\subsection{Class-Specific Reflexive Object Properties*}
+\subsection{Class-Specific Reflexive Object Properties*\textsuperscript{B}}
 
@@
 
-\subsection{Membership in Controlled Vocabularies.}
+\subsection{Membership in Controlled Vocabularies\textsuperscript{S}}
 
@@
 
-\subsection{IRI Pattern Matching}
+\subsection{IRI Pattern Matching\textsuperscript{S}}
 
@@
 
-\subsection{Literal Value Comparison}
+\subsection{Literal Value Comparison\textsuperscript{S}}
 
@@
 
-\subsection{Ordering}
+\subsection{Ordering\textsuperscript{C}}
 
@@
 
-\subsection{Validation Levels}
+\subsection{Validation Levels\textsuperscript{S}}
 
@@
 
-\subsection{String Operations}
+\subsection{String Operations\textsuperscript{S}}
 
@@
 
-\subsection{Context-Specific Valid Classes\textsuperscript{T}}
+\subsection{Context-Specific Valid Classes\textsuperscript{B}}
 
@@
 
-\subsection{Context-Specific Valid Properties\textsuperscript{T}}
+\subsection{Context-Specific Valid Properties\textsuperscript{B}}
 
@@
 
-\subsection{Default Values*\textsuperscript{T}}
+\subsection{Default Values*\textsuperscript{S}}
 
@@
 
-\subsection{Mathematical Operations}
+\subsection{Mathematical Operations\textsuperscript{C}}
 
@@
 
-\subsection{Language Tag Matching}
+\subsection{Language Tag Matching\textsuperscript{S}}
 
@@
 
-\subsection{Language Tag Cardinality}
+\subsection{Language Tag Cardinality\textsuperscript{S}}
 
@@
 
-\subsection{Whitespace Handling}
+\subsection{Whitespace Handling\textsuperscript{S}}
 
@@
 
-\subsection{HTML Handling}
+\subsection{HTML Handling\textsuperscript{S}}
 
@@
 
-\subsection{Conditional Properties}
+\subsection{Conditional Properties\textsuperscript{C}}
 
@@
 
-\subsection{Recommended Properties}
+\subsection{Recommended Properties\textsuperscript{S}}
 
@@
 
-\subsection{Handle RDF Collections}
+\subsection{Handle RDF Collections\textsuperscript{C}}
 
@@
 
-\subsection{Value is Valid for Datatype\textsuperscript{T}}
+\subsection{Value is Valid for Datatype\textsuperscript{B}}
 
@@
 
-\subsection{Use Sub-Super Relations in Validation\textsuperscript{T}}
+\subsection{Use Sub-Super Relations in Validation\textsuperscript{B}}
 
@@
 
-\subsection{Cardinality Shortcuts*\textsuperscript{T}}
+\subsection{Cardinality Shortcuts*\textsuperscript{B}}
 
@@
 
-\subsection{Aggregation}
+\subsection{Aggregation\textsuperscript{C}}
 
@@
 
-\subsection{Provenance}
+\subsection{Provenance\textsuperscript{S}}
 
@@
 
-\subsection{Comparison}
+\subsection{Comparison\textsuperscript{C}}
 
@@
 
-\subsection{Data Model Consistency}
+\subsection{Data Model Consistency\textsuperscript{C}}
 Is the data consistent with the intended semantics of the data model?
@@
 
-\subsection{Structure}
+\subsection{Structure\textsuperscript{C}}
 
@@
 
-\subsection{Labeling and Documentation}
+\subsection{Labeling and Documentation\textsuperscript{S}}
 
@@
 
-\subsection{Vocabulary\textsuperscript{T}}
+\subsection{Vocabulary\textsuperscript{B}}
 Vocabularies should not invent any new terms or use deprecated elements.
@@
 
-\subsection{Linked Data}
+\subsection{HTTP URI Scheme Violation\textsuperscript{S}}
 

### 2015-04-29 paper/paper7/paper7.tex
evaluation

@@
 by building the arithmetic mean over the individual vocabularies' percentage values. 
+\tb{More than 80\% of the overall approx. 55 million constraint violations are caused by \emph{QB} constraints.}
 
@@
 
-More than the half of them are $\mathcal{CT}_{B}$, nearly a third $\mathcal{CT}_{S}$, and only a sixth $\mathcal{CT}_{C}$ constraint types.
-For \emph{Disco}, \emph{QB}, and \emph{SKOS}, more than 50\% of the instantiated constraint types are $\mathcal{CT}_{B}$ constraint types 
-(for \emph{QB} even three quarters).
-\emph{Existential quantifications} (\emph{R-86}, 32.4\%, \emph{Disco}), \emph{data model consistency} (31.4\%, \emph{QB}), and \emph{structure} (28.6\%, \emph{SKOS}) are the constraint types the most constraints are instantiated from.
-Half of the overall 213 $\mathcal{CT}$ constraints are $\mathcal{CT}_{B}$ constraints (almost 40\% $\mathcal{C}_B ^{\mathcal{R}}$).
-This is not surprising as more than the half of the instantiated constraints types are $\mathcal{CT}_{B}$ constraint types.
-More than 50\% of the \emph{Disco} and \emph{QB} constraints are $\mathcal{CT}_{B}$ constraints.
-The \emph{SKOS} constraints, on the other side, are equally assigned to the three disjoint constraint type sets. 
-More than 80\% of the overall approx. 55 million constraint violations are caused by \emph{QB} constraints (see table \ref{tab:evaluation-constraint-violations}).
-The majority (86.7\%) of the constraint violations are caused by $\mathcal{CT}_{C}$ constraints and only 9\% by $\mathcal{CT}_{S}$ constraints.
-The fact that only 4\% of all constraint violations result from $\mathcal{CT}_{B}$ constraints, 
-even though, more than 50\% of all constraints are $\mathcal{CT}_{B}$ constraints,
-is an indicator that data producers achieve good data quality with respect to the constraints extracted by vocabularies.
-Two-thirds of the constraint violations, thrown for \emph{Disco} data sets, result from $\mathcal{CT}_{B}$ constraints,
-almost only $\mathcal{CT}_{C}$ constraints raised constraint violations for \emph{QB} data sets, and 
-nearly 80\% of the \emph{SKOS} constraint violations are caused by $\mathcal{CT}_{S}$ constraints.
+%More than the half of them are $\mathcal{CT}_{B}$, nearly a third $\mathcal{CT}_{S}$, and only a sixth $\mathcal{CT}_{C}$ constraint types.
+%For \emph{Disco}, \emph{QB}, and \emph{SKOS}, more than 50\% of the instantiated constraint types are $\mathcal{CT}_{B}$ constraint types 
+%(for \emph{QB} even three quarters).
+%\emph{Existential quantifications} (\emph{R-86}, 32.4\%, \emph{Disco}), \emph{data model consistency} (31.4\%, \emph{QB}), and \emph{structure} (28.6\%, \emph{SKOS}) are the constraint types the most constraints are instantiated from.
+
+Almost 1/2 of all 213 constraints and more than 50\% of the \emph{Disco} and the \emph{QB} constraints are vocabulary constraints.
+The \emph{SKOS} constraints, on the other side, are equally distributed among the three disjoint sets of constraint types. 
+\begin{hyp}
+A significant amount of 46 \% of the constraints are directly extractable from established and newly defined vocabularies. 
+\end{hyp}
+
+Nearly 1/2 of the constraint violations are caused by complex constraints, 1/3 by simple constraints, and 1/5 by vocabulary constraints.
+2/3 of the constraint violations, thrown for \emph{Disco} data sets, result from vocabulary constraints,
+almost only conplex constraints raised constraint violations for \emph{QB} data sets, and 
+nearly 80\% of the \emph{SKOS} constraint violations are caused by simple constraints.
+
+\begin{hyp}
+The fact that only 1/5 of all constraint violations result from vocabulary constraints, 
+even though, 46\% of all constraints are vocabulary constraints,
+indicates that in general data conforms to the intended syntax and semantics of vocabularies.
+\end{hyp}
+
+For established vocabularies, vocabulary constraints caused nearly 0\% of all constraint violations (e.g. only 1.777 constraint violations for \emph{QB} constraints).  
+For newly defined vocabularies, however, 2/3 of all constraint violations are raised by vocabulary constraints. 
+\begin{hyp}
+Complex constraints are met by data represented by established vocabularies but not by data represented by newly developed vocabularies. 
+\end{hyp}
+It is likely that a newly developed vocabulary is still subject of constant change, that published data may not be consistent with its current version,
+and that early adopters did not properly understand its formal specification.
+
 \begin{hyp}
@@
 \end{hyp} 
-These days, vocabulary and simple constraints can be easily, concisely, and intuitively expressed by either modeling languages (e.g., RDF, RDFS, OWL 2) or constraint languages (e.g., ShEx, ReSh, and SPIN).
-This is not the case, however, for complex constraints which still have to be expressed by plain SPARQL. 
-There is a huge motivation to extend existing constraint languages or to develop new constraint languages which enable to express complex constraints
-As a consequence, being able to express complex constraints more easily, concisely, and intuitively leads to significant improvements in data quality.
+\emph{Vocabulary} and \emph{simple constraints} can be easily, concisely, and intuitively expressed by either modeling languages (e.g., \emph{RDF}, \emph{RDFS}, \emph{OWL 2}) or constraint languages (e.g., \emph{ShEx}, \emph{ReSh}, \emph{SPIN}).
+This is not the case, however, for \emph{complex constraints} which in most cases still have to be expressed by plain \emph{SPARQL}. 
+As almost the half of all constraint violations are caused by \emph{complex constraints}, 
+data quality can be significantly improved when existing constraint languages are extended or new constraint languages are developed to express \emph{complex constraints} more easily, concisely, and intuitively.
 

### 2015-04-29 paper/paper 2/paper 2.tex
motivation
improved english and little technical change.

@@
 %%%% list of authors for the TOC (use if author list has to be modified)
-\institute{GESIS – Leibniz Institute for the Social Sciences, Germany\\
+\institute{GESIS ? Leibniz Institute for the Social Sciences, Germany\\
 \email{thomas.bosch@gesis.org},\\ 
@@
 restricts individuals of given classes to have properties of only one of multiple mutually exclusive property groups.
-\emph{Publications}, e.g., are either identified by an \emph{ISBN} and a \emph{title} (for books) or by an \emph{ISSN} and a \emph{title} (for periodical \emph{publications}), but it should not be possible to assign both identifiers to a given \emph{publication}, which can be expressed in \emph{ShEx} as follows:
+\emph{Publications} are either identified by an \emph{ISBN} and a \emph{title} (for books) or by an \emph{ISSN} and a \emph{title} (for periodical \emph{publications}), but it should not be possible to assign both identifiers to a given \emph{publication}, which can be expressed in \emph{ShEx} as follows:
 
@@
 restricts that no individual is connected by a given object property to itself \cite{Kroetzsch2012}.
-With the following \emph{irreflexive object property} constraint, e.g., one can state that individuals cannot be authors of themselves:
+With the following \emph{irreflexive object property} constraint, for instance, one can state that individuals cannot be authors of themselves:
 \begin{DL}
@@
 The \emph{primary key properties} constraint type (\emph{R-226}) is often useful to declare a given (datatype) property as the "primary key" of a class, so that a system can enforce uniqueness. 
-\emph{Books}, e.g., are uniquely identified by their \emph{ISBN} number, i.e., the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}, 
+For instance, \emph{Books} are uniquely identified by their \emph{ISBN} number, that is, the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}, 
 which can be represented by the \emph{RDF-CV} in form of a \emph{complex constraint} (see table \ref{tab:primary-key-properties-as-complex-constraints}):
@@
 We use the \emph{RDF-CV} to intermediately represent constraints in a generic way for these transformations.
-By defining mappings ($m(sc_{\alpha}), m(sc_{\beta})$) between equivalent \emph{specific constraints} and the corresponding \emph{generic constraint} (\emph{gc}) we are able to convert them automatically:
+By defining mappings between equivalent \emph{specific constraints}, and the corresponding \emph{generic constraint} (\emph{gc}) we are able to convert them automatically:
 
 \begin{DL}
-$ gc = m(sc_{\alpha}) = m(sc_{\beta}) $
+$ gc = m_1(sc_{\alpha}) = m_2(sc_{\beta}) $
 \end{DL}
@@
 We do not need to define mappings between each pair of semantically equivalent \emph{specific constraints}.
-Let's assume we are able to express a particular constraint type by 5/6/7/8/9/10 constraint languages.
+Let's assume we are able to express a particular constraint type by 5 constraint languages.
 Without the intermediate \emph{generic constraint}, we would have to define for each constraint type \emph{1} mapping for each pair of \emph{specific constraints} (expressed by different constraint languages)
-- that are \emph{\( {n \choose 2} \)} mappings (10/15/21/28/36/45 mappings).
-With an intermediate \emph{generic constraint}, however, we only need to define for each constraint type \emph{n} mappings (1 mapping for each \emph{specific constraint}) from \emph{n} \emph{specific constraints} to the corresponding \emph{generic constraint} (5/6/7/8/9/10 mappings).
+- that are \emph{\( {n \choose 2} \)} mappings which is not very helpful.
+With an intermediate \emph{generic constraint}, however, we only need to define for each constraint type \emph{n} mappings (1 mapping for each \emph{specific constraint}) from \emph{n} \emph{specific constraints} to the corresponding \emph{generic constraint}.
 
@@
 The \emph{DL} statement \ms{Publication $\equiv$ $\exists$ publisher.Publisher} is mapped to a \emph{(simple) generic constraint} conforming to the \emph{RDF-CV} (see table \ref{tab:existential-quantification-as-simple-constraints}).
-Then, one mapping (\emph{$m(sc_{OWL 2})$}, \emph{$m(sc_{ReSh})$}, \emph{$m(sc_{ShEx})$}, ...) is defined for each \emph{specific constraint} (\emph{$sc_{OWL 2}$}, \emph{$sc_{ReSh}$}, \emph{$sc_{ShEx}$}, ...) to the corresponding \emph{generic constraint} (\emph{gc}).
+Then, one mapping (\emph{$m_1(sc_{OWL 2})$}, \emph{$m_2(sc_{ReSh})$}, \emph{$m_3(sc_{ShEx})$}, ...) is defined for each \emph{specific constraint} (\emph{$sc_{OWL 2}$}, \emph{$sc_{ReSh}$}, \emph{$sc_{ShEx}$}, ...) to the corresponding \emph{generic constraint} (\emph{gc}).
 
@@
 
-We evaluated to which extend the five most promising constraint languages on being the standard fulfill each of the overall 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type.
+We evaluated to which extend the five most promising constraint languages on being the standard for fulfilling each of the overall 74 requirements to formulate RDF constraints (each corresponds to a constraint type).
 We recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} (serving as appendix of this paper) in which we explain each constraint type in detail and give examples for each (represented by different constraint languages).
 The technical report also contains mappings to \emph{DL} to logically underpin each constraint type and to determine which \emph{DL} constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
-If a constraint type can be expressed in \emph{DL}, we added the mapping to \emph{DL} and to the \emph{generic constraint} conforming to the \emph{RDF-CV}.
-In contrast, if a constraint type cannot be expressed in \emph{DL}, we only added the mapping to the \emph{generic constraint}.
-This way, we prove that each constraint type can be mapped to a \emph{generic constraint} and therefore be represented generically by means of the \emph{RDF-CV}.
+If a constraint type was expressible in \emph{DL}, we added the mapping to \emph{DL} and to the \emph{generic constraint} conforming to the \emph{RDF-CV}.
+In contrast, if a constraint type was not expressible in \emph{DL}, we only added the mapping to the \emph{generic constraint}.
+This way, we show that each constraint type can be mapped to a \emph{generic constraint} and therefore be represented generically by means of the \emph{RDF-CV}.
 Table \ref{tab:evaluation} displays the classification of constraint types according to the dimensions \emph{context}, \emph{complexity}, and \emph{DL expressivity}:
@@
 Almost two thirds of the constraint types are \emph{simple constraints} (e.g., \emph{R-55: object property paths}), a quarter are \emph{complex constraints} (e.g., \emph{R-45: ranges of literal values}), and
-nearly 15 percent are \emph{complex constraints} which can be formulated as \emph{simple constraints} when using them in terms of syntactic sugar (e.g., \emph{R-81/75/82/76/80/74: (un)qualified cardinality restrictions}).
+nearly 15 percent are \emph{complex constraints} which can be formulated as \emph{simple constraints} when used in terms of syntactic sugar (e.g., \emph{R-81/75/82/76/80/74: (un)qualified cardinality restrictions}).
 Constraint types can either be \emph{expressible in DL} or \emph{not} (\emph{DL expressivity}).

### 2015-04-29 paper/paper7/paper7.tex
evaluation

@@
 
-Data quality is not bad since only a small amount of the constraint violations are caused by error constraints
-\emph{SBE} domain experts associated almost the half of the constraints with the severity levels $\mathcal{SL}_{0}$ (\emph{informational}) (47\%) and $\mathcal{SL}_{2}$ (\emph{error}) (45\%);
-only 8.5\% are $\mathcal{SL}_{1}$ (\emph{warning}) constraints.
-The violation of 80\% of the \emph{QB} constraints is very serious ($\mathcal{SL}_{2}$).
-More than 50\% of the \emph{Disco} and \emph{SKOS} constraints, however, are assigned to the weakest default severity level ($\mathcal{SL}_{0}$).
+\begin{table}[H]
+		\scriptsize
+    \begin{center}
+    \begin{tabular}{@{}lcccccccc@{}}
+    %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
+    %\\  \cmidrule{2-3}
+		\hline
+    \multirow{2}{*}{} &
+      \multicolumn{2}{c}{\textbf{\emph{Disco}}} &
+      \multicolumn{2}{c}{\textbf{\emph{QB}}} &
+      \multicolumn{2}{c}{\textbf{\emph{SKOS}}} &
+      \multicolumn{2}{c}{\textbf{\emph{Total}}} \\
+    \textbf{} & C & CV & C & CV & C & CV & C & CV \\
+    \hline
+    %\\ \midrule
+		 & 143 & 3,575,002 & 35 & 45,635,861 & 35 & 5,540,988 & 213 & 54,751,851 \\
+		\hline
+		\textbf{\emph{complex}} & 25.9\% & 18.3\% & 37.1\% & \textbf{100\%} & \textbf{37.1\%} & 21.4\% & 33.4\% & \textbf{46.6\%} \\
+		\textbf{\emph{simple}} & 19.6\% & 15.7\% & 8.6\% & 0.0\% & \textbf{34.3\%} & \textbf{78.6\%} & 20.8\% & 31.4\% \\
+		\textbf{\emph{vocabulary}} & \textbf{54.6\%} & \textbf{66.1\%} & \textbf{54.3\%} & 0.0\% & \textbf{28.6\%} & 0.0\% & \textbf{45.8\%} & 22.0\% \\
+		%\hline
+		%\emph{CV (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 2,333,365 (65.3\%) & 1,777 (0\%) & 0 (0\%) & 2,335,142 (4.3\%) \\
+		%\emph{CV (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 28,000 (0.8\%) & 0 (0\%) & 0 (0\%) & 28,000 (0.1\%) \\
+		\hline
+		\textbf{\emph{info}} & \textbf{52.5\%} & \textbf{52.6\%} & 11.4\% & 0.0\% & \textbf{60.0\%} & 41.2\% & \textbf{41.3\%} & 31.3\% \\
+		\textbf{\emph{warning}} & 7.0\% & 29.4\% & 8.6\% & \textbf{99,8\%} & 14.3\% & \textbf{58.8\%} & 10.0\% & \textbf{62.7\%} \\
+		\textbf{\emph{error}} & 40.6\% & 18\% & \textbf{80.0\%} & 0.3\% & 25.7\% & 0.0\% & \textbf{48.8\%} & 6.1\%\\
+    \bottomrule
+    \end{tabular}
+    \\ \emph{C (constraints), CV (constraint violations)}
+    \caption{Constraints and Constraint Violations}
+		\label{tab:evaluation-constraint-violations}
+    \end{center}
+\end{table}
+
+63\% of all constraint violations are caused by warning constraints which are only 10\% of all constraints. 
+Only 6\% of the constraint violations are caused by error constraints which are 49\% of all constraints.
+
+\begin{hyp}
+Data quality is good since only 6\% of the constraint violations are caused by error constraints which are 49\% of all constraints.
+\end{hyp}
+
+80\% of the \emph{QB} constraints are error constraints.
+More than 50\% of the \emph{Disco} and \emph{SKOS} constraints, however, are informational constraints.
+
 For Disco, 1/6 of the constraint violations are serious.

### 2015-04-29 paper/paper7/paper7.tex
evaluation

@@
 Data quality is good since only 6\% of the constraint violations are caused by error constraints which are 49\% of all constraints.
+The percentage of severe constraint violations is very low, compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
 \end{hyp}
@@
 More than 50\% of the \emph{Disco} and \emph{SKOS} constraints, however, are informational constraints.
-
-For Disco, 1/6 of the constraint violations are serious.
-Although, only 8.5\% of all constraints are $\mathcal{SL}_{1}$ constraints,
-9 0f 10 constraint violations are caused by constraints associated with the default severity level $\mathcal{SL}_{1}$.
-More than 50\% of all constraint violations thrown for \emph{Disco} data sets are not seen to be that significant ($\mathcal{SL}_{0}$).
-Almost all constraint violations raised by \emph{QB} constraints and 59\% of the constraint violations caused by \emph{SKOS} constraints are classified as warnings ($\mathcal{SL}_{1}$).  
-As this evaluation serves as indication for \emph{good} or \emph{bad} (meta)data quality, 
-we conclude that
-the metadata quality of all evaluated \emph{Disco} data sets is \emph{good} and that the metadata quality of all evaluated \emph{QB} and \emph{SKOS} data sets is \emph{satisfactory}.
+For Disco, 1/6 of the constraint violations are caused by error constraints.
+Almost all constraint violations raised by \emph{QB} constraints and 59\% of the constraint violations caused by \emph{SKOS} constraints are warnings.  
 \begin{hyp}
@@
 as serious constraint violations occur partially.
+\end{hyp}
+
+\begin{hyp}
 For well-established vocabularies, the explicitly defined constraints are almost completely satisfied which demonstrates that constraint formulation in general works.
-\end{hyp}
-
-\begin{hyp}
-The percentage of severe constraint violations is very low, compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
 \end{hyp}

### 2015-04-29 paper/paper7/paper7.tex
evaluation

@@
 \begin{hyp}
-More than the half of the vocabulary constraints are associated with the severity level error and
-more than 3/4 of the simple constraints are only informational constraints. 
+More than the 1/2 of the vocabulary constraints are error constraints,
+more than 3/4 of the simple constraints are informational constraints, and
+complex constraints are either informational or error constraints. 
 \end{hyp}
+
+As vocabulary constraints are directly extractable from vocabularies and therefore ensure the syntax and semantics of vocabularies,
+violations of vocabulary constraints are more severe than violations caused by simple constraints which are easily defined in addition to vocabulary constraints.
+In many cases, complex constraints are also needed to express severe constraints which cannot be expressed by modeling languages.
+The relation between complexity and severity shows the importance to develop constraint languages
 

### 2015-04-29 paper/paper7/paper7.tex
evaluation
section 4

@@
 Therefore, this technical report contains mappings to \emph{DL} to logically underpin each requirement and to determine which \emph{DL} constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
-
-We developed a system to classify both RDF constraint types and RDF constraints to evaluate the quality of metadata and data which may be represented by any vocabulary.
+We classified both RDF constraint types and RDF constraints to evaluate the quality of metadata and data which may be represented by any vocabulary.
 %Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
-We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as first appendix of this paper) in which we describe 213 constraints of 53 distinct constraint types
-to validate tabular data (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), and thesauri (\emph{SKOS}).
-By applying the proposed classification system to several vocabularies to represent both metadata and data, we prove its generality \cite{BoschZapilkoWackerowEckert2015}.
+We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as first appendix of this paper) in which we describe 246 constraints of 53 distinct constraint types on six vocabularies \cite{BoschZapilkoWackerowEckert2015}.
 
@@
 In many cases, complex constraints are also needed to express severe constraints which cannot be expressed by modeling languages.
-The relation between complexity and severity shows the importance to develop constraint languages
+The relation between complexity and severity shows the importance to develop constraint languages which are enable to express severe complex constraints.
 

### 2015-04-29 paper/paper7/paper7.tex
Some notes

--- 2015-04-29 paper/paper7/paper7.tex
@@
 %\title{RDF Constraints to Ensure High Quality \\ of Metadata and Data}
-\title{RDF Constraint Types to Ensure High Data Quality}
+\title{Aspects of RDF Data Constraints in the Social, Behavioural and Economic Sciences}
 \subtitle{}
@@
 
-Based on the results, we postulate three important findings: (1) A significant amount of 47\% of the violations refer to complex constraints that are not easily expressible in existing languages which confirms the necessity to provide suitable constraint languages.
-(2) For well-established vocabularies, the explicitly defined constraints are almost completely satisfied which demonstrates that constraint formulation in general works.
+Based on the results, we postulate and discuss findings, like: (1) for well-established vocabularies, the explicitly defined constraints are almost completely satisfied which demonstrates that constraint formulation in general works.
+(2) A significant amount of 47\% of the violations refer to complex constraints that are not easily expressible in existing languages which confirms the necessity to provide suitable constraint languages.
 (3) The percentage of severe constraint violations is very low, compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
@@
 Increasingly, data professionals, data archives, data libraries, government statisticians (e.g. \url{data.gov}, \url{data.gov.uk}), and national statistical institutes
-are very interested in having their data be discovered and used by exposing their metadata (e.g. about unemployment rates or income) within the Web of Linked Data.
+are very interested in having their data be discovered and used by exposing their metadata (e.g.
+about unemployment rates or income\ke{wieso ist das metadata?
+Ich würde generell auch im text bei data bleiben, es sei denn, die unterscheidung von data und metadata ist relevant.}) within the Web of Linked Data.
 As \emph{DDI} XML documents are validated against diverse XSDs\footnote{\label{fnt:DDI-XSDs}\url{http://www.ddialliance.org/Specification/}} (see section \ref{related-work}),
@@
 
+\ke{in guter tradition unserer arbeitsgruppe würde ich mich als senior researcher um die einleitung kümmern, die gefällt mir so nicht}
+
 \section{Motivation}
@@
 Aggregated data is more and more published in form of CSV files,
-allowing to perform data calculations.
+allowing to perform data calculations.\ke{abgeshen davon dass ich more and more nicht mehr sehen kann, ist der zusammenhang mit RDF daten und damit RDF providern im nächsten satz unklar}
 %For these calculations, definitions of the columns are needed (e.g. is a given variable interpreted numerically or as a string).
@@
 Portals harvest metadata (as well as publicly available data) from multiple RDF data providers.
-To ensure high quality, (meta)data must satisfy certain criteria - specified in terms of RDF constraints.
+To ensure high quality, (meta)data must satisfy certain criteria - specified in terms of RDF constraints.\ke{verwirrend.
+wie gesagt, können wir nicht bei RDF data bleiben?
+was anderes behandelt ihr doch eh nicht und qb enthält doch keine metadaten.}
 
@@
 i.e., the violation of the first three constraints is more serious than the violation of the last constraint.
-If the intention of the researcher is to perform more sophisticated comparisons (use case 2), however, the user may raise the severity level of last constraint.
+If the intention of the researcher is to perform more sophisticated comparisons (use case 2), however, the user may raise the severity level of the last constraint.
+
+\ke{ich finde das immer noch recht verwirrend.
+Ist das mit den aggregierten Daten wichtig für dieses Paper?
+Wieso werden constraints nur gechecked wenn variablen auf vergleichbarkeit geprüft werden?
+das habt ihr doch gar nicht gemacht sondern ganz allgemein constraints für vokabulare aufgestellt.
+Ist QB und Disco nicht sowieso unabhängig von konkreten Variablen?}
 
@@
 %\label{running-example}
-\section{Vocabularies to Represent Metadata and Data in RDF}
+\section{Vocabularies to Represent Metadata and Data in RDF\ke{ganz schlechte überschrift... vorschlag: Examined Vocabularies oder Common Vocabularies in SBE sciences}}
 \label{rdf-representation}
@@
 %In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.
+
+For our evaluation, we examined four different vocabularies commonly used in or developed for the SBE sciences which are briefly introduced in the following.
+For three of them, we analysed actual data according to constraint violations.
+For PHDD, there is not yet enough data available so we limit our examination to the vocabulary itself.\ke{Neuer Absatz von mir...}
 
@@
 %(e.g., the year in which \emph{formal childcare} has been determined).
+\ke{Wieso springt das von einer sehr knappen Einführung direkt zu konkreten (beliebigen?) Variablen?
+Ich möchte wissen, wofür QB benutzt wird und gerne ein konkretes Beispiel sehen, um mir einen Data Cube vorstellen zu können.}
 
@@
 %This includes data documentation at the study and variable level as well as documentation materials, tools and further information. 
+\ke{Wieso jetzt wieder qb?}
 Aggregated (qb:DataSet) and underlying person-level data sets (\emph{disco:LogicalDataSet}) are connected by \emph{prov:wasDerivedFrom}. 

### 2015-04-29 paper/paper7/paper7.tex
section 4

--- 2015-04-29 paper/paper7/paper7.tex
@@
 
-According to the complexity of constraint types, the complete set of \emph{constraint types} ($\mathcal{CT}$) encompasses three disjoint \emph{sets of constraint types}:
+According to the complexity of constraint types, the complete set of \emph{constraint types} encompasses three disjoint \emph{sets of constraint types}:
 \begin{enumerate}
-	\item $\mathcal{CT}_{B}$: \textbf{\emph{Basic Constraint Types}}
-	\item $\mathcal{CT}_{S}$: \textbf{\emph{Simple Constraint Types}}
-	\item $\mathcal{CT}_{C}$: \textbf{\emph{Complex Constraint Types}}
+	\item \textbf{\emph{Vocabulary Constraint Types}}
+	\item \textbf{\emph{Simple Constraint Types}}
+	\item \textbf{\emph{Complex Constraint Types}}
 \end{enumerate}
@@
 The modeling languages \emph{RDF}, \emph{RDFS}, and \emph{OWL} are typically used to define vocabularies.
-\emph{Basic constraint types} ($\mathcal{CT}_{B}$) 
+\emph{Vocabulary constraint types}
 denotes the set of constraint types whose constraints 
-can be extracted completely automatically out of vocabularies.
+can be extracted completely automatically out of the formal specifications of vocabularies.
 As vocabularies have been specified using \emph{RDF}, \emph{RDFS}, and \emph{OWL},
-\emph{basic constraints} ensure that the data is consistent with the intended syntaxes, semantics, and integrity of vocabularies' data models.
+\emph{vocabulary constraints} ensure that the data is consistent with the intended syntaxes, semantics, and integrity of vocabularies' data models.
 %The {\em existential quantification} (\emph{R-86}) 
@@
 
-\emph{Simple constraint types} ($\mathcal{CT}_{S}$) is the set of constraint types whose constraints can be easily defined without much effort in addition to $\mathcal{CT}_{B}$ constraints.
-{\emph{Data property facets} (\emph{R-46}) is an example of an $\mathcal{CT}_{S}$ constraint type which enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
+\emph{Simple} and \emph{complex constraints} are in contrast to \emph{vocabulary constraints} not explicitly defined within formal specifications of vocabularies.
+\emph{Simple} and \emph{complex constraints} are defined according to textual descriptions of the intended semantics of vocabularies.  
+\emph{Simple constraint types} is the set of constraint types whose constraints can be easily defined without much effort in addition to \emph{vocabulary constraints}.
+{\emph{Data property facets} (\emph{R-46}) is an example of a \emph{simple constraint type} which enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
 The abstract of series/studies, e.g., should have a minimum length.
 
-\emph{Complex constraint types} ($\mathcal{CT}_{C}$) encompass constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
-Complex constraints show the importance of constraint languages enabling to describe more complex constraints.
+\emph{Complex constraint types} encompass constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
 For assessing the quality of thesauri, e.g., we concentrate on the graph-based structure and apply graph- and network-analysis techniques.
@@
 a thesaurus should not contain many orphan concepts, i.e., concepts without any associative or hierarchical relations, lacking context information valuable for search. 
+\emph{Complex constraints} show the importance to develop constraint languages enabling to describe more complex constraints.
 
@@
 
-\emph{SBE} experts determined the default \textbf{\emph{severity level}} (\emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.\tb{of the 213 constraints}
-We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ to $\mathcal{SL}_{2}$.
-According to the constraints' default severity level the complete set of constraints ($\mathcal{C}$) encompasses three disjoint \emph{sets of constraints}:
+\emph{SBE} experts determined the default \textbf{\emph{severity level}} (\emph{R-158}) for each of the 246 constraints to indicate how serious the violation of the constraint is.
+We propose an extensible metric to measure the continuum of severity levels ranging from \emph{informational} to \emph{error}.
+According to the constraints' default severity level, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:
 \begin{itemize}
-	\item $\mathcal{SL}_{0}$: set of constraints with \textbf{severity level \emph{informational}}
-	\item $\mathcal{SL}_{1}$: set of constraints with \textbf{severity level \emph{warning}}
-	\item $\mathcal{SL}_{2}$: set of constraints with \textbf{severity level \emph{error}}
+	\item \textbf{\emph{informational constraints}}: constraints with severity level {\emph{informational}
+	\item \textbf{\emph{warning constraints}}: constraints with severity level \emph{warning}
+	\item \textbf{\emph{error constraints}}: constraints with severity level \emph{error}
 \end{itemize}
-Violations of $\mathcal{SL}_{0}$ constraints point to desirable data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies. 
-Data not conforming to $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is syntactically and/or semantically not correctly represented.
-The difference between $\mathcal{SL}_{1}$ and $\mathcal{SL}_{2}$ constraints is that data, not conforming to $\mathcal{SL}_{1}$ but conforming to $\mathcal{SL}_{2}$ constraints, could be processed further,
-whereas data, not corresponding to $\mathcal{SL}_{2}$ constraints, cannot be processed further after validation. 
-As constraints of $\mathcal{CT}_{B}$ constraint types are derived from explicitly stated semantics of vocabularies, 
-their default severity levels are in most cases very strong ($\mathcal{SL}_{2}$) and 
-in average stronger than the severity levels of constraints assigned to $\mathcal{CT}_{S}$ and $\mathcal{CT}_{C}$ constraint types.
-As a consequence, violating many constraints of $\mathcal{CT}_{B}$ constraint types is an indicator for bad (meta)data quality\footnote{For simplicity reasons, we only assign severity levels to $\mathcal{CT}_{B}$ constraints in this paper in case they differ from $\mathcal{SL}_{2}$.}.
+Violations of \emph{informational constraints} point to desirable but not necessary data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies.
+Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
+The difference between \emph{warning} and \emph{error constraints} constraints is that data, not conforming to \emph{warning constraints} but conforming to \emph{error constraints}, could be processed further,
+whereas data, not corresponding to \emph{error constraints}, cannot be processed further after validation. 
+As constraints of \emph{vocabulary constraint types} are derived from explicitly stated semantics of vocabularies, 
+their default severity levels are in most cases very strong (\emph{error}) and 
+in average stronger than the severity levels of constraints assigned to \emph{simple and complex constraint types}.
+As a consequence, violating many constraints of \emph{vocabulary constraint types} is an indicator for bad (meta)data quality\footnote{For simplicity reasons, we only assign severity levels to \emph{vocabulary constraints} in this paper in case they differ from \emph{error constraints}.}.
 

### 2015-04-29 paper/paper7/paper7.tex
section 4

@@
 We propose an extensible metric to measure the continuum of severity levels ranging from \emph{informational} to \emph{error}.
-According to the constraints' default severity level, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:
+According to the default severity level of constraints, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:
 \begin{itemize}
@@
 Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
-The difference between \emph{warning} and \emph{error constraints} constraints is that data, not conforming to \emph{warning constraints} but conforming to \emph{error constraints}, could be processed further,
-whereas data, not corresponding to \emph{error constraints}, cannot be processed further after validation. 
-As constraints of \emph{vocabulary constraint types} are derived from explicitly stated semantics of vocabularies, 
+Data not conforming to \emph{warning constraints} but to \emph{error constraints} could be processed further.
+Data not corresponding to \emph{error constraints}, however, cannot be processed further after validation. 
+As the purpose of \emph{vocabulary constraints} is to ensure explicitly stated semantics of vocabularies, 
 their default severity levels are in most cases very strong (\emph{error}) and 
-in average stronger than the severity levels of constraints assigned to \emph{simple and complex constraint types}.
-As a consequence, violating many constraints of \emph{vocabulary constraint types} is an indicator for bad (meta)data quality\footnote{For simplicity reasons, we only assign severity levels to \emph{vocabulary constraints} in this paper in case they differ from \emph{error constraints}.}.
-
-Although, we provide default severity levels for each constraint, validation environments should enable users to adapt constraints' severity levels according to their individual needs.
+in average stronger than the severity levels of \emph{simple} and \emph{complex constraints}.
+As a consequence, violating many \emph{vocabulary constraints} is an indicator for bad (meta)data quality\footnote{For simplicity reasons, we only assign severity levels to \emph{vocabulary constraints} in this paper in case they differ from \emph{error constraints}.}.
+
+Although, we provide default severity levels for each constraint, validation environments should enable users to adapt the severity levels of constraints according to their individual needs.
 Validation environments should enable users to select which constraints to validate against depending on their individual use cases.
 For some use cases, 
-validating constraints of $\mathcal{CT}_{B}$ constraint types may be more important than validating constraints of $\mathcal{CT}_{S}$ or $\mathcal{CT}_{C}$ constraint types.
+validating \emph{vocabulary constraints} may be more important than validating \emph{simple} or \emph{complex constraints}.
 For other use cases,
-validating $\mathcal{SL}_{2}$ constraints may be sufficient without taking $\mathcal{SL}_{1}$ and $\mathcal{SL}_{0}$ constraints into account.
+validating \emph{error constraints} may be sufficient without taking \emph{warning} and \emph{informational constraints} into account.
 We evaluated the (meta)data quality of large real world data sets represented by multiple and different vocabularies to get an understanding  

### 2015-04-29 paper/paper7/paper7.tex
section 4

--- 2015-04-29 paper/paper7/paper7.tex
@@
 \begin{itemize}
-	\item \textbf{\emph{informational constraints}}: constraints with severity level {\emph{informational}
+	\item \textbf{\emph{informational constraints}}: constraints with severity level \emph{informational}
 	\item \textbf{\emph{warning constraints}}: constraints with severity level \emph{warning}
@@
 
-\section{Basic Constraint Types}
-\label{basic-constraint-types}
-
-As \emph{RDFS} and \emph{OWL} are typically used to define vocabularies, \emph{RDFS} and \emph{OWL} reasoning may be performed prior to validation. 
-Reasoning and validation are indeed very closely related. 
-\emph{Reasoning} is the process of determining what follows from what has been stated.
-%Both should be possible: (1) validation with reasoning and (2) validation without reasoning. 
-We divide the whole set of \emph{basic constraint types} ($\mathcal{CT}_{B}$) into two disjoint sets to investigate the affect of reasoning to the validation process: 
-\begin{enumerate}
-	\item $\mathcal{C}_B ^{\mathcal{R}}$ corresponds to axioms in \emph{OWL 2} and denotes the set of constraint types which enable performing reasoning prior to validation, especially when not all the knowledge is explicit (section \ref{basic-constraint-types-with-reasoning}).
-  \item $\overline{\mathcal{C}_B ^{\mathcal{R}}}$  denotes the set of constraint types for which reasoning cannot be done or does not improve the result in any obvious sense (section \ref{basic-constraint-types-without-reasoning}).
-\end{enumerate}
-
-\subsection{Basic Constraint Types with Reasoning}
-\label{basic-constraint-types-with-reasoning}
-
-Validation environments should enable users to decide if they wish to perform reasoning prior to validation.
-Reasoning as an optional pre validation step is beneficial for RDF validation as 
-(1) it may resolve constraint violations and  
-(2) it may cause useful constraint violations.
-A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
-%Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets}:
-%\begin{DL}
-%Catalog $\sqsubseteq$ $\forall$ dataset.Dataset
-%\end{DL}
-Consider the following DL knowledge base $\mathcal{K}$\footnote{A knowledge base is a collection of formal statements which corresponds to \emph{facts} or what is known explicitly.
-For simplicity reasons, we only write namespace prefixes in DL statements to avoid ambiguities.}:
-
-\begin{center}
-\begin{DL} 
-$\mathcal{K}=\{$ &\ms{LogicalDataSet $\sqsubseteq$ dcat:DataSet},\\
- &\ms{LogicalDataSet $\sqsubseteq \forall$ aggregation.qb:DataSet},\\
- %&\ms{dcat:DataSet $\equiv$ $\exists$ dcat:distribution . dcat:Distribution},\\
- &\ms{LogicalDataSet( logical-data-set )},\\
- &\ms{aggregation( logical-data-set, aggregated-data-set )}
- \}\\ 
-\end{DL}
-\end{center}
-
-As we know that only person-level data sets (\emph{disco:LogicalDataSet}) can derive (\emph{disco:aggregation}) aggregated data sets (\emph{qb:DataSet}), 
-{\em logical-data-set} is a \emph{disco:LogicalDataSet}, 
-and \emph{aggregated-data-set} is derived from \emph{logical-data-set},
-we conclude that \emph{aggregated-data-set} must be a \emph{qb:DataSet}.
-As \emph{aggregated-data-set} is not explicitly defined to be a \emph{qb:DataSet}, however, a constraint violation is raised.
-If we perform reasoning prior to validation, the constraint violation is resolved, as the implicit triple \ms{qb:DataSet(aggregated-data-set)} is inferred.
-
-Reasoning may also cause constraint violations which are needed to enhance data quality.
-With \emph{subsumption} (\emph{R-100}), one can state that \emph{disco:LogicalDataSet} is a sub-class of \emph{dcat:DataSet}, 
-i.e., each person-level data set is also a catalog data set.
-Thus, constraints on catalog data sets are also validated for person-level data sets;
-e.g., the \emph{existential quantification} below restricting that person-level data sets must have a distribution:
-
-\begin{center}
-\begin{DL} 
-$\mathcal{K}=\{$ 
- &\ms{DataSet $\equiv$ $\exists$ distribution.Distribution},\\
-&\ms{Variable $\equiv$ $\exists$ concept.Concept}
- \}\\ 
-\end{DL}
-\end{center}
-
-We extend $\mathcal{K}$ by \emph{existential quantifications} (\emph{R-86}) enforcing that instances of given classes must have some property relation to individuals/literals of certain types.
-Variables, e.g., should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
-%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
-The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
-The default severity level of the constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
-%If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
-%If metadata on data files, including the actual data, is missing (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the study is not sufficient.
-%Case quantity measures how many cases are collected for a study.
-%High case and variable quantities are indicators for high statistical quality and comprehensiveness of the underlying study ($\mathcal{SL}_{1}$).
-
-\begin{center}
-\begin{DL} 
-$\mathcal{K}=\{$ 
-  &\ms{fundedBy $\sqsubseteq$ contributor}
- \}\\ 
-\end{DL}
-\end{center}
-
-By stating that \emph{disco:fundedBy} is a sub property of \emph{dcterms:contributor},
-the {\em sub property} (\emph{R-54, R-64}) above assures that if a series is funded by an organization, then the organization must also contribute to the series.
-In case the \emph{sub-property} is applied without reasoning and $\mathcal{K}$ contains the triple \ms{disco:fundedBy} \ms{(EU-SILC,} \ms{organization)},
-a constraint violation is thrown if $\mathcal{K}$ does not explicitly include the triple \ms{dcterms:contributor} \ms{(EU-SILC,} \ms{organization)}.
-If the \emph{sub property} is applied with reasoning, on the other side, the latter triple is derived which resolves the constraint violation.
-
-%\begin{DL}
-%fundedBy $\sqsubseteq$ contributor
-%\end{DL}
-
-%\emph{Asymmetric object properties} (\emph{R-62}) restrict that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}.
-%Such constraints are defined for each object property for which a semantically equivalent object property pointing from the other direction would also be possible but is not defined within the vocabulary.
-%A \emph{disco:Variable}, e.g., may be based on (\emph{disco:basedOn}) a \emph{disco:RepresentedVariable}.
-%A \emph{disco:RepresentedVariable}, however, cannot be based on a \emph{disco:Variable} (\ms{$disco:basedOn \sqcap disco:basedOn^{-} \sqsubseteq \bot$}).
-
-%\emph{Property domain} (\emph{R-25, R-26}) and \emph{range} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties.
-%Only \emph{phdd:Tables}, e.g., can have \emph{phdd:isStructuredBy} relationships and
-%\emph{xkos:belongsTo} relationships can only point to \emph{skos:Concepts}:
-%\begin{DL}
-%$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table \\
-%$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept
-%\end{DL}
-
-%\begin{center}
-%\begin{DL} 
-%$\mathcal{K}=\{$ 
-  %&\ms{TableStructure $\sqsubseteq$ $\geq$1 column.Column}, \\
-	%&\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}, \\
-	%&\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition} \\ 
-	%&\ms{$\sqcap$ $\leq$1 structure.DataStructureDefinition}
- %\}\\ 
-%\end{DL}
-%\end{center}
-
-%\textbf{Cardinality Restrictions on Properties.}
-%An \emph{existential quantification} (\emph{R-86}) contains all those individuals that are connected by a property to individuals/literals of given classes or data ranges.
-%Every \emph{qb:SliceKey}, e.g., must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}).
-%\emph{Minimum/maximum/exact qualified cardinality restrictions} (\emph{R-74, R-75, R-76}) contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals of particular classes or data ranges.
-%A \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column},
-%a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}), and a \emph{qb:DataSet} is structured by (\emph{qb:structure}) exactly one \emph{qb:DataStructureDefinition}.
-%DATA-CUBE-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-
-%02: Unique data set (IC-1 [3]) - Every qb:Observation has (qb:dataSet) ex-
-%actly one associated qb:DataSet (Observation  ¥1 dataSet.DataSet [
-%¤1 dataSet.DataSet).
-%Severity level: ERROR
-%
-%(\emph{R-75: minimum qualified cardinality restrictions})
-%
-%DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-
-%02: Unique DSD (IC-2 [3]) - Every qb:DataSet has (qb:structure) exactly one
-%associated qb:DataStructureDefinition (DataSet  ¥1 structure.DataStructureDefinition
-%[ ¤1 structure.DataStructureDefinition).
-%Severity level: ERROR
-%
-%(\emph{R-74: exact qualified cardinality restrictions})
-%\footnote{\emph{DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02}}.
-%\textbf{Language Tag Cardinality.}
-
-\subsection{Basic Constraint Types without Reasoning}
-\label{basic-constraint-types-without-reasoning}
-
-$\overline{\mathcal{C}_B ^{\mathcal{R}}}$  denotes the set of constraint types for which reasoning cannot be done or does not improve the result in any obvious sense.
+\section{Vocabulary Constraint Types}
+\label{vocabulary-constraint-types}
+
 The constraint type \emph{vocabulary} guarantees that users do not invent new or use deprecated terms of vocabularies.
@@
 \emph{Value is valid for datatype} (\emph{R-223}) constraints serve to make sure that all literal values are valid with regard to their datatypes - as stated in the vocabularies.
-Thus, it is checked that all date values (e.g., {{\em dcterms:date}, \em disco:startDate}, {\em disco:endDate}) are actually of the datatype \emph{xsd:date} and that \emph{xsd:nonNegativeInteger} values (e.g.
+Thus, it is checked that all date values (e.g., {{\em dcterms:date}) are actually of the datatype \emph{xsd:date} and that \emph{xsd:nonNegativeInteger} values (e.g.
 \emph{disco:frequency}) are not negative.
@@
 \end{center}
-
+\tb{K einführen}
 All properties, not having the same domain and range types, are defined to be pairwise disjoint
@@
 Validation should \emph{exploit sub-super relations} in vocabularies (\emph{R-224}).
-If \emph{dcterms:coverage} and one of its sub-properties (\emph{dcterms:spatial}, \emph{dcterms:temporal}) are given,
+If \emph{dcterms:coverage} and one of its sub properties (\emph{dcterms:spatial}, \emph{dcterms:temporal}) are given,
 it is checked that \emph{dcterms:coverage} is not redundant with its sub-properties 
 which may indicate when the data is verbose/redundant or expressed at a too general level.
+
+-----
+
+\emph{Property domain} (\emph{R-25, R-26}) and \emph{range} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties.
+Only \emph{phdd:Tables}, e.g., can have \emph{phdd:isStructuredBy} relationships and
+\emph{xkos:belongsTo} relationships can only point to \emph{skos:Concepts}:
+\begin{DL}
+$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table \\
+$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept
+\end{DL}
+
+A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
+Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets}:
+\begin{DL}
+Catalog $\sqsubseteq$ $\forall$ dataset.Dataset
+\end{DL}
+
+%\textbf{Existential Quantifications.}
+\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals/literals of certain types.
+Variables, e.g., should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
+%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
+The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
+The default severity level of the constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
+\begin{DL}
+Variable $\equiv$ $\exists$ concept.Concept
+\end{DL}
+%If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
+%If metadata on data files, including the actual data, is missing (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the study is not sufficient.
+%Case quantity measures how many cases are collected for a study.
+%High case and variable quantities are indicators for high statistical quality and comprehensiveness of the underlying study ($\mathcal{SL}_{1}$).
+
+%\textbf{Cardinality Restrictions on Properties.}
+%An \emph{existential quantification} (\emph{R-86}) contains all those individuals that are connected by a property to individuals/literals of given classes or data ranges.
+%Every \emph{qb:SliceKey}, e.g., must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}).
+\emph{Minimum/maximum/exact qualified cardinality restrictions} (\emph{R-74, R-75, R-76}) contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals of particular classes or data ranges.
+A \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column},
+a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}), and a \emph{qb:DataSet} is structured by (\emph{qb:structure}) exactly one \emph{qb:DataStructureDefinition}.
+\begin{DL}
+TableStructure $\sqsubseteq$ $\geq$1 column.Column \\
+Variable $\sqsubseteq$ $\leq$1 concept.Concept \\
+DataSet $\sqsubseteq$ $\geq$1 structure.DSD $\sqcap$
+$\leq$1 structure.DSD
+\end{DL}
+
+%\textbf{Validation and Reasoning.}
+Some constraint types enable performing reasoning prior to validation which may resolve or cause constraint violations.
+With \emph{subsumption} (\emph{R-100}), one can state that \emph{xkos:ClassificationLevel} is a sub-class of \emph{skos:Collection}, i.e., each \emph{xkos:ClassificationLevel} must also be part of the \emph{skos:Collection} class extension.
+With \emph{sub properties} (\emph{R-54, R-64}), one can state that \emph{disco:fundedBy} is a sub-property of \emph{dcterms:contributor} - i.e., if a study is funded by an organization, then this organization contributed to this study.
+\begin{DL}
+ClassificationLevel $\sqsubseteq$ Collection \\
+fundedBy $\sqsubseteq$ contributor
+\end{DL}
+
+%\section{Basic Constraint Types}
+%\label{vocabulary-constraint-types}
+%
+%As \emph{RDFS} and \emph{OWL} are typically used to define vocabularies, \emph{RDFS} and \emph{OWL} reasoning may be performed prior to validation. 
+%Reasoning and validation are indeed very closely related. 
+%\emph{Reasoning} is the process of determining what follows from what has been stated.
+%%Both should be possible: (1) validation with reasoning and (2) validation without reasoning. 
+%We divide the whole set of \emph{basic constraint types} ($\mathcal{CT}_{B}$) into two disjoint sets to investigate the affect of reasoning to the validation process: 
+%\begin{enumerate}
+	%\item $\mathcal{C}_B ^{\mathcal{R}}$ corresponds to axioms in \emph{OWL 2} and denotes the set of constraint types which enable performing reasoning prior to validation, especially when not all the knowledge is explicit (section \ref{basic-constraint-types-with-reasoning}).
+  %\item $\overline{\mathcal{C}_B ^{\mathcal{R}}}$  denotes the set of constraint types for which reasoning cannot be done or does not improve the result in any obvious sense (section \ref{basic-constraint-types-without-reasoning}).
+%\end{enumerate}
+%
+%\subsection{Basic Constraint Types with Reasoning}
+%\label{basic-constraint-types-with-reasoning}
+%
+%Validation environments should enable users to decide if they wish to perform reasoning prior to validation.
+%Reasoning as an optional pre validation step is beneficial for RDF validation as 
+%(1) it may resolve constraint violations and  
+%(2) it may cause useful constraint violations.
+%A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
+%%Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets}:
+%%\begin{DL}
+%%Catalog $\sqsubseteq$ $\forall$ dataset.Dataset
+%%\end{DL}
+%Consider the following DL knowledge base $\mathcal{K}$\footnote{A knowledge base is a collection of formal statements which corresponds to \emph{facts} or what is known explicitly.
+For simplicity reasons, we only write namespace prefixes in DL statements to avoid ambiguities.}:
+%
+%\begin{center}
+%\begin{DL} 
+%$\mathcal{K}=\{$ &\ms{LogicalDataSet $\sqsubseteq$ dcat:DataSet},\\
+ %&\ms{LogicalDataSet $\sqsubseteq \forall$ aggregation.qb:DataSet},\\
+ %%&\ms{dcat:DataSet $\equiv$ $\exists$ dcat:distribution . dcat:Distribution},\\
+ %&\ms{LogicalDataSet( logical-data-set )},\\
+ %&\ms{aggregation( logical-data-set, aggregated-data-set )}
+ %\}\\ 
+%\end{DL}
+%\end{center}
+%
+%As we know that only person-level data sets (\emph{disco:LogicalDataSet}) can derive (\emph{disco:aggregation}) aggregated data sets (\emph{qb:DataSet}), 
+%{\em logical-data-set} is a \emph{disco:LogicalDataSet}, 
+%and \emph{aggregated-data-set} is derived from \emph{logical-data-set},
+%we conclude that \emph{aggregated-data-set} must be a \emph{qb:DataSet}.
+%As \emph{aggregated-data-set} is not explicitly defined to be a \emph{qb:DataSet}, however, a constraint violation is raised.
+%If we perform reasoning prior to validation, the constraint violation is resolved, as the implicit triple \ms{qb:DataSet(aggregated-data-set)} is inferred. 
+%
+%Reasoning may also cause constraint violations which are needed to enhance data quality.
+%With \emph{subsumption} (\emph{R-100}), one can state that \emph{disco:LogicalDataSet} is a sub-class of \emph{dcat:DataSet}, 
+%i.e., each person-level data set is also a catalog data set.
+%Thus, constraints on catalog data sets are also validated for person-level data sets;
+%e.g., the \emph{existential quantification} below restricting that person-level data sets must have a distribution: 
+%
+%\begin{center}
+%\begin{DL} 
+%$\mathcal{K}=\{$ 
+ %&\ms{DataSet $\equiv$ $\exists$ distribution.Distribution},\\
+%&\ms{Variable $\equiv$ $\exists$ concept.Concept}
+ %\}\\ 
+%\end{DL}
+%\end{center}
+%
+%We extend $\mathcal{K}$ by \emph{existential quantifications} (\emph{R-86}) enforcing that instances of given classes must have some property relation to individuals/literals of certain types.
+%Variables, e.g., should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
+%%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
+%The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
+%The default severity level of the constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
+%%If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
+%%If metadata on data files, including the actual data, is missing (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the study is not sufficient.
+%%Case quantity measures how many cases are collected for a study.
+%%High case and variable quantities are indicators for high statistical quality and comprehensiveness of the underlying study ($\mathcal{SL}_{1}$).
+%
+%\begin{center}
+%\begin{DL} 
+%$\mathcal{K}=\{$ 
+  %&\ms{fundedBy $\sqsubseteq$ contributor}
+ %\}\\ 
+%\end{DL}
+%\end{center}
+%
+%By stating that \emph{disco:fundedBy} is a sub property of \emph{dcterms:contributor},
+%the {\em sub property} (\emph{R-54, R-64}) above assures that if a series is funded by an organization, then the organization must also contribute to the series.
+%In case the \emph{sub-property} is applied without reasoning and $\mathcal{K}$ contains the triple \ms{disco:fundedBy} \ms{(EU-SILC,} \ms{organization)},
+%a constraint violation is thrown if $\mathcal{K}$ does not explicitly include the triple \ms{dcterms:contributor} \ms{(EU-SILC,} \ms{organization)}.
+%If the \emph{sub property} is applied with reasoning, on the other side, the latter triple is derived which resolves the constraint violation.
+%
+%%\begin{DL}
+%%fundedBy $\sqsubseteq$ contributor
+%%\end{DL} 
+%
+%%\emph{Asymmetric object properties} (\emph{R-62}) restrict that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}.
+%%Such constraints are defined for each object property for which a semantically equivalent object property pointing from the other direction would also be possible but is not defined within the vocabulary.
+%%A \emph{disco:Variable}, e.g., may be based on (\emph{disco:basedOn}) a \emph{disco:RepresentedVariable}.
+%%A \emph{disco:RepresentedVariable}, however, cannot be based on a \emph{disco:Variable} (\ms{$disco:basedOn \sqcap disco:basedOn^{-} \sqsubseteq \bot$}).
+%
+%%\emph{Property domain} (\emph{R-25, R-26}) and \emph{range} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties.
+%%Only \emph{phdd:Tables}, e.g., can have \emph{phdd:isStructuredBy} relationships and
+%%\emph{xkos:belongsTo} relationships can only point to \emph{skos:Concepts}:
+%%\begin{DL}
+%%$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table \\
+%%$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept
+%%\end{DL}
+%
+%%\begin{center}
+%%\begin{DL} 
+%%$\mathcal{K}=\{$ 
+  %%&\ms{TableStructure $\sqsubseteq$ $\geq$1 column.Column}, \\
+	%%&\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}, \\
+	%%&\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition} \\ 
+	%%&\ms{$\sqcap$ $\leq$1 structure.DataStructureDefinition}
+ %%\}\\ 
+%%\end{DL}
+%%\end{center}
+%
+%%\textbf{Cardinality Restrictions on Properties.}
+%%An \emph{existential quantification} (\emph{R-86}) contains all those individuals that are connected by a property to individuals/literals of given classes or data ranges.
+%%Every \emph{qb:SliceKey}, e.g., must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}).
+%%\emph{Minimum/maximum/exact qualified cardinality restrictions} (\emph{R-74, R-75, R-76}) contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals of particular classes or data ranges.
+%%A \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column},
+%%a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}), and a \emph{qb:DataSet} is structured by (\emph{qb:structure}) exactly one \emph{qb:DataStructureDefinition}.
+%%DATA-CUBE-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-
+%%02: Unique data set (IC-1 [3]) - Every qb:Observation has (qb:dataSet) ex-
+%%actly one associated qb:DataSet (Observation  ¥1 dataSet.DataSet [
+%%¤1 dataSet.DataSet).
+%%Severity level: ERROR
+%%
+%%(\emph{R-75: minimum qualified cardinality restrictions})
+%%
+%%DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-
+%%02: Unique DSD (IC-2 [3]) - Every qb:DataSet has (qb:structure) exactly one
+%%associated qb:DataStructureDefinition (DataSet  ¥1 structure.DataStructureDefinition
+%%[ ¤1 structure.DataStructureDefinition).
+%%Severity level: ERROR
+%%
+%%(\emph{R-74: exact qualified cardinality restrictions})
+%%\footnote{\emph{DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02}}.
+%%\textbf{Language Tag Cardinality.}
+%
+%\subsection{Basic Constraint Types without Reasoning}
+%\label{basic-constraint-types-without-reasoning}
+%
+%$\overline{\mathcal{C}_B ^{\mathcal{R}}}$  denotes the set of constraint types for which reasoning cannot be done or does not improve the result in any obvious sense.
+%The constraint type \emph{vocabulary} guarantees that users do not invent new or use deprecated terms of vocabularies.
+%%Out-dated classes and properties of previous vocabulary versions can be marked as deprecated.
+%%The constraint types \emph{context-specific valid classes and properties} (\emph{R-209; R-210}) can be used to specify which classes and properties are valid in which context - here a given vocabulary version.
+%\emph{Value is valid for datatype} (\emph{R-223}) constraints serve to make sure that all literal values are valid with regard to their datatypes - as stated in the vocabularies.
+%Thus, it is checked that all date values (e.g., {{\em dcterms:date}, \em disco:startDate}, {\em disco:endDate}) are actually of the datatype \emph{xsd:date} and that \emph{xsd:nonNegativeInteger} values (e.g.
+\emph{disco:frequency}) are not negative.
+%Depending on property datatypes, two different literal values have
+%a specific ordering with respect to operators like \textless  (\emph{R-43: literal value comparison}).
+%Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}).
+%
+%\begin{center}
+%\begin{DL} 
+%$\mathcal{K}=\{$ 
+	%&\ms{isStructuredBy $\sqsubseteq$ $\neg$ column}, \\
+	%&\ms{TableDescription $\sqcap$ ColumnDescription $\sqsubseteq$ $\perp$}, \\
+	%&\ms{CategoryStatistics $\equiv$} \\
+	%&\ms{$\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString}
+ %\}\\ 
+%\end{DL}
+%\end{center}
+%
+%All properties, not having the same domain and range types, are defined to be pairwise disjoint
+%(\emph{R-9: disjoint properties}), i.e., no individual \emph{x} can be connected to an individual/literal \emph{y} by disjoint properties (e.g., \emph{phdd:isStructuredBy} and \emph{phdd:column}).
+%All \emph{PHDD} classes (e.g., \emph{phdd:TableDescription}, \emph{phdd:ColumnDescription}) are pairwise disjoint (\emph{R-7: disjoint classes}),
+%i.e., individuals cannot be instances of multiple disjoint classes.
+%It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values (\emph{R-30/37: allowed values}). 
+%%\emph{Allowed values} (\emph{R-30, R-37}) for properties can be IRIs (matching one or multiple patterns), any literals, allowed literals (e.g.
+'red' 'blue' 'green'), and typed literals of one or multiple type(s) (e.g.
+\emph{xsd:string}).
+%\emph{disco:CategoryStatistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString}.
+%Validation should \emph{exploit sub-super relations} in vocabularies (\emph{R-224}).
+%If \emph{dcterms:coverage} and one of its sub-properties (\emph{dcterms:spatial}, \emph{dcterms:temporal}) are given,
+%it is checked that \emph{dcterms:coverage} is not redundant with its sub-properties 
+%which may indicate when the data is verbose/redundant or expressed at a too general level.
 
@@
 %(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of data models (section \ref{complex-constraint-types}).
-%(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges (section \ref{basic-constraint-types}).
+%(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges (section \ref{vocabulary-constraint-types}).
 %We determined the default \emph{severity level} for each constraint to indicate how serious the violation of the constraint is

### 2015-04-29 paper/paper7/paper7.tex

@@
 \section{Introduction}
-
-\tb{nur data und nicht metadata}
 
@@
 
+\ke{in guter tradition unserer arbeitsgruppe würde ich mich als senior researcher um die einleitung kümmern, die gefällt mir so nicht}\tb{sehr gerne}
+
 \section{Motivation}
@@
 %\label{running-example}
-\section{Vocabularies to Represent Metadata and Data in RDF}
+\section{Common Vocabularies in SBE Sciences}
 \label{rdf-representation}
@@
 %This includes data documentation at the study and variable level as well as documentation materials, tools and further information. 
+\ke{Wieso jetzt wieder qb?}\tb{ich möchte zeigen wie aggregierte daten und personenbezogene daten in RDF verbunden sind. Weglassen?}
 Aggregated (qb:DataSet) and underlying person-level data sets (\emph{disco:LogicalDataSet}) are connected by \emph{prov:wasDerivedFrom}. 
@@
 In close collaboration with several \emph{SBE} domain experts, we defined 246 constraint 
-of 53 different types on six vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classifies them according to the complexity level of their type and their severity level.
-For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4,26 billion triples) of \emph{SBE} research data on three vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
-These vocabularies are the central and most representative ones within the \emph{SBE} community. 
+of 53 different types on six vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classified them according to the complexity level of their type and their severity level.
+For 114 of these constraints, we evaluated the data quality of 15,694 data sets (4,26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
 We distinct two classes of vocabularies: 
-(1) established vocabularies which are widely adopted and accepted and 
-(2) newly developed vocabularies which are either recently published or are still in the publication process.
+(1) established vocabularies (e.g., \emph{QB}, \emph{SKOS}) which are widely adopted and accepted and 
+(2) newly developed vocabularies (e.g., \emph{Disco} which will be published in 2015) which are either recently published or are still in the publication process.
 It is likely that such a vocabulary is still subject of constant change, that published data may not be consistent with its current version,
 and that early adopters did not properly understand its formal specification.
-We investigate the quality of data conforming to the established vocabularies \emph{QB} and \emph{SKOS} and to the newly developed vocabulary \emph{Disco} which will be published in 2015.
-
-We evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets by means of both $\mathcal{C}_{C}$ and $\mathcal{C}_{T}$ constraints of the majority of the constraint types.
+Based on this evaluation we formulate hypotheses.
+Nevertheless, we have to be careful making general statements for all vocabularies 
+as these hypotheses still have to be verified or falsified in terms of future work 
+by evaluating the quality of data represented by additional established and newly developed vocabularies.
 
@@
 1,526 / 9,673,055 (\emph{Disco}) data sets / triples using the \emph{RDF Validator} in batch mode.
-That are more than 4.2 billion triples and 15 thousand data sets.
 We validated, i.a., 
@@
 We recently published a technical report\footnote{\label{technical-report-2}Available at: \url{http://arxiv.org/abs/1504.04478}} (serving as second appendix of this paper) 
-in which we describe the comprehensive evaluation in detail \cite{BoschZapilkoWackerowEckert2015-2}. 
+in which we describe the evaluation in detail \cite{BoschZapilkoWackerowEckert2015-2}. 
 As we evaluated nearly 10 thousand \emph{QB} data sets, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.
 
-Based on this evaluation we formulate hypotheses.
-Nevertheless, we have to be careful making general statements for all vocabularies 
-as these hypotheses still have to be verified or falsified in terms of future work 
-by evaluating the quality of data represented by additional established and newly developed vocabularies.
-
-\subsection{Evaluation Results and Discussion}
+\subsection{Evaluation Results and Formulation of Hypotheses}
 
@@
 Table \ref{tab:evaluation-constraint-violations} shows the results of the evaluation, more specifically the constraints and the constraint violations, which are caused by these constraints, in percent.
-The constraints and their resulting constraint violations are grouped by vocabulary, complexity level of their type, and severity level.
+The constraints and their raised constraint violations are grouped by vocabulary, complexity level of their type, and their severity level.
 The number of evaluated triples and data sets differs between the vocabularies
 as we evaluated 3.8 billion QB, 480 million SKOS, and 10 million Disco triples.
-In order to get suitable statements for all vocabularies,  
-we normalize the total values which apply for all vocabularies
-by building the arithmetic mean over the individual vocabularies' percentage values. 
-\tb{More than 80\% of the overall approx. 55 million constraint violations are caused by \emph{QB} constraints.}
+To be able to formulate hypotheses which apply for all vocabularies,  
+we normalize the total percentage values.
+As, e.g., 18\% of the Disco, 100\% of the QB, and 21\% of the \emph{SKOS} violations are caused by complex constraints,  
+we calculate that 46.6\% of the violations are raised by complex constraints of all vocabularies.
+%by building the arithmetic mean over the individual vocabularies' percentage values. 
+%\tb{More than 80\% of the overall approx. 55 million constraint violations are caused by \emph{QB} constraints.}
 
@@
 data quality can be significantly improved when existing constraint languages are extended or new constraint languages are developed to express \emph{complex constraints} more easily, concisely, and intuitively.
-
-\begin{table}[H]
-		\scriptsize
-    \begin{center}
-    \begin{tabular}{@{}lcccccccc@{}}
-    %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
-    %\\  \cmidrule{2-3}
-		\hline
-    \multirow{2}{*}{} &
-      \multicolumn{2}{c}{\textbf{\emph{Disco}}} &
-      \multicolumn{2}{c}{\textbf{\emph{QB}}} &
-      \multicolumn{2}{c}{\textbf{\emph{SKOS}}} &
-      \multicolumn{2}{c}{\textbf{\emph{Total}}} \\
-    \textbf{} & C & CV & C & CV & C & CV & C & CV \\
-    \hline
-    %\\ \midrule
-		 & 143 & 3,575,002 & 35 & 45,635,861 & 35 & 5,540,988 & 213 & 54,751,851 \\
-		\hline
-		\textbf{\emph{complex}} & 25.9\% & 18.3\% & 37.1\% & \textbf{100\%} & \textbf{37.1\%} & 21.4\% & 33.4\% & \textbf{46.6\%} \\
-		\textbf{\emph{simple}} & 19.6\% & 15.7\% & 8.6\% & 0.0\% & \textbf{34.3\%} & \textbf{78.6\%} & 20.8\% & 31.4\% \\
-		\textbf{\emph{vocabulary}} & \textbf{54.6\%} & \textbf{66.1\%} & \textbf{54.3\%} & 0.0\% & \textbf{28.6\%} & 0.0\% & \textbf{45.8\%} & 22.0\% \\
-		%\hline
-		%\emph{CV (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 2,333,365 (65.3\%) & 1,777 (0\%) & 0 (0\%) & 2,335,142 (4.3\%) \\
-		%\emph{CV (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 28,000 (0.8\%) & 0 (0\%) & 0 (0\%) & 28,000 (0.1\%) \\
-		\hline
-		\textbf{\emph{info}} & \textbf{52.5\%} & \textbf{52.6\%} & 11.4\% & 0.0\% & \textbf{60.0\%} & 41.2\% & \textbf{41.3\%} & 31.3\% \\
-		\textbf{\emph{warning}} & 7.0\% & 29.4\% & 8.6\% & \textbf{99,8\%} & 14.3\% & \textbf{58.8\%} & 10.0\% & \textbf{62.7\%} \\
-		\textbf{\emph{error}} & 40.6\% & 18\% & \textbf{80.0\%} & 0.3\% & 25.7\% & 0.0\% & \textbf{48.8\%} & 6.1\%\\
-    \bottomrule
-    \end{tabular}
-    \\ \emph{C (constraints), CV (constraint violations)}
-    \caption{Constraints and Constraint Violations}
-		\label{tab:evaluation-constraint-violations}
-    \end{center}
-\end{table}
 

### 2015-04-29 paper/paper7/paper7.tex
evaluation

@@
 The number of evaluated triples and data sets differs between the vocabularies
-as we evaluated 3.8 billion QB, 480 million SKOS, and 10 million Disco triples.
+as we evaluated 3.8 billion \emph{QB}, 480 million \emph{SKOS}, and 10 million \emph{Disco} triples.
 To be able to formulate hypotheses which apply for all vocabularies,  
 we normalize the total percentage values.
-As, e.g., 18\% of the Disco, 100\% of the QB, and 21\% of the \emph{SKOS} violations are caused by complex constraints,  
-we calculate that 46.6\% of the violations are raised by complex constraints of all vocabularies.
+As, e.g., 18\% of the \emph{Disco}, 100\% of the \emph{QB}, and 21\% of the \emph{SKOS} violations are caused by \emph{complex constraints},  
+we calculate that 46.6\% of the violations are raised by \emph{complex constraints} of all vocabularies.
 %by building the arithmetic mean over the individual vocabularies' percentage values. 
@@
 
-Almost 1/2 of all 213 constraints and more than 50\% of the \emph{Disco} and the \emph{QB} constraints are vocabulary constraints.
-The \emph{SKOS} constraints, on the other side, are equally distributed among the three disjoint sets of constraint types. 
+Almost 1/2 of all 213 constraints and more than 50\% of the \emph{Disco} and the \emph{QB} constraints are \emph{vocabulary constraints}.
+The \emph{SKOS} constraints are equally distributed among the three disjoint sets of constraint types. 
 \begin{hyp}
-A significant amount of 46 \% of the constraints are directly extractable from established and newly defined vocabularies. 
+A significant amount of 46 \% of the constraints are directly extractable from formal specifications of established and newly defined vocabularies. 
 \end{hyp}
 
-Nearly 1/2 of the constraint violations are caused by complex constraints, 1/3 by simple constraints, and 1/5 by vocabulary constraints.
-2/3 of the constraint violations, thrown for \emph{Disco} data sets, result from vocabulary constraints,
-almost only conplex constraints raised constraint violations for \emph{QB} data sets, and 
-nearly 80\% of the \emph{SKOS} constraint violations are caused by simple constraints.
+\begin{table}[H]
+		\scriptsize
+    \begin{center}
+    \begin{tabular}{@{}lcccccccc@{}}
+    %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
+    %\\  \cmidrule{2-3}
+		\hline
+    \multirow{2}{*}{} &
+      \multicolumn{2}{c}{\textbf{\emph{Disco}}} &
+      \multicolumn{2}{c}{\textbf{\emph{QB}}} &
+      \multicolumn{2}{c}{\textbf{\emph{SKOS}}} &
+      \multicolumn{2}{c}{\textbf{\emph{Total}}} \\
+    \textbf{} & C & CV & C & CV & C & CV & C & CV \\
+    \hline
+    %\\ \midrule
+		 & 143 & 3,575,002 & 35 & 45,635,861 & 35 & 5,540,988 & 213 & 54,751,851 \\
+		\hline
+		\textbf{\emph{complex}} & 25.9\% & 18.3\% & 37.1\% & \textbf{100\%} & \textbf{37.1\%} & 21.4\% & 33.4\% & \textbf{46.6\%} \\
+		\textbf{\emph{simple}} & 19.6\% & 15.7\% & 8.6\% & 0.0\% & \textbf{34.3\%} & \textbf{78.6\%} & 20.8\% & 31.4\% \\
+		\textbf{\emph{vocabulary}} & \textbf{54.6\%} & \textbf{66.1\%} & \textbf{54.3\%} & 0.0\% & \textbf{28.6\%} & 0.0\% & \textbf{45.8\%} & 22.0\% \\
+		%\hline
+		%\emph{CV (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 2,333,365 (65.3\%) & 1,777 (0\%) & 0 (0\%) & 2,335,142 (4.3\%) \\
+		%\emph{CV (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 28,000 (0.8\%) & 0 (0\%) & 0 (0\%) & 28,000 (0.1\%) \\
+		\hline
+		\textbf{\emph{info}} & \textbf{52.5\%} & \textbf{52.6\%} & 11.4\% & 0.0\% & \textbf{60.0\%} & 41.2\% & \textbf{41.3\%} & 31.3\% \\
+		\textbf{\emph{warning}} & 7.0\% & 29.4\% & 8.6\% & \textbf{99,8\%} & 14.3\% & \textbf{58.8\%} & 10.0\% & \textbf{62.7\%} \\
+		\textbf{\emph{error}} & 40.6\% & 18\% & \textbf{80.0\%} & 0.3\% & 25.7\% & 0.0\% & \textbf{48.8\%} & 6.1\%\\
+    \bottomrule
+    \end{tabular}
+    \\ \emph{C (constraints), CV (constraint violations)}
+    \caption{Constraints and Constraint Violations}
+		\label{tab:evaluation-constraint-violations}
+    \end{center}
+\end{table}
+
+Nearly 1/2 of the violations are caused by \emph{complex constraints}, 1/3 by \emph{simple constraints}, and 1/5 by \emph{vocabulary constraints}.
 
 \begin{hyp}
-The fact that only 1/5 of all constraint violations result from vocabulary constraints, 
+The fact that only 1/5 of all violations result from vocabulary constraints, 
 even though, 46\% of all constraints are vocabulary constraints,
-indicates that in general data conforms to the intended syntax and semantics of vocabularies.
+indicates good data quality in general (according to formal specifications of vocabularies).
 \end{hyp}
 
-For established vocabularies, vocabulary constraints caused nearly 0\% of all constraint violations (e.g. only 1.777 constraint violations for \emph{QB} constraints).  
-For newly defined vocabularies, however, 2/3 of all constraint violations are raised by vocabulary constraints. 
+2/3 of the \emph{Disco} violations result from \emph{vocabulary constraints},
+almost only \emph{complex constraints} raised \emph{QB} violations, and 
+nearly 80\% of the \emph{SKOS} violations are caused by \emph{simple constraints}.
+
+\begin{hyp}
+For established vocabularies, vocabulary constraints caused nearly 0\% of all violations\footnote{e.g. only 1.777 \emph{QB} violations}
+which indicates good data quality (according to formal specifications of vocabularies). 
+For newly defined vocabularies, however, 2/3 of all violations are raised by vocabulary constraints
+which indicates good data quality (according to formal specifications of vocabularies).
+\end{hyp}
+
 \begin{hyp}

### 2015-04-29 paper/paper7/paper7.tex
evaluation

@@
 %RDF data validation can only be performed semi-automatically, i.e., an automatic approach serves as basis for intellectual decisions.
+
+\section{Related Work}
+\label{related-work}
+
+%\textbf{XML vs. RDF Validation.}
+For data archives, research institutes, and data libraries,
+RDF validation according to predefined constraints is a much sought-after feature, 
+particularly as this is taken for granted in the XML world.
+DDI-XML documents, e.g., are validated against diverse XSDs\footnote{\url{http://www.ddialliance.org/Specification/}}.
+As certain constraints cannot be formulated and validated by XSDs, 
+so-called secondary-level validation tools like \emph{Schematron}\footnote{\url{https://msdn.microsoft.com/en-us/library/aa468554.aspx}} have been introduced to overcome the limitations of XML validation.
+\emph{Schematron} generates validation rules and validates XML documents according to them.
+With RDF validation, one can overcome drawbacks when validating XML documents\footnote{\url{http://www.xmlmind.com/xmleditor/_distrib/doc/xmltool/xsd_structure_limitations.html}}.
+It cannot be validated, e.g., if each code of a variable's code list is associated with a category (\emph{R-86}).
+Additionally, it cannot be validated that if an element has a specific value, then certain child elements must be present (\emph{R-71}).  
+A comprehensive comparison of XML and RDF validation, however, is not within the scope of this paper.
+
+%validation or relational databases: types, relations
+
+%\textbf{RDF Data Cube Vocabulary.}
+A well-formed \emph{RDF Data Cube} is an a RDF graph describing one or more instances of \emph{qb:DataSet} for which each of the 22 integrity constraints\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf}, defined within the \emph{QB} specification, passes.
+Each integrity constraint is expressed as narrative prose and, where possible, a SPARQL ASK query or query template. 
+If the ASK query is applied to an RDF graph then it will return true if that graph contains one or more \emph{QB} instances which violate the corresponding constraint \cite{CyganiakReynolds2014}.
+Mader, Haslhofer, and Isaac investigated how to support
+taxonomists in improving SKOS vocabularies by pointing out quality
+issues that go beyond the integrity constraints defined in the SKOS specification \cite{MaderHaslhoferIsaac2012}.
 
@@
 (2) newly developed vocabularies (e.g., \emph{Disco} which will be published in 2015) which are either recently published or are still in the publication process.
-It is likely that such a vocabulary is still subject of constant change, that published data may not be consistent with its current version,
-and that early adopters did not properly understand its formal specification.
+%It is likely that such a vocabulary is still subject of constant change, that published data may not be consistent with its current version,
+%and that early adopters did not properly understand its formal specification.
 Based on this evaluation we formulate hypotheses.
@@
 
+Nearly 1/2 of the violations are caused by \emph{complex constraints}, 1/3 by \emph{simple constraints}, and 1/5 by \emph{vocabulary constraints}.
+
+\begin{hyp}
+The fact that only 1/5 of all violations result from vocabulary constraints, 
+even though, 46\% of all constraints are vocabulary constraints,
+indicates good data quality in general (according to formal specifications of vocabularies).
+\end{hyp}
+
+2/3 of the \emph{Disco} violations result from \emph{vocabulary constraints},
+almost only \emph{complex constraints} raised \emph{QB} violations, and 
+nearly 80\% of the \emph{SKOS} violations are caused by \emph{simple constraints}.
+
+\begin{hyp}
+For established vocabularies, vocabulary constraints caused nearly 0\% of all violations\footnote{e.g. only 1.777 \emph{QB} violations}
+which indicates good data quality (according to formal specifications of vocabularies). 
+For newly defined vocabularies, however, 2/3 of all violations are raised by vocabulary constraints
+which indicates good data quality (according to formal specifications of vocabularies).
+\end{hyp}
+
+It is likely that a newly developed vocabulary is still subject of constant change, 
+that published data may not be consistent with its current version,
+and that early adopters did not properly understand its formal specification.
+
 \begin{table}[H]
@@
 
-Nearly 1/2 of the violations are caused by \emph{complex constraints}, 1/3 by \emph{simple constraints}, and 1/5 by \emph{vocabulary constraints}.
-
-\begin{hyp}
-The fact that only 1/5 of all violations result from vocabulary constraints, 
-even though, 46\% of all constraints are vocabulary constraints,
-indicates good data quality in general (according to formal specifications of vocabularies).
-\end{hyp}
-
-2/3 of the \emph{Disco} violations result from \emph{vocabulary constraints},
-almost only \emph{complex constraints} raised \emph{QB} violations, and 
-nearly 80\% of the \emph{SKOS} violations are caused by \emph{simple constraints}.
-
-\begin{hyp}
-For established vocabularies, vocabulary constraints caused nearly 0\% of all violations\footnote{e.g. only 1.777 \emph{QB} violations}
-which indicates good data quality (according to formal specifications of vocabularies). 
-For newly defined vocabularies, however, 2/3 of all violations are raised by vocabulary constraints
-which indicates good data quality (according to formal specifications of vocabularies).
-\end{hyp}
-
 \begin{hyp}
@@
 \end{hyp}
-It is likely that a newly developed vocabulary is still subject of constant change, that published data may not be consistent with its current version,
-and that early adopters did not properly understand its formal specification.
 
@@
 
-\section{Related Work}
-\label{related-work}
-
-%\textbf{XML vs. RDF Validation.}
-For data archives, research institutes, and data libraries,
-RDF validation according to predefined constraints is a much sought-after feature, 
-particularly as this is taken for granted in the XML world.
-DDI-XML documents, e.g., are validated against diverse XSDs\footnote{\url{http://www.ddialliance.org/Specification/}}.
-As certain constraints cannot be formulated and validated by XSDs, 
-so-called secondary-level validation tools like \emph{Schematron}\footnote{\url{https://msdn.microsoft.com/en-us/library/aa468554.aspx}} have been introduced to overcome the limitations of XML validation.
-\emph{Schematron} generates validation rules and validates XML documents according to them.
-With RDF validation, one can overcome drawbacks when validating XML documents\footnote{\url{http://www.xmlmind.com/xmleditor/_distrib/doc/xmltool/xsd_structure_limitations.html}}.
-It cannot be validated, e.g., if each code of a variable's code list is associated with a category (\emph{R-86}).
-Additionally, it cannot be validated that if an element has a specific value, then certain child elements must be present (\emph{R-71}).  
-A comprehensive comparison of XML and RDF validation, however, is not within the scope of this paper.
-
-%validation or relational databases: types, relations
-
-%\textbf{RDF Data Cube Vocabulary.}
-A well-formed \emph{RDF Data Cube} is an a RDF graph describing one or more instances of \emph{qb:DataSet} for which each of the 22 integrity constraints\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf}, defined within the \emph{QB} specification, passes.
-Each integrity constraint is expressed as narrative prose and, where possible, a SPARQL ASK query or query template. 
-If the ASK query is applied to an RDF graph then it will return true if that graph contains one or more \emph{QB} instances which violate the corresponding constraint \cite{CyganiakReynolds2014}.
-Mader, Haslhofer, and Isaac investigated how to support
-taxonomists in improving SKOS vocabularies by pointing out quality
-issues that go beyond the integrity constraints defined in the SKOS specification \cite{MaderHaslhoferIsaac2012}.
-
 \section{Conclusion and Future Work}

### 2015-04-29 paper/paper7/paper7.tex
evaluation

@@
 (2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).
+
+In this paper, we discuss constraints on RDF data in general.
+Note that the data represented in RDF can be data in the sense of SBE sciences, but also metadata about published or unpublished data.
+We generally refer to both simply as RDF data and only distinguish between data and metadata in the dataset descriptions and in the case that it matters for the purpose of this paper.\tb{hab ich eingefügt, ist der absatz von dir...}
 

### 2015-04-29 paper/paper7/paper7.tex
evaluation

@@
 \end{table}
-
-\begin{hyp}
-Complex constraints are met by data represented by established vocabularies but not by data represented by newly developed vocabularies. 
-\end{hyp}
 
@@
 
+\tb{
+die vokabular-beschreibungen klarer strukturieren. du nutzt plötzlich disco elemente, disco wird überhaupt nicht vernünftig eingeführt, obwohl es später untersucht wird
+alles, was nicht der aussage des papers (neuer titel, btw) dient, solltest du weglassen
+klare, einfache struktur: 1. grundidee (constraints identifizieren, validieren auf datensets, zu belastbaren aussagen kommen für die weitere entwicklung von constraint languages)
+2. vorstellung der untersuchten vokabulare
+3.
+beschreiben, wo die constraints herkommen, bzw.
+wie die generiert wurden.
+dabei auch auf die klassifikation eingehen, aber nur im hinblick auf die spätere auswertung, nicht als main contribution des papers
+4. evaluation mit beschreibung der datasets in setup (das les ich mir gleich mal durch, das hast du ja schon neu geschrieben)
+ja, und dann prägnante conclusion mit zusammenfassung der hypothesen, der bedutung für die weitere entwicklung von CLs und natürlich future work
+}
+
 \bibliography{../../literature/literature}{}

### 2015-04-29 paper/paper7/paper7.tex
evaluation

@@
 Therefore, this technical report contains mappings to \emph{DL} to logically underpin each requirement and to determine which \emph{DL} constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
-We classified both RDF constraint types and RDF constraints to evaluate the quality of metadata and data which may be represented by any vocabulary.
+We classified both RDF constraint types and RDF constraints to gain better insights into the quality of RDF data with respect to this classification, independent of the used vocabulary.
 %Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
@@
 
+\begin{hyp}
+A significant amount of 47\% of the violations refer to complex constraints that are not easily expressible in existing languages which confirms the necessity to provide suitable constraint languages.
+\end{hyp} 
+\emph{Vocabulary} and \emph{simple constraints} can be expressed easily, concisely, and intuitively by either modeling languages (e.g., \emph{RDF}, \emph{RDFS}, \emph{OWL 2}) or constraint languages (e.g., \emph{ShEx}, \emph{ReSh}, \emph{SPIN}).
+This is not the case, however, for \emph{complex constraints} which in most cases still can only be expressed by plain \emph{SPARQL}. 
+As almost 1/2 of all violations are caused by \emph{complex constraints}, 
+data quality can be significantly improved when \emph{complex constraints} can also be expressed more easily, concisely, and intuitively.
+Therefore, existing constraint languages have to be extended or new constraint languages have to be developed.
+
 \begin{table}[H]
@@
 \end{table}
-
-\begin{hyp}
-A significant amount of 47\% of the violations refer to complex constraints that are not easily expressible in existing languages which confirms the necessity to provide suitable constraint languages.
-\end{hyp} 
-\emph{Vocabulary} and \emph{simple constraints} can be easily, concisely, and intuitively expressed by either modeling languages (e.g., \emph{RDF}, \emph{RDFS}, \emph{OWL 2}) or constraint languages (e.g., \emph{ShEx}, \emph{ReSh}, \emph{SPIN}).
-This is not the case, however, for \emph{complex constraints} which in most cases still have to be expressed by plain \emph{SPARQL}. 
-As almost the half of all constraint violations are caused by \emph{complex constraints}, 
-data quality can be significantly improved when existing constraint languages are extended or new constraint languages are developed to express \emph{complex constraints} more easily, concisely, and intuitively.
 

### 2015-04-29 paper/paper7/paper7.tex
Section 5, classification

@@
 This way, it is expressible in \emph{OWL 2} that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:
+\ke{Ich dachte, das kommt aus dem Vokabular.
+Dann muss das heißen: For example, in PHDD, a minimum qualified cardinality constraint can be obtained from the OWL definition of this restriction class, ensuring that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:}
 \begin{ex}
@@
 \emph{Simple} and \emph{complex constraints} are defined according to textual descriptions of the intended semantics of vocabularies.  
-\emph{Simple constraint types} is the set of constraint types whose constraints can be easily defined without much effort in addition to \emph{vocabulary constraints}.
+\emph{Simple constraint types} is the set of constraint types whose constraints can be easily defined without much effort in addition to \ke{einfügen: the already defined (auf den Lesefluss achten, das ist eine sehr pragmatische klassifikation und muss nicht übertrieben formal und trocken geschrieben sein)} \emph{vocabulary constraints}.
 {\emph{Data property facets} (\emph{R-46}) is an example of a \emph{simple constraint type} which enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
@@
 a thesaurus should not contain many orphan concepts, i.e., concepts without any associative or hierarchical relations, lacking context information valuable for search. 
-\emph{Complex constraints} show the importance to develop constraint languages enabling to describe more complex constraints.
+\emph{Complex constraints} show the importance to develop constraint languages enabling to describe more complex constraints.\ke{der satz macht so keinen sinn...
+aber er ist ein weiteres gutes beispiel, warum du viel mehr auf die formulierungen achten musst.
+Ich weiß genau was du meinst, du hast auch recht, aber hier steht trotzdem ein sinnloser satz, so wie er formuliert ist.}
+
+\ke{ich würde da auch für simple und vor allem für complex konkrete beispiele in code einfügen}
 
@@
 
+\ke{da muss mindestens ein überleitender satz rein, der noch mal den unterschied von constraint types und types aufgreift und erklärt, dass es jetzt um konkrete constraints auf den vokabularen geht, deren severity eben vom konkreten kontext abhängt und nicht allgemein über den type bestimmt werden kann.}
+
 \emph{SBE} experts determined the default \textbf{\emph{severity level}} (\emph{R-158}) for each of the 246 constraints to indicate how serious the violation of the constraint is.
-We propose an extensible metric to measure the continuum of severity levels ranging from \emph{informational} to \emph{error}.
-According to the default severity level of constraints, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:
+We propose an extensible metric to measure the continuum of severity levels ranging from \emph{informational} to \emph{error}.\ke{oder etwas weniger anmaßend: we use the commonly accepted classification of log messages in software development and distingush informational, warning and error.}
+According to the default severity level of constraints, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:\ke{auch dieser satz macht keinen sinn für mich, ebensowenig wie die extrem erhellende auflistung, die gleich folgt...
+mein vorschlag von eben kann das komplett ersetzen.}
 \begin{itemize}
@@
 As a consequence, violating many \emph{vocabulary constraints} is an indicator for bad (meta)data quality\footnote{For simplicity reasons, we only assign severity levels to \emph{vocabulary constraints} in this paper in case they differ from \emph{error constraints}.}.
+\ke{den ganzen letzten absatz finde ich unübersichtlich.
+Kann man das nicht klarer sagen: Error sind syntaktische oder semantische fehler, die zu einem abbruch der datenverarbeitung führen sollten.
+warnings sind syntaktische oder semantische fehler, die aber normalerweise nicht zu einem abbruch führen müssen.
+verletzungen von informational constraints weisen auf potentielle verbesserungen in den daten hin, werden aber nicht als fehler angesehen (der satz war in ordnung).
+die fussnote ist doch vollkommen fehl am platz, oder?
+es werden ja nicht alle constraints aufgelistet und wie ihr das implementiert habt und ob ihr euch arbeit erspart habt weil ihr default severity bei bestimmten constraint types vorgebt, das interessiert doch keinen.}
 

### 2015-04-29 paper/paper7/paper7.tex
evaluation

--- 2015-04-29 paper/paper7/paper7.tex
@@
 
+63\% of all violations are caused by \emph{warning constraints} which are only 10\% of all constraints. 
+Only 6\% of the violations are caused by \emph{error constraints} which are 49\% of all constraints.
+
+\begin{hyp}
+In general, data quality is high (according to severity levels) since only 6\% of the violations are caused by error constraints which are 49\% of all defined constraints.
+\end{hyp}
+
+\begin{hyp}
+The percentage of severe violations is very low (6\%), compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
+\end{hyp}
+
 \begin{table}[H]
@@
 
-63\% of all constraint violations are caused by warning constraints which are only 10\% of all constraints. 
-Only 6\% of the constraint violations are caused by error constraints which are 49\% of all constraints.
-
-\begin{hyp}
-Data quality is good since only 6\% of the constraint violations are caused by error constraints which are 49\% of all constraints.
-The percentage of severe constraint violations is very low, compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
-\end{hyp}
-
 80\% of the \emph{QB} constraints are error constraints.
 More than 50\% of the \emph{Disco} and \emph{SKOS} constraints, however, are informational constraints.
-For Disco, 1/6 of the constraint violations are caused by error constraints.
-Almost all constraint violations raised by \emph{QB} constraints and 59\% of the constraint violations caused by \emph{SKOS} constraints are warnings.  
+1/6 of the Disco violations are caused by error constraints.
+Almost all \emph{QB} violations and 59\% of the \emph{SKOS} violations are caused by warning constraints.  
 \begin{hyp}
-In general, data quality is very high.
-The quality of data represented by established vocabularies is good,
-as serious constraint violations rarely appear.
-The quality of data represented by newly developed vocabularies, however, is worse,
-as serious constraint violations occur partially.
+For established vocabularies, the data quality is high,
+as serious violations rarely appear.
+For newly developed vocabularies, data quality is worse,
+as serious violations occur partially.
 \end{hyp}

### 2015-04-29 paper/paper7/paper7.tex
eval

@@
 of 53 different types on six vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classified them according to the complexity level of their type and their severity level.
+\ke{Alle vokabulare in section "vocabularies" eingeführt?}
 For 114 of these constraints, we evaluated the data quality of 15,694 data sets (4,26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
@@
 by evaluating the quality of data represented by additional established and newly developed vocabularies.
+\ke{das ist zu früh finde um schon einzuschränken, erst mal ergebnisse, dann hypothesen, dann kritische auseinandersetzung}
 
@@
 we calculate that 46.6\% of the violations are raised by \emph{complex constraints} of all vocabularies.
+\ke{Prozentwerte kann man nicht normalisieren...
+Du musst auch nicht erklären, wie man normalisiert, schon gar nicht mit Rechenbeispiel.
+"...
+and 10 million Disco triples.
+Therefore, we only use normalized relative values representing the percentage of constraints and constraint violations belonging to the respective class.}
+
 %by building the arithmetic mean over the individual vocabularies' percentage values. 

### 2015-04-29 paper/paper7/paper7.tex
evaluation

--- 2015-04-29 paper/paper7/paper7.tex
@@
 We distinct two classes of vocabularies: 
-(1) established vocabularies (e.g., \emph{QB}, \emph{SKOS}) which are widely adopted and accepted and 
+(1) well-established vocabularies (e.g., \emph{QB}, \emph{SKOS}) which are widely adopted and accepted and 
 (2) newly developed vocabularies (e.g., \emph{Disco} which will be published in 2015) which are either recently published or are still in the publication process.
@@
 as these hypotheses still have to be verified or falsified in terms of future work 
-by evaluating the quality of data represented by additional established and newly developed vocabularies.
+by evaluating the quality of data represented by additional well-established and newly developed vocabularies.
 
@@
 \begin{hyp}
-A significant amount of 46 \% of the constraints are directly extractable from formal specifications of established and newly defined vocabularies. 
+A significant amount of 46 \% of the constraints are directly extractable from formal specifications of well-established and newly defined vocabularies. 
 \end{hyp}
@@
 \begin{hyp}
-For established vocabularies, vocabulary constraints caused nearly 0\% of all violations\footnote{e.g. only 1.777 \emph{QB} violations}
-which indicates good data quality (according to formal specifications of vocabularies). 
+For well-established vocabularies, vocabulary constraints are almost completely satisfied\footnote{e.g.
+only 1.777 \emph{QB} violations} which indicates good data quality (according to formal specifications of vocabularies) and which demonstrates that constraint formulation in general works.
 For newly defined vocabularies, however, 2/3 of all violations are raised by vocabulary constraints
@@
 \begin{hyp}
-For established vocabularies, the data quality is high,
+For well-established vocabularies, data quality is high
 as serious violations rarely appear.
-For newly developed vocabularies, data quality is worse,
+For newly developed vocabularies, data quality is worse
 as serious violations occur partially.
-\end{hyp}
-
-\begin{hyp}
-For well-established vocabularies, the explicitly defined constraints are almost completely satisfied which demonstrates that constraint formulation in general works.
 \end{hyp}
@@
 
-\tb{difference between 0\% and 78.6\%}
-
-\tb{it has to be ensured that constraints within a particular set are not violated randomly  
-in case there are only a few constraints within a set}
-
 \tb{established vocabularies meet vocabulary constraints / data sets represented by established vocabularies meet vocabulary constraints which indicates good data quality}

### 2015-04-29 paper/paper7/paper7.tex

@@
 \label{rdf-representation}
-
+\tb{jeweils ein satz zu DCAT und XKOS}
 %In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.
@@
 of 53 different types on six vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classified them according to the complexity level of their type and their severity level.
+\ke{Alle vokabulare in section "vocabularies" eingeführt?}\tb{mache ich}
 For 114 of these constraints, we evaluated the data quality of 15,694 data sets (4,26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
@@
 by evaluating the quality of data represented by additional well-established and newly developed vocabularies.
+\ke{das ist zu früh finde um schon einzuschränken, erst mal ergebnisse, dann hypothesen, dann kritische auseinandersetzung}
 
@@
 To be able to formulate hypotheses which apply for all vocabularies, 
-we normalize the total percentage values.
-As, e.g., 18\% of the \emph{Disco}, 100\% of the \emph{QB}, and 21\% of the \emph{SKOS} violations are caused by \emph{complex constraints},  
-we calculate that 46.6\% of the violations are raised by \emph{complex constraints} of all vocabularies.
+we only use normalized relative values representing the percentage of constraints and constraint violations belonging to the respective class
+
 %by building the arithmetic mean over the individual vocabularies' percentage values. 
@@
 %\emph{Existential quantifications} (\emph{R-86}, 32.4\%, \emph{Disco}), \emph{data model consistency} (31.4\%, \emph{QB}), and \emph{structure} (28.6\%, \emph{SKOS}) are the constraint types the most constraints are instantiated from.
+
+\tb{Ich würde zu Beginn der Auswertung, nach den Tabellen, erklären, dass wir anhand der drei Vokabulare keine gesicherten allgemeinen Aussagen  machen können, aber dass wir im folgenden verschiedene Hypthesen aufstellen, die auf die Auswertung gestützt sind.
+/ ann also erst die Fakten berichten, wie zum Beispiel bestimmte Prozentwerte / Und dann die Hypothese als Schluss, z..B.
+dass die Datenqualität bezüglich in den etablierten Vokabularen hinterlegter Constraints sehr gut ist, was darauf hindeutet, dass das hinterlegen von constraints sinnvoll ist und von den datenanbietern auch beachtet wird.
+ganz eigentlich ist ja sogar nur das zweite unsere hypothese
+die datenqualität in unserem sample IST gut, das ist auch keine hypothese / es muss halt klar werden, dass wir die hypothese im anschluss nicht beweisen, sondern dass wir sie lediglich postulieren, allerdings nicht komplett aus der luft sondern als interpretation unserer ergebnisse / Was zwar kein beweis ist wegen geringer zahl der vokabulare, aber eben auch nicht nix}
 
@@
 
-\tb{established vocabularies meet vocabulary constraints / data sets represented by established vocabularies meet vocabulary constraints which indicates good data quality}
-
-\tb{QB data sets contain data and metadata and therefore there are the differences between constraint violations}
-
 %The constraints responsible for the largest amounts of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916; \emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102; \emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903; \emph{SKOS}).

### 2015-04-30 paper/paper7/paper7.tex
abstract, intro

@@
 \renewcommand{\arraystretch}{1.3}
-%
-%
-%\title{RDF Validation of Metadata \\ on Person-Level and Aggregated Data}
-%\title{RDF Constraints to Ensure High Quality \\ of Metadata and Data Represented by any Vocabulary }
-%\title{RDF Constraints to Ensure High Quality \\ of Metadata and Data}
 \title{Aspects of RDF Data Constraints in the Social, Behavioural and Economic Sciences}
@@
 particularly as this is taken for granted in the XML world.
-%The data most often used in research within the community around research data for the social, behavioural, and economic sciences (\emph{SBE}) is person-level data, i.e., data collected about individuals (households, businesses).
-%%The DDI-RDF Discovery Vocabulary is used to describe and to discover this kind of research data.
-%While performing research, the detailed, often access restricted person-level
-%data is aggregated into less confidential publicly available multi-dimensional tables which answer particular research questions and whose purpose is to gain an interest in further more detailed analyses on the underlying person-level data.
-To ensure high quality and trust, both metadata and data must satisfy certain criteria - specified in terms of RDF constraints. 
-%From 2012 to 2015 together with other Linked Data community members and \emph{SBE} experts, we developed diverse vocabularies to represent \emph{SBE} metadata and data in RDF.
-
 Based on our work in the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group, we identified and published by today 82 types of constraints that are required by various stakeholders for data applications.
-
 In this paper, we formulate 246 constraints of 53 different types on six different vocabularies (Disco, QB, SKOS, PHDD, DCAT, XKOS) and classify them according to the complexity level of their type and their severity level.
 For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4,26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.
-
-Based on the results, we postulate and discuss findings, like: (1) for well-established vocabularies, the explicitly defined constraints are almost completely satisfied which demonstrates that constraint formulation in general works.
+Based on the results, we formulate several hypotheses to direct the further development of constraint langugaes.
+
+\keywords{Constraint Validation, Data Quality, RDF}
+\end{abstract}
+
+\section{Introduction}
+
+%%% Findings aus dem Abstract
+%%% (1) for well-established vocabularies, the explicitly defined constraints are almost completely satisfied which demonstrates that constraint formulation in general works.
 (2) A significant amount of 47\% of the violations refer to complex constraints that are not easily expressible in existing languages which confirms the necessity to provide suitable constraint languages.
@@
 
-%The \textbf{contribution} of this paper is the development of a system 
-%(1) to classify RDF constraints (according to their severity levels) to evaluate the quality of (meta)data which may be represented by any vocabulary and 
-%(2) to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements.
-%By defining a huge amount of constraints of the majority of constraint types
-%to validate data sets from the community around research data for the \emph{social, behavioural, and economic (SBE) sciences},  
-%we prove the claim that the proposed classification system perfectly applies vocabulary-independent and therefore we prove its generality.
-%
-%We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple vocabularies to get an understanding
-%(1) which sets of constraint types (on different levels of complexity) and 
-%(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations.
-
-\keywords{RDF Validation, RDF Constraints, Metadata Quality, Data Quality, Tabular Data, DDI-RDF Discovery Vocabulary, RDF Data Cube Vocabulary, SKOS, Thesauri, Linked Data, Semantic Web}
-\end{abstract}
-
-\section{Introduction}
-
+The social, behavioural, and economic sciences (SBE) require high-quality data for their empirical research.
 For more than a decade, members of the \emph{SBE} community have been developing and using a
@@
 %and ICPSR - the largest SBE data archive in the US.
-Increasingly, data professionals, data archives, data libraries, government statisticians (e.g. \url{data.gov}, \url{data.gov.uk}), and national statistical institutes
-are very interested in having their data be discovered and used by exposing their metadata (e.g.
-about unemployment rates or income\ke{wieso ist das metadata?
-Ich würde generell auch im text bei data bleiben, es sei denn, die unterscheidung von data und metadata ist relevant.}) within the Web of Linked Data.
-As \emph{DDI} XML documents are validated against diverse XSDs\footnote{\label{fnt:DDI-XSDs}\url{http://www.ddialliance.org/Specification/}} (see section \ref{related-work}),
-the \emph{SBE} community is used to have this functionality in the XML world.
-%Recently, members of the \emph{SBE} and Linked Data community developed the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}}, 
-%an effort to expose \emph{DDI} metadata within the Web of Linked Data. 
-%For data archives, research institutes, and data libraries,
-%RDF data validation according to predefined constraints is a much sought-after feature, 
-%particularly as this is taken for granted in the XML world. 
-%as DDI-XML documents are validated against diverse XSDs\footnote{\label{fnt:DDI-XSDs}\url{http://www.ddialliance.org/Specification/}} (section \ref{related-work}).
-Several languages exist to formulate and check constraints on RDF data, ranging from \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles} to using \emph{OWL 2} as a constraint language and the SPARQL-based \emph{SPIN}\footnote{\url{http://spinRDF.org/}}.
+
+In XML, the definition of schemas containing data constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
+
+With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration.
+Therefore, not only existing vocabularies like SKOS are used;
+recently, members of the \emph{SBE} and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.
+
+For constraint formulation and validation on RDF data, several languages exist, like \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles}.
+\emph{OWL 2} is also used as a constraint language under a closed world assumption.
+With its direct support of validation via SPARQL, \emph{SPIN}%\footnote{\url{http://spinRDF.org/}}
+is very popular and certainly plays an important role for future developments in this field.
 %that more or less explicitly address the \emph{SBE} community.
+
 In 2013, the W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 

### 2015-04-30 paper/paper7/paper7.tex
evaluation

--- 2015-04-29 paper/paper7/paper7.tex
@@
 \label{rdf-representation}
-\tb{jeweils ein satz zu DCAT und XKOS}
+\tb{Ich habe XKOS und DCAT noch ganz am Ende eingeführt (jeweils nur 1 Satz)}
 %In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.
 
-For our evaluation, we examined four different vocabularies commonly used in or developed for the SBE sciences which are briefly introduced in the following.
+For our evaluation, we examined six different vocabularies commonly used in or developed for the SBE sciences which are briefly introduced in the following.
 For three of them, we analysed actual data according to constraint violations.
-For PHDD, there is not yet enough data available so we limit our examination to the vocabulary itself.\ke{Neuer Absatz von mir...}
+For PHDD, there is not yet enough data available so we limit our examination to the vocabulary itself.
 
@@
 organize types (\emph{skos:Concept}) of descriptive statistics (\emph{disco:SummaryStatistics}) like minimum, maximum, and arithmetic mean.
-%\emph{XKOS}\footnote{\url{https://github.com/linked-statistics/xkos}} is a SKOS extension to describe formal statistical classifications like the International Standard Classification of Occupations (\emph{ISCO}).
-%and the Statistical Classification of Economic Activities in the European Community \emph{NACE}.
+\emph{XKOS}\footnote{\url{https://github.com/linked-statistics/xkos}} is a SKOS extension to describe formal statistical classifications like the International Standard Classification of Occupations (\emph{ISCO}).
+and the Statistical Classification of Economic Activities in the European Community \emph{NACE}.
+\emph{DCAT} enables to represent data sets inside of data collections like portals, repositories, catalogs, and archives
+which serve as typical entry points when searching for data.
 
 %\textbf{Searching for (Meta)data.}
-%\emph{DCAT} enables to represent aggregated and person-level data sets inside of data collections like portals, repositories, catalogs, and archives
+%\emph{DCAT} enables to represent data sets inside of data collections like portals, repositories, catalogs, and archives
 %which serve as typical entry points when searching for data.
@@
 of 53 different types on six vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classified them according to the complexity level of their type and their severity level.
-\ke{Alle vokabulare in section "vocabularies" eingeführt?}\tb{mache ich}
 For 114 of these constraints, we evaluated the data quality of 15,694 data sets (4,26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.

### 2015-04-30 paper/paper7/paper7.tex
evaluation

@@
 In this paper, we formulate 246 constraints of 53 different types on six different vocabularies (Disco, QB, SKOS, PHDD, DCAT, XKOS) and classify them according to the complexity level of their type and their severity level.
-For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4,26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.
-Based on the results, we formulate several hypotheses to direct the further development of constraint langugaes.
+For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.
+Based on the results, we formulate several hypotheses to direct the further development of constraint languages.
 
@@
 Note that the data represented in RDF can be data in the sense of SBE sciences, but also metadata about published or unpublished data.
-We generally refer to both simply as RDF data and only distinguish between data and metadata in the dataset descriptions and in the case that it matters for the purpose of this paper.\tb{hab ich eingefügt, ist der absatz von dir...}
+We generally refer to both simply as RDF data and only distinguish between data and metadata in the data set descriptions and in the case that it matters for the purpose of this paper.
 
@@
 %As constraint types are used to define constraints on (meta)data expressed by any vocabulary, the proposed constraint classification can be applied generically, i.e. vocabulary-independent.
-
-\ke{in guter tradition unserer arbeitsgruppe würde ich mich als senior researcher um die einleitung kümmern, die gefällt mir so nicht}\tb{sehr gerne}
 
@@
 of 53 different types on six vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classified them according to the complexity level of their type and their severity level.
-For 114 of these constraints, we evaluated the data quality of 15,694 data sets (4,26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
+For 114 of these constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
 We distinct two classes of vocabularies: 
@@
 %and that early adopters did not properly understand its formal specification.
-Based on this evaluation we formulate hypotheses.
-Nevertheless, we have to be careful making general statements for all vocabularies 
-as these hypotheses still have to be verified or falsified in terms of future work 
-by evaluating the quality of data represented by additional well-established and newly developed vocabularies.
-\ke{das ist zu früh finde um schon einzuschränken, erst mal ergebnisse, dann hypothesen, dann kritische auseinandersetzung}
+\ke{ergebnisse, dann hypothesen, dann kritische auseinandersetzung}
 
@@
 \end{table}
+
+Based on the results, we formulate several hypotheses to direct the further development of constraint languages.
+Nevertheless, we have to be careful making general statements for all vocabularies 
+as these hypotheses still have to be verified or falsified in terms of future work 
+by evaluating the quality of data represented by additional well-established and newly developed vocabularies.
 

### 2015-04-30 paper/paper7/paper7.tex
evaluation

@@
 
-Based on the results, we formulate several hypotheses to direct the further development of constraint languages.
-Nevertheless, we have to be careful making general statements for all vocabularies 
-as these hypotheses still have to be verified or falsified in terms of future work 
+Based on the evaluation results on three vocabularies, 
+we cannot make valid general statements for all vocabularies,
+but we can formulate several hypotheses to direct the further development of constraint languages.
+As these hypotheses cannot be proved yet, 
+they still have to be verified or falsified in terms of future work 
 by evaluating the quality of data represented by additional well-established and newly developed vocabularies.
@@
 
-\tb{Ich würde zu Beginn der Auswertung, nach den Tabellen, erklären, dass wir anhand der drei Vokabulare keine gesicherten allgemeinen Aussagen  machen können, aber dass wir im folgenden verschiedene Hypthesen aufstellen, die auf die Auswertung gestützt sind.
-/ ann also erst die Fakten berichten, wie zum Beispiel bestimmte Prozentwerte / Und dann die Hypothese als Schluss, z..B.
+\tb{ann also erst die Fakten berichten, wie zum Beispiel bestimmte Prozentwerte / Und dann die Hypothese als Schluss, z..B.
 dass die Datenqualität bezüglich in den etablierten Vokabularen hinterlegter Constraints sehr gut ist, was darauf hindeutet, dass das hinterlegen von constraints sinnvoll ist und von den datenanbietern auch beachtet wird.
 ganz eigentlich ist ja sogar nur das zweite unsere hypothese
-die datenqualität in unserem sample IST gut, das ist auch keine hypothese / es muss halt klar werden, dass wir die hypothese im anschluss nicht beweisen, sondern dass wir sie lediglich postulieren, allerdings nicht komplett aus der luft sondern als interpretation unserer ergebnisse / Was zwar kein beweis ist wegen geringer zahl der vokabulare, aber eben auch nicht nix}
+die datenqualität in unserem sample IST gut, das ist auch keine hypothese}
 

### 2015-04-30 paper/paper7/paper7.tex
evaluation

@@
 
-Based on the evaluation results on three vocabularies, 
+As the evaluation is based on three vocabularies, 
 we cannot make valid general statements for all vocabularies,
@@
 As these hypotheses cannot be proved yet, 
-they still have to be verified or falsified in terms of future work 
-by evaluating the quality of data represented by additional well-established and newly developed vocabularies.
+they still have to be verified or falsified
+by evaluating the quality of data represented by further well-established and newly developed vocabularies.
 
@@
 
-\tb{ann also erst die Fakten berichten, wie zum Beispiel bestimmte Prozentwerte / Und dann die Hypothese als Schluss, z..B.
-dass die Datenqualität bezüglich in den etablierten Vokabularen hinterlegter Constraints sehr gut ist, was darauf hindeutet, dass das hinterlegen von constraints sinnvoll ist und von den datenanbietern auch beachtet wird.
-ganz eigentlich ist ja sogar nur das zweite unsere hypothese
-die datenqualität in unserem sample IST gut, das ist auch keine hypothese}
+\tb{1. Fakten (diese Fakten bewirken eine Erhöhung der Datenqualität) 2. Hypothese (unsere Interpretation der Ergebnisse, unsere Behauptung)}
 
@@
 2/3 of the \emph{Disco} violations result from \emph{vocabulary constraints},
-almost only \emph{complex constraints} raised \emph{QB} violations, and 
+\emph{QB} violations are almost only raised by \emph{complex constraints}, and 
 nearly 80\% of the \emph{SKOS} violations are caused by \emph{simple constraints}.
+For well-established vocabularies, vocabulary constraints are almost completely satisfied\footnote{e.g.
+only 1.777 \emph{QB} violations} which indicates good data quality according to formal specifications of vocabularies.
+This demonstrates that data providers take account of the formal specifications of well-established vocabularies and therefore constraint formulation in general works.
+For newly defined vocabularies, however, 2/3 of all violations are raised by vocabulary constraints
+which indicates bad data quality with regard to the formal specifications of newly defined vocabularies.
 
 \begin{hyp}
-For well-established vocabularies, vocabulary constraints are almost completely satisfied\footnote{e.g.
-only 1.777 \emph{QB} violations} which indicates good data quality (according to formal specifications of vocabularies) and which demonstrates that constraint formulation in general works.
-For newly defined vocabularies, however, 2/3 of all violations are raised by vocabulary constraints
-which indicates good data quality (according to formal specifications of vocabularies).
+Data represented by well-established vocabularies corresponds to formal specifications of these vocabularies which demonstrates that constraint formulation in general works. 
 \end{hyp}
 
-It is likely that a newly developed vocabulary is still subject of constant change, 
-that published data may not be consistent with its current version,
+\begin{hyp}
+Data represented by newly developed vocabularies, in contrast, does not correspond to formal specifications of these vocabularies.
+\end{hyp}
+
+It is likely that a newly developed vocabulary is still subject of constant change
 and that early adopters did not properly understand its formal specification.
+Thus, published data may not be consistent with its current version.
+In case newly developed vocabularies turn into well-established ones,
+their formal specifications and intended semantics will be clearer to data providers as the community will also have more experience in publishing data conforming to this vocabulary. 
+As a consequence, vocabulary constraints will be satisfied leading to better data quality.
 

### 2015-04-30 paper/paper7/paper7.tex
evaluation

@@
 nearly 80\% of the \emph{SKOS} violations are caused by \emph{simple constraints}.
-For well-established vocabularies, vocabulary constraints are almost completely satisfied\footnote{e.g.
+For well-established vocabularies, \emph{vocabulary constraints} are almost completely satisfied\footnote{e.g.
 only 1.777 \emph{QB} violations} which indicates good data quality according to formal specifications of vocabularies.
-This demonstrates that data providers take account of the formal specifications of well-established vocabularies and therefore constraint formulation in general works.
-For newly defined vocabularies, however, 2/3 of all violations are raised by vocabulary constraints
-which indicates bad data quality with regard to the formal specifications of newly defined vocabularies.
+%This demonstrates that data providers take account of the formal specifications of well-established vocabularies.
+For newly defined vocabularies, however, 2/3 of all violations are raised by \emph{vocabulary constraints}
+which indicates bad data quality with regard to the formal specifications of vocabularies.
 
@@
 Data represented by well-established vocabularies corresponds to formal specifications of these vocabularies which demonstrates that constraint formulation in general works. 
-\end{hyp}
-
-\begin{hyp}
 Data represented by newly developed vocabularies, in contrast, does not correspond to formal specifications of these vocabularies.
@@
 and that early adopters did not properly understand its formal specification.
-Thus, published data may not be consistent with its current version.
+Thus, published data may not be consistent with its current draft or version.
 In case newly developed vocabularies turn into well-established ones,
-their formal specifications and intended semantics will be clearer to data providers as the community will also have more experience in publishing data conforming to this vocabulary. 
-As a consequence, vocabulary constraints will be satisfied leading to better data quality.
+data providers are experienced in publishing their data represented by these vocabularies, 
+the formal specifications are more elaborated and therefore clearer to data providers. 
+As a consequence, vocabulary constraints are satisfied which leads to better data quality.
 

### 2015-04-30 paper/paper7/paper7.tex
evaluation

@@
 %and that early adopters did not properly understand its formal specification.
-\ke{ergebnisse, dann hypothesen, dann kritische auseinandersetzung}
+%\ke{ergebnisse, dann hypothesen, dann kritische auseinandersetzung}
 
@@
 
-\tb{1. Fakten (diese Fakten bewirken eine Erhöhung der Datenqualität) 2. Hypothese (unsere Interpretation der Ergebnisse, unsere Behauptung)}
+%\tb{1. Fakten (diese Fakten bewirken eine Erhöhung der Datenqualität) 2. Hypothese (unsere Interpretation der Ergebnisse, unsere Behauptung)}
 
 Almost 1/2 of all 213 constraints and more than 50\% of the \emph{Disco} and the \emph{QB} constraints are \emph{vocabulary constraints}.
-The \emph{SKOS} constraints are equally distributed among the three disjoint sets of constraint types. 
+The \emph{SKOS} constraints are nearly to the same extend \emph{vocabulary}, \emph{simple}, and \emph{complex constraints}. 
+Hence, a significant amount of 46 \% of the constraints are directly extractable from formal specifications of well-established and newly defined vocabularies. 
 \begin{hyp}
-A significant amount of 46 \% of the constraints are directly extractable from formal specifications of well-established and newly defined vocabularies. 
+As vocabulary constraints can be expressed by modeling languages like RDF, RDFS, and OWL 2,
+the further development of constraint languages should concentrate on expressing simple and especially complex constraints which in most cases can only be expressed by plain SPARQL.   
 \end{hyp}
@@
 In case newly developed vocabularies turn into well-established ones,
-data providers are experienced in publishing their data represented by these vocabularies, 
-the formal specifications are more elaborated and therefore clearer to data providers. 
+data providers are experienced in publishing their data in conformance with these vocabularies, 
+and the formal specifications are more elaborated and therefore clearer. 
 As a consequence, vocabulary constraints are satisfied which leads to better data quality.

### 2015-04-30 paper/paper7/paper7.tex
evaluation

@@
 The \emph{SKOS} constraints are nearly to the same extend \emph{vocabulary}, \emph{simple}, and \emph{complex constraints}. 
-Hence, a significant amount of 46 \% of the constraints are directly extractable from formal specifications of well-established and newly defined vocabularies. 
+%Hence, a significant amount of 46 \% of the constraints are directly extractable from formal specifications of well-established and newly defined vocabularies. 
 \begin{hyp}
-As vocabulary constraints can be expressed by modeling languages like RDF, RDFS, and OWL 2,
-the further development of constraint languages should concentrate on expressing simple and especially complex constraints which in most cases can only be expressed by plain SPARQL.   
+As a significant amount of 46 \% of the constraints are vocabulary constraints which can be expressed by modeling languages like RDF, RDFS, and OWL 2,
+the further development of constraint languages should concentrate on expressing simple and especially complex constraints which up to now in most cases can only be expressed by plain SPARQL.   
 \end{hyp}

### 2015-04-30 paper/paper7/paper7.tex
evaluation

@@
 Nearly 1/2 of the violations are caused by \emph{complex constraints}, 1/3 by \emph{simple constraints}, and 1/5 by \emph{vocabulary constraints}.
-
-\begin{hyp}
 The fact that only 1/5 of all violations result from vocabulary constraints, 
 even though, 46\% of all constraints are vocabulary constraints,
-indicates good data quality in general (according to formal specifications of vocabularies).
+indicates good data quality in general with regard to the formal specifications of vocabularies.
+\begin{hyp}
+For all vocabularies, data corresponds to their formal specifications which demonstrates that constraint formulation in general works. 
 \end{hyp}

### 2015-04-30 paper/paper7/paper7.tex
evaluation

@@
 
-Nearly 1/2 of the violations are caused by \emph{complex constraints}, 1/3 by \emph{simple constraints}, and 1/5 by \emph{vocabulary constraints}.
-The fact that only 1/5 of all violations result from vocabulary constraints, 
-even though, 46\% of all constraints are vocabulary constraints,
-indicates good data quality in general with regard to the formal specifications of vocabularies.
+Nearly 1/2 of all violations are caused by \emph{complex constraints}, 1/3 by \emph{simple constraints}, and 1/5 by \emph{vocabulary constraints}.
+The fact that only 1/5 of all violations result from \emph{vocabulary constraints}, 
+even though, 46\% of all constraints are \emph{vocabulary constraints},
+indicates good data quality for all vocabularies with regard to their formal specifications.
 \begin{hyp}

### 2015-04-30 paper/paper7/paper7.tex
evaluation

@@
 
-\begin{hyp}
-A significant amount of 47\% of the violations refer to complex constraints that are not easily expressible in existing languages which confirms the necessity to provide suitable constraint languages.
-\end{hyp} 
-\emph{Vocabulary} and \emph{simple constraints} can be expressed easily, concisely, and intuitively by either modeling languages (e.g., \emph{RDF}, \emph{RDFS}, \emph{OWL 2}) or constraint languages (e.g., \emph{ShEx}, \emph{ReSh}, \emph{SPIN}).
-This is not the case, however, for \emph{complex constraints} which in most cases still can only be expressed by plain \emph{SPARQL}. 
-As almost 1/2 of all violations are caused by \emph{complex constraints}, 
-data quality can be significantly improved when \emph{complex constraints} can also be expressed more easily, concisely, and intuitively.
-Therefore, existing constraint languages have to be extended or new constraint languages have to be developed.
-
-63\% of all violations are caused by \emph{warning constraints} which are only 10\% of all constraints. 
-Only 6\% of the violations are caused by \emph{error constraints} which are 49\% of all constraints.
-
-\begin{hyp}
-In general, data quality is high (according to severity levels) since only 6\% of the violations are caused by error constraints which are 49\% of all defined constraints.
-\end{hyp}
-
-\begin{hyp}
-The percentage of severe violations is very low (6\%), compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
-\end{hyp}
-
 \begin{table}[H]
@@
 \end{table}
+
+\begin{hyp}
+A significant amount of 47\% of the violations refer to complex constraints that are not easily, concisely, and intuitively expressible in existing constraint languages which confirms the necessity to provide suitable constraint languages.
+\end{hyp} 
+In general, \emph{vocabulary} and \emph{simple constraints} are easily, concisely, and intuitively expressible by either modeling languages (e.g., \emph{RDF}, \emph{RDFS}, \emph{OWL 2}) or constraint languages (e.g., \emph{ShEx}, \emph{ReSh}, \emph{SPIN}).
+This is not the case, however, for \emph{complex constraints} which in most cases are still only expressible by plain \emph{SPARQL}. 
+As almost 1/2 of all violations are caused by \emph{complex constraints}, 
+data quality can be significantly improved when suitable constraint languages are developed which enable to define \emph{complex constraints} in an easy, concise, and intuitive way.
+%Therefore, existing constraint languages have to be extended or new constraint languages have to be developed.
+
+63\% of all violations are caused by \emph{warning constraints} which are only 10\% of all constraints. 
+Only 6\% of the violations are caused by \emph{error constraints} which are 49\% of all constraints.
+
+\begin{hyp}
+In general, data quality is high (according to severity levels) since only 6\% of the violations are caused by error constraints which are 49\% of all defined constraints.
+\end{hyp}
+
+\begin{hyp}
+The percentage of severe violations is very low (6\%), compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
+\end{hyp}
 

### 2015-04-30 paper/paper7/paper7.tex
evaluation

@@
 
+\begin{hyp}
+A significant amount of 47\% of the violations refer to complex constraints that are not easily, concisely, and intuitively expressible in existing constraint languages which confirms the necessity to provide suitable constraint languages.
+\end{hyp} 
+In general, \emph{vocabulary} and \emph{simple constraints} are easily, concisely, and intuitively expressible by either modeling languages (e.g., \emph{RDF}, \emph{RDFS}, \emph{OWL 2}) or constraint languages (e.g., \emph{ShEx}, \emph{ReSh}, \emph{SPIN}).
+This is not the case, however, for \emph{complex constraints} which in most cases are still only expressible by plain \emph{SPARQL}. 
+As almost 1/2 of all violations are caused by \emph{complex constraints}, 
+data quality can be significantly improved when suitable constraint languages are developed which enable to define \emph{complex constraints} in an easy, concise, and intuitive way.
+%Therefore, existing constraint languages have to be extended or new constraint languages have to be developed.
+
 \begin{table}[H]
@@
 
+2/3 of all violations are caused by \emph{warning constraints} which are only 10\% of all constraints. 
+Only 6\% of the violations are caused by \emph{error constraints} which are 49\% of all constraints.
+1/3 of all violations are raised by informational constraints.
+This means that in general, data quality is high with regard to the severity level of constraints.
+
 \begin{hyp}
-A significant amount of 47\% of the violations refer to complex constraints that are not easily, concisely, and intuitively expressible in existing constraint languages which confirms the necessity to provide suitable constraint languages.
-\end{hyp} 
-In general, \emph{vocabulary} and \emph{simple constraints} are easily, concisely, and intuitively expressible by either modeling languages (e.g., \emph{RDF}, \emph{RDFS}, \emph{OWL 2}) or constraint languages (e.g., \emph{ShEx}, \emph{ReSh}, \emph{SPIN}).
-This is not the case, however, for \emph{complex constraints} which in most cases are still only expressible by plain \emph{SPARQL}. 
-As almost 1/2 of all violations are caused by \emph{complex constraints}, 
-data quality can be significantly improved when suitable constraint languages are developed which enable to define \emph{complex constraints} in an easy, concise, and intuitive way.
-%Therefore, existing constraint languages have to be extended or new constraint languages have to be developed.
-
-63\% of all violations are caused by \emph{warning constraints} which are only 10\% of all constraints. 
-Only 6\% of the violations are caused by \emph{error constraints} which are 49\% of all constraints.
-
-\begin{hyp}
-In general, data quality is high (according to severity levels) since only 6\% of the violations are caused by error constraints which are 49\% of all defined constraints.
-\end{hyp}
-
-\begin{hyp}
-The percentage of severe violations is very low (6\%), compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
+The percentage of severe violations is very low, compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
 \end{hyp}

### 2015-04-30 paper/paper7/paper7.tex
evaluation

@@
 by evaluating the quality of data represented by further well-established and newly developed vocabularies.
-
 %More than the half of them are $\mathcal{CT}_{B}$, nearly a third $\mathcal{CT}_{S}$, and only a sixth $\mathcal{CT}_{C}$ constraint types.
@@
 %\emph{Existential quantifications} (\emph{R-86}, 32.4\%, \emph{Disco}), \emph{data model consistency} (31.4\%, \emph{QB}), and \emph{structure} (28.6\%, \emph{SKOS}) are the constraint types the most constraints are instantiated from.
-
 %\tb{1. Fakten (diese Fakten bewirken eine Erhöhung der Datenqualität) 2. Hypothese (unsere Interpretation der Ergebnisse, unsere Behauptung)}
-
 Almost 1/2 of all 213 constraints and more than 50\% of the \emph{Disco} and the \emph{QB} constraints are \emph{vocabulary constraints}.
@@
 
-2/3 of all violations are caused by \emph{warning constraints} which are only 10\% of all constraints. 
-Only 6\% of the violations are caused by \emph{error constraints} which are 49\% of all constraints.
-1/3 of all violations are raised by informational constraints.
-This means that in general, data quality is high with regard to the severity level of constraints.
+1/2 of all constraints are \emph{error constraints} and
+10\% of all constraints are \emph{warning constraints}.
+\emph{Informational constraints} caused 1/3 and
+\emph{warning constraints} 2/3 of all violations.
+As the percentage of severe violations is very low for all vocabularies,
+data quality is high with regard to the severity level of constraints.
 

### 2015-04-30 paper/paper7/paper7.tex
evaluation

@@
 %Therefore, existing constraint languages have to be extended or new constraint languages have to be developed.
+1/2 of all constraints are \emph{error constraints} and
+10\% of all constraints are \emph{warning constraints}.
+\emph{Informational constraints} caused 1/3 and
+\emph{warning constraints} 2/3 of all violations.
+As the percentage of severe violations is very low for all vocabularies,
+data quality is high with regard to the severity level of constraints.
+
+\begin{hyp}
+The percentage of severe violations is very low, compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
+\end{hyp}
 
@@
 
-1/2 of all constraints are \emph{error constraints} and
-10\% of all constraints are \emph{warning constraints}.
-\emph{Informational constraints} caused 1/3 and
-\emph{warning constraints} 2/3 of all violations.
-As the percentage of severe violations is very low for all vocabularies,
-data quality is high with regard to the severity level of constraints.
-
-\begin{hyp}
-The percentage of severe violations is very low, compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
-\end{hyp}
-
-80\% of the \emph{QB} constraints are error constraints.
-More than 50\% of the \emph{Disco} and \emph{SKOS} constraints, however, are informational constraints.
-1/6 of the Disco violations are caused by error constraints.
-Almost all \emph{QB} violations and 59\% of the \emph{SKOS} violations are caused by warning constraints.  
-\begin{hyp}
+80\% of the \emph{QB} constraints are \emph{error constraints}.
+More than 50\% of the \emph{Disco} and \emph{SKOS} constraints, however, are \emph{informational constraints}.
+1/6 of the Disco violations are caused by \emph{error constraints} and
+almost all \emph{QB} violations and 59\% of the \emph{SKOS} violations are caused by \emph{warning constraints}.  
 For well-established vocabularies, data quality is high
@@
 as serious violations occur partially.
+Constraints are serious when they violate the integrity of vocabularies.
+For well-established vocabularies, it is well documented and the experience is high how to guarantee this integrity.
+This is not the case or newly-developed vocabularies.
+\begin{hyp}
+Especially for newly developed vocabularies, constraint languages should be used to a larger extend to meet severe constraints which guarantee their integrity.   
 \end{hyp}

### 2015-04-30 paper/paper7/paper7.tex
evaluation

@@
 \end{hyp}
-
-\begin{table}[H]
-		\scriptsize
-    \begin{center}
-    \begin{tabular}{@{}lcccccccc@{}}
-    %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
-    %\\  \cmidrule{2-3}
-		\hline
-    \multirow{2}{*}{} &
-      \multicolumn{2}{c}{\textbf{\emph{Disco}}} &
-      \multicolumn{2}{c}{\textbf{\emph{QB}}} &
-      \multicolumn{2}{c}{\textbf{\emph{SKOS}}} &
-      \multicolumn{2}{c}{\textbf{\emph{Total}}} \\
-    \textbf{} & C & CV & C & CV & C & CV & C & CV \\
-    \hline
-    %\\ \midrule
-		 & 143 & 3,575,002 & 35 & 45,635,861 & 35 & 5,540,988 & 213 & 54,751,851 \\
-		\hline
-		\textbf{\emph{complex}} & 25.9\% & 18.3\% & 37.1\% & \textbf{100\%} & \textbf{37.1\%} & 21.4\% & 33.4\% & \textbf{46.6\%} \\
-		\textbf{\emph{simple}} & 19.6\% & 15.7\% & 8.6\% & 0.0\% & \textbf{34.3\%} & \textbf{78.6\%} & 20.8\% & 31.4\% \\
-		\textbf{\emph{vocabulary}} & \textbf{54.6\%} & \textbf{66.1\%} & \textbf{54.3\%} & 0.0\% & \textbf{28.6\%} & 0.0\% & \textbf{45.8\%} & 22.0\% \\
-		%\hline
-		%\emph{CV (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 2,333,365 (65.3\%) & 1,777 (0\%) & 0 (0\%) & 2,335,142 (4.3\%) \\
-		%\emph{CV (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 28,000 (0.8\%) & 0 (0\%) & 0 (0\%) & 28,000 (0.1\%) \\
-		\hline
-		\textbf{\emph{info}} & \textbf{52.5\%} & \textbf{52.6\%} & 11.4\% & 0.0\% & \textbf{60.0\%} & 41.2\% & \textbf{41.3\%} & 31.3\% \\
-		\textbf{\emph{warning}} & 7.0\% & 29.4\% & 8.6\% & \textbf{99,8\%} & 14.3\% & \textbf{58.8\%} & 10.0\% & \textbf{62.7\%} \\
-		\textbf{\emph{error}} & 40.6\% & 18\% & \textbf{80.0\%} & 0.3\% & 25.7\% & 0.0\% & \textbf{48.8\%} & 6.1\%\\
-    \bottomrule
-    \end{tabular}
-    \\ \emph{C (constraints), CV (constraint violations)}
-    \caption{Constraints and Constraint Violations}
-		\label{tab:evaluation-constraint-violations}
-    \end{center}
-\end{table}
 
@@
 Table \ref{tab:evaluation-complexity-severity} shows the relation between the complexity and the severity level of all 213 constraints.
+More than 1/2 of the \emph{vocabulary constraints} are \emph{error constraints},
+more than 3/4 of the \emph{simple constraints} are \emph{informational constraints}, and
+\emph{complex constraints} are to the same extend \emph{informational} or \emph{error constraints}.
 
@@
 \begin{hyp}
-More than the 1/2 of the vocabulary constraints are error constraints,
-more than 3/4 of the simple constraints are informational constraints, and
-complex constraints are either informational or error constraints. 
+The further development of constraint languages should concentrate on how to express complex constraints as 44\% of all complex constraints are also serious ones.
 \end{hyp}
 
-As vocabulary constraints are directly extractable from vocabularies and therefore ensure the syntax and semantics of vocabularies,
-violations of vocabulary constraints are more severe than violations caused by simple constraints which are easily defined in addition to vocabulary constraints.
+As vocabulary constraints are contained within formal specifications of vocabularies and therefore directly ensure their syntax and semantics,
+violations of vocabulary constraints are more severe than violations caused by simple constraints which are not part of vocabularies.
 In many cases, complex constraints are also needed to express severe constraints which cannot be expressed by modeling languages.

### 2015-04-30 paper/paper7/paper7.tex
intro

--- 2015-04-30 paper/paper7/paper7.tex
@@
 In this paper, we formulate 246 constraints of 53 different types on six different vocabularies (Disco, QB, SKOS, PHDD, DCAT, XKOS) and classify them according to the complexity level of their type and their severity level.
-For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.
-Based on the results, we formulate several hypotheses to direct the further development of constraint languages.
+For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4,26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.
+\ke{check numbers}
+Based on the results, we formulate several hypotheses to direct the further development of constraint langugaes.
 
@@
 With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration.
-Therefore, not only existing vocabularies like SKOS are used;
+Therefore, not only established vocabularies like SKOS are used;
 recently, members of the \emph{SBE} and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.
 
-For constraint formulation and validation on RDF data, several languages exist, like \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles}.
+For constraint formulation and validation on RDF data, several languages exist or are currently developed, like \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles}.
 \emph{OWL 2} is also used as a constraint language under a closed world assumption.
@@
 is very popular and certainly plays an important role for future developments in this field.
-%that more or less explicitly address the \emph{SBE} community.
+It is particularly interesting as a means to validate arbitrary constraint languages by mapping them to SPARQL \cite{BoschEckert2014-2}.
+Yet, there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners.
+Further research and development therefore is needed.
 
@@
 In 2014, two working groups on RDF validation have been established to develop a language to express constraints on RDF data: 
-the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles task group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
-
-Bosch and Eckert \cite{BoschEckert2014} collected the findings of these working groups and initiated a database of RDF validation requirements
-which is available for contribution at \url{http://purl.org/net/rdf-validation}.
-The intention is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
-The requirements are classified to better evaluate existing solutions and each requirement is directly mapped to a constraint type which is expressible by at least one constraint language.
-As \emph{SPIN} is the within the RDF validation community accepted and widely adopted way to check constraints on RDF data, Bosch and Eckert \cite{BoschEckert2014-2} use \emph{SPIN} as basis to define a
-validation environment (available at \url{http://purl.org/net/rdfval-demo}) in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL.
-The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.
-
-%This paper aims to address two main \textbf{audiences}: 
-%(1) metadata practitioners seeking for how to represent metadata and data on different aggregation levels in RDF and
-%(2) metadata providers and harvesters ensuring high quality data and metadata by validating RDF data according to certain constraints.
+the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles task group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}} which among others bundles the requirements of data institutions of the cultural heritage and SBE sector and represents them in the W3C group.
+
+Within the DCMI task group, a collaboratively curated database of RDF validation requirements has been created which contains the findings of the working groups based on various case studies provided by data institutions \cite{BoschEckert2014}.
+It is publicly available and open for further contributions\footnote{Online at \url{http://purl.org/net/rdf-validation}}.
+
+The database connects requirements to use cases, case studies and implementations and forms the basis of this paper.
+To gain a better understanding about the role of certain requirements for data quality and in order to direct the further development of constraint langugaes, we collected constraints for commonly used vocabularies in the SBE domain, either from the vocabularies themselves or from domain and data experts.
+All in all, this lead to TODO constraints on TODO vocabularies.
+We let the experts classify the constraints according to the severity if they are violated.
+Furthermore, we classified the type of each constraint (corresponding to a requirement) based on its complexity ranging from types commonly found in vocabulary specificatons (e.g., domain and range), over types that are simply stated using common constraint languages (e.g., cardinality restrictions) to complex types that involve complex data structures or need more sophisticated langugaes to be easily expressible (e.g., constraints on network topologies).\ke{Thomas: Ok so?}
+
+As we do not want to base our conclusions on the evaluations of vocabularies and constraint definitions alone, we conducted a large-scale experiment and evaluated the data quality of 15,694 data sets (4,26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.
 
@@
 Note that the data represented in RDF can be data in the sense of SBE sciences, but also metadata about published or unpublished data.
-We generally refer to both simply as RDF data and only distinguish between data and metadata in the data set descriptions and in the case that it matters for the purpose of this paper.
+We generally refer to both simply as RDF data and only distinguish between data and metadata in the dataset descriptions and in the case that it matters for the purpose of this paper.\tb{hab ich eingefügt, ist der absatz von dir...}
 
@@
 %As constraint types are used to define constraints on (meta)data expressed by any vocabulary, the proposed constraint classification can be applied generically, i.e. vocabulary-independent.
+
+\ke{in guter tradition unserer arbeitsgruppe würde ich mich als senior researcher um die einleitung kümmern, die gefällt mir so nicht}\tb{sehr gerne}
 
@@
 \label{rdf-representation}
-\tb{Ich habe XKOS und DCAT noch ganz am Ende eingeführt (jeweils nur 1 Satz)}
+\tb{jeweils ein satz zu DCAT und XKOS}
 %In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.
 
-For our evaluation, we examined six different vocabularies commonly used in or developed for the SBE sciences which are briefly introduced in the following.
+For our evaluation, we examined four different vocabularies commonly used in or developed for the SBE sciences which are briefly introduced in the following.
 For three of them, we analysed actual data according to constraint violations.
-For PHDD, there is not yet enough data available so we limit our examination to the vocabulary itself.
+For PHDD, there is not yet enough data available so we limit our examination to the vocabulary itself.\ke{Neuer Absatz von mir...}
 
@@
 organize types (\emph{skos:Concept}) of descriptive statistics (\emph{disco:SummaryStatistics}) like minimum, maximum, and arithmetic mean.
-\emph{XKOS}\footnote{\url{https://github.com/linked-statistics/xkos}} is a SKOS extension to describe formal statistical classifications like the International Standard Classification of Occupations (\emph{ISCO}).
-and the Statistical Classification of Economic Activities in the European Community \emph{NACE}.
-\emph{DCAT} enables to represent data sets inside of data collections like portals, repositories, catalogs, and archives
-which serve as typical entry points when searching for data.
+%\emph{XKOS}\footnote{\url{https://github.com/linked-statistics/xkos}} is a SKOS extension to describe formal statistical classifications like the International Standard Classification of Occupations (\emph{ISCO}).
+%and the Statistical Classification of Economic Activities in the European Community \emph{NACE}.
 
 %\textbf{Searching for (Meta)data.}
-%\emph{DCAT} enables to represent data sets inside of data collections like portals, repositories, catalogs, and archives
+%\emph{DCAT} enables to represent aggregated and person-level data sets inside of data collections like portals, repositories, catalogs, and archives
 %which serve as typical entry points when searching for data.
@@
 of 53 different types on six vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classified them according to the complexity level of their type and their severity level.
-For 114 of these constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
+\ke{Alle vokabulare in section "vocabularies" eingeführt?}\tb{mache ich}
+For 114 of these constraints, we evaluated the data quality of 15,694 data sets (4,26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
 We distinct two classes of vocabularies: 
@@
 %and that early adopters did not properly understand its formal specification.
-%\ke{ergebnisse, dann hypothesen, dann kritische auseinandersetzung}
+Based on this evaluation we formulate hypotheses.
+Nevertheless, we have to be careful making general statements for all vocabularies 
+as these hypotheses still have to be verified or falsified in terms of future work 
+by evaluating the quality of data represented by additional well-established and newly developed vocabularies.
+\ke{das ist zu früh finde um schon einzuschränken, erst mal ergebnisse, dann hypothesen, dann kritische auseinandersetzung}
 
@@
 
-As the evaluation is based on three vocabularies, 
-we cannot make valid general statements for all vocabularies,
-but we can formulate several hypotheses to direct the further development of constraint languages.
-As these hypotheses cannot be proved yet, 
-they still have to be verified or falsified
-by evaluating the quality of data represented by further well-established and newly developed vocabularies.
 %More than the half of them are $\mathcal{CT}_{B}$, nearly a third $\mathcal{CT}_{S}$, and only a sixth $\mathcal{CT}_{C}$ constraint types.
@@
 %\emph{Existential quantifications} (\emph{R-86}, 32.4\%, \emph{Disco}), \emph{data model consistency} (31.4\%, \emph{QB}), and \emph{structure} (28.6\%, \emph{SKOS}) are the constraint types the most constraints are instantiated from.
-%\tb{1. Fakten (diese Fakten bewirken eine Erhöhung der Datenqualität) 2. Hypothese (unsere Interpretation der Ergebnisse, unsere Behauptung)}
+
+\tb{Ich würde zu Beginn der Auswertung, nach den Tabellen, erklären, dass wir anhand der drei Vokabulare keine gesicherten allgemeinen Aussagen  machen können, aber dass wir im folgenden verschiedene Hypthesen aufstellen, die auf die Auswertung gestützt sind.
+/ ann also erst die Fakten berichten, wie zum Beispiel bestimmte Prozentwerte / Und dann die Hypothese als Schluss, z..B.
+dass die Datenqualität bezüglich in den etablierten Vokabularen hinterlegter Constraints sehr gut ist, was darauf hindeutet, dass das hinterlegen von constraints sinnvoll ist und von den datenanbietern auch beachtet wird.
+ganz eigentlich ist ja sogar nur das zweite unsere hypothese
+die datenqualität in unserem sample IST gut, das ist auch keine hypothese / es muss halt klar werden, dass wir die hypothese im anschluss nicht beweisen, sondern dass wir sie lediglich postulieren, allerdings nicht komplett aus der luft sondern als interpretation unserer ergebnisse / Was zwar kein beweis ist wegen geringer zahl der vokabulare, aber eben auch nicht nix}
+
 Almost 1/2 of all 213 constraints and more than 50\% of the \emph{Disco} and the \emph{QB} constraints are \emph{vocabulary constraints}.
-The \emph{SKOS} constraints are nearly to the same extend \emph{vocabulary}, \emph{simple}, and \emph{complex constraints}. 
-%Hence, a significant amount of 46 \% of the constraints are directly extractable from formal specifications of well-established and newly defined vocabularies. 
+The \emph{SKOS} constraints are equally distributed among the three disjoint sets of constraint types. 
 \begin{hyp}
-As a significant amount of 46 \% of the constraints are vocabulary constraints which can be expressed by modeling languages like RDF, RDFS, and OWL 2,
-the further development of constraint languages should concentrate on expressing simple and especially complex constraints which up to now in most cases can only be expressed by plain SPARQL.   
+A significant amount of 46 \% of the constraints are directly extractable from formal specifications of well-established and newly defined vocabularies. 
 \end{hyp}
 
-Nearly 1/2 of all violations are caused by \emph{complex constraints}, 1/3 by \emph{simple constraints}, and 1/5 by \emph{vocabulary constraints}.
-The fact that only 1/5 of all violations result from \emph{vocabulary constraints}, 
-even though, 46\% of all constraints are \emph{vocabulary constraints},
-indicates good data quality for all vocabularies with regard to their formal specifications.
+Nearly 1/2 of the violations are caused by \emph{complex constraints}, 1/3 by \emph{simple constraints}, and 1/5 by \emph{vocabulary constraints}.
+
 \begin{hyp}
-For all vocabularies, data corresponds to their formal specifications which demonstrates that constraint formulation in general works. 
+The fact that only 1/5 of all violations result from vocabulary constraints, 
+even though, 46\% of all constraints are vocabulary constraints,
+indicates good data quality in general (according to formal specifications of vocabularies).
 \end{hyp}
@@
 2/3 of the \emph{Disco} violations result from \emph{vocabulary constraints},
-\emph{QB} violations are almost only raised by \emph{complex constraints}, and 
+almost only \emph{complex constraints} raised \emph{QB} violations, and 
 nearly 80\% of the \emph{SKOS} violations are caused by \emph{simple constraints}.
-For well-established vocabularies, \emph{vocabulary constraints} are almost completely satisfied\footnote{e.g.
-only 1.777 \emph{QB} violations} which indicates good data quality according to formal specifications of vocabularies.
-%This demonstrates that data providers take account of the formal specifications of well-established vocabularies.
-For newly defined vocabularies, however, 2/3 of all violations are raised by \emph{vocabulary constraints}
-which indicates bad data quality with regard to the formal specifications of vocabularies.
 
 \begin{hyp}
-Data represented by well-established vocabularies corresponds to formal specifications of these vocabularies which demonstrates that constraint formulation in general works. 
-Data represented by newly developed vocabularies, in contrast, does not correspond to formal specifications of these vocabularies.
+For well-established vocabularies, vocabulary constraints are almost completely satisfied\footnote{e.g.
+only 1.777 \emph{QB} violations} which indicates good data quality (according to formal specifications of vocabularies) and which demonstrates that constraint formulation in general works.
+For newly defined vocabularies, however, 2/3 of all violations are raised by vocabulary constraints
+which indicates good data quality (according to formal specifications of vocabularies).
 \end{hyp}
 
-It is likely that a newly developed vocabulary is still subject of constant change
+It is likely that a newly developed vocabulary is still subject of constant change, 
+that published data may not be consistent with its current version,
 and that early adopters did not properly understand its formal specification.
-Thus, published data may not be consistent with its current draft or version.
-In case newly developed vocabularies turn into well-established ones,
-data providers are experienced in publishing their data in conformance with these vocabularies, 
-and the formal specifications are more elaborated and therefore clearer. 
-As a consequence, vocabulary constraints are satisfied which leads to better data quality.
 
 \begin{hyp}
-A significant amount of 47\% of the violations refer to complex constraints that are not easily, concisely, and intuitively expressible in existing constraint languages which confirms the necessity to provide suitable constraint languages.
+A significant amount of 47\% of the violations refer to complex constraints that are not easily expressible in existing languages which confirms the necessity to provide suitable constraint languages.
 \end{hyp} 
-In general, \emph{vocabulary} and \emph{simple constraints} are easily, concisely, and intuitively expressible by either modeling languages (e.g., \emph{RDF}, \emph{RDFS}, \emph{OWL 2}) or constraint languages (e.g., \emph{ShEx}, \emph{ReSh}, \emph{SPIN}).
-This is not the case, however, for \emph{complex constraints} which in most cases are still only expressible by plain \emph{SPARQL}. 
+\emph{Vocabulary} and \emph{simple constraints} can be expressed easily, concisely, and intuitively by either modeling languages (e.g., \emph{RDF}, \emph{RDFS}, \emph{OWL 2}) or constraint languages (e.g., \emph{ShEx}, \emph{ReSh}, \emph{SPIN}).
+This is not the case, however, for \emph{complex constraints} which in most cases still can only be expressed by plain \emph{SPARQL}. 
 As almost 1/2 of all violations are caused by \emph{complex constraints}, 
-data quality can be significantly improved when suitable constraint languages are developed which enable to define \emph{complex constraints} in an easy, concise, and intuitive way.
-%Therefore, existing constraint languages have to be extended or new constraint languages have to be developed.
+data quality can be significantly improved when \emph{complex constraints} can also be expressed more easily, concisely, and intuitively.
+Therefore, existing constraint languages have to be extended or new constraint languages have to be developed.
+
+63\% of all violations are caused by \emph{warning constraints} which are only 10\% of all constraints. 
+Only 6\% of the violations are caused by \emph{error constraints} which are 49\% of all constraints.
+
+\begin{hyp}
+In general, data quality is high (according to severity levels) since only 6\% of the violations are caused by error constraints which are 49\% of all defined constraints.
+\end{hyp}
+
+\begin{hyp}
+The percentage of severe violations is very low (6\%), compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
+\end{hyp}
 
@@
 \end{table}
-
-1/2 of all constraints are \emph{error constraints} and
-10\% of all constraints are \emph{warning constraints}.
-\emph{Informational constraints} caused 1/3 and
-\emph{warning constraints} 2/3 of all violations.
-As the percentage of severe violations is very low for all vocabularies,
-data quality is high with regard to the severity level of constraints.
-
-\begin{hyp}
-The percentage of severe violations is very low, compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
-\end{hyp}
 

### 2015-04-30 paper/paper7/paper7.tex

--- 2015-04-30 paper/paper7/paper7.tex
@@
 For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.
-Based on the results, we formulate several hypotheses to direct the further development of constraint languages.
+\ke{check numbers}
+Based on the results, we formulate several hypotheses to direct the further development of constraint langugaes.
 
@@
 
-The modeling languages \emph{RDF}, \emph{RDFS}, and \emph{OWL} are typically used to define vocabularies.
+The modeling languages \emph{RDF}, \emph{RDFS}, and \emph{OWL} are typically used to formally specify vocabularies.
 \emph{Vocabulary constraint types}
 denotes the set of constraint types whose constraints 
-can be extracted completely automatically out of the formal specifications of vocabularies.
+can be extracted completely automatically out of formal specifications of vocabularies.
 As vocabularies have been specified using \emph{RDF}, \emph{RDFS}, and \emph{OWL},
@@
 \emph{Minimum qualified cardinality restrictions} (\emph{R-74}), e.g., guarantee that individuals of given classes are connected by particular properties to at least n different individuals/literals of certain classes or data ranges.
-This way, it is expressible in \emph{OWL 2} that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:
-\ke{Ich dachte, das kommt aus dem Vokabular.
-Dann muss das heißen: For example, in PHDD, a minimum qualified cardinality constraint can be obtained from the OWL definition of this restriction class, ensuring that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:}
+In \emph{PHDD}, a \emph{minimum qualified cardinality restriction} can be obtained from the OWL definition of this restriction class, ensuring that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:
 \begin{ex}
@@
 \emph{Simple} and \emph{complex constraints} are defined according to textual descriptions of the intended semantics of vocabularies.  
-\emph{Simple constraint types} is the set of constraint types whose constraints can be easily defined without much effort in addition to \ke{einfügen: the already defined (auf den Lesefluss achten, das ist eine sehr pragmatische klassifikation und muss nicht übertrieben formal und trocken geschrieben sein)} \emph{vocabulary constraints}.
+\emph{Simple constraint types} is the set of constraint types whose constraints can be easily defined without much effort in addition to the already defined \emph{vocabulary constraints}.
 {\emph{Data property facets} (\emph{R-46}) is an example of a \emph{simple constraint type} which enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
-The abstract of series/studies, e.g., should have a minimum length.
+The abstract of series/studies, e.g., should have a minimum length which is easily and concisely expressible by SPARQL: 
+\begin{ex}
+SELECT ?study WHERE {
+    ?study dcterms:abstract ?abstract . FILTER ( STRLEN ( ?abstract ) = 10 ) . }
+\end{ex}
 
@@
 a thesaurus should not contain many orphan concepts, i.e., concepts without any associative or hierarchical relations, lacking context information valuable for search.
-\emph{Complex constraints} show the importance to develop constraint languages enabling to describe more complex constraints.\ke{der satz macht so keinen sinn...
-aber er ist ein weiteres gutes beispiel, warum du viel mehr auf die formulierungen achten musst.
-Ich weiß genau was du meinst, du hast auch recht, aber hier steht trotzdem ein sinnloser satz, so wie er formuliert ist.}
-
-\ke{ich würde da auch für simple und vor allem für complex konkrete beispiele in code einfügen}
+This \emph{complex constraint} is only expressible by \emph{SPARQL} and not directly understandable:
+\begin{ex}
+SELECT ?concept WHERE {
+    ?concept a [rdfs:subClassOf* skos:Concept] .
+    FILTER NOT EXISTS { ?concept ?p ?o . 
+        FILTER ( ?p IN ( skos:related, skos:relatedMatch, skos:broader, ... ) ) . }
+\end{ex}
+\emph{Complex constraints} are in most cases only expressible by plain \emph{SPARQL}
+which shows the importance to develop suitable constraint languages.
 
@@
 
-\ke{da muss mindestens ein überleitender satz rein, der noch mal den unterschied von constraint types und types aufgreift und erklärt, dass es jetzt um konkrete constraints auf den vokabularen geht, deren severity eben vom konkreten kontext abhängt und nicht allgemein über den type bestimmt werden kann.}
-
+A concrete constraint is instantiated from one of the 82 constraint types and is defined for a specific vocabulary.
+It does not make sense to determine the severity of constraint violations of an entire constraint type,
+as the severity of the violation of a given constraint depends on the individual context and vocabulary.
+%as the violation of one constraint may be severe,
+%whereas, the violation of another constraint of the same type may be minor.
 \emph{SBE} experts determined the default \textbf{\emph{severity level}} (\emph{R-158}) for each of the 246 constraints to indicate how serious the violation of the constraint is.
-We propose an extensible metric to measure the continuum of severity levels ranging from \emph{informational} to \emph{error}.\ke{oder etwas weniger anmaßend: we use the commonly accepted classification of log messages in software development and distingush informational, warning and error.}
-According to the default severity level of constraints, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:\ke{auch dieser satz macht keinen sinn für mich, ebensowenig wie die extrem erhellende auflistung, die gleich folgt...
+%We propose an extensible metric to measure the continuum of severity levels ranging from \emph{informational} to \emph{error}.
+We use the commonly accepted classification of log messages in software development and distinguish \emph{informational}, \emph{warning} and \emph{error}.
+%According to the default severity level of constraints, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:\ke{auch dieser satz macht keinen sinn für mich, ebensowenig wie die extrem erhellende auflistung, die gleich folgt...
 mein vorschlag von eben kann das komplett ersetzen.}
-\begin{itemize}
-	\item \textbf{\emph{informational constraints}}: constraints with severity level \emph{informational}
-	\item \textbf{\emph{warning constraints}}: constraints with severity level \emph{warning}
-	\item \textbf{\emph{error constraints}}: constraints with severity level \emph{error}
-\end{itemize}
+%\begin{itemize}
+	%\item \textbf{\emph{informational constraints}}: constraints with severity level \emph{informational}
+	%\item \textbf{\emph{warning constraints}}: constraints with severity level \emph{warning}
+	%\item \textbf{\emph{error constraints}}: constraints with severity level \emph{error}
+%\end{itemize}
 Violations of \emph{informational constraints} point to desirable but not necessary data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies.
-Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
-Data not conforming to \emph{warning constraints} but to \emph{error constraints} could be processed further.
-Data not corresponding to \emph{error constraints}, however, cannot be processed further after validation. 
+They are not seen as serious errors.
+\emph{Errors} are syntactic or semantic errors which should cause the abortion of data processing. 
+\emph{Warnings} are syntactic or semantic errors which typically should not lead to an abortion of data processing.
+%Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
+%Data not conforming to \emph{warning constraints} but to \emph{error constraints} could be processed further.
+%Data not corresponding to \emph{error constraints}, however, cannot be processed further after validation. 
 As the purpose of \emph{vocabulary constraints} is to ensure explicitly stated semantics of vocabularies, 
@@
 in average stronger than the severity levels of \emph{simple} and \emph{complex constraints}.
-As a consequence, violating many \emph{vocabulary constraints} is an indicator for bad (meta)data quality\footnote{For simplicity reasons, we only assign severity levels to \emph{vocabulary constraints} in this paper in case they differ from \emph{error constraints}.}.
-\ke{den ganzen letzten absatz finde ich unübersichtlich.
-Kann man das nicht klarer sagen: Error sind syntaktische oder semantische fehler, die zu einem abbruch der datenverarbeitung führen sollten.
-warnings sind syntaktische oder semantische fehler, die aber normalerweise nicht zu einem abbruch führen müssen.
-verletzungen von informational constraints weisen auf potentielle verbesserungen in den daten hin, werden aber nicht als fehler angesehen (der satz war in ordnung).
-die fussnote ist doch vollkommen fehl am platz, oder?
-es werden ja nicht alle constraints aufgelistet und wie ihr das implementiert habt und ob ihr euch arbeit erspart habt weil ihr default severity bei bestimmten constraint types vorgebt, das interessiert doch keinen.}
+As a consequence, violating many \emph{vocabulary constraints} is an indicator for bad (meta)data quality.
 
@@
 Thus, it is checked that all date values (e.g., {{\em dcterms:date}) are actually of the datatype \emph{xsd:date} and that \emph{xsd:nonNegativeInteger} values (e.g.
-\emph{disco:frequency}) are not negative.
+\emph{disco:frequency}) are not negative\footnote{For simplicity reasons, we only assign severity levels to \emph{vocabulary constraints} if they differ from \emph{error}.}.
 Depending on property datatypes, two different literal values have
@@
 
-As vocabulary constraints are contained within formal specifications of vocabularies and therefore directly ensure their syntax and semantics,
-violations of vocabulary constraints are more severe than violations caused by simple constraints which are not part of vocabularies.
-In many cases, complex constraints are also needed to express severe constraints which cannot be expressed by modeling languages.
-The relation between complexity and severity shows the importance to develop constraint languages which are enable to express severe complex constraints.
+As \emph{vocabulary constraints} are part of formal specifications of vocabularies,
+violations of \emph{vocabulary constraints} are more severe than violations caused by \emph{simple constraints}.
+As \emph{SPARQL} is still used to express \emph{complex constraints} and as 44\% of all \emph{complex constraints} are serious,
+there is an obvious need to develop constraint languages which enable to express \emph{complex constraints}.
 
 \section{Conclusion and Future Work}
-
-\tb{ToDO}
 

### 2015-04-30 paper/paper7/paper7.tex
intro

@@
 
-\section{Motivation}
+\subsection{Motivation}
 \label{motivation}
@@
 Violations of \emph{informational constraints} point to desirable but not necessary data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies.
-They are not seen as serious errors.
+%They are not seen as serious errors.
 \emph{Errors} are syntactic or semantic errors which should cause the abortion of data processing. 
@@
 Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}).
-
+Consider the following \emph{DL} knowledge base $\mathcal{K}$\footnote{A knowledge base is a collection of formal statements which corresponds to \emph{facts} or what is known explicitly.
+For simplicity reasons, we do not state namespace prefixes in DL statements.}:
 \begin{center}
@@
 \end{center}
-\tb{K einführen}
+
 All properties, not having the same domain and range types, are defined to be pairwise disjoint
@@
 
+\begin{center}
+\begin{DL} 
+$\mathcal{K}=\{$ &\ms{Catalog $\sqsubseteq$ $\forall$ dataset.Dataset}, \\
+&\ms{$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table}, \\
+&\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}, \\
+&\ms{Variable $\equiv$ $\exists$ concept.Concept}
+\}\\ 
+\end{DL}
+\end{center}
+
 -----
 
+We extend $\mathcal{K}$ by \emph{existential quantifications} (\emph{R-86}) enforcing that instances of given classes must have some property relation to individuals/literals of certain types.
+Variables, e.g., should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
+%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
+The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
+The default severity level of the constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
+
+-----
+
+A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
+%Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets}:
+%\begin{DL}
+%Catalog $\sqsubseteq$ $\forall$ dataset.Dataset
+%\end{DL}
+Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets}.
 \emph{Property domain} (\emph{R-25, R-26}) and \emph{range} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties.
 Only \emph{phdd:Tables}, e.g., can have \emph{phdd:isStructuredBy} relationships and
-\emph{xkos:belongsTo} relationships can only point to \emph{skos:Concepts}:
-\begin{DL}
-$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table \\
-$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept
-\end{DL}
-
-A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
-Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets}:
-\begin{DL}
-Catalog $\sqsubseteq$ $\forall$ dataset.Dataset
-\end{DL}
-
-%\textbf{Existential Quantifications.}
+\emph{xkos:belongsTo} relationships can only point to \emph{skos:Concepts}.
 \emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals/literals of certain types.
@@
 The default severity level of the constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
-\begin{DL}
-Variable $\equiv$ $\exists$ concept.Concept
-\end{DL}
 %If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
@@
 %Every \emph{qb:SliceKey}, e.g., must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}).
-\emph{Minimum/maximum/exact qualified cardinality restrictions} (\emph{R-74, R-75, R-76}) contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals of particular classes or data ranges.
-A \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column},
-a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}), and a \emph{qb:DataSet} is structured by (\emph{qb:structure}) exactly one \emph{qb:DataStructureDefinition}.
-\begin{DL}
-TableStructure $\sqsubseteq$ $\geq$1 column.Column \\
-Variable $\sqsubseteq$ $\leq$1 concept.Concept \\
-DataSet $\sqsubseteq$ $\geq$1 structure.DSD $\sqcap$
-$\leq$1 structure.DSD
-\end{DL}
+%\emph{Minimum/maximum/exact qualified cardinality restrictions} (\emph{R-74, R-75, R-76}) contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals of particular classes or data ranges.
+%A \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column},
+%a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}), and a \emph{qb:DataSet} is structured by (\emph{qb:structure}) exactly one \emph{qb:DataStructureDefinition}.
+%\begin{DL}
+%TableStructure $\sqsubseteq$ $\geq$1 column.Column \\
+%Variable $\sqsubseteq$ $\leq$1 concept.Concept \\
+%DataSet $\sqsubseteq$ $\geq$1 structure.DSD $\sqcap$
+%$\leq$1 structure.DSD
+%\end{DL}
 
@@
 
-%\section{Basic Constraint Types}
-%\label{vocabulary-constraint-types}
-%
+\section{Basic Constraint Types}
+\label{vocabulary-constraint-types}
+
 %As \emph{RDFS} and \emph{OWL} are typically used to define vocabularies, \emph{RDFS} and \emph{OWL} reasoning may be performed prior to validation. 
@@
 %\end{enumerate}
-%
-%\subsection{Basic Constraint Types with Reasoning}
-%\label{basic-constraint-types-with-reasoning}
-%
-%Validation environments should enable users to decide if they wish to perform reasoning prior to validation.
-%Reasoning as an optional pre validation step is beneficial for RDF validation as 
-%(1) it may resolve constraint violations and  
-%(2) it may cause useful constraint violations.
+
+\subsection{Basic Constraint Types with Reasoning}
+\label{basic-constraint-types-with-reasoning}
+
+%%Validation environments should enable users to decide if they wish to perform reasoning prior to validation.
+%%Reasoning as an optional pre validation step is beneficial for RDF validation as 
+%%(1) it may resolve constraint violations and  
+%%(2) it may cause useful constraint violations.
 %A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
@@
 %e.g., the \emph{existential quantification} below restricting that person-level data sets must have a distribution:
-%
+
+\begin{center}
+\begin{DL} 
+$\mathcal{K}=\{$ 
+ &\ms{DataSet $\equiv$ $\exists$ distribution.Distribution},\\
+&\ms{Variable $\equiv$ $\exists$ concept.Concept}
+ \}\\ 
+\end{DL}
+\end{center}
+
+We extend $\mathcal{K}$ by \emph{existential quantifications} (\emph{R-86}) enforcing that instances of given classes must have some property relation to individuals/literals of certain types.
+Variables, e.g., should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
+%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
+The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
+The default severity level of the constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
+%If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
+%If metadata on data files, including the actual data, is missing (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the study is not sufficient.
+%Case quantity measures how many cases are collected for a study.
+%High case and variable quantities are indicators for high statistical quality and comprehensiveness of the underlying study ($\mathcal{SL}_{1}$).
+
+\begin{center}
+\begin{DL} 
+$\mathcal{K}=\{$ 
+  &\ms{fundedBy $\sqsubseteq$ contributor}
+ \}\\ 
+\end{DL}
+\end{center}
+
+By stating that \emph{disco:fundedBy} is a sub property of \emph{dcterms:contributor},
+the {\em sub property} (\emph{R-54, R-64}) above assures that if a series is funded by an organization, then the organization must also contribute to the series.
+In case the \emph{sub-property} is applied without reasoning and $\mathcal{K}$ contains the triple \ms{disco:fundedBy} \ms{(EU-SILC,} \ms{organization)},
+a constraint violation is thrown if $\mathcal{K}$ does not explicitly include the triple \ms{dcterms:contributor} \ms{(EU-SILC,} \ms{organization)}.
+If the \emph{sub property} is applied with reasoning, on the other side, the latter triple is derived which resolves the constraint violation.
+
+%\begin{DL}
+%fundedBy $\sqsubseteq$ contributor
+%\end{DL}
+
+%\emph{Asymmetric object properties} (\emph{R-62}) restrict that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}.
+%Such constraints are defined for each object property for which a semantically equivalent object property pointing from the other direction would also be possible but is not defined within the vocabulary.
+%A \emph{disco:Variable}, e.g., may be based on (\emph{disco:basedOn}) a \emph{disco:RepresentedVariable}.
+%A \emph{disco:RepresentedVariable}, however, cannot be based on a \emph{disco:Variable} (\ms{$disco:basedOn \sqcap disco:basedOn^{-} \sqsubseteq \bot$}).
+
+%\emph{Property domain} (\emph{R-25, R-26}) and \emph{range} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties.
+%Only \emph{phdd:Tables}, e.g., can have \emph{phdd:isStructuredBy} relationships and
+%\emph{xkos:belongsTo} relationships can only point to \emph{skos:Concepts}:
+%\begin{DL}
+%$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table \\
+%$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept
+%\end{DL}
+
 %\begin{center}
@@
 %$\mathcal{K}=\{$ 
- %&\ms{DataSet $\equiv$ $\exists$ distribution.Distribution},\\
-%&\ms{Variable $\equiv$ $\exists$ concept.Concept}
+  %&\ms{TableStructure $\sqsubseteq$ $\geq$1 column.Column}, \\
+	%&\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}, \\
+	%&\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition} \\ 
+	%&\ms{$\sqcap$ $\leq$1 structure.DataStructureDefinition}
  %\}\\ 
@@
 %\end{center}
-%
-%We extend $\mathcal{K}$ by \emph{existential quantifications} (\emph{R-86}) enforcing that instances of given classes must have some property relation to individuals/literals of certain types.
-%Variables, e.g., should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
-%%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
-%The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
-%The default severity level of the constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
-%%If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
-%%If metadata on data files, including the actual data, is missing (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the study is not sufficient.
-%%Case quantity measures how many cases are collected for a study.
-%%High case and variable quantities are indicators for high statistical quality and comprehensiveness of the underlying study ($\mathcal{SL}_{1}$).
-%
-%\begin{center}
-%\begin{DL} 
-%$\mathcal{K}=\{$ 
-  %&\ms{fundedBy $\sqsubseteq$ contributor}
- %\}\\ 
-%\end{DL}
-%\end{center}
-%
-%By stating that \emph{disco:fundedBy} is a sub property of \emph{dcterms:contributor},
-%the {\em sub property} (\emph{R-54, R-64}) above assures that if a series is funded by an organization, then the organization must also contribute to the series.
-%In case the \emph{sub-property} is applied without reasoning and $\mathcal{K}$ contains the triple \ms{disco:fundedBy} \ms{(EU-SILC,} \ms{organization)},
-%a constraint violation is thrown if $\mathcal{K}$ does not explicitly include the triple \ms{dcterms:contributor} \ms{(EU-SILC,} \ms{organization)}.
-%If the \emph{sub property} is applied with reasoning, on the other side, the latter triple is derived which resolves the constraint violation.
-%
-%%\begin{DL}
-%%fundedBy $\sqsubseteq$ contributor
-%%\end{DL} 
-%
-%%\emph{Asymmetric object properties} (\emph{R-62}) restrict that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}.
-%%Such constraints are defined for each object property for which a semantically equivalent object property pointing from the other direction would also be possible but is not defined within the vocabulary.
-%%A \emph{disco:Variable}, e.g., may be based on (\emph{disco:basedOn}) a \emph{disco:RepresentedVariable}.
-%%A \emph{disco:RepresentedVariable}, however, cannot be based on a \emph{disco:Variable} (\ms{$disco:basedOn \sqcap disco:basedOn^{-} \sqsubseteq \bot$}).
-%
-%%\emph{Property domain} (\emph{R-25, R-26}) and \emph{range} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties.
-%%Only \emph{phdd:Tables}, e.g., can have \emph{phdd:isStructuredBy} relationships and
-%%\emph{xkos:belongsTo} relationships can only point to \emph{skos:Concepts}:
-%%\begin{DL}
-%%$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table \\
-%%$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept
-%%\end{DL}
-%
-%%\begin{center}
-%%\begin{DL} 
-%%$\mathcal{K}=\{$ 
-  %%&\ms{TableStructure $\sqsubseteq$ $\geq$1 column.Column}, \\
-	%%&\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}, \\
-	%%&\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition} \\ 
-	%%&\ms{$\sqcap$ $\leq$1 structure.DataStructureDefinition}
- %%\}\\ 
-%%\end{DL}
-%%\end{center}
-%
-%%\textbf{Cardinality Restrictions on Properties.}
-%%An \emph{existential quantification} (\emph{R-86}) contains all those individuals that are connected by a property to individuals/literals of given classes or data ranges.
-%%Every \emph{qb:SliceKey}, e.g., must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}).
-%%\emph{Minimum/maximum/exact qualified cardinality restrictions} (\emph{R-74, R-75, R-76}) contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals of particular classes or data ranges.
-%%A \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column},
-%%a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}), and a \emph{qb:DataSet} is structured by (\emph{qb:structure}) exactly one \emph{qb:DataStructureDefinition}.
-%%DATA-CUBE-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-
-%%02: Unique data set (IC-1 [3]) - Every qb:Observation has (qb:dataSet) ex-
-%%actly one associated qb:DataSet (Observation  ¥1 dataSet.DataSet [
-%%¤1 dataSet.DataSet).
-%%Severity level: ERROR
-%%
-%%(\emph{R-75: minimum qualified cardinality restrictions})
-%%
-%%DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-
-%%02: Unique DSD (IC-2 [3]) - Every qb:DataSet has (qb:structure) exactly one
-%%associated qb:DataStructureDefinition (DataSet  ¥1 structure.DataStructureDefinition
-%%[ ¤1 structure.DataStructureDefinition).
-%%Severity level: ERROR
-%%
-%%(\emph{R-74: exact qualified cardinality restrictions})
-%%\footnote{\emph{DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02}}.
-%%\textbf{Language Tag Cardinality.}
-%
+
+%\textbf{Cardinality Restrictions on Properties.}
+%An \emph{existential quantification} (\emph{R-86}) contains all those individuals that are connected by a property to individuals/literals of given classes or data ranges.
+%Every \emph{qb:SliceKey}, e.g., must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}).
+%\emph{Minimum/maximum/exact qualified cardinality restrictions} (\emph{R-74, R-75, R-76}) contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals of particular classes or data ranges.
+%A \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column},
+%a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}), and a \emph{qb:DataSet} is structured by (\emph{qb:structure}) exactly one \emph{qb:DataStructureDefinition}.
+%DATA-CUBE-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-
+%02: Unique data set (IC-1 [3]) - Every qb:Observation has (qb:dataSet) ex-
+%actly one associated qb:DataSet (Observation  ¥1 dataSet.DataSet [
+%¤1 dataSet.DataSet).
+%Severity level: ERROR
+%
+%(\emph{R-75: minimum qualified cardinality restrictions})
+%
+%DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-
+%02: Unique DSD (IC-2 [3]) - Every qb:DataSet has (qb:structure) exactly one
+%associated qb:DataStructureDefinition (DataSet  ¥1 structure.DataStructureDefinition
+%[ ¤1 structure.DataStructureDefinition).
+%Severity level: ERROR
+%
+%(\emph{R-74: exact qualified cardinality restrictions})
+%\footnote{\emph{DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02}}.
+%\textbf{Language Tag Cardinality.}
+
 %\subsection{Basic Constraint Types without Reasoning}

### 2015-04-30 paper/paper7/paper7.tex
evaluation

--- 2015-04-30 paper/paper7/paper7.tex
@@
 For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.
-\ke{check numbers}
-Based on the results, we formulate several hypotheses to direct the further development of constraint langugaes.
+Based on the results, we formulate several hypotheses to direct the further development of constraint languages.
 
@@
 With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration.
-Therefore, not only established vocabularies like SKOS are used;
+Therefore, not only existing vocabularies like SKOS are used;
 recently, members of the \emph{SBE} and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.
 
-For constraint formulation and validation on RDF data, several languages exist or are currently developed, like \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles}.
+For constraint formulation and validation on RDF data, several languages exist, like \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles}.
 \emph{OWL 2} is also used as a constraint language under a closed world assumption.
@@
 is very popular and certainly plays an important role for future developments in this field.
-It is particularly interesting as a means to validate arbitrary constraint languages by mapping them to SPARQL \cite{BoschEckert2014-2}.
-Yet, there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners.
-Further research and development therefore is needed.
+%that more or less explicitly address the \emph{SBE} community.
 
@@
 In 2014, two working groups on RDF validation have been established to develop a language to express constraints on RDF data: 
-the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles task group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}} which among others bundles the requirements of data institutions of the cultural heritage and SBE sector and represents them in the W3C group.
-
-Within the DCMI task group, a collaboratively curated database of RDF validation requirements has been created which contains the findings of the working groups based on various case studies provided by data institutions \cite{BoschEckert2014}.
-It is publicly available and open for further contributions\footnote{Online at \url{http://purl.org/net/rdf-validation}}.
-
-The database connects requirements to use cases, case studies and implementations and forms the basis of this paper.
-To gain a better understanding about the role of certain requirements for data quality and in order to direct the further development of constraint langugaes, we collected constraints for commonly used vocabularies in the SBE domain, either from the vocabularies themselves or from domain and data experts.
-All in all, this lead to TODO constraints on TODO vocabularies.
-We let the experts classify the constraints according to the severity if they are violated.
-Furthermore, we classified the type of each constraint (corresponding to a requirement) based on its complexity ranging from types commonly found in vocabulary specificatons (e.g., domain and range), over types that are simply stated using common constraint languages (e.g., cardinality restrictions) to complex types that involve complex data structures or need more sophisticated langugaes to be easily expressible (e.g., constraints on network topologies).\ke{Thomas: Ok so?}
-
-As we do not want to base our conclusions on the evaluations of vocabularies and constraint definitions alone, we conducted a large-scale experiment and evaluated the data quality of 15,694 data sets (4,26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.
+the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles task group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
+
+Bosch and Eckert \cite{BoschEckert2014} collected the findings of these working groups and initiated a database of RDF validation requirements
+which is available for contribution at \url{http://purl.org/net/rdf-validation}.
+The intention is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
+The requirements are classified to better evaluate existing solutions and each requirement is directly mapped to a constraint type which is expressible by at least one constraint language.
+As \emph{SPIN} is the within the RDF validation community accepted and widely adopted way to check constraints on RDF data, Bosch and Eckert \cite{BoschEckert2014-2} use \emph{SPIN} as basis to define a
+validation environment (available at \url{http://purl.org/net/rdfval-demo}) in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL.
+The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.
+
+%This paper aims to address two main \textbf{audiences}: 
+%(1) metadata practitioners seeking for how to represent metadata and data on different aggregation levels in RDF and
+%(2) metadata providers and harvesters ensuring high quality data and metadata by validating RDF data according to certain constraints.
 
@@
 
-The modeling languages \emph{RDF}, \emph{RDFS}, and \emph{OWL} are typically used to formally specify vocabularies.
+The modeling languages \emph{RDF}, \emph{RDFS}, and \emph{OWL} are typically used to define vocabularies.
 \emph{Vocabulary constraint types}
 denotes the set of constraint types whose constraints 
-can be extracted completely automatically out of formal specifications of vocabularies.
+can be extracted completely automatically out of the formal specifications of vocabularies.
 As vocabularies have been specified using \emph{RDF}, \emph{RDFS}, and \emph{OWL},
@@
 \emph{Minimum qualified cardinality restrictions} (\emph{R-74}), e.g., guarantee that individuals of given classes are connected by particular properties to at least n different individuals/literals of certain classes or data ranges.
-In \emph{PHDD}, a \emph{minimum qualified cardinality restriction} can be obtained from the OWL definition of this restriction class, ensuring that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:
+This way, it is expressible in \emph{OWL 2} that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:
+\ke{Ich dachte, das kommt aus dem Vokabular.
+Dann muss das heißen: For example, in PHDD, a minimum qualified cardinality constraint can be obtained from the OWL definition of this restriction class, ensuring that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:}
 \begin{ex}
@@
 \emph{Simple} and \emph{complex constraints} are defined according to textual descriptions of the intended semantics of vocabularies.  
-\emph{Simple constraint types} is the set of constraint types whose constraints can be easily defined without much effort in addition to the already defined \emph{vocabulary constraints}.
+\emph{Simple constraint types} is the set of constraint types whose constraints can be easily defined without much effort in addition to \ke{einfügen: the already defined (auf den Lesefluss achten, das ist eine sehr pragmatische klassifikation und muss nicht übertrieben formal und trocken geschrieben sein)} \emph{vocabulary constraints}.
 {\emph{Data property facets} (\emph{R-46}) is an example of a \emph{simple constraint type} which enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
-The abstract of series/studies, e.g., should have a minimum length which is easily and concisely expressible by SPARQL: 
-\begin{ex}
-SELECT ?study WHERE {
-    ?study dcterms:abstract ?abstract . FILTER ( STRLEN ( ?abstract ) = 10 ) . }
-\end{ex}
+The abstract of series/studies, e.g., should have a minimum length.
 
@@
 a thesaurus should not contain many orphan concepts, i.e., concepts without any associative or hierarchical relations, lacking context information valuable for search. 
-This \emph{complex constraint} is only expressible by \emph{SPARQL} and not directly understandable:
-\begin{ex}
-SELECT ?concept WHERE {
-    ?concept a [rdfs:subClassOf* skos:Concept] .
-    FILTER NOT EXISTS { ?concept ?p ?o . 
-        FILTER ( ?p IN ( skos:related, skos:relatedMatch, skos:broader, ... ) ) . }
-\end{ex}
-\emph{Complex constraints} are in most cases only expressible by plain \emph{SPARQL}
-which shows the importance to develop suitable constraint languages.
+\emph{Complex constraints} show the importance to develop constraint languages enabling to describe more complex constraints.\ke{der satz macht so keinen sinn...
+aber er ist ein weiteres gutes beispiel, warum du viel mehr auf die formulierungen achten musst.
+Ich weiß genau was du meinst, du hast auch recht, aber hier steht trotzdem ein sinnloser satz, so wie er formuliert ist.}
+
+\ke{ich würde da auch für simple und vor allem für complex konkrete beispiele in code einfügen}
 
@@
 
-A concrete constraint is instantiated from one of the 82 constraint types and is defined for a specific vocabulary.
-It does not make sense to determine the severity of constraint violations of an entire constraint type,
-as the severity of the violation of a given constraint depends on the individual context and vocabulary.
-%as the violation of one constraint may be severe,
-%whereas, the violation of another constraint of the same type may be minor.
+\ke{da muss mindestens ein überleitender satz rein, der noch mal den unterschied von constraint types und types aufgreift und erklärt, dass es jetzt um konkrete constraints auf den vokabularen geht, deren severity eben vom konkreten kontext abhängt und nicht allgemein über den type bestimmt werden kann.}
+
 \emph{SBE} experts determined the default \textbf{\emph{severity level}} (\emph{R-158}) for each of the 246 constraints to indicate how serious the violation of the constraint is.
-%We propose an extensible metric to measure the continuum of severity levels ranging from \emph{informational} to \emph{error}.
-We use the commonly accepted classification of log messages in software development and distinguish \emph{informational}, \emph{warning} and \emph{error}.
-%According to the default severity level of constraints, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:\ke{auch dieser satz macht keinen sinn für mich, ebensowenig wie die extrem erhellende auflistung, die gleich folgt...
+We propose an extensible metric to measure the continuum of severity levels ranging from \emph{informational} to \emph{error}.\ke{oder etwas weniger anmaßend: we use the commonly accepted classification of log messages in software development and distingush informational, warning and error.}
+According to the default severity level of constraints, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:\ke{auch dieser satz macht keinen sinn für mich, ebensowenig wie die extrem erhellende auflistung, die gleich folgt...
 mein vorschlag von eben kann das komplett ersetzen.}
-%\begin{itemize}
-	%\item \textbf{\emph{informational constraints}}: constraints with severity level \emph{informational}
-	%\item \textbf{\emph{warning constraints}}: constraints with severity level \emph{warning}
-	%\item \textbf{\emph{error constraints}}: constraints with severity level \emph{error}
-%\end{itemize}
+\begin{itemize}
+	\item \textbf{\emph{informational constraints}}: constraints with severity level \emph{informational}
+	\item \textbf{\emph{warning constraints}}: constraints with severity level \emph{warning}
+	\item \textbf{\emph{error constraints}}: constraints with severity level \emph{error}
+\end{itemize}
 Violations of \emph{informational constraints} point to desirable but not necessary data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies.
-They are not seen as serious errors.
-\emph{Errors} are syntactic or semantic errors which should cause the abortion of data processing. 
-\emph{Warnings} are syntactic or semantic errors which typically should not lead to an abortion of data processing.
-%Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
-%Data not conforming to \emph{warning constraints} but to \emph{error constraints} could be processed further.
-%Data not corresponding to \emph{error constraints}, however, cannot be processed further after validation. 
+Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
+Data not conforming to \emph{warning constraints} but to \emph{error constraints} could be processed further.
+Data not corresponding to \emph{error constraints}, however, cannot be processed further after validation. 
 As the purpose of \emph{vocabulary constraints} is to ensure explicitly stated semantics of vocabularies, 
@@
 in average stronger than the severity levels of \emph{simple} and \emph{complex constraints}.
-As a consequence, violating many \emph{vocabulary constraints} is an indicator for bad (meta)data quality.
+As a consequence, violating many \emph{vocabulary constraints} is an indicator for bad (meta)data quality\footnote{For simplicity reasons, we only assign severity levels to \emph{vocabulary constraints} in this paper in case they differ from \emph{error constraints}.}.
+\ke{den ganzen letzten absatz finde ich unübersichtlich.
+Kann man das nicht klarer sagen: Error sind syntaktische oder semantische fehler, die zu einem abbruch der datenverarbeitung führen sollten.
+warnings sind syntaktische oder semantische fehler, die aber normalerweise nicht zu einem abbruch führen müssen.
+verletzungen von informational constraints weisen auf potentielle verbesserungen in den daten hin, werden aber nicht als fehler angesehen (der satz war in ordnung).
+die fussnote ist doch vollkommen fehl am platz, oder?
+es werden ja nicht alle constraints aufgelistet und wie ihr das implementiert habt und ob ihr euch arbeit erspart habt weil ihr default severity bei bestimmten constraint types vorgebt, das interessiert doch keinen.}
 
@@
 Thus, it is checked that all date values (e.g., {{\em dcterms:date}) are actually of the datatype \emph{xsd:date} and that \emph{xsd:nonNegativeInteger} values (e.g.
-\emph{disco:frequency}) are not negative\footnote{For simplicity reasons, we only assign severity levels to \emph{vocabulary constraints} if they differ from \emph{error}.}.
+\emph{disco:frequency}) are not negative.
 Depending on property datatypes, two different literal values have

### 2015-04-30 paper/paper7/paper7.tex
struktur
evaluation

@@
 
-\ke{da muss mindestens ein überleitender satz rein, der noch mal den unterschied von constraint types und types aufgreift und erklärt, dass es jetzt um konkrete constraints auf den vokabularen geht, deren severity eben vom konkreten kontext abhängt und nicht allgemein über den type bestimmt werden kann.}
-
+A concrete constraint is instantiated from one of the 82 constraint types and is defined for a specific vocabulary.
+It does not make sense to determine the severity of constraint violations of a constraint type,
+as the severity of the violation of a given constraint depends on the individual context and vocabulary.
+%as the violation of one constraint may be severe,
+%whereas, the violation of another constraint of the same type may be minor.
 \emph{SBE} experts determined the default \textbf{\emph{severity level}} (\emph{R-158}) for each of the 246 constraints to indicate how serious the violation of the constraint is.

### 2015-04-30 paper/paper7/paper7.tex
evaluation

@@
 A concrete constraint is instantiated from one of the 82 constraint types and is defined for a specific vocabulary.
-It does not make sense to determine the severity of constraint violations of a constraint type,
+It does not make sense to determine the severity of constraint violations of an entire constraint type,
 as the severity of the violation of a given constraint depends on the individual context and vocabulary.

### 2015-04-30 paper/paper7/paper7.tex
evaluation

@@
 \emph{SBE} experts determined the default \textbf{\emph{severity level}} (\emph{R-158}) for each of the 246 constraints to indicate how serious the violation of the constraint is.
-We propose an extensible metric to measure the continuum of severity levels ranging from \emph{informational} to \emph{error}.\ke{oder etwas weniger anmaßend: we use the commonly accepted classification of log messages in software development and distingush informational, warning and error.}
-According to the default severity level of constraints, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:\ke{auch dieser satz macht keinen sinn für mich, ebensowenig wie die extrem erhellende auflistung, die gleich folgt...
+%We propose an extensible metric to measure the continuum of severity levels ranging from \emph{informational} to \emph{error}.
+We use the commonly accepted classification of log messages in software development and distinguish \emph{informational}, \emph{warning} and \emph{error}.
+%According to the default severity level of constraints, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:\ke{auch dieser satz macht keinen sinn für mich, ebensowenig wie die extrem erhellende auflistung, die gleich folgt...
 mein vorschlag von eben kann das komplett ersetzen.}
-\begin{itemize}
-	\item \textbf{\emph{informational constraints}}: constraints with severity level \emph{informational}
-	\item \textbf{\emph{warning constraints}}: constraints with severity level \emph{warning}
-	\item \textbf{\emph{error constraints}}: constraints with severity level \emph{error}
-\end{itemize}
+%\begin{itemize}
+	%\item \textbf{\emph{informational constraints}}: constraints with severity level \emph{informational}
+	%\item \textbf{\emph{warning constraints}}: constraints with severity level \emph{warning}
+	%\item \textbf{\emph{error constraints}}: constraints with severity level \emph{error}
+%\end{itemize}
 Violations of \emph{informational constraints} point to desirable but not necessary data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies.
-Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
-Data not conforming to \emph{warning constraints} but to \emph{error constraints} could be processed further.
-Data not corresponding to \emph{error constraints}, however, cannot be processed further after validation. 
+They are not seen as serious errors.
+\emph{Errors} are syntactic or semantic errors which should cause the abortion of data processing. 
+\emph{Warnings} are syntactic or semantic errors which typically should not lead to an abortion of data processing.
+%Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
+%Data not conforming to \emph{warning constraints} but to \emph{error constraints} could be processed further.
+%Data not corresponding to \emph{error constraints}, however, cannot be processed further after validation. 
 As the purpose of \emph{vocabulary constraints} is to ensure explicitly stated semantics of vocabularies, 

### 2015-04-30 paper/paper7/paper7.tex
evaluation

@@
 \begin{DL} 
-$\mathcal{K}=\{$ &\ms{Catalog $\sqsubseteq$ $\forall$ dataset.Dataset}, \\
+$\mathcal{K}=\{$ &\ms{Variable $\equiv$ $\exists$ concept.Concept}, \\
+&\ms{Catalog $\sqsubseteq$ $\forall$ dataset.Dataset}, \\
 &\ms{$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table}, \\
-&\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}, \\
-&\ms{Variable $\equiv$ $\exists$ concept.Concept}
+&\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}
 \}\\ 
@@
 \end{center}
-
------
 
@@
 \emph{xkos:belongsTo} relationships can only point to \emph{skos:Concepts}.
-\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals/literals of certain types.
-Variables, e.g., should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
-%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
-The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
-The default severity level of the constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
+%\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals/literals of certain types.
+%Variables, e.g., should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
+%%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
+%The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
+%The default severity level of the constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
 %If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
@@
 
-\section{Basic Constraint Types}
-\label{vocabulary-constraint-types}
+%\section{Basic Constraint Types}
+%\label{vocabulary-constraint-types}
 
@@
 
-\subsection{Basic Constraint Types with Reasoning}
-\label{basic-constraint-types-with-reasoning}
+-----
+
+%\subsection{Basic Constraint Types with Reasoning}
+%\label{basic-constraint-types-with-reasoning}
 
@@
 
-\begin{center}
-\begin{DL} 
-$\mathcal{K}=\{$ 
- &\ms{DataSet $\equiv$ $\exists$ distribution.Distribution},\\
-&\ms{Variable $\equiv$ $\exists$ concept.Concept}
- \}\\ 
-\end{DL}
-\end{center}
-
-We extend $\mathcal{K}$ by \emph{existential quantifications} (\emph{R-86}) enforcing that instances of given classes must have some property relation to individuals/literals of certain types.
-Variables, e.g., should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
-%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
-The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
-The default severity level of the constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
+%\begin{center}
+%\begin{DL} 
+%$\mathcal{K}=\{$ 
+ %&\ms{DataSet $\equiv$ $\exists$ distribution.Distribution},\\
+%&\ms{Variable $\equiv$ $\exists$ concept.Concept}
+ %\}\\ 
+%\end{DL}
+%\end{center}
+
+%We extend $\mathcal{K}$ by \emph{existential quantifications} (\emph{R-86}) enforcing that instances of given classes must have some property relation to individuals/literals of certain types.
+%Variables, e.g., should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
+%%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
+%The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
+%The default severity level of the constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
 %If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.

### 2015-04-30 paper/paper7/paper7.tex

@@
 
-\section{Vocabulary Constraint Types}
+\subsection{Vocabulary Constraint Types}
 \label{vocabulary-constraint-types}
 
-The constraint type \emph{vocabulary} guarantees that users do not invent new or use deprecated terms of vocabularies.
+%The constraint type \emph{vocabulary} guarantees that users do not invent new or use deprecated terms of vocabularies.
 %Out-dated classes and properties of previous vocabulary versions can be marked as deprecated.
 %The constraint types \emph{context-specific valid classes and properties} (\emph{R-209; R-210}) can be used to specify which classes and properties are valid in which context - here a given vocabulary version.
-\emph{Value is valid for datatype} (\emph{R-223}) constraints serve to make sure that all literal values are valid with regard to their datatypes - as stated in the vocabularies.
-Thus, it is checked that all date values (e.g., {{\em dcterms:date}) are actually of the datatype \emph{xsd:date} and that \emph{xsd:nonNegativeInteger} values (e.g.
+%\emph{Value is valid for datatype} (\emph{R-223}) constraints serve to make sure that all literal values are valid with regard to their datatypes - as stated in the vocabularies.
+%Thus, it is checked that all date values (e.g., {{\em dcterms:date}) are actually of the datatype \emph{xsd:date} and that \emph{xsd:nonNegativeInteger} values (e.g.
 \emph{disco:frequency}) are not negative\footnote{For simplicity reasons, we only assign severity levels to \emph{vocabulary constraints} if they differ from \emph{error}.}.
-Depending on property datatypes, two different literal values have
-a specific ordering with respect to operators like \textless  (\emph{R-43: literal value comparison}).
-Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}).
+%Depending on property datatypes, two different literal values have
+%a specific ordering with respect to operators like \textless  (\emph{R-43: literal value comparison}).
+%Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}).
+
+%All properties, not having the same domain and range types, are defined to be pairwise disjoint
+%(\emph{R-9: disjoint properties}), i.e., no individual \emph{x} can be connected to an individual/literal \emph{y} by disjoint properties (e.g., \emph{phdd:isStructuredBy} and \emph{phdd:column}).
+%All \emph{PHDD} classes (e.g., \emph{phdd:TableDescription}, \emph{phdd:ColumnDescription}) are pairwise disjoint (\emph{R-7: disjoint classes}),
+%i.e., individuals cannot be instances of multiple disjoint classes.
+It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values (\emph{R-30/37: allowed values}). 
+%\emph{Allowed values} (\emph{R-30, R-37}) for properties can be IRIs (matching one or multiple patterns), any literals, allowed literals (e.g.
+'red' 'blue' 'green'), and typed literals of one or multiple type(s) (e.g.
+\emph{xsd:string}).
+\emph{disco:CategoryStatistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString}.
+%Validation should \emph{exploit sub-super relations} in vocabularies (\emph{R-224}).
+%If \emph{dcterms:coverage} and one of its sub properties (\emph{dcterms:spatial}, \emph{dcterms:temporal}) are given,
+%it is checked that \emph{dcterms:coverage} is not redundant with its sub-properties 
+%which may indicate when the data is verbose/redundant or expressed at a too general level.
 Consider the following \emph{DL} knowledge base $\mathcal{K}$\footnote{A knowledge base is a collection of formal statements which corresponds to \emph{facts} or what is known explicitly.
@@
 $\mathcal{K}=\{$ 
-	&\ms{isStructuredBy $\sqsubseteq$ $\neg$ column}, \\
-	&\ms{TableDescription $\sqcap$ ColumnDescription $\sqsubseteq$ $\perp$}, \\
+	%&\ms{isStructuredBy $\sqsubseteq$ $\neg$ column}, \\
+	%&\ms{TableDescription $\sqcap$ ColumnDescription $\sqsubseteq$ $\perp$}, \\
 	&\ms{CategoryStatistics $\equiv$} \\
-	&\ms{$\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString}
- \}\\ 
-\end{DL}
-\end{center}
-
-All properties, not having the same domain and range types, are defined to be pairwise disjoint
-(\emph{R-9: disjoint properties}), i.e., no individual \emph{x} can be connected to an individual/literal \emph{y} by disjoint properties (e.g., \emph{phdd:isStructuredBy} and \emph{phdd:column}).
-All \emph{PHDD} classes (e.g., \emph{phdd:TableDescription}, \emph{phdd:ColumnDescription}) are pairwise disjoint (\emph{R-7: disjoint classes}),
-i.e., individuals cannot be instances of multiple disjoint classes.
-It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values (\emph{R-30/37: allowed values}). 
-%\emph{Allowed values} (\emph{R-30, R-37}) for properties can be IRIs (matching one or multiple patterns), any literals, allowed literals (e.g.
-'red' 'blue' 'green'), and typed literals of one or multiple type(s) (e.g.
-\emph{xsd:string}).
-\emph{disco:CategoryStatistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString}.
-Validation should \emph{exploit sub-super relations} in vocabularies (\emph{R-224}).
-If \emph{dcterms:coverage} and one of its sub properties (\emph{dcterms:spatial}, \emph{dcterms:temporal}) are given,
-it is checked that \emph{dcterms:coverage} is not redundant with its sub-properties 
-which may indicate when the data is verbose/redundant or expressed at a too general level.
-
-\begin{center}
-\begin{DL} 
-$\mathcal{K}=\{$ &\ms{Variable $\equiv$ $\exists$ concept.Concept}, \\
+	&\ms{$\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString}, \\
+  &\ms{Variable $\equiv$ $\exists$ concept.Concept}, \\
   &\ms{Catalog $\sqsubseteq$ $\forall$ dataset.Dataset}, \\
@@
 
-We extend $\mathcal{K}$ by \emph{existential quantifications} (\emph{R-86}) enforcing that instances of given classes must have some property relation to individuals/literals of certain types.
-Variables, e.g., should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
+%We extend $\mathcal{K}$ by 
+\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals/literals of certain types.
+Variables, e.g., should have a relation to a theoretical concept (\emph{info}).
 %The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
 The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
-The default severity level of the constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
-
------
-
+The default severity level of this constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
 A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
@@
 Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets}.
-\emph{Property domain} (\emph{R-25, R-26}) and \emph{range} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties.
+\emph{Property domain} (\emph{R-25, R-26}) and \emph{range} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties:
 Only \emph{phdd:Tables}, e.g., can have \emph{phdd:isStructuredBy} relationships and
-\emph{xkos:belongsTo} relationships can only point to \emph{skos:Concepts}.
+\emph{xkos:belongsTo} relations can only point to \emph{skos:Concepts}.
 %\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals/literals of certain types.
@@
 
-%\textbf{Validation and Reasoning.}
-Some constraint types enable performing reasoning prior to validation which may resolve or cause constraint violations.
-With \emph{subsumption} (\emph{R-100}), one can state that \emph{xkos:ClassificationLevel} is a sub-class of \emph{skos:Collection}, i.e., each \emph{xkos:ClassificationLevel} must also be part of the \emph{skos:Collection} class extension.
-With \emph{sub properties} (\emph{R-54, R-64}), one can state that \emph{disco:fundedBy} is a sub-property of \emph{dcterms:contributor} - i.e., if a study is funded by an organization, then this organization contributed to this study.
-\begin{DL}
-ClassificationLevel $\sqsubseteq$ Collection \\
-fundedBy $\sqsubseteq$ contributor
-\end{DL}
+%%\textbf{Validation and Reasoning.}
+%Some constraint types enable performing reasoning prior to validation which may resolve or cause constraint violations.
+%With \emph{subsumption} (\emph{R-100}), one can state that \emph{xkos:ClassificationLevel} is a sub-class of \emph{skos:Collection}, i.e., each \emph{xkos:ClassificationLevel} must also be part of the \emph{skos:Collection} class extension.
+%With \emph{sub properties} (\emph{R-54, R-64}), one can state that \emph{disco:fundedBy} is a sub-property of \emph{dcterms:contributor} - i.e., if a study is funded by an organization, then this organization contributed to this study.
+%\begin{DL}
+%ClassificationLevel $\sqsubseteq$ Collection \\
+%fundedBy $\sqsubseteq$ contributor
+%\end{DL}
 
@@
 %\end{enumerate}
-
------
 
@@
 
-\begin{center}
-\begin{DL} 
-$\mathcal{K}=\{$ 
-  &\ms{fundedBy $\sqsubseteq$ contributor}
- \}\\ 
-\end{DL}
-\end{center}
-
-By stating that \emph{disco:fundedBy} is a sub property of \emph{dcterms:contributor},
-the {\em sub property} (\emph{R-54, R-64}) above assures that if a series is funded by an organization, then the organization must also contribute to the series.
-In case the \emph{sub-property} is applied without reasoning and $\mathcal{K}$ contains the triple \ms{disco:fundedBy} \ms{(EU-SILC,} \ms{organization)},
-a constraint violation is thrown if $\mathcal{K}$ does not explicitly include the triple \ms{dcterms:contributor} \ms{(EU-SILC,} \ms{organization)}.
-If the \emph{sub property} is applied with reasoning, on the other side, the latter triple is derived which resolves the constraint violation.
+%\begin{center}
+%\begin{DL} 
+%$\mathcal{K}=\{$ 
+  %&\ms{fundedBy $\sqsubseteq$ contributor}
+ %\}\\ 
+%\end{DL}
+%\end{center}
+%
+%By stating that \emph{disco:fundedBy} is a sub property of \emph{dcterms:contributor},
+%the {\em sub property} (\emph{R-54, R-64}) above assures that if a series is funded by an organization, then the organization must also contribute to the series.
+%In case the \emph{sub-property} is applied without reasoning and $\mathcal{K}$ contains the triple \ms{disco:fundedBy} \ms{(EU-SILC,} \ms{organization)},
+%a constraint violation is thrown if $\mathcal{K}$ does not explicitly include the triple \ms{dcterms:contributor} \ms{(EU-SILC,} \ms{organization)}.
+%If the \emph{sub property} is applied with reasoning, on the other side, the latter triple is derived which resolves the constraint violation.
 
@@
 
-\section{Simple Constraint Types}
+\subsection{Simple Constraint Types}
 
@@
 
-\section{Complex Constraint Types}
+\subsection{Complex Constraint Types}
 \label{complex-constraint-types}
@@
 
-\section{Implementation}
+\section{Evaluation}
+\label{evaluation}
+
+\subsection{Experimental Setup}
 \label{implementation}
@@
 
-\section{Evaluation}
-\label{evaluation}
-
-\subsection{Evaluation Setup}
+\ke{Überarbeiten und mit nächstem teil mergen. Nur das erzählen, was für die Auswertung auf den Datensets relevant ist. 114 constraints, 3 vokabulare, wie wurden die datasets daraufhin validiert.}
 

### 2015-04-30 paper/paper7/paper7.tex
4

@@
 Consider the following \emph{DL} knowledge base $\mathcal{K}$\footnote{A knowledge base is a collection of formal statements which corresponds to \emph{facts} or what is known explicitly.
-For simplicity reasons, we do not state namespace prefixes in DL statements.}:
+For simplicity reasons, we do not state namespace prefixes.}:
 \begin{center}
@@
 	%&\ms{TableDescription $\sqcap$ ColumnDescription $\sqsubseteq$ $\perp$}, \\
-	&\ms{CategoryStatistics $\equiv$} \\
-	&\ms{$\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString}, \\
-  &\ms{Variable $\equiv$ $\exists$ concept.Concept}, \\
-  &\ms{Catalog $\sqsubseteq$ $\forall$ dataset.Dataset}, \\
-  &\ms{$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table}, \\
-  &\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}
+	&\ms{CategoryStatistics $\equiv$ $\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString}, \\
+  &\ms{Variable $\equiv$ $\exists$ concept.Concept, Catalog $\sqsubseteq$ $\forall$ dataset.Dataset}, \\
+  &\ms{$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table, $\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}
 \}\\ 
@@
 \emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals/literals of certain types.
-Variables, e.g., should have a relation to a theoretical concept (\emph{info}).
+Variables, e.g., should have a relation to a theoretical concept (\emph{informational}).
 %The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
@@
 
-$\mathcal{CT}_{S}$ is the set of constraint types whose constraints can be easily defined without much effort in addition to $\mathcal{CT}_{B}$ constraints.
+%{Simple constraint types} is the set of constraint types whose constraints can be easily defined without much effort in addition to $\mathcal{CT}_{B}$ constraints.
 For data properties, it may be desirable to restrict that values of predefined languages must be present for determined number of times (\emph{R-48/49: language tag cardinality}):
 (1) It is checked if literal language tags are set.
-Some controlled vocabularies, e.g., contain literals in natural language, but without information what language has actually been used ($\mathcal{SL}_{1}$).
-(2) Language tags must conform to language standards ($\mathcal{SL}_{2}$). 
+Some controlled vocabularies, e.g., contain literals in natural language, but without information what language has actually been used (\emph{warning}).
+(2) Language tags must conform to language standards (\emph{error}). 
 (3) Some thesaurus concepts are labeled in only one, others in multiple languages. 
 It may be desirable to have each concept labeled in each of the languages that are also used on the other concepts,
-as language coverage incompleteness for some concepts may indicate shortcomings of thesauri ($\mathcal{SL}_{0}$)
+as language coverage incompleteness for some concepts may indicate shortcomings of thesauri (\emph{informational})
 \cite{MaderHaslhoferIsaac2012}.
-
 %\textbf{Validation and Reasoning.}
-\emph{Default values} (\emph{R-31, R-38}) for objects/literals of given properties are inferred automatically when properties are not present in the data.
-The value \emph{true} for the property {\em disco:isPublic} indicates that a {\em disco:LogicalDataSet} can be accessed by anyone.
-Per default, however, access to data sets should be restricted (\emph{false}) ($\mathcal{SL}_{0}$).
-Many properties are not necessarily required but \emph{recommended} within a particular context (\emph{R-72}).
-The property {\em skos:notation}, e.g., is not mandatory for {\em disco:Variable}s, but recommended to represent variable names ($\mathcal{SL}_{0}$).
+%\emph{Default values} (\emph{R-31, R-38}) for objects/literals of given properties are inferred automatically when properties are not present in the data.
+%The value \emph{true} for the property {\em disco:isPublic} indicates that a {\em disco:LogicalDataSet} can be accessed by anyone.
+%Per default, however, access to data sets should be restricted (\emph{false}) ($\mathcal{SL}_{0}$).
+%Many properties are not necessarily required but \emph{recommended} within a particular context (\emph{R-72}).
+%The property {\em skos:notation}, e.g., is not mandatory for {\em disco:Variable}s, but recommended to represent variable names ($\mathcal{SL}_{0}$).
 Percentage values are only valid when they are within the literal range of 0 and 100 (\emph{R-45: literal ranges}; $\mathcal{SL}_{2}$)
@@
 
-\begin{center}
-\begin{DL} 
-$\mathcal{K}=\{$ 
-	&\ms{(funct identifier$\sp{\overline{\ }})$, identifier keyfor Resource}
- \}\\ 
-\end{DL}
-\end{center}
+%\begin{center}
+%\begin{DL} 
+%$\mathcal{K}=\{$ 
+	%&\ms{(funct identifier$\sp{\overline{\ }})$, identifier keyfor Resource}
+ %\}\\ 
+%\end{DL}
+%\end{center}
 
@@
 In \emph{Disco}, resources are uniquely identified by the property \emph{adms:identifier},
-which is therefore inverse-functional,
-i.e., for each \emph{rdfs:Resource x}, there can be at most one distinct resource \emph{y} such that \emph{y} is connected by \emph{adms:identifier$\sp{\overline{\ }}$} to \emph{x} ($\mathcal{SL}_{2}$).
+which is therefore inverse-functional $(\ms{funct identifier}\sp{\overline{\ }})$,
+i.e., for each \emph{rdfs:Resource x}, there can be at most one distinct resource \emph{y} such that \emph{y} is connected by \emph{adms:identifier$\sp{\overline{\ }}$} to \emph{x} (\emph{error}).
 %\begin{DL}
@@
 Thus and as there are different sorts of key, and as keys can lead to undecidability, 
-\emph{DL} is extended with the construct \emph{keyfor} \cite{Lutz2005} which is implemented by the \emph{OWL 2} \emph{hasKey} construct.
+\emph{DL} is extended with the construct \emph{keyfor} (\ms{identifier \ms{keyfor} Resource}) \cite{Lutz2005} which is implemented by the \emph{OWL 2} \emph{hasKey} construct.
 %\emph{OWL 2} \emph{hasKey} implements \emph{keyfor} ($\mathcal{SL}_{2}$) and thus can be used to identify resources uniquely, to merge resources with identical key property values, and to recognize constraint violations.
@@
 
-$\mathcal{CT}_{C}$ denotes the set of constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
+%$\mathcal{CT}_{C}$ denotes the set of constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
 \emph{Data model consistency} constraints ensure the integrity of
@@
 and no two \emph{qb:Observations} in the same \emph{qb:DataSet}
-can have the same value for all dimensions ($\mathcal{SL}_{1}$).
+can have the same value for all dimensions (\emph{warning}).
 If a \emph{qb:DataSet} \emph{D} has a \emph{qb:Slice} \emph{S}, and \emph{S} has an
-\emph{qb:Observation} \emph{O}, then the \emph{qb:DataSet} corresponding to \emph{O} must be \emph{D} ($\mathcal{SL}_{1}$).
+\emph{qb:Observation} \emph{O}, then the \emph{qb:DataSet} corresponding to \emph{O} must be \emph{D} (\emph{warning}).
 %Relative frequencies of variable codes are calculated correctly, if the cumulative percentage (\emph{disco:cumulativePercentage}) of a given code exactly matches the cumulative percentage of the previous code
 %plus the percentage value (\emph{disco:percentage}) of the current code ($\mathcal{SL}_{2}$).
-{\em Mathematical Operations} (\emph{R-41, R-42}; e.g. date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
-The sum of percentage values of all variable codes, e.g., must exactly be 100 ($\mathcal{SL}_{2}$)
-and the minimum absolute frequency of all variable codes do not have to be greater than the maximum ($\mathcal{SL}_{2}$).
+%{\em Mathematical Operations} (\emph{R-41, R-42}; e.g. date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
+%The sum of percentage values of all variable codes, e.g., must exactly be 100 ($\mathcal{SL}_{2}$)
+%and the minimum absolute frequency of all variable codes do not have to be greater than the maximum ($\mathcal{SL}_{2}$).
 
@@
 If an abstract and an external description are absent, however,  
-a title or an alternative title should be given ($\mathcal{SL}_{1}$).
+a title or an alternative title should be given (\emph{warning}).
 In case a variable is represented in form of a code list, codes may be associated with categories, i.e., human-readable labels ($\mathcal{SL}_{0}$).
 The variable \emph{Education at pre-school}, e.g., is represented as ordered code list without any categories.
-If a {\em skos:Concept} represents a code (having {\em skos:notation} and {\em skos:prefLabel} properties), 
-then the property {\em disco:isValid} has to be stated indicating if the code stands for valid (\emph{true}) or missing (\emph{false}) cases ($\mathcal{SL}_{2}$).
+%If a {\em skos:Concept} represents a code (having {\em skos:notation} and {\em skos:prefLabel} properties), 
+%then the property {\em disco:isValid} has to be stated indicating if the code stands for valid (\emph{true}) or missing (\emph{false}) cases ($\mathcal{SL}_{2}$).
 \emph{Context-specific exclusive or of property groups} (\emph{R-11}) constraints
 restrict individuals of given classes to have properties defined within exactly one of multiple property groups.
-\emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes/categories), but not both ($\mathcal{SL}_{2}$).
+\emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes), but not both ($\mathcal{SL}_{2}$).
 

### 2015-04-30 paper/paper7/paper7.tex
4

@@
 %The property {\em skos:notation}, e.g., is not mandatory for {\em disco:Variable}s, but recommended to represent variable names ($\mathcal{SL}_{0}$).
-Percentage values are only valid when they are within the literal range of 0 and 100 (\emph{R-45: literal ranges}; $\mathcal{SL}_{2}$)
+Percentage values are only valid when they are within the literal range of 0 and 100 (\emph{R-45: literal ranges}; \emph{error})
 which is checked for \emph{disco:percentage} standing for the number of cases of a given code in relation to the total number of cases for a particular variable.
@@
 Every \emph{qb:Observation}, e.g., must have a value for each dimension
-declared in its \emph{qb:DataStructureDefinition} ($\mathcal{SL}_{2}$)
+declared in its \emph{qb:DataStructureDefinition} (\emph{error})
 and no two \emph{qb:Observations} in the same \emph{qb:DataSet}
@@
 %and the minimum absolute frequency of all variable codes do not have to be greater than the maximum ($\mathcal{SL}_{2}$).
-
 %\textbf{Hierarchies and Ordering.}
@@
 %, as, e.g., no hierarchical query expansion can be performed on search terms to find documents with more general content.) \cite{MaderHaslhoferIsaac2012}. 
-
 %A very common research question is to compare variables of multiple studies or countries (constraint type: \emph{comparison}).
@@
 %If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the remaining two constraints is getting more serious.
-
 %\textbf{Membership in Controlled Vocabularies.}
@@
 If a dimension property, e.g., has a \emph{qb:codeList},
-then the value of the dimension property on every \emph{qb:Observation} must be in the code list ($\mathcal{SL}_{2}$).
-Summary statistics types like minimum, maximum, and arithmetic mean are maintained within a controlled vocabulary.  
-Thus, summary statistics can only have \emph{disco:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType}, a \emph{skos:ConceptScheme} ($\mathcal{SL}_{2}$).
+then the value of the dimension property on every \emph{qb:Observation} must be in the code list (\emph{error}).
+%Summary statistics types like minimum, maximum, and arithmetic mean are maintained within a controlled vocabulary.  
+%Thus, summary statistics can only have \emph{disco:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType}, a \emph{skos:ConceptScheme} ($\mathcal{SL}_{2}$).
 Objects/literals can be declared to be ordered for given properties (\emph{R-121/217: ordering}).
 Variables, questions, and codes, e.g., are typically organized in a particular order. 
-If codes (\emph{skos:Concept}) should be ordered, they must be members (\emph{skos:memberList}) in an ordered collection (\emph{skos:OrderedCollection}), the variable's code list ($\mathcal{SL}_{0}$).
+If codes (\emph{skos:Concept}) should be ordered, they must be members (\emph{skos:memberList}) in an ordered collection (\emph{skos:OrderedCollection}), the variable's code list (\emph{informational}).
 
@@
 a title or an alternative title should be given (\emph{warning}).
-In case a variable is represented in form of a code list, codes may be associated with categories, i.e., human-readable labels ($\mathcal{SL}_{0}$).
+In case a variable is represented in form of a code list, codes may be associated with categories, i.e., human-readable labels (\emph{informational}).
 The variable \emph{Education at pre-school}, e.g., is represented as ordered code list without any categories.
@@
 restrict individuals of given classes to have properties defined within exactly one of multiple property groups.
-\emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes), but not both ($\mathcal{SL}_{2}$).
+\emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes), but not both (\emph{error}).
 

### 2015-04-30 paper/paper7/paper7.tex
implementation

@@
 
-SPARQL is generally seen as the method of choice to validate RDF data according to certain constraints.
-We use \emph{SPIN}, 
-a SPARQL-based way to formulate and check constraints, as basis to develop a
-validation environment (available at \url{http://purl.org/net/rdfval-demo})\footnote{Source code downloadable at: \url{https://github.com/boschthomas/rdf-validator}} to validate RDF data according to constraints expressed my arbitrary constraint languages like Shape Expressions,
-%\footnote{\url{http://www.w3.org/Submission/shex-primer/}}
-Resource Shapes, and the Web Ontology Language\footnote{SPIN mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} \cite{BoschEckert2014-2}.
-The \emph{RDF Validator} also validates RDF data to ensure correct syntax, semantics, and integrity of diverse vocabularies such as \emph{Disco}, \emph{QB}, \emph{SKOS}, and \emph{PHDD}.
-Although accessible within our validation tool, we provide all implemented constraints\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} in form of SPARQL CONSTRUCT queries.
-For the subsequent evaluation, we implemented 213 constraints on \emph{Disco}, \emph{QB}, \emph{SKOS}, and \emph{PHDD} data sets.
-The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.
-There is one SPIN construct template for each constraint type and vocabulary-specific constraint\footnote{For a comprehensive description of the \emph{RDF Validator}, we refer to \cite{BoschEckert2014-2}}.
-A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples indicating the subject and the properties causing constraint violations, and the reason why constraint violations have been raised.
-A SPIN construct template creates constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
-\emph{Missy}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}} provides comprehensive Linked Data services like diverse RDF exports of person-level metadata conforming to the \emph{Disco} vocabulary in form of multiple concrete syntaxes.
-
-\ke{Überarbeiten und mit nächstem teil mergen. Nur das erzählen, was für die Auswertung auf den Datensets relevant ist. 114 constraints, 3 vokabulare, wie wurden die datasets daraufhin validiert.}
+%\ke{Überarbeiten und mit nächstem teil mergen. Nur das erzählen, was für die Auswertung auf den Datensets relevant ist. 114 constraints, 3 vokabulare, wie wurden die datasets daraufhin validiert.}
 
@@
 of 53 different types on six vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classified them according to the complexity level of their type and their severity level.
-For 114 of these constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
+For 114 of these constraints\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}}, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
 We distinct two classes of vocabularies: 
@@
 4,178 / 477,737,281 (\emph{SKOS}), and 
-1,526 / 9,673,055 (\emph{Disco}) data sets / triples using the \emph{RDF Validator} in batch mode.
+1,526 / 9,673,055 (\emph{Disco}) data sets / triples using our validation environment in batch mode.
 We validated, i.a., 
@@
 As we evaluated nearly 10 thousand \emph{QB} data sets, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.
+
+As \emph{SPARQL} is generally seen as the method of choice to validate RDF data according to certain constraints,
+we use \emph{SPIN}, 
+a \emph{SPARQL}-based way to formulate and check constraints, as basis to develop a
+validation environment (available at \url{http://purl.org/net/rdfval-demo})\footnote{Source code downloadable at: \url{https://github.com/boschthomas/rdf-validator}} to validate RDF data according to constraints expressed my arbitrary constraint languages\footnote{SPIN mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} \cite{BoschEckert2014-2}.
+The \emph{RDF Validator} also validates RDF data according to constraints defined for vocabularies such as \emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, and \emph{XKOS}.
+%Although accessible within our validation tool, we provide all implemented constraints\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} in form of SPARQL CONSTRUCT queries.
+The \emph{SPIN} engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.
+There is one SPIN construct template for each constraint type\footnote{For a comprehensive description of the \emph{RDF Validator}, we refer to \cite{BoschEckert2014-2}}.
+A \emph{SPIN} construct template contains a \emph{SPARQL CONSTRUCT} query which generates constraint violation triples indicating the subject and the properties causing constraint violations, and the reason why constraint violations have been raised.
+A \emph{SPIN} construct template creates constraint violation triples if all triple patterns within the \emph{SPARQL WHERE clause} match.
+%\emph{Missy}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}} provides comprehensive Linked Data services like diverse RDF exports of person-level metadata conforming to the \emph{Disco} vocabulary in form of multiple concrete syntaxes.
 

### 2015-04-30 paper/paper7/paper7.tex
abstract

@@
 Based on our work in the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group, we identified and published by today 82 types of constraints that are required by various stakeholders for data applications.
-In this paper, we formulate 246 constraints of 53 different types on six different vocabularies (Disco, QB, SKOS, PHDD, DCAT, XKOS) and classify them according to the complexity level of their type and their severity level.
-For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.
-\ke{check numbers}
-Based on the results, we formulate several hypotheses to direct the further development of constraint langugaes.
+In this paper, we formulate 246 constraints of 53 different types on six different vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classify them according to the complexity level of their type and their severity level.
+For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
+\ke{check numbers}\tb{Zahlen stimmen!}
+Based on the results, we formulate several hypotheses to direct the further development of constraint languages.
 

### 2015-04-30 paper/paper7/paper7.tex
abstract

@@
 \label{rdf-representation}
-\tb{Ich habe XKOS und DCAT noch ganz am Ende eingeführt (jeweils nur 1 Satz)}
+\tb{Ich habe Beschreibungen von XKOS und DCAT noch ganz am Ende eingeführt (jeweils nur 1 Satz)}
 %In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.
 
-For our evaluation, we examined six different vocabularies commonly used in or developed for the SBE sciences which are briefly introduced in the following.
-For three of them, we analysed actual data according to constraint violations.
-For PHDD, there is not yet enough data available so we limit our examination to the vocabulary itself.
+For our evaluation, we examined six different vocabularies commonly used in or developed for the \emph{SBE} sciences which are briefly introduced in the following.
+For three of them, we analyzed actual data according to constraint violations.
+For \emph{PHDD} and \emph{XKOS}, there is not yet enough data available so we limit our examination to the vocabularies themselves.\tb{müssen wir auch noch schreiben wieso wie keine DCAT daten validiert haben?}
 

### 2015-04-30 paper/paper7/paper7.tex
abstract

@@
 
-The social, behavioural, and economic sciences (SBE) require high-quality data for their empirical research.
+The social, behavioural, and economic sciences (\emph{SBE}) require high-quality data for their empirical research.
 For more than a decade, members of the \emph{SBE} community have been developing and using a
@@
 With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration.
-Therefore, not only established vocabularies like SKOS are used;
+Therefore, not only established vocabularies like \emph{SKOS} are used;
 recently, members of the \emph{SBE} and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.
 
-For constraint formulation and validation on RDF data, several languages exist or are currently developed, like \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles}.
+For constraint formulation and validation on RDF data\tb{nicht validation of RDF data?}, several languages exist or are currently developed, like \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles}.
 \emph{OWL 2} is also used as a constraint language under a closed world assumption.
-With its direct support of validation via SPARQL, \emph{SPIN}%\footnote{\url{http://spinRDF.org/}}
+With its direct support of validation via \emph{SPARQL}, \emph{SPIN}%\footnote{\url{http://spinRDF.org/}}
 is very popular and certainly plays an important role for future developments in this field.
-It is particularly interesting as a means to validate arbitrary constraint languages by mapping them to SPARQL \cite{BoschEckert2014-2}.
+It is particularly interesting as a means to validate arbitrary constraint languages by mapping them to \emph{SPARQL} \cite{BoschEckert2014-2}.
 Yet, there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners.
@@
 In 2014, two working groups on RDF validation have been established to develop a language to express constraints on RDF data: 
-the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles task group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}} which among others bundles the requirements of data institutions of the cultural heritage and SBE sector and represents them in the W3C group.
+the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles task group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}} which among others bundles the requirements of data institutions of the cultural heritage and \emph{SBE} sector and represents them in the W3C group.
 
@@
 The database connects requirements to use cases, case studies and implementations and forms the basis of this paper.
-To gain a better understanding about the role of certain requirements for data quality and in order to direct the further development of constraint langugaes, we collected constraints for commonly used vocabularies in the SBE domain, either from the vocabularies themselves or from domain and data experts.
+To gain a better understanding about the role of certain requirements for data quality and in order to direct the further development of constraint languages, we collected constraints for commonly used vocabularies in the SBE domain, either from the vocabularies themselves or from domain and data experts.
 All in all, this lead to TODO constraints on TODO vocabularies.
 We let the experts classify the constraints according to the severity if they are violated.
-Furthermore, we classified the type of each constraint (corresponding to a requirement) based on its complexity ranging from types commonly found in vocabulary specificatons (e.g., domain and range), over types that are simply stated using common constraint languages (e.g., cardinality restrictions) to complex types that involve complex data structures or need more sophisticated langugaes to be easily expressible (e.g., constraints on network topologies).\ke{Thomas: Ok so?}
+Furthermore, we classified the type of each constraint (corresponding to a requirement) based on its complexity ranging from types commonly found in vocabulary specifications (e.g., domain and range), over types that are simply stated using common constraint languages (e.g., cardinality restrictions) to complex types that involve complex data structures or need more sophisticated languages to be easily expressible (e.g., constraints on network topologies).\ke{Thomas: Ok so?}
 

### 2015-04-30 paper/paper7/paper7.tex
abstract

@@
 The database connects requirements to use cases, case studies and implementations and forms the basis of this paper.
-To gain a better understanding about the role of certain requirements for data quality and in order to direct the further development of constraint languages, we collected constraints for commonly used vocabularies in the SBE domain, either from the vocabularies themselves or from domain and data experts.
-All in all, this lead to TODO constraints on TODO vocabularies.
+To gain a better understanding about the role of certain requirements for data quality and in order to direct the further development of constraint languages, we collected constraints for commonly used vocabularies in the \emph{SBE} domain, either from the vocabularies themselves or from domain and data experts.
+All in all, this lead to TODO constraints on TODO vocabularies\tb{246 constraints on six vocabularies}.
 We let the experts classify the constraints according to the severity if they are violated.
-Furthermore, we classified the type of each constraint (corresponding to a requirement) based on its complexity ranging from types commonly found in vocabulary specifications (e.g., domain and range), over types that are simply stated using common constraint languages (e.g., cardinality restrictions) to complex types that involve complex data structures or need more sophisticated languages to be easily expressible (e.g., constraints on network topologies).\ke{Thomas: Ok so?}
-
-As we do not want to base our conclusions on the evaluations of vocabularies and constraint definitions alone, we conducted a large-scale experiment and evaluated the data quality of 15,694 data sets (4,26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.
+Furthermore, we classified the type of each constraint (corresponding to a requirement) based on its complexity ranging from types commonly found in vocabulary specifications (e.g., domain and range)\tb{and cardinality restrictions}, over types that are simply stated using common constraint languages (e.g., cardinality restrictions\tb{nein, nimm hier language tag cardinalities / cardinalty restrictions können formal in vokabularen spezifiert werden}) to complex types that involve complex data structures or need more sophisticated languages to be easily expressible (e.g., constraints on network topologies\tb{vielleicht besser: constraint on graph-based structures}).
+
+As we do not want to base our conclusions on the evaluations of vocabularies and constraint definitions alone, we conducted a large-scale experiment and evaluated the data quality of 15,694 data sets (4,26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
 
@@
 In this paper, we discuss constraints on RDF data in general.
-Note that the data represented in RDF can be data in the sense of SBE sciences, but also metadata about published or unpublished data.
+Note that the data represented in RDF can be data in the sense of \emph{SBE} sciences, but also metadata about published or unpublished data.
 We generally refer to both simply as RDF data and only distinguish between data and metadata in the data set descriptions and in the case that it matters for the purpose of this paper.

### 2015-04-30 paper/paper7/paper7.tex
abstract

@@
 \label{rdf-representation}
-\tb{Ich habe Beschreibungen von XKOS und DCAT noch ganz am Ende eingeführt (jeweils nur 1 Satz)}
+\tb{Ich habe Beschreibungen von XKOS und DCAT noch ganz am Ende eingeführt (jeweils nur 1 Satz)}\tb{die vokabular-beschreibungen klarer strukturieren}
 %In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.
@@
 %This includes data documentation at the study and variable level as well as documentation materials, tools and further information. 
-\ke{Wieso jetzt wieder qb?}\tb{ich möchte zeigen wie aggregierte daten und personenbezogene daten in RDF verbunden sind. Weglassen?}
-Aggregated (qb:DataSet) and underlying person-level data sets (\emph{disco:LogicalDataSet}) are connected by \emph{prov:wasDerivedFrom}. 
+%\ke{Wieso jetzt wieder qb?}\tb{ich möchte zeigen wie aggregierte daten und personenbezogene daten in RDF verbunden sind. Weglassen?}
+%Aggregated (qb:DataSet) and underlying person-level data sets (\emph{disco:LogicalDataSet}) are connected by \emph{prov:wasDerivedFrom}. 
 The aggregated variable \emph{formal childcare} is calculated on the basis of six person-level variables 
@@
 
+\tb{je nach hypothese spezifische aufgaben um die hypothese zu beweisen}
 2/3 of the \emph{Disco} violations result from \emph{vocabulary constraints},
@@
 \end{hyp}
+
 In general, \emph{vocabulary} and \emph{simple constraints} are easily, concisely, and intuitively expressible by either modeling languages (e.g., \emph{RDF}, \emph{RDFS}, \emph{OWL 2}) or constraint languages (e.g., \emph{ShEx}, \emph{ReSh}, \emph{SPIN}).
@@
 \tb{ 
-die vokabular-beschreibungen klarer strukturieren. du nutzt plötzlich disco elemente, disco wird überhaupt nicht vernünftig eingeführt, obwohl es später untersucht wird
-alles, was nicht der aussage des papers (neuer titel, btw) dient, solltest du weglassen
 klare, einfache struktur: 1. grundidee (constraints identifizieren, validieren auf datensets, zu belastbaren aussagen kommen für die weitere entwicklung von constraint languages)

### 2015-04-30 paper/paper7/paper7.tex
answer questions

@@
 wie gesagt, können wir nicht bei RDF data bleiben?
-was anderes behandelt ihr doch eh nicht und qb enthält doch keine metadaten.}
+was anderes behandelt ihr doch eh nicht und qb enthält doch keine metadaten.} \tb{ich wollte nu beschreiben, dass data provider verantwortlich dafür sind, dass ihre daten festgelegten regeln / bedingungen / constraints entsprechen / wenn von mehreren data providern geharvestet wird, ist das noch eine zusätzliche dimension, können wir aber auch weglassen}
 

### 2015-04-30 paper/paper7/paper7.tex
answer questions

@@
 das habt ihr doch gar nicht gemacht sondern ganz allgemein constraints für vokabulare aufgestellt.
-Ist QB und Disco nicht sowieso unabhängig von konkreten Variablen?}
+Ist QB und Disco nicht sowieso unabhängig von konkreten Variablen?}\tb{das soll nur ein beipsiel sein, wann eine komplexere validierung im kontext von sbe sinn macht (1) + (2) sind vocabulary constraints und (3) + (4) sind complex constraints}
 
@@
 A \emph{qb:DataStructureDefinition} contains metadata of the data collection.
-The variable \emph{formal childcare} is modelled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
+The variable \emph{formal childcare} is modeled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
 The variables \emph{year}, \emph{duration}, \emph{age}, and \emph{country} are \emph{qb:dimensions}.
@@
 \ke{Wieso springt das von einer sehr knappen Einführung direkt zu konkreten (beliebigen?) Variablen?
-Ich möchte wissen, wofür QB benutzt wird und gerne ein konkretes Beispiel sehen, um mir einen Data Cube vorstellen zu können.}
+Ich möchte wissen, wofür QB benutzt wird und gerne ein konkretes Beispiel sehen, um mir einen Data Cube vorstellen zu können.}\tb{hmm, ich halte das beispiel für ein knappes und verständliches beipsiel wie eine tabelle in qb dargestellt wird / es ist auch der link enthalten zu der tabelle von eurostat}
 

### 2015-04-30 paper/paper7/paper7.tex
3

@@
 \label{rdf-representation}
-\tb{Ich habe Beschreibungen von XKOS und DCAT noch ganz am Ende eingeführt (jeweils nur 1 Satz)}\tb{die vokabular-beschreibungen klarer strukturieren}
+
 %In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.
@@
 For three of them, we analyzed actual data according to constraint violations.
-For \emph{PHDD} and \emph{XKOS}, there is not yet enough data available so we limit our examination to the vocabularies themselves.\tb{müssen wir auch noch schreiben wieso wie keine DCAT daten validiert haben?}
+For \emph{PHDD} and \emph{XKOS}, there is not yet enough data available so we limit our examination to the vocabularies themselves.
 
@@
 %(e.g., the year in which \emph{formal childcare} has been determined).
-\ke{Wieso springt das von einer sehr knappen Einführung direkt zu konkreten (beliebigen?) Variablen?
-Ich möchte wissen, wofür QB benutzt wird und gerne ein konkretes Beispiel sehen, um mir einen Data Cube vorstellen zu können.}\tb{hmm, ich halte das beispiel für ein knappes und verständliches beipsiel wie eine tabelle in qb dargestellt wird / es ist auch der link enthalten zu der tabelle von eurostat}
+%\ke{Wieso springt das von einer sehr knappen Einführung direkt zu konkreten (beliebigen?) Variablen?
+Ich möchte wissen, wofür QB benutzt wird und gerne ein konkretes %Beispiel sehen, um mir einen Data Cube vorstellen zu können.}\tb{hmm, ich halte das beispiel für ein knappes und verständliches beipsiel wie eine tabelle in qb dargestellt wird / es ist auch der link enthalten zu der tabelle von eurostat}
 
@@
 
-\tb{ 
-klare, einfache struktur: 1. grundidee (constraints identifizieren, validieren auf datensets, zu belastbaren aussagen kommen für die weitere entwicklung von constraint languages)
-2. vorstellung der untersuchten vokabulare
-3.
-beschreiben, wo die constraints herkommen, bzw.
-wie die generiert wurden.
-dabei auch auf die klassifikation eingehen, aber nur im hinblick auf die spätere auswertung, nicht als main contribution des papers
-4. evaluation mit beschreibung der datasets in setup (das les ich mir gleich mal durch, das hast du ja schon neu geschrieben)
-ja, und dann prägnante conclusion mit zusammenfassung der hypothesen, der bedutung für die weitere entwicklung von CLs und natürlich future work
-}
-
 \bibliography{../../literature/literature}{}

### 2015-04-30 paper/paper7/paper7.tex
hypotheses

@@
 		\hline
-		\textbf{\emph{complex}} & 25.9\% & 18.3\% & 37.1\% & \textbf{100\%} & \textbf{37.1\%} & 21.4\% & 33.4\% & \textbf{46.6\%} \\
+		\textbf{\emph{complex}} & 25.9\% & 18.3\% & 37.1\% & \textbf{100.0\%} & \textbf{37.1\%} & 21.4\% & 33.4\% & \textbf{46.6\%} \\
 		\textbf{\emph{simple}} & 19.6\% & 15.7\% & 8.6\% & 0.0\% & \textbf{34.3\%} & \textbf{78.6\%} & 20.8\% & 31.4\% \\
@@
 		\textbf{\emph{info}} & \textbf{52.5\%} & \textbf{52.6\%} & 11.4\% & 0.0\% & \textbf{60.0\%} & 41.2\% & \textbf{41.3\%} & 31.3\% \\
-		\textbf{\emph{warning}} & 7.0\% & 29.4\% & 8.6\% & \textbf{99,8\%} & 14.3\% & \textbf{58.8\%} & 10.0\% & \textbf{62.7\%} \\
-		\textbf{\emph{error}} & 40.6\% & 18\% & \textbf{80.0\%} & 0.3\% & 25.7\% & 0.0\% & \textbf{48.8\%} & 6.1\%\\
+		\textbf{\emph{warning}} & 7.0\% & 29.4\% & 8.6\% & \textbf{99.8\%} & 14.3\% & \textbf{58.8\%} & 10.0\% & \textbf{62.7\%} \\
+		\textbf{\emph{error}} & 40.6\% & 18.0\% & \textbf{80.0\%} & 0.3\% & 25.7\% & 0.0\% & \textbf{48.8\%} & 6.1\%\\
     \bottomrule
@@
 %\tb{1. Fakten (diese Fakten bewirken eine Erhöhung der Datenqualität) 2. Hypothese (unsere Interpretation der Ergebnisse, unsere Behauptung)}
-Almost 1/2 of all 213 constraints and more than 50\% of the \emph{Disco} and the \emph{QB} constraints are \emph{vocabulary constraints}.
+Almost 1/2 of all 213 constraints and more than 1/2 of the \emph{Disco} and the \emph{QB} constraints are \emph{vocabulary constraints}.
 The \emph{SKOS} constraints are nearly to the same extend \emph{vocabulary}, \emph{simple}, and \emph{complex constraints}. 
@@
 \begin{hyp}
-As a significant amount of 46 \% of the constraints are vocabulary constraints which can be expressed by modeling languages like RDF, RDFS, and OWL 2,
+%As a significant amount of 46 \% of the constraints are vocabulary constraints which can be expressed by modeling languages like RDF, RDFS, and OWL 2,
+%the further development of constraint languages should concentrate on expressing simple and especially complex constraints which up to now in most cases can only be expressed by plain SPARQL.   
+As a significant amount of 54 \% of the constraints are either simple or complex constraints,
 the further development of constraint languages should concentrate on expressing simple and especially complex constraints which up to now in most cases can only be expressed by plain SPARQL.  
@@
 
-\tb{je nach hypothese spezifische aufgaben um die hypothese zu beweisen}
+%\tb{je nach hypothese spezifische aufgaben um die hypothese zu beweisen}
 2/3 of the \emph{Disco} violations result from \emph{vocabulary constraints},
@@
 For well-established vocabularies, \emph{vocabulary constraints} are almost completely satisfied\footnote{e.g.
-only 1.777 \emph{QB} violations} which indicates good data quality according to formal specifications of vocabularies.
+only 1.777 \emph{QB} violations} which indicates good data quality according to their formal specifications.
 %This demonstrates that data providers take account of the formal specifications of well-established vocabularies.
 For newly defined vocabularies, however, 2/3 of all violations are raised by \emph{vocabulary constraints}
-which indicates bad data quality with regard to the formal specifications of vocabularies.
+which indicates bad data quality with regard to their formal specifications.
 
 \begin{hyp}
-Data represented by well-established vocabularies corresponds to formal specifications of these vocabularies which demonstrates that constraint formulation in general works. 
-Data represented by newly developed vocabularies, in contrast, does not correspond to formal specifications of these vocabularies.
+Data represented by well-established vocabularies corresponds to their formal specifications which demonstrates that constraint formulation in general works. 
+Data represented by newly developed vocabularies, in contrast, does not correspond to their formal specifications.
 \end{hyp}
@@
 In case newly developed vocabularies turn into well-established ones,
-data providers are experienced in publishing their data in conformance with these vocabularies, 
-and the formal specifications are more elaborated and therefore clearer. 
-As a consequence, vocabulary constraints are satisfied which leads to better data quality.
+data providers are experienced in publishing their data in conformance with these vocabularies
+and formal specifications are more elaborated. 
+As a consequence, \emph{vocabulary constraints} are satisfied to a greater extend which leads to better data quality.
 
@@
 
+\tb{sollen wir die beiden appendixe diese paper hier nochmals erwähnen?}
+
 \footnote{The first appendix of this paper describing each constraint in detail is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}}
 
-We implemented a validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages and to ensure correct syntax and semantics of diverse vocabularies such as \emph{Disco}, \emph{QB}, \emph{SKOS}, and \emph{PHDD} (section \ref{implementation}).
-We exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets (more than 4.2 billion triples and 15 thousand data sets) by means of 213  constraints of the majority of the constraint types\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).
+\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.}
+
+%We implemented a validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages and to ensure correct syntax and semantics of diverse vocabularies such as \emph{Disco}, \emph{QB}, \emph{SKOS}, and \emph{PHDD} (section \ref{implementation}).
+%We exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets (more than 4.2 billion triples and 15 thousand data sets) by means of 213  constraints of the majority of the constraint types\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).
+
+Based on the evaluation results,
+we formulated several hypotheses to direct the further development of constraint languages.
+To make valid general statements for all vocabularies, however,
+the hypotheses still have to be verified or falsified
+by evaluating the quality of data represented by more than three vocabularies.
+The main hypotheses are 
+(1) As a significant amount of 54 \% of the constraints are either simple or complex constraints,
+the further development of constraint languages should concentrate on expressing simple and especially complex constraints which up to now in most cases can only be expressed by plain SPARQL. 
+(2)
 

### 2015-04-30 paper/paper7/paper7.tex
hypotheses

@@
 For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
-\ke{check numbers}\tb{Zahlen stimmen!}
 Based on the results, we formulate several hypotheses to direct the further development of constraint languages.
@@
 
-For constraint formulation and validation on RDF data\tb{nicht validation of RDF data?}, several languages exist or are currently developed, like \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles}.
+For constraint formulation and validation of RDF data, several languages exist or are currently developed, like \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles}.
 \emph{OWL 2} is also used as a constraint language under a closed world assumption.
@@
 %the further development of constraint languages should concentrate on expressing simple and especially complex constraints which up to now in most cases can only be expressed by plain SPARQL.   
-As a significant amount of 54 \% of the constraints are either simple or complex constraints,
+As a significant amount of 54\% of the constraints are either simple or complex constraints,
 the further development of constraint languages should concentrate on expressing simple and especially complex constraints which up to now in most cases can only be expressed by plain SPARQL.  
@@
 \begin{hyp}
-A significant amount of 47\% of the violations refer to complex constraints that are not easily, concisely, and intuitively expressible in existing constraint languages which confirms the necessity to provide suitable constraint languages.
+A significant amount of 47\% of the violations refer to complex constraints that are not easily, concisely, and intuitively expressible by existing constraint languages which confirms the necessity to provide suitable constraint languages.
 \end{hyp}
 
-In general, \emph{vocabulary} and \emph{simple constraints} are easily, concisely, and intuitively expressible by either modeling languages (e.g., \emph{RDF}, \emph{RDFS}, \emph{OWL 2}) or constraint languages (e.g., \emph{ShEx}, \emph{ReSh}, \emph{SPIN}).
-This is not the case, however, for \emph{complex constraints} which in most cases are still only expressible by plain \emph{SPARQL}. 
+In general, \emph{vocabulary constraints} are expressible by either modeling languages (e.g., \emph{RDF}, \emph{RDFS}, \emph{OWL 2}) or constraint languages. 
+\emph{Simple constraints} and especially \emph{complex constraints}, however, are in most cases only expressible by plain \emph{SPARQL}. 
 As almost 1/2 of all violations are caused by \emph{complex constraints}, 
@@
 \emph{warning constraints} 2/3 of all violations.
-As the percentage of severe violations is very low for all vocabularies,
+As the percentage of severe violations is very low for all vocabularies (6.1\%),
 data quality is high with regard to the severity level of constraints.
@@
 The main hypotheses are 
-(1) As a significant amount of 54 \% of the constraints are either simple or complex constraints,
+(1) The percentage of severe violations is very low, compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
+(2) A significant amount of 47\% of the violations refer to complex constraints that are not easily, concisely, and intuitively expressible by existing constraint languages which confirms the necessity to provide suitable constraint languages.
+(3) As a significant amount of 54\% of the constraints are either simple or complex constraints,
 the further development of constraint languages should concentrate on expressing simple and especially complex constraints which up to now in most cases can only be expressed by plain SPARQL.
-(2)
 

### 2015-04-30 paper/paper7/paper7.tex
future work

@@
 To gain a better understanding about the role of certain requirements for data quality and in order to direct the further development of constraint languages, we collected constraints for commonly used vocabularies in the \emph{SBE} domain, either from the vocabularies themselves or from domain and data experts.
-All in all, this lead to TODO constraints on TODO vocabularies\tb{246 constraints on six vocabularies}.
+All in all, this lead to 246 constraints on six vocabularies.
 We let the experts classify the constraints according to the severity if they are violated.
-Furthermore, we classified the type of each constraint (corresponding to a requirement) based on its complexity ranging from types commonly found in vocabulary specifications (e.g., domain and range)\tb{and cardinality restrictions}, over types that are simply stated using common constraint languages (e.g., cardinality restrictions\tb{nein, nimm hier language tag cardinalities / cardinalty restrictions können formal in vokabularen spezifiert werden}) to complex types that involve complex data structures or need more sophisticated languages to be easily expressible (e.g., constraints on network topologies\tb{vielleicht besser: constraint on graph-based structures}).
+Furthermore, we classified the type of each constraint (corresponding to a requirement) based on its complexity ranging from types commonly found in vocabulary specifications (e.g., domain, range, and cardinality restrictions),
+over types that are simply stated using common constraint languages (e.g., language tag cardinality restrictions) to complex types that involve complex data structures or need more sophisticated languages to be easily expressible
+%(e.g., constraints on network topologies)
+(e.g., constraints on graph-based structures}).
 
@@
 \emph{xsd:string}).
-\emph{disco:CategoryStatistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString}.
+\emph{disco:Category} \emph{Statistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString}.
 %Validation should \emph{exploit sub-super relations} in vocabularies (\emph{R-224}).
@@
 We validated, i.a., 
-(1) \emph{QB} data sets published by the \emph{Australian Bureau of Statistics (ABS)},
-the \emph{European Central Bank (ECB)}, and the
-\emph{Organisation for Economic Co-operation and Development (OECD)},
+(1) \emph{QB} data sets published by the \emph{Australian Bureau of Statistics},
+the \emph{European Central Bank}, and the
+\emph{Organisation for Economic Co-operation and Development},
 (2) \emph{SKOS} thesauri like the \emph{AGROVOC Multilingual agricultural thesaurus},
 the \emph{STW Thesaurus for Economics}, and the
-\emph{Thesaurus for the Social Sciences (TheSoz)}, and
-(3) \emph{Disco} data sets provided by the \emph{Microdata Information System (Missy)}, 
-the \emph{DwB Discovery Portal}, the
-\emph{Danish Data Archive (DDA)}, and the
-\emph{Swedish National Data Service (SND)}.
+\emph{Thesaurus for the Social Sciences}, and
+(3) \emph{Disco} data sets provided by the \emph{Microdata Information System}, 
+the \emph{Data Without Boundaries Discovery Portal}, the
+\emph{Danish Data Archive}, and the
+\emph{Swedish National Data Service}.
 We recently published a technical report\footnote{\label{technical-report-2}Available at: \url{http://arxiv.org/abs/1504.04478}} (serving as second appendix of this paper) 
@@
     \\ \emph{C (constraints), CV (constraint violations)}
-    \caption{Constraints and Constraint Violations}
+    \caption{Constraints and constraint violations}
 		\label{tab:evaluation-constraint-violations}
@@
 as serious violations occur partially.
-Constraints are serious when they violate the integrity of vocabularies.
-For well-established vocabularies, it is well documented and the experience is high how to guarantee this integrity.
-This is not the case or newly-developed vocabularies.
+%Constraints are serious when they violate the integrity of vocabularies.
+%For well-established vocabularies, it is well documented and the experience is high how to guarantee this integrity
+%which is not the case or newly-developed vocabularies.
 \begin{hyp}
-Especially for newly developed vocabularies, constraint languages should be used to a larger extend to meet severe constraints which guarantee their integrity.   
+Especially for newly developed vocabularies, constraint languages should be used to a larger extend to meet severe constraints.   
 \end{hyp}
@@
     %\\ \emph{C (constraints), CT (constraint types)}
-    \caption{Complexity vs. Severity of Constraints}
+    \caption{Relation between complexity and severity level of constraints}
 		\label{tab:evaluation-complexity-severity}
@@
 
-\tb{sollen wir die beiden appendixe diese paper hier nochmals erwähnen?}
-
-\footnote{The first appendix of this paper describing each constraint in detail is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}}
-
-\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.}
-
 %We implemented a validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages and to ensure correct syntax and semantics of diverse vocabularies such as \emph{Disco}, \emph{QB}, \emph{SKOS}, and \emph{PHDD} (section \ref{implementation}).
@@
 
+We identified and published by today 82 types of constraints that are required by various stakeholders for data applications.
+In close collaboration with several SBE domain experts, we formulated 246 constraints\footnote{The first appendix of this paper describing each constraint in detail is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}}
+ of 53 different types on six different vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classified them according to the complexity level of their type and their severity level.
+
+For 114 of these constraints, we evaluated\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.}
+ the data quality of 15,694 data sets (4.26 billion triples) of research data for the \emph{SBE} sciences obtained from 33 SPARQL endpoints.
 Based on the evaluation results,
@@
 by evaluating the quality of data represented by more than three vocabularies.
-The main hypotheses are 
-(1) The percentage of severe violations is very low, compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
-(2) A significant amount of 47\% of the violations refer to complex constraints that are not easily, concisely, and intuitively expressible by existing constraint languages which confirms the necessity to provide suitable constraint languages.
-(3) As a significant amount of 54\% of the constraints are either simple or complex constraints,
-the further development of constraint languages should concentrate on expressing simple and especially complex constraints which up to now in most cases can only be expressed by plain SPARQL.
+The main hypotheses are: 
+(1) The percentage of severe violations is very low which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
+(2) The further development of constraint languages should concentrate on how to express \emph{complex constraints} as 44\% of all \emph{complex constraints} are also serious ones.
+(3) 47\% of the violations refer to complex constraints that are in most cases not expressible by existing constraint languages which confirms the necessity to provide suitable constraint languages.
+(4) As 54\% of the constraints are either \emph{simple} or \emph{complex constraints},
+the further development of constraint languages should concentrate on expressing \emph{simple} and especially \emph{complex constraints} which up to now in most cases can only be expressed by plain \emph{SPARQL}.
 

### 2015-05-01 paper/paper7/paper7.tex
motivation

@@
 
-The data most often used in research within the \emph{SBE} community is \emph{person-level data} (or more generally \emph{record-unit data}, i.e., data collected about individuals, businesses, and households) in form of responses to studies or taken from administrative registers
+The data most often used in research within \emph{SBE} sciences is \emph{person-level data} (or more generally \emph{record-unit data}, i.e., data collected about individuals, businesses, and households) in form of responses to studies or taken from administrative registers
 (such as hospital records, registers of births and deaths). 
@@
 The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying person-level data.
-Aggregated data is more and more published in form of CSV files,
-allowing to perform data calculations.\ke{abgeshen davon dass ich more and more nicht mehr sehen kann, ist der zusammenhang mit RDF daten und damit RDF providern im nächsten satz unklar}
+Aggregated data is published in form of CSV files,
+allowing to perform calculations on the data.
 %For these calculations, definitions of the columns are needed (e.g. is a given variable interpreted numerically or as a string).
@@
 %The data could be either represented in records with character-separated values (CSV) or in records with fixed length. 
-Portals harvest metadata (as well as publicly available data) from multiple RDF data providers.
-To ensure high quality, (meta)data must satisfy certain criteria - specified in terms of RDF constraints.\ke{verwirrend.
-wie gesagt, können wir nicht bei RDF data bleiben?
-was anderes behandelt ihr doch eh nicht und qb enthält doch keine metadaten.} \tb{ich wollte nu beschreiben, dass data provider verantwortlich dafür sind, dass ihre daten festgelegten regeln / bedingungen / constraints entsprechen / wenn von mehreren data providern geharvestet wird, ist das noch eine zusätzliche dimension, können wir aber auch weglassen}
+%Portals harvest metadata (as well as publicly available data) from multiple RDF data providers.
+\tb{To ensure high quality, data must satisfy certain criteria - specified in terms of RDF constraints.}
 
@@
 
-To determine if variables measuring \emph{age} 
+A very important and representative RDF validation use case within SBE sciences is the comparison of variables between data collections of different countries.
+Several constraints on RDF data are checked 
+to determine if variables measuring \emph{age} 
 - collected for different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
-are comparable, diverse constraints are checked:
+are comparable:
 (1) variable definitions must be available, 
@@
 
-\ke{ich finde das immer noch recht verwirrend.
-Ist das mit den aggregierten Daten wichtig für dieses Paper?
-Wieso werden constraints nur gechecked wenn variablen auf vergleichbarkeit geprüft werden?
+%\ke{Wieso werden constraints nur gechecked wenn variablen auf vergleichbarkeit geprüft werden?
 das habt ihr doch gar nicht gemacht sondern ganz allgemein constraints für vokabulare aufgestellt.

### 2015-05-01 paper/paper7/paper7.tex
motivation

@@
 
-A very important and representative RDF validation use case within SBE sciences is the comparison of variables between data collections of different countries.
-Several constraints on RDF data are checked 
+A very important and representative RDF validation case study within SBE sciences is the comparison of variables between data collections of different countries.
+Several constraints on RDF data are checked for each data collection
 to determine if variables measuring \emph{age} 
@@
 (4) code lists must either be identical or at least similar.
-If a researcher only wants to get a first overview over comparable variables (use case 1), 
+If a researcher only wants to get a first overview over the comparability of variables (use case 1), 
 covering the first three constraints may be sufficient,

### 2015-05-01 paper/paper7/paper7.tex
motivation

@@
 %Portals harvest metadata (as well as publicly available data) from multiple RDF data providers.
-\tb{To ensure high quality, data must satisfy certain criteria - specified in terms of RDF constraints.}
+%\tb{To ensure high quality, data must satisfy certain criteria - specified in terms of RDF constraints.}
 
@@
 A very important and representative RDF validation case study within SBE sciences is the comparison of variables between data collections of different countries.
-Several constraints on RDF data are checked for each data collection
+Several vocabulary-specific constraints on RDF data are checked for each data collection
 to determine if variables measuring \emph{age} 

### 2015-05-01 paper/paper7/paper7.tex
appendix

@@
 \label{classification}
-
+\tb{82 constraint types / 76 requirements}
 Bosch et al.
@@
 \emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}\cite{BoschNolleAcarEckert2015}.
-We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages.
+We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} (serving as first appendix of this paper) in which we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages.
 The knowledge representation formalism \emph{Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
@@
 %Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
-We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as first appendix of this paper) in which we describe 246 constraints of 53 distinct constraint types on six vocabularies \cite{BoschZapilkoWackerowEckert2015}.
+We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as second appendix of this paper) in which we describe 246 constraints of 53 distinct constraint types on six vocabularies \cite{BoschZapilkoWackerowEckert2015}.
 
@@
 \emph{Swedish National Data Service}.
-We recently published a technical report\footnote{\label{technical-report-2}Available at: \url{http://arxiv.org/abs/1504.04478}} (serving as second appendix of this paper) 
+We recently published a technical report\footnote{\label{technical-report-2}Available at: \url{http://arxiv.org/abs/1504.04478}} (serving as third appendix of this paper) 
 in which we describe the evaluation in detail \cite{BoschZapilkoWackerowEckert2015-2}. 
@@
 
-We identified and published by today 82 types of constraints that are required by various stakeholders for data applications.
-In close collaboration with several SBE domain experts, we formulated 246 constraints\footnote{The first appendix of this paper describing each constraint in detail is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}}
+We identified and published by today 82 types of constraints\footnote{The first appendix of this paper, in which we explain each requirement/constraint type in detail, is available at: \url{http://arxiv.org/abs/1501.03933} \cite{BoschNolleAcarEckert2015}}
+that are required by various stakeholders for data applications.
+In close collaboration with several SBE domain experts, we formulated 246 constraints\footnote{The second appendix of this paper, in which we describe each vocabulary-specific constraint in detail, is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}}
  of 53 different types on six different vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classified them according to the complexity level of their type and their severity level.
 
-For 114 of these constraints, we evaluated\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.}
+For 114 of these constraints, we evaluated\footnote{The third appendix of this paper, in which we describe the evaluation in detail, is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.}
  the data quality of 15,694 data sets (4.26 billion triples) of research data for the \emph{SBE} sciences obtained from 33 SPARQL endpoints.

### 2015-05-01 paper/paper7/paper7.tex
76 -> 82 constraint types
introduction

@@
 
-The \textbf{contribution} of this paper is the development of a system 
-\begin{enumerate}
-	\item to classify RDF constraints (according to their severity levels) to evaluate the quality of metadata and data which may be represented by any vocabulary and 
-	\item to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (sections \ref{classification} - \ref{complex-constraint-types}).
-\end{enumerate}
-By defining a huge amount of constraints of the majority of the constraint types,   
-we apply the developed classification system to several and different vocabularies from the \emph{SBE} domain to represent both metadata and data and therefore prove its generality.
-A complex and complete real world running example from the \emph{SBE} domain serves to prove the claim that the developed classification system perfectly applies for diverse vocabularies.
-%, i.e., that it does not matter which vocabularies are used to represent (meta)data and for which domains constraints are defined.
-We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
-how data in tabular format and metadata on person-level data sets, aggregated data sets, and thesauri are represented in RDF, 
-how therefore reused vocabularies are interrelated (section \ref{rdf-representation}),
-and how \emph{SBE} (meta)data is validated against constraints of different constraint types (sections \ref{classification} - \ref{complex-constraint-types}).
-We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple vocabularies to get an understanding
-(1) which sets of constraint types (on different levels of complexity) and 
-(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).
+%The \textbf{contribution} of this paper is the development of a system 
+%\begin{enumerate}
+	%\item to classify RDF constraints (according to their severity levels) to evaluate the quality of metadata and data which may be represented by any vocabulary and 
+	%\item to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (sections \ref{classification} - \ref{complex-constraint-types}).
+%\end{enumerate}
+%By defining a huge amount of constraints of the majority of the constraint types,   
+%we apply the developed classification system to several and different vocabularies from the \emph{SBE} domain to represent both metadata and data and therefore prove its generality.
+%A complex and complete real world running example from the \emph{SBE} domain serves to prove the claim that the developed classification system perfectly applies for diverse vocabularies.
+%%, i.e., that it does not matter which vocabularies are used to represent (meta)data and for which domains constraints are defined.
+%We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
+%how data in tabular format and metadata on person-level data sets, aggregated data sets, and thesauri are represented in RDF, 
+%how therefore reused vocabularies are interrelated (section \ref{rdf-representation}),
+%and how \emph{SBE} (meta)data is validated against constraints of different constraint types (sections \ref{classification} - \ref{complex-constraint-types}).
+%We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple vocabularies to get an understanding
+%(1) which sets of constraint types (on different levels of complexity) and 
+%(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).
 
@@
 \label{classification}
-\tb{82 constraint types / 76 requirements}
+
 Bosch et al.
-identified 76 requirements to formulate RDF constraints (e.g.
+identified 82 requirements to formulate RDF constraints (e.g.
 \emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}\cite{BoschNolleAcarEckert2015}.
@@
 Therefore, this technical report contains mappings to \emph{DL} to logically underpin each requirement and to determine which \emph{DL} constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
+%In total, we distinguish 82 RDF constraint types as we identified 6 RDF constraint types which are only necessary for validating particular vocabularies.
 We classified both RDF constraint types and RDF constraints to gain better insights into the quality of RDF data with respect to this classification, independent of the used vocabulary.

### 2015-05-01 paper/paper7/paper7.tex
introduction

@@
 To gain a better understanding about the role of certain requirements for data quality and in order to direct the further development of constraint languages, we collected constraints for commonly used vocabularies in the \emph{SBE} domain, either from the vocabularies themselves or from domain and data experts.
-All in all, this lead to 246 constraints on six vocabularies.
+All in all, this lead to 246 constraints  of 53 different types on six vocabularies.
+\tb{in total 82 constraint types}
 We let the experts classify the constraints according to the severity if they are violated.
@@
 We generally refer to both simply as RDF data and only distinguish between data and metadata in the data set descriptions and in the case that it matters for the purpose of this paper.
+The remainder of the paper is structured as follows.
 
@@
 that are required by various stakeholders for data applications.
-In close collaboration with several SBE domain experts, we formulated 246 constraints\footnote{The second appendix of this paper, in which we describe each vocabulary-specific constraint in detail, is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}}
+In close collaboration with several \emph{SBE} domain experts, we formulated 246 constraints\footnote{The second appendix of this paper, in which we describe each vocabulary-specific constraint in detail, is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}}
  of 53 different types on six different vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classified them according to the complexity level of their type and their severity level.

### 2015-05-01 paper/paper7/paper7.tex
introduction

@@
 %and ICPSR - the largest SBE data archive in the US.
-
 In XML, the definition of schemas containing data constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
-
 With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration.
@@
 It is publicly available and open for further contributions\footnote{Online at \url{http://purl.org/net/rdf-validation}}.
-
 The database connects requirements to use cases, case studies and implementations and forms the basis of this paper. 
+We distinguish 82 requirements to formulate RDF constraints; 
+each of them corresponding to an RDF constraint type.
+
 To gain a better understanding about the role of certain requirements for data quality and in order to direct the further development of constraint languages, we collected constraints for commonly used vocabularies in the \emph{SBE} domain, either from the vocabularies themselves or from domain and data experts.
 All in all, this lead to 246 constraints  of 53 different types on six vocabularies.
-\tb{in total 82 constraint types}
 We let the experts classify the constraints according to the severity if they are violated.
@@
 %(e.g., constraints on network topologies)
-(e.g., constraints on graph-based structures}).
-
-As we do not want to base our conclusions on the evaluations of vocabularies and constraint definitions alone, we conducted a large-scale experiment and evaluated the data quality of 15,694 data sets (4,26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
-
+(e.g., constraints on graph-based structures) (section \ref{classification}).
+
+As we do not want to base our conclusions on the evaluations of vocabularies and constraint definitions alone, we conducted a large-scale experiment.
+For 114 constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
+%evaluated the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
+Based on the evaluation results,
+we formulated several hypotheses to direct the further development of constraint languages.
+To make valid general statements for all vocabularies, however,
+the hypotheses still have to be verified or falsified
+by evaluating the quality of data represented by more than three vocabularies (section \ref{evaluation}).
 %The \textbf{contribution} of this paper is the development of a system 
@@
 %(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).
-
 In this paper, we discuss constraints on RDF data in general.
@@
 We generally refer to both simply as RDF data and only distinguish between data and metadata in the data set descriptions and in the case that it matters for the purpose of this paper.
-The remainder of the paper is structured as follows.
+%The remainder of the paper is structured as follows.
 
@@
 %As constraint types are used to define constraints on (meta)data expressed by any vocabulary, the proposed constraint classification can be applied generically, i.e. vocabulary-independent.
-
-\subsection{Motivation}
-\label{motivation}
 

### 2015-05-01 paper/paper7/paper7.tex
sec 4

--- 2015-05-01 paper/paper7/paper7.tex
@@
 %(e.g., constraints on network topologies)
-(e.g., constraints on graph-based structures}).
+(e.g., constraints on graph-based structures).
 
@@
 
-Bosch et al.
-identified 82 requirements to formulate RDF constraints (e.g.
-\emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}\cite{BoschNolleAcarEckert2015}.
-We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} (serving as first appendix of this paper) in which we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages.
-The knowledge representation formalism \emph{Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
-Therefore, this technical report contains mappings to \emph{DL} to logically underpin each requirement and to determine which \emph{DL} constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
+To gain better insights into the role that certain types of constraints play for the quality of RDF data, we use two simple classifications: on the one hand, we classify RDF constraint types according to their complexity and on the other hand, we classify concrete constraints formulated for a vocabulary according to the perceived severity of a violation.
+
+Within the working groups, we identified by today 82 requirements to formulate RDF constraints (e.g.
+\emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}.
+Within a technical report serving as first appendix of this paper we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages \cite{BoschNolleAcarEckert2015}.
+We provide mappings to representations in Description Logics (\emph{DL}) to logically underpin each requirement and to determine which \emph{DL} constructs are needed to express each constraint type.
+
 %In total, we distinguish 82 RDF constraint types as we identified 6 RDF constraint types which are only necessary for validating particular vocabularies.
-We classified both RDF constraint types and RDF constraints to gain better insights into the quality of RDF data with respect to this classification, independent of the used vocabulary.
+
 %Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
-We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as second appendix of this paper) in which we describe 246 constraints of 53 distinct constraint types on six vocabularies \cite{BoschZapilkoWackerowEckert2015}.
-
-\subsection{Classification of RDF Constraint Types}
+
+The classification of the 246 concrete constraints on 6 vocabularies according to severity levels is published in a second technical report serving as second appendix of this paper \cite{BoschZapilkoWackerowEckert2015}.
+In the following, we summarize the results for the purpose of our evaluation.
+
+\subsection{Complexity of Constraint Types}
 
@@
 \emph{Vocabulary constraint types}
-denotes the set of constraint types whose constraints 
-can be extracted completely automatically out of formal specifications of vocabularies.
-As vocabularies have been specified using \emph{RDF}, \emph{RDFS}, and \emph{OWL},
-\emph{vocabulary constraints} ensure that the data is consistent with the intended syntaxes, semantics, and integrity of vocabularies' data models.
+denotes the set of constraint types that are commonly found for constraints within formal specifications of vocabularies, i.e., constraints that are formulated using \emph{RDFS} and common constructs of \emph{OWL}.
+We determined this set based on the evaluation of the six vocabularies.
+\emph{Vocabulary constraints} generally can be seen as a basic level of constraints ensuring that the data is consistent with the intended syntaxes, semantics, and integrity of vocabularies' data models.
+
 %The {\em existential quantification} (\emph{R-86}) 
@@
 
-\emph{Simple} and \emph{complex constraints} are in contrast to \emph{vocabulary constraints} not explicitly defined within formal specifications of vocabularies.
-\emph{Simple} and \emph{complex constraints} are defined according to textual descriptions of the intended semantics of vocabularies.  
-\emph{Simple constraint types} is the set of constraint types whose constraints can be easily defined without much effort in addition to the already defined \emph{vocabulary constraints}.
-{\emph{Data property facets} (\emph{R-46}) is an example of a \emph{simple constraint type} which enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
+\emph{Simple} and \emph{complex constraints} are in contrast to \emph{vocabulary constraints} usually not (yet) explicitly defined within formal specifications of vocabularies.
+Instead, they are often defined in textual descriptions of the vocabularies.
+Additionally, we let our domain and data experts define constraints when they agreed that violating the constraint would affect the usefulness of the data.
+
+We further distinguished \emph{simple constraint types} as the set of constraint types whose constraints can be easily defined without much effort in addition to the already defined \emph{vocabulary constraints}.
+\emph{Data property facets} (\emph{R-46}) is an example of a \emph{simple constraint type} which enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
 The abstract of series/studies, e.g., should have a minimum length which is easily and concisely expressible by SPARQL: 
@@
 \end{ex}
+For these constraints, we expect a straight-forward support in future constraint languages.
 
@@
 \end{ex}
-\emph{Complex constraints} are in most cases only expressible by plain \emph{SPARQL}
-which shows the importance to develop suitable constraint languages.
-
-\subsection{Classification of RDF Constraints}
+\emph{Complex constraints} are today in most cases only expressible by plain \emph{SPARQL}. Depending on their usefulness, a support in constraint languages should be considered.
+
+\subsection{Severity of Constraints}
 
@@
 
+For the evaluat
+
 \subsection{Experimental Setup}

### 2015-05-01 paper/paper7/paper7.tex

@@
 %(e.g., constraints on network topologies)
-(e.g., constraints on graph-based structures).
-
-As we do not want to base our conclusions on the evaluations of vocabularies and constraint definitions alone, we conducted a large-scale experiment and evaluated the data quality of 15,694 data sets (4,26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
-
+(e.g., constraints on graph-based structures) (section \ref{classification}).
+
+As we do not want to base our conclusions on the evaluations of vocabularies and constraint definitions alone, we conducted a large-scale experiment.
+For 114 constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
+%evaluated the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
+Based on the evaluation results,
+we formulated several hypotheses to direct the further development of constraint languages.
+To make valid general statements for all vocabularies, however,
+the hypotheses still have to be verified or falsified
+by evaluating the quality of data represented by more than three vocabularies (section \ref{evaluation}).
 %The \textbf{contribution} of this paper is the development of a system 

### 2015-05-01 paper/paper7/paper7.tex
sec 4

@@
 %whereas, the violation of another constraint of the same type may be minor.
-\emph{SBE} experts determined the default \textbf{\emph{severity level}} (\emph{R-158}) for each of the 246 constraints to indicate how serious the violation of the constraint is.
+\emph{SBE} experts determined the default \textbf{\emph{severity level}}\footnote{The possibility to define severity levels in vocabularies is in itself a requirement (\emph{R-158}) defined by the DCMI task group.} for each of the 246 constraints to indicate how serious the violation of the constraint is.
 %We propose an extensible metric to measure the continuum of severity levels ranging from \emph{informational} to \emph{error}.
@@
 %They are not seen as serious errors.
+\emph{Warnings} are syntactic or semantic problems which typically should not lead to an abortion of data processing.
 \emph{Errors} are syntactic or semantic errors which should cause the abortion of data processing. 
-\emph{Warnings} are syntactic or semantic errors which typically should not lead to an abortion of data processing.
 %Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
@@
 %Data not corresponding to \emph{error constraints}, however, cannot be processed further after validation.
-As the purpose of \emph{vocabulary constraints} is to ensure explicitly stated semantics of vocabularies, 
-their default severity levels are in most cases very strong (\emph{error}) and 
-in average stronger than the severity levels of \emph{simple} and \emph{complex constraints}.
-As a consequence, violating many \emph{vocabulary constraints} is an indicator for bad (meta)data quality.
-
-Although, we provide default severity levels for each constraint, validation environments should enable users to adapt the severity levels of constraints according to their individual needs.
-Validation environments should enable users to select which constraints to validate against depending on their individual use cases.
-For some use cases, 
-validating \emph{vocabulary constraints} may be more important than validating \emph{simple} or \emph{complex constraints}.
-For other use cases,
-validating \emph{error constraints} may be sufficient without taking \emph{warning} and \emph{informational constraints} into account.
-We evaluated the (meta)data quality of large real world data sets represented by multiple and different vocabularies to get an understanding  
-(1) which sets of constraint types (on different levels of complexity) and 
-(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).
+
+Note that there is a correlation between the severity of a constraint and the complexity of its type: vocabulary constraint are in most cases classified with an \emph{error} level as they typically represent basic and important constraints; there is a reason why they have been included in the vocabulary specification.
+
+% Although, we provide default severity levels for each constraint, validation environments should enable users to adapt the severity levels of constraints according to their individual needs.
+% Validation environments should enable users to select which constraints to validate against depending on their individual use cases.
+% For some use cases, 
+% validating \emph{vocabulary constraints} may be more important than validating \emph{simple} or \emph{complex constraints}.
+% For other use cases,
+% validating \emph{error constraints} may be sufficient without taking \emph{warning} and \emph{informational constraints} into account.
+% We evaluated the (meta)data quality of large real world data sets represented by multiple and different vocabularies to get an understanding  
+% (1) which sets of constraint types (on different levels of complexity) and 
+% (2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).
 

### 2015-05-01 paper/paper7/paper7.tex
sec 4

@@
 
-\subsection{Vocabulary Constraint Types}
+\subsection{Examples}
 \label{vocabulary-constraint-types}
@@
 %i.e., individuals cannot be instances of multiple disjoint classes.
+\subsubsection*{Vocabulary Constraint Types.}
 It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values (\emph{R-30/37: allowed values}). 
@@
 
-\subsection{Simple Constraint Types}
+\subsubsection*{Simple Constraint Types.}
 
@@
 
-\subsection{Complex Constraint Types}
+\subsubsection*{Complex Constraint Types.}
 \label{complex-constraint-types}

### 2015-05-01 paper/paper7/paper7.tex
introduction

--- 2015-05-01 paper/paper7/paper7.tex
@@
 %\textbf{Metadata on Aggregated Data.}
-The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing metadata on \emph{data cubes}, i.e.
+The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e.
 multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}.
@@
 A \emph{qb:DataStructureDefinition} contains metadata of the data collection.
-The variable \emph{formal childcare} is modeled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
+The variable \emph{formal childcare}, e.g., is modeled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
 The variables \emph{year}, \emph{duration}, \emph{age}, and \emph{country} are \emph{qb:dimensions}.
@@
 The table structure is related to table columns (\emph{phdd:Column}) which are described by column descriptions (\emph{phdd:DelimitedColumnDescription}).
-For the column containing the cell values in percent, the column position (\emph{5}), the recommended data type (\emph{xsd:nonNegativeInteger}), and the storage format (\emph{TINYINT}) is stated. 
+For the column containing the actual cell values in percent, the column position (\emph{5}), the recommended data type (\emph{xsd:non} \emph{NegativeInteger}), and the storage format (\emph{TINYINT}) is stated.
 %The RDFication enables further aggregations and calculations, e.g., in order to compare \emph{formal childcare} between Northern and Southern Europe or between otherwise grouped countries.
@@
 %\textbf{Metadata on Person-Level Data.}
-For more detailed analyses we refer to the metadata on person-level data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}.
+For more detailed analyses we refer to the person-level data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}.
 %published by the \emph{Microdata Information System (MISSY)}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}}.
@@
 The aggregated variable \emph{formal childcare} is calculated on the basis of six person-level variables 
-(e.g., \emph{Education at pre-school}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC/2011/Cross-sectional/original#2011-Cross-sectional-RL010}})
+(e.g., \emph{Education at pre-school})
+%\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC/2011/Cross-sectional/original#2011-Cross-sectional-RL010}})
 %(2) Education at compulsory school,
@@
 The codes of the variable \emph{Education at pre-school} (number of education hours per week) are modeled as \emph{skos:Concepts} and 
-a \emph{skos:OrderedCollection} organizes them in a particular order within a \emph{skos:memberList}.
+a \emph{skos:OrderedCollection} organizes them in a particular order within a \emph{skos:member} \emph{List}.
 A variable may be associated with a theoretical concept (\emph{skos:Concept}). 
-\emph{skos:narrower} builds the hierarchy of theoretical concepts within a \emph{skos:ConceptScheme} of a series.
+\emph{skos:narrower} builds the hierarchy of theoretical concepts within a \emph{skos:Concept} \emph{Scheme} of a series.
 The variable \emph{Education at pre-school} is assigned to the theoretical concept \emph{Child Care} which is the narrower concept of \emph{Education} - one of the top concepts of the series \emph{EU-SILC}.
@@
 
-To gain better insights into the role that certain types of constraints play for the quality of RDF data, we use two simple classifications: on the one hand, we classify RDF constraint types according to their complexity and on the other hand, we classify concrete constraints formulated for a vocabulary according to the perceived severity of a violation.
-
-Within the working groups, we identified by today 82 requirements to formulate RDF constraints (e.g.
-\emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}.
-Within a technical report serving as first appendix of this paper we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages \cite{BoschNolleAcarEckert2015}.
-We provide mappings to representations in Description Logics (\emph{DL}) to logically underpin each requirement and to determine which \emph{DL} constructs are needed to express each constraint type.
-
+Bosch et al.
+identified 82 requirements to formulate RDF constraints (e.g.
+\emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}\cite{BoschNolleAcarEckert2015}.
+We published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} (serving as first appendix of this paper) in which we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages.
+The knowledge representation formalism \emph{Description logics (DL)}, with its  well-studied theoretical properties, provides the foundational basis for each constraint type.
+Therefore, this technical report contains mappings to \emph{DL} to logically underpin each requirement and to determine which \emph{DL} constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
 %In total, we distinguish 82 RDF constraint types as we identified 6 RDF constraint types which are only necessary for validating particular vocabularies.
-
+We classified both RDF constraint types and RDF constraints to gain better insights into the quality of RDF data with respect to this classification, independent of the used vocabulary.
 %Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
-
-The classification of the 246 concrete constraints on 6 vocabularies according to severity levels is published in a second technical report serving as second appendix of this paper \cite{BoschZapilkoWackerowEckert2015}.
-In the following, we summarize the results for the purpose of our evaluation.
-
-\subsection{Complexity of Constraint Types}
+We recently published a technical report\footnote{\label{technical-report-1}Available at: \url{http://arxiv.org/abs/1504.04479}} (serving as second appendix of this paper) in which we describe 246 constraints of 53 distinct constraint types on six vocabularies \cite{BoschZapilkoWackerowEckert2015}.
+
+\subsection{Classification of RDF Constraint Types}
 
@@
 \emph{Vocabulary constraint types}
-denotes the set of constraint types that are commonly found for constraints within formal specifications of vocabularies, i.e., constraints that are formulated using \emph{RDFS} and common constructs of \emph{OWL}.
-We determined this set based on the evaluation of the six vocabularies.
-\emph{Vocabulary constraints} generally can be seen as a basic level of constraints ensuring that the data is consistent with the intended syntaxes, semantics, and integrity of vocabularies' data models.
-
+denotes the set of constraint types whose constraints 
+can be extracted completely automatically out of formal specifications of vocabularies.
+As vocabularies have been specified using \emph{RDF}, \emph{RDFS}, and \emph{OWL},
+\emph{vocabulary constraints} ensure that the data is consistent with the intended syntaxes, semantics, and integrity of vocabularies' data models.
 %The {\em existential quantification} (\emph{R-86}) 
@@
 
-\emph{Simple} and \emph{complex constraints} are in contrast to \emph{vocabulary constraints} usually not (yet) explicitly defined within formal specifications of vocabularies.
-Instead, they are often defined in textual descriptions of the vocabularies.
-Additionally, we let our domain and data experts define constraints when they agreed that violating the constraint would affect the usefulness of the data.
-
-We further distinguished \emph{simple constraint types} as the set of constraint types whose constraints can be easily defined without much effort in addition to the already defined \emph{vocabulary constraints}.
-\emph{Data property facets} (\emph{R-46}) is an example of a \emph{simple constraint type} which enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
+\emph{Simple} and \emph{complex constraints} are in contrast to \emph{vocabulary constraints} not explicitly defined within formal specifications of vocabularies.
+\emph{Simple} and \emph{complex constraints} are defined according to textual descriptions of the intended semantics of vocabularies.  
+\emph{Simple constraint types} is the set of constraint types whose constraints can be easily defined without much effort in addition to the already defined \emph{vocabulary constraints}.
+{\emph{Data property facets} (\emph{R-46}) is an example of a \emph{simple constraint type} which enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
 The abstract of series/studies, e.g., should have a minimum length which is easily and concisely expressible by SPARQL: 
@@
 \end{ex}
-For these constraints, we expect a straight-forward support in future constraint languages.
 
@@
 \end{ex}
-\emph{Complex constraints} are today in most cases only expressible by plain \emph{SPARQL}. Depending on their usefulness, a support in constraint languages should be considered.
-
-\subsection{Severity of Constraints}
+\emph{Complex constraints} are in most cases only expressible by plain \emph{SPARQL}
+which shows the importance to develop suitable constraint languages.
+
+\subsection{Classification of RDF Constraints}
 
@@
 
-For the evaluat
-
 \subsection{Experimental Setup}

### 2015-05-01 paper/paper7/paper7.tex
introduction

@@
 Based on our work in the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group, we identified and published by today 82 types of constraints that are required by various stakeholders for data applications.
-In this paper, we formulate 246 constraints of 53 different types on six different vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classify them according to the complexity level of their type and their severity level.
+In this paper, we formulate 213 constraints of 53 different types on three different vocabularies (\emph{Disco}, \emph{QB}, and \emph{SKOS}) and classify them according to the complexity level of their type and their severity level.
 For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
@@
 To gain a better understanding about the role of certain requirements for data quality and in order to direct the further development of constraint languages, we collected constraints for commonly used vocabularies in the \emph{SBE} domain, either from the vocabularies themselves or from domain and data experts.
-All in all, this lead to 246 constraints  of 53 different types on six vocabularies.
+All in all, this lead to 213 constraints of 53 different types on three vocabularies.
 We let the experts classify the constraints according to the severity if they are violated.
@@
 
-For our evaluation, we examined six different vocabularies commonly used in or developed for the \emph{SBE} sciences which are briefly introduced in the following.
+We took all well-established and newly developed \emph{SBE} vocabularies into account and defined constraints for six vocabularies commonly used in or developed for the \emph{SBE} sciences which are briefly introduced in the following.
+For three of them, we analyzed actual data according to constraint violations, as for these vocabularies large data sets are already published.
+%e evaluated the data quality of large data sets on three of them, as for these vocabularies large data sets are published.
+
+%For our evaluation, we examined six different vocabularies commonly used in or developed for the \emph{SBE} sciences which are briefly introduced in the following.
 For three of them, we analyzed actual data according to constraint violations.
@@
 
-The classification of the 246 concrete constraints on 6 vocabularies according to severity levels is published in a second technical report serving as second appendix of this paper \cite{BoschZapilkoWackerowEckert2015}.
+The classification of the 213 concrete constraints on three vocabularies according to severity levels is published in a second technical report serving as second appendix of this paper \cite{BoschZapilkoWackerowEckert2015}.
 In the following, we summarize the results for the purpose of our evaluation.
@@
 %whereas, the violation of another constraint of the same type may be minor.
-\emph{SBE} experts determined the default \textbf{\emph{severity level}}\footnote{The possibility to define severity levels in vocabularies is in itself a requirement (\emph{R-158}) defined by the DCMI task group.} for each of the 246 constraints to indicate how serious the violation of the constraint is.
+\emph{SBE} experts determined the default \textbf{\emph{severity level}}\footnote{The possibility to define severity levels in vocabularies is in itself a requirement (\emph{R-158}) defined by the DCMI task group.} for each of the 213 constraints to indicate how serious the violation of the constraint is.
 %We propose an extensible metric to measure the continuum of severity levels ranging from \emph{informational} to \emph{error}.
@@
 that are required by various stakeholders for data applications.
-In close collaboration with several \emph{SBE} domain experts, we formulated 246 constraints\footnote{The second appendix of this paper, in which we describe each vocabulary-specific constraint in detail, is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}}
- of 53 different types on six different vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classified them according to the complexity level of their type and their severity level.
+In close collaboration with several \emph{SBE} domain experts, we formulated 213 constraints\footnote{The second appendix of this paper, in which we describe each vocabulary-specific constraint in detail, is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}}
+ of 53 different types on three different vocabularies (\emph{Disco}, \emph{QB}, and \emph{SKOS}) and classified them according to the complexity level of their type and their severity level.
 

### 2015-05-01 paper/paper7/paper7.tex
sec 5

--- 2015-05-01 paper/paper7/paper7.tex
@@
 
-For the evaluat
+In this section, we describe our findings based on an automatic constraint checking of a large dataset.
+Despite the large volume of the dataset in general, we have to keep in mind that this study only uses data for three vocabularies.
+As described in Section~\ref{rdf-representation}, for other vocabularies there is often not (yet) enough data openly available to draw general conclusions.
+The three vocabularies, however, are representative, cover different aspects of SBE data and are also a mixture of established vocabularies (\emph{QB}, \emph{SKOS}) and a vocabulary under development (\emph{Disco}).
+Due to this limitation, we will present several hypotheses together with a rationale based on the results for the three vocabularies.
+If the hypotheses hold generally is still to be determined, nevertheless they should provide valuable insights for future developments of constraint languages.
 
@@
 %in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$).
-In close collaboration with several \emph{SBE} domain experts, we defined 246 constraint 
-of 53 different types on six vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, \emph{XKOS}) and classified them according to the complexity level of their type and their severity level.
-For 114 of these constraints\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}}, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
-We distinct two classes of vocabularies: 
-(1) well-established vocabularies (e.g., \emph{QB}, \emph{SKOS}) which are widely adopted and accepted and 
-(2) newly developed vocabularies (e.g., \emph{Disco} which will be published in 2015) which are either recently published or are still in the publication process.
+On the three vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}), we identified and classified 114 of constraints,\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} as described before.
+We evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data using these vocabularies, obtained from 33 SPARQL endpoints.
+
+\emph{QB} and \emph{SKOS} are well-established vocabularies which are widely adopted and accepted. \emph{Disco} is a newly developed vocabulary which will be published in 2015.
+
 %It is likely that such a vocabulary is still subject of constant change, that published data may not be consistent with its current version,
@@
 
-We validated 
-9,990 / 3,775,983,610 (\emph{QB}),
-4,178 / 477,737,281 (\emph{SKOS}), and 
-1,526 / 9,673,055 (\emph{Disco}) data sets / triples using our validation environment in batch mode.
-We validated, i.a., 
+Table~\ref{tab:datasets} lists the number of datasets and the overall sizes in terms of triples for each of the vocabularies. We validated, i.a., 
 (1) \emph{QB} data sets published by the \emph{Australian Bureau of Statistics},
@@
 \emph{Swedish National Data Service}.
-We recently published a technical report\footnote{\label{technical-report-2}Available at: \url{http://arxiv.org/abs/1504.04478}} (serving as third appendix of this paper) 
-in which we describe the evaluation in detail \cite{BoschZapilkoWackerowEckert2015-2}. 
-As we evaluated nearly 10 thousand \emph{QB} data sets, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.
-
-As \emph{SPARQL} is generally seen as the method of choice to validate RDF data according to certain constraints,
-we use \emph{SPIN}, 
+
+\begin{table}[H]
+		\scriptsize
+    \begin{center}
+    \begin{tabular}{lrr}
+%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
+%    \\  \cmidrule{2-7}
+           \textbf{Vocabulary}
+           & \textbf{Datasets}
+           & \textbf{Triples}
+
+    \\ \midrule
+		%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
+		%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
+		%\hline
+		\textbf{\emph{QB}} & $9,990$   & $3,775,983,610$  \\
+		\textbf{\emph{SKOS}} & $4,178$  & $477,737,281$ \\
+		\textbf{\emph{Disco}} & $1,526$  & $9,673,055$  \\
+    \bottomrule
+    \end{tabular}
+    %\\ \emph{C (constraints), CT (constraint types)}
+    \caption{Evaluated datasets for each vocabulary}
+		\label{tab:datasets}
+    \end{center}
+\end{table}
+
+In a technical report serving as third appendix of this paper, we describe the evaluation in further detail \cite{BoschZapilkoWackerowEckert2015-2}.
+Furthermore, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.
+
+We use \emph{SPIN}, 
 a \emph{SPARQL}-based way to formulate and check constraints, as basis to develop a
-validation environment (available at \url{http://purl.org/net/rdfval-demo})\footnote{Source code downloadable at: \url{https://github.com/boschthomas/rdf-validator}} to validate RDF data according to constraints expressed my arbitrary constraint languages\footnote{SPIN mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} \cite{BoschEckert2014-2}.
-The \emph{RDF Validator} also validates RDF data according to constraints defined for vocabularies such as \emph{Disco}, \emph{QB}, \emph{SKOS}, \emph{PHDD}, \emph{DCAT}, and \emph{XKOS}.
+validation environment\footnote{Online demo available at \url{http://purl.org/net/rdfval-demo}, source code at: \url{https://github.com/boschthomas/rdf-validator}} to validate RDF data according to constraints expressed by arbitrary constraint languages\footnote{SPIN mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} \cite{BoschEckert2014-2}.
+
+The \emph{RDF Validator} can directly be used to validate arbitrary RDF data for the three vocabularies.
+Additionally, own constraints on vocabularies can be defined using several constraint languages.
+
 %Although accessible within our validation tool, we provide all implemented constraints\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} in form of SPARQL CONSTRUCT queries.
 The \emph{SPIN} engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.
-There is one SPIN construct template for each constraint type\footnote{For a comprehensive description of the \emph{RDF Validator}, we refer to \cite{BoschEckert2014-2}}.
+There is one SPIN construct template for each constraint type.
 A \emph{SPIN} construct template contains a \emph{SPARQL CONSTRUCT} query which generates constraint violation triples indicating the subject and the properties causing constraint violations, and the reason why constraint violations have been raised.

### 2015-05-01 paper/paper7/paper7.tex
introduction

--- 2015-05-01 paper/paper7/paper7.tex
@@
 %(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).
+
 In this paper, we discuss constraints on RDF data in general.
@@
 We generally refer to both simply as RDF data and only distinguish between data and metadata in the data set descriptions and in the case that it matters for the purpose of this paper.
-%The remainder of the paper is structured as follows.
+The underlying \emph{semantics} for RDF validation is \emph{UNA}/\emph{CWA}.
+RDF validation requires that different names represent different objects ({\em unique name assumption (UNA)}), whereas,
+\emph{OWL 2} is based on the {\em non-unique name assumption (nUNA)}.  
+%A data property is \emph{functional} (\emph{R-65}) if for each individual \emph{x}, there can be at most one distinct literal \emph{y} such that \emph{x} is connected by the data property to \emph{y}.
+(See \cite{resource} for this terminology.)
+%When assuming \emph{UNA}, the functional property {\em title} (\ms{funct (title)}) causes a clash
+%in case the book {\em Huckleberry-Finn} has more than one \emph{title}
+%(\ms{title(Huckleberry-Finn, The-Adventures-of-Huckleberry-Finn)}, \ms{title(Huckleberry-Finn, Die-Abenteuer-des-Huckleberry-Finn)}).
+%Assuming nUNA, however, reasoning concludes that the titles {\em The-Adventures-of-Huckleberry-Finn} and {\em Die-Abenteuer-des-Huckleberry-Finn} are the same (\ms{\{The-Adventures-of-Huckleberry-Finn\}} = \ms{\{Die-Abenteuer-des-Huckle} \ms{berry-}\ms{Finn\}}).
+Reasoning in \emph{OWL 2} is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true. 
+%which fits its primary design purpose to represent knowledge on the World Wide Web. 
+%Most of the constraint languages except OWL, have a major shortcoming of redundancy.
+%With its open-world semantics, used as a constraint language, OWL solves the redundancy problem. 
+%\tb{the following example does not show the redundancy problem!}
+%\tb{2. benefit: reasoning solves redundancy problem}
+%As each \emph{book} must have a \emph{title} (\ms{Book $\sqsubseteq \exists$ title.$\top$}) and {\em Hamlet} is a \emph{book} (\ms{Book(Hamlet)}),
+%{\em Hamlet} must have at least one \emph{title}.
+%In an \emph{OWA} setting, this axiom does not cause a constraint violation (even if there is no explicitly defined \emph{title}), since there must be a \emph{title} for this \emph{book} which we may not know.
+On the other hand, RDF validation scenarios require the {\em closed-world assumption (CWA)}, i.e., a statement is inferred to be false if it cannot be proved to be true.
+Classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals.
+This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past.  
+In case we use \emph{OWL 2} constructs in terms of constraints, we adopt the same semantics (CWA) that is for RDF validation in general.
 
@@
 The main hypotheses are: 
-(1) The percentage of severe violations is very low which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
-(2) The further development of constraint languages should concentrate on how to express \emph{complex constraints} as 44\% of all \emph{complex constraints} are also serious ones.
-(3) 47\% of the violations refer to complex constraints that are in most cases not expressible by existing constraint languages which confirms the necessity to provide suitable constraint languages.
-(4) As 54\% of the constraints are either \emph{simple} or \emph{complex constraints},
+\begin{enumerate}
+	\item The percentage of severe violations is very low which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
+  \item The further development of constraint languages should concentrate on how to express \emph{complex constraints} as 44\% of all \emph{complex constraints} are also serious ones.
+  \item 47\% of the violations refer to complex constraints that are in most cases not expressible by existing constraint languages which confirms the necessity to provide suitable constraint languages.
+  \item As 54\% of the constraints are either \emph{simple} or \emph{complex constraints},
 the further development of constraint languages should concentrate on expressing \emph{simple} and especially \emph{complex constraints} which up to now in most cases can only be expressed by plain \emph{SPARQL}.
+\end{enumerate}
 

### 2015-05-01 paper/paper7/paper7.tex
sec 5

--- 2015-05-01 paper/paper7/paper7.tex
@@
 %in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$).
-On the three vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}), we identified and classified 114 of constraints,\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} as described before.
-We evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data using these vocabularies, obtained from 33 SPARQL endpoints.
+On the three vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}), we identified and classified 213 constraints of which we implemented for the data validation 114 constraints.\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} The reason is simply that more time is needed for the remaining implementation.
+We ensured, however, that the implementation is equally distributed over the classes and vocabularies we have.
+We then evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data using these 114 constraints, obtained from 33 SPARQL endpoints.
 
@@
 The constraints and their raised constraint violations are grouped by vocabulary, complexity level of their type, and their severity level.
-The number of evaluated triples and data sets differs between the vocabularies
+The numbers of evaluated triples and data sets differ between the vocabularies
 as we evaluated 3.8 billion \emph{QB}, 480 million \emph{SKOS}, and 10 million \emph{Disco} triples.
@@
 %\tb{1. Fakten (diese Fakten bewirken eine Erhöhung der Datenqualität) 2. Hypothese (unsere Interpretation der Ergebnisse, unsere Behauptung)}
-Almost 1/2 of all 213 constraints and more than 1/2 of the \emph{Disco} and the \emph{QB} constraints are \emph{vocabulary constraints}.
+Almost 1/2 of all constraints and more than 1/2 of the \emph{Disco} and the \emph{QB} constraints are \emph{vocabulary constraints}.
 The \emph{SKOS} constraints are nearly to the same extend \emph{vocabulary}, \emph{simple}, and \emph{complex constraints}. 
@@
 indicates good data quality for all vocabularies with regard to their formal specifications.
-\begin{hyp}
-For all vocabularies, data corresponds to their formal specifications which demonstrates that constraint formulation in general works. 
-\end{hyp}
 
 %\tb{je nach hypothese spezifische aufgaben um die hypothese zu beweisen}
-2/3 of the \emph{Disco} violations result from \emph{vocabulary constraints},
+Moreover, while 2/3 of the \emph{Disco} violations result from \emph{vocabulary constraints},
 \emph{QB} violations are almost only raised by \emph{complex constraints}, and 
 nearly 80\% of the \emph{SKOS} violations are caused by \emph{simple constraints}.
-For well-established vocabularies, \emph{vocabulary constraints} are almost completely satisfied\footnote{e.g.
-only 1.777 \emph{QB} violations} which indicates good data quality according to their formal specifications.
+This means that for the well-established vocabularies \emph{QB} and \emph{SKOS}, \emph{vocabulary constraints} are almost completely satisfied which indicates generally a very impressive data quality, at least in the SBE domain and for the basic requirements.
 %This demonstrates that data providers take account of the formal specifications of well-established vocabularies.
-For newly defined vocabularies, however, 2/3 of all violations are raised by \emph{vocabulary constraints}
-which indicates bad data quality with regard to their formal specifications.
+
+For \emph{Disco}, data providers still have to understand the vocabulary and of course, data can not have high quality if the specification is not yet stable.
 
 \begin{hyp}
-Data represented by well-established vocabularies corresponds to their formal specifications which demonstrates that constraint formulation in general works. 
-Data represented by newly developed vocabularies, in contrast, does not correspond to their formal specifications.
+Data corresponds to their formal specifications which demonstrates that constraint formulation in general works. 
 \end{hyp}
@@
 \begin{hyp}
-Especially for newly developed vocabularies, constraint languages should be used to a larger extend to meet severe constraints.   
+Especially for newly developed vocabularies, constraint languages should be used to a larger extend to meet reduce severe violations.   
 \end{hyp}
@@
 \begin{hyp}
-The further development of constraint languages should concentrate on how to express complex constraints as 44\% of all complex constraints are also serious ones.
+There is significant demand for constraint languages that support the expression of complex constraints as 44\% of all complex constraints are also serious ones.
 \end{hyp}

### 2015-05-01 paper/paper7/paper7.tex
introduction

--- 2015-05-01 paper/paper7/paper7.tex
@@
 %(e.g., constraints on network topologies)
-(e.g., constraints on graph-based structures) (section \ref{classification}).
+(e.g., constraints on graph-based structures) (Section \ref{classification}).
 
@@
 the hypotheses still have to be verified or falsified
-by evaluating the quality of data represented by more than three vocabularies (section \ref{evaluation}).
+by evaluating the quality of data represented by more than three vocabularies (Section \ref{evaluation}).
 %The \textbf{contribution} of this paper is the development of a system 

### 2015-05-01 paper/paper7/paper7.tex
conclusion

@@
 
-We identified and published by today 82 types of constraints\footnote{The first appendix of this paper, in which we explain each requirement/constraint type in detail, is available at: \url{http://arxiv.org/abs/1501.03933} \cite{BoschNolleAcarEckert2015}}
-that are required by various stakeholders for data applications.
-In close collaboration with several \emph{SBE} domain experts, we formulated 213 constraints\footnote{The second appendix of this paper, in which we describe each vocabulary-specific constraint in detail, is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}}
- of 53 different types on three different vocabularies (\emph{Disco}, \emph{QB}, and \emph{SKOS}) and classified them according to the complexity level of their type and their severity level.
-
-For 114 of these constraints, we evaluated\footnote{The third appendix of this paper, in which we describe the evaluation in detail, is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.}
- the data quality of 15,694 data sets (4.26 billion triples) of research data for the \emph{SBE} sciences obtained from 33 SPARQL endpoints.
+We identified and published by today 82 types of constraints  that are required by various stakeholders for data applications.
+In close collaboration with several \emph{SBE} domain experts, we formulated 213 constraints of 53 different types on three different vocabularies (\emph{Disco}, \emph{QB}, and \emph{SKOS}) and classified them according to the complexity level of their type and their severity level.
+
+For 114 of these constraints, we evaluated  the data quality of 15,694 data sets (4.26 billion triples) of research data for the \emph{SBE} sciences obtained from 33 SPARQL endpoints.
+
 Based on the evaluation results,
 we formulated several hypotheses to direct the further development of constraint languages.
-To make valid general statements for all vocabularies, however,
-the hypotheses still have to be verified or falsified
-by evaluating the quality of data represented by more than three vocabularies.
+We regard to the results as hypotheses, as their general applicability beyond the examined vocabularies and for other domains is still to be confirmed.
+
 The main hypotheses are: 
@@
 
+We have been really impressed by the high quality of the \emph{QB} and \emph{SKOS} data.
+This is in contrast to the sometimes heard rumour that Linked Open Data lacks quality.
+We are actively involved in the further development and implementation of constraint languages and will use the results presented in the paper to set priorities on features where we expect the highest impact on the data quality of real-life data in the SBE domain.
+
 \bibliography{../../literature/literature}{}

### 2015-05-03 paper/paper 2/paper 2.tex
Erman feedback

@@
 \newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
+\newcommand{\er}[1]{\todo[size=\small, color=red!40]{\textbf{Erman:} #1}}
 \newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}
@@
 
-In order to develop a vocabulary to describe constraints of any constraint type in a generic way, what we need to do is to specify the vocabulary's underlying semantics and define the basic terminology for the formulation of constraints.
-The underlying \emph{semantics} for RDF validation are \emph{UNA} and \emph{CWA}.
-RDF validation requires that different names represent different objects ({\em unique name assumption (UNA)}), whereas,
-\emph{OWL 2} is based on the {\em non-unique name assumption (nUNA)}.
-\tb{ Erman: One usual problem is that, a constraint that says book should have a single author in OWA, does not mean that it has a unique author.
+\er{A constraint that says book should have a single author in OWA, does not mean that it has a unique author.
 In every model  (an interpretation that makes a set of DL knowledge base true), it can be the case that a book has a single author, however, bringing all those together, this author is not unique.
@@
 But this does not correspond to the intended constraint which is usual in CWA way.}
+
+In order to develop a vocabulary to describe constraints of any constraint type in a generic way, what we need to do is to specify the vocabulary's underlying semantics and to define the basic terminology for the formulation of constraints.
+
+\subsection{Semantics for RDF Validation}
+
+%The underlying \emph{semantics} for RDF validation is \emph{UNA} and \emph{CWA}.
+RDF validation requires that different names represent different objects ({\em unique name assumption (UNA)}), whereas,
+\emph{OWL 2} is based on the {\em non-unique name assumption (nUNA)}.  
 A data property is \emph{functional} (\emph{R-65}) if for each individual \emph{x}, there can be at most one distinct literal \emph{y} such that \emph{x} is connected by the data property to \emph{y}.
-(See \cite{resource} for this terminology.)
 When assuming \emph{UNA}, the functional property {\em title} (\ms{funct (title)}) causes a clash
@@
 
-Reasoning in \emph{OWL 2} is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true . 
+Reasoning in \emph{OWL 2} is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true. 
 %which fits its primary design purpose to represent knowledge on the World Wide Web. 
@@
 This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past.  
-In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general. 
-\tb{feedback from Erman: the major problem is semantics.
+%In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general. 
+%\tb{feedback from Erman: the major problem is semantics.
 OWL basically work in different semantics than others.
@@
 No.}
-\tb{Erman: The problem is OWL doesn't work CWA way, just because we want it.
-If a constraint is represented (recognized) by two different languages, that means, whenever it is violated in one language it is violated in other.
-Since the time is tight and we cannot provide formal semantics for it; nor formally prove those statements.
-We  can go on with whats at hand.
-}
-\tb{Erman thinks formal generic semantics should be defined / Thomas: what do you mean by this? / I inserted these 2 paragraphs about RDF validation semantics. Are your concerns resolved now? }
+\er{If a constraint is represented (recognized) by two different languages, that means, whenever it is violated in one language it is violated in other.
+We have to provide formal generic semantics for it; nor formally prove those statements.}
+
+\subsection{Basic Terminology for the Formulation of RDF Constraints}
 
@@
 The \emph{RDF-CV} does not contain any terms standing for \emph{simple} and \emph{complex constraints}, since \emph{context classes} of \emph{simple constraints} are just reused within \emph{complex constraints} (\emph{simple constraints} associated with \emph{context classes} must hold for individuals of these \emph{context classes}).
-\tb{Erman: If you say its expressible in RDF-CV, than you impose that RDF-CV is a language rather than a vocabulary.
+%\tb{Erman: If you say its expressible in RDF-CV, than you impose that RDF-CV is a language rather than a vocabulary.
 "in different contexts they call it signature which is the same thing".
@@
 As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to describe constraints of all possible constraint types.
+\er{use RDF-CV / not: expressible in RDF-CV / RDF-CV is a vocabulary, not a language}
 

### 2015-05-04 paper/paper 2/paper 2.tex
ESWC feedback
3.1

@@
 %%%% list of authors for the TOC (use if author list has to be modified)
-\institute{GESIS ? Leibniz Institute for the Social Sciences, Germany\\
+\institute{GESIS - Leibniz Institute for the Social Sciences, Germany\\
 \email{thomas.bosch@gesis.org},\\ 
@@
 
-\er{A constraint that says book should have a single author in OWA, does not mean that it has a unique author.
-In every model  (an interpretation that makes a set of DL knowledge base true), it can be the case that a book has a single author, however, bringing all those together, this author is not unique.
-In some models it is Ali, in others its Veli.
-And since in every model there is only one, DL sentences are satisfied.
-But this does not correspond to the intended constraint which is usual in CWA way.}
-
 In order to develop a vocabulary to describe constraints of any constraint type in a generic way, what we need to do is to specify the vocabulary's underlying semantics and to define the basic terminology for the formulation of constraints.
@@
 On the other hand, RDF validation scenarios require the {\em closed-world assumption (CWA)}, i.e., a statement is inferred to be false if it cannot be proved to be true.
-Classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals which yields a constraint violation.
+When assuming the \emph{CWA}, a constraint violation is raised as there is no explicitly defined title. 
+A constraint that says that a book must have at least one title in \emph{OWA}, 
+does not mean that the title has to be unique. 
+In every model  (an interpretation that makes a set of \emph{DL knowledge base} true), 
+it can be the case that a book has a single title, however, 
+this title is not unique. 
+In some models it is \emph{The-Adventures-of-Huckleberry-Finn}, in others it is \emph{Die-Abenteuer-des-Huckleberry-Finn}. 
+And since in every model there is only one, \emph{DL} sentences are satisfied. 
+But this does not correspond to the intended constraint which is usual in \emph{CWA} way.   
+%Classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals which yields a constraint violation.
 This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past.  
@@
 \er{If a constraint is represented (recognized) by two different languages, that means, whenever it is violated in one language it is violated in other.
-We have to provide formal generic semantics for it; nor formally prove those statements.}
+We have to provide formal generic semantics for it; formally prove those statements.}
+
+%Erman:
+%Section 3.1, explains a possible application only in an example specific to UNA and nUNA case, and I also have the 
+%feeling that it is so spread out to the whole work (paper1  especially), and in the core of technical parts. That is, whenever we mean CWA vs. OWA, we turn our head to UNA vs. nUNA.
+%
+%The thing I wanted to point out is that, the difference in CWA and OWA and its consequence/incompatibility is more general (as you also may probably noticed)  than the use of "UNA vs.
+nUNA".
+The example I gave  is independent from the assumption of UNA  or nUNA.
+%
+%You don't need to change something asap, but I think we can improve the exposition of any paper, by giving a classical constraint, how it is done classical in CWA, and how it is done in OWA, and then introducing the extra benefit, redundancy for instance.
+%
+%A constraint that says book should have a single author in OWA, does not mean that it has a unique author.
+In every model  (an interpretation that makes a set of DL knowledge base true), it can be the case that a book has a single author, however, bringing all those together, this author is not unique.
+In some models it is Ali, in others its Veli.
+And since in every model there is only one, DL sentences are satisfied.
+But this does not correspond to the intended constraint which is usual in CWA way.
 

### 2015-05-05 paper/paper 2/paper 2.tex
CWA/UNA

@@
 No.}
-\er{If a constraint is represented (recognized) by two different languages, that means, whenever it is violated in one language it is violated in other.
+
+comments from Erman:
+
+\begin{itemize}
+%\item If a constraint is represented (recognized) by two different languages, that means, whenever it is violated in one language it is violated in other.
 We have to provide formal generic semantics for it; formally prove those statements.}
+
+\item This is simple. You write that:
+In case we want to use OWL 2 as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general.
+The question is how to adopt CWA for OWL2, because it wont behave CWA way, just because we want it.
+So I say, in order to show that it behaves exactly we want it to, we should show that for the cases that we express a constraint (that we speak) in a classical constraint language, say, Scheme (therefore CWA) and  also OWL,  whenever the constraint in Scheme is violated, it's OWL correspondence is also violated.
+That shows that they behave in the same way, as they should.
+
+\item So if you read again my comment again, without knowing which semantics those constraint languages have, one actually does is to show, given an RDF-data it is violated in one language iff it is violated in other.
+And this actually corresponds to the very idea of transformation and generic semantics.
+
+\item Now, what is a generic semantics? 
+It is, the semantics we had in our mind, when typing this long document, that we tried to underpin by the DL language.
+However, regarding CWA and OWA, it is possible that we made some mistakes.
+In order to ensure that, say, if its DL, one needs to show that, a constraint/query written a particular language should have the same answer with its correspondent DL query.
+\end{itemize}
+
+We defined the formal generic semantics of the \emph{RDF-CV} (see appendix of this paper)
+as we mapped constraint types to DL and as we described the intended \emph{CWA} and \emph{UNA} behavior of constraint types.
+In order to specify transformations between specific constraints,
+first we have to ensure identical semantics.
+Constraint languages assume identical semantics, 
+if for each constraint the following condition holds:
+If a given constraint is represented by two different languages, 
+the validation results must be exactly the same,
+i.e., whenever it is violated in one language it is also violated in the other language.
+In order to show that languages have the same semantics,
+we expressed constraint types in different languages.
 

### 2015-05-05 paper/paper 2/paper 2.tex
RDF-CV semantics

--- 2015-05-04 paper/paper 2/paper 2.tex
@@
 
-\subsection{Semantics for RDF Validation}
+\subsection{RDF Validation Semantics}
 
 %The underlying \emph{semantics} for RDF validation is \emph{UNA} and \emph{CWA}.
-RDF validation requires that different names represent different objects ({\em unique name assumption (UNA)}), whereas,
+RDF validation requires that different names represent different objects (\emph{\textbf{unique name assumption (UNA)}}), whereas,
 \emph{OWL 2} is based on the {\em non-unique name assumption (nUNA)}.  
@@
 In an \emph{OWA} setting, this axiom does not cause a constraint violation (even if there is no explicitly defined \emph{title}), since there must be a \emph{title} for this \emph{book} which we may not know.
-On the other hand, RDF validation scenarios require the {\em closed-world assumption (CWA)}, i.e., a statement is inferred to be false if it cannot be proved to be true.
+On the other hand, RDF validation scenarios require the \emph{\textbf{closed-world assumption (CWA)}}, i.e., a statement is inferred to be false if it cannot be proved to be true.
 When assuming the \emph{CWA}, a constraint violation is raised as there is no explicitly defined title. 
@@
 This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past. 
+In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (\emph{CWA} and \emph{UNA}) as for RDF validation in general. 
 %In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general. 
@@
 No.}
-\er{If a constraint is represented (recognized) by two different languages, that means, whenever it is violated in one language it is violated in other.
+
+%comments from Erman:
+
+%\begin{itemize}
+%\item If a constraint is represented (recognized) by two different languages, that means, whenever it is violated in one language it is violated in other.
 We have to provide formal generic semantics for it; formally prove those statements.}
+
+%\item This is simple. You write that:
+%In case we want to use OWL 2 as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general.
+%The question is how to adopt CWA for OWL2, because it wont behave CWA way, just because we want it.
+So I say, in order to show that it behaves exactly we want it to, we should show that for the cases that we express a constraint (that we speak) in a classical constraint language, say, Scheme (therefore CWA) and  also OWL,  whenever the constraint in Scheme is violated, it's OWL correspondence is also violated.
+That shows that they behave in the same way, as they should.
+
+%\item So if you read again my comment again, without knowing which semantics those constraint languages have, one actually does is to show, given an RDF-data it is violated in one language iff it is violated in other.
+And this actually corresponds to the very idea of transformation and generic semantics.
+
+%\item Now, what is a generic semantics? 
+%It is, the semantics we had in our mind, when typing this long document, that we tried to underpin by the DL language.
+However, regarding CWA and OWA, it is possible that we made some mistakes.
+In order to ensure that, say, if its DL, one needs to show that, a constraint/query written a particular language should have the same answer with its correspondent DL query.
+%\end{itemize}
+
+We defined the \textbf{formal generic semantics of the vocabulary} to describe constraints of any constraint type in a generic way (see paper appendix):
+(1) We mapped constraint types to \emph{DL} to logically underpin them and 
+(2) we described the constraint types' intended behavior in terms of validation results depending on \emph{CWA} and \emph{UNA}.
+To be able to define mappings between \emph{specific constraints} (expressed by different languages) and \emph{generic constraints},
+we show for each constraint type that a constraint expressed by a particular language leads to the same answer as the corresponding \emph{DL} query.
+To be able to specify transformations between \emph{specific constraints} (expressed by different languages),
+identical semantics of the languages with regard to the particular constraint type has to be ensured.
+%Constraint languages assume identical semantics, 
+%if for each constraint the following condition holds:
+If a constraint is represented by \emph{ShEx} and \emph{OWL 2}, 
+the validation results must be exactly the same, i.e.,
+whenever the \emph{specific constraint} \emph{$sc_{ShEx}$} is violated, its \emph{$sc_{OWL 2}$} correspondence is also violated which shows that they behave in the same way.
+We expressed constraint types by different languages
+to document identical semantics for these languages with regard to appropriate constraint types.
 

### 2015-05-05 paper/paper 2/paper 2.tex
RDF-CV semantics

@@
 When assuming \emph{UNA}, the functional property {\em title} (\ms{funct (title)}) causes a clash
-in case the book {\em Huckleberry-Finn} has more than one \emph{title}
-(\ms{title(Huckleberry-Finn, The-Adventures-of-Huckleberry-Finn)}, \ms{title(Huckleberry-Finn, Die-Abenteuer-des-Huckleberry-Finn)}).
-Assuming nUNA, however, reasoning concludes that the titles {\em The-Adventures-of-Huckleberry-Finn} and {\em Die-Abenteuer-des-Huckleberry-Finn} are the same (\ms{\{The-Adventures-of-Huckleberry-Finn\}} = \ms{\{Die-Abenteuer-des-Huckle} \ms{berry-}\ms{Finn\}}).
+in case the book {\em Huckleberry-Finn} has more than one \emph{title}.
+%(\ms{title(Huckleberry-Finn,} \ms{The-Adventures-of-Huckleberry-Finn)}, \ms{title} \ms{(Huckleberry-Finn,} \ms{Die-Abenteuer-des-Huckleberry-Finn)}).
+Assuming \emph{nUNA}, however, reasoning concludes that the titles {\em The-Adventures-of-Huckleberry-Finn} and {\em Die-Abenteuer-des-Huckleberry-Finn} are the same. 
+%(\ms{\{The-Adventures-of-Huckleberry-Finn\}} = \ms{\{Die-Abenteuer-des-Huckle} \ms{berry-}\ms{Finn\}}).
 

### 2015-05-06 paper/paper 2/paper 2.tex
THE ROLE OF REASONING FOR RDF VALIDATION

@@
 In 2013, the W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
-where experts from industry, government, and academia discussed first use cases for RDF constraint\footnote{For simplicity reasons, we use the terms \emph{constraint types/constraints} instead of \emph{RDF constraint types/RDF constraints} in the rest of the paper} formulation and RDF data validation.
+where experts from industry, government, and academia discussed first use cases for RDF constraint\footnote{For simplicity reasons, we use the terms \emph{constraint types/constraints} instead of \emph{RDF constraint types/RDF constraints} in the remainder of the paper} formulation and RDF data validation.
 In 2014, two working groups on RDF validation have been established to focus on RDF validation: 

### 2015-05-08 paper/paper 2/paper 2.tex
feedback Erman

@@
 We identified requirements to formulate constraints for  validating RDF data and mapped each requirement to a constraint type.
-The majority of these constraint types can be expressed in description logics providing which provides logical underpinning.
+The majority of these constraint types can be expressed in description logics which provides their logical underpinning.
 
@@
 
-We defined the \textbf{formal generic semantics of the vocabulary} to describe constraints of any constraint type in a generic way (see paper appendix):
-(1) We mapped constraint types to \emph{DL} to logically underpin them and 
-(2) we described the constraint types' intended behavior in terms of validation results depending on \emph{CWA} and \emph{UNA}.
-To be able to define mappings between \emph{specific constraints} (expressed by different languages) and \emph{generic constraints},
-we show for each constraint type that a constraint expressed by a particular language leads to the same answer as the corresponding \emph{DL} query.
-To be able to specify transformations between \emph{specific constraints} (expressed by different languages),
-identical semantics of the languages with regard to the particular constraint type has to be ensured.
-%Constraint languages assume identical semantics, 
-%if for each constraint the following condition holds:
-If a constraint is represented by \emph{ShEx} and \emph{OWL 2}, 
-the validation results must be exactly the same, i.e.,
-whenever the \emph{specific constraint} \emph{$sc_{ShEx}$} is violated, its \emph{$sc_{OWL 2}$} correspondence is also violated which shows that they behave in the same way.
+We describe the intended behavior for each constraint type in terms of validation results depending on \emph{CWA} and \emph{UNA}.
+If any two constraints are semantically the same (w.r.t. RDF semantics), they should detect the same set of violations regardless of concrete RDF data, 
+which means whenever the constraints are applied to any RDF data they point out the same violations or they have the same effect.
+To be able to define mappings between semantically equivalent \emph{specific constraints} (expressed by different languages) and 
+between \emph{specific constraints} and \emph{generic constraints},
+we show for each constraint type that their constraints lead to exactly the same violations which shows that they behave in the same way. 
 We expressed constraint types by different languages
 to document identical semantics for these languages with regard to appropriate constraint types.
+
+%We defined the \textbf{formal generic semantics of the vocabulary} to describe constraints of any constraint type in a generic way (see paper appendix):
+%(1) We mapped constraint types to \emph{DL} to logically underpin them and 
+%(2) we described the constraint types' intended behavior in terms of validation results depending on \emph{CWA} and \emph{UNA}.
+%To be able to define mappings between \emph{specific constraints} (expressed by different languages) and \emph{generic constraints},
+%we show for each constraint type that a constraint expressed by a particular language leads to the same answer as the corresponding \emph{DL} query.
+%To be able to specify transformations between \emph{specific constraints} (expressed by different languages),
+%identical semantics of the languages with regard to the particular constraint type has to be ensured.
+%%Constraint languages assume identical semantics, 
+%%if for each constraint the following condition holds:
+%If a constraint is represented by \emph{ShEx} and \emph{OWL 2}, 
+%the validation results must be exactly the same, i.e.,
+%whenever the \emph{specific constraint} \emph{$sc_{ShEx}$} is violated, its \emph{$sc_{OWL 2}$} correspondence is also violated which shows that they behave in the same way.
+%We expressed constraint types by different languages
+%to document identical semantics for these languages with regard to appropriate constraint types.
+
+%\textcolor{red}{feedback from Erman:}
+
+\tb{use NO bold}
+
+\tb{Frage an Kai: wann soll ich in kursiv hervorheben?}
+
+%\textcolor{red}{
+%-About the paragraph; it says we defined a formal generic semantics.
+Did we?
+(if you think so please defend) but i think its not true.
+A formal semantics, is where you talk about an interpretation e.g., like in DL, there the semantics/interpretation is a mathematical object (therefore formally defined).
+What i believe is that paper propose  rather a schema for transforming constraint languages to one another (in particular to assess them in the first paper), that a person who doesn't know one language can have operation power etc..
+.
+%}
+%
+%\textcolor{red}{
+%-so I think we should get rid of this paragraph either totally or partially and you talk about the formulation instead briefly one-two sentence.
+I know that you wrote this paragraph to make my points and thanks a lot for that, but they were general remarks, so we cannot point out something that we do not do at that point, if its not at the "future work" or smth.
+Also this underpininng and  so on, these things were in the other paper (arxiv).
+If it has a point, then better referencing it.
+%}
+
+%\textcolor{red}{
+%-please be careful with the narration:
+%To be able to define mappings between specific constraints (expressed by different languages) and generic constraints, we show for each constraint type that a constraint expressed by a particular language leads to the same answer as the corresponding DL query.
+%When you read it and next sentence, it does not flow.  I know that it is not easy to write it nicely. But it also has technical problems, like
+%}
+%
+%\textcolor{red}{
+%A constraint  that is expected to give the same answer with a query.
+Those things are not of the same type.
+When I have written this query/constraint analogy, it was rather to provide an intuition.
+If we gonna talk about constraints; a constraint written in different languages always have the same restriction on any possible rdf-data.
+This means, if any two constraints are semantically the same (w.r.t.
+RDF data semantics), they should detect the same set of violations regardless of RDF data (which means whenever you apply them to any rdf data they point out the same violations or they have the same effect).
+Using a query language for validation, is a related but another thing.
+You actually know what it is better than I do.
+%}
 

### 2015-05-08 paper/paper 2/paper 2.tex
feedback Erman

@@
 
-We describe the intended behavior for each constraint type in terms of validation results depending on \emph{CWA} and \emph{UNA}.
-If any two constraints are semantically the same (w.r.t. RDF semantics), they should detect the same set of violations regardless of concrete RDF data, 
-which means whenever the constraints are applied to any RDF data they point out the same violations or they have the same effect.
+We recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} (serving as appendix of this paper) in which
+we describe the intended behavior of each constraint type in terms of validation results depending on \emph{CWA} and \emph{UNA}.
+If any two constraints are semantically the same (w.r.t. RDF semantics), they should detect the same set of violations regardless of RDF data, 
+which means whenever the constraints are applied to any RDF data they point out the same violations.
 To be able to define mappings between semantically equivalent \emph{specific constraints} (expressed by different languages) and 

### 2015-05-08 paper/paper 2/paper 2.tex
feedback Erman

@@
 
-\emph{Cardinality restrictions} can be expressed either generically (\textbf{\emph{generic constraints}}) by \emph{description logics (DL)} 
+\emph{Cardinality restrictions} can be expressed either generically (\emph{generic constraints}) by \emph{description logics (DL)} 
 %and extensions  
-or specifically (\textbf{\emph{specific constraints}}) by domain-specific constraint languages such as \emph{OWL 2}, \emph{DSP}, \emph{ShEx}, \emph{ReSh}, and \emph{SPIN}.
+or specifically (\emph{specific constraints}) by domain-specific constraint languages such as \emph{OWL 2}, \emph{DSP}, \emph{ShEx}, \emph{ReSh}, and \emph{SPIN}.
 The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
@@
 %(2) RDF practitioners thinking of how to provide aligned implementations for the validation of both existing an newly developed constraint languages.
-The main \textbf{contributions} of this paper are:
+The main contributions of this paper are:
 (1) we provide a basic terminology and classification system for RDF constraints (section \ref{sec:vocabulary}),
@@
 %The underlying \emph{semantics} for RDF validation is \emph{UNA} and \emph{CWA}.
-RDF validation requires that different names represent different objects (\emph{\textbf{unique name assumption (UNA)}}), whereas,
+RDF validation requires that different names represent different objects (\emph{unique name assumption (UNA)}), whereas,
 \emph{OWL 2} is based on the {\em non-unique name assumption (nUNA)}.  
@@
 In an \emph{OWA} setting, this axiom does not cause a constraint violation (even if there is no explicitly defined \emph{title}), since there must be a \emph{title} for this \emph{book} which we may not know.
-On the other hand, RDF validation scenarios require the \emph{\textbf{closed-world assumption (CWA)}}, i.e., a statement is inferred to be false if it cannot be proved to be true.
+On the other hand, RDF validation scenarios require the \emph{closed-world assumption (CWA)}, i.e., a statement is inferred to be false if it cannot be proved to be true.
 When assuming the \emph{CWA}, a constraint violation is raised as there is no explicitly defined title. 
@@
 we show for each constraint type that their constraints lead to exactly the same violations which shows that they behave in the same way. 
-We expressed constraint types by different languages
+We express constraint types by different languages
 to document identical semantics for these languages with regard to appropriate constraint types.
@@
 
-A \textbf{\emph{constraint language}} is a language which is used to formulate constraints.
-The W3C Data Shapes working group defines \textbf{\emph{RDF constraint}} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
+A \emph{constraint language} is a language which is used to formulate constraints.
+The W3C Data Shapes working group defines \emph{RDF constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
 We identified four dimensions to classify constraint types:
 \begin{itemize}
-  \item \textbf{\emph{Universality:}} \emph{specific constraints} vs. \emph{generic constraints}
-	\item \textbf{\emph{Complexity:}} \emph{simple constraints} vs. \emph{complex constraints}
-	\item \textbf{\emph{Context:}} \emph{property constraints} vs. \emph{class constraints}
-	\item \textbf{\emph{DL Expressivity:}} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}
+  \item \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints}
+	\item \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints}
+	\item \emph{Context:} \emph{property constraints} vs. \emph{class constraints}
+	\item \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}
 \end{itemize}
@@
 As there are already five promising constraint languages and our purpose is not to put a new constraint language, we rather developed a very simple lightweight vocabulary (only three classes, three object properties, and three data properties) which is universal enough to describe constraints of any constraint type expressible by any constraint language (see the conceptual model in figure \ref{fig:RDF-CV-conceptual-model}).
-We call this vocabulary the \textbf{\emph{RDF Constraints Vocabulary (RDF-CV)}}\footnote{Available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.
+We call this vocabulary the \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.
 
@@
 
-Constraints can be expressed either generically (\textbf{\emph{generic constraints}}) by the \emph{RDF-CV}   
-or specifically (\textbf{\emph{specific constraints}}) by domain-specific constraint languages.
+Constraints can be expressed either generically (\emph{generic constraints}) by the \emph{RDF-CV}   
+or specifically (\emph{specific constraints}) by domain-specific constraint languages.
 As the \emph{RDF-CV} describes constraints generically, the vocabulary does not distinguish constraints according to the dimension \emph{universality}. 
@@
 In contrast, there are certain constraint types which cannot be expressed in \emph{DL}, but are also expressible by the \emph{RDF-CV} . 
-\textbf{\emph{Complex constraints}} encompass \textbf{\emph{simple constraints}} (atomic constraints) and/or further \emph{complex constraints},
+\emph{Complex constraints} encompass \emph{simple constraints} (atomic constraints) and/or further \emph{complex constraints},
 i.e. \emph{DL} statements representing \emph{complex constraints} are created out of \emph{DL} statements standing for atomic and composed constraints (if expressible in \emph{DL}). 
-Simple constraints may be applied to either properties (\textbf{\emph{property constraints}}) or classes (\textbf{\emph{class constraints}}).
+Simple constraints may be applied to either properties (\emph{property constraints}) or classes (\emph{class constraints}).
 The \emph{RDF-CV} does not contain any terms standing for \emph{simple} and \emph{complex constraints}, since \emph{context classes} of \emph{simple constraints} are just reused within \emph{complex constraints} (\emph{simple constraints} associated with \emph{context classes} must hold for individuals of these \emph{context classes}).
@@
 
-Sub-classes of \textbf{\emph{simple constraints}} are \textbf{\emph{property constraints}} and \textbf{\emph{class constraints}} (see the \emph{RDF-CV} implementation model in figure \ref{fig:RDF-CV-implementation-model}).
+Sub-classes of \emph{simple constraints} are \emph{property constraints} and \emph{class constraints} (see the \emph{RDF-CV} implementation model in figure \ref{fig:RDF-CV-implementation-model}). 
 For both \emph{property} and \emph{class constraints} a \emph{context class}, a list of \emph{classes}, the \emph{constraining element}, and the \emph{constraining value} can be stated. 
@@
 
-A \emph{simple constraint} holds for all individuals of a \textbf{\emph{context class}}.
+A \emph{simple constraint} holds for all individuals of a \emph{context class}.
 Consider, e.g., the following \emph{minimum qualified cardinality restriction} on the object property \emph{author}, which restricts \emph{publications} to have at least one \emph{author} which is a \emph{person}:
@@
 
-The \textbf{\emph{constraining element}} indicates the actual type of constraint like \emph{DL} concept and role constructors, (in)equality, and further keywords for constraint types which cannot be expressed in \emph{DL} (e.g.
+The \emph{constraining element} indicates the actual type of constraint like \emph{DL} concept and role constructors, (in)equality, and further keywords for constraint types which cannot be expressed in \emph{DL} (e.g.
 regular expressions and constraining facets).
-In some cases, a constraint is only complete when in addition to the \emph{constraining element} a \textbf{\emph{constraining value}} is stated.
+In some cases, a constraint is only complete when in addition to the \emph{constraining element} a \emph{constraining value} is stated.
 The cardinality restriction 
@@
 The \emph{constraining element} of this \emph{property constraint} is the \emph{DL} at-least restriction \emph{$\geq$} and the \emph{constraining value} is \emph{1}.
-\emph{Simple constraints} may refer to a list of \textbf{\emph{classes}}.
+\emph{Simple constraints} may refer to a list of \emph{classes}.
 The qualified cardinality restriction above, e.g., refers to the class \emph{Person}, 
@@
 
-For \emph{property constraints}, \textbf{\emph{left}} and \textbf{\emph{right property lists}} are specified.
+For \emph{property constraints}, \emph{left} and \emph{right property lists} are specified.
 The assignment of properties to these lists happens relative to the \emph{constraining element} - which may be an operator (e.g., $\sqsubseteq$ in case of \emph{object property paths}).
@@
 
-\textbf{\emph{Complex constraints}} are composed out of \emph{simple constraints} and/or \emph{complex constraints}.
+\emph{Complex constraints} are composed out of \emph{simple constraints} and/or \emph{complex constraints}.
 \emph{Exclusive or} is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).

### 2015-05-08 paper/paper 2/paper 2.tex
feedback Erman

@@
 This causes confusion and weakens the common understanding between several parties about the semantics of particular constraints. Also, it raises  questions on how to ensure high data quality. 
-Therefore, when choosing a constraint language, say \ms{$\alpha$}, to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a semantically equivalent constraint in another other constraint language \ms{$\beta$} (see section \ref{sec:transformations}).
+Therefore, when choosing a constraint language, say \ms{$\alpha$}, to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a semantically equivalent constraint in another other constraint language \ms{$\beta$} (see Section \ref{sec:transformations}).
 This is important in order to enhance the interoperability of constraint languages and to resolve misunderstandings and ambiguities in the communication of RDF data producers and consumers, 
@@
 to perform validation on semantically equivalent \emph{specific constraints}, expressed by different constraint languages 
-i.e., validation is independent from the used constraint language (see section \ref{sec:validation}). 
+i.e., validation is independent from the used constraint language (see Section \ref{sec:validation}). 
 %i.e., validation leads to identical validation results - independently from the used constraint language (see section \ref{sec:validation}).
@@
 The main contributions of this paper are:
-(1) we provide a basic terminology and classification system for RDF constraints (section \ref{sec:vocabulary}),
-(2) we developed a vocabulary to describe constraints of any RDF constraint type generically and specified its underlying semantics (section \ref{sec:vocabulary}),
-(3) we show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful (section \ref{sec:transformations}), and
-(4) we explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages (section \ref{sec:validation}).
+(1) we provide a basic terminology and classification system for RDF constraints (Section \ref{sec:vocabulary}),
+(2) we developed a vocabulary to describe constraints of any RDF constraint type generically and specified its underlying semantics (Section \ref{sec:vocabulary}),
+(3) we show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful (Section \ref{sec:transformations}), and
+(4) we explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages (Section \ref{sec:validation}).
 %(if the validation is implemented once for the corresponding \emph{generic constraint type} to which the \emph{specific constraint type} is mapped)
@@
 \end{DL}
-The cardinality restriction is a constraint on the property \emph{author} and is therefore classified as a \emph{property constraint} which holds for all individuals of the class \emph{Publication} (see table \ref{tab:property-constraint-cardinality-restriction} for the mapping to \emph{RDF-CV}):
+The cardinality restriction is a constraint on the property \emph{author} and is therefore classified as a \emph{property constraint} which holds for all individuals of the class \emph{Publication} (see Table \ref{tab:property-constraint-cardinality-restriction} for the mapping to \emph{RDF-CV}):
 
@@
 \end{DL}
-Thus, when mapped to the \emph{RDF-CV} (see table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are on the left side of the \emph{constraining element} \emph{$\sqsubseteq$},
+Thus, when mapped to the \emph{RDF-CV} (see Table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are on the left side of the \emph{constraining element} \emph{$\sqsubseteq$},
 and the property \emph{authorOfGenre} is on the right side:
@@
 %but not for the triples \ms{Picard commandsEnterprise Enterprise} and \ms{Enterprise registryNumber "NCC-1701-E"\textasciicircum{}\textasciicircum{}RegistryNumber}.
-In table \ref{tab:simple-constraint-not-expressible-in-dl)}, the \emph{simple constraint} (\emph{literal pattern matching}) and the \emph{complex constraint} (\emph{universal restriction}) are mapped to the \emph{RDF-CV}:
+In Table \ref{tab:simple-constraint-not-expressible-in-dl)}, the \emph{simple constraint} (\emph{literal pattern matching}) and the \emph{complex constraint} (\emph{universal restriction}) are mapped to the \emph{RDF-CV}:
 
@@
 %\end{DL}
-The \emph{complex constraint} is mapped to the \emph{RDF-CV} (see table \ref{tab:complex-constraints}) and expressed in \emph{DL} as follows:
+The \emph{complex constraint} is mapped to the \emph{RDF-CV} (see Table \ref{tab:complex-constraints}) and expressed in \emph{DL} as follows:
 
@@
 we propose using them as \emph{simple constraints} - in terms of syntactic sugar.
-As a consequence, the \emph{context-specific exclusive or of property groups} constraint above is represented as a \emph{generic constraint} more intuitively and concisely (see table \ref{tab:simplified-complex-constraints}).
+As a consequence, the \emph{context-specific exclusive or of property groups} constraint above is represented as a \emph{generic constraint} more intuitively and concisely (see Table \ref{tab:simplified-complex-constraints}).
 
@@
 
-Almost 15 percent of all constraint types are \emph{complex constraints} which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar (see section \ref{sec:evaluation}).
+Almost 15 percent of all constraint types are \emph{complex constraints} which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar (see Section \ref{sec:evaluation}).
 
@@
 \end{DL}
-When mapped to the \emph{RDF-CV} (see table \ref{tab:irreflexive-object-properties-as-complex-constraints}), the \emph{complex constraint} aggregates three \emph{simple constraints} (one \emph{property} and two \emph{class constraints}):
+When mapped to the \emph{RDF-CV} (see Table \ref{tab:irreflexive-object-properties-as-complex-constraints}), the \emph{complex constraint} aggregates three \emph{simple constraints} (one \emph{property} and two \emph{class constraints}):
 
@@
 When using the \emph{OWL RBox axiom} \emph{role irreflexivity} in terms of syntactic sugar, 
-the \emph{complex constraint} can be expressed more concisely in form of a \emph{simple property constraint} with exactly the same semantics (see table \ref{tab:irreflexive-object-properties-as-simple-constraints}):
+the \emph{complex constraint} can be expressed more concisely in form of a \emph{simple property constraint} with exactly the same semantics (see Table \ref{tab:irreflexive-object-properties-as-simple-constraints}):
 
@@
 For instance, \emph{Books} are uniquely identified by their \emph{ISBN} number, that is, the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}, 
-which can be represented by the \emph{RDF-CV} in form of a \emph{complex constraint} (see table \ref{tab:primary-key-properties-as-complex-constraints}):
+which can be represented by the \emph{RDF-CV} in form of a \emph{complex constraint} (see Table \ref{tab:primary-key-properties-as-complex-constraints}):
 
@@
 \emph{DL} is extended with \emph{key boxes} and a special construct \emph{keyfor} \cite{Lutz2005}.
-When using the \emph{keyfor} \emph{DL} construct (\ms{isbn keyfor Book}), the \emph{complex constraint} can be expressed by only one \emph{simple property constraint} (see table \ref{tab:primary-key-properties-as-simple-constraints} for the mapping to the \emph{RDF-CV}).
+When using the \emph{keyfor} \emph{DL} construct (\ms{isbn keyfor Book}), the \emph{complex constraint} can be expressed by only one \emph{simple property constraint} (see Table \ref{tab:primary-key-properties-as-simple-constraints} for the mapping to the \emph{RDF-CV}).
 
@@
 
-The \emph{DL} statement \ms{Publication $\equiv$ $\exists$ publisher.Publisher} is mapped to a \emph{(simple) generic constraint} conforming to the \emph{RDF-CV} (see table \ref{tab:existential-quantification-as-simple-constraints}).
+The \emph{DL} statement \ms{Publication $\equiv$ $\exists$ publisher.Publisher} is mapped to a \emph{(simple) generic constraint} conforming to the \emph{RDF-CV} (see Table \ref{tab:existential-quantification-as-simple-constraints}).
 Then, one mapping (\emph{$m_1(sc_{OWL 2})$}, \emph{$m_2(sc_{ReSh})$}, \emph{$m_3(sc_{ShEx})$}, ...) is defined for each \emph{specific constraint} (\emph{$sc_{OWL 2}$}, \emph{$sc_{ReSh}$}, \emph{$sc_{ShEx}$}, ...) to the corresponding \emph{generic constraint} (\emph{gc}).

### 2015-05-08 paper/paper 2/paper 2.tex
feedback Erman

@@
 that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
-This constraint can be represented generically (\emph{generic constraint}) in \emph{DL} (\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}), but also specifically (\emph{specific constraint}) by multiple constraint languages:
+This constraint can be represented generically (\emph{generic constraint}) in \emph{DL} {\small\ms{(Publication $\sqsubseteq$ $\geq$1 author.Person)}}, but also specifically (\emph{specific constraint}) by multiple constraint languages:
 
@@
 As every \emph{publication} must have at least one \emph{author} which must be a \emph{person}, 
-and since the book \emph{The-Lord-Of-The-Rings} is a \emph{publication} \\(\ms{rdf:type(The-Lord-Of-The-Rings, Publication)}), 
+and since the book \emph{The-Lord-Of-The-Rings} is a \emph{publication} {\small\ms{(rdf:type(The-Lord-Of-The-Rings, Publication)),}} 
 it must have at least one \emph{author} relationship to a \emph{person}.
@@
 it has an \emph{author} which is not a \emph{person} \\
-(\ms{author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Hobbit)}), 
+{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Hobbit)),}} 
 or (3) if it has an \emph{author} for which no class is assigned
-(\ms{author(The-Lord-Of-The-Rings, Tolkien)}).
+{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)).}}
 In contrast, \emph{The-Lord-Of-The-Rings} is a valid \emph{publication}, if it is connected to a \emph{person} via the property \emph{author}
-(\ms{author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Person)}).
+{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Person)).}}
 
@@
 A data property is \emph{functional} (\emph{R-65}) if for each individual \emph{x}, there can be at most one distinct literal \emph{y} such that \emph{x} is connected by the data property to \emph{y}.
-When assuming \emph{UNA}, the functional property {\em title} (\ms{funct (title)}) causes a clash
+When assuming \emph{UNA}, the functional property {\em title} {\small\ms{(funct (title))}} causes a clash
 in case the book {\em Huckleberry-Finn} has more than one \emph{title}.
@@
 %\tb{2. benefit: reasoning solves redundancy problem}
-As each \emph{book} must have a \emph{title} (\ms{Book $\sqsubseteq \exists$ title.$\top$}) and {\em Hamlet} is a \emph{book} (\ms{Book(Hamlet)}),
+As each \emph{book} must have a \emph{title} {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a \emph{book} {\small\ms{(Book(Hamlet)),}}
 {\em Hamlet} must have at least one \emph{title}.
@@
 The cardinality restriction 
-\ms{$\geq$1 author.Person}, e.g., 
+{\small\ms{$\geq$1 author.Person}}, e.g., 
 constructs an anonymous class of all individuals having at least one \emph{author} relationship to \emph{persons}.
@@
 then \emph{x} is also related to \emph{y} by a particular object property. 
-As \emph{Stephen-Hawking} is the \emph{author} of the book \emph{A-Brief-History-Of-Time} (\ms{authorOf(Stephen-Hawking, A-Brief-History-Of-Time)}) whose \emph{genre} is \emph{Popular-Science} ({\ms{genre(A-Brief-History-Of-Time, Popular-Science)}),
-the following \emph{object property path} infers that \emph{Stephen-Hawking} is an \emph{author} of the \emph{genre} \emph{Popular-Science} (\ms{authorOfGenre(Stephen-Hawking, Popular-Science)}):
+As \emph{Stephen-Hawking} is the \emph{author} of the book \emph{A-Brief-History-Of-Time} {\small\ms{(authorOf(Stephen-Hawking, A-Brief-History-Of-Time))}} whose \emph{genre} is \emph{Popular-Science} {\small\ms{(genre(A-Brief-History-Of-Time, Popular-Science)),}}
+the following \emph{object property path} infers that \emph{Stephen-Hawking} is an \emph{author} of the \emph{genre} \emph{Popular-Science} {\small\ms{(authorOfGenre(Stephen-Hawking, Popular-Science)):}}
 \begin{DL}
@@
 
-As the \emph{The-Great-Gatsby} is a \emph{publication} (\ms{rdf:type(The-Great-Gatsby, Publication)}) having an \emph{ISBN} number (\ms{isbn(The-Great-Gatsby, '978-0241965672')}) and a \emph{title} (\ms{title(The-Great-Gatsby, 'The Great Gatsby')}) and not an additional \emph{ISSN} identifier, the \emph{The-Great-Gatsby} is a valid \emph{publication}.
+As the \emph{The-Great-Gatsby} is a \emph{publication} {\small\ms{(rdf:type(The-Great-Gatsby, Publication))}} having an \emph{ISBN} number {\small\ms{(isbn(The-Great-Gatsby, '978-0241965672'))}} and a \emph{title} {\small\ms{(title(The-Great-Gatsby, 'The Great Gatsby'))}} and not an additional \emph{ISSN} identifier, the \emph{The-Great-Gatsby} is a valid \emph{publication}.
 %\begin{DL}
@@
 
-The \emph{DL} statement \ms{Publication $\equiv$ $\exists$ publisher.Publisher} is mapped to a \emph{(simple) generic constraint} conforming to the \emph{RDF-CV} (see Table \ref{tab:existential-quantification-as-simple-constraints}).
+The \emph{DL} statement {\small\ms{Publication $\equiv$ $\exists$ publisher.Publisher}} is mapped to a \emph{(simple) generic constraint} conforming to the \emph{RDF-CV} (see Table \ref{tab:existential-quantification-as-simple-constraints}).
 Then, one mapping (\emph{$m_1(sc_{OWL 2})$}, \emph{$m_2(sc_{ReSh})$}, \emph{$m_3(sc_{ShEx})$}, ...) is defined for each \emph{specific constraint} (\emph{$sc_{OWL 2}$}, \emph{$sc_{ReSh}$}, \emph{$sc_{ShEx}$}, ...) to the corresponding \emph{generic constraint} (\emph{gc}).

### 2015-05-08 paper/paper 2/paper 2.tex
3.3 complexity

@@
 
-As there is no do-it-all language meeting the majority of requirements to formulate constraints, and to validate RDF data,
-
+As there is no do-it-all language meeting the majority of requirements to formulate constraints and to validate RDF data,
 %which can be used to express constraints and to validate RDF data, 
@@
 language selection heavily depends on the individual use case.  
-Loosely speaking, there are more than 10 candidate languages with different syntaxes and semantics, and we will focus on five which, in our opinion, are the most promising languages on being the standard constraint languages.
+There are more than 10 candidate languages with different syntaxes and semantics, and we will focus on five which, in our opinion, are the most promising languages on being the standard constraint languages.
 Those are
@@
 %min car more powerful than req. propery
-The idea behind this paper is to achieve complete RDF validation requirements coverage by representing any constraint type (each of them corresponding to a requirement to formulate constraints and to validate RDF data) in a generic way using a lightweight vocabulary, say,  consisting of only a few terms (see section \ref{sec:vocabulary}).
+The idea behind this paper is to achieve complete RDF validation requirements coverage by representing any constraint type (each of them corresponding to a requirement to formulate constraints on and to validate RDF data) in a generic way using a lightweight vocabulary which consists of only a few terms (see Section \ref{sec:vocabulary}).
 
@@
 This causes confusion and weakens the common understanding between several parties about the semantics of particular constraints. Also, it raises  questions on how to ensure high data quality. 
-Therefore, when choosing a constraint language, say \ms{$\alpha$}, to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a semantically equivalent constraint in another other constraint language \ms{$\beta$} (see Section \ref{sec:transformations}).
+Therefore, when choosing a constraint language, say \ms{$\alpha$}, to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a semantically equivalent constraint expressed by another constraint language \ms{$\beta$} (see Section \ref{sec:transformations}).
 This is important in order to enhance the interoperability of constraint languages and to resolve misunderstandings and ambiguities in the communication of RDF data producers and consumers, 
@@
 
-We provide a validation environment \footnote{Available \url{http://purl.org/net/rdfval-demo}} which enables to validate RDF data according to constraints expressed by diverse  constraint languages.
+We provide a validation environment\footnote{Available \url{http://purl.org/net/rdfval-demo}} which enables to validate RDF data according to constraints expressed by diverse  constraint languages.
 As a second step, the \emph{RDF Validator} is extended by validating RDF data conforming to constraints of any constraint type represented by any constraint language,  
-to perform validation on semantically equivalent \emph{specific constraints}, expressed by different constraint languages 
+to perform validation on semantically equivalent \emph{specific constraints}, expressed by different constraint languages, 
 i.e., validation is independent from the used constraint language (see Section \ref{sec:validation}). 
@@
 
-\tb{use NO bold}
-
 \tb{Frage an Kai: wann soll ich in kursiv hervorheben?}

### 2015-05-13 paper/RDF validation requirements/RDF validation requirements.tex
disco validation rules
CWA UNA dependency

--- 2015-01-16 paper/RDF validation requirements/RDF validation requirements.tex
@@
 
+\newenvironment{evaluation-cwa-una-dependency}{
+  \scriptsize
+  \sffamily
+  \vspace{0cm}
+	\begin{center}
+  \begin{tabular}{l|c}
+  \hline
+  \textbf{Constraint Type} & \textbf{CWA/UNA Dependent} \\
+  \hline
+
+}{
+  \hline
+  \end{tabular}
+  \linebreak
+	\end{center}
+}
+
+\newenvironment{cwa-una-dependency}{
+  \scriptsize
+  \sffamily
+  \vspace{0cm}
+	\begin{center}
+  \begin{tabular}{l|c|c}
+  \hline
+  \textbf{Constraint Type} & \textbf{CWA/UNA Dependent} & \textbf{CWA/UNA Dependent} \\
+  \hline
+
+}{
+  \hline
+  \end{tabular}
+  \linebreak
+	\end{center}
+}
+
 \usepackage{xspace}
@@
 \newcommand{\er}[1]{\todo[size=\small, color=red!40]{\textbf{Erman:} #1}}
+
+% tables
+\usepackage{array,graphicx}
+\usepackage{booktabs}
+\usepackage{pifont}
+\newcommand*\rot{\rotatebox{90}}
+\newcommand*\OK{\ding{51}}
+\usepackage{booktabs}
+\newcommand*\ON[0]{$\surd$}
+
+\usepackage{tablefootnote}
+
+\usepackage{float}
 
@@
 
-\section{Existential Quantification on Properties}
+\section{Existential Quantifications}
 
@@
 
-\section{Universal Quantification on Properties}
+\section{Universal Quantifications}
 
@@
 
-\section{Property Domain}
+\section{Property Domains}
 
@@
 
-\section{Property Range}
+\section{Property Ranges}
 
@@
 
-\section{Minimum Unqualified Cardinality Restrictions on Properties}
+\section{Minimum Unqualified Cardinality Restrictions}
 
@@
 
-\section{Minimum Qualified Cardinality Restrictions on Properties}
+\section{Minimum Qualified Cardinality Restrictions}
 
@@
 
-\section{Maximum Unqualified Cardinality Restrictions on Properties}
+\section{Maximum Unqualified Cardinality Restrictions}
 
@@
 
-\section{Maximum Qualified Cardinality Restrictions on Properties}
+\section{Maximum Qualified Cardinality Restrictions}
 
@@
 
-\section{Exact Unqualified Cardinality Restrictions on Properties}
+\section{Exact Unqualified Cardinality Restrictions}
 
@@
 
-\section{Exact Qualified Cardinality Restrictions on Properties}
+\section{Exact Qualified Cardinality Restrictions}
 
@@
 A resource cannot be its own child (dbo:child).
+
+\subsection{Class-Specific Irreflexive Object Properties*}
+
+A property is \emph{irreflexive} if it is never locally reflexive \cite{Kroetzsch2012}.
+An object property irreflexivity axiom states that the object property \emph{OP} is irreflexive - that is, no individual is connected by \emph{OP} to itself.
+\emph{Class-Specific Irreflexive Object Properties} are object properties which are irreflexive within a given context, e.g. a class.
 
@@
 
-\section{Define Order}
+\section{Ordering}
 
@@
 
-\section{Default Values}
+\section{Default Values*}
 
@@
 
-\section{Exploiting Class/Property Specialization Ontology Axioms}
+\section{Use Sub-Super Relations in Validation}
 
@@
 \end{gcotable}
+
+\section{Provenance}
+
+\section{Data Model Consistency}
+
+Is the data consistent with the intended semantics of the data model?
+Such validation rules ensure the integrity of the data according to the data model.
+
+\section{Structure}
+
+SKOS is based on RDF, which is a graph-based data model.
+Therefore we can concentrate on the vocabulary's graph-based structure for assessing the quality of SKOS vocabularies and apply graph- and network-analysis techniques.
+
+\section{Labeling and Documentation}
+
+\section{Vocabulary}
+Vocabularies should not invent any new terms or use deprecated elements.
+
+\section{HTTP URI Scheme Violation}
 
@@
 Context-Specific Valid Properties & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
-Default Values & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ & \ding{55} & $\checkmark$ \\
+Default Values* & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ & \ding{55} & $\checkmark$ \\
 Mathematical Operations & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
@@
 Context-Specific Valid Properties & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
-Default Values & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
+Default Values* & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
 Mathematical Operations & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
@@
 The majority - nearly 70\% - of the overall constraints are expressible in DL.
+
+\subsection{CWA and UNA Dependency}
+
+\begin{itemize}
+	\item Dependent on the \emph{CWA}: do further triples change the validation result?
+	\item Dependent on the \emph{UNA}: Do validation results changes in case two resources are the same?
+\end{itemize}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcc@{}}
+           & \multicolumn{2}{c}{\textbf{Dependency}}
+    \\  \cmidrule{2-3}
+    \\       \textbf{Constraint Types}
+           & \rot{\emph{CWA}}
+           & \rot{\emph{UNA}}
+    \\ \midrule
+		*Subsumption & $\checkmark$ & $\checkmark$ \\
+		*Class Equivalence & $\checkmark$ & $\checkmark$ \\
+		*Sub Properties & $\checkmark$  & $\checkmark$ \\
+		*Property Domain & $\checkmark$ & $\checkmark$ \\
+		*Property Range & $\checkmark$ & $\checkmark$ \\
+		*Inverse Object Properties & $\checkmark$ & $\checkmark$ \\
+		*Symmetric Object Properties & $\checkmark$ & $\checkmark$ \\
+		*Asymmetric Object Properties & \ding{55} & \ding{55} \\
+		*Reflexive Object Properties & $\checkmark$ & $\checkmark$ \\
+		*Irreflexive Object Properties & \ding{55} & \ding{55} \\
+		Disjoint Properties & \ding{55} & \ding{55} \\
+		Disjoint Classes & \ding{55} & \ding{55} \\
+		Context-Sp. Property Groups & $\checkmark$ & $\checkmark$ \\
+		Context-Sp. Inclusive OR of P. & $\checkmark$ & $\checkmark$ \\
+		Context-Sp. Inclusive OR of P. Groups & $\checkmark$ & $\checkmark$ \\
+		Recursive Queries & \ding{55} & \ding{55} \\
+		Individual Inequality & \ding{55} & \ding{55} \\
+		*Equivalent Properties & $\checkmark$ & $\checkmark$ \\
+		Property Assertions & $\checkmark$ & $\checkmark$ \\
+		Data Property Facets & \ding{55} & \ding{55} \\
+		Literal Pattern Matching & \ding{55} & \ding{55} \\
+		Negative Literal Pattern Matching & \ding{55} & \ding{55} \\
+		*Object Property Paths & $\checkmark$ & $\checkmark$ \\
+		*Intersection & $\checkmark$ & $\checkmark$ \\
+		*Disjunction & $\checkmark$ & $\checkmark$ \\
+		*Negation & \ding{55} & $\checkmark$ \\
+		*Existential Quantification & $\checkmark$ & \ding{55} \\
+		*Universal Quantification & \ding{55} & $\checkmark$ \\
+		*Minimum Unqualified Cardinality & $\checkmark$ & $\checkmark$ \\
+		*Minimum Qualified Cardinality & $\checkmark$ & $\checkmark$ \\
+		*Maximum Unqualified Cardinality & \ding{55} & $\checkmark$ \\
+		*Maximum Qualified Cardinality & \ding{55} & $\checkmark$ \\
+		*Exact Unqualified Cardinality & $\checkmark$ & $\checkmark$ \\
+		*Exact Qualified Cardinality & $\checkmark$ & $\checkmark$ \\
+		*Transitive Object Properties & $\checkmark$ & $\checkmark$ \\
+		Context-Sp. Exclusive OR of P. & \ding{55} & \ding{55} \\
+		Context-Sp. Exclusive OR of P. Groups & \ding{55} & \ding{55} \\	
+		Allowed Values & \ding{55} & \ding{55} \\
+		Not Allowed Values & \ding{55} & \ding{55} \\
+		Literal Ranges & \ding{55} & \ding{55} \\
+		Negative Literal Ranges & \ding{55} & \ding{55} \\
+		Required Properties & $\checkmark$ & $\checkmark$ \\
+		Optional Properties & \ding{55} & \ding{55} \\
+		Repeatable Properties & $\checkmark$ & \ding{55} \\
+		Negative Property Constraints & \ding{55} & $\checkmark$ \\
+		*Individual Equality & $\checkmark$ & \ding{55} \\
+		*Functional Properties & $\checkmark$ & $\checkmark$ \\
+		*Inverse-Functional Properties & $\checkmark$ & $\checkmark$ \\
+		*Value Restrictions & $\checkmark$ & $\checkmark$ \\
+		*Self Restrictions & $\checkmark$ & $\checkmark$ \\
+    \bottomrule
+    \end{tabular}
+		\label{tab:evaluation-cwa-una-dependency-1}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{@{}lcc@{}}
+           & \multicolumn{2}{c}{\textbf{Dependency}}
+    \\  \cmidrule{2-3}
+    \\       \textbf{Constraint Types}
+           & \rot{\emph{CWA}}
+           & \rot{\emph{UNA}}
+    \\ \midrule
+		Primary Key Properties & $\checkmark$ & $\checkmark$ \\
+		*Class-Specific Property Range & $\checkmark$ & \ding{55} \\
+		*Class-Sp. Reflexive Object P. & $\checkmark$ & $\checkmark$ \\
+		Membership in Controlled Vocabularies & $\checkmark$ & $\checkmark$ \\
+		IRI Pattern Matching & \ding{55} & \ding{55} \\
+		Literal Value Comparison & \ding{55} & \ding{55} \\
+		Define Order & $\checkmark$ & $\checkmark$ \\
+		Validation Levels & $\checkmark$ & $\checkmark$ \\
+		String Operations & \ding{55} & \ding{55} \\
+		Context-Specific Valid Classes & \ding{55} & $\checkmark$ \\
+		Context-Specific Valid Properties & \ding{55} & $\checkmark$ \\
+		Default Values* & $\checkmark$ & $\checkmark$ \\
+		Mathematical Operations & \ding{55} & \ding{55} \\
+		Language Tag Matching & $\checkmark$ & $\checkmark$ \\
+		Language Tag Cardinality & $\checkmark$ & $\checkmark$ \\
+		Whitespace Handling & \ding{55} & \ding{55} \\
+		HTML Handling & \ding{55} & \ding{55} \\
+		Conditional Properties & $\checkmark$ & $\checkmark$ \\
+		Recommended Properties & $\checkmark$ & $\checkmark$ \\
+		Handle RDF Collections & \ding{55} & \ding{55} \\
+		Value is Valid for Datatype & \ding{55} & \ding{55} \\
+		*Exploiting Class/Property Specialization Ontology Axioms & \ding{55} & $\checkmark$ \\
+		*Cardinality Shortcuts & $\checkmark$ & $\checkmark$ \\ 
+		Aggregations & \ding{55} & \ding{55} \\
+
+		Class-Specific Irreflexive Object Properties* & \ding{55} & $\checkmark$ \\
+		Provenance & $\checkmark$ & $\checkmark$ \\ 
+		Data Model Consistency & $\checkmark$ & $\checkmark$ \\ 
+		Structure & $\checkmark$ & $\checkmark$ \\  
+		Labeling and Documentation & $\checkmark$ & $\checkmark$ \\ 
+		Vocabulary & $\checkmark$ & \ding{55} \\
+		HTTP URI Scheme Violation & \ding{55} & \ding{55} \\
+    \bottomrule
+    \end{tabular}
+		\label{tab:evaluation-cwa-una-dependency-2}
+    \end{center}
+\end{table}
+
+%\subsection{Evaluation of CWA/UNA Dependency}
+%
+%
+%
+%\begin{evaluation-cwa-una-dependency}
+%*Subsumption & $\checkmark$ \\
+%*Class Equivalence & \ding{55} \\
+%*Sub Properties & $\checkmark$ \\
+%*Property Domain & $\checkmark$ \\ 
+%*Property Range & $\checkmark$ \\ 
+%*Inverse Object Properties & $\checkmark$ \\ 
+%*Symmetric Object Properties & $\checkmark$ \\ 
+%*Asymmetric Object Properties & $\checkmark$ \\ 
+%*Reflexive Object Properties & $\checkmark$ \\ 
+%*Irreflexive Object Properties & $\checkmark$ \\
+%Disjoint Properties & \ding{55} \\ 
+%Disjoint Classes & \ding{55} \\
+%Context-Sp. Property Groups & \ding{55} \\ 
+%Context-Sp. Inclusive OR of P. & \ding{55} \\
+%Context-Sp. Inclusive OR of P. Groups & \ding{55} \\ 
+%Recursive Queries & \ding{55} \\ 
+%Individual Inequality & $\checkmark$ \\ 
+%*Equivalent Properties & \ding{55} \\ 
+%Property Assertions & \ding{55} \\ 
+%Data Property Facets & \ding{55} \\ 
+%Literal Pattern Matching & \ding{55} \\ 
+%Negative Literal Pattern Matching & \ding{55} \\ 
+%*Object Property Paths & $\checkmark$ \\ 
+%*Intersection & $\checkmark$ \\ 
+%*Disjunction & $\checkmark$ \\ 
+%*Negation & $\checkmark$ \\ 
+%*Existential Quantification & $\checkmark$ \\ 
+%*Universal Quantification & $\checkmark$ \\ 
+%*Minimum Unqualified Cardinality & $\checkmark$ \\ 
+%*Minimum Qualified Cardinality & $\checkmark$ \\ 
+%*Maximum Unqualified Cardinality & $\checkmark$ \\ 
+%*Maximum Qualified Cardinality & $\checkmark$ \\ 
+%*Exact Unqualified Cardinality & $\checkmark$ \\ 
+%*Exact Qualified Cardinality & $\checkmark$ \\ 
+%*Transitive Object Properties & $\checkmark$ \\ 
+%Context-Sp. Exclusive OR of P. & $\checkmark$ \\ 
+%Context-Sp. Exclusive OR of P. Groups & $\checkmark$ \\
+%Allowed Values & $\checkmark$ \\ 
+%Not Allowed Values & $\checkmark$ \\ 
+%Literal Ranges & \ding{55} \\ 
+%Negative Literal Ranges & \ding{55} \\ 
+%Required Properties & $\checkmark$ \\ 
+%Optional Properties & \ding{55} \\
+%Repeatable Properties & $\checkmark$ \\ 
+%Negative Property Constraints & $\checkmark$ \\ 
+%*Individual Equality & $\checkmark$ \\ 
+%*Functional Properties & $\checkmark$ \\
+%*Inverse-Functional Properties & $\checkmark$ \\ 
+%*Value Restrictions & $\checkmark$ \\
+%*Self Restrictions & $\checkmark$ \\
+%Primary Key Properties & $\checkmark$ \\ 
+%*Class-Specific Property Range & $\checkmark$ \\ 
+%*Class-Sp. Reflexive Object P. & $\checkmark$ \\ 
+%Membership in Controlled Vocabularies & $\checkmark$ \\ 
+%IRI Pattern Matching & \ding{55} \\ 
+%Literal Value Comparison & \ding{55} \\ 
+%Define Order & \ding{55} \\ 
+%Validation Levels & \ding{55} \\ 
+%String Operations & \ding{55} \\ 
+%\end{evaluation-cwa-una-dependency}
+%
+%\begin{evaluation-cwa-una-dependency}
+%Context-Specific Valid Classes & \ding{55} \\
+%Context-Specific Valid Properties & \ding{55} \\ 
+%Default Values & \ding{55} \\ 
+%Mathematical Operations & \ding{55} \\ 
+%Language Tag Matching & \ding{55} \\ 
+%Language Tag Cardinality & $\checkmark$ \\ 
+%Whitespace Handling & \ding{55} \\ 
+%HTML Handling & \ding{55} \\ 
+%Conditional Properties & $\checkmark$ \\ 
+%Recommended Properties & \ding{55} \\ 
+%Handle RDF Collections & \ding{55} \\ 
+%Value is Valid for Datatype & \ding{55} \\ 
+%*Exploiting Class/Property Specialization Ontology Axioms & \ding{55} \\ 
+%*Cardinality Shortcuts & $\checkmark$ \\ 
+%Aggregations & \ding{55} \\ 
+%\end{evaluation-cwa-una-dependency}
+
+% -----
 

### 2015-05-15 paper/RDF validation requirements/RDF validation requirements.tex
evaluation

@@
 
-\subsection{Class-Specific Irreflexive Object Properties*}
+\subsection{Class-Specific Irreflexive Object Properties}
 
@@
 
-\ms{Define Order} corresponds to the requirements
+\ms{Ordering} corresponds to the requirements
 \ms{R-121-SPECIFY-ORDER-OF-RDF-} \ms{RESOURCES} and
@@
 
-\section{Default Values*}
+\section{Default Values}
 
@@
 *Sub Properties & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
-*Property Domain & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
-*Property Range & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
+*Property Domains & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
+*Property Ranges & \ding{55} & $\checkmark$ & $\checkmark$ & \ding{55} & \ding{55} & $\checkmark$ \\
 *Inverse Object Properties & \ding{55} & $\checkmark$ & $\checkmark$ & $\sim$ & \ding{55} & $\checkmark$ \\
@@
 *Negation & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
-*Existential Quantification & \ding{55} & $\checkmark$ & \ding{55} & $\sim$ & $\sim$ & $\checkmark$ \\
-*Universal Quantification & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+*Existential Quantifications & \ding{55} & $\checkmark$ & \ding{55} & $\sim$ & $\sim$ & $\checkmark$ \\
+*Universal Quantifications & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
 *Minimum Unqualified Cardinality & $\checkmark$ & $\checkmark$ & \ding{55} & $\sim$ & $\checkmark$ & $\checkmark$ \\
@@
 *Self Restrictions & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
-Primary Key Properties & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+*Primary Key Properties & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
 *Class-Specific Property Range & $\checkmark$ & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
@@
 Literal Value Comparison & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ & $\checkmark$ \\
-Define Order & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+Ordering & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
 Validation Levels & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
@@
 Context-Specific Valid Properties & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
-Default Values* & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ & \ding{55} & $\checkmark$ \\
+*Default Values & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ & \ding{55} & $\checkmark$ \\
 Mathematical Operations & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
@@
 Value is Valid for Datatype & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
-Exploiting Class/Property Specialization Ontology Axioms & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+Use Sub-Super Relations in Validation & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
 *Cardinality Shortcuts & \ding{55} & $\checkmark$ & \ding{55} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
 Aggregations & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+
+*Class-Specific Irreflexive Object Properties & \ding{55} & $\checkmark$ & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+Provenance & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+Data Model Consistency & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+Structure & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\  
+Labeling and Documentation & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+Vocabulary & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
+HTTP URI Scheme Violation & \ding{55} & \ding{55} & \ding{55} & \ding{55} & \ding{55} & $\checkmark$ \\
 \end{evaluation-overall}
@@
 *Sub Properties & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
-*Property Domain & $\checkmark$ & $\sim$ & $\checkmark$ \\ 
-*Property Range & $\checkmark$ & $\sim$ & $\checkmark$ \\ 
+*Property Domains & $\checkmark$ & $\sim$ & $\checkmark$ \\ 
+*Property Ranges & $\checkmark$ & $\sim$ & $\checkmark$ \\ 
 *Inverse Object Properties & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
@@
 *Negation & \ding{55} & $\checkmark$ & $\checkmark$ \\ 
-*Existential Quantification & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
-*Universal Quantification & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
+*Existential Quantifications & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
+*Universal Quantifications & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
 *Minimum Unqualified Cardinality & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
@@
 *Self Restrictions & $\sim$ & \ding{55} & $\checkmark$ \\
-Primary Key Properties & $\checkmark$ & $\sim$ & $\checkmark$ \\ 
+*Primary Key Properties & $\checkmark$ & $\sim$ & $\checkmark$ \\ 
 *Class-Specific Property Range & $\checkmark$ & $\sim$ & $\checkmark$ \\ 
@@
 Literal Value Comparison & $\checkmark$ & $\checkmark$ & \ding{55} \\   
-Define Order & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
+Ordering & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
 Validation Levels & $\sim$ & $\checkmark$ & \ding{55} \\
@@
 Context-Specific Valid Properties & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
-Default Values* & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
+*Default Values & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
 Mathematical Operations & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
@@
 Value is Valid for Datatype & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
-*Exploiting Class/Property Specialization Ontology Axioms & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
+Use Sub-Super Relations in Validation & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
 *Cardinality Shortcuts & $\checkmark$ & $\checkmark$ & $\checkmark$ \\  
 Aggregations & $\checkmark$ & $\checkmark$ & \ding{55} \\ 
+*Class-Specific Irreflexive Object Properties & & & \\
+Provenance & & & \\
+Data Model Consistency & & & \\
+Structure & & & \\  
+Labeling and Documentation & & & \\
+Vocabulary & & & \\
+HTTP URI Scheme Violation & & & \\
 \end{evaluation-generic}
@@
 		*Sub Properties & $\checkmark$  & $\checkmark$ \\
-		*Property Domain & $\checkmark$ & $\checkmark$ \\
-		*Property Range & $\checkmark$ & $\checkmark$ \\
+		*Property Domains & $\checkmark$ & $\checkmark$ \\
+		*Property Ranges & $\checkmark$ & $\checkmark$ \\
 		*Inverse Object Properties & $\checkmark$ & $\checkmark$ \\
@@
 		Disjoint Properties & \ding{55} & \ding{55} \\
-		Disjoint Classes & \ding{55} & \ding{55} \\
+		Disjoint Classes & \ding{55} & $\checkmark$ \\
 		Context-Sp. Property Groups & $\checkmark$ & $\checkmark$ \\
@@
 		*Disjunction & $\checkmark$ & $\checkmark$ \\
-		*Negation & \ding{55} & $\checkmark$ \\
-		*Existential Quantification & $\checkmark$ & \ding{55} \\
-		*Universal Quantification & \ding{55} & $\checkmark$ \\
+		*Negation & \ding{55} & \ding{55} \\
+		*Existential Quantifications & $\checkmark$ & $\checkmark$ \\
+		*Universal Quantifications & \ding{55} & $\checkmark$ \\
 		*Minimum Unqualified Cardinality & $\checkmark$ & $\checkmark$ \\
@@
 		*Transitive Object Properties & $\checkmark$ & $\checkmark$ \\
-		Context-Sp. Exclusive OR of P. & \ding{55} & \ding{55} \\
-		Context-Sp. Exclusive OR of P. Groups & \ding{55} & \ding{55} \\	
-		Allowed Values & \ding{55} & \ding{55} \\
-		Not Allowed Values & \ding{55} & \ding{55} \\
+		Context-Sp. Exclusive OR of P. & \ding{55} & $\checkmark$ \\
+		Context-Sp. Exclusive OR of P. Groups & \ding{55} & $\checkmark$ \\	
+		Allowed Values & \ding{55} & $\checkmark$ \\
+		Not Allowed Values & \ding{55} & $\checkmark$ \\
 		Literal Ranges & \ding{55} & \ding{55} \\
@@
     \\ \midrule
-		Primary Key Properties & $\checkmark$ & $\checkmark$ \\
-		*Class-Specific Property Range & $\checkmark$ & \ding{55} \\
+		*Primary Key Properties & $\checkmark$ & $\checkmark$ \\
+		*Class-Specific Property Range & $\checkmark$ & $\checkmark$ \\
 		*Class-Sp. Reflexive Object P. & $\checkmark$ & $\checkmark$ \\
 		Membership in Controlled Vocabularies & $\checkmark$ & $\checkmark$ \\
-		IRI Pattern Matching & \ding{55} & \ding{55} \\
+		IRI Pattern Matching & \ding{55} & $\checkmark$ \\
 		Literal Value Comparison & \ding{55} & \ding{55} \\
-		Define Order & $\checkmark$ & $\checkmark$ \\
-		Validation Levels & $\checkmark$ & $\checkmark$ \\
+		Ordering & $\checkmark$ & \ding{55} \\
+		Validation Levels & $\checkmark$ & \ding{55} \\
 		String Operations & \ding{55} & \ding{55} \\
-		Context-Specific Valid Classes & \ding{55} & $\checkmark$ \\
-		Context-Specific Valid Properties & \ding{55} & $\checkmark$ \\
-		Default Values* & $\checkmark$ & $\checkmark$ \\
+		Context-Specific Valid Classes & \ding{55} & \ding{55} \\
+		Context-Specific Valid Properties & \ding{55} & \ding{55} \\
+		*Default Values & $\checkmark$ & $\checkmark$ \\
 		Mathematical Operations & \ding{55} & \ding{55} \\
-		Language Tag Matching & $\checkmark$ & $\checkmark$ \\
+		Language Tag Matching & $\checkmark$ & \ding{55} \\
 		Language Tag Cardinality & $\checkmark$ & $\checkmark$ \\
@@
 		Value is Valid for Datatype & \ding{55} & \ding{55} \\
-		*Exploiting Class/Property Specialization Ontology Axioms & \ding{55} & $\checkmark$ \\
+		Use Sub-Super Relations in Validation & \ding{55} & $\checkmark$ \\
 		*Cardinality Shortcuts & $\checkmark$ & $\checkmark$ \\ 
 		Aggregations & \ding{55} & \ding{55} \\
-
-		Class-Specific Irreflexive Object Properties* & \ding{55} & $\checkmark$ \\
+		*Class-Specific Irreflexive Object Properties & \ding{55} & $\checkmark$ \\
 		Provenance & $\checkmark$ & $\checkmark$ \\ 
@@
 		Labeling and Documentation & $\checkmark$ & $\checkmark$ \\ 
-		Vocabulary & $\checkmark$ & \ding{55} \\
-		HTTP URI Scheme Violation & \ding{55} & \ding{55} \\
+		Vocabulary & $\checkmark$ & $\checkmark$ \\
+		HTTP URI Scheme Violation & \ding{55} & $\checkmark$ \\
     \bottomrule

### 2015-05-23 paper/paper 2/dc-2015.tex
DC 2015

--- 2015-05-08 paper/paper 2/paper 2.tex
@@
 %
-\documentclass{llncs}
-
-% allows for temporary adjustment of side margins
-\usepackage{chngpage}
-
-% just makes the table prettier (see \toprule, \bottomrule, etc. commands below)
-\usepackage{booktabs}
+\documentclass[a4paper,fontsize=11pt]{scrartcl}
+
+% Anpassungen an DC Template
+\usepackage[a4paper, left=2.9cm,right=2.87cm,bottom=3cm,top=3cm,headsep=1.27cm]{geometry}
+\setlength{\parskip}{0.5em}
+\renewcommand{\tablename}{TABLE} 
+\renewcommand{\figurename}{FIG} 
+\usepackage{titlesec}
+\titlespacing\section{0pt}{12pt plus 2pt minus 2pt}{6pt plus 1pt minus 1pt}
+\titlespacing\subsection{0pt}{12pt plus 2pt minus 2pt}{3pt plus 1pt minus 1pt}
+\addtokomafont{title}{\fontsize{14pt}{1em}\selectfont}
+\setkomafont{section}{\fontsize{12pt}{0pt}\selectfont}
+\addtokomafont{subsection}{\fontsize{11pt}{0pt}\selectfont}
+\addtokomafont{author}{\fontsize{12pt}{1em}\selectfont}
+\usepackage{scrpage2}
+\clearscrheadfoot
+\pagestyle{scrheadings}
+\renewcommand*{\titlepagestyle}{scrheadings}
+\chead{\fontsize{11pt}{0pt}\selectfont Proc. Int'l Conf. on Dublin Core and Metadata Applications 2015}
+\usepackage{apacite}
+
+\date{}
 
@@
 
-% footnotes
-\usepackage{scrextend}
-
 % Todos
-%\usepackage[colorinlistoftodos]{todonotes}
-%\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
-%\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}
-
-%\usepackage{makeidx}  % allows for indexgeneration
-
-%\usepackage{amsmath}
-\usepackage{amsmath, amssymb}
-\usepackage{mathabx}
+\usepackage[colorinlistoftodos]{todonotes}
+\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
+\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}
+
+% \usepackage{makeidx}  % allows for indexgeneration -- yes, but we don't need this
+
+\usepackage{amsmath}
 
@@
 \newcommand{\ms}[1]{\texttt{#1}}
-
-%\usepackage{listings}% http://ctan.org/pkg/listings
-%\lstset{
-  %numbers=left,numbersep=2mm,frame=single,mathescape,fontsize=\scriptsize
-%}
 
@@
 
-\newenvironment{gcotable-1}{
-  \scriptsize
-  \sffamily
-  \vspace{0cm}
-  \begin{tabular}{l|l|l|l|l|l}
-  \hline
-  \textbf{c. type} & \textbf{context concept} & \textbf{p. list} & \textbf{concepts} & \textbf{c. element} & \textbf{c. value} \\
-  \hline
-
-}{
-  \hline
-  \end{tabular}
-}
-
-\newenvironment{gcotable}{
-  \scriptsize
-  \sffamily
-  \vspace{0cm}
-	\begin{center}
-  \begin{tabular}{l|l|l|l|l|l|l}
-  \hline
-  \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
-  \hline
-
-}{
-  \hline
-  \end{tabular}
-	\end{center}
-}
+\usepackage{xspace}
+% Einfache und doppelte Anfuehrungszeichen
+\newcommand{\qs}{``} 
+\newcommand{\qe}{''\xspace} 
+\newcommand{\sqs}{`} 
+\newcommand{\sqe}{'\xspace}
+
+% checkmark
+\usepackage{tikz}
+\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
+
+% Xs
+\usepackage{pifont}
+
+% Tabellenabstände kleiner
+\setlength{\intextsep}{10pt} % Vertical space above & below [h] floats
+\setlength{\textfloatsep}{10pt} % Vertical space below (above) [t] ([b]) floats
+% \setlength{\abovecaptionskip}{0pt}
+% \setlength{\belowcaptionskip}{0pt}
+
+\usepackage{tabularx}
+\newcommand{\hr}{\hline\noalign{\smallskip}} % für die horizontalen linien in tabellen
 
@@
 
-\newenvironment{evaluation}{
-  %\scriptsize
-  %\sffamily
-  \vspace{0cm}
-	\begin{center}
-  \begin{tabular}{l|c|c|c|c|c|c}
-  \hline
-  \textbf{Constraint Class} & \textbf{DSP} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
-  \hline
-
-}{
-  \hline
-  \end{tabular}
-	\end{center}
-}
-
-\newenvironment{evaluation-generic-overview}{
-  %\scriptsize
-  %\sffamily
-  \vspace{0cm}
-	\begin{center}
-  \begin{tabular}{l|c|c}
-  \hline
-  \textbf{Constraint Classes} & \textbf{\#} & \textbf{\%} \\
-  \hline
-
-}{
-  \hline
-  \end{tabular}
-  %\linebreak
-	\end{center}
-}
-
-\usepackage{xspace}
-% Einfache und doppelte Anfuehrungszeichen
-\newcommand{\qs}{``} 
-\newcommand{\qe}{''\xspace} 
-\newcommand{\sqs}{`} 
-\newcommand{\sqe}{'\xspace}
-
-% checkmark
-\usepackage{tikz}
-\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
-
-% Xs
-\usepackage{pifont}
-
-% Tabellenabstände kleiner
-\setlength{\intextsep}{10pt} % Vertical space above & below [h] floats
-\setlength{\textfloatsep}{10pt} % Vertical space below (above) [t] ([b]) floats
-% \setlength{\abovecaptionskip}{0pt}
-% \setlength{\belowcaptionskip}{0pt}
-
-\usepackage{tabularx}
-\newcommand{\hr}{\hline\noalign{\smallskip}} % für die horizontalen linien in tabellen
-
-% pipe
-%\usepackage[T1]{fontenc}
-
-% Todos
-\usepackage[colorinlistoftodos]{todonotes}
-\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
-\newcommand{\er}[1]{\todo[size=\small, color=red!40]{\textbf{Erman:} #1}}
-\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}
-
-\setcounter{secnumdepth}{5}
-
 \begin{document}
 
-%
-%
-%\title{Formulating RDF Constraints and \\ Validating RDF Data Generically}
-\title{Formulating RDF Constraints Generically and Validating RDF Data Out-Of-The-Box }
-%\subtitle{}
-%
-\titlerunning{XXXXX}  % abbreviated title (for running head)
-%                                     also used for the TOC unless
-%                                     \toctitle is used
-%
-\author{Thomas Bosch\inst{1} \and Erman Acar\inst{2} \and Kai Eckert\inst{3}}
-%
-\authorrunning{XXXXX} % abbreviated author list (for running head)
-%
-%%%% list of authors for the TOC (use if author list has to be modified)
-\institute{GESIS - Leibniz Institute for the Social Sciences, Germany\\
-\email{thomas.bosch@gesis.org},\\ 
-\and
-University of Mannheim, Germany \\
-\email{erman@informatik.uni-mannheim.de} 
-\and
-Stuttgart Media University, Germany \\
-\email{eckert@hdm-stuttgart.de} 
-}
-
-\maketitle              % typeset the title of the contribution
-
-\begin{abstract}
-
-More and more domains adopt Linked Data principles
-and seek for ways to ensure data quality by validating RDF data according to predefined constraints.  In particular, as many communities are used to have this functionality in the XML world.
-XML Schema is the standard language to formulate constraints to validate XML documents.
-For RDF, however, there are several languages which can be used to express constraints on RDF data - but not a stand-alone standard one meeting the majority of RDF validation use cases. 
+\title{\vspace{-1em}Formulating RDF Constraints Generically and Validating RDF Data Out-Of-The-Box}
+
+\author{Thomas Bosch\\GESIS – Leibniz Institute \\for the Social Sciences, Germany\\thomas.bosch@gesis.org \and Kai Eckert\\Stuttgart Media University, Germany\\eckert@hdm-stuttgart.de}
+
+\maketitle
+\vspace{-3em}
+\section*{Abstract}
+Increasingly, various domains adopt Linked Data principles
+and seek for ways to ensure data quality by validating RDF data according to predefined constraints,
+in particular, as many communities are used to have this functionality in the XML world.
+%XML Schema is the standard language to formulate constraints to validate XML documents.
+%For RDF, however, there are several constraint languages - but not a stand-alone standard one meeting the majority of RDF validation use cases. 
+To formulate constraints and to validate RDF data, several languages exist or are currently developed,
+but there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners
 % Truth be told, we do may two things, blabla on and to blabla, however for the flow of the text we dont need to overkill the text.
 In abstract and introduction, we just give general idea so at such points we better focus on flow.
-We identified requirements to formulate constraints for  validating RDF data and mapped each requirement to a constraint type.
-The majority of these constraint types can be expressed in description logics which provides their logical underpinning.
-
+Based on our work in the \emph{DCMI RDF Application Profiles Task Group} and in cooperation with the \emph{W3C Data Shapes Working Group}, 
+we published by today 81 types of constraints that are required by various stakeholders for data applications.
+%The majority of these constraint types can be expressed in description logics which provides their logical underpinning.
 %In this paper, we provide a basic terminology and classification system for RDF constraints.\tb{The contributions of this paper are the following. (1)...}
@@
 
-\keywords{RDF Validation, RDF Constraints, RDF Validation Requirements, Linked Data, Semantic Web}
-\end{abstract}
-%
-
-% ---------------
+\hspace{-1.4em}
+\textbf{Keywords:}
+RDF validation; RDF constraints; RDF validation requirements; Linked Data; Semantic Web
 
@@
 In 2013, the W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
-where experts from industry, government, and academia discussed first use cases for RDF constraint\footnote{For simplicity reasons, we use the terms \emph{constraint types/constraints} instead of \emph{RDF constraint types/RDF constraints} in the remainder of the paper} formulation and RDF data validation.
+where experts from industry, government, and academia discussed first use cases for RDF constraint
+%\footnote{For simplicity reasons, we use the terms \emph{constraint types/constraints} instead of \emph{RDF constraint types/RDF constraints} in the remainder of the paper} 
+formulation and RDF data validation.
 In 2014, two working groups on RDF validation have been established to focus on RDF validation: 
 the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles task group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
-Bosch and Eckert \cite{BoschEckert2014} collected the findings of these working groups and initiated a database of RDF validation requirements
-which is available for contribution at \url{http://purl.org/net/rdf-validation}.
+Bosch and Eckert \cite{BoschEckert2014} collected the findings of these working groups and initiated a database of RDF validation requirements\footnote{Online available at \url{http://purl.org/net/rdf-validation}}
+which is available for contribution.
 The intention is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
-Bosch et al.
-identified 74 requirements to formulate constraints; each of them corresponding to a constraint type which can be expressed by at least one existing constraint language \cite{BoschNolleAcarEckert2015}.
+We identified 81 requirements to formulate constraints; each of them corresponding to a constraint type which can be expressed by at least one existing constraint language \cite{BoschNolleAcarEckert2015}.
 
@@
 
-\section{Motivation}
+\subsection{Motivation and Overview}
 
@@
 
-With \emph{minimum qualified cardinality restrictions} (\emph{R-75/81})\footnote{Requirements/constraint types are uniquely identified by alphanumeric technical identifiers like \emph{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}}, researchers from the library domain may restrict
+Requirements/constraint types are uniquely identified by alphanumeric technical identifiers.
+\emph{Minimum qualified cardinality restrictions} (\emph{R-75}), e.g., is a constraint type which corresponds to the requirement {\small\emph{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}}. 
+With \emph{minimum qualified cardinality restrictions}, researchers from the library domain may restrict
 that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
@@
 
-We provide a validation environment\footnote{Available \url{http://purl.org/net/rdfval-demo}} which enables to validate RDF data according to constraints expressed by diverse  constraint languages.
+We provide a validation environment\footnote{Online available at \url{http://purl.org/net/rdfval-demo}} which enables to validate RDF data according to constraints expressed by diverse  constraint languages.
 As a second step, the \emph{RDF Validator} is extended by validating RDF data conforming to constraints of any constraint type represented by any constraint language,  
@@
 
-\subsection{RDF Validation Semantics}
+\subsection{Underlying Semantics}
 
@@
 
-We recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} (serving as appendix of this paper) in which
+We recently published a technical report \cite{BoschNolleAcarEckert2015} (serving as appendix of this paper) in which
 we describe the intended behavior of each constraint type in terms of validation results depending on \emph{CWA} and \emph{UNA}.
@@
 
-\tb{Frage an Kai: wann soll ich in kursiv hervorheben?}
-
 %\textcolor{red}{
@@
 
-\subsection{Basic Terminology for the Formulation of RDF Constraints}
+\subsection{Basic Terminology}
+%\subsection{Basic Terminology for the Formulation of RDF Constraints}
 
@@
 As there are already five promising constraint languages and our purpose is not to put a new constraint language, we rather developed a very simple lightweight vocabulary (only three classes, three object properties, and three data properties) which is universal enough to describe constraints of any constraint type expressible by any constraint language (see the conceptual model in figure \ref{fig:RDF-CV-conceptual-model}).
-We call this vocabulary the \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.
+We call this vocabulary the \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.
 
@@
 As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to describe constraints of all possible constraint types.
-\er{use RDF-CV / not: expressible in RDF-CV / RDF-CV is a vocabulary, not a language}
-
-\subsection{\emph{Simple Constraints} (Expressible in \emph{DL})}
+\tb{use RDF-CV / not: expressible in RDF-CV / RDF-CV is a vocabulary, not a language}
+
+\subsection{\emph{Simple Constraints}}
+
+\subsubsection{\emph{Simple Constraints} (Expressible in \emph{DL})}
 
@@
   \vspace{0cm}
+	\caption{Property Constraint - Cardinality Restriction}
+	\label{tab:property-constraint-cardinality-restriction}
 	\centering
@@
 		\end{tabular}
-	\caption{Property Constraint - Cardinality Restriction}
-	\label{tab:property-constraint-cardinality-restriction}
 \end{table}
@@
   \vspace{0cm}
+	\caption{Property Constraint - Object Property Paths}
+	\label{tab:property-constraint-object-property-paths}
 	\centering
@@
 		\end{tabular}
-	\caption{Property Constraint - Object Property Paths}
-	\label{tab:property-constraint-object-property-paths}
 \end{table}
 
-\subsection{\emph{Simple Constraints} (Not Expressible in \emph{DL})}
+\subsubsection{\emph{Simple Constraints} (Not Expressible in \emph{DL})}
 
@@
   \vspace{0cm}
+	\caption{Simple Constraint (Not Expressible in DL)}
+	\label{tab:simple-constraint-not-expressible-in-dl)}
 	\centering
@@
 		\end{tabular}
-	\caption{Simple Constraint (Not Expressible in DL)}
-	\label{tab:simple-constraint-not-expressible-in-dl)}
 \end{table} %\tb{Erman, can you please format the regular expression in the table above correctly?}
@@
   \vspace{0cm}
+	\caption{Complex Constraints}
+	\label{tab:complex-constraints}
 	\centering
@@
 		\end{tabular}
-	\caption{Complex Constraints}
-	\label{tab:complex-constraints}
 \end{table}
@@
   \vspace{0cm}
+	\caption{Simplified Complex Constraints}
+	\label{tab:simplified-complex-constraints}
 	\centering
@@
 		\end{tabular}
-	\caption{Simplified Complex Constraints}
-	\label{tab:simplified-complex-constraints}
 \end{table}
 
-\subsection{\emph{Complex Constraints} as \emph{Simple Constraints}}
+\subsubsection{\emph{Complex Constraints} as \emph{Simple Constraints}}
 
@@
   \vspace{0cm}
+	\caption{Irreflexive Object Properties as Complex Constraints}
+	\label{tab:irreflexive-object-properties-as-complex-constraints}
 	\centering
@@
 		\end{tabular}
-	\caption{Irreflexive Object Properties as Complex Constraints}
-	\label{tab:irreflexive-object-properties-as-complex-constraints}
 \end{table}
@@
   \vspace{0cm}
+	\caption{Irreflexive Object Properties as Simple Constraints}
+	\label{tab:irreflexive-object-properties-as-simple-constraints}
 	\centering
@@
 		\end{tabular}
-	\caption{Irreflexive Object Properties as Simple Constraints}
-	\label{tab:irreflexive-object-properties-as-simple-constraints}
 \end{table}
@@
   \vspace{0cm}
+	\caption{Primary Key Properties as Complex Constraints}
+	\label{tab:primary-key-properties-as-complex-constraints}
 	\centering
@@
 		\end{tabular}
-	\caption{Primary Key Properties as Complex Constraints}
-	\label{tab:primary-key-properties-as-complex-constraints}
 \end{table}
@@
   \vspace{0cm}
+	\caption{Primary Key Properties as Simple Constraints}
+	\label{tab:primary-key-properties-as-simple-constraints}
 	\centering
@@
 		\end{tabular}
-	\caption{Primary Key Properties as Simple Constraints}
-	\label{tab:primary-key-properties-as-simple-constraints}
 \end{table}
@@
 %\section{Transformations between Specific Constraints}
+
 \section{How to Improve the Understandability of Constraints}
@@
   \vspace{0cm}
+	\caption{Existential Quantification as Simple Constraints}
+	\label{tab:existential-quantification-as-simple-constraints}
 	\centering
@@
 		\end{tabular}
-	\caption{Existential Quantification as Simple Constraints}
-	\label{tab:existential-quantification-as-simple-constraints}
 \end{table}
@@
 We use SPIN as basis to define a
-validation environment in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL
-(the implementation can be tested at \url{http://purl.org/net/rdfval-demo}).
-The SPIN engine checks for each resource if it satisfies all constraints, which are associated with the classes assigned to the resource, and generates a result RDF graph containing information about all constraint violations \cite{BoschEckert2014-2}.
+validation environment\footnote{Online demo available at \url{http://purl.org/net/rdfval-demo}, source code available at: \url{https://github.com/boschthomas/rdf-validator}\label{rdf-validator}} in which the validation of any constraint language can be implemented by representing them in SPARQL.
+The only limitation is that constraint languages must be represented in RDF.
+The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations \cite{BoschEckert2014-2}.
 This way, we are able to offer RDF data validation according to all \emph{specific constraints} (expressed by any constraint language) by defining mappings from each \emph{specific constraint} to \emph{SPIN}.
-We already specified mappings to \emph{SPIN} for all \emph{OWL 2} and \emph{DSP}\footnote{SPIN mappings: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} constructs and for some \emph{ReSh} and \emph{ShEx} constructs.
+We already specified mappings to \emph{SPIN} for all \emph{OWL 2} and \emph{DSP}\footnote{SPIN mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} constructs and for some \emph{ReSh} and \emph{ShEx} constructs.
 %We do not have to define a mapping to SPIN for each specific constraint. 
@@
 As a consequence, we only have to define one SPIN mapping for each constraint type corresponding to an RDF validation requirement.
-19 of the overall 74 identified constraint types can be expressed by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
+\textcolor{red}{19} of the overall 81 identified constraint types can be expressed by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
 This means that there must be 76 (four for each constraint type) implementations to validate RDF data according to 76 \emph{specific constraints} - instead of only 19 implementations (one for each \emph{generic constraint}) leading to identical validation results.
@@
 
-Within the \emph{RDF Validator}\footnote{For details about the validation environment see \cite{BoschEckert2014-2}}, we define one SPIN construct template for each \emph{generic constraint} and therefore constraint type.
+Within the \emph{RDF Validator}, we define one SPIN construct template for each \emph{generic constraint} and therefore constraint type.
 A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples (\emph{spin:ConstraintViolation}) indicating the subject (\emph{spin:violationRoot}) and the properties (\emph{spin:violationPath}) causing constraint violations, and the reason why constraint violations have been raised (\emph{rdfs:label}).
@@
 
-We provide a mapping from the \emph{RDF-CV} to SPIN\footnote{RDF-CV to SPIN: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}} 
+We provide a mapping from the \emph{RDF-CV} to SPIN\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}} 
 in order to automatically validate RDF data complying with each type of \emph{generic constraint} (\emph{simple}, \emph{complex}, \emph{property}, and \emph{class constraints}).
@@
 
-We evaluated to which extend the five most promising constraint languages on being the standard for fulfilling each of the overall 74 requirements to formulate RDF constraints (each corresponds to a constraint type).
-We recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} (serving as appendix of this paper) in which we explain each constraint type in detail and give examples for each (represented by different constraint languages).
+We evaluated to which extend the five most promising constraint languages on being the standard for fulfilling each of the overall 81 requirements to formulate RDF constraints (each corresponds to a constraint type).
+We recently published a technical report (serving as appendix of this paper) in which we explain each constraint type in detail and give examples for each (represented by different constraint languages).
 The technical report also contains mappings to \emph{DL} to logically underpin each constraint type and to determine which \emph{DL} constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
@@
   \vspace{0cm}
+	\caption{Evaluation}
+	\label{tab:evaluation}
 	\centering
@@
 		\end{tabular}
-	\caption{Evaluation}
-	\label{tab:evaluation}
 \end{table}
@@
 
-\tb{0.75 page / explain how typical constraints are expressed by different constraint languages}
+\tb{explain how typical constraints are expressed by the most common constraint languages}
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
 
 \section{Conclusion and Future Work}
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
 
@@
 
+\section{Old}
+
+\begin{ex}[commandchars=\\\{\}]
+:ArtficialIntelligence
+	a swrc:Book , \textit{:ToValidate} ;
+	dcterms:subject :ComputerScience .
+:ComputerScience
+	skos:Concept , \textit{:ToValidate} ;
+	dcam:memberOf :BookSubjects ;
+	skos:inScheme :BookSubjects ;
+	rdf:value "Computer Science"@en .
+:BookSubjects
+	a skos:ConceptScheme , \textit{:ToValidate} .
+\end{ex}
+
 \bibliography{../../literature/literature}{}
-\bibliographystyle{plain}
+\bibliographystyle{apacite}
 \setcounter{tocdepth}{1}

### 2015-05-23 paper/paper 2/dc-2015.tex
motivation

@@
 %For RDF, however, there are several constraint languages - but not a stand-alone standard one meeting the majority of RDF validation use cases. 
-To formulate constraints and to validate RDF data, several languages exist or are currently developed,
+To validate RDF data and to formulate constraints, several languages exist or are currently developed,
 but there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners
@@
 
-In 2013, the W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
-where experts from industry, government, and academia discussed first use cases for RDF constraint
-%\footnote{For simplicity reasons, we use the terms \emph{constraint types/constraints} instead of \emph{RDF constraint types/RDF constraints} in the remainder of the paper} 
-formulation and RDF data validation.
-In 2014, two working groups on RDF validation have been established to focus on RDF validation: 
-the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles task group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
-Bosch and Eckert \cite{BoschEckert2014} collected the findings of these working groups and initiated a database of RDF validation requirements\footnote{Online available at \url{http://purl.org/net/rdf-validation}}
-which is available for contribution.
-The intention is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
-We identified 81 requirements to formulate constraints; each of them corresponding to a constraint type which can be expressed by at least one existing constraint language \cite{BoschNolleAcarEckert2015}.
-
 Recently, RDF validation as a research field gained speed due to common needs of data practitioners.
@@
 While they embrace the openness of Linked Data and the data modeling principles provided by RDF, the data is still mostly represented in XML and this is unlikely to change any time soon.
-Among the reasons for the success of XML is the possibility to formulate fine-grained constraints to be met by the data and to validate the data according to these constraints using powerful systems like DTDs, XML Schemas, RELAX NG, or Schematron.
+Among the reasons for the success of XML is the possibility to formulate fine-grained constraints to be met by the data and to validate the data according to these constraints using powerful systems like \emph{DTD}, \emph{XML Schema}, \emph{RELAX NG}, or \emph{Schematron}.
 A typical example is the definition of a library record describing a book.
@@
 
+In 2013, the \emph{W3C} organized the \emph{RDF Validation Workshop}\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
+where experts from industry, government, and academia discussed first use cases for RDF data validation and constraint formulation.
+In 2014, two working groups on RDF validation have been established: 
+the \emph{W3C RDF Data Shapes Working Group}\footnote{\url{http://www.w3.org/2014/rds/charter}} and the \emph{DCMI RDF Application Profiles Task Group}\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
+We collected the findings of these working groups and initiated a database of RDF validation requirements\footnote{Online available at \url{http://purl.org/net/rdf-validation}} \cite{BoschEckert2014}.
+The intention is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
+Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group,
+we published by today 81 requirements to validate RDF data and to formulate constraints; 
+%each of them corresponding to a constraint type which in most cases can be expressed by multiple constraint languages. 
+each of them corresponds to a constraint type from which concrete constraints are instantiated to be checked on RDF data and
+which in most cases can be expressed by multiple constraint languages.
+Requirements/constraint types are uniquely identified by alphanumeric technical identifiers.
+\emph{Minimum qualified cardinality restrictions} (\emph{R-75}), e.g., is a constraint type which corresponds to the requirement {\small\emph{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}}.
+We recently published a technical report (serving as appendix of this paper) in which we explain each constraint type in detail and give examples for each represented by different constraint languages \cite{BoschNolleAcarEckert2015}.
+More than 10 constraint languages with different syntax and semantics exist or are currently developed. 
+We focus on the five most promising ones on being the standard like
+\emph{Shape Expressions (ShEx)}, \emph{Resource Shapes (ReSh)}, and \emph{Description Set Profiles (DSP)}. 
+The \emph{Web Ontology Language} \emph{(OWL)} in its current version \emph{OWL 2} can also be used as a constraint language.
+With its direct support of validation via \emph{SPARQL}, the \emph{SPARQL Inferencing Notation (SPIN)} is very popular and certainly plays an important role for the future development in this field. 
+%\emph{SPIN} is particularly interesting as a means to validate arbitrary constraint languages by mapping them to \emph{SPARQL} \cite{BoschEckert2014-2}.
+
 \subsection{Motivation and Overview}
 
-As there is no do-it-all language meeting the majority of requirements to formulate constraints and to validate RDF data,
+We evaluated for the five most common constraint languages which constraint types they enable to express \cite{BoschNolleAcarEckert2015}.
+As there exists no single best solution and none of the languages is able to meet all requirements raised by data practitioners,
 %which can be used to express constraints and to validate RDF data, 
 %(e.g. existential and universal quantification, cardinality restrictions, and exclusive or of properties)
-language selection heavily depends on the individual use case.  
-There are more than 10 candidate languages with different syntaxes and semantics, and we will focus on five which, in our opinion, are the most promising languages on being the standard constraint languages.
-Those are
-\emph{Description Set Profiles (DSP)},
-\emph{Resource Shapes (ReSh)}, 
-\emph{Shape Expressions (ShEx)},
-the \emph{SPARQL Inferencing Notation (SPIN)}, 
-and the \emph{Web Ontology Language (OWL 2)}.
 %\section{Ideas}
@@
 %min car more powerful than req. propery
-The idea behind this paper is to achieve complete RDF validation requirements coverage by representing any constraint type (each of them corresponding to a requirement to formulate constraints on and to validate RDF data) in a generic way using a lightweight vocabulary which consists of only a few terms (see Section \ref{sec:vocabulary}).
-
-\emph{Cardinality restrictions} can be expressed either generically (\emph{generic constraints}) by \emph{description logics (DL)} 
-%and extensions  
-or specifically (\emph{specific constraints}) by domain-specific constraint languages such as \emph{OWL 2}, \emph{DSP}, \emph{ShEx}, \emph{ReSh}, and \emph{SPIN}.
-The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
-For that reason, we map constraint types to \emph{DL} statements.
-
-Requirements/constraint types are uniquely identified by alphanumeric technical identifiers.
-\emph{Minimum qualified cardinality restrictions} (\emph{R-75}), e.g., is a constraint type which corresponds to the requirement {\small\emph{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}}. 
-With \emph{minimum qualified cardinality restrictions}, researchers from the library domain may restrict
+the idea behind this paper is to satisfy all RDF validation requirements
+by representing constraints of any constraint type in a generic way using a lightweight vocabulary which consists of only a few terms (Section \ref{sec:vocabulary}).
+The constraint type \emph{minimum qualified cardinality restrictions} (\emph{R-75}) can be instantiated to ensure
 that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
-This constraint can be represented generically (\emph{generic constraint}) in \emph{DL} {\small\ms{(Publication $\sqsubseteq$ $\geq$1 author.Person)}}, but also specifically (\emph{specific constraint}) by multiple constraint languages:
-
-\begin{ex}
-# OWL 2:
+This constraint can either be represented generically by \emph{description logics (DL)} {\small\ms{(Publication $\sqsubseteq$ $\geq$1 author.Person)}} or specifically by multiple domain-specific constraint languages:
+
+\begin{ex}[commandchars=\\\{\}]
+\textit{OWL 2:}
 Publication
@@
 
-# ShEx:
-Publication { author @Person{1, } }
-
-# ReSh:
+\textit{ShEx:}
+Publication \{ author @Person\{1, \} \}
+
+\textit{ReSh:}
 Publication a rs:ResourceShape ; rs:property [
@@
 
-# DSP:
+\textit{DSP:}
 [   a dsp:DescriptionTemplate ; 
@@
 \end{ex}
+
+The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
+For this reason, the appendix of this paper contains mappings to \emph{DL} to determine which \emph{DL} constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
 
@@
 
-We evaluated to which extend the five most promising constraint languages on being the standard for fulfilling each of the overall 81 requirements to formulate RDF constraints (each corresponds to a constraint type).
-We recently published a technical report (serving as appendix of this paper) in which we explain each constraint type in detail and give examples for each (represented by different constraint languages).
-The technical report also contains mappings to \emph{DL} to logically underpin each constraint type and to determine which \emph{DL} constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
+The appendix of this paper contains mappings to \emph{DL} to logically underpin each constraint type and to determine which \emph{DL} constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
 If a constraint type was expressible in \emph{DL}, we added the mapping to \emph{DL} and to the \emph{generic constraint} conforming to the \emph{RDF-CV}.
@@
 
-\section{Old}
-
-\begin{ex}[commandchars=\\\{\}]
-:ArtficialIntelligence
-	a swrc:Book , \textit{:ToValidate} ;
-	dcterms:subject :ComputerScience .
-:ComputerScience
-	skos:Concept , \textit{:ToValidate} ;
-	dcam:memberOf :BookSubjects ;
-	skos:inScheme :BookSubjects ;
-	rdf:value "Computer Science"@en .
-:BookSubjects
-	a skos:ConceptScheme , \textit{:ToValidate} .
-\end{ex}
-
 \bibliography{../../literature/literature}{}

### 2015-05-25 paper/paper 2/rdf-constraints-vocabulary.tex
RDF Constraints Vocabulary

--- 2015-05-08 paper/paper 2/paper 2.tex
@@
 %\title{Formulating RDF Constraints and \\ Validating RDF Data Generically}
-\title{Formulating RDF Constraints Generically and Validating RDF Data Out-Of-The-Box }
+\title{A Vocabulary to Describe RDF Constraints Generically}
 %\subtitle{}
@@
 %
-\author{Thomas Bosch\inst{1} \and Erman Acar\inst{2} \and Kai Eckert\inst{3}}
+\author{Thomas Bosch\inst{1} \and Kai Eckert\inst{3}}
 %
@@
 \and
-University of Mannheim, Germany \\
-\email{erman@informatik.uni-mannheim.de} 
-\and
 Stuttgart Media University, Germany \\
@@
 \begin{abstract}
-
-More and more domains adopt Linked Data principles
-and seek for ways to ensure data quality by validating RDF data according to predefined constraints.  In particular, as many communities are used to have this functionality in the XML world.
-XML Schema is the standard language to formulate constraints to validate XML documents.
-For RDF, however, there are several languages which can be used to express constraints on RDF data - but not a stand-alone standard one meeting the majority of RDF validation use cases. 
-% Truth be told, we do may two things, blabla on and to blabla, however for the flow of the text we dont need to overkill the text.
-In abstract and introduction, we just give general idea so at such points we better focus on flow.
-We identified requirements to formulate constraints for  validating RDF data and mapped each requirement to a constraint type.
-The majority of these constraint types can be expressed in description logics which provides their logical underpinning.
-
-%In this paper, we provide a basic terminology and classification system for RDF constraints.\tb{The contributions of this paper are the following. (1)...}
-%We developed a vocabulary to describe constraints of any RDF constraint type generically. 
-%%(whether expressible in description logics or not).
-%We show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful.
-%We explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages by providing mappings to generically expressed constraints.
-
-The contributions of this paper are:
-(1) we provide a basic terminology and classification system for RDF constraints,
-(2) we develop a vocabulary to describe constraints of any constraint type generically and specified its underlying semantics,
-(3) we show how to transform constraints which are expressed by any constraint language, into generically expressed constraints and discuss why these transformations are useful, and
-(4) we explain how to overcome the problems to implement the validation of each constraint type for diverse constraint languages.
+...
 
@@
 % ---------------
-
-\section{Introduction}
-%The purpose of OWL 2 ontologies is to perform reasoning on RDF data and not to validate RDF data conforming to these ontologies.
-%OWL 2 is based on the {\em non-unique name assumption} (nUNA) whereas RDF validation requires that different names represent different objects ({\em unique name assumption} (UNA)). 
-%Reasoning in OWL 2 is based on the semantics of {\em open-world assumption} (OWA), i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose: to represent knowledge on the World Wide Web.
-%On the other hand, many RDF validation scenarios require the {\em closed-world assumption} (CWA) (i.e., a statement is inferred to be false if it cannot be proved to be true).
-%This ambiguity in semantics is one of the main reasons why OWL 2 has not been adopted as a standard constraint language for RDF validation.  
-%For this reason, we cannot use OWL 2 ontologies for RDF validation as we use XML Schemas, DTDs, RELAX NG, or Schematron to validate XML documents.
-
-In 2013, the W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
-where experts from industry, government, and academia discussed first use cases for RDF constraint\footnote{For simplicity reasons, we use the terms \emph{constraint types/constraints} instead of \emph{RDF constraint types/RDF constraints} in the remainder of the paper} formulation and RDF data validation.
-In 2014, two working groups on RDF validation have been established to focus on RDF validation: 
-the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles task group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
-Bosch and Eckert \cite{BoschEckert2014} collected the findings of these working groups and initiated a database of RDF validation requirements
-which is available for contribution at \url{http://purl.org/net/rdf-validation}.
-The intention is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
-Bosch et al.
-identified 74 requirements to formulate constraints; each of them corresponding to a constraint type which can be expressed by at least one existing constraint language \cite{BoschNolleAcarEckert2015}.
-
-Recently, RDF validation as a research field gained speed due to common needs of data practitioners.
-A typical example is the library domain that co-developed and adopted Linked Data principles very early.
-For libraries, the common description of resources are key business and they have a long tradition in developing and using interoperable data formats.
-While they embrace the openness of Linked Data and the data modeling principles provided by RDF, the data is still mostly represented in XML and this is unlikely to change any time soon.
-Among the reasons for the success of XML is the possibility to formulate fine-grained constraints to be met by the data and to validate the data according to these constraints using powerful systems like DTDs, XML Schemas, RELAX NG, or Schematron.
-A typical example is the definition of a library record describing a book.
-There are clear rules which information has to be available to describe a book properly (required fields, like a title), but also how information like an ISBN number is properly represented.
-Libraries seek to make their own data reusable for general purposes, but also to enrich and interlink their own data.
-Checking if third-party data meets own requirements or validating existing data according to new needs for a Linked Data application are among common use cases for RDF validation.
-
-\section{Motivation}
-
-As there is no do-it-all language meeting the majority of requirements to formulate constraints and to validate RDF data,
-%which can be used to express constraints and to validate RDF data, 
-%(e.g. existential and universal quantification, cardinality restrictions, and exclusive or of properties)
-language selection heavily depends on the individual use case.  
-There are more than 10 candidate languages with different syntaxes and semantics, and we will focus on five which, in our opinion, are the most promising languages on being the standard constraint languages.
-Those are
-\emph{Description Set Profiles (DSP)},
-\emph{Resource Shapes (ReSh)}, 
-\emph{Shape Expressions (ShEx)},
-the \emph{SPARQL Inferencing Notation (SPIN)}, 
-and the \emph{Web Ontology Language (OWL 2)}.
-%\section{Ideas}
-%constraint design patterns:
-% - ontology design pattern.org
-% - DSP uses other design pattern
-% - constraint elements are the same / 
-% - constraint / constraint elements / constraint design patterns / constraint language
-%dependency between requirements / when this requirements is fulfilled then this is also fulfilled (e.g. min card and requ. car)
-%min car more powerful than req. propery
-The idea behind this paper is to achieve complete RDF validation requirements coverage by representing any constraint type (each of them corresponding to a requirement to formulate constraints on and to validate RDF data) in a generic way using a lightweight vocabulary which consists of only a few terms (see Section \ref{sec:vocabulary}).
-
-\emph{Cardinality restrictions} can be expressed either generically (\emph{generic constraints}) by \emph{description logics (DL)} 
-%and extensions  
-or specifically (\emph{specific constraints}) by domain-specific constraint languages such as \emph{OWL 2}, \emph{DSP}, \emph{ShEx}, \emph{ReSh}, and \emph{SPIN}.
-The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
-For that reason, we map constraint types to \emph{DL} statements.
-
-With \emph{minimum qualified cardinality restrictions} (\emph{R-75/81})\footnote{Requirements/constraint types are uniquely identified by alphanumeric technical identifiers like \emph{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}}, researchers from the library domain may restrict
-that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
-This constraint can be represented generically (\emph{generic constraint}) in \emph{DL} {\small\ms{(Publication $\sqsubseteq$ $\geq$1 author.Person)}}, but also specifically (\emph{specific constraint}) by multiple constraint languages:
-
-\begin{ex}
-# OWL 2:
-Publication
-    a owl:Restriction ;
-    owl:minQualifiedCardinality 1 ;
-    owl:onProperty author ;
-    owl:onClass Person .
-
-# ShEx:
-Publication { author @Person{1, } }
-
-# ReSh:
-Publication a rs:ResourceShape ; rs:property [
-    rs:name "author" ; rs:propertyDefinition author ;
-    rs:valueShape Person ;
-    rs:occurs rs:One-or-many ; ] .
-
-# DSP:
-[   a dsp:DescriptionTemplate ; 
-    dsp:resourceClass Publication ; 
-    dsp:statementTemplate [ a dsp:NonLiteralStatementTemplate ;
-        dsp:minOccur 1 ; dsp:maxOccur "infinity" ; 
-        dsp:property author ; 
-        dsp:nonLiteralConstraint [ a dsp:NonLiteralConstraint ;
-            dsp:valueClass Person ] ] ] .
-\end{ex}
-
-As every \emph{publication} must have at least one \emph{author} which must be a \emph{person}, 
-and since the book \emph{The-Lord-Of-The-Rings} is a \emph{publication} {\small\ms{(rdf:type(The-Lord-Of-The-Rings, Publication)),}} 
-it must have at least one \emph{author} relationship to a \emph{person}.
-Constraint violations are raised either (1) if
-\emph{The-Lord-Of-The-Rings} does not have any \emph{author} relationship, or (2) if 
-it has an \emph{author} which is not a \emph{person} \\
-{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Hobbit)),}} 
-or (3) if it has an \emph{author} for which no class is assigned
-{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)).}}
-In contrast, \emph{The-Lord-Of-The-Rings} is a valid \emph{publication}, if it is connected to a \emph{person} via the property \emph{author}
-{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Person)).}}
-
-As there is no standard way to formulate constraints, 
-semantically equivalent \emph{cardinality restrictions} may be represented by multiple constraint languages that have different syntax and semantics.
-This causes confusion and weakens the common understanding between several parties about the semantics of particular constraints. Also, it raises  questions on how to ensure high data quality. 
-Therefore, when choosing a constraint language, say \ms{$\alpha$}, to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a semantically equivalent constraint expressed by another constraint language \ms{$\beta$} (see Section \ref{sec:transformations}).
-This is important in order to enhance the interoperability of constraint languages and to resolve misunderstandings and ambiguities in the communication of RDF data producers and consumers, 
-since constraint transformations avoid the necessity to understand several constraint languages.
-
-We provide a validation environment\footnote{Available \url{http://purl.org/net/rdfval-demo}} which enables to validate RDF data according to constraints expressed by diverse  constraint languages.
-As a second step, the \emph{RDF Validator} is extended by validating RDF data conforming to constraints of any constraint type represented by any constraint language,  
-to perform validation on semantically equivalent \emph{specific constraints}, expressed by different constraint languages, 
-i.e., validation is independent from the used constraint language (see Section \ref{sec:validation}). 
-%i.e., validation leads to identical validation results - independently from the used constraint language (see section \ref{sec:validation}).
-We are able to offer an already implemented validation mechanism for any \emph{specific constraint} out-of-the-box, 
-(1) if we implement the validation of the corresponding \emph{generic constraint type} once and 
-(2) if we transform semantically equivalent \emph{specific constraints} into generically expressed constraints.
-
-%When domain experts use graphical user interfaces to define constraints in a user-friendly way (without the necessity to express constraints on their own), 
-%constraints can be mapped to either a specific or a generic constraint, as for both the validation is provided in the background.    
-%So, the user does not have to know how to express specific constraints using any constraint language.
-
-%Existing constraint languages can be extended and new constraint languages can be developed, if existing constraint languages are not sufficient to represent needed constraint types.
-
-%If (1) a new constraint type is expressed generically, (2) the \emph{generic constraint type} is mapped to \emph{specific constraint types} (expressed by constraint languages), and (3) the validation is implemented for this particular \emph{generic constraint type},
-%the validation of \emph{specific constraint types} is provided out of the box.
-%As a consequence, constraint language designers do not have to implement the validation of their constraint languages and each semantically equivalent \emph{specific constraint type} is validated the same way (i.e.
-leading to identical validation results).
-
-%This paper aims to address two main \textbf{audiences}:
-%(1) RDF data providers and consumers seeking how to ensure high data quality and thus for ways to enhance the interoperability and common understanding of constraints expressible by multiple constraint languages and
-%(2) RDF practitioners thinking of how to provide aligned implementations for the validation of both existing an newly developed constraint languages.
-The main contributions of this paper are:
-(1) we provide a basic terminology and classification system for RDF constraints (Section \ref{sec:vocabulary}),
-(2) we developed a vocabulary to describe constraints of any RDF constraint type generically and specified its underlying semantics (Section \ref{sec:vocabulary}),
-(3) we show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful (Section \ref{sec:transformations}), and
-(4) we explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages (Section \ref{sec:validation}).
-%(if the validation is implemented once for the corresponding \emph{generic constraint type} to which the \emph{specific constraint type} is mapped)
-
-%The remainder of the paper is as follows.
-
-%\begin{itemize}
-	%\item Any specific constraint (expressed by any constraint language) can be transformed into a generic constraint (expressed by the generic constraint language)
-	%\item Any specific constraint (expressed by any constraint language A) can be transformed into any specific constraint (expressed by any constraint language B)
-	%\item Any specific constraint (expressed by any constraint language) can be validated automatically (if an automatic validation is defined only once for corresponding generic constraint)
-	%\item We define a basic terminology and classification system for RDF constraints
-	%\item We developed an ontology describing any RDF constraint generically (whether expressible in DL or not)%which can also be expressed by any constraint language
-	%\item We present that any RDF constraint can be described by the developed ontology - whether the constraint can be expressed in DL or not 
-	%\item We show how to transform specific constraints (expressed by any constraint language \ms{$\alpha$}) into generic constraints and into specific constraints (expressed by any other constraint language \ms{$\beta$})
-  %\item We explain that any specific constraint can be validated automatically (if the validation is implemented only once for the corresponding generic constraint)
-%\end{itemize}
-
-%The \textbf{benefits} of our framework are:
-%\begin{itemize}
-	%\item Any specific constraint (expressed by any constraint language) can be transformed into a generic constraint (expressed by the generic constraint language)
-	%\item Any specific constraint (expressed by any constraint language A) can be transformed into any specific constraint (expressed by any constraint language B)
-	%\item Any specific constraint (expressed by any constraint language) can be validated automatically (if an automatic validation is defined only once for corresponding generic constraint)
-%\end{itemize}
-
-%\section{Running Example}
-%
-%Table \ref{tab:cardinality-restriction-mapped-to-vocabulary} shows the mapping between the \emph{cardinality restriction} represented in DL 
-%and the \emph{cardinality restriction} expressed by our developed vocabulary to describe any RDF constraint generically (see section~\ref{sec:ontology}):
-%
-%\begin{table}
-  %\scriptsize
-  %\sffamily
-  %\vspace{0cm}
-	%\centering
-		%\begin{tabular}{l|l|l|l|l|l|l}
-      %\textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
-      %\hline
-      %property & Publication & author & - & Person & $\geq$ & 1 \\
-		%\end{tabular}
-	%\caption{Cardinality Restriction Expressed Generically}
-	%\label{tab:cardinality-restriction-mapped-to-vocabulary}
-%\end{table}
-
-%According to this vocabulary, each constraint is either a constraint on classes or a constraint on properties.
-%The generically expressed cardinality restriction is represented in RDF as follows:
-%
-%\begin{ex}
-%[   a PropertyConstraint ;
-    %contextClass Publication ;
-    %leftProperties ( author ) ;
-    %classes ( Person ) ;
-    %constrainingElement ">=" ;
-    %constrainingValue 1 ] .
-%\end{ex}
-
-%Bosch and Eckert\cite{BoschEckert2014-2} use SPIN as basis to define a
-%validation environment in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL.
-%The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.
-%The generically expressed \emph{cardinality restriction} above is validated within the validation environment (see section \ref{sec:validation}) by means of a SPARQL CONSTRUCT query.
-
-%\begin{ex}
-%[   a PropertyConstraint ;
-    %contextClass ?cc ;
-    %leftProperties ( ?p1 ) ;
-    %classes ( ?c1 ) ;
-    %constrainingElement ">=" ;
-    %constrainingValue ?cv ] .
-%?subject rdf:type ?cc .
-%BIND ( qualifiedCardinality( ?subject, ?p1, ?c1 ) AS ?c ) .
-%FILTER ( ?c < ?cv ) .		  
-%\end{ex}
 
@@
 As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to describe constraints of all possible constraint types.
-\er{use RDF-CV / not: expressible in RDF-CV / RDF-CV is a vocabulary, not a language}
 
@@
 
-\section{Related Work}
-
-\tb{0.75 page / explain how typical constraints are expressed by different constraint languages}
-
 \section{Conclusion and Future Work}

### 2015-05-25 paper/paper 2/dc-2015.tex
RDF Constraints Vocabulary

@@
 \renewcommand{\tablename}{TABLE} 
-\renewcommand{\figurename}{FIG} 
+\renewcommand{\figurename}{FIG.} 
 \usepackage{titlesec}
@@
 \renewcommand*{\titlepagestyle}{scrheadings}
-\chead{\fontsize{11pt}{0pt}\selectfont Proc. Int'l Conf. on Dublin Core and Metadata Applications 2015}
+\chead{\fontsize{9pt}{0pt}\selectfont Proc. Int'l Conf. on Dublin Core and Metadata Applications 2015}
 \usepackage{apacite}
@@
 }
+
+% just makes the table prettier (see \toprule, \bottomrule, etc. commands below)
+\usepackage{booktabs}
+
+% Tabellenabstände kleiner
+\setlength{\intextsep}{10pt} % Vertical space above & below [h] floats
+\setlength{\textfloatsep}{10pt} % Vertical space below (above) [t] ([b]) floats
+% \setlength{\abovecaptionskip}{0pt}
+% \setlength{\belowcaptionskip}{0pt}
+
+\usepackage{tabularx}
+
+\usepackage{float}
 
@@
 
-We evaluated for the five most common constraint languages which constraint types they enable to express \cite{BoschNolleAcarEckert2015}.
-As there exists no single best solution and none of the languages is able to meet all requirements raised by data practitioners,
+We evaluated which constraint types the five most common constraint languages enable to express.
+The evaluation is explained in detail in the appendix of this paper \cite{BoschNolleAcarEckert2015}.
+Table \ref{tab:constraint-type-specific-expressivity} shows in percentage values (and absolute numbers in brackets) how many constraint types each language supports.
+
+\begin{table}[H]
+	\centering
+	  %\caption{Constraint Type Specific Expressivity}
+		\caption{Constraint Type Specific Expressivity of Constraint Languages}
+	  \scriptsize
+		\begin{tabular}{c|c|c|c|c}
+      %\textbf{Expressivity Class} & $Expr(\overline{\mathcal{CT}_R})$ (42) & $Expr(\mathcal{CT}_R)$ (32) \\		
+			\emph{DSP} & \emph{ReSh} & \emph{ShEx} & \emph{OWL 2} & \emph{SPIN} \\	
+      \hline
+			17.3 (14) & 25.9 (21) & 29.6 (24) & 67.9 (55) & \textbf{100.0} \textbf{(81)} 
+		\end{tabular}
+	\label{tab:constraint-type-specific-expressivity}
+\end{table}
+
+The fact that \emph{SPIN} supports all and that \emph{OWL 2} covers 2/3 of all constraint types
+emphasizes the significant role \emph{SPIN} and \emph{OWL 2} play for the future development of constraint languages.
+\emph{SPARQL} and therefore \emph{SPIN}, the \emph{SPARQL}-based way to formulate and check constraints, is generally seen as the method of choice to validate data according to certain constraints \cite{Fuerber2010},
+although, it is not ideal for their formulation. 
+In contrast, high-level constraint languages, which may be placed on top of \emph{SPARQL} and \emph{SPIN}, are comparatively easy to understand and constraints can be formulated more concisely.
+
+There exists no single best solution considered as high-level intuitive constraint language which enables to express constraints easily and concisely and which is able to meet all requirements raised by data practitioners.
 %which can be used to express constraints and to validate RDF data, 
@@
 %min car more powerful than req. propery
-the idea behind this paper is to satisfy all RDF validation requirements
-by representing constraints of any constraint type in a generic way using a lightweight vocabulary which consists of only a few terms (Section \ref{sec:vocabulary}).
+Thus, the idea behind this paper is to satisfy all RDF validation requirements
+by representing constraints of any constraint type in a generic way using a lightweight vocabulary which consists of only a few terms.
+We lately published a technical report (serving as second appendix of this paper) in which we describe the vocabulary in detail \cite{BoschEckert2015-2} (Section \ref{sec:vocabulary}).
 The constraint type \emph{minimum qualified cardinality restrictions} (\emph{R-75}) can be instantiated to ensure
@@
 
-As every \emph{publication} must have at least one \emph{author} which must be a \emph{person}, 
+As every \emph{publication} must have at least one \emph{author} which must be a \emph{person} 
 and since the book \emph{The-Lord-Of-The-Rings} is a \emph{publication} {\small\ms{(rdf:type(The-Lord-Of-The-Rings, Publication)),}} 
-it must have at least one \emph{author} relationship to a \emph{person}.
-Constraint violations are raised either (1) if
-\emph{The-Lord-Of-The-Rings} does not have any \emph{author} relationship, or (2) if 
-it has an \emph{author} which is not a \emph{person} \\
-{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Hobbit)),}} 
-or (3) if it has an \emph{author} for which no class is assigned
+the book must have at least one \emph{author} relationship to a \emph{person}.
+The constraint is violated either (1) if
+\emph{The-Lord-Of-The-Rings} does not have any \emph{author} relationship, 
+or (2) if the book has an \emph{author} which is not a \emph{person}
+{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)},} {\small\ms{rdf:type(Tolkien, Hobbit)),}} 
+or (3) if the book has an \emph{author} whose class is unknown
 {\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)).}}
-In contrast, \emph{The-Lord-Of-The-Rings} is a valid \emph{publication}, if it is connected to a \emph{person} via the property \emph{author}
+In contrast, the book is a valid \emph{publication}, if it is connected to a \emph{person} via the property \emph{author}
 {\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Person)).}}
@@
 As there is no standard way to formulate constraints, 
-semantically equivalent \emph{cardinality restrictions} may be represented by multiple constraint languages that have different syntax and semantics.
-This causes confusion and weakens the common understanding between several parties about the semantics of particular constraints. Also, it raises  questions on how to ensure high data quality. 
-Therefore, when choosing a constraint language, say \ms{$\alpha$}, to express a constraint of an arbitrary constraint type, it should be possible to transform this constraint into a semantically equivalent constraint expressed by another constraint language \ms{$\beta$} (see Section \ref{sec:transformations}).
-This is important in order to enhance the interoperability of constraint languages and to resolve misunderstandings and ambiguities in the communication of RDF data producers and consumers, 
-since constraint transformations avoid the necessity to understand several constraint languages.
-
-We provide a validation environment\footnote{Online available at \url{http://purl.org/net/rdfval-demo}} which enables to validate RDF data according to constraints expressed by diverse  constraint languages.
-As a second step, the \emph{RDF Validator} is extended by validating RDF data conforming to constraints of any constraint type represented by any constraint language,  
-to perform validation on semantically equivalent \emph{specific constraints}, expressed by different constraint languages, 
-i.e., validation is independent from the used constraint language (see Section \ref{sec:validation}). 
-%i.e., validation leads to identical validation results - independently from the used constraint language (see section \ref{sec:validation}).
-We are able to offer an already implemented validation mechanism for any \emph{specific constraint} out-of-the-box, 
-(1) if we implement the validation of the corresponding \emph{generic constraint type} once and 
-(2) if we transform semantically equivalent \emph{specific constraints} into generically expressed constraints.
+semantically equivalent \emph{minimum qualified cardinality restrictions} may be represented by multiple languages - each of them having different syntax and semantics.
+This causes confusion,
+weakens the common understanding between several parties about the meaning of particular constraints, and
+raises the question on how to ensure high data quality. 
+Therefore, when choosing a language, say \ms{$\alpha$}, to express a constraint of an arbitrary constraint type, 
+it should be possible to transform the constraint into a semantically equivalent constraint expressed by another constraint language \ms{$\beta$} (see Section \ref{sec:transformations}). 
+This is important in order to enhance the interoperability of constraint languages and to resolve misunderstandings and ambiguities in the communication of RDF data producers and consumers 
+since automatically performed constraint transformations avoid the necessity to understand several languages.
+
+We use \emph{SPIN} as basis to develop a validation environment\footnote{Online demo available at \url{http://purl.org/net/rdfval-demo}, source code available at: \url{https://github.com/boschthomas/rdf-validator}\label{rdf-validator}} to validate RDF data according to constraints of constraint types which are expressible by arbitrary constraint languages by mapping them to \emph{SPIN}\footnote{\emph{SPIN} mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}\label{spin-mappings}} \cite{BoschEckert2014-2}.
+The next step, however, is to extend the \emph{RDF Validator} to validate RDF data conforming to constraints of each of the 81 constraint types.
+
+Validation on semantically equivalent constraints, expressed by different constraint languages, 
+should lead to identical validation results, 
+i.e., validation should be performed independently from the used language (see Section \ref{sec:validation}).
+
+We are able to offer already implemented validation for constraints of constraint types expressed by arbitrary languages out-of-the-box, 
+(1) if we implement the validation of the corresponding generically represented constraint types once and 
+(2) if we transform semantically equivalent specifically expressed constraints into generically expressed constraints.
 
@@
 The main contributions of this paper are:
-(1) we provide a basic terminology and classification system for RDF constraints (Section \ref{sec:vocabulary}),
-(2) we developed a vocabulary to describe constraints of any RDF constraint type generically and specified its underlying semantics (Section \ref{sec:vocabulary}),
-(3) we show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful (Section \ref{sec:transformations}), and
-(4) we explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages (Section \ref{sec:validation}).
+(1) We provide a basic terminology and classification system for RDF constraints (Section \ref{sec:vocabulary}).
+(2) We developed a vocabulary to describe constraints of any RDF constraint type generically (Section \ref{sec:vocabulary}).
+(3) We show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful (Section \ref{sec:transformations}).
+(4) We explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages (Section \ref{sec:validation}).
 %(if the validation is implemented once for the corresponding \emph{generic constraint type} to which the \emph{specific constraint type} is mapped)
@@
 
-In order to develop a vocabulary to describe constraints of any constraint type in a generic way, what we need to do is to specify the vocabulary's underlying semantics and to define the basic terminology for the formulation of constraints.
-
-\subsection{Underlying Semantics}
-
-%The underlying \emph{semantics} for RDF validation is \emph{UNA} and \emph{CWA}.
-RDF validation requires that different names represent different objects (\emph{unique name assumption (UNA)}), whereas,
+Prerequisites to develop a vocabulary to describe constraints of any constraint type in a generic way are 
+(1) to specify the underlying semantics for validation and thus for the vocabulary and (2) to define a basic terminology and classification system to formulate constraints.
+
+\subsection{Semantics for RDF Validation}
+
+RDF validation and \emph{OWL 2} assume different semantics. 
+This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past.
+We compare semantics of RDF validation and of \emph{OWL 2} as we consider \emph{OWL 2} as a constraint language 
+when RDF validation semantics are applied.
+%
+\emph{OWL 2} is based on the {\em open-world assumption} (\emph{OWA}), i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose to represent knowledge on the \emph{WWW}.
+As each \emph{book} must have a \emph{title} {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a \emph{book} {\small\ms{(Book(Hamlet)),}}
+{\em Hamlet} must have at least one \emph{title} as well.
+In an \emph{OWA} setting, this constraint does not cause a violation, even if there is no explicitly defined \emph{title}, since there must be a \emph{title} for this \emph{book} which we may not know ($\mathcal{K}$ is consistent).
+As RDF validation has its origin in the XML world
+many RDF validation scenarios require the {\em closed-world assumption} (\emph{CWA}), i.e., a statement is inferred to be false if it cannot be proved to be true.
+Thus, classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals. 
+In the example, the \emph{CWA} yields to a violation since there is no explicitly defined \emph{title} for the \emph{book} {\em Hamlet}. 
+%
+Validation requires that different names represent different objects (\emph{unique name assumption (UNA)}), whereas,
 \emph{OWL 2} is based on the {\em non-unique name assumption (nUNA)}.  
-A data property is \emph{functional} (\emph{R-65}) if for each individual \emph{x}, there can be at most one distinct literal \emph{y} such that \emph{x} is connected by the data property to \emph{y}.
-When assuming \emph{UNA}, the functional property {\em title} {\small\ms{(funct (title))}} causes a clash
-in case the book {\em Huckleberry-Finn} has more than one \emph{title}.
-%(\ms{title(Huckleberry-Finn,} \ms{The-Adventures-of-Huckleberry-Finn)}, \ms{title} \ms{(Huckleberry-Finn,} \ms{Die-Abenteuer-des-Huckleberry-Finn)}).
-Assuming \emph{nUNA}, however, reasoning concludes that the titles {\em The-Adventures-of-Huckleberry-Finn} and {\em Die-Abenteuer-des-Huckleberry-Finn} are the same. 
-%(\ms{\{The-Adventures-of-Huckleberry-Finn\}} = \ms{\{Die-Abenteuer-des-Huckle} \ms{berry-}\ms{Finn\}}).
-
-Reasoning in \emph{OWL 2} is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true. 
-%which fits its primary design purpose to represent knowledge on the World Wide Web. 
-%Most of the constraint languages except OWL, have a major shortcoming of redundancy.
-%With its open-world semantics, used as a constraint language, OWL solves the redundancy problem. 
-%\tb{the following example does not show the redundancy problem!}
-%\tb{2. benefit: reasoning solves redundancy problem}
-As each \emph{book} must have a \emph{title} {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a \emph{book} {\small\ms{(Book(Hamlet)),}}
-{\em Hamlet} must have at least one \emph{title}.
-In an \emph{OWA} setting, this axiom does not cause a constraint violation (even if there is no explicitly defined \emph{title}), since there must be a \emph{title} for this \emph{book} which we may not know.
-On the other hand, RDF validation scenarios require the \emph{closed-world assumption (CWA)}, i.e., a statement is inferred to be false if it cannot be proved to be true.
-When assuming the \emph{CWA}, a constraint violation is raised as there is no explicitly defined title. 
-A constraint that says that a book must have at least one title in \emph{OWA}, 
-does not mean that the title has to be unique. 
-In every model  (an interpretation that makes a set of \emph{DL knowledge base} true), 
-it can be the case that a book has a single title, however, 
-this title is not unique. 
-In some models it is \emph{The-Adventures-of-Huckleberry-Finn}, in others it is \emph{Die-Abenteuer-des-Huckleberry-Finn}. 
-And since in every model there is only one, \emph{DL} sentences are satisfied. 
-But this does not correspond to the intended constraint which is usual in \emph{CWA} way.   
-%Classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals which yields a constraint violation.
-This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past. 
-In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (\emph{CWA} and \emph{UNA}) as for RDF validation in general. 
+If we define the property \emph{title} to be functional {\small\ms{(funct (title)),}} a \emph{book} can have at most one distinct \emph{title}.
+\emph{UNA} causes a clash
+if the \emph{book} {\em Huckleberry-Finn} has more than one \emph{title}.
+For \emph{nUNA}, however, reasoning concludes that the \emph{title} {\em The-Adventures-of-Huckleberry-Finn} must be the same as the \emph{title} {\em Die-Abenteuer-des-Huckleberry-Finn} 
+which resolves the violation. 
+%Although, \emph{OWL 2} does not assume \emph{UNA}, \emph{OWL 2} has the constructs \emph{owl:sameAs} and \emph{owl:differentFrom} to state that two names are the same or different.
+If validation would assume \emph{OWA} and \emph{nUNA}, validation won’t be that restrictive and therefore we won’t get the intended validation results.
+
+%\emph{OWL 2} reasoning is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true. 
+%%which fits its primary design purpose to represent knowledge on the World Wide Web. 
+%%Most of the constraint languages except OWL, have a major shortcoming of redundancy.
+%%With its open-world semantics, used as a constraint language, OWL solves the redundancy problem. 
+%%\tb{the following example does not show the redundancy problem!}
+%%\tb{2. benefit: reasoning solves redundancy problem}
+%As each \emph{book} must have a \emph{title} {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a \emph{book} {\small\ms{(Book(Hamlet)),}}
+%{\em Hamlet} must have at least one \emph{title}.
+%In an \emph{OWA} setting, this axiom does not cause a constraint violation (even if there is no explicitly defined \emph{title}), since there must be a \emph{title} for this \emph{book} which we may not know.
+%On the other hand, RDF validation scenarios require the \emph{closed-world assumption (CWA)}, i.e., a statement is inferred to be false if it cannot be proved to be true.
+%When assuming the \emph{CWA}, a constraint violation is raised as there is no explicitly defined title. 
+%A constraint that says that a book must have at least one title in \emph{OWA}, 
+%does not mean that the title has to be unique. 
+%In every model  (an interpretation that makes a set of \emph{DL knowledge base} true), 
+%it can be the case that a book has a single title, however, 
+%this title is not unique. 
+%In some models it is \emph{The-Adventures-of-Huckleberry-Finn}, in others it is \emph{Die-Abenteuer-des-Huckleberry-Finn}. 
+%And since in every model there is only one, \emph{DL} sentences are satisfied. 
+%But this does not correspond to the intended constraint which is usual in \emph{CWA} way.   
+%%Classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals which yields a constraint violation.
+%This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past. 
+%In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (\emph{CWA} and \emph{UNA}) as for RDF validation in general. 
 %In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general. 
@@
 
-We recently published a technical report \cite{BoschNolleAcarEckert2015} (serving as appendix of this paper) in which
-we describe the intended behavior of each constraint type in terms of validation results depending on \emph{CWA} and \emph{UNA}.
+Differences in semantics may lead to differences in validation results when applied to particular constraint types.
+For the majority of the constraint types, validation results differ (1) if the \emph{CWA} or the \emph{OWA} and (2) if the \emph{UNA} or the \emph{nUNA} is assumed \cite{BoschNolleAcarEckert2015}.
 If any two constraints are semantically the same (w.r.t. RDF semantics), they should detect the same set of violations regardless of RDF data, 
@@
 
-\subsection{Basic Terminology}
+\subsection{Basic Terminology and Classification System for RDF Constraints}
 %\subsection{Basic Terminology for the Formulation of RDF Constraints}
@@
 A \emph{constraint language} is a language which is used to formulate constraints.
-The W3C Data Shapes working group defines \emph{RDF constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
-We identified four dimensions to classify constraint types:
-\begin{itemize}
-  \item \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints}
-	\item \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints}
-	\item \emph{Context:} \emph{property constraints} vs. \emph{class constraints}
-	\item \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}
-\end{itemize}
-
-As there are already five promising constraint languages and our purpose is not to put a new constraint language, we rather developed a very simple lightweight vocabulary (only three classes, three object properties, and three data properties) which is universal enough to describe constraints of any constraint type expressible by any constraint language (see the conceptual model in figure \ref{fig:RDF-CV-conceptual-model}).
-We call this vocabulary the \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.
-
+The \emph{W3C} working group defines \emph{RDF constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
+As there are already five promising constraint languages, 
+our purpose is not to propose a new language.
+We rather developed a very simple lightweight vocabulary,
+consisting of only three classes, three object properties, and three data properties, 
+which is universal enough to describe constraints of any constraint type.
+We call this vocabulary the \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}} whose conceptual model is shown in Figure \ref{fig:RDF-CV-conceptual-model}.
 \begin{figure}
 	\centering
-		\includegraphics[width=0.80\textwidth]{images/RDF-CV-conceptual-model.png}
-	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} - conceptual model}
+		\includegraphics[width=0.60\textwidth]{images/RDF-CV-conceptual-model.png}
+	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} - Conceptual Model}
 	\label{fig:RDF-CV-conceptual-model}
@@
 
-Constraints can be expressed either generically (\emph{generic constraints}) by the \emph{RDF-CV}   
+We identified four dimensions to classify sets of constraints which can be instantiated from constraint types.
+For each constraint type, we evaluated \cite{BoschNolleAcarEckert2015} in with which set of constraints their instances of contained.
+For each set of constraints, we state the rounded number of associated constraint types in brackets.
+%\begin{itemize}
+  %\item \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints}
+	%\item \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints}
+	%\item \emph{Context:} \emph{property constraints} vs. \emph{class constraints}
+	%\item \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}
+%\end{itemize}
+%(1) \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints},
+%(2) \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints},
+%(3) \emph{Context:} \emph{property constraints} vs. \emph{class constraints}, and
+%(4) \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}.
+\textbf{\emph{Universality}:}
+Constraints are expressible either generically (\emph{generic constraints}) using the \emph{RDF-CV}   
 or specifically (\emph{specific constraints}) by domain-specific constraint languages. 
-As the \emph{RDF-CV} describes constraints generically, the vocabulary does not distinguish constraints according to the dimension \emph{universality}. 
-The majority of the constraint types can be expressed in \emph{DL}.
-In contrast, there are certain constraint types which cannot be expressed in \emph{DL}, but are also expressible by the \emph{RDF-CV} . 
-\emph{Complex constraints} encompass \emph{simple constraints} (atomic constraints) and/or further \emph{complex constraints},
-i.e. \emph{DL} statements representing \emph{complex constraints} are created out of \emph{DL} statements standing for atomic and composed constraints (if expressible in \emph{DL}). 
-Simple constraints may be applied to either properties (\emph{property constraints}) or classes (\emph{class constraints}).
-The \emph{RDF-CV} does not contain any terms standing for \emph{simple} and \emph{complex constraints}, since \emph{context classes} of \emph{simple constraints} are just reused within \emph{complex constraints} (\emph{simple constraints} associated with \emph{context classes} must hold for individuals of these \emph{context classes}).
-%\tb{Erman: If you say its expressible in RDF-CV, than you impose that RDF-CV is a language rather than a vocabulary.
-"in different contexts they call it signature which is the same thing".
-Generally, a language uses vocabulary to construct sentences, and the set of those sentences, is the language.} (see section \ref{sec:evaluation})
-As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to describe constraints of all possible constraint types.
-\tb{use RDF-CV / not: expressible in RDF-CV / RDF-CV is a vocabulary, not a language}
+\textbf{\emph{DL Expressivity}:}
+The \emph{RDF-CV} allows to describe 
+constraints which are \emph{expressible in DL} (70\%) and which are \emph{not expressible in DL} (30\%). 
+In case a constraint type is \emph{expressible in DL}, we determined which \emph{DL} constructs are needed to express the constraint type.
+In addition, we mapped constraints of each constraint type to \emph{generic constraints} conforming to the \emph{RDF-CV} \cite{BoschNolleAcarEckert2015}.
+This way, we show that constraints of each constraint type are representable as \emph{generic constraints} and therefore can be described generically by means of the \emph{RDF-CV}.
+\textbf{\emph{Complexity}:}
+\emph{Simple constraints} (2/3) denotes the set of atomic constraints. 
+%which can be instantiated from almost 2/3 of the constraint types.
+\emph{Complex constraints} (1/4) is the set of constraints which are created out of \emph{simple} and/or other \emph{complex constraints}.
+%and which are instances of 1/4 of the constraint types.
+In case \emph{complex constraints} are expressible in \emph{DL}, 
+\emph{DL} statements representing \emph{complex constraints} contain \emph{DL} statements standing for atomic and/or composed constraints. 
+Nearly 15\% of the \emph{complex constraints}, however, can be formulated as \emph{simple constraints} when using them in terms of syntactic sugar. 
+\textbf{\emph{Context}:}
+\emph{Simple constraints} are applied on properties (\emph{property constraints}, 2/3),
+on classes (\emph{class constraints}, 1/5), or
+on properties and classes (\emph{property and class constraints}, 1/10).
+%2/3 of all constraint types are types of \emph{property constraints}, 
+%1/5 of \emph{class constraints}, and 
+%approx. 10\% of \emph{property and class constraints}.
+\emph{Simple constraints} must hold for individuals of their \emph{context classes}.
+As \emph{context classes} of \emph{simple constraints} are reused within \emph{complex constraints},
+it does not make sense to have terms standing for \emph{simple} and \emph{complex constraints} within the \emph{RDF-CV}. 
+As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to generically describe constraints of all constraint types.
+%\tb{use RDF-CV / not: expressible in RDF-CV / RDF-CV is a vocabulary, not a language}
+Altogether, instances of the most of the constraint types are \emph{simple constraints on properties} which are \emph{expressible in DL}. 
+%Thus, the majority of constraint types are directly and relatively easy formulated in form of \emph{simple constraints} which can be mapped to equivalent \emph{DL} constructs.
 
@@
 
-\subsubsection{\emph{Simple Constraints} (Expressible in \emph{DL})}
-
-Sub-classes of \emph{simple constraints} are \emph{property constraints} and \emph{class constraints} (see the \emph{RDF-CV} implementation model in figure \ref{fig:RDF-CV-implementation-model}). 
-For both \emph{property} and \emph{class constraints} a \emph{context class}, a list of \emph{classes}, the \emph{constraining element}, and the \emph{constraining value} can be stated. 
-Lists of \emph{left} and \emph{right properties} can only be specified for \emph{property constraints}.
-
+The implementation model of the \emph{RDF-CV} (see Figure \ref{fig:RDF-CV-implementation-model}) shows that
+both \emph{property constraints} and \emph{class constraints} are \emph{simple constraints}. 
+%For both \emph{property} and \emph{class constraints} a \emph{context class}, a list of \emph{classes}, the \emph{constraining element}, and the \emph{constraining value} can be stated. 
+%Lists of \emph{left} and \emph{right properties} can only be specified for \emph{property constraints}.
 \begin{figure}
 	\centering
-		\includegraphics[width=0.70\textwidth]{images/RDF-CV-implementation-model.png}
-	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} - implementation model}
+		\includegraphics[width=0.60\textwidth]{images/RDF-CV-implementation-model.png}
+	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} - Implementation Model}
 	\label{fig:RDF-CV-implementation-model}
 \end{figure}
-
-A \emph{simple constraint} holds for all individuals of a \emph{context class}.
-Consider, e.g., the following \emph{minimum qualified cardinality restriction} on the object property \emph{author}, which restricts \emph{publications} to have at least one \emph{author} which is a \emph{person}:
-\begin{DL}
-$Publication \sqsubseteq \geq1 author . Person $
-\end{DL}
-The cardinality restriction is a constraint on the property \emph{author} and is therefore classified as a \emph{property constraint} which holds for all individuals of the class \emph{Publication} (see Table \ref{tab:property-constraint-cardinality-restriction} for the mapping to \emph{RDF-CV}):
-
-\begin{table}
+A \emph{simple constraint} holds for all individuals of their \emph{context class}.
+The \emph{minimum qualified cardinality restriction} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person,}}
+which restricts \emph{publications} to have at least one \emph{author} which must be a \emph{person},
+is an example of a \emph{property constraint} on \emph{author}
+which holds for all individuals of the class \emph{Publication}.
+Table \ref{tab:property-constraint-cardinality-restriction} displays the mapping to the \emph{RDF-CV}:
+\begin{table}[H]
   \scriptsize
@@
   \vspace{0cm}
-	\caption{Property Constraint - Cardinality Restriction}
+	\caption{Property Constraint - Minimum Qualified Cardinality Restriction}
 	\label{tab:property-constraint-cardinality-restriction}
@@
 		\begin{tabular}{l|l|l|l|l|l|l}
-      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
       \hline
@@
 
-The \emph{constraining element} indicates the actual type of constraint like \emph{DL} concept and role constructors, (in)equality, and further keywords for constraint types which cannot be expressed in \emph{DL} (e.g.
-regular expressions and constraining facets).
-In some cases, a constraint is only complete when in addition to the \emph{constraining element} a \emph{constraining value} is stated.
-The cardinality restriction 
-{\small\ms{$\geq$1 author.Person}}, e.g., 
-constructs an anonymous class of all individuals having at least one \emph{author} relationship to \emph{persons}.
-The \emph{constraining element} of this \emph{property constraint} is the \emph{DL} at-least restriction \emph{$\geq$} and the \emph{constraining value} is \emph{1}.
-\emph{Simple constraints} may refer to a list of \emph{classes}.
-The qualified cardinality restriction above, e.g., refers to the class \emph{Person}, 
-i.e. restricts the objects of the property \emph{author} to be of the class \emph{Person}.
-
+The \emph{constraining element} indicates the actual type of constraint like \emph{DL} concept and role constructors, (in)equality, and further keywords for constraint types which cannot be expressed in \emph{DL} (e.g., regular expressions and constraining facets).
+In some cases, a constraint is only complete when a \emph{constraining value} is stated in addition to the \emph{constraining element}.
+\emph{Simple constraints} may also refer to a list of \emph{classes}.
+The \emph{constraining element} of the \emph{property constraint} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person},} e.g.,  is the \emph{DL at-least restriction} \emph{$\geq$}, the \emph{constraining value} is \emph{1}, and
+the list of \emph{classes} includes \emph{Person} which restricts the objects of the property \emph{author} to be of the class \emph{Person}.
 For \emph{property constraints}, \emph{left} and \emph{right property lists} are specified.
-The assignment of properties to these lists happens relative to the \emph{constraining element} - which may be an operator (e.g., $\sqsubseteq$ in case of \emph{object property paths}).
-\emph{Object Property Paths} (\emph{R-55}; also called \emph{complex role inclusion axioms} in \emph{DL})
-express that, if an individual \emph{x} is connected by a sequence of object properties with an individual \emph{y}, 
+The assignment of properties to these lists happens relative to the \emph{constraining element} 
+which may be an operator like $\sqsubseteq$.
+\emph{Object Property Paths} (\emph{R-55})
+ensure that if an individual \emph{x} is connected by a sequence of object properties with an individual \emph{y}, 
 then \emph{x} is also related to \emph{y} by a particular object property. 
-As \emph{Stephen-Hawking} is the \emph{author} of the book \emph{A-Brief-History-Of-Time} {\small\ms{(authorOf(Stephen-Hawking, A-Brief-History-Of-Time))}} whose \emph{genre} is \emph{Popular-Science} {\small\ms{(genre(A-Brief-History-Of-Time, Popular-Science)),}}
-the following \emph{object property path} infers that \emph{Stephen-Hawking} is an \emph{author} of the \emph{genre} \emph{Popular-Science} {\small\ms{(authorOfGenre(Stephen-Hawking, Popular-Science)):}}
-\begin{DL}
-authorOf $\circ$ genre $\sqsubseteq$ authorOfGenre 
-\end{DL}
-Thus, when mapped to the \emph{RDF-CV} (see Table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are on the left side of the \emph{constraining element} \emph{$\sqsubseteq$},
-and the property \emph{authorOfGenre} is on the right side:
-
-\begin{table}
+As \emph{Stephen-Hawking} is the \emph{author} of the book \emph{A-Brief-History-Of-Time} 
+%{\small\ms{(authorOf(Stephen-Hawking, A-Brief-History-Of-Time))}} 
+whose \emph{genre} is \emph{Popular-Science}, 
+%{\small\ms{(genre(A-Brief-History-Of-Time, Popular-Science)),}}
+the \emph{object property path} {\small\ms{authorOf $\circ$ genre $\sqsubseteq$ authorOfGenre}} infers that \emph{Stephen-Hawking} is an \emph{author} of the \emph{genre} \emph{Popular-Science}. 
+%{\small\ms{(authorOfGenre(Stephen-Hawking, Popular-Science))}.}
+Thus, when mapped to the \emph{RDF-CV} (Table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are on the left side of the \emph{constraining element} \emph{$\sqsubseteq$}
+and the property \emph{authorOfGenre} is on the right side.
+As this \emph{property constraint} holds all individuals, the \emph{context class} is the \emph{DL top concept} $\top$ which stands for the super-class of all classes.
+\begin{table}[H]
   \scriptsize
@@
 
-\subsubsection{\emph{Simple Constraints} (Not Expressible in \emph{DL})}
-
-There are \emph{simple constraints} which cannot be expressed in \emph{DL} such as \emph{literal pattern matching}, \emph{literal value comparison}, \emph{literal ranges}, \emph{default values}, and \emph{language tag cardinality} \cite{BoschNolleAcarEckert2015}.
-% maybe additional constraint default values:
-% ear shape of races, e.g. vulcans / teeth color
-% mathematical operations
-
-{\em Literal pattern matching} (\emph{R-44}) restricts literals to match given patterns.
-The following \emph{universal restriction}, e.g., ensures that \emph{books} can only have valid \emph{ISBN} identifiers, 
-i.e., strings that match a given regular expression:
-\begin{DL}
-\ms{Book $\sqsubseteq$ $\forall$ identifier.ISBN} 
-\end{DL}
-Even though, the restriction of the datatype \emph{ISBN} cannot be expressed in \emph{DL}, \emph{OWL 2 DL} can be used to express the \emph{literal pattern matching} constraint:
-
-\begin{ex}
-ISBN a RDFS:Datatype ; owl:equivalentClass [ a RDFS:Datatype ;
-    owl:onDatatype xsd:string ; 
-    owl:withRestrictions ([ xsd:pattern "^\d{9}[\d|X]" ])] .
-\end{ex} 
-The first OWL 2 axiom explicitly declares {\em ISBN} to be a datatype.
+There are \emph{simple constraints} which are not expressible in \emph{DL} but can still be described using the \emph{RDF-CV} 
+such as constraints of the type \emph{literal pattern matching} (\emph{R-44}) which restrict literals to match given patterns.
+The \emph{universal restriction} {\small\ms{Book $\sqsubseteq$ $\forall$ identifier.ISBN}} ensures that \emph{books} can only have valid \emph{ISBN} identifiers, 
+i.e., strings that match a given regular expression.
+%Even though, the restriction of the datatype \emph{ISBN} cannot be expressed in \emph{DL}, \emph{OWL 2 DL} can be used to express the \emph{literal pattern matching} constraint:
+%\begin{ex}
+%ISBN a RDFS:Datatype ; owl:equivalentClass [ a RDFS:Datatype ;
+    %owl:onDatatype xsd:string ; 
+    %owl:withRestrictions ([ xsd:pattern "^\d{9}[\d|X]" ])] .
+%\end{ex} 
+%The first OWL 2 axiom explicitly declares {\em ISBN} to be a datatype.
 %\er{Why start from second and then first?
 Also better we say "owl axiom" when we talk axiom of owl, to prevent ambiguity.}\tb{resolved}
-The second OWL 2 axiom defines {\em ISBN} as an abbreviation for a datatype restriction on {\em xsd:string}. 
-The datatype {\em ISBN} can be used just like any other datatype like in the \emph{universal restriction} above.
+%The second OWL 2 axiom defines {\em ISBN} as an abbreviation for a datatype restriction on {\em xsd:string}. 
+%The datatype {\em ISBN} can be used just like any other datatype like in the \emph{universal restriction} above.
 %There are multiple use cases associated with the requirement to match literals according to given patterns (\emph{Literal Pattern Matching}\footnote{Corresponds to \emph{R-44-PATTERN-MATCHING-ON-RDF-LITERALS}}).
@@
 %The datatype \ms{RegistryNumber} can be used just like any other datatype like in the universal restriction above.
-The \emph{literal pattern matching} constraint validates \emph{ISBN} literals according to the regular expression causing constraint violations for triples which do not not match. 
+%The \emph{literal pattern matching} constraint validates \emph{ISBN} literals according to the regular expression causing constraint violations for triples which do not not match. 
 %\ms{Janeway commandsEnterprise Voyager} and \ms{Voyager registryNumber "NCC-74656"\textasciicircum{}\textasciicircum{}RegistryNumber}, 
 %but not for the triples \ms{Picard commandsEnterprise Enterprise} and \ms{Enterprise registryNumber "NCC-1701-E"\textasciicircum{}\textasciicircum{}RegistryNumber}.
-In Table \ref{tab:simple-constraint-not-expressible-in-dl)}, the \emph{simple constraint} (\emph{literal pattern matching}) and the \emph{complex constraint} (\emph{universal restriction}) are mapped to the \emph{RDF-CV}:
-
+Table \ref{tab:simple-constraint-not-expressible-in-dl)} presents 
+how the \emph{literal pattern matching} \emph{simple constraint} which is not expressible in \emph{DL} and 
+how the \emph{universal restriction} \emph{complex constraint} which is expressible in \emph{DL} are mapped to the \emph{RDF-CV}.
+Thereby, the \emph{context class} \emph{ISBN}, whose instances must satisfy the \emph{simple constraint}, 
+is reused within the list of \emph{classes} the \emph{complex constraint} refers to.
+The \emph{literal pattern matching} constraint type introduces the new \emph{constraining element} \emph{regex}.
+The validation of each \emph{constraining element}, so for \emph{regex}, has to be implemented only once.
+%In general, validation has to be implemented once for each \emph{generic constraint type} which is not expressible in \emph{DL}. 
 %\begin{gcotable}
@@
 %\end{gcotable}
-
-\begin{table}
+\begin{table}[H]
   \scriptsize
@@
 		\begin{tabular}{l|l|l|l|l|l|l}
-      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
       \hline
+      class & ISBN & - & - & xsd:string & regex & '\string^\text{$\backslash$d$\{9\}$[$\backslash$d$\mid$X]}\$' \\
       property & Book & identifier & - & ISBN & $\forall$ & - \\
-      class & ISBN & - & - & xsd:string & regex & '\string^\text{$\backslash$d$\{9\}$[$\backslash$d$\mid$X]}\$' \\
 		\end{tabular}
 \end{table} %\tb{Erman, can you please format the regular expression in the table above correctly?}
-The \emph{literal pattern matching} constraint type introduces the new \emph{constraining element} \emph{regex},
-for which a validation mechanism has to be implemented.
-Validation has to be implemented once for each \emph{generic constraint type} which is not expressible in \emph{DL}.
 
@@
 
-\begin{table}
+\begin{table}[H]
   \scriptsize
@@
 
-\section{Evaluation}
-\label{sec:evaluation}
-
-The appendix of this paper contains mappings to \emph{DL} to logically underpin each constraint type and to determine which \emph{DL} constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
-If a constraint type was expressible in \emph{DL}, we added the mapping to \emph{DL} and to the \emph{generic constraint} conforming to the \emph{RDF-CV}.
-In contrast, if a constraint type was not expressible in \emph{DL}, we only added the mapping to the \emph{generic constraint}.
-This way, we show that each constraint type can be mapped to a \emph{generic constraint} and therefore be represented generically by means of the \emph{RDF-CV}.
-Table \ref{tab:evaluation} displays the classification of constraint types according to the dimensions \emph{context}, \emph{complexity}, and \emph{DL expressivity}:
+%\section{Evaluation}
+%\label{sec:evaluation}
 
@@
 
-\begin{table}
-  %\scriptsize
-  %\sffamily
-  \vspace{0cm}
-	\caption{Evaluation}
-	\label{tab:evaluation}
-	\centering
-		\begin{tabular}{l|c|c}
-      \textbf{Classes of Constraint Types} & \textbf{\#} & \textbf{\%} \\
-      \hline
-%\textbf{\emph{Context}} & & \\
-\emph{Property Constraints} & 48 & 64.86 \\
-\emph{Class Constraints} & 17 & 22.96 \\
-\emph{Property and Class Constraints} & 9 & 12.16 \\
-\hline
-%\textbf{\emph{Complexity}} & & \\
-\emph{Simple Constraints} & 46 & 62.16 \\
-\emph{Simple Constraints} (Syntactic Sugar) & 10 & 13.51 \\
-\emph{Complex Constraints} & 18 & 24.32 \\
-\hline
-%\textbf{\emph{DL Expressivity}} & & \\
-\emph{DL Expressible} & 51 & 68.92 \\
-\emph{DL Not Expressible} & 23 & 31.08 \\
-\hline
-Total & 74 & 100 \\
-		\end{tabular}
-\end{table}
+%\begin{table}[H]
+  %%\scriptsize
+  %%\sffamily
+  %\vspace{0cm}
+	%\caption{Evaluation}
+	%\label{tab:evaluation}
+	%\centering
+		%\begin{tabular}{l|c|c}
+      %\textbf{Classes of Constraint Types} & \textbf{\#} & \textbf{\%} \\
+      %\hline
+%%\textbf{\emph{Context}} & & \\
+%\emph{Property Constraints} & 48 & 64.86 \\
+%\emph{Class Constraints} & 17 & 22.96 \\
+%\emph{Property and Class Constraints} & 9 & 12.16 \\
+%\hline
+%%\textbf{\emph{Complexity}} & & \\
+%\emph{Simple Constraints} & 46 & 62.16 \\
+%\emph{Simple Constraints} (Syntactic Sugar) & 10 & 13.51 \\
+%\emph{Complex Constraints} & 18 & 24.32 \\
+%\hline
+%%\textbf{\emph{DL Expressivity}} & & \\
+%\emph{DL Expressible} & 51 & 68.92 \\
+%\emph{DL Not Expressible} & 23 & 31.08 \\
+%\hline
+%Total & 74 & 100 \\
+		%\end{tabular}
+%\end{table}
 
@@
 
-Constraint types can be classified as \emph{property constraints} and \emph{class constraints} (\emph{context}).
-Two thirds of the total amount of constraint types are \emph{property constraints} (e.g., \emph{R-86: existential quantification} and \emph{R-91: universal quantification}), one fifth are \emph{class constraints} (e.g., \emph{R-30/37: allowed values} for objects/literals), and approx.
-10\% are composed of both \emph{property and class constraints} (e.g., \emph{R-13: context-specific exclusive or of property groups}).
-According to the dimesion \emph{complexity}, constraint types can be either atomic (\emph{simple constraints}) or complex (\emph{complex constraints}), i.e., created out of \emph{simple} and/or \emph{complex constraints}.
-Almost two thirds of the constraint types are \emph{simple constraints} (e.g., \emph{R-55: object property paths}), a quarter are \emph{complex constraints} (e.g., \emph{R-45: ranges of literal values}), and
-nearly 15 percent are \emph{complex constraints} which can be formulated as \emph{simple constraints} when used in terms of syntactic sugar (e.g., \emph{R-81/75/82/76/80/74: (un)qualified cardinality restrictions}).
-Constraint types can either be \emph{expressible in DL} or \emph{not} (\emph{DL expressivity}).
-The majority - nearly 70\% - of the overall constraint types are expressible in \emph{DL}.	
-\emph{Literal pattern matching} (\emph{R-44}) is an example of a constraint type which cannot be represented in \emph{DL}, but can also be represented generically by means of the \emph{RDF-CV}.
-Altogether, most of the constraint types are \emph{simple constraints on properties} which are \emph{expressible in DL}. 
-Thus, the majority of constraint types are directly and relatively easy formulated in form of \emph{simple constraints} which can be mapped to equivalent \emph{DL} constructs.
-
 \section{Related Work}

### 2015-05-27 paper/paper 2/dc-2015.tex
introduction

@@
 that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
-This constraint can either be represented generically by \emph{description logics (DL)} {\small\ms{(Publication $\sqsubseteq$ $\geq$1 author.Person)}} or specifically by multiple domain-specific constraint languages:
+This constraint can either be represented generically (\emph{generic constraints}) by \emph{description logics (DL)} {\small\ms{(Publication $\sqsubseteq$ $\geq$1 author.Person)}} or specifically (\emph{specific constraints}) by multiple domain-specific constraint languages:
 
 \begin{ex}[commandchars=\\\{\}]
-\textit{OWL 2:}
-Publication
-    a owl:Restriction ;
+\textit{OWL 2:} Publication a owl:Restriction ;
           owl:minQualifiedCardinality 1 ;
@@
 
-\textit{ShEx:}
-Publication \{ author @Person\{1, \} \}
-
-\textit{ReSh:}
-Publication a rs:ResourceShape ; rs:property [
-    rs:name "author" ; rs:propertyDefinition author ;
+\textit{ShEx:} Publication \{ author @Person\{1, \} \}
+
+\textit{ReSh:} Publication a rs:ResourceShape ; rs:property [
+          rs:propertyDefinition author ;
           rs:valueShape Person ;
@@
 
-\textit{DSP:}
-[   a dsp:DescriptionTemplate ; 
-    dsp:resourceClass Publication ; 
-    dsp:statementTemplate [ a dsp:NonLiteralStatementTemplate ;
+\textit{DSP:} [ dsp:resourceClass Publication ; dsp:statementTemplate [ 
           dsp:minOccur 1 ; dsp:maxOccur "infinity" ; 
           dsp:property author ; 
-        dsp:nonLiteralConstraint [ a dsp:NonLiteralConstraint ;
-            dsp:valueClass Person ] ] ] .
+          dsp:nonLiteralConstraint [ dsp:valueClass Person ] ] ] .
+
+\textit{SPIN:} CONSTRUCT \{ [ a spin:ConstraintViolation ... . ] \} WHERE \{ 
+          ?this ?p ?o ; a ?C .
+          BIND ( \textit{qualifiedCardinality}( ?this, ?p, ?C ) AS ?c ) .
+          BIND( STRDT ( STR ( ?c ), xsd:nonNegativeInteger ) AS ?cardinality ) .
+          FILTER ( ?cardinality < ?minimumCardinality ) . \}
+
+\textit{SPIN function qualifiedCardinality:}										
+SELECT ( COUNT ( ?arg1 ) AS ?c ) WHERE \{ ?arg1 ?arg2 ?o . ?o a ?arg3 . \}
 \end{ex}
@@
 For this reason, the appendix of this paper contains mappings to \emph{DL} to determine which \emph{DL} constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
-
 As every \emph{publication} must have at least one \emph{author} which must be a \emph{person} 
-and since the book \emph{The-Lord-Of-The-Rings} is a \emph{publication} {\small\ms{(rdf:type(The-Lord-Of-The-Rings, Publication)),}} 
-the book must have at least one \emph{author} relationship to a \emph{person}.
+and since the book \emph{The-Lord-Of-The-Rings} is a \emph{publication}, 
+%{\small\ms{(rdf:type(The-Lord-Of-The-Rings, Publication)),}} 
+it must have at least one \emph{author} relationship to a \emph{person}.
 The constraint is violated either (1) if
-\emph{The-Lord-Of-The-Rings} does not have any \emph{author} relationship, 
-or (2) if the book has an \emph{author} which is not a \emph{person}
-{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)},} {\small\ms{rdf:type(Tolkien, Hobbit)),}} 
-or (3) if the book has an \emph{author} whose class is unknown
-{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)).}}
-In contrast, the book is a valid \emph{publication}, if it is connected to a \emph{person} via the property \emph{author}
-{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Person)).}}
-
+the book does not have any \emph{author} relationship, 
+or (2) if it has an \emph{author} which is not a \emph{person},
+%{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)},} {\small\ms{rdf:type(Tolkien, Hobbit)),}} 
+or (3) if it has an \emph{author} whose class is unknown.
+%{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)).}}
+In contrast, the book is a valid \emph{publication}, if it is connected to a \emph{person} via the property \emph{author}.
+%{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Person)).}}
+
+The main contributions of this paper are:
+(1) We provide a basic terminology and classification system for RDF constraints (Section \ref{sec:vocabulary}).
+(2) As current high-level constraint languages do not support all constraint types, 
+we developed a vocabulary to describe constraints of any RDF constraint type generically (Section \ref{sec:vocabulary}).
+(3) We show how to enhance the interoperability of constraints expressed by different constraint languages by using the proposed vocabulary as an intermediate generic representation which enables transformations between semantically equivalent constraints of the same constraint type (Section \ref{sec:transformations}).
+(4) We explain how arbitrary constraint languages may reuse validation implementations which are provided once for each constraint type (Section \ref{sec:validation}).
+
+\subsection{How to Improve the Interoperability of RDF Constraints}
+\label{sec:transformations}
+
+RDF data providers have to ensure high data quality and therefore 
+that their data conforms to constraints which may be part of contracts between data providers and consumers.
 As there is no standard way to formulate constraints, 
-semantically equivalent \emph{minimum qualified cardinality restrictions} may be represented by multiple languages - each of them having different syntax and semantics.
-This causes confusion,
-weakens the common understanding between several parties about the meaning of particular constraints, and
-raises the question on how to ensure high data quality. 
-Therefore, when choosing a language, say \ms{$\alpha$}, to express a constraint of an arbitrary constraint type, 
-it should be possible to transform the constraint into a semantically equivalent constraint expressed by another constraint language \ms{$\beta$} (see Section \ref{sec:transformations}). 
-This is important in order to enhance the interoperability of constraint languages and to resolve misunderstandings and ambiguities in the communication of RDF data producers and consumers 
-since automatically performed constraint transformations avoid the necessity to understand several languages.
+semantically equivalent \emph{specific constraints}, so the \emph{minimum qualified cardinality restriction}, may be represented by a variety of languages - each of them having different syntax and semantics.
+This causes confusion and weakens the common understanding between several parties about the meaning of particular constraints.
+We propose transformations between semantically equivalent \emph{specific constraints}
+(1) to avoid the necessity to understand several languages,
+(2) to resolve misunderstandings in the communication of RDF data producers and consumers, and
+(3) to enhance the interoperability of constraint languages.
+
+We suggest to transform a \emph{specific constraint} (\emph{$sc_{\alpha}$}) of any constraint type expressed by language \emph{$\alpha$} into a semantically equivalent \emph{specific constraint} (\emph{$sc_{\beta}$}) of the same constraint type represented by any other language \emph{$\beta$}
+by using the developed vocabulary to intermediately represent constraints in a generic way. 
+%to enable these transformations.
+By defining mappings between equivalent \emph{specific constraints} and the corresponding \emph{generic constraint} (\emph{gc}) we are able to convert them automatically: 
+{\small\ms{$ gc = m_1(sc_{\alpha}) = m_2(sc_{\beta}) $}}.
+Thereby, we do not need to define mappings between each pair of semantically equivalent \emph{specific constraints}.
+Let's assume we are able to express constraints of the \emph{minimum qualified cardinality restrictions} constraint type by 10 languages.
+Without an intermediate generic representation, we would have to define for each constraint type one mapping between each pair of \emph{specific constraints} expressed by \emph{n} languages
+- that are \emph{\( {n \choose 2} \)} mappings (\emph{\( {10 \choose 2} \)} = 45 mappings).
+With an intermediate generic representation, on the other side, we only need to define for each constraint type \emph{n} mappings 
+%(1 mapping for each \emph{specific constraint}) 
+from \emph{n} \emph{specific constraints} to the corresponding \emph{generic constraint} (10 mappings).
+%Let's assume we are able to express a particular constraint type by 5/6/7/8/9/10 constraint languages.
+%Without the intermediate \emph{generic constraint}, we would have to define for each constraint type \emph{1} mapping for each pair of \emph{specific constraints} (expressed by different constraint languages)
+%that are \emph{\( {n \choose 2} \)} mappings (10/15/21/28/36/45 mappings).
+%With an intermediate \emph{generic constraint}, however, we only need to define for each constraint type \emph{n} mappings (1 mapping for each \emph{specific constraint}) from \emph{n} \emph{specific constraints} to the corresponding \emph{generic constraint} (5/6/7/8/9/10 mappings).
+For the \emph{minimum qualified cardinality restriction}, one mapping (\emph{$m_1(sc_{OWL 2})$}, \emph{$m_2(sc_{ShEx})$}, \emph{$m_3(sc_{ReSh})$}, \emph{$m_4(sc_{DSP})$},...) is defined for each \emph{specific constraint} (\emph{$sc_{OWL 2}$}, \emph{$sc_{ShEx}$}, \emph{$sc_{ReSh}$}, \emph{$sc_{DSP}$},...) to the corresponding \emph{generic constraint} (\emph{gc}).
+
+\subsection{How to Provide the Validation of RDF Constraints Out-Of-The-Box}
+\label{sec:validation}
 
@@
 (2) if we transform semantically equivalent specifically expressed constraints into generically expressed constraints.
+
+-----
+
+SPARQL is generally seen as the method of choice to validate RDF data according to certain constraints, although, it is not ideal for their formulation. 
+In contrast, OWL 2, DSP, ReSh, and ShEx constraints are comparatively easy to understand. 
+We use SPIN as basis to define a
+validation environment\footnote{Online demo available at \url{http://purl.org/net/rdfval-demo}, source code available at: \url{https://github.com/boschthomas/rdf-validator}\label{rdf-validator}} in which the validation of any constraint language can be implemented by representing them in SPARQL.
+The only limitation is that constraint languages must be represented in RDF.
+The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations \cite{BoschEckert2014-2}.
+This way, we are able to offer RDF data validation according to all \emph{specific constraints} (expressed by any constraint language) by defining mappings from each \emph{specific constraint} to \emph{SPIN}.
+We already specified mappings to \emph{SPIN} for all \emph{OWL 2} and \emph{DSP}\footnote{SPIN mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} constructs and for some \emph{ReSh} and \emph{ShEx} constructs.
+As constraint languages differ in syntax and semantics it is rather difficult to ensure that semantically equivalent \emph{specific constraints} always lead to identical validation results.
+
+We do not have to map each \emph{specific constraint} to SPIN and we get identical validation results for semantically equivalent \emph{specific constraints} (expressed by different constraint languages),
+(1) if we map semantically equivalent \emph{specific constraints} to the corresponding \emph{generic constraint} and 
+(2) if we map the \emph{generic constraint} to SPIN.
+As a consequence, we only have to define one SPIN mapping for each constraint type corresponding to an RDF validation requirement.
+\textcolor{red}{19} of the overall 81 identified constraint types can be expressed by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
+This means that there must be 76 (four for each constraint type) implementations to validate RDF data according to 76 \emph{specific constraints} - instead of only 19 implementations (one for each \emph{generic constraint}) leading to identical validation results.
+
+Within the \emph{RDF Validator}, we define one SPIN construct template for each \emph{generic constraint} and therefore constraint type.
+A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples (\emph{spin:ConstraintViolation}) indicating the subject (\emph{spin:violationRoot}) and the properties (\emph{spin:violationPath}) causing constraint violations, and the reason why constraint violations have been raised (\emph{rdfs:label}).
+A SPIN construct template creates constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
+
+\begin{DL}
+Publication $\equiv$ $\forall$ author.Person
+\end{DL}
+
+According to the \emph{universal quantification} (\emph{R-91}) above, \emph{authors} of \emph{publications} must be \emph{persons}.
+The SPARQL CONSTRUCT query for the constraint type \emph{universal quantification} is shown below:
+
+\begin{ex}
+CONSTRUCT {
+    [   a spin:ConstraintViolation ; spin:violationRoot ?subject ;
+        rdfs:label ?violationMessage ; spin:violationPath ?lp1 . ] }
+WHERE {	  
+    [   a gclo:PropertyConstraint ;
+        gclo:contextClass ?cc ;
+        gclo:leftProperties ( ?lp1 ) ;
+        gclo:classes ( ?c1 ) ;
+        gclo:constrainingElement "universal quantification" ] .
+    ?subject a ?cc .
+    ?subject ?lp1 ?o .
+    FILTER NOT EXISTS { ?o a ?c1 } . }
+\end{ex}
+
+We provide a mapping from the \emph{RDF-CV} to SPIN\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}} 
+in order to automatically validate RDF data complying with each type of \emph{generic constraint} (\emph{simple}, \emph{complex}, \emph{property}, and \emph{class constraints}).
 
@@
 %(2) RDF practitioners thinking of how to provide aligned implementations for the validation of both existing an newly developed constraint languages.
-The main contributions of this paper are:
-(1) We provide a basic terminology and classification system for RDF constraints (Section \ref{sec:vocabulary}).
-(2) We developed a vocabulary to describe constraints of any RDF constraint type generically (Section \ref{sec:vocabulary}).
-(3) We show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful (Section \ref{sec:transformations}).
-(4) We explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages (Section \ref{sec:validation}).
+
 %(if the validation is implemented once for the corresponding \emph{generic constraint type} to which the \emph{specific constraint type} is mapped)
@@
 \emph{DL} statements representing \emph{complex constraints} contain \emph{DL} statements standing for atomic and/or composed constraints. 
-Nearly 15\% of the \emph{complex constraints}, however, can be formulated as \emph{simple constraints} when using them in terms of syntactic sugar. 
+The constraints of almost 15\% of the constraint types are \emph{complex constraints}
+which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
 \textbf{\emph{Context}:}
@@
 
-\emph{Complex constraints} are composed out of \emph{simple constraints} and/or \emph{complex constraints}.
-\emph{Exclusive or} is a logical operation that outputs true whenever both inputs differ (one is true, the other is false).
-The \emph{complex constraint} \emph{context-specific exclusive or of property groups} (\emph{R-13})
-restricts individuals of given classes to have properties of only one of multiple mutually exclusive property groups.
-\emph{Publications} are either identified by an \emph{ISBN} and a \emph{title} (for books) or by an \emph{ISSN} and a \emph{title} (for periodical \emph{publications}), but it should not be possible to assign both identifiers to a given \emph{publication}, which can be expressed in \emph{ShEx} as follows:
+%\emph{Complex constraints} are composed out of \emph{simple constraints} and/or \emph{complex constraints}.
+\emph{Context-specific exclusive or of property groups} (\emph{R-13}) \emph{complex constraints}
+restrict individuals of given classes to have all properties of exactly one of multiple mutually exclusive property groups.
+\emph{Publications}, e.g., are either identified by an \emph{ISBN} and a \emph{title} (for books) or by an \emph{ISSN} and a \emph{title} (for periodical \emph{publications}), but it should not be possible to assign both identifiers to a given \emph{publication}.
+As the \emph{The-Great-Gatsby} is a \emph{publication} with an \emph{ISBN} and a \emph{title} without an \emph{ISSN}, 
+\emph{The-Great-Gatsby} is considered as a valid \emph{publication}.
+This \emph{complex constraint} is expressible specifically by \emph{ShEx} and generically by \emph{DL} (and can therefore be mapped to the \emph{RDF-CV} \cite{BoschEckert2015-2}):
 
@@
 
-\begin{ex}
-Publication { 
-    ( isbn string , title string ) |
-    ( issn string , title string ) }
+\begin{ex}[commandchars=\\\{\}]
+\textit{ShEx:} Publication { ( isbn string , title string ) | ( issn string , title string ) }
 \end{ex}
@@
 
-As the \emph{The-Great-Gatsby} is a \emph{publication} {\small\ms{(rdf:type(The-Great-Gatsby, Publication))}} having an \emph{ISBN} number {\small\ms{(isbn(The-Great-Gatsby, '978-0241965672'))}} and a \emph{title} {\small\ms{(title(The-Great-Gatsby, 'The Great Gatsby'))}} and not an additional \emph{ISSN} identifier, the \emph{The-Great-Gatsby} is a valid \emph{publication}.
 %\begin{DL}
@@
 %\end{DL}
-The \emph{complex constraint} is mapped to the \emph{RDF-CV} (see Table \ref{tab:complex-constraints}) and expressed in \emph{DL} as follows:
+%The \emph{complex constraint} is mapped to the \emph{RDF-CV} (see Table \ref{tab:complex-constraints}) and expressed in \emph{DL} as follows:
 
@@
 \begin{DL}
-Publication $\sqsubseteq$ ($\neg$E $\sqcap$ F) $\sqcup$ (E $\sqcap$ $\neg$F) \\ 
-E $\equiv$ A $\sqcap$ B \\
-F $\equiv$ C $\sqcap$ D \\
-A $\sqsubseteq$ $\geq$ 1 isbn.string $\sqcap$ $\leq$ 1 isbn.string \\
-B $\sqsubseteq$ $\geq$ 1 title.string $\sqcap$ $\leq$ 1 title.string \\
-C $\sqsubseteq$ $\geq$ 1 issn.string $\sqcap$ $\leq$ 1 issn.string \\
-D $\sqsubseteq$ $\geq$ 1 title.string $\sqcap$ $\leq$ 1 title.string \\
+\textbf{Publication $\sqsubseteq$ ($\neg$E $\sqcap$ F) $\sqcup$ (E $\sqcap$ $\neg$F)} , E $\equiv$ A $\sqcap$ B , F $\equiv$ C $\sqcap$ D \\
+A $\sqsubseteq$ $\geq$ 1 isbn.string $\sqcap$ $\leq$ 1 isbn.string , B $\sqsubseteq$ $\geq$ 1 title.string $\sqcap$ $\leq$ 1 title.string \\
+C $\sqsubseteq$ $\geq$ 1 issn.string $\sqcap$ $\leq$ 1 issn.string , D $\sqsubseteq$ $\geq$ 1 title.string $\sqcap$ $\leq$ 1 title.string \\
 \end{DL}
@@
 
-\begin{table}[H]
-  \scriptsize
-  \sffamily
-  \vspace{0cm}
-	\caption{Complex Constraints}
-	\label{tab:complex-constraints}
-	\centering
-		\begin{tabular}{l|l|l|l|l|l|l}
-      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
-      \hline
-class & Publication & - & - & $\neg$E $\sqcap$ F, E $\sqcap$ $\neg$F & $\sqcup$ & - \\
-class & $\neg$E $\sqcap$ F & - & - & $\neg$E, F & $\sqcap$ & - \\
-class & E $\sqcap$ $\neg$F & - & - & E, $\neg$F & $\sqcap$ & - \\
-class & $\neg$E & - & - & E & $\neg$ & - \\
-class & E & - & - & A, B & $\sqcap$ & - \\
-class & $\neg$F & - & - & F & $\neg$ & - \\
-class & F & - & - & C, D & $\sqcap$ & - \\
-class & A & - & - & A1, A2 & $\sqcap$ & - \\
-property & A1 & isbn & - & string & $\geq$ & 1 \\
-property & A2 & isbn & - & string & $\leq$ & 1 \\
-class & B & - & - & B1, B2 & $\sqcap$ & - \\
-property & B1 & title & - & string & $\geq$ & 1 \\
-property & B2 & title & - & string & $\leq$ & 1 \\
-class & C & - & - & C1, C2 & $\sqcap$ & - \\
-property & C1 & issn & - & string & $\geq$ & 1 \\
-property & C2 & issn & - & string & $\leq$ & 1 \\
-class & D & - & - & D1, D2 & $\sqcap$ & - \\
-property & D1 & title & - & string & $\geq$ & 1 \\
-property & D2 & title & - & string & $\leq$ & 1 \\
-		\end{tabular}
-\end{table}
+%\begin{table}[H]
+  %\scriptsize
+  %\sffamily
+  %\vspace{0cm}
+	%\caption{Complex Constraints}
+	%\label{tab:complex-constraints}
+	%\centering
+		%\begin{tabular}{l|l|l|l|l|l|l}
+      %\textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      %\hline
+%class & Publication & - & - & $\neg$E $\sqcap$ F, E $\sqcap$ $\neg$F & $\sqcup$ & - \\
+%class & $\neg$E $\sqcap$ F & - & - & $\neg$E, F & $\sqcap$ & - \\
+%class & E $\sqcap$ $\neg$F & - & - & E, $\neg$F & $\sqcap$ & - \\
+%class & $\neg$E & - & - & E & $\neg$ & - \\
+%class & E & - & - & A, B & $\sqcap$ & - \\
+%class & $\neg$F & - & - & F & $\neg$ & - \\
+%class & F & - & - & C, D & $\sqcap$ & - \\
+%class & A & - & - & A1, A2 & $\sqcap$ & - \\
+%property & A1 & isbn & - & string & $\geq$ & 1 \\
+%property & A2 & isbn & - & string & $\leq$ & 1 \\
+%class & B & - & - & B1, B2 & $\sqcap$ & - \\
+%property & B1 & title & - & string & $\geq$ & 1 \\
+%property & B2 & title & - & string & $\leq$ & 1 \\
+%class & C & - & - & C1, C2 & $\sqcap$ & - \\
+%property & C1 & issn & - & string & $\geq$ & 1 \\
+%property & C2 & issn & - & string & $\leq$ & 1 \\
+%class & D & - & - & D1, D2 & $\sqcap$ & - \\
+%property & D1 & title & - & string & $\geq$ & 1 \\
+%property & D2 & title & - & string & $\leq$ & 1 \\
+		%\end{tabular}
+%\end{table}
 
 %Even though, tools may generate \emph{generic constraints} automatically, this 
-\emph{Complex constraints} are composed of many other \emph{complex} (e.g. \emph{minimum and maximum qualified cardinality restrictions}) and \emph{simple constraints} (e.g. constraints on sets).
+The \emph{DL} statements demonstrate that the \emph{complex constraint} 
+is composed of many other \emph{complex} (e.g. \emph{minimum and maximum qualified cardinality restrictions}) and \emph{simple constraints} (e.g. constraints on sets).
 As \emph{exact (un)qualified cardinality restrictions (=n)} and \emph{exclusive or (XOR)} are frequently used \emph{complex constraints},
-we propose using them as \emph{simple constraints} - in terms of syntactic sugar.
-As a consequence, the \emph{context-specific exclusive or of property groups} constraint above is represented as a \emph{generic constraint} more intuitively and concisely (see Table \ref{tab:simplified-complex-constraints}).
+we propose using them in terms of syntactic sugar as \emph{simple constraints}.
+As a consequence, the \emph{context-specific exclusive or of property groups} \emph{complex constraint} is represented as a \emph{generic constraint} by means of the \emph{RDF-CV} more intuitively and concisely (Table \ref{tab:simplified-complex-constraints}).
 
@@
 
-\subsubsection{\emph{Complex Constraints} as \emph{Simple Constraints}}
-
-Almost 15 percent of all constraint types are \emph{complex constraints} which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar (see Section \ref{sec:evaluation}).
-
-There are three forms of \emph{OWL RBox axioms}: \emph{role inclusions}, \emph{equivalence} and \emph{disjointness}. 
-\emph{OWL} provides a variety of other axiom types: \emph{role transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity}. 
-These axiom types are sometimes considered as basic axiom types in \emph{DL} - using some suggestive notation such as
-\ms{Trans(ancestorOf)} to express that the role \emph{ancestorOf} is transitive.
-Such axioms, however, are just syntactic sugar - 
-all role characteristics can be expressed using the basic features of \emph{DL}.
-The \emph{irreflexive object properties} constraint type (\emph{R-60}) 
-restricts that no individual is connected by a given object property to itself \cite{Kroetzsch2012}.
-With the following \emph{irreflexive object property} constraint, for instance, one can state that individuals cannot be authors of themselves:
-\begin{DL}
-\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists authorOf.Self$}
-\end{DL}
-When mapped to the \emph{RDF-CV} (see Table \ref{tab:irreflexive-object-properties-as-complex-constraints}), the \emph{complex constraint} aggregates three \emph{simple constraints} (one \emph{property} and two \emph{class constraints}):
-
-%\begin{gcotable}
-%property & $\exists$ marriedTo . Self & marriedTo & - & Self & $\exists$ & - \\
-%class & $\neg$ $\exists$ marriedTo . Self & - & - & $\exists$ marriedTo . Self & $\neg$ & - \\
-%class & $\top$ & - & - & $\top$, $\neg$ $\exists$ marriedTo . Self & $\sqsubseteq$ & - \\
-%\end{gcotable}
-
-\begin{table}[H]
-  \scriptsize
-  \sffamily
-  \vspace{0cm}
-	\caption{Irreflexive Object Properties as Complex Constraints}
-	\label{tab:irreflexive-object-properties-as-complex-constraints}
-	\centering
-		\begin{tabular}{l|l|l|l|l|l|l}
-      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
-      \hline
-property & $\exists$ authorOf.Self & marriedTo & - & Self & $\exists$ & - \\
-class & $\neg$ $\exists$ authorOf.Self & - & - & $\exists$ authorOf.Self & $\neg$ & - \\
-class & $\top$ & - & - & $\top$, $\neg$ $\exists$ authorOf.Self & $\sqsubseteq$ & - \\
-		\end{tabular}
-\end{table}
-
-When using the \emph{OWL RBox axiom} \emph{role irreflexivity} in terms of syntactic sugar, 
-the \emph{complex constraint} can be expressed more concisely in form of a \emph{simple property constraint} with exactly the same semantics (see Table \ref{tab:irreflexive-object-properties-as-simple-constraints}):
-
-%\begin{gcotable}
-%property & $\top$ & marriedTo & - & - & irreflexive & - \\
-%\end{gcotable}
-
-\begin{table}[H]
-  \scriptsize
-  \sffamily
-  \vspace{0cm}
-	\caption{Irreflexive Object Properties as Simple Constraints}
-	\label{tab:irreflexive-object-properties-as-simple-constraints}
-	\centering
-		\begin{tabular}{l|l|l|l|l|l|l}
-      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
-      \hline
-property & $\top$ & authorOf & - & - & irreflexive & - \\
-		\end{tabular}
-\end{table}
-
-The \emph{primary key properties} constraint type (\emph{R-226}) is often useful to declare a given (datatype) property as the "primary key" of a class, so that a system can enforce uniqueness. 
-For instance, \emph{Books} are uniquely identified by their \emph{ISBN} number, that is, the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}, 
-which can be represented by the \emph{RDF-CV} in form of a \emph{complex constraint} (see Table \ref{tab:primary-key-properties-as-complex-constraints}):
+Constraints of almost 15\% of the constraint types are \emph{complex constraints}
+which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
+%There are three forms of \emph{OWL RBox axioms}: \emph{role inclusions}, \emph{equivalence} and \emph{disjointness}. 
+%\emph{OWL} provides a variety of other axiom types: \emph{role transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity}. 
+%These axiom types are sometimes considered as basic axiom types in \emph{DL} - using some suggestive notation such as
+%\ms{Trans(ancestorOf)} to express that the role \emph{ancestorOf} is transitive.
+%Such axioms, however, are just syntactic sugar - 
+%all role characteristics can be expressed using the basic features of \emph{DL}.
+%
+%The \emph{irreflexive object properties} constraint type (\emph{R-60}) 
+%restricts that no individual is connected by a given object property to itself \cite{Kroetzsch2012}.
+%With the following \emph{irreflexive object property} constraint, for instance, one can state that individuals cannot be authors of themselves:
+%\begin{DL}
+%\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists authorOf.Self$}
+%\end{DL}
+%When mapped to the \emph{RDF-CV} (see Table \ref{tab:irreflexive-object-properties-as-complex-constraints}), the \emph{complex constraint} aggregates three \emph{simple constraints} (one \emph{property} and two \emph{class constraints}):
+%
+%%\begin{gcotable}
+%%property & $\exists$ marriedTo . Self & marriedTo & - & Self & $\exists$ & - \\
+%%class & $\neg$ $\exists$ marriedTo . Self & - & - & $\exists$ marriedTo . Self & $\neg$ & - \\
+%%class & $\top$ & - & - & $\top$, $\neg$ $\exists$ marriedTo . Self & $\sqsubseteq$ & - \\
+%%\end{gcotable}
+%
+%\begin{table}[H]
+  %\scriptsize
+  %\sffamily
+  %\vspace{0cm}
+	%\caption{Irreflexive Object Properties as Complex Constraints}
+	%\label{tab:irreflexive-object-properties-as-complex-constraints}
+	%\centering
+		%\begin{tabular}{l|l|l|l|l|l|l}
+      %\textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      %\hline
+%property & $\exists$ authorOf.Self & marriedTo & - & Self & $\exists$ & - \\
+%class & $\neg$ $\exists$ authorOf.Self & - & - & $\exists$ authorOf.Self & $\neg$ & - \\
+%class & $\top$ & - & - & $\top$, $\neg$ $\exists$ authorOf.Self & $\sqsubseteq$ & - \\
+		%\end{tabular}
+%\end{table}
+%
+%When using the \emph{OWL RBox axiom} \emph{role irreflexivity} in terms of syntactic sugar, 
+%the \emph{complex constraint} can be expressed more concisely in form of a \emph{simple property constraint} with exactly the same semantics (see Table \ref{tab:irreflexive-object-properties-as-simple-constraints}):
+%
+%%\begin{gcotable}
+%%property & $\top$ & marriedTo & - & - & irreflexive & - \\
+%%\end{gcotable}
+%
+%\begin{table}[H]
+  %\scriptsize
+  %\sffamily
+  %\vspace{0cm}
+	%\caption{Irreflexive Object Properties as Simple Constraints}
+	%\label{tab:irreflexive-object-properties-as-simple-constraints}
+	%\centering
+		%\begin{tabular}{l|l|l|l|l|l|l}
+      %\textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      %\hline
+%property & $\top$ & authorOf & - & - & irreflexive & - \\
+		%\end{tabular}
+%\end{table}
+The \emph{primary key properties} constraint type (\emph{R-226}) is often useful to declare a given (datatype) property as the primary key of a class, so that a system can enforce uniqueness. 
+\emph{Books}, e.g., are uniquely identified by their \emph{ISBN}, i.e., the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}
+which can be represented using the \emph{RDF-CV} in form of a \emph{complex constraint} consisting of two \emph{simple constraints} (Table \ref{tab:primary-key-properties-as-complex-constraints}):
 
@@
 For these generalization purposes, as there are different sorts of keys, and as keys can lead to undecidability, 
-\emph{DL} is extended with \emph{key boxes} and a special construct \emph{keyfor} \cite{Lutz2005}.
-When using the \emph{keyfor} \emph{DL} construct (\ms{isbn keyfor Book}), the \emph{complex constraint} can be expressed by only one \emph{simple property constraint} (see Table \ref{tab:primary-key-properties-as-simple-constraints} for the mapping to the \emph{RDF-CV}).
+\emph{DL} is extended with a special construct \emph{keyfor} \cite{Lutz2005}.
+When using \emph{keyfor} (\ms{isbn keyfor Book}), 
+the \emph{complex constraint} can be simplified as a \emph{simple constraint} which looks like the following in RDF turtle syntax:
 
@@
 
-\begin{table}[H]
-  \scriptsize
-  \sffamily
-  \vspace{0cm}
-	\caption{Primary Key Properties as Simple Constraints}
-	\label{tab:primary-key-properties-as-simple-constraints}
-	\centering
-		\begin{tabular}{l|l|l|l|l|l|l}
-      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
-      \hline
-property & Book & isbn & - & - & keyfor & - \\
-		\end{tabular}
-\end{table}
-
+%\begin{table}[H]
+  %\scriptsize
+  %\sffamily
+  %\vspace{0cm}
+	%\caption{Primary Key Properties as Simple Constraints}
+	%\label{tab:primary-key-properties-as-simple-constraints}
+	%\centering
+		%\begin{tabular}{l|l|l|l|l|l|l}
+      %\textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      %\hline
+%property & Book & isbn & - & - & keyfor & - \\
+		%\end{tabular}
+%\end{table}
+
+\begin{ex}[commandchars=\\\{\}]
+[   a \textit{rdfcv:PropertyConstraint} , \textit{rdfcv:SimpleConstraint} ;
+    \textit{rdfcv:contextClass} Book ; \textit{rdfcv:leftProperties} ( isbn ) ; \textit{rdfcv:constrainingElement} "keyfor" ] .
+\end{ex}
+
+\emph{Complex constraints} of frequently used constraint types corresponding to \emph{DL} axioms like 
+\emph{transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity}
+can also be simplified in the same way, 
+as such axioms can be expressed using the basic features of \emph{DL} but can also be abbreviated when using them in form of syntactic sugar \cite{BoschEckert2015-2}
 %Starfleet officers, e.g., are uniquely identified by their command authorization code (e.g. to activate and cancel auto-destruct sequences).
@@
 
-\section{How to Improve the Understandability of Constraints}
-\label{sec:transformations}
-
-RDF data providers have to ensure that their data conforms to constraints which are explicitly defined within contracts between data providers and consumers.
-As there is no standard way to express constraints, they may be represented by a variety of constraint languages\footnote{Candidates for constraint languages are, i.a., SPIN, OWL 2, DSP, ShEx, ReSh, Bibframe, DQTP, Pellet ICV, RDFUnit, SPARQL, and Stardog ICV} - each of them different in syntax and semantics.
-To overcome the necessity to understand diverse constraint languages, 
-we propose to transform any \emph{specific constraint} (\emph{$sc_{\alpha}$}) (expressed by any constraint language \emph{$\alpha$}) into any other \emph{specific constraint} (\emph{$sc_{\beta}$}) (expressed by any other constraint language \emph{$\beta$}) - in case they have the same semantics.
-We use the \emph{RDF-CV} to intermediately represent constraints in a generic way for these transformations.
-By defining mappings between equivalent \emph{specific constraints}, and the corresponding \emph{generic constraint} (\emph{gc}) we are able to convert them automatically:
-
-\begin{DL}
-$ gc = m_1(sc_{\alpha}) = m_2(sc_{\beta}) $
-\end{DL}
-
-We do not need to define mappings between each pair of semantically equivalent \emph{specific constraints}.
-Let's assume we are able to express a particular constraint type by 5 constraint languages.
-Without the intermediate \emph{generic constraint}, we would have to define for each constraint type \emph{1} mapping for each pair of \emph{specific constraints} (expressed by different constraint languages)
-- that are \emph{\( {n \choose 2} \)} mappings which is not very helpful.
-With an intermediate \emph{generic constraint}, however, we only need to define for each constraint type \emph{n} mappings (1 mapping for each \emph{specific constraint}) from \emph{n} \emph{specific constraints} to the corresponding \emph{generic constraint}.
-
-%(n(n+1))/2
-
-%\begin{DL}
-%\(\sum \limits_{i=1}^n i = \frac{n(n+1)}{2}\)
-%\(\sum \limits_{i=1}^n i\)
-%\(\Binom{n}{2} \)
-%\( {n \choose 2} \)
-%\end{DL}
-
-\begin{DL}
-Publication $\equiv$ $\exists$ publisher.Publisher
-\end{DL}
-
-The {\em existential quantification} (\emph{R-86})
-%\ms{Publication $\equiv$ $\exists$ publisher.Publisher} 
-above restricts \emph{publications} to have at least one \emph{publisher} and can be expressed by at least 10 different constraint languages\footnote{OWL 2, SPARQL, ShEx, Bibframe, DSP, ReSh, SPIN, DQTP, Pellet IVC, and Stardog ICV}:
-
-\begin{ex}
-# OWL 2:
-[ a owl:Restriction ;
-  owl:onProperty publisher ;
-  owl:someValuesFrom Publisher ;
-  rdfs:subClassOf Publication ] .
-
-# SPARQL:
-ASK { ?x a Publication . FILTER NOT EXISTS { ?x publisher [ a Publisher ] } . }
-
-# ShEx:
-Publication {
-    publisher @Publisher{1,} }
-
-# DSP:
-descriptionTemplate a dsp:DescriptionTemplate ;
-    dsp:resourceClass Publication ; 
-    dsp:statementTemplate [ a dsp:NonLiteralStatementTemplate ;
-        dsp:minOccur 1 ; dsp:maxOccur "infinity" ; 
-        dsp:property publisher ; 
-        dsp:nonLiteralConstraint [ a dsp:NonLiteralConstraint ;
-            dsp:valueClass Publisher ] ] .
-
-# ReSh:
-Publication a rs:ResourceShape ; rs:property [
-    rs:propertyDefinition :publisher ;
-    rs:valueShape :Publisher ;
-    se:min 1 ; se:maxundefined true ; ] .
-
-# SPIN:
-CONSTRUCT {
-    _:cv a spin:ConstraintViolation ; spin:violationRoot ?subject ;
-         rdfs:label ?violationMessage ; spin:violationPath ?property . } WHERE 
-{ ?subject a ?classSubject . FILTER NOT EXISTS { ?subject ?property [ a ?classObject ] } . }
-\end{ex}
-
-%\emph{Allowed Values}\footnote{corresponds to \emph{R-30-ALLOWED-VALUES-FOR-RDF-OBJECTS} and \emph{R-37-ALLOWED-VALUES-FOR-RDF-LITERALS}}
-%is a common requirement (constraint type) to narrow down the value space of a property by an exhaustive enumeration of the valid values (both literals or resources). 
-%The Enterprise, e.g., is only commanded by the captains Archer, Kirk, and Picard.
-%This \emph{complex constraint} is composed of the two \emph{simple constraints} \emph{universal quantification} and \emph{allowed values} which can be represented in DL:
-
-%\begin{DL}
-%StarfleetCaptain $\equiv$ $\forall$ overruledBy . \{Commodore\} $\sqcup$ \{Admiral\}
-%\end{DL}
-
-%\begin{DL}
-%Enterprise $\equiv$ $\forall$ commandedBy . \{Archer\} $\sqcup$ \{Kirk\} $\sqcup$ \{Picard\}
-%\end{DL}
-
-%First, we map these DL statements to two \emph{simple generic constraints} corresponding to the \emph{RDF-CV} (we define the class \ms{EnterpriseCaptains} by simply enumerating its instances):
-
-The \emph{DL} statement {\small\ms{Publication $\equiv$ $\exists$ publisher.Publisher}} is mapped to a \emph{(simple) generic constraint} conforming to the \emph{RDF-CV} (see Table \ref{tab:existential-quantification-as-simple-constraints}).
-Then, one mapping (\emph{$m_1(sc_{OWL 2})$}, \emph{$m_2(sc_{ReSh})$}, \emph{$m_3(sc_{ShEx})$}, ...) is defined for each \emph{specific constraint} (\emph{$sc_{OWL 2}$}, \emph{$sc_{ReSh}$}, \emph{$sc_{ShEx}$}, ...) to the corresponding \emph{generic constraint} (\emph{gc}).
-
-%\begin{gcotable}
-%property & StarfleetCaptain & overruledBy & - & CaptainOverruler & $\forall$ & - \\
-%class & CaptainOverruler & - & - & \{Commodore\},\{Admiral\} & $\sqcup$ & - \\
-%\end{gcotable}
-
-%\begin{gcotable}
-%property & Enterprise & commandedBy & - & EnterpriseCaptains & $\forall$ & - \\
-%class & EnterpriseCaptains & - & - & \{Archer\},\{Kirk\},\{Picard\} & $\sqcup$ & - \\
-%\end{gcotable}
-
-\begin{table}[H]
-  \scriptsize
-  \sffamily
-  \vspace{0cm}
-	\caption{Existential Quantification as Simple Constraints}
-	\label{tab:existential-quantification-as-simple-constraints}
-	\centering
-		\begin{tabular}{l|l|l|l|l|l|l}
-      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
-      \hline
-property & Publication & publisher & - & Publisher & $\exists$ \\
-		\end{tabular}
-\end{table}
-
-%\begin{ex}
-%# OWL 2:
-%Enterprise rdfs:subClassOf [ a owl:Restriction .
-    %owl:onProperty commandedBy .
-    %owl:allValuesFrom [ a owl:Class ;
-        %owl:oneOf ( Archer Kirk Picard ) ] ] .
-%# ReSh:
-%Enterprise a rs:ResourceShape ; rs:property [
-    %rs:name "commandedBy" ; rs:propertyDefinition commandedBy ;
-    %rs:allowedValue Archer , Kirk , Picard ;
-    %rs:occurs rs:Exactly-one ; ] .
-%# ShEx:
-%Enterprise {
-    %commandedBy (Archer Kirk Picard) }
-%\end{ex}
-
-%\begin{ex}
-%# DSP:
-%[ a dsp:DescriptionTemplate ;
-    %dsp:resourceClass StarfleetCaptain ; 
-    %dsp:statementTemplate [ a dsp:NonLiteralStatementTemplate ; 
-        %dsp:property overruledBy ; 
-        %dsp:nonLiteralConstraint [ a dsp:NonLiteralConstraint ;
-            %dsp:valueClass Commodore , Admiral ] ] ] .
-%# OWL 2:
-%StarfleetCaptain rdfs:subClassOf [ a owl:Restriction .
-    %owl:onProperty overruledBy .
-    %owl:allValuesFrom [ a owl:Class ;
-        %owl:oneOf ( Commodore Admiral ) ] ] .
-%# ReSh:
-%%StarfleetCaptain a rs:ResourceShape ;
-    %%rs:property [
-        %%rs:name "overruledBy" ; rs:propertyDefinition overruledBy ;
-        %%rs:valueShape Commodore ; rs:occurs rs:Zero-or-many ; ] ;
-    %%rs:property [
-        %%rs:name "overruledBy" ; rs:propertyDefinition overruledBy ;
-        %%rs:valueShape Admiral ; rs:occurs rs:Zero-or-many ; ] ;
-%# ShEx:
-%:StarfleetCaptain {
-    %:overruledBy @:Commodore* , :overruledBy @:Admiral* }
-%\end{ex}
-
 %\section{Validation of Specific and Generic Constraints}
-\section{How to Provide Constraint Validation Out-Of-The-Box}
-\label{sec:validation}
-
-SPARQL is generally seen as the method of choice to validate RDF data according to certain constraints, although, it is not ideal for their formulation. 
-In contrast, OWL 2, DSP, ReSh, and ShEx constraints are comparatively easy to understand. 
-We use SPIN as basis to define a
-validation environment\footnote{Online demo available at \url{http://purl.org/net/rdfval-demo}, source code available at: \url{https://github.com/boschthomas/rdf-validator}\label{rdf-validator}} in which the validation of any constraint language can be implemented by representing them in SPARQL.
-The only limitation is that constraint languages must be represented in RDF.
-The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations \cite{BoschEckert2014-2}.
-This way, we are able to offer RDF data validation according to all \emph{specific constraints} (expressed by any constraint language) by defining mappings from each \emph{specific constraint} to \emph{SPIN}.
-We already specified mappings to \emph{SPIN} for all \emph{OWL 2} and \emph{DSP}\footnote{SPIN mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} constructs and for some \emph{ReSh} and \emph{ShEx} constructs.
-%We do not have to define a mapping to SPIN for each specific constraint. 
-%when we define a mapping to SPIN for each generic constraint.
-As constraint languages differ in syntax and semantics it is rather difficult to ensure that semantically equivalent \emph{specific constraints} always lead to identical validation results.
-
-We do not have to map each \emph{specific constraint} to SPIN and we get identical validation results for semantically equivalent \emph{specific constraints} (expressed by different constraint languages),
-(1) if we map semantically equivalent \emph{specific constraints} to the corresponding \emph{generic constraint} and 
-(2) if we map the \emph{generic constraint} to SPIN.
-As a consequence, we only have to define one SPIN mapping for each constraint type corresponding to an RDF validation requirement.
-\textcolor{red}{19} of the overall 81 identified constraint types can be expressed by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
-This means that there must be 76 (four for each constraint type) implementations to validate RDF data according to 76 \emph{specific constraints} - instead of only 19 implementations (one for each \emph{generic constraint}) leading to identical validation results.
-
-%The validation implementation of constraint languages is fully declarative,
-%consisting of a mapping from constraint languages to SPIN in form of SPARQL CONSTRUCT queries.
-%SPIN represents both the SPIN mappings and the SPARQL queries in RDF. 
-%Within the validation environment, we fully implemented the validation of all OWL 2 DL and DSP constructs 
-%(for the complete DSP validation see \cite{BoschEckert2014-2}).
-
-Within the \emph{RDF Validator}, we define one SPIN construct template for each \emph{generic constraint} and therefore constraint type.
-A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples (\emph{spin:ConstraintViolation}) indicating the subject (\emph{spin:violationRoot}) and the properties (\emph{spin:violationPath}) causing constraint violations, and the reason why constraint violations have been raised (\emph{rdfs:label}).
-A SPIN construct template creates constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
-
-\begin{DL}
-Publication $\equiv$ $\forall$ author.Person
-\end{DL}
-
-According to the \emph{universal quantification} (\emph{R-91}) above, \emph{authors} of \emph{publications} must be \emph{persons}.
-The SPARQL CONSTRUCT query for the constraint type \emph{universal quantification} is shown below:
-
-\begin{ex}
-CONSTRUCT {
-    [   a spin:ConstraintViolation ; spin:violationRoot ?subject ;
-        rdfs:label ?violationMessage ; spin:violationPath ?lp1 . ] }
-WHERE {	  
-    [   a gclo:PropertyConstraint ;
-        gclo:contextClass ?cc ;
-        gclo:leftProperties ( ?lp1 ) ;
-        gclo:classes ( ?c1 ) ;
-        gclo:constrainingElement "universal quantification" ] .
-    ?subject a ?cc .
-    ?subject ?lp1 ?o .
-    FILTER NOT EXISTS { ?o a ?c1 } . }
-\end{ex}
-
-We provide a mapping from the \emph{RDF-CV} to SPIN\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}} 
-in order to automatically validate RDF data complying with each type of \emph{generic constraint} (\emph{simple}, \emph{complex}, \emph{property}, and \emph{class constraints}).
-
-%\subsection{Not Allowed Values}
-
-%\section{Evaluation}
-%\label{sec:evaluation}
-
-%\begin{evaluation-generic-overview}
-%\emph{Property Constraints} & 48 & 65 (64.86) \\
-%\emph{Class Constraints} & 17 & 23 (22.96) \\
-%\emph{Property and Class Constraints} & 9 & 12 (12.16) \\
-%\hline
-%\emph{Simple Constraints} & 46 & 62 (62.16) \\
-%\emph{Simple Constraints} (Syntactic Sugar) & 10 & 14 (13.51) \\
-%\emph{Complex Constraints} & 18 & 24 (24.32) \\
-%\hline
-%\emph{DL Expressible} & 51 & 69 (68.92) \\
-%\emph{DL Not Expressible} & 23 & 31 (31.08) \\
-%\hline
-%Total & 74 & 100 \\
-%\end{evaluation-generic-overview}
-
-%\begin{table}[H]
-  %%\scriptsize
-  %%\sffamily
-  %\vspace{0cm}
-	%\caption{Evaluation}
-	%\label{tab:evaluation}
-	%\centering
-		%\begin{tabular}{l|c|c}
-      %\textbf{Classes of Constraint Types} & \textbf{\#} & \textbf{\%} \\
-      %\hline
-%%\textbf{\emph{Context}} & & \\
-%\emph{Property Constraints} & 48 & 64.86 \\
-%\emph{Class Constraints} & 17 & 22.96 \\
-%\emph{Property and Class Constraints} & 9 & 12.16 \\
-%\hline
-%%\textbf{\emph{Complexity}} & & \\
-%\emph{Simple Constraints} & 46 & 62.16 \\
-%\emph{Simple Constraints} (Syntactic Sugar) & 10 & 13.51 \\
-%\emph{Complex Constraints} & 18 & 24.32 \\
-%\hline
-%%\textbf{\emph{DL Expressivity}} & & \\
-%\emph{DL Expressible} & 51 & 68.92 \\
-%\emph{DL Not Expressible} & 23 & 31.08 \\
-%\hline
-%Total & 74 & 100 \\
-		%\end{tabular}
-%\end{table}
-
-%\newenvironment{evaluation-generic-overview}{
-  %%\scriptsize
-  %%\sffamily
-  %\vspace{0cm}
-	%\begin{center}
-  %\begin{tabular}{l|c|c}
-  %\hline
-  %\textbf{Constraint Classes} & \textbf{\#} & \textbf{\%} \\
-  %\hline
-%
-%}{
-  %\hline
-  %\end{tabular}
-  %%\linebreak
-	%\end{center}
-%}
 
@@
 
+-----
+
+-----
+
+-----
+
+-----
+
+-----
+
 \section{Conclusion and Future Work}
+
+-----
+
+-----
+
+-----
+
+-----
+
+-----
 

### 2015-05-27 paper/paper 2/dc-2015.tex
introduction

@@
 
+-----
+
+For the formulation of constraints, it is important that the constraint language is concise and intuitive and that the declarative constraint language is translated to an implementation language like SPARQL in order to execute constraint validation automatically.
+
+-----
+
 There exists no single best solution considered as high-level intuitive constraint language which enables to express constraints easily and concisely and which is able to meet all requirements raised by data practitioners.
@@
 We use \emph{SPIN} as basis to develop a validation environment\footnote{Online demo available at \url{http://purl.org/net/rdfval-demo}, source code available at: \url{https://github.com/boschthomas/rdf-validator}\label{rdf-validator}} to validate RDF data according to constraints of constraint types which are expressible by arbitrary constraint languages by mapping them to \emph{SPIN}\footnote{\emph{SPIN} mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}\label{spin-mappings}} \cite{BoschEckert2014-2}.
-The next step, however, is to extend the \emph{RDF Validator} to validate RDF data conforming to constraints of each of the 81 constraint types.
-
-Validation on semantically equivalent constraints, expressed by different constraint languages, 
-should lead to identical validation results, 
-i.e., validation should be performed independently from the used language (see Section \ref{sec:validation}).
-
-We are able to offer already implemented validation for constraints of constraint types expressed by arbitrary languages out-of-the-box, 
-(1) if we implement the validation of the corresponding generically represented constraint types once and 
-(2) if we transform semantically equivalent specifically expressed constraints into generically expressed constraints.
-
------
-
-SPARQL is generally seen as the method of choice to validate RDF data according to certain constraints, although, it is not ideal for their formulation. 
-In contrast, OWL 2, DSP, ReSh, and ShEx constraints are comparatively easy to understand. 
-We use SPIN as basis to define a
-validation environment\footnote{Online demo available at \url{http://purl.org/net/rdfval-demo}, source code available at: \url{https://github.com/boschthomas/rdf-validator}\label{rdf-validator}} in which the validation of any constraint language can be implemented by representing them in SPARQL.
-The only limitation is that constraint languages must be represented in RDF.
 The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations \cite{BoschEckert2014-2}.
-This way, we are able to offer RDF data validation according to all \emph{specific constraints} (expressed by any constraint language) by defining mappings from each \emph{specific constraint} to \emph{SPIN}.
-We already specified mappings to \emph{SPIN} for all \emph{OWL 2} and \emph{DSP}\footnote{SPIN mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} constructs and for some \emph{ReSh} and \emph{ShEx} constructs.
-As constraint languages differ in syntax and semantics it is rather difficult to ensure that semantically equivalent \emph{specific constraints} always lead to identical validation results.
-
-We do not have to map each \emph{specific constraint} to SPIN and we get identical validation results for semantically equivalent \emph{specific constraints} (expressed by different constraint languages),
-(1) if we map semantically equivalent \emph{specific constraints} to the corresponding \emph{generic constraint} and 
-(2) if we map the \emph{generic constraint} to SPIN.
-As a consequence, we only have to define one SPIN mapping for each constraint type corresponding to an RDF validation requirement.
-\textcolor{red}{19} of the overall 81 identified constraint types can be expressed by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
-This means that there must be 76 (four for each constraint type) implementations to validate RDF data according to 76 \emph{specific constraints} - instead of only 19 implementations (one for each \emph{generic constraint}) leading to identical validation results.
-
-Within the \emph{RDF Validator}, we define one SPIN construct template for each \emph{generic constraint} and therefore constraint type.
-A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples (\emph{spin:ConstraintViolation}) indicating the subject (\emph{spin:violationRoot}) and the properties (\emph{spin:violationPath}) causing constraint violations, and the reason why constraint violations have been raised (\emph{rdfs:label}).
-A SPIN construct template creates constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
-
-\begin{DL}
-Publication $\equiv$ $\forall$ author.Person
-\end{DL}
-
-According to the \emph{universal quantification} (\emph{R-91}) above, \emph{authors} of \emph{publications} must be \emph{persons}.
-The SPARQL CONSTRUCT query for the constraint type \emph{universal quantification} is shown below:
-
-\begin{ex}
-CONSTRUCT {
-    [   a spin:ConstraintViolation ; spin:violationRoot ?subject ;
-        rdfs:label ?violationMessage ; spin:violationPath ?lp1 . ] }
-WHERE {	  
-    [   a gclo:PropertyConstraint ;
-        gclo:contextClass ?cc ;
-        gclo:leftProperties ( ?lp1 ) ;
-        gclo:classes ( ?c1 ) ;
-        gclo:constrainingElement "universal quantification" ] .
-    ?subject a ?cc .
-    ?subject ?lp1 ?o .
-    FILTER NOT EXISTS { ?o a ?c1 } . }
-\end{ex}
-
-We provide a mapping from the \emph{RDF-CV} to SPIN\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}} 
-in order to automatically validate RDF data complying with each type of \emph{generic constraint} (\emph{simple}, \emph{complex}, \emph{property}, and \emph{class constraints}).
+The next step, however, was to extend the \emph{RDF Validator} to validate RDF data conforming to constraints of any constraint type
+by representing constraints generically using the proposed vocabulary.
+
+When language designers extend newly developed or existing constraint languages 
+in order to allow to formulate constraints of not yet supported constraint types,
+our proposal prevents the necessity to actually implement the validation of data
+according to constraints of these constraint types for each of those languages.  
+We enable to offer validation implementations for any constraint type whose \emph{specific constraints} may be expressed by any language out-of-the-box 
+by providing a \emph{SPIN} mapping
+%generic validation implementations once 
+for each constraint type\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}}  whose constraints are represented generically (for further details see \cite{BoschEckert2015-2}).
+%(2) by transforming \emph{specific constraints} into the appropriate \emph{generic constraint}.  
+All what language designers have to do is to specify for each constraint type one mapping from the \emph{specific constraint} expressed by a particular language to the corresponding \emph{generic constraint}.
+\textcolor{red}{19} of the overall 81 constraint types are expressible by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
+This means that for these \textcolor{red}{19} constraint types there must be \textcolor{red}{76} implementations (four for each constraint type) to actually validate RDF data according to \textcolor{red}{76} \emph{specific constraints} - instead of only \textcolor{red}{19} implementations (one for each \emph{generic constraint}) which lead for each constraint type to identical validation results independently from the used language.
+
+Our proposal makes sure that the validation on semantically equivalent \emph{specific constraints} expressed by different languages
+leads to exactly the same validation results, 
+i.e., that validation is performed independently of the used language.
+This is not the case, however, for existing languages since they are implemented independently form each other.
+Two constraints are identical w.r.t. RDF semantics, 
+if they detect the same set of violations regardless of RDF data, 
+which means whenever the constraints are applied to any RDF data they point out the same violations.
+As we use multiple languages to express constraints of constraint types in the appendix of this paper,
+we thereby document identical semantics of these languages with regard to given constraint types \cite{BoschNolleAcarEckert2015}.
+This is also needed to prove that semantically equivalent \emph{specific constraints} and corresponding \emph{generic constraints}
+behave in the same way with regard to validation results which semantically underpins bidirectional mappings.
 
@@
 In the example, the \emph{CWA} yields to a violation since there is no explicitly defined \emph{title} for the \emph{book} {\em Hamlet}.
-%
+
 Validation requires that different names represent different objects (\emph{unique name assumption (UNA)}), whereas,
@@
 For the majority of the constraint types, validation results differ (1) if the \emph{CWA} or the \emph{OWA} and (2) if the \emph{UNA} or the \emph{nUNA} is assumed \cite{BoschNolleAcarEckert2015}.
-If any two constraints are semantically the same (w.r.t. RDF semantics), they should detect the same set of violations regardless of RDF data, 
-which means whenever the constraints are applied to any RDF data they point out the same violations.
-To be able to define mappings between semantically equivalent \emph{specific constraints} (expressed by different languages) and 
-between \emph{specific constraints} and \emph{generic constraints},
-we show for each constraint type that their constraints lead to exactly the same violations which shows that they behave in the same way. 
-We express constraint types by different languages
-to document identical semantics for these languages with regard to appropriate constraint types.
 
@@
 
-\tb{explain how typical constraints are expressed by the most common constraint languages}
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
+In this section, we present current approaches for constraint formulation and validation which have been the most discussed in the mentioned workshops and WGs.
+These approaches differ in 2 dimensions: (1) the used constraint language and (2) if they offer validation systems.
+
+OWL, Resource Shapes (ReSh), Shape Expressions (ShEx), Description Set Profiles (DSPs), SPARQL, and SPIN are the most promising and applied constraint languages.
+Stardog ICV, Pellet ICV, and SPIN use OWL 2 constructs to formulate constraints.
+SPIN\footnote{http://spinrdf.org} provides a vocabulary to represent SPARQL queries as RDF triples
+and uses SPARQL to specify inference rules and logical constraints \cite{Fuerber2010}.
+The Pellet Integrity Constraint Validator (ICV)\footnote{http://clarkparsia.com/pellet/icv/} is a proof-of-concept extension for the OWL reasoner Pellet. 
+Stardog ICV\footnote{http://docs.stardog.com/icv/icv-specification.html} validates RDF data stored in a Stardog RDF database. 
+ReSh\footnote{http://www.w3.org/Submission/shapes/} defines its own RDF vocabulary Open Services for Lifecycle Collaboration (OSLC) to define constraints \cite{Ryman2013}. 
+ShEx\footnote{http://www.w3.org/2013/ShEx/Definition} also specifies a new constraint language whose syntax and semantics are similar to regular expressions.
+DCMI RDF Application Profile (AP)\footnote{http://dublincore.org/documents/singapore-framework/} and Bibframe\footnote{http://bibframe.org/} are approaches to specify profiles for application-specific purposes.
+DCMI RDF-AP uses DSP\footnote{http://dublincore.org/documents/dc-dsp/} as generic constraint language which is also intuitive for non-experts.
+The Bibframe constraint language has a strong overlap with DSP.
+Kontokostas et al. define 17 data quality integrity constraints represented as SPARQL query templates called Data Quality Test Patterns (DQTP) \cite{Kontokostas2014}. 
+Schemarama\footnote{http://swordfish.rdfweb.org/discovery/2001/01/schemarama/} is based on the Squish RDF language instead of SPARQL. 
+For XML, Schematron\footnote{http://www.schematron.com/} is an ISO standard for validation and quality control of XML documents based on XPath and XSLT. 
+XML Schema\footnote{http://www.w3.org/TR/xmlschema-1/} is the primary technology for specifying and constraining the structure of XML documents.
+
+In addition to constraint validation languages, SPIN (open source API), Stardog ICV (as part of the Stardog RDF database), DQTP (tests), Pellet ICV (extension of Pellet OWL reasoner) and ShEx offer executable validation systems using SPARQL as implementation language.
 

### 2015-05-28 paper/paper 2/dc-2015.tex
related work

@@
 although, it is not ideal for their formulation. 
-In contrast, high-level constraint languages, which may be placed on top of \emph{SPARQL} and \emph{SPIN}, are comparatively easy to understand and constraints can be formulated more concisely.
-
------
-
-For the formulation of constraints, it is important that the constraint language is concise and intuitive and that the declarative constraint language is translated to an implementation language like SPARQL in order to execute constraint validation automatically.
-
------
+In contrast, high-level constraint languages, which may be placed on top of \emph{SPARQL} and \emph{SPIN}, are comparatively easy to understand.
+%and constraints can be formulated more concisely. 
+For the formulation of constraints, it is important that the declarative language is concise and intuitive and 
+for the validation of RDF data, it is important that it is translated into an implementation language like SPARQL and SPIN.
 
@@
 
-In this section, we present current approaches for constraint formulation and validation which have been the most discussed in the mentioned workshops and WGs.
-These approaches differ in 2 dimensions: (1) the used constraint language and (2) if they offer validation systems.
-
-OWL, Resource Shapes (ReSh), Shape Expressions (ShEx), Description Set Profiles (DSPs), SPARQL, and SPIN are the most promising and applied constraint languages.
-Stardog ICV, Pellet ICV, and SPIN use OWL 2 constructs to formulate constraints.
-SPIN\footnote{http://spinrdf.org} provides a vocabulary to represent SPARQL queries as RDF triples
-and uses SPARQL to specify inference rules and logical constraints \cite{Fuerber2010}.
-The Pellet Integrity Constraint Validator (ICV)\footnote{http://clarkparsia.com/pellet/icv/} is a proof-of-concept extension for the OWL reasoner Pellet. 
-Stardog ICV\footnote{http://docs.stardog.com/icv/icv-specification.html} validates RDF data stored in a Stardog RDF database. 
-ReSh\footnote{http://www.w3.org/Submission/shapes/} defines its own RDF vocabulary Open Services for Lifecycle Collaboration (OSLC) to define constraints \cite{Ryman2013}. 
-ShEx\footnote{http://www.w3.org/2013/ShEx/Definition} also specifies a new constraint language whose syntax and semantics are similar to regular expressions.
-DCMI RDF Application Profile (AP)\footnote{http://dublincore.org/documents/singapore-framework/} and Bibframe\footnote{http://bibframe.org/} are approaches to specify profiles for application-specific purposes.
-DCMI RDF-AP uses DSP\footnote{http://dublincore.org/documents/dc-dsp/} as generic constraint language which is also intuitive for non-experts.
-The Bibframe constraint language has a strong overlap with DSP.
-Kontokostas et al. define 17 data quality integrity constraints represented as SPARQL query templates called Data Quality Test Patterns (DQTP) \cite{Kontokostas2014}. 
-Schemarama\footnote{http://swordfish.rdfweb.org/discovery/2001/01/schemarama/} is based on the Squish RDF language instead of SPARQL. 
-For XML, Schematron\footnote{http://www.schematron.com/} is an ISO standard for validation and quality control of XML documents based on XPath and XSLT. 
-XML Schema\footnote{http://www.w3.org/TR/xmlschema-1/} is the primary technology for specifying and constraining the structure of XML documents.
-
-In addition to constraint validation languages, SPIN (open source API), Stardog ICV (as part of the Stardog RDF database), DQTP (tests), Pellet ICV (extension of Pellet OWL reasoner) and ShEx offer executable validation systems using SPARQL as implementation language.
+In this section, we present current languages for constraint formulation and RDF data validation\footnote{
+\emph{SPARQL}: \url{http://www.w3.org/TR/sparql11-query}, 
+\emph{SPIN}: \url{http://spinrdf.org},
+\emph{Pellet ICV}: \url{http://clarkparsia.com/pellet/icv},
+\emph{Stardog ICV}: \url{http://docs.stardog.com/#_validating_constraints},
+\emph{ShEx}: \url{http://www.w3.org/Submission/shex-defn},
+\emph{ReSh}: \url{http://www.w3.org/Submission/shapes},
+\emph{DCMI RDF-AP}: \url{http://dublincore.org/documents/singapore-framework},
+\emph{Bibframe}: \url{http://bibframe.org},
+\emph{DSP}: \url{http://dublincore.org/documents/dc-dsp},
+\emph{RDF Schemarama}: \url{http://swordfish.rdfweb.org/discovery/2001/01/schemarama},
+\emph{Schematron}: \url{http://www.schematron.com},
+\emph{XML Schema}: \url{http://www.w3.org/TR/xmlschema-1},
+}.
+\emph{SPIN}, \emph{SPARQL}, \emph{OWL 2}, \emph{ShEx}, \emph{ReSh}, and \emph{DSP} are the six most promising and applied languages.
+%
+The query language for RDF \emph{SPARQL} is generally seen as the method of choice to validate data according to certain constraints \cite{Fuerber2010}, 
+although, it is not ideal for their formulation. 
+In contrast, high-level constraint languages are comparatively easy to understand and constraints can be formulated more concisely.
+Declarative languages may be placed on top of \emph{SPARQL} and \emph{SPIN} when using them as implementation languages.
+%
+\emph{SPIN} provides a vocabulary to represent \emph{SPARQL} queries as RDF triples
+and uses \emph{SPARQL} to specify logical constraints and inference rules \cite{Fuerber2010}.
+%
+\emph{Stardog ICV} and \emph{Pellet ICV} use \emph{OWL 2} constructs to formulate constraints.
+The \emph{Pellet Integrity Constraint Validator (ICV)} is a proof-of-concept extension for the \emph{OWL 2 DL} reasoner \emph{Pellet}. 
+\emph{Stardog ICV} 
+validates RDF data stored in a Stardog database according to 
+constraints which may be written in \emph{SPARQL}, \emph{OWL}, or \emph{SWRL}. 
+%
+\emph{ShEx} specifies a language whose syntax and semantics are similar to regular expressions.
+\emph{ShEx} associate RDF graphs with labeled patterns called \emph{shapes} 
+which are used to express formal constraints on the content of RDF graphs.
+%
+\emph{ReSh} defines its own vocabulary for specifying \emph{shapes} of RDF resources.
+Ryman et al. define \emph{shape} as a description of the set of triples a resource is expected to contain and of the integrity constraints those triples are required to satisfy \cite{Ryman2013}. 
+%
+\emph{DCMI RDF Application Profiles (AP)} and \emph{Bibframe} are approaches to specify profiles for application-specific purposes. 
+\emph{DCMI RDF-AP} uses \emph{DSP} as generic constraint language which is also intuitive for non-experts.
+The \emph{Bibliographic Framework Initiative (Bibframe)} defines a vocabulary which has a strong overlap with \emph{DSP}.
+%
+Kontokostas et al. define 17 data quality integrity constraints represented as \emph{SPARQL} query templates called \emph{Data Quality Test Patterns (DQTP)} \cite{Kontokostas2014}. 
+%
+\emph{RDF Schemarama} 
+is a proof-of-concept demonstrator based on ideas from \emph{Schematron}. 
+It allows to check that RDF data has required properties and
+it is based on \emph{Squish}, an SQL-ish query language for RDF, instead of \emph{SPARQL}. 
+%
+\emph{Schematron} is an ISO standard for the validation and quality control of XML documents based on XPath and XSLT. 
+%
+\emph{XML Schema} is the primary technology for specifying and constraining the structure of XML documents.
+%
+In addition to the formulation of constraints, \emph{SPIN} (open source API), \emph{Stardog ICV} (as part of the \emph{Stardog RDF database}), \emph{DQTP} (tests), \emph{Pellet ICV} (extension of \emph{Pellet OWL 2 DL} reasoner) and \emph{ShEx} offer executable validation systems using \emph{SPARQL} as implementation language.
 

### 2015-05-28 paper/paper 2/dc-2015.tex
conclusion

@@
 To validate RDF data and to formulate constraints, several languages exist or are currently developed,
-but there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners
+but there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners.
 % Truth be told, we do may two things, blabla on and to blabla, however for the flow of the text we dont need to overkill the text.
@@
 
-The contributions of this paper are:
-(1) we provide a basic terminology and classification system for RDF constraints,
-(2) we develop a vocabulary to describe constraints of any constraint type generically and specified its underlying semantics,
-(3) we show how to transform constraints which are expressed by any constraint language, into generically expressed constraints and discuss why these transformations are useful, and
-(4) we explain how to overcome the problems to implement the validation of each constraint type for diverse constraint languages.
+The main contributions of this paper are:
+(1) We provide a basic terminology and classification system for RDF constraints to lay a ground for discussions on RDF validation.
+(2) As current high-level constraint languages do not support all constraint types, 
+we developed a vocabulary to describe constraints of any constraint type in a generic way and specified its underlying semantics.
+(3) We show how to enhance the interoperability of constraints expressed by different languages by using the proposed vocabulary 
+to intermediately represent constraints 
+%as an intermediate generic representation 
+which enables transformations between semantically equivalent constraints.
+(4) We explain how constraint languages may reuse validation implementations which are provided once for each constraint type.
 
@@
 \textbf{Keywords:}
-RDF validation; RDF constraints; RDF validation requirements; Linked Data; Semantic Web
+RDF validation; RDF constraints; RDF constraint types, RDF validation requirements; Linked Data; Semantic Web
 
@@
 A typical example is the definition of a library record describing a book.
-There are clear rules which information has to be available to describe a book properly (required fields, like a title), but also how information like an ISBN number is properly represented.
+There are clear rules which information has to be available to describe a book properly, but also how information like an ISBN number is properly represented.
 Libraries seek to make their own data reusable for general purposes, but also to enrich and interlink their own data.
@@
 
-In 2013, the \emph{W3C} organized the \emph{RDF Validation Workshop}\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
-where experts from industry, government, and academia discussed first use cases for RDF data validation and constraint formulation.
+In 2013, the \emph{W3C} organized the \emph{RDF Validation Workshop}\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}
+where experts from industry, government, and academia discussed first RDF validation use cases. 
+%for RDF data validation and constraint formulation.
 In 2014, two working groups on RDF validation have been established: 
 the \emph{W3C RDF Data Shapes Working Group}\footnote{\url{http://www.w3.org/2014/rds/charter}} and the \emph{DCMI RDF Application Profiles Task Group}\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
-We collected the findings of these working groups and initiated a database of RDF validation requirements\footnote{Online available at \url{http://purl.org/net/rdf-validation}} \cite{BoschEckert2014}.
-The intention is to collaboratively collect case studies, use cases, requirements, and solutions regarding RDF validation in a comprehensive and structured way. 
+We collected the findings of these working groups and initiated a database of RDF validation requirements\footnote{Online available at \url{http://purl.org/net/rdf-validation}}
+with the intention to collaboratively collect case studies, use cases, requirements, and solutions in a comprehensive and structured way \cite{BoschEckert2014}. 
 Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group,
@@
 %each of them corresponding to a constraint type which in most cases can be expressed by multiple constraint languages. 
-each of them corresponds to a constraint type from which concrete constraints are instantiated to be checked on RDF data and
-which in most cases can be expressed by multiple constraint languages.
-Requirements/constraint types are uniquely identified by alphanumeric technical identifiers.
-\emph{Minimum qualified cardinality restrictions} (\emph{R-75}), e.g., is a constraint type which corresponds to the requirement {\small\emph{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}}.
-We recently published a technical report (serving as appendix of this paper) in which we explain each constraint type in detail and give examples for each represented by different constraint languages \cite{BoschNolleAcarEckert2015}.
+each of them corresponds to a constraint type from which concrete constraints are instantiated to be checked on RDF data. 
+%and which in most cases can be expressed by multiple constraint languages.
+%Requirements/constraint types are uniquely identified by alphanumeric technical identifiers.
+%\emph{Minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75}, e.g., is a constraint type which corresponds to the requirement {\small\emph{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}}.
+We recently published a technical report (serving as first appendix of this paper) in which we explain each constraint type in detail and give examples for each represented by different constraint languages \cite{BoschNolleAcarEckert2015}.
 More than 10 constraint languages with different syntax and semantics exist or are currently developed. 
@@
 
-We evaluated which constraint types the five most common constraint languages enable to express.
-The evaluation is explained in detail in the appendix of this paper \cite{BoschNolleAcarEckert2015}.
+We evaluated which constraint types the five most common constraint languages enable to express \cite{BoschNolleAcarEckert2015}.
+%The evaluation is explained in detail in the appendix of this paper \cite{BoschNolleAcarEckert2015}.
 Table \ref{tab:constraint-type-specific-expressivity} shows in percentage values (and absolute numbers in brackets) how many constraint types each language supports.
@@
 
-The fact that \emph{SPIN} supports all and that \emph{OWL 2} covers 2/3 of all constraint types
+The fact that \emph{SPIN} supports all and \emph{OWL 2} covers 2/3 of all constraint types
 emphasizes the significant role \emph{SPIN} and \emph{OWL 2} play for the future development of constraint languages.
@@
 although, it is not ideal for their formulation. 
-In contrast, high-level constraint languages, which may be placed on top of \emph{SPARQL} and \emph{SPIN}, are comparatively easy to understand.
-%and constraints can be formulated more concisely. 
-For the formulation of constraints, it is important that the declarative language is concise and intuitive and 
-for the validation of RDF data, it is important that it is translated into an implementation language like SPARQL and SPIN.
-
-There exists no single best solution considered as high-level intuitive constraint language which enables to express constraints easily and concisely and which is able to meet all requirements raised by data practitioners.
+In contrast, high-level constraint languages are comparatively easy to understand and constraints can be formulated more concisely.
+Declarative languages may be placed on top of \emph{SPARQL} and \emph{SPIN} when using them as implementation languages.
+
+There exists no single best solution considered as high-level intuitive constraint language which enables to express constraints in an easy and concise way and which is able to meet all requirements raised by data practitioners.
 %which can be used to express constraints and to validate RDF data, 
@@
 We lately published a technical report (serving as second appendix of this paper) in which we describe the vocabulary in detail \cite{BoschEckert2015-2} (Section \ref{sec:vocabulary}).
-The constraint type \emph{minimum qualified cardinality restrictions} (\emph{R-75}) can be instantiated to ensure
+The constraint type \emph{minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75} can be instantiated to ensure
 that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
-This constraint can either be represented generically (\emph{generic constraints}) by \emph{description logics (DL)} {\small\ms{(Publication $\sqsubseteq$ $\geq$1 author.Person)}} or specifically (\emph{specific constraints}) by multiple domain-specific constraint languages:
-
-\begin{ex}[commandchars=\\\{\}]
-\textit{OWL 2:} Publication a owl:Restriction ;
-          owl:minQualifiedCardinality 1 ;
-          owl:onProperty author ;
-          owl:onClass Person .
-
-\textit{ShEx:} Publication \{ author @Person\{1, \} \}
-
-\textit{ReSh:} Publication a rs:ResourceShape ; rs:property [
-          rs:propertyDefinition author ;
-          rs:valueShape Person ;
-          rs:occurs rs:One-or-many ; ] .
-
-\textit{DSP:} [ dsp:resourceClass Publication ; dsp:statementTemplate [ 
-          dsp:minOccur 1 ; dsp:maxOccur "infinity" ; 
-          dsp:property author ; 
-          dsp:nonLiteralConstraint [ dsp:valueClass Person ] ] ] .
-
-\textit{SPIN:} CONSTRUCT \{ [ a spin:ConstraintViolation ... . ] \} WHERE \{ 
-          ?this ?p ?o ; a ?C .
-          BIND ( \textit{qualifiedCardinality}( ?this, ?p, ?C ) AS ?c ) .
-          BIND( STRDT ( STR ( ?c ), xsd:nonNegativeInteger ) AS ?cardinality ) .
-          FILTER ( ?cardinality < ?minimumCardinality ) . \}
-
-\textit{SPIN function qualifiedCardinality:}										
-SELECT ( COUNT ( ?arg1 ) AS ?c ) WHERE \{ ?arg1 ?arg2 ?o . ?o a ?arg3 . \}
-\end{ex}
-
-The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
-For this reason, the appendix of this paper contains mappings to \emph{DL} to determine which \emph{DL} constructs are needed to express each constraint type \cite{BoschNolleAcarEckert2015}.
-As every \emph{publication} must have at least one \emph{author} which must be a \emph{person} 
-and since the book \emph{The-Lord-Of-The-Rings} is a \emph{publication}, 
+%As every \emph{publication} must have at least one \emph{author} which must be a \emph{person} 
+As the book \emph{The-Lord-Of-The-Rings} is a \emph{publication}, 
 %{\small\ms{(rdf:type(The-Lord-Of-The-Rings, Publication)),}} 
@@
 %{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)).}}
-In contrast, the book is a valid \emph{publication}, if it is connected to a \emph{person} via the property \emph{author}.
+%In contrast, the book is a valid \emph{publication}, if it is connected to a \emph{person} via the property \emph{author}.
 %{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Person)).}}
+This constraint can either be represented generically (\emph{generic constraint}) by \emph{description logics (DL)}: {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}} or specifically (\emph{specific constraint}) by multiple domain-specific constraint languages:
+
+\begin{ex}[commandchars=\\\{\}]
+\textit{OWL 2:} Publication a owl:Restriction ;
+          owl:minQualifiedCardinality 1 ;
+          owl:onProperty author ;
+          owl:onClass Person .
+
+\textit{ShEx:} Publication \{ author @Person\{1, \} \}
+
+\textit{ReSh:} Publication a rs:ResourceShape ; rs:property [
+          rs:propertyDefinition author ;
+          rs:valueShape Person ;
+          rs:occurs rs:One-or-many ; ] .
+
+\textit{DSP:} [ dsp:resourceClass Publication ; dsp:statementTemplate [ 
+          dsp:minOccur 1 ; dsp:maxOccur "infinity" ; 
+          dsp:property author ; 
+          dsp:nonLiteralConstraint [ dsp:valueClass Person ] ] ] .
+
+\textit{SPIN:} CONSTRUCT \{ [ a spin:ConstraintViolation ... . ] \} WHERE \{ 
+          ?this ?p ?o ; a ?C .
+          BIND ( \textit{qualifiedCardinality}( ?this, ?p, ?C ) AS ?c ) .
+          BIND( STRDT ( STR ( ?c ), xsd:nonNegativeInteger ) AS ?cardinality ) .
+          FILTER ( ?cardinality < ?minimumCardinality ) . \}
+
+\textit{SPIN function qualifiedCardinality:}										
+SELECT ( COUNT ( ?arg1 ) AS ?c ) WHERE \{ ?arg1 ?arg2 ?o . ?o a ?arg3 . \}
+\end{ex}
+
+The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
+For this reason, we mapped constraint types to \emph{DL} 
+in order to determine which \emph{DL} constructs are needed to express constraint types \cite{BoschNolleAcarEckert2015}.
 
 The main contributions of this paper are:
-(1) We provide a basic terminology and classification system for RDF constraints (Section \ref{sec:vocabulary}).
+(1) We provide a basic terminology and classification system for RDF constraints to lay a ground for discussions on RDF validation (Section \ref{sec:vocabulary}).
 (2) As current high-level constraint languages do not support all constraint types, 
-we developed a vocabulary to describe constraints of any RDF constraint type generically (Section \ref{sec:vocabulary}).
-(3) We show how to enhance the interoperability of constraints expressed by different constraint languages by using the proposed vocabulary as an intermediate generic representation which enables transformations between semantically equivalent constraints of the same constraint type (Section \ref{sec:transformations}).
-(4) We explain how arbitrary constraint languages may reuse validation implementations which are provided once for each constraint type (Section \ref{sec:validation}).
+we developed a vocabulary to describe constraints of any constraint type in a generic way and specified its underlying semantics (Section \ref{sec:vocabulary}).
+(3) We show how to enhance the interoperability of constraints expressed by different languages by using the proposed vocabulary 
+to intermediately represent constraints 
+%as an intermediate generic representation 
+which enables transformations between semantically equivalent constraints (Section \ref{sec:transformations}).
+(4) We explain how constraint languages may reuse validation implementations which are provided once for each constraint type (Section \ref{sec:validation}).
 
@@
 (1) to avoid the necessity to understand several languages,
-(2) to resolve misunderstandings in the communication of RDF data producers and consumers, and
+(2) to resolve misunderstandings about the meaning of particular constraints within the communication of RDF data producers and consumers, and
 (3) to enhance the interoperability of constraint languages.
@@
 Let's assume we are able to express constraints of the \emph{minimum qualified cardinality restrictions} constraint type by 10 languages.
-Without an intermediate generic representation, we would have to define for each constraint type one mapping between each pair of \emph{specific constraints} expressed by \emph{n} languages
+Without an intermediate generic representation of constraints, we would have to define for each constraint type one mapping between each pair of \emph{specific constraints} expressed by \emph{n} languages
 - that are \emph{\( {n \choose 2} \)} mappings (\emph{\( {10 \choose 2} \)} = 45 mappings).
-With an intermediate generic representation, on the other side, we only need to define for each constraint type \emph{n} mappings 
+With an intermediate generic representation of constraints, on the other side, we only need to define for each constraint type \emph{n} mappings 
 %(1 mapping for each \emph{specific constraint}) 
@@
 
-When language designers extend newly developed or existing constraint languages 
-in order to allow to formulate constraints of not yet supported constraint types,
+When language designers extend constraint languages 
+to be able to formulate constraints of not yet supported constraint types,
 our proposal prevents the necessity to actually implement the validation of data
 according to constraints of these constraint types for each of those languages.  
-We enable to offer validation implementations for any constraint type whose \emph{specific constraints} may be expressed by any language out-of-the-box 
+For any constraint language, we enable to offer a validation implementation of any constraint type out-of-the-box
+%validation implementations out-of-the-box for any constraint type whose \emph{specific constraints} may be expressed by any language  
 by providing a \emph{SPIN} mapping
 %generic validation implementations once 
-for each constraint type\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}}  whose constraints are represented generically (for further details see \cite{BoschEckert2015-2}).
+for each constraint type\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}\label{RDF-CV-2-SPIN}}  
+whose constraints are represented generically \cite{BoschEckert2015-2}.
 %(2) by transforming \emph{specific constraints} into the appropriate \emph{generic constraint}.  
-All what language designers have to do is to specify for each constraint type one mapping from the \emph{specific constraint} expressed by a particular language to the corresponding \emph{generic constraint}.
+All what language designers need to do is to specify for each constraint type they want to cover one mapping from the \emph{specific constraint} expressed by the language to the corresponding \emph{generic constraint}.
 \textcolor{red}{19} of the overall 81 constraint types are expressible by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
-This means that for these \textcolor{red}{19} constraint types there must be \textcolor{red}{76} implementations (four for each constraint type) to actually validate RDF data according to \textcolor{red}{76} \emph{specific constraints} - instead of only \textcolor{red}{19} implementations (one for each \emph{generic constraint}) which lead for each constraint type to identical validation results independently from the used language.
-
+This means that for these \textcolor{red}{19} constraint types there must be \textcolor{red}{76} implementations (four for each constraint type) to actually validate RDF data according to \textcolor{red}{76} \emph{specific constraints} - instead of only \textcolor{red}{19} implementations (one for each \emph{generic constraint}).
+%which lead for each constraint type to identical validation results independently from the language used to formulate the \emph{specific constraints}.
 Our proposal makes sure that the validation on semantically equivalent \emph{specific constraints} expressed by different languages
 leads to exactly the same validation results, 
-i.e., that validation is performed independently of the used language.
-This is not the case, however, for existing languages since they are implemented independently form each other.
-Two constraints are identical w.r.t. RDF semantics, 
-if they detect the same set of violations regardless of RDF data, 
-which means whenever the constraints are applied to any RDF data they point out the same violations.
-As we use multiple languages to express constraints of constraint types in the appendix of this paper,
-we thereby document identical semantics of these languages with regard to given constraint types \cite{BoschNolleAcarEckert2015}.
-This is also needed to prove that semantically equivalent \emph{specific constraints} and corresponding \emph{generic constraints}
-behave in the same way with regard to validation results which semantically underpins bidirectional mappings.
+i.e., that validation is performed independently from the used language.
+This is not the case, however, for existing languages due to differences in semantics and since they are implemented independently form each other.
 
@@
 For the majority of the constraint types, validation results differ (1) if the \emph{CWA} or the \emph{OWA} and (2) if the \emph{UNA} or the \emph{nUNA} is assumed \cite{BoschNolleAcarEckert2015}.
+
+Two constraints are identical w.r.t. RDF semantics, 
+if they detect the same set of violations regardless of RDF data, 
+which means whenever the constraints are applied to any RDF data they point out the same violations.
+As we use multiple languages to express constraints of constraint types, 
+%in the first appendix of this paper,
+we thereby document identical semantics of these languages with regard to given constraint types \cite{BoschNolleAcarEckert2015}.
+This is also needed to prove that semantically equivalent \emph{specific constraints} and corresponding \emph{generic constraints}
+behave in the same way with regard to validation results which semantically underpins bidirectional mappings.
 
@@
 \emph{DSP}: \url{http://dublincore.org/documents/dc-dsp},
-\emph{RDF Schemarama}: \url{http://swordfish.rdfweb.org/discovery/2001/01/schemarama},
-\emph{Schematron}: \url{http://www.schematron.com},
-\emph{XML Schema}: \url{http://www.w3.org/TR/xmlschema-1},
+\emph{RDF Schemarama}: \url{http://swordfish.rdfweb.org/discovery/2001/01/schemarama}
+%\emph{Schematron}: \url{http://www.schematron.com},
+%\emph{XML Schema}: \url{http://www.w3.org/TR/xmlschema-1},
 }.
@@
 %
-\emph{Schematron} is an ISO standard for the validation and quality control of XML documents based on XPath and XSLT. 
-%
-\emph{XML Schema} is the primary technology for specifying and constraining the structure of XML documents.
+%\emph{Schematron} is an ISO standard for the validation and quality control of XML documents based on XPath and XSLT. 
+%
+%\emph{XML Schema} is the primary technology for specifying and constraining the structure of XML documents.
 %
@@
 
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
-
------
+There exists no single best solution considered as high-level intuitive constraint language which enables to express constraints in an easy and concise way and which is able to meet all requirements raised by data practitioners.
+Thus, the idea behind this paper is to satisfy all RDF validation requirements
+by representing constraints of any constraint type in a generic way using a lightweight vocabulary which consists of only a few terms.
+
+Constraints can either be represented generically (\emph{generic constraint}) by \emph{description logics (DL)} or specifically (\emph{specific constraint}) by domain-specific constraint languages.
+Hence, we mapped constraint types to \emph{DL} 
+in order to determine which \emph{DL} constructs are needed to express constraint types \cite{BoschNolleAcarEckert2015}.
+
+We provide a basic terminology and classification system for RDF constraints to lay a ground for discussions on RDF validation (Section \ref{sec:vocabulary}).
+
+As there is no standard way to formulate constraints, 
+semantically equivalent \emph{specific constraints} may be represented by a variety of languages - each of them having different syntax and semantics.
+We propose transformations between semantically equivalent \emph{specific constraints}
+by using the proposed vocabulary to intermediately represent constraints in a generic way
+(1) to avoid the necessity to understand several languages,
+(2) to resolve misunderstandings about the meaning of particular constraints, and
+(3) to enhance the interoperability of constraint languages (Section \ref{sec:transformations}).
+
+We use \emph{SPIN} as basis to develop a validation environment\footref{rdf-validator} to validate RDF data according to constraints of constraint types which are expressible by arbitrary constraint languages by mapping them to \emph{SPIN}\footref{spin-mappings} \cite{BoschEckert2014-2}.
+When language designers extend constraint languages 
+to be able to formulate constraints of not yet supported constraint types,
+our proposal enables to reuse the validation implementation of these constraint types 
+by mapping \emph{specific constraints} expressed by the language to the corresponding \emph{generic constraint}.
+For any constraint language, we enable to offer a validation implementation of any constraint type out-of-the-box
+by providing a \emph{SPIN} mapping
+for each constraint type\footref{RDF-CV-2-SPIN}  
+whose constraints are represented generically \cite{BoschEckert2015-2}. 
+Furthermore, our proposal makes sure that the validation on semantically equivalent \emph{specific constraints} expressed by different languages
+leads to exactly the same validation results, 
+i.e., that validation is performed independently from the used language (Section \ref{sec:validation}).
 
 It is part of future work 
-(1) to extend the \emph{RDF Validator} by creating \emph{generic constraints} automatically according to inputs of domain experts who may not be familiar with the formulation of constraints,
-(2) to offer bidirectional transformations between all \emph{specific constraints} (expressed by all existing constraint languages) and the corresponding \emph{generic constraints}, and
-(3) to provide translations between semantically equivalent \emph{specific constraints} (expressed by any constraint language) by using \emph{generic constraints} as an intermediate transformation step.
+(1) to extend the \emph{RDF Validator} by generating \emph{generic constraints} according to inputs of domain experts who may not be familiar with the formulation of constraints,
+(2) to offer bidirectional transformations between \emph{specific constraints} expressed by the most common constraint languages and corresponding \emph{generic constraints}, and
+(3) to provide translations between semantically equivalent \emph{specific constraints} expressed by the most common constraint languages by using \emph{generic constraints} as intermediate representation.
+
 %\begin{itemize}

### 2015-05-29 paper/paper 2/dc-2015.tex
RDF-CV

@@
 The main contributions of this paper are:
-(1) We provide a basic terminology and classification system for RDF constraints to lay a ground for discussions on RDF validation.
+(1) We provide a basic terminology and classification system for RDF constraints to lay the ground for discussions on RDF validation.
 (2) As current high-level constraint languages do not support all constraint types, 
@@
 The main contributions of this paper are:
-(1) We provide a basic terminology and classification system for RDF constraints to lay a ground for discussions on RDF validation (Section \ref{sec:vocabulary}).
+(1) We provide a basic terminology and classification system for RDF constraints to lay the ground for discussions on RDF validation (Section \ref{sec:vocabulary}).
 (2) As current high-level constraint languages do not support all constraint types, 
@@
 Prerequisites to develop a vocabulary to describe constraints of any constraint type in a generic way are 
-(1) to specify the underlying semantics for validation and thus for the vocabulary and (2) to define a basic terminology and classification system to formulate constraints.
+(1) to specify the underlying semantics for validation and thus for the vocabulary and (2) to define a basic terminology and classification system for RDF constraints which lay the ground for discussions on validation.
 
@@
 This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past.
-We compare semantics of RDF validation and of \emph{OWL 2} as we consider \emph{OWL 2} as a constraint language 
-when RDF validation semantics are applied.
+We compare semantics of RDF validation and \emph{OWL 2} as \emph{OWL 2} is considered as a constraint language 
+when validation semantics is applied.
 %
 \emph{OWL 2} is based on the {\em open-world assumption} (\emph{OWA}), i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose to represent knowledge on the \emph{WWW}.
-As each \emph{book} must have a \emph{title} {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a \emph{book} {\small\ms{(Book(Hamlet)),}}
-{\em Hamlet} must have at least one \emph{title} as well.
-In an \emph{OWA} setting, this constraint does not cause a violation, even if there is no explicitly defined \emph{title}, since there must be a \emph{title} for this \emph{book} which we may not know ($\mathcal{K}$ is consistent).
+As each \emph{book} must have a \emph{title} {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a \emph{book}, %{\small\ms{(Book(Hamlet)),}}
+{\em Hamlet} must have at least one \emph{title}.
+In an \emph{OWA} setting, this constraint does not cause a violation, even if there is no explicitly defined \emph{title}, since there must be a \emph{title} for this \emph{book} which we may not know.
+%($\mathcal{K}$ is consistent).
 As RDF validation has its origin in the XML world
@@
 Thus, classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals. 
-In the example, the \emph{CWA} yields to a violation since there is no explicitly defined \emph{title} for the \emph{book} {\em Hamlet}.
-
+The \emph{CWA} yields to a violation since there is no explicitly defined \emph{title} for the \emph{book} {\em Hamlet}. 
+%
 Validation requires that different names represent different objects (\emph{unique name assumption (UNA)}), whereas,
@@
 If validation would assume \emph{OWA} and \emph{nUNA}, validation won’t be that restrictive and therefore we won’t get the intended validation results.
-
+%
 %\emph{OWL 2} reasoning is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true. 
@@
 No.}
-
+%
 %comments from Erman:
-
+%
 %\begin{itemize}
@@
 We have to provide formal generic semantics for it; formally prove those statements.}
-
+%
 %\item This is simple. You write that:
@@
 That shows that they behave in the same way, as they should.
-
+%
 %\item So if you read again my comment again, without knowing which semantics those constraint languages have, one actually does is to show, given an RDF-data it is violated in one language iff it is violated in other.
 And this actually corresponds to the very idea of transformation and generic semantics.
-
+%
 %\item Now, what is a generic semantics? 
@@
 %\end{itemize}
-
+%
 Differences in semantics may lead to differences in validation results when applied to particular constraint types.
-For the majority of the constraint types, validation results differ (1) if the \emph{CWA} or the \emph{OWA} and (2) if the \emph{UNA} or the \emph{nUNA} is assumed \cite{BoschNolleAcarEckert2015}.
-
-Two constraints are identical w.r.t. RDF semantics, 
+This is important 
+as for 56.8\% of the constraint types validation results differ if the \emph{CWA} or the \emph{OWA} 
+and as for 66.6\% of the constraint types validation results are different in case the \emph{UNA} or the \emph{nUNA} is assumed \cite{BoschNolleAcarEckert2015}.
+
+Constraints are identical w.r.t. RDF semantics, 
 if they detect the same set of violations regardless of RDF data, 
@@
 we thereby document identical semantics of these languages with regard to given constraint types \cite{BoschNolleAcarEckert2015}.
-This is also needed to prove that semantically equivalent \emph{specific constraints} and corresponding \emph{generic constraints}
-behave in the same way with regard to validation results which semantically underpins bidirectional mappings.
+This is also important to prove that semantically equivalent \emph{specific constraints} and corresponding \emph{generic constraints}
+behave in the same way w.r.t. validation results which semantically underpins bidirectional mappings.
 
@@
 As there are already five promising constraint languages, 
-our purpose is not to propose a new language.
-We rather developed a very simple lightweight vocabulary,
+our purpose was not to invent a new language.
+As there is no high-level declarative language which meets all RDF validation requirements,
+we rather developed a very simple lightweight vocabulary,
 consisting of only three classes, three object properties, and three data properties, 
@@
 
-We identified four dimensions to classify sets of constraints which can be instantiated from constraint types.
-For each constraint type, we evaluated \cite{BoschNolleAcarEckert2015} in with which set of constraints their instances of contained.
-For each set of constraints, we state the rounded number of associated constraint types in brackets.
+We classify sets of constraints according to four dimensions.
+For each constraint type, we evaluated \cite{BoschNolleAcarEckert2015} in which set of constraints their instances are contained.
+%In the following, we state the rounded number of associated constraint types in brackets.
 %\begin{itemize}
@@
 or specifically (\emph{specific constraints}) by domain-specific constraint languages. 
+As we express constraints of each constraint type in form of \emph{generic constraints} conforming to the \emph{RDF-CV} \cite{BoschNolleAcarEckert2015},
+we show that constraints of any constraint type can be described generically.
 \textbf{\emph{DL Expressivity}:}
 The \emph{RDF-CV} allows to describe 
-constraints which are \emph{expressible in DL} (70\%) and which are \emph{not expressible in DL} (30\%). 
-In case a constraint type is \emph{expressible in DL}, we determined which \emph{DL} constructs are needed to express the constraint type.
-In addition, we mapped constraints of each constraint type to \emph{generic constraints} conforming to the \emph{RDF-CV} \cite{BoschNolleAcarEckert2015}.
-This way, we show that constraints of each constraint type are representable as \emph{generic constraints} and therefore can be described generically by means of the \emph{RDF-CV}.
+constraints which are \emph{expressible in DL} (constraints of this set are instantiated from 70\% of the overall 81 constraint types) and which are \emph{not expressible in DL} (30\%). 
+%In case a constraint type is \emph{expressible in DL}, we determined which \emph{DL} constructs are needed to express the constraint type.
 \textbf{\emph{Complexity}:}
-\emph{Simple constraints} (2/3) denotes the set of atomic constraints. 
+\emph{Simple constraints} (2/3 of the constraint types) denotes the set of atomic constraints. 
 %which can be instantiated from almost 2/3 of the constraint types.
@@
 %and which are instances of 1/4 of the constraint types.
-In case \emph{complex constraints} are expressible in \emph{DL}, 
-\emph{DL} statements representing \emph{complex constraints} contain \emph{DL} statements standing for atomic and/or composed constraints. 
-The constraints of almost 15\% of the constraint types are \emph{complex constraints}
+%In case \emph{complex constraints} are expressible in \emph{DL}, 
+%\emph{DL} statements representing \emph{complex constraints} contain \emph{DL} statements standing for atomic and/or composed constraints. 
+Constraints of almost 15\% of the constraint types are \emph{complex constraints}
 which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
@@
 
-Constraints of almost 15\% of the constraint types are \emph{complex constraints}
-which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
+\emph{Complex constraints} can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
 %There are three forms of \emph{OWL RBox axioms}: \emph{role inclusions}, \emph{equivalence} and \emph{disjointness}. 
@@
 
+Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group,
+we published by today 81 requirements to validate RDF data and to formulate constraints; 
+each of them corresponds to a constraint type from which concrete constraints are instantiated to be checked on RDF data.
+
 There exists no single best solution considered as high-level intuitive constraint language which enables to express constraints in an easy and concise way and which is able to meet all requirements raised by data practitioners.
@@
 by representing constraints of any constraint type in a generic way using a lightweight vocabulary which consists of only a few terms.
-
 Constraints can either be represented generically (\emph{generic constraint}) by \emph{description logics (DL)} or specifically (\emph{specific constraint}) by domain-specific constraint languages.
@@
 in order to determine which \emph{DL} constructs are needed to express constraint types \cite{BoschNolleAcarEckert2015}.
-
-We provide a basic terminology and classification system for RDF constraints to lay a ground for discussions on RDF validation (Section \ref{sec:vocabulary}).
+Prerequisites to develop a vocabulary to describe constraints of any constraint type in a generic way are 
+(1) to specify the underlying semantics for validation and thus for the vocabulary and (2) to define a basic terminology and classification system for RDF constraints which lay the ground for discussions on validation \ref{sec:vocabulary}).
 

### 2015-05-29 paper/paper 2/dc-2015.tex
images

@@
 We call this vocabulary the \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}} whose conceptual model is shown in Figure \ref{fig:RDF-CV-conceptual-model}.
-\begin{figure}
+\begin{figure}[H]
 	\centering
 		\includegraphics[width=0.60\textwidth]{images/RDF-CV-conceptual-model.png}
-	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} - Conceptual Model}
+	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} Conceptual Model}
 	\label{fig:RDF-CV-conceptual-model}
@@
 
-The implementation model of the \emph{RDF-CV} (see Figure \ref{fig:RDF-CV-implementation-model}) shows that
+The implementation model of the \emph{RDF-CV} (Figure \ref{fig:RDF-CV-implementation-model}) shows that
 both \emph{property constraints} and \emph{class constraints} are \emph{simple constraints}. 
@@
 %Lists of \emph{left} and \emph{right properties} can only be specified for \emph{property constraints}.
-\begin{figure}
+\begin{figure}[H]
 	\centering
-		\includegraphics[width=0.60\textwidth]{images/RDF-CV-implementation-model.png}
-	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} - Implementation Model}
+		\includegraphics[width=0.80\textwidth]{images/RDF-CV-implementation-model.png}
+	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} Implementation Model}
 	\label{fig:RDF-CV-implementation-model}
@@
 which holds for all individuals of the class \emph{Publication}.
-Table \ref{tab:property-constraint-cardinality-restriction} displays the mapping to the \emph{RDF-CV}:
+Table \ref{tab:property-constraint-cardinality-restriction} displays the mapping to the \emph{RDF-CV}.
 \begin{table}[H]
@@
   \vspace{0cm}
-	\caption{Property Constraint - Minimum Qualified Cardinality Restriction}
+	\caption{Minimum Qualified Cardinality Restriction as Property Constraint}
 	\label{tab:property-constraint-cardinality-restriction}
 	\centering
-		\begin{tabular}{l|l|l|l|l|l|l}
-      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+		\begin{tabular}{c|c|c|c|c|c|c}
+      \textbf{constraint set} & \textbf{context class} & \textbf{left property list} & \textbf{right p. list} & \textbf{classes} & \textbf{constraining element} & \textbf{c. value} \\
       \hline
@@
 
-The \emph{constraining element} indicates the actual type of constraint like \emph{DL} concept and role constructors, (in)equality, and further keywords for constraint types which cannot be expressed in \emph{DL} (e.g., regular expressions and constraining facets).
-In some cases, a constraint is only complete when a \emph{constraining value} is stated in addition to the \emph{constraining element}.
-\emph{Simple constraints} may also refer to a list of \emph{classes}.
+The \emph{constraining element} indicates the actual type of constraint like \emph{DL} concept and role constructors, (in)equality, and further keywords for constraint types whose constraints cannot be expressed in \emph{DL} (e.g., regular expressions and constraining facets).
+In some cases, a constraint is only complete when a \emph{constraining value} is stated in addition to the \emph{constraining element}
+and \emph{simple constraints} may refer to a list of \emph{classes}.
 The \emph{constraining element} of the \emph{property constraint} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person},} e.g.,  is the \emph{DL at-least restriction} \emph{$\geq$}, the \emph{constraining value} is \emph{1}, and
@@
 %{\small\ms{(authorOfGenre(Stephen-Hawking, Popular-Science))}.}
-Thus, when mapped to the \emph{RDF-CV} (Table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are on the left side of the \emph{constraining element} \emph{$\sqsubseteq$}
-and the property \emph{authorOfGenre} is on the right side.
-As this \emph{property constraint} holds all individuals, the \emph{context class} is the \emph{DL top concept} $\top$ which stands for the super-class of all classes.
+Thus, when mapped to the \emph{RDF-CV} (Table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are placed on the left side of the \emph{constraining element} \emph{$\sqsubseteq$}
+and the property \emph{authorOfGenre} on the right side.
+As this \emph{property constraint} holds for all individuals within the data, the \emph{context class} is the \emph{DL top concept} $\top$ which stands for the super-class of all classes.
 \begin{table}[H]
@@
   \vspace{0cm}
-	\caption{Property Constraint - Object Property Paths}
+	\caption{Object Property Paths as Property Constraint}
 	\label{tab:property-constraint-object-property-paths}
@@
 is reused within the list of \emph{classes} the \emph{complex constraint} refers to.
-The \emph{literal pattern matching} constraint type introduces the new \emph{constraining element} \emph{regex}.
-The validation of each \emph{constraining element}, so for \emph{regex}, has to be implemented only once.
+The \emph{literal pattern matching} constraint type introduces the \emph{constraining element} \emph{regex}
+whose validation has to be implemented once like for any other \emph{constraining element}.
 %In general, validation has to be implemented once for each \emph{generic constraint type} which is not expressible in \emph{DL}. 
@@
   \vspace{0cm}
-	\caption{Simple Constraint (Not Expressible in DL)}
+	\caption{Simple Constraints which are not Expressible in DL)}
 	\label{tab:simple-constraint-not-expressible-in-dl)}
@@
 %\emph{Complex constraints} are composed out of \emph{simple constraints} and/or \emph{complex constraints}.
-\emph{Context-specific exclusive or of property groups} (\emph{R-13}) \emph{complex constraints}
+\emph{Complex constraints} of the constraint type \emph{context-specific exclusive or of property groups} (\emph{R-13}) 
 restrict individuals of given classes to have all properties of exactly one of multiple mutually exclusive property groups.
 \emph{Publications}, e.g., are either identified by an \emph{ISBN} and a \emph{title} (for books) or by an \emph{ISSN} and a \emph{title} (for periodical \emph{publications}), but it should not be possible to assign both identifiers to a given \emph{publication}.
-As the \emph{The-Great-Gatsby} is a \emph{publication} with an \emph{ISBN} and a \emph{title} without an \emph{ISSN}, 
+As \emph{The-Great-Gatsby} is a \emph{publication} with an \emph{ISBN} and a \emph{title} without an \emph{ISSN}, 
 \emph{The-Great-Gatsby} is considered as a valid \emph{publication}.
-This \emph{complex constraint} is expressible specifically by \emph{ShEx} and generically by \emph{DL} (and can therefore be mapped to the \emph{RDF-CV} \cite{BoschEckert2015-2}):
+The \emph{complex constraint} is generically expressible by \emph{DL}:
+%This \emph{complex constraint} is expressible specifically by \emph{ShEx} and generically by \emph{DL} (and can therefore be mapped to the \emph{RDF-CV} \cite{BoschEckert2015-2}).
 
@@
 
-\begin{ex}[commandchars=\\\{\}]
-\textit{ShEx:} Publication { ( isbn string , title string ) | ( issn string , title string ) }
-\end{ex}
+%\begin{ex}[commandchars=\\\{\}]
+%\textit{ShEx:} Publication { ( isbn string , title string ) | ( issn string , title string ) }
+%\end{ex}
 
@@
 As \emph{exact (un)qualified cardinality restrictions (=n)} and \emph{exclusive or (XOR)} are frequently used \emph{complex constraints},
-we propose using them in terms of syntactic sugar as \emph{simple constraints}.
+we propose to simplify them as \emph{simple constraints} in terms of syntactic sugar.
 As a consequence, the \emph{context-specific exclusive or of property groups} \emph{complex constraint} is represented as a \emph{generic constraint} by means of the \emph{RDF-CV} more intuitively and concisely (Table \ref{tab:simplified-complex-constraints}).
@@
 
-\emph{Complex constraints} can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
+%\emph{Complex constraints} can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
 %There are three forms of \emph{OWL RBox axioms}: \emph{role inclusions}, \emph{equivalence} and \emph{disjointness}. 
@@
 \emph{Books}, e.g., are uniquely identified by their \emph{ISBN}, i.e., the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}
-which can be represented using the \emph{RDF-CV} in form of a \emph{complex constraint} consisting of two \emph{simple constraints} (Table \ref{tab:primary-key-properties-as-complex-constraints}):
+which can be represented using the \emph{RDF-CV} in form of a \emph{complex constraint} consisting of two \emph{simple constraints} (Table \ref{tab:primary-key-properties-as-complex-constraints}).
 
@@
 When using \emph{keyfor} (\ms{isbn keyfor Book}), 
-the \emph{complex constraint} can be simplified as a \emph{simple constraint} which looks like the following in RDF turtle syntax:
+the \emph{complex constraint} can be formulated as a \emph{simple constraint} which looks like the following in concrete RDF turtle syntax:
 
@@
 can also be simplified in the same way, 
-as such axioms can be expressed using the basic features of \emph{DL} but can also be abbreviated when using them in form of syntactic sugar \cite{BoschEckert2015-2}
+as, although, such axioms can be expressed using basic \emph{DL} features, 
+\emph{DL} axioms like \emph{transitivity} can also be used in terms of syntactic sugar \cite{BoschEckert2015-2}.
 %Starfleet officers, e.g., are uniquely identified by their command authorization code (e.g. to activate and cancel auto-destruct sequences).

### 2015-05-29 paper/RDF validation requirements/RDF validation requirements.tex
evaluation

@@
 	\hline
-  \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+  \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
   \hline
@@
 \begin{gcotable}
-property & $\exists$ knows . Self & knows & - & Self & $\exists$ \\
-class & $\neg$ $\exists$ knows . Self & - & - & $\exists$ knows . Self & $\neg$ \\
-class & $\top$ & - & - & $\top$, $\neg$ $\exists$ knows . Self & $\sqsubseteq$ \\
+property & $\exists$ marriedTo . Self & knows & - & Self & $\exists$ \\
+class & $\neg$ $\exists$ marriedTo . Self & - & - & $\exists$ marriedTo . Self & $\neg$ \\
+class & $\top$ & - & - & $\top$, $\neg$ $\exists$ marriedTo . Self & $\sqsubseteq$ \\
 \end{gcotable}
@@
 \emph{Class-Specific Irreflexive Object Properties} are object properties which are irreflexive within a given context, e.g. a class.
+
+\subsection{Simple Example}
+
+\emph{Persons} cannot be married to themselves.
+
+\begin{DL}
+Person $\sqsubseteq$ $\neg$ $\exists  marriedTo . Self$ 
+\end{DL}
+
+\begin{gcotable}
+property & $\exists$ marriedTo . Self & knows & - & Self & $\exists$ \\
+class & $\neg$ $\exists$ marriedTo . Self & - & - & $\exists$ knows . Self & $\neg$ \\
+class & Person & - & - & Person, $\neg$ $\exists$ marriedTo . Self & $\sqsubseteq$ \\
+\end{gcotable}
+
+syntactic sugar:
+
+\begin{gcotable}
+property & Person & marriedTo & - & - & irreflexive \\
+\end{gcotable}
 
@@
 
+Any provenance information must be available for instances of given classes.
+
+\subsection{Simple Example}
+
+For \emph{publications}, any provenance information must be available.
+
+\begin{DL}
+Not expressible in DL!
+\end{DL}
+
+\begin{gcotable}
+class & Publication & - & - & - & provenance & - \\
+\end{gcotable}
+
 \section{Data Model Consistency}
@@
 
+\begin{DL}
+Not expressible in DL!
+\end{DL}
+
 \section{Structure}
@@
 
+\begin{DL}
+Not expressible in DL!
+\end{DL}
+
 \section{Labeling and Documentation}
 
+\begin{DL}
+Not expressible in DL!
+\end{DL}
+
 \section{Vocabulary}
+
 Vocabularies should not invent any new terms or use deprecated elements.
 
+\subsection{Simple Example}
+
+\begin{DL}
+Not expressible in DL!
+\end{DL}
+
+\begin{gcotable}
+class & $\top$ & - & - & - & vocabulary & - \\
+\end{gcotable}
+
 \section{HTTP URI Scheme Violation}
+
+\subsection{Simple Example}
+
+\begin{DL}
+Not expressible in DL!
+\end{DL}
+
+\begin{gcotable}
+class & $\top$ & - & - & - & HTTP URI Scheme Violation & - \\
+\end{gcotable}
 
@@
 \begin{evaluation-generic-overview}
-Property Constraints & 48 & 65 (64.86) \\
-Class Constraints & 17 & 23 (22.96) \\
-Property and Class Constraints & 9 & 12 (12.16) \\
+Property Constraints & 49 & 60 (60.49) \\
+Class Constraints & 20 & 25 (24.96) \\
+Property and Class Constraints & 12 & 15 (14.81) \\
 \hline
-Simple Constraints & 46 & 62 (62.16) \\
-Simple Constraints (Syntactic Sugar) & 10 & 14 (13.51) \\
-Complex Constraints & 18 & 24 (24.32) \\
+Simple Constraints & 49 & 60 (60.49) \\
+Simple Constraints (Syntactic Sugar) & 11 & 14 (13.58) \\
+Complex Constraints & 21 & 26 (25.93) \\
 \hline
-DL Expressible & 51 & 69 (68.92) \\
-DL Not Expressible & 23 & 31 (31.08) \\
+DL Expressible & 52 & 64 (64.2) \\
+DL Not Expressible & 29 & 36 (35.80) \\
 \hline
-Total & 74 & 100 \\
+Total & 81 & 100 \\
 \end{evaluation-generic-overview}
@@
 Aggregations & $\checkmark$ & $\checkmark$ & \ding{55} \\
-*Class-Specific Irreflexive Object Properties & & & \\
-Provenance & & & \\
-Data Model Consistency & & & \\
-Structure & & & \\  
-Labeling and Documentation & & & \\
-Vocabulary & & & \\
-HTTP URI Scheme Violation & & & \\
+
+*Class-Specific Irreflexive Object Properties & $\checkmark$ & $\sim$ & $\checkmark$ \\
+Provenance & \ding{55} & $\checkmark$ & \ding{55} \\
+Data Model Consistency & $\sim$ & \ding{55} & \ding{55} \\
+Structure & $\sim$ & \ding{55} & \ding{55} \\ 
+Labeling and Documentation & $\sim$ & \ding{55} & \ding{55} \\
+Vocabulary & \ding{55} & $\checkmark$ & \ding{55} \\
+HTTP URI Scheme Violation & \ding{55} & $\checkmark$ & \ding{55} \\
 \end{evaluation-generic}

### 2015-05-29 paper/paper 2/dc-2015.tex
evaluation

@@
 All what language designers need to do is to specify for each constraint type they want to cover one mapping from the \emph{specific constraint} expressed by the language to the corresponding \emph{generic constraint}.
-\textcolor{red}{19} of the overall 81 constraint types are expressible by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
-This means that for these \textcolor{red}{19} constraint types there must be \textcolor{red}{76} implementations (four for each constraint type) to actually validate RDF data according to \textcolor{red}{76} \emph{specific constraints} - instead of only \textcolor{red}{19} implementations (one for each \emph{generic constraint}).
+19 of the overall 81 constraint types are expressible by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
+This means that for these 19 constraint types there must be 76 implementations (four for each constraint type) to actually validate RDF data according to 76 \emph{specific constraints} - instead of only 19 implementations (one for each \emph{generic constraint}).
 %which lead for each constraint type to identical validation results independently from the language used to formulate the \emph{specific constraints}.
@@
 The \emph{RDF-CV} allows to describe 
-constraints which are \emph{expressible in DL} (constraints of this set are instantiated from 70\% of the overall 81 constraint types) and which are \emph{not expressible in DL} (30\%). 
+constraints which are \emph{expressible in DL} (constraints of this set are instantiated from 64\% of the overall 81 constraint types) and which are \emph{not expressible in DL} (36\%). 
 %In case a constraint type is \emph{expressible in DL}, we determined which \emph{DL} constructs are needed to express the constraint type.
 \textbf{\emph{Complexity}:}
-\emph{Simple constraints} (2/3 of the constraint types) denotes the set of atomic constraints. 
+\emph{Simple constraints} (60\% of the constraint types) denotes the set of atomic constraints. 
 %which can be instantiated from almost 2/3 of the constraint types.
-\emph{Complex constraints} (1/4) is the set of constraints which are created out of \emph{simple} and/or other \emph{complex constraints}.
+\emph{Complex constraints} (26\%) is the set of constraints which are created out of \emph{simple} and/or other \emph{complex constraints}.
 %and which are instances of 1/4 of the constraint types.
@@
 %\emph{DL} statements representing \emph{complex constraints} contain \emph{DL} statements standing for atomic and/or composed constraints. 
-Constraints of almost 15\% of the constraint types are \emph{complex constraints}
+Constraints of almost 14\% of the constraint types are \emph{complex constraints}
 which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
 \textbf{\emph{Context}:}
-\emph{Simple constraints} are applied on properties (\emph{property constraints}, 2/3),
-on classes (\emph{class constraints}, 1/5), or
-on properties and classes (\emph{property and class constraints}, 1/10).
+\emph{Simple constraints} are applied on properties (\emph{property constraints}, 60\%),
+on classes (\emph{class constraints}, 25\%), or
+on properties and classes (\emph{property and class constraints}, 15\%).
 %2/3 of all constraint types are types of \emph{property constraints}, 
@@
 
+%Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group, 
+%we published by today 81 constraint types \cite{BoschNolleAcarEckert2015}
+%which form the basis to
+%lay the ground for discussions on validation
+%by defining a basic terminology and classification system for RDF constraints.
+
 Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group,
@@
 each of them corresponds to a constraint type from which concrete constraints are instantiated to be checked on RDF data.
-
+These constraint types form the basis to
+lay the ground for discussions on validation
+by defining a basic terminology and classification system for RDF constraints.
+%
 There exists no single best solution considered as high-level intuitive constraint language which enables to express constraints in an easy and concise way and which is able to meet all requirements raised by data practitioners.
-Thus, the idea behind this paper is to satisfy all RDF validation requirements
+Thus, the idea behind this paper is to satisfy all requirements
 by representing constraints of any constraint type in a generic way using a lightweight vocabulary which consists of only a few terms.
-Constraints can either be represented generically (\emph{generic constraint}) by \emph{description logics (DL)} or specifically (\emph{specific constraint}) by domain-specific constraint languages.
-Hence, we mapped constraint types to \emph{DL} 
-in order to determine which \emph{DL} constructs are needed to express constraint types \cite{BoschNolleAcarEckert2015}.
-Prerequisites to develop a vocabulary to describe constraints of any constraint type in a generic way are 
-(1) to specify the underlying semantics for validation and thus for the vocabulary and (2) to define a basic terminology and classification system for RDF constraints which lay the ground for discussions on validation \ref{sec:vocabulary}).
+%To show that constraints can either be represented specifically (\emph{specific constraints}) by constraint languages
+%or generically (\emph{generic constraints}) by \emph{description logics (DL)},
+%we mapped constraint types to \emph{DL} 
+%to determine which \emph{DL} constructs are needed to express them \cite{BoschNolleAcarEckert2015} (Section \ref{sec:vocabulary}).
 
@@
 (2) to offer bidirectional transformations between \emph{specific constraints} expressed by the most common constraint languages and corresponding \emph{generic constraints}, and
-(3) to provide translations between semantically equivalent \emph{specific constraints} expressed by the most common constraint languages by using \emph{generic constraints} as intermediate representation.
+(3) to provide translations between semantically equivalent \emph{specific constraints} expressed by the most common constraint languages by using the developed vocabulary to intermediately represent constraints.
+Identifying RDF validation requirements is an ongoing process,
+so the task to map constraints of new constraint types to the vocabulary.
 

### 2015-06-11 paper/RDF validation requirements/RDF validation requirements.tex
abstract

@@
 
+\begin{DL}
+Not expressible in DL!
+\end{DL}
+
 \section{Literal Pattern Matching}
@@
 \begin{gcotable}
-property & $\top$ & position & - & 1-23 & range & - \\
-class & 1-23 & - & - & xsd:nonNegativeInteger & $\geq$ & 1 \\
-class & 1-23 & - & - & xsd:nonNegativeInteger & $\leq$ & 23 \\
+class & NumberPlayersPerWorldCupTeam & - & - & $\geq$1, $\leq$23 & $\sqcap$ & - \\
+class & $\geq$1 & - & - & xsd:nonNegativeInteger & $\geq$ & 1 \\
+class & $\leq$23 & - & - & xsd:nonNegativeInteger & $\leq$ & 23 \\
 \end{gcotable}
@@
 
+\subsection{Constraining Elements of Constraint Types}
+
+\begin{itemize}
+  \item Constraints of 64\% of all constraint type can be expressed using logical constructs from description logics.
+	\item We developed a vocabulary and for each constraint type we identified constraining elements to represent constraints of any constraint type.
+
+	\item In most cases, it is sufficient to use only 1 logical construct
+	\item Some combinations of logical constructs can be simplified to 1 logical construct which can be used in terms of syntactic sugar
+  \item constraints of the majority of the constraint types can be expressed logically by description logics
+	\item constraints of all constraint types can be expressed by constraining elements
+	\item For 1 constraint types, there can be multiple constraining elements
+	\item the validation of each constraining element has to be implemented
+	\item We use SPARQL as extension mechanism to express constraints of 3 constraint types which cannot be expressed otherwise as they are too complex to represent them using a high-level constraint language
+\end{itemize}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{lll}
+           \multicolumn{1}{l}{\textbf{Constraint Type}} & \multicolumn{1}{l}{\textbf{DL}} & \multicolumn{1}{l}{\textbf{Constraining Elements}}			 
+    \\ \midrule
+
+*Subsumption & $\sqsubseteq$ & sub-classes \\
+*Class Equivalence & $\equiv$ & equivalent classes \\
+*Sub Properties & $\sqsubseteq$ & sub-properties \\
+*Property Domain & $\exists$, $\sqsubseteq$ & domain \\
+*Property Range & $\sqsubseteq$, $\forall$ & range \\
+*Inverse Object Properties & inverse & \\
+%*Symmetric Object Properties & $\equiv$, inverse & symmetric \\
+*Symmetric Object Properties & symmetric &  \\
+%*Asymmetric Object Properties & $\sqsubseteq$, inverse & asymmetric \\
+*Asymmetric Object Properties & asymmetric &  \\
+%*Reflexive Object Properties & $\exists$, $\sqsubseteq$ & \textcolor{green}{reflexive} \\
+*Reflexive Object Properties & reflexive &  \\
+%*Irreflexive Object Properties & $\exists$, $\neg$, $\sqsubseteq$ & irreflexive \\
+*Irreflexive Object Properties & reflexive, $\neg$ & irreflexive \\
+Disjoint Properties & $\sqsubseteq$, $\neg$ & $\ne$ \\
+Disjoint Classes & $\sqcap$, $\sqsubseteq$ & $\ne$ \\
+Context-Sp. Property Groups & $\sqcap$ & property groups \\
+Context-Sp. Inclusive OR of P. & $\sqcup$ & inclusive or \\
+Context-Sp. Inclusive OR of P. Groups & $\sqcup$, $\sqcap$ & inclusive or, \\
+                                                          && property groups \\
+Recursive Queries & - & recursive \\
+Individual Inequality & $\ne$ & \\
+*Equivalent Properties & $\equiv$ & equivalent properties \\
+Property Assertions & = or $\ne$ & \\
+Data Property Facets & - & XSD or SPARQL constraining facets \\
+                        && examples: regex, xsd:pattern, ... \\
+Literal Pattern Matching & - & regex or xsd:pattern \\
+Negative Literal Pattern Matching & - & regex or xsd:pattern, $\neg$ \\ 
+*Object Property Paths & $\sqsubseteq$ & property paths \\
+*Intersection & $\sqcap$ & intersection \\
+*Disjunction & $\sqcup$ & disjunction \\
+*Negation & $\neg$ & negation \\
+*Existential Quantification & $\exists$ & existential quantification \\
+*Universal Quantification & $\forall$ & universal quantification \\
+*Minimum Unqualified Cardinality & $\geq$ & \\
+*Minimum Qualified Cardinality & $\geq$ & \\
+*Maximum Unqualified Cardinality & $\leq$ & \\
+*Maximum Qualified Cardinality & $\leq$ & \\
+*Exact Unqualified Cardinality & $\geq$, $\leq$, $\sqcap$ & = \\
+*Exact Qualified Cardinality & $\geq$, $\leq$, $\sqcap$ & = \\
+*Transitive Object Properties & $\sqsubseteq$ & transitive \\
+Context-Sp. Exclusive OR of P. & $\neg$, $\sqcap$, $\sqcup$ & XOR \\
+Context-Sp. Exclusive OR of P. Groups & $\neg$, $\sqcap$, $\sqcup$ & XOR, $\sqcap$ \\
+Allowed Values & $\sqcup$ & allowed \\
+Not Allowed Values & $\sqcup$, $\neg$ & not allowed \\
+%Literal Ranges & $\geq$, $\leq$, $\sqcap$ &  \\ 
+Literal Ranges & - & xsd:minInclusive \\
+               & & xsd:maxInclusive \\
+%Negative Literal Ranges & $\geq$, $\leq$, $\sqcap$, $\neg$ & \\  
+Negative Literal Ranges & - & xsd:minInclusive \\
+                        & & xsd:maxInclusive \\
+Required Properties & $\exists$ & required \\
+
+    \bottomrule
+    \end{tabular}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{lll}
+           \multicolumn{1}{l}{\textbf{Constraint Type}} & \multicolumn{1}{l}{\textbf{DL}} & \multicolumn{1}{l}{\textbf{Constraining Elements}}			 
+    \\ \midrule
+
+Optional Properties & $\exists$, $\sqsubseteq$ & optional \\
+Repeatable Properties & $\geq$ & repeatable \\
+Negative Property Constraints & $\neg$, $\exists$ & negative properties \\
+*Individual Equality & = & \\
+*Functional Properties & functional & \\ 
+*Inverse-Functional Properties & inverse, functional & inverse functional \\
+*Value Restrictions & $\exists$ & value restriction \\
+*Self Restrictions & $\exists$ & self restriction \\
+Primary Key Properties & inverse, functional & keyfor or primary key \\
+*Class-Specific Property Range & $\sqsubseteq$, $\exists$, $\neg$ & range \\
+*Class-Sp. Reflexive Object P. & reflexive & \\
+Membership in Controlled Vocabularies & $\forall$, $\sqcap$, $\sqcup$ & membership in \\
+  && controlled vocabularies \\
+IRI Pattern Matching & - & IRI pattern matching \\
+Literal Value Comparison & $>$ or $\geq$ or $<$ or & \\
+                         & $\leq$ or = or $\ne$ & \\
+Ordering & - & order \\ 
+Validation Levels & - & validation level \\ 
+String Operations & - & SPARQL string operations \\ 
+  && examples: STRLEN, \\ 
+	&& SUBSTR, CONTAINS \\
+Context-Specific Valid Classes & - & context-specific valid classes \\
+Context-Specific Valid Properties & - & context-specific valid properties \\
+Default Values & - & default values \\
+Mathematical Operations & - & example: multiplication \\
+Language Tag Matching & - & language tag matching \\
+Language Tag Cardinality & - & language tag minimum cardinality, \\
+                            && language tag maximum cardinality, \\
+													  && language tag exact cardinality \\
+Whitespace Handling & - & whitespace \\
+HTML Handling & - & html \\
+Conditional Properties & $\sqsubseteq$ & conditional \\
+Recommended Properties & - & recommended \\
+Handle RDF Collections & - & actions on RDF collections \\
+Value is Valid for Datatype & - & value is valid for datatype \\
+Use Sub-Super Relations in Validation & - & not redundant \\
+*Cardinality Shortcuts & & optional \& non-repeatable, \\
+                       & & optional \& repeatable \\
+											 & & mandatory \& non-repeatable \\
+											 & & mandatory \& repeatable \\
+Aggregations & - & aggregations \\
+                 && e.g., count \\
+*Class-Specific Irreflexive Object Properties & reflexive, $\neg$ & irreflexive \\
+Provenance & - & provenance \\   
+Data Model Consistency & - & SPARQL \\    
+Structure & - & SPARQL \\  
+Labeling and Documentation & - & SPARQL \\   
+Vocabulary & - & vocabulary \\  
+HTTP URI Scheme Violation & - & HTTP URI scheme violation \\
+
+    \bottomrule
+    \end{tabular}
+    \end{center}
+\end{table}
+
 \section{Conclusion and Future Work}

### 2015-06-11 paper/paper 2/dc-2015.tex
abstract

@@
 we published by today 81 types of constraints that are required by various stakeholders for data applications.
+
+As there are already five promising constraint languages, 
+our purpose is not to invent yet another constraint language.
+But as non of the current constraint languages does support all constraint types, 
+we developed a lightweight vocabulary to intermediately represent constraints of any constraint type in a generic way.
+Even though, this vocabulary is not considered to be a constraint language,
+constraints represented by the proposed vocabulary are intuitively understandable 
+as their structure is based on RDF terminology. 
+As we developed a vocabulary to represent constraint of any constraint type, 
+we are therefore able to provide a basic terminology and classification system for RDF constraints 
+to lay the ground for discussions on RDF validation.
+
+When using the developed vocabulary to intermediately represent constraints,
+depending on the individual type of constraint particular constraining elements can be applied.
+We base these constraining elements on formal logic.
+As constraints of 2/3 of all constraint types are expressible by logical constructs from description logics,
+we may use logical constructs as constraining elements.
+In order to be able to support all constraint types, however,
+we determined intuitive constraining elements in natural language like \emph{conditional properties}, \emph{allowed values}, and \emph{language tag minimum cardinality}.
+Constraints of the constraint type \emph{required properties}, e.g., can be expressed by the existential quantifier $\exists$ or more intuitively using the constraining element \emph{required properties}.
+
+As SPARQL is generally seen as the method of choice to validate data according to certain constraints and
+as RDF data can be validated on constraints of any constraint type by means of SPARQL,
+we use SPIN, a SPARQL-based way to validate RDF data, as implementation language 
+to actually execute the validation of RDF data.
+Thereby, constraints may either be 
+(1) expressed by domain specific constraint languages like OWL 2 and DSP or
+(2) represented generically by the proposed vocabulary.
+
 %The majority of these constraint types can be expressed in description logics which provides their logical underpinning.
@@
 
-The main contributions of this paper are:
-(1) We provide a basic terminology and classification system for RDF constraints to lay the ground for discussions on RDF validation.
-(2) As current high-level constraint languages do not support all constraint types, 
-we developed a vocabulary to describe constraints of any constraint type in a generic way and specified its underlying semantics.
-(3) We show how to enhance the interoperability of constraints expressed by different languages by using the proposed vocabulary 
-to intermediately represent constraints 
-%as an intermediate generic representation 
-which enables transformations between semantically equivalent constraints.
-(4) We explain how constraint languages may reuse validation implementations which are provided once for each constraint type.
+%The main contributions of this paper are:
+%(1) We provide a basic terminology and classification system for RDF constraints to lay the ground for discussions on RDF validation.
+%(2) As current high-level constraint languages do not support all constraint types, 
+%we developed a vocabulary to describe constraints of any constraint type in a generic way and specified its underlying semantics.
+%(3) We show how to enhance the interoperability of constraints expressed by different languages by using the proposed vocabulary 
+%to intermediately represent constraints 
+%%as an intermediate generic representation 
+%which enables transformations between semantically equivalent constraints.
+%(4) We explain how constraint languages may reuse validation implementations which are provided once for each constraint type.
 

### 2015-06-11 paper/paper 2/dc-2015.tex
abstract

@@
 But as non of the current constraint languages does support all constraint types, 
-we developed a lightweight vocabulary to intermediately represent constraints of any constraint type in a generic way.
+we developed a lightweight vocabulary to intermediately represent constraints of any constraint type.
 Even though, this vocabulary is not considered to be a constraint language,
-constraints represented by the proposed vocabulary are intuitively understandable 
-as their structure is based on RDF terminology. 
+constraints represented by the proposed vocabulary are easily understandable 
+as their structure is based on common RDF terminology like classes and properties. 
 As we developed a vocabulary to represent constraint of any constraint type, 
@@
 When using the developed vocabulary to intermediately represent constraints,
-depending on the individual type of constraint particular constraining elements can be applied.
+depending on the individual type of constraint one or multiple particular constraining elements are applied.
 We base these constraining elements on formal logic.
@@
 In order to be able to support all constraint types, however,
-we determined intuitive constraining elements in natural language like \emph{conditional properties}, \emph{allowed values}, and \emph{language tag minimum cardinality}.
-Constraints of the constraint type \emph{required properties}, e.g., can be expressed by the existential quantifier $\exists$ or more intuitively using the constraining element \emph{required properties}.
+we determined for each constraint type more intuitive constraining elements in natural language like \emph{conditional properties}, \emph{allowed values}, and \emph{language tag minimum cardinality}.
+A title is required for books.
+This constraint of the constraint type \emph{required properties (R-68)} can be either expressed by the existential quantifier $\exists$ from description logics or more intuitively using the constraining element \emph{required properties}.
 
@@
 (1) expressed by domain specific constraint languages like OWL 2 and DSP or
-(2) represented generically by the proposed vocabulary.
+(2) represented by the proposed vocabulary.
 

### 2015-06-11 paper/RDF validation requirements/RDF validation requirements.tex
abstract and mapping from constraint types to constraining elements

@@
   \item Constraints of 64\% of all constraint type can be expressed using logical constructs from description logics.	
-	\item We developed a vocabulary and for each constraint type we identified constraining elements to represent constraints of any constraint type.
-
-	\item In most cases, it is sufficient to use only 1 logical construct
-	\item Some combinations of logical constructs can be simplified to 1 logical construct which can be used in terms of syntactic sugar
-  \item constraints of the majority of the constraint types can be expressed logically by description logics
-	\item constraints of all constraint types can be expressed by constraining elements
-	\item For 1 constraint types, there can be multiple constraining elements
-	\item the validation of each constraining element has to be implemented
+	\item For a constraint types, there can be multiple constraining elements
+	\item The validation of each constraining element has to be implemented
 	\item We use SPARQL as extension mechanism to express constraints of 3 constraint types which cannot be expressed otherwise as they are too complex to represent them using a high-level constraint language
@@
 
-Optional Properties & $\exists$, $\sqsubseteq$ & optional \\
-Repeatable Properties & $\geq$ & repeatable \\
+Optional Properties & $\exists$, $\sqsubseteq$ & optional properties \\
+Repeatable Properties & $\geq$ & repeatable properties \\
 Negative Property Constraints & $\neg$, $\exists$ & negative properties \\

### 2015-06-11 paper/RDF validation requirements/RDF validation requirements.tex
abstract and mapping from constraint types to constraining elements

--- 2015-05-29 paper/RDF validation requirements/RDF validation requirements.tex
@@
 
+\subsection{Constraining Elements of Constraint Types}
+
+\begin{itemize}
+  \item Constraints of 64\% of all constraint type can be expressed using logical constructs from description logics.	
+	\item For a constraint types, there can be multiple constraining elements
+	\item The validation of each constraining element has to be implemented
+	\item We use SPARQL as extension mechanism to express constraints of 3 constraint types which cannot be expressed otherwise as they are too complex to represent them using a high-level constraint language
+\end{itemize}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{lll}
+           \multicolumn{1}{l}{\textbf{Constraint Type}} & \multicolumn{1}{l}{\textbf{DL}} & \multicolumn{1}{l}{\textbf{Constraining Elements}}			 
+    \\ \midrule
+
+*Subsumption & $\sqsubseteq$ & sub-classes \\
+*Class Equivalence & $\equiv$ & equivalent classes \\
+*Sub Properties & $\sqsubseteq$ & sub-properties \\
+*Property Domain & $\exists$, $\sqsubseteq$ & property domain \\
+*Property Range & $\sqsubseteq$, $\forall$ & property range \\
+*Inverse Object Properties & inverse & inverse properties \\
+%*Symmetric Object Properties & $\equiv$, inverse & symmetric \\
+*Symmetric Object Properties & symmetric & symmetric properties \\
+%*Asymmetric Object Properties & $\sqsubseteq$, inverse & asymmetric \\
+*Asymmetric Object Properties & asymmetric & asymmetric properties \\
+%*Reflexive Object Properties & $\exists$, $\sqsubseteq$ & \textcolor{green}{reflexive} \\
+*Reflexive Object Properties & reflexive & reflexive properties \\
+%*Irreflexive Object Properties & $\exists$, $\neg$, $\sqsubseteq$ & irreflexive \\
+*Irreflexive Object Properties & reflexive, $\neg$ & irreflexive properties \\
+Disjoint Properties & $\sqsubseteq$, $\neg$ & $\ne$ \\
+Disjoint Classes & $\sqcap$, $\sqsubseteq$ & $\ne$ \\
+Context-Sp. Property Groups & $\sqcap$ & property group \\
+Context-Sp. Inclusive OR of P. & $\sqcup$ & inclusive or of properties \\
+Context-Sp. Inclusive OR of P. Groups & $\sqcup$, $\sqcap$ & inclusive or of property groups, \\
+                                                          && property group \\
+Recursive Queries & - & recursive \\
+Individual Inequality & $\ne$ & \\
+*Equivalent Properties & $\equiv$ & equivalent properties \\
+Property Assertions & = or $\ne$ & \\
+Data Property Facets & - & XSD or SPARQL constraining facets \\
+                        && examples: regex, xsd:pattern, ... \\
+Literal Pattern Matching & - & regex or xsd:pattern \\
+Negative Literal Pattern Matching & - & regex or xsd:pattern, $\neg$ \\ 
+*Object Property Paths & $\sqsubseteq$ & property paths \\
+*Intersection & $\sqcap$ & intersection \\
+*Disjunction & $\sqcup$ & disjunction \\
+*Negation & $\neg$ & negation \\
+*Existential Quantification & $\exists$ & existential quantification \\
+*Universal Quantification & $\forall$ & universal quantification \\
+*Minimum Unqualified Cardinality & $\geq$ & \\
+*Minimum Qualified Cardinality & $\geq$ & \\
+*Maximum Unqualified Cardinality & $\leq$ & \\
+*Maximum Qualified Cardinality & $\leq$ & \\
+*Exact Unqualified Cardinality & $\geq$, $\leq$, $\sqcap$ & = \\
+*Exact Qualified Cardinality & $\geq$, $\leq$, $\sqcap$ & = \\
+*Transitive Object Properties & $\sqsubseteq$ & transitive properties \\
+Context-Sp. Exclusive OR of P. & $\neg$, $\sqcap$, $\sqcup$ & XOR of properties \\
+Context-Sp. Exclusive OR of P. Groups & $\neg$, $\sqcap$, $\sqcup$ & XOR of property groups \\
+                                                                 & & property group \\
+Allowed Values & $\sqcup$ & allowed values \\
+Not Allowed Values & $\sqcup$, $\neg$ & not allowed values \\
+%Literal Ranges & $\geq$, $\leq$, $\sqcap$ &  \\ 
+Literal Ranges & - & xsd:minInclusive \\
+               & & xsd:maxInclusive \\
+%Negative Literal Ranges & $\geq$, $\leq$, $\sqcap$, $\neg$ & \\  
+Negative Literal Ranges & - & xsd:minInclusive \\
+                        & & xsd:maxInclusive \\
+Required Properties & $\exists$ & required properties \\
+
+    \bottomrule
+    \end{tabular}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+    \begin{center}
+    \begin{tabular}{lll}
+           \multicolumn{1}{l}{\textbf{Constraint Type}} & \multicolumn{1}{l}{\textbf{DL}} & \multicolumn{1}{l}{\textbf{Constraining Elements}}			 
+    \\ \midrule
+
+Optional Properties & $\exists$, $\sqsubseteq$ & optional properties \\
+Repeatable Properties & $\geq$ & repeatable properties \\
+Negative Property Constraints & $\neg$, $\exists$ & negative properties \\
+*Individual Equality & = & \\
+*Functional Properties & functional & functional properties \\ 
+*Inverse-Functional Properties & inverse, functional & inverse functional properties \\
+*Value Restrictions & $\exists$ & value restriction \\
+*Self Restrictions & $\exists$ & self restriction \\
+Primary Key Properties & inverse, functional & keyfor or primary key \\
+*Class-Specific Property Range & $\sqsubseteq$, $\exists$, $\neg$ & property range \\
+*Class-Sp. Reflexive Object P. & reflexive & reflexive properties \\
+Membership in Controlled Vocabularies & $\forall$, $\sqcap$, $\sqcup$ & membership in \\
+  && controlled vocabularies \\
+IRI Pattern Matching & - & IRI pattern matching \\
+Literal Value Comparison & $>$ or $\geq$ or $<$ or & \\
+                         & $\leq$ or = or $\ne$ & \\
+Ordering & - & ordered properties, \\
+            && ordered values \\ 
+Validation Levels & - & validation level \\ 
+String Operations & - & SPARQL string operations \\ 
+  && examples: STRLEN, \\ 
+	&& SUBSTR, CONTAINS \\
+Context-Specific Valid Classes & - & context-specific valid classes \\
+Context-Specific Valid Properties & - & context-specific valid properties \\
+Default Values & - & default values \\
+Mathematical Operations & - & example: multiplication \\
+Language Tag Matching & - & language tag matching \\
+Language Tag Cardinality & - & language tag minimum cardinality, \\
+                            && language tag maximum cardinality, \\
+													  && language tag exact cardinality \\
+Whitespace Handling & - & whitespace \\
+HTML Handling & - & html \\
+Conditional Properties & $\sqsubseteq$ & conditional properties \\
+Recommended Properties & - & recommended properties \\
+Handle RDF Collections & - & actions on RDF collections \\
+Value is Valid for Datatype & - & value is valid for datatype \\
+Use Sub-Super Relations in Validation & - & not redundant properties \\
+*Cardinality Shortcuts & & optional \& non-repeatable properties, \\
+                       & & optional \& repeatable properties, \\
+											 & & mandatory \& non-repeatable properties, \\
+											 & & mandatory \& repeatable properties \\
+Aggregations & - & aggregations \\
+                 && e.g., count \\
+*Class-Specific Irreflexive Object Properties & reflexive, $\neg$ & irreflexive properties \\
+Provenance & - & provenance \\   
+Data Model Consistency & - & SPARQL \\    
+Structure & - & SPARQL \\  
+Labeling and Documentation & - & SPARQL \\   
+Vocabulary & - & vocabulary \\  
+HTTP URI Scheme Violation & - & HTTP URI scheme violation \\
+
+    \bottomrule
+    \end{tabular}
+    \end{center}
+\end{table}
+
 \section{Conclusion and Future Work}

### 2015-06-17 paper/paper 2/dc-2015.tex
neues abstract

--- 2015-05-29 paper/paper 2/dc-2015.tex
@@
 \addtokomafont{subsection}{\fontsize{11pt}{0pt}\selectfont}
-\addtokomafont{author}{\fontsize{12pt}{1em}\selectfont}
+% \addtokomafont{author}{\fontsize{12pt}{1em}\selectfont}
 \usepackage{scrpage2}
@@
 \section*{Abstract}
-Increasingly, various domains adopt Linked Data principles
-and seek for ways to ensure data quality by validating RDF data according to predefined constraints,
-in particular, as many communities are used to have this functionality in the XML world.
-%XML Schema is the standard language to formulate constraints to validate XML documents.
-%For RDF, however, there are several constraint languages - but not a stand-alone standard one meeting the majority of RDF validation use cases. 
-To validate RDF data and to formulate constraints, several languages exist or are currently developed,
-but there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners.
+In the context of the DCMI RDF Application Profile task group and the W3C Data Shapes Working Group solutions for the proper formulation and validation of constraints on RDF data are developed.
+Several approaches and constraint languages exist but there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners.
 % Truth be told, we do may two things, blabla on and to blabla, however for the flow of the text we dont need to overkill the text.
 In abstract and introduction, we just give general idea so at such points we better focus on flow.
-Based on our work in the \emph{DCMI RDF Application Profiles Task Group} and in cooperation with the \emph{W3C Data Shapes Working Group}, 
+
+To support the work, a comprehensive, community-driven database has been created where case studies, use cases, requirements and solutions are collected. Based on this database,
 we published by today 81 types of constraints that are required by various stakeholders for data applications.
+We generally use this collection of constraint types to gain a better understanding of the expressiveness of existing solutions and gaps that still need to be filled.
+
+Regarding the implementation of constraint languages, we already proposed to use high-level languages to describe the constraints, but map them to SPARQL queries in order to execute the actual validation; we demonstrated this approach for Description Set Profiles.
+
+In this paper, we generalize from the experience of implementing Description Set Profiles by introducing an abstraction layer that is able to describe any constraint type in a way that is more or less straight-forwardly transformable to SPARQL queries.
+It provides a basic terminology and classification system for RDF constraints to lay the ground for discussions on RDF validation.
+
+We demonstrate that using another layer on top of SPARQL helps to implement validation consistently accross constraint languages and simplifies the mapping of new languages.
+
+%When using the developed vocabulary to intermediately represent constraints,
+%depending on the individual type of constraint one or multiple particular constraining elements are applied.
+%We base these constraining elements on formal logic.
+%As constraints of 2/3 of all constraint types are expressible by logical constructs from description logics,
+%we may use logical constructs as constraining elements.
+%In order to be able to support all constraint types, however,
+%we determined for each constraint type more intuitive constraining elements in natural language like \emph{conditional properties}, \emph{allowed values}, and \emph{language tag minimum cardinality}.
+%A title is required for books.
+%This constraint of the constraint type \emph{required properties (R-68)} can be either expressed by the existential quantifier $\exists$ from description logics or more intuitively using the constraining element \emph{required properties}.
+
+%As SPARQL is generally seen as the method of choice to validate data according to certain constraints and
+%as RDF data can be validated on constraints of any constraint type by means of SPARQL,
+%we use SPIN, a SPARQL-based way to validate RDF data, as implementation language 
+%to actually execute the validation of RDF data.
+%Thereby, constraints may either be 
+%(1) expressed by domain specific constraint languages like OWL 2 and DSP or
+%(2) represented by the proposed vocabulary.
+
 %The majority of these constraint types can be expressed in description logics which provides their logical underpinning.

### 2015-06-17 paper/paper 2/dc-2015.tex
abstract feedback

@@
 In the context of the DCMI RDF Application Profile task group and the W3C Data Shapes Working Group solutions for the proper formulation and validation of constraints on RDF data are developed.
-Several approaches and constraint languages exist but there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners.
+\tb{solutions for the proper formulation of constraints and validation of RDF data on these constraints are developed}Several approaches and constraint languages exist but there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners.
 % Truth be told, we do may two things, blabla on and to blabla, however for the flow of the text we dont need to overkill the text.
@@
 We demonstrate that using another layer on top of SPARQL helps to implement validation consistently accross constraint languages and simplifies the mapping of new languages.
+\tb{ich denke hier wird nicht klar was es bedeutet neue sprachen zu mappen, auch nicht worauf und warum / Vorschlag: and simplifies the mapping of new languages to SPARQL / simplifies the task to actually implement new languages / simplifies the actual implementation of new languages}
 

### 2015-06-18 paper/paper 2/dc-2015.tex
abstract

--- 2015-06-17 paper/paper 2/dc-2015.tex
@@
 \section*{Abstract}
-In the context of the DCMI RDF Application Profile task group and the W3C Data Shapes Working Group solutions for the proper formulation and validation of constraints on RDF data are developed.
+In the context of the DCMI RDF Application Profile task group and the W3C Data Shapes Working Group solutions for the proper formulation of constraints and validation of RDF data on these constraints are developed.
 Several approaches and constraint languages exist but there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners.
-% Truth be told, we do may two things, blabla on and to blabla, however for the flow of the text we dont need to overkill the text.
-In abstract and introduction, we just give general idea so at such points we better focus on flow.
-
 To support the work, a comprehensive, community-driven database has been created where case studies, use cases, requirements and solutions are collected. Based on this database,
@@
 We generally use this collection of constraint types to gain a better understanding of the expressiveness of existing solutions and gaps that still need to be filled.
-
 Regarding the implementation of constraint languages, we already proposed to use high-level languages to describe the constraints, but map them to SPARQL queries in order to execute the actual validation; we demonstrated this approach for Description Set Profiles.
-
 In this paper, we generalize from the experience of implementing Description Set Profiles by introducing an abstraction layer that is able to describe any constraint type in a way that is more or less straight-forwardly transformable to SPARQL queries.
-It provides a basic terminology and classification system for RDF constraints to lay the ground for discussions on RDF validation.
-
-We demonstrate that using another layer on top of SPARQL helps to implement validation consistently accross constraint languages and simplifies the mapping of new languages.
+It provides a basic terminology and classification system for RDF constraints to foster discussions on RDF validation.
+We demonstrate that using another layer on top of SPARQL helps to implement validation consistently accross constraint languages and simplifies the actual implementation of new languages.
 

### 2015-06-18 paper/paper 2/dc-2015-abstract.tex
Final Abstract and Title

--- 2015-06-18 paper/paper 2/dc-2015.tex
@@
 
-\title{\vspace{-1em}Formulating RDF Constraints Generically and Validating RDF Data Out-Of-The-Box}
+\title{\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.}
 
@@
 
-%When using the developed vocabulary to intermediately represent constraints,
-%depending on the individual type of constraint one or multiple particular constraining elements are applied.
-%We base these constraining elements on formal logic.
-%As constraints of 2/3 of all constraint types are expressible by logical constructs from description logics,
-%we may use logical constructs as constraining elements.
-%In order to be able to support all constraint types, however,
-%we determined for each constraint type more intuitive constraining elements in natural language like \emph{conditional properties}, \emph{allowed values}, and \emph{language tag minimum cardinality}.
-%A title is required for books.
-%This constraint of the constraint type \emph{required properties (R-68)} can be either expressed by the existential quantifier $\exists$ from description logics or more intuitively using the constraining element \emph{required properties}.
-
-%As SPARQL is generally seen as the method of choice to validate data according to certain constraints and
-%as RDF data can be validated on constraints of any constraint type by means of SPARQL,
-%we use SPIN, a SPARQL-based way to validate RDF data, as implementation language 
-%to actually execute the validation of RDF data.
-%Thereby, constraints may either be 
-%(1) expressed by domain specific constraint languages like OWL 2 and DSP or
-%(2) represented by the proposed vocabulary.
-
-%The majority of these constraint types can be expressed in description logics which provides their logical underpinning.
-%In this paper, we provide a basic terminology and classification system for RDF constraints.\tb{The contributions of this paper are the following. (1)...}
-%We developed a vocabulary to describe constraints of any RDF constraint type generically. 
-%%(whether expressible in description logics or not).
-%We show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful.
-%We explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages by providing mappings to generically expressed constraints.
-
-%The main contributions of this paper are:
-%(1) We provide a basic terminology and classification system for RDF constraints to lay the ground for discussions on RDF validation.
-%(2) As current high-level constraint languages do not support all constraint types, 
-%we developed a vocabulary to describe constraints of any constraint type in a generic way and specified its underlying semantics.
-%(3) We show how to enhance the interoperability of constraints expressed by different languages by using the proposed vocabulary 
-%to intermediately represent constraints 
-%%as an intermediate generic representation 
-%which enables transformations between semantically equivalent constraints.
-%(4) We explain how constraint languages may reuse validation implementations which are provided once for each constraint type.
-
-\hspace{-1.4em}
-\textbf{Keywords:}
-RDF validation; RDF constraints; RDF constraint types, RDF validation requirements; Linked Data; Semantic Web
-
-\section{Introduction}
-%The purpose of OWL 2 ontologies is to perform reasoning on RDF data and not to validate RDF data conforming to these ontologies.
-%OWL 2 is based on the {\em non-unique name assumption} (nUNA) whereas RDF validation requires that different names represent different objects ({\em unique name assumption} (UNA)). 
-%Reasoning in OWL 2 is based on the semantics of {\em open-world assumption} (OWA), i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose: to represent knowledge on the World Wide Web.
-%On the other hand, many RDF validation scenarios require the {\em closed-world assumption} (CWA) (i.e., a statement is inferred to be false if it cannot be proved to be true).
-%This ambiguity in semantics is one of the main reasons why OWL 2 has not been adopted as a standard constraint language for RDF validation.  
-%For this reason, we cannot use OWL 2 ontologies for RDF validation as we use XML Schemas, DTDs, RELAX NG, or Schematron to validate XML documents.
-
-Recently, RDF validation as a research field gained speed due to common needs of data practitioners.
-A typical example is the library domain that co-developed and adopted Linked Data principles very early.
-For libraries, the common description of resources are key business and they have a long tradition in developing and using interoperable data formats.
-While they embrace the openness of Linked Data and the data modeling principles provided by RDF, the data is still mostly represented in XML and this is unlikely to change any time soon.
-Among the reasons for the success of XML is the possibility to formulate fine-grained constraints to be met by the data and to validate the data according to these constraints using powerful systems like \emph{DTD}, \emph{XML Schema}, \emph{RELAX NG}, or \emph{Schematron}.
-A typical example is the definition of a library record describing a book.
-There are clear rules which information has to be available to describe a book properly, but also how information like an ISBN number is properly represented.
-Libraries seek to make their own data reusable for general purposes, but also to enrich and interlink their own data.
-Checking if third-party data meets own requirements or validating existing data according to new needs for a Linked Data application are among common use cases for RDF validation.
-
-In 2013, the \emph{W3C} organized the \emph{RDF Validation Workshop}\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}
-where experts from industry, government, and academia discussed first RDF validation use cases. 
-%for RDF data validation and constraint formulation.
-In 2014, two working groups on RDF validation have been established: 
-the \emph{W3C RDF Data Shapes Working Group}\footnote{\url{http://www.w3.org/2014/rds/charter}} and the \emph{DCMI RDF Application Profiles Task Group}\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
-We collected the findings of these working groups and initiated a database of RDF validation requirements\footnote{Online available at \url{http://purl.org/net/rdf-validation}}
-with the intention to collaboratively collect case studies, use cases, requirements, and solutions in a comprehensive and structured way \cite{BoschEckert2014}. 
-Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group,
-we published by today 81 requirements to validate RDF data and to formulate constraints; 
-%each of them corresponding to a constraint type which in most cases can be expressed by multiple constraint languages. 
-each of them corresponds to a constraint type from which concrete constraints are instantiated to be checked on RDF data. 
-%and which in most cases can be expressed by multiple constraint languages.
-%Requirements/constraint types are uniquely identified by alphanumeric technical identifiers.
-%\emph{Minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75}, e.g., is a constraint type which corresponds to the requirement {\small\emph{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}}.
-We recently published a technical report (serving as first appendix of this paper) in which we explain each constraint type in detail and give examples for each represented by different constraint languages \cite{BoschNolleAcarEckert2015}.
-More than 10 constraint languages with different syntax and semantics exist or are currently developed. 
-We focus on the five most promising ones on being the standard like
-\emph{Shape Expressions (ShEx)}, \emph{Resource Shapes (ReSh)}, and \emph{Description Set Profiles (DSP)}. 
-The \emph{Web Ontology Language} \emph{(OWL)} in its current version \emph{OWL 2} can also be used as a constraint language.
-With its direct support of validation via \emph{SPARQL}, the \emph{SPARQL Inferencing Notation (SPIN)} is very popular and certainly plays an important role for the future development in this field. 
-%\emph{SPIN} is particularly interesting as a means to validate arbitrary constraint languages by mapping them to \emph{SPARQL} \cite{BoschEckert2014-2}.
-
-\subsection{Motivation and Overview}
-
-We evaluated which constraint types the five most common constraint languages enable to express \cite{BoschNolleAcarEckert2015}.
-%The evaluation is explained in detail in the appendix of this paper \cite{BoschNolleAcarEckert2015}.
-Table \ref{tab:constraint-type-specific-expressivity} shows in percentage values (and absolute numbers in brackets) how many constraint types each language supports.
-
-\begin{table}[H]
-	\centering
-	  %\caption{Constraint Type Specific Expressivity}
-		\caption{Constraint Type Specific Expressivity of Constraint Languages}
-	  \scriptsize
-		\begin{tabular}{c|c|c|c|c}
-      %\textbf{Expressivity Class} & $Expr(\overline{\mathcal{CT}_R})$ (42) & $Expr(\mathcal{CT}_R)$ (32) \\		
-			\emph{DSP} & \emph{ReSh} & \emph{ShEx} & \emph{OWL 2} & \emph{SPIN} \\	
-      \hline
-			17.3 (14) & 25.9 (21) & 29.6 (24) & 67.9 (55) & \textbf{100.0} \textbf{(81)} 
-		\end{tabular}
-	\label{tab:constraint-type-specific-expressivity}
-\end{table}
-
-The fact that \emph{SPIN} supports all and \emph{OWL 2} covers 2/3 of all constraint types
-emphasizes the significant role \emph{SPIN} and \emph{OWL 2} play for the future development of constraint languages.
-\emph{SPARQL} and therefore \emph{SPIN}, the \emph{SPARQL}-based way to formulate and check constraints, is generally seen as the method of choice to validate data according to certain constraints \cite{Fuerber2010},
-although, it is not ideal for their formulation. 
-In contrast, high-level constraint languages are comparatively easy to understand and constraints can be formulated more concisely.
-Declarative languages may be placed on top of \emph{SPARQL} and \emph{SPIN} when using them as implementation languages.
-
-There exists no single best solution considered as high-level intuitive constraint language which enables to express constraints in an easy and concise way and which is able to meet all requirements raised by data practitioners.
-%which can be used to express constraints and to validate RDF data, 
-%(e.g. existential and universal quantification, cardinality restrictions, and exclusive or of properties)
-%\section{Ideas}
-%constraint design patterns:
-% - ontology design pattern.org
-% - DSP uses other design pattern
-% - constraint elements are the same / 
-% - constraint / constraint elements / constraint design patterns / constraint language
-%dependency between requirements / when this requirements is fulfilled then this is also fulfilled (e.g. min card and requ. car)
-%min car more powerful than req. propery
-Thus, the idea behind this paper is to satisfy all RDF validation requirements
-by representing constraints of any constraint type in a generic way using a lightweight vocabulary which consists of only a few terms.
-We lately published a technical report (serving as second appendix of this paper) in which we describe the vocabulary in detail \cite{BoschEckert2015-2} (Section \ref{sec:vocabulary}).
-The constraint type \emph{minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75} can be instantiated to ensure
-that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
-%As every \emph{publication} must have at least one \emph{author} which must be a \emph{person} 
-As the book \emph{The-Lord-Of-The-Rings} is a \emph{publication}, 
-%{\small\ms{(rdf:type(The-Lord-Of-The-Rings, Publication)),}} 
-it must have at least one \emph{author} relationship to a \emph{person}.
-The constraint is violated either (1) if
-the book does not have any \emph{author} relationship, 
-or (2) if it has an \emph{author} which is not a \emph{person},
-%{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)},} {\small\ms{rdf:type(Tolkien, Hobbit)),}} 
-or (3) if it has an \emph{author} whose class is unknown.
-%{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)).}}
-%In contrast, the book is a valid \emph{publication}, if it is connected to a \emph{person} via the property \emph{author}.
-%{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Person)).}}
-This constraint can either be represented generically (\emph{generic constraint}) by \emph{description logics (DL)}: {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}} or specifically (\emph{specific constraint}) by multiple domain-specific constraint languages:
-
-\begin{ex}[commandchars=\\\{\}]
-\textit{OWL 2:} Publication a owl:Restriction ;
-          owl:minQualifiedCardinality 1 ;
-          owl:onProperty author ;
-          owl:onClass Person .
-
-\textit{ShEx:} Publication \{ author @Person\{1, \} \}
-
-\textit{ReSh:} Publication a rs:ResourceShape ; rs:property [
-          rs:propertyDefinition author ;
-          rs:valueShape Person ;
-          rs:occurs rs:One-or-many ; ] .
-
-\textit{DSP:} [ dsp:resourceClass Publication ; dsp:statementTemplate [ 
-          dsp:minOccur 1 ; dsp:maxOccur "infinity" ; 
-          dsp:property author ; 
-          dsp:nonLiteralConstraint [ dsp:valueClass Person ] ] ] .
-
-\textit{SPIN:} CONSTRUCT \{ [ a spin:ConstraintViolation ... . ] \} WHERE \{ 
-          ?this ?p ?o ; a ?C .
-          BIND ( \textit{qualifiedCardinality}( ?this, ?p, ?C ) AS ?c ) .
-          BIND( STRDT ( STR ( ?c ), xsd:nonNegativeInteger ) AS ?cardinality ) .
-          FILTER ( ?cardinality < ?minimumCardinality ) . \}
-
-\textit{SPIN function qualifiedCardinality:}										
-SELECT ( COUNT ( ?arg1 ) AS ?c ) WHERE \{ ?arg1 ?arg2 ?o . ?o a ?arg3 . \}
-\end{ex}
-
-The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
-For this reason, we mapped constraint types to \emph{DL} 
-in order to determine which \emph{DL} constructs are needed to express constraint types \cite{BoschNolleAcarEckert2015}.
-
-The main contributions of this paper are:
-(1) We provide a basic terminology and classification system for RDF constraints to lay the ground for discussions on RDF validation (Section \ref{sec:vocabulary}).
-(2) As current high-level constraint languages do not support all constraint types, 
-we developed a vocabulary to describe constraints of any constraint type in a generic way and specified its underlying semantics (Section \ref{sec:vocabulary}).
-(3) We show how to enhance the interoperability of constraints expressed by different languages by using the proposed vocabulary 
-to intermediately represent constraints 
-%as an intermediate generic representation 
-which enables transformations between semantically equivalent constraints (Section \ref{sec:transformations}).
-(4) We explain how constraint languages may reuse validation implementations which are provided once for each constraint type (Section \ref{sec:validation}).
-
-\subsection{How to Improve the Interoperability of RDF Constraints}
-\label{sec:transformations}
-
-RDF data providers have to ensure high data quality and therefore 
-that their data conforms to constraints which may be part of contracts between data providers and consumers.
-As there is no standard way to formulate constraints, 
-semantically equivalent \emph{specific constraints}, so the \emph{minimum qualified cardinality restriction}, may be represented by a variety of languages - each of them having different syntax and semantics.
-This causes confusion and weakens the common understanding between several parties about the meaning of particular constraints.
-We propose transformations between semantically equivalent \emph{specific constraints}
-(1) to avoid the necessity to understand several languages,
-(2) to resolve misunderstandings about the meaning of particular constraints within the communication of RDF data producers and consumers, and
-(3) to enhance the interoperability of constraint languages.
-
-We suggest to transform a \emph{specific constraint} (\emph{$sc_{\alpha}$}) of any constraint type expressed by language \emph{$\alpha$} into a semantically equivalent \emph{specific constraint} (\emph{$sc_{\beta}$}) of the same constraint type represented by any other language \emph{$\beta$}
-by using the developed vocabulary to intermediately represent constraints in a generic way. 
-%to enable these transformations.
-By defining mappings between equivalent \emph{specific constraints} and the corresponding \emph{generic constraint} (\emph{gc}) we are able to convert them automatically: 
-{\small\ms{$ gc = m_1(sc_{\alpha}) = m_2(sc_{\beta}) $}}.
-Thereby, we do not need to define mappings between each pair of semantically equivalent \emph{specific constraints}.
-Let's assume we are able to express constraints of the \emph{minimum qualified cardinality restrictions} constraint type by 10 languages.
-Without an intermediate generic representation of constraints, we would have to define for each constraint type one mapping between each pair of \emph{specific constraints} expressed by \emph{n} languages
-- that are \emph{\( {n \choose 2} \)} mappings (\emph{\( {10 \choose 2} \)} = 45 mappings).
-With an intermediate generic representation of constraints, on the other side, we only need to define for each constraint type \emph{n} mappings 
-%(1 mapping for each \emph{specific constraint}) 
-from \emph{n} \emph{specific constraints} to the corresponding \emph{generic constraint} (10 mappings).
-%Let's assume we are able to express a particular constraint type by 5/6/7/8/9/10 constraint languages.
-%Without the intermediate \emph{generic constraint}, we would have to define for each constraint type \emph{1} mapping for each pair of \emph{specific constraints} (expressed by different constraint languages)
-%that are \emph{\( {n \choose 2} \)} mappings (10/15/21/28/36/45 mappings).
-%With an intermediate \emph{generic constraint}, however, we only need to define for each constraint type \emph{n} mappings (1 mapping for each \emph{specific constraint}) from \emph{n} \emph{specific constraints} to the corresponding \emph{generic constraint} (5/6/7/8/9/10 mappings).
-For the \emph{minimum qualified cardinality restriction}, one mapping (\emph{$m_1(sc_{OWL 2})$}, \emph{$m_2(sc_{ShEx})$}, \emph{$m_3(sc_{ReSh})$}, \emph{$m_4(sc_{DSP})$},...) is defined for each \emph{specific constraint} (\emph{$sc_{OWL 2}$}, \emph{$sc_{ShEx}$}, \emph{$sc_{ReSh}$}, \emph{$sc_{DSP}$},...) to the corresponding \emph{generic constraint} (\emph{gc}).
-
-\subsection{How to Provide the Validation of RDF Constraints Out-Of-The-Box}
-\label{sec:validation}
-
-We use \emph{SPIN} as basis to develop a validation environment\footnote{Online demo available at \url{http://purl.org/net/rdfval-demo}, source code available at: \url{https://github.com/boschthomas/rdf-validator}\label{rdf-validator}} to validate RDF data according to constraints of constraint types which are expressible by arbitrary constraint languages by mapping them to \emph{SPIN}\footnote{\emph{SPIN} mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}\label{spin-mappings}} \cite{BoschEckert2014-2}.
-The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations \cite{BoschEckert2014-2}.
-The next step, however, was to extend the \emph{RDF Validator} to validate RDF data conforming to constraints of any constraint type
-by representing constraints generically using the proposed vocabulary.
-
-When language designers extend constraint languages 
-to be able to formulate constraints of not yet supported constraint types,
-our proposal prevents the necessity to actually implement the validation of data
-according to constraints of these constraint types for each of those languages.  
-For any constraint language, we enable to offer a validation implementation of any constraint type out-of-the-box
-%validation implementations out-of-the-box for any constraint type whose \emph{specific constraints} may be expressed by any language  
-by providing a \emph{SPIN} mapping
-%generic validation implementations once 
-for each constraint type\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}\label{RDF-CV-2-SPIN}}  
-whose constraints are represented generically \cite{BoschEckert2015-2}.
-%(2) by transforming \emph{specific constraints} into the appropriate \emph{generic constraint}.  
-All what language designers need to do is to specify for each constraint type they want to cover one mapping from the \emph{specific constraint} expressed by the language to the corresponding \emph{generic constraint}.
-19 of the overall 81 constraint types are expressible by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
-This means that for these 19 constraint types there must be 76 implementations (four for each constraint type) to actually validate RDF data according to 76 \emph{specific constraints} - instead of only 19 implementations (one for each \emph{generic constraint}).
-%which lead for each constraint type to identical validation results independently from the language used to formulate the \emph{specific constraints}.
-Our proposal makes sure that the validation on semantically equivalent \emph{specific constraints} expressed by different languages
-leads to exactly the same validation results, 
-i.e., that validation is performed independently from the used language.
-This is not the case, however, for existing languages due to differences in semantics and since they are implemented independently form each other.
-
-%When domain experts use graphical user interfaces to define constraints in a user-friendly way (without the necessity to express constraints on their own), 
-%constraints can be mapped to either a specific or a generic constraint, as for both the validation is provided in the background.    
-%So, the user does not have to know how to express specific constraints using any constraint language.
-
-%Existing constraint languages can be extended and new constraint languages can be developed, if existing constraint languages are not sufficient to represent needed constraint types.
-
-%If (1) a new constraint type is expressed generically, (2) the \emph{generic constraint type} is mapped to \emph{specific constraint types} (expressed by constraint languages), and (3) the validation is implemented for this particular \emph{generic constraint type},
-%the validation of \emph{specific constraint types} is provided out of the box.
-%As a consequence, constraint language designers do not have to implement the validation of their constraint languages and each semantically equivalent \emph{specific constraint type} is validated the same way (i.e.
-leading to identical validation results).
-
-%This paper aims to address two main \textbf{audiences}:
-%(1) RDF data providers and consumers seeking how to ensure high data quality and thus for ways to enhance the interoperability and common understanding of constraints expressible by multiple constraint languages and
-%(2) RDF practitioners thinking of how to provide aligned implementations for the validation of both existing an newly developed constraint languages.
-
-%(if the validation is implemented once for the corresponding \emph{generic constraint type} to which the \emph{specific constraint type} is mapped)
-
-%The remainder of the paper is as follows.
-
-%\begin{itemize}
-	%\item Any specific constraint (expressed by any constraint language) can be transformed into a generic constraint (expressed by the generic constraint language)
-	%\item Any specific constraint (expressed by any constraint language A) can be transformed into any specific constraint (expressed by any constraint language B)
-	%\item Any specific constraint (expressed by any constraint language) can be validated automatically (if an automatic validation is defined only once for corresponding generic constraint)
-	%\item We define a basic terminology and classification system for RDF constraints
-	%\item We developed an ontology describing any RDF constraint generically (whether expressible in DL or not)%which can also be expressed by any constraint language
-	%\item We present that any RDF constraint can be described by the developed ontology - whether the constraint can be expressed in DL or not 
-	%\item We show how to transform specific constraints (expressed by any constraint language \ms{$\alpha$}) into generic constraints and into specific constraints (expressed by any other constraint language \ms{$\beta$})
-  %\item We explain that any specific constraint can be validated automatically (if the validation is implemented only once for the corresponding generic constraint)
-%\end{itemize}
-
-%The \textbf{benefits} of our framework are:
-%\begin{itemize}
-	%\item Any specific constraint (expressed by any constraint language) can be transformed into a generic constraint (expressed by the generic constraint language)
-	%\item Any specific constraint (expressed by any constraint language A) can be transformed into any specific constraint (expressed by any constraint language B)
-	%\item Any specific constraint (expressed by any constraint language) can be validated automatically (if an automatic validation is defined only once for corresponding generic constraint)
-%\end{itemize}
-
-%\section{Running Example}
-%
-%Table \ref{tab:cardinality-restriction-mapped-to-vocabulary} shows the mapping between the \emph{cardinality restriction} represented in DL 
-%and the \emph{cardinality restriction} expressed by our developed vocabulary to describe any RDF constraint generically (see section~\ref{sec:ontology}):
-%
-%\begin{table}
-  %\scriptsize
-  %\sffamily
-  %\vspace{0cm}
-	%\centering
-		%\begin{tabular}{l|l|l|l|l|l|l}
-      %\textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
-      %\hline
-      %property & Publication & author & - & Person & $\geq$ & 1 \\
-		%\end{tabular}
-	%\caption{Cardinality Restriction Expressed Generically}
-	%\label{tab:cardinality-restriction-mapped-to-vocabulary}
-%\end{table}
-
-%According to this vocabulary, each constraint is either a constraint on classes or a constraint on properties.
-%The generically expressed cardinality restriction is represented in RDF as follows:
-%
-%\begin{ex}
-%[   a PropertyConstraint ;
-    %contextClass Publication ;
-    %leftProperties ( author ) ;
-    %classes ( Person ) ;
-    %constrainingElement ">=" ;
-    %constrainingValue 1 ] .
-%\end{ex}
-
-%Bosch and Eckert\cite{BoschEckert2014-2} use SPIN as basis to define a
-%validation environment in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL.
-%The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.
-%The generically expressed \emph{cardinality restriction} above is validated within the validation environment (see section \ref{sec:validation}) by means of a SPARQL CONSTRUCT query.
-
-%\begin{ex}
-%[   a PropertyConstraint ;
-    %contextClass ?cc ;
-    %leftProperties ( ?p1 ) ;
-    %classes ( ?c1 ) ;
-    %constrainingElement ">=" ;
-    %constrainingValue ?cv ] .
-%?subject rdf:type ?cc .
-%BIND ( qualifiedCardinality( ?subject, ?p1, ?c1 ) AS ?c ) .
-%FILTER ( ?c < ?cv ) .		  
-%\end{ex}
-
-\section{A Vocabulary to Describe RDF Constraints Generically} 
-\label{sec:vocabulary}
-
-Prerequisites to develop a vocabulary to describe constraints of any constraint type in a generic way are 
-(1) to specify the underlying semantics for validation and thus for the vocabulary and (2) to define a basic terminology and classification system for RDF constraints which lay the ground for discussions on validation.
-
-\subsection{Semantics for RDF Validation}
-
-RDF validation and \emph{OWL 2} assume different semantics. 
-This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past.
-We compare semantics of RDF validation and \emph{OWL 2} as \emph{OWL 2} is considered as a constraint language 
-when validation semantics is applied.
-%
-\emph{OWL 2} is based on the {\em open-world assumption} (\emph{OWA}), i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose to represent knowledge on the \emph{WWW}.
-As each \emph{book} must have a \emph{title} {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a \emph{book}, %{\small\ms{(Book(Hamlet)),}}
-{\em Hamlet} must have at least one \emph{title}.
-In an \emph{OWA} setting, this constraint does not cause a violation, even if there is no explicitly defined \emph{title}, since there must be a \emph{title} for this \emph{book} which we may not know.
-%($\mathcal{K}$ is consistent).
-As RDF validation has its origin in the XML world
-many RDF validation scenarios require the {\em closed-world assumption} (\emph{CWA}), i.e., a statement is inferred to be false if it cannot be proved to be true.
-Thus, classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals. 
-The \emph{CWA} yields to a violation since there is no explicitly defined \emph{title} for the \emph{book} {\em Hamlet}. 
-%
-Validation requires that different names represent different objects (\emph{unique name assumption (UNA)}), whereas,
-\emph{OWL 2} is based on the {\em non-unique name assumption (nUNA)}.  
-If we define the property \emph{title} to be functional {\small\ms{(funct (title)),}} a \emph{book} can have at most one distinct \emph{title}.
-\emph{UNA} causes a clash
-if the \emph{book} {\em Huckleberry-Finn} has more than one \emph{title}.
-For \emph{nUNA}, however, reasoning concludes that the \emph{title} {\em The-Adventures-of-Huckleberry-Finn} must be the same as the \emph{title} {\em Die-Abenteuer-des-Huckleberry-Finn} 
-which resolves the violation. 
-%Although, \emph{OWL 2} does not assume \emph{UNA}, \emph{OWL 2} has the constructs \emph{owl:sameAs} and \emph{owl:differentFrom} to state that two names are the same or different.
-If validation would assume \emph{OWA} and \emph{nUNA}, validation won’t be that restrictive and therefore we won’t get the intended validation results.
-%
-%\emph{OWL 2} reasoning is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true. 
-%%which fits its primary design purpose to represent knowledge on the World Wide Web. 
-%%Most of the constraint languages except OWL, have a major shortcoming of redundancy.
-%%With its open-world semantics, used as a constraint language, OWL solves the redundancy problem. 
-%%\tb{the following example does not show the redundancy problem!}
-%%\tb{2. benefit: reasoning solves redundancy problem}
-%As each \emph{book} must have a \emph{title} {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a \emph{book} {\small\ms{(Book(Hamlet)),}}
-%{\em Hamlet} must have at least one \emph{title}.
-%In an \emph{OWA} setting, this axiom does not cause a constraint violation (even if there is no explicitly defined \emph{title}), since there must be a \emph{title} for this \emph{book} which we may not know.
-%On the other hand, RDF validation scenarios require the \emph{closed-world assumption (CWA)}, i.e., a statement is inferred to be false if it cannot be proved to be true.
-%When assuming the \emph{CWA}, a constraint violation is raised as there is no explicitly defined title. 
-%A constraint that says that a book must have at least one title in \emph{OWA}, 
-%does not mean that the title has to be unique. 
-%In every model  (an interpretation that makes a set of \emph{DL knowledge base} true), 
-%it can be the case that a book has a single title, however, 
-%this title is not unique. 
-%In some models it is \emph{The-Adventures-of-Huckleberry-Finn}, in others it is \emph{Die-Abenteuer-des-Huckleberry-Finn}. 
-%And since in every model there is only one, \emph{DL} sentences are satisfied. 
-%But this does not correspond to the intended constraint which is usual in \emph{CWA} way.   
-%%Classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals which yields a constraint violation.
-%This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past. 
-%In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (\emph{CWA} and \emph{UNA}) as for RDF validation in general. 
-%In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general. 
-%\tb{feedback from Erman: the major problem is semantics.
-OWL basically work in different semantics than others.
-And their semantics are formal.
-Closed world vs.
-Open World is also a part of this.
-/ Thomas: I think your issue is tackled now?
-No.}
-%
-%comments from Erman:
-%
-%\begin{itemize}
-%\item If a constraint is represented (recognized) by two different languages, that means, whenever it is violated in one language it is violated in other.
-We have to provide formal generic semantics for it; formally prove those statements.}
-%
-%\item This is simple. You write that:
-%In case we want to use OWL 2 as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general.
-%The question is how to adopt CWA for OWL2, because it wont behave CWA way, just because we want it.
-So I say, in order to show that it behaves exactly we want it to, we should show that for the cases that we express a constraint (that we speak) in a classical constraint language, say, Scheme (therefore CWA) and  also OWL,  whenever the constraint in Scheme is violated, it's OWL correspondence is also violated.
-That shows that they behave in the same way, as they should.
-%
-%\item So if you read again my comment again, without knowing which semantics those constraint languages have, one actually does is to show, given an RDF-data it is violated in one language iff it is violated in other.
-And this actually corresponds to the very idea of transformation and generic semantics.
-%
-%\item Now, what is a generic semantics? 
-%It is, the semantics we had in our mind, when typing this long document, that we tried to underpin by the DL language.
-However, regarding CWA and OWA, it is possible that we made some mistakes.
-In order to ensure that, say, if its DL, one needs to show that, a constraint/query written a particular language should have the same answer with its correspondent DL query.
-%\end{itemize}
-%
-Differences in semantics may lead to differences in validation results when applied to particular constraint types.
-This is important 
-as for 56.8\% of the constraint types validation results differ if the \emph{CWA} or the \emph{OWA} 
-and as for 66.6\% of the constraint types validation results are different in case the \emph{UNA} or the \emph{nUNA} is assumed \cite{BoschNolleAcarEckert2015}.
-
-Constraints are identical w.r.t. RDF semantics, 
-if they detect the same set of violations regardless of RDF data, 
-which means whenever the constraints are applied to any RDF data they point out the same violations.
-As we use multiple languages to express constraints of constraint types, 
-%in the first appendix of this paper,
-we thereby document identical semantics of these languages with regard to given constraint types \cite{BoschNolleAcarEckert2015}.
-This is also important to prove that semantically equivalent \emph{specific constraints} and corresponding \emph{generic constraints}
-behave in the same way w.r.t. validation results which semantically underpins bidirectional mappings.
-
-%We defined the \textbf{formal generic semantics of the vocabulary} to describe constraints of any constraint type in a generic way (see paper appendix):
-%(1) We mapped constraint types to \emph{DL} to logically underpin them and 
-%(2) we described the constraint types' intended behavior in terms of validation results depending on \emph{CWA} and \emph{UNA}.
-%To be able to define mappings between \emph{specific constraints} (expressed by different languages) and \emph{generic constraints},
-%we show for each constraint type that a constraint expressed by a particular language leads to the same answer as the corresponding \emph{DL} query.
-%To be able to specify transformations between \emph{specific constraints} (expressed by different languages),
-%identical semantics of the languages with regard to the particular constraint type has to be ensured.
-%%Constraint languages assume identical semantics, 
-%%if for each constraint the following condition holds:
-%If a constraint is represented by \emph{ShEx} and \emph{OWL 2}, 
-%the validation results must be exactly the same, i.e.,
-%whenever the \emph{specific constraint} \emph{$sc_{ShEx}$} is violated, its \emph{$sc_{OWL 2}$} correspondence is also violated which shows that they behave in the same way.
-%We expressed constraint types by different languages
-%to document identical semantics for these languages with regard to appropriate constraint types.
-
-%\textcolor{red}{feedback from Erman:}
-
-%\textcolor{red}{
-%-About the paragraph; it says we defined a formal generic semantics.
-Did we?
-(if you think so please defend) but i think its not true.
-A formal semantics, is where you talk about an interpretation e.g., like in DL, there the semantics/interpretation is a mathematical object (therefore formally defined).
-What i believe is that paper propose  rather a schema for transforming constraint languages to one another (in particular to assess them in the first paper), that a person who doesn't know one language can have operation power etc..
-.
-%}
-%
-%\textcolor{red}{
-%-so I think we should get rid of this paragraph either totally or partially and you talk about the formulation instead briefly one-two sentence.
-I know that you wrote this paragraph to make my points and thanks a lot for that, but they were general remarks, so we cannot point out something that we do not do at that point, if its not at the "future work" or smth.
-Also this underpininng and  so on, these things were in the other paper (arxiv).
-If it has a point, then better referencing it.
-%}
-
-%\textcolor{red}{
-%-please be careful with the narration:
-%To be able to define mappings between specific constraints (expressed by different languages) and generic constraints, we show for each constraint type that a constraint expressed by a particular language leads to the same answer as the corresponding DL query.
-%When you read it and next sentence, it does not flow.  I know that it is not easy to write it nicely. But it also has technical problems, like
-%}
-%
-%\textcolor{red}{
-%A constraint  that is expected to give the same answer with a query.
-Those things are not of the same type.
-When I have written this query/constraint analogy, it was rather to provide an intuition.
-If we gonna talk about constraints; a constraint written in different languages always have the same restriction on any possible rdf-data.
-This means, if any two constraints are semantically the same (w.r.t.
-RDF data semantics), they should detect the same set of violations regardless of RDF data (which means whenever you apply them to any rdf data they point out the same violations or they have the same effect).
-Using a query language for validation, is a related but another thing.
-You actually know what it is better than I do.
-%}
-
-%Erman:
-%Section 3.1, explains a possible application only in an example specific to UNA and nUNA case, and I also have the 
-%feeling that it is so spread out to the whole work (paper1  especially), and in the core of technical parts. That is, whenever we mean CWA vs. OWA, we turn our head to UNA vs. nUNA.
-%
-%The thing I wanted to point out is that, the difference in CWA and OWA and its consequence/incompatibility is more general (as you also may probably noticed)  than the use of "UNA vs.
-nUNA".
-The example I gave  is independent from the assumption of UNA  or nUNA.
-%
-%You don't need to change something asap, but I think we can improve the exposition of any paper, by giving a classical constraint, how it is done classical in CWA, and how it is done in OWA, and then introducing the extra benefit, redundancy for instance.
-%
-%A constraint that says book should have a single author in OWA, does not mean that it has a unique author.
-In every model  (an interpretation that makes a set of DL knowledge base true), it can be the case that a book has a single author, however, bringing all those together, this author is not unique.
-In some models it is Ali, in others its Veli.
-And since in every model there is only one, DL sentences are satisfied.
-But this does not correspond to the intended constraint which is usual in CWA way.
-
-\subsection{Basic Terminology and Classification System for RDF Constraints}
-%\subsection{Basic Terminology for the Formulation of RDF Constraints}
-
-A \emph{constraint language} is a language which is used to formulate constraints.
-The \emph{W3C} working group defines \emph{RDF constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
-As there are already five promising constraint languages, 
-our purpose was not to invent a new language.
-As there is no high-level declarative language which meets all RDF validation requirements,
-we rather developed a very simple lightweight vocabulary,
-consisting of only three classes, three object properties, and three data properties, 
-which is universal enough to describe constraints of any constraint type.
-We call this vocabulary the \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}} whose conceptual model is shown in Figure \ref{fig:RDF-CV-conceptual-model}.
-\begin{figure}[H]
-	\centering
-		\includegraphics[width=0.60\textwidth]{images/RDF-CV-conceptual-model.png}
-	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} Conceptual Model}
-	\label{fig:RDF-CV-conceptual-model}
-\end{figure}
-
-We classify sets of constraints according to four dimensions.
-For each constraint type, we evaluated \cite{BoschNolleAcarEckert2015} in which set of constraints their instances are contained.
-%In the following, we state the rounded number of associated constraint types in brackets.
-%\begin{itemize}
-  %\item \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints}
-	%\item \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints}
-	%\item \emph{Context:} \emph{property constraints} vs. \emph{class constraints}
-	%\item \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}
-%\end{itemize}
-%(1) \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints},
-%(2) \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints},
-%(3) \emph{Context:} \emph{property constraints} vs. \emph{class constraints}, and
-%(4) \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}.
-\textbf{\emph{Universality}:}
-Constraints are expressible either generically (\emph{generic constraints}) using the \emph{RDF-CV}   
-or specifically (\emph{specific constraints}) by domain-specific constraint languages. 
-As we express constraints of each constraint type in form of \emph{generic constraints} conforming to the \emph{RDF-CV} \cite{BoschNolleAcarEckert2015},
-we show that constraints of any constraint type can be described generically.
-\textbf{\emph{DL Expressivity}:}
-The \emph{RDF-CV} allows to describe 
-constraints which are \emph{expressible in DL} (constraints of this set are instantiated from 64\% of the overall 81 constraint types) and which are \emph{not expressible in DL} (36\%). 
-%In case a constraint type is \emph{expressible in DL}, we determined which \emph{DL} constructs are needed to express the constraint type.
-\textbf{\emph{Complexity}:}
-\emph{Simple constraints} (60\% of the constraint types) denotes the set of atomic constraints. 
-%which can be instantiated from almost 2/3 of the constraint types.
-\emph{Complex constraints} (26\%) is the set of constraints which are created out of \emph{simple} and/or other \emph{complex constraints}.
-%and which are instances of 1/4 of the constraint types.
-%In case \emph{complex constraints} are expressible in \emph{DL}, 
-%\emph{DL} statements representing \emph{complex constraints} contain \emph{DL} statements standing for atomic and/or composed constraints. 
-Constraints of almost 14\% of the constraint types are \emph{complex constraints}
-which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
-\textbf{\emph{Context}:}
-\emph{Simple constraints} are applied on properties (\emph{property constraints}, 60\%),
-on classes (\emph{class constraints}, 25\%), or
-on properties and classes (\emph{property and class constraints}, 15\%).
-%2/3 of all constraint types are types of \emph{property constraints}, 
-%1/5 of \emph{class constraints}, and 
-%approx. 10\% of \emph{property and class constraints}.
-\emph{Simple constraints} must hold for individuals of their \emph{context classes}.
-As \emph{context classes} of \emph{simple constraints} are reused within \emph{complex constraints},
-it does not make sense to have terms standing for \emph{simple} and \emph{complex constraints} within the \emph{RDF-CV}. 
-As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to generically describe constraints of all constraint types.
-%\tb{use RDF-CV / not: expressible in RDF-CV / RDF-CV is a vocabulary, not a language}
-Altogether, instances of the most of the constraint types are \emph{simple constraints on properties} which are \emph{expressible in DL}. 
-%Thus, the majority of constraint types are directly and relatively easy formulated in form of \emph{simple constraints} which can be mapped to equivalent \emph{DL} constructs.
-
-\subsection{\emph{Simple Constraints}}
-
-The implementation model of the \emph{RDF-CV} (Figure \ref{fig:RDF-CV-implementation-model}) shows that
-both \emph{property constraints} and \emph{class constraints} are \emph{simple constraints}. 
-%For both \emph{property} and \emph{class constraints} a \emph{context class}, a list of \emph{classes}, the \emph{constraining element}, and the \emph{constraining value} can be stated. 
-%Lists of \emph{left} and \emph{right properties} can only be specified for \emph{property constraints}.
-\begin{figure}[H]
-	\centering
-		\includegraphics[width=0.80\textwidth]{images/RDF-CV-implementation-model.png}
-	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} Implementation Model}
-	\label{fig:RDF-CV-implementation-model}
-\end{figure}
-A \emph{simple constraint} holds for all individuals of their \emph{context class}.
-The \emph{minimum qualified cardinality restriction} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person,}}
-which restricts \emph{publications} to have at least one \emph{author} which must be a \emph{person},
-is an example of a \emph{property constraint} on \emph{author}
-which holds for all individuals of the class \emph{Publication}.
-Table \ref{tab:property-constraint-cardinality-restriction} displays the mapping to the \emph{RDF-CV}.
-\begin{table}[H]
-  \scriptsize
-  \sffamily
-  \vspace{0cm}
-	\caption{Minimum Qualified Cardinality Restriction as Property Constraint}
-	\label{tab:property-constraint-cardinality-restriction}
-	\centering
-		\begin{tabular}{c|c|c|c|c|c|c}
-      \textbf{constraint set} & \textbf{context class} & \textbf{left property list} & \textbf{right p. list} & \textbf{classes} & \textbf{constraining element} & \textbf{c. value} \\
-      \hline
-      property & Publication & author & - & Person & $\geq$ & 1 \\
-		\end{tabular}
-\end{table}
-
-The \emph{constraining element} indicates the actual type of constraint like \emph{DL} concept and role constructors, (in)equality, and further keywords for constraint types whose constraints cannot be expressed in \emph{DL} (e.g., regular expressions and constraining facets).
-In some cases, a constraint is only complete when a \emph{constraining value} is stated in addition to the \emph{constraining element}
-and \emph{simple constraints} may refer to a list of \emph{classes}.
-The \emph{constraining element} of the \emph{property constraint} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person},} e.g.,  is the \emph{DL at-least restriction} \emph{$\geq$}, the \emph{constraining value} is \emph{1}, and
-the list of \emph{classes} includes \emph{Person} which restricts the objects of the property \emph{author} to be of the class \emph{Person}.
-For \emph{property constraints}, \emph{left} and \emph{right property lists} are specified.
-The assignment of properties to these lists happens relative to the \emph{constraining element} 
-which may be an operator like $\sqsubseteq$.
-\emph{Object Property Paths} (\emph{R-55})
-ensure that if an individual \emph{x} is connected by a sequence of object properties with an individual \emph{y}, 
-then \emph{x} is also related to \emph{y} by a particular object property. 
-As \emph{Stephen-Hawking} is the \emph{author} of the book \emph{A-Brief-History-Of-Time} 
-%{\small\ms{(authorOf(Stephen-Hawking, A-Brief-History-Of-Time))}} 
-whose \emph{genre} is \emph{Popular-Science}, 
-%{\small\ms{(genre(A-Brief-History-Of-Time, Popular-Science)),}}
-the \emph{object property path} {\small\ms{authorOf $\circ$ genre $\sqsubseteq$ authorOfGenre}} infers that \emph{Stephen-Hawking} is an \emph{author} of the \emph{genre} \emph{Popular-Science}. 
-%{\small\ms{(authorOfGenre(Stephen-Hawking, Popular-Science))}.}
-Thus, when mapped to the \emph{RDF-CV} (Table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are placed on the left side of the \emph{constraining element} \emph{$\sqsubseteq$}
-and the property \emph{authorOfGenre} on the right side.
-As this \emph{property constraint} holds for all individuals within the data, the \emph{context class} is the \emph{DL top concept} $\top$ which stands for the super-class of all classes.
-\begin{table}[H]
-  \scriptsize
-  \sffamily
-  \vspace{0cm}
-	\caption{Object Property Paths as Property Constraint}
-	\label{tab:property-constraint-object-property-paths}
-	\centering
-		\begin{tabular}{l|l|l|l|l|l|l}
-      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
-      \hline
-      property & $\top$ & authorOf, genre & authorOfGenre & $\top$ & $\sqsubseteq$ & - \\
-		\end{tabular}
-\end{table}
-
-There are \emph{simple constraints} which are not expressible in \emph{DL} but can still be described using the \emph{RDF-CV} 
-such as constraints of the type \emph{literal pattern matching} (\emph{R-44}) which restrict literals to match given patterns.
-The \emph{universal restriction} {\small\ms{Book $\sqsubseteq$ $\forall$ identifier.ISBN}} ensures that \emph{books} can only have valid \emph{ISBN} identifiers, 
-i.e., strings that match a given regular expression.
-%Even though, the restriction of the datatype \emph{ISBN} cannot be expressed in \emph{DL}, \emph{OWL 2 DL} can be used to express the \emph{literal pattern matching} constraint:
-%\begin{ex}
-%ISBN a RDFS:Datatype ; owl:equivalentClass [ a RDFS:Datatype ;
-    %owl:onDatatype xsd:string ; 
-    %owl:withRestrictions ([ xsd:pattern "^\d{9}[\d|X]" ])] .
-%\end{ex} 
-%The first OWL 2 axiom explicitly declares {\em ISBN} to be a datatype.
-%\er{Why start from second and then first?
-Also better we say "owl axiom" when we talk axiom of owl, to prevent ambiguity.}\tb{resolved}
-%The second OWL 2 axiom defines {\em ISBN} as an abbreviation for a datatype restriction on {\em xsd:string}. 
-%The datatype {\em ISBN} can be used just like any other datatype like in the \emph{universal restriction} above.
-%There are multiple use cases associated with the requirement to match literals according to given patterns (\emph{Literal Pattern Matching}\footnote{Corresponds to \emph{R-44-PATTERN-MATCHING-ON-RDF-LITERALS}}).
-%The enterprise vessel, e.g.,  can only have the registry numbers "NCC-1701", "NCC-1701-A", "NCC-1701-B", "NCC-1701-C", "NCC-1701-D", or "NCC-1701-E".
-%The universal restriction can be represented in DL:
-%\ms{Enterprise $\sqsubseteq$ $\forall$ registryNumber.RegistryNumber}.
-%The restriction of the datatype \ms{RegistryNumber}, however, cannot be expressed in DL, but OWL 2 DL can be used anyway to express the literal pattern matching constraint:
-%
-%\begin{ex}
-%RegistryNumber
-    %a rdfs:Datatype ; owl:equivalentClass [ a rdfs:Datatype ;
-        %owl:onDatatype xsd:string ;
-        %owl:withRestrictions ( [ xsd:pattern "NCC-1701([-][A-E])?" ] ) ] .
-%\end{ex}
-%The second axiom defines \ms{RegistryNumber} as an abbreviation for a datatype restriction on \ms{xsd:string}. 
-%The first axiom explicitly declares \ms{RegistryNumber} to be a datatype. 
-%The datatype \ms{RegistryNumber} can be used just like any other datatype like in the universal restriction above.
-%The \emph{literal pattern matching} constraint validates \emph{ISBN} literals according to the regular expression causing constraint violations for triples which do not not match. 
-%\ms{Janeway commandsEnterprise Voyager} and \ms{Voyager registryNumber "NCC-74656"\textasciicircum{}\textasciicircum{}RegistryNumber}, 
-%but not for the triples \ms{Picard commandsEnterprise Enterprise} and \ms{Enterprise registryNumber "NCC-1701-E"\textasciicircum{}\textasciicircum{}RegistryNumber}.
-Table \ref{tab:simple-constraint-not-expressible-in-dl)} presents 
-how the \emph{literal pattern matching} \emph{simple constraint} which is not expressible in \emph{DL} and 
-how the \emph{universal restriction} \emph{complex constraint} which is expressible in \emph{DL} are mapped to the \emph{RDF-CV}.
-Thereby, the \emph{context class} \emph{ISBN}, whose instances must satisfy the \emph{simple constraint}, 
-is reused within the list of \emph{classes} the \emph{complex constraint} refers to.
-The \emph{literal pattern matching} constraint type introduces the \emph{constraining element} \emph{regex}
-whose validation has to be implemented once like for any other \emph{constraining element}.
-%In general, validation has to be implemented once for each \emph{generic constraint type} which is not expressible in \emph{DL}. 
-%\begin{gcotable}
-%property & Enterprise & registryNumber & - & RegistryNumber & $\forall$ & - \\
-%class & RegistryNumber & - & - & xsd:string & regex & 'NCC-1701([-][A-E])?' \\
-%\end{gcotable}
-\begin{table}[H]
-  \scriptsize
-  \sffamily
-  \vspace{0cm}
-	\caption{Simple Constraints which are not Expressible in DL)}
-	\label{tab:simple-constraint-not-expressible-in-dl)}
-	\centering
-		\begin{tabular}{l|l|l|l|l|l|l}
-      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
-      \hline
-      class & ISBN & - & - & xsd:string & regex & '\string^\text{$\backslash$d$\{9\}$[$\backslash$d$\mid$X]}\$' \\
-      property & Book & identifier & - & ISBN & $\forall$ & - \\
-		\end{tabular}
-\end{table} %\tb{Erman, can you please format the regular expression in the table above correctly?}
-
-\subsection{\emph{Complex Constraints}}
-
-%\emph{Complex constraints} are composed out of \emph{simple constraints} and/or \emph{complex constraints}.
-\emph{Complex constraints} of the constraint type \emph{context-specific exclusive or of property groups} (\emph{R-13}) 
-restrict individuals of given classes to have all properties of exactly one of multiple mutually exclusive property groups.
-\emph{Publications}, e.g., are either identified by an \emph{ISBN} and a \emph{title} (for books) or by an \emph{ISSN} and a \emph{title} (for periodical \emph{publications}), but it should not be possible to assign both identifiers to a given \emph{publication}.
-As \emph{The-Great-Gatsby} is a \emph{publication} with an \emph{ISBN} and a \emph{title} without an \emph{ISSN}, 
-\emph{The-Great-Gatsby} is considered as a valid \emph{publication}.
-The \emph{complex constraint} is generically expressible by \emph{DL}:
-%This \emph{complex constraint} is expressible specifically by \emph{ShEx} and generically by \emph{DL} (and can therefore be mapped to the \emph{RDF-CV} \cite{BoschEckert2015-2}).
-
-%Half-Klingons, e.g., either have a klingon mother and a human father or a human mother and a klingon father, which can be expressed by ShEx:
-
-%\begin{ex}
-%Half-Klingon { 
-    %( klingonMother Klingon , humanFather Human ) |
-    %( humanMother Human , klingonFather Klingon ) }
-%\end{ex}
-
-%\begin{ex}[commandchars=\\\{\}]
-%\textit{ShEx:} Publication { ( isbn string , title string ) | ( issn string , title string ) }
-%\end{ex}
-
-%As \ms{B'Elanna Torres} is a \ms{Half-Klingon} with a klingon mother and a human father, the following data is valid:
-
-%\begin{ex}
-%BElannaTorres a Half-Klingon ;
-    %klingonMother Miral ; humanFather JohnTorres .
-%\end{ex}
-
-%\begin{DL}
-%rdf:type(BElannaTorres,Half-Klingon) \\
-%klingonMother(BElannaTorres,Miral) \\
-%klingonMother(BElannaTorres,JohnTorres)
-%\end{DL}
-%The \emph{complex constraint} is mapped to the \emph{RDF-CV} (see Table \ref{tab:complex-constraints}) and expressed in \emph{DL} as follows:
-
-%\begin{DL}
-%Half-Klingon $\sqsubseteq$ ($\neg$E $\sqcap$ F) $\sqcup$ (E $\sqcap$ $\neg$F) \\ 
-%E $\equiv$ A $\sqcap$ B \\
-%F $\equiv$ C $\sqcap$ D \\
-%A $\sqsubseteq$ $\geq$ 1 klingonMother.Klingon $\sqcap$ $\leq$ 1 klingonMother.Klingon \\
-%B $\sqsubseteq$ $\geq$ 1 humanFather.Human $\sqcap$ $\leq$ 1 humanFather.Human \\
-%C $\sqsubseteq$ $\geq$ 1 humanMother.Human $\sqcap$ $\leq$ 1 humanMother.Human \\
-%D $\sqsubseteq$ $\geq$ 1 klingonFather.Klingon $\sqcap$ $\leq$ 1 klingonFather.Klingon \\
-%\end{DL}
-
-\begin{DL}
-\textbf{Publication $\sqsubseteq$ ($\neg$E $\sqcap$ F) $\sqcup$ (E $\sqcap$ $\neg$F)} , E $\equiv$ A $\sqcap$ B , F $\equiv$ C $\sqcap$ D \\
-A $\sqsubseteq$ $\geq$ 1 isbn.string $\sqcap$ $\leq$ 1 isbn.string , B $\sqsubseteq$ $\geq$ 1 title.string $\sqcap$ $\leq$ 1 title.string \\
-C $\sqsubseteq$ $\geq$ 1 issn.string $\sqcap$ $\leq$ 1 issn.string , D $\sqsubseteq$ $\geq$ 1 title.string $\sqcap$ $\leq$ 1 title.string \\
-\end{DL}
-
-%\begin{gcotable}
-%class & Half-Klingon & - & - & $\neg$E $\sqcap$ F, E $\sqcap$ $\neg$F & $\sqcup$ & - \\
-%class & $\neg$E $\sqcap$ F & - & - & $\neg$E, F & $\sqcap$ & - \\
-%class & E $\sqcap$ $\neg$F & - & - & E, $\neg$F & $\sqcap$ & - \\
-%class & $\neg$E & - & - & E & $\neg$ & - \\
-%class & E & - & - & A, B & $\sqcap$ & - \\
-%class & $\neg$F & - & - & F & $\neg$ & - \\
-%class & F & - & - & C, D & $\sqcap$ & - \\
-%class & A & - & - & A1, A2 & $\sqcap$ & - \\
-%property & A1 & klingonMother & - & Klingon & $\geq$ & 1 \\
-%property & A2 & klingonMother & - & Klingon & $\leq$ & 1 \\
-%class & B & - & - & B1, B2 & $\sqcap$ & - \\
-%property & B1 & humanFather & - & Human & $\geq$ & 1 \\
-%property & B2 & humanFather & - & Human & $\leq$ & 1 \\
-%class & C & - & - & C1, C2 & $\sqcap$ & - \\
-%property & C1 & humanMother & - & Human & $\geq$ & 1 \\
-%property & C2 & humanMother & - & Human & $\leq$ & 1 \\
-%class & D & - & - & D1, D2 & $\sqcap$ & - \\
-%property & D1 & klingonFather & - & Klingon & $\geq$ & 1 \\
-%property & D2 & klingonFather & - & Klingon & $\leq$ & 1 \\
-%\end{gcotable}
-
-%\begin{table}[H]
-  %\scriptsize
-  %\sffamily
-  %\vspace{0cm}
-	%\caption{Complex Constraints}
-	%\label{tab:complex-constraints}
-	%\centering
-		%\begin{tabular}{l|l|l|l|l|l|l}
-      %\textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
-      %\hline
-%class & Publication & - & - & $\neg$E $\sqcap$ F, E $\sqcap$ $\neg$F & $\sqcup$ & - \\
-%class & $\neg$E $\sqcap$ F & - & - & $\neg$E, F & $\sqcap$ & - \\
-%class & E $\sqcap$ $\neg$F & - & - & E, $\neg$F & $\sqcap$ & - \\
-%class & $\neg$E & - & - & E & $\neg$ & - \\
-%class & E & - & - & A, B & $\sqcap$ & - \\
-%class & $\neg$F & - & - & F & $\neg$ & - \\
-%class & F & - & - & C, D & $\sqcap$ & - \\
-%class & A & - & - & A1, A2 & $\sqcap$ & - \\
-%property & A1 & isbn & - & string & $\geq$ & 1 \\
-%property & A2 & isbn & - & string & $\leq$ & 1 \\
-%class & B & - & - & B1, B2 & $\sqcap$ & - \\
-%property & B1 & title & - & string & $\geq$ & 1 \\
-%property & B2 & title & - & string & $\leq$ & 1 \\
-%class & C & - & - & C1, C2 & $\sqcap$ & - \\
-%property & C1 & issn & - & string & $\geq$ & 1 \\
-%property & C2 & issn & - & string & $\leq$ & 1 \\
-%class & D & - & - & D1, D2 & $\sqcap$ & - \\
-%property & D1 & title & - & string & $\geq$ & 1 \\
-%property & D2 & title & - & string & $\leq$ & 1 \\
-		%\end{tabular}
-%\end{table}
-
-%Even though, tools may generate \emph{generic constraints} automatically, this 
-The \emph{DL} statements demonstrate that the \emph{complex constraint} 
-is composed of many other \emph{complex} (e.g. \emph{minimum and maximum qualified cardinality restrictions}) and \emph{simple constraints} (e.g. constraints on sets).
-As \emph{exact (un)qualified cardinality restrictions (=n)} and \emph{exclusive or (XOR)} are frequently used \emph{complex constraints},
-we propose to simplify them as \emph{simple constraints} in terms of syntactic sugar.
-As a consequence, the \emph{context-specific exclusive or of property groups} \emph{complex constraint} is represented as a \emph{generic constraint} by means of the \emph{RDF-CV} more intuitively and concisely (Table \ref{tab:simplified-complex-constraints}).
-
-%\begin{gcotable}
-%class & Half-Klingon & - & - & E, F & XOR \\
-%class & E & - & - & A, B & $\sqcap$ \\
-%class & F & - & - & C, D & $\sqcap$ \\
-%property & A & klingonMother & - & Klingon & = & 1 \\
-%property & B & humanFather & - & Human & = & 1 \\
-%property & C & humanMother & - & Human & = & 1 \\
-%property & D & klingonFather & - & Klingon & = & 1 \\
-%\end{gcotable}
-
-\begin{table}[H]
-  \scriptsize
-  \sffamily
-  \vspace{0cm}
-	\caption{Simplified Complex Constraints}
-	\label{tab:simplified-complex-constraints}
-	\centering
-		\begin{tabular}{l|l|l|l|l|l|l}
-      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
-      \hline
-class & Publication & - & - & E, F & XOR \\
-class & E & - & - & A, B & $\sqcap$ \\
-class & F & - & - & C, D & $\sqcap$ \\
-property & A & isbn & - & string & = & 1 \\
-property & B & title & - & string & = & 1 \\
-property & C & issn & - & string & = & 1 \\
-property & D & title & - & string & = & 1 \\
-		\end{tabular}
-\end{table}
-
-%\emph{Complex constraints} can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
-%There are three forms of \emph{OWL RBox axioms}: \emph{role inclusions}, \emph{equivalence} and \emph{disjointness}. 
-%\emph{OWL} provides a variety of other axiom types: \emph{role transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity}. 
-%These axiom types are sometimes considered as basic axiom types in \emph{DL} - using some suggestive notation such as
-%\ms{Trans(ancestorOf)} to express that the role \emph{ancestorOf} is transitive.
-%Such axioms, however, are just syntactic sugar - 
-%all role characteristics can be expressed using the basic features of \emph{DL}.
-%
-%The \emph{irreflexive object properties} constraint type (\emph{R-60}) 
-%restricts that no individual is connected by a given object property to itself \cite{Kroetzsch2012}.
-%With the following \emph{irreflexive object property} constraint, for instance, one can state that individuals cannot be authors of themselves:
-%\begin{DL}
-%\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists authorOf.Self$}
-%\end{DL}
-%When mapped to the \emph{RDF-CV} (see Table \ref{tab:irreflexive-object-properties-as-complex-constraints}), the \emph{complex constraint} aggregates three \emph{simple constraints} (one \emph{property} and two \emph{class constraints}):
-%
-%%\begin{gcotable}
-%%property & $\exists$ marriedTo . Self & marriedTo & - & Self & $\exists$ & - \\
-%%class & $\neg$ $\exists$ marriedTo . Self & - & - & $\exists$ marriedTo . Self & $\neg$ & - \\
-%%class & $\top$ & - & - & $\top$, $\neg$ $\exists$ marriedTo . Self & $\sqsubseteq$ & - \\
-%%\end{gcotable}
-%
-%\begin{table}[H]
-  %\scriptsize
-  %\sffamily
-  %\vspace{0cm}
-	%\caption{Irreflexive Object Properties as Complex Constraints}
-	%\label{tab:irreflexive-object-properties-as-complex-constraints}
-	%\centering
-		%\begin{tabular}{l|l|l|l|l|l|l}
-      %\textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
-      %\hline
-%property & $\exists$ authorOf.Self & marriedTo & - & Self & $\exists$ & - \\
-%class & $\neg$ $\exists$ authorOf.Self & - & - & $\exists$ authorOf.Self & $\neg$ & - \\
-%class & $\top$ & - & - & $\top$, $\neg$ $\exists$ authorOf.Self & $\sqsubseteq$ & - \\
-		%\end{tabular}
-%\end{table}
-%
-%When using the \emph{OWL RBox axiom} \emph{role irreflexivity} in terms of syntactic sugar, 
-%the \emph{complex constraint} can be expressed more concisely in form of a \emph{simple property constraint} with exactly the same semantics (see Table \ref{tab:irreflexive-object-properties-as-simple-constraints}):
-%
-%%\begin{gcotable}
-%%property & $\top$ & marriedTo & - & - & irreflexive & - \\
-%%\end{gcotable}
-%
-%\begin{table}[H]
-  %\scriptsize
-  %\sffamily
-  %\vspace{0cm}
-	%\caption{Irreflexive Object Properties as Simple Constraints}
-	%\label{tab:irreflexive-object-properties-as-simple-constraints}
-	%\centering
-		%\begin{tabular}{l|l|l|l|l|l|l}
-      %\textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
-      %\hline
-%property & $\top$ & authorOf & - & - & irreflexive & - \\
-		%\end{tabular}
-%\end{table}
-The \emph{primary key properties} constraint type (\emph{R-226}) is often useful to declare a given (datatype) property as the primary key of a class, so that a system can enforce uniqueness. 
-\emph{Books}, e.g., are uniquely identified by their \emph{ISBN}, i.e., the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}
-which can be represented using the \emph{RDF-CV} in form of a \emph{complex constraint} consisting of two \emph{simple constraints} (Table \ref{tab:primary-key-properties-as-complex-constraints}).
-
-%\begin{gcotable}
-%property & $\top$ & commandAuthorizationCode$^{-}$ & commandAuthorizationCode$^{-}$ & - & inverse & - \\
-%property & $\top$ & commandAuthorizationCode$^{-}$ & - & - & functional & - \\
-%\end{gcotable}
-
-\begin{table}[H]
-  \scriptsize
-  \sffamily
-  \vspace{0cm}
-	\caption{Primary Key Properties as Complex Constraints}
-	\label{tab:primary-key-properties-as-complex-constraints}
-	\centering
-		\begin{tabular}{l|l|l|l|l|l|l}
-      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
-      \hline
-property & $\top$ & isbn$^{-}$ & isbn$^{-}$ & - & inverse & - \\
-property & Book & isbn$^{-}$ & - & - & functional & - \\
-		\end{tabular}
-\end{table}
-
-\emph{Keys}, however, are even more general, i.e., a generalization of \emph{inverse functional properties} \cite{Schneider2009}.
-A key can be a datatype, an object property, or a chain of properties.
-For these generalization purposes, as there are different sorts of keys, and as keys can lead to undecidability, 
-\emph{DL} is extended with a special construct \emph{keyfor} \cite{Lutz2005}.
-When using \emph{keyfor} (\ms{isbn keyfor Book}), 
-the \emph{complex constraint} can be formulated as a \emph{simple constraint} which looks like the following in concrete RDF turtle syntax:
-
-%\begin{gcotable}
-%property & StarFleetOfficer & commandAuthorizationCode & - & - & keyfor & - \\
-%\end{gcotable}
-
-%\begin{table}[H]
-  %\scriptsize
-  %\sffamily
-  %\vspace{0cm}
-	%\caption{Primary Key Properties as Simple Constraints}
-	%\label{tab:primary-key-properties-as-simple-constraints}
-	%\centering
-		%\begin{tabular}{l|l|l|l|l|l|l}
-      %\textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
-      %\hline
-%property & Book & isbn & - & - & keyfor & - \\
-		%\end{tabular}
-%\end{table}
-
-\begin{ex}[commandchars=\\\{\}]
-[   a \textit{rdfcv:PropertyConstraint} , \textit{rdfcv:SimpleConstraint} ;
-    \textit{rdfcv:contextClass} Book ; \textit{rdfcv:leftProperties} ( isbn ) ; \textit{rdfcv:constrainingElement} "keyfor" ] .
-\end{ex}
-
-\emph{Complex constraints} of frequently used constraint types corresponding to \emph{DL} axioms like 
-\emph{transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity}
-can also be simplified in the same way, 
-as, although, such axioms can be expressed using basic \emph{DL} features, 
-\emph{DL} axioms like \emph{transitivity} can also be used in terms of syntactic sugar \cite{BoschEckert2015-2}.
-%Starfleet officers, e.g., are uniquely identified by their command authorization code (e.g. to activate and cancel auto-destruct sequences).
-%It means that the property \emph{commandAuthorizationCode} is inverse functional - mapped to DL and the \emph{RDF-CV} as follows:
-%
-%\begin{DL}
-%$(\ms{funct } commandAuthorizationCode\sp{\overline{\ }})$
-%\end{DL}
-%
-%%\begin{gcotable}
-%%property & $\top$ & commandAuthorizationCode$^{-}$ & commandAuthorizationCode$^{-}$ & - & inverse & - \\
-%%property & $\top$ & commandAuthorizationCode$^{-}$ & - & - & functional & - \\
-%%\end{gcotable}
-%
-%\begin{table}
-  %\scriptsize
-  %\sffamily
-  %\vspace{0cm}
-	%\centering
-		%\begin{tabular}{l|l|l|l|l|l|l}
-      %\textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
-      %\hline
-%property & $\top$ & commandAuthorizationCode$^{-}$ & commandAuthorizationCode$^{-}$ & - & inverse & - \\
-%property & $\top$ & commandAuthorizationCode$^{-}$ & - & - & functional & - \\
-		%\end{tabular}
-	%\caption{Primary Key Properties as Complex Constraints}
-	%\label{tab:primary-key-properties-as-complex-constraints}
-%\end{table}
-%
-%Keys, however, are even more general, i.e., a generalization of inverse functional properties \cite{Schneider2009}.
-%A key can be a datatype property, an object property, or a chain of properties.
-%For this generalization purposes, as there are different sorts of key, and as keys can lead to undecidability, 
-%DL is extended with \emph{key boxes} and a special \emph{keyfor} construct\cite{Lutz2005}.
-%This leads to the following DL and \emph{RDF-CV} mappings (only one \emph{simple property constraint}):
-%
-%\begin{DL}
-%commandAuthorizationCode \ms{keyfor} StarfleetOfficer
-%\end{DL}
-
-%\begin{table}
-  %\scriptsize
-  %\sffamily
-  %\vspace{0cm}
-	%\centering
-		%\begin{tabular}{l|l|l|l|l|l|l}
-      %\textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
-      %\hline
-%property & StarFleetOfficer & commandAuthorizationCode & - & - & keyfor & - \\
-		%\end{tabular}
-	%\caption{Primary Key Properties as Simple Constraints}
-	%\label{tab:primary-key-properties-as-simple-constraints}
-%\end{table}
-
-%\begin{itemize}
-  %\item domain and range
-	%\item Primary Key Properties
-	%\item ( Exact Qualified Cardinality Restrictions on Properties )
-%\end{itemize}
-
-%\subsection{Disjoint Classes}
-%
-%\begin{DL}
-%Hologram $\sqcap$ Human $\sqsubseteq$ $\perp$\\
-%Alternative:\\
-%$Hologram \sqsubseteq \neg Human$
-%\end{DL}
-%
-%\subsection{Minimum Qualified Cardinality Restrictions on Properties}
-%
-%\begin{DL}
-%$FederationCaptain \sqsubseteq Federation \sqcap \geq1 commandsVessel . Vessel $
-%\end{DL}
-
-%\section{Transformations and Automatic Validation of Specific Constraints}
-%\section{Transformations between Specific Constraints (Expressed by Different Constraint Languages)}
-%\section{Transformations between Specific Constraints}
-
-%\section{Validation of Specific and Generic Constraints}
-
-\section{Related Work}
-
-In this section, we present current languages for constraint formulation and RDF data validation\footnote{
-\emph{SPARQL}: \url{http://www.w3.org/TR/sparql11-query}, 
-\emph{SPIN}: \url{http://spinrdf.org},
-\emph{Pellet ICV}: \url{http://clarkparsia.com/pellet/icv},
-\emph{Stardog ICV}: \url{http://docs.stardog.com/#_validating_constraints},
-\emph{ShEx}: \url{http://www.w3.org/Submission/shex-defn},
-\emph{ReSh}: \url{http://www.w3.org/Submission/shapes},
-\emph{DCMI RDF-AP}: \url{http://dublincore.org/documents/singapore-framework},
-\emph{Bibframe}: \url{http://bibframe.org},
-\emph{DSP}: \url{http://dublincore.org/documents/dc-dsp},
-\emph{RDF Schemarama}: \url{http://swordfish.rdfweb.org/discovery/2001/01/schemarama}
-%\emph{Schematron}: \url{http://www.schematron.com},
-%\emph{XML Schema}: \url{http://www.w3.org/TR/xmlschema-1},
-}.
-\emph{SPIN}, \emph{SPARQL}, \emph{OWL 2}, \emph{ShEx}, \emph{ReSh}, and \emph{DSP} are the six most promising and applied languages.
-%
-The query language for RDF \emph{SPARQL} is generally seen as the method of choice to validate data according to certain constraints \cite{Fuerber2010}, 
-although, it is not ideal for their formulation. 
-In contrast, high-level constraint languages are comparatively easy to understand and constraints can be formulated more concisely.
-Declarative languages may be placed on top of \emph{SPARQL} and \emph{SPIN} when using them as implementation languages.
-%
-\emph{SPIN} provides a vocabulary to represent \emph{SPARQL} queries as RDF triples
-and uses \emph{SPARQL} to specify logical constraints and inference rules \cite{Fuerber2010}.
-%
-\emph{Stardog ICV} and \emph{Pellet ICV} use \emph{OWL 2} constructs to formulate constraints.
-The \emph{Pellet Integrity Constraint Validator (ICV)} is a proof-of-concept extension for the \emph{OWL 2 DL} reasoner \emph{Pellet}. 
-\emph{Stardog ICV} 
-validates RDF data stored in a Stardog database according to 
-constraints which may be written in \emph{SPARQL}, \emph{OWL}, or \emph{SWRL}. 
-%
-\emph{ShEx} specifies a language whose syntax and semantics are similar to regular expressions.
-\emph{ShEx} associate RDF graphs with labeled patterns called \emph{shapes} 
-which are used to express formal constraints on the content of RDF graphs.
-%
-\emph{ReSh} defines its own vocabulary for specifying \emph{shapes} of RDF resources.
-Ryman et al. define \emph{shape} as a description of the set of triples a resource is expected to contain and of the integrity constraints those triples are required to satisfy \cite{Ryman2013}. 
-%
-\emph{DCMI RDF Application Profiles (AP)} and \emph{Bibframe} are approaches to specify profiles for application-specific purposes. 
-\emph{DCMI RDF-AP} uses \emph{DSP} as generic constraint language which is also intuitive for non-experts.
-The \emph{Bibliographic Framework Initiative (Bibframe)} defines a vocabulary which has a strong overlap with \emph{DSP}.
-%
-Kontokostas et al. define 17 data quality integrity constraints represented as \emph{SPARQL} query templates called \emph{Data Quality Test Patterns (DQTP)} \cite{Kontokostas2014}. 
-%
-\emph{RDF Schemarama} 
-is a proof-of-concept demonstrator based on ideas from \emph{Schematron}. 
-It allows to check that RDF data has required properties and
-it is based on \emph{Squish}, an SQL-ish query language for RDF, instead of \emph{SPARQL}. 
-%
-%\emph{Schematron} is an ISO standard for the validation and quality control of XML documents based on XPath and XSLT. 
-%
-%\emph{XML Schema} is the primary technology for specifying and constraining the structure of XML documents.
-%
-In addition to the formulation of constraints, \emph{SPIN} (open source API), \emph{Stardog ICV} (as part of the \emph{Stardog RDF database}), \emph{DQTP} (tests), \emph{Pellet ICV} (extension of \emph{Pellet OWL 2 DL} reasoner) and \emph{ShEx} offer executable validation systems using \emph{SPARQL} as implementation language.
-
-\section{Conclusion and Future Work}
-
-%Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group, 
-%we published by today 81 constraint types \cite{BoschNolleAcarEckert2015}
-%which form the basis to
-%lay the ground for discussions on validation
-%by defining a basic terminology and classification system for RDF constraints.
-
-Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group,
-we published by today 81 requirements to validate RDF data and to formulate constraints; 
-each of them corresponds to a constraint type from which concrete constraints are instantiated to be checked on RDF data.
-These constraint types form the basis to
-lay the ground for discussions on validation
-by defining a basic terminology and classification system for RDF constraints.
-%
-There exists no single best solution considered as high-level intuitive constraint language which enables to express constraints in an easy and concise way and which is able to meet all requirements raised by data practitioners.
-Thus, the idea behind this paper is to satisfy all requirements
-by representing constraints of any constraint type in a generic way using a lightweight vocabulary which consists of only a few terms.
-%To show that constraints can either be represented specifically (\emph{specific constraints}) by constraint languages
-%or generically (\emph{generic constraints}) by \emph{description logics (DL)},
-%we mapped constraint types to \emph{DL} 
-%to determine which \emph{DL} constructs are needed to express them \cite{BoschNolleAcarEckert2015} (Section \ref{sec:vocabulary}).
-
-As there is no standard way to formulate constraints, 
-semantically equivalent \emph{specific constraints} may be represented by a variety of languages - each of them having different syntax and semantics.
-We propose transformations between semantically equivalent \emph{specific constraints}
-by using the proposed vocabulary to intermediately represent constraints in a generic way
-(1) to avoid the necessity to understand several languages,
-(2) to resolve misunderstandings about the meaning of particular constraints, and
-(3) to enhance the interoperability of constraint languages (Section \ref{sec:transformations}).
-
-We use \emph{SPIN} as basis to develop a validation environment\footref{rdf-validator} to validate RDF data according to constraints of constraint types which are expressible by arbitrary constraint languages by mapping them to \emph{SPIN}\footref{spin-mappings} \cite{BoschEckert2014-2}.
-When language designers extend constraint languages 
-to be able to formulate constraints of not yet supported constraint types,
-our proposal enables to reuse the validation implementation of these constraint types 
-by mapping \emph{specific constraints} expressed by the language to the corresponding \emph{generic constraint}.
-For any constraint language, we enable to offer a validation implementation of any constraint type out-of-the-box
-by providing a \emph{SPIN} mapping
-for each constraint type\footref{RDF-CV-2-SPIN}  
-whose constraints are represented generically \cite{BoschEckert2015-2}. 
-Furthermore, our proposal makes sure that the validation on semantically equivalent \emph{specific constraints} expressed by different languages
-leads to exactly the same validation results, 
-i.e., that validation is performed independently from the used language (Section \ref{sec:validation}).
-
-It is part of future work 
-(1) to extend the \emph{RDF Validator} by generating \emph{generic constraints} according to inputs of domain experts who may not be familiar with the formulation of constraints,
-(2) to offer bidirectional transformations between \emph{specific constraints} expressed by the most common constraint languages and corresponding \emph{generic constraints}, and
-(3) to provide translations between semantically equivalent \emph{specific constraints} expressed by the most common constraint languages by using the developed vocabulary to intermediately represent constraints.
-Identifying RDF validation requirements is an ongoing process,
-so the task to map constraints of new constraint types to the vocabulary.
-
-%\begin{itemize}
-	%\item to provide a GUI which generates generic constraints automatically according to inputs of domain experts who are not familiar with the formulation of constraints.
-	%\item to offer bidirectional transformations between specific constraints (expressed by multiple constraint languages) and generic constraints. 
-	%\item to provide translations between specific constraints (expressed by any specific constraint language) by using generic constraints as an intermediate transformation step.
-%\end{itemize}
-
-\bibliography{../../literature/literature}{}
-\bibliographystyle{apacite}
-\setcounter{tocdepth}{1}
 %\listoftodos

### 2015-07-07 paper/paper 2/dc-2015.tex
Final Abstract and Title
section 2

@@
 
-\section{A Vocabulary to Describe RDF Constraints Generically} 
+\section{A Vocabulary to Describe RDF Constraints of any RDF Constraint Type} 
 \label{sec:vocabulary}
 
-Prerequisites to develop a vocabulary to describe constraints of any constraint type in a generic way are 
-(1) to specify the underlying semantics for validation and thus for the vocabulary and (2) to define a basic terminology and classification system for RDF constraints which lay the ground for discussions on validation.
+Prerequisites to develop a vocabulary to describe RDF constraints of any RDF constraint type are (1) to specify the underlying semantics for RDF validation and thus for the vocabulary and (2) to define a basic terminology and classification system for RDF constraints which lay the ground for discussions on RDF validation.
 

### 2015-07-07 paper/paper 2/dc-2015.tex
section 2.1

@@
 \emph{Shape Expressions (ShEx)}, \emph{Resource Shapes (ReSh)}, and \emph{Description Set Profiles (DSP)}. 
-The \emph{Web Ontology Language} \emph{(OWL)} in its current version \emph{OWL 2} can also be used as a constraint language.
+The \emph{Web Ontology Language} \emph{(OWL)} in its current version OWL 2 can also be used as a constraint language.
 With its direct support of validation via \emph{SPARQL}, the \emph{SPARQL Inferencing Notation (SPIN)} is very popular and certainly plays an important role for the future development in this field. 
@@
       %\textbf{Expressivity Class} & $Expr(\overline{\mathcal{CT}_R})$ (42) & $Expr(\mathcal{CT}_R)$ (32) \\		
-			\emph{DSP} & \emph{ReSh} & \emph{ShEx} & \emph{OWL 2} & \emph{SPIN} \\	
+			\emph{DSP} & \emph{ReSh} & \emph{ShEx} & OWL 2 & \emph{SPIN} \\	
       \hline
@@
 
-The fact that \emph{SPIN} supports all and \emph{OWL 2} covers 2/3 of all constraint types
-emphasizes the significant role \emph{SPIN} and \emph{OWL 2} play for the future development of constraint languages.
+The fact that \emph{SPIN} supports all and OWL 2 covers 2/3 of all constraint types
+emphasizes the significant role \emph{SPIN} and OWL 2 play for the future development of constraint languages.
 \emph{SPARQL} and therefore \emph{SPIN}, the \emph{SPARQL}-based way to formulate and check constraints, is generally seen as the method of choice to validate data according to certain constraints \cite{Fuerber2010},
@@
 
-RDF validation and \emph{OWL 2} assume different semantics. 
-This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past.
-We compare semantics of RDF validation and \emph{OWL 2} as \emph{OWL 2} is considered as a constraint language 
-when validation semantics is applied.
-%
-\emph{OWL 2} is based on the {\em open-world assumption} (\emph{OWA}), i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose to represent knowledge on the \emph{WWW}.
-As each \emph{book} must have a \emph{title} {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a \emph{book}, %{\small\ms{(Book(Hamlet)),}}
-{\em Hamlet} must have at least one \emph{title}.
-In an \emph{OWA} setting, this constraint does not cause a violation, even if there is no explicitly defined \emph{title}, since there must be a \emph{title} for this \emph{book} which we may not know.
+RDF validation and OWL 2 assume different semantics. 
+This ambiguity in semantics is one of the main reasons why OWL 2 has not been adopted as a standard constraint language for RDF validation in the past.
+We compare semantics of RDF validation and OWL 2 as OWL 2 is considered as a constraint language 
+in case the semantics for RDF validation is applied.
+%
+OWL 2 is based on the {\em open-world assumption} (OWA), i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose to represent knowledge on the World Wide Web.
+As each book must have a title {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a book, %{\small\ms{(Book(Hamlet)),}}
+{\em Hamlet} must have a title as well.
+In an OWA setting, this constraint does not cause a violation, even if there is no explicitly defined title, since there must be a title for this book which we may not know. 
 %($\mathcal{K}$ is consistent).
 As RDF validation has its origin in the XML world
-many RDF validation scenarios require the {\em closed-world assumption} (\emph{CWA}), i.e., a statement is inferred to be false if it cannot be proved to be true.
-Thus, classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals. 
-The \emph{CWA} yields to a violation since there is no explicitly defined \emph{title} for the \emph{book} {\em Hamlet}. 
+many RDF validation scenarios require the {\em closed-world assumption} (CWA), i.e., a statement is inferred to be false if it cannot be proved to be true.
+Thus, classical constraint languages are based on the CWA where constraints need to be satisfied only by named individuals. 
+The CWA yields to a violation since there is no explicitly defined title for the book {\em Hamlet}. 
 %
 Validation requires that different names represent different objects (\emph{unique name assumption (UNA)}), whereas,
-\emph{OWL 2} is based on the {\em non-unique name assumption (nUNA)}.  
-If we define the property \emph{title} to be functional {\small\ms{(funct (title)),}} a \emph{book} can have at most one distinct \emph{title}.
-\emph{UNA} causes a clash
-if the \emph{book} {\em Huckleberry-Finn} has more than one \emph{title}.
-For \emph{nUNA}, however, reasoning concludes that the \emph{title} {\em The-Adventures-of-Huckleberry-Finn} must be the same as the \emph{title} {\em Die-Abenteuer-des-Huckleberry-Finn} 
+OWL 2 is based on the {\em non-unique name assumption (nUNA)}.  
+If we define the property title to be functional {\small\ms{(funct (title)),}} a book can have at most one distinct title.
+UNA causes a clash
+if the book {\em Huckleberry-Finn} has more than one title.
+For nUNA, however, reasoning concludes that the title {\em The-Adventures-of-Huckleberry-Finn} must be the same as the title {\em Die-Abenteuer-des-Huckleberry-Finn} 
 which resolves the violation. 
-%Although, \emph{OWL 2} does not assume \emph{UNA}, \emph{OWL 2} has the constructs \emph{owl:sameAs} and \emph{owl:differentFrom} to state that two names are the same or different.
-If validation would assume \emph{OWA} and \emph{nUNA}, validation won’t be that restrictive and therefore we won’t get the intended validation results.
-%
-%\emph{OWL 2} reasoning is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true. 
+%Although, OWL 2 does not assume UNA, OWL 2 has the constructs \emph{owl:sameAs} and \emph{owl:differentFrom} to state that two names are the same or different.
+If validation would assume OWA and nUNA, validation won’t be that restrictive and therefore we won’t get the intended validation results.
+%
+%OWL 2 reasoning is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true. 
 %%which fits its primary design purpose to represent knowledge on the World Wide Web. 
@@
 %%\tb{2. benefit: reasoning solves redundancy problem}
-%As each \emph{book} must have a \emph{title} {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a \emph{book} {\small\ms{(Book(Hamlet)),}}
-%{\em Hamlet} must have at least one \emph{title}.
-%In an \emph{OWA} setting, this axiom does not cause a constraint violation (even if there is no explicitly defined \emph{title}), since there must be a \emph{title} for this \emph{book} which we may not know.
+%As each book must have a title {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a book {\small\ms{(Book(Hamlet)),}}
+%{\em Hamlet} must have at least one title.
+%In an OWA setting, this axiom does not cause a constraint violation (even if there is no explicitly defined title), since there must be a title for this book which we may not know. 
 %On the other hand, RDF validation scenarios require the \emph{closed-world assumption (CWA)}, i.e., a statement is inferred to be false if it cannot be proved to be true.
-%When assuming the \emph{CWA}, a constraint violation is raised as there is no explicitly defined title. 
-%A constraint that says that a book must have at least one title in \emph{OWA}, 
+%When assuming the CWA, a constraint violation is raised as there is no explicitly defined title. 
+%A constraint that says that a book must have at least one title in OWA, 
 %does not mean that the title has to be unique. 
@@
 %And since in every model there is only one, \emph{DL} sentences are satisfied. 
-%But this does not correspond to the intended constraint which is usual in \emph{CWA} way.   
-%%Classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals which yields a constraint violation.
-%This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past. 
-%In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (\emph{CWA} and \emph{UNA}) as for RDF validation in general. 
-%In case we want to use \emph{OWL 2} as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general. 
+%But this does not correspond to the intended constraint which is usual in CWA way.   
+%%Classical constraint languages are based on the CWA where constraints need to be satisfied only by named individuals which yields a constraint violation.
+%This ambiguity in semantics is one of the main reasons why OWL 2 has not been adopted as a standard constraint language for RDF validation in the past. 
+%In case we want to use OWL 2 as a constraint language, we adopt the same semantics (CWA and UNA) as for RDF validation in general. 
+%In case we want to use OWL 2 as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general. 
 %\tb{feedback from Erman: the major problem is semantics.
@@
 This is important 
-as for 56.8\% of the constraint types validation results differ if the \emph{CWA} or the \emph{OWA} 
-and as for 66.6\% of the constraint types validation results are different in case the \emph{UNA} or the \emph{nUNA} is assumed \cite{BoschNolleAcarEckert2015}.
+as for 56.8\% of the constraint types validation results differ if the CWA or the OWA 
+and as for 66.6\% of the constraint types validation results are different in case the UNA or the nUNA is assumed \cite{BoschNolleAcarEckert2015}.
 
@@
 %(1) We mapped constraint types to \emph{DL} to logically underpin them and 
-%(2) we described the constraint types' intended behavior in terms of validation results depending on \emph{CWA} and \emph{UNA}.
+%(2) we described the constraint types' intended behavior in terms of validation results depending on CWA and UNA.
 %To be able to define mappings between \emph{specific constraints} (expressed by different languages) and \emph{generic constraints},
@@
 %%if for each constraint the following condition holds:
-%If a constraint is represented by \emph{ShEx} and \emph{OWL 2}, 
+%If a constraint is represented by \emph{ShEx} and OWL 2, 
 %the validation results must be exactly the same, i.e.,
@@
 restrict individuals of given classes to have all properties of exactly one of multiple mutually exclusive property groups.
-\emph{Publications}, e.g., are either identified by an \emph{ISBN} and a \emph{title} (for books) or by an \emph{ISSN} and a \emph{title} (for periodical \emph{publications}), but it should not be possible to assign both identifiers to a given \emph{publication}.
-As \emph{The-Great-Gatsby} is a \emph{publication} with an \emph{ISBN} and a \emph{title} without an \emph{ISSN}, 
+\emph{Publications}, e.g., are either identified by an \emph{ISBN} and a title (for books) or by an \emph{ISSN} and a title (for periodical \emph{publications}), but it should not be possible to assign both identifiers to a given \emph{publication}.
+As \emph{The-Great-Gatsby} is a \emph{publication} with an \emph{ISBN} and a title without an \emph{ISSN}, 
 \emph{The-Great-Gatsby} is considered as a valid \emph{publication}.
@@
 }.
-\emph{SPIN}, \emph{SPARQL}, \emph{OWL 2}, \emph{ShEx}, \emph{ReSh}, and \emph{DSP} are the six most promising and applied languages.
+\emph{SPIN}, \emph{SPARQL}, OWL 2, \emph{ShEx}, \emph{ReSh}, and \emph{DSP} are the six most promising and applied languages.
 %
@@
 %
-\emph{Stardog ICV} and \emph{Pellet ICV} use \emph{OWL 2} constructs to formulate constraints.
+\emph{Stardog ICV} and \emph{Pellet ICV} use OWL 2 constructs to formulate constraints.
 The \emph{Pellet Integrity Constraint Validator (ICV)} is a proof-of-concept extension for the \emph{OWL 2 DL} reasoner \emph{Pellet}. 

### 2015-07-07 paper/paper 2/dc-2015.tex
section 2.1

@@
 in case the semantics for RDF validation is applied.
-%
-OWL 2 is based on the {\em open-world assumption} (OWA), i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose to represent knowledge on the World Wide Web.
+
+OWL 2 is based on the {\em open-world assumption} \emph{(OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose to represent knowledge on the World Wide Web.
 As each book must have a title {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a book, %{\small\ms{(Book(Hamlet)),}}
@@
 %($\mathcal{K}$ is consistent).
-As RDF validation has its origin in the XML world
-many RDF validation scenarios require the {\em closed-world assumption} (CWA), i.e., a statement is inferred to be false if it cannot be proved to be true.
+As RDF validation has its origin in the XML world,
+many RDF validation scenarios require the {\em closed-world assumption} \emph{(CWA)}, i.e., a statement is inferred to be false if it cannot be proved to be true.
 Thus, classical constraint languages are based on the CWA where constraints need to be satisfied only by named individuals. 
-The CWA yields to a violation since there is no explicitly defined title for the book {\em Hamlet}. 
-%
-Validation requires that different names represent different objects (\emph{unique name assumption (UNA)}), whereas,
+Since there is no explicitly defined title for the book {\em Hamlet}, the CWA yields to a violation.
+
+RDF Validation requires that different names represent different objects (\emph{unique name assumption (UNA)}), whereas,
 OWL 2 is based on the {\em non-unique name assumption (nUNA)}.  
-If we define the property title to be functional {\small\ms{(funct (title)),}} a book can have at most one distinct title.
+If we define the property \emph{title} to be functional {\small\ms{(funct (title)),}} a book can have at most one distinct title.
 UNA causes a clash
@@
 %Although, OWL 2 does not assume UNA, OWL 2 has the constructs \emph{owl:sameAs} and \emph{owl:differentFrom} to state that two names are the same or different.
-If validation would assume OWA and nUNA, validation won’t be that restrictive and therefore we won’t get the intended validation results.
+
+If RDF validation would assume OWA and nUNA just like OWL 2 does, validation won’t be that restrictive and therefore we won’t get the intended validation results.
 %
@@
 This is important 
-as for 56.8\% of the constraint types validation results differ if the CWA or the OWA 
+as for 56.8\% of the constraint types validation results differ if the CWA or the OWA is assumed 
 and as for 66.6\% of the constraint types validation results are different in case the UNA or the nUNA is assumed \cite{BoschNolleAcarEckert2015}.
@@
 we thereby document identical semantics of these languages with regard to given constraint types \cite{BoschNolleAcarEckert2015}.
-This is also important to prove that semantically equivalent \emph{specific constraints} and corresponding \emph{generic constraints}
+This is also important in order to prove that semantically equivalent \emph{specific constraints} and corresponding \emph{generic constraints}
 behave in the same way w.r.t. validation results which semantically underpins bidirectional mappings.

### 2015-07-07 paper/paper 2/dc-2015.tex
section 2.2

@@
 A \emph{constraint language} is a language which is used to formulate constraints.
-The \emph{W3C} working group defines \emph{RDF constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
+The W3C working group defines \emph{RDF constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
 As there are already five promising constraint languages, 
-our purpose was not to invent a new language.
+our purpose is not to invent a new language.
 As there is no high-level declarative language which meets all RDF validation requirements,
@@
 %(4) \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}.
+
 \textbf{\emph{Universality}:}
@@
 we show that constraints of any constraint type can be described generically.
+
 \textbf{\emph{DL Expressivity}:}
 The \emph{RDF-CV} allows to describe 
-constraints which are \emph{expressible in DL} (constraints of this set are instantiated from 64\% of the overall 81 constraint types) and which are \emph{not expressible in DL} (36\%). 
+constraints which are either \emph{expressible in DL} (64\%) or which are \emph{not expressible in DL} (36\%).
+Constraints which are expressible in DL are instantiated from 64\% of the overall 81 constraint types.
+On the other hand, constraints which are not expressible in DL are assigned to 36\% of all constraint types.
 %In case a constraint type is \emph{expressible in DL}, we determined which \emph{DL} constructs are needed to express the constraint type.
+
 \textbf{\emph{Complexity}:}
@@
 which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
+
 \textbf{\emph{Context}:}
@@
 %approx. 10\% of \emph{property and class constraints}.
-\emph{Simple constraints} must hold for individuals of their \emph{context classes}.
+\emph{Simple constraints} must hold for individuals of their associated \emph{context classes}.
 As \emph{context classes} of \emph{simple constraints} are reused within \emph{complex constraints},
@@
 %\tb{use RDF-CV / not: expressible in RDF-CV / RDF-CV is a vocabulary, not a language}
+
 Altogether, instances of the most of the constraint types are \emph{simple constraints on properties} which are \emph{expressible in DL}. 

### 2015-07-07 paper/paper 2/dc-2015.tex
section 2.3

@@
 \end{figure}
-A \emph{simple constraint} holds for all individuals of their \emph{context class}.
+A \emph{simple constraint} holds for all individuals of their associated \emph{context class}.
 The \emph{minimum qualified cardinality restriction} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person,}}
@@
 which holds for all individuals of the class \emph{Publication}.
-Table \ref{tab:property-constraint-cardinality-restriction} displays the mapping to the \emph{RDF-CV}.
+Table \ref{tab:property-constraint-cardinality-restriction} displays how the \emph{property constraint} is generically represented using the \emph{RDF-CV}.
 \begin{table}[H]
@@
 
-The \emph{constraining element} indicates the actual type of constraint like \emph{DL} concept and role constructors, (in)equality, and further keywords for constraint types whose constraints cannot be expressed in \emph{DL} (e.g., regular expressions and constraining facets).
+The \emph{constraining element} indicates the actual type of constraint like \emph{DL} concept and role constructors ($\sqsubseteq$, $\equiv$, $\sqcap$, $\sqcup$, $\neg$, $\exists$, $\forall$, $\geq$, $\leq$), (in)equality (=, $\ne$), and further keywords for constraint types whose constraints cannot be expressed in \emph{DL} (e.g., regular expressions and constraining facets).
+We provide a complete list of all constraining elements which can be used to express constraints of any constraint type \cite{BoschNolleAcarEckert2015}.
+
 In some cases, a constraint is only complete when a \emph{constraining value} is stated in addition to the \emph{constraining element}

### 2015-07-07 paper/paper 2/dc-2015.tex
2.3

@@
 The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
-For this reason, we mapped constraint types to \emph{DL} 
-in order to determine which \emph{DL} constructs are needed to express constraint types \cite{BoschNolleAcarEckert2015}.
+For this reason, we mapped constraint types to DL 
+in order to determine which DL constructs are needed to express constraint types \cite{BoschNolleAcarEckert2015}.
 
@@
 %In some models it is \emph{The-Adventures-of-Huckleberry-Finn}, in others it is \emph{Die-Abenteuer-des-Huckleberry-Finn}. 
-%And since in every model there is only one, \emph{DL} sentences are satisfied. 
+%And since in every model there is only one, DL sentences are satisfied. 
 %But this does not correspond to the intended constraint which is usual in CWA way.   
@@
 %We defined the \textbf{formal generic semantics of the vocabulary} to describe constraints of any constraint type in a generic way (see paper appendix):
-%(1) We mapped constraint types to \emph{DL} to logically underpin them and 
+%(1) We mapped constraint types to DL to logically underpin them and 
 %(2) we described the constraint types' intended behavior in terms of validation results depending on CWA and UNA.
 %To be able to define mappings between \emph{specific constraints} (expressed by different languages) and \emph{generic constraints},
-%we show for each constraint type that a constraint expressed by a particular language leads to the same answer as the corresponding \emph{DL} query.
+%we show for each constraint type that a constraint expressed by a particular language leads to the same answer as the corresponding DL query.
 %To be able to specify transformations between \emph{specific constraints} (expressed by different languages),
@@
 On the other hand, constraints which are not expressible in DL are assigned to 36\% of all constraint types.
-%In case a constraint type is \emph{expressible in DL}, we determined which \emph{DL} constructs are needed to express the constraint type.
+%In case a constraint type is \emph{expressible in DL}, we determined which DL constructs are needed to express the constraint type.
 
@@
 %and which are instances of 1/4 of the constraint types.
-%In case \emph{complex constraints} are expressible in \emph{DL}, 
-%\emph{DL} statements representing \emph{complex constraints} contain \emph{DL} statements standing for atomic and/or composed constraints. 
+%In case \emph{complex constraints} are expressible in DL, 
+%DL statements representing \emph{complex constraints} contain DL statements standing for atomic and/or composed constraints. 
 Constraints of almost 14\% of the constraint types are \emph{complex constraints}
@@
 Altogether, instances of the most of the constraint types are \emph{simple constraints on properties} which are \emph{expressible in DL}. 
-%Thus, the majority of constraint types are directly and relatively easy formulated in form of \emph{simple constraints} which can be mapped to equivalent \emph{DL} constructs.
+%Thus, the majority of constraint types are directly and relatively easy formulated in form of \emph{simple constraints} which can be mapped to equivalent DL constructs.
 
@@
 
-The \emph{constraining element} indicates the actual type of constraint like \emph{DL} concept and role constructors ($\sqsubseteq$, $\equiv$, $\sqcap$, $\sqcup$, $\neg$, $\exists$, $\forall$, $\geq$, $\leq$), (in)equality (=, $\ne$), and further keywords for constraint types whose constraints cannot be expressed in \emph{DL} (e.g., regular expressions and constraining facets).
+%The \emph{constraining element} indicates the actual type of constraint like DL concept and role constructors ($\sqsubseteq$, $\equiv$, $\sqcap$, $\sqcup$, $\neg$, $\exists$, $\forall$, $\geq$, $\leq$), (in)equality (=, $\ne$), and further keywords for constraint types whose constraints cannot be expressed in DL (e.g., regular expressions and constraining facets).
+
+The \emph{constraining element} is an intuitive term which indicates the actual type of constraint.
+For the majority of the constraint types, there is exactly one constraining element.
+For the constraint type \emph{property domain (R-25, R-26)} which restricts the domain of properties, e.g., there is only one constraining element with exactly the same identifier \emph{property domain}.
+For a few constraint types, however, one constraining element is not sufficient to describe all possible constraints of a particular constraint type and therefore multiple constraining elements may be stated for these constraint types.
+The constraint type \emph{language tag cardinality (R-48, R-49)}, for instance, is used to restrict given data properties to have a minimum, maximum, or exact number of relationships to literals with certain language tags.
+Thus, three constraining elements are needed in order to be able to express each possible constraint of that comstraint type.
+
+If constraint types are expressible in DL, associated constraining elements are formally based on DL constructs like DL concept and role constructors ($\sqsubseteq$, $\equiv$, $\sqcap$, $\sqcup$, $\neg$, $\exists$, $\forall$, $\geq$, $\leq$) and (in)equality (=, $\ne$).
+In case, constraint types cannot be expressed in DL such as \emph{data property facets (R-46)} or \emph{literal pattern matching (R-44)}, we reuse widely used terms from SPARQL and the DCMI Metadata Terms like \emph{regex} and \emph{xsd:pattern}.
+For some constraint types like \emph{cardinality restrictions}, it is more intuitive to reuse the DL terms $\geq$ and $\leq$ as constraining elements instead of, for instance, \emph{minimum qualified cardinality restriction}.
 We provide a complete list of all constraining elements which can be used to express constraints of any constraint type \cite{BoschNolleAcarEckert2015}.
@@
 The \emph{constraining element} of the \emph{property constraint} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person},} e.g.,  is the \emph{DL at-least restriction} \emph{$\geq$}, the \emph{constraining value} is \emph{1}, and
-the list of \emph{classes} includes \emph{Person} which restricts the objects of the property \emph{author} to be of the class \emph{Person}.
+the list of \emph{classes} includes the class \emph{Person} which restricts the objects of the property \emph{author} to be persons.
+
 For \emph{property constraints}, \emph{left} and \emph{right property lists} are specified.
 The assignment of properties to these lists happens relative to the \emph{constraining element} 
-which may be an operator like $\sqsubseteq$.
+which may be a DL operator like $\sqsubseteq$.
 \emph{Object Property Paths} (\emph{R-55})
@@
 then \emph{x} is also related to \emph{y} by a particular object property. 
-As \emph{Stephen-Hawking} is the \emph{author} of the book \emph{A-Brief-History-Of-Time} 
+As \emph{Stephen-Hawking} is the author of the book \emph{A-Brief-History-Of-Time} 
 %{\small\ms{(authorOf(Stephen-Hawking, A-Brief-History-Of-Time))}} 
-whose \emph{genre} is \emph{Popular-Science}, 
+whose genre is \emph{Popular-Science}, 
 %{\small\ms{(genre(A-Brief-History-Of-Time, Popular-Science)),}}
-the \emph{object property path} {\small\ms{authorOf $\circ$ genre $\sqsubseteq$ authorOfGenre}} infers that \emph{Stephen-Hawking} is an \emph{author} of the \emph{genre} \emph{Popular-Science}. 
+the object property path {\small\ms{authorOf $\circ$ genre $\sqsubseteq$ authorOfGenre}} infers that \emph{Stephen-Hawking} is an author of the genre \emph{Popular-Science}. 
 %{\small\ms{(authorOfGenre(Stephen-Hawking, Popular-Science))}.}
-Thus, when mapped to the \emph{RDF-CV} (Table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are placed on the left side of the \emph{constraining element} \emph{$\sqsubseteq$}
-and the property \emph{authorOfGenre} on the right side.
-As this \emph{property constraint} holds for all individuals within the data, the \emph{context class} is the \emph{DL top concept} $\top$ which stands for the super-class of all classes.
+Thus, when representing the \emph{property constraint} using the \emph{RDF-CV} (see Table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are placed on the left side of the \emph{constraining element} \emph{$\sqsubseteq$}
+and the property \emph{authorOfGenre} on its right side.
+As this \emph{property constraint} holds for all individuals within the data, the \emph{context class} is set to the \emph{DL top concept} $\top$ which stands for the super-class of all classes.
 \begin{table}[H]
@@
 
-There are \emph{simple constraints} which are not expressible in \emph{DL} but can still be described using the \emph{RDF-CV} 
+There are \emph{simple constraints} which are not expressible in DL but can still be described using the \emph{RDF-CV} 
 such as constraints of the type \emph{literal pattern matching} (\emph{R-44}) which restrict literals to match given patterns.
@@
 i.e., strings that match a given regular expression.
-%Even though, the restriction of the datatype \emph{ISBN} cannot be expressed in \emph{DL}, \emph{OWL 2 DL} can be used to express the \emph{literal pattern matching} constraint:
+%Even though, the restriction of the datatype \emph{ISBN} cannot be expressed in DL, \emph{OWL 2 DL} can be used to express the \emph{literal pattern matching} constraint:
 %\begin{ex}
@@
 Table \ref{tab:simple-constraint-not-expressible-in-dl)} presents 
-how the \emph{literal pattern matching} \emph{simple constraint} which is not expressible in \emph{DL} and 
-how the \emph{universal restriction} \emph{complex constraint} which is expressible in \emph{DL} are mapped to the \emph{RDF-CV}.
+(1) how the \emph{literal pattern matching} \emph{simple constraint} which is not expressible in DL and 
+(2) how the \emph{universal restriction} \emph{complex constraint} which is expressible in DL are represented using the \emph{RDF-CV}.
 Thereby, the \emph{context class} \emph{ISBN}, whose instances must satisfy the \emph{simple constraint}, 
@@
 whose validation has to be implemented once like for any other \emph{constraining element}.
-%In general, validation has to be implemented once for each \emph{generic constraint type} which is not expressible in \emph{DL}. 
+%In general, validation has to be implemented once for each \emph{generic constraint type} which is not expressible in DL. 
 %\begin{gcotable}
@@
 \emph{The-Great-Gatsby} is considered as a valid \emph{publication}.
-The \emph{complex constraint} is generically expressible by \emph{DL}:
-%This \emph{complex constraint} is expressible specifically by \emph{ShEx} and generically by \emph{DL} (and can therefore be mapped to the \emph{RDF-CV} \cite{BoschEckert2015-2}).
+The \emph{complex constraint} is generically expressible by DL:
+%This \emph{complex constraint} is expressible specifically by \emph{ShEx} and generically by DL (and can therefore be mapped to the \emph{RDF-CV} \cite{BoschEckert2015-2}).
 
@@
 %\end{DL}
-%The \emph{complex constraint} is mapped to the \emph{RDF-CV} (see Table \ref{tab:complex-constraints}) and expressed in \emph{DL} as follows:
+%The \emph{complex constraint} is mapped to the \emph{RDF-CV} (see Table \ref{tab:complex-constraints}) and expressed in DL as follows:
 
@@
 %Even though, tools may generate \emph{generic constraints} automatically, this 
-The \emph{DL} statements demonstrate that the \emph{complex constraint} 
+The DL statements demonstrate that the \emph{complex constraint} 
 is composed of many other \emph{complex} (e.g. \emph{minimum and maximum qualified cardinality restrictions}) and \emph{simple constraints} (e.g. constraints on sets).
@@
 %\emph{OWL} provides a variety of other axiom types: \emph{role transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity}. 
-%These axiom types are sometimes considered as basic axiom types in \emph{DL} - using some suggestive notation such as
+%These axiom types are sometimes considered as basic axiom types in DL - using some suggestive notation such as
 %\ms{Trans(ancestorOf)} to express that the role \emph{ancestorOf} is transitive.
 %Such axioms, however, are just syntactic sugar - 
-%all role characteristics can be expressed using the basic features of \emph{DL}.
+%all role characteristics can be expressed using the basic features of DL.
 %
@@
 For these generalization purposes, as there are different sorts of keys, and as keys can lead to undecidability, 
-\emph{DL} is extended with a special construct \emph{keyfor} \cite{Lutz2005}.
+DL is extended with a special construct \emph{keyfor} \cite{Lutz2005}.
 When using \emph{keyfor} (\ms{isbn keyfor Book}), 
@@
 
-\emph{Complex constraints} of frequently used constraint types corresponding to \emph{DL} axioms like 
+\emph{Complex constraints} of frequently used constraint types corresponding to DL axioms like 
 \emph{transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity}
 can also be simplified in the same way, 
-as, although, such axioms can be expressed using basic \emph{DL} features, 
-\emph{DL} axioms like \emph{transitivity} can also be used in terms of syntactic sugar \cite{BoschEckert2015-2}.
+as, although, such axioms can be expressed using basic DL features, 
+DL axioms like \emph{transitivity} can also be used in terms of syntactic sugar \cite{BoschEckert2015-2}.
 %Starfleet officers, e.g., are uniquely identified by their command authorization code (e.g. to activate and cancel auto-destruct sequences).
@@
 %or generically (\emph{generic constraints}) by \emph{description logics (DL)},
-%we mapped constraint types to \emph{DL} 
-%to determine which \emph{DL} constructs are needed to express them \cite{BoschNolleAcarEckert2015} (Section \ref{sec:vocabulary}).
+%we mapped constraint types to DL 
+%to determine which DL constructs are needed to express them \cite{BoschNolleAcarEckert2015} (Section \ref{sec:vocabulary}).
 

### 2015-07-07 paper/paper 2/dc-2015.tex
2.3

@@
 For the majority of the constraint types, there is exactly one constraining element.
-For the constraint type \emph{property domain (R-25, R-26)} which restricts the domain of properties, e.g., there is only one constraining element with exactly the same identifier \emph{property domain}.
-For a few constraint types, however, one constraining element is not sufficient to describe all possible constraints of a particular constraint type and therefore multiple constraining elements may be stated for these constraint types.
-The constraint type \emph{language tag cardinality (R-48, R-49)}, for instance, is used to restrict given data properties to have a minimum, maximum, or exact number of relationships to literals with certain language tags.
-Thus, three constraining elements are needed in order to be able to express each possible constraint of that comstraint type.
-
-If constraint types are expressible in DL, associated constraining elements are formally based on DL constructs like DL concept and role constructors ($\sqsubseteq$, $\equiv$, $\sqcap$, $\sqcup$, $\neg$, $\exists$, $\forall$, $\geq$, $\leq$) and (in)equality (=, $\ne$).
-In case, constraint types cannot be expressed in DL such as \emph{data property facets (R-46)} or \emph{literal pattern matching (R-44)}, we reuse widely used terms from SPARQL and the DCMI Metadata Terms like \emph{regex} and \emph{xsd:pattern}.
+For the constraint type \emph{property domain (R-25, R-26)} whose constraints restrict domains of properties, e.g., there is only one constraining element with exactly the same identifier \emph{property domain}.
+For a few constraint types, however, one constraining element is not sufficient to describe all possible constraints of a particular constraint type and therefore multiple constraining elements may be stated.
+The constraint type \emph{language tag cardinality (R-48, R-49)}, for instance, is used to restrict data properties to have a minimum, maximum, or exact number of relationships to literals with selected language tags.
+Thus, three constraining elements are needed to express each possible constraint of that constraint type.
+
+If constraint types are expressible in DL, associated constraining elements are formally based on DL constructs like concept and role constructors ($\sqsubseteq$, $\equiv$, $\sqcap$, $\sqcup$, $\neg$, $\exists$, $\forall$, $\geq$, $\leq$), equality (=), and inequality ($\ne$).
+In case constraint types cannot be expressed in DL such as \emph{data property facets (R-46)} or \emph{literal pattern matching (R-44)}, we reuse terms from SPARQL (e.g., \emph{regex}) and XML Schema constraining facets (e.g., \emph{minInclusive}).
 For some constraint types like \emph{cardinality restrictions}, it is more intuitive to reuse the DL terms $\geq$ and $\leq$ as constraining elements instead of, for instance, \emph{minimum qualified cardinality restriction}.

### 2015-07-07 paper/paper 2/dc-2015.tex
2.3

@@
 If constraint types are expressible in DL, associated constraining elements are formally based on DL constructs like concept and role constructors ($\sqsubseteq$, $\equiv$, $\sqcap$, $\sqcup$, $\neg$, $\exists$, $\forall$, $\geq$, $\leq$), equality (=), and inequality ($\ne$).
-In case constraint types cannot be expressed in DL such as \emph{data property facets (R-46)} or \emph{literal pattern matching (R-44)}, we reuse terms from SPARQL (e.g., \emph{regex}) and XML Schema constraining facets (e.g., \emph{minInclusive}).
-For some constraint types like \emph{cardinality restrictions}, it is more intuitive to reuse the DL terms $\geq$ and $\leq$ as constraining elements instead of, for instance, \emph{minimum qualified cardinality restriction}.
+In case constraint types cannot be expressed in DL such as \emph{data property facets (R-46)} or \emph{literal pattern matching (R-44)}, we reuse widely known terms from SPARQL (e.g., \emph{regex}) or XML Schema (e.g., \emph{minInclusive}) as constraining elements.
+For some constraint types like \emph{minimum qualified cardinality restrictions (R-75)}, it is more intuitive and concise to directly apply DL constructs like the \emph{at-least restriction} ($\geq$) as constraining elements.
 We provide a complete list of all constraining elements which can be used to express constraints of any constraint type \cite{BoschNolleAcarEckert2015}.

### 2015-07-07 paper/paper 2/dc-2015.tex
2.3

@@
 \end{figure}
-A \emph{simple constraint} holds for all individuals of their associated \emph{context class}.
-The \emph{minimum qualified cardinality restriction} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person,}}
-which restricts \emph{publications} to have at least one \emph{author} which must be a \emph{person},
-is an example of a \emph{property constraint} on \emph{author}
+A simple constraint holds for all individuals of their associated \emph{context class}.
+The \emph{minimum qualified cardinality restriction (R-75)} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person,}}
+which restricts publications to have at least one author which must be a person,
+is an example of a property constraint on \emph{author}
 which holds for all individuals of the class \emph{Publication}.
-Table \ref{tab:property-constraint-cardinality-restriction} displays how the \emph{property constraint} is generically represented using the \emph{RDF-CV}.
+Table \ref{tab:property-constraint-cardinality-restriction} displays how the property constraint is generically represented using the RDF-CV.
 \begin{table}[H]
@@
 
-In some cases, a constraint is only complete when a \emph{constraining value} is stated in addition to the \emph{constraining element}
-and \emph{simple constraints} may refer to a list of \emph{classes}.
-The \emph{constraining element} of the \emph{property constraint} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person},} e.g.,  is the \emph{DL at-least restriction} \emph{$\geq$}, the \emph{constraining value} is \emph{1}, and
-the list of \emph{classes} includes the class \emph{Person} which restricts the objects of the property \emph{author} to be persons.
-
-For \emph{property constraints}, \emph{left} and \emph{right property lists} are specified.
-The assignment of properties to these lists happens relative to the \emph{constraining element} 
-which may be a DL operator like $\sqsubseteq$.
+In some cases, a constraint is only complete when a \emph{constraining value} is stated in addition to the constraining element
+and simple constraints may refer to a list of \emph{classes}.
+The constraining element of the property constraint {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person},} e.g., is \emph{$\geq$}, the constraining value is \emph{1}, and the list of classes includes the class \emph{Person} which restricts the objects of the property \emph{author} to be persons.
+
+For property constraints, \emph{left} and \emph{right property lists} are specified.
+The assignment of properties to these lists happens relative to the constraining element.
 \emph{Object Property Paths} (\emph{R-55})
@@
 %{\small\ms{(authorOfGenre(Stephen-Hawking, Popular-Science))}.}
-Thus, when representing the \emph{property constraint} using the \emph{RDF-CV} (see Table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are placed on the left side of the \emph{constraining element} \emph{$\sqsubseteq$}
+Thus, when representing the property constraint using the RDF-CV (see Table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are placed on the left side of the constraining element \emph{property paths}
 and the property \emph{authorOfGenre} on its right side.
-As this \emph{property constraint} holds for all individuals within the data, the \emph{context class} is set to the \emph{DL top concept} $\top$ which stands for the super-class of all classes.
+As this property constraint holds for all individuals within the data, the context class is set to the \emph{DL top concept} $\top$ which stands for the super-class of all possible classes.
 \begin{table}[H]
@@
       \hline
-      property & $\top$ & authorOf, genre & authorOfGenre & $\top$ & $\sqsubseteq$ & - \\
+      property & $\top$ & authorOf, genre & authorOfGenre & $\top$ & property paths & - \\
 		\end{tabular}
@@
 
-There are \emph{simple constraints} which are not expressible in DL but can still be described using the \emph{RDF-CV} 
-such as constraints of the type \emph{literal pattern matching} (\emph{R-44}) which restrict literals to match given patterns.
-The \emph{universal restriction} {\small\ms{Book $\sqsubseteq$ $\forall$ identifier.ISBN}} ensures that \emph{books} can only have valid \emph{ISBN} identifiers, 
-i.e., strings that match a given regular expression.
+There are simple constraints which are not expressible in DL but can still be described using the RDF-CV such as constraints of the type \emph{literal pattern matching} (\emph{R-44}) which restrict literals to match given patterns.
+The \emph{universal quantification (R-91)} {\small\ms{Book $\sqsubseteq$ $\forall$ identifier.ISBN}} ensures that \emph{books} can only have valid \emph{ISBN} identifiers, i.e., strings that match a given regular expression.
 %Even though, the restriction of the datatype \emph{ISBN} cannot be expressed in DL, \emph{OWL 2 DL} can be used to express the \emph{literal pattern matching} constraint:
@@
 %but not for the triples \ms{Picard commandsEnterprise Enterprise} and \ms{Enterprise registryNumber "NCC-1701-E"\textasciicircum{}\textasciicircum{}RegistryNumber}.
-Table \ref{tab:simple-constraint-not-expressible-in-dl)} presents 
-(1) how the \emph{literal pattern matching} \emph{simple constraint} which is not expressible in DL and 
-(2) how the \emph{universal restriction} \emph{complex constraint} which is expressible in DL are represented using the \emph{RDF-CV}.
-Thereby, the \emph{context class} \emph{ISBN}, whose instances must satisfy the \emph{simple constraint}, 
-is reused within the list of \emph{classes} the \emph{complex constraint} refers to.
-The \emph{literal pattern matching} constraint type introduces the \emph{constraining element} \emph{regex}
-whose validation has to be implemented once like for any other \emph{constraining element}.
+Table \ref{tab:simple-constraint-not-expressible-in-dl)} presents (1) in the first line how the literal pattern matching simple constraint which is not expressible in DL and (2) in the second line how the universal quantification complex constraint which is expressible in DL are represented using the RDF-CV.
+Thereby, the context class \emph{ISBN}, whose instances must satisfy the simple constraint, is reused within the list of classes the complex constraint refers to.
+The literal pattern matching constraint type introduces the constraining element \emph{regex} whose validation has to be implemented once like for any other constraining element.
 %In general, validation has to be implemented once for each \emph{generic constraint type} which is not expressible in DL. 
@@
       class & ISBN & - & - & xsd:string & regex & '\string^\text{$\backslash$d$\{9\}$[$\backslash$d$\mid$X]}\$' \\
-      property & Book & identifier & - & ISBN & $\forall$ & - \\
+      property & Book & identifier & - & ISBN & universal quantification & - \\
 		\end{tabular}
@@
 class & Publication & - & - & E, F & XOR \\
-class & E & - & - & A, B & $\sqcap$ \\
-class & F & - & - & C, D & $\sqcap$ \\
+class & E & - & - & A, B & intersection \\
+class & F & - & - & C, D & intersection \\
 property & A & isbn & - & string & = & 1 \\
@@
       \hline
-property & $\top$ & isbn$^{-}$ & isbn$^{-}$ & - & inverse & - \\
-property & Book & isbn$^{-}$ & - & - & functional & - \\
+property & $\top$ & isbn$^{-}$ & isbn$^{-}$ & - & inverse property & - \\
+property & Book & isbn$^{-}$ & - & - & functional property & - \\
 		\end{tabular}

### 2015-07-07 paper/paper 2/dc-2015.tex
2.3

@@
   \vspace{0cm}
-	\caption{Simple Constraints which are not Expressible in DL)}
+	\caption{Simple Constraints which are not Expressible in DL}
 	\label{tab:simple-constraint-not-expressible-in-dl)}
@@
 %\emph{Complex constraints} are composed out of \emph{simple constraints} and/or \emph{complex constraints}.
-\emph{Complex constraints} of the constraint type \emph{context-specific exclusive or of property groups} (\emph{R-13}) 
-restrict individuals of given classes to have all properties of exactly one of multiple mutually exclusive property groups.
-\emph{Publications}, e.g., are either identified by an \emph{ISBN} and a title (for books) or by an \emph{ISSN} and a title (for periodical \emph{publications}), but it should not be possible to assign both identifiers to a given \emph{publication}.
-As \emph{The-Great-Gatsby} is a \emph{publication} with an \emph{ISBN} and a title without an \emph{ISSN}, 
-\emph{The-Great-Gatsby} is considered as a valid \emph{publication}.
-The \emph{complex constraint} is generically expressible by DL:
+Complex constraints of the constraint type \emph{context-specific exclusive or of property groups} (\emph{R-13}) restrict individuals of given classes to have all properties of exactly one of multiple mutually exclusive property groups.
+Publications, e.g., are either identified by an \emph{ISBN} and a title (for books) or by an \emph{ISSN} and a title (for periodical publications), but it should not be possible to assign both identifiers to a given publication.
+As \emph{The-Great-Gatsby} is a publication with an \emph{ISBN} and a title without an \emph{ISSN}, \emph{The-Great-Gatsby} is considered as a valid publication.
+This complex constraint is generically expressible in DL:
 %This \emph{complex constraint} is expressible specifically by \emph{ShEx} and generically by DL (and can therefore be mapped to the \emph{RDF-CV} \cite{BoschEckert2015-2}).
@@
 %Even though, tools may generate \emph{generic constraints} automatically, this 
-The DL statements demonstrate that the \emph{complex constraint} 
-is composed of many other \emph{complex} (e.g. \emph{minimum and maximum qualified cardinality restrictions}) and \emph{simple constraints} (e.g. constraints on sets).
-As \emph{exact (un)qualified cardinality restrictions (=n)} and \emph{exclusive or (XOR)} are frequently used \emph{complex constraints},
-we propose to simplify them as \emph{simple constraints} in terms of syntactic sugar.
-As a consequence, the \emph{context-specific exclusive or of property groups} \emph{complex constraint} is represented as a \emph{generic constraint} by means of the \emph{RDF-CV} more intuitively and concisely (Table \ref{tab:simplified-complex-constraints}).
+The DL statements demonstrate that the complex constraint is composed of many other complex constraints (e.g., \emph{minimum and maximum qualified cardinality restrictions}) and simple constraints (e.g., constraints on sets).
+As \emph{exact (un)qualified cardinality restrictions (=n)} and \emph{exclusive or (XOR)} are frequently used complex constraints, we propose to simplify them as simple constraints in terms of syntactic sugar.
+As a consequence, the \emph{context-specific exclusive or of property groups} complex constraint is represented as a generic constraint by means of the RDF-CV more intuitively and concisely (see Table \ref{tab:simplified-complex-constraints}).
 
@@
       \hline
-class & Publication & - & - & E, F & XOR \\
-class & E & - & - & A, B & intersection \\
-class & F & - & - & C, D & intersection \\
+class & Publication & - & - & E, F & XOR of property groups & - \\
+class & E & - & - & A, B & intersection & - \\
+class & F & - & - & C, D & intersection & - \\
 property & A & isbn & - & string & = & 1 \\

### 2015-07-07 paper/paper 2/dc-2015.tex
2.3

@@
 %\end{table}
-The \emph{primary key properties} constraint type (\emph{R-226}) is often useful to declare a given (datatype) property as the primary key of a class, so that a system can enforce uniqueness. 
-\emph{Books}, e.g., are uniquely identified by their \emph{ISBN}, i.e., the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}
-which can be represented using the \emph{RDF-CV} in form of a \emph{complex constraint} consisting of two \emph{simple constraints} (Table \ref{tab:primary-key-properties-as-complex-constraints}).
+The \emph{primary key properties (R-226)} constraint type is often useful to declare a given (datatype) property as the primary key of a class, so that a system can enforce uniqueness. 
+Books, e.g., are uniquely identified by their \emph{ISBN}, i.e., the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}
+which can be represented using the RDF-CV in form of a complex constraint consisting of two simple constraints (see Table \ref{tab:primary-key-properties-as-complex-constraints}).
 
@@
 
-\emph{Keys}, however, are even more general, i.e., a generalization of \emph{inverse functional properties} \cite{Schneider2009}.
+Keys, however, are even more general, i.e., a generalization of inverse functional properties \cite{Schneider2009}.
 A key can be a datatype, an object property, or a chain of properties.
@@
 DL is extended with a special construct \emph{keyfor} \cite{Lutz2005}.
-When using \emph{keyfor} (\ms{isbn keyfor Book}), 
-the \emph{complex constraint} can be formulated as a \emph{simple constraint} which looks like the following in concrete RDF turtle syntax:
+When using keyfor (\ms{isbn keyfor Book}), 
+the complex constraint can be formulated as a simple constraint which looks like the following in concrete RDF turtle syntax:
 
@@
 
-\emph{Complex constraints} of frequently used constraint types corresponding to DL axioms like 
-\emph{transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity}
-can also be simplified in the same way, 
-as, although, such axioms can be expressed using basic DL features, 
-DL axioms like \emph{transitivity} can also be used in terms of syntactic sugar \cite{BoschEckert2015-2}.
+Complex constraints of frequently used constraint types which correspond to DL axioms like \emph{transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity} can also be simplified in form of simple constraints.
+Although, these DL axioms are expressible by basic DL features, they can also be used in terms of syntactic sugar \cite{BoschEckert2015-2}.
 %Starfleet officers, e.g., are uniquely identified by their command authorization code (e.g. to activate and cancel auto-destruct sequences).

### 2015-07-08 paper/paper 2/dc-2015.tex
2.3

@@
 There are simple constraints which are not expressible in DL but can still be described using the RDF-CV such as constraints of the type \emph{literal pattern matching} (\emph{R-44}) which restrict literals to match given patterns.
-The \emph{universal quantification (R-91)} {\small\ms{Book $\sqsubseteq$ $\forall$ identifier.ISBN}} ensures that \emph{books} can only have valid \emph{ISBN} identifiers, i.e., strings that match a given regular expression.
+The \emph{universal quantification (R-91)} {\small\ms{Book $\sqsubseteq$ $\forall$ identifier.ISBN}} ensures that books can only have valid \emph{ISBN} identifiers, i.e., strings that match a given regular expression.
 %Even though, the restriction of the datatype \emph{ISBN} cannot be expressed in DL, \emph{OWL 2 DL} can be used to express the \emph{literal pattern matching} constraint:
@@
 %but not for the triples \ms{Picard commandsEnterprise Enterprise} and \ms{Enterprise registryNumber "NCC-1701-E"\textasciicircum{}\textasciicircum{}RegistryNumber}.
+
+Even though, constraints of the type \emph{literal pattern matching} cannot be expressed in DL, OWL 2 can be used to formulate the constraint:
+
+\begin{ex}
+ISBN a RDFS:Datatype ; owl:equivalentClass [ a RDFS:Datatype ;
+    owl:onDatatype xsd:string ; 
+    owl:withRestrictions ([ xsd:pattern "^\d{9}[\d|X]$" ])] .
+\end{ex}\$$
+
+The first OWL 2 axiom explicitly declares {\em ISBN} to be a datatype.
+%\er{Why start from second and then first?
+Also better we say "owl axiom" when we talk axiom of owl, to prevent ambiguity.}\tb{resolved}
+The second OWL 2 axiom defines {\em ISBN} as an abbreviation for a datatype restriction on \emph{xsd:string}. 
+The datatype {\em ISBN} can be used just like any other datatype like in the universal quantification above.
+
 Table \ref{tab:simple-constraint-not-expressible-in-dl)} presents (1) in the first line how the literal pattern matching simple constraint which is not expressible in DL and (2) in the second line how the universal quantification complex constraint which is expressible in DL are represented using the RDF-CV.

### 2015-07-08 paper/paper 2/dc-2015.tex
2.4

@@
 %DL statements representing \emph{complex constraints} contain DL statements standing for atomic and/or composed constraints. 
-Constraints of almost 14\% of the constraint types are \emph{complex constraints}
-which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
+Constraints of almost 14\% of the constraint types are \emph{complex constraints} which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
 
@@
 Publications, e.g., are either identified by an \emph{ISBN} and a title (for books) or by an \emph{ISSN} and a title (for periodical publications), but it should not be possible to assign both identifiers to a given publication.
+This complex constraint is expressible in \emph{ShEx}:
+
+\begin{ex}
+Publication { 
+    ( isbn string , title string ) |
+    ( issn string , title string ) }
+\end{ex}
+
 As \emph{The-Great-Gatsby} is a publication with an \emph{ISBN} and a title without an \emph{ISSN}, \emph{The-Great-Gatsby} is considered as a valid publication.
@@
 %Even though, tools may generate \emph{generic constraints} automatically, this 
-The DL statements demonstrate that the complex constraint is composed of many other complex constraints (e.g., \emph{minimum and maximum qualified cardinality restrictions}) and simple constraints (e.g., constraints on sets).
-As \emph{exact (un)qualified cardinality restrictions (=n)} and \emph{exclusive or (XOR)} are frequently used complex constraints, we propose to simplify them as simple constraints in terms of syntactic sugar.
-As a consequence, the \emph{context-specific exclusive or of property groups} complex constraint is represented as a generic constraint by means of the RDF-CV more intuitively and concisely (see Table \ref{tab:simplified-complex-constraints}).
+The DL statements demonstrate that the complex constraint is composed of many other complex constraints (\emph{minimum (R-75) and maximum qualified cardinality restrictions (R-76)}) and simple constraints (\emph{intersection (R-15/16)}, \emph{disjunction (R-17/18)}, and \emph{negation (R-19/20)}).
+Constraints of almost 14\% of the constraint types are complex constraints which can be simplified and therefore formulated as simple constraints when using them in terms of syntactic sugar.
+As \emph{exact (un)qualified cardinality restrictions (=n)} and \emph{exclusive or (XOR) of property groups} are frequently used complex constraints, we propose to simplify them in form of simple constraints.
+As a consequence, the \emph{context-specific exclusive or of property groups (R-13)} complex constraint is represented as a generic constraint by means of the RDF-CV more intuitively and concisely (see Table \ref{tab:simplified-complex-constraints}).
 
@@
 When using keyfor (\ms{isbn keyfor Book}), 
-the complex constraint can be formulated as a simple constraint which looks like the following in concrete RDF turtle syntax:
+the complex constraint can be simplified and thus formulated as a simple constraint which looks like the following in concrete RDF turtle syntax:
 
@@
 Although, these DL axioms are expressible by basic DL features, they can also be used in terms of syntactic sugar \cite{BoschEckert2015-2}.
+
+Constraints of the \emph{irreflexive object properties (R-60)} constraint type ensure that no individual is connected by a given object property to itself \cite{Kroetzsch2012}.
+With the irreflexive object property constraint {\small\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists authorOf.Self$}}, e.g., one can state that individuals cannot be authors of themselves.
+When represented using the RDF-CV, the complex constraint aggregates three simple constraints - one property and two class constraints (see Table \ref{tab:irreflexive-object-properties-as-complex-constraints}).
+
+%\begin{gcotable}
+%property & $\exists$ marriedTo . Self & marriedTo & - & Self & $\exists$ & - \\
+%class & $\neg$ $\exists$ marriedTo . Self & - & - & $\exists$ marriedTo . Self & $\neg$ & - \\
+%class & $\top$ & - & - & $\top$, $\neg$ $\exists$ marriedTo . Self & $\sqsubseteq$ & - \\
+%\end{gcotable}
+
+\begin{table}[H]
+  \scriptsize
+  \sffamily
+  \vspace{0cm}
+	\caption{Irreflexive Object Properties as Complex Constraints}
+	\label{tab:irreflexive-object-properties-as-complex-constraints}
+	\centering
+		\begin{tabular}{l|l|l|l|l|l|l}
+      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      \hline
+property & $\exists$ authorOf.Self & authorOf & - & Self & existential quantification & - \\
+class & $\neg$ $\exists$ authorOf.Self & - & - & $\exists$ authorOf.Self & negation & - \\
+class & $\top$ & - & - & $\top$, $\neg$ $\exists$ authorOf.Self & sub-class & - \\
+		\end{tabular}
+\end{table}
+
+When using the irreflexive object property constraint in terms of syntactic sugar, 
+the complex constraint can be expressed more concisely in form of a simple property constraint with exactly the same semantics (see Table \ref{tab:irreflexive-object-properties-as-simple-constraints}):
+
+%\begin{gcotable}
+%property & $\top$ & marriedTo & - & - & irreflexive & - \\
+%\end{gcotable}
+
+\begin{table}[H]
+  \scriptsize
+  \sffamily
+  \vspace{0cm}
+	\caption{Irreflexive Object Properties as Simple Constraints}
+	\label{tab:irreflexive-object-properties-as-simple-constraints}
+	\centering
+		\begin{tabular}{l|l|l|l|l|l|l}
+      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      \hline
+property & $\top$ & authorOf & - & - & irreflexive property & - \\
+		\end{tabular}
+\end{table}
+
 %Starfleet officers, e.g., are uniquely identified by their command authorization code (e.g. to activate and cancel auto-destruct sequences).

### 2015-07-08 paper/paper 2/dc-2015.tex
related work

@@
 
-In this section, we present current languages for constraint formulation and RDF data validation\footnote{
+In this section, we present current languages for RDF constraint formulation and RDF data validation\footnote{
 \emph{SPARQL}: \url{http://www.w3.org/TR/sparql11-query}, 
@@
 }.
-\emph{SPIN}, \emph{SPARQL}, OWL 2, \emph{ShEx}, \emph{ReSh}, and \emph{DSP} are the six most promising and applied languages.
-%
-The query language for RDF \emph{SPARQL} is generally seen as the method of choice to validate data according to certain constraints \cite{Fuerber2010}, 
+SPIN, SPARQL, OWL 2, ShEx, ReSh, and DSP are the six most promising and mostly used constraint languages.
+
+The \emph{SPARQL Query Language for RDF} \cite{W3C-SPARQL1.1-Query-Language-2013} is generally seen as the method of choice to validate RDF data according to certain constraints \cite{Fuerber2010}, 
 although, it is not ideal for their formulation. 
 In contrast, high-level constraint languages are comparatively easy to understand and constraints can be formulated more concisely.
-Declarative languages may be placed on top of \emph{SPARQL} and \emph{SPIN} when using them as implementation languages.
-%
-\emph{SPIN} provides a vocabulary to represent \emph{SPARQL} queries as RDF triples
-and uses \emph{SPARQL} to specify logical constraints and inference rules \cite{Fuerber2010}.
-%
+Declarative languages may be placed on top of SPARQL and SPIN when using them as implementation languages.
+%
+The \emph{SPARQL Inferencing Notation (SPIN)} \cite{W3C-SPIN-2011} provides a vocabulary to represent SPARQL queries as RDF triples
+and uses SPARQL to specify logical constraints and inference rules \cite{Fuerber2010}.
+
 \emph{Stardog ICV} and \emph{Pellet ICV} use OWL 2 constructs to formulate constraints.
 The \emph{Pellet Integrity Constraint Validator (ICV)} is a proof-of-concept extension for the \emph{OWL 2 DL} reasoner \emph{Pellet}.
-\emph{Stardog ICV} 
-validates RDF data stored in a Stardog database according to 
-constraints which may be written in \emph{SPARQL}, \emph{OWL}, or \emph{SWRL}. 
-%
+\emph{Stardog ICV} validates RDF data stored in a Stardog database according to constraints which may be written in SPARQL, OWL, or SWRL.
+
 \emph{ShEx} specifies a language whose syntax and semantics are similar to regular expressions.
@@
 which are used to express formal constraints on the content of RDF graphs.
-%
+
 \emph{ReSh} defines its own vocabulary for specifying \emph{shapes} of RDF resources.
 Ryman et al. define \emph{shape} as a description of the set of triples a resource is expected to contain and of the integrity constraints those triples are required to satisfy \cite{Ryman2013}.
-%
+
 \emph{DCMI RDF Application Profiles (AP)} and \emph{Bibframe} are approaches to specify profiles for application-specific purposes. 
@@
 The \emph{Bibliographic Framework Initiative (Bibframe)} defines a vocabulary which has a strong overlap with \emph{DSP}.
-%
+
 Kontokostas et al. define 17 data quality integrity constraints represented as \emph{SPARQL} query templates called \emph{Data Quality Test Patterns (DQTP)} \cite{Kontokostas2014}.
-%
+
 \emph{RDF Schemarama} 
@@
 %\emph{XML Schema} is the primary technology for specifying and constraining the structure of XML documents.
-%
+
 In addition to the formulation of constraints, \emph{SPIN} (open source API), \emph{Stardog ICV} (as part of the \emph{Stardog RDF database}), \emph{DQTP} (tests), \emph{Pellet ICV} (extension of \emph{Pellet OWL 2 DL} reasoner) and \emph{ShEx} offer executable validation systems using \emph{SPARQL} as implementation language.

### 2015-07-08 paper/paper 2/dc-2015.tex
related work

@@
 
-\emph{Stardog ICV} and \emph{Pellet ICV} use OWL 2 constructs to formulate constraints.
-The \emph{Pellet Integrity Constraint Validator (ICV)} is a proof-of-concept extension for the \emph{OWL 2 DL} reasoner \emph{Pellet}.
-\emph{Stardog ICV} validates RDF data stored in a Stardog database according to constraints which may be written in SPARQL, OWL, or SWRL.
-
-\emph{ShEx} specifies a language whose syntax and semantics are similar to regular expressions.
-\emph{ShEx} associate RDF graphs with labeled patterns called \emph{shapes} 
-which are used to express formal constraints on the content of RDF graphs.
-
-\emph{ReSh} defines its own vocabulary for specifying \emph{shapes} of RDF resources.
-Ryman et al. define \emph{shape} as a description of the set of triples a resource is expected to contain and of the integrity constraints those triples are required to satisfy \cite{Ryman2013}.
+\emph{Stardog Integrity Constraint Validation (ICV)} and the \emph{Pellet Integrity Constraint Validator (ICV)} use OWL 2 constructs to formulate constraints.
+The Pellet ICV is a proof-of-concept extension for the OWL 2 DL reasoner \emph{Pellet} \cite{sirin2007pellet}.
+Stardog ICV validates RDF data stored in a Stardog database according to constraints which may be written in SPARQL, OWL 2, or SWRL \cite{Horrocks04}.
+
+\emph{Shape Expressions (ShEx)} \cite{W3C-ShEx-Primer-2014,W3C-ShEx-Definition-2014,Prud'hommeaux-2014,Boneva-2014} specifies a language whose syntax and semantics are similar to regular expressions.
+ShEx associate RDF graphs with labeled patterns called \emph{shapes} which are used to express formal constraints on the content of RDF graphs.
+\emph{Resource Shapes (ReSh)} \cite{W3C-ReSh-2014} defines its own vocabulary for specifying shapes of RDF resources.
+Ryman, Hors, and Speicher define \emph{shape} as a description of the set of triples a resource is expected to contain and as a description of the integrity constraints those triples are required to satisfy \cite{Ryman2013}.
 
@@
 The \emph{Bibliographic Framework Initiative (Bibframe)} defines a vocabulary which has a strong overlap with \emph{DSP}.
-
 Kontokostas et al. define 17 data quality integrity constraints represented as \emph{SPARQL} query templates called \emph{Data Quality Test Patterns (DQTP)} \cite{Kontokostas2014}.
@@
 In addition to the formulation of constraints, \emph{SPIN} (open source API), \emph{Stardog ICV} (as part of the \emph{Stardog RDF database}), \emph{DQTP} (tests), \emph{Pellet ICV} (extension of \emph{Pellet OWL 2 DL} reasoner) and \emph{ShEx} offer executable validation systems using \emph{SPARQL} as implementation language.
+
+\tb{SHACL}
 

### 2015-07-08 paper/paper 2/dc-2015.tex
related work

@@
 Declarative languages may be placed on top of SPARQL and SPIN when using them as implementation languages.
-%
 The \emph{SPARQL Inferencing Notation (SPIN)} \cite{W3C-SPIN-2011} provides a vocabulary to represent SPARQL queries as RDF triples
 and uses SPARQL to specify logical constraints and inference rules \cite{Fuerber2010}.
+Kontokostas et al.
+define 17 data quality integrity constraints represented as SPARQL query templates called \emph{Data Quality Test Patterns (DQTP)} \cite{Kontokostas2014}.
 
@@
 
-\emph{DCMI RDF Application Profiles (AP)} and \emph{Bibframe} are approaches to specify profiles for application-specific purposes. 
-\emph{DCMI RDF-AP} uses \emph{DSP} as generic constraint language which is also intuitive for non-experts.
-The \emph{Bibliographic Framework Initiative (Bibframe)} defines a vocabulary which has a strong overlap with \emph{DSP}.
-Kontokostas et al. define 17 data quality integrity constraints represented as \emph{SPARQL} query templates called \emph{Data Quality Test Patterns (DQTP)} \cite{Kontokostas2014}.
+The \emph{Dublin Core Application Profile (DCAP)} and \emph{Bibframe} are approaches to specify \emph{profiles} for application-specific purposes.
+The term \emph{profile} is widely used to refer to a document that describes how standards or specifications are deployed to support the requirements of a particular application, function, community, or context.
+In the metadata community, the term \emph{application profile} has been applied to describe the tailoring of standards for specific applications.
+A \emph{Dublin Core Application Profile (DCAP)} \cite{DCMI-DCAP-2009} defines metadata records which meet specific application needs while providing semantic interoperability with other applications on the basis of globally defined vocabularies and models.
+The \emph{Singapore Framework for Dublin Core Application Profiles} \cite{DCMI-Singapore-2008} is a framework for designing metadata and for defining DCAPs.
+The framework comprises descriptive components that are necessary or useful for documenting DCAPs.
+
+The \emph{DCMI Abstract Model} \cite{DCMI-Abstract-Model-2007} is required for formalizing a notion of machine-processable application profiles.
+It specifies an abstract model for Dublin Core metadata which is independent of any particular encoding syntax.
+Its primary purpose is to specify the components used in Dublin Core metadata.
+Nilsson et al.
+\cite{DCMI-DC-RDF-2008} depict how the constructs of the DCMI Abstract Model are represented using the abstract syntax of the RDF model.
+A \emph{Description Set Profile (DSP)} \cite{DCMI-DSP-2008} is a generic constraint language which is used to formally specify structural constraints on sets of resource descriptions within an application profile.
+DSP constrains resources that may be described by descriptions in a description set, the properties that may be used, and the values properties may point to.
+The \emph{Bibliographic Framework Initiative (Bibframe)} defines a vocabulary which has a strong overlap with DSP.
 

### 2015-07-08 paper/paper 2/dc-2015.tex
related work

@@
 \emph{DSP}: \url{http://dublincore.org/documents/dc-dsp},
-\emph{RDF Schemarama}: \url{http://swordfish.rdfweb.org/discovery/2001/01/schemarama}
+\emph{RDF Schemarama}: \url{http://www.xml.com/pub/a/2001/02/07/schemarama.html}
 %\emph{Schematron}: \url{http://www.schematron.com},
@@
 DSP constrains resources that may be described by descriptions in a description set, the properties that may be used, and the values properties may point to.
-The \emph{Bibliographic Framework Initiative (Bibframe)} defines a vocabulary which has a strong overlap with DSP.
-
-\emph{RDF Schemarama} 
-is a proof-of-concept demonstrator based on ideas from \emph{Schematron}. 
-It allows to check that RDF data has required properties and
-it is based on \emph{Squish}, an SQL-ish query language for RDF, instead of \emph{SPARQL}. 
+\emph{BIBFRAME} \cite{Kroeger-2013,Godby-2015,Miller-2012} is the result of the \emph{Bibliographic Framework Initiative} and defines a vocabulary \cite{DCMI-Bibframe-Authorities-2014,DCMI-Bibframe-Relationships-2014} which has a strong overlap with DSP.
+\emph{BIBFRAME Profiles} \cite{DCMI-Bibframe-Profiles-2014} are essentially identical to DCAPs.
+
+\emph{Schemarama} is a validation technique for specifying the types of sub-graphs you want to have connected to a particular set of nodes in an RDF Graph.
+Schemarama allows to check that RDF data has required properties.
+Schemarama is based on Schematron \cite{ISO/IEC-2006}, an XML schema and XML structure validation language which works by finding tree patterns within an XML document.
+Schemarama is also based on the \emph{Squish RDF Query language} \cite{Miller-2001}, an SQL-like query language for RDF, instead of SPARQL.
+
 %
@@
 
-In addition to the formulation of constraints, \emph{SPIN} (open source API), \emph{Stardog ICV} (as part of the \emph{Stardog RDF database}), \emph{DQTP} (tests), \emph{Pellet ICV} (extension of \emph{Pellet OWL 2 DL} reasoner) and \emph{ShEx} offer executable validation systems using \emph{SPARQL} as implementation language.
+In addition to the formulation of constraints, SPIN (open source API), Stardog ICV (as part of the Stardog RDF database), DQTP (tests), Pellet ICV (extension of Pellet OWL 2 DL reasoner) and ShEx offer executable validation systems using SPARQL as implementation language.
 

### 2015-07-08 paper/paper 2/dc-2015.tex
related work

@@
 
-In this section, we present current languages for RDF constraint formulation and RDF data validation\footnote{
-\emph{SPARQL}: \url{http://www.w3.org/TR/sparql11-query}, 
-\emph{SPIN}: \url{http://spinrdf.org},
-\emph{Pellet ICV}: \url{http://clarkparsia.com/pellet/icv},
-\emph{Stardog ICV}: \url{http://docs.stardog.com/#_validating_constraints},
-\emph{ShEx}: \url{http://www.w3.org/Submission/shex-defn},
-\emph{ReSh}: \url{http://www.w3.org/Submission/shapes},
-\emph{DCMI RDF-AP}: \url{http://dublincore.org/documents/singapore-framework},
-\emph{Bibframe}: \url{http://bibframe.org},
-\emph{DSP}: \url{http://dublincore.org/documents/dc-dsp},
-\emph{RDF Schemarama}: \url{http://www.xml.com/pub/a/2001/02/07/schemarama.html}
-%\emph{Schematron}: \url{http://www.schematron.com},
-%\emph{XML Schema}: \url{http://www.w3.org/TR/xmlschema-1},
-}.
+In this section, we present current languages for RDF constraint formulation and RDF data validation.
 SPIN, SPARQL, OWL 2, ShEx, ReSh, and DSP are the six most promising and mostly used constraint languages.
@@
 Declarative languages may be placed on top of SPARQL and SPIN when using them as implementation languages.
-The \emph{SPARQL Inferencing Notation (SPIN)} \cite{W3C-SPIN-2011} provides a vocabulary to represent SPARQL queries as RDF triples
+The \emph{SPARQL Inferencing Notation (SPIN)}\footnote{\url{http://spinrdf.org}} \cite{W3C-SPIN-2011} provides a vocabulary to represent SPARQL queries as RDF triples
 and uses SPARQL to specify logical constraints and inference rules \cite{Fuerber2010}.
@@
 \emph{Stardog Integrity Constraint Validation (ICV)} and the \emph{Pellet Integrity Constraint Validator (ICV)} use OWL 2 constructs to formulate constraints.
-The Pellet ICV is a proof-of-concept extension for the OWL 2 DL reasoner \emph{Pellet} \cite{sirin2007pellet}.
-Stardog ICV validates RDF data stored in a Stardog database according to constraints which may be written in SPARQL, OWL 2, or SWRL \cite{Horrocks04}.
+The Pellet ICV\footnote{\url{http://clarkparsia.com/pellet/icv}} is a proof-of-concept extension for the OWL 2 DL reasoner \emph{Pellet} \cite{sirin2007pellet}.
+Stardog ICV\footnote{\url{http://docs.stardog.com/#_validating_constraints}} validates RDF data stored in a Stardog database according to constraints which may be written in SPARQL, OWL 2, or SWRL \cite{Horrocks04}.
 
@@
 DSP constrains resources that may be described by descriptions in a description set, the properties that may be used, and the values properties may point to.
-\emph{BIBFRAME} \cite{Kroeger-2013,Godby-2015,Miller-2012} is the result of the \emph{Bibliographic Framework Initiative} and defines a vocabulary \cite{DCMI-Bibframe-Authorities-2014,DCMI-Bibframe-Relationships-2014} which has a strong overlap with DSP.
+\emph{BIBFRAME}\footnote{\url{http://bibframe.org}} \cite{Kroeger-2013,Godby-2015,Miller-2012} is the result of the \emph{Bibliographic Framework Initiative} and defines a vocabulary \cite{DCMI-Bibframe-Authorities-2014,DCMI-Bibframe-Relationships-2014} which has a strong overlap with DSP.
 \emph{BIBFRAME Profiles} \cite{DCMI-Bibframe-Profiles-2014} are essentially identical to DCAPs.
 
-\emph{Schemarama} is a validation technique for specifying the types of sub-graphs you want to have connected to a particular set of nodes in an RDF Graph.
+\emph{Schemarama}\footnote{\url{http://www.xml.com/pub/a/2001/02/07/schemarama.html}} is a validation technique for specifying the types of sub-graphs you want to have connected to a particular set of nodes in an RDF Graph.
 Schemarama allows to check that RDF data has required properties.
@@
 \tb{SHACL}
+
+\emph{Shapes Constraint Language (SHACL)} \cite{W3C-SHACL-2015,W3C-SHACL-2-2015,W3C-SHACL-3-2015}
 

### 2015-07-09 paper/paper 2/dc-2015.tex
related work

@@
 
-\tb{SHACL}
-
-\emph{Shapes Constraint Language (SHACL)} \cite{W3C-SHACL-2015,W3C-SHACL-2-2015,W3C-SHACL-3-2015}
+The W3C Data Shapes Working Group currently develops \emph{SHACL} \cite{W3C-SHACL-2015,W3C-SHACL-2-2015,W3C-SHACL-3-2015}, the \emph{Shapes Constraint Language}, an RDF vocabulary for describing RDF graph structures.
+Some of these graph structures are captured as \emph{shapes}, which group together constraints about the same RDF nodes.
+Shapes provide a high-level vocabulary to identify predicates and their associated cardinalities, datatypes and other constraints.
+Additional constraints can be associated with shapes using SPARQL and similar executable languages.
+These executable languages can also be used to define new high-level vocabulary terms.
+SHACL shapes can be used to communicate data structures associated with some process or interface, generate or validate data, or drive user interfaces.
 

### 2015-07-13 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
paper template

%% bare_conf.tex
%% V1.3
%% 2007/01/11
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[conference]{IEEEtran}
% Add the compsoc option for Computer Society conferences.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

%\usepackage{mdwmath}
%\usepackage{mdwtab}
% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
% especially mdwmath.sty and mdwtab.sty which are used to format equations
% and tables, respectively. The MDWtools set is already installed on most
% LaTeX systems. The lastest version and documentation is available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

%\usepackage{eqparbox}
% Also of notable interest is Scott Pakin's eqparbox package for creating
% (automatically sized) equal width boxes - aka "natural width parboxes".
% Available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/

% *** SUBFIGURE PACKAGES ***
%\usepackage[tight,footnotesize]{subfigure}
% subfigure.sty was written by Steven Douglas Cochran. This package makes it
% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
% work, it is a good idea to load it with the tight package option to reduce
% the amount of white space around the subfigures. subfigure.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
% subfigure.sty has been superceeded by subfig.sty.

%\usepackage[caption=false]{caption}
%\usepackage[font=footnotesize]{subfig}
% subfig.sty, also written by Steven Douglas Cochran, is the modern
% replacement for subfigure.sty. However, subfig.sty requires and
% automatically loads Axel Sommerfeldt's caption.sty which will override
% IEEEtran.cls handling of captions and this will result in nonIEEE style
% figure/table captions. To prevent this problem, be sure and preload
% caption.sty with its "caption=false" package option. This is will preserve
% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
% (recommended due to many improvements over 1.2) of subfig.sty supports
% the caption=false option directly:
%\usepackage[caption=false,font=footnotesize]{subfig}
%
% The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
% The latest version and documentation of caption.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Documentation is contained in the stfloats.sty comments as well as in the
% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
% does not allow \baselineskip to stretch. Authors submitting work to the
% IEEE should note that IEEE rarely uses double column equations and
% that authors should try to avoid such use. Do not be tempted to use the
% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
% not format its papers in such ways.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
% Read the url.sty source comments for usage information. Basically,
% \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Aspects of RDF Data Constraints in the Social, Behavioural, and Economic Sciences}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
%\author{\IEEEauthorblockN{Thomas Bosch}
%\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
%Georgia Institute of Technology\\
%Atlanta, Georgia 30332--0250\\
%Email: http://www.michaelshell.org/contact.html}
%\and
%\IEEEauthorblockN{Homer Simpson}
%\IEEEauthorblockA{Twentieth Century Fox\\
%Springfield, USA\\
%Email: homer@thesimpsons.com}
%\and
%\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
%\IEEEauthorblockA{Starfleet Academy\\
%San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212\\
%Fax: (888) 555--1212}}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
\author{\IEEEauthorblockN{Thomas Bosch\IEEEauthorrefmark{1},
Benjamin Zapilko\IEEEauthorrefmark{2},
Joachim Wackerow\IEEEauthorrefmark{3}, 
Kai Eckert\IEEEauthorrefmark{3}} %and
%Eldon Tyrell\IEEEauthorrefmark{4}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
Georgia Institute of Technology,
Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
Email: homer@thesimpsons.com}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
Telephone: (800) 555--1212, Fax: (888) 555--1212}
\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

\begin{abstract}
%\boldmath
The abstract goes here.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
% no \IEEEPARstart

%\hfill mds

%\hfill January 11, 2007

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command, the
% \label for the overall figure must come after \caption.
% \hfil must be used as a separator to get equal spacing.
% The subfigure.sty package works much the same way, except \subfigure is
% used instead of \subfloat.
%
%\begin{figure*}[!t]
%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
%\label{fig_second_case}}}
%\caption{Simulation results}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals/conferences use top floats
% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
% command of the stfloats package.

\section{Conclusion}
The conclusion goes here.

% conference papers do not normally have an appendix

% use section* for acknowledgement
\section*{Acknowledgment}

The authors would like to thank...

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

% that's all folks
\end{document}

### 2015-07-13 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
paper template

@@
 
+% allows for temporary adjustment of side margins
+\usepackage{chngpage}
+
+% just makes the table prettier (see \toprule, \bottomrule, etc. commands below)
+\usepackage{booktabs}
+
+\usepackage[utf8]{inputenc}
+%\usepackage[font=small,skip=0pt]{caption}
+
+% footnotes
+\usepackage{scrextend}
+
+% colors
+\usepackage[usenames, dvipsnames]{color}
+
+% underline
+\usepackage{tikz}
+\newcommand{\udensdot}[1]{%
+    \tikz[baseline=(todotted.base)]{
+        \node[inner sep=1pt,outer sep=0pt] (todotted) {#1};
+        \draw[densely dotted] (todotted.south west) -- (todotted.south east);
+    }%
+}%
+
+\newcommand{\uloosdot}[1]{%
+    \tikz[baseline=(todotted.base)]{
+        \node[inner sep=1pt,outer sep=0pt] (todotted) {#1};
+        \draw[loosely dotted] (todotted.south west) -- (todotted.south east);
+    }%
+}%
+
+\newcommand{\udash}[1]{%
+    \tikz[baseline=(todotted.base)]{
+        \node[inner sep=1pt,outer sep=0pt] (todotted) {#1};
+        \draw[dashed] (todotted.south west) -- (todotted.south east);
+    }%
+}%
+
+\newcommand{\udensdash}[1]{%
+    \tikz[baseline=(todotted.base)]{
+        \node[inner sep=1pt,outer sep=0pt] (todotted) {#1};
+        \draw[densely dashed] (todotted.south west) -- (todotted.south east);
+    }%
+}%
+
+\newcommand{\uloosdash}[1]{%
+    \tikz[baseline=(todotted.base)]{
+        \node[inner sep=1pt,outer sep=0pt] (todotted) {#1};
+        \draw[loosely dashed] (todotted.south west) -- (todotted.south east);
+    }%
+}%
+
+% URL handling
+\usepackage{url}
+\urlstyle{same}
+
+%\usepackage{makeidx}  % allows for indexgeneration
+
+%\usepackage{amsmath}
+\usepackage{amsmath, amssymb}
+\usepackage{mathabx}
+\usepackage{caption} 
+\captionsetup[table]{skip=10pt}
+
+% monospace within text
+\newcommand{\ms}[1]{\texttt{#1}}
+
+% examples
+\usepackage{fancyvrb}
+\DefineVerbatimEnvironment{ex}{Verbatim}{numbers=left,numbersep=2mm,frame=single,fontsize=\scriptsize}
+
+\usepackage{xspace}
+% Einfache und doppelte Anfuehrungszeichen
+\newcommand{\qs}{``} 
+\newcommand{\qe}{''\xspace} 
+\newcommand{\sqs}{`} 
+\newcommand{\sqe}{'\xspace}
+
+% checkmark
+\usepackage{tikz}
+\def\checkmark{\tikz\fill[scale=0.4](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;}
+
+% Xs
+\usepackage{pifont}
+
+% Tabellenabstände kleiner
+\setlength{\intextsep}{10pt} % Vertical space above & below [h] floats
+\setlength{\textfloatsep}{10pt} % Vertical space below (above) [t] ([b]) floats
+% \setlength{\abovecaptionskip}{0pt}
+% \setlength{\belowcaptionskip}{0pt}
+
+\usepackage{tabularx}
+\newcommand{\hr}{\hline\noalign{\smallskip}} % für die horizontalen linien in tabellen
+
+% Todos
+\usepackage[colorinlistoftodos]{todonotes}
+\newcommand{\ke}[1]{\todo[size=\small, color=red!40]{\textbf{Kai:} #1}}
+\newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}
+\newcommand{\er}[1]{\todo[size=\small, color=blue!40]{\textbf{Erman:} #1}}
+
+\newenvironment{table-1cols}{
+  \scriptsize
+  \sffamily
+  \vspace{0.3cm}
+  \begin{tabular}{l}
+  \hline
+  \textbf{Requirements} \\
+  \hline
+
+}{
+  \hline
+  \end{tabular}
+  \linebreak
+}
+
+\newenvironment{table-2cols}{
+  \scriptsize
+  \sffamily
+  \vspace{0.3cm}
+  \begin{tabular}{l|l}
+  \hline
+  \textbf{Requirements} & \textbf{Covering DSCLs} \\
+  \hline
+
+}{
+  \hline
+  \end{tabular}
+  \linebreak
+}
+
+\newenvironment{complexity}{
+  %\scriptsize
+  %\sffamily
+  %\vspace{0.3cm}
+  \begin{tabular}{l|l}
+  \hline
+  \textbf{Complexity Class} & \textbf{Complexity} \\
+  \hline
+
+}{
+  \hline
+  \end{tabular}
+  \linebreak
+}
+
+\newenvironment{DL}{
+  %\scriptsize
+  %\sffamily
+  \small
+  \vspace{0cm}
+	\begin{center}
+  \begin{tabular}{c l}
+
+}{
+  \end{tabular}
+	\end{center}
+}
+
+\newenvironment{evaluation}{
+  %\scriptsize
+  %\sffamily
+  %\vspace{0.3cm}
+  \begin{tabular}{l|c|c|c|c|c|c}
+  \hline
+  \textbf{Constraint Class} & \textbf{DSP} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
+  \hline
+
+}{
+  \hline
+  \end{tabular}
+  \linebreak
+}
+
+\newenvironment{constraint-languages-complexity}{
+  %\scriptsize
+  %\sffamily
+  %\vspace{0.3cm}
+  \begin{tabular}{l|c|c|c|c|c|c}
+  \hline
+  \textbf{Complexity Class} & \textbf{DSP} & \textbf{OWL2-DL} & \textbf{OWL2-QL} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
+  \hline
+
+}{
+  \hline
+  \end{tabular}
+  \linebreak
+}
+
+\newenvironment{user-fiendliness}{
+  %\scriptsize
+  %\sffamily
+  %\vspace{0.3cm}
+  \begin{tabular}{l|c|c|c|c|c}
+  \hline
+  \textbf{criterion} & \textbf{DSP} & \textbf{OWL2} & \textbf{ReSh} & \textbf{ShEx} & \textbf{SPIN} \\
+  \hline
+
+}{
+  \hline
+  \end{tabular}
+  \linebreak
+}
+
+\setcounter{secnumdepth}{5}
+
+% tables
+\usepackage{array,graphicx}
+\usepackage{booktabs}
+\usepackage{pifont}
+\newcommand*\rot{\rotatebox{90}}
+\newcommand*\OK{\ding{51}}
+\usepackage{booktabs}
+\newcommand*\ON[0]{$\surd$}
+
+\usepackage{tablefootnote}
+
+\usepackage{float}
+
+\usepackage{ntheorem}
+\newtheorem{hyp}{Hypothesis}
+
+\makeatletter
+\newcounter{subhyp} 
+\let\savedc@hyp\c@hyp
+\newenvironment{subhyp}
+ {%
+  \setcounter{subhyp}{0}%
+  \stepcounter{hyp}%
+  \edef\saved@hyp{\thehyp}% Save the current value of hyp
+  \let\c@hyp\c@subhyp     % Now hyp is subhyp
+  \renewcommand{\thehyp}{\saved@hyp\alph{hyp}}%
+ }
+ {}
+\newcommand{\normhyp}{%
+  \let\c@hyp\savedc@hyp % revert to the old one
+  \renewcommand\thehyp{\arabic{hyp}}%
+} 
+\makeatother
+
+\usepackage{multirow}
+
 \begin{document}
@@
 \author{\IEEEauthorblockN{Thomas Bosch\IEEEauthorrefmark{1},
-Benjamin Zapilko\IEEEauthorrefmark{2},
-Joachim Wackerow\IEEEauthorrefmark{3}, 
-Kai Eckert\IEEEauthorrefmark{3}} %and
+Benjamin Zapilko\IEEEauthorrefmark{1},
+Joachim Wackerow\IEEEauthorrefmark{1}, 
+Kai Eckert\IEEEauthorrefmark{2}} %and
 %Eldon Tyrell\IEEEauthorrefmark{4}}
-\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-Georgia Institute of Technology,
-Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-Email: homer@thesimpsons.com}
-\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-Telephone: (800) 555--1212, Fax: (888) 555--1212}
-\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
+\IEEEauthorblockA{\IEEEauthorrefmark{1}GESIS - Leibniz Institute for the Social Sciences, Mannheim, Germany\\
+Email: \{firstname.lastname\}@gesis.org}
+\IEEEauthorblockA{\IEEEauthorrefmark{2}Stuttgart Media University, Stuttgart, Germany\\
+Email: eckert@hdm-stuttgart.de}}
+%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
+%Telephone: (800) 555--1212, Fax: (888) 555--1212}
+%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
 
@@
 %\boldmath
-The abstract goes here.
+For research institutes, data libraries, and data archives,
+RDF data validation according to predefined constraints is a much sought-after feature, 
+particularly as this is taken for granted in the XML world.
+Based on our work in the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group, we identified and published by today 82 types of constraints that are required by various stakeholders for data applications.
+In this paper, we formulate 213 constraints of 53 different types on three different vocabularies (\emph{Disco}, \emph{QB}, and \emph{SKOS}) and classify them according to the complexity level of their type and their severity level.
+For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
+Based on the results, we formulate several hypotheses to direct the further development of constraint languages.
 \end{abstract}
@@
 
-\subsection{Subsection Heading Here}
-Subsection text here.
-
-\subsubsection{Subsubsection Heading Here}
-Subsubsection text here.
+%%% Findings aus dem Abstract
+%%% (1) for well-established vocabularies, the explicitly defined constraints are almost completely satisfied which demonstrates that constraint formulation in general works.
+(2) A significant amount of 47\% of the violations refer to complex constraints that are not easily expressible in existing languages which confirms the necessity to provide suitable constraint languages.
+(3) The percentage of severe constraint violations is very low, compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
+
+The social, behavioural, and economic sciences (\emph{SBE}) require high-quality data for their empirical research.
+For more than a decade, members of the \emph{SBE} community have been developing and using a
+metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)},
+an XML format to disseminate, manage,
+and reuse data collected and archived for research \cite{Vardigan2008}. 
+%DDI is heavily used by the CESSDA community of European national data archives, 
+%the International Household Survey Network community (made up of more than 90 statistical agencies),
+%and ICPSR - the largest SBE data archive in the US.
+In XML, the definition of schemas containing data constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
+With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration.
+Therefore, not only established vocabularies like \emph{SKOS} are used;
+recently, members of the \emph{SBE} and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.
+
+For constraint formulation and validation of RDF data, several languages exist or are currently developed, like \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles}.
+\emph{OWL 2} is also used as a constraint language under a closed world assumption.
+With its direct support of validation via \emph{SPARQL}, \emph{SPIN}%\footnote{\url{http://spinRDF.org/}}
+is very popular and certainly plays an important role for future developments in this field.
+It is particularly interesting as a means to validate arbitrary constraint languages by mapping them to \emph{SPARQL} \cite{BoschEckert2014-2}.
+Yet, there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners.
+Further research and development therefore is needed.
+
+In 2013, the W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
+where experts from industry, government, and academia discussed first use cases for RDF constraint formulation and RDF data validation.
+In 2014, two working groups on RDF validation have been established to develop a language to express constraints on RDF data: 
+the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles task group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}} which among others bundles the requirements of data institutions of the cultural heritage and \emph{SBE} sector and represents them in the W3C group.
+
+Within the DCMI task group, a collaboratively curated database of RDF validation requirements has been created which contains the findings of the working groups based on various case studies provided by data institutions \cite{BoschEckert2014}.
+It is publicly available and open for further contributions\footnote{Online at \url{http://purl.org/net/rdf-validation}}.
+The database connects requirements to use cases, case studies and implementations and forms the basis of this paper. 
+We distinguish 82 requirements to formulate RDF constraints; 
+each of them corresponding to an RDF constraint type.
+
+To gain a better understanding about the role of certain requirements for data quality and in order to direct the further development of constraint languages, we collected constraints for commonly used vocabularies in the \emph{SBE} domain, either from the vocabularies themselves or from domain and data experts.
+All in all, this lead to 213 constraints of 53 different types on three vocabularies.
+We let the experts classify the constraints according to the severity if they are violated.
+Furthermore, we classified the type of each constraint (corresponding to a requirement) based on its complexity ranging from types commonly found in vocabulary specifications (e.g., domain, range, and cardinality restrictions),
+over types that are simply stated using common constraint languages (e.g., language tag cardinality restrictions) to complex types that involve complex data structures or need more sophisticated languages to be easily expressible
+%(e.g., constraints on network topologies)
+(e.g., constraints on graph-based structures) (Section \ref{classification}).
+
+As we do not want to base our conclusions on the evaluations of vocabularies and constraint definitions alone, we conducted a large-scale experiment.
+For 114 constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
+%evaluated the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
+Based on the evaluation results,
+we formulated several hypotheses to direct the further development of constraint languages.
+To make valid general statements for all vocabularies, however,
+the hypotheses still have to be verified or falsified
+by evaluating the quality of data represented by more than three vocabularies (Section \ref{evaluation}).
+%The \textbf{contribution} of this paper is the development of a system 
+%\begin{enumerate}
+	%\item to classify RDF constraints (according to their severity levels) to evaluate the quality of metadata and data which may be represented by any vocabulary and 
+	%\item to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (sections \ref{classification} - \ref{complex-constraint-types}).
+%\end{enumerate}
+%By defining a huge amount of constraints of the majority of the constraint types,   
+%we apply the developed classification system to several and different vocabularies from the \emph{SBE} domain to represent both metadata and data and therefore prove its generality.
+%A complex and complete real world running example from the \emph{SBE} domain serves to prove the claim that the developed classification system perfectly applies for diverse vocabularies.
+%%, i.e., that it does not matter which vocabularies are used to represent (meta)data and for which domains constraints are defined.
+%We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
+%how data in tabular format and metadata on person-level data sets, aggregated data sets, and thesauri are represented in RDF, 
+%how therefore reused vocabularies are interrelated (section \ref{rdf-representation}),
+%and how \emph{SBE} (meta)data is validated against constraints of different constraint types (sections \ref{classification} - \ref{complex-constraint-types}).
+%We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple vocabularies to get an understanding
+%(1) which sets of constraint types (on different levels of complexity) and 
+%(2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).
+
+In this paper, we discuss constraints on RDF data in general.
+Note that the data represented in RDF can be data in the sense of \emph{SBE} sciences, but also metadata about published or unpublished data.
+We generally refer to both simply as RDF data and only distinguish between data and metadata in the data set descriptions and in the case that it matters for the purpose of this paper.
+The underlying \emph{semantics} for RDF validation is \emph{UNA}/\emph{CWA}.
+RDF validation requires that different names represent different objects ({\em unique name assumption (UNA)}), whereas,
+\emph{OWL 2} is based on the {\em non-unique name assumption (nUNA)}.  
+%A data property is \emph{functional} (\emph{R-65}) if for each individual \emph{x}, there can be at most one distinct literal \emph{y} such that \emph{x} is connected by the data property to \emph{y}.
+(See \cite{resource} for this terminology.)
+%When assuming \emph{UNA}, the functional property {\em title} (\ms{funct (title)}) causes a clash
+%in case the book {\em Huckleberry-Finn} has more than one \emph{title}
+%(\ms{title(Huckleberry-Finn, The-Adventures-of-Huckleberry-Finn)}, \ms{title(Huckleberry-Finn, Die-Abenteuer-des-Huckleberry-Finn)}).
+%Assuming nUNA, however, reasoning concludes that the titles {\em The-Adventures-of-Huckleberry-Finn} and {\em Die-Abenteuer-des-Huckleberry-Finn} are the same (\ms{\{The-Adventures-of-Huckleberry-Finn\}} = \ms{\{Die-Abenteuer-des-Huckle} \ms{berry-}\ms{Finn\}}).
+Reasoning in \emph{OWL 2} is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true. 
+%which fits its primary design purpose to represent knowledge on the World Wide Web. 
+%Most of the constraint languages except OWL, have a major shortcoming of redundancy.
+%With its open-world semantics, used as a constraint language, OWL solves the redundancy problem. 
+%\tb{the following example does not show the redundancy problem!}
+%\tb{2. benefit: reasoning solves redundancy problem}
+%As each \emph{book} must have a \emph{title} (\ms{Book $\sqsubseteq \exists$ title.$\top$}) and {\em Hamlet} is a \emph{book} (\ms{Book(Hamlet)}),
+%{\em Hamlet} must have at least one \emph{title}.
+%In an \emph{OWA} setting, this axiom does not cause a constraint violation (even if there is no explicitly defined \emph{title}), since there must be a \emph{title} for this \emph{book} which we may not know.
+On the other hand, RDF validation scenarios require the {\em closed-world assumption (CWA)}, i.e., a statement is inferred to be false if it cannot be proved to be true.
+Classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals.
+This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past.  
+In case we use \emph{OWL 2} constructs in terms of constraints, we adopt the same semantics (CWA) that is for RDF validation in general.
+
+%We propose an extensible metric to measure the continuum of severity levels to indicate how serious the violation of given constraints is.
+%Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary. 
+%As constraint types are used to define constraints on (meta)data expressed by any vocabulary, the proposed constraint classification can be applied generically, i.e. vocabulary-independent.
+
+The data most often used in research within \emph{SBE} sciences is \emph{person-level data} (or more generally \emph{record-unit data}, i.e., data collected about individuals, businesses, and households) in form of responses to studies or taken from administrative registers
+(such as hospital records, registers of births and deaths). 
+The range of person-level data is very broad - 
+including census, education, health data and business, social, and labor force surveys.  
+This type of research data is
+held within data archives or data libraries after it has been collected, so that it may be
+reused by future researchers.
+
+By its nature, person-level data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 
+Researchers typically represent their results as aggregated data in form of multi-dimensional tables with only a few columns; so-called \emph{variables} such as \emph{sex} or \emph{age}.
+%In performing their research, the detailed person-level
+%data is aggregated into multi-dimensional tables which answer particular research questions.
+Aggregated data, which answers particular research questions, is derived from person-level data by statistics on groups or aggregates such as frequencies and arithmetic means.
+%The SDMX metadata standard – used as the basis for \emph{QB} – and DDI have traditionally made efforts to align their content. 
+%Similarly, some of the developers of \emph{Disco} were also involved in the development of \emph{QB}, 
+%allowing the RDF versions of these standards to retain that alignment.
+%While \emph{Disco} and \emph{QB} provide terms for the description of data sets, 
+%both on a different level of aggregation, 
+%the \emph{Data Catalog Vocabulary (DCAT)}\footnote{\url{http://www.w3.org/TR/vocab-dcat/}} enables the representation of these data sets inside of data collections like repositories, catalogs, or archives.
+%The relationship between data collections and their contained data sets is useful, since such collections are a typical entry point when searching for data.
+%Although, in most cases aggregated data is still published in form of PDFs, 
+%it is more and more common to publish aggregated data as CSV files,
+The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying person-level data.
+Aggregated data is published in form of CSV files,
+allowing to perform calculations on the data.
+%For these calculations, definitions of the columns are needed (e.g. is a given variable interpreted numerically or as a string).
+%\emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} is a vocabulary to represent data in tabular format in RDF.\tb{tabular data} 
+%The data could be either represented in records with character-separated values (CSV) or in records with fixed length. 
+%Portals harvest metadata (as well as publicly available data) from multiple RDF data providers.
+%\tb{To ensure high quality, data must satisfy certain criteria - specified in terms of RDF constraints.}
+
+For more detailed analyses, researchers refer to person-level data including additional variables needed to answer subsequent research questions
+%Although not that common, the other direction is also possible, 
+%i.e. researchers may use metadata on person-level data to search for aggregated data.
+like the comparison of studies between countries.
+A \emph{study} represents the process by which a data set was generated or collected.
+Eurostat\footnote{\url{http://ec.europa.eu/eurostat}}, the statistical office of the European Union, provides research findings in form of aggregated data (downloadable as CSV files) and its metadata at European level that enable comparisons between countries.
+%This way, researchers get promising findings (in form of published tables with a few columns).
+%We use the availability of childcare services in European Union member states by year, duration, and child age leading to subsequent research questions as running example of this paper.
+%The first step is to determine in which countries the unemployment rate is collected and which other variables of each country-specific study are theoretically comparable and can therefore be used to answer the underlying research question.
+The variable \emph{formal childcare}\footnote{Aggregated data and its metadata is available at: \url{http://ec.europa.eu/eurostat/web/products-datasets/-/ilc_caindformal}} %(in contrast to childcare at home)
+captures the measured availability of childcare services in percent over the population in European Union member states by 
+the variables \emph{year}, \emph{duration} (in hours per week), \emph{age} of the child, and \emph{country}.
+Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
+The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger} or by a code list of age clusters (e.g., '0 to 10' and '11 to 20').
+
+A very important and representative RDF validation case study within SBE sciences is the comparison of variables between data collections of different countries.
+Several vocabulary-specific constraints on RDF data are checked for each data collection
+to determine if variables measuring \emph{age} 
+- collected for different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
+are comparable:
+(1) variable definitions must be available, 
+(2) for each code a human-readable label has to be specified,
+(3) code lists must be structured properly, and
+(4) code lists must either be identical or at least similar.
+If a researcher only wants to get a first overview over the comparability of variables (use case 1), 
+covering the first three constraints may be sufficient,
+i.e., the violation of the first three constraints is more serious than the violation of the last constraint.
+If the intention of the researcher is to perform more sophisticated comparisons (use case 2), however, the user may raise the severity level of the last constraint.
+
+%\ke{Wieso werden constraints nur gechecked wenn variablen auf vergleichbarkeit geprüft werden?
+das habt ihr doch gar nicht gemacht sondern ganz allgemein constraints für vokabulare aufgestellt.
+Ist QB und Disco nicht sowieso unabhängig von konkreten Variablen?}\tb{das soll nur ein beipsiel sein, wann eine komplexere validierung im kontext von sbe sinn macht (1) + (2) sind vocabulary constraints und (3) + (4) sind complex constraints}
+
+%After validating the metadata according to these constraints, portals offer added values to their customers, e.g., by searching over and comparing metadata of multiple providers.
+
+%\textbf{Data validation.}
+%Data providers and harvesters do not only offer metadata but also publicly available data on different level of aggregation.
+%To ensure high data quality, they have to check provenance information and to analyze and therefore validate the data according to predefined constraints (e.g.
+'are fundamental data fragments available?', and 'how does valid data look like?').
+%They validate, e.g., if fundamental data parts are available and define how valid data should look like (using syntactic rules).
+%Provenance (where does the data come from?) is an important aspect in evaluating data quality.
+%As data searchers know exactly which data sources they trust and which are reasonable to meet their individual use cases, 
+%RDF data validation can only be performed semi-automatically, i.e., an automatic approach serves as basis for intellectual decisions.
+
+\section{Related Work}
+\label{related-work}
+
+%\textbf{XML vs. RDF Validation.}
+For data archives, research institutes, and data libraries,
+RDF validation according to predefined constraints is a much sought-after feature, 
+particularly as this is taken for granted in the XML world.
+DDI-XML documents, e.g., are validated against diverse XSDs\footnote{\url{http://www.ddialliance.org/Specification/}}.
+As certain constraints cannot be formulated and validated by XSDs, 
+so-called secondary-level validation tools like \emph{Schematron}\footnote{\url{https://msdn.microsoft.com/en-us/library/aa468554.aspx}} have been introduced to overcome the limitations of XML validation.
+\emph{Schematron} generates validation rules and validates XML documents according to them.
+With RDF validation, one can overcome drawbacks when validating XML documents\footnote{\url{http://www.xmlmind.com/xmleditor/_distrib/doc/xmltool/xsd_structure_limitations.html}}.
+It cannot be validated, e.g., if each code of a variable's code list is associated with a category (\emph{R-86}).
+Additionally, it cannot be validated that if an element has a specific value, then certain child elements must be present (\emph{R-71}).  
+A comprehensive comparison of XML and RDF validation, however, is not within the scope of this paper.
+
+%validation or relational databases: types, relations
+
+%\textbf{RDF Data Cube Vocabulary.}
+A well-formed \emph{RDF Data Cube} is an a RDF graph describing one or more instances of \emph{qb:DataSet} for which each of the 22 integrity constraints\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf}, defined within the \emph{QB} specification, passes.
+Each integrity constraint is expressed as narrative prose and, where possible, a SPARQL ASK query or query template. 
+If the ASK query is applied to an RDF graph then it will return true if that graph contains one or more \emph{QB} instances which violate the corresponding constraint \cite{CyganiakReynolds2014}.
+Mader, Haslhofer, and Isaac investigated how to support
+taxonomists in improving SKOS vocabularies by pointing out quality
+issues that go beyond the integrity constraints defined in the SKOS specification \cite{MaderHaslhoferIsaac2012}.
+
+%\section{Running Example}
+%\label{running-example}
+\section{Common Vocabularies in SBE Sciences}
+\label{rdf-representation}
+
+%In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.
+
+We took all well-established and newly developed \emph{SBE} vocabularies into account and defined constraints for six vocabularies commonly used in or developed for the \emph{SBE} sciences which are briefly introduced in the following.
+For three of them, we analyzed actual data according to constraint violations, as for these vocabularies large data sets are already published.
+%e evaluated the data quality of large data sets on three of them, as for these vocabularies large data sets are published.
+
+%For our evaluation, we examined six different vocabularies commonly used in or developed for the \emph{SBE} sciences which are briefly introduced in the following.
+For three of them, we analyzed actual data according to constraint violations.
+For \emph{PHDD} and \emph{XKOS}, there is not yet enough data available so we limit our examination to the vocabularies themselves.
+
+%\textbf{Metadata on Aggregated Data.}
+The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e.
+multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}.
+%\emph{QB} represents metadata on multi-dimensional aggregate data in two files: a \emph{qb:DataSet} and a \emph{qb:DataStructureDefinition}.
+A \emph{qb:DataStructureDefinition} contains metadata of the data collection.
+The variable \emph{formal childcare}, e.g., is modeled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
+The variables \emph{year}, \emph{duration}, \emph{age}, and \emph{country} are \emph{qb:dimensions}.
+Data values, i.e., the availability of childcare services in percent over the population, are collected in a \emph{qb:DataSet}. 
+Each data value is represented inside a \emph{qb:Observation} which contains values for each dimension\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}}.
+%(e.g., the year in which \emph{formal childcare} has been determined).
+%\ke{Wieso springt das von einer sehr knappen Einführung direkt zu konkreten (beliebigen?) Variablen?
+Ich möchte wissen, wofür QB benutzt wird und gerne ein konkretes %Beispiel sehen, um mir einen Data Cube vorstellen zu können.}\tb{hmm, ich halte das beispiel für ein knappes und verständliches beipsiel wie eine tabelle in qb dargestellt wird / es ist auch der link enthalten zu der tabelle von eurostat}
+
+%\textbf{Rectangular Data.}
+\emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} is a vocabulary to represent data in tabular format in RDF enabling further aggregations and calculations.
+The data could be either represented in records with character-separated values (CSV) or fixed length. 
+\emph{Eurostat} provides a CSV file, a two-dimensional table (\emph{phdd:Table}) about \emph{formal childcare} 
+which is structured by a table structure (\emph{phdd:TableStructure}, \emph{phdd:Delimited})
+including information about the character set (\emph{ASCII}), the variable delimiter (\emph{,}), the new line marker (\emph{CRLF}), and the first line where the data starts (\emph{2}).
+The table structure is related to table columns (\emph{phdd:Column}) which are described by column descriptions (\emph{phdd:DelimitedColumnDescription}).
+For the column containing the actual cell values in percent, the column position (\emph{5}), the recommended data type (\emph{xsd:non} \emph{NegativeInteger}), and the storage format (\emph{TINYINT}) is stated.
+%The RDFication enables further aggregations and calculations, e.g., in order to compare \emph{formal childcare} between Northern and Southern Europe or between otherwise grouped countries.
+% macht mehr sinn wenn Tabelle in mehreren Dimensionen vorhanden ist ode wenn Klassifikationen wie ISCO verwendet werden
+
+%\textbf{Metadata on Person-Level Data.}
+For more detailed analyses we refer to the person-level data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}.
+%published by the \emph{Microdata Information System (MISSY)}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}}.
+Where data collection is cyclic, data sets may be released as \emph{series}, 
+where each cycle produces one or more data sets. 
+%\emph{Missy} is an online service platform that provides systematically structured metadata for official statistics on European person-level data sets. 
+%This includes data documentation at the study and variable level as well as documentation materials, tools and further information. 
+%\ke{Wieso jetzt wieder qb?}\tb{ich möchte zeigen wie aggregierte daten und personenbezogene daten in RDF verbunden sind. Weglassen?}
+%Aggregated (qb:DataSet) and underlying person-level data sets (\emph{disco:LogicalDataSet}) are connected by \emph{prov:wasDerivedFrom}. 
+The aggregated variable \emph{formal childcare} is calculated on the basis of six person-level variables 
+(e.g., \emph{Education at pre-school})
+%\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC/2011/Cross-sectional/original#2011-Cross-sectional-RL010}})
+%(2) Education at compulsory school,
+%(3) Child care at centre-based services,
+%(4) Child care at day-care centre,
+%(5) Child care by a professional child-minder, and
+%(6) Child care by grand-parents, household members, relatives, friends, neighbours.
+for which detailed metadata is given 
+%(definitions, descriptions, theoretical concepts, questions variables are based on, code lists, frequencies, descriptive statistics, countries, year of data collection, and classifications) 
+(e.g., code lists)
+enabling researchers to replicate the results shown in aggregated data tables.
+The \emph{DDI-RDF Discovery Vocabulary (Disco)} is a vocabulary to represent metadata on person-level data in RDF.
+The series (\emph{disco:StudyGroup}) \emph{EU-SILC} contains one study (\emph{disco:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
+\emph{dcterms:spatial} points to the countries for which the data has been collected.
+The study \emph{EU-SILC 2011} contains eight person-level data sets (\emph{disco:LogicalDataSet})
+including person-level variables (\emph{disco:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
+%Metadata on person-level data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
+%One common research question is ,e.g., the comparison of variables like 
+%\emph{formal childcare} between countries, for which the variable is collected within the context of an individual study, and other European or non European countries (e.g. OSCE).
+
+%\textbf{Organizations, Hierarchies, and Classifications.}
+%\textbf{Reusing SKOS.}
+The \emph{Simple Knowledge Organization System (SKOS)} is reused multiple times to build \emph{SBE} vocabularies.
+%Variables are constructed out of values and/or (un)ordered code lists.
+The codes of the variable \emph{Education at pre-school} (number of education hours per week) are modeled as \emph{skos:Concepts} and 
+a \emph{skos:OrderedCollection} organizes them in a particular order within a \emph{skos:member} \emph{List}.
+A variable may be associated with a theoretical concept (\emph{skos:Concept}). 
+\emph{skos:narrower} builds the hierarchy of theoretical concepts within a \emph{skos:Concept} \emph{Scheme} of a series.
+The variable \emph{Education at pre-school} is assigned to the theoretical concept \emph{Child Care} which is the narrower concept of \emph{Education} - one of the top concepts of the series \emph{EU-SILC}.
+Controlled vocabularies (\emph{skos:ConceptScheme}), serving as extension and reuse mechanism,
+organize types (\emph{skos:Concept}) of descriptive statistics (\emph{disco:SummaryStatistics}) like minimum, maximum, and arithmetic mean.
+\emph{XKOS}\footnote{\url{https://github.com/linked-statistics/xkos}} is a SKOS extension to describe formal statistical classifications like the International Standard Classification of Occupations (\emph{ISCO}).
+and the Statistical Classification of Economic Activities in the European Community \emph{NACE}.
+\emph{DCAT} enables to represent data sets inside of data collections like portals, repositories, catalogs, and archives
+which serve as typical entry points when searching for data.
+
+%\textbf{Searching for (Meta)data.}
+%\emph{DCAT} enables to represent data sets inside of data collections like portals, repositories, catalogs, and archives
+%which serve as typical entry points when searching for data.
+%Users search for aggregated and person-level data records (\emph{dcat:CatalogRecord}) inside data catalogs (\emph{dcat:Catalog}). 
+%As search differs depending on the users’ information need,
+%users may only search for records' metadata (e.g., \emph{dcterms:title}, \emph{dcterms:description}), 
+%or may formulate more sophisticated queries on aggregated and person-level data sets (\emph{dcat:Dataset}) or their
+%distributions (\emph{dcat:Distribution}) which are part of the records. 
+%Often, users search for data sets covering particular topics (\emph{dcat:keyword}, \emph{dcat:theme}), time periods (\emph{dcterms:temporal}),  or  locations (\emph{dcterms:spatial}), 
+%or for certain formats in which the data distribution is available (\emph{dcterms:format}).
+
+\section{Classification of Constraint Types and Constraints}
+\label{classification}
+
+To gain better insights into the role that certain types of constraints play for the quality of RDF data, we use two simple classifications: on the one hand, we classify RDF constraint types according to their complexity and on the other hand, we classify concrete constraints formulated for a vocabulary according to the perceived severity of a violation.
+
+Within the working groups, we identified by today 82 requirements to formulate RDF constraints (e.g.
+\emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}.
+Within a technical report serving as first appendix of this paper we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages \cite{BoschNolleAcarEckert2015}.
+We provide mappings to representations in Description Logics (\emph{DL}) to logically underpin each requirement and to determine which \emph{DL} constructs are needed to express each constraint type.
+
+%In total, we distinguish 82 RDF constraint types as we identified 6 RDF constraint types which are only necessary for validating particular vocabularies.
+
+%Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
+
+The classification of the 213 concrete constraints on three vocabularies according to severity levels is published in a second technical report serving as second appendix of this paper \cite{BoschZapilkoWackerowEckert2015}.
+In the following, we summarize the results for the purpose of our evaluation.
+
+\subsection{Complexity of Constraint Types}
+
+According to the complexity of constraint types, the complete set of \emph{constraint types} encompasses three disjoint \emph{sets of constraint types}:
+\begin{enumerate}
+	\item \textbf{\emph{Vocabulary Constraint Types}}
+	\item \textbf{\emph{Simple Constraint Types}}
+	\item \textbf{\emph{Complex Constraint Types}}
+\end{enumerate}
+
+The modeling languages \emph{RDF}, \emph{RDFS}, and \emph{OWL} are typically used to formally specify vocabularies.
+\emph{Vocabulary constraint types}
+denotes the set of constraint types that are commonly found for constraints within formal specifications of vocabularies, i.e., constraints that are formulated using \emph{RDFS} and common constructs of \emph{OWL}.
+We determined this set based on the evaluation of the six vocabularies.
+\emph{Vocabulary constraints} generally can be seen as a basic level of constraints ensuring that the data is consistent with the intended syntaxes, semantics, and integrity of vocabularies' data models.
+
+%The {\em existential quantification} (\emph{R-86}) 
+%\ms{Study $\equiv$ $\exists$ product.LogicalDataSet} (\emph{DL}), e.g., restricts studies to contain at least one data set which is expressible in OWL 2:
+\emph{Minimum qualified cardinality restrictions} (\emph{R-74}), e.g., guarantee that individuals of given classes are connected by particular properties to at least n different individuals/literals of certain classes or data ranges.
+In \emph{PHDD}, a \emph{minimum qualified cardinality restriction} can be obtained from the OWL definition of this restriction class, ensuring that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:
+\begin{ex}
+[   a owl:Restriction ; rdfs:subClassOf TableStructure ;
+    owl:minQualifiedCardinality 1 ;
+    owl:onProperty column ;
+    owl:onClass Column ] .
+\end{ex}
+
+\emph{Simple} and \emph{complex constraints} are in contrast to \emph{vocabulary constraints} usually not (yet) explicitly defined within formal specifications of vocabularies.
+Instead, they are often defined in textual descriptions of the vocabularies.
+Additionally, we let our domain and data experts define constraints when they agreed that violating the constraint would affect the usefulness of the data.
+
+We further distinguished \emph{simple constraint types} as the set of constraint types whose constraints can be easily defined without much effort in addition to the already defined \emph{vocabulary constraints}.
+\emph{Data property facets} (\emph{R-46}) is an example of a \emph{simple constraint type} which enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
+The abstract of series/studies, e.g., should have a minimum length which is easily and concisely expressible by SPARQL: 
+\begin{ex}
+SELECT ?study WHERE {
+    ?study dcterms:abstract ?abstract . FILTER ( STRLEN ( ?abstract ) = 10 ) . }
+\end{ex}
+For these constraints, we expect a straight-forward support in future constraint languages.
+
+\emph{Complex constraint types} encompass constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
+For assessing the quality of thesauri, e.g., we concentrate on the graph-based structure and apply graph- and network-analysis techniques.
+An example of such constraints of the constraint type \emph{structure} is that 
+a thesaurus should not contain many orphan concepts, i.e., concepts without any associative or hierarchical relations, lacking context information valuable for search.
+This \emph{complex constraint} is only expressible by \emph{SPARQL} and not directly understandable:
+\begin{ex}
+SELECT ?concept WHERE {
+    ?concept a [rdfs:subClassOf* skos:Concept] .
+    FILTER NOT EXISTS { ?concept ?p ?o . 
+        FILTER ( ?p IN ( skos:related, skos:relatedMatch, skos:broader, ... ) ) . }
+\end{ex}
+\emph{Complex constraints} are today in most cases only expressible by plain \emph{SPARQL}. Depending on their usefulness, a support in constraint languages should be considered.
+
+\subsection{Severity of Constraints}
+
+A concrete constraint is instantiated from one of the 82 constraint types and is defined for a specific vocabulary.
+It does not make sense to determine the severity of constraint violations of an entire constraint type,
+as the severity of the violation of a given constraint depends on the individual context and vocabulary.
+%as the violation of one constraint may be severe,
+%whereas, the violation of another constraint of the same type may be minor.
+\emph{SBE} experts determined the default \textbf{\emph{severity level}}\footnote{The possibility to define severity levels in vocabularies is in itself a requirement (\emph{R-158}) defined by the DCMI task group.} for each of the 213 constraints to indicate how serious the violation of the constraint is.
+%We propose an extensible metric to measure the continuum of severity levels ranging from \emph{informational} to \emph{error}.
+We use the commonly accepted classification of log messages in software development and distinguish \emph{informational}, \emph{warning} and \emph{error}.
+%According to the default severity level of constraints, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:\ke{auch dieser satz macht keinen sinn für mich, ebensowenig wie die extrem erhellende auflistung, die gleich folgt...
+mein vorschlag von eben kann das komplett ersetzen.}
+%\begin{itemize}
+	%\item \textbf{\emph{informational constraints}}: constraints with severity level \emph{informational}
+	%\item \textbf{\emph{warning constraints}}: constraints with severity level \emph{warning}
+	%\item \textbf{\emph{error constraints}}: constraints with severity level \emph{error}
+%\end{itemize}
+Violations of \emph{informational constraints} point to desirable but not necessary data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies.
+%They are not seen as serious errors.
+\emph{Warnings} are syntactic or semantic problems which typically should not lead to an abortion of data processing.
+\emph{Errors} are syntactic or semantic errors which should cause the abortion of data processing. 
+%Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
+%Data not conforming to \emph{warning constraints} but to \emph{error constraints} could be processed further.
+%Data not corresponding to \emph{error constraints}, however, cannot be processed further after validation.
+
+Note that there is a correlation between the severity of a constraint and the complexity of its type: vocabulary constraint are in most cases classified with an \emph{error} level as they typically represent basic and important constraints; there is a reason why they have been included in the vocabulary specification.
+
+% Although, we provide default severity levels for each constraint, validation environments should enable users to adapt the severity levels of constraints according to their individual needs.
+% Validation environments should enable users to select which constraints to validate against depending on their individual use cases.
+% For some use cases, 
+% validating \emph{vocabulary constraints} may be more important than validating \emph{simple} or \emph{complex constraints}.
+% For other use cases,
+% validating \emph{error constraints} may be sufficient without taking \emph{warning} and \emph{informational constraints} into account.
+% We evaluated the (meta)data quality of large real world data sets represented by multiple and different vocabularies to get an understanding  
+% (1) which sets of constraint types (on different levels of complexity) and 
+% (2) which sets of constraints (associated with particular severity levels) encompass the constraints causing the most/fewest constraint violations (see section \ref{evaluation}).
+
+%
+%- different sets of constraints for different use cases / use case specific constraints
+%
+%- validation against minimal set of requirements / constraints
+%
+%-----
+
+%further ideas:
+%
+%RDF validation scenarios require the closed-world assumption (CWA) (i.e., a statement is inferred to be false if it cannot be proved to be true).
+
+%use-case specific constraints, e.g., DCAT: searching for metadata
+%\tb{Thomas: ToDo}
+
+\subsection{Examples}
+\label{vocabulary-constraint-types}
+
+%The constraint type \emph{vocabulary} guarantees that users do not invent new or use deprecated terms of vocabularies.
+%Out-dated classes and properties of previous vocabulary versions can be marked as deprecated.
+%The constraint types \emph{context-specific valid classes and properties} (\emph{R-209; R-210}) can be used to specify which classes and properties are valid in which context - here a given vocabulary version.
+%\emph{Value is valid for datatype} (\emph{R-223}) constraints serve to make sure that all literal values are valid with regard to their datatypes - as stated in the vocabularies.
+%Thus, it is checked that all date values (e.g., {{\em dcterms:date}) are actually of the datatype \emph{xsd:date} and that \emph{xsd:nonNegativeInteger} values (e.g.
+\emph{disco:frequency}) are not negative\footnote{For simplicity reasons, we only assign severity levels to \emph{vocabulary constraints} if they differ from \emph{error}.}.
+%Depending on property datatypes, two different literal values have
+%a specific ordering with respect to operators like \textless  (\emph{R-43: literal value comparison}).
+%Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}).
+
+%All properties, not having the same domain and range types, are defined to be pairwise disjoint
+%(\emph{R-9: disjoint properties}), i.e., no individual \emph{x} can be connected to an individual/literal \emph{y} by disjoint properties (e.g., \emph{phdd:isStructuredBy} and \emph{phdd:column}).
+%All \emph{PHDD} classes (e.g., \emph{phdd:TableDescription}, \emph{phdd:ColumnDescription}) are pairwise disjoint (\emph{R-7: disjoint classes}),
+%i.e., individuals cannot be instances of multiple disjoint classes.
+\subsubsection*{Vocabulary Constraint Types.}
+It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values (\emph{R-30/37: allowed values}). 
+%\emph{Allowed values} (\emph{R-30, R-37}) for properties can be IRIs (matching one or multiple patterns), any literals, allowed literals (e.g.
+'red' 'blue' 'green'), and typed literals of one or multiple type(s) (e.g.
+\emph{xsd:string}).
+\emph{disco:Category} \emph{Statistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString}.
+%Validation should \emph{exploit sub-super relations} in vocabularies (\emph{R-224}).
+%If \emph{dcterms:coverage} and one of its sub properties (\emph{dcterms:spatial}, \emph{dcterms:temporal}) are given,
+%it is checked that \emph{dcterms:coverage} is not redundant with its sub-properties 
+%which may indicate when the data is verbose/redundant or expressed at a too general level.
+Consider the following \emph{DL} knowledge base $\mathcal{K}$\footnote{A knowledge base is a collection of formal statements which corresponds to \emph{facts} or what is known explicitly.
+For simplicity reasons, we do not state namespace prefixes.}:
+\begin{center}
+\begin{DL} 
+$\mathcal{K}=\{$ 
+	%&\ms{isStructuredBy $\sqsubseteq$ $\neg$ column}, \\
+	%&\ms{TableDescription $\sqcap$ ColumnDescription $\sqsubseteq$ $\perp$}, \\
+	&\ms{CategoryStatistics $\equiv$ $\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString}, \\
+  &\ms{Variable $\equiv$ $\exists$ concept.Concept, Catalog $\sqsubseteq$ $\forall$ dataset.Dataset}, \\
+  &\ms{$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table, $\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}
+\}\\ 
+\end{DL}
+\end{center}
+
+%We extend $\mathcal{K}$ by 
+\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals/literals of certain types.
+Variables, e.g., should have a relation to a theoretical concept (\emph{informational}).
+%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
+The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
+The default severity level of this constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
+A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
+%Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets}:
+%\begin{DL}
+%Catalog $\sqsubseteq$ $\forall$ dataset.Dataset
+%\end{DL}
+Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets}.
+\emph{Property domain} (\emph{R-25, R-26}) and \emph{range} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties:
+Only \emph{phdd:Tables}, e.g., can have \emph{phdd:isStructuredBy} relationships and
+\emph{xkos:belongsTo} relations can only point to \emph{skos:Concepts}.
+%\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals/literals of certain types.
+%Variables, e.g., should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
+%%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
+%The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
+%The default severity level of the constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
+%If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
+%If metadata on data files, including the actual data, is missing (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the study is not sufficient.
+%Case quantity measures how many cases are collected for a study.
+%High case and variable quantities are indicators for high statistical quality and comprehensiveness of the underlying study ($\mathcal{SL}_{1}$).
+
+%\textbf{Cardinality Restrictions on Properties.}
+%An \emph{existential quantification} (\emph{R-86}) contains all those individuals that are connected by a property to individuals/literals of given classes or data ranges.
+%Every \emph{qb:SliceKey}, e.g., must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}).
+%\emph{Minimum/maximum/exact qualified cardinality restrictions} (\emph{R-74, R-75, R-76}) contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals of particular classes or data ranges.
+%A \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column},
+%a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}), and a \emph{qb:DataSet} is structured by (\emph{qb:structure}) exactly one \emph{qb:DataStructureDefinition}.
+%\begin{DL}
+%TableStructure $\sqsubseteq$ $\geq$1 column.Column \\
+%Variable $\sqsubseteq$ $\leq$1 concept.Concept \\
+%DataSet $\sqsubseteq$ $\geq$1 structure.DSD $\sqcap$
+%$\leq$1 structure.DSD
+%\end{DL}
+
+%%\textbf{Validation and Reasoning.}
+%Some constraint types enable performing reasoning prior to validation which may resolve or cause constraint violations.
+%With \emph{subsumption} (\emph{R-100}), one can state that \emph{xkos:ClassificationLevel} is a sub-class of \emph{skos:Collection}, i.e., each \emph{xkos:ClassificationLevel} must also be part of the \emph{skos:Collection} class extension.
+%With \emph{sub properties} (\emph{R-54, R-64}), one can state that \emph{disco:fundedBy} is a sub-property of \emph{dcterms:contributor} - i.e., if a study is funded by an organization, then this organization contributed to this study.
+%\begin{DL}
+%ClassificationLevel $\sqsubseteq$ Collection \\
+%fundedBy $\sqsubseteq$ contributor
+%\end{DL}
+
+%\section{Basic Constraint Types}
+%\label{vocabulary-constraint-types}
+
+%As \emph{RDFS} and \emph{OWL} are typically used to define vocabularies, \emph{RDFS} and \emph{OWL} reasoning may be performed prior to validation. 
+%Reasoning and validation are indeed very closely related. 
+%\emph{Reasoning} is the process of determining what follows from what has been stated.
+%%Both should be possible: (1) validation with reasoning and (2) validation without reasoning. 
+%We divide the whole set of \emph{basic constraint types} ($\mathcal{CT}_{B}$) into two disjoint sets to investigate the affect of reasoning to the validation process: 
+%\begin{enumerate}
+	%\item $\mathcal{C}_B ^{\mathcal{R}}$ corresponds to axioms in \emph{OWL 2} and denotes the set of constraint types which enable performing reasoning prior to validation, especially when not all the knowledge is explicit (section \ref{basic-constraint-types-with-reasoning}).
+  %\item $\overline{\mathcal{C}_B ^{\mathcal{R}}}$  denotes the set of constraint types for which reasoning cannot be done or does not improve the result in any obvious sense (section \ref{basic-constraint-types-without-reasoning}).
+%\end{enumerate}
+
+%\subsection{Basic Constraint Types with Reasoning}
+%\label{basic-constraint-types-with-reasoning}
+
+%%Validation environments should enable users to decide if they wish to perform reasoning prior to validation.
+%%Reasoning as an optional pre validation step is beneficial for RDF validation as 
+%%(1) it may resolve constraint violations and  
+%%(2) it may cause useful constraint violations.
+%A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
+%%Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets}:
+%%\begin{DL}
+%%Catalog $\sqsubseteq$ $\forall$ dataset.Dataset
+%%\end{DL}
+%Consider the following DL knowledge base $\mathcal{K}$\footnote{A knowledge base is a collection of formal statements which corresponds to \emph{facts} or what is known explicitly.
+For simplicity reasons, we only write namespace prefixes in DL statements to avoid ambiguities.}:
+%
+%\begin{center}
+%\begin{DL} 
+%$\mathcal{K}=\{$ &\ms{LogicalDataSet $\sqsubseteq$ dcat:DataSet},\\
+ %&\ms{LogicalDataSet $\sqsubseteq \forall$ aggregation.qb:DataSet},\\
+ %%&\ms{dcat:DataSet $\equiv$ $\exists$ dcat:distribution . dcat:Distribution},\\
+ %&\ms{LogicalDataSet( logical-data-set )},\\
+ %&\ms{aggregation( logical-data-set, aggregated-data-set )}
+ %\}\\ 
+%\end{DL}
+%\end{center}
+%
+%As we know that only person-level data sets (\emph{disco:LogicalDataSet}) can derive (\emph{disco:aggregation}) aggregated data sets (\emph{qb:DataSet}), 
+%{\em logical-data-set} is a \emph{disco:LogicalDataSet}, 
+%and \emph{aggregated-data-set} is derived from \emph{logical-data-set},
+%we conclude that \emph{aggregated-data-set} must be a \emph{qb:DataSet}.
+%As \emph{aggregated-data-set} is not explicitly defined to be a \emph{qb:DataSet}, however, a constraint violation is raised.
+%If we perform reasoning prior to validation, the constraint violation is resolved, as the implicit triple \ms{qb:DataSet(aggregated-data-set)} is inferred. 
+%
+%Reasoning may also cause constraint violations which are needed to enhance data quality.
+%With \emph{subsumption} (\emph{R-100}), one can state that \emph{disco:LogicalDataSet} is a sub-class of \emph{dcat:DataSet}, 
+%i.e., each person-level data set is also a catalog data set.
+%Thus, constraints on catalog data sets are also validated for person-level data sets;
+%e.g., the \emph{existential quantification} below restricting that person-level data sets must have a distribution:
+
+%\begin{center}
+%\begin{DL} 
+%$\mathcal{K}=\{$ 
+ %&\ms{DataSet $\equiv$ $\exists$ distribution.Distribution},\\
+%&\ms{Variable $\equiv$ $\exists$ concept.Concept}
+ %\}\\ 
+%\end{DL}
+%\end{center}
+
+%We extend $\mathcal{K}$ by \emph{existential quantifications} (\emph{R-86}) enforcing that instances of given classes must have some property relation to individuals/literals of certain types.
+%Variables, e.g., should have a relation to a theoretical concept ($\mathcal{SL}_{0}$).
+%%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
+%The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
+%The default severity level of the constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
+%If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
+%If metadata on data files, including the actual data, is missing (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the study is not sufficient.
+%Case quantity measures how many cases are collected for a study.
+%High case and variable quantities are indicators for high statistical quality and comprehensiveness of the underlying study ($\mathcal{SL}_{1}$).
+
+%\begin{center}
+%\begin{DL} 
+%$\mathcal{K}=\{$ 
+  %&\ms{fundedBy $\sqsubseteq$ contributor}
+ %\}\\ 
+%\end{DL}
+%\end{center}
+%
+%By stating that \emph{disco:fundedBy} is a sub property of \emph{dcterms:contributor},
+%the {\em sub property} (\emph{R-54, R-64}) above assures that if a series is funded by an organization, then the organization must also contribute to the series.
+%In case the \emph{sub-property} is applied without reasoning and $\mathcal{K}$ contains the triple \ms{disco:fundedBy} \ms{(EU-SILC,} \ms{organization)},
+%a constraint violation is thrown if $\mathcal{K}$ does not explicitly include the triple \ms{dcterms:contributor} \ms{(EU-SILC,} \ms{organization)}.
+%If the \emph{sub property} is applied with reasoning, on the other side, the latter triple is derived which resolves the constraint violation.
+
+%\begin{DL}
+%fundedBy $\sqsubseteq$ contributor
+%\end{DL}
+
+%\emph{Asymmetric object properties} (\emph{R-62}) restrict that if individual \emph{x} is connected by the object property \emph{OP} to individual \emph{y}, then \emph{y} cannot be connected by \emph{OP} to \emph{x}.
+%Such constraints are defined for each object property for which a semantically equivalent object property pointing from the other direction would also be possible but is not defined within the vocabulary.
+%A \emph{disco:Variable}, e.g., may be based on (\emph{disco:basedOn}) a \emph{disco:RepresentedVariable}.
+%A \emph{disco:RepresentedVariable}, however, cannot be based on a \emph{disco:Variable} (\ms{$disco:basedOn \sqcap disco:basedOn^{-} \sqsubseteq \bot$}).
+
+%\emph{Property domain} (\emph{R-25, R-26}) and \emph{range} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties.
+%Only \emph{phdd:Tables}, e.g., can have \emph{phdd:isStructuredBy} relationships and
+%\emph{xkos:belongsTo} relationships can only point to \emph{skos:Concepts}:
+%\begin{DL}
+%$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table \\
+%$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept
+%\end{DL}
+
+%\begin{center}
+%\begin{DL} 
+%$\mathcal{K}=\{$ 
+  %&\ms{TableStructure $\sqsubseteq$ $\geq$1 column.Column}, \\
+	%&\ms{Variable $\sqsubseteq$ $\leq$1 concept.Concept}, \\
+	%&\ms{DataSet $\sqsubseteq$ $\geq$1 structure.DataStructureDefinition} \\ 
+	%&\ms{$\sqcap$ $\leq$1 structure.DataStructureDefinition}
+ %\}\\ 
+%\end{DL}
+%\end{center}
+
+%\textbf{Cardinality Restrictions on Properties.}
+%An \emph{existential quantification} (\emph{R-86}) contains all those individuals that are connected by a property to individuals/literals of given classes or data ranges.
+%Every \emph{qb:SliceKey}, e.g., must be associated with (\emph{qb:sliceKey}) a \emph{qb:DataStructureDefinition} (\ms{SliceKey $\sqsubseteq$ $\exists$ sliceKey$^{-}$.DataStructureDefinition}).
+%\emph{Minimum/maximum/exact qualified cardinality restrictions} (\emph{R-74, R-75, R-76}) contain all those individuals that are connected by a property to at least/at most/exactly n different individuals/literals of particular classes or data ranges.
+%A \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column},
+%a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}), and a \emph{qb:DataSet} is structured by (\emph{qb:structure}) exactly one \emph{qb:DataStructureDefinition}.
+%DATA-CUBE-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-
+%02: Unique data set (IC-1 [3]) - Every qb:Observation has (qb:dataSet) ex-
+%actly one associated qb:DataSet (Observation  ¥1 dataSet.DataSet [
+%¤1 dataSet.DataSet).
+%Severity level: ERROR
+%
+%(\emph{R-75: minimum qualified cardinality restrictions})
+%
+%DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-
+%02: Unique DSD (IC-2 [3]) - Every qb:DataSet has (qb:structure) exactly one
+%associated qb:DataStructureDefinition (DataSet  ¥1 structure.DataStructureDefinition
+%[ ¤1 structure.DataStructureDefinition).
+%Severity level: ERROR
+%
+%(\emph{R-74: exact qualified cardinality restrictions})
+%\footnote{\emph{DATA-CUBE-C-EXACT-QUALIFIED-CARDINALITY-RESTRICTIONS-02}}.
+%\textbf{Language Tag Cardinality.}
+
+%\subsection{Basic Constraint Types without Reasoning}
+%\label{basic-constraint-types-without-reasoning}
+%
+%$\overline{\mathcal{C}_B ^{\mathcal{R}}}$  denotes the set of constraint types for which reasoning cannot be done or does not improve the result in any obvious sense.
+%The constraint type \emph{vocabulary} guarantees that users do not invent new or use deprecated terms of vocabularies.
+%%Out-dated classes and properties of previous vocabulary versions can be marked as deprecated.
+%%The constraint types \emph{context-specific valid classes and properties} (\emph{R-209; R-210}) can be used to specify which classes and properties are valid in which context - here a given vocabulary version.
+%\emph{Value is valid for datatype} (\emph{R-223}) constraints serve to make sure that all literal values are valid with regard to their datatypes - as stated in the vocabularies.
+%Thus, it is checked that all date values (e.g., {{\em dcterms:date}, \em disco:startDate}, {\em disco:endDate}) are actually of the datatype \emph{xsd:date} and that \emph{xsd:nonNegativeInteger} values (e.g.
+\emph{disco:frequency}) are not negative.
+%Depending on property datatypes, two different literal values have
+%a specific ordering with respect to operators like \textless  (\emph{R-43: literal value comparison}).
+%Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}).
+%
+%\begin{center}
+%\begin{DL} 
+%$\mathcal{K}=\{$ 
+	%&\ms{isStructuredBy $\sqsubseteq$ $\neg$ column}, \\
+	%&\ms{TableDescription $\sqcap$ ColumnDescription $\sqsubseteq$ $\perp$}, \\
+	%&\ms{CategoryStatistics $\equiv$} \\
+	%&\ms{$\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString}
+ %\}\\ 
+%\end{DL}
+%\end{center}
+%
+%All properties, not having the same domain and range types, are defined to be pairwise disjoint
+%(\emph{R-9: disjoint properties}), i.e., no individual \emph{x} can be connected to an individual/literal \emph{y} by disjoint properties (e.g., \emph{phdd:isStructuredBy} and \emph{phdd:column}).
+%All \emph{PHDD} classes (e.g., \emph{phdd:TableDescription}, \emph{phdd:ColumnDescription}) are pairwise disjoint (\emph{R-7: disjoint classes}),
+%i.e., individuals cannot be instances of multiple disjoint classes.
+%It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values (\emph{R-30/37: allowed values}). 
+%%\emph{Allowed values} (\emph{R-30, R-37}) for properties can be IRIs (matching one or multiple patterns), any literals, allowed literals (e.g.
+'red' 'blue' 'green'), and typed literals of one or multiple type(s) (e.g.
+\emph{xsd:string}).
+%\emph{disco:CategoryStatistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString}.
+%Validation should \emph{exploit sub-super relations} in vocabularies (\emph{R-224}).
+%If \emph{dcterms:coverage} and one of its sub-properties (\emph{dcterms:spatial}, \emph{dcterms:temporal}) are given,
+%it is checked that \emph{dcterms:coverage} is not redundant with its sub-properties 
+%which may indicate when the data is verbose/redundant or expressed at a too general level.
+
+\subsubsection*{Simple Constraint Types.}
+
+%{Simple constraint types} is the set of constraint types whose constraints can be easily defined without much effort in addition to $\mathcal{CT}_{B}$ constraints.
+For data properties, it may be desirable to restrict that values of predefined languages must be present for determined number of times (\emph{R-48/49: language tag cardinality}):
+(1) It is checked if literal language tags are set.
+Some controlled vocabularies, e.g., contain literals in natural language, but without information what language has actually been used (\emph{warning}).
+(2) Language tags must conform to language standards (\emph{error}). 
+(3) Some thesaurus concepts are labeled in only one, others in multiple languages. 
+It may be desirable to have each concept labeled in each of the languages that are also used on the other concepts,
+as language coverage incompleteness for some concepts may indicate shortcomings of thesauri (\emph{informational})
+\cite{MaderHaslhoferIsaac2012}.
+%\textbf{Validation and Reasoning.}
+%\emph{Default values} (\emph{R-31, R-38}) for objects/literals of given properties are inferred automatically when properties are not present in the data.
+%The value \emph{true} for the property {\em disco:isPublic} indicates that a {\em disco:LogicalDataSet} can be accessed by anyone.
+%Per default, however, access to data sets should be restricted (\emph{false}) ($\mathcal{SL}_{0}$).
+%Many properties are not necessarily required but \emph{recommended} within a particular context (\emph{R-72}).
+%The property {\em skos:notation}, e.g., is not mandatory for {\em disco:Variable}s, but recommended to represent variable names ($\mathcal{SL}_{0}$).
+Percentage values are only valid when they are within the literal range of 0 and 100 (\emph{R-45: literal ranges}; \emph{error})
+which is checked for \emph{disco:percentage} standing for the number of cases of a given code in relation to the total number of cases for a particular variable.
+
+%\begin{center}
+%\begin{DL} 
+%$\mathcal{K}=\{$ 
+	%&\ms{(funct identifier$\sp{\overline{\ }})$, identifier keyfor Resource}
+ %\}\\ 
+%\end{DL}
+%\end{center}
+
+It is often useful to declare a given (data) property as the \emph{primary key} (\emph{R-226}) of a class, so that a system can enforce uniqueness and build URIs from user inputs and imported data. 
+In \emph{Disco}, resources are uniquely identified by the property \emph{adms:identifier},
+which is therefore inverse-functional $(\ms{funct identifier}\sp{\overline{\ }})$,
+i.e., for each \emph{rdfs:Resource x}, there can be at most one distinct resource \emph{y} such that \emph{y} is connected by \emph{adms:identifier$\sp{\overline{\ }}$} to \emph{x} (\emph{error}).
+%\begin{DL}
+%$(\ms{funct identifier}\sp{\overline{\ }})$
+%\end{DL} 
+Keys, however, are even more general than \emph{inverse-functional properties} (\emph{R-58}),
+as a key can be a data property, an object property, or a chain of properties \cite{Schneider2009}.
+Thus and as there are different sorts of key, and as keys can lead to undecidability, 
+\emph{DL} is extended with the construct \emph{keyfor} (\ms{identifier \ms{keyfor} Resource}) \cite{Lutz2005} which is implemented by the \emph{OWL 2} \emph{hasKey} construct.
+%\emph{OWL 2} \emph{hasKey} implements \emph{keyfor} ($\mathcal{SL}_{2}$) and thus can be used to identify resources uniquely, to merge resources with identical key property values, and to recognize constraint violations.
+%\begin{DL}
+%identifier \ms{keyfor} Resource
+%\end{DL}
+
+\subsubsection*{Complex Constraint Types.}
+\label{complex-constraint-types}
+
+%\textcolor{red}{
+%In this sub-chapter, we assign default severity levels to and describe constraints of diverse $\mathcal{CT}_{C}$ constraint types 
+%to ensure that the data is consistent with the intended syntax, semantics, and integrity of vocabularies' data models.
+%}
+%\textbf{Observations of Aggregated Data Sets.}
+%- for each dimension there should be a description and code lists.
+%- for each code list there should be a description.
+%- there should be a relationship to the underlying person-level data.
+
+%$\mathcal{CT}_{C}$ denotes the set of constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
+\emph{Data model consistency} constraints ensure the integrity of
+the data according to the intended semantics of vocabularies.
+Every \emph{qb:Observation}, e.g., must have a value for each dimension
+declared in its \emph{qb:DataStructureDefinition} (\emph{error})
+and no two \emph{qb:Observations} in the same \emph{qb:DataSet}
+can have the same value for all dimensions (\emph{warning}).
+If a \emph{qb:DataSet} \emph{D} has a \emph{qb:Slice} \emph{S}, and \emph{S} has an
+\emph{qb:Observation} \emph{O}, then the \emph{qb:DataSet} corresponding to \emph{O} must be \emph{D} (\emph{warning}).
+%Relative frequencies of variable codes are calculated correctly, if the cumulative percentage (\emph{disco:cumulativePercentage}) of a given code exactly matches the cumulative percentage of the previous code
+%plus the percentage value (\emph{disco:percentage}) of the current code ($\mathcal{SL}_{2}$).
+%{\em Mathematical Operations} (\emph{R-41, R-42}; e.g. date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
+%The sum of percentage values of all variable codes, e.g., must exactly be 100 ($\mathcal{SL}_{2}$)
+%and the minimum absolute frequency of all variable codes do not have to be greater than the maximum ($\mathcal{SL}_{2}$).
+%\textbf{Hierarchies and Ordering.}
+%\textbf{Structure and Ordering.}
+%For assessing the quality of \emph{SKOS} vocabularies, we concentrate on graph-based structures and apply graph- and network-analysis techniques (\emph{structure} constraints) like 
+%(1) a thesaurus should provide entry points (top concepts) to the data to provide efficient access and guidance for human users,
+%(2) concepts, internal to the tree, should not be indicated as top concepts, and
+%(3) a thesaurus should not contain many orphan concepts 
+%(concepts without any associative or hierarchical relations) lacking valuable context information for retrieval.
+%, as, e.g., no hierarchical query expansion can be performed on search terms to find documents with more general content.) \cite{MaderHaslhoferIsaac2012}. 
+%A very common research question is to compare variables of multiple studies or countries (constraint type: \emph{comparison}).
+%To compare variables 
+%(1) their code lists must be structured properly and
+%(2) their code lists must either be identical or at least similar.
+%If a researcher only wants to get a first overview over comparable variables (use case 1), 
+%covering the first constraint may be sufficient.
+%Thus, the severity level of the first constraint is stronger ($\mathcal{SL}_{2}$) than the one for the second constraint ($\mathcal{SL}_{0}$).
+%If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the second constraint is getting more serious
+%and the user may raise its severity level.
+%\textbf{Comparison.}
+%A very common research question is to compare variables of multiple studies or countries (constraint type: \emph{comparison}).
+%To compare variables, 
+%(1) variables and (2) variable definitions must be present,
+%(3) code lists must be structured properly,
+%(4) for each code an associated category must be specified, and
+%(5) code lists must either be identical or at least similar.
+%If a researcher wants to get a first overview over comparable variables (use case 1), 
+%covering the first three constraints may be sufficient.
+%Thus, the severity level of the first three constraints is stronger ($\mathcal{SL}_{2}$) than for the last two constraints ($\mathcal{SL}_{1}$ and $\mathcal{SL}_{0}$).
+%If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the remaining two constraints is getting more serious.
+%\textbf{Membership in Controlled Vocabularies.}
+In many cases, resources must be \emph{members of controlled vocabularies} (\emph{R-32}).
+If a dimension property, e.g., has a \emph{qb:codeList},
+then the value of the dimension property on every \emph{qb:Observation} must be in the code list (\emph{error}).
+%Summary statistics types like minimum, maximum, and arithmetic mean are maintained within a controlled vocabulary.  
+%Thus, summary statistics can only have \emph{disco:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType}, a \emph{skos:ConceptScheme} ($\mathcal{SL}_{2}$).
+Objects/literals can be declared to be ordered for given properties (\emph{R-121/217: ordering}).
+Variables, questions, and codes, e.g., are typically organized in a particular order. 
+If codes (\emph{skos:Concept}) should be ordered, they must be members (\emph{skos:memberList}) in an ordered collection (\emph{skos:OrderedCollection}), the variable's code list (\emph{informational}).
+
+%\textbf{Constraints on Properties.}
+It is useful to declare properties to be \emph{conditional} (\emph{R-71}), i.e., if particular properties exist (or do not exist), then other properties must also be present (or absent).
+To get an overview over a series/study either an abstract, a title, an alternative title, or links to external descriptions should be provided. 
+If an abstract and an external description are absent, however,  
+a title or an alternative title should be given (\emph{warning}).
+In case a variable is represented in form of a code list, codes may be associated with categories, i.e., human-readable labels (\emph{informational}).
+The variable \emph{Education at pre-school}, e.g., is represented as ordered code list without any categories.
+%If a {\em skos:Concept} represents a code (having {\em skos:notation} and {\em skos:prefLabel} properties), 
+%then the property {\em disco:isValid} has to be stated indicating if the code stands for valid (\emph{true}) or missing (\emph{false}) cases ($\mathcal{SL}_{2}$).
+\emph{Context-specific exclusive or of property groups} (\emph{R-11}) constraints
+restrict individuals of given classes to have properties defined within exactly one of multiple property groups.
+\emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes), but not both (\emph{error}).
+
+%\textbf{Constraints on Literals.}
+
+%\begin{center}
+%\begin{DL}
+%Concept $\sqsubseteq$ ($\neg$ D $\sqcap$ C) $\sqcup$ (D $\sqcap$ $\neg$ C), D $\equiv$ A $\sqcap$ B \\
+%A $\sqsubseteq$ $\geq$ 1 notation.string $\sqcap$ $\leq$ 1 notation.string \\
+%B $\sqsubseteq$ $\geq$ 1 prefLabel.string $\sqcap$ $\leq$ 1 prefLabel.string \\
+%C $\sqsubseteq$ $\geq$ 1 definition.string $\sqcap$ $\leq$ 1 definition.string \\
+%\end{DL}
+%\end{center}
+
+%\textbf{Searching for (Meta)data.}
+%
+%- DCAT
+%
+%\textbf{Data Integration.}
+%use RDF validation for data integration
+
+%\textbf{Series, Studies, Data Sets, and Data Files.}
+%It is useful to declare properties to be \emph{conditional} (\emph{R-71}), i.e., if particular properties exist (or do not exist), then other properties must also be present (or absent).
+%To get an overview over a series/study either an abstract, a title, an alternative title, or links to external descriptions should be provided. 
+%If an abstract and an external description are absent, however,  
+%a title or an alternative title should be given ($\mathcal{SL}_{1}$).
+%For datatype properties, it should be possible to declare frequently needed \emph{facets} ({\emph{R-46}) to validate input against simple conditions including min/max values, regular expressions, and string length.
+%The abstract of series/studies, e.g., should have a minimum length ($\mathcal{SL}_{1}$).
+%\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals of certain types.
+%If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
+%If metadata on data files, including the actual data, is missing (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the study is not sufficient.
+%Case quantity measures how many cases are collected for a study.
+%High case and variable quantities are indicators for high statistical quality and comprehensiveness of the underlying study ($\mathcal{SL}_{1}$).
+%
+%\textbf{Variables and Variable Comparison.}
+%Variables should be represented (\emph{R-86}; $\mathcal{SL}_{1}$) either as (un)ordered code lists or as unions of datatypes.
+%In case of a code list, associated categories (human-readable labels) may be stated (\emph{R-71}; $\mathcal{SL}_{0}$).
+%The variable \emph{Education at pre-school}, e.g., is represented as ordered code list without any categories.
+%If a {\em skos:Concept} represents a code (having {\em skos:notation} and {\em skos:prefLabel} properties), 
+%then the property {\em disco:isValid} has to be stated indicating if the code stands for valid (\emph{true}) or missing (\emph{false}) cases (\emph{R-71}; $\mathcal{SL}_{2}$).
+%Variables may have at least one relationship to a theoretical concept ({\emph{R-86}; $\mathcal{SL}_{0}$).
+%%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
+%The variable \emph{Education at pre-school},.e.g, is associated with the theoretical concept \emph{Child Care}. 
+%The default severity level of this constraint is weak, as in most cases research can be continued without associated theoretical concepts.
+%A very common research question is to compare variables of multiple studies or countries (\emph{comparison}).
+%To compare variables, 
+%(1) variables and (2) variable definitions must be present,
+%(3) code lists must be structured properly,
+%(4) for each code an associated category (human-readable label) must be specified, and
+%(5) code lists must either be identical or at least similar.
+%If a researcher wants to get a first overview over comparable variables (use case 1), 
+%covering the first three constraints may be sufficient for this purpose.
+%Thus, the severity level of the first three constraints is stronger ($\mathcal{SL}_{2}$) than the severity level of the next two constraints ($\mathcal{SL}_{1}$ and $\mathcal{SL}_{0}$).
+%If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the remaining two constraints is getting more serious.
+%
+%\textbf{Descriptive Statistics.}
+%The property \emph{disco:percentage} stands for the number of cases of a given code in relation to the total number of cases for a particular variable within a data set.
+%Percentage values are only valid when they are within the \emph{literal range} of 0 and 100 (\emph{R-45}; $\mathcal{SL}_{2}$).
+%{\em Mathematical Operations} (\emph{R-41, R-42}; e.g. date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
+%The sum of percentage values of all codes of a variable code list, e.g., must exactly be 100 ($\mathcal{SL}_{2}$)
+%and the minimum of all variable codes do not have to be greater than the maximum ($\mathcal{SL}_{2}$).
+%Codes (\emph{skos:Concept}) are ordered and therefore have fixed positions in an ordered collection (\emph{skos:OrderedCollection}) within variable representations.
+%In order to check the correctness of relative frequencies' calculations, the cumulative percentage (\emph{disco:cumulativePercentage}) of the current code must exactly be the cumulative percentage of the previous code
+%plus the percentage value (\emph{disco:percentage}) of the current code (\emph{data model consistency}; $\mathcal{SL}_{2}$).
+%
+%\textbf{Unique Identification.}
+%It is often useful to declare a given (data) property as the \emph{primary key} (\emph{R-226}) of a class, so that a system can enforce uniqueness and also automatically build URIs from user inputs and imported data.
+%In \emph{Disco}, resources are uniquely identified by the property \emph{adms:identifier},
+%which is therefore inverse-functional
+%$(\ms{funct identifier}\sp{\overline{\ }})$,
+%i.e.
+for each \emph{rdfs:Resource x}, there can be at most one distinct \emph{rdfs:Resource y} such that \emph{y} is connected by \emph{adms:identifier$\sp{\overline{\ }}$} to \emph{x} ($\mathcal{SL}_{2}$).
+%Keys, however, are even more general than inverse-functional properties (\emph{R-58}),
+%as a key can be a data, an object property, or a chain of properties \cite{Schneider2009}.
+%For this generalization purposes, as there are different sorts of key, and as keys can lead to undecidability, 
+%DL is extended with \emph{key boxes} and a special \emph{keyfor} construct (\ms{identifier \ms{keyfor} Resource}) \cite{Lutz2005}.
+%OWL 2 \emph{hasKey} implements \emph{keyfor} ($\mathcal{SL}_{2}$) and thus can be used to identify resources uniquely, to merge resources with identical key property values, and to recognize constraint violations.
+%%OWL 2 hasKey can be used to identify resources uniquely
+%%
+%%We used Protégé 5.
+%%
+%%example: owl:Thing owl:hasKey ( :hasSSN ) . :Peter :hasSSN "123-45-6789" .
+%%:Peter_Griffin :hasSSN "123-45-6789" .
+%%
+%%We use the predefined Reasoner HermiT.
+%%
+%%:Peter and :Peter_Griffin are derived as identical from the reasoner as they have the same value for :hasSSN.
+%%
+%%hasKey can be used to merge resources and to recognize constraint violations.
+%%
+%%Alternative to OWL 2 hasKey: concise bounded description (proposal of Dan)
+%%
+%%action: explore CBD document solution might be using both approaches
+%%
+%%benefit: additional identification to URI / IRI benefit: compound properties can be used as key
+%
+%
+%\textbf{Membership in Controlled Vocabularies.}
+%In many cases, resources must be members of controlled vocabularies (\emph{R-32}).
+%If a dimension property, e.g., has a \emph{qb:codeList},
+%then the value of the dimension property on every \emph{qb:Observation} must be in the code list ($\mathcal{SL}_{2}$).
+%Summary statistics types like minimum, maximum, and arithmetic mean are maintained within a controlled vocabulary.  
+%Summary statistics can only have \emph{disco:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType}, a \emph{skos:ConceptScheme} ($\mathcal{SL}_{2}$).
+%
+%%\begin{center}
+%%\begin{DL}
+%%SummaryStatistics $\sqsubseteq$ $\forall summaryStatisticType.A$ \\
+%%$A \equiv Concept \sqcap \forall inScheme . B$ \\
+%%$B \equiv ConceptScheme \sqcap \{SummaryStatisticType\}$
+%%\end{DL}
+%%\end{center}
+%
+%\textbf{Coverage.}
+%Information about the temporal (\emph{dcterms:temporal}), the spatial (\emph{dcterms:spatial}), and the topical coverage (\emph{dcterms:subject}) of series, studies, data sets, and data files (\emph{R-86}; $\mathcal{SL}_{1}$) is of interest when performing frequently formulated queries
+	%(e.g. to search for all data sets of given years (temporal coverage) in which data is collected in certain countries (spatial coverage) about particular topics (topical coverage)).
+%Depending on property datatypes,
+%two different literal values have
+%a specific ordering with respect to an operator like \textless (\emph{R-43: literal value comparison}).
+%Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}) ($\mathcal{SL}_{2}$).
+%
+%%\textbf{Organizations, Hierarchies, Classifications, and Ordering.}
+%\textbf{Hierarchies and Ordering.}
+%SKOS is based on RDF, which is a graph-based data model.
+Therefore, we can concentrate on the vocabulary's graph-based structure for assessing the quality of SKOS vocabularies and apply graph- and network-analysis techniques (\emph{structure}) like
+%(1) a vocabulary should provide entry points (top concepts) to the data to provide efficient access and guidance for human users,
+%(2) concepts, internal to the tree, should not be indicated as top concepts, and
+%(3) a vocabulary should not contain many orphan concepts 
+%(concepts without any associative or hierarchical relations) lacking valuable context information.
+A controlled vocabulary that contains many orphan concepts is less usable for search and retrieval use cases.
+%%, as, e.g., no hierarchical query expansion can be performed on search terms to find documents with more general content.) \cite{MaderHaslhoferIsaac2012}. 
+%Objects and literals can be \emph{ordered} (\emph{R-121, R-217}) for given properties.
+%\emph{Disco }variables, questions, and codes/categories are typically organized in a particular order. 
+%If a variable code list should be ordered, the variable representation should be of the type \emph{skos:OrderedCollection} containing multiple codes/categories (each represented as \emph{skos:Concept}) in a \emph{skos:memberList}.
+%
+%\textbf{Reusability.}
+%Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes/categories), but not both ($\mathcal{SL}_{2}$).
+%The constraint type \emph{context-specific exclusive or of property groups} (\emph{R-11})
+%restricts individuals of given classes to have exactly one of multiple property groups.
+
+\section{Evaluation}
+\label{evaluation}
+
+In this section, we describe our findings based on an automatic constraint checking of a large dataset.
+Despite the large volume of the dataset in general, we have to keep in mind that this study only uses data for three vocabularies.
+As described in Section~\ref{rdf-representation}, for other vocabularies there is often not (yet) enough data openly available to draw general conclusions.
+The three vocabularies, however, are representative, cover different aspects of SBE data and are also a mixture of established vocabularies (\emph{QB}, \emph{SKOS}) and a vocabulary under development (\emph{Disco}).
+Due to this limitation, we will present several hypotheses together with a rationale based on the results for the three vocabularies.
+If the hypotheses hold generally is still to be determined, nevertheless they should provide valuable insights for future developments of constraint languages.
+
+\subsection{Experimental Setup}
+\label{implementation}
+
+%\ke{Überarbeiten und mit nächstem teil mergen. Nur das erzählen, was für die Auswertung auf den Datensets relevant ist. 114 constraints, 3 vokabulare, wie wurden die datasets daraufhin validiert.}
+
+	%\item First, we assigned each constraint type to exactly one of the disjoint sets of constraint types 
+%in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$).
+On the three vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}), we identified and classified 213 constraints of which we implemented for the data validation 114 constraints.\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} The reason is simply that more time is needed for the remaining implementation.
+We ensured, however, that the implementation is equally distributed over the classes and vocabularies we have.
+We then evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data using these 114 constraints, obtained from 33 SPARQL endpoints.
+
+\emph{QB} and \emph{SKOS} are well-established vocabularies which are widely adopted and accepted. \emph{Disco} is a newly developed vocabulary which will be published in 2015.
+
+%It is likely that such a vocabulary is still subject of constant change, that published data may not be consistent with its current version,
+%and that early adopters did not properly understand its formal specification.
+%\ke{ergebnisse, dann hypothesen, dann kritische auseinandersetzung}
+
+Table~\ref{tab:datasets} lists the number of datasets and the overall sizes in terms of triples for each of the vocabularies. We validated, i.a., 
+(1) \emph{QB} data sets published by the \emph{Australian Bureau of Statistics},
+the \emph{European Central Bank}, and the
+\emph{Organisation for Economic Co-operation and Development},
+(2) \emph{SKOS} thesauri like the \emph{AGROVOC Multilingual agricultural thesaurus},
+the \emph{STW Thesaurus for Economics}, and the
+\emph{Thesaurus for the Social Sciences}, and
+(3) \emph{Disco} data sets provided by the \emph{Microdata Information System}, 
+the \emph{Data Without Boundaries Discovery Portal}, the
+\emph{Danish Data Archive}, and the
+\emph{Swedish National Data Service}.
+
+\begin{table}[H]
+		\scriptsize
+    \begin{center}
+    \begin{tabular}{lrr}
+%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
+%    \\  \cmidrule{2-7}
+           \textbf{Vocabulary}
+           & \textbf{Datasets}
+           & \textbf{Triples}
+
+    \\ \midrule
+		%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
+		%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
+		%\hline
+		\textbf{\emph{QB}} & $9,990$   & $3,775,983,610$  \\
+		\textbf{\emph{SKOS}} & $4,178$  & $477,737,281$ \\
+		\textbf{\emph{Disco}} & $1,526$  & $9,673,055$  \\
+    \bottomrule
+    \end{tabular}
+    %\\ \emph{C (constraints), CT (constraint types)}
+    \caption{Evaluated datasets for each vocabulary}
+		\label{tab:datasets}
+    \end{center}
+\end{table}
+
+In a technical report serving as third appendix of this paper, we describe the evaluation in further detail \cite{BoschZapilkoWackerowEckert2015-2}.
+Furthermore, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.
+
+We use \emph{SPIN}, 
+a \emph{SPARQL}-based way to formulate and check constraints, as basis to develop a
+validation environment\footnote{Online demo available at \url{http://purl.org/net/rdfval-demo}, source code at: \url{https://github.com/boschthomas/rdf-validator}} to validate RDF data according to constraints expressed by arbitrary constraint languages\footnote{SPIN mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} \cite{BoschEckert2014-2}.
+
+The \emph{RDF Validator} can directly be used to validate arbitrary RDF data for the three vocabularies.
+Additionally, own constraints on vocabularies can be defined using several constraint languages.
+
+%Although accessible within our validation tool, we provide all implemented constraints\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} in form of SPARQL CONSTRUCT queries.
+The \emph{SPIN} engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.
+There is one \emph{SPIN} construct template for each constraint type.
+A \emph{SPIN} construct template contains a \emph{SPARQL CONSTRUCT} query which generates constraint violation triples indicating the subject and the properties causing constraint violations, and the reason why constraint violations have been raised.
+A \emph{SPIN} construct template creates constraint violation triples if all triple patterns within the \emph{SPARQL WHERE clause} match.
+%\emph{Missy}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}} provides comprehensive Linked Data services like diverse RDF exports of person-level metadata conforming to the \emph{Disco} vocabulary in form of multiple concrete syntaxes.
+
+\subsection{Evaluation Results and Formulation of Hypotheses}
+
+%DCAT: 11 constraints defined
+%PHDD: 12
+%XKOS: 10
+
+%The majority (48 $\equiv$ 58.5\%) of the overall 82 $\mathcal{CT}$ constraint types are $\mathcal{CT}_{B}$ whose constraints can therefore be derived from vocabularies without any effort.
+%Among $\mathcal{CT}_{B}$, two-thirds (34 $\equiv$ 70.8\%) are $\mathcal{C}_B ^{\mathcal{R}}$, i.e., constraint types for which reasoning may be performed prior to validation, and one third (14 $\equiv$ 29.2\%) are $\overline{\mathcal{C}_B ^{\mathcal{R}}}$, i.e., constraint types for which reasoning does not make any sense.
+%A quarter (20 $\equiv$ 24.4\%) of all constraint types are $\mathcal{CT}_{S}$ and a sixth (14 $\equiv$ 17.1\%) are $\mathcal{CT}_{C}$.
+%
+%\begin{table}[H]
+		%\scriptsize
+    %\begin{center}
+    %\begin{tabular}{@{}lcccc@{}}
+%%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
+%%    \\  \cmidrule{2-7}
+    %\\       \textbf{Criteria}
+           %& \textbf{\emph{Disco}}
+           %& \textbf{\emph{QB}}
+					 %& \textbf{\emph{SKOS}}
+					 %& \textbf{Total}
+    %\\ \midrule
+		%%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
+		%%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
+		%%\hline
+		%\emph{CT} & 52 & 20 & 15 & 53 \\
+		%\hline
+		%$\mathcal{CT}_{C}$ & 9 (17.3\%) & 2 (10\%) & 2 (13.3\%) & 9 (17\%) \\
+		%$\mathcal{CT}_{S}$ & 16 (30.8\%) & 3 (15\%) & 4 (26,7\%) & 16 (30.2\%) \\
+		%$\mathcal{CT}_{B}$ & 27 (\textbf{51.9\%}) & 15 (\textbf{75\%}) & 9 (\textbf{60\%}) & 28 (\textbf{52.8\%}) \\
+		%\hline
+		%$\mathcal{C}_B ^{\mathcal{R}}$ & 18 (34.6\%) & 9 (45\%) & 4 (26.7\%) & 19 (35.9\%) \\
+		%$\overline{\mathcal{C}_B ^{\mathcal{R}}}$ & 9 (17.3\%) & 6 (30\%) & 5 (33.3\%) & 9 (17\%) \\
+    %\bottomrule
+    %\end{tabular}
+    %%\\ \emph{C (constraints), CT (constraint types)}
+    %\caption{Evaluation - Constraint Types}
+		%\label{tab:evaluation-constraint-types}
+    %\end{center}
+%\end{table}
+
+%Table \ref{tab:evaluation-constraint-types} displays the evaluation of the metadata quality on real world data sets regarding constraint types.
+Table \ref{tab:evaluation-constraint-violations} shows the results of the evaluation, more specifically the constraints and the constraint violations, which are caused by these constraints, in percent.
+The constraints and their raised constraint violations are grouped by vocabulary, complexity level of their type, and their severity level.
+The numbers of evaluated triples and data sets differ between the vocabularies
+as we evaluated 3.8 billion \emph{QB}, 480 million \emph{SKOS}, and 10 million \emph{Disco} triples.
+To be able to formulate hypotheses which apply for all vocabularies, 
+we only use normalized relative values representing the percentage of constraints and constraint violations belonging to the respective class
+
+%by building the arithmetic mean over the individual vocabularies' percentage values. 
+%\tb{More than 80\% of the overall approx. 55 million constraint violations are caused by \emph{QB} constraints.}
+
+\begin{table}[H]
+		\scriptsize
+    \begin{center}
+    \begin{tabular}{@{}lcccccccc@{}}
+    %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
+    %\\  \cmidrule{2-3}
+		\hline
+    \multirow{2}{*}{} &
+      \multicolumn{2}{c}{\textbf{\emph{Disco}}} &
+      \multicolumn{2}{c}{\textbf{\emph{QB}}} &
+      \multicolumn{2}{c}{\textbf{\emph{SKOS}}} &
+      \multicolumn{2}{c}{\textbf{\emph{Total}}} \\
+    \textbf{} & C & CV & C & CV & C & CV & C & CV \\
+    \hline
+    %\\ \midrule
+		 & 143 & 3,575,002 & 35 & 45,635,861 & 35 & 5,540,988 & 213 & 54,751,851 \\
+		\hline
+		\textbf{\emph{complex}} & 25.9\% & 18.3\% & 37.1\% & \textbf{100.0\%} & \textbf{37.1\%} & 21.4\% & 33.4\% & \textbf{46.6\%} \\
+		\textbf{\emph{simple}} & 19.6\% & 15.7\% & 8.6\% & 0.0\% & \textbf{34.3\%} & \textbf{78.6\%} & 20.8\% & 31.4\% \\
+		\textbf{\emph{vocabulary}} & \textbf{54.6\%} & \textbf{66.1\%} & \textbf{54.3\%} & 0.0\% & \textbf{28.6\%} & 0.0\% & \textbf{45.8\%} & 22.0\% \\
+		%\hline
+		%\emph{CV (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 2,333,365 (65.3\%) & 1,777 (0\%) & 0 (0\%) & 2,335,142 (4.3\%) \\
+		%\emph{CV (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 28,000 (0.8\%) & 0 (0\%) & 0 (0\%) & 28,000 (0.1\%) \\
+		\hline
+		\textbf{\emph{info}} & \textbf{52.5\%} & \textbf{52.6\%} & 11.4\% & 0.0\% & \textbf{60.0\%} & 41.2\% & \textbf{41.3\%} & 31.3\% \\
+		\textbf{\emph{warning}} & 7.0\% & 29.4\% & 8.6\% & \textbf{99.8\%} & 14.3\% & \textbf{58.8\%} & 10.0\% & \textbf{62.7\%} \\
+		\textbf{\emph{error}} & 40.6\% & 18.0\% & \textbf{80.0\%} & 0.3\% & 25.7\% & 0.0\% & \textbf{48.8\%} & 6.1\%\\
+    \bottomrule
+    \end{tabular}
+    \\ \emph{C (constraints), CV (constraint violations)}
+    \caption{Constraints and constraint violations}
+		\label{tab:evaluation-constraint-violations}
+    \end{center}
+\end{table}
+
+As the evaluation is based on three vocabularies, 
+we cannot make valid general statements for all vocabularies,
+but we can formulate several hypotheses to direct the further development of constraint languages.
+As these hypotheses cannot be proved yet, 
+they still have to be verified or falsified
+by evaluating the quality of data represented by further well-established and newly developed vocabularies.
+%More than the half of them are $\mathcal{CT}_{B}$, nearly a third $\mathcal{CT}_{S}$, and only a sixth $\mathcal{CT}_{C}$ constraint types.
+%For \emph{Disco}, \emph{QB}, and \emph{SKOS}, more than 50\% of the instantiated constraint types are $\mathcal{CT}_{B}$ constraint types 
+%(for \emph{QB} even three quarters).
+%\emph{Existential quantifications} (\emph{R-86}, 32.4\%, \emph{Disco}), \emph{data model consistency} (31.4\%, \emph{QB}), and \emph{structure} (28.6\%, \emph{SKOS}) are the constraint types the most constraints are instantiated from.
+%\tb{1. Fakten (diese Fakten bewirken eine Erhöhung der Datenqualität) 2. Hypothese (unsere Interpretation der Ergebnisse, unsere Behauptung)}
+Almost 1/2 of all constraints and more than 1/2 of the \emph{Disco} and the \emph{QB} constraints are \emph{vocabulary constraints}.
+The \emph{SKOS} constraints are nearly to the same extend \emph{vocabulary}, \emph{simple}, and \emph{complex constraints}. 
+%Hence, a significant amount of 46 \% of the constraints are directly extractable from formal specifications of well-established and newly defined vocabularies. 
+\begin{hyp}
+%As a significant amount of 46 \% of the constraints are vocabulary constraints which can be expressed by modeling languages like RDF, RDFS, and OWL 2,
+%the further development of constraint languages should concentrate on expressing simple and especially complex constraints which up to now in most cases can only be expressed by plain SPARQL.   
+As a significant amount of 54\% of the constraints are either simple or complex constraints,
+the further development of constraint languages should concentrate on expressing simple and especially complex constraints which up to now in most cases can only be expressed by plain SPARQL.  
+\end{hyp}
+
+Nearly 1/2 of all violations are caused by \emph{complex constraints}, 1/3 by \emph{simple constraints}, and 1/5 by \emph{vocabulary constraints}.
+The fact that only 1/5 of all violations result from \emph{vocabulary constraints}, 
+even though, 46\% of all constraints are \emph{vocabulary constraints},
+indicates good data quality for all vocabularies with regard to their formal specifications.
+
+%\tb{je nach hypothese spezifische aufgaben um die hypothese zu beweisen}
+Moreover, while 2/3 of the \emph{Disco} violations result from \emph{vocabulary constraints},
+\emph{QB} violations are almost only raised by \emph{complex constraints}, and 
+nearly 80\% of the \emph{SKOS} violations are caused by \emph{simple constraints}.
+This means that for the well-established vocabularies \emph{QB} and \emph{SKOS}, \emph{vocabulary constraints} are almost completely satisfied which indicates generally a very impressive data quality, at least in the SBE domain and for the basic requirements.
+%This demonstrates that data providers take account of the formal specifications of well-established vocabularies.
+
+For \emph{Disco}, data providers still have to understand the vocabulary and of course, data can not have high quality if the specification is not yet stable.
+
+\begin{hyp}
+Data corresponds to their formal specifications which demonstrates that constraint formulation in general works. 
+\end{hyp}
+
+It is likely that a newly developed vocabulary is still subject of constant change
+and that early adopters did not properly understand its formal specification.
+Thus, published data may not be consistent with its current draft or version.
+In case newly developed vocabularies turn into well-established ones,
+data providers are experienced in publishing their data in conformance with these vocabularies
+and formal specifications are more elaborated. 
+As a consequence, \emph{vocabulary constraints} are satisfied to a greater extend which leads to better data quality.
+
+\begin{hyp}
+A significant amount of 47\% of the violations refer to complex constraints that are not easily, concisely, and intuitively expressible by existing constraint languages which confirms the necessity to provide suitable constraint languages.
+\end{hyp}
+
+In general, \emph{vocabulary constraints} are expressible by either modeling languages (e.g., \emph{RDF}, \emph{RDFS}, \emph{OWL 2}) or constraint languages. 
+\emph{Simple constraints} and especially \emph{complex constraints}, however, are in most cases only expressible by plain \emph{SPARQL}. 
+As almost 1/2 of all violations are caused by \emph{complex constraints}, 
+data quality can be significantly improved when suitable constraint languages are developed which enable to define \emph{complex constraints} in an easy, concise, and intuitive way.
+%Therefore, existing constraint languages have to be extended or new constraint languages have to be developed.
+1/2 of all constraints are \emph{error constraints} and
+10\% of all constraints are \emph{warning constraints}.
+\emph{Informational constraints} caused 1/3 and
+\emph{warning constraints} 2/3 of all violations.
+As the percentage of severe violations is very low for all vocabularies (6.1\%),
+data quality is high with regard to the severity level of constraints.
+
+\begin{hyp}
+The percentage of severe violations is very low, compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
+\end{hyp}
+
+80\% of the \emph{QB} constraints are \emph{error constraints}.
+More than 50\% of the \emph{Disco} and \emph{SKOS} constraints, however, are \emph{informational constraints}.
+1/6 of the Disco violations are caused by \emph{error constraints} and
+almost all \emph{QB} violations and 59\% of the \emph{SKOS} violations are caused by \emph{warning constraints}.  
+For well-established vocabularies, data quality is high
+as serious violations rarely appear.
+For newly developed vocabularies, data quality is worse
+as serious violations occur partially.
+%Constraints are serious when they violate the integrity of vocabularies.
+%For well-established vocabularies, it is well documented and the experience is high how to guarantee this integrity
+%which is not the case or newly-developed vocabularies.
+\begin{hyp}
+Especially for newly developed vocabularies, constraint languages should be used to a larger extend to meet reduce severe violations.   
+\end{hyp}
+
+%For the vocabularies \emph{Disco}, \emph{QB}, and \emph{SKOS}, we defined 213 constraints of 53 constraint types .
+
+%\begin{table}[H]
+		%\scriptsize
+    %\begin{center}
+    %\begin{tabular}{@{}lcccc@{}}
+%%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
+%%    \\  \cmidrule{2-7}
+    %\\       \textbf{Criteria}
+           %& \textbf{\emph{Disco}}
+           %& \textbf{\emph{QB}}
+					 %& \textbf{\emph{SKOS}}
+					 %& \textbf{Total}
+    %\\ \midrule
+		%%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
+		%%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
+		%%\hline
+		%\emph{C} & 143 (67.1\%) & 35 (16.4\%) & 35 (16.4\%) & 213 \\
+		%\hline
+		%\emph{C (}$\mathcal{CT}_{C}$\emph{)} & 37 (25.9\%) & 13 (37.1\%) & 13 (\textbf{37.1\%}) & 63 (29.6\%) \\
+		%\emph{C (}$\mathcal{CT}_{S}$\emph{)} & 28 (19.6\%) & 3 (8.6\%) & 12 (\textbf{34.3\%}) & 43 (20.2\%) \\
+		%\emph{C (}$\mathcal{CT}_{B}$\emph{)} & 78 (\textbf{54.6\%}) & 19 (\textbf{54.3\%}) & 10 (\textbf{28.6\%}) & 107 (\textbf{50.2\%}) \\
+		%%\hline
+		%%\emph{C (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 67 (46.9\%) & 13 (37.1\%) & 4 (11.4\%) & 84 (39.4\%) \\
+		%%\emph{C (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 11 (7.7\%) & 6 (17.1\%) & 6 (17.1\%) & 23 (10.8\%) \\
+		%\hline
+		%\emph{C ($\mathcal{SL}_{0}$)} & 75 (\textbf{52.5\%}) & 4 (11.4\%) & 21 (\textbf{60\%}) & 100 (\textbf{46.9\%}) \\
+		%\emph{C ($\mathcal{SL}_{1}$)} & 10 (7\%) & 3 (8.6\%) & 5 (14.3\%) & 18 (8.5\%) \\
+		%\emph{C ($\mathcal{SL}_{2}$)} & 58 (40.6\%) & 28 (\textbf{80\%}) & 9 (25.7\%) & 95 (\textbf{44.6\%}) \\
+    %\bottomrule
+    %\end{tabular}
+    %%\\ \emph{C (constraints), CT (constraint types)}
+    %\caption{Evaluation - Constraints}
+		%\label{tab:evaluation-constraints}
+    %\end{center}
+%\end{table}
+
+%\begin{table}[H]
+		%\scriptsize
+    %\begin{center}
+    %\begin{tabular}{@{}lcccccccc@{}}
+%%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
+%%    \\  \cmidrule{2-7}
+    %\\       \textbf{}
+           %& \textbf{\emph{Disco}}
+           %& \textbf{\emph{QB}}
+					 %& \textbf{\emph{SKOS}}
+					 %& \textbf{Total}
+					 %& \textbf{\emph{Disco}}
+           %& \textbf{\emph{QB}}
+					 %& \textbf{\emph{SKOS}}
+					 %& \textbf{Total}
+    %\\ \midrule
+		 %& 3,575,002 & 45,635,861 & 5,540,988 & 54,751,851 & & & &  \\
+		%\hline
+		%\textbf{\emph{complex}} & 18.3\% & \textbf{100\%} & 21.4\% & \textbf{86.7\%} & & & & \\
+		%\textbf{\emph{simple}} & 15.7\% & 0.0\% & \textbf{78.6\%} & 9\% & & & & \\
+		%\textbf{\emph{vocabulary}} & \textbf{66.1\%} & 0.0\% & 0\% & 4.3\% & & & & \\
+		%%\hline
+		%%\emph{CV (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 2,333,365 (65.3\%) & 1,777 (0\%) & 0 (0\%) & 2,335,142 (4.3\%) \\
+		%%\emph{CV (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 28,000 (0.8\%) & 0 (0\%) & 0 (0\%) & 28,000 (0.1\%) \\
+		%\hline
+		%\textbf{\emph{info}} & \textbf{52.6\%} & 0.0\% & 41.2\% & 7.6\% & & & & \\
+		%\textbf{\emph{warning}} & 29.4\% & \textbf{99,8\%} & \textbf{58.8\%} & \textbf{91\%} & & & & \\
+		%\textbf{\emph{error}} & 18\% & 0.3\% & 0.0\% & 1.4\% & & & & \\
+    %\bottomrule
+    %\end{tabular}
+    %%\\ \emph{CV (constraint violations)}
+    %\caption{Constraint Violations}
+		%\label{tab:evaluation-constraint-violations}
+    %\end{center}
+%\end{table}
+
+%The constraints responsible for the largest amounts of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916; \emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102; \emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903; \emph{SKOS}).
+
+Table \ref{tab:evaluation-complexity-severity} shows the relation between the complexity and the severity level of all 213 constraints.
+More than 1/2 of the \emph{vocabulary constraints} are \emph{error constraints},
+more than 3/4 of the \emph{simple constraints} are \emph{informational constraints}, and
+\emph{complex constraints} are to the same extend \emph{informational} or \emph{error constraints}.
+
+\begin{table}[H]
+		\scriptsize
+    \begin{center}
+    \begin{tabular}{@{}lcccc@{}}
+%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
+%    \\  \cmidrule{2-7}
+    \\       \textbf{}
+           & \textbf{\emph{vocabulary}}
+           & \textbf{\emph{simple}}
+					 & \textbf{\emph{complex}}
+    \\ \midrule
+		%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
+		%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
+		%\hline
+		\textbf{\emph{info}} & 38.7 \% & \textbf{76.2 \%} & \textbf{42.3 \%} \\
+		\textbf{\emph{warning}} & 6.7 \% & 7.1 \% & 13.5 \% \\
+		\textbf{\emph{error}} & \textbf{54.6 \%} & 16.7 \% & \textbf{44.2 \%} \\
+    \bottomrule
+    \end{tabular}
+    %\\ \emph{C (constraints), CT (constraint types)}
+    \caption{Relation between complexity and severity level of constraints}
+		\label{tab:evaluation-complexity-severity}
+    \end{center}
+\end{table}
+
+\begin{hyp}
+There is significant demand for constraint languages that support the expression of complex constraints as 44\% of all complex constraints are also serious ones.
+\end{hyp}
+
+As \emph{vocabulary constraints} are part of formal specifications of vocabularies,
+violations of \emph{vocabulary constraints} are more severe than violations caused by \emph{simple constraints}.
+As \emph{SPARQL} is still used to express \emph{complex constraints} and as 44\% of all \emph{complex constraints} are serious,
+there is an obvious need to develop constraint languages which enable to express \emph{complex constraints}.
+
+\section{Conclusion and Future Work}
+
+%In this paper, we showed in form of a complete real world running example how to represent metadata on person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
+%We explained why RDF validation is important in this context and how metadata on person-level data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality\footnote{The first appendix of this paper describing each constraint in detail is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}} (\textbf{contribution 2}, section \ref{rdf-validation}).
+%We distinguish two validation types:
+%(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of data models (section \ref{complex-constraint-types}).
+%(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges (section \ref{vocabulary-constraint-types}).
+%We determined the default \emph{severity level} for each constraint to indicate how serious the violation of the constraint is
+%and propose an extensible metric to measure the continuum of severity levels.
+
+%We implemented a validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages and to ensure correct syntax and semantics of diverse vocabularies such as \emph{Disco}, \emph{QB}, \emph{SKOS}, and \emph{PHDD} (section \ref{implementation}).
+%We exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets (more than 4.2 billion triples and 15 thousand data sets) by means of 213  constraints of the majority of the constraint types\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).
+
+We identified and published by today 82 types of constraints  that are required by various stakeholders for data applications.
+In close collaboration with several \emph{SBE} domain experts, we formulated 213 constraints of 53 different types on three different vocabularies (\emph{Disco}, \emph{QB}, and \emph{SKOS}) and classified them according to the complexity level of their type and their severity level.
+
+For 114 of these constraints, we evaluated  the data quality of 15,694 data sets (4.26 billion triples) of research data for the \emph{SBE} sciences obtained from 33 SPARQL endpoints.
+
+Based on the evaluation results,
+we formulated several hypotheses to direct the further development of constraint languages.
+We regard to the results as hypotheses, as their general applicability beyond the examined vocabularies and for other domains is still to be confirmed.
+
+The main hypotheses are: 
+\begin{enumerate}
+	\item The percentage of severe violations is very low which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
+  \item The further development of constraint languages should concentrate on how to express \emph{complex constraints} as 44\% of all \emph{complex constraints} are also serious ones.
+  \item 47\% of the violations refer to complex constraints that are in most cases not expressible by existing constraint languages which confirms the necessity to provide suitable constraint languages.
+  \item As 54\% of the constraints are either \emph{simple} or \emph{complex constraints},
+the further development of constraint languages should concentrate on expressing \emph{simple} and especially \emph{complex constraints} which up to now in most cases can only be expressed by plain \emph{SPARQL}.
+\end{enumerate}
+
+We have been really impressed by the high quality of the \emph{QB} and \emph{SKOS} data.
+This is in contrast to the sometimes heard rumour that Linked Open Data lacks quality.
+We are actively involved in the further development and implementation of constraint languages and will use the results presented in the paper to set priorities on features where we expect the highest impact on the data quality of real-life data in the SBE domain.
 
@@
 
-\section{Conclusion}
-The conclusion goes here.
-
 % conference papers do not normally have an appendix
@@
 % use section* for acknowledgement
-\section*{Acknowledgment}
-
-The authors would like to thank...
+%\section*{Acknowledgment}
 
@@
 % http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
+\bibliographystyle{IEEEtran}
 % argument is your BibTeX string definitions and bibliography database(s)
 %\bibliography{IEEEabrv,../bib/paper}
+\bibliography{../../literature/literature}{}
 %
@@
 % (used to reserve space for the reference number labels box)
-\begin{thebibliography}{1}
-
-\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
-\end{thebibliography}
+%\begin{thebibliography}{1}
+%
+%\bibitem{IEEEhowto:kopka}
+%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
+  %0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+%
+%\end{thebibliography}
 

### 2015-07-13 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
paper template

@@
 SELECT ?study WHERE {
-    ?study dcterms:abstract ?abstract . FILTER ( STRLEN ( ?abstract ) = 10 ) . }
+    ?study dcterms:abstract ?abstract . 
+    FILTER ( STRLEN ( ?abstract ) = 10 ) . }
 \end{ex}
@@
     FILTER NOT EXISTS { ?concept ?p ?o . 
-        FILTER ( ?p IN ( skos:related, skos:relatedMatch, skos:broader, ... ) ) . }
+        FILTER ( ?p IN ( skos:related, skos:relatedMatch, 
+                         skos:broader, ... ) ) . }
 \end{ex}
@@
 	%&\ms{TableDescription $\sqcap$ ColumnDescription $\sqsubseteq$ $\perp$}, \\
-	&\ms{CategoryStatistics $\equiv$ $\forall$ computationBase.\{valid,invalid\} $\sqcap$ langString}, \\
-  &\ms{Variable $\equiv$ $\exists$ concept.Concept, Catalog $\sqsubseteq$ $\forall$ dataset.Dataset}, \\
-  &\ms{$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table, $\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}
+&{\small\ms{CategoryStatistics $\equiv$ $\forall$ computationBase.}} \\
+	&{\small\ms{    \{valid,invalid\} $\sqcap$ langString,}} \\
+  &{\small\ms{Variable $\equiv$ $\exists$ concept.Concept,}} \\
+	&{\small\ms{Catalog $\sqsubseteq$ $\forall$ dataset.Dataset,}} \\
+  &{\small\ms{$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table,}} \\
+	&{\small\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}}
 \}\\ 
@@
 In \emph{Disco}, resources are uniquely identified by the property \emph{adms:identifier},
-which is therefore inverse-functional $(\ms{funct identifier}\sp{\overline{\ }})$,
+which is therefore inverse-functional $({\small\ms{funct identifier}\sp{\overline{\ }}})$,
 i.e., for each \emph{rdfs:Resource x}, there can be at most one distinct resource \emph{y} such that \emph{y} is connected by \emph{adms:identifier$\sp{\overline{\ }}$} to \emph{x} (\emph{error}).
@@
 Thus and as there are different sorts of key, and as keys can lead to undecidability, 
-\emph{DL} is extended with the construct \emph{keyfor} (\ms{identifier \ms{keyfor} Resource}) \cite{Lutz2005} which is implemented by the \emph{OWL 2} \emph{hasKey} construct.
+\emph{DL} is extended with the construct \emph{keyfor} ({\small\ms{identifier \ms{keyfor} Resource}}) \cite{Lutz2005} which is implemented by the \emph{OWL 2} \emph{hasKey} construct.
 %\emph{OWL 2} \emph{hasKey} implements \emph{keyfor} ($\mathcal{SL}_{2}$) and thus can be used to identify resources uniquely, to merge resources with identical key property values, and to recognize constraint violations.
@@
 
-In this section, we describe our findings based on an automatic constraint checking of a large dataset.
-Despite the large volume of the dataset in general, we have to keep in mind that this study only uses data for three vocabularies.
+In this section, we describe our findings based on an automatic constraint checking of a large data set.
+Despite the large volume of the data set in general, we have to keep in mind that this study only uses data for three vocabularies.
 As described in Section~\ref{rdf-representation}, for other vocabularies there is often not (yet) enough data openly available to draw general conclusions.
@@
 
-Table~\ref{tab:datasets} lists the number of datasets and the overall sizes in terms of triples for each of the vocabularies. We validated, i.a., 
+Table~\ref{tab:datasets} lists the number of data sets and the overall sizes in terms of triples for each of the vocabularies. We validated, i.a., 
 (1) \emph{QB} data sets published by the \emph{Australian Bureau of Statistics},
@@
     \begin{center}
+		\caption{Evaluated Data Sets for each Vocabulary}
+		\label{tab:datasets}
     \begin{tabular}{lrr}
@@
            \textbf{Vocabulary}
-           & \textbf{Datasets}
+           & \textbf{Data Sets}
            & \textbf{Triples}
@@
     %\\ \emph{C (constraints), CT (constraint types)}
-    \caption{Evaluated datasets for each vocabulary}
-		\label{tab:datasets}
     \end{center}
@@
 
+%\begin{table}[H]
+		%\scriptsize
+    %\begin{center}
+		%\caption{Constraints and Constraint Violations}
+		%\label{tab:evaluation-constraint-violations}
+    %\begin{tabular}{@{}lcccccccc@{}}
+    %%       & \multicolumn{2}{c}{\textbf{Vocabularies}}
+    %%\\  \cmidrule{2-3}
+		%\hline
+    %\multirow{2}{*}{} &
+      %\multicolumn{2}{c}{\textbf{\emph{Disco}}} &
+      %\multicolumn{2}{c}{\textbf{\emph{QB}}} &
+      %\multicolumn{2}{c}{\textbf{\emph{SKOS}}} &
+      %\multicolumn{2}{c}{\textbf{\emph{Total}}} \\
+    %\textbf{} & C & CV & C & CV & C & CV & C & CV \\
+    %\hline
+    %%\\ \midrule
+		 %& 143 & 3,575,002 & 35 & 45,635,861 & 35 & 5,540,988 & 213 & 54,751,851 \\
+		%\hline
+		%\textbf{\emph{complex}} & 25.9\% & 18.3\% & 37.1\% & \textbf{100.0\%} & \textbf{37.1\%} & 21.4\% & 33.4\% & \textbf{46.6\%} \\
+		%\textbf{\emph{simple}} & 19.6\% & 15.7\% & 8.6\% & 0.0\% & \textbf{34.3\%} & \textbf{78.6\%} & 20.8\% & 31.4\% \\
+		%\textbf{\emph{vocabulary}} & \textbf{54.6\%} & \textbf{66.1\%} & \textbf{54.3\%} & 0.0\% & \textbf{28.6\%} & 0.0\% & \textbf{45.8\%} & 22.0\% \\
+		%%\hline
+		%%\emph{CV (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 2,333,365 (65.3\%) & 1,777 (0\%) & 0 (0\%) & 2,335,142 (4.3\%) \\
+		%%\emph{CV (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 28,000 (0.8\%) & 0 (0\%) & 0 (0\%) & 28,000 (0.1\%) \\
+		%\hline
+		%\textbf{\emph{info}} & \textbf{52.5\%} & \textbf{52.6\%} & 11.4\% & 0.0\% & \textbf{60.0\%} & 41.2\% & \textbf{41.3\%} & 31.3\% \\
+		%\textbf{\emph{warning}} & 7.0\% & 29.4\% & 8.6\% & \textbf{99.8\%} & 14.3\% & \textbf{58.8\%} & 10.0\% & \textbf{62.7\%} \\
+		%\textbf{\emph{error}} & 40.6\% & 18.0\% & \textbf{80.0\%} & 0.3\% & 25.7\% & 0.0\% & \textbf{48.8\%} & 6.1\%\\
+    %\bottomrule
+    %\end{tabular}
+    %\\ \emph{C (constraints), CV (constraint violations)}
+    %\end{center}
+%\end{table}
+
 \begin{table}[H]
@@
     \begin{center}
-    \begin{tabular}{@{}lcccccccc@{}}
+		\caption{Constraints and Constraint Violations (1)}
+		\label{tab:evaluation-constraint-violations}
+    \begin{tabular}{@{}lcccc@{}}
     %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
@@
       \multicolumn{2}{c}{\textbf{\emph{Disco}}} &
-      \multicolumn{2}{c}{\textbf{\emph{QB}}} &
-      \multicolumn{2}{c}{\textbf{\emph{SKOS}}} &
-      \multicolumn{2}{c}{\textbf{\emph{Total}}} \\
-    \textbf{} & C & CV & C & CV & C & CV & C & CV \\
+      \multicolumn{2}{c}{\textbf{\emph{QB}}} \\
+    \textbf{} & C & CV & C & CV \\
     \hline
     %\\ \midrule
-		 & 143 & 3,575,002 & 35 & 45,635,861 & 35 & 5,540,988 & 213 & 54,751,851 \\
-		\hline
-		\textbf{\emph{complex}} & 25.9\% & 18.3\% & 37.1\% & \textbf{100.0\%} & \textbf{37.1\%} & 21.4\% & 33.4\% & \textbf{46.6\%} \\
-		\textbf{\emph{simple}} & 19.6\% & 15.7\% & 8.6\% & 0.0\% & \textbf{34.3\%} & \textbf{78.6\%} & 20.8\% & 31.4\% \\
-		\textbf{\emph{vocabulary}} & \textbf{54.6\%} & \textbf{66.1\%} & \textbf{54.3\%} & 0.0\% & \textbf{28.6\%} & 0.0\% & \textbf{45.8\%} & 22.0\% \\
-		%\hline
-		%\emph{CV (}$\mathcal{C}_B ^{\mathcal{R}}$\emph{)} & 2,333,365 (65.3\%) & 1,777 (0\%) & 0 (0\%) & 2,335,142 (4.3\%) \\
-		%\emph{CV (}$\overline{\mathcal{C}_B ^{\mathcal{R}}}$\emph{)} & 28,000 (0.8\%) & 0 (0\%) & 0 (0\%) & 28,000 (0.1\%) \\
-		\hline
-		\textbf{\emph{info}} & \textbf{52.5\%} & \textbf{52.6\%} & 11.4\% & 0.0\% & \textbf{60.0\%} & 41.2\% & \textbf{41.3\%} & 31.3\% \\
-		\textbf{\emph{warning}} & 7.0\% & 29.4\% & 8.6\% & \textbf{99.8\%} & 14.3\% & \textbf{58.8\%} & 10.0\% & \textbf{62.7\%} \\
-		\textbf{\emph{error}} & 40.6\% & 18.0\% & \textbf{80.0\%} & 0.3\% & 25.7\% & 0.0\% & \textbf{48.8\%} & 6.1\%\\
+		 & 143 & 3,575,002 & 35 & 45,635,861 \\
+		\hline
+		\textbf{\emph{complex}} & 25.9\% & 18.3\% & 37.1\% & \textbf{100.0\%} \\
+		\textbf{\emph{simple}} & 19.6\% & 15.7\% & 8.6\% & 0.0\% \\
+		\textbf{\emph{vocabulary}} & \textbf{54.6\%} & \textbf{66.1\%} & \textbf{54.3\%} & 0.0\% \\
+		\hline
+		\textbf{\emph{info}} & \textbf{52.5\%} & \textbf{52.6\%} & 11.4\% & 0.0\% \\
+		\textbf{\emph{warning}} & 7.0\% & 29.4\% & 8.6\% & \textbf{99.8\%} \\
+		\textbf{\emph{error}} & 40.6\% & 18.0\% & \textbf{80.0\%} & 0.3\% \\
     \bottomrule
@@
     \\ \emph{C (constraints), CV (constraint violations)}
-    \caption{Constraints and constraint violations}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+		\scriptsize
+    \begin{center}
+		\caption{Constraints and Constraint Violations (2)}
 		\label{tab:evaluation-constraint-violations}
+    \begin{tabular}{@{}lcccc@{}}
+    %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
+    %\\  \cmidrule{2-3}
+		\hline
+    \multirow{2}{*}{} &
+      \multicolumn{2}{c}{\textbf{\emph{SKOS}}} &
+      \multicolumn{2}{c}{\textbf{\emph{Total}}} \\
+    \textbf{} & C & CV & C & CV \\
+    \hline
+    %\\ \midrule
+		 & 35 & 5,540,988 & 213 & 54,751,851 \\
+		\hline
+		\textbf{\emph{complex}} & \textbf{37.1\%} & 21.4\% & 33.4\% & \textbf{46.6\%} \\
+		\textbf{\emph{simple}} & \textbf{34.3\%} & \textbf{78.6\%} & 20.8\% & 31.4\% \\
+		\textbf{\emph{vocabulary}} & \textbf{28.6\%} & 0.0\% & \textbf{45.8\%} & 22.0\% \\
+		\hline
+		\textbf{\emph{info}} & \textbf{60.0\%} & 41.2\% & \textbf{41.3\%} & 31.3\% \\
+		\textbf{\emph{warning}} & 14.3\% & \textbf{58.8\%} & 10.0\% & \textbf{62.7\%} \\
+		\textbf{\emph{error}} & 25.7\% & 0.0\% & \textbf{48.8\%} & 6.1\%\\
+    \bottomrule
+    \end{tabular}
+    \\ \emph{C (constraints), CV (constraint violations)}
     \end{center}
@@
     \begin{center}
+		\caption{Relation between Complexity and Severity Level of Constraints}
+		\label{tab:evaluation-complexity-severity}
     \begin{tabular}{@{}lcccc@{}}
@@
     %\\ \emph{C (constraints), CT (constraint types)}
-    \caption{Relation between complexity and severity level of constraints}
-		\label{tab:evaluation-complexity-severity}
     \end{center}

### 2015-07-13 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
classification

@@
 For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
-Based on the results, we formulate several hypotheses to direct the further development of constraint languages.
+Based on the results, we formulate several hypotheses to direct the further development of constraint languages.\textcolor{red}{81 constraint types instead of 82?}
 \end{abstract}
@@
 \emph{OWL 2} is also used as a constraint language under a closed world assumption.
-With its direct support of validation via \emph{SPARQL}, \emph{SPIN}%\footnote{\url{http://spinRDF.org/}}
+With its direct support of validation via SPARQL, \emph{SPIN}%\footnote{\url{http://spinRDF.org/}}
 is very popular and certainly plays an important role for future developments in this field.
-It is particularly interesting as a means to validate arbitrary constraint languages by mapping them to \emph{SPARQL} \cite{BoschEckert2014-2}.
+It is particularly interesting as a means to validate arbitrary constraint languages by mapping them to SPARQL \cite{BoschEckert2014-2}.
 Yet, there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners.
@@
 	%\item to classify RDF constraints (according to their severity levels) to evaluate the quality of metadata and data which may be represented by any vocabulary and 
-	%\item to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (sections \ref{classification} - \ref{complex-constraint-types}).
+	%\item to classify RDF constraint types (according to their complexity) which in most cases correspond to RDF validation requirements\footnote{For simplicity reasons, we use the terms \emph{constraint types} and \emph{constraints} instead of \emph{RDF constraint types} and \emph{RDF constraints} in the rest of the paper} (sections \ref{classification} - \ref{SPARQL-based-constraint-types}).
 %\end{enumerate}
@@
 %how therefore reused vocabularies are interrelated (section \ref{rdf-representation}),
-%and how \emph{SBE} (meta)data is validated against constraints of different constraint types (sections \ref{classification} - \ref{complex-constraint-types}).
+%and how \emph{SBE} (meta)data is validated against constraints of different constraint types (sections \ref{classification} - \ref{SPARQL-based-constraint-types}).
 %We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple vocabularies to get an understanding
@@
 We generally refer to both simply as RDF data and only distinguish between data and metadata in the data set descriptions and in the case that it matters for the purpose of this paper.
-The underlying \emph{semantics} for RDF validation is \emph{UNA}/\emph{CWA}.
+The underlying \emph{semantics} for RDF validation is UNA/CWA.
 RDF validation requires that different names represent different objects ({\em unique name assumption (UNA)}), whereas,
@@
 (See \cite{resource} for this terminology.)
-%When assuming \emph{UNA}, the functional property {\em title} (\ms{funct (title)}) causes a clash
+%When assuming UNA, the functional property {\em title} (\ms{funct (title)}) causes a clash
 %in case the book {\em Huckleberry-Finn} has more than one \emph{title}
@@
 %{\em Hamlet} must have at least one \emph{title}.
-%In an \emph{OWA} setting, this axiom does not cause a constraint violation (even if there is no explicitly defined \emph{title}), since there must be a \emph{title} for this \emph{book} which we may not know.
+%In an OWA setting, this axiom does not cause a constraint violation (even if there is no explicitly defined \emph{title}), since there must be a \emph{title} for this \emph{book} which we may not know.
 On the other hand, RDF validation scenarios require the {\em closed-world assumption (CWA)}, i.e., a statement is inferred to be false if it cannot be proved to be true.
-Classical constraint languages are based on the \emph{CWA} where constraints need to be satisfied only by named individuals.
+Classical constraint languages are based on the CWA where constraints need to be satisfied only by named individuals.
 This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past.  
@@
 
-To gain better insights into the role that certain types of constraints play for the quality of RDF data, we use two simple classifications: on the one hand, we classify RDF constraint types according to their complexity and on the other hand, we classify concrete constraints formulated for a vocabulary according to the perceived severity of a violation.
-
-Within the working groups, we identified by today 82 requirements to formulate RDF constraints (e.g.
-\emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}.
+To gain better insights into the role that certain types of constraints play for the quality of RDF data, we use two simple classifications: on the one hand, we classify RDF constraint types whether they are expressible by different types of constraint languages and on the other hand, we classify concrete constraints formulated for a given vocabulary according to the perceived severity of a violation.
+
+Within the working groups, we identified by today 82 requirements to formulate RDF constraints (e.g., \emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}.
 Within a technical report serving as first appendix of this paper we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages \cite{BoschNolleAcarEckert2015}.
-We provide mappings to representations in Description Logics (\emph{DL}) to logically underpin each requirement and to determine which \emph{DL} constructs are needed to express each constraint type.
+We provide mappings to representations in description logics (DL) \cite{Baader-2003} to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type.
 
@@
 
-The classification of the 213 concrete constraints on three vocabularies according to severity levels is published in a second technical report serving as second appendix of this paper \cite{BoschZapilkoWackerowEckert2015}.
+The classification of the 114 concrete constraints on three vocabularies according to severity levels is published in a second technical report serving as second appendix of this paper \cite{BoschZapilkoWackerowEckert2015}.
 In the following, we summarize the results for the purpose of our evaluation.
 
-\subsection{Complexity of Constraint Types}
-
-According to the complexity of constraint types, the complete set of \emph{constraint types} encompasses three disjoint \emph{sets of constraint types}:
+\subsection{Classification of Constraint Types according to the Expressivity of Constraint Languages}
+
+According to the expressivity of constraint languages, the complete set of \emph{constraint types} encompasses three disjoint \emph{sets of constraint types}:
 \begin{enumerate}
-	\item \textbf{\emph{Vocabulary Constraint Types}}
-	\item \textbf{\emph{Simple Constraint Types}}
-	\item \textbf{\emph{Complex Constraint Types}}
+	\item \emph{RDFS/OWL Based}
+	\item \emph{Constraint Language Based}
+	\item \emph{SPARQL Based}
 \end{enumerate}
 
-The modeling languages \emph{RDF}, \emph{RDFS}, and \emph{OWL} are typically used to formally specify vocabularies.
-\emph{Vocabulary constraint types}
-denotes the set of constraint types that are commonly found for constraints within formal specifications of vocabularies, i.e., constraints that are formulated using \emph{RDFS} and common constructs of \emph{OWL}.
-We determined this set based on the evaluation of the six vocabularies.
-\emph{Vocabulary constraints} generally can be seen as a basic level of constraints ensuring that the data is consistent with the intended syntaxes, semantics, and integrity of vocabularies' data models.
+The modeling languages RDFS, and OWL are typically used to formally specify vocabularies.
+\emph{RDFS/OWL Based} denotes the set of constraint types which can be formulated with RDFS/OWL constructs using CWA/UNA semantics (without reasoning) and which are therefore commonly found within formal specifications of vocabularies.
+We determined this set based on the evaluation of the three vocabularies.
+\emph{RDFS/OWL Based} constraints generally can be seen as a basic level of constraints ensuring that the data is consistent with the formally and explicitly specified intended semantics as well as the integrity of vocabularies' conceptual models about data.
 
 %The {\em existential quantification} (\emph{R-86}) 
-%\ms{Study $\equiv$ $\exists$ product.LogicalDataSet} (\emph{DL}), e.g., restricts studies to contain at least one data set which is expressible in OWL 2:
-\emph{Minimum qualified cardinality restrictions} (\emph{R-74}), e.g., guarantee that individuals of given classes are connected by particular properties to at least n different individuals/literals of certain classes or data ranges.
-In \emph{PHDD}, a \emph{minimum qualified cardinality restriction} can be obtained from the OWL definition of this restriction class, ensuring that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:
+%\ms{Study $\equiv$ $\exists$ product.LogicalDataSet} (DL), e.g., restricts studies to contain at least one data set which is expressible in OWL 2:
+Constraints of the constraint type \emph{minimum qualified cardinality restrictions} (\emph{R-74}), e.g., guarantee that individuals of given classes are connected by particular properties to at least n different individuals/literals of certain classes or data ranges.
+In \emph{PHDD}, a \emph{minimum qualified cardinality restriction} can be obtained from a respective OWL axiom which ensures that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:
 \begin{ex}
@@
 
-\emph{Simple} and \emph{complex constraints} are in contrast to \emph{vocabulary constraints} usually not (yet) explicitly defined within formal specifications of vocabularies.
+\emph{Constraint Language Based} and \emph{SPARQL Based} constraints are in contrast to \emph{RDFS/OWL Based} constraints usually not (yet) explicitly defined within formal specifications of vocabularies.
 Instead, they are often defined in textual descriptions of the vocabularies.
@@
 
-We further distinguished \emph{simple constraint types} as the set of constraint types whose constraints can be easily defined without much effort in addition to the already defined \emph{vocabulary constraints}.
-\emph{Data property facets} (\emph{R-46}) is an example of a \emph{simple constraint type} which enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
-The abstract of series/studies, e.g., should have a minimum length which is easily and concisely expressible by SPARQL: 
-\begin{ex}
-SELECT ?study WHERE {
-    ?study dcterms:abstract ?abstract . 
-    FILTER ( STRLEN ( ?abstract ) = 10 ) . }
-\end{ex}
+We further distinguished \emph{Constraint Language Based} as the set of constraint types that are not \emph{RDF/OWL Based}, but can be expressed by common declarative high-level constraint languages like ShEx, ReSh, and DSP.
+SPARQL is considered as a low-level implementation language in this context, not a high-level constraint language.
+
+\textcolor{red}{example}
+
+%We further distinguished \emph{simple constraint types} as the set of constraint types whose constraints can be easily defined without much effort in addition to the already defined \emph{vocabulary constraints}.
+%\emph{Data property facets} (\emph{R-46}) is an example of a \emph{simple constraint type} which enables to declare frequently needed facets for data properties in order to validate input against simple conditions including min/max values, regular expressions, and string length.
+%The abstract of series/studies, e.g., should have a minimum length which is easily and concisely expressible by SPARQL: 
+%\begin{ex}
+%SELECT ?study WHERE {
+    %?study dcterms:abstract ?abstract . 
+    %FILTER ( STRLEN ( ?abstract ) = 10 ) . }
+%\end{ex}
 For these constraints, we expect a straight-forward support in future constraint languages.
 
-\emph{Complex constraint types} encompass constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
+%\emph{Complex constraint types} encompass constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
+\emph{SPARQL Based} encompass constraint types that are not expressible by RDFS/OWL or common constraint languages but by plain SPARQL.
 For assessing the quality of thesauri, e.g., we concentrate on the graph-based structure and apply graph- and network-analysis techniques.
@@
 a thesaurus should not contain many orphan concepts, i.e., concepts without any associative or hierarchical relations, lacking context information valuable for search.
-This \emph{complex constraint} is only expressible by \emph{SPARQL} and not directly understandable:
+This \emph{complex constraint} is only expressible by SPARQL and not directly understandable:
 \begin{ex}
@@
 \end{ex}
-\emph{Complex constraints} are today in most cases only expressible by plain \emph{SPARQL}. Depending on their usefulness, a support in constraint languages should be considered.
-
-\subsection{Severity of Constraints}
+\emph{SPARQL Based} constraint types are today in most cases only expressible by plain SPARQL. Depending on their usefulness, a support in constraint languages should be considered.
+
+\subsection{Classification of Constraints according to the Severity of Constraint Violations}
 
@@
 It does not make sense to determine the severity of constraint violations of an entire constraint type,
-as the severity of the violation of a given constraint depends on the individual context and vocabulary.
+as the severity of the violation of a constraint depends on the individual context and vocabulary.
 %as the violation of one constraint may be severe,
 %whereas, the violation of another constraint of the same type may be minor.
-\emph{SBE} experts determined the default \textbf{\emph{severity level}}\footnote{The possibility to define severity levels in vocabularies is in itself a requirement (\emph{R-158}) defined by the DCMI task group.} for each of the 213 constraints to indicate how serious the violation of the constraint is.
-%We propose an extensible metric to measure the continuum of severity levels ranging from \emph{informational} to \emph{error}.
-We use the commonly accepted classification of log messages in software development and distinguish \emph{informational}, \emph{warning} and \emph{error}.
+\emph{SBE} experts determined the default \emph{severity level}\footnote{The possibility to define severity levels in vocabularies is in itself a requirement (\emph{R-158}).} for each of the 114 constraints to indicate how serious the violation of the constraint is.
+We use the classification system of log messages in software development like \emph{Apache Log4j 2} \cite{Apache-2015}, the \emph{Java Logging API}\footnote{\url{http://docs.oracle.com/javase/7/docs/api/java/util/logging/Level.html}}, and the \emph{Apache Commons Logging API}\footnote{\url{http://commons.apache.org/proper/commons-logging/}} as many data practitioners also have experience in software development and software developers intuitively understand these levels.
+We simplify this commonly accepted classification system and distinguish the three severity levels \emph{informational}, \emph{warning} and \emph{error}.
 %According to the default severity level of constraints, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:\ke{auch dieser satz macht keinen sinn für mich, ebensowenig wie die extrem erhellende auflistung, die gleich folgt...
@@
 \emph{Warnings} are syntactic or semantic problems which typically should not lead to an abortion of data processing.
-\emph{Errors} are syntactic or semantic errors which should cause the abortion of data processing. 
+\emph{Errors} are syntactic or semantic errors which should cause the abortion of data processing. \textcolor{red}{examples for each in the subsequent section?}
 %Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
@@
 
-Note that there is a correlation between the severity of a constraint and the complexity of its type: vocabulary constraint are in most cases classified with an \emph{error} level as they typically represent basic and important constraints; there is a reason why they have been included in the vocabulary specification.
-
-% Although, we provide default severity levels for each constraint, validation environments should enable users to adapt the severity levels of constraints according to their individual needs.
+Note that there is a correlation between the severity of a constraint and the classification according to the expressivity of constraint languages of its type: \emph{RDFS/OWL Based} constraints are in most cases classified with an \emph{error} level as they typically represent basic and important constraints; there is a reason why they have been included in the vocabulary specification.
+Although, we provide default severity levels for each constraint, validation environments should enable users to adapt the severity levels of constraints according to their individual needs.
 % Validation environments should enable users to select which constraints to validate against depending on their individual use cases.
@@
 %i.e., individuals cannot be instances of multiple disjoint classes.
-\subsubsection*{Vocabulary Constraint Types.}
-It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values (\emph{R-30/37: allowed values}). 
+\subsubsection*{RDFS/OWL Based Constraint Types}
+\textcolor{red}{severity levels assigned for each constraint?}
+It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values (\emph{R-30/37: allowed values}):
 %\emph{Allowed values} (\emph{R-30, R-37}) for properties can be IRIs (matching one or multiple patterns), any literals, allowed literals (e.g.
@@
 \emph{xsd:string}).
-\emph{disco:Category} \emph{Statistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString}.
+\emph{disco:CategoryStatistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString} (default severity level: \emph{error}).
 %Validation should \emph{exploit sub-super relations} in vocabularies (\emph{R-224}).
@@
 %which may indicate when the data is verbose/redundant or expressed at a too general level.
-Consider the following \emph{DL} knowledge base $\mathcal{K}$\footnote{A knowledge base is a collection of formal statements which corresponds to \emph{facts} or what is known explicitly.
+Consider the following \emph{DL knowledge base} $\mathcal{K}$\footnote{A \emph{DL knowledge base} is a collection of formal statements which corresponds to \emph{facts} or what is known explicitly.
 For simplicity reasons, we do not state namespace prefixes.}:
@@
 &{\small\ms{CategoryStatistics $\equiv$ $\forall$ computationBase.}} \\
-	&{\small\ms{    \{valid,invalid\} $\sqcap$ langString,}} \\
+	&{\small\ms{\{valid,invalid\} $\sqcap$ langString,}} \\
   &{\small\ms{Variable $\equiv$ $\exists$ concept.Concept,}} \\
@@
 The default severity level of this constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
+
 A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
@@
 %\end{DL}
-Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets}.
-\emph{Property domain} (\emph{R-25, R-26}) and \emph{range} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties:
+Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets} (\emph{error}).
+\emph{Property domains} (\emph{R-25, R-26}) and \emph{property ranges} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties:
 Only \emph{phdd:Tables}, e.g., can have \emph{phdd:isStructuredBy} relationships and
-\emph{xkos:belongsTo} relations can only point to \emph{skos:Concepts}.
+\emph{xkos:belongsTo} relations (\emph{error}) can only point to \emph{skos:Concepts} (\emph{error}).
 %\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals/literals of certain types.
@@
 
-%As \emph{RDFS} and \emph{OWL} are typically used to define vocabularies, \emph{RDFS} and \emph{OWL} reasoning may be performed prior to validation. 
+%As RDFS and OWL are typically used to define vocabularies, RDFS and OWL reasoning may be performed prior to validation. 
 %Reasoning and validation are indeed very closely related. 
@@
 
-\subsubsection*{Simple Constraint Types.}
+\subsubsection*{Constraint Language Based}
 
@@
 Thus and as there are different sorts of key, and as keys can lead to undecidability, 
-\emph{DL} is extended with the construct \emph{keyfor} ({\small\ms{identifier \ms{keyfor} Resource}}) \cite{Lutz2005} which is implemented by the \emph{OWL 2} \emph{hasKey} construct.
+DL is extended with the construct \emph{keyfor} ({\small\ms{identifier \ms{keyfor} Resource}}) \cite{Lutz2005} which is implemented by the \emph{OWL 2} \emph{hasKey} construct.
 %\emph{OWL 2} \emph{hasKey} implements \emph{keyfor} ($\mathcal{SL}_{2}$) and thus can be used to identify resources uniquely, to merge resources with identical key property values, and to recognize constraint violations.
@@
 
-\subsubsection*{Complex Constraint Types.}
-\label{complex-constraint-types}
+\subsubsection*{SPARQL Based Constraint Types}
+\label{SPARQL-based-constraint-types}
 
@@
 We use \emph{SPIN}, 
-a \emph{SPARQL}-based way to formulate and check constraints, as basis to develop a
+a SPARQL-based way to formulate and check constraints, as basis to develop a
 validation environment\footnote{Online demo available at \url{http://purl.org/net/rdfval-demo}, source code at: \url{https://github.com/boschthomas/rdf-validator}} to validate RDF data according to constraints expressed by arbitrary constraint languages\footnote{SPIN mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} \cite{BoschEckert2014-2}.
@@
 %Table \ref{tab:evaluation-constraint-types} displays the evaluation of the metadata quality on real world data sets regarding constraint types.
-Table \ref{tab:evaluation-constraint-violations} shows the results of the evaluation, more specifically the constraints and the constraint violations, which are caused by these constraints, in percent.
+Tables \ref{tab:evaluation-constraint-violations-1} and \ref{tab:evaluation-constraint-violations-2} show the results of the evaluation, more specifically the constraints and the constraint violations, which are caused by these constraints, in percent.
 The constraints and their raised constraint violations are grouped by vocabulary, complexity level of their type, and their severity level.
@@
 		\caption{Constraints and Constraint Violations (1)}
-		\label{tab:evaluation-constraint-violations}
+		\label{tab:evaluation-constraint-violations-1}
     \begin{tabular}{@{}lcccc@{}}
@@
 		\caption{Constraints and Constraint Violations (2)}
-		\label{tab:evaluation-constraint-violations}
+		\label{tab:evaluation-constraint-violations-2}
     \begin{tabular}{@{}lcccc@{}}
@@
 
-In general, \emph{vocabulary constraints} are expressible by either modeling languages (e.g., \emph{RDF}, \emph{RDFS}, \emph{OWL 2}) or constraint languages. 
-\emph{Simple constraints} and especially \emph{complex constraints}, however, are in most cases only expressible by plain \emph{SPARQL}. 
+In general, \emph{vocabulary constraints} are expressible by either modeling languages (e.g., RDF, RDFS, \emph{OWL 2}) or constraint languages. 
+\emph{Simple constraints} and especially \emph{complex constraints}, however, are in most cases only expressible by plain SPARQL. 
 As almost 1/2 of all violations are caused by \emph{complex constraints}, 
@@
 violations of \emph{vocabulary constraints} are more severe than violations caused by \emph{simple constraints}.
-As \emph{SPARQL} is still used to express \emph{complex constraints} and as 44\% of all \emph{complex constraints} are serious,
+As SPARQL is still used to express \emph{complex constraints} and as 44\% of all \emph{complex constraints} are serious,
 there is an obvious need to develop constraint languages which enable to express \emph{complex constraints}.
@@
 %We distinguish two validation types:
-%(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of data models (section \ref{complex-constraint-types}).
+%(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of data models (section \ref{SPARQL-based-constraint-types}).
 %(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges (section \ref{vocabulary-constraint-types}).
@@
   \item As 54\% of the constraints are either \emph{simple} or \emph{complex constraints},
-the further development of constraint languages should concentrate on expressing \emph{simple} and especially \emph{complex constraints} which up to now in most cases can only be expressed by plain \emph{SPARQL}.
+the further development of constraint languages should concentrate on expressing \emph{simple} and especially \emph{complex constraints} which up to now in most cases can only be expressed by plain SPARQL.
 \end{enumerate}

### 2015-07-13 paper/RDF validation requirements/RDF validation requirements.tex
classification

@@
 *Sub Properties & $\sqsubseteq$ & sub-properties \\
-*Property Domain & $\exists$, $\sqsubseteq$ & property domain \\
-*Property Range & $\sqsubseteq$, $\forall$ & property range \\
+*Property Domains & $\exists$, $\sqsubseteq$ & property domain \\
+*Property Ranges & $\sqsubseteq$, $\forall$ & property range \\
 *Inverse Object Properties & inverse & inverse properties \\

### 2015-07-14 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
evaluation

@@
 
-According to the expressivity of constraint languages, the complete set of \emph{constraint types} encompasses three disjoint \emph{sets of constraint types}:
+According to the expressivity of constraint languages, the complete set of \emph{constraint types} encompasses three not disjoint \emph{sets of constraint types}:
 \begin{enumerate}
@@
 
-The modeling languages RDFS, and OWL are typically used to formally specify vocabularies.
+The modeling languages RDFS and OWL are typically used to formally specify vocabularies.
 \emph{RDFS/OWL Based} denotes the set of constraint types which can be formulated with RDFS/OWL constructs using CWA/UNA semantics (without reasoning) and which are therefore commonly found within formal specifications of vocabularies.
@@
 
-We further distinguished \emph{Constraint Language Based} as the set of constraint types that are not \emph{RDF/OWL Based}, but can be expressed by common declarative high-level constraint languages like ShEx, ReSh, and DSP.
-SPARQL is considered as a low-level implementation language in this context, not a high-level constraint language.
+We further distinguish \emph{Constraint Language Based} as the set of constraint types that can be expressed by common classical declarative high-level constraint languages like ShEx, ReSh, and DSP. 
+%RDFS, and OWL as we consider RDFS and OWL as constraint languages when assuming CWA/UNA semantics without reasoning. 
+There is a strong overlap between \emph{RDFS/OWL Based} and \emph{Constraint Language Based} constraint types as in many cases constraint types are expressible by classical constraint languages and OWL.
+SPARQL, however, is considered as a low-level implementation language in this context, not as a high-level constraint language.
 
@@
 %i.e., individuals cannot be instances of multiple disjoint classes.
-\subsubsection*{RDFS/OWL Based Constraint Types}
+\textbf{\emph{RDFS/OWL Based} constraint types.}
 \textcolor{red}{severity levels assigned for each constraint?}
@@
 
-\subsubsection*{Constraint Language Based}
-
+\textbf{\emph{Constraint Language Based} constraint types.}
 %{Simple constraint types} is the set of constraint types whose constraints can be easily defined without much effort in addition to $\mathcal{CT}_{B}$ constraints.
@@
 %\textbf{Validation and Reasoning.}
-%\emph{Default values} (\emph{R-31, R-38}) for objects/literals of given properties are inferred automatically when properties are not present in the data.
-%The value \emph{true} for the property {\em disco:isPublic} indicates that a {\em disco:LogicalDataSet} can be accessed by anyone.
-%Per default, however, access to data sets should be restricted (\emph{false}) ($\mathcal{SL}_{0}$).
-%Many properties are not necessarily required but \emph{recommended} within a particular context (\emph{R-72}).
-%The property {\em skos:notation}, e.g., is not mandatory for {\em disco:Variable}s, but recommended to represent variable names ($\mathcal{SL}_{0}$).
+
+\textcolor{red}{\emph{Context-specific exclusive or of property groups}} (\emph{R-11}) constraints
+restrict individuals of given classes to have properties defined within exactly one of multiple property groups.
+\emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes), but not both (\emph{error}).
+
+\textcolor{red}{\emph{Default values}} (\emph{R-31, R-38}) for objects/literals of given properties are inferred automatically when properties are not present in the data.
+The value \emph{true} for the property {\em disco:isPublic} indicates that a {\em disco:LogicalDataSet} can be accessed by anyone.
+Per default, however, access to data sets should be restricted (\emph{false}) ($\mathcal{SL}_{0}$).
+Many properties are not necessarily required but \emph{recommended} within a particular context (\emph{R-72}).
+The property {\em skos:notation}, e.g., is not mandatory for {\em disco:Variable}s, but recommended to represent variable names ($\mathcal{SL}_{0}$).
+
+Depending on property datatypes, two different literal values have
+a specific ordering with respect to operators like \textless  (\textcolor{red}{\emph{R-43: literal value comparison}}).
+Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}).
+
 Percentage values are only valid when they are within the literal range of 0 and 100 (\emph{R-45: literal ranges}; \emph{error})
@@
 
-\subsubsection*{SPARQL Based Constraint Types}
-\label{SPARQL-based-constraint-types}
-
+\textbf{\emph{SPARQL Based} constraint types.}
 %\textcolor{red}{
@@
 %- there should be a relationship to the underlying person-level data.
-
+%
 %$\mathcal{CT}_{C}$ denotes the set of constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
@@
 %then the property {\em disco:isValid} has to be stated indicating if the code stands for valid (\emph{true}) or missing (\emph{false}) cases ($\mathcal{SL}_{2}$).
-\emph{Context-specific exclusive or of property groups} (\emph{R-11}) constraints
-restrict individuals of given classes to have properties defined within exactly one of multiple property groups.
-\emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes), but not both (\emph{error}).
 
@@
 To be able to formulate hypotheses which apply for all vocabularies, 
-we only use normalized relative values representing the percentage of constraints and constraint violations belonging to the respective class
+we only use normalized relative values representing the percentage of constraints and constraint violations belonging to the respective class.
+There is a strong overlap between \emph{RDFS/OWL Based} and \emph{Constraint Language Based} constraint types as in many cases constraint types are expressible by classical constraint languages and OWL.
+This is the reason why the percentage values of constraints and violations grouped by the classification according to the expressivity of constraint languages do not accumulate to 100\%.
 
@@
     \begin{center}
-		\caption{Constraints and Constraint Violations (1)}
+		\caption{OLD}
 		\label{tab:evaluation-constraint-violations-1}
@@
     \begin{center}
+		\caption{OLD}
+		\label{tab:evaluation-constraint-violations-2}
+    \begin{tabular}{@{}lcccc@{}}
+    %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
+    %\\  \cmidrule{2-3}
+		\hline
+    \multirow{2}{*}{} &
+      \multicolumn{2}{c}{\textbf{\emph{SKOS}}} &
+      \multicolumn{2}{c}{\textbf{\emph{Total}}} \\
+    \textbf{} & C & CV & C & CV \\
+    \hline
+    %\\ \midrule
+		 & 35 & 5,540,988 & 213 & 54,751,851 \\
+		\hline
+		\textbf{\emph{complex}} & \textbf{37.1\%} & 21.4\% & 33.4\% & \textbf{46.6\%} \\
+		\textbf{\emph{simple}} & \textbf{34.3\%} & \textbf{78.6\%} & 20.8\% & 31.4\% \\
+		\textbf{\emph{vocabulary}} & \textbf{28.6\%} & 0.0\% & \textbf{45.8\%} & 22.0\% \\
+		\hline
+		\textbf{\emph{info}} & \textbf{60.0\%} & 41.2\% & \textbf{41.3\%} & 31.3\% \\
+		\textbf{\emph{warning}} & 14.3\% & \textbf{58.8\%} & 10.0\% & \textbf{62.7\%} \\
+		\textbf{\emph{error}} & 25.7\% & 0.0\% & \textbf{48.8\%} & 6.1\%\\
+    \bottomrule
+    \end{tabular}
+    \\ \emph{C (constraints), CV (constraint violations)}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+		\scriptsize
+    \begin{center}
+		\caption{Constraints and Constraint Violations (1)}
+		\label{tab:evaluation-constraint-violations-1}
+    \begin{tabular}{@{}lcccc@{}}
+    %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
+    %\\  \cmidrule{2-3}
+		\hline
+    \multirow{2}{*}{} &
+      \multicolumn{2}{c}{\textbf{\emph{Disco}}} &
+      \multicolumn{2}{c}{\textbf{\emph{QB}}} \\
+    \textbf{} & C & CV & C & CV \\
+    \hline
+    %\\ \midrule
+		 & 143 & 3,575,002 & 35 & 45,635,861 \\
+		\hline
+		\textbf{\emph{SPARQL}} & 44.8\% & 34.7\% & \textbf{54.3\%} & \textbf{100.0\%} \\
+		\textbf{\emph{CL}} & 42.0\% & \textbf{65.3\%} & 28.6\% & 0.0\% \\
+		\textbf{\emph{RDFS/OWL}} & \textbf{51.8\%} & \textbf{65.3\%} & 42.9\% & 0.0\% \\
+		\hline
+		\textbf{\emph{info}} & \textbf{52.5\%} & \textbf{52.6\%} & 11.4\% & 0.0\% \\
+		\textbf{\emph{warning}} & 7.0\% & 29.4\% & 8.6\% & \textbf{99.8\%} \\
+		\textbf{\emph{error}} & 40.6\% & 18.0\% & \textbf{80.0\%} & 0.3\% \\
+    \bottomrule
+    \end{tabular}
+    \\ \emph{C (constraints), CV (constraint violations)}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+		\scriptsize
+    \begin{center}
 		\caption{Constraints and Constraint Violations (2)}
@@
 		\hline
-		\textbf{\emph{complex}} & \textbf{37.1\%} & 21.4\% & 33.4\% & \textbf{46.6\%} \\
-		\textbf{\emph{simple}} & \textbf{34.3\%} & \textbf{78.6\%} & 20.8\% & 31.4\% \\
-		\textbf{\emph{vocabulary}} & \textbf{28.6\%} & 0.0\% & \textbf{45.8\%} & 22.0\% \\
+		\textbf{\emph{SPARQL}} & \textbf{80.0\%} & \textbf{100.0\%} & 59.7\% & 78.2\% \\
+		\textbf{\emph{CL}} & 0.0\% & 0.0\% & 23.5\% & 21.8\% \\
+		\textbf{\emph{RDFS/OWL}} & 20.0\% & 0.0\% & 38.2\% & 21.8\% \\
 		\hline

### 2015-07-14 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
evaluation

@@
 Based on our work in the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group, we identified and published by today 82 types of constraints that are required by various stakeholders for data applications.
-In this paper, we formulate 213 constraints of 53 different types on three different vocabularies (\emph{Disco}, \emph{QB}, and \emph{SKOS}) and classify them according to the complexity level of their type and their severity level.
+In this paper, we formulate 213 constraints of 53 different types on three different vocabularies (DDI-RDF, QB, and SKOS) and classify them according to the complexity level of their type and their severity level.
 For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
@@
 (3) The percentage of severe constraint violations is very low, compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
+
+\textcolor{red}{references to constraint languages}
 
@@
 With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration.
-Therefore, not only established vocabularies like \emph{SKOS} are used;
+Therefore, not only established vocabularies like SKOS are used;
 recently, members of the \emph{SBE} and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.
@@
 \emph{OWL 2} is also used as a constraint language under a closed world assumption.
-With its direct support of validation via SPARQL, \emph{SPIN}%\footnote{\url{http://spinRDF.org/}}
+With its direct support of validation via SPARQL, SPIN%\footnote{\url{http://spinRDF.org/}}
 is very popular and certainly plays an important role for future developments in this field.
@@
 As we do not want to base our conclusions on the evaluations of vocabularies and constraint definitions alone, we conducted a large-scale experiment.
-For 114 constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (\emph{Disco}, \emph{QB}, \emph{SKOS}) obtained from 33 SPARQL endpoints.
+For 114 constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (DDI-RDF, QB, SKOS) obtained from 33 SPARQL endpoints.
 %evaluated the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
@@
 Aggregated data, which answers particular research questions, is derived from person-level data by statistics on groups or aggregates such as frequencies and arithmetic means.
-%The SDMX metadata standard – used as the basis for \emph{QB} – and DDI have traditionally made efforts to align their content. 
-%Similarly, some of the developers of \emph{Disco} were also involved in the development of \emph{QB}, 
+%The SDMX metadata standard – used as the basis for QB – and DDI have traditionally made efforts to align their content. 
+%Similarly, some of the developers of DDI-RDF were also involved in the development of QB, 
 %allowing the RDF versions of these standards to retain that alignment.
-%While \emph{Disco} and \emph{QB} provide terms for the description of data sets, 
+%While DDI-RDF and QB provide terms for the description of data sets, 
 %both on a different level of aggregation, 
@@
 %\textbf{RDF Data Cube Vocabulary.}
-A well-formed \emph{RDF Data Cube} is an a RDF graph describing one or more instances of \emph{qb:DataSet} for which each of the 22 integrity constraints\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf}, defined within the \emph{QB} specification, passes.
+A well-formed \emph{RDF Data Cube} is an a RDF graph describing one or more instances of \emph{qb:DataSet} for which each of the 22 integrity constraints\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf}, defined within the QB specification, passes.
 Each integrity constraint is expressed as narrative prose and, where possible, a SPARQL ASK query or query template. 
-If the ASK query is applied to an RDF graph then it will return true if that graph contains one or more \emph{QB} instances which violate the corresponding constraint \cite{CyganiakReynolds2014}.
+If the ASK query is applied to an RDF graph then it will return true if that graph contains one or more QB instances which violate the corresponding constraint \cite{CyganiakReynolds2014}.
 Mader, Haslhofer, and Isaac investigated how to support
@@
 
-%In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (\emph{Disco}), aggregated data sets (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.
+%In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (DDI-RDF), aggregated data sets (QB), thesauri (SKOS), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.
 
@@
 multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}.
-%\emph{QB} represents metadata on multi-dimensional aggregate data in two files: a \emph{qb:DataSet} and a \emph{qb:DataStructureDefinition}.
+%QB represents metadata on multi-dimensional aggregate data in two files: a \emph{qb:DataSet} and a \emph{qb:DataStructureDefinition}.
 A \emph{qb:DataStructureDefinition} contains metadata of the data collection.
@@
 It is often useful to declare a given (data) property as the \emph{primary key} (\emph{R-226}) of a class, so that a system can enforce uniqueness and build URIs from user inputs and imported data. 
-In \emph{Disco}, resources are uniquely identified by the property \emph{adms:identifier},
+In DDI-RDF, resources are uniquely identified by the property \emph{adms:identifier},
 which is therefore inverse-functional $({\small\ms{funct identifier}\sp{\overline{\ }}})$,
@@
 %\textbf{Structure and Ordering.}
-%For assessing the quality of \emph{SKOS} vocabularies, we concentrate on graph-based structures and apply graph- and network-analysis techniques (\emph{structure} constraints) like 
+%For assessing the quality of SKOS vocabularies, we concentrate on graph-based structures and apply graph- and network-analysis techniques (\emph{structure} constraints) like 
 %(1) a thesaurus should provide entry points (top concepts) to the data to provide efficient access and guidance for human users,
@@
 %It is often useful to declare a given (data) property as the \emph{primary key} (\emph{R-226}) of a class, so that a system can enforce uniqueness and also automatically build URIs from user inputs and imported data.
-%In \emph{Disco}, resources are uniquely identified by the property \emph{adms:identifier},
+%In DDI-RDF, resources are uniquely identified by the property \emph{adms:identifier},
 %which is therefore inverse-functional
@@
 %\textbf{Reusability.}
-%Within the context of \emph{Disco}, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes/categories), but not both ($\mathcal{SL}_{2}$).
+%Within the context of DDI-RDF, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes/categories), but not both ($\mathcal{SL}_{2}$).
 %The constraint type \emph{context-specific exclusive or of property groups} (\emph{R-11})
@@
 As described in Section~\ref{rdf-representation}, for other vocabularies there is often not (yet) enough data openly available to draw general conclusions.
-The three vocabularies, however, are representative, cover different aspects of SBE data and are also a mixture of established vocabularies (\emph{QB}, \emph{SKOS}) and a vocabulary under development (\emph{Disco}).
+The three vocabularies, however, are representative, cover different aspects of \emph{SBE} data and are also a mixture of established vocabularies (QB, SKOS) and a vocabulary under development (DDI-RDF).
 Due to this limitation, we will present several hypotheses together with a rationale based on the results for the three vocabularies.
@@
 %in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$).
-On the three vocabularies (\emph{Disco}, \emph{QB}, \emph{SKOS}), we identified and classified 213 constraints of which we implemented for the data validation 114 constraints.\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} The reason is simply that more time is needed for the remaining implementation.
-We ensured, however, that the implementation is equally distributed over the classes and vocabularies we have.
+On the three vocabularies (DDI-RDF, QB, SKOS), we identified and classified 114 constraints\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} which we implemented for the data validation.
+We ensured that the implementation of the constraints is equally distributed over the classes and vocabularies we have.
 We then evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data using these 114 constraints, obtained from 33 SPARQL endpoints.
 
-\emph{QB} and \emph{SKOS} are well-established vocabularies which are widely adopted and accepted. \emph{Disco} is a newly developed vocabulary which will be published in 2015.
+QB and SKOS are well-established vocabularies which are widely adopted and accepted. DDI-RDF is a newly developed vocabulary which will be published in 2015.
 
@@
 Table~\ref{tab:datasets} lists the number of data sets and the overall sizes in terms of triples for each of the vocabularies. We validated, i.a., 
-(1) \emph{QB} data sets published by the \emph{Australian Bureau of Statistics},
+(1) QB data sets published by the \emph{Australian Bureau of Statistics},
 the \emph{European Central Bank}, and the
 \emph{Organisation for Economic Co-operation and Development},
-(2) \emph{SKOS} thesauri like the \emph{AGROVOC Multilingual agricultural thesaurus},
+(2) SKOS thesauri like the \emph{AGROVOC Multilingual agricultural thesaurus},
 the \emph{STW Thesaurus for Economics}, and the
 \emph{Thesaurus for the Social Sciences}, and
-(3) \emph{Disco} data sets provided by the \emph{Microdata Information System}, 
+(3) DDI-RDF data sets provided by the \emph{Microdata Information System}, 
 the \emph{Data Without Boundaries Discovery Portal}, the
@@
 		%\hline
-		\textbf{\emph{QB}} & $9,990$   & $3,775,983,610$  \\
-		\textbf{\emph{SKOS}} & $4,178$  & $477,737,281$ \\
-		\textbf{\emph{Disco}} & $1,526$  & $9,673,055$  \\
+		\textbf{QB} & $9,990$   & $3,775,983,610$  \\
+		\textbf{SKOS} & $4,178$  & $477,737,281$ \\
+		\textbf{DDI-RDF} & $1,526$  & $9,673,055$  \\
     \bottomrule
@@
 
-We use \emph{SPIN}, 
-a SPARQL-based way to formulate and check constraints, as basis to develop a
-validation environment\footnote{Online demo available at \url{http://purl.org/net/rdfval-demo}, source code at: \url{https://github.com/boschthomas/rdf-validator}} to validate RDF data according to constraints expressed by arbitrary constraint languages\footnote{SPIN mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} \cite{BoschEckert2014-2}.
+We use \emph{SPIN}, a SPARQL-based way to formulate and check constraints, as basis to develop a
+validation environment\footnote{Online demo available at: \url{http://purl.org/net/rdfval-demo}, source code at: \url{https://github.com/boschthomas/rdf-validator}} to validate RDF data according to constraints expressed by arbitrary constraint languages\footnote{SPIN mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} \cite{BoschEckert2014-2}.
 
@@
 %Although accessible within our validation tool, we provide all implemented constraints\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} in form of SPARQL CONSTRUCT queries.
-The \emph{SPIN} engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.
-There is one \emph{SPIN} construct template for each constraint type.
-A \emph{SPIN} construct template contains a \emph{SPARQL CONSTRUCT} query which generates constraint violation triples indicating the subject and the properties causing constraint violations, and the reason why constraint violations have been raised.
-A \emph{SPIN} construct template creates constraint violation triples if all triple patterns within the \emph{SPARQL WHERE clause} match.
-%\emph{Missy}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}} provides comprehensive Linked Data services like diverse RDF exports of person-level metadata conforming to the \emph{Disco} vocabulary in form of multiple concrete syntaxes.
+The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.
+There is one SPIN construct template for each constraint type.
+A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples indicating the subject and the properties causing constraint violations and the reason why constraint violations have been raised.
+A SPIN construct template creates constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
+%\emph{Missy}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}} provides comprehensive Linked Data services like diverse RDF exports of person-level metadata conforming to the DDI-RDF vocabulary in form of multiple concrete syntaxes.
 
@@
     %\\       \textbf{Criteria}
-           %& \textbf{\emph{Disco}}
-           %& \textbf{\emph{QB}}
-					 %& \textbf{\emph{SKOS}}
+           %& \textbf{DDI-RDF}
+           %& \textbf{QB}
+					 %& \textbf{SKOS}
 					 %& \textbf{Total}
@@
 Tables \ref{tab:evaluation-constraint-violations-1} and \ref{tab:evaluation-constraint-violations-2} show the results of the evaluation, more specifically the constraints and the constraint violations, which are caused by these constraints, in percent.
-The constraints and their raised constraint violations are grouped by vocabulary, complexity level of their type, and their severity level.
+The constraints and their raised constraint violations are grouped by vocabulary, the classification of their type according to the expressivity of constraint languages, and their severity level.
 The numbers of evaluated triples and data sets differ between the vocabularies
-as we evaluated 3.8 billion \emph{QB}, 480 million \emph{SKOS}, and 10 million \emph{Disco} triples.
+as we evaluated 3.8 billion QB, 480 million SKOS, and 10 million DDI-RDF triples.
 To be able to formulate hypotheses which apply for all vocabularies, 
-we only use normalized relative values representing the percentage of constraints and constraint violations belonging to the respective class.
+we only use normalized relative values representing the percentage of constraints and violations belonging to the respective class.
 There is a strong overlap between \emph{RDFS/OWL Based} and \emph{Constraint Language Based} constraint types as in many cases constraint types are expressible by classical constraint languages and OWL.
-This is the reason why the percentage values of constraints and violations grouped by the classification according to the expressivity of constraint languages do not accumulate to 100\%.
+This is the reason why the percentage values of constraints and violations grouped by the classification of their types according to the expressivity of constraint languages do not accumulate to 100\%.
 
 %by building the arithmetic mean over the individual vocabularies' percentage values. 
-%\tb{More than 80\% of the overall approx. 55 million constraint violations are caused by \emph{QB} constraints.}
+%\tb{More than 80\% of the overall approx. 55 million constraint violations are caused by QB constraints.}
 
@@
     %\multirow{2}{*}{} &
-      %\multicolumn{2}{c}{\textbf{\emph{Disco}}} &
-      %\multicolumn{2}{c}{\textbf{\emph{QB}}} &
-      %\multicolumn{2}{c}{\textbf{\emph{SKOS}}} &
+      %\multicolumn{2}{c}{\textbf{DDI-RDF}} &
+      %\multicolumn{2}{c}{\textbf{QB}} &
+      %\multicolumn{2}{c}{\textbf{SKOS}} &
       %\multicolumn{2}{c}{\textbf{\emph{Total}}} \\
@@
     \multirow{2}{*}{} &
-      \multicolumn{2}{c}{\textbf{\emph{Disco}}} &
-      \multicolumn{2}{c}{\textbf{\emph{QB}}} \\
+      \multicolumn{2}{c}{\textbf{DDI-RDF}} &
+      \multicolumn{2}{c}{\textbf{QB}} \\
     \textbf{} & C & CV & C & CV \\
@@
     \multirow{2}{*}{} &
-      \multicolumn{2}{c}{\textbf{\emph{SKOS}}} &
+      \multicolumn{2}{c}{\textbf{SKOS}} &
       \multicolumn{2}{c}{\textbf{\emph{Total}}} \\
@@
 		\hline
-		\textbf{\emph{SPARQL}} & \textbf{80.0\%} & \textbf{100.0\%} & 59.7\% & 78.2\% \\
+		\textbf{\emph{SPARQL}} & \textbf{80.0\%} & \textbf{100.0\%} & \textbf{59.7\%} & \textbf{78.2\%} \\
 		\textbf{\emph{CL}} & 0.0\% & 0.0\% & 23.5\% & 21.8\% \\
@@
 %More than the half of them are $\mathcal{CT}_{B}$, nearly a third $\mathcal{CT}_{S}$, and only a sixth $\mathcal{CT}_{C}$ constraint types.
-%For \emph{Disco}, \emph{QB}, and \emph{SKOS}, more than 50\% of the instantiated constraint types are $\mathcal{CT}_{B}$ constraint types 
-%(for \emph{QB} even three quarters).
-%\emph{Existential quantifications} (\emph{R-86}, 32.4\%, \emph{Disco}), \emph{data model consistency} (31.4\%, \emph{QB}), and \emph{structure} (28.6\%, \emph{SKOS}) are the constraint types the most constraints are instantiated from.
+%For DDI-RDF, QB, and SKOS, more than 50\% of the instantiated constraint types are $\mathcal{CT}_{B}$ constraint types 
+%(for QB even three quarters).
+%\emph{Existential quantifications} (\emph{R-86}, 32.4\%, DDI-RDF), \emph{data model consistency} (31.4\%, QB), and \emph{structure} (28.6\%, SKOS) are the constraint types the most constraints are instantiated from.
 %\tb{1. Fakten (diese Fakten bewirken eine Erhöhung der Datenqualität) 2. Hypothese (unsere Interpretation der Ergebnisse, unsere Behauptung)}
-Almost 1/2 of all constraints and more than 1/2 of the \emph{Disco} and the \emph{QB} constraints are \emph{vocabulary constraints}.
-The \emph{SKOS} constraints are nearly to the same extend \emph{vocabulary}, \emph{simple}, and \emph{complex constraints}. 
+
+Almost 60\% of all constraints, nearly 1/2 of the DDI-RDF, more than 1/2 of the QB, and 80\% of the SKOS constraints are \emph{SPARQL Based}.
 %Hence, a significant amount of 46 \% of the constraints are directly extractable from formal specifications of well-established and newly defined vocabularies. 
-\begin{hyp}
+%\begin{hyp}
 %As a significant amount of 46 \% of the constraints are vocabulary constraints which can be expressed by modeling languages like RDF, RDFS, and OWL 2,
 %the further development of constraint languages should concentrate on expressing simple and especially complex constraints which up to now in most cases can only be expressed by plain SPARQL.   
-As a significant amount of 54\% of the constraints are either simple or complex constraints,
-the further development of constraint languages should concentrate on expressing simple and especially complex constraints which up to now in most cases can only be expressed by plain SPARQL.  
+%As a significant amount of 54\% of the constraints are either simple or complex constraints,
+%the further development of constraint languages should concentrate on expressing simple and especially complex constraints which up to now in most cases can only be expressed by plain SPARQL.  
+%\end{hyp}
+\begin{hyp}
+As a significant amount of almost 60\% of the constraints are \emph{SPARQL Based},
+the further development of constraint languages will especially concentrate on expressing such complex constraints which up to now in most cases can only be expressed by plain SPARQL. 
 \end{hyp}
 
-Nearly 1/2 of all violations are caused by \emph{complex constraints}, 1/3 by \emph{simple constraints}, and 1/5 by \emph{vocabulary constraints}.
-The fact that only 1/5 of all violations result from \emph{vocabulary constraints}, 
-even though, 46\% of all constraints are \emph{vocabulary constraints},
-indicates good data quality for all vocabularies with regard to their formal specifications.
+Nearly 40\% of all constraints are \emph{RDFS/OWL Based} and only 23.5\% of all constraints are \emph{Constraint Language Based}.
+
+\begin{hyp}
+The first step to make progress in the further development of constraint languages will be to cover the constraint types which can already be formulated using RDFS and OWL.
+\end{hyp}
+
+For well-established vocabularies, the most formulated constraints are \emph{SPARQL Based} (2/3).
+For newly developed vocabularies, however, the most expressed constraints are \emph{RDFS/OWL Based} ($>$1/2).
+
+\begin{hyp}
+The more elaborate a vocabulary is, the more detailed and complex constraints are defined by domain experts using plain SPARQL.
+\end{hyp}
+
+These constraints are of such complexity that they can only be expressed by SPARQL.
+It should be an incentive for language designers to devise languages which are more intuitive than SPARQL in a way that also domain experts, which are not familiar with SPARQL, can formulate respective constraints.
+
+Nearly 80\% of all violations are caused by \emph{SPARQL Based}, 1/5 by \emph{Constraint Language Based}, and 1/5 by \emph{RDFS/OWL Based} constraints.
+The fact that only 1/5 of all violations result from \emph{RDFS/OWL Based} constraints, even though, almost 40\% of all constraints are \emph{RDFS/OWL Based}, indicates good data quality for all vocabularies with regard to their formal specifications.
+
+\begin{hyp}
+Data corresponds to the formal specifications of its vocabularies the data is conforming to. This demonstrates that constraint formulation in general works. 
+\end{hyp}
 
 %\tb{je nach hypothese spezifische aufgaben um die hypothese zu beweisen}
-Moreover, while 2/3 of the \emph{Disco} violations result from \emph{vocabulary constraints},
-\emph{QB} violations are almost only raised by \emph{complex constraints}, and 
-nearly 80\% of the \emph{SKOS} violations are caused by \emph{simple constraints}.
-This means that for the well-established vocabularies \emph{QB} and \emph{SKOS}, \emph{vocabulary constraints} are almost completely satisfied which indicates generally a very impressive data quality, at least in the SBE domain and for the basic requirements.
+Moreover, while 2/3 of the DDI-RDF violations result from \emph{RDFS/OWL Based} constraints,
+QB and SKOS violations are almost only raised by \emph{SPARQL Based} constraints.
+This means that for the well-established vocabularies, \emph{RDFS/OWL Based} constraints are almost completely satisfied which indicates generally a very impressive data quality, at least in the \emph{SBE} domain and for the basic requirements.
 %This demonstrates that data providers take account of the formal specifications of well-established vocabularies.
-
-For \emph{Disco}, data providers still have to understand the vocabulary and of course, data can not have high quality if the specification is not yet stable.
+For DDI-RDF, data providers still have to understand the vocabulary and of course, data can not have high quality if the specification is not yet stable.
 
 \begin{hyp}
-Data corresponds to their formal specifications which demonstrates that constraint formulation in general works. 
+For well-established vocabularies, RDFS/OWL Based constraints are almost completely satisfied which indicates good data quality in general and that basic data quality requirements are met.
 \end{hyp}
@@
 and that early adopters did not properly understand its formal specification.
-Thus, published data may not be consistent with its current draft or version.
+Thus, published data may not be consistent with the current draft of its conforming vocabulary.
 In case newly developed vocabularies turn into well-established ones,
@@
 and formal specifications are more elaborated. 
-As a consequence, \emph{vocabulary constraints} are satisfied to a greater extend which leads to better data quality.
+As a consequence, \emph{RDFS/OWL Based} constraints are satisfied to a greater extend which leads to better data quality.
 
 \begin{hyp}
-A significant amount of 47\% of the violations refer to complex constraints that are not easily, concisely, and intuitively expressible by existing constraint languages which confirms the necessity to provide suitable constraint languages.
+A significant amount of narrowly 80\% of the violations refer to SPARQL Based constraints that are not easily, concisely, and intuitively expressible by existing high-level constraint languages or RDFS and OWL which confirms the necessity to provide suitable constraint languages.
+Thus, the development of constraint languages will focus on enabling to express constraints which can up to now only be formulated by plain SPARQL.
 \end{hyp}
 
-In general, \emph{vocabulary constraints} are expressible by either modeling languages (e.g., RDF, RDFS, \emph{OWL 2}) or constraint languages. 
-\emph{Simple constraints} and especially \emph{complex constraints}, however, are in most cases only expressible by plain SPARQL. 
-As almost 1/2 of all violations are caused by \emph{complex constraints}, 
-data quality can be significantly improved when suitable constraint languages are developed which enable to define \emph{complex constraints} in an easy, concise, and intuitive way.
+\emph{RDFS/OWL Based} constraints are expressible by the modeling languages RDFS and OWL 2.
+\emph{SPARQL Based} constraints, however, are only expressible by plain SPARQL.
+As almost 80\% of all violations are caused by \emph{SPARQL Based} constraints, data quality can be significantly improved when suitable constraint languages are developed which enable to define \emph{SPARQL Based} constraints in an easy, concise, and intuitive way.
 %Therefore, existing constraint languages have to be extended or new constraint languages have to be developed.
-1/2 of all constraints are \emph{error constraints} and
-10\% of all constraints are \emph{warning constraints}.
-\emph{Informational constraints} caused 1/3 and
-\emph{warning constraints} 2/3 of all violations.
+
+\begin{table}[H]
+		\scriptsize
+    \begin{center}
+		\caption{Constraints and Constraint Violations (1)}
+		\label{tab:evaluation-constraint-violations-1}
+    \begin{tabular}{@{}lcccc@{}}
+    %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
+    %\\  \cmidrule{2-3}
+		\hline
+    \multirow{2}{*}{} &
+      \multicolumn{2}{c}{\textbf{DDI-RDF}} &
+      \multicolumn{2}{c}{\textbf{QB}} \\
+    \textbf{} & C & CV & C & CV \\
+    \hline
+    %\\ \midrule
+		 & 143 & 3,575,002 & 35 & 45,635,861 \\
+		\hline
+		\textbf{\emph{SPARQL}} & 44.8\% & 34.7\% & \textbf{54.3\%} & \textbf{100.0\%} \\
+		\textbf{\emph{CL}} & 42.0\% & \textbf{65.3\%} & 28.6\% & 0.0\% \\
+		\textbf{\emph{RDFS/OWL}} & \textbf{51.8\%} & \textbf{65.3\%} & 42.9\% & 0.0\% \\
+		\hline
+		\textbf{\emph{info}} & \textbf{52.5\%} & \textbf{52.6\%} & 11.4\% & 0.0\% \\
+		\textbf{\emph{warning}} & 7.0\% & 29.4\% & 8.6\% & \textbf{99.8\%} \\
+		\textbf{\emph{error}} & 40.6\% & 18.0\% & \textbf{80.0\%} & 0.3\% \\
+    \bottomrule
+    \end{tabular}
+    \\ \emph{C (constraints), CV (constraint violations)}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+		\scriptsize
+    \begin{center}
+		\caption{Constraints and Constraint Violations (2)}
+		\label{tab:evaluation-constraint-violations-2}
+    \begin{tabular}{@{}lcccc@{}}
+    %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
+    %\\  \cmidrule{2-3}
+		\hline
+    \multirow{2}{*}{} &
+      \multicolumn{2}{c}{\textbf{SKOS}} &
+      \multicolumn{2}{c}{\textbf{\emph{Total}}} \\
+    \textbf{} & C & CV & C & CV \\
+    \hline
+    %\\ \midrule
+		 & 35 & 5,540,988 & 213 & 54,751,851 \\
+		\hline
+		\textbf{\emph{SPARQL}} & \textbf{80.0\%} & \textbf{100.0\%} & \textbf{59.7\%} & \textbf{78.2\%} \\
+		\textbf{\emph{CL}} & 0.0\% & 0.0\% & 23.5\% & 21.8\% \\
+		\textbf{\emph{RDFS/OWL}} & 20.0\% & 0.0\% & 38.2\% & 21.8\% \\
+		\hline
+		\textbf{\emph{info}} & \textbf{60.0\%} & 41.2\% & \textbf{41.3\%} & 31.3\% \\
+		\textbf{\emph{warning}} & 14.3\% & \textbf{58.8\%} & 10.0\% & \textbf{62.7\%} \\
+		\textbf{\emph{error}} & 25.7\% & 0.0\% & \textbf{48.8\%} & 6.1\%\\
+    \bottomrule
+    \end{tabular}
+    \\ \emph{C (constraints), CV (constraint violations)}
+    \end{center}
+\end{table}
+
+Almost 1/2 of all constraints are \emph{error}, 40\% are \emph{informational}, and 10\% are \emph{warning} constraints.
+\emph{Informational} constraints caused 1/3 and
+\emph{warning} constraints 2/3 of all violations.
 As the percentage of severe violations is very low for all vocabularies (6.1\%),
@@
 
-80\% of the \emph{QB} constraints are \emph{error constraints}.
-More than 50\% of the \emph{Disco} and \emph{SKOS} constraints, however, are \emph{informational constraints}.
-1/6 of the Disco violations are caused by \emph{error constraints} and
-almost all \emph{QB} violations and 59\% of the \emph{SKOS} violations are caused by \emph{warning constraints}.  
+80\% of the QB constraints are \emph{error} constraints.
+More than 50\% of the DDI-RDF and SKOS constraints, however, are \emph{informational} constraints.
+1/6 of the Disco violations are caused by \emph{error} constraints and
+almost all QB violations and 59\% of the SKOS violations are caused by \emph{warning} constraints.  
 For well-established vocabularies, data quality is high
@@
 
-%For the vocabularies \emph{Disco}, \emph{QB}, and \emph{SKOS}, we defined 213 constraints of 53 constraint types .
+%For the vocabularies DDI-RDF, QB, and SKOS, we defined 213 constraints of 53 constraint types .
 
@@
     %\\       \textbf{}
-           %& \textbf{\emph{Disco}}
-           %& \textbf{\emph{QB}}
-					 %& \textbf{\emph{SKOS}}
+           %& \textbf{DDI-RDF}
+           %& \textbf{QB}
+					 %& \textbf{SKOS}
 					 %& \textbf{Total}
-					 %& \textbf{\emph{Disco}}
-           %& \textbf{\emph{QB}}
-					 %& \textbf{\emph{SKOS}}
+					 %& \textbf{DDI-RDF}
+           %& \textbf{QB}
+					 %& \textbf{SKOS}
 					 %& \textbf{Total}
@@
 
-%The constraints responsible for the largest amounts of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916; \emph{Disco}), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102; \emph{QB}), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903; \emph{SKOS}).
+%The constraints responsible for the largest amounts of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916; DDI-RDF), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102; QB), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903; SKOS).
 
 Table \ref{tab:evaluation-complexity-severity} shows the relation between the complexity and the severity level of all 213 constraints.
-More than 1/2 of the \emph{vocabulary constraints} are \emph{error constraints},
-more than 3/4 of the \emph{simple constraints} are \emph{informational constraints}, and
-\emph{complex constraints} are to the same extend \emph{informational} or \emph{error constraints}.
+More than 1/2 of the \emph{vocabulary constraints} are \emph{error} constraints,
+more than 3/4 of the \emph{simple constraints} are \emph{informational} constraints, and
+\emph{complex constraints} are to the same extend \emph{informational} or \emph{error} constraints.
 
@@
 
-%In this paper, we showed in form of a complete real world running example how to represent metadata on person-level data (\emph{Disco}), metadata on aggregated data (\emph{QB}), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
+%In this paper, we showed in form of a complete real world running example how to represent metadata on person-level data (DDI-RDF), metadata on aggregated data (QB), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
 %We explained why RDF validation is important in this context and how metadata on person-level data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality\footnote{The first appendix of this paper describing each constraint in detail is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}} (\textbf{contribution 2}, section \ref{rdf-validation}).
@@
 
-%We implemented a validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages and to ensure correct syntax and semantics of diverse vocabularies such as \emph{Disco}, \emph{QB}, \emph{SKOS}, and \emph{PHDD} (section \ref{implementation}).
-%We exhaustively evaluated the metadata quality of large real world aggregated (\emph{QB}), person-level (\emph{Disco}), and thesauri (\emph{SKOS}) data sets (more than 4.2 billion triples and 15 thousand data sets) by means of 213  constraints of the majority of the constraint types\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).
+%We implemented a validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages and to ensure correct syntax and semantics of diverse vocabularies such as DDI-RDF, QB, SKOS, and \emph{PHDD} (section \ref{implementation}).
+%We exhaustively evaluated the metadata quality of large real world aggregated (QB), person-level (DDI-RDF), and thesauri (SKOS) data sets (more than 4.2 billion triples and 15 thousand data sets) by means of 213  constraints of the majority of the constraint types\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).
 
 We identified and published by today 82 types of constraints  that are required by various stakeholders for data applications.
-In close collaboration with several \emph{SBE} domain experts, we formulated 213 constraints of 53 different types on three different vocabularies (\emph{Disco}, \emph{QB}, and \emph{SKOS}) and classified them according to the complexity level of their type and their severity level.
+In close collaboration with several \emph{SBE} domain experts, we formulated 213 constraints of 53 different types on three different vocabularies (DDI-RDF, QB, and SKOS) and classified them according to the complexity level of their type and their severity level.
 
@@
 
-We have been really impressed by the high quality of the \emph{QB} and \emph{SKOS} data.
+We have been really impressed by the high quality of the QB and SKOS data.
 This is in contrast to the sometimes heard rumour that Linked Open Data lacks quality.

### 2015-07-15 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
evaluation

@@
 In this paper, we formulate 213 constraints of 53 different types on three different vocabularies (DDI-RDF, QB, and SKOS) and classify them according to the complexity level of their type and their severity level.
-For 114 of these constraints, we evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
+For 115 of these constraints, we evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
 Based on the results, we formulate several hypotheses to direct the further development of constraint languages.\textcolor{red}{81 constraint types instead of 82?}
@@
 In XML, the definition of schemas containing data constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
-With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration.
+With the rise of the Web of Data, data professionals and institutions are very interested in having their data be DDI-RDFvered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration.
 Therefore, not only established vocabularies like SKOS are used;
-recently, members of the \emph{SBE} and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (Disco)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.
+recently, members of the \emph{SBE} and Linked Data community developed with the \emph{DDI-RDF DDI-RDFvery Vocabulary (DDI-RDF)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/DDI-RDFvery.html}} a means to expose \emph{DDI} metadata as Linked Data.
 
@@
 As we do not want to base our conclusions on the evaluations of vocabularies and constraint definitions alone, we conducted a large-scale experiment.
-For 114 constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (DDI-RDF, QB, SKOS) obtained from 33 SPARQL endpoints.
+For 115 constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (DDI-RDF, QB, SKOS) obtained from 33 SPARQL endpoints.
 %evaluated the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
@@
 das habt ihr doch gar nicht gemacht sondern ganz allgemein constraints für vokabulare aufgestellt.
-Ist QB und Disco nicht sowieso unabhängig von konkreten Variablen?}\tb{das soll nur ein beipsiel sein, wann eine komplexere validierung im kontext von sbe sinn macht (1) + (2) sind vocabulary constraints und (3) + (4) sind complex constraints}
+Ist QB und DDI-RDF nicht sowieso unabhängig von konkreten Variablen?}\tb{das soll nur ein beipsiel sein, wann eine komplexere validierung im kontext von sbe sinn macht (1) + (2) sind vocabulary constraints und (3) + (4) sind complex constraints}
 
@@
 %\ke{Wieso jetzt wieder qb?}\tb{ich möchte zeigen wie aggregierte daten und personenbezogene daten in RDF verbunden sind. Weglassen?}
-%Aggregated (qb:DataSet) and underlying person-level data sets (\emph{disco:LogicalDataSet}) are connected by \emph{prov:wasDerivedFrom}. 
+%Aggregated (qb:DataSet) and underlying person-level data sets (\emph{DDI-RDF:LogicalDataSet}) are connected by \emph{prov:wasDerivedFrom}. 
 The aggregated variable \emph{formal childcare} is calculated on the basis of six person-level variables 
@@
 enabling researchers to replicate the results shown in aggregated data tables.
-The \emph{DDI-RDF Discovery Vocabulary (Disco)} is a vocabulary to represent metadata on person-level data in RDF.
-The series (\emph{disco:StudyGroup}) \emph{EU-SILC} contains one study (\emph{disco:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
+The \emph{DDI-RDF DDI-RDFvery Vocabulary (DDI-RDF)} is a vocabulary to represent metadata on person-level data in RDF.
+The series (\emph{DDI-RDF:StudyGroup}) \emph{EU-SILC} contains one study (\emph{DDI-RDF:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
 \emph{dcterms:spatial} points to the countries for which the data has been collected.
-The study \emph{EU-SILC 2011} contains eight person-level data sets (\emph{disco:LogicalDataSet})
-including person-level variables (\emph{disco:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
+The study \emph{EU-SILC 2011} contains eight person-level data sets (\emph{DDI-RDF:LogicalDataSet})
+including person-level variables (\emph{DDI-RDF:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
 %Metadata on person-level data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
@@
 Controlled vocabularies (\emph{skos:ConceptScheme}), serving as extension and reuse mechanism,
-organize types (\emph{skos:Concept}) of descriptive statistics (\emph{disco:SummaryStatistics}) like minimum, maximum, and arithmetic mean.
+organize types (\emph{skos:Concept}) of descriptive statistics (\emph{DDI-RDF:SummaryStatistics}) like minimum, maximum, and arithmetic mean.
 \emph{XKOS}\footnote{\url{https://github.com/linked-statistics/xkos}} is a SKOS extension to describe formal statistical classifications like the International Standard Classification of Occupations (\emph{ISCO}).
@@
 
-The classification of the 114 concrete constraints on three vocabularies according to severity levels is published in a second technical report serving as second appendix of this paper \cite{BoschZapilkoWackerowEckert2015}.
+The classification of the 115 concrete constraints on three vocabularies according to severity levels is published in a second technical report serving as second appendix of this paper \cite{BoschZapilkoWackerowEckert2015}.
 In the following, we summarize the results for the purpose of our evaluation.
@@
 %whereas, the violation of another constraint of the same type may be minor.
-\emph{SBE} experts determined the default \emph{severity level}\footnote{The possibility to define severity levels in vocabularies is in itself a requirement (\emph{R-158}).} for each of the 114 constraints to indicate how serious the violation of the constraint is.
+\emph{SBE} experts determined the default \emph{severity level}\footnote{The possibility to define severity levels in vocabularies is in itself a requirement (\emph{R-158}).} for each of the 115 constraints to indicate how serious the violation of the constraint is.
 We use the classification system of log messages in software development like \emph{Apache Log4j 2} \cite{Apache-2015}, the \emph{Java Logging API}\footnote{\url{http://docs.oracle.com/javase/7/docs/api/java/util/logging/Level.html}}, and the \emph{Apache Commons Logging API}\footnote{\url{http://commons.apache.org/proper/commons-logging/}} as many data practitioners also have experience in software development and software developers intuitively understand these levels.
@@
 %Thus, it is checked that all date values (e.g., {{\em dcterms:date}) are actually of the datatype \emph{xsd:date} and that \emph{xsd:nonNegativeInteger} values (e.g.
-\emph{disco:frequency}) are not negative\footnote{For simplicity reasons, we only assign severity levels to \emph{vocabulary constraints} if they differ from \emph{error}.}.
+\emph{DDI-RDF:frequency}) are not negative\footnote{For simplicity reasons, we only assign severity levels to \emph{vocabulary constraints} if they differ from \emph{error}.}.
 %Depending on property datatypes, two different literal values have
 %a specific ordering with respect to operators like \textless  (\emph{R-43: literal value comparison}).
-%Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}).
+%Start dates (\emph{DDI-RDF:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{DDI-RDF:endDate}).
 
@@
 \emph{xsd:string}).
-\emph{disco:CategoryStatistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString} (default severity level: \emph{error}).
+\emph{DDI-RDF:CategoryStatistics}, e.g., can only have \emph{DDI-RDF:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString} (default severity level: \emph{error}).
 %Validation should \emph{exploit sub-super relations} in vocabularies (\emph{R-224}).
@@
 %A \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column},
-%a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}), and a \emph{qb:DataSet} is structured by (\emph{qb:structure}) exactly one \emph{qb:DataStructureDefinition}.
+%a \emph{DDI-RDF:Variable} has at most one \emph{DDI-RDF:concept} relationship to a theoretical concept (\emph{skos:Concept}), and a \emph{qb:DataSet} is structured by (\emph{qb:structure}) exactly one \emph{qb:DataStructureDefinition}.
 %\begin{DL}
@@
 %With \emph{subsumption} (\emph{R-100}), one can state that \emph{xkos:ClassificationLevel} is a sub-class of \emph{skos:Collection}, i.e., each \emph{xkos:ClassificationLevel} must also be part of the \emph{skos:Collection} class extension.
-%With \emph{sub properties} (\emph{R-54, R-64}), one can state that \emph{disco:fundedBy} is a sub-property of \emph{dcterms:contributor} - i.e., if a study is funded by an organization, then this organization contributed to this study.
+%With \emph{sub properties} (\emph{R-54, R-64}), one can state that \emph{DDI-RDF:fundedBy} is a sub-property of \emph{dcterms:contributor} - i.e., if a study is funded by an organization, then this organization contributed to this study.
 %\begin{DL}
@@
 %
-%As we know that only person-level data sets (\emph{disco:LogicalDataSet}) can derive (\emph{disco:aggregation}) aggregated data sets (\emph{qb:DataSet}), 
-%{\em logical-data-set} is a \emph{disco:LogicalDataSet}, 
+%As we know that only person-level data sets (\emph{DDI-RDF:LogicalDataSet}) can derive (\emph{DDI-RDF:aggregation}) aggregated data sets (\emph{qb:DataSet}), 
+%{\em logical-data-set} is a \emph{DDI-RDF:LogicalDataSet}, 
 %and \emph{aggregated-data-set} is derived from \emph{logical-data-set},
@@
 %Reasoning may also cause constraint violations which are needed to enhance data quality.
-%With \emph{subsumption} (\emph{R-100}), one can state that \emph{disco:LogicalDataSet} is a sub-class of \emph{dcat:DataSet}, 
+%With \emph{subsumption} (\emph{R-100}), one can state that \emph{DDI-RDF:LogicalDataSet} is a sub-class of \emph{dcat:DataSet}, 
 %i.e., each person-level data set is also a catalog data set.
@@
 %
-%By stating that \emph{disco:fundedBy} is a sub property of \emph{dcterms:contributor},
+%By stating that \emph{DDI-RDF:fundedBy} is a sub property of \emph{dcterms:contributor},
 %the {\em sub property} (\emph{R-54, R-64}) above assures that if a series is funded by an organization, then the organization must also contribute to the series.
-%In case the \emph{sub-property} is applied without reasoning and $\mathcal{K}$ contains the triple \ms{disco:fundedBy} \ms{(EU-SILC,} \ms{organization)},
+%In case the \emph{sub-property} is applied without reasoning and $\mathcal{K}$ contains the triple \ms{DDI-RDF:fundedBy} \ms{(EU-SILC,} \ms{organization)},
 %a constraint violation is thrown if $\mathcal{K}$ does not explicitly include the triple \ms{dcterms:contributor} \ms{(EU-SILC,} \ms{organization)}.
@@
 %Such constraints are defined for each object property for which a semantically equivalent object property pointing from the other direction would also be possible but is not defined within the vocabulary.
-%A \emph{disco:Variable}, e.g., may be based on (\emph{disco:basedOn}) a \emph{disco:RepresentedVariable}.
-%A \emph{disco:RepresentedVariable}, however, cannot be based on a \emph{disco:Variable} (\ms{$disco:basedOn \sqcap disco:basedOn^{-} \sqsubseteq \bot$}).
+%A \emph{DDI-RDF:Variable}, e.g., may be based on (\emph{DDI-RDF:basedOn}) a \emph{DDI-RDF:RepresentedVariable}.
+%A \emph{DDI-RDF:RepresentedVariable}, however, cannot be based on a \emph{DDI-RDF:Variable} (\ms{$DDI-RDF:basedOn \sqcap DDI-RDF:basedOn^{-} \sqsubseteq \bot$}).
 
@@
 %A \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column},
-%a \emph{disco:Variable} has at most one \emph{disco:concept} relationship to a theoretical concept (\emph{skos:Concept}), and a \emph{qb:DataSet} is structured by (\emph{qb:structure}) exactly one \emph{qb:DataStructureDefinition}.
+%a \emph{DDI-RDF:Variable} has at most one \emph{DDI-RDF:concept} relationship to a theoretical concept (\emph{skos:Concept}), and a \emph{qb:DataSet} is structured by (\emph{qb:structure}) exactly one \emph{qb:DataStructureDefinition}.
 %DATA-CUBE-C-MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-
@@
 %\emph{Value is valid for datatype} (\emph{R-223}) constraints serve to make sure that all literal values are valid with regard to their datatypes - as stated in the vocabularies.
-%Thus, it is checked that all date values (e.g., {{\em dcterms:date}, \em disco:startDate}, {\em disco:endDate}) are actually of the datatype \emph{xsd:date} and that \emph{xsd:nonNegativeInteger} values (e.g.
-\emph{disco:frequency}) are not negative.
+%Thus, it is checked that all date values (e.g., {{\em dcterms:date}, \em DDI-RDF:startDate}, {\em DDI-RDF:endDate}) are actually of the datatype \emph{xsd:date} and that \emph{xsd:nonNegativeInteger} values (e.g.
+\emph{DDI-RDF:frequency}) are not negative.
 %Depending on property datatypes, two different literal values have
 %a specific ordering with respect to operators like \textless  (\emph{R-43: literal value comparison}).
-%Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}).
+%Start dates (\emph{DDI-RDF:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{DDI-RDF:endDate}).
 %
@@
 \emph{xsd:string}).
-%\emph{disco:CategoryStatistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString}.
+%\emph{DDI-RDF:CategoryStatistics}, e.g., can only have \emph{DDI-RDF:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString}.
 %Validation should \emph{exploit sub-super relations} in vocabularies (\emph{R-224}).
@@
 \textcolor{red}{\emph{Default values}} (\emph{R-31, R-38}) for objects/literals of given properties are inferred automatically when properties are not present in the data.
-The value \emph{true} for the property {\em disco:isPublic} indicates that a {\em disco:LogicalDataSet} can be accessed by anyone.
+The value \emph{true} for the property {\em DDI-RDF:isPublic} indicates that a {\em DDI-RDF:LogicalDataSet} can be accessed by anyone.
 Per default, however, access to data sets should be restricted (\emph{false}) ($\mathcal{SL}_{0}$).
 Many properties are not necessarily required but \emph{recommended} within a particular context (\emph{R-72}).
-The property {\em skos:notation}, e.g., is not mandatory for {\em disco:Variable}s, but recommended to represent variable names ($\mathcal{SL}_{0}$).
+The property {\em skos:notation}, e.g., is not mandatory for {\em DDI-RDF:Variable}s, but recommended to represent variable names ($\mathcal{SL}_{0}$).
 
@@
 a specific ordering with respect to operators like \textless  (\textcolor{red}{\emph{R-43: literal value comparison}}).
-Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}).
+Start dates (\emph{DDI-RDF:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{DDI-RDF:endDate}).
 
 Percentage values are only valid when they are within the literal range of 0 and 100 (\emph{R-45: literal ranges}; \emph{error})
-which is checked for \emph{disco:percentage} standing for the number of cases of a given code in relation to the total number of cases for a particular variable.
+which is checked for \emph{DDI-RDF:percentage} standing for the number of cases of a given code in relation to the total number of cases for a particular variable.
 
@@
 \emph{qb:Observation} \emph{O}, then the \emph{qb:DataSet} corresponding to \emph{O} must be \emph{D} (\emph{warning}).
-%Relative frequencies of variable codes are calculated correctly, if the cumulative percentage (\emph{disco:cumulativePercentage}) of a given code exactly matches the cumulative percentage of the previous code
-%plus the percentage value (\emph{disco:percentage}) of the current code ($\mathcal{SL}_{2}$).
+%Relative frequencies of variable codes are calculated correctly, if the cumulative percentage (\emph{DDI-RDF:cumulativePercentage}) of a given code exactly matches the cumulative percentage of the previous code
+%plus the percentage value (\emph{DDI-RDF:percentage}) of the current code ($\mathcal{SL}_{2}$).
 %{\em Mathematical Operations} (\emph{R-41, R-42}; e.g. date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
@@
 %Summary statistics types like minimum, maximum, and arithmetic mean are maintained within a controlled vocabulary.  
-%Thus, summary statistics can only have \emph{disco:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType}, a \emph{skos:ConceptScheme} ($\mathcal{SL}_{2}$).
+%Thus, summary statistics can only have \emph{DDI-RDF:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType}, a \emph{skos:ConceptScheme} ($\mathcal{SL}_{2}$).
 Objects/literals can be declared to be ordered for given properties (\emph{R-121/217: ordering}).
@@
 %If a {\em skos:Concept} represents a code (having {\em skos:notation} and {\em skos:prefLabel} properties), 
-%then the property {\em disco:isValid} has to be stated indicating if the code stands for valid (\emph{true}) or missing (\emph{false}) cases ($\mathcal{SL}_{2}$).
+%then the property {\em DDI-RDF:isValid} has to be stated indicating if the code stands for valid (\emph{true}) or missing (\emph{false}) cases ($\mathcal{SL}_{2}$).
 
@@
 %If a {\em skos:Concept} represents a code (having {\em skos:notation} and {\em skos:prefLabel} properties), 
-%then the property {\em disco:isValid} has to be stated indicating if the code stands for valid (\emph{true}) or missing (\emph{false}) cases (\emph{R-71}; $\mathcal{SL}_{2}$).
+%then the property {\em DDI-RDF:isValid} has to be stated indicating if the code stands for valid (\emph{true}) or missing (\emph{false}) cases (\emph{R-71}; $\mathcal{SL}_{2}$).
 %Variables may have at least one relationship to a theoretical concept ({\emph{R-86}; $\mathcal{SL}_{0}$).
@@
 %\textbf{Descriptive Statistics.}
-%The property \emph{disco:percentage} stands for the number of cases of a given code in relation to the total number of cases for a particular variable within a data set.
+%The property \emph{DDI-RDF:percentage} stands for the number of cases of a given code in relation to the total number of cases for a particular variable within a data set.
 %Percentage values are only valid when they are within the \emph{literal range} of 0 and 100 (\emph{R-45}; $\mathcal{SL}_{2}$).
@@
 %Codes (\emph{skos:Concept}) are ordered and therefore have fixed positions in an ordered collection (\emph{skos:OrderedCollection}) within variable representations.
-%In order to check the correctness of relative frequencies' calculations, the cumulative percentage (\emph{disco:cumulativePercentage}) of the current code must exactly be the cumulative percentage of the previous code
-%plus the percentage value (\emph{disco:percentage}) of the current code (\emph{data model consistency}; $\mathcal{SL}_{2}$).
+%In order to check the correctness of relative frequencies' calculations, the cumulative percentage (\emph{DDI-RDF:cumulativePercentage}) of the current code must exactly be the cumulative percentage of the previous code
+%plus the percentage value (\emph{DDI-RDF:percentage}) of the current code (\emph{data model consistency}; $\mathcal{SL}_{2}$).
 %
@@
 %Summary statistics types like minimum, maximum, and arithmetic mean are maintained within a controlled vocabulary.  
-%Summary statistics can only have \emph{disco:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType}, a \emph{skos:ConceptScheme} ($\mathcal{SL}_{2}$).
+%Summary statistics can only have \emph{DDI-RDF:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType}, a \emph{skos:ConceptScheme} ($\mathcal{SL}_{2}$).
 %
@@
 %a specific ordering with respect to an operator like \textless (\emph{R-43: literal value comparison}).
-%Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}) ($\mathcal{SL}_{2}$).
+%Start dates (\emph{DDI-RDF:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{DDI-RDF:endDate}) ($\mathcal{SL}_{2}$).
 %
@@
 %Objects and literals can be \emph{ordered} (\emph{R-121, R-217}) for given properties.
-%\emph{Disco }variables, questions, and codes/categories are typically organized in a particular order. 
+%\emph{DDI-RDF }variables, questions, and codes/categories are typically organized in a particular order. 
 %If a variable code list should be ordered, the variable representation should be of the type \emph{skos:OrderedCollection} containing multiple codes/categories (each represented as \emph{skos:Concept}) in a \emph{skos:memberList}.
@@
 
-%\ke{Überarbeiten und mit nächstem teil mergen. Nur das erzählen, was für die Auswertung auf den Datensets relevant ist. 114 constraints, 3 vokabulare, wie wurden die datasets daraufhin validiert.}
+%\ke{Überarbeiten und mit nächstem teil mergen. Nur das erzählen, was für die Auswertung auf den Datensets relevant ist. 115 constraints, 3 vokabulare, wie wurden die datasets daraufhin validiert.}
 
@@
 %in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$).
-On the three vocabularies (DDI-RDF, QB, SKOS), we identified and classified 114 constraints\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} which we implemented for the data validation.
+On the three vocabularies (DDI-RDF, QB, SKOS), we identified and classified 115 constraints\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} which we implemented for the data validation.
 We ensured that the implementation of the constraints is equally distributed over the classes and vocabularies we have.
-We then evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data using these 114 constraints, obtained from 33 SPARQL endpoints.
+We then evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data using these 115 constraints, obtained from 33 SPARQL endpoints.
 
@@
 (3) DDI-RDF data sets provided by the \emph{Microdata Information System}, 
-the \emph{Data Without Boundaries Discovery Portal}, the
+the \emph{Data Without Boundaries DDI-RDFvery Portal}, the
 \emph{Danish Data Archive}, and the
@@
 Tables \ref{tab:evaluation-constraint-violations-1} and \ref{tab:evaluation-constraint-violations-2} show the results of the evaluation, more specifically the constraints and the constraint violations, which are caused by these constraints, in percent.
+The first numbers indicate the absolute amount of constraints and violations.
 The constraints and their raised constraint violations are grouped by vocabulary, the classification of their type according to the expressivity of constraint languages, and their severity level.
@@
 
-\begin{table}[H]
-		\scriptsize
-    \begin{center}
-		\caption{OLD}
-		\label{tab:evaluation-constraint-violations-1}
-    \begin{tabular}{@{}lcccc@{}}
-    %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
-    %\\  \cmidrule{2-3}
-		\hline
-    \multirow{2}{*}{} &
-      \multicolumn{2}{c}{\textbf{DDI-RDF}} &
-      \multicolumn{2}{c}{\textbf{QB}} \\
-    \textbf{} & C & CV & C & CV \\
-    \hline
-    %\\ \midrule
-		 & 143 & 3,575,002 & 35 & 45,635,861 \\
-		\hline
-		\textbf{\emph{complex}} & 25.9\% & 18.3\% & 37.1\% & \textbf{100.0\%} \\
-		\textbf{\emph{simple}} & 19.6\% & 15.7\% & 8.6\% & 0.0\% \\
-		\textbf{\emph{vocabulary}} & \textbf{54.6\%} & \textbf{66.1\%} & \textbf{54.3\%} & 0.0\% \\
-		\hline
-		\textbf{\emph{info}} & \textbf{52.5\%} & \textbf{52.6\%} & 11.4\% & 0.0\% \\
-		\textbf{\emph{warning}} & 7.0\% & 29.4\% & 8.6\% & \textbf{99.8\%} \\
-		\textbf{\emph{error}} & 40.6\% & 18.0\% & \textbf{80.0\%} & 0.3\% \\
-    \bottomrule
-    \end{tabular}
-    \\ \emph{C (constraints), CV (constraint violations)}
-    \end{center}
-\end{table}
-
-\begin{table}[H]
-		\scriptsize
-    \begin{center}
-		\caption{OLD}
-		\label{tab:evaluation-constraint-violations-2}
-    \begin{tabular}{@{}lcccc@{}}
-    %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
-    %\\  \cmidrule{2-3}
-		\hline
-    \multirow{2}{*}{} &
-      \multicolumn{2}{c}{\textbf{SKOS}} &
-      \multicolumn{2}{c}{\textbf{\emph{Total}}} \\
-    \textbf{} & C & CV & C & CV \\
-    \hline
-    %\\ \midrule
-		 & 35 & 5,540,988 & 213 & 54,751,851 \\
-		\hline
-		\textbf{\emph{complex}} & \textbf{37.1\%} & 21.4\% & 33.4\% & \textbf{46.6\%} \\
-		\textbf{\emph{simple}} & \textbf{34.3\%} & \textbf{78.6\%} & 20.8\% & 31.4\% \\
-		\textbf{\emph{vocabulary}} & \textbf{28.6\%} & 0.0\% & \textbf{45.8\%} & 22.0\% \\
-		\hline
-		\textbf{\emph{info}} & \textbf{60.0\%} & 41.2\% & \textbf{41.3\%} & 31.3\% \\
-		\textbf{\emph{warning}} & 14.3\% & \textbf{58.8\%} & 10.0\% & \textbf{62.7\%} \\
-		\textbf{\emph{error}} & 25.7\% & 0.0\% & \textbf{48.8\%} & 6.1\%\\
-    \bottomrule
-    \end{tabular}
-    \\ \emph{C (constraints), CV (constraint violations)}
-    \end{center}
-\end{table}
+%\begin{table}[H]
+		%\scriptsize
+    %\begin{center}
+		%\caption{OLD}
+		%\label{tab:evaluation-constraint-violations-1}
+    %\begin{tabular}{@{}lcccc@{}}
+    %%       & \multicolumn{2}{c}{\textbf{Vocabularies}}
+    %%\\  \cmidrule{2-3}
+		%\hline
+    %\multirow{2}{*}{} &
+      %\multicolumn{2}{c}{\textbf{DDI-RDF}} &
+      %\multicolumn{2}{c}{\textbf{QB}} \\
+    %\textbf{} & C & CV & C & CV \\
+    %\hline
+    %%\\ \midrule
+		 %& 143 & 3,575,002 & 35 & 45,635,861 \\
+		%\hline
+		%\textbf{\emph{complex}} & 25.9\% & 18.3\% & 37.1\% & \textbf{100.0\%} \\
+		%\textbf{\emph{simple}} & 19.6\% & 15.7\% & 8.6\% & 0.0\% \\
+		%\textbf{\emph{vocabulary}} & \textbf{54.6\%} & \textbf{66.1\%} & \textbf{54.3\%} & 0.0\% \\
+		%\hline
+		%\textbf{\emph{info}} & \textbf{52.5\%} & \textbf{52.6\%} & 11.4\% & 0.0\% \\
+		%\textbf{\emph{warning}} & 7.0\% & 29.4\% & 8.6\% & \textbf{99.8\%} \\
+		%\textbf{\emph{error}} & 40.6\% & 18.0\% & \textbf{80.0\%} & 0.3\% \\
+    %\bottomrule
+    %\end{tabular}
+    %\\ \emph{C (constraints), CV (constraint violations)}
+    %\end{center}
+%\end{table}
+%
+%\begin{table}[H]
+		%\scriptsize
+    %\begin{center}
+		%\caption{OLD}
+		%\label{tab:evaluation-constraint-violations-2}
+    %\begin{tabular}{@{}lcccc@{}}
+    %%       & \multicolumn{2}{c}{\textbf{Vocabularies}}
+    %%\\  \cmidrule{2-3}
+		%\hline
+    %\multirow{2}{*}{} &
+      %\multicolumn{2}{c}{\textbf{SKOS}} &
+      %\multicolumn{2}{c}{\textbf{\emph{Total}}} \\
+    %\textbf{} & C & CV & C & CV \\
+    %\hline
+    %%\\ \midrule
+		 %& 35 & 5,540,988 & 213 & 54,751,851 \\
+		%\hline
+		%\textbf{\emph{complex}} & \textbf{37.1\%} & 21.4\% & 33.4\% & \textbf{46.6\%} \\
+		%\textbf{\emph{simple}} & \textbf{34.3\%} & \textbf{78.6\%} & 20.8\% & 31.4\% \\
+		%\textbf{\emph{vocabulary}} & \textbf{28.6\%} & 0.0\% & \textbf{45.8\%} & 22.0\% \\
+		%\hline
+		%\textbf{\emph{info}} & \textbf{60.0\%} & 41.2\% & \textbf{41.3\%} & 31.3\% \\
+		%\textbf{\emph{warning}} & 14.3\% & \textbf{58.8\%} & 10.0\% & \textbf{62.7\%} \\
+		%\textbf{\emph{error}} & 25.7\% & 0.0\% & \textbf{48.8\%} & 6.1\%\\
+    %\bottomrule
+    %\end{tabular}
+    %\\ \emph{C (constraints), CV (constraint violations)}
+    %\end{center}
+%\end{table}
+
+%\begin{table}[H]
+		%\scriptsize
+    %\begin{center}
+		%\caption{Constraints and Constraint Violations (1)}
+		%\label{tab:evaluation-constraint-violations-1}
+    %\begin{tabular}{@{}lcccc@{}}
+    %%       & \multicolumn{2}{c}{\textbf{Vocabularies}}
+    %%\\  \cmidrule{2-3}
+		%\hline
+    %\multirow{2}{*}{} &
+      %\multicolumn{2}{c}{\textbf{DDI-RDF}} &
+      %\multicolumn{2}{c}{\textbf{QB}} \\
+    %\textbf{} & C & CV & C & CV \\
+    %\hline
+    %%\\ \midrule
+		 %& 143 & 3,575,002 & 35 & 45,635,861 \\
+		%\hline
+		%\textbf{\emph{SPARQL}} & 44.8\% & 34.7\% & \textbf{54.3\%} & \textbf{100.0\%} \\
+		%\textbf{\emph{CL}} & 42.0\% & \textbf{65.3\%} & 28.6\% & 0.0\% \\
+		%\textbf{\emph{RDFS/OWL}} & \textbf{51.8\%} & \textbf{65.3\%} & 42.9\% & 0.0\% \\
+		%\hline
+		%\textbf{\emph{info}} & \textbf{52.5\%} & \textbf{52.6\%} & 11.4\% & 0.0\% \\
+		%\textbf{\emph{warning}} & 7.0\% & 29.4\% & 8.6\% & \textbf{99.8\%} \\
+		%\textbf{\emph{error}} & 40.6\% & 18.0\% & \textbf{80.0\%} & 0.3\% \\
+    %\bottomrule
+    %\end{tabular}
+    %\\ \emph{C (constraints), CV (constraint violations)}
+    %\end{center}
+%\end{table}
+%
+%\begin{table}[H]
+		%\scriptsize
+    %\begin{center}
+		%\caption{Constraints and Constraint Violations (2)}
+		%\label{tab:evaluation-constraint-violations-2}
+    %\begin{tabular}{@{}lcccc@{}}
+    %%       & \multicolumn{2}{c}{\textbf{Vocabularies}}
+    %%\\  \cmidrule{2-3}
+		%\hline
+    %\multirow{2}{*}{} &
+      %\multicolumn{2}{c}{\textbf{SKOS}} &
+      %\multicolumn{2}{c}{\textbf{\emph{Total}}} \\
+    %\textbf{} & C & CV & C & CV \\
+    %\hline
+    %%\\ \midrule
+		 %& 35 & 5,540,988 & 213 & 54,751,851 \\
+		%\hline
+		%\textbf{\emph{SPARQL}} & \textbf{80.0\%} & \textbf{100.0\%} & \textbf{59.7\%} & \textbf{78.2\%} \\
+		%\textbf{\emph{CL}} & 0.0\% & 0.0\% & 23.5\% & 21.8\% \\
+		%\textbf{\emph{RDFS/OWL}} & 20.0\% & 0.0\% & 38.2\% & 21.8\% \\
+		%\hline
+		%\textbf{\emph{info}} & \textbf{60.0\%} & 41.2\% & \textbf{41.3\%} & 31.3\% \\
+		%\textbf{\emph{warning}} & 14.3\% & \textbf{58.8\%} & 10.0\% & \textbf{62.7\%} \\
+		%\textbf{\emph{error}} & 25.7\% & 0.0\% & \textbf{48.8\%} & 6.1\%\\
+    %\bottomrule
+    %\end{tabular}
+    %\\ \emph{C (constraints), CV (constraint violations)}
+    %\end{center}
+%\end{table}
 
@@
     %\\ \midrule
-		 & 143 & 3,575,002 & 35 & 45,635,861 \\
-		\hline
-		\textbf{\emph{SPARQL}} & 44.8\% & 34.7\% & \textbf{54.3\%} & \textbf{100.0\%} \\
-		\textbf{\emph{CL}} & 42.0\% & \textbf{65.3\%} & 28.6\% & 0.0\% \\
-		\textbf{\emph{RDFS/OWL}} & \textbf{51.8\%} & \textbf{65.3\%} & 42.9\% & 0.0\% \\
-		\hline
-		\textbf{\emph{info}} & \textbf{52.5\%} & \textbf{52.6\%} & 11.4\% & 0.0\% \\
-		\textbf{\emph{warning}} & 7.0\% & 29.4\% & 8.6\% & \textbf{99.8\%} \\
-		\textbf{\emph{error}} & 40.6\% & 18.0\% & \textbf{80.0\%} & 0.3\% \\
+		 & 78 & 3,575,002 & 20 & 45,635,861 \\
+		\hline
+		\textbf{\emph{SPARQL}} & 29.5 & 34.7 & \textbf{60.0} & \textbf{100.0} \\
+		\textbf{\emph{CL}} & \textbf{64.1} & \textbf{65.3} & 40.0 & 0.0 \\
+		\textbf{\emph{RDFS/OWL}} & \textbf{66.7} & \textbf{65.3} & 40.0 & 0.0 \\
+		\hline
+		\textbf{\emph{info}} & \textbf{52.5} & \textbf{52.6} & 11.4 & 0.0 \\
+		\textbf{\emph{warning}} & 7.0 & 29.4 & 8.6 & \textbf{99.8} \\
+		\textbf{\emph{error}} & 40.6 & 18.0 & \textbf{80.0} & 0.3 \\
     \bottomrule
@@
     %\\ \midrule
-		 & 35 & 5,540,988 & 213 & 54,751,851 \\
-		\hline
-		\textbf{\emph{SPARQL}} & \textbf{80.0\%} & \textbf{100.0\%} & \textbf{59.7\%} & \textbf{78.2\%} \\
-		\textbf{\emph{CL}} & 0.0\% & 0.0\% & 23.5\% & 21.8\% \\
-		\textbf{\emph{RDFS/OWL}} & 20.0\% & 0.0\% & 38.2\% & 21.8\% \\
-		\hline
-		\textbf{\emph{info}} & \textbf{60.0\%} & 41.2\% & \textbf{41.3\%} & 31.3\% \\
-		\textbf{\emph{warning}} & 14.3\% & \textbf{58.8\%} & 10.0\% & \textbf{62.7\%} \\
-		\textbf{\emph{error}} & 25.7\% & 0.0\% & \textbf{48.8\%} & 6.1\%\\
+		 & 17 & 5,540,988 & 115 & 54,751,851 \\
+		\hline
+		\textbf{\emph{SPARQL}} & \textbf{100.0} & \textbf{100.0} & \textbf{59.7} & \textbf{78.2} \\
+		\textbf{\emph{CL}} & 0.0 & 0.0 & 23.5 & 21.8 \\
+		\textbf{\emph{RDFS/OWL}} & 0.0 & 0.0 & 38.2 & 21.8 \\
+		\hline
+		\textbf{\emph{info}} & \textbf{60.0} & 41.2 & \textbf{41.3} & 31.3 \\
+		\textbf{\emph{warning}} & 14.3 & \textbf{58.8} & 10.0 & \textbf{62.7} \\
+		\textbf{\emph{error}} & 25.7 & 0.0 & \textbf{48.8} & 6.1\\
     \bottomrule
@@
 
-\begin{table}[H]
-		\scriptsize
-    \begin{center}
-		\caption{Constraints and Constraint Violations (1)}
-		\label{tab:evaluation-constraint-violations-1}
-    \begin{tabular}{@{}lcccc@{}}
-    %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
-    %\\  \cmidrule{2-3}
-		\hline
-    \multirow{2}{*}{} &
-      \multicolumn{2}{c}{\textbf{DDI-RDF}} &
-      \multicolumn{2}{c}{\textbf{QB}} \\
-    \textbf{} & C & CV & C & CV \\
-    \hline
-    %\\ \midrule
-		 & 143 & 3,575,002 & 35 & 45,635,861 \\
-		\hline
-		\textbf{\emph{SPARQL}} & 44.8\% & 34.7\% & \textbf{54.3\%} & \textbf{100.0\%} \\
-		\textbf{\emph{CL}} & 42.0\% & \textbf{65.3\%} & 28.6\% & 0.0\% \\
-		\textbf{\emph{RDFS/OWL}} & \textbf{51.8\%} & \textbf{65.3\%} & 42.9\% & 0.0\% \\
-		\hline
-		\textbf{\emph{info}} & \textbf{52.5\%} & \textbf{52.6\%} & 11.4\% & 0.0\% \\
-		\textbf{\emph{warning}} & 7.0\% & 29.4\% & 8.6\% & \textbf{99.8\%} \\
-		\textbf{\emph{error}} & 40.6\% & 18.0\% & \textbf{80.0\%} & 0.3\% \\
-    \bottomrule
-    \end{tabular}
-    \\ \emph{C (constraints), CV (constraint violations)}
-    \end{center}
-\end{table}
-
-\begin{table}[H]
-		\scriptsize
-    \begin{center}
-		\caption{Constraints and Constraint Violations (2)}
-		\label{tab:evaluation-constraint-violations-2}
-    \begin{tabular}{@{}lcccc@{}}
-    %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
-    %\\  \cmidrule{2-3}
-		\hline
-    \multirow{2}{*}{} &
-      \multicolumn{2}{c}{\textbf{SKOS}} &
-      \multicolumn{2}{c}{\textbf{\emph{Total}}} \\
-    \textbf{} & C & CV & C & CV \\
-    \hline
-    %\\ \midrule
-		 & 35 & 5,540,988 & 213 & 54,751,851 \\
-		\hline
-		\textbf{\emph{SPARQL}} & \textbf{80.0\%} & \textbf{100.0\%} & \textbf{59.7\%} & \textbf{78.2\%} \\
-		\textbf{\emph{CL}} & 0.0\% & 0.0\% & 23.5\% & 21.8\% \\
-		\textbf{\emph{RDFS/OWL}} & 20.0\% & 0.0\% & 38.2\% & 21.8\% \\
-		\hline
-		\textbf{\emph{info}} & \textbf{60.0\%} & 41.2\% & \textbf{41.3\%} & 31.3\% \\
-		\textbf{\emph{warning}} & 14.3\% & \textbf{58.8\%} & 10.0\% & \textbf{62.7\%} \\
-		\textbf{\emph{error}} & 25.7\% & 0.0\% & \textbf{48.8\%} & 6.1\%\\
-    \bottomrule
-    \end{tabular}
-    \\ \emph{C (constraints), CV (constraint violations)}
-    \end{center}
-\end{table}
-
-Almost 1/2 of all constraints are \emph{error}, 40\% are \emph{informational}, and 10\% are \emph{warning} constraints.
+%\begin{table}[H]
+		%\scriptsize
+    %\begin{center}
+		%\caption{Constraints and Constraint Violations (1)}
+		%\label{tab:evaluation-constraint-violations-1}
+    %\begin{tabular}{@{}lcccc@{}}
+    %%       & \multicolumn{2}{c}{\textbf{Vocabularies}}
+    %%\\  \cmidrule{2-3}
+		%\hline
+    %\multirow{2}{*}{} &
+      %\multicolumn{2}{c}{\textbf{DDI-RDF}} &
+      %\multicolumn{2}{c}{\textbf{QB}} \\
+    %\textbf{} & C & CV & C & CV \\
+    %\hline
+    %%\\ \midrule
+		 %& 143 & 3,575,002 & 35 & 45,635,861 \\
+		%\hline
+		%\textbf{\emph{SPARQL}} & 44.8\% & 34.7\% & \textbf{54.3\%} & \textbf{100.0\%} \\
+		%\textbf{\emph{CL}} & 42.0\% & \textbf{65.3\%} & 28.6\% & 0.0\% \\
+		%\textbf{\emph{RDFS/OWL}} & \textbf{51.8\%} & \textbf{65.3\%} & 42.9\% & 0.0\% \\
+		%\hline
+		%\textbf{\emph{info}} & \textbf{52.5\%} & \textbf{52.6\%} & 11.4\% & 0.0\% \\
+		%\textbf{\emph{warning}} & 7.0\% & 29.4\% & 8.6\% & \textbf{99.8\%} \\
+		%\textbf{\emph{error}} & 40.6\% & 18.0\% & \textbf{80.0\%} & 0.3\% \\
+    %\bottomrule
+    %\end{tabular}
+    %\\ \emph{C (constraints), CV (constraint violations)}
+    %\end{center}
+%\end{table}
+%
+%\begin{table}[H]
+		%\scriptsize
+    %\begin{center}
+		%\caption{Constraints and Constraint Violations (2)}
+		%\label{tab:evaluation-constraint-violations-2}
+    %\begin{tabular}{@{}lcccc@{}}
+    %%       & \multicolumn{2}{c}{\textbf{Vocabularies}}
+    %%\\  \cmidrule{2-3}
+		%\hline
+    %\multirow{2}{*}{} &
+      %\multicolumn{2}{c}{\textbf{SKOS}} &
+      %\multicolumn{2}{c}{\textbf{\emph{Total}}} \\
+    %\textbf{} & C & CV & C & CV \\
+    %\hline
+    %%\\ \midrule
+		 %& 35 & 5,540,988 & 213 & 54,751,851 \\
+		%\hline
+		%\textbf{\emph{SPARQL}} & \textbf{80.0\%} & \textbf{100.0\%} & \textbf{59.7\%} & \textbf{78.2\%} \\
+		%\textbf{\emph{CL}} & 0.0\% & 0.0\% & 23.5\% & 21.8\% \\
+		%\textbf{\emph{RDFS/OWL}} & 20.0\% & 0.0\% & 38.2\% & 21.8\% \\
+		%\hline
+		%\textbf{\emph{info}} & \textbf{60.0\%} & 41.2\% & \textbf{41.3\%} & 31.3\% \\
+		%\textbf{\emph{warning}} & 14.3\% & \textbf{58.8\%} & 10.0\% & \textbf{62.7\%} \\
+		%\textbf{\emph{error}} & 25.7\% & 0.0\% & \textbf{48.8\%} & 6.1\%\\
+    %\bottomrule
+    %\end{tabular}
+    %\\ \emph{C (constraints), CV (constraint violations)}
+    %\end{center}
+%\end{table}
+
+50\% of all constraints are \emph{error}, 40\% are \emph{informational}, and 10\% are \emph{warning} constraints.
 \emph{Informational} constraints caused 1/3 and
@@
 \begin{hyp}
-The percentage of severe violations is very low, compared to about 2/3 of warning violations and 1/3 of informational violations, which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
+The percentage of severe violations is very low, compared to about 2/3 of warning and 1/3 of informational violations.
+This implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
 \end{hyp}
@@
 More than 50\% of the DDI-RDF and SKOS constraints, however, are \emph{informational} constraints.
-1/6 of the Disco violations are caused by \emph{error} constraints and
+1/6 of the DDI-RDF violations are caused by \emph{error} constraints and
 almost all QB violations and 59\% of the SKOS violations are caused by \emph{warning} constraints.  
-For well-established vocabularies, data quality is high
-as serious violations rarely appear.
-For newly developed vocabularies, data quality is worse
-as serious violations occur partially.
 %Constraints are serious when they violate the integrity of vocabularies.
@@
 \begin{hyp}
-Especially for newly developed vocabularies, constraint languages should be used to a larger extend to meet reduce severe violations.   
+For well-established vocabularies, data quality is high as serious violations rarely appear. For newly developed vocabularies, data quality is worse as serious violations occur partially.   
 \end{hyp}
+
+Especially for newly developed vocabularies, constraint languages should be used to a larger extend to reduce severe violations.
 
@@
 
-%The constraints responsible for the largest amounts of constraint violations are \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} and \emph{DISCO-C-COMPARISON-VARIABLES-02} (both 547,916; DDI-RDF), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102; QB), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903; SKOS).
-
-Table \ref{tab:evaluation-complexity-severity} shows the relation between the complexity and the severity level of all 213 constraints.
+%The constraints responsible for the largest amounts of constraint violations are \emph{DDI-RDF-C-LABELING-AND-DOCUMENTATION-06} and \emph{DDI-RDF-C-COMPARISON-VARIABLES-02} (both 547,916; DDI-RDF), \emph{DATA-CUBE-C-DATA-MODEL-CONSISTENCY-05} (45,514,102; QB), and \emph{SKOS-C-LANGUAGE-TAG-CARDINALITY-01} (2,508,903; SKOS).
+
+%Table \ref{tab:evaluation-expressivity-severity} shows the relations between the severity level of the violations caused by all 115 constraints and the classification according to the expressivity of constraint languages of the constraint types of the violations in percent.
+80\% of the violations which are raised by either \emph{RDFS/OWL} or \emph{Constraint Language Based} constraints are caused by constraints with the severity level \emph{informational} (see Table \ref{tab:evaluation-expressivity-severity}) and almost all (94\%) of the violations which are caused by \emph{SPARQL Based} constraints are raised by \emph{warning} constraints.
+
+%Table \ref{tab:evaluation-constraints-expressivity-severity} shows the relations between the severity level of all 115 constraints and the classification of their types according to the expressivity of constraint languages in percent.
 More than 1/2 of the \emph{vocabulary constraints} are \emph{error} constraints,
@@
 
+%\begin{table}[H]
+		%\scriptsize
+    %\begin{center}
+		%\caption{OLD}
+		%\label{tab:evaluation-complexity-severity}
+    %\begin{tabular}{@{}lcccc@{}}
+%%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
+%%    \\  \cmidrule{2-7}
+    %\\       \textbf{}
+           %& \textbf{\emph{RDFS/OWL}}
+           %& \textbf{\emph{Constraint Language}}
+					 %& \textbf{\emph{SPARQL}}
+    %\\ \midrule
+		%%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
+		%%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
+		%%\hline
+		%\textbf{\emph{info}} & 38.7 \% & \textbf{76.2 \%} & \textbf{42.3 \%} \\
+		%\textbf{\emph{warning}} & 6.7 \% & 7.1 \% & 13.5 \% \\
+		%\textbf{\emph{error}} & \textbf{54.6 \%} & 16.7 \% & \textbf{44.2 \%} \\
+    %\bottomrule
+    %\end{tabular}
+    %%\\ \emph{C (constraints), CT (constraint types)}
+    %\end{center}
+%\end{table}
+
+%\begin{table}[H]
+		%\scriptsize
+    %\begin{center}
+		%\caption{Constraint Language Expressivity and Severity Level of Violations}
+		%\label{tab:evaluation-violations-expressivity-severity}
+    %\begin{tabular}{@{}lcccc@{}}
+%%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
+%%    \\  \cmidrule{2-7}
+    %\\       \textbf{}
+           %& \textbf{\emph{RDFS/OWL}}
+           %& \textbf{\emph{Constraint Language}}
+					 %& \textbf{\emph{SPARQL}}
+    %\\ \midrule
+		%%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
+		%%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
+		%%\hline
+		%\textbf{\emph{info}} & \textbf{79.64} & \textbf{79.60} & 4.39 \\
+		%\textbf{\emph{warning}} & 20.28 & 20.27 & \textbf{94.17} \\
+		%\textbf{\emph{error}} & 0.08 & 0.13 & 1.43 \\
+    %\bottomrule
+    %\end{tabular}
+    %%\\ \emph{C (constraints), CT (constraint types)}
+    %\end{center}
+%\end{table}
+
+%\begin{table}[H]
+		%\scriptsize
+    %\begin{center}
+		%\caption{Constraint Language Expressivity and Severity Level of Constraints}
+		%\label{tab:evaluation-constraints-expressivity-severity}
+    %\begin{tabular}{@{}lcccc@{}}
+%%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
+%%    \\  \cmidrule{2-7}
+    %\\       \textbf{}
+           %& \textbf{\emph{RDFS/OWL}}
+           %& \textbf{\emph{Constraint Language}}
+					 %& \textbf{\emph{SPARQL}}
+    %\\ \midrule
+		%%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
+		%%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
+		%%\hline
+		%\textbf{\emph{info}} & \textbf{79.64} & \textbf{79.60} & 4.39 \\
+		%\textbf{\emph{warning}} & 20.28 & 20.27 & \textbf{94.17} \\
+		%\textbf{\emph{error}} & 0.08 & 0.13 & 1.43 \\
+    %\bottomrule
+    %\end{tabular}
+    %%\\ \emph{C (constraints), CT (constraint types)}
+    %\end{center}
+%\end{table}
+
 \begin{table}[H]
@@
     \begin{center}
-		\caption{Relation between Complexity and Severity Level of Constraints}
-		\label{tab:evaluation-complexity-severity}
-    \begin{tabular}{@{}lcccc@{}}
-%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
-%    \\  \cmidrule{2-7}
-    \\       \textbf{}
-           & \textbf{\emph{vocabulary}}
-           & \textbf{\emph{simple}}
-					 & \textbf{\emph{complex}}
-    \\ \midrule
-		%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
-		%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
-		%\hline
-		\textbf{\emph{info}} & 38.7 \% & \textbf{76.2 \%} & \textbf{42.3 \%} \\
-		\textbf{\emph{warning}} & 6.7 \% & 7.1 \% & 13.5 \% \\
-		\textbf{\emph{error}} & \textbf{54.6 \%} & 16.7 \% & \textbf{44.2 \%} \\
+		\caption{Language Expressivity and Severity Level}
+		\label{tab:evaluation-expressivity-severity}
+    \begin{tabular}{@{}lcccccc@{}}
+    %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
+    %\\  \cmidrule{2-3}
+		\hline
+    \multirow{3}{*}{} &
+      \multicolumn{2}{c}{\textbf{RDFS/OWL}} &
+      \multicolumn{2}{c}{\textbf{\emph{CL}}} &
+      \multicolumn{2}{c}{\textbf{\emph{SPARQL}}} \\
+    \textbf{} & C & CV & C & CV & C & CV \\
+    \hline
+		\textbf{\emph{info}} & \textbf{52.5} & \textbf{79.64} & \textbf{55.2} & \textbf{79.60} & \textbf{45.1} & 4.39 \\
+		\textbf{\emph{warning}} & 18.0 & 20.28 & 15.5 & 20.27 & 19.6 & \textbf{94.17} \\
+		\textbf{\emph{error}} & 29.5 & 0.08 & 29.3 & 0.13 & 35.3 & 1.43 \\
     \bottomrule
     \end{tabular}
-    %\\ \emph{C (constraints), CT (constraint types)}
+		\\ \emph{C (constraints), CV (constraint violations)}
     \end{center}
@@
 
-For 114 of these constraints, we evaluated  the data quality of 15,694 data sets (4.26 billion triples) of research data for the \emph{SBE} sciences obtained from 33 SPARQL endpoints.
+For 115 of these constraints, we evaluated  the data quality of 15,694 data sets (4.26 billion triples) of research data for the \emph{SBE} sciences obtained from 33 SPARQL endpoints.
 

### 2015-07-15 paper/paper 2/dc-2015.tex
related work
Intro rewritten

@@
 
-Recently, RDF validation as a research field gained speed due to common needs of data practitioners.
-A typical example is the library domain that co-developed and adopted Linked Data principles very early.
-For libraries, the common description of resources are key business and they have a long tradition in developing and using interoperable data formats.
-While they embrace the openness of Linked Data and the data modeling principles provided by RDF, the data is still mostly represented in XML and this is unlikely to change any time soon.
+The proper validation of RDF data according to constraints is a common requirement of data practitioners. 
 Among the reasons for the success of XML is the possibility to formulate fine-grained constraints to be met by the data and to validate the data according to these constraints using powerful systems like \emph{DTD}, \emph{XML Schema}, \emph{RELAX NG}, or \emph{Schematron}.
-A typical example is the definition of a library record describing a book.
-There are clear rules which information has to be available to describe a book properly, but also how information like an ISBN number is properly represented.
-Libraries seek to make their own data reusable for general purposes, but also to enrich and interlink their own data.
-Checking if third-party data meets own requirements or validating existing data according to new needs for a Linked Data application are among common use cases for RDF validation.
 
@@
 Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group,
-we published by today 81 requirements to validate RDF data and to formulate constraints; 
-%each of them corresponding to a constraint type which in most cases can be expressed by multiple constraint languages. 
-each of them corresponds to a constraint type from which concrete constraints are instantiated to be checked on RDF data. 
-%and which in most cases can be expressed by multiple constraint languages.
-%Requirements/constraint types are uniquely identified by alphanumeric technical identifiers.
-%\emph{Minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75}, e.g., is a constraint type which corresponds to the requirement {\small\emph{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}}.
-We recently published a technical report (serving as first appendix of this paper) in which we explain each constraint type in detail and give examples for each represented by different constraint languages \cite{BoschNolleAcarEckert2015}.
-More than 10 constraint languages with different syntax and semantics exist or are currently developed. 
-We focus on the five most promising ones on being the standard like
-\emph{Shape Expressions (ShEx)}, \emph{Resource Shapes (ReSh)}, and \emph{Description Set Profiles (DSP)}. 
-The \emph{Web Ontology Language} \emph{(OWL)} in its current version OWL 2 can also be used as a constraint language.
-With its direct support of validation via \emph{SPARQL}, the \emph{SPARQL Inferencing Notation (SPIN)} is very popular and certainly plays an important role for the future development in this field. 
-%\emph{SPIN} is particularly interesting as a means to validate arbitrary constraint languages by mapping them to \emph{SPARQL} \cite{BoschEckert2014-2}.
-
-\subsection{Motivation and Overview}
-
-We evaluated which constraint types the five most common constraint languages enable to express \cite{BoschNolleAcarEckert2015}.
+we identified by today 81 constraint types, where each type corresponds to a specific requirement in the database.
+In a technical report, we explain each constraint type in detail and give examples for each represented by different constraint languages \cite{BoschNolleAcarEckert2015}.
+
+Various constraint languages exist or are being developed that support more or less of these constraint types.
+For our work, we focus on the following four as the ones that are most popular among data practitioners, often mentioned on mailing lists and/or being candidates or prototypes for the upcoming W3C recommendation:
+\emph{Description Set Profiles (DSP)}, \emph{Resource Shapes (ReSh)}, \emph{Shape Expressions (ShEx)}, and the \emph{Web Ontology Language} \emph{(OWL)}.
+Despite the fact that OWL is arguably not a constraint language, it is widely used in practice as such under the closed-world and unique naming assumptions.
+
+With its direct support of validation via \emph{SPARQL}, the \emph{SPARQL Inferencing Notation (SPIN)} is also very popular to formulate and check constraints \cite{Fuerber2010}.
+We consider SPIN a low-level language in contrast to the other constraint languages where specific language constructs exist to define constraints in a declarative and in comparison more intuitive way -- although SPARQL aficionados might object particularly to the latter point.
+
+The power of SPIN is shown in 
 %The evaluation is explained in detail in the appendix of this paper \cite{BoschNolleAcarEckert2015}.
-Table \ref{tab:constraint-type-specific-expressivity} shows in percentage values (and absolute numbers in brackets) how many constraint types each language supports.
-
-\begin{table}[H]
+Table \ref{tab:constraint-type-specific-expressivity}, where we list the fraction (and absolute numbers in brackets) of how many constraint types each of these languages supports \cite{BoschNolleAcarEckert2015}.
+We further see that OWL 2 is currently the most expressive high-level constraint language, at least according to the pure number of contraint types supported.
+This does not preclude that other constraint languages are better suited for certain applications, either because they support some types that are not supported by OWL or because the constraint representation is mroe appealing to the data practitioners -- producers as well as consumers who again might have different needs and preferences.
+
+\begin{table}
 	\centering
@@
 
-The fact that \emph{SPIN} supports all and OWL 2 covers 2/3 of all constraint types
-emphasizes the significant role \emph{SPIN} and OWL 2 play for the future development of constraint languages.
-\emph{SPARQL} and therefore \emph{SPIN}, the \emph{SPARQL}-based way to formulate and check constraints, is generally seen as the method of choice to validate data according to certain constraints \cite{Fuerber2010},
-although, it is not ideal for their formulation. 
-In contrast, high-level constraint languages are comparatively easy to understand and constraints can be formulated more concisely.
-Declarative languages may be placed on top of \emph{SPARQL} and \emph{SPIN} when using them as implementation languages.
-
-There exists no single best solution considered as high-level intuitive constraint language which enables to express constraints in an easy and concise way and which is able to meet all requirements raised by data practitioners.
-%which can be used to express constraints and to validate RDF data, 
-%(e.g. existential and universal quantification, cardinality restrictions, and exclusive or of properties)
-%\section{Ideas}
-%constraint design patterns:
-% - ontology design pattern.org
-% - DSP uses other design pattern
-% - constraint elements are the same / 
-% - constraint / constraint elements / constraint design patterns / constraint language
-%dependency between requirements / when this requirements is fulfilled then this is also fulfilled (e.g. min card and requ. car)
-%min car more powerful than req. propery
-Thus, the idea behind this paper is to satisfy all RDF validation requirements
-by representing constraints of any constraint type in a generic way using a lightweight vocabulary which consists of only a few terms.
-We lately published a technical report (serving as second appendix of this paper) in which we describe the vocabulary in detail \cite{BoschEckert2015-2} (Section \ref{sec:vocabulary}).
-The constraint type \emph{minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75} can be instantiated to ensure
+We formerly demonstrated that a high-level constraint language, Description Set Profiles, can be implemented by mapping the language to SPIN using SPARQL CONSTRUCT queries \cite{BoschEckert2014-2}.
+We provide a validation environment where own mappings from arbitrary constraint languages can be provided and tested.\footnote{Available at \url{http://purl.org/net/rdfval-demo}, source code available at: \url{https://github.com/boschthomas/rdf-validator}.}
+
+The creation of such mappings is in many cases not straight-forward and requires profound knowledge of SPARQL, as the following example demonstrates:
+
+The constraint type \emph{minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75}\footnote{Requirements are identified in the database by an R and a number, additionally an alphanumeric identifier is provided, in this case R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES.
+Online at: \url{http://lelystad.informatik.uni-mannheim.de/rdf-validation/?q=node/82}} can be used to formulate the constraint
 that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
-%As every \emph{publication} must have at least one \emph{author} which must be a \emph{person} 
-As the book \emph{The-Lord-Of-The-Rings} is a \emph{publication}, 
-%{\small\ms{(rdf:type(The-Lord-Of-The-Rings, Publication)),}} 
-it must have at least one \emph{author} relationship to a \emph{person}.
-The constraint is violated either (1) if
-the book does not have any \emph{author} relationship, 
-or (2) if it has an \emph{author} which is not a \emph{person},
-%{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)},} {\small\ms{rdf:type(Tolkien, Hobbit)),}} 
-or (3) if it has an \emph{author} whose class is unknown.
-%{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)).}}
-%In contrast, the book is a valid \emph{publication}, if it is connected to a \emph{person} via the property \emph{author}.
-%{\small\ms{(author(The-Lord-Of-The-Rings, Tolkien)}, \ms{rdf:type(Tolkien, Person)).}}
-This constraint can either be represented generically (\emph{generic constraint}) by \emph{description logics (DL)}: {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}} or specifically (\emph{specific constraint}) by multiple domain-specific constraint languages:
+
+This constraint can be expressed as follows using different constraint languages:
 
@@
 
-The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
-For this reason, we mapped constraint types to DL 
-in order to determine which DL constructs are needed to express constraint types \cite{BoschNolleAcarEckert2015}.
-
-The main contributions of this paper are:
-(1) We provide a basic terminology and classification system for RDF constraints to lay the ground for discussions on RDF validation (Section \ref{sec:vocabulary}).
-(2) As current high-level constraint languages do not support all constraint types, 
-we developed a vocabulary to describe constraints of any constraint type in a generic way and specified its underlying semantics (Section \ref{sec:vocabulary}).
-(3) We show how to enhance the interoperability of constraints expressed by different languages by using the proposed vocabulary 
-to intermediately represent constraints 
-%as an intermediate generic representation 
-which enables transformations between semantically equivalent constraints (Section \ref{sec:transformations}).
-(4) We explain how constraint languages may reuse validation implementations which are provided once for each constraint type (Section \ref{sec:validation}).
-
-\subsection{How to Improve the Interoperability of RDF Constraints}
-\label{sec:transformations}
-
-RDF data providers have to ensure high data quality and therefore 
-that their data conforms to constraints which may be part of contracts between data providers and consumers.
-As there is no standard way to formulate constraints, 
-semantically equivalent \emph{specific constraints}, so the \emph{minimum qualified cardinality restriction}, may be represented by a variety of languages - each of them having different syntax and semantics.
-This causes confusion and weakens the common understanding between several parties about the meaning of particular constraints.
-We propose transformations between semantically equivalent \emph{specific constraints}
-(1) to avoid the necessity to understand several languages,
-(2) to resolve misunderstandings about the meaning of particular constraints within the communication of RDF data producers and consumers, and
-(3) to enhance the interoperability of constraint languages.
-
-We suggest to transform a \emph{specific constraint} (\emph{$sc_{\alpha}$}) of any constraint type expressed by language \emph{$\alpha$} into a semantically equivalent \emph{specific constraint} (\emph{$sc_{\beta}$}) of the same constraint type represented by any other language \emph{$\beta$}
-by using the developed vocabulary to intermediately represent constraints in a generic way. 
-%to enable these transformations.
+Note that the SPIN representation is NOT a mapping, but a direct expression of the constraint using a SPARQL CONSTRUCT query that creates a spin:ConstraintViolation if the constraint is violated.
+The mapping for DSP is much more complicated and can be found in the mappings provided by us.\footnote{Online: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/DSP_SPIN-Mapping.ttl#L4665}}
+
+On the other hand, it can be seen that the higher-level constraint languages are comparatively similar, there seems to be a pattern, a common way to express this type of constraint.
+Therefore, a mapping from a high-level language to another high-level language would be considerably easier.
+Unfortunately, there is not (yet) a high-level language that supports all constraint types.
+
+In this paper, we build on the experience gained from mapping several constraint languages to SPIN and from the analysis of the identified constraint types to create an intermediate layer, a framework that is able to describe the mechanics of all constraint types and that can be used to map high-level languages more easily.
+
+%%% DL introduction, not needed here...
+% -This constraint can either be represented generically (\emph{generic constraint}) by \emph{description logics (DL)}: {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}} or
+%The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
+%For this reason, we mapped constraint types to DL 
+%in order to determine which DL constructs are needed to express constraint types \cite{BoschNolleAcarEckert2015}.
+
+% The main contributions are:
+% \begin{enumerate}
+%  \item We develop a framework to describe constraints of any constraint type in a generic way (Section \ref{sec:vocabulary}).
+%  \item We demonstrate the application of this framework by mapping different constraint language to a unified intermediate representation that is not only mapped to SPIN, but also enables transformations to semantically equivalent constraints in other high-level constraint languages (Section \ref{sec:transformations}).
+%  \item We separate the implementation of the constraint type in SPIN from its expression in a high-level constraint language which makes the implementation reusable and allows a consistent validation across constraint languages (Section \ref{sec:validation}).
+% \end{enumerate}
+%
+
+\section{Motivation}
+
+Even with an upcoming W3C recommendation, it can be expected that several constraint languages will be used in practice in future -- consider the situation in the XML world, where a standardized schema language was available from the beginning and yet additional ways to formulate and check constraints have been created.
+Therefore,
+semantically equivalent \emph{specific constraints} represented in different languages will exist.
+This raises two questions: 
+\begin{enumerate}
+ \item How can we ensure that two semantically equivalent constraints are actually validated consistently?
+ \item How can we support the transformation of semantically equivalent constraints from one contraint language to another?
+\end{enumerate}
+
+% \section{How to Provide the Validation of RDF Constraints Out-Of-The-Box}
+
+\paragraph{Consistent implementation.}
+Even though SPIN provides a convenient way to represent constraints and to validate data according to these constraints, the implementation of a high-level constraint language still requires a tedious mapping to SPIN with a certain degree of freedom as to how a constraint violation is actually represented and how exactly the violation of the contraint is checked.
+Our framework therefore proides a common ground that is solely based on the abstract definitions of the constraint types, as identified in our database. By providing a \emph{SPIN} mapping
+%generic validation implementations once 
+for each constraint type\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}\label{RDF-CV-2-SPIN}}, it is ensured that the details of the SPIN implementation are consistent irrespective of the constraint language and that the validation leads always to exactly the same results.
+
+\paragraph{Constraint transformations.} Consistent implementations of constraint languages provide some advantage, but it could be argued that they are not important enough to justify the additional layer.
+The situation, however, is different when transformations from one constraint language to another are desired, i.e., to transform a \emph{specific constraint} (\emph{$sc_{\alpha}$}) of any constraint type expressed by language \emph{$\alpha$} into a semantically equivalent \emph{specific constraint} (\emph{$sc_{\beta}$}) of the same constraint type represented by any other language \emph{$\beta$}.
 By defining mappings between equivalent \emph{specific constraints} and the corresponding \emph{generic constraint} (\emph{gc}) we are able to convert them automatically: 
-{\small\ms{$ gc = m_1(sc_{\alpha}) = m_2(sc_{\beta}) $}}.
-Thereby, we do not need to define mappings between each pair of semantically equivalent \emph{specific constraints}.
-Let's assume we are able to express constraints of the \emph{minimum qualified cardinality restrictions} constraint type by 10 languages.
-Without an intermediate generic representation of constraints, we would have to define for each constraint type one mapping between each pair of \emph{specific constraints} expressed by \emph{n} languages
-- that are \emph{\( {n \choose 2} \)} mappings (\emph{\( {10 \choose 2} \)} = 45 mappings).
-With an intermediate generic representation of constraints, on the other side, we only need to define for each constraint type \emph{n} mappings 
-%(1 mapping for each \emph{specific constraint}) 
-from \emph{n} \emph{specific constraints} to the corresponding \emph{generic constraint} (10 mappings).
-%Let's assume we are able to express a particular constraint type by 5/6/7/8/9/10 constraint languages.
-%Without the intermediate \emph{generic constraint}, we would have to define for each constraint type \emph{1} mapping for each pair of \emph{specific constraints} (expressed by different constraint languages)
-%that are \emph{\( {n \choose 2} \)} mappings (10/15/21/28/36/45 mappings).
-%With an intermediate \emph{generic constraint}, however, we only need to define for each constraint type \emph{n} mappings (1 mapping for each \emph{specific constraint}) from \emph{n} \emph{specific constraints} to the corresponding \emph{generic constraint} (5/6/7/8/9/10 mappings).
-For the \emph{minimum qualified cardinality restriction}, one mapping (\emph{$m_1(sc_{OWL 2})$}, \emph{$m_2(sc_{ShEx})$}, \emph{$m_3(sc_{ReSh})$}, \emph{$m_4(sc_{DSP})$},...) is defined for each \emph{specific constraint} (\emph{$sc_{OWL 2}$}, \emph{$sc_{ShEx}$}, \emph{$sc_{ReSh}$}, \emph{$sc_{DSP}$},...) to the corresponding \emph{generic constraint} (\emph{gc}).
-
-\subsection{How to Provide the Validation of RDF Constraints Out-Of-The-Box}
-\label{sec:validation}
-
-We use \emph{SPIN} as basis to develop a validation environment\footnote{Online demo available at \url{http://purl.org/net/rdfval-demo}, source code available at: \url{https://github.com/boschthomas/rdf-validator}\label{rdf-validator}} to validate RDF data according to constraints of constraint types which are expressible by arbitrary constraint languages by mapping them to \emph{SPIN}\footnote{\emph{SPIN} mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}\label{spin-mappings}} \cite{BoschEckert2014-2}.
-The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations \cite{BoschEckert2014-2}.
-The next step, however, was to extend the \emph{RDF Validator} to validate RDF data conforming to constraints of any constraint type
-by representing constraints generically using the proposed vocabulary.
-
-When language designers extend constraint languages 
-to be able to formulate constraints of not yet supported constraint types,
-our proposal prevents the necessity to actually implement the validation of data
-according to constraints of these constraint types for each of those languages.  
-For any constraint language, we enable to offer a validation implementation of any constraint type out-of-the-box
-%validation implementations out-of-the-box for any constraint type whose \emph{specific constraints} may be expressed by any language  
-by providing a \emph{SPIN} mapping
-%generic validation implementations once 
-for each constraint type\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}\label{RDF-CV-2-SPIN}}  
-whose constraints are represented generically \cite{BoschEckert2015-2}.
-%(2) by transforming \emph{specific constraints} into the appropriate \emph{generic constraint}.  
-All what language designers need to do is to specify for each constraint type they want to cover one mapping from the \emph{specific constraint} expressed by the language to the corresponding \emph{generic constraint}.
-19 of the overall 81 constraint types are expressible by at least four constraint languages \cite{BoschNolleAcarEckert2015}.
-This means that for these 19 constraint types there must be 76 implementations (four for each constraint type) to actually validate RDF data according to 76 \emph{specific constraints} - instead of only 19 implementations (one for each \emph{generic constraint}).
-%which lead for each constraint type to identical validation results independently from the language used to formulate the \emph{specific constraints}.
-Our proposal makes sure that the validation on semantically equivalent \emph{specific constraints} expressed by different languages
-leads to exactly the same validation results, 
-i.e., that validation is performed independently from the used language.
-This is not the case, however, for existing languages due to differences in semantics and since they are implemented independently form each other.
-
-%When domain experts use graphical user interfaces to define constraints in a user-friendly way (without the necessity to express constraints on their own), 
-%constraints can be mapped to either a specific or a generic constraint, as for both the validation is provided in the background.    
-%So, the user does not have to know how to express specific constraints using any constraint language.
-
-%Existing constraint languages can be extended and new constraint languages can be developed, if existing constraint languages are not sufficient to represent needed constraint types.
-
-%If (1) a new constraint type is expressed generically, (2) the \emph{generic constraint type} is mapped to \emph{specific constraint types} (expressed by constraint languages), and (3) the validation is implemented for this particular \emph{generic constraint type},
-%the validation of \emph{specific constraint types} is provided out of the box.
-%As a consequence, constraint language designers do not have to implement the validation of their constraint languages and each semantically equivalent \emph{specific constraint type} is validated the same way (i.e.
-leading to identical validation results).
-
-%This paper aims to address two main \textbf{audiences}:
-%(1) RDF data providers and consumers seeking how to ensure high data quality and thus for ways to enhance the interoperability and common understanding of constraints expressible by multiple constraint languages and
-%(2) RDF practitioners thinking of how to provide aligned implementations for the validation of both existing an newly developed constraint languages.
-
-%(if the validation is implemented once for the corresponding \emph{generic constraint type} to which the \emph{specific constraint type} is mapped)
-
-%The remainder of the paper is as follows.
-
-%\begin{itemize}
-	%\item Any specific constraint (expressed by any constraint language) can be transformed into a generic constraint (expressed by the generic constraint language)
-	%\item Any specific constraint (expressed by any constraint language A) can be transformed into any specific constraint (expressed by any constraint language B)
-	%\item Any specific constraint (expressed by any constraint language) can be validated automatically (if an automatic validation is defined only once for corresponding generic constraint)
-	%\item We define a basic terminology and classification system for RDF constraints
-	%\item We developed an ontology describing any RDF constraint generically (whether expressible in DL or not)%which can also be expressed by any constraint language
-	%\item We present that any RDF constraint can be described by the developed ontology - whether the constraint can be expressed in DL or not 
-	%\item We show how to transform specific constraints (expressed by any constraint language \ms{$\alpha$}) into generic constraints and into specific constraints (expressed by any other constraint language \ms{$\beta$})
-  %\item We explain that any specific constraint can be validated automatically (if the validation is implemented only once for the corresponding generic constraint)
-%\end{itemize}
-
-%The \textbf{benefits} of our framework are:
-%\begin{itemize}
-	%\item Any specific constraint (expressed by any constraint language) can be transformed into a generic constraint (expressed by the generic constraint language)
-	%\item Any specific constraint (expressed by any constraint language A) can be transformed into any specific constraint (expressed by any constraint language B)
-	%\item Any specific constraint (expressed by any constraint language) can be validated automatically (if an automatic validation is defined only once for corresponding generic constraint)
-%\end{itemize}
-
-%\section{Running Example}
-%
-%Table \ref{tab:cardinality-restriction-mapped-to-vocabulary} shows the mapping between the \emph{cardinality restriction} represented in DL 
-%and the \emph{cardinality restriction} expressed by our developed vocabulary to describe any RDF constraint generically (see section~\ref{sec:ontology}):
-%
-%\begin{table}
-  %\scriptsize
-  %\sffamily
-  %\vspace{0cm}
-	%\centering
-		%\begin{tabular}{l|l|l|l|l|l|l}
-      %\textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
-      %\hline
-      %property & Publication & author & - & Person & $\geq$ & 1 \\
-		%\end{tabular}
-	%\caption{Cardinality Restriction Expressed Generically}
-	%\label{tab:cardinality-restriction-mapped-to-vocabulary}
-%\end{table}
-
-%According to this vocabulary, each constraint is either a constraint on classes or a constraint on properties.
-%The generically expressed cardinality restriction is represented in RDF as follows:
-%
-%\begin{ex}
-%[   a PropertyConstraint ;
-    %contextClass Publication ;
-    %leftProperties ( author ) ;
-    %classes ( Person ) ;
-    %constrainingElement ">=" ;
-    %constrainingValue 1 ] .
-%\end{ex}
-
-%Bosch and Eckert\cite{BoschEckert2014-2} use SPIN as basis to define a
-%validation environment in which the validation of any constraint language\footnote{The only limitation is that constraint languages must be represented in RDF} can be implemented by representing them in SPARQL.
-%The SPIN engine checks for each resource if it satisfies all constraints (associated with its assigned classes) and generates a result RDF graph containing information about all constraint violations.
-%The generically expressed \emph{cardinality restriction} above is validated within the validation environment (see section \ref{sec:validation}) by means of a SPARQL CONSTRUCT query.
-
-%\begin{ex}
-%[   a PropertyConstraint ;
-    %contextClass ?cc ;
-    %leftProperties ( ?p1 ) ;
-    %classes ( ?c1 ) ;
-    %constrainingElement ">=" ;
-    %constrainingValue ?cv ] .
-%?subject rdf:type ?cc .
-%BIND ( qualifiedCardinality( ?subject, ?p1, ?c1 ) AS ?c ) .
-%FILTER ( ?c < ?cv ) .		  
-%\end{ex}
+\begin{align*}
+  gc &=  m_1(sc_{\alpha}) \\
+  sc_{\beta} &= m_2'(gc) 
+\end{align*}
+
+Thereby, we do not need to define mappings for each constraint type and each possible combination of constraint languages.
+Assuming that we are able to express a single constraint type like \emph{minimum qualified cardinality restrictions} within 10 languages, $n \cdot n-1 = 90$ mappings would be needed -- as mapping generally are not invertible.
+With an intermediate generic representation of constraints, on the other side, we only need to define for each constraint type $2n = 20$ mappings -- where $10$ mappings should already exist if we have an implementation in our framework.
+To summarize, if language developers are willing to provide two mappings -- forward and backward -- to our framework for each supported constraint type, we not only would get the consistent implementation of all languages, it would also be possible to transform semantically equivalent constraints into all constraint languages.
 
@@
 SPIN, SPARQL, OWL 2, ShEx, ReSh, and DSP are the six most promising and mostly used constraint languages.
+In addition, the W3C Data Shapes Working Group currently develops SHACL, an RDF vocabulary for describing RDF graph structures.
 

### 2015-07-16 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
minor

@@
 The first numbers indicate the absolute amount of constraints and violations.
-The constraints and their raised constraint violations are grouped by vocabulary, the classification of their type according to the expressivity of constraint languages, and their severity level.
+The constraints and their raised violations are grouped by vocabulary, by which languages constraints are expressed, and their severity level.
 The numbers of evaluated triples and data sets differ between the vocabularies
@@
 we only use normalized relative values representing the percentage of constraints and violations belonging to the respective class.
-There is a strong overlap between \emph{RDFS/OWL Based} and \emph{Constraint Language Based} constraint types as in many cases constraint types are expressible by classical constraint languages and OWL.
-This is the reason why the percentage values of constraints and violations grouped by the classification of their types according to the expressivity of constraint languages do not accumulate to 100\%.
+
+There is a strong overlap between \emph{RDFS/OWL} and \emph{Constraint Language Based} constraint types as in many cases constraint types are expressible by classical constraint languages and OWL.
+This is the reason why the percentage values of constraints and violations grouped by the classification of constraint types according to the expressivity of constraint languages do not accumulate to 100\%.
+
+As the evaluation is based on three vocabularies, 
+we cannot make valid general statements for all vocabularies,
+but we can formulate several hypotheses to direct the further development of constraint languages.
+As these hypotheses cannot be proved yet, 
+they still have to be verified or falsified
+by evaluating the quality of data represented by further well-established and newly developed vocabularies.
+
+\textcolor{red}{wurden die severity levels der constraints korrekt ausgezählt?}
 
@@
 		\hline
-		\textbf{\emph{info}} & \textbf{52.5} & \textbf{52.6} & 11.4 & 0.0 \\
-		\textbf{\emph{warning}} & 7.0 & 29.4 & 8.6 & \textbf{99.8} \\
-		\textbf{\emph{error}} & 40.6 & 18.0 & \textbf{80.0} & 0.3 \\
+		\textbf{\emph{info}} & \textbf{56.4} & \textbf{52.6} & 0.0 & 0.0 \\
+		\textbf{\emph{warning}} & 11.5 & 29.4 & 15.0 & \textbf{99.8} \\
+		\textbf{\emph{error}} & 32.1 & 18.0 & \textbf{85.0} & 0.3 \\
     \bottomrule
@@
 		\hline
-		\textbf{\emph{SPARQL}} & \textbf{100.0} & \textbf{100.0} & \textbf{59.7} & \textbf{78.2} \\
-		\textbf{\emph{CL}} & 0.0 & 0.0 & 23.5 & 21.8 \\
-		\textbf{\emph{RDFS/OWL}} & 0.0 & 0.0 & 38.2 & 21.8 \\
-		\hline
-		\textbf{\emph{info}} & \textbf{60.0} & 41.2 & \textbf{41.3} & 31.3 \\
-		\textbf{\emph{warning}} & 14.3 & \textbf{58.8} & 10.0 & \textbf{62.7} \\
-		\textbf{\emph{error}} & 25.7 & 0.0 & \textbf{48.8} & 6.1\\
+		\textbf{\emph{SPARQL}} & \textbf{100.0} & \textbf{100.0} & \textbf{63.2} & \textbf{78.2} \\
+		\textbf{\emph{CL}} & 0.0 & 0.0 & 34.7 & 21.8 \\
+		\textbf{\emph{RDFS/OWL}} & 0.0 & 0.0 & 35.6 & 21.8 \\
+		\hline
+		\textbf{\emph{info}} & \textbf{70.6} & 41.2 & \textbf{42.3} & 31.3 \\
+		\textbf{\emph{warning}} & 29.4 & \textbf{58.8} & 18.7 & \textbf{62.7} \\
+		\textbf{\emph{error}} & 0.0 & 0.0 & \textbf{39.0} & 6.1\\
     \bottomrule
@@
 
-Almost 60\% of all constraints, nearly 1/2 of the DDI-RDF, more than 1/2 of the QB, and 80\% of the SKOS constraints are \emph{SPARQL Based}.
+Almost 2/3 of all constraints, nearly 1/3 of the DDI-RDF, 60\% of the QB, and all SKOS constraints are \emph{SPARQL Based}.
+For well-established vocabularies, the most formulated constraints are \emph{SPARQL Based} (80\%).
+For newly developed vocabularies, however, the most expressed constraints are \emph{RDFS/OWL Based} (2/3).
+Nearly 80\% of all violations are caused by \emph{SPARQL}, 1/5 by \emph{Constraint Language}, and 1/5 by \emph{RDFS/OWL Based} constraints.
 %Hence, a significant amount of 46 \% of the constraints are directly extractable from formal specifications of well-established and newly defined vocabularies. 
@@
 \begin{hyp}
-As a significant amount of almost 60\% of the constraints are \emph{SPARQL Based},
-the further development of constraint languages will especially concentrate on expressing such complex constraints which up to now in most cases can only be expressed by plain SPARQL. 
+The facts that 80\% of all violations are raised by \emph{SPARQL Based} constraints and that 2/3 of all constraints are SPARQL Based, increases the importance for constraint languages to enable to express SPARQL Based constraints.
+Thus, the further development of constraint languages especially concentrates on expressing SPARQL Based constraints as data quality can be significantly improved when suitable constraint languages are developed which enable to define \emph{SPARQL Based} constraints in an easy, concise, and intuitive way.
+The more elaborate a vocabulary is, the more sophisticated and complex constraints are specified using SPARQL.
 \end{hyp}
 
-Nearly 40\% of all constraints are \emph{RDFS/OWL Based} and only 23.5\% of all constraints are \emph{Constraint Language Based}.
+These constraints are of such complexity that  up to now in most cases they can only be expressed by plain SPARQL.
+It should be an incentive for language designers to devise languages which are more intuitive than SPARQL in a way that also domain experts, which are not familiar with SPARQL, can formulate respective constraints.
+
+Nearly 1/3 of all constraints are either \emph{RDFS/OWL} or \emph{Constraint Language Based}.
 
 \begin{hyp}
-The first step to make progress in the further development of constraint languages will be to cover the constraint types which can already be formulated using RDFS and OWL.
+The first step to make progress in the further development of constraint languages is to cover the constraint types which can already be formulated using RDFS and OWL.
 \end{hyp}
 
-For well-established vocabularies, the most formulated constraints are \emph{SPARQL Based} (2/3).
-For newly developed vocabularies, however, the most expressed constraints are \emph{RDFS/OWL Based} ($>$1/2).
+The fact that only 1/5 of all violations result from \emph{RDFS/OWL Based} constraints, even though, 1/3 of all constraints are \emph{RDFS/OWL Based}, indicates good data quality for all vocabularies with regard to their formal specifications.
 
 \begin{hyp}
-The more elaborate a vocabulary is, the more detailed and complex constraints are defined by domain experts using plain SPARQL.
+Data corresponds to formal specifications of vocabularies the data is conforming to. 
+%This demonstrates that constraint formulation in general works. 
 \end{hyp}
 
-These constraints are of such complexity that they can only be expressed by SPARQL.
-It should be an incentive for language designers to devise languages which are more intuitive than SPARQL in a way that also domain experts, which are not familiar with SPARQL, can formulate respective constraints.
-
-Nearly 80\% of all violations are caused by \emph{SPARQL Based}, 1/5 by \emph{Constraint Language Based}, and 1/5 by \emph{RDFS/OWL Based} constraints.
-The fact that only 1/5 of all violations result from \emph{RDFS/OWL Based} constraints, even though, almost 40\% of all constraints are \emph{RDFS/OWL Based}, indicates good data quality for all vocabularies with regard to their formal specifications.
-
-\begin{hyp}
-Data corresponds to the formal specifications of its vocabularies the data is conforming to. This demonstrates that constraint formulation in general works. 
-\end{hyp}
-
 %\tb{je nach hypothese spezifische aufgaben um die hypothese zu beweisen}
-Moreover, while 2/3 of the DDI-RDF violations result from \emph{RDFS/OWL Based} constraints,
-QB and SKOS violations are almost only raised by \emph{SPARQL Based} constraints.
-This means that for the well-established vocabularies, \emph{RDFS/OWL Based} constraints are almost completely satisfied which indicates generally a very impressive data quality, at least in the \emph{SBE} domain and for the basic requirements.
+While 2/3 of the DDI-RDF violations result from \emph{RDFS/OWL Based} constraints,
+QB and SKOS violations are only raised by \emph{SPARQL Based} constraints.
+This means that for well-established vocabularies, \emph{RDFS/OWL Based} constraints are almost completely satisfied which indicates generally a very impressive data quality, at least in the \emph{SBE} domain and for the basic requirements.
 %This demonstrates that data providers take account of the formal specifications of well-established vocabularies.
@@
 For well-established vocabularies, RDFS/OWL Based constraints are almost completely satisfied which indicates good data quality in general and that basic data quality requirements are met.
+For newly developed vocabularies, however, data quality is poor as RDFS/OWL Based constraints are not fulfilled.
 \end{hyp}
@@
 As a consequence, \emph{RDFS/OWL Based} constraints are satisfied to a greater extend which leads to better data quality.  
-
-\begin{hyp}
-A significant amount of narrowly 80\% of the violations refer to SPARQL Based constraints that are not easily, concisely, and intuitively expressible by existing high-level constraint languages or RDFS and OWL which confirms the necessity to provide suitable constraint languages.
-Thus, the development of constraint languages will focus on enabling to express constraints which can up to now only be formulated by plain SPARQL.
-\end{hyp}
-
-\emph{RDFS/OWL Based} constraints are expressible by the modeling languages RDFS and OWL 2.
-\emph{SPARQL Based} constraints, however, are only expressible by plain SPARQL.
-As almost 80\% of all violations are caused by \emph{SPARQL Based} constraints, data quality can be significantly improved when suitable constraint languages are developed which enable to define \emph{SPARQL Based} constraints in an easy, concise, and intuitive way.
+%
+The reason why we only defined \emph{SPARQL Based} constraints for assessing the quality of thesauri is that literature and practice especially concentrate on graph-based structures of thesauri by applying graph- and network-analysis techniques which can only be implemented by SPARQL.
+
 %Therefore, existing constraint languages have to be extended or new constraint languages have to be developed.
@@
 \emph{warning} constraints 2/3 of all violations.
-As the percentage of severe violations is very low for all vocabularies (6.1\%),
-data quality is high with regard to the severity level of constraints.
+%As the percentage of severe violations is very low for all vocabularies (6.1\%),
+%data quality is high with regard to the severity level of constraints.
 
 \begin{hyp}
-The percentage of severe violations is very low, compared to about 2/3 of warning and 1/3 of informational violations.
-This implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
+Although, 1/2 of all constraints are error constraints, the percentage of severe violations is very low, compared to about 2/3 of warning and 1/3 of informational violations.
+This implies data quality is high with regard to the severity level of constraints and that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
 \end{hyp}
@@
 80\% of the violations which are raised by either \emph{RDFS/OWL} or \emph{Constraint Language Based} constraints are caused by constraints with the severity level \emph{informational} (see Table \ref{tab:evaluation-expressivity-severity}) and almost all (94\%) of the violations which are caused by \emph{SPARQL Based} constraints are raised by \emph{warning} constraints.
-
-%Table \ref{tab:evaluation-constraints-expressivity-severity} shows the relations between the severity level of all 115 constraints and the classification of their types according to the expressivity of constraint languages in percent.
-More than 1/2 of the \emph{vocabulary constraints} are \emph{error} constraints,
-more than 3/4 of the \emph{simple constraints} are \emph{informational} constraints, and
-\emph{complex constraints} are to the same extend \emph{informational} or \emph{error} constraints.
+Approx.
+1/2 of all constraints are \emph{informational} constraints regardless how their types are classified according to the expressivity of constraint languages.
 
@@
 \begin{hyp}
-There is significant demand for constraint languages that support the expression of complex constraints as 44\% of all complex constraints are also serious ones.
+Independent which language is used to formulate constraints, 1/2 of all constraints are informational, 1/3 are error, and 1/5 are warning constraints. 
+%Thereby, it does not matter which language is used to formulate constraints.
+Constraints expressed by RDFS/OWL or high-level constraint languages are of low severity, whereas the violation of constraints formulated by SPARQL is more serious.
+There is a significant demand for constraint languages that support the expression of SPARQL Based constraints as 94\% of all violations are caused by SPARQL Based constraints whose severity level is warning.
 \end{hyp}
 
-As \emph{vocabulary constraints} are part of formal specifications of vocabularies,
-violations of \emph{vocabulary constraints} are more severe than violations caused by \emph{simple constraints}.
-As SPARQL is still used to express \emph{complex constraints} and as 44\% of all \emph{complex constraints} are serious,
-there is an obvious need to develop constraint languages which enable to express \emph{complex constraints}.
+SPARQL seems to be used to formulate constraints whose violation is of higher severity than the violation of constraints expressed by either RDFS/OWL or high-level constraint languages.
+This is a surprising finding as the violation of \emph{RDFS/OWL Based} constraints should be of higher severity since these constraints may be part of vocabularies' formal specifications.
 

### 2015-07-16 paper/paper 2/dc-2015.tex
minor

@@
 \emph{Description Set Profiles (DSP)}, \emph{Resource Shapes (ReSh)}, \emph{Shape Expressions (ShEx)}, and the \emph{Web Ontology Language} \emph{(OWL)}.
-Despite the fact that OWL is arguably not a constraint language, it is widely used in practice as such under the closed-world and unique naming assumptions.
+Despite the fact that OWL is arguably not a constraint language, it is widely used in practice as such under the closed-world and unique name assumptions.
 
 With its direct support of validation via \emph{SPARQL}, the \emph{SPARQL Inferencing Notation (SPIN)} is also very popular to formulate and check constraints \cite{Fuerber2010}.
-We consider SPIN a low-level language in contrast to the other constraint languages where specific language constructs exist to define constraints in a declarative and in comparison more intuitive way -- although SPARQL aficionados might object particularly to the latter point.
+We consider SPIN as a low-level language in contrast to the other constraint languages where specific language constructs exist to define constraints in a declarative and in comparison more intuitive way -- although SPARQL aficionados might object particularly to the latter point.
 
@@
 Table \ref{tab:constraint-type-specific-expressivity}, where we list the fraction (and absolute numbers in brackets) of how many constraint types each of these languages supports \cite{BoschNolleAcarEckert2015}.
-We further see that OWL 2 is currently the most expressive high-level constraint language, at least according to the pure number of contraint types supported.
-This does not preclude that other constraint languages are better suited for certain applications, either because they support some types that are not supported by OWL or because the constraint representation is mroe appealing to the data practitioners -- producers as well as consumers who again might have different needs and preferences.
+We further see that OWL 2 is currently the most expressive high-level constraint language, at least according to the pure number of constraint types supported.
+This does not preclude that other constraint languages are better suited for certain applications, either because they support some types that are not supported by OWL or because the constraint representation is more appealing to the data practitioners -- producers as well as consumers who again might have different needs and preferences.
 

### 2015-07-16 paper/RDF validation requirements/RDF validation requirements.tex
constraining elements list completed

--- 2015-06-11 paper/RDF validation requirements/RDF validation requirements.tex
@@
 property & rdf:List & listElement & - & xsd:string & order & 1 \\
+\end{gcotable}
+
+\subsection{Simple Example}
+
+Property \emph{p} should be ordered, i.e., point to a list (rdf:List) of values.
+
+\begin{gcotable}
+property & $\top$ & p & - & - & ordered property & - \\
 \end{gcotable}
@@
 
-*Subsumption & $\sqsubseteq$ & sub-classes \\
-*Class Equivalence & $\equiv$ & equivalent classes \\
-*Sub Properties & $\sqsubseteq$ & sub-properties \\
-*Property Domain & $\exists$, $\sqsubseteq$ & domain \\
-*Property Range & $\sqsubseteq$, $\forall$ & range \\
-*Inverse Object Properties & inverse & \\
+*Subsumption & $\sqsubseteq$ & sub-class \\
+*Class Equivalence & $\equiv$ & equivalent class \\
+*Sub Properties & $\sqsubseteq$ & sub-property \\
+*Property Domains & $\exists$, $\sqsubseteq$ & property domain \\
+*Property Ranges & $\sqsubseteq$, $\forall$ & property range \\
+*Inverse Object Properties & inverse & inverse property \\
 %*Symmetric Object Properties & $\equiv$, inverse & symmetric \\
-*Symmetric Object Properties & symmetric &  \\
+*Symmetric Object Properties & symmetric & symmetric property \\
 %*Asymmetric Object Properties & $\sqsubseteq$, inverse & asymmetric \\
-*Asymmetric Object Properties & asymmetric &  \\
+*Asymmetric Object Properties & asymmetric & asymmetric property \\
 %*Reflexive Object Properties & $\exists$, $\sqsubseteq$ & \textcolor{green}{reflexive} \\
-*Reflexive Object Properties & reflexive &  \\
+*Reflexive Object Properties & reflexive & reflexive property \\
 %*Irreflexive Object Properties & $\exists$, $\neg$, $\sqsubseteq$ & irreflexive \\
-*Irreflexive Object Properties & reflexive, $\neg$ & irreflexive \\
-Disjoint Properties & $\sqsubseteq$, $\neg$ & $\ne$ \\
-Disjoint Classes & $\sqcap$, $\sqsubseteq$ & $\ne$ \\
-Context-Sp. Property Groups & $\sqcap$ & property groups \\
+*Irreflexive Object Properties & reflexive, $\neg$ & irreflexive property \\
+Disjoint Properties & $\sqsubseteq$, $\neg$ & disjoint property \\
+Disjoint Classes & $\sqcap$, $\sqsubseteq$ & disjoint class \\
+Context-Sp. Property Groups & $\sqcap$ & property group \\
 Context-Sp. Inclusive OR of P. & $\sqcup$ & inclusive or \\
-Context-Sp. Inclusive OR of P. Groups & $\sqcup$, $\sqcap$ & inclusive or, \\
-                                                          && property groups \\
+Context-Sp. Inclusive OR of P. Groups & $\sqcup$, $\sqcap$ & inclusive or \\
 Recursive Queries & - & recursive \\
-Individual Inequality & $\ne$ & \\
+Individual Inequality & $\ne$ & different individuals \\
 *Equivalent Properties & $\equiv$ & equivalent properties \\
-Property Assertions & = or $\ne$ & \\
-Data Property Facets & - & XSD or SPARQL constraining facets \\
-                        && examples: regex, xsd:pattern, ... \\
-Literal Pattern Matching & - & regex or xsd:pattern \\
-Negative Literal Pattern Matching & - & regex or xsd:pattern, $\neg$ \\ 
-*Object Property Paths & $\sqsubseteq$ & property paths \\
+Property Assertions & = or $\ne$ & =, $\ne$ \\
+Data Property Facets & - & SPARQL functions: \\
+                        && REGEX, STRLEN \\
+												&& XML Schema constraining facets: \\
+                        && xsd:length, xsd:minLength, xsd:maxLength, xsd:pattern, \\
+												&& xsd:enumeration, xsd:whiteSpace, xsd:maxInclusive, \\
+												&& xsd:maxExclusive,xsd:minExclusive, xsd:minInclusive, \\
+												&& xsd:totalDigits, xsd:fractionDigits \\
+Literal Pattern Matching & - & REGEX, xsd:pattern \\
+Negative Literal Pattern Matching & - & REGEX, xsd:pattern and $\neg$ \\ 
+*Object Property Paths & $\sqsubseteq$ & property path \\
 *Intersection & $\sqcap$ & intersection \\
@@
 *Universal Quantification & $\forall$ & universal quantification \\
-*Minimum Unqualified Cardinality & $\geq$ & \\
-*Minimum Qualified Cardinality & $\geq$ & \\
-*Maximum Unqualified Cardinality & $\leq$ & \\
-*Maximum Qualified Cardinality & $\leq$ & \\
+*Minimum Unqualified Cardinality & $\geq$ & $\geq$ \\
+*Minimum Qualified Cardinality & $\geq$ & $\geq$ \\
+*Maximum Unqualified Cardinality & $\leq$ & $\leq$ \\
+*Maximum Qualified Cardinality & $\leq$ & $\leq$ \\
 *Exact Unqualified Cardinality & $\geq$, $\leq$, $\sqcap$ & = \\
 *Exact Qualified Cardinality & $\geq$, $\leq$, $\sqcap$ & = \\
-*Transitive Object Properties & $\sqsubseteq$ & transitive \\
-Context-Sp. Exclusive OR of P. & $\neg$, $\sqcap$, $\sqcup$ & XOR \\
-Context-Sp. Exclusive OR of P. Groups & $\neg$, $\sqcap$, $\sqcup$ & XOR, $\sqcap$ \\
-Allowed Values & $\sqcup$ & allowed \\
-Not Allowed Values & $\sqcup$, $\neg$ & not allowed \\
+*Transitive Object Properties & $\sqsubseteq$ & transitive property \\
+Context-Sp. Exclusive OR of P. & $\neg$, $\sqcap$, $\sqcup$ & exclusive or \\
+Context-Sp. Exclusive OR of P. Groups & $\neg$, $\sqcap$, $\sqcup$ & exclusive or \\
+Allowed Values & $\sqcup$ & allowed values \\
+Not Allowed Values & $\sqcup$, $\neg$ & not allowed values \\
 %Literal Ranges & $\geq$, $\leq$, $\sqcap$ &  \\ 
-Literal Ranges & - & xsd:minInclusive \\
-               & & xsd:maxInclusive \\
+Literal Ranges & - & xsd:minInclusive, xsd:maxExclusive \\
+               & & xsd:maxInclusive, xsd:minExclusive \\
 %Negative Literal Ranges & $\geq$, $\leq$, $\sqcap$, $\neg$ & \\  
-Negative Literal Ranges & - & xsd:minInclusive \\
-                        & & xsd:maxInclusive \\
-Required Properties & $\exists$ & required \\
+Negative Literal Ranges & - & $\neg$ and \\  
+                        && xsd:minInclusive, xsd:maxExclusive \\
+                        && xsd:maxInclusive, xsd:minExclusive \\
+Required Properties & $\exists$ & required property \\
 
@@
 
-Optional Properties & $\exists$, $\sqsubseteq$ & optional properties \\
-Repeatable Properties & $\geq$ & repeatable properties \\
+Optional Properties & $\exists$, $\sqsubseteq$ & optional property \\
+Repeatable Properties & $\geq$ & repeatable property \\
 Negative Property Constraints & $\neg$, $\exists$ & negative properties \\
-*Individual Equality & = & \\
-*Functional Properties & functional & \\ 
-*Inverse-Functional Properties & inverse, functional & inverse functional \\
+*Individual Equality & = & equal individuals \\
+*Functional Properties & functional & functional property \\ 
+*Inverse-Functional Properties & inverse, functional & inverse functional property \\
 *Value Restrictions & $\exists$ & value restriction \\
 *Self Restrictions & $\exists$ & self restriction \\
-Primary Key Properties & inverse, functional & keyfor or primary key \\
-*Class-Specific Property Range & $\sqsubseteq$, $\exists$, $\neg$ & range \\
-*Class-Sp. Reflexive Object P. & reflexive & \\
-Membership in Controlled Vocabularies & $\forall$, $\sqcap$, $\sqcup$ & membership in \\
-  && controlled vocabularies \\
+Primary Key Properties & inverse, functional & primary key \\
+*Class-Specific Property Range & $\sqsubseteq$, $\exists$, $\neg$ & property range \\
+*Class-Sp. Reflexive Object P. & reflexive & reflexive property \\
+Membership in Controlled Vocabularies & $\forall$, $\sqcap$, $\sqcup$ & membership in controlled vocabularies \\
 IRI Pattern Matching & - & IRI pattern matching \\
-Literal Value Comparison & $>$ or $\geq$ or $<$ or & \\
+Literal Value Comparison & $>$ or $\geq$ or $<$ or & $>$, $\geq$, $<$, $\leq$, =, $\ne$ \\
                          & $\leq$ or = or $\ne$ & \\
-Ordering & - & order \\ 
+Ordering & - & ordered properties, ordered values \\ 
 Validation Levels & - & validation level \\ 
-String Operations & - & SPARQL string operations \\ 
-  && examples: STRLEN, \\ 
-	&& SUBSTR, CONTAINS \\
+String Operations & - & SPARQL string functions: \\ 
+                     && STRLEN, SUBSTR, UCASE, LCASE, \\
+										 && STRSTARTS, STRENDS, CONTAINS, \\ 
+										 && STRBEFORE, STRAFTER, ENCODE\_FOR\_URI, \\
+										 && CONCAT, langMatches, REGEX, REPLACE \\
 Context-Specific Valid Classes & - & context-specific valid classes \\
@@
 Default Values & - & default values \\
-Mathematical Operations & - & example: multiplication \\
+Mathematical Operations & - & addition, subtraction, multiplication, division \\
 Language Tag Matching & - & language tag matching \\
@@
 													  && language tag exact cardinality \\
-Whitespace Handling & - & whitespace \\
-HTML Handling & - & html \\
-Conditional Properties & $\sqsubseteq$ & conditional \\
-Recommended Properties & - & recommended \\
-Handle RDF Collections & - & actions on RDF collections \\
+Whitespace Handling & - & no whitespaces \\
+HTML Handling & - & no html \\
+Conditional Properties & $\sqsubseteq$ & conditional property \\
+Recommended Properties & - & recommended property \\
+Handle RDF Collections & - & actions on RDF collections: \\
+                          && append list element \\
 Value is Valid for Datatype & - & value is valid for datatype \\
-Use Sub-Super Relations in Validation & - & not redundant \\
-*Cardinality Shortcuts & & optional \& non-repeatable, \\
-                       & & optional \& repeatable \\
-											 & & mandatory \& non-repeatable \\
-											 & & mandatory \& repeatable \\
-Aggregations & - & aggregations \\
-                 && e.g., count \\
-*Class-Specific Irreflexive Object Properties & reflexive, $\neg$ & irreflexive \\
-Provenance & - & provenance \\   
-Data Model Consistency & - & SPARQL \\    
-Structure & - & SPARQL \\  
-Labeling and Documentation & - & SPARQL \\   
+Use Sub-Super Relations in Validation & - & non redundant properties \\
+*Cardinality Shortcuts & & optional \& non-repeatable property, \\
+                       & & optional \& repeatable property, \\
+											 & & mandatory \& non-repeatable property, \\
+											 & & mandatory \& repeatable property \\
+Aggregations & - & aggregations: \\
+                 && count \\
+*Class-Specific Irreflexive Object Properties & reflexive, $\neg$ & irreflexive property \\
+Provenance & - & provenance information required \\   
+Data Model Consistency & - & $<$SPARQL query$>$ \\    
+Structure & - & $<$SPARQL query$>$ \\  
+Labeling and Documentation & - & $<$SPARQL query$>$ \\   
 Vocabulary & - & vocabulary \\  

### 2015-07-16 paper/paper 2/dc-2015.tex
main part

--- 2015-07-15 paper/paper 2/dc-2015.tex
@@
 The power of SPIN is shown in 
-%The evaluation is explained in detail in the appendix of this paper \cite{BoschNolleAcarEckert2015}.
 Table \ref{tab:constraint-type-specific-expressivity}, where we list the fraction (and absolute numbers in brackets) of how many constraint types each of these languages supports \cite{BoschNolleAcarEckert2015}.
@@
           BIND( STRDT ( STR ( ?c ), xsd:nonNegativeInteger ) AS ?cardinality ) .
-          FILTER ( ?cardinality < ?minimumCardinality ) . \}
+          FILTER ( ?cardinality < 1 ) . 
+          FILTER ( ?C = Person ) .
+          FILTER ( ?p = author ) . \}
 
@@
 In this paper, we build on the experience gained from mapping several constraint languages to SPIN and from the analysis of the identified constraint types to create an intermediate layer, a framework that is able to describe the mechanics of all constraint types and that can be used to map high-level languages more easily.
-
-%%% DL introduction, not needed here...
-% -This constraint can either be represented generically (\emph{generic constraint}) by \emph{description logics (DL)}: {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}} or
-%The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
-%For this reason, we mapped constraint types to DL 
-%in order to determine which DL constructs are needed to express constraint types \cite{BoschNolleAcarEckert2015}.
-
-% The main contributions are:
-% \begin{enumerate}
-%  \item We develop a framework to describe constraints of any constraint type in a generic way (Section \ref{sec:vocabulary}).
-%  \item We demonstrate the application of this framework by mapping different constraint language to a unified intermediate representation that is not only mapped to SPIN, but also enables transformations to semantically equivalent constraints in other high-level constraint languages (Section \ref{sec:transformations}).
-%  \item We separate the implementation of the constraint type in SPIN from its expression in a high-level constraint language which makes the implementation reusable and allows a consistent validation across constraint languages (Section \ref{sec:validation}).
-% \end{enumerate}
-%
 
@@
 
-% \section{How to Provide the Validation of RDF Constraints Out-Of-The-Box}
-
 \paragraph{Consistent implementation.}
@@
 Our framework therefore proides a common ground that is solely based on the abstract definitions of the constraint types, as identified in our database. By providing a \emph{SPIN} mapping
-%generic validation implementations once 
 for each constraint type\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}\label{RDF-CV-2-SPIN}}, it is ensured that the details of the SPIN implementation are consistent irrespective of the constraint language and that the validation leads always to exactly the same results.
 
-\paragraph{Constraint transformations.} Consistent implementations of constraint languages provide some advantage, but it could be argued that they are not important enough to justify the additional layer.
+\paragraph{Constraint transformation.} Consistent implementations of constraint languages provide some advantage, but it could be argued that they are not important enough to justify the additional layer.
 The situation, however, is different when transformations from one constraint language to another are desired, i.e., to transform a \emph{specific constraint} (\emph{$sc_{\alpha}$}) of any constraint type expressed by language \emph{$\alpha$} into a semantically equivalent \emph{specific constraint} (\emph{$sc_{\beta}$}) of the same constraint type represented by any other language \emph{$\beta$}.
@@
 
-\section{A Vocabulary to Describe RDF Constraints of any RDF Constraint Type} 
+\section{Towards a framework} 
 \label{sec:vocabulary}
 
+When we implemented DSP and other constraint languages using SPARQL as intermediate language \cite{BoschEckert2014-2}, we found that many mappings actually resemble each other; particularly the mappings of the same constraint type in different languages, but also the mappings of different constraint types, though the latter only on a very superficial, structural level.
+The basic idea of our framework is very simple: we aim at reducing the representation of constraint types to the absolute minimum that has to be provided in a mapping to generate the appropriate SPIN implementation.
+Consider again our example from above for the SPIN implementation of \emph{minimum qualified cardinality restrictions}:
+
+\begin{ex}[commandchars=\\\{\}]
+\textit{SPIN:} CONSTRUCT \{ [ a spin:ConstraintViolation ... . ] \} WHERE \{ 
+          ?this ?p ?o ; a ?C .
+          BIND ( \textit{qualifiedCardinality}( ?this, ?p, ?C ) AS ?c ) .
+          BIND( STRDT ( STR ( ?c ), xsd:nonNegativeInteger ) AS ?cardinality ) .
+          FILTER ( ?cardinality < 1 ) . 
+          FILTER ( ?C = Person ) .
+          FILTER ( ?p = author ) . \}
+
+\textit{SPIN function qualifiedCardinality:}										
+SELECT ( COUNT ( ?arg1 ) AS ?c ) WHERE \{ ?arg1 ?arg2 ?o . ?o a ?arg3 . \}
+\end{ex}
+
+However this SPIN code looks like, all we have to provide to make it work is the desired minimum cardinality (?cardinality), the property to be constrained (?p) and the class for which this property should be constrained (?C).
+All other variables are bound internally.
+So we could reduce the effort of the mapping by simply providing these three values, which are readily available in all representations of this constraint type:
+
+\begin{ex}[commandchars=\\\{\}]
+\textit{OWL 2:} Publication a owl:Restriction ;
+          owl:minQualifiedCardinality 1 ;
+          owl:onProperty author ;
+          owl:onClass Person .
+
+\textit{ShEx:} Publication \{ author @Person\{1, \} \}
+
+\textit{ReSh:} Publication a rs:ResourceShape ; rs:property [
+          rs:propertyDefinition author ;
+          rs:valueShape Person ;
+          rs:occurs rs:One-or-many ; ] .
+
+\textit{DSP:} [ dsp:resourceClass Publication ; dsp:statementTemplate [ 
+          dsp:minOccur 1 ; dsp:maxOccur "infinity" ; 
+          dsp:property author ; 
+          dsp:nonLiteralConstraint [ dsp:valueClass Person ] ] ] .
+\end{ex}
+
+% -This constraint can either be represented generically (\emph{generic constraint}) by \emph{description logics (DL)}: {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}} or
+%The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
+%For this reason, we mapped constraint types to DL 
+%in order to determine which DL constructs are needed to express constraint types \cite{BoschNolleAcarEckert2015}.
+
 Prerequisites to develop a vocabulary to describe RDF constraints of any RDF constraint type are (1) to specify the underlying semantics for RDF validation and thus for the vocabulary and (2) to define a basic terminology and classification system for RDF constraints which lay the ground for discussions on RDF validation.
-
-\subsection{Semantics for RDF Validation}
 
@@
 If RDF validation would assume OWA and nUNA just like OWL 2 does, validation won’t be that restrictive and therefore we won’t get the intended validation results.
-%
-%OWL 2 reasoning is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true. 
-%%which fits its primary design purpose to represent knowledge on the World Wide Web. 
-%%Most of the constraint languages except OWL, have a major shortcoming of redundancy.
-%%With its open-world semantics, used as a constraint language, OWL solves the redundancy problem. 
-%%\tb{the following example does not show the redundancy problem!}
-%%\tb{2. benefit: reasoning solves redundancy problem}
-%As each book must have a title {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a book {\small\ms{(Book(Hamlet)),}}
-%{\em Hamlet} must have at least one title.
-%In an OWA setting, this axiom does not cause a constraint violation (even if there is no explicitly defined title), since there must be a title for this book which we may not know. 
-%On the other hand, RDF validation scenarios require the \emph{closed-world assumption (CWA)}, i.e., a statement is inferred to be false if it cannot be proved to be true.
-%When assuming the CWA, a constraint violation is raised as there is no explicitly defined title. 
-%A constraint that says that a book must have at least one title in OWA, 
-%does not mean that the title has to be unique. 
-%In every model  (an interpretation that makes a set of \emph{DL knowledge base} true), 
-%it can be the case that a book has a single title, however, 
-%this title is not unique. 
-%In some models it is \emph{The-Adventures-of-Huckleberry-Finn}, in others it is \emph{Die-Abenteuer-des-Huckleberry-Finn}. 
-%And since in every model there is only one, DL sentences are satisfied. 
-%But this does not correspond to the intended constraint which is usual in CWA way.   
-%%Classical constraint languages are based on the CWA where constraints need to be satisfied only by named individuals which yields a constraint violation.
-%This ambiguity in semantics is one of the main reasons why OWL 2 has not been adopted as a standard constraint language for RDF validation in the past. 
-%In case we want to use OWL 2 as a constraint language, we adopt the same semantics (CWA and UNA) as for RDF validation in general. 
-%In case we want to use OWL 2 as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general. 
-%\tb{feedback from Erman: the major problem is semantics.
-OWL basically work in different semantics than others.
-And their semantics are formal.
-Closed world vs.
-Open World is also a part of this.
-/ Thomas: I think your issue is tackled now?
-No.}
-%
-%comments from Erman:
-%
-%\begin{itemize}
-%\item If a constraint is represented (recognized) by two different languages, that means, whenever it is violated in one language it is violated in other.
-We have to provide formal generic semantics for it; formally prove those statements.}
-%
-%\item This is simple. You write that:
-%In case we want to use OWL 2 as a constraint language, we adopt the same semantics (CWA) that is for RDF validation in general.
-%The question is how to adopt CWA for OWL2, because it wont behave CWA way, just because we want it.
-So I say, in order to show that it behaves exactly we want it to, we should show that for the cases that we express a constraint (that we speak) in a classical constraint language, say, Scheme (therefore CWA) and  also OWL,  whenever the constraint in Scheme is violated, it's OWL correspondence is also violated.
-That shows that they behave in the same way, as they should.
-%
-%\item So if you read again my comment again, without knowing which semantics those constraint languages have, one actually does is to show, given an RDF-data it is violated in one language iff it is violated in other.
-And this actually corresponds to the very idea of transformation and generic semantics.
-%
-%\item Now, what is a generic semantics? 
-%It is, the semantics we had in our mind, when typing this long document, that we tried to underpin by the DL language.
-However, regarding CWA and OWA, it is possible that we made some mistakes.
-In order to ensure that, say, if its DL, one needs to show that, a constraint/query written a particular language should have the same answer with its correspondent DL query.
-%\end{itemize}
-%
+
 Differences in semantics may lead to differences in validation results when applied to particular constraint types.
@@
 
-%We defined the \textbf{formal generic semantics of the vocabulary} to describe constraints of any constraint type in a generic way (see paper appendix):
-%(1) We mapped constraint types to DL to logically underpin them and 
-%(2) we described the constraint types' intended behavior in terms of validation results depending on CWA and UNA.
-%To be able to define mappings between \emph{specific constraints} (expressed by different languages) and \emph{generic constraints},
-%we show for each constraint type that a constraint expressed by a particular language leads to the same answer as the corresponding DL query.
-%To be able to specify transformations between \emph{specific constraints} (expressed by different languages),
-%identical semantics of the languages with regard to the particular constraint type has to be ensured.
-%%Constraint languages assume identical semantics, 
-%%if for each constraint the following condition holds:
-%If a constraint is represented by \emph{ShEx} and OWL 2, 
-%the validation results must be exactly the same, i.e.,
-%whenever the \emph{specific constraint} \emph{$sc_{ShEx}$} is violated, its \emph{$sc_{OWL 2}$} correspondence is also violated which shows that they behave in the same way.
-%We expressed constraint types by different languages
-%to document identical semantics for these languages with regard to appropriate constraint types.
-
-%\textcolor{red}{feedback from Erman:}
-
-%\textcolor{red}{
-%-About the paragraph; it says we defined a formal generic semantics.
-Did we?
-(if you think so please defend) but i think its not true.
-A formal semantics, is where you talk about an interpretation e.g., like in DL, there the semantics/interpretation is a mathematical object (therefore formally defined).
-What i believe is that paper propose  rather a schema for transforming constraint languages to one another (in particular to assess them in the first paper), that a person who doesn't know one language can have operation power etc..
-.
-%}
-%
-%\textcolor{red}{
-%-so I think we should get rid of this paragraph either totally or partially and you talk about the formulation instead briefly one-two sentence.
-I know that you wrote this paragraph to make my points and thanks a lot for that, but they were general remarks, so we cannot point out something that we do not do at that point, if its not at the "future work" or smth.
-Also this underpininng and  so on, these things were in the other paper (arxiv).
-If it has a point, then better referencing it.
-%}
-
-%\textcolor{red}{
-%-please be careful with the narration:
-%To be able to define mappings between specific constraints (expressed by different languages) and generic constraints, we show for each constraint type that a constraint expressed by a particular language leads to the same answer as the corresponding DL query.
-%When you read it and next sentence, it does not flow.  I know that it is not easy to write it nicely. But it also has technical problems, like
-%}
-%
-%\textcolor{red}{
-%A constraint  that is expected to give the same answer with a query.
-Those things are not of the same type.
-When I have written this query/constraint analogy, it was rather to provide an intuition.
-If we gonna talk about constraints; a constraint written in different languages always have the same restriction on any possible rdf-data.
-This means, if any two constraints are semantically the same (w.r.t.
-RDF data semantics), they should detect the same set of violations regardless of RDF data (which means whenever you apply them to any rdf data they point out the same violations or they have the same effect).
-Using a query language for validation, is a related but another thing.
-You actually know what it is better than I do.
-%}
-
-%Erman:
-%Section 3.1, explains a possible application only in an example specific to UNA and nUNA case, and I also have the 
-%feeling that it is so spread out to the whole work (paper1  especially), and in the core of technical parts. That is, whenever we mean CWA vs. OWA, we turn our head to UNA vs. nUNA.
-%
-%The thing I wanted to point out is that, the difference in CWA and OWA and its consequence/incompatibility is more general (as you also may probably noticed)  than the use of "UNA vs.
-nUNA".
-The example I gave  is independent from the assumption of UNA  or nUNA.
-%
-%You don't need to change something asap, but I think we can improve the exposition of any paper, by giving a classical constraint, how it is done classical in CWA, and how it is done in OWA, and then introducing the extra benefit, redundancy for instance.
-%
-%A constraint that says book should have a single author in OWA, does not mean that it has a unique author.
-In every model  (an interpretation that makes a set of DL knowledge base true), it can be the case that a book has a single author, however, bringing all those together, this author is not unique.
-In some models it is Ali, in others its Veli.
-And since in every model there is only one, DL sentences are satisfied.
-But this does not correspond to the intended constraint which is usual in CWA way.
-
-\subsection{Basic Terminology and Classification System for RDF Constraints}
-%\subsection{Basic Terminology for the Formulation of RDF Constraints}
+\subsection{Constraining Elements}
 

### 2015-07-16 paper/paper 2/dc-2015.tex
Building blocks

@@
 
-% -This constraint can either be represented generically (\emph{generic constraint}) by \emph{description logics (DL)}: {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}} or
-%The knowledge representation formalism {\em DL}, with its  well-studied theoretical properties, provides the foundational basis to express constraints in a generic way. 
-%For this reason, we mapped constraint types to DL 
-%in order to determine which DL constructs are needed to express constraint types \cite{BoschNolleAcarEckert2015}.
+In further investigation of all kind of constraints and particularly the list of constraint types, we aimed at identifying the building blocks of such constraints to come up with a concise representation of every constraint type.
+
+\subsection{Building blocks}
+
+At the core, we use a very simple conceptual model for constraints, using a small vocabulary called \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.
+The conceptual model is shown in Figure \ref{fig:RDF-CV-conceptual-model}.
+\begin{figure}[H]
+	\centering
+		\includegraphics[width=0.60\textwidth]{images/RDF-CV.png}
+	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} Conceptual Model}
+	\label{fig:RDF-CV-conceptual-model}
+\end{figure}
+
+\emph{Simple constraints} denotes the set of atomic constraints with respect to a single constraining element -- we will come to the notion of a constraining element in a second.
+In contrast, there are
+\emph{complex constraints}, i.e., the set of constraints which are created out of \emph{simple} and/or other \emph{complex constraints}.
+This structure therefore allows to build complex constraints out of other (simple or complex) constraints.
+Regarding our database of constraint types, 60\% of the constraint types are simple constraints and 26\% are complex constraints.
+Constraints of additional 14\% of the constraint types are \emph{complex constraints} as well which can be simplified and therefore formulated as \emph{simple constraints} if additional constraining elements are introduced to cover them.
+
+The properties describing a simple constrained are very structural.
+The central property is the \emph{constraining element} which refers to one of 103 contraining elements described in our technical report \cite{BoschNolleAcarEckert2015}.
+Constraining elements are for example taken from Description Logics, another concrete example would be 'regex' where a regular expression is checked against some property value.
+Sometimes the constraining elements directly correspond to a constraint type, sometime (as for regex) they are shared by several constraint types.
+Complex constraints again need several constraing elements to be expressed.
+
+Irrespective of and additonal to the constraining element, there are properties to describe the actual constraint, they can also be seen as parameters for the constraining element.
+The \emph{context class} limits the constraint to individuals of a specific class.
+Depending on the constraining elements, a list of \emph{classes} can be provided, for example to determine the valid classes for a value or to define a class intersection to be used in a constraint.
+\emph{leftProperties} and \emph{rightProperties} are lists usually containing properties the constraint is applied to.
+A typical example for a constraint with a right hand side list of properties would be R43, literal value comparision, where constraints like birthDate < deathDate can be expressed.
+
+Finally, the \emph{constrainig value} contains a literal value to be checked against; for instance in the case of the 'regex' element, it contains the regular expression to be evaluated.
+
+This simple structure plus the constraining elements form the building blocks of our proposed framework.
+In the technical report \cite{BoschNolleAcarEckert2015}, we list for every constraint type its representation in our framework which not only shows that constraints of any constraint type can indeed be described generically in this way, but which also forms the starting point for any mappings using this framework.
+
+\textbf{\emph{DL Expressivity}:}
+The \emph{RDF-CV} allows to describe 
+constraints which are either \emph{expressible in DL} (64\%) or which are \emph{not expressible in DL} (36\%).
+Constraints which are expressible in DL are instantiated from 64\% of the overall 81 constraint types.
+On the other hand, constraints which are not expressible in DL are assigned to 36\% of all constraint types.
+%In case a constraint type is \emph{expressible in DL}, we determined which DL constructs are needed to express the constraint type.
+
+Altogether, instances of the most of the constraint types are \emph{simple constraints on properties} which are \emph{expressible in DL}.
 
@@
 
-\subsection{Constraining Elements}
-
-A \emph{constraint language} is a language which is used to formulate constraints.
-The W3C working group defines \emph{RDF constraint} as a component of a schema what needs to be satisfied\footnote{\url{https://www.w3.org/2014/data-shapes/wiki/Glossary}}.
-As there are already five promising constraint languages, 
-our purpose is not to invent a new language.
-As there is no high-level declarative language which meets all RDF validation requirements,
-we rather developed a very simple lightweight vocabulary,
-consisting of only three classes, three object properties, and three data properties, 
-which is universal enough to describe constraints of any constraint type.
-We call this vocabulary the \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}} whose conceptual model is shown in Figure \ref{fig:RDF-CV-conceptual-model}.
-\begin{figure}[H]
-	\centering
-		\includegraphics[width=0.60\textwidth]{images/RDF-CV-conceptual-model.png}
-	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} Conceptual Model}
-	\label{fig:RDF-CV-conceptual-model}
-\end{figure}
-
-We classify sets of constraints according to four dimensions.
-For each constraint type, we evaluated \cite{BoschNolleAcarEckert2015} in which set of constraints their instances are contained.
-%In the following, we state the rounded number of associated constraint types in brackets.
-%\begin{itemize}
-  %\item \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints}
-	%\item \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints}
-	%\item \emph{Context:} \emph{property constraints} vs. \emph{class constraints}
-	%\item \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}
-%\end{itemize}
-%(1) \emph{Universality:} \emph{specific constraints} vs. \emph{generic constraints},
-%(2) \emph{Complexity:} \emph{simple constraints} vs. \emph{complex constraints},
-%(3) \emph{Context:} \emph{property constraints} vs. \emph{class constraints}, and
-%(4) \emph{DL Expressivity:} \emph{constraints expressible in DL} vs. \emph{constraints not expressible in DL}.
-
-\textbf{\emph{Universality}:}
-Constraints are expressible either generically (\emph{generic constraints}) using the \emph{RDF-CV}   
-or specifically (\emph{specific constraints}) by domain-specific constraint languages. 
-As we express constraints of each constraint type in form of \emph{generic constraints} conforming to the \emph{RDF-CV} \cite{BoschNolleAcarEckert2015},
-we show that constraints of any constraint type can be described generically.
-
-\textbf{\emph{DL Expressivity}:}
-The \emph{RDF-CV} allows to describe 
-constraints which are either \emph{expressible in DL} (64\%) or which are \emph{not expressible in DL} (36\%).
-Constraints which are expressible in DL are instantiated from 64\% of the overall 81 constraint types.
-On the other hand, constraints which are not expressible in DL are assigned to 36\% of all constraint types.
-%In case a constraint type is \emph{expressible in DL}, we determined which DL constructs are needed to express the constraint type.
-
-\textbf{\emph{Complexity}:}
-\emph{Simple constraints} (60\% of the constraint types) denotes the set of atomic constraints. 
-%which can be instantiated from almost 2/3 of the constraint types.
-\emph{Complex constraints} (26\%) is the set of constraints which are created out of \emph{simple} and/or other \emph{complex constraints}.
-%and which are instances of 1/4 of the constraint types.
-%In case \emph{complex constraints} are expressible in DL, 
-%DL statements representing \emph{complex constraints} contain DL statements standing for atomic and/or composed constraints. 
-Constraints of almost 14\% of the constraint types are \emph{complex constraints} which can be simplified and therefore formulated as \emph{simple constraints} when using them in terms of syntactic sugar.
-
-\textbf{\emph{Context}:}
-\emph{Simple constraints} are applied on properties (\emph{property constraints}, 60\%),
-on classes (\emph{class constraints}, 25\%), or
-on properties and classes (\emph{property and class constraints}, 15\%).
-%2/3 of all constraint types are types of \emph{property constraints}, 
-%1/5 of \emph{class constraints}, and 
-%approx. 10\% of \emph{property and class constraints}.
-\emph{Simple constraints} must hold for individuals of their associated \emph{context classes}.
-As \emph{context classes} of \emph{simple constraints} are reused within \emph{complex constraints},
-it does not make sense to have terms standing for \emph{simple} and \emph{complex constraints} within the \emph{RDF-CV}. 
-As a consequence, the distinction of \emph{property} and \emph{class constraints} is sufficient to generically describe constraints of all constraint types.
-%\tb{use RDF-CV / not: expressible in RDF-CV / RDF-CV is a vocabulary, not a language}
-
-Altogether, instances of the most of the constraint types are \emph{simple constraints on properties} which are \emph{expressible in DL}. 
-%Thus, the majority of constraint types are directly and relatively easy formulated in form of \emph{simple constraints} which can be mapped to equivalent DL constructs.
-
 \subsection{\emph{Simple Constraints}}
 
-The implementation model of the \emph{RDF-CV} (Figure \ref{fig:RDF-CV-implementation-model}) shows that
-both \emph{property constraints} and \emph{class constraints} are \emph{simple constraints}. 
-%For both \emph{property} and \emph{class constraints} a \emph{context class}, a list of \emph{classes}, the \emph{constraining element}, and the \emph{constraining value} can be stated. 
-%Lists of \emph{left} and \emph{right properties} can only be specified for \emph{property constraints}.
-\begin{figure}[H]
-	\centering
-		\includegraphics[width=0.80\textwidth]{images/RDF-CV-implementation-model.png}
-	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} Implementation Model}
-	\label{fig:RDF-CV-implementation-model}
-\end{figure}
-A simple constraint holds for all individuals of their associated \emph{context class}.
 The \emph{minimum qualified cardinality restriction (R-75)} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person,}}

### 2015-07-16 paper/paper 2/dc-2015.tex
less than fixed

@@
 \emph{leftProperties} and \emph{rightProperties} are lists usually containing properties the constraint is applied to.
-A typical example for a constraint with a right hand side list of properties would be R43, literal value comparision, where constraints like birthDate < deathDate can be expressed.
+A typical example for a constraint with a right hand side list of properties would be R43, literal value comparision, where constraints like birthDate $<$ deathDate can be expressed.
 

### 2015-07-16 paper/paper 2/dc-2015.tex
semantics

@@
 
-\textbf{\emph{DL Expressivity}:}
-The \emph{RDF-CV} allows to describe 
-constraints which are either \emph{expressible in DL} (64\%) or which are \emph{not expressible in DL} (36\%).
-Constraints which are expressible in DL are instantiated from 64\% of the overall 81 constraint types.
-On the other hand, constraints which are not expressible in DL are assigned to 36\% of all constraint types.
-%In case a constraint type is \emph{expressible in DL}, we determined which DL constructs are needed to express the constraint type.
-
-Altogether, instances of the most of the constraint types are \emph{simple constraints on properties} which are \emph{expressible in DL}.
-
-Prerequisites to develop a vocabulary to describe RDF constraints of any RDF constraint type are (1) to specify the underlying semantics for RDF validation and thus for the vocabulary and (2) to define a basic terminology and classification system for RDF constraints which lay the ground for discussions on RDF validation.
-
-RDF validation and OWL 2 assume different semantics. 
-This ambiguity in semantics is one of the main reasons why OWL 2 has not been adopted as a standard constraint language for RDF validation in the past.
-We compare semantics of RDF validation and OWL 2 as OWL 2 is considered as a constraint language 
-in case the semantics for RDF validation is applied.
-
-OWL 2 is based on the {\em open-world assumption} \emph{(OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose to represent knowledge on the World Wide Web.
-As each book must have a title {\small\ms{(Book $\sqsubseteq \exists$ title.$\top$)}} and {\em Hamlet} is a book, %{\small\ms{(Book(Hamlet)),}}
-{\em Hamlet} must have a title as well.
-In an OWA setting, this constraint does not cause a violation, even if there is no explicitly defined title, since there must be a title for this book which we may not know. 
-%($\mathcal{K}$ is consistent).
-As RDF validation has its origin in the XML world,
-many RDF validation scenarios require the {\em closed-world assumption} \emph{(CWA)}, i.e., a statement is inferred to be false if it cannot be proved to be true.
-Thus, classical constraint languages are based on the CWA where constraints need to be satisfied only by named individuals. 
-Since there is no explicitly defined title for the book {\em Hamlet}, the CWA yields to a violation.
-
-RDF Validation requires that different names represent different objects (\emph{unique name assumption (UNA)}), whereas,
-OWL 2 is based on the {\em non-unique name assumption (nUNA)}.  
-If we define the property \emph{title} to be functional {\small\ms{(funct (title)),}} a book can have at most one distinct title.
-UNA causes a clash
-if the book {\em Huckleberry-Finn} has more than one title.
-For nUNA, however, reasoning concludes that the title {\em The-Adventures-of-Huckleberry-Finn} must be the same as the title {\em Die-Abenteuer-des-Huckleberry-Finn} 
-which resolves the violation. 
-%Although, OWL 2 does not assume UNA, OWL 2 has the constructs \emph{owl:sameAs} and \emph{owl:differentFrom} to state that two names are the same or different.
-
-If RDF validation would assume OWA and nUNA just like OWL 2 does, validation won’t be that restrictive and therefore we won’t get the intended validation results.
-
-Differences in semantics may lead to differences in validation results when applied to particular constraint types.
-This is important 
-as for 56.8\% of the constraint types validation results differ if the CWA or the OWA is assumed 
-and as for 66.6\% of the constraint types validation results are different in case the UNA or the nUNA is assumed \cite{BoschNolleAcarEckert2015}.
-
-Constraints are identical w.r.t. RDF semantics, 
+paragraph{Formal approach and semantics.}
+
+A cornerstone of the framework is the generic representation of a constraint, which can often be done using \emph{Description Logics (DL)}, as for the \emph{minimum qualified cardinality restrictions}: {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}}
+
+It turned out that 64\% of the 81 constraint types are actually expressible in DL.
+Only for the remaining 36\%, other means, i.e., other constraining elements, had to be identified.
+This is not surprising if we consider that OWL is based on Description Logics.
+When we talk about using Description Logics to represent constraints, we have to establish once more that the semantics of OWL and Description Logics differ from the semantics of constraint languages regarding the open world assumption (OWA) and the non-unique naming assumption (nUNA).
+Both are usually assumed when dealing with OWL or DL, whereas validation usually assumes a closed world (CWA) and unique naming (UNA), i.e., if a desired property is missing, this leads to a violation and if two resources are named differently, they are assumed to be different resources.
+
+We won't get into details about these assumptions here, but it has to be noted that the applied semantics have to be defined if validation is performed, as the results would differ under different semantics.
+Precisely, we found that for 56.8\% of the constraint types validation results differ if the CWA or the OWA is assumed
+and for 66.6\% of the constraint types validation results are different in case the UNA or the nUNA is assumed \cite{BoschNolleAcarEckert2015}.
+
+For the purpose of a consistent implementation and transformation of constraints, constraints are semantically equivalent  
 if they detect the same set of violations regardless of RDF data, 
 which means whenever the constraints are applied to any RDF data they point out the same violations.
-As we use multiple languages to express constraints of constraint types, 
-%in the first appendix of this paper,
-we thereby document identical semantics of these languages with regard to given constraint types \cite{BoschNolleAcarEckert2015}.
-This is also important in order to prove that semantically equivalent \emph{specific constraints} and corresponding \emph{generic constraints}
-behave in the same way w.r.t. validation results which semantically underpins bidirectional mappings.
 

### 2015-07-16 paper/paper 2/dc-2015.tex
typo
transformations

@@
 
-paragraph{Formal approach and semantics.}
+\paragraph{Formal approach and semantics.}
 
@@
 
+\subsection{Constraint Transformation}
+
+Constraint of the type \emph{minimum qualified cardinality restriction (R-75)} expressed in OWL 2:
+
+\begin{ex}[commandchars=\\\{\}]
+Publication 
+    a owl:Restriction ;
+    owl:minQualifiedCardinality 1 ;
+    owl:onProperty author ;
+    owl:onClass Person .
+\end{ex}
+
+The same constraint expressed generically using the RDF-CV:
+
+\begin{ex}[commandchars=\\\{\}]
+[   a rdfcv:SimpleConstraint ;
+    rdfcv:contextClass :Publication ;
+    rdfcv:leftProperties ( :author ) ;
+    rdfcv:classes ( :Person ) ;
+    rdfcv:constrainingElement "minimum qualified cardinality restriction" ;
+    rdfcv:constrainingValue 1 ] .
+\end{ex}
+
+SPIN inference rule to infer the generic constraint:
+
+\begin{ex}
+rdfcv2spin:ToInfer 
+	spin:rule [
+		a sp:Construct ;
+        	sp:text """
+            	CONSTRUCT {            
+                    :minimum-qualified-cardinality-restrictions
+                        a rdfcv:SimpleConstraint ;
+  				        rdfcv:contextClass ?this ;
+  				        rdfcv:leftProperties :leftProperties ;
+				        rdfcv:classes :classes ;
+				        rdfcv:constrainingElement "minimum qualified cardinality restriction" ;
+				        rdfcv:constrainingValue ?cv .  
+				    :leftProperties 
+				        rdf:first ?lp1 ;
+                        rdf:rest rdf:nil .    
+                    :classes 
+				        rdf:first ?c1 ;
+                        rdf:rest rdf:nil .  
+            	}
+            	WHERE {
+				    ?this
+				        a owl:Restriction ;
+				        owl:minQualifiedCardinality ?cv ;
+				        owl:onProperty ?lp1 ;
+				        owl:onClass ?c1 .         
+        		} """ ; ] .
+\end{ex}
+
+The property \emph{spin:rule} can be used to link an rdfs:Class with SPARQL CONSTRUCT queries.
+Each query defines an inference rule that is applied to all instances of the associated class and its subclasses.
+The inference rule defines how additional triples can be inferred from what is stated in the WHERE clause.
+For each binding of the pattern in the WHERE clause of the rule, the triple templates from the CONSTRUCT clause are instantiated and added as inferred triples to the underlying model.
+At query execution time, the SPARQL variable ?this is bound to the current instance of the class.
+
 \section{Related Work}

### 2015-07-16 paper/paper 2/dc-2015.tex
transformations

@@
 
-SPIN inference rule to infer the generic constraint:
+SPIN inference rule to infer the generic constraint out of the constraint expressed by OWL 2:
 
 \begin{ex}
-rdfcv2spin:ToInfer 
-	spin:rule [
-		a sp:Construct ;
-        	sp:text """
+owl:Thing 
+    spin:rule [ a sp:Construct ; sp:text """
         CONSTRUCT {            
@@
                 rdf:first ?c1 ;
-                        rdf:rest rdf:nil .  
-            	}
+                rdf:rest rdf:nil . }
         WHERE {
@@
                 owl:onProperty ?lp1 ;
-				        owl:onClass ?c1 .         
-        		} """ ; ] .
+                owl:onClass ?c1 . } """ ; ] .
 \end{ex}
@@
 At query execution time, the SPARQL variable ?this is bound to the current instance of the class.
+As each resource per default is assigned to the class owl:Thing, this inference rule is evaluated for each subject of the input RDF graph.
+
+SPIN inference rule to infer the OWL 2 constraint out of the generically expressed constraint:
 

### 2015-07-16 paper/paper 2/dc-2015.tex
transformations
inverse transformations

@@
 
-\subsection{Constraint Transformation}
+\subsection{Bidirectional Constraint Transformations}
 
@@
 
+\subsection{XXX}
+
+\begin{ex}
+owl:Thing 
+    spin:rule [ a sp:Construct ; sp:text """
+        CONSTRUCT {            
+            ?cc
+                a owl:Restriction ;
+                owl:minQualifiedCardinality ?cv ;
+                owl:onProperty ?lp1 ;
+                owl:onClass ?c1 . }
+        WHERE { 
+            ?this
+                a rdfcv:SimpleConstraint ;
+                rdfcv:contextClass ?cc ;
+                rdfcv:leftProperties ?leftProperties ;
+                rdfcv:classes ?classes ;
+                rdfcv:constrainingElement "minimum qualified cardinality restriction" ;
+                rdfcv:constrainingValue ?cv .  
+            ?leftProperties 
+                rdf:first ?lp1 ;
+                rdf:rest rdf:nil .    
+            ?classes 
+                rdf:first ?c1 ;
+                rdf:rest rdf:nil . } """ ; ] .
+\end{ex}
+
 \section{Related Work}

### 2015-07-16 paper/RDF validation requirements/RDF validation requirements.tex
3.2 and 3.3

@@
 *Universal Quantification & $\forall$ & universal quantification \\
-*Minimum Unqualified Cardinality & $\geq$ & $\geq$ \\
-*Minimum Qualified Cardinality & $\geq$ & $\geq$ \\
-*Maximum Unqualified Cardinality & $\leq$ & $\leq$ \\
-*Maximum Qualified Cardinality & $\leq$ & $\leq$ \\
-*Exact Unqualified Cardinality & $\geq$, $\leq$, $\sqcap$ & = \\
-*Exact Qualified Cardinality & $\geq$, $\leq$, $\sqcap$ & = \\
+*Minimum Unqualified Cardinality & $\geq$ &  minimum unqualified cardinality restriction \\
+*Minimum Qualified Cardinality & $\geq$ &  minimum qualified cardinality restriction \\
+*Maximum Unqualified Cardinality & $\leq$ &  maximum unqualified cardinality restriction \\
+*Maximum Qualified Cardinality & $\leq$ &  maximum qualified cardinality restriction \\
+*Exact Unqualified Cardinality & ( $\geq$, $\leq$, $\sqcap$ ) or = &  exact unqualified cardinality restriction \\
+*Exact Qualified Cardinality & ( $\geq$, $\leq$, $\sqcap$ ) or = &  exact qualified cardinality restriction \\
 *Transitive Object Properties & $\sqsubseteq$ & transitive property \\

### 2015-07-16 paper/paper 2/dc-2015.tex
3.2 and 3.3

@@
 which restricts publications to have at least one author which must be a person,
-is an example of a property constraint on \emph{author}
+is an example of a simple constraint on \emph{author}
 which holds for all individuals of the class \emph{Publication}.
-Table \ref{tab:property-constraint-cardinality-restriction} displays how the property constraint is generically represented using the RDF-CV.
+Table \ref{tab:property-constraint-cardinality-restriction} displays how the simple constraint is generically represented using the RDF-CV.
+Note that instead of the description logics construct $\geq$, the constraining element \emph{minimum qualified cardinality restriction} may be used.
+
 \begin{table}[H]
@@
 	\centering
-		\begin{tabular}{c|c|c|c|c|c|c}
-      \textbf{constraint set} & \textbf{context class} & \textbf{left property list} & \textbf{right p. list} & \textbf{classes} & \textbf{constraining element} & \textbf{c. value} \\
+		\begin{tabular}{c|c|c|c|c|c}
+      \textbf{context class} & \textbf{left property list} & \textbf{right p. list} & \textbf{classes} & \textbf{constraining element} & \textbf{c. value} \\
       \hline
-      property & Publication & author & - & Person & $\geq$ & 1 \\
+      Publication & author & - & Person & $\geq$ & 1 \\
 		\end{tabular}
@@
 	\centering
-		\begin{tabular}{l|l|l|l|l|l|l}
-      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+		\begin{tabular}{c|c|c|c|c|c}
+      \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
       \hline
-      property & $\top$ & authorOf, genre & authorOfGenre & $\top$ & property paths & - \\
+      $\top$ & authorOf, genre & authorOfGenre & $\top$ & property path & - \\
 		\end{tabular}
@@
 	\centering
-		\begin{tabular}{l|l|l|l|l|l|l}
-      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+		\begin{tabular}{c|c|c|c|c|c}
+      \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
       \hline
-      class & ISBN & - & - & xsd:string & regex & '\string^\text{$\backslash$d$\{9\}$[$\backslash$d$\mid$X]}\$' \\
-      property & Book & identifier & - & ISBN & universal quantification & - \\
+      ISBN & - & - & xsd:string & REGEX & '\string^\text{$\backslash$d$\{9\}$[$\backslash$d$\mid$X]}\$' \\
+      Book & identifier & - & ISBN & universal quantification & - \\
 		\end{tabular}
@@
 	\centering
-		\begin{tabular}{l|l|l|l|l|l|l}
-      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+		\begin{tabular}{c|c|c|c|c|c}
+      \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
       \hline
-class & Publication & - & - & E, F & XOR of property groups & - \\
-class & E & - & - & A, B & intersection & - \\
-class & F & - & - & C, D & intersection & - \\
-property & A & isbn & - & string & = & 1 \\
-property & B & title & - & string & = & 1 \\
-property & C & issn & - & string & = & 1 \\
-property & D & title & - & string & = & 1 \\
+Publication & - & - & E, F & exclusive or & - \\
+E & - & - & A, B & intersection & - \\
+F & - & - & C, D & intersection & - \\
+A & isbn & - & string & = & 1 \\
+B & title & - & string & = & 1 \\
+C & issn & - & string & = & 1 \\
+D & title & - & string & = & 1 \\
 		\end{tabular}
@@
 	\centering
-		\begin{tabular}{l|l|l|l|l|l|l}
-      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+		\begin{tabular}{c|c|c|c|c|c}
+      \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
       \hline
-property & $\top$ & isbn$^{-}$ & isbn$^{-}$ & - & inverse property & - \\
-property & Book & isbn$^{-}$ & - & - & functional property & - \\
+$\top$ & isbn$^{-}$ & isbn$^{-}$ & - & inverse property & - \\
+Book & isbn$^{-}$ & - & - & functional property & - \\
 		\end{tabular}
@@
 \begin{ex}[commandchars=\\\{\}]
-[   a \textit{rdfcv:PropertyConstraint} , \textit{rdfcv:SimpleConstraint} ;
-    \textit{rdfcv:contextClass} Book ; \textit{rdfcv:leftProperties} ( isbn ) ; \textit{rdfcv:constrainingElement} "keyfor" ] .
+[   a \textit{rdfcv:SimpleConstraint} ;
+    \textit{rdfcv:contextClass} Book ; 
+    \textit{rdfcv:leftProperties} ( isbn ) ; 
+    \textit{rdfcv:constrainingElement} "primary key" ] .
 \end{ex}
@@
 	\centering
-		\begin{tabular}{l|l|l|l|l|l|l}
-      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+		\begin{tabular}{c|c|c|c|c|c}
+      \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
       \hline
-property & $\exists$ authorOf.Self & authorOf & - & Self & existential quantification & - \\
-class & $\neg$ $\exists$ authorOf.Self & - & - & $\exists$ authorOf.Self & negation & - \\
-class & $\top$ & - & - & $\top$, $\neg$ $\exists$ authorOf.Self & sub-class & - \\
+$\exists$ authorOf.Self & authorOf & - & Self & existential quantification & - \\
+$\neg$ $\exists$ authorOf.Self & - & - & $\exists$ authorOf.Self & negation & - \\
+$\top$ & - & - & $\top$, $\neg$ $\exists$ authorOf.Self & sub-class & - \\
 		\end{tabular}
@@
 	\centering
-		\begin{tabular}{l|l|l|l|l|l|l}
-      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+		\begin{tabular}{c|c|c|c|c|c}
+      \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
       \hline
-property & $\top$ & authorOf & - & - & irreflexive property & - \\
+$\top$ & authorOf & - & - & irreflexive property & - \\
 		\end{tabular}

### 2015-07-16 paper/paper 2/dc-2015.tex
3.2

@@
 Constraining elements are for example taken from Description Logics, another concrete example would be 'regex' where a regular expression is checked against some property value.
-Sometimes the constraining elements directly correspond to a constraint type, sometime (as for regex) they are shared by several constraint types.
+In most cases, constraining elements directly correspond to a constraint type, sometimes (as for regex) they are shared by several constraint types.
 Complex constraints again need several constraing elements to be expressed.
@@
 For the majority of the constraint types, there is exactly one constraining element.
+Complex constraints need several constraining elements to be expressed.
 For the constraint type \emph{property domain (R-25, R-26)} whose constraints restrict domains of properties, e.g., there is only one constraining element with exactly the same identifier \emph{property domain}.
-For a few constraint types, however, one constraining element is not sufficient to describe all possible constraints of a particular constraint type and therefore multiple constraining elements may be stated.
+For some constraint types, however, one constraining element is not sufficient to describe all possible constraints of a particular constraint type and therefore multiple constraining elements may be stated.
 The constraint type \emph{language tag cardinality (R-48, R-49)}, for instance, is used to restrict data properties to have a minimum, maximum, or exact number of relationships to literals with selected language tags.

### 2015-07-16 paper/paper 2/dc-2015.tex
3.2

@@
 The central property is the \emph{constraining element} which refers to one of 103 contraining elements described in our technical report \cite{BoschNolleAcarEckert2015}.
-Constraining elements are for example taken from Description Logics, another concrete example would be 'regex' where a regular expression is checked against some property value.
-In most cases, constraining elements directly correspond to a constraint type, sometimes (as for regex) they are shared by several constraint types.
+Constraining elements are for example taken from Description Logics, another concrete example would be 'REGEX' where a regular expression is checked against some property value.
+In most cases, constraining elements directly correspond to a constraint type, sometimes (as for REGEX) they are shared by several constraint types.
 Complex constraints again need several constraing elements to be expressed.
@@
 
-Finally, the \emph{constrainig value} contains a literal value to be checked against; for instance in the case of the 'regex' element, it contains the regular expression to be evaluated.
+Finally, the \emph{constrainig value} contains a literal value to be checked against; for instance in the case of the 'REGEX' element, it contains the regular expression to be evaluated.
 
@@
 If constraint types are expressible in DL, associated constraining elements are formally based on DL constructs like concept and role constructors ($\sqsubseteq$, $\equiv$, $\sqcap$, $\sqcup$, $\neg$, $\exists$, $\forall$, $\geq$, $\leq$), equality (=), and inequality ($\ne$).
-In case constraint types cannot be expressed in DL such as \emph{data property facets (R-46)} or \emph{literal pattern matching (R-44)}, we reuse widely known terms from SPARQL (e.g., \emph{regex}) or XML Schema (e.g., \emph{minInclusive}) as constraining elements.
+In case constraint types cannot be expressed in DL such as \emph{data property facets (R-46)} or \emph{literal pattern matching (R-44)}, we reuse widely known terms from SPARQL (e.g., REGEX) or XML Schema constraining facets (e.g., \emph{xsd:minInclusive}) as constraining elements.
 For some constraint types like \emph{minimum qualified cardinality restrictions (R-75)}, it is more intuitive and concise to directly apply DL constructs like the \emph{at-least restriction} ($\geq$) as constraining elements.
-We provide a complete list of all constraining elements which can be used to express constraints of any constraint type \cite{BoschNolleAcarEckert2015}.
-
-In some cases, a constraint is only complete when a \emph{constraining value} is stated in addition to the constraining element
-and simple constraints may refer to a list of \emph{classes}.
-The constraining element of the property constraint {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person},} e.g., is \emph{$\geq$}, the constraining value is \emph{1}, and the list of classes includes the class \emph{Person} which restricts the objects of the property \emph{author} to be persons.
-
-For property constraints, \emph{left} and \emph{right property lists} are specified.
+We provide a complete list of all 103 constraining elements which can be used to express constraints of any constraint type \cite{BoschNolleAcarEckert2015}.
+
+Additional to the constraining element, there are properties of simple constraints which can be seen as parameters for the constraining element.
+In some cases, a simple constraint is only complete when a \emph{constraining value} is stated in conjunction with the constraining element.
+Depending on the constraining element, a list of \emph{classes} can be provided, for example to determine the valid classes for a value.
+The constraining element of the constraint {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person},} e.g., is \emph{$\geq$}, the constraining value is \emph{1}, and the list of classes includes the class \emph{Person} which restricts the objects of the property \emph{author} to be persons.
+
+\emph{Left} and \emph{right property lists} are lists usually containing properties the constraint is applied to.
+A typical example for a constraint with a right hand side list of properties would be a constraint of the type \emph{literal value comparison (R-43)} to express that birth dates must be before death dates ({\small\ms{birthDate $<$ deathDate}}).
 The assignment of properties to these lists happens relative to the constraining element.
-\emph{Object Property Paths} (\emph{R-55})
-ensure that if an individual \emph{x} is connected by a sequence of object properties with an individual \emph{y}, 
+\emph{Object property paths} (\emph{R-55}) ensure that if an individual \emph{x} is connected by a sequence of object properties with an individual \emph{y}, 
 then \emph{x} is also related to \emph{y} by a particular object property. 
@@
 %{\small\ms{(authorOfGenre(Stephen-Hawking, Popular-Science))}.}
-Thus, when representing the property constraint using the RDF-CV (see Table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are placed on the left side of the constraining element \emph{property paths}
+Thus, when representing the constraint using the RDF-CV (see Table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are placed on the left side of the constraining element \emph{property path}
 and the property \emph{authorOfGenre} on its right side.
-As this property constraint holds for all individuals within the data, the context class is set to the \emph{DL top concept} $\top$ which stands for the super-class of all possible classes.
+The \emph{context class} limits the constraint to individuals of a specific class.
+As the \emph{property path} constraint holds for all individuals within the data, the context class is set to the \emph{DL top concept} $\top$ which stands for the super-class of all possible classes.
 \begin{table}[H]
@@
 Thereby, the context class \emph{ISBN}, whose instances must satisfy the simple constraint, is reused within the list of classes the complex constraint refers to.
-The literal pattern matching constraint type introduces the constraining element \emph{regex} whose validation has to be implemented once like for any other constraining element.
+The literal pattern matching constraint type introduces the constraining element \emph{REGEX} whose validation has to be implemented once like for any other constraining element.
 %In general, validation has to be implemented once for each \emph{generic constraint type} which is not expressible in DL. 
@@
 %property & Enterprise & registryNumber & - & RegistryNumber & $\forall$ & - \\
-%class & RegistryNumber & - & - & xsd:string & regex & 'NCC-1701([-][A-E])?' \\
+%class & RegistryNumber & - & - & xsd:string & REGEX & 'NCC-1701([-][A-E])?' \\
 %\end{gcotable}

### 2015-07-16 paper/paper 2/dc-2015.tex
na

--- 2015-07-16 paper/paper 2/dc-2015.tex
@@
 \subsection{\emph{Simple Constraints}}
+In this and the following section, we provide examples for the representation of constraint types within the framework.
 
@@
 which restricts publications to have at least one author which must be a person,
-is an example of a simple constraint on \emph{author}
+is an example of a simple property constraint on \emph{author}
 which holds for all individuals of the class \emph{Publication}.
-Table \ref{tab:property-constraint-cardinality-restriction} displays how the simple constraint is generically represented using the RDF-CV.
-Note that instead of the description logics construct $\geq$, the constraining element \emph{minimum qualified cardinality restriction} may be used.
-
+Table \ref{tab:property-constraint-cardinality-restriction} displays how the property constraint is generically represented using the RDF-CV.
 \begin{table}[H]
@@
 	\centering
-		\begin{tabular}{c|c|c|c|c|c}
-      \textbf{context class} & \textbf{left property list} & \textbf{right p. list} & \textbf{classes} & \textbf{constraining element} & \textbf{c. value} \\
+		\begin{tabular}{c|c|c|c|c|c|c}
+      \textbf{constraint set} & \textbf{context class} & \textbf{left property list} & \textbf{right p. list} & \textbf{classes} & \textbf{constraining element} & \textbf{c. value} \\
       \hline
-      Publication & author & - & Person & $\geq$ & 1 \\
+      property & Publication & author & - & Person & $\geq$ & 1 \\
 		\end{tabular}
@@
 	\centering
-		\begin{tabular}{c|c|c|c|c|c}
-      \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+		\begin{tabular}{l|l|l|l|l|l|l}
+      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
       \hline
-      $\top$ & authorOf, genre & authorOfGenre & $\top$ & property path & - \\
+      property & $\top$ & authorOf, genre & authorOfGenre & $\top$ & property paths & - \\
 		\end{tabular}
@@
 	\centering
-		\begin{tabular}{c|c|c|c|c|c}
-      \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+		\begin{tabular}{l|l|l|l|l|l|l}
+      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
       \hline
-      ISBN & - & - & xsd:string & REGEX & '\string^\text{$\backslash$d$\{9\}$[$\backslash$d$\mid$X]}\$' \\
-      Book & identifier & - & ISBN & universal quantification & - \\
+      class & ISBN & - & - & xsd:string & regex & '\string^\text{$\backslash$d$\{9\}$[$\backslash$d$\mid$X]}\$' \\
+      property & Book & identifier & - & ISBN & universal quantification & - \\
 		\end{tabular}
@@
 	\centering
-		\begin{tabular}{c|c|c|c|c|c}
-      \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+		\begin{tabular}{l|l|l|l|l|l|l}
+      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
       \hline
-Publication & - & - & E, F & exclusive or & - \\
-E & - & - & A, B & intersection & - \\
-F & - & - & C, D & intersection & - \\
-A & isbn & - & string & = & 1 \\
-B & title & - & string & = & 1 \\
-C & issn & - & string & = & 1 \\
-D & title & - & string & = & 1 \\
+class & Publication & - & - & E, F & XOR of property groups & - \\
+class & E & - & - & A, B & intersection & - \\
+class & F & - & - & C, D & intersection & - \\
+property & A & isbn & - & string & = & 1 \\
+property & B & title & - & string & = & 1 \\
+property & C & issn & - & string & = & 1 \\
+property & D & title & - & string & = & 1 \\
 		\end{tabular}
@@
 	\centering
-		\begin{tabular}{c|c|c|c|c|c}
-      \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+		\begin{tabular}{l|l|l|l|l|l|l}
+      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
       \hline
-$\top$ & isbn$^{-}$ & isbn$^{-}$ & - & inverse property & - \\
-Book & isbn$^{-}$ & - & - & functional property & - \\
+property & $\top$ & isbn$^{-}$ & isbn$^{-}$ & - & inverse property & - \\
+property & Book & isbn$^{-}$ & - & - & functional property & - \\
 		\end{tabular}
@@
 \begin{ex}[commandchars=\\\{\}]
-[   a \textit{rdfcv:SimpleConstraint} ;
-    \textit{rdfcv:contextClass} Book ; 
-    \textit{rdfcv:leftProperties} ( isbn ) ; 
-    \textit{rdfcv:constrainingElement} "primary key" ] .
+[   a \textit{rdfcv:PropertyConstraint} , \textit{rdfcv:SimpleConstraint} ;
+    \textit{rdfcv:contextClass} Book ; \textit{rdfcv:leftProperties} ( isbn ) ; \textit{rdfcv:constrainingElement} "keyfor" ] .
 \end{ex}
@@
 	\centering
-		\begin{tabular}{c|c|c|c|c|c}
-      \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+		\begin{tabular}{l|l|l|l|l|l|l}
+      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
       \hline
-$\exists$ authorOf.Self & authorOf & - & Self & existential quantification & - \\
-$\neg$ $\exists$ authorOf.Self & - & - & $\exists$ authorOf.Self & negation & - \\
-$\top$ & - & - & $\top$, $\neg$ $\exists$ authorOf.Self & sub-class & - \\
+property & $\exists$ authorOf.Self & authorOf & - & Self & existential quantification & - \\
+class & $\neg$ $\exists$ authorOf.Self & - & - & $\exists$ authorOf.Self & negation & - \\
+class & $\top$ & - & - & $\top$, $\neg$ $\exists$ authorOf.Self & sub-class & - \\
 		\end{tabular}
@@
 	\centering
-		\begin{tabular}{c|c|c|c|c|c}
-      \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+		\begin{tabular}{l|l|l|l|l|l|l}
+      \textbf{c. type} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
       \hline
-$\top$ & authorOf & - & - & irreflexive property & - \\
+property & $\top$ & authorOf & - & - & irreflexive property & - \\
 		\end{tabular}
@@
 
-\subsection{Bidirectional Constraint Transformations}
+\subsection{Mapping implementation}
 
@@
 
-\subsection{XXX}
-
-\begin{ex}
-owl:Thing 
-    spin:rule [ a sp:Construct ; sp:text """
-        CONSTRUCT {            
-            ?cc
-                a owl:Restriction ;
-                owl:minQualifiedCardinality ?cv ;
-                owl:onProperty ?lp1 ;
-                owl:onClass ?c1 . }
-        WHERE { 
-            ?this
-                a rdfcv:SimpleConstraint ;
-                rdfcv:contextClass ?cc ;
-                rdfcv:leftProperties ?leftProperties ;
-                rdfcv:classes ?classes ;
-                rdfcv:constrainingElement "minimum qualified cardinality restriction" ;
-                rdfcv:constrainingValue ?cv .  
-            ?leftProperties 
-                rdf:first ?lp1 ;
-                rdf:rest rdf:nil .    
-            ?classes 
-                rdf:first ?c1 ;
-                rdf:rest rdf:nil . } """ ; ] .
-\end{ex}
-
 \section{Related Work}

### 2015-07-16 paper/paper 2/dc-2015.tex
3.2

--- 2015-07-16 paper/paper 2/dc-2015.tex
@@
 
-There are simple constraints which are not expressible in DL but can still be described using the RDF-CV such as constraints of the type \emph{literal pattern matching} (\emph{R-44}) which restrict literals to match given patterns.
+Constraints of 36\% of the constraint types are not expressible in DL but can still be described using the RDF-CV such as constraints of the type \emph{literal pattern matching} (\emph{R-44}) which restrict literals to match given patterns.
 The \emph{universal quantification (R-91)} {\small\ms{Book $\sqsubseteq$ $\forall$ identifier.ISBN}} ensures that books can only have valid \emph{ISBN} identifiers, i.e., strings that match a given regular expression.
@@
 
-Even though, constraints of the type \emph{literal pattern matching} cannot be expressed in DL, OWL 2 can be used to formulate the constraint:
+Even though, constraints of the type \emph{literal pattern matching} cannot be expressed in DL, OWL 2 can be used to formulate this constraint:
 
@@
 
-Table \ref{tab:simple-constraint-not-expressible-in-dl)} presents (1) in the first line how the literal pattern matching simple constraint which is not expressible in DL and (2) in the second line how the universal quantification complex constraint which is expressible in DL are represented using the RDF-CV.
-Thereby, the context class \emph{ISBN}, whose instances must satisfy the simple constraint, is reused within the list of classes the complex constraint refers to.
+Table \ref{tab:simple-constraint-not-expressible-in-dl)} presents (1) how the not in DL expressible literal pattern matching constraint and (2) how the in DL expressible universal quantification are both represented using the RDF-CV.
+Thereby, the context class \emph{ISBN}, whose instances must satisfy the literal pattern matching constraint, is reused within the list of classes the universal quantification refers to.
 The literal pattern matching constraint type introduces the constraining element \emph{REGEX} whose validation has to be implemented once like for any other constraining element.

### 2015-07-16 paper/paper 2/dc-2015.tex
3.3

@@
 %\emph{Complex constraints} are composed out of \emph{simple constraints} and/or \emph{complex constraints}.
-Complex constraints of the constraint type \emph{context-specific exclusive or of property groups} (\emph{R-13}) restrict individuals of given classes to have all properties of exactly one of multiple mutually exclusive property groups.
-Publications, e.g., are either identified by an \emph{ISBN} and a title (for books) or by an \emph{ISSN} and a title (for periodical publications), but it should not be possible to assign both identifiers to a given publication.
-This complex constraint is expressible in \emph{ShEx}:
+Complex constraints of the constraint type \emph{context-specific exclusive or of property groups (R-13)} restrict individuals of given classes to have all properties of exactly one of multiple mutually exclusive property groups.
+Publications, e.g., are either identified by an ISBN and a title (for books) or by an ISSN and a title (for periodical publications), but it should not be possible to assign both identifiers to a given publication.
+This complex constraint is expressible in ShEx:
 
@@
 
-As \emph{The-Great-Gatsby} is a publication with an \emph{ISBN} and a title without an \emph{ISSN}, \emph{The-Great-Gatsby} is considered as a valid publication.
+If \emph{The-Great-Gatsby} is a publication with an ISBN and a title without an ISSN, \emph{The-Great-Gatsby} is considered as a valid publication.
 This complex constraint is generically expressible in DL:
@@
 Constraints of almost 14\% of the constraint types are complex constraints which can be simplified and therefore formulated as simple constraints when using them in terms of syntactic sugar.
-As \emph{exact (un)qualified cardinality restrictions (=n)} and \emph{exclusive or (XOR) of property groups} are frequently used complex constraints, we propose to simplify them in form of simple constraints.
-As a consequence, the \emph{context-specific exclusive or of property groups (R-13)} complex constraint is represented as a generic constraint by means of the RDF-CV more intuitively and concisely (see Table \ref{tab:simplified-complex-constraints}).
+As \emph{exact (un)qualified cardinality restrictions (R-74/80) (=n)} and \emph{exclusive or of property groups (R-13)} are constraint types of frequently used complex constraints, we propose to simplify them in form of simple constraints.
+As a consequence, the \emph{context-specific exclusive or of property groups} complex constraint is represented as a generic constraint by means of the RDF-CV more intuitively and concisely (see Table \ref{tab:simplified-complex-constraints}).
 

### 2015-07-16 paper/paper 2/dc-2015.tex
3.4 3.5

--- 2015-07-16 paper/paper 2/dc-2015.tex
@@
 \section{Motivation}
-
+\label{sec:motivation}
 Even with an upcoming W3C recommendation, it can be expected that several constraint languages will be used in practice in future -- consider the situation in the XML world, where a standardized schema language was available from the beginning and yet additional ways to formulate and check constraints have been created.
@@
 
-Constraints of 36\% of the constraint types are not expressible in DL but can still be described using the RDF-CV such as constraints of the type \emph{literal pattern matching} (\emph{R-44}) which restrict literals to match given patterns.
+There are simple constraints which are not expressible in DL but can still be described using the RDF-CV such as constraints of the type \emph{literal pattern matching} (\emph{R-44}) which restrict literals to match given patterns.
 The \emph{universal quantification (R-91)} {\small\ms{Book $\sqsubseteq$ $\forall$ identifier.ISBN}} ensures that books can only have valid \emph{ISBN} identifiers, i.e., strings that match a given regular expression.
@@
 
-Even though, constraints of the type \emph{literal pattern matching} cannot be expressed in DL, OWL 2 can be used to formulate this constraint:
+Even though, constraints of the type \emph{literal pattern matching} cannot be expressed in DL, OWL 2 can be used to formulate the constraint:
 
@@
 
-Table \ref{tab:simple-constraint-not-expressible-in-dl)} presents (1) how the not in DL expressible literal pattern matching constraint and (2) how the in DL expressible universal quantification are both represented using the RDF-CV.
-Thereby, the context class \emph{ISBN}, whose instances must satisfy the literal pattern matching constraint, is reused within the list of classes the universal quantification refers to.
+Table \ref{tab:simple-constraint-not-expressible-in-dl)} presents (1) in the first line how the literal pattern matching simple constraint which is not expressible in DL and (2) in the second line how the universal quantification complex constraint which is expressible in DL are represented using the RDF-CV.
+Thereby, the context class \emph{ISBN}, whose instances must satisfy the simple constraint, is reused within the list of classes the complex constraint refers to.
 The literal pattern matching constraint type introduces the constraining element \emph{REGEX} whose validation has to be implemented once like for any other constraining element.
@@
 
-\subsection{Bidirectional Constraint Transformations}
-
-Constraint of the type \emph{minimum qualified cardinality restriction (R-75)} expressed in OWL 2:
+\subsection{Mapping implementation}
+
+If a language developer would like to use the framework for the implementation of a constraint language, the process is straight-forward.
+For a language construct, the corresponding constraint type has to be identified.
+Again we use the \emph{minimum qualified cardinality restriction (R-75)} type which is supported in OWL 2:
 
@@
 
-The same constraint expressed generically using the RDF-CV:
+From Table~\ref{tab:property-constraint-cardinality-restriction}, we know the representation in our framework, which corresponds to the following 
+RDF representation using RDF-CV:
 
@@
 
-SPIN inference rule to infer the generic constraint out of the constraint expressed by OWL 2:
+The mapping simply constructs this representation out of the OWL2 representation using a SPARQL CONSTRUCT query:
 
@@
 
-The property \emph{spin:rule} can be used to link an rdfs:Class with SPARQL CONSTRUCT queries.
+SPIN is used to execute the mapping, the property \emph{spin:rule} links an rdfs:Class with SPARQL CONSTRUCT queries.
 Each query defines an inference rule that is applied to all instances of the associated class and its subclasses.
@@
 
-SPIN inference rule to infer the OWL 2 constraint out of the generically expressed constraint:
-
-\subsection{XXX}
+The framework is implemented in exactly the same way by providing another mapping to create the actual SPIN/SPARQL query that validates the constraints and produces constraint violation messages if a constraint is violated, as described in our previous paper about the DSP implementation \cite{BoschEckert2014-2}.\footnote{At the time of this writing, not all mappings for the constraint types are implemented, but of course the implementations can be complemented and adapted to own requirements, as needed.
+The most recent implementation can be found here: \url{https://github.com/boschthomas/rdf-validation/blob/master/SPIN/RDF-CV-2-SPIN.ttl}.}
+
+\subsection{Constraint transformation}
+
+As stated in Section~\ref{sec:motivation}, we see a huge potential in the possibility to transform semantically equivalent constraints from one high level constraint language to another via the RDF-CV representation, to avoid that every possible combination of constraint languages has to be mapped separately.
+The following SPIN inference rule exemplifies this approach and provides a mapping from RDF-CV back to an OWL2 constraint:
 
@@
 
+It can be seen that the mapping is quite similar to the first mapping and basically simply switches the CONSTRUCT and WHERE part of the query, with slight adjustment in the structure of the variables.
+Potentially an even simpler representation for the mapping could be found that would enable the creation of forward and backward mappings out of it.
+We didn't investigate this further, though, and it is not yet clear if there can be cases where the backward mapping is more different.
+
 \section{Related Work}
@@
 
-The \emph{Dublin Core Application Profile (DCAP)} and \emph{Bibframe} are approaches to specify \emph{profiles} for application-specific purposes.
+The \emph{Dublin Core Application Profile (DCAP)} and \emph{Bibframe Profiles} are approaches to specify \emph{profiles} for application-specific purposes.
 The term \emph{profile} is widely used to refer to a document that describes how standards or specifications are deployed to support the requirements of a particular application, function, community, or context.

### 2015-07-16 paper/paper 2/dc-2015.tex
3.3

--- 2015-07-16 paper/paper 2/dc-2015.tex
@@
 The \emph{primary key properties (R-226)} constraint type is often useful to declare a given (datatype) property as the primary key of a class, so that a system can enforce uniqueness. 
-Books, e.g., are uniquely identified by their \emph{ISBN}, i.e., the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}
+Books, e.g., are uniquely identified by their ISBN, i.e., the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}
 which can be represented using the RDF-CV in form of a complex constraint consisting of two simple constraints (see Table \ref{tab:primary-key-properties-as-complex-constraints}).
@@
 With the irreflexive object property constraint {\small\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists authorOf.Self$}}, e.g., one can state that individuals cannot be authors of themselves.
-When represented using the RDF-CV, the complex constraint aggregates three simple constraints - one property and two class constraints (see Table \ref{tab:irreflexive-object-properties-as-complex-constraints}).
+When represented using the RDF-CV, the complex constraint aggregates three simple constraints (see Table \ref{tab:irreflexive-object-properties-as-complex-constraints}).
 
@@
 
-When using the irreflexive object property constraint in terms of syntactic sugar, 
+When using the \emph{irreflexive object property} constraint in terms of syntactic sugar, 
 the complex constraint can be expressed more concisely in form of a simple property constraint with exactly the same semantics (see Table \ref{tab:irreflexive-object-properties-as-simple-constraints}):

### 2015-07-16 paper/paper 2/dc-2015.tex
minor

@@
 \begin{ex}[commandchars=\\\{\}]
-Publication 
+:Publication 
     a owl:Restriction ;
     owl:minQualifiedCardinality 1 ;
-    owl:onProperty author ;
-    owl:onClass Person .
+    owl:onProperty :author ;
+    owl:onClass :Person .
 \end{ex}
@@
 For each binding of the pattern in the WHERE clause of the rule, the triple templates from the CONSTRUCT clause are instantiated and added as inferred triples to the underlying model.
-At query execution time, the SPARQL variable ?this is bound to the current instance of the class.
-As each resource per default is assigned to the class owl:Thing, this inference rule is evaluated for each subject of the input RDF graph.
+At query execution time, the SPARQL variable \emph{?this} is bound to the current instance of the class.
+As each resource per default is assigned to the class \emph{owl:Thing}, this inference rule is evaluated for each subject of the input RDF graph.
 
@@
 
-As stated in Section~\ref{sec:motivation}, we see a huge potential in the possibility to transform semantically equivalent constraints from one high level constraint language to another via the RDF-CV representation, to avoid that every possible combination of constraint languages has to be mapped separately.
+As stated in Section~\ref{sec:motivation}, we see a huge potential in the possibility to transform semantically equivalent constraints from one high-level constraint language to another via the RDF-CV representation, to avoid that every possible combination of constraint languages has to be mapped separately.
 The following SPIN inference rule exemplifies this approach and provides a mapping from RDF-CV back to an OWL2 constraint:

### 2015-07-16 paper/paper 2/dc-2015.tex
minor

@@
  \item How can we ensure that two semantically equivalent constraints are actually validated consistently?
- \item How can we support the transformation of semantically equivalent constraints from one contraint language to another?
+ \item How can we support the transformation of semantically equivalent constraints from one constraint language to another?
 \end{enumerate}
@@
 \paragraph{Consistent implementation.}
-Even though SPIN provides a convenient way to represent constraints and to validate data according to these constraints, the implementation of a high-level constraint language still requires a tedious mapping to SPIN with a certain degree of freedom as to how a constraint violation is actually represented and how exactly the violation of the contraint is checked.
-Our framework therefore proides a common ground that is solely based on the abstract definitions of the constraint types, as identified in our database. By providing a \emph{SPIN} mapping
+Even though SPIN provides a convenient way to represent constraints and to validate data according to these constraints, the implementation of a high-level constraint language still requires a tedious mapping to SPIN with a certain degree of freedom as to how a constraint violation is actually represented and how exactly the violation of the constraint is checked.
+Our framework therefore provides a common ground that is solely based on the abstract definitions of the constraint types, as identified in our database. By providing a SPIN mapping
 for each constraint type\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}\label{RDF-CV-2-SPIN}}, it is ensured that the details of the SPIN implementation are consistent irrespective of the constraint language and that the validation leads always to exactly the same results.
@@
 The properties describing a simple constrained are very structural.
-The central property is the \emph{constraining element} which refers to one of 103 contraining elements described in our technical report \cite{BoschNolleAcarEckert2015}.
+The central property is the \emph{constraining element} which refers to one of 103 constraining elements described in our technical report \cite{BoschNolleAcarEckert2015}.
 Constraining elements are for example taken from Description Logics, another concrete example would be 'REGEX' where a regular expression is checked against some property value.
 In most cases, constraining elements directly correspond to a constraint type, sometimes (as for REGEX) they are shared by several constraint types.
-Complex constraints again need several constraing elements to be expressed.
-
-Irrespective of and additonal to the constraining element, there are properties to describe the actual constraint, they can also be seen as parameters for the constraining element.
+Complex constraints again need several constraining elements to be expressed.
+
+Irrespective of and additional to the constraining element, there are properties to describe the actual constraint, they can also be seen as parameters for the constraining element.
 The \emph{context class} limits the constraint to individuals of a specific class.
@@
 \emph{leftProperties} and \emph{rightProperties} are lists usually containing properties the constraint is applied to.
-A typical example for a constraint with a right hand side list of properties would be R43, literal value comparision, where constraints like birthDate $<$ deathDate can be expressed.
-
-Finally, the \emph{constrainig value} contains a literal value to be checked against; for instance in the case of the 'REGEX' element, it contains the regular expression to be evaluated.
+A typical example for a constraint with a right hand side list of properties would be R43, literal value comparison, where constraints like birthDate $<$ deathDate can be expressed.
+
+Finally, the \emph{constraining value} contains a literal value to be checked against; for instance in the case of the 'REGEX' element, it contains the regular expression to be evaluated.
 

### 2015-07-16 paper/paper 2/dc-2015.tex
minor

@@
 The proper validation of RDF data according to constraints is a common requirement of data practitioners. 
-Among the reasons for the success of XML is the possibility to formulate fine-grained constraints to be met by the data and to validate the data according to these constraints using powerful systems like \emph{DTD}, \emph{XML Schema}, \emph{RELAX NG}, or \emph{Schematron}.
+Among the reasons for the success of XML is the possibility to formulate fine-grained constraints to be met by the data and to validate the data according to these constraints using powerful systems like DTD, XML Schema, RELAX NG, or Schematron.
 
@@
 
-\begin{table}
+\begin{table}[H]
 	\centering

### 2015-07-16 paper/paper 2/dc-2015.tex
minor

@@
 
-In 2013, the \emph{W3C} organized the \emph{RDF Validation Workshop}\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}
+In 2013, the W3C organized the \emph{RDF Validation Workshop}\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}
 where experts from industry, government, and academia discussed first RDF validation use cases. 
@@
 the \emph{W3C RDF Data Shapes Working Group}\footnote{\url{http://www.w3.org/2014/rds/charter}} and the \emph{DCMI RDF Application Profiles Task Group}\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
-We collected the findings of these working groups and initiated a database of RDF validation requirements\footnote{Online available at \url{http://purl.org/net/rdf-validation}}
+We collected the findings of these working groups and initiated a database of RDF validation requirements\footnote{Online available at: \url{http://purl.org/net/rdf-validation}}
 with the intention to collaboratively collect case studies, use cases, requirements, and solutions in a comprehensive and structured way \cite{BoschEckert2014}. 
-Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group,
+Based on our work in the DCMI and in cooperation with the W3C working group,
 we identified by today 81 constraint types, where each type corresponds to a specific requirement in the database.
@@
 For our work, we focus on the following four as the ones that are most popular among data practitioners, often mentioned on mailing lists and/or being candidates or prototypes for the upcoming W3C recommendation:
-\emph{Description Set Profiles (DSP)}, \emph{Resource Shapes (ReSh)}, \emph{Shape Expressions (ShEx)}, and the \emph{Web Ontology Language} \emph{(OWL)}.
+\emph{Description Set Profiles (DSP)}, \emph{Resource Shapes (ReSh)}, \emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}}, and the \emph{Web Ontology Language} \emph{(OWL)}.
 Despite the fact that OWL is arguably not a constraint language, it is widely used in practice as such under the closed-world and unique name assumptions.
 
-With its direct support of validation via \emph{SPARQL}, the \emph{SPARQL Inferencing Notation (SPIN)} is also very popular to formulate and check constraints \cite{Fuerber2010}.
+With its direct support of validation via SPARQL, the \emph{SPARQL Inferencing Notation (SPIN)}\footnote{\url{http://spinrdf.org/}} is also very popular to formulate and check constraints \cite{Fuerber2010}.
 We consider SPIN as a low-level language in contrast to the other constraint languages where specific language constructs exist to define constraints in a declarative and in comparison more intuitive way -- although SPARQL aficionados might object particularly to the latter point.
@@
 This is not surprising if we consider that OWL is based on Description Logics.
-When we talk about using Description Logics to represent constraints, we have to establish once more that the semantics of OWL and Description Logics differ from the semantics of constraint languages regarding the open world assumption (OWA) and the non-unique naming assumption (nUNA).
+When we talk about using Description Logics to represent constraints, we have to establish once more that the semantics of OWL and Description Logics differ from the semantics of constraint languages regarding the open world assumption (OWA) and the non-unique name assumption (nUNA).
 Both are usually assumed when dealing with OWL or DL, whereas validation usually assumes a closed world (CWA) and unique naming (UNA), i.e., if a desired property is missing, this leads to a violation and if two resources are named differently, they are assumed to be different resources.
@@
 Complex constraints of frequently used constraint types which correspond to DL axioms like \emph{transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity} can also be simplified in form of simple constraints.
-Although, these DL axioms are expressible by basic DL features, they can also be used in terms of syntactic sugar \cite{BoschEckert2015-2}.
+Although, these DL axioms are expressible by basic DL features, they can also be used in terms of syntactic sugar.
 
@@
 
-\emph{Shape Expressions (ShEx)} \cite{W3C-ShEx-Primer-2014,W3C-ShEx-Definition-2014,Prud'hommeaux-2014,Boneva-2014} specifies a language whose syntax and semantics are similar to regular expressions.
+\emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}} \cite{W3C-ShEx-Primer-2014,W3C-ShEx-Definition-2014,Prud'hommeaux-2014,Boneva-2014} specifies a language whose syntax and semantics are similar to regular expressions.
 ShEx associate RDF graphs with labeled patterns called \emph{shapes} which are used to express formal constraints on the content of RDF graphs.
@@
 for each constraint type\footref{RDF-CV-2-SPIN}  
-whose constraints are represented generically \cite{BoschEckert2015-2}. 
+whose constraints are represented generically. 
 Furthermore, our proposal makes sure that the validation on semantically equivalent \emph{specific constraints} expressed by different languages

### 2015-07-16 paper/paper 2/dc-2015.tex
conclusion

--- 2015-07-16 paper/paper 2/dc-2015.tex
@@
  \item How can we ensure that two semantically equivalent constraints are actually validated consistently?
- \item How can we support the transformation of semantically equivalent constraints from one constraint language to another?
+ \item How can we support the transformation of semantically equivalent constraints from one contraint language to another?
 \end{enumerate}
@@
 \paragraph{Consistent implementation.}
-Even though SPIN provides a convenient way to represent constraints and to validate data according to these constraints, the implementation of a high-level constraint language still requires a tedious mapping to SPIN with a certain degree of freedom as to how a constraint violation is actually represented and how exactly the violation of the constraint is checked.
-Our framework therefore provides a common ground that is solely based on the abstract definitions of the constraint types, as identified in our database. By providing a SPIN mapping
+Even though SPIN provides a convenient way to represent constraints and to validate data according to these constraints, the implementation of a high-level constraint language still requires a tedious mapping to SPIN with a certain degree of freedom as to how a constraint violation is actually represented and how exactly the violation of the contraint is checked.
+Our framework therefore proides a common ground that is solely based on the abstract definitions of the constraint types, as identified in our database. By providing a \emph{SPIN} mapping
 for each constraint type\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}\label{RDF-CV-2-SPIN}}, it is ensured that the details of the SPIN implementation are consistent irrespective of the constraint language and that the validation leads always to exactly the same results.
@@
 The properties describing a simple constrained are very structural.
-The central property is the \emph{constraining element} which refers to one of 103 constraining elements described in our technical report \cite{BoschNolleAcarEckert2015}.
+The central property is the \emph{constraining element} which refers to one of 103 contraining elements described in our technical report \cite{BoschNolleAcarEckert2015}.
 Constraining elements are for example taken from Description Logics, another concrete example would be 'REGEX' where a regular expression is checked against some property value.
 In most cases, constraining elements directly correspond to a constraint type, sometimes (as for REGEX) they are shared by several constraint types.
-Complex constraints again need several constraining elements to be expressed.
-
-Irrespective of and additional to the constraining element, there are properties to describe the actual constraint, they can also be seen as parameters for the constraining element.
+Complex constraints again need several constraing elements to be expressed.
+
+Irrespective of and additonal to the constraining element, there are properties to describe the actual constraint, they can also be seen as parameters for the constraining element.
 The \emph{context class} limits the constraint to individuals of a specific class.
@@
 \emph{leftProperties} and \emph{rightProperties} are lists usually containing properties the constraint is applied to.
-A typical example for a constraint with a right hand side list of properties would be R43, literal value comparison, where constraints like birthDate $<$ deathDate can be expressed.
-
-Finally, the \emph{constraining value} contains a literal value to be checked against; for instance in the case of the 'REGEX' element, it contains the regular expression to be evaluated.
+A typical example for a constraint with a right hand side list of properties would be R43, literal value comparision, where constraints like birthDate $<$ deathDate can be expressed.
+
+Finally, the \emph{constrainig value} contains a literal value to be checked against; for instance in the case of the 'REGEX' element, it contains the regular expression to be evaluated.
 
@@
 
-%Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group, 
-%we published by today 81 constraint types \cite{BoschNolleAcarEckert2015}
-%which form the basis to
-%lay the ground for discussions on validation
-%by defining a basic terminology and classification system for RDF constraints.
-
-Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group,
-we published by today 81 requirements to validate RDF data and to formulate constraints; 
-each of them corresponds to a constraint type from which concrete constraints are instantiated to be checked on RDF data.
-These constraint types form the basis to
-lay the ground for discussions on validation
-by defining a basic terminology and classification system for RDF constraints.
-%
-There exists no single best solution considered as high-level intuitive constraint language which enables to express constraints in an easy and concise way and which is able to meet all requirements raised by data practitioners.
-Thus, the idea behind this paper is to satisfy all requirements
-by representing constraints of any constraint type in a generic way using a lightweight vocabulary which consists of only a few terms.
-%To show that constraints can either be represented specifically (\emph{specific constraints}) by constraint languages
-%or generically (\emph{generic constraints}) by \emph{description logics (DL)},
-%we mapped constraint types to DL 
-%to determine which DL constructs are needed to express them \cite{BoschNolleAcarEckert2015} (Section \ref{sec:vocabulary}).
-
-As there is no standard way to formulate constraints, 
-semantically equivalent \emph{specific constraints} may be represented by a variety of languages - each of them having different syntax and semantics.
-We propose transformations between semantically equivalent \emph{specific constraints}
-by using the proposed vocabulary to intermediately represent constraints in a generic way
-(1) to avoid the necessity to understand several languages,
-(2) to resolve misunderstandings about the meaning of particular constraints, and
-(3) to enhance the interoperability of constraint languages (Section \ref{sec:transformations}).
-
-We use \emph{SPIN} as basis to develop a validation environment\footref{rdf-validator} to validate RDF data according to constraints of constraint types which are expressible by arbitrary constraint languages by mapping them to \emph{SPIN}\footref{spin-mappings} \cite{BoschEckert2014-2}.
-When language designers extend constraint languages 
-to be able to formulate constraints of not yet supported constraint types,
-our proposal enables to reuse the validation implementation of these constraint types 
-by mapping \emph{specific constraints} expressed by the language to the corresponding \emph{generic constraint}.
-For any constraint language, we enable to offer a validation implementation of any constraint type out-of-the-box
-by providing a \emph{SPIN} mapping
-for each constraint type\footref{RDF-CV-2-SPIN}  
-whose constraints are represented generically \cite{BoschEckert2015-2}. 
-Furthermore, our proposal makes sure that the validation on semantically equivalent \emph{specific constraints} expressed by different languages
-leads to exactly the same validation results, 
-i.e., that validation is performed independently from the used language (Section \ref{sec:validation}).
-
-It is part of future work 
-(1) to extend the \emph{RDF Validator} by generating \emph{generic constraints} according to inputs of domain experts who may not be familiar with the formulation of constraints,
-(2) to offer bidirectional transformations between \emph{specific constraints} expressed by the most common constraint languages and corresponding \emph{generic constraints}, and
-(3) to provide translations between semantically equivalent \emph{specific constraints} expressed by the most common constraint languages by using the developed vocabulary to intermediately represent constraints.
-Identifying RDF validation requirements is an ongoing process,
-so the task to map constraints of new constraint types to the vocabulary.
-
-%\begin{itemize}
-	%\item to provide a GUI which generates generic constraints automatically according to inputs of domain experts who are not familiar with the formulation of constraints.
-	%\item to offer bidirectional transformations between specific constraints (expressed by multiple constraint languages) and generic constraints. 
-	%\item to provide translations between specific constraints (expressed by any specific constraint language) by using generic constraints as an intermediate transformation step.
-%\end{itemize}
+In this paper, we outlined our idea of a general framework to support the mapping of high-level constraint languages to a generic representation, which subsequently can be used to generate validating SPIN/SPARQL queries to actually validate data against constraints provided in the high-level language.
+The framework consists of a very simple conceptual model using the RDF Constraints Vocabulary (RDF-CV) which has been introduced in this paper.
+The core of the framework is the definition of 103 constraining elements that are used to define all 81 types of constraints that to date have been identified within the \emph{DCMI RDF Application Profiles Task Group} and in cooperation with the \emph{W3C Data Shapes Working Group}.
+The full definition of all constraint types and the representation of the types in RDF-CV is provided in an accompanying technical report \cite{BoschNolleAcarEckert2015}.
+
+We have demonstrated how the framework can be used to map a constraint language to RDF-CV and also how to map back from RDF-CV to the constraint language.
+The latter enables the transformation of sematically equivalent constraints from one constraint language to another via the RDF-CV intermediate representation.
+
+We think that this approach is suitable
+\begin{enumerate}
+  \item to implement the validation of constraints consistently across constraint languages,
+  \item to support the extension of constraint languages by means of a simple mapping, and
+  \item to enhance or rather establish the interoperability of different constraint languages.
+\end{enumerate}
+
+It is part of future work to finalize the implementation of all 81 constraint types in our \emph{RDF Validator}, to fully map constraint languages to RDF-CV (first and foremost DSP and OWL) and of course keep the framework in sync with the ongoing work in the working groups.
 

### 2015-07-16 paper/paper 2/dc-2015.tex

--- 2015-07-16 paper/paper 2/dc-2015.tex
@@
 
-%Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group, 
-%we published by today 81 constraint types \cite{BoschNolleAcarEckert2015}
-%which form the basis to
-%lay the ground for discussions on validation
-%by defining a basic terminology and classification system for RDF constraints.
-
-Based on our work in the \emph{DCMI} and in cooperation with the \emph{W3C} working group,
-we published by today 81 requirements to validate RDF data and to formulate constraints; 
-each of them corresponds to a constraint type from which concrete constraints are instantiated to be checked on RDF data.
-These constraint types form the basis to
-lay the ground for discussions on validation
-by defining a basic terminology and classification system for RDF constraints.
-%
-There exists no single best solution considered as high-level intuitive constraint language which enables to express constraints in an easy and concise way and which is able to meet all requirements raised by data practitioners.
-Thus, the idea behind this paper is to satisfy all requirements
-by representing constraints of any constraint type in a generic way using a lightweight vocabulary which consists of only a few terms.
-%To show that constraints can either be represented specifically (\emph{specific constraints}) by constraint languages
-%or generically (\emph{generic constraints}) by \emph{description logics (DL)},
-%we mapped constraint types to DL 
-%to determine which DL constructs are needed to express them \cite{BoschNolleAcarEckert2015} (Section \ref{sec:vocabulary}).
-
-As there is no standard way to formulate constraints, 
-semantically equivalent \emph{specific constraints} may be represented by a variety of languages - each of them having different syntax and semantics.
-We propose transformations between semantically equivalent \emph{specific constraints}
-by using the proposed vocabulary to intermediately represent constraints in a generic way
-(1) to avoid the necessity to understand several languages,
-(2) to resolve misunderstandings about the meaning of particular constraints, and
-(3) to enhance the interoperability of constraint languages (Section \ref{sec:transformations}).
-
-We use \emph{SPIN} as basis to develop a validation environment\footref{rdf-validator} to validate RDF data according to constraints of constraint types which are expressible by arbitrary constraint languages by mapping them to \emph{SPIN}\footref{spin-mappings} \cite{BoschEckert2014-2}.
-When language designers extend constraint languages 
-to be able to formulate constraints of not yet supported constraint types,
-our proposal enables to reuse the validation implementation of these constraint types 
-by mapping \emph{specific constraints} expressed by the language to the corresponding \emph{generic constraint}.
-For any constraint language, we enable to offer a validation implementation of any constraint type out-of-the-box
-by providing a \emph{SPIN} mapping
-for each constraint type\footref{RDF-CV-2-SPIN}  
-whose constraints are represented generically. 
-Furthermore, our proposal makes sure that the validation on semantically equivalent \emph{specific constraints} expressed by different languages
-leads to exactly the same validation results, 
-i.e., that validation is performed independently from the used language (Section \ref{sec:validation}).
-
-It is part of future work 
-(1) to extend the \emph{RDF Validator} by generating \emph{generic constraints} according to inputs of domain experts who may not be familiar with the formulation of constraints,
-(2) to offer bidirectional transformations between \emph{specific constraints} expressed by the most common constraint languages and corresponding \emph{generic constraints}, and
-(3) to provide translations between semantically equivalent \emph{specific constraints} expressed by the most common constraint languages by using the developed vocabulary to intermediately represent constraints.
-Identifying RDF validation requirements is an ongoing process,
-so the task to map constraints of new constraint types to the vocabulary.
-
-%\begin{itemize}
-	%\item to provide a GUI which generates generic constraints automatically according to inputs of domain experts who are not familiar with the formulation of constraints.
-	%\item to offer bidirectional transformations between specific constraints (expressed by multiple constraint languages) and generic constraints. 
-	%\item to provide translations between specific constraints (expressed by any specific constraint language) by using generic constraints as an intermediate transformation step.
-%\end{itemize}
+In this paper, we outlined our idea of a general framework to support the mapping of high-level constraint languages to a generic representation, which subsequently can be used to generate validating SPIN/SPARQL queries to actually validate data against constraints provided in the high-level language.
+The framework consists of a very simple conceptual model using the RDF Constraints Vocabulary (RDF-CV) which has been introduced in this paper.
+The core of the framework is the definition of 103 constraining elements that are used to define all 81 types of constraints that to date have been identified within the \emph{DCMI RDF Application Profiles Task Group} and in cooperation with the \emph{W3C Data Shapes Working Group}.
+The full definition of all constraint types and the representation of the types in RDF-CV is provided in an accompanying technical report \cite{BoschNolleAcarEckert2015}.
+
+We have demonstrated how the framework can be used to map a constraint language to RDF-CV and also how to map back from RDF-CV to the constraint language.
+The latter enables the transformation of sematically equivalent constraints from one constraint language to another via the RDF-CV intermediate representation.
+
+We think that this approach is suitable
+\begin{enumerate}
+  \item to implement the validation of constraints consistently across constraint languages,
+  \item to support the extension of constraint languages by means of a simple mapping, and
+  \item to enhance or rather establish the interoperability of different constraint languages.
+\end{enumerate}
+
+It is part of future work to finalize the implementation of all 81 constraint types in our \emph{RDF Validator}, to fully map constraint languages to RDF-CV (first and foremost DSP and OWL) and of course keep the framework in sync with the ongoing work in the working groups.
 

### 2015-07-16 paper/paper 2/dc-2015.tex
minor

--- 2015-07-16 paper/paper 2/dc-2015.tex
@@
 For our work, we focus on the following four as the ones that are most popular among data practitioners, often mentioned on mailing lists and/or being candidates or prototypes for the upcoming W3C recommendation:
-\emph{Description Set Profiles (DSP)}, \emph{Resource Shapes (ReSh)}, \emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}}, and the \emph{Web Ontology Language} \emph{(OWL)}.
+\emph{Description Set Profiles (DSP)}\footnote{\url{ http://dublincore.org/documents/2008/03/31/dc-dsp/}}, \emph{Resource Shapes (ReSh)}, \emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}}, and the \emph{Web Ontology Language} \emph{(OWL)}.
 Despite the fact that OWL is arguably not a constraint language, it is widely used in practice as such under the closed-world and unique name assumptions.
@@
 \cite{DCMI-DC-RDF-2008} depict how the constructs of the DCMI Abstract Model are represented using the abstract syntax of the RDF model.
-A \emph{Description Set Profile (DSP)} \cite{DCMI-DSP-2008} is a generic constraint language which is used to formally specify structural constraints on sets of resource descriptions within an application profile.
+A \emph{Description Set Profile (DSP)}\footnote{\url{ http://dublincore.org/documents/2008/03/31/dc-dsp/}} \cite{DCMI-DSP-2008} is a generic constraint language which is used to formally specify structural constraints on sets of resource descriptions within an application profile.
 DSP constrains resources that may be described by descriptions in a description set, the properties that may be used, and the values properties may point to.

### 2015-07-16 paper/paper 2/dc-2015.tex
minor

@@
 For our work, we focus on the following four as the ones that are most popular among data practitioners, often mentioned on mailing lists and/or being candidates or prototypes for the upcoming W3C recommendation:
-\emph{Description Set Profiles (DSP)}\footnote{\url{ http://dublincore.org/documents/2008/03/31/dc-dsp/}}, \emph{Resource Shapes (ReSh)}, \emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}}, and the \emph{Web Ontology Language} \emph{(OWL)}.
+\emph{Description Set Profiles (DSP)}\footnote{\url{ http://dublincore.org/documents/2008/03/31/dc-dsp/}}, \emph{Resource Shapes (ReSh)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shapes-20140211/}}, \emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}}, and the \emph{Web Ontology Language} \emph{(OWL)}.
 Despite the fact that OWL is arguably not a constraint language, it is widely used in practice as such under the closed-world and unique name assumptions.

### 2015-07-16 paper/paper 2/dc-2015.tex
minor

--- 2015-07-16 paper/paper 2/dc-2015.tex
@@
 For our work, we focus on the following four as the ones that are most popular among data practitioners, often mentioned on mailing lists and/or being candidates or prototypes for the upcoming W3C recommendation:
-\emph{Description Set Profiles (DSP)}\footnote{\url{ http://dublincore.org/documents/2008/03/31/dc-dsp/}}, \emph{Resource Shapes (ReSh)}, \emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}}, and the \emph{Web Ontology Language} \emph{(OWL)}.
+\emph{Description Set Profiles (DSP)}\footnote{\url{ http://dublincore.org/documents/2008/03/31/dc-dsp/}}, \emph{Resource Shapes (ReSh)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shapes-20140211/}}, \emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}}, and the \emph{Web Ontology Language} \emph{(OWL)}\footnote{\url{http://www.w3.org/TR/owl2-syntax/}}.
 Despite the fact that OWL is arguably not a constraint language, it is widely used in practice as such under the closed-world and unique name assumptions.
@@
 ShEx associate RDF graphs with labeled patterns called \emph{shapes} which are used to express formal constraints on the content of RDF graphs.
-\emph{Resource Shapes (ReSh)} \cite{W3C-ReSh-2014} defines its own vocabulary for specifying shapes of RDF resources.
+\emph{Resource Shapes (ReSh)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shapes-20140211/}} \cite{W3C-ReSh-2014} defines its own vocabulary for specifying shapes of RDF resources.
 Ryman, Hors, and Speicher define \emph{shape} as a description of the set of triples a resource is expected to contain and as a description of the integrity constraints those triples are required to satisfy \cite{Ryman2013}.

### 2015-07-16 paper/paper 2/dc-2015.tex
Abstract

--- 2015-07-16 paper/paper 2/dc-2015.tex
@@
 Regarding the implementation of constraint languages, we already proposed to use high-level languages to describe the constraints, but map them to SPARQL queries in order to execute the actual validation; we demonstrated this approach for Description Set Profiles.
-In this paper, we generalize from the experience of implementing Description Set Profiles by introducing an abstraction layer that is able to describe any constraint type in a way that is more or less straight-forwardly transformable to SPARQL queries.
-It provides a basic terminology and classification system for RDF constraints to foster discussions on RDF validation.
-We demonstrate that using another layer on top of SPARQL helps to implement validation consistently accross constraint languages and simplifies the actual implementation of new languages.
-
-%When using the developed vocabulary to intermediately represent constraints,
-%depending on the individual type of constraint one or multiple particular constraining elements are applied.
-%We base these constraining elements on formal logic.
-%As constraints of 2/3 of all constraint types are expressible by logical constructs from description logics,
-%we may use logical constructs as constraining elements.
-%In order to be able to support all constraint types, however,
-%we determined for each constraint type more intuitive constraining elements in natural language like \emph{conditional properties}, \emph{allowed values}, and \emph{language tag minimum cardinality}.
-%A title is required for books.
-%This constraint of the constraint type \emph{required properties (R-68)} can be either expressed by the existential quantifier $\exists$ from description logics or more intuitively using the constraining element \emph{required properties}.
-
-%As SPARQL is generally seen as the method of choice to validate data according to certain constraints and
-%as RDF data can be validated on constraints of any constraint type by means of SPARQL,
-%we use SPIN, a SPARQL-based way to validate RDF data, as implementation language 
-%to actually execute the validation of RDF data.
-%Thereby, constraints may either be 
-%(1) expressed by domain specific constraint languages like OWL 2 and DSP or
-%(2) represented by the proposed vocabulary.
-
-%The majority of these constraint types can be expressed in description logics which provides their logical underpinning.
-%In this paper, we provide a basic terminology and classification system for RDF constraints.\tb{The contributions of this paper are the following. (1)...}
-%We developed a vocabulary to describe constraints of any RDF constraint type generically. 
-%%(whether expressible in description logics or not).
-%We show how to transform constraints, expressed by any constraint language \ms{$\alpha$}, into generically expressed constraints and into constraints represented by any other constraint language \ms{$\beta$} and discuss why these transformations are useful.
-%We explain how to overcome the necessity to implement the validation of each constraint type for multiple constraint languages by providing mappings to generically expressed constraints.
-
-%The main contributions of this paper are:
-%(1) We provide a basic terminology and classification system for RDF constraints to lay the ground for discussions on RDF validation.
-%(2) As current high-level constraint languages do not support all constraint types, 
-%we developed a vocabulary to describe constraints of any constraint type in a generic way and specified its underlying semantics.
-%(3) We show how to enhance the interoperability of constraints expressed by different languages by using the proposed vocabulary 
-%to intermediately represent constraints 
-%%as an intermediate generic representation 
-%which enables transformations between semantically equivalent constraints.
-%(4) We explain how constraint languages may reuse validation implementations which are provided once for each constraint type.
+In this paper, we generalize from the experience of implementing DSP by introducing an abstraction layer that is able to describe any constraint type in a way that mappings from high-level constraint languages to this intermediate representation can be created more or less straight-forwardly.
+We demonstrate that using another layer on top of SPARQL helps to implement validation consistently accross constraint languages, simplifies the actual implementation of new languages and supports the transformation of semantically equivalent constraints across constraint languages.
+
+%%%%% ORIGINAL, AS SUBMITTED
+% In the context of the DCMI RDF Application Profile task group and the W3C Data Shapes Working Group solutions for the proper formulation of constraints and validation of RDF data on these constraints are developed.
+Several approaches and constraint languages exist but there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners.
+% To support the work, a comprehensive, community-driven database has been created where case studies, use cases, requirements and solutions are collected. Based on this database,
+% we published by today 81 types of constraints that are required by various stakeholders for data applications.
+We generally use this collection of constraint types to gain a better understanding of the expressiveness of existing solutions and gaps that still need to be filled.
+% Regarding the implementation of constraint languages, we already proposed to use high-level languages to describe the constraints, but map them to SPARQL queries in order to execute the actual validation; we demonstrated this approach for Description Set Profiles.
+% In this paper, we generalize from the experience of implementing Description Set Profiles by introducing an abstraction layer that is able to describe any constraint type in a way that is more or less straight-forwardly transformable to SPARQL queries.
+% It provides a basic terminology and classification system for RDF constraints to foster discussions on RDF validation.
+% We demonstrate that using another layer on top of SPARQL helps to implement validation consistently accross constraint languages and simplifies the actual implementation of new languages.
 
@@
 \section{Introduction}
-%The purpose of OWL 2 ontologies is to perform reasoning on RDF data and not to validate RDF data conforming to these ontologies.
-%OWL 2 is based on the {\em non-unique name assumption} (nUNA) whereas RDF validation requires that different names represent different objects ({\em unique name assumption} (UNA)). 
-%Reasoning in OWL 2 is based on the semantics of {\em open-world assumption} (OWA), i.e., a statement cannot be inferred to be false if it cannot be proved to be true  which fits its primary design purpose: to represent knowledge on the World Wide Web.
-%On the other hand, many RDF validation scenarios require the {\em closed-world assumption} (CWA) (i.e., a statement is inferred to be false if it cannot be proved to be true).
-%This ambiguity in semantics is one of the main reasons why OWL 2 has not been adopted as a standard constraint language for RDF validation.  
-%For this reason, we cannot use OWL 2 ontologies for RDF validation as we use XML Schemas, DTDs, RELAX NG, or Schematron to validate XML documents.
 
@@
 For our work, we focus on the following four as the ones that are most popular among data practitioners, often mentioned on mailing lists and/or being candidates or prototypes for the upcoming W3C recommendation:
-\emph{Description Set Profiles (DSP)}\footnote{\url{ http://dublincore.org/documents/2008/03/31/dc-dsp/}}, \emph{Resource Shapes (ReSh)}, \emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}}, and the \emph{Web Ontology Language} \emph{(OWL)}.
+\emph{Description Set Profiles (DSP)}, \emph{Resource Shapes (ReSh)}, \emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}}, and the \emph{Web Ontology Language} \emph{(OWL)}.
 Despite the fact that OWL is arguably not a constraint language, it is widely used in practice as such under the closed-world and unique name assumptions.
@@
 \cite{DCMI-DC-RDF-2008} depict how the constructs of the DCMI Abstract Model are represented using the abstract syntax of the RDF model.
-A \emph{Description Set Profile (DSP)}\footnote{\url{ http://dublincore.org/documents/2008/03/31/dc-dsp/}} \cite{DCMI-DSP-2008} is a generic constraint language which is used to formally specify structural constraints on sets of resource descriptions within an application profile.
+A \emph{Description Set Profile (DSP)} \cite{DCMI-DSP-2008} is a generic constraint language which is used to formally specify structural constraints on sets of resource descriptions within an application profile.
 DSP constrains resources that may be described by descriptions in a description set, the properties that may be used, and the values properties may point to.

### 2015-07-16 paper/paper 2/dc-2015.tex

@@
 For our work, we focus on the following four as the ones that are most popular among data practitioners, often mentioned on mailing lists and/or being candidates or prototypes for the upcoming W3C recommendation:
-\emph{Description Set Profiles (DSP)}, \emph{Resource Shapes (ReSh)}, \emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}}, and the \emph{Web Ontology Language} \emph{(OWL)}.
+\emph{Description Set Profiles (DSP)}\footnote{\url{ http://dublincore.org/documents/2008/03/31/dc-dsp/}}, \emph{Resource Shapes (ReSh)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shapes-20140211/}}, \emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}}, and the \emph{Web Ontology Language} \emph{(OWL)}\footnote{\url{http://www.w3.org/TR/owl2-syntax/}}.
 Despite the fact that OWL is arguably not a constraint language, it is widely used in practice as such under the closed-world and unique name assumptions.

### 2015-07-16 paper/paper 2/dc-2015.tex
minor

--- 2015-07-16 paper/paper 2/dc-2015.tex
@@
 
-\emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}} \cite{W3C-ShEx-Primer-2014,W3C-ShEx-Definition-2014,Prud'hommeaux-2014,Boneva-2014} specifies a language whose syntax and semantics are similar to regular expressions.
+\emph{Shape Expressions (ShEx)} \cite{W3C-ShEx-Primer-2014,W3C-ShEx-Definition-2014,Prud'hommeaux-2014,Boneva-2014} specifies a language whose syntax and semantics are similar to regular expressions.
 ShEx associate RDF graphs with labeled patterns called \emph{shapes} which are used to express formal constraints on the content of RDF graphs.

### 2015-07-17 paper/paper 2/dc-2015.tex
abstract

@@
 We generally use this collection of constraint types to gain a better understanding of the expressiveness of existing solutions and gaps that still need to be filled.
-Regarding the implementation of constraint languages, we already proposed to use high-level languages to describe the constraints, but map them to SPARQL queries in order to execute the actual validation; we demonstrated this approach for Description Set Profiles.
-In this paper, we generalize from the experience of implementing DSP by introducing an abstraction layer that is able to describe any constraint type in a way that mappings from high-level constraint languages to this intermediate representation can be created more or less straight-forwardly.
-We demonstrate that using another layer on top of SPARQL helps to implement validation consistently accross constraint languages, simplifies the actual implementation of new languages and supports the transformation of semantically equivalent constraints across constraint languages.
+Regarding the implementation of constraint languages, we already proposed to use high-level languages to describe the constraints, but map them to SPARQL queries in order to execute the actual validation; we demonstrated this approach for \textcolor{red}{the Web Ontology Language in its current version 2 and }Description Set Profiles.
+In this paper, we generalize from the experience of implementing \textcolor{red}{OWL 2 and} DSP by introducing an abstraction layer that is able to describe \textcolor{red}{constraints of} any constraint type in a way that mappings from high-level constraint languages to this intermediate representation can be created more or less straight-forwardly.
+We demonstrate that using another layer on top of SPARQL helps to implement validation consistently accross constraint languages, simplifies the actual implementation of new languages, and supports the transformation of semantically equivalent constraints across constraint languages.
 
@@
 
+\tb{ToDo Thomas: OWL 2}
 \emph{Stardog Integrity Constraint Validation (ICV)} and the \emph{Pellet Integrity Constraint Validator (ICV)} use OWL 2 constructs to formulate constraints.

### 2015-07-17 paper/paper 2/dc-2015.tex
introduction

@@
 With its direct support of validation via SPARQL, the \emph{SPARQL Inferencing Notation (SPIN)}\footnote{\url{http://spinrdf.org/}} is also very popular to formulate and check constraints \cite{Fuerber2010}.
-We consider SPIN as a low-level language in contrast to the other constraint languages where specific language constructs exist to define constraints in a declarative and in comparison more intuitive way -- although SPARQL aficionados might object particularly to the latter point.
+We consider SPIN as a low-level language in contrast to the other constraint languages where specific language constructs exist to define constraints in a declarative and in comparison more intuitive way -- although, SPARQL aficionados might object particularly to the latter point.
 
@@
 
-We formerly demonstrated that a high-level constraint language, Description Set Profiles, can be implemented by mapping the language to SPIN using SPARQL CONSTRUCT queries \cite{BoschEckert2014-2}.
-We provide a validation environment where own mappings from arbitrary constraint languages can be provided and tested.\footnote{Available at \url{http://purl.org/net/rdfval-demo}, source code available at: \url{https://github.com/boschthomas/rdf-validator}.}
-
-The creation of such mappings is in many cases not straight-forward and requires profound knowledge of SPARQL, as the following example demonstrates:
-
+We formerly demonstrated that a high-level constraint language like OWL 2 and DSP can be implemented by mapping the language to SPIN using SPARQL CONSTRUCT queries \cite{BoschEckert2014-2}.
+We provide a validation environment where own mappings from arbitrary constraint languages can be provided and tested\footnote{Online available at: \url{http://purl.org/net/rdfval-demo}, source code online available at: \url{https://github.com/boschthomas/rdf-validator}.}.
+The only limitations are that the constraints have to
+be expressed in RDF and that the constraint language is expressable in SPARQL.
+
+The creation of such mappings is in many cases not straight-forward and requires profound knowledge of SPARQL, as the following example demonstrates. 
 The constraint type \emph{minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75}\footnote{Requirements are identified in the database by an R and a number, additionally an alphanumeric identifier is provided, in this case R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES.
-Online at: \url{http://lelystad.informatik.uni-mannheim.de/rdf-validation/?q=node/82}} can be used to formulate the constraint
-that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.
-
+Online at: \url{http://lelystad.informatik.uni-mannheim.de/rdf-validation/?q=node/82}} can be used to formulate the constraint that publications must have at least one author which must be a person.
 This constraint can be expressed as follows using different constraint languages:
@@
 Note that the SPIN representation is NOT a mapping, but a direct expression of the constraint using a SPARQL CONSTRUCT query that creates a spin:ConstraintViolation if the constraint is violated.
-The mapping for DSP is much more complicated and can be found in the mappings provided by us.\footnote{Online: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/DSP_SPIN-Mapping.ttl#L4665}}
+The mapping for DSP is much more complicated and can be found in the mappings provided by us\footnote{Online available at: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/DSP_SPIN-Mapping.ttl#L4665}}.
 

### 2015-07-17 paper/paper 2/dc-2015.tex
introduction

@@
 The creation of such mappings is in many cases not straight-forward and requires profound knowledge of SPARQL, as the following example demonstrates.
+\tb{diese beipsiel zeigt nur wie constraints desslben typs mit unterschiedlichen CL ausgedrückt wird!
+sollen wir hier noch ein codebeipsiel eines konkreten mappings dieses CT für DSP zeigen?}
 The constraint type \emph{minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75}\footnote{Requirements are identified in the database by an R and a number, additionally an alphanumeric identifier is provided, in this case R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES.
@@
 Note that the SPIN representation is NOT a mapping, but a direct expression of the constraint using a SPARQL CONSTRUCT query that creates a spin:ConstraintViolation if the constraint is violated.
-The mapping for DSP is much more complicated and can be found in the mappings provided by us\footnote{Online available at: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/DSP_SPIN-Mapping.ttl#L4665}}.
+The mappings for OWL 2 and DSP are much more complicated and can be found in the mappings provided by us\footnote{OWL 2 mapping online available at: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/OWL2_SPIN-Mapping.ttl}; DSP mapping online available at: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/DSP_SPIN-Mapping.ttl#L4665}}.
 

### 2015-07-17 paper/paper 2/dc-2015.tex
introduction

@@
 
-In this paper, we build on the experience gained from mapping several constraint languages to SPIN and from the analysis of the identified constraint types to create an intermediate layer, a framework that is able to describe the mechanics of all constraint types and that can be used to map high-level languages more easily.
+In this paper, we build on the experience gained from mapping several constraint languages to SPIN and from the analysis of the identified constraint types \tb{was haben wir analysiert?
+meinst du die constraint type specific expressivity of constraint languages?}to create an intermediate layer, a framework that is able to describe the mechanics of all constraint types and that can be used to map high-level languages more easily.
+\tb{sollten wir hier nicht alle contributions nennen?
+ich denke im abstact stehen sie alle}
 

### 2015-07-17 paper/paper 2/dc-2015.tex
introduction

--- 2015-07-17 paper/paper 2/dc-2015.tex
@@
 We generally use this collection of constraint types to gain a better understanding of the expressiveness of existing solutions and gaps that still need to be filled.
-Regarding the implementation of constraint languages, we already proposed to use high-level languages to describe the constraints, but map them to SPARQL queries in order to execute the actual validation; we demonstrated this approach for \textcolor{red}{the Web Ontology Language in its current version 2 and }Description Set Profiles.
-In this paper, we generalize from the experience of implementing \textcolor{red}{OWL 2 and} DSP by introducing an abstraction layer that is able to describe \textcolor{red}{constraints of} any constraint type in a way that mappings from high-level constraint languages to this intermediate representation can be created more or less straight-forwardly.
+Regarding the implementation of constraint languages, we already proposed to use high-level languages to describe the constraints, but map them to SPARQL queries in order to execute the actual validation; we demonstrated this approach for the Web Ontology Language in its current version 2 and Description Set Profiles.
+In this paper, we generalize from the experience of implementing OWL 2 and DSP by introducing an abstraction layer that is able to describe constraints of any constraint type in a way that mappings from high-level constraint languages to this intermediate representation can be created more or less straight-forwardly.
 We demonstrate that using another layer on top of SPARQL helps to implement validation consistently accross constraint languages, simplifies the actual implementation of new languages, and supports the transformation of semantically equivalent constraints across constraint languages.
@@
 For our work, we focus on the following four as the ones that are most popular among data practitioners, often mentioned on mailing lists and/or being candidates or prototypes for the upcoming W3C recommendation:
-\emph{Description Set Profiles (DSP)}\footnote{\url{ http://dublincore.org/documents/2008/03/31/dc-dsp/}}, \emph{Resource Shapes (ReSh)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shapes-20140211/}}, \emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}}, and the \emph{Web Ontology Language} \emph{(OWL)}\footnote{\url{http://www.w3.org/TR/owl2-syntax/}}.
+\emph{Description Set Profiles (DSP)}\footnote{\url{http://dublincore.org/documents/2008/03/31/dc-dsp/}}, \emph{Resource Shapes (ReSh)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shapes-20140211/}}, \emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}}, and the \emph{Web Ontology Language} \emph{(OWL)}\footnote{\url{http://www.w3.org/TR/owl2-syntax/}}.
 Despite the fact that OWL is arguably not a constraint language, it is widely used in practice as such under the closed-world and unique name assumptions.
@@
 
-The creation of such mappings is in many cases not straight-forward and requires profound knowledge of SPARQL, as the following example demonstrates. 
 The constraint type \emph{minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75}\footnote{Requirements are identified in the database by an R and a number, additionally an alphanumeric identifier is provided, in this case R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES.
@@
 \textit{DSP:} [ dsp:resourceClass Publication ; dsp:statementTemplate [ 
-          dsp:minOccur 1 ; dsp:maxOccur "infinity" ; 
+          dsp:minOccur 1 ; 
           dsp:property author ; 
@@
 Unfortunately, there is not (yet) a high-level language that supports all constraint types.
+
+The creation of mappings of constraint languages to SPIN is in many cases not straight-forward and requires profound knowledge of SPARQL, as the following example demonstrates.
+In this example, the validation of the \emph{minimum qualified cardinality restrictions} constraint type is implemented for DSP:
+
+\begin{ex}[commandchars=\\\{\}]
+CONSTRUCT \{
+    _:constraintViolation 
+        a spin:ConstraintViolation ;
+        rdfs:label ?violationMessage ;
+        spin:violationRoot ?this ;
+        spin:violationPath ?property ;
+        spin:violationSource ?violationSource . \}
+WHERE \{	
+    ?this a ?resourceClass .
+    ?descriptionTemplate 
+        dsp:resourceClass ?resourceClass ;
+        dsp:statementTemplate ?statementTemplate .
+    ?statementTemplate 
+        dsp:minOccur ?minimum ;
+        dsp:property ?property ;
+        dsp:nonLiteralConstraint ?nonLiteralConstraint .
+    ?nonLiteralConstraint dsp:valueClass ?valueClass .	
+    BIND ( \textit{qualifiedCardinality}( ?this, ?property, ?valueClass ) AS ?cardinality ) .
+    FILTER ( ?cardinality < ?minimum ) . \}
+\end{ex}
 
@@
 	\centering
-		\includegraphics[width=0.60\textwidth]{images/RDF-CV.png}
+		\includegraphics[width=0.80\textwidth]{images/RDF-CV.png}
 	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} Conceptual Model}
@@
 
-Finally, the \emph{constraining value} contains a literal value to be checked against; for instance in the case of the 'REGEX' element, it contains the regular expression to be evaluated.
+Finally, the \emph{constraining value} contains a literal value to be checked against; for instance in the case of the REGEX element, it contains the regular expression to be evaluated.
 
@@
 
-The mapping simply constructs this representation out of the OWL2 representation using a SPARQL CONSTRUCT query:
+The mapping simply constructs this representation out of the OWL 2 representation using a SPARQL CONSTRUCT query:
 
@@
 As stated in Section~\ref{sec:motivation}, we see a huge potential in the possibility to transform semantically equivalent constraints from one high-level constraint language to another via the RDF-CV representation, to avoid that every possible combination of constraint languages has to be mapped separately.
-The following SPIN inference rule exemplifies this approach and provides a mapping from RDF-CV back to an OWL2 constraint:
+The following SPIN inference rule exemplifies this approach and provides a mapping from RDF-CV back to an OWL 2 constraint:
 
@@
 
-\tb{ToDo Thomas: OWL 2}
 \emph{Stardog Integrity Constraint Validation (ICV)} and the \emph{Pellet Integrity Constraint Validator (ICV)} use OWL 2 constructs to formulate constraints.

### 2015-07-17 paper/paper 2/dc-2015.tex
minor

@@
 The framework consists of a very simple conceptual model using the RDF Constraints Vocabulary (RDF-CV) which has been introduced in this paper.
-The core of the framework is the definition of 103 constraining elements that are used to define all 81 types of constraints that to date have been identified within the \emph{DCMI RDF Application Profiles Task Group} and in cooperation with the \emph{W3C Data Shapes Working Group}.
-The full definition of all constraint types and the representation of the types in RDF-CV is provided in an accompanying technical report \cite{BoschNolleAcarEckert2015}.
+The core of the framework is the definition of 103 constraining elements that are used to define constraints of all 81 types that to date have been identified within the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group.
+The full definition of all constraint types and the generic representation of the types in RDF-CV is provided in an accompanying technical report \cite{BoschNolleAcarEckert2015}.
 
 We have demonstrated how the framework can be used to map a constraint language to RDF-CV and also how to map back from RDF-CV to the constraint language.
-The latter enables the transformation of sematically equivalent constraints from one constraint language to another via the RDF-CV intermediate representation.
+The latter enables the transformation of semantically equivalent constraints from one constraint language to another via the RDF-CV intermediate representation.
 
@@
 
-It is part of future work to finalize the implementation of all 81 constraint types in our \emph{RDF Validator}, to fully map constraint languages to RDF-CV (first and foremost DSP and OWL) and of course keep the framework in sync with the ongoing work in the working groups.
+It is part of future work to finalize the implementation of all 81 constraint types in our \emph{RDF Validator}, to fully map constraint languages to RDF-CV (first and foremost DSP and OWL 2) and of course keep the framework in sync with the ongoing work in the working groups.
 

### 2015-07-17 paper/paper 2/dc-2015.tex
related work

@@
 \textit{SPIN:} CONSTRUCT \{ [ a spin:ConstraintViolation ... . ] \} WHERE \{ 
-          ?this ?p ?o ; a ?C .
-          BIND ( \textit{qualifiedCardinality}( ?this, ?p, ?C ) AS ?c ) .
+          ?this 
+              a ?C1 ;
+              ?p ?o .
+          BIND ( \textit{qualifiedCardinality}( ?this, ?p, ?C2 ) AS ?c ) .
           BIND( STRDT ( STR ( ?c ), xsd:nonNegativeInteger ) AS ?cardinality ) .
           FILTER ( ?cardinality < 1 ) . 
-          FILTER ( ?C = Person ) .
+          FILTER ( ?C1 = Publication ) .
+          FILTER ( ?C2 = Person ) .
           FILTER ( ?p = author ) . \}
@@
 Therefore,
-semantically equivalent \emph{specific constraints} represented in different languages will exist.
+semantically equivalent constraints represented in different languages will exist.
 This raises two questions: 
@@
 Thereby, we do not need to define mappings for each constraint type and each possible combination of constraint languages.
-Assuming that we are able to express a single constraint type like \emph{minimum qualified cardinality restrictions} within 10 languages, $n \cdot n-1 = 90$ mappings would be needed -- as mapping generally are not invertible.
+Assuming that we are able to express a single constraint type like \emph{minimum qualified cardinality restrictions} within 10 languages, $n \cdot n-1 = 90$ mappings would be needed -- as mappings generally are not invertible.
 With an intermediate generic representation of constraints, on the other side, we only need to define for each constraint type $2n = 20$ mappings -- where $10$ mappings should already exist if we have an implementation in our framework.
@@
 
-When we implemented DSP and other constraint languages using SPARQL as intermediate language \cite{BoschEckert2014-2}, we found that many mappings actually resemble each other; particularly the mappings of the same constraint type in different languages, but also the mappings of different constraint types, though the latter only on a very superficial, structural level.
-The basic idea of our framework is very simple: we aim at reducing the representation of constraint types to the absolute minimum that has to be provided in a mapping to generate the appropriate SPIN implementation.
-Consider again our example from above for the SPIN implementation of \emph{minimum qualified cardinality restrictions}:
+When we fully implemented OWL 2 and DSP and to some extend other constraint languages using SPARQL as intermediate language \cite{BoschEckert2014-2}, we found that many mappings actually resemble each other; particularly the mappings of the same constraint type in different languages, but also the mappings of different constraint types, though the latter only on a very superficial, structural level.
+The basic idea of our framework is very simple: we aim at reducing the representation of constraints to the absolute minimum that has to be provided in a mapping to SPIN to implement the validation of constraints.
+% to generate the appropriate SPIN implementation. 
+Consider again our example from above for the SPIN representation of a constraint of the type \emph{minimum qualified cardinality restrictions}:
 
@@
 
-However this SPIN code looks like, all we have to provide to make it work is the desired minimum cardinality (?cardinality), the property to be constrained (?p) and the class for which this property should be constrained (?C).
+However this SPIN code looks like, all we have to provide to make it work is the desired minimum cardinality (?cardinality), the property to be constrained (?p), the class whose individuals must hold for the constraint (?C1), and the class for which this property should be constrained (?C2).
 All other variables are bound internally.
-So we could reduce the effort of the mapping by simply providing these three values, which are readily available in all representations of this constraint type:
+So we could reduce the effort of the mapping by simply providing these four values, which are readily available in all representations of this constraint type:
 
@@
 
+The \emph{Web Ontology Language (OWL)} \cite{W3C-OWL2-Primer-2012} formally specifies the intended semantics of conceptual models about data and therefore enables software to understand data.
+OWL has become a popular standard for data representation, data exchange, and data integration of heterogeneous data sources.
+Besides that, the retrieval of data benefits from semantic knowledge specified using OWL.
+In combination with the OWL-based \emph{Semantic Web Rule Language (SWRL)} \cite{Horrocks04}, OWL provides facilities for developing very powerful reasoning services.
+Reasoning on RDF data enables to derive implicit data out of explicitly stated data.
+OWL is based on formal logic and on the subject-predicate-object triples from RDF.
+OWL is actually a description logic with underlying formal semantics which allows one to assign truth values to syntactic expressions.
+OWL specifies semantic information about specific domains, describes relations between domain classes, and thus allows the sharing of conceptualizations.
+
+OWL is an expressive language for which description logics provides the foundational basis and which offers knowledge representation and reasoning services.
+Validation, however, is not the primary purpose of its design which has lead to claims that OWL cannot be used for validation.
+In practice, however, OWL is well-spread and RDFS/OWL constructs are widely used to tell people and applications about how valid instances should look like.
+In general, RDF documents follow the syntactic structure and the semantics of RDFS/OWL ontologies which could therefore not only be used for reasoning but also for validation.
+
 \emph{Stardog Integrity Constraint Validation (ICV)} and the \emph{Pellet Integrity Constraint Validator (ICV)} use OWL 2 constructs to formulate constraints.

### 2015-07-17 paper/paper 2/dc-2015.tex
introduction

@@
 With its direct support of validation via SPARQL, the \emph{SPARQL Inferencing Notation (SPIN)}\footnote{\url{http://spinrdf.org/}} is also very popular to formulate and check constraints \cite{Fuerber2010}.
-We consider SPIN as a low-level language in contrast to the other constraint languages where specific language constructs exist to define constraints in a declarative and in comparison more intuitive way -- although, SPARQL aficionados might object particularly to the latter point.
+We consider SPIN as a low-level language in contrast to the other constraint languages where specific language constructs exist to define constraints in a declarative and in comparison more intuitive way -- although SPARQL aficionados might object particularly to the latter point.
 
@@
 The constraint type \emph{minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75}\footnote{Requirements are identified in the database by an R and a number, additionally an alphanumeric identifier is provided, in this case R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES.
-Online at: \url{http://lelystad.informatik.uni-mannheim.de/rdf-validation/?q=node/82}} can be used to formulate the constraint that publications must have at least one author which must be a person.
+Online at: \url{http://lelystad.informatik.uni-mannheim.de/rdf-validation/?q=node/82}} can be instantiated to formulate the constraint that publications must have at least one author which must be a person.
 This constraint can be expressed as follows using different constraint languages:
@@
 
-Note that the SPIN representation is NOT a mapping, but a direct expression of the constraint using a SPARQL CONSTRUCT query that creates a spin:ConstraintViolation if the constraint is violated.
-The mappings for OWL 2 and DSP are much more complicated and can be found in the mappings provided by us\footnote{OWL 2 mapping online available at: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/OWL2_SPIN-Mapping.ttl}; DSP mapping online available at: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/DSP_SPIN-Mapping.ttl#L4665}}.
-
-On the other hand, it can be seen that the higher-level constraint languages are comparatively similar, there seems to be a pattern, a common way to express this type of constraint.
+Note that the SPIN representation of the constraint is NOT a SPIN mapping to implement the constraint, but a direct expression of the constraint using a SPARQL CONSTRUCT query that creates a spin:ConstraintViolation if the constraint is violated.
+
+It can be seen that the higher-level constraint languages are comparatively similar, there seems to be a pattern, a common way to express this type of constraint.
 Therefore, a mapping from a high-level language to another high-level language would be considerably easier.
@@
 
-The creation of mappings of constraint languages to SPIN is in many cases not straight-forward and requires profound knowledge of SPARQL, as the following example demonstrates.
+The creation of mappings of constraint languages to SPIN to implement their validation is in many cases not straight-forward and requires profound knowledge of SPARQL, as the following example demonstrates.
 In this example, the validation of the \emph{minimum qualified cardinality restrictions} constraint type is implemented for DSP:
@@
 \end{ex}
+
+The SPIN mappings for OWL 2 and DSP are rather complicated and can be found in the mappings provided by us\footnote{OWL 2 mapping online available at: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/OWL2_SPIN-Mapping.ttl}; DSP mapping online available at: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/DSP_SPIN-Mapping.ttl#L4665}}.
 
@@
 
-In this paper, we outlined our idea of a general framework to support the mapping of high-level constraint languages to a generic representation, which subsequently can be used to generate validating SPIN/SPARQL queries to actually validate data against constraints provided in the high-level language.
-The framework consists of a very simple conceptual model using the RDF Constraints Vocabulary (RDF-CV) which has been introduced in this paper.
-The core of the framework is the definition of 103 constraining elements that are used to define constraints of all 81 types that to date have been identified within the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group.
+In this paper, we outlined our idea of a general framework to support the mapping of high-level constraint languages to a generic representation, which subsequently can be used to generate validating SPIN/SPARQL queries to actually validate data against constraints provided in the high-level language.\tb{I do not understand this!} The framework consists of a very simple conceptual model using the \emph{RDF Constraints Vocabulary (RDF-CV)} which has been introduced in this paper.
+The core of the framework is the definition of 103 constraining elements that are used to define constraints of all 81 constraint types that to date have been identified within the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group.
 The full definition of all constraint types and the generic representation of the types in RDF-CV is provided in an accompanying technical report \cite{BoschNolleAcarEckert2015}.
@@
   \item to implement the validation of constraints consistently across constraint languages,
-  \item to support the extension of constraint languages by means of a simple mapping, and
+  \item to support the extension of constraint languages by means of a simple mapping\tb{was genau meinst du damit? wenn weitere constraint typen unterstützt werden sollen?}, and
   \item to enhance or rather establish the interoperability of different constraint languages.

### 2015-07-17 paper/paper 2/dc-2015.tex
minor

@@
 When we fully implemented OWL 2 and DSP and to some extend other constraint languages using SPARQL as intermediate language \cite{BoschEckert2014-2}, we found that many mappings actually resemble each other; particularly the mappings of the same constraint type in different languages, but also the mappings of different constraint types, though the latter only on a very superficial, structural level.
-The basic idea of our framework is very simple: we aim at reducing the representation of constraints to the absolute minimum that has to be provided in a mapping to SPIN to implement the validation of constraints.
+The basic idea of our framework is very simple: we aim at reducing the representation of constraints to the absolute minimum that has to be provided in a mapping to SPIN to implement the validation for constraint types.
 % to generate the appropriate SPIN implementation. 
@@
 
-However this SPIN code looks like, all we have to provide to make it work is the desired minimum cardinality (?cardinality), the property to be constrained (?p), the class whose individuals must hold for the constraint (?C1), and the class for which this property should be constrained (?C2).
+However this SPIN code looks like, all we have to provide to make it work is the desired minimum cardinality (?cardinality), the property to be constrained (?p), the class whose individuals must hold for the constraint (?C1), and the class for which the property should be constrained (?C2).
 All other variables are bound internally.

### 2015-07-18 paper/paper 2/dc-2015.tex
DL

@@
 
-\section{Towards a framework} 
+\section{Towards a Framework} 
 \label{sec:vocabulary}
@@
 
-\subsection{Building blocks}
-
-At the core, we use a very simple conceptual model for constraints, using a small vocabulary called \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.
-The conceptual model is shown in Figure \ref{fig:RDF-CV-conceptual-model}.
+\subsection{Building Blocks}
+
+At the core, we use a very simple conceptual model for constraints (see Figure \ref{fig:RDF-CV-conceptual-model}), using a small lightweight vocabulary called \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.\tb{ToDo: actualize vocabulary}
 \begin{figure}[H]
@@
 
+\emph{RDF constraints} are either simple constraints or complex constraints.
 \emph{Simple constraints} denotes the set of atomic constraints with respect to a single constraining element -- we will come to the notion of a constraining element in a second.
-In contrast, there are
-\emph{complex constraints}, i.e., the set of constraints which are created out of \emph{simple} and/or other \emph{complex constraints}.
+In contrast, there are \emph{complex constraints}, i.e., the set of constraints which are created out of simple and/or other complex constraints.
 This structure therefore allows to build complex constraints out of other (simple or complex) constraints.
-Regarding our database of constraint types, 60\% of the constraint types are simple constraints and 26\% are complex constraints.
-Constraints of additional 14\% of the constraint types are \emph{complex constraints} as well which can be simplified and therefore formulated as \emph{simple constraints} if additional constraining elements are introduced to cover them.
+Regarding our database of constraint types, 60\% of the constraint types are used to instantiate simple constraints and 26\% complex constraints.
+Constraints of additional 14\% of the constraint types are complex constraints as well which can be simplified and therefore formulated as simple constraints if additional constraining elements are introduced to cover them.
 
@@
 The central property is the \emph{constraining element} which refers to one of 103 constraining elements described in our technical report \cite{BoschNolleAcarEckert2015}.
-Constraining elements are for example taken from Description Logics, another concrete example would be 'REGEX' where a regular expression is checked against some property value.
+Constraining elements are for example taken from Description Logics, another concrete example would be REGEX where a regular expression is checked against some property value.
 In most cases, constraining elements directly correspond to a constraint type, sometimes (as for REGEX) they are shared by several constraint types.
@@
 
-A cornerstone of the framework is the generic representation of a constraint, which can often be done using \emph{Description Logics (DL)}, as for the \emph{minimum qualified cardinality restrictions}: {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}}
+A cornerstone of the framework is the generic representation of a constraint, which can often be done using \emph{Description Logics (DL)} \cite{Kroetzsch2012,Baader-2003,Baader-Nutt-2003}, as for the \emph{minimum qualified cardinality restrictions}: {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person.}}  This way, the knowledge representation formalism DL with its well-studied theoretical properties provides the foundational basis for the framework.
 
@@
 Only for the remaining 36\%, other means, i.e., other constraining elements, had to be identified.
-This is not surprising if we consider that OWL is based on Description Logics.
-When we talk about using Description Logics to represent constraints, we have to establish once more that the semantics of OWL and Description Logics differ from the semantics of constraint languages regarding the open world assumption (OWA) and the non-unique name assumption (nUNA).
+This is not surprising if we consider that OWL is based on DL.
+When we talk about using DL to represent constraints, we have to establish once more that the semantics of OWL and DL differ from the semantics of constraint languages regarding the open world assumption (OWA) and the non-unique name assumption (nUNA).
 Both are usually assumed when dealing with OWL or DL, whereas validation usually assumes a closed world (CWA) and unique naming (UNA), i.e., if a desired property is missing, this leads to a violation and if two resources are named differently, they are assumed to be different resources.
@@
 Table \ref{tab:property-constraint-cardinality-restriction} displays how the simple constraint is generically represented using the RDF-CV.
-Note that instead of the description logics construct $\geq$, the constraining element \emph{minimum qualified cardinality restriction} may be used.
+Note that instead of the DL construct $\geq$, the constraining element \emph{minimum qualified cardinality restriction} may be used.
 
@@
 
-\subsection{Mapping implementation}
+\subsection{Mapping Implementation}
 
@@
 
-\subsection{Constraint transformation}
+\subsection{Constraint Transformation}
 
@@
 
-OWL is an expressive language for which description logics provides the foundational basis and which offers knowledge representation and reasoning services.
+OWL is an expressive language for which DL provides the foundational basis and which offers knowledge representation and reasoning services.
 Validation, however, is not the primary purpose of its design which has lead to claims that OWL cannot be used for validation.

### 2015-07-18 paper/paper 2/dc-2015.tex
3.1

@@
 
-At the core, we use a very simple conceptual model for constraints (see Figure \ref{fig:RDF-CV-conceptual-model}), using a small lightweight vocabulary called \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.\tb{ToDo: actualize vocabulary}
+At the core, we use a very simple conceptual model for constraints (see Figure \ref{fig:RDF-CV-conceptual-model}), using a small lightweight vocabulary called \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.\tb{ToDo for Thomas: actualize vocabulary}
 \begin{figure}[H]
@@
 
-The properties describing a simple constrained are very structural.
+The properties describing a simple constraint are very structural\tb{Kai, do you mean structured?}.
 The central property is the \emph{constraining element} which refers to one of 103 constraining elements described in our technical report \cite{BoschNolleAcarEckert2015}.
-Constraining elements are for example taken from Description Logics, another concrete example would be REGEX where a regular expression is checked against some property value.
+Constraining elements are for example taken from Description Logics, another concrete example would be the SPARQL function REGEX where a regular expression is checked against some property value.
 In most cases, constraining elements directly correspond to a constraint type, sometimes (as for REGEX) they are shared by several constraint types.
@@
 \emph{leftProperties} and \emph{rightProperties} are lists usually containing properties the constraint is applied to.
-A typical example for a constraint with a right hand side list of properties would be R43, literal value comparison, where constraints like birthDate $<$ deathDate can be expressed.
-
+A typical example for a constraint type with a right hand side list of properties would be \emph{literal value comparison (R-43)}, where constraints like {\small\ms{birthDate $<$ deathDate}} can be expressed.
 Finally, the \emph{constraining value} contains a literal value to be checked against; for instance in the case of the REGEX element, it contains the regular expression to be evaluated.

### 2015-07-18 paper/paper 2/dc-2015.tex
3.1

@@
 
-A cornerstone of the framework is the generic representation of a constraint, which can often be done using \emph{Description Logics (DL)} \cite{Kroetzsch2012,Baader-2003,Baader-Nutt-2003}, as for the \emph{minimum qualified cardinality restrictions}: {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person.}}  This way, the knowledge representation formalism DL with its well-studied theoretical properties provides the foundational basis for the framework.
+A cornerstone of the framework is the generic representation of a constraint, which can often be done using Description Logics, as for the \emph{minimum qualified cardinality restriction} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person.}}  This way, the knowledge representation formalism \emph{Description Logics (DL)} \cite{Kroetzsch2012,Baader-2003,Baader-Nutt-2003} with its well-studied theoretical properties provides the foundational basis for the framework.
 

### 2015-07-18 paper/paper 2/dc-2015.tex
3.4

@@
 
-For the purpose of a consistent implementation and transformation of constraints, constraints are semantically equivalent  
-if they detect the same set of violations regardless of RDF data, 
-which means whenever the constraints are applied to any RDF data they point out the same violations.
+For the purpose of a consistent implementation and transformation of constraints, constraints are \emph{semantically equivalent} if they detect the same set of violations regardless of RDF data, which means whenever the constraints are applied to any RDF data they point out the same violations.
 
@@
 The \emph{context class} limits the constraint to individuals of a specific class.
-As the \emph{property path} constraint holds for all individuals within the data, the context class is set to the \emph{DL top concept} $\top$ which stands for the super-class of all possible classes.
+\tb{ToDo: A context class may be an RDFS class, an OWL class, or an RDFS datatype as...} As the \emph{property path} constraint holds for all individuals within the data, the context class is set to the \emph{DL top concept} $\top$ which stands for the super-class of all possible classes.
 \begin{table}[H]
@@
 
-If a language developer would like to use the framework for the implementation of a constraint language, the process is straight-forward.
+If a language developer would like to use the framework for the implementation of a constraint language or individual language constructs, the process is straight-forward.
 For a language construct, the corresponding constraint type has to be identified.
-Again we use the \emph{minimum qualified cardinality restriction (R-75)} type which is supported in OWL 2:
+Again we use the constraint {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}} of the type \emph{minimum qualified cardinality restrictions (R-75)} which is supported in OWL 2:
 
@@
 
-From Table~\ref{tab:property-constraint-cardinality-restriction}, we know the representation in our framework, which corresponds to the following 
-RDF representation using RDF-CV:
+From Table~\ref{tab:property-constraint-cardinality-restriction}, we know the representation in our framework, which corresponds to the following RDF representation using the RDF-CV:
 
@@
 
-The mapping simply constructs this representation out of the OWL 2 representation using a SPARQL CONSTRUCT query:
+The mapping simply constructs this generic representation out of the specific OWL 2 representation using a SPARQL CONSTRUCT query:
 
@@
 
-SPIN is used to execute the mapping, the property \emph{spin:rule} links an rdfs:Class with SPARQL CONSTRUCT queries.
+The SPIN engine is used to execute the mapping, the property \emph{spin:rule} links an rdfs:Class with SPARQL CONSTRUCT queries.
 Each query defines an inference rule that is applied to all instances of the associated class and its subclasses.
@@
 
-The framework is implemented in exactly the same way by providing another mapping to create the actual SPIN/SPARQL query that validates the constraints and produces constraint violation messages if a constraint is violated, as described in our previous paper about the DSP implementation \cite{BoschEckert2014-2}.\footnote{At the time of this writing, not all mappings for the constraint types are implemented, but of course the implementations can be complemented and adapted to own requirements, as needed.
-The most recent implementation can be found here: \url{https://github.com/boschthomas/rdf-validation/blob/master/SPIN/RDF-CV-2-SPIN.ttl}.}
+The framework and therefore the constraint types are implemented in exactly the same way by providing other SPIN mappings which encompass the SPIN/SPARQL queries that validate constraints and produce constraint violation messages if a constraint is violated, as described in our previous paper about the DSP implementation \cite{BoschEckert2014-2}\footnote{At the time of this writing, not all mappings for the constraint types are implemented, but of course the implementations can be complemented and adapted to own requirements, as needed.
+The most recent implementation can be found here: \url{https://github.com/boschthomas/rdf-validation/blob/master/SPIN/RDF-CV-2-SPIN.ttl}}.
 

### 2015-07-18 paper/paper 2/dc-2015.tex
3.5

@@
 As stated in Section~\ref{sec:motivation}, we see a huge potential in the possibility to transform semantically equivalent constraints from one high-level constraint language to another via the RDF-CV representation, to avoid that every possible combination of constraint languages has to be mapped separately.
-The following SPIN inference rule exemplifies this approach and provides a mapping from RDF-CV back to an OWL 2 constraint:
+The following SPIN inference rule exemplifies this approach and provides a mapping from RDF-CV back to the OWL 2 constraint of the type \emph{minimum qualified cardinality restrictions}:
 

### 2015-07-20 paper/paper 2/dc-2015.tex
3.5
formal spec of RDF-CV

@@
 
-\title{\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.}
+\title{\vspace{-1em}Guidance, Please! Towards a Framework for RDF-based Constraint Languages.}
 
@@
 The only limitations are that the constraints have to
-be expressed in RDF and that the constraint language is expressable in SPARQL.
+be expressed in RDF and that the constraint language is expressible in SPARQL.
 
@@
 
-At the core, we use a very simple conceptual model for constraints (see Figure \ref{fig:RDF-CV-conceptual-model}), using a small lightweight vocabulary called \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.\tb{ToDo for Thomas: actualize vocabulary}
+At the core, we use a very simple conceptual model for constraints (see Figure \ref{fig:RDF-CV-conceptual-model}), using a small lightweight vocabulary called \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Formal specification and HTML documentation online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}}.
 \begin{figure}[H]
@@
 The \emph{context class} limits the constraint to individuals of a specific class.
-\tb{ToDo: A context class may be an RDFS class, an OWL class, or an RDFS datatype as...} As the \emph{property path} constraint holds for all individuals within the data, the context class is set to the \emph{DL top concept} $\top$ which stands for the super-class of all possible classes.
+A context class may be an rdfs:Class, an owl:Class (as sub-class of rdfs:Class), or an rdfs:Datatype which is both an instance of and a sub-class of rdfs:Class.
+As the \emph{property path} constraint holds for all individuals within the data, the context class is set to the \emph{DL top concept} $\top$ which stands for the super-class of all possible classes.
 \begin{table}[H]
@@
 
-In this paper, we outlined our idea of a general framework to support the mapping of high-level constraint languages to a generic representation, which subsequently can be used to generate validating SPIN/SPARQL queries to actually validate data against constraints provided in the high-level language.\tb{I do not understand this!} The framework consists of a very simple conceptual model using the \emph{RDF Constraints Vocabulary (RDF-CV)} which has been introduced in this paper.
+In this paper, we outlined our idea of a general framework to support the mapping of high-level constraint languages to a generic representation, which subsequently can be used to generate validating SPIN/SPARQL queries to actually validate data against constraints provided in the high-level language.\tb{Aus der generischen Repräsentierung können die SPIN mappings zur Validierung generiert werden?
+das verstehe ich nicht} The framework consists of a very simple conceptual model using the \emph{RDF Constraints Vocabulary (RDF-CV)} which has been introduced in this paper.
 The core of the framework is the definition of 103 constraining elements that are used to define constraints of all 81 constraint types that to date have been identified within the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group.

### 2015-07-20 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
evaluation completes, conclusion

@@
 particularly as this is taken for granted in the XML world.
-Based on our work in the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group, we identified and published by today 82 types of constraints that are required by various stakeholders for data applications.
-In this paper, we formulate 213 constraints of 53 different types on three different vocabularies (DDI-RDF, QB, and SKOS) and classify them according to the complexity level of their type and their severity level.
-For 115 of these constraints, we evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
-Based on the results, we formulate several hypotheses to direct the further development of constraint languages.\textcolor{red}{81 constraint types instead of 82?}
+Based on our work in the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group, we identified and published by today 81 types of constraints that are required by various stakeholders for data applications.
+In this paper, we formulate 115 constraints on three different vocabularies (DDI-RDF, QB, and SKOS) and classify them according to their severity level and whether their type is expressible by different types of constraint languages.
+We evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic sciences obtained from 33 SPARQL endpoints.
+Based on the results, we formulate several hypotheses to direct the further development of constraint languages.
 \end{abstract}
@@
 
-Within the DCMI task group, a collaboratively curated database of RDF validation requirements has been created which contains the findings of the working groups based on various case studies provided by data institutions \cite{BoschEckert2014}.
+Within the DCMI task group, a collaboratively curated database of RDF validation requirements has been created which contains the findings of the working groups based on various case studies provided by data institutions \cite{BoschEckert2014} \tb{bibliography error}.
 It is publicly available and open for further contributions\footnote{Online at \url{http://purl.org/net/rdf-validation}}.
 The database connects requirements to use cases, case studies and implementations and forms the basis of this paper. 
-We distinguish 82 requirements to formulate RDF constraints; 
+We distinguish 81 requirements to formulate RDF constraints; 
 each of them corresponding to an RDF constraint type.
@@
 
-A very important and representative RDF validation case study within SBE sciences is the comparison of variables between data collections of different countries.
+A very important and representative RDF validation case study within \emph{SBE} sciences is the comparison of variables between data collections of different countries.
 Several vocabulary-specific constraints on RDF data are checked for each data collection
@@
 enabling researchers to replicate the results shown in aggregated data tables.
-The \emph{DDI-RDF DDI-RDFvery Vocabulary (DDI-RDF)} is a vocabulary to represent metadata on person-level data in RDF.
+The \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)} is a vocabulary to represent metadata on person-level data in RDF.
 The series (\emph{DDI-RDF:StudyGroup}) \emph{EU-SILC} contains one study (\emph{DDI-RDF:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
@@
 
-To gain better insights into the role that certain types of constraints play for the quality of RDF data, we use two simple classifications: on the one hand, we classify RDF constraint types whether they are expressible by different types of constraint languages and on the other hand, we classify concrete constraints formulated for a given vocabulary according to the perceived severity of a violation.
-
-Within the working groups, we identified by today 82 requirements to formulate RDF constraints (e.g., \emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}.
-Within a technical report serving as first appendix of this paper we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages \cite{BoschNolleAcarEckert2015}.
-We provide mappings to representations in description logics (DL) \cite{Baader-2003} to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type.
-
-%In total, we distinguish 82 RDF constraint types as we identified 6 RDF constraint types which are only necessary for validating particular vocabularies.
-
+To gain better insights into the role that certain types of constraints play for the quality of RDF data, we use two simple classifications: on the one hand, we classify RDF constraint types whether they are expressible by different types of constraint languages and on the other hand, we classify constraints formulated for a given vocabulary according to the perceived severity of its violation.
+
+Within the working groups, we identified by today 81 requirements to formulate RDF constraints (e.g., \emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}.
+Within a technical report, we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages \cite{BoschNolleAcarEckert2015}.
+We provide mappings to representations in Description Logics (DL) \cite{Baader-2003} to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type.
+%In total, we distinguish 81 RDF constraint types as we identified 6 RDF constraint types which are only necessary for validating particular vocabularies.
 %Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
-
-The classification of the 115 concrete constraints on three vocabularies according to severity levels is published in a second technical report serving as second appendix of this paper \cite{BoschZapilkoWackerowEckert2015}.
+The classification of the 115 concrete constraints on three vocabularies according to severity levels is published in a technical report \cite{BoschZapilkoWackerowEckert2015}.
 In the following, we summarize the results for the purpose of our evaluation.
@@
 
-According to the expressivity of constraint languages, the complete set of \emph{constraint types} encompasses three not disjoint \emph{sets of constraint types}:
+According to the expressivity of constraint languages, the complete set of constraint types encompasses three not disjoint sets of constraint types:
 \begin{enumerate}
@@
 The modeling languages RDFS and OWL are typically used to formally specify vocabularies.
-\emph{RDFS/OWL Based} denotes the set of constraint types which can be formulated with RDFS/OWL constructs using CWA/UNA semantics (without reasoning) and which are therefore commonly found within formal specifications of vocabularies.
+\emph{RDFS/OWL Based} denotes the set of constraint types which can be formulated with RDFS/OWL constructs using CWA/UNA semantics without reasoning and which are therefore commonly found within formal specifications of vocabularies.
 We determined this set based on the evaluation of the three vocabularies.
@@
 Constraints of the constraint type \emph{minimum qualified cardinality restrictions} (\emph{R-74}), e.g., guarantee that individuals of given classes are connected by particular properties to at least n different individuals/literals of certain classes or data ranges.
-In \emph{PHDD}, a \emph{minimum qualified cardinality restriction} can be obtained from a respective OWL axiom which ensures that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:
+For \emph{DDI-RDF}, a \emph{minimum qualified cardinality restriction} can be obtained from a respective OWL axiom which ensures that a \emph{disco:Questionnaire} has (\emph{disco:question}) at least one \emph{disco:Question}:
 \begin{ex}
-[   a owl:Restriction ; rdfs:subClassOf TableStructure ;
+[   a owl:Restriction ; rdfs:subClassOf Questionnaire ;
     owl:minQualifiedCardinality 1 ;
-    owl:onProperty column ;
-    owl:onClass Column ] .
+    owl:onProperty question ;
+    owl:onClass Question ] .
 \end{ex}
 
+%In \emph{PHDD}, a \emph{minimum qualified cardinality restriction} can be obtained from a respective OWL axiom which ensures that a \emph{phdd:TableStructure} has (\emph{phdd:column}) at least one \emph{phdd:Column}:
+%\begin{ex}
+%[   a owl:Restriction ; rdfs:subClassOf TableStructure ;
+    %owl:minQualifiedCardinality 1 ;
+    %owl:onProperty column ;
+    %owl:onClass Column ] .
+%\end{ex}
+
 \emph{Constraint Language Based} and \emph{SPARQL Based} constraints are in contrast to \emph{RDFS/OWL Based} constraints usually not (yet) explicitly defined within formal specifications of vocabularies.
-Instead, they are often defined in textual descriptions of the vocabularies.
+Instead, they are often defined within textual descriptions of vocabularies.
 Additionally, we let our domain and data experts define constraints when they agreed that violating the constraint would affect the usefulness of the data.
@@
 There is a strong overlap between \emph{RDFS/OWL Based} and \emph{Constraint Language Based} constraint types as in many cases constraint types are expressible by classical constraint languages and OWL.
-SPARQL, however, is considered as a low-level implementation language in this context, not as a high-level constraint language.
-
-\textcolor{red}{example}
+SPARQL, however, is considered as a low-level implementation language in this context.
+In contrast to SPARQL, high-level constraint languages are comparatively easy to understand and constraints can be formulated more concisely.
+Declarative languages may be placed on top of SPARQL when using it as an implementation languages.
+For these \emph{Constraint Language Based} constraints, we expect a straight-forward support in future constraint languages.
+
+\emph{Context-specific exclusive or of property groups} (\emph{R-11}) is a constraint type which can be formulated by a high-level constraint language.
+Constraints of this type restrict individuals of given classes to have properties defined within exactly one of multiple mutually exclusive property groups.
+\emph{skos:Concept}s, e.g., can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes), but not both:
+%(\emph{error}).
+
+\begin{ex}[commandchars=\\\{\}]
+\textit{ShEx:} Concept \{ 
+    ( definition string ) |
+    ( notation string , prefLabel string ) \}
+\end{ex}
 
@@
 %\end{ex}
-For these constraints, we expect a straight-forward support in future constraint languages.
 
 %\emph{Complex constraint types} encompass constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
-\emph{SPARQL Based} encompass constraint types that are not expressible by RDFS/OWL or common constraint languages but by plain SPARQL.
+The set \emph{SPARQL Based} encompasses constraint types that are not expressible by RDFS/OWL or common constraint languages but by plain SPARQL.
 For assessing the quality of thesauri, e.g., we concentrate on the graph-based structure and apply graph- and network-analysis techniques.
@@
 a thesaurus should not contain many orphan concepts, i.e., concepts without any associative or hierarchical relations, lacking context information valuable for search.
-This \emph{complex constraint} is only expressible by SPARQL and not directly understandable:
+As the complexity of this constraint is relatively high, it is only expressible by SPARQL and not directly understandable:
 \begin{ex}
@@
         FILTER ( ?p IN ( skos:related, skos:relatedMatch, 
-                         skos:broader, ... ) ) . }
+                         skos:broader, ... ) ) . } }
 \end{ex}
@@
 
-A concrete constraint is instantiated from one of the 82 constraint types and is defined for a specific vocabulary.
+A concrete constraint is instantiated from one of the 81 constraint types and is defined for a specific vocabulary.
 It does not make sense to determine the severity of constraint violations of an entire constraint type,
@@
 
-Note that there is a correlation between the severity of a constraint and the classification according to the expressivity of constraint languages of its type: \emph{RDFS/OWL Based} constraints are in most cases classified with an \emph{error} level as they typically represent basic and important constraints; there is a reason why they have been included in the vocabulary specification.
-Although, we provide default severity levels for each constraint, validation environments should enable users to adapt the severity levels of constraints according to their individual needs.
+Note that there is a correlation between the severity of a constraint and the classification according to the expressivity of constraint languages of its type: \emph{RDFS/OWL Based} constraints are in many cases classified with an \emph{error} level as they typically represent basic and important constraints; there is a reason why they have been included in the vocabulary specification.
+Although we provide default severity levels for each constraint, validation environments should enable users to adapt the severity constraints' levels according to their individual needs.
 % Validation environments should enable users to select which constraints to validate against depending on their individual use cases.
@@
 
-\textcolor{red}{\emph{Context-specific exclusive or of property groups}} (\emph{R-11}) constraints
-restrict individuals of given classes to have properties defined within exactly one of multiple property groups.
-\emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes), but not both (\emph{error}).
-
 \textcolor{red}{\emph{Default values}} (\emph{R-31, R-38}) for objects/literals of given properties are inferred automatically when properties are not present in the data.
 The value \emph{true} for the property {\em DDI-RDF:isPublic} indicates that a {\em DDI-RDF:LogicalDataSet} can be accessed by anyone.
-Per default, however, access to data sets should be restricted (\emph{false}) ($\mathcal{SL}_{0}$).
+Per default, however, access to data sets should be restricted (\emph{false}) (\emph{informational}).
 Many properties are not necessarily required but \emph{recommended} within a particular context (\emph{R-72}).
-The property {\em skos:notation}, e.g., is not mandatory for {\em DDI-RDF:Variable}s, but recommended to represent variable names ($\mathcal{SL}_{0}$).
+The property {\em skos:notation}, e.g., is not mandatory for {\em DDI-RDF:Variable}s, but recommended to represent variable names (\emph{informational}).
 
@@
 
-In a technical report serving as third appendix of this paper, we describe the evaluation in further detail \cite{BoschZapilkoWackerowEckert2015-2}.
+In a technical report, we describe the evaluation in further detail \cite{BoschZapilkoWackerowEckert2015-2}.
 Furthermore, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.
@@
 
-%The majority (48 $\equiv$ 58.5\%) of the overall 82 $\mathcal{CT}$ constraint types are $\mathcal{CT}_{B}$ whose constraints can therefore be derived from vocabularies without any effort.
+%The majority (48 $\equiv$ 58.5\%) of the overall 81 $\mathcal{CT}$ constraint types are $\mathcal{CT}_{B}$ whose constraints can therefore be derived from vocabularies without any effort.
 %Among $\mathcal{CT}_{B}$, two-thirds (34 $\equiv$ 70.8\%) are $\mathcal{C}_B ^{\mathcal{R}}$, i.e., constraint types for which reasoning may be performed prior to validation, and one third (14 $\equiv$ 29.2\%) are $\overline{\mathcal{C}_B ^{\mathcal{R}}}$, i.e., constraint types for which reasoning does not make any sense.
@@
 The first numbers indicate the absolute amount of constraints and violations.
-The constraints and their raised violations are grouped by vocabulary, by which languages constraints are expressed, and their severity level.
+The constraints and their raised violations are grouped by vocabulary, which type of language the constraints are expressed with, and their severity level.
 The numbers of evaluated triples and data sets differ between the vocabularies
@@
 To be able to formulate hypotheses which apply for all vocabularies, 
-we only use normalized relative values representing the percentage of constraints and violations belonging to the respective class.
+we only use normalized relative values representing the percentage of constraints and violations belonging to the respective set of constraint types.
 
@@
 by evaluating the quality of data represented by further well-established and newly developed vocabularies.
-
-\textcolor{red}{wurden die severity levels der constraints korrekt ausgezählt?}
 
@@
 \begin{hyp}
-The facts that 80\% of all violations are raised by \emph{SPARQL Based} constraints and that 2/3 of all constraints are SPARQL Based, increases the importance for constraint languages to enable to express SPARQL Based constraints.
-Thus, the further development of constraint languages especially concentrates on expressing SPARQL Based constraints as data quality can be significantly improved when suitable constraint languages are developed which enable to define \emph{SPARQL Based} constraints in an easy, concise, and intuitive way.
-The more elaborate a vocabulary is, the more sophisticated and complex constraints are specified using SPARQL.
+The facts that 80\% of all violations are raised by SPARQL Based constraints and that 2/3 of all constraints are SPARQL Based, increases the importance to formulate constraints, which up to now can only be expressed in SPARQL, using high-level constraint languages.
+Data quality can be significantly improved when suitable constraint languages are developed which enable to define SPARQL Based constraints in an easy, concise, and intuitive way.
+Thereby, the more elaborate a vocabulary is, the more sophisticated and complex constraints are specified using SPARQL.
 \end{hyp}
@@
 
-Nearly 1/3 of all constraints are either \emph{RDFS/OWL} or \emph{Constraint Language Based}.
+%Nearly 1/3 of all constraints are either \emph{RDFS/OWL} or \emph{Constraint Language Based}.
+
+%The fact that only 1/5 of all violations result from \emph{RDFS/OWL Based} constraints, even though 1/3 of all constraints are \emph{RDFS/OWL Based}, indicates good data quality for all vocabularies with regard to their formal specifications.
 
 \begin{hyp}
-The first step to make progress in the further development of constraint languages is to cover the constraint types which can already be formulated using RDFS and OWL.
+The fact that only 1/5 of all violations result from RDFS/OWL Based constraints, even though 1/3 of all constraints are RDFS/OWL Based, indicates good data quality for all vocabularies with regard to their formal specifications.
+%Data corresponds to formal specifications of vocabularies the data is conforming to. 
+%This demonstrates that constraint formulation in general works. 
 \end{hyp}
 
-The fact that only 1/5 of all violations result from \emph{RDFS/OWL Based} constraints, even though, 1/3 of all constraints are \emph{RDFS/OWL Based}, indicates good data quality for all vocabularies with regard to their formal specifications.
-
 \begin{hyp}
-Data corresponds to formal specifications of vocabularies the data is conforming to. 
-%This demonstrates that constraint formulation in general works. 
+As 1/3 of all constraints are RDFS/OWL Based, the first step to make progress in the further development of constraint languages is to cover the constraint types which can already be formulated using RDFS and OWL.
 \end{hyp}
@@
 QB and SKOS violations are only raised by \emph{SPARQL Based} constraints.
-This means that for well-established vocabularies, \emph{RDFS/OWL Based} constraints are almost completely satisfied which indicates generally a very impressive data quality, at least in the \emph{SBE} domain and for the basic requirements.
-%This demonstrates that data providers take account of the formal specifications of well-established vocabularies.
-For DDI-RDF, data providers still have to understand the vocabulary and of course, data can not have high quality if the specification is not yet stable.
 
 \begin{hyp}
-For well-established vocabularies, RDFS/OWL Based constraints are almost completely satisfied which indicates good data quality in general and that basic data quality requirements are met.
+For well-established vocabularies, RDFS/OWL Based constraints are almost completely satisfied which indicates generally a very impressive data quality, at least in the SBE domain and for the basic requirements.
 For newly developed vocabularies, however, data quality is poor as RDFS/OWL Based constraints are not fulfilled.
@@
 
+For DDI-RDF, data providers still have to understand the vocabulary and of course, data can not have high quality if the specification is not yet stable.
 It is likely that a newly developed vocabulary is still subject of constant change
@@
 
-50\% of all constraints are \emph{error}, 40\% are \emph{informational}, and 10\% are \emph{warning} constraints.
-\emph{Informational} constraints caused 1/3 and
-\emph{warning} constraints 2/3 of all violations.
+Almost 40\% of all constraints are \emph{error}, more than 40\% are \emph{informational}, and nearly 20\% are \emph{warning} constraints.
+\emph{Informational} constraints caused almost 1/3 and
+\emph{warning} constraints narrowly 2/3 of all violations.
 %As the percentage of severe violations is very low for all vocabularies (6.1\%),
@@
 \begin{hyp}
-Although, 1/2 of all constraints are error constraints, the percentage of severe violations is very low, compared to about 2/3 of warning and 1/3 of informational violations.
-This implies data quality is high with regard to the severity level of constraints and that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
+Although 40\% of all constraints are error constraints, the percentage of severe violations is very low, compared to about 2/3 of warning and 1/3 of informational violations.
+This implies that data quality is high with regard to the severity level of constraints and that proper constraint languages can significantly improve data quality beyond fundamental requirements.
 \end{hyp}
 
-80\% of the QB constraints are \emph{error} constraints.
+85\% of the QB constraints are \emph{error} constraints.
 More than 50\% of the DDI-RDF and SKOS constraints, however, are \emph{informational} constraints.
@@
 \begin{hyp}
-For well-established vocabularies, data quality is high as serious violations rarely appear. For newly developed vocabularies, data quality is worse as serious violations occur partially.   
+For well-established vocabularies, data quality is high as serious violations rarely appear. For newly developed vocabularies, however, data quality is worse as serious violations occur partially.   
 \end{hyp}
 
-Especially for newly developed vocabularies, constraint languages should be used to a larger extend to reduce severe violations.
+Especially for newly developed vocabularies, constraint languages should be used to a larger extend to define appropriate constraints in order to detect and solve severe violations.
+%to reduce severe violations by checking and solving them.
 
@@
 \begin{hyp}
-Independent which language is used to formulate constraints, 1/2 of all constraints are informational, 1/3 are error, and 1/5 are warning constraints. 
+Whatever language is used to formulate constraints, 1/2 of all constraints are informational, 1/3 are error, and 1/5 are warning constraints. 
 %Thereby, it does not matter which language is used to formulate constraints.
-Constraints expressed by RDFS/OWL or high-level constraint languages are of low severity, whereas the violation of constraints formulated by SPARQL is more serious.
-There is a significant demand for constraint languages that support the expression of SPARQL Based constraints as 94\% of all violations are caused by SPARQL Based constraints whose severity level is warning.
+Violations caused by constraints expressed by RDFS/OWL or high-level constraint languages are of low severity, whereas the violation of constraints formulated by SPARQL is more serious.
+There is a significant demand for languages that support the expression of SPARQL Based constraints as 94\% of all violations are caused by these constraints whose severity level is warning.
 \end{hyp}
@@
 SPARQL seems to be used to formulate constraints whose violation is of higher severity than the violation of constraints expressed by either RDFS/OWL or high-level constraint languages.
-This is a surprising finding as the violation of \emph{RDFS/OWL Based} constraints should be of higher severity since these constraints may be part of vocabularies' formal specifications.
+This is a surprising finding as the violation of \emph{RDFS/OWL Based} constraints should be of higher severity than \emph{informational} since these constraints are expected to be basic constraints as they are in many cases part of vocabularies' formal specifications.
+%and (2)
+%the purpose of high-level constraint languages should be to enable to define constraints of higher severity than \emph{informational}.
 
@@
 
-We identified and published by today 82 types of constraints  that are required by various stakeholders for data applications.
-In close collaboration with several \emph{SBE} domain experts, we formulated 213 constraints of 53 different types on three different vocabularies (DDI-RDF, QB, and SKOS) and classified them according to the complexity level of their type and their severity level.
-
-For 115 of these constraints, we evaluated  the data quality of 15,694 data sets (4.26 billion triples) of research data for the \emph{SBE} sciences obtained from 33 SPARQL endpoints.
+We identified and published by today 81 types of constraints  that are required by various stakeholders for data applications.
+In close collaboration with several domain experts for the social, behavioural, and economic sciences (\emph{SBE}), we formulated 115 constraints on three different vocabularies (DDI-RDF, QB, and SKOS) and classified them according to their severity level and  whether their type is expressible by different types of constraint languages - RDFS/OWL, high-level constraint languages, and SPARQL.
+We evaluated  the data quality of 15,694 data sets (4.26 billion triples) of research data for the \emph{SBE} sciences obtained from 33 SPARQL endpoints.
 
@@
 We regard to the results as hypotheses, as their general applicability beyond the examined vocabularies and for other domains is still to be confirmed.
-
 The main hypotheses are:
+
 \begin{enumerate}
-	\item The percentage of severe violations is very low which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
-  \item The further development of constraint languages should concentrate on how to express \emph{complex constraints} as 44\% of all \emph{complex constraints} are also serious ones.
-  \item 47\% of the violations refer to complex constraints that are in most cases not expressible by existing constraint languages which confirms the necessity to provide suitable constraint languages.
-  \item As 54\% of the constraints are either \emph{simple} or \emph{complex constraints},
-the further development of constraint languages should concentrate on expressing \emph{simple} and especially \emph{complex constraints} which up to now in most cases can only be expressed by plain SPARQL.
+\item
+\emph{Data quality can be significantly improved when suitable constraint languages are developed which enable to define 
+constraints, which up to now can only be expressed by plain SPARQL, in an easy, concise, and intuitive way.
+Thereby, the more elaborate a vocabulary is, the more sophisticated and complex constraints are specified using SPARQL.}
+\item
+\emph{The fact that only 1/5 of all violations result from RDFS/OWL Based constraints, even though 1/3 of all constraints are RDFS/OWL Based, indicates good data quality for all vocabularies with regard to their formal specifications.}
+\item
+\emph{Although 40\% of all constraints are error constraints, the percentage of severe violations is very low, compared to about 2/3 of warning and 1/3 of informational violations.
+This implies that data quality is high with regard to the severity level of constraints and that proper constraint languages can significantly improve data quality beyond fundamental requirements.}
+\item
+\emph{Whatever language is used to formulate constraints, 1/2 of all constraints are informational, 1/3 are error, and 1/5 are warning constraints. 
+Violations caused by constraints expressed by RDFS/OWL or high-level constraint languages are of low severity, whereas the violation of constraints formulated by SPARQL is more serious.
+There is a significant demand for languages that support the expression of SPARQL Based constraints causing 94\% of all violations.}
 \end{enumerate}
+
+%\begin{enumerate}
+	%\item The percentage of severe violations is very low which implies that proper constraint languages can significantly improve the data quality beyond fundamental requirements.
+  %\item The further development of constraint languages should concentrate on how to express \emph{complex constraints} as 44\% of all \emph{complex constraints} are also serious ones.
+  %\item 47\% of the violations refer to complex constraints that are in most cases not expressible by existing constraint languages which confirms the necessity to provide suitable constraint languages.
+  %\item As 54\% of the constraints are either \emph{simple} or \emph{complex constraints},
+%the further development of constraint languages should concentrate on expressing \emph{simple} and especially \emph{complex constraints} which up to now in most cases can only be expressed by plain SPARQL.
+%\end{enumerate}
 
@@
 This is in contrast to the sometimes heard rumour that Linked Open Data lacks quality.
-We are actively involved in the further development and implementation of constraint languages and will use the results presented in the paper to set priorities on features where we expect the highest impact on the data quality of real-life data in the SBE domain.
+We are actively involved in the further development and implementation of constraint languages and will use the results presented in the paper to set priorities on features where we expect the highest impact on the data quality of real-life data in the \emph{SBE} domain.
 

### 2015-07-21 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
classification

@@
 \textbf{\emph{RDFS/OWL Based} constraint types.}
-\textcolor{red}{severity levels assigned for each constraint?}
 It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values (\emph{R-30/37: allowed values}):
@@
 \emph{xsd:string}).
-\emph{DDI-RDF:CategoryStatistics}, e.g., can only have \emph{DDI-RDF:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString} (default severity level: \emph{error}).
+\emph{disco:CategoryStatistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString} (default severity level: \emph{error}).
 %Validation should \emph{exploit sub-super relations} in vocabularies (\emph{R-224}).
@@
 %which may indicate when the data is verbose/redundant or expressed at a too general level.
-Consider the following \emph{DL knowledge base} $\mathcal{K}$\footnote{A \emph{DL knowledge base} is a collection of formal statements which corresponds to \emph{facts} or what is known explicitly.
+Consider the following \emph{DL knowledge base} $\mathcal{K}$\footnote{A \emph{DL knowledge base} is a collection of formal statements which correspond to \emph{facts} or what is known explicitly.
 For simplicity reasons, we do not state namespace prefixes.}:
@@
 %\end{DL}
-Only \emph{dcat:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets} (\emph{error}).
+Only \emph{\textcolor{red}{dcat}:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets} (\emph{error}).
 \emph{Property domains} (\emph{R-25, R-26}) and \emph{property ranges} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties:
-Only \emph{phdd:Tables}, e.g., can have \emph{phdd:isStructuredBy} relationships and
-\emph{xkos:belongsTo} relations (\emph{error}) can only point to \emph{skos:Concepts} (\emph{error}).
+Only \emph{phdd:Tables}, e.g., can have \emph{\textcolor{red}{phdd}:isStructuredBy} relationships (\emph{error}) and \emph{\textcolor{red}{xkos}:belongsTo} relations can only point to \emph{skos:Concepts} (\emph{error}).
+
+It is often useful to declare a given (data) property as the \emph{primary key} (\emph{R-226}) of a class, so that a system can enforce uniqueness and build URIs from user inputs and imported data. 
+In DDI-RDF, resources are uniquely identified by the property \emph{adms:identifier},
+which is therefore inverse-functional $({\small\ms{funct identifier}\sp{\overline{\ }}})$,
+i.e., for each \emph{rdfs:Resource x}, there can be at most one distinct resource \emph{y} such that \emph{y} is connected by \emph{adms:identifier$\sp{\overline{\ }}$} to \emph{x} (\emph{error}).
+%\begin{DL}
+%$(\ms{funct identifier}\sp{\overline{\ }})$
+%\end{DL} 
+Keys, however, are even more general than \emph{inverse-functional properties} (\emph{R-58}),
+as a key can be a data property, an object property, or a chain of properties \cite{Schneider2009}.
+Thus and as there are different sorts of key, and as keys can lead to undecidability, 
+DL is extended with the construct \emph{keyfor} ({\small\ms{identifier \ms{keyfor} Resource}}) \cite{Lutz2005} which is implemented by the \emph{OWL 2} \emph{hasKey} construct.
+
 %\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals/literals of certain types.
@@
 %{Simple constraint types} is the set of constraint types whose constraints can be easily defined without much effort in addition to $\mathcal{CT}_{B}$ constraints.
-For data properties, it may be desirable to restrict that values of predefined languages must be present for determined number of times (\emph{R-48/49: language tag cardinality}):
-(1) It is checked if literal language tags are set.
-Some controlled vocabularies, e.g., contain literals in natural language, but without information what language has actually been used (\emph{warning}).
-(2) Language tags must conform to language standards (\emph{error}). 
-(3) Some thesaurus concepts are labeled in only one, others in multiple languages. 
-It may be desirable to have each concept labeled in each of the languages that are also used on the other concepts,
-as language coverage incompleteness for some concepts may indicate shortcomings of thesauri (\emph{informational})
-\cite{MaderHaslhoferIsaac2012}.
 %\textbf{Validation and Reasoning.}
 
-\textcolor{red}{\emph{Default values}} (\emph{R-31, R-38}) for objects/literals of given properties are inferred automatically when properties are not present in the data.
-The value \emph{true} for the property {\em DDI-RDF:isPublic} indicates that a {\em DDI-RDF:LogicalDataSet} can be accessed by anyone.
+Depending on property datatypes, two different literal values have
+a specific ordering with respect to operators like \textless  (\emph{R-43: literal value comparison}).
+Start dates (\emph{disco:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{disco:endDate}).
+
+%Percentage values are only valid when they are within the literal range of 0 and 100 (\emph{R-45: literal ranges}; \emph{error})
+%which is checked for \emph{DDI-RDF:percentage} standing for the number of cases of a given code in relation to the total number of cases for a particular variable.
+
+In many cases, resources must be \emph{members of controlled vocabularies} (\emph{R-32}).
+If a QB dimension property, e.g., has a \emph{qb:codeList},
+then the value of the dimension property on every \emph{qb:Observation} must be in the code list (\emph{error}).
+
+\emph{Default values} (\emph{R-31, R-38}) for objects/literals of given properties are inferred automatically when properties are not present in the data.
+The value \emph{true} for the property {\em disco:isPublic} indicates that a {\em disco:LogicalDataSet} can be accessed by anyone.
 Per default, however, access to data sets should be restricted (\emph{false}) (\emph{informational}).
-Many properties are not necessarily required but \emph{recommended} within a particular context (\emph{R-72}).
-The property {\em skos:notation}, e.g., is not mandatory for {\em DDI-RDF:Variable}s, but recommended to represent variable names (\emph{informational}).
-
-Depending on property datatypes, two different literal values have
-a specific ordering with respect to operators like \textless  (\textcolor{red}{\emph{R-43: literal value comparison}}).
-Start dates (\emph{DDI-RDF:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{DDI-RDF:endDate}).
-
-Percentage values are only valid when they are within the literal range of 0 and 100 (\emph{R-45: literal ranges}; \emph{error})
-which is checked for \emph{DDI-RDF:percentage} standing for the number of cases of a given code in relation to the total number of cases for a particular variable.
+
+%Many properties are not necessarily required but \emph{recommended} within a particular context (\emph{R-72}).
+%The property {\em skos:notation}, e.g., is not mandatory for {\em disco:Variable}s, but recommended to represent variable names (\emph{informational}).
 
@@
 
-It is often useful to declare a given (data) property as the \emph{primary key} (\emph{R-226}) of a class, so that a system can enforce uniqueness and build URIs from user inputs and imported data. 
-In DDI-RDF, resources are uniquely identified by the property \emph{adms:identifier},
-which is therefore inverse-functional $({\small\ms{funct identifier}\sp{\overline{\ }}})$,
-i.e., for each \emph{rdfs:Resource x}, there can be at most one distinct resource \emph{y} such that \emph{y} is connected by \emph{adms:identifier$\sp{\overline{\ }}$} to \emph{x} (\emph{error}).
-%\begin{DL}
-%$(\ms{funct identifier}\sp{\overline{\ }})$
-%\end{DL} 
-Keys, however, are even more general than \emph{inverse-functional properties} (\emph{R-58}),
-as a key can be a data property, an object property, or a chain of properties \cite{Schneider2009}.
-Thus and as there are different sorts of key, and as keys can lead to undecidability, 
-DL is extended with the construct \emph{keyfor} ({\small\ms{identifier \ms{keyfor} Resource}}) \cite{Lutz2005} which is implemented by the \emph{OWL 2} \emph{hasKey} construct.
 %\emph{OWL 2} \emph{hasKey} implements \emph{keyfor} ($\mathcal{SL}_{2}$) and thus can be used to identify resources uniquely, to merge resources with identical key property values, and to recognize constraint violations.
@@
 %\textbf{Membership in Controlled Vocabularies.}
-In many cases, resources must be \emph{members of controlled vocabularies} (\emph{R-32}).
-If a dimension property, e.g., has a \emph{qb:codeList},
-then the value of the dimension property on every \emph{qb:Observation} must be in the code list (\emph{error}).
+
 %Summary statistics types like minimum, maximum, and arithmetic mean are maintained within a controlled vocabulary.  
@@
 The variable \emph{Education at pre-school}, e.g., is represented as ordered code list without any categories.
+
+For data properties, it may be desirable to restrict that values of predefined languages must be present for determined number of times (\emph{R-48/49: language tag cardinality}):
+(1) It is checked if literal language tags are set.
+Some controlled vocabularies, e.g., contain literals in natural language, but without information what language has actually been used (\emph{warning}).
+(2) Language tags must conform to language standards (\emph{error}). 
+(3) Some thesaurus concepts are labeled in only one, others in multiple languages. 
+It may be desirable to have each concept labeled in each of the languages that are also used on the other concepts,
+as language coverage incompleteness for some concepts may indicate shortcomings of thesauri (\emph{informational})
+\cite{MaderHaslhoferIsaac2012}.
+
 %If a {\em skos:Concept} represents a code (having {\em skos:notation} and {\em skos:prefLabel} properties), 

### 2015-07-21 paper/paper 2/dc-2015.tex
Klammer zu viel

@@
 
-At the core, we use a very simple conceptual model for constraints (see Figure \ref{fig:RDF-CV-conceptual-model}), using a small lightweight vocabulary called \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Formal specification and HTML documentation online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}}.
+At the core, we use a very simple conceptual model for constraints (see Figure \ref{fig:RDF-CV-conceptual-model}), using a small lightweight vocabulary called \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Formal specification and HTML documentation online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.
 \begin{figure}[H]

### 2015-07-22 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
introduction

@@
 
-\textcolor{red}{references to constraint languages}
-
-The social, behavioural, and economic sciences (\emph{SBE}) require high-quality data for their empirical research.
-For more than a decade, members of the \emph{SBE} community have been developing and using a
-metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)},
-an XML format to disseminate, manage,
-and reuse data collected and archived for research \cite{Vardigan2008}. 
-%DDI is heavily used by the CESSDA community of European national data archives, 
-%the International Household Survey Network community (made up of more than 90 statistical agencies),
-%and ICPSR - the largest SBE data archive in the US.
-In XML, the definition of schemas containing data constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
-With the rise of the Web of Data, data professionals and institutions are very interested in having their data be DDI-RDFvered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration.
-Therefore, not only established vocabularies like SKOS are used;
-recently, members of the \emph{SBE} and Linked Data community developed with the \emph{DDI-RDF DDI-RDFvery Vocabulary (DDI-RDF)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/DDI-RDFvery.html}} a means to expose \emph{DDI} metadata as Linked Data.
-
-For constraint formulation and validation of RDF data, several languages exist or are currently developed, like \emph{Shape Expressions}, \emph{Resource Shapes} or \emph{Description Set Profiles}.
-\emph{OWL 2} is also used as a constraint language under a closed world assumption.
-With its direct support of validation via SPARQL, SPIN%\footnote{\url{http://spinRDF.org/}}
-is very popular and certainly plays an important role for future developments in this field.
+For constraint formulation and RDF data validation, several languages exist or are currently developed: \emph{Shape Expressions (ShEx)}, \emph{Resource Shapes (ReSh)}, \emph{Description Set Profiles (DSP)}, \emph{OWL 2}, the \emph{SPARQL Inferencing Notation (SPIN)}, and \emph{SPARQL} are the six most promising and widely used constraint languages.
+OWL 2 is used as a constraint language under the closed-world and unique name assumptions.
+The W3C currently develops \emph{SHACL}, an RDF vocabulary for describing RDF graph structures.
+With its direct support of validation via SPARQL, SPIN is very popular and certainly plays an important role for future developments in this field.
 It is particularly interesting as a means to validate arbitrary constraint languages by mapping them to SPARQL \cite{BoschEckert2014-2}.
@@
 In 2013, the W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
-where experts from industry, government, and academia discussed first use cases for RDF constraint formulation and RDF data validation.
+where experts from industry, government, and academia discussed first use cases for constraint formulation and RDF data validation.
 In 2014, two working groups on RDF validation have been established to develop a language to express constraints on RDF data: 
-the W3C RDF Data Shapes working group\footnote{\url{http://www.w3.org/2014/rds/charter}} and the DCMI RDF Application Profiles task group\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}} which among others bundles the requirements of data institutions of the cultural heritage and \emph{SBE} sector and represents them in the W3C group.
-
-Within the DCMI task group, a collaboratively curated database of RDF validation requirements has been created which contains the findings of the working groups based on various case studies provided by data institutions \cite{BoschEckert2014} \tb{bibliography error}.
-It is publicly available and open for further contributions\footnote{Online at \url{http://purl.org/net/rdf-validation}}.
-The database connects requirements to use cases, case studies and implementations and forms the basis of this paper. 
-We distinguish 81 requirements to formulate RDF constraints; 
-each of them corresponding to an RDF constraint type.
+the \emph{W3C RDF Data Shapes Working Group}\footnote{\url{http://www.w3.org/2014/rds/charter}} (33 participants of 19 organizations) and the \emph{DCMI RDF Application Profiles Task Group}\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}} (29 people of 22 organizations) which among others bundles the requirements of data institutions of the cultural heritage sector and the social, behavioural, and economic (\emph{SBE}) sciences and represents them in the W3C group.
+
+Within the DCMI task group, a collaboratively curated database of RDF validation requirements has been created which contains the findings of the working groups based on various case studies provided by data institutions \cite{BoschEckert2014}.
+It is publicly available and open for further contributions\footnote{Online available at \url{http://purl.org/net/rdf-validation}}.
+The database connects requirements to use cases, case studies, and implementations and forms the basis of this paper. 
+We distinguish 81 requirements to formulate constraints on RDF data; 
+each of them corresponding to a constraint type.
 
 To gain a better understanding about the role of certain requirements for data quality and in order to direct the further development of constraint languages, we collected constraints for commonly used vocabularies in the \emph{SBE} domain, either from the vocabularies themselves or from domain and data experts.
-All in all, this lead to 213 constraints of 53 different types on three vocabularies.
-We let the experts classify the constraints according to the severity if they are violated.
-Furthermore, we classified the type of each constraint (corresponding to a requirement) based on its complexity ranging from types commonly found in vocabulary specifications (e.g., domain, range, and cardinality restrictions),
-over types that are simply stated using common constraint languages (e.g., language tag cardinality restrictions) to complex types that involve complex data structures or need more sophisticated languages to be easily expressible
-%(e.g., constraints on network topologies)
-(e.g., constraints on graph-based structures) (Section \ref{classification}).
-
-As we do not want to base our conclusions on the evaluations of vocabularies and constraint definitions alone, we conducted a large-scale experiment.
-For 115 constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (DDI-RDF, QB, SKOS) obtained from 33 SPARQL endpoints.
+All in all, this lead to 115 constraints on three vocabularies.
+We let the experts classify the constraints according to the severity of their violation.
+Furthermore, we classified the type of each constraint based on whether it is expressible by RDFS/OWL, common high-level constraint languages, or only by plain SPARQL (see Chapter \ref{classification}).
+
+As we do not want to base our conclusions on the evaluation of vocabularies and constraint definitions alone, we conducted a large-scale experiment.
+For all these 115 constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (DDI-RDF, QB, SKOS) obtained from 33 SPARQL endpoints.
 %evaluated the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
 Based on the evaluation results,
-we formulated several hypotheses to direct the further development of constraint languages.
+we formulate several hypotheses to direct the further development of constraint languages.
 To make valid general statements for all vocabularies, however,
@@
 %We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
-%how data in tabular format and metadata on person-level data sets, aggregated data sets, and thesauri are represented in RDF, 
+%how data in tabular format and metadata on record-unit data sets, aggregated data sets, and thesauri are represented in RDF, 
 %how therefore reused vocabularies are interrelated (section \ref{rdf-representation}),
@@
 Note that the data represented in RDF can be data in the sense of \emph{SBE} sciences, but also metadata about published or unpublished data.
-We generally refer to both simply as RDF data and only distinguish between data and metadata in the data set descriptions and in the case that it matters for the purpose of this paper.
-The underlying \emph{semantics} for RDF validation is UNA/CWA.
+We generally refer to both simply as RDF data and only distinguish between data and metadata in the data set descriptions.
+%and in the case that it matters for the purpose of this paper.
+
+%We propose an extensible metric to measure the continuum of severity levels to indicate how serious the violation of given constraints is.
+%Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary. 
+%As constraint types are used to define constraints on (meta)data expressed by any vocabulary, the proposed constraint classification can be applied generically, i.e. vocabulary-independent.
+
+\section{Related Work}
+\label{related-work}
+
+%\textbf{XML vs. RDF Validation.}
+For data archives, research institutes, and data libraries,
+RDF validation according to predefined constraints is a much sought-after feature, 
+particularly as this is taken for granted in the XML world.
+DDI-XML documents, e.g., are validated against diverse XSDs\footnote{\url{http://www.ddialliance.org/Specification/}}.
+As certain constraints cannot be formulated and validated by XSDs, 
+so-called secondary-level validation tools like \emph{Schematron}\footnote{\url{https://msdn.microsoft.com/en-us/library/aa468554.aspx}} 
+have been introduced to overcome the limitations of XML validation.
+\emph{Schematron} generates validation rules and validates XML documents according to them.
+With RDF validation, one can overcome drawbacks when validating XML documents\footnote{\url{http://www.xmlmind.com/xmleditor/_distrib/doc/xmltool/xsd_structure_limitations.html}}.
+It cannot be validated, e.g., if each code of a variable's code list is associated with a category (\emph{R-86}) and if an element has a specific value, then certain child elements must be present (\emph{R-71}).
+A comprehensive comparison of XML and RDF validation, however, is not within the scope of this paper.
+
+%validation or relational databases: types, relations
+
+%\textbf{RDF Data Cube Vocabulary.}
+A well-formed \emph{RDF Data Cube} is an a RDF graph describing one or more instances of \emph{qb:DataSet} for which each of the 22 integrity constraints\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf}, defined within the QB specification, passes.
+Each integrity constraint is expressed as narrative prose and, where possible, a SPARQL ASK query or query template. 
+If the ASK query is applied to an RDF graph then it will return true if that graph contains one or more QB instances which violate the corresponding constraint \cite{CyganiakReynolds2014}.
+
+Mader, Haslhofer, and Isaac \cite{MaderHaslhoferIsaac2012} investigated how to support
+taxonomists in improving SKOS vocabularies by pointing out quality
+issues that go beyond the integrity constraints defined in the SKOS specification.
+
+\emph{Stardog ICV} and \emph{Pellet ICV} use OWL 2 constructs to formulate constraints.
+\emph{OWL} in its current version 2 is an expressive language which is based on formal logic and on the subject-predicate-object triples from RDF.
+OWL offers knowledge representation and reasoning services in combination with \emph{SWRL}.
+Validation, however, is not the primary purpose of its design which has lead to claims that OWL cannot be used for validation.
+\cite{Motik-2007} and \cite{Motik-2009}, e.g., discuss the differences between constraints and RDFS/OWL axioms.
+In practice, however, OWL is well-spread and RDFS/OWL constructs are widely used to tell people and applications about how valid instances should look like.
+In general, RDF documents follow the semantics of RDFS/OWL ontologies which could therefore not only be used for reasoning but also for validation.
+
+The underlying semantics for RDF validation is CWA/UNA.
 RDF validation requires that different names represent different objects ({\em unique name assumption (UNA)}), whereas,
-\emph{OWL 2} is based on the {\em non-unique name assumption (nUNA)}.  
+OWL is based on the {\em non-unique name assumption (nUNA)}.  
 %A data property is \emph{functional} (\emph{R-65}) if for each individual \emph{x}, there can be at most one distinct literal \emph{y} such that \emph{x} is connected by the data property to \emph{y}.
@@
 %Assuming nUNA, however, reasoning concludes that the titles {\em The-Adventures-of-Huckleberry-Finn} and {\em Die-Abenteuer-des-Huckleberry-Finn} are the same (\ms{\{The-Adventures-of-Huckleberry-Finn\}} = \ms{\{Die-Abenteuer-des-Huckle} \ms{berry-}\ms{Finn\}}).
-Reasoning in \emph{OWL 2} is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true. 
+Reasoning in OWL is based on the {\em open-world assumption (OWA)}, i.e., a statement cannot be inferred to be false if it cannot be proved to be true. 
 %which fits its primary design purpose to represent knowledge on the World Wide Web. 
@@
 On the other hand, RDF validation scenarios require the {\em closed-world assumption (CWA)}, i.e., a statement is inferred to be false if it cannot be proved to be true. 
-Classical constraint languages are based on the CWA where constraints need to be satisfied only by named individuals.
-This ambiguity in semantics is one of the main reasons why \emph{OWL 2} has not been adopted as a standard constraint language for RDF validation in the past.  
-In case we use \emph{OWL 2} constructs in terms of constraints, we adopt the same semantics (CWA) that is for RDF validation in general.
-
-%We propose an extensible metric to measure the continuum of severity levels to indicate how serious the violation of given constraints is.
-%Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary. 
-%As constraint types are used to define constraints on (meta)data expressed by any vocabulary, the proposed constraint classification can be applied generically, i.e. vocabulary-independent.
-
-The data most often used in research within \emph{SBE} sciences is \emph{person-level data} (or more generally \emph{record-unit data}, i.e., data collected about individuals, businesses, and households) in form of responses to studies or taken from administrative registers
-(such as hospital records, registers of births and deaths). 
-The range of person-level data is very broad - 
+This ambiguity in semantics is one of the main reasons why OWL has not been adopted as a standard constraint language for RDF validation in the past.  
+\cite{Tao-2010} propose an alternative semantics for OWL using CWA/UNA so that it could be used to validate integrity constraints.
+\cite{Patel-Schneider-2015} claims that DL and therefore OWL axioms can be interpreted in a closed-world setting and used for constraint checking.
+When using OWL axioms in terms of constraints, we adopt the same semantics that is used for RDF validation.
+
+%\section{Running Example}
+%\label{running-example}
+\section{Common Vocabularies in SBE Sciences}
+\label{rdf-representation}
+
+We took all well-established and newly developed \emph{SBE} vocabularies into account and defined constraints for three vocabularies commonly used in the \emph{SBE} sciences which are briefly introduced in the following.
+We analyzed actual data according to constraint violations, as for these vocabularies large data sets are already published.
+
+\emph{SBE} sciences require high-quality data for their empirical research. For more than a decade, members of the \emph{SBE} community have been developing and using a
+metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)},
+an XML format to disseminate, manage,
+and reuse data collected and archived for research \cite{Vardigan2008}. 
+%DDI is heavily used by the CESSDA community of European national data archives, 
+%the International Household Survey Network community (made up of more than 90 statistical agencies),
+%and ICPSR - the largest SBE data archive in the US.
+In XML, the definition of schemas containing data constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
+With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration.
+Therefore, not only established vocabularies like SKOS are used;
+recently, members of the \emph{SBE} and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.
+
+%In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on record-unit data sets (DDI-RDF), aggregated data sets (QB), thesauri (SKOS), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.
+
+-----
+
+The data most often used in research within \emph{SBE} sciences is \emph{record-unit data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers
+such as hospital records, registers of births and deaths. 
+The range of record-unit data is very broad - 
 including census, education, health data and business, social, and labor force surveys.  
@@
 
-By its nature, person-level data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 
+By its nature, record-unit data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 
 Researchers typically represent their results as aggregated data in form of multi-dimensional tables with only a few columns; so-called \emph{variables} such as \emph{sex} or \emph{age}.
-%In performing their research, the detailed person-level
-%data is aggregated into multi-dimensional tables which answer particular research questions.
-Aggregated data, which answers particular research questions, is derived from person-level data by statistics on groups or aggregates such as frequencies and arithmetic means.
-%The SDMX metadata standard – used as the basis for QB – and DDI have traditionally made efforts to align their content. 
-%Similarly, some of the developers of DDI-RDF were also involved in the development of QB, 
-%allowing the RDF versions of these standards to retain that alignment.
-%While DDI-RDF and QB provide terms for the description of data sets, 
-%both on a different level of aggregation, 
-%the \emph{Data Catalog Vocabulary (DCAT)}\footnote{\url{http://www.w3.org/TR/vocab-dcat/}} enables the representation of these data sets inside of data collections like repositories, catalogs, or archives.
-%The relationship between data collections and their contained data sets is useful, since such collections are a typical entry point when searching for data.
-%Although, in most cases aggregated data is still published in form of PDFs, 
-%it is more and more common to publish aggregated data as CSV files,
-The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying person-level data.
+Aggregated data, which answers particular research questions, is derived from record-unit data by statistics on groups or aggregates such as frequencies and arithmetic means.
+The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying record-unit data.
 Aggregated data is published in form of CSV files,
 allowing to perform calculations on the data.
-%For these calculations, definitions of the columns are needed (e.g. is a given variable interpreted numerically or as a string).
-%\emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} is a vocabulary to represent data in tabular format in RDF.\tb{tabular data} 
-%The data could be either represented in records with character-separated values (CSV) or in records with fixed length. 
-%Portals harvest metadata (as well as publicly available data) from multiple RDF data providers.
-%\tb{To ensure high quality, data must satisfy certain criteria - specified in terms of RDF constraints.}
-
-For more detailed analyses, researchers refer to person-level data including additional variables needed to answer subsequent research questions
-%Although not that common, the other direction is also possible, 
-%i.e. researchers may use metadata on person-level data to search for aggregated data.
-like the comparison of studies between countries.
+
+For more detailed analyses, researchers refer to record-unit data including additional variables needed to answer subsequent research questions like the comparison of studies between countries.
 A \emph{study} represents the process by which a data set was generated or collected.
-Eurostat\footnote{\url{http://ec.europa.eu/eurostat}}, the statistical office of the European Union, provides research findings in form of aggregated data (downloadable as CSV files) and its metadata at European level that enable comparisons between countries.
-%This way, researchers get promising findings (in form of published tables with a few columns).
-%We use the availability of childcare services in European Union member states by year, duration, and child age leading to subsequent research questions as running example of this paper.
-%The first step is to determine in which countries the unemployment rate is collected and which other variables of each country-specific study are theoretically comparable and can therefore be used to answer the underlying research question.
-The variable \emph{formal childcare}\footnote{Aggregated data and its metadata is available at: \url{http://ec.europa.eu/eurostat/web/products-datasets/-/ilc_caindformal}} %(in contrast to childcare at home)
-captures the measured availability of childcare services in percent over the population in European Union member states by 
-the variables \emph{year}, \emph{duration} (in hours per week), \emph{age} of the child, and \emph{country}.
-Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
-The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger} or by a code list of age clusters (e.g., '0 to 10' and '11 to 20').
-
-A very important and representative RDF validation case study within \emph{SBE} sciences is the comparison of variables between data collections of different countries.
-Several vocabulary-specific constraints on RDF data are checked for each data collection
-to determine if variables measuring \emph{age} 
-- collected for different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
-are comparable:
-(1) variable definitions must be available, 
-(2) for each code a human-readable label has to be specified,
-(3) code lists must be structured properly, and
-(4) code lists must either be identical or at least similar.
-If a researcher only wants to get a first overview over the comparability of variables (use case 1), 
-covering the first three constraints may be sufficient,
-i.e., the violation of the first three constraints is more serious than the violation of the last constraint.
-If the intention of the researcher is to perform more sophisticated comparisons (use case 2), however, the user may raise the severity level of the last constraint.
-
-%\ke{Wieso werden constraints nur gechecked wenn variablen auf vergleichbarkeit geprüft werden?
-das habt ihr doch gar nicht gemacht sondern ganz allgemein constraints für vokabulare aufgestellt.
-Ist QB und DDI-RDF nicht sowieso unabhängig von konkreten Variablen?}\tb{das soll nur ein beipsiel sein, wann eine komplexere validierung im kontext von sbe sinn macht (1) + (2) sind vocabulary constraints und (3) + (4) sind complex constraints}
-
-%After validating the metadata according to these constraints, portals offer added values to their customers, e.g., by searching over and comparing metadata of multiple providers.
-
-%\textbf{Data validation.}
-%Data providers and harvesters do not only offer metadata but also publicly available data on different level of aggregation.
-%To ensure high data quality, they have to check provenance information and to analyze and therefore validate the data according to predefined constraints (e.g.
-'are fundamental data fragments available?', and 'how does valid data look like?').
-%They validate, e.g., if fundamental data parts are available and define how valid data should look like (using syntactic rules).
-%Provenance (where does the data come from?) is an important aspect in evaluating data quality.
-%As data searchers know exactly which data sources they trust and which are reasonable to meet their individual use cases, 
-%RDF data validation can only be performed semi-automatically, i.e., an automatic approach serves as basis for intellectual decisions.
-
-\section{Related Work}
-\label{related-work}
-
-%\textbf{XML vs. RDF Validation.}
-For data archives, research institutes, and data libraries,
-RDF validation according to predefined constraints is a much sought-after feature, 
-particularly as this is taken for granted in the XML world.
-DDI-XML documents, e.g., are validated against diverse XSDs\footnote{\url{http://www.ddialliance.org/Specification/}}.
-As certain constraints cannot be formulated and validated by XSDs, 
-so-called secondary-level validation tools like \emph{Schematron}\footnote{\url{https://msdn.microsoft.com/en-us/library/aa468554.aspx}} have been introduced to overcome the limitations of XML validation.
-\emph{Schematron} generates validation rules and validates XML documents according to them.
-With RDF validation, one can overcome drawbacks when validating XML documents\footnote{\url{http://www.xmlmind.com/xmleditor/_distrib/doc/xmltool/xsd_structure_limitations.html}}.
-It cannot be validated, e.g., if each code of a variable's code list is associated with a category (\emph{R-86}).
-Additionally, it cannot be validated that if an element has a specific value, then certain child elements must be present (\emph{R-71}).  
-A comprehensive comparison of XML and RDF validation, however, is not within the scope of this paper.
-
-%validation or relational databases: types, relations
-
-%\textbf{RDF Data Cube Vocabulary.}
-A well-formed \emph{RDF Data Cube} is an a RDF graph describing one or more instances of \emph{qb:DataSet} for which each of the 22 integrity constraints\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf}, defined within the QB specification, passes.
-Each integrity constraint is expressed as narrative prose and, where possible, a SPARQL ASK query or query template. 
-If the ASK query is applied to an RDF graph then it will return true if that graph contains one or more QB instances which violate the corresponding constraint \cite{CyganiakReynolds2014}.
-Mader, Haslhofer, and Isaac investigated how to support
-taxonomists in improving SKOS vocabularies by pointing out quality
-issues that go beyond the integrity constraints defined in the SKOS specification \cite{MaderHaslhoferIsaac2012}.
-
-%\section{Running Example}
-%\label{running-example}
-\section{Common Vocabularies in SBE Sciences}
-\label{rdf-representation}
-
-%In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on person-level data sets (DDI-RDF), aggregated data sets (QB), thesauri (SKOS), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.
-
-We took all well-established and newly developed \emph{SBE} vocabularies into account and defined constraints for six vocabularies commonly used in or developed for the \emph{SBE} sciences which are briefly introduced in the following.
-For three of them, we analyzed actual data according to constraint violations, as for these vocabularies large data sets are already published.
+
+-----
+
 %e evaluated the data quality of large data sets on three of them, as for these vocabularies large data sets are published.
@@
 
-%\textbf{Rectangular Data.}
-\emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} is a vocabulary to represent data in tabular format in RDF enabling further aggregations and calculations.
-The data could be either represented in records with character-separated values (CSV) or fixed length. 
-\emph{Eurostat} provides a CSV file, a two-dimensional table (\emph{phdd:Table}) about \emph{formal childcare} 
-which is structured by a table structure (\emph{phdd:TableStructure}, \emph{phdd:Delimited})
-including information about the character set (\emph{ASCII}), the variable delimiter (\emph{,}), the new line marker (\emph{CRLF}), and the first line where the data starts (\emph{2}).
-The table structure is related to table columns (\emph{phdd:Column}) which are described by column descriptions (\emph{phdd:DelimitedColumnDescription}).
-For the column containing the actual cell values in percent, the column position (\emph{5}), the recommended data type (\emph{xsd:non} \emph{NegativeInteger}), and the storage format (\emph{TINYINT}) is stated.
-%The RDFication enables further aggregations and calculations, e.g., in order to compare \emph{formal childcare} between Northern and Southern Europe or between otherwise grouped countries.
-% macht mehr sinn wenn Tabelle in mehreren Dimensionen vorhanden ist ode wenn Klassifikationen wie ISCO verwendet werden
-
-%\textbf{Metadata on Person-Level Data.}
-For more detailed analyses we refer to the person-level data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}.
+For more detailed analyses we refer to the record-unit data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}.
 %published by the \emph{Microdata Information System (MISSY)}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}}.
@@
 where each cycle produces one or more data sets. 
-%\emph{Missy} is an online service platform that provides systematically structured metadata for official statistics on European person-level data sets. 
+%\emph{Missy} is an online service platform that provides systematically structured metadata for official statistics on European record-unit data sets. 
 %This includes data documentation at the study and variable level as well as documentation materials, tools and further information. 
 %\ke{Wieso jetzt wieder qb?}\tb{ich möchte zeigen wie aggregierte daten und personenbezogene daten in RDF verbunden sind. Weglassen?}
-%Aggregated (qb:DataSet) and underlying person-level data sets (\emph{DDI-RDF:LogicalDataSet}) are connected by \emph{prov:wasDerivedFrom}. 
-The aggregated variable \emph{formal childcare} is calculated on the basis of six person-level variables 
+%Aggregated (qb:DataSet) and underlying record-unit data sets (\emph{DDI-RDF:LogicalDataSet}) are connected by \emph{prov:wasDerivedFrom}. 
+The aggregated variable \emph{formal childcare} is calculated on the basis of six record-unit variables 
 (e.g., \emph{Education at pre-school})
@@
 enabling researchers to replicate the results shown in aggregated data tables.
-The \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)} is a vocabulary to represent metadata on person-level data in RDF.
+The \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)} is a vocabulary to represent metadata on record-unit data in RDF.
 The series (\emph{DDI-RDF:StudyGroup}) \emph{EU-SILC} contains one study (\emph{DDI-RDF:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
 \emph{dcterms:spatial} points to the countries for which the data has been collected.
-The study \emph{EU-SILC 2011} contains eight person-level data sets (\emph{DDI-RDF:LogicalDataSet})
-including person-level variables (\emph{DDI-RDF:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
-%Metadata on person-level data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
+The study \emph{EU-SILC 2011} contains eight record-unit data sets (\emph{DDI-RDF:LogicalDataSet})
+including record-unit variables (\emph{DDI-RDF:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
+%Metadata on record-unit data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
 %One common research question is ,e.g., the comparison of variables like 
@@
 
-%\textbf{Organizations, Hierarchies, and Classifications.}
-%\textbf{Reusing SKOS.}
 The \emph{Simple Knowledge Organization System (SKOS)} is reused multiple times to build \emph{SBE} vocabularies.
-%Variables are constructed out of values and/or (un)ordered code lists.
 The codes of the variable \emph{Education at pre-school} (number of education hours per week) are modeled as \emph{skos:Concepts} and 
@@
 organize types (\emph{skos:Concept}) of descriptive statistics (\emph{DDI-RDF:SummaryStatistics}) like minimum, maximum, and arithmetic mean.
-\emph{XKOS}\footnote{\url{https://github.com/linked-statistics/xkos}} is a SKOS extension to describe formal statistical classifications like the International Standard Classification of Occupations (\emph{ISCO}).
-and the Statistical Classification of Economic Activities in the European Community \emph{NACE}.
-\emph{DCAT} enables to represent data sets inside of data collections like portals, repositories, catalogs, and archives
-which serve as typical entry points when searching for data.
-
-%\textbf{Searching for (Meta)data.}
+
+%% ---------------
+%% Backup of 'Common Vocabularies in SBE Sciences'
+%
+%
+%\section{Common Vocabularies in SBE Sciences}
+%\label{rdf-representation}
+%
+%\emph{SBE} sciences require high-quality data for their empirical research. For more than a decade, members of the \emph{SBE} community have been developing and using a
+%metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)},
+%an XML format to disseminate, manage,
+%and reuse data collected and archived for research \cite{Vardigan2008}. 
+%In XML, the definition of schemas containing data constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
+%With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration.
+Therefore, not only established vocabularies like SKOS are used;
+%recently, members of the \emph{SBE} and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.
+%
+%The data most often used in research within \emph{SBE} sciences is \emph{record-unit data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers
+%such as hospital records, registers of births and deaths. 
+%The range of record-unit data is very broad - 
+%including census, education, health data and business, social, and labor force surveys.  
+%This type of research data is
+%held within data archives or data libraries after it has been collected, so that it may be
+%reused by future researchers. 
+%
+%By its nature, record-unit data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 
+%Researchers typically represent their results as aggregated data in form of multi-dimensional tables with only a few columns; so-called \emph{variables} such as \emph{sex} or \emph{age}.
+%Aggregated data, which answers particular research questions, is derived from record-unit data by statistics on groups or aggregates such as frequencies and arithmetic means.
+%The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying record-unit data.
+%Aggregated data is published in form of CSV files,
+%allowing to perform calculations on the data.
+%
+%For more detailed analyses, researchers refer to record-unit data including additional variables needed to answer subsequent research questions
+%like the comparison of studies between countries.
+%A \emph{study} represents the process by which a data set was generated or collected.
+%Eurostat\footnote{\url{http://ec.europa.eu/eurostat}}, the statistical office of the European Union, provides research findings in form of aggregated data (downloadable as CSV files) and its metadata at European level that enable comparisons between countries.
+%The variable \emph{formal childcare}\footnote{Aggregated data and its metadata is available at: \url{http://ec.europa.eu/eurostat/web/products-datasets/-/ilc_caindformal}} %(in contrast to childcare at home)
+%captures the measured availability of childcare services in percent over the population in European Union member states by 
+%the variables \emph{year}, \emph{duration} (in hours per week), \emph{age} of the child, and \emph{country}.
+%Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
+%The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger} or by a code list of age clusters (e.g., '0 to 10' and '11 to 20'). 
+%
+%A very important and representative RDF validation case study within \emph{SBE} sciences is the comparison of variables between data collections of different countries.
+%Several vocabulary-specific constraints on RDF data are checked for each data collection
+%to determine if variables measuring \emph{age} 
+%- collected for different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
+%are comparable:
+%(1) variable definitions must be available, 
+%(2) for each code a human-readable label has to be specified,
+%(3) code lists must be structured properly, and
+%(4) code lists must either be identical or at least similar.
+%If a researcher only wants to get a first overview over the comparability of variables (use case 1), 
+%covering the first three constraints may be sufficient,
+%i.e., the violation of the first three constraints is more serious than the violation of the last constraint.
+%If the intention of the researcher is to perform more sophisticated comparisons (use case 2), however, the user may raise the severity level of the last constraint.
+%
+%We took all well-established and newly developed \emph{SBE} vocabularies into account and defined constraints for six vocabularies commonly used in or developed for the \emph{SBE} sciences which are briefly introduced in the following.
+%For three of them, we analyzed actual data according to constraint violations, as for these vocabularies large data sets are already published.
+%
+%The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e.
+multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}.
+%A \emph{qb:DataStructureDefinition} contains metadata of the data collection.
+%The variable \emph{formal childcare}, e.g., is modeled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
+%The variables \emph{year}, \emph{duration}, \emph{age}, and \emph{country} are \emph{qb:dimensions}.
+%Data values, i.e., the availability of childcare services in percent over the population, are collected in a \emph{qb:DataSet}. 
+%Each data value is represented inside a \emph{qb:Observation} which contains values for each dimension\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}}.
+%
+%\emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} is a vocabulary to represent data in tabular format in RDF enabling further aggregations and calculations.
+%The data could be either represented in records with character-separated values (CSV) or fixed length. 
+%
+%For more detailed analyses we refer to the record-unit data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}.
+%Where data collection is cyclic, data sets may be released as \emph{series}, 
+%where each cycle produces one or more data sets. 
+%The aggregated variable \emph{formal childcare} is calculated on the basis of six record-unit variables 
+%(e.g., \emph{Education at pre-school})
+%for which detailed metadata is given 
+%(e.g., code lists)
+%enabling researchers to replicate the results shown in aggregated data tables.
+%The \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)} is a vocabulary to represent metadata on record-unit data in RDF.
+%The series (\emph{DDI-RDF:StudyGroup}) \emph{EU-SILC} contains one study (\emph{DDI-RDF:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
+%\emph{dcterms:spatial} points to the countries for which the data has been collected.
+%The study \emph{EU-SILC 2011} contains eight record-unit data sets (\emph{DDI-RDF:LogicalDataSet})
+%including record-unit variables (\emph{DDI-RDF:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
+%
+%The \emph{Simple Knowledge Organization System (SKOS)} is reused multiple times to build \emph{SBE} vocabularies.
+%The codes of the variable \emph{Education at pre-school} (number of education hours per week) are modeled as \emph{skos:Concepts} and 
+%a \emph{skos:OrderedCollection} organizes them in a particular order within a \emph{skos:member} \emph{List}.
+%A variable may be associated with a theoretical concept (\emph{skos:Concept}). 
+%\emph{skos:narrower} builds the hierarchy of theoretical concepts within a \emph{skos:Concept} \emph{Scheme} of a series.
+%The variable \emph{Education at pre-school} is assigned to the theoretical concept \emph{Child Care} which is the narrower concept of \emph{Education} - one of the top concepts of the series \emph{EU-SILC}.
+%Controlled vocabularies (\emph{skos:ConceptScheme}), serving as extension and reuse mechanism,
+%organize types (\emph{skos:Concept}) of descriptive statistics (\emph{DDI-RDF:SummaryStatistics}) like minimum, maximum, and arithmetic mean.
+%\emph{XKOS}\footnote{\url{https://github.com/linked-statistics/xkos}} is a SKOS extension to describe formal statistical classifications like the International Standard Classification of Occupations (\emph{ISCO}).
+%and the Statistical Classification of Economic Activities in the European Community \emph{NACE}.
 %\emph{DCAT} enables to represent data sets inside of data collections like portals, repositories, catalogs, and archives
 %which serve as typical entry points when searching for data.
-%Users search for aggregated and person-level data records (\emph{dcat:CatalogRecord}) inside data catalogs (\emph{dcat:Catalog}). 
-%As search differs depending on the users’ information need,
-%users may only search for records' metadata (e.g., \emph{dcterms:title}, \emph{dcterms:description}), 
-%or may formulate more sophisticated queries on aggregated and person-level data sets (\emph{dcat:Dataset}) or their
-%distributions (\emph{dcat:Distribution}) which are part of the records. 
-%Often, users search for data sets covering particular topics (\emph{dcat:keyword}, \emph{dcat:theme}), time periods (\emph{dcterms:temporal}),  or  locations (\emph{dcterms:spatial}), 
-%or for certain formats in which the data distribution is available (\emph{dcterms:format}).
+
+% Backup of 'Common Vocabularies in SBE Sciences'
+% -----
 
@@
 %Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
-The classification of the 115 concrete constraints on three vocabularies according to severity levels is published in a technical report \cite{BoschZapilkoWackerowEckert2015}.
+For the three vocabularies, several \emph{SBE} domain experts determined the default severity level of the 115 concrete constraints, which we published in a technical report \cite{BoschZapilkoWackerowEckert2015}.
 In the following, we summarize the results for the purpose of our evaluation.
@@
 The modeling languages RDFS and OWL are typically used to formally specify vocabularies.
-\emph{RDFS/OWL Based} denotes the set of constraint types which can be formulated with RDFS/OWL constructs using CWA/UNA semantics without reasoning and which are therefore commonly found within formal specifications of vocabularies.
-We determined this set based on the evaluation of the three vocabularies.
+\emph{RDFS/OWL Based} denotes the set of constraint types which can be formulated with RDFS/OWL axioms which we use in terms of constraints with CWA/UNA semantics and without reasoning\footnote{The entailment regime is to be decided by the implementors.
+It is our point that reasoning affects validation and that a proper definition of the reasoning to be applied is needed.}.
+RDFS/OWL axioms are commonly found within formal specifications of vocabularies.
+We determined this set based on the evaluation of the three vocabularies we performed without reasoning.
 \emph{RDFS/OWL Based} constraints generally can be seen as a basic level of constraints ensuring that the data is consistent with the formally and explicitly specified intended semantics as well as the integrity of vocabularies' conceptual models about data.
@@
 \emph{Warnings} are syntactic or semantic problems which typically should not lead to an abortion of data processing.
-\emph{Errors} are syntactic or semantic errors which should cause the abortion of data processing. \textcolor{red}{examples for each in the subsequent section?}
+\emph{Errors} are syntactic or semantic errors which should cause the abortion of data processing. 
 %Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
@@
 Thus and as there are different sorts of key, and as keys can lead to undecidability, 
-DL is extended with the construct \emph{keyfor} ({\small\ms{identifier \ms{keyfor} Resource}}) \cite{Lutz2005} which is implemented by the \emph{OWL 2} \emph{hasKey} construct.
+DL is extended with the construct \emph{keyfor} ({\small\ms{identifier \ms{keyfor} Resource}}) \cite{Lutz2005} which is implemented by the OWL 2 \emph{hasKey} construct.
 
@@
 %
-%As we know that only person-level data sets (\emph{DDI-RDF:LogicalDataSet}) can derive (\emph{DDI-RDF:aggregation}) aggregated data sets (\emph{qb:DataSet}), 
+%As we know that only record-unit data sets (\emph{DDI-RDF:LogicalDataSet}) can derive (\emph{DDI-RDF:aggregation}) aggregated data sets (\emph{qb:DataSet}), 
 %{\em logical-data-set} is a \emph{DDI-RDF:LogicalDataSet}, 
@@
 %With \emph{subsumption} (\emph{R-100}), one can state that \emph{DDI-RDF:LogicalDataSet} is a sub-class of \emph{dcat:DataSet}, 
-%i.e., each person-level data set is also a catalog data set.
-%Thus, constraints on catalog data sets are also validated for person-level data sets;
-%e.g., the \emph{existential quantification} below restricting that person-level data sets must have a distribution:
+%i.e., each record-unit data set is also a catalog data set.
+%Thus, constraints on catalog data sets are also validated for record-unit data sets;
+%e.g., the \emph{existential quantification} below restricting that record-unit data sets must have a distribution:
 
@@
 %- for each code list there should be a description.
-%- there should be a relationship to the underlying person-level data.
+%- there should be a relationship to the underlying record-unit data.
 %
@@
 Furthermore, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.
-
+\tb{why SPIN?}
 We use \emph{SPIN}, a SPARQL-based way to formulate and check constraints, as basis to develop a
@@
 A SPIN construct template creates constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
-%\emph{Missy}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}} provides comprehensive Linked Data services like diverse RDF exports of person-level metadata conforming to the DDI-RDF vocabulary in form of multiple concrete syntaxes.
+%\emph{Missy}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}} provides comprehensive Linked Data services like diverse RDF exports of record-unit metadata conforming to the DDI-RDF vocabulary in form of multiple concrete syntaxes.
 
@@
 
-%In this paper, we showed in form of a complete real world running example how to represent metadata on person-level data (DDI-RDF), metadata on aggregated data (QB), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
-%We explained why RDF validation is important in this context and how metadata on person-level data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality\footnote{The first appendix of this paper describing each constraint in detail is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}} (\textbf{contribution 2}, section \ref{rdf-validation}).
+%In this paper, we showed in form of a complete real world running example how to represent metadata on record-unit data (DDI-RDF), metadata on aggregated data (QB), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
+%We explained why RDF validation is important in this context and how metadata on record-unit data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality\footnote{The first appendix of this paper describing each constraint in detail is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}} (\textbf{contribution 2}, section \ref{rdf-validation}).
 %We distinguish two validation types:
@@
 %We implemented a validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages and to ensure correct syntax and semantics of diverse vocabularies such as DDI-RDF, QB, SKOS, and \emph{PHDD} (section \ref{implementation}).
-%We exhaustively evaluated the metadata quality of large real world aggregated (QB), person-level (DDI-RDF), and thesauri (SKOS) data sets (more than 4.2 billion triples and 15 thousand data sets) by means of 213  constraints of the majority of the constraint types\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).
+%We exhaustively evaluated the metadata quality of large real world aggregated (QB), record-unit (DDI-RDF), and thesauri (SKOS) data sets (more than 4.2 billion triples and 15 thousand data sets) by means of 213  constraints of the majority of the constraint types\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).
 

### 2015-07-22 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
SBE vocabularies

@@
 and reuse data collected and archived for research \cite{Vardigan2008}. 
-%DDI is heavily used by the CESSDA community of European national data archives, 
-%the International Household Survey Network community (made up of more than 90 statistical agencies),
-%and ICPSR - the largest SBE data archive in the US.
 In XML, the definition of schemas containing data constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
@@
 
-%In this section, we describe how data in rectangular format (\emph{PHDD}) and metadata on record-unit data sets (DDI-RDF), aggregated data sets (QB), thesauri (SKOS), and statistical classifications (\emph{XKOS}) are represented in RDF\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}} and how therefore reused vocabularies are interrelated.
-
------
-
-The data most often used in research within \emph{SBE} sciences is \emph{record-unit data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers
-such as hospital records, registers of births and deaths. 
-The range of record-unit data is very broad - 
-including census, education, health data and business, social, and labor force surveys.  
-This type of research data is
-held within data archives or data libraries after it has been collected, so that it may be
-reused by future researchers.
-
+The data most often used in research within \emph{SBE} sciences is \emph{record-unit data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers such as hospital records, registers of births and deaths.
+A \emph{study} represents the process by which a data set was generated or collected.
+The range of record-unit data is very broad - including census, education, health data and business, social, and labor force surveys.
+This type of research data is held within data archives or data libraries after it has been collected, so that it may be reused by future researchers.
 By its nature, record-unit data is highly confidential and access is often only permitted for qualified researchers who must apply for access.
-Researchers typically represent their results as aggregated data in form of multi-dimensional tables with only a few columns; so-called \emph{variables} such as \emph{sex} or \emph{age}.
+Researchers typically represent their results as aggregated data in form of multi-dimensional tables with only a few columns: so-called \emph{variables} such as \emph{sex} or \emph{age}.
 Aggregated data, which answers particular research questions, is derived from record-unit data by statistics on groups or aggregates such as frequencies and arithmetic means.
 The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying record-unit data.
-Aggregated data is published in form of CSV files,
-allowing to perform calculations on the data.
-
-For more detailed analyses, researchers refer to record-unit data including additional variables needed to answer subsequent research questions like the comparison of studies between countries.
-A \emph{study} represents the process by which a data set was generated or collected.
-
------
-
-%e evaluated the data quality of large data sets on three of them, as for these vocabularies large data sets are published.
-
-%For our evaluation, we examined six different vocabularies commonly used in or developed for the \emph{SBE} sciences which are briefly introduced in the following.
-For three of them, we analyzed actual data according to constraint violations.
-For \emph{PHDD} and \emph{XKOS}, there is not yet enough data available so we limit our examination to the vocabularies themselves.
-
-%\textbf{Metadata on Aggregated Data.}
-The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e.
-multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}.
+For more detailed analyses, researchers refer to record-unit data including additional variables needed to answer subsequent research questions.
+
+\emph{Formal childcare} is an example of an aggregated variable which captures the measured availability of childcare services in percent over the population in European Union member states by 
+the dimensions \emph{year}, \emph{duration}, \emph{age} of the child, and \emph{country}.
+Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
+The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger} or by a code list of age clusters (e.g., '0 to 10' and '11 to 20'). 
+The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e., multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}.
 %QB represents metadata on multi-dimensional aggregate data in two files: a \emph{qb:DataSet} and a \emph{qb:DataStructureDefinition}.
 A \emph{qb:DataStructureDefinition} contains metadata of the data collection.
-The variable \emph{formal childcare}, e.g., is modeled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
-The variables \emph{year}, \emph{duration}, \emph{age}, and \emph{country} are \emph{qb:dimensions}.
+The variable \emph{formal childcare} is modeled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
+\emph{year}, \emph{duration}, \emph{age}, and \emph{country} are \emph{qb:dimensions}.
 Data values, i.e., the availability of childcare services in percent over the population, are collected in a \emph{qb:DataSet}. 
-Each data value is represented inside a \emph{qb:Observation} which contains values for each dimension\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}}.
+Each data value is represented inside a \emph{qb:Observation} which contains values for each dimension. 
 %(e.g., the year in which \emph{formal childcare} has been determined).
@@
 
-For more detailed analyses we refer to the record-unit data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}.
-%published by the \emph{Microdata Information System (MISSY)}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}}.
-Where data collection is cyclic, data sets may be released as \emph{series}, 
-where each cycle produces one or more data sets. 
-%\emph{Missy} is an online service platform that provides systematically structured metadata for official statistics on European record-unit data sets. 
-%This includes data documentation at the study and variable level as well as documentation materials, tools and further information. 
-%\ke{Wieso jetzt wieder qb?}\tb{ich möchte zeigen wie aggregierte daten und personenbezogene daten in RDF verbunden sind. Weglassen?}
-%Aggregated (qb:DataSet) and underlying record-unit data sets (\emph{DDI-RDF:LogicalDataSet}) are connected by \emph{prov:wasDerivedFrom}. 
-The aggregated variable \emph{formal childcare} is calculated on the basis of six record-unit variables 
-(e.g., \emph{Education at pre-school})
-%\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC/2011/Cross-sectional/original#2011-Cross-sectional-RL010}})
-%(2) Education at compulsory school,
-%(3) Child care at centre-based services,
-%(4) Child care at day-care centre,
-%(5) Child care by a professional child-minder, and
-%(6) Child care by grand-parents, household members, relatives, friends, neighbours.
-for which detailed metadata is given 
-%(definitions, descriptions, theoretical concepts, questions variables are based on, code lists, frequencies, descriptive statistics, countries, year of data collection, and classifications) 
-(e.g., code lists)
-enabling researchers to replicate the results shown in aggregated data tables.
-The \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)} is a vocabulary to represent metadata on record-unit data in RDF.
-The series (\emph{DDI-RDF:StudyGroup}) \emph{EU-SILC} contains one study (\emph{DDI-RDF:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
-\emph{dcterms:spatial} points to the countries for which the data has been collected.
-The study \emph{EU-SILC 2011} contains eight record-unit data sets (\emph{DDI-RDF:LogicalDataSet})
-including record-unit variables (\emph{DDI-RDF:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
+For more detailed analyses we refer to the underlying record-unit data.
+The aggregated variable \emph{formal childcare} is calculated on the basis of six record-unit variables (i.a., \emph{Education at pre-school}) for which detailed metadata is given (i.a., code lists) enabling researchers to replicate the results shown in aggregated data tables.
+\emph{DDI-RDF} is used to represent metadata on record-unit data in RDF.
+%The series (\emph{DDI-RDF:StudyGroup}) \emph{EU-SILC} contains one study (\emph{DDI-RDF:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
+%\emph{dcterms:spatial} points to the countries for which the data has been collected.
+The study for which the record-unit data has been collected 
+%\emph{EU-SILC 2011} 
+contains eight record-unit data sets (\emph{disco:LogicalDataSet})
+including variables (\emph{disco:Variable}) like the six ones needed to calculate the variable \emph{formal childcare}.
 %Metadata on record-unit data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.

### 2015-07-22 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
introduction

@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{Aspects of RDF Data Constraints in the Social, Behavioural, and Economic Sciences}
+%\title{Aspects of RDF Data Constraints in the Social, Behavioural, and Economic Sciences}
+\title{Validating RDF Data Quality using Constraints to Direct the Development of Constraint Languages}
 
@@
 The \emph{Simple Knowledge Organization System (SKOS)} is reused multiple times to build \emph{SBE} vocabularies.
-The codes of the variable \emph{Education at pre-school} (number of education hours per week) are modeled as \emph{skos:Concepts} and 
-a \emph{skos:OrderedCollection} organizes them in a particular order within a \emph{skos:member} \emph{List}.
-A variable may be associated with a theoretical concept (\emph{skos:Concept}). 
-\emph{skos:narrower} builds the hierarchy of theoretical concepts within a \emph{skos:Concept} \emph{Scheme} of a series.
-The variable \emph{Education at pre-school} is assigned to the theoretical concept \emph{Child Care} which is the narrower concept of \emph{Education} - one of the top concepts of the series \emph{EU-SILC}.
+The codes of the variable \emph{Education at pre-school} are modeled as \emph{skos:Concepts} and 
+a \emph{skos:OrderedCollection} organizes them in a particular order within a \emph{skos:memberList}.
+A variable may be associated with a theoretical concept (\emph{skos:Concept}) and \emph{skos:narrower} builds the hierarchy of theoretical concepts within a \emph{skos:ConceptScheme} of a study.
+The variable \emph{Education at pre-school} is assigned to the theoretical concept \emph{Child Care} which is a narrower concept of the top concept \emph{Education}.
 Controlled vocabularies (\emph{skos:ConceptScheme}), serving as extension and reuse mechanism,
-organize types (\emph{skos:Concept}) of descriptive statistics (\emph{DDI-RDF:SummaryStatistics}) like minimum, maximum, and arithmetic mean.
+organize types (\emph{skos:Concept}) of descriptive statistics (\emph{disco:SummaryStatistics}) like minimum, maximum, and arithmetic mean.
 
@@
 It is useful to declare properties to be \emph{conditional} (\emph{R-71}), i.e., if particular properties exist (or do not exist), then other properties must also be present (or absent).
-To get an overview over a series/study either an abstract, a title, an alternative title, or links to external descriptions should be provided. 
+To get an overview over a study either an abstract, a title, an alternative title, or links to external descriptions should be provided. 
 If an abstract and an external description are absent, however,  

### 2015-07-22 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
introduction

@@
 Based on our work in the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group, we identified and published by today 81 types of constraints that are required by various stakeholders for data applications.
-In this paper, we formulate 115 constraints on three different vocabularies (DDI-RDF, QB, and SKOS) and classify them according to their severity level and whether their type is expressible by different types of constraint languages.
+In this paper, we formulate 115 constraints on three different vocabularies (DDI-RDF, QB, and SKOS) and classify them according to (1) the severity of an occurring violation and (2) which types of constraint languages are able to express their type of constraint.
 We evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic sciences obtained from 33 SPARQL endpoints.

### 2015-07-22 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
proofreading

--- 2015-07-22 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
@@
 Based on our work in the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group, we identified and published by today 81 types of constraints that are required by various stakeholders for data applications.
-In this paper, we formulate 115 constraints on three different vocabularies (DDI-RDF, QB, and SKOS) and classify them according to their severity level and whether their type is expressible by different types of constraint languages.
+In this paper, in collaboration with several domain experts we formulate 115 constraints on three different vocabularies (DDI-RDF, QB, and SKOS) and classify them according to (1) the severity of an occurring violation and (2) which types of constraint languages are able to express their type of constraint.
 We evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic sciences obtained from 33 SPARQL endpoints.
@@
 
-For constraint formulation and RDF data validation, several languages exist or are currently developed: \emph{Shape Expressions (ShEx)}, \emph{Resource Shapes (ReSh)}, \emph{Description Set Profiles (DSP)}, \emph{OWL 2}, the \emph{SPARQL Inferencing Notation (SPIN)}, and \emph{SPARQL} are the six most promising and widely used constraint languages.
+For constraint formulation and RDF data validation, several languages exist or are currently developed.
+\emph{Shape Expressions (ShEx)}, \emph{Resource Shapes (ReSh)}, \emph{Description Set Profiles (DSP)}, \emph{OWL 2}, the \emph{SPARQL Inferencing Notation (SPIN)}, and \emph{SPARQL} are the six most promising and widely used constraint languages.
 OWL 2 is used as a constraint language under the closed-world and unique name assumptions.
@@
 
-Within the DCMI task group, a collaboratively curated database of RDF validation requirements has been created which contains the findings of the working groups based on various case studies provided by data institutions \cite{BoschEckert2014}.
-It is publicly available and open for further contributions\footnote{Online available at \url{http://purl.org/net/rdf-validation}}.
+Within the DCMI task group, a collaboratively curated database of RDF validation requirements\footnote{Online available at: \url{http://purl.org/net/rdf-validation}} has been created which contains the findings of the working groups based on various case studies provided by data institutions \cite{BoschEckert2014}.
+It is publicly available and open for further contributions.
 The database connects requirements to use cases, case studies, and implementations and forms the basis of this paper. 
@@
 
-To gain a better understanding about the role of certain requirements for data quality and in order to direct the further development of constraint languages, we collected constraints for commonly used vocabularies in the \emph{SBE} domain, either from the vocabularies themselves or from domain and data experts.
+To gain a better understanding about the role of certain requirements for data quality and in order to direct the further development of constraint languages, we collected constraints for commonly used vocabularies in the \emph{SBE} domain (see Section \ref{sbe-vocabularies}), either from the vocabularies themselves or from domain and data experts.
 All in all, this lead to 115 constraints on three vocabularies.
@@
 
+%\section{Running Example}
+%\label{running-example}
+\section{Common Vocabularies in SBE Sciences}
+\label{sbe-vocabularies}
+
+We took all well-established and newly developed \emph{SBE} vocabularies into account and defined constraints for three vocabularies commonly used in the \emph{SBE} sciences which are briefly introduced in the following.
+We analyzed actual data according to constraint violations, as for these vocabularies large data sets are already published.
+
+\emph{SBE} sciences require high-quality data for their empirical research. For more than a decade, members of the \emph{SBE} community have been developing and using a
+metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)},
+an XML format to disseminate, manage,
+and reuse data collected and archived for research \cite{Vardigan2008}. 
+In XML, the definition of schemas containing data constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
+With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration.
+Therefore, not only established vocabularies like SKOS are used;
+recently, members of the \emph{SBE} and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.
+
+The data most often used in research within \emph{SBE} sciences is \emph{record-unit data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers such as hospital records, registers of births and deaths.
+A \emph{study} represents the process by which a data set was generated or collected.
+The range of record-unit data is very broad - including census, education, health data and business, social, and labor force surveys.
+This type of research data is held within data archives or data libraries after it has been collected, so that it may be reused by future researchers.
+By its nature, record-unit data is highly confidential and access is often only permitted for qualified researchers who must apply for access.
+Researchers typically represent their results as aggregated data in form of multi-dimensional tables with only a few columns: so-called \emph{variables} such as \emph{sex} or \emph{age}.
+Aggregated data, which answers particular research questions, is derived from record-unit data by statistics on groups or aggregates such as frequencies and arithmetic means.
+The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying record-unit data.
+For more detailed analyses, researchers refer to record-unit data including additional variables needed to answer subsequent research questions.
+
+\emph{Formal childcare} is an example of an aggregated variable which captures the measured availability of childcare services in percent over the population in European Union member states by 
+the dimensions \emph{year}, \emph{duration}, \emph{age} of the child, and \emph{country}.
+Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
+The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger} or by a code list of age clusters (e.g., '0 to 10' and '11 to 20'). 
+The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e., multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}.
+%QB represents metadata on multi-dimensional aggregate data in two files: a \emph{qb:DataSet} and a \emph{qb:DataStructureDefinition}.
+A \emph{qb:DataStructureDefinition} contains metadata of the data collection.
+The variable \emph{formal childcare} is modeled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
+\emph{Year}, \emph{duration}, \emph{age}, and \emph{country} are \emph{qb:dimensions}.
+Data values, i.e., the availability of childcare services in percent over the population, are collected in a \emph{qb:DataSet}. 
+Each data value is represented inside a \emph{qb:Observation} which contains values for each dimension. 
+%(e.g., the year in which \emph{formal childcare} has been determined).
+%\ke{Wieso springt das von einer sehr knappen Einführung direkt zu konkreten (beliebigen?) Variablen?
+Ich möchte wissen, wofür QB benutzt wird und gerne ein konkretes %Beispiel sehen, um mir einen Data Cube vorstellen zu können.}\tb{hmm, ich halte das beispiel für ein knappes und verständliches beipsiel wie eine tabelle in qb dargestellt wird / es ist auch der link enthalten zu der tabelle von eurostat}
+
+For more detailed analyses we refer to the underlying record-unit data.
+The aggregated variable \emph{formal childcare} is calculated on the basis of six record-unit variables (i.a., \emph{Education at pre-school}) for which detailed metadata is given (i.a., code lists) enabling researchers to replicate the results shown in aggregated data tables.
+\emph{DDI-RDF} is used to represent metadata on record-unit data in RDF.
+%The series (\emph{DDI-RDF:StudyGroup}) \emph{EU-SILC} contains one study (\emph{DDI-RDF:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
+%\emph{dcterms:spatial} points to the countries for which the data has been collected.
+The study (\emph{disco:Study}) for which the record-unit data has been collected 
+%\emph{EU-SILC 2011} 
+contains eight data sets (\emph{disco:LogicalDataSet})
+including variables (\emph{disco:Variable}) like the six ones needed to calculate the variable \emph{formal childcare}.
+%Metadata on record-unit data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
+%One common research question is ,e.g., the comparison of variables like 
+%\emph{formal childcare} between countries, for which the variable is collected within the context of an individual study, and other European or non European countries (e.g. OSCE).
+
+The \emph{Simple Knowledge Organization System (SKOS)} is reused multiple times to build \emph{SBE} vocabularies.
+The codes of the variable \emph{Education at pre-school} are modeled as \emph{skos:Concepts} and 
+a \emph{skos:OrderedCollection} organizes them in a particular order within a \emph{skos:memberList}.
+A variable may be associated with a theoretical concept (\emph{skos:Concept}) and \emph{skos:narrower} builds the hierarchy of theoretical concepts within a \emph{skos:ConceptScheme} of a study.
+The variable \emph{Education at pre-school} is assigned to the theoretical concept \emph{Child Care} which is a narrower concept of the top concept \emph{Education}.
+Controlled vocabularies (\emph{skos:ConceptScheme}), serving as extension and reuse mechanism,
+organize types (\emph{skos:Concept}) of descriptive statistics (\emph{disco:SummaryStatistics}) like minimum, maximum, and arithmetic mean.
+
+%% ---------------
+%% Backup of 'Common Vocabularies in SBE Sciences'
+%
+%
+%\section{Common Vocabularies in SBE Sciences}
+%\label{rdf-representation}
+%
+%\emph{SBE} sciences require high-quality data for their empirical research. For more than a decade, members of the \emph{SBE} community have been developing and using a
+%metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)},
+%an XML format to disseminate, manage,
+%and reuse data collected and archived for research \cite{Vardigan2008}. 
+%In XML, the definition of schemas containing data constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
+%With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration.
+Therefore, not only established vocabularies like SKOS are used;
+%recently, members of the \emph{SBE} and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.
+%
+%The data most often used in research within \emph{SBE} sciences is \emph{record-unit data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers
+%such as hospital records, registers of births and deaths. 
+%The range of record-unit data is very broad - 
+%including census, education, health data and business, social, and labor force surveys.  
+%This type of research data is
+%held within data archives or data libraries after it has been collected, so that it may be
+%reused by future researchers. 
+%
+%By its nature, record-unit data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 
+%Researchers typically represent their results as aggregated data in form of multi-dimensional tables with only a few columns; so-called \emph{variables} such as \emph{sex} or \emph{age}.
+%Aggregated data, which answers particular research questions, is derived from record-unit data by statistics on groups or aggregates such as frequencies and arithmetic means.
+%The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying record-unit data.
+%Aggregated data is published in form of CSV files,
+%allowing to perform calculations on the data.
+%
+%For more detailed analyses, researchers refer to record-unit data including additional variables needed to answer subsequent research questions
+%like the comparison of studies between countries.
+%A \emph{study} represents the process by which a data set was generated or collected.
+%Eurostat\footnote{\url{http://ec.europa.eu/eurostat}}, the statistical office of the European Union, provides research findings in form of aggregated data (downloadable as CSV files) and its metadata at European level that enable comparisons between countries.
+%The variable \emph{formal childcare}\footnote{Aggregated data and its metadata is available at: \url{http://ec.europa.eu/eurostat/web/products-datasets/-/ilc_caindformal}} %(in contrast to childcare at home)
+%captures the measured availability of childcare services in percent over the population in European Union member states by 
+%the variables \emph{year}, \emph{duration} (in hours per week), \emph{age} of the child, and \emph{country}.
+%Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
+%The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger} or by a code list of age clusters (e.g., '0 to 10' and '11 to 20'). 
+%
+%A very important and representative RDF validation case study within \emph{SBE} sciences is the comparison of variables between data collections of different countries.
+%Several vocabulary-specific constraints on RDF data are checked for each data collection
+%to determine if variables measuring \emph{age} 
+%- collected for different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
+%are comparable:
+%(1) variable definitions must be available, 
+%(2) for each code a human-readable label has to be specified,
+%(3) code lists must be structured properly, and
+%(4) code lists must either be identical or at least similar.
+%If a researcher only wants to get a first overview over the comparability of variables (use case 1), 
+%covering the first three constraints may be sufficient,
+%i.e., the violation of the first three constraints is more serious than the violation of the last constraint.
+%If the intention of the researcher is to perform more sophisticated comparisons (use case 2), however, the user may raise the severity level of the last constraint.
+%
+%We took all well-established and newly developed \emph{SBE} vocabularies into account and defined constraints for six vocabularies commonly used in or developed for the \emph{SBE} sciences which are briefly introduced in the following.
+%For three of them, we analyzed actual data according to constraint violations, as for these vocabularies large data sets are already published.
+%
+%The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e.
+multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}.
+%A \emph{qb:DataStructureDefinition} contains metadata of the data collection.
+%The variable \emph{formal childcare}, e.g., is modeled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
+%The variables \emph{year}, \emph{duration}, \emph{age}, and \emph{country} are \emph{qb:dimensions}.
+%Data values, i.e., the availability of childcare services in percent over the population, are collected in a \emph{qb:DataSet}. 
+%Each data value is represented inside a \emph{qb:Observation} which contains values for each dimension\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}}.
+%
+%\emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} is a vocabulary to represent data in tabular format in RDF enabling further aggregations and calculations.
+%The data could be either represented in records with character-separated values (CSV) or fixed length. 
+%
+%For more detailed analyses we refer to the record-unit data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}.
+%Where data collection is cyclic, data sets may be released as \emph{series}, 
+%where each cycle produces one or more data sets. 
+%The aggregated variable \emph{formal childcare} is calculated on the basis of six record-unit variables 
+%(e.g., \emph{Education at pre-school})
+%for which detailed metadata is given 
+%(e.g., code lists)
+%enabling researchers to replicate the results shown in aggregated data tables.
+%The \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)} is a vocabulary to represent metadata on record-unit data in RDF.
+%The series (\emph{DDI-RDF:StudyGroup}) \emph{EU-SILC} contains one study (\emph{DDI-RDF:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
+%\emph{dcterms:spatial} points to the countries for which the data has been collected.
+%The study \emph{EU-SILC 2011} contains eight record-unit data sets (\emph{DDI-RDF:LogicalDataSet})
+%including record-unit variables (\emph{DDI-RDF:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
+%
+%The \emph{Simple Knowledge Organization System (SKOS)} is reused multiple times to build \emph{SBE} vocabularies.
+%The codes of the variable \emph{Education at pre-school} (number of education hours per week) are modeled as \emph{skos:Concepts} and 
+%a \emph{skos:OrderedCollection} organizes them in a particular order within a \emph{skos:member} \emph{List}.
+%A variable may be associated with a theoretical concept (\emph{skos:Concept}). 
+%\emph{skos:narrower} builds the hierarchy of theoretical concepts within a \emph{skos:Concept} \emph{Scheme} of a series.
+%The variable \emph{Education at pre-school} is assigned to the theoretical concept \emph{Child Care} which is the narrower concept of \emph{Education} - one of the top concepts of the series \emph{EU-SILC}.
+%Controlled vocabularies (\emph{skos:ConceptScheme}), serving as extension and reuse mechanism,
+%organize types (\emph{skos:Concept}) of descriptive statistics (\emph{DDI-RDF:SummaryStatistics}) like minimum, maximum, and arithmetic mean.
+%\emph{XKOS}\footnote{\url{https://github.com/linked-statistics/xkos}} is a SKOS extension to describe formal statistical classifications like the International Standard Classification of Occupations (\emph{ISCO}).
+%and the Statistical Classification of Economic Activities in the European Community \emph{NACE}.
+%\emph{DCAT} enables to represent data sets inside of data collections like portals, repositories, catalogs, and archives
+%which serve as typical entry points when searching for data.
+
+% Backup of 'Common Vocabularies in SBE Sciences'
+% -----
+
 \section{Related Work}
@@
 particularly as this is taken for granted in the XML world.
-DDI-XML documents, e.g., are validated against diverse XSDs\footnote{\url{http://www.ddialliance.org/Specification/}}.
-As certain constraints cannot be formulated and validated by XSDs, 
+DDI-XML documents, e.g., are validated against diverse XML Schemas.
+%\footnote{\url{http://www.ddialliance.org/Specification/}}.
+As certain constraints cannot be formulated and validated by XML Schemas, 
 so-called secondary-level validation tools like \emph{Schematron}\footnote{\url{https://msdn.microsoft.com/en-us/library/aa468554.aspx}} 
 have been introduced to overcome the limitations of XML validation.
-\emph{Schematron} generates validation rules and validates XML documents according to them.
-With RDF validation, one can overcome drawbacks when validating XML documents\footnote{\url{http://www.xmlmind.com/xmleditor/_distrib/doc/xmltool/xsd_structure_limitations.html}}.
-It cannot be validated, e.g., if each code of a variable's code list is associated with a category (\emph{R-86}) and if an element has a specific value, then certain child elements must be present (\emph{R-71}).
-A comprehensive comparison of XML and RDF validation, however, is not within the scope of this paper.
-
-%validation or relational databases: types, relations
-
-%\textbf{RDF Data Cube Vocabulary.}
+Schematron generates validation rules and validates XML documents according to them.
+With RDF validation, one can overcome the drawbacks when validating XML documents\footnote{\url{http://www.xmlmind.com/xmleditor/_distrib/doc/xmltool/xsd_structure_limitations.html}}.
+It cannot be validated, e.g., if each code of a variable's code list is associated with a category and that if an element has a specific value then certain child elements must be present.
+
 A well-formed \emph{RDF Data Cube} is an a RDF graph describing one or more instances of \emph{qb:DataSet} for which each of the 22 integrity constraints\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf}, defined within the QB specification, passes.
-Each integrity constraint is expressed as narrative prose and, where possible, a SPARQL ASK query or query template. 
-If the ASK query is applied to an RDF graph then it will return true if that graph contains one or more QB instances which violate the corresponding constraint \cite{CyganiakReynolds2014}.
-
-Mader, Haslhofer, and Isaac \cite{MaderHaslhoferIsaac2012} investigated how to support
+Each integrity constraint is expressed as narrative prose and, where possible, as a SPARQL ASK query or query template. 
+If the ASK query is applied to an RDF graph then it will return true if that graph contains one or more QB instances which violate the corresponding constraint.
+
+\cite{MaderHaslhoferIsaac2012} investigated how to support
 taxonomists in improving SKOS vocabularies by pointing out quality
@@
 
-The underlying semantics for RDF validation is CWA/UNA.
-RDF validation requires that different names represent different objects ({\em unique name assumption (UNA)}), whereas,
+The semantics which is applied for RDF validation is CWA/UNA.
+RDF validation requires that different names represent different objects ({\em unique name assumption (UNA)}), whereas
 OWL is based on the {\em non-unique name assumption (nUNA)}.  
@@
 When using OWL axioms in terms of constraints, we adopt the same semantics that is used for RDF validation.
-
-%\section{Running Example}
-%\label{running-example}
-\section{Common Vocabularies in SBE Sciences}
-\label{rdf-representation}
-
-We took all well-established and newly developed \emph{SBE} vocabularies into account and defined constraints for three vocabularies commonly used in the \emph{SBE} sciences which are briefly introduced in the following.
-We analyzed actual data according to constraint violations, as for these vocabularies large data sets are already published.
-
-\emph{SBE} sciences require high-quality data for their empirical research. For more than a decade, members of the \emph{SBE} community have been developing and using a
-metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)},
-an XML format to disseminate, manage,
-and reuse data collected and archived for research \cite{Vardigan2008}. 
-In XML, the definition of schemas containing data constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
-With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration.
-Therefore, not only established vocabularies like SKOS are used;
-recently, members of the \emph{SBE} and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.
-
-The data most often used in research within \emph{SBE} sciences is \emph{record-unit data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers such as hospital records, registers of births and deaths.
-A \emph{study} represents the process by which a data set was generated or collected.
-The range of record-unit data is very broad - including census, education, health data and business, social, and labor force surveys.
-This type of research data is held within data archives or data libraries after it has been collected, so that it may be reused by future researchers.
-By its nature, record-unit data is highly confidential and access is often only permitted for qualified researchers who must apply for access.
-Researchers typically represent their results as aggregated data in form of multi-dimensional tables with only a few columns: so-called \emph{variables} such as \emph{sex} or \emph{age}.
-Aggregated data, which answers particular research questions, is derived from record-unit data by statistics on groups or aggregates such as frequencies and arithmetic means.
-The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying record-unit data.
-For more detailed analyses, researchers refer to record-unit data including additional variables needed to answer subsequent research questions.
-
-\emph{Formal childcare} is an example of an aggregated variable which captures the measured availability of childcare services in percent over the population in European Union member states by 
-the dimensions \emph{year}, \emph{duration}, \emph{age} of the child, and \emph{country}.
-Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
-The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger} or by a code list of age clusters (e.g., '0 to 10' and '11 to 20'). 
-The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e., multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}.
-%QB represents metadata on multi-dimensional aggregate data in two files: a \emph{qb:DataSet} and a \emph{qb:DataStructureDefinition}.
-A \emph{qb:DataStructureDefinition} contains metadata of the data collection.
-The variable \emph{formal childcare} is modeled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
-\emph{year}, \emph{duration}, \emph{age}, and \emph{country} are \emph{qb:dimensions}.
-Data values, i.e., the availability of childcare services in percent over the population, are collected in a \emph{qb:DataSet}. 
-Each data value is represented inside a \emph{qb:Observation} which contains values for each dimension. 
-%(e.g., the year in which \emph{formal childcare} has been determined).
-%\ke{Wieso springt das von einer sehr knappen Einführung direkt zu konkreten (beliebigen?) Variablen?
-Ich möchte wissen, wofür QB benutzt wird und gerne ein konkretes %Beispiel sehen, um mir einen Data Cube vorstellen zu können.}\tb{hmm, ich halte das beispiel für ein knappes und verständliches beipsiel wie eine tabelle in qb dargestellt wird / es ist auch der link enthalten zu der tabelle von eurostat}
-
-For more detailed analyses we refer to the underlying record-unit data.
-The aggregated variable \emph{formal childcare} is calculated on the basis of six record-unit variables (i.a., \emph{Education at pre-school}) for which detailed metadata is given (i.a., code lists) enabling researchers to replicate the results shown in aggregated data tables.
-\emph{DDI-RDF} is used to represent metadata on record-unit data in RDF.
-%The series (\emph{DDI-RDF:StudyGroup}) \emph{EU-SILC} contains one study (\emph{DDI-RDF:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
-%\emph{dcterms:spatial} points to the countries for which the data has been collected.
-The study for which the record-unit data has been collected 
-%\emph{EU-SILC 2011} 
-contains eight record-unit data sets (\emph{disco:LogicalDataSet})
-including variables (\emph{disco:Variable}) like the six ones needed to calculate the variable \emph{formal childcare}.
-%Metadata on record-unit data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
-%One common research question is ,e.g., the comparison of variables like 
-%\emph{formal childcare} between countries, for which the variable is collected within the context of an individual study, and other European or non European countries (e.g. OSCE).
-
-The \emph{Simple Knowledge Organization System (SKOS)} is reused multiple times to build \emph{SBE} vocabularies.
-The codes of the variable \emph{Education at pre-school} are modeled as \emph{skos:Concepts} and 
-a \emph{skos:OrderedCollection} organizes them in a particular order within a \emph{skos:memberList}.
-A variable may be associated with a theoretical concept (\emph{skos:Concept}) and \emph{skos:narrower} builds the hierarchy of theoretical concepts within a \emph{skos:ConceptScheme} of a study.
-The variable \emph{Education at pre-school} is assigned to the theoretical concept \emph{Child Care} which is a narrower concept of the top concept \emph{Education}.
-Controlled vocabularies (\emph{skos:ConceptScheme}), serving as extension and reuse mechanism,
-organize types (\emph{skos:Concept}) of descriptive statistics (\emph{disco:SummaryStatistics}) like minimum, maximum, and arithmetic mean.
-
-%% ---------------
-%% Backup of 'Common Vocabularies in SBE Sciences'
-%
-%
-%\section{Common Vocabularies in SBE Sciences}
-%\label{rdf-representation}
-%
-%\emph{SBE} sciences require high-quality data for their empirical research. For more than a decade, members of the \emph{SBE} community have been developing and using a
-%metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)},
-%an XML format to disseminate, manage,
-%and reuse data collected and archived for research \cite{Vardigan2008}. 
-%In XML, the definition of schemas containing data constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
-%With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration.
-Therefore, not only established vocabularies like SKOS are used;
-%recently, members of the \emph{SBE} and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.
-%
-%The data most often used in research within \emph{SBE} sciences is \emph{record-unit data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers
-%such as hospital records, registers of births and deaths. 
-%The range of record-unit data is very broad - 
-%including census, education, health data and business, social, and labor force surveys.  
-%This type of research data is
-%held within data archives or data libraries after it has been collected, so that it may be
-%reused by future researchers. 
-%
-%By its nature, record-unit data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 
-%Researchers typically represent their results as aggregated data in form of multi-dimensional tables with only a few columns; so-called \emph{variables} such as \emph{sex} or \emph{age}.
-%Aggregated data, which answers particular research questions, is derived from record-unit data by statistics on groups or aggregates such as frequencies and arithmetic means.
-%The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying record-unit data.
-%Aggregated data is published in form of CSV files,
-%allowing to perform calculations on the data.
-%
-%For more detailed analyses, researchers refer to record-unit data including additional variables needed to answer subsequent research questions
-%like the comparison of studies between countries.
-%A \emph{study} represents the process by which a data set was generated or collected.
-%Eurostat\footnote{\url{http://ec.europa.eu/eurostat}}, the statistical office of the European Union, provides research findings in form of aggregated data (downloadable as CSV files) and its metadata at European level that enable comparisons between countries.
-%The variable \emph{formal childcare}\footnote{Aggregated data and its metadata is available at: \url{http://ec.europa.eu/eurostat/web/products-datasets/-/ilc_caindformal}} %(in contrast to childcare at home)
-%captures the measured availability of childcare services in percent over the population in European Union member states by 
-%the variables \emph{year}, \emph{duration} (in hours per week), \emph{age} of the child, and \emph{country}.
-%Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
-%The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger} or by a code list of age clusters (e.g., '0 to 10' and '11 to 20'). 
-%
-%A very important and representative RDF validation case study within \emph{SBE} sciences is the comparison of variables between data collections of different countries.
-%Several vocabulary-specific constraints on RDF data are checked for each data collection
-%to determine if variables measuring \emph{age} 
-%- collected for different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
-%are comparable:
-%(1) variable definitions must be available, 
-%(2) for each code a human-readable label has to be specified,
-%(3) code lists must be structured properly, and
-%(4) code lists must either be identical or at least similar.
-%If a researcher only wants to get a first overview over the comparability of variables (use case 1), 
-%covering the first three constraints may be sufficient,
-%i.e., the violation of the first three constraints is more serious than the violation of the last constraint.
-%If the intention of the researcher is to perform more sophisticated comparisons (use case 2), however, the user may raise the severity level of the last constraint.
-%
-%We took all well-established and newly developed \emph{SBE} vocabularies into account and defined constraints for six vocabularies commonly used in or developed for the \emph{SBE} sciences which are briefly introduced in the following.
-%For three of them, we analyzed actual data according to constraint violations, as for these vocabularies large data sets are already published.
-%
-%The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e.
-multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}.
-%A \emph{qb:DataStructureDefinition} contains metadata of the data collection.
-%The variable \emph{formal childcare}, e.g., is modeled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
-%The variables \emph{year}, \emph{duration}, \emph{age}, and \emph{country} are \emph{qb:dimensions}.
-%Data values, i.e., the availability of childcare services in percent over the population, are collected in a \emph{qb:DataSet}. 
-%Each data value is represented inside a \emph{qb:Observation} which contains values for each dimension\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}}.
-%
-%\emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} is a vocabulary to represent data in tabular format in RDF enabling further aggregations and calculations.
-%The data could be either represented in records with character-separated values (CSV) or fixed length. 
-%
-%For more detailed analyses we refer to the record-unit data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}.
-%Where data collection is cyclic, data sets may be released as \emph{series}, 
-%where each cycle produces one or more data sets. 
-%The aggregated variable \emph{formal childcare} is calculated on the basis of six record-unit variables 
-%(e.g., \emph{Education at pre-school})
-%for which detailed metadata is given 
-%(e.g., code lists)
-%enabling researchers to replicate the results shown in aggregated data tables.
-%The \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)} is a vocabulary to represent metadata on record-unit data in RDF.
-%The series (\emph{DDI-RDF:StudyGroup}) \emph{EU-SILC} contains one study (\emph{DDI-RDF:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
-%\emph{dcterms:spatial} points to the countries for which the data has been collected.
-%The study \emph{EU-SILC 2011} contains eight record-unit data sets (\emph{DDI-RDF:LogicalDataSet})
-%including record-unit variables (\emph{DDI-RDF:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
-%
-%The \emph{Simple Knowledge Organization System (SKOS)} is reused multiple times to build \emph{SBE} vocabularies.
-%The codes of the variable \emph{Education at pre-school} (number of education hours per week) are modeled as \emph{skos:Concepts} and 
-%a \emph{skos:OrderedCollection} organizes them in a particular order within a \emph{skos:member} \emph{List}.
-%A variable may be associated with a theoretical concept (\emph{skos:Concept}). 
-%\emph{skos:narrower} builds the hierarchy of theoretical concepts within a \emph{skos:Concept} \emph{Scheme} of a series.
-%The variable \emph{Education at pre-school} is assigned to the theoretical concept \emph{Child Care} which is the narrower concept of \emph{Education} - one of the top concepts of the series \emph{EU-SILC}.
-%Controlled vocabularies (\emph{skos:ConceptScheme}), serving as extension and reuse mechanism,
-%organize types (\emph{skos:Concept}) of descriptive statistics (\emph{DDI-RDF:SummaryStatistics}) like minimum, maximum, and arithmetic mean.
-%\emph{XKOS}\footnote{\url{https://github.com/linked-statistics/xkos}} is a SKOS extension to describe formal statistical classifications like the International Standard Classification of Occupations (\emph{ISCO}).
-%and the Statistical Classification of Economic Activities in the European Community \emph{NACE}.
-%\emph{DCAT} enables to represent data sets inside of data collections like portals, repositories, catalogs, and archives
-%which serve as typical entry points when searching for data.
-
-% Backup of 'Common Vocabularies in SBE Sciences'
-% -----
 
@@
 Despite the large volume of the data set in general, we have to keep in mind that this study only uses data for three vocabularies.
-As described in Section~\ref{rdf-representation}, for other vocabularies there is often not (yet) enough data openly available to draw general conclusions.
+As described in Section~\ref{sbe-vocabularies}, for other vocabularies there is often not (yet) enough data openly available to draw general conclusions.
 The three vocabularies, however, are representative, cover different aspects of \emph{SBE} data and are also a mixture of established vocabularies (QB, SKOS) and a vocabulary under development (DDI-RDF).
@@
 %in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$).
-On the three vocabularies (DDI-RDF, QB, SKOS), we identified and classified 115 constraints\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} which we implemented for the data validation.
+On the three vocabularies (DDI-RDF, QB, SKOS), we identified and classified 115 constraints\footnote{All 115 implemented constraints online available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} which we implemented for the data validation.
 We ensured that the implementation of the constraints is equally distributed over the classes and vocabularies we have.
@@
 In a technical report, we describe the evaluation in further detail \cite{BoschZapilkoWackerowEckert2015-2}.
-Furthermore, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.
-\tb{why SPIN?}
-We use \emph{SPIN}, a SPARQL-based way to formulate and check constraints, as basis to develop a
-validation environment\footnote{Online demo available at: \url{http://purl.org/net/rdfval-demo}, source code at: \url{https://github.com/boschthomas/rdf-validator}} to validate RDF data according to constraints expressed by arbitrary constraint languages\footnote{SPIN mappings available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} \cite{BoschEckert2014-2}.
-
-The \emph{RDF Validator} can directly be used to validate arbitrary RDF data for the three vocabularies.
+Furthermore, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Online available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.
+
+Since the validation of each of the 81 constraint types can be implemented using SPARQL, we use \emph{SPIN}, a SPARQL-based way to formulate and check constraints, as basis to develop a
+validation environment to validate RDF data according to constraints expressed by arbitrary constraint languages\footnote{Constraint language implementations online available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} \cite{BoschEckert2014-2}.
+The \emph{RDF Validator}\footnote{Online demo available at: \url{http://purl.org/net/rdfval-demo}, source code at: \url{https://github.com/boschthomas/rdf-validator}} can directly be used to validate arbitrary RDF data for the three vocabularies.
 Additionally, own constraints on vocabularies can be defined using several constraint languages.
-
-%Although accessible within our validation tool, we provide all implemented constraints\footnote{\url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} in form of SPARQL CONSTRUCT queries.
 The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.

### 2015-07-23 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
classification

@@
 We let the experts classify the constraints according to the severity of their violation.
-Furthermore, we classified the type of each constraint based on whether it is expressible by RDFS/OWL, common high-level constraint languages, or only by plain SPARQL (see Chapter \ref{classification}).
+Furthermore, we classified each constraint type based on whether it is expressible by RDFS/OWL, common high-level constraint languages, or only by plain SPARQL (see Chapter \ref{classification}).
 
@@
 
-To gain better insights into the role that certain types of constraints play for the quality of RDF data, we use two simple classifications: on the one hand, we classify RDF constraint types whether they are expressible by different types of constraint languages and on the other hand, we classify constraints formulated for a given vocabulary according to the perceived severity of its violation.
+To gain better insights into the role that certain types of constraints play for the quality of RDF data, we use two simple classifications: on the one hand, we classify RDF constraint types whether they are expressible by different types of constraint languages and on the other hand, we classify constraints formulated for a given vocabulary according to the perceived severity of their violation.
 
@@
 The modeling languages RDFS and OWL are typically used to formally specify vocabularies.
-\emph{RDFS/OWL Based} denotes the set of constraint types which can be formulated with RDFS/OWL axioms which we use in terms of constraints with CWA/UNA semantics and without reasoning\footnote{The entailment regime is to be decided by the implementors.
+\emph{RDFS/OWL Based} denotes the set of constraint types which can be formulated with RDFS/OWL axioms which we use in terms of constraints with CWA/UNA semantics and without reasoning\footnote{The entailment regime is to be decided by the implementers.
 It is our point that reasoning affects validation and that a proper definition of the reasoning to be applied is needed.}.
@@
 %RDFS, and OWL as we consider RDFS and OWL as constraint languages when assuming CWA/UNA semantics without reasoning. 
-There is a strong overlap between \emph{RDFS/OWL Based} and \emph{Constraint Language Based} constraint types as in many cases constraint types are expressible by classical constraint languages and OWL.
+There is a strong overlap between \emph{RDFS/OWL} and \emph{Constraint Language Based} constraint types as in many cases constraint types are expressible by both classical constraint languages and OWL.
 SPARQL, however, is considered as a low-level implementation language in this context.
@@
 %\emph{Complex constraint types} encompass constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
-The set \emph{SPARQL Based} encompasses constraint types that are not expressible by RDFS/OWL or common constraint languages but by plain SPARQL.
+The set \emph{SPARQL Based} encompasses constraint types that are not expressible by RDFS/OWL or common high-level constraint languages but by plain SPARQL.
 For assessing the quality of thesauri, e.g., we concentrate on the graph-based structure and apply graph- and network-analysis techniques.
@@
 \end{ex}
-\emph{SPARQL Based} constraint types are today in most cases only expressible by plain SPARQL. Depending on their usefulness, a support in constraint languages should be considered.
+\emph{SPARQL Based} constraint types are today only expressible by plain SPARQL. Depending on their usefulness, a support in constraint languages should be considered.
 
@@
 We use the classification system of log messages in software development like \emph{Apache Log4j 2} \cite{Apache-2015}, the \emph{Java Logging API}\footnote{\url{http://docs.oracle.com/javase/7/docs/api/java/util/logging/Level.html}}, and the \emph{Apache Commons Logging API}\footnote{\url{http://commons.apache.org/proper/commons-logging/}} as many data practitioners also have experience in software development and software developers intuitively understand these levels.
-We simplify this commonly accepted classification system and distinguish the three severity levels \emph{informational}, \emph{warning} and \emph{error}.
+We simplify this commonly accepted classification system and distinguish the three severity levels (1) \emph{informational}, (2) \emph{warning} and (3) \emph{error}.
 %According to the default severity level of constraints, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:\ke{auch dieser satz macht keinen sinn für mich, ebensowenig wie die extrem erhellende auflistung, die gleich folgt...
@@
 %\end{itemize}
-Violations of \emph{informational constraints} point to desirable but not necessary data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies.
+Violations of \emph{informational} constraints point to desirable but not necessary data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies.
 %They are not seen as serious errors.
@@
 Note that there is a correlation between the severity of a constraint and the classification according to the expressivity of constraint languages of its type: \emph{RDFS/OWL Based} constraints are in many cases classified with an \emph{error} level as they typically represent basic and important constraints; there is a reason why they have been included in the vocabulary specification.
-Although we provide default severity levels for each constraint, validation environments should enable users to adapt the severity constraints' levels according to their individual needs.
+Although we provide default severity levels for each constraint, validation environments should enable users to adapt the severity levels of constraints according to their individual needs.
 % Validation environments should enable users to select which constraints to validate against depending on their individual use cases.
@@
 %which may indicate when the data is verbose/redundant or expressed at a too general level.
-Consider the following \emph{DL knowledge base} $\mathcal{K}$\footnote{A \emph{DL knowledge base} is a collection of formal statements which correspond to \emph{facts} or what is known explicitly.
-For simplicity reasons, we do not state namespace prefixes.}:
+Consider the following \emph{DL knowledge base} $\mathcal{K}$\footnote{A \emph{DL knowledge base} is a collection of formal statements which correspond to \emph{facts} or what is known explicitly. }:
 \begin{center}
@@
 %\end{DL}
-Only \emph{\textcolor{red}{dcat}:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets} (\emph{error}).
+%Only \emph{\textcolor{red}{dcat}:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets} (\emph{error}).
+Only \emph{qb:DataSets}, e.g., can have \emph{qb:structure} relationships to \emph{qb:DataStructureDefinitions} (\emph{error}).
 \emph{Property domains} (\emph{R-25, R-26}) and \emph{property ranges} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties:
-Only \emph{phdd:Tables}, e.g., can have \emph{\textcolor{red}{phdd}:isStructuredBy} relationships (\emph{error}) and \emph{\textcolor{red}{xkos}:belongsTo} relations can only point to \emph{skos:Concepts} (\emph{error}).
+%Only \emph{phdd:Tables}, e.g., can have \emph{\textcolor{red}{phdd}:isStructuredBy} relationships (\emph{error}) and \emph{\textcolor{red}{xkos}:belongsTo} relations can only point to \emph{skos:Concepts} (\emph{error}).
+Only \emph{skos:ConceptSchemes}, e.g., can have \emph{skos:hasTopConcept} relationships (\emph{error}) and \emph{disco:variable} relations can only point to \emph{disco:Variables} (\emph{error}).
 
@@
 as a key can be a data property, an object property, or a chain of properties \cite{Schneider2009}.
-Thus and as there are different sorts of key, and as keys can lead to undecidability, 
+For this reason, as there are different sorts of key, and as keys can lead to undecidability, 
 DL is extended with the construct \emph{keyfor} ({\small\ms{identifier \ms{keyfor} Resource}}) \cite{Lutz2005} which is implemented by the OWL 2 \emph{hasKey} construct.
@@
 %\textbf{Validation and Reasoning.}
-
 Depending on property datatypes, two different literal values have
@@
 
-\emph{Default values} (\emph{R-31, R-38}) for objects/literals of given properties are inferred automatically when properties are not present in the data.
+\emph{Default values} for objects (\emph{R-31}) or literals (\emph{R-38}) of given properties are inferred automatically when properties are not present in the data.
 The value \emph{true} for the property {\em disco:isPublic} indicates that a {\em disco:LogicalDataSet} can be accessed by anyone.
@@
 %$\mathcal{CT}_{C}$ denotes the set of constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
-\emph{Data model consistency} constraints ensure the integrity of
+The purpose of \emph{data model consistency} constraints is to ensure the integrity of
 the data according to the intended semantics of vocabularies.

### 2015-07-23 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
finalized paper

@@
 As described in Section~\ref{sbe-vocabularies}, for other vocabularies there is often not (yet) enough data openly available to draw general conclusions.
-The three vocabularies, however, are representative, cover different aspects of \emph{SBE} data and are also a mixture of established vocabularies (QB, SKOS) and a vocabulary under development (DDI-RDF).
+The three vocabularies, however, are representative, cover different aspects of \emph{SBE} data and are also a mixture of widely adopted and accepted well-established vocabularies (QB, SKOS) and a vocabulary under development (DDI-RDF\footnote{Expected publication at the end of the year 2015}).
 Due to this limitation, we will present several hypotheses together with a rationale based on the results for the three vocabularies.
@@
 %in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$).
-On the three vocabularies (DDI-RDF, QB, SKOS), we identified and classified 115 constraints\footnote{All 115 implemented constraints online available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} which we implemented for the data validation.
+On the three vocabularies (DDI-RDF, QB, SKOS), we identified and classified 115 constraints\footnote{All 115 implemented constraints online available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} which we implemented for data validation.
 We ensured that the implementation of the constraints is equally distributed over the classes and vocabularies we have.
@@
 
-QB and SKOS are well-established vocabularies which are widely adopted and accepted. DDI-RDF is a newly developed vocabulary which will be published in 2015.
+%QB and SKOS are well-established vocabularies which are widely adopted and accepted. DDI-RDF is a newly developed vocabulary which will be published in 2015.
 
@@
 (3) DDI-RDF data sets provided by the \emph{Microdata Information System}, 
-the \emph{Data Without Boundaries DDI-RDFvery Portal}, the
+the \emph{Data Without Boundaries Discovery Portal}, the
 \emph{Danish Data Archive}, and the
 \emph{Swedish National Data Service}.
+In a technical report, we describe the evaluation in further detail \cite{BoschZapilkoWackerowEckert2015-2}.
+Furthermore, we published the evaluation results for each QB data set in form of one document per SPARQL endpoint\footnote{Online available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.
 
@@
 \end{table}
-
-In a technical report, we describe the evaluation in further detail \cite{BoschZapilkoWackerowEckert2015-2}.
-Furthermore, we published the evaluation results for each data set in form of one document per SPARQL endpoint\footnote{Online available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.
 
@@
 %Table \ref{tab:evaluation-constraint-types} displays the evaluation of the metadata quality on real world data sets regarding constraint types.
-Tables \ref{tab:evaluation-constraint-violations-1} and \ref{tab:evaluation-constraint-violations-2} show the results of the evaluation, more specifically the constraints and the constraint violations, which are caused by these constraints, in percent.
-The first numbers indicate the absolute amount of constraints and violations.
-The constraints and their raised violations are grouped by vocabulary, which type of language the constraints are expressed with, and their severity level.
+Tables \ref{tab:evaluation-constraint-violations-1} and \ref{tab:evaluation-constraint-violations-2} show the results of the evaluation, more specifically the constraints and the constraint violations, which are caused by these constraints, in percent; whereas the first numbers indicate the absolute amount of constraints and violations.
+The constraints and their raised violations are grouped by vocabulary, which type of language the constraint types are formulated with, and their severity level.
 The numbers of evaluated triples and data sets differ between the vocabularies
@@
 		\label{tab:evaluation-constraint-violations-1}
-    \begin{tabular}{@{}lcccc@{}}
+    \begin{tabular}{@{}lcc|cc@{}}
     %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
     %\\  \cmidrule{2-3}
-		\hline
+		%\hline
     \multirow{2}{*}{} &
@@
 		\label{tab:evaluation-constraint-violations-2}
-    \begin{tabular}{@{}lcccc@{}}
+    \begin{tabular}{@{}lcc|cc@{}}
     %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
     %\\  \cmidrule{2-3}
-		\hline
+		%\hline
     \multirow{2}{*}{} &
@@
 		\label{tab:evaluation-expressivity-severity}
-    \begin{tabular}{@{}lcccccc@{}}
+    \begin{tabular}{@{}lcc|cc|cc@{}}
     %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
     %\\  \cmidrule{2-3}
-		\hline
+		%\hline
     \multirow{3}{*}{} &
@@
 we formulated several hypotheses to direct the further development of constraint languages.
-We regard to the results as hypotheses, as their general applicability beyond the examined vocabularies and for other domains is still to be confirmed.
+We regard the results as hypotheses, as their general applicability beyond the examined vocabularies and for other domains is still to be confirmed.
 The main hypotheses are:

### 2015-07-23 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
finalized paper

@@
 \newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}
-\newcommand{\er}[1]{\todo[size=\small, color=blue!40]{\textbf{Erman:} #1}}
+\newcommand{\bz}[1]{\todo[size=\small, color=blue!40]{\textbf{Erman:} #1}}
 
@@
 In contrast to SPARQL, high-level constraint languages are comparatively easy to understand and constraints can be formulated more concisely.
-Declarative languages may be placed on top of SPARQL when using it as an implementation languages.
+Declarative languages may be placed on top of SPARQL when using it as an implementation language.
 For these \emph{Constraint Language Based} constraints, we expect a straight-forward support in future constraint languages.
@@
 As described in Section~\ref{sbe-vocabularies}, for other vocabularies there is often not (yet) enough data openly available to draw general conclusions.
-The three vocabularies, however, are representative, cover different aspects of \emph{SBE} data and are also a mixture of widely adopted and accepted well-established vocabularies (QB, SKOS) and a vocabulary under development (DDI-RDF\footnote{Expected publication at the end of the year 2015}).
+The three vocabularies, however, are representative, cover different aspects of \emph{SBE} data, and are also a mixture of widely adopted and accepted well-established vocabularies (QB, SKOS) and a vocabulary under development (DDI-RDF\footnote{Expected publication at the end of the year 2015}).
 Due to this limitation, we will present several hypotheses together with a rationale based on the results for the three vocabularies.

### 2015-07-24 paper/paper 2/dc-2015.tex
Tom's review

@@
 \section*{Abstract}
-In the context of the DCMI RDF Application Profile task group and the W3C Data Shapes Working Group solutions for the proper formulation of constraints and validation of RDF data on these constraints are developed.
+In the context of the DCMI RDF Application Profile task group and the W3C Data Shapes Working Group solutions for the proper formulation of constraints and validation of RDF data on these constraints are being developed.
 Several approaches and constraint languages exist but there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners.
 To support the work, a comprehensive, community-driven database has been created where case studies, use cases, requirements and solutions are collected. Based on this database,
-we published by today 81 types of constraints that are required by various stakeholders for data applications.
-We generally use this collection of constraint types to gain a better understanding of the expressiveness of existing solutions and gaps that still need to be filled.
-Regarding the implementation of constraint languages, we already proposed to use high-level languages to describe the constraints, but map them to SPARQL queries in order to execute the actual validation; we demonstrated this approach for the Web Ontology Language in its current version 2 and Description Set Profiles.
+we have hitherto published 81 types of constraints that are required by various stakeholders for data applications.
+We are using this collection of constraint types to gain a better understanding of the expressiveness of existing solutions and gaps that still need to be filled.
+Regarding the implementation of constraint languages, we have already proposed to use high-level languages to describe the constraints, but map them to SPARQL queries in order to execute the actual validation; we have demonstrated this approach for the Web Ontology Language in its current version 2 and Description Set Profiles.
 In this paper, we generalize from the experience of implementing OWL 2 and DSP by introducing an abstraction layer that is able to describe constraints of any constraint type in a way that mappings from high-level constraint languages to this intermediate representation can be created more or less straight-forwardly.
@@
 %for RDF data validation and constraint formulation.
-In 2014, two working groups on RDF validation have been established: 
+In 2014, two working groups on RDF validation were established: 
 the \emph{W3C RDF Data Shapes Working Group}\footnote{\url{http://www.w3.org/2014/rds/charter}} and the \emph{DCMI RDF Application Profiles Task Group}\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.

### 2015-07-24 paper/paper 2/dc-2015.tex
feedback Kai

@@
 
-The properties describing a simple constraint are very structural\tb{Kai, do you mean structured?}.
+The properties describing a simple constraint are very structural, i.e., the properties describe the structure of constraints.
 The central property is the \emph{constraining element} which refers to one of 103 constraining elements described in our technical report \cite{BoschNolleAcarEckert2015}.
@@
 
-In this paper, we outlined our idea of a general framework to support the mapping of high-level constraint languages to a generic representation, which subsequently can be used to generate validating SPIN/SPARQL queries to actually validate data against constraints provided in the high-level language.\tb{Aus der generischen Repräsentierung können die SPIN mappings zur Validierung generiert werden?
-das verstehe ich nicht} The framework consists of a very simple conceptual model using the \emph{RDF Constraints Vocabulary (RDF-CV)} which has been introduced in this paper.
+In this paper, we outlined our idea of a general framework to support the mapping of high-level constraint languages to a generic representation, which can directly be validated by providing a mapping from the generic representation to SPIN/SPARQL queries to actually validate data against constraints provided in the high-level language.
+The framework consists of a very simple conceptual model using the \emph{RDF Constraints Vocabulary (RDF-CV)} which has been introduced in this paper.
 The core of the framework is the definition of 103 constraining elements that are used to define constraints of all 81 constraint types that to date have been identified within the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group.
@@
   \item to implement the validation of constraints consistently across constraint languages,
-  \item to support the extension of constraint languages by means of a simple mapping\tb{was genau meinst du damit? wenn weitere constraint typen unterstützt werden sollen?}, and
+  \item to support the extension of constraint languages when additional constraint types should be supported by means of a simple mapping, and
   \item to enhance or rather establish the interoperability of different constraint languages.

### 2015-07-26 paper/paper 2/dc-2015.tex
Final read-through Kai

@@
 In 2014, two working groups on RDF validation were established: 
-the \emph{W3C RDF Data Shapes Working Group}\footnote{\url{http://www.w3.org/2014/rds/charter}} and the \emph{DCMI RDF Application Profiles Task Group}\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}.
+the \emph{W3C RDF Data Shapes Working Group}\footnote{\url{http://www.w3.org/2014/rds/charter}} and the \emph{DCMI RDF Application Profiles Task Group}.\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}}
 We collected the findings of these working groups and initiated a database of RDF validation requirements\footnote{Online available at: \url{http://purl.org/net/rdf-validation}}
@@
 For our work, we focus on the following four as the ones that are most popular among data practitioners, often mentioned on mailing lists and/or being candidates or prototypes for the upcoming W3C recommendation:
-\emph{Description Set Profiles (DSP)}\footnote{\url{http://dublincore.org/documents/2008/03/31/dc-dsp/}}, \emph{Resource Shapes (ReSh)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shapes-20140211/}}, \emph{Shape Expressions (ShEx)}\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}}, and the \emph{Web Ontology Language} \emph{(OWL)}\footnote{\url{http://www.w3.org/TR/owl2-syntax/}}.
-Despite the fact that OWL is arguably not a constraint language, it is widely used in practice as such under the closed-world and unique name assumptions.
+\emph{Description Set Profiles (DSP)},\footnote{\url{http://dublincore.org/documents/2008/03/31/dc-dsp/}} \emph{Resource Shapes (ReSh)},\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shapes-20140211/}} \emph{Shape Expressions (ShEx)},\footnote{\url{http://www.w3.org/Submission/2014/SUBM-shex-primer-20140602/}} and the \emph{Web Ontology Language} \emph{(OWL)}.\footnote{\url{http://www.w3.org/TR/owl2-syntax/}} Despite the fact that OWL is arguably not a constraint language, it is widely used in practice as such under the closed-world and unique name assumptions.
 
@@
 We formerly demonstrated that a high-level constraint language like OWL 2 and DSP can be implemented by mapping the language to SPIN using SPARQL CONSTRUCT queries \cite{BoschEckert2014-2}.
-We provide a validation environment where own mappings from arbitrary constraint languages can be provided and tested\footnote{Online available at: \url{http://purl.org/net/rdfval-demo}, source code online available at: \url{https://github.com/boschthomas/rdf-validator}.}.
-The only limitations are that the constraints have to
+We provide a validation environment where own mappings from arbitrary constraint languages can be provided and tested.\footnote{Online available at: \url{http://purl.org/net/rdfval-demo}, source code online available at: \url{https://github.com/boschthomas/rdf-validator}.} The only limitations are that the constraints have to
 be expressed in RDF and that the constraint language is expressible in SPARQL.
@@
 
-Note that the SPIN representation of the constraint is NOT a SPIN mapping to implement the constraint, but a direct expression of the constraint using a SPARQL CONSTRUCT query that creates a spin:ConstraintViolation if the constraint is violated.
+Note that the SPIN representation of the constraint is \emph{not} a SPIN mapping to implement the constraint, but a direct expression of the constraint using a SPARQL CONSTRUCT query that creates a spin:ConstraintViolation if the constraint is violated.
 
@@
 
-The SPIN mappings for OWL 2 and DSP are rather complicated and can be found in the mappings provided by us\footnote{OWL 2 mapping online available at: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/OWL2_SPIN-Mapping.ttl}; DSP mapping online available at: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/DSP_SPIN-Mapping.ttl#L4665}}.
+The SPIN mappings for OWL 2 and DSP are rather complicated and can be found in the mappings provided by us.\footnote{OWL 2 mapping online available at: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/OWL2_SPIN-Mapping.ttl}; DSP mapping online available at: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/DSP_SPIN-Mapping.ttl#L4665}}
 
@@
 \paragraph{Constraint transformation.} Consistent implementations of constraint languages provide some advantage, but it could be argued that they are not important enough to justify the additional layer.
-The situation, however, is different when transformations from one constraint language to another are desired, i.e., to transform a \emph{specific constraint} (\emph{$sc_{\alpha}$}) of any constraint type expressed by language \emph{$\alpha$} into a semantically equivalent \emph{specific constraint} (\emph{$sc_{\beta}$}) of the same constraint type represented by any other language \emph{$\beta$}.
+The situation, however, is different when transformations from one constraint language to another are desired, i.e., to transform a \emph{specific constraint} \emph{$sc_{\alpha}$} of any constraint type expressed by language \emph{$\alpha$} into a semantically equivalent \emph{specific constraint} \emph{$sc_{\beta}$} of the same constraint type represented by any other language \emph{$\beta$}.
 By defining mappings between equivalent \emph{specific constraints} and the corresponding \emph{generic constraint} (\emph{gc}) we are able to convert them automatically: 
 \begin{align*}
-  gc &=  m_1(sc_{\alpha}) \\
-  sc_{\beta} &= m_2'(gc) 
+  gc &=  m_{\alpha}(sc_{\alpha}) \\
+  sc_{\beta} &= m_{\beta}'(gc) 
 \end{align*}
@@
 With an intermediate generic representation of constraints, on the other side, we only need to define for each constraint type $2n = 20$ mappings -- where $10$ mappings should already exist if we have an implementation in our framework.
-To summarize, if language developers are willing to provide two mappings -- forward and backward -- to our framework for each supported constraint type, we not only would get the consistent implementation of all languages, it would also be possible to transform semantically equivalent constraints into all constraint languages.
+To summarize, if language developers are willing to provide two mappings -- forward ($m$) and backward ($m'$) -- to our framework for each supported constraint type, we not only would get the consistent implementation of all languages, it would also be possible to transform semantically equivalent constraints into all constraint languages.
 
@@
 
-At the core, we use a very simple conceptual model for constraints (see Figure \ref{fig:RDF-CV-conceptual-model}), using a small lightweight vocabulary called \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Formal specification and HTML documentation online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.
+At the core, we use a very simple conceptual model for constraints (see Figure \ref{fig:RDF-CV-conceptual-model}), using a small lightweight vocabulary called \emph{RDF Constraints Vocabulary (RDF-CV)}.\footnote{Formal specification and HTML documentation online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}
 \begin{figure}[H]
@@
 
-A cornerstone of the framework is the generic representation of a constraint, which can often be done using Description Logics, as for the \emph{minimum qualified cardinality restriction} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person.}}  This way, the knowledge representation formalism \emph{Description Logics (DL)} \cite{Kroetzsch2012,Baader-2003,Baader-Nutt-2003} with its well-studied theoretical properties provides the foundational basis for the framework.
+A cornerstone of the framework is the generic representation of a constraint, which can often be done using Description Logics.
+For example the \emph{minimum qualified cardinality restriction} can be expressed as {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}}.
+This way, the knowledge representation formalism \emph{Description Logics (DL)} \cite{Kroetzsch2012,Baader-2003,Baader-Nutt-2003} with its well-studied theoretical properties provides the foundational basis for the framework.
 
@@
 
-For the purpose of a consistent implementation and transformation of constraints, constraints are \emph{semantically equivalent} if they detect the same set of violations regardless of RDF data, which means whenever the constraints are applied to any RDF data they point out the same violations.
+For the purpose of a consistent implementation and transformation of constraints, constraints are considered \emph{semantically equivalent} if they detect the same set of violations regardless of RDF data, which means whenever the constraints are applied to any RDF data they point out the same violations.
 
@@
 Table \ref{tab:property-constraint-cardinality-restriction} displays how the simple constraint is generically represented using the RDF-CV. 
-Note that instead of the DL construct $\geq$, the constraining element \emph{minimum qualified cardinality restriction} may be used.
+% Note that instead of the DL construct $\geq$, the constraining element \emph{minimum qualified cardinality restriction} may be used.
 
@@
 The \emph{constraining element} is an intuitive term which indicates the actual type of constraint.
-For the majority of the constraint types, there is exactly one constraining element.
-Complex constraints need several constraining elements to be expressed.
-For the constraint type \emph{property domain (R-25, R-26)} whose constraints restrict domains of properties, e.g., there is only one constraining element with exactly the same identifier \emph{property domain}.
-For some constraint types, however, one constraining element is not sufficient to describe all possible constraints of a particular constraint type and therefore multiple constraining elements may be stated.
-The constraint type \emph{language tag cardinality (R-48, R-49)}, for instance, is used to restrict data properties to have a minimum, maximum, or exact number of relationships to literals with selected language tags.
+For the majority of the constraint types, there is exactly one constraining element, for instance \emph{property domain (R-25, R-26)} restricts domains of properties and there is only one constraining element with exactly the same identifier \emph{property domain}.
+Complex constraints, however, need several constraining elements to be expressed, for instance \emph{language tag cardinality (R-48, R-49)}\ke{ich hab das etwas umgestellt, bin mir aber nicht sicher, ob r-48/49 complex sind.
+Ggf.
+bitte anpassen, eventuell den satz oder absatz auch rausziehen vor "simple constraints", wenn da erst mal geklärt wird, was das ist.} is used to restrict data properties to have a minimum, maximum, or exact number of relationships to literals with selected language tags.
 Thus, three constraining elements are needed to express each possible constraint of that constraint type.
+This example also illustrates that the granularity of the constraint types varies and certainly often is debatable.
+Keep in mind that they correspond to requirements as identified by the working groups.
+The constraining elements, as in this example, are closer to atomic elements of constraints.
 
@@
 In case constraint types cannot be expressed in DL such as \emph{data property facets (R-46)} or \emph{literal pattern matching (R-44)}, we reuse widely known terms from SPARQL (e.g., REGEX) or XML Schema constraining facets (e.g., \emph{xsd:minInclusive}) as constraining elements.
-For some constraint types like \emph{minimum qualified cardinality restrictions (R-75)}, it is more intuitive and concise to directly apply DL constructs like the \emph{at-least restriction} ($\geq$) as constraining elements.
+% For some constraint types like \emph{minimum qualified cardinality restrictions (R-75)}, it is more intuitive and concise to directly apply DL constructs like the \emph{at-least restriction} ($\geq$) as constraining elements.
 We provide a complete list of all 103 constraining elements which can be used to express constraints of any constraint type \cite{BoschNolleAcarEckert2015}.
@@
 The constraining element of the constraint {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person},} e.g., is \emph{$\geq$}, the constraining value is \emph{1}, and the list of classes includes the class \emph{Person} which restricts the objects of the property \emph{author} to be persons.
-
-\emph{Left} and \emph{right property lists} are lists usually containing properties the constraint is applied to.
+%\emph{Left} and \emph{right property lists} are lists usually containing properties the constraint is applied to.
 A typical example for a constraint with a right hand side list of properties would be a constraint of the type \emph{literal value comparison (R-43)} to express that birth dates must be before death dates ({\small\ms{birthDate $<$ deathDate}}).
-The assignment of properties to these lists happens relative to the constraining element.
+The assignment of properties to the left or right property lists depends on the constraining element.
+
 \emph{Object property paths} (\emph{R-55}) ensure that if an individual \emph{x} is connected by a sequence of object properties with an individual \emph{y}, 
@@
 
-Even though, constraints of the type \emph{literal pattern matching} cannot be expressed in DL, OWL 2 can be used to formulate this constraint:
+Even though constraints of the type \emph{literal pattern matching} cannot be expressed in DL, OWL 2 can be used to formulate this constraint:
 
@@
 \end{table}
+\ke{eins der isbn- in der tabelle ist doch falsch, oder? inverse von isbn- ist doch isbn...}
 
@@
 Complex constraints of frequently used constraint types which correspond to DL axioms like \emph{transitivity}, \emph{symmetry}, \emph{asymmetry}, \emph{reflexivity} and \emph{irreflexivity} can also be simplified in form of simple constraints.
-Although, these DL axioms are expressible by basic DL features, they can also be used in terms of syntactic sugar.
+Although these DL axioms are expressible by basic DL features, they can also be used in terms of syntactic sugar.
 
@@
 
-If a language developer would like to use the framework for the implementation of a constraint language or individual language constructs, the process is straight-forward.
-For a language construct, the corresponding constraint type has to be identified.
+Using the framework for the implementation of a constraint language is straight-forward.
+For each language construct, the corresponding constraint type has to be identified.
 Again we use the constraint {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}} of the type \emph{minimum qualified cardinality restrictions (R-75)} which is supported in OWL 2:
@@
 
-The framework and therefore the constraint types are implemented in exactly the same way by providing other SPIN mappings which encompass the SPIN/SPARQL queries that validate constraints and produce constraint violation messages if a constraint is violated, as described in our previous paper about the DSP implementation \cite{BoschEckert2014-2}\footnote{At the time of this writing, not all mappings for the constraint types are implemented, but of course the implementations can be complemented and adapted to own requirements, as needed.
-The most recent implementation can be found here: \url{https://github.com/boschthomas/rdf-validation/blob/master/SPIN/RDF-CV-2-SPIN.ttl}}.
+The framework and therefore the constraint types are implemented in exactly the same way by providing other SPIN mappings which encompass the SPIN/SPARQL queries that validate constraints and produce constraint violation messages if a constraint is violated, as described in our previous paper about the DSP implementation \cite{BoschEckert2014-2}.\footnote{At the time of this writing, not all mappings for the constraint types are implemented, but of course the implementations can be complemented and adapted to own requirements, as needed.
+The most recent implementation can be found here: \url{https://github.com/boschthomas/rdf-validation/blob/master/SPIN/RDF-CV-2-SPIN.ttl}}
 
@@
 
-OWL is an expressive language for which DL provides the foundational basis and which offers knowledge representation and reasoning services.
-Validation, however, is not the primary purpose of its design which has lead to claims that OWL cannot be used for validation.
+Because of the design of OWL for reasoning, there are claims that OWL cannot be used for validation.
 In practice, however, OWL is well-spread and RDFS/OWL constructs are widely used to tell people and applications about how valid instances should look like.

### 2015-07-27 paper/paper 2/dc-2015.tex
paper finalized

@@
 For the majority of the constraint types, there is exactly one constraining element, for instance \emph{property domain (R-25, R-26)} restricts domains of properties and there is only one constraining element with exactly the same identifier \emph{property domain}.
-Complex constraints, however, need several constraining elements to be expressed, for instance \emph{language tag cardinality (R-48, R-49)}\ke{ich hab das etwas umgestellt, bin mir aber nicht sicher, ob r-48/49 complex sind.
-Ggf.
-bitte anpassen, eventuell den satz oder absatz auch rausziehen vor "simple constraints", wenn da erst mal geklärt wird, was das ist.} is used to restrict data properties to have a minimum, maximum, or exact number of relationships to literals with selected language tags.
+Some constraint types, however, need several constraining elements to be expressed, for instance \emph{language tag cardinality (R-48, R-49)} is used to restrict data properties to have a minimum, maximum, or exact number of relationships to literals with selected language tags.
 Thus, three constraining elements are needed to express each possible constraint of that constraint type.
@@
 The \emph{primary key properties (R-226)} constraint type is often useful to declare a given (datatype) property as the primary key of a class, so that a system can enforce uniqueness. 
-Books, e.g., are uniquely identified by their ISBN, i.e., the property \emph{isbn} is inverse functional \ms{$(\ms{funct } isbn\sp{\overline{\ }})$}
+Books, e.g., are uniquely identified by their ISBN, i.e., the property \emph{isbn} is inverse functional {\small\ms{$(\ms{funct } isbn\sp{\overline{\ }})$}}
 which can be represented using the RDF-CV in form of a complex constraint consisting of two simple constraints (see Table \ref{tab:primary-key-properties-as-complex-constraints}).
+The meaning of these simple constraints is that ISBN identifiers can only have {\small\ms{$isbn\sp{\overline{\ }}$}} relations to at most one distinct book.
 
@@
 %\end{gcotable}
+
+%\begin{table}[H]
+  %\scriptsize
+  %\sffamily
+  %\vspace{0cm}
+	%\caption{Primary Key Properties as Complex Constraints}
+	%\label{tab:primary-key-properties-as-complex-constraints}
+	%\centering
+		%\begin{tabular}{c|c|c|c|c|c}
+      %\textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
+      %\hline
+%$\top$ & isbn$^{-}$ & isbn & - & inverse property & - \\
+%Book & isbn$^{-}$ & - & - & functional property & - \\
+		%\end{tabular}
+%\end{table}
 
@@
       \hline
-$\top$ & isbn$^{-}$ & isbn$^{-}$ & - & inverse property & - \\
-Book & isbn$^{-}$ & - & - & functional property & - \\
+$\top$ & isbn$^{-}$ & isbn & - & inverse property & - \\
+Book & isbn$^{-}$ & - & - & $\leq$ & 1 \\
 		\end{tabular}
 \end{table}
-\ke{eins der isbn- in der tabelle ist doch falsch, oder? inverse von isbn- ist doch isbn...}
 

### 2015-07-28 paper/paper 2/dc-2015.tex
DC paper finalized

@@
       %\textbf{Expressivity Class} & $Expr(\overline{\mathcal{CT}_R})$ (42) & $Expr(\mathcal{CT}_R)$ (32) \\		
-			\emph{DSP} & \emph{ReSh} & \emph{ShEx} & OWL 2 & \emph{SPIN} \\	
+			DSP & ReSh & ShEx & OWL 2 & SPIN \\	
       \hline
@@
 
-The constraint type \emph{minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75}\footnote{Requirements are identified in the database by an R and a number, additionally an alphanumeric identifier is provided, in this case R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES.
+The constraint type \emph{minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75}\footnote{Requirements are identified in the database by an R and a number, additionally an alphanumeric identifier is provided, in this case \emph{R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES}.
 Online at: \url{http://lelystad.informatik.uni-mannheim.de/rdf-validation/?q=node/82}} can be instantiated to formulate the constraint that publications must have at least one author which must be a person.
@@
 Our framework therefore provides a common ground that is solely based on the abstract definitions of the constraint types, as identified in our database. By providing a SPIN mapping
-for each constraint type\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}\label{RDF-CV-2-SPIN}}, it is ensured that the details of the SPIN implementation are consistent irrespective of the constraint language and that the validation leads always to exactly the same results.
+for each constraint type,\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}\label{RDF-CV-2-SPIN}} it is ensured that the details of the SPIN implementation are consistent irrespective of the constraint language and that the validation leads always to exactly the same results.
 
@@
 Constraints of the \emph{irreflexive object properties (R-60)} constraint type ensure that no individual is connected by a given object property to itself \cite{Kroetzsch2012}.
-With the irreflexive object property constraint {\small\ms{$\top$ $\sqsubseteq$ $\neg$ $\exists authorOf.Self$}}, e.g., one can state that individuals cannot be authors of themselves.
+With the irreflexive object property constraint {\small\ms{$\top$ $\sqsubseteq$ $\neg$$\exists authorOf.Self$}}, e.g., one can state that individuals cannot be authors of themselves.
 When represented using the RDF-CV, the complex constraint aggregates three simple constraints (see Table \ref{tab:irreflexive-object-properties-as-complex-constraints}).
@@
 $\exists$ authorOf.Self & authorOf & - & Self & existential quantification & - \\
-$\neg$ $\exists$ authorOf.Self & - & - & $\exists$ authorOf.Self & negation & - \\
-$\top$ & - & - & $\top$, $\neg$ $\exists$ authorOf.Self & sub-class & - \\
+$\neg$$\exists$ authorOf.Self & - & - & $\exists$ authorOf.Self & negation & - \\
+$\top$ & - & - & $\top$, $\neg$$\exists$ authorOf.Self & sub-class & - \\
 		\end{tabular}
@@
 
-The \emph{Dublin Core Application Profile (DCAP)} and \emph{Bibframe Profiles} are approaches to specify \emph{profiles} for application-specific purposes.
+The \emph{Dublin Core Application Profile (DCAP)} and \emph{Bibframe Profiles} are approaches to specify profiles for application-specific purposes.
 The term \emph{profile} is widely used to refer to a document that describes how standards or specifications are deployed to support the requirements of a particular application, function, community, or context.

### 2015-08-12 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
unit-record

@@
 %We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
-%how data in tabular format and metadata on record-unit data sets, aggregated data sets, and thesauri are represented in RDF, 
+%how data in tabular format and metadata on unit-record data sets, aggregated data sets, and thesauri are represented in RDF, 
 %how therefore reused vocabularies are interrelated (section \ref{rdf-representation}),
@@
 
-The data most often used in research within \emph{SBE} sciences is \emph{record-unit data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers such as hospital records, registers of births and deaths.
+The data most often used in research within \emph{SBE} sciences is \emph{unit-record data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers such as hospital records, registers of births and deaths.
 A \emph{study} represents the process by which a data set was generated or collected.
-The range of record-unit data is very broad - including census, education, health data and business, social, and labor force surveys.
+The range of unit-record data is very broad - including census, education, health data and business, social, and labor force surveys.
 This type of research data is held within data archives or data libraries after it has been collected, so that it may be reused by future researchers.
-By its nature, record-unit data is highly confidential and access is often only permitted for qualified researchers who must apply for access.
+By its nature, unit-record data is highly confidential and access is often only permitted for qualified researchers who must apply for access.
 Researchers typically represent their results as aggregated data in form of multi-dimensional tables with only a few columns: so-called \emph{variables} such as \emph{sex} or \emph{age}.
-Aggregated data, which answers particular research questions, is derived from record-unit data by statistics on groups or aggregates such as frequencies and arithmetic means.
-The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying record-unit data.
-For more detailed analyses, researchers refer to record-unit data including additional variables needed to answer subsequent research questions.
+Aggregated data, which answers particular research questions, is derived from unit-record data by statistics on groups or aggregates such as frequencies and arithmetic means.
+The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying unit-record data.
+For more detailed analyses, researchers refer to unit-record data including additional variables needed to answer subsequent research questions.
 
@@
 
-For more detailed analyses we refer to the underlying record-unit data.
+For more detailed analyses we refer to the underlying unit-record data.
 The aggregated variable \emph{formal childcare} is calculated on the basis of six record-unit variables (i.a., \emph{Education at pre-school}) for which detailed metadata is given (i.a., code lists) enabling researchers to replicate the results shown in aggregated data tables.
-\emph{DDI-RDF} is used to represent metadata on record-unit data in RDF.
+\emph{DDI-RDF} is used to represent metadata on unit-record data in RDF.
 %The series (\emph{DDI-RDF:StudyGroup}) \emph{EU-SILC} contains one study (\emph{DDI-RDF:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
 %\emph{dcterms:spatial} points to the countries for which the data has been collected.
-The study (\emph{disco:Study}) for which the record-unit data has been collected 
+The study (\emph{disco:Study}) for which the unit-record data has been collected 
 %\emph{EU-SILC 2011} 
@@
 including variables (\emph{disco:Variable}) like the six ones needed to calculate the variable \emph{formal childcare}.
-%Metadata on record-unit data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
+%Metadata on unit-record data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
 %One common research question is ,e.g., the comparison of variables like 
@@
 %
-%The data most often used in research within \emph{SBE} sciences is \emph{record-unit data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers
+%The data most often used in research within \emph{SBE} sciences is \emph{unit-record data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers
 %such as hospital records, registers of births and deaths. 
-%The range of record-unit data is very broad - 
+%The range of unit-record data is very broad - 
 %including census, education, health data and business, social, and labor force surveys.  
@@
 %
-%By its nature, record-unit data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 
+%By its nature, unit-record data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 
 %Researchers typically represent their results as aggregated data in form of multi-dimensional tables with only a few columns; so-called \emph{variables} such as \emph{sex} or \emph{age}.
-%Aggregated data, which answers particular research questions, is derived from record-unit data by statistics on groups or aggregates such as frequencies and arithmetic means.
-%The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying record-unit data.
+%Aggregated data, which answers particular research questions, is derived from unit-record data by statistics on groups or aggregates such as frequencies and arithmetic means.
+%The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying unit-record data.
 %Aggregated data is published in form of CSV files,
@@
 %
-%For more detailed analyses, researchers refer to record-unit data including additional variables needed to answer subsequent research questions
+%For more detailed analyses, researchers refer to unit-record data including additional variables needed to answer subsequent research questions
 %like the comparison of studies between countries.
@@
 %
-%For more detailed analyses we refer to the record-unit data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}.
+%For more detailed analyses we refer to the unit-record data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}.
 %Where data collection is cyclic, data sets may be released as \emph{series}, 
@@
 %enabling researchers to replicate the results shown in aggregated data tables.
-%The \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)} is a vocabulary to represent metadata on record-unit data in RDF.
+%The \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)} is a vocabulary to represent metadata on unit-record data in RDF.
 %The series (\emph{DDI-RDF:StudyGroup}) \emph{EU-SILC} contains one study (\emph{DDI-RDF:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
 %\emph{dcterms:spatial} points to the countries for which the data has been collected.
-%The study \emph{EU-SILC 2011} contains eight record-unit data sets (\emph{DDI-RDF:LogicalDataSet})
+%The study \emph{EU-SILC 2011} contains eight unit-record data sets (\emph{DDI-RDF:LogicalDataSet})
 %including record-unit variables (\emph{DDI-RDF:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
@@
 %
-%As we know that only record-unit data sets (\emph{DDI-RDF:LogicalDataSet}) can derive (\emph{DDI-RDF:aggregation}) aggregated data sets (\emph{qb:DataSet}), 
+%As we know that only unit-record data sets (\emph{DDI-RDF:LogicalDataSet}) can derive (\emph{DDI-RDF:aggregation}) aggregated data sets (\emph{qb:DataSet}), 
 %{\em logical-data-set} is a \emph{DDI-RDF:LogicalDataSet}, 
@@
 %With \emph{subsumption} (\emph{R-100}), one can state that \emph{DDI-RDF:LogicalDataSet} is a sub-class of \emph{dcat:DataSet}, 
-%i.e., each record-unit data set is also a catalog data set.
-%Thus, constraints on catalog data sets are also validated for record-unit data sets;
-%e.g., the \emph{existential quantification} below restricting that record-unit data sets must have a distribution:
+%i.e., each unit-record data set is also a catalog data set.
+%Thus, constraints on catalog data sets are also validated for unit-record data sets;
+%e.g., the \emph{existential quantification} below restricting that unit-record data sets must have a distribution:
 
@@
 %- for each code list there should be a description.
-%- there should be a relationship to the underlying record-unit data.
+%- there should be a relationship to the underlying unit-record data.
 %
@@
 
-%In this paper, we showed in form of a complete real world running example how to represent metadata on record-unit data (DDI-RDF), metadata on aggregated data (QB), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
-%We explained why RDF validation is important in this context and how metadata on record-unit data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality\footnote{The first appendix of this paper describing each constraint in detail is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}} (\textbf{contribution 2}, section \ref{rdf-validation}).
+%In this paper, we showed in form of a complete real world running example how to represent metadata on unit-record data (DDI-RDF), metadata on aggregated data (QB), and data on both aggregation levels in a rectangular format (\emph{PHDD}) in RDF and how therefore used vocabularies are interrelated (\textbf{contribution 1}, section \ref{rdf-representation}).
+%We explained why RDF validation is important in this context and how metadata on unit-record data, aggregated data, thesauri, and statistical classifications as well as data on both aggregation levels is validated against constraints to ensure high (meta)data quality\footnote{The first appendix of this paper describing each constraint in detail is available at: \url{http://arxiv.org/abs/1504.04479} \cite{BoschZapilkoWackerowEckert2015}} (\textbf{contribution 2}, section \ref{rdf-validation}).
 %We distinguish two validation types:

### 2015-08-12 paper/paper 2/dc-2015.tex
unit-record

@@
 
-It is part of future work to finalize the implementation of all 81 constraint types in our \emph{RDF Validator}, to fully map constraint languages to RDF-CV (first and foremost DSP and OWL 2) and of course keep the framework in sync with the ongoing work in the working groups.
+It is part of future work to finalize the implementation of all 81 constraint types in our \emph{RDF Validator}, to fully map constraint languages to the RDF-CV (first and foremost DSP and OWL 2), and of course to keep the framework in sync with the ongoing work in the working groups.
 

### 2015-09-09 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
findings

@@
 \usepackage{ntheorem}
-\newtheorem{hyp}{Hypothesis}
+\newtheorem{hyp}{Finding}
 
@@
 
-In 2013, the W3C organized the RDF Validation Workshop\footnote{\url{http://www.w3.org/2012/12/rdf-val/}}, 
+In 2013, the W3C organized the RDF Validation Workshop,\footnote{\url{http://www.w3.org/2012/12/rdf-val/}} 
 where experts from industry, government, and academia discussed first use cases for constraint formulation and RDF data validation.
 In 2014, two working groups on RDF validation have been established to develop a language to express constraints on RDF data: 
-the \emph{W3C RDF Data Shapes Working Group}\footnote{\url{http://www.w3.org/2014/rds/charter}} (33 participants of 19 organizations) and the \emph{DCMI RDF Application Profiles Task Group}\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}} (29 people of 22 organizations) which among others bundles the requirements of data institutions of the cultural heritage sector and the social, behavioural, and economic (\emph{SBE}) sciences and represents them in the W3C group.
+the \emph{W3C RDF Data Shapes Working Group}\footnote{\url{http://www.w3.org/2014/rds/charter}} (33 participants of 19 organizations) and the \emph{DCMI RDF Application Profiles Task Group}\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}} (29 people of 22 organizations) which among others bundles the requirements of data institutions of the cultural heritage sector and the \emph{social, behavioural, and economic (SBE)} sciences and represents them in the W3C group.
 
@@
 
-To gain a better understanding about the role of certain requirements for data quality and in order to direct the further development of constraint languages, we collected constraints for commonly used vocabularies in the \emph{SBE} domain (see Section \ref{sbe-vocabularies}), either from the vocabularies themselves or from domain and data experts.
-All in all, this lead to 115 constraints on three vocabularies.
+In this paper, we collected constraints for commonly used vocabularies in the SBE domain (see Section \ref{sbe-vocabularies}), either from the vocabularies themselves or from domain and data experts, in order to gain a better understanding about the role of certain requirements for data quality and to direct the further development of constraint languages.
+All in all, this lead to 115 constraints on three vocabularies
 We let the experts classify the constraints according to the severity of their violation.
@@
 As we do not want to base our conclusions on the evaluation of vocabularies and constraint definitions alone, we conducted a large-scale experiment.
-For all these 115 constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data on three common vocabularies in \emph{SBE} sciences (DDI-RDF, QB, SKOS) obtained from 33 SPARQL endpoints.
-%evaluated the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (\emph{SBE}) sciences obtained from 33 SPARQL endpoints.
+For all these 115 constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of SBE research data on three common vocabularies in SBE sciences (DDI-RDF, QB, SKOS) obtained from 33 SPARQL endpoints.
+%evaluated the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.
 Based on the evaluation results,
-we formulate several hypotheses to direct the further development of constraint languages.
+we formulate several findings to direct the further development of constraint languages.
 To make valid general statements for all vocabularies, however,
-the hypotheses still have to be verified or falsified
+these findings still have to be verified or falsified
 by evaluating the quality of data represented by more than three vocabularies (Section \ref{evaluation}).
@@
 %By defining a huge amount of constraints of the majority of the constraint types,   
-%we apply the developed classification system to several and different vocabularies from the \emph{SBE} domain to represent both metadata and data and therefore prove its generality.
-%A complex and complete real world running example from the \emph{SBE} domain serves to prove the claim that the developed classification system perfectly applies for diverse vocabularies.
+%we apply the developed classification system to several and different vocabularies from the SBE domain to represent both metadata and data and therefore prove its generality.
+%A complex and complete real world running example from the SBE domain serves to prove the claim that the developed classification system perfectly applies for diverse vocabularies.
 %%, i.e., that it does not matter which vocabularies are used to represent (meta)data and for which domains constraints are defined.
-%We describe why RDF validation is important for the \emph{SBE} community (section \ref{motivation}), 
+%We describe why RDF validation is important for the SBE community (section \ref{motivation}), 
 %how data in tabular format and metadata on unit-record data sets, aggregated data sets, and thesauri are represented in RDF, 
 %how therefore reused vocabularies are interrelated (section \ref{rdf-representation}),
-%and how \emph{SBE} (meta)data is validated against constraints of different constraint types (sections \ref{classification} - \ref{SPARQL-based-constraint-types}).
-%We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the \emph{SBE} domain represented by multiple vocabularies to get an understanding
+%and how SBE (meta)data is validated against constraints of different constraint types (sections \ref{classification} - \ref{SPARQL-based-constraint-types}).
+%We evaluated the (meta)data quality of large real world data sets (more than 4.2 billion triples and 15 thousand data sets) from the SBE domain represented by multiple vocabularies to get an understanding
 %(1) which sets of constraint types (on different levels of complexity) and 
@@
 In this paper, we discuss constraints on RDF data in general.
-Note that the data represented in RDF can be data in the sense of \emph{SBE} sciences, but also metadata about published or unpublished data.
+Note that the data represented in RDF can be data in the sense of SBE sciences, but also metadata about published or unpublished data.
 We generally refer to both simply as RDF data and only distinguish between data and metadata in the data set descriptions.
@@
 
-We took all well-established and newly developed \emph{SBE} vocabularies into account and defined constraints for three vocabularies commonly used in the \emph{SBE} sciences which are briefly introduced in the following.
+We took all well-established and newly developed SBE vocabularies into account and defined constraints for three vocabularies commonly used in the SBE sciences which are briefly introduced in the following.
 We analyzed actual data according to constraint violations, as for these vocabularies large data sets are already published.
 
-\emph{SBE} sciences require high-quality data for their empirical research. For more than a decade, members of the \emph{SBE} community have been developing and using a
+SBE sciences require high-quality data for their empirical research. For more than a decade, members of the SBE community have been developing and using a
 metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)},
@@
 Therefore, not only established vocabularies like SKOS are used;
-recently, members of the \emph{SBE} and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.
-
-The data most often used in research within \emph{SBE} sciences is \emph{unit-record data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers such as hospital records, registers of births and deaths.
+recently, members of the SBE and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.
+
+The data most often used in research within SBE sciences is \emph{unit-record data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers such as hospital records, registers of births and deaths.
 A \emph{study} represents the process by which a data set was generated or collected.
@@
 
-The \emph{Simple Knowledge Organization System (SKOS)} is reused multiple times to build \emph{SBE} vocabularies.
+The \emph{Simple Knowledge Organization System (SKOS)} is reused multiple times to build SBE vocabularies.
 The codes of the variable \emph{Education at pre-school} are modeled as \emph{skos:Concepts} and 
@@
 %
-%\emph{SBE} sciences require high-quality data for their empirical research. For more than a decade, members of the \emph{SBE} community have been developing and using a
+%SBE sciences require high-quality data for their empirical research. For more than a decade, members of the SBE community have been developing and using a
 %metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)},
@@
 Therefore, not only established vocabularies like SKOS are used;
-%recently, members of the \emph{SBE} and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.
-%
-%The data most often used in research within \emph{SBE} sciences is \emph{unit-record data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers
+%recently, members of the SBE and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.
+%
+%The data most often used in research within SBE sciences is \emph{unit-record data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers
 %such as hospital records, registers of births and deaths. 
@@
 %
-%A very important and representative RDF validation case study within \emph{SBE} sciences is the comparison of variables between data collections of different countries.
+%A very important and representative RDF validation case study within SBE sciences is the comparison of variables between data collections of different countries.
 %Several vocabulary-specific constraints on RDF data are checked for each data collection
@@
 %
-%We took all well-established and newly developed \emph{SBE} vocabularies into account and defined constraints for six vocabularies commonly used in or developed for the \emph{SBE} sciences which are briefly introduced in the following.
+%We took all well-established and newly developed SBE vocabularies into account and defined constraints for six vocabularies commonly used in or developed for the SBE sciences which are briefly introduced in the following.
 %For three of them, we analyzed actual data according to constraint violations, as for these vocabularies large data sets are already published.
@@
 %
-%The \emph{Simple Knowledge Organization System (SKOS)} is reused multiple times to build \emph{SBE} vocabularies.
+%The \emph{Simple Knowledge Organization System (SKOS)} is reused multiple times to build SBE vocabularies.
 %The codes of the variable \emph{Education at pre-school} (number of education hours per week) are modeled as \emph{skos:Concepts} and 
@@
 %Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
-For the three vocabularies, several \emph{SBE} domain experts determined the default severity level of the 115 concrete constraints, which we published in a technical report \cite{BoschZapilkoWackerowEckert2015}.
+For the three vocabularies, several SBE domain experts determined the default severity level of the 115 concrete constraints, which we published in a technical report \cite{BoschZapilkoWackerowEckert2015}.
 In the following, we summarize the results for the purpose of our evaluation.
@@
 %whereas, the violation of another constraint of the same type may be minor.
-\emph{SBE} experts determined the default \emph{severity level}\footnote{The possibility to define severity levels in vocabularies is in itself a requirement (\emph{R-158}).} for each of the 115 constraints to indicate how serious the violation of the constraint is.
+SBE experts determined the default \emph{severity level}\footnote{The possibility to define severity levels in vocabularies is in itself a requirement (\emph{R-158}).} for each of the 115 constraints to indicate how serious the violation of the constraint is.
 We use the classification system of log messages in software development like \emph{Apache Log4j 2} \cite{Apache-2015}, the \emph{Java Logging API}\footnote{\url{http://docs.oracle.com/javase/7/docs/api/java/util/logging/Level.html}}, and the \emph{Apache Commons Logging API}\footnote{\url{http://commons.apache.org/proper/commons-logging/}} as many data practitioners also have experience in software development and software developers intuitively understand these levels.
@@
 As described in Section~\ref{sbe-vocabularies}, for other vocabularies there is often not (yet) enough data openly available to draw general conclusions.
-The three vocabularies, however, are representative, cover different aspects of \emph{SBE} data, and are also a mixture of widely adopted and accepted well-established vocabularies (QB, SKOS) and a vocabulary under development (DDI-RDF\footnote{Expected publication at the end of the year 2015}).
-Due to this limitation, we will present several hypotheses together with a rationale based on the results for the three vocabularies.
-If the hypotheses hold generally is still to be determined, nevertheless they should provide valuable insights for future developments of constraint languages.
+The three vocabularies, however, are representative, cover different aspects of SBE data, and are also a mixture of widely adopted and accepted well-established vocabularies (QB, SKOS) and a vocabulary under development (DDI-RDF\footnote{Expected publication at the end of the year 2015}).
+Due to this limitation, we present several findings together with a rationale based on the results for the three vocabularies.
+If these findings hold generally is still to be determined, nevertheless they should provide valuable insights for future developments of constraint languages.
 
@@
 %in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$).
-On the three vocabularies (DDI-RDF, QB, SKOS), we identified and classified 115 constraints\footnote{All 115 implemented constraints online available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} which we implemented for data validation.
+On the three vocabularies (DDI-RDF, QB, SKOS), we identified and classified 115 constraints\footnote{All 115 implemented constraints are online available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} which we implemented for data validation.
 We ensured that the implementation of the constraints is equally distributed over the classes and vocabularies we have.
-We then evaluated the data quality of 15,694 data sets (4.26 billion triples) of \emph{SBE} research data using these 115 constraints, obtained from 33 SPARQL endpoints.
+We then evaluated the data quality of 15,694 data sets (4.26 billion triples) of SBE research data using these 115 constraints, obtained from 33 SPARQL endpoints.
 
@@
 
-Table~\ref{tab:datasets} lists the number of data sets and the overall sizes in terms of triples for each of the vocabularies. We validated, i.a., 
+Table~\ref{tab:datasets} lists the number of validated data sets and the overall sizes in terms of triples for each of the vocabularies. We validated, i.a., 
 (1) QB data sets published by the \emph{Australian Bureau of Statistics},
@@
 In a technical report, we describe the evaluation in further detail \cite{BoschZapilkoWackerowEckert2015-2}.
-Furthermore, we published the evaluation results for each QB data set in form of one document per SPARQL endpoint\footnote{Online available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}.
+Furthermore, we published the evaluation results for each QB data set in form of one document per SPARQL endpoint.\footnote{Online available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}
 
@@
     \begin{center}
-		\caption{Evaluated Data Sets for each Vocabulary}
+		\caption{Validated Data Sets for each Vocabulary}
 		\label{tab:datasets}
@@
 validation environment to validate RDF data according to constraints expressed by arbitrary constraint languages\footnote{Constraint language implementations online available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} \cite{BoschEckert2014-2}.
-The \emph{RDF Validator}\footnote{Online demo available at: \url{http://purl.org/net/rdfval-demo}, source code at: \url{https://github.com/boschthomas/rdf-validator}} can directly be used to validate arbitrary RDF data for the three vocabularies.
-Additionally, own constraints on vocabularies can be defined using several constraint languages.
+The \emph{RDF Validator}\footnote{Online demo available at: \url{http://purl.org/net/rdfval-demo}, source code online available at: \url{https://github.com/boschthomas/rdf-validator}} can directly be used to validate arbitrary RDF data for the three vocabularies.
+Additionally, own constraints on any vocabulary can be defined using several constraint languages.
 The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.
@@
 
-\subsection{Evaluation Results and Formulation of Hypotheses}
+\subsection{Evaluation Results and Formulation of Findings}
 
@@
 %Table \ref{tab:evaluation-constraint-types} displays the evaluation of the metadata quality on real world data sets regarding constraint types.
-Tables \ref{tab:evaluation-constraint-violations-1} and \ref{tab:evaluation-constraint-violations-2} show the results of the evaluation, more specifically the constraints and the constraint violations, which are caused by these constraints, in percent; whereas the first numbers indicate the absolute amount of constraints and violations.
+Tables \ref{tab:evaluation-constraint-violations-1} and \ref{tab:evaluation-constraint-violations-2} show the results of the evaluation, more specifically the constraints and the constraint violations, which are caused by these constraints, in percent; whereas the numbers in the first line indicate the absolute amount of constraints and violations.
 The constraints and their raised violations are grouped by vocabulary, which type of language the constraint types are formulated with, and their severity level.
-The numbers of evaluated triples and data sets differ between the vocabularies
-as we evaluated 3.8 billion QB, 480 million SKOS, and 10 million DDI-RDF triples.
-To be able to formulate hypotheses which apply for all vocabularies, 
-we only use normalized relative values representing the percentage of constraints and violations belonging to the respective set of constraint types.
-
-There is a strong overlap between \emph{RDFS/OWL} and \emph{Constraint Language Based} constraint types as in many cases constraint types are expressible by classical constraint languages and OWL.
+The numbers of validated triples and data sets differ between the vocabularies
+as we validated 3.8 billion QB, 480 million SKOS, and 10 million DDI-RDF triples.
+To be able to formulate findings which apply for all vocabularies, 
+we only use normalized relative values representing the percentage of constraints and violations belonging to the respective sets.
+
+There is a strong overlap between \emph{RDFS/OWL} and \emph{Constraint Language Based} constraint types as in many cases constraint types are expressible by RDFS/OWL and classical constraint languages.
 This is the reason why the percentage values of constraints and violations grouped by the classification of constraint types according to the expressivity of constraint languages do not accumulate to 100\%.
@@
 we cannot make valid general statements for all vocabularies,
-but we can formulate several hypotheses to direct the further development of constraint languages.
-As these hypotheses cannot be proved yet, 
+but we can formulate several findings to direct the further development of constraint languages.
+As these findings cannot be proved yet, 
 they still have to be verified or falsified
@@
 For newly developed vocabularies, however, the most expressed constraints are \emph{RDFS/OWL Based} (2/3).
+%
 Nearly 80\% of all violations are caused by \emph{SPARQL}, 1/5 by \emph{Constraint Language}, and 1/5 by \emph{RDFS/OWL Based} constraints.
@@
 \begin{hyp}
-For well-established vocabularies, RDFS/OWL Based constraints are almost completely satisfied which indicates generally a very impressive data quality, at least in the SBE domain and for the basic requirements.
+For well-established vocabularies, RDFS/OWL Based constraints are almost completely satisfied which generally indicates very impressive data quality, at least in the SBE domain and for the basic requirements.
 For newly developed vocabularies, however, data quality is poor as RDFS/OWL Based constraints are not fulfilled.
@@
 
-For DDI-RDF, data providers still have to understand the vocabulary and of course, data can not have high quality if the specification is not yet stable.
+For DDI-RDF, data providers still have to understand the vocabulary and of course data cannot have high quality if the specification is not yet stable.
 It is likely that a newly developed vocabulary is still subject of constant change
@@
 %
-The reason why we only defined \emph{SPARQL Based} constraints for assessing the quality of thesauri is that literature and practice especially concentrate on graph-based structures of thesauri by applying graph- and network-analysis techniques which can only be implemented by SPARQL.
+The reason why we only defined \emph{SPARQL Based} constraints for assessing the quality of thesauri is that literature and practice especially concentrate on evaluating graph-based structures of thesauri by applying graph- and network-analysis techniques which can only be implemented by SPARQL.
 
@@
 SPARQL seems to be used to formulate constraints whose violation is of higher severity than the violation of constraints expressed by either RDFS/OWL or high-level constraint languages.
-This is a surprising finding as the violation of \emph{RDFS/OWL Based} constraints should be of higher severity than \emph{informational} since these constraints are expected to be basic constraints as they are in many cases part of vocabularies' formal specifications.
+This is a surprising finding as the violation of \emph{RDFS/OWL Based} constraints should be of higher severity than \emph{informational} constraints since \emph{RDFS/OWL Based} constraints are expected to be basic constraints as they are in many cases part of vocabularies' formal specifications.
 %and (2)
@@
 We identified and published by today 81 types of constraints  that are required by various stakeholders for data applications.
-In close collaboration with several domain experts for the social, behavioural, and economic sciences (\emph{SBE}), we formulated 115 constraints on three different vocabularies (DDI-RDF, QB, and SKOS) and classified them according to their severity level and  whether their type is expressible by different types of constraint languages - RDFS/OWL, high-level constraint languages, and SPARQL.
-We evaluated  the data quality of 15,694 data sets (4.26 billion triples) of research data for the \emph{SBE} sciences obtained from 33 SPARQL endpoints.
-
-Based on the evaluation results,
-we formulated several hypotheses to direct the further development of constraint languages.
-We regard the results as hypotheses, as their general applicability beyond the examined vocabularies and for other domains is still to be confirmed.
-The main hypotheses are:
+In close collaboration with several domain experts for the social, behavioural, and economic sciences (SBE), we formulated 115 constraints on three different vocabularies (DDI-RDF, QB, and SKOS) and classified them according to their severity level and  whether their type is expressible by different types of constraint languages - RDFS/OWL, high-level constraint languages, and SPARQL.
+Using these constraints, we evaluated  the data quality of 15,694 data sets (4.26 billion triples) of research data for the SBE sciences obtained from 33 SPARQL endpoints.
+
+Based on the evaluation results, we formulated several findings to direct the further development of constraint languages.
+The general applicability of these findings, however, is still to be confirmed beyond the examined vocabularies and for other domains.
+The main findings are:
 
@@
 This is in contrast to the sometimes heard rumour that Linked Open Data lacks quality.
-We are actively involved in the further development and implementation of constraint languages and will use the results presented in the paper to set priorities on features where we expect the highest impact on the data quality of real-life data in the \emph{SBE} domain.
+We are actively involved in the further development and implementation of constraint languages and will use the results presented in the paper to set priorities on features where we expect the highest impact on the data quality of real-life data in the SBE domain.
 

### 2015-09-10 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
proofreading

@@
 SBE sciences require high-quality data for their empirical research. For more than a decade, members of the SBE community have been developing and using a
-metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)},
+metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)}, \footnote{\url{http://www.ddialliance.org/Specification/}}
 an XML format to disseminate, manage,
 and reuse data collected and archived for research \cite{Vardigan2008}. 
-In XML, the definition of schemas containing data constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
+In XML, the definition of schemas containing constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
 With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration.
@@
 For more detailed analyses we refer to the underlying unit-record data.
-The aggregated variable \emph{formal childcare} is calculated on the basis of six record-unit variables (i.a., \emph{Education at pre-school}) for which detailed metadata is given (i.a., code lists) enabling researchers to replicate the results shown in aggregated data tables.
+The aggregated variable \emph{formal childcare} is calculated on the basis of six unit-record variables (i.a., \emph{Education at pre-school}) for which detailed metadata is given (i.a., code lists) enabling researchers to replicate the results shown in aggregated data tables.
 \emph{DDI-RDF} is used to represent metadata on unit-record data in RDF.
@@
 
-The \emph{Simple Knowledge Organization System (SKOS)} is reused multiple times to build SBE vocabularies.
+The \emph{Simple Knowledge Organization System (SKOS)} is reused to a large extend to build SBE vocabularies.
 The codes of the variable \emph{Education at pre-school} are modeled as \emph{skos:Concepts} and 
@@
 %where each cycle produces one or more data sets. 
-%The aggregated variable \emph{formal childcare} is calculated on the basis of six record-unit variables 
+%The aggregated variable \emph{formal childcare} is calculated on the basis of six unit-record variables 
 %(e.g., \emph{Education at pre-school})
@@
 %The study \emph{EU-SILC 2011} contains eight unit-record data sets (\emph{DDI-RDF:LogicalDataSet})
-%including record-unit variables (\emph{DDI-RDF:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
+%including unit-record variables (\emph{DDI-RDF:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
 %
@@
 Schematron generates validation rules and validates XML documents according to them.
-With RDF validation, one can overcome the drawbacks when validating XML documents\footnote{\url{http://www.xmlmind.com/xmleditor/_distrib/doc/xmltool/xsd_structure_limitations.html}}.
+With RDF validation, one can overcome the drawbacks when validating XML documents.\footnote{\url{http://www.xmlmind.com/xmleditor/_distrib/doc/xmltool/xsd_structure_limitations.html}}
 It cannot be validated, e.g., if each code of a variable's code list is associated with a category and that if an element has a specific value then certain child elements must be present.
 
-A well-formed \emph{RDF Data Cube} is an a RDF graph describing one or more instances of \emph{qb:DataSet} for which each of the 22 integrity constraints\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf}, defined within the QB specification, passes.
+A well-formed \emph{RDF Data Cube} is an RDF graph describing one or more instances of \emph{qb:DataSet} for which each of the 22 integrity constraints,\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf} defined within the QB specification, passes.
 Each integrity constraint is expressed as narrative prose and, where possible, as a SPARQL ASK query or query template. 
@@
 
-Within the working groups, we identified by today 81 requirements to formulate RDF constraints (e.g., \emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}.
+Within the working groups, we identified by today 81 requirements to formulate RDF constraints (e.g., \emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type.\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}
 Within a technical report, we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages \cite{BoschNolleAcarEckert2015}.
@@
 For the three vocabularies, several SBE domain experts determined the default severity level of the 115 concrete constraints, which we published in a technical report \cite{BoschZapilkoWackerowEckert2015}.
-In the following, we summarize the results for the purpose of our evaluation.
+In the following, we summarize the classifications of constraint types and constraints for the purpose of our evaluation.
 
@@
 
+\textbf{\emph{RDFS/OWL Based}.}
 The modeling languages RDFS and OWL are typically used to formally specify vocabularies.
-\emph{RDFS/OWL Based} denotes the set of constraint types which can be formulated with RDFS/OWL axioms which we use in terms of constraints with CWA/UNA semantics and without reasoning\footnote{The entailment regime is to be decided by the implementers.
-It is our point that reasoning affects validation and that a proper definition of the reasoning to be applied is needed.}.
-RDFS/OWL axioms are commonly found within formal specifications of vocabularies.
+\emph{RDFS/OWL Based} denotes the set of constraint types which can be formulated with RDFS/OWL axioms which we use in terms of constraints with CWA/UNA semantics and without reasoning.\footnote{The entailment regime is to be decided by the implementers.
+It is our point that reasoning affects validation and that a proper definition of the reasoning to be applied is needed.} RDFS/OWL axioms are commonly found within formal specifications of vocabularies.
 We determined this set based on the evaluation of the three vocabularies we performed without reasoning.
@@
 %\ms{Study $\equiv$ $\exists$ product.LogicalDataSet} (DL), e.g., restricts studies to contain at least one data set which is expressible in OWL 2:
-Constraints of the constraint type \emph{minimum qualified cardinality restrictions} (\emph{R-74}), e.g., guarantee that individuals of given classes are connected by particular properties to at least n different individuals/literals of certain classes or data ranges.
+Constraints of the type \emph{minimum qualified cardinality restrictions} (\emph{R-74}), e.g., guarantee that individuals of given classes are connected by particular properties to at least n different individuals/literals of certain classes or data ranges.
 For \emph{DDI-RDF}, a \emph{minimum qualified cardinality restriction} can be obtained from a respective OWL axiom which ensures that a \emph{disco:Questionnaire} has (\emph{disco:question}) at least one \emph{disco:Question}:
@@
 
-\emph{Constraint Language Based} and \emph{SPARQL Based} constraints are in contrast to \emph{RDFS/OWL Based} constraints usually not (yet) explicitly defined within formal specifications of vocabularies.
+\emph{Constraint Language Based} and \emph{SPARQL Based} are in contrast to \emph{RDFS/OWL Based} constraints usually not (yet) explicitly defined within formal specifications of vocabularies.
 Instead, they are often defined within textual descriptions of vocabularies.
@@
 
+\textbf{\emph{Constraint Language Based}.}
 We further distinguish \emph{Constraint Language Based} as the set of constraint types that can be expressed by common classical declarative high-level constraint languages like ShEx, ReSh, and DSP. 
@@
 %\emph{Complex constraint types} encompass constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
+\textbf{\emph{SPARQL Based}.}
 The set \emph{SPARQL Based} encompasses constraint types that are not expressible by RDFS/OWL or common high-level constraint languages but by plain SPARQL.
@@
 %i.e., individuals cannot be instances of multiple disjoint classes.
-\textbf{\emph{RDFS/OWL Based} constraint types.}
+\textbf{\emph{RDFS/OWL Based}.}
 It is a common requirement to narrow down the value space of properties by an exhaustive enumeration of valid values (\emph{R-30/37: allowed values}):
@@
 
-\textbf{\emph{Constraint Language Based} constraint types.}
+\textbf{\emph{Constraint Language Based}.}
 %{Simple constraint types} is the set of constraint types whose constraints can be easily defined without much effort in addition to $\mathcal{CT}_{B}$ constraints.
@@
 
-\textbf{\emph{SPARQL Based} constraint types.}
+\textbf{\emph{SPARQL Based}.}
 %\textcolor{red}{
@@
 A SPIN construct template creates constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
-%\emph{Missy}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}} provides comprehensive Linked Data services like diverse RDF exports of record-unit metadata conforming to the DDI-RDF vocabulary in form of multiple concrete syntaxes.
+%\emph{Missy}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}} provides comprehensive Linked Data services like diverse RDF exports of unit-record metadata conforming to the DDI-RDF vocabulary in form of multiple concrete syntaxes.
 
@@
 %We implemented a validation environment (available at \url{http://purl.org/net/rdfval-demo}) to validate RDF data according to constraints expressed my arbitrary constraint languages and to ensure correct syntax and semantics of diverse vocabularies such as DDI-RDF, QB, SKOS, and \emph{PHDD} (section \ref{implementation}).
-%We exhaustively evaluated the metadata quality of large real world aggregated (QB), record-unit (DDI-RDF), and thesauri (SKOS) data sets (more than 4.2 billion triples and 15 thousand data sets) by means of 213  constraints of the majority of the constraint types\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).
+%We exhaustively evaluated the metadata quality of large real world aggregated (QB), unit-record (DDI-RDF), and thesauri (SKOS) data sets (more than 4.2 billion triples and 15 thousand data sets) by means of 213  constraints of the majority of the constraint types\footnote{The second appendix of this paper describing the evaluation in detail is available at: \url{http://arxiv.org/abs/1504.04478} \cite{BoschZapilkoWackerowEckert2015-2}.} (section \ref{evaluation}).
 

### 2015-09-10 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
proofreading

@@
 It does not make sense to determine the severity of constraint violations of an entire constraint type,
-as the severity of the violation of a constraint depends on the individual context and vocabulary.
+as the severity depends on the individual context and vocabulary.
 %as the violation of one constraint may be severe,
@@
 SBE experts determined the default \emph{severity level}\footnote{The possibility to define severity levels in vocabularies is in itself a requirement (\emph{R-158}).} for each of the 115 constraints to indicate how serious the violation of the constraint is.
-We use the classification system of log messages in software development like \emph{Apache Log4j 2} \cite{Apache-2015}, the \emph{Java Logging API}\footnote{\url{http://docs.oracle.com/javase/7/docs/api/java/util/logging/Level.html}}, and the \emph{Apache Commons Logging API}\footnote{\url{http://commons.apache.org/proper/commons-logging/}} as many data practitioners also have experience in software development and software developers intuitively understand these levels.
-We simplify this commonly accepted classification system and distinguish the three severity levels (1) \emph{informational}, (2) \emph{warning} and (3) \emph{error}.
+We use the classification system of log messages in software development like \emph{Apache Log4j 2} \cite{Apache-2015}, the \emph{Java Logging API},\footnote{\url{http://docs.oracle.com/javase/7/docs/api/java/util/logging/Level.html}} and the \emph{Apache Commons Logging API}\footnote{\url{http://commons.apache.org/proper/commons-logging/}} as many data practitioners also have experience in software development and software developers intuitively understand these levels.
+We simplify this commonly accepted classification system and distinguish the three severity levels (1) \emph{informational}, (2) \emph{warning}, and (3) \emph{error}.
 %According to the default severity level of constraints, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:\ke{auch dieser satz macht keinen sinn für mich, ebensowenig wie die extrem erhellende auflistung, die gleich folgt...
@@
 \emph{Warnings} are syntactic or semantic problems which typically should not lead to an abortion of data processing.
-\emph{Errors} are syntactic or semantic errors which should cause the abortion of data processing. 
+\emph{Errors}, in contrast, are syntactic or semantic errors which should cause the abortion of data processing. 
 %Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
@@
 %which may indicate when the data is verbose/redundant or expressed at a too general level.
-Consider the following \emph{DL knowledge base} $\mathcal{K}$\footnote{A \emph{DL knowledge base} is a collection of formal statements which correspond to \emph{facts} or what is known explicitly. }:
+Consider the following \emph{DL knowledge base} $\mathcal{K}$:\footnote{A \emph{DL knowledge base} is a collection of formal statements which correspond to \emph{facts} or what is known explicitly. }
 \begin{center}
@@
 The default severity level of this constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
-
+%
 A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.

### 2015-09-10 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
formerly Bosch

@@
 % 
-\author{\IEEEauthorblockN{Thomas Bosch\IEEEauthorrefmark{1},
+\author{\IEEEauthorblockN{Thomas Hartmann (formerly Bosch)\IEEEauthorrefmark{1},
 Benjamin Zapilko\IEEEauthorrefmark{1},

### 2015-09-10 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
minor

@@
 % can use linebreaks \\ within to get better formatting as desired
-%\title{Aspects of RDF Data Constraints in the Social, Behavioural, and Economic Sciences}
+%\title{Aspects of RDF Data Constraints in the Social, behavioral, and Economic Sciences}
 \title{Validating RDF Data Quality using Constraints to Direct the Development of Constraint Languages}
@@
 In this paper, in collaboration with several domain experts we formulate 115 constraints on three different vocabularies (DDI-RDF, QB, and SKOS) and classify them according to (1) the severity of an occurring violation and (2) which types of constraint languages are able to express their type of constraint.
-We evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic sciences obtained from 33 SPARQL endpoints.
+We evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioral, and economic sciences obtained from 33 SPARQL endpoints.
 Based on the results, we formulate several hypotheses to direct the further development of constraint languages.
@@
 In 2014, two working groups on RDF validation have been established to develop a language to express constraints on RDF data: 
-the \emph{W3C RDF Data Shapes Working Group}\footnote{\url{http://www.w3.org/2014/rds/charter}} (33 participants of 19 organizations) and the \emph{DCMI RDF Application Profiles Task Group}\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}} (29 people of 22 organizations) which among others bundles the requirements of data institutions of the cultural heritage sector and the \emph{social, behavioural, and economic (SBE)} sciences and represents them in the W3C group.
+the \emph{W3C RDF Data Shapes Working Group}\footnote{\url{http://www.w3.org/2014/rds/charter}} (33 participants of 19 organizations) and the \emph{DCMI RDF Application Profiles Task Group}\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}} (29 people of 22 organizations) which among others bundles the requirements of data institutions of the cultural heritage sector and the \emph{social, behavioral, and economic (SBE)} sciences and represents them in the W3C group.
 
@@
 In this paper, we collected constraints for commonly used vocabularies in the SBE domain (see Section \ref{sbe-vocabularies}), either from the vocabularies themselves or from domain and data experts, in order to gain a better understanding about the role of certain requirements for data quality and to direct the further development of constraint languages.
-All in all, this lead to 115 constraints on three vocabularies
+All in all, this lead to 115 constraints on three vocabularies.
 We let the experts classify the constraints according to the severity of their violation.
@@
 For all these 115 constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of SBE research data on three common vocabularies in SBE sciences (DDI-RDF, QB, SKOS) obtained from 33 SPARQL endpoints.
-%evaluated the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioural, and economic (SBE) sciences obtained from 33 SPARQL endpoints.
+%evaluated the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioral, and economic (SBE) sciences obtained from 33 SPARQL endpoints.
 Based on the evaluation results,
@@
 We identified and published by today 81 types of constraints  that are required by various stakeholders for data applications.
-In close collaboration with several domain experts for the social, behavioural, and economic sciences (SBE), we formulated 115 constraints on three different vocabularies (DDI-RDF, QB, and SKOS) and classified them according to their severity level and  whether their type is expressible by different types of constraint languages - RDFS/OWL, high-level constraint languages, and SPARQL.
+In close collaboration with several domain experts for the social, behavioral, and economic sciences (SBE), we formulated 115 constraints on three different vocabularies (DDI-RDF, QB, and SKOS) and classified them according to their severity level and  whether their type is expressible by different types of constraint languages - RDFS/OWL, high-level constraint languages, and SPARQL.
 Using these constraints, we evaluated  the data quality of 15,694 data sets (4.26 billion triples) of research data for the SBE sciences obtained from 33 SPARQL endpoints.

### 2015-09-11 paper/IEEE-ICSC-2016/technical-reports/IEEE-ICSC-2016-constraints.tex
TRs

--- 2015-04-17 paper/paper7/paper7-appendix.tex
@@
 %
-\title{RDF Constraints to Validate}
-\subtitle{Rectangular Data and Metadata on Person-Level Data, Aggregated Data, Thesauri, and Statistical Classifications}
+\title{Constraints to Validate RDF Data Quality on}
+\subtitle{Common Vocabularies in the Social, Behavioral, and Economic Sciences}
 
@@
 To ensure high quality of and trust in both metadata and data, their representation in RDF must satisfy certain criteria - specified in terms of RDF constraints.
-From 2012 to 2015 together with other Linked Data community members and experts from the social, behavioural, and economic sciences (\emph{SBE}), we developed diverse vocabularies to represent \emph{SBE} metadata and rectangular data in RDF.
-The \emph{DDI-RDF Discovery Vocabulary (Disco)} 
+From 2012 to 2015 together with other Linked Data community members and experts from the social, behavioral, and economic sciences (\emph{SBE}), we developed diverse vocabularies to represent \emph{SBE} metadata and rectangular data in RDF.
+
+The \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)} 
 is designed to support the dissemination, management,
-and reuse of person-level data, i.e., data about individuals, households, and businesses, collected in form of responses to studies and archived for research purposes.
-The \emph{RDF Data Cube Vocabulary (Data Cube)} is a W3C recommendation for expressing \emph{data cubes}, i.e. multi-dimensional aggregate data. 
-\emph{Physical Data Description (PHDD)} is a vocabulary to model data in rectangular format. 
+and reuse of unit-record data, i.e., data about individuals, households, and businesses, collected in form of responses to studies and archived for research purposes.
+The \emph{RDF Data Cube Vocabulary (QB)} is a W3C recommendation for expressing \emph{data cubes}, i.e. multi-dimensional aggregate data and its metadata. 
+\emph{Physical Data Description (PHDD)} is a vocabulary to model data in rectangular format, i.e., tabular data. 
 The data could either be represented in records with character-separated values (\emph{CSV}) or fixed length. 
@@
 
-In this paper, we describe RDF constraints to validate metadata on person-level data (\emph{Disco}), aggregated data (\emph{Data Cube}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) and to validate rectangular data (\emph{PHDD}).
-We assign RDF constraints to RDF constraint types either corresponding to RDF validation requirements or to data model specific constraint types.
+In this paper, we describe RDF constraints to validate metadata on unit-record data (\emph{DDI-RDF}), aggregated data (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) and to validate tabular data (\emph{PHDD}) - all of them represented in RDF.
+We classified these constraints according to the severity of occurring constraint violations.
 This technical report is updated continuously as modifying, adding, and deleting constraints remains ongoing work.
 
-\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, RDF Data Cube Vocabulary, Thesauri, SKOS, Rectangular Data, Statistical Classifications, XKOS, Linked Data, Semantic Web}
+\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, RDF Data Cube Vocabulary, Thesauri, SKOS, Tabular Data, Statistical Classifications, Linked Data, Semantic Web}
 \end{abstract}
@@
 
-Bosch and Eckert initiated a comprehensive database\footnote{Publicly available at \url{http://purl.org/net/rdf-validation}.} on RDF validation requirements to collect case studies, use cases, and requirements \cite{BoschEckert2014}.
-It is continuously updated and used to evaluate and to compare various existing solutions for RDF constraint formulation and validation. 
-Requirements are classified to provide a high-level view on different solutions and to facilitate a better understanding of the problem domain.
-Bosch et al. identified in total 74 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
-They recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which they explain each requirement (constraint type) in detail and give examples for each (represented by listed constraint languages) \cite{BoschNolleAcarEckert2015}.
-Where appropriate constraint types are related to complementary requirements of the RDF validation requirements database.
-
-We distinguish two validation types:
-(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of given data models.
-(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges.
-We determined the default \emph{severity level} (corresponds to requirement \emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
-We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ (informational) via $\mathcal{SL}_{1}$ (warning) to $\mathcal{SL}_{2}$ (error). 
-Although we provide default severity levels for each constraint, users should be able to specify severity levels of constraints they need to validate for their individual use cases, i.e., users should be able to define use case specific severity levels for constraints.
-
-The following two sections encompass RDF constraints classified as constraint types either corresponding to RDF validation requirements (section \ref{RDF-validation-requirements-constraint-types}) or data model specific constraint types (section \ref{data-model-specific-constraint-types}).
-Constraint types marked with an asterisk (*) can be used as OWL 2 axioms.
-Thus, reasoners may be used prior to the validation to infer implicit triples which may resolve or cause constraint violations.
-$\mathcal{C}_{T}$ constraint types are marked with the superscript\textsuperscript{T}.
-As $\mathcal{C}_{T}$ and $\mathcal{C}_{C}$ are disjoint sets, $\mathcal{C}_{C}$ constraint types are not explicitly marked.
-
-%\section{RDF Constraints to Validate Metadata and Data}
-
-\section{RDF Constraint Types Corresponding to RDF Validation Requirements}
-\label{RDF-validation-requirements-constraint-types}
-
-\subsection{Subsumption*\textsuperscript{T}}
+For constraint formulation and RDF data validation, several languages exist or are currently developed.
+\emph{Shape Expressions (ShEx)}, \emph{Resource Shapes (ReSh)}, \emph{Description Set Profiles (DSP)}, \emph{OWL 2}, the \emph{SPARQL Inferencing Notation (SPIN)}, and \emph{SPARQL} are the six most promising and widely used constraint languages.
+OWL 2 is used as a constraint language under the closed-world and unique name assumptions.
+The W3C currently develops \emph{SHACL}, an RDF vocabulary for describing RDF graph structures.
+With its direct support of validation via SPARQL, SPIN is very popular and certainly plays an important role for future developments in this field.
+It is particularly interesting as a means to validate arbitrary constraint languages by mapping them to SPARQL \cite{BoschEckert2014-2}.
+Yet, there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners.
+Further research and development therefore is needed.
+
+In 2013, the W3C organized the RDF Validation Workshop,\footnote{\url{http://www.w3.org/2012/12/rdf-val/}} 
+where experts from industry, government, and academia discussed first use cases for constraint formulation and RDF data validation.
+In 2014, two working groups on RDF validation have been established to develop a language to express constraints on RDF data: 
+the \emph{W3C RDF Data Shapes Working Group}\footnote{\url{http://www.w3.org/2014/rds/charter}} (33 participants of 19 organizations) and the \emph{DCMI RDF Application Profiles Task Group}\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}} (29 people of 22 organizations) which among others bundles the requirements of data institutions of the cultural heritage sector and the \emph{social, behavioral, and economic (SBE)} sciences and represents them in the W3C group.
+
+Within the DCMI task group, a collaboratively curated database of RDF validation requirements\footnote{Online available at: \url{http://purl.org/net/rdf-validation}} has been created which contains the findings of the working groups based on various case studies provided by data institutions \cite{BoschEckert2014}.
+It is publicly available and open for further contributions.
+The database connects requirements to use cases, case studies, and implementations and forms the basis of this paper. 
+We distinguish 81 requirements to formulate constraints on RDF data; 
+each of them corresponding to a constraint type.
+
+In this paper, we collected constraints for commonly used vocabularies in the SBE domain (see Section \ref{sbe-vocabularies}), either from the vocabularies themselves or from domain and data experts, in order to gain a better understanding about the role of certain requirements for data quality and to direct the further development of constraint languages.
+We let the experts classify the constraints according to the severity of their violation.
+
+\section{Common Vocabularies in SBE Sciences}
+\label{sbe-vocabularies}
+
+We took all well-established and newly developed SBE vocabularies into account and defined constraints for three vocabularies commonly used in the SBE sciences which are briefly introduced in the following.
+We analyzed actual data according to constraint violations, as for these vocabularies large data sets are already published.
+
+SBE sciences require high-quality data for their empirical research. For more than a decade, members of the SBE community have been developing and using a
+metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)}, \footnote{\url{http://www.ddialliance.org/Specification/}}
+an XML format to disseminate, manage,
+and reuse data collected and archived for research \cite{Vardigan2008}. 
+In XML, the definition of schemas containing constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
+With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration.
+Therefore, not only established vocabularies like SKOS are used;
+recently, members of the SBE and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.
+
+The data most often used in research within SBE sciences is \emph{unit-record data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers such as hospital records, registers of births and deaths.
+A \emph{study} represents the process by which a data set was generated or collected.
+The range of unit-record data is very broad - including census, education, health data and business, social, and labor force surveys.
+This type of research data is held within data archives or data libraries after it has been collected, so that it may be reused by future researchers.
+By its nature, unit-record data is highly confidential and access is often only permitted for qualified researchers who must apply for access.
+Researchers typically represent their results as aggregated data in form of multi-dimensional tables with only a few columns: so-called \emph{variables} such as \emph{sex} or \emph{age}.
+Aggregated data, which answers particular research questions, is derived from unit-record data by statistics on groups or aggregates such as frequencies and arithmetic means.
+The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying unit-record data.
+For more detailed analyses, researchers refer to unit-record data including additional variables needed to answer subsequent research questions.
+
+\emph{Formal childcare} is an example of an aggregated variable which captures the measured availability of childcare services in percent over the population in European Union member states by 
+the dimensions \emph{year}, \emph{duration}, \emph{age} of the child, and \emph{country}.
+Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
+The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger} or by a code list of age clusters (e.g., '0 to 10' and '11 to 20'). 
+The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e., multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}.
+%QB represents metadata on multi-dimensional aggregate data in two files: a \emph{qb:DataSet} and a \emph{qb:DataStructureDefinition}.
+A \emph{qb:DataStructureDefinition} contains metadata of the data collection.
+The variable \emph{formal childcare} is modeled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
+\emph{Year}, \emph{duration}, \emph{age}, and \emph{country} are \emph{qb:dimensions}.
+Data values, i.e., the availability of childcare services in percent over the population, are collected in a \emph{qb:DataSet}. 
+Each data value is represented inside a \emph{qb:Observation} which contains values for each dimension. 
+%(e.g., the year in which \emph{formal childcare} has been determined).
+%\ke{Wieso springt das von einer sehr knappen Einführung direkt zu konkreten (beliebigen?) Variablen?
+Ich möchte wissen, wofür QB benutzt wird und gerne ein konkretes %Beispiel sehen, um mir einen Data Cube vorstellen zu können.}\tb{hmm, ich halte das beispiel für ein knappes und verständliches beipsiel wie eine tabelle in qb dargestellt wird / es ist auch der link enthalten zu der tabelle von eurostat}
+
+For more detailed analyses we refer to the underlying unit-record data.
+The aggregated variable \emph{formal childcare} is calculated on the basis of six unit-record variables (i.a., \emph{Education at pre-school}) for which detailed metadata is given (i.a., code lists) enabling researchers to replicate the results shown in aggregated data tables.
+\emph{DDI-RDF} is used to represent metadata on unit-record data in RDF.
+%The series (\emph{DDI-RDF:StudyGroup}) \emph{EU-SILC} contains one study (\emph{DDI-RDF:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
+%\emph{dcterms:spatial} points to the countries for which the data has been collected.
+The study (\emph{disco:Study}) for which the unit-record data has been collected 
+%\emph{EU-SILC 2011} 
+contains eight data sets (\emph{disco:LogicalDataSet})
+including variables (\emph{disco:Variable}) like the six ones needed to calculate the variable \emph{formal childcare}.
+%Metadata on unit-record data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
+%One common research question is ,e.g., the comparison of variables like 
+%\emph{formal childcare} between countries, for which the variable is collected within the context of an individual study, and other European or non European countries (e.g. OSCE).
+
+The \emph{Simple Knowledge Organization System (SKOS)} is reused to a large extend to build SBE vocabularies.
+The codes of the variable \emph{Education at pre-school} are modeled as \emph{skos:Concepts} and 
+a \emph{skos:OrderedCollection} organizes them in a particular order within a \emph{skos:memberList}.
+A variable may be associated with a theoretical concept (\emph{skos:Concept}) and \emph{skos:narrower} builds the hierarchy of theoretical concepts within a \emph{skos:ConceptScheme} of a study.
+The variable \emph{Education at pre-school} is assigned to the theoretical concept \emph{Child Care} which is a narrower concept of the top concept \emph{Education}.
+Controlled vocabularies (\emph{skos:ConceptScheme}), serving as extension and reuse mechanism,
+organize types (\emph{skos:Concept}) of descriptive statistics (\emph{disco:SummaryStatistics}) like minimum, maximum, and arithmetic mean.
+
+\section{Classification of RDF Constraints according to the Severity of Constraint Violations}
+
+A concrete constraint is instantiated from one of the 81 constraint types and is defined for a specific vocabulary.
+It does not make sense to determine the severity of constraint violations of an entire constraint type,
+as the severity depends on the individual context and vocabulary.
+%as the violation of one constraint may be severe,
+%whereas, the violation of another constraint of the same type may be minor.
+SBE experts determined the default \emph{severity level}\footnote{The possibility to define severity levels in vocabularies is in itself a requirement (\emph{R-158}).} for each constraint to indicate how serious the violation of the constraint is.
+We use the classification system of log messages in software development like \emph{Apache Log4j 2} \cite{Apache-2015}, the \emph{Java Logging API},\footnote{\url{http://docs.oracle.com/javase/7/docs/api/java/util/logging/Level.html}} and the \emph{Apache Commons Logging API}\footnote{\url{http://commons.apache.org/proper/commons-logging/}} as many data practitioners also have experience in software development and software developers intuitively understand these levels.
+We simplify this commonly accepted classification system and distinguish the three severity levels (1) \emph{informational}, (2) \emph{warning}, and (3) \emph{error}.
+%According to the default severity level of constraints, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:\ke{auch dieser satz macht keinen sinn für mich, ebensowenig wie die extrem erhellende auflistung, die gleich folgt...
+mein vorschlag von eben kann das komplett ersetzen.}
+%\begin{itemize}
+	%\item \textbf{\emph{informational constraints}}: constraints with severity level \emph{informational}
+	%\item \textbf{\emph{warning constraints}}: constraints with severity level \emph{warning}
+	%\item \textbf{\emph{error constraints}}: constraints with severity level \emph{error}
+%\end{itemize}
+Violations of \emph{informational} constraints point to desirable but not necessary data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies.
+%They are not seen as serious errors.
+\emph{Warnings} are syntactic or semantic problems which typically should not lead to an abortion of data processing.
+\emph{Errors}, in contrast, are syntactic or semantic errors which should cause the abortion of data processing. 
+%Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
+%Data not conforming to \emph{warning constraints} but to \emph{error constraints} could be processed further.
+%Data not corresponding to \emph{error constraints}, however, cannot be processed further after validation. 
+Although we provide default severity levels for each constraint, validation environments should enable users to adapt the severity levels of constraints according to their individual needs.
+
+\section{RDF Constraints by RDF Constraint Type}
+
+\subsection{Subsumption}
 
@@
 
-\subsection{Class Equivalence*\textsuperscript{T}}
+\subsection{Class Equivalence}
 
@@
 
-\subsection{Sub Properties*\textsuperscript{T}}
+\subsection{Sub Properties}
 
@@
 
-\subsection{Property Domains*\textsuperscript{T}}
+\subsection{Property Domains}
 
@@
 
-\subsection{Property Ranges*\textsuperscript{T}}
+\subsection{Property Ranges}
 
@@
 
-\subsection{Inverse Object Properties*}
+\subsection{Inverse Object Properties}
 
@@
 
-\subsection{Symmetric Object Properties*}
+\subsection{Symmetric Object Properties}
 
@@
 
-\subsection{Asymmetric Object Properties*\textsuperscript{T}}
+\subsection{Asymmetric Object Properties}
 
@@
 
-\subsection{Reflexive Object Properties*}
+\subsection{Reflexive Object Properties}
 
@@
 
-\subsection{Irreflexive Object Properties*}
+\subsection{Irreflexive Object Properties}
 
@@
 
-\subsection{Disjoint Properties\textsuperscript{T}}
+\subsection{Disjoint Properties}
 
@@
 
-\subsection{Disjoint Classes\textsuperscript{T}}
+\subsection{Disjoint Classes}
 
@@
 
-\subsection{Equivalent Properties*\textsuperscript{T}}
+\subsection{Equivalent Properties}
 
@@
 
-\subsection{Object Property Paths*}
+\subsection{Object Property Paths}
 
@@
 
-\subsection{Intersection*}
+\subsection{Intersection}
 
@@
 
-\subsection{Disjunction*}
+\subsection{Disjunction}
 
@@
 
-\subsection{Negation*}
+\subsection{Negation}
 
@@
 
-\subsection{Existential Quantifications*\textsuperscript{T}}
+\subsection{Existential Quantifications}
 
@@
 
-\subsection{Universal Quantifications*\textsuperscript{T}}
+\subsection{Universal Quantifications}
 
@@
 
-\subsection{Minimum Unqualified Cardinality Restrictions*\textsuperscript{T}}
+\subsection{Minimum Unqualified Cardinality Restrictions}
 
@@
 
-\subsection{Minimum Qualified Cardinality Restrictions*\textsuperscript{T}}
+\subsection{Minimum Qualified Cardinality Restrictions}
 
@@
 
-\subsection{Maximum Unqualified Cardinality Restrictions*\textsuperscript{T}}
+\subsection{Maximum Unqualified Cardinality Restrictions}
 
@@
 
-\subsection{Maximum Qualified Cardinality Restrictions*\textsuperscript{T}}
+\subsection{Maximum Qualified Cardinality Restrictions}
 
@@
 
-\subsection{Exact Unqualified Cardinality Restrictions*\textsuperscript{T}}
+\subsection{Exact Unqualified Cardinality Restrictions}
 
@@
 
-\subsection{Exact Qualified Cardinality Restrictions*\textsuperscript{T}}
+\subsection{Exact Qualified Cardinality Restrictions}
 
@@
 
-\subsection{Transitive Object Properties*}
+\subsection{Transitive Object Properties}
 
@@
 
-\subsection{Allowed Values\textsuperscript{T}}
+\subsection{Allowed Values}
 
@@
 
-\subsection{Required Properties\textsuperscript{T}}
+\subsection{Required Properties}
 
@@
 
-\subsection{Optional Properties\textsuperscript{T}}
+\subsection{Optional Properties}
 
@@
 
-\subsection{Repeatable Properties\textsuperscript{T}}
+\subsection{Repeatable Properties}
 
@@
 
-\subsection{Individual Equality*}
+\subsection{Individual Equality}
 
@@
 
-\subsection{Functional Properties*}
+\subsection{Functional Properties}
 
@@
 
-\subsection{Inverse-Functional Properties*}
+\subsection{Inverse-Functional Properties}
 
@@
 
-\subsection{Value Restrictions*}
+\subsection{Value Restrictions}
 
@@
 
-\subsection{Self Restrictions*}
+\subsection{Self Restrictions}
 
@@
 
-\subsection{Class-Specific Property Range*\textsuperscript{T}}
+\subsection{Class-Specific Property Range}
 
@@
 
-\subsection{Class-Specific Reflexive Object Properties*}
+\subsection{Class-Specific Reflexive Object Properties}
 
@@
 
-\subsection{Membership in Controlled Vocabularies.}
+\subsection{Membership in Controlled Vocabularies}
 
@@
 
-\subsection{Context-Specific Valid Classes\textsuperscript{T}}
+\subsection{Context-Specific Valid Classes}
 
@@
 
-\subsection{Context-Specific Valid Properties\textsuperscript{T}}
+\subsection{Context-Specific Valid Properties}
 
@@
 
-\subsection{Default Values*\textsuperscript{T}}
+\subsection{Default Values}
 
@@
 
-\subsection{Value is Valid for Datatype\textsuperscript{T}}
+\subsection{Value is Valid for Datatype}
 
@@
 
-\subsection{Use Sub-Super Relations in Validation\textsuperscript{T}}
-
-\footnote{\emph{R-224-USE-SUB-SUPER-RELATIONS-IN-VALIDATION}}
+\subsection[Use Sub-Super Relations in Validation] {Use Sub-Super Relations in Validation\footnote{\emph{R-224-USE-SUB-SUPER-RELATIONS-IN-VALIDATION}}}
+
+%\subsection{Use Sub-Super Relations in Validation{\footnote{\emph{R-224-USE-SUB-SUPER-RELATIONS-IN-VALIDATION}}}}
 
@@
 
-\subsection{Cardinality Shortcuts*\textsuperscript{T}}
+\subsection{Cardinality Shortcuts}
 
@@
 
-\subsection{Aggregation}
+\subsection{Aggregations}
 
@@
 
-\section{Data Model Specific RDF Constraint Types}
-\label{data-model-specific-constraint-types}
-
 \subsection{Comparison}
+\setcounter{subsection}{76}
 
@@
 
-\subsection{Vocabulary\textsuperscript{T}}
+\subsection{Vocabulary}
 Vocabularies should not invent any new terms or use deprecated elements.
@@
 
-\subsection{Linked Data}
+\subsection{HTTP URI Scheme Violation}
 
@@
 
-\bibliography{../../literature/literature}{}
+\section{Conclusion}
+
+We identified and published by today 81 types of constraints  that are required by various stakeholders for data applications.
+In close collaboration with several domain experts for the social, behavioral, and economic sciences (SBE), we formulated constraints on common SBE vocabularies and classified them according to their severity level.
+
+\bibliography{../../../literature/literature}{}
 \bibliographystyle{plain}

### 2015-09-11 paper/IEEE-ICSC-2016/technical-reports/IEEE-ICSC-2016-evaluation.tex
TRs

--- 2015-04-08 paper/paper7/paper7-evaluation.tex
@@
 
+\usepackage{multirow}
+
 \begin{document}
@@
 %
-\title{An Evaluation of RDF Constraint Types to Validate Metadata on Person-Level and Aggregated Data}
-\subtitle{}
+%\title{An Evaluation \\
+%of Metadata and Data Quality}
+%\subtitle{on unit-record, Aggregated, Thesauri, Statistical Classifications, and Rectangular Data Sets}
+
+\title{Evaluating the Quality of RDF Data Sets on}
+\subtitle{Common Vocabularies in the Social, Behavioral, and Economic Sciences}
+
+%\title{An Evaluation}
+%\subtitle{of the Quality of Metadata on unit-record, Aggregated, Thesauri, and Statistical Classifications Data Sets and of the Quality of Rectangular Data}
 
@@
 \begin{abstract}
-...
-
-\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, Disco, RDF Data Cube Vocabulary, Linked Data, Semantic Web}
+From 2012 to 2015 together with other Linked Data community members and experts from the social, behavioral, and economic sciences (\emph{SBE}), we developed diverse vocabularies to represent SBE metadata and tabular data in RDF.
+The \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)} 
+is designed to support the dissemination, management,
+and reuse of unit-record data, i.e., data about individuals, households, and businesses, collected in form of responses to studies and archived for research purposes.
+The \emph{RDF Data Cube Vocabulary (QB)} is a W3C recommendation for expressing \emph{data cubes}, i.e. multi-dimensional aggregate data and its metadata. 
+\emph{Physical Data Description (PHDD)} is a vocabulary to model data in rectangular format, i.e., tabular data. 
+The data could either be represented in records with character-separated values (CSV) or fixed length. 
+The \emph{Simple Knowledge Organization System (SKOS)} is a vocabulary to build knowledge organization systems such as thesauri, classification schemes, and taxonomies.
+XKOS is a SKOS extension to describe formal statistical classifications.
+
+To ensure high quality of and trust in both metadata and data, their representation in RDF must satisfy certain criteria - specified in terms of RDF constraints.
+In this paper, we evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioral, and economic sciences obtained from 33 SPARQL endpoints.
+We checked 115 constraints on three different and representative SBE vocabularies (DDI-RDF, QB, and SKOS) by means of the \emph{RDF Validator}, a validation environment which is available at \url{http://purl.org/net/rdfval-demo}.
+
+\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, RDF Data Cube Vocabulary, Thesauri, SKOS, Linked Data, Semantic Web}
 \end{abstract}
 
+\section{Introduction}
+
+For constraint formulation and RDF data validation, several languages exist or are currently developed.
+\emph{Shape Expressions (ShEx)}, \emph{Resource Shapes (ReSh)}, \emph{Description Set Profiles (DSP)}, \emph{OWL 2}, the \emph{SPARQL Inferencing Notation (SPIN)}, and \emph{SPARQL} are the six most promising and widely used constraint languages.
+OWL 2 is used as a constraint language under the closed-world and unique name assumptions.
+The W3C currently develops \emph{SHACL}, an RDF vocabulary for describing RDF graph structures.
+With its direct support of validation via SPARQL, SPIN is very popular and certainly plays an important role for future developments in this field.
+It is particularly interesting as a means to validate arbitrary constraint languages by mapping them to SPARQL \cite{BoschEckert2014-2}.
+Yet, there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners.
+Further research and development therefore is needed.
+
+In 2013, the W3C organized the RDF Validation Workshop,\footnote{\url{http://www.w3.org/2012/12/rdf-val/}} 
+where experts from industry, government, and academia discussed first use cases for constraint formulation and RDF data validation.
+In 2014, two working groups on RDF validation have been established to develop a language to express constraints on RDF data: 
+the \emph{W3C RDF Data Shapes Working Group}\footnote{\url{http://www.w3.org/2014/rds/charter}} (33 participants of 19 organizations) and the \emph{DCMI RDF Application Profiles Task Group}\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}} (29 people of 22 organizations) which among others bundles the requirements of data institutions of the cultural heritage sector and the \emph{social, behavioral, and economic (SBE)} sciences and represents them in the W3C group.
+
+Within the DCMI task group, a collaboratively curated database of RDF validation requirements\footnote{Online available at: \url{http://purl.org/net/rdf-validation}} has been created which contains the findings of the working groups based on various case studies provided by data institutions \cite{BoschEckert2014}.
+It is publicly available and open for further contributions.
+The database connects requirements to use cases, case studies, and implementations and forms the basis of this paper. 
+We distinguish 81 requirements to formulate constraints on RDF data; 
+each of them corresponding to a constraint type.
+
+We collected constraints for commonly used vocabularies in the SBE domain, either from the vocabularies themselves or from domain and data experts, in order to gain a better understanding about the role of certain requirements for data quality and to direct the further development of constraint languages.
+All in all, this lead to 115 constraints we implemented on three vocabularies.
+We let the experts classify the constraints according to the severity of their violation.
+
+As we do not want to base our conclusions on the evaluation of vocabularies and constraint definitions alone, we conducted a large-scale experiment.
+For all these implemented 115 constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of SBE research data on three common vocabularies in SBE sciences (DDI-RDF, QB, SKOS) obtained from 33 SPARQL endpoints.
+
+\section{Common Vocabularies in SBE Sciences}
+\label{sbe-vocabularies}
+
+We took all well-established and newly developed SBE vocabularies into account and defined constraints for three vocabularies commonly used in the SBE sciences which are briefly introduced in the following.
+We analyzed actual data according to constraint violations, as for these vocabularies large data sets are already published.
+
+SBE sciences require high-quality data for their empirical research. For more than a decade, members of the SBE community have been developing and using a
+metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)}, \footnote{\url{http://www.ddialliance.org/Specification/}}
+an XML format to disseminate, manage,
+and reuse data collected and archived for research \cite{Vardigan2008}. 
+In XML, the definition of schemas containing constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
+With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration.
+Therefore, not only established vocabularies like SKOS are used;
+recently, members of the SBE and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.
+
+The data most often used in research within SBE sciences is \emph{unit-record data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers such as hospital records, registers of births and deaths.
+A \emph{study} represents the process by which a data set was generated or collected.
+The range of unit-record data is very broad - including census, education, health data and business, social, and labor force surveys.
+This type of research data is held within data archives or data libraries after it has been collected, so that it may be reused by future researchers.
+By its nature, unit-record data is highly confidential and access is often only permitted for qualified researchers who must apply for access.
+Researchers typically represent their results as aggregated data in form of multi-dimensional tables with only a few columns: so-called \emph{variables} such as \emph{sex} or \emph{age}.
+Aggregated data, which answers particular research questions, is derived from unit-record data by statistics on groups or aggregates such as frequencies and arithmetic means.
+The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying unit-record data.
+For more detailed analyses, researchers refer to unit-record data including additional variables needed to answer subsequent research questions.
+
+\emph{Formal childcare} is an example of an aggregated variable which captures the measured availability of childcare services in percent over the population in European Union member states by 
+the dimensions \emph{year}, \emph{duration}, \emph{age} of the child, and \emph{country}.
+Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
+The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger} or by a code list of age clusters (e.g., '0 to 10' and '11 to 20'). 
+The \emph{RDF QB Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{QBs}, i.e., multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}.
+%QB represents metadata on multi-dimensional aggregate data in two files: a \emph{qb:DataSet} and a \emph{qb:DataStructureDefinition}.
+A \emph{qb:DataStructureDefinition} contains metadata of the data collection.
+The variable \emph{formal childcare} is modeled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
+\emph{Year}, \emph{duration}, \emph{age}, and \emph{country} are \emph{qb:dimensions}.
+Data values, i.e., the availability of childcare services in percent over the population, are collected in a \emph{qb:DataSet}. 
+Each data value is represented inside a \emph{qb:Observation} which contains values for each dimension. 
+%(e.g., the year in which \emph{formal childcare} has been determined).
+%\ke{Wieso springt das von einer sehr knappen Einführung direkt zu konkreten (beliebigen?) Variablen?
+Ich möchte wissen, wofür QB benutzt wird und gerne ein konkretes %Beispiel sehen, um mir einen QB vorstellen zu können.}\tb{hmm, ich halte das beispiel für ein knappes und verständliches beipsiel wie eine tabelle in qb dargestellt wird / es ist auch der link enthalten zu der tabelle von eurostat}
+
+For more detailed analyses we refer to the underlying unit-record data.
+The aggregated variable \emph{formal childcare} is calculated on the basis of six unit-record variables (i.a., \emph{Education at pre-school}) for which detailed metadata is given (i.a., code lists) enabling researchers to replicate the results shown in aggregated data tables.
+\emph{DDI-RDF} is used to represent metadata on unit-record data in RDF.
+%The series (\emph{DDI-RDF:StudyGroup}) \emph{EU-SILC} contains one study (\emph{DDI-RDF:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
+%\emph{dcterms:spatial} points to the countries for which the data has been collected.
+The study (\emph{disco:Study}) for which the unit-record data has been collected 
+%\emph{EU-SILC 2011} 
+contains eight data sets (\emph{disco:LogicalDataSet})
+including variables (\emph{disco:Variable}) like the six ones needed to calculate the variable \emph{formal childcare}.
+%Metadata on unit-record data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
+%One common research question is ,e.g., the comparison of variables like 
+%\emph{formal childcare} between countries, for which the variable is collected within the context of an individual study, and other European or non European countries (e.g. OSCE).
+
+The \emph{Simple Knowledge Organization System (SKOS)} is reused to a large extend to build SBE vocabularies.
+The codes of the variable \emph{Education at pre-school} are modeled as \emph{skos:Concepts} and 
+a \emph{skos:OrderedCollection} organizes them in a particular order within a \emph{skos:memberList}.
+A variable may be associated with a theoretical concept (\emph{skos:Concept}) and \emph{skos:narrower} builds the hierarchy of theoretical concepts within a \emph{skos:ConceptScheme} of a study.
+The variable \emph{Education at pre-school} is assigned to the theoretical concept \emph{Child Care} which is a narrower concept of the top concept \emph{Education}.
+Controlled vocabularies (\emph{skos:ConceptScheme}), serving as extension and reuse mechanism,
+organize types (\emph{skos:Concept}) of descriptive statistics (\emph{disco:SummaryStatistics}) like minimum, maximum, and arithmetic mean.
+
+\section{Classification of Constraint Types and Constraints}
+\label{classification}
+
+To gain better insights into the role that certain types of constraints play for the quality of RDF data, we use two simple classifications: on the one hand, we classify RDF constraint types whether they are expressible by different types of constraint languages and on the other hand, we classify constraints formulated for a given vocabulary according to the perceived severity of their violation.
+
+Within the working groups, we identified by today 81 requirements to formulate RDF constraints (e.g., \emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type.\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}
+Within a technical report, we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages \cite{BoschNolleAcarEckert2015}.
+We provide mappings to representations in Description Logics (DL) \cite{Baader-2003} to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type.
+%In total, we distinguish 81 RDF constraint types as we identified 6 RDF constraint types which are only necessary for validating particular vocabularies.
+%Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
+For the three vocabularies, several SBE domain experts determined the default severity level of the 115 concrete constraints, which we published in a technical report \cite{BoschZapilkoWackerowEckert2015}.
+In the following, we summarize the classifications of constraint types and constraints for the purpose of our evaluation.
+
+\subsection{Classification of Constraint Types according to the Expressivity of Constraint Languages}
+
+According to the expressivity of constraint languages, the complete set of constraint types encompasses three not disjoint sets of constraint types:
+\begin{enumerate}
+	\item \emph{RDFS/OWL Based}
+	\item \emph{Constraint Language Based}
+	\item \emph{SPARQL Based}
+\end{enumerate}
+
+\textbf{\emph{RDFS/OWL Based}.}
+The modeling languages RDFS and OWL are typically used to formally specify vocabularies.
+\emph{RDFS/OWL Based} denotes the set of constraint types which can be formulated with RDFS/OWL axioms which we use in terms of constraints with CWA/UNA semantics and without reasoning.\footnote{The entailment regime is to be decided by the implementers.
+It is our point that reasoning affects validation and that a proper definition of the reasoning to be applied is needed.}
+
+\textbf{\emph{Constraint Language Based}.}
+We further distinguish \emph{Constraint Language Based} as the set of constraint types that can be expressed by common classical declarative high-level constraint languages like ShEx, ReSh, and DSP. 
+%RDFS, and OWL as we consider RDFS and OWL as constraint languages when assuming CWA/UNA semantics without reasoning. 
+There is a strong overlap between \emph{RDFS/OWL} and \emph{Constraint Language Based} constraint types as in many cases constraint types are expressible by both classical constraint languages and OWL.
+SPARQL, however, is considered as a low-level implementation language in this context.
+In contrast to SPARQL, high-level constraint languages are comparatively easy to understand and constraints can be formulated more concisely.
+Declarative languages may be placed on top of SPARQL when using it as an implementation language.
+
+\textbf{\emph{SPARQL Based}.}
+The set \emph{SPARQL Based} encompasses constraint types that are not expressible by RDFS/OWL or common high-level constraint languages but by plain SPARQL.
+
+\subsection{Classification of RDF Constraints according to the Severity of Constraint Violations}
+
+A concrete constraint is instantiated from one of the 81 constraint types and is defined for a specific vocabulary.
+It does not make sense to determine the severity of constraint violations of an entire constraint type,
+as the severity depends on the individual context and vocabulary.
+%as the violation of one constraint may be severe,
+%whereas, the violation of another constraint of the same type may be minor.
+SBE experts determined the default \emph{severity level}\footnote{The possibility to define severity levels in vocabularies is in itself a requirement (\emph{R-158}).} for each constraint to indicate how serious the violation of the constraint is.
+We use the classification system of log messages in software development like \emph{Apache Log4j 2} \cite{Apache-2015}, the \emph{Java Logging API},\footnote{\url{http://docs.oracle.com/javase/7/docs/api/java/util/logging/Level.html}} and the \emph{Apache Commons Logging API}\footnote{\url{http://commons.apache.org/proper/commons-logging/}} as many data practitioners also have experience in software development and software developers intuitively understand these levels.
+We simplify this commonly accepted classification system and distinguish the three severity levels (1) \emph{informational}, (2) \emph{warning}, and (3) \emph{error}.
+%According to the default severity level of constraints, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:\ke{auch dieser satz macht keinen sinn für mich, ebensowenig wie die extrem erhellende auflistung, die gleich folgt...
+mein vorschlag von eben kann das komplett ersetzen.}
+%\begin{itemize}
+	%\item \textbf{\emph{informational constraints}}: constraints with severity level \emph{informational}
+	%\item \textbf{\emph{warning constraints}}: constraints with severity level \emph{warning}
+	%\item \textbf{\emph{error constraints}}: constraints with severity level \emph{error}
+%\end{itemize}
+Violations of \emph{informational} constraints point to desirable but not necessary data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies.
+%They are not seen as serious errors.
+\emph{Warnings} are syntactic or semantic problems which typically should not lead to an abortion of data processing.
+\emph{Errors}, in contrast, are syntactic or semantic errors which should cause the abortion of data processing. 
+%Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
+%Data not conforming to \emph{warning constraints} but to \emph{error constraints} could be processed further.
+%Data not corresponding to \emph{error constraints}, however, cannot be processed further after validation. 
+Although we provide default severity levels for each constraint, validation environments should enable users to adapt the severity levels of constraints according to their individual needs.
+
 \section{Evaluation}
 
-\begin{table}[H]
-    \begin{center}
-    \begin{tabular}{@{}lcccccc@{}}
-           & \multicolumn{6}{c}{\textbf{Vocabularies}}
-    \\  \cmidrule{2-7}
-    \\       \textbf{Criteria (Counts)}
-           & \textbf{\rot{Person-Level Metadata (Disco)}}
-           & \textbf{\rot{Aggregated Metadata (Data Cube)}}
-					 & \textbf{\rot{Thesauri (SKOS)}}
-					 & \textbf{\rot{Rectangular Data (PHDD)}}
-					 & \textbf{\rot{Statistical Classifications (XKOS)}}
-					 & \textbf{\rot{Total}}
-    \\ \midrule
-		\emph{Validated Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 \\
-		\emph{Validated Data Sets} & 1,526 & 9,990 & 4,178 \\
-		\hline
-		\emph{Constraint Violations} & \textcolor{red}{XXXXX} \\
-		\emph{Constraint Violations ($\mathcal{SL}_{0}$)} & \textcolor{red}{XXXXX} \\
-		\emph{Constraint Violations ($\mathcal{SL}_{1}$)} & 473,574 $\equiv$ \textcolor{red}{XXXXX}\% \\
-    \emph{Constraint Violations ($\mathcal{SL}_{2}$)} & \textcolor{red}{XXXXX} \\
-				\hline
-		\emph{Constraint Types} & 52 (15\textbar 37) \\
-		\emph{Constraint Types} ($\mathcal{C}_{C}$) & 30 $\equiv$ 57.7 \% \\
-		\emph{Constraint Types} ($\mathcal{C}_{T}$) & 22 $\equiv$ 42.3 \% \\
-		\hline
-		\emph{Constraints} & 142 (77\textbar 65) \\
-		\emph{Constraints} ($\mathcal{C}_{C}$) & 72 $\equiv$ 50.7 \% \\
-		\emph{Constraints} ($\mathcal{C}_{T}$) & 70 $\equiv$ 49.3 \% \\
-		\emph{Constraints ($\mathcal{SL}_{0}$)} & 75 $\equiv$ 52.8\% (44\textbar 31)\\
-		\emph{Constraints ($\mathcal{SL}_{1}$)} & 9 $\equiv$ 6.3\% (8\textbar 1)\\
-		\emph{Constraints ($\mathcal{SL}_{2}$)} & 58 $\equiv$ 40.8\% (25\textbar 33)\\
-    \bottomrule
-    \end{tabular}
-    \caption{Evaluation}
-		\label{tab:evaluation}
-    \end{center}
-\end{table}
+In this section, we describe our results based on an automatic constraint checking of a large data set.
+Despite the large volume of the data set in general, we have to keep in mind that this study only uses data for three vocabularies.
+As described in Section~\ref{sbe-vocabularies}, for other vocabularies there is often not (yet) enough data openly available to draw general conclusions.
+The three vocabularies, however, are representative, cover different aspects of SBE data, and are also a mixture of widely adopted and accepted well-established vocabularies (QB, SKOS) and a vocabulary under development (DDI-RDF\footnote{Expected publication at the end of the year 2015}).
+
+\subsection{Experimental Setup}
+\label{implementation}
+
+%\ke{Überarbeiten und mit nächstem teil mergen. Nur das erzählen, was für die Auswertung auf den Datensets relevant ist. 115 constraints, 3 vokabulare, wie wurden die datasets daraufhin validiert.}
+
+	%\item First, we assigned each constraint type to exactly one of the disjoint sets of constraint types 
+%in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$).
+On the three vocabularies (DDI-RDF, QB, SKOS), we identified and classified 115 constraints\footnote{All 115 implemented constraints are online available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} which we implemented for data validation.
+We ensured that the implementation of the constraints is equally distributed over the classes and vocabularies we have.
+We then evaluated the data quality of 15,694 data sets (4.26 billion triples) of SBE research data using these 115 constraints, obtained from 33 SPARQL endpoints.
+
+%QB and SKOS are well-established vocabularies which are widely adopted and accepted. DDI-RDF is a newly developed vocabulary which will be published in 2015.
+
+%It is likely that such a vocabulary is still subject of constant change, that published data may not be consistent with its current version,
+%and that early adopters did not properly understand its formal specification.
+%\ke{ergebnisse, dann hypothesen, dann kritische auseinandersetzung}
+
+Table~\ref{tab:datasets} lists the number of validated data sets and the overall sizes in terms of triples for each of the vocabularies. We validated, i.a., 
+(1) QB data sets published by the \emph{Australian Bureau of Statistics},
+the \emph{European Central Bank}, and the
+\emph{Organisation for Economic Co-operation and Development},
+(2) SKOS thesauri like the \emph{AGROVOC Multilingual agricultural thesaurus},
+the \emph{STW Thesaurus for Economics}, and the
+\emph{Thesaurus for the Social Sciences}, and
+(3) DDI-RDF data sets provided by the \emph{Microdata Information System}, 
+the \emph{Data Without Boundaries Discovery Portal}, the
+\emph{Danish Data Archive}, and the
+\emph{Swedish National Data Service}.
+We published the evaluation results for each QB data set in form of one document per SPARQL endpoint.\footnote{Online available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}
+
+\begin{table}[H]
+		\scriptsize
+    \begin{center}
+		\caption{Validated Data Sets for each Vocabulary}
+		\label{tab:datasets}
+    \begin{tabular}{lrr}
+%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
+%    \\  \cmidrule{2-7}
+           \textbf{Vocabulary}
+           & \textbf{Data Sets}
+           & \textbf{Triples}
+
+    \\ \midrule
+		%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
+		%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
+		%\hline
+		\textbf{QB} & $9,990$   & $3,775,983,610$  \\
+		\textbf{SKOS} & $4,178$  & $477,737,281$ \\
+		\textbf{DDI-RDF} & $1,526$  & $9,673,055$  \\
+    \bottomrule
+    \end{tabular}
+    %\\ \emph{C (constraints), CT (constraint types)}
+    \end{center}
+\end{table}
+
+Since the validation of each of the 81 constraint types can be implemented using SPARQL, we use \emph{SPIN}, a SPARQL-based way to formulate and check constraints, as basis to develop a
+validation environment to validate RDF data according to constraints expressed by arbitrary constraint languages\footnote{Constraint language implementations online available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} \cite{BoschEckert2014-2}.
+The \emph{RDF Validator}\footnote{Online demo available at: \url{http://purl.org/net/rdfval-demo}, source code online available at: \url{https://github.com/boschthomas/rdf-validator}} can directly be used to validate arbitrary RDF data for the three vocabularies.
+Additionally, own constraints on any vocabulary can be defined using several constraint languages.
+The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.
+There is one SPIN construct template for each constraint type.
+A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples indicating the subject and the properties causing constraint violations and the reason why constraint violations have been raised.
+A SPIN construct template creates constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
+%\emph{Missy}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}} provides comprehensive Linked Data services like diverse RDF exports of unit-record metadata conforming to the DDI-RDF vocabulary in form of multiple concrete syntaxes.
+
+\subsection{Evaluation Results}
+
+%DCAT: 11 constraints defined
+%PHDD: 12
+%XKOS: 10
+
+%The majority (48 $\equiv$ 58.5\%) of the overall 81 $\mathcal{CT}$ constraint types are $\mathcal{CT}_{B}$ whose constraints can therefore be derived from vocabularies without any effort.
+%Among $\mathcal{CT}_{B}$, two-thirds (34 $\equiv$ 70.8\%) are $\mathcal{C}_B ^{\mathcal{R}}$, i.e., constraint types for which reasoning may be performed prior to validation, and one third (14 $\equiv$ 29.2\%) are $\overline{\mathcal{C}_B ^{\mathcal{R}}}$, i.e., constraint types for which reasoning does not make any sense.
+%A quarter (20 $\equiv$ 24.4\%) of all constraint types are $\mathcal{CT}_{S}$ and a sixth (14 $\equiv$ 17.1\%) are $\mathcal{CT}_{C}$.
+%
+%\begin{table}[H]
+		%\scriptsize
+    %\begin{center}
+    %\begin{tabular}{@{}lcccc@{}}
+%%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
+%%    \\  \cmidrule{2-7}
+    %\\       \textbf{Criteria}
+           %& \textbf{DDI-RDF}
+           %& \textbf{QB}
+					 %& \textbf{SKOS}
+					 %& \textbf{Total}
+    %\\ \midrule
+		%%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
+		%%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
+		%%\hline
+		%\emph{CT} & 52 & 20 & 15 & 53 \\
+		%\hline
+		%$\mathcal{CT}_{C}$ & 9 (17.3\%) & 2 (10\%) & 2 (13.3\%) & 9 (17\%) \\
+		%$\mathcal{CT}_{S}$ & 16 (30.8\%) & 3 (15\%) & 4 (26,7\%) & 16 (30.2\%) \\
+		%$\mathcal{CT}_{B}$ & 27 (\textbf{51.9\%}) & 15 (\textbf{75\%}) & 9 (\textbf{60\%}) & 28 (\textbf{52.8\%}) \\
+		%\hline
+		%$\mathcal{C}_B ^{\mathcal{R}}$ & 18 (34.6\%) & 9 (45\%) & 4 (26.7\%) & 19 (35.9\%) \\
+		%$\overline{\mathcal{C}_B ^{\mathcal{R}}}$ & 9 (17.3\%) & 6 (30\%) & 5 (33.3\%) & 9 (17\%) \\
+    %\bottomrule
+    %\end{tabular}
+    %%\\ \emph{C (constraints), CT (constraint types)}
+    %\caption{Evaluation - Constraint Types}
+		%\label{tab:evaluation-constraint-types}
+    %\end{center}
+%\end{table}
+
+%Table \ref{tab:evaluation-constraint-types} displays the evaluation of the metadata quality on real world data sets regarding constraint types.
+Tables \ref{tab:evaluation-constraint-violations-1} and \ref{tab:evaluation-constraint-violations-2} show the results of the evaluation, more specifically the constraints and the constraint violations, which are caused by these constraints, in percent; whereas the numbers in the first line indicate the absolute amount of constraints and violations.
+The constraints and their raised violations are grouped by vocabulary, which type of language the constraint types are formulated with, and their severity level.
+The numbers of validated triples and data sets differ between the vocabularies
+as we validated 3.8 billion QB, 480 million SKOS, and 10 million DDI-RDF triples.
+To be able to formulate findings which apply for all vocabularies, 
+we only use normalized relative values representing the percentage of constraints and violations belonging to the respective sets.
+
+There is a strong overlap between \emph{RDFS/OWL} and \emph{Constraint Language Based} constraint types as in many cases constraint types are expressible by RDFS/OWL and classical constraint languages.
+This is the reason why the percentage values of constraints and violations grouped by the classification of constraint types according to the expressivity of constraint languages do not accumulate to 100\%.
+
+\begin{table}[H]
+		\scriptsize
+    \begin{center}
+		\caption{Constraints and Constraint Violations (1)}
+		\label{tab:evaluation-constraint-violations-1}
+    \begin{tabular}{@{}lcc|cc@{}}
+    %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
+    %\\  \cmidrule{2-3}
+		%\hline
+    \multirow{2}{*}{} &
+      \multicolumn{2}{c}{\textbf{DDI-RDF}} &
+      \multicolumn{2}{c}{\textbf{QB}} \\
+    \textbf{} & C & CV & C & CV \\
+    \hline
+    %\\ \midrule
+		 & 78 & 3,575,002 & 20 & 45,635,861 \\
+		\hline
+		\textbf{\emph{SPARQL}} & 29.5 & 34.7 & \textbf{60.0} & \textbf{100.0} \\
+		\textbf{\emph{CL}} & \textbf{64.1} & \textbf{65.3} & 40.0 & 0.0 \\
+		\textbf{\emph{RDFS/OWL}} & \textbf{66.7} & \textbf{65.3} & 40.0 & 0.0 \\
+		\hline
+		\textbf{\emph{info}} & \textbf{56.4} & \textbf{52.6} & 0.0 & 0.0 \\
+		\textbf{\emph{warning}} & 11.5 & 29.4 & 15.0 & \textbf{99.8} \\
+		\textbf{\emph{error}} & 32.1 & 18.0 & \textbf{85.0} & 0.3 \\
+    \bottomrule
+    \end{tabular}
+    \\ \emph{C (constraints), CV (constraint violations)}
+    \end{center}
+\end{table}
+
+\begin{table}[H]
+		\scriptsize
+    \begin{center}
+		\caption{Constraints and Constraint Violations (2)}
+		\label{tab:evaluation-constraint-violations-2}
+    \begin{tabular}{@{}lcc|cc@{}}
+    %       & \multicolumn{2}{c}{\textbf{Vocabularies}}
+    %\\  \cmidrule{2-3}
+		%\hline
+    \multirow{2}{*}{} &
+      \multicolumn{2}{c}{\textbf{SKOS}} &
+      \multicolumn{2}{c}{\textbf{\emph{Total}}} \\
+    \textbf{} & C & CV & C & CV \\
+    \hline
+    %\\ \midrule
+		 & 17 & 5,540,988 & 115 & 54,751,851 \\
+		\hline
+		\textbf{\emph{SPARQL}} & \textbf{100.0} & \textbf{100.0} & \textbf{63.2} & \textbf{78.2} \\
+		\textbf{\emph{CL}} & 0.0 & 0.0 & 34.7 & 21.8 \\
+		\textbf{\emph{RDFS/OWL}} & 0.0 & 0.0 & 35.6 & 21.8 \\
+		\hline
+		\textbf{\emph{info}} & \textbf{70.6} & 41.2 & \textbf{42.3} & 31.3 \\
+		\textbf{\emph{warning}} & 29.4 & \textbf{58.8} & 18.7 & \textbf{62.7} \\
+		\textbf{\emph{error}} & 0.0 & 0.0 & \textbf{39.0} & 6.1\\
+    \bottomrule
+    \end{tabular}
+    \\ \emph{C (constraints), CV (constraint violations)}
+    \end{center}
+\end{table}
+
+%More than the half of them are $\mathcal{CT}_{B}$, nearly a third $\mathcal{CT}_{S}$, and only a sixth $\mathcal{CT}_{C}$ constraint types.
+%For DDI-RDF, QB, and SKOS, more than 50\% of the instantiated constraint types are $\mathcal{CT}_{B}$ constraint types 
+%(for QB even three quarters).
+%\emph{Existential quantifications} (\emph{R-86}, 32.4\%, DDI-RDF), \emph{data model consistency} (31.4\%, QB), and \emph{structure} (28.6\%, SKOS) are the constraint types the most constraints are instantiated from.
+%\tb{1. Fakten (diese Fakten bewirken eine Erhöhung der Datenqualität) 2. Hypothese (unsere Interpretation der Ergebnisse, unsere Behauptung)}
 
@@
 
-\begin{table}
+In this sub-section, we describe how the tables in this paper should be read.
+Table \ref{tab:legend} gives an overview over the symbols used in subsequent tables of the detailed evaluation.
+
+\begin{table}[H]
 	\centering
@@
 			\hline
-			\textbf{\emph{(X)}} & The validation of \emph{X} data sets could not be finished \\
-			           & due to SPARQL endpoints' technical restrictions (e.g. the defined timeout). \\
-			\hline
-			\textbf{\emph{\textsuperscript{*}}} & severity level $\mathcal{SL}_{0}$ (informational) \\
-			\hline
-			\textbf{\emph{\textsuperscript{**}}} & severity level $\mathcal{SL}_{1}$ (warning) \\
-			\hline
-			\textbf{\emph{\textsuperscript{***}}} & severity level $\mathcal{SL}_{2}$ (error) \\
+			\textbf{\emph{(X)}} & The validation of \emph{X} data sets could not be finished, \\
+			           & due to SPARQL endpoints' technical restrictions (e.g., defined timeouts). \\
+			\hline
+			\textbf{\emph{\textsuperscript{*}}} & default severity level \emph{informational} \\
+			\textbf{\emph{\textsuperscript{**}}} & default severity level \emph{warning} \\
+			\textbf{\emph{\textsuperscript{***}}} & default severity level \emph{error} \\
 		\end{tabular}
@@
 It is likely that there are more than \emph{X} constraint violations.
-Although, the result set contains not the whole set of raised constraint violation triples,
-the constraint can be used as an indicator if there data not conforming to the constraint and
+Although the result set contains not the whole set of raised constraint violation triples,
+the constraint can be used as an indicator if there is data not conforming to the constraint and
 to resolve constraint violations step by step. 
@@
 As part of future work, the performance will be improved. 
-
-\section{Person-Level Metadata (Disco)}
-
-\subsection{Evaluation Results}
-
-Legend: total (implemented\textbar not yet implemented)
+\end{itemize}
+
+\section{Evaluation of Metadata on Unit-Record Data Sets (DDI-RDF)}
+
+In this section, the quality of the metadata on unit-record data sets (DDI-RDF) is evaluated by validating appropriate RDF constraints assigned to several RDF constraint types.
+First, we give an overview on the evaluated data sets and finally we provide details about the evaluation.
+
+\subsection{Data Sets Overview}
+
+Tables \ref{tab:disco-data-sets-abbreviations} and \ref{tab:disco-sparql-endpoints} give an overview on the evaluated DDI-RDF data sets, their abbreviations, and publicly available SPARQL endpoints.
+Table \ref{tab:disco-overview} comprehends the number of triples, data sets, and instances of multiple vocabulary-specific classes.
 
@@
 		\begin{tabular}{l|l}
-      \textbf{Evaluation Criteria} & \textbf{Counts} \\		
-      \hline
-		\emph{Validated Triples} & 9,673,055 \\
-		\emph{Validated Data Sets} & 1,526 \\
-		\hline
-		\emph{Constraint Violations} & \textcolor{red}{XXXXX} \\
-		\emph{Constraint Violations ($\mathcal{SL}_{0}$)} & \textcolor{red}{XXXXX} \\
-		\emph{Constraint Violations ($\mathcal{SL}_{1}$)} & 473,574 $\equiv$ \textcolor{red}{XXXXX}\% \\
-    \emph{Constraint Violations ($\mathcal{SL}_{2}$)} & \textcolor{red}{XXXXX} \\
-		\hline
-		\emph{Constraint (Most Constraint Violations)} & \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} (547,916) \\
-		                                               & \emph{DISCO-C-COMPARISON-VARIABLES-02} (547,916) \\
-		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{0}$))} & \emph{DISCO-C-LABELING-AND-DOCUMENTATION-06} (547,916) \\
-		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{1}$))} & \emph{DISCO-C-EXISTENTIAL-QUANTIFICATIONS-46} (468,807) \\
-		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{2}$))} & \emph{DISCO-C-COMPARISON-VARIABLES-02} (547,916) \\
-		\hline
-		\emph{Constraint Types} & 52 (15\textbar 37) \\
-		\emph{Constraint Types} ($\mathcal{C}_{C}$) & 30 $\equiv$ 57.7 \% \\
-		\emph{Constraint Types} ($\mathcal{C}_{T}$) & 22 $\equiv$ 42.3 \% \\
-		\hline
-		\emph{Constraint Types (Most Constraints)} & 1. Existential Quantifications: 46 $\equiv$ 32.4\% (46\textbar 0) \\
-		                                            & 2. Data Model Consistency: 7 (1\textbar 6) \\
-																								& 3. Aggregation: 7 (0\textbar 7) \\
-		\emph{Constraint Type (Most Constraints ($\mathcal{SL}_{2}$))} & Existential Quantifications: 9 (9\textbar 0) \\
-		\hline
-		\emph{Constraints} & 142 (77\textbar 65) \\
-		\emph{Constraints} ($\mathcal{C}_{C}$) & 72 $\equiv$ 50.7 \% \\
-		\emph{Constraints} ($\mathcal{C}_{T}$) & 70 $\equiv$ 49.3 \% \\
-		\emph{Constraints ($\mathcal{SL}_{0}$)} & 75 $\equiv$ 52.8\% (44\textbar 31)\\
-		\emph{Constraints ($\mathcal{SL}_{1}$)} & 9 $\equiv$ 6.3\% (8\textbar 1)\\
-		\emph{Constraints ($\mathcal{SL}_{2}$)} & 58 $\equiv$ 40.8\% (25\textbar 33)\\
-		\end{tabular}
-    \caption{Evaluation of Disco Data Sets - Evaluation Results}
-		\label{tab:disco-evaluation-results}
-\end{table}
-
-%\begin{table}[H]
-    %\begin{center}
-    %\begin{tabular}{@{}lc@{}}
-           %& \multicolumn{1}{c}{\textbf{Constraint Types}}
-    %\\  \cmidrule{2-2}
-    %\\       \textbf{Criteria (Counts)}
-           %& \textbf{\rot{Existential Quantifications}}
-    %\\ \midrule
-		%\emph{Constraints / Constraint Type} & 46 \\
-    %\bottomrule
-    %\end{tabular}
-    %\caption{Evaluation of Disco Data Sets - Evaluation Results (2)}
-		%\label{tab:disco-evaluation-results-2}
-    %\end{center}
-%\end{table}
-
-\subsection{Data Sets Overview}
-
-\begin{table}[H]
-	\centering
-		\begin{tabular}{l|l}
-      \textbf{Abbr.} & \textbf{Disco Data Sets} \\		
+      \textbf{Abbr.} & \textbf{DDI-RDF Data Sets} \\		
       \hline
@@
 		\end{tabular}
-	\caption{Disco Data Sets Abbreviations}
+	\caption{DDI-RDF Data Sets Abbreviations}
 	\label{tab:disco-data-sets-abbreviations}
@@
     \end{tabular}
-    \caption{Disco Data Sets Overview}
+    \caption{DDI-RDF Data Sets Overview}
 		\label{tab:disco-overview}
@@
 		\end{tabular}
-	\caption{Disco SPARQL Endpoints}
+	\caption{DDI-RDF SPARQL Endpoints}
 	\label{tab:disco-sparql-endpoints}
@@
 \subsection{Detailed Evaluation}
+
+In this sub-section, we give details about the evaluation in form of diverse tables containing the number of constraint violations per evaluated data set and constraint of particular constraint types.
 
@@
     \end{tabular}
-    \caption{Evaluation of Disco Data Sets - Existential Quantifications (1)}
+    \caption{Evaluation of DDI-RDF Data Sets - Existential Quantifications (1)}
 		\label{tab:evaluation-disco-existential-quantifications-1}
@@
     \end{tabular}
-    \caption{Evaluation of Disco Data Sets - Existential Quantifications (2)}
+    \caption{Evaluation of DDI-RDF Data Sets - Existential Quantifications (2)}
 		\label{tab:evaluation-disco-existential-quantifications-2}
@@
     \end{tabular}
-    \caption{Evaluation of Disco Data Sets - Existential Quantifications (3)}
+    \caption{Evaluation of DDI-RDF Data Sets - Existential Quantifications (3)}
 		\label{tab:evaluation-disco-existential-quantifications-3}
@@
     \end{tabular}
-    \caption{Evaluation of Disco Data Sets - Existential Quantifications (4)}
+    \caption{Evaluation of DDI-RDF Data Sets - Existential Quantifications (4)}
 		\label{tab:evaluation-disco-existential-quantifications-4}
@@
     \end{tabular}
-    \caption{Evaluation of Disco Data Sets - Existential Quantifications (5)}
+    \caption{Evaluation of DDI-RDF Data Sets - Existential Quantifications (5)}
 		\label{tab:evaluation-disco-existential-quantifications-5}
@@
     \end{tabular}
-    \caption{Evaluation of Disco Data Sets - Conditional Properties}
+    \caption{Evaluation of DDI-RDF Data Sets - Conditional Properties}
 		\label{tab:evaluation-disco-conditional-properties}
@@
     \end{tabular}
-    \caption{Evaluation of Disco Data Sets - Provenance}
+    \caption{Evaluation of DDI-RDF Data Sets - Provenance}
 		\label{tab:evaluation-disco-provenance}
@@
     \end{tabular}
-    \caption{Evaluation of Disco Data Sets - Labeling and Documentation}
+    \caption{Evaluation of DDI-RDF Data Sets - Labeling and Documentation}
 		\label{tab:evaluation-disco-labeling-and-documentation}
@@
     \end{tabular}
-    \caption{Evaluation of Disco Data Sets - Data Model Consistency}
+    \caption{Evaluation of DDI-RDF Data Sets - Data Model Consistency}
 		\label{tab:evaluation-disco-data-model-consistency}
@@
     \end{tabular}
-    \caption{Evaluation of Disco Data Sets - Comparison}
+    \caption{Evaluation of DDI-RDF Data Sets - Comparison}
 		\label{tab:evaluation-disco-comparison}
@@
     \end{tabular}
-    \caption{Evaluation of Disco Data Sets - Mathematical Operations}
+    \caption{Evaluation of DDI-RDF Data Sets - Mathematical Operations}
 		\label{tab:evaluation-disco-mathematical-operations}
@@
     \end{tabular}
-    \caption{Evaluation of Disco Data Sets - Language Tags}
+    \caption{Evaluation of DDI-RDF Data Sets - Language Tags}
 		\label{tab:evaluation-disco-language-tags}
@@
     \end{tabular}
-    \caption{Evaluation of Disco Data Sets - Aggregation}
+    \caption{Evaluation of DDI-RDF Data Sets - Aggregation}
 		\label{tab:evaluation-disco-aggregation}
@@
     \\  \cmidrule{2-4}
-    \\       \textbf{Disco Constraints}
+    \\       \textbf{DDI-RDF Constraints}
            & \rot{\emph{Missy}}
@@
     \end{tabular}
-    \caption{Evaluation of Disco Data Sets - Disco Constraints (1)}
+    \caption{Evaluation of DDI-RDF Data Sets - DDI-RDF Constraints (1)}
 		\label{tab:evaluation-disco-disco-constraints-1}
@@
 		\emph{DISCO-C-VALUE-IS-VALID-FOR-DATATYPE-02}\textsuperscript{***} & $\checkmark$ & $\checkmark$ & $\checkmark$ \\
-		\emph{DISCO-C-SUBSUMPTION-01 (!)}\textsuperscript{***} \\
+		\emph{DISCO-C-SUBSUMPTION-01 (!)}\textsuperscript{***}\textsuperscript{B} \\
 		\emph{DISCO-C-CLASS-EQUIVALENCE-01 (!)}\textsuperscript{*} \\
@@
     \end{tabular}
-    \caption{Evaluation of Disco Data Sets - Disco Constraints (2)}
+    \caption{Evaluation of DDI-RDF Data Sets - DDI-RDF Constraints (2)}
 		\label{tab:evaluation-disco-disco-constraints-2}
@@
     \end{tabular}
-    \caption{Evaluation of Disco Data Sets - Disco Constraints (3)}
+    \caption{Evaluation of DDI-RDF Data Sets - DDI-RDF Constraints (3)}
 		\label{tab:evaluation-disco-disco-constraints-3}
@@
     \end{tabular}
-    \caption{Evaluation of Disco Data Sets - Disco Constraints (4)}
+    \caption{Evaluation of DDI-RDF Data Sets - DDI-RDF Constraints (4)}
 		\label{tab:evaluation-disco-disco-constraints-4}
@@
     \end{tabular}
-    \caption{Evaluation of Disco Data Sets - Disco Constraints (5)}
+    \caption{Evaluation of DDI-RDF Data Sets - DDI-RDF Constraints (5)}
 		\label{tab:evaluation-disco-disco-constraints-5}
@@
     \end{tabular}
-    \caption{Evaluation of Disco Data Sets - Disco Constraints (6)}
+    \caption{Evaluation of DDI-RDF Data Sets - DDI-RDF Constraints (6)}
 		\label{tab:evaluation-disco-disco-constraints-6}
@@
 
-\section{Aggregated Metadata (Data Cube)}
-
-\subsection{Evaluation Results}
-
-\begin{table}[H]
-	\centering
-		\begin{tabular}{l|l}
-      \textbf{Evaluation Criteria} & \textbf{Counts} \\		
-      \hline
-		\emph{Validated Triples} & 3,775,983,610 \\
-		\emph{Validated Data Sets} & 9,990 \\
-		\hline
-		\emph{Constraint Violations} & 45,635,846 \\
-		\emph{Constraint Violations ($\mathcal{SL}_{0}$)} & 0 $\equiv$ 0\% \\
-		\emph{Constraint Violations ($\mathcal{SL}_{1}$)} & 45,520,613 $\equiv$ 99.75\% \\
-    \emph{Constraint Violations ($\mathcal{SL}_{2}$)} & 115,233 $\equiv$ 0.25\% \\
-		\hline
-		\emph{Constraint (Most Constraint Violations)} & \emph{DATA-MODEL-CONSISTENCY-05} (45,514,102) \\
-		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{0}$))} & - \\
-		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{1}$))} & \emph{DATA-MODEL-CONSISTENCY-05} (45,514,102) \\
-		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{2}$))} & \emph{MINIMUM-QUALIFIED-CARDINALITY-RESTRICTIONS-02} \\
-		                                                                    & (1,556) \\
-		\hline
-		\emph{Constraint Types} & 20 (7\textbar 13) \\
-		\emph{Constraint Types} ($\mathcal{C}_{C}$) & 5 $\equiv$ 25 \% \\
-		\emph{Constraint Types} ($\mathcal{C}_{T}$) & 15 $\equiv$ 75 \% \\
-		\hline
-		\emph{Constraint Types (Most Constraints)} & 1. Data Model Consistency: 11 $\equiv$ 31.4\% (10\textbar 1) \\
-		                                           & 2. Existential Quantifications: 4 $\equiv$ 11.4\% (4\textbar 0) \\
-		\emph{Constraint Type (Most Constraints ($\mathcal{SL}_{2}$))} & Data Model Consistency: 8 $\equiv$ 22.9\% (7\textbar 1) \\
-		\hline
-		\emph{Constraints} & 35 (20\textbar 15) \\
-		\emph{Constraints} ($\mathcal{C}_{C}$) & 16 (12\textbar 4) \\
-		\emph{Constraints} ($\mathcal{C}_{T}$) & 19 (8\textbar 11) \\
-		\emph{Constraints ($\mathcal{SL}_{0}$)} & 4 $\equiv$ 11.4\% (0\textbar 4) \\
-		\emph{Constraints ($\mathcal{SL}_{1}$)} & 3 $\equiv$ 8.6\% (3\textbar 0) \\
-		\emph{Constraints ($\mathcal{SL}_{2}$)} & 28 $\equiv$ 80\% (17\textbar 11) \\
-		\end{tabular}
-    \caption{Evaluation of Data Cube Data Sets - Evaluation Results}
-		\label{tab:data-cube-evaluation-results}
-\end{table}
+\section{Evaluation of Metadata and Data of Aggregated Data Sets (QB)}
+
+In this section, the quality of the metadata on aggregated data (QB) data sets and of the data sets themselves is evaluated by validating appropriate RDF constraints assigned to several RDF constraint types.
+First, we we give an overview on the evaluated data sets and finally we provide details about the evaluation.
 
@@
 
-\begin{itemize}
-  \item overview over Data Cube data sets\footnote{\url{http://270a.info/}; \url{http://datahub.io/de/dataset?tags=format-qb}} 
-  \item \url{http://ontologycentral.com/}
-\end{itemize}
+There are websites giving an overview on available QB data sets\footnote{\url{http://270a.info/}; \url{http://datahub.io/de/dataset?tags=format-qb}; \url{http://ontologycentral.com/}}. 
+Tables \ref{tab:data-cube-data-sets-abbreviations} and \ref{tab:data-cube-sparql-endpoints} give an overview on the evaluated QB data sets, their abbreviations, and publicly available SPARQL endpoints.
+Table \ref{tab:data-cube-overview} comprehends the number of triples, data sets, and instances of multiple vocabulary-specific classes.
 
@@
 		%\end{tabular}
-	%\caption{Data Cube Data Sets}
+	%\caption{QB Data Sets}
 	%\label{tab:data-cube-data-sets}
@@
 		\begin{tabular}{l|l}
-      \textbf{Abbr.} & \textbf{Data Cube Data Sets} \\		
+      \textbf{Abbr.} & \textbf{QB Data Sets} \\		
       \hline
@@
 		\end{tabular}
-	\caption{Data Cube Data Sets Abbreviations}
+	\caption{QB Data Sets Abbreviations}
 	\label{tab:data-cube-data-sets-abbreviations}
@@
     \end{tabular}
-    \caption{Data Cube Data Sets Overview}
+    \caption{QB Data Sets Overview}
+		\label{tab:data-cube-overview}
     \end{center}
@@
 		\end{tabular}
-	\caption{Data Cube SPARQL Endpoints}
+	\caption{QB SPARQL Endpoints}
 	\label{tab:data-cube-sparql-endpoints}
@@
     \end{tabular}
-    \caption{Evaluation of Data Cube Data Sets - Data Model Consistency (1)}
+    \caption{Evaluation of QB Data Sets - Data Model Consistency (1)}
 		\label{evaluation-of-data-cube-data-sets-data-model-consistency-1}
@@
     \end{tabular}
-    \caption{Evaluation of Data Cube Data Sets - Data Model Consistency (2)}
+    \caption{Evaluation of QB Data Sets - Data Model Consistency (2)}
 		\label{evaluation-of-data-cube-data-sets-data-model-consistency-1}
@@
     \end{tabular}
-    \caption{Evaluation of Data Cube Data Sets - Existential Quantifications}
+    \caption{Evaluation of QB Data Sets - Existential Quantifications}
     \end{center}
@@
     \end{tabular}
-    \caption{Evaluation of Data Cube Data Sets - Cardinality Restrictions (1)}
+    \caption{Evaluation of QB Data Sets - Cardinality Restrictions (1)}
     \end{center}
@@
     \end{tabular}
-    \caption{Evaluation of Data Cube Data Sets - Cardinality Restrictions (2)}
+    \caption{Evaluation of QB Data Sets - Cardinality Restrictions (2)}
     \end{center}
@@
     \end{tabular}
-    \caption{Evaluation of Data Cube Data Sets - Structure}
+    \caption{Evaluation of QB Data Sets - Structure}
     \end{center}
@@
     \end{tabular}
-    \caption{Evaluation of Data Cube Data Sets - Constraints (1)}
+    \caption{Evaluation of QB Data Sets - Constraints (1)}
     \end{center}
@@
     \end{tabular}
-    \caption{Evaluation of Data Cube Data Sets - Constraints (2)}
-    \end{center}
-\end{table}
-
-\section{Thesauri (SKOS)}
-
-\subsection{Evaluation Results}
-
-\begin{table}[H]
-	\centering
-		\begin{tabular}{l|l}
-      \textbf{Evaluation Criteria} & \textbf{Counts} \\		
-      \hline
-		\emph{Validated Triples} & \textcolor{red}{XXXXX} \\
-		\emph{Validated Data Sets} & \textcolor{red}{XXXXX} \\
-		\hline
-		\emph{Constraint Violations} & \textcolor{red}{XXXXX} \\
-		\emph{Constraint Violations ($\mathcal{SL}_{0}$)} & \textcolor{red}{XXXXX} \\
-		\emph{Constraint Violations ($\mathcal{SL}_{1}$)} & \textcolor{red}{XXXXX} $\equiv$ \textcolor{red}{XXXXX}\% \\
-    \emph{Constraint Violations ($\mathcal{SL}_{2}$)} & \textcolor{red}{XXXXX} \\
-		\hline
-		\emph{Constraint (Most Constraint Violations)} & \emph{LANGUAGE-TAG-CARDINALITY-01} (2,508,903) \\
-		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{0}$))} & \emph{LABELING-AND-DOCUMENTATION-06} (1,022,362) \\
-		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{1}$))} & \emph{LANGUAGE-TAG-CARDINALITY-01} (2,508,903) \\
-		\emph{Constraint (Most Constraint Violations ($\mathcal{SL}_{2}$))} & - \\
-		\hline
-		\emph{Constraint Types} & 14 (4\textbar 10) \\
-		\emph{Constraint Types} ($\mathcal{C}_{C}$) & 5 $\equiv$ 35.7\% \\
-		\emph{Constraint Types} ($\mathcal{C}_{T}$) & 9 $\equiv$ 64.3\% \\
-		\hline
-		\emph{Constraint Types (Most Constraints)} & 1. Structure: 10 $\equiv$ XX\% (8\textbar 2) \\
-		                                           & 2. Labeling and Documentation: 6 $\equiv$ XX\% (5\textbar 1) \\
-																							 & 3. Language Tag Cardinality: 4 $\equiv$ XX\% (4\textbar 0) \\
-		\emph{Constraint Type (Most Constraints ($\mathcal{SL}_{2}$))} & Structure: 1 (0\textbar 1) \\
-		\hline
-		\emph{Constraints} & 35 (17\textbar 18) \\
-		\emph{Constraints} ($\mathcal{C}_{C}$) & 21 (13\textbar 8) \\
-		\emph{Constraints} ($\mathcal{C}_{T}$) & 14 (4\textbar 10) \\
-		\emph{Constraints ($\mathcal{SL}_{0}$)} & 21 $\equiv$ 60\% (12\textbar 9) \\
-		\emph{Constraints ($\mathcal{SL}_{1}$)} & 5 $\equiv$ 14.3\% (5\textbar 0) \\
-		\emph{Constraints ($\mathcal{SL}_{2}$)} & 9 $\equiv$ 25.7\% (0\textbar 9) \\
-		\end{tabular}
-    \caption{Evaluation of Thesauri Data Sets - Evaluation Results}
-		\label{tab:thesauri-evaluation-results}
-\end{table}
+    \caption{Evaluation of QB Data Sets - Constraints (2)}
+    \end{center}
+\end{table}
+
+\section{Evaluation of Metadata on Thesauri (SKOS)}
+
+In this section, the quality of the metadata on thesauri (SKOS) is evaluated by validating appropriate RDF constraints assigned to several RDF constraint types.
+First, we give an overview on the evaluated thesauri and finally we provide details about the evaluation.
 
@@
 
-\begin{itemize}
-  \item overview over SKOS data sets\footnote{\url{http://datahub.io/de/dataset?tags=format-skos}}
-	\item overview over thesauri\footnote{\url{http://datahub.io/de/dataset?tags=thesaurus}} (table \ref{tab:thesauri-overview})
-\end{itemize}
+There is a website giving an overview on available SKOS data sets\footnote{\url{http://datahub.io/de/dataset?tags=format-skos}}
+and another one giving an overview on available thesauri\footnote{\url{http://datahub.io/de/dataset?tags=thesaurus}}.
+Tables \ref{tab:thesauri-abbreviations} and \ref{tab:thesauri-sparql-endpoints} give an overview on the evaluated thesauri, their abbreviations, and publicly available SPARQL endpoints.
+Table \ref{tab:thesauri-overview} comprehends the number of triples, data sets, and instances of multiple vocabulary-specific classes.
 
@@
 
+In this sub-section, we give details about the evaluation in form of diverse tables containing the number of constraint violations per evaluated data set and constraint of particular constraint types.
+
 \begin{table}[H]
@@
 
-\section{Rectangular Data (PHDD)}
-
-\tb{ToDo}
-
-\subsection{Evaluation Results}
-
-\subsection{Data Sets Overview}
-
-\subsection{Detailed Evaluation}
-
-\section{Statistical Classifications (XKOS)}
-
-\tb{ToDo}
-
-\subsection{Evaluation Results}
+\section{Evaluation of Metadata on Statistical Classifications (XKOS)}
+
+As part of future work, the quality of metadata on statistical classifications (XKOS) data sets will be evaluated by validating appropriate RDF constraints assigned to several RDF constraint types.
 
@@
 		\emph{CJ} & \emph{Nomenclature des catégories juridiques}\tablefootnote{\url{http://rdf.insee.fr/codes/index.html}} \\
-		\emph{ISIC} & \emph{}\tablefootnote{\url{}} \\
-		\emph{ISCO} & \emph{}\tablefootnote{\url{}} \\
+		\emph{ISIC} & \\
+		\emph{ISCO} & \emph{International Standard Classification of Occupations} \\
 		\end{tabular}
@@
 
-\begin{itemize}
-	\item \emph{Nomenclature d'activités française (NAF)}: French classification expressed in XKOS. the French refinement of the NACE, because it has explanatory notes.
-	\item \emph{Nomenclature des Professions et Catégories Socioprofessionnelles (PCS)}: French classification expressed in XKOS.
-	\item \emph{Nomenclature des catégories juridiques (CJ)}: French classification expressed in XKOS.
-	\item \emph{ISIC}: has explanatory notes too. 
-	\item \emph{ISCO}
-\end{itemize}
-
-\begin{table}[H]
-    \begin{center}
-    \begin{tabular}{@{}lccccccccccc@{}}
-           & \multicolumn{6}{c}{\textbf{Counts}}
-    \\  \cmidrule{2-7}
-    \\       \textbf{Data Sets}
-           & \textbf{\rot{triples}}
-           & \textbf{\rot{}}
-           & \textbf{\rot{}}
-           & \textbf{\rot{}}
-           & \textbf{\rot{}}
-					 & \textbf{\rot{}}
-					 & \textbf{\rot{}}
-    \\ \midrule
-    \emph{NAF} &  &  &  &  &  & \\
-		\emph{PCS} &  &  &  &  &  & \\
-		\emph{CJ} &  &  &  &  &  & \\
-		\emph{ISIC} &  &  &  &  &  & \\
-		\emph{ISCO} &  &  &  &  &  & \\
-		\hline
-		\textbf{Total} & & & & & & \\
-    \bottomrule
-    \end{tabular}
-    \caption{Statistical Classifications Overview}
-		\label{tab:statistical-classifications-overview}
-    \end{center}
-\end{table}
-
-\subsection{Detailed Evaluation}
-
-\bibliography{../../literature/literature}{}
+\emph{Nomenclature d'activités française (NAF)} is the French refinement of the \emph{NACE} classification expressed in XKOS having explanatory notes.
+\emph{Nomenclature des Professions et Catégories Socioprofessionnelles (PCS)} and \emph{Nomenclature des catégories juridiques (CJ)} are French classifications expressed in XKOS.
+The statistical classification \emph{ISIC} has explanatory notes too.
+
+%\begin{table}[H]
+    %\begin{center}
+    %\begin{tabular}{@{}lccccccccccc@{}}
+           %& \multicolumn{6}{c}{\textbf{Counts}}
+    %\\  \cmidrule{2-7}
+    %\\       \textbf{Data Sets}
+           %& \textbf{\rot{triples}}
+           %& \textbf{\rot{}}
+           %& \textbf{\rot{}}
+           %& \textbf{\rot{}}
+           %& \textbf{\rot{}}
+					 %& \textbf{\rot{}}
+					 %& \textbf{\rot{}}
+    %\\ \midrule
+    %\emph{NAF} &  &  &  &  &  & \\
+		%\emph{PCS} &  &  &  &  &  & \\
+		%\emph{CJ} &  &  &  &  &  & \\
+		%\emph{ISIC} &  &  &  &  &  & \\
+		%\emph{ISCO} &  &  &  &  &  & \\
+		%\hline
+		%\textbf{Total} & & & & & & \\
+    %\bottomrule
+    %\end{tabular}
+    %\caption{Statistical Classifications Overview}
+		%\label{tab:statistical-classifications-overview}
+    %\end{center}
+%\end{table}
+
+\section{Conclusion}
+
+We identified and published by today 81 types of constraints that are required by various stakeholders for data applications.
+In close collaboration with several domain experts for the social, behavioral, and economic sciences (SBE), we formulated and implemented 115 constraints on three different vocabularies (DDI-RDF, QB, and SKOS) and classified them according to their severity level and  whether their type is expressible by different types of constraint languages - RDFS/OWL, high-level constraint languages, and SPARQL.
+Using these constraints, we evaluated  the data quality of 15,694 data sets (4.26 billion triples) of research data for the SBE sciences obtained from 33 SPARQL endpoints.
+
+\bibliography{../../../literature/literature}{}
 \bibliographystyle{plain}

### 2015-09-11 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
minor
Letzte Anmerkungen Kai

@@
 % 
-\author{\IEEEauthorblockN{Thomas Hartmann (formerly Bosch)\IEEEauthorrefmark{1},
+\author{\IEEEauthorblockN{Thomas Hartmann\IEEEauthorrefmark{1},
 Benjamin Zapilko\IEEEauthorrefmark{1},
@@
 Based on our work in the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group, we identified and published by today 81 types of constraints that are required by various stakeholders for data applications.
-In this paper, in collaboration with several domain experts we formulate 115 constraints on three different vocabularies (DDI-RDF, QB, and SKOS) and classify them according to (1) the severity of an occurring violation and (2) which types of constraint languages are able to express their type of constraint.
+In this paper, in collaboration with several domain experts we formulate 115 constraints on three different vocabularies (DDI-RDF, QB, and SKOS) and classify them according to (1) the severity of an occurring violation and (2) the complexity of the constraint expression in common constraint languages.
 We evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioral, and economic sciences obtained from 33 SPARQL endpoints.
-Based on the results, we formulate several hypotheses to direct the further development of constraint languages.
+Based on the results, we formulate several findings to direct the further development of constraint languages.
 \end{abstract}
@@
 We let the experts classify the constraints according to the severity of their violation.
-Furthermore, we classified each constraint type based on whether it is expressible by RDFS/OWL, common high-level constraint languages, or only by plain SPARQL (see Chapter \ref{classification}).
+Furthermore, we classified each constraint type based on whether it is expressible by RDFS/OWL, common high-level constraint languages, or only by plain SPARQL (see Chapter~\ref{classification}).
 
@@
 In XML, the definition of schemas containing constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
-With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration.
+With the rise of the Web of Data, data professionals and institutions are very interested in publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate discovery and reuse.
 Therefore, not only established vocabularies like SKOS are used;
@@
 
-The data most often used in research within SBE sciences is \emph{unit-record data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers such as hospital records, registers of births and deaths.
+The data most often used in research within SBE sciences is \emph{unit-record data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers such as hospital records or registers of births and deaths.
 A \emph{study} represents the process by which a data set was generated or collected.
@@
 Aggregated data, which answers particular research questions, is derived from unit-record data by statistics on groups or aggregates such as frequencies and arithmetic means.
-The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying unit-record data.
+The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses of the underlying unit-record data.
 For more detailed analyses, researchers refer to unit-record data including additional variables needed to answer subsequent research questions.
@@
 
-Within the working groups, we identified by today 81 requirements to formulate RDF constraints (e.g., \emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type.\footnote{Constraint types and constraints are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}
+Within the working groups, we identified by today 81 requirements to formulate RDF constraints (e.g., \emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type.\footnote{Constraint types are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}
 Within a technical report, we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages \cite{BoschNolleAcarEckert2015}.
@@
 It is our point that reasoning affects validation and that a proper definition of the reasoning to be applied is needed.} RDFS/OWL axioms are commonly found within formal specifications of vocabularies.
-We determined this set based on the evaluation of the three vocabularies we performed without reasoning.
 \emph{RDFS/OWL Based} constraints generally can be seen as a basic level of constraints ensuring that the data is consistent with the formally and explicitly specified intended semantics as well as the integrity of vocabularies' conceptual models about data.
@@
 %\ms{Study $\equiv$ $\exists$ product.LogicalDataSet} (DL), e.g., restricts studies to contain at least one data set which is expressible in OWL 2:
-Constraints of the type \emph{minimum qualified cardinality restrictions} (\emph{R-74}), e.g., guarantee that individuals of given classes are connected by particular properties to at least n different individuals/literals of certain classes or data ranges.
+Constraints of the type \emph{minimum qualified cardinality restrictions} (\emph{R-75}), e.g., guarantee that individuals of given classes are connected by particular properties to at least n different individuals/literals of certain classes or data ranges.
 For \emph{DDI-RDF}, a \emph{minimum qualified cardinality restriction} can be obtained from a respective OWL axiom which ensures that a \emph{disco:Questionnaire} has (\emph{disco:question}) at least one \emph{disco:Question}:
@@
 Constraints of this type restrict individuals of given classes to have properties defined within exactly one of multiple mutually exclusive property groups.
-\emph{skos:Concept}s, e.g., can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes), but not both:
+\emph{skos:Concept}s, e.g., can have either \emph{skos:definition} (when interpreted as theo\-reti\-cal concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes), but not both:\ke{Wo kommt das constraint her?
+In SKOS gilt das nicht generell.}
 %(\emph{error}).
@@
 
-\subsection{Examples}
+\subsection{Examples}\ke{die examples finde ich sehr schwer zu lesen, es fehlt auch eine einleitung aus der hervorgeht, wieso die beispiele hier eigentlich aufgeführt werden.}
 \label{vocabulary-constraint-types}
@@
 In this section, we describe our findings based on an automatic constraint checking of a large data set.
-Despite the large volume of the data set in general, we have to keep in mind that this study only uses data for three vocabularies.
+Despite the large volume of the data set in general, this study only uses data for three vocabularies.
 As described in Section~\ref{sbe-vocabularies}, for other vocabularies there is often not (yet) enough data openly available to draw general conclusions.
-The three vocabularies, however, are representative, cover different aspects of SBE data, and are also a mixture of widely adopted and accepted well-established vocabularies (QB, SKOS) and a vocabulary under development (DDI-RDF\footnote{Expected publication at the end of the year 2015}).
-Due to this limitation, we present several findings together with a rationale based on the results for the three vocabularies.
-If these findings hold generally is still to be determined, nevertheless they should provide valuable insights for future developments of constraint languages.
+The three vocabularies, however, are representative, cover different aspects of SBE data, and are also a mixture of widely adopted and accepted well-established vocabularies (QB, SKOS) and a vocabulary under development (DDI-RDF\footnote{Expected publication end of 2015.}).
+If our findings hold generally is still to be determined, nevertheless they provide valuable insights for future developments of constraint languages.
 
@@
 We ensured that the implementation of the constraints is equally distributed over the classes and vocabularies we have.
-We then evaluated the data quality of 15,694 data sets (4.26 billion triples) of SBE research data using these 115 constraints, obtained from 33 SPARQL endpoints.
+We then evaluated the data quality of 15,694 data sets (4.26 billion triples) of SBE research data using these 115 constraints, obtained from 33 SPARQL endpoints.\ke{Das ist eine Wiederholung, ggf.
+streichen, falls Platz knapp}
 
@@
 
-As the evaluation is based on three vocabularies, 
-we cannot make valid general statements for all vocabularies,
-but we can formulate several findings to direct the further development of constraint languages.
-As these findings cannot be proved yet, 
-they still have to be verified or falsified
-by evaluating the quality of data represented by further well-established and newly developed vocabularies.
+\ke{da kam noch mal der limitations disclaimer, ich denke, einmal reicht... habs auskommentiert}
+%As the evaluation is based on three vocabularies, 
+%we cannot make valid general statements for all vocabularies,
+%but we can formulate several findings to direct the further development of constraint languages.
+%As these findings cannot be proved yet, 
+%they still have to be verified or falsified
+%by evaluating the quality of data represented by further well-established and newly developed vocabularies.
 
@@
 %which is not the case or newly-developed vocabularies.
-\begin{hyp}
+\begin{hyp}\ke{das ist doch das gleiche wie 4, oder?}
 For well-established vocabularies, data quality is high as serious violations rarely appear. For newly developed vocabularies, however, data quality is worse as serious violations occur partially.   
@@
 
-Especially for newly developed vocabularies, constraint languages should be used to a larger extend to define appropriate constraints in order to detect and solve severe violations.
+Especially for newly developed vocabularies, constraint languages should be used to a larger extend to define appropriate constraints in order to detect and solve severe violations.\ke{aber das wird doch gemacht, halt mit RDFS und OWL, weswegen die etablierten ja besser sind.}
 %to reduce severe violations by checking and solving them.
@@
 This is a surprising finding as the violation of \emph{RDFS/OWL Based} constraints should be of higher severity than \emph{informational} constraints since \emph{RDFS/OWL Based} constraints are expected to be basic constraints as they are in many cases part of vocabularies' formal specifications.
+\ke{das letzte finding und die erläuterung finde ich konfus.
+violations gibts doch bei rdfs/owl hauptsächlich informational, weil die wirklich wichtigen eingehalten werden.
+sparql based kann man ja bis jetzt nicht anders formulieren, insofern ist zu erwarten, dass da auch warning constraints weniger eingehalten werden, wenn man welche auf warning level formuliert.
+Ist das nicht eh ein Artefakt basierend auf letztlich 1 oder 2 constraints die ihr formuliert habt?}
 %and (2)
@@
 constraints, which up to now can only be expressed by plain SPARQL, in an easy, concise, and intuitive way.
-Thereby, the more elaborate a vocabulary is, the more sophisticated and complex constraints are specified using SPARQL.}
+Thereby, the more elaborate a vocabulary is, the more sophisticated and complex constraints are specified using SPARQL.\ke{Nachsatz verstehe ich nicht...}}
 \item
@@
 We are actively involved in the further development and implementation of constraint languages and will use the results presented in the paper to set priorities on features where we expect the highest impact on the data quality of real-life data in the SBE domain.
-
+\ke{in die conclusion sollte noch rein, dass constraint languages per se funktionieren zur erhöhung der datenqualität und deswegen mit hochdruck an der weiterentwicklung gearbeitet werden muss.}
 % An example of a floating figure using the graphicx package.

### 2015-09-12 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
Bens Kommentare

@@
 \newcommand{\tb}[1]{\todo[size=\small, color=green!40]{\textbf{Thomas:} #1}}
-\newcommand{\bz}[1]{\todo[size=\small, color=blue!40]{\textbf{Erman:} #1}}
+\newcommand{\bz}[1]{\todo[size=\small, color=blue!40]{\textbf{Ben:} #1}}
 
@@
 \emph{skos:Concept}s, e.g., can have either \emph{skos:definition} (when interpreted as theo\-reti\-cal concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes), but not both:\ke{Wo kommt das constraint her?
-In SKOS gilt das nicht generell.}
+In SKOS gilt das nicht generell.}\bz{Wenn das Constraint keinen SKOS-Ursprung hat, sollten wir ein anderes Beispiel in dem Satz nennen.}
 %(\emph{error}).
@@
 %which is not the case or newly-developed vocabularies.
-\begin{hyp}\ke{das ist doch das gleiche wie 4, oder?}
+\begin{hyp}\ke{das ist doch das gleiche wie 4, oder?}\bz{Stimme Kai zu. Finding 4 und 6 koennte man zusammenfassen oder falls es doch Unterschiede gibt, muessen die staerker hervorgehoben werden.}
 For well-established vocabularies, data quality is high as serious violations rarely appear. For newly developed vocabularies, however, data quality is worse as serious violations occur partially.   
@@
 constraints, which up to now can only be expressed by plain SPARQL, in an easy, concise, and intuitive way.
-Thereby, the more elaborate a vocabulary is, the more sophisticated and complex constraints are specified using SPARQL.\ke{Nachsatz verstehe ich nicht...}}
+Thereby, the more elaborate a vocabulary is, the more sophisticated and complex constraints are specified using SPARQL.\ke{Nachsatz verstehe ich nicht...}\bz{Thomas, meinst du: the more elaborate a vocabulary is, the more sophisticated and complex constraints are necessary which can up to now only specified using SPARQL.}}
 \item

### 2015-09-12 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
findings

@@
 Constraints of this type restrict individuals of given classes to have properties defined within exactly one of multiple mutually exclusive property groups.
-\emph{skos:Concept}s, e.g., can have either \emph{skos:definition} (when interpreted as theo\-reti\-cal concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes), but not both:\ke{Wo kommt das constraint her?
-In SKOS gilt das nicht generell.}\bz{Wenn das Constraint keinen SKOS-Ursprung hat, sollten wir ein anderes Beispiel in dem Satz nennen.}
+Within the context of DDI-RDF, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theo\-reti\-cal concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes), but not both:
 %(\emph{error}).
@@
 
-\subsection{Examples}\ke{die examples finde ich sehr schwer zu lesen, es fehlt auch eine einleitung aus der hervorgeht, wieso die beispiele hier eigentlich aufgeführt werden.}
+\subsection{Examples}
+%\ke{die examples finde ich sehr schwer zu lesen, es fehlt auch eine einleitung aus der hervorgeht, wieso die beispiele hier eigentlich aufgeführt werden.}
 \label{vocabulary-constraint-types}
+
+To get an overview on the constraint types, we delineate concrete constraints on the three vocabularies for each set of constraint type and classify them according to their severity.
 
@@
 The three vocabularies, however, are representative, cover different aspects of SBE data, and are also a mixture of widely adopted and accepted well-established vocabularies (QB, SKOS) and a vocabulary under development (DDI-RDF\footnote{Expected publication end of 2015.}).
-If our findings hold generally is still to be determined, nevertheless they provide valuable insights for future developments of constraint languages.
+%If our findings hold generally is still to be determined, nevertheless they provide valuable insights for future developments of constraint languages.
+As the evaluation is based on three vocabularies, 
+we cannot make valid general statements for all vocabularies,
+but we can formulate several findings to direct the further development of constraint languages.
+As these findings cannot be proved yet, 
+they still have to be verified or falsified
+by evaluating the quality of data represented by further well-established and newly developed vocabularies.
 
@@
 We ensured that the implementation of the constraints is equally distributed over the classes and vocabularies we have.
-We then evaluated the data quality of 15,694 data sets (4.26 billion triples) of SBE research data using these 115 constraints, obtained from 33 SPARQL endpoints.\ke{Das ist eine Wiederholung, ggf.
-streichen, falls Platz knapp}
+We then evaluated the data quality of 15,694 data sets (4.26 billion triples) of SBE research data using these 115 constraints, obtained from 33 SPARQL endpoints.
+%\ke{Das ist eine Wiederholung, ggf. streichen, falls Platz knapp}
 
@@
 
-\ke{da kam noch mal der limitations disclaimer, ich denke, einmal reicht... habs auskommentiert}
+%\ke{da kam noch mal der limitations disclaimer, ich denke, einmal reicht... habs auskommentiert}
 %As the evaluation is based on three vocabularies, 
@@
 %which is not the case or newly-developed vocabularies.
-\begin{hyp}\ke{das ist doch das gleiche wie 4, oder?}\bz{Stimme Kai zu. Finding 4 und 6 koennte man zusammenfassen oder falls es doch Unterschiede gibt, muessen die staerker hervorgehoben werden.}
+\begin{hyp}
+%\ke{das ist doch das gleiche wie 4, oder?}\bz{Stimme Kai zu. Finding 4 und 6 koennte man zusammenfassen oder falls es doch Unterschiede gibt, muessen die staerker hervorgehoben werden.}
 For well-established vocabularies, data quality is high as serious violations rarely appear. For newly developed vocabularies, however, data quality is worse as serious violations occur partially.   
@@
 
-Especially for newly developed vocabularies, constraint languages should be used to a larger extend to define appropriate constraints in order to detect and solve severe violations.\ke{aber das wird doch gemacht, halt mit RDFS und OWL, weswegen die etablierten ja besser sind.}
+Especially for newly developed vocabularies, constraint languages should be used to a larger extend in addition to RDFS/OWL in order to define appropriate constraints to detect and solve severe violations.
+%\ke{aber das wird doch gemacht, halt mit RDFS und OWL, weswegen die etablierten ja besser sind.}
 %to reduce severe violations by checking and solving them.
@@
 %Thereby, it does not matter which language is used to formulate constraints.
-Violations caused by constraints expressed by RDFS/OWL or high-level constraint languages are of low severity, whereas the violation of constraints formulated by SPARQL is more serious.
-There is a significant demand for languages that support the expression of SPARQL Based constraints as 94\% of all violations are caused by these constraints whose severity level is warning.
 \end{hyp}
 
-SPARQL seems to be used to formulate constraints whose violation is of higher severity than the violation of constraints expressed by either RDFS/OWL or high-level constraint languages.
+The fact that regardless of the language 1/2 of all constraints are \emph{informational} indicates that the purpose of constraints for users is mostly just to point to desirable but not necessary data improvements in terms of syntax and semantics of vocabularies.
+
+\begin{hyp}
+Regardless of the type of the used language, there are only a few violations raised by important constraints which stands for good data quality in general.
+In contrast, constraints of low severity, expressed by RDFS/OWL or high-level constraint languages, are violated to a large extent (80\%), whereas more serious constraints, expressed by SPARQL, are violated to an even larger extend (94\%).
+%Violations caused by constraints expressed by RDFS/OWL or high-level constraint languages are of low severity (as the important constraints are satisfied), whereas the violation of constraints formulated by SPARQL is more serious.
+There is a significant demand for languages that support the expression of SPARQL Based constraints.
+\end{hyp}
+
+The reason why there is a significant demand for languages supporting \emph{SPARQL Based} constraints is that 94\% of all violations, which are caused by \emph{SPARQL Based} constraints, are also raised by \emph{warning} constraints.
+This means that data quality may be improved in case these \emph{warning} constraints are adequately tackled which is more likely when these constraints are expressible not only by SPARQL but also by high-level constraint languages enabling to formulate constraints more intuitively and concisely.
+
+%SPARQL seems to be used to formulate constraints whose violation is of higher severity than the violation of constraints expressed by either RDFS/OWL or high-level constraint languages.
 This is a surprising finding as the violation of \emph{RDFS/OWL Based} constraints should be of higher severity than \emph{informational} constraints since \emph{RDFS/OWL Based} constraints are expected to be basic constraints as they are in many cases part of vocabularies' formal specifications.
-\ke{das letzte finding und die erläuterung finde ich konfus.
-violations gibts doch bei rdfs/owl hauptsächlich informational, weil die wirklich wichtigen eingehalten werden.
-sparql based kann man ja bis jetzt nicht anders formulieren, insofern ist zu erwarten, dass da auch warning constraints weniger eingehalten werden, wenn man welche auf warning level formuliert.
-Ist das nicht eh ein Artefakt basierend auf letztlich 1 oder 2 constraints die ihr formuliert habt?}
+
+%\textcolor{red}{
+%das letzte finding und die erläuterung finde ich konfus.
+violations gibts doch bei rdfs/owl hauptsächlich informational, weil die% wirklich wichtigen eingehalten werden.
+sparql based kann man ja bis jetzt nicht anders formulieren, insofern ist zu erwarten, dass da% auch warning constraints weniger eingehalten werden, wenn man welche auf warning level formuliert.
+Ist das nicht eh ein Artefakt %basierend auf letztlich 1 oder 2 constraints die ihr formuliert habt?
+%}
+
 %and (2)

### 2015-09-12 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
findings

@@
 \item
-\emph{Data quality can be significantly improved when suitable constraint languages are developed which enable to define 
+\emph{Data quality can be significantly improved when suitable constraint languages are developed enabling to define 
 constraints, which up to now can only be expressed by plain SPARQL, in an easy, concise, and intuitive way.
-Thereby, the more elaborate a vocabulary is, the more sophisticated and complex constraints are specified using SPARQL.\ke{Nachsatz verstehe ich nicht...}\bz{Thomas, meinst du: the more elaborate a vocabulary is, the more sophisticated and complex constraints are necessary which can up to now only specified using SPARQL.}}
+Thereby, the more elaborate a vocabulary is, the more sophisticated and complex constraints are necessary which can up to now only be specified by SPARQL.}
 \item

### 2015-09-12 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
findings

@@
 We have been really impressed by the high quality of the QB and SKOS data.
-This is in contrast to the sometimes heard rumour that Linked Open Data lacks quality.
+This is in contrast to the sometimes heard rumor that Linked Open Data lacks quality.
 We are actively involved in the further development and implementation of constraint languages and will use the results presented in the paper to set priorities on features where we expect the highest impact on the data quality of real-life data in the SBE domain.
-\ke{in die conclusion sollte noch rein, dass constraint languages per se funktionieren zur erhöhung der datenqualität und deswegen mit hochdruck an der weiterentwicklung gearbeitet werden muss.}
+As the use of constraint languages per se enhances data quality, it must be continued working intensively on their further development.
+
+%\ke{in die conclusion sollte noch rein, dass constraint languages per se funktionieren zur erhöhung der datenqualität und deswegen mit hochdruck an der weiterentwicklung gearbeitet werden muss.}
 % An example of a floating figure using the graphicx package.

### 2015-09-12 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
findings

@@
 
-We identified and published by today 81 types of constraints  that are required by various stakeholders for data applications.
-In close collaboration with several domain experts for the social, behavioral, and economic sciences (SBE), we formulated 115 constraints on three different vocabularies (DDI-RDF, QB, and SKOS) and classified them according to their severity level and  whether their type is expressible by different types of constraint languages - RDFS/OWL, high-level constraint languages, and SPARQL.
+We published by today 81 constraint types that are required by various stakeholders for data applications.
+In close collaboration with several domain experts for the social, behavioral, and economic sciences (SBE), we formulated 115 constraints on three different vocabularies (DDI-RDF, QB, SKOS) and classified them according to their severity level and  whether their type is expressible by different types of constraint languages - RDFS/OWL, high-level constraint languages, and SPARQL.
 Using these constraints, we evaluated  the data quality of 15,694 data sets (4.26 billion triples) of research data for the SBE sciences obtained from 33 SPARQL endpoints.
@@
 \item
-\emph{The fact that only 1/5 of all violations result from RDFS/OWL Based constraints, even though 1/3 of all constraints are RDFS/OWL Based, indicates good data quality for all vocabularies with regard to their formal specifications.}
+\emph{As only 1/5 of all violations result from RDFS/OWL Based constraints, even though 1/3 of all constraints are RDFS/OWL Based, data quality is high for all vocabularies with regard to their formal specifications.}
 \item

### 2015-09-14 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
feedback Kai findings

@@
 an XML format to disseminate, manage,
-and reuse data collected and archived for research \cite{Vardigan2008}. 
+and reuse data collected and archived for research. 
+%\cite{Vardigan-2008}. 
 In XML, the definition of schemas containing constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
@@
 
-Note that there is a correlation between the severity of a constraint and the classification according to the expressivity of constraint languages of its type: \emph{RDFS/OWL Based} constraints are in many cases classified with an \emph{error} level as they typically represent basic and important constraints; there is a reason why they have been included in the vocabulary specification.
+Note that there is a correlation between the severity of a constraint and the classification according to the expressivity of constraint languages of its type: \emph{RDFS/OWL Based} constraints are in many cases classified with an \emph{error} level as they typically represent basic constraints; there is a reason why they have been included in the vocabulary specification.
 Although we provide default severity levels for each constraint, validation environments should enable users to adapt the severity levels of constraints according to their individual needs.
@@
 
-85\% of the QB constraints are \emph{error} constraints.
-More than 50\% of the DDI-RDF and SKOS constraints, however, are \emph{informational} constraints.
+We did not detect violations of \emph{error} constraints for well-established vocabularies, even though 85\% of the QB constraints are \emph{error} constraints. 
+%85\% of the QB constraints are \emph{error} constraints.
+More than 50\% of the DDI-RDF and SKOS constraints are \emph{informational} constraints.
 1/6 of the DDI-RDF violations are caused by \emph{error} constraints and
-almost all QB violations and 59\% of the SKOS violations are caused by \emph{warning} constraints.  
+almost all QB and 59\% of the SKOS violations are caused by \emph{warning} constraints. 
+%For well-established vocabularies, we detected no violations of \emph{error} constraints.  
 %Constraints are serious when they violate the integrity of vocabularies.
@@
 %which is not the case or newly-developed vocabularies.
+
 \begin{hyp}
 %\ke{das ist doch das gleiche wie 4, oder?}\bz{Stimme Kai zu. Finding 4 und 6 koennte man zusammenfassen oder falls es doch Unterschiede gibt, muessen die staerker hervorgehoben werden.}
-For well-established vocabularies, data quality is high as serious violations rarely appear. For newly developed vocabularies, however, data quality is worse as serious violations occur partially.   
+For well-established vocabularies, data quality is high as serious violations rarely appear (0.3\% for QB).
+For newly developed vocabularies, however, data quality is worse as serious violations occur partially (1/6 for DDI-RDF).
 \end{hyp}
@@
 
-The fact that regardless of the language 1/2 of all constraints are \emph{informational} indicates that the purpose of constraints for users is mostly just to point to desirable but not necessary data improvements in terms of syntax and semantics of vocabularies.
+The fact that regardless of the language 1/2 of all constraints are \emph{informational} 
+%indicates that the purpose of constraints for users is mostly just to point to desirable but not necessary data improvements in terms of syntax and semantics of vocabularies. 
+indicates the importance that constraint languages support
+constraints on several levels. Constraints are by far not only to
+prevent certain usages of a vocabulary, they are rather needed to
+provide better guidance for improved interoperability.
 
 \begin{hyp}
-Regardless of the type of the used language, there are only a few violations raised by important constraints which stands for good data quality in general.
+Regardless of the type of the used language, there are only a few violations raised by \emph{error} constraints which stands for good data quality in general.
 In contrast, constraints of low severity, expressed by RDFS/OWL or high-level constraint languages, are violated to a large extent (80\%), whereas more serious constraints, expressed by SPARQL, are violated to an even larger extend (94\%).
@@
 
-The reason why there is a significant demand for languages supporting \emph{SPARQL Based} constraints is that 94\% of all violations, which are caused by \emph{SPARQL Based} constraints, are also raised by \emph{warning} constraints.
+%The reason why there is a significant demand for languages supporting \emph{SPARQL Based} constraints is that 94\% of all violations, which are caused by \emph{SPARQL Based} constraints, are also raised by \emph{warning} constraints.
 This means that data quality may be improved in case these \emph{warning} constraints are adequately tackled which is more likely when these constraints are expressible not only by SPARQL but also by high-level constraint languages enabling to formulate constraints more intuitively and concisely.
+
+94\% of the violations of SPARQL-based constraints are warnings. This
+means that data quality could be improved significantly, if these
+constraints are met. This is more likely when these constraints
+are expressible not only by SPARQL but also by high-level
+constraint languages enabling to formulate constraints more
+intuitively and concisely.
 

### 2015-10-13 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
final submission

@@
 %RDFS, and OWL as we consider RDFS and OWL as constraint languages when assuming CWA/UNA semantics without reasoning. 
-There is a strong overlap between \emph{RDFS/OWL} and \emph{Constraint Language Based} constraint types as in many cases constraint types are expressible by both classical constraint languages and OWL.
+There is a strong overlap between \emph{RDFS/OWL} and \emph{Constraint Language Based} constraint types as in many cases constraint types are expressible by both classical constraint languages and RDFS/OWL.
 SPARQL, however, is considered as a low-level implementation language in this context.
@@
 Declarative languages may be placed on top of SPARQL when using it as an implementation language.
-For these \emph{Constraint Language Based} constraints, we expect a straight-forward support in future constraint languages.
+For these \emph{Constraint Language Based} constraint types, we expect a straight-forward support in future constraint languages.
 
@@
 
-To get an overview on the constraint types, we delineate concrete constraints on the three vocabularies for each set of constraint type and classify them according to their severity.
+To get an overview on the sets of constraint types, we delineate concrete constraints on the three vocabularies for each set of constraint type and classify them according to their severity.
 
@@
   &{\small\ms{Variable $\equiv$ $\exists$ concept.Concept,}} \\
-	&{\small\ms{Catalog $\sqsubseteq$ $\forall$ dataset.Dataset,}} \\
-  &{\small\ms{$\exists$ isStructuredBy.$\top$ $\sqsubseteq$ Table,}} \\
-	&{\small\ms{$\top$ $\sqsubseteq$ $\forall$ belongsTo.Concept}}
+	&{\small\ms{DataSet $\sqsubseteq$ $\forall$ structure.DataStructureDef,}} \\
+  &{\small\ms{$\exists$ hasTopConcept.$\top$ $\sqsubseteq$ ConceptScheme,}} \\
+	&{\small\ms{$\top$ $\sqsubseteq$ $\forall$ variable.Variable}}
 \}\\ 
@@
 %Only \emph{phdd:Tables}, e.g., can have \emph{\textcolor{red}{phdd}:isStructuredBy} relationships (\emph{error}) and \emph{\textcolor{red}{xkos}:belongsTo} relations can only point to \emph{skos:Concepts} (\emph{error}).
-Only \emph{skos:ConceptSchemes}, e.g., can have \emph{skos:hasTopConcept} relationships (\emph{error}) and \emph{disco:variable} relations can only point to \emph{disco:Variables} (\emph{error}).
+only \emph{skos:ConceptSchemes}, e.g., can have \emph{skos:hasTopConcept} relationships (\emph{error}) and \emph{disco:variable} relations can only point to \emph{disco:Variables} (\emph{error}).
 
@@
 It is useful to declare properties to be \emph{conditional} (\emph{R-71}), i.e., if particular properties exist (or do not exist), then other properties must also be present (or absent).
-To get an overview over a study either an abstract, a title, an alternative title, or links to external descriptions should be provided. 
+To get an overview on a study either an abstract, a title, an alternative title, or links to external descriptions should be provided. 
 If an abstract and an external description are absent, however,  
@@
 In case a variable is represented in form of a code list, codes may be associated with categories, i.e., human-readable labels (\emph{informational}).
-The variable \emph{Education at pre-school}, e.g., is represented as ordered code list without any categories.
+The variable \emph{Education at pre-school}, e.g., is represented as an ordered code list without any categories.
 
@@
 In this section, we describe our findings based on an automatic constraint checking of a large data set.
-Despite the large volume of the data set in general, this study only uses data for three vocabularies.
+Despite the large volume of the data sets in general, this study only uses data for three vocabularies.
 As described in Section~\ref{sbe-vocabularies}, for other vocabularies there is often not (yet) enough data openly available to draw general conclusions.
@@
 We published by today 81 constraint types that are required by various stakeholders for data applications.
-In close collaboration with several domain experts for the social, behavioral, and economic sciences (SBE), we formulated 115 constraints on three different vocabularies (DDI-RDF, QB, SKOS) and classified them according to their severity level and  whether their type is expressible by different types of constraint languages - RDFS/OWL, high-level constraint languages, and SPARQL.
+In close collaboration with several domain experts for the social, behavioral, and economic (SBE) sciences, we formulated 115 constraints on three different vocabularies (DDI-RDF, QB, SKOS) and classified them according to their severity level and  whether their type is expressible by different types of constraint languages - RDFS/OWL, high-level constraint languages, and SPARQL.
 Using these constraints, we evaluated  the data quality of 15,694 data sets (4.26 billion triples) of research data for the SBE sciences obtained from 33 SPARQL endpoints.

### 2015-10-13 paper/IEEE-ICSC-2016/technical-reports/IEEE-ICSC-2016-constraints.tex
findings
final submission

@@
 %
-\author{Thomas Bosch\inst{1} \and Benjamin Zapilko\inst{1} \and Joachim Wackerow\inst{1} \and Kai Eckert\inst{2}}
+\author{Thomas Hartmann\inst{1} \and Benjamin Zapilko\inst{1} \and Joachim Wackerow\inst{1} \and Kai Eckert\inst{2}}
 %
@@
 an XML format to disseminate, manage,
-and reuse data collected and archived for research \cite{Vardigan2008}. 
+and reuse data collected and archived for research \cite{Vardigan-2008}. 
 In XML, the definition of schemas containing constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
@@
 
-	\textcolor{blue}{
 	\item \textbf{{\em DISCO-C-LITERAL-RANGES-02:}}
@@
 	\end{itemize}
-	}
 

### 2015-10-13 paper/IEEE-ICSC-2016/technical-reports/IEEE-ICSC-2016-evaluation.tex
findings
final submission

@@
       \emph{Missy} & \url{http://svko-missy:8181/openrdf-workbench/repositories/native-java-store/summary} \\
+			             & \url{www.gesis.org/missy/sparql} \\
 			\emph{DwB} & \url{http://dwb-dev.nsd.uib.no/sparql} \\
@@
       \hline
-    \emph{TheSoz} & \emph{Thesaurus for the Social Sciences}\tablefootnote{\url{http://www.ecb.europa.eu/home/html/index.en.html}} \\
+    \emph{TheSoz} & \emph{Thesaurus for the Social Sciences}\tablefootnote{\url{http://www.gesis.org/en/services/research/thesauri-und-klassifikationen/social-science-thesaurus/}} \\
 	  \emph{STW} & \emph{Thesaurus for Economics}\tablefootnote{\url{http://zbw.eu/stw/versions/latest/about}} \\

### 2016-03-13 paper/IJSC-2016/IJSC-2016-comments.tex
IJSC-2016

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Trim Size: 9.75in x 6.5in
%% Text Area: 8in (include Runningheads) x 5in
%% ws-ijsc.tex     14-2-07
%% Tex file to use with ws-ijsc.cls written in Latex2E. 
%% The content, structure, format and layout of this style file is the 
%% property of World Scientific Publishing Co. Pte. Ltd. 
%% Copyright 1995, 2002 by World Scientific Publishing Co. 
%% All rights are reserved.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%

\documentclass{ws-ijsc}

\begin{document}

\markboth{Authors' Names}
{Instructions for Typing Manuscripts (Paper's Title)}

%%%%%%%%%%%%%%%%%%%%% Publisher's Area please ignore %%%%%%%%%%%%%%%
%
\catchline{}{}{}{}{}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Summary of the new added content as well as the differences between the journal version and the conference version}

\maketitle

\begin{abstract}

\end{abstract}

\section{Introduction}

\begin{itemlist}
 \item Minor changes
\end{itemlist}

\section{Common Vocabularies in the SBE Sciences}

\begin{itemlist}
 \item We give an in-depth description of common vocabularies in the SBE sciences and not just a too short overview on them.
 \item We describe a complete running example how SBE sciences data and metadata is represented in RDF.
 \item We introduce a representative RDF validation case study.
 \item We inserted a paragraph about Data Catalog Vocabulary (DCAT) which enables to represent data sets inside of data collections like portals, repositories, catalogs, and archives which serve as typical entry points when searching for data.
\end{itemlist}

\section{Related Work}

\begin{itemlist}
 \item No changes
\end{itemlist}

\section{Classification of Constraint Types and Constraints}

\begin{itemlist}
 \item Complete walk through and minor corrections
\end{itemlist}

\section{Implementation}

\begin{itemlist}
 \item We meticulously described how we implemented our validation environment which can directly be used to validate RDF data against constraints expressed in any RDF-based constraint language and extracted from or defined for any RDF vocabulary. 
\end{itemlist}

\section{Evaluation}

\begin{itemlist}
 \item Complete walk through and minor corrections
\end{itemlist}

\section{Conclusion and Future Work}

\begin{itemlist}
 \item One additional main finding
 \item 2 additional paragraphs
\end{itemlist}

\section{references}

\begin{itemlist}
 \item We included 20 new references of high-quality.
\end{itemlist}

\end{document}

### 2016-03-13 paper/IJSC-2016/IJSC-2016.tex
IJSC-2016

--- 2015-10-13 paper/IEEE-ICSC-2016/IEEE-ICSC-2016.tex
@@
-%% bare_conf.tex
-%% V1.3
-%% 2007/01/11
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Trim Size: 9.75in x 6.5in
+%% Text Area: 8in (include Runningheads) x 5in
+%% ws-ijsc.tex     14-2-07
+%% Tex file to use with ws-ijsc.cls written in Latex2E. 
+%% The content, structure, format and layout of this style file is the 
+%% property of World Scientific Publishing Co. Pte. Ltd. 
+%% Copyright 1995, 2002 by World Scientific Publishing Co. 
+%% All rights are reserved.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%
-%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
-%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. IEEE's font choices can trigger bugs that do  ***
-% *** not appear when using other class files.                            ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-% Note that the a4paper option is mainly intended so that authors in
-% countries using A4 can easily print to A4 and see how their papers will
-% look in print - the typesetting of the document will not typically be
-% affected with changes in paper size (but the bottom and side margins will).
-% Use the testflow package mentioned above to verify correct handling of
-% both paper sizes by the user's LaTeX system.
-%
-% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
-% should be used if it is desired that the figures are to be displayed in
-% draft mode.
-%
-\documentclass[conference]{IEEEtran}
-% Add the compsoc option for Computer Society conferences.
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[conference]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-%\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
-% not currently provide for hyperlinked citations.
-% The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at: 
-% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
-% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-%\usepackage[cmex10]{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics. If using
-% it, be sure to load this package with the cmex10 option to ensure that
-% only type 1 fonts will utilized at all point sizes. Without this option,
-% it is possible that some math symbols, particularly those within
-% footnotes, will be rendered in bitmap form which will result in a
-% document that can not be IEEE Xplore compliant!
-%
-% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
-% There is also a support site at:
-% http://algorithms.berlios.de/index.html
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/tools/
-
-%\usepackage{mdwmath}
-%\usepackage{mdwtab}
-% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
-% especially mdwmath.sty and mdwtab.sty which are used to format equations
-% and tables, respectively. The MDWtools set is already installed on most
-% LaTeX systems. The lastest version and documentation is available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-%\usepackage{eqparbox}
-% Also of notable interest is Scott Pakin's eqparbox package for creating
-% (automatically sized) equal width boxes - aka "natural width parboxes".
-% Available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/
-
-% *** SUBFIGURE PACKAGES ***
-%\usepackage[tight,footnotesize]{subfigure}
-% subfigure.sty was written by Steven Douglas Cochran. This package makes it
-% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
-% work, it is a good idea to load it with the tight package option to reduce
-% the amount of white space around the subfigures. subfigure.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at:
-% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
-% subfigure.sty has been superceeded by subfig.sty.
-
-%\usepackage[caption=false]{caption}
-%\usepackage[font=footnotesize]{subfig}
-% subfig.sty, also written by Steven Douglas Cochran, is the modern
-% replacement for subfigure.sty. However, subfig.sty requires and
-% automatically loads Axel Sommerfeldt's caption.sty which will override
-% IEEEtran.cls handling of captions and this will result in nonIEEE style
-% figure/table captions. To prevent this problem, be sure and preload
-% caption.sty with its "caption=false" package option. This is will preserve
-% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
-% (recommended due to many improvements over 1.2) of subfig.sty supports
-% the caption=false option directly:
-%\usepackage[caption=false,font=footnotesize]{subfig}
-%
-% The latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
-% The latest version and documentation of caption.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure. The latest version and documentation can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/base/
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
-% Documentation is contained in the stfloats.sty comments as well as in the
-% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
-% does not allow \baselineskip to stretch. Authors submitting work to the
-% IEEE should note that IEEE rarely uses double column equations and
-% that authors should try to avoid such use. Do not be tempted to use the
-% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
-% not format its papers in such ways.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
-% Read the url.sty source comments for usage information. Basically,
-% \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
+
+\documentclass{ws-ijsc}
 
@@
 \begin{document}
-%
-% paper title
-% can use linebreaks \\ within to get better formatting as desired
-%\title{Aspects of RDF Data Constraints in the Social, behavioral, and Economic Sciences}
-\title{Validating RDF Data Quality using Constraints to Direct the Development of Constraint Languages}
-
-% author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
-%\author{\IEEEauthorblockN{Thomas Bosch}
-%\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
-%Georgia Institute of Technology\\
-%Atlanta, Georgia 30332--0250\\
-%Email: http://www.michaelshell.org/contact.html}
-%\and
-%\IEEEauthorblockN{Homer Simpson}
-%\IEEEauthorblockA{Twentieth Century Fox\\
-%Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\and
-%\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
-%\IEEEauthorblockA{Starfleet Academy\\
-%San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212\\
-%Fax: (888) 555--1212}}
-
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
-
-% for over three affiliations, or if they all won't fit within the width
-% of the page, use this alternative format:
-% 
-\author{\IEEEauthorblockN{Thomas Hartmann\IEEEauthorrefmark{1},
-Benjamin Zapilko\IEEEauthorrefmark{1},
-Joachim Wackerow\IEEEauthorrefmark{1}, 
-Kai Eckert\IEEEauthorrefmark{2}} %and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-\IEEEauthorblockA{\IEEEauthorrefmark{1}GESIS - Leibniz Institute for the Social Sciences, Mannheim, Germany\\
-Email: \{firstname.lastname\}@gesis.org}
-\IEEEauthorblockA{\IEEEauthorrefmark{2}Stuttgart Media University, Stuttgart, Germany\\
-Email: eckert@hdm-stuttgart.de}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
+
+\markboth{Thomas Hartmann, Benjamin Zapilko, Joachim Wackerow, Kai Eckert}
+{Directing the Development of Constraint Languages}
+
+%%%%%%%%%%%%%%%%%%%%% Publisher's Area please ignore %%%%%%%%%%%%%%%
+%
+\catchline{}{}{}{}{}
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\title{DIRECTING THE DEVELOPMENT OF CONSTRAINT LANGUAGES BY CHECKING CONSTRAINTS ON RDF DATA}
+
+\author{THOMAS HARTMANN}
+
+\address{Monitoring Society and Social Change, GESIS - Leibniz Institute for the Social Sciences, \\ Square B2 1,
+Mannheim, 68159, Germany\,\\
+\email{thomas.hartmann@gesis.org}
+\http{www.gesis.org}
+}
+
+\author{BENJAMIN ZAPILKO}
+
+\address{Knowledge Technologies for the Social Sciences, GESIS - Leibniz Institute for the Social Sciences, Unter Sachsenhausen 6-8\\
+Cologne, 50667, Germany\,\\
+\email{benjamin.zapilko@gesis.org}
+}
+
+\author{JOACHIM WACKEROW}
+
+\address{Monitoring Society and Social Change, GESIS - Leibniz Institute for the Social Sciences, \\ Square B2 1,
+Mannheim, 68159, Germany\,\\
+\email{joachim.wackerow@gesis.org}
+}
+
+\author{KAI ECKERT}
+
+\address{WISS Research Group, Faculty of Information and Communication, Stuttgart Media University, \\ Nobelstraße 10,
+Stuttgart, 70569, Germany\,\\
+\email{eckert@hdm-stuttgart.de}
+}
+
 \maketitle
 
+\begin{history}
+\received{(Day Month Year)}
+\revised{(Day Month Year)}
+\accepted{(Day Month Year)}
+%\comby{(xxxxxxxxxx)}
+\end{history}
+
 \begin{abstract}
-%\boldmath
 For research institutes, data libraries, and data archives,
-RDF data validation according to predefined constraints is a much sought-after feature, 
+validating RDF data according to predefined constraints is a much sought-after feature, 
 particularly as this is taken for granted in the XML world.
-Based on our work in the DCMI RDF Application Profiles Task Group and in cooperation with the W3C Data Shapes Working Group, we identified and published by today 81 types of constraints that are required by various stakeholders for data applications.
-In this paper, in collaboration with several domain experts we formulate 115 constraints on three different vocabularies (DDI-RDF, QB, and SKOS) and classify them according to (1) the severity of an occurring violation and (2) the complexity of the constraint expression in common constraint languages.
-We evaluate the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioral, and economic sciences obtained from 33 SPARQL endpoints.
-Based on the results, we formulate several findings to direct the further development of constraint languages.
+Based on our work in two international working groups on RDF validation and jointly identified requirements to formulate constraints and validate RDF data, we have published 81 types of constraints that are required by various stakeholders for data applications.
+
+In this paper, we evaluate the usability of identified constraint types for assessing RDF data quality by (1) collecting and classifying 115 constraints on vocabularies commonly used in the social, behavioral, and economic sciences, either from the vocabularies themselves or from domain experts, and (2) validating 15,694 data sets (4.26 billion triples) of research data against these constraints.
+We classify each constraint according to (1) the severity of occurring violations and (2) based on which types of constraint languages are able to express its constraint type.
+Based on the large-scale evaluation, we formulate several findings to direct the further development of constraint languages.
 \end{abstract}
-% IEEEtran.cls defaults to using nonbold math in the Abstract.
-% This preserves the distinction between vectors and scalars. However,
-% if the conference you are submitting to favors bold math in the abstract,
-% then you can use LaTeX's standard command \boldmath at the very start
-% of the abstract to achieve this. Many IEEE journals/conferences frown on
-% math in the abstract anyway.
-
-% no keywords
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
+
+\keywords{RDF Data Validation; RDF Data Quality; Constraint Languages; Semantic Web; Linked Data; RDF.}
 
@@
 For constraint formulation and RDF data validation, several languages exist or are currently developed.
-\emph{Shape Expressions (ShEx)}, \emph{Resource Shapes (ReSh)}, \emph{Description Set Profiles (DSP)}, \emph{OWL 2}, the \emph{SPARQL Inferencing Notation (SPIN)}, and \emph{SPARQL} are the six most promising and widely used constraint languages.
-OWL 2 is used as a constraint language under the closed-world and unique name assumptions.
-The W3C currently develops \emph{SHACL}, an RDF vocabulary for describing RDF graph structures.
+\emph{Shape Expressions (ShEx)}, \emph{Resource Shapes (ReSh)}, \emph{Description Set Profiles (DSP)}, the \emph{Web Ontology Language (OWL)}, the \emph{SPARQL Inferencing Notation (SPIN)}, and the \emph{SPARQL Query Language for RDF} are the six most promising and widely used constraint languages.
+OWL is used as a constraint language under the closed-world and unique name assumptions.
 With its direct support of validation via SPARQL, SPIN is very popular and certainly plays an important role for future developments in this field.
 It is particularly interesting as a means to validate arbitrary constraint languages by mapping them to SPARQL \cite{BoschEckert2014-2}.
+In addition, the W3C currently develops the \emph{Shapes Constraint Language (SHACL)}, an RDF vocabulary for describing RDF graph structures.
 Yet, there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners.
-Further research and development therefore is needed.
-
-In 2013, the W3C organized the RDF Validation Workshop,\footnote{\url{http://www.w3.org/2012/12/rdf-val/}} 
+This is the reason why further research on RDF validation and the development of constraint languages is needed.
+
+In 2013, the W3C organized the RDF Validation Workshop,
 where experts from industry, government, and academia discussed first use cases for constraint formulation and RDF data validation.
 In 2014, two working groups on RDF validation have been established to develop a language to express constraints on RDF data: 
-the \emph{W3C RDF Data Shapes Working Group}\footnote{\url{http://www.w3.org/2014/rds/charter}} (33 participants of 19 organizations) and the \emph{DCMI RDF Application Profiles Task Group}\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}} (29 people of 22 organizations) which among others bundles the requirements of data institutions of the cultural heritage sector and the \emph{social, behavioral, and economic (SBE)} sciences and represents them in the W3C group.
-
-Within the DCMI task group, a collaboratively curated database of RDF validation requirements\footnote{Online available at: \url{http://purl.org/net/rdf-validation}} has been created which contains the findings of the working groups based on various case studies provided by data institutions \cite{BoschEckert2014}.
-It is publicly available and open for further contributions.
-The database connects requirements to use cases, case studies, and implementations and forms the basis of this paper. 
-We distinguish 81 requirements to formulate constraints on RDF data; 
-each of them corresponding to a constraint type.
-
-In this paper, we collected constraints for commonly used vocabularies in the SBE domain (see Section \ref{sbe-vocabularies}), either from the vocabularies themselves or from domain and data experts, in order to gain a better understanding about the role of certain requirements for data quality and to direct the further development of constraint languages.
-All in all, this lead to 115 constraints on three vocabularies.
+the \emph{W3C RDF Data Shapes Working Group} and the \emph{DCMI RDF Application Profiles Task Group} which among others bundles the requirements of data institutions of the cultural heritage sector and the \emph{social, behavioral, and economic (SBE)} sciences and represents them in the W3C working group.
+
+Within the DCMI working group, a collaboratively curated database of RDF validation requirements, online available at \url{http://purl.org/net/rdf-validation}, has been created which contains the findings of the working groups based on various case studies provided by various data institutions \cite{BoschEckert2014}.
+The database connects requirements to use cases, case studies, and solutions and forms the basis of this paper. 
+Based on our work in these working groups and jointly identified requirements to formulate constraints and validate RDF data, we have published 81 types of constraints; each of them corresponding to a requirement in the database.
+
+In this paper, we collected 115 constraints for three vocabularies commonly used in the SBE domain (see Sec.
+\ref{sbe-vocabularies}), either from the vocabularies themselves or from several domain and data experts, in order to gain a better understanding about the role of certain constraint types for assessing data quality.
 We let the experts classify the constraints according to the severity of their violation.
-Furthermore, we classified each constraint type based on whether it is expressible by RDFS/OWL, common high-level constraint languages, or only by plain SPARQL (see Chapter~\ref{classification}).
+Furthermore, we classified each constraint type based on whether it is expressible by RDFS/OWL, common high-level constraint languages, or only by plain SPARQL (see Sec.~\ref{classification}).
 
 As we do not want to base our conclusions on the evaluation of vocabularies and constraint definitions alone, we conducted a large-scale experiment.
-For all these 115 constraints, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of SBE research data on three common vocabularies in SBE sciences (DDI-RDF, QB, SKOS) obtained from 33 SPARQL endpoints.
+For all these 115 constraints on the vocabularies DDI-RDF, QB, and SKOS, we evaluated the data quality of 15,694 data sets (4.26 billion triples) of SBE research data, obtained from 33 SPARQL endpoints.
 %evaluated the data quality of 15,694 data sets (4.26 billion triples) of research data for the social, behavioral, and economic (SBE) sciences obtained from 33 SPARQL endpoints.
@@
 these findings still have to be verified or falsified
-by evaluating the quality of data represented by more than three vocabularies (Section \ref{evaluation}).
+by evaluating the quality of data represented by more than three vocabularies (see Sec. \ref{evaluation}).
 %The \textbf{contribution} of this paper is the development of a system 
@@
 
+In Sec.
+\ref{implementation}, we delineate how we implemented our validation environment which can directly be used to validate RDF data against constraints expressed in any RDF-based constraint language and extracted from or defined for any RDF vocabulary.
+
 In this paper, we discuss constraints on RDF data in general.
-Note that the data represented in RDF can be data in the sense of SBE sciences, but also metadata about published or unpublished data.
+Note that the data represented in RDF can be data in the sense of the SBE sciences, but also metadata about published or unpublished data.
 We generally refer to both simply as RDF data and only distinguish between data and metadata in the data set descriptions.
@@
 %\label{running-example}
-\section{Common Vocabularies in SBE Sciences}
+\section{Common Vocabularies in the SBE Sciences}
 \label{sbe-vocabularies}
 
-We took all well-established and newly developed SBE vocabularies into account and defined constraints for three vocabularies commonly used in the SBE sciences which are briefly introduced in the following.
-We analyzed actual data according to constraint violations, as for these vocabularies large data sets are already published.
-
-SBE sciences require high-quality data for their empirical research. For more than a decade, members of the SBE community have been developing and using a
-metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)}, \footnote{\url{http://www.ddialliance.org/Specification/}}
-an XML format to disseminate, manage,
-and reuse data collected and archived for research. 
-%\cite{Vardigan-2008}. 
-In XML, the definition of schemas containing constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
-With the rise of the Web of Data, data professionals and institutions are very interested in publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate discovery and reuse.
-Therefore, not only established vocabularies like SKOS are used;
-recently, members of the SBE and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.
-
-The data most often used in research within SBE sciences is \emph{unit-record data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers such as hospital records or registers of births and deaths.
+We took all well-established and newly developed SBE vocabularies into account and defined constraints for three vocabularies commonly used in the SBE sciences.
+We analyzed actual data according to constraint violations, as for these vocabularies large data sets have already been published.
+
+%-----
+%
+%The data most often used in research within SBE sciences is \emph{unit-record data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers such as hospital records or registers of births and deaths.
 A \emph{study} represents the process by which a data set was generated or collected.
@@
 For more detailed analyses, researchers refer to unit-record data including additional variables needed to answer subsequent research questions.
-
+%
+%\emph{Formal childcare} is an example of an aggregated variable which captures the measured availability of childcare services in percent over the population in European Union member states by 
+%the dimensions \emph{year}, \emph{duration}, \emph{age} of the child, and \emph{country}.
+%Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
+%The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger} or by a code list of age clusters (e.g., '0 to 10' and '11 to 20'). 
+%The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e., multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}.
+%%QB represents metadata on multi-dimensional aggregate data in two files: a \emph{qb:DataSet} and a \emph{qb:DataStructureDefinition}.
+%A \emph{qb:DataStructureDefinition} contains metadata of the data collection.
+%The variable \emph{formal childcare} is modeled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
+%\emph{Year}, \emph{duration}, \emph{age}, and \emph{country} are \emph{qb:dimensions}.
+%Data values, i.e., the availability of childcare services in percent over the population, are collected in a \emph{qb:DataSet}. 
+%Each data value is represented inside a \emph{qb:Observation} which contains values for each dimension. 
+%%(e.g., the year in which \emph{formal childcare} has been determined).
+%%\ke{Wieso springt das von einer sehr knappen Einführung direkt zu konkreten (beliebigen?) Variablen?
+Ich möchte wissen, wofür QB benutzt wird und gerne ein konkretes %Beispiel sehen, um mir einen Data Cube vorstellen zu können.}\tb{hmm, ich halte das beispiel für ein knappes und verständliches beipsiel wie eine tabelle in qb dargestellt wird / es ist auch der link enthalten zu der tabelle von eurostat}
+%
+%For more detailed analyses we refer to the underlying unit-record data.
+The aggregated variable \emph{formal childcare} is calculated on the basis of six unit-record variables (i.a., \emph{Education at pre-school}) for which detailed metadata is given (i.a., code lists) enabling researchers to replicate the results shown in aggregated data tables.
+%\emph{DDI-RDF} is used to represent metadata on unit-record data in RDF.
+%%The series (\emph{DDI-RDF:StudyGroup}) \emph{EU-SILC} contains one study (\emph{DDI-RDF:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
+%%\emph{dcterms:spatial} points to the countries for which the data has been collected.
+%The study (\emph{disco:Study}) for which the unit-record data has been collected 
+%%\emph{EU-SILC 2011} 
+%contains eight data sets (\emph{disco:LogicalDataSet})
+%including variables (\emph{disco:Variable}) like the six ones needed to calculate the variable \emph{formal childcare}.
+%%Metadata on unit-record data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
+%%One common research question is ,e.g., the comparison of variables like 
+%%\emph{formal childcare} between countries, for which the variable is collected within the context of an individual study, and other European or non European countries (e.g. OSCE).
+%
+%The \emph{Simple Knowledge Organization System (SKOS)} is reused to a large extend to build SBE vocabularies.
+%The codes of the variable \emph{Education at pre-school} are modeled as \emph{skos:Concepts} and 
+%a \emph{skos:OrderedCollection} organizes them in a particular order within a \emph{skos:memberList}.
+%A variable may be associated with a theoretical concept (\emph{skos:Concept}) and \emph{skos:narrower} builds the hierarchy of theoretical concepts within a \emph{skos:ConceptScheme} of a study.
+%The variable \emph{Education at pre-school} is assigned to the theoretical concept \emph{Child Care} which is a narrower concept of the top concept \emph{Education}.
+%Controlled vocabularies (\emph{skos:ConceptScheme}), serving as extension and reuse mechanism,
+%organize types (\emph{skos:Concept}) of descriptive statistics (\emph{disco:SummaryStatistics}) like minimum, maximum, and arithmetic mean.
+
+The data most often used in research within SBE sciences is \emph{unit-record data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers such as hospital records, registers of births and deaths.
+A \emph{study} represents the process by which a data set was generated or collected.
+The range of unit-record data is very broad - including census, education, and health data and business, social, and labor force surveys.
+This type of research data is held within data archives or data libraries after it has been collected, so that it may be reused by future researchers.
+
+\subsection{Vocabularies for representing multi-dimensional aggregated data and its metadata}
+
+By its nature, unit-record data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 
+Researchers typically represent their results as aggregated data in form of multi-dimensional tables with only a few columns, so-called \emph{variables} such as \emph{sex} or \emph{age}.
+Aggregated data, which answers particular research questions, is derived from unit-record data by statistics on groups or aggregates such as frequencies and arithmetic means.
+The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying unit-record data.
+Aggregated data is published in form of CSV files,
+allowing to perform calculations on the data.
+
+For more detailed analyses, researchers refer to unit-record data including additional variables needed to answer subsequent research questions
+like the comparison of studies between countries.
+\emph{Eurostat}, the statistical office of the European Union, provides research findings in form of aggregated data (downloadable as CSV files) and its metadata on European level that enable comparisons between countries.
 \emph{Formal childcare} is an example of an aggregated variable which captures the measured availability of childcare services in percent over the population in European Union member states by 
@@
 The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger} or by a code list of age clusters (e.g., '0 to 10' and '11 to 20').
-The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e., multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}.
+
+A representative RDF validation case study within the SBE sciences is to ensure correctness when comparing variables between data collections of different countries.
+Several vocabulary-specific constraints on RDF data are checked for each data collection
+in order to determine if variables measuring \emph{age} 
+- collected for different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
+are comparable:
+(1) variable definitions must be available, 
+(2) for each code a human-readable label has to be specified,
+(3) code lists must be structured properly, and
+(4) code lists must either be identical or at least similar.
+If a researcher only wants to get a first overview on the comparability of variables (use case 1), 
+covering the first three constraints may be sufficient,
+i.e., the violation of the first three constraints is more serious than the violation of the last constraint.
+If the intention of the researcher is to perform more sophisticated comparisons (use case 2), however, the user may raise the severity level of the last constraint.
+
+The \emph{RDF Data Cube Vocabulary (QB)} \cite{CyganiakReynolds2014} is a W3C recommendation for representing \emph{data cubes}, i.e., multi-dimensional aggregated data and its metadata, in RDF \cite{Cyganiak2010}.
 %QB represents metadata on multi-dimensional aggregate data in two files: a \emph{qb:DataSet} and a \emph{qb:DataStructureDefinition}.
-A \emph{qb:DataStructureDefinition} contains metadata of the data collection.
+A \emph{qb:DataStructureDefinition} contains metadata on the data collection.
 The variable \emph{formal childcare} is modeled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
@@
 Data values, i.e., the availability of childcare services in percent over the population, are collected in a \emph{qb:DataSet}. 
-Each data value is represented inside a \emph{qb:Observation} which contains values for each dimension. 
-%(e.g., the year in which \emph{formal childcare} has been determined).
-%\ke{Wieso springt das von einer sehr knappen Einführung direkt zu konkreten (beliebigen?) Variablen?
-Ich möchte wissen, wofür QB benutzt wird und gerne ein konkretes %Beispiel sehen, um mir einen Data Cube vorstellen zu können.}\tb{hmm, ich halte das beispiel für ein knappes und verständliches beipsiel wie eine tabelle in qb dargestellt wird / es ist auch der link enthalten zu der tabelle von eurostat}
-
-For more detailed analyses we refer to the underlying unit-record data.
-The aggregated variable \emph{formal childcare} is calculated on the basis of six unit-record variables (i.a., \emph{Education at pre-school}) for which detailed metadata is given (i.a., code lists) enabling researchers to replicate the results shown in aggregated data tables.
-\emph{DDI-RDF} is used to represent metadata on unit-record data in RDF.
-%The series (\emph{DDI-RDF:StudyGroup}) \emph{EU-SILC} contains one study (\emph{DDI-RDF:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
-%\emph{dcterms:spatial} points to the countries for which the data has been collected.
-The study (\emph{disco:Study}) for which the unit-record data has been collected 
-%\emph{EU-SILC 2011} 
-contains eight data sets (\emph{disco:LogicalDataSet})
-including variables (\emph{disco:Variable}) like the six ones needed to calculate the variable \emph{formal childcare}.
-%Metadata on unit-record data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
-%One common research question is ,e.g., the comparison of variables like 
-%\emph{formal childcare} between countries, for which the variable is collected within the context of an individual study, and other European or non European countries (e.g. OSCE).
-
-The \emph{Simple Knowledge Organization System (SKOS)} is reused to a large extend to build SBE vocabularies.
-The codes of the variable \emph{Education at pre-school} are modeled as \emph{skos:Concepts} and 
-a \emph{skos:OrderedCollection} organizes them in a particular order within a \emph{skos:memberList}.
-A variable may be associated with a theoretical concept (\emph{skos:Concept}) and \emph{skos:narrower} builds the hierarchy of theoretical concepts within a \emph{skos:ConceptScheme} of a study.
-The variable \emph{Education at pre-school} is assigned to the theoretical concept \emph{Child Care} which is a narrower concept of the top concept \emph{Education}.
-Controlled vocabularies (\emph{skos:ConceptScheme}), serving as extension and reuse mechanism,
-organize types (\emph{skos:Concept}) of descriptive statistics (\emph{disco:SummaryStatistics}) like minimum, maximum, and arithmetic mean.
-
-%% ---------------
-%% Backup of 'Common Vocabularies in SBE Sciences'
-%
-%
-%\section{Common Vocabularies in SBE Sciences}
-%\label{rdf-representation}
-%
-%SBE sciences require high-quality data for their empirical research. For more than a decade, members of the SBE community have been developing and using a
-%metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)},
-%an XML format to disseminate, manage,
-%and reuse data collected and archived for research \cite{Vardigan2008}. 
-%In XML, the definition of schemas containing data constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
-%With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration.
-Therefore, not only established vocabularies like SKOS are used;
-%recently, members of the SBE and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.
-%
-%The data most often used in research within SBE sciences is \emph{unit-record data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers
-%such as hospital records, registers of births and deaths. 
-%The range of unit-record data is very broad - 
-%including census, education, health data and business, social, and labor force surveys.  
-%This type of research data is
-%held within data archives or data libraries after it has been collected, so that it may be
-%reused by future researchers. 
-%
-%By its nature, unit-record data is highly confidential and access is often only permitted for qualified researchers who must apply for access. 
-%Researchers typically represent their results as aggregated data in form of multi-dimensional tables with only a few columns; so-called \emph{variables} such as \emph{sex} or \emph{age}.
-%Aggregated data, which answers particular research questions, is derived from unit-record data by statistics on groups or aggregates such as frequencies and arithmetic means.
-%The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying unit-record data.
-%Aggregated data is published in form of CSV files,
-%allowing to perform calculations on the data.
-%
-%For more detailed analyses, researchers refer to unit-record data including additional variables needed to answer subsequent research questions
-%like the comparison of studies between countries.
-%A \emph{study} represents the process by which a data set was generated or collected.
-%Eurostat\footnote{\url{http://ec.europa.eu/eurostat}}, the statistical office of the European Union, provides research findings in form of aggregated data (downloadable as CSV files) and its metadata at European level that enable comparisons between countries.
-%The variable \emph{formal childcare}\footnote{Aggregated data and its metadata is available at: \url{http://ec.europa.eu/eurostat/web/products-datasets/-/ilc_caindformal}} %(in contrast to childcare at home)
-%captures the measured availability of childcare services in percent over the population in European Union member states by 
-%the variables \emph{year}, \emph{duration} (in hours per week), \emph{age} of the child, and \emph{country}.
-%Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
-%The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger} or by a code list of age clusters (e.g., '0 to 10' and '11 to 20'). 
-%
-%A very important and representative RDF validation case study within SBE sciences is the comparison of variables between data collections of different countries.
-%Several vocabulary-specific constraints on RDF data are checked for each data collection
-%to determine if variables measuring \emph{age} 
-%- collected for different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
-%are comparable:
-%(1) variable definitions must be available, 
-%(2) for each code a human-readable label has to be specified,
-%(3) code lists must be structured properly, and
-%(4) code lists must either be identical or at least similar.
-%If a researcher only wants to get a first overview over the comparability of variables (use case 1), 
-%covering the first three constraints may be sufficient,
-%i.e., the violation of the first three constraints is more serious than the violation of the last constraint.
-%If the intention of the researcher is to perform more sophisticated comparisons (use case 2), however, the user may raise the severity level of the last constraint.
-%
-%We took all well-established and newly developed SBE vocabularies into account and defined constraints for six vocabularies commonly used in or developed for the SBE sciences which are briefly introduced in the following.
-%For three of them, we analyzed actual data according to constraint violations, as for these vocabularies large data sets are already published.
-%
-%The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e.
-multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}.
-%A \emph{qb:DataStructureDefinition} contains metadata of the data collection.
-%The variable \emph{formal childcare}, e.g., is modeled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
-%The variables \emph{year}, \emph{duration}, \emph{age}, and \emph{country} are \emph{qb:dimensions}.
-%Data values, i.e., the availability of childcare services in percent over the population, are collected in a \emph{qb:DataSet}. 
-%Each data value is represented inside a \emph{qb:Observation} which contains values for each dimension\footnote{The complete running example in RDF is available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/data/running-example}}.
-%
-%\emph{Physical Data Description (PHDD)}\footnote{\url{https://github.com/linked-statistics/physical-data-description}} is a vocabulary to represent data in tabular format in RDF enabling further aggregations and calculations.
-%The data could be either represented in records with character-separated values (CSV) or fixed length. 
-%
-%For more detailed analyses we refer to the unit-record data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}}.
-%Where data collection is cyclic, data sets may be released as \emph{series}, 
-%where each cycle produces one or more data sets. 
-%The aggregated variable \emph{formal childcare} is calculated on the basis of six unit-record variables 
-%(e.g., \emph{Education at pre-school})
-%for which detailed metadata is given 
-%(e.g., code lists)
-%enabling researchers to replicate the results shown in aggregated data tables.
-%The \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)} is a vocabulary to represent metadata on unit-record data in RDF.
-%The series (\emph{DDI-RDF:StudyGroup}) \emph{EU-SILC} contains one study (\emph{DDI-RDF:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
-%\emph{dcterms:spatial} points to the countries for which the data has been collected.
-%The study \emph{EU-SILC 2011} contains eight unit-record data sets (\emph{DDI-RDF:LogicalDataSet})
-%including unit-record variables (\emph{DDI-RDF:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
-%
-%The \emph{Simple Knowledge Organization System (SKOS)} is reused multiple times to build SBE vocabularies.
-%The codes of the variable \emph{Education at pre-school} (number of education hours per week) are modeled as \emph{skos:Concepts} and 
-%a \emph{skos:OrderedCollection} organizes them in a particular order within a \emph{skos:member} \emph{List}.
-%A variable may be associated with a theoretical concept (\emph{skos:Concept}). 
-%\emph{skos:narrower} builds the hierarchy of theoretical concepts within a \emph{skos:Concept} \emph{Scheme} of a series.
-%The variable \emph{Education at pre-school} is assigned to the theoretical concept \emph{Child Care} which is the narrower concept of \emph{Education} - one of the top concepts of the series \emph{EU-SILC}.
-%Controlled vocabularies (\emph{skos:ConceptScheme}), serving as extension and reuse mechanism,
-%organize types (\emph{skos:Concept}) of descriptive statistics (\emph{DDI-RDF:SummaryStatistics}) like minimum, maximum, and arithmetic mean.
-%\emph{XKOS}\footnote{\url{https://github.com/linked-statistics/xkos}} is a SKOS extension to describe formal statistical classifications like the International Standard Classification of Occupations (\emph{ISCO}).
-%and the Statistical Classification of Economic Activities in the European Community \emph{NACE}.
-%\emph{DCAT} enables to represent data sets inside of data collections like portals, repositories, catalogs, and archives
-%which serve as typical entry points when searching for data.
-
-% Backup of 'Common Vocabularies in SBE Sciences'
-% -----
+Each data value is represented inside a \emph{qb:Observation} containing the values for each dimension \cite{Cyganiak-2010}.
+
+The development of QB is based on the \emph{Statistical Core Vocabulary (SCOVO)} \cite{Hausenblas-2012,Hausenblas-2009,Cyganiak2010}, an RDFS-based, lightweight, and extensible vocabulary for representing statistical data on the Web.
+SCOVO offers a basic core of classes and properties for representing data sets, multiple dimensions, and statistical items.
+\cite{Vrandecic-2010} extend SCOVO with a vocabulary enabling the connection of SCOVO-described
+data sets with external vocabularies to perform more complex data analyses and improve discoverability and reusability.
+
+\subsection{Vocabulary for representing metadata on data in tabular format}
+
+\emph{Physical Data Description (PHDD)} \cite{WackerowHoyleBosch2015} is a vocabulary to represent metadata about data in tabular format as well as its physical properties in RDF, enabling further aggregations and calculations.
+The data could either be represented in records with character-separated values (CSV) or fixed length.
+PHDD is usable standalone or together with related vocabularies like DDI-RDF or DCAT.
+The combined usage of PHDD, DDI-RDF, and DCAT enables the creation of data repositories providing metadata for the description of collections, data discovery, and the processing of the data.
+Descriptions in PHDD could be added to web pages which enables an automatic processing of the data by programs.
+
+Eurostat provides a CSV file, a two-dimensional table (\emph{phdd:Table}) about the variable \emph{formal childcare} 
+which is structured by a table structure (\emph{phdd:TableStructure}, \emph{phdd:Delimited})
+including information about the character set (\emph{ASCII}), the variable delimiter (\emph{,}), the new line marker (\emph{CRLF}), and the first line where the data starts (\emph{2}).
+The table structure is related to table columns (\emph{phdd:Column}) which are described by column descriptions (\emph{phdd:DelimitedColumnDescription}).
+For the column containing the cell values in percent, the column position (\emph{5}), the recommended data type (\emph{xsd:nonNegativeInteger}), and the storage format (\emph{TINYINT}) are given.
+
+\subsection{Vocabulary for representing metadata on unit-record data}
+
+The SBE sciences require high-quality data for their empirical research. For more than a decade, members of the SBE community have been developing and using a
+metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)} \cite{Vardigan-2008},
+an XML format to disseminate, manage,
+and reuse data collected and archived for research. 
+%\cite{Vardigan-2008}. 
+In XML, the definition of schemas containing constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
+With the rise of the Web of Data, data professionals and institutions are very interested in publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate discovery and reuse.
+Recently, members of the SBE and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)} \cite{BoschCyganiakWackerowZapilko2015} a means to expose DDI metadata as Linked Data.
+
+For more detailed analyses, we refer to the unit-record data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}.
+Where data collection is cyclic, data sets may be released as \emph{series}, 
+where each cycle produces one or more data sets. 
+The aggregated variable \emph{formal childcare} is calculated on the basis of six unit-record variables 
+(i.a., \emph{Education at pre-school})
+for which detailed metadata is given 
+(i.a., code lists)
+enabling researchers to replicate the results shown in aggregated data tables.
+
+DDI-RDF is used to represent metadata on unit-record data in RDF.
+The series (\emph{disco:StudyGroup}) EU-SILC contains one study (\emph{disco:Study}) for each year (\emph{dcterms:temporal}) of data collection.
+The property \emph{dcterms:spatial} points to the countries for which the data has been collected.
+The study \emph{EU-SILC 2011} contains eight unit-record data sets (\emph{disco:LogicalDataSet}) including unit-record variables (\emph{disco:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
+
+\subsection{Vocabularies for representing knowledge organization systems and formal statistical classifications}
+
+The \emph{Simple Knowledge Organization System (SKOS)} \cite{W3C-SKOS-2009,Isaac-2009} is a vocabulary to represent knowledge organization systems such as thesauri, classification schemes, and taxonomies.
+Using SKOS, a knowledge organization system is expressible as machine-readable data in a machine-processable standard format for the Semantic Web.
+It can then be exchanged between computer applications and published in a machine-readable format in the Web \cite{Isaac-2009}.
+SKOS provides high interoperability with other standards, formats, and applications as it is based on RDF, the standard model for data interchange on the Web.
+SKOS is used to represent term relations, term hierarchies, and the structure and semantics of vocabularies.
+A vocabulary is typically represented as a \emph{skos:ConceptScheme} that holds multiple \emph{skos:Concepts} which can be linked to other \emph{skos:Concepts} by hierarchical and associative properties that are oriented on relations of the ISO norms for thesauri like \emph{skos:broader}, \emph{skos:narrower}, and \emph{skos:related}.
+
+Thesauri organize complex relations between terms even on the lexical level.
+The \emph{SKOS Simple Knowledge Organization System eXtension for Labels (SKOS-XL)} \cite{Miles-2009} defines an extension for SKOS, providing additional support for describing and linking lexical entities.
+This provides a complexity of relationships between terms which is needed by several vocabularies.
+
+SKOS is reused multiple times to build SBE vocabularies.
+The codes of the variable \emph{Education at pre-school} (measuring the number of education hours per week) are modeled as \emph{skos:Concepts} and a \emph{skos:OrderedCollection} organizes them in a particular order within a \emph{skos:memberList}.
+A variable may be associated with a theoretical concept (\emph{skos:Concept}).
+Hierarchies of theoretical concepts are built within a \emph{skos:ConceptScheme} of a series using \emph{skos:narrower}.
+The variable \emph{Education at pre-school} is assigned to the theoretical concept \emph{Child Care} which is the narrower concept of \emph{Education}, one of the top concepts of the series EU-SILC.
+Controlled vocabularies (\emph{skos:ConceptScheme}), serving as extension and reuse mechanism, organize types (\emph{skos:Concept}) of descriptive statistics (\emph{disco:SummaryStatistics}) like minimum, maximum, and arithmetic mean.
+
+The \emph{SKOS Extension for Statistics (XKOS)} \cite{Cotton-2015} is a vocabulary to describe formal statistical classifications and introduce refinements of SKOS semantic properties \cite{Cotton-2013}.
+A formal statistical classification is a hierarchical concept scheme including concepts, associated codes (numeric string labels), short textual labels, definitions, and longer descriptions that include rules for their use.
+
+%There is a common need within the SBE sciences to represent the structure and textual properties of formal statistical classifications like the International Standard Classification of Occupations (ISCO) and the Statistical Classification of Economic Activities in the European Community (NACE) as well as different types of relations between classifications and contained concepts in RDF.
+%LOD is used to create Web artifacts that machines can interpret, so publishing machine-readable statistical classifications as SKOS instances is desired \cite{Cotton-2013}.
+
+XKOS extends SKOS for the needs of statistical classifications like the \emph{International Standard Classification of Occupations (ISCO)} and the \emph{Statistical Classification of Economic Activities in the European Community (NACE)}.
+It does so in two main directions.
+First, it defines a number of terms that enable the representation of statistical classifications with their structure and textual properties, as well as different types of relations between classifications and contained concepts.
+Second, it refines SKOS semantic properties to allow the use of more specific relations between concepts.
+Those specific relations can be used for the representation of classifications or for any other case where SKOS is employed \cite{Cotton-Gillman-Jaques-2013}.
+The National Institute of Statistics and Economic Studies (Insee) already provides diverse statistical classifications in RDF conforming to XKOS.
+
+\subsection{Vocabulary for representing data sets inside of data collections}
+
+The \emph{Data Catalog Vocabulary (DCAT)} \cite{Maali-2014} enables to represent data sets inside of data collections like portals, repositories, catalogs, and archives
+which serve as typical entry points when searching for data.
+Users search for aggregated and unit-record data records (\emph{dcat:CatalogRecord}) in data catalogs (\emph{dcat:Catalog}). 
+As search differs depending on users’ information needs,
+they may only search for records' metadata (e.g., \emph{dcterms:title}, \emph{dcterms:description}), 
+or they may formulate more sophisticated queries on aggregated and unit-record data sets (\emph{dcat:Dataset}) or their
+distributions (\emph{dcat:Distribution}) which are part of the records. 
+Often, users search for data sets covering particular topics (\emph{dcat:keyword}, \emph{dcat:theme}), time periods (\emph{dcterms:temporal}),  or  locations (\emph{dcterms:spatial}), 
+or for certain formats in which the data distribution is available (\emph{dcterms:format}).
 
@@
 As certain constraints cannot be formulated and validated by XML Schemas, 
-so-called secondary-level validation tools like \emph{Schematron}\footnote{\url{https://msdn.microsoft.com/en-us/library/aa468554.aspx}} 
+so-called secondary-level validation tools like \emph{Schematron}
 have been introduced to overcome the limitations of XML validation.
 Schematron generates validation rules and validates XML documents according to them.
-With RDF validation, one can overcome the drawbacks when validating XML documents.\footnote{\url{http://www.xmlmind.com/xmleditor/_distrib/doc/xmltool/xsd_structure_limitations.html}}
+With RDF validation, one can overcome the drawbacks when validating XML documents.
 It cannot be validated, e.g., if each code of a variable's code list is associated with a category and that if an element has a specific value then certain child elements must be present.
 
-A well-formed \emph{RDF Data Cube} is an RDF graph describing one or more instances of \emph{qb:DataSet} for which each of the 22 integrity constraints,\footnote{http://www.w3.org/TR/vocab-data-cube/\#wf} defined within the QB specification, passes.
+A well-formed \emph{RDF Data Cube} is an RDF graph describing one or more instances of \emph{qb:DataSet} for which each of the 22 integrity constraints, defined within the QB specification, passes \cite{CyganiakReynolds2014}.
 Each integrity constraint is expressed as narrative prose and, where possible, as a SPARQL ASK query or query template.
@@
 
-To gain better insights into the role that certain types of constraints play for the quality of RDF data, we use two simple classifications: on the one hand, we classify RDF constraint types whether they are expressible by different types of constraint languages and on the other hand, we classify constraints formulated for a given vocabulary according to the perceived severity of their violation.
-
-Within the working groups, we identified by today 81 requirements to formulate RDF constraints (e.g., \emph{R-75: minimum qualified cardinality restrictions}); each of them corresponding to an RDF constraint type.\footnote{Constraint types are uniquely identified by alphanumeric technical identifiers like \emph{R-71-CONDITIONAL-PROPERTIES}}
-Within a technical report, we explain each requirement/constraint type in detail and give examples for each expressed by different constraint languages \cite{BoschNolleAcarEckert2015}.
-We provide mappings to representations in Description Logics (DL) \cite{Baader-2003} to logically underpin each requirement and to determine which DL constructs are needed to express each constraint type.
-%In total, we distinguish 81 RDF constraint types as we identified 6 RDF constraint types which are only necessary for validating particular vocabularies.
-%Constraints are instantiated from constraint types in order to validate both metadata and data represented by any vocabulary; thus, the proposed classification system is vocabulary-independent and therefore applicable generically.
-For the three vocabularies, several SBE domain experts determined the default severity level of the 115 concrete constraints, which we published in a technical report \cite{BoschZapilkoWackerowEckert2015}.
+To gain insights into the role that certain types of constraints play for assessing the quality of RDF data, we use two simple classifications.
+On the one hand, we classify constraint types based on whether they are expressible by different types of constraint languages.
+On the other hand, we let several domain experts classify constraints, which are formulated for a given vocabulary, according to the perceived severity of their violation.
+
+For the three vocabularies, several SBE domain experts determined the severity level for each of the 115 constraints.
+In a technical report, we provide detailed textual descriptions for all these constraints as well as their assignments to constraint types and severity levels \cite{BoschZapilkoWackerowEckert2015}.
 In the following, we summarize the classifications of constraint types and constraints for the purpose of our evaluation.
 
-\subsection{Classification of Constraint Types according to the Expressivity of Constraint Languages}
-
-According to the expressivity of constraint languages, the complete set of constraint types encompasses three not disjoint sets of constraint types:
+\subsection{Classification of constraint types according to the expressivity of constraint language types}
+
+According to the expressivity of three different types of constraint languages, the complete set of constraint types encompasses the subsequent three not disjoint sets of constraint types:
+
 \begin{enumerate}
@@
 \textbf{\emph{RDFS/OWL Based}.}
-The modeling languages RDFS and OWL are typically used to formally specify vocabularies.
-\emph{RDFS/OWL Based} denotes the set of constraint types which can be formulated with RDFS/OWL axioms which we use in terms of constraints with CWA/UNA semantics and without reasoning.\footnote{The entailment regime is to be decided by the implementers.
-It is our point that reasoning affects validation and that a proper definition of the reasoning to be applied is needed.} RDFS/OWL axioms are commonly found within formal specifications of vocabularies.
-\emph{RDFS/OWL Based} constraints generally can be seen as a basic level of constraints ensuring that the data is consistent with the formally and explicitly specified intended semantics as well as the integrity of vocabularies' conceptual models about data.
+\emph{RDFS/OWL Based} denotes the set of constraint types which can be formulated with RDFS/OWL axioms when using them in terms of constraints with CWA/UNA semantics and without reasoning.
+The entailment regime is to be decided by the implementers.
+It is our point that reasoning affects validation and that a proper definition of the reasoning to be applied is needed.
+
+The modeling languages RDFS and OWL are typically used to formally specify vocabularies and RDFS/OWL axioms are commonly found within formal specifications of vocabularies.
+In general, constraints instantiated from \emph{RDFS/OWL Based} constraint types can be seen as a basic level of constraints ensuring that the data is consistent with the formally and explicitly specified intended semantics of vocabularies as well as with the integrity of vocabularies' conceptual models about data.
 
@@
 Constraints of the type \emph{minimum qualified cardinality restrictions} (\emph{R-75}), e.g., guarantee that individuals of given classes are connected by particular properties to at least n different individuals/literals of certain classes or data ranges.
-For \emph{DDI-RDF}, a \emph{minimum qualified cardinality restriction} can be obtained from a respective OWL axiom which ensures that a \emph{disco:Questionnaire} has (\emph{disco:question}) at least one \emph{disco:Question}:
-\begin{ex}
-[   a owl:Restriction ; rdfs:subClassOf Questionnaire ;
+For \emph{DDI-RDF}, a \emph{minimum qualified cardinality restriction} can be obtained from a respective OWL axiom to ensure that each \emph{disco:Questionnaire} includes (\emph{disco:question}) at least one \emph{disco:Question}:
+
+\begin{ex}[commandchars=\\\{\}]
+\textit{OWL:}
+disco:Questionnaire rdfs:subClassOf
+  [ a owl:Restriction ; 
     owl:minQualifiedCardinality 1 ;
-    owl:onProperty question ;
-    owl:onClass Question ] .
+    owl:onProperty disco:question ;
+    owl:onClass disco:Question ] .
 \end{ex}
@@
 
-\emph{Constraint Language Based} and \emph{SPARQL Based} are in contrast to \emph{RDFS/OWL Based} constraints usually not (yet) explicitly defined within formal specifications of vocabularies.
-Instead, they are often defined within textual descriptions of vocabularies.
-Additionally, we let our domain and data experts define constraints when they agreed that violating the constraint would affect the usefulness of the data.
-
+In contrast to \emph{RDFS/OWL Based} constraints, \emph{Constraint Language} and \emph{SPARQL Based} constraints are usually not (yet) explicitly defined within formal specifications of vocabularies.
+Instead, they are often specified within formal as well as informal textual descriptions of vocabularies.
+Additionally, we let domain experts define constraints when they agreed that violating these constraints would affect the usefulness of the data.
+
+\par\bigskip
 \textbf{\emph{Constraint Language Based}.}
-We further distinguish \emph{Constraint Language Based} as the set of constraint types that can be expressed by common classical declarative high-level constraint languages like ShEx, ReSh, and DSP. 
+We further distinguish \emph{Constraint Language Based} as the set of constraint types that can be expressed by classical high-level constraint languages like ShEx, ReSh, and DSP. 
 %RDFS, and OWL as we consider RDFS and OWL as constraint languages when assuming CWA/UNA semantics without reasoning. 
@@
 SPARQL, however, is considered as a low-level implementation language in this context.
-In contrast to SPARQL, high-level constraint languages are comparatively easy to understand and constraints can be formulated more concisely.
-Declarative languages may be placed on top of SPARQL when using it as an implementation language.
-For these \emph{Constraint Language Based} constraint types, we expect a straight-forward support in future constraint languages.
-
-\emph{Context-specific exclusive or of property groups} (\emph{R-11}) is a constraint type which can be formulated by a high-level constraint language.
-Constraints of this type restrict individuals of given classes to have properties defined within exactly one of multiple mutually exclusive property groups.
-Within the context of DDI-RDF, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theo\-reti\-cal concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes), but not both:
+In contrast to SPARQL, high-level constraint languages are comparatively easy to understand and constraints can be formulated in a more concise way.
+Declarative languages may be placed on top of SPARQL when using it as an execution language.
+For \emph{Constraint Language Based} constraint types, we expect a straight-forward support in future constraint languages.
+
+\emph{Context-specific exclusive or of property groups} (\emph{R-13}) is a constraint type which can be formulated by the high-level constraint language ShEx.
+Constraints of this type restrict individuals of given classes to have property links of properties defined within exactly one of multiple mutually exclusive property groups.
+Within the context of DDI-RDF, e.g., \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theo\-reti\-cal concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes), but not both:
 %(\emph{error}).
@@
 \begin{ex}[commandchars=\\\{\}]
-\textit{ShEx:} Concept \{ 
-    ( definition string ) |
-    ( notation string , prefLabel string ) \}
+\textit{ShEx:} 
+skos:Concept \{ 
+    ( skos:definition xsd:string ) |
+    ( skos:notation xsd:string , skos:prefLabel xsd:string ) \}
 \end{ex}
@@
 The set \emph{SPARQL Based} encompasses constraint types that are not expressible by RDFS/OWL or common high-level constraint languages but by plain SPARQL.
-For assessing the quality of thesauri, e.g., we concentrate on the graph-based structure and apply graph- and network-analysis techniques.
+For assessing the quality of thesauri, e.g., we concentrate on their graph-based structure and apply graph- and network-analysis techniques.
 An example of such constraints of the constraint type \emph{structure} is that 
 a thesaurus should not contain many orphan concepts, i.e., concepts without any associative or hierarchical relations, lacking context information valuable for search.
-As the complexity of this constraint is relatively high, it is only expressible by SPARQL and not directly understandable:
-\begin{ex}
-SELECT ?concept WHERE {
-    ?concept a [rdfs:subClassOf* skos:Concept] .
-    FILTER NOT EXISTS { ?concept ?p ?o . 
+As the complexity of this constraint is relatively high, it is only expressible by SPARQL, not that intuitive, and quite complex:
+
+\begin{ex}[commandchars=\\\{\}]
+\textit{SPARQL:} 
+SELECT ?concept WHERE \{
+    ?concept a [ rdfs:subClassOf* skos:Concept ] .
+    FILTER NOT EXISTS \{ ?concept ?p ?o . 
         FILTER ( ?p IN ( skos:related, skos:relatedMatch, 
-                         skos:broader, ... ) ) . } }
+                         skos:broader, ... ) ) . \} \}
 \end{ex}
-\emph{SPARQL Based} constraint types are today only expressible by plain SPARQL. Depending on their usefulness, a support in constraint languages should be considered.
-
-\subsection{Classification of Constraints according to the Severity of Constraint Violations}
-
-A concrete constraint is instantiated from one of the 81 constraint types and is defined for a specific vocabulary.
+
+\emph{SPARQL Based} constraint types are today only expressible by plain SPARQL. Depending on their usefulness, a support in high-level constraint languages should be considered.
+
+\subsection{Classification of constraints according to the severity of constraint violations}
+
+A concrete constraint is instantiated from one of the 81 constraint types and defined for a specific vocabulary.
 It does not make sense to determine the severity of constraint violations of an entire constraint type,
@@
 %whereas, the violation of another constraint of the same type may be minor.
-SBE experts determined the default \emph{severity level}\footnote{The possibility to define severity levels in vocabularies is in itself a requirement (\emph{R-158}).} for each of the 115 constraints to indicate how serious the violation of the constraint is.
-We use the classification system of log messages in software development like \emph{Apache Log4j 2} \cite{Apache-2015}, the \emph{Java Logging API},\footnote{\url{http://docs.oracle.com/javase/7/docs/api/java/util/logging/Level.html}} and the \emph{Apache Commons Logging API}\footnote{\url{http://commons.apache.org/proper/commons-logging/}} as many data practitioners also have experience in software development and software developers intuitively understand these levels.
+SBE experts determined the default \emph{severity level} for each of the 115 constraints to indicate how serious the violation of the constraint is.
+Although we provide default severity levels for each constraint, validation environments should enable users to adapt the severity levels of constraints according to their individual needs.
+The possibility to define severity levels for concrete constraints is in itself a requirement (\emph{R-158}).
+
+We use the classification system of log messages in software development like \emph{Apache Log4j 2}, the \emph{Java Logging API}, and the \emph{Apache Commons Logging API} as many data practitioners also have experience in software development and software developers intuitively understand these levels.
 We simplify this commonly accepted classification system and distinguish the three severity levels (1) \emph{informational}, (2) \emph{warning}, and (3) \emph{error}.
@@
 %They are not seen as serious errors.
-\emph{Warnings} are syntactic or semantic problems which typically should not lead to an abortion of data processing.
+\emph{Warnings} indicate syntactic or semantic problems which typically should not lead to an abortion of data processing.
 \emph{Errors}, in contrast, are syntactic or semantic errors which should cause the abortion of data processing. 
@@
 
-Note that there is a correlation between the severity of a constraint and the classification according to the expressivity of constraint languages of its type: \emph{RDFS/OWL Based} constraints are in many cases classified with an \emph{error} level as they typically represent basic constraints; there is a reason why they have been included in the vocabulary specification.
-Although we provide default severity levels for each constraint, validation environments should enable users to adapt the severity levels of constraints according to their individual needs.
+Note that there is indeed a correlation between the severity of a constraint and the classification of its type: \emph{RDFS/OWL Based} constraints are in many cases associated with an \emph{error} level as they typically represent basic constraints: there is a reason why they have been included in the vocabulary specification.
 % Validation environments should enable users to select which constraints to validate against depending on their individual use cases.
@@
 
-\subsection{Examples}
-%\ke{die examples finde ich sehr schwer zu lesen, es fehlt auch eine einleitung aus der hervorgeht, wieso die beispiele hier eigentlich aufgeführt werden.}
-\label{vocabulary-constraint-types}
-
-To get an overview on the sets of constraint types, we delineate concrete constraints on the three vocabularies for each set of constraint type and classify them according to their severity.
+\subsection{Classification examples}
+
+To get an overview on the constraint types contained in each of the three sets of constraint types, we delineate concrete constraints on the three vocabularies, group them by constraint type set, and classify them according to the severity of their violation.
 
@@
 %i.e., individuals cannot be instances of multiple disjoint classes.
+
+\par\bigskip
 \textbf{\emph{RDFS/OWL Based}.}
@@
 \emph{xsd:string}).
-\emph{disco:CategoryStatistics}, e.g., can only have \emph{disco:computationBase} relationships to the values \emph{valid} and \emph{invalid} of the datatype \emph{rdf:langString} (default severity level: \emph{error}).
+\emph{disco:CategoryStatistics}, e.g., can only have \emph{disco:computationBase} relationships to the literals \emph{"valid"} and \emph{"invalid"} of the datatype \emph{rdf:langString} (default severity level: \emph{error}).
 %Validation should \emph{exploit sub-super relations} in vocabularies (\emph{R-224}).
@@
 %which may indicate when the data is verbose/redundant or expressed at a too general level.
-Consider the following \emph{DL knowledge base} $\mathcal{K}$:\footnote{A \emph{DL knowledge base} is a collection of formal statements which correspond to \emph{facts} or what is known explicitly. }
+Consider the following \emph{DL knowledge base} $\mathcal{K}$, a collection of formal statements corresponding to \emph{facts} or what is known explicitly:
 \begin{center}
@@
   &{\small\ms{Variable $\equiv$ $\exists$ concept.Concept,}} \\
-	&{\small\ms{DataSet $\sqsubseteq$ $\forall$ structure.DataStructureDef,}} \\
+	&{\small\ms{DataSet $\sqsubseteq$ $\forall$ structure.DataStructureDefinition,}} \\
   &{\small\ms{$\exists$ hasTopConcept.$\top$ $\sqsubseteq$ ConceptScheme,}} \\
@@
 %We extend $\mathcal{K}$ by 
-\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals/literals of certain types.
+The constraint type \emph{existential quantifications} (\emph{R-86}) can be used to enforce that instances of given classes must have some property relation to individuals/literals of certain types.
 Variables, e.g., should have a relation to a theoretical concept (\emph{informational}).
 %The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
-The variable \emph{Education at pre-school} is associated with the theoretical concept \emph{Child Care}. 
 The default severity level of this constraint is weak, as in most cases research can be continued without having information about the theoretical concept of a variable.
-%
+
 A \emph{universal quantification} (\emph{R-91}) contains all those individuals that are connected by a property only to individuals/literals of particular classes  or data ranges.
@@
 %Only \emph{\textcolor{red}{dcat}:Catalogs}, e.g., can have \emph{dcat:dataset} relationships to \emph{dcat:Datasets} (\emph{error}).
-Only \emph{qb:DataSets}, e.g., can have \emph{qb:structure} relationships to \emph{qb:DataStructureDefinitions} (\emph{error}).
-\emph{Property domains} (\emph{R-25, R-26}) and \emph{property ranges} (\emph{R-28, R-35}) constraints restrict domains and ranges of properties:
+Resources of the type \emph{qb:DataSet}, e.g., can only have \emph{qb:structure} relationships to \emph{qb:DataStructureDefinitions} (\emph{error}).
+
+\emph{Property domains} (\emph{R-25}) and \emph{property ranges} (\emph{R-35}) constraints restrict domains and ranges of properties:
 %Only \emph{phdd:Tables}, e.g., can have \emph{\textcolor{red}{phdd}:isStructuredBy} relationships (\emph{error}) and \emph{\textcolor{red}{xkos}:belongsTo} relations can only point to \emph{skos:Concepts} (\emph{error}).
@@
 
+\par\bigskip
 \textbf{\emph{Constraint Language Based}.}
@@
 If a QB dimension property, e.g., has a \emph{qb:codeList},
-then the value of the dimension property on every \emph{qb:Observation} must be in the code list (\emph{error}).
-
-\emph{Default values} for objects (\emph{R-31}) or literals (\emph{R-38}) of given properties are inferred automatically when properties are not present in the data.
+then the value of the dimension property on every \emph{qb:Observation} must be in that code list (\emph{error}).
+
+\emph{Default values} for objects (\emph{R-31}) or literals (\emph{R-38}) of given properties are inferred automatically when the properties are not present in the data.
 The value \emph{true} for the property {\em disco:isPublic} indicates that a {\em disco:LogicalDataSet} can be accessed by anyone.
@@
 
+\par\bigskip
 \textbf{\emph{SPARQL Based}.}
@@
 %$\mathcal{CT}_{C}$ denotes the set of constraint types for which the definition of constraints is rather complex and cannot be derived from vocabulary definitions.
-The purpose of \emph{data model consistency} constraints is to ensure the integrity of
-the data according to the intended semantics of vocabularies.
+The purpose of constraints of the type \emph{data model consistency} is to ensure the integrity of
+the data according to the intended semantics of vocabularies’ conceptual models about data.
 Every \emph{qb:Observation}, e.g., must have a value for each dimension
@@
 can have the same value for all dimensions (\emph{warning}).
-If a \emph{qb:DataSet} \emph{D} has a \emph{qb:Slice} \emph{S}, and \emph{S} has an
+If a \emph{qb:DataSet} \emph{D} has a \emph{qb:Slice} \emph{S}, and \emph{S} has a
 \emph{qb:Observation} \emph{O}, then the \emph{qb:DataSet} corresponding to \emph{O} must be \emph{D} (\emph{warning}).
@@
 Variables, questions, and codes, e.g., are typically organized in a particular order. 
-If codes (\emph{skos:Concept}) should be ordered, they must be members (\emph{skos:memberList}) in an ordered collection (\emph{skos:OrderedCollection}), the variable's code list (\emph{informational}).
+If codes (\emph{skos:Concept}) should be ordered, they must be members (\emph{skos:memberList}) in an ordered collection (\emph{skos:Ordered} \emph{Collection}) representing the code list of a variable (\emph{informational}).
 
@@
 It is useful to declare properties to be \emph{conditional} (\emph{R-71}), i.e., if particular properties exist (or do not exist), then other properties must also be present (or absent).
-To get an overview on a study either an abstract, a title, an alternative title, or links to external descriptions should be provided. 
+To get an overview on a study, either an abstract, a title, an alternative title, or links to external descriptions should be provided. 
 If an abstract and an external description are absent, however,  
@@
 In case a variable is represented in form of a code list, codes may be associated with categories, i.e., human-readable labels (\emph{informational}).
-The variable \emph{Education at pre-school}, e.g., is represented as an ordered code list without any categories.
 
@@
 
-%If a {\em skos:Concept} represents a code (having {\em skos:notation} and {\em skos:prefLabel} properties), 
-%then the property {\em DDI-RDF:isValid} has to be stated indicating if the code stands for valid (\emph{true}) or missing (\emph{false}) cases ($\mathcal{SL}_{2}$).
-
-%\textbf{Constraints on Literals.}
-
-%\begin{center}
-%\begin{DL}
-%Concept $\sqsubseteq$ ($\neg$ D $\sqcap$ C) $\sqcup$ (D $\sqcap$ $\neg$ C), D $\equiv$ A $\sqcap$ B \\
-%A $\sqsubseteq$ $\geq$ 1 notation.string $\sqcap$ $\leq$ 1 notation.string \\
-%B $\sqsubseteq$ $\geq$ 1 prefLabel.string $\sqcap$ $\leq$ 1 prefLabel.string \\
-%C $\sqsubseteq$ $\geq$ 1 definition.string $\sqcap$ $\leq$ 1 definition.string \\
-%\end{DL}
-%\end{center}
-
-%\textbf{Searching for (Meta)data.}
-%
-%- DCAT
-%
-%\textbf{Data Integration.}
-%use RDF validation for data integration
-
-%\textbf{Series, Studies, Data Sets, and Data Files.}
-%It is useful to declare properties to be \emph{conditional} (\emph{R-71}), i.e., if particular properties exist (or do not exist), then other properties must also be present (or absent).
-%To get an overview over a series/study either an abstract, a title, an alternative title, or links to external descriptions should be provided. 
-%If an abstract and an external description are absent, however,  
-%a title or an alternative title should be given ($\mathcal{SL}_{1}$).
-%For datatype properties, it should be possible to declare frequently needed \emph{facets} ({\emph{R-46}) to validate input against simple conditions including min/max values, regular expressions, and string length.
-%The abstract of series/studies, e.g., should have a minimum length ($\mathcal{SL}_{1}$).
-%\emph{Existential quantifications} (\emph{R-86}) enforce that instances of given classes must have some property relation to individuals of certain types.
-%If a study, e.g., does not contain any data set ($\mathcal{SL}_{2}$), the actual description of the data is missing which may indicate that it is very hard or unlikely to get access to the data.
-%If metadata on data files, including the actual data, is missing (especially case and variable quantities; $\mathcal{SL}_{1}$), the description of the data sets and the study is not sufficient.
-%Case quantity measures how many cases are collected for a study.
-%High case and variable quantities are indicators for high statistical quality and comprehensiveness of the underlying study ($\mathcal{SL}_{1}$).
-%
-%\textbf{Variables and Variable Comparison.}
-%Variables should be represented (\emph{R-86}; $\mathcal{SL}_{1}$) either as (un)ordered code lists or as unions of datatypes.
-%In case of a code list, associated categories (human-readable labels) may be stated (\emph{R-71}; $\mathcal{SL}_{0}$).
-%The variable \emph{Education at pre-school}, e.g., is represented as ordered code list without any categories.
-%If a {\em skos:Concept} represents a code (having {\em skos:notation} and {\em skos:prefLabel} properties), 
-%then the property {\em DDI-RDF:isValid} has to be stated indicating if the code stands for valid (\emph{true}) or missing (\emph{false}) cases (\emph{R-71}; $\mathcal{SL}_{2}$).
-%Variables may have at least one relationship to a theoretical concept ({\emph{R-86}; $\mathcal{SL}_{0}$).
-%%The variables \emph{number of school years} and \emph{highest educational degree}, e.g., are associated with the theoretical concept \emph{education}. 
-%The variable \emph{Education at pre-school},.e.g, is associated with the theoretical concept \emph{Child Care}. 
-%The default severity level of this constraint is weak, as in most cases research can be continued without associated theoretical concepts.
-%A very common research question is to compare variables of multiple studies or countries (\emph{comparison}).
-%To compare variables, 
-%(1) variables and (2) variable definitions must be present,
-%(3) code lists must be structured properly,
-%(4) for each code an associated category (human-readable label) must be specified, and
-%(5) code lists must either be identical or at least similar.
-%If a researcher wants to get a first overview over comparable variables (use case 1), 
-%covering the first three constraints may be sufficient for this purpose.
-%Thus, the severity level of the first three constraints is stronger ($\mathcal{SL}_{2}$) than the severity level of the next two constraints ($\mathcal{SL}_{1}$ and $\mathcal{SL}_{0}$).
-%If the intention of the researcher is to perform more detailed comparisons (use case 2), however, the violation of the remaining two constraints is getting more serious.
-%
-%\textbf{Descriptive Statistics.}
-%The property \emph{DDI-RDF:percentage} stands for the number of cases of a given code in relation to the total number of cases for a particular variable within a data set.
-%Percentage values are only valid when they are within the \emph{literal range} of 0 and 100 (\emph{R-45}; $\mathcal{SL}_{2}$).
-%{\em Mathematical Operations} (\emph{R-41, R-42}; e.g. date calculations and statistical computations like average, mean, and sum) are performed to ensure the integrity of data models.
-%The sum of percentage values of all codes of a variable code list, e.g., must exactly be 100 ($\mathcal{SL}_{2}$)
-%and the minimum of all variable codes do not have to be greater than the maximum ($\mathcal{SL}_{2}$).
-%Codes (\emph{skos:Concept}) are ordered and therefore have fixed positions in an ordered collection (\emph{skos:OrderedCollection}) within variable representations.
-%In order to check the correctness of relative frequencies' calculations, the cumulative percentage (\emph{DDI-RDF:cumulativePercentage}) of the current code must exactly be the cumulative percentage of the previous code
-%plus the percentage value (\emph{DDI-RDF:percentage}) of the current code (\emph{data model consistency}; $\mathcal{SL}_{2}$).
-%
-%\textbf{Unique Identification.}
-%It is often useful to declare a given (data) property as the \emph{primary key} (\emph{R-226}) of a class, so that a system can enforce uniqueness and also automatically build URIs from user inputs and imported data.
-%In DDI-RDF, resources are uniquely identified by the property \emph{adms:identifier},
-%which is therefore inverse-functional
-%$(\ms{funct identifier}\sp{\overline{\ }})$,
-%i.e.
-for each \emph{rdfs:Resource x}, there can be at most one distinct \emph{rdfs:Resource y} such that \emph{y} is connected by \emph{adms:identifier$\sp{\overline{\ }}$} to \emph{x} ($\mathcal{SL}_{2}$).
-%Keys, however, are even more general than inverse-functional properties (\emph{R-58}),
-%as a key can be a data, an object property, or a chain of properties \cite{Schneider2009}.
-%For this generalization purposes, as there are different sorts of key, and as keys can lead to undecidability, 
-%DL is extended with \emph{key boxes} and a special \emph{keyfor} construct (\ms{identifier \ms{keyfor} Resource}) \cite{Lutz2005}.
-%OWL 2 \emph{hasKey} implements \emph{keyfor} ($\mathcal{SL}_{2}$) and thus can be used to identify resources uniquely, to merge resources with identical key property values, and to recognize constraint violations.
-%%OWL 2 hasKey can be used to identify resources uniquely
-%%
-%%We used Protégé 5.
-%%
-%%example: owl:Thing owl:hasKey ( :hasSSN ) . :Peter :hasSSN "123-45-6789" .
-%%:Peter_Griffin :hasSSN "123-45-6789" .
-%%
-%%We use the predefined Reasoner HermiT.
-%%
-%%:Peter and :Peter_Griffin are derived as identical from the reasoner as they have the same value for :hasSSN.
-%%
-%%hasKey can be used to merge resources and to recognize constraint violations.
-%%
-%%Alternative to OWL 2 hasKey: concise bounded description (proposal of Dan)
-%%
-%%action: explore CBD document solution might be using both approaches
-%%
-%%benefit: additional identification to URI / IRI benefit: compound properties can be used as key
-%
-%
-%\textbf{Membership in Controlled Vocabularies.}
-%In many cases, resources must be members of controlled vocabularies (\emph{R-32}).
-%If a dimension property, e.g., has a \emph{qb:codeList},
-%then the value of the dimension property on every \emph{qb:Observation} must be in the code list ($\mathcal{SL}_{2}$).
-%Summary statistics types like minimum, maximum, and arithmetic mean are maintained within a controlled vocabulary.  
-%Summary statistics can only have \emph{DDI-RDF:summaryStatisticType} relationships to \emph{skos:Concept}s which must be members of the controlled vocabulary \emph{ddicv:SummaryStatisticType}, a \emph{skos:ConceptScheme} ($\mathcal{SL}_{2}$).
-%
-%%\begin{center}
-%%\begin{DL}
-%%SummaryStatistics $\sqsubseteq$ $\forall summaryStatisticType.A$ \\
-%%$A \equiv Concept \sqcap \forall inScheme . B$ \\
-%%$B \equiv ConceptScheme \sqcap \{SummaryStatisticType\}$
-%%\end{DL}
-%%\end{center}
-%
-%\textbf{Coverage.}
-%Information about the temporal (\emph{dcterms:temporal}), the spatial (\emph{dcterms:spatial}), and the topical coverage (\emph{dcterms:subject}) of series, studies, data sets, and data files (\emph{R-86}; $\mathcal{SL}_{1}$) is of interest when performing frequently formulated queries
-	%(e.g. to search for all data sets of given years (temporal coverage) in which data is collected in certain countries (spatial coverage) about particular topics (topical coverage)).
-%Depending on property datatypes,
-%two different literal values have
-%a specific ordering with respect to an operator like \textless (\emph{R-43: literal value comparison}).
-%Start dates (\emph{DDI-RDF:startDate}), e.g., must be before (\emph{\textless}) end dates (\emph{DDI-RDF:endDate}) ($\mathcal{SL}_{2}$).
-%
-%%\textbf{Organizations, Hierarchies, Classifications, and Ordering.}
-%\textbf{Hierarchies and Ordering.}
-%SKOS is based on RDF, which is a graph-based data model.
-Therefore, we can concentrate on the vocabulary's graph-based structure for assessing the quality of SKOS vocabularies and apply graph- and network-analysis techniques (\emph{structure}) like
-%(1) a vocabulary should provide entry points (top concepts) to the data to provide efficient access and guidance for human users,
-%(2) concepts, internal to the tree, should not be indicated as top concepts, and
-%(3) a vocabulary should not contain many orphan concepts 
-%(concepts without any associative or hierarchical relations) lacking valuable context information.
-A controlled vocabulary that contains many orphan concepts is less usable for search and retrieval use cases.
-%%, as, e.g., no hierarchical query expansion can be performed on search terms to find documents with more general content.) \cite{MaderHaslhoferIsaac2012}. 
-%Objects and literals can be \emph{ordered} (\emph{R-121, R-217}) for given properties.
-%\emph{DDI-RDF }variables, questions, and codes/categories are typically organized in a particular order. 
-%If a variable code list should be ordered, the variable representation should be of the type \emph{skos:OrderedCollection} containing multiple codes/categories (each represented as \emph{skos:Concept}) in a \emph{skos:memberList}.
-%
-%\textbf{Reusability.}
-%Within the context of DDI-RDF, \emph{skos:Concept}s can have either \emph{skos:definition} (when interpreted as theoretical concepts) or \emph{skos:notation} and \emph{skos:prefLabel} properties (when interpreted as codes/categories), but not both ($\mathcal{SL}_{2}$).
-%The constraint type \emph{context-specific exclusive or of property groups} (\emph{R-11})
-%restricts individuals of given classes to have exactly one of multiple property groups.
+\section{Implementation}
+\label{implementation}
+
+We claim that RDF data can be validated on constraints of each type expressed in any RDF-based language using SPARQL as low-level executing language.
+This claim is supported by the subsequent facts: \cite{SirinTao2009} showed that constraints can be translated into non-recursive Datalog programs for validation, while \cite{Angles2008} proved that SPARQL has the same expressive power as non-recursive Datalog programs.
+Therefore, data validation can be reduced to SPARQL query answering and SPARQL queries can be executed to validate RDF data against constraints of any type represented in any RDF-based language which has to be expressible in SPARQL.
+
+Since the validation of each of the 81 constraint types can be implemented using SPARQL, we use \emph{SPIN}, a SPARQL-based way to formulate and check constraints, as basis to develop a
+validation environment to validate RDF data according to constraints expressed in arbitrary constraint languages \cite{BoschEckert2014-2}.
+The \emph{RDF Validator}, online available at \url{http://purl.org/net/rdfval-demo}, can directly be used to validate RDF data against constraints extracted from or defined for the three vocabularies DDI-RDF, QB, and SKOS.
+Additionally, own constraints on any vocabulary can be defined using several constraint languages.
+
+The overall idea is that we see constraint languages as domain-specific languages, hence \emph{domain-specific constraint languages (DSCL)}, that are translated into SPARQL and executed on RDF data within our validation environment we based on SPIN.
+Language designers are shifting attention from general purpose languages to domain-specific languages.
+\emph{General-purpose languages} like Java and C++ for programming have been the primary focus of language research for a long time.
+The idea was to create only one language that is better suited for programming than any other language \cite{Taha-2008}.
+
+A \emph{domain-specific language} \cite{Fowler-2010} is a small, usually declarative language, tailored to a particular kind of problem \cite{Raja-2010} and offering substantial gains in expressiveness and ease of use compared with general purpose languages for the domain in question \cite{Mernik-2005}.
+Instead of aiming to be the best for solving any kind of computing problem, domain-specific languages aim to be particularly good for solving a specific class of problems, and in doing so they are often much more accessible to the general public than traditional general-purpose languages .
+
+The translation of a DSCL into SPARQL queries is done once, for instance, by the designer of the DSCL, and provided in form of a \emph{SPIN mapping} plus optional \emph{pre-processing} instructions. 
+From a user's perspective, all that is needed is a representation of \emph{constraints} in the DSCL and some \emph{data} to be validated against these constraints.
+All these resources are purely declarative and provided in RDF or as SPARQL queries.
+The actual execution of the constraint validation process is trivial using SPIN and illustrated in Figure~\ref{fig:constraint-validation-process}.
+%\begin{figure}[H]
+	%\centering
+		%\includegraphics[width=1.00\textwidth]{constraint-validation-process.png}
+	%\caption{Constraint Validation Process}
+	%\label{fig:constraint-validation-process}
+%\end{figure}
+
+\begin{figure}[b]
+\centerline{\psfig{file=constraint-validation-process.png,width=11cm}}
+\vspace*{8pt}
+\caption{Constraint Validation Process}
+\label{fig:constraint-validation-process}
+\end{figure}
+
+First, an RDF graph has to be populated as follows:
+\begin{enumerate}
+\item The \emph{data} is loaded that is to be validated,
+\item the \emph{constraints} in the DSCL are loaded,
+\item the \emph{SPIN mapping} is loaded that contains the SPARQL representation of the DSCL, and 
+\item the \emph{pre-processing} is performed, which can be provided in form of SPARQL CONSTRUCT queries.
+\end{enumerate}
+
+%When the input RDF graph is ready, the SPIN engine checks for each resource if it satisfies all constraints defined in the DSCL and generates a result RDF graph containing information about all constraint violations.
+With this framework, we have all we need to implement our own DSCL.
+
+When the input RDF graph is ready, the SPIN engine checks for each resource if it satisfies all constraints defined in the DSCL and associated with the classes assigned to the resource, and generates a result RDF graph containing information about all constraint violations.
+With this framework, we have all we need to implement our own DSCL.
+
+%With this implementation, there is one obvious limitation of our approach: the DSCL needs an RDF serialization.
+For OWL, DSP, ShEx, and ReSh, this is the case, but in the future, we would like to support non-RDF based languages as well.
+With this implementation, there are two obvious limitations of our approach: (1) constraints must be representable in RDF and (2) constraint languages must be expressible in SPARQL, i.e., the actual checking of constraints of each type the language supports must be expressible in form of a SPARQL query.
+For OWL 2, DSP, ShEx, ReSh, and SHACL, this is the case, but in the future, non-RDF based languages are expected to be supported as well.
+
+\subsection{Connect SPIN to your data}
+
+A SPIN mapping consists of multiple \emph{SPIN construct templates} - each of them containing a SPARQL query executable to validate RDF data against constraints of a particular type.
+These templates are linked to the generic class \emph{ToValidate} whose instances are validated on constraints of a certain type expressed in the DSCL for which the mapping is defined:
+
+\begin{ex}[commandchars=\\\{\}]
+\textit{:ToValidate}
+    spin:constraint 
+        [ a dsp2spin:StatementTemplates_MinimumOccurrenceConstraint ] .
+\end{ex}
+
+As the mapping is designed to be independent of any concrete data, the class \emph{ToValidate} is purely generic.
+Instead of using such a generic class, it is also possible to link a template, responsible to check constraints of a given type, to the classes \emph{owl:Thing} or \emph{rdfs:Resource} to achieve that all instances of the input RDF graph are validated on constraints of that type.
+
+Neither of these classes has to be assigned manually and explicitly to instances within the data to be validated.
+They are either implicitly inferred by means of reasoning or explicitly assigned during the \emph{pre-processing} step, both in an automatic way.
+A reasonable approach would be to specify \emph{ToValidate} as super-class of all classes whose instances should actually be validated against constraints (in the case of DSP: classes that are linked via \ms{dsp:resourceClass} to a description template); this can be accomplished by a suitable SPARQL CONSTRUCT query that is executed before the validation starts.
+After \emph{pre-processing}, the data might look like in the following code snippet -- with the added assignment to the generic class in italics.
+%\emph{Description-Logic-Handbook} denotes a book with the subject \qs Computer Science\qe:
+
+\begin{ex}[commandchars=\\\{\}]
+:Description-Logic-Handbook
+    a :Computer-Science-Book , \textit{:ToValidate} ;
+    :subject "Computer Science" .
+\end{ex}
+
+\subsection{Mapping from a DSCL to SPIN}
+
+The mapping from a DSCL to SPIN is performed by creating SPIN construct templates - one for each constraint type that is supported by the DSCL, so for the constraint type \emph{minimum unqualified cardinality restrictions (R-81)} expressible in DSP:
+%a minimum occurrence that is required:
+
+\begin{ex}[commandchars=\\\{\}]
+dsp2spin:StatementTemplates_MinimumOccurrenceConstraint
+    a \textit{spin:ConstructTemplate} ; 
+    spin:body [
+        a sp:Construct ;
+        sp:templates (...) ;
+        sp:where (...) ] .	
+\end{ex}
+
+\subsubsection{Representing validation results as constraint violations in RDF}
+
+This is the general structure of a SPIN construct template representing a SPARQL CONSTRUCT query in RDF.
+We use SPARQL CONSTRUCT queries to generate descriptions for each detected constraint violation:
+
+\begin{ex}[commandchars=\\\{\}]
+CONSTRUCT \{
+    _:constraintViolation 
+        a \textit{spin:ConstraintViolation} ;
+        spin:violationRoot ?subject ;
+        rdfs:label ?violationMessage ;
+        spin:violationSource ?violationSource ;
+        :severityLevel ?severityLevel ;
+        spin:violationPath ?violationPath ;
+        spin:fix ?violationFix \}
+\end{ex}
+%\pagebreak
+In SPIN, the CONSTRUCT part of a SPARQL CONSTRUCT query is represented in RDF as follows:
+
+\begin{ex}[commandchars=\\\{\}]
+a \textit{sp:Construct} ;
+sp:templates ( 
+    [   sp:subject _:constraintViolation ; 
+        sp:predicate rdf:type ; 
+        sp:object spin:ConstraintViolation ]
+    [   sp:subject _:constraintViolation ; 
+        sp:predicate rdfs:label ; 
+        sp:object [ sp:varName "violationMessage" ] ] ... ) ;
+\end{ex}
+
+Representing constraint violations and therefore validation results in RDF enables to process them further by means of Semantic Web technologies.
+SPIN construct templates generate constraint violation triples indicating the subject, the properties, and the constraints causing the violations and the reason why violations have been raised.
+
+A SPIN construct template creates constraint violation triples if all triple patterns within the SPARQL WHERE clause of the SPARQL CONSTRUCT query match.
+If we specify the existential quantification that a book must have at least one author and if the book \emph{The-Hound-Of-The-Baskervilles} has no \emph{author} relationship, all the triple patterns within the SPARQL WHERE clause match and the SPIN construct template for checking constraints of the type \emph{existential quantifications (R-86)} generates a violation triple.
+
+Constraint violations (\emph{spin:constraintViolation}) should provide useful messages (\emph{rdfs:label}) explaining the reasons why the data did not satisfy the constraint in order to assist data debugging and repair.
+In addition, constraint violation triples contain references to the subjects (\emph{spin:violationRoot}), the properties (\emph{spin:violationPath}), and the constraints (\emph{spin:violationSource}) causing the violations.
+In the example, the subject \emph{The-Hound-Of-The-Baskervilles}, the property \emph{author}, and the \emph{existential quantification} caused the violation.
+
+Constraint violation triples may be linked to useful messages explaining how to overcome raised violations.
+To fix constraint violations (\emph{spin:fix}), we may give some guidance how to become valid data either by adding, modifying, or deleting triples.
+To indicate how severe the violation of a constraint is, we introduce a new property to classify constraints according to different levels of severity (\emph{severityLevel}) like \emph{informational}, \emph{warning}, and \emph{error}.
+It is also important to find not validated triples, i.e., triples which have not been validated against any constraint, as it may be enforced that every triple of the input graph has to be validated.
+
+%The SPARQL variable \emph{this} represents the current resource for which the constraint is checked.
+
+\subsubsection{Representing constraint checks in RDF}
+
+%As for the CONSTRUCT part of the SPARQL CONSTRUCT query, SPIN represents the WHERE clause, i.e., the actual check if constraints of a given type hold for the data, in RDF as well:
+%
+%\begin{ex}
+%[   sp:subject [ sp:varName "subject" ] ; 
+    %sp:predicate rdf:type ; 
+    %sp:object [ sp:varName "resourceClass" ] ]
+%\end{ex}
+
+One of the main benefits of SPIN is that arbitrary SPARQL queries and thus constraint checks are representable as RDF triples. 
+SPIN provides a vocabulary, the \emph{SPIN SPARQL Syntax}, to model SPARQL queries in RDF \cite{Knublauch-2011}. 
+%The benefits of an RDF representation of constraint checks are:
+%\begin{itemize}
+%\item 
+%Constraint checks can be consistently stored together with ontologies, constraints, and the data.
+%\item
+%Constraint checks can be easily shared on the Web of Data.
+%\item
+%Constraint validation can be executed automatically by a SPARQL execution engine.
+%\item
+%Constraint checks can directly be processed by a plethora of already existing RDF tools.
+%\item
+%Constraint checks are linkable to constraints and RDF data.
+%\end{itemize}
+An RDF representation of constraint checks enables that
+(1) they can be consistently stored together with ontologies, constraints, and the data,
+(2) they can easily be shared on the Web of Data,
+(3) they can directly be processed by a plethora of already existing RDF tools,
+(4) they are linkable to constraints and RDF data, and
+(5) the validation of RDF data can automatically be executed by SPARQL execution engines.
+
+As for the CONSTRUCT part of the SPARQL CONSTRUCT query, SPIN also represents the WHERE clause in RDF, i.e., the actual check if constraints of a given type hold for the data.
+The subsequent code snippet demonstrates how SPIN represents SPARQL 1.1 NOT EXISTS \cite{W3C-SPARQL1.1-Query-Language-2013} filter expressions in RDF ({\small\ms{FILTER NOT EXISTS \{ ?book author ?person \}}}) using the RDF Turtle syntax:
+
+\begin{ex}[commandchars=\\\{\}]
+[   a sp:Filter ;
+    sp:expression [
+        a sp:notExists ;
+        sp:elements ( 
+            [   sp:subject [ sp:varName "book" ] ;
+                sp:predicate author ;
+                sp:object [ sp:varName "person" ] ] ) ] ] )
+\end{ex}
+
+As the mapping of a DSCL to SPIN is defined for all constraint types supported by the DSCL and hence independently of concrete constraints, constraints of all these types are generally checked for each instance of the generic class \emph{ToValidate}.
+Therefore, the WHERE clause of a template always has to be restricted to classes for which concrete constraints are actually defined - in the case of DSP, the resource classes substituting the SPARQL variable \emph{?resourceClass}:
+
+\begin{ex}
+WHERE { ?subject rdf:type ?resourceClass . }
+\end{ex}
 
@@
 
-In this section, we describe our findings based on an automatic constraint checking of a large data set.
-Despite the large volume of the data sets in general, this study only uses data for three vocabularies.
-As described in Section~\ref{sbe-vocabularies}, for other vocabularies there is often not (yet) enough data openly available to draw general conclusions.
-The three vocabularies, however, are representative, cover different aspects of SBE data, and are also a mixture of widely adopted and accepted well-established vocabularies (QB, SKOS) and a vocabulary under development (DDI-RDF\footnote{Expected publication end of 2015.}).
-%If our findings hold generally is still to be determined, nevertheless they provide valuable insights for future developments of constraint languages.
-As the evaluation is based on three vocabularies, 
-we cannot make valid general statements for all vocabularies,
-but we can formulate several findings to direct the further development of constraint languages.
-As these findings cannot be proved yet, 
-they still have to be verified or falsified
-by evaluating the quality of data represented by further well-established and newly developed vocabularies.
-
-\subsection{Experimental Setup}
-\label{implementation}
-
-%\ke{Überarbeiten und mit nächstem teil mergen. Nur das erzählen, was für die Auswertung auf den Datensets relevant ist. 115 constraints, 3 vokabulare, wie wurden die datasets daraufhin validiert.}
-
-	%\item First, we assigned each constraint type to exactly one of the disjoint sets of constraint types 
-%in order to get an overview how many constraint types in relation to the total amount of constraint types are extractable from vocabularies ($\mathcal{CT}_{B}$), are easily definable ($\mathcal{CT}_{S}$), and are rather difficult to specify ($\mathcal{CT}_{C}$).
-On the three vocabularies (DDI-RDF, QB, SKOS), we identified and classified 115 constraints\footnote{All 115 implemented constraints are online available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/constraints}} which we implemented for data validation.
-We ensured that the implementation of the constraints is equally distributed over the classes and vocabularies we have.
-We then evaluated the data quality of 15,694 data sets (4.26 billion triples) of SBE research data using these 115 constraints, obtained from 33 SPARQL endpoints.
-%\ke{Das ist eine Wiederholung, ggf. streichen, falls Platz knapp}
-
-%QB and SKOS are well-established vocabularies which are widely adopted and accepted. DDI-RDF is a newly developed vocabulary which will be published in 2015.
-
-%It is likely that such a vocabulary is still subject of constant change, that published data may not be consistent with its current version,
-%and that early adopters did not properly understand its formal specification.
-%\ke{ergebnisse, dann hypothesen, dann kritische auseinandersetzung}
-
-Table~\ref{tab:datasets} lists the number of validated data sets and the overall sizes in terms of triples for each of the vocabularies. We validated, i.a., 
+In this section, based on an automatic constraint checking of a large amount of RDF data sets, we formulate several findings to gain valuable insights and make recommendations to direct the further development of constraint languages.
+
+Despite the large volume of the evaluated data sets in general, we have to keep in mind that in this study we only validate data against constraints for three vocabularies.
+We took all well-established and newly developed SBE vocabularies into account and defined constraints for the three vocabularies of them, which are most commonly used in the SBE sciences.
+For these three vocabularies, large data sets have already been published.
+For other SBE vocabularies, however, there is often not (yet) enough data openly available to draw general conclusions.
+Yet, these three vocabularies are representative, cover different aspects of SBE research data, and are also a mixture of widely adopted, accepted, and well-established vocabularies (QB and SKOS) on the one side and a vocabulary under development (DDI-RDF) on the other side.
+
+As the evaluation is based on only three vocabularies, we cannot make valid general statements for all vocabularies, but we can formulate several findings and make recommendations to direct the further development of constraint languages.
+As these findings cannot be proved yet, they still have to be verified or falsified by evaluating the quality of RDF data represented by further well-established and newly developed vocabularies - used within the SBE sciences and other domains.
+
+\subsection{Experimental setup}
+
+On the three vocabularies DDI-RDF, QB, and SKOS, we collected 115 constraints,\footnote{Implementations of all 115 constraints are online available at: \url{https://github.com/github-thomas-hartmann/phd-thesis/tree/master/chapter/chapter-9/constraints}} either from the vocabularies themselves or from several domain experts, and classified and implemented them for data validation.
+We ensured that these constraints are equally distributed over the sets and vocabularies we have.
+We then evaluated the data quality of 15,694 data sets (4.26 billion triples) of SBE research data, obtained from 33 SPARQL endpoints, by validating the data against these 115 constraints.
+Table~\ref{tab:datasets} lists the number of validated data sets and the overall sizes in terms of validated triples for each of the vocabularies.
+
+\begin{table}[h]
+		\scriptsize
+    \begin{center}
+		\caption{Number of Validated Data Sets and Triples for each Vocabulary}
+		\label{tab:datasets}
+    \begin{tabular}{llr}
+%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
+%    \\  \cmidrule{2-7}
+           \textbf{Vocabulary}
+           & \textbf{Data Sets}
+           & \textbf{Triples}
+
+    \\ \midrule
+		%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
+		%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
+		%\hline
+		\textbf{QB} & $9,990$   & $3,775,983,610$  \\
+		\textbf{SKOS} & $4,178$  & $477,737,281$ \\
+		\textbf{DDI-RDF} & $1,526$  & $9,673,055$  \\
+    \bottomrule
+    \end{tabular}
+    %\\ \emph{C (constraints), CT (constraint types)}
+    \end{center}
+\end{table}
+
+We validated, i.a., 
 (1) QB data sets published by the \emph{Australian Bureau of Statistics},
@@
 \emph{Swedish National Data Service}.
-In a technical report, we describe the evaluation in further detail \cite{BoschZapilkoWackerowEckert2015-2}.
-Furthermore, we published the evaluation results for each QB data set in form of one document per SPARQL endpoint.\footnote{Online available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/evaluation/data-sets/data-cube}}
-
-\begin{table}[H]
-		\scriptsize
-    \begin{center}
-		\caption{Validated Data Sets for each Vocabulary}
-		\label{tab:datasets}
-    \begin{tabular}{lrr}
-%           & \multicolumn{6}{c}{\textbf{Vocabularies}}
-%    \\  \cmidrule{2-7}
-           \textbf{Vocabulary}
-           & \textbf{Data Sets}
-           & \textbf{Triples}
-
-    \\ \midrule
-		%\emph{Triples} & 9,673,055 & 3,775,983,610 & 477,737,281 & 4,263,393,946 \\
-		%\emph{Data Sets} & 1,526 & 9,990 & 4,178 & 15,694 \\
-		%\hline
-		\textbf{QB} & $9,990$   & $3,775,983,610$  \\
-		\textbf{SKOS} & $4,178$  & $477,737,281$ \\
-		\textbf{DDI-RDF} & $1,526$  & $9,673,055$  \\
-    \bottomrule
-    \end{tabular}
-    %\\ \emph{C (constraints), CT (constraint types)}
-    \end{center}
-\end{table}
-
-Since the validation of each of the 81 constraint types can be implemented using SPARQL, we use \emph{SPIN}, a SPARQL-based way to formulate and check constraints, as basis to develop a
-validation environment to validate RDF data according to constraints expressed by arbitrary constraint languages\footnote{Constraint language implementations online available at: \url{https://github.com/boschthomas/rdf-validation/tree/master/SPIN}} \cite{BoschEckert2014-2}.
-The \emph{RDF Validator}\footnote{Online demo available at: \url{http://purl.org/net/rdfval-demo}, source code online available at: \url{https://github.com/boschthomas/rdf-validator}} can directly be used to validate arbitrary RDF data for the three vocabularies.
-Additionally, own constraints on any vocabulary can be defined using several constraint languages.
-The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.
-There is one SPIN construct template for each constraint type.
-A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples indicating the subject and the properties causing constraint violations and the reason why constraint violations have been raised.
-A SPIN construct template creates constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
-%\emph{Missy}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}} provides comprehensive Linked Data services like diverse RDF exports of unit-record metadata conforming to the DDI-RDF vocabulary in form of multiple concrete syntaxes.
-
-\subsection{Evaluation Results and Formulation of Findings}
+In a technical report, we describe the evaluation in further detail for each vocabulary, queried SPARQL endpoint, and constraint \cite{BoschZapilkoWackerowEckert2015-2}.
+Furthermore, we have published the evaluation results for each QB data set in form of one document per SPARQL endpoint.\footnote{Online available at: \url{https://github.com/github-thomas-hartmann/phd-thesis/tree/master/chapter/chapter-9/evaluation/data-sets/QB}}
+
+%Since the validation of each of the 81 constraint types can be implemented using SPARQL, we use SPIN, a SPARQL-based way to formulate and check constraints, as basis to develop a
+%validation environment to validate RDF data according to constraints expressed by arbitrary constraint languages.\footnote{Constraint language implementations online available at: \url{https://github.com/github-thomas-hartmann/phd-thesis/tree/master/rdf-validation/constraint-languages/implementations}}
+%The \emph{RDF Validator}, online available at \url{http://purl.org/net/rdfval-demo}, can directly be used to validate arbitrary RDF data according to constraints extracted from the three vocabularies.\footnote{Vocabulary implementations online available at: \url{https://github.com/github-thomas-hartmann/phd-thesis/tree/master/rdf-validation/vocabularies/implementations}} Additionally, own constraints on any vocabulary can be defined using several constraint languages.
+%
+%The SPIN engine checks for each resource if it satisfies all constraints, which are associated with its assigned classes, and generates a result RDF graph containing information about all constraint violations.
+%There is one SPIN construct template for each constraint type.
+%A SPIN construct template contains a SPARQL CONSTRUCT query which generates constraint violation triples indicating the subject and the properties causing constraint violations and the reason why constraint violations have been raised.
+%A SPIN construct template creates constraint violation triples if all triple patterns within the SPARQL WHERE clause match.
+
+\subsection{Evaluation results and formulation of findings}
 
@@
 %Table \ref{tab:evaluation-constraint-types} displays the evaluation of the metadata quality on real world data sets regarding constraint types.
-Tables \ref{tab:evaluation-constraint-violations-1} and \ref{tab:evaluation-constraint-violations-2} show the results of the evaluation, more specifically the constraints and the constraint violations, which are caused by these constraints, in percent; whereas the numbers in the first line indicate the absolute amount of constraints and violations.
-The constraints and their raised violations are grouped by vocabulary, which type of language the constraint types are formulated with, and their severity level.
+Tables \ref{tab:evaluation-constraint-violations-1} and \ref{tab:evaluation-constraint-violations-2} show the results of the evaluation, more specifically the numbers of constraints and constraint violations, which are caused by these constraints, in percent; whereas the numbers in the first line indicate the absolute amount of constraints and violations.
+The constraints and their raised violations are grouped by vocabulary, which type of language the types of the constraints are formulated with, and their severity level.
+
 The numbers of validated triples and data sets differ between the vocabularies
@@
 There is a strong overlap between \emph{RDFS/OWL} and \emph{Constraint Language Based} constraint types as in many cases constraint types are expressible by RDFS/OWL and classical constraint languages.
-This is the reason why the percentage values of constraints and violations grouped by the classification of constraint types according to the expressivity of constraint languages do not accumulate to 100\%.
+This is the reason why the percentage values of constraints and violations grouped by the classification of constraint types according to the expressivity of constraint language types do not accumulate to 100\%.
 
@@
 
-\begin{table}[H]
+\begin{table}[h]
 		\scriptsize
     \begin{center}
-		\caption{Constraints and Constraint Violations (1)}
+		\caption{Evaluation Results (1)}
 		\label{tab:evaluation-constraint-violations-1}
@@
 
-\begin{table}[H]
+\begin{table}[h]
 		\scriptsize
     \begin{center}
-		\caption{Constraints and Constraint Violations (2)}
+		\caption{Evaluation Results (2)}
 		\label{tab:evaluation-constraint-violations-2}
@@
 %\end{hyp}
-\begin{hyp}
-The facts that 80\% of all violations are raised by SPARQL Based constraints and that 2/3 of all constraints are SPARQL Based, increases the importance to formulate constraints, which up to now can only be expressed in SPARQL, using high-level constraint languages.
+\par\bigskip
+{\centering\textbf{Finding 1}}
+\emph{The facts that 80\% of all violations are raised by SPARQL Based constraints and that 2/3 of all constraints are SPARQL Based, increases the importance to formulate constraints, which up to now can only be expressed in SPARQL, using high-level constraint languages.
 Data quality can be significantly improved when suitable constraint languages are developed which enable to define SPARQL Based constraints in an easy, concise, and intuitive way.
-Thereby, the more elaborate a vocabulary is, the more sophisticated and complex constraints are specified using SPARQL.
-\end{hyp}
+Thereby, the more elaborate a vocabulary is, the more sophisticated and complex constraints are specified using SPARQL.}
+\par\bigskip
 
@@
 
-\begin{hyp}
-The fact that only 1/5 of all violations result from RDFS/OWL Based constraints, even though 1/3 of all constraints are RDFS/OWL Based, indicates good data quality for all vocabularies with regard to their formal specifications.
-%Data corresponds to formal specifications of vocabularies the data is conforming to. 
-%This demonstrates that constraint formulation in general works. 
-\end{hyp}
-
-\begin{hyp}
-As 1/3 of all constraints are RDFS/OWL Based, the first step to make progress in the further development of constraint languages is to cover the constraint types which can already be formulated using RDFS and OWL.
-\end{hyp}
+\par\bigskip
+{\centering\textbf{Finding 2}}
+\emph{The fact that only 1/5 of all violations result from RDFS/OWL Based constraints, even though more than 1/3 of all constraints are RDFS/OWL Based, indicates good data quality for all vocabularies with regard to their formal specifications.}
+\par\bigskip
+
+{\centering\textbf{Finding 3}}
+\emph{As more than 1/3 of all constraints are RDFS/OWL Based, the first step to make progress in the further development of constraint languages is to cover the constraint types which can already be formulated using RDFS and OWL.}
+\par\bigskip
 
@@
 
-\begin{hyp}
-For well-established vocabularies, RDFS/OWL Based constraints are almost completely satisfied which generally indicates very impressive data quality, at least in the SBE domain and for the basic requirements.
-For newly developed vocabularies, however, data quality is poor as RDFS/OWL Based constraints are not fulfilled.
-\end{hyp}
+\par\bigskip
+{\centering\textbf{Finding 4}}
+\emph{For well-established vocabularies, RDFS/OWL Based constraints are almost completely satisfied which generally indicates very impressive data quality, at least in the SBE domain and for the basic requirements.
+For newly developed vocabularies, however, data quality is poor as RDFS/OWL Based constraints are not fulfilled.}
+\par\bigskip
 
@@
 Thus, published data may not be consistent with the current draft of its conforming vocabulary.
-In case newly developed vocabularies turn into well-established ones,
+
+When vocabularies under development turn into well-established ones,
 data providers are experienced in publishing their data in conformance with these vocabularies
@@
 As a consequence, \emph{RDFS/OWL Based} constraints are satisfied to a greater extend which leads to better data quality.
-%
-The reason why we only defined \emph{SPARQL Based} constraints for assessing the quality of thesauri is that literature and practice especially concentrate on evaluating graph-based structures of thesauri by applying graph- and network-analysis techniques which can only be implemented by SPARQL.
+
+The reason why we only defined \emph{SPARQL Based} constraints on SKOS for assessing the quality of thesauri is that literature and practice especially concentrate on evaluating graph-based structures of thesauri by applying graph- and network-analysis techniques which are of such complexity that they can only be implemented in SPARQL.
 
@@
 Almost 40\% of all constraints are \emph{error}, more than 40\% are \emph{informational}, and nearly 20\% are \emph{warning} constraints.
-\emph{Informational} constraints caused almost 1/3 and
+\emph{Informational} constraints caused approximately 1/3 and
 \emph{warning} constraints narrowly 2/3 of all violations.
@@
 
-\begin{hyp}
-Although 40\% of all constraints are error constraints, the percentage of severe violations is very low, compared to about 2/3 of warning and 1/3 of informational violations.
-This implies that data quality is high with regard to the severity level of constraints and that proper constraint languages can significantly improve data quality beyond fundamental requirements.
-\end{hyp}
+\par\bigskip
+{\centering\textbf{Finding 5}}
+\emph{Although 40\% of all constraints are error constraints, the percentage of severe violations is very low, compared to about 2/3 of warning and 1/3 of informational violations.
+This implies that data quality is high with regard to the severity level of constraints and that proper constraint languages can significantly improve data quality beyond fundamental requirements.}
+\par\bigskip
 
@@
 %85\% of the QB constraints are \emph{error} constraints.
-More than 50\% of the DDI-RDF and SKOS constraints are \emph{informational} constraints.
+More than 50\% of the DDI-RDF constraints and more than 70\% of the SKOS constraints are \emph{informational} constraints.
 1/6 of the DDI-RDF violations are caused by \emph{error} constraints and
@@
 
-\begin{hyp}
-%\ke{das ist doch das gleiche wie 4, oder?}\bz{Stimme Kai zu. Finding 4 und 6 koennte man zusammenfassen oder falls es doch Unterschiede gibt, muessen die staerker hervorgehoben werden.}
-For well-established vocabularies, data quality is high as serious violations rarely appear (0.3\% for QB).
-For newly developed vocabularies, however, data quality is worse as serious violations occur partially (1/6 for DDI-RDF).
-\end{hyp}
-
-Especially for newly developed vocabularies, constraint languages should be used to a larger extend in addition to RDFS/OWL in order to define appropriate constraints to detect and solve severe violations.
+\par\bigskip
+{\centering\textbf{Finding 6}}
+\emph{For well-established vocabularies, data quality is high as serious violations rarely appear (0.3\% for QB).
+For newly developed vocabularies, however, data quality is worse as serious violations occur partially (1/6 for DDI-RDF).}
+\par\bigskip
+
+Especially for vocabularies under development, constraint languages should be used to a larger extend in addition to RDFS/OWL in order to define appropriate constraints to detect and solve severe violations.
 %\ke{aber das wird doch gemacht, halt mit RDFS und OWL, weswegen die etablierten ja besser sind.}
@@
 %Table \ref{tab:evaluation-expressivity-severity} shows the relations between the severity level of the violations caused by all 115 constraints and the classification according to the expressivity of constraint languages of the constraint types of the violations in percent.
-80\% of the violations which are raised by either \emph{RDFS/OWL} or \emph{Constraint Language Based} constraints are caused by constraints with the severity level \emph{informational} (see Table \ref{tab:evaluation-expressivity-severity}) and almost all (94\%) of the violations which are caused by \emph{SPARQL Based} constraints are raised by \emph{warning} constraints.
-Approx.
-1/2 of all constraints are \emph{informational} constraints regardless how their types are classified according to the expressivity of constraint languages.
+80\% of the violations, which are raised by either \emph{RDFS/OWL} or \emph{Constraint Language Based} constraints, are caused by constraints with the severity level \emph{informational} (see Table \ref{tab:evaluation-expressivity-severity}) and almost all (94\%) of the violations, which are caused by \emph{SPARQL Based} constraints, are raised by \emph{warning} constraints.
+Approximately 1/2 of all constraints are \emph{informational} constraints regardless how their types are classified according to the expressivity of constraint language types.
 
@@
 
-\begin{table}[H]
+\begin{table}[h]
 		\scriptsize
     \begin{center}
-		\caption{Language Expressivity and Severity Level}
+		\caption{Constraints and Violations by Language Type and Severity}
 		\label{tab:evaluation-expressivity-severity}
@@
 
-\begin{hyp}
-Whatever language is used to formulate constraints, 1/2 of all constraints are informational, 1/3 are error, and 1/5 are warning constraints. 
-%Thereby, it does not matter which language is used to formulate constraints.
-\end{hyp}
-
-The fact that regardless of the language 1/2 of all constraints are \emph{informational} 
+\par\bigskip
+{\centering\textbf{Finding 7}}
+\emph{Whatever language is used to formulate constraints, 1/2 of all constraints are informational, 1/3 are error, and 1/5 are warning constraints.}
+\par\bigskip
+
+The fact, that regardless of the language used to specify constraints, 1/2 of all constraints are \emph{informational} 
 %indicates that the purpose of constraints for users is mostly just to point to desirable but not necessary data improvements in terms of syntax and semantics of vocabularies. 
 indicates the importance that constraint languages support
-constraints on several levels. Constraints are by far not only to
+constraints on multiple levels. Constraints are by far not only used to
 prevent certain usages of a vocabulary, they are rather needed to
@@
 
-\begin{hyp}
-Regardless of the type of the used language, there are only a few violations raised by \emph{error} constraints which stands for good data quality in general.
-In contrast, constraints of low severity, expressed by RDFS/OWL or high-level constraint languages, are violated to a large extent (80\%), whereas more serious constraints, expressed by SPARQL, are violated to an even larger extend (94\%).
-%Violations caused by constraints expressed by RDFS/OWL or high-level constraint languages are of low severity (as the important constraints are satisfied), whereas the violation of constraints formulated by SPARQL is more serious.
-There is a significant demand for languages that support the expression of SPARQL Based constraints.
-\end{hyp}
+\par\bigskip
+{\centering\textbf{Finding 8}}
+\emph{Regardless of the type of the used language, there are only a few violations raised by error constraints which stands for good data quality in general.
+In contrast, constraints of low severity, expressible by RDFS/OWL or high-level constraint languages, are violated to a large extent (80\%), whereas more serious warning constraints, only expressible by SPARQL, are violated to an even larger extend (94\%).}
+\par\bigskip
 
@@
 
-94\% of the violations of SPARQL-based constraints are warnings. This
-means that data quality could be improved significantly, if these
-constraints are met. This is more likely when these constraints
-are expressible not only by SPARQL but also by high-level
-constraint languages enabling to formulate constraints more
-intuitively and concisely.
-
-%SPARQL seems to be used to formulate constraints whose violation is of higher severity than the violation of constraints expressed by either RDFS/OWL or high-level constraint languages.
-This is a surprising finding as the violation of \emph{RDFS/OWL Based} constraints should be of higher severity than \emph{informational} constraints since \emph{RDFS/OWL Based} constraints are expected to be basic constraints as they are in many cases part of vocabularies' formal specifications.
-
-%\textcolor{red}{
-%das letzte finding und die erläuterung finde ich konfus.
-violations gibts doch bei rdfs/owl hauptsächlich informational, weil die% wirklich wichtigen eingehalten werden.
-sparql based kann man ja bis jetzt nicht anders formulieren, insofern ist zu erwarten, dass da% auch warning constraints weniger eingehalten werden, wenn man welche auf warning level formuliert.
-Ist das nicht eh ein Artefakt %basierend auf letztlich 1 oder 2 constraints die ihr formuliert habt?
-%}
-
-%and (2)
-%the purpose of high-level constraint languages should be to enable to define constraints of higher severity than \emph{informational}.
+94\% of the violations caused by \emph{SPARQL Based} constraints are \emph{warnings}, which
+means that data quality could be significantly improved when solving these quite serious violations. We claim that this is more likely when these \emph{SPARQL Based} constraints 
+are not only expressible by plain SPARQL but also by high-level
+constraint languages enabling to formulate such constraints in a more
+intuitive and concise way.
 
@@
 
-We published by today 81 constraint types that are required by various stakeholders for data applications.
-In close collaboration with several domain experts for the social, behavioral, and economic (SBE) sciences, we formulated 115 constraints on three different vocabularies (DDI-RDF, QB, SKOS) and classified them according to their severity level and  whether their type is expressible by different types of constraint languages - RDFS/OWL, high-level constraint languages, and SPARQL.
-Using these constraints, we evaluated  the data quality of 15,694 data sets (4.26 billion triples) of research data for the SBE sciences obtained from 33 SPARQL endpoints.
+We captured 115 constraints on three vocabularies commonly used within the social, behavioral, and economic (SBE) sciences (DDI-RDF, QB, and SKOS), either from the vocabularies themselves or from several domain experts, and classified them based on by which of the three types of constraint languages (\emph{RDFS/OWL Based}, \emph{Constraint Language Based}, and \emph{SPARQL Based}) their constraint types can be expressed.
+
+In addition, we let the domain experts classify each constraint according to the severity of its violation.
+Although we provide default severity levels for each constraint, validation environments should enable users to adapt the severity levels of constraints according to their individual needs.
+We simplify the classification system of log messages in software development and differentiate between the three severity levels \emph{informational}, \emph{warning}, and \emph{error}.
+
+By validating against these constraints, we evaluated  the data quality of 15,694 data sets (4.26 billion triples) of SBE research data, obtained from 33 SPARQL endpoints.
+This way, we gain a better understanding about the role of certain constraint types for assessing the quality of RDF data and therefore the usability of identified constraint types for determining RDF data quality.
 
@@
 \emph{Data quality can be significantly improved when suitable constraint languages are developed enabling to define 
-constraints, which up to now can only be expressed by plain SPARQL, in an easy, concise, and intuitive way.
-Thereby, the more elaborate a vocabulary is, the more sophisticated and complex constraints are necessary which can up to now only be specified by SPARQL.}
+constraints - which up to now can only be expressed by plain SPARQL - in an easy, concise, and intuitive way.
+Thereby, the more elaborate a vocabulary is, the more sophisticated and complex constraints are necessary, which in most cases can only be specified in SPARQL.}
 \item
-\emph{As only 1/5 of all violations result from RDFS/OWL Based constraints, even though 1/3 of all constraints are RDFS/OWL Based, data quality is high for all vocabularies with regard to their formal specifications.}
+\emph{As only 1/5 of all violations result from constraints which are expressible in RDFS or OWL, even though 1/3 of all constraints are representable in RDFS/OWL, data quality is high for all vocabularies with regard to their formal specifications.}
 \item
-\emph{Although 40\% of all constraints are error constraints, the percentage of severe violations is very low, compared to about 2/3 of warning and 1/3 of informational violations.
-This implies that data quality is high with regard to the severity level of constraints and that proper constraint languages can significantly improve data quality beyond fundamental requirements.}
+\emph{Although 40\% of all constraints are associated with the severity level error, the percentage of severe violations is very low - compared to about 2/3 of warning and 1/3 of informational violations.
+This implies that data quality is high with regard to the severity of constraints and that proper constraint languages can significantly improve data quality beyond fundamental requirements.}
 \item
 \emph{Whatever language is used to formulate constraints, 1/2 of all constraints are informational, 1/3 are error, and 1/5 are warning constraints.
-Violations caused by constraints expressed by RDFS/OWL or high-level constraint languages are of low severity, whereas the violation of constraints formulated by SPARQL is more serious.
-There is a significant demand for languages that support the expression of SPARQL Based constraints causing 94\% of all violations.}
+This fact emphasizes the importance that constraint languages support multiple levels of severity.}
+\item
+\emph{Violations caused by constraints representable by RDFS/OWL or high-level constraint languages are of low severity, whereas the violation of constraints, only expressible in SPARQL, is more serious.
+This is the reason why there is a significant demand for high-level constraint languages that support the expression of constraints which up to now can only be formulated by plain SPARQL.}
 \end{enumerate}
@@
 
-%\ke{in die conclusion sollte noch rein, dass constraint languages per se funktionieren zur erhöhung der datenqualität und deswegen mit hochdruck an der weiterentwicklung gearbeitet werden muss.}
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation Results}
-%\label{fig_sim}
-%\end{figure}
-
-% Note that IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command, the
-% \label for the overall figure must come after \caption.
-% \hfil must be used as a separator to get equal spacing.
-% The subfigure.sty package works much the same way, except \subfigure is
-% used instead of \subfloat.
-%
-%\begin{figure*}[!t]
-%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
-%\label{fig_second_case}}}
-%\caption{Simulation results}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-
-% An example of a floating table. Note that, for IEEE style tables, the 
-% \caption command should come BEFORE the table. Table text will default to
-% \footnotesize as IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
-% Note that IEEE does not put floats in the very first column - or typically
-% anywhere on the first page for that matter. Also, in-text middle ("here")
-% positioning is not used. Most IEEE journals/conferences use top floats
-% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
-% command of the stfloats package.
-
-% conference papers do not normally have an appendix
-
-% use section* for acknowledgement
-%\section*{Acknowledgment}
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
+%\appendix
+
 \bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-\bibliography{../../literature/literature}{}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-%\begin{thebibliography}{1}
-%
-%\bibitem{IEEEhowto:kopka}
-%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  %0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-%
-%\end{thebibliography}
-
-% that's all folks
+\bibliography{literature}{}
+
 \end{document}

### 2016-03-13 paper/IJSC-2016/ws-ijsc.tex
IJSC-2016

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Trim Size: 9.75in x 6.5in
%% Text Area: 8in (include Runningheads) x 5in
%% ws-ijsc.tex     14-2-07
%% Tex file to use with ws-ijsc.cls written in Latex2E. 
%% The content, structure, format and layout of this style file is the 
%% property of World Scientific Publishing Co. Pte. Ltd. 
%% Copyright 1995, 2002 by World Scientific Publishing Co. 
%% All rights are reserved.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%

\documentclass{ws-ijsc}

\begin{document}

\markboth{Authors' Names}
{Instructions for Typing Manuscripts (Paper's Title)}

%%%%%%%%%%%%%%%%%%%%% Publisher's Area please ignore %%%%%%%%%%%%%%%
%
\catchline{}{}{}{}{}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{INSTRUCTIONS FOR TYPESETTING MANUSCRIPTS \\
USING COMPUTER SOFTWARE\footnote{For the title, try not to 
use more than 3 lines. Typeset the title in 10 pt bold and uppercase.}}

\author{FIRST AUTHOR\footnote{
Typeset names in 8 pt Roman, uppercase. Use the footnote to indicate the
present or permanent address of the author.}}

\address{University Department, University Name, Address\\
City, State ZIP/Zone,Country\,\footnote{State completely without 
abbreviations, the affiliation and mailing address, 
including country. Typeset in 8 pt italic.}\\
\email{author\_id@domain\_name\footnote{Typeset author e-mail 
address in single line.}}
\http{$<$webaddress$>$}
}

\author{SECOND AUTHOR}

\address{Group, Laboratory, Address\\
City, State ZIP/Zone, Country\\
author\_id@domain\_name
}

\maketitle

\begin{history}
\received{(Day Month Year)}
\revised{(Day Month Year)}
\accepted{(Day Month Year)}
%\comby{(xxxxxxxxxx)}
\end{history}

\begin{abstract}
The abstract should summarize the context, content and conclusions of
the paper in less than 200 words. It should not contain any reference
citations or displayed equations. Typeset the abstract in 8 pt Roman
with baselineskip of 10 pt, making an indentation of 1.5 pica on the
left and right margins.
\end{abstract}

\keywords{Keyword1; keyword2; keyword3.}

\section{General Appearance \label{ga}}

Contributions to {\it International Journal of 
Semantic Computing} will mostly be processed by
using the authors' source files. These should be submitted with
the manuscripts, and resubmitted in the final form if a paper requires
revision before being accepted for publication.

\section{The Main Text \label{sec1}}
Authors are encouraged to have their contribution checked for grammar. 
American spelling should be used. Abbreviations are
allowed but should be spelt out in full when first used. Integers ten
and below are to be spelt out. Italicize foreign language phrases
(e.g.~Latin, French). Example to cross link for section numbers and 
the main text, Sec.~\ref{sec1}.

The text is to be typeset in 10 pt Roman, single spaced with
baselineskip of 13~pt. Text area (including copyright block) is 
8 inches high and 5 inches wide for the first page.  Text area
(excluding running title) is 7.7 inches high and 5 inches wide for
subsequent pages.  Final pagination and insertion of running titles
will be done by the publisher.

\section{Major Headings}

Major headings should be typeset in boldface with the first letter of
important words capitalized.

\subsection{Sub-headings}

Sub-headings should be typeset in boldface italic and capitalize
the first letter of the first word only. Section number to be in
boldface Roman.

\subsubsection{Sub-subheadings}

Typeset sub-subheadings in medium face italic and capitalize the first
letter of the first word only. Section numbers to be in Roman.

\subsection{Numbering and spacing}

Sections, sub-sections and sub-subsections are numbered in Arabic.
Use double spacing before all section headings, and single spacing
after section headings. Flush left all paragraphs that follow after
section headings.

\subsection{Lists of items}

List may be presented with each item marked by bullets and numbers.

\subsection*{Bulleted items}

\begin{itemlist}
 \item item one,
 \item item two,
 \item item three.
\end{itemlist}

\subsection*{Numbered items}

\begin{arabiclist}
 \item item one,
 \item item two,
 \item item three.
\end{arabiclist}

The order of subdivisions of items in bullet and numbered lists
may be presented as follows:

\subsection*{Bulleted items}

\begin{itemize}
\item First item in the first level
\item Second item in the first level
\begin{itemize}
\item First item in the second level 
\item Second item in the second level
\begin{itemize}
\item First item in the third level 
\item Second item in the third level
\end{itemize}
\item Third item in the second level
\item Fourth item in the second level
\end{itemize}
\item Third item in the first level
\item Fourth item in the first level
\end{itemize}

\subsection*{Numbered items}

\begin{arabiclist}
\item First item in the first level
\item Second item in the first level
\begin{alphlist}[(a)]
\item First item in the second level 
\item Second item in the second level
\begin{romanlist}[iii.]
\item First item in the third level 
\item Second item in the third level
\item Third item in the third level
\end{romanlist}
\item Third item in the second level
\item Fourth item in the second level
\end{alphlist}
\item Third item in the first level
\item Fourth item in the first level
\end{arabiclist}

\section{Equations}

Displayed equations should be numbered consecutively,
with the number set flush right and enclosed in parentheses. The
equation numbers should be consecutive within the contribution.
\begin{equation}
\mu(n, t) = \frac{\sum^\infty_{i=1} 1(d_i < t, N(d_i) = n)}{
\int^t_{\sigma=0} 1(N(\sigma) = n)d\sigma}\, .
\label{eq:jaa}
\end{equation}

Equations should be referred to in abbreviated form,
e.g.~``Eq.~(\ref{eq:jaa})'' or ``(2)''. In multiple-line
equations, the number should be given on the last line.

Displayed equations are to be centered on the page width.
Standard English letters like x are to appear as $x$
(italicized) in the text if they are used as mathematical
symbols. Punctuation marks are used at the end of equations as
if they appeared directly in the text.

\section{Theorem Environments}

\begin{theorem}
Theorems$,$ lemmas$,$ definitions$,$ etc. are set on a separate 
paragraph$,$ with extra 1 line space above and below. They are to 
be numbered consecutively within the contribution.
\end{theorem}

\begin{lemma}
Theorems$,$ lemmas$,$ definitions$,$ etc. are set on a separate 
paragraph$,$ with extra 1 line space above and below. They are to be 
numbered consecutively within the contribution.
\end{lemma}

\begin{proof}
The word `Proof' should be type in boldface. Proofs
should end with\break
a box. 
\end{proof}

\section{Illustrations and Photographs}

\begin{figure}[b]
\centerline{\psfig{file=ijscf1.eps,width=5cm}}
\vspace*{8pt}
\caption{A schematic illustration of dissociative recombination. The
direct mechanism, 4m$^2_\pi$ is initiated when the
molecular ion S$_{\rm L}$ captures an electron with kinetic energy.}
\end{figure}

Figures are to be inserted in the text nearest their first
reference.  Figure placements can be either top or bottom.
Original india ink drawings of glossy prints are
preferred. Please send one set of originals with copies. If the
author requires the publisher to reduce the figures, ensure that
the figures (including letterings and numbers) are large enough
to be clearly seen after reduction. If photographs are to be
used, only black and white ones are acceptable.

Figures are to be sequentially numbered in Arabic numerals. The
caption must be placed below the figure. Typeset in 8 pt Roman with
baselineskip of 10~pt. Long captions are to be justified by the
``page-width''.  Use double spacing between a caption and the text
that follows immediately.

Previously published material must be accompanied by written
permission from the author and publisher.

\section{Tables}

Tables should be inserted in the text as close to the point of
reference as possible. Some space should be left above and below
the table.

Tables should be numbered sequentially in the text in Arabic
numerals. Captions are to be centralized above the tables.
Typeset tables and captions in 8 pt Roman with
baselineskip of 10 pt. Long captions are to be justified by 
the ``table-width''.

\begin{table}[h]
\tbl{Comparison of acoustic for frequencies for piston-cylinder problem.}
{\begin{tabular}{@{}cccc@{}} \toprule
Piston mass & Analytical frequency & TRIA6-$S_1$ model &
\% Error \\
& (Rad/s) & (Rad/s) \\ \colrule
1.0\hphantom{00} & \hphantom{0}281.0 & \hphantom{0}280.81 & 0.07 \\
0.1\hphantom{00} & \hphantom{0}876.0 & \hphantom{0}875.74 & 0.03 \\
0.01\hphantom{0} & 2441.0 & 2441.0\hphantom{0} & 0.0\hphantom{0} \\
0.001 & 4130.0 & 4129.3\hphantom{0} & 0.16\\ \botrule
\end{tabular}}
\begin{tabnote}
Table notes.
\end{tabnote}
\begin{tabfootnote}
\tabmark{a} Table footnote A.\\
\tabmark{b} Table footnote B.
\end{tabfootnote}
\end{table}

If tables need to extend over to a second page, the continuation
of the table should be preceded by a caption, 
e.g.~``{\it Table 2.} $(${\it Continued}$)$''. Notes to tables are
placed below the final row of the table and should be flushleft.
Footnotes in tables shouldbe indicated by superscript lowercase letters
and placed beneath the table.

\section{Running Heads}

Please provide a shortened runninghead (not more than eight words) for
the title of your paper. This will appear on the top right-hand side
of your paper.

\section{Footnotes}

Footnotes should be numbered sequentially in superscript
lowercase roman letters.\footnote{Footnotes should be
typeset in 8 pt Roman at the bottom of the page.}

\appendix

\section{Appendices}

Appendices should be used only when absolutely necessary. They
should come before the References. If there is more than one
appendix, number them alphabetically. Number displayed equations
occurring in the Appendix in this way, e.g.~(\ref{appeqn}), (A.2),
etc.
\begin{equation}
\mu(n, t) = \frac{\sum^\infty_{i=1} 1(d_i < t, N(d_i) 
= n)}{\int^t_{\sigma=0} 1(N(\sigma) = n)d\sigma}\,.
\label{appeqn}
\end{equation}

\section*{References}
References are to be listed in the order cited in the text in Arabic 
numerals.  They can be typed after punctuation marks, 
e.g.~``$\ldots$ in the statement \cite{birk}.'' or used directly,
e.g.~``e.g.~``see [\refcite{bergm}] for examples.'' Please list 
using the style shown in the following examples.  For journal names, 
use the standard abbreviations.  Typeset references in 9 pt Roman 
with baselineskip of 11pt.

\section*{Acknowledgements}

This section should come before the References. Funding
information may also be included here.

\begin{thebibliography}{00}

\bibitem{alth} K.-D. Althoff, A. Birk, S. Hartkopf, and W. M\"{u}ller,
Managing software engineering experience for comprehensive reuse, in
{\it Proc.  11th Int. Conf. on Software Engineering}, Kaiserslautern,
Germany, 1999.

\bibitem{birk} K.-D. Althoff, A. Birk, and C. Tautz, The experience 
factory approach: Realizing learning from experience in software 
development organizations, in {\it Proc. 10th German Workshop 
on Machine Learning $($FGML'97$)$}, University of Karlsruhe, 1997, 
pp.~6--8.

\bibitem{basili} V. R. Basili, G. Caldiera, and H. D. Rombach, The
experience factory, in \textit{Encyclopedia of Software Engineering},
ed. J. J. Marciniak,  (John Wiley \& Sons, 1994), pp. 469--476.

\bibitem{romb} V. R. Basili and H. D. Rombach, The TAME project: Towards
improvement-oriented software environments, \textit{IEEE Trans.  on
Software Engineering} {\bf SE-14}(6) (1988) 758--773.

\bibitem{becker} U. Becker-Kornstaedt and R. Webby, A Comprehensive Schema 
Integrating Software Process Modelling and Software Measurement, 
Fraunhofer IESE-Report No. 047.99 (Ed.: Fraunhofer IESE, 1999), 
http://www.iese.fhg.de/Publications/Iese{\_}reports/.

\bibitem{bergm} R. Bergmann and U. Eisenecker, Case-based reasoning for
supporting reuse of object-oriented software: A case study, in {\it
Proc.  Expert Systems} {\bf 95} (1996) 152--169.

\bibitem{ncard} D. N. Card and R. L. Glass, \textit{Measuring Software
Design Quality} (Prentice Hall, Englewood Cliffs, NJ, 1990).

\bibitem{derid} D. Deridder, A concept-oriented approach to support software 
maintenance and reuse activities, in {\it Proc. Workshop on 
Knowledge-Based Object-Oriented Software Engineering at 16th European 
Conference on Object-Oriented Programming $($ECOOP 2002$)$}, M\'{a}laga, 
Spain, 2002.

\bibitem{estay} C. Estay and J. Pastor, Improving action research in
information systems with project management, in {\it Proc. Americas
Conference on Information Systems}, Long Beach, CA, USA, 2000,
pp.~1558--1561.

\bibitem{falbo} R. A. Falbo, C. S. Menezes, and A. R. Rocha, Using
ontologies to improve knowledge integration in software engineering
environments, in {\it Proc. 4th Conference on Information Systems
Analysis and Synthesis}, Orlando, Florida, USA, 1998.
\end{thebibliography}

\end{document}
